### 2017-03-22 manuscripts/PNAS/chazthm_pnas.tex
first commit

\documentclass[9pt,twocolumn]{pnas-new}
% Use the lineno option to display guide line numbers if required.
% Note that the use of elements such as single-column equations
% may affect the guide line number alignment.

%%% CHAZ TODO %%%
% replace dictionary learning with 'sparse linear coding'

%%% CHRIS TODO %%
% steamroll

% IMPORTED PACKAGES
\usepackage{amsmath, amssymb, amsthm} 
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{conjecture}{Conjecture}
\newtheorem{problem}{Problem}
\newtheorem{question}{Question}
\newtheorem{proposition}{Proposition}
\newtheorem{definition}{Definition}
\newtheorem{corollary}{Corollary}
\newtheorem{remark}{Remark}
\newtheorem{example}{Example}

%\usepackage[pdftex]{graphicx}

% *** ALIGNMENT PACKAGES ***
\usepackage{array}
%\usepackage{cite}

\templatetype{pnasresearcharticle} % Choose template 
% {pnasresearcharticle} = Template for a two-column research article
% {pnasmathematics} = Template for a one-column mathematics article
% {pnasinvited} = Template for a PNAS invited submission

\title{On the uniqueness and stability of dictionaries for sparse representation of noisy signals}

% Use letters for affiliations, numbers to show equal authorship (if applicable) and to indicate the corresponding author
\author[a,1]{Charles J. Garfinkle}
\author[a,1]{Christopher J. Hillar}

\affil[a]{Redwood Center for Theoretical Neuroscience, Berkeley, CA, USA}

% Please give the surname of the lead author for the running footer
\leadauthor{Garfinkle}

% Please add here a significance statement to explain the relevance of your work
%\significancestatement{Authors must submit a 120-word maximum statement about the significance of their research paper written at a level understandable to an undergraduate educated scientist outside their field of speciality. The primary goal of the Significance Statement is to explain the relevance of the work in broad context to a broad readership. The Significance Statement appears in the paper itself and is required for all research papers.}

\significancestatement{Many naturally occurring signals (e.g. patches of visual scenery, speech audio, electrocardiograms) have been usefully characterized as parsimonious combinations of building blocks drawn from a large `dictionary' of elementary waveforms. Absent analytic descriptions of these signal classes, it usually falls to machine learning algorithms to infer a suitable dictionary given a large set of examples from the class. We give conditions guaranteeing when the optimal dictionary of a given size is uniquely and consistently determined by data, regardless of the algorithm used to compute it. Our results provide theoretical grounding for the application of dictionary learning algorithms to the problem of recovering sparse signals from unknown noisy compressive measurements.}

% Please include corresponding author, author contribution and author declaration information
\authordeclaration{The authors declare no conflict of interest.}
%\equalauthors{\textsuperscript{1}C.G. proved Theorem 1 and C.H. proved Theorem 2.}
\correspondingauthor{\textsuperscript{1}To whom correspondence should be addressed. E-mail: cjg@berkeley.edu, chillar@msri.org}

% Keywords are not mandatory, but authors are strongly encouraged to provide them. If provided, please include two to five keywords, separated by the pipe symbol, e.g:
\keywords{Sparse linear coding, dictionary learning, compressed sensing}

\begin{abstract}
Dictionary learning methods for sparse linear coding have exposed underlying structure in many kinds of natural signals.
However, universal theorems guaranteeing the statistical consistency of inference in this model are lacking.
Here, we prove that for almost all diverse enough datasets generated from the sparse coding model, latent dictionaries and sparse codes are uniquely determined up to an error commensurate with measurement noise.
Applications are given to data analysis, neuroscience, and engineering.
\end{abstract}

\dates{This manuscript was compiled on \today}
\doi{\url{www.pnas.org/cgi/doi/10.1073/pnas.XXXXXXXXXX}}

\begin{document}

% Optional adjustment to line up main text (after abstract) of first page with line numbers, when using both lineno and twocolumn options.
% You should only change this length when you've finalised the article contents.
\verticaladjustment{-2pt}

\maketitle
\thispagestyle{firststyle}
\ifthenelse{\boolean{shortarticle}}{\ifthenelse{\boolean{singlecolumn}}{\abscontentformatted}{\abscontent}}{}

% If your first paragraph (i.e. with the \dropcap) contains a list environment (quote, quotation, theorem, definition, enumerate, itemize...), the line after the list may have some extra indentation. If this is the case, add \parshape=0 to the end of the list environment.
\dropcap{D}ictionary learning methods for sparse coding have been under active development ever since their application to natural images brought about an exciting discovery in computational neuroscience: that simple-cell response properties emerge from efficient coding principles \cite{Olshausen96, hurri1996image, bell1997independent, van1998independent}. Much of the subsequent work in dictionary learning has come out of the signal processing and machine learning communities, which have found sparse representations to be a powerful tool for the manipulation of signals lacking much known analytic structure (see \cite{Zhang15} for a comprehensive review). This motivates the data-driven approach to inferring optimal dictionaries for a wide variety of signal classes for which, traditionally, representations have been constructed using methods of harmonic analysis (e.g., the Fourier basis, wavelets, curvelets, etc.). A popular formulation of the idea is to find a set of $m$ `elementary' waveforms, at most $k$ of which need be linearly combined to represent each $n$-dimensional signal in a dataset of size $N$, typically where $k < m \ll N$. 
%\dropcap{D}ictionary learning methods for sparse coding have been under active development ever since their application to natural images brought about an exciting discovery in computational neuroscience: that simple-cell response properties emerge from efficient coding principles \cite{Olshausen96, hurri1996image, bell1997independent, van1998independent}. Much of the subsequent work in dictionary learning has come out of the signal processing and machine learning communities, whose interest in sparse representations as a practical tool motivates the data-driven approach to inferring optimal dictionaries (see \cite{Zhang15} for a comprehensive review). A popular formulation of the idea is to find a set of $m$ `elementary' signals, at most $k$ of which need be linearly combined to represent each $n$-dimensional signal in a dataset of size $N$, typically where $k < m \ll N$.

Blind source identification first started \cite{sato1975method}.

We address here a question of fundamental concern to this enterprise: \emph{When are dictionaries and the sparse representations they provide uniquely determined by data?} An affirmative answer speaks also to the important question of whether or not a dictionary adapted to a finite number of samples from a signal class will generalize in its ability to represent all signals in the class; see, for instance, the method of forgery detection by analysis of local painting style proposed in \cite{hughes2010, Olshausen10}. Fortunately, algorithms with proven recovery of generating dictionaries under certain conditions have recently been proposed (see \cite[Sec.~I-E]{Sun16} for a summary of the state-of-the-art). It has remained unknown, however, when the dictionary learning problem is well-posed (as per Hadamard \cite{Hadamard1902}) in general -- that is, independent of all methodological idiosyncracies.
%[**TODO** make sure the claim here is right...or would it be punchier to talk about the fact that everyone always gets Gabors on natural images?]
%- algos with proven recovery of generating dictionary
%- analyses of when target dictionary is local optimizer of natural recovery criteria
%- efficient algos that globally solve DR; detailed models differ but all assume each col has bounded sparsity and nonzero coefs have sub-Gaussian magnitudes

The main finding of this work is that for any $k < m$, every dictionary satisfying the spark condition \eqref{SparkCondition} from compressed sensing is identifiable from as few as $N = m + m(k-1){m \choose k}$ $k$-sparse linear combinations of its elements up to an error linear in the noise (Thm.~\ref{DeterministicUniquenessTheorem}). In fact, provided $(n, m, k)$ satisfy the nearly-optimal compressed sensing inequality \eqref{CScondition}, in almost all cases the dictionary learning problem is well-posed given enough data (Cor.~\ref{ProbabilisticCor}). Interestingly, these guarantees hold even without constraining the recovered matrix to satisfy the spark condition. Imposing this constraint does, however, allow us to state a modification of our main result that applies to the case where only an upper bound on the number of dictionary elements is known (Thm.~\ref{DeterministicUniquenessTheorem2}). We hope the explicit, algorithm-independent criteria we provide here may serve as a useful tool in future analyses of dictionary learning procedures.

We state the problem considered here more precisely as follows. Fix a dictionary represented as the columns $\mathbf{A}_j$ ($j = 1,\ldots,m$) of a matrix $\mathbf{A} \in \mathbb R^{n \times m}$ and suppose a dataset $Z$ consists of measurements:
\begin{align}\label{LinearModel}
\mathbf{z}_i = \mathbf{A}\mathbf{x}_i + \mathbf{n}_i,\indent \text{$i=1,\ldots,N$},
\end{align}
for $k$-\emph{sparse} $\mathbf{x}_i \in \mathbb{R}^m$ having at most $k$ nonzero entries and \emph{noise} $\mathbf{n}_i \in \mathbb{R}^n$, with bounded norm $\| \mathbf{n}_i \|_2 \leq  \eta$ representing our combined worst-case uncertainty in  measuring $\mathbf{A}\mathbf{x}_i$.

\begin{problem}[Sparse linear coding]\label{InverseProblem}
Find a matrix $\mathbf{B}$ and $k$-sparse $\mathbf{\hat x}_1, \ldots, \mathbf{\hat x}_N \in \mathbb{R}^m$ such that $\|\mathbf{z}_i - \mathbf{B}\mathbf{\hat x}_i\|_2 \leq \eta$ for all $i$.
\end{problem}

Note that by formulating the problem in this way we have introduced the following ambiguity. Any particular solution represents a whole class of equivalent dictionaries $BPD$ and codes $D^{-1}P^{\top}\mathbf{\hat x}_i$, where $P$ is any permutation matrix and $D$ any invertible diagonal matrix. We therefore consider only whether solutions to Problem~\ref{InverseProblem} are unique up to this equivalence \cite{Li15}. Alternatively, one may seek a unique solution (in the usual sense) in the quotient space induced by the action of the transformation group of matrices $PD$.

Previous work \cite{li2004analysis, Georgiev05, Aharon06, Hillar15} on the noiseless case $\eta = 0$ has shown that the solution (when it exists) is indeed unique in the sense described above provided the $\mathbf{x}_i$ are sufficiently diverse and the matrix $\mathbf{A}$ satisfies the \textit{spark condition}:
\begin{align}\label{SparkCondition}
\mathbf{A}\mathbf{x}_1 = \mathbf{A}\mathbf{x}_2 \implies \mathbf{x}_1 = \mathbf{x}_2,\indent \text{for all $k$-sparse } \mathbf{x}_1, \mathbf{x}_2.
\end{align}
%
which would be, in any case, a necessary condition for uniqueness if we knew only that the $\mathbf{x}_i$ are $k$-sparse. We introduce the following terminology to handle $\eta > 0$. 
\begin{definition}
Fix $Y = \{ \mathbf{y}_1, \ldots, \mathbf{y}_N\} \subset \mathbb{R}^n$. We say $Y$ has a \emph{$k$-sparse representation in $m$ dimensions} if there exists a matrix $\mathbf{A}$ and $k$-sparse $\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$ such that $\mathbf{y}_i = \mathbf{A}\mathbf{x}_i$ for all $i$. %Equivalently, $\mathbf{Y} = \mathbf{A}\mathbf{X}$ for $\mathbf{Y}$ and $\mathbf{X}$ having the $\mathbf{y}_i$ and $\mathbf{x}_i$ as their columns, respectively. 
This representation is \emph{stable} if for every $\delta_1, \delta_2 \geq 0$, there exists $\varepsilon = \varepsilon(\delta_1, \delta_2) \geq 0$ (with $\varepsilon > 0$ when  $\delta_1, \delta_2 > 0$) such that if a matrix $\mathbf{B}$ and $k$-sparse $\mathbf{\hat x}_1, \ldots, \mathbf{\hat x}_N \in \mathbb{R}^m$ satisfy
\begin{align*}
\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\hat x}_i\|_2 \leq \varepsilon \ \ \text{for all $i$}
\end{align*}
%
then there is some permutation matrix $\mathbf{P}$ and invertible diagonal matrix $\mathbf{D}$ such that for all $i, j$:
\begin{align}\label{def1}
\|\mathbf{A}_j - (\mathbf{BPD})_j\|_2 \leq \delta_1 \ \ \text{and} \ \ \|\mathbf{x}_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\hat x}_i\|_1 \leq \delta_2.
\end{align}
\end{definition}
% Kato mentions a distance between n-tuples that minimizes the maximum difference over all possible orderings of one of the n-tuples.
% Make just 'sparse representation in m-dimensions? (i.e. with k unspecified?)

We ask here: \emph{When does $Y$ have a stable $k$-sparse representation in $m$ dimensions?} To see how an answer to this question informs the interpretation of solutions to Problem \ref{InverseProblem}, suppose that \mbox{$Y = \{\mathbf{A} \mathbf{x}_1, \ldots, \mathbf{A}\mathbf{x}_N\}$} has a stable $k$-sparse representation in $m$ dimensions and fix $\delta_1, \delta_2$ to be the desired accuracy in recovery \eqref{def1}. Consider now any dataset $Z$ generated as in \eqref{LinearModel} that has $\eta \leq \frac{1}{2} \varepsilon(\delta_1, \delta_2)$. Then, any dictionary $\mathbf{B}$ and $k$-sparse $\mathbf{\hat x}_1, \ldots, \mathbf{\hat x}_N$ solving Problem \ref{InverseProblem} are necessarily close to the original matrix $\mathbf{A}$ and codes $\mathbf{x}_i$ (i.e., satisfy \eqref{def1}). Our results, outlined in Sec.~\ref{Results}, include an explicit form for $\varepsilon(\delta_1, \delta_2)$ in Thm.~\ref{DeterministicUniquenessTheorem}.

In the next section, we give precise statements of our main results, which include an explicit form for $\varepsilon(\delta_1, \delta_2)$. We then prove our main theorem (Thm.~\ref{DeterministicUniquenessTheorem}) in Sec.~\ref{DUT} while stating some additional definitions and lemmas required for the proof, including our main tool from combinatorial matrix analysis (Lem.~\ref{MainLemma}). Our proof is a refinement of the arguments in \cite{Hillar15} to handle noise and to reduce the sufficient number of samples for all $k < m$ from $N=k{m \choose k}^2$ to $N = m + m(k-1){m \choose k}$. All other proofs are relegated to the Supplemental. Finally, several applications are considered in our discussion, Sec.~\ref{Discussion}.

\section{Results}

Before stating our main results, we explain how the spark condition \eqref{SparkCondition} relates to the \emph{lower bound} \cite{Grcar10} of $\mathbf{A}$, written $L(\mathbf{A})$, which is the largest number $\alpha$ such that \mbox{$\|\mathbf{A}\mathbf{x}\|_2 \geq \alpha\|\mathbf{x}\|_2$} for all $\mathbf{x} \in \mathbb{R}^m$. By compactness, every injective linear map has a nonzero lower bound; hence, if $\mathbf{A}$ satisfies \eqref{SparkCondition}, then every submatrix formed from $2k$ of its columns or less has a nonzero lower bound. We therefore define the following domain-restricted lower bound of $\mathbf{A}$:
\begin{align*}
L_k(\mathbf{A}) := \frac{1}{\sqrt{k}}\max \{ \alpha : \|\mathbf{A}\mathbf{x}\|_2 \geq \alpha\|\mathbf{x}\|_2 \text{ for all $k$-sparse } \mathbf{x}\}.
\end{align*} 
Clearly, $L_k(\mathbf{A}) \geq L_{k'}(\mathbf{A})$ whenever $k < k'$, and for any $\mathbf{A}$ satisfying \eqref{SparkCondition}, we have $L_{k'}(\mathbf{A}) > 0$ for all $k' \leq 2k$. Note that subtracting $L_k(\mathbf{A})$ from one yields what is known in the compressed sensing literature as the (asymmetric) lower restricted isometry constant \cite{Blanchard2011, Foucart2009}.

We let $[m]$ denote the set $\{1, \ldots, m\}$ and $2^{[m]}$ ts power set, and we write ${[m] \choose k}$ to denote the set of subsets of $[m]$ of size $k$. Let $\text{Span}\{\mathbf{v}_1, \ldots, \mathbf{v}_\ell\}$ be the $\mathbb{R}$-linear span of vectors $\mathbf{v}_1, \ldots, \mathbf{v}_\ell$. A vector $\mathbf{x}$ is then said to be \emph{supported} on $S \subseteq [m]$ when $\mathbf{x} \in \text{Span} \{\mathbf{e}_j\}_{j\in S}$, where $\mathbf{e}_j$ are the standard $m$-dimensional basis vectors We denote by $\mathbf{M}_j$ the $j$th column of a matrix $\mathbf{M}$ and similarly by $\mathbf{M}_S$ the sub-matrix formed by the columns of $\mathbf{M}$ indexed by $S$. We interpret $\text{Span}\{\mathbf{M}_\emptyset\} = \{\textbf{0}\}$, where $\emptyset$ is the empty set. We say a set system $E \subseteq 2^{[m]}$ is of rank $k$ when $|S| \leq k$ for every $S \in E$ (and $k$-uniform when equality holds). We say $E$ is \emph{regular} when every element of $[m]$ is contained in exactly $\ell$ elements of $E$ for some $\ell > 0$ (for given $\ell$, we say $E$ is $\ell$-regular).

\begin{definition}
Given a set system $E \subseteq 2^{[m]}$, the \emph{star} $F(i)$ centered at $i$ is the set of $S \in E$ containing $i$. We say $E$ satisfies the \emph{singleton intersection property} when $\cap_{S \in F(i)} S = \{i\}$ for all $i \in [m]$. 
\end{definition}

\begin{proposition}
For every $k < m$, there is a regular $k$-uniform set system that satisfies the singleton intersection property.
\end{proposition}
Consider, for instance, the set of consecutive intervals of length $k$ in some cyclic order on $[m]$.

The following result gives an elaborated answer to our question from the introduction. Recall that a set of $k$-sparse vectors is in \emph{general linear position} when any $k$ of them are linearly independent.

\begin{theorem}\label{DeterministicUniquenessTheorem}
Fix integers $n$ and $k < m$. Suppose $\mathbf{A}~\in~\mathbb{R}^{n \times m}$ satisfies \eqref{SparkCondition} and that \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} include at least \mbox{$(k-1){m \choose k}+1$} vectors in general linear position supported on each set in some regular $E \subseteq {[m] \choose k}$ satisfying the singleton intersection property. Then there exists a constant $C_1 > 0$ for which the following holds for all $\varepsilon < L_2(\mathbf{A}) / C_1$. %\frac{L_2(\mathbf{A})}{\sqrt{2}}C_1^{-1}$:

Every matrix $\mathbf{B} \in \mathbb{R}^{n \times m}$ for which for some $k$-sparse $\mathbf{\hat x}_1, \ldots, \mathbf{\hat x}_N \in \mathbb{R}^{m}$ we have \mbox{$\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\hat x}_i\|_2 \leq \varepsilon$} for all $i$ necessarily satisfies:
\begin{align}\label{Cstable}
\|\mathbf{A}_j-(\mathbf{B}\mathbf{PD})_j\|_2 \leq C_1 \varepsilon \ \ \text{for all $j \in [m]$}
\end{align}
%
for some permutation matrix $\mathbf{P}$ and invertible diagonal matrix $\mathbf{D}$.\footnote{We note that the condition $\varepsilon < L_2(\mathbf{A})$ above is necessary. When \mbox{$\mathbf{A}$ = $I$} and $\mathbf{x}_i = \mathbf{e}_i$, it turns out that $C_1 = 1$ and there is a $\mathbf{B}$ and $1$-sparse $\mathbf{\hat x}_i$ with $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\hat x}_i\|_2 \leq \varepsilon$ violating \eqref{Cstable}.}
Furthermore if $\varepsilon < L_{2k}(\mathbf{A}) / C_1$ then $\mathbf{B}$ also satisfies \eqref{SparkCondition} with $L_{2k}(\mathbf{B}\mathbf{PD}) \geq L_{2k}(\mathbf{A}) - C_1 \varepsilon$ and we in fact have:
\begin{align}\label{b-PDa}
\|\mathbf{x}_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\hat x}_i\|_1 &\leq \frac{\varepsilon}{\sqrt{2k}} \left( \frac{ 1+C_1 \|\mathbf{x}_i\|_1 }{ L_{2k}(\mathbf{A}) -  C_1\varepsilon } \right).
 \ \ \text{for all $i \in [N]$}.
\end{align}
\end{theorem}

For clarity of exposition, we delay explicitly defining the (effective) constant $C_1 = C_1(\mathbf{A}, \{\mathbf{x}_i\}_{i=1}^N, E)$ until Section \ref{DUT} (\eqref{Cdef}), since it requires additional definitions not critical to the statement of our results.

An important consequence of Thm.~\ref{DeterministicUniquenessTheorem} is that \eqref{def1} is guaranteed provided $\varepsilon$ does not exceed:
\begin{align}\label{epsdel}
\varepsilon(\delta_1, \delta_2) := \min \left\{ \frac{\delta_1}{ C_1 }, \frac{ \delta_2 L_{2k}(\mathbf{A})}{ 1 + C_1 \left( \max_{i \in [N]} \|\mathbf{x}_i\|_1  + \delta_2 \right) } \right\}.
\end{align}

Note also that Thm~\ref{DeterminsiticUniquenessTheorem} gives conditions for when a single solution to Problem~\ref{InverseProblem} in fact represents \emph{all} possible solutions, related by transformations of the form $PD$.

\begin{corollary}\label{DeterministicUniquenessCorollary}
Given $n, m$, $k < m$ and a regular set system $E \subseteq 2^{[m]}$ of rank $k$ satisfying the singleton intersection property, there are $N =  |E| \left[ (k-1){m \choose k}+1 \right]$ vectors \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} such that every matrix $\mathbf{A} \in \mathbb{R}^{n \times m}$ satisfying \eqref{SparkCondition} generates a set $Y = \{\mathbf{A}\mathbf{x}_1, \ldots, \mathbf{A}\mathbf{x}_N\}$ with a stable $k$-sparse representation in $m$ dimensions.
\end{corollary}

\begin{proposition}
If $E$ is an $\ell$-regular set system of rank $k$ satisfying the singleton intersection property then $|E| \geq \ell m/k$. 
\end{proposition}
This is easy to see by noting that $|E|k \geq \sum_{S \in E}|S| = \sum_{i \in [m]} \deg(i) = \ell m$. In certain cases there exist simple constructions achieving this minimum; for example, when $k = \sqrt{m}$ one can take $E$ to be the rows and columns formed by arranging the elements of $[m]$ in a square grid.

It is straightforward to provide a probabilistic extension of Thm.~\ref{DeterministicUniquenessTheorem} using the following fact in random matrix theory.  The matrix $\mathbf{A} \in \mathbb{R}^{n \times m}$ satisfies \eqref{SparkCondition} with probability one (or with ``high probability" for discrete variables) 
provided:
\begin{align}\label{CScondition}
n \geq \gamma k\log\left(\frac{m}{k}\right),
\end{align}
%
where $\gamma$ is a positive constant dependent on the particular distribution from which the entries of $\mathbf{A}$ are sampled i.i.d. (many ensembles suffice, e.g. \cite[Sec.~4]{Baraniuk08}).

In fact, the spark condition can be made explicit.  Let $\mathbf{A}$  be the $n \times m$ matrix of $nm$ indeterminates $A_{ij}$. When real numbers are substituted for all the $A_{ij}$, the resulting matrix satisfies \eqref{SparkCondition} if and only if the following polynomial is nonzero:
\begin{align*}
f(\mathbf{A}) = \prod_{S \in {[m] \choose k}} \sum_{S' \in {[n] \choose k}} (\det \mathbf{A}_{S',S})^2,
\end{align*}
%
where for any $S' \in {[n] \choose k}$ and $S \in {[m] \choose k}$, the symbol $\mathbf{A}_{S',S}$ denotes the submatrix of entries $A_{ij}$ with $(i,j) \in S' \times S$.

Since $f$ is a real analytic function, it is enough to show that at least \emph{one} substitution of real numbers satisfies $f(\mathbf{A}) \neq 0$ to conclude that its zeroes form a set with measure zero. Hence, \emph{every} $n \times m$ matrix $\mathbf{A}$ outside a set of measure zero satisfies \eqref{SparkCondition} provided \eqref{CScondition} holds for a value of $\gamma$ for \emph{some} distribution. We remark that the precise relationship between $m$, $n$, and $k$ guaranteeing that $f$ is not identically zero is still an open problem in real algebraic geometry [**TODO** cite recent work?]. In any case, we set $\gamma_0$ to be the smallest known such $\gamma$.

It so happens that a similar statement applies to sets of vectors with a stable sparse representation. As in \cite[Sec.~IV]{Hillar15}, consider the ``symbolic" dataset $Y = \{\mathbf{A}\mathbf{x}_1,\ldots,\mathbf{A} \mathbf{x}_N\}$ generated by indeterminate $\mathbf{A}$ and $k$-sparse $\mathbf{x}_1, \ldots, \mathbf{x}_N$.

\begin{theorem}\label{robustPolythm} %label is fucking up formatting..???
Fix $n, m$, and $k < m$. There is a polynomial in the entries of $\mathbf{A}$ and the $\mathbf{x}_i$ with the following property:  if the polynomial evaluates to a nonzero number and at least \mbox{$(k-1){m \choose k}+1$} of the resulting vectors $\mathbf{x}_i$ are supported on each $S \in E$ for some regular $k$-uniform $E \subseteq 2^{[m]}$ satisfying the singleton intersection property, then $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$ (Def.~\ref{Uniqueness}). In particular, either no substitutions impart to $Y$ this property or all but a Borel set of measure zero do. 
\end{theorem}

% this is cool, but let's just save it for later...i can ask around.  -cjh
%An interesting open question in real algebraic geometry is which collections of $(m,n,k)$ determine this last ``or".

\begin{corollary}\label{ProbabilisticCor}
Fix $n, m$, and $k$ satisfying \eqref{CScondition} for $\gamma = \gamma_0$, and let the entries of the matrix $\mathbf{A} \in \mathbb{R}^{n \times m}$ and $k$-sparse vectors $\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$ be drawn independently from probability measures absolutely continuous with respect to the standard Borel measure $\mu$. If at least $(k-1){m \choose k} + 1$ of the vectors $\mathbf{x}_i$ are supported on each $S \in E$ for some regular $k$-uniform $E \subseteq 2^{[m]}$ satisfying the singleton intersection property, then $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$ with probability one.
\end{corollary}

[ ** TODO ** elaborate a little on these? ]

Next, we address the case when only an upper bound $m'$ on the latent dimension $m$ is known (assuming that $\mathbf{B}$ satisfies \eqref{SparkCondition}).

\begin{theorem}\label{DeterministicUniquenessTheorem2}
Fix integers $n$ and $k < m \leq m'$ and matrices $\mathbf{A}~\in~\mathbb{R}^{n \times m}$ and $\mathbf{B} \in \mathbb{R}^{n \times m'}$ both satisfying \eqref{SparkCondition}. Suppose \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} include at least \mbox{$(k-1){m' \choose k}+1$} vectors in general linear position supported on each set in some $k$-uniform $E \subseteq 2^{[m]}$ satisfying the singleton intersection property. Then there exists a constant $C_3 > 0$ for which the following holds.

If for some $k$-sparse $\mathbf{\hat x}_1, \ldots, \mathbf{\hat x}_N \in \mathbb{R}^{m'}$ and $\varepsilon < L_2(\mathbf{A}) / C_3$ we have \mbox{$\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\hat x}_i\|_2 \leq \varepsilon$} for all $i$, then:
\begin{align}\label{Cstablem'}
\|\mathbf{A}_j-(\mathbf{B}_J\mathbf{PD})_j\|_2 \leq C_3\varepsilon \ \ \text{for all $j \in [m]$}
\end{align}
%
for some $J \in {[m'] \choose m}$, permutation matrix $\mathbf{P}$, and invertible diagonal matrix $\mathbf{D}$.
\end{theorem}

In other words, the columns of $B$ contain (up to noise, after appropriate scaling) the columns of the original dictionary $\mathbf{A}$. Similarly, one can show by the same arguments at the beginning of Sec.~\ref{DUT} that the $\mathbf{\hat x}_i$ contain the original codes $\mathbf{x}_i$. The constant $C_3$ here is expression (\ref{Cdef2}) from the proof of Thm.~\ref{DeterministicUniquenessTheorem2}. Note that, in contrast to Thm.~\ref{DeterministicUniquenessTheorem}, this constant is dependent on $\mathbf{B}$; hence, \eqref{Cstablem'} holds for \emph{all} matrices $\mathbf{B} \in \mathbb{R}^{n \times m'}$ satisfying the spark condition only in the case $\varepsilon = 0$.

\section{Proof of Theorem~\ref{DeterministicUniquenessTheorem}}\label{DUT}

% ======== b - PDa =========

We demonstrate first of all how \eqref{Cstable} in fact already implies the recovery result \eqref{b-PDa} when $\varepsilon < L_{2k}(\mathbf{A}) / C_1$. For all $2k$-sparse $\mathbf{x} \in \mathbb{R}^m$, the triangle inequality gives \mbox{$\|(\mathbf{A}-\mathbf{BPD})\mathbf{x}\|_2  \leq C_1\varepsilon \|\mathbf{x}\|_1 \leq C_1 \varepsilon \sqrt{2k}  \|\mathbf{x}\|_2$}. Thus, 
\begin{align*}
\|\mathbf{BPD}\mathbf{x}\|_2 
&\geq | \|\mathbf{A}\mathbf{x}\|_2 - \|(\mathbf{A}-\mathbf{BPD})\mathbf{x}\|_2 | \\
&\geq \sqrt{2k} (L_{2k}(\mathbf{A}) -  C_1\varepsilon) \|\mathbf{x}\|_2,
\end{align*}
%
where we may drop the absolute value due to the upper bound on $\varepsilon$. Hence, $L_{2k}(\mathbf{BPD}) \geq L_{2k}(\mathbf{A}) - C_1\varepsilon  > 0$ and \eqref{b-PDa} then follows from:
\begin{align*}
\|\mathbf{x}_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\hat x}_i \|_1
%&\leq \sqrt{2k} |\mathbf{x}_i - D^{-1}P^{\top}\mathbf{\hat x}_i\|_2 \\
&\leq \frac{\|\mathbf{BPD}(\mathbf{x}_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\hat x}_i)\|_2}{\sqrt{2k}L_{2k}(\mathbf{BPD})} \\
&\leq \frac{\|\mathbf{B}\mathbf{\hat x}_i - \mathbf{A}\mathbf{x}_i\|_2 + \|(\mathbf{A} - \mathbf{BPD})\mathbf{x}_i\|_2}{\sqrt{2k}L_{2k}(\mathbf{BPD})} \\
&\leq \frac{\varepsilon (1+C_1 \|\mathbf{x}_i\|_1)}{\sqrt{2k}L_{2k}(\mathbf{BPD})}.
%&\leq \frac{\varepsilon}{\sqrt{2k}} \left( \frac{ 1+C_1 \|\mathbf{x}_i\|_1 }{ L_{2k}(\mathbf{A}) -  C_1\varepsilon } \right).
%\leq \frac{\varepsilon }{\varepsilon_0 - \varepsilon} \left( C_1^{-1}+|\mathbf{x}_i\|_1 \right).
\end{align*}

We establish \eqref{Cstable} in the first place by arguments that flow loosely as follows. Pigeonholing the data into its set of possible supports with respect to the matrix $\mathbf{B}$, one sees that the column space of every $\mathbf{A}_S$ with $S \in E$ must be proximal (in a sense yet to be defined; see Def.~\ref{dDef}) to the column space of some $n \times k$ submatrix of $\mathbf{B}$. \eqref{Cstable} is then immediately implied by our result in combinatorial matrix analysis (Lem.~\ref{MainLemma}), which we derive by the following arguments (see the Supplemental for the full proof). First, we show that the aforementioned proximity between $k$-dimensional subspaces implies a proximity between smaller subspaces spanned by columns of $\mathbf{A}$ indexed by the intersections of sets in $E$ and those spanned by as many or fewer columns of $\mathbf{B}$. Another pigeonholing argument here combined with our assumptions on $E$ (e.g., the singleton intersection property) reveals that, in fact, each column of $\mathbf{A}$ spans a subspace proximal to that spanned by some column of $\mathbf{B}$. \eqref{Cstable} is a simple consequence of this last fact, which actually constitutes the proof of the theorem for the case $k=1$. We present this special case now before restating the above arguments in greater detail.

In fact, in the case $k=1$ we can relax our assumptions even further and assume that the matrix $\mathbf{B}$ has only at least as many columns as $\mathbf{A}$; as we will see, the conclusions of Thm.~\ref{DeterministicUniquenessTheorem} then hold for some $n \times m$ submatrix of $\mathbf{B}$.

We note first that $\|\mathbf{x}\|_1 \leq \sqrt{k} \|\mathbf{x}\|_2$ for $k$-sparse $\mathbf{x} \in \mathbb{R}^m$, which implies by definition of $L_k(A)$ the following inequality which we often use:
\begin{align}\label{delrho}
L_k(\mathbf{A}) \leq \frac{\|\mathbf{A}\mathbf{x}\|_2}{\sqrt{k} \|\mathbf{x}\|_2} %\leq \frac{\|\mathbf{x}\|_1}{\sqrt{k} \|\mathbf{x}\|_2} \max_{i \in [m]}\|\mathbf{A}_i\|_2 
\leq  \max_{i \in [m]}\|\mathbf{A}_i\|_2.
\end{align}

\begin{proof}[Proof ($k=1$)]
Note that the only 1-uniform set system satisfying the singleton intersection property is $[m]$; hence, we have $\mathbf{x}_i = c_i \mathbf{e}_i$ for $c_i \in \mathbb{R} \setminus \{\mathbf{0}\}$, $i \in [m]$. In this case we may take $C_1$ to be any value satisfying $C_1^{-1} \leq \min_{j \in [m]} |c_{j}|$.

Fix $\mathbf{A} \in \mathbb{R}^{n \times m}$ satisfying \eqref{SparkCondition} and suppose that for some $\mathbf{B} \in \mathbb{R}^{n \times m'}$ ($m' \geq m$) and $1$-sparse $\mathbf{\hat x}_i \in \mathbb{R}^{m'}$ we have  $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\hat x}_i\|_2 \leq \varepsilon < L_2(\mathbf{A}) / C_1$ for all $i$. Then there are $c'_1, \ldots, c'_m \in \mathbb{R}$ and $\pi: [m] \to [m']$ with:
\begin{align}\label{1D}
\|c_j\mathbf{A}_j - c'_j\mathbf{B}_{\pi(j)}\|_2 \leq \varepsilon, \ \ \text{for all $j$}.
\end{align} 
Note that $c'_j \neq 0$ for all $j$ since otherwise by \eqref{delrho} and definition of $C_1$ we would have $\|c_j\mathbf{A}_j\|_2 < \min_{\ell \in [m]}\|c_{\ell}\mathbf{A}_{\ell}\|_2$.

We  now show that $\pi$ is injective (and thus is a permutation if $m' = m$). Suppose that $\pi(i) = \pi(j) = \ell$ for some $i \neq j$ and $\ell$. Then, $\|c_{j}\mathbf{A}_{j} - c'_{j}\mathbf{B}_{\ell}\|_2 \leq \varepsilon$ and $\|c_{i}\mathbf{A}_{i} - c'_{i} \mathbf{B}_{\ell}\|_2  \leq \varepsilon$. Scaling and summing these inequalities by $|c'_{i}|$ and $|c'_{j}|$, respectively, and applying the triangle inequality, we obtain:
\begin{align*}%\label{contra}
(|c'_{i}| + |c'_{j}|) \varepsilon
&\geq\|\mathbf{A}(c'_{i}c_{j} \mathbf{e}_{j} - c'_{j}c_{i}\mathbf{e}_{i})\|_2 \nonumber \\ 
&\geq  \left( |c'_{i}| + |c'_{j}| \right) L_2(\mathbf{A}) \min_{\ell \in [m]} |c_\ell |,
\end{align*}
%
which contradicts the upper bound $\varepsilon < L_2(\mathbf{A})/C_1$. Hence, the map $\pi$ is injective. Setting $J = \pi([m])$ and letting $P = \left( \mathbf{e}_{\pi(1)} \cdots \mathbf{e}_{\pi(m)}\right)$ and $D = \text{diag}(\frac{c'_1}{c_1},\ldots,\frac{c'_m}{c_m})$, we see that \eqref{1D} becomes, for all $j \in [m]$:
\begin{align*}%\label{k=1result}
\|\mathbf{A}_j - (\mathbf{B}_J\mathbf{PD})_j\|_2 
= \|\mathbf{A}_j - \frac{c'_j}{c_j}\mathbf{B}_{\pi(j)}\|_2 
\leq \frac{\varepsilon}{|c_j|} 
\leq C_1\varepsilon.
\end{align*}
\end{proof}

%\begin{remark}
%The above arguments can be easily modified to show that the conclusions of Thm.~\ref{DeterministicUniquenessTheorem} in this case ($k=1$) hold for some $n \times m$ submatrix of $\mathbf{B}$ in the event where only an upper bound on the number of columns in $\mathbf{A}$ is known; i.e., the recovered matrix $\mathbf{B}$ is set to have as many or more columns than $\mathbf{A}$. 
%\end{remark}

%It is easy to see that when $m < m'$, the above result holds for the submatrix of $B$ composed of columns indexed by the image of $\pi$.

We require a few additional tools to extend the proof to the general case $k < m$. These include a general notion of distance (Def.~\ref{dDef}) and angle (Def.~\ref{FriedrichsDefinition}) between subspaces and a stability result in matrix analysis (Lem.~\ref{MainLemma}).

\begin{definition}\label{dDef}
For any point $\mathbf{u}$, let $\text{dist}(\mathbf{u}, V) := \inf \{\| \mathbf{u}-\mathbf{v} \|_2: \mathbf{v} \in V\}$ be the distance of $\mathbf{u}$ from the set $V$. For subspaces $U,V \subseteq \mathbb{R}^m$, we define: %[Kato p.197]
\begin{align}\label{d}
d(U,V) := \sup_{\mathbf{u} \in U, \|\mathbf{u}\|_2 = 1} \text{dist}(\mathbf{u},V).
\end{align}
Note that $d(U,\{\textbf{0}\}) = 1$ for $U \neq \{\mathbf{0}\}$, whereas if $U = \{\textbf{0}\}$ then $d$ has no meaning; in this case we set $d(\{\textbf{0}\},V) = 0$ for any $V$.
\end{definition}
%Note that the supremum is always achievable by a point in $U$ when $U, V \subseteq \mathbb{R}^m$.

We note the following facts about $d$. For subspaces $U,V \subseteq \mathbb{R}^m$, we have \cite[Cor.~2.6]{Kato2013}:
\begin{align}\label{dimLem}
d(U,V) < 1 \implies \dim(U) \leq \dim(V).
\end{align}
%
and \cite[Lem.~3.2]{Morris10}:
\begin{align}\label{eqdim}
\dim(U) = \dim(V) \implies d(U,V) = d(V,U).
\end{align}

%\begin{lemma}\label{dimLem} %Kato p.200, 
%\cite[Cor.~2.6]{Kato2013} For subspaces $U,V \subseteq \mathbb{R}^m$, $d(U,V) < 1$ implies $\dim(U) \leq \dim(V)$. 
%\end{lemma}

%\begin{lemma}\label{eqdim}
%\cite[Lem.~3.2]{Morris10} If $\dim(U) = \dim(V)$ then $d(U,V) = d(V,U)$. 
%\end{lemma}

Our result in combinatorial matrix analysis is the following.

\begin{lemma}\label{MainLemma}
Fix integers $n$ and $k < m$ and suppose $\mathbf{A} \in \mathbb{R}^{n \times m}$ satisfies \eqref{SparkCondition}. There exists a constant $C_2 > 0$ for which the following holds for all $\varepsilon < L_2(\mathbf{A}) / C_2$. If for some  $\mathbf{B} \in \mathbb{R}^{n \times m}$ and regular $E \subseteq2^{[m]}$ satisfying the singleton intersection property there exists a size-preserving map $\pi: E \mapsto 2^{[m]}$ satisfying
\begin{align}\label{GapUpperBound}
d(\text{Span}\{\mathbf{A}_{S}\}, \text{Span}\{\mathbf{B}_{\pi(S)}\}) \leq \varepsilon \ \ \text{for all $S \in E$},
\end{align}
%
then there exists some permutation matrix $\mathbf{P}$ and invertible diagonal matrix $\mathbf{D}$ such that:
\begin{align}\label{MainLemmaBPD}
\|\mathbf{A}_j - (\mathbf{BPD})_j\|_2 \leq C_2 \varepsilon, \indent \text{for } j \in [m].
\end{align}
\end{lemma}

The constant $C_1$ in Thm.~\ref{DeterministicUniquenessTheorem} is then given by:
\begin{align}
C_1(\mathbf{A}, \{\mathbf{x}_i\}_{i=1}^N, E) := \frac{ C_2(\mathbf{A}, E) } { \min_{S \in E} L_k(\mathbf{AX}_{I(S)}) },
\end{align}
%
where $\mathbf{X}$ is the $m \times N$ matrix with columns $\mathbf{x}_i$ and $I(S) := \{i : \text{supp}(\mathbf{x}_i) = S\}$.\footnote{We can be sure $C_1 > 0$ is well-defined (provided $C_2$ is well-defined) since $L_k(\mathbf{A}), L_k(\mathbf{X}_{I(S)}) > 0$ by the spark condition and general linear position of the $\mathbf{x}_i$; hence $\|\mathbf{A}_j\|_2 > 0$ for all $j$ and for all $S \in E$ we have $\|\mathbf{AX}_{I(S)}\mathbf{c}\|_2 \geq L_k(\mathbf{A})\|\mathbf{X}_{I(S)}\mathbf{c}\|_2 \geq L_k(\mathbf{A}) L_k(\mathbf{X}_{I(S)})\|\mathbf{c}\|_2$ for all $k$-sparse $\mathbf{c}$ and therefore $L_k(\mathbf{AX}_{I(S)}) \geq L_k(\mathbf{A}) L_k(\mathbf{X}_{I(S)}) > 0$.} The constant $C_2 = C_2(\mathbf{A}, E)$ is defined explicitly below in terms of the following technical quantity based on one used in \cite{Deutsch12} to analyze the convergence of the alternating projections algorithm for projecting a point onto the intersection of a set of subspaces. We use it to bound the distance between a point and the intersection of a set of subspaces given an upper bound on its distance from each subspace individually.

\begin{definition}\label{SpecialSupportSet}\label{FriedrichsDefinition}
For subspaces $V_1, \ldots, V_\ell \subseteq \mathbb{R}^m$, set $r := 1$ when $\ell = 1$ and define for $\ell \geq 2$:
\begin{align*}
r(\{V_i\}_{i=1}^\ell) := 1 - \left(1 -  \max \prod_{i=1}^{\ell-1} \sin^2  \theta \left(V_i, \cap_{j>i} V_j \right)  \right)^{1/2},
\end{align*} 
%
where the maximum is taken over all possible orderings\footnote{We modify the quantity in \cite{Deutsch12} in this way since the subspace ordering is irrelevant to our purpose.} of the $V_i$ and where the angle $\theta \in (0,\frac{\pi}{2}]$ is defined in terms of its cosine as \cite[Def.~9.4]{Deutsch12}:
\begin{align*}
\cos{\theta(U,W)} := \max\left\{ |\langle \mathbf{u}, \mathbf{w} \rangle|: \substack{ \mathbf{u} \in U \cap (U \cap W)^\perp, \|\mathbf{u}\|_2 \leq 1 \\ \mathbf{w} \in W \cap (U \cap W)^\perp, \|\mathbf{w}\|_2 \leq 1 } \right\}.
\end{align*}
\end{definition}
Note that since $\theta \in (0,\frac{\pi}{2}]$, we always have $0 < r \leq 1$. (We acknowledge the somewhat counter-intuitive property that $\theta =  \pi/2$ when $U = V$ and when $U \perp V$.)  %\textbf{Note:} we can also define $\theta$ by \cite[Lem.~9.5]{Deutsch12}:
%\begin{align*}
%\cos{\theta(U,W)} := \max\left\{ |\langle \mathbf{u}, \mathbf{w} \rangle|: \mathbf{u} \in U \cap (U \cap W)^\perp, \|\mathbf{u}\|_2 \leq 1, \mathbf{w} \in W \|\mathbf{w}\|_2 \leq 1  \right\}.
%\end{align*}

The constant $C_2$ in Lem.~\ref{MainLemma} is then given by:\footnote{Note that $C_2 > 0$ is well-defined since $r > 0$ by definition.}
\begin{align}
C_2(\mathbf{A}, E) := \frac{ 2^{|E|} \max_{i \in [m]} \|\mathbf{A}_i\|_2}{ \min_{F \subseteq E} r( \{ \text{Span}\{\mathbf{A}_{S}\} \}_{S \in F}) }.
\end{align}

The reader may verify that this definition leads to a value for $C_1$ consistent with that used in our proof of the case $k=1$ above.

\begin{proof}[Proof ($k < m$)] 
%We begin by showing that for every $S \in E$ there is some $S' \in {[m] \choose k}$ for which the distance $d(\text{Span}\{\mathbf{A}_S\}, \text{Span}\{\mathbf{B}_S'\})$ is controlled by $\varepsilon$. Fix $S \in E$. Since there are $(k-1){m \choose k}+1$ vectors $\mathbf{x}_i$ supported on $S$, the pigeon-hole principle implies that there exists some $S' \in {[m] \choose k}$ and some set of $k$ indices $J(S)$ such that the supports of all $\mathbf{x}_i$ and $\mathbf{\hat x}_i$ with $i \in J(S)$ are contained in $S$ and $S'$, respectively.

%%% No |S| = k assumption %%%
We begin by showing that for every $S \in E$ there is some $S' \subseteq [m]$, $|S'| \leq k$ for which the distance $d(\text{Span}\{\mathbf{A}_S\}, \text{Span}\{\mathbf{B}_S'\})$ is controlled by $\varepsilon$. Fix $S \in E$. Since there are $(k-1){m \choose k}+1$ vectors $\mathbf{x}_i$ supported on $S$, the pigeon-hole principle implies that there exists some $S' \in {[m] \choose k}$ and some set of $k$ indices $J(S)$ such that the supports of all $\mathbf{x}_i$ and $\mathbf{\hat x}_i$ with $i \in J(S)$ are contained in $S$ and $S'$, respectively.

Let $\mathbf{X}$ and $\mathbf{X}'$ be the $m \times N$ matrices with columns $\mathbf{x}_i$ and $\mathbf{\hat x}_i$, respectively. It follows from the general linear position of the $\mathbf{x}_i$ and the linear independence of every $k$ columns of $\mathbf{A}$ that $L_k(\mathbf{AX}_{J(S)}) > 0$; that is, the columns of the $n \times k$ matrix $\mathbf{AX}_{J(S)}$ are linearly independent and thus form a basis for $\text{Span}\{\mathbf{A}_{S}\}$. Fixing $\mathbf{y} \in \text{Span}\{\mathbf{A}_{S}\}$, there then exists a unique $\mathbf{c} = (c_1, \ldots, c_k) \in \mathbb{R}^k$ such that $\mathbf{y} = \mathbf{AX}_{J(S)}\mathbf{c}$. Letting \mbox{$\mathbf{y'} = \mathbf{BX}'_{J(S)}\mathbf{c}$}, which is in $\text{Span}\{\mathbf{B}_{S'}\}$, we have:
\begin{align*}
\|\mathbf{y} - \mathbf{y'}\|_2 
&= \|\sum_{i=1}^k c_i(\mathbf{AX}_{J(S)} - \mathbf{BX}'_{J(S)})_i\|_2
\leq \varepsilon \sum_{i=1}^k |c_i| \\
&\leq \varepsilon \sqrt{k}  \|\mathbf{c}\|_2 
%\leq \frac{\varepsilon \sqrt{k}}{L(\mathbf{A}X_{J(S)})} \|\mathbf{A}X_{J(S)}\mathbf{c}\|_2 
= \frac{\varepsilon}{L_k(\mathbf{AX}_{J(S)})} \|\mathbf{y}\|_2,
\end{align*}
where the last equality is by definition of the domain-restricted matrix lower bound $L_k$. It follows that for all $S \in E$,
\begin{align}\label{rhs222}
d(\text{Span}\{\mathbf{A}_S\}, \text{Span}\{\mathbf{B}_{S'}\}) 
\leq \frac{\varepsilon}{ \min_{S \in E} L_k(\mathbf{AX}_{I(S)}) } 
%\leq \frac{\varepsilon}{L(\mathbf{AX}_{J(S)})}.
%&< \left( \frac{ L_2(\mathbf{A}) }{ 2^{|E|} \max_{j \in [m]} \|\mathbf{A}_j\|_2 } \right) \frac{ \min_{S \in E} L_k(\mathbf{AX}_{I(S)}) } { L(\mathbf{AX}_{J(S)}) } \min_{\substack{F \subseteq E}} r( \{ \text{Span}\{\mathbf{A}_{S}\} \}_{S \in F}) \\
\end{align}
The result then follows by  Lem.~\ref{MainLemma}, with the map $\pi: E \to {[m] \choose k}$ defined by the association $S \mapsto S'$ above.
%\begin{align}
%\delta= \frac{\varepsilon}{ \min_{S \in E} L_k(\mathbf{AX}_{I(S)}) } = \frac{ C \varepsilon }{ \tilde C } < \frac{L_2(\mathbf{A})}{\tilde C}
%\end{align}
\end{proof}

%We then show that the map over subsets of column indices defined by this association is such that the number of common elements shared by sets in its domain bounds the number of elements common to their images under this map.

\section{Discussion}\label{Discussion}

In this note, we generalize the approach of \cite{Hillar15} to the uniqueness of solutions to Problem~\ref{InverseProblem} to the case of noisy measurements while also reducing the number of required samples.
% from $N=k{m \choose k}^2$ to $N = m(k-1){m \choose k}+m$. 
% CUT OK? Surprisingly, almost all $n \times m$ dictionaries satisfying the standard assumption \eqref{CScondition} from compressed sensing (CS) are identifiable from enough generic noisy $k$-sparse linear combinations of their elements, up to an error linear in the noise. Moreover, if solutions are constrained to satisfy \eqref{SparkCondition}, then only an upper bound on the number of dictionary elements need be taken as given. 
We remark that our result in the deterministic case (Thm.~\ref{DeterministicUniquenessTheorem}) accounts for \emph{worst-case} noise, whereas the ``effective'' noise might be much smaller when it is sampled from a given distribution; in such cases, the constants $C_1, C_3$ in Thms.~\ref{DeterministicUniquenessTheorem},~\ref{DeterministicUniquenessTheorem2} will be much smaller with high probability.
We note also that these results extend trivially to cases where point-wise injective nonlinearities are applied to the data. We close by outlining four diverse application areas.

% FRITZ: Inverse problems instead of Data Analysis. Don't assume that everyone is assuming they are recovering ground truth. Cite results again and state implications! Focus on them (probabilistic ones too).
\textbf{Inverse Problems}.  
Our results provide theoretical grounding for the use of sparse linear coding in blind source separation, wherein the goal is to infer the generating dictionary and sparse codes from noisy measurements generated as in \eqref{LinearModel} (e.g., recovering a rat's position on a linear track from local field potentials in Hippocampus \cite{Agarwal14}). It would be of practical utility therefore to determine the best possible dependence of $\varepsilon$ on $\delta_1, \delta_2$ (see \eqref{epsdel}) as well as the minimal requirements on the number and diversity of generating codes. %We encourage researchers to extend our results and tighten these parameters.

[Effective computation of stable datasets, at least in principle.]

\textbf{Theoretical Neuroscience}.
Sparse dictionary learning and related methods have recovered characteristic components of natural images \cite{Olshausen96, hurri1996image, bell1997independent, van1998independent} and sounds \cite{bellsejnowski1996, smithlewicki2006, Carlson12}, reproducing response properties of cortical neurons. Our theorems suggest that this correspondence could be due to the uniqueness of sparse representations. Furthermore, our guarantees justify the hypothesis of \cite{Coulter10} and \cite{Isely10} that sparse codes passed through a communication bottleneck in the brain can be recovered from random projections via (unsupervised) biologically plausible sparse dictionary learning (e.g., \cite{rehnsommer2007, rozell2007neurally, hu2014hebbian}).   
%TODO: add reproduction of response propeties in olfactory cortex?

% Reiterate probabilistic result in the smooth analysis part?
\textbf{Smoothed Analysis}.
The main concept in smoothed analysis \cite{Spielman04} is that certain algorithms having exponential worst-case behavior are, nonetheless, efficient if certain (typically, measure zero in the continuous case and with ``low probability" in the discrete case) pathological input sets are avoided. Our results imply that if there is an efficient ``smoothed" algorithm for solving Problem \ref{InverseProblem} given enough samples, then for generic inputs this algorithm determines the unique original solution. We note that avoiding certain pathological sets of inputs is often a necessary technicality for dictionary learning \cite{Razaviyayn15, Tillmann15}.

\textbf{Engineering}.
Several groups utilize compressed sensing for signal processing tasks: MRI analysis \cite{lustig2008compressed},  image compression \cite{Duarte08}, and, more recently, the design of an ultrafast camera \cite{Gao14}. Given such effective uses of compressed sensing, it is only a matter of time before these systems incorporate sparse dictionary learning to encode and process data. Guarantees such as those offered by our theorems allow any such device to be equivalent to any other (having different initial parameters and data samples) as long as enough data originate from a statistically identical system.

\acknow{We thank Friedrich Sommer for turning our attention to the dictionary learning problem, Darren Rhea for sharing early explorations, and Ian Morris for posting identity \eqref{SubspaceMetricSameDim} online.}

\showacknow % Display the acknowledgments section

% \pnasbreak % splits and balances the columns before the references.
% If you see unexpected formatting errors, try commenting out this line
% as it can run into problems with floats and footnotes on the final page.
%\pnasbreak %was causing only first two pages to print..??

% Bibliography
\bibliography{chazthm_pnas}

%% SUPPLEMENTAL INFO? %%%
%\begin{remark}
%Actually, $\mathbf{A}$ need not be injective on all $k$-sparse vectors for Theorem \ref{DeterministicUniquenessTheorem} to hold; rather, it need only be injective the set of all vectors with supports in $E$. [** TODO ** we will probably have to redefine $L_2$ since it is over all $k$-sparse vectors -- may have to instead define $L_E$.] Wait, $E$ need not be regular for $B$ sat. spark cond. Also it need not be $k$-regular!
%\end{remark}

\clearpage

\section{Proof of Main Lemma}

We require some auxiliary lemmas.

\begin{lemma}\label{SpanIntersectionLemma}
Let $\mathbf{M} \in \mathbb{R}^{n \times m}$. If every $2k$ columns of $\mathbf{M}$ are linearly independent, then for any $F \subseteq 2^{[m]}$ of rank $k$, we have:
\begin{align*}
\text{\rm Span}\{\mathbf{M}_{\cap F}\}  = \cap_{S \in F} \text{\rm Span}\{\mathbf{M}_S\}.
\end{align*}
\end{lemma}
\begin{proof}
By induction, it is enough to prove the lemma when $|F| = 2$. The proof now follows directly from the assumption.
\end{proof}

% This can be made tighter by using Pythagoras' Thm for first projection instead of triangle inequality. 
\begin{lemma}\label{DistanceToIntersectionLemma}
Fix $k \geq 2$. Let $V_1, \ldots, V_k$ be subspaces of $\mathbb{R}^m$ and set $V = \cap_{i = 1}^k V_i$. For every $\mathbf{x} \in \mathbb{R}^m$, we have:
\begin{align}\label{DTILeq}
\text{\rm dist}(\mathbf{x}, V) \leq \frac{1}{r(\{V_i\}_{i = 1}^k)} \sum_{i=1}^k \text{\rm dist}(\mathbf{x}, V_i),
\end{align}
where $r$ is given in Def.~\ref{SpecialSupportSet}.
\end{lemma}
\begin{proof} 
Fix $\mathbf{x} \in \mathbb{R}^m$ and $k \geq 2$. Recall that the orthogonal projection onto a subspace $V \subseteq \mathbb{R}^m$ is the mapping $\Pi_V$ from $\mathbb{R}^m$ to $V$ that associates with each $\mathbf{x}$ its unique nearest point in $V$, i.e. $\|\mathbf{x} - \Pi_V\mathbf{x}\|_2 = \text{dist}(\mathbf{x}, V)$.
% Since subspaces of real vector spaces are closed, we can replace inf with min in def. of orthogonal projection

We begin the proof by observing that:
%Use Pythagoras' Theorem first?
\begin{align}\label{f}
\|\mathbf{x} - \Pi_V\mathbf{x}\|_2 &\leq \|\mathbf{x} - \Pi_{V_k} \mathbf{x}\|_2 + \|\Pi_{V_k}  \mathbf{x} - \Pi_{V_k}\Pi_{V_{k-1}}\mathbf{x}\|_2 \nonumber \\
&\ \ \ + \cdots + \|\Pi_{V_k} \Pi_{V_{k-1}}\cdots \Pi_{V_1} \mathbf{x} - \Pi_V \mathbf{x}\|_2 \nonumber \\
&\leq \|\Pi_{V_k}\cdots\Pi_{V_{1}} \mathbf{x} - \Pi_V \mathbf{x}\|_2 + \sum_{\ell=1}^k \|\mathbf{x} - \Pi_{V_{\ell}} \mathbf{x}\|_2,
\end{align}
%
by the triangle inequality and the fact that the spectral norm $\|\Pi_{V_{\ell}}\|_2 \leq 1$ for all $\ell$ (since $\Pi_{V_{\ell}}$ are orthogonal projections).

The desired result \eqref{DTILeq} now follows by bounding the second term on the right-hand side using the following fact \cite[Thm.~9.33]{Deutsch12}:
\begin{align}
\|\Pi_{V_k}\Pi_{V_{k-1}}\cdots\Pi_{V_1} \mathbf{x} - \Pi_V\mathbf{x}\|_2 \leq z \|\mathbf{x}\|_2, %  \indent \text{for } \mathbf{x} \in \mathbb{R}^m,
\end{align}
for \mbox{$z^2= 1 - \prod_{\ell =1}^{k-1}(1-z_{\ell}^2)$} and \mbox{$z_{\ell} = \cos\theta\left(V_{\ell}, \cap_{s=\ell+1}^k V_s\right)$}. Together with $\Pi_{V_\ell} \Pi_V = \Pi_V$ for all $\ell = 1, \ldots, k$ and $\Pi_V^2 = \Pi_V$, this yields:
\begin{align*}
\|\Pi_{V_k} \cdots \Pi_{V_1}\mathbf{x}  - \Pi_V \mathbf{x} \|_2 
&= \|\left( \Pi_{V_k} \cdots\Pi_{V_1} - \Pi_V \right) (\mathbf{x} - \Pi_V\mathbf{x})\|_2 \\
&\leq z\|\mathbf{x} - \Pi_V\mathbf{x}\|_2.
\end{align*}

Plugging this into \eqref{f} and rearranging yields \eqref{DTILeq} after substituting $r(\{V_i\}_{i=1}^k)$ for $1 - z$ (as $z$ may depend on the arbitrary ordering of the $V_i$).
\end{proof}

\begin{lemma}\label{NonEmptyLemma} 
Suppose $E \subseteq 2^{[m]}$ is $\ell$-regular and satisfies the singleton intersection property. If there exists a map $\pi: E \to 2^{[m]}$ such that $\sum_{S \in E} |S| = \sum_{S \in E} |\pi(S)|$ and:
\begin{align}\label{cond}
|\cap_{S \in F} \pi(S)| \leq |\cap_{S \in F} S | \ \ \text{for all } F \subseteq E,
\end{align}
%
then $\pi(E)$ is $\ell$-regular and satisfies the singleton intersection property. In particular, $|\cap_{S \in F} S| = 1$ if and only if $|\cap_{S \in F} \pi(S)| = 1$. 
\end{lemma}
\begin{proof}
Fix $T = \{(j, S): j \in \pi(S), S \in E\}$. We have $|T| = \sum_{S \in E} |\pi(S)| = \sum_{S \in E} |S| = \sum_{i \in [m]} \deg(i) = \ell m$ by regularity of $E$. Note that by \eqref{cond} there can be no more than $\ell$ elements of $T$ with a given first index, since $E$ is $\ell$-regular. Pigeonholing the elements of $T$ with respect to the set of possible first indices, we see then that for each $j$ there must be exactly $\ell$ elements of $T$ with $j$ as a first index; hence, $\pi(E)$ is $\ell$-regular.

Fix $j$ and let $F(j) = \{S \in E: j \in \pi(S)\}$ be the preimage of the star in $\pi(E)$ centered at $j$, which is of size $\ell$ by the above arguments. It follows from \eqref{cond} that $\cap_{S \in F(j)} S$ is nonempty. In fact, we must have $|\cap _{S \in F(j)} S| = 1$, since $E$ is $\ell$-regular and satisfies the singleton intersection property. It follows by \eqref{cond} that $\cap_{S \in F(j)} \pi(S) = \{j\}$. Thus $\pi(E)$ satisfies the singleton intersection property as well, and the preimage of every one of the $m$ stars in $\pi(E)$ is a star in $E$.

It remains to show that every star in $E$ maps through $\pi$ to some star in $\pi(E)$. This follows by pigeonholing the $m$ stars of $\pi(E)$ with respect to their $m$ possible preimages if no two stars in $\pi(E)$ share the same preimage. This indeed must be the case, since $F(i) = F(j)$ implies $\{i\} = \cap_{S \in F(i)} \pi(S) = \cap_{S \in F(j)} \pi(S) = \{j\}$.
\end{proof}

\begin{proof}[Proof of Main Lemma]
We first claim $\dim(\text{Span}\{\mathbf{B}_{\pi(S)}\}) = \dim(\text{Span}\{\mathbf{A}_{S}\})$ for all $S \in E$. To see why, note that the right-hand side of \eqref{GapUpperBound} is then strictly less than one, since $r \leq 1$ and $L_2(\mathbf{A}) \leq 1$ by \eqref{delrho}. By \eqref{dimLem} it then follows that $|\pi(S)| \geq \dim(\text{Span}\{\mathbf{B}_{\pi(S)}\}) \geq \dim(\text{Span}\{\mathbf{A}_{S}\}) = |S|$, with the equality due to $\mathbf{A}$ satisfying \eqref{SparkCondition}; hence, $\dim(\text{Span}\{\mathbf{B}_{\pi(S)}\}) = \dim(\text{Span}\{\mathbf{A}_{S}\})$ (since $|S| = |\pi(S)|$). It follows that the columns of $\mathbf{B}_{\pi(S)}$ are linearly independent and, by \eqref{eqdim}:% and $\mathbf{B}_i \neq \textbf{0}$ for all $i$.
\begin{align}\label{eq2}
d(\text{Span}\{\mathbf{B}_{\pi(S)}\}, \text{Span}\{\mathbf{A}_S\} ) = d(\text{Span}\{\mathbf{A}_S\}, \text{Span}\{\mathbf{B}_{\pi(S)}\}).
\end{align}
We will now show that:
\begin{align}\label{fact2}
|\bigcap_{S \in F} \pi(S)| \leq |\bigcap_{S \in F} S |, \ \ \text{for all } \ F \subseteq E.
\end{align}

Fix $F \subseteq E$. Since $\text{Span}\{\mathbf{B}_{\cap_{S \in F}\pi(S)}\} \subseteq \cap_{S \in F} \text{Span}\{\mathbf{B}_{\pi(S)}\}$, if $\cap_{S \in F} \text{Span}\{\mathbf{B}_{\pi(S)}\} = \textbf{0}$ then we must have $|\cap_{S \in F} \pi(S)| = 0$ (as $\mathbf{B}_i \neq \textbf{0}$ for all $i$) and \eqref{fact2} trivially holds. Suppose then that the intersection is not the zero vector. By Lem.~\ref{SpanIntersectionLemma} and Lem.~\ref{DistanceToIntersectionLemma}, and incorporating \eqref{eq2} and \eqref{GapUpperBound}, we have:
\begin{align}\label{randoml}
d( \text{Span}&\{\mathbf{B}_{\cap_{S \in F}\pi(S)}\}, \text{Span}\{\mathbf{A}_{\cap_{S \in F} S}\}  ) \nonumber \\
&\leq d\left( \cap_{S \in F} \text{Span}\{\mathbf{B}_{\pi(S)}\}, \cap_{S \in F} \text{Span}\{\mathbf{A}_{S}\} \right) \nonumber \\
&\leq \sum_{S \in F} \frac{ d\left( \cap_{T \in F} \text{Span}\{\mathbf{B}_{\pi(T)}\},\text{Span}\{\mathbf{A}_{S}\} \right) }{ r( \{ \text{Span}\{\mathbf{A}_{T}\}_{T \in F}) } \nonumber \\
&\leq \sum_{S \in F} \frac{ d\left( \text{Span}\{\mathbf{B}_{\pi(S)}\},\text{Span}\{\mathbf{A}_{S}\} \right) }{ r( \{ \text{Span}\{\mathbf{A}_{T}\}_{T \in F}) }\nonumber \\
%&\leq \frac{1}{r( \{ \text{Span}\{\mathbf{A}_{S}\}_{S \in F})} \sum_{S \in F} \frac{ \varepsilon }{ L(\mathbf{AX}_{J(S)}) } \nonumber \\
&\leq \frac{|F| \delta}{r( \{ \text{Span}\{\mathbf{A}_{S}\} \}_{S \in F})} 
%&< L_2(\mathbf{A}) \frac{|F| }{ 2^{|E|}} \left( \frac{ \min_{\substack{F \subseteq E}} r( \{ \text{Span}\{\mathbf{A}_{S}\}_{S \in F}) }{ r( \{ \text{Span}\{\mathbf{A}_{S}\}_{S \in F}) } \right) \left( \frac{\min_{S \in E} L_k(\mathbf{AX}_{I(S)}) }{ \min_{T \in F} L(\mathbf{AX}_{J(T)}) } \right) \nonumber \\
\leq \tilde C_2 \delta, 
\end{align}
%
Note that since $\delta < L_2(\mathbf{A}) / \tilde C_2$, by \eqref{delrho} the right-hand side in \eqref{rando} is strictly less than one, so \eqref{dimLem} implies that $\dim(\text{Span}\{\mathbf{B}_{\cap_{S \in F}\pi(S)}\}) \leq \dim(\text{Span}\{\mathbf{A}_{\cap_{S \in F} S}\})$ and \eqref{fact2} follows from the linear independence of the columns of $\mathbf{A}_{S}$ and $\mathbf{B}_{\pi(S)}$ for all $S \in F$.

Now, fix $\ell \in [m]$. Since $E$ satisfies the singleton intersection property, $\{\ell\} = \cap F(\ell)$ for the star $F(\ell) \subseteq E$. By \eqref{fact2}, we have that $\cap_{S \in F(\ell)} \pi(S)$ is either empty or it contains a single element. Lem.~\ref{NonEmptyLemma} ensures the latter case is the only possibility. Thus, the association $\ell \mapsto \cap_{S \in F(\ell)} \pi(S)$ defines a map $\hat \pi: [m] \to [m]$ and $\dim(\text{Span}\{\mathbf{B}_{\hat \pi(\ell)}\}) = 1$, since $\mathbf{B}_i \neq \textbf{0}$ for all $i$. By \eqref{eqdim}, it follows from \eqref{rando} that $d\left( \text{Span}\{\mathbf{A}_\ell\}, \text{Span}\{ \mathbf{B}_{\hat \pi(\ell)} \} \right) \leq C_2\delta$. Since $\ell$ is arbitrary, fixing $\hat \varepsilon = C_2\delta$ it follows from \eqref{rando} that for every basis vector $\mathbf{e}_\ell \in \mathbb{R}^m$ there exists some $c'_\ell \in \mathbb{R}$ such that $\|\mathbf{A}\mathbf{e}_\ell - c'_\ell \mathbf{B}\mathbf{e}_{\hat \pi(\ell)}\|_2 \leq \hat \varepsilon < L_2(\mathbf{A})$. This is exactly the supposition in \eqref{1D} (letting $c_i = \|\mathbf{A}_i\|_2^{-1}$ for all $i$) and the result follows from the subsequent arguments for the case $k=1$ in Sec.~\ref{DUT}.
\end{proof}

The above arguments can be easily modified to prove the following variation of Lem.~\ref{MainLemma}, key to proving Thm.~\ref{DeterministicUniquenessTheorem2}.

\begin{lemma}\label{MainLemma2}
Fix integers $n$ and $k < m \leq m'$ and suppose $\mathbf{A}~\in~\mathbb{R}^{n \times m}$ and $\mathbf{B} \in \mathbb{R}^{n \times m'}$ both satisfiy \eqref{SparkCondition}. There exists a constant $C_4 > 0$ for which for all $\varepsilon < L_2(\mathbf{A}) / C_4$ the following holds. If for some $E \subseteq2^{[m]}$ satisfying the singleton intersection property there exists a size-preserving map $\pi: E \mapsto 2^{[m']}$ satisfying:
\begin{align}\label{GapUpperBound}
d(\text{Span}\{\mathbf{A}_{S}\}, \text{Span}\{\mathbf{B}_{\pi(S)}\}) \leq \varepsilon \ \ \text{for all $S \in E$},
\end{align}
%
then for some $J \in {[m'] \choose m}$, permutation matrix $\mathbf{P}$ and invertible diagonal matrix $\mathbf{D}$, we have:
\begin{align}\label{MainLemmaBPD}
\|\mathbf{A}_j - (\mathbf{BPD})_j\|_2 \leq C_4 \varepsilon, \indent \text{for } j \in [m].
\end{align}
The constant $C_4$ is given by:
\begin{align}\label{Cdefm'}
C_4 := \frac{2^{|E|}}{R} \max_{j \in [m]} \|\mathbf{A}_j\|_2
\end{align}
%
with $R$ being the lesser of $\min_{\substack{F \subseteq E}} r( \{ \text{Span}\{\mathbf{A}_{S}\} \}_{S \in F})$ and $\min_{\substack{F \subseteq {[m'] \choose k}}} r( \{ \text{Span}\{\mathbf{B}_{S}\} \}_{S \in F})$.
\end{lemma}

\begin{proof}
The proof is very similar to the case $m' = m$, the difference being that now we may not invoke Lem.~\ref{NonEmptyLemma} (which requires $m' = m$) to infer from \eqref{fact2} that $| \cap_{S \in F(i)} \pi(S) | = 1$ for all stars $F(i)$. We circumvent this issue by instead assuming the spark condition on $\mathbf{B}$, which allows us to swap the roles of $\mathbf{A}$ and $\mathbf{B}$ in the arguments leading to the derivation of \eqref{fact2} to prove the opposite inequality for every star $F(i)$. Of course, this requires that the constant $C_4$  depend on $\mathbf{B}$. By these arguments we establish that $| \cap_{S \in F(i)} \pi(S) | = 1$ for all stars $F(i)$, yielding an injective map $\hat \pi: [m] \to [m']$. The result then follows from the proof of the case $k=1$. 
\end{proof}

\section{Proofs of Thms.~\ref{robustPolythm} \& \ref{DeterministicUniquenessTheorem2} and Cors.~\ref{DeterministicUniquenessCorollary} \& \ref{ProbabilisticCor}}\label{AppendixB}

\begin{proof}[Proof of Cor.~\ref{DeterministicUniquenessCorollary}]
We need only demonstrate how to produce $N$ vectors $\mathbf{a}_i$ such that for some $E \subseteq {[m] \choose k}$ satisfying the singleton intersection property there are \mbox{$(k-1){m \choose k}+1$} vectors supported on each $S \in E$ in general linear position. Let $\gamma_1, \ldots, \gamma_N$ be any distinct numbers. Then the columns of the $k \times N$ matrix $V = (\gamma^i_j)^{k,N}_{i,j=1}$ are in general linear position (since the $\gamma_j$ are distinct, any $k \times k$ ``Vandermonde" sub-determinant is nonzero). Next, fix some $E \subseteq {[m] \choose k}$ satisfying the singleton intersection property. Finally, form the $k$-sparse vectors $\mathbf{a}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$ with supports $S \in E$ (partitioning the $\mathbf{x}_i$ evenly among these supports so that each contains $(k-1){m \choose k}+1$ vectors $\mathbf{x}_i$) by setting the nonzero values $\mathbf{x}_i$ to be those contained in the $i$th column of $V$.
\end{proof}
% Actually this is even overkill since

We now determine classes of datasets $Y$ having a stable sparse representation that are cut out by a single polynomial equation.

\begin{proof}[Proof of Thm.~\ref{robustPolythm}]
We sketch the argument, leaving the details to the reader.
Let $M$ be the $n \times m$ matrix with columns $\mathbf{A}\mathbf{x}_i$, $i \in [N]$.  Consider the following polynomial \cite[Sec.~IV]{Hillar15} in the entries of $\mathbf{A}$ and the $\mathbf{x}_i$:
\begin{align*}
g(\mathbf{A}, \{\mathbf{x}_i\}_{i=1}^N) = \prod_{S \in {[n] \choose k}} \sum_{S' \in {[N] \choose k}} (\det M_{S',S})^2,
\end{align*}
with notation as in Sec.~\ref{Results}.

It can be checked that when $g$ is nonzero for a substitution of real numbers for the indeterminates, all of the genericity requirements on $\mathbf{A}$ and $\mathbf{x}_i$ in our proofs of stability in Thm.~\ref{DeterministicUniquenessTheorem} are satisfied (in particular, the spark condition on $\mathbf{A}$). The statement of the theorem now follows directly.
\end{proof}

\begin{proof}[Proof of Cor.~\ref{ProbabilisticCor}]
First, note that if a set of measure spaces $\{(X_{\ell}, \Sigma_{\ell}, \nu_{\ell})\}_{\ell=1}^p$ is such that $\nu_{\ell}$ is absolutely continuous with respect to $\mu$ for all $\ell = 1, \ldots, p$, where $\mu$ is the standard Borel measure on $\mathbb{R}$, then the product measure $\prod_{\ell=1}^p \nu_{\ell}$ is absolutely continuous with respect to the standard Borel product measure on $\mathbb{R}^p$ (e.g.,  \cite{folland2013real}). By Thm.~\ref{robustPolythm}, there is a polynomial that is nonzero whenever $Y$ has a stable $k$-sparse representation in $\mathbb R^m$; in particular, this property (stability) holds with probability one.
\end{proof}

\begin{proof}[Proof of Thm.~\ref{DeterministicUniquenessTheorem2}]
The proof is the same as that of the case $m' = m$, only now we establish a map $\pi: E \to {[m'] \choose k}$ by pigeonholing $(k-1){m' \choose k} + 1$ vectors with respect to holes $[m']$ and eventually applying Lem.~\ref{MainLemma2} instead of Lem.~\ref{MainLemma}.

In this case the constant $C_3$ is given by:
\begin{align}\label{Cdefm'}
C_3 := \frac{2^{|E|} \max_{j \in [m]} \|\mathbf{A}_j\|_2}{ R \min_{S \in E} L_k(\mathbf{AX}_{I(S)}) },
\end{align}
%
with $R$ being the lesser of $\min_{\substack{F \subseteq E}} r( \{ \text{Span}\{\mathbf{A}_{S}\} \}_{S \in F})$ and $\min_{\substack{F \subseteq {[m'] \choose k}}} r( \{ \text{Span}\{\mathbf{B}_{S}\} \}_{S \in F})$.
\end{proof}

\end{document}

### 2017-03-23 manuscripts/PNAS/chazthm_pnas.tex
bib update
minor update

@@
 
-Before stating our main results, we explain how the spark condition \eqref{SparkCondition} relates to the \emph{lower bound} \cite{Grcar10} of $\mathbf{A}$, written $L(\mathbf{A})$, which is the largest number $\alpha$ such that \mbox{$\|\mathbf{A}\mathbf{x}\|_2 \geq \alpha\|\mathbf{x}\|_2$} for all $\mathbf{x} \in \mathbb{R}^m$.
+Before stating our main results, we explain how the spark condition \eqref{SparkCondition} relates to the \emph{lower bound} \cite{Grcar10} of $\mathbf{A}$, which is the largest number $\alpha$ such that \mbox{$\|\mathbf{A}\mathbf{x}\|_2 \geq \alpha\|\mathbf{x}\|_2$} for all $\mathbf{x} \in \mathbb{R}^m$.
 By compactness, every injective linear map has a nonzero lower bound; hence, if $\mathbf{A}$ satisfies \eqref{SparkCondition}, then every submatrix formed from $2k$ of its columns or less has a nonzero lower bound.
@@
 
+[State this without reference to special set $E$]
 \begin{theorem}\label{DeterministicUniquenessTheorem}
@@
 \begin{align}\label{b-PDa}
-\|\mathbf{x}_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\hat x}_i\|_1 &\leq \frac{\varepsilon}{\sqrt{2k}} \left( \frac{ 1+C_1 \|\mathbf{x}_i\|_1 }{ L_{2k}(\mathbf{A}) -  C_1\varepsilon } \right).
+\|\mathbf{x}_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\hat x}_i\|_1 &\leq  \left( \frac{ 1+C_1 \|\mathbf{x}_i\|_1 }{ L_{2k}(\mathbf{A}) -  C_1\varepsilon } \right) \varepsilon,
  \ \ \text{for all $i \in [N]$}.
@@
 
-\begin{proposition}
-If $E$ is an $\ell$-regular set system of rank $k$ satisfying the singleton intersection property then $|E| \geq \ell m/k$. 
-\end{proposition}
+%\begin{proposition}
+%If $E$ is an $\ell$-regular set system of rank $k$ satisfying the singleton intersection property then $|E| \geq \ell m/k$. 
+%\end{proposition}
+Note that if $E$ is an $\ell$-regular set system of rank $k$ satisfying the singleton intersection property then $|E| \geq \ell m/k$.
 This is easy to see by noting that $|E|k \geq \sum_{S \in E}|S| = \sum_{i \in [m]} \deg(i) = \ell m$.
@@
 Since $f$ is a real analytic function, it is enough to show that at least \emph{one} substitution of real numbers satisfies $f(\mathbf{A}) \neq 0$ to conclude that its zeroes form a set with measure zero.
-Hence, \emph{every} $n \times m$ matrix $\mathbf{A}$ outside a set of measure zero satisfies \eqref{SparkCondition} provided \eqref{CScondition} holds for a value of $\gamma$ for \emph{some} distribution.
+Hence, \emph{every} $n \times m$ matrix $\mathbf{A}$ outside such a set satisfies \eqref{SparkCondition} provided \eqref{CScondition} holds for a value of $\gamma$ for \emph{some} distribution.
 We remark that the precise relationship between $m$, $n$, and $k$ guaranteeing that $f$ is not identically zero is still an open problem in real algebraic geometry [**TODO** cite recent work?].
@@
 Fix integers $n$ and $k < m \leq m'$ and matrices $\mathbf{A}~\in~\mathbb{R}^{n \times m}$ and $\mathbf{B} \in \mathbb{R}^{n \times m'}$ both satisfying \eqref{SparkCondition}.
-Suppose \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} include at least \mbox{$(k-1){m' \choose k}+1$} vectors in general linear position supported on each set in some $k$-uniform $E \subseteq 2^{[m]}$ satisfying the singleton intersection property.
+Suppose \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} include at least \mbox{$(k-1){m' \choose k}+1$} $k$-sparse vectors in general linear position supported on each set in some $k$-uniform $E \subseteq 2^{[m]}$ satisfying the singleton intersection property.
 Then there exists a constant $C_3 > 0$ for which the following holds.
@@
 % ======== b - PDa =========
+First note that $\|\mathbf{x}\|_1 \leq \sqrt{k} \|\mathbf{x}\|_2$ for $k$-sparse $\mathbf{x} \in \mathbb{R}^m$, which by definition of $L_k(A)$ implies the following often used inequality:
+\begin{align}\label{delrho}
+L_k(\mathbf{A}) \leq \frac{\|\mathbf{A}\mathbf{x}\|_2}{\sqrt{k} \|\mathbf{x}\|_2} %\leq \frac{\|\mathbf{x}\|_1}{\sqrt{k} \|\mathbf{x}\|_2} \max_{i \in [m]}\|\mathbf{A}_i\|_2 
+\leq  \max_{i \in [m]}\|\mathbf{A}_i\|_2.
+\end{align}
 
-We demonstrate first of all how \eqref{Cstable} in fact already implies the recovery result \eqref{b-PDa} when $\varepsilon < L_{2k}(\mathbf{A}) / C_1$.
+Our first step is to demonstrate how \eqref{Cstable} already implies the recovery result \eqref{b-PDa} when $\varepsilon < L_{2k}(\mathbf{A}) / C_1$.
 For all $2k$-sparse $\mathbf{x} \in \mathbb{R}^m$, the triangle inequality gives \mbox{$\|(\mathbf{A}-\mathbf{BPD})\mathbf{x}\|_2  \leq C_1\varepsilon \|\mathbf{x}\|_1 \leq C_1 \varepsilon \sqrt{2k}  \|\mathbf{x}\|_2$}.
@@
 %
-where we may drop the absolute value due to the upper bound on $\varepsilon$. Hence, $L_{2k}(\mathbf{BPD}) \geq L_{2k}(\mathbf{A}) - C_1\varepsilon  > 0$ and \eqref{b-PDa} then follows from:
+where we drop the absolute value due to the upper bound on $\varepsilon$. Hence, $L_{2k}(\mathbf{BPD}) \geq L_{2k}(\mathbf{A}) - C_1\varepsilon  > 0$ and \eqref{b-PDa} then follows from:
 \begin{align*}
@@
 %&\leq \sqrt{2k} |\mathbf{x}_i - D^{-1}P^{\top}\mathbf{\hat x}_i\|_2 \\
-&\leq \frac{\|\mathbf{BPD}(\mathbf{x}_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\hat x}_i)\|_2}{\sqrt{2k}L_{2k}(\mathbf{BPD})} \\
-&\leq \frac{\|\mathbf{B}\mathbf{\hat x}_i - \mathbf{A}\mathbf{x}_i\|_2 + \|(\mathbf{A} - \mathbf{BPD})\mathbf{x}_i\|_2}{\sqrt{2k}L_{2k}(\mathbf{BPD})} \\
-&\leq \frac{\varepsilon (1+C_1 \|\mathbf{x}_i\|_1)}{\sqrt{2k}L_{2k}(\mathbf{BPD})}.
+&\leq \frac{\|\mathbf{BPD}(\mathbf{x}_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\hat x}_i)\|_2}{L_{2k}(\mathbf{BPD})} \\
+&\leq \frac{\|\mathbf{B}\mathbf{\hat x}_i - \mathbf{A}\mathbf{x}_i\|_2 + \|(\mathbf{A} - \mathbf{BPD})\mathbf{x}_i\|_2}{L_{2k}(\mathbf{BPD})} \\
+&\leq \frac{\varepsilon (1+C_1 \|\mathbf{x}_i\|_1)}{L_{2k}(\mathbf{BPD})}.
 %&\leq \frac{\varepsilon}{\sqrt{2k}} \left( \frac{ 1+C_1 \|\mathbf{x}_i\|_1 }{ L_{2k}(\mathbf{A}) -  C_1\varepsilon } \right).
@@
 We establish \eqref{Cstable} in the first place by arguments that flow loosely as follows.
-Pigeonholing the data into its set of possible supports with respect to the matrix $\mathbf{B}$, one sees that the column space of every $\mathbf{A}_S$ with $S \in E$ must be proximal (in a sense yet to be defined; see Def.~\ref{dDef}) to the column space of some $n \times k$ submatrix of $\mathbf{B}$.
+Pigeonholing the data into its set of possible supports with respect to the matrix $\mathbf{B}$, one sees that the column space of every $\mathbf{A}_S$ with $S \in E$ must be nearby (in a sense yet to be defined; see Def.~\ref{dDef}) the column space of some $n \times k$ submatrix of $\mathbf{B}$.
 \eqref{Cstable} is then immediately implied by our result in combinatorial matrix analysis (Lem.~\ref{MainLemma}), which we derive by the following arguments (see the Supplemental for the full proof).
@@
 In fact, in the case $k=1$ we can relax our assumptions even further and assume that the matrix $\mathbf{B}$ has only at least as many columns as $\mathbf{A}$; as we will see, the conclusions of Thm.~\ref{DeterministicUniquenessTheorem} then hold for some $n \times m$ submatrix of $\mathbf{B}$.
-
-We note first that $\|\mathbf{x}\|_1 \leq \sqrt{k} \|\mathbf{x}\|_2$ for $k$-sparse $\mathbf{x} \in \mathbb{R}^m$, which implies by definition of $L_k(A)$ the following inequality which we often use:
-\begin{align}\label{delrho}
-L_k(\mathbf{A}) \leq \frac{\|\mathbf{A}\mathbf{x}\|_2}{\sqrt{k} \|\mathbf{x}\|_2} %\leq \frac{\|\mathbf{x}\|_1}{\sqrt{k} \|\mathbf{x}\|_2} \max_{i \in [m]}\|\mathbf{A}_i\|_2 
-\leq  \max_{i \in [m]}\|\mathbf{A}_i\|_2.
-\end{align}
 
@@
 \begin{align*}
-\cos{\theta(U,W)} := \max\left\{ |\langle \mathbf{u}, \mathbf{w} \rangle|: \substack{ \mathbf{u} \in U \cap (U \cap W)^\perp, \|\mathbf{u}\|_2 \leq 1 \\ \mathbf{w} \in W \cap (U \cap W)^\perp, \|\mathbf{w}\|_2 \leq 1 } \right\}.
+\cos{\theta(U,W)} := \max\left\{ |\langle \mathbf{u}, \mathbf{w} \rangle|: \substack{ \mathbf{u} \in U \cap (U \cap W)^\perp, \ \|\mathbf{u}\|_2 \leq 1 \\ \mathbf{w} \in W \cap (U \cap W)^\perp, \  \|\mathbf{w}\|_2 \leq 1 } \right\}.
 \end{align*}
@@
 
-The constant $C_2$ in Lem.~\ref{MainLemma} is then given by:\footnote{Note that $C_2 > 0$ is well-defined since $r > 0$ by definition.}
+The constant $C_2$ in Lem.~\ref{MainLemma} is then given by:  % \footnote{Note that $C_2 > 0$ is well-defined since $r > 0$ by definition.}
 \begin{align}
@@
 d(\text{Span}\{\mathbf{A}_S\}, \text{Span}\{\mathbf{B}_{S'}\}) 
-\leq \frac{\varepsilon}{ \min_{S \in E} L_k(\mathbf{AX}_{I(S)}) } 
+\leq \frac{\varepsilon}{ \min_{S \in E} L_k(\mathbf{AX}_{I(S)}) }.
 %\leq \frac{\varepsilon}{L(\mathbf{AX}_{J(S)})}.
@@
 
-In this note, we generalize the approach of \cite{Hillar15} to the uniqueness of solutions to Problem~\ref{InverseProblem} to the case of noisy measurements while also reducing the number of required samples.
+In this note, we generalize the approach of \cite{Hillar15} to the uniqueness of solutions to Problem~\ref{InverseProblem} for noisy measurements while also reducing the number of required samples.
 % from $N=k{m \choose k}^2$ to $N = m(k-1){m \choose k}+m$. 

### 2017-03-27 manuscripts/PNAS/chazthm_pnas.tex
SteamRoll page 1

@@
 \begin{abstract}
-Dictionary learning methods for sparse linear coding have exposed underlying structure in many kinds of natural signals.
-However, universal theorems guaranteeing the statistical consistency of inference in this model are lacking.
-Here, we prove that for almost all diverse enough datasets generated from the sparse coding model, latent dictionaries and sparse codes are uniquely determined up to an error commensurate with measurement noise.
+Dictionary learning for sparse linear coding has exposed underlying structure in many natural signals.
+However, there are few universal theorems guaranteeing uniqueness of model estimation independent of implementation.
+Here, we prove that for all diverse enough datasets generated from the sparse coding model, latent dictionaries and codes are uniquely determined up to measurement error.
 Applications are given to data analysis, neuroscience, and engineering.
@@
 
-\dates{This manuscript was compiled on \today}
+% \dates{This manuscript was compiled on \today}
 \doi{\url{www.pnas.org/cgi/doi/10.1073/pnas.XXXXXXXXXX}}
@@
 If this is the case, add \parshape=0 to the end of the list environment.
-\dropcap{D}ictionary learning methods for sparse coding have been under active development ever since their application to natural images brought about an exciting discovery in computational neuroscience: that simple-cell response properties emerge from efficient coding principles \cite{Olshausen96, hurri1996image, bell1997independent, van1998independent}.
-Much of the subsequent work in dictionary learning has come out of the signal processing and machine learning communities, which have found sparse representations to be a powerful tool for the manipulation of signals lacking much known analytic structure (see \cite{Zhang15} for a comprehensive review).
-This motivates the data-driven approach to inferring optimal dictionaries for a wide variety of signal classes for which, traditionally, representations have been constructed using methods of harmonic analysis (e.g., the Fourier basis, wavelets, curvelets, etc.).
-A popular formulation of the idea is to find a set of $m$ `elementary' waveforms, at most $k$ of which need be linearly combined to represent each $n$-dimensional signal in a dataset of size $N$, typically where $k < m \ll N$.
-%\dropcap{D}ictionary learning methods for sparse coding have been under active development ever since their application to natural images brought about an exciting discovery in computational neuroscience: that simple-cell response properties emerge from efficient coding principles \cite{Olshausen96, hurri1996image, bell1997independent, van1998independent}.
-Much of the subsequent work in dictionary learning has come out of the signal processing and machine learning communities, whose interest in sparse representations as a practical tool motivates the data-driven approach to inferring optimal dictionaries (see \cite{Zhang15} for a comprehensive review).
-A popular formulation of the idea is to find a set of $m$ `elementary' signals, at most $k$ of which need be linearly combined to represent each $n$-dimensional signal in a dataset of size $N$, typically where $k < m \ll N$.
+\dropcap{B}lind source identification is a classical problem in signal processing \cite{sato1975method}.  
+One popular modern formulation of the idea is to find a dictionary of $m$ elementary waveforms, at most $k$ of which need be linearly combined to represent each $n$-dimensional signal in a dataset of size $N$, typically where $k < m \ll N$.
+Approximating solutions to this problem have
+provided insight into the structure of many signals lacking explicit analytic structure (see \cite{Zhang15} for a comprehensive review). 
+In particular, it has been shown that response properties of simple-cell neurons in mammalian visual cortex emerge from learning a dictionary for sparse linear coding of natural images \cite{Olshausen96, hurri1996image, bell1997independent, van1998independent}, a major advance in computational neuroscience.
+A fundamental aspect of this finding is that the latent waveforms (``Gabors'') estimated from data appear to be canonical; i.e., they are found in learned dictionaries independent of algorithmic implementation or natural image training set.
 
-Blind source identification first started \cite{sato1975method}.
+% (e.g., Fourier bases, wavelets, etc.)
 
-We address here a question of fundamental concern to this enterprise: \emph{When are dictionaries and the sparse representations they provide uniquely determined by data?} An affirmative answer speaks also to the important question of whether or not a dictionary adapted to a finite number of samples from a signal class will generalize in its ability to represent all signals in the class; see, for instance, the method of forgery detection by analysis of local painting style proposed in \cite{hughes2010, Olshausen10}.
-Fortunately, algorithms with proven recovery of generating dictionaries under certain conditions have recently been proposed (see \cite[Sec.~I-E]{Sun16} for a summary of the state-of-the-art).
-It has remained unknown, however, when the dictionary learning problem is well-posed (as per Hadamard \cite{Hadamard1902}) in general -- that is, independent of all methodological idiosyncracies.
+Motivated by these discoveries and earlier work in the theory of neural communication \cite{Coulter10, Isely10}, we address when dictionaries and sparse representations are uniquely determined by data.
+Answers to this question also have other real-world implications.
+For example, a sparse coding analysis of local painting style can be used for forgery detection \cite{hughes2010, Olshausen10}, but only if sparse components of the artwork are independent of implementation idiosyncrasies.
+Fortunately, algorithms with proven recovery of generating dictionaries under certain
+conditions have recently been proposed (see \cite[Sec.~I-E]{Sun16} for a summary of the state-of-the-art).  However,
+there are few general theorems explaining the general phenomenon of uniqueness.
+
+Here, we prove very generally that uniqueness in sparse linear coding is an expected property of the model.
+In other words, whenever enough sparsely represented data generated from a dictionary (satisfying a spark condition) are observed, the original codes and dictionary are uniquely determined up to an error that is commensurate with the measurement noise.
+Applications of this result include:  (1) a sufficient diversity of sparse codes sent through a random linear compressive channel are unique, (2) the sparse linear coding problem is well-posed in the sense of Hadamard \cite{Hadamard1902}, and (3) an explanation for universal representation of natural signals in neuroscience.
+
+% It has remained unknown, however, when the dictionary learning problem is well-posed (as per Hadamard \cite{Hadamard1902}) in general -- that is, independent of all methodological idiosyncracies.
 %[**TODO** make sure the claim here is right...or would it be punchier to talk about the fact that everyone always gets Gabors on natural images?]
@@
 
-The main finding of this work is that for any $k < m$, every dictionary satisfying the spark condition \eqref{SparkCondition} from compressed sensing is identifiable from as few as $N = m + m(k-1){m \choose k}$ $k$-sparse linear combinations of its elements up to an error linear in the noise (Thm.~\ref{DeterministicUniquenessTheorem}).
-In fact, provided $(n, m, k)$ satisfy the nearly-optimal compressed sensing inequality \eqref{CScondition}, in almost all cases the dictionary learning problem is well-posed given enough data (Cor.~\ref{ProbabilisticCor}).
-Interestingly, these guarantees hold even without constraining the recovered matrix to satisfy the spark condition.
-Imposing this constraint does, however, allow us to state a modification of our main result that applies to the case where only an upper bound on the number of dictionary elements is known (Thm.~\ref{DeterministicUniquenessTheorem2}).
-We hope the explicit, algorithm-independent criteria we provide here may serve as a useful tool in future analyses of dictionary learning procedures.
-
-We state the problem considered here more precisely as follows.
-Fix a dictionary represented as the columns $\mathbf{A}_j$ ($j = 1,\ldots,m$) of a matrix $\mathbf{A} \in \mathbb R^{n \times m}$ and suppose a dataset $Z$ consists of measurements:
+More formally, let $\mathbf{A} \in \mathbb R^{n \times m}$ be a matrix with columns $\mathbf{A}_j$ ($j = 1,\ldots,m$) and let dataset $Z$ consist of measurements:
 \begin{align}\label{LinearModel}
@@
 for $k$-\emph{sparse} $\mathbf{x}_i \in \mathbb{R}^m$ having at most $k$ nonzero entries and \emph{noise} $\mathbf{n}_i \in \mathbb{R}^n$, with bounded norm $\| \mathbf{n}_i \|_2 \leq  \eta$ representing our combined worst-case uncertainty in  measuring $\mathbf{A}\mathbf{x}_i$.
+The precise mathematical problem addressed here is the following.
+% We address the uniqueness properties for the following linear coding question in signal processing.
 
@@
 
-Note that by formulating the problem in this way we have introduced the following ambiguity.
-Any particular solution represents a whole class of equivalent dictionaries $BPD$ and codes $D^{-1}P^{\top}\mathbf{\hat x}_i$, where $P$ is any permutation matrix and $D$ any invertible diagonal matrix.
-We therefore consider only whether solutions to Problem~\ref{InverseProblem} are unique up to this equivalence \cite{Li15}.
+Note that any particular solution $(\mathbf{B}, \mathbf{\hat x}_1 \ldots, \mathbf{\hat x}_N)$ to this problem gives rise to an orbit of other solutions $(\mathbf{BPD}, \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\hat x}_1 \ldots, \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\hat x}_N)$, where $\mathbf{P}$ is any permutation matrix and $\mathbf{D}$ any invertible diagonal.
+We therefore consider whether solutions to Problem~\ref{InverseProblem} are unique only up to this ambiguity.  More specifically, 
+we seek conditions for when sparsely coded datasets have a stable unique representation.
+
+% More specifically,  we seek sufficient conditions on when sparsely coded datasets have a stable unique representation.
+
+% We therefore consider only whether solutions to Problem~\ref{InverseProblem} are unique up to this equivalence \cite{Li15}
+
+% Note that by formulating the problem in this way we have introduced the following ambiguity.
+Any particular solution represents .
 Alternatively, one may seek a unique solution (in the usual sense) in the quotient space induced by the action of the transformation group of matrices $PD$.
 
-Previous work \cite{li2004analysis, Georgiev05, Aharon06, Hillar15} on the noiseless case $\eta = 0$ has shown that the solution (when it exists) is indeed unique in the sense described above provided the $\mathbf{x}_i$ are sufficiently diverse and the matrix $\mathbf{A}$ satisfies the \textit{spark condition}:
-\begin{align}\label{SparkCondition}
-\mathbf{A}\mathbf{x}_1 = \mathbf{A}\mathbf{x}_2 \implies \mathbf{x}_1 = \mathbf{x}_2,\indent \text{for all $k$-sparse } \mathbf{x}_1, \mathbf{x}_2.
-\end{align}
-%
-which would be, in any case, a necessary condition for uniqueness if we knew only that the $\mathbf{x}_i$ are $k$-sparse. We introduce the following terminology to handle $\eta > 0$. 
-\begin{definition}
+%  noiseless case $\eta = 0$
+
+%  We introduce the following terminology to handle $\eta > 0$. 
+\begin{definition}\label{maindef}
 Fix $Y = \{ \mathbf{y}_1, \ldots, \mathbf{y}_N\} \subset \mathbb{R}^n$.
-We say $Y$ has a \emph{$k$-sparse representation in $m$ dimensions} if there exists a matrix $\mathbf{A}$ and $k$-sparse $\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$ such that $\mathbf{y}_i = \mathbf{A}\mathbf{x}_i$ for all $i$.
+We say $Y$ has a \textbf{$k$-sparse representation in $m$ dimensions} if there exists a matrix $\mathbf{A}$ and $k$-sparse $\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$ such that $\mathbf{y}_i = \mathbf{A}\mathbf{x}_i$ for all $i$.
 %Equivalently, $\mathbf{Y} = \mathbf{A}\mathbf{X}$ for $\mathbf{Y}$ and $\mathbf{X}$ having the $\mathbf{y}_i$ and $\mathbf{x}_i$ as their columns, respectively.
-This representation is \emph{stable} if for every $\delta_1, \delta_2 \geq 0$, there exists $\varepsilon = \varepsilon(\delta_1, \delta_2) \geq 0$ (with $\varepsilon > 0$ when  $\delta_1, \delta_2 > 0$) such that if a matrix $\mathbf{B}$ and $k$-sparse $\mathbf{\hat x}_1, \ldots, \mathbf{\hat x}_N \in \mathbb{R}^m$ satisfy
+This representation is \textbf{stable} if for every $\delta_1, \delta_2 \geq 0$, there exists $\varepsilon = \varepsilon(\delta_1, \delta_2) \geq 0$ (with $\varepsilon > 0$ when  $\delta_1, \delta_2 > 0$) such that if a matrix $\mathbf{B}$ and $k$-sparse $\mathbf{\hat x}_1, \ldots, \mathbf{\hat x}_N \in \mathbb{R}^m$ satisfy:
 \begin{align*}
-\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\hat x}_i\|_2 \leq \varepsilon \ \ \text{for all $i$}
+\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\hat x}_i\|_2 \leq \varepsilon, \ \ \text{for all $i$},
 \end{align*}
@@
 
-We ask here: \emph{When does $Y$ have a stable $k$-sparse representation in $m$ dimensions?} To see how an answer to this question informs the interpretation of solutions to Problem \ref{InverseProblem}, suppose that \mbox{$Y = \{\mathbf{A} \mathbf{x}_1, \ldots, \mathbf{A}\mathbf{x}_N\}$} has a stable $k$-sparse representation in $m$ dimensions and fix $\delta_1, \delta_2$ to be the desired accuracy in recovery \eqref{def1}.
-Consider now any dataset $Z$ generated as in \eqref{LinearModel} that has $\eta \leq \frac{1}{2} \varepsilon(\delta_1, \delta_2)$.
+To see how Definition \ref{maindef} directly relates to Problem \ref{InverseProblem}, suppose that $Y$
+% \mbox{$Y = \{\mathbf{A} \mathbf{x}_1, \ldots, \mathbf{A}\mathbf{x}_N\}$} 
+has a stable $k$-sparse representation in $m$ dimensions and fix $\delta_1, \delta_2$ to be the desired accuracy in \eqref{def1}.
+Consider now any dataset $Z$ generated as in \eqref{LinearModel} with $\eta \leq \frac{1}{2} \varepsilon(\delta_1, \delta_2)$.
 Then, any dictionary $\mathbf{B}$ and $k$-sparse $\mathbf{\hat x}_1, \ldots, \mathbf{\hat x}_N$ solving Problem \ref{InverseProblem} are necessarily close to the original matrix $\mathbf{A}$ and codes $\mathbf{x}_i$ (i.e., satisfy \eqref{def1}).
-Our results, outlined in Sec.~\ref{Results}, include an explicit form for $\varepsilon(\delta_1, \delta_2)$ in Thm.~\ref{DeterministicUniquenessTheorem}.
+
+%Our results, outlined in Sec.~\ref{Results}, include an explicit form for $\varepsilon(\delta_1, \delta_2)$ in Thm.~\ref{DeterministicUniquenessTheorem}.
+
+% We ask here: \emph{When does $Y$ have a stable $k$-sparse representation?}
+
+Previous theoretical work on Problem \ref{InverseProblem} for the noiseless case $\eta =0$ (e.g., \cite{li2004analysis, Georgiev05, Aharon06, Hillar15}) has shown that a solution (when it exists) is indeed unique provided the $\mathbf{x}_i$ are sufficiently diverse and the generating matrix $\mathbf{A}$ satisfies the \textit{spark condition} from compressed sensing (CS):
+\begin{align}\label{SparkCondition}
+\mathbf{A}\mathbf{x}_1 = \mathbf{A}\mathbf{x}_2 \implies \mathbf{x}_1 = \mathbf{x}_2, \ \ \ \text{for all $k$-sparse } \mathbf{x}_1, \mathbf{x}_2,
+\end{align}
+%
+which would be, in any case, a necessary condition for uniqueness if it were known only that $\mathbf{x}_i$ are $k$-sparse.
+
+Our main technical finding is that a sufficient diversity of measurements generated from any dictionary satisfying the spark condition 
+has a stable sparse representation.
+More specifically, such dictionaries are uniquely identifiable from as few as \mbox{$N = m + m(k-1){m \choose k}$} sparse linear combinations of its columns up to an error that is linear in the measurement noise (Thm.~\ref{DeterministicUniquenessTheorem}).
+In fact, provided $(n, m, k)$ satisfy the CS inequality \eqref{CScondition}, in almost all cases the dictionary learning problem is well-posed given enough data (Cor.~\ref{ProbabilisticCor}).
+Importantly, these guarantees hold without assuming the recovered matrix satisfies the spark condition.
+Our results  also apply when only an upper bound on the number of dictionary elements is known (Thm.~\ref{DeterministicUniquenessTheorem2}).
+We hope the explicit, algorithm-independent criteria we provide here are useful tools in future analyses of dictionary learning.
 
@@
 We then prove our main theorem (Thm.~\ref{DeterministicUniquenessTheorem}) in Sec.~\ref{DUT} while stating some additional definitions and lemmas required for the proof, including our main tool from combinatorial matrix analysis (Lem.~\ref{MainLemma}).
-Our proof is a refinement of the arguments in \cite{Hillar15} to handle noise and to reduce the sufficient number of samples for all $k < m$ from $N=k{m \choose k}^2$ to $N = m + m(k-1){m \choose k}$.
 All other proofs are relegated to the Supplemental.
+Our approach is a refinement of the one found in \cite{Hillar15} to handle noise and to reduce the sufficient number of samples.
+%for all $k < m$ from $N=k{m \choose k}^2$ to $N = m + m(k-1){m \choose k}$. 
 Finally, several applications are considered in our discussion, Sec.~\ref{Discussion}.
@@
 \begin{align*}
-f(\mathbf{A}) = \prod_{S \in {[m] \choose k}} \sum_{S' \in {[n] \choose k}} (\det \mathbf{A}_{S',S})^2,
+f(\mathbf{A}) := \prod_{S \in {[m] \choose k}} \sum_{S' \in {[n] \choose k}} (\det \mathbf{A}_{S',S})^2,
 \end{align*}
@@
 where for any $S' \in {[n] \choose k}$ and $S \in {[m] \choose k}$, the symbol $\mathbf{A}_{S',S}$ denotes the submatrix of entries $A_{ij}$ with $(i,j) \in S' \times S$.
+We note that the large number of terms in this product is likely necessary due to the NP-hardness of deciding whether $A$ satisfies a given spark condition \cite{tillmann2014computational}.
 
@@
 
+Phrased 
+in the language of Hadamard \cite{Hadamard1902}),
+
 In this note, we generalize the approach of \cite{Hillar15} to the uniqueness of solutions to Problem~\ref{InverseProblem} for noisy measurements while also reducing the number of required samples.
@@
 Furthermore, our guarantees justify the hypothesis of \cite{Coulter10} and \cite{Isely10} that sparse codes passed through a communication bottleneck in the brain can be recovered from random projections via (unsupervised) biologically plausible sparse dictionary learning (e.g., \cite{rehnsommer2007, rozell2007neurally, hu2014hebbian}).
+
+Invariance in neuroscience: Pitts \cite{pitts1947}.
 %TODO: add reproduction of response propeties in olfactory cortex?

### 2017-03-27 manuscripts/PNAS/chazthm_pnas.tex
more SR up to page 2

@@
 %
-which would be, in any case, a necessary condition for uniqueness if it were known only that $\mathbf{x}_i$ are $k$-sparse.
+which would be, in any case, necessary for uniqueness.
 
@@
 has a stable sparse representation.
-More specifically, such dictionaries are uniquely identifiable from as few as \mbox{$N = m + m(k-1){m \choose k}$} sparse linear combinations of its columns up to an error that is linear in the measurement noise (Thm.~\ref{DeterministicUniquenessTheorem}).
-In fact, provided $(n, m, k)$ satisfy the CS inequality \eqref{CScondition}, in almost all cases the dictionary learning problem is well-posed given enough data (Cor.~\ref{ProbabilisticCor}).
+More specifically, such dictionaries are uniquely identifiable from as few as \mbox{$N = m + m(k-1){m \choose k}$} sparse linear combinations of their columns up to an error that is linear in the measurement noise (Thm.~\ref{DeterministicUniquenessTheorem}).
+In fact, provided $(n, m, k)$ satisfy CS inequality \eqref{CScondition}, in almost all cases the dictionary learning problem is well-posed given enough data (Cor.~\ref{ProbabilisticCor}).
 Importantly, these guarantees hold without assuming the recovered matrix satisfies the spark condition.
-Our results  also apply when only an upper bound on the number of dictionary elements is known (Thm.~\ref{DeterministicUniquenessTheorem2}).
-We hope the explicit, algorithm-independent criteria we provide here are useful tools in future analyses of dictionary learning.
+Our results  also apply when only an upper bound on the number of dictionary elements is known.
+The explicit, algorithm-independent criteria we provide should be a useful tool in the theory of sparse dictionary learning.
+% (Thm.~\ref{DeterministicUniquenessTheorem2})
 
 In the next section, we give precise statements of our main results, which include an explicit form for $\varepsilon(\delta_1, \delta_2)$.
-We then prove our main theorem (Thm.~\ref{DeterministicUniquenessTheorem}) in Sec.~\ref{DUT} while stating some additional definitions and lemmas required for the proof, including our main tool from combinatorial matrix analysis (Lem.~\ref{MainLemma}).
+We then prove our main theorem (Thm.~\ref{DeterministicUniquenessTheorem}) in Sec.~\ref{DUT} after stating some additional definitions and lemmas required for the proof, including our main tool from combinatorial matrix analysis (Lem.~\ref{MainLemma}).
 All other proofs are relegated to the Supplemental.
@@
 Before stating our main results, we explain how the spark condition \eqref{SparkCondition} relates to the \emph{lower bound} \cite{Grcar10} of $\mathbf{A}$, which is the largest number $\alpha$ such that \mbox{$\|\mathbf{A}\mathbf{x}\|_2 \geq \alpha\|\mathbf{x}\|_2$} for all $\mathbf{x} \in \mathbb{R}^m$.
-By compactness, every injective linear map has a nonzero lower bound; hence, if $\mathbf{A}$ satisfies \eqref{SparkCondition}, then every submatrix formed from $2k$ of its columns or less has a nonzero lower bound.
+By compactness of the unit sphere, every injective linear map has a nonzero lower bound; hence, if $\mathbf{A}$ satisfies \eqref{SparkCondition}, then each submatrix formed from $2k$ of its columns or less has a nonzero lower bound.
 We therefore define the following domain-restricted lower bound of $\mathbf{A}$:
@@
 \end{align*} 
-Clearly, $L_k(\mathbf{A}) \geq L_{k'}(\mathbf{A})$ whenever $k < k'$, and for any $\mathbf{A}$ satisfying \eqref{SparkCondition}, we have $L_{k'}(\mathbf{A}) > 0$ for all $k' \leq 2k$.
-Note that subtracting $L_k(\mathbf{A})$ from one yields what is known in the compressed sensing literature as the (asymmetric) lower restricted isometry constant \cite{Blanchard2011, Foucart2009}.
+Clearly, $L_k(\mathbf{A}) \geq L_{k'}(\mathbf{A})$ whenever $k < k'$, and for any $\mathbf{A}$ satisfying the spark condition, we have $L_{k'}(\mathbf{A}) > 0$ for all $k' \leq 2k$.
+Note that subtracting $\sqrt{k} L_k(\mathbf{A})$ [*** TODO: check is this correct ***] from one yields what is known in the compressed sensing literature as the (asymmetric) lower restricted isometry constant \cite{Blanchard2011, Foucart2009}.
 
-We let $[m]$ denote the set $\{1, \ldots, m\}$ and $2^{[m]}$ ts power set, and we write ${[m] \choose k}$ to denote the set of subsets of $[m]$ of size $k$.
+An important contribution of our work is to identify combinatorial criteria on the support sets of generating codes that allow for stable sparse 
+representations.
+Let $[m]$ denote the set $\{1, \ldots, m\}$, $2^{[m]}$ its power set, and ${[m] \choose k}$ the set of subsets of $[m]$ of size $k$.
 Let $\text{Span}\{\mathbf{v}_1, \ldots, \mathbf{v}_\ell\}$ be the $\mathbb{R}$-linear span of vectors $\mathbf{v}_1, \ldots, \mathbf{v}_\ell$.
@@
 We interpret $\text{Span}\{\mathbf{M}_\emptyset\} = \{\textbf{0}\}$, where $\emptyset$ is the empty set.
-We say a set system $E \subseteq 2^{[m]}$ is of rank $k$ when $|S| \leq k$ for every $S \in E$ (and $k$-uniform when equality holds).
+We say a hypergraph $E \subseteq 2^{[m]}$ is of rank $k$ when $|S| \leq k$ for every $S \in E$ (and $k$-uniform when equality holds).
 We say $E$ is \emph{regular} when every element of $[m]$ is contained in exactly $\ell$ elements of $E$ for some $\ell > 0$ (for given $\ell$, we say $E$ is $\ell$-regular).
@@
 \begin{definition}
-Given a set system $E \subseteq 2^{[m]}$, the \emph{star} $F(i)$ centered at $i$ is the set of $S \in E$ containing $i$.
-We say $E$ satisfies the \emph{singleton intersection property} when $\cap_{S \in F(i)} S = \{i\}$ for all $i \in [m]$.
+Given a hypergraph $E \subseteq 2^{[m]}$, the \textbf{star} $F(i)$ centered at $i$ is the set of $S \in E$ containing $i$.
+We say $E$ satisfies the \textbf{singleton intersection property} (SIP) when $\cap_{S \in F(i)} S = \{i\}$ for all $i \in [m]$.
 \end{definition}
@@
 \begin{proposition}
-For every $k < m$, there is a regular $k$-uniform set system that satisfies the singleton intersection property.
+For every $k < m$, there is a regular $k$-uniform hypergraph that satisfies the singleton intersection property.
 \end{proposition}
@@
 
-The following result gives an elaborated answer to our question from the introduction.
 Recall that a set of $k$-sparse vectors is in \emph{general linear position} when any $k$ of them are linearly independent.
+The following is the technical statement of our main result.
 
-[State this without reference to special set $E$]
+[*** TODO: Combine with Theorem 3 ***]
 \begin{theorem}\label{DeterministicUniquenessTheorem}
-Fix integers $n$ and $k < m$.
-Suppose $\mathbf{A}~\in~\mathbb{R}^{n \times m}$ satisfies \eqref{SparkCondition} and that \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} include at least \mbox{$(k-1){m \choose k}+1$} vectors in general linear position supported on each set in some regular $E \subseteq {[m] \choose k}$ satisfying the singleton intersection property.
+Fix integers $1 \leq p \leq m$, $n$, and $k < m \leq m' \leq \frac{\ell m - (p-1)}{\ell - 1}$.
+Suppose $\mathbf{A}~\in~\mathbb{R}^{n \times m}$ satisfies \eqref{SparkCondition} and that \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} include at least \mbox{$(k-1){m \choose k}+1$} vectors in general linear position supported on each set in some $\ell$-regular $E \subseteq {[m] \choose k}$ satisfying the SIP.
 Then there exists a constant $C_1 > 0$ for which the following holds for all $\varepsilon < L_2(\mathbf{A}) / C_1$.
@@
 %
-for some permutation matrix $\mathbf{P}$ and invertible diagonal matrix $\mathbf{D}$.\footnote{We note that the condition $\varepsilon < L_2(\mathbf{A})$ above is necessary.
+for some permutation matrix $\mathbf{P}$ and invertible diagonal matrix $\mathbf{D}$.
+%\footnote{We note that the condition $\varepsilon < L_2(\mathbf{A})$ above is necessary.
 When \mbox{$\mathbf{A}$ = $I$} and $\mathbf{x}_i = \mathbf{e}_i$, it turns out that $C_1 = 1$ and there is a $\mathbf{B}$ and $1$-sparse $\mathbf{\hat x}_i$ with $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\hat x}_i\|_2 \leq \varepsilon$ violating \eqref{Cstable}.}
@@
 
-An important consequence of Thm.~\ref{DeterministicUniquenessTheorem} is that \eqref{def1} is guaranteed provided $\varepsilon$ does not exceed:
+An important consequence of Thm.~\ref{DeterministicUniquenessTheorem} is that \eqref{def1} is guaranteed provided $\varepsilon$ does not exceed: [*** TODO: verify this is still correct ***]
 \begin{align}\label{epsdel}
@@
 
-Note also that Thm~\ref{DeterminsiticUniquenessTheorem} gives conditions for when a single solution to Problem~\ref{InverseProblem} in fact represents \emph{all} possible solutions, related by transformations of the form $PD$.
+% Note also that Thm~\ref{DeterminsiticUniquenessTheorem} gives conditions for when a single solution to Problem~\ref{InverseProblem} in fact represents \emph{all} possible solutions, related by transformations of the form $PD$.
 
 \begin{corollary}\label{DeterministicUniquenessCorollary}
-Given $n, m$, $k < m$ and a regular set system $E \subseteq 2^{[m]}$ of rank $k$ satisfying the singleton intersection property, there are $N =  |E| \left[ (k-1){m \choose k}+1 \right]$ vectors \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} such that every matrix $\mathbf{A} \in \mathbb{R}^{n \times m}$ satisfying \eqref{SparkCondition} generates a set $Y = \{\mathbf{A}\mathbf{x}_1, \ldots, \mathbf{A}\mathbf{x}_N\}$ with a stable $k$-sparse representation in $m$ dimensions.
+Given $n, m$, $k < m$ and a regular hypergraph $E \subseteq 2^{[m]}$ of rank $k$ satisfying the singleton intersection property, there are $N =  |E| \left[ (k-1){m \choose k}+1 \right]$ vectors \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} such that every matrix $\mathbf{A} \in \mathbb{R}^{n \times m}$ satisfying \eqref{SparkCondition} generates a dataset $Y = \{\mathbf{A}\mathbf{x}_1, \ldots, \mathbf{A}\mathbf{x}_N\}$ with a stable $k$-sparse representation in $m$ dimensions.
 \end{corollary}
@@
 %\begin{proposition}
-%If $E$ is an $\ell$-regular set system of rank $k$ satisfying the singleton intersection property then $|E| \geq \ell m/k$. 
+%If $E$ is an $\ell$-regular hypergraph of rank $k$ satisfying the singleton intersection property then $|E| \geq \ell m/k$. 
 %\end{proposition}
-Note that if $E$ is an $\ell$-regular set system of rank $k$ satisfying the singleton intersection property then $|E| \geq \ell m/k$.
+Note that if $E$ is an $\ell$-regular hypergraph of rank $k$ satisfying the singleton intersection property then $|E| \geq \ell m/k$.
 This is easy to see by noting that $|E|k \geq \sum_{S \in E}|S| = \sum_{i \in [m]} \deg(i) = \ell m$.
@@
 It is straightforward to provide a probabilistic extension of Thm.~\ref{DeterministicUniquenessTheorem} using the following fact in random matrix theory.
-The matrix $\mathbf{A} \in \mathbb{R}^{n \times m}$ satisfies \eqref{SparkCondition} with probability one (or with ``high probability" for discrete variables)
+The matrix $\mathbf{A} \in \mathbb{R}^{n \times m}$ satisfies \eqref{SparkCondition} with probability one (or with ``high probability'' for discrete variables)
 provided:
@@
 %
-where $\gamma$ is a positive constant dependent on the particular distribution from which the entries of $\mathbf{A}$ are sampled i.i.d. (many ensembles suffice, e.g. \cite[Sec.~4]{Baraniuk08}).
+where $\gamma$ is a positive constant that depends on the particular distribution from which the entries of $\mathbf{A}$ are sampled i.i.d. (many ensembles suffice, e.g. \cite[Sec.~4]{Baraniuk08}).
 
@@
 Let $\mathbf{A}$  be the $n \times m$ matrix of $nm$ indeterminates $A_{ij}$.
-When real numbers are substituted for all the $A_{ij}$, the resulting matrix satisfies \eqref{SparkCondition} if and only if the following polynomial is nonzero:
+When real numbers are substituted for $A_{ij}$, the resulting matrix satisfies \eqref{SparkCondition} if and only if the following polynomial is nonzero:
 \begin{align*}
@@
 where for any $S' \in {[n] \choose k}$ and $S \in {[m] \choose k}$, the symbol $\mathbf{A}_{S',S}$ denotes the submatrix of entries $A_{ij}$ with $(i,j) \in S' \times S$.
-We note that the large number of terms in this product is likely necessary due to the NP-hardness of deciding whether $A$ satisfies a given spark condition \cite{tillmann2014computational}.
+We note that the large number of terms in this product is likely necessary due to the NP-hardness of deciding whether a given matrix $A$ satisfies the spark condition \cite{tillmann2014computational}.
 
-Since $f$ is a real analytic function, it is enough to show that at least \emph{one} substitution of real numbers satisfies $f(\mathbf{A}) \neq 0$ to conclude that its zeroes form a set with measure zero.
-Hence, \emph{every} $n \times m$ matrix $\mathbf{A}$ outside such a set satisfies \eqref{SparkCondition} provided \eqref{CScondition} holds for a value of $\gamma$ for \emph{some} distribution.
-We remark that the precise relationship between $m$, $n$, and $k$ guaranteeing that $f$ is not identically zero is still an open problem in real algebraic geometry [**TODO** cite recent work?].
+Since $f$ is a real analytic function, it is enough to show that at least one substitution of real numbers satisfies $f(\mathbf{A}) \neq 0$ to conclude that its zeroes form a set with measure zero.
+Hence, almost every $n \times m$ real matrix $\mathbf{A}$ satisfies \eqref{SparkCondition} provided \eqref{CScondition} holds for a value of $\gamma$ for some distribution.
+We remark that the precise relationship between $m$, $n$, and $k$ guaranteeing that $f$ is not identically zero is a challenging problem in real algebraic geometry.
 In any case, we set $\gamma_0$ to be the smallest known such $\gamma$.
@@
 It so happens that a similar statement applies to sets of vectors with a stable sparse representation.
-As in \cite[Sec.~IV]{Hillar15}, consider the ``symbolic" dataset $Y = \{\mathbf{A}\mathbf{x}_1,\ldots,\mathbf{A} \mathbf{x}_N\}$ generated by indeterminate $\mathbf{A}$ and $k$-sparse $\mathbf{x}_1, \ldots, \mathbf{x}_N$.
+As in \cite[Sec.~IV]{Hillar15}, consider the ``symbolic'' dataset $Y = \{\mathbf{A}\mathbf{x}_1,\ldots,\mathbf{A} \mathbf{x}_N\}$ generated by indeterminate $\mathbf{A}$ and $k$-sparse $\mathbf{x}_1, \ldots, \mathbf{x}_N$.
 
@@
 \begin{proof}[Proof ($k=1$)]
-Note that the only 1-uniform set system satisfying the singleton intersection property is $[m]$; hence, we have $\mathbf{x}_i = c_i \mathbf{e}_i$ for $c_i \in \mathbb{R} \setminus \{\mathbf{0}\}$, $i \in [m]$.
+Note that the only 1-uniform hypergraph satisfying the singleton intersection property is $[m]$; hence, we have $\mathbf{x}_i = c_i \mathbf{e}_i$ for $c_i \in \mathbb{R} \setminus \{\mathbf{0}\}$, $i \in [m]$.
 In this case we may take $C_1$ to be any value satisfying $C_1^{-1} \leq \min_{j \in [m]} |c_{j}|$.

### 2017-03-27 manuscripts/PNAS/chazthm_pnas.tex
chaz

--- 2017-03-23 manuscripts/PNAS/chazthm_pnas.tex
@@
 % Please include corresponding author, author contribution and author declaration information
+\authorcontributions{C.G. proved Theorem 1. C.H. proved Theorem 2.}
 \authordeclaration{The authors declare no conflict of interest.}
 %\equalauthors{\textsuperscript{1}C.G. proved Theorem 1 and C.H. proved Theorem 2.}
-\correspondingauthor{\textsuperscript{1}To whom correspondence should be addressed. E-mail: cjg@berkeley.edu, chillar@msri.org}
+\correspondingauthor{\textsuperscript{1}To whom correspondence should be addressed. E-mail: cjg@berkeley.edu, cav@mac.com}
 
 % Keywords are not mandatory, but authors are strongly encouraged to provide them. If provided, please include two to five keywords, separated by the pipe symbol, e.g:
-\keywords{Sparse linear coding, dictionary learning, compressed sensing}
+\keywords{Keyword 1 $|$ Keyword 2 $|$ Keyword 3 $|$ ...}
 
 \begin{abstract}
-Dictionary learning methods for sparse linear coding have exposed underlying structure in many kinds of natural signals.
+Dictionary learning methods for sparse coding have exposed underlying structure in many kinds of natural signals.
 However, universal theorems guaranteeing the statistical consistency of inference in this model are lacking.
@@
 Much of the subsequent work in dictionary learning has come out of the signal processing and machine learning communities, which have found sparse representations to be a powerful tool for the manipulation of signals lacking much known analytic structure (see \cite{Zhang15} for a comprehensive review).
-This motivates the data-driven approach to inferring optimal dictionaries for a wide variety of signal classes for which, traditionally, representations have been constructed using methods of harmonic analysis (e.g., the Fourier basis, wavelets, curvelets, etc.).
+This motivates the data-driven approach to inferring optimal dictionaries for a wide variety of signal classes for which, traditionally, representations have been constructed using methods of harmonic analysis (e.g.
+the Fourier basis, wavelets, curvelets, etc.).
 A popular formulation of the idea is to find a set of $m$ `elementary' waveforms, at most $k$ of which need be linearly combined to represent each $n$-dimensional signal in a dataset of size $N$, typically where $k < m \ll N$.
@@
 A popular formulation of the idea is to find a set of $m$ `elementary' signals, at most $k$ of which need be linearly combined to represent each $n$-dimensional signal in a dataset of size $N$, typically where $k < m \ll N$.
-
-Blind source identification first started \cite{sato1975method}.
 
@@
 
-The main finding of this work is that for any $k < m$, every dictionary satisfying the spark condition \eqref{SparkCondition} from compressed sensing is identifiable from as few as $N = m + m(k-1){m \choose k}$ $k$-sparse linear combinations of its elements up to an error linear in the noise (Thm.~\ref{DeterministicUniquenessTheorem}).
-In fact, provided $(n, m, k)$ satisfy the nearly-optimal compressed sensing inequality \eqref{CScondition}, in almost all cases the dictionary learning problem is well-posed given enough data (Cor.~\ref{ProbabilisticCor}).
+The main finding of this work is that for any $k < m$, every dictionary satisfying the spark condition \eqref{SparkCondition} from compressive sensing is identifiable from as few as $N = m + m(k-1){m \choose k}$ sparse linear combinations of its elements up to an error linear in the noise (Thm.~\ref{DeterministicUniquenessTheorem}).
+In fact, provided $(n, m, k)$ satisfy the nearly-optimal compressive sensing inequality \eqref{CScondition}, in almost all cases the dictionary learning problem is well-posed given enough data (Cor.~\ref{ProbabilisticCor}).
 Interestingly, these guarantees hold even without constraining the recovered matrix to satisfy the spark condition.
@@
 We state the problem considered here more precisely as follows.
-Fix a dictionary represented as the columns $\mathbf{A}_j$ ($j = 1,\ldots,m$) of a matrix $\mathbf{A} \in \mathbb R^{n \times m}$ and suppose a dataset $Z$ consists of measurements:
+Fix a dictionary represented as the columns $\mathbf{A}_j$ of a matrix $\mathbf{A} \in \mathbb R^{n \times m}$ and suppose a dataset $Z$ consists of measurements:
 \begin{align}\label{LinearModel}
@@
 
-\begin{problem}[Sparse linear coding]\label{InverseProblem}
+\begin{problem}[Sparse Linear Coding]\label{InverseProblem}
 Find a matrix $\mathbf{B}$ and $k$-sparse $\mathbf{\hat x}_1, \ldots, \mathbf{\hat x}_N \in \mathbb{R}^m$ such that $\|\mathbf{z}_i - \mathbf{B}\mathbf{\hat x}_i\|_2 \leq \eta$ for all $i$.
@@
 %
-which would be, in any case, a necessary condition for uniqueness if we knew only that the $\mathbf{x}_i$ are $k$-sparse. We introduce the following terminology to handle $\eta > 0$. 
+which would be a necessary condition for uniqueness if we knew only that the $\mathbf{x}_i$ are $k$-sparse. We introduce the following terminology to handle $\eta > 0$. 
 \begin{definition}
@@
 %
-then there is some permutation matrix $\mathbf{P}$ and invertible diagonal matrix $\mathbf{D}$ such that for all $i, j$:
+then there is some permutation matrix $\mathbf{P}$ and invertible diagonal matrix $\mathbf{D}$ such that for all $i = 1,\ldots,N$ and $j = 1,\ldots,m$:
 \begin{align}\label{def1}
@@
 Our proof is a refinement of the arguments in \cite{Hillar15} to handle noise and to reduce the sufficient number of samples for all $k < m$ from $N=k{m \choose k}^2$ to $N = m + m(k-1){m \choose k}$.
-All other proofs are relegated to the Supplemental.
+All other proofs are relegated to the Appendix.
 Finally, several applications are considered in our discussion, Sec.~\ref{Discussion}.
@@
 
-Before stating our main results, we explain how the spark condition \eqref{SparkCondition} relates to the \emph{lower bound} \cite{Grcar10} of $\mathbf{A}$, which is the largest number $\alpha$ such that \mbox{$\|\mathbf{A}\mathbf{x}\|_2 \geq \alpha\|\mathbf{x}\|_2$} for all $\mathbf{x} \in \mathbb{R}^m$.
+Before stating our results, we explain how the spark condition \eqref{SparkCondition} relates to the \emph{lower bound} \cite{Grcar10} of $\mathbf{A}$, written $L(\mathbf{A})$, which is the largest number $\alpha$ such that \mbox{$\|\mathbf{A}\mathbf{x}\|_2 \geq \alpha\|\mathbf{x}\|_2$} for all $\mathbf{x} \in \mathbb{R}^m$.
 By compactness, every injective linear map has a nonzero lower bound; hence, if $\mathbf{A}$ satisfies \eqref{SparkCondition}, then every submatrix formed from $2k$ of its columns or less has a nonzero lower bound.
@@
 Clearly, $L_k(\mathbf{A}) \geq L_{k'}(\mathbf{A})$ whenever $k < k'$, and for any $\mathbf{A}$ satisfying \eqref{SparkCondition}, we have $L_{k'}(\mathbf{A}) > 0$ for all $k' \leq 2k$.
-Note that subtracting $L_k(\mathbf{A})$ from one yields what is known in the compressed sensing literature as the (asymmetric) lower restricted isometry constant \cite{Blanchard2011, Foucart2009}.
+Note that subtracting $L_k(\mathbf{A})$ from one yields what is known in the compressive sensing literature as the (asymmetric) lower restricted isometry constant \cite{Blanchard2011, Foucart2009}.
 
-We let $[m]$ denote the set $\{1, \ldots, m\}$ and $2^{[m]}$ ts power set, and we write ${[m] \choose k}$ to denote the set of subsets of $[m]$ of size $k$.
+We let $[m]$ denote the set $\{1, \ldots, m\}$, let $2^{[m]}$ denote its power set, and write ${[m] \choose k}$ to denote the set of subsets of $[m]$ of size $k$.
 Let $\text{Span}\{\mathbf{v}_1, \ldots, \mathbf{v}_\ell\}$ be the $\mathbb{R}$-linear span of vectors $\mathbf{v}_1, \ldots, \mathbf{v}_\ell$.
@@
 
-[State this without reference to special set $E$]
 \begin{theorem}\label{DeterministicUniquenessTheorem}
@@
 for some permutation matrix $\mathbf{P}$ and invertible diagonal matrix $\mathbf{D}$.\footnote{We note that the condition $\varepsilon < L_2(\mathbf{A})$ above is necessary.
-When \mbox{$\mathbf{A}$ = $I$} and $\mathbf{x}_i = \mathbf{e}_i$, it turns out that $C_1 = 1$ and there is a $\mathbf{B}$ and $1$-sparse $\mathbf{\hat x}_i$ with $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\hat x}_i\|_2 \leq \varepsilon$ violating \eqref{Cstable}.}
+When \mbox{$\mathbf{A}$ = $I$} and $\mathbf{x}_i = \mathbf{e}_i$ it turns out that $C_1 = 1$ and there is a $\mathbf{B}$ and $1$-sparse $\mathbf{\hat x}_i$ with $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\hat x}_i\|_2 \leq \varepsilon$ violating \eqref{Cstable}.}
 Furthermore if $\varepsilon < L_{2k}(\mathbf{A}) / C_1$ then $\mathbf{B}$ also satisfies \eqref{SparkCondition} with $L_{2k}(\mathbf{B}\mathbf{PD}) \geq L_{2k}(\mathbf{A}) - C_1 \varepsilon$ and we in fact have:
 \begin{align}\label{b-PDa}
-\|\mathbf{x}_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\hat x}_i\|_1 &\leq  \left( \frac{ 1+C_1 \|\mathbf{x}_i\|_1 }{ L_{2k}(\mathbf{A}) -  C_1\varepsilon } \right) \varepsilon,
+\|\mathbf{x}_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\hat x}_i\|_1 &\leq \frac{\varepsilon}{\sqrt{2k}} \left( \frac{ 1+C_1 \|\mathbf{x}_i\|_1 }{ L_{2k}(\mathbf{A}) -  C_1\varepsilon } \right).
  \ \ \text{for all $i \in [N]$}.
@@
 
-For clarity of exposition, we delay explicitly defining the (effective) constant $C_1 = C_1(\mathbf{A}, \{\mathbf{x}_i\}_{i=1}^N, E)$ until Section \ref{DUT} (\eqref{Cdef}), since it requires additional definitions not critical to the statement of our results.
+For clarity of exposition, we delay explicitly defining the constant $C_1 = C_1(\mathbf{A}, \{\mathbf{x}_i\}_{i=1}^N, E)$ until Section \ref{DUT} (\eqref{Cdef}), since it requires additional definitions not critical to the statement of our results.
 
@@
 
-%\begin{proposition}
-%If $E$ is an $\ell$-regular set system of rank $k$ satisfying the singleton intersection property then $|E| \geq \ell m/k$. 
-%\end{proposition}
-Note that if $E$ is an $\ell$-regular set system of rank $k$ satisfying the singleton intersection property then $|E| \geq \ell m/k$.
+\begin{proposition}
+If $E$ is an $\ell$-regular set system of rank $k$ satisfying the singleton intersection property then $|E| \geq \ell m/k$. 
+\end{proposition}
 This is easy to see by noting that $|E|k \geq \sum_{S \in E}|S| = \sum_{i \in [m]} \deg(i) = \ell m$.
@@
 Since $f$ is a real analytic function, it is enough to show that at least \emph{one} substitution of real numbers satisfies $f(\mathbf{A}) \neq 0$ to conclude that its zeroes form a set with measure zero.
-Hence, \emph{every} $n \times m$ matrix $\mathbf{A}$ outside such a set satisfies \eqref{SparkCondition} provided \eqref{CScondition} holds for a value of $\gamma$ for \emph{some} distribution.
+Hence, \emph{every} $n \times m$ matrix $\mathbf{A}$ outside a set of measure zero satisfies \eqref{SparkCondition} provided \eqref{CScondition} holds for a value of $\gamma$ for \emph{some} distribution.
 We remark that the precise relationship between $m$, $n$, and $k$ guaranteeing that $f$ is not identically zero is still an open problem in real algebraic geometry [**TODO** cite recent work?].
@@
 Fix integers $n$ and $k < m \leq m'$ and matrices $\mathbf{A}~\in~\mathbb{R}^{n \times m}$ and $\mathbf{B} \in \mathbb{R}^{n \times m'}$ both satisfying \eqref{SparkCondition}.
-Suppose \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} include at least \mbox{$(k-1){m' \choose k}+1$} $k$-sparse vectors in general linear position supported on each set in some $k$-uniform $E \subseteq 2^{[m]}$ satisfying the singleton intersection property.
+Suppose \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} include at least \mbox{$(k-1){m' \choose k}+1$} vectors in general linear position supported on each set in some $k$-uniform $E \subseteq 2^{[m]}$ satisfying the singleton intersection property.
 Then there exists a constant $C_3 > 0$ for which the following holds.
@@
 %
-for some $J \in {[m'] \choose m}$, permutation matrix $\mathbf{P}$, and invertible diagonal matrix $\mathbf{D}$.
+for some $J \in {[m'] \choose m}$, permutation matrix $\mathbf{P}$ and invertible diagonal matrix $\mathbf{D}$.
 \end{theorem}
@@
 The constant $C_3$ here is expression (\ref{Cdef2}) from the proof of Thm.~\ref{DeterministicUniquenessTheorem2}.
-Note that, in contrast to Thm.~\ref{DeterministicUniquenessTheorem}, this constant is dependent on $\mathbf{B}$; hence, \eqref{Cstablem'} holds for \emph{all} matrices $\mathbf{B} \in \mathbb{R}^{n \times m'}$ satisfying the spark condition only in the case $\varepsilon = 0$.
+Note that, in contrast to Thm.~\ref{DeterministicUniquenessTheorem}, this constant is is dependent on $\mathbf{B}$; hence \eqref{Cstablem'} holds for \emph{all} matrices $\mathbf{B} \in \mathbb{R}^{n \times m'}$ satisfying the spark condition only in the case $\varepsilon = 0$.
 
@@
 % ======== b - PDa =========
-First note that $\|\mathbf{x}\|_1 \leq \sqrt{k} \|\mathbf{x}\|_2$ for $k$-sparse $\mathbf{x} \in \mathbb{R}^m$, which by definition of $L_k(A)$ implies the following often used inequality:
-\begin{align}\label{delrho}
-L_k(\mathbf{A}) \leq \frac{\|\mathbf{A}\mathbf{x}\|_2}{\sqrt{k} \|\mathbf{x}\|_2} %\leq \frac{\|\mathbf{x}\|_1}{\sqrt{k} \|\mathbf{x}\|_2} \max_{i \in [m]}\|\mathbf{A}_i\|_2 
-\leq  \max_{i \in [m]}\|\mathbf{A}_i\|_2.
-\end{align}
 
-Our first step is to demonstrate how \eqref{Cstable} already implies the recovery result \eqref{b-PDa} when $\varepsilon < L_{2k}(\mathbf{A}) / C_1$.
+We demonstrate first of all how \eqref{Cstable} in fact already implies the recovery result \eqref{b-PDa} when $\varepsilon < L_{2k}(\mathbf{A}) / C_1$.
 For all $2k$-sparse $\mathbf{x} \in \mathbb{R}^m$, the triangle inequality gives \mbox{$\|(\mathbf{A}-\mathbf{BPD})\mathbf{x}\|_2  \leq C_1\varepsilon \|\mathbf{x}\|_1 \leq C_1 \varepsilon \sqrt{2k}  \|\mathbf{x}\|_2$}.
@@
 %
-where we drop the absolute value due to the upper bound on $\varepsilon$. Hence, $L_{2k}(\mathbf{BPD}) \geq L_{2k}(\mathbf{A}) - C_1\varepsilon  > 0$ and \eqref{b-PDa} then follows from:
+where we may drop the absolute value due to the upper bound on $\varepsilon$. Hence, $L_{2k}(\mathbf{BPD}) \geq L_{2k}(\mathbf{A}) - C_1\varepsilon  > 0$ and \eqref{b-PDa} then follows from:
 \begin{align*}
@@
 %&\leq \sqrt{2k} |\mathbf{x}_i - D^{-1}P^{\top}\mathbf{\hat x}_i\|_2 \\
-&\leq \frac{\|\mathbf{BPD}(\mathbf{x}_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\hat x}_i)\|_2}{L_{2k}(\mathbf{BPD})} \\
-&\leq \frac{\|\mathbf{B}\mathbf{\hat x}_i - \mathbf{A}\mathbf{x}_i\|_2 + \|(\mathbf{A} - \mathbf{BPD})\mathbf{x}_i\|_2}{L_{2k}(\mathbf{BPD})} \\
-&\leq \frac{\varepsilon (1+C_1 \|\mathbf{x}_i\|_1)}{L_{2k}(\mathbf{BPD})}.
+&\leq \frac{\|\mathbf{BPD}(\mathbf{x}_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\hat x}_i)\|_2}{\sqrt{2k}L_{2k}(\mathbf{BPD})} \\
+&\leq \frac{\|\mathbf{B}\mathbf{\hat x}_i - \mathbf{A}\mathbf{x}_i\|_2 + \|(\mathbf{A} - \mathbf{BPD})\mathbf{x}_i\|_2}{\sqrt{2k}L_{2k}(\mathbf{BPD})} \\
+&\leq \frac{\varepsilon (1+C_1 \|\mathbf{x}_i\|_1)}{\sqrt{2k}L_{2k}(\mathbf{BPD})}.
 %&\leq \frac{\varepsilon}{\sqrt{2k}} \left( \frac{ 1+C_1 \|\mathbf{x}_i\|_1 }{ L_{2k}(\mathbf{A}) -  C_1\varepsilon } \right).
@@
 We establish \eqref{Cstable} in the first place by arguments that flow loosely as follows.
-Pigeonholing the data into its set of possible supports with respect to the matrix $\mathbf{B}$, one sees that the column space of every $\mathbf{A}_S$ with $S \in E$ must be nearby (in a sense yet to be defined; see Def.~\ref{dDef}) the column space of some $n \times k$ submatrix of $\mathbf{B}$.
-\eqref{Cstable} is then immediately implied by our result in combinatorial matrix analysis (Lem.~\ref{MainLemma}), which we derive by the following arguments (see the Supplemental for the full proof).
+Pigeonholing the data into its set of possible supports with respect to the matrix $\mathbf{B}$, one sees that the column space of every $\mathbf{A}_S$ with $S \in E$ must be proximal (in a sense yet to be defined; see Def.~\ref{dDef}) to the column space of some $n \times k$ submatrix of $\mathbf{B}$.
+\eqref{Cstable} is then immediately implied by our result in combinatorial matrix analysis (Lem.~\ref{MainLemma}), which we derive by the following arguments (see the Appendix for the full proof).
 First, we show that the aforementioned proximity between $k$-dimensional subspaces implies a proximity between smaller subspaces spanned by columns of $\mathbf{A}$ indexed by the intersections of sets in $E$ and those spanned by as many or fewer columns of $\mathbf{B}$.
-Another pigeonholing argument here combined with our assumptions on $E$ (e.g., the singleton intersection property) reveals that, in fact, each column of $\mathbf{A}$ spans a subspace proximal to that spanned by some column of $\mathbf{B}$.
+Another pigeonholing argument here combined with our assumptions on $E$ (e.g.
+the singleton intersection property) reveals that, in fact, each column of $\mathbf{A}$ spans a subspace proximal to that spanned by some column of $\mathbf{B}$.
 \eqref{Cstable} is a simple consequence of this last fact, which actually constitutes the proof of the theorem for the case $k=1$.
@@
 
+We note first that $\|\mathbf{x}\|_1 \leq \sqrt{k} \|\mathbf{x}\|_2$ for $k$-sparse $\mathbf{x} \in \mathbb{R}^m$, which implies by definition of $L_k(A)$ the following inequality which we often use:
+\begin{align}\label{delrho}
+L_k(\mathbf{A}) \leq \frac{\|\mathbf{A}\mathbf{x}\|_2}{\sqrt{k} \|\mathbf{x}\|_2} %\leq \frac{\|\mathbf{x}\|_1}{\sqrt{k} \|\mathbf{x}\|_2} \max_{i \in [m]}\|\mathbf{A}_i\|_2 
+\leq  \max_{i \in [m]}\|\mathbf{A}_i\|_2.
+\end{align}
+
 \begin{proof}[Proof ($k=1$)]
-Note that the only 1-uniform set system satisfying the singleton intersection property is $[m]$; hence, we have $\mathbf{x}_i = c_i \mathbf{e}_i$ for $c_i \in \mathbb{R} \setminus \{\mathbf{0}\}$, $i \in [m]$.
+Note that the only 1-uniform set system satisfying the singleton intersection property is $[m]$; hence we have $\mathbf{x}_i = c_i \mathbf{e}_i$ for $c_i \in \mathbb{R} \setminus \{\mathbf{0}\}$, $i \in [m]$.
 In this case we may take $C_1$ to be any value satisfying $C_1^{-1} \leq \min_{j \in [m]} |c_{j}|$.
@@
 %
-where $\mathbf{X}$ is the $m \times N$ matrix with columns $\mathbf{x}_i$ and $I(S) := \{i : \text{supp}(\mathbf{x}_i) = S\}$.\footnote{We can be sure $C_1 > 0$ is well-defined (provided $C_2$ is well-defined) since $L_k(\mathbf{A}), L_k(\mathbf{X}_{I(S)}) > 0$ by the spark condition and general linear position of the $\mathbf{x}_i$; hence $\|\mathbf{A}_j\|_2 > 0$ for all $j$ and for all $S \in E$ we have $\|\mathbf{AX}_{I(S)}\mathbf{c}\|_2 \geq L_k(\mathbf{A})\|\mathbf{X}_{I(S)}\mathbf{c}\|_2 \geq L_k(\mathbf{A}) L_k(\mathbf{X}_{I(S)})\|\mathbf{c}\|_2$ for all $k$-sparse $\mathbf{c}$ and therefore $L_k(\mathbf{AX}_{I(S)}) \geq L_k(\mathbf{A}) L_k(\mathbf{X}_{I(S)}) > 0$.} The constant $C_2 = C_2(\mathbf{A}, E)$ is defined explicitly below in terms of the following technical quantity based on one used in \cite{Deutsch12} to analyze the convergence of the alternating projections algorithm for projecting a point onto the intersection of a set of subspaces.
+where $\mathbf{X}$ is the $m \times N$ matrix with columns $\mathbf{x}_i$ and $I(S) := \{i : \text{supp}(\mathbf{x}_i) = S\}$.\footnote{We can be sure $C_1 > 0$ is well-defined (provided $C_2$ is well-defined) since $L_k(\mathbf{A}), L_k(\mathbf{X}_{I(S)}) > 0$ by the spark condition and general linear position of the $\mathbf{x}_i$; hence $\|\mathbf{A}_j\|_2 > 0$ for all $j$ and for all $S \in E$ we have $\|\mathbf{AX}_{I(S)}\mathbf{c}\|_2 \geq L_k(\mathbf{A})\|\mathbf{X}_{I(S)}\mathbf{c}\|_2 \geq L_k(\mathbf{A}) L_k(\mathbf{X}_{I(S)})\|\mathbf{c}\|_2$ for all $k$-sparse $\mathbf{c}$ and therefore $L_k(\mathbf{AX}_{I(S)}) \geq L_k(\mathbf{A}) L_k(\mathbf{X}_{I(S)}) > 0$.} The constant $C_2 = C_2(\mathbf{A}, E)$ is defined explicitly below in terms of the following (somewhat unintuitive) quantity based on one used in \cite{Deutsch12} to analyze the convergence of the alternating projections algorithm for projecting a point onto the intersection of a set of subspaces.
 We use it to bound the distance between a point and the intersection of a set of subspaces given an upper bound on its distance from each subspace individually.
@@
 \begin{align*}
-\cos{\theta(U,W)} := \max\left\{ |\langle \mathbf{u}, \mathbf{w} \rangle|: \substack{ \mathbf{u} \in U \cap (U \cap W)^\perp, \ \|\mathbf{u}\|_2 \leq 1 \\ \mathbf{w} \in W \cap (U \cap W)^\perp, \  \|\mathbf{w}\|_2 \leq 1 } \right\}.
+\cos{\theta(U,W)} := \max\left\{ |\langle \mathbf{u}, \mathbf{w} \rangle|: \substack{ \mathbf{u} \in U \cap (U \cap W)^\perp, \|\mathbf{u}\|_2 \leq 1 \\ \mathbf{w} \in W \cap (U \cap W)^\perp, \|\mathbf{w}\|_2 \leq 1 } \right\}.
 \end{align*}
@@
 
-The constant $C_2$ in Lem.~\ref{MainLemma} is then given by:  % \footnote{Note that $C_2 > 0$ is well-defined since $r > 0$ by definition.}
+The constant $C_2$ in Lem.~\ref{MainLemma} is then given by:\footnote{Note that $C_2 > 0$ is well-defined since $r > 0$ by definition.}
 \begin{align}
@@
 d(\text{Span}\{\mathbf{A}_S\}, \text{Span}\{\mathbf{B}_{S'}\}) 
-\leq \frac{\varepsilon}{ \min_{S \in E} L_k(\mathbf{AX}_{I(S)}) }.
+\leq \frac{\varepsilon}{ \min_{S \in E} L_k(\mathbf{AX}_{I(S)}) } 
 %\leq \frac{\varepsilon}{L(\mathbf{AX}_{J(S)})}.
@@
 
-In this note, we generalize the approach of \cite{Hillar15} to the uniqueness of solutions to Problem~\ref{InverseProblem} for noisy measurements while also reducing the number of required samples.
+In this note, we generalize recent results \cite{Hillar15} on the uniqueness of solutions to Problem~\ref{InverseProblem} to the case of noisy measurements while also significantly reducing the number of required samples.
 % from $N=k{m \choose k}^2$ to $N = m(k-1){m \choose k}+m$. 
@@
 Moreover, if solutions are constrained to satisfy \eqref{SparkCondition}, then only an upper bound on the number of dictionary elements need be taken as given.
-We remark that our result in the deterministic case (Thm.~\ref{DeterministicUniquenessTheorem}) accounts for \emph{worst-case} noise, whereas the ``effective'' noise might be much smaller when it is sampled from a given distribution; in such cases, the constants $C_1, C_3$ in Thms.~\ref{DeterministicUniquenessTheorem},~\ref{DeterministicUniquenessTheorem2} will be much smaller with high probability.
+We remark that our result in the deterministic case (Thm.~\ref{DeterministicUniquenessTheorem}) accounts for \emph{worst-case} noise, whereas the ``effective'' noise might be much smaller when it is sampled from a given distribution; in such cases, the constants $C_1, C_3$ in Thms.~\ref{DeterministicUniquenessTheorem},~\ref{DeterministicUniquenessTheorem2} may be much smaller with high probability.
 We note also that these results extend trivially to cases where point-wise injective nonlinearities are applied to the data. We close by outlining four diverse application areas.
@@
 \textbf{Inverse Problems}.  
-Our results provide theoretical grounding for the use of sparse linear coding in blind source separation, wherein the goal is to infer the generating dictionary and sparse codes from noisy measurements generated as in \eqref{LinearModel} (e.g., recovering a rat's position on a linear track from local field potentials in Hippocampus \cite{Agarwal14}).
+Our results provide theoretical grounding for the use of sparse dictionary learning in blind source separation, wherein the goal is to infer the generating dictionary and sparse codes from noisy measurements generated as in \eqref{LinearModel} (e.g., recovering a rat's position on a linear track from local field potentials in Hippocampus \cite{Agarwal14}).
 It would be of practical utility therefore to determine the best possible dependence of $\varepsilon$ on $\delta_1, \delta_2$ (see \eqref{epsdel}) as well as the minimal requirements on the number and diversity of generating codes.
 %We encourage researchers to extend our results and tighten these parameters.
-
-[Effective computation of stable datasets, at least in principle.]
 
@@
 Our theorems suggest that this correspondence could be due to the uniqueness of sparse representations.
-Furthermore, our guarantees justify the hypothesis of \cite{Coulter10} and \cite{Isely10} that sparse codes passed through a communication bottleneck in the brain can be recovered from random projections via (unsupervised) biologically plausible sparse dictionary learning (e.g., \cite{rehnsommer2007, rozell2007neurally, hu2014hebbian}).
+Furthermore, our guarantees justify the hypothesis of \cite{Coulter10} and \cite{Isely10} that sparse codes passed through a communication bottleneck in the brain can be recovered from random projections via (unsupervised) biologically plausible sparse dictionary learning (e.g., \cite{rozell2007neurally, hu2014hebbian}).
 %TODO: add reproduction of response propeties in olfactory cortex?
@@
 Our results imply that if there is an efficient ``smoothed" algorithm for solving Problem \ref{InverseProblem} given enough samples, then for generic inputs this algorithm determines the unique original solution.
-We note that avoiding certain pathological sets of inputs is often a necessary technicality for dictionary learning \cite{Razaviyayn15, Tillmann15}.
+We note that avoiding ``bad" (NP-hard) sets of inputs is a necessary technicality for dictionary learning \cite{Razaviyayn15, Tillmann15}.
 
 \textbf{Engineering}.
-Several groups utilize compressed sensing for signal processing tasks: MRI analysis \cite{lustig2008compressed},  image compression \cite{Duarte08}, and, more recently, the design of an ultrafast camera \cite{Gao14}.
-Given such effective uses of compressed sensing, it is only a matter of time before these systems incorporate sparse dictionary learning to encode and process data.
+Several groups utilize compressive sensing for signal processing tasks: MRI analysis \cite{lustig2008compressed},  image compression \cite{Duarte08}, and, more recently, the design of an ultrafast camera \cite{Gao14}.
+Given such effective uses of compressive sensing, it is only a matter of time before these systems incorporate sparse dictionary learning to encode and process data.
 Guarantees such as those offered by our theorems allow any such device to be equivalent to any other (having different initial parameters and data samples) as long as enough data originate from a statistically identical system.

### 2017-03-27 manuscripts/PNAS/chazthm_pnas.tex
chazthm_pnas.tex

--- 2017-03-27 manuscripts/PNAS/chazthm_pnas.tex
@@
 Fortunately, algorithms with proven recovery of generating dictionaries under certain
-conditions have recently been proposed (see \cite[Sec.~I-E]{Sun16} for a summary of the state-of-the-art).  However,
-there are few general theorems explaining the general phenomenon of uniqueness.
+conditions have recently been proposed (see \cite[Sec.~I-E]{Sun16} for a summary of the state-of-the-art).  However, there are few universal theorems explaining the general phenomenon of uniqueness.
 
@@
 
-Note that any particular solution $(\mathbf{B}, \mathbf{\hat x}_1 \ldots, \mathbf{\hat x}_N)$ to this problem gives rise to an orbit of other solutions $(\mathbf{BPD}, \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\hat x}_1 \ldots, \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\hat x}_N)$, where $\mathbf{P}$ is any permutation matrix and $\mathbf{D}$ any invertible diagonal.
+Note that any particular solution $(\mathbf{B}, \mathbf{\hat x}_1 \ldots, \mathbf{\hat x}_N)$ to this problem gives rise to an orbit of other solutions $(\mathbf{BPD}, \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\hat x}_1, \ldots, \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\hat x}_N)$, where $\mathbf{P}$ is any permutation matrix and $\mathbf{D}$ any invertible diagonal.
 We therefore consider whether solutions to Problem~\ref{InverseProblem} are unique only up to this ambiguity.  More specifically, 
@@
 Fix $Y = \{ \mathbf{y}_1, \ldots, \mathbf{y}_N\} \subset \mathbb{R}^n$.
-We say $Y$ has a \textbf{$k$-sparse representation in $m$ dimensions} if there exists a matrix $\mathbf{A}$ and $k$-sparse $\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$ such that $\mathbf{y}_i = \mathbf{A}\mathbf{x}_i$ for all $i$.
+We say $Y$ has a \textbf{$k$-sparse linear representation in $m$ dimensions} if there exists a matrix $\mathbf{A}$ and $k$-sparse $\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$ such that $\mathbf{y}_i = \mathbf{A}\mathbf{x}_i$ for all $i$.
 %Equivalently, $\mathbf{Y} = \mathbf{A}\mathbf{X}$ for $\mathbf{Y}$ and $\mathbf{X}$ having the $\mathbf{y}_i$ and $\mathbf{x}_i$ as their columns, respectively.
@@
 % \mbox{$Y = \{\mathbf{A} \mathbf{x}_1, \ldots, \mathbf{A}\mathbf{x}_N\}$} 
-has a stable $k$-sparse representation in $m$ dimensions and fix $\delta_1, \delta_2$ to be the desired accuracy in \eqref{def1}.
+has a stable $k$-sparse linear representation in $m$ dimensions and fix $\delta_1, \delta_2$ to be the desired accuracy in \eqref{def1}.
 Consider now any dataset $Z$ generated as in \eqref{LinearModel} with $\eta \leq \frac{1}{2} \varepsilon(\delta_1, \delta_2)$.
@@
 
-[*** TODO: Combine with Theorem 3 ***]
 \begin{theorem}\label{DeterministicUniquenessTheorem}
-Fix integers $1 \leq p \leq m$, $n$, and $k < m \leq m' \leq \frac{\ell m - (p-1)}{\ell - 1}$.
-Suppose $\mathbf{A}~\in~\mathbb{R}^{n \times m}$ satisfies \eqref{SparkCondition} and that \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} include at least \mbox{$(k-1){m \choose k}+1$} vectors in general linear position supported on each set in some $\ell$-regular $E \subseteq {[m] \choose k}$ satisfying the SIP.
+% Fix positive integers $k, \ell, m, m', n, p$ satisfying $k < m$ and $p \leq m \leq m' \leq (\ell m - p) / (\ell - 1)$. 
+Fix integers $n, \ell$ and $k < m \leq \hat m$.
+Suppose $\mathbf{A}~\in~\mathbb{R}^{n \times m}$ satisfies \eqref{SparkCondition} and that $k$-sparse \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} contain at least \mbox{$(k-1){\hat m \choose k}+1$} vectors supported in general linear position on each set in some $\ell$-regular $E \subseteq {[m] \choose k}$ satisfying the SIP.
 Then there exists a constant $C_1 > 0$ for which the following holds for all $\varepsilon < L_2(\mathbf{A}) / C_1$.
-%\frac{L_2(\mathbf{A})}{\sqrt{2}}C_1^{-1}$:
 
-Every matrix $\mathbf{B} \in \mathbb{R}^{n \times m}$ for which for some $k$-sparse $\mathbf{\hat x}_1, \ldots, \mathbf{\hat x}_N \in \mathbb{R}^{m}$ we have \mbox{$\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\hat x}_i\|_2 \leq \varepsilon$} for all $i$ necessarily satisfies:
+Every matrix $\mathbf{B} \in \mathbb{R}^{n \times \hat m}$ for which for some $k$-sparse $\mathbf{\hat x}_1, \ldots, \mathbf{\hat x}_N \in \mathbb{R}^{\hat m}$ we have \mbox{$\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\hat x}_i\|_2 \leq \varepsilon$} for all $i$ necessarily satisfies:
 \begin{align}\label{Cstable}
-\|\mathbf{A}_j-(\mathbf{B}\mathbf{PD})_j\|_2 \leq C_1 \varepsilon \ \ \text{for all $j \in [m]$}
+\|\mathbf{A}_{\phi(j)} - (\mathbf{B}_{J}\mathbf{PD})_j\|_2 \leq C_1 \varepsilon \ \ \text{for $j = 1, \ldots, |J|$}
 \end{align}
 %
-for some permutation matrix $\mathbf{P}$ and invertible diagonal matrix $\mathbf{D}$.
+for some $J \subseteq [\hat m]$ of size \mbox{$\lfloor \hat m - \ell(\hat m - m) \rfloor$}, injective map $\phi$, permutation matrix $\mathbf{P}$ and invertible diagonal matrix $\mathbf{D}$.
 %\footnote{We note that the condition $\varepsilon < L_2(\mathbf{A})$ above is necessary.
 When \mbox{$\mathbf{A}$ = $I$} and $\mathbf{x}_i = \mathbf{e}_i$, it turns out that $C_1 = 1$ and there is a $\mathbf{B}$ and $1$-sparse $\mathbf{\hat x}_i$ with $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\hat x}_i\|_2 \leq \varepsilon$ violating \eqref{Cstable}.}
-Furthermore if $\varepsilon < L_{2k}(\mathbf{A}) / C_1$ then $\mathbf{B}$ also satisfies \eqref{SparkCondition} with $L_{2k}(\mathbf{B}\mathbf{PD}) \geq L_{2k}(\mathbf{A}) - C_1 \varepsilon$ and we in fact have:
+
+Furthermore if $\varepsilon < L_{2k}(\mathbf{A}) / C_1$ then $\mathbf{B}_J$ also satisfies \eqref{SparkCondition} with $L_{2k}(\mathbf{B}_J\mathbf{PD}) \geq L_{2k}(\mathbf{A}) - C_1 \varepsilon$ and we in fact have [ ** TODO ** ]:
 \begin{align}\label{b-PDa}
@@
 
+In other words, the smaller the difference $\hat m - m$, the more columns and coefficients of the original $n \times m$ dictionary $\mathbf{A}$ and $m$-dimensional codes $\mathbf{x}_i$ contained (up to noise) in the appropriately scaled $n \times \hat m$ dictionary $\mathbf{B}$ and $\hat m$-dimensional codes $\mathbf{\hat x}_i$.
+In particular, if $\hat m = m$ then all columns of $\mathbf{A}$ and coefficients of each $\mathbf{x}_i$ recoverable, as per Def.~\ref{maindef}.
 For clarity of exposition, we delay explicitly defining the (effective) constant $C_1 = C_1(\mathbf{A}, \{\mathbf{x}_i\}_{i=1}^N, E)$ until Section \ref{DUT} (\eqref{Cdef}), since it requires additional definitions not critical to the statement of our results.
@@
 
-Next, we address the case when only an upper bound $m'$ on the latent dimension $m$ is known (assuming that $\mathbf{B}$ satisfies \eqref{SparkCondition}).
+%Next, we address the case when only an upper bound $m'$ on the latent dimension $m$ is known (assuming that $\mathbf{B}$ satisfies \eqref{SparkCondition}).
 
-\begin{theorem}\label{DeterministicUniquenessTheorem2}
-Fix integers $n$ and $k < m \leq m'$ and matrices $\mathbf{A}~\in~\mathbb{R}^{n \times m}$ and $\mathbf{B} \in \mathbb{R}^{n \times m'}$ both satisfying \eqref{SparkCondition}.
+%\begin{theorem}\label{DeterministicUniquenessTheorem2}
+%Fix integers $n$ and $k < m \leq m'$ and matrices $\mathbf{A}~\in~\mathbb{R}^{n \times m}$ and $\mathbf{B} \in \mathbb{R}^{n \times m'}$ both satisfying \eqref{SparkCondition}.
 Suppose \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} include at least \mbox{$(k-1){m' \choose k}+1$} $k$-sparse vectors in general linear position supported on each set in some $k$-uniform $E \subseteq 2^{[m]}$ satisfying the singleton intersection property.
@@
 
-If for some $k$-sparse $\mathbf{\hat x}_1, \ldots, \mathbf{\hat x}_N \in \mathbb{R}^{m'}$ and $\varepsilon < L_2(\mathbf{A}) / C_3$ we have \mbox{$\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\hat x}_i\|_2 \leq \varepsilon$} for all $i$, then:
-\begin{align}\label{Cstablem'}
-\|\mathbf{A}_j-(\mathbf{B}_J\mathbf{PD})_j\|_2 \leq C_3\varepsilon \ \ \text{for all $j \in [m]$}
-\end{align}
+%If for some $k$-sparse $\mathbf{\hat x}_1, \ldots, \mathbf{\hat x}_N \in \mathbb{R}^{m'}$ and $\varepsilon < L_2(\mathbf{A}) / C_3$ we have \mbox{$\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\hat x}_i\|_2 \leq \varepsilon$} for all $i$, then:
+%\begin{align}\label{Cstablem'}
+%\|\mathbf{A}_j-(\mathbf{B}_J\mathbf{PD})_j\|_2 \leq C_3\varepsilon \ \ \text{for all $j \in [m]$}
+%\end{align}
 %
-for some $J \in {[m'] \choose m}$, permutation matrix $\mathbf{P}$, and invertible diagonal matrix $\mathbf{D}$.
-\end{theorem}
+%for some $J \in {[m'] \choose m}$, permutation matrix $\mathbf{P}$, and invertible diagonal matrix $\mathbf{D}$.
+%\end{theorem}
 
-In other words, the columns of $B$ contain (up to noise, after appropriate scaling) the columns of the original dictionary $\mathbf{A}$.
+%In other words, the columns of $B$ contain (up to noise, after appropriate scaling) the columns of the original dictionary $\mathbf{A}$.
 Similarly, one can show by the same arguments at the beginning of Sec.~\ref{DUT} that the $\mathbf{\hat x}_i$ contain the original codes $\mathbf{x}_i$.

### 2017-03-28 manuscripts/PNAS/chazthm_pnas.tex
sml updates

@@
 
-\significancestatement{Many naturally occurring signals (e.g.
+\significancestatement{[*** REDO ***] Many naturally occurring signals (e.g.
 patches of visual scenery, speech audio, electrocardiograms) have been usefully characterized as parsimonious combinations of building blocks drawn from a large `dictionary' of elementary waveforms.
@@
 Note that any particular solution $(\mathbf{B}, \mathbf{\hat x}_1 \ldots, \mathbf{\hat x}_N)$ to this problem gives rise to an orbit of other solutions $(\mathbf{BPD}, \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\hat x}_1, \ldots, \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\hat x}_N)$, where $\mathbf{P}$ is any permutation matrix and $\mathbf{D}$ any invertible diagonal.
-We therefore consider whether solutions to Problem~\ref{InverseProblem} are unique only up to this ambiguity.  More specifically, 
+We therefore consider whether solutions to Prob.~\ref{InverseProblem} are unique only up to this ambiguity.  More specifically, 
 we seek conditions for when sparsely coded datasets have a stable unique representation.
@@
 
-To see how Definition \ref{maindef} directly relates to Problem \ref{InverseProblem}, suppose that $Y$
+To see how Def. \ref{maindef} directly relates to Prob. \ref{InverseProblem}, suppose that $Y$
 % \mbox{$Y = \{\mathbf{A} \mathbf{x}_1, \ldots, \mathbf{A}\mathbf{x}_N\}$} 
-has a stable $k$-sparse linear representation in $m$ dimensions and fix $\delta_1, \delta_2$ to be the desired accuracy in \eqref{def1}.
+has a stable $k$-sparse linear representation in $m$ dimensions and fix $\delta_1, \delta_2$ to be the desired recovery accuracy in \eqref{def1}.
 Consider now any dataset $Z$ generated as in \eqref{LinearModel} with $\eta \leq \frac{1}{2} \varepsilon(\delta_1, \delta_2)$.
-Then, any dictionary $\mathbf{B}$ and $k$-sparse $\mathbf{\hat x}_1, \ldots, \mathbf{\hat x}_N$ solving Problem \ref{InverseProblem} are necessarily close to the original matrix $\mathbf{A}$ and codes $\mathbf{x}_i$ (i.e., satisfy \eqref{def1}).
+Then from the triangle inequality, it follows that any matrix $\mathbf{B}$ and $k$-sparse $\mathbf{\hat x}_1, \ldots, \mathbf{\hat x}_N$ solving Prob.~\ref{InverseProblem} are necessarily close to the original dictionary $\mathbf{A}$ and codes $\mathbf{x}_i$.
 
@@
 
-Previous theoretical work on Problem \ref{InverseProblem} for the noiseless case $\eta =0$ (e.g., \cite{li2004analysis, Georgiev05, Aharon06, Hillar15}) has shown that a solution (when it exists) is indeed unique provided the $\mathbf{x}_i$ are sufficiently diverse and the generating matrix $\mathbf{A}$ satisfies the \textit{spark condition} from compressed sensing (CS):
+Previous theoretical work on Prob.~\ref{InverseProblem} for the noiseless case $\eta =0$ (e.g., \cite{li2004analysis, Georgiev05, Aharon06, Hillar15}) has shown that a solution (when it exists) is indeed unique provided the $\mathbf{x}_i$ are sufficiently diverse and the generating matrix $\mathbf{A}$ satisfies the \textit{spark condition} from compressed sensing (CS):
 \begin{align}\label{SparkCondition}
@@
 All other proofs are relegated to the Supplemental.
-Our approach is a refinement of the one found in \cite{Hillar15} to handle noise and to reduce the sufficient number of samples.
+%Our approach is a refinement of the one found in \cite{Hillar15} to handle noise and to reduce the sufficient number of samples.
 %for all $k < m$ from $N=k{m \choose k}^2$ to $N = m + m(k-1){m \choose k}$. 
@@
 
-Before stating our main results, we explain how the spark condition \eqref{SparkCondition} relates to the \emph{lower bound} \cite{Grcar10} of $\mathbf{A}$, which is the largest number $\alpha$ such that \mbox{$\|\mathbf{A}\mathbf{x}\|_2 \geq \alpha\|\mathbf{x}\|_2$} for all $\mathbf{x} \in \mathbb{R}^m$.
+To prepare for the statements of our main results, we first describe a quantitative version of the spark condition.  % We first explain how the spark condition \eqref{SparkCondition} relates to t
+The \emph{lower bound} \cite{Grcar10} of a matrix $\mathbf{A} \in \mathbb R^{n \times m}$ is the largest number $\alpha$ such that \mbox{$\|\mathbf{A}\mathbf{x}\|_2 \geq \alpha\|\mathbf{x}\|_2$} for all $\mathbf{x} \in \mathbb{R}^m$.
 By compactness of the unit sphere, every injective linear map has a nonzero lower bound; hence, if $\mathbf{A}$ satisfies \eqref{SparkCondition}, then each submatrix formed from $2k$ of its columns or less has a nonzero lower bound.
@@
 
-An important contribution of our work is to identify combinatorial criteria on the support sets of generating codes that allow for stable sparse 
+% an important contribution of our work is to
+Next, we identify our combinatorial criteria on the support sets of generating codes that allow for stable sparse 
 representations.
@@
 We interpret $\text{Span}\{\mathbf{M}_\emptyset\} = \{\textbf{0}\}$, where $\emptyset$ is the empty set.
-We say a hypergraph $E \subseteq 2^{[m]}$ is of rank $k$ when $|S| \leq k$ for every $S \in E$ (and $k$-uniform when equality holds).
+We say a hypergraph $E \subseteq 2^{[m]}$ is of \textit{rank} $k$ when $|S| \leq k$ for every $S \in E$ (and \textit{$k$-uniform} when equality holds).
 We say $E$ is \emph{regular} when every element of $[m]$ is contained in exactly $\ell$ elements of $E$ for some $\ell > 0$ (for given $\ell$, we say $E$ is $\ell$-regular).
@@
 
-Recall that a set of $k$-sparse vectors is in \emph{general linear position} when any $k$ of them are linearly independent.
+We say that a set of $k$-sparse vectors is in \emph{general linear position} when any $k$ of them are linearly independent.
 The following is the technical statement of our main result.
@@
 Suppose $\mathbf{A}~\in~\mathbb{R}^{n \times m}$ satisfies \eqref{SparkCondition} and that $k$-sparse \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} contain at least \mbox{$(k-1){\hat m \choose k}+1$} vectors supported in general linear position on each set in some $\ell$-regular $E \subseteq {[m] \choose k}$ satisfying the SIP.
-Then there exists a constant $C_1 > 0$ for which the following holds for all $\varepsilon < L_2(\mathbf{A}) / C_1$.
+There exists a constant $C_1 > 0$ for which the following holds for all $\varepsilon < L_2(\mathbf{A}) / C_1$.
 
-Every matrix $\mathbf{B} \in \mathbb{R}^{n \times \hat m}$ for which for some $k$-sparse $\mathbf{\hat x}_1, \ldots, \mathbf{\hat x}_N \in \mathbb{R}^{\hat m}$ we have \mbox{$\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\hat x}_i\|_2 \leq \varepsilon$} for all $i$ necessarily satisfies:
+Every matrix $\mathbf{B} \in \mathbb{R}^{n \times \hat m}$ and $k$-sparse $\mathbf{\hat x}_1, \ldots, \mathbf{\hat x}_N \in \mathbb{R}^{\hat m}$ with  \mbox{$\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\hat x}_i\|_2 \leq \varepsilon$} for all $i$ necessarily satisfies:
 \begin{align}\label{Cstable}
-\|\mathbf{A}_{\phi(j)} - (\mathbf{B}_{J}\mathbf{PD})_j\|_2 \leq C_1 \varepsilon \ \ \text{for $j = 1, \ldots, |J|$}
+\|\mathbf{A}_{\phi(j)} - (\mathbf{B}_{J}\mathbf{PD})_j\|_2 \leq C_1 \varepsilon, \ \ \text{for $j = 1, \ldots, |J|$},
 \end{align}
@@
 In particular, if $\hat m = m$ then all columns of $\mathbf{A}$ and coefficients of each $\mathbf{x}_i$ recoverable, as per Def.~\ref{maindef}.
-For clarity of exposition, we delay explicitly defining the (effective) constant $C_1 = C_1(\mathbf{A}, \{\mathbf{x}_i\}_{i=1}^N, E)$ until Section \ref{DUT} (\eqref{Cdef}), since it requires additional definitions not critical to the statement of our results.
+For clarity of exposition, we delay defining the (explicit) constant $C_1 = C_1(\mathbf{A}, \{\mathbf{x}_i\}_{i=1}^N, E)$ until Section \ref{DUT} (\eqref{Cdef}), since it requires additional definitions not critical to the statement of our results.
 
@@
 \begin{align}\label{epsdel}
-\varepsilon(\delta_1, \delta_2) := \min \left\{ \frac{\delta_1}{ C_1 }, \frac{ \delta_2 L_{2k}(\mathbf{A})}{ 1 + C_1 \left( \max_{i \in [N]} \|\mathbf{x}_i\|_1  + \delta_2 \right) } \right\}.
+\varepsilon(\delta_1, \delta_2) := \min \left\{ \frac{\delta_1}{ C_1 }, \frac{ \delta_2 (L_{2k}(\mathbf{A}) -  C_1\varepsilon)}{ 1 + C_1 \left( \max_{i \in [N]} \|\mathbf{x}_i\|_1  + \delta_2 \right) } \right\}.
 \end{align}
@@
 \begin{corollary}\label{DeterministicUniquenessCorollary}
-Given $n, m$, $k < m$ and a regular hypergraph $E \subseteq 2^{[m]}$ of rank $k$ satisfying the singleton intersection property, there are $N =  |E| \left[ (k-1){m \choose k}+1 \right]$ vectors \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} such that every matrix $\mathbf{A} \in \mathbb{R}^{n \times m}$ satisfying \eqref{SparkCondition} generates a dataset $Y = \{\mathbf{A}\mathbf{x}_1, \ldots, \mathbf{A}\mathbf{x}_N\}$ with a stable $k$-sparse representation in $m$ dimensions.
+Given $n, m$, $k < m$, and a regular hypergraph $E \subseteq 2^{[m]}$ of rank $k$ satisfying the singleton intersection property, there are $N =  |E| \left[ (k-1){m \choose k}+1 \right]$ vectors \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} such that every matrix $\mathbf{A} \in \mathbb{R}^{n \times m}$ satisfying \eqref{SparkCondition} generates a dataset $Y = \{\mathbf{A}\mathbf{x}_1, \ldots, \mathbf{A}\mathbf{x}_N\}$ with a stable $k$-sparse representation in $m$ dimensions.
 \end{corollary}
+\begin{proof}
+Something quick here.
+\end{proof}
 
@@
 This is easy to see by noting that $|E|k \geq \sum_{S \in E}|S| = \sum_{i \in [m]} \deg(i) = \ell m$.
-In certain cases there exist simple constructions achieving this minimum; for example, when $k = \sqrt{m}$ one can take $E$ to be the rows and columns formed by arranging the elements of $[m]$ in a square grid.
+In certain cases, there exist simple constructions achieving this minimum; for example, when $k = \sqrt{m}$ one can take $E$ to be the rows and columns formed by arranging the elements of $[m]$ in a square grid.
 
 It is straightforward to provide a probabilistic extension of Thm.~\ref{DeterministicUniquenessTheorem} using the following fact in random matrix theory.
-The matrix $\mathbf{A} \in \mathbb{R}^{n \times m}$ satisfies \eqref{SparkCondition} with probability one (or with ``high probability'' for discrete variables)
+A random matrix $\mathbf{A} \in \mathbb{R}^{n \times m}$ satisfies \eqref{SparkCondition} with probability one (or with ``high probability'' for discrete variables)
 provided:
@@
 
-Since $f$ is a real analytic function, it is enough to show that at least one substitution of real numbers satisfies $f(\mathbf{A}) \neq 0$ to conclude that its zeroes form a set with measure zero.
+Since $f$ is a real analytic function, it is enough for one substitution of real numbers to satisfy $f(\mathbf{A}) \neq 0$ to conclude that its zeroes form a set with measure zero.
 Hence, almost every $n \times m$ real matrix $\mathbf{A}$ satisfies \eqref{SparkCondition} provided \eqref{CScondition} holds for a value of $\gamma$ for some distribution.
@@
 
-It so happens that a similar statement applies to sets of vectors with a stable sparse representation.
+% It so happens that a similar statement applies to sets of vectors with a stable sparse representation.
 As in \cite[Sec.~IV]{Hillar15}, consider the ``symbolic'' dataset $Y = \{\mathbf{A}\mathbf{x}_1,\ldots,\mathbf{A} \mathbf{x}_N\}$ generated by indeterminate $\mathbf{A}$ and $k$-sparse $\mathbf{x}_1, \ldots, \mathbf{x}_N$.
@@
 
-Our first step is to demonstrate how \eqref{Cstable} already implies the recovery result \eqref{b-PDa} when $\varepsilon < L_{2k}(\mathbf{A}) / C_1$.
+Our first step is to demonstrate how dictionary recovery \eqref{Cstable} already implies sparse code recovery \eqref{b-PDa} when $\varepsilon < L_{2k}(\mathbf{A}) / C_1$.
 For all $2k$-sparse $\mathbf{x} \in \mathbb{R}^m$, the triangle inequality gives \mbox{$\|(\mathbf{A}-\mathbf{BPD})\mathbf{x}\|_2  \leq C_1\varepsilon \|\mathbf{x}\|_1 \leq C_1 \varepsilon \sqrt{2k}  \|\mathbf{x}\|_2$}.
@@
 
-We establish \eqref{Cstable} in the first place by arguments that flow loosely as follows.
+The heart of the matter is therefore \eqref{Cstable}, which we now establish using the following approach.
 Pigeonholing the data into its set of possible supports with respect to the matrix $\mathbf{B}$, one sees that the column space of every $\mathbf{A}_S$ with $S \in E$ must be nearby (in a sense yet to be defined; see Def.~\ref{dDef}) the column space of some $n \times k$ submatrix of $\mathbf{B}$.
-\eqref{Cstable} is then immediately implied by our result in combinatorial matrix analysis (Lem.~\ref{MainLemma}), which we derive by the following arguments (see the Supplemental for the full proof).
-First, we show that the aforementioned proximity between $k$-dimensional subspaces implies a proximity between smaller subspaces spanned by columns of $\mathbf{A}$ indexed by the intersections of sets in $E$ and those spanned by as many or fewer columns of $\mathbf{B}$.
-Another pigeonholing argument here combined with our assumptions on $E$ (e.g., the singleton intersection property) reveals that, in fact, each column of $\mathbf{A}$ spans a subspace proximal to that spanned by some column of $\mathbf{B}$.
-\eqref{Cstable} is a simple consequence of this last fact, which actually constitutes the proof of the theorem for the case $k=1$.
-We present this special case now before restating the above arguments in greater detail.
+\eqref{Cstable} is then immediately implied by our result in combinatorial matrix analysis (Lem.~\ref{MainLemma}).
 
 In fact, in the case $k=1$ we can relax our assumptions even further and assume that the matrix $\mathbf{B}$ has only at least as many columns as $\mathbf{A}$; as we will see, the conclusions of Thm.~\ref{DeterministicUniquenessTheorem} then hold for some $n \times m$ submatrix of $\mathbf{B}$.
+[*** ???
+***]
 
@@
 \end{align}
-Note that $d(U,\{\textbf{0}\}) = 1$ for $U \neq \{\mathbf{0}\}$, whereas if $U = \{\textbf{0}\}$ then $d$ has no meaning; in this case we set $d(\{\textbf{0}\},V) = 0$ for any $V$.
+Note that $d(U,\{\textbf{0}\}) = 1$ for $U \neq \{\mathbf{0}\}$, whereas if $U = \{\textbf{0}\}$ then $d$ has no meaning; in this case, set $d(\{\textbf{0}\},V) = 0$ for any $V$.
 \end{definition}
@@
 
-Our result in combinatorial matrix analysis is the following.
+Our result in combinatorial matrix analysis is the following, which we derive by the following arguments (see the Supplemental for the full proof).
+First, we show that the aforementioned proximity between $k$-dimensional subspaces implies a proximity between smaller subspaces spanned by columns of $\mathbf{A}$ indexed by the intersections of sets in $E$ and those spanned by as many or fewer columns of $\mathbf{B}$.
+Another pigeonholing argument here combined with our assumptions on $E$ (e.g., the singleton intersection property) reveals that, in fact, each column of $\mathbf{A}$ spans a subspace proximal to that spanned by some column of $\mathbf{B}$.
+\eqref{Cstable} is a simple consequence of this last fact, which actually constitutes the proof of the theorem for the case $k=1$.
+We present this special case now before restating the above arguments in greater detail.
 
 \begin{lemma}\label{MainLemma}
-Fix integers $n$ and $k < m$ and suppose $\mathbf{A} \in \mathbb{R}^{n \times m}$ satisfies \eqref{SparkCondition}.
+Fix integers $n$ and $k < m$, and suppose $\mathbf{A} \in \mathbb{R}^{n \times m}$ satisfies the spark condition \eqref{SparkCondition}.
 There exists a constant $C_2 > 0$ for which the following holds for all $\varepsilon < L_2(\mathbf{A}) / C_2$.
-If for some  $\mathbf{B} \in \mathbb{R}^{n \times m}$ and regular $E \subseteq2^{[m]}$ satisfying the singleton intersection property there exists a size-preserving map $\pi: E \mapsto 2^{[m]}$ satisfying
+If for some  $\mathbf{B} \in \mathbb{R}^{n \times m}$ and regular $E \subseteq2^{[m]}$ satisfying the singleton intersection property there exists a size-preserving map $\pi: E \mapsto 2^{[m]}$ satisfying:
 \begin{align}\label{GapUpperBound}
-d(\text{Span}\{\mathbf{A}_{S}\}, \text{Span}\{\mathbf{B}_{\pi(S)}\}) \leq \varepsilon \ \ \text{for all $S \in E$},
+d(\text{Span}\{\mathbf{A}_{S}\}, \text{Span}\{\mathbf{B}_{\pi(S)}\}) \leq \varepsilon, \ \ \text{for all $S \in E$},
 \end{align}
@@
 \end{definition}
-Note that since $\theta \in (0,\frac{\pi}{2}]$, we always have $0 < r \leq 1$.
+Note that $\theta \in (0,\frac{\pi}{2}]$ implies $0 < r \leq 1$.
 (We acknowledge the somewhat counter-intuitive property that $\theta =  \pi/2$ when $U = V$ and when $U \perp V$.)  %\textbf{Note:} we can also define $\theta$ by \cite[Lem.~9.5]{Deutsch12}:
@@
 
-In this note, we generalize the approach of \cite{Hillar15} to the uniqueness of solutions to Problem~\ref{InverseProblem} for noisy measurements while also reducing the number of required samples.
+In this note, we generalize the approach of \cite{Hillar15} to the uniqueness of solutions to Prob.~\ref{InverseProblem} for noisy measurements while also reducing the number of required samples.
 % from $N=k{m \choose k}^2$ to $N = m(k-1){m \choose k}+m$. 
@@
 
+Mention sparse matrix factorization.
+
 [Effective computation of stable datasets, at least in principle.]
@@
 % Reiterate probabilistic result in the smooth analysis part?
-\textbf{Smoothed Analysis}.
-The main concept in smoothed analysis \cite{Spielman04} is that certain algorithms having exponential worst-case behavior are, nonetheless, efficient if certain (typically, measure zero in the continuous case and with ``low probability" in the discrete case) pathological input sets are avoided.
-Our results imply that if there is an efficient ``smoothed" algorithm for solving Problem \ref{InverseProblem} given enough samples, then for generic inputs this algorithm determines the unique original solution.
+%\textbf{Smoothed Analysis}.
+%The main concept in smoothed analysis \cite{Spielman04} is that certain algorithms having exponential worst-case behavior are, nonetheless, efficient if certain (typically, measure zero in the continuous case and with ``low probability" in the discrete case) pathological input sets are avoided.
+Our results imply that if there is an efficient ``smoothed" algorithm for solving Prob.~\ref{InverseProblem} given enough samples, then for generic inputs this algorithm determines the unique original solution.
 We note that avoiding certain pathological sets of inputs is often a necessary technicality for dictionary learning \cite{Razaviyayn15, Tillmann15}.
@@
 \begin{lemma}\label{SpanIntersectionLemma}
-Let $\mathbf{M} \in \mathbb{R}^{n \times m}$. If every $2k$ columns of $\mathbf{M}$ are linearly independent, then for any $F \subseteq 2^{[m]}$ of rank $k$, we have:
+Let $\mathbf{M} \in \mathbb{R}^{n \times m}$. If every $2k$ columns of $\mathbf{M}$ are linearly independent, then for any $F \subseteq 2^{[m]}$ of rank $k$:
 \begin{align*}
@@
 Fix $\mathbf{x} \in \mathbb{R}^m$ and $k \geq 2$.
-Recall that the orthogonal projection onto a subspace $V \subseteq \mathbb{R}^m$ is the mapping $\Pi_V$ from $\mathbb{R}^m$ to $V$ that associates with each $\mathbf{x}$ its unique nearest point in $V$, i.e.
-$\|\mathbf{x} - \Pi_V\mathbf{x}\|_2 = \text{dist}(\mathbf{x}, V)$.
+Recall that the orthogonal projection onto a subspace $V \subseteq \mathbb{R}^m$ is the mapping $\Pi_V$ from $\mathbb{R}^m$ to $V$ that associates with each $\mathbf{x}$ its unique nearest point in $V$; i.e., $\|\mathbf{x} - \Pi_V\mathbf{x}\|_2 = \text{dist}(\mathbf{x}, V)$.
 % Since subspaces of real vector spaces are closed, we can replace inf with min in def. of orthogonal projection
@@
 To see why, note that the right-hand side of \eqref{GapUpperBound} is then strictly less than one, since $r \leq 1$ and $L_2(\mathbf{A}) \leq 1$ by \eqref{delrho}.
-By \eqref{dimLem} it then follows that $|\pi(S)| \geq \dim(\text{Span}\{\mathbf{B}_{\pi(S)}\}) \geq \dim(\text{Span}\{\mathbf{A}_{S}\}) = |S|$, with the equality due to $\mathbf{A}$ satisfying \eqref{SparkCondition}; hence, $\dim(\text{Span}\{\mathbf{B}_{\pi(S)}\}) = \dim(\text{Span}\{\mathbf{A}_{S}\})$ (since $|S| = |\pi(S)|$).
+By \eqref{dimLem}, it then follows that $|\pi(S)| \geq \dim(\text{Span}\{\mathbf{B}_{\pi(S)}\}) \geq \dim(\text{Span}\{\mathbf{A}_{S}\}) = |S|$, with the equality due to $\mathbf{A}$ satisfying \eqref{SparkCondition}; hence, $\dim(\text{Span}\{\mathbf{B}_{\pi(S)}\}) = \dim(\text{Span}\{\mathbf{A}_{S}\})$ (since $|S| = |\pi(S)|$).
 It follows that the columns of $\mathbf{B}_{\pi(S)}$ are linearly independent and, by \eqref{eqdim}:% and $\mathbf{B}_i \neq \textbf{0}$ for all $i$.
@@
 Next, fix some $E \subseteq {[m] \choose k}$ satisfying the singleton intersection property.
-Finally, form the $k$-sparse vectors $\mathbf{a}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$ with supports $S \in E$ (partitioning the $\mathbf{x}_i$ evenly among these supports so that each contains $(k-1){m \choose k}+1$ vectors $\mathbf{x}_i$) by setting the nonzero values $\mathbf{x}_i$ to be those contained in the $i$th column of $V$.
+Finally, form the $k$-sparse vectors $\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$ with supports $S \in E$ (partitioning the $\mathbf{x}_i$ evenly among these supports so that each contains $(k-1){m \choose k}+1$ vectors $\mathbf{x}_i$) by setting the nonzero values $\mathbf{x}_i$ to be those contained in the $i$th column of $V$.
 \end{proof}

### 2017-03-28 manuscripts/PNAS/chazthm_pnas.tex
more sml update

@@
 % Keywords are not mandatory, but authors are strongly encouraged to provide them. If provided, please include two to five keywords, separated by the pipe symbol, e.g:
-\keywords{Sparse linear coding, dictionary learning, compressed sensing}
+\keywords{Sparse linear coding, dictionary learning, uniqueness, compressed sensing}
 
@@
 %Equivalently, $\mathbf{Y} = \mathbf{A}\mathbf{X}$ for $\mathbf{Y}$ and $\mathbf{X}$ having the $\mathbf{y}_i$ and $\mathbf{x}_i$ as their columns, respectively.
-This representation is \textbf{stable} if for every $\delta_1, \delta_2 \geq 0$, there exists $\varepsilon = \varepsilon(\delta_1, \delta_2) \geq 0$ (with $\varepsilon > 0$ when  $\delta_1, \delta_2 > 0$) such that if a matrix $\mathbf{B}$ and $k$-sparse $\mathbf{\hat x}_1, \ldots, \mathbf{\hat x}_N \in \mathbb{R}^m$ satisfy:
+This representation is \textbf{stable} if for every $\delta_1, \delta_2 \geq 0$, there exists $\varepsilon(\delta_1, \delta_2) \geq 0$ (with $\varepsilon > 0$ when  $\delta_1, \delta_2 > 0$) such that if $\mathbf{B}$ and $k$-sparse $\mathbf{\hat x}_1, \ldots, \mathbf{\hat x}_N \in \mathbb{R}^m$ satisfy:
 \begin{align*}
@@
 % \mbox{$Y = \{\mathbf{A} \mathbf{x}_1, \ldots, \mathbf{A}\mathbf{x}_N\}$} 
-has a stable $k$-sparse linear representation in $m$ dimensions and fix $\delta_1, \delta_2$ to be the desired recovery accuracy in \eqref{def1}.
+has a stable $k$-sparse linear representation and fix $\delta_1, \delta_2$ to be the desired recovery accuracy in \eqref{def1}.
 Consider now any dataset $Z$ generated as in \eqref{LinearModel} with $\eta \leq \frac{1}{2} \varepsilon(\delta_1, \delta_2)$.
@@
 %for all $k < m$ from $N=k{m \choose k}^2$ to $N = m + m(k-1){m \choose k}$. 
-Finally, several applications are considered in our discussion, Sec.~\ref{Discussion}.
+Finally, we present several applications in Discussion Sec.~\ref{Discussion}.
 
@@
 Clearly, $L_k(\mathbf{A}) \geq L_{k'}(\mathbf{A})$ whenever $k < k'$, and for any $\mathbf{A}$ satisfying the spark condition, we have $L_{k'}(\mathbf{A}) > 0$ for all $k' \leq 2k$.
-Note that subtracting $\sqrt{k} L_k(\mathbf{A})$ [*** TODO: check is this correct ***] from one yields what is known in the compressed sensing literature as the (asymmetric) lower restricted isometry constant \cite{Blanchard2011, Foucart2009}.
+Note that the quantity $1 - \sqrt{k} L_k(\mathbf{A})$ [*** TODO: check is this correct ***] is known in the CS literature as the (asymmetric) lower restricted isometry constant \cite{Blanchard2011, Foucart2009}.
 
 % an important contribution of our work is to
-Next, we identify our combinatorial criteria on the support sets of generating codes that allow for stable sparse 
+Next, we identify the combinatorial criteria on support sets of generating codes allowing for stable sparse 
 representations.
-Let $[m]$ denote the set $\{1, \ldots, m\}$, $2^{[m]}$ its power set, and ${[m] \choose k}$ the set of subsets of $[m]$ of size $k$.
-Let $\text{Span}\{\mathbf{v}_1, \ldots, \mathbf{v}_\ell\}$ be the $\mathbb{R}$-linear span of vectors $\mathbf{v}_1, \ldots, \mathbf{v}_\ell$.
-A vector $\mathbf{x}$ is then said to be \emph{supported} on $S \subseteq [m]$ when $\mathbf{x} \in \text{Span} \{\mathbf{e}_j\}_{j\in S}$, where $\mathbf{e}_j$ are the standard $m$-dimensional basis vectors We denote by $\mathbf{M}_j$ the $j$th column of a matrix $\mathbf{M}$ and similarly by $\mathbf{M}_S$ the sub-matrix formed by the columns of $\mathbf{M}$ indexed by $S$.
-We interpret $\text{Span}\{\mathbf{M}_\emptyset\} = \{\textbf{0}\}$, where $\emptyset$ is the empty set.
-We say a hypergraph $E \subseteq 2^{[m]}$ is of \textit{rank} $k$ when $|S| \leq k$ for every $S \in E$ (and \textit{$k$-uniform} when equality holds).
+Let $[m]$ denote the set $\{1, \ldots, m\}$, its power set by $2^{[m]}$, and ${[m] \choose k}$ the set of subsets of $[m]$ of size $k$.
+Let $\text{\rm Span}\{\mathbf{v}_1, \ldots, \mathbf{v}_\ell\}$ be the $\mathbb{R}$-linear span of vectors $\mathbf{v}_1, \ldots, \mathbf{v}_\ell$.
+A vector $\mathbf{x}$ is said to be \emph{supported} on $S \subseteq [m]$, written supp$(\mathbf{x}) = S$, when $\mathbf{x} \in \text{\rm Span} \{\mathbf{e}_j\}_{j\in S}$, where $\mathbf{e}_j$ are the standard basis elements in $\mathbb R^m$.
+We denote by $\mathbf{M}_j$ the $j$th column of a matrix $\mathbf{M}$ and similarly by $\mathbf{M}_S$ the sub-matrix formed by the columns of $\mathbf{M}$ indexed by $S$ ($\text{\rm Span}\{\mathbf{M}_\emptyset\} := \{\textbf{0}\}$).
+We say a hypergraph $E \subseteq 2^{[m]}$ is of \textit{rank} $k$ when every $S \in E$ has cardinality $|S| \leq k$ (and \textit{$k$-uniform} when equality holds).
 We say $E$ is \emph{regular} when every element of $[m]$ is contained in exactly $\ell$ elements of $E$ for some $\ell > 0$ (for given $\ell$, we say $E$ is $\ell$-regular).
@@
 Fix integers $n, \ell$ and $k < m \leq \hat m$.
-Suppose $\mathbf{A}~\in~\mathbb{R}^{n \times m}$ satisfies \eqref{SparkCondition} and that $k$-sparse \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} contain at least \mbox{$(k-1){\hat m \choose k}+1$} vectors supported in general linear position on each set in some $\ell$-regular $E \subseteq {[m] \choose k}$ satisfying the SIP.
+Suppose $\mathbf{A}~\in~\mathbb{R}^{n \times m}$ satisfies the spark condition \eqref{SparkCondition} and that $k$-sparse \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} contain at least \mbox{$(k-1){\hat m \choose k}+1$} vectors supported in general linear position on each set in some $\ell$-regular $E \subseteq {[m] \choose k}$ satisfying the SIP.
 There exists a constant $C_1 > 0$ for which the following holds for all $\varepsilon < L_2(\mathbf{A}) / C_1$.
@@
 %
-for some $J \subseteq [\hat m]$ of size \mbox{$\lfloor \hat m - \ell(\hat m - m) \rfloor$}, injective map $\phi$, permutation matrix $\mathbf{P}$ and invertible diagonal matrix $\mathbf{D}$.
+for some $J \subseteq [\hat m]$ of size \mbox{$\lfloor \hat m - \ell(\hat m - m) \rfloor$}, injective map $\phi$, permutation matrix $\mathbf{P}$, and invertible diagonal matrix $\mathbf{D}$.
 %\footnote{We note that the condition $\varepsilon < L_2(\mathbf{A})$ above is necessary.
@@
 
-Furthermore if $\varepsilon < L_{2k}(\mathbf{A}) / C_1$ then $\mathbf{B}_J$ also satisfies \eqref{SparkCondition} with $L_{2k}(\mathbf{B}_J\mathbf{PD}) \geq L_{2k}(\mathbf{A}) - C_1 \varepsilon$ and we in fact have [ ** TODO ** ]:
+Furthermore, if $\varepsilon < L_{2k}(\mathbf{A}) / C_1$, then $\mathbf{B}_J$ also satisfies \eqref{SparkCondition} with $L_{2k}(\mathbf{B}_J\mathbf{PD}) \geq L_{2k}(\mathbf{A}) - C_1 \varepsilon$, and:
 \begin{align}\label{b-PDa}
@@
 In other words, the smaller the difference $\hat m - m$, the more columns and coefficients of the original $n \times m$ dictionary $\mathbf{A}$ and $m$-dimensional codes $\mathbf{x}_i$ contained (up to noise) in the appropriately scaled $n \times \hat m$ dictionary $\mathbf{B}$ and $\hat m$-dimensional codes $\mathbf{\hat x}_i$.
-In particular, if $\hat m = m$ then all columns of $\mathbf{A}$ and coefficients of each $\mathbf{x}_i$ recoverable, as per Def.~\ref{maindef}.
-For clarity of exposition, we delay defining the (explicit) constant $C_1 = C_1(\mathbf{A}, \{\mathbf{x}_i\}_{i=1}^N, E)$ until Section \ref{DUT} (\eqref{Cdef}), since it requires additional definitions not critical to the statement of our results.
+In particular, when $\hat m = m$ all columns of $\mathbf{A}$ and coefficients of each $\mathbf{x}_i$ recoverable, as per Def.~\ref{maindef}.
+For expositional clarity, we delay defining the (explicit) constant $C_1 = C_1(\mathbf{A}, \{\mathbf{x}_i\}_{i=1}^N, E)$ until Section \ref{DUT} (\eqref{Cdef}), since it requires additional definitions not critical to the statement of our results.
 
@@
 
-Since $f$ is a real analytic function, it is enough for one substitution of real numbers to satisfy $f(\mathbf{A}) \neq 0$ to conclude that its zeroes form a set with measure zero.
+Since $f$ is a real analytic function, one substitution of real numbers with $f(\mathbf{A}) \neq 0$ implies that its zeroes form a set with measure zero.
 Hence, almost every $n \times m$ real matrix $\mathbf{A}$ satisfies \eqref{SparkCondition} provided \eqref{CScondition} holds for a value of $\gamma$ for some distribution.
@@
 
-Our first step is to demonstrate how dictionary recovery \eqref{Cstable} already implies sparse code recovery \eqref{b-PDa} when $\varepsilon < L_{2k}(\mathbf{A}) / C_1$.
+Our first step is to show how dictionary recovery \eqref{Cstable} already implies sparse code recovery \eqref{b-PDa} when $\varepsilon < L_{2k}(\mathbf{A}) / C_1$.
 For all $2k$-sparse $\mathbf{x} \in \mathbb{R}^m$, the triangle inequality gives \mbox{$\|(\mathbf{A}-\mathbf{BPD})\mathbf{x}\|_2  \leq C_1\varepsilon \|\mathbf{x}\|_1 \leq C_1 \varepsilon \sqrt{2k}  \|\mathbf{x}\|_2$}.
@@
 Pigeonholing the data into its set of possible supports with respect to the matrix $\mathbf{B}$, one sees that the column space of every $\mathbf{A}_S$ with $S \in E$ must be nearby (in a sense yet to be defined; see Def.~\ref{dDef}) the column space of some $n \times k$ submatrix of $\mathbf{B}$.
-\eqref{Cstable} is then immediately implied by our result in combinatorial matrix analysis (Lem.~\ref{MainLemma}).
+\eqref{Cstable} then follows from our result in combinatorial matrix analysis (Lem.~\ref{MainLemma}).
 
@@
 \begin{definition}\label{dDef}
-For any point $\mathbf{u}$, let $\text{dist}(\mathbf{u}, V) := \inf \{\| \mathbf{u}-\mathbf{v} \|_2: \mathbf{v} \in V\}$ be the distance of $\mathbf{u}$ from the set $V$.
+For any point $\mathbf{u}$, let $\text{\rm dist}(\mathbf{u}, V) := \inf \{\| \mathbf{u}-\mathbf{v} \|_2: \mathbf{v} \in V\}$ be the distance of $\mathbf{u}$ from the set $V$.
 For subspaces $U,V \subseteq \mathbb{R}^m$, we define: %[Kato p.197]
 \begin{align}\label{d}
-d(U,V) := \sup_{\mathbf{u} \in U, \|\mathbf{u}\|_2 = 1} \text{dist}(\mathbf{u},V).
+d(U,V) := \sup_{\mathbf{u} \in U, \|\mathbf{u}\|_2 = 1} \text{\rm dist}(\mathbf{u},V).
 \end{align}
@@
 \begin{align}\label{GapUpperBound}
-d(\text{Span}\{\mathbf{A}_{S}\}, \text{Span}\{\mathbf{B}_{\pi(S)}\}) \leq \varepsilon, \ \ \text{for all $S \in E$},
+d(\text{\rm Span}\{\mathbf{A}_{S}\}, \text{\rm Span}\{\mathbf{B}_{\pi(S)}\}) \leq \varepsilon, \ \ \text{for all $S \in E$},
 \end{align}
@@
 \begin{align}
-C_2(\mathbf{A}, E) := \frac{ 2^{|E|} \max_{i \in [m]} \|\mathbf{A}_i\|_2}{ \min_{F \subseteq E} r( \{ \text{Span}\{\mathbf{A}_{S}\} \}_{S \in F}) }.
+C_2(\mathbf{A}, E) := \frac{ 2^{|E|} \max_{i \in [m]} \|\mathbf{A}_i\|_2}{ \min_{F \subseteq E} r( \{ \text{\rm Span}\{\mathbf{A}_{S}\} \}_{S \in F}) }.
 \end{align}
 
-The reader may verify that this definition leads to a value for $C_1$ consistent with that used in our proof of the case $k=1$ above.
+Note that this definition leads to a value for $C_1$ consistent with that used in our proof of the case $k=1$ above.
 
 \begin{proof}[Proof ($k < m$)] 
-%We begin by showing that for every $S \in E$ there is some $S' \in {[m] \choose k}$ for which the distance $d(\text{Span}\{\mathbf{A}_S\}, \text{Span}\{\mathbf{B}_S'\})$ is controlled by $\varepsilon$.
+%We begin by showing that for every $S \in E$ there is some $S' \in {[m] \choose k}$ for which the distance $d(\text{\rm Span}\{\mathbf{A}_S\}, \text{\rm Span}\{\mathbf{B}_S'\})$ is controlled by $\varepsilon$.
 Fix $S \in E$.
@@
 %%% No |S| = k assumption %%%
-We begin by showing that for every $S \in E$ there is some $S' \subseteq [m]$, $|S'| \leq k$ for which the distance $d(\text{Span}\{\mathbf{A}_S\}, \text{Span}\{\mathbf{B}_S'\})$ is controlled by $\varepsilon$.
+We begin by showing that for every $S \in E$ there is some $S' \subseteq [m]$, $|S'| \leq k$ for which the distance $d(\text{\rm Span}\{\mathbf{A}_S\}, \text{\rm Span}\{\mathbf{B}_S'\})$ is controlled by $\varepsilon$.
 Fix $S \in E$.
@@
 Let $\mathbf{X}$ and $\mathbf{X}'$ be the $m \times N$ matrices with columns $\mathbf{x}_i$ and $\mathbf{\hat x}_i$, respectively.
-It follows from the general linear position of the $\mathbf{x}_i$ and the linear independence of every $k$ columns of $\mathbf{A}$ that $L_k(\mathbf{AX}_{J(S)}) > 0$; that is, the columns of the $n \times k$ matrix $\mathbf{AX}_{J(S)}$ are linearly independent and thus form a basis for $\text{Span}\{\mathbf{A}_{S}\}$.
-Fixing $\mathbf{y} \in \text{Span}\{\mathbf{A}_{S}\}$, there then exists a unique $\mathbf{c} = (c_1, \ldots, c_k) \in \mathbb{R}^k$ such that $\mathbf{y} = \mathbf{AX}_{J(S)}\mathbf{c}$.
-Letting \mbox{$\mathbf{y'} = \mathbf{BX}'_{J(S)}\mathbf{c}$}, which is in $\text{Span}\{\mathbf{B}_{S'}\}$, we have:
+It follows from the general linear position of the $\mathbf{x}_i$ and the linear independence of every $k$ columns of $\mathbf{A}$ that $L_k(\mathbf{AX}_{J(S)}) > 0$; that is, the columns of the $n \times k$ matrix $\mathbf{AX}_{J(S)}$ are linearly independent and thus form a basis for $\text{\rm Span}\{\mathbf{A}_{S}\}$.
+Fixing $\mathbf{y} \in \text{\rm Span}\{\mathbf{A}_{S}\}$, there then exists a unique $\mathbf{c} = (c_1, \ldots, c_k) \in \mathbb{R}^k$ such that $\mathbf{y} = \mathbf{AX}_{J(S)}\mathbf{c}$.
+Letting \mbox{$\mathbf{y'} = \mathbf{BX}'_{J(S)}\mathbf{c}$}, which is in $\text{\rm Span}\{\mathbf{B}_{S'}\}$, we have:
 \begin{align*}
@@
 \begin{align}\label{rhs222}
-d(\text{Span}\{\mathbf{A}_S\}, \text{Span}\{\mathbf{B}_{S'}\}) 
+d(\text{\rm Span}\{\mathbf{A}_S\}, \text{\rm Span}\{\mathbf{B}_{S'}\}) 
 \leq \frac{\varepsilon}{ \min_{S \in E} L_k(\mathbf{AX}_{I(S)}) }.
 %\leq \frac{\varepsilon}{L(\mathbf{AX}_{J(S)})}.
-%&< \left( \frac{ L_2(\mathbf{A}) }{ 2^{|E|} \max_{j \in [m]} \|\mathbf{A}_j\|_2 } \right) \frac{ \min_{S \in E} L_k(\mathbf{AX}_{I(S)}) } { L(\mathbf{AX}_{J(S)}) } \min_{\substack{F \subseteq E}} r( \{ \text{Span}\{\mathbf{A}_{S}\} \}_{S \in F}) \\
+%&< \left( \frac{ L_2(\mathbf{A}) }{ 2^{|E|} \max_{j \in [m]} \|\mathbf{A}_j\|_2 } \right) \frac{ \min_{S \in E} L_k(\mathbf{AX}_{I(S)}) } { L(\mathbf{AX}_{J(S)}) } \min_{\substack{F \subseteq E}} r( \{ \text{\rm Span}\{\mathbf{A}_{S}\} \}_{S \in F}) \\
 \end{align}
@@
 We remark that our result in the deterministic case (Thm.~\ref{DeterministicUniquenessTheorem}) accounts for \emph{worst-case} noise, whereas the ``effective'' noise might be much smaller when it is sampled from a given distribution; in such cases, the constants $C_1, C_3$ in Thms.~\ref{DeterministicUniquenessTheorem},~\ref{DeterministicUniquenessTheorem2} will be much smaller with high probability.
-We note also that these results extend trivially to cases where point-wise injective nonlinearities are applied to the data. We close by outlining four diverse application areas.
+We note also that these results extend trivially to cases where point-wise injective nonlinearities are applied to the data. We close by outlining several diverse application areas.
 
@@
 Fix $\mathbf{x} \in \mathbb{R}^m$ and $k \geq 2$.
-Recall that the orthogonal projection onto a subspace $V \subseteq \mathbb{R}^m$ is the mapping $\Pi_V$ from $\mathbb{R}^m$ to $V$ that associates with each $\mathbf{x}$ its unique nearest point in $V$; i.e., $\|\mathbf{x} - \Pi_V\mathbf{x}\|_2 = \text{dist}(\mathbf{x}, V)$.
+Recall that the orthogonal projection onto a subspace $V \subseteq \mathbb{R}^m$ is the mapping $\Pi_V$ from $\mathbb{R}^m$ to $V$ that associates with each $\mathbf{x}$ its unique nearest point in $V$; i.e., $\|\mathbf{x} - \Pi_V\mathbf{x}\|_2 = \text{\rm dist}(\mathbf{x}, V)$.
 % Since subspaces of real vector spaces are closed, we can replace inf with min in def. of orthogonal projection
@@
 \begin{proof}[Proof of Main Lemma]
-We first claim $\dim(\text{Span}\{\mathbf{B}_{\pi(S)}\}) = \dim(\text{Span}\{\mathbf{A}_{S}\})$ for all $S \in E$.
+We first claim $\dim(\text{\rm Span}\{\mathbf{B}_{\pi(S)}\}) = \dim(\text{\rm Span}\{\mathbf{A}_{S}\})$ for all $S \in E$.
 To see why, note that the right-hand side of \eqref{GapUpperBound} is then strictly less than one, since $r \leq 1$ and $L_2(\mathbf{A}) \leq 1$ by \eqref{delrho}.
-By \eqref{dimLem}, it then follows that $|\pi(S)| \geq \dim(\text{Span}\{\mathbf{B}_{\pi(S)}\}) \geq \dim(\text{Span}\{\mathbf{A}_{S}\}) = |S|$, with the equality due to $\mathbf{A}$ satisfying \eqref{SparkCondition}; hence, $\dim(\text{Span}\{\mathbf{B}_{\pi(S)}\}) = \dim(\text{Span}\{\mathbf{A}_{S}\})$ (since $|S| = |\pi(S)|$).
+By \eqref{dimLem}, it then follows that $|\pi(S)| \geq \dim(\text{\rm Span}\{\mathbf{B}_{\pi(S)}\}) \geq \dim(\text{\rm Span}\{\mathbf{A}_{S}\}) = |S|$, with the equality due to $\mathbf{A}$ satisfying \eqref{SparkCondition}; hence, $\dim(\text{\rm Span}\{\mathbf{B}_{\pi(S)}\}) = \dim(\text{\rm Span}\{\mathbf{A}_{S}\})$ (since $|S| = |\pi(S)|$).
 It follows that the columns of $\mathbf{B}_{\pi(S)}$ are linearly independent and, by \eqref{eqdim}:% and $\mathbf{B}_i \neq \textbf{0}$ for all $i$.
 \begin{align}\label{eq2}
-d(\text{Span}\{\mathbf{B}_{\pi(S)}\}, \text{Span}\{\mathbf{A}_S\} ) = d(\text{Span}\{\mathbf{A}_S\}, \text{Span}\{\mathbf{B}_{\pi(S)}\}).
+d(\text{\rm Span}\{\mathbf{B}_{\pi(S)}\}, \text{\rm Span}\{\mathbf{A}_S\} ) = d(\text{\rm Span}\{\mathbf{A}_S\}, \text{\rm Span}\{\mathbf{B}_{\pi(S)}\}).
 \end{align}
@@
 Fix $F \subseteq E$.
-Since $\text{Span}\{\mathbf{B}_{\cap_{S \in F}\pi(S)}\} \subseteq \cap_{S \in F} \text{Span}\{\mathbf{B}_{\pi(S)}\}$, if $\cap_{S \in F} \text{Span}\{\mathbf{B}_{\pi(S)}\} = \textbf{0}$ then we must have $|\cap_{S \in F} \pi(S)| = 0$ (as $\mathbf{B}_i \neq \textbf{0}$ for all $i$) and \eqref{fact2} trivially holds.
+Since $\text{\rm Span}\{\mathbf{B}_{\cap_{S \in F}\pi(S)}\} \subseteq \cap_{S \in F} \text{\rm Span}\{\mathbf{B}_{\pi(S)}\}$, if $\cap_{S \in F} \text{\rm Span}\{\mathbf{B}_{\pi(S)}\} = \textbf{0}$ then we must have $|\cap_{S \in F} \pi(S)| = 0$ (as $\mathbf{B}_i \neq \textbf{0}$ for all $i$) and \eqref{fact2} trivially holds.
 Suppose then that the intersection is not the zero vector.
@@
 \begin{align}\label{randoml}
-d( \text{Span}&\{\mathbf{B}_{\cap_{S \in F}\pi(S)}\}, \text{Span}\{\mathbf{A}_{\cap_{S \in F} S}\}  ) \nonumber \\
-&\leq d\left( \cap_{S \in F} \text{Span}\{\mathbf{B}_{\pi(S)}\}, \cap_{S \in F} \text{Span}\{\mathbf{A}_{S}\} \right) \nonumber \\
-&\leq \sum_{S \in F} \frac{ d\left( \cap_{T \in F} \text{Span}\{\mathbf{B}_{\pi(T)}\},\text{Span}\{\mathbf{A}_{S}\} \right) }{ r( \{ \text{Span}\{\mathbf{A}_{T}\}_{T \in F}) } \nonumber \\
-&\leq \sum_{S \in F} \frac{ d\left( \text{Span}\{\mathbf{B}_{\pi(S)}\},\text{Span}\{\mathbf{A}_{S}\} \right) }{ r( \{ \text{Span}\{\mathbf{A}_{T}\}_{T \in F}) }\nonumber \\
-%&\leq \frac{1}{r( \{ \text{Span}\{\mathbf{A}_{S}\}_{S \in F})} \sum_{S \in F} \frac{ \varepsilon }{ L(\mathbf{AX}_{J(S)}) } \nonumber \\
-&\leq \frac{|F| \delta}{r( \{ \text{Span}\{\mathbf{A}_{S}\} \}_{S \in F})} 
-%&< L_2(\mathbf{A}) \frac{|F| }{ 2^{|E|}} \left( \frac{ \min_{\substack{F \subseteq E}} r( \{ \text{Span}\{\mathbf{A}_{S}\}_{S \in F}) }{ r( \{ \text{Span}\{\mathbf{A}_{S}\}_{S \in F}) } \right) \left( \frac{\min_{S \in E} L_k(\mathbf{AX}_{I(S)}) }{ \min_{T \in F} L(\mathbf{AX}_{J(T)}) } \right) \nonumber \\
+d( \text{\rm Span}&\{\mathbf{B}_{\cap_{S \in F}\pi(S)}\}, \text{\rm Span}\{\mathbf{A}_{\cap_{S \in F} S}\}  ) \nonumber \\
+&\leq d\left( \cap_{S \in F} \text{\rm Span}\{\mathbf{B}_{\pi(S)}\}, \cap_{S \in F} \text{\rm Span}\{\mathbf{A}_{S}\} \right) \nonumber \\
+&\leq \sum_{S \in F} \frac{ d\left( \cap_{T \in F} \text{\rm Span}\{\mathbf{B}_{\pi(T)}\},\text{\rm Span}\{\mathbf{A}_{S}\} \right) }{ r( \{ \text{\rm Span}\{\mathbf{A}_{T}\}_{T \in F}) } \nonumber \\
+&\leq \sum_{S \in F} \frac{ d\left( \text{\rm Span}\{\mathbf{B}_{\pi(S)}\},\text{\rm Span}\{\mathbf{A}_{S}\} \right) }{ r( \{ \text{\rm Span}\{\mathbf{A}_{T}\}_{T \in F}) }\nonumber \\
+%&\leq \frac{1}{r( \{ \text{\rm Span}\{\mathbf{A}_{S}\}_{S \in F})} \sum_{S \in F} \frac{ \varepsilon }{ L(\mathbf{AX}_{J(S)}) } \nonumber \\
+&\leq \frac{|F| \delta}{r( \{ \text{\rm Span}\{\mathbf{A}_{S}\} \}_{S \in F})} 
+%&< L_2(\mathbf{A}) \frac{|F| }{ 2^{|E|}} \left( \frac{ \min_{\substack{F \subseteq E}} r( \{ \text{\rm Span}\{\mathbf{A}_{S}\}_{S \in F}) }{ r( \{ \text{\rm Span}\{\mathbf{A}_{S}\}_{S \in F}) } \right) \left( \frac{\min_{S \in E} L_k(\mathbf{AX}_{I(S)}) }{ \min_{T \in F} L(\mathbf{AX}_{J(T)}) } \right) \nonumber \\
 \leq \tilde C_2 \delta, 
@@
 %
-Note that since $\delta < L_2(\mathbf{A}) / \tilde C_2$, by \eqref{delrho} the right-hand side in \eqref{rando} is strictly less than one, so \eqref{dimLem} implies that $\dim(\text{Span}\{\mathbf{B}_{\cap_{S \in F}\pi(S)}\}) \leq \dim(\text{Span}\{\mathbf{A}_{\cap_{S \in F} S}\})$ and \eqref{fact2} follows from the linear independence of the columns of $\mathbf{A}_{S}$ and $\mathbf{B}_{\pi(S)}$ for all $S \in F$.
+Note that since $\delta < L_2(\mathbf{A}) / \tilde C_2$, by \eqref{delrho} the right-hand side in \eqref{rando} is strictly less than one, so \eqref{dimLem} implies that $\dim(\text{\rm Span}\{\mathbf{B}_{\cap_{S \in F}\pi(S)}\}) \leq \dim(\text{\rm Span}\{\mathbf{A}_{\cap_{S \in F} S}\})$ and \eqref{fact2} follows from the linear independence of the columns of $\mathbf{A}_{S}$ and $\mathbf{B}_{\pi(S)}$ for all $S \in F$.
 
@@
 Lem.~\ref{NonEmptyLemma} ensures the latter case is the only possibility.
-Thus, the association $\ell \mapsto \cap_{S \in F(\ell)} \pi(S)$ defines a map $\hat \pi: [m] \to [m]$ and $\dim(\text{Span}\{\mathbf{B}_{\hat \pi(\ell)}\}) = 1$, since $\mathbf{B}_i \neq \textbf{0}$ for all $i$.
-By \eqref{eqdim}, it follows from \eqref{rando} that $d\left( \text{Span}\{\mathbf{A}_\ell\}, \text{Span}\{ \mathbf{B}_{\hat \pi(\ell)} \} \right) \leq C_2\delta$.
+Thus, the association $\ell \mapsto \cap_{S \in F(\ell)} \pi(S)$ defines a map $\hat \pi: [m] \to [m]$ and $\dim(\text{\rm Span}\{\mathbf{B}_{\hat \pi(\ell)}\}) = 1$, since $\mathbf{B}_i \neq \textbf{0}$ for all $i$.
+By \eqref{eqdim}, it follows from \eqref{rando} that $d\left( \text{\rm Span}\{\mathbf{A}_\ell\}, \text{\rm Span}\{ \mathbf{B}_{\hat \pi(\ell)} \} \right) \leq C_2\delta$.
 Since $\ell$ is arbitrary, fixing $\hat \varepsilon = C_2\delta$ it follows from \eqref{rando} that for every basis vector $\mathbf{e}_\ell \in \mathbb{R}^m$ there exists some $c'_\ell \in \mathbb{R}$ such that $\|\mathbf{A}\mathbf{e}_\ell - c'_\ell \mathbf{B}\mathbf{e}_{\hat \pi(\ell)}\|_2 \leq \hat \varepsilon < L_2(\mathbf{A})$.
@@
 \begin{align}\label{GapUpperBound}
-d(\text{Span}\{\mathbf{A}_{S}\}, \text{Span}\{\mathbf{B}_{\pi(S)}\}) \leq \varepsilon \ \ \text{for all $S \in E$},
+d(\text{\rm Span}\{\mathbf{A}_{S}\}, \text{\rm Span}\{\mathbf{B}_{\pi(S)}\}) \leq \varepsilon \ \ \text{for all $S \in E$},
 \end{align}
@@
 %
-with $R$ being the lesser of $\min_{\substack{F \subseteq E}} r( \{ \text{Span}\{\mathbf{A}_{S}\} \}_{S \in F})$ and $\min_{\substack{F \subseteq {[m'] \choose k}}} r( \{ \text{Span}\{\mathbf{B}_{S}\} \}_{S \in F})$.
+with $R$ being the lesser of $\min_{\substack{F \subseteq E}} r( \{ \text{\rm Span}\{\mathbf{A}_{S}\} \}_{S \in F})$ and $\min_{\substack{F \subseteq {[m'] \choose k}}} r( \{ \text{\rm Span}\{\mathbf{B}_{S}\} \}_{S \in F})$.
 \end{lemma}
@@
 %
-with $R$ being the lesser of $\min_{\substack{F \subseteq E}} r( \{ \text{Span}\{\mathbf{A}_{S}\} \}_{S \in F})$ and $\min_{\substack{F \subseteq {[m'] \choose k}}} r( \{ \text{Span}\{\mathbf{B}_{S}\} \}_{S \in F})$.
+with $R$ being the lesser of $\min_{\substack{F \subseteq E}} r( \{ \text{\rm Span}\{\mathbf{A}_{S}\} \}_{S \in F})$ and $\min_{\substack{F \subseteq {[m'] \choose k}}} r( \{ \text{\rm Span}\{\mathbf{B}_{S}\} \}_{S \in F})$.
 \end{proof}

### 2017-03-29 manuscripts/PNAS/chazthm_pnas.tex
lem

@@
 %%% CHAZ TODO %%%
-% replace dictionary learning with 'sparse linear coding'
 
@@
 \begin{lemma}\label{NonEmptyLemma} 
+Fix integers $\ell$ and $m \leq \hat m$.
 Suppose $E \subseteq 2^{[m]}$ is $\ell$-regular and satisfies the singleton intersection property.
-If there exists a map $\pi: E \to 2^{[m]}$ such that $\sum_{S \in E} |S| = \sum_{S \in E} |\pi(S)|$ and:
+If there exists a map $\pi: E \to 2^{[\hat m]}$ such that $\sum_{S \in E} |S| = \sum_{S \in E} |\pi(S)|$ and:
 \begin{align}\label{cond}
@@
 %
-then $\pi(E)$ is $\ell$-regular and satisfies the singleton intersection property. In particular, $|\cap_{S \in F} S| = 1$ if and only if $|\cap_{S \in F} \pi(S)| = 1$. 
+then the association $i \mapsto \cap \pi(F(i))$ defines an injective map from $[J]$ to $[\hat m]$ for some $J \subseteq [m]$ of size $\hat m - \ell(\hat m - m)$.
+In particular, if $\hat m = m$ then the map $\pi$ is induced by a permutation.
+%$\pi(E)$ is $\ell$-regular and satisfies the singleton intersection property. In particular, $|\cap_{S \in F} S| = 1$ if and only if $|\cap_{S \in F} \pi(S)| = 1$. 
 \end{lemma}
 \begin{proof}
-Fix $T = \{(j, S): j \in \pi(S), S \in E\}$.
+[* TODO * Chris rewrite for $\hat m$] Fix $T = \{(j, S): j \in \pi(S), S \in E\}$.
 We have $|T| = \sum_{S \in E} |\pi(S)| = \sum_{S \in E} |S| = \sum_{i \in [m]} \deg(i) = \ell m$ by regularity of $E$.

### 2017-03-29 manuscripts/PNAS/chazthm_pnas.tex
merge

--- 2017-03-28 manuscripts/PNAS/chazthm_pnas.tex
@@
 representations.
-Let $[m]$ denote the set $\{1, \ldots, m\}$, its power set by $2^{[m]}$, and ${[m] \choose k}$ the set of subsets of $[m]$ of size $k$.
+Let $[m]$ denote the set $\{1, \ldots, m\}$, its power set $2^{[m]}$, and ${[m] \choose k}$ the set of subsets of $[m]$ of size $k$.
 Let $\text{\rm Span}\{\mathbf{v}_1, \ldots, \mathbf{v}_\ell\}$ be the $\mathbb{R}$-linear span of vectors $\mathbf{v}_1, \ldots, \mathbf{v}_\ell$.
 A vector $\mathbf{x}$ is said to be \emph{supported} on $S \subseteq [m]$, written supp$(\mathbf{x}) = S$, when $\mathbf{x} \in \text{\rm Span} \{\mathbf{e}_j\}_{j\in S}$, where $\mathbf{e}_j$ are the standard basis elements in $\mathbb R^m$.
-We denote by $\mathbf{M}_j$ the $j$th column of a matrix $\mathbf{M}$ and similarly by $\mathbf{M}_S$ the sub-matrix formed by the columns of $\mathbf{M}$ indexed by $S$ ($\text{\rm Span}\{\mathbf{M}_\emptyset\} := \{\textbf{0}\}$).
-We say a hypergraph $E \subseteq 2^{[m]}$ is of \textit{rank} $k$ when every $S \in E$ has cardinality $|S| \leq k$ (and \textit{$k$-uniform} when equality holds).
-We say $E$ is \emph{regular} when every element of $[m]$ is contained in exactly $\ell$ elements of $E$ for some $\ell > 0$ (for given $\ell$, we say $E$ is $\ell$-regular).
+Let $\mathbf{M}_j$ be the $j$th column of a matrix $\mathbf{M}$ and similarly let $\mathbf{M}_S$ be the submatrix formed by the columns of $\mathbf{M}$ indexed by $S$ (we set $\text{\rm Span}\{\mathbf{M}_\emptyset\} := \{\textbf{0}\}$).
+We say a hypergraph $E \subseteq 2^{[m]}$ has \textit{rank} $k$ when every $S \in E$ has cardinality $|S| \leq k$ (and \textit{$k$-uniform} when equality holds).
+We also say $E$ is \emph{regular} when every element of $[m]$ is contained in exactly $\ell$ elements of $E$ for some $\ell > 0$ (for given $\ell$, we say $E$ is $\ell$-regular).
 
 \begin{definition}
-Given a hypergraph $E \subseteq 2^{[m]}$, the \textbf{star} $F(i)$ centered at $i$ is the set of $S \in E$ containing $i$.
-We say $E$ satisfies the \textbf{singleton intersection property} (SIP) when $\cap_{S \in F(i)} S = \{i\}$ for all $i \in [m]$.
+Given a hypergraph $E \subseteq 2^{[m]}$, the \textbf{star} $F(i)$ centered at $i$ is the collection of $S \in E$ containing $i$.
+We say $E$ satisfies the \textbf{singleton intersection property} (\textbf{SIP}) when $\cap_{S \in F(i)} S = \{i\}$ for all $i \in [m]$.
 \end{definition}
@@
 % Fix positive integers $k, \ell, m, m', n, p$ satisfying $k < m$ and $p \leq m \leq m' \leq (\ell m - p) / (\ell - 1)$. 
-Fix integers $n, \ell$ and $k < m \leq \hat m$.
+Fix integers $n, \ell$, and $k < m \leq \hat m$.
 Suppose $\mathbf{A}~\in~\mathbb{R}^{n \times m}$ satisfies the spark condition \eqref{SparkCondition} and that $k$-sparse \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} contain at least \mbox{$(k-1){\hat m \choose k}+1$} vectors supported in general linear position on each set in some $\ell$-regular $E \subseteq {[m] \choose k}$ satisfying the SIP.
@@
 In particular, when $\hat m = m$ all columns of $\mathbf{A}$ and coefficients of each $\mathbf{x}_i$ recoverable, as per Def.~\ref{maindef}.
-For expositional clarity, we delay defining the (explicit) constant $C_1 = C_1(\mathbf{A}, \{\mathbf{x}_i\}_{i=1}^N, E)$ until Section \ref{DUT} (\eqref{Cdef}), since it requires additional definitions not critical to the statement of our results.
+For expositional clarity, we delay defining the (explicit) constant $C_1 = C_1(\mathbf{A}, \{\mathbf{x}_i\}_{i=1}^N, E)$ until Section \ref{DUT} (\eqref{Cdef}).
+% , since it requires additional definitions not critical to the statement of our results.
 
@@
 \begin{corollary}\label{DeterministicUniquenessCorollary}
-Given $n, m$, $k < m$, and a regular hypergraph $E \subseteq 2^{[m]}$ of rank $k$ satisfying the singleton intersection property, there are $N =  |E| \left[ (k-1){m \choose k}+1 \right]$ vectors \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} such that every matrix $\mathbf{A} \in \mathbb{R}^{n \times m}$ satisfying \eqref{SparkCondition} generates a dataset $Y = \{\mathbf{A}\mathbf{x}_1, \ldots, \mathbf{A}\mathbf{x}_N\}$ with a stable $k$-sparse representation in $m$ dimensions.
+Given $n, m$, $k < m$, and a regular hypergraph $E \subseteq {[m] \choose k}$ of rank $k$ with the SIP, there are $N =  |E| \left[ (k-1){m \choose k}+1 \right]$ vectors \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} such that every matrix $\mathbf{A} \in \mathbb{R}^{n \times m}$ satisfying \eqref{SparkCondition} generates a dataset $Y = \{\mathbf{A}\mathbf{x}_1, \ldots, \mathbf{A}\mathbf{x}_N\}$ with a stable $k$-sparse representation in $m$ dimensions.
 \end{corollary}
@@
 %
-where $\gamma$ is a positive constant that depends on the particular distribution from which the entries of $\mathbf{A}$ are sampled i.i.d. (many ensembles suffice, e.g. \cite[Sec.~4]{Baraniuk08}).
+in which $\gamma$ is a positive constant that depends on the particular distribution from which the entries of $\mathbf{A}$ are sampled i.i.d. (many ensembles suffice, e.g. \cite[Sec.~4]{Baraniuk08}).
 
-In fact, the spark condition can be made explicit.
+We motivate our next theorem by the following observation:  the spark condition can be made explicit.
 Let $\mathbf{A}$  be the $n \times m$ matrix of $nm$ indeterminates $A_{ij}$.
@@
 
-Since $f$ is a real analytic function, one substitution of real numbers with $f(\mathbf{A}) \neq 0$ implies that its zeroes form a set with measure zero.
+Since $f$ is a real analytic function, one substitution of real numbers with $f(\mathbf{A}) \neq 0$ implies that its zeroes form a set of (Borel) measure zero.
 Hence, almost every $n \times m$ real matrix $\mathbf{A}$ satisfies \eqref{SparkCondition} provided \eqref{CScondition} holds for a value of $\gamma$ for some distribution.

### 2017-03-29 manuscripts/PNAS/chazthm_pnas.tex
more edits

@@
 
-Since $f$ is a real analytic function, one substitution of real numbers with $f(\mathbf{A}) \neq 0$ implies that its zeroes form a set of (Borel) measure zero.
+Since $f$ is a real analytic function, having one substitution of real numbers with $f(\mathbf{A}) \neq 0$ implies that its zeroes form a set of (Borel) measure zero.
 Hence, almost every $n \times m$ real matrix $\mathbf{A}$ satisfies \eqref{SparkCondition} provided \eqref{CScondition} holds for a value of $\gamma$ for some distribution.
@@
 
-In fact, in the case $k=1$ we can relax our assumptions even further and assume that the matrix $\mathbf{B}$ has only at least as many columns as $\mathbf{A}$; as we will see, the conclusions of Thm.~\ref{DeterministicUniquenessTheorem} then hold for some $n \times m$ submatrix of $\mathbf{B}$.
+%In fact, in the case $k=1$ we can relax our assumptions even further and assume that the matrix $\mathbf{B}$ has only at least as many columns as $\mathbf{A}$; as we will see, the conclusions of Thm.~\ref{DeterministicUniquenessTheorem} then hold for some $n \times m$ submatrix of $\mathbf{B}$.
 [*** ???
@@
 \begin{proof}[Proof ($k=1$)]
-Note that the only 1-uniform hypergraph satisfying the singleton intersection property is $[m]$; hence, we have $\mathbf{x}_i = c_i \mathbf{e}_i$ for $c_i \in \mathbb{R} \setminus \{\mathbf{0}\}$, $i \in [m]$.
-In this case we may take $C_1$ to be any value satisfying $C_1^{-1} \leq \min_{j \in [m]} |c_{j}|$.
+The only 1-uniform hypergraph satisfying the singleton intersection property is $[m]$; hence, we have $\mathbf{x}_i = c_i \mathbf{e}_i$ for $c_i \in \mathbb{R} \setminus \{\mathbf{0}\}$, $i \in [m]$.
+In this case we may take $C_1 = 1/ \min_{\ell \in [m]} |c_{\ell}|$.
 
-Fix $\mathbf{A} \in \mathbb{R}^{n \times m}$ satisfying \eqref{SparkCondition} and suppose that for some $\mathbf{B} \in \mathbb{R}^{n \times m'}$ ($m' \geq m$) and $1$-sparse $\mathbf{\hat x}_i \in \mathbb{R}^{m'}$ we have  $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\hat x}_i\|_2 \leq \varepsilon < L_2(\mathbf{A}) / C_1$ for all $i$.
-Then there are $c'_1, \ldots, c'_m \in \mathbb{R}$ and $\pi: [m] \to [m']$ with:
+Fix $\mathbf{A} \in \mathbb{R}^{n \times m}$ satisfying \eqref{SparkCondition} and suppose that for some $\mathbf{B} \in \mathbb{R}^{n \times \hat m}$ ($\hat m \geq m$) and $1$-sparse $\mathbf{\hat x}_i \in \mathbb{R}^{\hat m}$ we have  $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\hat x}_i\|_2 \leq \varepsilon < L_2(\mathbf{A}) / C_1$ for all $i$.
+Then there are $c'_1, \ldots, c'_m \in \mathbb{R}$ and $\pi: [m] \to [\hat m]$ with:
 \begin{align}\label{1D}
@@
 
-We  now show that $\pi$ is injective (and thus is a permutation if $m' = m$).
+We  now show that $\pi$ is injective (and thus is a permutation if $\hat m = m$).
 Suppose that $\pi(i) = \pi(j) = \ell$ for some $i \neq j$ and $\ell$.
@@
 %
-which contradicts the upper bound $\varepsilon < L_2(\mathbf{A})/C_1$.
+which contradicts the bound $\varepsilon < L_2(\mathbf{A})/C_1$.
 Hence, the map $\pi$ is injective.
-Setting $J = \pi([m])$ and letting $P = \left( \mathbf{e}_{\pi(1)} \cdots \mathbf{e}_{\pi(m)}\right)$ and $D = \text{diag}(\frac{c'_1}{c_1},\ldots,\frac{c'_m}{c_m})$, we see that \eqref{1D} becomes, for all $j \in [m]$:
+Setting $J = \pi([m])$ and letting $P = \left( \mathbf{e}_{\pi(1)} \cdots \mathbf{e}_{\pi(m)}\right)$ and $D = \text{diag}(\frac{\hat{c}_1}{c_1},\ldots,\frac{\hat{c}_m}{c_m})$, we see that \eqref{1D} becomes, for all $j \in [m]$:
 \begin{align*}%\label{k=1result}
@@
 \begin{align}\label{d}
-d(U,V) := \sup_{\mathbf{u} \in U, \|\mathbf{u}\|_2 = 1} \text{\rm dist}(\mathbf{u},V).
+d(U,V) := \sup_{\mathbf{u} \in U, \ \|\mathbf{u}\|_2 = 1} \text{\rm dist}(\mathbf{u},V).
 \end{align}
@@
 \eqref{Cstable} is a simple consequence of this last fact, which actually constitutes the proof of the theorem for the case $k=1$.
-We present this special case now before restating the above arguments in greater detail.
+% We present this special case now before restating the above arguments in greater detail.
 
@@
 [Effective computation of stable datasets, at least in principle.]
+[maybe smooth analysis something here]
 
@@
 \begin{lemma}\label{MainLemma2}
-Fix integers $n$ and $k < m \leq m'$ and suppose $\mathbf{A}~\in~\mathbb{R}^{n \times m}$ and $\mathbf{B} \in \mathbb{R}^{n \times m'}$ both satisfiy \eqref{SparkCondition}.
+Fix integers $n$ and $k < m \leq \hat m$ and suppose $\mathbf{A}~\in~\mathbb{R}^{n \times m}$ and $\mathbf{B} \in \mathbb{R}^{n \times \hat m}$ both satisfiy \eqref{SparkCondition}.
 There exists a constant $C_4 > 0$ for which for all $\varepsilon < L_2(\mathbf{A}) / C_4$ the following holds.
-If for some $E \subseteq2^{[m]}$ satisfying the singleton intersection property there exists a size-preserving map $\pi: E \mapsto 2^{[m']}$ satisfying:
+If for some $E \subseteq2^{[m]}$ satisfying the singleton intersection property there exists a size-preserving map $\pi: E \mapsto 2^{[\hat m]}$ satisfying:
 \begin{align}\label{GapUpperBound}
@@
 %
-then for some $J \in {[m'] \choose m}$, permutation matrix $\mathbf{P}$ and invertible diagonal matrix $\mathbf{D}$, we have:
+then for some $J \in {[\hat m] \choose m}$, permutation matrix $\mathbf{P}$ and invertible diagonal matrix $\mathbf{D}$, we have:
 \begin{align}\label{MainLemmaBPD}
@@
 The constant $C_4$ is given by:
-\begin{align}\label{Cdefm'}
+\begin{align}\label{Cdefm}
 C_4 := \frac{2^{|E|}}{R} \max_{j \in [m]} \|\mathbf{A}_j\|_2
@@
 %
-with $R$ being the lesser of $\min_{\substack{F \subseteq E}} r( \{ \text{\rm Span}\{\mathbf{A}_{S}\} \}_{S \in F})$ and $\min_{\substack{F \subseteq {[m'] \choose k}}} r( \{ \text{\rm Span}\{\mathbf{B}_{S}\} \}_{S \in F})$.
+with $R$ being the lesser of $\min_{\substack{F \subseteq E}} r( \{ \text{\rm Span}\{\mathbf{A}_{S}\} \}_{S \in F})$ and $\min_{\substack{F \subseteq {[\hat m] \choose k}}} r( \{ \text{\rm Span}\{\mathbf{B}_{S}\} \}_{S \in F})$.
 \end{lemma}
@@
 \begin{proof}
-The proof is very similar to the case $m' = m$, the difference being that now we may not invoke Lem.~\ref{NonEmptyLemma} (which requires $m' = m$) to infer from \eqref{fact2} that $| \cap_{S \in F(i)} \pi(S) | = 1$ for all stars $F(i)$.
+The proof is very similar to the case $\hat m = m$, the difference being that now we may not invoke Lem.~\ref{NonEmptyLemma} (which requires $\hat m = m$) to infer from \eqref{fact2} that $| \cap_{S \in F(i)} \pi(S) | = 1$ for all stars $F(i)$.
 We circumvent this issue by instead assuming the spark condition on $\mathbf{B}$, which allows us to swap the roles of $\mathbf{A}$ and $\mathbf{B}$ in the arguments leading to the derivation of \eqref{fact2} to prove the opposite inequality for every star $F(i)$.
 Of course, this requires that the constant $C_4$  depend on $\mathbf{B}$.
-By these arguments we establish that $| \cap_{S \in F(i)} \pi(S) | = 1$ for all stars $F(i)$, yielding an injective map $\hat \pi: [m] \to [m']$.
+By these arguments we establish that $| \cap_{S \in F(i)} \pi(S) | = 1$ for all stars $F(i)$, yielding an injective map $\hat \pi: [m] \to [\hat m]$.
 The result then follows from the proof of the case $k=1$.
@@
 \begin{proof}[Proof of Thm.~\ref{DeterministicUniquenessTheorem2}]
-The proof is the same as that of the case $m' = m$, only now we establish a map $\pi: E \to {[m'] \choose k}$ by pigeonholing $(k-1){m' \choose k} + 1$ vectors with respect to holes $[m']$ and eventually applying Lem.~\ref{MainLemma2} instead of Lem.~\ref{MainLemma}.
+The proof is the same as that of the case $\hat m = m$, only now we establish a map $\pi: E \to {[\hat m] \choose k}$ by pigeonholing $(k-1){\hat m \choose k} + 1$ vectors with respect to holes $[\hat m]$ and eventually applying Lem.~\ref{MainLemma2} instead of Lem.~\ref{MainLemma}.
 
 In this case the constant $C_3$ is given by:
-\begin{align}\label{Cdefm'}
+\begin{align}\label{Cdefm}
 C_3 := \frac{2^{|E|} \max_{j \in [m]} \|\mathbf{A}_j\|_2}{ R \min_{S \in E} L_k(\mathbf{AX}_{I(S)}) },
@@
 %
-with $R$ being the lesser of $\min_{\substack{F \subseteq E}} r( \{ \text{\rm Span}\{\mathbf{A}_{S}\} \}_{S \in F})$ and $\min_{\substack{F \subseteq {[m'] \choose k}}} r( \{ \text{\rm Span}\{\mathbf{B}_{S}\} \}_{S \in F})$.
+with $R$ being the lesser of $\min_{\substack{F \subseteq E}} r( \{ \text{\rm Span}\{\mathbf{A}_{S}\} \}_{S \in F})$ and $\min_{\substack{F \subseteq {[\hat m] \choose k}}} r( \{ \text{\rm Span}\{\mathbf{B}_{S}\} \}_{S \in F})$.
 \end{proof}

### 2017-03-29 manuscripts/PNAS/chazthm_pnas.tex
more good ol fashioned SR-ing

@@
 \begin{align}\label{LinearModel}
-\mathbf{z}_i = \mathbf{A}\mathbf{x}_i + \mathbf{n}_i,\indent \text{$i=1,\ldots,N$},
+\mathbf{z}_i = \mathbf{A}\mathbf{x}_i + \mathbf{n}_i,\ \ \  \text{$i=1,\ldots,N$},
 \end{align}
@@
 \begin{align*}
-\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\hat x}_i\|_2 \leq \varepsilon, \ \ \text{for all $i$},
+\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\hat x}_i\|_2 \leq \varepsilon,\ \ \   \text{for all $i$},
 \end{align*}
@@
 
-\begin{proposition}
-For every $k < m$, there is a regular $k$-uniform hypergraph that satisfies the singleton intersection property.
-\end{proposition}
-Consider, for instance, the set of consecutive intervals of length $k$ in some cyclic order on $[m]$.
+It is easy to verify that for every $k < m$, there is a regular $k$-uniform hypergraph that satisfies the SIP; for instance, consecutive intervals of length $k$ in some cyclic order on $[m]$.
+%\begin{proposition}
+%For every $k < m$, there is a regular $k$-uniform hypergraph that satisfies the singleton intersection property.
+%\end{proposition}
 
 We say that a set of $k$-sparse vectors is in \emph{general linear position} when any $k$ of them are linearly independent.
-The following is the technical statement of our main result.
+The following is the precise statement of our main result.
 
 \begin{theorem}\label{DeterministicUniquenessTheorem}
-% Fix positive integers $k, \ell, m, m', n, p$ satisfying $k < m$ and $p \leq m \leq m' \leq (\ell m - p) / (\ell - 1)$. 
-Fix integers $n, \ell$, and $k < m \leq \hat m$.
-Suppose $\mathbf{A}~\in~\mathbb{R}^{n \times m}$ satisfies the spark condition \eqref{SparkCondition} and that $k$-sparse \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} contain at least \mbox{$(k-1){\hat m \choose k}+1$} vectors supported in general linear position on each set in some $\ell$-regular $E \subseteq {[m] \choose k}$ satisfying the SIP.
+Fix integers $n, \ell$, and $k < m$.
+Suppose $\mathbf{A}~\in~\mathbb{R}^{n \times m}$ satisfies the spark condition \eqref{SparkCondition} and that $k$-sparse \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} contain at least \mbox{$(k-1){\hat m \choose k}+1$} vectors supported in general linear position on each set in some $\ell$-regular $E \subseteq {[m] \choose k}$ with the SIP.
 There exists a constant $C_1 > 0$ for which the following holds for all $\varepsilon < L_2(\mathbf{A}) / C_1$.
 
-Every matrix $\mathbf{B} \in \mathbb{R}^{n \times \hat m}$ and $k$-sparse $\mathbf{\hat x}_1, \ldots, \mathbf{\hat x}_N \in \mathbb{R}^{\hat m}$ with  \mbox{$\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\hat x}_i\|_2 \leq \varepsilon$} for all $i$ necessarily satisfies:
+Every matrix $\mathbf{B} \in \mathbb{R}^{n \times m}$ and $k$-sparse $\mathbf{\hat x}_1, \ldots, \mathbf{\hat x}_N \in \mathbb{R}^{m}$ with  \mbox{$\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\hat x}_i\|_2 \leq \varepsilon$} for all $i$ necessarily satisfies:
 \begin{align}\label{Cstable}
-\|\mathbf{A}_{\phi(j)} - (\mathbf{B}_{J}\mathbf{PD})_j\|_2 \leq C_1 \varepsilon, \ \ \text{for $j = 1, \ldots, |J|$},
+\|\mathbf{A}_j - (\mathbf{B}\mathbf{PD})_j\|_2 \leq C_1 \varepsilon,\ \ \   \text{for all $j \in [m]$},
 \end{align}
-%
-for some $J \subseteq [\hat m]$ of size \mbox{$\lfloor \hat m - \ell(\hat m - m) \rfloor$}, injective map $\phi$, permutation matrix $\mathbf{P}$, and invertible diagonal matrix $\mathbf{D}$.
-%\footnote{We note that the condition $\varepsilon < L_2(\mathbf{A})$ above is necessary.
-When \mbox{$\mathbf{A}$ = $I$} and $\mathbf{x}_i = \mathbf{e}_i$, it turns out that $C_1 = 1$ and there is a $\mathbf{B}$ and $1$-sparse $\mathbf{\hat x}_i$ with $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\hat x}_i\|_2 \leq \varepsilon$ violating \eqref{Cstable}.}
+for some permutation matrix $\mathbf{P}$ and invertible diagonal $\mathbf{D}$.
 
-Furthermore, if $\varepsilon < L_{2k}(\mathbf{A}) / C_1$, then $\mathbf{B}_J$ also satisfies \eqref{SparkCondition} with $L_{2k}(\mathbf{B}_J\mathbf{PD}) \geq L_{2k}(\mathbf{A}) - C_1 \varepsilon$, and:
+Furthermore, if $\varepsilon < L_{2k}(\mathbf{A}) / C_1$, then $\mathbf{B}$ also satisfies \eqref{SparkCondition} with $L_{2k}(\mathbf{B}\mathbf{PD}) \geq L_{2k}(\mathbf{A}) - C_1 \varepsilon$, and:
 \begin{align}\label{b-PDa}
-\|\mathbf{x}_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\hat x}_i\|_1 &\leq  \left( \frac{ 1+C_1 \|\mathbf{x}_i\|_1 }{ L_{2k}(\mathbf{A}) -  C_1\varepsilon } \right) \varepsilon,
- \ \ \text{for all $i \in [N]$}.
+\|\mathbf{x}_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\hat x}_i\|_1 &\leq  \left( \frac{ 1+C_1 \|\mathbf{x}_i\|_1 }{ L_{2k}(\mathbf{A}) -  C_1\varepsilon } \right) \varepsilon,\ \ \   \text{for all $i \in [N]$}.
 \end{align}
@@
 
-In other words, the smaller the difference $\hat m - m$, the more columns and coefficients of the original $n \times m$ dictionary $\mathbf{A}$ and $m$-dimensional codes $\mathbf{x}_i$ contained (up to noise) in the appropriately scaled $n \times \hat m$ dictionary $\mathbf{B}$ and $\hat m$-dimensional codes $\mathbf{\hat x}_i$.
+%\begin{theorem}\label{DeterministicUniquenessTheorem}
+%Fix integers $n, \ell$, and $k < m \leq \hat m$.
+Suppose $\mathbf{A}~\in~\mathbb{R}^{n \times m}$ satisfies the spark condition \eqref{SparkCondition} and that $k$-sparse \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} contain at least \mbox{$(k-1){\hat m \choose k}+1$} vectors supported in general linear position on each set in some $\ell$-regular $E \subseteq {[m] \choose k}$ satisfying the SIP.
+There exists a constant $C_1 > 0$ for which the following holds for all $\varepsilon < L_2(\mathbf{A}) / C_1$.
+%
+%Every matrix $\mathbf{B} \in \mathbb{R}^{n \times \hat m}$ and $k$-sparse $\mathbf{\hat x}_1, \ldots, \mathbf{\hat x}_N \in \mathbb{R}^{\hat m}$ with  \mbox{$\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\hat x}_i\|_2 \leq \varepsilon$} for all $i$ necessarily satisfies:
+%\begin{align}\label{Cstable}
+%\|\mathbf{A}_{\phi(j)} - (\mathbf{B}_{J}\mathbf{PD})_j\|_2 \leq C_1 \varepsilon,\ \ \   \text{for $j = 1, \ldots, |J|$},
+%\end{align}
+%%
+%for some $J \subseteq [\hat m]$ of size \mbox{$\lfloor \hat m - \ell(\hat m - m) \rfloor$}, injective map $\phi$, permutation matrix $\mathbf{P}$, and invertible diagonal matrix $\mathbf{D}$.
+%%\footnote{We note that the condition $\varepsilon < L_2(\mathbf{A})$ above is necessary.
+When \mbox{$\mathbf{A}$ = $I$} and $\mathbf{x}_i = \mathbf{e}_i$, it turns out that $C_1 = 1$ and there is a $\mathbf{B}$ and $1$-sparse $\mathbf{\hat x}_i$ with $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\hat x}_i\|_2 \leq \varepsilon$ violating \eqref{Cstable}.}
+%
+%Furthermore, if $\varepsilon < L_{2k}(\mathbf{A}) / C_1$, then $\mathbf{B}_J$ also satisfies \eqref{SparkCondition} with $L_{2k}(\mathbf{B}_J\mathbf{PD}) \geq L_{2k}(\mathbf{A}) - C_1 \varepsilon$, and:
+%\begin{align}\label{b-PDa}
+%\|\mathbf{x}_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\hat x}_i\|_1 &\leq  \left( \frac{ 1+C_1 \|\mathbf{x}_i\|_1 }{ L_{2k}(\mathbf{A}) -  C_1\varepsilon } \right) \varepsilon,\ \ \   \text{for all $i \in [N]$}.
+%\end{align}
+%\end{theorem}
+
+%In other words, the smaller the difference $\hat m - m$, the more columns and coefficients of the original $n \times m$ dictionary $\mathbf{A}$ and $m$-dimensional codes $\mathbf{x}_i$ contained (up to noise) in the appropriately scaled $n \times \hat m$ dictionary $\mathbf{B}$ and $\hat m$-dimensional codes $\mathbf{\hat x}_i$.
 In particular, when $\hat m = m$ all columns of $\mathbf{A}$ and coefficients of each $\mathbf{x}_i$ recoverable, as per Def.~\ref{maindef}.
-For expositional clarity, we delay defining the (explicit) constant $C_1 = C_1(\mathbf{A}, \{\mathbf{x}_i\}_{i=1}^N, E)$ until Section \ref{DUT} (\eqref{Cdef}).
+
+For expositional clarity, we delay defining the (explicit) constant $C_1 = C_1(\mathbf{A}, \{\mathbf{x}_i\}_{i=1}^N, E)$ until Section \ref{DUT} (\eqref{Cdef1}).
 % , since it requires additional definitions not critical to the statement of our results.
@@
 \begin{corollary}\label{DeterministicUniquenessCorollary}
-Given $n, m$, $k < m$, and a regular hypergraph $E \subseteq {[m] \choose k}$ of rank $k$ with the SIP, there are $N =  |E| \left[ (k-1){m \choose k}+1 \right]$ vectors \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} such that every matrix $\mathbf{A} \in \mathbb{R}^{n \times m}$ satisfying \eqref{SparkCondition} generates a dataset $Y = \{\mathbf{A}\mathbf{x}_1, \ldots, \mathbf{A}\mathbf{x}_N\}$ with a stable $k$-sparse representation in $m$ dimensions.
+Given $n, m$, $k < m$, and a regular hypergraph $E \subseteq {[m] \choose k}$ with the SIP, there are $N =  |E| \left[ 1 + (k-1){m \choose k} \right]$ vectors \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} such that every matrix $\mathbf{A} \in \mathbb{R}^{n \times m}$ satisfying \eqref{SparkCondition} generates a dataset $Y = \{\mathbf{A}\mathbf{x}_1, \ldots, \mathbf{A}\mathbf{x}_N\}$ with a stable $k$-sparse representation in $m$ dimensions.
 \end{corollary}
@@
 %\end{proposition}
-Note that if $E$ is an $\ell$-regular hypergraph of rank $k$ satisfying the singleton intersection property then $|E| \geq \ell m/k$.
-This is easy to see by noting that $|E|k \geq \sum_{S \in E}|S| = \sum_{i \in [m]} \deg(i) = \ell m$.
+Note that if $E$ is an $\ell$-regular hypergraph of rank $k$ satisfying the singleton intersection property, then $|E| \geq \ell m/k$.
+This is easy to see from $|E|k \geq \sum_{S \in E}|S| = \sum_{i \in [m]} \deg(i) = \ell m$.
 In certain cases, there exist simple constructions achieving this minimum; for example, when $k = \sqrt{m}$ one can take $E$ to be the rows and columns formed by arranging the elements of $[m]$ in a square grid.
+In light of Cor.~\ref{DeterministicUniquenessCorollary}, it would be  interesting problem to determine minimal such $E$.
 
-It is straightforward to provide a probabilistic extension of Thm.~\ref{DeterministicUniquenessTheorem} using the following fact in random matrix theory.
+There are other less direct consequences of Thm.~\ref{DeterministicUniquenessTheorem} to stability in sparse linear coding.
+The following implication relates the result to more common optimization formulations of the problem.
+
+\begin{theorem}
+Fix integers $n, \ell$ and $k < m$.
+Suppose $\mathbf{A}~\in~\mathbb{R}^{n \times m}$ satisfies the spark condition and that $k$-sparse \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} contain at least \mbox{$(k+1)\left[ 1 + (k-1){ m \choose k} \right]$} vectors supported in general linear position on each set in some $\ell$-regular $E \subseteq {[m] \choose k}$ satisfying the SIP.
+There exists a constant $C_1 > 0$ for which the following holds for all $\varepsilon < L_2(\mathbf{A}) / C_1$.
+
+Every solution to the constrained $\ell_0$ optimization problem:
+\begin{align}\label{minsum}
+\arg \min_{ \substack{ \mathbf{B} \in \mathbb{R}^{n \times m} \\ \mathbf{\hat x}_i, \ldots, \mathbf{\hat x}_N \in \mathbb{R}^{m} } } \sum_{i = 1}^N \|\mathbf{\hat x}_i\|_0 \ \ \text{s.t.} \ \ \|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\hat x}_i\|_2 \leq \varepsilon, \ \ \text{$i \in [N]$},
+\end{align}
+necessarily satisfies \eqref{Cstable}.
+\end{theorem}
+
+\begin{proof}
+[*** Incomplete ***]
+We argue for a lower bound on the number of $k$-sparse vectors $\mathbf{\hat x}_i$ and then apply Thm.~\ref{DeterministicUniquenessCorollary}.
+Let $n_p$ be the number of vectors $\mathbf{\hat x}_i$ satisfying $\|\mathbf{\hat x}_i\|_0 = p$, so that $\sum_{p = 1}^{\hat m} n_p = N$.
+Since the $\mathbf{x}_i$ are all $k$-sparse, by \eqref{minsum} we have:
+\begin{align}
+k \sum_{p = 1}^{m} n_p = kN \geq \sum_{i=1}^N \|\mathbf{x}_i\|_0 \geq \sum_{i=1}^N \|\mathbf{\hat x}_i\|_0 = \sum_{p=1}^{m} p n_p 
+\end{align}
+\[\implies \sum_{p \leq k} (k-p)n_p \geq \sum_{p > k} (p-k) n_p.\]
+Hence,
+\begin{align}
+k \sum_{p \leq k} n_p \geq \sum_{p \leq k} (k-p)n_p \geq \sum_{p > k} (p-k) n_p \geq \sum_{p > k} n_p
+\end{align}
+\[ = N - \sum_{p \leq k} n_p \implies \sum_{p \leq k} n_p \geq N / (k+1).\]
+
+That is, at least $N / (k+1)$ of the vectors $\mathbf{\hat x}_i$ are $k$-sparse.
+Therefore, there is some $N' \subseteq [N]$ for which for each $S \in E$ there are $(k-1){m \choose k}+1$ of the vectors $\mathbf{x}_i$ with $i \in [N']$ supported on $S$ and for which $\mathbf{\hat x}_i$ is $k$-sparse for all $i \in [N']$.
+By Thm.~\ref{DeterministicUniquenessCorollary}, \eqref{Cstable} follows.
+\end{proof}
+
+Another straightforward application of Thm.~\ref{DeterministicUniquenessTheorem} is a probabilistic extension that uses the following fact in random matrix theory.
 A random matrix $\mathbf{A} \in \mathbb{R}^{n \times m}$ satisfies \eqref{SparkCondition} with probability one (or with ``high probability'' for discrete variables)
@@
 \end{align}
-%
 in which $\gamma$ is a positive constant that depends on the particular distribution from which the entries of $\mathbf{A}$ are sampled i.i.d. (many ensembles suffice, e.g. \cite[Sec.~4]{Baraniuk08}).
 
-We motivate our next theorem by the following observation:  the spark condition can be made explicit.
+In fact, 
+% We motivate our next theorem by the following observation:  
+the spark condition can be made explicit.
 Let $\mathbf{A}$  be the $n \times m$ matrix of $nm$ indeterminates $A_{ij}$.
@@
 Fix $n, m$, and $k < m$.
-There is a polynomial in the entries of $\mathbf{A}$ and the $\mathbf{x}_i$ with the following property:  if the polynomial evaluates to a nonzero number and at least \mbox{$(k-1){m \choose k}+1$} of the resulting vectors $\mathbf{x}_i$ are supported on each $S \in E$ for some regular $k$-uniform $E \subseteq 2^{[m]}$ satisfying the singleton intersection property, then $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$ (Def.~\ref{Uniqueness}).
+There is a polynomial in the entries of $\mathbf{A}$ and the $\mathbf{x}_i$ with the following property:  if the polynomial evaluates to a nonzero number and at least \mbox{$(k-1){m \choose k}+1$} of the resulting vectors $\mathbf{x}_i$ are supported on each $S \in E$ for some regular $E \subseteq {[m] \choose k}$ with the SIP, then $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$ (Def.~\ref{maindef}).
 In particular, either no substitutions impart to $Y$ this property or all but a Borel set of measure zero do.
@@
 \begin{corollary}\label{ProbabilisticCor}
-Fix $n, m$, and $k$ satisfying \eqref{CScondition} for $\gamma = \gamma_0$, and let the entries of the matrix $\mathbf{A} \in \mathbb{R}^{n \times m}$ and $k$-sparse vectors $\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$ be drawn independently from probability measures absolutely continuous with respect to the standard Borel measure $\mu$.
-If at least $(k-1){m \choose k} + 1$ of the vectors $\mathbf{x}_i$ are supported on each $S \in E$ for some regular $k$-uniform $E \subseteq 2^{[m]}$ satisfying the singleton intersection property, then $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$ with probability one.
+Fix $n, m$, and $k$ satisfying \eqref{CScondition} for $\gamma = \gamma_0$, and let the entries of $\mathbf{A} \in \mathbb{R}^{n \times m}$ and $k$-sparse $\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$ be drawn independently from probability measures absolutely continuous with respect to the standard Borel measure $\mu$.
+If at least $(k-1){m \choose k} + 1$ of the vectors $\mathbf{x}_i$ are supported on each $S \in E$ for a regular $E \subseteq {[m] \choose k}$ with the SIP, then $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$ with probability one.
 \end{corollary}
@@
 
-\begin{proof}[Proof ($k=1$)]
-The only 1-uniform hypergraph satisfying the singleton intersection property is $[m]$; hence, we have $\mathbf{x}_i = c_i \mathbf{e}_i$ for $c_i \in \mathbb{R} \setminus \{\mathbf{0}\}$, $i \in [m]$.
-In this case we may take $C_1 = 1/ \min_{\ell \in [m]} |c_{\ell}|$.
+\begin{proof}[Proof of Thm.~\ref{DeterministicUniquenessCorollary} for $k=1$]
+The only 1-uniform hypergraph with the SIP is $[m]$; hence, we have $\mathbf{x}_i = c_i \mathbf{e}_i$ for $c_i \in \mathbb{R} \setminus \{\mathbf{0}\}$, $i \in [m]$.
+In this case, we may take $C_1 = 1/ \min_{\ell \in [m]} |c_{\ell}|$.
 
@@
 \begin{align}\label{1D}
-\|c_j\mathbf{A}_j - c'_j\mathbf{B}_{\pi(j)}\|_2 \leq \varepsilon, \ \ \text{for all $j$}.
+\|c_j\mathbf{A}_j - c'_j\mathbf{B}_{\pi(j)}\|_2 \leq \varepsilon,\ \ \   \text{for all $j$}.
 \end{align} 
@@
 \begin{align}\label{dimLem}
-d(U,V) < 1 \implies \dim(U) \leq \dim(V).
+d(U,V) < 1 \implies \dim(U) \leq \dim(V),
 \end{align}
@@
 \begin{align}\label{GapUpperBound}
-d(\text{\rm Span}\{\mathbf{A}_{S}\}, \text{\rm Span}\{\mathbf{B}_{\pi(S)}\}) \leq \varepsilon, \ \ \text{for all $S \in E$},
+d(\text{\rm Span}\{\mathbf{A}_{S}\}, \text{\rm Span}\{\mathbf{B}_{\pi(S)}\}) \leq \varepsilon,\ \ \   \text{for all $S \in E$},
 \end{align}
@@
 \begin{align}\label{MainLemmaBPD}
-\|\mathbf{A}_j - (\mathbf{BPD})_j\|_2 \leq C_2 \varepsilon, \indent \text{for } j \in [m].
+\|\mathbf{A}_j - (\mathbf{BPD})_j\|_2 \leq C_2 \varepsilon, \ \ \  \text{for } j \in [m].
 \end{align}
@@
 The constant $C_1$ in Thm.~\ref{DeterministicUniquenessTheorem} is then given by:
-\begin{align}
+\begin{align}\label{Cdef1}
 C_1(\mathbf{A}, \{\mathbf{x}_i\}_{i=1}^N, E) := \frac{ C_2(\mathbf{A}, E) } { \min_{S \in E} L_k(\mathbf{AX}_{I(S)}) },
@@
 %
-where $\mathbf{X}$ is the $m \times N$ matrix with columns $\mathbf{x}_i$ and $I(S) := \{i : \text{supp}(\mathbf{x}_i) = S\}$.\footnote{We can be sure $C_1 > 0$ is well-defined (provided $C_2$ is well-defined) since $L_k(\mathbf{A}), L_k(\mathbf{X}_{I(S)}) > 0$ by the spark condition and general linear position of the $\mathbf{x}_i$; hence $\|\mathbf{A}_j\|_2 > 0$ for all $j$ and for all $S \in E$ we have $\|\mathbf{AX}_{I(S)}\mathbf{c}\|_2 \geq L_k(\mathbf{A})\|\mathbf{X}_{I(S)}\mathbf{c}\|_2 \geq L_k(\mathbf{A}) L_k(\mathbf{X}_{I(S)})\|\mathbf{c}\|_2$ for all $k$-sparse $\mathbf{c}$ and therefore $L_k(\mathbf{AX}_{I(S)}) \geq L_k(\mathbf{A}) L_k(\mathbf{X}_{I(S)}) > 0$.} The constant $C_2 = C_2(\mathbf{A}, E)$ is defined explicitly below in terms of the following technical quantity based on one used in \cite{Deutsch12} to analyze the convergence of the alternating projections algorithm for projecting a point onto the intersection of a set of subspaces.
+where $\mathbf{X}$ is the $m \times N$ matrix with columns $\mathbf{x}_i$ and $I(S) := \{i : \text{supp}(\mathbf{x}_i) = S\}$.\footnote{We can be sure $C_1 > 0$ is well-defined (provided $C_2$ is well-defined) since $L_k(\mathbf{A}), L_k(\mathbf{X}_{I(S)}) > 0$ by the spark condition and general linear position of the $\mathbf{x}_i$; hence $\|\mathbf{A}_j\|_2 > 0$ for all $j$ and for all $S \in E$ we have $\|\mathbf{AX}_{I(S)}\mathbf{c}\|_2 \geq L_k(\mathbf{A})\|\mathbf{X}_{I(S)}\mathbf{c}\|_2 \geq L_k(\mathbf{A}) L_k(\mathbf{X}_{I(S)})\|\mathbf{c}\|_2$ for all $k$-sparse $\mathbf{c}$ and therefore $L_k(\mathbf{AX}_{I(S)}) \geq L_k(\mathbf{A}) L_k(\mathbf{X}_{I(S)}) > 0$.} The constant $C_2 = C_2(\mathbf{A}, E)$ is defined below in terms of a technical quantity related to one used in \cite{Deutsch12} to analyze the convergence of the alternating projections algorithm.
+% for projecting a point onto the intersection of a set of subspaces. 
 We use it to bound the distance between a point and the intersection of a set of subspaces given an upper bound on its distance from each subspace individually.
@@
 The constant $C_2$ in Lem.~\ref{MainLemma} is then given by:  % \footnote{Note that $C_2 > 0$ is well-defined since $r > 0$ by definition.}
-\begin{align}
+\begin{align}\label{Cdef2}
 C_2(\mathbf{A}, E) := \frac{ 2^{|E|} \max_{i \in [m]} \|\mathbf{A}_i\|_2}{ \min_{F \subseteq E} r( \{ \text{\rm Span}\{\mathbf{A}_{S}\} \}_{S \in F}) }.
 \end{align}
+%Note that when $k=1$ the constant $C_1$ is consistent with the value in our proof of the case $k=1$.
 
-Note that this definition leads to a value for $C_1$ consistent with that used in our proof of the case $k=1$ above.
-
-\begin{proof}[Proof ($k < m$)] 
+\begin{proof}[Proof of Thm.~\ref{DeterministicUniquenessCorollary} for $k < m$] 
 %We begin by showing that for every $S \in E$ there is some $S' \in {[m] \choose k}$ for which the distance $d(\text{\rm Span}\{\mathbf{A}_S\}, \text{\rm Span}\{\mathbf{B}_S'\})$ is controlled by $\varepsilon$.
@@
 
-Phrased 
-in the language of Hadamard \cite{Hadamard1902}),
-
  In this note, we generalize the approach of \cite{Hillar15} to the uniqueness of solutions to Prob.~\ref{InverseProblem} for noisy measurements while also reducing the number of required samples.
@@
 Moreover, if solutions are constrained to satisfy \eqref{SparkCondition}, then only an upper bound on the number of dictionary elements need be taken as given.
-We remark that our result in the deterministic case (Thm.~\ref{DeterministicUniquenessTheorem}) accounts for \emph{worst-case} noise, whereas the ``effective'' noise might be much smaller when it is sampled from a given distribution; in such cases, the constants $C_1, C_3$ in Thms.~\ref{DeterministicUniquenessTheorem},~\ref{DeterministicUniquenessTheorem2} will be much smaller with high probability.
-We note also that these results extend trivially to cases where point-wise injective nonlinearities are applied to the data. We close by outlining several diverse application areas.
+We remark that our result in the deterministic case (Thm.~\ref{DeterministicUniquenessTheorem}) accounts for \emph{worst-case} noise, whereas the ``effective'' noise might be much smaller when it is sampled from a given distribution; in such cases, the constants $C_1, C_3$ in our theorems %Thms.~\ref{DeterministicUniquenessTheorem},~\ref{DeterministicUniquenessTheorem2}
+will be much smaller with high probability.
+We note also that these results extend trivially to cases where point-wise injective nonlinearities are applied to the data. 
+We close with several application areas.
 
@@
 %We encourage researchers to extend our results and tighten these parameters.
-
-Mention sparse matrix factorization.
-
-[Effective computation of stable datasets, at least in principle.]
+Phrased in the language of Hadamard \cite{Hadamard1902}),  Mention sparse matrix factorization. [Effective computation of stable datasets, at least in principle.]
 [maybe smooth analysis something here]
@@
 Furthermore, our guarantees justify the hypothesis of \cite{Coulter10} and \cite{Isely10} that sparse codes passed through a communication bottleneck in the brain can be recovered from random projections via (unsupervised) biologically plausible sparse dictionary learning (e.g., \cite{rehnsommer2007, rozell2007neurally, hu2014hebbian}).
-
-Invariance in neuroscience: Pitts \cite{pitts1947}.
+Invariance: \cite{pitts1947}.
 %TODO: add reproduction of response propeties in olfactory cortex?
@@
 
-\acknow{We thank Friedrich Sommer for turning our attention to the dictionary learning problem, Darren Rhea for sharing early explorations, and Ian Morris for posting identity \eqref{SubspaceMetricSameDim} online.}
+\acknow{We thank Friedrich Sommer for introducing us to sparse dictionary learning, Darren Rhea for sharing early explorations, and Ian Morris for posting \eqref{eqdim} online.}
 
@@
 \begin{align}
-\|\Pi_{V_k}\Pi_{V_{k-1}}\cdots\Pi_{V_1} \mathbf{x} - \Pi_V\mathbf{x}\|_2 \leq z \|\mathbf{x}\|_2, %  \indent \text{for } \mathbf{x} \in \mathbb{R}^m,
+\|\Pi_{V_k}\Pi_{V_{k-1}}\cdots\Pi_{V_1} \mathbf{x} - \Pi_V\mathbf{x}\|_2 \leq z \|\mathbf{x}\|_2, %  \ \ \  \text{for } \mathbf{x} \in \mathbb{R}^m,
 \end{align}
@@
 \begin{align}\label{cond}
-|\cap_{S \in F} \pi(S)| \leq |\cap_{S \in F} S | \ \ \text{for all } F \subseteq E,
+|\cap_{S \in F} \pi(S)| \leq |\cap_{S \in F} S |,\ \ \   \text{for all } F \subseteq E,
 \end{align}
@@
 \begin{align}\label{fact2}
-|\bigcap_{S \in F} \pi(S)| \leq |\bigcap_{S \in F} S |, \ \ \text{for all } \ F \subseteq E.
+|\bigcap_{S \in F} \pi(S)| \leq |\bigcap_{S \in F} S |,\ \ \   \text{for all } \ F \subseteq E.
 \end{align}
@@
 \begin{align}\label{GapUpperBound}
-d(\text{\rm Span}\{\mathbf{A}_{S}\}, \text{\rm Span}\{\mathbf{B}_{\pi(S)}\}) \leq \varepsilon \ \ \text{for all $S \in E$},
+d(\text{\rm Span}\{\mathbf{A}_{S}\}, \text{\rm Span}\{\mathbf{B}_{\pi(S)}\}) \leq \varepsilon, \ \ \   \text{for all $S \in E$},
 \end{align}
@@
 \begin{align}\label{MainLemmaBPD}
-\|\mathbf{A}_j - (\mathbf{BPD})_j\|_2 \leq C_4 \varepsilon, \indent \text{for } j \in [m].
+\|\mathbf{A}_j - (\mathbf{BPD})_j\|_2 \leq C_4 \varepsilon, \ \ \  \text{for } j \in [m].
 \end{align}

### 2017-03-30 manuscripts/PNAS/chazthm_pnas.tex
getting closer

@@
 In other words, whenever enough sparsely represented data generated from a dictionary (satisfying a spark condition) are observed, the original codes and dictionary are uniquely determined up to an error that is commensurate with the measurement noise.
-Applications of this result include:  (1) a sufficient diversity of sparse codes sent through a random linear compressive channel are unique, (2) the sparse linear coding problem is well-posed in the sense of Hadamard \cite{Hadamard1902}, and (3) an explanation for universal representation of natural signals in neuroscience.
+Applications of this result include:  1) a sufficient diversity of sparse codes sent through a random linear compressive channel are unique, 2) the sparse linear coding problem is well-posed in the sense of Hadamard \cite{Hadamard1902}, and 3) an explanation for universal representation of natural signals in neuroscience.
 
@@
 \begin{proof}
-Something quick here.
+Given Thm.\ref{DeterministicUniquenessTheorem}, one needs only to produce sparse codes in general linear position.
+However, this is straightforward (e.g., with a ``Vandermonde'' construction \cite{Hillar15}).
 \end{proof}
@@
 %\end{proposition}
-Note that if $E$ is an $\ell$-regular hypergraph of rank $k$ satisfying the singleton intersection property, then $|E| \geq \ell m/k$.
-This is easy to see from $|E|k \geq \sum_{S \in E}|S| = \sum_{i \in [m]} \deg(i) = \ell m$.
-In certain cases, there exist simple constructions achieving this minimum; for example, when $k = \sqrt{m}$ one can take $E$ to be the rows and columns formed by arranging the elements of $[m]$ in a square grid.
-In light of Cor.~\ref{DeterministicUniquenessCorollary}, it would be  interesting problem to determine minimal such $E$.
+As mentioned above, it is easy to construct such $E$ with $|E| = m$, implying the lower bound for sample size $N$ from the introduction.
+Note that if $E$ is an $\ell$-regular hypergraph of rank $k$ satisfying the SIP, then $|E| \geq \ell m/k$: \[|E|k \geq \sum_{S \in E}|S| = \sum_{i \in [m]} \deg(i) = \ell m.\] In certain cases, there are simple constructions achieving this minimum; for example, when $k = \sqrt{m}$ one can take $E$ to be the rows and columns formed by arranging $[m]$ in a square grid.
+In light of Cor.~\ref{DeterministicUniquenessCorollary}, it would be interesting to determine other minimal such $E$.
 
 There are other less direct consequences of Thm.~\ref{DeterministicUniquenessTheorem} to stability in sparse linear coding.
-The following implication relates the result to more common optimization formulations of the problem.
+The following implication relates the result to more common optimization formulations.
 
 \begin{theorem}
-Fix integers $n, \ell$ and $k < m$.
-Suppose $\mathbf{A}~\in~\mathbb{R}^{n \times m}$ satisfies the spark condition and that $k$-sparse \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} contain at least \mbox{$(k+1)\left[ 1 + (k-1){ m \choose k} \right]$} vectors supported in general linear position on each set in some $\ell$-regular $E \subseteq {[m] \choose k}$ satisfying the SIP.
+Fix integers $n, \ell$, and $k < m$.
+Suppose $\mathbf{A}~\in~\mathbb{R}^{n \times m}$ satisfies the spark condition \eqref{SparkCondition} and that $k$-sparse \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} contain at least \mbox{$(k+1)\left[ 1 + (k-1){ m \choose k} \right]$} vectors supported in general linear position on each set in some $\ell$-regular $E \subseteq {[m] \choose k}$ satisfying the SIP.
 There exists a constant $C_1 > 0$ for which the following holds for all $\varepsilon < L_2(\mathbf{A}) / C_1$.
 
-Every solution to the constrained $\ell_0$ optimization problem:
+Every solution $B$ to the constrained $\ell_0$ optimization:
 \begin{align}\label{minsum}
@@
 \begin{proof}
+We argue for a lower bound on the number of $k$-sparse vectors $\mathbf{\hat x}_i$ and then apply Thm.~\ref{DeterministicUniquenessCorollary}. 
 [*** Incomplete ***]
-We argue for a lower bound on the number of $k$-sparse vectors $\mathbf{\hat x}_i$ and then apply Thm.~\ref{DeterministicUniquenessCorollary}.
 Let $n_p$ be the number of vectors $\mathbf{\hat x}_i$ satisfying $\|\mathbf{\hat x}_i\|_0 = p$, so that $\sum_{p = 1}^{\hat m} n_p = N$.
@@
 
-Another straightforward application of Thm.~\ref{DeterministicUniquenessTheorem} is a probabilistic extension that uses the following fact in random matrix theory.
+Another straightforward application of Thm.~\ref{DeterministicUniquenessTheorem} is a probabilistic extension that uses the following often used application of random matrix theory to compressed sensing.
 A random matrix $\mathbf{A} \in \mathbb{R}^{n \times m}$ satisfies \eqref{SparkCondition} with probability one (or with ``high probability'' for discrete variables)
@@
 
-[ ** TODO ** elaborate a little on these? ]
+% [ ** TODO ** elaborate a little on these? ]
 
@@
 Fix $\mathbf{A} \in \mathbb{R}^{n \times m}$ satisfying \eqref{SparkCondition} and suppose that for some $\mathbf{B} \in \mathbb{R}^{n \times \hat m}$ ($\hat m \geq m$) and $1$-sparse $\mathbf{\hat x}_i \in \mathbb{R}^{\hat m}$ we have  $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\hat x}_i\|_2 \leq \varepsilon < L_2(\mathbf{A}) / C_1$ for all $i$.
-Then there are $c'_1, \ldots, c'_m \in \mathbb{R}$ and $\pi: [m] \to [\hat m]$ with:
+Then there are $\hat{c}_1, \ldots, \hat{c}_m \in \mathbb{R}$ and $\pi: [m] \to [\hat m]$ with:
 \begin{align}\label{1D}
-\|c_j\mathbf{A}_j - c'_j\mathbf{B}_{\pi(j)}\|_2 \leq \varepsilon,\ \ \   \text{for all $j$}.
+\|c_j\mathbf{A}_j - \hat{c}_j\mathbf{B}_{\pi(j)}\|_2 \leq \varepsilon,\ \ \   \text{for all $j$}.
 \end{align} 
-Note that $c'_j \neq 0$ for all $j$ since otherwise by \eqref{delrho} and definition of $C_1$ we would have $\|c_j\mathbf{A}_j\|_2 < \min_{\ell \in [m]}\|c_{\ell}\mathbf{A}_{\ell}\|_2$.
+Note that $\hat{c}_j \neq 0$ for all $j$ since otherwise by \eqref{delrho} and definition of $C_1$ we would have $\|c_j\mathbf{A}_j\|_2 < \min_{\ell \in [m]}\|c_{\ell}\mathbf{A}_{\ell}\|_2$.
 
@@
 Suppose that $\pi(i) = \pi(j) = \ell$ for some $i \neq j$ and $\ell$.
-Then, $\|c_{j}\mathbf{A}_{j} - c'_{j}\mathbf{B}_{\ell}\|_2 \leq \varepsilon$ and $\|c_{i}\mathbf{A}_{i} - c'_{i} \mathbf{B}_{\ell}\|_2  \leq \varepsilon$.
-Scaling and summing these inequalities by $|c'_{i}|$ and $|c'_{j}|$, respectively, and applying the triangle inequality, we obtain:
+Then, $\|c_{j}\mathbf{A}_{j} - \hat{c}_{j}\mathbf{B}_{\ell}\|_2 \leq \varepsilon$ and $\|c_{i}\mathbf{A}_{i} - \hat{c}_{i} \mathbf{B}_{\ell}\|_2  \leq \varepsilon$.
+Scaling and summing these inequalities by $|\hat{c}_{i}|$ and $|\hat{c}_{j}|$, respectively, and applying the triangle inequality, we obtain:
 \begin{align*}%\label{contra}
-(|c'_{i}| + |c'_{j}|) \varepsilon
-&\geq\|\mathbf{A}(c'_{i}c_{j} \mathbf{e}_{j} - c'_{j}c_{i}\mathbf{e}_{i})\|_2 \nonumber \\ 
-&\geq  \left( |c'_{i}| + |c'_{j}| \right) L_2(\mathbf{A}) \min_{\ell \in [m]} |c_\ell |,
+(|\hat{c}_{i}| + |\hat{c}_{j}|) \varepsilon
+&\geq\|\mathbf{A}(\hat{c}_{i}c_{j} \mathbf{e}_{j} - \hat{c}_{j}c_{i}\mathbf{e}_{i})\|_2 \nonumber \\ 
+&\geq  \left( |\hat{c}_{i}| + |\hat{c}_{j}| \right) L_2(\mathbf{A}) \min_{\ell \in [m]} |c_\ell |,
 \end{align*}
@@
 \|\mathbf{A}_j - (\mathbf{B}_J\mathbf{PD})_j\|_2 
-= \|\mathbf{A}_j - \frac{c'_j}{c_j}\mathbf{B}_{\pi(j)}\|_2 
+= \|\mathbf{A}_j - \frac{\hat{c}_j}{c_j}\mathbf{B}_{\pi(j)}\|_2 
 \leq \frac{\varepsilon}{|c_j|} 
@@
 
-Our result in combinatorial matrix analysis is the following, which we derive by the following arguments (see the Supplemental for the full proof).
+Our result in combinatorial matrix analysis is the following.
+
+%, which we derive by the following arguments (see the Supplemental for the full proof).
 First, we show that the aforementioned proximity between $k$-dimensional subspaces implies a proximity between smaller subspaces spanned by columns of $\mathbf{A}$ indexed by the intersections of sets in $E$ and those spanned by as many or fewer columns of $\mathbf{B}$.
@@
 %
-then there exists some permutation matrix $\mathbf{P}$ and invertible diagonal matrix $\mathbf{D}$ such that:
+then there exists a permutation matrix $\mathbf{P}$ and invertible diagonal matrix $\mathbf{D}$ with:
 \begin{align}\label{MainLemmaBPD}
@@
 Fix $S \in E$.
-Since there are $(k-1){m \choose k}+1$ vectors $\mathbf{x}_i$ supported on $S$, the pigeon-hole principle implies that there exists some $S' \in {[m] \choose k}$ and some set of $k$ indices $J(S)$ such that the supports of all $\mathbf{x}_i$ and $\mathbf{\hat x}_i$ with $i \in J(S)$ are contained in $S$ and $S'$, respectively.
+Since there are $(k-1){m \choose k}+1$ vectors $\mathbf{x}_i$ supported on $S$, the pigeon-hole principle implies that there exists some $S' \in {[m] \choose k}$ and some set of $k$ indices $I(S)$ such that the supports of all $\mathbf{x}_i$ and $\mathbf{\hat x}_i$ with $i \in I(S)$ are contained in $S$ and $S'$, respectively.
 
-Let $\mathbf{X}$ and $\mathbf{X}'$ be the $m \times N$ matrices with columns $\mathbf{x}_i$ and $\mathbf{\hat x}_i$, respectively.
+Let $\mathbf{X}$ and $\mathbf{\hat{X}}$ be the $m \times N$ matrices with columns $\mathbf{x}_i$ and $\mathbf{\hat x}_i$, respectively.
 It follows from the general linear position of the $\mathbf{x}_i$ and the linear independence of every $k$ columns of $\mathbf{A}$ that $L_k(\mathbf{AX}_{J(S)}) > 0$; that is, the columns of the $n \times k$ matrix $\mathbf{AX}_{J(S)}$ are linearly independent and thus form a basis for $\text{\rm Span}\{\mathbf{A}_{S}\}$.
 Fixing $\mathbf{y} \in \text{\rm Span}\{\mathbf{A}_{S}\}$, there then exists a unique $\mathbf{c} = (c_1, \ldots, c_k) \in \mathbb{R}^k$ such that $\mathbf{y} = \mathbf{AX}_{J(S)}\mathbf{c}$.
-Letting \mbox{$\mathbf{y'} = \mathbf{BX}'_{J(S)}\mathbf{c}$}, which is in $\text{\rm Span}\{\mathbf{B}_{S'}\}$, we have:
+Letting \mbox{$\mathbf{\hat{y}} = \mathbf{B\hat{X}}_{J(S)}\mathbf{c}$}, which is in $\text{\rm Span}\{\mathbf{B}_{S'}\}$, we have:
 \begin{align*}
-\|\mathbf{y} - \mathbf{y'}\|_2 
-&= \|\sum_{i=1}^k c_i(\mathbf{AX}_{J(S)} - \mathbf{BX}'_{J(S)})_i\|_2
+\|\mathbf{y} - \mathbf{\hat{y}}\|_2 
+&= \|\sum_{i=1}^k c_i(\mathbf{AX}_{J(S)} - \mathbf{B\hat{X}}_{J(S)})_i\|_2
 \leq \varepsilon \sum_{i=1}^k |c_i| \\
@@
 
- In this note, we generalize the approach of \cite{Hillar15} to the uniqueness of solutions to Prob.~\ref{InverseProblem} for noisy measurements while also reducing the number of required samples.
+In this note, we generalize the approach of \cite{Hillar15} for showing uniqueness in Prob.~\ref{InverseProblem} to the case of noisy measurements while also reducing the sufficient number of samples.
 % from $N=k{m \choose k}^2$ to $N = m(k-1){m \choose k}+m$. 
@@
 We remark that our result in the deterministic case (Thm.~\ref{DeterministicUniquenessTheorem}) accounts for \emph{worst-case} noise, whereas the ``effective'' noise might be much smaller when it is sampled from a given distribution; in such cases, the constants $C_1, C_3$ in our theorems %Thms.~\ref{DeterministicUniquenessTheorem},~\ref{DeterministicUniquenessTheorem2}
-will be much smaller with high probability.
-We note also that these results extend trivially to cases where point-wise injective nonlinearities are applied to the data. 
+will be smaller. %We note also that these results extend trivially to cases where point-wise injective nonlinearities are applied to the data. 
 We close with several application areas.
@@
 Guarantees such as those offered by our theorems allow any such device to be equivalent to any other (having different initial parameters and data samples) as long as enough data originate from a statistically identical system.
+
+As a final remark, we hope that researchers in sparse linear coding continue to improve on the bounds and constants here.
 

### 2017-03-30 manuscripts/PNAS/chazthm_pnas.tex
chaz changes

@@
 Let $\mathbf{M}_j$ be the $j$th column of a matrix $\mathbf{M}$ and similarly let $\mathbf{M}_S$ be the submatrix formed by the columns of $\mathbf{M}$ indexed by $S$ (we set $\text{\rm Span}\{\mathbf{M}_\emptyset\} := \{\textbf{0}\}$).
-We say a hypergraph $E \subseteq 2^{[m]}$ has \textit{rank} $k$ when every $S \in E$ has cardinality $|S| \leq k$ (and \textit{$k$-uniform} when equality holds).
+[ ** TODO ** the hypergraph is the pair $([m],E)$, not just $E$ ] We say a hypergraph $E \subseteq 2^{[m]}$ is \textit{$k$-uniform} when every $S \in E$ has cardinality $k$.
 We also say $E$ is \emph{regular} when every element of $[m]$ is contained in exactly $\ell$ elements of $E$ for some $\ell > 0$ (for given $\ell$, we say $E$ is $\ell$-regular).
@@
 %\end{proposition}
-As mentioned above, it is easy to construct such $E$ with $|E| = m$, implying the lower bound for sample size $N$ from the introduction.
-Note that if $E$ is an $\ell$-regular hypergraph of rank $k$ satisfying the SIP, then $|E| \geq \ell m/k$: \[|E|k \geq \sum_{S \in E}|S| = \sum_{i \in [m]} \deg(i) = \ell m.\] In certain cases, there are simple constructions achieving this minimum; for example, when $k = \sqrt{m}$ one can take $E$ to be the rows and columns formed by arranging $[m]$ in a square grid.
+Note that every $\ell$-regular hypergraph $E \subseteq {[m] \choose k}$ satisfies: \[|E|k = \sum_{S \in E}|S| = \sum_{i \in [m]} \deg(i) = \ell m.\] As mentioned above, it is easy to construct such an $E$ satisfying the SIP with $|E| = m$, implying the lower bound for sample size $N$ from the introduction.
+In certain cases, the SIP can be achieved with $|E| < m$; for example, when $k = \sqrt{m}$ one can take $E$ to be the rows and columns formed by arranging $[m]$ in a square grid.
 In light of Cor.~\ref{DeterministicUniquenessCorollary}, it would be interesting to determine other minimal such $E$.
+[ ** TODO ** can we show for every $k, m$ that there is an $E$ satisfying the SIP with $|E| = \ell m/k$ for every $\ell$ such that $\ell m/k$ is an integer?
+Then lower bound on $N$ comes from the smallest such $\ell$.]
 
@@
 Fix integers $n, \ell$, and $k < m$.
-Suppose $\mathbf{A}~\in~\mathbb{R}^{n \times m}$ satisfies the spark condition \eqref{SparkCondition} and that $k$-sparse \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} contain at least \mbox{$(k+1)\left[ 1 + (k-1){ m \choose k} \right]$} vectors supported in general linear position on each set in some $\ell$-regular $E \subseteq {[m] \choose k}$ satisfying the SIP.
+Suppose $\mathbf{A}~\in~\mathbb{R}^{n \times m}$ satisfies the spark condition \eqref{SparkCondition} and that $k$-sparse \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} contain at least \mbox{$k \left[ 1 + (k-1){ m \choose k} \right]$} vectors supported in general linear position on each set in some $\ell$-regular $E \subseteq {[m] \choose k}$ satisfying the SIP.
 There exists a constant $C_1 > 0$ for which the following holds for all $\varepsilon < L_2(\mathbf{A}) / C_1$.
 
-Every solution $B$ to the constrained $\ell_0$ optimization:
+Every solution $\mathbf{B}, \mathbf{\hat x}_i, \ldots, \mathbf{\hat x}_N$ to the constrained $\ell_0$ optimization:
 \begin{align}\label{minsum}
-\arg \min_{ \substack{ \mathbf{B} \in \mathbb{R}^{n \times m} \\ \mathbf{\hat x}_i, \ldots, \mathbf{\hat x}_N \in \mathbb{R}^{m} } } \sum_{i = 1}^N \|\mathbf{\hat x}_i\|_0 \ \ \text{s.t.} \ \ \|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\hat x}_i\|_2 \leq \varepsilon, \ \ \text{$i \in [N]$},
+\arg \min \sum_{i = 1}^N \|\mathbf{\hat x}_i\|_0 \ \ \text{s.t.} \ \ \|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\hat x}_i\|_2 \leq \varepsilon, \ \ \text{$i \in [N]$},
 \end{align}
-necessarily satisfies \eqref{Cstable}.
+necessarily satisfies \eqref{Cstable} and \eqref{b-PDa}.
 \end{theorem}
@@
 [*** Incomplete ***]
-Let $n_p$ be the number of vectors $\mathbf{\hat x}_i$ satisfying $\|\mathbf{\hat x}_i\|_0 = p$, so that $\sum_{p = 1}^{\hat m} n_p = N$.
+Let $n_p$ be the number of vectors $\mathbf{\hat x}_i$ satisfying $\|\mathbf{\hat x}_i\|_0 = p$, so that $\sum_{p = 1}^{m} n_p = N$.
 Since the $\mathbf{x}_i$ are all $k$-sparse, by \eqref{minsum} we have:
@@
 \end{align}
-\[\implies \sum_{p \leq k} (k-p)n_p \geq \sum_{p > k} (p-k) n_p.\]
+\[\implies \sum_{p = 1}^k (k-p)n_p \geq \sum_{p = k+1}^{\hat m} (p-k) n_p.\]
 Hence,
 \begin{align}
-k \sum_{p \leq k} n_p \geq \sum_{p \leq k} (k-p)n_p \geq \sum_{p > k} (p-k) n_p \geq \sum_{p > k} n_p
+(k-1) \sum_{p =1}^k n_p \geq \sum_{p = 1}^k (k-p)n_p \geq \sum_{p = k+1}^{m} (p-k) n_p
 \end{align}
-\[ = N - \sum_{p \leq k} n_p \implies \sum_{p \leq k} n_p \geq N / (k+1).\]
+\[ \geq \sum_{p = k+1}^{m} n_p = N - \sum_{p = 1}^k n_p \implies \sum_{p =1}^k n_p \geq N / k.\]
 
-That is, at least $N / (k+1)$ of the vectors $\mathbf{\hat x}_i$ are $k$-sparse.
+That is, at least $N / k$ of the vectors $\mathbf{\hat x}_i$ are $k$-sparse.
 Therefore, there is some $N' \subseteq [N]$ for which for each $S \in E$ there are $(k-1){m \choose k}+1$ of the vectors $\mathbf{x}_i$ with $i \in [N']$ supported on $S$ and for which $\mathbf{\hat x}_i$ is $k$-sparse for all $i \in [N']$.
-By Thm.~\ref{DeterministicUniquenessCorollary}, \eqref{Cstable} follows.
+By Thm.~\ref{DeterministicUniquenessCorollary}, \eqref{Cstable} and \eqref{b-PDa} follow.
 \end{proof}
@@
 
-The above arguments can be easily modified to prove the following variation of Lem.~\ref{MainLemma}, key to proving Thm.~\ref{DeterministicUniquenessTheorem2}.
+%The above arguments can be easily modified to prove the following variation of Lem.~\ref{MainLemma}, key to proving Thm.~\ref{DeterministicUniquenessTheorem2}.
 
-\begin{lemma}\label{MainLemma2}
-Fix integers $n$ and $k < m \leq \hat m$ and suppose $\mathbf{A}~\in~\mathbb{R}^{n \times m}$ and $\mathbf{B} \in \mathbb{R}^{n \times \hat m}$ both satisfiy \eqref{SparkCondition}.
+%\begin{lemma}\label{MainLemma2}
+%Fix integers $n$ and $k < m \leq \hat m$ and suppose $\mathbf{A}~\in~\mathbb{R}^{n \times m}$ and $\mathbf{B} \in \mathbb{R}^{n \times \hat m}$ both satisfiy \eqref{SparkCondition}.
 There exists a constant $C_4 > 0$ for which for all $\varepsilon < L_2(\mathbf{A}) / C_4$ the following holds.
 If for some $E \subseteq2^{[m]}$ satisfying the singleton intersection property there exists a size-preserving map $\pi: E \mapsto 2^{[\hat m]}$ satisfying:
-\begin{align}\label{GapUpperBound}
-d(\text{\rm Span}\{\mathbf{A}_{S}\}, \text{\rm Span}\{\mathbf{B}_{\pi(S)}\}) \leq \varepsilon, \ \ \   \text{for all $S \in E$},
-\end{align}
+%\begin{align}\label{GapUpperBound}
+%d(\text{\rm Span}\{\mathbf{A}_{S}\}, \text{\rm Span}\{\mathbf{B}_{\pi(S)}\}) \leq \varepsilon, \ \ \   \text{for all $S \in E$},
+%\end{align}
 %
-then for some $J \in {[\hat m] \choose m}$, permutation matrix $\mathbf{P}$ and invertible diagonal matrix $\mathbf{D}$, we have:
-\begin{align}\label{MainLemmaBPD}
-\|\mathbf{A}_j - (\mathbf{BPD})_j\|_2 \leq C_4 \varepsilon, \ \ \  \text{for } j \in [m].
-\end{align}
-The constant $C_4$ is given by:
-\begin{align}\label{Cdefm}
-C_4 := \frac{2^{|E|}}{R} \max_{j \in [m]} \|\mathbf{A}_j\|_2
-\end{align}
+%then for some $J \in {[\hat m] \choose m}$, permutation matrix $\mathbf{P}$ and invertible diagonal matrix $\mathbf{D}$, we have:
+%\begin{align}\label{MainLemmaBPD}
+%\|\mathbf{A}_j - (\mathbf{BPD})_j\|_2 \leq C_4 \varepsilon, \ \ \  \text{for } j \in [m].
+%\end{align}
+%The constant $C_4$ is given by:
+%\begin{align}\label{Cdefm}
+%C_4 := \frac{2^{|E|}}{R} \max_{j \in [m]} \|\mathbf{A}_j\|_2
+%\end{align}
 %
-with $R$ being the lesser of $\min_{\substack{F \subseteq E}} r( \{ \text{\rm Span}\{\mathbf{A}_{S}\} \}_{S \in F})$ and $\min_{\substack{F \subseteq {[\hat m] \choose k}}} r( \{ \text{\rm Span}\{\mathbf{B}_{S}\} \}_{S \in F})$.
-\end{lemma}
+%with $R$ being the lesser of $\min_{\substack{F \subseteq E}} r( \{ \text{\rm Span}\{\mathbf{A}_{S}\} \}_{S \in F})$ and $\min_{\substack{F \subseteq {[\hat m] \choose k}}} r( \{ \text{\rm Span}\{\mathbf{B}_{S}\} \}_{S \in F})$.
+%\end{lemma}
 
-\begin{proof}
-The proof is very similar to the case $\hat m = m$, the difference being that now we may not invoke Lem.~\ref{NonEmptyLemma} (which requires $\hat m = m$) to infer from \eqref{fact2} that $| \cap_{S \in F(i)} \pi(S) | = 1$ for all stars $F(i)$.
+%\begin{proof}
+%The proof is very similar to the case $\hat m = m$, the difference being that now we may not invoke Lem.~\ref{NonEmptyLemma} (which requires $\hat m = m$) to infer from \eqref{fact2} that $| \cap_{S \in F(i)} \pi(S) | = 1$ for all stars $F(i)$.
 We circumvent this issue by instead assuming the spark condition on $\mathbf{B}$, which allows us to swap the roles of $\mathbf{A}$ and $\mathbf{B}$ in the arguments leading to the derivation of \eqref{fact2} to prove the opposite inequality for every star $F(i)$.
@@
 The result then follows from the proof of the case $k=1$.
-\end{proof}
+%\end{proof}
 
-\section{Proofs of Thms.~\ref{robustPolythm} \& \ref{DeterministicUniquenessTheorem2} and Cors.~\ref{DeterministicUniquenessCorollary} \& \ref{ProbabilisticCor}}\label{AppendixB}
+\section{Proofs of Thm.~\ref{robustPolythm} and Cor.~\ref{ProbabilisticCor}}\label{AppendixB} %Cors.~\ref{DeterministicUniquenessCorollary} \& \ref{ProbabilisticCor}}\label{AppendixB}
 
-\begin{proof}[Proof of Cor.~\ref{DeterministicUniquenessCorollary}]
-We need only demonstrate how to produce $N$ vectors $\mathbf{a}_i$ such that for some $E \subseteq {[m] \choose k}$ satisfying the singleton intersection property there are \mbox{$(k-1){m \choose k}+1$} vectors supported on each $S \in E$ in general linear position.
+%\begin{proof}[Proof of Cor.~\ref{DeterministicUniquenessCorollary}]
+%We need only demonstrate how to produce $N$ vectors $\mathbf{a}_i$ such that for some $E \subseteq {[m] \choose k}$ satisfying the singleton intersection property there are \mbox{$(k-1){m \choose k}+1$} vectors supported on each $S \in E$ in general linear position.
 Let $\gamma_1, \ldots, \gamma_N$ be any distinct numbers.
@@
 Finally, form the $k$-sparse vectors $\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$ with supports $S \in E$ (partitioning the $\mathbf{x}_i$ evenly among these supports so that each contains $(k-1){m \choose k}+1$ vectors $\mathbf{x}_i$) by setting the nonzero values $\mathbf{x}_i$ to be those contained in the $i$th column of $V$.
-\end{proof}
+%\end{proof}
 % Actually this is even overkill since
@@
 
-\begin{proof}[Proof of Thm.~\ref{DeterministicUniquenessTheorem2}]
-The proof is the same as that of the case $\hat m = m$, only now we establish a map $\pi: E \to {[\hat m] \choose k}$ by pigeonholing $(k-1){\hat m \choose k} + 1$ vectors with respect to holes $[\hat m]$ and eventually applying Lem.~\ref{MainLemma2} instead of Lem.~\ref{MainLemma}.
+%\begin{proof}[Proof of Thm.~\ref{DeterministicUniquenessTheorem2}]
+%The proof is the same as that of the case $\hat m = m$, only now we establish a map $\pi: E \to {[\hat m] \choose k}$ by pigeonholing $(k-1){\hat m \choose k} + 1$ vectors with respect to holes $[\hat m]$ and eventually applying Lem.~\ref{MainLemma2} instead of Lem.~\ref{MainLemma}.
 
-In this case the constant $C_3$ is given by:
-\begin{align}\label{Cdefm}
-C_3 := \frac{2^{|E|} \max_{j \in [m]} \|\mathbf{A}_j\|_2}{ R \min_{S \in E} L_k(\mathbf{AX}_{I(S)}) },
-\end{align}
+%In this case the constant $C_3$ is given by:
+%\begin{align}\label{Cdefm}
+%C_3 := \frac{2^{|E|} \max_{j \in [m]} \|\mathbf{A}_j\|_2}{ R \min_{S \in E} L_k(\mathbf{AX}_{I(S)}) },
+%\end{align}
 %
-with $R$ being the lesser of $\min_{\substack{F \subseteq E}} r( \{ \text{\rm Span}\{\mathbf{A}_{S}\} \}_{S \in F})$ and $\min_{\substack{F \subseteq {[\hat m] \choose k}}} r( \{ \text{\rm Span}\{\mathbf{B}_{S}\} \}_{S \in F})$.
-\end{proof}
+%with $R$ being the lesser of $\min_{\substack{F \subseteq E}} r( \{ \text{\rm Span}\{\mathbf{A}_{S}\} \}_{S \in F})$ and $\min_{\substack{F \subseteq {[\hat m] \choose k}}} r( \{ \text{\rm Span}\{\mathbf{B}_{S}\} \}_{S \in F})$.
+%\end{proof}
 

### 2017-03-31 manuscripts/PNAS/chazthm_pnas.tex
sml updates

--- 2017-03-30 manuscripts/PNAS/chazthm_pnas.tex
@@
 As mentioned above, it is easy to construct such $E$ with $|E| = m$, implying the lower bound for sample size $N$ from the introduction.
-Note that if $E$ is an $\ell$-regular hypergraph of rank $k$ satisfying the SIP, then $|E| \geq \ell m/k$: \[|E|k \geq \sum_{S \in E}|S| = \sum_{i \in [m]} \deg(i) = \ell m.\] In certain cases, there are simple constructions achieving this minimum; for example, when $k = \sqrt{m}$ one can take $E$ to be the rows and columns formed by arranging $[m]$ in a square grid.
+A straightforward calculation verifies that if $E$ is an $\ell$-regular hypergraph of rank $k$ satisfying the SIP, then $|E| \geq \ell m/k$.
+%Note that if $E$ is an $\ell$-regular hypergraph of rank $k$ satisfying the SIP, then $|E| \geq \ell m/k$: \[|E|k \geq \sum_{S \in E}|S| = \sum_{i \in [m]} \deg(i) = \ell m.\] 
+In certain cases, there are simple constructions achieving this minimum; for example, when $k = \sqrt{m}$ one can take $E$ to be the rows and columns formed by arranging $[m]$ in a square grid.
 In light of Cor.~\ref{DeterministicUniquenessCorollary}, it would be interesting to determine other minimal such $E$.
@@
 Moreover, if solutions are constrained to satisfy \eqref{SparkCondition}, then only an upper bound on the number of dictionary elements need be taken as given.
-We remark that our result in the deterministic case (Thm.~\ref{DeterministicUniquenessTheorem}) accounts for \emph{worst-case} noise, whereas the ``effective'' noise might be much smaller when it is sampled from a given distribution; in such cases, the constants $C_1, C_3$ in our theorems %Thms.~\ref{DeterministicUniquenessTheorem},~\ref{DeterministicUniquenessTheorem2}
-will be smaller. %We note also that these results extend trivially to cases where point-wise injective nonlinearities are applied to the data. 
+One interesting aspect of our contribution is a combinatorial criteria (regular hypergraphs satisfying the singular intersection property) for choosing support sets for original sparse codes; fully understanding those combinatorial designs allowing for stable representations of datasets is the subject of future work.
+We also remark that our main uniqueness result (Thm.~\ref{DeterministicUniquenessTheorem}) accounts for deterministic ``worst-case'' noise, whereas the ``effective'' noise might be much smaller when it is sampled from a given distribution; in such cases, the constants in our theorems %Thms.~\ref{DeterministicUniquenessTheorem},~\ref{DeterministicUniquenessTheorem2}
+will be different. %We note also that these results extend trivially to cases where point-wise injective nonlinearities are applied to the data. 
 We close with several application areas.

### 2017-03-31 manuscripts/PNAS/chazthm_pnas.tex

--- 2017-03-30 manuscripts/PNAS/chazthm_pnas.tex
@@
 %\end{proposition}
+%<<<<<<< HEAD
+%As mentioned above, it is easy to construct such $E$ with $|E| = m$, implying the lower bound for sample size $N$ from the introduction.
+%A straightforward calculation verifies that if $E$ is an $\ell$-regular hypergraph of rank $k$ satisfying the SIP, then $|E| \geq \ell m/k$.
+%%Note that if $E$ is an $\ell$-regular hypergraph of rank $k$ satisfying the SIP, then $|E| \geq \ell m/k$: \[|E|k \geq \sum_{S \in E}|S| = \sum_{i \in [m]} \deg(i) = \ell m.\] 
+%In certain cases, there are simple constructions achieving this minimum; for example, when $k = \sqrt{m}$ one can take $E$ to be the rows and columns formed by arranging $[m]$ in a square grid.
+In light of Cor.~\ref{DeterministicUniquenessCorollary}, it would be interesting to determine other minimal such $E$.
+%=======
 Note that every $\ell$-regular hypergraph $E \subseteq {[m] \choose k}$ satisfies: \[|E|k = \sum_{S \in E}|S| = \sum_{i \in [m]} \deg(i) = \ell m.\] As mentioned above, it is easy to construct such an $E$ satisfying the SIP with $|E| = m$, implying the lower bound for sample size $N$ from the introduction.
@@
 Then lower bound on $N$ comes from the smallest such $\ell$.]
+>>>>>>> 3944a59e6740a7138ee040e4263310467ecfbc4e
 

### 2017-03-31 manuscripts/PNAS/chazthm_pnas.tex
sml updates

@@
 
-\significancestatement{[*** REDO ***] Many naturally occurring signals (e.g.
-patches of visual scenery, speech audio, electrocardiograms) have been usefully characterized as parsimonious combinations of building blocks drawn from a large `dictionary' of elementary waveforms.
-Absent analytic descriptions of these signal classes, it usually falls to machine learning algorithms to infer a suitable dictionary given a large set of examples from the class.
-We give conditions guaranteeing when the optimal dictionary of a given size is uniquely and consistently determined by data, regardless of the algorithm used to compute it.
-Our results provide theoretical grounding for the application of dictionary learning algorithms to the problem of recovering sparse signals from unknown noisy compressive measurements.}
+\significancestatement{Many naturally occurring signals (visual scenery, speech, electrocardiograms, etc.) can be characterized as parsimonious combinations of elementary waveforms drawn from a large dictionary.
+Absent analytic descriptions of these signal classes, it falls on algorithms from machine learning to extract such structures given many examples from a class.
+We give conditions guaranteeing when the dictionary of a given size is uniquely and stably determined by data, regardless of the algorithm used to compute it.
+These results provide theoretical grounding for  the application of dictionary learning to recover sparse signals from unknown noisy compressive measurements.}
 
@@
 
-To prepare for the statements of our main results, we first describe a quantitative version of the spark condition.  % We first explain how the spark condition \eqref{SparkCondition} relates to t
-The \emph{lower bound} \cite{Grcar10} of a matrix $\mathbf{A} \in \mathbb R^{n \times m}$ is the largest number $\alpha$ such that \mbox{$\|\mathbf{A}\mathbf{x}\|_2 \geq \alpha\|\mathbf{x}\|_2$} for all $\mathbf{x} \in \mathbb{R}^m$.
-By compactness of the unit sphere, every injective linear map has a nonzero lower bound; hence, if $\mathbf{A}$ satisfies \eqref{SparkCondition}, then each submatrix formed from $2k$ of its columns or less has a nonzero lower bound.
-We therefore define the following domain-restricted lower bound of $\mathbf{A}$:
-\begin{align*}
-L_k(\mathbf{A}) := \frac{1}{\sqrt{k}}\max \{ \alpha : \|\mathbf{A}\mathbf{x}\|_2 \geq \alpha\|\mathbf{x}\|_2 \text{ for all $k$-sparse } \mathbf{x}\}.
-\end{align*} 
-Clearly, $L_k(\mathbf{A}) \geq L_{k'}(\mathbf{A})$ whenever $k < k'$, and for any $\mathbf{A}$ satisfying the spark condition, we have $L_{k'}(\mathbf{A}) > 0$ for all $k' \leq 2k$.
-Note that the quantity $1 - \sqrt{k} L_k(\mathbf{A})$ [*** TODO: check is this correct ***] is known in the CS literature as the (asymmetric) lower restricted isometry constant \cite{Blanchard2011, Foucart2009}.
+In preparation for stating our main results, we first identify the combinatorial criteria on support sets of generating codes allowing for stable sparse 
+representations.  Let $\{1, \ldots, m\}$ be denoted $[m]$, its power set $2^{[m]}$, and ${[m] \choose k}$ the set of subsets of $[m]$ of size $k$. 
+% Let $\text{\rm Span}\{\mathbf{v}_1, \ldots, \mathbf{v}_\ell\}$ be the $\mathbb{R}$-linear span of vectors $\mathbf{v}_1, \ldots, \mathbf{v}_\ell$. 
+A vector $\mathbf{x}$ is said to be \emph{supported} on $S \subseteq [m]$ %, written supp$(\mathbf{x}) = S$, 
+when $\mathbf{x} \in \text{\rm Span} \{\mathbf{e}_j\}_{j\in S}$, where $\mathbf{e}_j$ are the standard basis in $\mathbb R^m$.
+Let $\mathbf{M}_j$ be the $j$th column of a matrix $\mathbf{M}$ and similarly let $\mathbf{M}_S$ be the submatrix formed by the columns of $\mathbf{M}$ indexed by $S$ (we set $\text{\rm Span}\{\mathbf{M}_\emptyset\} := \{\textbf{0}\}$).
 
-% an important contribution of our work is to
-Next, we identify the combinatorial criteria on support sets of generating codes allowing for stable sparse 
-representations.
-Let $[m]$ denote the set $\{1, \ldots, m\}$, its power set $2^{[m]}$, and ${[m] \choose k}$ the set of subsets of $[m]$ of size $k$.
-Let $\text{\rm Span}\{\mathbf{v}_1, \ldots, \mathbf{v}_\ell\}$ be the $\mathbb{R}$-linear span of vectors $\mathbf{v}_1, \ldots, \mathbf{v}_\ell$.
-A vector $\mathbf{x}$ is said to be \emph{supported} on $S \subseteq [m]$, written supp$(\mathbf{x}) = S$, when $\mathbf{x} \in \text{\rm Span} \{\mathbf{e}_j\}_{j\in S}$, where $\mathbf{e}_j$ are the standard basis elements in $\mathbb R^m$.
-Let $\mathbf{M}_j$ be the $j$th column of a matrix $\mathbf{M}$ and similarly let $\mathbf{M}_S$ be the submatrix formed by the columns of $\mathbf{M}$ indexed by $S$ (we set $\text{\rm Span}\{\mathbf{M}_\emptyset\} := \{\textbf{0}\}$).
-[ ** TODO ** the hypergraph is the pair $([m],E)$, not just $E$ ] We say a hypergraph $E \subseteq 2^{[m]}$ is \textit{$k$-uniform} when every $S \in E$ has cardinality $k$.
-We also say $E$ is \emph{regular} when every element of $[m]$ is contained in exactly $\ell$ elements of $E$ for some $\ell > 0$ (for given $\ell$, we say $E$ is $\ell$-regular).
+We say a hypergraph $E \subseteq 2^{[m]}$ on vertices $[m]$ is \textit{$k$-uniform} when every $S \in E$ has cardinality $k$.
+We also say $E$ is \emph{regular} when every element of $[m]$ is contained in exactly $\ell$ elements of $E$ for some $\ell > 0$ (for given $\ell$, we say $E$ is \textit{$\ell$-regular}).
 
 \begin{definition}
-Given a hypergraph $E \subseteq 2^{[m]}$, the \textbf{star} $F(i)$ centered at $i$ is the collection of $S \in E$ containing $i$.
-We say $E$ satisfies the \textbf{singleton intersection property} (\textbf{SIP}) when $\cap_{S \in F(i)} S = \{i\}$ for all $i \in [m]$.
+Given $E \subseteq 2^{[m]}$, the \textbf{star} $F(i)$ at $i$ are those $S \in E$ with $i \in S$.
+We say $E$ has the \textbf{singleton intersection property} (\textbf{SIP}) when $\cap_{S \in F(i)} S = \{i\}$ for all $i \in [m]$.
 \end{definition}
@@
 
-We say that a set of $k$-sparse vectors is in \emph{general linear position} when any $k$ of them are linearly independent.
+%The second ingredient necessary for the statement of Thm.~\ref{DeterministicUniquenessTheorem} 
+Next, we describe a quantitative version of the spark condition.  % We first explain how the spark condition \eqref{SparkCondition} relates to t
+The \emph{lower bound} \cite{Grcar10} of a matrix $\mathbf{A} \in \mathbb R^{n \times m}$ is the largest number $\alpha$ such that \mbox{$\|\mathbf{A}\mathbf{x}\|_2 \geq \alpha\|\mathbf{x}\|_2$} for all $\mathbf{x} \in \mathbb{R}^m$.
+By compactness of the unit sphere, every injective linear map has a nonzero lower bound; hence, if $\mathbf{A}$ satisfies \eqref{SparkCondition}, then each submatrix formed from $2k$ of its columns or less has a nonzero lower bound.
+We therefore define the following domain-restricted lower bound:
+\begin{align*}
+L_k(\mathbf{A}) := \frac{1}{\sqrt{k}}\max \{ \alpha : \|\mathbf{A}\mathbf{x}\|_2 \geq \alpha\|\mathbf{x}\|_2 \text{ for all $k$-sparse } \mathbf{x}\}.
+\end{align*}
+
+Clearly, $L_k(\mathbf{A}) \geq L_{k'}(\mathbf{A})$ whenever $k < k'$, and for any $\mathbf{A}$ satisfying \eqref{SparkCondition}, we have $L_{k'}(\mathbf{A}) > 0$ for  $k' \leq 2k$.
+The quantity $1 - \sqrt{k} L_k(\mathbf{A})$ is also known in the CS literature as the (asymmetric) lower restricted isometry constant \cite{Blanchard2011, Foucart2009}.
+
+We also say that a set of $k$-sparse vectors is in \emph{general linear position} when any $k$ of them are linearly independent.
 The following is the precise statement of our main result.
@@
 Given Thm.\ref{DeterministicUniquenessTheorem}, one needs only to produce sparse codes in general linear position.
-However, this is straightforward (e.g., with a ``Vandermonde'' construction \cite{Hillar15}).
+However, this is straightforward with a ``Vandermonde'' matrix construction (e.g., see \cite{Hillar15}).
 \end{proof}
@@
 %=======
-Note that every $\ell$-regular hypergraph $E \subseteq {[m] \choose k}$ satisfies: \[|E|k = \sum_{S \in E}|S| = \sum_{i \in [m]} \deg(i) = \ell m.\] As mentioned above, it is easy to construct such an $E$ satisfying the SIP with $|E| = m$, implying the lower bound for sample size $N$ from the introduction.
+%Note that every $\ell$-regular hypergraph $E \subseteq {[m] \choose k}$ satisfies: \[|E|k = \sum_{S \in E}|S| = \sum_{i \in [m]} \deg(i) = \ell m.\] 
+As mentioned above, it is easy to construct a regular hypergraph $E \subseteq {[m] \choose k}$ with the SIP having size $|E| = m$, implying the lower bound for sample size $N$ from the introduction.
 In certain cases, the SIP can be achieved with $|E| < m$; for example, when $k = \sqrt{m}$ one can take $E$ to be the rows and columns formed by arranging $[m]$ in a square grid.
-In light of Cor.~\ref{DeterministicUniquenessCorollary}, it would be interesting to determine other minimal such $E$.
-[ ** TODO ** can we show for every $k, m$ that there is an $E$ satisfying the SIP with $|E| = \ell m/k$ for every $\ell$ such that $\ell m/k$ is an integer?
+In light of Cor.~\ref{DeterministicUniquenessCorollary}, it would be interesting to determine other such $E$.
+%[ ** TODO ** can we show for every $k, m$ that there is an $E$ satisfying the SIP with $|E| = \ell m/k$ for every $\ell$ such that $\ell m/k$ is an integer?
 Then lower bound on $N$ comes from the smallest such $\ell$.]
->>>>>>> 3944a59e6740a7138ee040e4263310467ecfbc4e
 
@@
 \begin{theorem}
-Fix integers $n, \ell$, and $k < m$.
-Suppose $\mathbf{A}~\in~\mathbb{R}^{n \times m}$ satisfies the spark condition \eqref{SparkCondition} and that $k$-sparse \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} contain at least \mbox{$k \left[ 1 + (k-1){ m \choose k} \right]$} vectors supported in general linear position on each set in some $\ell$-regular $E \subseteq {[m] \choose k}$ satisfying the SIP.
-There exists a constant $C_1 > 0$ for which the following holds for all $\varepsilon < L_2(\mathbf{A}) / C_1$.
-
-Every solution $\mathbf{B}, \mathbf{\hat x}_i, \ldots, \mathbf{\hat x}_N$ to the constrained $\ell_0$ optimization:
+Fix $n, \ell$, and $k < m$.
+Suppose $\mathbf{A}~\in~\mathbb{R}^{n \times m}$ satisfies the spark condition \eqref{SparkCondition} and that $k$-sparse \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} have at least \mbox{$k \left[ 1 + (k-1){ m \choose k} \right]$} vectors supported in general linear position on each set in an $\ell$-regular $E \subseteq {[m] \choose k}$ with the SIP.
+Given any $\delta_1, \delta_2 \geq 0$ and $\varepsilon \leq \varepsilon(\delta_1, \delta_2)$, the following holds.
+% (\eqref{epsdel}).
+% $\varepsilon < L_2(\mathbf{A}) / C_1$.
+%There exists a constant $C_1 > 0$ for which the following holds for all $\varepsilon < L_2(\mathbf{A}) / C_1$.
+Every solution $\mathbf{B}, \mathbf{\hat x}_i, \ldots, \mathbf{\hat x}_N$ to the constrained $\ell_0$ optimization problem:
 \begin{align}\label{minsum}
@@
 \end{align}
-necessarily satisfies \eqref{Cstable} and \eqref{b-PDa}.
+necessarily satisfies the recovery inequalities in \eqref{def1}. % \eqref{Cstable} and \eqref{b-PDa}.
 \end{theorem}
@@
 \begin{proof}
-We argue for a lower bound on the number of $k$-sparse vectors $\mathbf{\hat x}_i$ and then apply Thm.~\ref{DeterministicUniquenessCorollary}. 
-[*** Incomplete ***]
-Let $n_p$ be the number of vectors $\mathbf{\hat x}_i$ satisfying $\|\mathbf{\hat x}_i\|_0 = p$, so that $\sum_{p = 1}^{m} n_p = N$.
+We derive a lower bound on the number of $k$-sparse vectors $\mathbf{\hat x}_i$ and then apply Thm.~\ref{DeterministicUniquenessCorollary}. 
+Let $n_p$ be the number of $\mathbf{\hat x}_i$ with $\|\mathbf{\hat x}_i\|_0 = p$.  %, so that $\sum_{p = 1}^{m} n_p = N$. 
 Since the $\mathbf{x}_i$ are all $k$-sparse, by \eqref{minsum} we have:
@@
 
-That is, at least $N / k$ of the vectors $\mathbf{\hat x}_i$ are $k$-sparse.
+In particular, at least $N / k$ of the $\mathbf{\hat x}_i$ are $k$-sparse.
 Therefore, there is some $N' \subseteq [N]$ for which for each $S \in E$ there are $(k-1){m \choose k}+1$ of the vectors $\mathbf{x}_i$ with $i \in [N']$ supported on $S$ and for which $\mathbf{\hat x}_i$ is $k$-sparse for all $i \in [N']$.

### 2017-03-31 manuscripts/PNAS/chazthm_pnas.tex
more SR

@@
 Absent analytic descriptions of these signal classes, it falls on algorithms from machine learning to extract such structures given many examples from a class.
-We give conditions guaranteeing when the dictionary of a given size is uniquely and stably determined by data, regardless of the algorithm used to compute it.
-These results provide theoretical grounding for  the application of dictionary learning to recover sparse signals from unknown noisy compressive measurements.}
+We give conditions guaranteeing when a dictionary of a given size is uniquely and stably determined by data, regardless of the algorithm used to compute it.
+These results provide theoretical grounding for  the application of dictionary learning to recovering sparse signals from unknown noisy compressive measurements.}
 
@@
 has a stable sparse representation.
-More specifically, such dictionaries are uniquely identifiable from as few as \mbox{$N = m + m(k-1){m \choose k}$} sparse linear combinations of their columns up to an error that is linear in the measurement noise (Thm.~\ref{DeterministicUniquenessTheorem}).
+More specifically, such dictionaries are uniquely identifiable from as few as \mbox{$N = m(k-1){m \choose k} + m$} sparse linear combinations of their columns up to an error that is linear in the measurement noise (Thm.~\ref{DeterministicUniquenessTheorem}).
 In fact, provided $(n, m, k)$ satisfy CS inequality \eqref{CScondition}, in almost all cases the dictionary learning problem is well-posed given enough data (Cor.~\ref{ProbabilisticCor}).
@@
 Fix integers $n, \ell$, and $k < m$.
-Suppose $\mathbf{A}~\in~\mathbb{R}^{n \times m}$ satisfies the spark condition \eqref{SparkCondition} and that $k$-sparse \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} contain at least \mbox{$(k-1){\hat m \choose k}+1$} vectors supported in general linear position on each set in some $\ell$-regular $E \subseteq {[m] \choose k}$ with the SIP.
+Suppose $\mathbf{A}~\in~\mathbb{R}^{n \times m}$ satisfies the spark condition \eqref{SparkCondition} and that $k$-sparse \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} contain at least \mbox{$(k-1){m \choose k}+1$} vectors supported in general linear position on each set in some $\ell$-regular $E \subseteq {[m] \choose k}$ with the SIP.
 There exists a constant $C_1 > 0$ for which the following holds for all $\varepsilon < L_2(\mathbf{A}) / C_1$.
@@
 
-An important consequence of Thm.~\ref{DeterministicUniquenessTheorem} is that \eqref{def1} is guaranteed provided $\varepsilon$ does not exceed: [*** TODO: verify this is still correct ***]
+An important consequence of Thm.~\ref{DeterministicUniquenessTheorem} is that \eqref{def1} is guaranteed provided $\varepsilon$ does not exceed: % [*** TODO: verify this is still correct ***]
 \begin{align}\label{epsdel}
@@
 \begin{corollary}\label{DeterministicUniquenessCorollary}
-Given $n, m$, $k < m$, and a regular hypergraph $E \subseteq {[m] \choose k}$ with the SIP, there are $N =  |E| \left[ 1 + (k-1){m \choose k} \right]$ vectors \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} such that every matrix $\mathbf{A} \in \mathbb{R}^{n \times m}$ satisfying \eqref{SparkCondition} generates a dataset $Y = \{\mathbf{A}\mathbf{x}_1, \ldots, \mathbf{A}\mathbf{x}_N\}$ with a stable $k$-sparse representation in $m$ dimensions.
+Given $n, m$, $k < m$, and a regular hypergraph $E \subseteq {[m] \choose k}$ with the SIP, there are $N =  |E| \left[ (k-1){m \choose k} + 1  \right]$ vectors \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} such that every matrix $\mathbf{A} \in \mathbb{R}^{n \times m}$ satisfying \eqref{SparkCondition} generates a dataset $Y = \{\mathbf{A}\mathbf{x}_1, \ldots, \mathbf{A}\mathbf{x}_N\}$ with a stable $k$-sparse representation in $m$ dimensions.
 \end{corollary}
@@
 Fix $n, \ell$, and $k < m$.
-Suppose $\mathbf{A}~\in~\mathbb{R}^{n \times m}$ satisfies the spark condition \eqref{SparkCondition} and that $k$-sparse \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} have at least \mbox{$k \left[ 1 + (k-1){ m \choose k} \right]$} vectors supported in general linear position on each set in an $\ell$-regular $E \subseteq {[m] \choose k}$ with the SIP.
+Suppose $\mathbf{A}~\in~\mathbb{R}^{n \times m}$ satisfies the spark condition \eqref{SparkCondition} and that $k$-sparse \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} have at least \mbox{$k \left[ (k-1){ m \choose k} + 1 \right]$} vectors supported in general linear position on each set in an $\ell$-regular $E \subseteq {[m] \choose k}$ with the SIP.
 Given any $\delta_1, \delta_2 \geq 0$ and $\varepsilon \leq \varepsilon(\delta_1, \delta_2)$, the following holds.
@@
 \begin{proof}
-We derive a lower bound on the number of $k$-sparse vectors $\mathbf{\hat x}_i$ and then apply Thm.~\ref{DeterministicUniquenessCorollary}. 
+We derive a lower bound on the number of $k$-sparse  $\mathbf{\hat x}_i$ and then apply Thm.~\ref{DeterministicUniquenessCorollary}. 
+[*** This proof still has a gap ***]
 Let $n_p$ be the number of $\mathbf{\hat x}_i$ with $\|\mathbf{\hat x}_i\|_0 = p$.  %, so that $\sum_{p = 1}^{m} n_p = N$. 
@@
 \end{align}
-\[\implies \sum_{p = 1}^k (k-p)n_p \geq \sum_{p = k+1}^{\hat m} (p-k) n_p.\]
+\[\implies \sum_{p = 1}^k (k-p)n_p \geq \sum_{p = k+1}^{m} (p-k) n_p.\]
 Hence,
@@
 Therefore, there is some $N' \subseteq [N]$ for which for each $S \in E$ there are $(k-1){m \choose k}+1$ of the vectors $\mathbf{x}_i$ with $i \in [N']$ supported on $S$ and for which $\mathbf{\hat x}_i$ is $k$-sparse for all $i \in [N']$.
-By Thm.~\ref{DeterministicUniquenessCorollary}, \eqref{Cstable} and \eqref{b-PDa} follow.
+The result now follows directly from Thm.~\ref{DeterministicUniquenessCorollary}.
+% \eqref{Cstable} and \eqref{b-PDa} follow.
 \end{proof}
 
-Another straightforward application of Thm.~\ref{DeterministicUniquenessTheorem} is a probabilistic extension that uses the following often used application of random matrix theory to compressed sensing.
-A random matrix $\mathbf{A} \in \mathbb{R}^{n \times m}$ satisfies \eqref{SparkCondition} with probability one (or with ``high probability'' for discrete variables)
+Another straightforward application of Thm.~\ref{DeterministicUniquenessTheorem} is a probabilistic extension, which takes advantage of the following well-known application of random matrix theory to compressed sensing.
+A random $n \times m$ matrix obeys \eqref{SparkCondition} with probability one (or ``high probability'' for discrete variables)
 provided:
@@
 \end{align}
-in which $\gamma$ is a positive constant that depends on the particular distribution from which the entries of $\mathbf{A}$ are sampled i.i.d. (many ensembles suffice, e.g. \cite[Sec.~4]{Baraniuk08}).
+in which $\gamma >0$ is a constant that depends on the particular distribution from which the entries of $\mathbf{A}$ are sampled i.i.d. (many ensembles suffice, e.g. see \cite[Sec.~4]{Baraniuk08}).
 
@@
 
-% It so happens that a similar statement applies to sets of vectors with a stable sparse representation.
+A similar phenomenon applies to sets of vectors with a stable sparse representation.
 As in \cite[Sec.~IV]{Hillar15}, consider the ``symbolic'' dataset $Y = \{\mathbf{A}\mathbf{x}_1,\ldots,\mathbf{A} \mathbf{x}_N\}$ generated by indeterminate $\mathbf{A}$ and $k$-sparse $\mathbf{x}_1, \ldots, \mathbf{x}_N$.
@@
 L_k(\mathbf{A}) \leq \frac{\|\mathbf{A}\mathbf{x}\|_2}{\sqrt{k} \|\mathbf{x}\|_2} %\leq \frac{\|\mathbf{x}\|_1}{\sqrt{k} \|\mathbf{x}\|_2} \max_{i \in [m]}\|\mathbf{A}_i\|_2 
-\leq  \max_{i \in [m]}\|\mathbf{A}_i\|_2.
+\leq  \max_{j \in [m]}\|\mathbf{A}_j\|_2.
 \end{align}
@@
 %
-where we drop the absolute value due to the upper bound on $\varepsilon$. Hence, $L_{2k}(\mathbf{BPD}) \geq L_{2k}(\mathbf{A}) - C_1\varepsilon  > 0$ and \eqref{b-PDa} then follows from:
+%where we drop the absolute value due to the upper bound on $\varepsilon$. 
+Hence, $L_{2k}(\mathbf{BPD}) \geq L_{2k}(\mathbf{A}) - C_1\varepsilon  > 0$ and \eqref{b-PDa} then follows from:
 \begin{align*}
@@
 
-The heart of the matter is therefore \eqref{Cstable}, which we now establish using the following approach.
-Pigeonholing the data into its set of possible supports with respect to the matrix $\mathbf{B}$, one sees that the column space of every $\mathbf{A}_S$ with $S \in E$ must be nearby (in a sense yet to be defined; see Def.~\ref{dDef}) the column space of some $n \times k$ submatrix of $\mathbf{B}$.
-\eqref{Cstable} then follows from our result in combinatorial matrix analysis (Lem.~\ref{MainLemma}).
+The heart of the matter is therefore \eqref{Cstable}, which we now finally establish, but first in the important special case $k = 1$.
 
@@
 Fix $\mathbf{A} \in \mathbb{R}^{n \times m}$ satisfying \eqref{SparkCondition} and suppose that for some $\mathbf{B} \in \mathbb{R}^{n \times \hat m}$ ($\hat m \geq m$) and $1$-sparse $\mathbf{\hat x}_i \in \mathbb{R}^{\hat m}$ we have  $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\hat x}_i\|_2 \leq \varepsilon < L_2(\mathbf{A}) / C_1$ for all $i$.
-Then there are $\hat{c}_1, \ldots, \hat{c}_m \in \mathbb{R}$ and $\pi: [m] \to [\hat m]$ with:
+Then, there are $\hat{c}_1, \ldots, \hat{c}_m \in \mathbb{R}$ and a map $\pi: [m] \to [\hat m]$ with:
 \begin{align}\label{1D}
@@
 \end{align} 
-Note that $\hat{c}_j \neq 0$ for all $j$ since otherwise by \eqref{delrho} and definition of $C_1$ we would have $\|c_j\mathbf{A}_j\|_2 < \min_{\ell \in [m]}\|c_{\ell}\mathbf{A}_{\ell}\|_2$.
+Note that $\hat{c}_j \neq 0$ since otherwise by \eqref{delrho} and definition of $C_1$ we would have $\|c_j\mathbf{A}_j\|_2 < \min_{\ell \in [m]}\|c_{\ell}\mathbf{A}_{\ell}\|_2$.
+[*** TODO:  This doesn't seem correct ***]
 
@@
 There exists a constant $C_2 > 0$ for which the following holds for all $\varepsilon < L_2(\mathbf{A}) / C_2$.
-If for some  $\mathbf{B} \in \mathbb{R}^{n \times m}$ and regular $E \subseteq2^{[m]}$ satisfying the singleton intersection property there exists a size-preserving map $\pi: E \mapsto 2^{[m]}$ satisfying:
+If for some  $\mathbf{B} \in \mathbb{R}^{n \times m}$ and regular $E \subseteq {[m] \choose k}$ satisfying the SIP there exists a map $\pi: E \mapsto {[m] \choose k}$ satisfying:
 \begin{align}\label{GapUpperBound}
@@
 \begin{align}\label{MainLemmaBPD}
-\|\mathbf{A}_j - (\mathbf{BPD})_j\|_2 \leq C_2 \varepsilon, \ \ \  \text{for } j \in [m].
+\|\mathbf{A}_j - (\mathbf{BPD})_j\|_2 \leq C_2 \varepsilon, \ \ \  \text{for all } j \in [m].
 \end{align}
@@
 
-The constant $C_2$ in Lem.~\ref{MainLemma} is then given by:  % \footnote{Note that $C_2 > 0$ is well-defined since $r > 0$ by definition.}
+The constant $C_2$ in Lem.~\ref{MainLemma} can then be expressed as:  % \footnote{Note that $C_2 > 0$ is well-defined since $r > 0$ by definition.}
 \begin{align}\label{Cdef2}
@@
 \end{align*}
-where the last equality is by definition of the domain-restricted matrix lower bound $L_k$. It follows that for all $S \in E$,
+where the last equality is by definition of $L_k$. It follows that for all $S \in E$,
 \begin{align}\label{rhs222}
@@
 \textbf{Theoretical Neuroscience}.
-Sparse dictionary learning and related methods have recovered characteristic components of natural images \cite{Olshausen96, hurri1996image, bell1997independent, van1998independent} and sounds \cite{bellsejnowski1996, smithlewicki2006, Carlson12}, reproducing response properties of cortical neurons.
+Sparse dictionary learning and related methods have recovered characteristic components of natural images and sounds \cite{bellsejnowski1996, smithlewicki2006, Carlson12}, reproducing response properties of cortical neurons.
 Our theorems suggest that this correspondence could be due to the uniqueness of sparse representations.
-Furthermore, our guarantees justify the hypothesis of \cite{Coulter10} and \cite{Isely10} that sparse codes passed through a communication bottleneck in the brain can be recovered from random projections via (unsupervised) biologically plausible sparse dictionary learning (e.g., \cite{rehnsommer2007, rozell2007neurally, hu2014hebbian}).
+Furthermore, our guarantees justify the hypothesis of \cite{Coulter10, Isely10} that sparse codes passed through a communication bottleneck in the brain can be recovered from random projections via (unsupervised) biologically plausible sparse dictionary learning (e.g., \cite{rehnsommer2007, rozell2007neurally, hu2014hebbian}).
 Invariance: \cite{pitts1947}.

### 2017-03-31 manuscripts/PNAS/chazthm_pnas.tex
sml edits

@@
 %
-where the maximum is taken over all possible orderings\footnote{We modify the quantity in \cite{Deutsch12} in this way since the subspace ordering is irrelevant to our purpose.} of the $V_i$ and where the angle $\theta \in (0,\frac{\pi}{2}]$ is defined in terms of its cosine as \cite[Def.~9.4]{Deutsch12}:
+where the maximum is taken over all orderings\footnote{We modify the quantity in \cite{Deutsch12} in this way since the subspace ordering is irrelevant to our purpose.} of the $V_i$ and the angle $\theta \in (0,\frac{\pi}{2}]$ is defined implicitly as \cite[Def.~9.4]{Deutsch12}:
 \begin{align*}
@@
 %%% No |S| = k assumption %%%
-We begin by showing that for every $S \in E$ there is some $S' \subseteq [m]$, $|S'| \leq k$ for which the distance $d(\text{\rm Span}\{\mathbf{A}_S\}, \text{\rm Span}\{\mathbf{B}_S'\})$ is controlled by $\varepsilon$.
+We begin by showing that for every $S \in E$ there is some $S' \subseteq [m]$, $|S'| \leq k$, for which the distance $d(\text{\rm Span}\{\mathbf{A}_S\}, \text{\rm Span}\{\mathbf{B}_{S'}\})$ is controlled by $\varepsilon$.
 Fix $S \in E$.
@@
 \|\mathbf{y} - \mathbf{\hat{y}}\|_2 
-&= \|\sum_{i=1}^k c_i(\mathbf{AX}_{J(S)} - \mathbf{B\hat{X}}_{J(S)})_i\|_2
+&= \|\sum_{i=1}^k c_i(\mathbf{AX}_{I(S)} - \mathbf{B\hat{X}}_{I(S)})_i\|_2
 \leq \varepsilon \sum_{i=1}^k |c_i| \\
@@
 %\leq \frac{\varepsilon \sqrt{k}}{L(\mathbf{A}X_{J(S)})} \|\mathbf{A}X_{J(S)}\mathbf{c}\|_2 
-= \frac{\varepsilon}{L_k(\mathbf{AX}_{J(S)})} \|\mathbf{y}\|_2,
+= \frac{\varepsilon}{L_k(\mathbf{AX}_{I(S)})} \|\mathbf{y}\|_2,
 \end{align*}
@@
 
-Plugging this into \eqref{f} and rearranging yields \eqref{DTILeq} after substituting $r(\{V_i\}_{i=1}^k)$ for $1 - z$ (as $z$ may depend on the arbitrary ordering of the $V_i$).
+Substituting this into \eqref{f} and rearranging yields \eqref{DTILeq} after substituting $r(\{V_i\}_{i=1}^k)$ for $1 - z$ (as $z$ may depend on the arbitrary ordering of the $V_i$).
 \end{proof}

### 2017-04-01 manuscripts/PNAS/chazthm_pnas.tex
chaz

@@
 
-Clearly, $L_k(\mathbf{A}) \geq L_{k'}(\mathbf{A})$ whenever $k < k'$, and for any $\mathbf{A}$ satisfying \eqref{SparkCondition}, we have $L_{k'}(\mathbf{A}) > 0$ for  $k' \leq 2k$.
+Clearly, $\sqrt{k} L_k(\mathbf{A}) \geq \sqrt{k'}L_{k'}(\mathbf{A})$ whenever $k < k'$, and for any $\mathbf{A}$ satisfying \eqref{SparkCondition}, we have $L_{k'}(\mathbf{A}) > 0$ for  $k' \leq 2k$.
 The quantity $1 - \sqrt{k} L_k(\mathbf{A})$ is also known in the CS literature as the (asymmetric) lower restricted isometry constant \cite{Blanchard2011, Foucart2009}.
@@
 \end{align} 
-Note that $\hat{c}_j \neq 0$ since otherwise by \eqref{delrho} and definition of $C_1$ we would have $\|c_j\mathbf{A}_j\|_2 < \min_{\ell \in [m]}\|c_{\ell}\mathbf{A}_{\ell}\|_2$.
+Note that $\hat{c}_j \neq 0$, since otherwise (by definition of $L_2(\mathbf{A})$) we reach the contradiction $|c_j| < \min_{\ell \in [m]} | c_\ell |$.
+%by \eqref{delrho} and definition of $C_1$ we would have $\|c_j\mathbf{A}_j\|_2 < \min_{\ell \in [m]}\|c_{\ell}\mathbf{A}_{\ell}\|_2$.
 [*** TODO:  This doesn't seem correct ***]
+%\begin{align*}
+%|c_j| \sqrt{2} L_2(\mathbf{A}) \leq \|\mathbf{A}(c_j\mathbf{e}_j)\|_2 \leq \varepsilon < L_2(\mathbf{A}) \min_{\ell \in [m]} | c_\ell |.
+%\end{align*}
 
@@
 %\leq \frac{\varepsilon \sqrt{k}}{L(\mathbf{A}X_{J(S)})} \|\mathbf{A}X_{J(S)}\mathbf{c}\|_2 
-= \frac{\varepsilon}{L_k(\mathbf{AX}_{I(S)})} \|\mathbf{y}\|_2,
+\leq \frac{\varepsilon}{L_k(\mathbf{AX}_{I(S)})} \|\mathbf{y}\|_2,
 \end{align*}
-where the last equality is by definition of $L_k$. It follows that for all $S \in E$,
+where the last inequality is by definition of $L_k$. It follows that for all $S \in E$,
 \begin{align}\label{rhs222}

### 2017-04-01 manuscripts/PNAS/chazthm_pnas.tex
almost a complete draft

@@
 A similar phenomenon applies to sets of vectors with a stable sparse representation.
-As in \cite[Sec.~IV]{Hillar15}, consider the ``symbolic'' dataset $Y = \{\mathbf{A}\mathbf{x}_1,\ldots,\mathbf{A} \mathbf{x}_N\}$ generated by indeterminate $\mathbf{A}$ and $k$-sparse $\mathbf{x}_1, \ldots, \mathbf{x}_N$.
+As in \cite[Sec.~IV]{Hillar15}, consider the ``symbolic'' dataset $Y = \{\mathbf{A}\mathbf{x}_1,\ldots,\mathbf{A} \mathbf{x}_N\}$ generated by indeterminate $\mathbf{A}$ and indeterminate $k$-sparse $\mathbf{x}_1, \ldots, \mathbf{x}_N$.
 
@@
 \begin{definition}\label{dDef}
-For any point $\mathbf{u}$, let $\text{\rm dist}(\mathbf{u}, V) := \inf \{\| \mathbf{u}-\mathbf{v} \|_2: \mathbf{v} \in V\}$ be the distance of $\mathbf{u}$ from the set $V$.
-For subspaces $U,V \subseteq \mathbb{R}^m$, we define: %[Kato p.197]
+For $\mathbf{u} \in \mathbb R^m$, let $\text{\rm dist}(\mathbf{u}, V) := \inf \{\| \mathbf{u}-\mathbf{v} \|_2: \mathbf{v} \in V\}$, and for subspaces $U,V \subseteq \mathbb{R}^m$, define\footnote{Although identical, note the reference \cite{Morris10} defines the supremum over the unit ball.}: %[Kato p.197]
 \begin{align}\label{d}
@@
 
-Our result in combinatorial matrix analysis is the following.
+Our result in combinatorial matrix theory is the following.
 
@@
 There exists a constant $C_2 > 0$ for which the following holds for all $\varepsilon < L_2(\mathbf{A}) / C_2$.
-If for some  $\mathbf{B} \in \mathbb{R}^{n \times m}$ and regular $E \subseteq {[m] \choose k}$ satisfying the SIP there exists a map $\pi: E \mapsto {[m] \choose k}$ satisfying:
+If for some  $\mathbf{B} \in \mathbb{R}^{n \times m}$ and regular $E \subseteq {[m] \choose k}$ with the SIP there exists a map $\pi: E \mapsto {[m] \choose k}$ satisfying:
 \begin{align}\label{GapUpperBound}
@@
 
-The constant $C_1$ in Thm.~\ref{DeterministicUniquenessTheorem} is then given by:
+The constant $C_1$ in Thm.~\ref{DeterministicUniquenessTheorem} is then given by\footnote{We can be sure $C_1 > 0$ since $L_k(\mathbf{A}), L_k(\mathbf{X}_{I(S)}) > 0$ by the spark condition and general linear position of the $\mathbf{x}_i$; hence $\|\mathbf{A}_j\|_2 > 0$ for all $j$ and for all $S \in E$ we have $\|\mathbf{AX}_{I(S)}\mathbf{c}\|_2 \geq L_k(\mathbf{A})\|\mathbf{X}_{I(S)}\mathbf{c}\|_2 \geq L_k(\mathbf{A}) L_k(\mathbf{X}_{I(S)})\|\mathbf{c}\|_2$ for all $k$-sparse $\mathbf{c}$, and therefore $L_k(\mathbf{AX}_{I(S)}) \geq L_k(\mathbf{A}) L_k(\mathbf{X}_{I(S)}) > 0$.}:
 \begin{align}\label{Cdef1}
@@
 %
-where $\mathbf{X}$ is the $m \times N$ matrix with columns $\mathbf{x}_i$ and $I(S) := \{i : \text{supp}(\mathbf{x}_i) = S\}$.\footnote{We can be sure $C_1 > 0$ is well-defined (provided $C_2$ is well-defined) since $L_k(\mathbf{A}), L_k(\mathbf{X}_{I(S)}) > 0$ by the spark condition and general linear position of the $\mathbf{x}_i$; hence $\|\mathbf{A}_j\|_2 > 0$ for all $j$ and for all $S \in E$ we have $\|\mathbf{AX}_{I(S)}\mathbf{c}\|_2 \geq L_k(\mathbf{A})\|\mathbf{X}_{I(S)}\mathbf{c}\|_2 \geq L_k(\mathbf{A}) L_k(\mathbf{X}_{I(S)})\|\mathbf{c}\|_2$ for all $k$-sparse $\mathbf{c}$ and therefore $L_k(\mathbf{AX}_{I(S)}) \geq L_k(\mathbf{A}) L_k(\mathbf{X}_{I(S)}) > 0$.} The constant $C_2 = C_2(\mathbf{A}, E)$ is defined below in terms of a technical quantity related to one used in \cite{Deutsch12} to analyze the convergence of the alternating projections algorithm.
+where $\mathbf{X}$ is the $m \times N$ matrix with columns $\mathbf{x}_i$ and $I(S)$ is defined as those $i \in [N]$ with supports in $S$.
+The constant $C_2 = C_2(\mathbf{A}, E)$ is defined below in terms of one used in \cite{Deutsch12} to analyze the convergence of the alternating projections algorithm.
 % for projecting a point onto the intersection of a set of subspaces. 
@@
 \begin{align}\label{Cdef2}
-C_2(\mathbf{A}, E) := \frac{ 2^{|E|} \max_{i \in [m]} \|\mathbf{A}_i\|_2}{ \min_{F \subseteq E} r( \{ \text{\rm Span}\{\mathbf{A}_{S}\} \}_{S \in F}) }.
+C_2(\mathbf{A}, E) := \frac{ 2^{|E|} \max_{j \in [m]} \|\mathbf{A}_j\|_2}{ \min_{F \subseteq E} r( \{ \text{\rm Span}\{\mathbf{A}_{S}\} \}_{S \in F}) }.
 \end{align}
@@
 Since there are $(k-1){m \choose k}+1$ vectors $\mathbf{x}_i$ supported on $S$, the pigeon-hole principle implies that there exists some $S' \in {[m] \choose k}$ and some set of $k$ indices $J(S)$ such that the supports of all $\mathbf{x}_i$ and $\mathbf{\hat x}_i$ with $i \in J(S)$ are contained in $S$ and $S'$, respectively.
-
 %%% No |S| = k assumption %%%
-We begin by showing that for every $S \in E$ there is some $S' \subseteq [m]$, $|S'| \leq k$, for which the distance $d(\text{\rm Span}\{\mathbf{A}_S\}, \text{\rm Span}\{\mathbf{B}_{S'}\})$ is controlled by $\varepsilon$.
-Fix $S \in E$.
+We shall show that for every $S \in E$ there is some $S' \subseteq [m]$, $|S'| \leq k$, for which the distance $d(\text{\rm Span}\{\mathbf{A}_S\}, \text{\rm Span}\{\mathbf{B}_{S'}\})$ is controlled by $\varepsilon$.
 Since there are $(k-1){m \choose k}+1$ vectors $\mathbf{x}_i$ supported on $S$, the pigeon-hole principle implies that there exists some $S' \in {[m] \choose k}$ and some set of $k$ indices $I(S)$ such that the supports of all $\mathbf{x}_i$ and $\mathbf{\hat x}_i$ with $i \in I(S)$ are contained in $S$ and $S'$, respectively.
@@
 Let $\mathbf{X}$ and $\mathbf{\hat{X}}$ be the $m \times N$ matrices with columns $\mathbf{x}_i$ and $\mathbf{\hat x}_i$, respectively.
-It follows from the general linear position of the $\mathbf{x}_i$ and the linear independence of every $k$ columns of $\mathbf{A}$ that $L_k(\mathbf{AX}_{J(S)}) > 0$; that is, the columns of the $n \times k$ matrix $\mathbf{AX}_{J(S)}$ are linearly independent and thus form a basis for $\text{\rm Span}\{\mathbf{A}_{S}\}$.
-Fixing $\mathbf{y} \in \text{\rm Span}\{\mathbf{A}_{S}\}$, there then exists a unique $\mathbf{c} = (c_1, \ldots, c_k) \in \mathbb{R}^k$ such that $\mathbf{y} = \mathbf{AX}_{J(S)}\mathbf{c}$.
-Letting \mbox{$\mathbf{\hat{y}} = \mathbf{B\hat{X}}_{J(S)}\mathbf{c}$}, which is in $\text{\rm Span}\{\mathbf{B}_{S'}\}$, we have:
+It follows from the general linear position of the $\mathbf{x}_i$ and the linear independence of every $k$ columns of $\mathbf{A}$ that $L_k(\mathbf{AX}_{I(S)}) > 0$; that is, the columns of the $n \times k$ matrix $\mathbf{AX}_{I(S)}$ form a basis for $\text{\rm Span}\{\mathbf{A}_{S}\}$.
+Fixing $\mathbf{y} \in \text{\rm Span}\{\mathbf{A}_{S}\}$, there exists a unique $\mathbf{c} = (c_1, \ldots, c_k) \in \mathbb{R}^k$ such that $\mathbf{y} = \mathbf{AX}_{I(S)}\mathbf{c}$.
+Setting \mbox{$\mathbf{\hat{y}} = \mathbf{B\hat{X}}_{I(S)}\mathbf{c} \in \text{\rm Span}\{\mathbf{B}_{S'}\}$}, we have:
 \begin{align*}
@@
 \end{align*}
-where the last inequality is by definition of $L_k$. It follows that for all $S \in E$,
+where the last inequality is by definition of $L_k$. Also, from Def.~\ref{dDef}, it follows that for all $S \in E$,
 \begin{align}\label{rhs222}
@@
 \end{align}
-The result then follows by  Lem.~\ref{MainLemma}, with the map $\pi: E \to {[m] \choose k}$ defined by the association $S \mapsto S'$ above.
+Finally, applying Lem.~\ref{MainLemma} with the map $\pi: E \to {[m] \choose k}$ defined by $S \mapsto S'$ above completes the proof.
 %\begin{align}
@@
 [maybe smooth analysis something here]
+We hope that researchers in sparse linear coding continue to improve on the bounds and constants here.
 
@@
 Several groups utilize compressed sensing for signal processing tasks: MRI analysis \cite{lustig2008compressed},  image compression \cite{Duarte08}, and, more recently, the design of an ultrafast camera \cite{Gao14}.
-Given such effective uses of compressed sensing, it is only a matter of time before these systems incorporate sparse dictionary learning to encode and process data.
+Given such effective uses of CS, it is only a matter of time before these systems incorporate sparse dictionary learning to encode and process data.
 Guarantees such as those offered by our theorems allow any such device to be equivalent to any other (having different initial parameters and data samples) as long as enough data originate from a statistically identical system.
-
-As a final remark, we hope that researchers in sparse linear coding continue to improve on the bounds and constants here.
 
@@
 \begin{lemma}\label{SpanIntersectionLemma}
-Let $\mathbf{M} \in \mathbb{R}^{n \times m}$. If every $2k$ columns of $\mathbf{M}$ are linearly independent, then for any $F \subseteq 2^{[m]}$ of rank $k$:
+Let $\mathbf{M} \in \mathbb{R}^{n \times m}$. If every $2k$ columns of $\mathbf{M}$ are linearly independent, then for any $F \subseteq {[m] \choose k}$:
 \begin{align*}
@@
 \begin{proof} 
-Fix $\mathbf{x} \in \mathbb{R}^m$ and $k \geq 2$.
-Recall that the orthogonal projection onto a subspace $V \subseteq \mathbb{R}^m$ is the mapping $\Pi_V$ from $\mathbb{R}^m$ to $V$ that associates with each $\mathbf{x}$ its unique nearest point in $V$; i.e., $\|\mathbf{x} - \Pi_V\mathbf{x}\|_2 = \text{\rm dist}(\mathbf{x}, V)$.
+Recall that orthogonal projection onto a subspace $V \subseteq \mathbb{R}^m$ is the mapping $\Pi_V: \mathbb{R}^m \to V$ that associates with each $\mathbf{x}$ its unique nearest point in $V$; i.e., $\|\mathbf{x} - \Pi_V\mathbf{x}\|_2 = \text{\rm dist}(\mathbf{x}, V)$.
 % Since subspaces of real vector spaces are closed, we can replace inf with min in def. of orthogonal projection
 
-We begin the proof by observing that:
+We begin the proof by observing:
 %Use Pythagoras' Theorem first?
@@
 %
-by the triangle inequality and the fact that the spectral norm $\|\Pi_{V_{\ell}}\|_2 \leq 1$ for all $\ell$ (since $\Pi_{V_{\ell}}$ are orthogonal projections).
+using the triangle inequality and that the spectral norm satisfies $\|\Pi_{V_{\ell}}\|_2 \leq 1$ for all $\ell$ (since $\Pi_{V_{\ell}}$ are orthogonal projections).
 
@@
 
-Substituting this into \eqref{f} and rearranging yields \eqref{DTILeq} after substituting $r(\{V_i\}_{i=1}^k)$ for $1 - z$ (as $z$ may depend on the arbitrary ordering of the $V_i$).
+Substituting this into \eqref{f} and rearranging yields \eqref{DTILeq} after replacing $1 - z$ with $r(\{V_i\}_{i=1}^k)$ (as $z$ may depend on the arbitrary ordering of the $V_i$).
 \end{proof}
@@
 \begin{lemma}\label{NonEmptyLemma} 
-Fix integers $\ell$ and $m \leq \hat m$.
+Fix $\ell$ and $m \leq \hat m$.
 Suppose $E \subseteq 2^{[m]}$ is $\ell$-regular and satisfies the singleton intersection property.
-If there exists a map $\pi: E \to 2^{[\hat m]}$ such that $\sum_{S \in E} |S| = \sum_{S \in E} |\pi(S)|$ and:
+If there is a map $\pi: E \to 2^{[\hat m]}$ with $\sum_{S \in E} |S| = \sum_{S \in E} |\pi(S)|$ and:
 \begin{align}\label{cond}
-|\cap_{S \in F} \pi(S)| \leq |\cap_{S \in F} S |,\ \ \   \text{for all } F \subseteq E,
+|\bigcap_{S \in F} \pi(S)| \leq |\bigcap_{S \in F} S |,\ \ \   \text{for all } F \subseteq E,
 \end{align}
@@
 \end{align}
-We will now show that:
-\begin{align}\label{fact2}
-|\bigcap_{S \in F} \pi(S)| \leq |\bigcap_{S \in F} S |,\ \ \   \text{for all } \ F \subseteq E.
-\end{align}
+We will now show that \eqref{cond} holds.
+%\begin{align}\label{fact2}
+%|\bigcap_{S \in F} \pi(S)| \leq |\bigcap_{S \in F} S |,\ \ \   \text{for all } \ F \subseteq E.
+%\end{align}
 
 Fix $F \subseteq E$.
-Since $\text{\rm Span}\{\mathbf{B}_{\cap_{S \in F}\pi(S)}\} \subseteq \cap_{S \in F} \text{\rm Span}\{\mathbf{B}_{\pi(S)}\}$, if $\cap_{S \in F} \text{\rm Span}\{\mathbf{B}_{\pi(S)}\} = \textbf{0}$ then we must have $|\cap_{S \in F} \pi(S)| = 0$ (as $\mathbf{B}_i \neq \textbf{0}$ for all $i$) and \eqref{fact2} trivially holds.
+Since $\text{\rm Span}\{\mathbf{B}_{\cap_{S \in F}\pi(S)}\} \subseteq \cap_{S \in F} \text{\rm Span}\{\mathbf{B}_{\pi(S)}\}$, if $\cap_{S \in F} \text{\rm Span}\{\mathbf{B}_{\pi(S)}\} = \textbf{0}$ then we must have $|\cap_{S \in F} \pi(S)| = 0$ (as $\mathbf{B}_i \neq \textbf{0}$ for all $i$) and \eqref{cond} trivially holds.
 Suppose then that the intersection is not the zero vector.
@@
 %&\leq \frac{1}{r( \{ \text{\rm Span}\{\mathbf{A}_{S}\}_{S \in F})} \sum_{S \in F} \frac{ \varepsilon }{ L(\mathbf{AX}_{J(S)}) } \nonumber \\
-&\leq \frac{|F| \delta}{r( \{ \text{\rm Span}\{\mathbf{A}_{S}\} \}_{S \in F})} 
+&\leq \frac{|F| \varepsilon}{r( \{ \text{\rm Span}\{\mathbf{A}_{S}\} \}_{S \in F})} 
 %&< L_2(\mathbf{A}) \frac{|F| }{ 2^{|E|}} \left( \frac{ \min_{\substack{F \subseteq E}} r( \{ \text{\rm Span}\{\mathbf{A}_{S}\}_{S \in F}) }{ r( \{ \text{\rm Span}\{\mathbf{A}_{S}\}_{S \in F}) } \right) \left( \frac{\min_{S \in E} L_k(\mathbf{AX}_{I(S)}) }{ \min_{T \in F} L(\mathbf{AX}_{J(T)}) } \right) \nonumber \\
-\leq \tilde C_2 \delta, 
+\leq C_2 \varepsilon. 
 \end{align}
 %
-Note that since $\delta < L_2(\mathbf{A}) / \tilde C_2$, by \eqref{delrho} the right-hand side in \eqref{rando} is strictly less than one, so \eqref{dimLem} implies that $\dim(\text{\rm Span}\{\mathbf{B}_{\cap_{S \in F}\pi(S)}\}) \leq \dim(\text{\rm Span}\{\mathbf{A}_{\cap_{S \in F} S}\})$ and \eqref{fact2} follows from the linear independence of the columns of $\mathbf{A}_{S}$ and $\mathbf{B}_{\pi(S)}$ for all $S \in F$.
+Note that since $\varepsilon < L_2(\mathbf{A}) / \tilde C_2$, by \eqref{delrho} the right-hand side in \eqref{randoml} is strictly less than one, so \eqref{dimLem} implies that $\dim(\text{\rm Span}\{\mathbf{B}_{\cap_{S \in F}\pi(S)}\}) \leq \dim(\text{\rm Span}\{\mathbf{A}_{\cap_{S \in F} S}\})$ and \eqref{fact2} follows from the linear independence of the columns of $\mathbf{A}_{S}$ and $\mathbf{B}_{\pi(S)}$ for all $S \in F$.
 
@@
 Since $E$ satisfies the singleton intersection property, $\{\ell\} = \cap F(\ell)$ for the star $F(\ell) \subseteq E$.
-By \eqref{fact2}, we have that $\cap_{S \in F(\ell)} \pi(S)$ is either empty or it contains a single element.
+By \eqref{cond}, we have that $\cap_{S \in F(\ell)} \pi(S)$ is either empty or it contains a single element.
 Lem.~\ref{NonEmptyLemma} ensures the latter case is the only possibility.
 Thus, the association $\ell \mapsto \cap_{S \in F(\ell)} \pi(S)$ defines a map $\hat \pi: [m] \to [m]$ and $\dim(\text{\rm Span}\{\mathbf{B}_{\hat \pi(\ell)}\}) = 1$, since $\mathbf{B}_i \neq \textbf{0}$ for all $i$.
-By \eqref{eqdim}, it follows from \eqref{rando} that $d\left( \text{\rm Span}\{\mathbf{A}_\ell\}, \text{\rm Span}\{ \mathbf{B}_{\hat \pi(\ell)} \} \right) \leq C_2\delta$.
-Since $\ell$ is arbitrary, fixing $\hat \varepsilon = C_2\delta$ it follows from \eqref{rando} that for every basis vector $\mathbf{e}_\ell \in \mathbb{R}^m$ there exists some $c'_\ell \in \mathbb{R}$ such that $\|\mathbf{A}\mathbf{e}_\ell - c'_\ell \mathbf{B}\mathbf{e}_{\hat \pi(\ell)}\|_2 \leq \hat \varepsilon < L_2(\mathbf{A})$.
+By \eqref{eqdim}, it follows from \eqref{randoml} that $d\left( \text{\rm Span}\{\mathbf{A}_\ell\}, \text{\rm Span}\{ \mathbf{B}_{\hat \pi(\ell)} \} \right) \leq C_2 \varepsilon$.
+Since $\ell$ is arbitrary, fixing $\hat \varepsilon = C_2\delta$ it follows from \eqref{randoml} that for every basis vector $\mathbf{e}_\ell \in \mathbb{R}^m$ there exists some $c'_\ell \in \mathbb{R}$ such that $\|\mathbf{A}\mathbf{e}_\ell - c'_\ell \mathbf{B}\mathbf{e}_{\hat \pi(\ell)}\|_2 \leq \hat \varepsilon < L_2(\mathbf{A})$.
 This is exactly the supposition in \eqref{1D} (letting $c_i = \|\mathbf{A}_i\|_2^{-1}$ for all $i$) and the result follows from the subsequent arguments for the case $k=1$ in Sec.~\ref{DUT}.

### 2017-04-01 manuscripts/PNAS/chazthm_pnas.tex
chaz

--- 2017-04-01 manuscripts/PNAS/chazthm_pnas.tex
@@
 
-\begin{theorem}
+\begin{corollary}
 Fix $n, \ell$, and $k < m$.
-Suppose $\mathbf{A}~\in~\mathbb{R}^{n \times m}$ satisfies the spark condition \eqref{SparkCondition} and that $k$-sparse \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} have at least \mbox{$k \left[ (k-1){ m \choose k} + 1 \right]$} vectors supported in general linear position on each set in an $\ell$-regular $E \subseteq {[m] \choose k}$ with the SIP.
+Suppose $\mathbf{A}~\in~\mathbb{R}^{n \times m}$ satisfies the spark condition \eqref{SparkCondition} and that $k$-sparse \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} have at least \mbox{$\left[ (k-1){ m \choose k} + 1 \right] + (k-1)^2{m \choose k-1}$} vectors supported in general linear position on each set in an $\ell$-regular $E \subseteq {[m] \choose k}$ with the SIP.
 Given any $\delta_1, \delta_2 \geq 0$ and $\varepsilon \leq \varepsilon(\delta_1, \delta_2)$, the following holds.
@@
 necessarily satisfies the recovery inequalities in \eqref{def1}. % \eqref{Cstable} and \eqref{b-PDa}.
-\end{theorem}
+\end{corollary}
 
@@
 We derive a lower bound on the number of $k$-sparse $\mathbf{\hat x}_i$ and then apply Thm.~\ref{DeterministicUniquenessCorollary}. 
-[*** This proof still has a gap ***]
-Let $n_p$ be the number of $\mathbf{\hat x}_i$ with $\|\mathbf{\hat x}_i\|_0 = p$.  %, so that $\sum_{p = 1}^{m} n_p = N$. 
+First, note that $\|\mathbf{\hat x}_i\|_0 \neq 0$ for all $i$, since otherwise we would have $\mathbf{A}\mathbf{x}_i = \mathbf{B}\mathbf{\hat x}_i = \mathbf{0} \implies \mathbf{x}_i = \mathbf{0}$ by the spark condition, contradicting the general linear position of the $\mathbf{x}_i$.
+Let $n_p$ be the number of $\mathbf{\hat x}_i$ with $\|\mathbf{\hat x}_i\|_0 = p$.
+%, so that $\sum_{p = 1}^{m} n_p = N$.
 Since the $\mathbf{x}_i$ are all $k$-sparse, by \eqref{minsum} we have:
@@
 \begin{align}
-(k-1) \sum_{p =1}^k n_p \geq \sum_{p = 1}^k (k-p)n_p \geq \sum_{p = k+1}^{m} (p-k) n_p
+\sum_{p = k+1}^m n_p \leq \sum_{p = k+1}^m (p-k) n_p \leq \sum_{p = 1}^k (k-p)n_p \leq (k-1) \sum_{p = 1}^{k-1} n_p.
 \end{align}
-\[ \geq \sum_{p = k+1}^{m} n_p = N - \sum_{p = 1}^k n_p \implies \sum_{p =1}^k n_p \geq N / k.\]
-
-In particular, at least $N / k$ of the $\mathbf{\hat x}_i$ are $k$-sparse.
-Therefore, there is some $N' \subseteq [N]$ for which for each $S \in E$ there are $(k-1){m \choose k}+1$ of the vectors $\mathbf{x}_i$ with $i \in [N']$ supported on $S$ and for which $\mathbf{\hat x}_i$ is $k$-sparse for all $i \in [N']$.
+%\[ \implies \sum_{p = k+1}^m n_p \leq (k-1)^2 {\hat m \choose k-1} \]
+By the spark condition and general linear position of the $\mathbf{x}_i$, every $k$ vectors $\mathbf{Ax}_i$ span a $k$-dimensional space; hence, at most $k-1$ vectors $\mathbf{\hat x}_i$ can share a support of size $k-1$ or less, and the number of $(k-1)$-sparse vectors $\mathbf{\hat x}_i$ is then bounded from above by $(k-1) { m \choose k-1}$.
+It follows that at least $N - (k-1)^2 {m \choose k-1}$ of the vectors $\mathbf{\hat  x}_i$ are $k$-sparse, and that there must then be some $N' \subseteq [N]$ for which for each $S \in E$ there are $(k-1){m \choose k}+1$ of the vectors $\mathbf{x}_i$ with $i \in [N']$ supported on $S$ and for which $\mathbf{\hat x}_i$ is $k$-sparse for all $i \in [N']$.
 The result now follows directly from Thm.~\ref{DeterministicUniquenessCorollary}.
@@
 \begin{lemma}\label{NonEmptyLemma} 
-Fix integers $\ell$ and $m \leq \hat m$.
+Fix integers $\ell, m$ and $\hat m$.
 Suppose $E \subseteq 2^{[m]}$ is $\ell$-regular and satisfies the singleton intersection property.
@@
 %
-then the association $i \mapsto \cap \pi(F(i))$ defines an injective map from $[J]$ to $[\hat m]$ for some $J \subseteq [m]$ of size $\hat m - \ell(\hat m - m)$.
+then $\hat m \geq m$ and the association $i \mapsto \cap \pi(F(i))$ defines an injective map from $[J]$ to $[\hat m]$ for some $J \subseteq [m]$ of size $\hat m - \ell(\hat m - m)$.
 In particular, if $\hat m = m$ then the map $\pi$ is induced by a permutation.
@@
 \begin{proof}
-[* TODO * Chris rewrite for $\hat m$] Fix $T = \{(j, S): j \in \pi(S), S \in E\}$.
-We have $|T| = \sum_{S \in E} |\pi(S)| = \sum_{S \in E} |S| = \sum_{i \in [m]} \deg(i) = \ell m$ by regularity of $E$.
-Note that by \eqref{cond} there can be no more than $\ell$ elements of $T$ with a given first index, since $E$ is $\ell$-regular.
-Pigeonholing the elements of $T$ with respect to the set of possible first indices, we see then that for each $j$ there must be exactly $\ell$ elements of $T$ with $j$ as a first index; hence, $\pi(E)$ is $\ell$-regular.
+[ ** TODO ** rewrite for $\hat m > m$. ]
+We first show that $\hat m \geq m$.
+Fix $T = \{(j, S): j \in \pi(S), S \in E\}$.
+Then $|T| = \sum_{S \in E} |\pi(S)| = \sum_{S \in E} |S| = \sum_{i \in [m]} \deg(i) = \ell m$ by regularity of $E$.
+If $\hat m < m$ then by pigeonholing the $m \ell \geq \ell (\hat m + 1) \geq [(\ell + 1) - 1] \hat m + 1$ elements of $T$ with respect to the set $[\hat m]$ of possible first indices, we see that there must exist at least $\ell + 1$ elements of $T$ having the same first index.
+But by \eqref{cond} there can be no more than $\ell$ elements of $T$ with a given first index, since $E$ is $\ell$-regular.
+Hence $\hat m \geq m$.
+Again, pigeonholing the elements of $T$ with respect to the set $[\hat m]$ of possible first indices, we see that for each $j$ there must be exactly $\ell$ elements of $T$ with $j$ as a first index; hence, $\pi(E)$ is $\ell$-regular.
 

### 2017-04-01 manuscripts/PNAS/chazthm_pnas.tex

--- 2017-04-01 manuscripts/PNAS/chazthm_pnas.tex
@@
 \begin{lemma}\label{NonEmptyLemma} 
-Fix $\ell$ and $m \leq \hat m$.
+Fix integers $\ell, m$ and $\hat m$.
 Suppose $E \subseteq 2^{[m]}$ is $\ell$-regular and satisfies the singleton intersection property.
-If there is a map $\pi: E \to 2^{[\hat m]}$ with $\sum_{S \in E} |S| = \sum_{S \in E} |\pi(S)|$ and:
+If there exists a map $\pi: E \to 2^{[\hat m]}$ such that $\sum_{S \in E} |S| = \sum_{S \in E} |\pi(S)|$ and:
 \begin{align}\label{cond}

### 2017-04-01 manuscripts/PNAS/chazthm_pnas.tex
meh
discuso

--- 2017-04-01 manuscripts/PNAS/chazthm_pnas.tex
@@
 
-\begin{definition}
+\begin{definition}\label{sip}
 Given $E \subseteq 2^{[m]}$, the \textbf{star} $F(i)$ at $i$ are those $S \in E$ with $i \in S$.
@@
 In this note, we generalize the approach of \cite{Hillar15} for showing uniqueness in Prob.~\ref{InverseProblem} to the case of noisy measurements while also reducing the sufficient number of samples.
+% FRITZ: Inverse problems instead of Data Analysis.
+Don't assume that everyone is assuming they are recovering ground truth.
+Cite results again and state implications!
+Focus on them (probabilistic ones too).
+Our results provide theoretical grounding for the use of sparse linear coding in blind source separation, wherein the goal is to infer the generating dictionary and sparse codes from noisy measurements generated as in \eqref{LinearModel}.
+Such results are motivated by the seemingly universal representations discovered by training a sparse linear coding model with natural data, independently of specific algorithmic implementation.
+We also collect a set of useful mathematical tools and basic results for future research.
+% We close with several application areas.
+
+%\textbf{Inverse Problems}.  
 % from $N=k{m \choose k}^2$ to $N = m(k-1){m \choose k}+m$. 
@@
 Moreover, if solutions are constrained to satisfy \eqref{SparkCondition}, then only an upper bound on the number of dictionary elements need be taken as given.
-One interesting aspect of our contribution is a combinatorial criteria (regular hypergraphs satisfying the singular intersection property) for choosing support sets for original sparse codes; fully understanding those combinatorial designs allowing for stable representations of datasets is the subject of future work.
+One interesting aspect of our contribution is a combinatorial criteria (regular hypergraphs satisfying the singular intersection property, Def.~\ref{sip}) for choosing support sets for original sparse codes.
+Fully understanding those combinatorial designs allowing for stable representations of datasets is an interesting research area for the future.
 We also remark that our main uniqueness result (Thm.~\ref{DeterministicUniquenessTheorem}) accounts for deterministic ``worst-case'' noise, whereas the ``effective'' noise might be much smaller when it is sampled from a given distribution; in such cases, the constants in our theorems %Thms.~\ref{DeterministicUniquenessTheorem},~\ref{DeterministicUniquenessTheorem2}
-will be different. %We note also that these results extend trivially to cases where point-wise injective nonlinearities are applied to the data. 
-We close with several application areas.
+should be better. %We note also that these results extend trivially to cases where point-wise injective nonlinearities are applied to the data.
 
-% FRITZ: Inverse problems instead of Data Analysis.
-Don't assume that everyone is assuming they are recovering ground truth.
-Cite results again and state implications!
-Focus on them (probabilistic ones too).
-\textbf{Inverse Problems}.  
-Our results provide theoretical grounding for the use of sparse linear coding in blind source separation, wherein the goal is to infer the generating dictionary and sparse codes from noisy measurements generated as in \eqref{LinearModel} (e.g., recovering a rat's position on a linear track from local field potentials in Hippocampus \cite{Agarwal14}).
-It would be of practical utility therefore to determine the best possible dependence of $\varepsilon$ on $\delta_1, \delta_2$ (see \eqref{epsdel}) as well as the minimal requirements on the number and diversity of generating codes.
+As an inverse problem to be approximated by a (typically) numerical algorithm, what we have shown here is that the sparse linear coding model  generally produces \textit{well-posed} optimizations.
+This early concept of Hadamard \cite{Hadamard1902}) can be paraphrased as the idea that algorithms inverting a parameterized model of data should have unique solutions that are continuous in the data.
+In other words, perturbing slightly a dataset should only slightly influence the uniqueness of parameters in the model, rather than discontinuously affect the character of optimization involved.
+In this regard, we provide explicit constants in terms of original latent parameters, although they are too expensive to compute for any practical utility.
+% We hope that researchers in sparse linear coding continue to improve on the bounds and constants here.
+
+One of the technical difficulties in our main theorem is the absence of a spark condition assumption on alternate dictionaries; in fact, several results here are much simpler to prove when such an assumption is made.
+However, in general, it cannot necessarily be assumed that a learned dictionary have satisfy the spark condition.
+In addition, guaranteeing that a dictionary has this property is probably intractable given its NP-hardness \cite{tillmann2014computational}.
+It would be of practical utility to determine the best possible dependence of $\varepsilon$ on $\delta_1, \delta_2$ (see \eqref{epsdel}) as well as the minimal requirements on the number and diversity of generating codes.
 %We encourage researchers to extend our results and tighten these parameters.
-Phrased in the language of Hadamard \cite{Hadamard1902}),  Mention sparse matrix factorization. [Effective computation of stable datasets, at least in principle.]
-[maybe smooth analysis something here]
-We hope that researchers in sparse linear coding continue to improve on the bounds and constants here.
 
-\textbf{Theoretical Neuroscience}.
-Sparse dictionary learning and related methods have recovered characteristic components of natural images and sounds \cite{bellsejnowski1996, smithlewicki2006, Carlson12}, reproducing response properties of cortical neurons.
+%\textbf{Theoretical Neuroscience}.
+In the field of theoretical neuroscience, sparse dictionary learning and related methods have recovered characteristic components of natural images and sounds \cite{bellsejnowski1996, smithlewicki2006, Carlson12}, reproducing response properties of cortical neurons.
 Our theorems suggest that this correspondence could be due to the uniqueness of sparse representations.
 Furthermore, our guarantees justify the hypothesis of \cite{Coulter10, Isely10} that sparse codes passed through a communication bottleneck in the brain can be recovered from random projections via (unsupervised) biologically plausible sparse dictionary learning (e.g., \cite{rehnsommer2007, rozell2007neurally, hu2014hebbian}).
-Invariance: \cite{pitts1947}.
+In fact, the concept of ``universal'' objects in the brain is an early idea in neuroscience theory \cite{pitts1947}.
+But this is also in data science applications.
+For instance, when recovering a rat's position on a linear track from learning a sparse linear model on  local field potentials in Hippocampus \cite{Agarwal14}.
+
 %TODO: add reproduction of response propeties in olfactory cortex?
@@
 
-\textbf{Engineering}.
-Several groups utilize compressed sensing for signal processing tasks: MRI analysis \cite{lustig2008compressed},  image compression \cite{Duarte08}, and, more recently, the design of an ultrafast camera \cite{Gao14}.
+%\textbf{Engineering}.
+In engineering, several groups have utilized compressed sensing for signal processing tasks: MRI analysis \cite{lustig2008compressed},  image compression \cite{Duarte08}, and, more recently, the design of an ultrafast camera \cite{Gao14}.
 Given such effective uses of CS, it is only a matter of time before these systems incorporate sparse dictionary learning to encode and process data.

### 2017-04-01 manuscripts/PNAS/chazthm_pnas.tex

@@
 %\end{proposition}
-%<<<<<<< HEAD
-%As mentioned above, it is easy to construct such $E$ with $|E| = m$, implying the lower bound for sample size $N$ from the introduction.
-%A straightforward calculation verifies that if $E$ is an $\ell$-regular hypergraph of rank $k$ satisfying the SIP, then $|E| \geq \ell m/k$.
-%%Note that if $E$ is an $\ell$-regular hypergraph of rank $k$ satisfying the SIP, then $|E| \geq \ell m/k$: \[|E|k \geq \sum_{S \in E}|S| = \sum_{i \in [m]} \deg(i) = \ell m.\] 
-%In certain cases, there are simple constructions achieving this minimum; for example, when $k = \sqrt{m}$ one can take $E$ to be the rows and columns formed by arranging $[m]$ in a square grid.
-In light of Cor.~\ref{DeterministicUniquenessCorollary}, it would be interesting to determine other minimal such $E$.
-%=======
 %Note that every $\ell$-regular hypergraph $E \subseteq {[m] \choose k}$ satisfies: \[|E|k = \sum_{S \in E}|S| = \sum_{i \in [m]} \deg(i) = \ell m.\] 
@@
 \begin{align}\label{minsum}
-\arg \min \sum_{i = 1}^N \|\mathbf{\hat x}_i\|_0 \ \ \text{s.t.} \ \ \|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\hat x}_i\|_2 \leq \varepsilon, \ \ \text{$i \in [N]$},
+\arg \min \sum_{i = 1}^N \|\mathbf{\hat x}_i\|_0 \ \ \text{s.t.} \ \ \mathbf{B}\mathbf{\hat x}_i = \mathbf{A}\mathbf{x}_i, \ \ \text{$i \in [N]$}, %\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\hat x}_i\|_2 \leq \varepsilon, \ \ \text{$i \in [N]$},
 \end{align}
 necessarily satisfies the recovery inequalities in \eqref{def1}. % \eqref{Cstable} and \eqref{b-PDa}.
-\end{theorem}
+\end{corollary}
 

### 2017-04-01 manuscripts/PNAS/chazthm_pnas.tex
discussion SR

@@
 
-In this note, we generalize the approach of \cite{Hillar15} for showing uniqueness in Prob.~\ref{InverseProblem} to the case of noisy measurements while also reducing the sufficient number of samples.
+In this note, we generalize the approach of \cite{Hillar15} to prove uniqueness in Prob.~\ref{InverseProblem} for the case of noisy measurements while also reducing the sufficient number of samples.
 % FRITZ: Inverse problems instead of Data Analysis.
@@
 Focus on them (probabilistic ones too).
-Our results provide theoretical grounding for the use of sparse linear coding in blind source separation, wherein the goal is to infer the generating dictionary and sparse codes from noisy measurements generated as in \eqref{LinearModel}.
-Such results are motivated by the seemingly universal representations discovered by training a sparse linear coding model with natural data, independently of specific algorithmic implementation.
-We also collect a set of useful mathematical tools and basic results for future research.
+Our results provide theoretical grounding for the use of sparse linear coding in blind source separation, wherein the goal is to infer the generating dictionary and sparse codes from noisy measurements, \eqref{LinearModel}.
+We also collect a set of useful mathematical tools and basic facts for future research.
+The main motivation for this work, however, was to understand how seemingly universal and stable representations are discovered by training a sparse linear coding model on natural data, independent of specific algorithmic implementation.
+We elaborate more on these applications below after discussing  theoretical aspects.
 % We close with several application areas.
@@
 Moreover, if solutions are constrained to satisfy \eqref{SparkCondition}, then only an upper bound on the number of dictionary elements need be taken as given.
-One interesting aspect of our contribution is a combinatorial criteria (regular hypergraphs satisfying the singular intersection property, Def.~\ref{sip}) for choosing support sets for original sparse codes.
+
+What we have shown here is that as an inverse problem to be approximated by a numerical algorithm, the sparse linear coding model  generally produces \textit{well-posed} optimizations.
+This early concept of Hadamard \cite{Hadamard1902} can be paraphrased as the idea that good parameterized models should pose optimization problems with solutions that are stable; that is, continuous in the data.
+In other words, perturbing a dataset by a small amount should only slightly influence the identifiability or uniqueness of parameters in the model, rather than discontinuously affect the character of optimization involved.
+In this regard, we demonstrate a linear relationship between noise in the data and the unique solution in  sparse linear coding, with explicit constants expressed in terms of original latent parameters.
+Nonetheless, it would be of practical utility to determine the best possible dependence of $\varepsilon$ on $\delta_1, \delta_2$ in \eqref{epsdel} as well as the minimal requirements on the number and diversity of generating codes, and we hope that other researchers continue to improve and extend our results.
+% , although they are too computationally expensive to be of practical value.  We hope .
+
+One notable component of our contribution is a combinatorial criteria (regular hypergraphs satisfying the singular intersection property, Def.~\ref{sip}) for choosing support sets for original sparse codes.
 Fully understanding those combinatorial designs allowing for stable representations of datasets is an interesting research area for the future.
-We also remark that our main uniqueness result (Thm.~\ref{DeterministicUniquenessTheorem}) accounts for deterministic ``worst-case'' noise, whereas the ``effective'' noise might be much smaller when it is sampled from a given distribution; in such cases, the constants in our theorems %Thms.~\ref{DeterministicUniquenessTheorem},~\ref{DeterministicUniquenessTheorem2}
-should be better. %We note also that these results extend trivially to cases where point-wise injective nonlinearities are applied to the data.
+We also remark that our main uniqueness result (Thm.~\ref{DeterministicUniquenessTheorem}) accounts for deterministic ``worst-case'' noise, whereas the ``effective'' noise might be much smaller when it is sampled from a given distribution; in such cases, the constants in our results %Thms.~\ref{DeterministicUniquenessTheorem},~\ref{DeterministicUniquenessTheorem2}
+will improve. %We note also that these results extend trivially to cases where point-wise injective nonlinearities are applied to the data.
 
-As an inverse problem to be approximated by a (typically) numerical algorithm, what we have shown here is that the sparse linear coding model  generally produces \textit{well-posed} optimizations.
-This early concept of Hadamard \cite{Hadamard1902}) can be paraphrased as the idea that algorithms inverting a parameterized model of data should have unique solutions that are continuous in the data.
-In other words, perturbing slightly a dataset should only slightly influence the uniqueness of parameters in the model, rather than discontinuously affect the character of optimization involved.
-In this regard, we provide explicit constants in terms of original latent parameters, although they are too expensive to compute for any practical utility.
-% We hope that researchers in sparse linear coding continue to improve on the bounds and constants here.
+A technical difficulty in our main theorem is the absence of a spark condition assumption on alternate data factorizations.
+Although mathematically interesting that no such requirement is necessary, there are other reasons to desire such a theoretical guarantee.
+For instance, it is difficult to ensure an algorithm maintain a dictionary satisfying \eqref{SparkCondition} at each learning stage; indeed, even certifying that a dictionary has this property is probably intractable given its NP-hardness \cite{tillmann2014computational}.
 
-One of the technical difficulties in our main theorem is the absence of a spark condition assumption on alternate dictionaries; in fact, several results here are much simpler to prove when such an assumption is made.
-However, in general, it cannot necessarily be assumed that a learned dictionary have satisfy the spark condition.
-In addition, guaranteeing that a dictionary has this property is probably intractable given its NP-hardness \cite{tillmann2014computational}.
-It would be of practical utility to determine the best possible dependence of $\varepsilon$ on $\delta_1, \delta_2$ (see \eqref{epsdel}) as well as the minimal requirements on the number and diversity of generating codes.
-%We encourage researchers to extend our results and tighten these parameters.
+In fact, though, uniqueness guarantees with minimal assumptions apply to all areas of data science and engineering that utilize learned sparse representations.
+For example, several groups have utilized compressed sensing for signal processing tasks: MRI analysis \cite{lustig2008compressed},  image compression \cite{Duarte08}, and, more recently, the design of an ultrafast camera \cite{Gao14}.
+Given such effective uses of CS, it is only a matter of time before these systems incorporate sparse representational learning to encode and process data (e.g., in a device that learns structure from motion \cite{kong2016prior}).
+In these cases, guarantees such as those offered by our theorems allow any device to be equivalent to any other (having different initial parameters, data samples, and perhaps algorithms) as long as enough data originate from a statistically identical system.
+%Data science:
+%  
+%in a common application of compressed sensing in engineering
 
 %\textbf{Theoretical Neuroscience}.
-In the field of theoretical neuroscience, sparse dictionary learning and related methods have recovered characteristic components of natural images and sounds \cite{bellsejnowski1996, smithlewicki2006, Carlson12}, reproducing response properties of cortical neurons.
-Our theorems suggest that this correspondence could be due to the uniqueness of sparse representations.
+Additionally, in the field of theoretical neuroscience, sparse dictionary learning and related methods have recovered characteristic components of natural images \cite{Olshausen96, hurri1996image, bell1997independent, van1998independent} and sounds \cite{bellsejnowski1996, smithlewicki2006, Carlson12}, reproducing response properties of cortical neurons.
+Our theorems suggest that this correspondence could be due to  sparse representations being ``universal'' in natural data, an early mathematical idea in neural theory \cite{pitts1947}.
 Furthermore, our guarantees justify the hypothesis of \cite{Coulter10, Isely10} that sparse codes passed through a communication bottleneck in the brain can be recovered from random projections via (unsupervised) biologically plausible sparse dictionary learning (e.g., \cite{rehnsommer2007, rozell2007neurally, hu2014hebbian}).
-In fact, the concept of ``universal'' objects in the brain is an early idea in neuroscience theory \cite{pitts1947}.
-But this is also in data science applications.
+
+%In fact, the concept of ``universal'' objects in the brain is .
+
+%But this is also in data science applications.
 For instance, when recovering a rat's position on a linear track from learning a sparse linear model on  local field potentials in Hippocampus \cite{Agarwal14}.
@@
 %\textbf{Engineering}.
-In engineering, several groups have utilized compressed sensing for signal processing tasks: MRI analysis \cite{lustig2008compressed},  image compression \cite{Duarte08}, and, more recently, the design of an ultrafast camera \cite{Gao14}.
-Given such effective uses of CS, it is only a matter of time before these systems incorporate sparse dictionary learning to encode and process data.
-Guarantees such as those offered by our theorems allow any such device to be equivalent to any other (having different initial parameters and data samples) as long as enough data originate from a statistically identical system.
 

### 2017-04-01 manuscripts/PNAS/chazthm_pnas.tex
sml updates and bib

@@
 Here, we prove that for all diverse enough datasets generated from the sparse coding model, latent dictionaries and codes are uniquely determined up to measurement error.
-Applications are given to data analysis, neuroscience, and engineering.
+Applications are given to data analysis, engineering, and neuroscience.
 \end{abstract}
@@
 \begin{align}\label{Cstable}
-\|\mathbf{A}_j - (\mathbf{B}\mathbf{PD})_j\|_2 \leq C_1 \varepsilon,\ \ \   \text{for all $j \in [m]$},
+\|\mathbf{A}_j - (\mathbf{B}\mathbf{PD})_j\|_2 \leq C_1 \varepsilon,\ \ \   \text{for  $j \in [m]$},
 \end{align}
@@
 \begin{align}\label{b-PDa}
-\|\mathbf{x}_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\hat x}_i\|_1 &\leq  \left( \frac{ 1+C_1 \|\mathbf{x}_i\|_1 }{ L_{2k}(\mathbf{A}) -  C_1\varepsilon } \right) \varepsilon,\ \ \   \text{for all $i \in [N]$}.
+\|\mathbf{x}_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\hat x}_i\|_1 &\leq  \left( \frac{ 1+C_1 \|\mathbf{x}_i\|_1 }{ L_{2k}(\mathbf{A}) -  C_1\varepsilon } \right) \varepsilon,\ \ \   \text{for $i \in [N]$}.
 \end{align}
@@
 
-For expositional clarity, we delay defining the (explicit) constant $C_1 = C_1(\mathbf{A}, \{\mathbf{x}_i\}_{i=1}^N, E)$ until Section \ref{DUT} (\eqref{Cdef1}).
-% , since it requires additional definitions not critical to the statement of our results.
-
-An important consequence of Thm.~\ref{DeterministicUniquenessTheorem} is that \eqref{def1} is guaranteed provided $\varepsilon$ does not exceed: % [*** TODO: verify this is still correct ***]
+An important consequence of Thm.~\ref{DeterministicUniquenessTheorem} is that \eqref{def1} is guaranteed provided $\varepsilon$ in Def.~\ref{maindef} does not exceed: % [*** TODO: verify this is still correct ***]
 \begin{align}\label{epsdel}
@@
 \end{align}
+For expositional clarity, we delay defining the (explicit) constant $C_1 = C_1(\mathbf{A}, \{\mathbf{x}_i\}_{i=1}^N, E)$ until Section \ref{DUT} (\eqref{Cdef1}).
+% , since it requires additional definitions not critical to the statement of our results.
 
@@
 Fix $n, \ell$, and $k < m$.
-Suppose $\mathbf{A}~\in~\mathbb{R}^{n \times m}$ satisfies the spark condition \eqref{SparkCondition} and that $k$-sparse \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} have at least \mbox{$\left[ (k-1){ m \choose k} + 1 \right] + (k-1)^2{m \choose k-1}$} vectors supported in general linear position on each set in an $\ell$-regular $E \subseteq {[m] \choose k}$ with the SIP.
-Given any $\delta_1, \delta_2 \geq 0$ and $\varepsilon \leq \varepsilon(\delta_1, \delta_2)$, the following holds.
-% (\eqref{epsdel}).
+Let $\mathbf{A}~\in~\mathbb{R}^{n \times m}$ satisfy the spark condition \eqref{SparkCondition} and $k$-sparse \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} have at least \mbox{$\left[ (k-1){ m \choose k} + 1 \right] + (k-1)^2{m \choose k-1}$} vectors supported in general linear position on each set in an $\ell$-regular $E \subseteq {[m] \choose k}$ with the SIP.
+Given any $\delta_1, \delta_2 \geq 0$ and $\varepsilon \leq \varepsilon(\delta_1, \delta_2)$,  % (\eqref{epsdel}).
 % $\varepsilon < L_2(\mathbf{A}) / C_1$.
 %There exists a constant $C_1 > 0$ for which the following holds for all $\varepsilon < L_2(\mathbf{A}) / C_1$.
-Every solution $\mathbf{B}, \mathbf{\hat x}_i, \ldots, \mathbf{\hat x}_N$ to the constrained $\ell_0$ optimization problem:
+every solution $\mathbf{B}, \mathbf{\hat x}_i, \ldots, \mathbf{\hat x}_N$ to the $\ell_0$ optimization problem:
 \begin{align}\label{minsum}
@@
 \begin{align}
-k \sum_{p = 1}^{m} n_p = kN \geq \sum_{i=1}^N \|\mathbf{x}_i\|_0 \geq \sum_{i=1}^N \|\mathbf{\hat x}_i\|_0 = \sum_{p=1}^{m} p n_p 
+k \sum_{p = 1}^{m} n_p = kN \geq \sum_{i=1}^N \|\mathbf{x}_i\|_0 \geq \sum_{i=1}^N \|\mathbf{\hat x}_i\|_0 = \sum_{p=1}^{m} p n_p.
 \end{align}
-\[\implies \sum_{p = 1}^k (k-p)n_p \geq \sum_{p = k+1}^{m} (p-k) n_p.\]
+%\[\implies \sum_{p = 1}^k (k-p)n_p \geq \sum_{p = k+1}^{m} (p-k) n_p.\]
 Hence,
@@
 %\[ \implies \sum_{p = k+1}^m n_p \leq (k-1)^2 {\hat m \choose k-1} \]
+
 By the spark condition and general linear position of the $\mathbf{x}_i$, every $k$ vectors $\mathbf{Ax}_i$ span a $k$-dimensional space; hence, at most $k-1$ vectors $\mathbf{\hat x}_i$ can share a support of size $k-1$ or less, and the number of $(k-1)$-sparse vectors $\mathbf{\hat x}_i$ is then bounded from above by $(k-1) { m \choose k-1}$.
@@
 %%% No |S| = k assumption %%%
-We shall show that for every $S \in E$ there is some $S' \subseteq [m]$, $|S'| \leq k$, for which the distance $d(\text{\rm Span}\{\mathbf{A}_S\}, \text{\rm Span}\{\mathbf{B}_{S'}\})$ is controlled by $\varepsilon$.
+We shall show that for every $S \in E$ there is some $S' \in {[m] \choose k}$, for which the distance $d(\text{\rm Span}\{\mathbf{A}_S\}, \text{\rm Span}\{\mathbf{B}_{S'}\})$ is controlled by $\varepsilon$.
+Applying Lem.~\ref{MainLemma} with the map $\pi$ defined by $S \mapsto S'$ then completes the proof.
 Since there are $(k-1){m \choose k}+1$ vectors $\mathbf{x}_i$ supported on $S$, the pigeon-hole principle implies that there exists some $S' \in {[m] \choose k}$ and some set of $k$ indices $I(S)$ such that the supports of all $\mathbf{x}_i$ and $\mathbf{\hat x}_i$ with $i \in I(S)$ are contained in $S$ and $S'$, respectively.
@@
 \end{align*}
-where the last inequality is by definition of $L_k$. Also, from Def.~\ref{dDef}, it follows that for all $S \in E$,
+where the last inequality is by definition of $L_k$. Finally, from Def.~\ref{dDef}, it follows that for all $S \in E$,
 \begin{align}\label{rhs222}
@@
 \end{align}
-Finally, applying Lem.~\ref{MainLemma} with the map $\pi: E \to {[m] \choose k}$ defined by $S \mapsto S'$ above completes the proof.
 %\begin{align}
@@
 In this regard, we demonstrate a linear relationship between noise in the data and the unique solution in  sparse linear coding, with explicit constants expressed in terms of original latent parameters.
-Nonetheless, it would be of practical utility to determine the best possible dependence of $\varepsilon$ on $\delta_1, \delta_2$ in \eqref{epsdel} as well as the minimal requirements on the number and diversity of generating codes, and we hope that other researchers continue to improve and extend our results.
+Nonetheless, it would be of practical utility to determine the best possible dependence of $\varepsilon$ on $\delta_1, \delta_2$ in Def.\ref{maindef} as well as the minimal requirements on the number and diversity of generating codes, and we hope that other researchers continue to improve and extend our results.
 % , although they are too computationally expensive to be of practical value.  We hope .
@@
 
-A technical difficulty in our main theorem is the absence of a spark condition assumption on alternate data factorizations.
-Although mathematically interesting that no such requirement is necessary, there are other reasons to desire such a theoretical guarantee.
-For instance, it is difficult to ensure an algorithm maintain a dictionary satisfying \eqref{SparkCondition} at each learning stage; indeed, even certifying that a dictionary has this property is probably intractable given its NP-hardness \cite{tillmann2014computational}.
+A technical difficulty in our main theorem is the absence of a spark condition assumption on alternate sparse data factorizations.
+Although mathematically interesting that no such requirement is necessary, there are other reasons to seek out such a theoretical guarantee.
+For instance, it is difficult to ensure an algorithm maintain a dictionary satisfying \eqref{SparkCondition} at each learning stage; indeed, even certifying  a dictionary has this property is likely intractable given its NP-hardness \cite{tillmann2014computational}.
 
@@
 Given such effective uses of CS, it is only a matter of time before these systems incorporate sparse representational learning to encode and process data (e.g., in a device that learns structure from motion \cite{kong2016prior}).
-In these cases, guarantees such as those offered by our theorems allow any device to be equivalent to any other (having different initial parameters, data samples, and perhaps algorithms) as long as enough data originate from a statistically identical system.
+In these cases, assurances such as those offered by our theorems ensure that different devices (with different initialization, samples, etc.) are equivalent as soon as enough data originate from a statistically identical system.
 %Data science:
@@
 Additionally, in the field of theoretical neuroscience, sparse dictionary learning and related methods have recovered characteristic components of natural images \cite{Olshausen96, hurri1996image, bell1997independent, van1998independent} and sounds \cite{bellsejnowski1996, smithlewicki2006, Carlson12}, reproducing response properties of cortical neurons.
-Our theorems suggest that this correspondence could be due to  sparse representations being ``universal'' in natural data, an early mathematical idea in neural theory \cite{pitts1947}.
+Our results suggest that this correspondence could be due to  sparse representations being ``universal'' in natural data, an early mathematical idea in neural theory \cite{pitts1947}.
 Furthermore, our guarantees justify the hypothesis of \cite{Coulter10, Isely10} that sparse codes passed through a communication bottleneck in the brain can be recovered from random projections via (unsupervised) biologically plausible sparse dictionary learning (e.g., \cite{rehnsommer2007, rozell2007neurally, hu2014hebbian}).

### 2017-04-02 manuscripts/PNAS/chazthm_pnas.tex
m prime

--- 2017-04-01 manuscripts/PNAS/chazthm_pnas.tex
@@
 
-\begin{definition}\label{sip}
+\begin{definition}
 Given $E \subseteq 2^{[m]}$, the \textbf{star} $F(i)$ at $i$ are those $S \in E$ with $i \in S$.
@@
 \begin{theorem}\label{DeterministicUniquenessTheorem}
-Fix integers $n, \ell$, and $k < m$.
-Suppose $\mathbf{A}~\in~\mathbb{R}^{n \times m}$ satisfies the spark condition \eqref{SparkCondition} and that $k$-sparse \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} contain at least \mbox{$(k-1){m \choose k}+1$} vectors supported in general linear position on each set in some $\ell$-regular $E \subseteq {[m] \choose k}$ with the SIP.
-There exists a constant $C_1 > 0$ for which the following holds for all $\varepsilon < L_2(\mathbf{A}) / C_1$.
+%Fix integers $n, \ell$, and $k < m$. 
+Suppose $\mathbf{A}~\in~\mathbb{R}^{n \times m}$ satisfies the spark condition \eqref{SparkCondition} for some $k < m$ and that $k$-sparse \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} contain at least \mbox{$(k-1){m \choose k}+1$} vectors supported in general linear position on each set in some $\ell$-regular $E \subseteq {[m] \choose k}$ with the SIP.
+Then there exists a constant $C_1 > 0$ for which the following holds for all $\varepsilon < L_2(\mathbf{A}) / C_1$.
 
-Every matrix $\mathbf{B} \in \mathbb{R}^{n \times m}$ and $k$-sparse $\mathbf{\hat x}_1, \ldots, \mathbf{\hat x}_N \in \mathbb{R}^{m}$ with  \mbox{$\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\hat x}_i\|_2 \leq \varepsilon$} for all $i$ necessarily satisfies:
+Every matrix $\mathbf{B} \in \mathbb{R}^{n \times \hat m}$ and $k$-sparse $\mathbf{\hat x}_1, \ldots, \mathbf{\hat x}_N \in \mathbb{R}^{\hat m}$ with  \mbox{$\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\hat x}_i\|_2 \leq \varepsilon$} for all $i$ must have $\hat m \geq m$ and, provided $p = \hat m - \ell(\hat m - m)$ is positive, necessarily satisfy:
 \begin{align}\label{Cstable}
-\|\mathbf{A}_j - (\mathbf{B}\mathbf{PD})_j\|_2 \leq C_1 \varepsilon,\ \ \   \text{for all $j \in [m]$},
+\|(\mathbf{A}_J- \mathbf{B}_{\hat J} \mathbf{PD} )_j\|_2 \leq C_1 \varepsilon \ \  \text{for all $j \in [J]$},
 \end{align}
-for some permutation matrix $\mathbf{P}$ and invertible diagonal $\mathbf{D}$.
+for some $J \in {[m] \choose p}$, $\hat J \in {[\hat m] \choose p}$, permutation matrix $\mathbf{P}$ and invertible diagonal matrix $\mathbf{D}$.
 
-Furthermore, if $\varepsilon < L_{2k}(\mathbf{A}) / C_1$, then $\mathbf{B}$ also satisfies \eqref{SparkCondition} with $L_{2k}(\mathbf{B}\mathbf{PD}) \geq L_{2k}(\mathbf{A}) - C_1 \varepsilon$, and:
+[ ** TODO ** write $\hat m$ version ] Furthermore, if $\varepsilon < L_{2k}(\mathbf{A}) / C_1$, then $\mathbf{B}$ also satisfies \eqref{SparkCondition} with $L_{2k}(\mathbf{B}\mathbf{PD}) \geq L_{2k}(\mathbf{A}) - C_1 \varepsilon$, and:
 \begin{align}\label{b-PDa}
@@
 \end{theorem}
+
+%\begin{theorem}\label{DeterministicUniquenessTheorem}
+%Fix integers $n, \ell$, and $k < m$.
+Suppose $\mathbf{A}~\in~\mathbb{R}^{n \times m}$ satisfies the spark condition \eqref{SparkCondition} and that $k$-sparse \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} contain at least \mbox{$(k-1){m \choose k}+1$} vectors supported in general linear position on each set in some $\ell$-regular $E \subseteq {[m] \choose k}$ with the SIP.
+There exists a constant $C_1 > 0$ for which the following holds for all $\varepsilon < L_2(\mathbf{A}) / C_1$.
+
+%Every matrix $\mathbf{B} \in \mathbb{R}^{n \times m}$ and $k$-sparse $\mathbf{\hat x}_1, \ldots, \mathbf{\hat x}_N \in \mathbb{R}^{m}$ with  \mbox{$\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\hat x}_i\|_2 \leq \varepsilon$} for all $i$ necessarily satisfies:
+%\begin{align}\label{Cstable}
+%\|\mathbf{A}_j - (\mathbf{B}\mathbf{PD})_j\|_2 \leq C_1 \varepsilon,\ \ \   \text{for all $j \in [m]$},
+%\end{align}
+%for some permutation matrix $\mathbf{P}$ and invertible diagonal $\mathbf{D}$.
+
+%Furthermore, if $\varepsilon < L_{2k}(\mathbf{A}) / C_1$, then $\mathbf{B}$ also satisfies \eqref{SparkCondition} with $L_{2k}(\mathbf{B}\mathbf{PD}) \geq L_{2k}(\mathbf{A}) - C_1 \varepsilon$, and:
+%\begin{align}\label{b-PDa}
+%\|\mathbf{x}_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\hat x}_i\|_1 &\leq  \left( \frac{ 1+C_1 \|\mathbf{x}_i\|_1 }{ L_{2k}(\mathbf{A}) -  C_1\varepsilon } \right) \varepsilon,\ \ \   \text{for all $i \in [N]$}.
+%\end{align}
+%\end{theorem}
 
@@
 \begin{lemma}\label{MainLemma}
-Fix integers $n$ and $k < m$, and suppose $\mathbf{A} \in \mathbb{R}^{n \times m}$ satisfies the spark condition \eqref{SparkCondition}.
+%Fix integers $k, \ell, m, \hat m$ and $n$ with $k < m$. 
+Suppose $\mathbf{A} \in \mathbb{R}^{n \times m}$ satisfies the spark condition \eqref{SparkCondition} for some $k < m$ and that $E \subseteq {[m] \choose k}$ is $\ell$-regular and satisfies the SIP.
+Then there exists a constant $C_2 > 0$ for which the following holds for all $\varepsilon < L_2(\mathbf{A}) / C_2$.
+
+If for some  $\mathbf{B} \in \mathbb{R}^{n \times \hat m}$ and map $\pi: E \mapsto {[\hat m] \choose k}$ we have:
+\begin{align}\label{GapUpperBound}
+d(\text{\rm Span}\{\mathbf{A}_{S}\}, \text{\rm Span}\{\mathbf{B}_{\pi(S)}\}) \leq \varepsilon \ \   \text{for all $S \in E$},
+\end{align}
+%
+then $\hat m \geq m$ and, provided $p = \hat m - \ell(\hat m - m)$ is positive:
+\begin{align}\label{MainLemmaBPD}
+\|(\mathbf{A}_J - \mathbf{B}_{\hat J}\mathbf{PD})_j\|_2 \leq C_2 \varepsilon, \indent \text{for } j \in [J].
+\end{align}
+for some $J \in {[m] \choose p}$, $\hat J \in {[\hat m] \choose p}$, permutation matrix $\mathbf{P}$ and invertible diagonal matrix $\mathbf{D}$.
+\end{lemma}
+
+%\begin{lemma}\label{MainLemma}
+%Fix integers $n$ and $k < m$, and suppose $\mathbf{A} \in \mathbb{R}^{n \times m}$ satisfies the spark condition \eqref{SparkCondition}.
 There exists a constant $C_2 > 0$ for which the following holds for all $\varepsilon < L_2(\mathbf{A}) / C_2$.
 If for some  $\mathbf{B} \in \mathbb{R}^{n \times m}$ and regular $E \subseteq {[m] \choose k}$ with the SIP there exists a map $\pi: E \mapsto {[m] \choose k}$ satisfying:
-\begin{align}\label{GapUpperBound}
-d(\text{\rm Span}\{\mathbf{A}_{S}\}, \text{\rm Span}\{\mathbf{B}_{\pi(S)}\}) \leq \varepsilon,\ \ \   \text{for all $S \in E$},
-\end{align}
+%\begin{align}\label{GapUpperBound}
+%d(\text{\rm Span}\{\mathbf{A}_{S}\}, \text{\rm Span}\{\mathbf{B}_{\pi(S)}\}) \leq \varepsilon,\ \ \   \text{for all $S \in E$},
+%\end{align}
 %
-then there exists a permutation matrix $\mathbf{P}$ and invertible diagonal matrix $\mathbf{D}$ with:
-\begin{align}\label{MainLemmaBPD}
-\|\mathbf{A}_j - (\mathbf{BPD})_j\|_2 \leq C_2 \varepsilon, \ \ \  \text{for all } j \in [m].
-\end{align}
-\end{lemma}
+%then there exists a permutation matrix $\mathbf{P}$ and invertible diagonal matrix $\mathbf{D}$ with:
+%\begin{align}\label{MainLemmaBPD}
+%\|\mathbf{A}_j - (\mathbf{BPD})_j\|_2 \leq C_2 \varepsilon, \ \ \  \text{for all } j \in [m].
+%\end{align}
+%\end{lemma}
 
@@
 In this note, we generalize the approach of \cite{Hillar15} for showing uniqueness in Prob.~\ref{InverseProblem} to the case of noisy measurements while also reducing the sufficient number of samples.
+% from $N=k{m \choose k}^2$ to $N = m(k-1){m \choose k}+m$. 
+% CUT OK?
+Surprisingly, almost all $n \times m$ dictionaries satisfying the standard assumption \eqref{CScondition} from compressed sensing (CS) are identifiable from enough generic noisy $k$-sparse linear combinations of their elements, up to an error linear in the noise.
+Moreover, if solutions are constrained to satisfy \eqref{SparkCondition}, then only an upper bound on the number of dictionary elements need be taken as given.
+One interesting aspect of our contribution is a combinatorial criteria (regular hypergraphs satisfying the singular intersection property) for choosing support sets for original sparse codes; fully understanding those combinatorial designs allowing for stable representations of datasets is the subject of future work.
+We also remark that our main uniqueness result (Thm.~\ref{DeterministicUniquenessTheorem}) accounts for deterministic ``worst-case'' noise, whereas the ``effective'' noise might be much smaller when it is sampled from a given distribution; in such cases, the constants in our theorems %Thms.~\ref{DeterministicUniquenessTheorem},~\ref{DeterministicUniquenessTheorem2}
+will be different. %We note also that these results extend trivially to cases where point-wise injective nonlinearities are applied to the data. 
+We close with several application areas.
+
 % FRITZ: Inverse problems instead of Data Analysis.
@@
 Focus on them (probabilistic ones too).
-Our results provide theoretical grounding for the use of sparse linear coding in blind source separation, wherein the goal is to infer the generating dictionary and sparse codes from noisy measurements generated as in \eqref{LinearModel}.
-Such results are motivated by the seemingly universal representations discovered by training a sparse linear coding model with natural data, independently of specific algorithmic implementation.
-We also collect a set of useful mathematical tools and basic results for future research.
-% We close with several application areas.
+\textbf{Inverse Problems}.  
+Our results provide theoretical grounding for the use of sparse linear coding in blind source separation, wherein the goal is to infer the generating dictionary and sparse codes from noisy measurements generated as in \eqref{LinearModel} (e.g., recovering a rat's position on a linear track from local field potentials in Hippocampus \cite{Agarwal14}).
+It would be of practical utility therefore to determine the best possible dependence of $\varepsilon$ on $\delta_1, \delta_2$ (see \eqref{epsdel}) as well as the minimal requirements on the number and diversity of generating codes.
+%We encourage researchers to extend our results and tighten these parameters.
+Phrased in the language of Hadamard \cite{Hadamard1902}),  Mention sparse matrix factorization. [Effective computation of stable datasets, at least in principle.]
+[maybe smooth analysis something here]
+We hope that researchers in sparse linear coding continue to improve on the bounds and constants here.
 
-%\textbf{Inverse Problems}.  
-% from $N=k{m \choose k}^2$ to $N = m(k-1){m \choose k}+m$. 
-% CUT OK?
-Surprisingly, almost all $n \times m$ dictionaries satisfying the standard assumption \eqref{CScondition} from compressed sensing (CS) are identifiable from enough generic noisy $k$-sparse linear combinations of their elements, up to an error linear in the noise.
-Moreover, if solutions are constrained to satisfy \eqref{SparkCondition}, then only an upper bound on the number of dictionary elements need be taken as given.
-One interesting aspect of our contribution is a combinatorial criteria (regular hypergraphs satisfying the singular intersection property, Def.~\ref{sip}) for choosing support sets for original sparse codes.
-Fully understanding those combinatorial designs allowing for stable representations of datasets is an interesting research area for the future.
-We also remark that our main uniqueness result (Thm.~\ref{DeterministicUniquenessTheorem}) accounts for deterministic ``worst-case'' noise, whereas the ``effective'' noise might be much smaller when it is sampled from a given distribution; in such cases, the constants in our theorems %Thms.~\ref{DeterministicUniquenessTheorem},~\ref{DeterministicUniquenessTheorem2}
-should be better. %We note also that these results extend trivially to cases where point-wise injective nonlinearities are applied to the data.
-
-As an inverse problem to be approximated by a (typically) numerical algorithm, what we have shown here is that the sparse linear coding model  generally produces \textit{well-posed} optimizations.
-This early concept of Hadamard \cite{Hadamard1902}) can be paraphrased as the idea that algorithms inverting a parameterized model of data should have unique solutions that are continuous in the data.
-In other words, perturbing slightly a dataset should only slightly influence the uniqueness of parameters in the model, rather than discontinuously affect the character of optimization involved.
-In this regard, we provide explicit constants in terms of original latent parameters, although they are too expensive to compute for any practical utility.
-% We hope that researchers in sparse linear coding continue to improve on the bounds and constants here.
-
-One of the technical difficulties in our main theorem is the absence of a spark condition assumption on alternate dictionaries; in fact, several results here are much simpler to prove when such an assumption is made.
-However, in general, it cannot necessarily be assumed that a learned dictionary have satisfy the spark condition.
-In addition, guaranteeing that a dictionary has this property is probably intractable given its NP-hardness \cite{tillmann2014computational}.
-It would be of practical utility to determine the best possible dependence of $\varepsilon$ on $\delta_1, \delta_2$ (see \eqref{epsdel}) as well as the minimal requirements on the number and diversity of generating codes.
-%We encourage researchers to extend our results and tighten these parameters.
-
-%\textbf{Theoretical Neuroscience}.
-In the field of theoretical neuroscience, sparse dictionary learning and related methods have recovered characteristic components of natural images and sounds \cite{bellsejnowski1996, smithlewicki2006, Carlson12}, reproducing response properties of cortical neurons.
+\textbf{Theoretical Neuroscience}.
+Sparse dictionary learning and related methods have recovered characteristic components of natural images and sounds \cite{bellsejnowski1996, smithlewicki2006, Carlson12}, reproducing response properties of cortical neurons.
 Our theorems suggest that this correspondence could be due to the uniqueness of sparse representations.
 Furthermore, our guarantees justify the hypothesis of \cite{Coulter10, Isely10} that sparse codes passed through a communication bottleneck in the brain can be recovered from random projections via (unsupervised) biologically plausible sparse dictionary learning (e.g., \cite{rehnsommer2007, rozell2007neurally, hu2014hebbian}).
-In fact, the concept of ``universal'' objects in the brain is an early idea in neuroscience theory \cite{pitts1947}.
-But this is also in data science applications.
-For instance, when recovering a rat's position on a linear track from learning a sparse linear model on  local field potentials in Hippocampus \cite{Agarwal14}.
-
+Invariance: \cite{pitts1947}.
 %TODO: add reproduction of response propeties in olfactory cortex?
@@
 
-%\textbf{Engineering}.
-In engineering, several groups have utilized compressed sensing for signal processing tasks: MRI analysis \cite{lustig2008compressed},  image compression \cite{Duarte08}, and, more recently, the design of an ultrafast camera \cite{Gao14}.
+\textbf{Engineering}.
+Several groups utilize compressed sensing for signal processing tasks: MRI analysis \cite{lustig2008compressed},  image compression \cite{Duarte08}, and, more recently, the design of an ultrafast camera \cite{Gao14}.
 Given such effective uses of CS, it is only a matter of time before these systems incorporate sparse dictionary learning to encode and process data.

### 2017-04-02 manuscripts/PNAS/chazthm_pnas.tex

--- 2017-04-01 manuscripts/PNAS/chazthm_pnas.tex
@@
 \begin{theorem}\label{DeterministicUniquenessTheorem}
-Fix integers $n, \ell$, and $k < m$.
-Suppose $\mathbf{A}~\in~\mathbb{R}^{n \times m}$ satisfies the spark condition \eqref{SparkCondition} and that $k$-sparse \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} contain at least \mbox{$(k-1){m \choose k}+1$} vectors supported in general linear position on each set in some $\ell$-regular $E \subseteq {[m] \choose k}$ with the SIP.
-There exists a constant $C_1 > 0$ for which the following holds for all $\varepsilon < L_2(\mathbf{A}) / C_1$.
+%Fix integers $n, \ell$, and $k < m$. 
+Suppose $\mathbf{A}~\in~\mathbb{R}^{n \times m}$ satisfies the spark condition \eqref{SparkCondition} for some $k < m$ and that $k$-sparse \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} contain at least \mbox{$(k-1){m \choose k}+1$} vectors supported in general linear position on each set in some $\ell$-regular $E \subseteq {[m] \choose k}$ with the SIP.
+Then there exists a constant $C_1 > 0$ for which the following holds for all $\varepsilon < L_2(\mathbf{A}) / C_1$.
 
-Every matrix $\mathbf{B} \in \mathbb{R}^{n \times m}$ and $k$-sparse $\mathbf{\hat x}_1, \ldots, \mathbf{\hat x}_N \in \mathbb{R}^{m}$ with  \mbox{$\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\hat x}_i\|_2 \leq \varepsilon$} for all $i$ necessarily satisfies:
+Every matrix $\mathbf{B} \in \mathbb{R}^{n \times \hat m}$ and $k$-sparse $\mathbf{\hat x}_1, \ldots, \mathbf{\hat x}_N \in \mathbb{R}^{\hat m}$ with  \mbox{$\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\hat x}_i\|_2 \leq \varepsilon$} for all $i$ must have $\hat m \geq m$ and, provided $p = \hat m - \ell(\hat m - m)$ is positive, necessarily satisfy:
 \begin{align}\label{Cstable}
-\|\mathbf{A}_j - (\mathbf{B}\mathbf{PD})_j\|_2 \leq C_1 \varepsilon,\ \ \   \text{for  $j \in [m]$},
+\|(\mathbf{A}_J- \mathbf{B}_{\hat J} \mathbf{PD} )_j\|_2 \leq C_1 \varepsilon \ \  \text{for all $j \in [J]$},
 \end{align}
-for some permutation matrix $\mathbf{P}$ and invertible diagonal $\mathbf{D}$.
+for some $J \in {[m] \choose p}$, $\hat J \in {[\hat m] \choose p}$, permutation matrix $\mathbf{P}$ and invertible diagonal matrix $\mathbf{D}$.
 
-Furthermore, if $\varepsilon < L_{2k}(\mathbf{A}) / C_1$, then $\mathbf{B}$ also satisfies \eqref{SparkCondition} with $L_{2k}(\mathbf{B}\mathbf{PD}) \geq L_{2k}(\mathbf{A}) - C_1 \varepsilon$, and:
+[ ** TODO ** write $\hat m$ version ] Furthermore, if $\varepsilon < L_{2k}(\mathbf{A}) / C_1$, then $\mathbf{B}$ also satisfies \eqref{SparkCondition} with $L_{2k}(\mathbf{B}\mathbf{PD}) \geq L_{2k}(\mathbf{A}) - C_1 \varepsilon$, and:
 \begin{align}\label{b-PDa}
@@
 \begin{proof}
-[ ** TODO ** rewrite for $\hat m > m$. ]
 We first show that $\hat m \geq m$.
@@
 Hence $\hat m \geq m$.
+
+[ ** TODO ** rewrite for $\hat m > m$. ]
 Again, pigeonholing the elements of $T$ with respect to the set $[\hat m]$ of possible first indices, we see that for each $j$ there must be exactly $\ell$ elements of $T$ with $j$ as a first index; hence, $\pi(E)$ is $\ell$-regular.

### 2017-04-03 manuscripts/PNAS/chazthm_pnas.tex
update but still TODOs

@@
 
-Our main technical finding is that a sufficient diversity of measurements generated from any dictionary satisfying the spark condition 
+Our main technical finding is that a sufficient quantity of measurements generated from any dictionary satisfying the spark condition 
 has a stable sparse representation.
@@
 \begin{align}\label{Cstable}
-\|(\mathbf{A}_J- \mathbf{B}_{\hat J} \mathbf{PD} )_j\|_2 \leq C_1 \varepsilon \ \  \text{for all $j \in [J]$},
+\|(\mathbf{A}_J- \mathbf{B}_{\hat J} \mathbf{PD} )_j\|_2 \leq C_1 \varepsilon, \ \  \text{for all $j \in J$},
 \end{align}
-for some $J \in {[m] \choose p}$, $\hat J \in {[\hat m] \choose p}$, permutation matrix $\mathbf{P}$ and invertible diagonal matrix $\mathbf{D}$.
+for some $J \in {[m] \choose p}$, $\hat J \in {[\hat m] \choose p}$, permutation matrix $\mathbf{P}$, and invertible diagonal matrix $\mathbf{D}$.
 
@@
 \begin{corollary}
-Fix $n, \ell$, and $k < m$.
-Let $\mathbf{A}~\in~\mathbb{R}^{n \times m}$ satisfy the spark condition \eqref{SparkCondition} and $k$-sparse \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} have at least \mbox{$\left[ (k-1){ m \choose k} + 1 \right] + (k-1)^2{m \choose k-1}$} vectors supported in general linear position on each set in an $\ell$-regular $E \subseteq {[m] \choose k}$ with the SIP.
-Given any $\delta_1, \delta_2 \geq 0$ and $\varepsilon \leq \varepsilon(\delta_1, \delta_2)$,  % (\eqref{epsdel}).
-% $\varepsilon < L_2(\mathbf{A}) / C_1$.
-%There exists a constant $C_1 > 0$ for which the following holds for all $\varepsilon < L_2(\mathbf{A}) / C_1$.
-every solution $\mathbf{B}, \mathbf{\hat x}_i, \ldots, \mathbf{\hat x}_N$ to the $\ell_0$ optimization problem:
+Suppose $\mathbf{A}~\in~\mathbb{R}^{n \times m}$ satisfies the spark condition \eqref{SparkCondition} for some $k < m$ and that $k$-sparse $\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$ contain at least $\left[ (k-1){m \choose k} + 1 \right] + |E|k(k-1){m \choose k-1}$ vectors supported in general linear position on each set in some $\ell$-regular $E \subseteq {[m] \choose k}$ with the SIP.
+Then there exists a constant $C_1 > 0$ for which the following holds for all $\varepsilon < L_2(\mathbf{A}) / C_1$.
+
+Every matrix $\mathbf{B} \in \mathbb{R}^{n \times \hat m}$ and set of vectors $\mathbf{\hat x}_1, \ldots, \mathbf{\hat x}_N \in \mathbb{R}^{\hat m}$ that solve:
 \begin{align}\label{minsum}
-\arg \min \sum_{i = 1}^N \|\mathbf{\hat x}_i\|_0 \ \ \text{s.t.} \ \ \mathbf{B}\mathbf{\hat x}_i = \mathbf{A}\mathbf{x}_i, \ \ \text{$i \in [N]$}, %\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\hat x}_i\|_2 \leq \varepsilon, \ \ \text{$i \in [N]$},
+\min \sum_{i = 1}^N \|\mathbf{\hat x}_i\|_0 \ \ 
+\text{subject to} \ \ \|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\hat x}_i\|_2 \leq \varepsilon, \ \ \text{for all $i$},
 \end{align}
-necessarily satisfies the recovery inequalities in \eqref{def1}. % \eqref{Cstable} and \eqref{b-PDa}.
+%
+must have $\hat m \geq m$ and, provided $p = \hat m - \ell(\hat m - m)$ is positive, necessarily satisfy:
+\begin{align}\label{Cstable}
+\|(\mathbf{A}_J- \mathbf{B}_{\hat J} \mathbf{PD} )_j\|_2 \leq C_1 \varepsilon \ \  \text{for all $j \in J$},
+\end{align}
+for some $J \in {[m] \choose p}$, $\hat J \in {[\hat m] \choose p}$, permutation matrix $\mathbf{P}$, and invertible diagonal matrix $\mathbf{D}$.
 \end{corollary}
@@
 We derive a lower bound on the number of $k$-sparse $\mathbf{\hat x}_i$ and then apply Thm.~\ref{DeterministicUniquenessCorollary}. 
-First, note that $\|\mathbf{\hat x}_i\|_0 \neq 0$ for all $i$, since otherwise we would have $\mathbf{A}\mathbf{x}_i = \mathbf{B}\mathbf{\hat x}_i = \mathbf{0} \implies \mathbf{x}_i = \mathbf{0}$ by the spark condition, contradicting the general linear position of the $\mathbf{x}_i$.
+Let $n_p$ be the number of $\mathbf{\hat x}_i$ with $\|\mathbf{\hat x}_i\|_0 = p$.  %, so that $\sum_{p = 1}^{m} n_p = N$. 
+Since the $\mathbf{x}_i$ are all $k$-sparse, by \eqref{minsum} we have:
+\begin{align}
+k \sum_{p = 0}^{m} n_p = kN \geq \sum_{i=0}^N \|\mathbf{x}_i\|_0 \geq \sum_{i=0}^N \|\mathbf{\hat x}_i\|_0 = \sum_{p=0}^{m} p n_p.
+\end{align}
+Hence,
+\begin{align}\label{eqn}
+\sum_{p = k+1}^m n_p \leq \sum_{p = k+1}^m (p-k) n_p \leq \sum_{p = 0}^k (k-p)n_p \leq k \sum_{p = 0}^{k-1} n_p.
+\end{align}
+
+Let $\mathbf{X}$ and $\mathbf{\hat{X}}$ be the $m \times N$ matrices with columns $\mathbf{x}_i$ and $\mathbf{\hat x}_i$, respectively, and let $I(S) = \{i \in [N]: \text{supp}(\mathbf{x}_i) \subseteq S\}$.
+It follows from the general linear position of the $\mathbf{x}_i$ and the linear independence of every $k$ columns of $\mathbf{A}$ that $L_k(\mathbf{AX}_{I(S)}) > 0$ for all $S \in E$; that is, for every $S \in E$, the columns of every $n \times k$ submatrix of $\mathbf{AX}_{I(S)}$ form a basis for $\text{\rm Span}\{\mathbf{A}_S\}$.
+Suppose there are $(k-1)|E| + 1$ vectors $\mathbf{x}_i$ for which the corresponding $\mathbf{\hat x}_i$ $(i \in J)$ share a support $\hat S$.
+By the pigeonhole principle, there must be some $S \in E$ supporting $k$ or more of these vectors $\mathbf{x}_i$; let them be indexed by $J \subseteq I(S)$.
+Fixing $\mathbf{y} \in \text{\rm Span}\{ \mathbf{A}_S \}$, there exists a unique $\mathbf{c} = (c_1, \ldots, c_k) \in \mathbb{R}^k$ such that $\mathbf{y} = \mathbf{AX}_{J}\mathbf{c}$.
+Setting \mbox{$\mathbf{\hat{y}} = \mathbf{B\hat{X}}_{J}\mathbf{c} \in \text{\rm Span}\{\mathbf{B}_{\hat S}\}$}, we have:
+\begin{align*}
+\|\mathbf{y} - \mathbf{\hat{y}}\|_2 
+&= \|\sum_{i=1}^k c_i(\mathbf{AX}_J - \mathbf{B\hat{X}}_J)_i\|_2
+\leq \varepsilon \sum_{i=1}^k |c_i| \\
+&\leq \varepsilon \sqrt{k}  \|\mathbf{c}\|_2 
+\leq \frac{\varepsilon}{L_k(\mathbf{AX}_J)} \|\mathbf{y}\|_2,
+\end{align*}
+where the last inequality is by definition of $L_k$. From Def.~\ref{dDef}, it follows that:
+\begin{align}\label{rhs222}
+d(\text{\rm Span}\{\mathbf{A}_S\}, \text{\rm Span}\{\mathbf{B}_{\hat S}\}) 
+\leq \frac{\varepsilon}{ \min_{S \in E}L_k(\mathbf{AX}_{I(S)}) }.
+\end{align}
+
+Since (by our upper bound on $\varepsilon$) the RHS is strictly less than one, we have by \eqref{dimlem} that $k = \dim(\text{Span}(\mathbf{AX}_J)) \leq \dim(\text{Span}\{\mathbf{B}_{\hat S}\}) \leq |\hat S|$.
+Hence, if $|E|(k-1) + 1$ or more vectors $\mathbf{\hat x}_i$ share the same support, they cannot be $(k-1)$-sparse and the number of $(k-1)$-sparse vectors $\mathbf{\hat x}_i$ must then be bounded from above by $|E|(k-1){ m \choose k-1}$.
+Taking \eqref{eqn} into account, it follows that at least $N - |E|k(k-1){ m \choose k-1}$ of the vectors $\mathbf{\hat  x}_i$ are $k$-sparse, and there must then be some $N' \subseteq [N]$ for which for each $S \in E$ there are $(k-1){m \choose k}+1$ of the vectors $\mathbf{x}_i$ with $i \in [N']$ supported on $S$ and for which $\mathbf{\hat x}_i$ is $k$-sparse for all $i \in [N']$.
+The result now follows directly from Thm.~\ref{DeterministicUniquenessCorollary}.
+\end{proof}
+
+%\begin{corollary}
+%Fix $n, \ell$, and $k < m$.
+Let $\mathbf{A}~\in~\mathbb{R}^{n \times m}$ satisfy the spark condition \eqref{SparkCondition} and $k$-sparse \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} have at least \mbox{$\left[ (k-1){ m \choose k} + 1 \right] + (k-1)^2{m \choose k-1}$} vectors supported in general linear position on each set in an $\ell$-regular $E \subseteq {[m] \choose k}$ with the SIP.
+Given any $\delta_1, \delta_2 \geq 0$ and $\varepsilon \leq \varepsilon(\delta_1, \delta_2)$,
+%every solution $\mathbf{B}, \mathbf{\hat x}_i, \ldots, \mathbf{\hat x}_N$ to the $\ell_0$ optimization problem:
+%\begin{align}\label{minsum}
+%\arg \min \sum_{i = 1}^N \|\mathbf{\hat x}_i\|_0 \ \ \text{s.t.} \ \ \mathbf{B}\mathbf{\hat x}_i = \mathbf{A}\mathbf{x}_i, \ \ \text{$i \in [N]$}, %\|\mathbf{A}\end{align}
+%necessarily satisfies the recovery inequalities in \eqref{def1}. % \eqref{Cstable} and \eqref{b-PDa}.
+%\end{corollary}
+%
+%\begin{proof}
+%We derive a lower bound on the number of $k$-sparse $\mathbf{\hat x}_i$ and then apply Thm.~\ref{DeterministicUniquenessCorollary}. 
+%First, note that $\|\mathbf{\hat x}_i\|_0 \neq 0$ for all $i$, since otherwise we would have $\mathbf{A}\mathbf{x}_i = \mathbf{B}\mathbf{\hat x}_i = \mathbf{0} \implies \mathbf{x}_i = \mathbf{0}$ by the spark condition, contradicting the general linear position of the $\mathbf{x}_i$.
 Let $n_p$ be the number of $\mathbf{\hat x}_i$ with $\|\mathbf{\hat x}_i\|_0 = p$.
 %, so that $\sum_{p = 1}^{m} n_p = N$.
-Since the $\mathbf{x}_i$ are all $k$-sparse, by \eqref{minsum} we have:
-\begin{align}
-k \sum_{p = 1}^{m} n_p = kN \geq \sum_{i=1}^N \|\mathbf{x}_i\|_0 \geq \sum_{i=1}^N \|\mathbf{\hat x}_i\|_0 = \sum_{p=1}^{m} p n_p.
-\end{align}
-%\[\implies \sum_{p = 1}^k (k-p)n_p \geq \sum_{p = k+1}^{m} (p-k) n_p.\]
-Hence,
-\begin{align}
-\sum_{p = k+1}^m n_p \leq \sum_{p = k+1}^m (p-k) n_p \leq \sum_{p = 1}^k (k-p)n_p \leq (k-1) \sum_{p = 1}^{k-1} n_p.
-\end{align}
-%\[ \implies \sum_{p = k+1}^m n_p \leq (k-1)^2 {\hat m \choose k-1} \]
-
-By the spark condition and general linear position of the $\mathbf{x}_i$, every $k$ vectors $\mathbf{Ax}_i$ span a $k$-dimensional space; hence, at most $k-1$ vectors $\mathbf{\hat x}_i$ can share a support of size $k-1$ or less, and the number of $(k-1)$-sparse vectors $\mathbf{\hat x}_i$ is then bounded from above by $(k-1) { m \choose k-1}$.
+%Since the $\mathbf{x}_i$ are all $k$-sparse, by \eqref{minsum} we have:
+%\begin{align}
+%k \sum_{p = 1}^{m} n_p = kN \geq \sum_{i=1}^N \|\mathbf{x}_i\|_0 \geq \sum_{i=1}^N \|\mathbf{\hat x}_i\|_0 = \sum_{p=1}^{m} p n_p.
+%\end{align}
+%%\[\implies \sum_{p = 1}^k (k-p)n_p \geq \sum_{p = k+1}^{m} (p-k) n_p.\]
+%Hence,
+%\begin{align}
+%\sum_{p = k+1}^m n_p \leq \sum_{p = k+1}^m (p-k) n_p \leq \sum_{p = 1}^k (k-p)n_p \leq (k-1) \sum_{p = 1}^{k-1} n_p.
+%\end{align}
+%%\[ \implies \sum_{p = k+1}^m n_p \leq (k-1)^2 {\hat m \choose k-1} \]
+%
+%By the spark condition and general linear position of the $\mathbf{x}_i$, every $k$ vectors $\mathbf{Ax}_i$ span a $k$-dimensional space; hence, at most $k-1$ vectors $\mathbf{\hat x}_i$ can share a support of size $k-1$ or less, and the number of $(k-1)$-sparse vectors $\mathbf{\hat x}_i$ is then bounded from above by $(k-1) { m \choose k-1}$.
 It follows that at least $N - (k-1)^2 {m \choose k-1}$ of the vectors $\mathbf{\hat  x}_i$ are $k$-sparse, and that there must then be some $N' \subseteq [N]$ for which for each $S \in E$ there are $(k-1){m \choose k}+1$ of the vectors $\mathbf{x}_i$ with $i \in [N']$ supported on $S$ and for which $\mathbf{\hat x}_i$ is $k$-sparse for all $i \in [N']$.
@@
 % \eqref{Cstable} and \eqref{b-PDa} follow.
-\end{proof}
+%\end{proof}
 
@@
 Hence, the map $\pi$ is injective.
-Setting $J = \pi([m])$ and letting $P = \left( \mathbf{e}_{\pi(1)} \cdots \mathbf{e}_{\pi(m)}\right)$ and $D = \text{diag}(\frac{\hat{c}_1}{c_1},\ldots,\frac{\hat{c}_m}{c_m})$, we see that \eqref{1D} becomes, for all $j \in [m]$:
+Setting $J = [m]$, $\hat J = \pi([m])$, and letting $P = \left( \mathbf{e}_{\pi(1)} \cdots \mathbf{e}_{\pi(m)}\right)$ and $D = \text{diag}(\frac{\hat{c}_1}{c_1},\ldots,\frac{\hat{c}_m}{c_m})$, we see that \eqref{1D} becomes, for all $j \in [m]$:
 \begin{align*}%\label{k=1result}
@@
 \begin{align}\label{GapUpperBound}
-d(\text{\rm Span}\{\mathbf{A}_{S}\}, \text{\rm Span}\{\mathbf{B}_{\pi(S)}\}) \leq \varepsilon \ \   \text{for all $S \in E$},
+d(\text{\rm Span}\{\mathbf{A}_{S}\}, \text{\rm Span}\{\mathbf{B}_{\pi(S)}\}) \leq \varepsilon, \ \   \text{for all $S \in E$},
 \end{align}
@@
 \begin{align}\label{MainLemmaBPD}
-\|(\mathbf{A}_J - \mathbf{B}_{\hat J}\mathbf{PD})_j\|_2 \leq C_2 \varepsilon, \indent \text{for } j \in [J].
+\|(\mathbf{A}_J - \mathbf{B}_{\hat J}\mathbf{PD})_j\|_2 \leq C_2 \varepsilon, \indent \text{for } j \in J.
 \end{align}
-for some $J \in {[m] \choose p}$, $\hat J \in {[\hat m] \choose p}$, permutation matrix $\mathbf{P}$ and invertible diagonal matrix $\mathbf{D}$.
+for some $J \in {[m] \choose p}$, $\hat J \in {[\hat m] \choose p}$, permutation matrix $\mathbf{P}$, and invertible diagonal matrix $\mathbf{D}$.
 \end{lemma}
@@
 What we have shown here is that as an inverse problem to be approximated by a numerical algorithm, the sparse linear coding model  generally produces \textit{well-posed} optimizations.
-This early concept of Hadamard \cite{Hadamard1902} can be paraphrased as the idea that good parameterized models should pose optimization problems with solutions that are stable; that is, continuous in the data.
+This early concept of Hadamard \cite{Hadamard1902} can be paraphrased as the idea that good parameterized models should pose optimization problems with solutions that are \textit{stable}; that is, continuous in the data.
 In other words, perturbing a dataset by a small amount should only slightly influence the identifiability or uniqueness of parameters in the model, rather than discontinuously affect the character of optimization involved.
-In this regard, we demonstrate a linear relationship between noise in the data and the unique solution in  sparse linear coding, with explicit constants expressed in terms of original latent parameters.
+In this regard, we demonstrate a linear relationship, \eqref{epsdel}, between noise in the data and the unique solution in  sparse linear coding, with explicit constants expressed in terms of original latent parameters.
 Nonetheless, it would be of practical utility to determine the best possible dependence of $\varepsilon$ on $\delta_1, \delta_2$ in Def.\ref{maindef} as well as the minimal requirements on the number and diversity of generating codes, and we hope that other researchers continue to improve and extend our results.
@@
 For instance, it is difficult to ensure an algorithm maintain a dictionary satisfying \eqref{SparkCondition} at each learning stage; indeed, even certifying  a dictionary has this property is likely intractable given its NP-hardness \cite{tillmann2014computational}.
+[*** TODO:  Mention relationship of $N$ being a polynomial in $(m,k)$ as giving an NP-hardness result using this Tillmann one ***]
 
@@
 Given such effective uses of CS, it is only a matter of time before these systems incorporate sparse representational learning to encode and process data (e.g., in a device that learns structure from motion \cite{kong2016prior}).
-In these cases, assurances such as those offered by our theorems ensure that different devices (with different initialization, samples, etc.) are equivalent as soon as enough data originate from a statistically identical system.
+In these cases, assurances such as those offered by our theorems certify that different devices (with different initialization, samples, etc.) are equivalent as soon as enough data originate from a statistically identical system.
 %Data science:
@@
 Our results suggest that this correspondence could be due to  sparse representations being ``universal'' in natural data, an early mathematical idea in neural theory \cite{pitts1947}.
-Furthermore, our guarantees justify the hypothesis of \cite{Coulter10, Isely10} that sparse codes passed through a communication bottleneck in the brain can be recovered from random projections via (unsupervised) biologically plausible sparse dictionary learning (e.g., \cite{rehnsommer2007, rozell2007neurally, hu2014hebbian}).
+Furthermore, our guarantees justify the hypothesis of \cite{Coulter10, Isely10} that sparse codes passed through a communication bottleneck in the brain are recovered from random projections via (unsupervised) biologically plausible sparse dictionary learning (e.g., \cite{rehnsommer2007, rozell2007neurally, hu2014hebbian}).
 
@@
 %
-then $\hat m \geq m$ and the association $i \mapsto \cap \pi(F(i))$ defines an injective map from $[J]$ to $[\hat m]$ for some $J \subseteq [m]$ of size $\hat m - \ell(\hat m - m)$.
+then $\hat m \geq m$ and the association $i \mapsto \cap \pi(F(i))$ defines an injective map from $J$ to $[\hat m]$ for some $J \subseteq [m]$ of size $\hat m - \ell(\hat m - m)$.
 In particular, if $\hat m = m$ then the map $\pi$ is induced by a permutation.

### 2017-04-04 manuscripts/PNAS/chazthm_pnas.tex
SR up to mid pg 4

@@
 
-% Please add here a significance statement to explain the relevance of your work
-%\significancestatement{Authors must submit a 120-word maximum statement about the significance of their research paper written at a level understandable to an undergraduate educated scientist outside their field of speciality.
-The primary goal of the Significance Statement is to explain the relevance of the work in broad context to a broad readership.
-The Significance Statement appears in the paper itself and is required for all research papers.}
-
 \significancestatement{Many naturally occurring signals (visual scenery, speech, electrocardiograms, etc.) can be characterized as parsimonious combinations of elementary waveforms drawn from a large dictionary.
@@
 
-% Please include corresponding author, author contribution and author declaration information
 \authordeclaration{The authors declare no conflict of interest.}
-%\equalauthors{\textsuperscript{1}C.G. proved Theorem 1 and C.H. proved Theorem 2.}
 \correspondingauthor{\textsuperscript{1}To whom correspondence should be addressed. E-mail: cjg@berkeley.edu, chillar@msri.org}
 
-% Keywords are not mandatory, but authors are strongly encouraged to provide them. If provided, please include two to five keywords, separated by the pipe symbol, e.g:
 \keywords{Sparse linear coding, dictionary learning, uniqueness, compressed sensing}
@@
 
-% It has remained unknown, however, when the dictionary learning problem is well-posed (as per Hadamard \cite{Hadamard1902}) in general -- that is, independent of all methodological idiosyncracies.
-%[**TODO** make sure the claim here is right...or would it be punchier to talk about the fact that everyone always gets Gabors on natural images?]
-%- algos with proven recovery of generating dictionary
-%- analyses of when target dictionary is local optimizer of natural recovery criteria
-%- efficient algos that globally solve DR; detailed models differ but all assume each col has bounded sparsity and nonzero coefs have sub-Gaussian magnitudes
-
 More formally, let $\mathbf{A} \in \mathbb R^{n \times m}$ be a matrix with columns $\mathbf{A}_j$ ($j = 1,\ldots,m$) and let dataset $Z$ consist of measurements:
@@
 The precise mathematical problem addressed here is the following.
-% We address the uniqueness properties for the following linear coding question in signal processing.
 
 \begin{problem}[Sparse linear coding]\label{InverseProblem}
-Find a matrix $\mathbf{B}$ and $k$-sparse $\mathbf{\hat x}_1, \ldots, \mathbf{\hat x}_N \in \mathbb{R}^m$ such that $\|\mathbf{z}_i - \mathbf{B}\mathbf{\hat x}_i\|_2 \leq \eta$ for all $i$.
+Find a matrix $\mathbf{B}$ and $k$-sparse $\mathbf{\bar x}_1, \ldots, \mathbf{\bar x}_N \in \mathbb{R}^m$ such that $\|\mathbf{z}_i - \mathbf{B}\mathbf{\bar x}_i\|_2 \leq \eta$ for all $i$.
 \end{problem}
 
-Note that any particular solution $(\mathbf{B}, \mathbf{\hat x}_1 \ldots, \mathbf{\hat x}_N)$ to this problem gives rise to an orbit of other solutions $(\mathbf{BPD}, \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\hat x}_1, \ldots, \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\hat x}_N)$, where $\mathbf{P}$ is any permutation matrix and $\mathbf{D}$ any invertible diagonal.
+Note that any particular solution $(\mathbf{B}, \mathbf{\bar x}_1 \ldots, \mathbf{\bar x}_N)$ to this problem gives rise to an orbit of other solutions $(\mathbf{BPD}, \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\bar x}_1, \ldots, \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\bar x}_N)$, where $\mathbf{P}$ is any permutation matrix and $\mathbf{D}$ any invertible diagonal.
 We therefore consider whether solutions to Prob.~\ref{InverseProblem} are unique only up to this ambiguity.  More specifically, 
@@
 
-% More specifically,  we seek sufficient conditions on when sparsely coded datasets have a stable unique representation.
-
-% We therefore consider only whether solutions to Problem~\ref{InverseProblem} are unique up to this equivalence \cite{Li15}
-
-% Note that by formulating the problem in this way we have introduced the following ambiguity.
-Any particular solution represents .
-Alternatively, one may seek a unique solution (in the usual sense) in the quotient space induced by the action of the transformation group of matrices $PD$.
-
-%  noiseless case $\eta = 0$
-
-%  We introduce the following terminology to handle $\eta > 0$. 
 \begin{definition}\label{maindef}
@@
 %Equivalently, $\mathbf{Y} = \mathbf{A}\mathbf{X}$ for $\mathbf{Y}$ and $\mathbf{X}$ having the $\mathbf{y}_i$ and $\mathbf{x}_i$ as their columns, respectively.
-This representation is \textbf{stable} if for every $\delta_1, \delta_2 \geq 0$, there exists $\varepsilon(\delta_1, \delta_2) \geq 0$ (with $\varepsilon > 0$ when  $\delta_1, \delta_2 > 0$) such that if $\mathbf{B}$ and $k$-sparse $\mathbf{\hat x}_1, \ldots, \mathbf{\hat x}_N \in \mathbb{R}^m$ satisfy:
+This representation is \textbf{stable} if for every $\delta_1, \delta_2 \geq 0$, there exists $\varepsilon(\delta_1, \delta_2) \geq 0$ (with $\varepsilon > 0$ when  $\delta_1, \delta_2 > 0$) such that if $\mathbf{B}$ and $k$-sparse $\mathbf{\bar x}_1, \ldots, \mathbf{\bar x}_N \in \mathbb{R}^m$ satisfy:
 \begin{align*}
-\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\hat x}_i\|_2 \leq \varepsilon,\ \ \   \text{for all $i$},
+\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\bar x}_i\|_2 \leq \varepsilon,\ \ \   \text{for all $i$},
 \end{align*}
@@
 \begin{align}\label{def1}
-\|\mathbf{A}_j - (\mathbf{BPD})_j\|_2 \leq \delta_1 \ \ \text{and} \ \ \|\mathbf{x}_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\hat x}_i\|_1 \leq \delta_2.
+\|\mathbf{A}_j - (\mathbf{BPD})_j\|_2 \leq \delta_1 \ \ \text{and} \ \ \|\mathbf{x}_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\bar x}_i\|_1 \leq \delta_2.
 \end{align}
 \end{definition}
-% Kato mentions a distance between n-tuples that minimizes the maximum difference over all possible orderings of one of the n-tuples.
-% Make just 'sparse representation in m-dimensions? (i.e. with k unspecified?)
 
@@
 Consider now any dataset $Z$ generated as in \eqref{LinearModel} with $\eta \leq \frac{1}{2} \varepsilon(\delta_1, \delta_2)$.
-Then from the triangle inequality, it follows that any matrix $\mathbf{B}$ and $k$-sparse $\mathbf{\hat x}_1, \ldots, \mathbf{\hat x}_N$ solving Prob.~\ref{InverseProblem} are necessarily close to the original dictionary $\mathbf{A}$ and codes $\mathbf{x}_i$.
-
-%Our results, outlined in Sec.~\ref{Results}, include an explicit form for $\varepsilon(\delta_1, \delta_2)$ in Thm.~\ref{DeterministicUniquenessTheorem}.
-
-% We ask here: \emph{When does $Y$ have a stable $k$-sparse representation?}
+Then from the triangle inequality, it follows that any matrix $\mathbf{B}$ and $k$-sparse $\mathbf{\bar x}_1, \ldots, \mathbf{\bar x}_N$ solving Prob.~\ref{InverseProblem} are necessarily close to the original dictionary $\mathbf{A}$ and sparse codes $\mathbf{x}_i$.
 
@@
 The explicit, algorithm-independent criteria we provide should be a useful tool in the theory of sparse dictionary learning.
-% (Thm.~\ref{DeterministicUniquenessTheorem2})
 
@@
 All other proofs are relegated to the Supplemental.
-%Our approach is a refinement of the one found in \cite{Hillar15} to handle noise and to reduce the sufficient number of samples.
-%for all $k < m$ from $N=k{m \choose k}^2$ to $N = m + m(k-1){m \choose k}$. 
 Finally, we present several applications in Discussion Sec.~\ref{Discussion}.
@@
 
-In preparation for stating our main results, we first identify the combinatorial criteria on support sets of generating codes allowing for stable sparse 
+Before stating main results, we first identify the combinatorial criteria on support sets of generating codes allowing for stable sparse 
 representations.  Let $\{1, \ldots, m\}$ be denoted $[m]$, its power set $2^{[m]}$, and ${[m] \choose k}$ the set of subsets of $[m]$ of size $k$. 
 % Let $\text{\rm Span}\{\mathbf{v}_1, \ldots, \mathbf{v}_\ell\}$ be the $\mathbb{R}$-linear span of vectors $\mathbf{v}_1, \ldots, \mathbf{v}_\ell$. 
-A vector $\mathbf{x}$ is said to be \emph{supported} on $S \subseteq [m]$ %, written supp$(\mathbf{x}) = S$, 
-when $\mathbf{x} \in \text{\rm Span} \{\mathbf{e}_j\}_{j\in S}$, where $\mathbf{e}_j$ are the standard basis in $\mathbb R^m$.
+A vector $\mathbf{x}$ is said to be \emph{supported} on $S \subseteq [m]$ %,
+when $\mathbf{x} \in \text{\rm Span} \{\mathbf{e}_j\}_{j\in S}$, where $\mathbf{e}_j$ are the standard basis in $\mathbb R^m$.  We also write
+ supp$(\mathbf{x}) = S$ when $S$ indexes the nonzero components of $\mathbf{x}$.
 Let $\mathbf{M}_j$ be the $j$th column of a matrix $\mathbf{M}$ and similarly let $\mathbf{M}_S$ be the submatrix formed by the columns of $\mathbf{M}$ indexed by $S$ (we set $\text{\rm Span}\{\mathbf{M}_\emptyset\} := \{\textbf{0}\}$).
@@
 By compactness of the unit sphere, every injective linear map has a nonzero lower bound; hence, if $\mathbf{A}$ satisfies \eqref{SparkCondition}, then each submatrix formed from $2k$ of its columns or less has a nonzero lower bound.
-We therefore define the following domain-restricted lower bound:
+This motivates the following definition: % We therefore define the following domain-restricted lower bound:
 \begin{align*}
@@
 
-We also say that a set of $k$-sparse vectors is in \emph{general linear position} when any $k$ of them are linearly independent.
+We say that a set of $k$-sparse vectors is in \emph{general linear position} when any $k$ of them are linearly independent.
 The following is the precise statement of our main result.
@@
 %Fix integers $n, \ell$, and $k < m$. 
-Suppose $\mathbf{A}~\in~\mathbb{R}^{n \times m}$ satisfies the spark condition \eqref{SparkCondition} for some $k < m$ and that $k$-sparse \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} contain at least \mbox{$(k-1){m \choose k}+1$} vectors supported in general linear position on each set in some $\ell$-regular $E \subseteq {[m] \choose k}$ with the SIP.
-Then there exists a constant $C_1 > 0$ for which the following holds for all $\varepsilon < L_2(\mathbf{A}) / C_1$.
+Let $\mathbf{A}~\in~\mathbb{R}^{n \times m}$ satisfy \eqref{SparkCondition} for $k < m$, and suppose for some $\bar m$ more than \mbox{$(k-1){\bar m \choose k}$} $k$-sparse \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} are supported in general linear position on each set in an $\ell$-regular $E \subseteq {[m] \choose k}$ with the SIP.
+There is a constant $C_1 > 0$ for which the following hold for $\varepsilon < L_2(\mathbf{A}) / C_1$.
 
-Every matrix $\mathbf{B} \in \mathbb{R}^{n \times \hat m}$ and $k$-sparse $\mathbf{\hat x}_1, \ldots, \mathbf{\hat x}_N \in \mathbb{R}^{\hat m}$ with  \mbox{$\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\hat x}_i\|_2 \leq \varepsilon$} for all $i$ must have $\hat m \geq m$ and, provided $p = \hat m - \ell(\hat m - m)$ is positive, necessarily satisfy:
+1.) Every matrix $\mathbf{B} \in \mathbb{R}^{n \times \bar m}$ and $k$-sparse $\mathbf{\bar x}_1, \ldots, \mathbf{\bar x}_N \in \mathbb{R}^{\bar m}$ with  \mbox{$\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\bar x}_i\|_2 \leq \varepsilon$} for all $i$ must have $\bar m \geq m$ and, provided $p = \bar m - \ell(\bar m - m)$ is positive, necessarily satisfy:
 \begin{align}\label{Cstable}
-\|(\mathbf{A}_J- \mathbf{B}_{\hat J} \mathbf{PD} )_j\|_2 \leq C_1 \varepsilon, \ \  \text{for all $j \in J$},
+\|(\mathbf{A}_J- \mathbf{B}_{\bar J} \mathbf{PD} )_j\|_2 \leq C_1 \varepsilon, \ \  \text{for $j \in J$},
 \end{align}
-for some $J \in {[m] \choose p}$, $\hat J \in {[\hat m] \choose p}$, permutation matrix $\mathbf{P}$, and invertible diagonal matrix $\mathbf{D}$.
+for some $J \in {[m] \choose p}$, $\bar J \in {[\bar m] \choose p}$, permutation matrix $\mathbf{P}$, and invertible diagonal matrix $\mathbf{D}$.
 
-[ ** TODO ** write $\hat m$ version ] Furthermore, if $\varepsilon < L_{2k}(\mathbf{A}) / C_1$, then $\mathbf{B}$ also satisfies \eqref{SparkCondition} with $L_{2k}(\mathbf{B}\mathbf{PD}) \geq L_{2k}(\mathbf{A}) - C_1 \varepsilon$, and:
+2.) Restricting dictionaries and sparse codes to respective $J, \bar{J}$, we furthermore have that if $\varepsilon < L_{2k}(\mathbf{A}) / C_1$, then $\mathbf{B}$ also satisfies \eqref{SparkCondition} with $L_{2k}(\mathbf{B}\mathbf{PD}) \geq L_{2k}(\mathbf{A}) - C_1 \varepsilon$, and:
 \begin{align}\label{b-PDa}
-\|\mathbf{x}_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\hat x}_i\|_1 &\leq  \left( \frac{ 1+C_1 \|\mathbf{x}_i\|_1 }{ L_{2k}(\mathbf{A}) -  C_1\varepsilon } \right) \varepsilon,\ \ \   \text{for $i \in [N]$}.
+\|\mathbf{x}_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\bar x}_i\|_1 &\leq  \left( \frac{ 1+C_1 \|\mathbf{x}_i\|_1 }{ L_{2k}(\mathbf{A}) -  C_1\varepsilon } \right) \varepsilon,\ \ \   \text{for $i \in [N]$}.
 \end{align}
@@
 
-%Every matrix $\mathbf{B} \in \mathbb{R}^{n \times m}$ and $k$-sparse $\mathbf{\hat x}_1, \ldots, \mathbf{\hat x}_N \in \mathbb{R}^{m}$ with  \mbox{$\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\hat x}_i\|_2 \leq \varepsilon$} for all $i$ necessarily satisfies:
+%Every matrix $\mathbf{B} \in \mathbb{R}^{n \times m}$ and $k$-sparse $\mathbf{\bar x}_1, \ldots, \mathbf{\bar x}_N \in \mathbb{R}^{m}$ with  \mbox{$\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\bar x}_i\|_2 \leq \varepsilon$} for all $i$ necessarily satisfies:
 %\begin{align}\label{Cstable}
@@
 %\begin{align}\label{b-PDa}
-%\|\mathbf{x}_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\hat x}_i\|_1 &\leq  \left( \frac{ 1+C_1 \|\mathbf{x}_i\|_1 }{ L_{2k}(\mathbf{A}) -  C_1\varepsilon } \right) \varepsilon,\ \ \   \text{for all $i \in [N]$}.
+%\|\mathbf{x}_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\bar x}_i\|_1 &\leq  \left( \frac{ 1+C_1 \|\mathbf{x}_i\|_1 }{ L_{2k}(\mathbf{A}) -  C_1\varepsilon } \right) \varepsilon,\ \ \   \text{for all $i \in [N]$}.
 %\end{align}
@@
 %\begin{theorem}\label{DeterministicUniquenessTheorem}
-%Fix integers $n, \ell$, and $k < m \leq \hat m$.
-Suppose $\mathbf{A}~\in~\mathbb{R}^{n \times m}$ satisfies the spark condition \eqref{SparkCondition} and that $k$-sparse \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} contain at least \mbox{$(k-1){\hat m \choose k}+1$} vectors supported in general linear position on each set in some $\ell$-regular $E \subseteq {[m] \choose k}$ satisfying the SIP.
+%Fix integers $n, \ell$, and $k < m \leq \bar m$.
+Suppose $\mathbf{A}~\in~\mathbb{R}^{n \times m}$ satisfies the spark condition \eqref{SparkCondition} and that $k$-sparse \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} contain at least \mbox{$(k-1){\bar m \choose k}+1$} vectors supported in general linear position on each set in some $\ell$-regular $E \subseteq {[m] \choose k}$ satisfying the SIP.
 There exists a constant $C_1 > 0$ for which the following holds for all $\varepsilon < L_2(\mathbf{A}) / C_1$.
 %
-%Every matrix $\mathbf{B} \in \mathbb{R}^{n \times \hat m}$ and $k$-sparse $\mathbf{\hat x}_1, \ldots, \mathbf{\hat x}_N \in \mathbb{R}^{\hat m}$ with  \mbox{$\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\hat x}_i\|_2 \leq \varepsilon$} for all $i$ necessarily satisfies:
+%Every matrix $\mathbf{B} \in \mathbb{R}^{n \times \bar m}$ and $k$-sparse $\mathbf{\bar x}_1, \ldots, \mathbf{\bar x}_N \in \mathbb{R}^{\bar m}$ with  \mbox{$\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\bar x}_i\|_2 \leq \varepsilon$} for all $i$ necessarily satisfies:
 %\begin{align}\label{Cstable}
@@
 %%
-%for some $J \subseteq [\hat m]$ of size \mbox{$\lfloor \hat m - \ell(\hat m - m) \rfloor$}, injective map $\phi$, permutation matrix $\mathbf{P}$, and invertible diagonal matrix $\mathbf{D}$.
+%for some $J \subseteq [\bar m]$ of size \mbox{$\lfloor \bar m - \ell(\bar m - m) \rfloor$}, injective map $\phi$, permutation matrix $\mathbf{P}$, and invertible diagonal matrix $\mathbf{D}$.
 %%\footnote{We note that the condition $\varepsilon < L_2(\mathbf{A})$ above is necessary.
-When \mbox{$\mathbf{A}$ = $I$} and $\mathbf{x}_i = \mathbf{e}_i$, it turns out that $C_1 = 1$ and there is a $\mathbf{B}$ and $1$-sparse $\mathbf{\hat x}_i$ with $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\hat x}_i\|_2 \leq \varepsilon$ violating \eqref{Cstable}.}
+When \mbox{$\mathbf{A}$ = $I$} and $\mathbf{x}_i = \mathbf{e}_i$, it turns out that $C_1 = 1$ and there is a $\mathbf{B}$ and $1$-sparse $\mathbf{\bar x}_i$ with $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\bar x}_i\|_2 \leq \varepsilon$ violating \eqref{Cstable}.}
 %
@@
 
-%In other words, the smaller the difference $\hat m - m$, the more columns and coefficients of the original $n \times m$ dictionary $\mathbf{A}$ and $m$-dimensional codes $\mathbf{x}_i$ contained (up to noise) in the appropriately scaled $n \times \hat m$ dictionary $\mathbf{B}$ and $\hat m$-dimensional codes $\mathbf{\hat x}_i$.
-In particular, when $\hat m = m$ all columns of $\mathbf{A}$ and coefficients of each $\mathbf{x}_i$ recoverable, as per Def.~\ref{maindef}.
+%In other words, the smaller the difference $\bar m - m$, the more columns and coefficients of the original $n \times m$ dictionary $\mathbf{A}$ and $m$-dimensional codes $\mathbf{x}_i$ contained (up to noise) in the appropriately scaled $n \times \bar m$ dictionary $\mathbf{B}$ and $\bar m$-dimensional codes $\mathbf{\bar x}_i$.
+In particular, when $\bar m = m$ all columns of $\mathbf{A}$ and coefficients of each $\mathbf{x}_i$ recoverable, as per Def.~\ref{maindef}.
 
@@
 \begin{align}\label{epsdel}
-\varepsilon(\delta_1, \delta_2) := \min \left\{ \frac{\delta_1}{ C_1 }, \frac{ \delta_2 (L_{2k}(\mathbf{A}) -  C_1\varepsilon)}{ 1 + C_1 \left( \max_{i \in [N]} \|\mathbf{x}_i\|_1  + \delta_2 \right) } \right\}.
+\varepsilon(\delta_1, \delta_2) := \min \left\{ \frac{\delta_1}{ C_1 }, \frac{ \delta_2 L_{2k}(\mathbf{A})}{ 1 + C_1 \left( \max_{i \in [N]} \|\mathbf{x}_i\|_1  + \delta_2 \right) } \right\}.
 \end{align}
@@
 \begin{proof}
-Given Thm.\ref{DeterministicUniquenessTheorem}, one needs only to produce sparse codes in general linear position.
+The implication of Thm.\ref{DeterministicUniquenessTheorem} in the case $\bar{m} = m$ is precisely that such a $Y$ has a stable sparse representation (Def.~\ref{maindef}).
+It remains, therefore, only to produce sparse codes in general linear position.
 However, this is straightforward with a ``Vandermonde'' matrix construction (e.g., see \cite{Hillar15}).
@@
 %Note that every $\ell$-regular hypergraph $E \subseteq {[m] \choose k}$ satisfies: \[|E|k = \sum_{S \in E}|S| = \sum_{i \in [m]} \deg(i) = \ell m.\] 
-As mentioned above, it is easy to construct a regular hypergraph $E \subseteq {[m] \choose k}$ with the SIP having size $|E| = m$, implying the lower bound for sample size $N$ from the introduction.
+As mentioned above, it is easy to construct a regular hypergraph $E \subseteq {[m] \choose k}$ with the SIP having cardinality $|E| = m$, implying the lower bound for sample size $N$ from the introduction.
 In certain cases, the SIP can be achieved with $|E| < m$; for example, when $k = \sqrt{m}$ one can take $E$ to be the rows and columns formed by arranging $[m]$ in a square grid.
-In light of Cor.~\ref{DeterministicUniquenessCorollary}, it would be interesting to determine other such $E$.
+%In light of Cor.~\ref{DeterministicUniquenessCorollary}, it would be interesting to determine other such $E$.
 %[ ** TODO ** can we show for every $k, m$ that there is an $E$ satisfying the SIP with $|E| = \ell m/k$ for every $\ell$ such that $\ell m/k$ is an integer?
@@
 
-\begin{corollary}
-Suppose $\mathbf{A}~\in~\mathbb{R}^{n \times m}$ satisfies the spark condition \eqref{SparkCondition} for some $k < m$ and that $k$-sparse $\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$ contain at least $\left[ (k-1){m \choose k} + 1 \right] + |E|k(k-1){m \choose k-1}$ vectors supported in general linear position on each set in some $\ell$-regular $E \subseteq {[m] \choose k}$ with the SIP.
+\begin{corollary}\label{SLCopt}
+Consider the assumptions as in Thm.\ref{DeterministicUniquenessTheorem} with $1 + (k-1){\bar m \choose k} + |E|k(k-1){\bar m \choose k-1}$ vectors supported on each $S \in E$.
+%Suppose $\mathbf{A}~\in~\mathbb{R}^{n \times m}$ satisfies the spark condition \eqref{SparkCondition} for some $k < m$ and that $k$-sparse $\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$ contain more than $(k-1){m \choose k} + |E|k(k-1){m \choose k-1}$ vectors supported in general linear position on each set in some $\ell$-regular $E \subseteq {[m] \choose k}$ with the SIP.
 Then there exists a constant $C_1 > 0$ for which the following holds for all $\varepsilon < L_2(\mathbf{A}) / C_1$.
-
-Every matrix $\mathbf{B} \in \mathbb{R}^{n \times \hat m}$ and set of vectors $\mathbf{\hat x}_1, \ldots, \mathbf{\hat x}_N \in \mathbb{R}^{\hat m}$ that solve:
+All matrices $\mathbf{B} \in \mathbb{R}^{n \times \bar m}$ and $\mathbf{\bar x}_1, \ldots, \mathbf{\bar x}_N \in \mathbb{R}^{\bar m}$ solving:
 \begin{align}\label{minsum}
-\min \sum_{i = 1}^N \|\mathbf{\hat x}_i\|_0 \ \ 
-\text{subject to} \ \ \|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\hat x}_i\|_2 \leq \varepsilon, \ \ \text{for all $i$},
+\min \sum_{i = 1}^N \|\mathbf{\bar x}_i\|_0 \ \ 
+\text{subject to} \ \ \|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\bar x}_i\|_2 \leq \varepsilon, \ \text{for all $i$},
 \end{align}
 %
-must have $\hat m \geq m$ and, provided $p = \hat m - \ell(\hat m - m)$ is positive, necessarily satisfy:
-\begin{align}\label{Cstable}
-\|(\mathbf{A}_J- \mathbf{B}_{\hat J} \mathbf{PD} )_j\|_2 \leq C_1 \varepsilon \ \  \text{for all $j \in J$},
-\end{align}
-for some $J \in {[m] \choose p}$, $\hat J \in {[\hat m] \choose p}$, permutation matrix $\mathbf{P}$, and invertible diagonal matrix $\mathbf{D}$.
+necessarily satisfy implications 1.) and 2.) from Thm.~\ref{DeterministicUniquenessTheorem}.
+%must have $\bar m \geq m$ and, provided $p = \bar m - \ell(\bar m - m) > 0$, necessarily satisfy \eqref{Cstable}
+%%\begin{align}\label{Cstable}
+%%\|(\mathbf{A}_J- \mathbf{B}_{\bar J} \mathbf{PD} )_j\|_2 \leq C_1 \varepsilon, \ \  \text{for  $j \in J$},
+%%\end{align}
+%for some $J \in {[m] \choose p}$, $\bar J \in {[\bar m] \choose p}$, permutation matrix $\mathbf{P}$, and invertible diagonal matrix $\mathbf{D}$.
 \end{corollary}
-
-\begin{proof}
-We derive a lower bound on the number of $k$-sparse $\mathbf{\hat x}_i$ and then apply Thm.~\ref{DeterministicUniquenessCorollary}. 
-Let $n_p$ be the number of $\mathbf{\hat x}_i$ with $\|\mathbf{\hat x}_i\|_0 = p$.  %, so that $\sum_{p = 1}^{m} n_p = N$. 
-Since the $\mathbf{x}_i$ are all $k$-sparse, by \eqref{minsum} we have:
-\begin{align}
-k \sum_{p = 0}^{m} n_p = kN \geq \sum_{i=0}^N \|\mathbf{x}_i\|_0 \geq \sum_{i=0}^N \|\mathbf{\hat x}_i\|_0 = \sum_{p=0}^{m} p n_p.
-\end{align}
-Hence,
-\begin{align}\label{eqn}
-\sum_{p = k+1}^m n_p \leq \sum_{p = k+1}^m (p-k) n_p \leq \sum_{p = 0}^k (k-p)n_p \leq k \sum_{p = 0}^{k-1} n_p.
-\end{align}
-
-Let $\mathbf{X}$ and $\mathbf{\hat{X}}$ be the $m \times N$ matrices with columns $\mathbf{x}_i$ and $\mathbf{\hat x}_i$, respectively, and let $I(S) = \{i \in [N]: \text{supp}(\mathbf{x}_i) \subseteq S\}$.
-It follows from the general linear position of the $\mathbf{x}_i$ and the linear independence of every $k$ columns of $\mathbf{A}$ that $L_k(\mathbf{AX}_{I(S)}) > 0$ for all $S \in E$; that is, for every $S \in E$, the columns of every $n \times k$ submatrix of $\mathbf{AX}_{I(S)}$ form a basis for $\text{\rm Span}\{\mathbf{A}_S\}$.
-Suppose there are $(k-1)|E| + 1$ vectors $\mathbf{x}_i$ for which the corresponding $\mathbf{\hat x}_i$ $(i \in J)$ share a support $\hat S$.
-By the pigeonhole principle, there must be some $S \in E$ supporting $k$ or more of these vectors $\mathbf{x}_i$; let them be indexed by $J \subseteq I(S)$.
-Fixing $\mathbf{y} \in \text{\rm Span}\{ \mathbf{A}_S \}$, there exists a unique $\mathbf{c} = (c_1, \ldots, c_k) \in \mathbb{R}^k$ such that $\mathbf{y} = \mathbf{AX}_{J}\mathbf{c}$.
-Setting \mbox{$\mathbf{\hat{y}} = \mathbf{B\hat{X}}_{J}\mathbf{c} \in \text{\rm Span}\{\mathbf{B}_{\hat S}\}$}, we have:
-\begin{align*}
-\|\mathbf{y} - \mathbf{\hat{y}}\|_2 
-&= \|\sum_{i=1}^k c_i(\mathbf{AX}_J - \mathbf{B\hat{X}}_J)_i\|_2
-\leq \varepsilon \sum_{i=1}^k |c_i| \\
-&\leq \varepsilon \sqrt{k}  \|\mathbf{c}\|_2 
-\leq \frac{\varepsilon}{L_k(\mathbf{AX}_J)} \|\mathbf{y}\|_2,
-\end{align*}
-where the last inequality is by definition of $L_k$. From Def.~\ref{dDef}, it follows that:
-\begin{align}\label{rhs222}
-d(\text{\rm Span}\{\mathbf{A}_S\}, \text{\rm Span}\{\mathbf{B}_{\hat S}\}) 
-\leq \frac{\varepsilon}{ \min_{S \in E}L_k(\mathbf{AX}_{I(S)}) }.
-\end{align}
-
-Since (by our upper bound on $\varepsilon$) the RHS is strictly less than one, we have by \eqref{dimlem} that $k = \dim(\text{Span}(\mathbf{AX}_J)) \leq \dim(\text{Span}\{\mathbf{B}_{\hat S}\}) \leq |\hat S|$.
-Hence, if $|E|(k-1) + 1$ or more vectors $\mathbf{\hat x}_i$ share the same support, they cannot be $(k-1)$-sparse and the number of $(k-1)$-sparse vectors $\mathbf{\hat x}_i$ must then be bounded from above by $|E|(k-1){ m \choose k-1}$.
-Taking \eqref{eqn} into account, it follows that at least $N - |E|k(k-1){ m \choose k-1}$ of the vectors $\mathbf{\hat  x}_i$ are $k$-sparse, and there must then be some $N' \subseteq [N]$ for which for each $S \in E$ there are $(k-1){m \choose k}+1$ of the vectors $\mathbf{x}_i$ with $i \in [N']$ supported on $S$ and for which $\mathbf{\hat x}_i$ is $k$-sparse for all $i \in [N']$.
-The result now follows directly from Thm.~\ref{DeterministicUniquenessCorollary}.
-\end{proof}
 
@@
 Given any $\delta_1, \delta_2 \geq 0$ and $\varepsilon \leq \varepsilon(\delta_1, \delta_2)$,
-%every solution $\mathbf{B}, \mathbf{\hat x}_i, \ldots, \mathbf{\hat x}_N$ to the $\ell_0$ optimization problem:
+%every solution $\mathbf{B}, \mathbf{\bar x}_i, \ldots, \mathbf{\bar x}_N$ to the $\ell_0$ optimization problem:
 %\begin{align}\label{minsum}
-%\arg \min \sum_{i = 1}^N \|\mathbf{\hat x}_i\|_0 \ \ \text{s.t.} \ \ \mathbf{B}\mathbf{\hat x}_i = \mathbf{A}\mathbf{x}_i, \ \ \text{$i \in [N]$}, %\|\mathbf{A}\end{align}
+%\arg \min \sum_{i = 1}^N \|\mathbf{\bar x}_i\|_0 \ \ \text{s.t.} \ \ \mathbf{B}\mathbf{\bar x}_i = \mathbf{A}\mathbf{x}_i, \ \ \text{$i \in [N]$}, %\|\mathbf{A}\end{align}
 %necessarily satisfies the recovery inequalities in \eqref{def1}. % \eqref{Cstable} and \eqref{b-PDa}.
@@
 %\begin{proof}
-%We derive a lower bound on the number of $k$-sparse $\mathbf{\hat x}_i$ and then apply Thm.~\ref{DeterministicUniquenessCorollary}. 
-%First, note that $\|\mathbf{\hat x}_i\|_0 \neq 0$ for all $i$, since otherwise we would have $\mathbf{A}\mathbf{x}_i = \mathbf{B}\mathbf{\hat x}_i = \mathbf{0} \implies \mathbf{x}_i = \mathbf{0}$ by the spark condition, contradicting the general linear position of the $\mathbf{x}_i$.
-Let $n_p$ be the number of $\mathbf{\hat x}_i$ with $\|\mathbf{\hat x}_i\|_0 = p$.
+%We derive a lower bound on the number of $k$-sparse $\mathbf{\bar x}_i$ and then apply Thm.~\ref{DeterministicUniquenessCorollary}. 
+%First, note that $\|\mathbf{\bar x}_i\|_0 \neq 0$ for all $i$, since otherwise we would have $\mathbf{A}\mathbf{x}_i = \mathbf{B}\mathbf{\bar x}_i = \mathbf{0} \implies \mathbf{x}_i = \mathbf{0}$ by the spark condition, contradicting the general linear position of the $\mathbf{x}_i$.
+Let $n_p$ be the number of $\mathbf{\bar x}_i$ with $\|\mathbf{\bar x}_i\|_0 = p$.
 %, so that $\sum_{p = 1}^{m} n_p = N$.
@@
 %\begin{align}
-%k \sum_{p = 1}^{m} n_p = kN \geq \sum_{i=1}^N \|\mathbf{x}_i\|_0 \geq \sum_{i=1}^N \|\mathbf{\hat x}_i\|_0 = \sum_{p=1}^{m} p n_p.
+%k \sum_{p = 1}^{m} n_p = kN \geq \sum_{i=1}^N \|\mathbf{x}_i\|_0 \geq \sum_{i=1}^N \|\mathbf{\bar x}_i\|_0 = \sum_{p=1}^{m} p n_p.
 %\end{align}
@@
 %\end{align}
-%%\[ \implies \sum_{p = k+1}^m n_p \leq (k-1)^2 {\hat m \choose k-1} \]
+%%\[ \implies \sum_{p = k+1}^m n_p \leq (k-1)^2 {\bar m \choose k-1} \]
 %
-%By the spark condition and general linear position of the $\mathbf{x}_i$, every $k$ vectors $\mathbf{Ax}_i$ span a $k$-dimensional space; hence, at most $k-1$ vectors $\mathbf{\hat x}_i$ can share a support of size $k-1$ or less, and the number of $(k-1)$-sparse vectors $\mathbf{\hat x}_i$ is then bounded from above by $(k-1) { m \choose k-1}$.
-It follows that at least $N - (k-1)^2 {m \choose k-1}$ of the vectors $\mathbf{\hat  x}_i$ are $k$-sparse, and that there must then be some $N' \subseteq [N]$ for which for each $S \in E$ there are $(k-1){m \choose k}+1$ of the vectors $\mathbf{x}_i$ with $i \in [N']$ supported on $S$ and for which $\mathbf{\hat x}_i$ is $k$-sparse for all $i \in [N']$.
+%By the spark condition and general linear position of the $\mathbf{x}_i$, every $k$ vectors $\mathbf{Ax}_i$ span a $k$-dimensional space; hence, at most $k-1$ vectors $\mathbf{\bar x}_i$ can share a support of size $k-1$ or less, and the number of $(k-1)$-sparse vectors $\mathbf{\bar x}_i$ is then bounded from above by $(k-1) { m \choose k-1}$.
+It follows that at least $N - (k-1)^2 {m \choose k-1}$ of the vectors $\mathbf{\bar  x}_i$ are $k$-sparse, and that there must then be some $N' \subseteq [N]$ for which for each $S \in E$ there are $(k-1){m \choose k}+1$ of the vectors $\mathbf{x}_i$ with $i \in [N']$ supported on $S$ and for which $\mathbf{\bar x}_i$ is $k$-sparse for all $i \in [N']$.
 The result now follows directly from Thm.~\ref{DeterministicUniquenessCorollary}.
@@
 
-A similar phenomenon applies to sets of vectors with a stable sparse representation.
+A similar phenomenon applies to datasets of vectors with a stable sparse representation.
 As in \cite[Sec.~IV]{Hillar15}, consider the ``symbolic'' dataset $Y = \{\mathbf{A}\mathbf{x}_1,\ldots,\mathbf{A} \mathbf{x}_N\}$ generated by indeterminate $\mathbf{A}$ and indeterminate $k$-sparse $\mathbf{x}_1, \ldots, \mathbf{x}_N$.
@@
 \begin{theorem}\label{robustPolythm} %label is fucking up formatting..???
-Fix $n, m$, and $k < m$.
-There is a polynomial in the entries of $\mathbf{A}$ and the $\mathbf{x}_i$ with the following property:  if the polynomial evaluates to a nonzero number and at least \mbox{$(k-1){m \choose k}+1$} of the resulting vectors $\mathbf{x}_i$ are supported on each $S \in E$ for some regular $E \subseteq {[m] \choose k}$ with the SIP, then $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$ (Def.~\ref{maindef}).
+%Fix $n, m$, and $k < m$. 
+There is a polynomial in the entries of $\mathbf{A}$ and the $\mathbf{x}_i$ with the following property:  if the polynomial evaluates to a nonzero number and more than \mbox{$(k-1){m \choose k}$} of the resulting vectors $\mathbf{x}_i$ are supported on each $S \in E$ for some regular $E \subseteq {[m] \choose k}$ with the SIP, then $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$ (Def.~\ref{maindef}).
 In particular, either no substitutions impart to $Y$ this property or all but a Borel set of measure zero do.
@@
 Fix $n, m$, and $k$ satisfying \eqref{CScondition} for $\gamma = \gamma_0$, and let the entries of $\mathbf{A} \in \mathbb{R}^{n \times m}$ and $k$-sparse $\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$ be drawn independently from probability measures absolutely continuous with respect to the standard Borel measure $\mu$.
-If at least $(k-1){m \choose k} + 1$ of the vectors $\mathbf{x}_i$ are supported on each $S \in E$ for a regular $E \subseteq {[m] \choose k}$ with the SIP, then $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$ with probability one.
+If more than $(k-1){m \choose k} + 1$ of the vectors $\mathbf{x}_i$ are supported on each $S \in E$ for a regular $E \subseteq {[m] \choose k}$ with the SIP, then $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$ with probability one.
 \end{corollary}
 
-% [ ** TODO ** elaborate a little on these? ]
+Thus, choosing dictionary and sparse codes ``randomly'' generates datasets with stable sparse representations almost certainly, as long as the relevant parameters satisfy \eqref{CScondition}.
 
@@
 
-%If for some $k$-sparse $\mathbf{\hat x}_1, \ldots, \mathbf{\hat x}_N \in \mathbb{R}^{m'}$ and $\varepsilon < L_2(\mathbf{A}) / C_3$ we have \mbox{$\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\hat x}_i\|_2 \leq \varepsilon$} for all $i$, then:
+%If for some $k$-sparse $\mathbf{\bar x}_1, \ldots, \mathbf{\bar x}_N \in \mathbb{R}^{m'}$ and $\varepsilon < L_2(\mathbf{A}) / C_3$ we have \mbox{$\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\bar x}_i\|_2 \leq \varepsilon$} for all $i$, then:
 %\begin{align}\label{Cstablem'}
@@
 %In other words, the columns of $B$ contain (up to noise, after appropriate scaling) the columns of the original dictionary $\mathbf{A}$.
-Similarly, one can show by the same arguments at the beginning of Sec.~\ref{DUT} that the $\mathbf{\hat x}_i$ contain the original codes $\mathbf{x}_i$.
+Similarly, one can show by the same arguments at the beginning of Sec.~\ref{DUT} that the $\mathbf{\bar x}_i$ contain the original codes $\mathbf{x}_i$.
 The constant $C_3$ here is expression (\ref{Cdef2}) from the proof of Thm.~\ref{DeterministicUniquenessTheorem2}.
@@
 &\geq | \|\mathbf{A}\mathbf{x}\|_2 - \|(\mathbf{A}-\mathbf{BPD})\mathbf{x}\|_2 | \\
-&\geq \sqrt{2k} (L_{2k}(\mathbf{A}) -  C_1\varepsilon) \|\mathbf{x}\|_2,
+&\geq \sqrt{2k} (L_{2k}(\mathbf{A}) -  C_1\varepsilon) \|\mathbf{x}\|_2.
 \end{align*}
@@
 \begin{align*}
-\|\mathbf{x}_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\hat x}_i \|_1
-%&\leq \sqrt{2k} |\mathbf{x}_i - D^{-1}P^{\top}\mathbf{\hat x}_i\|_2 \\
-&\leq \frac{\|\mathbf{BPD}(\mathbf{x}_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\hat x}_i)\|_2}{L_{2k}(\mathbf{BPD})} \\
-&\leq \frac{\|\mathbf{B}\mathbf{\hat x}_i - \mathbf{A}\mathbf{x}_i\|_2 + \|(\mathbf{A} - \mathbf{BPD})\mathbf{x}_i\|_2}{L_{2k}(\mathbf{BPD})} \\
+\|\mathbf{x}_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\bar x}_i \|_1
+%&\leq \sqrt{2k} |\mathbf{x}_i - D^{-1}P^{\top}\mathbf{\bar x}_i\|_2 \\
+&\leq \frac{\|\mathbf{BPD}(\mathbf{x}_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\bar x}_i)\|_2}{L_{2k}(\mathbf{BPD})} \\
+&\leq \frac{\|\mathbf{B}\mathbf{\bar x}_i - \mathbf{A}\mathbf{x}_i\|_2 + \|(\mathbf{A} - \mathbf{BPD})\mathbf{x}_i\|_2}{L_{2k}(\mathbf{BPD})} \\
 &\leq \frac{\varepsilon (1+C_1 \|\mathbf{x}_i\|_1)}{L_{2k}(\mathbf{BPD})}.
@@
 
-Fix $\mathbf{A} \in \mathbb{R}^{n \times m}$ satisfying \eqref{SparkCondition} and suppose that for some $\mathbf{B} \in \mathbb{R}^{n \times \hat m}$ ($\hat m \geq m$) and $1$-sparse $\mathbf{\hat x}_i \in \mathbb{R}^{\hat m}$ we have  $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\hat x}_i\|_2 \leq \varepsilon < L_2(\mathbf{A}) / C_1$ for all $i$.
-Then, there are $\hat{c}_1, \ldots, \hat{c}_m \in \mathbb{R}$ and a map $\pi: [m] \to [\hat m]$ with:
+Fix $\mathbf{A} \in \mathbb{R}^{n \times m}$ satisfying \eqref{SparkCondition} and suppose that for some $\mathbf{B} \in \mathbb{R}^{n \times \bar m}$ and $1$-sparse $\mathbf{\bar x}_i \in \mathbb{R}^{\bar m}$ we have  $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\bar x}_i\|_2 \leq \varepsilon < L_2(\mathbf{A}) / C_1$ for all $i$.
+Then, there are $\bar{c}_1, \ldots, \bar{c}_m \in \mathbb{R}$ and a map $\pi: [m] \to [\bar m]$ with:
 \begin{align}\label{1D}
-\|c_j\mathbf{A}_j - \hat{c}_j\mathbf{B}_{\pi(j)}\|_2 \leq \varepsilon,\ \ \   \text{for all $j$}.
+\|c_j\mathbf{A}_j - \bar{c}_j\mathbf{B}_{\pi(j)}\|_2 \leq \varepsilon,\ \ \text{for $j \in [m]$}.
 \end{align} 
-Note that $\hat{c}_j \neq 0$, since otherwise (by definition of $L_2(\mathbf{A})$) we reach the contradiction $|c_j| < \min_{\ell \in [m]} | c_\ell |$.
+Note that if $\bar{c}_j = 0$, then $\|c_j\mathbf{A}_j \|_2 \leq \varepsilon$ implies from \eqref{delrho} that $|c_j| < \min_{\ell \in [m]} | c_\ell |$, a contradiction.
+Thus, $\bar{c}_j \neq 0$, $j \in [m]$.
+%Note that $\bar{c}_j \neq 0$, since otherwise (by definition of $L_2(\mathbf{A})$) we reach the contradiction $|c_j| < \min_{\ell \in [m]} | c_\ell |$.
 %by \eqref{delrho} and definition of $C_1$ we would have $\|c_j\mathbf{A}_j\|_2 < \min_{\ell \in [m]}\|c_{\ell}\mathbf{A}_{\ell}\|_2$.
@@
 
-We  now show that $\pi$ is injective (and thus is a permutation if $\hat m = m$).
+We  now show that $\pi$ is injective (and thus is a permutation if $\bar m = m$).
 Suppose that $\pi(i) = \pi(j) = \ell$ for some $i \neq j$ and $\ell$.
-Then, $\|c_{j}\mathbf{A}_{j} - \hat{c}_{j}\mathbf{B}_{\ell}\|_2 \leq \varepsilon$ and $\|c_{i}\mathbf{A}_{i} - \hat{c}_{i} \mathbf{B}_{\ell}\|_2  \leq \varepsilon$.
-Scaling and summing these inequalities by $|\hat{c}_{i}|$ and $|\hat{c}_{j}|$, respectively, and applying the triangle inequality, we obtain:
+Then, $\|c_{j}\mathbf{A}_{j} - \bar{c}_{j}\mathbf{B}_{\ell}\|_2 \leq \varepsilon$ and $\|c_{i}\mathbf{A}_{i} - \bar{c}_{i} \mathbf{B}_{\ell}\|_2  \leq \varepsilon$.
+Scaling and summing these inequalities by $|\bar{c}_{i}|$ and $|\bar{c}_{j}|$, respectively, and applying the triangle inequality, we obtain:
 \begin{align*}%\label{contra}
-(|\hat{c}_{i}| + |\hat{c}_{j}|) \varepsilon
-&\geq\|\mathbf{A}(\hat{c}_{i}c_{j} \mathbf{e}_{j} - \hat{c}_{j}c_{i}\mathbf{e}_{i})\|_2 \nonumber \\ 
-&\geq  \left( |\hat{c}_{i}| + |\hat{c}_{j}| \right) L_2(\mathbf{A}) \min_{\ell \in [m]} |c_\ell |,
+(|\bar{c}_{i}| + |\bar{c}_{j}|) \varepsilon
+&\geq\|\mathbf{A}(\bar{c}_{i}c_{j} \mathbf{e}_{j} - \bar{c}_{j}c_{i}\mathbf{e}_{i})\|_2 \nonumber \\ 
+&\geq  \left( |\bar{c}_{i}| + |\bar{c}_{j}| \right) L_2(\mathbf{A}) \min_{\ell \in [m]} |c_\ell |,
 \end{align*}
@@
 which contradicts the bound $\varepsilon < L_2(\mathbf{A})/C_1$.
-Hence, the map $\pi$ is injective.
-Setting $J = [m]$, $\hat J = \pi([m])$, and letting $P = \left( \mathbf{e}_{\pi(1)} \cdots \mathbf{e}_{\pi(m)}\right)$ and $D = \text{diag}(\frac{\hat{c}_1}{c_1},\ldots,\frac{\hat{c}_m}{c_m})$, we see that \eqref{1D} becomes, for all $j \in [m]$:
+Hence, the map $\pi$ is injective and $\bar m \geq m$.
+Setting $J = [m]$, $\bar J = \pi([m])$, and letting $P = \left( \mathbf{e}_{\pi(1)} \cdots \mathbf{e}_{\pi(m)}\right)$ and $D = \text{diag}(\frac{\bar{c}_1}{c_1},\ldots,\frac{\bar{c}_m}{c_m})$, we see that \eqref{1D} becomes, for all $j \in [m]$:
 \begin{align*}%\label{k=1result}
 \|\mathbf{A}_j - (\mathbf{B}_J\mathbf{PD})_j\|_2 
-= \|\mathbf{A}_j - \frac{\hat{c}_j}{c_j}\mathbf{B}_{\pi(j)}\|_2 
+= \|\mathbf{A}_j - \frac{\bar{c}_j}{c_j}\mathbf{B}_{\pi(j)}\|_2 
 \leq \frac{\varepsilon}{|c_j|} 
@@
 \begin{definition}\label{dDef}
-For $\mathbf{u} \in \mathbb R^m$, let $\text{\rm dist}(\mathbf{u}, V) := \inf \{\| \mathbf{u}-\mathbf{v} \|_2: \mathbf{v} \in V\}$, and for subspaces $U,V \subseteq \mathbb{R}^m$, define\footnote{Although identical, note the reference \cite{Morris10} defines the supremum over the unit ball.}: %[Kato p.197]
+For $\mathbf{u} \in \mathbb R^m$, let $\text{\rm dist}(\mathbf{u}, V) := \inf \{\| \mathbf{u}-\mathbf{v} \|_2: \mathbf{v} \in V\}$, and for vector spaces $U,V \subseteq \mathbb{R}^m$, define:
+%\footnote{Although identical, note the reference \cite{Morris10} defines the supremum over the unit ball.}: %[Kato p.197]
 \begin{align}\label{d}
-d(U,V) := \sup_{\mathbf{u} \in U, \ \|\mathbf{u}\|_2 = 1} \text{\rm dist}(\mathbf{u},V).
+d(U,V) := \sup_{\mathbf{u} \in U, \ \|\mathbf{u}\|_2 \leq 1} \text{\rm dist}(\mathbf{u},V).
 \end{align}
-Note that $d(U,\{\textbf{0}\}) = 1$ for $U \neq \{\mathbf{0}\}$, whereas if $U = \{\textbf{0}\}$ then $d$ has no meaning; in this case, set $d(\{\textbf{0}\},V) = 0$ for any $V$.
+% Note that $d(U,\{\textbf{0}\}) = 1$ for $U \neq \{\mathbf{0}\}$, whereas if $U = \{\textbf{0}\}$ then $d$ has no meaning; in this case, set $d(\{\textbf{0}\},V) = 0$ for any $V$.
 \end{definition}
@@
 \begin{lemma}\label{MainLemma}
-%Fix integers $k, \ell, m, \hat m$ and $n$ with $k < m$. 
+%Fix integers $k, \ell, m, \bar m$ and $n$ with $k < m$. 
 Suppose $\mathbf{A} \in \mathbb{R}^{n \times m}$ satisfies the spark condition \eqref{SparkCondition} for some $k < m$ and that $E \subseteq {[m] \choose k}$ is $\ell$-regular and satisfies the SIP.
-Then there exists a constant $C_2 > 0$ for which the following holds for all $\varepsilon < L_2(\mathbf{A}) / C_2$.
+There is a constant $C_2 > 0$ for which the following holds for all $\varepsilon < L_2(\mathbf{A}) / C_2$.
 
-If for some  $\mathbf{B} \in \mathbb{R}^{n \times \hat m}$ and map $\pi: E \mapsto {[\hat m] \choose k}$ we have:
+If for some  $\mathbf{B} \in \mathbb{R}^{n \times \bar m}$ and map $\pi: E \mapsto {[\bar m] \choose k}$ we have:
 \begin{align}\label{GapUpperBound}
-d(\text{\rm Span}\{\mathbf{A}_{S}\}, \text{\rm Span}\{\mathbf{B}_{\pi(S)}\}) \leq \varepsilon, \ \   \text{for all $S \in E$},
+d(\text{\rm Span}\{\mathbf{A}_{S}\}, \text{\rm Span}\{\mathbf{B}_{\pi(S)}\}) \leq \varepsilon, \ \  \text{for $S \in E$},
 \end{align}
 %
-then $\hat m \geq m$ and, provided $p = \hat m - \ell(\hat m - m)$ is positive:
+then $\bar m \geq m$, and if $p = \bar m - \ell(\bar m - m)$ is positive:
 \begin{align}\label{MainLemmaBPD}
-\|(\mathbf{A}_J - \mathbf{B}_{\hat J}\mathbf{PD})_j\|_2 \leq C_2 \varepsilon, \indent \text{for } j \in J.
+\|(\mathbf{A}_J - \mathbf{B}_{\bar J}\mathbf{PD})_j\|_2 \leq C_2 \varepsilon, \ \  \text{for } j \in J,
 \end{align}
-for some $J \in {[m] \choose p}$, $\hat J \in {[\hat m] \choose p}$, permutation matrix $\mathbf{P}$, and invertible diagonal matrix $\mathbf{D}$.
+for some $J \in {[m] \choose p}$, $\bar J \in {[\bar m] \choose p}$, permutation matrix $\mathbf{P}$, and invertible diagonal matrix $\mathbf{D}$.
 \end{lemma}
@@
 
-The constant $C_1$ in Thm.~\ref{DeterministicUniquenessTheorem} is then given by\footnote{We can be sure $C_1 > 0$ since $L_k(\mathbf{A}), L_k(\mathbf{X}_{I(S)}) > 0$ by the spark condition and general linear position of the $\mathbf{x}_i$; hence $\|\mathbf{A}_j\|_2 > 0$ for all $j$ and for all $S \in E$ we have $\|\mathbf{AX}_{I(S)}\mathbf{c}\|_2 \geq L_k(\mathbf{A})\|\mathbf{X}_{I(S)}\mathbf{c}\|_2 \geq L_k(\mathbf{A}) L_k(\mathbf{X}_{I(S)})\|\mathbf{c}\|_2$ for all $k$-sparse $\mathbf{c}$, and therefore $L_k(\mathbf{AX}_{I(S)}) \geq L_k(\mathbf{A}) L_k(\mathbf{X}_{I(S)}) > 0$.}:
+The constant $C_1$ in Thm.~\ref{DeterministicUniquenessTheorem} is then given by\footnote{Note that $\|\mathbf{AX}_{I(S)}\mathbf{c}\|_2 \geq \sqrt{k} L_k(\mathbf{A})\|\mathbf{X}_{I(S)}\mathbf{c}\|_2 \geq k L_k(\mathbf{A}) L_k(\mathbf{X}_{I(S)})\|\mathbf{c}\|_2$ for $S \in E$ and $k$-sparse $\mathbf{c}$.
+Therefore, $\sqrt{k} L_k(\mathbf{AX}_{I(S)}) \geq k L_k(\mathbf{A}) L_k(\mathbf{X}_{I(S)}) > 0$ since $L_k(\mathbf{A}), L_k(\mathbf{X}_{I(S)}) > 0$ by \eqref{SparkCondition} and general linear position of the $\mathbf{x}_i$.
+Thus, $C_1 > 0$.
+}:
 \begin{align}\label{Cdef1}
@@
 \end{definition}
-Note that $\theta \in (0,\frac{\pi}{2}]$ implies $0 < r \leq 1$.
-(We acknowledge the somewhat counter-intuitive property that $\theta =  \pi/2$ when $U = V$ and when $U \perp V$.)  %\textbf{Note:} we can also define $\theta$ by \cite[Lem.~9.5]{Deutsch12}:
+Note that $\theta \in (0,\frac{\pi}{2}]$ implies $0 < r \leq 1$.\footnote{We acknowledge the counter-intuitive property that $\theta =  \pi/2$ when $U = V$ and when $U \perp V$.}  %\textbf{Note:} we can also define $\theta$ by \cite[Lem.~9.5]{Deutsch12}:
 %\begin{align*}
@@
 %\end{align*}
-
 The constant $C_2$ in Lem.~\ref{MainLemma} can then be expressed as:  % \footnote{Note that $C_2 > 0$ is well-defined since $r > 0$ by definition.}
@@
 Fix $S \in E$.
-Since there are $(k-1){m \choose k}+1$ vectors $\mathbf{x}_i$ supported on $S$, the pigeon-hole principle implies that there exists some $S' \in {[m] \choose k}$ and some set of $k$ indices $J(S)$ such that the supports of all $\mathbf{x}_i$ and $\mathbf{\hat x}_i$ with $i \in J(S)$ are contained in $S$ and $S'$, respectively.
+Since there are $(k-1){m \choose k}+1$ vectors $\mathbf{x}_i$ supported on $S$, the pigeon-hole principle implies that there exists some $S' \in {[m] \choose k}$ and some set of $k$ indices $J(S)$ such that the supports of all $\mathbf{x}_i$ and $\mathbf{\bar x}_i$ with $i \in J(S)$ are contained in $S$ and $S'$, respectively.
 %%% No |S| = k assumption %%%
-We shall show that for every $S \in E$ there is some $S' \in {[m] \choose k}$, for which the distance $d(\text{\rm Span}\{\mathbf{A}_S\}, \text{\rm Span}\{\mathbf{B}_{S'}\})$ is controlled by $\varepsilon$.
-Applying Lem.~\ref{MainLemma} with the map $\pi$ defined by $S \mapsto S'$ then completes the proof.
-Since there are $(k-1){m \choose k}+1$ vectors $\mathbf{x}_i$ supported on $S$, the pigeon-hole principle implies that there exists some $S' \in {[m] \choose k}$ and some set of $k$ indices $I(S)$ such that the supports of all $\mathbf{x}_i$ and $\mathbf{\hat x}_i$ with $i \in I(S)$ are contained in $S$ and $S'$, respectively.
+We shall show that for every $S \in E$ there is some $\bar S \in {[m] \choose k}$, for which the distance $d(\text{\rm Span}\{\mathbf{A}_S\}, \text{\rm Span}\{\mathbf{B}_{\bar S}\})$ is controlled by $\varepsilon$.
+Applying Lem.~\ref{MainLemma} with the map $\pi$ defined by $S \mapsto \bar S$ then completes the proof.
+Since there are $(k-1){m \choose k}+1$ vectors $\mathbf{x}_i$ supported on $S$, the pigeon-hole principle implies that there exists some $\bar S \in {[m] \choose k}$ and some set of $k$ indices $I(S)$ such that the supports of all $\mathbf{x}_i$ and $\mathbf{\bar x}_i$ with $i \in I(S)$ are contained in $S$ and $\bar S$, respectively.
 
-Let $\mathbf{X}$ and $\mathbf{\hat{X}}$ be the $m \times N$ matrices with columns $\mathbf{x}_i$ and $\mathbf{\hat x}_i$, respectively.
+Let $\mathbf{X}$ and $\mathbf{\bar{X}}$ be the $m \times N$ matrices with columns $\mathbf{x}_i$ and $\mathbf{\bar x}_i$, respectively.
 It follows from the general linear position of the $\mathbf{x}_i$ and the linear independence of every $k$ columns of $\mathbf{A}$ that $L_k(\mathbf{AX}_{I(S)}) > 0$; that is, the columns of the $n \times k$ matrix $\mathbf{AX}_{I(S)}$ form a basis for $\text{\rm Span}\{\mathbf{A}_{S}\}$.
-Fixing $\mathbf{y} \in \text{\rm Span}\{\mathbf{A}_{S}\}$, there exists a unique $\mathbf{c} = (c_1, \ldots, c_k) \in \mathbb{R}^k$ such that $\mathbf{y} = \mathbf{AX}_{I(S)}\mathbf{c}$.
-Setting \mbox{$\mathbf{\hat{y}} = \mathbf{B\hat{X}}_{I(S)}\mathbf{c} \in \text{\rm Span}\{\mathbf{B}_{S'}\}$}, we have:
+Fixing $\mathbf{y} \in \text{\rm Span}\{\mathbf{A}_{S}\}$, there exists $\mathbf{c} = (c_1, \ldots, c_k) \in \mathbb{R}^k$ such that $\mathbf{y} = \mathbf{AX}_{I(S)}\mathbf{c}$.
+Setting \mbox{$\mathbf{\bar{y}} = \mathbf{B\bar{X}}_{I(S)}\mathbf{c} \in \text{\rm Span}\{\mathbf{B}_{\bar S}\}$}, we have:
 \begin{align*}
-\|\mathbf{y} - \mathbf{\hat{y}}\|_2 
-&= \|\sum_{i=1}^k c_i(\mathbf{AX}_{I(S)} - \mathbf{B\hat{X}}_{I(S)})_i\|_2
+\|\mathbf{y} - \mathbf{\bar{y}}\|_2 
+&= \|\sum_{i=1}^k c_i(\mathbf{AX}_{I(S)} - \mathbf{B\bar{X}}_{I(S)})_i\|_2
 \leq \varepsilon \sum_{i=1}^k |c_i| \\
@@
 \begin{align}\label{rhs222}
-d(\text{\rm Span}\{\mathbf{A}_S\}, \text{\rm Span}\{\mathbf{B}_{S'}\}) 
+d(\text{\rm Span}\{\mathbf{A}_S\}, \text{\rm Span}\{\mathbf{B}_{\bar S}\}) 
 \leq \frac{\varepsilon}{ \min_{S \in E} L_k(\mathbf{AX}_{I(S)}) }.
@@
 %We then show that the map over subsets of column indices defined by this association is such that the number of common elements shared by sets in its domain bounds the number of elements common to their images under this map.
+
+ \begin{proof}[Proof of Cor.~\ref{SLCopt}]
+We bound the number of $k$-sparse $\mathbf{\bar x}_i$ and then apply Thm.~\ref{DeterministicUniquenessCorollary}. 
+Let $n_p$ be the number of $\mathbf{\bar x}_i$ with $\|\mathbf{\bar x}_i\|_0 = p$.  %, so that $\sum_{p = 1}^{m} n_p = N$. 
+Since the $\mathbf{x}_i$ are all $k$-sparse, by \eqref{minsum} we have:
+%\begin{align}
+\mbox{$k \sum_{p = 0}^{m} n_p \geq \sum_{i=0}^N \|\mathbf{x}_i\|_0 \geq \sum_{i=0}^N \|\mathbf{\bar x}_i\|_0 = \sum_{p=0}^{m} p n_p.$}
+%\end{align}
+Hence,
+\begin{align}\label{eqn}
+\sum_{p = k+1}^m n_p \leq \sum_{p = k+1}^m (p-k) n_p \leq \sum_{p = 0}^k (k-p)n_p \leq k \sum_{p = 0}^{k-1} n_p.
+\end{align}
+
+Let $\mathbf{X}$ and $\mathbf{\bar{X}}$ be the $m \times N$ matrices with columns $\mathbf{x}_i$ and $\mathbf{\bar x}_i$, respectively, and let $I(S) = \{i \in [N]: \text{supp}(\mathbf{x}_i) \subseteq S\}$.
+From previous arguments, we have for every $S \in E$, the columns of every $n \times k$ submatrix of $\mathbf{AX}_{I(S)}$ form a basis for $\text{\rm Span}\{\mathbf{A}_S\}$.
+% the general linear position of the $\mathbf{x}_i$ and the linear independence of every $k$ columns of $\mathbf{A}$ that $L_k(\mathbf{AX}_{I(S)}) > 0$ for all $S \in E$; that is, for every $S \in E$, the columns of every $n \times k$ submatrix of $\mathbf{AX}_{I(S)}$ form a basis for $\text{\rm Span}\{\mathbf{A}_S\}$.
+Suppose there are $(k-1)|E| + 1$ vectors $\mathbf{x}_i$ for which the corresponding $\mathbf{\bar x}_i$ $(i \in J)$ share a support $\bar S$.
+By the pigeonhole principle, there must be some $S \in E$ supporting $k$ or more of these vectors $\mathbf{x}_i$; let them be indexed by $J \subseteq I(S)$.
+By the argument as in the proof of Thm.\ref{DeterministicUniquenessTheorem}, we also have \eqref{rhs222}.
+
+%Fixing $\mathbf{y} \in \text{\rm Span}\{ \mathbf{A}_S \}$, there exists $\mathbf{c} = (c_1, \ldots, c_k) \in \mathbb{R}^k$ such that $\mathbf{y} = \mathbf{AX}_{J}\mathbf{c}$.
+Setting \mbox{$\mathbf{\bar{y}} = \mathbf{B\bar{X}}_{J}\mathbf{c} \in \text{\rm Span}\{\mathbf{B}_{\bar S}\}$}, we have:
+%\begin{align*}
+%\|\mathbf{y} - \mathbf{\bar{y}}\|_2 
+%&= \|\sum_{i=1}^k c_i(\mathbf{AX}_J - \mathbf{B\bar{X}}_J)_i\|_2
+%\leq \varepsilon \sum_{i=1}^k |c_i| \\
+%&\leq \varepsilon \sqrt{k}  \|\mathbf{c}\|_2 
+%\leq \frac{\varepsilon}{L_k(\mathbf{AX}_J)} \|\mathbf{y}\|_2,
+%\end{align*}
+%where the last inequality is by definition of $L_k$. From Def.~\ref{dDef}, it follows that:
+%\begin{align}\label{rhs222}
+%d(\text{\rm Span}\{\mathbf{A}_S\}, \text{\rm Span}\{\mathbf{B}_{\bar S}\}) 
+%\leq \frac{\varepsilon}{ \min_{S \in E}L_k(\mathbf{AX}_{I(S)}) }.
+%\end{align}
+
+Our bound on $\varepsilon$ implies that the right-hand side is less than one, so that by \eqref{dimLem} we have $k = \dim(\text{Span}(\mathbf{AX}_J)) \leq \dim(\text{Span}\{\mathbf{B}_{\bar S}\}) \leq |\bar S|$.
+Hence, if $|E|(k-1) + 1$ or more vectors $\mathbf{\bar x}_i$ share the same support, they cannot be $(k-1)$-sparse, and the number of $(k-1)$-sparse vectors $\mathbf{\bar x}_i$ must then be bounded from above by $|E|(k-1){ m \choose k-1}$.
+Taking \eqref{eqn} into account, it follows that at least $N - |E|k(k-1){ m \choose k-1}$ of the vectors $\mathbf{\bar  x}_i$ are $k$-sparse, and there must then be some $N' \subseteq [N]$ for which for each $S \in E$ there are $(k-1){m \choose k}+1$ of the vectors $\mathbf{x}_i$ with $i \in [N']$ supported on $S$ and for which $\mathbf{\bar x}_i$ is $k$-sparse for all $i \in [N']$.
+The result now follows directly from Thm.~\ref{DeterministicUniquenessCorollary}.
+\end{proof}
 
@@
 Fully understanding those combinatorial designs allowing for stable representations of datasets is an interesting research area for the future.
-We also remark that our main uniqueness result (Thm.~\ref{DeterministicUniquenessTheorem}) accounts for deterministic ``worst-case'' noise, whereas the ``effective'' noise might be much smaller when it is sampled from a given distribution; in such cases, the constants in our results %Thms.~\ref{DeterministicUniquenessTheorem},~\ref{DeterministicUniquenessTheorem2}
+For instance, whether there is a support set size $N$ that is polynomial in $m,k$ gauanteeing the conclusions of Thm.~\ref{DeterministicUniquenessTheorem} has implications for the computational complexity of Prob.\ref{InverseProblem} and related questions \cite{Tillmann15}.
+We also remark that our main uniqueness result accounts for deterministic ``worst-case'' noise, whereas the ``effective'' noise might be much smaller when it is sampled from a given distribution; in such cases, the constants  %Thms.~\ref{DeterministicUniquenessTheorem},~\ref{DeterministicUniquenessTheorem2}
 will improve. %We note also that these results extend trivially to cases where point-wise injective nonlinearities are applied to the data.
@@
 For instance, it is difficult to ensure an algorithm maintain a dictionary satisfying \eqref{SparkCondition} at each learning stage; indeed, even certifying  a dictionary has this property is likely intractable given its NP-hardness \cite{tillmann2014computational}.
-[*** TODO:  Mention relationship of $N$ being a polynomial in $(m,k)$ as giving an NP-hardness result using this Tillmann one ***]
 
@@
 \begin{lemma}\label{NonEmptyLemma} 
-Fix integers $\ell, m$ and $\hat m$.
+Fix integers $\ell, m$ and $\bar m$.
 Suppose $E \subseteq 2^{[m]}$ is $\ell$-regular and satisfies the singleton intersection property.
-If there exists a map $\pi: E \to 2^{[\hat m]}$ such that $\sum_{S \in E} |S| = \sum_{S \in E} |\pi(S)|$ and:
+If there exists a map $\pi: E \to 2^{[\bar m]}$ such that $\sum_{S \in E} |S| = \sum_{S \in E} |\pi(S)|$ and:
 \begin{align}\label{cond}
-|\bigcap_{S \in F} \pi(S)| \leq |\bigcap_{S \in F} S |,\ \ \   \text{for all } F \subseteq E,
+|\bigcap_{S \in F} \pi(S)| \leq |\bigcap_{S \in F} S |,\ \ \   \text{for } F \subseteq E,
 \end{align}
 %
-then $\hat m \geq m$ and the association $i \mapsto \cap \pi(F(i))$ defines an injective map from $J$ to $[\hat m]$ for some $J \subseteq [m]$ of size $\hat m - \ell(\hat m - m)$.
-In particular, if $\hat m = m$ then the map $\pi$ is induced by a permutation.
+then $\bar m \geq m$ and the association $i \mapsto \cap \pi(F(i))$ defines an injective map from $J$ to $[\bar m]$ for some $J \subseteq [m]$ of size $\bar m - \ell(\bar m - m)$.
+In particular, if $\bar m = m$ then the map $\pi$ is induced by a permutation.
 %$\pi(E)$ is $\ell$-regular and satisfies the singleton intersection property. In particular, $|\cap_{S \in F} S| = 1$ if and only if $|\cap_{S \in F} \pi(S)| = 1$. 
@@
 \begin{proof}
-We first show that $\hat m \geq m$.
+We first show that $\bar m \geq m$.
 Fix $T = \{(j, S): j \in \pi(S), S \in E\}$.
 Then $|T| = \sum_{S \in E} |\pi(S)| = \sum_{S \in E} |S| = \sum_{i \in [m]} \deg(i) = \ell m$ by regularity of $E$.
-If $\hat m < m$ then by pigeonholing the $m \ell \geq \ell (\hat m + 1) \geq [(\ell + 1) - 1] \hat m + 1$ elements of $T$ with respect to the set $[\hat m]$ of possible first indices, we see that there must exist at least $\ell + 1$ elements of $T$ having the same first index.
+If $\bar m < m$ then by pigeonholing the $m \ell \geq \ell (\bar m + 1) \geq [(\ell + 1) - 1] \bar m + 1$ elements of $T$ with respect to the set $[\bar m]$ of possible first indices, we see that there must exist at least $\ell + 1$ elements of $T$ having the same first index.
 But by \eqref{cond} there can be no more than $\ell$ elements of $T$ with a given first index, since $E$ is $\ell$-regular.
-Hence $\hat m \geq m$.
+Hence $\bar m \geq m$.
 
-[ ** TODO ** rewrite for $\hat m > m$. ]
-Again, pigeonholing the elements of $T$ with respect to the set $[\hat m]$ of possible first indices, we see that for each $j$ there must be exactly $\ell$ elements of $T$ with $j$ as a first index; hence, $\pi(E)$ is $\ell$-regular.
+[ ** TODO ** rewrite for $\bar m > m$. ]
+Again, pigeonholing the elements of $T$ with respect to the set $[\bar m]$ of possible first indices, we see that for each $j$ there must be exactly $\ell$ elements of $T$ with $j$ as a first index; hence, $\pi(E)$ is $\ell$-regular.
 
@@
 Lem.~\ref{NonEmptyLemma} ensures the latter case is the only possibility.
-Thus, the association $\ell \mapsto \cap_{S \in F(\ell)} \pi(S)$ defines a map $\hat \pi: [m] \to [m]$ and $\dim(\text{\rm Span}\{\mathbf{B}_{\hat \pi(\ell)}\}) = 1$, since $\mathbf{B}_i \neq \textbf{0}$ for all $i$.
-By \eqref{eqdim}, it follows from \eqref{randoml} that $d\left( \text{\rm Span}\{\mathbf{A}_\ell\}, \text{\rm Span}\{ \mathbf{B}_{\hat \pi(\ell)} \} \right) \leq C_2 \varepsilon$.
-Since $\ell$ is arbitrary, fixing $\hat \varepsilon = C_2\delta$ it follows from \eqref{randoml} that for every basis vector $\mathbf{e}_\ell \in \mathbb{R}^m$ there exists some $c'_\ell \in \mathbb{R}$ such that $\|\mathbf{A}\mathbf{e}_\ell - c'_\ell \mathbf{B}\mathbf{e}_{\hat \pi(\ell)}\|_2 \leq \hat \varepsilon < L_2(\mathbf{A})$.
+Thus, the association $\ell \mapsto \cap_{S \in F(\ell)} \pi(S)$ defines a map $\bar \pi: [m] \to [m]$ and $\dim(\text{\rm Span}\{\mathbf{B}_{\bar \pi(\ell)}\}) = 1$, since $\mathbf{B}_i \neq \textbf{0}$ for all $i$.
+By \eqref{eqdim}, it follows from \eqref{randoml} that $d\left( \text{\rm Span}\{\mathbf{A}_\ell\}, \text{\rm Span}\{ \mathbf{B}_{\bar \pi(\ell)} \} \right) \leq C_2 \varepsilon$.
+Since $\ell$ is arbitrary, fixing $\bar \varepsilon = C_2\delta$ it follows from \eqref{randoml} that for every basis vector $\mathbf{e}_\ell \in \mathbb{R}^m$ there exists some $c'_\ell \in \mathbb{R}$ such that $\|\mathbf{A}\mathbf{e}_\ell - c'_\ell \mathbf{B}\mathbf{e}_{\bar \pi(\ell)}\|_2 \leq \bar \varepsilon < L_2(\mathbf{A})$.
 This is exactly the supposition in \eqref{1D} (letting $c_i = \|\mathbf{A}_i\|_2^{-1}$ for all $i$) and the result follows from the subsequent arguments for the case $k=1$ in Sec.~\ref{DUT}.
@@
 %\begin{lemma}\label{MainLemma2}
-%Fix integers $n$ and $k < m \leq \hat m$ and suppose $\mathbf{A}~\in~\mathbb{R}^{n \times m}$ and $\mathbf{B} \in \mathbb{R}^{n \times \hat m}$ both satisfiy \eqref{SparkCondition}.
+%Fix integers $n$ and $k < m \leq \bar m$ and suppose $\mathbf{A}~\in~\mathbb{R}^{n \times m}$ and $\mathbf{B} \in \mathbb{R}^{n \times \bar m}$ both satisfiy \eqref{SparkCondition}.
 There exists a constant $C_4 > 0$ for which for all $\varepsilon < L_2(\mathbf{A}) / C_4$ the following holds.
-If for some $E \subseteq2^{[m]}$ satisfying the singleton intersection property there exists a size-preserving map $\pi: E \mapsto 2^{[\hat m]}$ satisfying:
+If for some $E \subseteq2^{[m]}$ satisfying the singleton intersection property there exists a size-preserving map $\pi: E \mapsto 2^{[\bar m]}$ satisfying:
 %\begin{align}\label{GapUpperBound}
@@
 %
-%then for some $J \in {[\hat m] \choose m}$, permutation matrix $\mathbf{P}$ and invertible diagonal matrix $\mathbf{D}$, we have:
+%then for some $J \in {[\bar m] \choose m}$, permutation matrix $\mathbf{P}$ and invertible diagonal matrix $\mathbf{D}$, we have:
 %\begin{align}\label{MainLemmaBPD}
@@
 %
-%with $R$ being the lesser of $\min_{\substack{F \subseteq E}} r( \{ \text{\rm Span}\{\mathbf{A}_{S}\} \}_{S \in F})$ and $\min_{\substack{F \subseteq {[\hat m] \choose k}}} r( \{ \text{\rm Span}\{\mathbf{B}_{S}\} \}_{S \in F})$.
+%with $R$ being the lesser of $\min_{\substack{F \subseteq E}} r( \{ \text{\rm Span}\{\mathbf{A}_{S}\} \}_{S \in F})$ and $\min_{\substack{F \subseteq {[\bar m] \choose k}}} r( \{ \text{\rm Span}\{\mathbf{B}_{S}\} \}_{S \in F})$.
 %\end{lemma}
@@
 %\begin{proof}
-%The proof is very similar to the case $\hat m = m$, the difference being that now we may not invoke Lem.~\ref{NonEmptyLemma} (which requires $\hat m = m$) to infer from \eqref{fact2} that $| \cap_{S \in F(i)} \pi(S) | = 1$ for all stars $F(i)$.
+%The proof is very similar to the case $\bar m = m$, the difference being that now we may not invoke Lem.~\ref{NonEmptyLemma} (which requires $\bar m = m$) to infer from \eqref{fact2} that $| \cap_{S \in F(i)} \pi(S) | = 1$ for all stars $F(i)$.
 We circumvent this issue by instead assuming the spark condition on $\mathbf{B}$, which allows us to swap the roles of $\mathbf{A}$ and $\mathbf{B}$ in the arguments leading to the derivation of \eqref{fact2} to prove the opposite inequality for every star $F(i)$.
 Of course, this requires that the constant $C_4$  depend on $\mathbf{B}$.
-By these arguments we establish that $| \cap_{S \in F(i)} \pi(S) | = 1$ for all stars $F(i)$, yielding an injective map $\hat \pi: [m] \to [\hat m]$.
+By these arguments we establish that $| \cap_{S \in F(i)} \pi(S) | = 1$ for all stars $F(i)$, yielding an injective map $\bar \pi: [m] \to [\bar m]$.
 The result then follows from the proof of the case $k=1$.
@@
 %\begin{proof}[Proof of Thm.~\ref{DeterministicUniquenessTheorem2}]
-%The proof is the same as that of the case $\hat m = m$, only now we establish a map $\pi: E \to {[\hat m] \choose k}$ by pigeonholing $(k-1){\hat m \choose k} + 1$ vectors with respect to holes $[\hat m]$ and eventually applying Lem.~\ref{MainLemma2} instead of Lem.~\ref{MainLemma}.
+%The proof is the same as that of the case $\bar m = m$, only now we establish a map $\pi: E \to {[\bar m] \choose k}$ by pigeonholing $(k-1){\bar m \choose k} + 1$ vectors with respect to holes $[\bar m]$ and eventually applying Lem.~\ref{MainLemma2} instead of Lem.~\ref{MainLemma}.
 
@@
 %
-%with $R$ being the lesser of $\min_{\substack{F \subseteq E}} r( \{ \text{\rm Span}\{\mathbf{A}_{S}\} \}_{S \in F})$ and $\min_{\substack{F \subseteq {[\hat m] \choose k}}} r( \{ \text{\rm Span}\{\mathbf{B}_{S}\} \}_{S \in F})$.
+%with $R$ being the lesser of $\min_{\substack{F \subseteq E}} r( \{ \text{\rm Span}\{\mathbf{A}_{S}\} \}_{S \in F})$ and $\min_{\substack{F \subseteq {[\bar m] \choose k}}} r( \{ \text{\rm Span}\{\mathbf{B}_{S}\} \}_{S \in F})$.
 %\end{proof}

### 2017-04-04 manuscripts/PNAS/chazthm_pnas.tex
chaz things

@@
 %Fix integers $n, \ell$, and $k < m$. 
-Let $\mathbf{A}~\in~\mathbb{R}^{n \times m}$ satisfy \eqref{SparkCondition} for $k < m$, and suppose for some $\bar m$ more than \mbox{$(k-1){\bar m \choose k}$} $k$-sparse \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} are supported in general linear position on each set in an $\ell$-regular $E \subseteq {[m] \choose k}$ with the SIP.
+Let $\mathbf{A}~\in~\mathbb{R}^{n \times m}$ satisfy \eqref{SparkCondition} for $k < m$, and suppose for some $\bar m$ that more than \mbox{$(k-1){\bar m \choose k}$} $k$-sparse \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} are supported in general linear position on each set in an $\ell$-regular $E \subseteq {[m] \choose k}$ with the SIP.
 There is a constant $C_1 > 0$ for which the following hold for $\varepsilon < L_2(\mathbf{A}) / C_1$.
 
-1.) Every matrix $\mathbf{B} \in \mathbb{R}^{n \times \bar m}$ and $k$-sparse $\mathbf{\bar x}_1, \ldots, \mathbf{\bar x}_N \in \mathbb{R}^{\bar m}$ with  \mbox{$\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\bar x}_i\|_2 \leq \varepsilon$} for all $i$ must have $\bar m \geq m$ and, provided $p = \bar m - \ell(\bar m - m)$ is positive, necessarily satisfy:
+1) Every matrix $\mathbf{B} \in \mathbb{R}^{n \times \bar m}$ and $k$-sparse $\mathbf{\bar x}_1, \ldots, \mathbf{\bar x}_N \in \mathbb{R}^{\bar m}$ with  \mbox{$\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\bar x}_i\|_2 \leq \varepsilon$} for all $i$ must have $\bar m \geq m$ and, provided $p = \bar m - \ell(\bar m - m)$ is positive, necessarily satisfy:
 \begin{align}\label{Cstable}
@@
 
-2.) Restricting dictionaries and sparse codes to respective $J, \bar{J}$, we furthermore have that if $\varepsilon < L_{2k}(\mathbf{A}) / C_1$, then $\mathbf{B}$ also satisfies \eqref{SparkCondition} with $L_{2k}(\mathbf{B}\mathbf{PD}) \geq L_{2k}(\mathbf{A}) - C_1 \varepsilon$, and:
+2) Restricting dictionaries and sparse codes to respective $J, \bar{J}$, we furthermore have that if $\varepsilon < L_{2k}(\mathbf{A}) / C_1$, then $\mathbf{B}$ also satisfies \eqref{SparkCondition} with $L_{2k}(\mathbf{B}\mathbf{PD}) \geq L_{2k}(\mathbf{A}) - C_1 \varepsilon$, and:
 \begin{align}\label{b-PDa}
@@
 As mentioned above, it is easy to construct a regular hypergraph $E \subseteq {[m] \choose k}$ with the SIP having cardinality $|E| = m$, implying the lower bound for sample size $N$ from the introduction.
-In certain cases, the SIP can be achieved with $|E| < m$; for example, when $k = \sqrt{m}$ one can take $E$ to be the rows and columns formed by arranging $[m]$ in a square grid.
+In many cases, the SIP can be achieved with $|E| < m$; for example, when $k = \sqrt{m}$ one can take $E$ to be the rows and columns formed by arranging $[m]$ in a square grid.
 %In light of Cor.~\ref{DeterministicUniquenessCorollary}, it would be interesting to determine other such $E$.
@@
 \begin{corollary}\label{SLCopt}
-Consider the assumptions as in Thm.\ref{DeterministicUniquenessTheorem} with $1 + (k-1){\bar m \choose k} + |E|k(k-1){\bar m \choose k-1}$ vectors supported on each $S \in E$.
-%Suppose $\mathbf{A}~\in~\mathbb{R}^{n \times m}$ satisfies the spark condition \eqref{SparkCondition} for some $k < m$ and that $k$-sparse $\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$ contain more than $(k-1){m \choose k} + |E|k(k-1){m \choose k-1}$ vectors supported in general linear position on each set in some $\ell$-regular $E \subseteq {[m] \choose k}$ with the SIP.
-Then there exists a constant $C_1 > 0$ for which the following holds for all $\varepsilon < L_2(\mathbf{A}) / C_1$.
-All matrices $\mathbf{B} \in \mathbb{R}^{n \times \bar m}$ and $\mathbf{\bar x}_1, \ldots, \mathbf{\bar x}_N \in \mathbb{R}^{\bar m}$ solving:
+If the assumptions of Thm.\ref{DeterministicUniquenessTheorem} hold with more than $(k-1)\left[ {\bar m \choose k} + |E|k{\bar m \choose k-1}\right]$ vectors $\mathbf{x}_i$ supported on each $S \in E$, then all matrices $\mathbf{B} \in \mathbb{R}^{n \times \bar m}$ and $\mathbf{\bar x}_1, \ldots, \mathbf{\bar x}_N \in \mathbb{R}^{\bar m}$ solving:
 \begin{align}\label{minsum}
@@
 %
-necessarily satisfy implications 1.) and 2.) from Thm.~\ref{DeterministicUniquenessTheorem}.
+necessarily satisfy implications 1) and 2) from Thm.~\ref{DeterministicUniquenessTheorem}.
 %must have $\bar m \geq m$ and, provided $p = \bar m - \ell(\bar m - m) > 0$, necessarily satisfy \eqref{Cstable}
@@
 Fix $n, m$, and $k$ satisfying \eqref{CScondition} for $\gamma = \gamma_0$, and let the entries of $\mathbf{A} \in \mathbb{R}^{n \times m}$ and $k$-sparse $\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$ be drawn independently from probability measures absolutely continuous with respect to the standard Borel measure $\mu$.
-If more than $(k-1){m \choose k} + 1$ of the vectors $\mathbf{x}_i$ are supported on each $S \in E$ for a regular $E \subseteq {[m] \choose k}$ with the SIP, then $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$ with probability one.
+If more than $(k-1){m \choose k}$ of the vectors $\mathbf{x}_i$ are supported on each $S \in E$ for a regular $E \subseteq {[m] \choose k}$ with the SIP, then $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$ with probability one.
 \end{corollary}
@@
 
-\section{Proof of Theorem~\ref{DeterministicUniquenessTheorem}}\label{DUT}
+\section{Proof of Theorem~\ref{DeterministicUniquenessTheorem} and Corollary~\ref{SLCopt}}\label{DUT}
 
@@
 
+Given a sequence of vectors $\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$, we let $\mathbf{X}$ be the $m \times N$ matrix with columns $\mathbf{x}_i$ and $I(S) := \{i \in [N]: \text{supp}(\mathbf{x}_i) \subseteq S\}$.
 The constant $C_1$ in Thm.~\ref{DeterministicUniquenessTheorem} is then given by\footnote{Note that $\|\mathbf{AX}_{I(S)}\mathbf{c}\|_2 \geq \sqrt{k} L_k(\mathbf{A})\|\mathbf{X}_{I(S)}\mathbf{c}\|_2 \geq k L_k(\mathbf{A}) L_k(\mathbf{X}_{I(S)})\|\mathbf{c}\|_2$ for $S \in E$ and $k$-sparse $\mathbf{c}$.
@@
 \begin{align}\label{Cdef1}
-C_1(\mathbf{A}, \{\mathbf{x}_i\}_{i=1}^N, E) := \frac{ C_2(\mathbf{A}, E) } { \min_{S \in E} L_k(\mathbf{AX}_{I(S)}) },
+C_1(\mathbf{A}, \{\mathbf{x}_i\}_{i=1}^N, E) := \frac{ C_2(\mathbf{A}, E) } { \min_{S \in E} L_k(\mathbf{AX}_{I(S)}) }.
 \end{align}
-%
-where $\mathbf{X}$ is the $m \times N$ matrix with columns $\mathbf{x}_i$ and $I(S)$ is defined as those $i \in [N]$ with supports in $S$.
+
 The constant $C_2 = C_2(\mathbf{A}, E)$ is defined below in terms of one used in \cite{Deutsch12} to analyze the convergence of the alternating projections algorithm.
@@
 Applying Lem.~\ref{MainLemma} with the map $\pi$ defined by $S \mapsto \bar S$ then completes the proof.
-Since there are $(k-1){m \choose k}+1$ vectors $\mathbf{x}_i$ supported on $S$, the pigeon-hole principle implies that there exists some $\bar S \in {[m] \choose k}$ and some set of $k$ indices $I(S)$ such that the supports of all $\mathbf{x}_i$ and $\mathbf{\bar x}_i$ with $i \in I(S)$ are contained in $S$ and $\bar S$, respectively.
+Since there are $(k-1){\bar m \choose k}+1$ vectors $\mathbf{x}_i$ supported on $S$, the pigeon-hole principle implies that there exists some $\bar S \in {[\bar m] \choose k}$ and some set of $k$ indices $K$ such that the supports of all $\mathbf{x}_i$ and $\mathbf{\bar x}_i$ with $i \in K$ are contained in $S$ and $\bar S$, respectively.
 
-Let $\mathbf{X}$ and $\mathbf{\bar{X}}$ be the $m \times N$ matrices with columns $\mathbf{x}_i$ and $\mathbf{\bar x}_i$, respectively.
-It follows from the general linear position of the $\mathbf{x}_i$ and the linear independence of every $k$ columns of $\mathbf{A}$ that $L_k(\mathbf{AX}_{I(S)}) > 0$; that is, the columns of the $n \times k$ matrix $\mathbf{AX}_{I(S)}$ form a basis for $\text{\rm Span}\{\mathbf{A}_{S}\}$.
-Fixing $\mathbf{y} \in \text{\rm Span}\{\mathbf{A}_{S}\}$, there exists $\mathbf{c} = (c_1, \ldots, c_k) \in \mathbb{R}^k$ such that $\mathbf{y} = \mathbf{AX}_{I(S)}\mathbf{c}$.
-Setting \mbox{$\mathbf{\bar{y}} = \mathbf{B\bar{X}}_{I(S)}\mathbf{c} \in \text{\rm Span}\{\mathbf{B}_{\bar S}\}$}, we have:
+%Let $\mathbf{X}$ and $\mathbf{\bar{X}}$ be the $m \times N$ matrices with columns $\mathbf{x}_i$ and $\mathbf{\bar x}_i$, respectively. 
+It follows from the general linear position of the $\mathbf{x}_i$ and the linear independence of every $k$ columns of $\mathbf{A}$ that $L_k(\mathbf{AX}_{I(S)}) > 0$; that is, the columns of the $n \times k$ matrix $\mathbf{AX}_K$ form a basis for $\text{\rm Span}\{\mathbf{A}_{S}\}$.
+Fixing $\mathbf{y} \in \text{\rm Span}\{\mathbf{A}_{S}\}$, there exists $\mathbf{c} = (c_1, \ldots, c_k) \in \mathbb{R}^k$ such that $\mathbf{y} = \mathbf{AX}_K\mathbf{c}$.
+Setting \mbox{$\mathbf{\bar{y}} = \mathbf{B\bar{X}}_K\mathbf{c} \in \text{\rm Span}\{\mathbf{B}_{\bar S}\}$}, we have:
 \begin{align*}
 \|\mathbf{y} - \mathbf{\bar{y}}\|_2 
-&= \|\sum_{i=1}^k c_i(\mathbf{AX}_{I(S)} - \mathbf{B\bar{X}}_{I(S)})_i\|_2
+&= \|\sum_{i=1}^k c_i(\mathbf{AX}_K - \mathbf{B\bar{X}}_K)_i\|_2
 \leq \varepsilon \sum_{i=1}^k |c_i| \\
@@
 %\leq \frac{\varepsilon \sqrt{k}}{L(\mathbf{A}X_{J(S)})} \|\mathbf{A}X_{J(S)}\mathbf{c}\|_2 
-\leq \frac{\varepsilon}{L_k(\mathbf{AX}_{I(S)})} \|\mathbf{y}\|_2,
+\leq \frac{\varepsilon}{L_k(\mathbf{AX}_K)} \|\mathbf{y}\|_2,
 \end{align*}
@@
 \leq \frac{\varepsilon}{ \min_{S \in E} L_k(\mathbf{AX}_{I(S)}) }.
-%\leq \frac{\varepsilon}{L(\mathbf{AX}_{J(S)})}.
-%&< \left( \frac{ L_2(\mathbf{A}) }{ 2^{|E|} \max_{j \in [m]} \|\mathbf{A}_j\|_2 } \right) \frac{ \min_{S \in E} L_k(\mathbf{AX}_{I(S)}) } { L(\mathbf{AX}_{J(S)}) } \min_{\substack{F \subseteq E}} r( \{ \text{\rm Span}\{\mathbf{A}_{S}\} \}_{S \in F}) \\
 \end{align}
-%\begin{align}
-%\delta= \frac{\varepsilon}{ \min_{S \in E} L_k(\mathbf{AX}_{I(S)}) } = \frac{ C \varepsilon }{ \tilde C } < \frac{L_2(\mathbf{A})}{\tilde C}
-%\end{align}
 \end{proof}
@@
 
-Let $\mathbf{X}$ and $\mathbf{\bar{X}}$ be the $m \times N$ matrices with columns $\mathbf{x}_i$ and $\mathbf{\bar x}_i$, respectively, and let $I(S) = \{i \in [N]: \text{supp}(\mathbf{x}_i) \subseteq S\}$.
+We will show that no more than $(k-1)|E|$ vectors $\mathbf{\bar x}_i$ can share a support of cardinality less than $k$. 
+%Let $\mathbf{X}$ and $\mathbf{\bar{X}}$ be the $m \times N$ and $\bar m \times N$ matrices with columns $\mathbf{x}_i$ and $\mathbf{\bar x}_i$, respectively, and let $I(S) = \{i \in [N]: \text{supp}(\mathbf{x}_i) \subseteq S\}$.
 From previous arguments, we have for every $S \in E$, the columns of every $n \times k$ submatrix of $\mathbf{AX}_{I(S)}$ form a basis for $\text{\rm Span}\{\mathbf{A}_S\}$.
 % the general linear position of the $\mathbf{x}_i$ and the linear independence of every $k$ columns of $\mathbf{A}$ that $L_k(\mathbf{AX}_{I(S)}) > 0$ for all $S \in E$; that is, for every $S \in E$, the columns of every $n \times k$ submatrix of $\mathbf{AX}_{I(S)}$ form a basis for $\text{\rm Span}\{\mathbf{A}_S\}$.
-Suppose there are $(k-1)|E| + 1$ vectors $\mathbf{x}_i$ for which the corresponding $\mathbf{\bar x}_i$ $(i \in J)$ share a support $\bar S$.
-By the pigeonhole principle, there must be some $S \in E$ supporting $k$ or more of these vectors $\mathbf{x}_i$; let them be indexed by $J \subseteq I(S)$.
+Suppose there are more than $(k-1)|E|$ vectors $\mathbf{\bar x}_i$ sharing a support $\bar S$ of cardinality less than $k$.
+By the pigeonhole principle, there must be some $S \in E$ supporting $k$ or more of the corresponding $\mathbf{x}_i$; let them be indexed by $K \subseteq I(S)$.
 By the argument as in the proof of Thm.\ref{DeterministicUniquenessTheorem}, we also have \eqref{rhs222}.
+Since our bound on $\varepsilon$ implies that the right-hand side of \eqref{rhs222} is less than one, by \eqref{dimLem} we have $k = \dim(\text{Span}(\mathbf{A}_S)) \leq \dim(\text{Span}\{\mathbf{B}_{\bar S}\}) \leq |\bar S|$, a contradiction.
 
-%Fixing $\mathbf{y} \in \text{\rm Span}\{ \mathbf{A}_S \}$, there exists $\mathbf{c} = (c_1, \ldots, c_k) \in \mathbb{R}^k$ such that $\mathbf{y} = \mathbf{AX}_{J}\mathbf{c}$.
-Setting \mbox{$\mathbf{\bar{y}} = \mathbf{B\bar{X}}_{J}\mathbf{c} \in \text{\rm Span}\{\mathbf{B}_{\bar S}\}$}, we have:
-%\begin{align*}
-%\|\mathbf{y} - \mathbf{\bar{y}}\|_2 
-%&= \|\sum_{i=1}^k c_i(\mathbf{AX}_J - \mathbf{B\bar{X}}_J)_i\|_2
-%\leq \varepsilon \sum_{i=1}^k |c_i| \\
-%&\leq \varepsilon \sqrt{k}  \|\mathbf{c}\|_2 
-%\leq \frac{\varepsilon}{L_k(\mathbf{AX}_J)} \|\mathbf{y}\|_2,
-%\end{align*}
-%where the last inequality is by definition of $L_k$. From Def.~\ref{dDef}, it follows that:
-%\begin{align}\label{rhs222}
-%d(\text{\rm Span}\{\mathbf{A}_S\}, \text{\rm Span}\{\mathbf{B}_{\bar S}\}) 
-%\leq \frac{\varepsilon}{ \min_{S \in E}L_k(\mathbf{AX}_{I(S)}) }.
-%\end{align}
-
-Our bound on $\varepsilon$ implies that the right-hand side is less than one, so that by \eqref{dimLem} we have $k = \dim(\text{Span}(\mathbf{AX}_J)) \leq \dim(\text{Span}\{\mathbf{B}_{\bar S}\}) \leq |\bar S|$.
-Hence, if $|E|(k-1) + 1$ or more vectors $\mathbf{\bar x}_i$ share the same support, they cannot be $(k-1)$-sparse, and the number of $(k-1)$-sparse vectors $\mathbf{\bar x}_i$ must then be bounded from above by $|E|(k-1){ m \choose k-1}$.
-Taking \eqref{eqn} into account, it follows that at least $N - |E|k(k-1){ m \choose k-1}$ of the vectors $\mathbf{\bar  x}_i$ are $k$-sparse, and there must then be some $N' \subseteq [N]$ for which for each $S \in E$ there are $(k-1){m \choose k}+1$ of the vectors $\mathbf{x}_i$ with $i \in [N']$ supported on $S$ and for which $\mathbf{\bar x}_i$ is $k$-sparse for all $i \in [N']$.
+Hence, the number of $(k-1)$-sparse vectors $\mathbf{\bar x}_i$ is no greater than $|E|(k-1){ m \choose k-1}$.
+Taking \eqref{eqn} into account, it follows that at least $N - |E|k(k-1){ m \choose k-1}$ of the vectors $\mathbf{\bar  x}_i$ are $k$-sparse.
+Therefore, more than $(k-1){m \choose k}$ of the vectors $\mathbf{x}_i$ supported on each $S \in E$ have corresponding $\mathbf{\hat x}_i$ that are also $k$-sparse.
 The result now follows directly from Thm.~\ref{DeterministicUniquenessCorollary}.

### 2017-04-05 manuscripts/PNAS/chazthm_pnas.tex
almost there

@@
  supp$(\mathbf{x}) = S$ when $S$ indexes the nonzero components of $\mathbf{x}$.
-Let $\mathbf{M}_j$ be the $j$th column of a matrix $\mathbf{M}$ and similarly let $\mathbf{M}_S$ be the submatrix formed by the columns of $\mathbf{M}$ indexed by $S$ (we set $\text{\rm Span}\{\mathbf{M}_\emptyset\} := \{\textbf{0}\}$).
+Let $\mathbf{M}_S$ be the submatrix formed by the columns of $\mathbf{M}$ indexed by $S$, where we set $\text{\rm Span}\{\mathbf{M}_\emptyset\} := \{\textbf{0}\}$.
 
@@
 \end{align}
-For expositional clarity, we delay defining the (explicit) constant $C_1 = C_1(\mathbf{A}, \{\mathbf{x}_i\}_{i=1}^N, E)$ until Section \ref{DUT} (\eqref{Cdef1}).
-% , since it requires additional definitions not critical to the statement of our results.
+We delay defining the constant $C_1$ until Section \ref{DUT} (\eqref{Cdef1}).  % , since it requires additional definitions not critical to the statement of our results.
 
@@
 Since $f$ is a real analytic function, having one substitution of real numbers with $f(\mathbf{A}) \neq 0$ implies that its zeroes form a set of (Borel) measure zero.
-Hence, almost every $n \times m$ real matrix $\mathbf{A}$ satisfies \eqref{SparkCondition} provided \eqref{CScondition} holds for a value of $\gamma$ for some distribution.
-We remark that the precise relationship between $m$, $n$, and $k$ guaranteeing that $f$ is not identically zero is a challenging problem in real algebraic geometry.
+Hence, almost every $n \times m$ real matrix $\mathbf{A}$ satisfies \eqref{SparkCondition} provided \eqref{CScondition} holds with a $\gamma$ for some distribution.
+We set $\gamma_0$ to be the smallest known such $\gamma$.
+% We remark that the precise relationship between $m$, $n$, and $k$ guaranteeing that $f$ is not identically zero is a challenging problem in real algebraic geometry.
 In any case, we set $\gamma_0$ to be the smallest known such $\gamma$.
@@
 
-Thus, choosing dictionary and sparse codes ``randomly'' generates datasets with stable sparse representations almost certainly, as long as the relevant parameters satisfy \eqref{CScondition}.
+Thus, choosing dictionary and sparse codes ``randomly'' generate data with stable sparse representations almost certainly.
+% , as long as the relevant parameters satisfy \eqref{CScondition}.
 

### 2017-04-05 manuscripts/PNAS/chazthm_pnas.tex
main paper SRed

@@
 \begin{lemma}\label{MainLemma}
-%Fix integers $k, \ell, m, \bar m$ and $n$ with $k < m$. 
-Suppose $\mathbf{A} \in \mathbb{R}^{n \times m}$ satisfies the spark condition \eqref{SparkCondition} for some $k < m$ and that $E \subseteq {[m] \choose k}$ is $\ell$-regular and satisfies the SIP.
+%Suppose $\mathbf{A} \in \mathbb{R}^{n \times m}$ satisfies the spark condition \eqref{SparkCondition} for some $k < m$ and that $E \subseteq {[m] \choose k}$ is $\ell$-regular and satisfies the SIP.
 There is a constant $C_2 > 0$ for which the following holds for all $\varepsilon < L_2(\mathbf{A}) / C_2$.
+Suppose $\mathbf{A} \in \mathbb{R}^{n \times m}$ satisfies \eqref{SparkCondition} for some $k < m$ and that $E \subseteq {[m] \choose k}$ is $\ell$-regular with the SIP.
+There exists $C_2 > 0$ for which the following holds for all $\varepsilon < L_2(\mathbf{A}) / C_2$.
 
@@
 
-Given a sequence of vectors $\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$, we let $\mathbf{X}$ be the $m \times N$ matrix with columns $\mathbf{x}_i$ and $I(S) := \{i \in [N]: \text{supp}(\mathbf{x}_i) \subseteq S\}$.
-The constant $C_1$ in Thm.~\ref{DeterministicUniquenessTheorem} is then given by\footnote{Note that $\|\mathbf{AX}_{I(S)}\mathbf{c}\|_2 \geq \sqrt{k} L_k(\mathbf{A})\|\mathbf{X}_{I(S)}\mathbf{c}\|_2 \geq k L_k(\mathbf{A}) L_k(\mathbf{X}_{I(S)})\|\mathbf{c}\|_2$ for $S \in E$ and $k$-sparse $\mathbf{c}$.
+Given vectors $\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$, we let $\mathbf{X}$ be the $m \times N$ matrix with columns $\mathbf{x}_i$ and $I(S) := \{i \in [N]: \text{supp}(\mathbf{x}_i) \subseteq S\}$.
+The constant $C_1$ in Thm.~\ref{DeterministicUniquenessTheorem} is then defined by\footnote{Note that $\|\mathbf{AX}_{I(S)}\mathbf{c}\|_2 \geq \sqrt{k} L_k(\mathbf{A})\|\mathbf{X}_{I(S)}\mathbf{c}\|_2 \geq k L_k(\mathbf{A}) L_k(\mathbf{X}_{I(S)})\|\mathbf{c}\|_2$ for $S \in E$ and $k$-sparse $\mathbf{c}$.
 Therefore, $\sqrt{k} L_k(\mathbf{AX}_{I(S)}) \geq k L_k(\mathbf{A}) L_k(\mathbf{X}_{I(S)}) > 0$ since $L_k(\mathbf{A}), L_k(\mathbf{X}_{I(S)}) > 0$ by \eqref{SparkCondition} and general linear position of the $\mathbf{x}_i$.
@@
 
-The constant $C_2 = C_2(\mathbf{A}, E)$ is defined below in terms of one used in \cite{Deutsch12} to analyze the convergence of the alternating projections algorithm.
+The constant $C_2 = C_2(\mathbf{A}, E)$ is given below in terms of one used in \cite{Deutsch12} to analyze the convergence of the alternating projections algorithm.
 % for projecting a point onto the intersection of a set of subspaces. 
@@
 \end{definition}
-Note that $\theta \in (0,\frac{\pi}{2}]$ implies $0 < r \leq 1$.\footnote{We acknowledge the counter-intuitive property that $\theta =  \pi/2$ when $U = V$ and when $U \perp V$.}  %\textbf{Note:} we can also define $\theta$ by \cite[Lem.~9.5]{Deutsch12}:
+Note that $\theta \in (0,\frac{\pi}{2}]$ implies $0 < r \leq 1$.\footnote{We acknowledge the counter-intuitive property that $\theta =  \pi/2$ when $U = V$ or $U \perp V$.}  %\textbf{Note:} we can also define $\theta$ by \cite[Lem.~9.5]{Deutsch12}:
 %\begin{align*}
@@
 \end{align}
-%Note that when $k=1$ the constant $C_1$ is consistent with the value in our proof of the case $k=1$.
+Note that $k=1$ gives the same $C_1$ as that used to prove $k=1$.
 
 \begin{proof}[Proof of Thm.~\ref{DeterministicUniquenessCorollary} for $k < m$] 
-%We begin by showing that for every $S \in E$ there is some $S' \in {[m] \choose k}$ for which the distance $d(\text{\rm Span}\{\mathbf{A}_S\}, \text{\rm Span}\{\mathbf{B}_S'\})$ is controlled by $\varepsilon$.
-Fix $S \in E$.
-Since there are $(k-1){m \choose k}+1$ vectors $\mathbf{x}_i$ supported on $S$, the pigeon-hole principle implies that there exists some $S' \in {[m] \choose k}$ and some set of $k$ indices $J(S)$ such that the supports of all $\mathbf{x}_i$ and $\mathbf{\bar x}_i$ with $i \in J(S)$ are contained in $S$ and $S'$, respectively.
-%%% No |S| = k assumption %%%
-We shall show that for every $S \in E$ there is some $\bar S \in {[m] \choose k}$, for which the distance $d(\text{\rm Span}\{\mathbf{A}_S\}, \text{\rm Span}\{\mathbf{B}_{\bar S}\})$ is controlled by $\varepsilon$.
+We shall show that for every $S \in E$ there is some $\bar S \in {[\bar m] \choose k}$, for which the distance $d(\text{\rm Span}\{\mathbf{A}_S\}, \text{\rm Span}\{\mathbf{B}_{\bar S}\})$ is controlled by $\varepsilon$.
 Applying Lem.~\ref{MainLemma} with the map $\pi$ defined by $S \mapsto \bar S$ then completes the proof.
-Since there are $(k-1){\bar m \choose k}+1$ vectors $\mathbf{x}_i$ supported on $S$, the pigeon-hole principle implies that there exists some $\bar S \in {[\bar m] \choose k}$ and some set of $k$ indices $K$ such that the supports of all $\mathbf{x}_i$ and $\mathbf{\bar x}_i$ with $i \in K$ are contained in $S$ and $\bar S$, respectively.
+
+Since there are $(k-1){\bar m \choose k}+1$ vectors $\mathbf{x}_i$ supported on $S$, the pigeonhole principle implies that there is some $\bar S \in {[\bar m] \choose k}$ and some set of $k$ indices $K$ such that the supports of all $\mathbf{x}_i$ and $\mathbf{\bar x}_i$ with $i \in K$ are contained in $S$ and $\bar S$, respectively.
 
 %Let $\mathbf{X}$ and $\mathbf{\bar{X}}$ be the $m \times N$ matrices with columns $\mathbf{x}_i$ and $\mathbf{\bar x}_i$, respectively. 
-It follows from the general linear position of the $\mathbf{x}_i$ and the linear independence of every $k$ columns of $\mathbf{A}$ that $L_k(\mathbf{AX}_{I(S)}) > 0$; that is, the columns of the $n \times k$ matrix $\mathbf{AX}_K$ form a basis for $\text{\rm Span}\{\mathbf{A}_{S}\}$.
-Fixing $\mathbf{y} \in \text{\rm Span}\{\mathbf{A}_{S}\}$, there exists $\mathbf{c} = (c_1, \ldots, c_k) \in \mathbb{R}^k$ such that $\mathbf{y} = \mathbf{AX}_K\mathbf{c}$.
+It follows from the general linear position of the $\mathbf{x}_i$ and the linear independence of every $k$ columns of $\mathbf{A}$ that $L_k(\mathbf{AX}_{K}) > 0$; that is, the columns of the $n \times k$ matrix $\mathbf{AX}_K$ form a basis for $\text{\rm Span}\{\mathbf{A}_{S}\}$.
+Fixing $\mathbf{0} \neq \mathbf{y} \in \text{\rm Span}\{\mathbf{A}_{S}\}$, there exists $\mathbf{0} \neq \mathbf{c} = (c_1, \ldots, c_k) \in \mathbb{R}^k$ such that $\mathbf{y} = \mathbf{AX}_K\mathbf{c}$.
 Setting \mbox{$\mathbf{\bar{y}} = \mathbf{B\bar{X}}_K\mathbf{c} \in \text{\rm Span}\{\mathbf{B}_{\bar S}\}$}, we have:
@@
 \end{align*}
-where the last inequality is by definition of $L_k$. Finally, from Def.~\ref{dDef}, it follows that for all $S \in E$,
+where the last inequality follows directly from the definition of $L_k$. Finally, from Def.~\ref{dDef}, it follows that:
 \begin{align}\label{rhs222}
 d(\text{\rm Span}\{\mathbf{A}_S\}, \text{\rm Span}\{\mathbf{B}_{\bar S}\}) 
-\leq \frac{\varepsilon}{ \min_{S \in E} L_k(\mathbf{AX}_{I(S)}) }.
+\leq \frac{\varepsilon}{  L_k(\mathbf{AX}_{K}) }.
 \end{align}
+In particular, with $C_1$ as in \eqref{Cdef1}, the theorem follows.
 \end{proof}
+% for all $S \in E$:
+%\begin{align}\label{rhs222}
+%d(\text{\rm Span}\{\mathbf{A}_S\}, \text{\rm Span}\{\mathbf{B}_{\bar S}\}) 
+%\leq \frac{\varepsilon}{ \min_{S \in E} L_k(\mathbf{AX}_{I(S)}) }.
+%\end{align}
+%\end{proof}
 
@@
 
-We will show that no more than $(k-1)|E|$ vectors $\mathbf{\bar x}_i$ can share a support of cardinality less than $k$. 
+We now show that no more than $(k-1)|E|$ of the $\mathbf{\bar x}_i$ share a support of size less than $k$. 
 %Let $\mathbf{X}$ and $\mathbf{\bar{X}}$ be the $m \times N$ and $\bar m \times N$ matrices with columns $\mathbf{x}_i$ and $\mathbf{\bar x}_i$, respectively, and let $I(S) = \{i \in [N]: \text{supp}(\mathbf{x}_i) \subseteq S\}$.
-From previous arguments, we have for every $S \in E$, the columns of every $n \times k$ submatrix of $\mathbf{AX}_{I(S)}$ form a basis for $\text{\rm Span}\{\mathbf{A}_S\}$.
+From previous arguments, for every $S \in E$, the columns of each $n \times k$ submatrix of $\mathbf{AX}_{I(S)}$ form a basis for $\text{\rm Span}\{\mathbf{A}_S\}$.
 % the general linear position of the $\mathbf{x}_i$ and the linear independence of every $k$ columns of $\mathbf{A}$ that $L_k(\mathbf{AX}_{I(S)}) > 0$ for all $S \in E$; that is, for every $S \in E$, the columns of every $n \times k$ submatrix of $\mathbf{AX}_{I(S)}$ form a basis for $\text{\rm Span}\{\mathbf{A}_S\}$.
-Suppose there are more than $(k-1)|E|$ vectors $\mathbf{\bar x}_i$ sharing a support $\bar S$ of cardinality less than $k$.
-By the pigeonhole principle, there must be some $S \in E$ supporting $k$ or more of the corresponding $\mathbf{x}_i$; let them be indexed by $K \subseteq I(S)$.
+Suppose that more than $(k-1)|E|$ vectors $\mathbf{\bar x}_i$ share a support $\bar S$ of size $|\bar{S}| < k$.
+By the pigeonhole principle, there is some $S \in E$ supporting $k$ or more of the corresponding $\mathbf{x}_i$; let them be indexed by $K \subseteq I(S)$.
 By the argument as in the proof of Thm.\ref{DeterministicUniquenessTheorem}, we also have \eqref{rhs222}.
-Since our bound on $\varepsilon$ implies that the right-hand side of \eqref{rhs222} is less than one, by \eqref{dimLem} we have $k = \dim(\text{Span}(\mathbf{A}_S)) \leq \dim(\text{Span}\{\mathbf{B}_{\bar S}\}) \leq |\bar S|$, a contradiction.
+Since our bound on $\varepsilon$ implies that the right-hand side of \eqref{rhs222} is less than one, by \eqref{dimLem}: \[k = \dim(\text{Span}(\mathbf{A}_S)) \leq \dim(\text{Span}\{\mathbf{B}_{\bar S}\}) \leq |\bar S|,\] a contradiction.
 
@@
 Taking \eqref{eqn} into account, it follows that at least $N - |E|k(k-1){ m \choose k-1}$ of the vectors $\mathbf{\bar  x}_i$ are $k$-sparse.
-Therefore, more than $(k-1){m \choose k}$ of the vectors $\mathbf{x}_i$ supported on each $S \in E$ have corresponding $\mathbf{\hat x}_i$ that are also $k$-sparse.
+Therefore, more than $(k-1){m \choose k}$ of the vectors $\mathbf{x}_i$ supported on each $S \in E$ have corresponding $\mathbf{\bar x}_i$ that are also $k$-sparse.
 The result now follows directly from Thm.~\ref{DeterministicUniquenessCorollary}.

### 2017-04-05 manuscripts/PNAS/chazthm_pnas.tex
almost done with Supp

@@
 
-We require some auxiliary lemmas.
+In this supplemental, we prove Lem.\ref{MainLemma} after stating auxiliary lemmas.
 
@@
 \begin{align*}
-\text{\rm Span}\{\mathbf{M}_{\cap F}\}  = \cap_{S \in F} \text{\rm Span}\{\mathbf{M}_S\}.
+\text{\rm Span}\{\mathbf{M}_{\cap F}\}  = \bigcap_{S \in F} \text{\rm Span}\{\mathbf{M}_S\}.
 \end{align*}
@@
 \begin{proof}
-By induction, it is enough to prove the lemma when $|F| = 2$. The proof now follows directly from the assumption.
+Using induction on $|F|$, it is enough to prove the lemma when $|F| = 2$; but this case follows directly from the assumption.
 \end{proof}
@@
 \begin{lemma}\label{DistanceToIntersectionLemma}
-Fix $k \geq 2$. Let $V_1, \ldots, V_k$ be subspaces of $\mathbb{R}^m$ and set $V = \cap_{i = 1}^k V_i$. For every $\mathbf{x} \in \mathbb{R}^m$, we have:
+Fix $k \geq 2$.
+Let $V_1, \ldots, V_k$ be subspaces of $\mathbb{R}^m$ and set $V = \cap_{i = 1}^k V_i$.
+For  $\mathbf{x} \in \mathbb{R}^m$, we have (where $r$ is given in Def.~\ref{SpecialSupportSet}):
 \begin{align}\label{DTILeq}
-\text{\rm dist}(\mathbf{x}, V) \leq \frac{1}{r(\{V_i\}_{i = 1}^k)} \sum_{i=1}^k \text{\rm dist}(\mathbf{x}, V_i),
+\text{\rm dist}(\mathbf{x}, V) \leq \frac{1}{r(\{V_i\}_{i = 1}^k)} \sum_{i=1}^k \text{\rm dist}(\mathbf{x}, V_i).
 \end{align}
-where $r$ is given in Def.~\ref{SpecialSupportSet}.
 \end{lemma}
@@
 % Since subspaces of real vector spaces are closed, we can replace inf with min in def. of orthogonal projection
-
-We begin the proof by observing:
+Next, observe:
 %Use Pythagoras' Theorem first?
@@
 
-The desired result \eqref{DTILeq} now follows by bounding the second term on the right-hand side using the following fact \cite[Thm.~9.33]{Deutsch12}:
+The desired result, \eqref{DTILeq}, now follows by bounding the second term on the right-hand side using the following fact \cite[Thm.~9.33]{Deutsch12}:
 \begin{align}
@@
 for \mbox{$z^2= 1 - \prod_{\ell =1}^{k-1}(1-z_{\ell}^2)$} and \mbox{$z_{\ell} = \cos\theta\left(V_{\ell}, \cap_{s=\ell+1}^k V_s\right)$}.
-Together with $\Pi_{V_\ell} \Pi_V = \Pi_V$ for all $\ell = 1, \ldots, k$ and $\Pi_V^2 = \Pi_V$, this yields:
+Together with $\Pi_{V_\ell} \Pi_V = \Pi_V$ for all $\ell \in [k]$ and $\Pi_V^2 = \Pi_V$ yields:
 \begin{align*}
@@
 
-Substituting this into \eqref{f} and rearranging yields \eqref{DTILeq} after replacing $1 - z$ with $r(\{V_i\}_{i=1}^k)$ (as $z$ may depend on the arbitrary ordering of the $V_i$).
+Finally, substituting this into \eqref{f} and rearranging produces \eqref{DTILeq} after replacing $1 - z$ with $r(\{V_i\}_{i=1}^k)$.
+% ($z$ may depend on the ordering).
 \end{proof}
@@
 \begin{lemma}\label{NonEmptyLemma} 
-Fix integers $\ell, m$ and $\bar m$.
-Suppose $E \subseteq 2^{[m]}$ is $\ell$-regular and satisfies the singleton intersection property.
-If there exists a map $\pi: E \to 2^{[\bar m]}$ such that $\sum_{S \in E} |S| = \sum_{S \in E} |\pi(S)|$ and:
+Fix $\ell, m$, and $\bar m$. Suppose $E \subseteq 2^{[m]}$ is $\ell$-regular with the SIP.  If $\pi: E \to 2^{[\bar m]}$ has $\sum_{S \in E} |S| = \sum_{S \in E} |\pi(S)|$ and:
 \begin{align}\label{cond}
@@
 Hence $\bar m \geq m$.
-
-[ ** TODO ** rewrite for $\bar m > m$. ]
 Again, pigeonholing the elements of $T$ with respect to the set $[\bar m]$ of possible first indices, we see that for each $j$ there must be exactly $\ell$ elements of $T$ with $j$ as a first index; hence, $\pi(E)$ is $\ell$-regular.
-
 Fix $j$ and let $F(j) = \{S \in E: j \in \pi(S)\}$ be the preimage of the star in $\pi(E)$ centered at $j$, which is of size $\ell$ by the above arguments.
@@
 Thus $\pi(E)$ satisfies the singleton intersection property as well, and the preimage of every one of the $m$ stars in $\pi(E)$ is a star in $E$.
-
 It remains to show that every star in $E$ maps through $\pi$ to some star in $\pi(E)$.
@@
 \end{align}
-We will now show that \eqref{cond} holds.
+%We will now show that \eqref{cond} holds.
 %\begin{align}\label{fact2}
@@
 \end{align}
-%
 Note that since $\varepsilon < L_2(\mathbf{A}) / \tilde C_2$, by \eqref{delrho} the right-hand side in \eqref{randoml} is strictly less than one, so \eqref{dimLem} implies that $\dim(\text{\rm Span}\{\mathbf{B}_{\cap_{S \in F}\pi(S)}\}) \leq \dim(\text{\rm Span}\{\mathbf{A}_{\cap_{S \in F} S}\})$ and \eqref{fact2} follows from the linear independence of the columns of $\mathbf{A}_{S}$ and $\mathbf{B}_{\pi(S)}$ for all $S \in F$.
-
 Now, fix $\ell \in [m]$.
@@
 
-We now determine classes of datasets $Y$ having a stable sparse representation that are cut out by a single polynomial equation.
+%We now determine classes of datasets $Y$ having a stable sparse representation that are cut out by a single polynomial equation.
 
 \begin{proof}[Proof of Thm.~\ref{robustPolythm}]
-We sketch the argument, leaving the details to the reader. 
-Let $M$ be the $n \times m$ matrix with columns $\mathbf{A}\mathbf{x}_i$, $i \in [N]$.
-Consider the following polynomial \cite[Sec.~IV]{Hillar15} in the entries of $\mathbf{A}$ and the $\mathbf{x}_i$:
+% We sketch the argument, leaving the details to the reader. 
+Let $M$ be the matrix with columns $\mathbf{A}\mathbf{x}_i$, $i \in [N]$.  Consider the polynomial \cite[Sec.~IV]{Hillar15} in the entries of $\mathbf{A}$ and $\mathbf{x}_i$:
 \begin{align*}
@@
 with notation as in Sec.~\ref{Results}.  
-
 It can be checked that when $g$ is nonzero for a substitution of real numbers for the indeterminates, all of the genericity requirements on $\mathbf{A}$ and $\mathbf{x}_i$ in our proofs of stability in Thm.~\ref{DeterministicUniquenessTheorem} are satisfied (in particular, the spark condition on $\mathbf{A}$).
-The statement of the theorem now follows directly.
+% The statement of the theorem now follows directly.
 \end{proof}

### 2017-04-06 manuscripts/PNAS/chazthm_pnas.tex
sleek

@@
 More specifically, such dictionaries are uniquely identifiable from as few as \mbox{$N = m(k-1){m \choose k} + m$} sparse linear combinations of their columns up to an error that is linear in the measurement noise (Thm.~\ref{DeterministicUniquenessTheorem}).
-In fact, provided $(n, m, k)$ satisfy CS inequality \eqref{CScondition}, in almost all cases the dictionary learning problem is well-posed given enough data (Cor.~\ref{ProbabilisticCor}).
+In fact, provided $n \geq k$, %$(n, m, k)$ satisfy CS inequality \eqref{CScondition},
+in almost all cases the dictionary learning problem is well-posed given enough data (Cor.~\ref{ProbabilisticCor}).
 Importantly, these guarantees hold without assuming the recovered matrix satisfies the spark condition.
@@
 
-Another straightforward application of Thm.~\ref{DeterministicUniquenessTheorem} is a probabilistic extension, which takes advantage of the following well-known application of random matrix theory to compressed sensing.
-A random $n \times m$ matrix obeys \eqref{SparkCondition} with probability one (or ``high probability'' for discrete variables)
-provided:
-\begin{align}\label{CScondition}
-n \geq \gamma k\log\left(\frac{m}{k}\right),
-\end{align}
-in which $\gamma >0$ is a constant that depends on the particular distribution from which the entries of $\mathbf{A}$ are sampled i.i.d. (many ensembles suffice, e.g. see \cite[Sec.~4]{Baraniuk08}).
+%Another straightforward application of Thm.~\ref{DeterministicUniquenessTheorem} is a probabilistic extension, which takes advantage of the following well-known application of random matrix theory to compressed sensing.
+A random $n \times m$ matrix obeys \eqref{SparkCondition} with probability one (or ``high probability'' for discrete variables) provided:
+%\begin{align}\label{CScondition}
+%n \geq \gamma k\log\left(\frac{m}{k}\right),
+%\end{align}
+%in which $\gamma >0$ is a constant that depends on the particular distribution from which the entries of $\mathbf{A}$ are sampled i.i.d. (many ensembles suffice, e.g. see \cite[Sec.~4]{Baraniuk08}).
 
-In fact, 
-% We motivate our next theorem by the following observation:  
-the spark condition can be made explicit.
+Another straightforward application of Thm.~\ref{DeterministicUniquenessTheorem} is a probabilistic extension made possible by noticing that the spark condition can in fact be made explicit.
 Let $\mathbf{A}$  be the $n \times m$ matrix of $nm$ indeterminates $A_{ij}$.
@@
 Since $f$ is a real analytic function, having one substitution of real numbers with $f(\mathbf{A}) \neq 0$ implies that its zeroes form a set of (Borel) measure zero.
-Hence, almost every $n \times m$ real matrix $\mathbf{A}$ satisfies \eqref{SparkCondition} provided \eqref{CScondition} holds with a $\gamma$ for some distribution.
+Fortunately, it is easy to construct such a matrix $\mathbf{A}$ by inserting $n-k$ rows of zeros into a $k \times m$ ``Vandermonde" matrix construction.
+%Let $\gamma_1, \ldots, \gamma_m$ be any distinct numbers.
+Then the columns of the $k \times m$ matrix $V = (\gamma^{\ell}_i)^{k,m}_{\ell,i=1}$ are in general linear position (since the $\gamma_i$ are distinct, any $k \times k$ ``Vandermonde" sub-determinant is nonzero).
+Concatenating $n-k$ rows of zeros to the bottom of this matrix yields a $n \times m$ matrix $\mathbf{A}$ satisfying the spark condition, i.e.
+with $f(\mathbf{A}) = 0$.
+Hence, almost every real matrix $\mathbf{A}$ with at least $k$ rows and columns satisfies \eqref{SparkCondition}.
+%\eqref{CScondition} holds with a $\gamma$ for some distribution.
 We set $\gamma_0$ to be the smallest known such $\gamma$.
@@
 %Fix $n, m$, and $k < m$. 
-There is a polynomial in the entries of $\mathbf{A}$ and the $\mathbf{x}_i$ with the following property:  if the polynomial evaluates to a nonzero number and more than \mbox{$(k-1){m \choose k}$} of the resulting vectors $\mathbf{x}_i$ are supported on each $S \in E$ for some regular $E \subseteq {[m] \choose k}$ with the SIP, then $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$ (Def.~\ref{maindef}).
+There is a polynomial in the entries of $\mathbf{A}$ and the $\mathbf{x}_i$ with the following property:  if the polynomial evaluates to a nonzero number and more than \mbox{$(k-1){m \choose k}$} of the resulting vectors $\mathbf{x}_i$ are supported on each $S \in E$ for some regular $E \subseteq {[m] \choose k}$ with the SIP, then $Y$ has a stable $k$-sparse representation in $m$ dimensions (Def.~\ref{maindef}).
 In particular, either no substitutions impart to $Y$ this property or all but a Borel set of measure zero do.
@@
 \begin{corollary}\label{ProbabilisticCor}
-Fix $n, m$, and $k$ satisfying \eqref{CScondition} for $\gamma = \gamma_0$, and let the entries of $\mathbf{A} \in \mathbb{R}^{n \times m}$ and $k$-sparse $\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$ be drawn independently from probability measures absolutely continuous with respect to the standard Borel measure $\mu$.
-If more than $(k-1){m \choose k}$ of the vectors $\mathbf{x}_i$ are supported on each $S \in E$ for a regular $E \subseteq {[m] \choose k}$ with the SIP, then $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$ with probability one.
+Fix $n, m$ and $k$ such that $n \geq k < m$ % satisfying \eqref{CScondition} for $\gamma = \gamma_0$, 
+and let the entries of $\mathbf{A} \in \mathbb{R}^{n \times m}$ and $k$-sparse $\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$ be drawn independently from probability measures absolutely continuous with respect to the standard Borel measure $\mu$.
+If more than $(k-1){m \choose k}$ of the vectors $\mathbf{x}_i$ are supported on each $S \in E$ for a regular $E \subseteq {[m] \choose k}$ with the SIP, then $Y$ has a stable $k$-sparse representation in $m$ dimensions with probability one.
 \end{corollary}

### 2017-04-06 manuscripts/PNAS/chazthm_pnas.tex
2 more TODOs in Supp

@@
 There is a polynomial in the entries of $\mathbf{A}$ and the $\mathbf{x}_i$ with the following property:  if the polynomial evaluates to a nonzero number and more than \mbox{$(k-1){m \choose k}$} of the resulting vectors $\mathbf{x}_i$ are supported on each $S \in E$ for some regular $E \subseteq {[m] \choose k}$ with the SIP, then $Y$ has a stable $k$-sparse representation in $m$ dimensions (Def.~\ref{maindef}).
-In particular, either no substitutions impart to $Y$ this property or all but a Borel set of measure zero do.
+In particular, no substitutions give $Y$ this property or all but a Borel set of measure zero do.
 \end{theorem}
@@
 \begin{corollary}\label{ProbabilisticCor}
-Fix $n, m$ and $k$ such that $n \geq k < m$ % satisfying \eqref{CScondition} for $\gamma = \gamma_0$, 
+Fix $n, m$ and $k$ with $n \geq k < m$, % satisfying \eqref{CScondition} for $\gamma = \gamma_0$, 
 and let the entries of $\mathbf{A} \in \mathbb{R}^{n \times m}$ and $k$-sparse $\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$ be drawn independently from probability measures absolutely continuous with respect to the standard Borel measure $\mu$.
@@
 
-We note the following facts about $d$. For subspaces $U,V \subseteq \mathbb{R}^m$, we have \cite[Cor.~2.6]{Kato2013}:
+We note the following facts about $d$. For subspaces $U \subseteq U', V \subseteq \mathbb{R}^m$, we have $d(U,V) \leq d(U',V)$ and \cite[Cor.~2.6]{Kato2013}:
 \begin{align}\label{dimLem}
-d(U,V) < 1 \implies \dim(U) \leq \dim(V),
+d(U,V) < 1 \implies \dim(U) \leq \dim(V).
 \end{align}
 %
-and \cite[Lem.~3.2]{Morris10}:
+Also, from \cite[Lem.~3.2]{Morris10}:
 \begin{align}\label{eqdim}
@@
 %$\pi(E)$ is $\ell$-regular and satisfies the singleton intersection property. In particular, $|\cap_{S \in F} S| = 1$ if and only if $|\cap_{S \in F} \pi(S)| = 1$. 
+[*** TODO: Chris to Finish ***]
 \end{lemma}
@@
 
-\begin{proof}[Proof of Main Lemma]
-We first claim $\dim(\text{\rm Span}\{\mathbf{B}_{\pi(S)}\}) = \dim(\text{\rm Span}\{\mathbf{A}_{S}\})$ for all $S \in E$.
-To see why, note that the right-hand side of \eqref{GapUpperBound} is then strictly less than one, since $r \leq 1$ and $L_2(\mathbf{A}) \leq 1$ by \eqref{delrho}.
-By \eqref{dimLem}, it then follows that $|\pi(S)| \geq \dim(\text{\rm Span}\{\mathbf{B}_{\pi(S)}\}) \geq \dim(\text{\rm Span}\{\mathbf{A}_{S}\}) = |S|$, with the equality due to $\mathbf{A}$ satisfying \eqref{SparkCondition}; hence, $\dim(\text{\rm Span}\{\mathbf{B}_{\pi(S)}\}) = \dim(\text{\rm Span}\{\mathbf{A}_{S}\})$ (since $|S| = |\pi(S)|$).
-It follows that the columns of $\mathbf{B}_{\pi(S)}$ are linearly independent and, by \eqref{eqdim}:% and $\mathbf{B}_i \neq \textbf{0}$ for all $i$.
+\begin{proof}[Proof of Lem.\ref{MainLemma}]
+We first claim that $\text{\rm Span}\{\mathbf{B}_{\pi(S)}\}$ and $\text{\rm Span}\{\mathbf{A}_{S}\}$ have the same dimension for all $S \in E$.
+To see why, note that the right-hand side of \eqref{GapUpperBound} is strictly less than one, since $r \leq 1$ and $L_2(\mathbf{A}) \leq \max_{j \in [m]}\|\mathbf{A}_j\|_2$ by \eqref{delrho}.
+From \eqref{dimLem}, it then follows that $|\pi(S)| \geq \dim(\text{\rm Span}\{\mathbf{B}_{\pi(S)}\}) \geq \dim(\text{\rm Span}\{\mathbf{A}_{S}\}) = |S|$, with the equality due to $\mathbf{A}$ satisfying \eqref{SparkCondition}; hence, $\dim(\text{\rm Span}\{\mathbf{B}_{\pi(S)}\}) = \dim(\text{\rm Span}\{\mathbf{A}_{S}\})$ (since $|S| = |\pi(S)|$).
+The columns of $\mathbf{B}_{\pi(S)}$ are thus linearly independent and by \eqref{eqdim}:% and $\mathbf{B}_i \neq \textbf{0}$ for all $i$.
 \begin{align}\label{eq2}
@@
 \end{align}
-%We will now show that \eqref{cond} holds.
+We next verify \eqref{cond} holds.  
 %\begin{align}\label{fact2}
@@
 Fix $F \subseteq E$.
-Since $\text{\rm Span}\{\mathbf{B}_{\cap_{S \in F}\pi(S)}\} \subseteq \cap_{S \in F} \text{\rm Span}\{\mathbf{B}_{\pi(S)}\}$, if $\cap_{S \in F} \text{\rm Span}\{\mathbf{B}_{\pi(S)}\} = \textbf{0}$ then we must have $|\cap_{S \in F} \pi(S)| = 0$ (as $\mathbf{B}_i \neq \textbf{0}$ for all $i$) and \eqref{cond} trivially holds.
-Suppose then that the intersection is not the zero vector.
-By Lem.~\ref{SpanIntersectionLemma} and Lem.~\ref{DistanceToIntersectionLemma}, and incorporating \eqref{eq2} and \eqref{GapUpperBound}, we have:
+Since $\text{\rm Span}\{\mathbf{B}_{\cap_{S \in F}\pi(S)}\} \subseteq \cap_{S \in F} \text{\rm Span}\{\mathbf{B}_{\pi(S)}\}$, if $\cap_{S \in F} \text{\rm Span}\{\mathbf{B}_{\pi(S)}\} = \{\textbf{0}\}$, then $|\cap_{S \in F} \pi(S)| = 0$ (as $\mathbf{B}_i \neq \{\textbf{0}\}$ for all $i$) and \eqref{cond} trivially holds.
+On the other hand, suppose the intersection is not the zero vector.
+Using Lem.~\ref{SpanIntersectionLemma} and Lem.~\ref{DistanceToIntersectionLemma}, and incorporating \eqref{eq2} and \eqref{GapUpperBound}, we have:
 \begin{align}\label{randoml}
@@
 \end{align}
-Note that since $\varepsilon < L_2(\mathbf{A}) / \tilde C_2$, by \eqref{delrho} the right-hand side in \eqref{randoml} is strictly less than one, so \eqref{dimLem} implies that $\dim(\text{\rm Span}\{\mathbf{B}_{\cap_{S \in F}\pi(S)}\}) \leq \dim(\text{\rm Span}\{\mathbf{A}_{\cap_{S \in F} S}\})$ and \eqref{fact2} follows from the linear independence of the columns of $\mathbf{A}_{S}$ and $\mathbf{B}_{\pi(S)}$ for all $S \in F$.
-Now, fix $\ell \in [m]$.
+The right-hand side in \eqref{randoml} is strictly less than one, so \eqref{dimLem} implies that $\dim(\text{\rm Span}\{\mathbf{B}_{\cap_{S \in F}\pi(S)}\}) \leq \dim(\text{\rm Span}\{\mathbf{A}_{\cap_{S \in F} S}\})$ and \eqref{cond} follows from the linear independence of the columns of $\mathbf{A}_{S}$ and $\mathbf{B}_{\pi(S)}$ for all $S \in F$.
+
+[*** TODO: Check this last move here: ***]
+Applying Lem.\ref{NonEmptyLemma}, there is a $J \subseteq [m]$ and injective map $\bar{\pi}: J \to [\bar m]$ with $\|\mathbf{A}\mathbf{e}_j - \bar{c}_j \mathbf{B}\mathbf{e}_{\bar \pi(j)}\|_2 \leq \varepsilon < L_2(\mathbf{A})/C_1$, for some $\bar{c}_j \in \mathbb R$ and all $j \in J$.
+%Now, fix $\ell \in [m]$.
 Since $E$ satisfies the singleton intersection property, $\{\ell\} = \cap F(\ell)$ for the star $F(\ell) \subseteq E$.
@@
 Since $\ell$ is arbitrary, fixing $\bar \varepsilon = C_2\delta$ it follows from \eqref{randoml} that for every basis vector $\mathbf{e}_\ell \in \mathbb{R}^m$ there exists some $c'_\ell \in \mathbb{R}$ such that $\|\mathbf{A}\mathbf{e}_\ell - c'_\ell \mathbf{B}\mathbf{e}_{\bar \pi(\ell)}\|_2 \leq \bar \varepsilon < L_2(\mathbf{A})$.
-This is exactly the supposition in \eqref{1D} (letting $c_i = \|\mathbf{A}_i\|_2^{-1}$ for all $i$) and the result follows from the subsequent arguments for the case $k=1$ in Sec.~\ref{DUT}.
+This is exactly the supposition in \eqref{1D} (letting $c_i = \|\mathbf{A}_i\|_2^{-1}$ for all $i$) and
+The result now follows from the $k=1$ case in Sec.~\ref{DUT}.
 \end{proof}
+
+%; applying Lem.\ref{NonEmptyLemma} finishes the proof.
 
@@
 
-\section{Proofs of Thm.~\ref{robustPolythm} and Cor.~\ref{ProbabilisticCor}}\label{AppendixB} %Cors.~\ref{DeterministicUniquenessCorollary} \& \ref{ProbabilisticCor}}\label{AppendixB}
+\section{Proof (sketches) of Thm.~\ref{robustPolythm} and Cor.~\ref{ProbabilisticCor}}\label{AppendixB} %Cors.~\ref{DeterministicUniquenessCorollary} \& \ref{ProbabilisticCor}}\label{AppendixB}
 
@@
 
-\begin{proof}[Proof of Thm.~\ref{robustPolythm}]
+\begin{proof}[Proof (sketch) of Thm.~\ref{robustPolythm}]
 % We sketch the argument, leaving the details to the reader. 

### 2017-04-06 manuscripts/PNAS/chazthm_pnas.tex
sml edts

@@
 
-\section{Results}
+\section{Results}\label{results}
 
@@
 %$\pi(E)$ is $\ell$-regular and satisfies the singleton intersection property. In particular, $|\cap_{S \in F} S| = 1$ if and only if $|\cap_{S \in F} \pi(S)| = 1$. 
-[*** TODO: Chris to Finish ***]
+[*** TODO: Insert the final proof here ***]
 \end{lemma}
@@
 
-\section{Proof (sketches) of Thm.~\ref{robustPolythm} and Cor.~\ref{ProbabilisticCor}}\label{AppendixB} %Cors.~\ref{DeterministicUniquenessCorollary} \& \ref{ProbabilisticCor}}\label{AppendixB}
+\section{Proofs of Thm.~\ref{robustPolythm} and Cor.~\ref{ProbabilisticCor}}\label{AppendixB} %Cors.~\ref{DeterministicUniquenessCorollary} \& \ref{ProbabilisticCor}}\label{AppendixB}
 
@@
 \begin{proof}[Proof (sketch) of Thm.~\ref{robustPolythm}]
-% We sketch the argument, leaving the details to the reader. 
-Let $M$ be the matrix with columns $\mathbf{A}\mathbf{x}_i$, $i \in [N]$.  Consider the polynomial \cite[Sec.~IV]{Hillar15} in the entries of $\mathbf{A}$ and $\mathbf{x}_i$:
+% We sketch the argument, leaving the details to the reader.  %\cite[Sec.~IV]{Hillar15}
+Let $M$ be the matrix with columns $\mathbf{A}\mathbf{x}_i$, $i \in [N]$.  Consider the following polynomial in the entries of $\mathbf{A}$, $\mathbf{x}_i$:
 \begin{align*}
@@
 \end{align*}
-with notation as in Sec.~\ref{Results}.  
+with notation as in Sec.~\ref{results}.
 It can be checked that when $g$ is nonzero for a substitution of real numbers for the indeterminates, all of the genericity requirements on $\mathbf{A}$ and $\mathbf{x}_i$ in our proofs of stability in Thm.~\ref{DeterministicUniquenessTheorem} are satisfied (in particular, the spark condition on $\mathbf{A}$).
@@
 
-\begin{proof}[Proof of Cor.~\ref{ProbabilisticCor}]
-First, note that if a set of measure spaces $\{(X_{\ell}, \Sigma_{\ell}, \nu_{\ell})\}_{\ell=1}^p$ is such that $\nu_{\ell}$ is absolutely continuous with respect to $\mu$ for all $\ell = 1, \ldots, p$, where $\mu$ is the standard Borel measure on $\mathbb{R}$, then the product measure $\prod_{\ell=1}^p \nu_{\ell}$ is absolutely continuous with respect to the standard Borel product measure on $\mathbb{R}^p$ (e.g.,  \cite{folland2013real}).
+\begin{proof}[Proof (sketch) of Cor.~\ref{ProbabilisticCor}]
+First, note that if a set of measure spaces $\{(X_{\ell}, \Sigma_{\ell}, \nu_{\ell})\}_{\ell=1}^p$ has $\nu_{\ell}$ is absolutely continuous with respect to $\mu$ for all $\ell \in [p]$, where $\mu$ is the standard Borel measure on $\mathbb{R}$, then the product measure $\prod_{\ell=1}^p \nu_{\ell}$ is absolutely continuous with respect to the standard Borel product measure on $\mathbb{R}^p$ (e.g.,  \cite{folland2013real}).
 By Thm.~\ref{robustPolythm}, there is a polynomial that is nonzero whenever $Y$ has a stable $k$-sparse representation in $\mathbb R^m$; in particular, this property (stability) holds with probability one.

### 2017-04-06 manuscripts/PNAS/chazthm_pnas.tex
changes
eqn ref

--- 2017-04-06 manuscripts/PNAS/chazthm_pnas.tex
@@
 
-\section{Results}
+\section{Results}\label{Results}
 
@@
 %In other words, the smaller the difference $\bar m - m$, the more columns and coefficients of the original $n \times m$ dictionary $\mathbf{A}$ and $m$-dimensional codes $\mathbf{x}_i$ contained (up to noise) in the appropriately scaled $n \times \bar m$ dictionary $\mathbf{B}$ and $\bar m$-dimensional codes $\mathbf{\bar x}_i$.
-In particular, when $\bar m = m$ all columns of $\mathbf{A}$ and coefficients of each $\mathbf{x}_i$ recoverable, as per Def.~\ref{maindef}.
+%In particular, when $\bar m = m$ all columns of $\mathbf{A}$ and coefficients of each $\mathbf{x}_i$ recoverable, as per Def.~\ref{maindef}.
 
@@
 \end{align}
-Note that since $\varepsilon < L_2(\mathbf{A}) / \tilde C_2$, by \eqref{delrho} the right-hand side in \eqref{randoml} is strictly less than one, so \eqref{dimLem} implies that $\dim(\text{\rm Span}\{\mathbf{B}_{\cap_{S \in F}\pi(S)}\}) \leq \dim(\text{\rm Span}\{\mathbf{A}_{\cap_{S \in F} S}\})$ and \eqref{fact2} follows from the linear independence of the columns of $\mathbf{A}_{S}$ and $\mathbf{B}_{\pi(S)}$ for all $S \in F$.
+Note that since $\varepsilon < L_2(\mathbf{A}) / \tilde C_2$, by \eqref{delrho} the right-hand side in \eqref{randoml} is strictly less than one, so \eqref{dimLem} implies that $\dim(\text{\rm Span}\{\mathbf{B}_{\cap_{S \in F}\pi(S)}\}) \leq \dim(\text{\rm Span}\{\mathbf{A}_{\cap_{S \in F} S}\})$ and \eqref{cond} follows from the linear independence of the columns of $\mathbf{A}_{S}$ and $\mathbf{B}_{\pi(S)}$ for all $S \in F$.
 Now, fix $\ell \in [m]$.

### 2017-04-06 manuscripts/PNAS/chazthm_pnas.tex
main lemma

@@
 \begin{proof}[Proof of Main Lemma]
-We first claim $\dim(\text{\rm Span}\{\mathbf{B}_{\pi(S)}\}) = \dim(\text{\rm Span}\{\mathbf{A}_{S}\})$ for all $S \in E$.
-To see why, note that the right-hand side of \eqref{GapUpperBound} is then strictly less than one, since $r \leq 1$ and $L_2(\mathbf{A}) \leq 1$ by \eqref{delrho}.
-By \eqref{dimLem}, it then follows that $|\pi(S)| \geq \dim(\text{\rm Span}\{\mathbf{B}_{\pi(S)}\}) \geq \dim(\text{\rm Span}\{\mathbf{A}_{S}\}) = |S|$, with the equality due to $\mathbf{A}$ satisfying \eqref{SparkCondition}; hence, $\dim(\text{\rm Span}\{\mathbf{B}_{\pi(S)}\}) = \dim(\text{\rm Span}\{\mathbf{A}_{S}\})$ (since $|S| = |\pi(S)|$).
-It follows that the columns of $\mathbf{B}_{\pi(S)}$ are linearly independent and, by \eqref{eqdim}:% and $\mathbf{B}_i \neq \textbf{0}$ for all $i$.
+We begin by showing that: 
 \begin{align}\label{eq2}
@@
 \end{align}
-%We will now show that \eqref{cond} holds.
+%We first claim $\dim(\text{\rm Span}\{\mathbf{B}_{\pi(S)}\}) = \dim(\text{\rm Span}\{\mathbf{A}_{S}\})$ for all $S \in E$. 
+Since the right-hand side of \eqref{GapUpperBound} is strictly less than one (by \eqref{delrho} and $r \leq 1$), it follows by \eqref{dimLem} that $|\pi(S)| \geq \dim(\text{\rm Span}\{\mathbf{B}_{\pi(S)}\}) \geq \dim(\text{\rm Span}\{\mathbf{A}_{S}\}) = |S|$, with the equality due to $\mathbf{A}$ satisfying \eqref{SparkCondition}.
+Since $|S| = |\pi(S)|$, we therefore have $\dim(\text{\rm Span}\{\mathbf{B}_{\pi(S)}\}) = \dim(\text{\rm Span}\{\mathbf{A}_{S}\})$, and \eqref{eq2} follows by \eqref{eqdim}.
+Note that the columns of $\mathbf{B}_{\pi(S)}$ are therefore linearly independent, for all $S \in E$.
+
+We will now show that \eqref{cond} holds.
 %\begin{align}\label{fact2}
@@
 %\end{align}
-
 Fix $F \subseteq E$.
-Since $\text{\rm Span}\{\mathbf{B}_{\cap_{S \in F}\pi(S)}\} \subseteq \cap_{S \in F} \text{\rm Span}\{\mathbf{B}_{\pi(S)}\}$, if $\cap_{S \in F} \text{\rm Span}\{\mathbf{B}_{\pi(S)}\} = \textbf{0}$ then we must have $|\cap_{S \in F} \pi(S)| = 0$ (as $\mathbf{B}_i \neq \textbf{0}$ for all $i$) and \eqref{cond} trivially holds.
+Since $\text{\rm Span}\{\mathbf{B}_{\cap_{S \in F}\pi(S)}\} \subseteq \cap_{S \in F} \text{\rm Span}\{\mathbf{B}_{\pi(S)}\}$, if $\cap_{S \in F} \text{\rm Span}\{\mathbf{B}_{\pi(S)}\} = \textbf{0}$ then we must have $|\cap_{S \in F} \pi(S)| = 0$ (as the columns of $\mathbf{B}_{\pi(S)}$ are linearly independent) and \eqref{cond} trivially holds.
 Suppose then that the intersection is not the zero vector.
@@
 &\leq d\left( \cap_{S \in F} \text{\rm Span}\{\mathbf{B}_{\pi(S)}\}, \cap_{S \in F} \text{\rm Span}\{\mathbf{A}_{S}\} \right) \nonumber \\
-&\leq \sum_{S \in F} \frac{ d\left( \cap_{T \in F} \text{\rm Span}\{\mathbf{B}_{\pi(T)}\},\text{\rm Span}\{\mathbf{A}_{S}\} \right) }{ r( \{ \text{\rm Span}\{\mathbf{A}_{T}\}_{T \in F}) } \nonumber \\
-&\leq \sum_{S \in F} \frac{ d\left( \text{\rm Span}\{\mathbf{B}_{\pi(S)}\},\text{\rm Span}\{\mathbf{A}_{S}\} \right) }{ r( \{ \text{\rm Span}\{\mathbf{A}_{T}\}_{T \in F}) }\nonumber \\
+&\leq \sum_{T \in F} \frac{ d\left( \cap_{S \in F} \text{\rm Span}\{\mathbf{B}_{\pi(S)}\},\text{\rm Span}\{\mathbf{A}_{T}\} \right) }{ r( \{ \text{\rm Span}\{\mathbf{A}_{S}\}_{S \in F}) } \nonumber \\
+&\leq \sum_{T \in F} \frac{ d\left( \text{\rm Span}\{\mathbf{B}_{\pi(T)}\},\text{\rm Span}\{\mathbf{A}_{T}\} \right) }{ r( \{ \text{\rm Span}\{\mathbf{A}_{S}\}_{S \in F}) }\nonumber \\
 %&\leq \frac{1}{r( \{ \text{\rm Span}\{\mathbf{A}_{S}\}_{S \in F})} \sum_{S \in F} \frac{ \varepsilon }{ L(\mathbf{AX}_{J(S)}) } \nonumber \\
@@
 %&< L_2(\mathbf{A}) \frac{|F| }{ 2^{|E|}} \left( \frac{ \min_{\substack{F \subseteq E}} r( \{ \text{\rm Span}\{\mathbf{A}_{S}\}_{S \in F}) }{ r( \{ \text{\rm Span}\{\mathbf{A}_{S}\}_{S \in F}) } \right) \left( \frac{\min_{S \in E} L_k(\mathbf{AX}_{I(S)}) }{ \min_{T \in F} L(\mathbf{AX}_{J(T)}) } \right) \nonumber \\
-\leq C_2 \varepsilon. 
+\leq \frac{C_2 \varepsilon}{\max_i\|\mathbf{A}_i\|_2}. 
 \end{align}
-Note that since $\varepsilon < L_2(\mathbf{A}) / \tilde C_2$, by \eqref{delrho} the right-hand side in \eqref{randoml} is strictly less than one, so \eqref{dimLem} implies that $\dim(\text{\rm Span}\{\mathbf{B}_{\cap_{S \in F}\pi(S)}\}) \leq \dim(\text{\rm Span}\{\mathbf{A}_{\cap_{S \in F} S}\})$ and \eqref{cond} follows from the linear independence of the columns of $\mathbf{A}_{S}$ and $\mathbf{B}_{\pi(S)}$ for all $S \in F$.
-Now, fix $\ell \in [m]$.
+Since $\varepsilon < L_2(\mathbf{A}) / C_2$, by \eqref{delrho} the right-hand side in \eqref{randoml} is strictly less than one.
+Hence, $\dim(\text{\rm Span}\{\mathbf{B}_{\cap_{S \in F}\pi(S)}\}) \leq \dim(\text{\rm Span}\{\mathbf{A}_{\cap_{S \in F} S}\})$ by \eqref{dimLem}, and \eqref{cond} follows from the linear independence of the columns of $\mathbf{A}_{S}$ and $\mathbf{B}_{\pi(S)}$ for all $S \in F$.
+
+%Now, fix $\ell \in [m]$.
 Since $E$ satisfies the singleton intersection property, $\{\ell\} = \cap F(\ell)$ for the star $F(\ell) \subseteq E$.
@@
 Lem.~\ref{NonEmptyLemma} ensures the latter case is the only possibility.
-Thus, the association $\ell \mapsto \cap_{S \in F(\ell)} \pi(S)$ defines a map $\bar \pi: [m] \to [m]$ and $\dim(\text{\rm Span}\{\mathbf{B}_{\bar \pi(\ell)}\}) = 1$, since $\mathbf{B}_i \neq \textbf{0}$ for all $i$.
-By \eqref{eqdim}, it follows from \eqref{randoml} that $d\left( \text{\rm Span}\{\mathbf{A}_\ell\}, \text{\rm Span}\{ \mathbf{B}_{\bar \pi(\ell)} \} \right) \leq C_2 \varepsilon$.
-Since $\ell$ is arbitrary, fixing $\bar \varepsilon = C_2\delta$ it follows from \eqref{randoml} that for every basis vector $\mathbf{e}_\ell \in \mathbb{R}^m$ there exists some $c'_\ell \in \mathbb{R}$ such that $\|\mathbf{A}\mathbf{e}_\ell - c'_\ell \mathbf{B}\mathbf{e}_{\bar \pi(\ell)}\|_2 \leq \bar \varepsilon < L_2(\mathbf{A})$.
-This is exactly the supposition in \eqref{1D} (letting $c_i = \|\mathbf{A}_i\|_2^{-1}$ for all $i$) and the result follows from the subsequent arguments for the case $k=1$ in Sec.~\ref{DUT}.
+Now, by Lem.~\ref{NonEmptyLemma}, the association $i \mapsto \cap \pi(F(i))$ defines an injective map $\bar \pi: J \to [\bar m]$ for some $J \subseteq [m]$ of size $\bar m - \ell(\bar m - m)$, and we can be sure that $\mathbf{B}_{\bar \pi(i)} \neq \mathbf{0}$ for all $i \in J$ since the columns of $\mathbf{B}_{\pi(S)}$ are linearly independent for all $S \in E$.
+It then follows from \eqref{eqdim} and \eqref{randoml} that $d\left( \text{\rm Span}\{\mathbf{A}_i\}, \text{\rm Span}\{ \mathbf{B}_{\bar \pi(i)} \} \right) \leq C_2 \varepsilon / \max_i \|\mathbf{A}_i\|_2$ for all $i \in J$.
+Fixing $\bar \varepsilon = C_2\varepsilon$ and letting $c_i = \|\mathbf{A}_i\|_2^{-1}$, we thus have that for every basis vector $\mathbf{e}_i \in \mathbb{R}^m$ with $i \in J$ there exists some $c'_i \in \mathbb{R}$ such that $\|c_i\mathbf{A}\mathbf{e}_i - c'_i \mathbf{B}\mathbf{e}_{\bar \pi(i)}\|_2 \leq \bar \varepsilon < L_2(\mathbf{A}) \min_{i\in J} c_i$.
+This is exactly the supposition in \eqref{1D}, and the result follows from the subsequent arguments for the case $k=1$ in Sec.~\ref{DUT} applied to the submatrix $\mathbf{A}_J$.
 \end{proof}

### 2017-04-07 manuscripts/PNAS/chazthm_pnas.tex
chaz SR

@@
 We give conditions guaranteeing when a dictionary of a given size is uniquely and stably determined by data, regardless of the algorithm used to compute it.
-These results provide theoretical grounding for  the application of dictionary learning to recovering sparse signals from unknown noisy compressive measurements.}
+We propose an explanation for universal representation of natural signals in sparse coding models from neuroscience.
+%These results provide theoretical grounding for  the application of dictionary learning to recovering sparse signals from unknown noisy compressive measurements.
+}
 
@@
 If this is the case, add \parshape=0 to the end of the list environment.
-\dropcap{B}lind source identification is a classical problem in signal processing \cite{sato1975method}.  
-One popular modern formulation of the idea is to find a dictionary of $m$ elementary waveforms, at most $k$ of which need be linearly combined to represent each $n$-dimensional signal in a dataset of size $N$, typically where $k < m \ll N$.
-Approximating solutions to this problem have
-provided insight into the structure of many signals lacking explicit analytic structure (see \cite{Zhang15} for a comprehensive review). 
-In particular, it has been shown that response properties of simple-cell neurons in mammalian visual cortex emerge from learning a dictionary for sparse linear coding of natural images \cite{Olshausen96, hurri1996image, bell1997independent, van1998independent}, a major advance in computational neuroscience.
-A fundamental aspect of this finding is that the latent waveforms (``Gabors'') estimated from data appear to be canonical; i.e., they are found in learned dictionaries independent of algorithmic implementation or natural image training set.
+\dropcap{B}lind source separation is a classic inverse problem in signal processing \cite{sato1975method}.
+One constraint commonly imposed is that each of $N$ observed $n$-dimensional signals consists of a linear combination of at most $k$ elementary waveforms drawn from some unknown `dictionary' of size $m$, typically where $k < m \ll N$ (see \cite{Zhang15} for a comprehensive review of this and related models).
+%A popular underlying assumption is that there exists a `dictionary' of $m$ elementary waveforms, at most $k$ of which need be linearly combined to represent each signal in a given dataset of size $N$, typically where $k < m \ll N$.
+Approximate solutions to this problem have provided insight into the structure of many signal classes lacking explicit analytic descriptions [cite?]. 
+In particular, it has been shown that response properties of simple-cell neurons in mammalian visual cortex emerge from the optimization of a dictionary to represent small patches of natural images \cite{Olshausen96, hurri1996image, bell1997independent, van1998independent}, a major advance in computational neuroscience.
+A curious aspect of this finding is that the latent waveforms (``Gabors'') estimated from data appear to be canonical [cite?]; %\cite{donoho2001can}
+i.e., they are found in learned dictionaries independent of algorithmic implementation or natural image training set.
 
@@
 Answers to this question also have other real-world implications.
-For example, a sparse coding analysis of local painting style can be used for forgery detection \cite{hughes2010, Olshausen10}, but only if sparse components of the artwork are independent of implementation idiosyncrasies.
+For example, a sparse coding analysis of local painting style can be used for forgery detection \cite{hughes2010, Olshausen10}, but only if sparse components of the artwork can be consistently estimated.
+% are independent of implementation idiosyncrasies.
 Fortunately, algorithms with proven recovery of generating dictionaries under certain 
-conditions have recently been proposed (see \cite[Sec.~I-E]{Sun16} for a summary of the state-of-the-art).  However, there are few universal theorems explaining the general phenomenon of uniqueness.
+conditions have recently been proposed (see \cite[Sec.~I-E]{Sun16} for a summary of the state-of-the-art). There are few theorems one can cite to explain the general phenomenon of uniqueness, however.
 
-Here, we prove very generally that uniqueness in sparse linear coding is an expected property of the model.
-In other words, whenever enough sparsely represented data generated from a dictionary (satisfying a spark condition) are observed, the original codes and dictionary are uniquely determined up to an error that is commensurate with the measurement noise.
-Applications of this result include:  1) a sufficient diversity of sparse codes sent through a random linear compressive channel are unique, 2) the sparse linear coding problem is well-posed in the sense of Hadamard \cite{Hadamard1902}, and 3) an explanation for universal representation of natural signals in neuroscience.
+Here, we prove very generally that uniqueness and stability in sparse linear coding is an expected property of the model.
+%; that is, it is a well-posed problem (in the sense of Hadamard \cite{Hadamard1902}).
+%In other words, whenever enough sparsely represented data generated from a dictionary (satisfying a spark condition) are observed, the original codes and dictionary are uniquely determined up to an error that is commensurate with the measurement noise.
+More specifically, dictionaries are identifiable from as few as \mbox{$N = m(k-1){m \choose k} + m$} sparse linear combinations of their columns up to an error that is linear in the measurement noise (Thm.~\ref{DeterministicUniquenessTheorem}).
+In fact, provided $n \geq k$, in almost all cases the dictionary learning problem is well-posed (in the sense of Hadamard \cite{Hadamard1902}) given enough data (Cor.~\ref{ProbabilisticCor}).
+Importantly, these guarantees hold without assuming the recovered matrix satisfies a spark condition.
+Our results  also apply when only an upper bound on the number $m$ of dictionary elements is known.
+The explicit, algorithm-independent criteria we provide should be a useful tool in the theory of dictionary learning.
+
+Applications of our results include:  1) a sufficient diversity of sparse codes sent through a random linear compressive channel are identifiable and 2) an explanation for universal representation of natural signals in sparse coding models from neuroscience.
 
@@
 
-Our main technical finding is that a sufficient quantity of measurements generated from any dictionary satisfying the spark condition 
-has a stable sparse representation.
-More specifically, such dictionaries are uniquely identifiable from as few as \mbox{$N = m(k-1){m \choose k} + m$} sparse linear combinations of their columns up to an error that is linear in the measurement noise (Thm.~\ref{DeterministicUniquenessTheorem}).
-In fact, provided $n \geq k$, %$(n, m, k)$ satisfy CS inequality \eqref{CScondition},
-in almost all cases the dictionary learning problem is well-posed given enough data (Cor.~\ref{ProbabilisticCor}).
-Importantly, these guarantees hold without assuming the recovered matrix satisfies the spark condition.
+%Our main technical finding is that a sufficient quantity of measurements generated from any dictionary satisfying the spark condition has a stable sparse representation.
+More specifically, such dictionaries are identifiable from as few as \mbox{$N = m(k-1){m \choose k} + m$} sparse linear combinations of their columns up to an error that is linear in the measurement noise (Thm.~\ref{DeterministicUniquenessTheorem}).
+In fact, provided $n \geq k$, in almost all cases the dictionary learning problem is well-posed (in the sense of Hadamard \cite{Hadamard1902}) given enough data (Cor.~\ref{ProbabilisticCor}).
+Importantly, these guarantees hold without assuming the recovered matrix satisfies a spark condition.
 Our results  also apply when only an upper bound on the number of dictionary elements is known.
-The explicit, algorithm-independent criteria we provide should be a useful tool in the theory of sparse dictionary learning.
+The explicit, algorithm-independent criteria we provide should be a useful tool in the theory of dictionary learning.
 
@@
 We then prove our main theorem (Thm.~\ref{DeterministicUniquenessTheorem}) in Sec.~\ref{DUT} after stating some additional definitions and lemmas required for the proof, including our main tool from combinatorial matrix analysis (Lem.~\ref{MainLemma}).
+We also give a simple argument extending our uniqueness guarantees to the following more common optimization formulation of the sparse linear coding problem (Cor.~\ref{SLCopt}):
+
+\begin{problem}\label{OptimizationProblem}
+Find a matrix $\mathbf{B} \in \mathbb{R}^{\bar m}$ and $k$-sparse $\mathbf{\bar x}_1, \ldots, \mathbf{\bar x}_N \in \mathbb{R}^m$ that solve:
+\begin{align}\label{minsum}
+\min \sum_{i = 1}^N \|\mathbf{\bar x}_i\|_0 \ \ 
+\text{subject to} \ \ \|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\bar x}_i\|_2 \leq \varepsilon, \ \text{for all $i$}.
+\end{align}
+\end{problem}
+
 All other proofs are relegated to the Supplemental. 
@@
 
-There are other less direct consequences of Thm.~\ref{DeterministicUniquenessTheorem} to stability in sparse linear coding.
-The following implication relates the result to more common optimization formulations.
+There are other less direct consequences of Thm.~\ref{DeterministicUniquenessTheorem} to stability in sparse linear coding. Consider the optimization problem posed in Prob.~\ref{SLCopt}.
 
 \begin{corollary}\label{SLCopt}
-If the assumptions of Thm.\ref{DeterministicUniquenessTheorem} hold with more than $(k-1)\left[ {\bar m \choose k} + |E|k{\bar m \choose k-1}\right]$ vectors $\mathbf{x}_i$ supported on each $S \in E$, then all matrices $\mathbf{B} \in \mathbb{R}^{n \times \bar m}$ and $\mathbf{\bar x}_1, \ldots, \mathbf{\bar x}_N \in \mathbb{R}^{\bar m}$ solving:
-\begin{align}\label{minsum}
-\min \sum_{i = 1}^N \|\mathbf{\bar x}_i\|_0 \ \ 
-\text{subject to} \ \ \|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\bar x}_i\|_2 \leq \varepsilon, \ \text{for all $i$},
-\end{align}
+If the assumptions of Thm.\ref{DeterministicUniquenessTheorem} hold with more than $(k-1)\left[ {\bar m \choose k} + |E|k{\bar m \choose k-1}\right]$ vectors $\mathbf{x}_i$ supported on each $S \in E$, then all solutions to Prob.~\ref{OptimizationProblem} necessarily satisfy implications 1) and 2) from Thm.~\ref{DeterministicUniquenessTheorem}.
+\end{corollary}
+%\begin{corollary}\label{SLCopt}
+%If the assumptions of Thm.\ref{DeterministicUniquenessTheorem} hold with more than $(k-1)\left[ {\bar m \choose k} + |E|k{\bar m \choose k-1}\right]$ vectors $\mathbf{x}_i$ supported on each $S \in E$, then all matrices $\mathbf{B} \in \mathbb{R}^{n \times \bar m}$ and $\mathbf{\bar x}_1, \ldots, \mathbf{\bar x}_N \in \mathbb{R}^{\bar m}$ solving:
+%\begin{align}\label{minsum}
+%\min \sum_{i = 1}^N \|\mathbf{\bar x}_i\|_0 \ \ 
+%\text{subject to} \ \ \|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\bar x}_i\|_2 \leq \varepsilon, \ \text{for all $i$},
+%\end{align}
 %
-necessarily satisfy implications 1) and 2) from Thm.~\ref{DeterministicUniquenessTheorem}.
+%necessarily satisfy implications 1) and 2) from Thm.~\ref{DeterministicUniquenessTheorem}.
+
 %must have $\bar m \geq m$ and, provided $p = \bar m - \ell(\bar m - m) > 0$, necessarily satisfy \eqref{Cstable}
@@
 %for some $J \in {[m] \choose p}$, $\bar J \in {[\bar m] \choose p}$, permutation matrix $\mathbf{P}$, and invertible diagonal matrix $\mathbf{D}$.
-\end{corollary}
+%\end{corollary}
 
@@
 
-\section{Proof of Theorem~\ref{DeterministicUniquenessTheorem} and Corollary~\ref{SLCopt}}\label{DUT}
+\section{Proofs of Theorem~\ref{DeterministicUniquenessTheorem} and Corollary~\ref{SLCopt}}\label{DUT}
 
@@
 
-In this note, we generalize the approach of \cite{Hillar15} to prove uniqueness in Prob.~\ref{InverseProblem} for the case of noisy measurements while also reducing the sufficient number of samples.
+In this note, we generalize the approach of \cite{Hillar15} to prove the stability of unique solutions to Probs.~\ref{InverseProblem} and \ref{OptimizationProblem} while also significantly reducing the known sample complexity.
 % FRITZ: Inverse problems instead of Data Analysis.
@@
 Focus on them (probabilistic ones too).
-Our results provide theoretical grounding for the use of sparse linear coding in blind source separation, wherein the goal is to infer the generating dictionary and sparse codes from noisy measurements, \eqref{LinearModel}.
+Our results provide theoretical support to the application of the sparse linear coding model to blind source separation problems, wherein the goal is to infer the generating dictionary and sparse codes from noisy measurements, \eqref{LinearModel}.
 We also collect a set of useful mathematical tools and basic facts for future research.
-The main motivation for this work, however, was to understand how seemingly universal and stable representations are discovered by training a sparse linear coding model on natural data, independent of specific algorithmic implementation.
+The main motivation for this work, however, was to understand how seemingly universal and stable representations emerge from sparse coding models fit to natural data by a variety of methodologies.
 We elaborate more on these applications below after discussing theoretical aspects.
@@
 
-What we have shown here is that as an inverse problem to be approximated by a numerical algorithm, the sparse linear coding model  generally produces \textit{well-posed} optimizations.
-This early concept of Hadamard \cite{Hadamard1902} can be paraphrased as the idea that good parameterized models should pose optimization problems with solutions that are \textit{stable}; that is, continuous in the data.
-In other words, perturbing a dataset by a small amount should only slightly influence the identifiability or uniqueness of parameters in the model, rather than discontinuously affect the character of optimization involved.
-In this regard, we demonstrate a linear relationship, \eqref{epsdel}, between noise in the data and the unique solution in  sparse linear coding, with explicit constants expressed in terms of original latent parameters.
-Nonetheless, it would be of practical utility to determine the best possible dependence of $\varepsilon$ on $\delta_1, \delta_2$ in Def.\ref{maindef} as well as the minimal requirements on the number and diversity of generating codes, and we hope that other researchers continue to improve and extend our results.
-% , although they are too computationally expensive to be of practical value.  We hope .
+What we have shown here is that the sparse linear coding model generally produces a \textit{well-posed} inverse problem to be approximately solved by a numerical algorithm.
+This early concept of Hadamard \cite{Hadamard1902} can be paraphrased as the idea that inferences from observations should be robust to the inevitable uncertainty in measurement; that is, continuous in the data.
+In other words, perturbing a dataset by a small amount should only slightly influence the inferred parameters.
+In this regard, for the sparse linear coding model we demonstrate a linear relationship, \eqref{epsdel}, between measurement noise and the deviation of any solution from the true parameters, with explicit constants expressed in terms of these parameters.
+Moreover, we show that even if the meta-parameter defining the number of dictionary elements is overestimated, a subset of parameters are still identifiable.
+It would be of practical utility to determine the best possible dependence of $\varepsilon$ on $\delta_1, \delta_2$ in Def.\ref{maindef} as well as the minimal requirements on the number and diversity of generating codes, and we hope that other researchers continue to improve and extend our results.
 
-One notable component of our contribution is a combinatorial criteria (regular hypergraphs satisfying the singular intersection property, Def.~\ref{sip}) for choosing support sets for original sparse codes.
-Fully understanding those combinatorial designs allowing for stable representations of datasets is an interesting research area for the future.
-For instance, whether there is a support set size $N$ that is polynomial in $m,k$ gauanteeing the conclusions of Thm.~\ref{DeterministicUniquenessTheorem} has implications for the computational complexity of Prob.\ref{InverseProblem} and related questions \cite{Tillmann15}.
+%We note also that these results extend trivially to cases where point-wise injective nonlinearities are applied to the data.
+
+One notable component of our contribution is a combinatorial criteria (regular hypergraphs satisfying the singular intersection property, Def.~\ref{sip}) for the support sets of sparse codes key to the identification of the dictionary.
+Fully understanding those combinatorial designs allowing for stable sparse representations is an interesting research area for the future.
+For instance, whether there is a support set size $N$ that is polynomial in $m,k$ gauranteeing the conclusions of Thm.~\ref{DeterministicUniquenessTheorem} has implications for the computational complexity of Probs.~\ref{InverseProblem} and \ref{OptimizationProblem} and related questions \cite{Tillmann15}.
 We also remark that our main uniqueness result accounts for deterministic ``worst-case'' noise, whereas the ``effective'' noise might be much smaller when it is sampled from a given distribution; in such cases, the constants  %Thms.~\ref{DeterministicUniquenessTheorem},~\ref{DeterministicUniquenessTheorem2}
-will improve. %We note also that these results extend trivially to cases where point-wise injective nonlinearities are applied to the data.
+will improve.
 
-A technical difficulty in our main theorem is the absence of a spark condition assumption on alternate sparse data factorizations.
+A technical difficulty in proving Thm.~\ref{DeterministicUniquenessTheorem} was the absence of a spark condition assumption on solutions to Prob.~\ref{InverseProblem}.
 Although mathematically interesting that no such requirement is necessary, there are other reasons to seek out such a theoretical guarantee.
-For instance, it is difficult to ensure an algorithm maintain a dictionary satisfying \eqref{SparkCondition} at each learning stage; indeed, even certifying  a dictionary has this property is likely intractable given its NP-hardness \cite{tillmann2014computational}.
+For instance, it is difficult to ensure that an algorithm maintain a dictionary satisfying \eqref{SparkCondition} at each iteration; indeed, even certifying a dictionary has this property is likely intractable given its NP-hardness \cite{tillmann2014computational}.
 

### 2017-04-07 manuscripts/PNAS/chazthm_pnas.tex
edits put in lem 4 proof

@@
 We give conditions guaranteeing when a dictionary of a given size is uniquely and stably determined by data, regardless of the algorithm used to compute it.
-We propose an explanation for universal representation of natural signals in sparse coding models from neuroscience.
+The result provides an explanation for universal representation of natural signals from sparse coding models.
 %These results provide theoretical grounding for  the application of dictionary learning to recovering sparse signals from unknown noisy compressive measurements.
@@
 If this is the case, add \parshape=0 to the end of the list environment.
-\dropcap{B}lind source separation is a classic inverse problem in signal processing \cite{sato1975method}.
-One constraint commonly imposed is that each of $N$ observed $n$-dimensional signals consists of a linear combination of at most $k$ elementary waveforms drawn from some unknown `dictionary' of size $m$, typically where $k < m \ll N$ (see \cite{Zhang15} for a comprehensive review of this and related models).
+\dropcap{B}lind source separation is a classical inverse problem in signal processing \cite{sato1975method}.
+One constraint commonly imposed is that each of $N$ observed $n$-dimensional signals are a linear combination of at most $k$ elementary waveforms drawn from some unknown ``dictionary'' of size $m$, typically where $k < m \ll N$ (see \cite{Zhang15} for a comprehensive review of this and related models).
 %A popular underlying assumption is that there exists a `dictionary' of $m$ elementary waveforms, at most $k$ of which need be linearly combined to represent each signal in a given dataset of size $N$, typically where $k < m \ll N$.
-Approximate solutions to this problem have provided insight into the structure of many signal classes lacking explicit analytic descriptions [cite?]. 
-In particular, it has been shown that response properties of simple-cell neurons in mammalian visual cortex emerge from the optimization of a dictionary to represent small patches of natural images \cite{Olshausen96, hurri1996image, bell1997independent, van1998independent}, a major advance in computational neuroscience.
-A curious aspect of this finding is that the latent waveforms (``Gabors'') estimated from data appear to be canonical [cite?]; %\cite{donoho2001can}
+Approximating solutions to this sparsity-constrained inverse problem have provided insight into the structure of many signal classes lacking explicit descriptions (e.g., in vision \cite{wang2015sparse}).
+In particular, it has been shown that response properties of simple-cell neurons in mammalian visual cortex emerge from optimizing a dictionary to represent small patches of natural images \cite{Olshausen96, hurri1996image, bell1997independent, van1998independent}, a major advance in computational neuroscience.
+A curious aspect of this finding is that the latent waveforms (``Gabors'') estimated from data appear to be canonical \cite{donoho2001can};
 i.e., they are found in learned dictionaries independent of algorithmic implementation or natural image training set.
@@
 Answers to this question also have other real-world implications.
-For example, a sparse coding analysis of local painting style can be used for forgery detection \cite{hughes2010, Olshausen10}, but only if sparse components of the artwork can be consistently estimated.
+For example, a sparse coding analysis of local painting style can be used for forgery detection \cite{hughes2010, Olshausen10}, but only if the identifying sparse components of the artwork can be consistently estimated.
 % are independent of implementation idiosyncrasies.
 Fortunately, algorithms with proven recovery of generating dictionaries under certain 
-conditions have recently been proposed (see \cite[Sec.~I-E]{Sun16} for a summary of the state-of-the-art). There are few theorems one can cite to explain the general phenomenon of uniqueness, however.
+conditions have recently been proposed (see \cite[Sec.~I-E]{Sun16} for a summary of the state-of-the-art).
+However, there are few theorems in the literature explaining this general phenomenon of uniqueness.
 
@@
 
-Applications of our results include:  1) a sufficient diversity of sparse codes sent through a random linear compressive channel are identifiable and 2) an explanation for universal representation of natural signals in sparse coding models from neuroscience.
+Direct applications include: 1) a sufficient diversity of sparse codes sent through a random linear compressive channel are identifiable and 2) an explanation for universal representation of natural signals in sparse coding models from neuroscience.
 
@@
 We then prove our main theorem (Thm.~\ref{DeterministicUniquenessTheorem}) in Sec.~\ref{DUT} after stating some additional definitions and lemmas required for the proof, including our main tool from combinatorial matrix analysis (Lem.~\ref{MainLemma}).
-We also give a simple argument extending our uniqueness guarantees to the following more common optimization formulation of the sparse linear coding problem (Cor.~\ref{SLCopt}):
+We also give a simple argument extending our uniqueness guarantees to the following more common optimization formulation of the sparse linear coding problem (Cor.~\ref{SLCopt}).
 
 \begin{problem}\label{OptimizationProblem}
-Find a matrix $\mathbf{B} \in \mathbb{R}^{\bar m}$ and $k$-sparse $\mathbf{\bar x}_1, \ldots, \mathbf{\bar x}_N \in \mathbb{R}^m$ that solve:
+Find a matrix $\mathbf{B} \in \mathbb{R}^{\bar m}$ and $k$-sparse $\mathbf{\bar x}_1, \ldots, \mathbf{\bar x}_N \in \mathbb{R}^{\bar m}$ that solve:
 \begin{align}\label{minsum}
@@
 
-There are other less direct consequences of Thm.~\ref{DeterministicUniquenessTheorem} to stability in sparse linear coding. Consider the optimization problem posed in Prob.~\ref{SLCopt}.
+There are other less direct consequences of Thm.~\ref{DeterministicUniquenessTheorem} to stability in sparse linear coding.
+For instance, consider its implications for the optimization problem posed in Prob.~\ref{SLCopt}.
 
@@
 
-Another straightforward application of Thm.~\ref{DeterministicUniquenessTheorem} is a probabilistic extension made possible by noticing that the spark condition can in fact be made explicit.
+Another straightforward application of Thm.~\ref{DeterministicUniquenessTheorem} is a probabilistic extension made possible by noticing that the spark condition has an analytic characterization.
 Let $\mathbf{A}$  be the $n \times m$ matrix of $nm$ indeterminates $A_{ij}$.
@@
 
-Since $f$ is a real analytic function, having one substitution of real numbers with $f(\mathbf{A}) \neq 0$ implies that its zeroes form a set of (Borel) measure zero.
-Fortunately, it is easy to construct such a matrix $\mathbf{A}$ by inserting $n-k$ rows of zeros into a $k \times m$ ``Vandermonde" matrix construction.
+Since $f$ is an analytic function, having one substitution of real numbers with $f(\mathbf{A}) \neq 0$ implies that its zeroes form a set of measure zero.
+Fortunately, such a matrix $\mathbf{A}$ is easily constructed by adding rows of zeroes to any $k \times m$ ``Vandermonde'' matrix $[\gamma_i^j]_{i,j=1}^{k,m}$ with distinct $\gamma_i$ (so that each term in the product above is nonzero).
+%$A_{ij} = \gamma_i (since the $\gamma_i$ are distinct, any $k \times k$ ``Vandermonde'' sub-determinant is nonzero)
+%inserting $n-k$ rows of zeros into a $k \times m$ ``Vandermonde" matrix construction.
 %Let $\gamma_1, \ldots, \gamma_m$ be any distinct numbers.
@@
 Hence, almost every real matrix $\mathbf{A}$ with at least $k$ rows and columns satisfies \eqref{SparkCondition}.
-%\eqref{CScondition} holds with a $\gamma$ for some distribution.
-We set $\gamma_0$ to be the smallest known such $\gamma$.
-% We remark that the precise relationship between $m$, $n$, and $k$ guaranteeing that $f$ is not identically zero is a challenging problem in real algebraic geometry.
-In any case, we set $\gamma_0$ to be the smallest known such $\gamma$.
 
@@
 
-\begin{theorem}\label{robustPolythm} %label is fucking up formatting..???
-%Fix $n, m$, and $k < m$. 
-There is a polynomial in the entries of $\mathbf{A}$ and the $\mathbf{x}_i$ with the following property:  if the polynomial evaluates to a nonzero number and more than \mbox{$(k-1){m \choose k}$} of the resulting vectors $\mathbf{x}_i$ are supported on each $S \in E$ for some regular $E \subseteq {[m] \choose k}$ with the SIP, then $Y$ has a stable $k$-sparse representation in $m$ dimensions (Def.~\ref{maindef}).
-In particular, either no substitutions impart to $Y$ this property or all but a Borel set of measure zero do.
+\begin{theorem}\label{robustPolythm}
+There is a polynomial in the entries of $\mathbf{A}$ and $\mathbf{x}_i$ with the following property:  if the polynomial evaluates to a nonzero number and more than \mbox{$(k-1){m \choose k}$} of the resulting $\mathbf{x}_i$ are supported on each $S \in E$ for some regular $E \subseteq {[m] \choose k}$ with the SIP, then $Y$ has a stable $k$-sparse representation in $m$ dimensions (Def.~\ref{maindef}).
+In particular, no substitutions impart to $Y$ this property or all but a Borel set of measure zero do.
 \end{theorem}
-
-% this is cool, but let's just save it for later...i can ask around.  -cjh
-%An interesting open question in real algebraic geometry is which collections of $(m,n,k)$ determine this last ``or".
 
@@
 
-Our first step is to show how dictionary recovery \eqref{Cstable} already implies sparse code recovery \eqref{b-PDa} when $\varepsilon < L_{2k}(\mathbf{A}) / C_1$.
-For all $2k$-sparse $\mathbf{x} \in \mathbb{R}^m$, the triangle inequality gives \mbox{$\|(\mathbf{A}-\mathbf{BPD})\mathbf{x}\|_2  \leq C_1\varepsilon \|\mathbf{x}\|_1 \leq C_1 \varepsilon \sqrt{2k}  \|\mathbf{x}\|_2$}.
+Our first step is to show how dictionary recovery \eqref{Cstable} already implies sparse code recovery \eqref{b-PDa} when \mbox{$\varepsilon < L_{2k}(\mathbf{A}) / C_1$}.
+For $2k$-sparse $\mathbf{x} \in \mathbb{R}^m$, the triangle inequality gives \mbox{$\|(\mathbf{A}-\mathbf{BPD})\mathbf{x}\|_2  \leq C_1\varepsilon \|\mathbf{x}\|_1 \leq C_1 \varepsilon \sqrt{2k}  \|\mathbf{x}\|_2$}.
 Thus,
@@
 
-We note the following facts about $d$. For subspaces $U,V \subseteq \mathbb{R}^m$, we have \cite[Cor.~2.6]{Kato2013}:
+We note the following facts about $d$. For subspaces $U \subseteq U', V \subseteq \mathbb{R}^m$, we have $d(U,V) \leq d(U',V)$ and \cite[Cor.~2.6]{Kato2013}:
 \begin{align}\label{dimLem}
-d(U,V) < 1 \implies \dim(U) \leq \dim(V),
+d(U,V) < 1 \implies \dim(U) \leq \dim(V).
 \end{align}
-%
-and \cite[Lem.~3.2]{Morris10}:
+Also, from \cite[Lem.~3.2]{Morris10}, we have:
 \begin{align}\label{eqdim}
@@
 \begin{proof}
-We first show that $\bar m \geq m$.
+Let $T_1 = \{(i, S): i \in \pi(S), S \in E\}$.
+Then, $|T_1| = \sum_{S \in E} |\pi(S)| = \sum_{S \in E} |S| = \ell m$ by regularity of $E$.
+Thus, $|T_1| > \bar m (\ell -1) + (p-1) > \bar m (\ell -1)$.
+Using the pigeonhole property, it follows that there are at least $\ell$ elements of $T_1$ sharing the same first coordinate.
+Let $F_1$ be the preimage of this family under $\pi$.
+By the assumption \eqref{cond}, the intersection of $F_1$ is nonempty, and in fact must contain exactly $\ell$ elements.
+Thus, $F_1$ is the star of some element $i_1 \in [m]$.
+From the SIP, the intersection of sets in $F_1$ is $\{i_1\}$, which by \eqref{cond} implies that the intersection of $\pi(S)$ with $S \in F_1$ also contains exactly one element.
+Set $T_2 = T_1 \setminus \{(i,S) \in T_1: i = i_1\}$, which contains at least $(\bar m - 1)(\ell -1)$ sets.
+Iterating this argument $p = \bar{m} - \ell(\bar m - m)$ times produces the conclusion in the lemma with $J = \{i_1, \ldots, i_p\}$.
+%We first show that $\bar m \geq m$.
 Fix $T = \{(j, S): j \in \pi(S), S \in E\}$.
@@
 Hence $\bar m \geq m$.
-Again, pigeonholing the elements of $T$ with respect to the set $[\bar m]$ of possible first indices, we see that for each $j$ there must be exactly $\ell$ elements of $T$ with $j$ as a first index; hence, $\pi(E)$ is $\ell$-regular.
-Fix $j$ and let $F(j) = \{S \in E: j \in \pi(S)\}$ be the preimage of the star in $\pi(E)$ centered at $j$, which is of size $\ell$ by the above arguments.
+%Again, pigeonholing the elements of $T$ with respect to the set $[\bar m]$ of possible first indices, we see that for each $j$ there must be exactly $\ell$ elements of $T$ with $j$ as a first index; hence, $\pi(E)$ is $\ell$-regular.
+%Fix $j$ and let $F(j) = \{S \in E: j \in \pi(S)\}$ be the preimage of the star in $\pi(E)$ centered at $j$, which is of size $\ell$ by the above arguments.
 It follows from \eqref{cond} that $\cap_{S \in F(j)} S$ is nonempty.
@@
 
-\begin{proof}[Proof of Main Lemma]
+\begin{proof}[Proof of Lem.\ref{MainLemma}]
 We begin by showing that: 
@@
 
-We will now show that \eqref{cond} holds.
+We next verify \eqref{cond} holds.
 %\begin{align}\label{fact2}
@@
 
-\begin{proof}[Proof of Thm.~\ref{robustPolythm}]
+\begin{proof}[Proof (sketch) of Thm.~\ref{robustPolythm}]
 % We sketch the argument, leaving the details to the reader. 
-Let $M$ be the matrix with columns $\mathbf{A}\mathbf{x}_i$, $i \in [N]$.  Consider the polynomial \cite[Sec.~IV]{Hillar15} in the entries of $\mathbf{A}$ and $\mathbf{x}_i$:
+Let $M$ be the matrix with columns $\mathbf{A}\mathbf{x}_i$, $i \in [N]$.  Consider the polynomial in the entries of $\mathbf{A}$ and $\mathbf{x}_i$:
 \begin{align*}
-g(\mathbf{A}, \{\mathbf{x}_i\}_{i=1}^N) = \prod_{S \in {[n] \choose k}} \sum_{S' \in {[N] \choose k}} (\det M_{S',S})^2,
+g(\mathbf{A}, \{\mathbf{x}_i\}_{i=1}^N) := \prod_{S \in {[n] \choose k}} \sum_{S' \in {[N] \choose k}} (\det M_{S',S})^2,
 \end{align*}

### 2017-04-07 manuscripts/PNAS/chazthm_pnas.tex
elaborated

--- 2017-04-07 manuscripts/PNAS/chazthm_pnas.tex
@@
 \begin{corollary}\label{SLCopt}
-If the assumptions of Thm.\ref{DeterministicUniquenessTheorem} hold with more than $(k-1)\left[ {\bar m \choose k} + |E|k{\bar m \choose k-1}\right]$ vectors $\mathbf{x}_i$ supported on each $S \in E$, then all solutions to Prob.~\ref{OptimizationProblem} necessarily satisfy implications 1) and 2) from Thm.~\ref{DeterministicUniquenessTheorem}.
+If the assumptions of Thm.\ref{DeterministicUniquenessTheorem} hold with more than $(k-1)\left[ {\bar m \choose k} + |E|k{m \choose k-1}\right]$ vectors $\mathbf{x}_i$ supported on each $S \in E$, then all solutions to Prob.~\ref{OptimizationProblem} necessarily satisfy implications 1) and 2) from Thm.~\ref{DeterministicUniquenessTheorem}.
 \end{corollary}
@@
 Since $f$ is a real analytic function, having one substitution of real numbers with $f(\mathbf{A}) \neq 0$ implies that its zeroes form a set of (Borel) measure zero.
-Fortunately, it is easy to construct such a matrix $\mathbf{A}$ by inserting $n-k$ rows of zeros into a $k \times m$ ``Vandermonde" matrix construction.
+Fortunately, it is easy to construct such an $n \times m$ matrix $\mathbf{A}$ for any $n \geq \max(2k,m)$ by inserting enough rows of zeros into a $\max(2k, m) \times m$ ``Vandermonde" matrix construction.
 %Let $\gamma_1, \ldots, \gamma_m$ be any distinct numbers.
@@
 with $f(\mathbf{A}) = 0$.
-Hence, almost every real matrix $\mathbf{A}$ with at least $k$ rows and columns satisfies \eqref{SparkCondition}.
+Hence, almost every real $n \times m$ matrix $\mathbf{A}$ with $n \geq \max(2k,m)$ satisfies \eqref{SparkCondition}.
 %\eqref{CScondition} holds with a $\gamma$ for some distribution.
@@
 \begin{corollary}\label{ProbabilisticCor}
-Fix $n, m$ and $k$ such that $n \geq k < m$ % satisfying \eqref{CScondition} for $\gamma = \gamma_0$, 
+Fix $k < m$ and $n \geq \max(2k, m)$ % satisfying \eqref{CScondition} for $\gamma = \gamma_0$, 
 and let the entries of $\mathbf{A} \in \mathbb{R}^{n \times m}$ and $k$-sparse $\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$ be drawn independently from probability measures absolutely continuous with respect to the standard Borel measure $\mu$.
@@
 %\begin{align}
-\mbox{$k \sum_{p = 0}^{m} n_p \geq \sum_{i=0}^N \|\mathbf{x}_i\|_0 \geq \sum_{i=0}^N \|\mathbf{\bar x}_i\|_0 = \sum_{p=0}^{m} p n_p.$}
+\mbox{$k \sum_{p = 0}^{\bar m} n_p \geq \sum_{i=0}^N \|\mathbf{x}_i\|_0 \geq \sum_{i=0}^N \|\mathbf{\bar x}_i\|_0 = \sum_{p=0}^{\bar m} p n_p.$}
 %\end{align}
@@
 \begin{align}\label{eqn}
-\sum_{p = k+1}^m n_p \leq \sum_{p = k+1}^m (p-k) n_p \leq \sum_{p = 0}^k (k-p)n_p \leq k \sum_{p = 0}^{k-1} n_p.
+\sum_{p = k+1}^{\bar m} n_p \leq \sum_{p = k+1}^{\bar m} (p-k) n_p \leq \sum_{p = 0}^k (k-p)n_p \leq k \sum_{p = 0}^{k-1} n_p.
 \end{align}
@@
 
-Hence, the number of $(k-1)$-sparse vectors $\mathbf{\bar x}_i$ is no greater than $|E|(k-1){ m \choose k-1}$.
-Taking \eqref{eqn} into account, it follows that at least $N - |E|k(k-1){ m \choose k-1}$ of the vectors $\mathbf{\bar  x}_i$ are $k$-sparse.
-Therefore, more than $(k-1){m \choose k}$ of the vectors $\mathbf{x}_i$ supported on each $S \in E$ have corresponding $\mathbf{\bar x}_i$ that are also $k$-sparse.
+Hence, the total number of $(k-1)$-sparse vectors $\mathbf{\bar x}_i$ is no greater than $|E|(k-1){ m \choose k-1}$.
+Taking \eqref{eqn} into account, no more than $|E|k(k-1){ m \choose k-1}$ vectors $\mathbf{\bar x}_i$ are \emph{not} $k$-sparse.
+Since for every $S \in E$ there are over $(k-1)\left[ {\bar m \choose k} + |E|k{ m \choose k-1} \right]$ vectors $\mathbf{x}_i$ supported there, it follows that more than $(k-1){\bar m \choose k}$ of them must have corresponding $\mathbf{\bar x}_i$ that are also $k$-sparse.
 The result now follows directly from Thm.~\ref{DeterministicUniquenessCorollary}.

### 2017-04-08 manuscripts/PNAS/chazthm_pnas.tex
SR complete

@@
 By the argument as in the proof of Thm.\ref{DeterministicUniquenessTheorem}, we also have \eqref{rhs222}.
-Since our bound on $\varepsilon$ implies that the right-hand side of \eqref{rhs222} is less than one, by \eqref{dimLem}: \[k = \dim(\text{Span}(\mathbf{A}_S)) \leq \dim(\text{Span}\{\mathbf{B}_{\bar S}\}) \leq |\bar S|,\] a contradiction.
+Since our bound on $\varepsilon$ implies that the right-hand side of \eqref{rhs222} is less than one, by \eqref{dimLem} we have the contradiction: \[k = \dim(\text{Span}(\mathbf{A}_S)) \leq \dim(\text{Span}\{\mathbf{B}_{\bar S}\}) \leq |\bar S|.\]
 
@@
 For instance, whether there is a support set size $N$ that is polynomial in $m,k$ gauranteeing the conclusions of Thm.~\ref{DeterministicUniquenessTheorem} has implications for the computational complexity of Probs.~\ref{InverseProblem} and \ref{OptimizationProblem} and related questions \cite{Tillmann15}.
-We also remark that our main uniqueness result accounts for deterministic ``worst-case'' noise, whereas the ``effective'' noise might be much smaller when it is sampled from a given distribution; in such cases, the constants  %Thms.~\ref{DeterministicUniquenessTheorem},~\ref{DeterministicUniquenessTheorem2}
+We also remark that our uniqueness result accounts for deterministic ``worst-case'' noise, whereas the ``effective'' noise might be smaller when sampled from a distribution; in such cases, the constants  %Thms.~\ref{DeterministicUniquenessTheorem},~\ref{DeterministicUniquenessTheorem2}
 will improve.
@@
 Our results suggest that this correspondence could be due to  sparse representations being ``universal'' in natural data, an early mathematical idea in neural theory \cite{pitts1947}.
-Furthermore, our guarantees justify the hypothesis of \cite{Coulter10, Isely10} that sparse codes passed through a communication bottleneck in the brain are recovered from random projections via (unsupervised) biologically plausible sparse dictionary learning (e.g., \cite{rehnsommer2007, rozell2007neurally, hu2014hebbian}).
+Furthermore, our guarantees justify the hypothesis of \cite{Coulter10, Isely10} that sparse codes passed through a communication bottleneck in the brain are recovered from random projections via (unsupervised) biologically plausible sparse coding (e.g., \cite{rehnsommer2007, rozell2007neurally, hu2014hebbian}).
 
-%In fact, the concept of ``universal'' objects in the brain is .
+% \small{\small{\textbf{ACKNOWLEDGMENTS.}}} We thank Friedrich Sommer and Darren Rhea for early thoughts, and Ian Morris for \eqref{eqdim}.
 
-%But this is also in data science applications.
-For instance, when recovering a rat's position on a linear track from learning a sparse linear model on  local field potentials in Hippocampus \cite{Agarwal14}.
-
-%TODO: add reproduction of response propeties in olfactory cortex?
-
-% Reiterate probabilistic result in the smooth analysis part?
-%\textbf{Smoothed Analysis}.
-%The main concept in smoothed analysis \cite{Spielman04} is that certain algorithms having exponential worst-case behavior are, nonetheless, efficient if certain (typically, measure zero in the continuous case and with ``low probability" in the discrete case) pathological input sets are avoided.
-Our results imply that if there is an efficient ``smoothed" algorithm for solving Prob.~\ref{InverseProblem} given enough samples, then for generic inputs this algorithm determines the unique original solution.
-We note that avoiding certain pathological sets of inputs is often a necessary technicality for dictionary learning \cite{Razaviyayn15, Tillmann15}.
-
-%\textbf{Engineering}.
-
-\acknow{We thank Friedrich Sommer for introducing us to sparse dictionary learning, Darren Rhea for sharing early explorations, and Ian Morris for posting \eqref{eqdim} online.}
-
+% This breaks:  Proof of Main Lemma 1 somehow appears earlier than it should be....weird
+\acknow{We thank Friedrich Sommer and Darren Rhea for early thoughts, and Ian Morris for posting \eqref{eqdim} online.}
  \showacknow % Display the acknowledgments section
 
-% \pnasbreak % splits and balances the columns before the references.
-% If you see unexpected formatting errors, try commenting out this line
-% as it can run into problems with floats and footnotes on the final page.
-%\pnasbreak %was causing only first two pages to print..??
-
-% Bibliography
 \bibliography{chazthm_pnas}
-
-%% SUPPLEMENTAL INFO? %%%
-%\begin{remark}
-%Actually, $\mathbf{A}$ need not be injective on all $k$-sparse vectors for Theorem \ref{DeterministicUniquenessTheorem} to hold; rather, it need only be injective the set of all vectors with supports in $E$.
-[** TODO ** we will probably have to redefine $L_2$ since it is over all $k$-sparse vectors -- may have to instead define $L_E$.] Wait, $E$ need not be regular for $B$ sat.
-spark cond.
-Also it need not be $k$-regular!
-%\end{remark}
 
@@
 
-% This can be made tighter by using Pythagoras' Thm for first projection instead of triangle inequality. 
 \begin{lemma}\label{DistanceToIntersectionLemma}
@@
 Recall that orthogonal projection onto a subspace $V \subseteq \mathbb{R}^m$ is the mapping $\Pi_V: \mathbb{R}^m \to V$ that associates with each $\mathbf{x}$ its unique nearest point in $V$; i.e., $\|\mathbf{x} - \Pi_V\mathbf{x}\|_2 = \text{\rm dist}(\mathbf{x}, V)$.
-% Since subspaces of real vector spaces are closed, we can replace inf with min in def. of orthogonal projection
 Next, observe:
-%Use Pythagoras' Theorem first?
 \begin{align}\label{f}
@@
 \end{align}
-%
 using the triangle inequality and that the spectral norm satisfies $\|\Pi_{V_{\ell}}\|_2 \leq 1$ for all $\ell$ (since $\Pi_{V_{\ell}}$ are orthogonal projections).
@@
 \begin{align}
-\|\Pi_{V_k}\Pi_{V_{k-1}}\cdots\Pi_{V_1} \mathbf{x} - \Pi_V\mathbf{x}\|_2 \leq z \|\mathbf{x}\|_2, %  \ \ \  \text{for } \mathbf{x} \in \mathbb{R}^m,
+\|\Pi_{V_k}\Pi_{V_{k-1}}\cdots\Pi_{V_1} \mathbf{x} - \Pi_V\mathbf{x}\|_2 \leq z \|\mathbf{x}\|_2,
 \end{align}
@@
 Finally, substituting this into \eqref{f} and rearranging produces \eqref{DTILeq} after replacing $1 - z$ with $r(\{V_i\}_{i=1}^k)$.
-% ($z$ may depend on the ordering).
 \end{proof}
@@
 \end{align}
-%
 then $\bar m \geq m$ and the association $i \mapsto \cap \pi(F(i))$ defines an injective map from $J$ to $[\bar m]$ for some $J \subseteq [m]$ of size $\bar m - \ell(\bar m - m)$.
 In particular, if $\bar m = m$ then the map $\pi$ is induced by a permutation.
-%$\pi(E)$ is $\ell$-regular and satisfies the singleton intersection property. In particular, $|\cap_{S \in F} S| = 1$ if and only if $|\cap_{S \in F} \pi(S)| = 1$. 
 \end{lemma}
+
 \begin{proof}
-Let $T_1 = \{(i, S): i \in \pi(S), S \in E\}$.
-Then, $|T_1| = \sum_{S \in E} |\pi(S)| = \sum_{S \in E} |S| = \ell m$ by regularity of $E$.
-Thus, $|T_1| > \bar m (\ell -1) + (p-1) > \bar m (\ell -1)$.
-Using the pigeonhole property, it follows that there are at least $\ell$ elements of $T_1$ sharing the same first coordinate.
+Consider the collection of pairs: \[T_1 = \{(i, S): i \in \pi(S), S \in E\},\] which number $|T_1| = \sum_{S \in E} |\pi(S)| = \sum_{S \in E} |S| = \ell m$ by regularity of $E$.  
+We first show that $\bar m \geq m$.
+Otherwise, if $\bar m < m$, then by pigeonholing the $m \ell \geq \ell (\bar m + 1) \geq [(\ell + 1) - 1] \bar m + 1$ elements of $T_1$ with respect to the set $[\bar m]$ of possible first indices, we see that there must exist at least $\ell + 1$ elements of $T_1$ having the same first index.
+But by \eqref{cond} there can be no more than $\ell$ elements of $T_1$ with a given first index, since $E$ is $\ell$-regular.
+Hence $\bar m \geq m$.
+
+Next, since \[|T_1| > \bar m (\ell -1) + (p-1) > \bar m (\ell -1),\] the pigeonhole principle also implies that there are at least $\ell$ elements of $T_1$ sharing the same first coordinate.
 Let $F_1$ be the preimage of this family under $\pi$.
@@
 Set $T_2 = T_1 \setminus \{(i,S) \in T_1: i = i_1\}$, which contains at least $(\bar m - 1)(\ell -1)$ sets.
-Iterating this argument $p = \bar{m} - \ell(\bar m - m)$ times produces the conclusion in the lemma with $J = \{i_1, \ldots, i_p\}$.
-%We first show that $\bar m \geq m$.
-Fix $T = \{(j, S): j \in \pi(S), S \in E\}$.
-Then $|T| = \sum_{S \in E} |\pi(S)| = \sum_{S \in E} |S| = \sum_{i \in [m]} \deg(i) = \ell m$ by regularity of $E$.
-If $\bar m < m$ then by pigeonholing the $m \ell \geq \ell (\bar m + 1) \geq [(\ell + 1) - 1] \bar m + 1$ elements of $T$ with respect to the set $[\bar m]$ of possible first indices, we see that there must exist at least $\ell + 1$ elements of $T$ having the same first index.
-But by \eqref{cond} there can be no more than $\ell$ elements of $T$ with a given first index, since $E$ is $\ell$-regular.
-Hence $\bar m \geq m$.
-%Again, pigeonholing the elements of $T$ with respect to the set $[\bar m]$ of possible first indices, we see that for each $j$ there must be exactly $\ell$ elements of $T$ with $j$ as a first index; hence, $\pi(E)$ is $\ell$-regular.
-%Fix $j$ and let $F(j) = \{S \in E: j \in \pi(S)\}$ be the preimage of the star in $\pi(E)$ centered at $j$, which is of size $\ell$ by the above arguments.
-It follows from \eqref{cond} that $\cap_{S \in F(j)} S$ is nonempty.
-In fact, we must have $|\cap _{S \in F(j)} S| = 1$, since $E$ is $\ell$-regular and satisfies the singleton intersection property.
-It follows by \eqref{cond} that $\cap_{S \in F(j)} \pi(S) = \{j\}$.
-Thus $\pi(E)$ satisfies the singleton intersection property as well, and the preimage of every one of the $m$ stars in $\pi(E)$ is a star in $E$.
-It remains to show that every star in $E$ maps through $\pi$ to some star in $\pi(E)$.
-This follows by pigeonholing the $m$ stars of $\pi(E)$ with respect to their $m$ possible preimages if no two stars in $\pi(E)$ share the same preimage.
-This indeed must be the case, since $F(i) = F(j)$ implies $\{i\} = \cap_{S \in F(i)} \pi(S) = \cap_{S \in F(j)} \pi(S) = \{j\}$.
+Iterating this argument $p = \bar{m} - \ell(\bar m - m)$ times produces the desired $J = \{i_1, \ldots, i_p\} \subseteq [m]$.
 \end{proof}
-
 \begin{proof}[Proof of Lem.\ref{MainLemma}]
@@
 \end{align}
-%We first claim $\dim(\text{\rm Span}\{\mathbf{B}_{\pi(S)}\}) = \dim(\text{\rm Span}\{\mathbf{A}_{S}\})$ for all $S \in E$. 
 Since the right-hand side of \eqref{GapUpperBound} is strictly less than one (by \eqref{delrho} and $r \leq 1$), it follows by \eqref{dimLem} that $|\pi(S)| \geq \dim(\text{\rm Span}\{\mathbf{B}_{\pi(S)}\}) \geq \dim(\text{\rm Span}\{\mathbf{A}_{S}\}) = |S|$, with the equality due to $\mathbf{A}$ satisfying \eqref{SparkCondition}.
@@
 We next verify \eqref{cond} holds.
-%\begin{align}\label{fact2}
-%|\bigcap_{S \in F} \pi(S)| \leq |\bigcap_{S \in F} S |,\ \ \   \text{for all } \ F \subseteq E.
-%\end{align}
 Fix $F \subseteq E$.
@@
 &\leq \sum_{T \in F} \frac{ d\left( \text{\rm Span}\{\mathbf{B}_{\pi(T)}\},\text{\rm Span}\{\mathbf{A}_{T}\} \right) }{ r( \{ \text{\rm Span}\{\mathbf{A}_{S}\}_{S \in F}) }\nonumber \\
-%&\leq \frac{1}{r( \{ \text{\rm Span}\{\mathbf{A}_{S}\}_{S \in F})} \sum_{S \in F} \frac{ \varepsilon }{ L(\mathbf{AX}_{J(S)}) } \nonumber \\
 &\leq \frac{|F| \varepsilon}{r( \{ \text{\rm Span}\{\mathbf{A}_{S}\} \}_{S \in F})} 
-%&< L_2(\mathbf{A}) \frac{|F| }{ 2^{|E|}} \left( \frac{ \min_{\substack{F \subseteq E}} r( \{ \text{\rm Span}\{\mathbf{A}_{S}\}_{S \in F}) }{ r( \{ \text{\rm Span}\{\mathbf{A}_{S}\}_{S \in F}) } \right) \left( \frac{\min_{S \in E} L_k(\mathbf{AX}_{I(S)}) }{ \min_{T \in F} L(\mathbf{AX}_{J(T)}) } \right) \nonumber \\
 \leq \frac{C_2 \varepsilon}{\max_i\|\mathbf{A}_i\|_2}. 
@@
 
-%Now, fix $\ell \in [m]$.
-Since $E$ satisfies the singleton intersection property, $\{\ell\} = \cap F(\ell)$ for the star $F(\ell) \subseteq E$.
-By \eqref{cond}, we have that $\cap_{S \in F(\ell)} \pi(S)$ is either empty or it contains a single element.
-Lem.~\ref{NonEmptyLemma} ensures the latter case is the only possibility.
 Now, by Lem.~\ref{NonEmptyLemma}, the association $i \mapsto \cap \pi(F(i))$ defines an injective map $\bar \pi: J \to [\bar m]$ for some $J \subseteq [m]$ of size $\bar m - \ell(\bar m - m)$, and we can be sure that $\mathbf{B}_{\bar \pi(i)} \neq \mathbf{0}$ for all $i \in J$ since the columns of $\mathbf{B}_{\pi(S)}$ are linearly independent for all $S \in E$.
@@
 Fixing $\bar \varepsilon = C_2\varepsilon$ and letting $c_i = \|\mathbf{A}_i\|_2^{-1}$, we thus have that for every basis vector $\mathbf{e}_i \in \mathbb{R}^m$ with $i \in J$ there exists some $c'_i \in \mathbb{R}$ such that $\|c_i\mathbf{A}\mathbf{e}_i - c'_i \mathbf{B}\mathbf{e}_{\bar \pi(i)}\|_2 \leq \bar \varepsilon < L_2(\mathbf{A}) \min_{i\in J} c_i$.
-This is exactly the supposition in \eqref{1D}, and the result follows from the subsequent arguments for the case $k=1$ in Sec.~\ref{DUT} applied to the submatrix $\mathbf{A}_J$.
+This is exactly the supposition in \eqref{1D}, and the result follows from the case $k=1$ in Sec.~\ref{DUT} applied to the submatrix $\mathbf{A}_J$.
 \end{proof}
 
-%The above arguments can be easily modified to prove the following variation of Lem.~\ref{MainLemma}, key to proving Thm.~\ref{DeterministicUniquenessTheorem2}.
-
-%\begin{lemma}\label{MainLemma2}
-%Fix integers $n$ and $k < m \leq \bar m$ and suppose $\mathbf{A}~\in~\mathbb{R}^{n \times m}$ and $\mathbf{B} \in \mathbb{R}^{n \times \bar m}$ both satisfiy \eqref{SparkCondition}.
-There exists a constant $C_4 > 0$ for which for all $\varepsilon < L_2(\mathbf{A}) / C_4$ the following holds.
-If for some $E \subseteq2^{[m]}$ satisfying the singleton intersection property there exists a size-preserving map $\pi: E \mapsto 2^{[\bar m]}$ satisfying:
-%\begin{align}\label{GapUpperBound}
-%d(\text{\rm Span}\{\mathbf{A}_{S}\}, \text{\rm Span}\{\mathbf{B}_{\pi(S)}\}) \leq \varepsilon, \ \ \   \text{for all $S \in E$},
-%\end{align}
-%
-%then for some $J \in {[\bar m] \choose m}$, permutation matrix $\mathbf{P}$ and invertible diagonal matrix $\mathbf{D}$, we have:
-%\begin{align}\label{MainLemmaBPD}
-%\|\mathbf{A}_j - (\mathbf{BPD})_j\|_2 \leq C_4 \varepsilon, \ \ \  \text{for } j \in [m].
-%\end{align}
-%The constant $C_4$ is given by:
-%\begin{align}\label{Cdefm}
-%C_4 := \frac{2^{|E|}}{R} \max_{j \in [m]} \|\mathbf{A}_j\|_2
-%\end{align}
-%
-%with $R$ being the lesser of $\min_{\substack{F \subseteq E}} r( \{ \text{\rm Span}\{\mathbf{A}_{S}\} \}_{S \in F})$ and $\min_{\substack{F \subseteq {[\bar m] \choose k}}} r( \{ \text{\rm Span}\{\mathbf{B}_{S}\} \}_{S \in F})$.
-%\end{lemma}
-
-%\begin{proof}
-%The proof is very similar to the case $\bar m = m$, the difference being that now we may not invoke Lem.~\ref{NonEmptyLemma} (which requires $\bar m = m$) to infer from \eqref{fact2} that $| \cap_{S \in F(i)} \pi(S) | = 1$ for all stars $F(i)$.
-We circumvent this issue by instead assuming the spark condition on $\mathbf{B}$, which allows us to swap the roles of $\mathbf{A}$ and $\mathbf{B}$ in the arguments leading to the derivation of \eqref{fact2} to prove the opposite inequality for every star $F(i)$.
-Of course, this requires that the constant $C_4$  depend on $\mathbf{B}$.
-By these arguments we establish that $| \cap_{S \in F(i)} \pi(S) | = 1$ for all stars $F(i)$, yielding an injective map $\bar \pi: [m] \to [\bar m]$.
-The result then follows from the proof of the case $k=1$.
-%\end{proof}
-
-\section{Proofs of Thm.~\ref{robustPolythm} and Cor.~\ref{ProbabilisticCor}}\label{AppendixB} %Cors.~\ref{DeterministicUniquenessCorollary} \& \ref{ProbabilisticCor}}\label{AppendixB}
-
-%\begin{proof}[Proof of Cor.~\ref{DeterministicUniquenessCorollary}]
-%We need only demonstrate how to produce $N$ vectors $\mathbf{a}_i$ such that for some $E \subseteq {[m] \choose k}$ satisfying the singleton intersection property there are \mbox{$(k-1){m \choose k}+1$} vectors supported on each $S \in E$ in general linear position.
-Let $\gamma_1, \ldots, \gamma_N$ be any distinct numbers.
-Then the columns of the $k \times N$ matrix $V = (\gamma^i_j)^{k,N}_{i,j=1}$ are in general linear position (since the $\gamma_j$ are distinct, any $k \times k$ ``Vandermonde" sub-determinant is nonzero).
-Next, fix some $E \subseteq {[m] \choose k}$ satisfying the singleton intersection property.
-Finally, form the $k$-sparse vectors $\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$ with supports $S \in E$ (partitioning the $\mathbf{x}_i$ evenly among these supports so that each contains $(k-1){m \choose k}+1$ vectors $\mathbf{x}_i$) by setting the nonzero values $\mathbf{x}_i$ to be those contained in the $i$th column of $V$.
-%\end{proof}
-% Actually this is even overkill since
-
-%We now determine classes of datasets $Y$ having a stable sparse representation that are cut out by a single polynomial equation.
+\section{Proofs of Thm.~\ref{robustPolythm} and Cor.~\ref{ProbabilisticCor}}
 
 \begin{proof}[Proof (sketch) of Thm.~\ref{robustPolythm}]
-% We sketch the argument, leaving the details to the reader. 
 Let $M$ be the matrix with columns $\mathbf{A}\mathbf{x}_i$, $i \in [N]$.  Consider the polynomial in the entries of $\mathbf{A}$ and $\mathbf{x}_i$:
@@
 It can be checked that when $g$ is nonzero for a substitution of real numbers for the indeterminates, all of the genericity requirements on $\mathbf{A}$ and $\mathbf{x}_i$ in our proofs of stability in Thm.~\ref{DeterministicUniquenessTheorem} are satisfied (in particular, the spark condition on $\mathbf{A}$).
-% The statement of the theorem now follows directly.
 \end{proof}
@@
 
-%\begin{proof}[Proof of Thm.~\ref{DeterministicUniquenessTheorem2}]
-%The proof is the same as that of the case $\bar m = m$, only now we establish a map $\pi: E \to {[\bar m] \choose k}$ by pigeonholing $(k-1){\bar m \choose k} + 1$ vectors with respect to holes $[\bar m]$ and eventually applying Lem.~\ref{MainLemma2} instead of Lem.~\ref{MainLemma}.
-
-%In this case the constant $C_3$ is given by:
-%\begin{align}\label{Cdefm}
-%C_3 := \frac{2^{|E|} \max_{j \in [m]} \|\mathbf{A}_j\|_2}{ R \min_{S \in E} L_k(\mathbf{AX}_{I(S)}) },
-%\end{align}
-%
-%with $R$ being the lesser of $\min_{\substack{F \subseteq E}} r( \{ \text{\rm Span}\{\mathbf{A}_{S}\} \}_{S \in F})$ and $\min_{\substack{F \subseteq {[\bar m] \choose k}}} r( \{ \text{\rm Span}\{\mathbf{B}_{S}\} \}_{S \in F})$.
-%\end{proof}
-
 \end{document}

### 2017-04-08 manuscripts/PNAS/chazthm_pnas.tex
typo

@@
 \end{align}
-then $\bar m \geq m$ and the association $i \mapsto \cap \pi(F(i))$ defines an injective map from $J$ to $[\bar m]$ for some $J \subseteq [m]$ of size $\bar m - \ell(\bar m - m)$.
+then $\bar m \geq m$ and the association $i \mapsto \cap \pi(F(i))$ defines an injective map from $J$ to $[\bar m]$ for some $J \subseteq [m]$ of size $p = \bar m - \ell(\bar m - m)$.
 In particular, if $\bar m = m$ then the map $\pi$ is induced by a permutation.

### 2017-04-10 manuscripts/PNAS/chazthm_pnas.tex
SR Lem 4

@@
 
+%\begin{lemma}\label{NonEmptyLemma} 
+%Fix $\ell, m$, and $\bar m$. Suppose $E \subseteq 2^{[m]}$ is $\ell$-regular with the SIP.  If $\pi: E \to 2^{[\bar m]}$ has $\sum_{S \in E} |S| = \sum_{S \in E} |\pi(S)|$ and:
+%\begin{align}\label{cond}
+%|\bigcap_{S \in F} \pi(S)| \leq |\bigcap_{S \in F} S |,\ \ \   \text{for } F \subseteq E,
+%\end{align}
+%then $\bar m \geq m$ and the association $i \mapsto \cap \pi(F(i))$ defines an injective map from $J$ to $[\bar m]$ for some $J \subseteq [m]$ of size $p = \bar m - \ell(\bar m - m)$.
+In particular, if $\bar m = m$ then the map $\pi$ is induced by a permutation.
+%\end{lemma}
+% i'm placing this on hold since one thing i found was that i needed pi to be injective, but for that i needed the fact that |pi(S)| = |S|
+
 \begin{lemma}\label{NonEmptyLemma} 
-Fix $\ell, m$, and $\bar m$. Suppose $E \subseteq 2^{[m]}$ is $\ell$-regular with the SIP.  If $\pi: E \to 2^{[\bar m]}$ has $\sum_{S \in E} |S| = \sum_{S \in E} |\pi(S)|$ and:
+Fix $\ell, m$, and $\bar m$. Suppose $E \subseteq 2^{[m]}$ is $\ell$-regular with the SIP.  If $\pi: E \to 2^{[\bar m]}$ has $|S| = |\pi(S)|$ and:
 \begin{align}\label{cond}
@@
 \begin{proof}
-Consider the collection of pairs: \[T_1 = \{(i, S): i \in \pi(S), S \in E\},\] which number $|T_1| = \sum_{S \in E} |\pi(S)| = \sum_{S \in E} |S| = \ell m$ by regularity of $E$.  
-We first show that $\bar m \geq m$.
-Otherwise, if $\bar m < m$, then by pigeonholing the $m \ell \geq \ell (\bar m + 1) \geq [(\ell + 1) - 1] \bar m + 1$ elements of $T_1$ with respect to the set $[\bar m]$ of possible first indices, we see that there must exist at least $\ell + 1$ elements of $T_1$ having the same first index.
-But by \eqref{cond} there can be no more than $\ell$ elements of $T_1$ with a given first index, since $E$ is $\ell$-regular.
-Hence $\bar m \geq m$.
+First observe that assumption \eqref{cond} already constrains $\pi$ to be injective:  if $S_1 \neq S_2$, then $|\pi(S_1) \cap \pi(S_2)| \leq |S_1 \cap S_2| < \max\{|S_1|, |S_2|\} = \max\{|\pi(S_1)|, |\pi(S_2)|\}$, which implies that $\pi(S_1) \neq \pi(S_2)$.
+Next, consider the collection of pairs: \[T_1 := \{(i, S): i \in \pi(S), S \in E\},\] which number $|T_1| = \sum_{S \in E} |\pi(S)| = \sum_{S \in E} |S| = \ell m$ by regularity of $E$.
+Our second observation is that $\bar m \geq m$.
+Otherwise, if $\bar m < m$, then by pigeonholing the $m \ell \geq \ell (\bar m + 1) \geq [(\ell + 1) - 1] \bar m + 1$ elements of $T_1$ with respect to the set $[\bar m]$ of possible first indices, there must exist at least $\ell + 1$ elements of $T_1$ having the same first index.
+But by \eqref{cond} and injectivity of $\pi$, we then have more than $\ell$ edges in $E$ with common element, a contradiction to regularity.
 
-Next, since \[|T_1| > \bar m (\ell -1) + (p-1) > \bar m (\ell -1),\] the pigeonhole principle also implies that there are at least $\ell$ elements of $T_1$ sharing the same first coordinate.
+Since $|T_1| > \bar m (\ell -1) + (p-1) \geq \bar m (\ell -1)$, the pigeonhole principle also implies that there are at least $\ell$ elements of $T_1$ sharing the same first coordinate.
 Let $F_1$ be the preimage of this family under $\pi$.
@@
 From the SIP, the intersection of sets in $F_1$ is $\{i_1\}$, which by \eqref{cond} implies that the intersection of $\pi(S)$ with $S \in F_1$ also contains exactly one element.
-Set $T_2 = T_1 \setminus \{(i,S) \in T_1: i = i_1\}$, which contains at least $(\bar m - 1)(\ell -1)$ sets.
-Iterating this argument $p = \bar{m} - \ell(\bar m - m)$ times produces the desired $J = \{i_1, \ldots, i_p\} \subseteq [m]$.
+If $p > 1$, then define $T_2 := T_1 \setminus \{(i,S) \in T_1: i = i_1\}$, which contains more than $(\bar m - 1)(\ell -1)$ sets, and produce by the same argument a (necessarily) different index $i_2$.
+Iterating $p = \bar{m} - \ell(\bar m - m)$ times this loop yields the desired $J = \{i_1, \ldots, i_p\} \subseteq [m]$.
 \end{proof}
@@
 Fix $F \subseteq E$.
-Since $\text{\rm Span}\{\mathbf{B}_{\cap_{S \in F}\pi(S)}\} \subseteq \cap_{S \in F} \text{\rm Span}\{\mathbf{B}_{\pi(S)}\}$, if $\cap_{S \in F} \text{\rm Span}\{\mathbf{B}_{\pi(S)}\} = \textbf{0}$ then we must have $|\cap_{S \in F} \pi(S)| = 0$ (as the columns of $\mathbf{B}_{\pi(S)}$ are linearly independent) and \eqref{cond} trivially holds.
+Since $\text{\rm Span}\{\mathbf{B}_{\cap_{S \in F}\pi(S)}\} \subseteq \cap_{S \in F} \text{\rm Span}\{\mathbf{B}_{\pi(S)}\}$, if $\cap_{S \in F} \text{\rm Span}\{\mathbf{B}_{\pi(S)}\} = \{\textbf{0}\}$ then we must have $|\cap_{S \in F} \pi(S)| = 0$ (as the columns of $\mathbf{B}_{\pi(S)}$ are linearly independent) and \eqref{cond} trivially holds.
 Suppose then that the intersection is not the zero vector.

### 2017-04-10 manuscripts/PNAS/chazthm_pnas.tex
SR Main Lemma proof

@@
 \end{align}
-Since the right-hand side of \eqref{GapUpperBound} is strictly less than one (by \eqref{delrho} and $r \leq 1$), it follows by \eqref{dimLem} that $|\pi(S)| \geq \dim(\text{\rm Span}\{\mathbf{B}_{\pi(S)}\}) \geq \dim(\text{\rm Span}\{\mathbf{A}_{S}\}) = |S|$, with the equality due to $\mathbf{A}$ satisfying \eqref{SparkCondition}.
-Since $|S| = |\pi(S)|$, we therefore have $\dim(\text{\rm Span}\{\mathbf{B}_{\pi(S)}\}) = \dim(\text{\rm Span}\{\mathbf{A}_{S}\})$, and \eqref{eq2} follows by \eqref{eqdim}.
+Since the right-hand side of \eqref{GapUpperBound} is less than one (by \eqref{delrho} and $r \leq 1$), it follows from \eqref{dimLem} that $|\pi(S)| \geq \dim(\text{\rm Span}\{\mathbf{B}_{\pi(S)}\}) \geq \dim(\text{\rm Span}\{\mathbf{A}_{S}\}) = |S|$, with the equality due to $\mathbf{A}$ satisfying \eqref{SparkCondition}.
+Since $|S| = |\pi(S)|$, we have $\dim(\text{\rm Span}\{\mathbf{B}_{\pi(S)}\}) = \dim(\text{\rm Span}\{\mathbf{A}_{S}\})$, and \eqref{eq2} follows using \eqref{eqdim}.
 Note that the columns of $\mathbf{B}_{\pi(S)}$ are therefore linearly independent, for all $S \in E$.
@@
 Fix $F \subseteq E$.
-Since $\text{\rm Span}\{\mathbf{B}_{\cap_{S \in F}\pi(S)}\} \subseteq \cap_{S \in F} \text{\rm Span}\{\mathbf{B}_{\pi(S)}\}$, if $\cap_{S \in F} \text{\rm Span}\{\mathbf{B}_{\pi(S)}\} = \{\textbf{0}\}$ then we must have $|\cap_{S \in F} \pi(S)| = 0$ (as the columns of $\mathbf{B}_{\pi(S)}$ are linearly independent) and \eqref{cond} trivially holds.
+Since $\text{\rm Span}\{\mathbf{B}_{\cap_{S \in F}\pi(S)}\} \subseteq \cap_{S \in F} \text{\rm Span}\{\mathbf{B}_{\pi(S)}\}$, if $\cap_{S \in F} \text{\rm Span}\{\mathbf{B}_{\pi(S)}\} = \{\textbf{0}\}$, then we must have $|\cap_{S \in F} \pi(S)| = 0$ (as the columns of $\mathbf{B}_{\pi(S)}$ are linearly independent) and \eqref{cond} trivially holds.
 Suppose then that the intersection is not the zero vector.
@@
 It then follows from \eqref{eqdim} and \eqref{randoml} that $d\left( \text{\rm Span}\{\mathbf{A}_i\}, \text{\rm Span}\{ \mathbf{B}_{\bar \pi(i)} \} \right) \leq C_2 \varepsilon / \max_i \|\mathbf{A}_i\|_2$ for all $i \in J$.
-Fixing $\bar \varepsilon = C_2\varepsilon$ and letting $c_i = \|\mathbf{A}_i\|_2^{-1}$, we thus have that for every basis vector $\mathbf{e}_i \in \mathbb{R}^m$ with $i \in J$ there exists some $c'_i \in \mathbb{R}$ such that $\|c_i\mathbf{A}\mathbf{e}_i - c'_i \mathbf{B}\mathbf{e}_{\bar \pi(i)}\|_2 \leq \bar \varepsilon < L_2(\mathbf{A}) \min_{i\in J} c_i$.
-This is exactly the supposition in \eqref{1D}, and the result follows from the case $k=1$ in Sec.~\ref{DUT} applied to the submatrix $\mathbf{A}_J$.
+Fixing $\bar \varepsilon = C_2\varepsilon$ and letting $c_i = \|\mathbf{A}_i\|_2^{-1}$, we thus have that for every basis vector $\mathbf{e}_i \in \mathbb{R}^m$ with $i \in J$ there exists some $\bar{c}_i \in \mathbb{R}$ such that $\|c_i\mathbf{A}\mathbf{e}_i - \bar{c}_i \mathbf{B}\mathbf{e}_{\bar \pi(i)}\|_2 \leq \bar \varepsilon < L_2(\mathbf{A}) \min_{i\in J} |c_i|$.
+But this is exactly the supposition in \eqref{1D}, and the result follows from the case $k=1$ in Sec.~\ref{DUT} applied to the submatrix $\mathbf{A}_J$.
 \end{proof}

### 2017-04-10 manuscripts/PNAS/chazthm_pnas.tex
minor edits Lem 4 proof

@@
 Let $F_1$ be the preimage of this family under $\pi$.
-By the assumption \eqref{cond}, the intersection of $F_1$ is nonempty, and in fact must contain exactly $\ell$ elements.
-Thus, $F_1$ is the star of some element $i_1 \in [m]$.
+By the assumption \eqref{cond}, the intersection of $F_1$ is nonempty, and in fact must contain exactly $\ell$ elements by regularity.
+%Thus, $F_1$ is the star of some element $i_1 \in [m]$.  
 From the SIP, the intersection of sets in $F_1$ is $\{i_1\}$, which by \eqref{cond} implies that the intersection of $\pi(S)$ with $S \in F_1$ also contains exactly one element.

### 2017-04-10 manuscripts/PNAS/chazthm_pnas.tex
lil edits

--- 2017-04-10 manuscripts/PNAS/chazthm_pnas.tex
@@
 More specifically, dictionaries are identifiable from as few as \mbox{$N = m(k-1){m \choose k} + m$} sparse linear combinations of their columns up to an error that is linear in the measurement noise (Thm.~\ref{DeterministicUniquenessTheorem}).
-In fact, provided $n \geq k$, in almost all cases the dictionary learning problem is well-posed (in the sense of Hadamard \cite{Hadamard1902}) given enough data (Cor.~\ref{ProbabilisticCor}).
+In fact, provided $n \geq \max(2k,m)$, in almost all cases the dictionary learning problem is well-posed (in the sense of Hadamard \cite{Hadamard1902}) given enough data (Cor.~\ref{ProbabilisticCor}).
 Importantly, these guarantees hold without assuming the recovered matrix satisfies a spark condition.
-Our results  also apply when only an upper bound on the number $m$ of dictionary elements is known.
+Our results also apply when the number $m$ of dictionary elements is unknown.
 The explicit, algorithm-independent criteria we provide should be a useful tool in the theory of dictionary learning.
@@
 Since $f$ is an analytic function, having one substitution of real numbers with $f(\mathbf{A}) \neq 0$ implies that its zeroes form a set of measure zero.
-Fortunately, such a matrix $\mathbf{A}$ is easily constructed by adding rows of zeroes to any $k \times m$ ``Vandermonde'' matrix $[\gamma_i^j]_{i,j=1}^{k,m}$ with distinct $\gamma_i$ (so that each term in the product above is nonzero).
+Fortunately, such a matrix $\mathbf{A}$ is easily constructed by adding rows of zeroes to any $\max(2k,m) \times m$ ``Vandermonde'' matrix $[\gamma_i^j]_{i,j=1}^{k,m}$ with distinct $\gamma_i$ (so that each term in the product above is nonzero).
 %$A_{ij} = \gamma_i (since the $\gamma_i$ are distinct, any $k \times k$ ``Vandermonde'' sub-determinant is nonzero)
@@
 with $f(\mathbf{A}) = 0$.
-Hence, almost every real matrix $\mathbf{A}$ with at least $k$ rows and columns satisfies \eqref{SparkCondition}.
+Hence, almost every real $n \times m$ matrix $\mathbf{A}$ with $n \geq \max(2k,m)$ satisfies \eqref{SparkCondition}.
 
@@
 
-In fact, though, uniqueness guarantees with minimal assumptions apply to all areas of data science and engineering that utilize learned sparse representations.
-For example, several groups have utilized compressed sensing for signal processing tasks: MRI analysis \cite{lustig2008compressed}, image compression \cite{Duarte08}, and, more recently, the design of an ultrafast camera \cite{Gao14}.
-Given such effective uses of CS, it is only a matter of time before these systems incorporate sparse representational learning to encode and process data (e.g., in a device that learns structure from motion \cite{kong2016prior}).
+In fact, uniqueness guarantees with minimal assumptions apply to all areas of data science and engineering that utilize learned sparse representations.
+For example, several groups have utilized compressive sensing for signal processing tasks: MRI analysis \cite{lustig2008compressed}, image compression \cite{Duarte08}, and, more recently, the design of an ultrafast camera \cite{Gao14}.
+Given such effective uses of compressive sensing, it is only a matter of time before these systems incorporate sparse representational learning to encode and process data (e.g., in a device that learns structure from motion \cite{kong2016prior}).
 In these cases, assurances such as those offered by our theorems certify that different devices (with different initialization, samples, etc.) are equivalent as soon as enough data originate from a statistically identical system.
@@
 
-%\begin{lemma}\label{NonEmptyLemma} 
-%Fix $\ell, m$, and $\bar m$. Suppose $E \subseteq 2^{[m]}$ is $\ell$-regular with the SIP.  If $\pi: E \to 2^{[\bar m]}$ has $\sum_{S \in E} |S| = \sum_{S \in E} |\pi(S)|$ and:
-%\begin{align}\label{cond}
-%|\bigcap_{S \in F} \pi(S)| \leq |\bigcap_{S \in F} S |,\ \ \   \text{for } F \subseteq E,
-%\end{align}
-%then $\bar m \geq m$ and the association $i \mapsto \cap \pi(F(i))$ defines an injective map from $J$ to $[\bar m]$ for some $J \subseteq [m]$ of size $p = \bar m - \ell(\bar m - m)$.
-In particular, if $\bar m = m$ then the map $\pi$ is induced by a permutation.
-%\end{lemma}
-% i'm placing this on hold since one thing i found was that i needed pi to be injective, but for that i needed the fact that |pi(S)| = |S|
-
 \begin{lemma}\label{NonEmptyLemma} 
-Fix $\ell, m$, and $\bar m$. Suppose $E \subseteq 2^{[m]}$ is $\ell$-regular with the SIP.  If $\pi: E \to 2^{[\bar m]}$ has $|S| = |\pi(S)|$ and:
+Fix $\ell, m$, and $\bar m$. Suppose $E \subseteq 2^{[m]}$ is $\ell$-regular with the SIP.  If $\pi: E \to 2^{[\bar m]}$ has $\sum_{S \in E} |S| = \sum_{S \in E} |\pi(S)|$ and:
 \begin{align}\label{cond}
@@
 \begin{proof}
-First observe that assumption \eqref{cond} already constrains $\pi$ to be injective:  if $S_1 \neq S_2$, then $|\pi(S_1) \cap \pi(S_2)| \leq |S_1 \cap S_2| < \max\{|S_1|, |S_2|\} = \max\{|\pi(S_1)|, |\pi(S_2)|\}$, which implies that $\pi(S_1) \neq \pi(S_2)$.
-Next, consider the collection of pairs: \[T_1 := \{(i, S): i \in \pi(S), S \in E\},\] which number $|T_1| = \sum_{S \in E} |\pi(S)| = \sum_{S \in E} |S| = \ell m$ by regularity of $E$.
-Our second observation is that $\bar m \geq m$.
-Otherwise, if $\bar m < m$, then by pigeonholing the $m \ell \geq \ell (\bar m + 1) \geq [(\ell + 1) - 1] \bar m + 1$ elements of $T_1$ with respect to the set $[\bar m]$ of possible first indices, there must exist at least $\ell + 1$ elements of $T_1$ having the same first index.
-But by \eqref{cond} and injectivity of $\pi$, we then have more than $\ell$ edges in $E$ with common element, a contradiction to regularity.
+Consider the collection of pairs: \[T_1 = \{(i, S): i \in \pi(S), S \in E\},\] which number $|T_1| = \sum_{S \in E} |\pi(S)| = \sum_{S \in E} |S| = \ell m$ by regularity of $E$.  
+We first show that $\bar m \geq m$.
+Otherwise, if $\bar m < m$, then by pigeonholing the $m \ell \geq \ell (\bar m + 1) \geq [(\ell + 1) - 1] \bar m + 1$ elements of $T_1$ with respect to the set $[\bar m]$ of possible first indices, we see that there must exist at least $\ell + 1$ elements of $T_1$ having the same first index.
+But by \eqref{cond} there can be no more than $\ell$ elements of $T_1$ with a given first index, since $E$ is $\ell$-regular.
+Hence $\bar m \geq m$.
 
-Since $|T_1| > \bar m (\ell -1) + (p-1) \geq \bar m (\ell -1)$, the pigeonhole principle also implies that there are at least $\ell$ elements of $T_1$ sharing the same first coordinate.
+Next, since \[|T_1| > \bar m (\ell -1) + (p-1) > \bar m (\ell -1),\] the pigeonhole principle also implies that there are at least $\ell$ elements of $T_1$ sharing the same first coordinate.
 Let $F_1$ be the preimage of this family under $\pi$.
@@
 From the SIP, the intersection of sets in $F_1$ is $\{i_1\}$, which by \eqref{cond} implies that the intersection of $\pi(S)$ with $S \in F_1$ also contains exactly one element.
-If $p > 1$, then define $T_2 := T_1 \setminus \{(i,S) \in T_1: i = i_1\}$, which contains more than $(\bar m - 1)(\ell -1)$ sets, and produce by the same argument a (necessarily) different index $i_2$.
-Iterating $p = \bar{m} - \ell(\bar m - m)$ times this loop yields the desired $J = \{i_1, \ldots, i_p\} \subseteq [m]$.
+Set $T_2 = T_1 \setminus \{(i,S) \in T_1: i = i_1\}$, which contains at least $(\bar m - 1)(\ell -1)$ sets.
+Iterating this argument $p = \bar{m} - \ell(\bar m - m)$ times produces the desired $J = \{i_1, \ldots, i_p\} \subseteq [m]$.
 \end{proof}
@@
 Fix $F \subseteq E$.
-Since $\text{\rm Span}\{\mathbf{B}_{\cap_{S \in F}\pi(S)}\} \subseteq \cap_{S \in F} \text{\rm Span}\{\mathbf{B}_{\pi(S)}\}$, if $\cap_{S \in F} \text{\rm Span}\{\mathbf{B}_{\pi(S)}\} = \{\textbf{0}\}$ then we must have $|\cap_{S \in F} \pi(S)| = 0$ (as the columns of $\mathbf{B}_{\pi(S)}$ are linearly independent) and \eqref{cond} trivially holds.
+Since $\text{\rm Span}\{\mathbf{B}_{\cap_{S \in F}\pi(S)}\} \subseteq \cap_{S \in F} \text{\rm Span}\{\mathbf{B}_{\pi(S)}\}$, if $\cap_{S \in F} \text{\rm Span}\{\mathbf{B}_{\pi(S)}\} = \textbf{0}$ then we must have $|\cap_{S \in F} \pi(S)| = 0$ (as the columns of $\mathbf{B}_{\pi(S)}$ are linearly independent) and \eqref{cond} trivially holds.
 Suppose then that the intersection is not the zero vector.

### 2017-04-11 manuscripts/PNAS/chazthm_pnas.tex
some edits

@@
 
-\significancestatement{Many naturally occurring signals (visual scenery, speech, electrocardiograms, etc.) can be characterized as parsimonious combinations of elementary waveforms drawn from a large dictionary.
-Absent analytic descriptions of these signal classes, it falls on algorithms from machine learning to extract such structures given many examples from a class.
-We give conditions guaranteeing when a dictionary of a given size is uniquely and stably determined by data, regardless of the algorithm used to compute it.
-The result provides an explanation for universal representation of natural signals from sparse coding models.
+\significancestatement{Many naturally occurring signals (visual scenery, speech, electroencephalograms, etc.) for which we lack theoretically motivated formal models can be usefully characterized as parsimonious combinations of elementary waveforms drawn from a large `dictionary'.
+We give general conditions guaranteeing when such dictionaries are uniquely and stably determined by enough data.
+The result provides theoretical grounding for the application of dictionary learning methods to problems of blind source separation, and may help to explain the observed universality of emergent representations in sparse coding models of some natural phenomena.
 %These results provide theoretical grounding for  the application of dictionary learning to recovering sparse signals from unknown noisy compressive measurements.
@@
 \authordeclaration{The authors declare no conflict of interest.}
-\correspondingauthor{\textsuperscript{1}To whom correspondence should be addressed. E-mail: cjg@berkeley.edu, chillar@msri.org}
+\correspondingauthor{\textsuperscript{1}To whom correspondence should be addressed. E-mail: chaz@berkeley.edu, chillar@msri.org}
 
-\keywords{Sparse linear coding, dictionary learning, uniqueness, compressed sensing}
+\keywords{Sparse coding, dictionary learning, identifiability, compressive sensing}
 
@@
 If this is the case, add \parshape=0 to the end of the list environment.
-\dropcap{B}lind source separation is a classical inverse problem in signal processing \cite{sato1975method}.
-One constraint commonly imposed is that each of $N$ observed $n$-dimensional signals are a linear combination of at most $k$ elementary waveforms drawn from some unknown ``dictionary'' of size $m$, typically where $k < m \ll N$ (see \cite{Zhang15} for a comprehensive review of this and related models).
+\dropcap{B}lind source separation is a classical problem in signal processing \cite{sato1975method}.
+One common assumption is that each of $N$ observed $n$-dimensional signals is a linear combination of at most $k$ elementary waveforms drawn from some unknown ``dictionary'' of size $m$, typically with $k < m \ll N$ (see \cite{Zhang15} for a comprehensive review of this and related models).
 %A popular underlying assumption is that there exists a `dictionary' of $m$ elementary waveforms, at most $k$ of which need be linearly combined to represent each signal in a given dataset of size $N$, typically where $k < m \ll N$.
@@
 In particular, it has been shown that response properties of simple-cell neurons in mammalian visual cortex emerge from optimizing a dictionary to represent small patches of natural images \cite{Olshausen96, hurri1996image, bell1997independent, van1998independent}, a major advance in computational neuroscience.
-A curious aspect of this finding is that the latent waveforms (``Gabors'') estimated from data appear to be canonical \cite{donoho2001can};
+A curious aspect of this finding is that the latent waveforms (e.g.
+`Gabor' wavelets) estimated from data appear to be canonical \cite{donoho2001can};
 i.e., they are found in learned dictionaries independent of algorithmic implementation or natural image training set.
@@
 %In other words, whenever enough sparsely represented data generated from a dictionary (satisfying a spark condition) are observed, the original codes and dictionary are uniquely determined up to an error that is commensurate with the measurement noise.
-More specifically, dictionaries are identifiable from as few as \mbox{$N = m(k-1){m \choose k} + m$} sparse linear combinations of their columns up to an error that is linear in the measurement noise (Thm.~\ref{DeterministicUniquenessTheorem}).
-In fact, provided $n \geq \max(2k,m)$, in almost all cases the dictionary learning problem is well-posed (in the sense of Hadamard \cite{Hadamard1902}) given enough data (Cor.~\ref{ProbabilisticCor}).
-Importantly, these guarantees hold without assuming the recovered matrix satisfies a spark condition.
-Our results also apply when the number $m$ of dictionary elements is unknown.
-The explicit, algorithm-independent criteria we provide should be a useful tool in the theory of dictionary learning.
-
-Direct applications include: 1) a sufficient diversity of sparse codes sent through a random linear compressive channel are identifiable and 2) an explanation for universal representation of natural signals in sparse coding models from neuroscience.
+More specifically, dictionaries that preserve sparse codes (i.e., satisfy a `spark condition') are identifiable from as few as \mbox{$N = m(k-1){m \choose k} + m$} noisy sparse linear combinations of their columns up to an error linear in the noise (Thm.~\ref{DeterministicUniquenessTheorem}).
+In fact, provided $n \geq \min(2k,m)$, in almost all cases the dictionary learning problem is well-posed (as per Hadamard \cite{Hadamard1902}) given enough data (Cor.~\ref{ProbabilisticCor}).
+Importantly, these guarantees hold without assuming the recovered matrix satisfies a spark condition, even when the number $m$ of dictionary elements is unknown.
+The explicit, algorithm-independent criteria we provide should be a useful tool to dictionary learning theory.
 
@@
 
-Note that any particular solution $(\mathbf{B}, \mathbf{\bar x}_1 \ldots, \mathbf{\bar x}_N)$ to this problem gives rise to an orbit of other solutions $(\mathbf{BPD}, \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\bar x}_1, \ldots, \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\bar x}_N)$, where $\mathbf{P}$ is any permutation matrix and $\mathbf{D}$ any invertible diagonal.
+Note that any particular solution $(\mathbf{B}, \mathbf{\bar x}_1 \ldots, \mathbf{\bar x}_N)$ to this problem gives rise to an orbit of equivalent solutions $(\mathbf{BPD}, \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\bar x}_1, \ldots, \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\bar x}_N)$, where $\mathbf{P}$ is any permutation matrix and $\mathbf{D}$ any invertible diagonal.
 We therefore consider whether solutions to Prob.~\ref{InverseProblem} are unique only up to this ambiguity.  More specifically, 
@@
 Fix $Y = \{ \mathbf{y}_1, \ldots, \mathbf{y}_N\} \subset \mathbb{R}^n$.
-We say $Y$ has a \textbf{$k$-sparse linear representation in $m$ dimensions} if there exists a matrix $\mathbf{A}$ and $k$-sparse $\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$ such that $\mathbf{y}_i = \mathbf{A}\mathbf{x}_i$ for all $i$.
+We say $Y$ has a \textbf{$k$-sparse representation in $m$ dimensions} if there exists a matrix $\mathbf{A}$ and $k$-sparse $\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$ such that $\mathbf{y}_i = \mathbf{A}\mathbf{x}_i$ for all $i$.
 %Equivalently, $\mathbf{Y} = \mathbf{A}\mathbf{X}$ for $\mathbf{Y}$ and $\mathbf{X}$ having the $\mathbf{y}_i$ and $\mathbf{x}_i$ as their columns, respectively.
@@
 Consider now any dataset $Z$ generated as in \eqref{LinearModel} with $\eta \leq \frac{1}{2} \varepsilon(\delta_1, \delta_2)$.
-Then from the triangle inequality, it follows that any matrix $\mathbf{B}$ and $k$-sparse $\mathbf{\bar x}_1, \ldots, \mathbf{\bar x}_N$ solving Prob.~\ref{InverseProblem} are necessarily close to the original dictionary $\mathbf{A}$ and sparse codes $\mathbf{x}_i$.
+Then from the triangle inequality, it follows that any matrix $\mathbf{B}$ and $k$-sparse $\mathbf{\bar x}_1, \ldots, \mathbf{\bar x}_N \in \mathbb{R}^m$ solving Prob.~\ref{InverseProblem} are necessarily close to the original dictionary $\mathbf{A}$ and sparse codes $\mathbf{x}_i$.
 
-Previous theoretical work on Prob.~\ref{InverseProblem} for the noiseless case $\eta =0$ (e.g., \cite{li2004analysis, Georgiev05, Aharon06, Hillar15}) has shown that a solution (when it exists) is indeed unique provided the $\mathbf{x}_i$ are sufficiently diverse and the generating matrix $\mathbf{A}$ satisfies the \textit{spark condition} from compressed sensing (CS):
+Previous theoretical work on Prob.~\ref{InverseProblem} has adressed only the noiseless case $\eta =0$ (e.g., \cite{li2004analysis, Georgiev05, Aharon06, Hillar15}), showing that a solution (when it exists) is indeed unique provided the $\mathbf{x}_i$ are sufficiently diverse and the generating matrix $\mathbf{A}$ satisfies the \textit{spark condition} from compressed sensing (CS):
 \begin{align}\label{SparkCondition}
@@
 In the next section, we give precise statements of our main results, which include an explicit form for $\varepsilon(\delta_1, \delta_2)$.
-We then prove our main theorem (Thm.~\ref{DeterministicUniquenessTheorem}) in Sec.~\ref{DUT} after stating some additional definitions and lemmas required for the proof, including our main tool from combinatorial matrix analysis (Lem.~\ref{MainLemma}).
-We also give a simple argument extending our uniqueness guarantees to the following more common optimization formulation of the sparse linear coding problem (Cor.~\ref{SLCopt}).
+We then prove our main theorem (Thm.~\ref{DeterministicUniquenessTheorem}) in Sec.~\ref{DUT} after stating some additional definitions and lemmas required for the proof, including a useful result in combinatorial matrix analysis (Lem.~\ref{MainLemma}).
+We also give a simple argument extending our uniqueness guarantees to the following more common optimization formulation of the sparse coding problem (Cor.~\ref{SLCopt}).
 
@@
 Finally, we present several applications in Discussion Sec.~\ref{Discussion}.
+These include: 1) a sufficient diversity of sparse codes sent through a random linear compressive channel are identifiable and 2) an explanation for universal representation of natural signals in sparse coding models from neuroscience.
 
@@
 
-Before stating main results, we first identify the combinatorial criteria on support sets of generating codes allowing for stable sparse 
+Before stating our main results, we first identify the combinatorial criteria on support sets of generating codes allowing for stable sparse 
 representations.  Let $\{1, \ldots, m\}$ be denoted $[m]$, its power set $2^{[m]}$, and ${[m] \choose k}$ the set of subsets of $[m]$ of size $k$. 
@@
 
-Clearly, $\sqrt{k} L_k(\mathbf{A}) \geq \sqrt{k'}L_{k'}(\mathbf{A})$ whenever $k < k'$, and for any $\mathbf{A}$ satisfying \eqref{SparkCondition}, we have $L_{k'}(\mathbf{A}) > 0$ for  $k' \leq 2k$.
-The quantity $1 - \sqrt{k} L_k(\mathbf{A})$ is also known in the CS literature as the (asymmetric) lower restricted isometry constant \cite{Blanchard2011, Foucart2009}.
+%Clearly, $\sqrt{k} L_k(\mathbf{A}) \geq \sqrt{k'}L_{k'}(\mathbf{A})$ whenever $k < k'$, and 
+Clearly, for any $\mathbf{A}$ satisfying \eqref{SparkCondition}, we have $L_{k'}(\mathbf{A}) > 0$ for  $k' \leq 2k$.
+We note that the quantity $1 - \sqrt{k} L_k(\mathbf{A})$ is also known in the CS literature as the (asymmetric) lower restricted isometry constant \cite{Blanchard2011}.%, Foucart2009}.
 
@@
 
-1) Every matrix $\mathbf{B} \in \mathbb{R}^{n \times \bar m}$ and $k$-sparse $\mathbf{\bar x}_1, \ldots, \mathbf{\bar x}_N \in \mathbb{R}^{\bar m}$ with  \mbox{$\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\bar x}_i\|_2 \leq \varepsilon$} for all $i$ must have $\bar m \geq m$ and, provided $p = \bar m - \ell(\bar m - m)$ is positive, necessarily satisfy:
+1) Every matrix $\mathbf{B}$ and $k$-sparse $\mathbf{\bar x}_1, \ldots, \mathbf{\bar x}_N \in \mathbb{R}^{\bar m}$ with  \mbox{$\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\bar x}_i\|_2 \leq \varepsilon$} for all $i$ must have $\bar m \geq m$ and, provided $p = \bar m - \ell(\bar m - m)$ is positive, necessarily satisfy:
 \begin{align}\label{Cstable}
@@
 Since $f$ is an analytic function, having one substitution of real numbers with $f(\mathbf{A}) \neq 0$ implies that its zeroes form a set of measure zero.
-Fortunately, such a matrix $\mathbf{A}$ is easily constructed by adding rows of zeroes to any $\max(2k,m) \times m$ ``Vandermonde'' matrix $[\gamma_i^j]_{i,j=1}^{k,m}$ with distinct $\gamma_i$ (so that each term in the product above is nonzero).
+Fortunately, such a matrix $\mathbf{A}$ is easily constructed by adding rows of zeroes to any $\min(2k,m) \times m$ ``Vandermonde'' matrix $[\gamma_i^j]_{i,j=1}^{k,m}$ with distinct $\gamma_i$ (so that each term in the product above is nonzero).
 %$A_{ij} = \gamma_i (since the $\gamma_i$ are distinct, any $k \times k$ ``Vandermonde'' sub-determinant is nonzero)
@@
 \begin{corollary}\label{ProbabilisticCor}
-Fix $k < m$ and $n \geq \max(2k, m)$ % satisfying \eqref{CScondition} for $\gamma = \gamma_0$, 
+Fix $k < m$ and $n \geq \min(2k, m)$ % satisfying \eqref{CScondition} for $\gamma = \gamma_0$, 
 and let the entries of $\mathbf{A} \in \mathbb{R}^{n \times m}$ and $k$-sparse $\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$ be drawn independently from probability measures absolutely continuous with respect to the standard Borel measure $\mu$.
@@
 We also collect a set of useful mathematical tools and basic facts for future research.
-The main motivation for this work, however, was to understand how seemingly universal and stable representations emerge from sparse coding models fit to natural data by a variety of methodologies.
+The main motivation for this work, however, was to understand how seemingly universal representations emerge from sparse coding models fit to natural data by a variety of methodologies.
 We elaborate more on these applications below after discussing theoretical aspects.
@@
 In this regard, for the sparse linear coding model we demonstrate a linear relationship, \eqref{epsdel}, between measurement noise and the deviation of any solution from the true parameters, with explicit constants expressed in terms of these parameters.
-Moreover, we show that even if the meta-parameter defining the number of dictionary elements is overestimated, a subset of parameters are still identifiable.
-It would be of practical utility to determine the best possible dependence of $\varepsilon$ on $\delta_1, \delta_2$ in Def.\ref{maindef} as well as the minimal requirements on the number and diversity of generating codes, and we hope that other researchers continue to improve and extend our results.
+Moreover, we show that even if the meta-parameter defining the number of dictionary elements is overestimated, a subset of parameters may still be identifiable.
+We remark that our uniqueness result accounts for deterministic ``worst-case'' noise, whereas the ``effective'' noise might be smaller when sampled from a distribution; in such cases, the constants %Thms.~\ref{DeterministicUniquenessTheorem},~\ref{DeterministicUniquenessTheorem2}
+will improve as well.
+It would therefore be of practical utility to determine the best possible dependence of $\varepsilon$ on $\delta_1, \delta_2$ in Def.\ref{maindef} as well as the minimal requirements on the number and diversity of generating codes, and we hope that other researchers continue to improve and extend our results.
 
@@
 
-One notable component of our contribution is a combinatorial criteria (regular hypergraphs satisfying the singular intersection property, Def.~\ref{sip}) for the support sets of sparse codes key to the identification of the dictionary.
+One notable component of our contribution is a combinatorial criteria (regular hypergraphs satisfying the singleton intersection property, Def.~\ref{sip}) for the support sets of sparse codes key to the identification of the dictionary.
 Fully understanding those combinatorial designs allowing for stable sparse representations is an interesting research area for the future.
 For instance, whether there is a support set size $N$ that is polynomial in $m,k$ gauranteeing the conclusions of Thm.~\ref{DeterministicUniquenessTheorem} has implications for the computational complexity of Probs.~\ref{InverseProblem} and \ref{OptimizationProblem} and related questions \cite{Tillmann15}.
-We also remark that our uniqueness result accounts for deterministic ``worst-case'' noise, whereas the ``effective'' noise might be smaller when sampled from a distribution; in such cases, the constants  %Thms.~\ref{DeterministicUniquenessTheorem},~\ref{DeterministicUniquenessTheorem2}
-will improve.
 

### 2017-04-11 manuscripts/PNAS/chazthm_pnas.tex
intro edits

@@
 
-\significancestatement{Many naturally occurring signals (visual scenery, speech, electroencephalograms, etc.) for which we lack theoretically motivated formal models can be usefully characterized as parsimonious combinations of elementary waveforms drawn from a large `dictionary'.
+\significancestatement{Many naturally occurring signals (visual scenery, speech, EEG, etc.) lacking domain-specific formal models can nonetheless be usefully characterized as parsimonious combinations of elementary waveforms drawn from a large `dictionary'.
 We give general conditions guaranteeing when such dictionaries are uniquely and stably determined by enough data.
-The result provides theoretical grounding for the application of dictionary learning methods to problems of blind source separation, and may help to explain the observed universality of emergent representations in sparse coding models of some natural phenomena.
+The result justifies the application of this model to problems in blind source separation, and may help to explain the observed universality of emergent representations in sparse coding models of some natural phenomena.
 %These results provide theoretical grounding for  the application of dictionary learning to recovering sparse signals from unknown noisy compressive measurements.
@@
 \dropcap{B}lind source separation is a classical problem in signal processing \cite{sato1975method}.
-One common assumption is that each of $N$ observed $n$-dimensional signals is a linear combination of at most $k$ elementary waveforms drawn from some unknown ``dictionary'' of size $m$, typically with $k < m \ll N$ (see \cite{Zhang15} for a comprehensive review of this and related models).
+A common modern assumption is that each of $N$ observed $n$-dimensional signals is a (noisy) linear combination of at most $k$ elementary waveforms drawn from some unknown ``dictionary'' of size $m$, typically with $k < m \ll N$ (see \cite{Zhang15} for a comprehensive review of this and related models).
 %A popular underlying assumption is that there exists a `dictionary' of $m$ elementary waveforms, at most $k$ of which need be linearly combined to represent each signal in a given dataset of size $N$, typically where $k < m \ll N$.
-Approximating solutions to this sparsity-constrained inverse problem have provided insight into the structure of many signal classes lacking explicit descriptions (e.g., in vision \cite{wang2015sparse}).
+Approximating solutions to this sparsity-constrained inverse problem have provided insight into the structure of many signal classes lacking domain-specific formal models (e.g., in vision \cite{wang2015sparse}).
 In particular, it has been shown that response properties of simple-cell neurons in mammalian visual cortex emerge from optimizing a dictionary to represent small patches of natural images \cite{Olshausen96, hurri1996image, bell1997independent, van1998independent}, a major advance in computational neuroscience.
@@
 
-Motivated by these discoveries and earlier work in the theory of neural communication \cite{Coulter10, Isely10}, we address when dictionaries and sparse representations are uniquely determined by data.
+Motivated by these discoveries and earlier work in the theory of neural communication \cite{Coulter10, Isely10}, we address when dictionaries and the sparse representations they induce are uniquely determined by data.
 Answers to this question also have other real-world implications.
@@
 Fortunately, algorithms with proven recovery of generating dictionaries under certain 
-conditions have recently been proposed (see \cite[Sec.~I-E]{Sun16} for a summary of the state-of-the-art).
-However, there are few theorems in the literature explaining this general phenomenon of uniqueness.
+conditions have recently been proposed (see \cite[Sec.~I-E]{Sun16} for a summary of the state-of-the-art). Few theorems, however, can be cited to explain this uniqueness phenomenon more generally.
 
@@
 In fact, provided $n \geq \min(2k,m)$, in almost all cases the dictionary learning problem is well-posed (as per Hadamard \cite{Hadamard1902}) given enough data (Cor.~\ref{ProbabilisticCor}).
-Importantly, these guarantees hold without assuming the recovered matrix satisfies a spark condition, even when the number $m$ of dictionary elements is unknown.
-The explicit, algorithm-independent criteria we provide should be a useful tool to dictionary learning theory.
+Moreover, these guarantees hold without assuming the recovered matrix satisfies a spark condition, even when the number $m$ of dictionary elements is unknown.
+The explicit, algorithm-independent criteria we provide should be a useful tool in the theory of sparse representations.
+
+%Other applications include: 1) a sufficient diversity of sparse codes sent through a random linear compressive channel are identifiable and 2) an explanation for universal representation of natural signals in sparse coding models from neuroscience.
 
@@
 Note that any particular solution $(\mathbf{B}, \mathbf{\bar x}_1 \ldots, \mathbf{\bar x}_N)$ to this problem gives rise to an orbit of equivalent solutions $(\mathbf{BPD}, \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\bar x}_1, \ldots, \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\bar x}_N)$, where $\mathbf{P}$ is any permutation matrix and $\mathbf{D}$ any invertible diagonal.
-We therefore consider whether solutions to Prob.~\ref{InverseProblem} are unique only up to this ambiguity.  More specifically, 
-we seek conditions for when sparsely coded datasets have a stable unique representation.
+Previous theoretical work addressing the noiseless case $\eta =0$ (e.g., \cite{li2004analysis, Georgiev05, Aharon06, Hillar15}) has shown that a solution to Prob.~\ref{InverseProblem} (when it exists) is indeed unique up to this inherent ambiguity provided the $\mathbf{x}_i$ are sufficiently diverse and the generating matrix $\mathbf{A}$ satisfies the \textit{spark condition} from compressive sensing (CS):
+\begin{align}\label{SparkCondition}
+\mathbf{A}\mathbf{x}_1 = \mathbf{A}\mathbf{x}_2 \implies \mathbf{x}_1 = \mathbf{x}_2, \ \ \ \text{for all $k$-sparse } \mathbf{x}_1, \mathbf{x}_2,
+\end{align}
+%
+which would be, in any case, necessary for uniqueness. Our concern here is the stability of these solutions with respect to noise in the data.
 
@@
 % \mbox{$Y = \{\mathbf{A} \mathbf{x}_1, \ldots, \mathbf{A}\mathbf{x}_N\}$} 
-has a stable $k$-sparse linear representation and fix $\delta_1, \delta_2$ to be the desired recovery accuracy in \eqref{def1}.
+has a stable $k$-sparse representation in $m$ dimensions and fix $\delta_1, \delta_2$ to be the desired recovery accuracy in \eqref{def1}.
 Consider now any dataset $Z$ generated as in \eqref{LinearModel} with $\eta \leq \frac{1}{2} \varepsilon(\delta_1, \delta_2)$.
 Then from the triangle inequality, it follows that any matrix $\mathbf{B}$ and $k$-sparse $\mathbf{\bar x}_1, \ldots, \mathbf{\bar x}_N \in \mathbb{R}^m$ solving Prob.~\ref{InverseProblem} are necessarily close to the original dictionary $\mathbf{A}$ and sparse codes $\mathbf{x}_i$.
-
-Previous theoretical work on Prob.~\ref{InverseProblem} has adressed only the noiseless case $\eta =0$ (e.g., \cite{li2004analysis, Georgiev05, Aharon06, Hillar15}), showing that a solution (when it exists) is indeed unique provided the $\mathbf{x}_i$ are sufficiently diverse and the generating matrix $\mathbf{A}$ satisfies the \textit{spark condition} from compressed sensing (CS):
-\begin{align}\label{SparkCondition}
-\mathbf{A}\mathbf{x}_1 = \mathbf{A}\mathbf{x}_2 \implies \mathbf{x}_1 = \mathbf{x}_2, \ \ \ \text{for all $k$-sparse } \mathbf{x}_1, \mathbf{x}_2,
-\end{align}
-%
-which would be, in any case, necessary for uniqueness.
 
@@
 We then prove our main theorem (Thm.~\ref{DeterministicUniquenessTheorem}) in Sec.~\ref{DUT} after stating some additional definitions and lemmas required for the proof, including a useful result in combinatorial matrix analysis (Lem.~\ref{MainLemma}).
-We also give a simple argument extending our uniqueness guarantees to the following more common optimization formulation of the sparse coding problem (Cor.~\ref{SLCopt}).
+We also give a simple argument extending our guarantees to the following more common optimization formulation of the dictionary learning problem (Cor.~\ref{SLCopt}).
 
@@
 Finally, we present several applications in Discussion Sec.~\ref{Discussion}.
-These include: 1) a sufficient diversity of sparse codes sent through a random linear compressive channel are identifiable and 2) an explanation for universal representation of natural signals in sparse coding models from neuroscience.
 

### 2017-04-12 manuscripts/PNAS/chazthm_pnas.tex
results edit

@@
 
-\significancestatement{Many naturally occurring signals (visual scenery, speech, EEG, etc.) lacking domain-specific formal models can nonetheless be usefully characterized as parsimonious combinations of elementary waveforms drawn from a large `dictionary'.
-We give general conditions guaranteeing when such dictionaries are uniquely and stably determined by enough data.
-The result justifies the application of this model to problems in blind source separation, and may help to explain the observed universality of emergent representations in sparse coding models of some natural phenomena.
+\significancestatement{Many naturally occurring signals (visual scenery, speech, EEG, etc.) lacking domain-specific formal models can nonetheless be usefully characterized as combinations of few elementary waveforms drawn from a large `dictionary'.
+We give general conditions guaranteeing when such dictionaries are uniquely and stably determined by data.
+The result justifies the application of this model to blind source separation, and may help to explain the observed universality of emergent representations in sparse coding models of some natural phenomena.
 %These results provide theoretical grounding for  the application of dictionary learning to recovering sparse signals from unknown noisy compressive measurements.
@@
 
-Before stating our main results, we first identify the combinatorial criteria on support sets of generating codes allowing for stable sparse 
-representations.  Let $\{1, \ldots, m\}$ be denoted $[m]$, its power set $2^{[m]}$, and ${[m] \choose k}$ the set of subsets of $[m]$ of size $k$. 
+Before stating our main results, we first identify combinatorial criteria on the support sets of generating codes that demand stable sparse representations.
+Letting $\{1, \ldots, m\}$ be denoted $[m]$, its power set $2^{[m]}$, and ${[m] \choose k}$ the set of subsets of $[m]$ of size $k$,
 % Let $\text{\rm Span}\{\mathbf{v}_1, \ldots, \mathbf{v}_\ell\}$ be the $\mathbb{R}$-linear span of vectors $\mathbf{v}_1, \ldots, \mathbf{v}_\ell$. 
-A vector $\mathbf{x}$ is said to be \emph{supported} on $S \subseteq [m]$ %,
-when $\mathbf{x} \in \text{\rm Span} \{\mathbf{e}_j\}_{j\in S}$, where $\mathbf{e}_j$ are the standard basis in $\mathbb R^m$.  We also write
- supp$(\mathbf{x}) = S$ when $S$ indexes the nonzero components of $\mathbf{x}$.
-Let $\mathbf{M}_S$ be the submatrix formed by the columns of $\mathbf{M}$ indexed by $S$, where we set $\text{\rm Span}\{\mathbf{M}_\emptyset\} := \{\textbf{0}\}$.
-
-We say a hypergraph $E \subseteq 2^{[m]}$ on vertices $[m]$ is \textit{$k$-uniform} when every $S \in E$ has cardinality $k$.
+we say a hypergraph $E \subseteq 2^{[m]}$ on vertices $[m]$ is \textit{$k$-uniform} when in fact $E \subseteq {[m] \choose k}$.
 We also say $E$ is \emph{regular} when every element of $[m]$ is contained in exactly $\ell$ elements of $E$ for some $\ell > 0$ (for given $\ell$, we say $E$ is \textit{$\ell$-regular}).
@@
 \begin{definition}\label{sip}
-Given $E \subseteq 2^{[m]}$, the \textbf{star} $F(i)$ at $i$ are those $S \in E$ with $i \in S$.
-We say $E$ has the \textbf{singleton intersection property} (\textbf{SIP}) when $\cap_{S \in F(i)} S = \{i\}$ for all $i \in [m]$.
+Given $E \subseteq 2^{[m]}$, the \textbf{star} $F(i)$ at $i$ is the set of $S \in E$ with $i \in S$.
+We say $E$ has the \textbf{singleton intersection property} (\textbf{SIP}) when $\cap F(i) = \{i\}$ for all $i \in [m]$.
 \end{definition}
@@
 
+The following theorem is the precise statement of our main result. 
+A vector $\mathbf{x}$ is said to be \emph{supported} on $S \subseteq [m]$ %,
+when $\mathbf{x} \in \text{\rm Span} \{\mathbf{e}_j\}_{j\in S}$, where $\mathbf{e}_j$ are the standard basis in $\mathbb R^m$.
+Denote by $\mathbf{M}_S$ the submatrix formed by the columns of $\mathbf{M}$ indexed by $S$, where we set $\text{\rm Span}\{\mathbf{M}_\emptyset\} := \{\textbf{0}\}$, and similarly by $\mathbf{x}^J$ the subvector formed from the entries of $\mathbf{x}$ indexed by $J$.
 We say that a set of $k$-sparse vectors is in \emph{general linear position} when any $k$ of them are linearly independent.
-The following is the precise statement of our main result.
 
@@
 Let $\mathbf{A}~\in~\mathbb{R}^{n \times m}$ satisfy \eqref{SparkCondition} for $k < m$, and suppose for some $\bar m$ that more than \mbox{$(k-1){\bar m \choose k}$} $k$-sparse \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} are supported in general linear position on each set in an $\ell$-regular $E \subseteq {[m] \choose k}$ with the SIP.
-There is a constant $C_1 > 0$ for which the following hold for $\varepsilon < L_2(\mathbf{A}) / C_1$.
+There is a constant\footnote{We delay defining the constant $C_1$ until Section \ref{DUT} (\eqref{Cdef1}).} $C_1 > 0$ for which the following holds for $\varepsilon < L_2(\mathbf{A}) / C_1$.
 
-1) Every matrix $\mathbf{B}$ and $k$-sparse $\mathbf{\bar x}_1, \ldots, \mathbf{\bar x}_N \in \mathbb{R}^{\bar m}$ with  \mbox{$\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\bar x}_i\|_2 \leq \varepsilon$} for all $i$ must have $\bar m \geq m$ and, provided $p = \bar m - \ell(\bar m - m)$ is positive, necessarily satisfy:
+Every matrix $\mathbf{B}$ and $k$-sparse $\mathbf{\bar x}_1, \ldots, \mathbf{\bar x}_N \in \mathbb{R}^{\bar m}$ with  \mbox{$\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\bar x}_i\|_2 \leq \varepsilon$} for all $i$ must have $\bar m \geq m$ and, provided $p = \bar m - \ell(\bar m - m)$ is positive, necessarily satisfy:
 \begin{align}\label{Cstable}
@@
 
-2) Restricting dictionaries and sparse codes to respective $J, \bar{J}$, we furthermore have that if $\varepsilon < L_{2k}(\mathbf{A}) / C_1$, then $\mathbf{B}$ also satisfies \eqref{SparkCondition} with $L_{2k}(\mathbf{B}\mathbf{PD}) \geq L_{2k}(\mathbf{A}) - C_1 \varepsilon$, and:
+Furthermore, if $\varepsilon < L_{2k}(\mathbf{A}) / C_1$, then $\mathbf{B}_{\bar J}$ also satisfies \eqref{SparkCondition} with $L_{2k}(\mathbf{B}_{\bar J}\mathbf{PD}) \geq L_{2k}(\mathbf{A}_J) - C_1 \varepsilon$, and:
 \begin{align}\label{b-PDa}
-\|\mathbf{x}_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\bar x}_i\|_1 &\leq  \left( \frac{ 1+C_1 \|\mathbf{x}_i\|_1 }{ L_{2k}(\mathbf{A}) -  C_1\varepsilon } \right) \varepsilon,\ \ \   \text{for $i \in [N]$}.
+\|\mathbf{x}_i^J - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\bar x}_i^{\bar J}\|_1 &\leq  \left( \frac{ 1+C_1 \|\mathbf{x}_i^{J}\|_1 }{ L_{2k}(\mathbf{A}_J) -  C_1\varepsilon } \right) \varepsilon,\ \ \   \text{for $i \in [N]$}.
 \end{align}
@@
 
-%In other words, the smaller the difference $\bar m - m$, the more columns and coefficients of the original $n \times m$ dictionary $\mathbf{A}$ and $m$-dimensional codes $\mathbf{x}_i$ contained (up to noise) in the appropriately scaled $n \times \bar m$ dictionary $\mathbf{B}$ and $\bar m$-dimensional codes $\mathbf{\bar x}_i$.
+In other words, the smaller the difference $\bar m - m$, the more columns and coefficients of the original dictionary $\mathbf{A}$ and codes $\mathbf{x}_i$ contained (up to noise) in the appropriately scaled dictionary $\mathbf{B}$ and codes $\mathbf{\bar x}_i$.
 %In particular, when $\bar m = m$ all columns of $\mathbf{A}$ and coefficients of each $\mathbf{x}_i$ recoverable, as per Def.~\ref{maindef}. 
-
-An important consequence of Thm.~\ref{DeterministicUniquenessTheorem} is that \eqref{def1} is guaranteed provided $\varepsilon$ in Def.~\ref{maindef} does not exceed: % [*** TODO: verify this is still correct ***]
+The implication in the case $\bar{m} = m$ is precisely that $Y = \{\mathbf{Ax}_1, \ldots, \mathbf{Ax}_N\}$ has a stable $k$-sparse representation in $m$ dimensions, with \eqref{def1} guaranteed provided $\varepsilon$ in Def.~\ref{maindef} does not exceed:
 \begin{align}\label{epsdel}
@@
 \end{align}
-We delay defining the constant $C_1$ until Section \ref{DUT} (\eqref{Cdef1}).  % , since it requires additional definitions not critical to the statement of our results.
+  % , since it requires additional definitions not critical to the statement of our results.
 
 % Note also that Thm~\ref{DeterminsiticUniquenessTheorem} gives conditions for when a single solution to Problem~\ref{InverseProblem} in fact represents \emph{all} possible solutions, related by transformations of the form $PD$.
+
+In fact, it is straightforward to produce sparse codes in general linear position with a ``Vandermonde'' matrix construction (e.g., see \cite{Hillar15}). We therefore have:
 
@@
 \end{corollary}
-\begin{proof}
-The implication of Thm.\ref{DeterministicUniquenessTheorem} in the case $\bar{m} = m$ is precisely that such a $Y$ has a stable sparse representation (Def.~\ref{maindef}).
-It remains, therefore, only to produce sparse codes in general linear position.
-However, this is straightforward with a ``Vandermonde'' matrix construction (e.g., see \cite{Hillar15}).
-\end{proof}
 
@@
 As mentioned above, it is easy to construct a regular hypergraph $E \subseteq {[m] \choose k}$ with the SIP having cardinality $|E| = m$, implying the lower bound for sample size $N$ from the introduction.
-In many cases, the SIP can be achieved with $|E| < m$; for example, when $k = \sqrt{m}$ one can take $E$ to be the rows and columns formed by arranging $[m]$ in a square grid.
+In many cases, however, the SIP can be achieved with far fewer supports; for example, when $k = \sqrt{m}$ one can take $E$ to be the $2k$ rows and columns formed by arranging $[m]$ in a square grid.
 %In light of Cor.~\ref{DeterministicUniquenessCorollary}, it would be interesting to determine other such $E$.
@@
 
-There are other less direct consequences of Thm.~\ref{DeterministicUniquenessTheorem} to stability in sparse linear coding.
-For instance, consider its implications for the optimization problem posed in Prob.~\ref{SLCopt}.
+It turns out that Thm.~\ref{DeterministicUniquenessTheorem} also has implications for the optimization problem posed in Prob.~\ref{SLCopt}:
 
 \begin{corollary}\label{SLCopt}
-If the assumptions of Thm.\ref{DeterministicUniquenessTheorem} hold with more than $(k-1)\left[ {\bar m \choose k} + |E|k{m \choose k-1}\right]$ vectors $\mathbf{x}_i$ supported on each $S \in E$, then all solutions to Prob.~\ref{OptimizationProblem} necessarily satisfy implications 1) and 2) from Thm.~\ref{DeterministicUniquenessTheorem}.
+If all of the assumptions of Thm.\ref{DeterministicUniquenessTheorem} hold with more than $(k-1)\left[ {\bar m \choose k} + |E|k{m \choose k-1}\right]$ vectors $\mathbf{x}_i$ supported on each $S \in E$, then all solutions to Prob.~\ref{OptimizationProblem} necessarily satisfy the implications \eqref{Cstable} and \eqref{b-PDa} of Thm.~\ref{DeterministicUniquenessTheorem}.
 \end{corollary}
@@
 
-Another straightforward application of Thm.~\ref{DeterministicUniquenessTheorem} is a probabilistic extension made possible by noticing that the spark condition has an analytic characterization.
+Another straightforward extension of Thm.~\ref{DeterministicUniquenessTheorem} applies to probabilistic scenarios and follows from the following analytic characterization of the spark condition.
 Let $\mathbf{A}$  be the $n \times m$ matrix of $nm$ indeterminates $A_{ij}$.
@@
 \begin{theorem}\label{robustPolythm}
-There is a polynomial in the entries of $\mathbf{A}$ and $\mathbf{x}_i$ with the following property:  if the polynomial evaluates to a nonzero number and more than \mbox{$(k-1){m \choose k}$} of the resulting $\mathbf{x}_i$ are supported on each $S \in E$ for some regular $E \subseteq {[m] \choose k}$ with the SIP, then $Y$ has a stable $k$-sparse representation in $m$ dimensions (Def.~\ref{maindef}).
-In particular, no substitutions impart to $Y$ this property or all but a Borel set of measure zero do.
+There is a polynomial $g$ in the entries of $\mathbf{A}$ and $\mathbf{x}_i$ with the following property:  if $g$ evaluates to a nonzero number and more than \mbox{$(k-1){m \choose k}$} of the resulting $\mathbf{x}_i$ are supported on each $S \in E$ for some regular $E \subseteq {[m] \choose k}$ with the SIP, then $Y$ has a stable $k$-sparse representation in $m$ dimensions (Def.~\ref{maindef}).
+In particular, either no substitutions impart to $Y$ this property or all but a Borel set of measure zero do.
 \end{theorem}
@@
 
-Thus, choosing dictionary and sparse codes ``randomly'' generate data with stable sparse representations almost certainly.
+Thus, choosing dictionary and sparse codes ``randomly'' from \emph{any} continuous distribution generates data with stable sparse representations almost certainly.
 % , as long as the relevant parameters satisfy \eqref{CScondition}.

### 2017-04-12 manuscripts/PNAS/chazthm_pnas.tex
chaz edits

@@
 \significancestatement{Many naturally occurring signals (visual scenery, speech, EEG, etc.) lacking domain-specific formal models can nonetheless be usefully characterized as combinations of few elementary waveforms drawn from a large `dictionary'.
-We give general conditions guaranteeing when such dictionaries are uniquely and stably determined by data.
-The result justifies the application of this model to blind source separation, and may help to explain the observed universality of emergent representations in sparse coding models of some natural phenomena.
+We give general conditions guaranteeing when such dictionaries are uniquely and stably determined by data, justifying the application of this model as a constraint in blind source separation.
+We suggest the result may help explain the observed universality of emergent representations in sparse coding models of some natural phenomena.
 %These results provide theoretical grounding for  the application of dictionary learning to recovering sparse signals from unknown noisy compressive measurements.
@@
 
-Before stating our main results, we first identify combinatorial criteria on the support sets of generating codes that demand stable sparse representations.
+Before stating our main results, we first identify combinatorial criteria on the support sets of generating codes that imply stable sparse representations.
 Letting $\{1, \ldots, m\}$ be denoted $[m]$, its power set $2^{[m]}$, and ${[m] \choose k}$ the set of subsets of $[m]$ of size $k$,
@@
 
-The following theorem is the precise statement of our main result. 
-A vector $\mathbf{x}$ is said to be \emph{supported} on $S \subseteq [m]$ %,
-when $\mathbf{x} \in \text{\rm Span} \{\mathbf{e}_j\}_{j\in S}$, where $\mathbf{e}_j$ are the standard basis in $\mathbb R^m$.
+A vector $\mathbf{x}$ is said to be \emph{supported} on $S \subseteq [m]$ when $\mathbf{x} \in \text{\rm Span} \{\mathbf{e}_j\}_{j\in S}$, where $\mathbf{e}_j$ are the standard basis in $\mathbb R^m$.
 Denote by $\mathbf{M}_S$ the submatrix formed by the columns of $\mathbf{M}$ indexed by $S$, where we set $\text{\rm Span}\{\mathbf{M}_\emptyset\} := \{\textbf{0}\}$, and similarly by $\mathbf{x}^J$ the subvector formed from the entries of $\mathbf{x}$ indexed by $J$.
-We say that a set of $k$-sparse vectors is in \emph{general linear position} when any $k$ of them are linearly independent.
+A set of $k$-sparse vectors is said to be in \emph{general linear position} when any $k$ of them are linearly independent.
+The following is a precise statement of our main result.
 
@@
 
-In other words, the smaller the difference $\bar m - m$, the more columns and coefficients of the original dictionary $\mathbf{A}$ and codes $\mathbf{x}_i$ contained (up to noise) in the appropriately scaled dictionary $\mathbf{B}$ and codes $\mathbf{\bar x}_i$.
+To be clear, Thm.~\ref{DeterministicUniquenessTheorem} says that the smaller the difference $\bar m - m$, the more columns and coefficients of the original dictionary $\mathbf{A}$ and codes $\mathbf{x}_i$ contained (up to noise) in the appropriately scaled dictionary $\mathbf{B}$ and codes $\mathbf{\bar x}_i$.
 %In particular, when $\bar m = m$ all columns of $\mathbf{A}$ and coefficients of each $\mathbf{x}_i$ recoverable, as per Def.~\ref{maindef}. 
@@
 
-In fact, it is straightforward to produce sparse codes in general linear position with a ``Vandermonde'' matrix construction (e.g., see \cite{Hillar15}). We therefore have:
+It so happens that producing sparse codes in general linear position is straightforward with a ``Vandermonde'' matrix construction (e.g., see \cite{Hillar15}). We therefore have:
 
@@
 %Note that every $\ell$-regular hypergraph $E \subseteq {[m] \choose k}$ satisfies: \[|E|k = \sum_{S \in E}|S| = \sum_{i \in [m]} \deg(i) = \ell m.\] 
-As mentioned above, it is easy to construct a regular hypergraph $E \subseteq {[m] \choose k}$ with the SIP having cardinality $|E| = m$, implying the lower bound for sample size $N$ from the introduction.
+As already mentioned, it is easy to construct a regular hypergraph $E \subseteq {[m] \choose k}$ with the SIP having cardinality $|E| = m$, implying the lower bound for sample size $N$ from the introduction.
 In many cases, however, the SIP can be achieved with far fewer supports; for example, when $k = \sqrt{m}$ one can take $E$ to be the $2k$ rows and columns formed by arranging $[m]$ in a square grid.
@@
 
-It turns out that Thm.~\ref{DeterministicUniquenessTheorem} also has implications for the optimization problem posed in Prob.~\ref{SLCopt}:
+There are other less direct consequences of Thm.~\ref{DeterministicUniquenessTheorem}. For instance, it has the following implications for the optimization problem posed in Prob.~\ref{SLCopt}:
 
@@
 
-Another straightforward extension of Thm.~\ref{DeterministicUniquenessTheorem} applies to probabilistic scenarios and follows from the following analytic characterization of the spark condition.
+Another extension of Thm.~\ref{DeterministicUniquenessTheorem} follows from the following analytic characterization of the spark condition.
 Let $\mathbf{A}$  be the $n \times m$ matrix of $nm$ indeterminates $A_{ij}$.
@@
 
-Thus, choosing dictionary and sparse codes ``randomly'' from \emph{any} continuous distribution generates data with stable sparse representations almost certainly.
+Thus, choosing the dictionary and sparse codes ``randomly'' from \emph{any} continuous distribution generates data with stable sparse representations almost certainly.
 % , as long as the relevant parameters satisfy \eqref{CScondition}.
-
 %Next, we address the case when only an upper bound $m'$ on the latent dimension $m$ is known (assuming that $\mathbf{B}$ satisfies \eqref{SparkCondition}).
@@
 % ======== b - PDa =========
-First note that $\|\mathbf{x}\|_1 \leq \sqrt{k} \|\mathbf{x}\|_2$ for $k$-sparse $\mathbf{x} \in \mathbb{R}^m$, which by definition of $L_k(A)$ implies the following often used inequality:
+First, note that $\|\mathbf{x}\|_1 \leq \sqrt{k} \|\mathbf{x}\|_2$ for $k$-sparse $\mathbf{x} \in \mathbb{R}^m$, which by definition of $L_k(A)$ implies the following inequality:
 \begin{align}\label{delrho}
 L_k(\mathbf{A}) \leq \frac{\|\mathbf{A}\mathbf{x}\|_2}{\sqrt{k} \|\mathbf{x}\|_2} %\leq \frac{\|\mathbf{x}\|_1}{\sqrt{k} \|\mathbf{x}\|_2} \max_{i \in [m]}\|\mathbf{A}_i\|_2 
-\leq  \max_{j \in [m]}\|\mathbf{A}_j\|_2.
+\leq  \max_{j \in [m]}\|\mathbf{A}_j\|_2,
 \end{align}
+%
+which we frequently use.
 
-Our first step is to show how dictionary recovery \eqref{Cstable} already implies sparse code recovery \eqref{b-PDa} when \mbox{$\varepsilon < L_{2k}(\mathbf{A}) / C_1$}.
+We begin by showing how dictionary recovery \eqref{Cstable} already implies sparse code recovery \eqref{b-PDa} when \mbox{$\varepsilon < L_{2k}(\mathbf{A}) / C_1$}, assuming without loss of generality that $\bar m = m$.
 For $2k$-sparse $\mathbf{x} \in \mathbb{R}^m$, the triangle inequality gives \mbox{$\|(\mathbf{A}-\mathbf{BPD})\mathbf{x}\|_2  \leq C_1\varepsilon \|\mathbf{x}\|_1 \leq C_1 \varepsilon \sqrt{2k}  \|\mathbf{x}\|_2$}.
@@
 %where we drop the absolute value due to the upper bound on $\varepsilon$. 
-Hence, $L_{2k}(\mathbf{BPD}) \geq L_{2k}(\mathbf{A}) - C_1\varepsilon  > 0$ and \eqref{b-PDa} then follows from:
+Hence, $L_{2k}(\mathbf{BPD}) \geq L_{2k}(\mathbf{A}) - C_1\varepsilon  > 0$. \eqref{b-PDa} then follows from:
 \begin{align*}
@@
 &\leq \frac{\|\mathbf{BPD}(\mathbf{x}_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\bar x}_i)\|_2}{L_{2k}(\mathbf{BPD})} \\
-&\leq \frac{\|\mathbf{B}\mathbf{\bar x}_i - \mathbf{A}\mathbf{x}_i\|_2 + \|(\mathbf{A} - \mathbf{BPD})\mathbf{x}_i\|_2}{L_{2k}(\mathbf{BPD})} \\
-&\leq \frac{\varepsilon (1+C_1 \|\mathbf{x}_i\|_1)}{L_{2k}(\mathbf{BPD})}.
+&\leq \frac{\|(\mathbf{BPD} - \mathbf{A})\mathbf{x}_i\|_2 + \|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\bar x}_i\|_2}{L_{2k}(\mathbf{BPD})} \\
+&\leq \frac{\varepsilon (1 + C_1 \|\mathbf{x}_i\|_1)}{L_{2k}(\mathbf{BPD})}.
 %&\leq \frac{\varepsilon}{\sqrt{2k}} \left( \frac{ 1+C_1 \|\mathbf{x}_i\|_1 }{ L_{2k}(\mathbf{A}) -  C_1\varepsilon } \right).
@@
 
-The heart of the matter is therefore \eqref{Cstable}, which we now finally establish, but first in the important special case $k = 1$.
+The heart of the matter is therefore \eqref{Cstable}, which we now finally establish, first in the important special case $k = 1$.
 
@@
 \begin{proof}[Proof of Thm.~\ref{DeterministicUniquenessCorollary} for $k=1$]
-The only 1-uniform hypergraph with the SIP is $[m]$; hence, we have $\mathbf{x}_i = c_i \mathbf{e}_i$ for $c_i \in \mathbb{R} \setminus \{\mathbf{0}\}$, $i \in [m]$.
-In this case, we may take $C_1 = 1/ \min_{\ell \in [m]} |c_{\ell}|$.
+Since the only 1-uniform hypergraph with the SIP is $[m]$, we have $\mathbf{x}_i = c_i \mathbf{e}_i$ for $c_i \in \mathbb{R} \setminus \{\mathbf{0}\}$, $i \in [m]$.
+In this case, we may take any $C_1 \geq 1/ \min_{\ell \in [m]} |c_{\ell}|$.
 
-Fix $\mathbf{A} \in \mathbb{R}^{n \times m}$ satisfying \eqref{SparkCondition} and suppose that for some $\mathbf{B} \in \mathbb{R}^{n \times \bar m}$ and $1$-sparse $\mathbf{\bar x}_i \in \mathbb{R}^{\bar m}$ we have  $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\bar x}_i\|_2 \leq \varepsilon < L_2(\mathbf{A}) / C_1$ for all $i$.
-Then, there are $\bar{c}_1, \ldots, \bar{c}_m \in \mathbb{R}$ and a map $\pi: [m] \to [\bar m]$ with:
+Fix $\mathbf{A} \in \mathbb{R}^{n \times m}$ satisfying \eqref{SparkCondition} and suppose that for some $\mathbf{B}$ and $1$-sparse $\mathbf{\bar x}_i \in \mathbb{R}^{\bar m}$ we have  $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\bar x}_i\|_2 \leq \varepsilon < L_2(\mathbf{A}) / C_1$ for all $i$.
+Then, there exist $\bar{c}_1, \ldots, \bar{c}_m \in \mathbb{R}$ and a map $\pi: [m] \to [\bar m]$ such that:
 \begin{align}\label{1D}
@@
 
-We  now show that $\pi$ is injective (and thus is a permutation if $\bar m = m$).
+We  now show that $\pi$ is injective (in particular, a permutation if $\bar m = m$).
 Suppose that $\pi(i) = \pi(j) = \ell$ for some $i \neq j$ and $\ell$.
@@
 which contradicts the bound $\varepsilon < L_2(\mathbf{A})/C_1$.
-Hence, the map $\pi$ is injective and $\bar m \geq m$.
+Hence, the map $\pi$ is injective and therefore $\bar m \geq m$.
 Setting $J = [m]$, $\bar J = \pi([m])$, and letting $P = \left( \mathbf{e}_{\pi(1)} \cdots \mathbf{e}_{\pi(m)}\right)$ and $D = \text{diag}(\frac{\bar{c}_1}{c_1},\ldots,\frac{\bar{c}_m}{c_m})$, we see that \eqref{1D} becomes, for all $j \in [m]$:
@@
 We require a few additional tools to extend the proof to the general case $k < m$.
-These include a general notion of distance (Def.~\ref{dDef}) and angle (Def.~\ref{FriedrichsDefinition}) between subspaces and a stability result in matrix analysis (Lem.~\ref{MainLemma}).
+These include a general notion of distance (Def.~\ref{dDef}) and angle (Def.~\ref{FriedrichsDefinition}) between subspaces and a stability result in combinatorial matrix analysis (Lem.~\ref{MainLemma}).
 
 \begin{definition}\label{dDef}
-For $\mathbf{u} \in \mathbb R^m$, let $\text{\rm dist}(\mathbf{u}, V) := \inf \{\| \mathbf{u}-\mathbf{v} \|_2: \mathbf{v} \in V\}$, and for vector spaces $U,V \subseteq \mathbb{R}^m$, define:
+For $\mathbf{u} \in \mathbb R^m$ and vector spaces $U,V \subseteq \mathbb{R}^m$, let $\text{\rm dist}(\mathbf{u}, V) := \inf \{\| \mathbf{u}-\mathbf{v} \|_2: \mathbf{v} \in V\}$ and define:
 %\footnote{Although identical, note the reference \cite{Morris10} defines the supremum over the unit ball.}: %[Kato p.197]
@@
 
-Our result in combinatorial matrix theory is the following.
+Our result in combinatorial matrix analysis is the following.
 
@@
 
-Given vectors $\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$, we let $\mathbf{X}$ be the $m \times N$ matrix with columns $\mathbf{x}_i$ and $I(S) := \{i \in [N]: \text{supp}(\mathbf{x}_i) \subseteq S\}$.
 The constant $C_1$ in Thm.~\ref{DeterministicUniquenessTheorem} is then defined by\footnote{Note that $\|\mathbf{AX}_{I(S)}\mathbf{c}\|_2 \geq \sqrt{k} L_k(\mathbf{A})\|\mathbf{X}_{I(S)}\mathbf{c}\|_2 \geq k L_k(\mathbf{A}) L_k(\mathbf{X}_{I(S)})\|\mathbf{c}\|_2$ for $S \in E$ and $k$-sparse $\mathbf{c}$.
 Therefore, $\sqrt{k} L_k(\mathbf{AX}_{I(S)}) \geq k L_k(\mathbf{A}) L_k(\mathbf{X}_{I(S)}) > 0$ since $L_k(\mathbf{A}), L_k(\mathbf{X}_{I(S)}) > 0$ by \eqref{SparkCondition} and general linear position of the $\mathbf{x}_i$.
-Thus, $C_1 > 0$.
-}:
+Thus, $C_1 > 0$.}:
 \begin{align}\label{Cdef1}
@@
 \end{align}
+%, we let 
+where, given vectors $\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$, we denote by $\mathbf{X}$ the $m \times N$ matrix with columns $\mathbf{x}_i$ and by $I(S)$ the set of indices $i$ for which the support of $\mathbf{x}_i$ is contained in $S$.
+% := \{i \in [N]: \text{supp}(\mathbf{x}_i) \subseteq S\}$.
 
-The constant $C_2 = C_2(\mathbf{A}, E)$ is given below in terms of one used in \cite{Deutsch12} to analyze the convergence of the alternating projections algorithm.
-% for projecting a point onto the intersection of a set of subspaces. 
-We use it to bound the distance between a point and the intersection of a set of subspaces given an upper bound on its distance from each subspace individually.
+The constant $C_2 = C_2(\mathbf{A}, E)$ is given in turn below, in terms of one used in \cite{Deutsch12} to analyze the convergence of the alternating projections algorithm for projecting a point onto an intersection of subspaces.
+We use it to bound the distance between a point and the intersection of subspaces given an upper bound on its distance from each individual subspace.
 
@@
 \begin{align}\label{Cdef2}
-C_2(\mathbf{A}, E) := \frac{ 2^{|E|} \max_{j \in [m]} \|\mathbf{A}_j\|_2}{ \min_{F \subseteq E} r( \{ \text{\rm Span}\{\mathbf{A}_{S}\} \}_{S \in F}) }.
+C_2(\mathbf{A}, E) := \frac{ 2^{|E|} \max_{j \in [m]} \|\mathbf{A}_j\|_2}{ \min_{F \subseteq E} r( \{ \text{\rm Span}\{\mathbf{A}_{S}\} \}_{S \in F}) },
 \end{align}
-Note that $k=1$ gives the same $C_1$ as that used to prove $k=1$.
+%
+which we remark is consistent with the assumption on $C_1$ in the proof of Thm.~\ref{DeterministicUniquenessTheorem} for the case $k=1$.
 
 \begin{proof}[Proof of Thm.~\ref{DeterministicUniquenessCorollary} for $k < m$] 
-We shall show that for every $S \in E$ there is some $\bar S \in {[\bar m] \choose k}$, for which the distance $d(\text{\rm Span}\{\mathbf{A}_S\}, \text{\rm Span}\{\mathbf{B}_{\bar S}\})$ is controlled by $\varepsilon$.
+We shall show that for every $S \in E$ there is some $\bar S \in {[\bar m] \choose k}$ for which the distance $d(\text{\rm Span}\{\mathbf{A}_S\}, \text{\rm Span}\{\mathbf{B}_{\bar S}\})$ is controlled by $\varepsilon$.
 Applying Lem.~\ref{MainLemma} with the map $\pi$ defined by $S \mapsto \bar S$ then completes the proof.
 
-Since there are $(k-1){\bar m \choose k}+1$ vectors $\mathbf{x}_i$ supported on $S$, the pigeonhole principle implies that there is some $\bar S \in {[\bar m] \choose k}$ and some set of $k$ indices $K$ such that the supports of all $\mathbf{x}_i$ and $\mathbf{\bar x}_i$ with $i \in K$ are contained in $S$ and $\bar S$, respectively.
+Since there are more than $(k-1){\bar m \choose k}$ vectors $\mathbf{x}_i$ supported on $S$, by the pigeonhole principle there must be some $\bar S \in {[\bar m] \choose k}$ and set of $k$ indices $K$ such that the supports of all $\mathbf{x}_i$ and $\mathbf{\bar x}_i$ with $i \in K$ are contained in $S$ and $\bar S$, respectively.
 
 %Let $\mathbf{X}$ and $\mathbf{\bar{X}}$ be the $m \times N$ matrices with columns $\mathbf{x}_i$ and $\mathbf{\bar x}_i$, respectively. 
-It follows from the general linear position of the $\mathbf{x}_i$ and the linear independence of every $k$ columns of $\mathbf{A}$ that $L_k(\mathbf{AX}_{K}) > 0$; that is, the columns of the $n \times k$ matrix $\mathbf{AX}_K$ form a basis for $\text{\rm Span}\{\mathbf{A}_{S}\}$.
+It follows from the general linear position of the $\mathbf{x}_i$ and the linear independence of every $2k$ columns of $\mathbf{A}$ that $L_k(\mathbf{AX}_{K}) > 0$; that is, the columns of the $n \times k$ matrix $\mathbf{AX}_K$ form a basis for $\text{\rm Span}\{\mathbf{A}_{S}\}$.
 Fixing $\mathbf{0} \neq \mathbf{y} \in \text{\rm Span}\{\mathbf{A}_{S}\}$, there exists $\mathbf{0} \neq \mathbf{c} = (c_1, \ldots, c_k) \in \mathbb{R}^k$ such that $\mathbf{y} = \mathbf{AX}_K\mathbf{c}$.
@@
 \end{align*}
-where the last inequality follows directly from the definition of $L_k$. Finally, from Def.~\ref{dDef}, it follows that:
+where the last inequality follows directly from the definition of $L_k$. Finally, from Def.~\ref{dDef} we have:
 \begin{align}\label{rhs222}
 d(\text{\rm Span}\{\mathbf{A}_S\}, \text{\rm Span}\{\mathbf{B}_{\bar S}\}) 
-\leq \frac{\varepsilon}{  L_k(\mathbf{AX}_{K}) }.
+\leq \frac{\varepsilon}{  L_k(\mathbf{AX}_{K}) },
 \end{align}
-In particular, with $C_1$ as in \eqref{Cdef1}, the theorem follows.
+%
+from which the result follows by \eqref{Cdef1} and Lem.~\ref{MainLemma}.
+%With $C_1$ as in 
 \end{proof}
@@
 By the pigeonhole principle, there is some $S \in E$ supporting $k$ or more of the corresponding $\mathbf{x}_i$; let them be indexed by $K \subseteq I(S)$.
-By the argument as in the proof of Thm.\ref{DeterministicUniquenessTheorem}, we also have \eqref{rhs222}.
-Since our bound on $\varepsilon$ implies that the right-hand side of \eqref{rhs222} is less than one, by \eqref{dimLem} we have the contradiction: \[k = \dim(\text{Span}(\mathbf{A}_S)) \leq \dim(\text{Span}\{\mathbf{B}_{\bar S}\}) \leq |\bar S|.\]
+By the same argument as in the proof of Thm.\ref{DeterministicUniquenessTheorem}, we also have \eqref{rhs222}.
+Our bound on $\varepsilon$ implies the right-hand side of \eqref{rhs222} is less than one; hence, by \eqref{dimLem} we have the contradiction:
+\[k = \dim(\text{Span}(\mathbf{A}_S)) \leq \dim(\text{Span}\{\mathbf{B}_{\bar S}\}) \leq |\bar S|.\]
 
-Hence, the total number of $(k-1)$-sparse vectors $\mathbf{\bar x}_i$ is no greater than $|E|(k-1){ m \choose k-1}$.
-Taking \eqref{eqn} into account, no more than $|E|k(k-1){ m \choose k-1}$ vectors $\mathbf{\bar x}_i$ are \emph{not} $k$-sparse.
-Since for every $S \in E$ there are over $(k-1)\left[ {\bar m \choose k} + |E|k{ m \choose k-1} \right]$ vectors $\mathbf{x}_i$ supported there, it follows that more than $(k-1){\bar m \choose k}$ of them must have corresponding $\mathbf{\bar x}_i$ that are also $k$-sparse.
+The total number of $(k-1)$-sparse vectors $\mathbf{\bar x}_i$ can thus no greater than $|E|(k-1){ \bar m \choose k-1}$.
+Taking \eqref{eqn} into account, no more than $|E|k(k-1){ \bar m \choose k-1}$ vectors $\mathbf{\bar x}_i$ are \emph{not} $k$-sparse.
+Since for every $S \in E$ there are over $(k-1)\left[ {\bar m \choose k} + |E|k{ \bar m \choose k-1} \right]$ vectors $\mathbf{x}_i$ supported there, it follows that more than $(k-1){\bar m \choose k}$ of them must have corresponding $\mathbf{\bar x}_i$ that are also $k$-sparse.
 The result now follows directly from Thm.~\ref{DeterministicUniquenessCorollary}.

### 2017-04-12 manuscripts/PNAS/chazthm_pnas.tex
done?

@@
 
-In this note, we generalize the approach of \cite{Hillar15} to prove the stability of unique solutions to Probs.~\ref{InverseProblem} and \ref{OptimizationProblem} while also significantly reducing the known sample complexity.
+In this note, we generalized the approach of \cite{Hillar15} to prove the stability of unique solutions to Probs.~\ref{InverseProblem} and \ref{OptimizationProblem} and significantly reduce the known sample complexity.
 % FRITZ: Inverse problems instead of Data Analysis.
@@
 Focus on them (probabilistic ones too).
-Our results provide theoretical support to the application of the sparse linear coding model to blind source separation problems, wherein the goal is to infer the generating dictionary and sparse codes from noisy measurements, \eqref{LinearModel}.
+Our results justify the application of the sparse linear coding model to blind source separation problems, wherein the goal is to infer the generating dictionary and sparse codes from noisy measurements, \eqref{LinearModel}.
 We also collect a set of useful mathematical tools and basic facts for future research.
@@
 What we have shown here is that the sparse linear coding model generally produces a \textit{well-posed} inverse problem to be approximately solved by a numerical algorithm.
-This early concept of Hadamard \cite{Hadamard1902} can be paraphrased as the idea that inferences from observations should be robust to the inevitable uncertainty in measurement; that is, continuous in the data.
-In other words, perturbing a dataset by a small amount should only slightly influence the inferred parameters.
+This early concept of Hadamard \cite{Hadamard1902} can be paraphrased as the idea that inferences from observations should be robust to the inevitable uncertainty in measurement.
+In other words, a small perturbation of the data should result in only slightly different inferred parameters.
 In this regard, for the sparse linear coding model we demonstrate a linear relationship, \eqref{epsdel}, between measurement noise and the deviation of any solution from the true parameters, with explicit constants expressed in terms of these parameters.
-Moreover, we show that even if the meta-parameter defining the number of dictionary elements is overestimated, a subset of parameters may still be identifiable.
-We remark that our uniqueness result accounts for deterministic ``worst-case'' noise, whereas the ``effective'' noise might be smaller when sampled from a distribution; in such cases, the constants %Thms.~\ref{DeterministicUniquenessTheorem},~\ref{DeterministicUniquenessTheorem2}
+Moreover, we show that even if the meta-parameter for the number of dictionary elements is overestimated, a subset of parameters may still be identifiable up to noise.
+It would therefore be of practical utility to determine the best possible dependence of $\varepsilon$ on $\delta_1, \delta_2$ in Def.\ref{maindef} as well as the minimal requirements on the number and diversity of generating codes, and we hope that other researchers continue to improve and extend our results.
+We remark that our constants have been derived for deterministic ``worst-case'' noise, whereas the ``effective'' noise might be smaller when sampled from a distribution; in such cases, the constants %Thms.~\ref{DeterministicUniquenessTheorem},~\ref{DeterministicUniquenessTheorem2}
 will improve as well.
-It would therefore be of practical utility to determine the best possible dependence of $\varepsilon$ on $\delta_1, \delta_2$ in Def.\ref{maindef} as well as the minimal requirements on the number and diversity of generating codes, and we hope that other researchers continue to improve and extend our results.
 
@@
 In fact, uniqueness guarantees with minimal assumptions apply to all areas of data science and engineering that utilize learned sparse representations.
-For example, several groups have utilized compressive sensing for signal processing tasks: MRI analysis \cite{lustig2008compressed}, image compression \cite{Duarte08}, and, more recently, the design of an ultrafast camera \cite{Gao14}.
-Given such effective uses of compressive sensing, it is only a matter of time before these systems incorporate sparse representational learning to encode and process data (e.g., in a device that learns structure from motion \cite{kong2016prior}).
-In these cases, assurances such as those offered by our theorems certify that different devices (with different initialization, samples, etc.) are equivalent as soon as enough data originate from a statistically identical system.
+For example, several groups have applied compressive sensing to signal processing tasks: MRI analysis \cite{lustig2008compressed}, image compression \cite{Duarte08}, and, more recently, the design of an ultrafast camera \cite{Gao14}.
+Given such effective uses of compressive sensing, it is only a matter of time before these systems incorporate dictionary learning to encode and process data (e.g., in a device that learns structure from motion \cite{kong2016prior}).
+In these cases, assurances such as those offered by our theorems certify that different devices (with different initialization, samples, etc.) will learn equivalent representations given enough data from statistically identical systems.
 %Data science:
@@
 %\textbf{Theoretical Neuroscience}.
-Additionally, in the field of theoretical neuroscience, sparse dictionary learning and related methods have recovered characteristic components of natural images \cite{Olshausen96, hurri1996image, bell1997independent, van1998independent} and sounds \cite{bellsejnowski1996, smithlewicki2006, Carlson12}, reproducing response properties of cortical neurons.
-Our results suggest that this correspondence could be due to  sparse representations being ``universal'' in natural data, an early mathematical idea in neural theory \cite{pitts1947}.
-Furthermore, our guarantees justify the hypothesis of \cite{Coulter10, Isely10} that sparse codes passed through a communication bottleneck in the brain are recovered from random projections via (unsupervised) biologically plausible sparse coding (e.g., \cite{rehnsommer2007, rozell2007neurally, hu2014hebbian}).
+In the field of theoretical neuroscience in particular, dictionary learning for sparse coding and related methods have recovered characteristic components of natural images \cite{Olshausen96, hurri1996image, bell1997independent, van1998independent} and sounds \cite{bellsejnowski1996, smithlewicki2006, Carlson12} that reproduce response properties of cortical neurons.
+Our results suggest that this correspondence could be due to the ``universality'' of sparse representations in natural data, an early mathematical idea in neural theory \cite{pitts1947}.
+Furthermore, they justify the hypothesis of \cite{Coulter10, Isely10} that sparse codes passed through information bottlenecks in the brain are recovered from random projections via (unsupervised) biologically plausible sparse coding (e.g., \cite{rehnsommer2007, rozell2007neurally, hu2014hebbian}).
 

### 2017-04-12 manuscripts/PNAS/chazthm_pnas.tex
added a space lol

@@
 
-In this supplemental, we prove Lem.\ref{MainLemma} after stating auxiliary lemmas.
+In this supplemental, we prove Lem.~\ref{MainLemma} after stating auxiliary lemmas.
 
@@
 \end{proof}
-\begin{proof}[Proof of Lem.\ref{MainLemma}]
+
+\begin{proof}[Proof of Lem.~\ref{MainLemma}]
 We begin by showing that: 

### 2017-04-12 manuscripts/PNAS/chazthm_pnas.tex
ye

@@
 
-\significancestatement{Many naturally occurring signals (visual scenery, speech, EEG, etc.) lacking domain-specific formal models can nonetheless be usefully characterized as combinations of few elementary waveforms drawn from a large `dictionary'.
-We give general conditions guaranteeing when such dictionaries are uniquely and stably determined by data, justifying the application of this model as a constraint in blind source separation.
-We suggest the result may help explain the observed universality of emergent representations in sparse coding models of some natural phenomena.
+\significancestatement{Many naturally occurring signals (visual scenery, speech, EEG, etc.) lacking domain-specific formal models can nonetheless be usefully characterized as linear combinations of few elementary waveforms drawn from a large `dictionary'.
+We give general conditions guaranteeing when such dictionaries are uniquely and stably determined by data.
+%, justifying the application of this model as a constraint in blind source separation.
+The result may help explain the observed universality of emergent representations in sparse coding models of some natural phenomena.
 %These results provide theoretical grounding for  the application of dictionary learning to recovering sparse signals from unknown noisy compressive measurements.

### 2017-04-12 manuscripts/PNAS/chazthm_pnas.tex
chaz

@@
 Answers to this question also have other real-world implications.
-For example, a sparse coding analysis of local painting style can be used for forgery detection \cite{hughes2010, Olshausen10}, but only if the identifying sparse components of the artwork can be consistently estimated.
+For example, a sparse coding analysis of local painting style can be used for forgery detection \cite{hughes2010, Olshausen10}, but only if all dictionaries consistent with training data do not differ appreciably in their ability to sparsely encode new samples.
+%the identifying sparse components of the artwork can be consistently estimated.
 % are independent of implementation idiosyncrasies.
@@
 Fix $Y = \{ \mathbf{y}_1, \ldots, \mathbf{y}_N\} \subset \mathbb{R}^n$.
-We say $Y$ has a \textbf{$k$-sparse representation in $m$ dimensions} if there exists a matrix $\mathbf{A}$ and $k$-sparse $\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$ such that $\mathbf{y}_i = \mathbf{A}\mathbf{x}_i$ for all $i$.
+We say $Y$ has a \textbf{$k$-sparse representation in $\mathbb{R}^m$} if there exists a matrix $\mathbf{A}$ and $k$-sparse $\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$ such that $\mathbf{y}_i = \mathbf{A}\mathbf{x}_i$ for all $i$.
 %Equivalently, $\mathbf{Y} = \mathbf{A}\mathbf{X}$ for $\mathbf{Y}$ and $\mathbf{X}$ having the $\mathbf{y}_i$ and $\mathbf{x}_i$ as their columns, respectively.
@@
 % \mbox{$Y = \{\mathbf{A} \mathbf{x}_1, \ldots, \mathbf{A}\mathbf{x}_N\}$} 
-has a stable $k$-sparse representation in $m$ dimensions and fix $\delta_1, \delta_2$ to be the desired recovery accuracy in \eqref{def1}.
+has a stable $k$-sparse representation in $\mathbb{R}^m$ and fix $\delta_1, \delta_2$ to be the desired recovery accuracy in \eqref{def1}.
 Consider now any dataset $Z$ generated as in \eqref{LinearModel} with $\eta \leq \frac{1}{2} \varepsilon(\delta_1, \delta_2)$.
@@
 %In particular, when $\bar m = m$ all columns of $\mathbf{A}$ and coefficients of each $\mathbf{x}_i$ recoverable, as per Def.~\ref{maindef}. 
-The implication in the case $\bar{m} = m$ is precisely that $Y = \{\mathbf{Ax}_1, \ldots, \mathbf{Ax}_N\}$ has a stable $k$-sparse representation in $m$ dimensions, with \eqref{def1} guaranteed provided $\varepsilon$ in Def.~\ref{maindef} does not exceed:
+The implication in the case $\bar{m} = m$ is precisely that $Y = \{\mathbf{Ax}_1, \ldots, \mathbf{Ax}_N\}$ has a stable $k$-sparse representation in $\mathbb{R}^m$, with \eqref{def1} guaranteed provided $\varepsilon$ in Def.~\ref{maindef} does not exceed:
 \begin{align}\label{epsdel}
@@
 \begin{corollary}\label{DeterministicUniquenessCorollary}
-Given $n, m$, $k < m$, and a regular hypergraph $E \subseteq {[m] \choose k}$ with the SIP, there are $N =  |E| \left[ (k-1){m \choose k} + 1  \right]$ vectors \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} such that every matrix $\mathbf{A} \in \mathbb{R}^{n \times m}$ satisfying \eqref{SparkCondition} generates a dataset $Y = \{\mathbf{A}\mathbf{x}_1, \ldots, \mathbf{A}\mathbf{x}_N\}$ with a stable $k$-sparse representation in $m$ dimensions.
+Given $n, m$, $k < m$, and a regular hypergraph $E \subseteq {[m] \choose k}$ with the SIP, there are $N =  |E| \left[ (k-1){m \choose k} + 1  \right]$ vectors \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} such that every matrix $\mathbf{A} \in \mathbb{R}^{n \times m}$ satisfying \eqref{SparkCondition} generates a dataset $Y = \{\mathbf{A}\mathbf{x}_1, \ldots, \mathbf{A}\mathbf{x}_N\}$ with a stable $k$-sparse representation in $\mathbb{R}^m$.
 \end{corollary}
@@
 \begin{theorem}\label{robustPolythm}
-There is a polynomial $g$ in the entries of $\mathbf{A}$ and $\mathbf{x}_i$ with the following property:  if $g$ evaluates to a nonzero number and more than \mbox{$(k-1){m \choose k}$} of the resulting $\mathbf{x}_i$ are supported on each $S \in E$ for some regular $E \subseteq {[m] \choose k}$ with the SIP, then $Y$ has a stable $k$-sparse representation in $m$ dimensions (Def.~\ref{maindef}).
+There is a polynomial $g$ in the entries of $\mathbf{A}$ and $\mathbf{x}_i$ with the following property:  if $g$ evaluates to a nonzero number and more than \mbox{$(k-1){m \choose k}$} of the resulting $\mathbf{x}_i$ are supported on each $S \in E$ for some regular $E \subseteq {[m] \choose k}$ with the SIP, then $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$ (Def.~\ref{maindef}).
 In particular, either no substitutions impart to $Y$ this property or all but a Borel set of measure zero do.
@@
 and let the entries of $\mathbf{A} \in \mathbb{R}^{n \times m}$ and $k$-sparse $\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$ be drawn independently from probability measures absolutely continuous with respect to the standard Borel measure $\mu$.
-If more than $(k-1){m \choose k}$ of the vectors $\mathbf{x}_i$ are supported on each $S \in E$ for a regular $E \subseteq {[m] \choose k}$ with the SIP, then $Y$ has a stable $k$-sparse representation in $m$ dimensions with probability one.
+If more than $(k-1){m \choose k}$ of the vectors $\mathbf{x}_i$ are supported on each $S \in E$ for a regular $E \subseteq {[m] \choose k}$ with the SIP, then $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$ with probability one.
 \end{corollary}
@@
 \begin{proof} 
-Recall that orthogonal projection onto a subspace $V \subseteq \mathbb{R}^m$ is the mapping $\Pi_V: \mathbb{R}^m \to V$ that associates with each $\mathbf{x}$ its unique nearest point in $V$; i.e., $\|\mathbf{x} - \Pi_V\mathbf{x}\|_2 = \text{\rm dist}(\mathbf{x}, V)$.
+Recall the orthogonal projection onto a subspace $V \subseteq \mathbb{R}^m$ is the mapping $\Pi_V: \mathbb{R}^m \to V$ that associates with each $\mathbf{x}$ its unique nearest point in $V$; i.e., $\|\mathbf{x} - \Pi_V\mathbf{x}\|_2 = \text{\rm dist}(\mathbf{x}, V)$.
 Next, observe:
@@
 \end{align}
-for \mbox{$z^2= 1 - \prod_{\ell =1}^{k-1}(1-z_{\ell}^2)$} and \mbox{$z_{\ell} = \cos\theta\left(V_{\ell}, \cap_{s=\ell+1}^k V_s\right)$}.
-Together with $\Pi_{V_\ell} \Pi_V = \Pi_V$ for all $\ell \in [k]$ and $\Pi_V^2 = \Pi_V$ yields:
+for \mbox{$z^2= 1 - \prod_{\ell =1}^{k-1}(1-z_{\ell}^2)$} and \mbox{$z_{\ell} = \cos\theta\left(V_{\ell}, \cap_{s=\ell+1}^k V_s\right)$}, recalling $\theta$ from Def.~\ref{FriedrichsDefinition}.
+Together with $\Pi_{V_\ell} \Pi_V = \Pi_V$ for all $\ell \in [k]$ and $\Pi_V^2 = \Pi_V$, this yields:
 \begin{align*}
@@
 \begin{lemma}\label{NonEmptyLemma} 
-Fix $\ell, m$, and $\bar m$. Suppose $E \subseteq 2^{[m]}$ is $\ell$-regular with the SIP.  If $\pi: E \to 2^{[\bar m]}$ has $|S| = |\pi(S)|$ and:
+Fix $\ell, m$, and $\bar m$ such that $p = \bar m - \ell(\bar m - m)$ is positive.
+Suppose $E \subseteq 2^{[m]}$ is $\ell$-regular with the SIP.
+If a map $\pi: E \to 2^{[\bar m]}$ has $|S| = |\pi(S)|$ and:
 \begin{align}\label{cond}
-|\bigcap_{S \in F} \pi(S)| \leq |\bigcap_{S \in F} S |,\ \ \   \text{for } F \subseteq E,
+%|\bigcap_{S \in F} \pi(S)| \leq |\bigcap_{S \in F} S |,\ \ \   \text{for } F \subseteq E,
+|\cap \pi(F)| \leq |\cap F |,\ \ \   \text{for } F \subseteq E,
 \end{align}
-then $\bar m \geq m$ and the association $i \mapsto \cap \pi(F(i))$ defines an injective map from $J$ to $[\bar m]$ for some $J \subseteq [m]$ of size $p = \bar m - \ell(\bar m - m)$.
-In particular, if $\bar m = m$ then the map $\pi$ is induced by a permutation.
+then $\bar m \geq m$ and the association $i \mapsto \cap \pi(F(i))$ defines an injective map from $J$ to $[\bar m]$ for some $J \in {[m] \choose p}$.
+In particular, if $\bar m = m$ then $\pi$ is induced by a permutation on $[m]$.
 \end{lemma}
@@
 \begin{proof}
-First observe that assumption \eqref{cond} already constrains $\pi$ to be injective:  if $S_1 \neq S_2$, then $|\pi(S_1) \cap \pi(S_2)| \leq |S_1 \cap S_2| < \max\{|S_1|, |S_2|\} = \max\{|\pi(S_1)|, |\pi(S_2)|\}$, which implies that $\pi(S_1) \neq \pi(S_2)$.
+First, note that assumption \eqref{cond} already constrains $\pi$ to be injective:  if $S_1 \neq S_2$, then $|\pi(S_1) \cap \pi(S_2)| \leq |S_1 \cap S_2| < \max\{|S_1|, |S_2|\} = \max\{|\pi(S_1)|, |\pi(S_2)|\}$, which implies that $\pi(S_1) \neq \pi(S_2)$.
 Next, consider the collection of pairs: \[T_1 := \{(i, S): i \in \pi(S), S \in E\},\] which number $|T_1| = \sum_{S \in E} |\pi(S)| = \sum_{S \in E} |S| = \ell m$ by regularity of $E$.
-Our second observation is that $\bar m \geq m$.
-Otherwise, if $\bar m < m$, then by pigeonholing the $m \ell \geq \ell (\bar m + 1) \geq [(\ell + 1) - 1] \bar m + 1$ elements of $T_1$ with respect to the set $[\bar m]$ of possible first indices, there must exist at least $\ell + 1$ elements of $T_1$ having the same first index.
-But by \eqref{cond} and injectivity of $\pi$, we then have more than $\ell$ edges in $E$ with common element, a contradiction to regularity.
+We apply the pigeonhole principle to make two observations.
+The first is that $\bar m \geq m$.
+Otherwise, pigeonholing $\ell m > \ell \bar m$ elements of $T_1$ with respect to the set $[\bar m]$ of possible first indices would require at least $\ell + 1$ elements of $T_1$ to have the same first index.
+But by \eqref{cond} and injectivity of $\pi$, we then have more than $\ell$ edges in $E$ with a common element, contradicting regularity.
 
-Since $|T_1| > \bar m (\ell -1) + (p-1) \geq \bar m (\ell -1)$, the pigeonhole principle also implies that there are at least $\ell$ elements of $T_1$ sharing the same first coordinate.
+The second observation is that since $\ell m = \bar m (\ell - 1) + p$ and $p > 0$, there must be at least $\ell$ elements of $T_1$ sharing the same first coordinate.
 Let $F_1$ be the preimage of this family under $\pi$.
@@
 From the SIP, the intersection of sets in $F_1$ is $\{i_1\}$, which by \eqref{cond} implies that the intersection of $\pi(S)$ with $S \in F_1$ also contains exactly one element.
-If $p > 1$, then define $T_2 := T_1 \setminus \{(i,S) \in T_1: i = i_1\}$, which contains more than $(\bar m - 1)(\ell -1)$ sets, and produce by the same argument a (necessarily) different index $i_2$.
-Iterating $p = \bar{m} - \ell(\bar m - m)$ times this loop yields the desired $J = \{i_1, \ldots, i_p\} \subseteq [m]$.
+If $p = 1$ then we are done.
+Otherwise, define $T_2 := T_1 \setminus \{(i,S) \in T_1: i = i_1\}$, which contains $(\bar m - 1)(\ell -1) + (p-1)$ elements having $\bar m - 1$ possible first indices, and produce by the same argument a (necessarily) different index $i_2$.
+Iterating this loop $p$ times yields the desired $J = \{i_1, \ldots, i_p\} \subseteq [m]$.
 \end{proof}
@@
 
-We next verify \eqref{cond} holds.
+We next verify that \eqref{cond} holds.
 Fix $F \subseteq E$.
-Since $\text{\rm Span}\{\mathbf{B}_{\cap_{S \in F}\pi(S)}\} \subseteq \cap_{S \in F} \text{\rm Span}\{\mathbf{B}_{\pi(S)}\}$, if $\cap_{S \in F} \text{\rm Span}\{\mathbf{B}_{\pi(S)}\} = \{\textbf{0}\}$, then we must have $|\cap_{S \in F} \pi(S)| = 0$ (as the columns of $\mathbf{B}_{\pi(S)}$ are linearly independent) and \eqref{cond} trivially holds.
+Since $\text{\rm Span}\{\mathbf{B}_{\cap_{S \in F}\pi(S)}\} \subseteq \cap_{S \in F} \text{\rm Span}\{\mathbf{B}_{\pi(S)}\}$, if $\cap_{S \in F} \text{\rm Span}\{\mathbf{B}_{\pi(S)}\} = \{\textbf{0}\}$, then we must have $|\cap_{S \in F} \pi(S)| = 0$ (as the columns of $\mathbf{B}_{\pi(S)}$ are linearly independent) and \eqref{cond} is trivially true.
 Suppose then that the intersection is not the zero vector.
@@
 \begin{align*}
-g(\mathbf{A}, \{\mathbf{x}_i\}_{i=1}^N) := \prod_{S \in {[n] \choose k}} \sum_{S' \in {[N] \choose k}} (\det M_{S',S})^2,
+g(\mathbf{A}, \{\mathbf{x}_i\}_{i=1}^N) := \prod_{S \in {[N] \choose k}} \sum_{S' \in {[n] \choose k}} (\det M_{S',S})^2,
 \end{align*}
@@
 \begin{proof}[Proof (sketch) of Cor.~\ref{ProbabilisticCor}]
-First, note that if a set of measure spaces $\{(X_{\ell}, \Sigma_{\ell}, \nu_{\ell})\}_{\ell=1}^p$ has $\nu_{\ell}$ is absolutely continuous with respect to $\mu$ for all $\ell \in [p]$, where $\mu$ is the standard Borel measure on $\mathbb{R}$, then the product measure $\prod_{\ell=1}^p \nu_{\ell}$ is absolutely continuous with respect to the standard Borel product measure on $\mathbb{R}^p$ (e.g.,  \cite{folland2013real}).
-By Thm.~\ref{robustPolythm}, there is a polynomial that is nonzero whenever $Y$ has a stable $k$-sparse representation in $\mathbb R^m$; in particular, this property (stability) holds with probability one.
+First, note that if a set of measure spaces $\{(X_{\ell}, \Sigma_{\ell}, \nu_{\ell})\}_{\ell=1}^p$ has that $\nu_{\ell}$ is absolutely continuous with respect to $\mu$ for all $\ell \in [p]$, where $\mu$ is the standard Borel measure on $\mathbb{R}$, then the product measure $\prod_{\ell=1}^p \nu_{\ell}$ is absolutely continuous with respect to the standard Borel product measure on $\mathbb{R}^p$ (e.g.,  \cite{folland2013real}).
+By Thm.~\ref{robustPolythm}, there is a polynomial that is nonzero whenever $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$; in particular, this property (stability) holds with probability one.
 \end{proof}

### 2017-04-12 manuscripts/PNAS/chazthm_pnas.tex
chaz

@@
 We give general conditions guaranteeing when such dictionaries are uniquely and stably determined by data.
-%, justifying the application of this model as a constraint in blind source separation.
-The result may help explain the observed universality of emergent representations in sparse coding models of some natural phenomena.
+The result justifies the use of this model as a constraint for blind source separation, and may help explain the observed universality of emergent representations in sparse coding models of some natural phenomena.
 %These results provide theoretical grounding for  the application of dictionary learning to recovering sparse signals from unknown noisy compressive measurements.
@@
 
-\keywords{Sparse coding, dictionary learning, identifiability, compressive sensing}
+\keywords{Sparse coding, dictionary learning, matrix factorization, compressive sensing, inverse problems}
 
 \begin{abstract}
-Dictionary learning for sparse linear coding has exposed underlying structure in many natural signals.
-However, there are few universal theorems guaranteeing uniqueness of model estimation independent of implementation.
-Here, we prove that for all diverse enough datasets generated from the sparse coding model, latent dictionaries and codes are uniquely determined up to measurement error.
+Dictionary learning for sparse linear coding has exposed some characteristic properties of many natural signals.
+However, universal theorems which guarantee the consistency of estimation in this model are lacking.
+Here, we prove that for all diverse enough datasets generated from the sparse coding model, latent dictionaries and codes are uniquely and stably determined up to measurement error.
 Applications are given to data analysis, engineering, and neuroscience.

### 2017-04-13 manuscripts/PNAS/chazthm_pnas.tex
tiny edit

@@
 \begin{corollary}\label{SLCopt}
-If all of the assumptions of Thm.\ref{DeterministicUniquenessTheorem} hold with more than $(k-1)\left[ {\bar m \choose k} + |E|k{m \choose k-1}\right]$ vectors $\mathbf{x}_i$ supported on each $S \in E$, then all solutions to Prob.~\ref{OptimizationProblem} necessarily satisfy the implications \eqref{Cstable} and \eqref{b-PDa} of Thm.~\ref{DeterministicUniquenessTheorem}.
+If all of the assumptions of Thm.\ref{DeterministicUniquenessTheorem} hold with more than $(k-1)\left[ {\bar m \choose k} + |E|k{\bar m \choose k-1}\right]$ vectors $\mathbf{x}_i$ supported on each $S \in E$, then all solutions to Prob.~\ref{OptimizationProblem} necessarily satisfy the implications \eqref{Cstable} and \eqref{b-PDa} of Thm.~\ref{DeterministicUniquenessTheorem}.
 \end{corollary}

### 2017-04-13 manuscripts/PNAS/chazthm_pnas.tex
tiny typos

@@
 Next, we describe a quantitative version of the spark condition.  % We first explain how the spark condition \eqref{SparkCondition} relates to t
-The \emph{lower bound} \cite{Grcar10} of a matrix $\mathbf{A} \in \mathbb R^{n \times m}$ is the largest number $\alpha$ such that \mbox{$\|\mathbf{A}\mathbf{x}\|_2 \geq \alpha\|\mathbf{x}\|_2$} for all $\mathbf{x} \in \mathbb{R}^m$.
-By compactness of the unit sphere, every injective linear map has a nonzero lower bound; hence, if $\mathbf{A}$ satisfies \eqref{SparkCondition}, then each submatrix formed from $2k$ of its columns or less has a nonzero lower bound.
+The \emph{lower bound} \cite{Grcar10} of a matrix $\mathbf{M} \in \mathbb R^{n \times m}$ is the largest number $\alpha$ such that \mbox{$\|\mathbf{M}\mathbf{x}\|_2 \geq \alpha\|\mathbf{x}\|_2$} for all $\mathbf{x} \in \mathbb{R}^m$.
+By compactness of the unit sphere, every injective linear map has a nonzero lower bound; hence, if $\mathbf{M}$ satisfies \eqref{SparkCondition}, then each submatrix formed from $2k$ of its columns or less has a nonzero lower bound.
 This motivates the following definition: % We therefore define the following domain-restricted lower bound:
 \begin{align*}
-L_k(\mathbf{A}) := \frac{1}{\sqrt{k}}\max \{ \alpha : \|\mathbf{A}\mathbf{x}\|_2 \geq \alpha\|\mathbf{x}\|_2 \text{ for all $k$-sparse } \mathbf{x}\}.
+L_k(\mathbf{M}) := \frac{1}{\sqrt{k}}\max \{ \alpha : \|\mathbf{M}\mathbf{x}\|_2 \geq \alpha\|\mathbf{x}\|_2 \text{ for all $k$-sparse } \mathbf{x}\}.
 \end{align*}
@@
 %Clearly, $\sqrt{k} L_k(\mathbf{A}) \geq \sqrt{k'}L_{k'}(\mathbf{A})$ whenever $k < k'$, and 
-Clearly, for any $\mathbf{A}$ satisfying \eqref{SparkCondition}, we have $L_{k'}(\mathbf{A}) > 0$ for  $k' \leq 2k$.
-We note that the quantity $1 - \sqrt{k} L_k(\mathbf{A})$ is also known in the CS literature as the (asymmetric) lower restricted isometry constant \cite{Blanchard2011}.%, Foucart2009}.
+Clearly, for any $\mathbf{M}$ satisfying \eqref{SparkCondition}, we have $L_{k'}(\mathbf{M}) > 0$ for  $k' \leq 2k$.
+We note that the quantity $1 - \sqrt{k} L_k(\mathbf{M})$ is also known in the CS literature as the (asymmetric) lower restricted isometry constant \cite{Blanchard2011}.%, Foucart2009}.
 
-A vector $\mathbf{x}$ is said to be \emph{supported} on $S \subseteq [m]$ when $\mathbf{x} \in \text{\rm Span} \{\mathbf{e}_j\}_{j\in S}$, where $\mathbf{e}_j$ are the standard basis in $\mathbb R^m$.
-Denote by $\mathbf{M}_S$ the submatrix formed by the columns of $\mathbf{M}$ indexed by $S$, where we set $\text{\rm Span}\{\mathbf{M}_\emptyset\} := \{\textbf{0}\}$, and similarly by $\mathbf{x}^J$ the subvector formed from the entries of $\mathbf{x}$ indexed by $J$.
+A vector $\mathbf{x}$ is said to be \emph{supported} on $S \subseteq [m]$ when $\mathbf{x} \in \text{\rm Span}( \{\mathbf{e}_j\}_{j\in S})$, where $\mathbf{e}_j$ are the standard basis in $\mathbb R^m$.
+For any index set $J$, denote by by $\mathbf{x}^J$ the subvector formed from the entries of $\mathbf{x}$ indexed by $J$, and similarly by $\mathbf{M}_J$ the submatrix formed by the columns of $\mathbf{M}$ indexed by $J$, where we set $\text{\rm Span}\{\mathbf{M}_\emptyset\} := \{\textbf{0}\}$.
 A set of $k$-sparse vectors is said to be in \emph{general linear position} when any $k$ of them are linearly independent.
@@
 Let $\mathbf{A}~\in~\mathbb{R}^{n \times m}$ satisfy \eqref{SparkCondition} for $k < m$, and suppose for some $\bar m$ that more than \mbox{$(k-1){\bar m \choose k}$} $k$-sparse \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} are supported in general linear position on each set in an $\ell$-regular $E \subseteq {[m] \choose k}$ with the SIP.
-There is a constant\footnote{We delay defining the constant $C_1$ until Section \ref{DUT} (\eqref{Cdef1}).} $C_1 > 0$ for which the following holds for $\varepsilon < L_2(\mathbf{A}) / C_1$.
+There is a constant\footnote{We delay defining the constant $C_1$ until Section \ref{DUT} (\eqref{Cdef1}).} $C_1 > 0$ for which the following holds for $\varepsilon < L_2(\mathbf{A}) / C_1$:
 
@@
 
-Furthermore, if $\varepsilon < L_{2k}(\mathbf{A}) / C_1$, then $\mathbf{B}_{\bar J}$ also satisfies \eqref{SparkCondition} with $L_{2k}(\mathbf{B}_{\bar J}\mathbf{PD}) \geq L_{2k}(\mathbf{A}_J) - C_1 \varepsilon$, and:
+Furthermore, if $\varepsilon < L_{2k}(\mathbf{A}_J) / C_1$, then $\mathbf{B}_{\bar J}$ also satisfies \eqref{SparkCondition} with $L_{2k}(\mathbf{B}_{\bar J}\mathbf{PD}) \geq L_{2k}(\mathbf{A}_J) - C_1 \varepsilon$, and:
 \begin{align}\label{b-PDa}
@@
 where for any $S' \in {[n] \choose k}$ and $S \in {[m] \choose k}$, the symbol $\mathbf{A}_{S',S}$ denotes the submatrix of entries $A_{ij}$ with $(i,j) \in S' \times S$.
-We note that the large number of terms in this product is likely necessary due to the NP-hardness of deciding whether a given matrix $A$ satisfies the spark condition \cite{tillmann2014computational}.
+We note that the large number of terms in this product is likely necessary due to the NP-hardness of deciding whether a given matrix $\mathbf{A}$ satisfies the spark condition \cite{tillmann2014computational}.
 
@@
 with $f(\mathbf{A}) = 0$.
-Hence, almost every real $n \times m$ matrix $\mathbf{A}$ with $n \geq \max(2k,m)$ satisfies \eqref{SparkCondition}.
+Hence, almost every real $n \times m$ matrix $\mathbf{A}$ with $n \geq \min(2k,m)$ satisfies \eqref{SparkCondition}.
 
@@
 % ======== b - PDa =========
-First, note that $\|\mathbf{x}\|_1 \leq \sqrt{k} \|\mathbf{x}\|_2$ for $k$-sparse $\mathbf{x} \in \mathbb{R}^m$, which by definition of $L_k(A)$ implies the following inequality:
+First, note that $\|\mathbf{x}\|_1 \leq \sqrt{k} \|\mathbf{x}\|_2$ for $k$-sparse $\mathbf{x} \in \mathbb{R}^m$, which by definition of $L_k$ implies the following inequality:
 \begin{align}\label{delrho}
@@
 Hence, the map $\pi$ is injective and therefore $\bar m \geq m$.
-Setting $J = [m]$, $\bar J = \pi([m])$, and letting $P = \left( \mathbf{e}_{\pi(1)} \cdots \mathbf{e}_{\pi(m)}\right)$ and $D = \text{diag}(\frac{\bar{c}_1}{c_1},\ldots,\frac{\bar{c}_m}{c_m})$, we see that \eqref{1D} becomes, for all $j \in [m]$:
+Setting $\bar J = \pi([m])$ and letting $P = \left( \mathbf{e}_{\pi(1)} \cdots \mathbf{e}_{\pi(m)}\right)$ and $D = \text{diag}(\frac{\bar{c}_1}{c_1},\ldots,\frac{\bar{c}_m}{c_m})$, we see that \eqref{1D} becomes, for all $j \in [m]$:
 \begin{align*}%\label{k=1result}
-\|\mathbf{A}_j - (\mathbf{B}_J\mathbf{PD})_j\|_2 
+\|(\mathbf{A} - \mathbf{B}_{\bar J}\mathbf{PD})_j\|_2 
 = \|\mathbf{A}_j - \frac{\bar{c}_j}{c_j}\mathbf{B}_{\pi(j)}\|_2 
@@
 We require a few additional tools to extend the proof to the general case $k < m$.
-These include a general notion of distance (Def.~\ref{dDef}) and angle (Def.~\ref{FriedrichsDefinition}) between subspaces and a stability result in combinatorial matrix analysis (Lem.~\ref{MainLemma}).
+These include a generalized notion of distance (Def.~\ref{dDef}) and angle (Def.~\ref{FriedrichsDefinition}) between subspaces and a stability result in combinatorial matrix analysis (Lem.~\ref{MainLemma}).
 
@@
 
-The constant $C_1$ in Thm.~\ref{DeterministicUniquenessTheorem} is then defined by\footnote{Note that $\|\mathbf{AX}_{I(S)}\mathbf{c}\|_2 \geq \sqrt{k} L_k(\mathbf{A})\|\mathbf{X}_{I(S)}\mathbf{c}\|_2 \geq k L_k(\mathbf{A}) L_k(\mathbf{X}_{I(S)})\|\mathbf{c}\|_2$ for $S \in E$ and $k$-sparse $\mathbf{c}$.
+The constant $C_1 > 0$ in Thm.~\ref{DeterministicUniquenessTheorem} is then defined by\footnote{Note that $\|\mathbf{AX}_{I(S)}\mathbf{c}\|_2 \geq \sqrt{k} L_k(\mathbf{A})\|\mathbf{X}_{I(S)}\mathbf{c}\|_2 \geq k L_k(\mathbf{A}) L_k(\mathbf{X}_{I(S)})\|\mathbf{c}\|_2$ for $S \in E$ and $k$-sparse $\mathbf{c}$.
 Therefore, $\sqrt{k} L_k(\mathbf{AX}_{I(S)}) \geq k L_k(\mathbf{A}) L_k(\mathbf{X}_{I(S)}) > 0$ since $L_k(\mathbf{A}), L_k(\mathbf{X}_{I(S)}) > 0$ by \eqref{SparkCondition} and general linear position of the $\mathbf{x}_i$.
@@
 %
-which we remark is consistent with the assumption on $C_1$ in the proof of Thm.~\ref{DeterministicUniquenessTheorem} for the case $k=1$.
+which we remark is consistent with the assumption on $C_1$ in the proof of the case $k=1$ at the beginning of this section.
 
@@
 
-In this note, we generalized the approach of \cite{Hillar15} to prove the stability of unique solutions to Probs.~\ref{InverseProblem} and \ref{OptimizationProblem} and significantly reduce the known sample complexity.
+In this note, we generalized the approach of \cite{Hillar15} to prove the stability of unique solutions to Probs.~\ref{InverseProblem} and \ref{OptimizationProblem} while significantly reducing the known sample complexity.
 % FRITZ: Inverse problems instead of Data Analysis.
@@
 The main motivation for this work, however, was to understand how seemingly universal representations emerge from sparse coding models fit to natural data by a variety of methodologies.
-We elaborate more on these applications below after discussing theoretical aspects.
+We elaborate on these applications below after discussing theoretical aspects.
 % We close with several application areas.

### 2017-04-13 manuscripts/PNAS/chazthm_pnas.tex
sml edits removed all comments

@@
 We give general conditions guaranteeing when such dictionaries are uniquely and stably determined by data.
-The result justifies the use of this model as a constraint for blind source separation, and may help explain the observed universality of emergent representations in sparse coding models of some natural phenomena.
-%These results provide theoretical grounding for  the application of dictionary learning to recovering sparse signals from unknown noisy compressive measurements.
+The result justifies the use of this model as a constraint for blind source separation, and may help explain the observed universality of emergent representations in sparse models of some natural phenomena.
 }
@@
 A common modern assumption is that each of $N$ observed $n$-dimensional signals is a (noisy) linear combination of at most $k$ elementary waveforms drawn from some unknown ``dictionary'' of size $m$, typically with $k < m \ll N$ (see \cite{Zhang15} for a comprehensive review of this and related models).
-%A popular underlying assumption is that there exists a `dictionary' of $m$ elementary waveforms, at most $k$ of which need be linearly combined to represent each signal in a given dataset of size $N$, typically where $k < m \ll N$.
 Approximating solutions to this sparsity-constrained inverse problem have provided insight into the structure of many signal classes lacking domain-specific formal models (e.g., in vision \cite{wang2015sparse}).
@@
 `Gabor' wavelets) estimated from data appear to be canonical \cite{donoho2001can};
-i.e., they are found in learned dictionaries independent of algorithmic implementation or natural image training set.
-
-% (e.g., Fourier bases, wavelets, etc.)
+i.e., they are found in learned dictionaries independent of algorithm or natural image training set.
 
@@
 For example, a sparse coding analysis of local painting style can be used for forgery detection \cite{hughes2010, Olshausen10}, but only if all dictionaries consistent with training data do not differ appreciably in their ability to sparsely encode new samples.
-%the identifying sparse components of the artwork can be consistently estimated.
-% are independent of implementation idiosyncrasies.
 Fortunately, algorithms with proven recovery of generating dictionaries under certain 
@@
 Here, we prove very generally that uniqueness and stability in sparse linear coding is an expected property of the model. 
-%; that is, it is a well-posed problem (in the sense of Hadamard \cite{Hadamard1902}).
-%In other words, whenever enough sparsely represented data generated from a dictionary (satisfying a spark condition) are observed, the original codes and dictionary are uniquely determined up to an error that is commensurate with the measurement noise.
 More specifically, dictionaries that preserve sparse codes (i.e., satisfy a `spark condition') are identifiable from as few as \mbox{$N = m(k-1){m \choose k} + m$} noisy sparse linear combinations of their columns up to an error linear in the noise (Thm.~\ref{DeterministicUniquenessTheorem}).
@@
 Moreover, these guarantees hold without assuming the recovered matrix satisfies a spark condition, even when the number $m$ of dictionary elements is unknown.
-The explicit, algorithm-independent criteria we provide should be a useful tool in the theory of sparse representations.
-
-%Other applications include: 1) a sufficient diversity of sparse codes sent through a random linear compressive channel are identifiable and 2) an explanation for universal representation of natural signals in sparse coding models from neuroscience.
+The explicit, algorithm-independent criteria we provide should be a useful theoretical tool.
+%  in the theory of sparse representations.
 
@@
 %
-which would be, in any case, necessary for uniqueness. Our concern here is the stability of these solutions with respect to noise in the data.
+which would be, in any case, necessary for uniqueness. Our concern here is solution stability with respect to noise.
 
@@
 We say $Y$ has a \textbf{$k$-sparse representation in $\mathbb{R}^m$} if there exists a matrix $\mathbf{A}$ and $k$-sparse $\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$ such that $\mathbf{y}_i = \mathbf{A}\mathbf{x}_i$ for all $i$.
-%Equivalently, $\mathbf{Y} = \mathbf{A}\mathbf{X}$ for $\mathbf{Y}$ and $\mathbf{X}$ having the $\mathbf{y}_i$ and $\mathbf{x}_i$ as their columns, respectively.
 This representation is \textbf{stable} if for every $\delta_1, \delta_2 \geq 0$, there exists $\varepsilon(\delta_1, \delta_2) \geq 0$ (with $\varepsilon > 0$ when  $\delta_1, \delta_2 > 0$) such that if $\mathbf{B}$ and $k$-sparse $\mathbf{\bar x}_1, \ldots, \mathbf{\bar x}_N \in \mathbb{R}^m$ satisfy:
@@
 To see how Def. \ref{maindef} directly relates to Prob. \ref{InverseProblem}, suppose that $Y$
-% \mbox{$Y = \{\mathbf{A} \mathbf{x}_1, \ldots, \mathbf{A}\mathbf{x}_N\}$} 
+
 has a stable $k$-sparse representation in $\mathbb{R}^m$ and fix $\delta_1, \delta_2$ to be the desired recovery accuracy in \eqref{def1}.
@@
 Then from the triangle inequality, it follows that any matrix $\mathbf{B}$ and $k$-sparse $\mathbf{\bar x}_1, \ldots, \mathbf{\bar x}_N \in \mathbb{R}^m$ solving Prob.~\ref{InverseProblem} are necessarily close to the original dictionary $\mathbf{A}$ and sparse codes $\mathbf{x}_i$.
-
-%Our main technical finding is that a sufficient quantity of measurements generated from any dictionary satisfying the spark condition has a stable sparse representation.
-More specifically, such dictionaries are identifiable from as few as \mbox{$N = m(k-1){m \choose k} + m$} sparse linear combinations of their columns up to an error that is linear in the measurement noise (Thm.~\ref{DeterministicUniquenessTheorem}).
-In fact, provided $n \geq k$, in almost all cases the dictionary learning problem is well-posed (in the sense of Hadamard \cite{Hadamard1902}) given enough data (Cor.~\ref{ProbabilisticCor}).
-Importantly, these guarantees hold without assuming the recovered matrix satisfies a spark condition.
-Our results  also apply when only an upper bound on the number of dictionary elements is known.
-The explicit, algorithm-independent criteria we provide should be a useful tool in the theory of dictionary learning.
 
@@
 Letting $\{1, \ldots, m\}$ be denoted $[m]$, its power set $2^{[m]}$, and ${[m] \choose k}$ the set of subsets of $[m]$ of size $k$,
-% Let $\text{\rm Span}\{\mathbf{v}_1, \ldots, \mathbf{v}_\ell\}$ be the $\mathbb{R}$-linear span of vectors $\mathbf{v}_1, \ldots, \mathbf{v}_\ell$. 
 we say a hypergraph $E \subseteq 2^{[m]}$ on vertices $[m]$ is \textit{$k$-uniform} when in fact $E \subseteq {[m] \choose k}$.
@@
 It is easy to verify that for every $k < m$, there is a regular $k$-uniform hypergraph that satisfies the SIP; for instance, consecutive intervals of length $k$ in some cyclic order on $[m]$.
-%\begin{proposition}
-%For every $k < m$, there is a regular $k$-uniform hypergraph that satisfies the singleton intersection property.
-%\end{proposition}
 
-%The second ingredient necessary for the statement of Thm.~\ref{DeterministicUniquenessTheorem} 
-Next, we describe a quantitative version of the spark condition.  % We first explain how the spark condition \eqref{SparkCondition} relates to t
+Next, we describe a quantitative version of the spark condition.  
 The \emph{lower bound} \cite{Grcar10} of a matrix $\mathbf{M} \in \mathbb R^{n \times m}$ is the largest number $\alpha$ such that \mbox{$\|\mathbf{M}\mathbf{x}\|_2 \geq \alpha\|\mathbf{x}\|_2$} for all $\mathbf{x} \in \mathbb{R}^m$.
 By compactness of the unit sphere, every injective linear map has a nonzero lower bound; hence, if $\mathbf{M}$ satisfies \eqref{SparkCondition}, then each submatrix formed from $2k$ of its columns or less has a nonzero lower bound.
-This motivates the following definition: % We therefore define the following domain-restricted lower bound:
+This motivates the following definition:
 \begin{align*}
@@
 
-%Clearly, $\sqrt{k} L_k(\mathbf{A}) \geq \sqrt{k'}L_{k'}(\mathbf{A})$ whenever $k < k'$, and 
 Clearly, for any $\mathbf{M}$ satisfying \eqref{SparkCondition}, we have $L_{k'}(\mathbf{M}) > 0$ for  $k' \leq 2k$.
-We note that the quantity $1 - \sqrt{k} L_k(\mathbf{M})$ is also known in the CS literature as the (asymmetric) lower restricted isometry constant \cite{Blanchard2011}.%, Foucart2009}.
+We note that the quantity $1 - \sqrt{k} L_k(\mathbf{M})$ is also known in the CS literature as the (asymmetric) lower restricted isometry constant \cite{Blanchard2011}.
 
@@
 \begin{theorem}\label{DeterministicUniquenessTheorem}
-%Fix integers $n, \ell$, and $k < m$. 
 Let $\mathbf{A}~\in~\mathbb{R}^{n \times m}$ satisfy \eqref{SparkCondition} for $k < m$, and suppose for some $\bar m$ that more than \mbox{$(k-1){\bar m \choose k}$} $k$-sparse \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} are supported in general linear position on each set in an $\ell$-regular $E \subseteq {[m] \choose k}$ with the SIP.
@@
 
-%\begin{theorem}\label{DeterministicUniquenessTheorem}
-%Fix integers $n, \ell$, and $k < m$.
-Suppose $\mathbf{A}~\in~\mathbb{R}^{n \times m}$ satisfies the spark condition \eqref{SparkCondition} and that $k$-sparse \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} contain at least \mbox{$(k-1){m \choose k}+1$} vectors supported in general linear position on each set in some $\ell$-regular $E \subseteq {[m] \choose k}$ with the SIP.
-There exists a constant $C_1 > 0$ for which the following holds for all $\varepsilon < L_2(\mathbf{A}) / C_1$.
-
-%Every matrix $\mathbf{B} \in \mathbb{R}^{n \times m}$ and $k$-sparse $\mathbf{\bar x}_1, \ldots, \mathbf{\bar x}_N \in \mathbb{R}^{m}$ with  \mbox{$\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\bar x}_i\|_2 \leq \varepsilon$} for all $i$ necessarily satisfies:
-%\begin{align}\label{Cstable}
-%\|\mathbf{A}_j - (\mathbf{B}\mathbf{PD})_j\|_2 \leq C_1 \varepsilon,\ \ \   \text{for all $j \in [m]$},
-%\end{align}
-%for some permutation matrix $\mathbf{P}$ and invertible diagonal $\mathbf{D}$.
-
-%Furthermore, if $\varepsilon < L_{2k}(\mathbf{A}) / C_1$, then $\mathbf{B}$ also satisfies \eqref{SparkCondition} with $L_{2k}(\mathbf{B}\mathbf{PD}) \geq L_{2k}(\mathbf{A}) - C_1 \varepsilon$, and:
-%\begin{align}\label{b-PDa}
-%\|\mathbf{x}_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\bar x}_i\|_1 &\leq  \left( \frac{ 1+C_1 \|\mathbf{x}_i\|_1 }{ L_{2k}(\mathbf{A}) -  C_1\varepsilon } \right) \varepsilon,\ \ \   \text{for all $i \in [N]$}.
-%\end{align}
-%\end{theorem}
-
-%\begin{theorem}\label{DeterministicUniquenessTheorem}
-%Fix integers $n, \ell$, and $k < m \leq \bar m$.
-Suppose $\mathbf{A}~\in~\mathbb{R}^{n \times m}$ satisfies the spark condition \eqref{SparkCondition} and that $k$-sparse \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} contain at least \mbox{$(k-1){\bar m \choose k}+1$} vectors supported in general linear position on each set in some $\ell$-regular $E \subseteq {[m] \choose k}$ satisfying the SIP.
-There exists a constant $C_1 > 0$ for which the following holds for all $\varepsilon < L_2(\mathbf{A}) / C_1$.
-%
-%Every matrix $\mathbf{B} \in \mathbb{R}^{n \times \bar m}$ and $k$-sparse $\mathbf{\bar x}_1, \ldots, \mathbf{\bar x}_N \in \mathbb{R}^{\bar m}$ with  \mbox{$\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\bar x}_i\|_2 \leq \varepsilon$} for all $i$ necessarily satisfies:
-%\begin{align}\label{Cstable}
-%\|\mathbf{A}_{\phi(j)} - (\mathbf{B}_{J}\mathbf{PD})_j\|_2 \leq C_1 \varepsilon,\ \ \   \text{for $j = 1, \ldots, |J|$},
-%\end{align}
-%%
-%for some $J \subseteq [\bar m]$ of size \mbox{$\lfloor \bar m - \ell(\bar m - m) \rfloor$}, injective map $\phi$, permutation matrix $\mathbf{P}$, and invertible diagonal matrix $\mathbf{D}$.
-%%\footnote{We note that the condition $\varepsilon < L_2(\mathbf{A})$ above is necessary.
-When \mbox{$\mathbf{A}$ = $I$} and $\mathbf{x}_i = \mathbf{e}_i$, it turns out that $C_1 = 1$ and there is a $\mathbf{B}$ and $1$-sparse $\mathbf{\bar x}_i$ with $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\bar x}_i\|_2 \leq \varepsilon$ violating \eqref{Cstable}.}
-%
-%Furthermore, if $\varepsilon < L_{2k}(\mathbf{A}) / C_1$, then $\mathbf{B}_J$ also satisfies \eqref{SparkCondition} with $L_{2k}(\mathbf{B}_J\mathbf{PD}) \geq L_{2k}(\mathbf{A}) - C_1 \varepsilon$, and:
-%\begin{align}\label{b-PDa}
-%\|\mathbf{x}_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\bar x}_i\|_1 &\leq  \left( \frac{ 1+C_1 \|\mathbf{x}_i\|_1 }{ L_{2k}(\mathbf{A}) -  C_1\varepsilon } \right) \varepsilon,\ \ \   \text{for all $i \in [N]$}.
-%\end{align}
-%\end{theorem}
-
 To be clear, Thm.~\ref{DeterministicUniquenessTheorem} says that the smaller the difference $\bar m - m$, the more columns and coefficients of the original dictionary $\mathbf{A}$ and codes $\mathbf{x}_i$ contained (up to noise) in the appropriately scaled dictionary $\mathbf{B}$ and codes $\mathbf{\bar x}_i$.
-%In particular, when $\bar m = m$ all columns of $\mathbf{A}$ and coefficients of each $\mathbf{x}_i$ recoverable, as per Def.~\ref{maindef}. 
 The implication in the case $\bar{m} = m$ is precisely that $Y = \{\mathbf{Ax}_1, \ldots, \mathbf{Ax}_N\}$ has a stable $k$-sparse representation in $\mathbb{R}^m$, with \eqref{def1} guaranteed provided $\varepsilon$ in Def.~\ref{maindef} does not exceed:
@@
 \end{align}
-  % , since it requires additional definitions not critical to the statement of our results.
-
-% Note also that Thm~\ref{DeterminsiticUniquenessTheorem} gives conditions for when a single solution to Problem~\ref{InverseProblem} in fact represents \emph{all} possible solutions, related by transformations of the form $PD$.
 
@@
 
-%\begin{proposition}
-%If $E$ is an $\ell$-regular hypergraph of rank $k$ satisfying the singleton intersection property then $|E| \geq \ell m/k$. 
-%\end{proposition}
-%Note that every $\ell$-regular hypergraph $E \subseteq {[m] \choose k}$ satisfies: \[|E|k = \sum_{S \in E}|S| = \sum_{i \in [m]} \deg(i) = \ell m.\] 
 As already mentioned, it is easy to construct a regular hypergraph $E \subseteq {[m] \choose k}$ with the SIP having cardinality $|E| = m$, implying the lower bound for sample size $N$ from the introduction.
 In many cases, however, the SIP can be achieved with far fewer supports; for example, when $k = \sqrt{m}$ one can take $E$ to be the $2k$ rows and columns formed by arranging $[m]$ in a square grid.
-%In light of Cor.~\ref{DeterministicUniquenessCorollary}, it would be interesting to determine other such $E$.
-%[ ** TODO ** can we show for every $k, m$ that there is an $E$ satisfying the SIP with $|E| = \ell m/k$ for every $\ell$ such that $\ell m/k$ is an integer?
-Then lower bound on $N$ comes from the smallest such $\ell$.]
 
@@
 \end{corollary}
-%\begin{corollary}\label{SLCopt}
-%If the assumptions of Thm.\ref{DeterministicUniquenessTheorem} hold with more than $(k-1)\left[ {\bar m \choose k} + |E|k{\bar m \choose k-1}\right]$ vectors $\mathbf{x}_i$ supported on each $S \in E$, then all matrices $\mathbf{B} \in \mathbb{R}^{n \times \bar m}$ and $\mathbf{\bar x}_1, \ldots, \mathbf{\bar x}_N \in \mathbb{R}^{\bar m}$ solving:
-%\begin{align}\label{minsum}
-%\min \sum_{i = 1}^N \|\mathbf{\bar x}_i\|_0 \ \ 
-%\text{subject to} \ \ \|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\bar x}_i\|_2 \leq \varepsilon, \ \text{for all $i$},
-%\end{align}
-%
-%necessarily satisfy implications 1) and 2) from Thm.~\ref{DeterministicUniquenessTheorem}.
-
-%must have $\bar m \geq m$ and, provided $p = \bar m - \ell(\bar m - m) > 0$, necessarily satisfy \eqref{Cstable}
-%%\begin{align}\label{Cstable}
-%%\|(\mathbf{A}_J- \mathbf{B}_{\bar J} \mathbf{PD} )_j\|_2 \leq C_1 \varepsilon, \ \  \text{for  $j \in J$},
-%%\end{align}
-%for some $J \in {[m] \choose p}$, $\bar J \in {[\bar m] \choose p}$, permutation matrix $\mathbf{P}$, and invertible diagonal matrix $\mathbf{D}$.
-%\end{corollary}
-
-%\begin{corollary}
-%Fix $n, \ell$, and $k < m$.
-Let $\mathbf{A}~\in~\mathbb{R}^{n \times m}$ satisfy the spark condition \eqref{SparkCondition} and $k$-sparse \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} have at least \mbox{$\left[ (k-1){ m \choose k} + 1 \right] + (k-1)^2{m \choose k-1}$} vectors supported in general linear position on each set in an $\ell$-regular $E \subseteq {[m] \choose k}$ with the SIP.
-Given any $\delta_1, \delta_2 \geq 0$ and $\varepsilon \leq \varepsilon(\delta_1, \delta_2)$,
-%every solution $\mathbf{B}, \mathbf{\bar x}_i, \ldots, \mathbf{\bar x}_N$ to the $\ell_0$ optimization problem:
-%\begin{align}\label{minsum}
-%\arg \min \sum_{i = 1}^N \|\mathbf{\bar x}_i\|_0 \ \ \text{s.t.} \ \ \mathbf{B}\mathbf{\bar x}_i = \mathbf{A}\mathbf{x}_i, \ \ \text{$i \in [N]$}, %\|\mathbf{A}\end{align}
-%necessarily satisfies the recovery inequalities in \eqref{def1}. % \eqref{Cstable} and \eqref{b-PDa}.
-%\end{corollary}
-%
-%\begin{proof}
-%We derive a lower bound on the number of $k$-sparse $\mathbf{\bar x}_i$ and then apply Thm.~\ref{DeterministicUniquenessCorollary}. 
-%First, note that $\|\mathbf{\bar x}_i\|_0 \neq 0$ for all $i$, since otherwise we would have $\mathbf{A}\mathbf{x}_i = \mathbf{B}\mathbf{\bar x}_i = \mathbf{0} \implies \mathbf{x}_i = \mathbf{0}$ by the spark condition, contradicting the general linear position of the $\mathbf{x}_i$.
-Let $n_p$ be the number of $\mathbf{\bar x}_i$ with $\|\mathbf{\bar x}_i\|_0 = p$.
-%, so that $\sum_{p = 1}^{m} n_p = N$.
-%Since the $\mathbf{x}_i$ are all $k$-sparse, by \eqref{minsum} we have:
-%\begin{align}
-%k \sum_{p = 1}^{m} n_p = kN \geq \sum_{i=1}^N \|\mathbf{x}_i\|_0 \geq \sum_{i=1}^N \|\mathbf{\bar x}_i\|_0 = \sum_{p=1}^{m} p n_p.
-%\end{align}
-%%\[\implies \sum_{p = 1}^k (k-p)n_p \geq \sum_{p = k+1}^{m} (p-k) n_p.\]
-%Hence,
-%\begin{align}
-%\sum_{p = k+1}^m n_p \leq \sum_{p = k+1}^m (p-k) n_p \leq \sum_{p = 1}^k (k-p)n_p \leq (k-1) \sum_{p = 1}^{k-1} n_p.
-%\end{align}
-%%\[ \implies \sum_{p = k+1}^m n_p \leq (k-1)^2 {\bar m \choose k-1} \]
-%
-%By the spark condition and general linear position of the $\mathbf{x}_i$, every $k$ vectors $\mathbf{Ax}_i$ span a $k$-dimensional space; hence, at most $k-1$ vectors $\mathbf{\bar x}_i$ can share a support of size $k-1$ or less, and the number of $(k-1)$-sparse vectors $\mathbf{\bar x}_i$ is then bounded from above by $(k-1) { m \choose k-1}$.
-It follows that at least $N - (k-1)^2 {m \choose k-1}$ of the vectors $\mathbf{\bar  x}_i$ are $k$-sparse, and that there must then be some $N' \subseteq [N]$ for which for each $S \in E$ there are $(k-1){m \choose k}+1$ of the vectors $\mathbf{x}_i$ with $i \in [N']$ supported on $S$ and for which $\mathbf{\bar x}_i$ is $k$-sparse for all $i \in [N']$.
-The result now follows directly from Thm.~\ref{DeterministicUniquenessCorollary}.
-% \eqref{Cstable} and \eqref{b-PDa} follow.
-%\end{proof}
-
-%Another straightforward application of Thm.~\ref{DeterministicUniquenessTheorem} is a probabilistic extension, which takes advantage of the following well-known application of random matrix theory to compressed sensing.
-A random $n \times m$ matrix obeys \eqref{SparkCondition} with probability one (or ``high probability'' for discrete variables) provided:
-%\begin{align}\label{CScondition}
-%n \geq \gamma k\log\left(\frac{m}{k}\right),
-%\end{align}
-%in which $\gamma >0$ is a constant that depends on the particular distribution from which the entries of $\mathbf{A}$ are sampled i.i.d. (many ensembles suffice, e.g. see \cite[Sec.~4]{Baraniuk08}).
 
@@
 Since $f$ is an analytic function, having one substitution of real numbers with $f(\mathbf{A}) \neq 0$ implies that its zeroes form a set of measure zero.
-Fortunately, such a matrix $\mathbf{A}$ is easily constructed by adding rows of zeroes to any $\min(2k,m) \times m$ ``Vandermonde'' matrix $[\gamma_i^j]_{i,j=1}^{k,m}$ with distinct $\gamma_i$ (so that each term in the product above is nonzero).
-%$A_{ij} = \gamma_i (since the $\gamma_i$ are distinct, any $k \times k$ ``Vandermonde'' sub-determinant is nonzero)
-%inserting $n-k$ rows of zeros into a $k \times m$ ``Vandermonde" matrix construction.
-%Let $\gamma_1, \ldots, \gamma_m$ be any distinct numbers.
-Then the columns of the $k \times m$ matrix $V = (\gamma^{\ell}_i)^{k,m}_{\ell,i=1}$ are in general linear position (since the $\gamma_i$ are distinct, any $k \times k$ ``Vandermonde" sub-determinant is nonzero).
-Concatenating $n-k$ rows of zeros to the bottom of this matrix yields a $n \times m$ matrix $\mathbf{A}$ satisfying the spark condition, i.e.
-with $f(\mathbf{A}) = 0$.
+Fortunately, such a matrix $\mathbf{A}$ is easily constructed by adding rows of zeroes to any $\min(2k,m) \times m$ Vandermonde matrix $[\gamma_i^j]_{i,j=1}^{k,m}$ with distinct $\gamma_i$ (so that each term in the product above is nonzero).
 Hence, almost every real $n \times m$ matrix $\mathbf{A}$ with $n \geq \min(2k,m)$ satisfies \eqref{SparkCondition}.
@@
 \begin{corollary}\label{ProbabilisticCor}
-Fix $k < m$ and $n \geq \min(2k, m)$ % satisfying \eqref{CScondition} for $\gamma = \gamma_0$, 
+Fix $k < m$ and $n \geq \min(2k, m)$ 
 and let the entries of $\mathbf{A} \in \mathbb{R}^{n \times m}$ and $k$-sparse $\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$ be drawn independently from probability measures absolutely continuous with respect to the standard Borel measure $\mu$.
@@
 Thus, choosing the dictionary and sparse codes ``randomly'' from \emph{any} continuous distribution generates data with stable sparse representations almost certainly.
-% , as long as the relevant parameters satisfy \eqref{CScondition}.
-%Next, we address the case when only an upper bound $m'$ on the latent dimension $m$ is known (assuming that $\mathbf{B}$ satisfies \eqref{SparkCondition}).
-
-%\begin{theorem}\label{DeterministicUniquenessTheorem2}
-%Fix integers $n$ and $k < m \leq m'$ and matrices $\mathbf{A}~\in~\mathbb{R}^{n \times m}$ and $\mathbf{B} \in \mathbb{R}^{n \times m'}$ both satisfying \eqref{SparkCondition}.
-Suppose \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} include at least \mbox{$(k-1){m' \choose k}+1$} $k$-sparse vectors in general linear position supported on each set in some $k$-uniform $E \subseteq 2^{[m]}$ satisfying the singleton intersection property.
-Then there exists a constant $C_3 > 0$ for which the following holds.
-
-%If for some $k$-sparse $\mathbf{\bar x}_1, \ldots, \mathbf{\bar x}_N \in \mathbb{R}^{m'}$ and $\varepsilon < L_2(\mathbf{A}) / C_3$ we have \mbox{$\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\bar x}_i\|_2 \leq \varepsilon$} for all $i$, then:
-%\begin{align}\label{Cstablem'}
-%\|\mathbf{A}_j-(\mathbf{B}_J\mathbf{PD})_j\|_2 \leq C_3\varepsilon \ \ \text{for all $j \in [m]$}
-%\end{align}
-%
-%for some $J \in {[m'] \choose m}$, permutation matrix $\mathbf{P}$, and invertible diagonal matrix $\mathbf{D}$.
-%\end{theorem}
-
-%In other words, the columns of $B$ contain (up to noise, after appropriate scaling) the columns of the original dictionary $\mathbf{A}$.
-Similarly, one can show by the same arguments at the beginning of Sec.~\ref{DUT} that the $\mathbf{\bar x}_i$ contain the original codes $\mathbf{x}_i$.
-The constant $C_3$ here is expression (\ref{Cdef2}) from the proof of Thm.~\ref{DeterministicUniquenessTheorem2}.
-Note that, in contrast to Thm.~\ref{DeterministicUniquenessTheorem}, this constant is dependent on $\mathbf{B}$; hence, \eqref{Cstablem'} holds for \emph{all} matrices $\mathbf{B} \in \mathbb{R}^{n \times m'}$ satisfying the spark condition only in the case $\varepsilon = 0$.
 
@@
 \begin{align}\label{delrho}
-L_k(\mathbf{A}) \leq \frac{\|\mathbf{A}\mathbf{x}\|_2}{\sqrt{k} \|\mathbf{x}\|_2} %\leq \frac{\|\mathbf{x}\|_1}{\sqrt{k} \|\mathbf{x}\|_2} \max_{i \in [m]}\|\mathbf{A}_i\|_2 
+L_k(\mathbf{A}) \leq \frac{\|\mathbf{A}\mathbf{x}\|_2}{\sqrt{k} \|\mathbf{x}\|_2} 
 \leq  \max_{j \in [m]}\|\mathbf{A}_j\|_2,
 \end{align}
-%
 which we frequently use.
@@
 \end{align*}
-%
-%where we drop the absolute value due to the upper bound on $\varepsilon$. 
+
 Hence, $L_{2k}(\mathbf{BPD}) \geq L_{2k}(\mathbf{A}) - C_1\varepsilon  > 0$. \eqref{b-PDa} then follows from:
@@
 \|\mathbf{x}_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\bar x}_i \|_1
-%&\leq \sqrt{2k} |\mathbf{x}_i - D^{-1}P^{\top}\mathbf{\bar x}_i\|_2 \\
 &\leq \frac{\|\mathbf{BPD}(\mathbf{x}_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\bar x}_i)\|_2}{L_{2k}(\mathbf{BPD})} \\
@@
 &\leq \frac{\varepsilon (1 + C_1 \|\mathbf{x}_i\|_1)}{L_{2k}(\mathbf{BPD})}.
-%&\leq \frac{\varepsilon}{\sqrt{2k}} \left( \frac{ 1+C_1 \|\mathbf{x}_i\|_1 }{ L_{2k}(\mathbf{A}) -  C_1\varepsilon } \right).
-%\leq \frac{\varepsilon }{\varepsilon_0 - \varepsilon} \left( C_1^{-1}+|\mathbf{x}_i\|_1 \right).
 \end{align*}
@@
 The heart of the matter is therefore \eqref{Cstable}, which we now finally establish, first in the important special case $k = 1$.
-
-%In fact, in the case $k=1$ we can relax our assumptions even further and assume that the matrix $\mathbf{B}$ has only at least as many columns as $\mathbf{A}$; as we will see, the conclusions of Thm.~\ref{DeterministicUniquenessTheorem} then hold for some $n \times m$ submatrix of $\mathbf{B}$.
-[*** ???
-***]
 
@@
 Thus, $\bar{c}_j \neq 0$, $j \in [m]$.
-%Note that $\bar{c}_j \neq 0$, since otherwise (by definition of $L_2(\mathbf{A})$) we reach the contradiction $|c_j| < \min_{\ell \in [m]} | c_\ell |$.
-%by \eqref{delrho} and definition of $C_1$ we would have $\|c_j\mathbf{A}_j\|_2 < \min_{\ell \in [m]}\|c_{\ell}\mathbf{A}_{\ell}\|_2$.
-[*** TODO:  This doesn't seem correct ***]
-%\begin{align*}
-%|c_j| \sqrt{2} L_2(\mathbf{A}) \leq \|\mathbf{A}(c_j\mathbf{e}_j)\|_2 \leq \varepsilon < L_2(\mathbf{A}) \min_{\ell \in [m]} | c_\ell |.
-%\end{align*}
 
@@
 Scaling and summing these inequalities by $|\bar{c}_{i}|$ and $|\bar{c}_{j}|$, respectively, and applying the triangle inequality, we obtain:
-\begin{align*}%\label{contra}
+\begin{align*}
 (|\bar{c}_{i}| + |\bar{c}_{j}|) \varepsilon
@@
 \end{align*}
-%
 which contradicts the bound $\varepsilon < L_2(\mathbf{A})/C_1$.
@@
 Setting $\bar J = \pi([m])$ and letting $P = \left( \mathbf{e}_{\pi(1)} \cdots \mathbf{e}_{\pi(m)}\right)$ and $D = \text{diag}(\frac{\bar{c}_1}{c_1},\ldots,\frac{\bar{c}_m}{c_m})$, we see that \eqref{1D} becomes, for all $j \in [m]$:
-\begin{align*}%\label{k=1result}
+\begin{align*}
 \|(\mathbf{A} - \mathbf{B}_{\bar J}\mathbf{PD})_j\|_2 
@@
 
-%\begin{remark}
-%The above arguments can be easily modified to show that the conclusions of Thm.~\ref{DeterministicUniquenessTheorem} in this case ($k=1$) hold for some $n \times m$ submatrix of $\mathbf{B}$ in the event where only an upper bound on the number of columns in $\mathbf{A}$ is known; i.e., the recovered matrix $\mathbf{B}$ is set to have as many or more columns than $\mathbf{A}$.
-%\end{remark}
-
-%It is easy to see that when $m < m'$, the above result holds for the submatrix of $B$ composed of columns indexed by the image of $\pi$.
-
 We require a few additional tools to extend the proof to the general case $k < m$.
@@
 For $\mathbf{u} \in \mathbb R^m$ and vector spaces $U,V \subseteq \mathbb{R}^m$, let $\text{\rm dist}(\mathbf{u}, V) := \inf \{\| \mathbf{u}-\mathbf{v} \|_2: \mathbf{v} \in V\}$ and define:
-%\footnote{Although identical, note the reference \cite{Morris10} defines the supremum over the unit ball.}: %[Kato p.197]
 \begin{align}\label{d}
@@
 \end{align}
-% Note that $d(U,\{\textbf{0}\}) = 1$ for $U \neq \{\mathbf{0}\}$, whereas if $U = \{\textbf{0}\}$ then $d$ has no meaning; in this case, set $d(\{\textbf{0}\},V) = 0$ for any $V$.
 \end{definition}
-%Note that the supremum is always achievable by a point in $U$ when $U, V \subseteq \mathbb{R}^m$.
 
@@
 
-%\begin{lemma}\label{dimLem} %Kato p.200, 
-%\cite[Cor.~2.6]{Kato2013} For subspaces $U,V \subseteq \mathbb{R}^m$, $d(U,V) < 1$ implies $\dim(U) \leq \dim(V)$. 
-%\end{lemma}
-
-%\begin{lemma}\label{eqdim}
-%\cite[Lem.~3.2]{Morris10} If $\dim(U) = \dim(V)$ then $d(U,V) = d(V,U)$. 
-%\end{lemma}
-
 Our result in combinatorial matrix analysis is the following.
 
-%, which we derive by the following arguments (see the Supplemental for the full proof).
-First, we show that the aforementioned proximity between $k$-dimensional subspaces implies a proximity between smaller subspaces spanned by columns of $\mathbf{A}$ indexed by the intersections of sets in $E$ and those spanned by as many or fewer columns of $\mathbf{B}$.
-Another pigeonholing argument here combined with our assumptions on $E$ (e.g., the singleton intersection property) reveals that, in fact, each column of $\mathbf{A}$ spans a subspace proximal to that spanned by some column of $\mathbf{B}$.
-\eqref{Cstable} is a simple consequence of this last fact, which actually constitutes the proof of the theorem for the case $k=1$.
-% We present this special case now before restating the above arguments in greater detail.
-
 \begin{lemma}\label{MainLemma}
-%Suppose $\mathbf{A} \in \mathbb{R}^{n \times m}$ satisfies the spark condition \eqref{SparkCondition} for some $k < m$ and that $E \subseteq {[m] \choose k}$ is $\ell$-regular and satisfies the SIP.
-There is a constant $C_2 > 0$ for which the following holds for all $\varepsilon < L_2(\mathbf{A}) / C_2$.
 Suppose $\mathbf{A} \in \mathbb{R}^{n \times m}$ satisfies \eqref{SparkCondition} for some $k < m$ and that $E \subseteq {[m] \choose k}$ is $\ell$-regular with the SIP.
@@
 \end{align}
-%
 then $\bar m \geq m$, and if $p = \bar m - \ell(\bar m - m)$ is positive:
@@
 
-%\begin{lemma}\label{MainLemma}
-%Fix integers $n$ and $k < m$, and suppose $\mathbf{A} \in \mathbb{R}^{n \times m}$ satisfies the spark condition \eqref{SparkCondition}.
-There exists a constant $C_2 > 0$ for which the following holds for all $\varepsilon < L_2(\mathbf{A}) / C_2$.
-If for some  $\mathbf{B} \in \mathbb{R}^{n \times m}$ and regular $E \subseteq {[m] \choose k}$ with the SIP there exists a map $\pi: E \mapsto {[m] \choose k}$ satisfying:
-%\begin{align}\label{GapUpperBound}
-%d(\text{\rm Span}\{\mathbf{A}_{S}\}, \text{\rm Span}\{\mathbf{B}_{\pi(S)}\}) \leq \varepsilon,\ \ \   \text{for all $S \in E$},
-%\end{align}
-%
-%then there exists a permutation matrix $\mathbf{P}$ and invertible diagonal matrix $\mathbf{D}$ with:
-%\begin{align}\label{MainLemmaBPD}
-%\|\mathbf{A}_j - (\mathbf{BPD})_j\|_2 \leq C_2 \varepsilon, \ \ \  \text{for all } j \in [m].
-%\end{align}
-%\end{lemma}
-
 The constant $C_1 > 0$ in Thm.~\ref{DeterministicUniquenessTheorem} is then defined by\footnote{Note that $\|\mathbf{AX}_{I(S)}\mathbf{c}\|_2 \geq \sqrt{k} L_k(\mathbf{A})\|\mathbf{X}_{I(S)}\mathbf{c}\|_2 \geq k L_k(\mathbf{A}) L_k(\mathbf{X}_{I(S)})\|\mathbf{c}\|_2$ for $S \in E$ and $k$-sparse $\mathbf{c}$.
@@
 \end{align}
-%, we let 
 where, given vectors $\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$, we denote by $\mathbf{X}$ the $m \times N$ matrix with columns $\mathbf{x}_i$ and by $I(S)$ the set of indices $i$ for which the support of $\mathbf{x}_i$ is contained in $S$.
-% := \{i \in [N]: \text{supp}(\mathbf{x}_i) \subseteq S\}$.
 
@@
 \end{definition}
-Note that $\theta \in (0,\frac{\pi}{2}]$ implies $0 < r \leq 1$.\footnote{We acknowledge the counter-intuitive property that $\theta =  \pi/2$ when $U = V$ or $U \perp V$.}  %\textbf{Note:} we can also define $\theta$ by \cite[Lem.~9.5]{Deutsch12}:
-%\begin{align*}
-%\cos{\theta(U,W)} := \max\left\{ |\langle \mathbf{u}, \mathbf{w} \rangle|: \mathbf{u} \in U \cap (U \cap W)^\perp, \|\mathbf{u}\|_2 \leq 1, \mathbf{w} \in W \|\mathbf{w}\|_2 \leq 1  \right\}.
-%\end{align*}
-The constant $C_2$ in Lem.~\ref{MainLemma} can then be expressed as:  % \footnote{Note that $C_2 > 0$ is well-defined since $r > 0$ by definition.}
+Note that $\theta \in (0,\frac{\pi}{2}]$ implies $0 < r \leq 1$.\footnote{We acknowledge the counter-intuitive property that $\theta =  \pi/2$ when $U = V$ or $U \perp V$.}  
+The constant $C_2$ in Lem.~\ref{MainLemma} can then be expressed as:  
 \begin{align}\label{Cdef2}
@@
 
-%Let $\mathbf{X}$ and $\mathbf{\bar{X}}$ be the $m \times N$ matrices with columns $\mathbf{x}_i$ and $\mathbf{\bar x}_i$, respectively. 
 It follows from the general linear position of the $\mathbf{x}_i$ and the linear independence of every $2k$ columns of $\mathbf{A}$ that $L_k(\mathbf{AX}_{K}) > 0$; that is, the columns of the $n \times k$ matrix $\mathbf{AX}_K$ form a basis for $\text{\rm Span}\{\mathbf{A}_{S}\}$.
@@
 &\leq \varepsilon \sqrt{k}  \|\mathbf{c}\|_2 
-%\leq \frac{\varepsilon \sqrt{k}}{L(\mathbf{A}X_{J(S)})} \|\mathbf{A}X_{J(S)}\mathbf{c}\|_2 
 \leq \frac{\varepsilon}{L_k(\mathbf{AX}_K)} \|\mathbf{y}\|_2,
@@
 from which the result follows by \eqref{Cdef1} and Lem.~\ref{MainLemma}.
-%With $C_1$ as in 
 \end{proof}
-% for all $S \in E$:
-%\begin{align}\label{rhs222}
-%d(\text{\rm Span}\{\mathbf{A}_S\}, \text{\rm Span}\{\mathbf{B}_{\bar S}\}) 
-%\leq \frac{\varepsilon}{ \min_{S \in E} L_k(\mathbf{AX}_{I(S)}) }.
-%\end{align}
-%\end{proof}
-
-%We then show that the map over subsets of column indices defined by this association is such that the number of common elements shared by sets in its domain bounds the number of elements common to their images under this map.
 
@@
 We bound the number of $k$-sparse $\mathbf{\bar x}_i$ and then apply Thm.~\ref{DeterministicUniquenessCorollary}. 
-Let $n_p$ be the number of $\mathbf{\bar x}_i$ with $\|\mathbf{\bar x}_i\|_0 = p$.  %, so that $\sum_{p = 1}^{m} n_p = N$. 
+Let $n_p$ be the number of $\mathbf{\bar x}_i$ with $\|\mathbf{\bar x}_i\|_0 = p$.
 Since the $\mathbf{x}_i$ are all $k$-sparse, by \eqref{minsum} we have:
-%\begin{align}
 \mbox{$k \sum_{p = 0}^{\bar m} n_p \geq \sum_{i=0}^N \|\mathbf{x}_i\|_0 \geq \sum_{i=0}^N \|\mathbf{\bar x}_i\|_0 = \sum_{p=0}^{\bar m} p n_p.$}
-%\end{align}
 Hence,
@@
 We now show that no more than $(k-1)|E|$ of the $\mathbf{\bar x}_i$ share a support of size less than $k$. 
-%Let $\mathbf{X}$ and $\mathbf{\bar{X}}$ be the $m \times N$ and $\bar m \times N$ matrices with columns $\mathbf{x}_i$ and $\mathbf{\bar x}_i$, respectively, and let $I(S) = \{i \in [N]: \text{supp}(\mathbf{x}_i) \subseteq S\}$.
 From previous arguments, for every $S \in E$, the columns of each $n \times k$ submatrix of $\mathbf{AX}_{I(S)}$ form a basis for $\text{\rm Span}\{\mathbf{A}_S\}$.
-% the general linear position of the $\mathbf{x}_i$ and the linear independence of every $k$ columns of $\mathbf{A}$ that $L_k(\mathbf{AX}_{I(S)}) > 0$ for all $S \in E$; that is, for every $S \in E$, the columns of every $n \times k$ submatrix of $\mathbf{AX}_{I(S)}$ form a basis for $\text{\rm Span}\{\mathbf{A}_S\}$.
 Suppose that more than $(k-1)|E|$ vectors $\mathbf{\bar x}_i$ share a support $\bar S$ of size $|\bar{S}| < k$.
@@
 In this note, we generalized the approach of \cite{Hillar15} to prove the stability of unique solutions to Probs.~\ref{InverseProblem} and \ref{OptimizationProblem} while significantly reducing the known sample complexity.
-% FRITZ: Inverse problems instead of Data Analysis.
-Don't assume that everyone is assuming they are recovering ground truth.
-Cite results again and state implications!
-Focus on them (probabilistic ones too).
 Our results justify the application of the sparse linear coding model to blind source separation problems, wherein the goal is to infer the generating dictionary and sparse codes from noisy measurements, \eqref{LinearModel}.
@@
 We elaborate on these applications below after discussing theoretical aspects.
-% We close with several application areas.
-
-%\textbf{Inverse Problems}.  
-% from $N=k{m \choose k}^2$ to $N = m(k-1){m \choose k}+m$. 
-% CUT OK?
-Surprisingly, almost all $n \times m$ dictionaries satisfying the standard assumption \eqref{CScondition} from compressed sensing (CS) are identifiable from enough generic noisy $k$-sparse linear combinations of their elements, up to an error linear in the noise.
-Moreover, if solutions are constrained to satisfy \eqref{SparkCondition}, then only an upper bound on the number of dictionary elements need be taken as given.
 
@@
 It would therefore be of practical utility to determine the best possible dependence of $\varepsilon$ on $\delta_1, \delta_2$ in Def.\ref{maindef} as well as the minimal requirements on the number and diversity of generating codes, and we hope that other researchers continue to improve and extend our results.
-We remark that our constants have been derived for deterministic ``worst-case'' noise, whereas the ``effective'' noise might be smaller when sampled from a distribution; in such cases, the constants %Thms.~\ref{DeterministicUniquenessTheorem},~\ref{DeterministicUniquenessTheorem2}
+We remark that our constants have been derived for deterministic ``worst-case'' noise, whereas the ``effective'' noise might be smaller when sampled from a distribution; in such cases, the constants
 will improve as well.
-
-%We note also that these results extend trivially to cases where point-wise injective nonlinearities are applied to the data.
 
@@
 In these cases, assurances such as those offered by our theorems certify that different devices (with different initialization, samples, etc.) will learn equivalent representations given enough data from statistically identical systems.
-%Data science:
-%  
-%in a common application of compressed sensing in engineering
 
-%\textbf{Theoretical Neuroscience}.
 In the field of theoretical neuroscience in particular, dictionary learning for sparse coding and related methods have recovered characteristic components of natural images \cite{Olshausen96, hurri1996image, bell1997independent, van1998independent} and sounds \cite{bellsejnowski1996, smithlewicki2006, Carlson12} that reproduce response properties of cortical neurons.
@@
 
-% \small{\small{\textbf{ACKNOWLEDGMENTS.}}} We thank Friedrich Sommer and Darren Rhea for early thoughts, and Ian Morris for \eqref{eqdim}.
-
-% This breaks:  Proof of Main Lemma 1 somehow appears earlier than it should be....weird
 \acknow{We thank Friedrich Sommer and Darren Rhea for early thoughts, and Ian Morris for posting \eqref{eqdim} online.}
@@
 
-%\begin{lemma}\label{NonEmptyLemma} 
-%Fix $\ell, m$, and $\bar m$. Suppose $E \subseteq 2^{[m]}$ is $\ell$-regular with the SIP.  If $\pi: E \to 2^{[\bar m]}$ has $\sum_{S \in E} |S| = \sum_{S \in E} |\pi(S)|$ and:
-%\begin{align}\label{cond}
-%|\bigcap_{S \in F} \pi(S)| \leq |\bigcap_{S \in F} S |,\ \ \   \text{for } F \subseteq E,
-%\end{align}
-%then $\bar m \geq m$ and the association $i \mapsto \cap \pi(F(i))$ defines an injective map from $J$ to $[\bar m]$ for some $J \subseteq [m]$ of size $p = \bar m - \ell(\bar m - m)$.
-In particular, if $\bar m = m$ then the map $\pi$ is induced by a permutation.
-%\end{lemma}
-% i'm placing this on hold since one thing i found was that i needed pi to be injective, but for that i needed the fact that |pi(S)| = |S|
-
 \begin{lemma}\label{NonEmptyLemma} 
@@
 \begin{align}\label{cond}
-%|\bigcap_{S \in F} \pi(S)| \leq |\bigcap_{S \in F} S |,\ \ \   \text{for } F \subseteq E,
 |\cap \pi(F)| \leq |\cap F |,\ \ \   \text{for } F \subseteq E,
@@
 By the assumption \eqref{cond}, the intersection of $F_1$ is nonempty, and in fact must contain exactly $\ell$ elements by regularity.
-%Thus, $F_1$ is the star of some element $i_1 \in [m]$.  
 From the SIP, the intersection of sets in $F_1$ is $\{i_1\}$, which by \eqref{cond} implies that the intersection of $\pi(S)$ with $S \in F_1$ also contains exactly one element.

### 2017-04-13 manuscripts/PNAS/chazthm_pnas.tex
got rid of CS abbrev

@@
 Note that any particular solution $(\mathbf{B}, \mathbf{\bar x}_1 \ldots, \mathbf{\bar x}_N)$ to this problem gives rise to an orbit of equivalent solutions $(\mathbf{BPD}, \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\bar x}_1, \ldots, \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\bar x}_N)$, where $\mathbf{P}$ is any permutation matrix and $\mathbf{D}$ any invertible diagonal.
-Previous theoretical work addressing the noiseless case $\eta =0$ (e.g., \cite{li2004analysis, Georgiev05, Aharon06, Hillar15}) has shown that a solution to Prob.~\ref{InverseProblem} (when it exists) is indeed unique up to this inherent ambiguity provided the $\mathbf{x}_i$ are sufficiently diverse and the generating matrix $\mathbf{A}$ satisfies the \textit{spark condition} from compressive sensing (CS):
+Previous theoretical work addressing the noiseless case $\eta =0$ (e.g., \cite{li2004analysis, Georgiev05, Aharon06, Hillar15}) has shown that a solution to Prob.~\ref{InverseProblem} (when it exists) is indeed unique up to this inherent ambiguity provided the $\mathbf{x}_i$ are sufficiently diverse and the generating matrix $\mathbf{A}$ satisfies the \textit{spark condition} from compressive sensing:
 \begin{align}\label{SparkCondition}
@@
 
-To see how Def. \ref{maindef} directly relates to Prob. \ref{InverseProblem}, suppose that $Y$
-
-has a stable $k$-sparse representation in $\mathbb{R}^m$ and fix $\delta_1, \delta_2$ to be the desired recovery accuracy in \eqref{def1}.
+To see how Def.
+\ref{maindef} directly relates to Prob.
+\ref{InverseProblem}, suppose that $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$ and fix $\delta_1, \delta_2$ to be the desired recovery accuracy in \eqref{def1}.
 Consider now any dataset $Z$ generated as in \eqref{LinearModel} with $\eta \leq \frac{1}{2} \varepsilon(\delta_1, \delta_2)$.
@@
 Clearly, for any $\mathbf{M}$ satisfying \eqref{SparkCondition}, we have $L_{k'}(\mathbf{M}) > 0$ for  $k' \leq 2k$.
-We note that the quantity $1 - \sqrt{k} L_k(\mathbf{M})$ is also known in the CS literature as the (asymmetric) lower restricted isometry constant \cite{Blanchard2011}.
+We note that the quantity $1 - \sqrt{k} L_k(\mathbf{M})$ is also known in the compressive sensing literature as the (asymmetric) lower restricted isometry constant \cite{Blanchard2011}.
 
@@
 We require a few additional tools to extend the proof to the general case $k < m$.
-These include a generalized notion of distance (Def.~\ref{dDef}) and angle (Def.~\ref{FriedrichsDefinition}) between subspaces and a stability result in combinatorial matrix analysis (Lem.~\ref{MainLemma}).
+These include a generalized notion of distance (Def.~\ref{dDef}) and angle (Def.~\ref{FriedrichsDefinition}) between subspaces as well as a stability result in combinatorial matrix analysis (Lem.~\ref{MainLemma}).
 

### 2017-04-14 manuscripts/PNAS/chazthm_pnas.tex
fixed pnas weirdness
last edit
clarify thm 2

@@
 There is a polynomial $g$ in the entries of $\mathbf{A}$ and $\mathbf{x}_i$ with the following property:  if $g$ evaluates to a nonzero number and more than \mbox{$(k-1){m \choose k}$} of the resulting $\mathbf{x}_i$ are supported on each $S \in E$ for some regular $E \subseteq {[m] \choose k}$ with the SIP, then $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$ (Def.~\ref{maindef}).
-In particular, either no substitutions impart to $Y$ this property or all but a Borel set of measure zero do.
+In particular, all -- except for a Borel set of measure zero -- substitutions impart to $Y$ this property.
 \end{theorem}
@@
 
-Thus, choosing the dictionary and sparse codes ``randomly'' from \emph{any} continuous distribution generates data with stable sparse representations almost certainly.
+Thus, choosing the dictionary and sparse codes ``randomly'' almost certainly generates data with stable sparse representations.
 
@@
 
-\clearpage
+\pnasbreak
 
@@
 
+\pnasbreak
+
 \end{document}

### 2017-04-16 manuscripts/PNAS/chazthm_pnas.tex
problem 2 typo

@@
 \begin{problem}\label{OptimizationProblem}
-Find a matrix $\mathbf{B} \in \mathbb{R}^{\bar m}$ and $k$-sparse $\mathbf{\bar x}_1, \ldots, \mathbf{\bar x}_N \in \mathbb{R}^{\bar m}$ that solve:
+Find a matrix $\mathbf{B} \in \mathbb{R}^{\bar m}$ and vectors \mbox{$\mathbf{\bar x}_1, \ldots, \mathbf{\bar x}_N \in \mathbb{R}^{\bar m}$} that solve:
 \begin{align}\label{minsum}

### 2017-06-29 manuscripts/PNAS/lil' lemma.tex
lil lemma

\documentclass[journal, onecolumn]{IEEEtran}

% *** MATH PACKAGES ***
\usepackage{amsmath, amssymb, amsthm} 
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{conjecture}{Conjecture}
\newtheorem{problem}{Problem}
\newtheorem{question}{Question}
\newtheorem{proposition}{Proposition}
\newtheorem{definition}{Definition}
\newtheorem{corollary}{Corollary}
\newtheorem{remark}{Remark}
\newtheorem{example}{Example}

\usepackage[pdftex]{graphicx}

% *** ALIGNMENT PACKAGES ***
\usepackage{array}

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}

\begin{document}

\title{lil' Lemma}

\author{C. Garfinkle}

\maketitle

\begin{lemma}
Suppose $E \subseteq 2^{[m]}$ is a hypergraph with the SIP and let $d_1 \geq d_2 \geq \ldots \geq d_m$ be the degree sequence of nodes in $E$. If for some $\bar m$ the map $\pi: E \to 2^{[\bar m]}$ has $\sum_{S \in E} |\pi(S)| = \sum_{S \in E} |S|$ and:
\begin{align}\label{cond}
|\cap \pi(F)| \leq |\cap F | \text{ for all } F \subseteq E,
\end{align}
then $\bar m \geq\sum_i d_i / d_1$ and the association $i \mapsto \cap \pi(F(i))$ defines an injective map from $J$ to $[\bar m]$ for some $J \in {[m] \choose p}$, where $p$ (provided it exists) is the largest positive integer in $\{1, \ldots, m\}$ satisfying:
\begin{align}\label{pcond}
\sum_{i=\ell}^{m} d_{i} > (\bar m + 1 - \ell) (d_\ell - 1) \ \ \text{for all } \ell \leq p.
\end{align}
If $\bar m < \sum_i d_i / (d_1 - 1)$ then $p \geq 1$. 
In particular, if $\bar m = m$ and $E$ is regular, then $\pi$ is induced by a permutation on $[m]$. 
\end{lemma}

\begin{proof}
Consider the collection of pairs: $T_1 := \{(i, S): i \in \pi(S), S \in E\}$, which number $|T_1| = \sum_{S \in E} |\pi(S)| = \sum_{S \in E} |S| = \sum_{i \in [m]} d_i$. Note that assumption \eqref{cond} implies $\bar m \geq |T_1| / d_1$, since otherwise pigeonholing the elements of $T_1$ with respect to their set of possible first indices $[\bar m]$ would lead us to conclude that there are more than $d_1$ sets in $E$ sharing a common element. %QUESTION: Do we really need to say this..?

By \eqref{pcond} we have $|T_1| >  \bar m (d_1 - 1)$, which implies, again by the pigeonhole principle, that there must be at least $d_1$ elements of $T_1$ sharing the same first index. By \eqref{cond}, the intersection of the set $F_1$ consisting of their second indices is non-empty. As $d_1 \geq d_i$ for all $i$, and $E$ satisfies the SIP, it must be that the sets in $F_1$ intersect at a singleton. Since $\cap \pi(F_1)$ is non-empty, applying \eqref{cond} again implies $\cap \pi(F_1) = \{i_1\}$ for some $i_1 \in [m]$.

If $p=1$ then we are done. Otherwise, define $T_2 := T_1 \setminus \{(i_1,S) \in T_1: S \in E\}$, which contains $|T_2| = |T_1| - d_1 = \sum_{i=2}^m d_i$ ordered pairs having $\bar m - 1$ distinct first indices. By \eqref{pcond} we have $|T_2| > (\bar m - 1)(d_2 - 1)$ and reiterating the above arguments produces a (necessarily) distinct index $i_2$. Iterating the arguments $p$ times yields the set of singletons \mbox{$J = \{\cap F_1, \ldots, \cap F_p\} \subseteq [m]$}.
\end{proof}

\begin{remark}[Regular hypergraphs]
Note that if $E$ is $d$-regular then $\sum_{i=\ell}^m d = (m-\ell+1) d$ and we have $\bar m \geq \sum_i d_i / d_1 \geq m$ while \eqref{pcond} becomes $\ell < \bar m - (\bar m - m) d + 1$ for all $\ell \leq p$. Hence, it suffices to know that $p = \bar m - (\bar m - m) d$ is positive to know that \eqref{pcond} is satisfied, which is true if an only if $\bar m < md / (d+1)$. Hence we must have $m \leq \bar m < md / (d-1)$ for the conclusion of the lemma to hold for some non-empty $J \subseteq [m]$. We therefore have $J = [m]$ when $\bar m = m$ and $E$ is regular. 
%Hence, the lemma holds for the largest number $p \leq \bar m - (\bar m - m) d$ in the interval $1 \leq p \leq m$, which is guaranteed for $p = \bar m - (\bar m - m) d$ if $m \leq \bar m \leq (md-1) / (d-1)$. We can't have $\bar m < m$ since $\bar m \geq \sum_i d_i / d_1 = m$ by the contradiction discussed in the proof. 
\end{remark}

\begin{remark}[General hypergraphs]
For what range of values of $\bar m$ can we guarantee there exists some $p \in \{1, \ldots, m\}$ in general? If $\bar m < \sum_i d_i / (d_1-1)$ then we can peel off at least one index for any hypergraph, i.e. $p \geq 1$. Can we find a lower bound on $\bar m$ in general, though (not just for regular hypergraphs)? The difficulty is we have to make sure \eqref{pcond} holds for \emph{all} values of $\ell \leq p$, which was easy for regular hypergraphs (by the resulting transitivity of \eqref{pcond}). My thought is that in general the lower bound $\bar m \geq \sum_i d_i / d_1$ which *has* to hold given \eqref{cond} might not correspond to what condition \eqref{pcond}, which comes from our crappy pigeonholing, gives us as a constraint on $\bar m$ when we make the substitution $p=m$ (as was the case for regular hypergraphs). Could we have $\bar m < m$ but still recover a positive $p$ number of indices?
\end{remark}

\begin{question}
Do we only need $E$ to satisfy the SIP on the $p$ nodes of highest degree, those we end up isolating, for all of Chaz' Thm. to run through? That would be good!
\end{question}

\end{document}

### 2017-07-09 manuscripts/PNAS/chazthm_pnas.tex
tiny edit
newness

@@
 % Use letters for affiliations, numbers to show equal authorship (if applicable) and to indicate the corresponding author
-\author[a,1]{Charles J. Garfinkle}
+\author[a,b, 1]{Charles J. Garfinkle}
 \author[a,1]{Christopher J. Hillar}
@@
 \affil[a]{Redwood Center for Theoretical Neuroscience, Berkeley, CA, USA}
+\affil[b]{Helen Wills Neuroscience Institute, UC Berkeley}
 
@@
 
+\pagebreak
+
 To see how Def.
@@
 
-All other proofs are relegated to the Supplemental. 
+All other proofs are relegated to the Section \ref{proofs}. 
 Finally, we present several applications in Discussion Sec.~\ref{Discussion}.
@@
 \begin{definition}\label{sip}
-Given $E \subseteq 2^{[m]}$, the \textbf{star} $F(i)$ at $i$ is the set of $S \in E$ with $i \in S$.
-We say $E$ has the \textbf{singleton intersection property} (\textbf{SIP}) when $\cap F(i) = \{i\}$ for all $i \in [m]$.
+Given $E \subseteq 2^{[m]}$, the \textbf{star} $H(i)$ at $i$ is the set of $S \in E$ with $i \in S$.
+We say $E$ has the \textbf{singleton intersection property} (\textbf{SIP}) when $\cap H(i) = \{i\}$ for all $i \in [m]$.
+%We say $E$ has the SIP \textbf{of order $p$} when $\cap F(i) = \{i\}$ for every node $i$ for which $\text{deg(i)} \geq d_p$, where $d_1 \geq \ldots \geq d_m$ is the degree sequence of $E$.
 \end{definition}
 
-It is easy to verify that for every $k < m$, there is a regular $k$-uniform hypergraph that satisfies the SIP; for instance, consecutive intervals of length $k$ in some cyclic order on $[m]$.
-
 Next, we describe a quantitative version of the spark condition.  
-The \emph{lower bound} \cite{Grcar10} of a matrix $\mathbf{M} \in \mathbb R^{n \times m}$ is the largest number $\alpha$ such that \mbox{$\|\mathbf{M}\mathbf{x}\|_2 \geq \alpha\|\mathbf{x}\|_2$} for all $\mathbf{x} \in \mathbb{R}^m$.
+The \emph{lower bound} $L$ of a matrix $\mathbf{M} \in \mathbb R^{n \times m}$ is the largest number $\alpha$ such that \mbox{$\|\mathbf{M}\mathbf{x}\|_2 \geq \alpha\|\mathbf{x}\|_2$} for all $\mathbf{x} \in \mathbb{R}^m$ \cite{Grcar10}.
 By compactness of the unit sphere, every injective linear map has a nonzero lower bound; hence, if $\mathbf{M}$ satisfies \eqref{SparkCondition}, then each submatrix formed from $2k$ of its columns or less has a nonzero lower bound.
 This motivates the following definition:
+%\begin{align*}
+%L_k(\mathbf{M}) := \frac{1}{\sqrt{k}}\max \{ \alpha : \|\mathbf{M}\mathbf{x}\|_2 \geq \alpha\|\mathbf{x}\|_2 \text{ for all $k$-sparse } \mathbf{x}\}.
+%\end{align*}
 \begin{align*}
-L_k(\mathbf{M}) := \frac{1}{\sqrt{k}}\max \{ \alpha : \|\mathbf{M}\mathbf{x}\|_2 \geq \alpha\|\mathbf{x}\|_2 \text{ for all $k$-sparse } \mathbf{x}\}.
+L_E(\mathbf{M}) := \inf \left\{ \frac{ \|\mathbf{M}_{S \cup S'}\mathbf{x}\|_2 }{ \sqrt{2k} \|\mathbf{x}\|_2} : \mathbf{x} \in \mathbb{R}^{|S\cup S'|}, \ \ S,S' \in E \right\}
+%\frac{1}{\sqrt{k}}\max \{ \alpha : \|\mathbf{M}\mathbf{x}\|_2 \geq \alpha\|\mathbf{x}\|_2 \text{ for all $k$-sparse } \mathbf{x}\}.
 \end{align*} 
+%
+and we write $L_{2k}:= L_E$ when $E = {[m] \choose k}$. Note that $ L = L_{\{[m]\}}$ whereas $L_{[m]} = L_2$. [TODO: note that $L_2$ implied by $L_E$]
 
@@
 \begin{theorem}\label{DeterministicUniquenessTheorem}
-Let $\mathbf{A}~\in~\mathbb{R}^{n \times m}$ satisfy \eqref{SparkCondition} for $k < m$, and suppose for some $\bar m$ that more than \mbox{$(k-1){\bar m \choose k}$} $k$-sparse \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} are supported in general linear position on each set in an $\ell$-regular $E \subseteq {[m] \choose k}$ with the SIP.
-There is a constant\footnote{We delay defining the constant $C_1$ until Section \ref{DUT} (\eqref{Cdef1}).} $C_1 > 0$ for which the following holds for $\varepsilon < L_2(\mathbf{A}) / C_1$:
+Fix a matrix $\mathbf{A} \in \mathbb{R}^{n \times m}$ with $L_E(\mathbf{A}) > 0$ for some regular $E \subseteq {[m] \choose k}$ with the SIP.
+If the sequence \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} contains, for each $S \in E$, more than $(k-1){m \choose k}$ vectors in general linear position supported on $S$, then there is a constant\footnote{We delay defining the constant $C_1$ until Section \ref{DUT} (\eqref{Cdef1}).} $C_1 > 0$ for which the following holds for all $\varepsilon < L_{2}(\mathbf{A}) / C_1$:
 
-Every matrix $\mathbf{B}$ and $k$-sparse $\mathbf{\bar x}_1, \ldots, \mathbf{\bar x}_N \in \mathbb{R}^{\bar m}$ with  \mbox{$\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\bar x}_i\|_2 \leq \varepsilon$} for all $i$ must have $\bar m \geq m$ and, provided $p = \bar m - \ell(\bar m - m)$ is positive, necessarily satisfy:
+Every real $n \times \bar m$ matrix $\mathbf{B}$ for which there exist $k$-sparse $\mathbf{\bar x}_1, \ldots, \mathbf{\bar x}_N$ satisfying \mbox{$\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\bar x}_i\|_2 \leq \varepsilon$} for all $i$ has $\bar m \geq m$ and, provided $\bar m < mr/(r-1)$, an associated permutation $\mathbf{P}$ and invertible diagonal $\mathbf{D}$ such that:
 \begin{align}\label{Cstable}
-\|(\mathbf{A}_J- \mathbf{B}_{\bar J} \mathbf{PD} )_j\|_2 \leq C_1 \varepsilon, \ \  \text{for $j \in J$},
+\|(\mathbf{A_J})_j- \mathbf{B}_{\bar J} \mathbf{PD}_j\|_2 \leq C_1 \varepsilon \ \ \text{for all } j \in J,
 \end{align}
-for some $J \in {[m] \choose p}$, $\bar J \in {[\bar m] \choose p}$, permutation matrix $\mathbf{P}$, and invertible diagonal matrix $\mathbf{D}$.
+%
+for some non-empty $J, \bar J \subseteq [m]$ of size $\bar m - r(\bar m - m)$.
 
-Furthermore, if $\varepsilon < L_{2k}(\mathbf{A}_J) / C_1$, then $\mathbf{B}_{\bar J}$ also satisfies \eqref{SparkCondition} with $L_{2k}(\mathbf{B}_{\bar J}\mathbf{PD}) \geq L_{2k}(\mathbf{A}_J) - C_1 \varepsilon$, and:
+Moreover, if in fact $L_{2k}(\mathbf{A}) > 0$ and $\varepsilon < L_{2k}(\mathbf{A}) / C_1$ then $L_{2k}(\mathbf{B}\mathbf{PD}) \geq L_{2k}(\mathbf{A}) - C_1 \varepsilon$ and:
 \begin{align}\label{b-PDa}
-\|\mathbf{x}_i^J - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\bar x}_i^{\bar J}\|_1 &\leq  \left( \frac{ 1+C_1 \|\mathbf{x}_i^{J}\|_1 }{ L_{2k}(\mathbf{A}_J) -  C_1\varepsilon } \right) \varepsilon,\ \ \   \text{for $i \in [N]$}.
+\|\mathbf{x}^J_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\bar x}^{\bar J}_i\|_1 &\leq  \left( \frac{ 1+C_1 \|\mathbf{x}^{J}_i\|_1 }{ L_{2k}(\mathbf{A}) -  C_1\varepsilon } \right) \varepsilon,\ \ \   \text{for $i \in [N]$}.
 \end{align}
 \end{theorem}
+% You can recover matrices that don't satisfy the spark condition, but to uniquely recover k-sparse codes (since no limitation on their supports!) you need to have the spark condition.
+i guess...?
+Or can we use our knowledge of the particular permutation P to get rid of spark condition?
 
+%To be clear, the implication of Thm.~\ref{DeterministicUniquenessTheorem} is that $Y = \{\mathbf{Ax}_1, \ldots, \mathbf{Ax}_N\}$ has a stable $k$-sparse representation in $\mathbb{R}^m$, with \eqref{def1} guaranteed provided $\varepsilon$ in Def.~\ref{maindef} does not exceed:
 To be clear, Thm.~\ref{DeterministicUniquenessTheorem} says that the smaller the difference $\bar m - m$, the more columns and coefficients of the original dictionary $\mathbf{A}$ and codes $\mathbf{x}_i$ contained (up to noise) in the appropriately scaled dictionary $\mathbf{B}$ and codes $\mathbf{\bar x}_i$.
-The implication in the case $\bar{m} = m$ is precisely that $Y = \{\mathbf{Ax}_1, \ldots, \mathbf{Ax}_N\}$ has a stable $k$-sparse representation in $\mathbb{R}^m$, with \eqref{def1} guaranteed provided $\varepsilon$ in Def.~\ref{maindef} does not exceed:
+The implication in the case $\bar m = m$ is that $Y = \{\mathbf{Ax}_1, \ldots, \mathbf{Ax}_N\}$ has a stable $k$-sparse representation in $\mathbb{R}^m$, with \eqref{def1} guaranteed provided $\varepsilon$ in Def.~\ref{maindef} does not exceed:
 \begin{align}\label{epsdel}
@@
 
-It so happens that producing sparse codes in general linear position is straightforward with a ``Vandermonde'' matrix construction (e.g., see \cite{Hillar15}). We therefore have:
+%In fact, a more general result (stated clearly in the next section) can be gleaned from our method of proving Thm.~\ref{DeterministicUniquenessTheorem}.
+Briefly, in cases where $\mathbf{B}$ has $\bar m \neq m$ columns, or $E$ is not regular or only partially satisfying the SIP, a relation between $\bar m$ and the degree sequence of nodes in $E$ gives indices $J \subseteq [m]$ defining a submatrix $\mathbf{A}_J$ and subvectors $\mathbf{x}_i^J$ that are recoverable in the sense of \eqref{Cstable} and \eqref{b-PDa}.
+For example, if $E$ is $\ell$-regular with the SIP but $m \leq \bar m < m\ell/(\ell - 1)$ then we have nonzero $|J| = \bar m - \ell(\bar m - m)$.
+The implication here is that the smaller the difference $\bar m - m$, the more columns and code entries of the original $n \times m$ dictionary $\mathbf{A}$ and codes $\mathbf{x}_i$ contained (up to noise) in the appropriately scaled $n \times \bar m$ dictionary $\mathbf{B}$ and codes $\mathbf{\bar x}_i$.
+When $\bar m = m$, we recover Thm.~\ref{DeterministicUniquenessTheorem}.
+Regarding the assumptions of Thm.~\ref{DeterministicUniquenessTheorem}, it is easy to verify that for every $k < m$, there is a regular $k$-uniform hypergraph that satisfies the SIP; for instance, consecutive intervals of length $k$ in some cyclic order on $[m]$.
+In fact, even if $E$ is not regular or only partially satisfies the SIP, a relation between $\bar m$ and the degree sequence of nodes in $E$ may give the indices $J \subseteq [m]$.
+For sake of brevity, we delay to the next section a clear statement of this more general result.
+
+It also happens that producing sparse codes $\mathbf{x}_i$ in general linear position is straightforward with a ``Vandermonde'' matrix construction (e.g., see \cite{Hillar15}). We therefore have:
 
@@
 
-As already mentioned, it is easy to construct a regular hypergraph $E \subseteq {[m] \choose k}$ with the SIP having cardinality $|E| = m$, implying the lower bound for sample size $N$ from the introduction.
-In many cases, however, the SIP can be achieved with far fewer supports; for example, when $k = \sqrt{m}$ one can take $E$ to be the $2k$ rows and columns formed by arranging $[m]$ in a square grid.
+As already mentioned, there exist $k$-uniform regular hypergraphs $E$ with the SIP having cardinality $|E| = m$, implying the lower bound for sample size $N$ from the introduction.
+In many cases, however, the SIP can be achieved with far fewer supports; for example, when $k = \sqrt{m}$, take $E$ to be the $2k$ rows and columns formed by arranging $[m]$ in a square grid.
 
@@
 \end{corollary}
+
+%\pagebreak
 
@@
 
-Since $f$ is an analytic function, having one substitution of real numbers with $f(\mathbf{A}) \neq 0$ implies that its zeroes form a set of measure zero.
+Since $f$ is an analytic function, if there exists one substitution of a real matrix $\mathbf{A}$ such that $f(\mathbf{A}) \neq 0$ then the zeroes of $f$ in fact form a set of measure zero.
 Fortunately, such a matrix $\mathbf{A}$ is easily constructed by adding rows of zeroes to any $\min(2k,m) \times m$ Vandermonde matrix $[\gamma_i^j]_{i,j=1}^{k,m}$ with distinct $\gamma_i$ (so that each term in the product above is nonzero).
-Hence, almost every real $n \times m$ matrix $\mathbf{A}$ with $n \geq \min(2k,m)$ satisfies \eqref{SparkCondition}.
+Hence, almost every real $n \times m$ matrix with $n \geq \min(2k,m)$ satisfies \eqref{SparkCondition}.
 
@@
 \begin{corollary}\label{ProbabilisticCor}
-Fix $k < m$ and $n \geq \min(2k, m)$ 
-and let the entries of $\mathbf{A} \in \mathbb{R}^{n \times m}$ and $k$-sparse $\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$ be drawn independently from probability measures absolutely continuous with respect to the standard Borel measure $\mu$.
+Fix $k < m$ and $n \geq \min(2k, m)$ and let the entries of $\mathbf{A} \in \mathbb{R}^{n \times m}$ and $k$-sparse $\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$ be drawn independently from probability measures absolutely continuous with respect to the standard Borel measure $\mu$.
 If more than $(k-1){m \choose k}$ of the vectors $\mathbf{x}_i$ are supported on each $S \in E$ for a regular $E \subseteq {[m] \choose k}$ with the SIP, then $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$ with probability one.
@@
 
+As mentioned in the previous section, Thm.~\ref{DeterministicUniquenessTheorem} is a particular case of a more general result that forgoes the assumptions of regularity and SIP on the hypergraph $E \subseteq {[m] \choose k}$.
+If instead we require only that the stars $\cap H(i)$ intersect at singletons for all $i \leq q$ (assuming that the nodes of $E$ are labeled in some order of non-increasing degree), we have that $\bar m \geq k|E| / \deg(1)$ and, provided $\bar m < k|E| / (\deg(1) - 1)$, the non-empty submatrix $J$ is of size equal to the largest number $p$ satisfying:
+\begin{align}\label{pcond}
+\sum_{i=\ell}^{m} \deg(i) > (\bar m + 1 - \ell) (\deg(\ell) - 1) \ \ \text{for all } \ell \leq p \leq q.
+\end{align}
+Specifically, $J$ consists of the union of the set of all nodes of degree exceeding $\deg(p)$ and some subset of those nodes with degrees equal to $\deg(p)$.
+For the benefit of the reader, we do not prove this more general result below; it can be gleaned by examining how exactly Lemma \ref{NonEmptyLemma} is incorporated into the proof of Lem.~\ref{MainLemma}.
+%As mentioned in the previous section, Thm.~\ref{DeterministicUniquenessTheorem} is a particular case of a more general result, which requires a looser set of constraints on the hypergraph $E$ and which applies to $n \times \bar m$ matrices $\mathbf{B}$ (and $\bar m$-dimensional codes $\mathbf{\bar x}_i$) with $\bar m \neq m$:
+
+%Fix $\bar m$ and suppose the assumptions of Thm.~\ref{DeterministicUniquenessTheorem} hold, only now with the constraints on $E \subseteq {[m] \choose k}$ being just that $|\cap H(i)| = 1$ for all $i \leq q$ (assuming w.l.o.g.
+that the nodes of $E$ are labeled in some order of non-increasing degree), and with more than $(k-1){\bar m \choose k}$ vectors $\mathbf{x}_i$ supported in g.l.p.
+on each $S \in E$.
+Then we must have $\bar m \geq k|E| / \deg(1)$ and, provided $\bar m < k|E| / (\deg(1) - 1)$, the guarantee \eqref{Cstable} holds for a submatrix $\mathbf{A}_J$, where $J \subseteq[m]$ is nonempty and of a size equal to the largest number $p$ satisfying:
+%\begin{align}\label{pcond}
+%\sum_{i=\ell}^{m} \deg(i) > (\bar m + 1 - \ell) (\deg(\ell) - 1) \ \ \text{for all } \ell \leq p \leq q.
+%\end{align}
+%Specifically, $J$ consists of the union of the set of all nodes of degree exceeding $\deg(p)$ and some subset of those nodes with degrees equal to $\deg(p)$.
+
+%For the benefit of the reader, we prove below the case where we forgo only the constraint that $\bar m = m$.
+This yields the implication $\bar m \geq m$ and \eqref{pcond} reduces to $|J| = \bar m - r(\bar m - m)$.
+The extension to the general result above can be seen by examining how exactly Lemma \ref{NonEmptyLemma} is incorporated into the overall proof.
+
 % ======== b - PDa =========
-First, note that $\|\mathbf{x}\|_1 \leq \sqrt{k} \|\mathbf{x}\|_2$ for $k$-sparse $\mathbf{x} \in \mathbb{R}^m$, which by definition of $L_k$ implies the following inequality:
+
+We now begin our proof of Thm.~\ref{DeterministicUniquenessTheorem} by showing how dictionary recovery \eqref{Cstable} already implies sparse code recovery \eqref{b-PDa} when $L_{2k}(\mathbf{A}) > 0$ and \mbox{$\varepsilon < L_{2k}(\mathbf{A}) / C_1$}, assuming without loss of generality that $\bar m = m$.
+First, note that $\|\mathbf{x}\|_1 \leq \sqrt{k} \|\mathbf{x}\|_2$ for $k$-sparse $\mathbf{x} \in \mathbb{R}^m$, which by definition of $L_E$ implies the following frequently applied inequality valid for any $E \subseteq 2^{[m]}$:
 \begin{align}\label{delrho}
-L_k(\mathbf{A}) \leq \frac{\|\mathbf{A}\mathbf{x}\|_2}{\sqrt{k} \|\mathbf{x}\|_2} 
+L_{E}(\mathbf{A}) \leq \frac{\|\mathbf{A}\mathbf{x}\|_2}{\sqrt{2k} \|\mathbf{x}\|_2} 
 \leq  \max_{j \in [m]}\|\mathbf{A}_j\|_2,
 \end{align}
-which we frequently use.
-
-We begin by showing how dictionary recovery \eqref{Cstable} already implies sparse code recovery \eqref{b-PDa} when \mbox{$\varepsilon < L_{2k}(\mathbf{A}) / C_1$}, assuming without loss of generality that $\bar m = m$.
-For $2k$-sparse $\mathbf{x} \in \mathbb{R}^m$, the triangle inequality gives \mbox{$\|(\mathbf{A}-\mathbf{BPD})\mathbf{x}\|_2  \leq C_1\varepsilon \|\mathbf{x}\|_1 \leq C_1 \varepsilon \sqrt{2k}  \|\mathbf{x}\|_2$}.
+For $k$-sparse $\mathbf{x} \in \mathbb{R}^m$, the triangle inequality gives \mbox{$\|(\mathbf{A}-\mathbf{BPD})\mathbf{x}\|_2  \leq C_1\varepsilon \|\mathbf{x}\|_1 \leq C_1 \varepsilon \sqrt{2k}  \|\mathbf{x}\|_2$}.
 Thus,
@@
 \begin{lemma}\label{MainLemma}
-Suppose $\mathbf{A} \in \mathbb{R}^{n \times m}$ satisfies \eqref{SparkCondition} for some $k < m$ and that $E \subseteq {[m] \choose k}$ is $\ell$-regular with the SIP.
-There exists $C_2 > 0$ for which the following holds for all $\varepsilon < L_2(\mathbf{A}) / C_2$.
+Suppose $\mathbf{A} \in \mathbb{R}^{n \times m}$ has $L_E(\mathbf{A}) > 0$ for some $r$-regular $E \subseteq {[m] \choose k}$ with the SIP.
+There exists $C_2 > 0$ for which the following holds for all $\varepsilon < L_2(\mathbf{A}) / C_2$:
 
@@
 \end{align}
-then $\bar m \geq m$, and if $p = \bar m - \ell(\bar m - m)$ is positive:
+then $\bar m \geq m$, and provided $\bar m < mr /(r-1)$, there exists a permutation matrix $\mathbf{P}$ and invertible diagonal matrix $\mathbf{D}$ such that:
 \begin{align}\label{MainLemmaBPD}
-\|(\mathbf{A}_J - \mathbf{B}_{\bar J}\mathbf{PD})_j\|_2 \leq C_2 \varepsilon, \ \  \text{for } j \in J,
+\|(\mathbf{A}_J)_j - \mathbf{BPD}_j\|_2 \leq C_2 \varepsilon, \ \  \text{for } j \in J,
 \end{align}
-for some $J \in {[m] \choose p}$, $\bar J \in {[\bar m] \choose p}$, permutation matrix $\mathbf{P}$, and invertible diagonal matrix $\mathbf{D}$.
+for some non-empty $J$ of size $\bar m - r(\bar m - m)$.
 \end{lemma}
+
+%\begin{lemma}\label{MainLemma}
+%Fix $\mathbf{A} \in \mathbb{R}^{n \times m}$ with $L_E(\mathbf{A}) > 0$ for some regular $E \subseteq {[m] \choose k}$ with the SIP.
+There exists a constant $C_2 > 0$ for which the following holds for all $\varepsilon < L_2(\mathbf{A}) / C_2$:
+
+%If a matrix $\mathbf{B} \in \mathbb{R}^{n \times m}$ and map $\pi: E \mapsto {m \choose k}$ satisfy:
+%\begin{align}\label{GapUpperBound}
+%d(\text{\rm Span}\{\mathbf{A}_{S}\}, \text{\rm Span}\{\mathbf{B}_{\pi(S)}\}) \leq \varepsilon, \ \ \text{for $S \in E$},
+%\end{align}
+%then there exist a permutation matrix $\mathbf{P}$ and invertible diagonal matrix $\mathbf{D}$ such that:
+%\begin{align}\label{MainLemmaBPD}
+%\|\mathbf{A}_j - \mathbf{BPD}_j\|_2 \leq C_2 \varepsilon, \ \  \text{for } j \in [m],
+%\end{align}
+%\end{lemma}
 
@@
 
-Since there are more than $(k-1){\bar m \choose k}$ vectors $\mathbf{x}_i$ supported on $S$, by the pigeonhole principle there must be some $\bar S \in {[\bar m] \choose k}$ and set of $k$ indices $K$ such that the supports of all $\mathbf{x}_i$ and $\mathbf{\bar x}_i$ with $i \in K$ are contained in $S$ and $\bar S$, respectively.
+Since there are more than $(k-1){\bar m \choose k}$ vectors $\mathbf{x}_i$ supported on $S$, by the pigeonhole principle there must be some $\bar S \in {[\bar m] \choose k}$ and set of $k$ indices $K \subseteq I(S)$ such that the supports of all $\mathbf{\bar x}_i$ with $i \in K$ are subsets of $\bar S$.
 
-It follows from the general linear position of the $\mathbf{x}_i$ and the linear independence of every $2k$ columns of $\mathbf{A}$ that $L_k(\mathbf{AX}_{K}) > 0$; that is, the columns of the $n \times k$ matrix $\mathbf{AX}_K$ form a basis for $\text{\rm Span}\{\mathbf{A}_{S}\}$.
-Fixing $\mathbf{0} \neq \mathbf{y} \in \text{\rm Span}\{\mathbf{A}_{S}\}$, there exists $\mathbf{0} \neq \mathbf{c} = (c_1, \ldots, c_k) \in \mathbb{R}^k$ such that $\mathbf{y} = \mathbf{AX}_K\mathbf{c}$.
+It follows from the general linear position of the $\mathbf{x}_i$ and the linear independence of the columns of $\mathbf{A}_S$ that $L(\mathbf{AX}_{K}) > 0$; that is, the columns of the $n \times k$ matrix $\mathbf{AX}_K$ form a basis for $\text{\rm Span}\{\mathbf{A}_{S}\}$.
+Fixing $\mathbf{0} \neq \mathbf{y} \in \text{\rm Span}\{\mathbf{A}_{S}\}$, there then exists $\mathbf{0} \neq \mathbf{c} = (c_1, \ldots, c_k) \in \mathbb{R}^k$ such that $\mathbf{y} = \mathbf{AX}_K\mathbf{c}$.
 Setting \mbox{$\mathbf{\bar{y}} = \mathbf{B\bar{X}}_K\mathbf{c} \in \text{\rm Span}\{\mathbf{B}_{\bar S}\}$}, we have:
@@
 &\leq \varepsilon \sqrt{k}  \|\mathbf{c}\|_2 
-\leq \frac{\varepsilon}{L_k(\mathbf{AX}_K)} \|\mathbf{y}\|_2,
+\leq \frac{\varepsilon}{L(\mathbf{AX}_K)} \|\mathbf{y}\|_2,
 \end{align*}
-where the last inequality follows directly from the definition of $L_k$. Finally, from Def.~\ref{dDef} we have:
+where the last inequality follows directly from the definition of $L$. From Def.~\ref{dDef} we have:
 \begin{align}\label{rhs222}
 d(\text{\rm Span}\{\mathbf{A}_S\}, \text{\rm Span}\{\mathbf{B}_{\bar S}\}) 
-\leq \frac{\varepsilon}{  L_k(\mathbf{AX}_{K}) },
+\leq \frac{\varepsilon}{  L(\mathbf{AX}_{K}) } \leq \varepsilon \frac{C_1}{C_2},
 \end{align}
 %
-from which the result follows by \eqref{Cdef1} and Lem.~\ref{MainLemma}.
+where the second inequality follows from $L(\mathbf{AX}_{K}) \geq L_k(\mathbf{AX}_{I(S)})$ and \eqref{Cdef1}. Since $\varepsilon < L_2(\mathbf{A})/C_1$, the result follows by Lem.~\ref{MainLemma}, .
 \end{proof}
@@
 \section{Discussion}\label{Discussion}
-
-In this note, we generalized the approach of \cite{Hillar15} to prove the stability of unique solutions to Probs.~\ref{InverseProblem} and \ref{OptimizationProblem} while significantly reducing the known sample complexity.
+[ TODO ]
+%[mention dictionary size independence]
+%In this note, we generalized the approach of \cite{Hillar15} to prove the stability of unique solutions to Probs.~\ref{InverseProblem} and \ref{OptimizationProblem} while significantly reducing the known sample complexity.
 Our results justify the application of the sparse linear coding model to blind source separation problems, wherein the goal is to infer the generating dictionary and sparse codes from noisy measurements, \eqref{LinearModel}.
@@
 
-What we have shown here is that the sparse linear coding model generally produces a \textit{well-posed} inverse problem to be approximately solved by a numerical algorithm.
+%What we have shown here is that the sparse linear coding model generally produces a \textit{well-posed} inverse problem to be approximately solved by a numerical algorithm.
 This early concept of Hadamard \cite{Hadamard1902} can be paraphrased as the idea that inferences from observations should be robust to the inevitable uncertainty in measurement.
@@
 It would therefore be of practical utility to determine the best possible dependence of $\varepsilon$ on $\delta_1, \delta_2$ in Def.\ref{maindef} as well as the minimal requirements on the number and diversity of generating codes, and we hope that other researchers continue to improve and extend our results.
-We remark that our constants have been derived for deterministic ``worst-case'' noise, whereas the ``effective'' noise might be smaller when sampled from a distribution; in such cases, the constants
-will improve as well.
+We remark that our constants have been derived for deterministic ``worst-case'' noise, whereas the ``effective'' noise might be smaller when sampled from a distribution; in such cases, the constants will improve as well.
 
-One notable component of our contribution is a combinatorial criteria (regular hypergraphs satisfying the singleton intersection property, Def.~\ref{sip}) for the support sets of sparse codes key to the identification of the dictionary.
+%One notable component of our contribution is a combinatorial criteria (regular hypergraphs satisfying the singleton intersection property, Def.~\ref{sip}) for the support sets of sparse codes key to the identification of the dictionary.
 Fully understanding those combinatorial designs allowing for stable sparse representations is an interesting research area for the future.
@@
 
-A technical difficulty in proving Thm.~\ref{DeterministicUniquenessTheorem} was the absence of a spark condition assumption on solutions to Prob.~\ref{InverseProblem}.
+%A technical difficulty in proving Thm.~\ref{DeterministicUniquenessTheorem} was the absence of a spark condition assumption on solutions to Prob.~\ref{InverseProblem}.
 Although mathematically interesting that no such requirement is necessary, there are other reasons to seek out such a theoretical guarantee.
@@
 
-In fact, uniqueness guarantees with minimal assumptions apply to all areas of data science and engineering that utilize learned sparse representations.
+%In fact, uniqueness guarantees with minimal assumptions apply to all areas of data science and engineering that utilize learned sparse representations.
 For example, several groups have applied compressive sensing to signal processing tasks: MRI analysis \cite{lustig2008compressed}, image compression \cite{Duarte08}, and, more recently, the design of an ultrafast camera \cite{Gao14}.
@@
 
-In the field of theoretical neuroscience in particular, dictionary learning for sparse coding and related methods have recovered characteristic components of natural images \cite{Olshausen96, hurri1996image, bell1997independent, van1998independent} and sounds \cite{bellsejnowski1996, smithlewicki2006, Carlson12} that reproduce response properties of cortical neurons.
+%In the field of theoretical neuroscience in particular, dictionary learning for sparse coding and related methods have recovered characteristic components of natural images \cite{Olshausen96, hurri1996image, bell1997independent, van1998independent} and sounds \cite{bellsejnowski1996, smithlewicki2006, Carlson12} that reproduce response properties of cortical neurons.
 Our results suggest that this correspondence could be due to the ``universality'' of sparse representations in natural data, an early mathematical idea in neural theory \cite{pitts1947}.
@@
 
-\pnasbreak
+\pagebreak
 
-\section{Proof of Main Lemma}
+\section{Appendix}\label{proofs}
 
-In this supplemental, we prove Lem.~\ref{MainLemma} after stating auxiliary lemmas.
+We prove Lem.~\ref{MainLemma} after stating auxiliary lemmas and then sketch the proofs of Thm.~\ref{robustPolythm} and Cor.~\ref{ProbabilisticCor}.
+
+%\begin{lemma}\label{SpanIntersectionLemma}
+%Let $\mathbf{M} \in \mathbb{R}^{n \times m}$. If every $2k$ columns of $\mathbf{M}$ are linearly independent, then for any $F \subseteq {[m] \choose k}$:
+%\begin{align*}
+%\text{\rm Span}\{\mathbf{M}_{\cap F}\}  = \bigcap_{S \in F} \text{\rm Span}\{\mathbf{M}_S\}.
+%\end{align*}
+%\end{lemma}
+%\begin{proof}
+%Using induction on $|F|$, it is enough to prove the lemma when $|F| = 2$; but this case follows directly from the assumption.
+%\end{proof}
 
 \begin{lemma}\label{SpanIntersectionLemma}
-Let $\mathbf{M} \in \mathbb{R}^{n \times m}$. If every $2k$ columns of $\mathbf{M}$ are linearly independent, then for any $F \subseteq {[m] \choose k}$:
+If $f: U \to V$ is an injective function then:
 \begin{align*}
-\text{\rm Span}\{\mathbf{M}_{\cap F}\}  = \bigcap_{S \in F} \text{\rm Span}\{\mathbf{M}_S\}.
+f\left(\cap_{i=1}^\ell U_i \right) =  \cap_{i=1}^\ell f\left(U_i\right) \ \ \text{for any } U_1, \ldots, U_\ell \subseteq U.
 \end{align*}
+%In particular, if for some $E \in 2^{[m]}$ the map $M \in \mathbb{R}^{n \times m}$ is injective on $\cup_{S \in E} \text{Span}\{e_i\}_{i \in S}$ then $\text{Span}\{ M_{\cap_{S \in E} S} \} = \cap_{S \in E} \text{Span}\{M_S\}$.
 \end{lemma}
 \begin{proof}
-Using induction on $|F|$, it is enough to prove the lemma when $|F| = 2$; but this case follows directly from the assumption.
+By induction it is enough to prove the case $|n| = 2$, but this case follows directly from the assumtion.
+%Clearly, for any map $f$, if $w \in f(U \cap V)$ then $w \in f(U)$ and $w \in f(V)$, hence $w \in f(U) \cap f(V)$.
+If $w \in f(U) \cap f(V)$ then $w \in f(U)$ and $w \in f(V)$, hence $w = f(u) = f(v)$ for some $u \in U$ and $v \in V$, implying $u = v$ by injectivity of $f$.
+Hence $u \in U \cap V$, and $w \in f(U \cap V)$.
 \end{proof}
@@
 \begin{lemma}\label{NonEmptyLemma}
-Fix $\ell, m$, and $\bar m$ such that $p = \bar m - \ell(\bar m - m)$ is positive.
-Suppose $E \subseteq 2^{[m]}$ is $\ell$-regular with the SIP.
-If a map $\pi: E \to 2^{[\bar m]}$ has $|S| = |\pi(S)|$ and:
+Fix a hypergraph $E \subseteq 2^{[m]}$ with nodes labeled in order of non-increasing degree and for which $|\cap H(i)| = 1$ for all $i \leq q$.
+Fix $\bar m$ and let $p \leq q$ be the largest number satisfying:
+\begin{align}\label{pcond}
+\sum_{i=\ell}^{m} \deg(i) > (\bar m + 1 - \ell) (\deg(\ell) - 1) \ \ \text{for all } \ell \leq p.
+\end{align}
+
+If the map $\pi: E \to 2^{[\bar m]}$ has $\sum_{S \in E} (|\pi(S)| -|S|) \geq 0$ and:
 \begin{align}\label{cond}
-|\cap \pi(F)| \leq |\cap F |,\ \ \   \text{for } F \subseteq E,
+|\cap \pi(F)| \leq |\cap F | \text{ for all } F \subseteq E,
 \end{align}
-then $\bar m \geq m$ and the association $i \mapsto \cap \pi(F(i))$ defines an injective map from $J$ to $[\bar m]$ for some $J \in {[m] \choose p}$.
-In particular, if $\bar m = m$ then $\pi$ is induced by a permutation on $[m]$.
+then $\bar m \geq\sum_i \deg(i) / \deg(1)$, and if $\bar m < \sum_i \deg(i) / (\deg(1) - 1)$ then the association $i \mapsto \cap \pi(F(i))$ defines an injective map to $[\bar m]$ from some $J \subseteq [m]$ of size $p \geq 1$ consisting of the union of the set of all nodes of degree exceeding $\deg(p)$ and some set of nodes all having degree equal to $\deg(p)$.
+In particular, if $E$ is $d$-regular then $p = \bar m - d(\bar m - m)$.
 \end{lemma}
@@
 \begin{proof}
-First, note that assumption \eqref{cond} already constrains $\pi$ to be injective:  if $S_1 \neq S_2$, then $|\pi(S_1) \cap \pi(S_2)| \leq |S_1 \cap S_2| < \max\{|S_1|, |S_2|\} = \max\{|\pi(S_1)|, |\pi(S_2)|\}$, which implies that $\pi(S_1) \neq \pi(S_2)$.
-Next, consider the collection of pairs: \[T_1 := \{(i, S): i \in \pi(S), S \in E\},\] which number $|T_1| = \sum_{S \in E} |\pi(S)| = \sum_{S \in E} |S| = \ell m$ by regularity of $E$.
-We apply the pigeonhole principle to make two observations.
-The first is that $\bar m \geq m$.
-Otherwise, pigeonholing $\ell m > \ell \bar m$ elements of $T_1$ with respect to the set $[\bar m]$ of possible first indices would require at least $\ell + 1$ elements of $T_1$ to have the same first index.
-But by \eqref{cond} and injectivity of $\pi$, we then have more than $\ell$ edges in $E$ with a common element, contradicting regularity.
+Consider the collection of pairs: $T_1 := \{(i, S): i \in \pi(S), S \in E\}$, which number $|T_1| = \sum_{S \in E} |\pi(S)| \geq \sum_{S \in E} |S| = \sum_{i \in [m]} \deg(i)$.
+Note that assumption \eqref{cond} implies $\bar m \geq |T_1| / \deg(1)$, since otherwise pigeonholing the elements of $T_1$ with respect to their set of possible first indices $[\bar m]$ would lead us to conclude that there are more than $\deg(1)$ sets in $E$ sharing a common element.
+%QUESTION: Do we really need to say this..?
 
-The second observation is that since $\ell m = \bar m (\ell - 1) + p$ and $p > 0$, there must be at least $\ell$ elements of $T_1$ sharing the same first coordinate.
-Let $F_1$ be the preimage of this family under $\pi$.
-By the assumption \eqref{cond}, the intersection of $F_1$ is nonempty, and in fact must contain exactly $\ell$ elements by regularity.
-From the SIP, the intersection of sets in $F_1$ is $\{i_1\}$, which by \eqref{cond} implies that the intersection of $\pi(S)$ with $S \in F_1$ also contains exactly one element.
-If $p = 1$ then we are done.
-Otherwise, define $T_2 := T_1 \setminus \{(i,S) \in T_1: i = i_1\}$, which contains $(\bar m - 1)(\ell -1) + (p-1)$ elements having $\bar m - 1$ possible first indices, and produce by the same argument a (necessarily) different index $i_2$.
-Iterating this loop $p$ times yields the desired $J = \{i_1, \ldots, i_p\} \subseteq [m]$.
+By \eqref{pcond} and the upper bound on $\bar m$ we have $|T_1| >  \bar m (\deg(1) - 1)$, which implies, again by the pigeonhole principle, that there must be at least $\deg(1)$ elements of $T_1$ sharing the same first index.
+By \eqref{cond}, the intersection of the set $F_1$ consisting of their second indices is non-empty.
+As $p \leq q$ and $\deg(1) \geq \deg(i)$ for all $i$, it must be that $\cap F_1| = 1$.
+Since $\cap \pi(F_1)$ is non-empty, applying \eqref{cond} again implies $\cap \pi(F_1) = \{i_1\}$ for some $i_1 \in [m]$.
+If $p=1$ then we are done.
+Otherwise, define $T_2 := T_1 \setminus \{(i,S) \in T_1: i = i_1\}$, which contains $|T_2| = |T_1| - \deg(1) = \sum_{i=2}^m \deg(i)$ ordered pairs having $\bar m - 1$ distinct first indices.
+By \eqref{pcond} we have $|T_2| > (\bar m - 1)(\deg(2) - 1)$ and reiterating the above arguments produces a (necessarily) distinct index $i_2$.
+Iterating the arguments $p$ times yields the set of singletons \mbox{$J = \{\cap F_1, \ldots, \cap F_p\} \subseteq [m]$}.
+
+%When $E$ is $r$-regular, equation \eqref{pcond} becomes $(m+1-\ell)r > (\bar m +1 - \ell)(r-1)$ which simplifies to $\ell \leq \bar m - (\bar m - m)r$; hence $p = \bar m - (\bar m - m)r$, which is positive by our upper bound on $\bar m$.
 \end{proof}
@@
 \end{align}
-Since the right-hand side of \eqref{GapUpperBound} is less than one (by \eqref{delrho} and $r \leq 1$), it follows from \eqref{dimLem} that $|\pi(S)| \geq \dim(\text{\rm Span}\{\mathbf{B}_{\pi(S)}\}) \geq \dim(\text{\rm Span}\{\mathbf{A}_{S}\}) = |S|$, with the equality due to $\mathbf{A}$ satisfying \eqref{SparkCondition}.
-Since $|S| = |\pi(S)|$, we have $\dim(\text{\rm Span}\{\mathbf{B}_{\pi(S)}\}) = \dim(\text{\rm Span}\{\mathbf{A}_{S}\})$, and \eqref{eq2} follows using \eqref{eqdim}.
+Since the right-hand side of \eqref{GapUpperBound} is less than one (by \eqref{delrho} and $r \leq 1$), it follows from \eqref{dimLem} that $|\pi(S)| \geq \dim(\text{\rm Span}\{\mathbf{B}_{\pi(S)}\}) \geq \dim(\text{\rm Span}\{\mathbf{A}_{S}\}) = |S|$, with the equality by injectivity of $\mathbf{A}$.
+Since $|S| = |\pi(S)|$, we in fact have $\dim(\text{\rm Span}\{\mathbf{B}_{\pi(S)}\}) = \dim(\text{\rm Span}\{\mathbf{A}_{S}\})$, and \eqref{eq2} follows using \eqref{eqdim}.
 Note that the columns of $\mathbf{B}_{\pi(S)}$ are therefore linearly independent, for all $S \in E$.
 
-We next verify that \eqref{cond} holds.
+We next show that \eqref{cond} holds.
 Fix $F \subseteq E$.
-Since $\text{\rm Span}\{\mathbf{B}_{\cap_{S \in F}\pi(S)}\} \subseteq \cap_{S \in F} \text{\rm Span}\{\mathbf{B}_{\pi(S)}\}$, if $\cap_{S \in F} \text{\rm Span}\{\mathbf{B}_{\pi(S)}\} = \{\textbf{0}\}$, then we must have $|\cap_{S \in F} \pi(S)| = 0$ (as the columns of $\mathbf{B}_{\pi(S)}$ are linearly independent) and \eqref{cond} is trivially true.
+Since $\text{\rm Span}\{\mathbf{B}_{\cap \pi(F)}\} \subseteq \cap_{S \in F} \text{\rm Span}\{\mathbf{B}_{\pi(S)}\}$, if $\cap_{S \in F} \text{\rm Span}\{\mathbf{B}_{\pi(S)}\} = \{\textbf{0}\}$, then we must have $|\cap_{S \in F} \pi(S)| = 0$ (as the columns of $\mathbf{B}_{\pi(S)}$ are linearly independent) and \eqref{cond} is trivially true.
 Suppose then that the intersection is not the zero vector.
-By Lem.~\ref{SpanIntersectionLemma} and Lem.~\ref{DistanceToIntersectionLemma}, and incorporating \eqref{eq2} and \eqref{GapUpperBound}, we have:
+By Lem.~\ref{SpanIntersectionLemma} and Lem.~\ref{DistanceToIntersectionLemma}, and then incorporating \eqref{eq2} and \eqref{GapUpperBound}, we have:
 \begin{align}\label{randoml}
-d( \text{\rm Span}&\{\mathbf{B}_{\cap_{S \in F}\pi(S)}\}, \text{\rm Span}\{\mathbf{A}_{\cap_{S \in F} S}\}  ) \nonumber \\
+d( \text{\rm Span}&\{\mathbf{B}_{\cap \pi(F)}\}, \text{\rm Span}\{\mathbf{A}_{\cap F}\}  ) \nonumber \\
 &\leq d\left( \cap_{S \in F} \text{\rm Span}\{\mathbf{B}_{\pi(S)}\}, \cap_{S \in F} \text{\rm Span}\{\mathbf{A}_{S}\} \right) \nonumber \\
-&\leq \sum_{T \in F} \frac{ d\left( \cap_{S \in F} \text{\rm Span}\{\mathbf{B}_{\pi(S)}\},\text{\rm Span}\{\mathbf{A}_{T}\} \right) }{ r( \{ \text{\rm Span}\{\mathbf{A}_{S}\}_{S \in F}) } \nonumber \\
-&\leq \sum_{T \in F} \frac{ d\left( \text{\rm Span}\{\mathbf{B}_{\pi(T)}\},\text{\rm Span}\{\mathbf{A}_{T}\} \right) }{ r( \{ \text{\rm Span}\{\mathbf{A}_{S}\}_{S \in F}) }\nonumber \\
-&\leq \frac{|F| \varepsilon}{r( \{ \text{\rm Span}\{\mathbf{A}_{S}\} \}_{S \in F})} 
+&\leq \sum_{T \in F} \frac{ d\left( \cap_{S \in F} \text{\rm Span}\{\mathbf{B}_{\pi(S)}\},\text{\rm Span}\{\mathbf{A}_{T}\} \right) }{ r(  \text{\rm Span}\{\mathbf{A}_{S}\}_{S \in F}) } \nonumber \\
+&\leq \sum_{T \in F} \frac{ d\left( \text{\rm Span}\{\mathbf{B}_{\pi(T)}\},\text{\rm Span}\{\mathbf{A}_{T}\} \right) }{ r( \text{\rm Span}\{\mathbf{A}_{S}\}_{S \in F}) }\nonumber \\
+&\leq \frac{|F| \varepsilon}{r( \text{\rm Span}\{\mathbf{A}_{S}\}_{S \in F})} 
 \leq \frac{C_2 \varepsilon}{\max_i\|\mathbf{A}_i\|_2}. 
 \end{align}
+%
+where the third inequality follows from the definition of $d$ as a supremum.
 Since $\varepsilon < L_2(\mathbf{A}) / C_2$, by \eqref{delrho} the right-hand side in \eqref{randoml} is strictly less than one.
-Hence, $\dim(\text{\rm Span}\{\mathbf{B}_{\cap_{S \in F}\pi(S)}\}) \leq \dim(\text{\rm Span}\{\mathbf{A}_{\cap_{S \in F} S}\})$ by \eqref{dimLem}, and \eqref{cond} follows from the linear independence of the columns of $\mathbf{A}_{S}$ and $\mathbf{B}_{\pi(S)}$ for all $S \in F$.
+Hence, $\dim(\text{\rm Span}\{\mathbf{B}_{\cap \pi(F)}\}) \leq \dim(\text{\rm Span}\{\mathbf{A}_{\cap F}\})$ by \eqref{dimLem}, and \eqref{cond} follows from the linear independence of the columns of $\mathbf{A}_{S}$ and $\mathbf{B}_{\pi(S)}$ for all $S \in F$.
 
-Now, by Lem.~\ref{NonEmptyLemma}, the association $i \mapsto \cap \pi(F(i))$ defines an injective map $\bar \pi: J \to [\bar m]$ for some $J \subseteq [m]$ of size $\bar m - \ell(\bar m - m)$, and we can be sure that $\mathbf{B}_{\bar \pi(i)} \neq \mathbf{0}$ for all $i \in J$ since the columns of $\mathbf{B}_{\pi(S)}$ are linearly independent for all $S \in E$.
+Now, by Lem.~\ref{NonEmptyLemma}, the association $i \mapsto \cap \pi(F(i))$ defines an injective map $\bar \pi: J \to [\bar m]$ for some $J \in {[m] \choose p}$ with $p$ given by \eqref{pcond}, and we can be sure that $\mathbf{B}_{\bar \pi(i)} \neq \mathbf{0}$ for all $i \in J$ since the columns of $\mathbf{B}_{\pi(S)}$ are linearly independent for all $S \in E$.
 It then follows from \eqref{eqdim} and \eqref{randoml} that $d\left( \text{\rm Span}\{\mathbf{A}_i\}, \text{\rm Span}\{ \mathbf{B}_{\bar \pi(i)} \} \right) \leq C_2 \varepsilon / \max_i \|\mathbf{A}_i\|_2$ for all $i \in J$.
@@
 
-\section{Proofs of Thm.~\ref{robustPolythm} and Cor.~\ref{ProbabilisticCor}}
+%\section{Proofs of Thm.~\ref{robustPolythm} and Cor.~\ref{ProbabilisticCor}}
 
@@
 
-\pnasbreak
+%\pnasbreak
 

### 2017-07-10 manuscripts/PNAS/chazthm_pnas.tex
newness

@@
 Before stating our main results, we first identify combinatorial criteria on the support sets of generating codes that imply stable sparse representations.
-Letting $\{1, \ldots, m\}$ be denoted $[m]$, its power set $2^{[m]}$, and ${[m] \choose k}$ the set of subsets of $[m]$ of size $k$,
-we say a hypergraph $E \subseteq 2^{[m]}$ on vertices $[m]$ is \textit{$k$-uniform} when in fact $E \subseteq {[m] \choose k}$.
-We also say $E$ is \emph{regular} when every element of $[m]$ is contained in exactly $\ell$ elements of $E$ for some $\ell > 0$ (for given $\ell$, we say $E$ is \textit{$\ell$-regular}).
+Letting $\{1, \ldots, m\}$ be denoted $[m]$, its power set $2^{[m]}$, and ${[m] \choose k}$ the set of subsets of $[m]$ of size $k$, we say a hypergraph $E \subseteq 2^{[m]}$ on vertices $[m]$ is \textit{$k$-uniform} when in fact $E \subseteq {[m] \choose k}$.
+The \emph{degree} $\deg(i)$ of a node $i \in [m]$ is the number of elements in $E$ which contain $i$, and we say $E$ is \emph{regular} when for some $r$ we have $\deg(i) = r$ for all $i$ (for given $r$, we say $E$ is \textit{$r$-regular}).
 
@@
 %
-and we write $L_{2k}:= L_E$ when $E = {[m] \choose k}$. Note that $ L = L_{\{[m]\}}$ whereas $L_{[m]} = L_2$. [TODO: note that $L_2$ implied by $L_E$]
+and we write $L_{2k}:= L_E$ when $E = {[m] \choose k}$. Note that $ L = L_{\{[m]\}}$ whereas $L_{[m]} = L_2$. [TODO: Note when $L_2 > 0$ is implied by $L_E > 0$.]
 
@@
 \begin{theorem}\label{DeterministicUniquenessTheorem}
-Fix a matrix $\mathbf{A} \in \mathbb{R}^{n \times m}$ with $L_E(\mathbf{A}) > 0$ for some regular $E \subseteq {[m] \choose k}$ with the SIP.
-If the sequence \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} contains, for each $S \in E$, more than $(k-1){m \choose k}$ vectors in general linear position supported on $S$, then there is a constant\footnote{We delay defining the constant $C_1$ until Section \ref{DUT} (\eqref{Cdef1}).} $C_1 > 0$ for which the following holds for all $\varepsilon < L_{2}(\mathbf{A}) / C_1$:
+Fix a real $n \times m$ matrix $\mathbf{A}$ with $L_E(\mathbf{A}) > 0$ for some $r$-regular $E \subseteq {[m] \choose k}$ with the SIP.
+If the sequence \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} contains, for each $S \in E$, more than $(k-1){m \choose k}$ $k$-sparse vectors in general linear position supported on $S$, then there is a constant\footnote{We delay defining the constant $C_1$ until Section \ref{DUT} (\eqref{Cdef1}).} $C_1 > 0$ for which the following holds for all $\varepsilon < L_{2}(\mathbf{A}) / C_1$:
 
-Every real $n \times \bar m$ matrix $\mathbf{B}$ for which there exist $k$-sparse $\mathbf{\bar x}_1, \ldots, \mathbf{\bar x}_N$ satisfying \mbox{$\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\bar x}_i\|_2 \leq \varepsilon$} for all $i$ has $\bar m \geq m$ and, provided $\bar m < mr/(r-1)$, an associated permutation $\mathbf{P}$ and invertible diagonal $\mathbf{D}$ such that:
+Every real $n \times \bar m$ matrix $\mathbf{B}$ for which there exist $k$-sparse $\mathbf{\bar x}_1, \ldots, \mathbf{\bar x}_N$ satisfying \mbox{$\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\bar x}_i\|_2 \leq \varepsilon$} for all $i$ has $\bar m \geq m$ and, provided $\bar m < mr/(r-1)$,
 \begin{align}\label{Cstable}
@@
 %
-for some non-empty $J, \bar J \subseteq [m]$ of size $\bar m - r(\bar m - m)$.
+for some non-empty $J, \bar J$ of size $\bar m - r(\bar m - m)$, permutation $\mathbf{P}$ and invertible diagonal $\mathbf{D}$.
 
@@
 When $\bar m = m$, we recover Thm.~\ref{DeterministicUniquenessTheorem}.
-Regarding the assumptions of Thm.~\ref{DeterministicUniquenessTheorem}, it is easy to verify that for every $k < m$, there is a regular $k$-uniform hypergraph that satisfies the SIP; for instance, consecutive intervals of length $k$ in some cyclic order on $[m]$.
+Regarding the assumptions of Thm.~\ref{DeterministicUniquenessTheorem}, it is easy to verify that for every $k < m$, there is a regular $k$-uniform hypergraph that satisfies the SIP; for instance, take the consecutive intervals of length $k$ in some cyclic order on $[m]$.
 In fact, even if $E$ is not regular or only partially satisfies the SIP, a relation between $\bar m$ and the degree sequence of nodes in $E$ may give the indices $J \subseteq [m]$.
@@
 
-As mentioned in the previous section, Thm.~\ref{DeterministicUniquenessTheorem} is a particular case of a more general result that forgoes the assumptions of regularity and SIP on the hypergraph $E \subseteq {[m] \choose k}$.
+As mentioned in the previous section, Thm.~\ref{DeterministicUniquenessTheorem} is a particular case of a more general result that forgoes the assumption that $E \subseteq {[m] \choose k}$ is regular and satisfies the SIP.
 If instead we require only that the stars $\cap H(i)$ intersect at singletons for all $i \leq q$ (assuming that the nodes of $E$ are labeled in some order of non-increasing degree), we have that $\bar m \geq k|E| / \deg(1)$ and, provided $\bar m < k|E| / (\deg(1) - 1)$, the non-empty submatrix $J$ is of size equal to the largest number $p$ satisfying:
@@
 
-We now begin our proof of Thm.~\ref{DeterministicUniquenessTheorem} by showing how dictionary recovery \eqref{Cstable} already implies sparse code recovery \eqref{b-PDa} when $L_{2k}(\mathbf{A}) > 0$ and \mbox{$\varepsilon < L_{2k}(\mathbf{A}) / C_1$}, assuming without loss of generality that $\bar m = m$.
-First, note that $\|\mathbf{x}\|_1 \leq \sqrt{k} \|\mathbf{x}\|_2$ for $k$-sparse $\mathbf{x} \in \mathbb{R}^m$, which by definition of $L_E$ implies the following frequently applied inequality valid for any $E \subseteq 2^{[m]}$:
+We now begin our proof of Thm.~\ref{DeterministicUniquenessTheorem} by showing how dictionary recovery \eqref{Cstable} already implies sparse code recovery \eqref{b-PDa} when $L_{2k}(\mathbf{A}) > 0$ and \mbox{$\varepsilon < L_{2k}(\mathbf{A}) / C_1$}, temporarily assuming (without loss of generality) that $\bar m = m$.
+First, note that $\|\mathbf{x}\|_1 \leq \sqrt{k} \|\mathbf{x}\|_2$ for $k$-sparse $\mathbf{x} \in \mathbb{R}^m$, which by definition of $L_{2k}$ implies the following frequently applied inequality:
 \begin{align}\label{delrho}
-L_{E}(\mathbf{A}) \leq \frac{\|\mathbf{A}\mathbf{x}\|_2}{\sqrt{2k} \|\mathbf{x}\|_2} 
-\leq  \max_{j \in [m]}\|\mathbf{A}_j\|_2,
+L_{2k}(\mathbf{A}) \leq \frac{\|\mathbf{A}\mathbf{x}\|_2}{\sqrt{2k} \|\mathbf{x}\|_2} 
+\leq  \max_{j \in [m]}\|\mathbf{A}_j\|_2.
 \end{align}
@@
 \begin{align}\label{MainLemmaBPD}
-\|(\mathbf{A}_J)_j - \mathbf{BPD}_j\|_2 \leq C_2 \varepsilon, \ \  \text{for } j \in J,
+\|(\mathbf{A}_J)_j - \mathbf{B}_{\bar J} \mathbf{PD}_j\|_2 \leq C_2 \varepsilon, \ \  \text{for } j \in J,
 \end{align}
-for some non-empty $J$ of size $\bar m - r(\bar m - m)$.
+for some non-empty $J, \bar J$ of size $\bar m - r(\bar m - m)$.
 \end{lemma}
@@
 %[mention dictionary size independence]
-%In this note, we generalized the approach of \cite{Hillar15} to prove the stability of unique solutions to Probs.~\ref{InverseProblem} and \ref{OptimizationProblem} while significantly reducing the known sample complexity.
+In this note, we generalized the approach of \cite{Hillar15} to prove the stability of unique solutions to Probs.~\ref{InverseProblem} and \ref{OptimizationProblem} while significantly reducing the known sample complexity.
 Our results justify the application of the sparse linear coding model to blind source separation problems, wherein the goal is to infer the generating dictionary and sparse codes from noisy measurements, \eqref{LinearModel}.
@@
 
-%What we have shown here is that the sparse linear coding model generally produces a \textit{well-posed} inverse problem to be approximately solved by a numerical algorithm.
+What we have shown here is that the sparse linear coding model generally produces a \textit{well-posed} inverse problem to be approximately solved by a numerical algorithm.
 This early concept of Hadamard \cite{Hadamard1902} can be paraphrased as the idea that inferences from observations should be robust to the inevitable uncertainty in measurement.
@@
 
-%One notable component of our contribution is a combinatorial criteria (regular hypergraphs satisfying the singleton intersection property, Def.~\ref{sip}) for the support sets of sparse codes key to the identification of the dictionary.
+One notable component of our contribution is a combinatorial criteria (regular hypergraphs satisfying the singleton intersection property, Def.~\ref{sip}) for the support sets of sparse codes key to the identification of the dictionary.
 Fully understanding those combinatorial designs allowing for stable sparse representations is an interesting research area for the future.
@@
 
-%A technical difficulty in proving Thm.~\ref{DeterministicUniquenessTheorem} was the absence of a spark condition assumption on solutions to Prob.~\ref{InverseProblem}.
+A technical difficulty in proving Thm.~\ref{DeterministicUniquenessTheorem} was the absence of a spark condition assumption on solutions to Prob.~\ref{InverseProblem}.
 Although mathematically interesting that no such requirement is necessary, there are other reasons to seek out such a theoretical guarantee.
@@
 
-%In fact, uniqueness guarantees with minimal assumptions apply to all areas of data science and engineering that utilize learned sparse representations.
+In fact, uniqueness guarantees with minimal assumptions apply to all areas of data science and engineering that utilize learned sparse representations.
 For example, several groups have applied compressive sensing to signal processing tasks: MRI analysis \cite{lustig2008compressed}, image compression \cite{Duarte08}, and, more recently, the design of an ultrafast camera \cite{Gao14}.
@@
 
-%In the field of theoretical neuroscience in particular, dictionary learning for sparse coding and related methods have recovered characteristic components of natural images \cite{Olshausen96, hurri1996image, bell1997independent, van1998independent} and sounds \cite{bellsejnowski1996, smithlewicki2006, Carlson12} that reproduce response properties of cortical neurons.
+In the field of theoretical neuroscience in particular, dictionary learning for sparse coding and related methods have recovered characteristic components of natural images \cite{Olshausen96, hurri1996image, bell1997independent, van1998independent} and sounds \cite{bellsejnowski1996, smithlewicki2006, Carlson12} that reproduce response properties of cortical neurons.
 Our results suggest that this correspondence could be due to the ``universality'' of sparse representations in natural data, an early mathematical idea in neural theory \cite{pitts1947}.
@@
 \end{align}
-then $\bar m \geq\sum_i \deg(i) / \deg(1)$, and if $\bar m < \sum_i \deg(i) / (\deg(1) - 1)$ then the association $i \mapsto \cap \pi(F(i))$ defines an injective map to $[\bar m]$ from some $J \subseteq [m]$ of size $p \geq 1$ consisting of the union of the set of all nodes of degree exceeding $\deg(p)$ and some set of nodes all having degree equal to $\deg(p)$.
-In particular, if $E$ is $d$-regular then $p = \bar m - d(\bar m - m)$.
+then $\bar m \geq\sum_i \deg(i) / \deg(1)$, and if $\bar m < \sum_i \deg(i) / (\deg(1) - 1)$ then the association $i \mapsto \cap \pi(F(i))$ defines an injective map to $[\bar m]$ from some non-empty $J \subseteq [m]$ of size $p$ consisting of the union of the set of all nodes of degree exceeding $\deg(p)$ and some set of nodes all having degree equal to $\deg(p)$.
+In particular, if $E$ is $r$-regular then $|J| = \bar m - r(\bar m - m)$.
 \end{lemma}

### 2017-07-13 manuscripts/PNAS/chazthm_pnas.tex
newness
mathcal{H}

@@
 % Use the lineno option to display guide line numbers if required.
-% Note that the use of elements such as single-column equations
-% may affect the guide line number alignment.
+% Note that the use of elements such as single-column equations may affect the guide line number alignment.
 
-%%% CHAZ TODO %%%
-
-%%% CHRIS TODO %%
-% steamroll
+%%% TODO %%%
+% Describe the connection between dictionary learning and union of subspace learning.
+Dictionaries are the top elements of the subspace intersection semi-lattice over reverse-inclusion.
+We identify subspaces generated by the elements of $A$ by showing that every $B$ must include these subspaces in its intersection semi-lattice.
+The dictionary elements are then inside these subspaces, so the lower the dimensionality of these subspaces the better.
+% Shoutout to research on subspace arrangements? Not just "union of subspaces" model?
+% Write Main Lemma or Lil lemma as a map between two intersection semi-lattices with a constraint (on the dimension of subspace? or on size of edge?)?
+% Give example of when we might expect k-uniformity, i.e. x_i in glp on k-dimensional subspaces. Orbit under group action of a k-dimensional subspace?
 
@@
 \usepackage{array}
+\usepackage{bm}
 %\usepackage{cite}
@@
 Here, we prove very generally that uniqueness and stability in sparse linear coding is an expected property of the model. 
-More specifically, dictionaries that preserve sparse codes (i.e., satisfy a `spark condition') are identifiable from as few as \mbox{$N = m(k-1){m \choose k} + m$} noisy sparse linear combinations of their columns up to an error linear in the noise (Thm.~\ref{DeterministicUniquenessTheorem}).
+More specifically, dictionaries that preserve sparse codes (e.g., satisfy a `spark condition') are identifiable from as few as \mbox{$N = m(k-1){m \choose k} + m$} noisy sparse linear combinations of their columns up to an error linear in the noise (Thm.~\ref{DeterministicUniquenessTheorem}).
 In fact, provided $n \geq \min(2k,m)$, in almost all cases the dictionary learning problem is well-posed (as per Hadamard \cite{Hadamard1902}) given enough data (Cor.~\ref{ProbabilisticCor}).
@@
 
-Before stating our main results, we first identify combinatorial criteria on the support sets of generating codes that imply stable sparse representations.
-Letting $\{1, \ldots, m\}$ be denoted $[m]$, its power set $2^{[m]}$, and ${[m] \choose k}$ the set of subsets of $[m]$ of size $k$, we say a hypergraph $E \subseteq 2^{[m]}$ on vertices $[m]$ is \textit{$k$-uniform} when in fact $E \subseteq {[m] \choose k}$.
-The \emph{degree} $\deg(i)$ of a node $i \in [m]$ is the number of elements in $E$ which contain $i$, and we say $E$ is \emph{regular} when for some $r$ we have $\deg(i) = r$ for all $i$ (for given $r$, we say $E$ is \textit{$r$-regular}).
+Before stating our main result, we identify combinatorial criteria on the support sets of the generating codes $\mathbf{x}_i$ that imply stable sparse representations.
+Letting $\{1, \ldots, m\}$ be denoted $[m]$, its power set $2^{[m]}$, and ${[m] \choose k}$ the set of subsets of $[m]$ of size $k$, we say a hypergraph $\mathcal{H} \subseteq 2^{[m]}$ on vertices $[m]$ is \textit{$k$-uniform} when in fact $\mathcal{H} \subseteq {[m] \choose k}$.
+The \emph{degree} $\deg(i)$ of a node $i \in [m]$ is the number of sets in $\mathcal{H}$ that contain $i$, and we say $\mathcal{H}$ is \emph{regular} when for some $r$ we have $\deg(i) = r$ for all $i$ (for given $r$, we say $\mathcal{H}$ is \textit{$r$-regular}).
 
 \begin{definition}\label{sip}
-Given $E \subseteq 2^{[m]}$, the \textbf{star} $H(i)$ at $i$ is the set of $S \in E$ with $i \in S$.
-We say $E$ has the \textbf{singleton intersection property} (\textbf{SIP}) when $\cap H(i) = \{i\}$ for all $i \in [m]$.
-%We say $E$ has the SIP \textbf{of order $p$} when $\cap F(i) = \{i\}$ for every node $i$ for which $\text{deg(i)} \geq d_p$, where $d_1 \geq \ldots \geq d_m$ is the degree sequence of $E$.
+Given $\mathcal{H} \subseteq 2^{[m]}$, the \textbf{star} $\mathcal{G}(i)$ at $i$ is the set of $S \in \mathcal{H}$ with $i \in S$.
+We say $\mathcal{H}$ has the \textbf{singleton intersection property} (\textbf{SIP}) when $\cap \mathcal{G}(i) = \{i\}$ for all $i \in [m]$.
 \end{definition}
 
-Next, we describe a quantitative version of the spark condition.  
+Next, we describe a quantitative version of the spark condition \eqref{SparkCondition}.
 The \emph{lower bound} $L$ of a matrix $\mathbf{M} \in \mathbb R^{n \times m}$ is the largest number $\alpha$ such that \mbox{$\|\mathbf{M}\mathbf{x}\|_2 \geq \alpha\|\mathbf{x}\|_2$} for all $\mathbf{x} \in \mathbb{R}^m$ \cite{Grcar10}.
 By compactness of the unit sphere, every injective linear map has a nonzero lower bound; hence, if $\mathbf{M}$ satisfies \eqref{SparkCondition}, then each submatrix formed from $2k$ of its columns or less has a nonzero lower bound.
-This motivates the following definition:
+
+We generalize this domain-restricted lower bound to a \emph{union of subspaces} model \cite{lu2008theory, vidal2005generalized} derived from the hypergraph $\mathcal{H}$.
+Let $\mathbf{M}_J$ be the submatrix formed by the columns of $\mathbf{M}$ indexed by $J$ and let $\bm{\mathcal{M}}_J := \text{span}\{\mathbf{M}_J\}$, with $\bm{\mathcal{M}}_\emptyset := \mathbf{0}$.
+We define:
+\begin{align*}
+L_\mathcal{H}(\mathbf{M}) := \inf \left\{ \frac{ \|\mathbf{M}(\mathbf{x}_1-\mathbf{x}_2)\|_2 }{ \sqrt{2k} \|\mathbf{x}_1-\mathbf{x}_2\|_2} : \mathbf{x}_1, \mathbf{x}_2 \in \cup_{S \in \mathcal{H}} \bm{\mathcal{M}}_S \right\},
+%\frac{1}{\sqrt{k}}\max \{ \alpha : \|\mathbf{M}\mathbf{x}\|_2 \geq \alpha\|\mathbf{x}\|_2 \text{ for all $k$-sparse } \mathbf{x}\}.
+\end{align*} 
+%
+%This motivates the following definition: 
 %\begin{align*}
@@
 %\end{align*}
-\begin{align*}
-L_E(\mathbf{M}) := \inf \left\{ \frac{ \|\mathbf{M}_{S \cup S'}\mathbf{x}\|_2 }{ \sqrt{2k} \|\mathbf{x}\|_2} : \mathbf{x} \in \mathbb{R}^{|S\cup S'|}, \ \ S,S' \in E \right\}
+%\begin{align*}
+%L_\mathcal{H}(\mathbf{M}) := \inf \left\{ \frac{ \|\mathbf{M}_{S \cup S'}\mathbf{x}\|_2 }{ \sqrt{2k} \|\mathbf{x}\|_2} : \mathbf{x} \in \mathbb{R}^{|S\cup S'|}, \ \ S,S' \in \mathcal{H} \right\}
 %\frac{1}{\sqrt{k}}\max \{ \alpha : \|\mathbf{M}\mathbf{x}\|_2 \geq \alpha\|\mathbf{x}\|_2 \text{ for all $k$-sparse } \mathbf{x}\}.
-\end{align*} 
+%\end{align*} 
 %
-and we write $L_{2k}:= L_E$ when $E = {[m] \choose k}$. Note that $ L = L_{\{[m]\}}$ whereas $L_{[m]} = L_2$. [TODO: Note when $L_2 > 0$ is implied by $L_E > 0$.]
+where we write $L_{2k}:= L_\mathcal{H}$ when $\mathcal{H} = {[m] \choose k}$.
+Beware that $ L = L_{\{[m]\}}$ whereas $L_{[m]} = L_2$.
+[TODO: Note when $L_2 > 0$ is implied by $L_\mathcal{H} > 0$.] We note that the quantity $1 - \sqrt{k} L_k(\mathbf{M})$ is also known in the compressive sensing literature as the (asymmetric) lower restricted isometry constant \cite{Blanchard2011}.
+Clearly, for any $\mathbf{M}$ satisfying \eqref{SparkCondition}, we have $L_{k'}(\mathbf{M}) > 0$ for  $k' \leq 2k$.
 
-Clearly, for any $\mathbf{M}$ satisfying \eqref{SparkCondition}, we have $L_{k'}(\mathbf{M}) > 0$ for  $k' \leq 2k$.
-We note that the quantity $1 - \sqrt{k} L_k(\mathbf{M})$ is also known in the compressive sensing literature as the (asymmetric) lower restricted isometry constant \cite{Blanchard2011}.
-
-A vector $\mathbf{x}$ is said to be \emph{supported} on $S \subseteq [m]$ when $\mathbf{x} \in \text{\rm Span}( \{\mathbf{e}_j\}_{j\in S})$, where $\mathbf{e}_j$ are the standard basis in $\mathbb R^m$.
-For any index set $J$, denote by by $\mathbf{x}^J$ the subvector formed from the entries of $\mathbf{x}$ indexed by $J$, and similarly by $\mathbf{M}_J$ the submatrix formed by the columns of $\mathbf{M}$ indexed by $J$, where we set $\text{\rm Span}\{\mathbf{M}_\emptyset\} := \{\textbf{0}\}$.
+A vector $\mathbf{x}$ is said to be \emph{supported} on $S \subseteq [m]$ when $\mathbf{x} \in \text{\rm span}\{\mathbf{e}_j: j\in S\}$, where $\mathbf{e}_j$ are the standard basis in $\mathbb R^m$.
+Denote by $\mathbf{x}^J$ the subvector formed from the entries of $\mathbf{x}$ indexed by $J$.
 A set of $k$-sparse vectors is said to be in \emph{general linear position} when any $k$ of them are linearly independent.
@@
 \begin{theorem}\label{DeterministicUniquenessTheorem}
-Fix a real $n \times m$ matrix $\mathbf{A}$ with $L_E(\mathbf{A}) > 0$ for some $r$-regular $E \subseteq {[m] \choose k}$ with the SIP.
-If the sequence \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} contains, for each $S \in E$, more than $(k-1){m \choose k}$ $k$-sparse vectors in general linear position supported on $S$, then there is a constant\footnote{We delay defining the constant $C_1$ until Section \ref{DUT} (\eqref{Cdef1}).} $C_1 > 0$ for which the following holds for all $\varepsilon < L_{2}(\mathbf{A}) / C_1$:
+Fix a real $n \times m$ matrix $\mathbf{A}$ with $L_\mathcal{H}(\mathbf{A}) > 0$ for some $r$-regular $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP.
+If the sequence \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} contains, for each $S \in \mathcal{H}$, more than $(k-1){m \choose k}$ $k$-sparse vectors in general linear position supported on $S$, then there is a constant\footnote{We delay defining the constant $C_1$ until Section \ref{DUT} (\eqref{Cdef1}).} $C_1 > 0$ for which the following holds for all $\varepsilon < L_{2}(\mathbf{A}) / C_1$:
 
@@
 \begin{align}\label{b-PDa}
-\|\mathbf{x}^J_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\bar x}^{\bar J}_i\|_1 &\leq  \left( \frac{ 1+C_1 \|\mathbf{x}^{J}_i\|_1 }{ L_{2k}(\mathbf{A}) -  C_1\varepsilon } \right) \varepsilon,\ \ \   \text{for $i \in [N]$}.
+\|\mathbf{x}^J_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\bar x}^{\bar J}_i\|_1 &\leq  \left( \frac{ 1+C_1 \|\mathbf{x}^{J}_i\|_1 }{ L_{2k}(\mathbf{A}) -  C_1\varepsilon } \right) \varepsilon \ \  \text{for $i \in [N]$}.
 \end{align}
@@
 %In fact, a more general result (stated clearly in the next section) can be gleaned from our method of proving Thm.~\ref{DeterministicUniquenessTheorem}.
-Briefly, in cases where $\mathbf{B}$ has $\bar m \neq m$ columns, or $E$ is not regular or only partially satisfying the SIP, a relation between $\bar m$ and the degree sequence of nodes in $E$ gives indices $J \subseteq [m]$ defining a submatrix $\mathbf{A}_J$ and subvectors $\mathbf{x}_i^J$ that are recoverable in the sense of \eqref{Cstable} and \eqref{b-PDa}.
-For example, if $E$ is $\ell$-regular with the SIP but $m \leq \bar m < m\ell/(\ell - 1)$ then we have nonzero $|J| = \bar m - \ell(\bar m - m)$.
+Briefly, in cases where $\mathbf{B}$ has $\bar m \neq m$ columns, or $\mathcal{H}$ is not regular or only partially satisfying the SIP, a relation between $\bar m$ and the degree sequence of nodes in $\mathcal{H}$ gives indices $J \subseteq [m]$ defining a submatrix $\mathbf{A}_J$ and subvectors $\mathbf{x}_i^J$ that are recoverable in the sense of \eqref{Cstable} and \eqref{b-PDa}.
+For example, if $\mathcal{H}$ is $\ell$-regular with the SIP but $m \leq \bar m < m\ell/(\ell - 1)$ then we have nonzero $|J| = \bar m - \ell(\bar m - m)$.
 The implication here is that the smaller the difference $\bar m - m$, the more columns and code entries of the original $n \times m$ dictionary $\mathbf{A}$ and codes $\mathbf{x}_i$ contained (up to noise) in the appropriately scaled $n \times \bar m$ dictionary $\mathbf{B}$ and codes $\mathbf{\bar x}_i$.
@@
 Regarding the assumptions of Thm.~\ref{DeterministicUniquenessTheorem}, it is easy to verify that for every $k < m$, there is a regular $k$-uniform hypergraph that satisfies the SIP; for instance, take the consecutive intervals of length $k$ in some cyclic order on $[m]$.
-In fact, even if $E$ is not regular or only partially satisfies the SIP, a relation between $\bar m$ and the degree sequence of nodes in $E$ may give the indices $J \subseteq [m]$.
+In fact, even if $\mathcal{H}$ is not regular or only partially satisfies the SIP, a relation between $\bar m$ and the degree sequence of nodes in $\mathcal{H}$ may give the indices $J \subseteq [m]$.
 For sake of brevity, we delay to the next section a clear statement of this more general result.
@@
 \begin{corollary}\label{DeterministicUniquenessCorollary}
-Given $n, m$, $k < m$, and a regular hypergraph $E \subseteq {[m] \choose k}$ with the SIP, there are $N =  |E| \left[ (k-1){m \choose k} + 1  \right]$ vectors \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} such that every matrix $\mathbf{A} \in \mathbb{R}^{n \times m}$ satisfying \eqref{SparkCondition} generates a dataset $Y = \{\mathbf{A}\mathbf{x}_1, \ldots, \mathbf{A}\mathbf{x}_N\}$ with a stable $k$-sparse representation in $\mathbb{R}^m$.
+Given $n, m$, $k < m$, and a regular hypergraph $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP, there are $N =  |\mathcal{H}| \left[ (k-1){m \choose k} + 1  \right]$ vectors \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} such that every matrix $\mathbf{A} \in \mathbb{R}^{n \times m}$ satisfying \eqref{SparkCondition} generates a dataset $Y = \{\mathbf{A}\mathbf{x}_1, \ldots, \mathbf{A}\mathbf{x}_N\}$ with a stable $k$-sparse representation in $\mathbb{R}^m$.
 \end{corollary}
 
-As already mentioned, there exist $k$-uniform regular hypergraphs $E$ with the SIP having cardinality $|E| = m$, implying the lower bound for sample size $N$ from the introduction.
-In many cases, however, the SIP can be achieved with far fewer supports; for example, when $k = \sqrt{m}$, take $E$ to be the $2k$ rows and columns formed by arranging $[m]$ in a square grid.
+As already mentioned, there exist $k$-uniform regular hypergraphs $\mathcal{H}$ with the SIP having cardinality $|\mathcal{H}| = m$, implying the lower bound for sample size $N$ from the introduction.
+In many cases, however, the SIP can be achieved with far fewer supports; for example, when $k = \sqrt{m}$, take $\mathcal{H}$ to be the $2k$ rows and columns formed by arranging $[m]$ in a square grid.
 
@@
 \begin{corollary}\label{SLCopt}
-If all of the assumptions of Thm.\ref{DeterministicUniquenessTheorem} hold with more than $(k-1)\left[ {\bar m \choose k} + |E|k{\bar m \choose k-1}\right]$ vectors $\mathbf{x}_i$ supported on each $S \in E$, then all solutions to Prob.~\ref{OptimizationProblem} necessarily satisfy the implications \eqref{Cstable} and \eqref{b-PDa} of Thm.~\ref{DeterministicUniquenessTheorem}.
+If all of the assumptions of Thm.\ref{DeterministicUniquenessTheorem} hold with more than $(k-1)\left[ {\bar m \choose k} + |\mathcal{H}|k{\bar m \choose k-1}\right]$ vectors $\mathbf{x}_i$ supported on each $S \in \mathcal{H}$, then all solutions to Prob.~\ref{OptimizationProblem} necessarily satisfy the implications \eqref{Cstable} and \eqref{b-PDa} of Thm.~\ref{DeterministicUniquenessTheorem}.
 \end{corollary}
@@
 \begin{theorem}\label{robustPolythm}
-There is a polynomial $g$ in the entries of $\mathbf{A}$ and $\mathbf{x}_i$ with the following property:  if $g$ evaluates to a nonzero number and more than \mbox{$(k-1){m \choose k}$} of the resulting $\mathbf{x}_i$ are supported on each $S \in E$ for some regular $E \subseteq {[m] \choose k}$ with the SIP, then $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$ (Def.~\ref{maindef}).
+There is a polynomial $g$ in the entries of $\mathbf{A}$ and $\mathbf{x}_i$ with the following property:  if $g$ evaluates to a nonzero number and more than \mbox{$(k-1){m \choose k}$} of the resulting $\mathbf{x}_i$ are supported on each $S \in \mathcal{H}$ for some regular $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP, then $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$ (Def.~\ref{maindef}).
 In particular, all -- except for a Borel set of measure zero -- substitutions impart to $Y$ this property.
@@
 Fix $k < m$ and $n \geq \min(2k, m)$ and let the entries of $\mathbf{A} \in \mathbb{R}^{n \times m}$ and $k$-sparse $\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$ be drawn independently from probability measures absolutely continuous with respect to the standard Borel measure $\mu$.
-If more than $(k-1){m \choose k}$ of the vectors $\mathbf{x}_i$ are supported on each $S \in E$ for a regular $E \subseteq {[m] \choose k}$ with the SIP, then $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$ with probability one.
+If more than $(k-1){m \choose k}$ of the vectors $\mathbf{x}_i$ are supported on each $S \in \mathcal{H}$ for a regular $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP, then $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$ with probability one.
 \end{corollary}
@@
 
-As mentioned in the previous section, Thm.~\ref{DeterministicUniquenessTheorem} is a particular case of a more general result that forgoes the assumption that $E \subseteq {[m] \choose k}$ is regular and satisfies the SIP.
-If instead we require only that the stars $\cap H(i)$ intersect at singletons for all $i \leq q$ (assuming that the nodes of $E$ are labeled in some order of non-increasing degree), we have that $\bar m \geq k|E| / \deg(1)$ and, provided $\bar m < k|E| / (\deg(1) - 1)$, the non-empty submatrix $J$ is of size equal to the largest number $p$ satisfying:
+As mentioned in the previous section, Thm.~\ref{DeterministicUniquenessTheorem} is a particular case of a more general result that forgoes the assumption that $\mathcal{H} \subseteq {[m] \choose k}$ is regular and satisfies the SIP.
+If instead we require only that the stars $\cap H(i)$ intersect at singletons for all $i \leq q$ (assuming that the nodes of $\mathcal{H}$ are labeled in some order of non-increasing degree), we have that $\bar m \geq k|\mathcal{H}| / \deg(1)$ and, provided $\bar m < k|\mathcal{H}| / (\deg(1) - 1)$, the non-empty submatrix $J$ is of size equal to the largest number $p$ satisfying:
 \begin{align}\label{pcond}
@@
 For the benefit of the reader, we do not prove this more general result below; it can be gleaned by examining how exactly Lemma \ref{NonEmptyLemma} is incorporated into the proof of Lem.~\ref{MainLemma}.
-%As mentioned in the previous section, Thm.~\ref{DeterministicUniquenessTheorem} is a particular case of a more general result, which requires a looser set of constraints on the hypergraph $E$ and which applies to $n \times \bar m$ matrices $\mathbf{B}$ (and $\bar m$-dimensional codes $\mathbf{\bar x}_i$) with $\bar m \neq m$:
+%As mentioned in the previous section, Thm.~\ref{DeterministicUniquenessTheorem} is a particular case of a more general result, which requires a looser set of constraints on the hypergraph $\mathcal{H}$ and which applies to $n \times \bar m$ matrices $\mathbf{B}$ (and $\bar m$-dimensional codes $\mathbf{\bar x}_i$) with $\bar m \neq m$:
 
-%Fix $\bar m$ and suppose the assumptions of Thm.~\ref{DeterministicUniquenessTheorem} hold, only now with the constraints on $E \subseteq {[m] \choose k}$ being just that $|\cap H(i)| = 1$ for all $i \leq q$ (assuming w.l.o.g.
-that the nodes of $E$ are labeled in some order of non-increasing degree), and with more than $(k-1){\bar m \choose k}$ vectors $\mathbf{x}_i$ supported in g.l.p.
-on each $S \in E$.
-Then we must have $\bar m \geq k|E| / \deg(1)$ and, provided $\bar m < k|E| / (\deg(1) - 1)$, the guarantee \eqref{Cstable} holds for a submatrix $\mathbf{A}_J$, where $J \subseteq[m]$ is nonempty and of a size equal to the largest number $p$ satisfying:
+%Fix $\bar m$ and suppose the assumptions of Thm.~\ref{DeterministicUniquenessTheorem} hold, only now with the constraints on $\mathcal{H} \subseteq {[m] \choose k}$ being just that $|\cap H(i)| = 1$ for all $i \leq q$ (assuming w.l.o.g.
+that the nodes of $\mathcal{H}$ are labeled in some order of non-increasing degree), and with more than $(k-1){\bar m \choose k}$ vectors $\mathbf{x}_i$ supported in g.l.p.
+on each $S \in \mathcal{H}$.
+Then we must have $\bar m \geq k|\mathcal{H}| / \deg(1)$ and, provided $\bar m < k|\mathcal{H}| / (\deg(1) - 1)$, the guarantee \eqref{Cstable} holds for a submatrix $\mathbf{A}_J$, where $J \subseteq[m]$ is nonempty and of a size equal to the largest number $p$ satisfying:
 %\begin{align}\label{pcond}
@@
 
-The heart of the matter is therefore \eqref{Cstable}, which we now finally establish, first in the important special case $k = 1$.
+The heart of the matter is therefore \eqref{Cstable}, which we now finally establish, first in the important special case $k = 1$
 
@@
 \begin{lemma}\label{MainLemma}
-Suppose $\mathbf{A} \in \mathbb{R}^{n \times m}$ has $L_E(\mathbf{A}) > 0$ for some $r$-regular $E \subseteq {[m] \choose k}$ with the SIP.
+Suppose $\mathbf{A} \in \mathbb{R}^{n \times m}$ has $L_\mathcal{H}(\mathbf{A}) > 0$ for some $r$-regular $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP.
 There exists $C_2 > 0$ for which the following holds for all $\varepsilon < L_2(\mathbf{A}) / C_2$:
@@
 \begin{align}\label{GapUpperBound}
-d(\text{\rm Span}\{\mathbf{A}_{S}\}, \text{\rm Span}\{\mathbf{B}_{\pi(S)}\}) \leq \varepsilon, \ \  \text{for $S \in E$},
+d(\bm{\mathcal{A}}_S, \bm{\mathcal{B}}_{\pi(S)}) \leq \varepsilon, \ \  \text{for $S \in \mathcal{H}$},
 \end{align}
@@
 %\begin{lemma}\label{MainLemma}
-%Fix $\mathbf{A} \in \mathbb{R}^{n \times m}$ with $L_E(\mathbf{A}) > 0$ for some regular $E \subseteq {[m] \choose k}$ with the SIP.
+%Fix $\mathbf{A} \in \mathbb{R}^{n \times m}$ with $L_\mathcal{H}(\mathbf{A}) > 0$ for some regular $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP.
 There exists a constant $C_2 > 0$ for which the following holds for all $\varepsilon < L_2(\mathbf{A}) / C_2$:
@@
 %\begin{align}\label{GapUpperBound}
-%d(\text{\rm Span}\{\mathbf{A}_{S}\}, \text{\rm Span}\{\mathbf{B}_{\pi(S)}\}) \leq \varepsilon, \ \ \text{for $S \in E$},
+%d(\text{\rm span}\{\mathbf{A}_{S}\}, \bm{\mathcal{B}}_{\pi(S)}) \leq \varepsilon, \ \ \text{for $S \in \mathcal{H}$},
 %\end{align}
@@
 
-The constant $C_1 > 0$ in Thm.~\ref{DeterministicUniquenessTheorem} is then defined by\footnote{Note that $\|\mathbf{AX}_{I(S)}\mathbf{c}\|_2 \geq \sqrt{k} L_k(\mathbf{A})\|\mathbf{X}_{I(S)}\mathbf{c}\|_2 \geq k L_k(\mathbf{A}) L_k(\mathbf{X}_{I(S)})\|\mathbf{c}\|_2$ for $S \in E$ and $k$-sparse $\mathbf{c}$.
+The constant $C_1 > 0$ in Thm.~\ref{DeterministicUniquenessTheorem} is then defined by\footnote{Note that $\|\mathbf{AX}_{I(S)}\mathbf{c}\|_2 \geq \sqrt{k} L_k(\mathbf{A})\|\mathbf{X}_{I(S)}\mathbf{c}\|_2 \geq k L_k(\mathbf{A}) L_k(\mathbf{X}_{I(S)})\|\mathbf{c}\|_2$ for $S \in \mathcal{H}$ and $k$-sparse $\mathbf{c}$.
 Therefore, $\sqrt{k} L_k(\mathbf{AX}_{I(S)}) \geq k L_k(\mathbf{A}) L_k(\mathbf{X}_{I(S)}) > 0$ since $L_k(\mathbf{A}), L_k(\mathbf{X}_{I(S)}) > 0$ by \eqref{SparkCondition} and general linear position of the $\mathbf{x}_i$.
@@
 \begin{align}\label{Cdef1}
-C_1(\mathbf{A}, \{\mathbf{x}_i\}_{i=1}^N, E) := \frac{ C_2(\mathbf{A}, E) } { \min_{S \in E} L_k(\mathbf{AX}_{I(S)}) }.
+C_1(\mathbf{A}, \{\mathbf{x}_i\}_{i=1}^N, \mathcal{H}) := \frac{ C_2(\mathbf{A}, \mathcal{H}) } { \min_{S \in \mathcal{H}} L_k(\mathbf{AX}_{I(S)}) }.
 \end{align}
@@
 
-The constant $C_2 = C_2(\mathbf{A}, E)$ is given in turn below, in terms of one used in \cite{Deutsch12} to analyze the convergence of the alternating projections algorithm for projecting a point onto an intersection of subspaces.
+The constant $C_2 = C_2(\mathbf{A}, \mathcal{H})$ is given in turn below, in terms of one used in \cite{Deutsch12} to analyze the convergence of the alternating projections algorithm for projecting a point onto an intersection of subspaces.
 We use it to bound the distance between a point and the intersection of subspaces given an upper bound on its distance from each individual subspace.
@@
 \begin{definition}\label{SpecialSupportSet}\label{FriedrichsDefinition}
-For subspaces $V_1, \ldots, V_\ell \subseteq \mathbb{R}^m$, set $r := 1$ when $\ell = 1$ and define for $\ell \geq 2$:
+For a subspace arrangement $V_1, \ldots, V_\ell \subseteq \mathbb{R}^m$, set $r := 1$ when $\ell = 1$ and define for $\ell \geq 2$:
 \begin{align*}
@@
 \begin{align}\label{Cdef2}
-C_2(\mathbf{A}, E) := \frac{ 2^{|E|} \max_{j \in [m]} \|\mathbf{A}_j\|_2}{ \min_{F \subseteq E} r( \{ \text{\rm Span}\{\mathbf{A}_{S}\} \}_{S \in F}) },
+C_2(\mathbf{A}, \mathcal{H}) := \frac{ 2^{|\mathcal{H}|} \max_{j \in [m]} \|\mathbf{A}_j\|_2}{ \min_{F \subseteq \mathcal{H}} r( \{ \bm{\mathcal{A}}_S \}_{S \in F}) },
 \end{align}
@@
 \begin{proof}[Proof of Thm.~\ref{DeterministicUniquenessCorollary} for $k < m$] 
-We shall show that for every $S \in E$ there is some $\bar S \in {[\bar m] \choose k}$ for which the distance $d(\text{\rm Span}\{\mathbf{A}_S\}, \text{\rm Span}\{\mathbf{B}_{\bar S}\})$ is controlled by $\varepsilon$.
+We demonstrate the existence of a map $\pi: \mathcal{H} \to 2^{[\bar m]}$ for which the distance $d(\bm{\mathcal{A}}_S, \bm{\mathcal{B}}_{\pi(S)})$ is controlled by $\varepsilon$.
+Applying Lem.~\ref{MainLemma} then completes the proof.
+
+%We shall show that for every $S \in \mathcal{H}$ there is some $\bar S \in {[\bar m] \choose k}$ for which the distance $d(\bm{\mathcal{A}}_S, \bm{\mathcal{B}}_{\bar S})$ is controlled by $\varepsilon$.
 Applying Lem.~\ref{MainLemma} with the map $\pi$ defined by $S \mapsto \bar S$ then completes the proof.
@@
 
-It follows from the general linear position of the $\mathbf{x}_i$ and the linear independence of the columns of $\mathbf{A}_S$ that $L(\mathbf{AX}_{K}) > 0$; that is, the columns of the $n \times k$ matrix $\mathbf{AX}_K$ form a basis for $\text{\rm Span}\{\mathbf{A}_{S}\}$.
-Fixing $\mathbf{0} \neq \mathbf{y} \in \text{\rm Span}\{\mathbf{A}_{S}\}$, there then exists $\mathbf{0} \neq \mathbf{c} = (c_1, \ldots, c_k) \in \mathbb{R}^k$ such that $\mathbf{y} = \mathbf{AX}_K\mathbf{c}$.
-Setting \mbox{$\mathbf{\bar{y}} = \mathbf{B\bar{X}}_K\mathbf{c} \in \text{\rm Span}\{\mathbf{B}_{\bar S}\}$}, we have:
+It follows from $L_\mathcal{H}(\mathbf{A}) > 0$ and the general linear position of the $\mathbf{x}_i$ that $L(\mathbf{AX}_{K}) > 0$; that is, the columns of the $n \times k$ matrix $\mathbf{AX}_K$ form a basis for $\bm{\mathcal{A}}_S$.
+Fixing $\mathbf{0} \neq \mathbf{y} \in \bm{\mathcal{A}}_S$, there then exists $\mathbf{0} \neq \mathbf{c} = (c_1, \ldots, c_k) \in \mathbb{R}^k$ such that $\mathbf{y} = \mathbf{AX}_K\mathbf{c}$.
+Setting \mbox{$\mathbf{\bar{y}} = \mathbf{B\bar{X}}_K\mathbf{c} \in \bm{\mathcal{B}}_{\bar S}$}, we have:
 \begin{align*}
@@
 \begin{align}\label{rhs222}
-d(\text{\rm Span}\{\mathbf{A}_S\}, \text{\rm Span}\{\mathbf{B}_{\bar S}\}) 
+d(\bm{\mathcal{A}}_S, \bm{\mathcal{B}}_{\bar S}) 
 \leq \frac{\varepsilon}{  L(\mathbf{AX}_{K}) } \leq \varepsilon \frac{C_1}{C_2},
@@
 
-We now show that no more than $(k-1)|E|$ of the $\mathbf{\bar x}_i$ share a support of size less than $k$. 
-From previous arguments, for every $S \in E$, the columns of each $n \times k$ submatrix of $\mathbf{AX}_{I(S)}$ form a basis for $\text{\rm Span}\{\mathbf{A}_S\}$.
-Suppose that more than $(k-1)|E|$ vectors $\mathbf{\bar x}_i$ share a support $\bar S$ of size $|\bar{S}| < k$.
-By the pigeonhole principle, there is some $S \in E$ supporting $k$ or more of the corresponding $\mathbf{x}_i$; let them be indexed by $K \subseteq I(S)$.
+We now show that no more than $(k-1)|\mathcal{H}|$ of the $\mathbf{\bar x}_i$ share a support of size less than $k$. 
+From previous arguments, for every $S \in \mathcal{H}$, the columns of each $n \times k$ submatrix of $\mathbf{AX}_{I(S)}$ form a basis for $\bm{\mathcal{A}}_S$.
+Suppose that more than $(k-1)|\mathcal{H}|$ vectors $\mathbf{\bar x}_i$ share a support $\bar S$ of size $|\bar{S}| < k$.
+By the pigeonhole principle, there is some $S \in \mathcal{H}$ supporting $k$ or more of the corresponding $\mathbf{x}_i$; let them be indexed by $K \subseteq I(S)$.
 By the same argument as in the proof of Thm.\ref{DeterministicUniquenessTheorem}, we also have \eqref{rhs222}.
-Our bound on $\varepsilon$ implies the right-hand side of \eqref{rhs222} is less than one; hence, by \eqref{dimLem} we have the contradiction:
-\[k = \dim(\text{Span}(\mathbf{A}_S)) \leq \dim(\text{Span}\{\mathbf{B}_{\bar S}\}) \leq |\bar S|.\]
+Our bound on $\varepsilon$ implies the right-hand side of \eqref{rhs222} is less than one; hence, by \eqref{dimLem} we have the contradiction $k = \dim(\bm{\mathcal{A}}_S) \leq \dim(\bm{\mathcal{B}}_{\bar S}) \leq |\bar S|.$
 
-The total number of $(k-1)$-sparse vectors $\mathbf{\bar x}_i$ can thus no greater than $|E|(k-1){ \bar m \choose k-1}$.
-Taking \eqref{eqn} into account, no more than $|E|k(k-1){ \bar m \choose k-1}$ vectors $\mathbf{\bar x}_i$ are \emph{not} $k$-sparse.
-Since for every $S \in E$ there are over $(k-1)\left[ {\bar m \choose k} + |E|k{ \bar m \choose k-1} \right]$ vectors $\mathbf{x}_i$ supported there, it follows that more than $(k-1){\bar m \choose k}$ of them must have corresponding $\mathbf{\bar x}_i$ that are also $k$-sparse.
+The total number of $(k-1)$-sparse vectors $\mathbf{\bar x}_i$ can thus no greater than $|\mathcal{H}|(k-1){ \bar m \choose k-1}$.
+Taking \eqref{eqn} into account, no more than $|\mathcal{H}|k(k-1){ \bar m \choose k-1}$ vectors $\mathbf{\bar x}_i$ are \emph{not} $k$-sparse.
+Since for every $S \in \mathcal{H}$ there are over $(k-1)\left[ {\bar m \choose k} + |\mathcal{H}|k{ \bar m \choose k-1} \right]$ vectors $\mathbf{x}_i$ supported there, it follows that more than $(k-1){\bar m \choose k}$ of them must have corresponding $\mathbf{\bar x}_i$ that are also $k$-sparse.
 The result now follows directly from Thm.~\ref{DeterministicUniquenessCorollary}.
@@
 \section{Discussion}\label{Discussion}
-[ TODO ]
 %[mention dictionary size independence]
@@
 
-\pagebreak
+%\pagebreak
 
@@
 
-%\begin{lemma}\label{SpanIntersectionLemma}
+%\begin{lemma}\label{spanIntersectionLemma}
 %Let $\mathbf{M} \in \mathbb{R}^{n \times m}$. If every $2k$ columns of $\mathbf{M}$ are linearly independent, then for any $F \subseteq {[m] \choose k}$:
 %\begin{align*}
-%\text{\rm Span}\{\mathbf{M}_{\cap F}\}  = \bigcap_{S \in F} \text{\rm Span}\{\mathbf{M}_S\}.
+%\text{\rm span}\{\mathbf{M}_{\cap F}\}  = \bigcap_{S \in F} \text{\rm span}\{\mathbf{M}_S\}.
 %\end{align*}
@@
 
-\begin{lemma}\label{SpanIntersectionLemma}
+\begin{lemma}\label{spanIntersectionLemma}
 If $f: U \to V$ is an injective function then:
@@
 \end{align*}
-%In particular, if for some $E \in 2^{[m]}$ the map $M \in \mathbb{R}^{n \times m}$ is injective on $\cup_{S \in E} \text{Span}\{e_i\}_{i \in S}$ then $\text{Span}\{ M_{\cap_{S \in E} S} \} = \cap_{S \in E} \text{Span}\{M_S\}$.
+%In particular, if for some $E \in 2^{[m]}$ the map $M \in \mathbb{R}^{n \times m}$ is injective on $\cup_{S \in \mathcal{H}} \text{span}\{e_i\}_{i \in S}$ then $\text{span}\{ M_{\cap_{S \in \mathcal{H}} S} \} = \cap_{S \in \mathcal{H}} \text{span}\{M_S\}$.
 \end{lemma}
@@
 \begin{lemma}\label{NonEmptyLemma}
-Fix a hypergraph $E \subseteq 2^{[m]}$ with nodes labeled in order of non-increasing degree and for which $|\cap H(i)| = 1$ for all $i \leq q$.
+Fix a hypergraph $\mathcal{H} \subseteq 2^{[m]}$ with nodes labeled in order of non-increasing degree and for which $|\cap H(i)| = 1$ for all $i \leq q$.
 Fix $\bar m$ and let $p \leq q$ be the largest number satisfying:
@@
 
-If the map $\pi: E \to 2^{[\bar m]}$ has $\sum_{S \in E} (|\pi(S)| -|S|) \geq 0$ and:
+If the map $\pi: E \to 2^{[\bar m]}$ has $\sum_{S \in \mathcal{H}} (|\pi(S)| -|S|) \geq 0$ and:
 \begin{align}\label{cond}
-|\cap \pi(F)| \leq |\cap F | \text{ for all } F \subseteq E,
+|\cap \pi(F)| \leq |\cap F | \text{ for all } F \subseteq \mathcal{H},
 \end{align}
 then $\bar m \geq\sum_i \deg(i) / \deg(1)$, and if $\bar m < \sum_i \deg(i) / (\deg(1) - 1)$ then the association $i \mapsto \cap \pi(F(i))$ defines an injective map to $[\bar m]$ from some non-empty $J \subseteq [m]$ of size $p$ consisting of the union of the set of all nodes of degree exceeding $\deg(p)$ and some set of nodes all having degree equal to $\deg(p)$.
-In particular, if $E$ is $r$-regular then $|J| = \bar m - r(\bar m - m)$.
+In particular, if $\mathcal{H}$ is $r$-regular then $|J| = \bar m - r(\bar m - m)$.
 \end{lemma}
@@
 \begin{proof}
-Consider the collection of pairs: $T_1 := \{(i, S): i \in \pi(S), S \in E\}$, which number $|T_1| = \sum_{S \in E} |\pi(S)| \geq \sum_{S \in E} |S| = \sum_{i \in [m]} \deg(i)$.
-Note that assumption \eqref{cond} implies $\bar m \geq |T_1| / \deg(1)$, since otherwise pigeonholing the elements of $T_1$ with respect to their set of possible first indices $[\bar m]$ would lead us to conclude that there are more than $\deg(1)$ sets in $E$ sharing a common element.
+Consider the collection of pairs: $T_1 := \{(i, S): i \in \pi(S), S \in \mathcal{H}\}$, which number $|T_1| = \sum_{S \in \mathcal{H}} |\pi(S)| \geq \sum_{S \in \mathcal{H}} |S| = \sum_{i \in [m]} \deg(i)$.
+Note that assumption \eqref{cond} implies $\bar m \geq |T_1| / \deg(1)$, since otherwise pigeonholing the elements of $T_1$ with respect to their set of possible first indices $[\bar m]$ would lead us to conclude that there are more than $\deg(1)$ sets in $\mathcal{H}$ sharing a common element.
 %QUESTION: Do we really need to say this..?
@@
 By \eqref{cond}, the intersection of the set $F_1$ consisting of their second indices is non-empty.
-As $p \leq q$ and $\deg(1) \geq \deg(i)$ for all $i$, it must be that $\cap F_1| = 1$.
+As $p \leq q$ and $\deg(1) \geq \deg(i)$ for all $i$, it must be that $|\cap F_1| = 1$.
 Since $\cap \pi(F_1)$ is non-empty, applying \eqref{cond} again implies $\cap \pi(F_1) = \{i_1\}$ for some $i_1 \in [m]$.
@@
 Iterating the arguments $p$ times yields the set of singletons \mbox{$J = \{\cap F_1, \ldots, \cap F_p\} \subseteq [m]$}.
-
-%When $E$ is $r$-regular, equation \eqref{pcond} becomes $(m+1-\ell)r > (\bar m +1 - \ell)(r-1)$ which simplifies to $\ell \leq \bar m - (\bar m - m)r$; hence $p = \bar m - (\bar m - m)r$, which is positive by our upper bound on $\bar m$.
+%TODO: Let T_1 be the set of all pairs $T_1 := \{(R, S): R \subseteq \pi(S), S \in \mathcal{H}\}$ 
 \end{proof}
@@
 \begin{proof}[Proof of Lem.~\ref{MainLemma}]
-We begin by showing that: 
-\begin{align}\label{eq2}
-d(\text{\rm Span}\{\mathbf{B}_{\pi(S)}\}, \text{\rm Span}\{\mathbf{A}_S\} ) = d(\text{\rm Span}\{\mathbf{A}_S\}, \text{\rm Span}\{\mathbf{B}_{\pi(S)}\}).
-\end{align}
-Since the right-hand side of \eqref{GapUpperBound} is less than one (by \eqref{delrho} and $r \leq 1$), it follows from \eqref{dimLem} that $|\pi(S)| \geq \dim(\text{\rm Span}\{\mathbf{B}_{\pi(S)}\}) \geq \dim(\text{\rm Span}\{\mathbf{A}_{S}\}) = |S|$, with the equality by injectivity of $\mathbf{A}$.
-Since $|S| = |\pi(S)|$, we in fact have $\dim(\text{\rm Span}\{\mathbf{B}_{\pi(S)}\}) = \dim(\text{\rm Span}\{\mathbf{A}_{S}\})$, and \eqref{eq2} follows using \eqref{eqdim}.
-Note that the columns of $\mathbf{B}_{\pi(S)}$ are therefore linearly independent, for all $S \in E$.
+We will show how the bound \eqref{GapUpperBound} trickles through the intersection semi-lattices of the subspace arrangements $\{\bm{\mathcal{A}}_S\}_{S \in \mathcal{H}}$ and $\{\bm{\mathcal{B}}_{\bar S}\}_{\bar S \in \pi(\mathcal{H})}$ to yield \eqref{MainLemmaBPD} by virtue of the SIP.
+
+We begin by showing that $\dim(\bm{\mathcal{B}}_{\pi(S)}) = \dim(\bm{\mathcal{A}}_S)$ for all $S \in \mathcal{H}$. 
+Since the right-hand side of \eqref{GapUpperBound} is less than one (by \eqref{delrho} and $r \leq 1$), it follows from \eqref{dimLem} that $|\pi(S)| \geq \dim(\bm{\mathcal{B}}_{\pi(S)}) \geq \dim(\bm{\mathcal{A}}_S) = |S|$, with the equality by injectivity of $\mathbf{A}$.
+Since $|S| = |\pi(S)|$, the required fact follows.
+Note that the columns of $\mathbf{B}_{\pi(S)}$ are therefore linearly independent, for all $S \in \mathcal{H}$.
 
 We next show that \eqref{cond} holds.
-Fix $F \subseteq E$.
-Since $\text{\rm Span}\{\mathbf{B}_{\cap \pi(F)}\} \subseteq \cap_{S \in F} \text{\rm Span}\{\mathbf{B}_{\pi(S)}\}$, if $\cap_{S \in F} \text{\rm Span}\{\mathbf{B}_{\pi(S)}\} = \{\textbf{0}\}$, then we must have $|\cap_{S \in F} \pi(S)| = 0$ (as the columns of $\mathbf{B}_{\pi(S)}$ are linearly independent) and \eqref{cond} is trivially true.
+Fix $F \subseteq \mathcal{H}$.
+Since $\bm{\mathcal{B}}_{\cap \pi(F)}\} \subseteq \cap_{S \in F} \bm{\mathcal{B}}_{\pi(S)}$, if $\cap_{S \in F} \bm{\mathcal{B}}_{\pi(S)} = \{\textbf{0}\}$, then we must have $|\cap_{S \in F} \pi(S)| = 0$ (as the columns of $\mathbf{B}_{\pi(S)}$ are linearly independent) and \eqref{cond} is trivially true.
 Suppose then that the intersection is not the zero vector.
-By Lem.~\ref{SpanIntersectionLemma} and Lem.~\ref{DistanceToIntersectionLemma}, and then incorporating \eqref{eq2} and \eqref{GapUpperBound}, we have:
+By Lem.~\ref{eqdim} and Lem.~\ref{DistanceToIntersectionLemma}, and then incorporating \eqref{eq2} and \eqref{GapUpperBound}, we have:
 \begin{align}\label{randoml}
-d( \text{\rm Span}&\{\mathbf{B}_{\cap \pi(F)}\}, \text{\rm Span}\{\mathbf{A}_{\cap F}\}  ) \nonumber \\
-&\leq d\left( \cap_{S \in F} \text{\rm Span}\{\mathbf{B}_{\pi(S)}\}, \cap_{S \in F} \text{\rm Span}\{\mathbf{A}_{S}\} \right) \nonumber \\
-&\leq \sum_{T \in F} \frac{ d\left( \cap_{S \in F} \text{\rm Span}\{\mathbf{B}_{\pi(S)}\},\text{\rm Span}\{\mathbf{A}_{T}\} \right) }{ r(  \text{\rm Span}\{\mathbf{A}_{S}\}_{S \in F}) } \nonumber \\
-&\leq \sum_{T \in F} \frac{ d\left( \text{\rm Span}\{\mathbf{B}_{\pi(T)}\},\text{\rm Span}\{\mathbf{A}_{T}\} \right) }{ r( \text{\rm Span}\{\mathbf{A}_{S}\}_{S \in F}) }\nonumber \\
-&\leq \frac{|F| \varepsilon}{r( \text{\rm Span}\{\mathbf{A}_{S}\}_{S \in F})} 
+d(\bm{\mathcal{B}}_{\cap \pi(F)}&, \bm{\mathcal{A}}_{\cap F}  ) 
+\leq d\left( \cap_{S \in F} \bm{\mathcal{B}}_{\pi(S)}, \cap_{S \in F} \bm{\mathcal{A}}_S \right) \nonumber \\
+&\leq \sum_{T \in F} \frac{ d\left( \cap_{S \in F} \bm{\mathcal{B}}_{\pi(S)},\bm{\mathcal{A}_{T}} \right) }{ r(  \{\bm{\mathcal{A}}_S\}_{S \in F}) }
+\leq \sum_{T \in F} \frac{ d\left( \bm{\mathcal{B}}_{\pi(T)},\bm{\mathbf{A}}_{T} \right) }{ r( \{\bm{\mathcal{A}}_S\}_{S \in F}) }\nonumber \\
+&\leq \frac{|F| \varepsilon}{r( \{\bm{\mathcal{A}}_S\}_{S \in F})} 
 \leq \frac{C_2 \varepsilon}{\max_i\|\mathbf{A}_i\|_2}. 
@@
 Since $\varepsilon < L_2(\mathbf{A}) / C_2$, by \eqref{delrho} the right-hand side in \eqref{randoml} is strictly less than one.
-Hence, $\dim(\text{\rm Span}\{\mathbf{B}_{\cap \pi(F)}\}) \leq \dim(\text{\rm Span}\{\mathbf{A}_{\cap F}\})$ by \eqref{dimLem}, and \eqref{cond} follows from the linear independence of the columns of $\mathbf{A}_{S}$ and $\mathbf{B}_{\pi(S)}$ for all $S \in F$.
+Hence, $\dim(\text{\rm span}\{\mathbf{B}_{\cap \pi(F)}\}) \leq \dim(\text{\rm span}\{\mathbf{A}_{\cap F}\})$ by \eqref{dimLem}, and \eqref{cond} follows from the linear independence of the columns of $\mathbf{A}_{S}$ and $\mathbf{B}_{\pi(S)}$ for all $S \in F$.
 
-Now, by Lem.~\ref{NonEmptyLemma}, the association $i \mapsto \cap \pi(F(i))$ defines an injective map $\bar \pi: J \to [\bar m]$ for some $J \in {[m] \choose p}$ with $p$ given by \eqref{pcond}, and we can be sure that $\mathbf{B}_{\bar \pi(i)} \neq \mathbf{0}$ for all $i \in J$ since the columns of $\mathbf{B}_{\pi(S)}$ are linearly independent for all $S \in E$.
-It then follows from \eqref{eqdim} and \eqref{randoml} that $d\left( \text{\rm Span}\{\mathbf{A}_i\}, \text{\rm Span}\{ \mathbf{B}_{\bar \pi(i)} \} \right) \leq C_2 \varepsilon / \max_i \|\mathbf{A}_i\|_2$ for all $i \in J$.
+Now, by Lem.~\ref{NonEmptyLemma}, the association $i \mapsto \cap \pi(F(i))$ defines an injective map $\bar \pi: J \to [\bar m]$ for some $J \in {[m] \choose p}$ with $p$ given by \eqref{pcond}, and we can be sure that $\mathbf{B}_{\bar \pi(i)} \neq \mathbf{0}$ for all $i \in J$ since the columns of $\mathbf{B}_{\pi(S)}$ are linearly independent for all $S \in \mathcal{H}$.
+It then follows from \eqref{eqdim} and \eqref{randoml} that $d\left( \text{\rm span}\{\mathbf{A}_i\}, \text{\rm span}\{ \mathbf{B}_{\bar \pi(i)} \} \right) \leq C_2 \varepsilon / \max_i \|\mathbf{A}_i\|_2$ for all $i \in J$.
 Fixing $\bar \varepsilon = C_2\varepsilon$ and letting $c_i = \|\mathbf{A}_i\|_2^{-1}$, we thus have that for every basis vector $\mathbf{e}_i \in \mathbb{R}^m$ with $i \in J$ there exists some $\bar{c}_i \in \mathbb{R}$ such that $\|c_i\mathbf{A}\mathbf{e}_i - \bar{c}_i \mathbf{B}\mathbf{e}_{\bar \pi(i)}\|_2 \leq \bar \varepsilon < L_2(\mathbf{A}) \min_{i\in J} |c_i|$.

### 2017-07-13 manuscripts/PNAS/chazthm_pnas.tex
needs steamroll

@@
 
-%%% TODO %%%
+% TODO %
+% *** Put ell1 norm into the denominator of L_k *** ?
+% Give example of when we might expect k-uniformity, i.e. x_i in glp on k-dimensional subspaces. Orbit under group action of a k-dimensional subspace?
+% Proof of cor 2 can do sum starting with p=1 since they are in general linear position, hence none can be 0. but whatever.
+
+%%% Subspace Arrangement..Semi-lattices..? %%%
 % Describe the connection between dictionary learning and union of subspace learning.
@@
 % Write Main Lemma or Lil lemma as a map between two intersection semi-lattices with a constraint (on the dimension of subspace? or on size of edge?)?
-% Give example of when we might expect k-uniformity, i.e. x_i in glp on k-dimensional subspaces. Orbit under group action of a k-dimensional subspace?
+%See pg. 257 of GPCA textbook that alludes to the connection between DL and deep learning -- could se way we take a step toward identifiability theory in deep learning? lol
 
@@
 
-\significancestatement{Many naturally occurring signals (visual scenery, speech, EEG, etc.) lacking domain-specific formal models can nonetheless be usefully characterized as linear combinations of few elementary waveforms drawn from a large `dictionary'.
+\significancestatement{Many natural signals (visual scenery, speech, EEG, etc.) lacking domain-specific formal models can nonetheless be usefully characterized as linear combinations of few elementary waveforms drawn from a large `dictionary'.
 We give general conditions guaranteeing when such dictionaries are uniquely and stably determined by data.
-The result justifies the use of this model as a constraint for blind source separation, and may help explain the observed universality of emergent representations in sparse models of some natural phenomena.
+The result justifies the use of this model as a constraint for blind source separation, and helps explain the observed universality of emergent representations in sparse models of certain natural phenomena.
 }
@@
 \begin{abstract}
-Dictionary learning for sparse linear coding has exposed some characteristic properties of many natural signals.
-However, universal theorems which guarantee the consistency of estimation in this model are lacking.
+Dictionary learning for sparse linear coding has exposed characteristic properties of natural signals.
+However, a universal theorem guaranteeing the consistency of estimation in this model is lacking.
 Here, we prove that for all diverse enough datasets generated from the sparse coding model, latent dictionaries and codes are uniquely and stably determined up to measurement error.
@@
 for $k$-\emph{sparse} $\mathbf{x}_i \in \mathbb{R}^m$ having at most $k$ nonzero entries and \emph{noise} $\mathbf{n}_i \in \mathbb{R}^n$, with bounded norm $\| \mathbf{n}_i \|_2 \leq  \eta$ representing our combined worst-case uncertainty in  measuring $\mathbf{A}\mathbf{x}_i$.
-The precise mathematical problem addressed here is the following.
+The first mathematical problem addressed here is the following.
 
@@
 \begin{align}\label{def1}
-\|\mathbf{A}_j - (\mathbf{BPD})_j\|_2 \leq \delta_1 \ \ \text{and} \ \ \|\mathbf{x}_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\bar x}_i\|_1 \leq \delta_2.
+\|\mathbf{A}_j - \mathbf{BPD}_j\|_2 \leq \delta_1 \ \ \text{and} \ \ \|\mathbf{x}_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\bar x}_i\|_1 \leq \delta_2.
 \end{align}
@@
 We then prove our main theorem (Thm.~\ref{DeterministicUniquenessTheorem}) in Sec.~\ref{DUT} after stating some additional definitions and lemmas required for the proof, including a useful result in combinatorial matrix analysis (Lem.~\ref{MainLemma}).
-We also give a simple argument extending our guarantees to the following more common optimization formulation of the dictionary learning problem (Cor.~\ref{SLCopt}).
+We also give a simple argument that extends our guarantees to the following more common optimization formulation of the dictionary learning problem (Cor.~\ref{SLCopt}).
 
 \begin{problem}\label{OptimizationProblem}
-Find a matrix $\mathbf{B} \in \mathbb{R}^{\bar m}$ and vectors \mbox{$\mathbf{\bar x}_1, \ldots, \mathbf{\bar x}_N \in \mathbb{R}^{\bar m}$} that solve:
+Find a matrix $\mathbf{B} \in \mathbb{R}^m$ and vectors \mbox{$\mathbf{\bar x}_1, \ldots, \mathbf{\bar x}_N \in \mathbb{R}^m$} that solve:
 \begin{align}\label{minsum}
 \min \sum_{i = 1}^N \|\mathbf{\bar x}_i\|_0 \ \ 
-\text{subject to} \ \ \|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\bar x}_i\|_2 \leq \varepsilon, \ \text{for all $i$}.
+\text{subject to} \ \ \|\mathbf{z}_i - \mathbf{B}\mathbf{\bar x}_i\|_2 \leq \eta, \ \text{for all $i$}.
 \end{align}
@@
 The \emph{degree} $\deg(i)$ of a node $i \in [m]$ is the number of sets in $\mathcal{H}$ that contain $i$, and we say $\mathcal{H}$ is \emph{regular} when for some $r$ we have $\deg(i) = r$ for all $i$ (for given $r$, we say $\mathcal{H}$ is \textit{$r$-regular}).
+We also write $\mathcal{H} + \mathcal{H} := \{ S \cup S': S, S' \in \mathcal{H}\}$.
 
 \begin{definition}\label{sip}
-Given $\mathcal{H} \subseteq 2^{[m]}$, the \textbf{star} $\mathcal{G}(i)$ at $i$ is the set of $S \in \mathcal{H}$ with $i \in S$.
-We say $\mathcal{H}$ has the \textbf{singleton intersection property} (\textbf{SIP}) when $\cap \mathcal{G}(i) = \{i\}$ for all $i \in [m]$.
+Given $\mathcal{H} \subseteq 2^{[m]}$, the \textbf{star} $h(i)$ is the collection of sets in $\mathcal{H}$ containing $i$.
+We say $\mathcal{H}$ has the \textbf{singleton intersection property} (\textbf{SIP}) when $\cap h(i) = \{i\}$ for all $i \in [m]$.
 \end{definition}
@@
 The \emph{lower bound} $L$ of a matrix $\mathbf{M} \in \mathbb R^{n \times m}$ is the largest number $\alpha$ such that \mbox{$\|\mathbf{M}\mathbf{x}\|_2 \geq \alpha\|\mathbf{x}\|_2$} for all $\mathbf{x} \in \mathbb{R}^m$ \cite{Grcar10}.
-By compactness of the unit sphere, every injective linear map has a nonzero lower bound; hence, if $\mathbf{M}$ satisfies \eqref{SparkCondition}, then each submatrix formed from $2k$ of its columns or less has a nonzero lower bound.
+By compactness of the unit sphere, every injective linear map has a nonzero lower bound; hence, if $\mathbf{M}$ satisfies the spark condition then each submatrix formed from $2k$ of its columns or less has a nonzero lower bound.
 
-We generalize this domain-restricted lower bound to a \emph{union of subspaces} model \cite{lu2008theory, vidal2005generalized} derived from the hypergraph $\mathcal{H}$.
-Let $\mathbf{M}_J$ be the submatrix formed by the columns of $\mathbf{M}$ indexed by $J$ and let $\bm{\mathcal{M}}_J := \text{span}\{\mathbf{M}_J\}$, with $\bm{\mathcal{M}}_\emptyset := \mathbf{0}$.
-We define:
-\begin{align*}
-L_\mathcal{H}(\mathbf{M}) := \inf \left\{ \frac{ \|\mathbf{M}(\mathbf{x}_1-\mathbf{x}_2)\|_2 }{ \sqrt{2k} \|\mathbf{x}_1-\mathbf{x}_2\|_2} : \mathbf{x}_1, \mathbf{x}_2 \in \cup_{S \in \mathcal{H}} \bm{\mathcal{M}}_S \right\},
-%\frac{1}{\sqrt{k}}\max \{ \alpha : \|\mathbf{M}\mathbf{x}\|_2 \geq \alpha\|\mathbf{x}\|_2 \text{ for all $k$-sparse } \mathbf{x}\}.
-\end{align*} 
+We generalize this domain-restricted lower bound to a \emph{union of subspaces} model \cite{vidal2005generalized} derived from the hypergraph $\mathcal{H}$.
+Letting $\mathbf{M}_J$ denote the submatrix formed by the columns of $\mathbf{M}$ indexed by $J$ (with $\mathbf{M}_\emptyset := \mathbf{0}$), we define:
+%\begin{align*} 
+%L_\mathcal{H}(\mathbf{M}) := \inf \left\{ \frac{ \|\mathbf{M}(\mathbf{x}_1-\mathbf{x}_2)\|_2 }{ \sqrt{2k} \|\mathbf{x}_1-\mathbf{x}_2\|_2} : \mathbf{x}_1, \mathbf{x}_2 \in \cup_{S \in \mathcal{H}} \bm{\mathcal{M}}_S \right\},
+%\end{align*} 
 %
-%This motivates the following definition: 
+%where we write $L_{2k}$ in place of $L_\mathcal{H}$ when $\mathcal{H} = {[m] \choose k}$.
+Note that if $\mathcal{H}$ covers $[m]$, then $L_2 > L_\mathcal{H}$.\footnote{The reader should beware that $L_2 = L_{[m]}$, whereas $L = L_{\{[m]\}}$.
+For even $k$, the quantity $1 - \sqrt{k} L_k(\mathbf{M})$ is also known in the compressive sensing literature as the (asymmetric) lower restricted isometry constant \cite{Blanchard2011}.} Clearly, for any $\mathbf{M}$ satisfying \eqref{SparkCondition}, we have $L_{k'}(\mathbf{M}) > 0$ for  $k' \leq 2k$.
 %\begin{align*}
-%L_k(\mathbf{M}) := \frac{1}{\sqrt{k}}\max \{ \alpha : \|\mathbf{M}\mathbf{x}\|_2 \geq \alpha\|\mathbf{x}\|_2 \text{ for all $k$-sparse } \mathbf{x}\}.
+%L_\mathcal{H}(\mathbf{M}) := \inf \left\{ \frac{ \|\mathbf{M}_S\mathbf{x}\|_2 }{ \sqrt{k} \|\mathbf{x}\|_2} : S \in \mathcal{H} \right\},
 %\end{align*} 
 %\begin{align*}
-%L_\mathcal{H}(\mathbf{M}) := \inf \left\{ \frac{ \|\mathbf{M}_{S \cup S'}\mathbf{x}\|_2 }{ \sqrt{2k} \|\mathbf{x}\|_2} : \mathbf{x} \in \mathbb{R}^{|S\cup S'|}, \ \ S,S' \in \mathcal{H} \right\}
-%\frac{1}{\sqrt{k}}\max \{ \alpha : \|\mathbf{M}\mathbf{x}\|_2 \geq \alpha\|\mathbf{x}\|_2 \text{ for all $k$-sparse } \mathbf{x}\}.
+%L_\mathcal{H}(\mathbf{M}) := \max \left\{ \alpha: \|\mathbf{M}_S\mathbf{x}\|_2 \geq \alpha \sqrt{k} \|\mathbf{x}\|_2 : S \in \mathcal{H}, \ \ \mathbf{x} \in \mathbb{R}^m \right\},
 %\end{align*} 
+\begin{align}\label{Ldef}
+L_\mathcal{H}(\mathbf{M}) := \frac{1}{\sqrt{k}} \inf \left\{ \frac{\|\mathbf{M}_S\mathbf{x}\|_2}{ \|\mathbf{x}\|_2} : S \in \mathcal{H}, \ \ \mathbf{x} \in \mathbb{R}^m \right\},
+\end{align} 
 %
-where we write $L_{2k}:= L_\mathcal{H}$ when $\mathcal{H} = {[m] \choose k}$.
-Beware that $ L = L_{\{[m]\}}$ whereas $L_{[m]} = L_2$.
-[TODO: Note when $L_2 > 0$ is implied by $L_\mathcal{H} > 0$.] We note that the quantity $1 - \sqrt{k} L_k(\mathbf{M})$ is also known in the compressive sensing literature as the (asymmetric) lower restricted isometry constant \cite{Blanchard2011}.
-Clearly, for any $\mathbf{M}$ satisfying \eqref{SparkCondition}, we have $L_{k'}(\mathbf{M}) > 0$ for  $k' \leq 2k$.
+where we write $L_{k}$ when $\mathcal{H} = {[m] \choose k}$.\footnote{We note that the quantity $1 - \sqrt{k} L_k(\mathbf{M})$ is also known in the compressive sensing literature as the (asymmetric) lower restricted isometry constant \cite{Blanchard2011}.} Clearly, for any $\mathbf{M}$ satisfying \eqref{SparkCondition}, we have $L_{k'}(\mathbf{M}) > 0$ for  $k' \leq 2k$.
+Note that if $\mathcal{H}$ covers $[m]$ then $L_2 \geq L_{\mathcal{H}+\mathcal{H}}$.
 
-A vector $\mathbf{x}$ is said to be \emph{supported} on $S \subseteq [m]$ when $\mathbf{x} \in \text{\rm span}\{\mathbf{e}_j: j\in S\}$, where $\mathbf{e}_j$ are the standard basis in $\mathbb R^m$.
+A vector $\mathbf{x}$ is said to be \emph{supported} in $S \subseteq [m]$ when $\mathbf{x} \in \text{\rm span}\{\mathbf{e}_j: j\in S\}$, where $\mathbf{e}_j$ are the standard basis in $\mathbb R^m$.
 Denote by $\mathbf{x}^J$ the subvector formed from the entries of $\mathbf{x}$ indexed by $J$.
@@
 \begin{theorem}\label{DeterministicUniquenessTheorem}
-Fix a real $n \times m$ matrix $\mathbf{A}$ with $L_\mathcal{H}(\mathbf{A}) > 0$ for some $r$-regular $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP.
-If the sequence \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} contains, for each $S \in \mathcal{H}$, more than $(k-1){m \choose k}$ $k$-sparse vectors in general linear position supported on $S$, then there is a constant\footnote{We delay defining the constant $C_1$ until Section \ref{DUT} (\eqref{Cdef1}).} $C_1 > 0$ for which the following holds for all $\varepsilon < L_{2}(\mathbf{A}) / C_1$:
+Fix a real $n \times m$ matrix $\mathbf{A}$ with $L_{\mathcal{H}+\mathcal{H}}(\mathbf{A}) > 0$ for some $r$-regular $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP.
+If the sequence \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} contains, for each $S \in \mathcal{H}$, more than $(k-1){m \choose k}$ $k$-sparse vectors in general linear position supported in $S$, then there is a constant\footnote{We delay defining the constant $C_1$ until Section \ref{DUT} (\eqref{Cdef1}).} $C_1 > 0$ for which the following holds for all $\varepsilon < L_{2}(\mathbf{A}) / C_1$:
 
@@
 \begin{align}\label{Cstable}
-\|(\mathbf{A_J})_j- \mathbf{B}_{\bar J} \mathbf{PD}_j\|_2 \leq C_1 \varepsilon \ \ \text{for all } j \in J,
+\|\mathbf{A}_j- \mathbf{B}_{\bar J} \mathbf{PD}_j\|_2 \leq C_1 \varepsilon \ \ \text{for all } j \in J,
 \end{align}
 %
-for some non-empty $J, \bar J$ of size $\bar m - r(\bar m - m)$, permutation $\mathbf{P}$ and invertible diagonal $\mathbf{D}$.
+for some non-empty $J, \bar J$ of size $\bar m - r(\bar m - m)$, some permutation $\mathbf{P}$ and invertible diagonal $\mathbf{D}$.
 
-Moreover, if in fact $L_{2k}(\mathbf{A}) > 0$ and $\varepsilon < L_{2k}(\mathbf{A}) / C_1$ then $L_{2k}(\mathbf{B}\mathbf{PD}) \geq L_{2k}(\mathbf{A}) - C_1 \varepsilon$ and:
+Moreover, if in fact $\varepsilon < L_{2k}(\mathbf{A}) / C_1$ (provided $L_{2k}(\mathbf{A}) > 0$), then $L_{2k}(\mathbf{B}\mathbf{PD}) \geq L_{2k}(\mathbf{A}) - C_1 \varepsilon$ and:
 \begin{align}\label{b-PDa}
@@
 To be clear, Thm.~\ref{DeterministicUniquenessTheorem} says that the smaller the difference $\bar m - m$, the more columns and coefficients of the original dictionary $\mathbf{A}$ and codes $\mathbf{x}_i$ contained (up to noise) in the appropriately scaled dictionary $\mathbf{B}$ and codes $\mathbf{\bar x}_i$.
-The implication in the case $\bar m = m$ is that $Y = \{\mathbf{Ax}_1, \ldots, \mathbf{Ax}_N\}$ has a stable $k$-sparse representation in $\mathbb{R}^m$, with \eqref{def1} guaranteed provided $\varepsilon$ in Def.~\ref{maindef} does not exceed:
+The implication for $\bar m = m$ is that $Y = \{\mathbf{Ax}_1, \ldots, \mathbf{Ax}_N\}$ has a stable $k$-sparse representation in $\mathbb{R}^m$, with \eqref{def1} guaranteed provided $\varepsilon$ in Def.~\ref{maindef} does not exceed:
 \begin{align}\label{epsdel}
@@
 \begin{corollary}\label{DeterministicUniquenessCorollary}
-Given $n, m$, $k < m$, and a regular hypergraph $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP, there are $N =  |\mathcal{H}| \left[ (k-1){m \choose k} + 1  \right]$ vectors \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} such that every matrix $\mathbf{A} \in \mathbb{R}^{n \times m}$ satisfying \eqref{SparkCondition} generates a dataset $Y = \{\mathbf{A}\mathbf{x}_1, \ldots, \mathbf{A}\mathbf{x}_N\}$ with a stable $k$-sparse representation in $\mathbb{R}^m$.
+Given a regular hypergraph $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP, there are $N =  |\mathcal{H}| \left[ (k-1){m \choose k} + 1  \right]$ vectors \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} such that every matrix $\mathbf{A}$ with $L_{\mathcal{H}+\mathcal{H}}(\mathbf{A}) > 0$ generates a dataset $Y = \{\mathbf{A}\mathbf{x}_1, \ldots, \mathbf{A}\mathbf{x}_N\}$ with a stable $k$-sparse representation in $\mathbb{R}^m$.
 \end{corollary}
 
-As already mentioned, there exist $k$-uniform regular hypergraphs $\mathcal{H}$ with the SIP having cardinality $|\mathcal{H}| = m$, implying the lower bound for sample size $N$ from the introduction.
-In many cases, however, the SIP can be achieved with far fewer supports; for example, when $k = \sqrt{m}$, take $\mathcal{H}$ to be the $2k$ rows and columns formed by arranging $[m]$ in a square grid.
+As mentioned above, there exist $k$-uniform regular hypergraphs $\mathcal{H}$ with the SIP having cardinality $|\mathcal{H}| = m$, implying the lower bound for sample size $N$ from the introduction.
+In many cases, however, the SIP is achievable with far fewer supports; for example, when $k = \sqrt{m}$, take $\mathcal{H}$ to be the $2k$ rows and columns formed by arranging $[m]$ in a square grid.
 
@@
 \begin{corollary}\label{SLCopt}
-If all of the assumptions of Thm.\ref{DeterministicUniquenessTheorem} hold with more than $(k-1)\left[ {\bar m \choose k} + |\mathcal{H}|k{\bar m \choose k-1}\right]$ vectors $\mathbf{x}_i$ supported on each $S \in \mathcal{H}$, then all solutions to Prob.~\ref{OptimizationProblem} necessarily satisfy the implications \eqref{Cstable} and \eqref{b-PDa} of Thm.~\ref{DeterministicUniquenessTheorem}.
+If all of the assumptions of Thm.\ref{DeterministicUniquenessTheorem} hold, only now with more than $(k-1)\left[ {\bar m \choose k} + |\mathcal{H}|k{\bar m \choose k-1}\right]$ vectors $\mathbf{x}_i$ supported in each $S \in \mathcal{H}$, then all solutions to Prob.~\ref{OptimizationProblem} necessarily satisfy the implications \eqref{Cstable} and \eqref{b-PDa} of Thm.~\ref{DeterministicUniquenessTheorem}.
 \end{corollary}
@@
 \begin{theorem}\label{robustPolythm}
-There is a polynomial $g$ in the entries of $\mathbf{A}$ and $\mathbf{x}_i$ with the following property:  if $g$ evaluates to a nonzero number and more than \mbox{$(k-1){m \choose k}$} of the resulting $\mathbf{x}_i$ are supported on each $S \in \mathcal{H}$ for some regular $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP, then $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$ (Def.~\ref{maindef}).
+There is a polynomial $g$ in the entries of $\mathbf{A}$ and $\mathbf{x}_i$ with the following property:  if $g$ evaluates to a nonzero number and more than \mbox{$(k-1){m \choose k}$} of the resulting $\mathbf{x}_i$ are supported in each $S \in \mathcal{H}$ for some regular $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP, then $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$ (Def.~\ref{maindef}).
 In particular, all -- except for a Borel set of measure zero -- substitutions impart to $Y$ this property.
@@
 Fix $k < m$ and $n \geq \min(2k, m)$ and let the entries of $\mathbf{A} \in \mathbb{R}^{n \times m}$ and $k$-sparse $\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$ be drawn independently from probability measures absolutely continuous with respect to the standard Borel measure $\mu$.
-If more than $(k-1){m \choose k}$ of the vectors $\mathbf{x}_i$ are supported on each $S \in \mathcal{H}$ for a regular $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP, then $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$ with probability one.
+If more than $(k-1){m \choose k}$ of the vectors $\mathbf{x}_i$ are supported in each $S \in \mathcal{H}$ for a regular $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP, then $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$ with probability one.
 \end{corollary}
 
-Thus, choosing the dictionary and sparse codes ``randomly'' almost certainly generates data with stable sparse representations.
+Thus, choosing the dictionary and sparse codes ``randomly'' almost certainly generates data with a stable sparse representation.
 
@@
 As mentioned in the previous section, Thm.~\ref{DeterministicUniquenessTheorem} is a particular case of a more general result that forgoes the assumption that $\mathcal{H} \subseteq {[m] \choose k}$ is regular and satisfies the SIP.
-If instead we require only that the stars $\cap H(i)$ intersect at singletons for all $i \leq q$ (assuming that the nodes of $\mathcal{H}$ are labeled in some order of non-increasing degree), we have that $\bar m \geq k|\mathcal{H}| / \deg(1)$ and, provided $\bar m < k|\mathcal{H}| / (\deg(1) - 1)$, the non-empty submatrix $J$ is of size equal to the largest number $p$ satisfying:
+If instead we require only that the stars $\cap h(i)$ intersect at singletons for all $i \leq q$ (assuming that the nodes of $\mathcal{H}$ are labeled in some order of non-increasing degree), we have that $\bar m \geq k|\mathcal{H}| / \deg(1)$ and, provided $\bar m < k|\mathcal{H}| / (\deg(1) - 1)$, the non-empty submatrix $J$ is of size equal to the largest number $p$ satisfying:
 \begin{align}\label{pcond}
@@
 \end{align}
-Specifically, $J$ consists of the union of the set of all nodes of degree exceeding $\deg(p)$ and some subset of those nodes with degrees equal to $\deg(p)$.
-For the benefit of the reader, we do not prove this more general result below; it can be gleaned by examining how exactly Lemma \ref{NonEmptyLemma} is incorporated into the proof of Lem.~\ref{MainLemma}.
+Specifically, $J$ contains all nodes of degree exceeding $\deg(p)$ and some subset of those with degreee equal to $\deg(p)$.
+For the benefit of the reader, we do not prove explicitly this more general result below; it can be discerned from how exactly Lemma \ref{NonEmptyLemma} is incorporated into the proof of Lem.~\ref{MainLemma}.
 %As mentioned in the previous section, Thm.~\ref{DeterministicUniquenessTheorem} is a particular case of a more general result, which requires a looser set of constraints on the hypergraph $\mathcal{H}$ and which applies to $n \times \bar m$ matrices $\mathbf{B}$ (and $\bar m$-dimensional codes $\mathbf{\bar x}_i$) with $\bar m \neq m$:
@@
 
-We now begin our proof of Thm.~\ref{DeterministicUniquenessTheorem} by showing how dictionary recovery \eqref{Cstable} already implies sparse code recovery \eqref{b-PDa} when $L_{2k}(\mathbf{A}) > 0$ and \mbox{$\varepsilon < L_{2k}(\mathbf{A}) / C_1$}, temporarily assuming (without loss of generality) that $\bar m = m$.
-First, note that $\|\mathbf{x}\|_1 \leq \sqrt{k} \|\mathbf{x}\|_2$ for $k$-sparse $\mathbf{x} \in \mathbb{R}^m$, which by definition of $L_{2k}$ implies the following frequently applied inequality:
+We now begin our proof of Thm.~\ref{DeterministicUniquenessTheorem} by showing how dictionary recovery \eqref{Cstable} already implies sparse code recovery \eqref{b-PDa} when \mbox{$\varepsilon < L_{2k}(\mathbf{A}) / C_1$} (provided $L_{2k}(\mathbf{A}) > 0$), temporarily assuming (without loss of generality) that $\bar m = m$.
+First, note that since $\|\mathbf{A}\mathbf{x}\|_2 \leq \max_j\|\mathbf{A}_j\|_2\|\mathbf{x}\|_1$ and $\|\mathbf{x}\|_1 \leq \sqrt{k} \|\mathbf{x}\|_2$ for $k$-sparse $\mathbf{x}$, by \eqref{Ldef} we have the following frequently applied inequality:
 \begin{align}\label{delrho}
-L_{2k}(\mathbf{A}) \leq \frac{\|\mathbf{A}\mathbf{x}\|_2}{\sqrt{2k} \|\mathbf{x}\|_2} 
-\leq  \max_{j \in [m]}\|\mathbf{A}_j\|_2.
+L_{\mathcal{H} + \mathcal{H}}(\mathbf{A}) %\leq \frac{\|\mathbf{A}\mathbf{x}\|_2}{\sqrt{2k} \|\mathbf{x}\|_2} 
+\leq  \max_j\|\mathbf{A}_j\|_2.
 \end{align}
-For $k$-sparse $\mathbf{x} \in \mathbb{R}^m$, the triangle inequality gives \mbox{$\|(\mathbf{A}-\mathbf{BPD})\mathbf{x}\|_2  \leq C_1\varepsilon \|\mathbf{x}\|_1 \leq C_1 \varepsilon \sqrt{2k}  \|\mathbf{x}\|_2$}.
-Thus,
+For $2k$-sparse $\mathbf{x} \in \mathbb{R}^m$, the triangle inequality gives \mbox{$\|(\mathbf{A}-\mathbf{BPD})\mathbf{x}\|_2  \leq C_1\varepsilon \|\mathbf{x}\|_1 \leq C_1 \varepsilon \sqrt{2k}  \|\mathbf{x}\|_2$}.
+Thus:
 \begin{align*}
@@
 &\geq | \|\mathbf{A}\mathbf{x}\|_2 - \|(\mathbf{A}-\mathbf{BPD})\mathbf{x}\|_2 | \\
-&\geq \sqrt{2k} (L_{2k}(\mathbf{A}) -  C_1\varepsilon) \|\mathbf{x}\|_2.
+&\geq \sqrt{2k} (L_{2k}(\mathbf{A}) -  C_1\varepsilon) \|\mathbf{x}\|_2,
 \end{align*}
-
-Hence, $L_{2k}(\mathbf{BPD}) \geq L_{2k}(\mathbf{A}) - C_1\varepsilon  > 0$. \eqref{b-PDa} then follows from:
+%
+since $\varepsilon < L_{2k}(\mathbf{A}) / C_1$. Hence, $L_{2k}(\mathbf{BPD}) \geq L_{2k}(\mathbf{A}) - C_1\varepsilon  > 0$, and \eqref{b-PDa} then follows from:
 \begin{align*}
@@
 \end{align} 
-Note that if $\bar{c}_j = 0$, then $\|c_j\mathbf{A}_j \|_2 \leq \varepsilon$ implies from \eqref{delrho} that $|c_j| < \min_{\ell \in [m]} | c_\ell |$, a contradiction.
-Thus, $\bar{c}_j \neq 0$, $j \in [m]$.
+Note that if $\bar{c}_j = 0$, then $\|c_j\mathbf{A}_j \|_2 \leq \varepsilon$ implies from \eqref{delrho} that $|c_j| < \min_{\ell \in [m]} | c_\ell |$, a contradiction.  Thus, $\bar{c}_j \neq 0$.
 
@@
 \begin{align*}
-\|(\mathbf{A} - \mathbf{B}_{\bar J}\mathbf{PD})_j\|_2 
+\|\mathbf{A}_j - \mathbf{B}_{\bar J}\mathbf{PD}_j\|_2 
 = \|\mathbf{A}_j - \frac{\bar{c}_j}{c_j}\mathbf{B}_{\pi(j)}\|_2 
@@
 
-Our result in combinatorial matrix analysis is the following.
+Our result in combinatorial matrix analysis is the following. Let $\bm{\mathcal{M}}$ denote the column-span of a matrix $\mathbf{M}$.
 
 \begin{lemma}\label{MainLemma}
-Suppose $\mathbf{A} \in \mathbb{R}^{n \times m}$ has $L_\mathcal{H}(\mathbf{A}) > 0$ for some $r$-regular $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP.
+Suppose $\mathbf{A} \in \mathbb{R}^{n \times m}$ has $L_{\mathcal{H}+\mathcal{H}}(\mathbf{A}) > 0$ for some $r$-regular $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP.
 There exists $C_2 > 0$ for which the following holds for all $\varepsilon < L_2(\mathbf{A}) / C_2$:
@@
 \begin{align}\label{MainLemmaBPD}
-\|(\mathbf{A}_J)_j - \mathbf{B}_{\bar J} \mathbf{PD}_j\|_2 \leq C_2 \varepsilon, \ \  \text{for } j \in J,
+\|\mathbf{A}_j - \mathbf{B}_{\bar J} \mathbf{PD}_j\|_2 \leq C_2 \varepsilon, \ \  \text{for } j \in J,
 \end{align}
@@
 
-The constant $C_1 > 0$ in Thm.~\ref{DeterministicUniquenessTheorem} is then defined by\footnote{Note that $\|\mathbf{AX}_{I(S)}\mathbf{c}\|_2 \geq \sqrt{k} L_k(\mathbf{A})\|\mathbf{X}_{I(S)}\mathbf{c}\|_2 \geq k L_k(\mathbf{A}) L_k(\mathbf{X}_{I(S)})\|\mathbf{c}\|_2$ for $S \in \mathcal{H}$ and $k$-sparse $\mathbf{c}$.
-Therefore, $\sqrt{k} L_k(\mathbf{AX}_{I(S)}) \geq k L_k(\mathbf{A}) L_k(\mathbf{X}_{I(S)}) > 0$ since $L_k(\mathbf{A}), L_k(\mathbf{X}_{I(S)}) > 0$ by \eqref{SparkCondition} and general linear position of the $\mathbf{x}_i$.
+The constant $C_1 > 0$ in Thm.~\ref{DeterministicUniquenessTheorem} is then given by\footnote{Note that $\|\mathbf{AX}_{I(S)}\mathbf{c}\|_2 \geq \sqrt{k} L_\mathcal{H}(\mathbf{A})\|\mathbf{X}_{I(S)}\mathbf{c}\|_2 \geq k L_\mathcal{H}(\mathbf{A}) L_k(\mathbf{X}_{I(S)})\|\mathbf{c}\|_2$ for $S \in \mathcal{H}$ and $k$-sparse $\mathbf{c}$.
+Therefore, $L_k(\mathbf{AX}_{I(S)}) \geq \sqrt{k} L_\mathcal{H}(\mathbf{A}) L_k(\mathbf{X}_{I(S)}) > 0$ since $L_{\mathcal{H}+\mathcal{H}}(\mathbf{A})> 0$ and $L_k(\mathbf{X}_{I(S)}) > 0$ by general linear position of the $\mathbf{x}_i$.
 Thus, $C_1 > 0$.}:
@@
 \end{align}
-where, given vectors $\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$, we denote by $\mathbf{X}$ the $m \times N$ matrix with columns $\mathbf{x}_i$ and by $I(S)$ the set of indices $i$ for which the support of $\mathbf{x}_i$ is contained in $S$.
+where, given vectors $\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$, we denote by $\mathbf{X}$ the $m \times N$ matrix with columns $\mathbf{x}_i$ and by $I(S)$ the set of indices $i$ for which $\mathbf{x}_i$ is supported in $S$.
 
@@
 \begin{definition}\label{SpecialSupportSet}\label{FriedrichsDefinition}
-For a subspace arrangement $V_1, \ldots, V_\ell \subseteq \mathbb{R}^m$, set $r := 1$ when $\ell = 1$ and define for $\ell \geq 2$:
+For subspaces $V_1, \ldots, V_\ell \subseteq \mathbb{R}^m$, set $r := 1$ when $\ell = 1$ and define for $\ell \geq 2$:
 \begin{align*}
@@
 \begin{align}\label{Cdef2}
-C_2(\mathbf{A}, \mathcal{H}) := \frac{ 2^{|\mathcal{H}|} \max_{j \in [m]} \|\mathbf{A}_j\|_2}{ \min_{F \subseteq \mathcal{H}} r( \{ \bm{\mathcal{A}}_S \}_{S \in F}) },
+C_2(\mathbf{A}, \mathcal{H}) := \frac{ 2^{|\mathcal{H}|} \max_{j \in [m]} \|\mathbf{A}_j\|_2}{ \min_{\mathcal{G} \subseteq \mathcal{H}} r( \{ \bm{\mathcal{A}}_S \}_{S \in \mathcal{G}}) },
 \end{align}
@@
 
-Since there are more than $(k-1){\bar m \choose k}$ vectors $\mathbf{x}_i$ supported on $S$, by the pigeonhole principle there must be some $\bar S \in {[\bar m] \choose k}$ and set of $k$ indices $K \subseteq I(S)$ such that the supports of all $\mathbf{\bar x}_i$ with $i \in K$ are subsets of $\bar S$.
+Since there are more than $(k-1){\bar m \choose k}$ vectors $\mathbf{x}_i$ supported in $S$, by the pigeonhole principle there must be some $\bar S \in {[\bar m] \choose k}$ and set of $k$ indices $K \subseteq I(S)$ such that all $\mathbf{\bar x}_i$ with $i \in K$ are supported in $\bar S$.
 
-It follows from $L_\mathcal{H}(\mathbf{A}) > 0$ and the general linear position of the $\mathbf{x}_i$ that $L(\mathbf{AX}_{K}) > 0$; that is, the columns of the $n \times k$ matrix $\mathbf{AX}_K$ form a basis for $\bm{\mathcal{A}}_S$.
+It follows from $L_{\mathcal{H}+\mathcal{H}}(\mathbf{A}) > 0$ and the general linear position of the $\mathbf{x}_i$ that $L(\mathbf{AX}_{K}) > 0$; that is, the columns of the $n \times k$ matrix $\mathbf{AX}_K$ form a basis for $\bm{\mathcal{A}}_S$.
 Fixing $\mathbf{0} \neq \mathbf{y} \in \bm{\mathcal{A}}_S$, there then exists $\mathbf{0} \neq \mathbf{c} = (c_1, \ldots, c_k) \in \mathbb{R}^k$ such that $\mathbf{y} = \mathbf{AX}_K\mathbf{c}$.
@@
 \end{align*}
-where the last inequality follows directly from the definition of $L$. From Def.~\ref{dDef} we have:
+where the last inequality follows directly from \eqref{Ldef}. From Def.~\ref{dDef} we have:
 \begin{align}\label{rhs222}
@@
 %
-where the second inequality follows from $L(\mathbf{AX}_{K}) \geq L_k(\mathbf{AX}_{I(S)})$ and \eqref{Cdef1}. Since $\varepsilon < L_2(\mathbf{A})/C_1$, the result follows by Lem.~\ref{MainLemma}, .
+where the second inequality is due to $L(\mathbf{AX}_{K}) \geq L_k(\mathbf{AX}_{I(S)})$ and \eqref{Cdef1}. Since $\varepsilon < L_2(\mathbf{A})/C_1$, the result follows by Lem.~\ref{MainLemma}, .
 \end{proof}
@@
 We bound the number of $k$-sparse $\mathbf{\bar x}_i$ and then apply Thm.~\ref{DeterministicUniquenessCorollary}.
-Let $n_p$ be the number of $\mathbf{\bar x}_i$ with $\|\mathbf{\bar x}_i\|_0 = p$.
+First, observe that no more than $(k-1)|\mathcal{H}|$ of the $\mathbf{\bar x}_i$ share a support $\bar S$ of size less than $k$; otherwise, by the pigeonhole principle, at least $k$ of these indices $i$ belong to the same $K \subseteq I(S)$ for some $S \in \mathcal{H}$ and (as argued previously) \eqref{rhs222} follows.
+Since the right-hand side of \eqref{rhs222} is less than one, by \eqref{dimLem} we have the contradiction $k = \dim(\bm{\mathcal{A}}_S) \leq \dim(\bm{\mathcal{B}}_{\bar S}) \leq |\bar S|.$ The total number of $(k-1)$-sparse vectors $\mathbf{\bar x}_i$ can thus not exceed $|\mathcal{H}|(k-1){ \bar m \choose k-1}$.
+
+We now apply this fact to bound the number of $k$-sparse $\mathbf{\bar x}_i$. Let $n_p$ be the number of $\mathbf{\bar x}_i$ with $\|\mathbf{\bar x}_i\|_0 = p$.
 Since the $\mathbf{x}_i$ are all $k$-sparse, by \eqref{minsum} we have:
@@
 
-We now show that no more than $(k-1)|\mathcal{H}|$ of the $\mathbf{\bar x}_i$ share a support of size less than $k$. 
-From previous arguments, for every $S \in \mathcal{H}$, the columns of each $n \times k$ submatrix of $\mathbf{AX}_{I(S)}$ form a basis for $\bm{\mathcal{A}}_S$.
-Suppose that more than $(k-1)|\mathcal{H}|$ vectors $\mathbf{\bar x}_i$ share a support $\bar S$ of size $|\bar{S}| < k$.
-By the pigeonhole principle, there is some $S \in \mathcal{H}$ supporting $k$ or more of the corresponding $\mathbf{x}_i$; let them be indexed by $K \subseteq I(S)$.
-By the same argument as in the proof of Thm.\ref{DeterministicUniquenessTheorem}, we also have \eqref{rhs222}.
-Our bound on $\varepsilon$ implies the right-hand side of \eqref{rhs222} is less than one; hence, by \eqref{dimLem} we have the contradiction $k = \dim(\bm{\mathcal{A}}_S) \leq \dim(\bm{\mathcal{B}}_{\bar S}) \leq |\bar S|.$
-
-The total number of $(k-1)$-sparse vectors $\mathbf{\bar x}_i$ can thus no greater than $|\mathcal{H}|(k-1){ \bar m \choose k-1}$.
-Taking \eqref{eqn} into account, no more than $|\mathcal{H}|k(k-1){ \bar m \choose k-1}$ vectors $\mathbf{\bar x}_i$ are \emph{not} $k$-sparse.
-Since for every $S \in \mathcal{H}$ there are over $(k-1)\left[ {\bar m \choose k} + |\mathcal{H}|k{ \bar m \choose k-1} \right]$ vectors $\mathbf{x}_i$ supported there, it follows that more than $(k-1){\bar m \choose k}$ of them must have corresponding $\mathbf{\bar x}_i$ that are also $k$-sparse.
+Therefore, no more than $|\mathcal{H}|k(k-1){ \bar m \choose k-1}$ vectors $\mathbf{\bar x}_i$ are \emph{not} $k$-sparse.
+Since for every $S \in \mathcal{H}$ there are over $(k-1)\left[ {\bar m \choose k} + |\mathcal{H}|k{ \bar m \choose k-1} \right]$ vectors $\mathbf{x}_i$ supported there, it follows that more than $(k-1){\bar m \choose k}$ of them have corresponding $\mathbf{\bar x}_i$ that are $k$-sparse.
 The result now follows directly from Thm.~\ref{DeterministicUniquenessCorollary}.
@@
 \begin{lemma}\label{spanIntersectionLemma}
-If $f: U \to V$ is an injective function then:
-\begin{align*}
-f\left(\cap_{i=1}^\ell U_i \right) =  \cap_{i=1}^\ell f\left(U_i\right) \ \ \text{for any } U_1, \ldots, U_\ell \subseteq U.
-\end{align*}
+If $f: U \to V$ is an injective function then $f\left(\cap_{i=1}^\ell U_i \right) =  \cap_{i=1}^\ell f\left(U_i\right)$ for any $U_1, \ldots, U_\ell \subseteq U$.
 %In particular, if for some $E \in 2^{[m]}$ the map $M \in \mathbb{R}^{n \times m}$ is injective on $\cup_{S \in \mathcal{H}} \text{span}\{e_i\}_{i \in S}$ then $\text{span}\{ M_{\cap_{S \in \mathcal{H}} S} \} = \cap_{S \in \mathcal{H}} \text{span}\{M_S\}$.
@@
 \begin{lemma}\label{NonEmptyLemma}
-Fix a hypergraph $\mathcal{H} \subseteq 2^{[m]}$ with nodes labeled in order of non-increasing degree and for which $|\cap H(i)| = 1$ for all $i \leq q$.
+Fix a hypergraph $\mathcal{H} \subseteq 2^{[m]}$ with nodes labeled in order of non-increasing degree and for which $|\cap h(i)| = 1$ for all $i \leq q$.
 Fix $\bar m$ and let $p \leq q$ be the largest number satisfying:
@@
 \begin{align}\label{cond}
-|\cap \pi(F)| \leq |\cap F | \text{ for all } F \subseteq \mathcal{H},
+|\cap \pi(\mathcal{G})| \leq |\cap \mathcal{G} | \text{ for all } \mathcal{G} \subseteq \mathcal{H},
 \end{align}
-then $\bar m \geq\sum_i \deg(i) / \deg(1)$, and if $\bar m < \sum_i \deg(i) / (\deg(1) - 1)$ then the association $i \mapsto \cap \pi(F(i))$ defines an injective map to $[\bar m]$ from some non-empty $J \subseteq [m]$ of size $p$ consisting of the union of the set of all nodes of degree exceeding $\deg(p)$ and some set of nodes all having degree equal to $\deg(p)$.
+then $\bar m \geq\sum_i \deg(i) / \deg(1)$, and if $\bar m < \sum_i \deg(i) / (\deg(1) - 1)$ then the association $i \mapsto \cap \pi(h(i))$ defines an injective map to $[\bar m]$ from some non-empty $J \subseteq [m]$ of size $p$ consisting of the union of the set of all nodes of degree exceeding $\deg(p)$ and some set of nodes all having degree equal to $\deg(p)$.
 In particular, if $\mathcal{H}$ is $r$-regular then $|J| = \bar m - r(\bar m - m)$.
@@
 By \eqref{pcond} and the upper bound on $\bar m$ we have $|T_1| >  \bar m (\deg(1) - 1)$, which implies, again by the pigeonhole principle, that there must be at least $\deg(1)$ elements of $T_1$ sharing the same first index.
-By \eqref{cond}, the intersection of the set $F_1$ consisting of their second indices is non-empty.
-As $p \leq q$ and $\deg(1) \geq \deg(i)$ for all $i$, it must be that $|\cap F_1| = 1$.
-Since $\cap \pi(F_1)$ is non-empty, applying \eqref{cond} again implies $\cap \pi(F_1) = \{i_1\}$ for some $i_1 \in [m]$.
+By \eqref{cond}, the intersection of the set $\mathcal{G}_1$ consisting of their second indices is non-empty.
+As $p \leq q$ and $\deg(1) \geq \deg(i)$ for all $i$, it must be that $|\cap \mathcal{G}_1| = 1$.
+Since $\cap \pi(\mathcal{G}_1)$ is non-empty, applying \eqref{cond} again implies $\cap \pi(\mathcal{G}_1) = \{i_1\}$ for some $i_1 \in [m]$.
 If $p=1$ then we are done.
@@
 By \eqref{pcond} we have $|T_2| > (\bar m - 1)(\deg(2) - 1)$ and reiterating the above arguments produces a (necessarily) distinct index $i_2$.
-Iterating the arguments $p$ times yields the set of singletons \mbox{$J = \{\cap F_1, \ldots, \cap F_p\} \subseteq [m]$}.
+Iterating the arguments $p$ times yields the set of singletons \mbox{$J = \{\cap \mathcal{G}_1, \ldots, \cap \mathcal{G}_p\} \subseteq [m]$}.
 %TODO: Let T_1 be the set of all pairs $T_1 := \{(R, S): R \subseteq \pi(S), S \in \mathcal{H}\}$ 
@@
 \begin{proof}[Proof of Lem.~\ref{MainLemma}]
-We will show how the bound \eqref{GapUpperBound} trickles through the intersection semi-lattices of the subspace arrangements $\{\bm{\mathcal{A}}_S\}_{S \in \mathcal{H}}$ and $\{\bm{\mathcal{B}}_{\bar S}\}_{\bar S \in \pi(\mathcal{H})}$ to yield \eqref{MainLemmaBPD} by virtue of the SIP.
+We will show that the bound \eqref{GapUpperBound} trickles through the intersection semi-lattices of $\{\bm{\mathcal{A}}_S\}_{S \in \mathcal{H}}$ and $\{\bm{\mathcal{B}}_{\bar S}\}_{\bar S \in \pi(\mathcal{H})}$ to yield \eqref{MainLemmaBPD} by virtue of the SIP.
 
-We begin by showing that $\dim(\bm{\mathcal{B}}_{\pi(S)}) = \dim(\bm{\mathcal{A}}_S)$ for all $S \in \mathcal{H}$. 
+We begin by showing that:
+\begin{align}\label{eq2}
+\dim(\bm{\mathcal{B}}_{\pi(S)}) = \dim(\bm{\mathcal{A}}_S) \ \ \text{for all $S \in \mathcal{H}$}. 
+\end{align}
 Since the right-hand side of \eqref{GapUpperBound} is less than one (by \eqref{delrho} and $r \leq 1$), it follows from \eqref{dimLem} that $|\pi(S)| \geq \dim(\bm{\mathcal{B}}_{\pi(S)}) \geq \dim(\bm{\mathcal{A}}_S) = |S|$, with the equality by injectivity of $\mathbf{A}$.
@@
 We next show that \eqref{cond} holds.
-Fix $F \subseteq \mathcal{H}$.
-Since $\bm{\mathcal{B}}_{\cap \pi(F)}\} \subseteq \cap_{S \in F} \bm{\mathcal{B}}_{\pi(S)}$, if $\cap_{S \in F} \bm{\mathcal{B}}_{\pi(S)} = \{\textbf{0}\}$, then we must have $|\cap_{S \in F} \pi(S)| = 0$ (as the columns of $\mathbf{B}_{\pi(S)}$ are linearly independent) and \eqref{cond} is trivially true.
+Fix $\mathcal{G} \subseteq \mathcal{H}$.
+Since $\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})} \subseteq \cap_{S \in \mathcal{G}} \bm{\mathcal{B}}_{\pi(S)}$, if $\cap_{S \in \mathcal{G}} \bm{\mathcal{B}}_{\pi(S)} = \{\textbf{0}\}$, then we must have $|\cap_{S \in \mathcal{G}} \pi(S)| = 0$ (as the columns of $\mathbf{B}_{\pi(S)}$ are linearly independent) and \eqref{cond} is trivially true.
 Suppose then that the intersection is not the zero vector.
-By Lem.~\ref{eqdim} and Lem.~\ref{DistanceToIntersectionLemma}, and then incorporating \eqref{eq2} and \eqref{GapUpperBound}, we have:
+Applying (in order) Lem.~\ref{eqdim}, Lem.~\ref{DistanceToIntersectionLemma}, \eqref{dDef}, \eqref{eq2} and finally \eqref{GapUpperBound}, we have:
 \begin{align}\label{randoml}
-d(\bm{\mathcal{B}}_{\cap \pi(F)}&, \bm{\mathcal{A}}_{\cap F}  ) 
-\leq d\left( \cap_{S \in F} \bm{\mathcal{B}}_{\pi(S)}, \cap_{S \in F} \bm{\mathcal{A}}_S \right) \nonumber \\
-&\leq \sum_{T \in F} \frac{ d\left( \cap_{S \in F} \bm{\mathcal{B}}_{\pi(S)},\bm{\mathcal{A}_{T}} \right) }{ r(  \{\bm{\mathcal{A}}_S\}_{S \in F}) }
-\leq \sum_{T \in F} \frac{ d\left( \bm{\mathcal{B}}_{\pi(T)},\bm{\mathbf{A}}_{T} \right) }{ r( \{\bm{\mathcal{A}}_S\}_{S \in F}) }\nonumber \\
-&\leq \frac{|F| \varepsilon}{r( \{\bm{\mathcal{A}}_S\}_{S \in F})} 
+d(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}&, \bm{\mathcal{A}}_{\cap \mathcal{G}}  ) 
+\leq d\left( \cap_{S \in \mathcal{G}} \bm{\mathcal{B}}_{\pi(S)}, \cap_{S \in \mathcal{G}} \bm{\mathcal{A}}_S \right) \nonumber \\
+&\leq \sum_{T \in \mathcal{G}} \frac{ d\left( \cap_{S \in \mathcal{G}} \bm{\mathcal{B}}_{\pi(S)},\bm{\mathcal{A}_{T}} \right) }{ r(  \{\bm{\mathcal{A}}_S\}_{S \in \mathcal{G}}) }
+\leq \sum_{T \in \mathcal{G}} \frac{ d\left( \bm{\mathcal{B}}_{\pi(T)},\bm{\mathbf{A}}_{T} \right) }{ r( \{\bm{\mathcal{A}}_S\}_{S \in \mathcal{G}}) }\nonumber \\
+&\leq \frac{|\mathcal{G}| \varepsilon}{r( \{\bm{\mathcal{A}}_S\}_{S \in \mathcal{G}})} 
 \leq \frac{C_2 \varepsilon}{\max_i\|\mathbf{A}_i\|_2}. 
 \end{align}
-%
-where the third inequality follows from the definition of $d$ as a supremum.
+
 Since $\varepsilon < L_2(\mathbf{A}) / C_2$, by \eqref{delrho} the right-hand side in \eqref{randoml} is strictly less than one.
-Hence, $\dim(\text{\rm span}\{\mathbf{B}_{\cap \pi(F)}\}) \leq \dim(\text{\rm span}\{\mathbf{A}_{\cap F}\})$ by \eqref{dimLem}, and \eqref{cond} follows from the linear independence of the columns of $\mathbf{A}_{S}$ and $\mathbf{B}_{\pi(S)}$ for all $S \in F$.
+Hence, $\dim(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}) \leq \dim(\bm{\mathcal{A}}_{\cap \mathcal{G}})$ by \eqref{dimLem}, and \eqref{cond} follows from the linear independence of the columns of $\mathbf{A}_{S}$ and $\mathbf{B}_{\pi(S)}$ for all $S \in \mathcal{G}$.
 
-Now, by Lem.~\ref{NonEmptyLemma}, the association $i \mapsto \cap \pi(F(i))$ defines an injective map $\bar \pi: J \to [\bar m]$ for some $J \in {[m] \choose p}$ with $p$ given by \eqref{pcond}, and we can be sure that $\mathbf{B}_{\bar \pi(i)} \neq \mathbf{0}$ for all $i \in J$ since the columns of $\mathbf{B}_{\pi(S)}$ are linearly independent for all $S \in \mathcal{H}$.
-It then follows from \eqref{eqdim} and \eqref{randoml} that $d\left( \text{\rm span}\{\mathbf{A}_i\}, \text{\rm span}\{ \mathbf{B}_{\bar \pi(i)} \} \right) \leq C_2 \varepsilon / \max_i \|\mathbf{A}_i\|_2$ for all $i \in J$.
+Now, by Lem.~\ref{NonEmptyLemma}, the association $i \mapsto \cap \pi(h(i))$ defines an injective map $\bar \pi: J \to [\bar m]$ for some $J \in {[m] \choose p}$ with $p$ given by \eqref{pcond}, and we can be sure that $\mathbf{B}_{\bar \pi(i)} \neq \mathbf{0}$ for all $i \in J$ since the columns of $\mathbf{B}_{\pi(S)}$ are linearly independent for all $S \in \mathcal{H}$.
+It then follows from \eqref{eqdim} and \eqref{randoml} that $d\left( \bm{\mathcal{A}}_i, \bm{\mathcal{B}}_{\bar \pi(i)} \right) \leq C_2 \varepsilon / \max_i \|\mathbf{A}_i\|_2$ for all $i \in J$.
 Fixing $\bar \varepsilon = C_2\varepsilon$ and letting $c_i = \|\mathbf{A}_i\|_2^{-1}$, we thus have that for every basis vector $\mathbf{e}_i \in \mathbb{R}^m$ with $i \in J$ there exists some $\bar{c}_i \in \mathbb{R}$ such that $\|c_i\mathbf{A}\mathbf{e}_i - \bar{c}_i \mathbf{B}\mathbf{e}_{\bar \pi(i)}\|_2 \leq \bar \varepsilon < L_2(\mathbf{A}) \min_{i\in J} |c_i|$.

### 2017-07-31 manuscripts/PNAS/review/point_by_point_response.txt
responses

Reviewer Comments:

Reviewer #1:

Comments : 
SUMMARY OF THE PAPER

The paper finds conditions under which solutions for the sparse linear coding problem are unique. In sparse linear coding, one is given a matrix Y and the problem is to find a dictionary A and sparse coefficient matrix X such that Y=AX, up to a bounded uncertainty. This paper finds conditions under which A and X are unique up to scalings and permutation. Previous works looked at the noise-free case; this work considers the case of "noisy" measurements and proves a stability condition.

GENERAL COMMENTS

-----------------
Overall, while I think that the manuscript makes a solid contribution, I believe is better suited to a more specialized journal. Unlike many journals, PNAS gives a criterion for significance: that the paper be within the top 10% of publications and should be of interest to a general scientific audience. Without compelling evidence to the contrary from the authors, it seems to me that the submission does not rise to that level. 
-----------------

RESPONSE: We agree that the significance of our results and their relevance to the general scientific audience warrant a more compelling exposition in the manuscript. [Summarize high level major points in our cover here.  Also, mention we try to flesh this out in the next comment below.]

-----------------
Since the result is an extension of the noise-free result of [Hillar & Sommer (2015)] to a noisy case, the authors should provide better justification for the significance of contributions. 
-----------------

RESPONSE:

Our main result is not simply an extension of the noise-free result of [Hillar & Sommer (2015)] to the noisy case. Furthermore, our solution to Problem 2 is the first of its kind. See below.

-----------------
The main result seems to be based on an approach similar to [Hillar & Sommer (2015)], and there is little to no discussion of the computability and tightness of the sufficient condition for stability in the main results. Thus, the submission does not seem to be greatly more valuable than [Hillar & Sommer (2015)] and also not conclusive regarding the central problems of sparse linear coding and dictionary learning. That being said, the paper (with the modifications below) would certainly merit publication in very solid journal like IEEE Transactions on Information Theory, where it would be a median paper, in my opinion.  
-----------------

RESPONSE:

Mathy:

This is actually a significant applied mathematical result.  and is is not simply a generalization of the noise-free results.
we have significant brand new results, including Problem 2, the optimization formulation of the sparse coding problem, which is
the one of most interest to optimization theorist and practitioners of their methods. in the sense that we do generalize the noise-free
result, it is a significantly more difficult endeavor with noise, and our results in this regard provide more tools for 
scientists to understand the theoretical implications of their sparse liner coding setups. 
Moreover, it is a very clean and usable statement of theorems and results, with minimal possible assumptions.

Theorem 1 is Generalization, but our novel combinatorial proof techniques that give more powerful conclusions: 
reduction in number samples to determine model
full spark condition not needed
m'>m, 
in certain settings, polynomial amount of data to determine the model
mathematical domain for sparsity and combinatorics
we did the hard work of finding right tools for noisy dictionary learning theory, complete self-contained treatment.

computational aspects:
we add new material on computational complexity considerations, including fully polynomial result in certain cases.
all our constants are explicit
we are dealing with NP-hard situation, we should expect difficult -- in fact, the NP-hardness of dictionary learning with noise.
Tillman: the expert on this says that Problem 1's computational complexity 
https://arxiv.org/pdf/1405.6664.pdf
Maybe we can solve Tillman's problem

The remaining very difficult problem is determining the smallest number of samples that determine the model.
but we think we have made progress on this and brought non-trivial, but elegant, tools to bear on the problem.

Sciency

Occam's razor -- Problem 1, basic move in lots of data science
"dictionary learning" (278,000), dictionary learning (154,000,000)
the central (NP-Hard) problem of dictionary learning approximated using L1-optimization.  "all interesting problems are NP-hard".
in fact, there has never been an experiment with zero noise, so the results of [Hillar Sommer] affect zero scientists.
new theorem on optimization formulation of the result -- that's how scientists approach their data
completes the theory of NIPS ACS making viable actual result in theory of mind -- theories have to be resilient to noise or their nothing
applies to thousands of scientific algorithmic theory of sparse linear coding -- removes one step for them to write algorithm papers
universals in perception -- with noise (as all datasets have noise) lends further understanding to the basic problem of universal coding from sensors to cortex.
applied optimization theory: Hadamard well-posed, sparse linear coding with learning has a natural consistency, versus Deep Learning non-uniqueness of models. big win for sparse coding as a model: theoretical grounding for what you are doing.

-----------------
DETAILED COMMENTS

-- The paper does a good job of motivating the general problem of sparse coding to a general audience. In particular, there is a good review of the areas in which dictionary learning arises.

-- I think the biggest potential issue for publication in PNAS is that the significance of the result needs more discussion. Specifically, the authors could address why going from the noise-free case to the noisy case is not incremental. PNAS specifically targets submissions that go beyond what could be published in a more specialized journal. Could the authors, for example, contrast the proof technique between the noisy and noise-free cases? Or, perhaps, the practical implications? 
-----------------

RESPONSE: (first of all, it's not incremental) measure zero versus full measure hello.  moreover, many other results, including m'>m, ....

-----------------
-- A second general problem was that it was difficult for me to understand the theorem conditions and sample complexity. For example, in Theorem 1, I think you meant to say:

Let A satisfy eqn [2], x_1,...,x_N be a set of k-sparse vectors, and E \subseteq \choose{[m],k}, and \bar{m} be given and satisfy the following property:

For every S \in E, there exists a subset of x_1,...,x_N of at least size (k-1)\choose{\bar{m},k} with support in S. Moreover, any k vectors in this subset are linearly independent.

Is this what you meant? 
-----------------

RESPONSE: Yes, thank you for helping us to clarify our statements. We have updated the manuscript to reflect this.

-----------------
-- Related point: Is there a condition on \ell in Theorem 1? 
-----------------

RESPONSE: Yes, thanks for this question. We have made the statement more clear to reflect the relationship between m' and l.

-----------------
-- The paper could also compare the sample complexity results on N with those given in the noise-free case. For example, Table I in reference (18) gives a comparison of sample complexity requirements for different conditions in the noise-free case. Where would the results of this paper stand in that table?

-- Otherwise, all the math seemed correct. 
-----------------

RESPONSE: We appreciate this question and have added comparison discussion (all numbers improve in this work). Many thanks for your careful review of the mathematics. We have tried and continue to try to be as clear, concise, and correct as we possibly can to elevate this work into the top echelon of applied mathematical theory papers.

-----------------
Reviewer #2:

Comments : 
The paper presents an extension of existing conditions for uniqueness of the existence of a sparsity-inducing dictionary for a given set of data vectors that depends on the sampling of the resulting data subspaces. The extension considers the stability of dictionary learning in terms of the degree of variability present in distinct, feasible sparsity dictionary representations for the data under a constraint on the representation accuracy. A similar condition on the sampling of the underlying subspaces is obtained.

The paper's writing and composition is clear (with an exception detailed below), concise, and relevant to the topic. The analytical work appears to be correct to the best of my understanding, and the paper's combined use of several results in the literature to extend an existing dictionary learning uniqueness condition to a new dictionary learning stability condition appears to be original.

Some questions that remain and may be worth discussing deal with the practical impact of these results. When is it possible to determine (numerically) if enough data has been gathered to obtain an accurate estimate of the underlying sparsity dictionary? Are the conditions and constants/metrics provided in this paper feasible to compute? Is there any new intuition to be had regarding the necessary sampling of the union of subspaces from this analysis (with respect to the intuition obtained from existing uniqueness results)? In these terms, it is also unclear to me if a theoretical extension of the uniqueness results to the stability results merit publication in PNAS given the "top 10%" and "sufficient general interest" requirements for publication. It definitely is deserving of publication in a specialty journal.

The work presented is analytical and does not rely on data validation.

In the paragraph "Since f is an analytic function..." (page 3) it is argued that a specific construction of a suitable matrix implies that "almost every real nxm matrix... satisfies Eq. (2)". This appears to overstate the result, in my opinion - can the authors elaborate on why "almost every real matrix" can be obtained from this construction based on a Vandermonde matrix with additional zero rows?

Some typos appear in Eq. (24), closing } missing from the denominators of the second and third inequalities. Additionally, it was not clear to me how B_{pi(S)} change to B_{pi(T)}.

*********************

PUBLICATION INFORMATION

High resolution files are required for figures that will appear in the main text of the article and must be uploaded with the final version of your manuscript. Resolution of at least 1200 dpi is needed for all line art, 600 dpi for images that combine line art with photographs/halftones, and 300 dpi for color or grayscale photographic images. Please review the PNAS digital art guidelines.

Authors are invited to submit scientifically interesting and visually arresting cover illustrations (see the PNAS cover archive. Cover images must be original, and exclusive rights to publish will convey to PNAS. Cover images may be used in promotional materials, including but not limited to brochures, advertisements, and posters. Cover submissions should include a brief lay-language caption (50-60 words), credit information (e.g., photograph courtesy of...), and the manuscript number, author name, phone, and email. Images should be 21.5 cm wide by 22.5 cm high. Files should be .eps or .tif and in RGB (red, green, blue) color mode. Please submit electronic files with your revised manuscript in the PNAS online submission system or to PNASCovers@nas.edu as soon as possible. If you cannot submit electronic files, or if your files are too large to email, contact the PNAS office. See the Information for Authors for details. Covers are selected from papers that have been assigned to an issue, after authors have returned proofs.

### 2017-08-02 manuscripts/PNAS/review/point_by_point_response.txt
pt by pt response

@@
-Reviewer Comments:
-
-Reviewer #1:
-
-Comments : 
-SUMMARY OF THE PAPER
-
-The paper finds conditions under which solutions for the sparse linear coding problem are unique.
-In sparse linear coding, one is given a matrix Y and the problem is to find a dictionary A and sparse coefficient matrix X such that Y=AX, up to a bounded uncertainty.
-This paper finds conditions under which A and X are unique up to scalings and permutation.
-Previous works looked at the noise-free case; this work considers the case of "noisy" measurements and proves a stability condition.
-
-GENERAL COMMENTS
-
------------------
-Overall, while I think that the manuscript makes a solid contribution, I believe is better suited to a more specialized journal.
-Unlike many journals, PNAS gives a criterion for significance: that the paper be within the top 10% of publications and should be of interest to a general scientific audience.
-Without compelling evidence to the contrary from the authors, it seems to me that the submission does not rise to that level.
------------------
-
-RESPONSE: We agree that the significance of our results and their relevance to the general scientific audience warrant a more compelling exposition in the manuscript.
-[Summarize high level major points in our cover here.
-Also, mention we try to flesh this out in the next comment below.]
-
------------------
-Since the result is an extension of the noise-free result of [Hillar & Sommer (2015)] to a noisy case, the authors should provide better justification for the significance of contributions. 
------------------
-
-RESPONSE:
-
-Our main result is not simply an extension of the noise-free result of [Hillar & Sommer (2015)] to the noisy case. Furthermore, our solution to Problem 2 is the first of its kind. See below.
-
------------------
-The main result seems to be based on an approach similar to [Hillar & Sommer (2015)], and there is little to no discussion of the computability and tightness of the sufficient condition for stability in the main results.
-Thus, the submission does not seem to be greatly more valuable than [Hillar & Sommer (2015)] and also not conclusive regarding the central problems of sparse linear coding and dictionary learning.
-That being said, the paper (with the modifications below) would certainly merit publication in very solid journal like IEEE Transactions on Information Theory, where it would be a median paper, in my opinion.
------------------
-
-RESPONSE:
-
+*** NOTES ***
 Mathy:
@@
 big win for sparse coding as a model: theoretical grounding for what you are doing.
+*** ***
+
+Reviewer Comments:
+
+Reviewer #1:
+
+Comments : 
+SUMMARY OF THE PAPER
+
+The paper finds conditions under which solutions for the sparse linear coding problem are unique.
+In sparse linear coding, one is given a matrix Y and the problem is to find a dictionary A and sparse coefficient matrix X such that Y=AX, up to a bounded uncertainty.
+This paper finds conditions under which A and X are unique up to scalings and permutation.
+Previous works looked at the noise-free case; this work considers the case of "noisy" measurements and proves a stability condition.
+
+GENERAL COMMENTS
+
+-----------------
+Overall, while I think that the manuscript makes a solid contribution, I believe is better suited to a more specialized journal.
+Unlike many journals, PNAS gives a criterion for significance: that the paper be within the top 10% of publications and should be of interest to a general scientific audience.
+Without compelling evidence to the contrary from the authors, it seems to me that the submission does not rise to that level.
+-----------------
+
+RESPONSE: We have included in our revised manuscript a more compelling exposition of the significance of our results and their relevance to the general scientific audience, and thank the editor for the opportunity to address this concern shared by both reviewers.
+[Summarize high level major points in our cover here.
+Also, mention we try to flesh this out in the next comment below.]
+
+-----------------	
+Since the result is an extension of the noise-free result of [Hillar & Sommer (2015)] to a noisy case, the authors should provide better justification for the significance of contributions.
+The main result seems to be based on an approach similar to [Hillar & Sommer (2015)], and there is little to no discussion of the computability and tightness of the sufficient condition for stability in the main results.
+Thus, the submission does not seem to be greatly more valuable than [Hillar & Sommer (2015)] and also not conclusive regarding the central problems of sparse linear coding and dictionary learning.
+That being said, the paper (with the modifications below) would certainly merit publication in very solid journal like IEEE Transactions on Information Theory, where it would be a median paper, in my opinion.
+-----------------
+
+RESPONSE:
+
+We agree with the reviewer that an extension of the noise-free result of [Hillar & Sommer (2015)] to the noisy case — while a significant, non-incremental advancement in applied mathematics with actual practical implications — would not necessarily merit publication in PNAS on its own.
+It seems to us, however, that the reviewer may not have noticed that our main result in fact generalizes the noise-free result of [Hillar & Sommer (2015)] far beyond a straight-forward extension to the noisy case in ways which have provided valuable insight into the dictionary learning model, and that a significant deviation in approach was necessary to prove these new facts.
+Furthermore, our solution (Cor.
+2) to the optimization formulation of the dictionary learning problem (Prob.
+2) — that of most interest to optimization theorists and practitioners of their methods — is a significant result that is, to our knowledge, the first result of its kind in both the noise-free and noisy domains.
+We discuss all of these points in our response to the reviewer’s more detailed comments.
+
+As per the reviewer’s request, we have included in the updated manuscript a discussion of the computability of sufficient conditions for recovery (they are, indeed, computable).
+While we admit the manuscript is not *conclusive* regarding the central problems of sparse linear coding and dictionary learning (i.e.
+we have not provided tightness conditions, as the reviewer has pointed out), we believe we have uncovered the fundamental underlying combinatorial structure at play, that being the intersection semi-lattice of a hyper-graph and its transformation under the map \pi.
 
@@
 
-RESPONSE: (first of all, it's not incremental) measure zero versus full measure hello.  moreover, many other results, including m'>m, ....
+RESPONSE:
+
+With all due respect to the reviewer, we believe the practical implication of a noisy result over a noiseless result is plainly evident: never has there been an experiment without noise and an unstable model is therefore useless in practice.
+It seems to us that the reviewer’s fundamental concern is that our proof may amount to too straight-forward of an extension of the approach taken in [Hillar & Sommer (2015)] to satisfy the criterion for publication in PNAS.
+We believe this concern stems from two misconceptions the reviewer seems to have: that our main result is merely an extension of that in [Hillar & Sommer (2015)] to the noisy case, and that our proof technique is merely an incremental tweak on the approach taken in [Hillar & Sommer (2015)].
+
+It is understandable from the presentation of our proof of Thm.
+1 that our approach appears on the surface to be a straight-forward extension of the approach taken in [Hillar & Sommer (2015)].
+As observed by our second reviewer, however, the extension to noise did indeed require an original combination of several results in the literature.
+Beyond the modifications required for this extension, our proof of (Thm.
+1) differs from the approach taken by [Hillar & Sommer (2015)] in a key way tucked into the proof of our Main Lemma — more specifically, with the addition of Lemma 5.
+[More detail on what goes down in Lemma 5?] We have updated the manuscript to make the reader aware of this.
+To be clear, this new combinatorial perspective we take on the problem has so-far yielded the following powerful new conclusions.
+
+1) A significant reduction in sample complexity: To identify the n x m generating dictionary A, [Hillar & Sommer (2015)] require that data be sampled from *every* k-dimensional subspace spanned by the m columns of A (that is, {m \choose k} subspaces in total).
+We show that the data need only be sampled from m subspaces in total (e.g.
+those supported by consecutive intervals of length k in some cyclic order on [m]) and in some cases as few as 2\sqrt{m} (e.g.
+when m = k^2, take the supports to be the rows and columns of [m] arranged in a square grid).
+
+2) An extension to the case where the number of dictionary elements is unknown: The results of [Hillar & Sommer (2015)] only apply to the case where the matrix B has the same number of columns as A.
+We forgo this assumption and show that B must have at least as many columns as A and contains (up to noise) a subset of the columns of A.
+The size of this subset depends on a simple relation between the number of columns of B and the regularity of the support-set hypergraph.
+
+3) No spark condition requirement for the generating matrix A: One of the mathematically significant contributions made by [Hillar & Sommer (2015)] was to forgo the constraint that the recovery matrix B also satisfy the spark condition, in contrast to all previously known uniqueness results which (either explicitly or implicitly) made this assumption.
+Our proof is powerful enough to show that, in fact, even the matrix A need not satisfy the spark condition to be identifiable!
+Rather, it need only be injective on the union of subspaces with supports that form sets in a hypergraph satisfying the SIP.
+We had omitted this point in our original submission of the manuscript to keep things simple, but have decided to include this interesting fact in our resubmission given that a recently approved NSF grant _____ makes use of this fact in its description of methods.
+This also required us to redefine the restricted matrix lower bound L to be in terms of a hypergraph, which is an interesting object for further study in its own right.
+
+[4) Implications for the computational complexity of the dictionary learning problem.
+If the size of the support set of reconstructing codes is polynomial in m,k then the pigeonholing argument in the proof of Thm.
+1 requires only a polynomial number of samples distributed over a polynomial number of supports; thus N is polynomial in m, k.
+[Chris?] This point was only hinted at in the Discussion section of our original submission, but we have included it in the updated manuscript to make clear the power of our approach over that taken in [Hillar & Sommer (2015)].
+
+We also wish to reiterate that our solution to Problem 2, that of most interest to practitioners of dictionary learning methods, is the first of its kind in both the noise-free and noisy domains.
+This seems to not have been clearly communicated in the Discussion section of our submitted manuscript, which begins: “In this note, we generalized the approach of (18) to prove the stability of unique solutions to Probs.
+1 and 2 while significantly reducing the known sample complexity.” We have revised our re-submitted manuscript to make it clear that a solution to Problem 2 has never been supplied before in the literature until now [right?].
 
@@
 
-RESPONSE: Yes, thank you for helping us to clarify our statements. We have updated the manuscript to reflect this.
+RESPONSE: Yes, though actually for every S \in E there are *more than* (k-1)\choose{\bar{m},k} vectors with support in S (not “at least”).
+Thank you for helping us to clarify our statements.
+We have updated the manuscript to make these conditions unambiguous.
 
@@
 
-RESPONSE: Yes, thanks for this question. We have made the statement more clear to reflect the relationship between m' and l.
+RESPONSE: Yes, thanks for this question.
+The condition on \ell is perhaps best understood as a condition on \bar m not being too large (given \ell) in order to guarantee the recovery of at least one dictionary element.
+We have updated the manuscript to reflect this, and the condition now reads “provided \bar m < \ell m / (\ell - 1)” where previously it read “provided p = \bar m − \ell( \bar m − m )$ is positive”.
 
@@
 
-RESPONSE: We appreciate this question and have added comparison discussion (all numbers improve in this work).
+RESPONSE: We appreciate this question and have added a discussion of this comparison to the manuscript (all sample complexities improve in this work) [DO THIS].
 Many thanks for your careful review of the mathematics.
@@
 -----------------
+
 Reviewer #2:
@@
 Some questions that remain and may be worth discussing deal with the practical impact of these results.
+
+-----------------
 When is it possible to determine (numerically) if enough data has been gathered to obtain an accurate estimate of the underlying sparsity dictionary? 
+-----------------
+
+RESPONSE: What we have discovered is that there exists a procedure by which one may check a proposed solution to determine its uniqueness. [TODO]
+
+-----------------
 Are the conditions and constants/metrics provided in this paper feasible to compute?
+-----------------
+
+RESPONSE: We have determined explicit forms for the constants in Theorem 1. [Are they feasible to compute..?]
+
+-----------------
 Is there any new intuition to be had regarding the necessary sampling of the union of subspaces from this analysis (with respect to the intuition obtained from existing uniqueness results)?
+-----------------
+
+RESPONSE: Yes, there is indeed.
+While all existing uniqueness results require a sufficient number of samples be drawn from *each* of {m \choose k} possible supports, we have shown that in fact it is enough that a sufficient number of samples be drawn from every support in a subset of drastically smaller size, provided this subset forms a regular hypergraph satisfying the singleton intersection property.
+As was pointed out in our manuscript, a support set of size m satisfying these criteria can always be constructed for any k < m (e.g.
+take the consecutive intervals of length k in some cyclic order on [m]), and in certain cases such a set can be constructed from as few as 2\sqrt(m) supports (e.g.
+when m = k^2, take the supports to be the rows and columns of [m] arranged in a square grid).
+
+-----------------
 In these terms, it is also unclear to me if a theoretical extension of the uniqueness results to the stability results merit publication in PNAS given the "top 10%" and "sufficient general interest" requirements for publication.
@@
 The work presented is analytical and does not rely on data validation. 
+-----------------
 
+RESPONSE: See our response to the first reviewer’s identical concern. It seems both reviewers haven’t noticed that our results generalize far beyond a straight-forward extension to the noisy case.
+
+-----------------
 In the paragraph "Since f is an analytic function..." (page 3) it is argued that a specific construction of a suitable matrix implies that "almost every real nxm matrix...
@@
 This appears to overstate the result, in my opinion - can the authors elaborate on why "almost every real matrix" can be obtained from this construction based on a Vandermonde matrix with additional zero rows?
+-----------------
 
+RESPONSE: The point we make here is not that almost every real matrix satisfying Eq.
+(2) can be obtained from the construction we provide; rather, the point is that almost every matrix satisfies Eq.
+(2) because at least one matrix does (e.g.
+our construction) and therefore, since f is analytic, the set of all those that don’t satisfy the condition has measure zero.
+
+-----------------
 Some typos appear in Eq. (24), closing } missing from the denominators of the second and third inequalities. Additionally, it was not clear to me how B_{pi(S)} change to B_{pi(T)}. 
+-----------------
+
+RESPONSE: Thank you for pointing out this typo in the second and third inequalities of Eq.
+(24).
+We have also clarified in our resubmission how it is B_{pi(S)} changes to B_{pi(T)} (it is because d(U, V) \leq d(U’,V) whenever U \subseteq U’).
+
+-----------------
 

### 2017-08-02 manuscripts/PNAS/review/point_by_point_response.txt
pt by pt response

@@
 
-We agree with the reviewer that an extension of the noise-free result of [Hillar & Sommer (2015)] to the noisy case — while a significant, non-incremental advancement in applied mathematics with actual practical implications — would not necessarily merit publication in PNAS on its own.
-It seems to us, however, that the reviewer may not have noticed that our main result in fact generalizes the noise-free result of [Hillar & Sommer (2015)] far beyond a straight-forward extension to the noisy case in ways which have provided valuable insight into the dictionary learning model, and that a significant deviation in approach was necessary to prove these new facts.
-Furthermore, our solution (Cor.
+We agree with the reviewer that a straight-forward extension of the noise-free result of [Hillar & Sommer (2015)] to the noisy case — while a significant, non-incremental advancement in applied mathematics with actual practical implications — would not necessarily merit publication in PNAS on its own.
+It seems to us, however, that the reviewer may not have noticed that our main result in fact generalizes the noise-free result of [Hillar & Sommer (2015)] far beyond a simple extension to the noisy case in ways which have provided valuable insight into the dictionary learning model, and that a significant deviation in approach was necessary to prove these new facts.
+Moreover, our solution (Cor.
 2) to the optimization formulation of the dictionary learning problem (Prob.
-2) — that of most interest to optimization theorists and practitioners of their methods — is a significant result that is, to our knowledge, the first result of its kind in both the noise-free and noisy domains.
-We discuss all of these points in our response to the reviewer’s more detailed comments.
+2) — that of most interest to optimization theorists and practitioners of their methods — is a significant result that is, to our knowledge, the first of its kind in both the noise-free and noisy domains.
+We discuss all of these points below in our response to the reviewer’s more detailed comments.
 
-As per the reviewer’s request, we have included in the updated manuscript a discussion of the computability of sufficient conditions for recovery (they are, indeed, computable).
-While we admit the manuscript is not *conclusive* regarding the central problems of sparse linear coding and dictionary learning (i.e.
-we have not provided tightness conditions, as the reviewer has pointed out), we believe we have uncovered the fundamental underlying combinatorial structure at play, that being the intersection semi-lattice of a hyper-graph and its transformation under the map \pi.
+The reviewer has pointed out that the manuscript is not *conclusive* regarding the central problems of sparse linear coding and dictionary learning.
+While this may be so, we believe we have uncovered the fundamental underlying combinatorial structure at play (i.e.
+the intersection semi-lattice of a hyper-graph and its transformation under the map \pi) and that our sample complexity N is on the order of the tightest possible given our lack of any additional assumptions at all on the reproducing matrix B and codes \tilde x_i.
+As per the reviewer’s request, we have updated the manuscript to include a discussion of the computability of sufficient conditions for recovery (they are, indeed, computable).
 
@@
 It seems to us that the reviewer’s fundamental concern is that our proof may amount to too straight-forward of an extension of the approach taken in [Hillar & Sommer (2015)] to satisfy the criterion for publication in PNAS.
-We believe this concern stems from two misconceptions the reviewer seems to have: that our main result is merely an extension of that in [Hillar & Sommer (2015)] to the noisy case, and that our proof technique is merely an incremental tweak on the approach taken in [Hillar & Sommer (2015)].
+We believe this concern stems from two misconceptions the reviewer seems to have: that our main result is merely an extension of that in [Hillar & Sommer (2015)] to the noisy case, and that our proof technique is only an incremental tweak on the approach taken in [Hillar & Sommer (2015)].
 

### 2017-08-02 manuscripts/PNAS/review/point_by_point_response.txt
point_by_point_response.txt

@@
 
-With all due respect to the reviewer, we believe the practical implication of a noisy result over a noiseless result is plainly evident: never has there been an experiment without noise and an unstable model is therefore useless in practice.
-It seems to us that the reviewer’s fundamental concern is that our proof may amount to too straight-forward of an extension of the approach taken in [Hillar & Sommer (2015)] to satisfy the criterion for publication in PNAS.
-We believe this concern stems from two misconceptions the reviewer seems to have: that our main result is merely an extension of that in [Hillar & Sommer (2015)] to the noisy case, and that our proof technique is only an incremental tweak on the approach taken in [Hillar & Sommer (2015)].
+With all due respect to the reviewer, we believe the practical implications of a noisy result over a noiseless result are plainly evident: never has there been an experiment without noise and an unstable model is therefore useless in practice.
+It seems to us that the reviewer’s fundamental concern is more likely that our proof may amount to too straight-forward of an extension of the approach taken in [Hillar & Sommer (2015)] to satisfy the criterion for publication in PNAS.
+We believe this concern stems from two misconceptions the reviewer seems to us to have: that our main result (Thm.
+1) is merely an extension of that in [Hillar & Sommer (2015)] to the noisy case, and that our proof technique is only an incremental tweak on the approach taken in [Hillar & Sommer (2015)].
 
-It is understandable from the presentation of our proof of Thm.
-1 that our approach appears on the surface to be a straight-forward extension of the approach taken in [Hillar & Sommer (2015)].
-As observed by our second reviewer, however, the extension to noise did indeed require an original combination of several results in the literature.
-Beyond the modifications required for this extension, our proof of (Thm.
-1) differs from the approach taken by [Hillar & Sommer (2015)] in a key way tucked into the proof of our Main Lemma — more specifically, with the addition of Lemma 5.
-[More detail on what goes down in Lemma 5?] We have updated the manuscript to make the reader aware of this.
-To be clear, this new combinatorial perspective we take on the problem has so-far yielded the following powerful new conclusions.
+It is understandable from the presentation of our proof of our main result (Thm.
+1) that our approach appears on the surface to be a straight-forward extension of that taken in [Hillar & Sommer (2015)].
+As observed by our second reviewer, however, the extension to the noisy case did indeed require an original combination of several results in the literature.
+Aside from these required modifications, our proof of (Thm.
+1) differs from the approach taken by [Hillar & Sommer (2015)] in a key way that is tucked into the proof of our Main Lemma — more specifically, by the addition of Lemma 5.
+[More detail on what goes down in Lemma 5?] We have updated the manuscript to make the reader more keenly aware of this.
+To be clear, this new combinatorial perspective we take on the problem yields the following powerful new conclusions beyond those in [Hillar & Sommer (2015)].
 
@@
 1 requires only a polynomial number of samples distributed over a polynomial number of supports; thus N is polynomial in m, k.
-[Chris?] This point was only hinted at in the Discussion section of our original submission, but we have included it in the updated manuscript to make clear the power of our approach over that taken in [Hillar & Sommer (2015)].
+[Chris?
+How does this have implications..?] This point was only hinted at in the Discussion section of our original submission, but we have included it in the updated manuscript to make clear the power of our approach over that taken in [Hillar & Sommer (2015)].
 
@@
 Thank you for helping us to clarify our statements.
-We have updated the manuscript to make these conditions unambiguous.
+We have updated the manuscript to disambiguate these conditions.
 
@@
 
-RESPONSE: See our response to the first reviewer’s identical concern. It seems both reviewers haven’t noticed that our results generalize far beyond a straight-forward extension to the noisy case.
+RESPONSE: We have addressed this concern in our response to the first reviewer’s identical comment.
+It seems both reviewers haven’t noticed that our results generalize the results of [Hillar & Sommer (2015)] far beyond a straight-forward extension to the noisy case.
 
@@
 RESPONSE: The point we make here is not that almost every real matrix satisfying Eq.
-(2) can be obtained from the construction we provide; rather, the point is that almost every matrix satisfies Eq.
+(2) can be obtained from the construction based on a Vandermonde matrix which we provide; rather, the point is that almost every matrix satisfies Eq.
 (2) because at least one matrix does (e.g.
 our construction) and therefore, since f is analytic, the set of all those that don’t satisfy the condition has measure zero.
+We have updated the manuscript to make this argument more clear.
 
@@
 (24).
-We have also clarified in our resubmission how it is B_{pi(S)} changes to B_{pi(T)} (it is because d(U, V) \leq d(U’,V) whenever U \subseteq U’).
+We have also clarified in our resubmission how it is that B_{pi(S)} can be replaced with B_{pi(T)} (it is because d(U, V) \leq d(U’,V) whenever U \subseteq U’).
 

### 2017-08-03 manuscripts/PNAS/review/point_by_point_response.txt
point_by_point_response.txt

@@
 
-We agree with the reviewer that a straight-forward extension of the noise-free result of [Hillar & Sommer (2015)] to the noisy case — while a significant, non-incremental advancement in applied mathematics with actual practical implications — would not necessarily merit publication in PNAS on its own.
-It seems to us, however, that the reviewer may not have noticed that our main result in fact generalizes the noise-free result of [Hillar & Sommer (2015)] far beyond a simple extension to the noisy case in ways which have provided valuable insight into the dictionary learning model, and that a significant deviation in approach was necessary to prove these new facts.
+We agree with the reviewer that a straight-forward extension of the noise-free result of [Hillar & Sommer (2015)] to the noisy case — while still a significant advancement in applied mathematics with actual practical implications — would not necessarily merit publication in PNAS on its own.
+It seems to us, however, that the reviewer hasn’t noticed that our main result in fact generalizes the noise-free result of [Hillar & Sommer (2015)] far beyond a simple extension to the noisy case in ways which provide greatly more valuable insight into the dictionary learning model, and that a significant deviation from their approach was necessary to prove these new facts.
 Moreover, our solution (Cor.
@@
 2) — that of most interest to optimization theorists and practitioners of their methods — is a significant result that is, to our knowledge, the first of its kind in both the noise-free and noisy domains.
-We discuss all of these points below in our response to the reviewer’s more detailed comments.
+We discuss all of these points below in our response to the reviewer’s “detailed comments”.
 
-The reviewer has pointed out that the manuscript is not *conclusive* regarding the central problems of sparse linear coding and dictionary learning.
-While this may be so, we believe we have uncovered the fundamental underlying combinatorial structure at play (i.e.
-the intersection semi-lattice of a hyper-graph and its transformation under the map \pi) and that our sample complexity N is on the order of the tightest possible given our lack of any additional assumptions at all on the reproducing matrix B and codes \tilde x_i.
-As per the reviewer’s request, we have updated the manuscript to include a discussion of the computability of sufficient conditions for recovery (they are, indeed, computable).
+Before moving on to our response to the detailed comments, we address briefly the issues of computability and tightness raised by the reviewer.
+The sufficient conditions for recovery are indeed computable and we have updated the manuscript to include a discussion of this fact.
+It is true, however, that we have not proven the tightness of these conditions and the manuscript is therefore not *conclusive* regarding the central problems of sparse linear coding.
+We believe that the fundamental characteristics of our results will likely remain unchanged upon any further tightening, and have opted instead to include in our revised manuscript a discussion of where such improvements would come from (e.g.
+a tightening of Lemma 4).
+Regarding the sample complexity N, we believe that we have uncovered the fundamental underlying combinatorial structure at play (i.e.
+the intersection semi-lattice of a hyper-graph and its transformation under the map \pi) and that our N is on the order of the tightest possible given a lack of any additional assumptions at all on the reproducing matrix B and codes \tilde x_i.
 
@@
 It seems to us that the reviewer’s fundamental concern is more likely that our proof may amount to too straight-forward of an extension of the approach taken in [Hillar & Sommer (2015)] to satisfy the criterion for publication in PNAS.
-We believe this concern stems from two misconceptions the reviewer seems to us to have: that our main result (Thm.
+We believe this concern stems from two misconceptions of the reviewer: that our main result (Thm.
 1) is merely an extension of that in [Hillar & Sommer (2015)] to the noisy case, and that our proof technique is only an incremental tweak on the approach taken in [Hillar & Sommer (2015)].
@@
 [More detail on what goes down in Lemma 5?] We have updated the manuscript to make the reader more keenly aware of this.
-To be clear, this new combinatorial perspective we take on the problem yields the following powerful new conclusions beyond those in [Hillar & Sommer (2015)].
+To be clear, the perspective we take on the problem yields the following powerful new conclusions beyond those from [Hillar & Sommer (2015)]:
 
@@
 
-[4) Implications for the computational complexity of the dictionary learning problem.
-If the size of the support set of reconstructing codes is polynomial in m,k then the pigeonholing argument in the proof of Thm.
+[4) Implications for the computational complexity of the dictionary learning problem: If the size of the support set of reconstructing codes is polynomial in m,k then the pigeonholing argument in the proof of Thm.
 1 requires only a polynomial number of samples distributed over a polynomial number of supports; thus N is polynomial in m, k.
@@
 We also wish to reiterate that our solution to Problem 2, that of most interest to practitioners of dictionary learning methods, is the first of its kind in both the noise-free and noisy domains.
-This seems to not have been clearly communicated in the Discussion section of our submitted manuscript, which begins: “In this note, we generalized the approach of (18) to prove the stability of unique solutions to Probs.
+We recognize that this was not clearly communicated in the Discussion section of our submitted manuscript, which begins: “In this note, we generalized the approach of (18) to prove the stability of unique solutions to Probs.
 1 and 2 while significantly reducing the known sample complexity.” We have revised our re-submitted manuscript to make it clear that a solution to Problem 2 has never been supplied before in the literature until now [right?].

### 2017-08-03 manuscripts/PNAS/review/point_by_point_response.txt
simple start to cover

@@
-*** NOTES ***
-Mathy:
-
-This is actually a significant applied mathematical result.  and is is not simply a generalization of the noise-free results.
-we have significant brand new results, including Problem 2, the optimization formulation of the sparse coding problem, which is
-the one of most interest to optimization theorist and practitioners of their methods. in the sense that we do generalize the noise-free
-result, it is a significantly more difficult endeavor with noise, and our results in this regard provide more tools for 
-scientists to understand the theoretical implications of their sparse liner coding setups. 
-Moreover, it is a very clean and usable statement of theorems and results, with minimal possible assumptions.
-
-Theorem 1 is Generalization, but our novel combinatorial proof techniques that give more powerful conclusions: 
-reduction in number samples to determine model
-full spark condition not needed
-m'>m, 
-in certain settings, polynomial amount of data to determine the model
-mathematical domain for sparsity and combinatorics
-we did the hard work of finding right tools for noisy dictionary learning theory, complete self-contained treatment.
-
-computational aspects:
-we add new material on computational complexity considerations, including fully polynomial result in certain cases.
-all our constants are explicit
-we are dealing with NP-hard situation, we should expect difficult -- in fact, the NP-hardness of dictionary learning with noise.
-Tillman: the expert on this says that Problem 1's computational complexity 
-https://arxiv.org/pdf/1405.6664.pdf
-Maybe we can solve Tillman's problem
-
-The remaining very difficult problem is determining the smallest number of samples that determine the model.
-but we think we have made progress on this and brought non-trivial, but elegant, tools to bear on the problem.
-
-Sciency
-
-Occam's razor -- Problem 1, basic move in lots of data science
-"dictionary learning" (278,000), dictionary learning (154,000,000)
-the central (NP-Hard) problem of dictionary learning approximated using L1-optimization.  "all interesting problems are NP-hard".
-in fact, there has never been an experiment with zero noise, so the results of [Hillar Sommer] affect zero scientists.
-new theorem on optimization formulation of the result -- that's how scientists approach their data
-completes the theory of NIPS ACS making viable actual result in theory of mind -- theories have to be resilient to noise or their nothing
-applies to thousands of scientific algorithmic theory of sparse linear coding -- removes one step for them to write algorithm papers
-universals in perception -- with noise (as all datasets have noise) lends further understanding to the basic problem of universal coding from sensors to cortex.
-applied optimization theory: Hadamard well-posed, sparse linear coding with learning has a natural consistency, versus Deep Learning non-uniqueness of models.
-big win for sparse coding as a model: theoretical grounding for what you are doing.
-*** ***
-
+-----------------
 Reviewer Comments:
@@
 
------------------
 Overall, while I think that the manuscript makes a solid contribution, I believe is better suited to a more specialized journal.
@@
 -----------------
-
 Reviewer #2:
@@
 
------------------
 When is it possible to determine (numerically) if enough data has been gathered to obtain an accurate estimate of the underlying sparsity dictionary? 
@@
 We have also clarified in our resubmission how it is that B_{pi(S)} can be replaced with B_{pi(T)} (it is because d(U, V) \leq d(U’,V) whenever U \subseteq U’).
-
------------------
-
-*********************
-
-PUBLICATION INFORMATION
-
-High resolution files are required for figures that will appear in the main text of the article and must be uploaded with the final version of your manuscript.
-Resolution of at least 1200 dpi is needed for all line art, 600 dpi for images that combine line art with photographs/halftones, and 300 dpi for color or grayscale photographic images.
-Please review the PNAS digital art guidelines.
-
-Authors are invited to submit scientifically interesting and visually arresting cover illustrations (see the PNAS cover archive.
-Cover images must be original, and exclusive rights to publish will convey to PNAS.
-Cover images may be used in promotional materials, including but not limited to brochures, advertisements, and posters.
-Cover submissions should include a brief lay-language caption (50-60 words), credit information (e.g., photograph courtesy of...), and the manuscript number, author name, phone, and email.
-Images should be 21.5 cm wide by 22.5 cm high.
-Files should be .eps or .tif and in RGB (red, green, blue) color mode.
-Please submit electronic files with your revised manuscript in the PNAS online submission system or to PNASCovers@nas.edu as soon as possible.
-If you cannot submit electronic files, or if your files are too large to email, contact the PNAS office.
-See the Information for Authors for details.
-Covers are selected from papers that have been assigned to an issue, after authors have returned proofs.

### 2017-08-03 manuscripts/PNAS/chazthm_pnas.tex
more cover, added ganguli ref main txt

@@
 \end{align}
-%
+
 which would be, in any case, necessary for uniqueness. Our concern here is solution stability with respect to noise.
@@
 \end{align*}
-%
+
 then there is some permutation matrix $\mathbf{P}$ and invertible diagonal matrix $\mathbf{D}$ such that for all $i, j$:
@@
 Our results suggest that this correspondence could be due to the ``universality'' of sparse representations in natural data, an early mathematical idea in neural theory \cite{pitts1947}.
-Furthermore, they justify the hypothesis of \cite{Coulter10, Isely10} that sparse codes passed through information bottlenecks in the brain are recovered from random projections via (unsupervised) biologically plausible sparse coding (e.g., \cite{rehnsommer2007, rozell2007neurally, hu2014hebbian}).
+Furthermore, they justify the hypothesis of \cite{Coulter10, Isely10} that sparse codes passed through information bottlenecks in the brain are recovered from random projections via (unsupervised) biologically plausible sparse coding (e.g., \cite{rehnsommer2007, rozell2007neurally, ganguli2012compressed, hu2014hebbian}).
 

### 2017-08-03 manuscripts/PNAS/review/point_by_point_response.txt
point_by_point_response.txt

--- 2017-08-03 manuscripts/PNAS/review/point_by_point_response.txt
@@
 
-We agree with the reviewer that a straight-forward extension of the noise-free result of [Hillar & Sommer (2015)] to the noisy case — while still a significant advancement in applied mathematics with actual practical implications — would not necessarily merit publication in PNAS on its own.
-It seems to us, however, that the reviewer hasn’t noticed that our main result in fact generalizes the noise-free result of [Hillar & Sommer (2015)] far beyond a simple extension to the noisy case in ways which provide greatly more valuable insight into the dictionary learning model, and that a significant deviation from their approach was necessary to prove these new facts.
+We agree with the reviewer that a straight-forward extension of the approach and noise-free result of [Hillar & Sommer (2015)] to the noisy case — while still a significant advancement in applied mathematics with actual practical implications — would not necessarily merit publication in PNAS on its own.
+The reviewer, however, seems to have overlooked the fact that our main result (Thm.
+1) generalizes the noise-free result of [Hillar & Sommer (2015)] far beyond a simple extension to the noisy case in ways which provide valuable insight into the dictionary learning model.
+No explicit comparison was made in the manuscript, but a significant deviation from the approach taken in [Hillar & Sommer (2015)] was necessary to prove these new facts.
 Moreover, our solution (Cor.
 2) to the optimization formulation of the dictionary learning problem (Prob.
-2) — that of most interest to optimization theorists and practitioners of their methods — is a significant result that is, to our knowledge, the first of its kind in both the noise-free and noisy domains.
-We discuss all of these points below in our response to the reviewer’s “detailed comments”.
+2) — that of most interest to optimization theorists and practitioners of their methods — is the first of its kind in both the noise-free and noisy domains.
+We discuss all of these points in more detail in our response to the reviewer’s later “detailed comments”.
 
-Before moving on to our response to the detailed comments, we address briefly the issues of computability and tightness raised by the reviewer.
-The sufficient conditions for recovery are indeed computable and we have updated the manuscript to include a discussion of this fact.
+We have included in our updated manuscript a discussion of the computability of the sufficient conditions (they are, indeed, computable), as per the reviewer’s request.
 It is true, however, that we have not proven the tightness of these conditions and the manuscript is therefore not *conclusive* regarding the central problems of sparse linear coding.
-We believe that the fundamental characteristics of our results will likely remain unchanged upon any further tightening, and have opted instead to include in our revised manuscript a discussion of where such improvements would come from (e.g.
-a tightening of Lemma 4).
-Regarding the sample complexity N, we believe that we have uncovered the fundamental underlying combinatorial structure at play (i.e.
-the intersection semi-lattice of a hyper-graph and its transformation under the map \pi) and that our N is on the order of the tightest possible given a lack of any additional assumptions at all on the reproducing matrix B and codes \tilde x_i.
+We believe that these sufficient conditions yield strong enough conclusions to stand on their own.
+Nonetheless, we have included in our revised manuscript some discussion of where the results can be tightened (e.g.
+Lem.
+4).
+As for tightness of the sample complexity N, we believe that our N is on the order of the smallest possible given a lack of any additional assumptions *at all* on the reproducing matrix B and sparse codes \tilde x_i.
+A sample complexity polynomial in (m,k) can be achieved, however, by limiting the size of the support set of the \tilde x_i, and we have revised the manuscript to discuss this fact (which, incidentally, does *not* follow from the results of [Hillar & Sommer (2015)] in the noiseless case).
 
@@
 
-With all due respect to the reviewer, we believe the practical implications of a noisy result over a noiseless result are plainly evident: never has there been an experiment without noise and an unstable model is therefore useless in practice.
-It seems to us that the reviewer’s fundamental concern is more likely that our proof may amount to too straight-forward of an extension of the approach taken in [Hillar & Sommer (2015)] to satisfy the criterion for publication in PNAS.
+With all due respect to the reviewer, we believe the most compelling practical implication of a noisy result over a noiseless result is plainly evident: never has there been an experiment without noise and an unstable model is therefore useless in practice.
+We assume the reviewer must instead be concerned with what additional practical “take-away” message our manuscript contains.
+In brief, it is this: there exists a procedure by which one can determine if one’s proposed solution to Prob.
+1 or Prob.
+2 is indeed unique.
+We have updated the manuscript with an explicit statement of this fact.
+
+The reviewer also seems concerned that, regardless of practical implications, our proof may amount to too straight-forward of an extension of the approach taken in [Hillar & Sommer (2015)] to satisfy the criterion for publication in PNAS.
 We believe this concern stems from two misconceptions of the reviewer: that our main result (Thm.
@@
 [More detail on what goes down in Lemma 5?] We have updated the manuscript to make the reader more keenly aware of this.
-To be clear, the perspective we take on the problem yields the following powerful new conclusions beyond those from [Hillar & Sommer (2015)]:
+To be clear, the perspective we take on the problem yields the following powerful new conclusions beyond those of a straight-forward extension of the noiseless result of [Hillar & Sommer (2015)] to the noisy case:
 

### 2017-08-03 manuscripts/PNAS/chazthm_pnas.tex
chaz

--- 2017-07-13 manuscripts/PNAS/chazthm_pnas.tex
@@
 % Give example of when we might expect k-uniformity, i.e. x_i in glp on k-dimensional subspaces. Orbit under group action of a k-dimensional subspace?
-% Proof of cor 2 can do sum starting with p=1 since they are in general linear position, hence none can be 0. but whatever.
 
@@
 For $\mathbf{u} \in \mathbb R^m$ and vector spaces $U,V \subseteq \mathbb{R}^m$, let $\text{\rm dist}(\mathbf{u}, V) := \inf \{\| \mathbf{u}-\mathbf{v} \|_2: \mathbf{v} \in V\}$ and define:
-\begin{align}\label{d}
+\begin{align}
 d(U,V) := \sup_{\mathbf{u} \in U, \ \|\mathbf{u}\|_2 \leq 1} \text{\rm dist}(\mathbf{u},V).
@@
 %[mention dictionary size independence]
+
+% A significant implication is that the constant $C_1$ of Thm.~\ref{DeterministicUniquenessTheorem} can be computed efficiently if we restrict the class of possible supports for the $\mathbf{\bar x}_i$.
+
 In this note, we generalized the approach of \cite{Hillar15} to prove the stability of unique solutions to Probs.~\ref{InverseProblem} and \ref{OptimizationProblem} while significantly reducing the known sample complexity.
@@
 Fully understanding those combinatorial designs allowing for stable sparse representations is an interesting research area for the future.
-For instance, whether there is a support set size $N$ that is polynomial in $m,k$ gauranteeing the conclusions of Thm.~\ref{DeterministicUniquenessTheorem} has implications for the computational complexity of Probs.~\ref{InverseProblem} and \ref{OptimizationProblem} and related questions \cite{Tillmann15}.
+For instance, whether there is a sample size $N$ that is polynomial in $m,k$ gauranteeing the conclusions of Thm.~\ref{DeterministicUniquenessTheorem} has implications for the computational complexity of Probs.~\ref{InverseProblem} and \ref{OptimizationProblem} and related questions \cite{Tillmann15}.
+A re-examination of pigeonholing argument in the proof of Thm.~\ref{DeterministicUniquenessTheorem} demonstrates that this can in fact be achieved if one restricts the supports of the $\mathbf{\bar x}_i$ to a class that grows polynomially in $m, k$.
 
-A technical difficulty in proving Thm.~\ref{DeterministicUniquenessTheorem} was the absence of a spark condition assumption on solutions to Prob.~\ref{InverseProblem}.
+A technical difficulty in proving Thm.~\ref{DeterministicUniquenessTheorem} was the absence of any kind of assumption on solutions to Prob.~\ref{InverseProblem}.
 Although mathematically interesting that no such requirement is necessary, there are other reasons to seek out such a theoretical guarantee.
@@
 
-We begin by showing that:
-\begin{align}\label{eq2}
-\dim(\bm{\mathcal{B}}_{\pi(S)}) = \dim(\bm{\mathcal{A}}_S) \ \ \text{for all $S \in \mathcal{H}$}. 
-\end{align}
+We begin by showing that $\dim(\bm{\mathcal{B}}_{\pi(S)}) = \dim(\bm{\mathcal{A}}_S)$ for all $S \in \mathcal{H}$.
 Since the right-hand side of \eqref{GapUpperBound} is less than one (by \eqref{delrho} and $r \leq 1$), it follows from \eqref{dimLem} that $|\pi(S)| \geq \dim(\bm{\mathcal{B}}_{\pi(S)}) \geq \dim(\bm{\mathcal{A}}_S) = |S|$, with the equality by injectivity of $\mathbf{A}$.
@@
 Suppose then that the intersection is not the zero vector.
-Applying (in order) Lem.~\ref{eqdim}, Lem.~\ref{DistanceToIntersectionLemma}, \eqref{dDef}, \eqref{eq2} and finally \eqref{GapUpperBound}, we have:
+Keeping in mind that $d(U,V) \leq d(U',V)$ whenever $U \subseteq U'$ and applying (in order) Lem.~\ref{spanIntersectionLemma}, Lem.~\ref{DistanceToIntersectionLemma}, \eqref{eqdim}, \eqref{GapUpperBound} and finally \eqref{Cdef2} gives:
 \begin{align}\label{randoml}

### 2017-08-03 manuscripts/PNAS/review/point_by_point_response.txt
chaz pt by pt

@@
 
-The reviewer also seems concerned that, regardless of practical implications, our proof may amount to too straight-forward of an extension of the approach taken in [Hillar & Sommer (2015)] to satisfy the criterion for publication in PNAS.
-We believe this concern stems from two misconceptions of the reviewer: that our main result (Thm.
-1) is merely an extension of that in [Hillar & Sommer (2015)] to the noisy case, and that our proof technique is only an incremental tweak on the approach taken in [Hillar & Sommer (2015)].
+The reviewer also raises the concern that, regardless of practical implications, our results may amount to an incremental advance over those of [Hillar & Sommer (2015)] requiring only a straight-forward extension of their approach.
+We disagree with this assessment on both counts: our main result (Thm.
+1) goes far beyond a simple extension of that in [Hillar & Sommer (2015)] to the noisy case, and our method of proof includes a significant deviation from their approach.
 
@@
 
-We also wish to reiterate that our solution to Problem 2, that of most interest to practitioners of dictionary learning methods, is the first of its kind in both the noise-free and noisy domains.
+We also wish to reiterate that our solution to Prob.
+2, that of most interest to practitioners of dictionary learning methods, is the first of its kind in both the noise-free and noisy domains.
 We recognize that this was not clearly communicated in the Discussion section of our submitted manuscript, which begins: “In this note, we generalized the approach of (18) to prove the stability of unique solutions to Probs.
@@
 
-RESPONSE: What we have discovered is that there exists a procedure by which one may check a proposed solution to determine its uniqueness. [TODO]
+RESPONSE: A statement of this very general nature requires that we calculate the probability that all of the conditions of Thm.
+1 are satisfied by random data.
+We have provided an ‘almost certain’ guarantee of this flavor in Cor 3, wherein the sparse vector supports are constrained to form hypergraph satisfying the SIP.
+It would be interesting to calculate furthermore the probability that random supports form a hypergraph satisfying the SIP.
+We think we have cracked open a nice set of interesting combinatorial problems (with practical implications!) to be solved by the community.
 
@@
 
-RESPONSE: We have addressed this concern in our response to the first reviewer’s identical comment.
-It seems both reviewers haven’t noticed that our results generalize the results of [Hillar & Sommer (2015)] far beyond a straight-forward extension to the noisy case.
+RESPONSE: Both reviewers have raised this concern and we again thank the editor for the opportunity to address it.
+It seems both reviewers haven’t noticed the several ways in which our results generalize the modern results of [Hillar & Sommer (2015)] beyond a straight-forward extension to the noisy case, not to mention our solution to the optimization Prob.
+2, which is the first of its kind and of most interest to practitioners.
+We have already discussed these points in detail in our response to the first reviewer’s identical comment.
 
@@
 our construction) and therefore, since f is analytic, the set of all those that don’t satisfy the condition has measure zero.
-We have updated the manuscript to make this argument more clear.
+We have updated the manuscript to clarify this argument for our readers.
 

### 2017-08-05 manuscripts/PNAS/chazthm_pnas.tex
L1-norm extension, references omitted

@@
 
-\acknow{We thank Friedrich Sommer and Darren Rhea for early thoughts, and Ian Morris for posting \eqref{eqdim} online.}
-\showacknow % Display the acknowledgments section
+%\acknow{We thank Friedrich Sommer and Darren Rhea for early thoughts, and Ian Morris for posting \eqref{eqdim} online.}
+%\showacknow % Display the acknowledgments section
 
-\bibliography{chazthm_pnas}
-
-%\pagebreak
+%\bibliography{chazthm_pnas}
 
@@
 
-%\pnasbreak
+\clearpage
+
+\section{$\ell_1$-norm Extension}
+
+\begin{problem}\label{OptimizationProblemL1}
+Find a matrix $\mathbf{B} \in \mathbb{R}^m$ and vectors \mbox{$\mathbf{\bar x}_1, \ldots, \mathbf{\bar x}_N \in \mathbb{R}^m$} that solve:
+\begin{align}\label{minsum}
+\min \sum_{i = 1}^N \|\mathbf{\bar x}_i\|_1 \ \ 
+\text{subject to} \ \ \|\mathbf{z}_i - \mathbf{B}\mathbf{\bar x}_i\|_2 \leq \eta, \ \text{for all $i$}.
+\end{align}
+\end{problem}
+
+\begin{corollary}\label{SLCopt}
+Fix $\alpha > 0$ and suppose all of the assumptions of Thm.\ref{DeterministicUniquenessTheorem} hold with the following modifications:
+\begin{enumerate}
+\item The nonzero elements of all $k$-sparse $\mathbf{x}_i$ are bounded above by $\beta$, where $\beta < \frac{\alpha(k+1)}{k}$.
+\item More than $(k-1){\bar m \choose k} + q$ vectors $\mathbf{x}_i$ are supported in each $S \in \mathcal{H}$, where
+\[ q = \left[\frac{\alpha}{\beta}(k+1) - k\right]^{-1}k|\mathcal{H}|(k-1){\bar m \choose k-1}. \]
+\end{enumerate}
+Then all solutions to Prob.~\ref{OptimizationProblemL1} for which the nonzero elements of all $\mathbf{\bar x}_i$ are bounded below by $\alpha$ necessarily satisfy the implications \eqref{Cstable} and \eqref{b-PDa} of Thm.~\ref{DeterministicUniquenessTheorem}.
+\end{corollary}
+
+\begin{proof}[Proof of Cor.~\ref{SLCopt}]
+We bound the number of $k$-sparse $\mathbf{\bar x}_i$ and then apply Thm.~\ref{DeterministicUniquenessCorollary}.
+First, observe that no more than $(k-1)|\mathcal{H}|$ of the $\mathbf{\bar x}_i$ share a support $\bar S$ of size less than $k$; otherwise, by the pigeonhole principle, at least $k$ of these indices $i$ belong to the same $K \subseteq I(S)$ for some $S \in \mathcal{H}$ and (as argued previously) \eqref{rhs222} follows.
+Since the right-hand side of \eqref{rhs222} is less than one, by \eqref{dimLem} we have the contradiction $k = \dim(\bm{\mathcal{A}}_S) \leq \dim(\bm{\mathcal{B}}_{\bar S}) \leq |\bar S|.$ The total number of $(k-1)$-sparse vectors $\mathbf{\bar x}_i$ can thus not exceed $|\mathcal{H}|(k-1){ \bar m \choose k-1}$.
+
+Next, observe that the assumptions of the lemma imply:
+\begin{align*}
+\alpha \sum_i \|\mathbf{\bar x}_i\|_0 \leq \sum_i \|\mathbf{\bar x}_i\|_1 \leq \sum_i \|\mathbf{x}_i\|_1 \leq \beta \sum_i \|\mathbf{\bar x}_i\|_0.
+\end{align*}
+
+We now apply these facts to bound the number of $k$-sparse $\mathbf{\bar x}_i$.
+Let $n_p$ be the number of $\mathbf{\bar x}_i$ with $\|\mathbf{\bar x}_i\|_0 = p$.
+Since the $\mathbf{x}_i$ are all $k$-sparse, by \eqref{minsum} we have:
+\begin{align*}
+k \sum_{p = 0}^{\bar m} n_p = k N \geq \sum_{i=0}^N \|\mathbf{x}_i\|_0 \geq \frac{\alpha}{\beta} \sum_{i=0}^N \|\mathbf{\bar x}_i\|_0 = \frac{\alpha}{\beta} \sum_{p=0}^{\bar m} p n_p.
+\end{align*}
+Hence, 
+\begin{align*}
+\left[ \frac{\alpha(k+1)}{\beta} - k\right] \sum_{p = k+1}^{\bar m} n_p 
+&\leq \sum_{p = k+1}^{\bar m} (\frac{\alpha}{\beta} p-k) n_p
+\leq \sum_{p = 0}^k (k - \frac{\alpha}{\beta} p)n_p \\
+&\leq k \sum_{p = 0}^{k-1} n_p 
+\leq k|\mathcal{H}|(k-1){ \bar m \choose k-1}
+\end{align*}
+
+Therefore, no more than $q$ vectors $\mathbf{\bar x}_i$ are \emph{not} $k$-sparse.
+Since for every $S \in \mathcal{H}$ there are over $(k-1){\bar m \choose k} + q$ vectors $\mathbf{x}_i$ supported there, it follows that more than $(k-1){\bar m \choose k}$ of them have corresponding $\mathbf{\bar x}_i$ that are $k$-sparse.
+The result now follows directly from Thm.~\ref{DeterministicUniquenessCorollary}.
+\end{proof}
 

### 2017-08-07 manuscripts/PNAS/chazthm_pnas.tex
fixed typo
chaz

--- 2017-08-03 manuscripts/PNAS/chazthm_pnas.tex
@@
 \begin{problem}\label{OptimizationProblem}
-Find a matrix $\mathbf{B} \in \mathbb{R}^m$ and vectors \mbox{$\mathbf{\bar x}_1, \ldots, \mathbf{\bar x}_N \in \mathbb{R}^m$} that solve:
+Find a matrix $\mathbf{B}$ and vectors \mbox{$\mathbf{\bar x}_1, \ldots, \mathbf{\bar x}_N \in \mathbb{R}^m$} that solve:
 \begin{align}\label{minsum}
@@
 
-%\pagebreak
-
 \section{Appendix}\label{proofs}
@@
 
-%\pnasbreak
+\clearpage
+
+\section{$\ell_1$-norm Extension}
+
+\begin{problem}\label{OptimizationProblemL1}
+Find a matrix $\mathbf{B}$ and vectors \mbox{$\mathbf{\bar x}_1, \ldots, \mathbf{\bar x}_N \in \mathbb{R}^m$} that solve:
+\begin{align}\label{minsum}
+\min \sum_{i = 1}^N \|\mathbf{\bar x}_i\|_1 \ \ 
+\text{subject to} \ \ \|\mathbf{z}_i - \mathbf{B}\mathbf{\bar x}_i\|_2 \leq \eta, \ \text{for all $i$}.
+\end{align}
+\end{problem}
+
+%\begin{corollary}\label{SLCopt}
+%Fix $\alpha > 0$ and suppose all of the assumptions of Thm.\ref{DeterministicUniquenessTheorem} hold with the following modifications:
+%\begin{enumerate}
+%\item The coefficients of all $k$-sparse $\mathbf{x}_i$ are drawn from $[-\beta, \beta]$, where $\beta < \frac{\alpha(k+1)}{k}$.
+%\item More than $(k-1){\bar m \choose k} + q$ vectors $\mathbf{x}_i$ are supported in each $S \in \mathcal{H}$, where
+%\[ q = \left[\frac{\alpha}{\beta}(k+1) - k\right]^{-1}k|\mathcal{H}|(k-1){\bar m \choose k-1}. \]
+%\end{enumerate}
+%Then all solutions to Prob.~\ref{OptimizationProblemL1} for which the nonzero elements of all $\mathbf{\bar x}_i$ lie outside $[-\alpha, \alpha]$ necessarily satisfy the implications \eqref{Cstable} and \eqref{b-PDa} of Thm.~\ref{DeterministicUniquenessTheorem}.
+%\end{corollary}
+
+%\begin{proof}[Proof of Cor.~\ref{SLCopt}]
+%We bound the number of $k$-sparse $\mathbf{\bar x}_i$ and then apply Thm.~\ref{DeterministicUniquenessCorollary}.
+First, observe that no more than $(k-1)|\mathcal{H}|$ of the $\mathbf{\bar x}_i$ share a support $\bar S$ of size less than $k$; otherwise, by the pigeonhole principle, at least $k$ of these indices $i$ belong to the same $K \subseteq I(S)$ for some $S \in \mathcal{H}$ and (as argued previously) \eqref{rhs222} follows.
+Since the right-hand side of \eqref{rhs222} is less than one, by \eqref{dimLem} we have the contradiction $k = \dim(\bm{\mathcal{A}}_S) \leq \dim(\bm{\mathcal{B}}_{\bar S}) \leq |\bar S|.$ The total number of $(k-1)$-sparse vectors $\mathbf{\bar x}_i$ can thus not exceed $|\mathcal{H}|(k-1){ \bar m \choose k-1}$.
+
+%Next, observe that the assumptions of the lemma imply:
+%\begin{align*}
+%\alpha \sum_i \|\mathbf{\bar x}_i\|_0 \leq \sum_i \|\mathbf{\bar x}_i\|_1 \leq \sum_i \|\mathbf{x}_i\|_1 \leq \beta \sum_i \|\mathbf{x}_i\|_0.
+%\end{align*}
+
+%We now apply these facts to bound the number of $k$-sparse $\mathbf{\bar x}_i$.
+Let $n_p$ be the number of $\mathbf{\bar x}_i$ with $\|\mathbf{\bar x}_i\|_0 = p$.
+Since the $\mathbf{x}_i$ are all $k$-sparse, we have:
+%\begin{align*}
+%k \sum_{p = 0}^{\bar m} n_p = k N \geq \sum_{i=0}^N \|\mathbf{x}_i\|_0 \geq \frac{\alpha}{\beta} \sum_{i=0}^N \|\mathbf{\bar x}_i\|_0 = \frac{\alpha}{\beta} \sum_{p=0}^{\bar m} p n_p.
+%\end{align*}
+%Hence, 
+%\begin{align*}
+%\left[ \frac{\alpha(k+1)}{\beta} - k\right] \sum_{p = k+1}^{\bar m} n_p 
+%&\leq \sum_{p = k+1}^{\bar m} (\frac{\alpha}{\beta} p-k) n_p
+%\leq \sum_{p = 0}^k (k - \frac{\alpha}{\beta} p)n_p \\
+%&\leq k \sum_{p = 0}^k n_p 
+%\leq k(1-\frac{\alpha}{\beta})n_k + k|\mathcal{H}|(k-1){ \bar m \choose k-1}
+%\end{align*}
+
+%[Shit, we need $\alpha = \beta$.] Therefore, no more than $q$ vectors $\mathbf{\bar x}_i$ are \emph{not} $k$-sparse.
+Since for every $S \in \mathcal{H}$ there are over $(k-1){\bar m \choose k} + q$ vectors $\mathbf{x}_i$ supported there, it follows that more than $(k-1){\bar m \choose k}$ of them have corresponding $\mathbf{\bar x}_i$ that are $k$-sparse.
+The result now follows directly from Thm.~\ref{DeterministicUniquenessCorollary}.
+%\end{proof}
+
+%\pagebreak
+
+%\begin{corollary}\label{SLCoptL1}
+%If all of the assumptions of Thm.\ref{DeterministicUniquenessTheorem} hold, only now with more than $(k-1)\left[ {\bar m \choose k} + |\mathcal{H}|k{\bar m \choose k-1}\right]$ vectors $\mathbf{x}_i$ supported in each $S \in \mathcal{H}$, then every solution to Prob.~\ref{OptimizationProblemL1} for which the average absolute nonzero coefficient of the $\mathbf{\bar x}_i$ is bounded below by that of the $\mathbf{x}_i$ necessarily satisfies the implications \eqref{Cstable} and \eqref{b-PDa} of Thm.~\ref{DeterministicUniquenessTheorem}.
+%\end{corollary}
+
+%\begin{proof}[Proof of Cor.~\ref{SLCoptL1}]
+%Since the average absolute nonzero coefficient of the $\mathbf{x}_i$ is given by $\alpha = \sum_i \|\mathbf{x}_i\|_1 / \sum_i \|\mathbf{x}_i\|_0$, we have:
+%\begin{align*}
+%\alpha \sum_i \|\mathbf{\bar x}_i\|_0 \leq \sum_i \|\mathbf{\bar x}_i\|_1 \leq \sum_i \|\mathbf{x}_i\|_1 = \alpha \sum_i \|\mathbf{x}_i\|_0.
+%\end{align*}
+%
+%and the result follows by the same arguments as in the proof of Cor.~\ref{SLCopt}.
+%\end{proof}
 

### 2017-08-07 manuscripts/PNAS/review/point_by_point_response.txt
cover update P=NP relationship

@@
 
-We agree with the reviewer that a straight-forward extension of the approach and noise-free result of [Hillar & Sommer (2015)] to the noisy case — while still a significant advancement in applied mathematics with actual practical implications — would not necessarily merit publication in PNAS on its own.
+We agree with the reviewer that a straightforward extension of the approach and noise-free result of [Hillar & Sommer (2015)] to the noisy case — while still a significant advancement in applied mathematics with actual practical implications — would not necessarily merit publication in PNAS on its own.
 The reviewer, however, seems to have overlooked the fact that our main result (Thm.
@@
 
-The reviewer also raises the concern that, regardless of practical implications, our results may amount to an incremental advance over those of [Hillar & Sommer (2015)] requiring only a straight-forward extension of their approach.
+The reviewer also raises the concern that, regardless of practical implications, our results may amount to an incremental advance over those of [Hillar & Sommer (2015)], requiring only a straightforward extension of their approach.
 We disagree with this assessment on both counts: our main result (Thm.
@@
 It is understandable from the presentation of our proof of our main result (Thm.
-1) that our approach appears on the surface to be a straight-forward extension of that taken in [Hillar & Sommer (2015)].
+1) that our approach appears on the surface to be a straightforward extension of that taken in [Hillar & Sommer (2015)].
 As observed by our second reviewer, however, the extension to the noisy case did indeed require an original combination of several results in the literature.
@@
 [More detail on what goes down in Lemma 5?] We have updated the manuscript to make the reader more keenly aware of this.
-To be clear, the perspective we take on the problem yields the following powerful new conclusions beyond those of a straight-forward extension of the noiseless result of [Hillar & Sommer (2015)] to the noisy case:
+To be clear, the perspective we take on the problem yields the following powerful new conclusions beyond those of a straightforward extension of the noiseless result of [Hillar & Sommer (2015)] to the noisy case:
 
@@
 
-[4) Implications for the computational complexity of the dictionary learning problem: If the size of the support set of reconstructing codes is polynomial in m,k then the pigeonholing argument in the proof of Thm.
+4) Implications for the computational complexity of the dictionary learning problem: If the size of the support set of reconstructing codes is polynomial in m,k then the pigeonholing argument in the proof of Thm.
 1 requires only a polynomial number of samples distributed over a polynomial number of supports; thus N is polynomial in m, k.
 [Chris?
-How does this have implications..?] This point was only hinted at in the Discussion section of our original submission, but we have included it in the updated manuscript to make clear the power of our approach over that taken in [Hillar & Sommer (2015)].
+How does this have implications..?
+ANS: use the P1 and P2 => P=NP] This point was only hinted at in the Discussion section of our original submission, but we have included it in the updated manuscript to make clear the power of our approach over that taken in [Hillar & Sommer (2015)].
 
@@
 RESPONSE: Both reviewers have raised this concern and we again thank the editor for the opportunity to address it.
-It seems both reviewers haven’t noticed the several ways in which our results generalize the modern results of [Hillar & Sommer (2015)] beyond a straight-forward extension to the noisy case, not to mention our solution to the optimization Prob.
+It seems both reviewers have not noticed the several ways in which our results generalize the modern results of [Hillar & Sommer (2015)] beyond a straightforward extension to the noisy case, not to mention our solution to the optimization Prob.
 2, which is the first of its kind and of most interest to practitioners.

### 2017-08-07 manuscripts/PNAS/review/point_by_point_response.txt
.

--- 2017-08-03 manuscripts/PNAS/review/point_by_point_response.txt
@@
 
-We agree with the reviewer that a straight-forward extension of the approach and noise-free result of [Hillar & Sommer (2015)] to the noisy case — while still a significant advancement in applied mathematics with actual practical implications — would not necessarily merit publication in PNAS on its own.
+We agree with the reviewer that a straightforward extension of the approach and noise-free result of [Hillar & Sommer (2015)] to the noisy case — while still a significant advancement in applied mathematics with actual practical implications — would not necessarily merit publication in PNAS on its own.
 The reviewer, however, seems to have overlooked the fact that our main result (Thm.
 1) generalizes the noise-free result of [Hillar & Sommer (2015)] far beyond a simple extension to the noisy case in ways which provide valuable insight into the dictionary learning model.
-No explicit comparison was made in the manuscript, but a significant deviation from the approach taken in [Hillar & Sommer (2015)] was necessary to prove these new facts.
+A significant deviation from the approach taken in [Hillar & Sommer (2015)] was necessary to prove these new facts, although no explicit comparison was made in the manuscript.
 Moreover, our solution (Cor.
@@
 We recognize that this was not clearly communicated in the Discussion section of our submitted manuscript, which begins: “In this note, we generalized the approach of (18) to prove the stability of unique solutions to Probs.
-1 and 2 while significantly reducing the known sample complexity.” We have revised our re-submitted manuscript to make it clear that a solution to Problem 2 has never been supplied before in the literature until now [right?].
+1 and 2 […]” We have revised our re-submitted manuscript to make it clear that a solution to Problem 2 has never been supplied before in the literature until now [right?].
 
@@
 1 are satisfied by random data.
-We have provided an ‘almost certain’ guarantee of this flavor in Cor 3, wherein the sparse vector supports are constrained to form hypergraph satisfying the SIP.
+We have provided an ‘almost certain’ guarantee of this flavor in Cor 3, wherein the sparse vector supports are constrained to form a hypergraph satisfying the SIP.
 It would be interesting to calculate furthermore the probability that random supports form a hypergraph satisfying the SIP.

### 2017-08-07 manuscripts/PNAS/review/point_by_point_response.txt

--- 2017-08-07 manuscripts/PNAS/review/point_by_point_response.txt
@@
 1) generalizes the noise-free result of [Hillar & Sommer (2015)] far beyond a simple extension to the noisy case in ways which provide valuable insight into the dictionary learning model.
-No explicit comparison was made in the manuscript, but a significant deviation from the approach taken in [Hillar & Sommer (2015)] was necessary to prove these new facts.
+A significant deviation from the approach taken in [Hillar & Sommer (2015)] was necessary to prove these new facts, although no explicit comparison was made in the manuscript.
 Moreover, our solution (Cor.

### 2017-08-11 manuscripts/PNAS/review/point_by_point_response.txt

@@
 
-RESPONSE: We have included in our revised manuscript a more compelling exposition of the significance of our results and their relevance to the general scientific audience, and thank the editor for the opportunity to address this concern shared by both reviewers.
-[Summarize high level major points in our cover here.
-Also, mention we try to flesh this out in the next comment below.]
+RESPONSE: We have included in our revised manuscript a more compelling exposition of the significance of our results and their relevance to the general scientific audience, and we thank the editor for the opportunity to address this concern shared by both reviewers.
 
@@
 1) generalizes the noise-free result of [Hillar & Sommer (2015)] far beyond a simple extension to the noisy case in ways which provide valuable insight into the dictionary learning model.
-A significant deviation from the approach taken in [Hillar & Sommer (2015)] was necessary to prove these new facts, although no explicit comparison was made in the manuscript.
+A significant deviation from the approach taken in [Hillar & Sommer (2015)] was necessary to prove these new facts.
 Moreover, our solution (Cor.
 2) to the optimization formulation of the dictionary learning problem (Prob.
-2) — that of most interest to optimization theorists and practitioners of their methods — is the first of its kind in both the noise-free and noisy domains.
+2) — that of most interest to optimization theorists and practitioners of their methods — is the first of its kind (to our knowledge) in both the noise-free and noisy domains.
 We discuss all of these points in more detail in our response to the reviewer’s later “detailed comments”.
@@
 4).
-As for tightness of the sample complexity N, we believe that our N is on the order of the smallest possible given a lack of any additional assumptions *at all* on the reproducing matrix B and sparse codes \tilde x_i.
 A sample complexity polynomial in (m,k) can be achieved, however, by limiting the size of the support set of the \tilde x_i, and we have revised the manuscript to discuss this fact (which, incidentally, does *not* follow from the results of [Hillar & Sommer (2015)] in the noiseless case).
+[And for fixed k […]]
 
@@
 1) differs from the approach taken by [Hillar & Sommer (2015)] in a key way that is tucked into the proof of our Main Lemma — more specifically, by the addition of Lemma 5.
-[More detail on what goes down in Lemma 5?] We have updated the manuscript to make the reader more keenly aware of this.
+We have updated the manuscript to make the reader more keenly aware of this.
 To be clear, the perspective we take on the problem yields the following powerful new conclusions beyond those of a straightforward extension of the noiseless result of [Hillar & Sommer (2015)] to the noisy case:
 
-1) A significant reduction in sample complexity: To identify the n x m generating dictionary A, [Hillar & Sommer (2015)] require that data be sampled from *every* k-dimensional subspace spanned by the m columns of A (that is, {m \choose k} subspaces in total).
+1) An extension to the case where the number of dictionary elements is unknown: The results of [Hillar & Sommer (2015)] only apply to the case where the matrix B has the same number of columns as A.
+We forgo this assumption and show that B must have at least as many columns as A and contains (up to noise) a subset of the columns of A.
+The size of this subset depends on a simple relation between the number of columns of B and the regularity of the support-set hypergraph.
+
+2) A significant reduction in sample complexity: To identify the n x m generating dictionary A, [Hillar & Sommer (2015)] require that data be sampled from *every* k-dimensional subspace spanned by the m columns of A (that is, {m \choose k} subspaces in total).
 We show that the data need only be sampled from m subspaces in total (e.g.
@@
 
-2) An extension to the case where the number of dictionary elements is unknown: The results of [Hillar & Sommer (2015)] only apply to the case where the matrix B has the same number of columns as A.
-We forgo this assumption and show that B must have at least as many columns as A and contains (up to noise) a subset of the columns of A.
-The size of this subset depends on a simple relation between the number of columns of B and the regularity of the support-set hypergraph.
+3) Implications for the computational complexity of the dictionary learning problem: If the size of the support set of reconstructing codes is polynomial in m,k then the pigeonholing argument in the proof of Thm.
+1 requires only a polynomial number of samples distributed over a polynomial number of supports; thus N is polynomial in m, k.
+This point was only hinted at in the Discussion section of our original submission, but we have included it in the updated manuscript to make clear the power of our approach over that taken in [Hillar & Sommer (2015)].
+[For fixed k…]
 
-3) No spark condition requirement for the generating matrix A: One of the mathematically significant contributions made by [Hillar & Sommer (2015)] was to forgo the constraint that the recovery matrix B also satisfy the spark condition, in contrast to all previously known uniqueness results which (either explicitly or implicitly) made this assumption.
+4) No spark condition requirement for the generating matrix A: One of the mathematically significant contributions made by [Hillar & Sommer (2015)] was to forgo the constraint that the recovery matrix B also satisfy the spark condition, in contrast to all previously known uniqueness results which (either explicitly or implicitly) made this assumption.
 Our proof is powerful enough to show that, in fact, even the matrix A need not satisfy the spark condition to be identifiable!
-Rather, it need only be injective on the union of subspaces with supports that form sets in a hypergraph satisfying the SIP.
-We had omitted this point in our original submission of the manuscript to keep things simple, but have decided to include this interesting fact in our resubmission given that a recently approved NSF grant _____ makes use of this fact in its description of methods.
+Rather, it need only be injective on the union of subspaces with supports that form sets in a hypergraph satisfying the singleton intersection property (SIP).
+We had omitted this point in our original submission of the manuscript to keep things simple, but have decided to include this interesting fact in our resubmission.
 This also required us to redefine the restricted matrix lower bound L to be in terms of a hypergraph, which is an interesting object for further study in its own right.
 
-4) Implications for the computational complexity of the dictionary learning problem: If the size of the support set of reconstructing codes is polynomial in m,k then the pigeonholing argument in the proof of Thm.
-1 requires only a polynomial number of samples distributed over a polynomial number of supports; thus N is polynomial in m, k.
-[Chris?
-How does this have implications..?
-ANS: use the P1 and P2 => P=NP] This point was only hinted at in the Discussion section of our original submission, but we have included it in the updated manuscript to make clear the power of our approach over that taken in [Hillar & Sommer (2015)].
-
 We also wish to reiterate that our solution to Prob.
-2, that of most interest to practitioners of dictionary learning methods, is the first of its kind in both the noise-free and noisy domains.
+2, that of most interest to practitioners of dictionary learning methods, is to our knowledge the first of its kind in both the noise-free and noisy domains.
 We recognize that this was not clearly communicated in the Discussion section of our submitted manuscript, which begins: “In this note, we generalized the approach of (18) to prove the stability of unique solutions to Probs.
-1 and 2 […]” We have revised our re-submitted manuscript to make it clear that a solution to Problem 2 has never been supplied before in the literature until now [right?].
+1 and 2 […]”
 
@@
 The condition on \ell is perhaps best understood as a condition on \bar m not being too large (given \ell) in order to guarantee the recovery of at least one dictionary element.
-We have updated the manuscript to reflect this, and the condition now reads “provided \bar m < \ell m / (\ell - 1)” where previously it read “provided p = \bar m − \ell( \bar m − m )$ is positive”.
+We have updated the manuscript to reflect this, and the condition now reads “provided \bar m < \ell m / (\ell - 1)” where previously it read “provided p = \bar m − \ell( \bar m − m ) is positive”.
 
@@
 We have tried and continue to try to be as clear, concise, and correct as we possibly can to elevate this work into the top echelon of applied mathematical theory papers.
+
+[Do comparison here, state that noiseless is a corollary of our noisy and therefore we don’t discuss the comparison in the paper.
+They have the table only because they needed randomness to get what we get with SIP.
+We’re willing to add it if you insist, but we think it detracts from the paper..]
 
@@
 
+[We could have done this but we believe what sets our results apart from the vast majority of results in this field so far is its deterministic nature from which any probabilistic result can be derived, e.g.
+the ones we give]
+
 -----------------
@@
 
-RESPONSE: We have determined explicit forms for the constants in Theorem 1. [Are they feasible to compute..?]
+RESPONSE: We have determined explicit forms for the effectively computable constants in Theorem 1.
+[But they are not feasible to compute, since they require calculating the RIP of all k-wise subsets of the data.
+Revive NP-hard argument?]
 
@@
 RESPONSE: Yes, there is indeed.
-While all existing uniqueness results require a sufficient number of samples be drawn from *each* of {m \choose k} possible supports, we have shown that in fact it is enough that a sufficient number of samples be drawn from every support in a subset of drastically smaller size, provided this subset forms a regular hypergraph satisfying the singleton intersection property.
+While all existing uniqueness results require a sufficient number of samples be drawn from *each* of {m \choose k} possible supports, we have shown that it is enough that a sufficient number of samples be drawn from every support in a subset of drastically smaller size, provided this subset forms a regular hypergraph satisfying the SIP.
 As was pointed out in our manuscript, a support set of size m satisfying these criteria can always be constructed for any k < m (e.g.
@@
 It seems both reviewers have not noticed the several ways in which our results generalize the modern results of [Hillar & Sommer (2015)] beyond a straightforward extension to the noisy case, not to mention our solution to the optimization Prob.
-2, which is the first of its kind and of most interest to practitioners.
+2, which as far as we know is the first of its kind and of most interest to practitioners.
 We have already discussed these points in detail in our response to the first reviewer’s identical comment.

### 2017-08-12 manuscripts/PNAS/review/point_by_point_response.txt
proof comparison

@@
 
-The reviewer also raises the concern that, regardless of practical implications, our results may amount to an incremental advance over those of [Hillar & Sommer (2015)], requiring only a straightforward extension of their approach.
+** IS THAT ENOUGH FOR PRACTICAL IMPLICATIONS..? **
+
+The reviewer also raises the concern that, regardless of practical implications, our results may amount to an incremental advance over those of [Hillar & Sommer (2015)] by way of similar techniques.
 We disagree with this assessment on both counts: our main result (Thm.
-1) goes far beyond a simple extension of that in [Hillar & Sommer (2015)] to the noisy case, and our method of proof includes a significant deviation from their approach.
+1) goes far beyond a straightforward extension of that in [Hillar & Sommer (2015)] to the noisy case and this required a significant deviation from their approach.
 
-It is understandable from the presentation of our proof of our main result (Thm.
-1) that our approach appears on the surface to be a straightforward extension of that taken in [Hillar & Sommer (2015)].
+It is understandable that the reviewer may have thought otherwise, considering how the proof of Thm.
+1 is presented in the manuscript.
 As observed by our second reviewer, however, the extension to the noisy case did indeed require an original combination of several results in the literature.
-Aside from these required modifications, our proof of (Thm.
-1) differs from the approach taken by [Hillar & Sommer (2015)] in a key way that is tucked into the proof of our Main Lemma — more specifically, by the addition of Lemma 5.
-We have updated the manuscript to make the reader more keenly aware of this.
-To be clear, the perspective we take on the problem yields the following powerful new conclusions beyond those of a straightforward extension of the noiseless result of [Hillar & Sommer (2015)] to the noisy case:
+Specifically, the main difficulty was to generalize Lemma 1 to the case where the k-dimensional subspaces spanned by corresponding sub-matrices of A and B are assumed only to be proximal (small ‘d’), and not identical as in [Hillar & Sommer (2015)].
+In contrast to the noiseless case, here it must be explicitly demonstrated that this proximity relation is propagated through the repeated intersections of these sub-matrix spans all the way down to the spans of dictionary elements themselves.
+We designed and proved Lemma 4 to address this issue, which draws its bound from the convergence guarantees of an alternating projections algorithm first proposed by von Neumann.
+This result, combined with a little known fact about the distance ‘d’ requiring proof in [Morris; Advances in Mathematics], constitute the more sophisticated and obscure components of the deduction in eq.(26).
+To reiterate, this step is completely trivial in the noiseless case and required no mention for the inductive steps taken in [HS15].
+
+Our proof of Lemma 1 diverges perhaps even more significantly from the approach taken in [HS15] by way of Lemma 5.
+Key to our reduction of the sample complexity given in [HS15] by an exponential factor is the introduction of a combinatorial design (the ‘singleton intersection property’) for the support sets.
+Since in this case the map \pi from supports in the hypergraph to {[m] \choose k} is not surjective, one cannot apply the same inductive method as in [HS15], which freely chooses supports in the codomain to intersect at (k-1) nodes and map back to some corresponding (k-1)-sized intersection of supports in the domain.
+Instead, we demonstrate the surprising fact that by pigeonholing the images of supports in the (SIP-satisfying) hypergraph one can still guarantee a bijection between the nodes and therefore the subspaces spanned by individual dictionary elements.
+We note that it was necessary to forgo inductive methods altogether in order to prove this fact for all hypergraphs satisfying the SIP; otherwise, we would require that the supports in the hypergraph have intersections of size k’ for every k’ < k (e.g.
+this is not the case for the small SIP example we give consisting of the rows and columns of nodes arranged in a square grid).
+Again, to our surprise, it so happens that this new induction-less argument easily generalizes to the case where B has an arbitrary number of columns, in which case we find that a one-to-one correspondence exists between a subset of columns of A and B of a size that has a nice closed-form expression for regular SIP hypergraphs.
+
+To be clear, the new perspective we take on the problem yields the following powerful conclusions beyond those of a straightforward extension of the noiseless result of [Hillar & Sommer (2015)] to the noisy case:
 
@@
 when m = k^2, take the supports to be the rows and columns of [m] arranged in a square grid).
-
-3) Implications for the computational complexity of the dictionary learning problem: If the size of the support set of reconstructing codes is polynomial in m,k then the pigeonholing argument in the proof of Thm.
+Moreover, if the size of the support set of reconstructing codes is polynomial in m,k then the pigeonholing argument in the proof of Thm.
 1 requires only a polynomial number of samples distributed over a polynomial number of supports; thus N is polynomial in m, k.
@@
 
-4) No spark condition requirement for the generating matrix A: One of the mathematically significant contributions made by [Hillar & Sommer (2015)] was to forgo the constraint that the recovery matrix B also satisfy the spark condition, in contrast to all previously known uniqueness results which (either explicitly or implicitly) made this assumption.
+3) No spark condition requirement for the generating matrix A: One of the mathematically significant contributions made by [Hillar & Sommer (2015)] was to forgo the constraint that the recovery matrix B also satisfy the spark condition, in contrast to all previously known uniqueness results which (either explicitly or implicitly) made this assumption.
 Our proof is powerful enough to show that, in fact, even the matrix A need not satisfy the spark condition to be identifiable!
@@
 
-We also wish to reiterate that our solution to Prob.
+We must also mention here that our solution to Prob.
 2, that of most interest to practitioners of dictionary learning methods, is to our knowledge the first of its kind in both the noise-free and noisy domains.

### 2017-08-13 manuscripts/PNAS/review/point_by_point_response.txt
chaz

@@
 We assume the reviewer must instead be concerned with what additional practical “take-away” message our manuscript contains.
-In brief, it is this: there exists a procedure by which one can determine if one’s proposed solution to Prob.
+In brief, it is this: we have outlined a procedure by which one can determine if one’s proposed solution to Prob.
 1 or Prob.
@@
 As observed by our second reviewer, however, the extension to the noisy case did indeed require an original combination of several results in the literature.
-Specifically, the main difficulty was to generalize Lemma 1 to the case where the k-dimensional subspaces spanned by corresponding sub-matrices of A and B are assumed only to be proximal (small ‘d’), and not identical as in [Hillar & Sommer (2015)].
+Specifically, the main difficulty was to generalize Lemma 1 to the case where the k-dimensional subspaces spanned by corresponding (through the map \pi) sub-matrices of A and B are assumed only to be proximal (small ‘d’), and not identical as in [Hillar & Sommer (2015)].
 In contrast to the noiseless case, here it must be explicitly demonstrated that this proximity relation is propagated through the repeated intersections of these sub-matrix spans all the way down to the spans of dictionary elements themselves.

### 2017-08-13 manuscripts/PNAS/review/point_by_point_response.txt
pnt by pnt update

--- 2017-08-12 manuscripts/PNAS/review/point_by_point_response.txt
@@
+References for Cover Letter and Point-by-point Response:
+
+[IHS10] Isely, Hillar, Sommer, Advances in neural information processing systems (NIPS), 2010.
+[GS12] Ganguli, Sompolinksi, Annual review of neuroscience, 2012.
+[TP14] Tillman, Pfetsch, IEEE Transactions on information processing, 2014.
+[HS15] Hillar, Sommer, IEEE Transactions on information processing, 2015.
+
 -----------------
@@
 -----------------
-Since the result is an extension of the noise-free result of [Hillar & Sommer (2015)] to a noisy case, the authors should provide better justification for the significance of contributions.
-The main result seems to be based on an approach similar to [Hillar & Sommer (2015)], and there is little to no discussion of the computability and tightness of the sufficient condition for stability in the main results.
-Thus, the submission does not seem to be greatly more valuable than [Hillar & Sommer (2015)] and also not conclusive regarding the central problems of sparse linear coding and dictionary learning.
+Since the result is an extension of the noise-free result of [HS15] to a noisy case, the authors should provide better justification for the significance of contributions.
+The main result seems to be based on an approach similar to [HS15], and there is little to no discussion of the computability and tightness of the sufficient condition for stability in the main results.
+Thus, the submission does not seem to be greatly more valuable than [HS15] and also not conclusive regarding the central problems of sparse linear coding and dictionary learning.
 That being said, the paper (with the modifications below) would certainly merit publication in very solid journal like IEEE Transactions on Information Theory, where it would be a median paper, in my opinion.
@@
 
-We agree with the reviewer that a straightforward extension of the approach and noise-free result of [Hillar & Sommer (2015)] to the noisy case — while still a significant advancement in applied mathematics with actual practical implications — would not necessarily merit publication in PNAS on its own.
+We agree with the reviewer that a straightforward extension of the approach and noise-free result of [HS15] to the noisy case — while still a significant advancement in applied mathematics with actual practical implications — would not necessarily merit publication in PNAS on its own.
 The reviewer, however, seems to have overlooked the fact that our main result (Thm.
-1) generalizes the noise-free result of [Hillar & Sommer (2015)] far beyond a simple extension to the noisy case in ways which provide valuable insight into the dictionary learning model.
-A significant deviation from the approach taken in [Hillar & Sommer (2015)] was necessary to prove these new facts.
+1) generalizes the noise-free result of [HS15] far beyond a simple extension to the noisy case in ways which provide valuable insight into the dictionary learning model.
+A significant deviation from the approach taken in [HS15] was necessary to prove these new facts.
 Moreover, our solution (Cor.
@@
 2) — that of most interest to optimization theorists and practitioners of their methods — is the first of its kind (to our knowledge) in both the noise-free and noisy domains.
-We discuss all of these points in more detail in our response to the reviewer’s later “detailed comments”.
+We discuss all of these points in more detail in our response to the reviewer’s later "detailed comments".
+[???WORDING OF THIS PARAGRAPH COULD IMPROVE???]
 
 We have included in our updated manuscript a discussion of the computability of the sufficient conditions (they are, indeed, computable), as per the reviewer’s request.
-It is true, however, that we have not proven the tightness of these conditions and the manuscript is therefore not *conclusive* regarding the central problems of sparse linear coding.
-We believe that these sufficient conditions yield strong enough conclusions to stand on their own.
+The main constants in our work -- C_1, C_2 -- are indeed computable, elementarily, in terms of two positive quantities that are natural in our context: (a) the "Lower Bound" L_H(A) of a matrix A given a hypergraph H (the support structure of sparse x's generating the data), which is a measure of how much A has a "spark condition" supported on H, and (b) the value in Def.
+4 of r(V_1,...,V_l) given subspaces V_i corresponding to spans of A's columns, which bounds the distance between an intersection of such spans and each one individually.
+The first quantity (a) is, in some form or another, related to standard objects in the field and may be computed as the smallest singular value of a particular matrix; in particular, for fixed sparsity constraint k on H, the lower bound L_H(A) is efficiently computable (polynomial time).
+Because deciding L_H(A) > 0 is already NP-hard [TP14], it seems likely that without fixing a sparsity level there is no efficient computation in general for (a).
+The calculation of (b) involves determining "canonical angles" between subspaces, which is usually reduced again to a numerical (efficient) singular value decomposition given the fixed subspaces.
+However, upon close inspection, C_2 nonetheless requires an exponential number of instances of computing r.
+Thus, while our constants are effective (an algorithm exists to compute them), they are not necessarily polynomially-time computable.
+
+Another natural question that arises is the mathematical "tightness" of result statements for the three types of quantities: (a) required coding error eps(delta_1, delta_2) sufficient to guarantee uniqueness in terms of desired dictionary delta_1 and sparse representation error delta_2, (b) the constants C_1 and C_2 involved in our sufficient linear bound on eps(delta_1, delta_2), and (c) the number of sufficient samples N guaranteeing uniqueness.
+With respect to (a), even with fixed dictionary, the recovery of sparse representations up to an error that is linear in the noise is classically optimal (up to constants).
+Thus, the fact that we have a sufficient error in coding for uniqueness being linear in terms of both the desired dictionary and sparse vector recovery error is optimal.
+Although optimal up to constants, our solution to Problem 1 involves constants C_1 and C_2, but it would be interesting and relevant for practical applications to determine the minimal such constants.
+In the case of sparsity k=1, we have given an example showing optimality of constants in this case.
+Finally, with respect to (c), we regard this is a fundamental open problem in the field: how many sparsely generated samples determine the linear coding model?
+(One reason to be skeptical that a polynomial suffice is again [Tillman-Pfetsch-2014].)  However, there is some good news -- if k is fixed and we constrain sparse codes \hat{x}_i to come from a polynomial number of supports, then a polynomial number of samples N is enough to guarantee uniqueness.
+In particular, a sample complexity polynomial in (m,k) can be achieved by limiting the size of the support set of the \tilde x_i, and we have revised the manuscript to discuss this fact (which, incidentally, does not follow from the results of [HS15] in the noiseless case).
+
+It is true, however, that we have not proven the tightness of these conditions and the manuscript is therefore not conclusive regarding the central problems of sparse linear coding.
+We believe that these sufficient conditions yield strong enough conclusions to stand on their own; for instance, in synchronizing device parameters for a particular sparsely representable sensory ensemble.
 Nonetheless, we have included in our revised manuscript some discussion of where the results can be tightened (e.g.
@@
 4).
-A sample complexity polynomial in (m,k) can be achieved, however, by limiting the size of the support set of the \tilde x_i, and we have revised the manuscript to discuss this fact (which, incidentally, does *not* follow from the results of [Hillar & Sommer (2015)] in the noiseless case).
-[And for fixed k […]]
 
@@
 We assume the reviewer must instead be concerned with what additional practical “take-away” message our manuscript contains.
-In brief, it is this: there exists a procedure by which one can determine if one’s proposed solution to Prob.
+One significant one is the outline of a procedure which can affirm if one’s proposed solution to Prob.
 1 or Prob.
@@
 
-** IS THAT ENOUGH FOR PRACTICAL IMPLICATIONS..? **
-
-The reviewer also raises the concern that, regardless of practical implications, our results may amount to an incremental advance over those of [Hillar & Sommer (2015)] by way of similar techniques.
+The reviewer also raises the concern that, regardless of practical implications, our results may amount to an incremental advance over those of [HS15] by way of similar techniques.
 We disagree with this assessment on both counts: our main result (Thm.
-1) goes far beyond a straightforward extension of that in [Hillar & Sommer (2015)] to the noisy case and this required a significant deviation from their approach.
+1) goes far beyond a straightforward extension of that in [HS15] to the noisy case and this required a significant deviation from their approach.
 
@@
 1 is presented in the manuscript.
-As observed by our second reviewer, however, the extension to the noisy case did indeed require an original combination of several results in the literature.
-Specifically, the main difficulty was to generalize Lemma 1 to the case where the k-dimensional subspaces spanned by corresponding sub-matrices of A and B are assumed only to be proximal (small ‘d’), and not identical as in [Hillar & Sommer (2015)].
-In contrast to the noiseless case, here it must be explicitly demonstrated that this proximity relation is propagated through the repeated intersections of these sub-matrix spans all the way down to the spans of dictionary elements themselves.
+As observed by our second reviewer, however, the extension to the noisy case did indeed require an novel combination of several results in the literature.
+Specifically, the main difficulty was to generalize Lemma 1 to the case where the k-dimensional subspaces spanned by corresponding (through the map \pi) submatrices of A and B are assumed only to be proximal (small ‘d’), and not identical as in [HS15].
+In contrast to the noiseless case, here it must be explicitly demonstrated that this proximity relation is propagated through the repeated intersections of these submatrix spans all the way down to the spans of dictionary elements themselves.
 We designed and proved Lemma 4 to address this issue, which draws its bound from the convergence guarantees of an alternating projections algorithm first proposed by von Neumann.
@@
 Our proof of Lemma 1 diverges perhaps even more significantly from the approach taken in [HS15] by way of Lemma 5.
-Key to our reduction of the sample complexity given in [HS15] by an exponential factor is the introduction of a combinatorial design (the ‘singleton intersection property’) for the support sets.
+Key to our reduction of the sample complexity given in [HS15] by an exponential factor is the introduction of a combinatorial design (the "singleton intersection property") for support sets.
 Since in this case the map \pi from supports in the hypergraph to {[m] \choose k} is not surjective, one cannot apply the same inductive method as in [HS15], which freely chooses supports in the codomain to intersect at (k-1) nodes and map back to some corresponding (k-1)-sized intersection of supports in the domain.
@@
 
-To be clear, the new perspective we take on the problem yields the following powerful conclusions beyond those of a straightforward extension of the noiseless result of [Hillar & Sommer (2015)] to the noisy case:
+To be clear, the new perspective we take on the problem yields the following powerful conclusions beyond those of a straightforward extension of [HS15] to noise:
 
-1) An extension to the case where the number of dictionary elements is unknown: The results of [Hillar & Sommer (2015)] only apply to the case where the matrix B has the same number of columns as A.
+1) An extension to the case where the number of dictionary elements is unknown: The results of [HS15] only apply to the case where the matrix B has the same number of columns as A.
 We forgo this assumption and show that B must have at least as many columns as A and contains (up to noise) a subset of the columns of A.
@@
 
-2) A significant reduction in sample complexity: To identify the n x m generating dictionary A, [Hillar & Sommer (2015)] require that data be sampled from *every* k-dimensional subspace spanned by the m columns of A (that is, {m \choose k} subspaces in total).
+2) A significant reduction in sample complexity: To identify the n x m generating dictionary A, [HS15] require that data be sampled from every k-dimensional subspace spanned by the m columns of A (that is, {m \choose k} subspaces in total).
 We show that the data need only be sampled from m subspaces in total (e.g.
@@
 when m = k^2, take the supports to be the rows and columns of [m] arranged in a square grid).
-Moreover, if the size of the support set of reconstructing codes is polynomial in m,k then the pigeonholing argument in the proof of Thm.
-1 requires only a polynomial number of samples distributed over a polynomial number of supports; thus N is polynomial in m, k.
-This point was only hinted at in the Discussion section of our original submission, but we have included it in the updated manuscript to make clear the power of our approach over that taken in [Hillar & Sommer (2015)].
-[For fixed k…]
+Moreover, if the size of the support set of reconstructing codes is polynomial in m and k, then the pigeonholing argument in the proof of Thm.
+1 requires only a polynomial number of samples distributed over a polynomial number of supports; thus, N is polynomial in m, k.
+This point was only hinted at in the Discussion section of our original submission, but we have included it in the updated manuscript to make clear the power of our approach over that taken in [HS15].
 
-3) No spark condition requirement for the generating matrix A: One of the mathematically significant contributions made by [Hillar & Sommer (2015)] was to forgo the constraint that the recovery matrix B also satisfy the spark condition, in contrast to all previously known uniqueness results which (either explicitly or implicitly) made this assumption.
+3) No spark condition requirement for the generating matrix A: One of the mathematically significant contributions made by [HS15] was to forgo the constraint that the recovery matrix B also satisfy the spark condition, in contrast to all previously known uniqueness results which (either explicitly or implicitly) made this assumption.
 Our proof is powerful enough to show that, in fact, even the matrix A need not satisfy the spark condition to be identifiable!
-Rather, it need only be injective on the union of subspaces with supports that form sets in a hypergraph satisfying the singleton intersection property (SIP).
+[???DO WE HAVE AN EXAMPLE OF THIS KIND OF MATRIX A???]  Rather, it need only be injective on the union of subspaces with supports that form sets in a hypergraph satisfying the singleton intersection property (SIP).
 We had omitted this point in our original submission of the manuscript to keep things simple, but have decided to include this interesting fact in our resubmission.
@@
 2, that of most interest to practitioners of dictionary learning methods, is to our knowledge the first of its kind in both the noise-free and noisy domains.
-We recognize that this was not clearly communicated in the Discussion section of our submitted manuscript, which begins: “In this note, we generalized the approach of (18) to prove the stability of unique solutions to Probs.
-1 and 2 […]”
+We recognize that this was not clearly communicated in the Discussion section of our submitted manuscript, and we have adjusted the manuscript accordingly.
+
+Finally, we should mention that our main mathematical results justify the neurally plausible model of bottleneck communication between brain regions, first explained in depth in this NIPS paper [IHS10] and then in a review of sparse linear coding applications to neuroscience [GS12].
 
@@
 
-RESPONSE: Yes, though actually for every S \in E there are *more than* (k-1)\choose{\bar{m},k} vectors with support in S (not “at least”).
+RESPONSE: Yes, though actually for every S \in E there are "more than" (k-1)\choose{\bar{m},k} vectors with support in S (not “at least”).
 Thank you for helping us to clarify our statements.
@@
 
-RESPONSE: We appreciate this question and have added a discussion of this comparison to the manuscript (all sample complexities improve in this work) [DO THIS].
+RESPONSE: We appreciate this question and have added comments of this comparison to the manuscript (all sample complexities improve in this work).
 Many thanks for your careful review of the mathematics.
 We have tried and continue to try to be as clear, concise, and correct as we possibly can to elevate this work into the top echelon of applied mathematical theory papers.
-
-[Do comparison here, state that noiseless is a corollary of our noisy and therefore we don’t discuss the comparison in the paper.
-They have the table only because they needed randomness to get what we get with SIP.
-We’re willing to add it if you insist, but we think it detracts from the paper..]
 
@@
 1 are satisfied by random data.
-We have provided an ‘almost certain’ guarantee of this flavor in Cor 3, wherein the sparse vector supports are constrained to form a hypergraph satisfying the SIP.
+We have provided an "almost certain" guarantee of this flavor in Cor 3, wherein the sparse vector supports are constrained to form a hypergraph satisfying the SIP.
 It would be interesting to calculate furthermore the probability that random supports form a hypergraph satisfying the SIP.
@@
 RESPONSE: We have determined explicit forms for the effectively computable constants in Theorem 1.
-[But they are not feasible to compute, since they require calculating the RIP of all k-wise subsets of the data.
-Revive NP-hard argument?]
 
@@
 RESPONSE: Yes, there is indeed.
-While all existing uniqueness results require a sufficient number of samples be drawn from *each* of {m \choose k} possible supports, we have shown that it is enough that a sufficient number of samples be drawn from every support in a subset of drastically smaller size, provided this subset forms a regular hypergraph satisfying the SIP.
+While all existing uniqueness results require a sufficient number of samples be drawn from each of {m \choose k} possible supports, we have shown that it is enough that a sufficient number of samples be drawn from every support in a subset of drastically smaller size, provided this subset forms a regular hypergraph satisfying the SIP.
 As was pointed out in our manuscript, a support set of size m satisfying these criteria can always be constructed for any k < m (e.g.
@@
 RESPONSE: Both reviewers have raised this concern and we again thank the editor for the opportunity to address it.
-It seems both reviewers have not noticed the several ways in which our results generalize the modern results of [Hillar & Sommer (2015)] beyond a straightforward extension to the noisy case, not to mention our solution to the optimization Prob.
+It seems both reviewers have not noticed the several ways in which our results generalize the modern results of [HS15] beyond a straightforward extension to the noisy case, not to mention our solution to the optimization Prob.
 2, which as far as we know is the first of its kind and of most interest to practitioners.

### 2017-08-13 manuscripts/PNAS/review/point_by_point_response.txt
coring

--- 2017-08-13 manuscripts/PNAS/review/point_by_point_response.txt
@@
 We have also clarified in our resubmission how it is that B_{pi(S)} can be replaced with B_{pi(T)} (it is because d(U, V) \leq d(U’,V) whenever U \subseteq U’).
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Checking algorithm for Problem 1:
+- Learn by any algorithm a dictionary A and codes x_i that solve Problem 1.
+- Check that that A and the x_i satisfy the assumptions of Thm. 1:
+   - List the support sets of the x_i 
+      - Discard those for which there are (k-1){m \choose k} or fewer x_i with that support.
+      - Discard those for which the supported x_i are not in GLP. (This should also exclude any supports less than k in size.)
+   - From the support sets that remain, list all k-uniform hypergraphs with supports drawn from this set that satisfy the SIP
+   - List the k-uniform hypergraphs over which A is injective.
+   - Discard those for which there aren’t more than (k-1){m \choose k} x_i in general linear position on each support of the hyper graph.
+   - For each of the hyper graphs, determine from A, the x_i 
+   - If A satisfies spark condition, check that the x_i in some hypergraph satisfying the SIP have enough samples each, calculate the constants, check that you encode below the constants.

### 2017-08-14 manuscripts/PNAS/chazthm_pnas.tex
added todos in manu

@@
 
-\significancestatement{Many natural signals (visual scenery, speech, EEG, etc.) lacking domain-specific formal models can nonetheless be usefully characterized as linear combinations of few elementary waveforms drawn from a large `dictionary'.
+\significancestatement{Many natural signals (visual scenery, speech, EEG, etc.) lacking domain-specific formal models can nonetheless be usefully characterized as linear combinations of few elementary waveforms drawn from a large ``dictionary".
 We give general conditions guaranteeing when such dictionaries are uniquely and stably determined by data.
@@
 
-\authordeclaration{The authors declare no conflict of interest.}
+% \authordeclaration{The authors declare no conflict of interest.}
 \correspondingauthor{\textsuperscript{1}To whom correspondence should be addressed. E-mail: chaz@berkeley.edu, chillar@msri.org}
@@
 
+We comment that quite often theorists in algorithm development solve the related $\ell_1$ problem, which can be shown to be applicable to 
+solving $\ell_0$ problems in certain cases.  [*** IMPROVE ON THIS ***]
+
 All other proofs are relegated to the Section \ref{proofs}. 
@@
 
+[*** Make notation $L_{2\mathcal{H}}$ ***]
+
 A vector $\mathbf{x}$ is said to be \emph{supported} in $S \subseteq [m]$ when $\mathbf{x} \in \text{\rm span}\{\mathbf{e}_j: j\in S\}$, where $\mathbf{e}_j$ are the standard basis in $\mathbb R^m$.
@@
 
+[*** TODO: remove $J$ from this ***]
+
 %To be clear, the implication of Thm.~\ref{DeterministicUniquenessTheorem} is that $Y = \{\mathbf{Ax}_1, \ldots, \mathbf{Ax}_N\}$ has a stable $k$-sparse representation in $\mathbb{R}^m$, with \eqref{def1} guaranteed provided $\varepsilon$ in Def.~\ref{maindef} does not exceed:
@@
 For sake of brevity, we delay to the next section a clear statement of this more general result.
+
+[*** Explain Weaker than spark condition example ***]
 
@@
 
+[*** We remark about algorithms ***]
+
+We remark that there is a strong application to theoretical neuroscience.
+
+\begin{corollary}
+Unsupervised neurally plausible sparse feature learning through a wiring bottleneck recovers original sensory representations and neural activities.
+\end{corollary}
+
+[*** Make clearer / motivate better ***]
+
+[*** Also discuss uniquness of sparse sensory representations more generally, like Gabors ***]
+
 \section{Proofs of Theorem~\ref{DeterministicUniquenessTheorem} and Corollary~\ref{SLCopt}}\label{DUT}
 
-As mentioned in the previous section, Thm.~\ref{DeterministicUniquenessTheorem} is a particular case of a more general result that forgoes the assumption that $\mathcal{H} \subseteq {[m] \choose k}$ is regular and satisfies the SIP.
+%%%%%%%%%%%%%%
+% need to cut maybe: 
+%As mentioned in the previous section, Thm.~\ref{DeterministicUniquenessTheorem} is a particular case of a more general result that forgoes the assumption that $\mathcal{H} \subseteq {[m] \choose k}$ is regular and satisfies the SIP.
 If instead we require only that the stars $\cap h(i)$ intersect at singletons for all $i \leq q$ (assuming that the nodes of $\mathcal{H}$ are labeled in some order of non-increasing degree), we have that $\bar m \geq k|\mathcal{H}| / \deg(1)$ and, provided $\bar m < k|\mathcal{H}| / (\deg(1) - 1)$, the non-empty submatrix $J$ is of size equal to the largest number $p$ satisfying:
-\begin{align}\label{pcond}
-\sum_{i=\ell}^{m} \deg(i) > (\bar m + 1 - \ell) (\deg(\ell) - 1) \ \ \text{for all } \ell \leq p \leq q.
-\end{align}
-Specifically, $J$ contains all nodes of degree exceeding $\deg(p)$ and some subset of those with degreee equal to $\deg(p)$.
+%\begin{align}\label{pcond}
+%\sum_{i=\ell}^{m} \deg(i) > (\bar m + 1 - \ell) (\deg(\ell) - 1) \ \ \text{for all } \ell \leq p \leq q.
+%\end{align}
+%Specifically, $J$ contains all nodes of degree exceeding $\deg(p)$ and some subset of those with degreee equal to $\deg(p)$.
 For the benefit of the reader, we do not prove explicitly this more general result below; it can be discerned from how exactly Lemma \ref{NonEmptyLemma} is incorporated into the proof of Lem.~\ref{MainLemma}.
+%%%%%%%%%%%%%%%%
+
 %As mentioned in the previous section, Thm.~\ref{DeterministicUniquenessTheorem} is a particular case of a more general result, which requires a looser set of constraints on the hypergraph $\mathcal{H}$ and which applies to $n \times \bar m$ matrices $\mathbf{B}$ (and $\bar m$-dimensional codes $\mathbf{\bar x}_i$) with $\bar m \neq m$:
@@
 
-In this note, we generalized the approach of \cite{Hillar15} to prove the stability of unique solutions to Probs.~\ref{InverseProblem} and \ref{OptimizationProblem} while significantly reducing the known sample complexity.
+[*** ADD:  Ganguli, Deep Learning, constants, tightness, ***]
+
+In this note, we prove the stability of unique solutions to Probs.~\ref{InverseProblem} and \ref{OptimizationProblem} while significantly reducing the known sample complexity.
 Our results justify the application of the sparse linear coding model to blind source separation problems, wherein the goal is to infer the generating dictionary and sparse codes from noisy measurements, \eqref{LinearModel}.
@@
 
+Deep learning noise issues: \cite{szegedy2013intriguing, goodfellow2014explaining}.
+
 \acknow{We thank Friedrich Sommer and Darren Rhea for early thoughts, and Ian Morris for posting \eqref{eqdim} online.}
 \showacknow % Display the acknowledgments section
+
+[*** TODO: make journals abbreviated references ***]
 
@@
 \begin{proof}[Proof (sketch) of Cor.~\ref{ProbabilisticCor}]
-First, note that if a set of measure spaces $\{(X_{\ell}, \Sigma_{\ell}, \nu_{\ell})\}_{\ell=1}^p$ has that $\nu_{\ell}$ is absolutely continuous with respect to $\mu$ for all $\ell \in [p]$, where $\mu$ is the standard Borel measure on $\mathbb{R}$, then the product measure $\prod_{\ell=1}^p \nu_{\ell}$ is absolutely continuous with respect to the standard Borel product measure on $\mathbb{R}^p$ (e.g.,  \cite{folland2013real}).
+First, note that if a set of measure spaces $\{(X_{\ell}, \Sigma_{\ell}, \nu_{\ell})\}_{\ell=1}^p$ has that $\nu_{\ell}$ is absolutely continuous with respect to $\mu$ for all $\ell \in [p]$, where $\mu$ is the standard Borel measure on $\mathbb{R}$, then the product measure $\prod_{\ell=1}^p \nu_{\ell}$ is absolutely continuous with respect to the standard Borel product measure on $\mathbb{R}^p$.
+% for space:  (e.g.,  \cite{folland2013real}).
 By Thm.~\ref{robustPolythm}, there is a polynomial that is nonzero whenever $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$; in particular, this property (stability) holds with probability one.
@@
 
-\clearpage
+%\clearpage
 
-\section{$\ell_1$-norm Extension}
-
-\begin{problem}\label{OptimizationProblemL1}
-Find a matrix $\mathbf{B}$ and vectors \mbox{$\mathbf{\bar x}_1, \ldots, \mathbf{\bar x}_N \in \mathbb{R}^m$} that solve:
-\begin{align}\label{minsum}
-\min \sum_{i = 1}^N \|\mathbf{\bar x}_i\|_1 \ \ 
-\text{subject to} \ \ \|\mathbf{z}_i - \mathbf{B}\mathbf{\bar x}_i\|_2 \leq \eta, \ \text{for all $i$}.
-\end{align}
-\end{problem}
+%\section{$\ell_1$-norm Extension}
+%
+%\begin{problem}\label{OptimizationProblemL1}
+%Find a matrix $\mathbf{B}$ and vectors \mbox{$\mathbf{\bar x}_1, \ldots, \mathbf{\bar x}_N \in \mathbb{R}^m$} that solve:
+%\begin{align}\label{minsum}
+%\min \sum_{i = 1}^N \|\mathbf{\bar x}_i\|_1 \ \ 
+%\text{subject to} \ \ \|\mathbf{z}_i - \mathbf{B}\mathbf{\bar x}_i\|_2 \leq \eta, \ \text{for all $i$}.
+%\end{align}
+%\end{problem}
 

### 2017-08-14 manuscripts/PNAS/chazthm_pnas.tex
chaz

@@
 
-\keywords{Sparse coding, dictionary learning, matrix factorization, compressive sensing, inverse problems}
+\keywords{Sparse coding, dictionary learning, matrix factorization, compressive sensing, inverse problems, blind source separation}
 
@@
 \end{align}
-
-which would be, in any case, necessary for uniqueness. Our concern here is solution stability with respect to noise.
+%
+which would be, in any case, necessary for uniqueness of the $\mathbf{x}_i$. Our concern here is solution stability with respect to noise.
 
@@
 where we write $L_{k}$ when $\mathcal{H} = {[m] \choose k}$.\footnote{We note that the quantity $1 - \sqrt{k} L_k(\mathbf{M})$ is also known in the compressive sensing literature as the (asymmetric) lower restricted isometry constant \cite{Blanchard2011}.} Clearly, for any $\mathbf{M}$ satisfying \eqref{SparkCondition}, we have $L_{k'}(\mathbf{M}) > 0$ for  $k' \leq 2k$.
-Note that if $\mathcal{H}$ covers $[m]$ then $L_2 \geq L_{\mathcal{H}+\mathcal{H}}$.
-
-[*** Make notation $L_{2\mathcal{H}}$ ***]
+Note that if $\mathcal{H}$ covers $[m]$ then $L_2 \geq L_{2\mathcal{H}}$.
 
 A vector $\mathbf{x}$ is said to be \emph{supported} in $S \subseteq [m]$ when $\mathbf{x} \in \text{\rm span}\{\mathbf{e}_j: j\in S\}$, where $\mathbf{e}_j$ are the standard basis in $\mathbb R^m$. 
-Denote by $\mathbf{x}^J$ the subvector formed from the entries of $\mathbf{x}$ indexed by $J$.
-A set of $k$-sparse vectors is said to be in \emph{general linear position} when any $k$ of them are linearly independent.
-The following is a precise statement of our main result.
+%Denote by $\mathbf{x}^J$ the subvector formed from the entries of $\mathbf{x}$ indexed by $J$. 
+A set of $k$-sparse vectors is said to be in \emph{general linear position} when any $k$ of them are linearly independent. The following is a precise statement of our main result.
 
 \begin{theorem}\label{DeterministicUniquenessTheorem}
-Fix a real $n \times m$ matrix $\mathbf{A}$ with $L_{\mathcal{H}+\mathcal{H}}(\mathbf{A}) > 0$ for some $r$-regular $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP.
-If the sequence \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} contains, for each $S \in \mathcal{H}$, more than $(k-1){m \choose k}$ $k$-sparse vectors in general linear position supported in $S$, then there is a constant\footnote{We delay defining the constant $C_1$ until Section \ref{DUT} (\eqref{Cdef1}).} $C_1 > 0$ for which the following holds for all $\varepsilon < L_{2}(\mathbf{A}) / C_1$:
+Fix a real $n \times m$ matrix $\mathbf{A}$ with $L_{2\mathcal{H}}(\mathbf{A}) > 0$ for some $r$-regular $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP.
+If the sequence \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} contains, for each $S \in \mathcal{H}$, more than $(k-1){m \choose k}$ $k$-sparse vectors in general linear position supported in $S$, then there is a constant\footnote{We delay defining the constant $C_1$ until Section \ref{DUT} (\eqref{Cdef1}).} $C_1 > 0$ for which the following holds for all\footnote{The condition $\varepsilon < L_2(\mathbf{A}) /C_1$ is necessary; otherwise,  with \mbox{$\mathbf{A}$ = $\mathbf{I}$} and $\mathbf{a}_i = \mathbf{e}_i$, there is a $\mathbf{B}$ and $1$-sparse $\mathbf{b}_i$ with $|\mathbf{A}\mathbf{a}_i - \mathbf{B}\mathbf{b}_i|_2 \leq \varepsilon$ violating \eqref{Cstable}.} $\varepsilon < L_{2}(\mathbf{A}) / C_1$:
 
@@
 \begin{align}\label{b-PDa}
-\|\mathbf{x}^J_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\bar x}^{\bar J}_i\|_1 &\leq  \left( \frac{ 1+C_1 \|\mathbf{x}^{J}_i\|_1 }{ L_{2k}(\mathbf{A}) -  C_1\varepsilon } \right) \varepsilon \ \  \text{for $i \in [N]$}.
+%\|\mathbf{x}^J_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\bar x}^{\bar J}_i\|_1 &\leq  \left( \frac{ 1+C_1 \|\mathbf{x}^{J}_i\|_1 }{ L_{2k}(\mathbf{A}) -  C_1\varepsilon } \right) \varepsilon \ \  \text{for $i \in [N]$}.
+\|\mathbf{x}_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\bar x}_i\|_1 &\leq  \left( \frac{ 1+C_1 \|\mathbf{x}_i\|_1 }{ L_{2k}(\mathbf{A}) -  C_1\varepsilon } \right) \varepsilon \ \  \text{for $i \in [N]$}.
 \end{align}
+%
+where $\mathbf{x}_i$ and $\mathbf{\bar x}_i$ here represent subvectors formed from the entries indexed by $J$ and $\bar J$, respectively. 
 \end{theorem}
-% You can recover matrices that don't satisfy the spark condition, but to uniquely recover k-sparse codes (since no limitation on their supports!) you need to have the spark condition.
-i guess...?
-Or can we use our knowledge of the particular permutation P to get rid of spark condition?
-
-[*** TODO: remove $J$ from this ***]
 
@@
 \end{align}
-
 %In fact, a more general result (stated clearly in the next section) can be gleaned from our method of proving Thm.~\ref{DeterministicUniquenessTheorem}.
@@
 When $\bar m = m$, we recover Thm.~\ref{DeterministicUniquenessTheorem}.
-Regarding the assumptions of Thm.~\ref{DeterministicUniquenessTheorem}, it is easy to verify that for every $k < m$, there is a regular $k$-uniform hypergraph that satisfies the SIP; for instance, take the consecutive intervals of length $k$ in some cyclic order on $[m]$.
-In fact, even if $\mathcal{H}$ is not regular or only partially satisfies the SIP, a relation between $\bar m$ and the degree sequence of nodes in $\mathcal{H}$ may give the indices $J \subseteq [m]$.
+
+%In fact, even if $\mathcal{H}$ is not regular or only partially satisfies the SIP, a relation between $\bar m$ and the degree sequence of nodes in $\mathcal{H}$ may give the indices $J \subseteq [m]$.
 For sake of brevity, we delay to the next section a clear statement of this more general result.
 
-[*** Explain Weaker than spark condition example ***]
-
-It also happens that producing sparse codes $\mathbf{x}_i$ in general linear position is straightforward with a ``Vandermonde'' matrix construction (e.g., see \cite{Hillar15}). We therefore have:
+%Regarding the assumptions of Thm.~\ref{DeterministicUniquenessTheorem}, 
+It so happens that producing sparse codes $\mathbf{x}_i$ in general linear position is straightforward with a ``Vandermonde'' matrix construction (e.g., see \cite{Hillar15}). We therefore have:
 
 \begin{corollary}\label{DeterministicUniquenessCorollary}
-Given a regular hypergraph $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP, there are $N =  |\mathcal{H}| \left[ (k-1){m \choose k} + 1  \right]$ vectors \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} such that every matrix $\mathbf{A}$ with $L_{\mathcal{H}+\mathcal{H}}(\mathbf{A}) > 0$ generates a dataset $Y = \{\mathbf{A}\mathbf{x}_1, \ldots, \mathbf{A}\mathbf{x}_N\}$ with a stable $k$-sparse representation in $\mathbb{R}^m$.
+Given a regular hypergraph $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP, there are $N =  |\mathcal{H}| \left[ (k-1){m \choose k} + 1  \right]$ vectors \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} such that every matrix $\mathbf{A}$ with $L_{2\mathcal{H}}(\mathbf{A}) > 0$ generates a dataset $Y = \{\mathbf{A}\mathbf{x}_1, \ldots, \mathbf{A}\mathbf{x}_N\}$ with a stable $k$-sparse representation in $\mathbb{R}^m$.
 \end{corollary}
 
-As mentioned above, there exist $k$-uniform regular hypergraphs $\mathcal{H}$ with the SIP having cardinality $|\mathcal{H}| = m$, implying the lower bound for sample size $N$ from the introduction.
+One can easily verify that for every $k < m$, there is a regular $k$-uniform hypergraph that satisfies the SIP; for instance, take $\mathcal{H}$ to be the consecutive intervals of length $k$ in some cyclic order on $[m]$, for which Cor.~\ref{DeterministicUniquenessCorollary} implies the lower bound for sample size $N$ from the introduction.
 In many cases, however, the SIP is achievable with far fewer supports; for example, when $k = \sqrt{m}$, take $\mathcal{H}$ to be the $2k$ rows and columns formed by arranging $[m]$ in a square grid.
+
+%As mentioned above, there exist $k$-uniform regular hypergraphs $\mathcal{H}$ with the SIP having cardinality $|\mathcal{H}| = m$,
+
+We note that unlike what previous works have required, $\mathbf{A}$ need not satisfy the spark condition to be recoverable from data.
+As an example for $k=2$, let $\mathbf{A} = [ \mathbf{e}_1, \ldots, \mathbf{e}_5, \mathbf{v}]$ where $\mathbf{v} = \mathbf{e}_1 + \mathbf{e}_3 + \mathbf{e}_5$.
+and take $\mathcal{H}$ to be the set of all consecutive pairs of $[m]$ arranged in cyclic order.
+Then $\mathbf{A}$ satisfies the assumptions of Thm.~\ref{DeterministicUniquenessTheorem} without satisfying the spark condition.
+%(since $\{ \mathbf{A}_1, \mathbf{A}_3, \mathbf{A}_5, \mathbf{A}_6\}$ is not a linearly independent set).
 
@@
 \begin{align}\label{delrho}
-L_{\mathcal{H} + \mathcal{H}}(\mathbf{A}) %\leq \frac{\|\mathbf{A}\mathbf{x}\|_2}{\sqrt{2k} \|\mathbf{x}\|_2} 
+L_{2\mathcal{H}}(\mathbf{A}) %\leq \frac{\|\mathbf{A}\mathbf{x}\|_2}{\sqrt{2k} \|\mathbf{x}\|_2} 
 \leq  \max_j\|\mathbf{A}_j\|_2.
@@
 \begin{lemma}\label{MainLemma}
-Suppose $\mathbf{A} \in \mathbb{R}^{n \times m}$ has $L_{\mathcal{H}+\mathcal{H}}(\mathbf{A}) > 0$ for some $r$-regular $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP.
+Suppose $\mathbf{A} \in \mathbb{R}^{n \times m}$ has $L_{2\mathcal{H}}(\mathbf{A}) > 0$ for some $r$-regular $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP.
 There exists $C_2 > 0$ for which the following holds for all $\varepsilon < L_2(\mathbf{A}) / C_2$:
@@
 The constant $C_1 > 0$ in Thm.~\ref{DeterministicUniquenessTheorem} is then given by\footnote{Note that $\|\mathbf{AX}_{I(S)}\mathbf{c}\|_2 \geq \sqrt{k} L_\mathcal{H}(\mathbf{A})\|\mathbf{X}_{I(S)}\mathbf{c}\|_2 \geq k L_\mathcal{H}(\mathbf{A}) L_k(\mathbf{X}_{I(S)})\|\mathbf{c}\|_2$ for $S \in \mathcal{H}$ and $k$-sparse $\mathbf{c}$.
-Therefore, $L_k(\mathbf{AX}_{I(S)}) \geq \sqrt{k} L_\mathcal{H}(\mathbf{A}) L_k(\mathbf{X}_{I(S)}) > 0$ since $L_{\mathcal{H}+\mathcal{H}}(\mathbf{A})> 0$ and $L_k(\mathbf{X}_{I(S)}) > 0$ by general linear position of the $\mathbf{x}_i$.
+Therefore, $L_k(\mathbf{AX}_{I(S)}) \geq \sqrt{k} L_\mathcal{H}(\mathbf{A}) L_k(\mathbf{X}_{I(S)}) > 0$ since $L_{2\mathcal{H}}(\mathbf{A})> 0$ and $L_k(\mathbf{X}_{I(S)}) > 0$ by general linear position of the $\mathbf{x}_i$.
 Thus, $C_1 > 0$.}:
@@
 
-It follows from $L_{\mathcal{H}+\mathcal{H}}(\mathbf{A}) > 0$ and the general linear position of the $\mathbf{x}_i$ that $L(\mathbf{AX}_{K}) > 0$; that is, the columns of the $n \times k$ matrix $\mathbf{AX}_K$ form a basis for $\bm{\mathcal{A}}_S$.
+It follows from $L_{2\mathcal{H}}(\mathbf{A}) > 0$ and the general linear position of the $\mathbf{x}_i$ that $L(\mathbf{AX}_{K}) > 0$; that is, the columns of the $n \times k$ matrix $\mathbf{AX}_K$ form a basis for $\bm{\mathcal{A}}_S$.
 Fixing $\mathbf{0} \neq \mathbf{y} \in \bm{\mathcal{A}}_S$, there then exists $\mathbf{0} \neq \mathbf{c} = (c_1, \ldots, c_k) \in \mathbb{R}^k$ such that $\mathbf{y} = \mathbf{AX}_K\mathbf{c}$.
@@
 We bound the number of $k$-sparse $\mathbf{\bar x}_i$ and then apply Thm.~\ref{DeterministicUniquenessCorollary}. 
-First, observe that no more than $(k-1)|\mathcal{H}|$ of the $\mathbf{\bar x}_i$ share a support $\bar S$ of size less than $k$; otherwise, by the pigeonhole principle, at least $k$ of these indices $i$ belong to the same $K \subseteq I(S)$ for some $S \in \mathcal{H}$ and (as argued previously) \eqref{rhs222} follows.
-Since the right-hand side of \eqref{rhs222} is less than one, by \eqref{dimLem} we have the contradiction $k = \dim(\bm{\mathcal{A}}_S) \leq \dim(\bm{\mathcal{B}}_{\bar S}) \leq |\bar S|.$ The total number of $(k-1)$-sparse vectors $\mathbf{\bar x}_i$ can thus not exceed $|\mathcal{H}|(k-1){ \bar m \choose k-1}$.
-
-We now apply this fact to bound the number of $k$-sparse $\mathbf{\bar x}_i$. Let $n_p$ be the number of $\mathbf{\bar x}_i$ with $\|\mathbf{\bar x}_i\|_0 = p$.
+%We now apply this fact to bound the number of $k$-sparse $\mathbf{\bar x}_i$. 
+Let $n_p$ be the number of $\mathbf{\bar x}_i$ with $\|\mathbf{\bar x}_i\|_0 = p$.
 Since the $\mathbf{x}_i$ are all $k$-sparse, by \eqref{minsum} we have:
@@
 \begin{align}\label{eqn}
-\sum_{p = k+1}^{\bar m} n_p \leq \sum_{p = k+1}^{\bar m} (p-k) n_p \leq \sum_{p = 0}^k (k-p)n_p \leq k \sum_{p = 0}^{k-1} n_p.
+\sum_{p = k+1}^{\bar m} n_p \leq \sum_{p = k+1}^{\bar m} (p-k) n_p \leq \sum_{p = 0}^k (k-p)n_p \leq k \sum_{p = 0}^{k-1} n_p,
 \end{align}
+%
+demonstrating that the number vectors $\mathbf{\bar x}_i$ that are \emph{not} $k$-sparse is controlled by how many are $(k-1)$-sparse.
 
-Therefore, no more than $|\mathcal{H}|k(k-1){ \bar m \choose k-1}$ vectors $\mathbf{\bar x}_i$ are \emph{not} $k$-sparse.
+Next, observe that no more than $(k-1)|\mathcal{H}|$ of the $\mathbf{\bar x}_i$ share a support $\bar S$ of size less than $k$; otherwise, by the pigeonhole principle, at least $k$ of these indices $i$ belong to the same $K \subseteq I(S)$ for some $S \in \mathcal{H}$ and (as argued previously) \eqref{rhs222} follows.
+Since the right-hand side of \eqref{rhs222} is less than one, by \eqref{dimLem} we have the contradiction $k = \dim(\bm{\mathcal{A}}_S) \leq \dim(\bm{\mathcal{B}}_{\bar S}) \leq |\bar S|.$ The total number of $(k-1)$-sparse vectors $\mathbf{\bar x}_i$ can thus not exceed $|\mathcal{H}|(k-1){ \bar m \choose k-1}$.
+
+Therefore, no more than $|\mathcal{H}|k(k-1){ \bar m \choose k-1}$ vectors $\mathbf{\bar x}_i$ are not $k$-sparse.
 Since for every $S \in \mathcal{H}$ there are over $(k-1)\left[ {\bar m \choose k} + |\mathcal{H}|k{ \bar m \choose k-1} \right]$ vectors $\mathbf{x}_i$ supported there, it follows that more than $(k-1){\bar m \choose k}$ of them have corresponding $\mathbf{\bar x}_i$ that are $k$-sparse.

### 2017-08-14 manuscripts/PNAS/chazthm_pnas.tex
refs fixed and minor typos in manu

@@
 
-\keywords{Sparse coding, dictionary learning, matrix factorization, compressive sensing, inverse problems, blind source separation}
+\keywords{Sparse coding, dictionary learning, matrix factorization, compressed sensing, inverse problems, blind source separation}
 
@@
 
-Motivated by these discoveries and earlier work in the theory of neural communication \cite{Coulter10, Isely10}, we address when dictionaries and the sparse representations they induce are uniquely determined by data.
+Motivated by these discoveries and earlier work in the theory of neural communication \cite{Isely10}, we address when dictionaries and the sparse representations they induce are uniquely determined by data.
 Answers to this question also have other real-world implications.
@@
 Note that any particular solution $(\mathbf{B}, \mathbf{\bar x}_1 \ldots, \mathbf{\bar x}_N)$ to this problem gives rise to an orbit of equivalent solutions $(\mathbf{BPD}, \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\bar x}_1, \ldots, \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\bar x}_N)$, where $\mathbf{P}$ is any permutation matrix and $\mathbf{D}$ any invertible diagonal.
-Previous theoretical work addressing the noiseless case $\eta =0$ (e.g., \cite{li2004analysis, Georgiev05, Aharon06, Hillar15}) has shown that a solution to Prob.~\ref{InverseProblem} (when it exists) is indeed unique up to this inherent ambiguity provided the $\mathbf{x}_i$ are sufficiently diverse and the generating matrix $\mathbf{A}$ satisfies the \textit{spark condition} from compressive sensing:
+Previous theoretical work addressing the noiseless case $\eta =0$ (e.g., \cite{li2004analysis, Georgiev05, Aharon06, Hillar15}) has shown that a solution to Prob.~\ref{InverseProblem} (when it exists) is indeed unique up to this inherent ambiguity provided the $\mathbf{x}_i$ are sufficiently diverse and the generating matrix $\mathbf{A}$ satisfies the \textit{spark condition} from compressed sensing:
 \begin{align}\label{SparkCondition}
@@
 Note that if $\mathcal{H}$ covers $[m]$, then $L_2 > L_\mathcal{H}$.\footnote{The reader should beware that $L_2 = L_{[m]}$, whereas $L = L_{\{[m]\}}$.
-For even $k$, the quantity $1 - \sqrt{k} L_k(\mathbf{M})$ is also known in the compressive sensing literature as the (asymmetric) lower restricted isometry constant \cite{Blanchard2011}.} Clearly, for any $\mathbf{M}$ satisfying \eqref{SparkCondition}, we have $L_{k'}(\mathbf{M}) > 0$ for  $k' \leq 2k$.
+For even $k$, the quantity $1 - \sqrt{k} L_k(\mathbf{M})$ is also known in the compressed sensing literature as the (asymmetric) lower restricted isometry constant \cite{Blanchard2011}.} Clearly, for any $\mathbf{M}$ satisfying \eqref{SparkCondition}, we have $L_{k'}(\mathbf{M}) > 0$ for  $k' \leq 2k$.
 %\begin{align*}
@@
 %
-where we write $L_{k}$ when $\mathcal{H} = {[m] \choose k}$.\footnote{We note that the quantity $1 - \sqrt{k} L_k(\mathbf{M})$ is also known in the compressive sensing literature as the (asymmetric) lower restricted isometry constant \cite{Blanchard2011}.} Clearly, for any $\mathbf{M}$ satisfying \eqref{SparkCondition}, we have $L_{k'}(\mathbf{M}) > 0$ for  $k' \leq 2k$.
+where we write $L_{k}$ when $\mathcal{H} = {[m] \choose k}$.\footnote{We note that the quantity $1 - \sqrt{k} L_k(\mathbf{M})$ is also known in the compressed sensing literature as the (asymmetric) lower restricted isometry constant \cite{Blanchard2011}.} Clearly, for any $\mathbf{M}$ satisfying \eqref{SparkCondition}, we have $L_{k'}(\mathbf{M}) > 0$ for  $k' \leq 2k$.
 Note that if $\mathcal{H}$ covers $[m]$ then $L_2 \geq L_{2\mathcal{H}}$.
@@
 %
-for some non-empty $J, \bar J$ of size $\bar m - r(\bar m - m)$, some permutation $\mathbf{P}$ and invertible diagonal $\mathbf{D}$.
+for some nonempty $J, \bar J$ of size $\bar m - r(\bar m - m)$, some permutation $\mathbf{P}$ and invertible diagonal $\mathbf{D}$.
 
@@
 %Regarding the assumptions of Thm.~\ref{DeterministicUniquenessTheorem}, 
-It so happens that producing sparse codes $\mathbf{x}_i$ in general linear position is straightforward with a ``Vandermonde'' matrix construction (e.g., see \cite{Hillar15}). We therefore have:
+It so happens that producing sparse codes $\mathbf{x}_i$ in general linear position is straightforward with a ``Vandermonde'' matrix construction (e.g., see \cite{Hillar15}).
 
@@
 %As mentioned in the previous section, Thm.~\ref{DeterministicUniquenessTheorem} is a particular case of a more general result that forgoes the assumption that $\mathcal{H} \subseteq {[m] \choose k}$ is regular and satisfies the SIP.
-If instead we require only that the stars $\cap h(i)$ intersect at singletons for all $i \leq q$ (assuming that the nodes of $\mathcal{H}$ are labeled in some order of non-increasing degree), we have that $\bar m \geq k|\mathcal{H}| / \deg(1)$ and, provided $\bar m < k|\mathcal{H}| / (\deg(1) - 1)$, the non-empty submatrix $J$ is of size equal to the largest number $p$ satisfying:
+If instead we require only that the stars $\cap h(i)$ intersect at singletons for all $i \leq q$ (assuming that the nodes of $\mathcal{H}$ are labeled in some order of non-increasing degree), we have that $\bar m \geq k|\mathcal{H}| / \deg(1)$ and, provided $\bar m < k|\mathcal{H}| / (\deg(1) - 1)$, the nonempty submatrix $J$ is of size equal to the largest number $p$ satisfying:
 %\begin{align}\label{pcond}
@@
 \end{align}
-then $\bar m \geq m$, and provided $\bar m < mr /(r-1)$, there exists a permutation matrix $\mathbf{P}$ and invertible diagonal matrix $\mathbf{D}$ such that:
+then $\bar m \geq m$, and provided $\bar m < mr /(r-1)$, there is a permutation matrix $\mathbf{P}$ and invertible diagonal $\mathbf{D}$ such that:
 \begin{align}\label{MainLemmaBPD}
@@
 \end{align}
-for some non-empty $J, \bar J$ of size $\bar m - r(\bar m - m)$.
+for some nonempty $J, \bar J$ of size $\bar m - r(\bar m - m)$.
 \end{lemma}
@@
 
-Since there are more than $(k-1){\bar m \choose k}$ vectors $\mathbf{x}_i$ supported in $S$, by the pigeonhole principle there must be some $\bar S \in {[\bar m] \choose k}$ and set of $k$ indices $K \subseteq I(S)$ such that all $\mathbf{\bar x}_i$ with $i \in K$ are supported in $\bar S$.
+Since there are more than $(k-1){\bar m \choose k}$ vectors $\mathbf{x}_i$ supported in $S$, the pigeonhole principle gives $\bar S \in {[\bar m] \choose k}$ and a set of $k$ indices $K \subseteq I(S)$ with all $\mathbf{\bar x}_i$, $i \in K$, supported in $\bar S$.
 
@@
 %
-where the second inequality is due to $L(\mathbf{AX}_{K}) \geq L_k(\mathbf{AX}_{I(S)})$ and \eqref{Cdef1}. Since $\varepsilon < L_2(\mathbf{A})/C_1$, the result follows by Lem.~\ref{MainLemma}, .
+where the second inequality is due to $L(\mathbf{AX}_{K}) \geq L_k(\mathbf{AX}_{I(S)})$ and \eqref{Cdef1}. Finally, apply Lem.~\ref{MainLemma} with $\varepsilon < L_2(\mathbf{A})/C_1$.
 \end{proof}
@@
 The main motivation for this work, however, was to understand how seemingly universal representations emerge from sparse coding models fit to natural data by a variety of methodologies.
-We elaborate on these applications below after discussing theoretical aspects.
+We elaborate on these applications below.
 
@@
 It would therefore be of practical utility to determine the best possible dependence of $\varepsilon$ on $\delta_1, \delta_2$ in Def.\ref{maindef} as well as the minimal requirements on the number and diversity of generating codes, and we hope that other researchers continue to improve and extend our results.
-We remark that our constants have been derived for deterministic ``worst-case'' noise, whereas the ``effective'' noise might be smaller when sampled from a distribution; in such cases, the constants will improve as well.
+We remark that our constants have been derived for deterministic ``worst-case'' noise, whereas the ``effective'' noise might be smaller when sampled from a distribution.
+% ; in such cases, the constants will improve as well.
 
@@
 For instance, whether there is a sample size $N$ that is polynomial in $m,k$ gauranteeing the conclusions of Thm.~\ref{DeterministicUniquenessTheorem} has implications for the computational complexity of Probs.~\ref{InverseProblem} and \ref{OptimizationProblem} and related questions \cite{Tillmann15}.
-A re-examination of pigeonholing argument in the proof of Thm.~\ref{DeterministicUniquenessTheorem} demonstrates that this can in fact be achieved if one restricts the supports of the $\mathbf{\bar x}_i$ to a class that grows polynomially in $m, k$.
+A reexamination of pigeonholing argument in the proof of Thm.~\ref{DeterministicUniquenessTheorem} demonstrates that this can in fact be achieved if one restricts the supports of the $\mathbf{\bar x}_i$ to a class that grows polynomially in $m, k$.
 
@@
 In fact, uniqueness guarantees with minimal assumptions apply to all areas of data science and engineering that utilize learned sparse representations.
-For example, several groups have applied compressive sensing to signal processing tasks: MRI analysis \cite{lustig2008compressed}, image compression \cite{Duarte08}, and, more recently, the design of an ultrafast camera \cite{Gao14}.
-Given such effective uses of compressive sensing, it is only a matter of time before these systems incorporate dictionary learning to encode and process data (e.g., in a device that learns structure from motion \cite{kong2016prior}).
+For example, several groups have applied compressed sensing to signal processing tasks: MRI analysis \cite{lustig2008compressed}, image compression \cite{Duarte08}, and, more recently, the design of an ultrafast camera \cite{Gao14}.
+Given such effective uses of compressed sensing, it is only a matter of time before these systems incorporate dictionary learning to encode and process data (e.g., in a device that learns structure from motion \cite{kong2016prior}).
 In these cases, assurances such as those offered by our theorems certify that different devices (with different initialization, samples, etc.) will learn equivalent representations given enough data from statistically identical systems.
@@
 Our results suggest that this correspondence could be due to the ``universality'' of sparse representations in natural data, an early mathematical idea in neural theory \cite{pitts1947}.
-Furthermore, they justify the hypothesis of \cite{Coulter10, Isely10} that sparse codes passed through information bottlenecks in the brain are recovered from random projections via (unsupervised) biologically plausible sparse coding (e.g., \cite{rehnsommer2007, rozell2007neurally, ganguli2012compressed, hu2014hebbian}).
+Furthermore, they justify the hypothesis of \cite{Isely10} that sparse codes passed through information bottlenecks in the brain are recovered from random projections via (unsupervised) biologically plausible sparse coding (e.g., \cite{rehnsommer2007, rozell2007neurally, ganguli2012compressed, hu2014hebbian}).
 
-Deep learning noise issues: \cite{szegedy2013intriguing, goodfellow2014explaining}.
+Deep learning noise issues: \cite{goodfellow2014explaining}.
 
@@
 \showacknow % Display the acknowledgments section
-
-[*** TODO: make journals abbreviated references ***]
 
@@
 \end{align}
-then $\bar m \geq\sum_i \deg(i) / \deg(1)$, and if $\bar m < \sum_i \deg(i) / (\deg(1) - 1)$ then the association $i \mapsto \cap \pi(h(i))$ defines an injective map to $[\bar m]$ from some non-empty $J \subseteq [m]$ of size $p$ consisting of the union of the set of all nodes of degree exceeding $\deg(p)$ and some set of nodes all having degree equal to $\deg(p)$.
+then $\bar m \geq\sum_i \deg(i) / \deg(1)$, and if $\bar m < \sum_i \deg(i) / (\deg(1) - 1)$ then the association $i \mapsto \cap \pi(h(i))$ defines an injective map to $[\bar m]$ from some nonempty $J \subseteq [m]$ of size $p$ consisting of the union of the set of all nodes of degree exceeding $\deg(p)$ and some set of nodes all having degree equal to $\deg(p)$.
 In particular, if $\mathcal{H}$ is $r$-regular then $|J| = \bar m - r(\bar m - m)$.
@@
 By \eqref{pcond} and the upper bound on $\bar m$ we have $|T_1| >  \bar m (\deg(1) - 1)$, which implies, again by the pigeonhole principle, that there must be at least $\deg(1)$ elements of $T_1$ sharing the same first index.
-By \eqref{cond}, the intersection of the set $\mathcal{G}_1$ consisting of their second indices is non-empty.
+By \eqref{cond}, the intersection of the set $\mathcal{G}_1$ consisting of their second indices is nonempty.
 As $p \leq q$ and $\deg(1) \geq \deg(i)$ for all $i$, it must be that $|\cap \mathcal{G}_1| = 1$.
-Since $\cap \pi(\mathcal{G}_1)$ is non-empty, applying \eqref{cond} again implies $\cap \pi(\mathcal{G}_1) = \{i_1\}$ for some $i_1 \in [m]$.
+Since $\cap \pi(\mathcal{G}_1)$ is nonempty, applying \eqref{cond} again implies $\cap \pi(\mathcal{G}_1) = \{i_1\}$ for some $i_1 \in [m]$.
 If $p=1$ then we are done.

### 2017-08-14 manuscripts/PNAS/chazthm_pnas.tex
more edits appendix

@@
 for \mbox{$z^2= 1 - \prod_{\ell =1}^{k-1}(1-z_{\ell}^2)$} and \mbox{$z_{\ell} = \cos\theta\left(V_{\ell}, \cap_{s=\ell+1}^k V_s\right)$}, recalling $\theta$ from Def.~\ref{FriedrichsDefinition}.
-Together with $\Pi_{V_\ell} \Pi_V = \Pi_V$ for all $\ell \in [k]$ and $\Pi_V^2 = \Pi_V$, this yields:
-\begin{align*}
-\|\Pi_{V_k} \cdots \Pi_{V_1}\mathbf{x}  - \Pi_V \mathbf{x} \|_2 
-&= \|\left( \Pi_{V_k} \cdots\Pi_{V_1} - \Pi_V \right) (\mathbf{x} - \Pi_V\mathbf{x})\|_2 \\
-&\leq z\|\mathbf{x} - \Pi_V\mathbf{x}\|_2.
-\end{align*}
+Together with $\Pi_{V_\ell} \Pi_V = \Pi_V$ for all $\ell \in [k]$ and $\Pi_V^2 = \Pi_V$, this implies that $\|\Pi_{V_k} \cdots \Pi_{V_1}\mathbf{x}  - \Pi_V \mathbf{x} \|_2$ satisfies:
+\[\| ( \Pi_{V_k} \cdots\Pi_{V_1} - \Pi_V ) (\mathbf{x} - \Pi_V\mathbf{x})\|_2 \leq z\|\mathbf{x} - \Pi_V\mathbf{x}\|_2.\]
 
@@
 Consider the collection of pairs: $T_1 := \{(i, S): i \in \pi(S), S \in \mathcal{H}\}$, which number $|T_1| = \sum_{S \in \mathcal{H}} |\pi(S)| \geq \sum_{S \in \mathcal{H}} |S| = \sum_{i \in [m]} \deg(i)$.
-Note that assumption \eqref{cond} implies $\bar m \geq |T_1| / \deg(1)$, since otherwise pigeonholing the elements of $T_1$ with respect to their set of possible first indices $[\bar m]$ would lead us to conclude that there are more than $\deg(1)$ sets in $\mathcal{H}$ sharing a common element.
+Note that assumption \eqref{cond} implies $\bar m \geq |T_1| / \deg(1)$, since otherwise pigeonholing the elements of $T_1$ with respect to their set of possible first indices $[\bar m]$ would contradict that there are more than $\deg(1)$ sets in $\mathcal{H}$ sharing a common element.
 %QUESTION: Do we really need to say this..?
@@
 % for space:  (e.g.,  \cite{folland2013real}).
-By Thm.~\ref{robustPolythm}, there is a polynomial that is nonzero whenever $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$; in particular, this property (stability) holds with probability one.
+By Thm.~\ref{robustPolythm}, there is a polynomial that is nonzero when $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$; in particular, stability holds with probability one.
 \end{proof}

### 2017-08-14 manuscripts/PNAS/chazthm_pnas.tex
chaz

--- 2017-08-14 manuscripts/PNAS/chazthm_pnas.tex
@@
 \begin{corollary}
-Unsupervised neurally plausible sparse feature learning through a wiring bottleneck recovers original sensory representations and neural activities.
+Unsupervised neurally plausible sparse feature learning through a wiring bottleneck recovers neural activities representing original sensory stimuli.
 \end{corollary}

### 2017-08-14 manuscripts/PNAS/chazthm_pnas.tex
sec 1 SR

--- 2017-08-14 manuscripts/PNAS/chazthm_pnas.tex
@@
 We give general conditions guaranteeing when such dictionaries are uniquely and stably determined by data.
-The result justifies the use of this model as a constraint for blind source separation, and helps explain the observed universality of emergent representations in sparse models of certain natural phenomena.
+The result justifies the use of this model as a constraint for blind source separation and helps explain the observed universality of emergent representations in sparse models of certain natural phenomena.
 }
@@
 \dropcap{B}lind source separation is a classical problem in signal processing \cite{sato1975method}.
-A common modern assumption is that each of $N$ observed $n$-dimensional signals is a (noisy) linear combination of at most $k$ elementary waveforms drawn from some unknown ``dictionary'' of size $m$, typically with $k < m \ll N$ (see \cite{Zhang15} for a comprehensive review of this and related models).
+In one common modern formulation, each of $N$ observed $n$-dimensional signals is a (noisy) linear combination of at most $k$ elementary waveforms drawn from some unknown ``dictionary'' of size $m$, typically with $k < m \ll N$ (see \cite{Zhang15} for a comprehensive review of this and related models).
 Approximating solutions to this sparsity-constrained inverse problem have provided insight into the structure of many signal classes lacking domain-specific formal models (e.g., in vision \cite{wang2015sparse}).
@@
 Fortunately, algorithms with proven recovery of generating dictionaries under certain 
-conditions have recently been proposed (see \cite[Sec.~I-E]{Sun16} for a summary of the state-of-the-art). Few theorems, however, can be cited to explain this uniqueness phenomenon more generally.
+conditions have recently been proposed (see \cite[Sec.~I-E]{Sun16} for a summary of the state-of-the-art). Few theorems, however, can be cited to explain this uniqueness phenomenon more broadly.
 
 Here, we prove very generally that uniqueness and stability in sparse linear coding is an expected property of the model. 
-More specifically, dictionaries that preserve sparse codes (e.g., satisfy a `spark condition') are identifiable from as few as \mbox{$N = m(k-1){m \choose k} + m$} noisy sparse linear combinations of their columns up to an error linear in the noise (Thm.~\ref{DeterministicUniquenessTheorem}).
+More specifically, dictionaries that preserve sparse codes (e.g., satisfy a ``spark condition'') are identifiable from as few as \mbox{$N = m(k-1){m \choose k} + m$} noisy sparse linear combinations of their columns up to an error that is linear in the noise (Thm.~\ref{DeterministicUniquenessTheorem}).
 In fact, provided $n \geq \min(2k,m)$, in almost all cases the dictionary learning problem is well-posed (as per Hadamard \cite{Hadamard1902}) given enough data (Cor.~\ref{ProbabilisticCor}).
-Moreover, these guarantees hold without assuming the recovered matrix satisfies a spark condition, even when the number $m$ of dictionary elements is unknown.
-The explicit, algorithm-independent criteria we provide should be a useful theoretical tool.
-%  in the theory of sparse representations.
+Moreover, these explicit, algorithm-independent guarantees hold without assuming the recovered matrix satisfies a spark condition, and even when the number $m$ of dictionary elements is unknown.
 
@@
 \end{align*}
-
 then there is some permutation matrix $\mathbf{P}$ and invertible diagonal matrix $\mathbf{D}$ such that for all $i, j$:
@@
 
-%\pagebreak
-
 To see how Def.
@@
 Consider now any dataset $Z$ generated as in \eqref{LinearModel} with $\eta \leq \frac{1}{2} \varepsilon(\delta_1, \delta_2)$.
-Then from the triangle inequality, it follows that any matrix $\mathbf{B}$ and $k$-sparse $\mathbf{\bar x}_1, \ldots, \mathbf{\bar x}_N \in \mathbb{R}^m$ solving Prob.~\ref{InverseProblem} are necessarily close to the original dictionary $\mathbf{A}$ and sparse codes $\mathbf{x}_i$.
+Then from the triangle inequality, it follows that any matrix $\mathbf{B}$ and $k$-sparse $\mathbf{\bar x}_1, \ldots, \mathbf{\bar x}_N \in \mathbb{R}^m$ solving Prob.~\ref{InverseProblem} are necessarily within $\delta_1, \delta_2$ of the original dictionary $\mathbf{A}$ and sparse codes $\mathbf{x}_i$.
 
@@
 We then prove our main theorem (Thm.~\ref{DeterministicUniquenessTheorem}) in Sec.~\ref{DUT} after stating some additional definitions and lemmas required for the proof, including a useful result in combinatorial matrix analysis (Lem.~\ref{MainLemma}).
-We also give a simple argument that extends our guarantees to the following more common optimization formulation of the dictionary learning problem (Cor.~\ref{SLCopt}).
+We also provide an argument that extends our guarantees to the following more common optimization formulation of the dictionary learning problem (Cor.~\ref{SLCopt}).
 
 \begin{problem}\label{OptimizationProblem}
-Find a matrix $\mathbf{B}$ and vectors \mbox{$\mathbf{\bar x}_1, \ldots, \mathbf{\bar x}_N \in \mathbb{R}^m$} that solve:
+Find $\mathbf{B}$ and \mbox{$\mathbf{\bar x}_1, \ldots, \mathbf{\bar x}_N \in \mathbb{R}^m$} that solve:
 \begin{align}\label{minsum}
@@
 \end{problem}
-
-We comment that quite often theorists in algorithm development solve the related $\ell_1$ problem, which can be shown to be applicable to 
-solving $\ell_0$ problems in certain cases.  [*** IMPROVE ON THIS ***]
-
-All other proofs are relegated to the Section \ref{proofs}. 
-Finally, we present several applications in Discussion Sec.~\ref{Discussion}.
+Finally, in Sec.~\ref{Discussion}, we explain how our results fit into the literature and present several applications of our findings.
 
@@
 The \emph{degree} $\deg(i)$ of a node $i \in [m]$ is the number of sets in $\mathcal{H}$ that contain $i$, and we say $\mathcal{H}$ is \emph{regular} when for some $r$ we have $\deg(i) = r$ for all $i$ (for given $r$, we say $\mathcal{H}$ is \textit{$r$-regular}).
-We also write $\mathcal{H} + \mathcal{H} := \{ S \cup S': S, S' \in \mathcal{H}\}$.
+We also write $2 \mathcal{H} := \{ S \cup S': S, S' \in \mathcal{H}\}$.
 

### 2017-08-14 manuscripts/PNAS/review/point_by_point_response.txt

--- 2017-08-13 manuscripts/PNAS/review/point_by_point_response.txt
@@
+TODO:
+- MAKE SURE WE DON’T REFER TO L_H(A) BEFORE EXPLAINING THAT WE’VE GENERALIZED IT IN OUR RESUBMISSION FROM L_K(A)
+
 References for Cover Letter and Point-by-point Response:
@@
 [HS15] Hillar, Sommer, IEEE Transactions on information processing, 2015.
+[M10] Morris I (2010), Advances in Mathematics 225(6):3425–3445.
 
@@
 The reviewer, however, seems to have overlooked the fact that our main result (Thm.
-1) generalizes the noise-free result of [HS15] far beyond a simple extension to the noisy case in ways which provide valuable insight into the dictionary learning model.
-A significant deviation from the approach taken in [HS15] was necessary to prove these new facts.
+1) generalizes the noise-free result of [HS15] far beyond a simple extension to the noisy case in ways which provide valuable insight into the dictionary learning model and that a significant deviation from the approach taken in [HS15] was necessary to prove these new facts.
 Moreover, our solution (Cor.
 2) to the optimization formulation of the dictionary learning problem (Prob.
-2) — that of most interest to optimization theorists and practitioners of their methods — is the first of its kind (to our knowledge) in both the noise-free and noisy domains.
+2) — that of most interest to optimization theorists and practitioners of their methods — is (to our knowledge) the first of its kind in both the noise-free and noisy domains.
 We discuss all of these points in more detail in our response to the reviewer’s later "detailed comments".
-[???WORDING OF THIS PARAGRAPH COULD IMPROVE???]
 
 We have included in our updated manuscript a discussion of the computability of the sufficient conditions (they are, indeed, computable), as per the reviewer’s request.
-The main constants in our work -- C_1, C_2 -- are indeed computable, elementarily, in terms of two positive quantities that are natural in our context: (a) the "Lower Bound" L_H(A) of a matrix A given a hypergraph H (the support structure of sparse x's generating the data), which is a measure of how much A has a "spark condition" supported on H, and (b) the value in Def.
-4 of r(V_1,...,V_l) given subspaces V_i corresponding to spans of A's columns, which bounds the distance between an intersection of such spans and each one individually.
-The first quantity (a) is, in some form or another, related to standard objects in the field and may be computed as the smallest singular value of a particular matrix; in particular, for fixed sparsity constraint k on H, the lower bound L_H(A) is efficiently computable (polynomial time).
+The main constants in our work -- C_1, C_2 -- are computable, elementarily, in terms of two positive quantities that are natural in our context: (a) the "Lower Bound" L_H(A) of a matrix A given a hypergraph H (the support sets of sparse x's generating the data), which is a measure of how distinguishable two x’s with supports in H are by their images under A, and (b) the value in Def.
+4 of r(V_1,...,V_l) given subspaces V_i spanned by columns of A, which bounds the distance between intersections of such subspaces and each subspace individually.
+The first quantity (a) is, in some form or another, related to standard objects in the field and may be computed as the smallest singular value of a set of specific sub-matrices; in particular, for fixed sparsity constraint k on H, the lower bound L_H(A) is efficiently computable (polynomial time).
 Because deciding L_H(A) > 0 is already NP-hard [TP14], it seems likely that without fixing a sparsity level there is no efficient computation in general for (a).
@@
 Thus, the fact that we have a sufficient error in coding for uniqueness being linear in terms of both the desired dictionary and sparse vector recovery error is optimal.
-Although optimal up to constants, our solution to Problem 1 involves constants C_1 and C_2, but it would be interesting and relevant for practical applications to determine the minimal such constants.
+Although optimal up to constants, our solution to Problem 1 involves constants C_1 and C_2, it would be interesting and relevant for practical applications to determine the minimal such constants.
 In the case of sparsity k=1, we have given an example showing optimality of constants in this case.
-Finally, with respect to (c), we regard this is a fundamental open problem in the field: how many sparsely generated samples determine the linear coding model?
-(One reason to be skeptical that a polynomial suffice is again [Tillman-Pfetsch-2014].)  However, there is some good news -- if k is fixed and we constrain sparse codes \hat{x}_i to come from a polynomial number of supports, then a polynomial number of samples N is enough to guarantee uniqueness.
+Finally, with respect to (c), we regard this as a fundamental open problem in the field: how many sparsely generated samples determine the linear coding model?
+(One reason to be skeptical that a polynomial suffice is again [TP14].)  However, there is some good news -- if k is fixed and we constrain sparse codes \hat{x}_i to come from a polynomial number of supports, then a polynomial number of samples N is enough to guarantee uniqueness.
 In particular, a sample complexity polynomial in (m,k) can be achieved by limiting the size of the support set of the \tilde x_i, and we have revised the manuscript to discuss this fact (which, incidentally, does not follow from the results of [HS15] in the noiseless case).
@@
 2 is indeed unique.
-We have updated the manuscript with an explicit statement of this fact.
+We have updated the manuscript with an explicit statement of this fact, and also outline the procedure here:
+
+Given a dictionary A and codes x_i that solve Problem 1 (e.g. learned by any algorithm), check that that they satisfy the assumptions of Thm. 1:
+   - List the support sets of the x_i 
+      - Discard those for which there are (k-1){m \choose k} or fewer x_i with that support.
+      - Discard those for which the supported x_i are not in GLP. (This should also exclude any supports less than k in size.)
+   - From the support sets that remain, list all SIP-satisfying hypergraphs that are subsets of this set
+   - Discard those for which L_{2H}(A) = 0.
+   - For each of the remaining hypergraphs, determine the constant C_1 from A and the x_i (or for every subset of the x_i of size (k-1){m \choose k})
+   - Check that the derived upper bound on \varepsilon exceeds that of the original problem. If yes, the solution is “unique”.
 
@@
 We designed and proved Lemma 4 to address this issue, which draws its bound from the convergence guarantees of an alternating projections algorithm first proposed by von Neumann.
-This result, combined with a little known fact about the distance ‘d’ requiring proof in [Morris; Advances in Mathematics], constitute the more sophisticated and obscure components of the deduction in eq.(26).
+This result, combined with a little known fact about the distance ‘d’ requiring proof in [M10], constitute the more sophisticated and obscure components of the deduction in eq.(26).
 To reiterate, this step is completely trivial in the noiseless case and required no mention for the inductive steps taken in [HS15].
@@
 Since in this case the map \pi from supports in the hypergraph to {[m] \choose k} is not surjective, one cannot apply the same inductive method as in [HS15], which freely chooses supports in the codomain to intersect at (k-1) nodes and map back to some corresponding (k-1)-sized intersection of supports in the domain.
-Instead, we demonstrate the surprising fact that by pigeonholing the images of supports in the (SIP-satisfying) hypergraph one can still guarantee a bijection between the nodes and therefore the subspaces spanned by individual dictionary elements.
+Instead, we demonstrate the surprising fact that by pigeonholing the images of supports in the (SIP-satisfying) hypergraph H one can still guarantee a bijection between the nodes and therefore the subspaces spanned by individual dictionary elements.
 We note that it was necessary to forgo inductive methods altogether in order to prove this fact for all hypergraphs satisfying the SIP; otherwise, we would require that the supports in the hypergraph have intersections of size k’ for every k’ < k (e.g.
@@
 
-To be clear, the new perspective we take on the problem yields the following powerful conclusions beyond those of a straightforward extension of [HS15] to noise:
+To be clear, the new perspective we take on the problem yields the following powerful conclusions beyond those of a straightforward extension of [HS15] to the noisy case:
 
@@
 when m = k^2, take the supports to be the rows and columns of [m] arranged in a square grid).
-Moreover, if the size of the support set of reconstructing codes is polynomial in m and k, then the pigeonholing argument in the proof of Thm.
+Moreover, if the size of the support set of reconstructing codes is known to be polynomial in m and k, then the pigeonholing argument in the proof of Thm.
 1 requires only a polynomial number of samples distributed over a polynomial number of supports; thus, N is polynomial in m, k.
@@
 Our proof is powerful enough to show that, in fact, even the matrix A need not satisfy the spark condition to be identifiable!
-[???DO WE HAVE AN EXAMPLE OF THIS KIND OF MATRIX A???]  Rather, it need only be injective on the union of subspaces with supports that form sets in a hypergraph satisfying the singleton intersection property (SIP).
-We had omitted this point in our original submission of the manuscript to keep things simple, but have decided to include this interesting fact in our resubmission.
+Rather, it need only be injective on the union of subspaces with supports that form sets in a hypergraph satisfying the singleton intersection property (SIP).
+(For example, consider the matrix A = [e_1, …, e_5, v] where v = e_1 + e_3 + e_5.
+and take H to be the set of all consecutive pairs of [m] arranged in cyclic order.
+Then A satisfies the assumptions of Thm.
+1 without satisfying the spark condition.) We had omitted this point in our original submission of the manuscript to keep things simple, but have decided to include this fact in our resubmission.
 This also required us to redefine the restricted matrix lower bound L to be in terms of a hypergraph, which is an interesting object for further study in its own right.
 
-We must also mention here that our solution to Prob.
+We must also reiterate here that our solution to Prob.
 2, that of most interest to practitioners of dictionary learning methods, is to our knowledge the first of its kind in both the noise-free and noisy domains.
@@
 We have provided an "almost certain" guarantee of this flavor in Cor 3, wherein the sparse vector supports are constrained to form a hypergraph satisfying the SIP.
-It would be interesting to calculate furthermore the probability that random supports form a hypergraph satisfying the SIP.
-We think we have cracked open a nice set of interesting combinatorial problems (with practical implications!) to be solved by the community.
-
-[We could have done this but we believe what sets our results apart from the vast majority of results in this field so far is its deterministic nature from which any probabilistic result can be derived, e.g.
-the ones we give]
+It would be useful and interesting to calculate furthermore the probability that random supports form a hypergraph satisfying the SIP.
+We have opted not to include these calculations due in part to space constraints, but also because we believe that what sets our work apart from the vast majority of results in the field is their deterministic nature, e.g.
+they do not depend on any kind of assumption about the random distribution from which the sparse coefficients or dictionary entries are drawn.
 

### 2017-08-15 manuscripts/PNAS/chazthm_pnas.tex
chaz

--- 2017-08-14 manuscripts/PNAS/chazthm_pnas.tex
@@
 The \emph{degree} $\deg(i)$ of a node $i \in [m]$ is the number of sets in $\mathcal{H}$ that contain $i$, and we say $\mathcal{H}$ is \emph{regular} when for some $r$ we have $\deg(i) = r$ for all $i$ (for given $r$, we say $\mathcal{H}$ is \textit{$r$-regular}).
-We also write $\mathcal{H} + \mathcal{H} := \{ S \cup S': S, S' \in \mathcal{H}\}$.
+We also write $2\mathcal{H} := \{ S \cup S': S, S' \in \mathcal{H}\}$.
 
@@
 \end{align}
+
+A strong practical implication of this result is the following: there is an effective procedure by which one can affirm if one's proposed solution $(\mathbf{B}, \mathbf{\bar x}_1, \ldots, \mathbf{x}_N)$ to Prob.~\ref{InverseProblem} is indeed unique (up to noise and inherent ambiguities).
+One simply need check that $\mathbf{B}$ and the $\mathbf{\bar x}_i$ satisfy the assumptions of Thm.~\ref{DeterministicUniquenessTheorem} on $\mathbf{A}$ and the $\mathbf{x}_i$, respectively.
+
 %In fact, a more general result (stated clearly in the next section) can be gleaned from our method of proving Thm.~\ref{DeterministicUniquenessTheorem}.
@@
 
-%Regarding the assumptions of Thm.~\ref{DeterministicUniquenessTheorem}, 
-It so happens that producing sparse codes $\mathbf{x}_i$ in general linear position is straightforward with a ``Vandermonde'' matrix construction (e.g., see \cite{Hillar15}).
+Regarding the assumptions of Thm.~\ref{DeterministicUniquenessTheorem}, it so happens that sparse codes $\mathbf{x}_i$ in general linear position are straightforward to produce with a ``Vandermonde'' matrix construction \cite{Hillar15}.
 
@@
 
-One can easily verify that for every $k < m$, there is a regular $k$-uniform hypergraph that satisfies the SIP; for instance, take $\mathcal{H}$ to be the consecutive intervals of length $k$ in some cyclic order on $[m]$, for which Cor.~\ref{DeterministicUniquenessCorollary} implies the lower bound for sample size $N$ from the introduction.
+One can also easily verify that for every $k < m$, there is a regular $k$-uniform hypergraph that satisfies the SIP; for instance, take $\mathcal{H}$ to be the consecutive intervals of length $k$ in some cyclic order on $[m]$, for which Cor.~\ref{DeterministicUniquenessCorollary} implies the lower bound for sample size $N$ from the introduction.
 In many cases, however, the SIP is achievable with far fewer supports; for example, when $k = \sqrt{m}$, take $\mathcal{H}$ to be the $2k$ rows and columns formed by arranging $[m]$ in a square grid.
@@
 
-We note that unlike what previous works have required, $\mathbf{A}$ need not satisfy the spark condition to be recoverable from data.
+We furthermore note that unlike what previous works \cite{li2004analysis, Georgiev05, Aharon06, Hillar15} have required, $\mathbf{A}$ need not satisfy the spark condition to be recoverable from data.
 As an example for $k=2$, let $\mathbf{A} = [ \mathbf{e}_1, \ldots, \mathbf{e}_5, \mathbf{v}]$ where $\mathbf{v} = \mathbf{e}_1 + \mathbf{e}_3 + \mathbf{e}_5$.
@@
 
-[*** We remark about algorithms ***]
-
-We remark that there is a strong application to theoretical neuroscience.
+We remark that these results have a strong application to theoretical neuroscience, justifying what may be the first hypothesized theory of compressive communication between sparsely active neural populations \cite{Isely10, ganguli2012compressed}.
 
 \begin{corollary}
-Unsupervised neurally plausible sparse feature learning through a wiring bottleneck recovers neural activities representing original sensory stimuli.
+Random noisy (linear) compression of sparse neural activities $\mathbf{x}_i$ is decompressible by any neurally plausible unsupervised sparse feature learning algorithm.
 \end{corollary}
-
-[*** Make clearer / motivate better ***]
 

### 2017-08-15 manuscripts/PNAS/chazthm_pnas.tex

--- 2017-08-14 manuscripts/PNAS/chazthm_pnas.tex
@@
 The \emph{degree} $\deg(i)$ of a node $i \in [m]$ is the number of sets in $\mathcal{H}$ that contain $i$, and we say $\mathcal{H}$ is \emph{regular} when for some $r$ we have $\deg(i) = r$ for all $i$ (for given $r$, we say $\mathcal{H}$ is \textit{$r$-regular}).
-We also write $2 \mathcal{H} := \{ S \cup S': S, S' \in \mathcal{H}\}$.
+We also write $2\mathcal{H} := \{ S \cup S': S, S' \in \mathcal{H}\}$.
 
@@
 
-[*** We remark about algorithms ***]
-
-We remark that there is a strong application to theoretical neuroscience.
+We remark that these results have a strong application to theoretical neuroscience, justifying what may be the first hypothesized theory of compressive communication between sparsely active neural populations \cite{Isely10, ganguli2012compressed}.
 
 \begin{corollary}
-Unsupervised neurally plausible sparse feature learning through a wiring bottleneck recovers original sensory representations and neural activities.
+Random noisy (linear) compression of sparse neural activities $\mathbf{x}_i$ is decompressible by any neurally plausible unsupervised sparse feature learning algorithm.
 \end{corollary}
-
-[*** Make clearer / motivate better ***]
 

### 2017-08-15 manuscripts/PNAS/chazthm_pnas.tex
chaz

@@
 Next, observe that no more than $(k-1)|\mathcal{H}|$ of the $\mathbf{\bar x}_i$ share a support $\bar S$ of size less than $k$; otherwise, by the pigeonhole principle, at least $k$ of these indices $i$ belong to the same $K \subseteq I(S)$ for some $S \in \mathcal{H}$ and (as argued previously) \eqref{rhs222} follows.
-Since the right-hand side of \eqref{rhs222} is less than one, by \eqref{dimLem} we have the contradiction $k = \dim(\bm{\mathcal{A}}_S) \leq \dim(\bm{\mathcal{B}}_{\bar S}) \leq |\bar S|.$ The total number of $(k-1)$-sparse vectors $\mathbf{\bar x}_i$ can thus not exceed $|\mathcal{H}|(k-1){ \bar m \choose k-1}$.
+Since the right-hand side of \eqref{rhs222} is less than one, by \eqref{dimLem} we have the contradiction $k = \dim(\bm{\mathcal{A}}_S) \leq \dim(\bm{\mathcal{B}}_{\bar S}) \leq |\bar S|.$
 
-Therefore, no more than $|\mathcal{H}|k(k-1){ \bar m \choose k-1}$ vectors $\mathbf{\bar x}_i$ are not $k$-sparse.
+The total number of $(k-1)$-sparse vectors $\mathbf{\bar x}_i$ can thus not exceed $|\mathcal{H}|(k-1){ \bar m \choose k-1}$.
+By \eqref{eqn} no more than $|\mathcal{H}|k(k-1){ \bar m \choose k-1}$ vectors $\mathbf{\bar x}_i$ are not $k$-sparse.
 Since for every $S \in \mathcal{H}$ there are over $(k-1)\left[ {\bar m \choose k} + |\mathcal{H}|k{ \bar m \choose k-1} \right]$ vectors $\mathbf{x}_i$ supported there, it follows that more than $(k-1){\bar m \choose k}$ of them have corresponding $\mathbf{\bar x}_i$ that are $k$-sparse.

### 2017-08-15 manuscripts/PNAS/chazthm_pnas.tex
sec 2 SR

@@
 
-Before stating our main result, we identify combinatorial criteria on the support sets of the generating codes $\mathbf{x}_i$ that imply stable sparse representations.
-Letting $\{1, \ldots, m\}$ be denoted $[m]$, its power set $2^{[m]}$, and ${[m] \choose k}$ the set of subsets of $[m]$ of size $k$, we say a hypergraph $\mathcal{H} \subseteq 2^{[m]}$ on vertices $[m]$ is \textit{$k$-uniform} when in fact $\mathcal{H} \subseteq {[m] \choose k}$.
-The \emph{degree} $\deg(i)$ of a node $i \in [m]$ is the number of sets in $\mathcal{H}$ that contain $i$, and we say $\mathcal{H}$ is \emph{regular} when for some $r$ we have $\deg(i) = r$ for all $i$ (for given $r$, we say $\mathcal{H}$ is \textit{$r$-regular}).
+Before stating our results precisely, we identify criteria on the support sets of the generating codes $\mathbf{x}_i$ that imply stable sparse representations.
+Letting $\{1, \ldots, m\}$ be denoted $[m]$, its power set $2^{[m]}$, and ${[m] \choose k}$ the set of subsets of $[m]$ of size $k$, we say a hypergraph $\mathcal{H} \subseteq 2^{[m]}$ on vertices $[m]$ is \textit{$k$-uniform} when $\mathcal{H} \subseteq {[m] \choose k}$.
+The \emph{degree} $\deg(i)$ of a node $i \in [m]$ is the number of sets in $\mathcal{H}$ that contain $i$, and we say $\mathcal{H}$ is \emph{regular} when for some $r$ we have $\deg(i) = r$ for all $i$ (given such an $r$, we say $\mathcal{H}$ is \textit{$r$-regular}).
 We also write $2\mathcal{H} := \{ S \cup S': S, S' \in \mathcal{H}\}$.
@@
 \begin{definition}\label{sip}
-Given $\mathcal{H} \subseteq 2^{[m]}$, the \textbf{star} $h(i)$ is the collection of sets in $\mathcal{H}$ containing $i$.
-We say $\mathcal{H}$ has the \textbf{singleton intersection property} (\textbf{SIP}) when $\cap h(i) = \{i\}$ for all $i \in [m]$.
+Given $\mathcal{H} \subseteq 2^{[m]}$, the \textbf{star} $\sigma(i)$ is the collection of sets in $\mathcal{H}$ containing $i$.
+We say $\mathcal{H}$ has the \textbf{singleton intersection property} (\textbf{SIP}) when $\cap \sigma(i) = \{i\}$ for all $i \in [m]$.
 \end{definition}
 
-Next, we describe a quantitative version of the spark condition \eqref{SparkCondition}.
-The \emph{lower bound} $L$ of a matrix $\mathbf{M} \in \mathbb R^{n \times m}$ is the largest number $\alpha$ such that \mbox{$\|\mathbf{M}\mathbf{x}\|_2 \geq \alpha\|\mathbf{x}\|_2$} for all $\mathbf{x} \in \mathbb{R}^m$ \cite{Grcar10}.
-By compactness of the unit sphere, every injective linear map has a nonzero lower bound; hence, if $\mathbf{M}$ satisfies the spark condition then each submatrix formed from $2k$ of its columns or less has a nonzero lower bound.
+Next, we describe a quantitative version of the spark condition.
+The \emph{lower bound} $L$ of a matrix $\mathbf{M} \in \mathbb R^{n \times m}$ is the largest $\alpha$ such that \mbox{$\|\mathbf{M}\mathbf{x}\|_2 \geq \alpha\|\mathbf{x}\|_2$} for all $\mathbf{x} \in \mathbb{R}^m$ \cite{Grcar10}.
+By compactness of the sphere, every injective linear map has nonzero lower bound; hence, if $\mathbf{M}$ satisfies \eqref{SparkCondition}, then each submatrix formed from $2k$ of its columns or less has $L > 0$.
 
-We generalize this domain-restricted lower bound to a \emph{union of subspaces} model \cite{vidal2005generalized} derived from the hypergraph $\mathcal{H}$.
+We generalize the  lower bound to a domain-restricted \emph{union of subspaces} model \cite{vidal2005generalized} derived from the hypergraph $\mathcal{H}$.
 Letting $\mathbf{M}_J$ denote the submatrix formed by the columns of $\mathbf{M}$ indexed by $J$ (with $\mathbf{M}_\emptyset := \mathbf{0}$), we define:
@@
 \begin{align}\label{Ldef}
-L_\mathcal{H}(\mathbf{M}) := \frac{1}{\sqrt{k}} \inf \left\{ \frac{\|\mathbf{M}_S\mathbf{x}\|_2}{ \|\mathbf{x}\|_2} : S \in \mathcal{H}, \ \ \mathbf{x} \in \mathbb{R}^m \right\},
+L_\mathcal{H}(\mathbf{M}) := \frac{1}{\sqrt{k}} \inf \left\{ \frac{\|\mathbf{M}_S\mathbf{x}\|_2}{ \|\mathbf{x}\|_2} : S \in \mathcal{H}, \ \ \mathbf{x} \in \mathbb{R}^{|S|} \right\},
 \end{align} 
 %
-where we write $L_{k}$ when $\mathcal{H} = {[m] \choose k}$.\footnote{We note that the quantity $1 - \sqrt{k} L_k(\mathbf{M})$ is also known in the compressed sensing literature as the (asymmetric) lower restricted isometry constant \cite{Blanchard2011}.} Clearly, for any $\mathbf{M}$ satisfying \eqref{SparkCondition}, we have $L_{k'}(\mathbf{M}) > 0$ for  $k' \leq 2k$.
+where we write $L_{k}$ when $\mathcal{H} = {[m] \choose k}$.\footnote{We note that $1 - \sqrt{k} L_k(\mathbf{M})$ is known as the asymmetric lower restricted isometry constant \cite{Blanchard2011}.} Clearly, for any $\mathbf{M}$ satisfying \eqref{SparkCondition}, we have $L_{k'}(\mathbf{M}) > 0$ for  $k' \leq 2k$.
 Note that if $\mathcal{H}$ covers $[m]$ then $L_2 \geq L_{2\mathcal{H}}$.
@@
 \begin{theorem}\label{DeterministicUniquenessTheorem}
-Fix a real $n \times m$ matrix $\mathbf{A}$ with $L_{2\mathcal{H}}(\mathbf{A}) > 0$ for some $r$-regular $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP.
-If the sequence \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} contains, for each $S \in \mathcal{H}$, more than $(k-1){m \choose k}$ $k$-sparse vectors in general linear position supported in $S$, then there is a constant\footnote{We delay defining the constant $C_1$ until Section \ref{DUT} (\eqref{Cdef1}).} $C_1 > 0$ for which the following holds for all\footnote{The condition $\varepsilon < L_2(\mathbf{A}) /C_1$ is necessary; otherwise,  with \mbox{$\mathbf{A}$ = $\mathbf{I}$} and $\mathbf{a}_i = \mathbf{e}_i$, there is a $\mathbf{B}$ and $1$-sparse $\mathbf{b}_i$ with $|\mathbf{A}\mathbf{a}_i - \mathbf{B}\mathbf{b}_i|_2 \leq \varepsilon$ violating \eqref{Cstable}.} $\varepsilon < L_{2}(\mathbf{A}) / C_1$:
+Fix an $n \times m$ matrix $\mathbf{A}$ with $L_{2\mathcal{H}}(\mathbf{A}) > 0$ for an $r$-regular $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP.
+If \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} contains, for each $S \in \mathcal{H}$, more than $(k-1){m \choose k}$ $k$-sparse vectors in general linear position supported in $S$, then there is a constant $C_1 > 0$ with the following holding for all\footnote{The condition $\varepsilon < L_2(\mathbf{A}) /C_1$ is necessary; otherwise,  with \mbox{$\mathbf{A}$ = $\mathbf{I}$} and $\mathbf{a}_i = \mathbf{e}_i$, there is a $\mathbf{B}$ and $1$-sparse $\mathbf{b}_i$ with $|\mathbf{A}\mathbf{a}_i - \mathbf{B}\mathbf{b}_i|_2 \leq \varepsilon$ violating \eqref{Cstable}.} $\varepsilon < L_{2}(\mathbf{A}) / C_1$:
 
-Every real $n \times \bar m$ matrix $\mathbf{B}$ for which there exist $k$-sparse $\mathbf{\bar x}_1, \ldots, \mathbf{\bar x}_N$ satisfying \mbox{$\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\bar x}_i\|_2 \leq \varepsilon$} for all $i$ has $\bar m \geq m$ and, provided $\bar m < mr/(r-1)$,
+Every $n \times \bar m$ matrix $\mathbf{B}$ for which there exist $k$-sparse $\mathbf{\bar x}_1, \ldots, \mathbf{\bar x}_N$ satisfying \mbox{$\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\bar x}_i\|_2 \leq \varepsilon$} for all $i$ has $\bar m \geq m$ and, provided $\bar m < mr/(r-1)$,
 \begin{align}\label{Cstable}
-\|\mathbf{A}_j- \mathbf{B}_{\bar J} \mathbf{PD}_j\|_2 \leq C_1 \varepsilon \ \ \text{for all } j \in J,
+\|\mathbf{A}_j- \mathbf{B}_{\bar J} \mathbf{PD}_j\|_2 \leq C_1 \varepsilon, \ \ \text{for all } j \in J,
 \end{align}
 %
-for some nonempty $J, \bar J$ of size $\bar m - r(\bar m - m)$, some permutation $\mathbf{P}$ and invertible diagonal $\mathbf{D}$.
+for some nonempty $J \subseteq [m]$ and $\bar J \subseteq [m]$ of size $\bar m - r(\bar m - m)$, permutation matrix $\mathbf{P}$, and and invertible diagonal matrix $\mathbf{D}$.
 
-Moreover, if in fact $\varepsilon < L_{2k}(\mathbf{A}) / C_1$ (provided $L_{2k}(\mathbf{A}) > 0$), then $L_{2k}(\mathbf{B}\mathbf{PD}) \geq L_{2k}(\mathbf{A}) - C_1 \varepsilon$ and:
+Moreover, if in addition $\varepsilon < L_{2k}(\mathbf{A}) / C_1$ (provided $L_{2k}(\mathbf{A}) > 0$), then $L_{2k}(\mathbf{B}\mathbf{PD}) \geq L_{2k}(\mathbf{A}) - C_1 \varepsilon$ and:
 \begin{align}\label{b-PDa}
 %\|\mathbf{x}^J_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\bar x}^{\bar J}_i\|_1 &\leq  \left( \frac{ 1+C_1 \|\mathbf{x}^{J}_i\|_1 }{ L_{2k}(\mathbf{A}) -  C_1\varepsilon } \right) \varepsilon \ \  \text{for $i \in [N]$}.
-\|\mathbf{x}_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\bar x}_i\|_1 &\leq  \left( \frac{ 1+C_1 \|\mathbf{x}_i\|_1 }{ L_{2k}(\mathbf{A}) -  C_1\varepsilon } \right) \varepsilon \ \  \text{for $i \in [N]$}.
+\|\mathbf{x}_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\bar x}_i\|_1 &\leq  \left( \frac{ 1+C_1 \|\mathbf{x}_i\|_1 }{ L_{2k}(\mathbf{A}) -  C_1\varepsilon } \right) \varepsilon, \ \  \text{for $i \in [N]$},
 \end{align}
 %
-where $\mathbf{x}_i$ and $\mathbf{\bar x}_i$ here represent subvectors formed from the entries indexed by $J$ and $\bar J$, respectively. 
+where $\mathbf{x}_i$ and $\mathbf{\bar x}_i$ here represent subvectors formed from restricting to entries indexed by $J$ and $\bar J$, respectively. 
 \end{theorem}
 
+We delay defining the explicit constant $C_1$ until Section \ref{DUT} (\eqref{Cdef1}).
 %To be clear, the implication of Thm.~\ref{DeterministicUniquenessTheorem} is that $Y = \{\mathbf{Ax}_1, \ldots, \mathbf{Ax}_N\}$ has a stable $k$-sparse representation in $\mathbb{R}^m$, with \eqref{def1} guaranteed provided $\varepsilon$ in Def.~\ref{maindef} does not exceed:
-To be clear, Thm.~\ref{DeterministicUniquenessTheorem} says that the smaller the difference $\bar m - m$, the more columns and coefficients of the original dictionary $\mathbf{A}$ and codes $\mathbf{x}_i$ contained (up to noise) in the appropriately scaled dictionary $\mathbf{B}$ and codes $\mathbf{\bar x}_i$.
-The implication for $\bar m = m$ is that $Y = \{\mathbf{Ax}_1, \ldots, \mathbf{Ax}_N\}$ has a stable $k$-sparse representation in $\mathbb{R}^m$, with \eqref{def1} guaranteed provided $\varepsilon$ in Def.~\ref{maindef} does not exceed:
+To be clear, Thm.~\ref{DeterministicUniquenessTheorem} says that the smaller the difference $\bar m - m$, the more columns and coefficients of the original dictionary $\mathbf{A}$ and codes $\mathbf{x}_i$ are contained (up to noise) in the appropriately scaled dictionary $\mathbf{B}$ and codes $\mathbf{\bar x}_i$.
+When $\bar m = m$, the theorem implies that  $Y = \{\mathbf{Ax}_1, \ldots, \mathbf{Ax}_N\}$ has a stable $k$-sparse representation in $\mathbb{R}^m$, with \eqref{def1} guaranteed provided $\varepsilon$ in Def.~\ref{maindef} does not exceed:
 \begin{align}\label{epsdel}
@@
 
-Regarding the assumptions of Thm.~\ref{DeterministicUniquenessTheorem}, it so happens that sparse codes $\mathbf{x}_i$ in general linear position are straightforward to produce with a ``Vandermonde'' matrix construction \cite{Hillar15}.
+Regarding the assumptions of Thm.~\ref{DeterministicUniquenessTheorem}, it so happens that sparse codes $\mathbf{x}_i$ in general linear position are straightforward to produce with a ``Vandermonde'' matrix construction \cite{Hillar15}, leading to the following.
 
@@
 
-We furthermore note that unlike what previous works \cite{li2004analysis, Georgiev05, Aharon06, Hillar15} have required, $\mathbf{A}$ need not satisfy the spark condition to be recoverable from data.
-As an example for $k=2$, let $\mathbf{A} = [ \mathbf{e}_1, \ldots, \mathbf{e}_5, \mathbf{v}]$ where $\mathbf{v} = \mathbf{e}_1 + \mathbf{e}_3 + \mathbf{e}_5$.
-and take $\mathcal{H}$ to be the set of all consecutive pairs of $[m]$ arranged in cyclic order.
-Then $\mathbf{A}$ satisfies the assumptions of Thm.~\ref{DeterministicUniquenessTheorem} without satisfying the spark condition.
+We furthermore note that unlike the requirements of previous works \cite{li2004analysis, Georgiev05, Aharon06, Hillar15}, matrix $\mathbf{A}$ need not satisfy the spark condition to be recoverable from data.
+As a simple example for $k=2$, let $\mathbf{A} = [ \mathbf{e}_1, \ldots, \mathbf{e}_5, \mathbf{v}]$ where $\mathbf{v} = \mathbf{e}_1 + \mathbf{e}_3 + \mathbf{e}_5$, and take $\mathcal{H}$ to be the set of all consecutive pairs of $[m]$ arranged in cyclic order.
+Then, $\mathbf{A}$ satisfies the assumptions of Thm.~\ref{DeterministicUniquenessTheorem} but not the spark condition.
 %(since $\{ \mathbf{A}_1, \mathbf{A}_3, \mathbf{A}_5, \mathbf{A}_6\}$ is not a linearly independent set).
 
-There are other less direct consequences of Thm.~\ref{DeterministicUniquenessTheorem}. For instance, it has the following implications for the optimization problem posed in Prob.~\ref{SLCopt}:
+There are other less direct consequences of Thm.~\ref{DeterministicUniquenessTheorem}, such as the following implication for optimization Prob.~\ref{SLCopt}.
 
 \begin{corollary}\label{SLCopt}
-If all of the assumptions of Thm.\ref{DeterministicUniquenessTheorem} hold, only now with more than $(k-1)\left[ {\bar m \choose k} + |\mathcal{H}|k{\bar m \choose k-1}\right]$ vectors $\mathbf{x}_i$ supported in each $S \in \mathcal{H}$, then all solutions to Prob.~\ref{OptimizationProblem} necessarily satisfy the implications \eqref{Cstable} and \eqref{b-PDa} of Thm.~\ref{DeterministicUniquenessTheorem}.
+If the assumptions of Thm.\ref{DeterministicUniquenessTheorem} hold, only now with more than $(k-1)\left[ {\bar m \choose k} + |\mathcal{H}|k{\bar m \choose k-1}\right]$ vectors $\mathbf{x}_i$ supported in each $S \in \mathcal{H}$, then all solutions to Prob.~\ref{OptimizationProblem} necessarily satisfy implications \eqref{Cstable} and \eqref{b-PDa} of Thm.~\ref{DeterministicUniquenessTheorem}.
 \end{corollary}
 
-%\pagebreak
-
-Another extension of Thm.~\ref{DeterministicUniquenessTheorem} follows from the following analytic characterization of the spark condition.
+Another extension of Thm.~\ref{DeterministicUniquenessTheorem} arises from the following analytic characterization of the spark condition.
 Let $\mathbf{A}$  be the $n \times m$ matrix of $nm$ indeterminates $A_{ij}$.
@@
 
-Since $f$ is an analytic function, if there exists one substitution of a real matrix $\mathbf{A}$ such that $f(\mathbf{A}) \neq 0$ then the zeroes of $f$ in fact form a set of measure zero.
-Fortunately, such a matrix $\mathbf{A}$ is easily constructed by adding rows of zeroes to any $\min(2k,m) \times m$ Vandermonde matrix $[\gamma_i^j]_{i,j=1}^{k,m}$ with distinct $\gamma_i$ (so that each term in the product above is nonzero).
+Since $f$ is analytic, having a single substitution of a real matrix $\mathbf{A}$ with $f(\mathbf{A}) \neq 0$ necessarily implies that the zeroes of $f$, in fact, form a set of measure zero.
+Fortunately, such a matrix $\mathbf{A}$ is easily constructed by adding rows of zeroes to any $\min(2k,m) \times m$ Vandermonde matrix $[\gamma_i^j]_{i,j=1}^{k,m}$ with distinct $\gamma_i$ (so that each term in the product above for $f$ is nonzero).
 Hence, almost every real $n \times m$ matrix with $n \geq \min(2k,m)$ satisfies \eqref{SparkCondition}.
@@
 \begin{corollary}\label{ProbabilisticCor}
-Fix $k < m$ and $n \geq \min(2k, m)$ and let the entries of $\mathbf{A} \in \mathbb{R}^{n \times m}$ and $k$-sparse $\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$ be drawn independently from probability measures absolutely continuous with respect to the standard Borel measure $\mu$.
+Fix $k < m$, $n \geq \min(2k, m)$, and let the entries of $\mathbf{A} \in \mathbb{R}^{n \times m}$ and $k$-sparse $\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$ be drawn independently from probability measures absolutely continuous with respect to the standard Borel measure $\mu$.
 If more than $(k-1){m \choose k}$ of the vectors $\mathbf{x}_i$ are supported in each $S \in \mathcal{H}$ for a regular $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP, then $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$ with probability one.

### 2017-08-15 manuscripts/PNAS/chazthm_pnas.tex
eqn fix more SR results

@@
 \newtheorem{example}{Example}
+
+\renewcommand{\eqref}[1]{\textnormal{[\ref{#1}]}}
 
@@
 where we write $L_{k}$ when $\mathcal{H} = {[m] \choose k}$.\footnote{We note that $1 - \sqrt{k} L_k(\mathbf{M})$ is known as the asymmetric lower restricted isometry constant \cite{Blanchard2011}.} Clearly, for any $\mathbf{M}$ satisfying \eqref{SparkCondition}, we have $L_{k'}(\mathbf{M}) > 0$ for  $k' \leq 2k$.
-Note that if $\mathcal{H}$ covers $[m]$ then $L_2 \geq L_{2\mathcal{H}}$.
+Note that if $\mathcal{H}$ covers $[m]$ t(i.e., $\cup \mathcal{H} = [m]$), then $L_2 \geq L_{2\mathcal{H}}$.
 
@@
 %Denote by $\mathbf{x}^J$ the subvector formed from the entries of $\mathbf{x}$ indexed by $J$. 
-A set of $k$-sparse vectors is said to be in \emph{general linear position} when any $k$ of them are linearly independent. The following is a precise statement of our main result.
+A set of $k$-sparse vectors is said to be in \emph{general linear position} when any $k$ of them are linearly independent.
+The following is a precise statement of our main result.
+Only the quantity $C_1$ is undefined until later (in Sec.~\ref{DUT}, Eq.~\eqref{Cdef1}).
 
@@
 
-We delay defining the explicit constant $C_1$ until Section \ref{DUT} (\eqref{Cdef1}).
+%We delay defining the explicit constant $C_1$ until Section \ref{DUT} (\eqref{Cdef1}).
 %To be clear, the implication of Thm.~\ref{DeterministicUniquenessTheorem} is that $Y = \{\mathbf{Ax}_1, \ldots, \mathbf{Ax}_N\}$ has a stable $k$-sparse representation in $\mathbb{R}^m$, with \eqref{def1} guaranteed provided $\varepsilon$ in Def.~\ref{maindef} does not exceed:
 To be clear, Thm.~\ref{DeterministicUniquenessTheorem} says that the smaller the difference $\bar m - m$, the more columns and coefficients of the original dictionary $\mathbf{A}$ and codes $\mathbf{x}_i$ are contained (up to noise) in the appropriately scaled dictionary $\mathbf{B}$ and codes $\mathbf{\bar x}_i$.
-When $\bar m = m$, the theorem implies that  $Y = \{\mathbf{Ax}_1, \ldots, \mathbf{Ax}_N\}$ has a stable $k$-sparse representation in $\mathbb{R}^m$, with \eqref{def1} guaranteed provided $\varepsilon$ in Def.~\ref{maindef} does not exceed:
+When $\bar m = m$, the theorem implies that  $Y = \{\mathbf{Ax}_1, \ldots, \mathbf{Ax}_N\}$ has a stable $k$-sparse representation in $\mathbb{R}^m$, with inequality \eqref{def1} guaranteed provided $\varepsilon$ in Def.~\ref{maindef} does not exceed:
 \begin{align}\label{epsdel}

### 2017-08-15 manuscripts/PNAS/chazthm_pnas.tex
sml edts

@@
 
-We remark that these results have a strong application to theoretical neuroscience, justifying what may be the first hypothesized theory of compressive communication between sparsely active neural populations \cite{Isely10, ganguli2012compressed}.
+We remark that these results have a strong application to theoretical neuroscience, mathematically justifying one of the few hypothesized theories of compressive communication between sparsely active neural populations \cite{Isely10, ganguli2012compressed}.
 
 \begin{corollary}
-Random noisy (linear) compression of sparse neural activities $\mathbf{x}_i$ is decompressible by any neurally plausible unsupervised sparse feature learning algorithm.
+Random noisy (linear) compression of sparse neural activities is decodable by any neurally-plausible unsupervised sparse (linear) feature learning algorithm.
 \end{corollary}

### 2017-08-15 manuscripts/PNAS/chazthm_pnas.tex
chaz

@@
 
-\begin{corollary}
-Random noisy (linear) compression of sparse neural activities is decodable by any neurally-plausible unsupervised sparse (linear) feature learning algorithm.
-\end{corollary}
-
-[*** Also discuss uniquness of sparse sensory representations more generally, like Gabors ***]
+\begin{proposition}
+Random noisy (linear) compression of sparse neural activities is decodable by any neurally-plausible unsupervised sparse (linear) feature learning algorithm that solves Prob.~\ref{DeterministicUniquenessTheorem} or \ref{SLCopt} (e.g.
+\cite{rehnsommer2007, rozell2007neurally}).
+\end{proposition}
+%\cite{rehnsommer2007, rozell2007neurally, ganguli2012compressed, hu2014hebbian}
 
@@
 Our results suggest that this correspondence could be due to the ``universality'' of sparse representations in natural data, an early mathematical idea in neural theory \cite{pitts1947}.
-Furthermore, they justify the hypothesis of \cite{Isely10} that sparse codes passed through information bottlenecks in the brain are recovered from random projections via (unsupervised) biologically plausible sparse coding (e.g., \cite{rehnsommer2007, rozell2007neurally, ganguli2012compressed, hu2014hebbian}).
+%Furthermore, they justify the hypothesis of \cite{Isely10} that sparse codes passed through information bottlenecks in the brain are recovered from random projections via (unsupervised) biologically plausible sparse coding (e.g., \cite{rehnsommer2007, rozell2007neurally, ganguli2012compressed, hu2014hebbian}).
 

### 2017-08-15 manuscripts/PNAS/chazthm_pnas.tex
minor updates

@@
 
-% \authordeclaration{The authors declare no conflict of interest.}
+\authordeclaration{The authors declare no conflict of interest.}
 \correspondingauthor{\textsuperscript{1}To whom correspondence should be addressed. E-mail: chaz@berkeley.edu, chillar@msri.org}
 
-\keywords{Sparse coding, dictionary learning, matrix factorization, compressed sensing, inverse problems, blind source separation}
+\keywords{Sparse linear coding, dictionary learning, matrix factorization, compressed sensing, inverse problems, blind source separation}
 
@@
 %
-which would be, in any case, necessary for uniqueness of the $\mathbf{x}_i$. Our concern here is solution stability with respect to noise.
+which would be, in any case, necessary for uniqueness of the $\mathbf{x}_i$. Our concern here is solution stability in the practical setting of noise.
 
@@
 \end{problem}
-Finally, in Sec.~\ref{Discussion}, we explain how our results fit into the literature and present several applications of our findings.
+Finally, in Sec.~\ref{Discussion}, we present several applications of our findings.
 

### 2017-08-15 manuscripts/PNAS/chazthm_pnas.tex
squished

--- 2017-08-15 manuscripts/PNAS/chazthm_pnas.tex
@@
 \dropcap{B}lind source separation is a classical problem in signal processing \cite{sato1975method}.
-In one common modern formulation, each of $N$ observed $n$-dimensional signals is a (noisy) linear combination of at most $k$ elementary waveforms drawn from some unknown ``dictionary'' of size $m$, typically with $k < m \ll N$ (see \cite{Zhang15} for a comprehensive review of this and related models).
+In one common modern formulation, each of $N$ observed $n$-dimensional signals is a (noisy) linear combination of at most $k$ elementary waveforms drawn from some unknown ``dictionary'' of size $m$, typically with $m \ll N$ (see \cite{Zhang15} for a comprehensive review of this and related models).
 Approximating solutions to this sparsity-constrained inverse problem have provided insight into the structure of many signal classes lacking domain-specific formal models (e.g., in vision \cite{wang2015sparse}).
@@
 Fortunately, algorithms with proven recovery of generating dictionaries under certain 
-conditions have recently been proposed (see \cite[Sec.~I-E]{Sun16} for a summary of the state-of-the-art). Few theorems, however, can be cited to explain this uniqueness phenomenon more broadly.
+conditions have recently been proposed (see \cite[Sec.~I-E]{Sun16} for a summary of the state-of-the-art).
+Few theorems, however, can be cited to explain this uniqueness phenomenon more broadly; in particular, a universal guarantee in the context of noise has yet to emerge.
 
@@
 where we write $L_{k}$ when $\mathcal{H} = {[m] \choose k}$.\footnote{We note that $1 - \sqrt{k} L_k(\mathbf{M})$ is known as the asymmetric lower restricted isometry constant \cite{Blanchard2011}.} Clearly, for any $\mathbf{M}$ satisfying \eqref{SparkCondition}, we have $L_{k'}(\mathbf{M}) > 0$ for  $k' \leq 2k$.
-Note that if $\mathcal{H}$ covers $[m]$ t(i.e., $\cup \mathcal{H} = [m]$), then $L_2 \geq L_{2\mathcal{H}}$.
+Note that if $\mathcal{H}$ covers $[m]$ (i.e., $\cup \mathcal{H} = [m]$), then $L_2 \geq L_{2\mathcal{H}}$.
 
@@
 The following is a precise statement of our main result.
-Only the quantity $C_1$ is undefined until later (in Sec.~\ref{DUT}, Eq.~\eqref{Cdef1}).
+Only the quantity $C_1$ is left undefined until later (in Sec.~\ref{DUT}, Eq.~\eqref{Cdef1}).
 
@@
 
-Moreover, if in addition $\varepsilon < L_{2k}(\mathbf{A}) / C_1$ (provided $L_{2k}(\mathbf{A}) > 0$), then $L_{2k}(\mathbf{B}\mathbf{PD}) \geq L_{2k}(\mathbf{A}) - C_1 \varepsilon$ and:
+Moreover, if $L_{2k}(\mathbf{A}) > 0$ and $\varepsilon < L_{2k}(\mathbf{A}) / C_1$, then $L_{2k}(\mathbf{B}\mathbf{PD}) \geq L_{2k}(\mathbf{A}) - C_1 \varepsilon$ and:
 \begin{align}\label{b-PDa}
@@
 
-A strong practical implication of this result is the following: there is an effective procedure by which one can affirm if one's proposed solution $(\mathbf{B}, \mathbf{\bar x}_1, \ldots, \mathbf{x}_N)$ to Prob.~\ref{InverseProblem} is indeed unique (up to noise and inherent ambiguities).
-One simply need check that $\mathbf{B}$ and the $\mathbf{\bar x}_i$ satisfy the assumptions of Thm.~\ref{DeterministicUniquenessTheorem} on $\mathbf{A}$ and the $\mathbf{x}_i$, respectively.
+An immediate practical implication of this result is that there exists a practical procedure to affirm if one's proposed solution $(\mathbf{B}, \mathbf{\bar x}_1, \ldots, \mathbf{x}_N)$ to Prob.~\ref{InverseProblem} is indeed unique (up to noise and inherent ambiguities): simply check that $\mathbf{B}$ and the $\mathbf{\bar x}_i$ satisfy the assumptions on $\mathbf{A}$ and the $\mathbf{x}_i$ in Thm.~\ref{DeterministicUniquenessTheorem}.
 
@@
 
-One can also easily verify that for every $k < m$, there is a regular $k$-uniform hypergraph that satisfies the SIP; for instance, take $\mathcal{H}$ to be the consecutive intervals of length $k$ in some cyclic order on $[m]$, for which Cor.~\ref{DeterministicUniquenessCorollary} implies the lower bound for sample size $N$ from the introduction.
+One can also verify that for every $k < m$, there is a regular $k$-uniform hypergraph that satisfies the SIP; for instance, take $\mathcal{H}$ to be the consecutive intervals of length $k$ in some cyclic order on $[m]$, for which Cor.~\ref{DeterministicUniquenessCorollary} implies the lower bound for sample size $N$ from the introduction.
 In many cases, however, the SIP is achievable with far fewer supports; for example, when $k = \sqrt{m}$, take $\mathcal{H}$ to be the $2k$ rows and columns formed by arranging $[m]$ in a square grid.
@@
 
-We furthermore note that unlike the requirements of previous works \cite{li2004analysis, Georgiev05, Aharon06, Hillar15}, matrix $\mathbf{A}$ need not satisfy the spark condition to be recoverable from data.
+We furthermore note that unlike the requirements of previous works \cite{li2004analysis, Georgiev05, Aharon06, Hillar15}, the matrix $\mathbf{A}$ need not satisfy the spark condition to be recoverable from data.
 As a simple example for $k=2$, let $\mathbf{A} = [ \mathbf{e}_1, \ldots, \mathbf{e}_5, \mathbf{v}]$ where $\mathbf{v} = \mathbf{e}_1 + \mathbf{e}_3 + \mathbf{e}_5$, and take $\mathcal{H}$ to be the set of all consecutive pairs of $[m]$ arranged in cyclic order.

### 2017-08-15 manuscripts/PNAS/chazthm_pnas.tex
squished
sec 2

--- 2017-08-15 manuscripts/PNAS/chazthm_pnas.tex
@@
 %
-which would be, in any case, necessary for uniqueness of the $\mathbf{x}_i$. Our concern here is solution stability in the practical setting of noise.
+which would be, in any case, necessary for uniqueness of the $\mathbf{x}_i$. Here, we study stability in the practical setting of noise.
 
@@
 We then prove our main theorem (Thm.~\ref{DeterministicUniquenessTheorem}) in Sec.~\ref{DUT} after stating some additional definitions and lemmas required for the proof, including a useful result in combinatorial matrix analysis (Lem.~\ref{MainLemma}).
-We also provide an argument that extends our guarantees to the following more common optimization formulation of the dictionary learning problem (Cor.~\ref{SLCopt}).
+We also provide an argument that extends our guarantees to the following more common optimization formulation of the dictionary learning problem (Thm.~\ref{SLCopt}).
 
@@
 \end{problem}
-Finally, in Sec.~\ref{Discussion}, we present several applications of our findings.
+Finally, in Sec.~\ref{Discussion}, we discuss both theoretical and practical applications of our main mathematical findings.
 
@@
 where we write $L_{k}$ when $\mathcal{H} = {[m] \choose k}$.\footnote{We note that $1 - \sqrt{k} L_k(\mathbf{M})$ is known as the asymmetric lower restricted isometry constant \cite{Blanchard2011}.} Clearly, for any $\mathbf{M}$ satisfying \eqref{SparkCondition}, we have $L_{k'}(\mathbf{M}) > 0$ for  $k' \leq 2k$.
-Note that if $\mathcal{H}$ covers $[m]$ t(i.e., $\cup \mathcal{H} = [m]$), then $L_2 \geq L_{2\mathcal{H}}$.
+Note that if $\mathcal{H}$ \textit{covers} $[m]$ (i.e., $\cup \mathcal{H} = [m]$), then $L_2 \geq L_{2\mathcal{H}}$.
 
@@
 The following is a precise statement of our main result.
-Only the quantity $C_1$ is undefined until later (in Sec.~\ref{DUT}, Eq.~\eqref{Cdef1}).
+Only the quantity $C_1 = C_1(\mathbf{A}, \{\mathbf{x}_i\}_{i=1}^N, \mathcal{H})$ is undefined (until Sec.~\ref{DUT}, Eq.~\eqref{Cdef1}).
 
@@
 Fix an $n \times m$ matrix $\mathbf{A}$ with $L_{2\mathcal{H}}(\mathbf{A}) > 0$ for an $r$-regular $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP.
-If \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} contains, for each $S \in \mathcal{H}$, more than $(k-1){m \choose k}$ $k$-sparse vectors in general linear position supported in $S$, then there is a constant $C_1 > 0$ with the following holding for all\footnote{The condition $\varepsilon < L_2(\mathbf{A}) /C_1$ is necessary; otherwise,  with \mbox{$\mathbf{A}$ = $\mathbf{I}$} and $\mathbf{a}_i = \mathbf{e}_i$, there is a $\mathbf{B}$ and $1$-sparse $\mathbf{b}_i$ with $|\mathbf{A}\mathbf{a}_i - \mathbf{B}\mathbf{b}_i|_2 \leq \varepsilon$ violating \eqref{Cstable}.} $\varepsilon < L_{2}(\mathbf{A}) / C_1$:
+If \mbox{$\{\mathbf{x}_1, \ldots, \mathbf{x}_N\} \subset \mathbb{R}^m$} contains, for each $S \in \mathcal{H}$, more than $(k-1){m \choose k}$ $k$-sparse vectors in general linear position supported in $S$, then there is $C_1 > 0$ with the following holding for all\footnote{The condition $\varepsilon < L_2(\mathbf{A}) /C_1$ is necessary; otherwise,  with \mbox{$\mathbf{A}$ = $\mathbf{I}$} and $\mathbf{x}_i = \mathbf{e}_i$, there is $\mathbf{\bar{x}}$ and $1$-sparse $\mathbf{b}_i$ with $|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\bar{x}}_i|_2 \leq \varepsilon$, violating \eqref{Cstable}.} $\varepsilon < L_{2}(\mathbf{A}) / C_1$:
 
@@
 %To be clear, the implication of Thm.~\ref{DeterministicUniquenessTheorem} is that $Y = \{\mathbf{Ax}_1, \ldots, \mathbf{Ax}_N\}$ has a stable $k$-sparse representation in $\mathbb{R}^m$, with \eqref{def1} guaranteed provided $\varepsilon$ in Def.~\ref{maindef} does not exceed:
-To be clear, Thm.~\ref{DeterministicUniquenessTheorem} says that the smaller the difference $\bar m - m$, the more columns and coefficients of the original dictionary $\mathbf{A}$ and codes $\mathbf{x}_i$ are contained (up to noise) in the appropriately scaled dictionary $\mathbf{B}$ and codes $\mathbf{\bar x}_i$.
-When $\bar m = m$, the theorem implies that  $Y = \{\mathbf{Ax}_1, \ldots, \mathbf{Ax}_N\}$ has a stable $k$-sparse representation in $\mathbb{R}^m$, with inequality \eqref{def1} guaranteed provided $\varepsilon$ in Def.~\ref{maindef} does not exceed:
+In words, Thm.~\ref{DeterministicUniquenessTheorem} says that the smaller the difference $\bar m - m$ between recovery and original latent dictionary sizes, the more columns and coefficients of the original dictionary $\mathbf{A}$ and codes $\mathbf{x}_i$ are contained (up to noise) in the appropriately scaled dictionary $\mathbf{B}$ and codes $\mathbf{\bar x}_i$.
+In the particular case when $\bar m = m$, the theorem directly implies that  $Y = \{\mathbf{Ax}_1, \ldots, \mathbf{Ax}_N\}$ has a stable $k$-sparse representation in $\mathbb{R}^m$, with inequalities \eqref{def1} guaranteed provided $\varepsilon$ in Def.~\ref{maindef} does not exceed:
 \begin{align}\label{epsdel}
-\varepsilon(\delta_1, \delta_2) := \min \left\{ \frac{\delta_1}{ C_1 }, \frac{ \delta_2 L_{2k}(\mathbf{A})}{ 1 + C_1 \left( \max_{i \in [N]} \|\mathbf{x}_i\|_1  + \delta_2 \right) } \right\}.
+\varepsilon(\delta_1, \delta_2) := \min \left\{ \frac{\delta_1}{ C_1 }, \frac{ \delta_2 L_{2k}(\mathbf{A})}{ 1 + C_1 \left( \delta_2 + \max_{i \in [N]} \|\mathbf{x}_i\|_1  \right) } \right\}.
 \end{align}
 
-A strong practical implication of this result is the following: there is an effective procedure by which one can affirm if one's proposed solution $(\mathbf{B}, \mathbf{\bar x}_1, \ldots, \mathbf{x}_N)$ to Prob.~\ref{InverseProblem} is indeed unique (up to noise and inherent ambiguities).
-One simply need check that $\mathbf{B}$ and the $\mathbf{\bar x}_i$ satisfy the assumptions of Thm.~\ref{DeterministicUniquenessTheorem} on $\mathbf{A}$ and the $\mathbf{x}_i$, respectively.
+Note that sparse codes $\mathbf{x}_i$ with a shared support that are in general linear position are straightforward to produce using a ``Vandermonde'' matrix construction (i.e., use the columns of the matrix $[\gamma_{i}^j]_{i,j=1}^{k,N}$, for distinct nonzero $\gamma_i$).
+Thus, the assumptions of Thm.~\ref{DeterministicUniquenessTheorem} are easily met, leading to the following direct application to uniqueness in dictionary learning, Prob.~\ref{InverseProblem}.
+
+\begin{corollary}\label{DeterministicUniquenessCorollary}
+Given a regular hypergraph $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP, there are $N =  |\mathcal{H}| \left[ (k-1){m \choose k} + 1  \right]$ vectors \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} such that every matrix $\mathbf{A}$ with $L_{2\mathcal{H}}(\mathbf{A}) > 0$ generates a dataset $Y = \{\mathbf{A}\mathbf{x}_1, \ldots, \mathbf{A}\mathbf{x}_N\}$ with a stable $k$-sparse representation in $\mathbb{R}^m$.
+\end{corollary}
+
+One can also easily verify that for every $k < m$, there is a regular $k$-uniform hypergraph with the SIP; for instance, take $\mathcal{H}$ to be the consecutive intervals of length $k$ in some cyclic order on $[m]$.
+In this case, a direct consequence of Cor.~\ref{DeterministicUniquenessCorollary} is rigorous verification of the lower bound \mbox{$N = m(k-1){m \choose k} + m$} for sufficient sample size from the introduction.
+In many cases, however, the SIP is achievable with far fewer supports.
+For example, when $k = \sqrt{m}$, simply take $\mathcal{H}$ to be the $2k$ rows and columns formed by arranging $[m]$ in a square grid.
+
+Another practical implication of this result is the following: there is an effective procedure by which one can affirm if one's proposed solution $(\mathbf{B}, \mathbf{\bar x}_1, \ldots, \mathbf{x}_N)$ to Prob.~\ref{InverseProblem} is indeed unique (up to noise and inherent ambiguities).
+One simply checks that $\mathbf{B}$ and the $\mathbf{\bar x}_i$ satisfy the respective assumptions of Thm.~\ref{DeterministicUniquenessTheorem}.
+%.
+on $\mathbf{A}$ and the $\mathbf{x}_i$, respectively.
 
@@
 
-Regarding the assumptions of Thm.~\ref{DeterministicUniquenessTheorem}, it so happens that sparse codes $\mathbf{x}_i$ in general linear position are straightforward to produce with a ``Vandermonde'' matrix construction \cite{Hillar15}, leading to the following.
-
-\begin{corollary}\label{DeterministicUniquenessCorollary}
-Given a regular hypergraph $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP, there are $N =  |\mathcal{H}| \left[ (k-1){m \choose k} + 1  \right]$ vectors \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} such that every matrix $\mathbf{A}$ with $L_{2\mathcal{H}}(\mathbf{A}) > 0$ generates a dataset $Y = \{\mathbf{A}\mathbf{x}_1, \ldots, \mathbf{A}\mathbf{x}_N\}$ with a stable $k$-sparse representation in $\mathbb{R}^m$.
-\end{corollary}
-
-One can also easily verify that for every $k < m$, there is a regular $k$-uniform hypergraph that satisfies the SIP; for instance, take $\mathcal{H}$ to be the consecutive intervals of length $k$ in some cyclic order on $[m]$, for which Cor.~\ref{DeterministicUniquenessCorollary} implies the lower bound for sample size $N$ from the introduction.
-In many cases, however, the SIP is achievable with far fewer supports; for example, when $k = \sqrt{m}$, take $\mathcal{H}$ to be the $2k$ rows and columns formed by arranging $[m]$ in a square grid.
-
 %As mentioned above, there exist $k$-uniform regular hypergraphs $\mathcal{H}$ with the SIP having cardinality $|\mathcal{H}| = m$,
@@
 
-There are other less direct consequences of Thm.~\ref{DeterministicUniquenessTheorem}, such as the following implication for optimization Prob.~\ref{SLCopt}.
+There are other less direct consequences of Thm.~\ref{DeterministicUniquenessTheorem}.
+For instance, we use it to prove uniqueness for the optimization formulation of dictionary learning, Prob.~\ref{SLCopt}, the main object of interest for those applying dictionary learning to data.
 
-\begin{corollary}\label{SLCopt}
+\begin{theorem}\label{SLCopt}
 If the assumptions of Thm.\ref{DeterministicUniquenessTheorem} hold, only now with more than $(k-1)\left[ {\bar m \choose k} + |\mathcal{H}|k{\bar m \choose k-1}\right]$ vectors $\mathbf{x}_i$ supported in each $S \in \mathcal{H}$, then all solutions to Prob.~\ref{OptimizationProblem} necessarily satisfy implications \eqref{Cstable} and \eqref{b-PDa} of Thm.~\ref{DeterministicUniquenessTheorem}.
-\end{corollary}
+\end{theorem}
 
@@
 
-\section{Proofs of Theorem~\ref{DeterministicUniquenessTheorem} and Corollary~\ref{SLCopt}}\label{DUT}
+\section{Proofs of Theorems~\ref{DeterministicUniquenessTheorem} and ~\ref{SLCopt}}\label{DUT}
 
@@
 
-\begin{proof}[Proof of Cor.~\ref{SLCopt}]
+\begin{proof}[Proof of Thm.~\ref{SLCopt}]
 We bound the number of $k$-sparse $\mathbf{\bar x}_i$ and then apply Thm.~\ref{DeterministicUniquenessCorollary}. 

### 2017-08-15 manuscripts/PNAS/chazthm_pnas.tex

@@
 \end{definition}
+
+\pagebreak
 
@@
 Only the quantity $C_1 = C_1(\mathbf{A}, \{\mathbf{x}_i\}_{i=1}^N, \mathcal{H})$ is undefined (until Sec.~\ref{DUT}, Eq.~\eqref{Cdef1}).
+%=======
+%where we write $L_{k}$ when $\mathcal{H} = {[m] \choose k}$.\footnote{We note that $1 - \sqrt{k} L_k(\mathbf{M})$ is known as the asymmetric lower restricted isometry constant \cite{Blanchard2011}.} Clearly, for any $\mathbf{M}$ satisfying \eqref{SparkCondition}, we have $L_{k'}(\mathbf{M}) > 0$ for  $k' \leq 2k$.
+Note that if $\mathcal{H}$ covers $[m]$ (i.e., $\cup \mathcal{H} = [m]$), then $L_2 \geq L_{2\mathcal{H}}$.
+% 
+%A vector $\mathbf{x}$ is said to be \emph{supported} in $S \subseteq [m]$ when $\mathbf{x} \in \text{\rm span}\{\mathbf{e}_j: j\in S\}$, where $\mathbf{e}_j$ are the standard basis in $\mathbb R^m$. 
+%%Denote by $\mathbf{x}^J$ the subvector formed from the entries of $\mathbf{x}$ indexed by $J$. 
+%A set of $k$-sparse vectors is said to be in \emph{general linear position} when any $k$ of them are linearly independent.
+The following is a precise statement of our main result.
+Only the quantity $C_1$ is left undefined until later (in Sec.~\ref{DUT}, Eq.~\eqref{Cdef1}).
+%>>>>>>> d1407a275dc391dabad7bb62d3e659f9a4ac4624
 
@@
 Fix an $n \times m$ matrix $\mathbf{A}$ with $L_{2\mathcal{H}}(\mathbf{A}) > 0$ for an $r$-regular $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP.
-If \mbox{$\{\mathbf{x}_1, \ldots, \mathbf{x}_N\} \subset \mathbb{R}^m$} contains, for each $S \in \mathcal{H}$, more than $(k-1){m \choose k}$ $k$-sparse vectors in general linear position supported in $S$, then there is $C_1 > 0$ with the following holding for all\footnote{The condition $\varepsilon < L_2(\mathbf{A}) /C_1$ is necessary; otherwise,  with \mbox{$\mathbf{A}$ = $\mathbf{I}$} and $\mathbf{x}_i = \mathbf{e}_i$, there is $\mathbf{\bar{x}}$ and $1$-sparse $\mathbf{b}_i$ with $|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\bar{x}}_i|_2 \leq \varepsilon$, violating \eqref{Cstable}.} $\varepsilon < L_{2}(\mathbf{A}) / C_1$:
+If \mbox{$\{\mathbf{x}_1, \ldots, \mathbf{x}_N\} \subset \mathbb{R}^m$} contains, for each $S \in \mathcal{H}$, more than $(k-1){m \choose k}$ $k$-sparse vectors in general linear position supported in $S$, then there is $C_1 > 0$ with the following holding for all\footnote{The condition $\varepsilon < L_2(\mathbf{A}) /C_1$ is necessary; otherwise,  with \mbox{$\mathbf{A}$ = $\mathbf{I}$} and $\mathbf{x}_i = \mathbf{e}_i$, there is a matrix $\mathbf{B}$ and $1$-sparse $\mathbf{\bar{x}}_i$ with $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\bar{x}}_i \|_2 \leq \varepsilon$, but nonetheless violating \eqref{Cstable}.} $\varepsilon < L_{2}(\mathbf{A}) / C_1$:
 
@@
 Thus, the assumptions of Thm.~\ref{DeterministicUniquenessTheorem} are easily met, leading to the following direct application to uniqueness in dictionary learning, Prob.~\ref{InverseProblem}.
+%=======
+%An immediate practical implication of this result is that there exists a practical procedure to affirm if one's proposed solution $(\mathbf{B}, \mathbf{\bar x}_1, \ldots, \mathbf{x}_N)$ to Prob.~\ref{InverseProblem} is indeed unique (up to noise and inherent ambiguities): simply check that $\mathbf{B}$ and the $\mathbf{\bar x}_i$ satisfy the assumptions on $\mathbf{A}$ and the $\mathbf{x}_i$ in Thm.~\ref{DeterministicUniquenessTheorem}.
+%
+%%In fact, a more general result (stated clearly in the next section) can be gleaned from our method of proving Thm.~\ref{DeterministicUniquenessTheorem}.
+Briefly, in cases where $\mathbf{B}$ has $\bar m \neq m$ columns, or $\mathcal{H}$ is not regular or only partially satisfying the SIP, a relation between $\bar m$ and the degree sequence of nodes in $\mathcal{H}$ gives indices $J \subseteq [m]$ defining a submatrix $\mathbf{A}_J$ and subvectors $\mathbf{x}_i^J$ that are recoverable in the sense of \eqref{Cstable} and \eqref{b-PDa}.
+For example, if $\mathcal{H}$ is $\ell$-regular with the SIP but $m \leq \bar m < m\ell/(\ell - 1)$ then we have nonzero $|J| = \bar m - \ell(\bar m - m)$.
+The implication here is that the smaller the difference $\bar m - m$, the more columns and code entries of the original $n \times m$ dictionary $\mathbf{A}$ and codes $\mathbf{x}_i$ contained (up to noise) in the appropriately scaled $n \times \bar m$ dictionary $\mathbf{B}$ and codes $\mathbf{\bar x}_i$.
+When $\bar m = m$, we recover Thm.~\ref{DeterministicUniquenessTheorem}.
+%
+%%In fact, even if $\mathcal{H}$ is not regular or only partially satisfies the SIP, a relation between $\bar m$ and the degree sequence of nodes in $\mathcal{H}$ may give the indices $J \subseteq [m]$.
+For sake of brevity, we delay to the next section a clear statement of this more general result.
+%
+%Regarding the assumptions of Thm.~\ref{DeterministicUniquenessTheorem}, it so happens that sparse codes $\mathbf{x}_i$ in general linear position are straightforward to produce with a ``Vandermonde'' matrix construction \cite{Hillar15}, leading to the following.
+%>>>>>>> d1407a275dc391dabad7bb62d3e659f9a4ac4624
 
@@
 
+%=======
+%One can also verify that for every $k < m$, there is a regular $k$-uniform hypergraph that satisfies the SIP; for instance, take $\mathcal{H}$ to be the consecutive intervals of length $k$ in some cyclic order on $[m]$, for which Cor.~\ref{DeterministicUniquenessCorollary} implies the lower bound for sample size $N$ from the introduction.
+In many cases, however, the SIP is achievable with far fewer supports; for example, when $k = \sqrt{m}$, take $\mathcal{H}$ to be the $2k$ rows and columns formed by arranging $[m]$ in a square grid.
+%>>>>>>> d1407a275dc391dabad7bb62d3e659f9a4ac4624
+
 %As mentioned above, there exist $k$-uniform regular hypergraphs $\mathcal{H}$ with the SIP having cardinality $|\mathcal{H}| = m$,
 
-We furthermore note that unlike the requirements of previous works \cite{li2004analysis, Georgiev05, Aharon06, Hillar15}, matrix $\mathbf{A}$ need not satisfy the spark condition to be recoverable from data.
+We furthermore note that unlike the requirements of previous works \cite{li2004analysis, Georgiev05, Aharon06, Hillar15}, the matrix $\mathbf{A}$ need not satisfy the spark condition to be recoverable from data.
 As a simple example for $k=2$, let $\mathbf{A} = [ \mathbf{e}_1, \ldots, \mathbf{e}_5, \mathbf{v}]$ where $\mathbf{v} = \mathbf{e}_1 + \mathbf{e}_3 + \mathbf{e}_5$, and take $\mathcal{H}$ to be the set of all consecutive pairs of $[m]$ arranged in cyclic order.

### 2017-08-15 manuscripts/PNAS/chazthm_pnas.tex
chaz
more sec 1

@@
 Fix an $n \times m$ matrix $\mathbf{A}$ with $L_{2\mathcal{H}}(\mathbf{A}) > 0$ for an $r$-regular $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP.
-If \mbox{$\{\mathbf{x}_1, \ldots, \mathbf{x}_N\} \subset \mathbb{R}^m$} contains, for each $S \in \mathcal{H}$, more than $(k-1){m \choose k}$ $k$-sparse vectors in general linear position supported in $S$, then there is $C_1 > 0$ with the following holding for all\footnote{The condition $\varepsilon < L_2(\mathbf{A}) /C_1$ is necessary; otherwise,  with \mbox{$\mathbf{A}$ = $\mathbf{I}$} and $\mathbf{x}_i = \mathbf{e}_i$, there is a matrix $\mathbf{B}$ and $1$-sparse $\mathbf{\bar{x}}_i$ with $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\bar{x}}_i \|_2 \leq \varepsilon$, but nonetheless violating \eqref{Cstable}.} $\varepsilon < L_{2}(\mathbf{A}) / C_1$:
+If \mbox{$\{\mathbf{x}_1, \ldots, \mathbf{x}_N\} \subset \mathbb{R}^m$} contains, for each $S \in \mathcal{H}$, more than $(k-1){m \choose k}$ $k$-sparse vectors in general linear position supported in $S$, then there is $C_1 > 0$ with the following holding for all\footnote{The condition $\varepsilon < L_2(\mathbf{A}) /C_1$ is necessary; otherwise,  with \mbox{$\mathbf{A}$ = $\mathbf{I}$} and $\mathbf{x}_i = \mathbf{e}_i$, there is a matrix $\mathbf{B}$ and $1$-sparse $\mathbf{\bar{x}}_i$ with $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\bar{x}}_i \|_2 \leq \varepsilon$, nonetheless, violating \eqref{Cstable}.} $\varepsilon < L_{2}(\mathbf{A}) / C_1$:
 
@@
 One simply checks that $\mathbf{B}$ and the $\mathbf{\bar x}_i$ satisfy the respective assumptions of Thm.~\ref{DeterministicUniquenessTheorem}.
-%.
-on $\mathbf{A}$ and the $\mathbf{x}_i$, respectively.
+%. on $\mathbf{A}$ and the $\mathbf{x}_i$, respectively.
 
@@
 We furthermore note that unlike the requirements of previous works \cite{li2004analysis, Georgiev05, Aharon06, Hillar15}, the matrix $\mathbf{A}$ need not satisfy the spark condition to be recoverable from data.
-As a simple example for $k=2$, let $\mathbf{A} = [ \mathbf{e}_1, \ldots, \mathbf{e}_5, \mathbf{v}]$ where $\mathbf{v} = \mathbf{e}_1 + \mathbf{e}_3 + \mathbf{e}_5$, and take $\mathcal{H}$ to be the set of all consecutive pairs of $[m]$ arranged in cyclic order.
-Then, $\mathbf{A}$ satisfies the assumptions of Thm.~\ref{DeterministicUniquenessTheorem} but not the spark condition.
+As a simple example for $k=2$, let $\mathbf{A} = [ \mathbf{e}_1, \ldots, \mathbf{e}_5, \mathbf{v}]$ where $\mathbf{v} = \mathbf{e}_1 + \mathbf{e}_3 + \mathbf{e}_5$, and take $\mathcal{H}$ to be all consecutive pairs of $[m]$ arranged in cyclic order.
+Then, $\mathbf{A}$ satisfies the assumptions of Thm.~\ref{DeterministicUniquenessTheorem} but not \eqref{SparkCondition}.
 %(since $\{ \mathbf{A}_1, \mathbf{A}_3, \mathbf{A}_5, \mathbf{A}_6\}$ is not a linearly independent set).
+This weakening of condition \eqref{SparkCondition} allows for a practical amount of data (polynomial-time for fixed sparsity $k$) for guaranteeing stable sparse representation.
 
@@
 Since $f$ is analytic, having a single substitution of a real matrix $\mathbf{A}$ with $f(\mathbf{A}) \neq 0$ necessarily implies that the zeroes of $f$, in fact, form a set of measure zero.
-Fortunately, such a matrix $\mathbf{A}$ is easily constructed by adding rows of zeroes to any $\min(2k,m) \times m$ Vandermonde matrix $[\gamma_i^j]_{i,j=1}^{k,m}$ with distinct $\gamma_i$ (so that each term in the product above for $f$ is nonzero).
-Hence, almost every real $n \times m$ matrix with $n \geq \min(2k,m)$ satisfies \eqref{SparkCondition}.
+Fortunately, such a matrix $\mathbf{A}$ is easily constructed by adding rows of zeroes to any $\min(2k,m) \times m$ Vandermonde matrix as described above (so that each term in the product above for $f$ is nonzero).
+Hence, almost every $n \times m$ matrix with $n \geq \min(2k,m)$ satisfies \eqref{SparkCondition}.
 
@@
 
-Thus, choosing the dictionary and sparse codes ``randomly'' almost certainly generates data with a stable sparse representation.
+Thus, choosing the dictionary and codes ``randomly'' almost certainly generates data with a stable sparse representation.
 
@@
 \begin{proof}
-By induction it is enough to prove the case $|n| = 2$, but this case follows directly from the assumtion.
+By induction it is enough to prove the case $|n| = 2$, but this case follows directly from the assumption.
 %Clearly, for any map $f$, if $w \in f(U \cap V)$ then $w \in f(U)$ and $w \in f(V)$, hence $w \in f(U) \cap f(V)$.

### 2017-08-15 manuscripts/PNAS/review/point_by_point_response.txt

@@
 TODO:
-- MAKE SURE WE DON’T REFER TO L_H(A) BEFORE EXPLAINING THAT WE’VE GENERALIZED IT IN OUR RESUBMISSION FROM L_K(A)
 
@@
 We have included in our updated manuscript a discussion of the computability of the sufficient conditions (they are, indeed, computable), as per the reviewer’s request.
-The main constants in our work -- C_1, C_2 -- are computable, elementarily, in terms of two positive quantities that are natural in our context: (a) the "Lower Bound" L_H(A) of a matrix A given a hypergraph H (the support sets of sparse x's generating the data), which is a measure of how distinguishable two x’s with supports in H are by their images under A, and (b) the value in Def.
+The main constants in our work -- C_1, C_2 -- are computable, elementarily, in terms of two positive quantities that are natural in our context: (a) the "Lower Bound" L_H(A) of a matrix A given a hypergraph H (the support sets of sparse x's generating the data — see *NOTE* below this paragraph), which is a measure of how distinguishable two x’s with supports in H are by their images under A, and (b) the value in Def.
 4 of r(V_1,...,V_l) given subspaces V_i spanned by columns of A, which bounds the distance between intersections of such subspaces and each subspace individually.
@@
 Thus, while our constants are effective (an algorithm exists to compute them), they are not necessarily polynomially-time computable.
+
+*NOTE* We have introduced for reasons discussed below the notion of L_H(A) in our re-submission where previously (in our original submission) we had defined only L_k(A).
 
@@
 2 is indeed unique.
-We have updated the manuscript with an explicit statement of this fact, and also outline the procedure here:
+We have updated the manuscript with an explicit statement of this fact, and outline one such procedure here:
 
@@
    - Check that the derived upper bound on \varepsilon exceeds that of the original problem. If yes, the solution is “unique”.
+
+More practical implications arise from our discovery of sufficient combinatorial designs for support sets of generating codes x_i, which have implications for polynomial time.
+Moreover, we have shown that a subset of dictionary elements are recoverable even if the number of dictionary elements in total is unknown; these observations are discussed in more detail below.
 
@@
 This point was only hinted at in the Discussion section of our original submission, but we have included it in the updated manuscript to make clear the power of our approach over that taken in [HS15].
+We are aware of only one work treating combinatorial hypergraph designs in the setting of dictionary learning, "An incidence geometry approach to dictionary learning" (arxiv, non-published paper)
 
@@
 
-RESPONSE: We appreciate this question and have added comments of this comparison to the manuscript (all sample complexities improve in this work).
+RESPONSE: We appreciate this question but, since in all comparable cases the sample complexities improve in this work, we feel that an explicit comparison would not be the best use of our limited space; although we are willing to do so if necessary.
 Many thanks for your careful review of the mathematics.

### 2017-08-15 manuscripts/PNAS/review/point_by_point_response.txt
crafty edits

@@
 
-[IHS10] Isely, Hillar, Sommer, Advances in neural information processing systems (NIPS), 2010.
-[GS12] Ganguli, Sompolinksi, Annual review of neuroscience, 2012.
-[TP14] Tillman, Pfetsch, IEEE Transactions on information processing, 2014.
-[HS15] Hillar, Sommer, IEEE Transactions on information processing, 2015.
-[M10] Morris I (2010), Advances in Mathematics 225(6):3425–3445.
+(IHS10) Isely, Hillar, Sommer, Advances in neural information processing systems, 2010.
+(GS12) Ganguli, Sompolinksi, Annual review of neuroscience, 2012.
+(TP14) Tillman, Pfetsch, IEEE Transactions on information processing, 2014.
+(HS15) Hillar, Sommer, IEEE Transactions on information processing, 2015.
+(M10) Morris I (2010), Advances in Mathematics 225(6):3425–3445.
 
@@
 -----------------
-Since the result is an extension of the noise-free result of [HS15] to a noisy case, the authors should provide better justification for the significance of contributions.
-The main result seems to be based on an approach similar to [HS15], and there is little to no discussion of the computability and tightness of the sufficient condition for stability in the main results.
-Thus, the submission does not seem to be greatly more valuable than [HS15] and also not conclusive regarding the central problems of sparse linear coding and dictionary learning.
+Since the result is an extension of the noise-free result of (HS15) to a noisy case, the authors should provide betzer justification for the significance of contributions.
+The main result seems to be based on an approach similar to (HS15), and there is little to no discussion of the computability and tightness of the sufficient condition for stability in the main results.
+Thus, the submission does not seem to be greatly more valuable than (HS15) and also not conclusive regarding the central problems of sparse linear coding and dictionary learning.
 That being said, the paper (with the modifications below) would certainly merit publication in very solid journal like IEEE Transactions on Information Theory, where it would be a median paper, in my opinion.
@@
 
-We agree with the reviewer that a straightforward extension of the approach and noise-free result of [HS15] to the noisy case — while still a significant advancement in applied mathematics with actual practical implications — would not necessarily merit publication in PNAS on its own.
+We agree with the reviewer that a straightforward extension of the approach and noise-free result of (HS15) to the noisy case — while still a significant advancement in applied mathematics with actual practical implications — would not necessarily merit publication in PNAS on its own.
 The reviewer, however, seems to have overlooked the fact that our main result (Thm.
-1) generalizes the noise-free result of [HS15] far beyond a simple extension to the noisy case in ways which provide valuable insight into the dictionary learning model and that a significant deviation from the approach taken in [HS15] was necessary to prove these new facts.
+1) generalizes the noise-free result of (HS15) far beyond a simple extension to the noisy case in ways which provide valuable insight into the dictionary learning model and that a significant deviation from the approach taken in (HS15) was necessary to prove these new facts.
 Moreover, our solution (Cor.
@@
 The first quantity (a) is, in some form or another, related to standard objects in the field and may be computed as the smallest singular value of a set of specific sub-matrices; in particular, for fixed sparsity constraint k on H, the lower bound L_H(A) is efficiently computable (polynomial time).
-Because deciding L_H(A) > 0 is already NP-hard [TP14], it seems likely that without fixing a sparsity level there is no efficient computation in general for (a).
+Because deciding L_H(A) > 0 is already NP-hard (TP14), it seems likely that without fixing a sparsity level there is no efficient computation in general for (a).
 The calculation of (b) involves determining "canonical angles" between subspaces, which is usually reduced again to a numerical (efficient) singular value decomposition given the fixed subspaces.
@@
 Finally, with respect to (c), we regard this as a fundamental open problem in the field: how many sparsely generated samples determine the linear coding model?
-(One reason to be skeptical that a polynomial suffice is again [TP14].)  However, there is some good news -- if k is fixed and we constrain sparse codes \hat{x}_i to come from a polynomial number of supports, then a polynomial number of samples N is enough to guarantee uniqueness.
-In particular, a sample complexity polynomial in (m,k) can be achieved by limiting the size of the support set of the \tilde x_i, and we have revised the manuscript to discuss this fact (which, incidentally, does not follow from the results of [HS15] in the noiseless case).
+(One reason to be skeptical that a polynomial suffice is again (TP14).)  However, there is some good news -- if k is fixed and we constrain sparse codes \hat{x}_i to come from a polynomial number of supports, then a polynomial number of samples N is enough to guarantee uniqueness.
+In particular, a sample complexity polynomial in (m,k) can be achieved by limiting the size of the support set of the \tilde x_i, and we have revised the manuscript to discuss this fact (which, incidentally, does not follow from the results of (HS15) in the noiseless case).
 
@@
 
-The reviewer also raises the concern that, regardless of practical implications, our results may amount to an incremental advance over those of [HS15] by way of similar techniques.
+The reviewer also raises the concern that, regardless of practical implications, our results may amount to an incremental advance over those of (HS15) by way of similar techniques.
 We disagree with this assessment on both counts: our main result (Thm.
-1) goes far beyond a straightforward extension of that in [HS15] to the noisy case and this required a significant deviation from their approach.
+1) goes far beyond a straightforward extension of that in (HS15) to the noisy case and this required a significant deviation from their approach.
 
@@
 As observed by our second reviewer, however, the extension to the noisy case did indeed require an novel combination of several results in the literature.
-Specifically, the main difficulty was to generalize Lemma 1 to the case where the k-dimensional subspaces spanned by corresponding (through the map \pi) submatrices of A and B are assumed only to be proximal (small ‘d’), and not identical as in [HS15].
+Specifically, the main difficulty was to generalize Lemma 1 to the case where the k-dimensional subspaces spanned by corresponding (through the map \pi) submatrices of A and B are assumed only to be proximal (small ‘d’), and not identical as in (HS15).
 In contrast to the noiseless case, here it must be explicitly demonstrated that this proximity relation is propagated through the repeated intersections of these submatrix spans all the way down to the spans of dictionary elements themselves.
 We designed and proved Lemma 4 to address this issue, which draws its bound from the convergence guarantees of an alternating projections algorithm first proposed by von Neumann.
-This result, combined with a little known fact about the distance ‘d’ requiring proof in [M10], constitute the more sophisticated and obscure components of the deduction in eq.(26).
-To reiterate, this step is completely trivial in the noiseless case and required no mention for the inductive steps taken in [HS15].
+This result, combined with a little known fact about the distance ‘d’ requiring proof in (M10), constitute the more sophisticated and obscure components of the deduction in eq.(26).
+To reiterate, this step is completely trivial in the noiseless case and required no mention for the inductive steps taken in (HS15).
 
-Our proof of Lemma 1 diverges perhaps even more significantly from the approach taken in [HS15] by way of Lemma 5.
-Key to our reduction of the sample complexity given in [HS15] by an exponential factor is the introduction of a combinatorial design (the "singleton intersection property") for support sets.
-Since in this case the map \pi from supports in the hypergraph to {[m] \choose k} is not surjective, one cannot apply the same inductive method as in [HS15], which freely chooses supports in the codomain to intersect at (k-1) nodes and map back to some corresponding (k-1)-sized intersection of supports in the domain.
+Our proof of Lemma 1 diverges perhaps even more significantly from the approach taken in (HS15) by way of Lemma 5.
+Key to our reduction of the sample complexity given in (HS15) by an exponential factor is the introduction of a combinatorial design (the "singleton intersection property") for support sets.
+Since in this case the map \pi from supports in the hypergraph to {[m] \choose k} is not surjective, one cannot apply the same inductive method as in (HS15), which freely chooses supports in the codomain to intersect at (k-1) nodes and map back to some corresponding (k-1)-sized intersection of supports in the domain.
 Instead, we demonstrate the surprising fact that by pigeonholing the images of supports in the (SIP-satisfying) hypergraph H one can still guarantee a bijection between the nodes and therefore the subspaces spanned by individual dictionary elements.
@@
 
-To be clear, the new perspective we take on the problem yields the following powerful conclusions beyond those of a straightforward extension of [HS15] to the noisy case:
+To be clear, the new perspective we take on the problem yields the following powerful conclusions beyond those of a straightforward extension of (HS15) to the noisy case:
 
-1) An extension to the case where the number of dictionary elements is unknown: The results of [HS15] only apply to the case where the matrix B has the same number of columns as A.
+1) An extension to the case where the number of dictionary elements is unknown: The results of (HS15) only apply to the case where the matrix B has the same number of columns as A.
 We forgo this assumption and show that B must have at least as many columns as A and contains (up to noise) a subset of the columns of A.
@@
 
-2) A significant reduction in sample complexity: To identify the n x m generating dictionary A, [HS15] require that data be sampled from every k-dimensional subspace spanned by the m columns of A (that is, {m \choose k} subspaces in total).
+2) A significant reduction in sample complexity: To identify the n x m generating dictionary A, (HS15) require that data be sampled from every k-dimensional subspace spanned by the m columns of A (that is, {m \choose k} subspaces in total).
 We show that the data need only be sampled from m subspaces in total (e.g.
@@
 1 requires only a polynomial number of samples distributed over a polynomial number of supports; thus, N is polynomial in m, k.
-This point was only hinted at in the Discussion section of our original submission, but we have included it in the updated manuscript to make clear the power of our approach over that taken in [HS15].
+This point was only hinted at in the Discussion section of our original submission, but we have included it in the updated manuscript to make clear the power of our approach over that taken in (HS15).
 We are aware of only one work treating combinatorial hypergraph designs in the setting of dictionary learning, "An incidence geometry approach to dictionary learning" (arxiv, non-published paper)
 
-3) No spark condition requirement for the generating matrix A: One of the mathematically significant contributions made by [HS15] was to forgo the constraint that the recovery matrix B also satisfy the spark condition, in contrast to all previously known uniqueness results which (either explicitly or implicitly) made this assumption.
+3) No spark condition requirement for the generating matrix A: One of the mathematically significant contributions made by (HS15) was to forgo the constraint that the recovery matrix B also satisfy the spark condition, in contrast to all previously known uniqueness results which (either explicitly or implicitly) made this assumption.
 Our proof is powerful enough to show that, in fact, even the matrix A need not satisfy the spark condition to be identifiable!
 Rather, it need only be injective on the union of subspaces with supports that form sets in a hypergraph satisfying the singleton intersection property (SIP).
-(For example, consider the matrix A = [e_1, …, e_5, v] where v = e_1 + e_3 + e_5.
+(For example, consider the matrix A = [e_1,..., e_5, v] where v = e_1 + e_3 + e_5.
 and take H to be the set of all consecutive pairs of [m] arranged in cyclic order.
@@
 
-Finally, we should mention that our main mathematical results justify the neurally plausible model of bottleneck communication between brain regions, first explained in depth in this NIPS paper [IHS10] and then in a review of sparse linear coding applications to neuroscience [GS12].
+Finally, we should mention that our main mathematical results justify the neurally plausible model of bottleneck communication between brain regions, first explained in depth in this NIPS paper (IHS10) and then in a review of sparse linear coding applications to neuroscience (GS12).
 
@@
 RESPONSE: Both reviewers have raised this concern and we again thank the editor for the opportunity to address it.
-It seems both reviewers have not noticed the several ways in which our results generalize the modern results of [HS15] beyond a straightforward extension to the noisy case, not to mention our solution to the optimization Prob.
+It seems both reviewers have not noticed the several ways in which our results generalize the modern results of (HS15) beyond a straightforward extension to the noisy case, not to mention our solution to the optimization Prob.
 2, which as far as we know is the first of its kind and of most interest to practitioners.

### 2017-08-15 manuscripts/PNAS/chazthm_pnas.tex
crafty edits

@@
 
-Another practical implication of this result is the following: there is an effective procedure by which one can affirm if one's proposed solution $(\mathbf{B}, \mathbf{\bar x}_1, \ldots, \mathbf{x}_N)$ to Prob.~\ref{InverseProblem} is indeed unique (up to noise and inherent ambiguities).
+Another practical implication of Thm.\ref{DeterministicUniquenessTheorem} is the following: there is an effective procedure sufficient to affirm if a proposed solution $(\mathbf{B}, \mathbf{\bar x}_1, \ldots, \mathbf{x}_N)$ to Prob.~\ref{InverseProblem} is indeed unique (up to noise and inherent ambiguities).
 One simply checks that $\mathbf{B}$ and the $\mathbf{\bar x}_i$ satisfy the respective assumptions of Thm.~\ref{DeterministicUniquenessTheorem}.
@@
 %(since $\{ \mathbf{A}_1, \mathbf{A}_3, \mathbf{A}_5, \mathbf{A}_6\}$ is not a linearly independent set).
-This weakening of condition \eqref{SparkCondition} allows for a practical amount of data (polynomial-time for fixed sparsity $k$) for guaranteeing stable sparse representation.
+This weakening allows for a practical amount of data (polynomial-time for fixed sparsity $k$)  guaranteeing stable dictionaries.
 
 There are other less direct consequences of Thm.~\ref{DeterministicUniquenessTheorem}.
-For instance, we use it to prove uniqueness for the optimization formulation of dictionary learning, Prob.~\ref{SLCopt}, the main object of interest for those applying dictionary learning to data.
+For instance, we use it to prove uniqueness for the optimization formulation of dictionary learning, Prob.~\ref{SLCopt}, the main object of interest for those applying dictionary learning to their data.
 
 \begin{theorem}\label{SLCopt}
-If the assumptions of Thm.\ref{DeterministicUniquenessTheorem} hold, only now with more than $(k-1)\left[ {\bar m \choose k} + |\mathcal{H}|k{\bar m \choose k-1}\right]$ vectors $\mathbf{x}_i$ supported in each $S \in \mathcal{H}$, then all solutions to Prob.~\ref{OptimizationProblem} necessarily satisfy implications \eqref{Cstable} and \eqref{b-PDa} of Thm.~\ref{DeterministicUniquenessTheorem}.
+If the assumptions of Thm.\ref{DeterministicUniquenessTheorem} hold, only now with more than $(k-1)\left[ {\bar m \choose k} + |\mathcal{H}|k{\bar m \choose k-1}\right]$ vectors $\mathbf{x}_i$ supported in each $S \in \mathcal{H}$, then all solutions to Prob.~\ref{OptimizationProblem} necessarily satisfy recovery inequalities \eqref{Cstable} and \eqref{b-PDa} of Thm.~\ref{DeterministicUniquenessTheorem}.
 \end{theorem}
@@
 
-Since $f$ is analytic, having a single substitution of a real matrix $\mathbf{A}$ with $f(\mathbf{A}) \neq 0$ necessarily implies that the zeroes of $f$, in fact, form a set of measure zero.
+Since $f$ is analytic, having a single substitution of a real matrix $\mathbf{A}$ with $f(\mathbf{A}) \neq 0$ necessarily implies that the zeroes of $f$ form a set of measure zero.
 Fortunately, such a matrix $\mathbf{A}$ is easily constructed by adding rows of zeroes to any $\min(2k,m) \times m$ Vandermonde matrix as described above (so that each term in the product above for $f$ is nonzero).
@@
 
-We remark that these results have a strong application to theoretical neuroscience, mathematically justifying one of the few hypothesized theories of compressive communication between sparsely active neural populations \cite{Isely10, ganguli2012compressed}.
+We remark that these results have a surprising application to theoretical neuroscience by mathematically justifying one of the few hypothesized theories of compressive communication between sparsely active neural populations \cite{Isely10}.
 
@@
 
-The heart of the matter is therefore \eqref{Cstable}, which we now finally establish, first in the important special case $k = 1$
+The heart of the matter is therefore \eqref{Cstable}, which we now establish, first in the important special case $k = 1$
 
@@
 \end{align*}
-where the last inequality follows directly from \eqref{Ldef}. From Def.~\ref{dDef} we have:
+where the last inequality follows directly from \eqref{Ldef}. From Def.~\ref{dDef}:
 \begin{align}\label{rhs222}
@@
 % A significant implication is that the constant $C_1$ of Thm.~\ref{DeterministicUniquenessTheorem} can be computed efficiently if we restrict the class of possible supports for the $\mathbf{\bar x}_i$.
-
-[*** ADD:  Ganguli, Deep Learning, constants, tightness, ***]
 
@@
 \end{align}
-
 If the map $\pi: E \to 2^{[\bar m]}$ has $\sum_{S \in \mathcal{H}} (|\pi(S)| -|S|) \geq 0$ and:
@@
 Suppose then that the intersection is not the zero vector.
-Keeping in mind that $d(U,V) \leq d(U',V)$ whenever $U \subseteq U'$ and applying (in order) Lem.~\ref{spanIntersectionLemma}, Lem.~\ref{DistanceToIntersectionLemma}, \eqref{eqdim}, \eqref{GapUpperBound} and finally \eqref{Cdef2} gives:
+Keeping in mind that $d(U,V) \leq d(U',V)$ whenever $U \subseteq U'$ and applying (in order) Lem.~\ref{spanIntersectionLemma}, Lem.~\ref{DistanceToIntersectionLemma}, \eqref{eqdim}, \eqref{GapUpperBound}, and \eqref{Cdef2} gives:
 \begin{align}\label{randoml}
@@
 
-Since $\varepsilon < L_2(\mathbf{A}) / C_2$, by \eqref{delrho} the right-hand side in \eqref{randoml} is strictly less than one.
+Since $\varepsilon < L_2(\mathbf{A}) / C_2$, by \eqref{delrho} the right-hand side in \eqref{randoml} is less than one.
 Hence, $\dim(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}) \leq \dim(\bm{\mathcal{A}}_{\cap \mathcal{G}})$ by \eqref{dimLem}, and \eqref{cond} follows from the linear independence of the columns of $\mathbf{A}_{S}$ and $\mathbf{B}_{\pi(S)}$ for all $S \in \mathcal{G}$.
@@
 % for space:  (e.g.,  \cite{folland2013real}).
-By Thm.~\ref{robustPolythm}, there is a polynomial that is nonzero when $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$; in particular, stability holds with probability one.
+By Thm.~\ref{robustPolythm}, there is a polynomial that is nonzero when $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$; in particular, stability is almost sure.
 \end{proof}

### 2017-08-15 manuscripts/PNAS/chazthm_pnas.tex
chaz

--- 2017-08-15 manuscripts/PNAS/chazthm_pnas.tex
@@
 The following is a precise statement of our main result.
-Only the quantity $C_1 = C_1(\mathbf{A}, \{\mathbf{x}_i\}_{i=1}^N, \mathcal{H})$ is undefined (until Sec.~\ref{DUT}, Eq.~\eqref{Cdef1}).
+For sake of brevity, the quantity $C_1 = C_1(\mathbf{A}, \{\mathbf{x}_i\}_{i=1}^N, \mathcal{H})$ is left undefined until Sec.~\ref{DUT} (see \eqref{Cdef1}).
 %=======
@@
 Fix an $n \times m$ matrix $\mathbf{A}$ with $L_{2\mathcal{H}}(\mathbf{A}) > 0$ for an $r$-regular $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP.
-If \mbox{$\{\mathbf{x}_1, \ldots, \mathbf{x}_N\} \subset \mathbb{R}^m$} contains, for each $S \in \mathcal{H}$, more than $(k-1){m \choose k}$ $k$-sparse vectors in general linear position supported in $S$, then there is $C_1 > 0$ with the following holding for all\footnote{The condition $\varepsilon < L_2(\mathbf{A}) /C_1$ is necessary; otherwise,  with \mbox{$\mathbf{A}$ = $\mathbf{I}$} and $\mathbf{x}_i = \mathbf{e}_i$, there is a matrix $\mathbf{B}$ and $1$-sparse $\mathbf{\bar{x}}_i$ with $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\bar{x}}_i \|_2 \leq \varepsilon$, but nonetheless violating \eqref{Cstable}.} $\varepsilon < L_{2}(\mathbf{A}) / C_1$:
+If \mbox{$\{\mathbf{x}_1, \ldots, \mathbf{x}_N\} \subset \mathbb{R}^m$} contains, for each $S \in \mathcal{H}$, more than $(k-1){m \choose k}$ $k$-sparse vectors in general linear position all supported in $S$, then there is $C_1 > 0$ with the following holding for all\footnote{The condition $\varepsilon < L_2(\mathbf{A}) /C_1$ is necessary; otherwise,  with \mbox{$\mathbf{A}$ = $\mathbf{I}$} and $\mathbf{x}_i = \mathbf{e}_i$, there is a matrix $\mathbf{B}$ and $1$-sparse $\mathbf{\bar{x}}_i$ with $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\bar{x}}_i \|_2 \leq \varepsilon$, but nonetheless violating \eqref{Cstable}.} $\varepsilon < L_{2}(\mathbf{A}) / C_1$:
 
@@
 Another practical implication of this result is the following: there is an effective procedure by which one can affirm if one's proposed solution $(\mathbf{B}, \mathbf{\bar x}_1, \ldots, \mathbf{x}_N)$ to Prob.~\ref{InverseProblem} is indeed unique (up to noise and inherent ambiguities).
-One simply checks that $\mathbf{B}$ and the $\mathbf{\bar x}_i$ satisfy the respective assumptions of Thm.~\ref{DeterministicUniquenessTheorem}.
+One simply checks that $\mathbf{B}$ and the $\mathbf{\bar x}_i$ satisfy the respective assumptions of Thm.~\ref{DeterministicUniquenessTheorem}, for which all quantities are effectively computable.
 %.

### 2017-08-15 manuscripts/PNAS/chazthm_pnas.tex
sml edits manu

--- 2017-08-15 manuscripts/PNAS/chazthm_pnas.tex
@@
 Since for every $S \in \mathcal{H}$ there are over $(k-1)\left[ {\bar m \choose k} + |\mathcal{H}|k{ \bar m \choose k-1} \right]$ vectors $\mathbf{x}_i$ supported there, it follows that more than $(k-1){\bar m \choose k}$ of them have corresponding $\mathbf{\bar x}_i$ that are $k$-sparse.
-The result now follows directly from Thm.~\ref{DeterministicUniquenessCorollary}.
+The result now follows from Thm.~\ref{DeterministicUniquenessCorollary}.
 \end{proof}
@@
 In the field of theoretical neuroscience in particular, dictionary learning for sparse coding and related methods have recovered characteristic components of natural images \cite{Olshausen96, hurri1996image, bell1997independent, van1998independent} and sounds \cite{bellsejnowski1996, smithlewicki2006, Carlson12} that reproduce response properties of cortical neurons.
-Our results suggest that this correspondence could be due to the ``universality'' of sparse representations in natural data, an early mathematical idea in neural theory \cite{pitts1947}.
+Our results suggest that this correspondence could be due to the ``universality'' of sparse representations in natural data, an early idea in neural theory \cite{pitts1947}.
 %Furthermore, they justify the hypothesis of \cite{Isely10} that sparse codes passed through information bottlenecks in the brain are recovered from random projections via (unsupervised) biologically plausible sparse coding (e.g., \cite{rehnsommer2007, rozell2007neurally, ganguli2012compressed, hu2014hebbian}).
-
 Deep learning noise issues: \cite{goodfellow2014explaining}.

### 2017-08-15 manuscripts/PNAS/chazthm_pnas.tex
6 pages

@@
 \end{align*}
+\vspace{-.2 cm}
 \end{proof}
@@
 In this note, we prove the stability of unique solutions to Probs.~\ref{InverseProblem} and \ref{OptimizationProblem} while significantly reducing the known sample complexity.
-Our results justify the application of the sparse linear coding model to blind source separation problems, wherein the goal is to infer the generating dictionary and sparse codes from noisy measurements, \eqref{LinearModel}.
+Our results justify the application of the sparse linear coding model to blind source separation problems, wherein the goal is to infer the generating dictionary and sparse codes from noisy measurements, as in \eqref{LinearModel}.
 We also collect a set of useful mathematical tools and basic facts for future research.
-The main motivation for this work, however, was to understand how seemingly universal representations emerge from sparse coding models fit to natural data by a variety of methodologies.
-We elaborate on these applications below.
+The main motivation for this work, however, was to understand how seemingly universal representations emerge from various sparse coding models fit to natural data.
 
@@
 Moreover, we show that even if the meta-parameter for the number of dictionary elements is overestimated, a subset of parameters may still be identifiable up to noise.
-It would therefore be of practical utility to determine the best possible dependence of $\varepsilon$ on $\delta_1, \delta_2$ in Def.\ref{maindef} as well as the minimal requirements on the number and diversity of generating codes, and we hope that other researchers continue to improve and extend our results.
 We remark that our constants have been derived for deterministic ``worst-case'' noise, whereas the ``effective'' noise might be smaller when sampled from a distribution.
-% ; in such cases, the constants will improve as well.
 
@@
 For instance, whether there is a sample size $N$ that is polynomial in $m,k$ gauranteeing the conclusions of Thm.~\ref{DeterministicUniquenessTheorem} has implications for the computational complexity of Probs.~\ref{InverseProblem} and \ref{OptimizationProblem} and related questions \cite{Tillmann15}.
-A reexamination of pigeonholing argument in the proof of Thm.~\ref{DeterministicUniquenessTheorem} demonstrates that this can in fact be achieved if one restricts the supports of the $\mathbf{\bar x}_i$ to a class that grows polynomially in $m, k$.
+A reexamination of the pigeonholing argument in the proof of Thm.~\ref{DeterministicUniquenessTheorem} demonstrates that this can in fact be achieved if one restricts the supports of the $\mathbf{\bar x}_i$ to a class that grows polynomially in $m, k$.
 
-A technical difficulty in proving Thm.~\ref{DeterministicUniquenessTheorem} was the absence of any kind of assumption on solutions to Prob.~\ref{InverseProblem}.
+A technical difficulty in proving Thm.~\ref{DeterministicUniquenessTheorem} is the absence of any assumption on dictionaries in solutions to Prob.~\ref{InverseProblem}.
 Although mathematically interesting that no such requirement is necessary, there are other reasons to seek out such a theoretical guarantee.
-For instance, it is difficult to ensure that an algorithm maintain a dictionary satisfying \eqref{SparkCondition} at each iteration; indeed, even certifying a dictionary has this property is likely intractable given its NP-hardness \cite{tillmann2014computational}.
+For instance, it is difficult to ensure that an algorithm maintain a dictionary satisfying the spark condition \eqref{SparkCondition} at each iteration; indeed, even certifying a dictionary has this property is likely intractable given its NP-hardness \cite{tillmann2014computational}.
 
@@
 
-In the field of theoretical neuroscience in particular, dictionary learning for sparse coding and related methods have recovered characteristic components of natural images \cite{Olshausen96, hurri1996image, bell1997independent, van1998independent} and sounds \cite{bellsejnowski1996, smithlewicki2006, Carlson12} that reproduce response properties of cortical neurons.
+In the field of theoretical neuroscience in particular, dictionary learning for sparse coding and related methods have recovered characteristic components of natural images \cite{Olshausen96, hurri1996image, bell1997independent, van1998independent} and sounds \cite{bellsejnowski1996, smithlewicki2006, Carlson12} that some of the reproduce response properties of cortical neurons.
 Our results suggest that this correspondence could be due to the ``universality'' of sparse representations in natural data, an early idea in neural theory \cite{pitts1947}.
@@
 \begin{proof}[Proof (sketch) of Thm.~\ref{robustPolythm}]
-Let $M$ be the matrix with columns $\mathbf{A}\mathbf{x}_i$, $i \in [N]$.  Consider the polynomial in the entries of $\mathbf{A}$ and $\mathbf{x}_i$:
+Let $\textbf{M}$ be the matrix with columns $\mathbf{A}\mathbf{x}_i$, $i \in [N]$.  Consider the polynomial in the entries of $\mathbf{A}$ and $\mathbf{x}_i$:
 \begin{align*}
-g(\mathbf{A}, \{\mathbf{x}_i\}_{i=1}^N) := \prod_{S \in {[N] \choose k}} \sum_{S' \in {[n] \choose k}} (\det M_{S',S})^2,
+g(\mathbf{A}, \{\mathbf{x}_i\}_{i=1}^N) := \prod_{S \in {[N] \choose k}} \sum_{S' \in {[n] \choose k}} (\det \textbf{M}_{S',S})^2,
 \end{align*}
@@
 % for space:  (e.g.,  \cite{folland2013real}).
-By Thm.~\ref{robustPolythm}, there is a polynomial that is nonzero when $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$; in particular, stability is almost sure.
+By Thm.~\ref{robustPolythm}, there is a polynomial that is nonzero when $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$; in particular, stability holds almost surely.
 \end{proof}

### 2017-08-15 manuscripts/PNAS/chazthm_pnas.tex

--- 2017-08-15 manuscripts/PNAS/chazthm_pnas.tex
@@
 %\cite{rehnsommer2007, rozell2007neurally, ganguli2012compressed, hu2014hebbian}
+
+%\pagebreak
 
@@
 Since for every $S \in \mathcal{H}$ there are over $(k-1)\left[ {\bar m \choose k} + |\mathcal{H}|k{ \bar m \choose k-1} \right]$ vectors $\mathbf{x}_i$ supported there, it follows that more than $(k-1){\bar m \choose k}$ of them have corresponding $\mathbf{\bar x}_i$ that are $k$-sparse.
-The result now follows from Thm.~\ref{DeterministicUniquenessCorollary}.
+The result now follows directly from Thm.~\ref{DeterministicUniquenessCorollary}.
 \end{proof}
@@
 In the field of theoretical neuroscience in particular, dictionary learning for sparse coding and related methods have recovered characteristic components of natural images \cite{Olshausen96, hurri1996image, bell1997independent, van1998independent} and sounds \cite{bellsejnowski1996, smithlewicki2006, Carlson12} that reproduce response properties of cortical neurons.
-Our results suggest that this correspondence could be due to the ``universality'' of sparse representations in natural data, an early idea in neural theory \cite{pitts1947}.
+Our results suggest that this correspondence could be due to the ``universality'' of sparse representations in natural data, an early mathematical idea in neural theory \cite{pitts1947}.
 %Furthermore, they justify the hypothesis of \cite{Isely10} that sparse codes passed through information bottlenecks in the brain are recovered from random projections via (unsupervised) biologically plausible sparse coding (e.g., \cite{rehnsommer2007, rozell2007neurally, ganguli2012compressed, hu2014hebbian}).
+
 Deep learning noise issues: \cite{goodfellow2014explaining}.

### 2017-08-15 manuscripts/PNAS/chazthm_pnas.tex
chaz

--- 2017-08-15 manuscripts/PNAS/chazthm_pnas.tex
@@
 \begin{corollary}\label{DeterministicUniquenessCorollary}
-Given a regular hypergraph $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP, there are $N =  |\mathcal{H}| \left[ (k-1){m \choose k} + 1  \right]$ vectors \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} such that every matrix $\mathbf{A}$ with $L_{2\mathcal{H}}(\mathbf{A}) > 0$ generates a dataset $Y = \{\mathbf{A}\mathbf{x}_1, \ldots, \mathbf{A}\mathbf{x}_N\}$ with a stable $k$-sparse representation in $\mathbb{R}^m$.
+Given a regular hypergraph $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP, there are $N =  |\mathcal{H}| \left[ (k-1){m \choose k} + 1  \right]$ vectors \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} such that every matrix $\mathbf{A}$ with $L_{2k}(\mathbf{A}) > 0$ generates a dataset $Y = \{\mathbf{A}\mathbf{x}_1, \ldots, \mathbf{A}\mathbf{x}_N\}$ with a stable $k$-sparse representation in $\mathbb{R}^m$.
 \end{corollary}
+% Needs to be L_{2k}(A) > 0 to guarantee sparse vector recovery
 
@@
 
-Another practical implication of Thm.\ref{DeterministicUniquenessTheorem} is the following: there is an effective procedure sufficient to affirm if a proposed solution $(\mathbf{B}, \mathbf{\bar x}_1, \ldots, \mathbf{x}_N)$ to Prob.~\ref{InverseProblem} is indeed unique (up to noise and inherent ambiguities).
+Another practical implication of Thm.\ref{DeterministicUniquenessTheorem} is the following: there is an effective procedure sufficient to affirm if a proposed solution to Prob.~\ref{InverseProblem} is indeed unique (up to noise and inherent ambiguities).
+One simply checks that the matrix and sparse codes satisfy the respective assumptions of Thm.~\ref{DeterministicUniquenessTheorem} on $\mathbf{A}$ and the $\mathbf{x}_i$.
+%Another practical implication of Thm.\ref{DeterministicUniquenessTheorem} is the following: there is an effective procedure sufficient to affirm if a proposed solution $(\mathbf{B}, \mathbf{\bar x}_1, \ldots, \mathbf{x}_N)$ to Prob.~\ref{InverseProblem} is indeed unique (up to noise and inherent ambiguities).
 One simply checks that $\mathbf{B}$ and the $\mathbf{\bar x}_i$ satisfy the respective assumptions of Thm.~\ref{DeterministicUniquenessTheorem}.
@@
 %
-where the maximum is taken over all orderings\footnote{We modify the quantity in \cite{Deutsch12} in this way since the subspace ordering is irrelevant to our purpose.} of the $V_i$ and the angle $\theta \in (0,\frac{\pi}{2}]$ is defined implicitly as \cite[Def.~9.4]{Deutsch12}:
+where the maximum is taken over all orderings 
+%\footnote{We modify the quantity in \cite{Deutsch12} in this way since the subspace ordering is irrelevant to our purpose.} 
+of the $V_i$ and the angle $\theta \in (0,\frac{\pi}{2}]$ is defined implicitly as \cite[Def.~9.4]{Deutsch12}:
 \begin{align*}

### 2017-08-15 manuscripts/PNAS/review/point_by_point_response.txt
pt by pt

--- 2017-08-15 manuscripts/PNAS/review/point_by_point_response.txt
@@
 
-RESPONSE: We appreciate this question but, since in all comparable cases the sample complexities improve in this work, we feel that an explicit comparison would not be the best use of our limited space; although we are willing to do so if necessary.
+RESPONSE: In brief, since all of the theorems and corollaries in [HS15] are corollaries of our theorems, all sample complexities improve by our work.
+The main point of difference between our statements about sample complexity and those of [HS15] is the assumed constraint on the underlying support set of sparse codes x_i.
+Our theory of combinatorial designs (the ‘singleton intersection property’) requires only that there be a sufficient number of x_i drawn from each support in a hypergraph satisfying the SIP, whereas the theory in [HS15] requires that a sufficient number of x_i be drawn from *every* support of size k in [m].
+Here, we make an explicit comparison with Table I in [HS15] row by row, assuming for our results that sufficient data have been sampled from all supports in a hypergraph H satisfying the SIP:
+
+ROW I.
+Our result here is |H|(k-1){m \choose k} + 1.
+We improve on the result in [HS15] by an exponential factor since our theory does not require that data be sampled with every possible support of size k in [m]; as noted in our manuscript, for every k < m there exists a hypergraph H with |H| = m that satisfies the SIP.
+
+ROW 2.
+Our result here is again |H|(k-1){m \choose k} + 1 with *certainty*, not with *almost certainty* (i.e.
+probability 1) as in [HS15].
+Here the authors in [HS15] have applied probabilistic arguments to achieve an almost certain result with a sample complexity on the same order as that for which we have achieved a certain result by means of our theory of combinatorial designs.
+
+ROW 3.
+We cannot make a direct comparison here because we have not calculated the probability that a random set of supports satisfy the SIP (see our response to a similar question by the second reviewer).
+We think this is an interesting problem for the community to solve; regardless, the result of [HS15] here is implied by our more general theory.
+
+ROW 4.
+Our result here is |H|(k-1){m \choose k} + 1 with probability 1.
+Here is the only case where the sample complexity stated in [HS15] is technically better than ours, but it differs in flavor: their x_i are assumed to be distributed as (k+1) samples per support for every support of size k in [m], whereas ours supposes that (k-1){m \choose k} codes x_i are distributed over each support in some hypergraph H satisfying the SIP.
+Regardless, the (technically) lower result of [HS15] is still implied by our more general theory in the case \varepsilon = 0 with the addition of their probabilistic argument.
+
+ROW 5: Again, we cannot make a direct comparison here for the reason stated in ROW 3.
+
+While we appreciate this question, we feel that since our results improve in every case except for one noise-free technicality (ROW 4), and since the results of [HS15] are all entailed anyway by our more general theory, an explicit comparison such as that which we provided above would not be the best use of our limited space in the manuscript; although we are willing to add a discussion about this if necessary.
 Many thanks for your careful review of the mathematics.

### 2017-08-16 manuscripts/PNAS/chazthm_pnas.tex
poly data

@@
 %(since $\{ \mathbf{A}_1, \mathbf{A}_3, \mathbf{A}_5, \mathbf{A}_6\}$ is not a linearly independent set).
-This weakening allows for a practical amount of data (polynomial-time for fixed sparsity $k$)  guaranteeing stable dictionaries.
+This weakening allows for a practical (polynomial) amount of data to still guarantee a stable dictionary in the case where the set of sparse supports for the $\mathbf{\bar x}_i$ is known to have a size that grows polynomially in $m, k$.
 

### 2017-08-16 manuscripts/PNAS/chazthm_pnas.tex
lemma 4

@@
 Letting $\{1, \ldots, m\}$ be denoted $[m]$, its power set $2^{[m]}$, and ${[m] \choose k}$ the set of subsets of $[m]$ of size $k$, we say a hypergraph $\mathcal{H} \subseteq 2^{[m]}$ on vertices $[m]$ is \textit{$k$-uniform} when $\mathcal{H} \subseteq {[m] \choose k}$.
-The \emph{degree} $\deg(i)$ of a node $i \in [m]$ is the number of sets in $\mathcal{H}$ that contain $i$, and we say $\mathcal{H}$ is \emph{regular} when for some $r$ we have $\deg(i) = r$ for all $i$ (given such an $r$, we say $\mathcal{H}$ is \textit{$r$-regular}).
+The \emph{degree} $\deg_\mathcal{H}(i)$ of a node $i \in [m]$ is the number of sets in $\mathcal{H}$ that contain $i$, and we say $\mathcal{H}$ is \emph{regular} when for some $r$ we have $\deg_\mathcal{H}(i) = r$ for all $i$ (given such an $r$, we say $\mathcal{H}$ is \textit{$r$-regular}).
 We also write $2\mathcal{H} := \{ S \cup S': S, S' \in \mathcal{H}\}$.
@@
 \begin{lemma}\label{NonEmptyLemma} 
-Fix a hypergraph $\mathcal{H} \subseteq 2^{[m]}$ with nodes labeled in order of non-increasing degree and for which $|\cap h(i)| = 1$ for all $i \leq q$.
-Fix $\bar m$ and let $p \leq q$ be the largest number satisfying:
-\begin{align}\label{pcond}
-\sum_{i=\ell}^{m} \deg(i) > (\bar m + 1 - \ell) (\deg(\ell) - 1) \ \ \text{for all } \ell \leq p.
+Fix an $r$-regular hypergraph $\mathcal{H} \subseteq 2^{[m]}$ satisfying the SIP.
+If the map $\pi: \mathcal{H} \to 2^{[\bar m]}$ has $\sum_{S \in \mathcal{H}} |\pi(S)| \geq \sum_{S \in \mathcal{H}} |S|$ and:
+\begin{align}\label{cond}
+|\cap \pi(\mathcal{G})| \leq |\cap \mathcal{G} |,\ \ \   \text{for } \mathcal{G} \subseteq \mathcal{H},
 \end{align}
-If the map $\pi: E \to 2^{[\bar m]}$ has $\sum_{S \in \mathcal{H}} (|\pi(S)| -|S|) \geq 0$ and:
-\begin{align}\label{cond}
-|\cap \pi(\mathcal{G})| \leq |\cap \mathcal{G} | \text{ for all } \mathcal{G} \subseteq \mathcal{H},
-\end{align}
-then $\bar m \geq\sum_i \deg(i) / \deg(1)$, and if $\bar m < \sum_i \deg(i) / (\deg(1) - 1)$ then the association $i \mapsto \cap \pi(h(i))$ defines an injective map to $[\bar m]$ from some nonempty $J \subseteq [m]$ of size $p$ consisting of the union of the set of all nodes of degree exceeding $\deg(p)$ and some set of nodes all having degree equal to $\deg(p)$.
-In particular, if $\mathcal{H}$ is $r$-regular then $|J| = \bar m - r(\bar m - m)$.
+%
+then $\bar m \geq m$, and if $\bar m < mr / (r-1)$ then the association $i \mapsto \cap \pi(\sigma(i))$ defines an injective map from $J$ to $[\bar m]$ for some $J \in {[m] \choose p}$.
+In particular, if $\bar m = m$ then $\pi$ is induced by a permutation on $[m]$.
 \end{lemma}
@@
 \begin{proof}
-Consider the collection of pairs: $T_1 := \{(i, S): i \in \pi(S), S \in \mathcal{H}\}$, which number $|T_1| = \sum_{S \in \mathcal{H}} |\pi(S)| \geq \sum_{S \in \mathcal{H}} |S| = \sum_{i \in [m]} \deg(i)$.
-Note that assumption \eqref{cond} implies $\bar m \geq |T_1| / \deg(1)$, since otherwise pigeonholing the elements of $T_1$ with respect to their set of possible first indices $[\bar m]$ would contradict that there are more than $\deg(1)$ sets in $\mathcal{H}$ sharing a common element.
-%QUESTION: Do we really need to say this..?
+Consider the collection of pairs: $T_1 := \{(i, S): i \in \pi(S), S \in \mathcal{H}\}$, which number $|T_1| = \sum_{S \in \mathcal{H}} |\pi(S)| \geq \sum_{S \in \mathcal{H}} |S| = \sum_{i \in [m]} \deg_\mathcal{H}(i) = mr$.
+Note that \eqref{cond} implies $\bar m \geq |T_1| / r = m$, since otherwise pigeonholing the elements of $T_1$ with respect to their possible first indices $[\bar m]$ would imply $\deg_\mathcal{H}(i) > r$ for some $i \in [m]$.
 
-By \eqref{pcond} and the upper bound on $\bar m$ we have $|T_1| >  \bar m (\deg(1) - 1)$, which implies, again by the pigeonhole principle, that there must be at least $\deg(1)$ elements of $T_1$ sharing the same first index.
-By \eqref{cond}, the intersection of the set $\mathcal{G}_1$ consisting of their second indices is nonempty.
-As $p \leq q$ and $\deg(1) \geq \deg(i)$ for all $i$, it must be that $|\cap \mathcal{G}_1| = 1$.
+If $\bar m < mr / (r-1)$ then, letting $p := \bar m - r( \bar m - m)$, we have $|T_1| = \bar m (r - 1) + p$ for positive $p$.
+By the pigeonhole principle, there must then be at least $r$ elements of $T_1$ sharing the same first index.
+By \eqref{cond}, the intersection of the set $\mathcal{G}_1$ consisting of their second indices is nonempty; hence $|\cap \mathcal{G}_1| = 1$ by $r$-regularity and the SIP.
 Since $\cap \pi(\mathcal{G}_1)$ is nonempty, applying \eqref{cond} again implies $\cap \pi(\mathcal{G}_1) = \{i_1\}$ for some $i_1 \in [m]$.
 If $p=1$ then we are done.
-Otherwise, define $T_2 := T_1 \setminus \{(i,S) \in T_1: i = i_1\}$, which contains $|T_2| = |T_1| - \deg(1) = \sum_{i=2}^m \deg(i)$ ordered pairs having $\bar m - 1$ distinct first indices.
-By \eqref{pcond} we have $|T_2| > (\bar m - 1)(\deg(2) - 1)$ and reiterating the above arguments produces a (necessarily) distinct index $i_2$.
-Iterating the arguments $p$ times yields the set of singletons \mbox{$J = \{\cap \mathcal{G}_1, \ldots, \cap \mathcal{G}_p\} \subseteq [m]$}.
-%TODO: Let T_1 be the set of all pairs $T_1 := \{(R, S): R \subseteq \pi(S), S \in \mathcal{H}\}$ 
+Otherwise, define $T_2 := T_1 \setminus \{(i,S) \in T_1: i = i_1\}$, which contains $|T_2| = |T_1| - r = (\bar m - 1)(r-1) + (p-1)$ ordered pairs having $\bar m - 1$ distinct first indices.
+Reiterating the above arguments produces a (necessarily) distinct index $i_2$.
+Iterating the arguments $p$ times yields the set of singletons \mbox{$J = \{i_1, \ldots, i_p\} \subseteq [m]$}.
 \end{proof}

### 2017-08-16 manuscripts/PNAS/chazthm_pnas.tex
chaz

@@
 
-We remark that these results have a surprising application to theoretical neuroscience by mathematically justifying one of the few hypothesized theories of compressive communication between sparsely active neural populations \cite{Isely10}.
+We remark that these results have an important application to theoretical neuroscience by mathematically justifying one of the few hypothesized theories of bottleneck communication between sparsely active neural populations \cite{Isely10}.
 
 \begin{proposition}
-Random noisy (linear) compression of sparse neural activities is decodable by any neurally-plausible unsupervised sparse (linear) feature learning algorithm that solves Prob.~\ref{DeterministicUniquenessTheorem} or \ref{SLCopt} (e.g.
+Sparse neural population activity is recoverable from random (linear) noisy compression by any method that solves Prob.~\ref{DeterministicUniquenessTheorem} or \ref{SLCopt}; in particular, via biophysically plausible unsupervised sparse coding (e.g.
 \cite{rehnsommer2007, rozell2007neurally}).

### 2017-08-16 manuscripts/PNAS/chazthm_pnas.tex
typos

@@
 \begin{align*}
-r(\{V_i\}_{i=1}^\ell) := 1 - \left(1 -  \max \prod_{i=1}^{\ell-1} \sin^2  \theta \left(V_i, \cap_{j>i} V_j \right)  \right)^{1/2},
+\xi(\{V_i\}_{i=1}^\ell) := 1 - \left(1 -  \max \prod_{i=1}^{\ell-1} \sin^2  \theta \left(V_i, \cap_{j>i} V_j \right)  \right)^{1/2},
 \end{align*} 
@@
 \begin{align}\label{Cdef2}
-C_2(\mathbf{A}, \mathcal{H}) := \frac{ 2^{|\mathcal{H}|} \max_{j \in [m]} \|\mathbf{A}_j\|_2}{ \min_{\mathcal{G} \subseteq \mathcal{H}} r( \{ \bm{\mathcal{A}}_S \}_{S \in \mathcal{G}}) },
+C_2(\mathbf{A}, \mathcal{H}) := \frac{ 2^{|\mathcal{H}|} \max_{j \in [m]} \|\mathbf{A}_j\|_2}{ \min_{\mathcal{G} \subseteq \mathcal{H}} \xi( \{ \bm{\mathcal{A}}_S \}_{S \in \mathcal{G}}) },
 \end{align}
@@
 \begin{align}\label{DTILeq}
-\text{\rm dist}(\mathbf{x}, V) \leq \frac{1}{r(\{V_i\}_{i = 1}^k)} \sum_{i=1}^k \text{\rm dist}(\mathbf{x}, V_i).
+\text{\rm dist}(\mathbf{x}, V) \leq \frac{1}{\xi(\{V_i\}_{i = 1}^k)} \sum_{i=1}^k \text{\rm dist}(\mathbf{x}, V_i).
 \end{align}
@@
 
-Finally, substituting this into \eqref{f} and rearranging produces \eqref{DTILeq} after replacing $1 - z$ with $r(\{V_i\}_{i=1}^k)$.
+Finally, substituting this into \eqref{f} and rearranging produces \eqref{DTILeq} after replacing $1 - z$ with $\xi(\{V_i\}_{i=1}^k)$.
 \end{proof}
@@
 %
-then $\bar m \geq m$, and if $\bar m < mr / (r-1)$ then the association $i \mapsto \cap \pi(\sigma(i))$ defines an injective map from $J$ to $[\bar m]$ for some $J \in {[m] \choose p}$.
+then $\bar m \geq m$, and if $\bar m < mr / (r-1)$ then the association $i \mapsto \cap \pi(\sigma(i))$ defines an injective map to $[\bar m]$ from some $J \subseteq [m]$ of size $\bar m - r(\bar m - m)$.
 In particular, if $\bar m = m$ then $\pi$ is induced by a permutation on $[m]$.
@@
 \leq d\left( \cap_{S \in \mathcal{G}} \bm{\mathcal{B}}_{\pi(S)}, \cap_{S \in \mathcal{G}} \bm{\mathcal{A}}_S \right) \nonumber \\
-&\leq \sum_{T \in \mathcal{G}} \frac{ d\left( \cap_{S \in \mathcal{G}} \bm{\mathcal{B}}_{\pi(S)},\bm{\mathcal{A}_{T}} \right) }{ r(  \{\bm{\mathcal{A}}_S\}_{S \in \mathcal{G}}) }
-\leq \sum_{T \in \mathcal{G}} \frac{ d\left( \bm{\mathcal{B}}_{\pi(T)},\bm{\mathbf{A}}_{T} \right) }{ r( \{\bm{\mathcal{A}}_S\}_{S \in \mathcal{G}}) }\nonumber \\
-&\leq \frac{|\mathcal{G}| \varepsilon}{r( \{\bm{\mathcal{A}}_S\}_{S \in \mathcal{G}})} 
+&\leq \sum_{T \in \mathcal{G}} \frac{ d\left( \cap_{S \in \mathcal{G}} \bm{\mathcal{B}}_{\pi(S)},\bm{\mathcal{A}_{T}} \right) }{ \xi(  \{\bm{\mathcal{A}}_S\}_{S \in \mathcal{G}}) }
+\leq \sum_{T \in \mathcal{G}} \frac{ d\left( \bm{\mathcal{B}}_{\pi(T)},\bm{\mathbf{A}}_{T} \right) }{ \xi( \{\bm{\mathcal{A}}_S\}_{S \in \mathcal{G}}) }\nonumber \\
+&\leq \frac{|\mathcal{G}| \varepsilon}{\xi( \{\bm{\mathcal{A}}_S\}_{S \in \mathcal{G}})} 
 \leq \frac{C_2 \varepsilon}{\max_i\|\mathbf{A}_i\|_2}. 
@@
 
-Now, by Lem.~\ref{NonEmptyLemma}, the association $i \mapsto \cap \pi(h(i))$ defines an injective map $\bar \pi: J \to [\bar m]$ for some $J \in {[m] \choose p}$ with $p$ given by \eqref{pcond}, and we can be sure that $\mathbf{B}_{\bar \pi(i)} \neq \mathbf{0}$ for all $i \in J$ since the columns of $\mathbf{B}_{\pi(S)}$ are linearly independent for all $S \in \mathcal{H}$.
+Now, by Lem.~\ref{NonEmptyLemma}, the association $i \mapsto \cap \pi(h(i))$ defines an injective map $\bar \pi: J \to [\bar m]$ for some $J \subseteq [m]$ of size $\bar m - r(\bar m - m)$, and we can be sure that $\mathbf{B}_{\bar \pi(i)} \neq \mathbf{0}$ for all $i \in J$ since the columns of $\mathbf{B}_{\pi(S)}$ are linearly independent for all $S \in \mathcal{H}$.
 It then follows from \eqref{eqdim} and \eqref{randoml} that $d\left( \bm{\mathcal{A}}_i, \bm{\mathcal{B}}_{\bar \pi(i)} \right) \leq C_2 \varepsilon / \max_i \|\mathbf{A}_i\|_2$ for all $i \in J$.

### 2017-08-16 manuscripts/PNAS/chazthm_pnas.tex
k to 2k in f(A)

@@
 \begin{align*}
-f(\mathbf{A}) := \prod_{S \in {[m] \choose k}} \sum_{S' \in {[n] \choose k}} (\det \mathbf{A}_{S',S})^2,
+f(\mathbf{A}) := \prod_{S \in {[m] \choose 2k}} \sum_{S' \in {[n] \choose 2k}} (\det \mathbf{A}_{S',S})^2,
 \end{align*}
 %
-where for any $S' \in {[n] \choose k}$ and $S \in {[m] \choose k}$, the symbol $\mathbf{A}_{S',S}$ denotes the submatrix of entries $A_{ij}$ with $(i,j) \in S' \times S$.
+where for any $S' \in {[n] \choose 2k}$ and $S \in {[m] \choose 2k}$, the symbol $\mathbf{A}_{S',S}$ denotes the submatrix of entries $A_{ij}$ with $(i,j) \in S' \times S$.
 We note that the large number of terms in this product is likely necessary due to the NP-hardness of deciding whether a given matrix $\mathbf{A}$ satisfies the spark condition \cite{tillmann2014computational}.
@@
 Since $f$ is analytic, having a single substitution of a real matrix $\mathbf{A}$ with $f(\mathbf{A}) \neq 0$ necessarily implies that the zeroes of $f$ form a set of measure zero.
+Fortunately, such a matrix $\mathbf{A}$ is easily constructed by adding rows of zeroes to any $\min(2k,m) \times m$ Vandermonde matrix as described above (so that each term in the product above for $f$ is nonzero).
+Hence, almost every $n \times m$ matrix with $n \geq \min(2k,m)$ satisfies \eqref{SparkCondition}.
+
+%Another extension of Thm.~\ref{DeterministicUniquenessTheorem} arises from the following analytic characterization of the spark condition.
+Let $\mathbf{A}$  be the $n \times m$ matrix of $nm$ indeterminates $A_{ij}$.
+When real numbers are substituted for $A_{ij}$, the resulting matrix satisfies \eqref{SparkCondition} if and only if the following polynomial is nonzero:
+%\begin{align*}
+%f(\mathbf{A}) := \prod_{S \in {[m] \choose k}} \sum_{S' \in {[n] \choose k}} (\det \mathbf{A}_{S',S})^2,
+%\end{align*}
+%
+%where for any $S' \in {[n] \choose k}$ and $S \in {[m] \choose k}$, the symbol $\mathbf{A}_{S',S}$ denotes the submatrix of entries $A_{ij}$ with $(i,j) \in S' \times S$.
+We note that the large number of terms in this product is likely necessary due to the NP-hardness of deciding whether a given matrix $\mathbf{A}$ satisfies the spark condition \cite{tillmann2014computational}.
+
+%Since $f$ is analytic, having a single substitution of a real matrix $\mathbf{A}$ with $f(\mathbf{A}) \neq 0$ necessarily implies that the zeroes of $f$ form a set of measure zero.
 Fortunately, such a matrix $\mathbf{A}$ is easily constructed by adding rows of zeroes to any $\min(2k,m) \times m$ Vandermonde matrix as described above (so that each term in the product above for $f$ is nonzero).

### 2017-08-16 manuscripts/PNAS/chazthm_pnas.tex
k to 2k in Thm3 pf
sml updates

@@
 The following is a precise statement of our main result.
-For sake of brevity, the quantity $C_1 = C_1(\mathbf{A}, \{\mathbf{x}_i\}_{i=1}^N, \mathcal{H})$ is left undefined until Sec.~\ref{DUT} (see \eqref{Cdef1}).
+The quantity $C_1 = C_1(\mathbf{A}, \{\mathbf{x}_i\}_{i=1}^N, \mathcal{H})$ is left undefined until Sec.~\ref{DUT} (see \eqref{Cdef1}).
 %=======
@@
 Another practical implication of Thm.\ref{DeterministicUniquenessTheorem} is the following: there is an effective procedure sufficient to affirm if a proposed solution to Prob.~\ref{InverseProblem} is indeed unique (up to noise and inherent ambiguities).
-One simply checks that the matrix and sparse codes satisfy the respective assumptions of Thm.~\ref{DeterministicUniquenessTheorem} on $\mathbf{A}$ and the $\mathbf{x}_i$.
+One simply checks that the matrix and codes satisfy the respective assumptions of Thm.~\ref{DeterministicUniquenessTheorem} on $\mathbf{A}$ and the $\mathbf{x}_i$.
 %Another practical implication of Thm.\ref{DeterministicUniquenessTheorem} is the following: there is an effective procedure sufficient to affirm if a proposed solution $(\mathbf{B}, \mathbf{\bar x}_1, \ldots, \mathbf{x}_N)$ to Prob.~\ref{InverseProblem} is indeed unique (up to noise and inherent ambiguities).
@@
 %(since $\{ \mathbf{A}_1, \mathbf{A}_3, \mathbf{A}_5, \mathbf{A}_6\}$ is not a linearly independent set).
-This weakening allows for a practical (polynomial) amount of data to still guarantee a stable dictionary in the case where the set of sparse supports for the $\mathbf{\bar x}_i$ is known to have a size that grows polynomially in $m, k$.
+This weakening allows for a practical (polynomial) amount of data to still guarantee a stable dictionary in the case where the set of sparse supports for the $\mathbf{\bar x}_i$ is known to have a size that grows polynomially in $m$ and $k$.
 
 There are other less direct consequences of Thm.~\ref{DeterministicUniquenessTheorem}.
-For instance, we use it to prove uniqueness for the optimization formulation of dictionary learning, Prob.~\ref{SLCopt}, the main object of interest for those applying dictionary learning to their data.
+For instance, we use it to prove uniqueness for the optimization formulation of sparse linear coding, Prob.~\ref{SLCopt}, the main object of interest for those applying dictionary learning to their data.
 
@@
 Let $\mathbf{A}$  be the $n \times m$ matrix of $nm$ indeterminates $A_{ij}$.
-When real numbers are substituted for $A_{ij}$, the resulting matrix satisfies \eqref{SparkCondition} if and only if the following polynomial is nonzero:
+When real numbers are substituted for $A_{ij}$, the resulting matrix satisfies condition \eqref{SparkCondition} if and only if the following polynomial is nonzero:
 \begin{align*}
@@
 
-Since $f$ is analytic, having a single substitution of a real matrix $\mathbf{A}$ with $f(\mathbf{A}) \neq 0$ necessarily implies that the zeroes of $f$ form a set of measure zero.
+Since $f$ is analytic, having a single substitution of a real matrix $\mathbf{A}$ with $f(\mathbf{A}) \neq 0$ necessarily implies that the zeroes of $f$ form a set of (Borel) measure zero.
 Fortunately, such a matrix $\mathbf{A}$ is easily constructed by adding rows of zeroes to any $\min(2k,m) \times m$ Vandermonde matrix as described above (so that each term in the product above for $f$ is nonzero).
@@
 \begin{proposition}
-Sparse neural population activity is recoverable from random (linear) noisy compression by any method that solves Prob.~\ref{DeterministicUniquenessTheorem} or \ref{SLCopt}; in particular, via biophysically plausible unsupervised sparse coding (e.g.
+Sparse neural population activity is recoverable from noisy random linear compression by any method that solves Prob.~\ref{DeterministicUniquenessTheorem} or \ref{SLCopt}; in particular, via biophysically plausible unsupervised sparse linear coding (e.g.
 \cite{rehnsommer2007, rozell2007neurally}).
@@
 
-The heart of the matter is therefore \eqref{Cstable}, which we now establish, first in the important special case $k = 1$
+The heart of the matter is therefore \eqref{Cstable}, which we now establish, first in the important special case of $k = 1$.
 
@@
 %Furthermore, they justify the hypothesis of \cite{Isely10} that sparse codes passed through information bottlenecks in the brain are recovered from random projections via (unsupervised) biologically plausible sparse coding (e.g., \cite{rehnsommer2007, rozell2007neurally, ganguli2012compressed, hu2014hebbian}).
-Deep learning noise issues: \cite{goodfellow2014explaining}.
+Deep learning noise issues: \cite{goodfellow2014explaining} and neuroscience theory \cite{ganguli2012compressed}.
 
@@
 \begin{align*}
-g(\mathbf{A}, \{\mathbf{x}_i\}_{i=1}^N) := \prod_{S \in {[N] \choose k}} \sum_{S' \in {[n] \choose k}} (\det \textbf{M}_{S',S})^2,
+g(\mathbf{A}, \{\mathbf{x}_i\}_{i=1}^N) := \prod_{S \in {[N] \choose 2k}} \sum_{S' \in {[n] \choose 2k}} (\det \textbf{M}_{S',S})^2,
 \end{align*}

### 2017-08-16 manuscripts/PNAS/review/point_by_point_response.txt
[] to () in pnt by pnt refs

--- 2017-08-15 manuscripts/PNAS/review/point_by_point_response.txt
@@
 
-(IHS10) Isely, Hillar, Sommer, Advances in neural information processing systems, 2010.
+(IHS10) Isely, Hillar, Sommer, Advances in neural information processing systems (NIPS), 2010.
 (GS12) Ganguli, Sompolinksi, Annual review of neuroscience, 2012.
@@
 -----------------
-Since the result is an extension of the noise-free result of (HS15) to a noisy case, the authors should provide betzer justification for the significance of contributions.
+Since the result is an extension of the noise-free result of (HS15) to a noisy case, the authors should provide better justification for the significance of contributions.
 The main result seems to be based on an approach similar to (HS15), and there is little to no discussion of the computability and tightness of the sufficient condition for stability in the main results.
@@
 Rather, it need only be injective on the union of subspaces with supports that form sets in a hypergraph satisfying the singleton intersection property (SIP).
-(For example, consider the matrix A = [e_1,..., e_5, v] where v = e_1 + e_3 + e_5.
+(For example, consider the matrix A = [e_1, …, e_5, v] where v = e_1 + e_3 + e_5.
 and take H to be the set of all consecutive pairs of [m] arranged in cyclic order.
@@
 
-RESPONSE: We appreciate this question but, since in all comparable cases the sample complexities improve in this work, we feel that an explicit comparison would not be the best use of our limited space; although we are willing to do so if necessary.
+RESPONSE: In brief, since all of the theorems and corollaries in (HS15) are corollaries of our theorems, all sample complexities improve by our work.
+The main point of difference between our statements about sample complexity and those of (HS15) is the assumed constraint on the underlying support set of sparse codes x_i.
+Our theory of combinatorial designs (the ‘singleton intersection property’) requires only that there be a sufficient number of x_i drawn from each support in a hypergraph satisfying the SIP, whereas the theory in (HS15) requires that a sufficient number of x_i be drawn from *every* support of size k in [m].
+Here, we make an explicit comparison with Table I in (HS15) row by row, assuming for our results that sufficient data have been sampled from all supports in a hypergraph H satisfying the SIP:
+
+ROW I.
+Our result here is |H|(k-1){m \choose k} + 1.
+We improve on the result in (HS15) by an exponential factor since our theory does not require that data be sampled with every possible support of size k in [m]; as noted in our manuscript, for every k < m there exists a hypergraph H with |H| = m that satisfies the SIP.
+
+ROW 2.
+Our result here is again |H|(k-1){m \choose k} + 1 with *certainty*, not with *almost certainty* (i.e.
+probability 1) as in (HS15).
+Here the authors in (HS15) have applied probabilistic arguments to achieve an almost certain result with a sample complexity on the same order as that for which we have achieved a certain result by means of our theory of combinatorial designs.
+
+ROW 3.
+We cannot make a direct comparison here because we have not calculated the probability that a random set of supports satisfy the SIP (see our response to a similar question by the second reviewer).
+We think this is an interesting problem for the community to solve; regardless, the result of (HS15) here is implied by our more general theory.
+
+ROW 4.
+Our result here is |H|(k-1){m \choose k} + 1 with probability 1.
+Here is the only case where the sample complexity stated in (HS15) is technically better than ours, but it differs in flavor: their x_i are assumed to be distributed as (k+1) samples per support for every support of size k in [m], whereas ours supposes that (k-1){m \choose k} codes x_i are distributed over each support in some hypergraph H satisfying the SIP.
+Regardless, the (technically) lower result of (HS15) is still implied by our more general theory in the case \varepsilon = 0 with the addition of their probabilistic argument.
+
+ROW 5: Again, we cannot make a direct comparison here for the reason stated in ROW 3.
+
+While we appreciate this question, we feel that since our results improve in every case except for one noise-free technicality (ROW 4), and since the results of (HS15) are all entailed anyway by our more general theory, an explicit comparison such as that which we provided above would not be the best use of our limited space in the manuscript; although we are willing to add a discussion about this if necessary.
 Many thanks for your careful review of the mathematics.

### 2017-08-16 manuscripts/PNAS/chazthm_pnas.tex
prop1

@@
 
-\begin{proposition}
+\begin{proposition}\label{neuroprop}
 Sparse neural population activity is recoverable from noisy random linear compression by any method that solves Prob.~\ref{DeterministicUniquenessTheorem} or \ref{SLCopt}; in particular, via biophysically plausible unsupervised sparse linear coding (e.g.
-\cite{rehnsommer2007, rozell2007neurally}).
+\cite{rehnsommer2007, rozell2007neurally, ganguli2012compressed}).
 \end{proposition}

### 2017-08-16 manuscripts/PNAS/chazthm_pnas.tex
chaz

--- 2017-08-16 manuscripts/PNAS/chazthm_pnas.tex
@@
 % A significant implication is that the constant $C_1$ of Thm.~\ref{DeterministicUniquenessTheorem} can be computed efficiently if we restrict the class of possible supports for the $\mathbf{\bar x}_i$.
+In the last several decades, from JPEG's dominance in image compression to the discovery of intrinsic "Gabor" wavelets in natural images to the detection of forgeries to artificial "cat detecting neurons" in machine intelligence, sparse linear coding has become a standard tool in signal analysis, allowing for the unsupervised discovery of myriad insights about natural signals.
+A compelling feature of the model is its simple instantiation of the principle of Occam's razor.
+For instance, a natural video can be modeled, quite accurately, as a linear combination of a small number of spatiotemporal "basis functions", each representing an archetypical feature latent in the data.
+In the field of theoretical neuroscience in particular, dictionary learning for sparse coding and related methods have recovered characteristic components of natural images \cite{Olshausen96, hurri1996image, bell1997independent, van1998independent} and sounds \cite{bellsejnowski1996, smithlewicki2006, Carlson12} that reproduce response properties of certain cortical neurons.
+The main motivation for this work was to understand how such seemingly universal representations emerge from sparse coding models fit to natural signals.
 
-In this note, we prove the stability of unique solutions to Probs.~\ref{InverseProblem} and \ref{OptimizationProblem} while significantly reducing the known sample complexity.
-Our results justify the application of the sparse linear coding model to blind source separation problems, wherein the goal is to infer the generating dictionary and sparse codes from noisy measurements, as in \eqref{LinearModel}.
-We also collect a set of useful mathematical tools and basic facts for future research.
-The main motivation for this work, however, was to understand how seemingly universal representations emerge from various sparse coding models fit to natural data.
-
-What we have shown here is that the sparse linear coding model generally produces a \textit{well-posed} inverse problem to be approximately solved by a numerical algorithm.
-This early concept of Hadamard \cite{Hadamard1902} can be paraphrased as the idea that inferences from observations should be robust to the inevitable uncertainty in measurement.
+We have proven the uniqueness and stability of solutions to Probs.~\ref{InverseProblem} and \ref{OptimizationProblem}, conclusively demonstrating that this parsimonious model of (noisy) natural data is well-posed in the sense of Hadamard \cite{Hadamard1902}, a long-standing necessary property of reductionist models in science.
+This early concept can be paraphrased as the idea that inferences from observations should be robust to the inevitable uncertainty in measurement.
 In other words, a small perturbation of the data should result in only slightly different inferred parameters.
@@
 Moreover, we show that even if the meta-parameter for the number of dictionary elements is overestimated, a subset of parameters may still be identifiable up to noise.
-We remark that our constants have been derived for deterministic ``worst-case'' noise, whereas the ``effective'' noise might be smaller when sampled from a distribution.
+%This work justifies the application of the sparse linear coding model to blind source separation problems, wherein the goal is to infer the generating dictionary and sparse codes from noisy measurements, as in \eqref{LinearModel}.
+We also collect a set of useful mathematical tools and basic facts for future research.
 
@@
 Fully understanding those combinatorial designs allowing for stable sparse representations is an interesting research area for the future.
-For instance, whether there is a sample size $N$ that is polynomial in $m,k$ gauranteeing the conclusions of Thm.~\ref{DeterministicUniquenessTheorem} has implications for the computational complexity of Probs.~\ref{InverseProblem} and \ref{OptimizationProblem} and related questions \cite{Tillmann15}.
-A reexamination of the pigeonholing argument in the proof of Thm.~\ref{DeterministicUniquenessTheorem} demonstrates that this can in fact be achieved if one restricts the supports of the $\mathbf{\bar x}_i$ to a class that grows polynomially in $m, k$.
+%For instance, whether there is a sample size $N$ that is polynomial in $m,k$ gauranteeing the conclusions of Thm.~\ref{DeterministicUniquenessTheorem} has implications for the computational complexity of Probs.~\ref{InverseProblem} and \ref{OptimizationProblem} and related questions \cite{Tillmann15}.
+A reexamination of the pigeonholing argument in the proof of Thm.~\ref{DeterministicUniquenessTheorem} demonstrates that this result enables a practical amount of data to determine the model if one restricts the supports of the $\mathbf{\bar x}_i$ to a class that grows polynomially in $m, k$.
 
@@
 
-In the field of theoretical neuroscience in particular, dictionary learning for sparse coding and related methods have recovered characteristic components of natural images \cite{Olshausen96, hurri1996image, bell1997independent, van1998independent} and sounds \cite{bellsejnowski1996, smithlewicki2006, Carlson12} that some of the reproduce response properties of cortical neurons.
+We remark that our constants have been derived for deterministic ``worst-case'' noise, whereas the ``effective'' noise might be smaller when sampled from a distribution.
+
  Our results suggest that this correspondence could be due to the ``universality'' of sparse representations in natural data, an early idea in neural theory \cite{pitts1947}.
@@
 Deep learning noise issues: \cite{goodfellow2014explaining} and neuroscience theory \cite{ganguli2012compressed}.
+
+Sparse coding also forms the theoretical basis of one of the few hypothesized methods of bottleneck communication between sparsely active neural populations.
 

### 2017-08-17 manuscripts/PNAS/chazthm_pnas.tex
discussion

--- 2017-08-16 manuscripts/PNAS/chazthm_pnas.tex
@@
 % A significant implication is that the constant $C_1$ of Thm.~\ref{DeterministicUniquenessTheorem} can be computed efficiently if we restrict the class of possible supports for the $\mathbf{\bar x}_i$.
+In the last several decades, from JPEG's dominance in image compression to the discovery of intrinsic ``Gabor'' wavelets in natural images \cite{donoho2001can} to the detection of forgeries \cite{hughes2010, Olshausen10} to artificial ``cat detecting neurons'' in machine intelligence, sparse linear coding has become a standard tool in signal analysis, allowing for the unsupervised discovery of myriad insights into natural signals.
+%A compelling feature of this model is its simple instantiation of the principle of Occam's razor: a natural video, for instance, is modeled as a linear combination of a small number of spatiotemporal building blocks, each representing an archetypical feature latent in the data.
+In the field of theoretical neuroscience in particular, dictionary learning for sparse linear coding and related methods have recovered characteristic components of natural images \cite{Olshausen96, hurri1996image, bell1997independent, van1998independent} and sounds \cite{bellsejnowski1996, smithlewicki2006, Carlson12} that reproduce some response properties of certain cortical neurons.
+The motivation for our work here was to understand when such universal representations can be expected to emerge from the sparse linear coding model.
 
-In this note, we prove the stability of unique solutions to Probs.~\ref{InverseProblem} and \ref{OptimizationProblem} while significantly reducing the known sample complexity.
-Our results justify the application of the sparse linear coding model to blind source separation problems, wherein the goal is to infer the generating dictionary and sparse codes from noisy measurements, as in \eqref{LinearModel}.
+%We have demonstrated the uniqueness and stability of solutions to Prob. \ref{InverseProblem} and the related Prob. \ref{OptimizationProblem}, 
+To this end, we have conclusively verified that inference in this parsimonious model of (noisy) natural data is a well-posed problem in the sense of Hadamard \cite{Hadamard1902}, a long-standing necessary property of reductionist models in science.
+This notion summarizes the idea that inferences from observations should be robust to the inevitable uncertainty in measurement.
+In this regard, we demonstrate rigorously that, given sufficient data and suitable dictionary, Prob.~\ref{OptimizationProblem} reduces to an instance of Prob.~\ref{InverseProblem} to which applies our main result (Thm.~\ref{DeterministicUniquenessTheorem}): every dictionary and sparse codes solving Prob.~\ref{InverseProblem} are equivalent up to inherent relabeling/scaling ambiguities and a discrepancy (error) that scales linearly with the measurement noise or modeling inaccuracy; and we provide explicit constants expressed in terms of these latent parameters.
+%In other words, a small perturbation of the data should result in only slightly different inferred parameters. 
+%Moreover, we show that even if the meta-parameter for the number of dictionary elements is overestimated, a subset of parameters may still be identifiable up to noise. 
+%This work justifies the application of the sparse linear coding model to blind source separation problems, wherein the goal is to infer the generating dictionary and sparse codes from noisy measurements, as in \eqref{LinearModel}.
 We also collect a set of useful mathematical tools and basic facts for future research.
-The main motivation for this work, however, was to understand how seemingly universal representations emerge from various sparse coding models fit to natural data.
 
-What we have shown here is that the sparse linear coding model generally produces a \textit{well-posed} inverse problem to be approximately solved by a numerical algorithm.
-This early concept of Hadamard \cite{Hadamard1902} can be paraphrased as the idea that inferences from observations should be robust to the inevitable uncertainty in measurement.
-In other words, a small perturbation of the data should result in only slightly different inferred parameters.
-In this regard, for the sparse linear coding model we demonstrate a linear relationship, \eqref{epsdel}, between measurement noise and the deviation of any solution from the true parameters, with explicit constants expressed in terms of these parameters.
-Moreover, we show that even if the meta-parameter for the number of dictionary elements is overestimated, a subset of parameters may still be identifiable up to noise.
-We remark that our constants have been derived for deterministic ``worst-case'' noise, whereas the ``effective'' noise might be smaller when sampled from a distribution.
+An immediate application of our theoretical work is Prop.~\ref{neuroprop}, which certifies the validity of perhaps the only published theory of neurally-plausible bottleneck communication between brain regions -- that unsupervised feature (dictionary) learning in a significantly smaller space of nervous activity can recover noisy sparse codes sent through a randomly-constructed (but unknown) wiring bottleneck \cite{Isely10}.
+We refer the reader to \cite{ganguli2012compressed} for a discussion of this application's significance and more on the interactions between sparse linear coding and neuroscience.
 
-One notable component of our contribution is a combinatorial criteria (regular hypergraphs satisfying the singleton intersection property, Def.~\ref{sip}) for the support sets of sparse codes key to the identification of the dictionary.
-Fully understanding those combinatorial designs allowing for stable sparse representations is an interesting research area for the future.
-For instance, whether there is a sample size $N$ that is polynomial in $m,k$ gauranteeing the conclusions of Thm.~\ref{DeterministicUniquenessTheorem} has implications for the computational complexity of Probs.~\ref{InverseProblem} and \ref{OptimizationProblem} and related questions \cite{Tillmann15}.
-A reexamination of the pigeonholing argument in the proof of Thm.~\ref{DeterministicUniquenessTheorem} demonstrates that this can in fact be achieved if one restricts the supports of the $\mathbf{\bar x}_i$ to a class that grows polynomially in $m, k$.
+One of the major innovations in our work is a theory of combinatorial designs for support sets (the ``singleton intersection property'') that provides a handle on the complexities of intersecting subspaces in dictionary learning problems.
+We incorporate this idea into a new fundamental lemma in combinatorial matrix theory (Lem.~\ref{MainLemma}) that will be useful in any noisy setting where uniqueness up to feature relabelling/scaling is desirable, and which draws upon the definition of a new matrix lower bound induced by a given hypergraph.
+Our novel combined combinatorial and analytical proof allows for the following new theoretical advances over previous works (e.g.
+\cite{Hillar15}) beyond an extension to the noisy case: 1) the number of dictionary elements can be unknown; 2) data require a polynomial, not exponential, number of distinct sparse supports and in certain settings a practical (polynomial) number of samples in total is sufficient; and 3) the spark condition is not necessary for recovery of the dictionary.
 
@@
 In these cases, assurances such as those offered by our theorems certify that different devices (with different initialization, samples, etc.) will learn equivalent representations given enough data from statistically identical systems.
+To contrast with the current hot topic of ``Deep Learning'', there are few such uniqueness guarantees for these multi-layer feedforward models of data.
+Moreover, it is now well-known in the community that even minuscule amounts of (``adversarial'') signal noise can dramatically alter their output \cite{goodfellow2014explaining}.
+In particular, it appears that a main reason for the sustained interest in unsupervised (sparse) dictionary learning for data analysis has been the assumed well-posedness of the model, confirmation of which forms the core of our  findings.
 
-In the field of theoretical neuroscience in particular, dictionary learning for sparse coding and related methods have recovered characteristic components of natural images \cite{Olshausen96, hurri1996image, bell1997independent, van1998independent} and sounds \cite{bellsejnowski1996, smithlewicki2006, Carlson12} that some of the reproduce response properties of cortical neurons.
-Our results suggest that this correspondence could be due to the ``universality'' of sparse representations in natural data, an early idea in neural theory \cite{pitts1947}.
-%Furthermore, they justify the hypothesis of \cite{Isely10} that sparse codes passed through information bottlenecks in the brain are recovered from random projections via (unsupervised) biologically plausible sparse coding (e.g., \cite{rehnsommer2007, rozell2007neurally, ganguli2012compressed, hu2014hebbian}).
-Deep learning noise issues: \cite{goodfellow2014explaining} and neuroscience theory \cite{ganguli2012compressed}.
+ [*** TODO: PUT in paper sprinkled TIGHTNESS and COMPUTABILITY ***]
+
+%We make a final remark about the tightness of our results and the computability of our derived constants.
+%We remark that our constants have been derived for deterministic ``worst-case'' noise, whereas the ``effective'' noise might be smaller when sampled from a distribution.
+
+%Our results suggest that this correspondence could be due to the ``universality'' of sparse representations in natural data, an early idea in neural theory \cite{pitts1947}.
+
+%A reexamination of the pigeonholing argument in the proof of Thm.~\ref{DeterministicUniquenessTheorem} demonstrates that this result enables a practical amount of data to determine the model if one restricts the supports of the $\mathbf{\bar x}_i$ to a class that grows polynomially in $m, k$.
 

### 2017-08-17 manuscripts/PNAS/chazthm_pnas.tex
chaz

@@
 
+Before moving on to our proofs, we discuss briefly the computability and tightness of our results. [* DO THIS *]
 %\pagebreak
@@
 
+[* PUT COMPUTABILITY IN HERE *]
+
 \begin{proof}[Proof of Thm.~\ref{DeterministicUniquenessCorollary} for $k < m$] 
@@
 \end{proof}
+
+We remark that if $k$ is held fixed, or if the size of the support set of reconstructing codes is known to be polynomial in $m$ and $k$, then a practical (polynomial) amount of data is enough to determine the model.\footnote{In the latter case, the pigeonholing argument in the proof of Thm.~\ref{DeterministicUniquenessTheorem} requires only a polynomial number of samples distributed over a polynomial number of supports.}
 
@@
 This notion summarizes the idea that inferences from observations should be robust to the inevitable uncertainty in measurement.
-In this regard, we demonstrate rigorously that, given sufficient data and suitable dictionary, Prob.~\ref{OptimizationProblem} reduces to an instance of Prob.~\ref{InverseProblem} to which applies our main result (Thm.~\ref{DeterministicUniquenessTheorem}): every dictionary and sparse codes solving Prob.~\ref{InverseProblem} are equivalent up to inherent relabeling/scaling ambiguities and a discrepancy (error) that scales linearly with the measurement noise or modeling inaccuracy; and we provide explicit constants expressed in terms of these latent parameters.
+In this regard, we demonstrate rigorously that, given sufficient data and suitable dictionary, Prob.~\ref{OptimizationProblem} reduces to an instance of Prob.~\ref{InverseProblem} to which applies our main result (Thm.~\ref{DeterministicUniquenessTheorem}): every dictionary and sparse codes solving Prob.~\ref{InverseProblem} are equivalent up to inherent relabeling/scaling ambiguities and a discrepancy (error) that scales linearly with the measurement noise or modeling inaccuracy; and we provide explicit, computable constants expressed in terms of these latent parameters.
 %In other words, a small perturbation of the data should result in only slightly different inferred parameters. 
@@
 In particular, it appears that a main reason for the sustained interest in unsupervised (sparse) dictionary learning for data analysis has been the assumed well-posedness of the model, confirmation of which forms the core of our  findings.
-
- [*** TODO: PUT in paper sprinkled TIGHTNESS and COMPUTABILITY ***]
 

### 2017-08-17 manuscripts/PNAS/chazthm_pnas.tex
chaz

@@
 Before moving on to our proofs, we discuss briefly the computability and tightness of our results. [* DO THIS *]
+
+We remark that if $k$ is held fixed, or if the size of the support set of reconstructing codes is known to be polynomial in $\bar m$ and $k$, then a practical (polynomial) amount of data is enough to determine the model.\footnote{In the latter case, a re-examination of the pigeonholing argument in the proof of Thm.~\ref{DeterministicUniquenessTheorem} shows that only a polynomial number of samples distributed over a polynomial number of supports.}
 %\pagebreak
@@
 \end{proof}
-
-We remark that if $k$ is held fixed, or if the size of the support set of reconstructing codes is known to be polynomial in $m$ and $k$, then a practical (polynomial) amount of data is enough to determine the model.\footnote{In the latter case, the pigeonholing argument in the proof of Thm.~\ref{DeterministicUniquenessTheorem} requires only a polynomial number of samples distributed over a polynomial number of supports.}
 

### 2017-08-17 manuscripts/PNAS/review/point_by_point_response.txt
chaz

@@
-TODO:
-
 References for Cover Letter and Point-by-point Response:
@@
 The main constants in our work -- C_1, C_2 -- are computable, elementarily, in terms of two positive quantities that are natural in our context: (a) the "Lower Bound" L_H(A) of a matrix A given a hypergraph H (the support sets of sparse x's generating the data — see *NOTE* below this paragraph), which is a measure of how distinguishable two x’s with supports in H are by their images under A, and (b) the value in Def.
-4 of r(V_1,...,V_l) given subspaces V_i spanned by columns of A, which bounds the distance between intersections of such subspaces and each subspace individually.
+4 of \xi(V_1,…,V_l) given subspaces V_i spanned by columns of A, which bounds the distance between intersections of such subspaces and each subspace individually.
 The first quantity (a) is, in some form or another, related to standard objects in the field and may be computed as the smallest singular value of a set of specific sub-matrices; in particular, for fixed sparsity constraint k on H, the lower bound L_H(A) is efficiently computable (polynomial time).
@@
 The calculation of (b) involves determining "canonical angles" between subspaces, which is usually reduced again to a numerical (efficient) singular value decomposition given the fixed subspaces.
-However, upon close inspection, C_2 nonetheless requires an exponential number of instances of computing r.
-Thus, while our constants are effective (an algorithm exists to compute them), they are not necessarily polynomially-time computable.
+However, upon close inspection, C_2 nonetheless requires an exponential number of instances of computing \xi.
+Thus, while our constants are effective (an algorithm exists to compute them), they are not necessarily polynomial-time computable.
 

### 2017-08-17 manuscripts/PNAS/chazthm_pnas.tex
chaz

--- 2017-08-17 manuscripts/PNAS/chazthm_pnas.tex
@@
 
-Before moving on to our proofs, we discuss briefly the computability and tightness of our results. [* DO THIS *]
-%\pagebreak
+Before moving on to proofs, we discuss briefly the tightness of our results for quantities: (a) the required coding error $\varepsilon(\delta_1, \delta_2)$ sufficient to guarantee uniqueness in terms of desired dictionary and sparse representation errors $\delta_1, \delta_2$, and (b) the number of required samples, $N$.
+With respect to (a), even with fixed dictionary, the recovery of sparse representations up to an error that is linear in the noise is classically optimal (up to constants).
+%Thus, having both sufficient error in coding for uniqueness being linear in terms of both the desired dictionary and sparse vector recovery error is optimal.
+We regard (b) as a basic open problem: how many samples determine the sparse linear coding model?
+If $k$ is held fixed or if the size of the support set of reconstructing codes is known to be polynomial in $\bar m$ and $k$, then a practical (polynomial) amount of data is enough to determine the model.\footnote{In the latter case, a reexamination of the pigeonholing argument in the proof of Thm.~\ref{DeterministicUniquenessTheorem} shows that only a polynomial number of samples distributed over a polynomial number of supports suffices.} Reasons to be skeptical that a polynomial amount suffice in general, however, can be found in \cite{tillmann2014computational, tillmann2015computational}.
 
@@
 \begin{definition}\label{SpecialSupportSet}\label{FriedrichsDefinition}
-For subspaces $V_1, \ldots, V_\ell \subseteq \mathbb{R}^m$, set $r := 1$ when $\ell = 1$ and define for $\ell \geq 2$:
+For subspaces $V_1, \ldots, V_\ell \subseteq \mathbb{R}^m$, set $\xi := 1$ when $\ell = 1$ and define for $\ell \geq 2$:
 \begin{align*}
@@
 \end{definition}
-Note that $\theta \in (0,\frac{\pi}{2}]$ implies $0 < r \leq 1$.\footnote{We acknowledge the counter-intuitive property that $\theta =  \pi/2$ when $U = V$ or $U \perp V$.}  
+Note that $\theta \in (0,\frac{\pi}{2}]$ implies $0 < \xi \leq 1$.\footnote{We acknowledge the counter-intuitive property that $\theta =  \pi/2$ when $U = V$ or $U \perp V$.}  
 The constant $C_2$ in Lem.~\ref{MainLemma} can then be expressed as:  
@@
 
-[* PUT COMPUTABILITY IN HERE *]
+Note that the explicit constants $C_1$ and $C_2$ are effectively computable.
+(The quantity $L_k$, may be computed as the smallest singular value of a certain matrix, while the quantity $\xi$ involves computing ``canonical angles'' between subspaces, which reduce again to an efficient singular value decomposition.) Because deciding $L_{k}(\mathbf{A}) > 0$ is already NP-hard \cite{tillmann2014computational}, it seems likely that without fixing a sparsity level there is no efficient computation $L_k$ in general; for fixed sparsity $k$, however, it is computable in polynomial time.
+Regardless, to calculate $C_2$ nonetheless requires an exponential number of queries to $\xi$.
+Thus, $C_1$ and $C_2$ are not necessarily polynomial-time computable.
 
@@
 
-We remark that if $k$ is held fixed, or if the size of the support set of reconstructing codes is known to be polynomial in $m$ and $k$, then a practical (polynomial) amount of data is enough to determine the model.\footnote{In the latter case, the pigeonholing argument in the proof of Thm.~\ref{DeterministicUniquenessTheorem} requires only a polynomial number of samples distributed over a polynomial number of supports.}
-
 \begin{proof}[Proof of Thm.~\ref{SLCopt}]
@@
 % A significant implication is that the constant $C_1$ of Thm.~\ref{DeterministicUniquenessTheorem} can be computed efficiently if we restrict the class of possible supports for the $\mathbf{\bar x}_i$.
-In the last several decades, from JPEG's dominance in image compression to the discovery of intrinsic ``Gabor'' wavelets in natural images \cite{donoho2001can} to the detection of forgeries \cite{hughes2010, Olshausen10} to artificial ``cat detecting neurons'' in machine intelligence, sparse linear coding has become a standard tool in signal analysis, allowing for the unsupervised discovery of myriad insights into natural signals.
+Over the last twenty years, from the discovery of intrinsic ``Gabor'' wavelets in natural images \cite{donoho2001can} to the detection of forgeries \cite{hughes2010, Olshausen10}, 
+sparse linear coding has become a standard tool in signal analysis, allowing for the unsupervised discovery of myriad insights into natural signals in a variety of scientific fields. 
 %A compelling feature of this model is its simple instantiation of the principle of Occam's razor: a natural video, for instance, is modeled as a linear combination of a small number of spatiotemporal building blocks, each representing an archetypical feature latent in the data.
-In the field of theoretical neuroscience in particular, dictionary learning for sparse linear coding and related methods have recovered characteristic components of natural images \cite{Olshausen96, hurri1996image, bell1997independent, van1998independent} and sounds \cite{bellsejnowski1996, smithlewicki2006, Carlson12} that reproduce some response properties of certain cortical neurons.
-The motivation for our work here was to understand when such universal representations can be expected to emerge from the sparse linear coding model.
+For theoretical neuroscience in particular, dictionary learning for sparse linear coding and related methods have recovered characteristic components of natural images \cite{Olshausen96, hurri1996image, bell1997independent, van1998independent} and sounds \cite{bellsejnowski1996, smithlewicki2006} that reproduce response properties of certain cortical neurons.
+In this work, we sought to understand when such universal representations be expected to emerge from the sparse linear coding model.
+%to the recovery of ``mouse neuronal activity representing location on a track \cite{agarwal2014spatially}
 
@@
 
-One of the major innovations in our work is a theory of combinatorial designs for support sets (the ``singleton intersection property'') that provides a handle on the complexities of intersecting subspaces in dictionary learning problems.
+One of the major innovations in our work is a theory of combinatorial designs for support sets (the ``singleton intersection property'') key to the identification of the dictionary.
 We incorporate this idea into a new fundamental lemma in combinatorial matrix theory (Lem.~\ref{MainLemma}) that will be useful in any noisy setting where uniqueness up to feature relabelling/scaling is desirable, and which draws upon the definition of a new matrix lower bound induced by a given hypergraph.
-Our novel combined combinatorial and analytical proof allows for the following new theoretical advances over previous works (e.g.
-\cite{Hillar15}) beyond an extension to the noisy case: 1) the number of dictionary elements can be unknown; 2) data require a polynomial, not exponential, number of distinct sparse supports and in certain settings a practical (polynomial) number of samples in total is sufficient; and 3) the spark condition is not necessary for recovery of the dictionary.
+Our arguments allow for the following theoretical advances: the dictionary size can be unknown; data require a polynomial, not exponential, number of distinct sparse supports and in certain settings a polynomial number of samples in total is sufficient; and the spark condition is not necessary for dictionary recovery.
 
@@
 In these cases, assurances such as those offered by our theorems certify that different devices (with different initialization, samples, etc.) will learn equivalent representations given enough data from statistically identical systems.
+
 To contrast with the current hot topic of ``Deep Learning'', there are few such uniqueness guarantees for these multi-layer feedforward models of data.
-Moreover, it is now well-known in the community that even minuscule amounts of (``adversarial'') signal noise can dramatically alter their output \cite{goodfellow2014explaining}.
-In particular, it appears that a main reason for the sustained interest in unsupervised (sparse) dictionary learning for data analysis has been the assumed well-posedness of the model, confirmation of which forms the core of our  findings.
+Moreover, there is evidence that even minuscule amounts of (``adversarial'') signal noise can dramatically alter their output \cite{goodfellow2014explaining}.
+In particular, a main reason for the sustained interest in dictionary learning for data analysis appears to be the assumed well-posedness of the model, confirmation of which forms the core of our  findings.
 

### 2017-08-17 manuscripts/PNAS/chazthm_pnas.tex
chaz

@@
 
-Before moving on to proofs, we discuss briefly the tightness of our results for quantities: (a) the required coding error $\varepsilon(\delta_1, \delta_2)$ sufficient to guarantee uniqueness in terms of desired dictionary and sparse representation errors $\delta_1, \delta_2$, and (b) the number of required samples, $N$.
-With respect to (a), even with fixed dictionary, the recovery of sparse representations up to an error that is linear in the noise is classically optimal (up to constants).
-%Thus, having both sufficient error in coding for uniqueness being linear in terms of both the desired dictionary and sparse vector recovery error is optimal.
-We regard (b) as a basic open problem: how many samples determine the sparse linear coding model?
+Before moving on to proofs, we discuss briefly the tightness of our number of required samples, $N$.
+We regard this as a basic open problem: how many samples determine the sparse linear coding model?
 If $k$ is held fixed or if the size of the support set of reconstructing codes is known to be polynomial in $\bar m$ and $k$, then a practical (polynomial) amount of data is enough to determine the model.\footnote{In the latter case, a reexamination of the pigeonholing argument in the proof of Thm.~\ref{DeterministicUniquenessTheorem} shows that only a polynomial number of samples distributed over a polynomial number of supports suffices.} Reasons to be skeptical that a polynomial amount suffice in general, however, can be found in \cite{tillmann2014computational, tillmann2015computational}.
@@
 
-Note that the explicit constants $C_1$ and $C_2$ are effectively computable.
+We note that the explicit constants $C_1$ and $C_2$ are effectively computable.
 (The quantity $L_k$, may be computed as the smallest singular value of a certain matrix, while the quantity $\xi$ involves computing ``canonical angles'' between subspaces, which reduce again to an efficient singular value decomposition.) Because deciding $L_{k}(\mathbf{A}) > 0$ is already NP-hard \cite{tillmann2014computational}, it seems likely that without fixing a sparsity level there is no efficient computation $L_k$ in general; for fixed sparsity $k$, however, it is computable in polynomial time.
-Regardless, to calculate $C_2$ nonetheless requires an exponential number of queries to $\xi$.
+Regardless, to calculate $C_2$ requires an exponential number of queries to $\xi$.
 Thus, $C_1$ and $C_2$ are not necessarily polynomial-time computable.

### 2017-08-17 manuscripts/PNAS/chazthm_pnas.tex
discussion

@@
 
-We furthermore note that unlike the requirements of previous works \cite{li2004analysis, Georgiev05, Aharon06, Hillar15}, the matrix $\mathbf{A}$ need not satisfy the spark condition to be recoverable from data.
+We furthermore note that unlike in previous works \cite{li2004analysis, Georgiev05, Aharon06, Hillar15}, the matrix $\mathbf{A}$ need not satisfy the spark condition to be recoverable from data.
 As a simple example for $k=2$, let $\mathbf{A} = [ \mathbf{e}_1, \ldots, \mathbf{e}_5, \mathbf{v}]$ where $\mathbf{v} = \mathbf{e}_1 + \mathbf{e}_3 + \mathbf{e}_5$, and take $\mathcal{H}$ to be all consecutive pairs of $[m]$ arranged in cyclic order.
@@
 %(since $\{ \mathbf{A}_1, \mathbf{A}_3, \mathbf{A}_5, \mathbf{A}_6\}$ is not a linearly independent set).
-This weakening allows for a practical (polynomial) amount of data to still guarantee a stable dictionary in the case where the set of sparse supports for the $\mathbf{\bar x}_i$ is known to have a size that grows polynomially in $m$ and $k$.
+%This weakening allows for a practical (polynomial) amount of data to still guarantee a stable dictionary in the case where the set of sparse supports for the $\mathbf{\bar x}_i$ is known to have a size that grows polynomially in $m$ and $k$.
 
@@
 
-Before moving on to proofs, we discuss briefly the tightness of our number of required samples, $N$.
-We regard this as a basic open problem: how many samples determine the sparse linear coding model?
-If $k$ is held fixed or if the size of the support set of reconstructing codes is known to be polynomial in $\bar m$ and $k$, then a practical (polynomial) amount of data is enough to determine the model.\footnote{In the latter case, a reexamination of the pigeonholing argument in the proof of Thm.~\ref{DeterministicUniquenessTheorem} shows that only a polynomial number of samples distributed over a polynomial number of supports suffices.} Reasons to be skeptical that a polynomial amount suffice in general, however, can be found in \cite{tillmann2014computational, tillmann2015computational}.
+We close this section with a remark on sample complexity.
+A basic open problem remains: how many samples are necessary to determine the sparse linear coding model?
+If $k$ is held fixed or if the size of the support set of reconstructing codes is known to be polynomial in $\bar m$ and $k$, then a practical (polynomial) amount of data suffices.\footnote{In the latter case, a reexamination of the pigeonholing argument in the proof of Thm.~\ref{DeterministicUniquenessTheorem} requires a polynomial number of samples distributed over a polynomial number of supports.} Reasons to be skeptical that this holds in general, however, can be found in \cite{tillmann2014computational, tillmann2015computational}.
 
@@
 
-We note that the explicit constants $C_1$ and $C_2$ are effectively computable.
-(The quantity $L_k$, may be computed as the smallest singular value of a certain matrix, while the quantity $\xi$ involves computing ``canonical angles'' between subspaces, which reduce again to an efficient singular value decomposition.) Because deciding $L_{k}(\mathbf{A}) > 0$ is already NP-hard \cite{tillmann2014computational}, it seems likely that without fixing a sparsity level there is no efficient computation $L_k$ in general; for fixed sparsity $k$, however, it is computable in polynomial time.
-Regardless, to calculate $C_2$ requires an exponential number of queries to $\xi$.
-Thus, $C_1$ and $C_2$ are not necessarily polynomial-time computable.
+The pragmatic reader should note that the explicit constants $C_1$ and $C_2$ are effectively computable.
+(The quantity $L_k$, may be computed as the smallest singular value of a certain matrix, while the quantity $\xi$ involves computing ``canonical angles'' between subspaces, which reduce again to an efficient singular value decomposition.) There is no efficient computation of $L_k$ in general, however, since even $L_{k} > 0$ is NP-hard \cite{tillmann2014computational}; although fixing $k$ yields polynomial complexity.
+Calculating $C_2$, however, requires an exponential number of queries to $\xi$; thus, $C_1$ and $C_2$ are not computable in polynomial time.
 
@@
 \section{Discussion}\label{Discussion}
-%[mention dictionary size independence]
 
-% A significant implication is that the constant $C_1$ of Thm.~\ref{DeterministicUniquenessTheorem} can be computed efficiently if we restrict the class of possible supports for the $\mathbf{\bar x}_i$.
-Over the last twenty years, from the discovery of intrinsic ``Gabor'' wavelets in natural images \cite{donoho2001can} to the detection of forgeries \cite{hughes2010, Olshausen10}, 
-sparse linear coding has become a standard tool in signal analysis, allowing for the unsupervised discovery of myriad insights into natural signals in a variety of scientific fields. 
+The goal of this work was to explain the emergence of consistent characteristic representations from sparse linear coding models fit to natural data despite the varied assumptions underlying the many practical methods in current use.
+To this end, we have taken an important step toward unifying the hundreds (if not thousands) of publications on the topic by demonstrating very general, deterministic conditions under which the identification of parameters in this parsimonious model is not only possible but also robust to the inevitable uncertainty permeating measurement and model choice.
+
+Specifically, we have shown that, given sufficient data and suitable dictionary, the problem of seeking a dictionary and sparse codes with minimal average support size over the data (Prob.~\ref{OptimizationProblem}) reduces to an instance of Prob.~\ref{InverseProblem}, to which our main result (Thm.~\ref{DeterministicUniquenessTheorem}) applies: every dictionary and sparse codes solving Prob.~\ref{InverseProblem} are equivalent up to inherent relabeling/scaling ambiguities and a discrepancy (error) that scales linearly with the measurement noise or modeling inaccuracy.
+The constants we provide are explicit and computable; hence, there is an effective procedure sufficient to affirm if a proposed solution to Probs.~\ref{DeterministicUniquenessTheorem} or \ref{OptimizationProblem} is indeed unique (up to noise and inherent ambiguities).
+
+An immediate application of our theoretical work is Prop.~\ref{neuroprop}, which certifies the validity of perhaps the only published theory to date of neurally-plausible bottleneck communication in the brain: that sparse coding via dictionary learning in a compressed space of nervous activity can recover sparse codes sent through a randomly-constructed (but unknown) noisy wiring bottleneck \cite{Isely10}.\footnote{We refer the reader to \cite{ganguli2012compressed} for a discussion of this application's significance and more on the interactions between sparse linear coding and neuroscience.}
+
 %A compelling feature of this model is its simple instantiation of the principle of Occam's razor: a natural video, for instance, is modeled as a linear combination of a small number of spatiotemporal building blocks, each representing an archetypical feature latent in the data.
-For theoretical neuroscience in particular, dictionary learning for sparse linear coding and related methods have recovered characteristic components of natural images \cite{Olshausen96, hurri1996image, bell1997independent, van1998independent} and sounds \cite{bellsejnowski1996, smithlewicki2006} that reproduce response properties of certain cortical neurons.
-In this work, we sought to understand when such universal representations be expected to emerge from the sparse linear coding model.
+
+%For theoretical neuroscience in particular, dictionary learning and related methods have recovered characteristic components of natural images \cite{Olshausen96, hurri1996image, bell1997independent, van1998independent} and sounds \cite{bellsejnowski1996, smithlewicki2006} that reproduce response properties of certain cortical neurons.
+
 %to the recovery of ``mouse neuronal activity representing location on a track \cite{agarwal2014spatially}
 
-%We have demonstrated the uniqueness and stability of solutions to Prob. \ref{InverseProblem} and the related Prob. \ref{OptimizationProblem}, 
-To this end, we have conclusively verified that inference in this parsimonious model of (noisy) natural data is a well-posed problem in the sense of Hadamard \cite{Hadamard1902}, a long-standing necessary property of reductionist models in science.
-This notion summarizes the idea that inferences from observations should be robust to the inevitable uncertainty in measurement.
-In this regard, we demonstrate rigorously that, given sufficient data and suitable dictionary, Prob.~\ref{OptimizationProblem} reduces to an instance of Prob.~\ref{InverseProblem} to which applies our main result (Thm.~\ref{DeterministicUniquenessTheorem}): every dictionary and sparse codes solving Prob.~\ref{InverseProblem} are equivalent up to inherent relabeling/scaling ambiguities and a discrepancy (error) that scales linearly with the measurement noise or modeling inaccuracy; and we provide explicit, computable constants expressed in terms of these latent parameters.
-%In other words, a small perturbation of the data should result in only slightly different inferred parameters. 
 %Moreover, we show that even if the meta-parameter for the number of dictionary elements is overestimated, a subset of parameters may still be identifiable up to noise.
-%This work justifies the application of the sparse linear coding model to blind source separation problems, wherein the goal is to infer the generating dictionary and sparse codes from noisy measurements, as in \eqref{LinearModel}.
-We also collect a set of useful mathematical tools and basic facts for future research.
 
-An immediate application of our theoretical work is Prop.~\ref{neuroprop}, which certifies the validity of perhaps the only published theory of neurally-plausible bottleneck communication between brain regions -- that unsupervised feature (dictionary) learning in a significantly smaller space of nervous activity can recover noisy sparse codes sent through a randomly-constructed (but unknown) wiring bottleneck \cite{Isely10}.
-We refer the reader to \cite{ganguli2012compressed} for a discussion of this application's significance and more on the interactions between sparse linear coding and neuroscience.
+Beyond an original extension to the noisy regime, a major innovation in our work is a theory of combinatorial designs for support sets (the ``singleton intersection property'') key to the identification of the dictionary.
+We incorporate this idea into a new fundamental lemma in combinatorial matrix theory (Lem.~\ref{MainLemma}), which draws upon the definition of a new matrix lower bound induced by a hypergraph.
+Theoretical advances enabled by our combinatorial approach include: the dictionary size can be unknown and yet still a subset of parameters are recoverable; data require a polynomial, not exponential, number of distinct sparse supports and in certain settings a polynomial number of samples in total is sufficient; the dictionary need not satisfy the spark condition to be identifiable from data.
 
-One of the major innovations in our work is a theory of combinatorial designs for support sets (the ``singleton intersection property'') key to the identification of the dictionary.
-We incorporate this idea into a new fundamental lemma in combinatorial matrix theory (Lem.~\ref{MainLemma}) that will be useful in any noisy setting where uniqueness up to feature relabelling/scaling is desirable, and which draws upon the definition of a new matrix lower bound induced by a given hypergraph.
-Our arguments allow for the following theoretical advances: the dictionary size can be unknown; data require a polynomial, not exponential, number of distinct sparse supports and in certain settings a polynomial number of samples in total is sufficient; and the spark condition is not necessary for dictionary recovery.
-
-A technical difficulty in proving Thm.~\ref{DeterministicUniquenessTheorem} is the absence of any assumption on dictionaries in solutions to Prob.~\ref{InverseProblem}.
+One technical difficulty in proving Thm.~\ref{DeterministicUniquenessTheorem} is the absence of any assumption on dictionaries in solutions to Prob.~\ref{InverseProblem}.
 Although mathematically interesting that no such requirement is necessary, there are other reasons to seek out such a theoretical guarantee.
@@
 Moreover, there is evidence that even minuscule amounts of (``adversarial'') signal noise can dramatically alter their output \cite{goodfellow2014explaining}.
-In particular, a main reason for the sustained interest in dictionary learning for data analysis appears to be the assumed well-posedness of the model, confirmation of which forms the core of our  findings.
+In particular, a main reason for the sustained interest in dictionary learning as an unsupervised method for data analysis appears to be the assumed well-posedness of parameter identification in the model, confirmation of which forms the core of our  findings.
+
+%Since its inception some twenty years ago, sparse linear coding has become a standard tool in signal analysis, yielding myriad insights into the structure of natural signals across a variety of scientific domains.
+In this work,
 
@@
 %Our results suggest that this correspondence could be due to the ``universality'' of sparse representations in natural data, an early idea in neural theory \cite{pitts1947}.
-
-%A reexamination of the pigeonholing argument in the proof of Thm.~\ref{DeterministicUniquenessTheorem} demonstrates that this result enables a practical amount of data to determine the model if one restricts the supports of the $\mathbf{\bar x}_i$ to a class that grows polynomially in $m, k$.
 

### 2017-08-17 manuscripts/PNAS/chazthm_pnas.tex
6 pages!!

@@
 \end{problem}
+We then sketch the proof of a probabilistic extension of Thm.~\ref{DeterministicUniquenessTheorem} to random data and dictionaries (Thm.~\ref{robustPolythm} and Cor.~\ref{ProbabilisticCor}).
 Finally, in Sec.~\ref{Discussion}, we discuss both theoretical and practical applications of our main mathematical findings.
@@
 
-\section{Proofs of Theorems~\ref{DeterministicUniquenessTheorem} and ~\ref{SLCopt}}\label{DUT}
+\section{Proofs}\label{DUT} % of Theorems~\ref{DeterministicUniquenessTheorem} and ~\ref{SLCopt}}\label{DUT}
 
@@
 
-The pragmatic reader should note that the explicit constants $C_1$ and $C_2$ are effectively computable.
-(The quantity $L_k$, may be computed as the smallest singular value of a certain matrix, while the quantity $\xi$ involves computing ``canonical angles'' between subspaces, which reduce again to an efficient singular value decomposition.) There is no efficient computation of $L_k$ in general, however, since even $L_{k} > 0$ is NP-hard \cite{tillmann2014computational}; although fixing $k$ yields polynomial complexity.
-Calculating $C_2$, however, requires an exponential number of queries to $\xi$; thus, $C_1$ and $C_2$ are not computable in polynomial time.
+The pragmatic reader should note that the explicit constants $C_1$ and $C_2$ are effectively computable: the quantity $L_k$, may be computed as the smallest singular value of a certain matrix, while the quantity $\xi$ involves computing ``canonical angles'' between subspaces, which reduce again to an efficient singular value decomposition.
+There is no efficient computation of $L_k$ in general, however, since even $L_{k} > 0$ is NP-hard \cite{tillmann2014computational}; although fixing $k$ yields polynomial complexity.
+Moreover, calculating $C_2$ requires an exponential number of queries to $\xi$; thus, $C_1$ and $C_2$ are not computable in polynomial time.
 
@@
 
+\begin{proof}[Proof (sketch) of Thm.~\ref{robustPolythm}]
+Let $\textbf{M}$ be the matrix with columns $\mathbf{A}\mathbf{x}_i$, $i \in [N]$.  Consider the polynomial in the indeterminate entries of $\mathbf{A}$ and $\mathbf{x}_i$:
+\begin{align*}
+g(\mathbf{A}, \{\mathbf{x}_i\}_{i=1}^N) := \prod_{S \in {[N] \choose 2k}} \sum_{S' \in {[n] \choose 2k}} (\det \textbf{M}_{S',S})^2,
+\end{align*}
+with notation as in Sec.~\ref{Results}.  
+It can be checked that when $g$ is nonzero for a substitution of real numbers for the indeterminates, all of the genericity requirements on $\mathbf{A}$ and $\mathbf{x}_i$ in our proofs of stability in Thm.~\ref{DeterministicUniquenessTheorem} are satisfied (in particular, the spark condition on $\mathbf{A}$).
+\end{proof}
+
+\begin{proof}[Proof (sketch) of Cor.~\ref{ProbabilisticCor}]
+First, note that if a set of measure spaces $\{(X_{\ell}, \Sigma_{\ell}, \nu_{\ell})\}_{\ell=1}^p$ has that $\nu_{\ell}$ is absolutely continuous with respect to $\mu$ for all $\ell \in [p]$, where $\mu$ is the standard Borel measure on $\mathbb{R}$, then the product measure $\prod_{\ell=1}^p \nu_{\ell}$ is absolutely continuous with respect to the standard Borel product measure on $\mathbb{R}^p$.
+% for space:  (e.g.,  \cite{folland2013real}).
+By Thm.~\ref{robustPolythm}, there is a polynomial that is nonzero when $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$; in particular, stability holds almost surely.
+\end{proof}
+
 \section{Discussion}\label{Discussion}
 
-The goal of this work was to explain the emergence of consistent characteristic representations from sparse linear coding models fit to natural data despite the varied assumptions underlying the many practical methods in current use.
+The goal of this work was to explain the emergence of consistent characteristic representations from sparse linear coding models fit to natural data despite the varied assumptions underlying the many algorithms in current use.
 To this end, we have taken an important step toward unifying the hundreds (if not thousands) of publications on the topic by demonstrating very general, deterministic conditions under which the identification of parameters in this parsimonious model is not only possible but also robust to the inevitable uncertainty permeating measurement and model choice.
 
-Specifically, we have shown that, given sufficient data and suitable dictionary, the problem of seeking a dictionary and sparse codes with minimal average support size over the data (Prob.~\ref{OptimizationProblem}) reduces to an instance of Prob.~\ref{InverseProblem}, to which our main result (Thm.~\ref{DeterministicUniquenessTheorem}) applies: every dictionary and sparse codes solving Prob.~\ref{InverseProblem} are equivalent up to inherent relabeling/scaling ambiguities and a discrepancy (error) that scales linearly with the measurement noise or modeling inaccuracy.
-The constants we provide are explicit and computable; hence, there is an effective procedure sufficient to affirm if a proposed solution to Probs.~\ref{DeterministicUniquenessTheorem} or \ref{OptimizationProblem} is indeed unique (up to noise and inherent ambiguities).
+Specifically, we have shown that, given sufficient data, the problem of seeking a dictionary and sparse codes with minimal average support size (Prob.~\ref{OptimizationProblem}) reduces to an instance of Prob.~\ref{InverseProblem}, to which our main result (Thm.~\ref{DeterministicUniquenessTheorem}) applies: every dictionary and sparse codes consistent with the data are equivalent up to inherent relabeling/scaling ambiguities and a discrepancy (error) that scales linearly with the measurement noise or modeling inaccuracy.
+The constants we provide are explicit and computable; as such, there is an effective procedure that affirms if a proposed solution to Probs.~\ref{DeterministicUniquenessTheorem} or \ref{OptimizationProblem} is indeed unique up to noise and inherent ambiguities.
 
-An immediate application of our theoretical work is Prop.~\ref{neuroprop}, which certifies the validity of perhaps the only published theory to date of neurally-plausible bottleneck communication in the brain: that sparse coding via dictionary learning in a compressed space of nervous activity can recover sparse codes sent through a randomly-constructed (but unknown) noisy wiring bottleneck \cite{Isely10}.\footnote{We refer the reader to \cite{ganguli2012compressed} for a discussion of this application's significance and more on the interactions between sparse linear coding and neuroscience.}
+An immediate application of our theoretical work is Prop.~\ref{neuroprop}, which certifies the validity of perhaps the only published theory of neurally-plausible bottleneck communication in the brain: that sparse linear coding in a compressed space of nerval activity can recover sparse codes sent through a randomly-constructed (but unknown) noisy wiring bottleneck \cite{Isely10}.\footnote{We refer the reader to \cite{ganguli2012compressed} for a discussion of this application's significance and more on the interactions between sparse linear coding and neuroscience.}
 
@@
 
-Beyond an original extension to the noisy regime, a major innovation in our work is a theory of combinatorial designs for support sets (the ``singleton intersection property'') key to the identification of the dictionary.
-We incorporate this idea into a new fundamental lemma in combinatorial matrix theory (Lem.~\ref{MainLemma}), which draws upon the definition of a new matrix lower bound induced by a hypergraph.
-Theoretical advances enabled by our combinatorial approach include: the dictionary size can be unknown and yet still a subset of parameters are recoverable; data require a polynomial, not exponential, number of distinct sparse supports and in certain settings a polynomial number of samples in total is sufficient; the dictionary need not satisfy the spark condition to be identifiable from data.
+Beyond an original extension of existing noiseless guarantees to the noisy regime, a major innovation in our work is a theory of combinatorial designs for support sets key to the identification of the dictionary.
+We incorporate this idea into a new fundamental lemma in matrix theory (Lem.~\ref{MainLemma}), drawing on the definition of a new matrix lower bound induced by a hypergraph satisfying a ``singleton intersection property''.
+Advances enabled by our combinatorial approach include: a subset of dictionary elements is recoverable even if dictionary size is overestimated; data require only a polynomial number of distinct sparse supports; the spark condition is not a necessary property of recoverable dictionaries.
 
-One technical difficulty in proving Thm.~\ref{DeterministicUniquenessTheorem} is the absence of any assumption on dictionaries in solutions to Prob.~\ref{InverseProblem}.
-Although mathematically interesting that no such requirement is necessary, there are other reasons to seek out such a theoretical guarantee.
-For instance, it is difficult to ensure that an algorithm maintain a dictionary satisfying the spark condition \eqref{SparkCondition} at each iteration; indeed, even certifying a dictionary has this property is likely intractable given its NP-hardness \cite{tillmann2014computational}.
+One technical difficulty in proving Thm.~\ref{DeterministicUniquenessTheorem} is the absence of any assumption at all on dictionaries in solutions to Prob.~\ref{InverseProblem}.
+We sought such a guarantee since it is difficult to ensure that an algorithm maintain a dictionary satisfying the spark condition \eqref{SparkCondition} at each iteration, an implicit requirement of all previous works except \cite{Hillar15}; indeed, even certifying a dictionary has this property is likely intractable given its NP-hardness \cite{tillmann2014computational}.
 
-In fact, uniqueness guarantees with minimal assumptions apply to all areas of data science and engineering that utilize learned sparse representations.
+In fact, uniqueness guarantees with minimal assumptions apply to all areas of data science and engineering utilizing learned sparse structure.
 For example, several groups have applied compressed sensing to signal processing tasks: MRI analysis \cite{lustig2008compressed}, image compression \cite{Duarte08}, and, more recently, the design of an ultrafast camera \cite{Gao14}.
 Given such effective uses of compressed sensing, it is only a matter of time before these systems incorporate dictionary learning to encode and process data (e.g., in a device that learns structure from motion \cite{kong2016prior}).
-In these cases, assurances such as those offered by our theorems certify that different devices (with different initialization, samples, etc.) will learn equivalent representations given enough data from statistically identical systems.
-
-To contrast with the current hot topic of ``Deep Learning'', there are few such uniqueness guarantees for these multi-layer feedforward models of data.
-Moreover, there is evidence that even minuscule amounts of (``adversarial'') signal noise can dramatically alter their output \cite{goodfellow2014explaining}.
-In particular, a main reason for the sustained interest in dictionary learning as an unsupervised method for data analysis appears to be the assumed well-posedness of parameter identification in the model, confirmation of which forms the core of our  findings.
+In these cases, assurances such as those offered by our theorems certify that different devices (with different initialization, samples, etc.) will learn equivalent representations given enough data from statistically identical systems.\footnote{To contrast with the current hot topic of ``Deep Learning'', there are few such uniqueness guarantees for these multi-layer feedforward models of data; moreover, there is evidence that even minuscule amounts of (``adversarial'') signal noise can dramatically alter their output \cite{goodfellow2014explaining}.} Indeed, it seems a main reason for the sustained interest in dictionary learning as an unsupervised method for data analysis appears to be the assumed well-posedness of parameter identification in the model, confirmation of which forms the core of our  findings.
 
@@
 
-We prove Lem.~\ref{MainLemma} after stating auxiliary lemmas and then sketch the proofs of Thm.~\ref{robustPolythm} and Cor.~\ref{ProbabilisticCor}.
+We prove Lem.~\ref{MainLemma} after stating auxiliary lemmas.% and then sketch the proofs of Thm.~\ref{robustPolythm} and Cor.~\ref{ProbabilisticCor}.
 
@@
 then $\bar m \geq m$, and if $\bar m < mr / (r-1)$ then the association $i \mapsto \cap \pi(\sigma(i))$ defines an injective map to $[\bar m]$ from some $J \subseteq [m]$ of size $\bar m - r(\bar m - m)$.
-In particular, if $\bar m = m$ then $\pi$ is induced by a permutation on $[m]$.
+%In particular, if $\bar m = m$ then $\pi$ is induced by a permutation on $[m]$.
 \end{lemma}
@@
 \begin{proof}[Proof of Lem.~\ref{MainLemma}]
-We will show that the bound \eqref{GapUpperBound} trickles through the intersection semi-lattices of $\{\bm{\mathcal{A}}_S\}_{S \in \mathcal{H}}$ and $\{\bm{\mathcal{B}}_{\bar S}\}_{\bar S \in \pi(\mathcal{H})}$ to yield \eqref{MainLemmaBPD} by virtue of the SIP.
+%We will show that the bound \eqref{GapUpperBound} trickles through the intersection semi-lattices of $\{\bm{\mathcal{A}}_S\}_{S \in \mathcal{H}}$ and $\{\bm{\mathcal{B}}_{\bar S}\}_{\bar S \in \pi(\mathcal{H})}$ to yield \eqref{MainLemmaBPD} by virtue of the SIP.
 
@@
 Since $|S| = |\pi(S)|$, the required fact follows.
-Note that the columns of $\mathbf{B}_{\pi(S)}$ are therefore linearly independent, for all $S \in \mathcal{H}$.
+Note that $\mathbf{B}_{\pi(S)}$ therefore has full column-rank, for all $S \in \mathcal{H}$.
 
@@
 
-Since $\varepsilon < L_2(\mathbf{A}) / C_2$, by \eqref{delrho} the right-hand side in \eqref{randoml} is less than one.
-Hence, $\dim(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}) \leq \dim(\bm{\mathcal{A}}_{\cap \mathcal{G}})$ by \eqref{dimLem}, and \eqref{cond} follows from the linear independence of the columns of $\mathbf{A}_{S}$ and $\mathbf{B}_{\pi(S)}$ for all $S \in \mathcal{G}$.
+Since $\varepsilon < L_2(\mathbf{A}) / C_2$, by \eqref{delrho} the upper bound in \eqref{randoml} is less than one; hence, $\dim(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}) \leq \dim(\bm{\mathcal{A}}_{\cap \mathcal{G}})$ by \eqref{dimLem}, and \eqref{cond} follows from the full column-rank of $\mathbf{A}_{S}$ and $\mathbf{B}_{\pi(S)}$ for all $S \in \mathcal{G}$.
 
@@
 %\section{Proofs of Thm.~\ref{robustPolythm} and Cor.~\ref{ProbabilisticCor}}
-
-\begin{proof}[Proof (sketch) of Thm.~\ref{robustPolythm}]
-Let $\textbf{M}$ be the matrix with columns $\mathbf{A}\mathbf{x}_i$, $i \in [N]$.  Consider the polynomial in the entries of $\mathbf{A}$ and $\mathbf{x}_i$:
-\begin{align*}
-g(\mathbf{A}, \{\mathbf{x}_i\}_{i=1}^N) := \prod_{S \in {[N] \choose 2k}} \sum_{S' \in {[n] \choose 2k}} (\det \textbf{M}_{S',S})^2,
-\end{align*}
-with notation as in Sec.~\ref{Results}.  
-It can be checked that when $g$ is nonzero for a substitution of real numbers for the indeterminates, all of the genericity requirements on $\mathbf{A}$ and $\mathbf{x}_i$ in our proofs of stability in Thm.~\ref{DeterministicUniquenessTheorem} are satisfied (in particular, the spark condition on $\mathbf{A}$).
-\end{proof}
-
-\begin{proof}[Proof (sketch) of Cor.~\ref{ProbabilisticCor}]
-First, note that if a set of measure spaces $\{(X_{\ell}, \Sigma_{\ell}, \nu_{\ell})\}_{\ell=1}^p$ has that $\nu_{\ell}$ is absolutely continuous with respect to $\mu$ for all $\ell \in [p]$, where $\mu$ is the standard Borel measure on $\mathbb{R}$, then the product measure $\prod_{\ell=1}^p \nu_{\ell}$ is absolutely continuous with respect to the standard Borel product measure on $\mathbb{R}^p$.
-% for space:  (e.g.,  \cite{folland2013real}).
-By Thm.~\ref{robustPolythm}, there is a polynomial that is nonzero when $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$; in particular, stability holds almost surely.
-\end{proof}
 

### 2017-08-17 manuscripts/PNAS/chazthm_pnas.tex
discussion

@@
 Another practical implication of Thm.\ref{DeterministicUniquenessTheorem} is the following: there is an effective procedure sufficient to affirm if a proposed solution to Prob.~\ref{InverseProblem} is indeed unique (up to noise and inherent ambiguities).
-One simply checks that the matrix and codes satisfy the respective assumptions of Thm.~\ref{DeterministicUniquenessTheorem} on $\mathbf{A}$ and the $\mathbf{x}_i$.
+One simply checks that the matrix and codes satisfy the respective (computable) assumptions of Thm.~\ref{DeterministicUniquenessTheorem} on $\mathbf{A}$ and the $\mathbf{x}_i$.
 %Another practical implication of Thm.\ref{DeterministicUniquenessTheorem} is the following: there is an effective procedure sufficient to affirm if a proposed solution $(\mathbf{B}, \mathbf{\bar x}_1, \ldots, \mathbf{x}_N)$ to Prob.~\ref{InverseProblem} is indeed unique (up to noise and inherent ambiguities).
@@
 
-An immediate application of our theoretical work is Prop.~\ref{neuroprop}, which certifies the validity of perhaps the only published theory of neurally-plausible bottleneck communication in the brain: that sparse linear coding in a compressed space of nerval activity can recover sparse codes sent through a randomly-constructed (but unknown) noisy wiring bottleneck \cite{Isely10}.\footnote{We refer the reader to \cite{ganguli2012compressed} for a discussion of this application's significance and more on the interactions between sparse linear coding and neuroscience.}
+An immediate application of our theoretical work is Prop.~\ref{neuroprop}, which certifies the validity of perhaps the only published theory of neurally-plausible bottleneck communication in the brain: that sparse linear coding in a compressed space of neural activity can recover sparse codes sent through a randomly-constructed (but unknown) noisy wiring bottleneck \cite{Isely10}.\footnote{We refer the reader to \cite{ganguli2012compressed} for a discussion of this application's significance and more on the interactions between sparse linear coding and neuroscience.}
 
@@
 
-Beyond an original extension of existing noiseless guarantees to the noisy regime, a major innovation in our work is a theory of combinatorial designs for support sets key to the identification of the dictionary.
+Beyond an original extension of existing noiseless guarantees \cite{Hillar15} to the noisy regime, a major innovation in our work is a theory of combinatorial designs for support sets key to the identification of the dictionary.
 We incorporate this idea into a new fundamental lemma in matrix theory (Lem.~\ref{MainLemma}), drawing on the definition of a new matrix lower bound induced by a hypergraph satisfying a ``singleton intersection property''.
-Advances enabled by our combinatorial approach include: a subset of dictionary elements is recoverable even if dictionary size is overestimated; data require only a polynomial number of distinct sparse supports; the spark condition is not a necessary property of recoverable dictionaries.
+Advances enabled by our combinatorial approach include: 1) a subset of dictionary elements is recoverable even if dictionary size is overestimated, 2) data require only a polynomial number of distinct sparse supports, and 3) the spark condition is not a necessary property of recoverable dictionaries.
 
-One technical difficulty in proving Thm.~\ref{DeterministicUniquenessTheorem} is the absence of any assumption at all on dictionaries in solutions to Prob.~\ref{InverseProblem}.
-We sought such a guarantee since it is difficult to ensure that an algorithm maintain a dictionary satisfying the spark condition \eqref{SparkCondition} at each iteration, an implicit requirement of all previous works except \cite{Hillar15}; indeed, even certifying a dictionary has this property is likely intractable given its NP-hardness \cite{tillmann2014computational}.
+A technical difficulty in proving Thm.~\ref{DeterministicUniquenessTheorem} is the absence of any assumption at all on dictionaries in solutions to Prob.~\ref{InverseProblem}.
+We sought such a guarantee because of the practical difficulty of ensuring that an algorithm maintain a dictionary satisfying the spark condition \eqref{SparkCondition} at each iteration, an implicit requirement of all previous works except \cite{Hillar15}; indeed, even certifying a dictionary has this property is NP-hard \cite{tillmann2014computational}.
 
@@
 Given such effective uses of compressed sensing, it is only a matter of time before these systems incorporate dictionary learning to encode and process data (e.g., in a device that learns structure from motion \cite{kong2016prior}).
-In these cases, assurances such as those offered by our theorems certify that different devices (with different initialization, samples, etc.) will learn equivalent representations given enough data from statistically identical systems.\footnote{To contrast with the current hot topic of ``Deep Learning'', there are few such uniqueness guarantees for these multi-layer feedforward models of data; moreover, there is evidence that even minuscule amounts of (``adversarial'') signal noise can dramatically alter their output \cite{goodfellow2014explaining}.} Indeed, it seems a main reason for the sustained interest in dictionary learning as an unsupervised method for data analysis appears to be the assumed well-posedness of parameter identification in the model, confirmation of which forms the core of our  findings.
+In these cases, assurances such as those offered by our theorems certify that different devices (with different initialization, samples, etc.) will learn equivalent representations given enough data from statistically identical systems.\footnote{To contrast with the current hot topic of ``Deep Learning'', there are few such uniqueness guarantees for these multi-layer feedforward models of data; moreover, there is evidence that even minuscule amounts of (``adversarial'') signal noise can dramatically alter their output \cite{goodfellow2014explaining}.} Indeed, it seems a main reason for the sustained interest in dictionary learning as an unsupervised method for data analysis appears to be the assumed well-posedness of parameter identification in the sparse linear coding model, confirmation of which forms the core of our theoretical findings.
 

### 2017-08-17 manuscripts/PNAS/chazthm_pnas.tex
discussion

@@
 
-We prove Lem.~\ref{MainLemma} after stating auxiliary lemmas.% and then sketch the proofs of Thm.~\ref{robustPolythm} and Cor.~\ref{ProbabilisticCor}.
+In this section, we prove Lem.~\ref{MainLemma} after stating auxiliary lemmas.% and then sketch the proofs of Thm.~\ref{robustPolythm} and Cor.~\ref{ProbabilisticCor}.
 

### 2017-08-17 manuscripts/PNAS/chazthm_pnas.tex
chaz

@@
 
-We close this section with a remark on sample complexity.
+We close this section with a comment on sample complexity.
 A basic open problem remains: how many samples are necessary to determine the sparse linear coding model?
@@
 
-The goal of this work was to explain the emergence of consistent characteristic representations from sparse linear coding models fit to natural data despite the varied assumptions underlying the many algorithms in current use.
+The goal of this work was to explain the emergence of characteristic representations from sparse linear coding models fit to natural data despite the varied assumptions underlying the many algorithms in current use.
 To this end, we have taken an important step toward unifying the hundreds (if not thousands) of publications on the topic by demonstrating very general, deterministic conditions under which the identification of parameters in this parsimonious model is not only possible but also robust to the inevitable uncertainty permeating measurement and model choice.
@@
 Beyond an original extension of existing noiseless guarantees \cite{Hillar15} to the noisy regime, a major innovation in our work is a theory of combinatorial designs for support sets key to the identification of the dictionary.
-We incorporate this idea into a new fundamental lemma in matrix theory (Lem.~\ref{MainLemma}), drawing on the definition of a new matrix lower bound induced by a hypergraph satisfying a ``singleton intersection property''.
-Advances enabled by our combinatorial approach include: 1) a subset of dictionary elements is recoverable even if dictionary size is overestimated, 2) data require only a polynomial number of distinct sparse supports, and 3) the spark condition is not a necessary property of recoverable dictionaries.
+We incorporate this idea into a new fundamental lemma in matrix theory (Lem.~\ref{MainLemma}) which draws on the definition of a new matrix lower bound induced by a hypergraph satisfying a ``singleton intersection property''.
+Insights enabled by our combinatorial approach include: 1) a subset of dictionary elements is recoverable even if dictionary size is overestimated, 2) data require only a polynomial number of distinct sparse supports, and 3) the spark condition is not a necessary property of recoverable dictionaries.
 

### 2017-08-17 manuscripts/PNAS/review/point_by_point_response.txt
chaz

@@
 We have included in our updated manuscript a discussion of the computability of the sufficient conditions (they are, indeed, computable), as per the reviewer’s request.
-The main constants in our work -- C_1, C_2 -- are computable, elementarily, in terms of two positive quantities that are natural in our context: (a) the "Lower Bound" L_H(A) of a matrix A given a hypergraph H (the support sets of sparse x's generating the data — see *NOTE* below this paragraph), which is a measure of how distinguishable two x’s with supports in H are by their images under A, and (b) the value in Def.
+The main constants in our work -- C_1, C_2 -- are computable, elementarily, in terms of two positive quantities that are natural in our context: (a) the restricted “Lower Bound" L_k(M) of a matrix M, which is a measure of how distinguishable two k-sparse x’s are by their images under M, and (b) the value in Def.
 4 of \xi(V_1,…,V_l) given subspaces V_i spanned by columns of A, which bounds the distance between intersections of such subspaces and each subspace individually.
-The first quantity (a) is, in some form or another, related to standard objects in the field and may be computed as the smallest singular value of a set of specific sub-matrices; in particular, for fixed sparsity constraint k on H, the lower bound L_H(A) is efficiently computable (polynomial time).
-Because deciding L_H(A) > 0 is already NP-hard (TP14), it seems likely that without fixing a sparsity level there is no efficient computation in general for (a).
+The first quantity (a) is, in some form or another, related to standard objects in the field and may be computed as the smallest singular value of a set of specific sub-matrices; in particular, for fixed sparsity constraint k, the lower bound L_k(A) is efficiently computable (polynomial time).
+Because deciding L_k(A) > 0 is already NP-hard (TP14), it seems likely that without fixing a sparsity level there is no efficient computation in general for (a).
 The calculation of (b) involves determining "canonical angles" between subspaces, which is usually reduced again to a numerical (efficient) singular value decomposition given the fixed subspaces.
@@
 Thus, while our constants are effective (an algorithm exists to compute them), they are not necessarily polynomial-time computable.
-
-*NOTE* We have introduced for reasons discussed below the notion of L_H(A) in our re-submission where previously (in our original submission) we had defined only L_k(A).
 
@@
 We believe that these sufficient conditions yield strong enough conclusions to stand on their own; for instance, in synchronizing device parameters for a particular sparsely representable sensory ensemble.
-Nonetheless, we have included in our revised manuscript some discussion of where the results can be tightened (e.g.
-Lem.
-4).
 
@@
 1 without satisfying the spark condition.) We had omitted this point in our original submission of the manuscript to keep things simple, but have decided to include this fact in our resubmission.
-This also required us to redefine the restricted matrix lower bound L to be in terms of a hypergraph, which is an interesting object for further study in its own right.
+This also required us to redefine the restricted matrix lower bound L_k to be in terms of a hypergraph H (L_H in the revised manuscript), which is an interesting object for further study in its own right.
 
@@
 Our theory of combinatorial designs (the ‘singleton intersection property’) requires only that there be a sufficient number of x_i drawn from each support in a hypergraph satisfying the SIP, whereas the theory in (HS15) requires that a sufficient number of x_i be drawn from *every* support of size k in [m].
-Here, we make an explicit comparison with Table I in (HS15) row by row, assuming for our results that sufficient data have been sampled from all supports in a hypergraph H satisfying the SIP:
+Below, we make an explicit comparison with Table I in (HS15) row by row, assuming for our results that sufficient data have been sampled from all supports in a hypergraph H satisfying the SIP:
 
@@
 We cannot make a direct comparison here because we have not calculated the probability that a random set of supports satisfy the SIP (see our response to a similar question by the second reviewer).
-We think this is an interesting problem for the community to solve; regardless, the result of (HS15) here is implied by our more general theory.
+We think this is an interesting problem for the community to solve; regardless, the result of (HS15) here is still implied by our more general theory.
 
@@
 Here is the only case where the sample complexity stated in (HS15) is technically better than ours, but it differs in flavor: their x_i are assumed to be distributed as (k+1) samples per support for every support of size k in [m], whereas ours supposes that (k-1){m \choose k} codes x_i are distributed over each support in some hypergraph H satisfying the SIP.
-Regardless, the (technically) lower result of (HS15) is still implied by our more general theory in the case \varepsilon = 0 with the addition of their probabilistic argument.
+Regardless, the (technically) better result of (HS15) is still implied by our more general theory in the case \varepsilon = 0 with the addition of their probabilistic argument.
 
@@
 
-While we appreciate this question, we feel that since our results improve in every case except for one noise-free technicality (ROW 4), and since the results of (HS15) are all entailed anyway by our more general theory, an explicit comparison such as that which we provided above would not be the best use of our limited space in the manuscript; although we are willing to add a discussion about this if necessary.
+To sum up, while we appreciate this question, we feel that since our results improve in every case except for one noise-free technicality (ROW 4), and since the results of (HS15) are all entailed anyway by our more general theory, an explicit comparison such as that which we provided above would not be the best use of our limited space in the manuscript; although we are willing to add a discussion about this if necessary.
 Many thanks for your careful review of the mathematics.
@@
 
-RESPONSE: We have determined explicit forms for the effectively computable constants in Theorem 1.
+RESPONSE: We have determined explicit forms for the effectively computable constants in Theorem 1, but they are not necessarily feasible to compute.
+We have included discussion of this in the revised manuscript.
 

### 2017-08-18 manuscripts/PNAS/chazthm_pnas.tex
sml things

@@
 Fix an $n \times m$ matrix $\mathbf{A}$ with $L_{2\mathcal{H}}(\mathbf{A}) > 0$ for an $r$-regular $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP.
-If \mbox{$\{\mathbf{x}_1, \ldots, \mathbf{x}_N\} \subset \mathbb{R}^m$} contains, for each $S \in \mathcal{H}$, more than $(k-1){m \choose k}$ $k$-sparse vectors in general linear position supported in $S$, then there is $C_1 > 0$ with the following holding for all\footnote{The condition $\varepsilon < L_2(\mathbf{A}) /C_1$ is necessary; otherwise,  with \mbox{$\mathbf{A}$ = $\mathbf{I}$} and $\mathbf{x}_i = \mathbf{e}_i$, there is a matrix $\mathbf{B}$ and $1$-sparse $\mathbf{\bar{x}}_i$ with $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\bar{x}}_i \|_2 \leq \varepsilon$, nonetheless, violating \eqref{Cstable}.} $\varepsilon < L_{2}(\mathbf{A}) / C_1$:
+If \mbox{$\{\mathbf{x}_1, \ldots, \mathbf{x}_N\} \subset \mathbb{R}^m$} contains, for each $S \in \mathcal{H}$, more than $(k-1){m \choose k}$ $k$-sparse vectors in general linear position supported in $S$, then there is $C_1 > 0$ with the following holding for all\footnote{The condition $\varepsilon < L_2(\mathbf{A}) /C_1$ is necessary; otherwise,  with \mbox{$\mathbf{A}$ = $\mathbf{I}$} and $\mathbf{x}_i = \mathbf{e}_i$, there is a matrix $\mathbf{B}$ and $1$-sparse $\mathbf{\bar{x}}_i$ with $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\bar{x}}_i \|_2 \leq \varepsilon$ that nonetheless violates \eqref{Cstable}.} $\varepsilon < L_{2}(\mathbf{A}) / C_1$:
 
@@
 The total number of $(k-1)$-sparse vectors $\mathbf{\bar x}_i$ can thus not exceed $|\mathcal{H}|(k-1){ \bar m \choose k-1}$.
-By \eqref{eqn} no more than $|\mathcal{H}|k(k-1){ \bar m \choose k-1}$ vectors $\mathbf{\bar x}_i$ are not $k$-sparse.
+By \eqref{eqn}, no more than $|\mathcal{H}|k(k-1){ \bar m \choose k-1}$ vectors $\mathbf{\bar x}_i$ are not $k$-sparse.
 Since for every $S \in \mathcal{H}$ there are over $(k-1)\left[ {\bar m \choose k} + |\mathcal{H}|k{ \bar m \choose k-1} \right]$ vectors $\mathbf{x}_i$ supported there, it follows that more than $(k-1){\bar m \choose k}$ of them have corresponding $\mathbf{\bar x}_i$ that are $k$-sparse.
@@
 
-The goal of this work was to explain the emergence of characteristic representations from sparse linear coding models fit to natural data despite the varied assumptions underlying the many algorithms in current use.
+The goal of this work was to explain the emergence of characteristic representations from sparse linear coding models fit to natural data, despite the varied assumptions underlying the many algorithms in current use.
 To this end, we have taken an important step toward unifying the hundreds (if not thousands) of publications on the topic by demonstrating very general, deterministic conditions under which the identification of parameters in this parsimonious model is not only possible but also robust to the inevitable uncertainty permeating measurement and model choice.
@@
 Beyond an original extension of existing noiseless guarantees \cite{Hillar15} to the noisy regime, a major innovation in our work is a theory of combinatorial designs for support sets key to the identification of the dictionary.
-We incorporate this idea into a new fundamental lemma in matrix theory (Lem.~\ref{MainLemma}) which draws on the definition of a new matrix lower bound induced by a hypergraph satisfying a ``singleton intersection property''.
+We incorporate this idea into a new fundamental lemma in matrix theory (Lem.~\ref{MainLemma}) that draws upon the definition of a new matrix lower bound induced by a hypergraph satisfying a ``singleton intersection property''.
 Insights enabled by our combinatorial approach include: 1) a subset of dictionary elements is recoverable even if dictionary size is overestimated, 2) data require only a polynomial number of distinct sparse supports, and 3) the spark condition is not a necessary property of recoverable dictionaries.

### 2017-08-18 manuscripts/PNAS/chazthm_pnas.tex
minor edits

--- 2017-08-17 manuscripts/PNAS/chazthm_pnas.tex
@@
 In the next section, we give precise statements of our main results, which include an explicit form for $\varepsilon(\delta_1, \delta_2)$.
-We then prove our main theorem (Thm.~\ref{DeterministicUniquenessTheorem}) in Sec.~\ref{DUT} after stating some additional definitions and lemmas required for the proof, including a useful result in combinatorial matrix analysis (Lem.~\ref{MainLemma}).
+We then prove our main theorem (Thm.~\ref{DeterministicUniquenessTheorem}) in Sec.~\ref{DUT} after stating some additional definitions and lemmas required for the proof, including a useful result in combinatorial matrix analysis (Lem.~\ref{MainLemma}, proven in Appendix).
 We also provide an argument that extends our guarantees to the following more common optimization formulation of the dictionary learning problem (Thm.~\ref{SLCopt}).
@@
 The following is a precise statement of our main result.
-The quantity $C_1 = C_1(\mathbf{A}, \{\mathbf{x}_i\}_{i=1}^N, \mathcal{H})$ is left undefined until Sec.~\ref{DUT} (see \eqref{Cdef1}).
-%=======
-%where we write $L_{k}$ when $\mathcal{H} = {[m] \choose k}$.\footnote{We note that $1 - \sqrt{k} L_k(\mathbf{M})$ is known as the asymmetric lower restricted isometry constant \cite{Blanchard2011}.} Clearly, for any $\mathbf{M}$ satisfying \eqref{SparkCondition}, we have $L_{k'}(\mathbf{M}) > 0$ for  $k' \leq 2k$.
-Note that if $\mathcal{H}$ covers $[m]$ (i.e., $\cup \mathcal{H} = [m]$), then $L_2 \geq L_{2\mathcal{H}}$.
-% 
-%A vector $\mathbf{x}$ is said to be \emph{supported} in $S \subseteq [m]$ when $\mathbf{x} \in \text{\rm span}\{\mathbf{e}_j: j\in S\}$, where $\mathbf{e}_j$ are the standard basis in $\mathbb R^m$. 
-%%Denote by $\mathbf{x}^J$ the subvector formed from the entries of $\mathbf{x}$ indexed by $J$. 
-%A set of $k$-sparse vectors is said to be in \emph{general linear position} when any $k$ of them are linearly independent.
-The following is a precise statement of our main result.
-Only the quantity $C_1$ is left undefined until later (in Sec.~\ref{DUT}, Eq.~\eqref{Cdef1}).
-%>>>>>>> d1407a275dc391dabad7bb62d3e659f9a4ac4624
+We leave the quantity $C_1 = C_1(\mathbf{A}, \{\mathbf{x}_i\}_{i=1}^N, \mathcal{H})$ undefined until Sec.~\ref{DUT} (see \eqref{Cdef1}).
+
+%eps-tightness COUNTER-EXAMPLE:
+%Consider the alternate dictionary $B = \left(\mathbf{0}, \frac{1}{2}(\mathbf{e}_1 + \mathbf{e}_2), \mathbf{e}_3, \ldots, \mathbf{e}_{m} \right)$ and sparse codes $\mathbf{b}_i = \mathbf{e}_2$ for $i = 1, 2$ and $\mathbf{b}_i = \mathbf{e}_i$ for $i = 3, \ldots, m$.
+Then $|A\mathbf{a}_i - B\mathbf{b}_i| = 1/\sqrt{2}$ for $i = 1, 2$ (and $0$ otherwise).
+If there were permutation and invertible diagonal matrices $P \in \mathbb{R}^{m \times m}$ and $D \in \mathbb{R}^{m \times m}$ such that $|(A-BPD)\mathbf{e}_i| \leq C\varepsilon$ for all $i \in [m]$, then we would reach the contradiction $1 = |P^{-1}\mathbf{e}_1|_2 = |(A-BPD)P^{-1}\mathbf{e}_1|_2 \leq 1/\sqrt{2}$.
 
@@
 Fix an $n \times m$ matrix $\mathbf{A}$ with $L_{2\mathcal{H}}(\mathbf{A}) > 0$ for an $r$-regular $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP.
-If \mbox{$\{\mathbf{x}_1, \ldots, \mathbf{x}_N\} \subset \mathbb{R}^m$} contains, for each $S \in \mathcal{H}$, more than $(k-1){m \choose k}$ $k$-sparse vectors in general linear position supported in $S$, then there is $C_1 > 0$ with the following holding for all\footnote{The condition $\varepsilon < L_2(\mathbf{A}) /C_1$ is necessary; otherwise,  with \mbox{$\mathbf{A}$ = $\mathbf{I}$} and $\mathbf{x}_i = \mathbf{e}_i$, there is a matrix $\mathbf{B}$ and $1$-sparse $\mathbf{\bar{x}}_i$ with $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\bar{x}}_i \|_2 \leq \varepsilon$, nonetheless, violating \eqref{Cstable}.} $\varepsilon < L_{2}(\mathbf{A}) / C_1$:
+If \mbox{$\{\mathbf{x}_1, \ldots, \mathbf{x}_N\} \subset \mathbb{R}^m$} contains, for each $S \in \mathcal{H}$, more than $(k-1){m \choose k}$ $k$-sparse vectors in general linear position supported in $S$, then there is $C_1 > 0$ with the following holding for all\footnote{The condition $\varepsilon < L_2(\mathbf{A}) /C_1$ is necessary; otherwise,  with \mbox{$\mathbf{A}$ = $\mathbf{I}$} and $\mathbf{x}_i = \mathbf{e}_i$, there is a matrix $\mathbf{B}$ satisfying $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\bar{x}}_i \|_2 \leq \varepsilon$ for $1$-sparse $\mathbf{\bar{x}}_i$ that nonetheless violates \eqref{Cstable}.} $\varepsilon < L_{2}(\mathbf{A}) / C_1$:
 
@@
 %
-for some nonempty $J \subseteq [m]$ and $\bar J \subseteq [m]$ of size $\bar m - r(\bar m - m)$, permutation matrix $\mathbf{P}$, and and invertible diagonal matrix $\mathbf{D}$.
+for some nonempty $J \subseteq [m]$ and $\bar J \subseteq [\bar m]$ of size $\bar m - r(\bar m - m)$, permutation matrix $\mathbf{P}$, and and invertible diagonal matrix $\mathbf{D}$.
 
@@
 
-We note the following facts about $d$. For subspaces $U \subseteq U', V \subseteq \mathbb{R}^m$, we have $d(U,V) \leq d(U',V)$ and \cite[Cor.~2.6]{Kato2013}:
+We note the following facts about $d$. For subspaces $U \subseteq U', V \subseteq \mathbb{R}^m$, we have $d(U,V) \leq d(U',V)$ and \cite[Ch.~4 Cor.~2.6]{Kato2013}: %Kato p.223
 \begin{align}\label{dimLem}

### 2017-08-18 manuscripts/PNAS/chazthm_pnas.tex

@@
 Fix an $n \times m$ matrix $\mathbf{A}$ with $L_{2\mathcal{H}}(\mathbf{A}) > 0$ for an $r$-regular $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP.
-If \mbox{$\{\mathbf{x}_1, \ldots, \mathbf{x}_N\} \subset \mathbb{R}^m$} contains, for each $S \in \mathcal{H}$, more than $(k-1){m \choose k}$ $k$-sparse vectors in general linear position supported in $S$, then there is $C_1 > 0$ with the following holding for all\footnote{The condition $\varepsilon < L_2(\mathbf{A}) /C_1$ is necessary; otherwise,  with \mbox{$\mathbf{A}$ = $\mathbf{I}$} and $\mathbf{x}_i = \mathbf{e}_i$, there is a matrix $\mathbf{B}$ satisfying $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\bar{x}}_i \|_2 \leq \varepsilon$ for $1$-sparse $\mathbf{\bar{x}}_i$ that nonetheless violates \eqref{Cstable}.} $\varepsilon < L_{2}(\mathbf{A}) / C_1$:
+If \mbox{$\{\mathbf{x}_1, \ldots, \mathbf{x}_N\} \subset \mathbb{R}^m$} contains, for each $S \in \mathcal{H}$, more than $(k-1){m \choose k}$ $k$-sparse vectors in general linear position supported in $S$, then there is $C_1 > 0$ with the following holding for all\footnote{The condition $\varepsilon < L_2(\mathbf{A}) /C_1$ is necessary; otherwise,  with \mbox{$\mathbf{A}$ = $\mathbf{I}$} and $\mathbf{x}_i = \mathbf{e}_i$, there is a matrix $\mathbf{B}$ and $1$-sparse $\mathbf{\bar{x}}_i$ with $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\bar{x}}_i \|_2 \leq \varepsilon$ that nonetheless violates \eqref{Cstable}.} $\varepsilon < L_{2}(\mathbf{A}) / C_1$:
 

### 2017-08-18 manuscripts/PNAS/chazthm_pnas.tex

@@
 As a simple example for $k=2$, let $\mathbf{A} = [ \mathbf{e}_1, \ldots, \mathbf{e}_5, \mathbf{v}]$ where $\mathbf{v} = \mathbf{e}_1 + \mathbf{e}_3 + \mathbf{e}_5$, and take $\mathcal{H}$ to be all consecutive pairs of $[m]$ arranged in cyclic order.
-Then, $\mathbf{A}$ satisfies the assumptions of Thm.~\ref{DeterministicUniquenessTheorem} but not \eqref{SparkCondition}.
+Then, dictionary $\mathbf{A}$ satisfies the assumptions of Thm.~\ref{DeterministicUniquenessTheorem} but not \eqref{SparkCondition}.
 %(since $\{ \mathbf{A}_1, \mathbf{A}_3, \mathbf{A}_5, \mathbf{A}_6\}$ is not a linearly independent set).
@@
 Sparse neural population activity is recoverable from noisy random linear compression by any method that solves Prob.~\ref{DeterministicUniquenessTheorem} or \ref{SLCopt}; in particular, via biophysically plausible unsupervised sparse linear coding (e.g.
-\cite{rehnsommer2007, rozell2007neurally, ganguli2012compressed}).
+\cite{rehnsommer2007, rozell2007neurally}).
 \end{proposition}
@@
 A basic open problem remains: how many samples are necessary to determine the sparse linear coding model?
-If $k$ is held fixed or if the size of the support set of reconstructing codes is known to be polynomial in $\bar m$ and $k$, then a practical (polynomial) amount of data suffices.\footnote{In the latter case, a reexamination of the pigeonholing argument in the proof of Thm.~\ref{DeterministicUniquenessTheorem} requires a polynomial number of samples distributed over a polynomial number of supports.} Reasons to be skeptical that this holds in general, however, can be found in \cite{tillmann2014computational, tillmann2015computational}.
+If $k$ is held fixed or if the size of the support set of reconstructing codes is known to be polynomial in $\bar m$ and $k$, then a practical (polynomial) amount of data suffices.\footnote{In the latter case, a reexamination of the pigeonholing argument in the proof of Thm.~\ref{DeterministicUniquenessTheorem} requires a polynomial number of samples distributed over a polynomial number of supports.} Reasons to be skeptical that this holds in general, however, can be found in \cite{tillmann2014computational, Tillmann15}.
 
@@
 
-In this section, we prove Lem.~\ref{MainLemma} after stating auxiliary lemmas.% and then sketch the proofs of Thm.~\ref{robustPolythm} and Cor.~\ref{ProbabilisticCor}.
+In this section, we prove Lem.~\ref{MainLemma} after stating and proving some auxiliary lemmas.% and then sketch the proofs of Thm.~\ref{robustPolythm} and Cor.~\ref{ProbabilisticCor}.
 

### 2017-08-19 manuscripts/PNAS/review/point_by_point_response.txt
cover pnt by pnt SR

@@
 (TP14) Tillman, Pfetsch, IEEE Transactions on information processing, 2014.
+(T15) Tillman, IEEE Signal Processing Letters, 2015.
 (HS15) Hillar, Sommer, IEEE Transactions on information processing, 2015.
@@
 
-RESPONSE: We have included in our revised manuscript a more compelling exposition of the significance of our results and their relevance to the general scientific audience, and we thank the editor for the opportunity to address this concern shared by both reviewers.
+RESPONSE: We have included in our revised manuscript a more compelling exposition of the significance of our results and their relevance to a general scientific audience, and we thank the editor for the opportunity to address this concern shared by both reviewers.
 
@@
 We agree with the reviewer that a straightforward extension of the approach and noise-free result of (HS15) to the noisy case — while still a significant advancement in applied mathematics with actual practical implications — would not necessarily merit publication in PNAS on its own.
-The reviewer, however, seems to have overlooked the fact that our main result (Thm.
-1) generalizes the noise-free result of (HS15) far beyond a simple extension to the noisy case in ways which provide valuable insight into the dictionary learning model and that a significant deviation from the approach taken in (HS15) was necessary to prove these new facts.
-Moreover, our solution (Cor.
+However, our main result (Thm.
+1) generalizes the noise-free result of (HS15) far beyond a simple extension to the noisy case in ways which provide valuable insight into the dictionary learning model and, moreover, a significant deviation from the approach taken in (HS15) was necessary to prove these new facts.
+Additionally, our solution (Cor.
 2) to the optimization formulation of the dictionary learning problem (Prob.
-2) — that of most interest to optimization theorists and practitioners of their methods — is (to our knowledge) the first of its kind in both the noise-free and noisy domains.
+2) — of most interest to optimization theorists and practitioners of their methods — is (to our knowledge) the first of its kind in both the noise-free and noisy domains.
 We discuss all of these points in more detail in our response to the reviewer’s later "detailed comments".
 
-We have included in our updated manuscript a discussion of the computability of the sufficient conditions (they are, indeed, computable), as per the reviewer’s request.
-The main constants in our work -- C_1, C_2 -- are computable, elementarily, in terms of two positive quantities that are natural in our context: (a) the restricted “Lower Bound" L_k(M) of a matrix M, which is a measure of how distinguishable two k-sparse x’s are by their images under M, and (b) the value in Def.
-4 of \xi(V_1,…,V_l) given subspaces V_i spanned by columns of A, which bounds the distance between intersections of such subspaces and each subspace individually.
+As per the reviewer’s request, we have included in our updated manuscript a discussion of the computability of the sufficient conditions (they are, indeed, computable.
+The main constants in our work -- C_1, C_2 -- are computable, elementarily, in terms of two positive quantities that are natural in our context: (a) the restricted "Lower Bound" L_k(M) of a matrix M, which is a measure of how distinguishable two k-sparse x’s are by their images under M, and (b) the value in Def.
+4 of \xi(V_1,..,V_l) given subspaces V_i spanned by columns of A, which bounds the distance between intersections of such subspaces and each subspace individually.
 The first quantity (a) is, in some form or another, related to standard objects in the field and may be computed as the smallest singular value of a set of specific sub-matrices; in particular, for fixed sparsity constraint k, the lower bound L_k(A) is efficiently computable (polynomial time).
@@
 
-Another natural question that arises is the mathematical "tightness" of result statements for the three types of quantities: (a) required coding error eps(delta_1, delta_2) sufficient to guarantee uniqueness in terms of desired dictionary delta_1 and sparse representation error delta_2, (b) the constants C_1 and C_2 involved in our sufficient linear bound on eps(delta_1, delta_2), and (c) the number of sufficient samples N guaranteeing uniqueness.
+We next respond to the reviewer's question about the mathematical "tightness" for the three types of quantities in our results : (a) required coding error eps(delta_1, delta_2) sufficient to guarantee uniqueness in terms of desired dictionary delta_1 and sparse representation error delta_2, (b) the constants C_1 and C_2 involved in our sufficient linear bound on eps(delta_1, delta_2) in terms of the noise, and (c) the number of sufficient samples N guaranteeing uniqueness.
 With respect to (a), even with fixed dictionary, the recovery of sparse representations up to an error that is linear in the noise is classically optimal (up to constants).
-Thus, the fact that we have a sufficient error in coding for uniqueness being linear in terms of both the desired dictionary and sparse vector recovery error is optimal.
-Although optimal up to constants, our solution to Problem 1 involves constants C_1 and C_2, it would be interesting and relevant for practical applications to determine the minimal such constants.
+Thus, the fact that we have a sufficient error in coding for uniqueness being linear for both the desired dictionary and sparse vector recovery error is optimal.
+Although optimal, our solution to Problem 1 involves constants C_1 and C_2, and it would be interesting and relevant for practical applications to determine the minimal such constants.
 In the case of sparsity k=1, we have given an example showing optimality of constants in this case.
 Finally, with respect to (c), we regard this as a fundamental open problem in the field: how many sparsely generated samples determine the linear coding model?
-(One reason to be skeptical that a polynomial suffice is again (TP14).)  However, there is some good news -- if k is fixed and we constrain sparse codes \hat{x}_i to come from a polynomial number of supports, then a polynomial number of samples N is enough to guarantee uniqueness.
+(One reason to be skeptical that a polynomial suffice is again (TP14, T15).)  However, there is some good news -- if k is fixed and we constrain sparse codes \hat{x}_i to come from a polynomial number of supports, then a polynomial number of samples N is enough to guarantee uniqueness.
 In particular, a sample complexity polynomial in (m,k) can be achieved by limiting the size of the support set of the \tilde x_i, and we have revised the manuscript to discuss this fact (which, incidentally, does not follow from the results of (HS15) in the noiseless case).
@@
 With all due respect to the reviewer, we believe the most compelling practical implication of a noisy result over a noiseless result is plainly evident: never has there been an experiment without noise and an unstable model is therefore useless in practice.
-We assume the reviewer must instead be concerned with what additional practical “take-away” message our manuscript contains.
-One significant one is the outline of a procedure which can affirm if one’s proposed solution to Prob.
+We assume the reviewer must instead be concerned with what additional practical "take-away" message our manuscript contains.
+One significant one is the outline of a procedure that can (sufficiently) affirm if one’s proposed solution to Prob.
 1 or Prob.
@@
       - Discard those for which there are (k-1){m \choose k} or fewer x_i with that support.
-      - Discard those for which the supported x_i are not in GLP. (This should also exclude any supports less than k in size.)
+      - Discard those for which the supported x_i are not in general linear position. (This should also exclude any supports less than k in size.)
    - From the support sets that remain, list all SIP-satisfying hypergraphs that are subsets of this set
@@
    - For each of the remaining hypergraphs, determine the constant C_1 from A and the x_i (or for every subset of the x_i of size (k-1){m \choose k})
-   - Check that the derived upper bound on \varepsilon exceeds that of the original problem. If yes, the solution is “unique”.
+   - Check that the derived upper bound on \varepsilon exceeds that of the original problem. If yes, the solution is "unique".
 
-More practical implications arise from our discovery of sufficient combinatorial designs for support sets of generating codes x_i, which have implications for polynomial time.
+There are other practical (polynomial time) implications of our discovery of sufficient combinatorial designs for support sets of generating codes x_i.
 Moreover, we have shown that a subset of dictionary elements are recoverable even if the number of dictionary elements in total is unknown; these observations are discussed in more detail below.
@@
 1 is presented in the manuscript.
-As observed by our second reviewer, however, the extension to the noisy case did indeed require an novel combination of several results in the literature.
+As observed by our second reviewer, however, the extension to the noisy case did indeed require a novel combination of several results in the literature.
 Specifically, the main difficulty was to generalize Lemma 1 to the case where the k-dimensional subspaces spanned by corresponding (through the map \pi) submatrices of A and B are assumed only to be proximal (small ‘d’), and not identical as in (HS15).
@@
 We designed and proved Lemma 4 to address this issue, which draws its bound from the convergence guarantees of an alternating projections algorithm first proposed by von Neumann.
-This result, combined with a little known fact about the distance ‘d’ requiring proof in (M10), constitute the more sophisticated and obscure components of the deduction in eq.(26).
+This result, combined with a little known fact about the distance ‘d’ requiring proof in (M10), constitute the more sophisticated and obscure components of the deduction in Eq.
+(26).
 To reiterate, this step is completely trivial in the noiseless case and required no mention for the inductive steps taken in (HS15).
@@
 Since in this case the map \pi from supports in the hypergraph to {[m] \choose k} is not surjective, one cannot apply the same inductive method as in (HS15), which freely chooses supports in the codomain to intersect at (k-1) nodes and map back to some corresponding (k-1)-sized intersection of supports in the domain.
-Instead, we demonstrate the surprising fact that by pigeonholing the images of supports in the (SIP-satisfying) hypergraph H one can still guarantee a bijection between the nodes and therefore the subspaces spanned by individual dictionary elements.
+Instead, we demonstrate the surprising fact that by pigeonholing the images of supports in the (SIP-satisfying) hypergraph H, one can still guarantee a bijection between the nodes and therefore the subspaces spanned by individual dictionary elements.
 We note that it was necessary to forgo inductive methods altogether in order to prove this fact for all hypergraphs satisfying the SIP; otherwise, we would require that the supports in the hypergraph have intersections of size k’ for every k’ < k (e.g.
@@
 This point was only hinted at in the Discussion section of our original submission, but we have included it in the updated manuscript to make clear the power of our approach over that taken in (HS15).
-We are aware of only one work treating combinatorial hypergraph designs in the setting of dictionary learning, "An incidence geometry approach to dictionary learning" (arxiv, non-published paper)
+We are aware of only one work treating combinatorial hypergraph designs in the setting of dictionary learning, "An incidence geometry approach to dictionary learning" (arxiv, non-published paper).
 
@@
 Rather, it need only be injective on the union of subspaces with supports that form sets in a hypergraph satisfying the singleton intersection property (SIP).
-(For example, consider the matrix A = [e_1, …, e_5, v] where v = e_1 + e_3 + e_5.
-and take H to be the set of all consecutive pairs of [m] arranged in cyclic order.
+(For example, consider the matrix A = [e_1,.., e_5, v] where v = e_1 + e_3 + e_5, and take H to be the set of all consecutive pairs of [m] arranged in cyclic order.
 Then A satisfies the assumptions of Thm.
@@
 
-Let A satisfy eqn [2], x_1,...,x_N be a set of k-sparse vectors, and E \subseteq \choose{[m],k}, and \bar{m} be given and satisfy the following property:
+Let A satisfy eqn [2], x_1,..,x_N be a set of k-sparse vectors, and E \subseteq \choose{[m],k}, and \bar{m} be given and satisfy the following property:
 
-For every S \in E, there exists a subset of x_1,...,x_N of at least size (k-1)\choose{\bar{m},k} with support in S. Moreover, any k vectors in this subset are linearly independent.
+For every S \in E, there exists a subset of x_1,..,x_N of at least size (k-1)\choose{\bar{m},k} with support in S. Moreover, any k vectors in this subset are linearly independent.
 
@@
 
-RESPONSE: Yes, though actually for every S \in E there are "more than" (k-1)\choose{\bar{m},k} vectors with support in S (not “at least”).
+RESPONSE: Yes, though actually for every S \in E there are "more than" (k-1)\choose{\bar{m},k} vectors with support in S (not "at least").
 Thank you for helping us to clarify our statements.
@@
 The condition on \ell is perhaps best understood as a condition on \bar m not being too large (given \ell) in order to guarantee the recovery of at least one dictionary element.
-We have updated the manuscript to reflect this, and the condition now reads “provided \bar m < \ell m / (\ell - 1)” where previously it read “provided p = \bar m − \ell( \bar m − m ) is positive”.
+We have updated the manuscript to reflect this, and the condition now reads "provided \bar m < \ell m / (\ell - 1)" where previously it read "provided p = \bar m − \ell( \bar m − m ) is positive".
 
@@
 The main point of difference between our statements about sample complexity and those of (HS15) is the assumed constraint on the underlying support set of sparse codes x_i.
-Our theory of combinatorial designs (the ‘singleton intersection property’) requires only that there be a sufficient number of x_i drawn from each support in a hypergraph satisfying the SIP, whereas the theory in (HS15) requires that a sufficient number of x_i be drawn from *every* support of size k in [m].
+Our theory of combinatorial designs (the singleton intersection property) requires only that there be a sufficient number of x_i drawn from each support in a hypergraph satisfying the SIP, whereas the theory in (HS15) requires that a sufficient number of x_i be drawn from every support of size k in [m].
 Below, we make an explicit comparison with Table I in (HS15) row by row, assuming for our results that sufficient data have been sampled from all supports in a hypergraph H satisfying the SIP:
@@
 ROW 2.
-Our result here is again |H|(k-1){m \choose k} + 1 with *certainty*, not with *almost certainty* (i.e.
+Our result here is again |H|(k-1){m \choose k} + 1 with certainty, not with almost certainty (i.e.
 probability 1) as in (HS15).
-Here the authors in (HS15) have applied probabilistic arguments to achieve an almost certain result with a sample complexity on the same order as that for which we have achieved a certain result by means of our theory of combinatorial designs.
+Here, the authors in (HS15) have applied probabilistic arguments to achieve an almost certain result with a sample complexity on the same order as that for which we have achieved a certain result by means of our theory of combinatorial designs.
 
@@
 (2) because at least one matrix does (e.g.
-our construction) and therefore, since f is analytic, the set of all those that don’t satisfy the condition has measure zero.
+our construction) and therefore, since f is analytic, the set of all those that do not satisfy the condition has measure zero.
 We have updated the manuscript to clarify this argument for our readers.

### 2017-08-19 manuscripts/PNAS/chazthm_pnas.tex
SR main manu

@@
 
-\significancestatement{Many natural signals (visual scenery, speech, EEG, etc.) lacking domain-specific formal models can nonetheless be usefully characterized as linear combinations of few elementary waveforms drawn from a large ``dictionary".
+\significancestatement{Many natural signals (visual scenery, speech, EEG, etc.) lacking domain-specific formal models can nonetheless be usefully characterized as linear combinations of few elementary waveforms drawn from a large ``dictionary''.
 We give general conditions guaranteeing when such dictionaries are uniquely and stably determined by data.
@@
 In particular, it has been shown that response properties of simple-cell neurons in mammalian visual cortex emerge from optimizing a dictionary to represent small patches of natural images \cite{Olshausen96, hurri1996image, bell1997independent, van1998independent}, a major advance in computational neuroscience.
-A curious aspect of this finding is that the latent waveforms (e.g.
-`Gabor' wavelets) estimated from data appear to be canonical \cite{donoho2001can};
+A curious aspect of this finding is that the latent waveforms (e.g., ``Gabor'' wavelets) estimated from data appear to be canonical \cite{donoho2001can};
 i.e., they are found in learned dictionaries independent of algorithm or natural image training set.
@@
 Consider now any dataset $Z$ generated as in \eqref{LinearModel} with $\eta \leq \frac{1}{2} \varepsilon(\delta_1, \delta_2)$.
-Then from the triangle inequality, it follows that any matrix $\mathbf{B}$ and $k$-sparse $\mathbf{\bar x}_1, \ldots, \mathbf{\bar x}_N \in \mathbb{R}^m$ solving Prob.~\ref{InverseProblem} are necessarily within $\delta_1, \delta_2$ of the original dictionary $\mathbf{A}$ and sparse codes $\mathbf{x}_i$.
+Then from the triangle inequality, it follows that any matrix $\mathbf{B}$ and $k$-sparse $\mathbf{\bar x}_1, \ldots, \mathbf{\bar x}_N \in \mathbb{R}^m$ solving Prob.~\ref{InverseProblem} are necessarily within $\delta_1, \delta_2$ of the original dictionary $\mathbf{A}$ and codes $\mathbf{x}_i$, respectively.
 
@@
 The \emph{lower bound} $L$ of a matrix $\mathbf{M} \in \mathbb R^{n \times m}$ is the largest $\alpha$ such that \mbox{$\|\mathbf{M}\mathbf{x}\|_2 \geq \alpha\|\mathbf{x}\|_2$} for all $\mathbf{x} \in \mathbb{R}^m$ \cite{Grcar10}.
-By compactness of the sphere, every injective linear map has nonzero lower bound; hence, if $\mathbf{M}$ satisfies \eqref{SparkCondition}, then each submatrix formed from $2k$ of its columns or less has $L > 0$.
+By compactness of the unit sphere, every injective linear map has nonzero lower bound; hence, if $\mathbf{M}$ satisfies \eqref{SparkCondition}, then each submatrix formed from $2k$ of its columns or less has $L > 0$.
 
-We generalize the  lower bound to a domain-restricted \emph{union of subspaces} model \cite{vidal2005generalized} derived from the hypergraph $\mathcal{H}$.
-Letting $\mathbf{M}_J$ denote the submatrix formed by the columns of $\mathbf{M}$ indexed by $J$ (with $\mathbf{M}_\emptyset := \mathbf{0}$), we define:
+We generalize the  lower bound to a domain-restricted \emph{union of subspaces} model \cite{vidal2005generalized} derived from a hypergraph $\mathcal{H}$.
+Letting $\mathbf{M}_J$ denote the submatrix formed by the columns of $\mathbf{M}$ indexed by $J \subseteq [m]$ (with $\mathbf{M}_\emptyset := \mathbf{0}$), we define:
 %\begin{align*} 
@@
 
-A vector $\mathbf{x}$ is said to be \emph{supported} in $S \subseteq [m]$ when $\mathbf{x} \in \text{\rm span}\{\mathbf{e}_j: j\in S\}$, where $\mathbf{e}_j$ are the standard basis in $\mathbb R^m$. 
+A vector $\mathbf{x}$ is said to be \emph{supported} in $S \subseteq [m]$ when $\mathbf{x} \in \text{\rm span}\{\mathbf{e}_j: j\in S\}$, where $\mathbf{e}_j$ are the standard column basis in $\mathbb R^m$.
 %Denote by $\mathbf{x}^J$ the subvector formed from the entries of $\mathbf{x}$ indexed by $J$. 
@@
 The following is a precise statement of our main result.
-We leave the quantity $C_1 = C_1(\mathbf{A}, \{\mathbf{x}_i\}_{i=1}^N, \mathcal{H})$ undefined until Sec.~\ref{DUT} (see \eqref{Cdef1}).
+We leave the quantity $C_1 = C_1(\mathbf{A}, \{\mathbf{x}_i\}_{i=1}^N, \mathcal{H})$ undefined until Eq.~\eqref{Cdef1}.
 
@@
 \begin{corollary}\label{DeterministicUniquenessCorollary}
-Given a regular hypergraph $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP, there are $N =  |\mathcal{H}| \left[ (k-1){m \choose k} + 1  \right]$ vectors \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} such that every matrix $\mathbf{A}$ with $L_{2k}(\mathbf{A}) > 0$ generates a dataset $Y = \{\mathbf{A}\mathbf{x}_1, \ldots, \mathbf{A}\mathbf{x}_N\}$ with a stable $k$-sparse representation in $\mathbb{R}^m$.
+Given a regular hypergraph $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP, there are $N =  |\mathcal{H}| \left[ (k-1){m \choose k} + 1  \right]$ vectors \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} such that every matrix $\mathbf{A}$ with $L_{2k}(\mathbf{A}) > 0$ generates a dataset $Y = \{\mathbf{A}\mathbf{x}_1, \ldots, \mathbf{A}\mathbf{x}_N\}$ with a stable $k$-sparse representation in $\mathbb{R}^m$ (with $\varepsilon(\delta_1,\delta_2)$ as in \eqref{epsdel}).
 \end{corollary}
@@
 \begin{theorem}\label{SLCopt}
-If the assumptions of Thm.\ref{DeterministicUniquenessTheorem} hold, only now with more than $(k-1)\left[ {\bar m \choose k} + |\mathcal{H}|k{\bar m \choose k-1}\right]$ vectors $\mathbf{x}_i$ supported in each $S \in \mathcal{H}$, then all solutions to Prob.~\ref{OptimizationProblem} necessarily satisfy recovery inequalities \eqref{Cstable} and \eqref{b-PDa} of Thm.~\ref{DeterministicUniquenessTheorem}.
+If the assumptions of Thm.\ref{DeterministicUniquenessTheorem} hold, only now with more than $(k-1)\left[ {\bar m \choose k} + |\mathcal{H}|k{\bar m \choose k-1}\right]$ vectors $\mathbf{x}_i$ supported in each $S \in \mathcal{H}$, then all solutions to Prob.~\ref{OptimizationProblem} with $\eta \leq \varepsilon / 2$ necessarily satisfy recovery inequalities \eqref{Cstable} and \eqref{b-PDa} of Thm.~\ref{DeterministicUniquenessTheorem}.
 \end{theorem}
@@
 \begin{corollary}\label{ProbabilisticCor}
-Fix $k < m$, $n \geq \min(2k, m)$, and let the entries of $\mathbf{A} \in \mathbb{R}^{n \times m}$ and $k$-sparse $\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$ be drawn independently from probability measures absolutely continuous with respect to the standard Borel measure $\mu$.
+Fix $m > k$, $n \geq \min(2k, m)$, and let the entries of $\mathbf{A} \in \mathbb{R}^{n \times m}$ and $k$-sparse $\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$ be drawn independently from probability measures absolutely continuous with respect to the standard Borel measure.
 If more than $(k-1){m \choose k}$ of the vectors $\mathbf{x}_i$ are supported in each $S \in \mathcal{H}$ for a regular $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP, then $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$ with probability one.
@@
 \begin{proposition}\label{neuroprop}
-Sparse neural population activity is recoverable from noisy random linear compression by any method that solves Prob.~\ref{DeterministicUniquenessTheorem} or \ref{SLCopt}; in particular, via biophysically plausible unsupervised sparse linear coding (e.g.
-\cite{rehnsommer2007, rozell2007neurally}).
+Sparse neural population activity is recoverable from noisy random linear compression by any method that solves Prob.~\ref{DeterministicUniquenessTheorem} or \ref{SLCopt}; in particular, via biophysically plausible unsupervised sparse linear coding (e.g., \cite{rehnsommer2007, rozell2007neurally}).
 \end{proposition}
@@
 \end{align}
-for some nonempty $J, \bar J$ of size $\bar m - r(\bar m - m)$.
+for some nonempty $J \subseteq [m], \bar J \subseteq[\bar{m}]$ of size $\bar m - r(\bar m - m)$.
 \end{lemma}
@@
 \begin{align}\label{Cdef1}
-C_1(\mathbf{A}, \{\mathbf{x}_i\}_{i=1}^N, \mathcal{H}) := \frac{ C_2(\mathbf{A}, \mathcal{H}) } { \min_{S \in \mathcal{H}} L_k(\mathbf{AX}_{I(S)}) }.
+C_1(\mathbf{A}, \{\mathbf{x}_i\}_{i=1}^N, \mathcal{H}) := \frac{ C_2(\mathbf{A}, \mathcal{H}) } { \min_{S \in \mathcal{H}} L_k(\mathbf{AX}_{I(S)}) },
 \end{align}
@@
 The pragmatic reader should note that the explicit constants $C_1$ and $C_2$ are effectively computable: the quantity $L_k$, may be computed as the smallest singular value of a certain matrix, while the quantity $\xi$ involves computing ``canonical angles'' between subspaces, which reduce again to an efficient singular value decomposition.
-There is no efficient computation of $L_k$ in general, however, since even $L_{k} > 0$ is NP-hard \cite{tillmann2014computational}; although fixing $k$ yields polynomial complexity.
+There is no efficient computation of $L_k$ in general, however, since even $L_{k} > 0$ is NP-hard \cite{tillmann2014computational}; although, fixing $k$, yields polynomial complexity.
 Moreover, calculating $C_2$ requires an exponential number of queries to $\xi$; thus, $C_1$ and $C_2$ are not computable in polynomial time.
@@
 Let $V_1, \ldots, V_k$ be subspaces of $\mathbb{R}^m$ and set $V = \cap_{i = 1}^k V_i$.
-For  $\mathbf{x} \in \mathbb{R}^m$, we have (where $r$ is given in Def.~\ref{SpecialSupportSet}):
+For  $\mathbf{x} \in \mathbb{R}^m$, we have (where $\xi$ is given in Def.~\ref{SpecialSupportSet}):
 \begin{align}\label{DTILeq}
@@
 %
-then $\bar m \geq m$, and if $\bar m < mr / (r-1)$ then the association $i \mapsto \cap \pi(\sigma(i))$ defines an injective map to $[\bar m]$ from some $J \subseteq [m]$ of size $\bar m - r(\bar m - m)$.
+then $\bar m \geq m$; and if $\bar m < mr / (r-1)$, the association $i \mapsto \cap \pi(\sigma(i))$ defines an injective map to $[\bar m]$ from some $J \subseteq [m]$ of size $\bar m - r(\bar m - m)$.
 %In particular, if $\bar m = m$ then $\pi$ is induced by a permutation on $[m]$.
@@
 If $\bar m < mr / (r-1)$ then, letting $p := \bar m - r( \bar m - m)$, we have $|T_1| = \bar m (r - 1) + p$ for positive $p$.
-By the pigeonhole principle, there must then be at least $r$ elements of $T_1$ sharing the same first index.
-By \eqref{cond}, the intersection of the set $\mathcal{G}_1$ consisting of their second indices is nonempty; hence $|\cap \mathcal{G}_1| = 1$ by $r$-regularity and the SIP.
-Since $\cap \pi(\mathcal{G}_1)$ is nonempty, applying \eqref{cond} again implies $\cap \pi(\mathcal{G}_1) = \{i_1\}$ for some $i_1 \in [m]$.
-If $p=1$ then we are done.
+By the pigeonhole principle again, there must then be at least $r$ elements of $T_1$ sharing the same first index.
+By \eqref{cond}, the intersection of the set $\mathcal{G}_1$ consisting of their second indices is nonempty; hence, $|\cap \mathcal{G}_1| = 1$ by $r$-regularity and the SIP.
+Since $\cap \pi(\mathcal{G}_1)$ is nonempty, applying \eqref{cond} again gives $\cap \pi(\mathcal{G}_1) = \{i_1\}$ for some $i_1 \in [m]$.
+If $p=1$, then we are done.
 Otherwise, define $T_2 := T_1 \setminus \{(i,S) \in T_1: i = i_1\}$, which contains $|T_2| = |T_1| - r = (\bar m - 1)(r-1) + (p-1)$ ordered pairs having $\bar m - 1$ distinct first indices.
@@
 Since $|S| = |\pi(S)|$, the required fact follows.
-Note that $\mathbf{B}_{\pi(S)}$ therefore has full column-rank, for all $S \in \mathcal{H}$.
+Note that $\mathbf{B}_{\pi(S)}$ therefore has full column-rank for all $S \in \mathcal{H}$.
 

### 2017-08-20 manuscripts/PNAS/chazthm_pnas.tex
edits

--- 2017-08-18 manuscripts/PNAS/chazthm_pnas.tex
@@
 %
-where we write $L_{k}$ when $\mathcal{H} = {[m] \choose k}$.\footnote{We note that $1 - \sqrt{k} L_k(\mathbf{M})$ is known as the asymmetric lower restricted isometry constant \cite{Blanchard2011}.} Clearly, for any $\mathbf{M}$ satisfying \eqref{SparkCondition}, we have $L_{k'}(\mathbf{M}) > 0$ for  $k' \leq 2k$.
-Note that if $\mathcal{H}$ \textit{covers} $[m]$ (i.e., $\cup \mathcal{H} = [m]$), then $L_2 \geq L_{2\mathcal{H}}$.
+where we write $L_{k}$ when $\mathcal{H} = {[m] \choose k}$.\footnote{We note that $1 - \sqrt{k} L_k(\mathbf{M})$ is known as the asymmetric lower restricted isometry constant for matrices $\mathbf{M}$ with unit $\ell_2$-norm columns \cite{Blanchard2011}.} Clearly, for any $\mathbf{M}$ satisfying \eqref{SparkCondition}, we have $L_{k'}(\mathbf{M}) > 0$ for  $k' \leq 2k$.
+Note that if $\mathcal{H} \subseteq {[m] \choose k}$ has $\cup \mathcal{H} = [m]$, then $L_2 \geq L_{2\mathcal{H}} \geq L_{2k}$.
 
@@
 \begin{align}\label{delrho}
-L_{2\mathcal{H}}(\mathbf{A}) %\leq \frac{\|\mathbf{A}\mathbf{x}\|_2}{\sqrt{2k} \|\mathbf{x}\|_2} 
+L_2(\mathbf{A}) %\leq \frac{\|\mathbf{A}\mathbf{x}\|_2}{\sqrt{2k} \|\mathbf{x}\|_2} 
 \leq  \max_j\|\mathbf{A}_j\|_2.

### 2017-08-20 manuscripts/PNAS/chazthm_pnas.tex
6 pages again

@@
 Another practical implication of Thm.\ref{DeterministicUniquenessTheorem} is the following: there is an effective procedure sufficient to affirm if a proposed solution to Prob.~\ref{InverseProblem} is indeed unique (up to noise and inherent ambiguities).
-One simply checks that the matrix and codes satisfy the respective (computable) assumptions of Thm.~\ref{DeterministicUniquenessTheorem} on $\mathbf{A}$ and the $\mathbf{x}_i$.
+Simply check that the matrix and codes satisfy the (computable) assumptions of Thm.~\ref{DeterministicUniquenessTheorem} on $\mathbf{A}$ and the $\mathbf{x}_i$.
 %Another practical implication of Thm.\ref{DeterministicUniquenessTheorem} is the following: there is an effective procedure sufficient to affirm if a proposed solution $(\mathbf{B}, \mathbf{\bar x}_1, \ldots, \mathbf{x}_N)$ to Prob.~\ref{InverseProblem} is indeed unique (up to noise and inherent ambiguities).
@@
 
-We note the following facts about $d$. For subspaces $U \subseteq U', V \subseteq \mathbb{R}^m$, we have $d(U,V) \leq d(U',V)$ and \cite[Ch.~4 Cor.~2.6]{Kato2013}: %Kato p.223
+We note the following facts. For subspaces $U \subseteq U', V \subseteq \mathbb{R}^m$, we have $d(U,V) \leq d(U',V)$ and \cite[Ch.~4 Cor.~2.6]{Kato2013}: %Kato p.223
 \begin{align}\label{dimLem}

### 2017-08-20 manuscripts/PNAS/chazthm_pnas.tex
sml updates

@@
 
-If for some  $\mathbf{B} \in \mathbb{R}^{n \times \bar m}$ and map $\pi: E \mapsto {[\bar m] \choose k}$ we have:
+If for some  $\mathbf{B} \in \mathbb{R}^{n \times \bar m}$ and map $\pi: E \mapsto {[\bar m] \choose k}$, we have:
 \begin{align}\label{GapUpperBound}
-d(\bm{\mathcal{A}}_S, \bm{\mathcal{B}}_{\pi(S)}) \leq \varepsilon, \ \  \text{for $S \in \mathcal{H}$},
+d(\bm{\mathcal{A}}_S, \bm{\mathcal{B}}_{\pi(S)}) \leq \varepsilon, \ \  \text{for $S \in \mathcal{H}$};
 \end{align}
-then $\bar m \geq m$, and provided $\bar m < mr /(r-1)$, there is a permutation matrix $\mathbf{P}$ and invertible diagonal $\mathbf{D}$ such that:
+then $\bar m \geq m$, and, provided $\bar m < mr /(r-1)$, there is a permutation matrix $\mathbf{P}$ and invertible diagonal $\mathbf{D}$ such that:
 \begin{align}\label{MainLemmaBPD}
@@
 There is no efficient computation of $L_k$ in general, however, since even $L_{k} > 0$ is NP-hard \cite{tillmann2014computational}; although, fixing $k$, yields polynomial complexity.
-Moreover, calculating $C_2$ requires an exponential number of queries to $\xi$; thus, $C_1$ and $C_2$ are not computable in polynomial time.
+Moreover, calculating $C_2$ requires an exponential number of queries to $\xi$; thus, as presented, $C_1$ and $C_2$ are not efficiently computable.
 
@@
 By \eqref{eqn}, no more than $|\mathcal{H}|k(k-1){ \bar m \choose k-1}$ vectors $\mathbf{\bar x}_i$ are not $k$-sparse.
-Since for every $S \in \mathcal{H}$ there are over $(k-1)\left[ {\bar m \choose k} + |\mathcal{H}|k{ \bar m \choose k-1} \right]$ vectors $\mathbf{x}_i$ supported there, it follows that more than $(k-1){\bar m \choose k}$ of them have corresponding $\mathbf{\bar x}_i$ that are $k$-sparse.
+Since for every $S \in \mathcal{H}$ there are over $(k-1)\left[ {\bar m \choose k} + |\mathcal{H}|k{ \bar m \choose k-1} \right]$ vectors $\mathbf{x}_i$ supported there, it must be that more than $(k-1){\bar m \choose k}$ of them have corresponding $\mathbf{\bar x}_i$ that are $k$-sparse.
 The result now follows from Thm.~\ref{DeterministicUniquenessCorollary}.
@@
 Specifically, we have shown that, given sufficient data, the problem of seeking a dictionary and sparse codes with minimal average support size (Prob.~\ref{OptimizationProblem}) reduces to an instance of Prob.~\ref{InverseProblem}, to which our main result (Thm.~\ref{DeterministicUniquenessTheorem}) applies: every dictionary and sparse codes consistent with the data are equivalent up to inherent relabeling/scaling ambiguities and a discrepancy (error) that scales linearly with the measurement noise or modeling inaccuracy.
-The constants we provide are explicit and computable; as such, there is an effective procedure that affirms if a proposed solution to Probs.~\ref{DeterministicUniquenessTheorem} or \ref{OptimizationProblem} is indeed unique up to noise and inherent ambiguities.
+The constants we provide are explicit and computable; as such, there is an effective procedure that sufficiently affirms if a proposed solution to Probs.~\ref{DeterministicUniquenessTheorem} or \ref{OptimizationProblem} is indeed unique up to noise and inherent ambiguities.
 
@@
 
-In fact, uniqueness guarantees with minimal assumptions apply to all areas of data science and engineering utilizing learned sparse structure.
+In fact, uniqueness guarantees with minimal assumptions apply to all areas of data science and engineering that utilize learned sparse structure.
 For example, several groups have applied compressed sensing to signal processing tasks: MRI analysis \cite{lustig2008compressed}, image compression \cite{Duarte08}, and, more recently, the design of an ultrafast camera \cite{Gao14}.
@@
 %
-then $\bar m \geq m$; and if $\bar m < mr / (r-1)$, the association $i \mapsto \cap \pi(\sigma(i))$ defines an injective map to $[\bar m]$ from some $J \subseteq [m]$ of size $\bar m - r(\bar m - m)$.
+then $\bar m \geq m$; and if $\bar m < mr / (r-1)$, the association $i \mapsto \cap \pi(\sigma(i))$ is an injective map to $[\bar m]$ from some $J \subseteq [m]$ of size $\bar m - r(\bar m - m)$.
 %In particular, if $\bar m = m$ then $\pi$ is induced by a permutation on $[m]$.
@@
 Otherwise, define $T_2 := T_1 \setminus \{(i,S) \in T_1: i = i_1\}$, which contains $|T_2| = |T_1| - r = (\bar m - 1)(r-1) + (p-1)$ ordered pairs having $\bar m - 1$ distinct first indices.
-Reiterating the above arguments produces a (necessarily) distinct index $i_2$.
+Repeating the above arguments produces a (necessarily) distinct index $i_2$.
 Iterating the arguments $p$ times yields the set of singletons \mbox{$J = \{i_1, \ldots, i_p\} \subseteq [m]$}.

### 2017-08-20 manuscripts/PNAS/chazthm_pnas.tex
got rid of L_2 stupidness

--- 2017-08-20 manuscripts/PNAS/chazthm_pnas.tex
@@
 %
-where we write $L_{k}$ when $\mathcal{H} = {[m] \choose k}$.\footnote{We note that $1 - \sqrt{k} L_k(\mathbf{M})$ is known as the asymmetric lower restricted isometry constant for matrices $\mathbf{M}$ with unit $\ell_2$-norm columns \cite{Blanchard2011}.} Clearly, for any $\mathbf{M}$ satisfying \eqref{SparkCondition}, we have $L_{k'}(\mathbf{M}) > 0$ for  $k' \leq 2k$.
-Note that if $\mathcal{H} \subseteq {[m] \choose k}$ has $\cup \mathcal{H} = [m]$, then $L_2 \geq L_{2\mathcal{H}} \geq L_{2k}$.
+where we write $L_{k}$ when $\mathcal{H} = {[m] \choose k}$.\footnote{We note that $1 - \sqrt{k} L_k(\mathbf{M})$ is known as the asymmetric lower restricted isometry constant for matrices $\mathbf{M}$ with unit $\ell_2$-norm columns \cite{Blanchard2011}.} Clearly, $L_{k'}(\mathbf{M}) \geq L_k(\mathbf{M})$ whenever $k' \leq k$ and $L_{2k}(\mathbf{M}) > 0$ for $\mathbf{M}$ satisfying \eqref{SparkCondition}.% Note that if $\mathcal{H} \subseteq {[m] \choose k}$ has $\cup \mathcal{H} = [m]$, then $L_2 \geq L_{2\mathcal{H}} \geq L_{2k}$.
 
@@
 
-We now begin our proof of Thm.~\ref{DeterministicUniquenessTheorem} by showing how dictionary recovery \eqref{Cstable} already implies sparse code recovery \eqref{b-PDa} when \mbox{$\varepsilon < L_{2k}(\mathbf{A}) / C_1$} (provided $L_{2k}(\mathbf{A}) > 0$), temporarily assuming (without loss of generality) that $\bar m = m$.
-First, note that since $\|\mathbf{A}\mathbf{x}\|_2 \leq \max_j\|\mathbf{A}_j\|_2\|\mathbf{x}\|_1$ and $\|\mathbf{x}\|_1 \leq \sqrt{k} \|\mathbf{x}\|_2$ for $k$-sparse $\mathbf{x}$, by \eqref{Ldef} we have the following frequently applied inequality:
-\begin{align}\label{delrho}
-L_2(\mathbf{A}) %\leq \frac{\|\mathbf{A}\mathbf{x}\|_2}{\sqrt{2k} \|\mathbf{x}\|_2} 
-\leq  \max_j\|\mathbf{A}_j\|_2.
-\end{align}
+We now begin our proof of Thm.~\ref{DeterministicUniquenessTheorem} by showing how dictionary recovery \eqref{Cstable} already implies sparse code recovery \eqref{b-PDa} when \mbox{$\varepsilon < L_{2k}(\mathbf{A}) / C_1$} (provided $\mathbf{A}$ satisfies \eqref{SparkCondition}), temporarily assuming (without loss of generality) that $\bar m = m$.
 For $2k$-sparse $\mathbf{x} \in \mathbb{R}^m$, the triangle inequality gives \mbox{$\|(\mathbf{A}-\mathbf{BPD})\mathbf{x}\|_2  \leq C_1\varepsilon \|\mathbf{x}\|_1 \leq C_1 \varepsilon \sqrt{2k}  \|\mathbf{x}\|_2$}.
@@
 \end{align} 
-Note that if $\bar{c}_j = 0$, then $\|c_j\mathbf{A}_j \|_2 \leq \varepsilon$ implies from \eqref{delrho} that $|c_j| < \min_{\ell \in [m]} | c_\ell |$, a contradiction.  Thus, $\bar{c}_j \neq 0$.
+Note that $\bar{c}_j \neq 0$, since otherwise we have the contradiction $\|\mathbf{A}_j \|_2 \leq C_1 |c_j| \|\mathbf{A}_j \|_2  < L_2(\mathbf{A}) \leq L_1(\mathbf{A}) = \min_{i \in [m]} \|\mathbf{A}_i\|_2$.
+%implies by \eqref{delrho} the contradiction $|c_j| < \min_{\ell \in [m]} | c_\ell |$.
 
@@
 
-In this section, we prove Lem.~\ref{MainLemma} after stating and proving some auxiliary lemmas.% and then sketch the proofs of Thm.~\ref{robustPolythm} and Cor.~\ref{ProbabilisticCor}.
+In this section, we prove Lem.~\ref{MainLemma} after stating and proving some auxiliary lemmas. 
+%First, note that since $\|\mathbf{A}\mathbf{x}\|_2 \leq \max_j\|\mathbf{A}_j\|_2\|\mathbf{x}\|_1$ and $\|\mathbf{x}\|_1 \leq \sqrt{k} \|\mathbf{x}\|_2$ for $k$-sparse $\mathbf{x}$, by \eqref{Ldef} we have the following frequently applied inequality:
+%\begin{align}\label{delrho}
+%L_{k'}(\mathbf{A}) \leq  \max_j\|\mathbf{A}_j\|_2 \ \ \text{for all $k' \leq 2k$}.
+%\end{align}
+
+% and then sketch the proofs of Thm.~\ref{robustPolythm} and Cor.~\ref{ProbabilisticCor}.
 
@@
 We begin by showing that $\dim(\bm{\mathcal{B}}_{\pi(S)}) = \dim(\bm{\mathcal{A}}_S)$ for all $S \in \mathcal{H}$.
-Since the right-hand side of \eqref{GapUpperBound} is less than one (by \eqref{delrho} and $r \leq 1$), it follows from \eqref{dimLem} that $|\pi(S)| \geq \dim(\bm{\mathcal{B}}_{\pi(S)}) \geq \dim(\bm{\mathcal{A}}_S) = |S|$, with the equality by injectivity of $\mathbf{A}$.
+Note that since $\|\mathbf{A}\mathbf{x}\|_2 \leq \max_j\|\mathbf{A}_j\|_2\|\mathbf{x}\|_1$ and $\|\mathbf{x}\|_1 \leq \sqrt{2} \|\mathbf{x}\|_2$ for all $2$-sparse $\mathbf{x}$, by \eqref{Ldef} we have $L_2(\mathbf{A}) \leq \max_j\|\mathbf{A}_j\|_2$ and therefore (as $\xi \leq 1$), the right-hand side of \eqref{GapUpperBound} is less than one.
+It follows from \eqref{dimLem} that $|\pi(S)| \geq \dim(\bm{\mathcal{B}}_{\pi(S)}) \geq \dim(\bm{\mathcal{A}}_S) = |S|$, with the equality by injectivity of $\mathbf{A}$.
 Since $|S| = |\pi(S)|$, the required fact follows.
@@
 &\leq \frac{|\mathcal{G}| \varepsilon}{\xi( \{\bm{\mathcal{A}}_S\}_{S \in \mathcal{G}})} 
-\leq \frac{C_2 \varepsilon}{\max_i\|\mathbf{A}_i\|_2}. 
+\leq \frac{C_2 \varepsilon}{\max_j\|\mathbf{A}_j\|_2}. 
 \end{align}
 
-Since $\varepsilon < L_2(\mathbf{A}) / C_2$, by \eqref{delrho} the upper bound in \eqref{randoml} is less than one; hence, $\dim(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}) \leq \dim(\bm{\mathcal{A}}_{\cap \mathcal{G}})$ by \eqref{dimLem}, and \eqref{cond} follows from the full column-rank of $\mathbf{A}_{S}$ and $\mathbf{B}_{\pi(S)}$ for all $S \in \mathcal{G}$.
+Since $C_2 \varepsilon < L_2(\mathbf{A}) \leq \max_j\|\mathbf{A}_j\|_2$, we have by \eqref{dimLem} that $\dim(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}) \leq \dim(\bm{\mathcal{A}}_{\cap \mathcal{G}})$, and \eqref{cond} follows from the full column-rank of $\mathbf{A}_{S}$ and $\mathbf{B}_{\pi(S)}$ for all $S \in \mathcal{G}$.
 

### 2017-08-20 manuscripts/PNAS/chazthm_pnas.tex
chaz

@@
 %
-where we write $L_{k}$ when $\mathcal{H} = {[m] \choose k}$.\footnote{We note that $1 - \sqrt{k} L_k(\mathbf{M})$ is known as the asymmetric lower restricted isometry constant for matrices $\mathbf{M}$ with unit $\ell_2$-norm columns \cite{Blanchard2011}.} Clearly, $L_{k'}(\mathbf{M}) \geq L_k(\mathbf{M})$ whenever $k' \leq k$ and $L_{2k}(\mathbf{M}) > 0$ for $\mathbf{M}$ satisfying \eqref{SparkCondition}.% Note that if $\mathcal{H} \subseteq {[m] \choose k}$ has $\cup \mathcal{H} = [m]$, then $L_2 \geq L_{2\mathcal{H}} \geq L_{2k}$.
+where we write $L_{k}$ when $\mathcal{H} = {[m] \choose k}$.\footnote{We note that $1 - \sqrt{k} L_k(\mathbf{M})$ is known as the asymmetric lower restricted isometry constant for matrices $\mathbf{M}$ with unit $\ell_2$-norm columns \cite{Blanchard2011}.} Clearly, $L_{k'}(\mathbf{M}) \geq L_k(\mathbf{M})$ whenever $k' \leq k$ and $L_{2k}(\mathbf{M}) > 0$ for $\mathbf{M}$ satisfying \eqref{SparkCondition}.
+Note also that $L_2 \geq L_{2\mathcal{H}} \geq L_{2k}$ if $\mathcal{H} \subseteq {[m] \choose k}$ has $\cup \mathcal{H} = [m]$.
 
@@
 %
-where the second inequality is due to $L(\mathbf{AX}_{K}) \geq L_k(\mathbf{AX}_{I(S)})$ and \eqref{Cdef1}. Finally, apply Lem.~\ref{MainLemma} with $\varepsilon < L_2(\mathbf{A})/C_1$.
+where the second inequality is due to $L(\mathbf{AX}_{K}) \geq L_k(\mathbf{AX}_{I(S)})$ and \eqref{Cdef1}.
+Finally, apply Lem.~\ref{MainLemma} with $\varepsilon < L_2(\mathbf{A})/C_1$.
+% L_2(A) > 0 by def of L, since L_2H(A) > 0 and H covers [m]
 \end{proof}

### 2017-08-20 manuscripts/PNAS/chazthm_pnas.tex
h to sigma

@@
 %As mentioned in the previous section, Thm.~\ref{DeterministicUniquenessTheorem} is a particular case of a more general result that forgoes the assumption that $\mathcal{H} \subseteq {[m] \choose k}$ is regular and satisfies the SIP.
-If instead we require only that the stars $\cap h(i)$ intersect at singletons for all $i \leq q$ (assuming that the nodes of $\mathcal{H}$ are labeled in some order of non-increasing degree), we have that $\bar m \geq k|\mathcal{H}| / \deg(1)$ and, provided $\bar m < k|\mathcal{H}| / (\deg(1) - 1)$, the nonempty submatrix $J$ is of size equal to the largest number $p$ satisfying:
+If instead we require only that the stars $\cap \sigma(i)$ intersect at singletons for all $i \leq q$ (assuming that the nodes of $\mathcal{H}$ are labeled in some order of non-increasing degree), we have that $\bar m \geq k|\mathcal{H}| / \deg(1)$ and, provided $\bar m < k|\mathcal{H}| / (\deg(1) - 1)$, the nonempty submatrix $J$ is of size equal to the largest number $p$ satisfying:
 %\begin{align}\label{pcond}
@@
 
-Now, by Lem.~\ref{NonEmptyLemma}, the association $i \mapsto \cap \pi(h(i))$ defines an injective map $\bar \pi: J \to [\bar m]$ for some $J \subseteq [m]$ of size $\bar m - r(\bar m - m)$, and we can be sure that $\mathbf{B}_{\bar \pi(i)} \neq \mathbf{0}$ for all $i \in J$ since the columns of $\mathbf{B}_{\pi(S)}$ are linearly independent for all $S \in \mathcal{H}$.
+Now, by Lem.~\ref{NonEmptyLemma}, the association $i \mapsto \cap \pi(\sigma(i))$ defines an injective map $\bar \pi: J \to [\bar m]$ for some $J \subseteq [m]$ of size $\bar m - r(\bar m - m)$, and we can be sure that $\mathbf{B}_{\bar \pi(i)} \neq \mathbf{0}$ for all $i \in J$ since the columns of $\mathbf{B}_{\pi(S)}$ are linearly independent for all $S \in \mathcal{H}$.
 It then follows from \eqref{eqdim} and \eqref{randoml} that $d\left( \bm{\mathcal{A}}_i, \bm{\mathcal{B}}_{\bar \pi(i)} \right) \leq C_2 \varepsilon / \max_i \|\mathbf{A}_i\|_2$ for all $i \in J$.

### 2017-08-20 manuscripts/PNAS/chazthm_pnas.tex
chaz

@@
 %
-where we write $L_{k}$ when $\mathcal{H} = {[m] \choose k}$.\footnote{We note that $1 - \sqrt{k} L_k(\mathbf{M})$ is known as the asymmetric lower restricted isometry constant for matrices $\mathbf{M}$ with unit $\ell_2$-norm columns \cite{Blanchard2011}.} Clearly, $L_{k'}(\mathbf{M}) \geq L_k(\mathbf{M})$ whenever $k' \leq k$ and $L_{2k}(\mathbf{M}) > 0$ for $\mathbf{M}$ satisfying \eqref{SparkCondition}.
+where we write $L_{k}$ when $\mathcal{H} = {[m] \choose k}$.\footnote{We note that $1 - \sqrt{k} L_k(\mathbf{M})$ is known as the asymmetric lower restricted isometry constant for matrices $\mathbf{M}$ with unit $\ell_2$-norm columns \cite{Blanchard2011}.} Clearly, $L_{2k}(\mathbf{M}) > 0$ for $\mathbf{M}$ satisfying \eqref{SparkCondition} and $L_{k'}(\mathbf{M}) \geq L_k(\mathbf{M})$ whenever $k' \leq k$.
 Note also that $L_2 \geq L_{2\mathcal{H}} \geq L_{2k}$ if $\mathcal{H} \subseteq {[m] \choose k}$ has $\cup \mathcal{H} = [m]$.

### 2017-08-21 manuscripts/PNAS/review/point_by_point_response.txt
chaz

@@
 That being said, the paper (with the modifications below) would certainly merit publication in very solid journal like IEEE Transactions on Information Theory, where it would be a median paper, in my opinion.
+
+[ ** but we haven’t discussed tightness of constants eps given delta_1, delta_2 in the manuscript… ** ]
 -----------------
@@
 
-As per the reviewer’s request, we have included in our updated manuscript a discussion of the computability of the sufficient conditions (they are, indeed, computable.
-The main constants in our work -- C_1, C_2 -- are computable, elementarily, in terms of two positive quantities that are natural in our context: (a) the restricted "Lower Bound" L_k(M) of a matrix M, which is a measure of how distinguishable two k-sparse x’s are by their images under M, and (b) the value in Def.
+As per the reviewer’s request, we have included in our updated manuscript a discussion of the computability of the sufficient conditions (they are, indeed, computable).
+The main constants in our work -- C_1, C_2 -- are computable, elementarily, in terms of two positive quantities that are natural in our context: (a) the restricted "Lower Bound" L_k(M) of a matrix M, which is a measure of how distinguishable two (k/2)-sparse x’s are by their images under M, and (b) the value in Def.
 4 of \xi(V_1,..,V_l) given subspaces V_i spanned by columns of A, which bounds the distance between intersections of such subspaces and each subspace individually.
@@
 
+[ ** we good on the paragraph below..? ** ]
+
 We next respond to the reviewer's question about the mathematical "tightness" for the three types of quantities in our results : (a) required coding error eps(delta_1, delta_2) sufficient to guarantee uniqueness in terms of desired dictionary delta_1 and sparse representation error delta_2, (b) the constants C_1 and C_2 involved in our sufficient linear bound on eps(delta_1, delta_2) in terms of the noise, and (c) the number of sufficient samples N guaranteeing uniqueness.
@@
 Finally, with respect to (c), we regard this as a fundamental open problem in the field: how many sparsely generated samples determine the linear coding model?
-(One reason to be skeptical that a polynomial suffice is again (TP14, T15).)  However, there is some good news -- if k is fixed and we constrain sparse codes \hat{x}_i to come from a polynomial number of supports, then a polynomial number of samples N is enough to guarantee uniqueness.
-In particular, a sample complexity polynomial in (m,k) can be achieved by limiting the size of the support set of the \tilde x_i, and we have revised the manuscript to discuss this fact (which, incidentally, does not follow from the results of (HS15) in the noiseless case).
+(One reason to be skeptical that a polynomial suffice is again (TP14, T15).)  However, there is some good news -- if k is fixed or if the sparse codes \bar x_i are known to come from a polynomial number of supports, then a polynomial number of samples N is enough to guarantee uniqueness.
+We have revised the manuscript to discuss this last fact (which, incidentally, does not follow from the results of (HS15) in the noiseless case).
 
@@
 We have updated the manuscript with an explicit statement of this fact, and outline one such procedure here:
+
+[ ** go through the algorithm below again *** ]
 
@@
 
+[ ** sophisticated and obscure above or should we just say obscure? ** ]
+
 Our proof of Lemma 1 diverges perhaps even more significantly from the approach taken in (HS15) by way of Lemma 5.
@@
 Moreover, if the size of the support set of reconstructing codes is known to be polynomial in m and k, then the pigeonholing argument in the proof of Thm.
-1 requires only a polynomial number of samples distributed over a polynomial number of supports; thus, N is polynomial in m, k.
+1 requires only a polynomial number of samples distributed over a polynomial number of supports; thus, N is then polynomial in \bar m, k.
 This point was only hinted at in the Discussion section of our original submission, but we have included it in the updated manuscript to make clear the power of our approach over that taken in (HS15).
 We are aware of only one work treating combinatorial hypergraph designs in the setting of dictionary learning, "An incidence geometry approach to dictionary learning" (arxiv, non-published paper).
+
+[ ** should we say exactly what the above paper does so that they don’t think we’ve repeated them or anything..? ** ]
 
@@
 We have updated the manuscript to reflect this, and the condition now reads "provided \bar m < \ell m / (\ell - 1)" where previously it read "provided p = \bar m − \ell( \bar m − m ) is positive".
+(Note: in the resubmitted manuscript, we have actually opted to use r instead of \ell for the regularity of the hypergraph.)
 
@@
 The main point of difference between our statements about sample complexity and those of (HS15) is the assumed constraint on the underlying support set of sparse codes x_i.
-Our theory of combinatorial designs (the singleton intersection property) requires only that there be a sufficient number of x_i drawn from each support in a hypergraph satisfying the SIP, whereas the theory in (HS15) requires that a sufficient number of x_i be drawn from every support of size k in [m].
+Our theory of combinatorial designs (the “singleton intersection property”) requires only that there be a sufficient number of x_i drawn from each support in a hypergraph satisfying the SIP, whereas the theory in (HS15) requires that a sufficient number of x_i be drawn from every support of size k in [m].
 Below, we make an explicit comparison with Table I in (HS15) row by row, assuming for our results that sufficient data have been sampled from all supports in a hypergraph H satisfying the SIP:
@@
 We have opted not to include these calculations due in part to space constraints, but also because we believe that what sets our work apart from the vast majority of results in the field is their deterministic nature, e.g.
-they do not depend on any kind of assumption about the random distribution from which the sparse coefficients or dictionary entries are drawn.
+they do not depend on any kind of assumption about the particular random distribution from which the sparse coefficients or dictionary entries are drawn.
 

### 2017-08-21 manuscripts/PNAS/chazthm_pnas.tex
chaz

@@
 % TODO %
+% Mention computability of eps(d1,d2) in terms of C1?
 % *** Put ell1 norm into the denominator of L_k *** ?
@@
 Fix an $n \times m$ matrix $\mathbf{A}$ with $L_{2\mathcal{H}}(\mathbf{A}) > 0$ for an $r$-regular $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP.
-If \mbox{$\{\mathbf{x}_1, \ldots, \mathbf{x}_N\} \subset \mathbb{R}^m$} contains, for each $S \in \mathcal{H}$, more than $(k-1){m \choose k}$ $k$-sparse vectors in general linear position supported in $S$, then there is $C_1 > 0$ with the following holding for all\footnote{The condition $\varepsilon < L_2(\mathbf{A}) /C_1$ is necessary; otherwise,  with \mbox{$\mathbf{A}$ = $\mathbf{I}$} and $\mathbf{x}_i = \mathbf{e}_i$, there is a matrix $\mathbf{B}$ and $1$-sparse $\mathbf{\bar{x}}_i$ with $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\bar{x}}_i \|_2 \leq \varepsilon$ that nonetheless violates \eqref{Cstable}.} $\varepsilon < L_{2}(\mathbf{A}) / C_1$:
+If \mbox{$\{\mathbf{x}_1, \ldots, \mathbf{x}_N\} \subset \mathbb{R}^m$} contains, for each $S \in \mathcal{H}$, more than $(k-1){m \choose k}$ $k$-sparse vectors in general linear position supported in $S$, then there is $C_1 > 0$ with the following holding for all%\footnote{The condition $\varepsilon < L_2(\mathbf{A}) /C_1$ is necessary; otherwise,  with \mbox{$\mathbf{A}$ = $\mathbf{I}$} and $\mathbf{x}_i = \mathbf{e}_i$, there is a matrix $\mathbf{B}$ and $1$-sparse $\mathbf{\bar{x}}_i$ with $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\bar{x}}_i \|_2 \leq \varepsilon$ that nonetheless violates \eqref{Cstable}.} $\varepsilon < L_{2}(\mathbf{A}) / C_1$:
+\footnote{The condition $\varepsilon < L_2(\mathbf{A}) /C_1$ is necessary; otherwise, with \mbox{$\mathbf{A}$ = $\mathbf{I}$} and $\mathbf{x}_i = \mathbf{e}_i$, the matrix $\mathbf{B} = \left[\mathbf{0}, \frac{1}{2}(\mathbf{e}_1 + \mathbf{e}_2), \mathbf{e}_3, \ldots, \mathbf{e}_{m} \right]$ and 1-sparse codes $\mathbf{\bar x}_i = \mathbf{e}_2$ for $i = 1, 2$ and $\mathbf{\bar x}_i = \mathbf{e}_i$ for $i \geq 3$ satisfy $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\bar{x}}_i \|_2 \leq \varepsilon$ but nonetheless violate \eqref{Cstable}.} $\varepsilon < L_{2}(\mathbf{A}) / C_1$:
 
@@
 Note that sparse codes $\mathbf{x}_i$ with a shared support that are in general linear position are straightforward to produce using a ``Vandermonde'' matrix construction (i.e., use the columns of the matrix $[\gamma_{i}^j]_{i,j=1}^{k,N}$, for distinct nonzero $\gamma_i$).
-Thus, the assumptions of Thm.~\ref{DeterministicUniquenessTheorem} are easily met, leading to the following direct application to uniqueness in dictionary learning, Prob.~\ref{InverseProblem}.
+Thus, the assumptions of Thm.~\ref{DeterministicUniquenessTheorem} are easily met, leading to the following direct application to uniqueness in sparse linear coding.
+% (Prob.~\ref{InverseProblem}).
 %=======

### 2017-08-21 manuscripts/PNAS/chazthm_pnas.tex
sml edits fixed rozell ref

@@
 for $k$-\emph{sparse} $\mathbf{x}_i \in \mathbb{R}^m$ having at most $k$ nonzero entries and \emph{noise} $\mathbf{n}_i \in \mathbb{R}^n$, with bounded norm $\| \mathbf{n}_i \|_2 \leq  \eta$ representing our combined worst-case uncertainty in  measuring $\mathbf{A}\mathbf{x}_i$.
-The first mathematical problem addressed here is the following.
+The first mathematical problem we address is the following.
 
@@
 \begin{align}\label{Ldef}
-L_\mathcal{H}(\mathbf{M}) := \frac{1}{\sqrt{k}} \inf \left\{ \frac{\|\mathbf{M}_S\mathbf{x}\|_2}{ \|\mathbf{x}\|_2} : S \in \mathcal{H}, \ \ \mathbf{x} \in \mathbb{R}^{|S|} \right\},
+L_\mathcal{H}(\mathbf{M}) := \frac{1}{\sqrt{k}} \min \left\{ \frac{\|\mathbf{M}_S\mathbf{x}\|_2}{ \|\mathbf{x}\|_2} : S \in \mathcal{H}, \ \ \mathbf{x} \in \mathbb{R}^{|S|} \right\},
 \end{align} 
@@
 
-A vector $\mathbf{x}$ is said to be \emph{supported} in $S \subseteq [m]$ when $\mathbf{x} \in \text{\rm span}\{\mathbf{e}_j: j\in S\}$, where $\mathbf{e}_j$ are the standard column basis in $\mathbb R^m$.
+A vector $\mathbf{x}$ is said to be \emph{supported} in $S \subseteq [m]$ when $\mathbf{x} \in \text{\rm span}\{\mathbf{e}_j: j\in S\}$, where $\mathbf{e}_j$ form the standard column basis in $\mathbb R^m$.
 %Denote by $\mathbf{x}^J$ the subvector formed from the entries of $\mathbf{x}$ indexed by $J$. 
@@
 Repeating the above arguments produces a (necessarily) distinct index $i_2$.
-Iterating the arguments $p$ times yields the set of singletons \mbox{$J = \{i_1, \ldots, i_p\} \subseteq [m]$}.
+Iterating this $p$ times yields the set of singletons \mbox{$J = \{i_1, \ldots, i_p\} \subseteq [m]$}.
 \end{proof}

### 2017-08-21 manuscripts/PNAS/chazthm_pnas.tex
chaz

@@
 By \eqref{cond}, the intersection of the set $\mathcal{G}_1$ consisting of their second indices is nonempty; hence, $|\cap \mathcal{G}_1| = 1$ by $r$-regularity and the SIP.
-Since $\cap \pi(\mathcal{G}_1)$ is nonempty, applying \eqref{cond} again gives $\cap \pi(\mathcal{G}_1) = \{i_1\}$ for some $i_1 \in [m]$.
+Since $\cap \pi(\mathcal{G}_1)$ is nonempty, applying \eqref{cond} again gives $\cap \pi(\mathcal{G}_1) = \{i_1\}$ for some $i_1 \in [\bar m]$.
 If $p=1$, then we are done.
@@
 Repeating the above arguments produces a (necessarily) distinct index $i_2$.
-Iterating this $p$ times yields the set of singletons \mbox{$J = \{i_1, \ldots, i_p\} \subseteq [m]$}.
+Iterating the arguments $p$ times yields the set of singletons \mbox{$\bar J = \{i_1, \ldots, i_p\} \subseteq [\bar m]$}.
 \end{proof}

### 2017-08-21 manuscripts/PNAS/review/point_by_point_response.txt
added linear optimality ref

@@
 (IHS10) Isely, Hillar, Sommer, Advances in neural information processing systems (NIPS), 2010.
+(M10) Morris I (2010), Advances in Mathematics 225(6):3425–3445.
 (GS12) Ganguli, Sompolinksi, Annual review of neuroscience, 2012.
+(ACD13) Arias-Castro, Candes, Davenport, IEEE Trans. Inf. Theory, 2013
 (TP14) Tillman, Pfetsch, IEEE Transactions on information processing, 2014.
@@
 (HS15) Hillar, Sommer, IEEE Transactions on information processing, 2015.
-(M10) Morris I (2010), Advances in Mathematics 225(6):3425–3445.
 
@@
 That being said, the paper (with the modifications below) would certainly merit publication in very solid journal like IEEE Transactions on Information Theory, where it would be a median paper, in my opinion.
-
-[ ** but we haven’t discussed tightness of constants eps given delta_1, delta_2 in the manuscript… ** ]
 -----------------
@@
 
-[ ** we good on the paragraph below..? ** ]
-
 We next respond to the reviewer's question about the mathematical "tightness" for the three types of quantities in our results : (a) required coding error eps(delta_1, delta_2) sufficient to guarantee uniqueness in terms of desired dictionary delta_1 and sparse representation error delta_2, (b) the constants C_1 and C_2 involved in our sufficient linear bound on eps(delta_1, delta_2) in terms of the noise, and (c) the number of sufficient samples N guaranteeing uniqueness.
-With respect to (a), even with fixed dictionary, the recovery of sparse representations up to an error that is linear in the noise is classically optimal (up to constants).
+With respect to (a), even with fixed dictionary, the recovery of sparse representations up to an error that is linear in the noise is essentially optimal (ACD13) (up to constants).
 Thus, the fact that we have a sufficient error in coding for uniqueness being linear for both the desired dictionary and sparse vector recovery error is optimal.
@@
 We designed and proved Lemma 4 to address this issue, which draws its bound from the convergence guarantees of an alternating projections algorithm first proposed by von Neumann.
-This result, combined with a little known fact about the distance ‘d’ requiring proof in (M10), constitute the more sophisticated and obscure components of the deduction in Eq.
+This result, combined with a little known fact about the distance ‘d’ requiring proof in (M10), constitute the more obscure components of the deduction in Eq.
 (26).
 To reiterate, this step is completely trivial in the noiseless case and required no mention for the inductive steps taken in (HS15).
-
-[ ** sophisticated and obscure above or should we just say obscure? ** ]
 
@@
 This point was only hinted at in the Discussion section of our original submission, but we have included it in the updated manuscript to make clear the power of our approach over that taken in (HS15).
-We are aware of only one work treating combinatorial hypergraph designs in the setting of dictionary learning, "An incidence geometry approach to dictionary learning" (arxiv, non-published paper).
-
-[ ** should we say exactly what the above paper does so that they don’t think we’ve repeated them or anything..? ** ]
 

### 2017-08-21 manuscripts/PNAS/chazthm_pnas.tex
added linear optimality ref

--- 2017-08-21 manuscripts/PNAS/chazthm_pnas.tex
@@
 
-We close this section with a comment on sample complexity.
-A basic open problem remains: how many samples are necessary to determine the sparse linear coding model?
+We close this section with comments on optimality.
+Our linear scaling for $\varepsilon$ in \eqref{epsdel} is essentially optimal (e.g., see \cite{arias2013fundamental}), but a basic open problem remains: how many samples are necessary to determine the sparse linear coding model?
 If $k$ is held fixed or if the size of the support set of reconstructing codes is known to be polynomial in $\bar m$ and $k$, then a practical (polynomial) amount of data suffices.\footnote{In the latter case, a reexamination of the pigeonholing argument in the proof of Thm.~\ref{DeterministicUniquenessTheorem} requires a polynomial number of samples distributed over a polynomial number of supports.} Reasons to be skeptical that this holds in general, however, can be found in \cite{tillmann2014computational, Tillmann15}.
@@
 Given such effective uses of compressed sensing, it is only a matter of time before these systems incorporate dictionary learning to encode and process data (e.g., in a device that learns structure from motion \cite{kong2016prior}).
-In these cases, assurances such as those offered by our theorems certify that different devices (with different initialization, samples, etc.) will learn equivalent representations given enough data from statistically identical systems.\footnote{To contrast with the current hot topic of ``Deep Learning'', there are few such uniqueness guarantees for these multi-layer feedforward models of data; moreover, there is evidence that even minuscule amounts of (``adversarial'') signal noise can dramatically alter their output \cite{goodfellow2014explaining}.} Indeed, it seems a main reason for the sustained interest in dictionary learning as an unsupervised method for data analysis appears to be the assumed well-posedness of parameter identification in the sparse linear coding model, confirmation of which forms the core of our theoretical findings.
+Assurances such as those offered by our theorems certify that different devices (with different initialization, samples, etc.) will learn equivalent representations given enough data from statistically identical systems.\footnote{To contrast with the current hot topic of ``Deep Learning'', there are few such uniqueness guarantees for these multi-layer feedforward models of data; moreover, there is evidence that even minuscule amounts of (``adversarial'') signal noise can dramatically alter their output \cite{goodfellow2014explaining}.} Indeed, it seems a main reason for the sustained interest in dictionary learning as an unsupervised method for data analysis is the assumed well-posedness of parameter identification in the sparse linear coding model, confirmation of which forms the core of our theoretical findings.
 
@@
 
-In this section, we prove Lem.~\ref{MainLemma} after stating and proving some auxiliary lemmas. 
+In this section, we prove Lem.~\ref{MainLemma} and some auxiliary lemmas.  % stating and proving some auxiliary lemmas. 
 %First, note that since $\|\mathbf{A}\mathbf{x}\|_2 \leq \max_j\|\mathbf{A}_j\|_2\|\mathbf{x}\|_1$ and $\|\mathbf{x}\|_1 \leq \sqrt{k} \|\mathbf{x}\|_2$ for $k$-sparse $\mathbf{x}$, by \eqref{Ldef} we have the following frequently applied inequality:

### 2017-08-21 manuscripts/PNAS/review/point_by_point_response.txt
pnt by pnt updates

@@
 
-It is true, however, that we have not proven the tightness of these conditions and the manuscript is therefore not conclusive regarding the central problems of sparse linear coding.
-We believe that these sufficient conditions yield strong enough conclusions to stand on their own; for instance, in synchronizing device parameters for a particular sparsely representable sensory ensemble.
+It is true, however, that we have not determined the tightest conditions regarding the constants and sample size necessary for uniqueness in sparse linear coding.
+However, we believe that these sufficient conditions yield strong enough conclusions to stand on their own; for instance, in synchronizing device parameters for a particular sparsely representable sensory ensemble.
 
@@
 We have updated the manuscript with an explicit statement of this fact, and outline one such procedure here:
-
-[ ** go through the algorithm below again *** ]
 

### 2017-08-21 manuscripts/PNAS/review/point_by_point_response.txt
chaz

--- 2017-08-21 manuscripts/PNAS/review/point_by_point_response.txt
@@
 
-[ ** but we haven’t discussed tightness of constants eps given delta_1, delta_2 in the manuscript… ** ]
 -----------------
@@
 Thus, while our constants are effective (an algorithm exists to compute them), they are not necessarily polynomial-time computable.
-
-[ ** we good on the paragraph below..? ** ]
-
+1
 We next respond to the reviewer's question about the mathematical "tightness" for the three types of quantities in our results : (a) required coding error eps(delta_1, delta_2) sufficient to guarantee uniqueness in terms of desired dictionary delta_1 and sparse representation error delta_2, (b) the constants C_1 and C_2 involved in our sufficient linear bound on eps(delta_1, delta_2) in terms of the noise, and (c) the number of sufficient samples N guaranteeing uniqueness.
@@
 
-[ ** go through the algorithm below again *** ]
-
 Given a dictionary A and codes x_i that solve Problem 1 (e.g. learned by any algorithm), check that that they satisfy the assumptions of Thm. 1:
@@
 To reiterate, this step is completely trivial in the noiseless case and required no mention for the inductive steps taken in (HS15).
-
-[ ** sophisticated and obscure above or should we just say obscure? ** ]
 

### 2017-08-21 manuscripts/PNAS/chazthm_pnas.tex
chaz

--- 2017-08-21 manuscripts/PNAS/chazthm_pnas.tex
@@
 % TODO %
+% bar J in Lem 4?
 % Mention computability of eps(d1,d2) in terms of C1?
@@
 Otherwise, define $T_2 := T_1 \setminus \{(i,S) \in T_1: i = i_1\}$, which contains $|T_2| = |T_1| - r = (\bar m - 1)(r-1) + (p-1)$ ordered pairs having $\bar m - 1$ distinct first indices.
-Repeating the above arguments produces a (necessarily) distinct index $i_2$.
-Iterating the arguments $p$ times yields the set of singletons \mbox{$\bar J = \{i_1, \ldots, i_p\} \subseteq [\bar m]$}.
+Repeating the above arguments produces a (necessarily, by $r$-regularity and the SIP) distinct $\mathcal{G}_2 \subseteq \mathcal{H}$ and corresponding $i_2 \in [\bar m]$.
+Iterating the arguments $p$ times yields the set of singletons \mbox{$J = \{\cap \mathcal{G}_1, \ldots, \cap \mathcal{G}_p\} \subseteq [m]$}.
 \end{proof}

### 2017-08-21 manuscripts/PNAS/chazthm_pnas.tex
back to 6 pages

@@
 \end{align*}
-\vspace{-.2 cm}
+%\vspace{-.2 cm}
 \end{proof}
@@
 
-An immediate application of our theoretical work is Prop.~\ref{neuroprop}, which certifies the validity of perhaps the only published theory of neurally-plausible bottleneck communication in the brain: that sparse linear coding in a compressed space of neural activity can recover sparse codes sent through a randomly-constructed (but unknown) noisy wiring bottleneck \cite{Isely10}.\footnote{We refer the reader to \cite{ganguli2012compressed} for a discussion of this application's significance and more on the interactions between sparse linear coding and neuroscience.}
+An immediate application of our theoretical work is Prop.~\ref{neuroprop}, which certifies the validity of perhaps the only published theory of neurally-plausible bottleneck communication in the brain: that sparse linear coding in a compressed space of neural activity can recover sparse codes sent through a randomly-constructed (but unknown) noisy wiring bottleneck \cite{Isely10}.\footnote{We refer the reader to \cite{ganguli2012compressed} for more on interactions between dictionary learning and neuroscience.}
 
@@
 Given such effective uses of compressed sensing, it is only a matter of time before these systems incorporate dictionary learning to encode and process data (e.g., in a device that learns structure from motion \cite{kong2016prior}).
-Assurances such as those offered by our theorems certify that different devices (with different initialization, samples, etc.) will learn equivalent representations given enough data from statistically identical systems.\footnote{To contrast with the current hot topic of ``Deep Learning'', there are few such uniqueness guarantees for these multi-layer feedforward models of data; moreover, there is evidence that even minuscule amounts of (``adversarial'') signal noise can dramatically alter their output \cite{goodfellow2014explaining}.} Indeed, it seems a main reason for the sustained interest in dictionary learning as an unsupervised method for data analysis is the assumed well-posedness of parameter identification in the sparse linear coding model, confirmation of which forms the core of our theoretical findings.
+Assurances such as those offered by our theorems certify that different devices (with different initialization, etc.) will learn equivalent representations given enough data from statistically identical systems.\footnote{To contrast with the current hot topic of ``Deep Learning'', there are few such uniqueness guarantees for these models of data; moreover, even small noise can dramatically alter their output \cite{goodfellow2014explaining}.} Indeed, it seems a main reason for the sustained interest in dictionary learning as an unsupervised method for data analysis is the assumed well-posedness of parameter identification in the sparse linear coding model, confirmation of which forms the core of our theoretical findings.
 
@@
 \bibliography{chazthm_pnas}
+
+\vspace{-.15 cm}
 
@@
 \end{proof}
-
+%\vspace{-.2 cm}
 \begin{lemma}\label{DistanceToIntersectionLemma}
@@
 For  $\mathbf{x} \in \mathbb{R}^m$, we have (where $\xi$ is given in Def.~\ref{SpecialSupportSet}):
+\vspace{-.2 cm}
 \begin{align}\label{DTILeq}
@@
 \end{lemma}
+%\vspace{-.3 cm}
 \begin{proof} 
@@
 \end{proof}
-
+%\vspace{-.4 cm}
 \begin{lemma}\label{NonEmptyLemma} 

### 2017-08-21 manuscripts/PNAS/chazthm_pnas.tex
final?? chaz edits

@@
 
-We generalize the  lower bound to a domain-restricted \emph{union of subspaces} model \cite{vidal2005generalized} derived from a hypergraph $\mathcal{H}$.
+We generalize the  lower bound to a domain-restricted \emph{union of subspaces} model \cite{vidal2005generalized} derived from a hypergraph $\mathcal{H} \subseteq {[m] \choose k}$.
 Letting $\mathbf{M}_J$ denote the submatrix formed by the columns of $\mathbf{M}$ indexed by $J \subseteq [m]$ (with $\mathbf{M}_\emptyset := \mathbf{0}$), we define:
@@
 
-One can also easily verify that for every $k < m$, there is a regular $k$-uniform hypergraph with the SIP; for instance, take $\mathcal{H}$ to be the consecutive intervals of length $k$ in some cyclic order on $[m]$.
+One can also easily verify that for every $k < m$, there are regular $k$-uniform hypergraphs with the SIP besides the obvious $\mathcal{H} = {[m] \choose k}$; for instance, take $\mathcal{H}$ to be the consecutive intervals of length $k$ in some cyclic order on $[m]$.
 In this case, a direct consequence of Cor.~\ref{DeterministicUniquenessCorollary} is rigorous verification of the lower bound \mbox{$N = m(k-1){m \choose k} + m$} for sufficient sample size from the introduction.
@@
 
-Another practical implication of Thm.\ref{DeterministicUniquenessTheorem} is the following: there is an effective procedure sufficient to affirm if a proposed solution to Prob.~\ref{InverseProblem} is indeed unique (up to noise and inherent ambiguities).
+Another practical implication of Thm.~\ref{DeterministicUniquenessTheorem} is the following: there is an effective procedure sufficient to affirm if a proposed solution to Prob.~\ref{InverseProblem} is indeed unique (up to noise and inherent ambiguities).
 Simply check that the matrix and codes satisfy the (computable) assumptions of Thm.~\ref{DeterministicUniquenessTheorem} on $\mathbf{A}$ and the $\mathbf{x}_i$.
@@
 As a simple example for $k=2$, let $\mathbf{A} = [ \mathbf{e}_1, \ldots, \mathbf{e}_5, \mathbf{v}]$ where $\mathbf{v} = \mathbf{e}_1 + \mathbf{e}_3 + \mathbf{e}_5$, and take $\mathcal{H}$ to be all consecutive pairs of $[m]$ arranged in cyclic order.
-Then, dictionary $\mathbf{A}$ satisfies the assumptions of Thm.~\ref{DeterministicUniquenessTheorem} but not \eqref{SparkCondition}.
+Then, dictionary $\mathbf{A}$ satisfies the assumptions of Thm.~\ref{DeterministicUniquenessTheorem} underlying \eqref{Cstable} without satisfying \eqref{SparkCondition}.
 %(since $\{ \mathbf{A}_1, \mathbf{A}_3, \mathbf{A}_5, \mathbf{A}_6\}$ is not a linearly independent set).
@@
 \begin{theorem}\label{SLCopt}
-If the assumptions of Thm.\ref{DeterministicUniquenessTheorem} hold, only now with more than $(k-1)\left[ {\bar m \choose k} + |\mathcal{H}|k{\bar m \choose k-1}\right]$ vectors $\mathbf{x}_i$ supported in each $S \in \mathcal{H}$, then all solutions to Prob.~\ref{OptimizationProblem} with $\eta \leq \varepsilon / 2$ necessarily satisfy recovery inequalities \eqref{Cstable} and \eqref{b-PDa} of Thm.~\ref{DeterministicUniquenessTheorem}.
+If the assumptions of Thm.~\ref{DeterministicUniquenessTheorem} hold, only now with more than $(k-1)\left[ {\bar m \choose k} + |\mathcal{H}|k{\bar m \choose k-1}\right]$ vectors $\mathbf{x}_i$ supported in each $S \in \mathcal{H}$, then all solutions to Prob.~\ref{OptimizationProblem} with $\eta \leq \varepsilon / 2$ necessarily satisfy recovery inequalities \eqref{Cstable} and \eqref{b-PDa} of Thm.~\ref{DeterministicUniquenessTheorem}.
 \end{theorem}
@@
 Let $\mathbf{A}$  be the $n \times m$ matrix of $nm$ indeterminates $A_{ij}$.
-When real numbers are substituted for $A_{ij}$, the resulting matrix satisfies condition \eqref{SparkCondition} if and only if the following polynomial is nonzero:
+When real numbers are substituted for $A_{ij}$, the resulting matrix satisfies \eqref{SparkCondition} if and only if the following polynomial is nonzero:
 \begin{align*}
@@
 
-If for some  $\mathbf{B} \in \mathbb{R}^{n \times \bar m}$ and map $\pi: E \mapsto {[\bar m] \choose k}$, we have:
+If for some  $\mathbf{B} \in \mathbb{R}^{n \times \bar m}$ and map $\pi: \mathcal{H} \mapsto {[\bar m] \choose k}$, we have:
 \begin{align}\label{GapUpperBound}
@@
 \end{align}
-for some nonempty $J \subseteq [m], \bar J \subseteq[\bar{m}]$ of size $\bar m - r(\bar m - m)$.
+for some nonempty $J \subseteq [m]$ and $\bar J \subseteq[\bar{m}]$ of size $\bar m - r(\bar m - m)$.
 \end{lemma}

### 2017-08-21 manuscripts/PNAS/chazthm_pnas.tex
chaz
last sml edits

@@
 % Use letters for affiliations, numbers to show equal authorship (if applicable) and to indicate the corresponding author
-\author[a,b, 1]{Charles J. Garfinkle}
+\author[a,b,1]{Charles J. Garfinkle}
 \author[a,1]{Christopher J. Hillar}
@@
 
-\keywords{Sparse linear coding, dictionary learning, matrix factorization, compressed sensing, inverse problems, blind source separation}
+\keywords{Sparse coding, dictionary learning, matrix factorization, compressed sensing, inverse problems, blind source separation}
 
@@
 %\|\mathbf{x}^J_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\bar x}^{\bar J}_i\|_1 &\leq  \left( \frac{ 1+C_1 \|\mathbf{x}^{J}_i\|_1 }{ L_{2k}(\mathbf{A}) -  C_1\varepsilon } \right) \varepsilon \ \  \text{for $i \in [N]$}.
-\|\mathbf{x}_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\bar x}_i\|_1 &\leq  \left( \frac{ 1+C_1 \|\mathbf{x}_i\|_1 }{ L_{2k}(\mathbf{A}) -  C_1\varepsilon } \right) \varepsilon, \ \  \text{for $i \in [N]$},
+\|\mathbf{x}_i - \left(\mathbf{D}^{-1}\mathbf{P}^{\top}\right)_{\bar J}\mathbf{\bar x}_i\|_1 &\leq  \left( \frac{ 1+C_1 \|\mathbf{x}_i\|_1 }{ L_{2k}(\mathbf{A}) -  C_1\varepsilon } \right) \varepsilon, \ \  \text{for $i \in [N]$},
 \end{align}
@@
 
-The pragmatic reader should note that the explicit constants $C_1$ and $C_2$ are effectively computable: the quantity $L_k$, may be computed as the smallest singular value of a certain matrix, while the quantity $\xi$ involves computing ``canonical angles'' between subspaces, which reduce again to an efficient singular value decomposition.
-There is no efficient computation of $L_k$ in general, however, since even $L_{k} > 0$ is NP-hard \cite{tillmann2014computational}; although, fixing $k$, yields polynomial complexity.
-Moreover, calculating $C_2$ requires an exponential number of queries to $\xi$; thus, as presented, $C_1$ and $C_2$ are not efficiently computable.
+The pragmatic reader should note that the explicit constants $C_1$ and $C_2$ are effectively computable: the quantity $L_k$ may be calculated as the smallest singular value of a certain matrix, while the quantity $\xi$ involves computing ``canonical angles'' between subspaces, which reduce again to an efficient singular value decomposition.
+There is no known fast computation of $L_k$ in general, however, since even $L_{k} > 0$ is NP-hard \cite{tillmann2014computational}; although fixing $k$ yields polynomial complexity.
+Moreover, calculating $C_2$ requires an exponential number of queries to $\xi$.
+Thus, as presented, $C_1$ and $C_2$ are not efficiently computable.
 
@@
 
-The total number of $(k-1)$-sparse vectors $\mathbf{\bar x}_i$ can thus not exceed $|\mathcal{H}|(k-1){ \bar m \choose k-1}$.
+The total number of $(k-1)$-sparse vectors $\mathbf{\bar x}_i$ thus can not exceed $|\mathcal{H}|(k-1){ \bar m \choose k-1}$.
 By \eqref{eqn}, no more than $|\mathcal{H}|k(k-1){ \bar m \choose k-1}$ vectors $\mathbf{\bar x}_i$ are not $k$-sparse.
@@
 \begin{lemma}\label{spanIntersectionLemma}
-If $f: U \to V$ is an injective function then $f\left(\cap_{i=1}^\ell U_i \right) =  \cap_{i=1}^\ell f\left(U_i\right)$ for any $U_1, \ldots, U_\ell \subseteq U$.
+If $f: U \to V$ is an injective function, then $f\left(\cap_{i=1}^\ell U_i \right) =  \cap_{i=1}^\ell f\left(U_i\right)$ for any $U_1, \ldots, U_\ell \subseteq U$.
 %In particular, if for some $E \in 2^{[m]}$ the map $M \in \mathbb{R}^{n \times m}$ is injective on $\cup_{S \in \mathcal{H}} \text{span}\{e_i\}_{i \in S}$ then $\text{span}\{ M_{\cap_{S \in \mathcal{H}} S} \} = \cap_{S \in \mathcal{H}} \text{span}\{M_S\}$.
@@
 Repeating the above arguments produces a (necessarily, by $r$-regularity and the SIP) distinct $\mathcal{G}_2 \subseteq \mathcal{H}$ and corresponding $i_2 \in [\bar m]$.
-Iterating the arguments $p$ times yields the set of singletons \mbox{$J = \{\cap \mathcal{G}_1, \ldots, \cap \mathcal{G}_p\} \subseteq [m]$}.
+Finally, iterating this $p$ times in total yields the set of singletons \mbox{$J = \{\cap \mathcal{G}_1, \ldots, \cap \mathcal{G}_p\} \subseteq [m]$}.
 \end{proof}

### 2017-08-21 manuscripts/PNAS/review/point_by_point_response.txt
chaz

--- 2017-08-21 manuscripts/PNAS/review/point_by_point_response.txt
@@
 That being said, the paper (with the modifications below) would certainly merit publication in very solid journal like IEEE Transactions on Information Theory, where it would be a median paper, in my opinion.
+
 -----------------
@@
 It is true, however, that we have not determined the tightest conditions regarding the constants and sample size necessary for uniqueness in sparse linear coding.
-However, we believe that these sufficient conditions yield strong enough conclusions to stand on their own; for instance, in synchronizing device parameters for a particular sparsely representable sensory ensemble.
+We nevertheless believe that these sufficient conditions yield strong enough conclusions to stand on their own; for instance, in synchronizing device parameters for a particular sparsely representable sensory ensemble.
 

### 2017-08-21 manuscripts/PNAS/review/point_by_point_response.txt
chaz

@@
 Then A satisfies the assumptions of Thm.
-1 without satisfying the spark condition.) We had omitted this point in our original submission of the manuscript to keep things simple, but have decided to include this fact in our resubmission.
+1 for dictionary recovery without satisfying the spark condition.) We had omitted this point in our original submission of the manuscript to keep things simple, but have decided to include this fact in our resubmission.
 This also required us to redefine the restricted matrix lower bound L_k to be in terms of a hypergraph H (L_H in the revised manuscript), which is an interesting object for further study in its own right.

### 2017-08-21 manuscripts/PNAS/review/point_by_point_response.txt
chaz

@@
 2, that of most interest to practitioners of dictionary learning methods, is to our knowledge the first of its kind in both the noise-free and noisy domains.
-We recognize that this was not clearly communicated in the Discussion section of our submitted manuscript, and we have adjusted the manuscript accordingly.
+We recognize that this was not clearly communicated in the Discussion section of our submitted manuscript.
 
@@
 
-RESPONSE: Yes, though actually for every S \in E there are "more than" (k-1)\choose{\bar{m},k} vectors with support in S (not "at least").
+RESPONSE: Yes, though actually for every S \in E (now \mathcal{H} in the revised manuscript) there are "more than" (k-1)\choose{\bar{m},k} vectors with support in S (not "at least").
 Thank you for helping us to clarify our statements.

### 2017-08-21 manuscripts/PNAS/review/point_by_point_response.txt
cor 3 should be cor 2, fixed this

@@
 We have updated the manuscript to reflect this, and the condition now reads "provided \bar m < \ell m / (\ell - 1)" where previously it read "provided p = \bar m − \ell( \bar m − m ) is positive".
-(Note: in the resubmitted manuscript, we have actually opted to use r instead of \ell for the regularity of the hypergraph.)
+(Note: in the revised manuscript, we have actually opted to use r instead of \ell for the regularity of the hypergraph.)
 
@@
 1 are satisfied by random data.
-We have provided an "almost certain" guarantee of this flavor in Cor 3, wherein the sparse vector supports are constrained to form a hypergraph satisfying the SIP.
+We have provided an "almost certain" guarantee of this flavor in Cor 2, wherein the sparse vector supports are constrained to form a hypergraph satisfying the SIP.
 It would be useful and interesting to calculate furthermore the probability that random supports form a hypergraph satisfying the SIP.

### 2017-08-21 manuscripts/PNAS/review/point_by_point_response.txt
chaz

@@
 We have opted not to include these calculations due in part to space constraints, but also because we believe that what sets our work apart from the vast majority of results in the field is their deterministic nature, e.g.
-they do not depend on any kind of assumption about the particular random distribution from which the sparse coefficients or dictionary entries are drawn.
+they do not depend on any kind of assumption about the particular random distribution from which the sparse supports, coefficients, or dictionary entries are drawn.
 

### 2017-08-22 manuscripts/PNAS/chazthm_pnas.tex
final edits

@@
 
-The constant $C_2 = C_2(\mathbf{A}, \mathcal{H})$ is given in turn below, in terms of one used in \cite{Deutsch12} to analyze the convergence of the alternating projections algorithm for projecting a point onto an intersection of subspaces.
-We use it to bound the distance between a point and the intersection of subspaces given an upper bound on its distance from each individual subspace.
+The constant $C_2 = C_2(\mathbf{A}, \mathcal{H})$, in turn, will be presented relative to a quantity from \cite{Deutsch12} used to analyze the convergence of the alternating projections algorithm. 
+More specifically, the following definition is used to bound the distance between a point and the intersection of subspaces given an upper bound on its distance from each individual subspace in Lem.~\ref{DistanceToIntersectionLemma}, below.
 

### 2017-08-22 manuscripts/PNAS/chazthm_pnas.tex
last sml edits

@@
 \dropcap{B}lind source separation is a classical problem in signal processing \cite{sato1975method}.
-In one common modern formulation, each of $N$ observed $n$-dimensional signals is a (noisy) linear combination of at most $k$ elementary waveforms drawn from some unknown ``dictionary'' of size $m$, typically with $m \ll N$ (see \cite{Zhang15} for a comprehensive review of this and related models).
+In one common modern formulation, each of $N$ observed $n$-dimensional signals is a (noisy) linear combination of at most $k$ elementary waveforms drawn from some unknown dictionary of size $m$, typically with $m \ll N$ (see \cite{Zhang15} for a comprehensive review of this and related models).
 Approximating solutions to this sparsity-constrained inverse problem have provided insight into the structure of many signal classes lacking domain-specific formal models (e.g., in vision \cite{wang2015sparse}).
@@
 A curious aspect of this finding is that the latent waveforms (e.g., ``Gabor'' wavelets) estimated from data appear to be canonical \cite{donoho2001can};
-i.e., they are found in learned dictionaries independent of algorithm or natural image training set.
+i.e., they are found in learned dictionaries independent of algorithm or image training set.
 
@@
 conditions have recently been proposed (see \cite[Sec.~I-E]{Sun16} for a summary of the state-of-the-art).
-Few theorems, however, can be cited to explain this uniqueness phenomenon more broadly; in particular, a universal guarantee in the context of noise has yet to emerge.
+Few theorems, however, can be cited to explain this uniqueness more broadly; in particular, a universal guarantee in the context of noise has yet to emerge.
 
@@
 \begin{problem}[Sparse linear coding]\label{InverseProblem}
-Find a matrix $\mathbf{B}$ and $k$-sparse $\mathbf{\bar x}_1, \ldots, \mathbf{\bar x}_N \in \mathbb{R}^m$ such that $\|\mathbf{z}_i - \mathbf{B}\mathbf{\bar x}_i\|_2 \leq \eta$ for all $i$.
+Find a matrix $\mathbf{B}$ and $k$-sparse $\mathbf{\bar x}_1, \ldots, \mathbf{\bar x}_N \in \mathbb{R}^m$ so that $\|\mathbf{z}_i - \mathbf{B}\mathbf{\bar x}_i\|_2 \leq \eta$ for all $i$.
 \end{problem}
@@
 \end{definition}
-
-\pagebreak
 
@@
 
-\vspace{-.15 cm}
+%\vspace{-.15 cm}
 
@@
 For  $\mathbf{x} \in \mathbb{R}^m$, we have (where $\xi$ is given in Def.~\ref{SpecialSupportSet}):
-\vspace{-.2 cm}
+%\vspace{-.2 cm}
 \begin{align}\label{DTILeq}

### 2017-11-15 manuscripts/PNAS/second review/code/constants.py
code

@@ -1,0 +1,90 @@
+from decomp_svd import subspace_angles
+import numpy as np
+
+def friedrichs(U,V):
+    """
+    Calculates the Friedrichs angle between subspaces U and V (in radians).
+
+    The Friedrichs angle is the smallest nonzero principle angle.
+
+    Alternatively, it is the (s+1)th principal angle when dim(U \cap V) = s.
+    """
+    angles = subspace_angles(U,V)
+    nz_angles = angles > 1e-10 #> np.finfo(float).eps
+    if np.any(nz_angles):
+        min_nz_angle = np.sort(angles[nz_angles])[0]
+        return min_nz_angle
+    else:
+        return 0.
+
+def xi(A, G):
+    """
+    Calculates xi({A_S}_{S \in G})
+
+    (Assumes A is injective on H, so the intersection of the span is the span of the intersection.)
+    """
+    if len(G) == 1:
+        return 1 # by definition
+    Gs = itertools.permutations(G)
+    prods = []
+    for Gseq in Gs: # loop through all orderings of elements in G
+        prod = 1.
+        for i, Si in enumerate(Gseq[:-1]):
+            cap_Sj = list(set.intersection(*map(set, Gseq[i+1:])))
+            if cap_Sj: # otherwise they intersect only at 0 and sin(theta) = 1, since every subspace forms pi/2 angle with 0 (weird)
+                theta = friedrichs(A[:,Si], A[:,cap_Sj])
+                prod *=  np.sin(theta)**2
+        prods.append(prod)
+    return 1 - np.sqrt(1 - np.max(prods))
+
+#def powerset(s):
+#    return [[x for j, x in enumerate(s) if (i >> j) & 1] for i in range(2**len(s))]
+
+def C_2(A, H, r):
+    """
+    Ouputs the constant C2
+
+    A: n x m dictionary matrix (2d numpy array)
+    H: hypergraph (list of lists in range(m))
+    r: regularity of H
+    """
+    xi_Gs = [] # xi is in (0,1]
+    for G in itertools.combinations(H, r): # loop over subsets of H of size r
+        xi_Gs.append( xi(A, G) )
+    max_A = np.max( np.linalg.norm(A, axis=0) )
+    return len(H) * max_A / min(xi_Gs)
+
+if __name__ == '__main__':
+    #np.random.seed(0)
+    H = [ # cyclic order
[…]

### 2017-11-15 manuscripts/PNAS/second review/code/constants.py
code

@@ -1,5 +1,6 @@
 from decomp_svd import subspace_angles
 import numpy as np
+import itertools
 
 def friedrichs(U,V):
     """
@@ -75,7 +76,7 @@ if __name__ == '__main__':
     r = 2
     """
     c2s = []
-    for i in range(1):
+    for i in range(1000):
         #A = np.eye(9,9)\
         A = np.random.randn(4,9)
         A = np.dot( A, np.diag(1./np.linalg.norm(A,axis=0)) ) # normalize

### 2017-11-15 manuscripts/PNAS/second review/code/constants.py
chaz

@@ -57,6 +57,7 @@ def C_2(A, H, r):
 
 if __name__ == '__main__':
     #np.random.seed(0)
+    """
     H = [ # cyclic order
         [0,1,2],
         [1,2,3],
@@ -64,28 +65,35 @@ if __name__ == '__main__':
         [3,0,1]
         ]
     r = 3
-    """    ]
+    """
     H = [ # rows and cols of square array
-        [0,1,2],
-        [3,4,5],
-        [6,7,8],
-        [0,3,6],
-        [1,4,7],
-        [2,5,8]
+        [0,1,2,3],
+        [4,5,6,7],
+        [8,9,10,11],
+        [12,13,14,15],
+        [0,4,8,12],
+        [1,5,9,13],
+        [2,6,10,14],
+        [3,7,11,15]
         ]
     r = 2
-    """
     c2s = []
-    for i in range(1000):
+    pcntiles = []
+    for i in range(10000):
         #A = np.eye(9,9)\
-        A = np.random.randn(4,9)
+        A = np.random.randn(16,16)
         A = np.dot( A, np.diag(1./np.linalg.norm(A,axis=0)) ) # normalize
         c2 = C_2(A, H, r)
         #print('%1.3f' % c2)
         c2s.append(c2)
+        if (i > 1000) & (i % 100 == 0):
+            print(i)
+            pcntiles.append( np.percentile(c2s,95) )
 
     import matplotlib.pyplot as pp
     pp.ion()
     c2s = np.array(c2s)
     pp.hist(c2s[c2s<1000], bins=40)
     pp.show()
+    pp.figure();
+    pp.plot(pcntiles)

### 2017-11-15 manuscripts/PNAS/second review/response.txt
minor edits response

BIBLIOGRAPHY:
Quantification of artistic style through sparse coding analysis in the drawings of Pieter Bruegel the Elder, PNAS
Stability-driven nonnegative matrix factorization to interpret spatial gene expression and build local gene networks

-------------------------------------

Editor Comments:

I actually don't want a revision at the moment, just a response.

My job as editor is certainly to not get suckered.

I think the claims are undeniably important, but I'm not clear on exactly
how we get there.

Both of the referees are somewhat skeptical of the extent of the
contribution being made. They both say you're overselling. Your cover
letter goes into detail covering contributions, and some of what you say is
convincing. But parts are simply lawyerly.

Here are some things I'm thinking in the back of my mind.

(a) This is at best about local stability, rather than stability. The size
of the neighborhood where you're getting stability is presumably almost
infinitesimal in general. While I agree that the paper is written in a
quantitative way and has as you say constants which can be quantitative, it
is I would say after a few readings, more
seemingly-quantitative-but-actually-purely-qualitative.
If it could be shown to be surprisingly effective in some specific case, I
might withdraw from this position.

-------------------------------------

RESPONSE:

We are somewhat confused by this statement as we understand even the tightest possible noise bound to be necessarily "local" and approaching zero as the domain-restricted matrix lower-bound vanishes, e.g. as the number of dictionary elements grows infinite. One need only consider the case k=1, where every dictionary element spans a ray through the origin, and each identifiable datum generated from the model (1) lies within a cylinder of radius \eta around one (and only one) of these rays. Clearly, for bounded data in a finite dimensional space, this radius is cannot remain finite in the limit of infinitely many distinct rays.

It seems instead the concern is that the bound is in general so small it is "practically" infinitesimal. Indeed, our guarantees apply to the deterministic “worst-case” scenario where noise is isotropic and "what can go wrong, will go wrong". Calculations specific to the data at hand would consider the probability distribution of confounding noise and yield more forgiving probabilistic guarantees.

We have simulated the distribution of noise that can be tolerated in the deterministic worst-case for some generic matrices and sparse data supported on our two example hypergraphs from the introduction.

[TODO calculate constant]

-------------------------------------

(b) Point (a) is important because when you say these results somehow
validate various neuroscience ideas, I am saying in the back of my mind
that you're bravely talking yourself on a ledge. Namely, nothing in
neuroscience can really depend on infinitesimal stability. Trying to make a
claim like this seems to undermine your credibility with me. It seems the
referees had the same problem.

-------------------------------------

RESPONSE:

Our response to point (a) aside, and though we are not inclined to assume that neural circuits are incapable of extreme precision [citations?], we actually share your skepticism here. However, we simply confirm the well-posedness of the problem which specialists in the field have suggested neural circuits may be solving (see e.g. Ganguli paper, NIPS paper) and feel it is their credibility, if anyone’s, that should be questioned and not ours.

If you are nevertheless reluctant to become complicit in propagating this neuroscientific hypothesis, we have no qualms downplaying it in the manuscript. Instead, we could discuss the relevance of our results to recent work applying dictionary learning and related methods to solve inverse problems in other areas of science. For example, TODO (PNAS Bin Yu paper, PNAS Forgery, Agarwal Science).

-------------------------------------

(c) It's not clear why exact uniqueness should be so important for
neuroscience. It seems more likely that mere similarity is what's maybe
important. In the same sense it's not clear why formal Lipschitz stability
in the mathematical sense should be so important for neuroscience. It seems
more important that some sort of qualitative similarity should persist
under perturbations.

-------------------------------------

RESPONSE:

Look, man, we didn’t invent this stuff; we’re just here cleaning it up. Here's how the hypothesis is rationalized:

Suppose some quantities of interest are encoded in the sparse activity of neurons in the sending region, sparse for whatever reason [e.g. machine learning papers on representations/sparsity, note that sparse activity has been observed in brains]. These quantities are to be transmitted to some distant region through as few wires (axons) as possible, e.g. due to space constraints inside the skull.

The hypothesis is that the brain, up-to-date on the latest fad, solves this problem by applying a (noisy) "random" projection into the lower-dimensional space spanned by these axons. The neurons in the receiving region are then tasked with decoding the quantities of interest from this compressed signal. Suppose, however, that they cannot read out this information directly from the compressed signal. Rather, the neurons in the receiving region must first reproduce the original sparse pattern of activity before they can decode from it the quantities of interest (perhaps this sparse representation has the same advantages in the receiving region as in the sending region). Moreover — and this is central to the hypothesis — they must accomplish this feat without knowledge of the random projection applied by the sender, i.e. via dictionary learning.

In this way, the "qualitative similarity" (i.e. between the quantities of interest) to which you refer is contingent on the uniqueness and stability of sparse representations. We have proven that *any* dictionary learning procedure implemented in the receiving region (biologically plausible algorithms are an active area of research [cite]) that does "well enough" will indeed yield a sparse activity pattern (at least, up to an inherent relabelling ambiguity) that is ‘similar’ to the original pattern in the sending region. (The stability criterion need not be Lipschitz continuity, but it just so happens to be; note that Def. 1 imposes no such constraint.)

It is entirely possible, and in our opinion very likely, that the encoding and decoding procedures utilized by actual nervous networks are far more sophisticated. The science is just not there yet. At the very least, we have proven that the only published hypothesis regarding how this could be done is well-founded, mathematically.

-------------------------------------

(d) An editor who doesn't want to get suckered is always looking at papers
to find a very specific 'gadget' or 'gadgets' that mark the distinction
between the submitted work and 'obvious', 'trivial' work.

I can't really tell if the hypergraph construct is such a gadget. It's
really only handled in passing and only two examples are mentioned.

-------------------------------------

RESPONSE:

In our previous response, we described in detail how the perspective we take on the problem enables the following insights beyond a "trivial" (not really!) extension of (HS15) to the noisy case:

1) a subset of dictionary elements is recoverable even if dictionary size is overestimated,
2) data require only a polynomial number of distinct sparse supports,
3) the spark condition is not a necessary property of recoverable dictionaries.

All of these generalizations are direct consequences of defining a new matrix lower bound induced by a hypergraph. We therefore believe the term "gadget" downplays the insight this construct offers into the problem. It is certainly not only treated in passing, as it is present in every one of our theorems. We have provided only a few obvious hypergraph constructions because the point is that there even *is* a theory of hypergraphs underlying this problem. Our examples briefly demonstrate the gains to be made from this discovery, so as to entice the community into fully exploring its ramifications in practice.

-------------------------------------

I can't really tell if your cardinality bound on the number of samples
needed for a stable representation is one such gadget. I am unable on my
own to conjure up an example where I might have thought an exponential
number of samples would be required but you show me very explicitly that
no, a dramatically smaller number is required.

-------------------------------------

RESPONSE:

If there is any one "gadget" to which we may credit our results, it is the pigeon-hole principle. While we have not managed to exorcise exponentiality from the number of required samples in general (which may very well be impossible), we have applied the pigeon-hole principle in a novel way (Lem. 5) to prove that only a polynomial number of sparse supports are necessary in general for stable identification of the generating dictionary. In our view, this lends much more legitimacy to the use of this model in practice, where data in general are unlikely to exhibit the exponentially many possible k-wise combinations of dictionary elements (as all previous results have required).

-------------------------------------

So I'm at a standstill. I would need to be convinced that you have actual
gadgets that go beyond what I would have come up with and that the
identifiability problem is dramatically different than what an 'obvious' or
'easy-to-guess' solution might say, by showing me something very concrete
that I can understand. The lack of any explicit implementation on a
computer on a specific example doesn't help.

-------------------------------------

RESPONSE:

Frankly, we feel at a loss here. It seems to us that assessing a solution as "obvious" after-the-fact, when it has already informed one’s intuition, is fundamentally unfair. It’s always easy to guess, easier to guess wrong, and hardest to prove. Still, we offer a nice surprise for everyone who reads our paper and realizes how absurd it is that they have never come across Def. 1 anywhere in the literature on dictionary learning before.

Problems 1 and 2 have been studied for two decades now, and no one has pointed out the relation between them, nor the existence of the underlying hypergraph structure and its numerous ramifications. Our solution to Prob. 2, that of most interest to practitioners of dictionary learning methods, is the first of its kind in both the noise-free and noisy domains. If these solutions are the "easy-to-guess", "obvious" solutions, then so be it; we cannot change geometry. Actually, we prefer results for which intuition can play its role in lending credence to the truth. Would you have even believed us if we claimed polynomial sample complexity?

-------------------------------------

Reviewer #2
Suitable Quality? Yes
Sufficient General Interest? No
Conclusions Justified? Yes
Clearly Written? No
Procedures Described? Not Applicable
Willingness to Re-review? Yes

Comments
In my opinion, while the extension from exact to noisy stability of
dictionary learning (DL) is significant, the fact that the analysis relies
on metrics of the data that are not feasible to compute limits its impact
to the scientific community beyond computer science and applied
mathematics. While the authors state in their response that their results
validate the extensive successful use of DL in practice, there seems to be
little impact to this given that the methodology is already in widespread
use; instead, practical criteria that allows practitioners to establish
whether the data model obtained from DL is optimal or not would have very
high impact. My questions in the review were probing whether any
contribution of this type was present, and the responses appear to point
toward a negative answer.

-------------------------------------

RESPONSE:

What sets our work apart from the vast majority of results in the field is that they do not depend on any kind of assumption about the particular random distribution from which the sparse supports, coefficients, or dictionary entries are drawn. As a result, our paper only directly justifies "in principle" the inferences of those who apply DL methods to inverse problems in their research. Our "target" practitioner, however, is not the scientist who seeks a black box yielding the probability of their inferences; rather, it is the statistician or computer scientist who builds these black boxes on a case-by-case basis. On the statistical side, we have forged a path for high-impact results that derive from our deterministic guarantees the statistical criteria underlying the inferences in more domain-specific probabilistic models. On the computational side, we halve the work it takes to prove the consistency of any dictionary learning algorithm. We expect our work will make many such assists in the coming seasons, and just as in the game of hockey, we think this deserves as much acknowledgement as the goal.

### 2017-11-17 manuscripts/PNAS/second review/code/constants.py
C1 denominator

@@ -1,6 +1,7 @@
 from decomp_svd import subspace_angles
 import numpy as np
 import itertools
+import operator as op
 
 def friedrichs(U,V):
     """
@@ -55,6 +56,31 @@ def C_2(A, H, r):
     max_A = np.max( np.linalg.norm(A, axis=0) )
     return len(H) * max_A / min(xi_Gs)
 
+def C1_denom(A, X, H, k, num_rand_ksets=10 ** 2):
+    """
+    Ouputs the denominator in the def of constant C1
+
+    ************
+    ASSUMES: first (k-1)(m choose k) are supported on H[0], etc
+             [so that N = |H|(k-1)(m choose k)]
+    ************
+
+    A: n x m dictionary matrix (2d numpy array)
+    X: m x N matrix of N k-sparse codes
+    H: hypergraph (list of lists in range(m))
+    k: sparsity k of support sets
+    """
+    m = A.shape[1]
+    minC1 = 0
+    num_supp = (k - 1) * choose(m, k)
+    for c, S in enumerate(H):
+        AX = np.dot(A, X[:, c * num_supp:(c + 1) * num_supp])
+        for trial in range(num_rand_ksets):
+            K = np.random.choice(num_supp, k)
+            u, s, v = np.linalg.svd(AX[:, K])
+            minC1 = min(minC1, s[-1])
+    return minC1
+
 if __name__ == '__main__':
     #np.random.seed(0)
     """
@@ -76,24 +102,42 @@ if __name__ == '__main__':
         [2,6,10,14],
         [3,7,11,15]
         ]
-    r = 2
-    c2s = []
-    pcntiles = []
-    for i in range(10000):
+    r = 2; k = 4; m = 16; n = 16
+    num_supp = (k - 1) * choose(m, k); N = len(H) * num_supp
+    num_trials = 1000
+    Cs = np.zeros((num_trials, 2))  # 0:C1, 1:C2
+    pcntiles = np.zeros((num_trials, 2))  # 0:C1, 1:C2
+    for i in range(num_trials):
         #A = np.eye(9,9)\
-        A = np.random.randn(16,16)
+        A = np.random.randn(n, m)
         A = np.dot( A, np.diag(1./np.linalg.norm(A,axis=0)) ) # normalize
-        c2 = C_2(A, H, r)
+
+        X = np.zeros((m, N))
[…]

### 2017-11-17 manuscripts/PNAS/second review/code/constants.py
C1 bug fix

@@ -71,7 +71,7 @@ def C1_denom(A, X, H, k, num_rand_ksets=10 ** 2):
     k: sparsity k of support sets
     """
     m = A.shape[1]
-    minC1 = 0
+    minC1 = np.inf
     num_supp = (k - 1) * choose(m, k)
     for c, S in enumerate(H):
         AX = np.dot(A, X[:, c * num_supp:(c + 1) * num_supp])
@@ -104,11 +104,12 @@ if __name__ == '__main__':
         ]
     r = 2; k = 4; m = 16; n = 16
     num_supp = (k - 1) * choose(m, k); N = len(H) * num_supp
-    num_trials = 1000
+    num_trials = 3
     Cs = np.zeros((num_trials, 2))  # 0:C1, 1:C2
     pcntiles = np.zeros((num_trials, 2))  # 0:C1, 1:C2
     for i in range(num_trials):
         #A = np.eye(9,9)\
+        print("Trial %d" % i)
         A = np.random.randn(n, m)
         A = np.dot( A, np.diag(1./np.linalg.norm(A,axis=0)) ) # normalize
 
@@ -134,7 +135,7 @@ if __name__ == '__main__':
 
     plt.figure()
     C1s = Cs[:, 0]
-    pp.hist(C1s, bins=40)
+    pp.hist(C1s, bins=100)
     pp.show()
     pp.title('C1s')
 

### 2017-11-21 manuscripts/PNAS/second review/chazthm_pnas.tex
chaz

--- 2017-08-22 manuscripts/PNAS/chazthm_pnas.tex
@@
 % TODO %
-% bar J in Lem 4?
-% Mention computability of eps(d1,d2) in terms of C1?
+% Mention all matrices are real
+% Do we mention that the Appendix contains proof of Lem. 1?
 % *** Put ell1 norm into the denominator of L_k *** ?
 % Give example of when we might expect k-uniformity, i.e. x_i in glp on k-dimensional subspaces. Orbit under group action of a k-dimensional subspace?
+% If not thousands...?
 
@@
 
-Here, we prove very generally that uniqueness and stability in sparse linear coding is an expected property of the model. 
+Here, we prove very generally that uniqueness and stability is an expected property of the sparse linear coding model. 
 More specifically, dictionaries that preserve sparse codes (e.g., satisfy a ``spark condition'') are identifiable from as few as \mbox{$N = m(k-1){m \choose k} + m$} noisy sparse linear combinations of their columns up to an error that is linear in the noise (Thm.~\ref{DeterministicUniquenessTheorem}).
@@
 \end{align}
-for $k$-\emph{sparse} $\mathbf{x}_i \in \mathbb{R}^m$ having at most $k$ nonzero entries and \emph{noise} $\mathbf{n}_i \in \mathbb{R}^n$, with bounded norm $\| \mathbf{n}_i \|_2 \leq  \eta$ representing our combined worst-case uncertainty in  measuring $\mathbf{A}\mathbf{x}_i$.
+for $k$-\emph{sparse} $\mathbf{x}_i \in \mathbb{R}^m$ having at most $k<m$ nonzero entries and \emph{noise} $\mathbf{n}_i \in \mathbb{R}^n$, with bounded norm $\| \mathbf{n}_i \|_2 \leq  \eta$ representing our combined worst-case uncertainty in  measuring $\mathbf{A}\mathbf{x}_i$.
 The first mathematical problem we address is the following.
@@
 We say $Y$ has a \textbf{$k$-sparse representation in $\mathbb{R}^m$} if there exists a matrix $\mathbf{A}$ and $k$-sparse $\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$ such that $\mathbf{y}_i = \mathbf{A}\mathbf{x}_i$ for all $i$.
-This representation is \textbf{stable} if for every $\delta_1, \delta_2 \geq 0$, there exists $\varepsilon(\delta_1, \delta_2) \geq 0$ (with $\varepsilon > 0$ when  $\delta_1, \delta_2 > 0$) such that if $\mathbf{B}$ and $k$-sparse $\mathbf{\bar x}_1, \ldots, \mathbf{\bar x}_N \in \mathbb{R}^m$ satisfy:
+This representation is \textbf{stable} if for every $\delta_1, \delta_2 \geq 0$, there exists some $\varepsilon = \varepsilon(\delta_1, \delta_2)$ that is strictly positive for positive $\delta_1$ and $\delta_2$ such that if $\mathbf{B}$ and $k$-sparse $\mathbf{\bar x}_1, \ldots, \mathbf{\bar x}_N \in \mathbb{R}^m$ satisfy:
 \begin{align*}
-\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\bar x}_i\|_2 \leq \varepsilon,\ \ \   \text{for all $i$},
+	\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\bar x}_i\|_2 \leq \varepsilon(\delta_1, \delta_2),\ \ \   \text{for all $i$},
 \end{align*}
@@
 Next, we describe a quantitative version of the spark condition.
-The \emph{lower bound} $L$ of a matrix $\mathbf{M} \in \mathbb R^{n \times m}$ is the largest $\alpha$ such that \mbox{$\|\mathbf{M}\mathbf{x}\|_2 \geq \alpha\|\mathbf{x}\|_2$} for all $\mathbf{x} \in \mathbb{R}^m$ \cite{Grcar10}.
-By compactness of the unit sphere, every injective linear map has nonzero lower bound; hence, if $\mathbf{M}$ satisfies \eqref{SparkCondition}, then each submatrix formed from $2k$ of its columns or less has $L > 0$.
+The \emph{lower bound} of a matrix $\mathbf{M} \in \mathbb R^{n \times m}$ is the largest $\alpha$ such that \mbox{$\|\mathbf{M}\mathbf{x}\|_2 \geq \alpha\|\mathbf{x}\|_2$} for all $\mathbf{x} \in \mathbb{R}^m$ \cite{Grcar10}.
+By compactness of the unit sphere, every injective linear map has nonzero lower bound; hence, if $\mathbf{M}$ satisfies \eqref{SparkCondition}, then each submatrix formed from $2k$ of its columns or less has a strictly positive lower bound.
 
@@
 
-Every $n \times \bar m$ matrix $\mathbf{B}$ for which there exist $k$-sparse $\mathbf{\bar x}_1, \ldots, \mathbf{\bar x}_N$ satisfying \mbox{$\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\bar x}_i\|_2 \leq \varepsilon$} for all $i$ has $\bar m \geq m$ and, provided $\bar m < mr/(r-1)$,
+Every $n \times \bar m$ matrix $\mathbf{B}$ for which there are $k$-sparse $\mathbf{\bar x}_1, \ldots, \mathbf{\bar x}_N$ satisfying \mbox{$\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\bar x}_i\|_2 \leq \varepsilon$} for all $i$ has $\bar m \geq m$ and, provided $\bar m < mr/(r-1)$,
 \begin{align}\label{Cstable}
@@
 %
-for some nonempty $J \subseteq [m]$ and $\bar J \subseteq [\bar m]$ of size $\bar m - r(\bar m - m)$, permutation matrix $\mathbf{P}$, and and invertible diagonal matrix $\mathbf{D}$.
+for some nonempty $\bar J \subseteq [\bar m]$ and $J \subseteq [m]$ of size $\bar m - r(\bar m - m)$, permutation matrix $\mathbf{P}$, and and invertible diagonal matrix $\mathbf{D}$.
 
-Moreover, if $L_{2k}(\mathbf{A}) > 0$ and $\varepsilon < L_{2k}(\mathbf{A}) / C_1$, then $L_{2k}(\mathbf{B}\mathbf{PD}) \geq L_{2k}(\mathbf{A}) - C_1 \varepsilon$ and:
+Moreover, if $A$ satisfies \eqref{SparkCondition} and $\varepsilon < L_{2k}(\mathbf{A}) / C_1$, then $L_{2k}(\mathbf{B}\mathbf{PD}) \geq L_{2k}(\mathbf{A}) - C_1 \varepsilon$ and:
 \begin{align}\label{b-PDa}
@@
 In words, Thm.~\ref{DeterministicUniquenessTheorem} says that the smaller the difference $\bar m - m$ between recovery and original latent dictionary sizes, the more columns and coefficients of the original dictionary $\mathbf{A}$ and codes $\mathbf{x}_i$ are contained (up to noise) in the appropriately scaled dictionary $\mathbf{B}$ and codes $\mathbf{\bar x}_i$.
-In the particular case when $\bar m = m$, the theorem directly implies that  $Y = \{\mathbf{Ax}_1, \ldots, \mathbf{Ax}_N\}$ has a stable $k$-sparse representation in $\mathbb{R}^m$, with inequalities \eqref{def1} guaranteed provided $\varepsilon$ in Def.~\ref{maindef} does not exceed:
+In the particular case when $\bar m = m$, the theorem directly implies that  $Y = \{\mathbf{Ax}_1, \ldots, \mathbf{Ax}_N\}$ has a stable $k$-sparse representation in $\mathbb{R}^m$, with inequalities \eqref{def1} guaranteed for $\varepsilon$ in Def.~\ref{maindef} given by:
 \begin{align}\label{epsdel}
@@
 
-We note the following facts. For subspaces $U \subseteq U', V \subseteq \mathbb{R}^m$, we have $d(U,V) \leq d(U',V)$ and \cite[Ch.~4 Cor.~2.6]{Kato2013}: %Kato p.223
+We note the following facts. If $U' \subseteq U$, then $d(U',V) \leq d(U,V)$ and \cite[Ch.~4 Cor.~2.6]{Kato2013}: %Kato p.223
 \begin{align}\label{dimLem}
@@
 
-Our result in combinatorial matrix analysis is the following. Let $\bm{\mathcal{M}}$ denote the column-span of a matrix $\mathbf{M}$.
+Our result in combinatorial matrix analysis is the following. Let $\bm{\mathcal{M}}_S$ denote the column-span of a submatrix $\mathbf{M}_S$.
 
 \begin{lemma}\label{MainLemma}
-Suppose $\mathbf{A} \in \mathbb{R}^{n \times m}$ has $L_{2\mathcal{H}}(\mathbf{A}) > 0$ for some $r$-regular $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP.
+Suppose the $n \times m$ matrix $\mathbf{A}$ has $L_{2\mathcal{H}}(\mathbf{A}) > 0$ for some $r$-regular $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP.
 There exists $C_2 > 0$ for which the following holds for all $\varepsilon < L_2(\mathbf{A}) / C_2$:
 
-If for some  $\mathbf{B} \in \mathbb{R}^{n \times \bar m}$ and map $\pi: \mathcal{H} \mapsto {[\bar m] \choose k}$, we have:
+If for some $n \times \bar m$ matrix $\mathbf{B}$ and map $\pi: \mathcal{H} \mapsto {[\bar m] \choose k}$, we have:
 \begin{align}\label{GapUpperBound}
@@
 The constant $C_2 = C_2(\mathbf{A}, \mathcal{H})$, in turn, will be presented relative to a quantity from \cite{Deutsch12} used to analyze the convergence of the alternating projections algorithm. 
-More specifically, the following definition is used to bound the distance between a point and the intersection of subspaces given an upper bound on its distance from each individual subspace in Lem.~\ref{DistanceToIntersectionLemma}, below.
+More specifically, in Lem.~\ref{DistanceToIntersectionLemma} below, the following definition is used to bound the distance between a point and the intersection of subspaces given an upper bound on its distance from each individual subspace.
 
@@
 \end{definition}
-Note that $\theta \in (0,\frac{\pi}{2}]$ implies $0 < \xi \leq 1$.\footnote{We acknowledge the counter-intuitive property that $\theta =  \pi/2$ when $U = V$ or $U \perp V$.}  
+Note that $\theta \in (0,\frac{\pi}{2}]$ implies $0 < \xi \leq 1$.\footnote{We acknowledge the counter-intuitive property that $\theta =  \pi/2$ when $U \subseteq W$}  
 The constant $C_2$ in Lem.~\ref{MainLemma} can then be expressed as:  
 \begin{align}\label{Cdef2}
-C_2(\mathbf{A}, \mathcal{H}) := \frac{ 2^{|\mathcal{H}|} \max_{j \in [m]} \|\mathbf{A}_j\|_2}{ \min_{\mathcal{G} \subseteq \mathcal{H}} \xi( \{ \bm{\mathcal{A}}_S \}_{S \in \mathcal{G}}) },
+	C_2(\mathbf{A}, \mathcal{H}) := \frac{ (r+1) \max_{j \in [m]} \|\mathbf{A}_j\|_2}{ \min_{\mathcal{G} \subseteq {\mathcal{H} \choose r} \cup {\mathcal{H} \choose r+1}} \xi( \{ \bm{\mathcal{A}}_S \}_{S \in \mathcal{G}}) },
 \end{align}
@@
 
-Beyond an original extension of existing noiseless guarantees \cite{Hillar15} to the noisy regime, a major innovation in our work is a theory of combinatorial designs for support sets key to the identification of the dictionary.
-We incorporate this idea into a new fundamental lemma in matrix theory (Lem.~\ref{MainLemma}) that draws upon the definition of a new matrix lower bound induced by a hypergraph satisfying a ``singleton intersection property''.
+Beyond an original extension of existing noiseless guarantees \cite{Hillar15} to the noisy regime and their application to Prob.~\ref{OptimizationProblem}, a major innovation in our work is a theory of combinatorial designs for support sets key to the identification of the dictionary.
+We incorporate this idea into a new fundamental lemma in matrix theory (Lem.~\ref{MainLemma}) that draws upon the definition of a new matrix lower bound induced by a hypergraph.
 Insights enabled by our combinatorial approach include: 1) a subset of dictionary elements is recoverable even if dictionary size is overestimated, 2) data require only a polynomial number of distinct sparse supports, and 3) the spark condition is not a necessary property of recoverable dictionaries.
@@
 \begin{align}\label{cond}
-|\cap \pi(\mathcal{G})| \leq |\cap \mathcal{G} |,\ \ \   \text{for } \mathcal{G} \subseteq \mathcal{H},
+	|\cap \pi(\mathcal{G})| \leq |\cap \mathcal{G} |,\ \ \   \text{for } \mathcal{G} \in {\mathcal{H} \choose r} \cup {\mathcal{H} \choose r+1},
 \end{align}
 %
-then $\bar m \geq m$; and if $\bar m < mr / (r-1)$, the association $i \mapsto \cap \pi(\sigma(i))$ is an injective map to $[\bar m]$ from some $J \subseteq [m]$ of size $\bar m - r(\bar m - m)$.
+then $\bar m \geq m$, and if $\bar m < mr / (r-1)$ then the association $i \mapsto \cap \pi(\sigma(i))$ is an injective map to $[\bar m]$ from some $J \subseteq [m]$ of size $\bar m - r(\bar m - m)$.
 %In particular, if $\bar m = m$ then $\pi$ is induced by a permutation on $[m]$.
@@
 Consider the collection of pairs: $T_1 := \{(i, S): i \in \pi(S), S \in \mathcal{H}\}$, which number $|T_1| = \sum_{S \in \mathcal{H}} |\pi(S)| \geq \sum_{S \in \mathcal{H}} |S| = \sum_{i \in [m]} \deg_\mathcal{H}(i) = mr$.
-Note that \eqref{cond} implies $\bar m \geq |T_1| / r = m$, since otherwise pigeonholing the elements of $T_1$ with respect to their possible first indices $[\bar m]$ would imply $\deg_\mathcal{H}(i) > r$ for some $i \in [m]$.
+Note that \eqref{cond} implies $|T_1| \leq \bar m r$, since otherwise pigeonholing the elements of $T_1$ with respect to their possible first indices $[\bar m]$ would imply $\deg_\mathcal{H}(i) > r$ for some $i \in [m]$.
+Thus $\bar m \geq m$.
 
-If $\bar m < mr / (r-1)$ then, letting $p := \bar m - r( \bar m - m)$, we have $|T_1| = \bar m (r - 1) + p$ for positive $p$.
-By the pigeonhole principle again, there must then be at least $r$ elements of $T_1$ sharing the same first index.
-By \eqref{cond}, the intersection of the set $\mathcal{G}_1$ consisting of their second indices is nonempty; hence, $|\cap \mathcal{G}_1| = 1$ by $r$-regularity and the SIP.
+If $\bar m < mr / (r-1)$ then $p := \bar m - r( \bar m - m)$ is positive and $|T_1| \geq \bar m (r - 1) + p$.
+Pigeonholing $T_1$ into $[\bar m]$ again, there must be $r$ elements of $T_1$ sharing the same first index.
+By \eqref{cond}, the intersection of the set $\mathcal{G}_1$ of their second indices is nonempty; hence, $|\cap \mathcal{G}_1| = 1$ by $r$-regularity and the SIP.
 Since $\cap \pi(\mathcal{G}_1)$ is nonempty, applying \eqref{cond} again gives $\cap \pi(\mathcal{G}_1) = \{i_1\}$ for some $i_1 \in [\bar m]$.
 If $p=1$, then we are done.
-Otherwise, define $T_2 := T_1 \setminus \{(i,S) \in T_1: i = i_1\}$, which contains $|T_2| = |T_1| - r = (\bar m - 1)(r-1) + (p-1)$ ordered pairs having $\bar m - 1$ distinct first indices.
-Repeating the above arguments produces a (necessarily, by $r$-regularity and the SIP) distinct $\mathcal{G}_2 \subseteq \mathcal{H}$ and corresponding $i_2 \in [\bar m]$.
+Otherwise, define $T_2 := T_1 \setminus \{(i,S) \in T_1: i = i_1\}$, which contains $|T_2| = |T_1| - r \geq (\bar m - 1)(r-1) + (p-1)$ ordered pairs having $\bar m - 1$ distinct first indices.
+Repeating the above arguments produces a (necessarily, by $r$-regularity and the SIP) distinct $\mathcal{G}_2 \in {\mathcal{H} \choose r}$ and corresponding $i_2 \in [\bar m]$.
 Finally, iterating this $p$ times in total yields the set of singletons \mbox{$J = \{\cap \mathcal{G}_1, \ldots, \cap \mathcal{G}_p\} \subseteq [m]$}.
@@
 We next show that \eqref{cond} holds.
-Fix $\mathcal{G} \subseteq \mathcal{H}$.
-Since $\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})} \subseteq \cap_{S \in \mathcal{G}} \bm{\mathcal{B}}_{\pi(S)}$, if $\cap_{S \in \mathcal{G}} \bm{\mathcal{B}}_{\pi(S)} = \{\textbf{0}\}$, then we must have $|\cap_{S \in \mathcal{G}} \pi(S)| = 0$ (as the columns of $\mathbf{B}_{\pi(S)}$ are linearly independent) and \eqref{cond} is trivially true.
+Fix $\mathcal{G} \subseteq {\mathcal{H} \choose r} \cup {\mathcal{H} \choose r+1}$.
+Since $\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})} \subseteq \cap_{S \in \mathcal{G}} \bm{\mathcal{B}}_{\pi(S)}$, if $\cap_{S \in \mathcal{G}} \bm{\mathcal{B}}_{\pi(S)} = \{\textbf{0}\}$, then we must have $|\cap \pi(\mathcal{G})| = 0$ (as the columns of $\mathbf{B}_{\pi(S)}$ are linearly independent) and \eqref{cond} is trivially true.
 Suppose then that the intersection is not the zero vector.
-Keeping in mind that $d(U,V) \leq d(U',V)$ whenever $U \subseteq U'$ and applying (in order) Lem.~\ref{spanIntersectionLemma}, Lem.~\ref{DistanceToIntersectionLemma}, \eqref{eqdim}, \eqref{GapUpperBound}, and \eqref{Cdef2} gives:
+Keeping in mind that $d(U',V) \leq d(U,V)$ whenever $U' \subseteq U$ and applying (in order) Lem.~\ref{spanIntersectionLemma}, Lem.~\ref{DistanceToIntersectionLemma}, \eqref{eqdim}, \eqref{GapUpperBound}, and \eqref{Cdef2} gives:
 \begin{align}\label{randoml}

### 2017-11-21 manuscripts/PNAS/second review/code/constants.py

@@ -2,6 +2,7 @@ from decomp_svd import subspace_angles
 import numpy as np
 import itertools
 import operator as op
+from scipy.misc import comb as choose
 
 def friedrichs(U,V):
     """
@@ -12,7 +13,7 @@ def friedrichs(U,V):
     Alternatively, it is the (s+1)th principal angle when dim(U \cap V) = s.
     """
     angles = subspace_angles(U,V)
-    nz_angles = angles > 1e-10 #> np.finfo(float).eps
+    nz_angles = angles > np.finfo(float).eps
     if np.any(nz_angles):
         min_nz_angle = np.sort(angles[nz_angles])[0]
         return min_nz_angle
@@ -39,10 +40,7 @@ def xi(A, G):
         prods.append(prod)
     return 1 - np.sqrt(1 - np.max(prods))
 
-#def powerset(s):
-#    return [[x for j, x in enumerate(s) if (i >> j) & 1] for i in range(2**len(s))]
-
-def C_2(A, H, r):
+def C2(A, H, r):
     """
     Ouputs the constant C2
 
@@ -56,13 +54,26 @@ def C_2(A, H, r):
     max_A = np.max( np.linalg.norm(A, axis=0) )
     return len(H) * max_A / min(xi_Gs)
 
-def C1_denom(A, X, H, k, num_rand_ksets=10 ** 2):
+def L_k(M, k, n_samples = None):
+    vals = []
+    if n_samples is None:
+        supports = itertools.combinations(range(M.shape[1]), k)
+    else:
+        supports = [np.random.choice(M.shape[1],k) for i in range(n_samples)]
+    for S in supports:
+        u, s, v = np.linalg.svd(M[:,S])
+        vals.append(s[-1])
+    return np.percentile(vals, 1 ) #min(np.array(vals)[np.array(vals) > 1e-14]) # #min(vals)
+
+def C1_denom(A, Xs, H, num_rand_ksets = None):
     """
     Ouputs the denominator in the def of constant C1
 
     ************
-    ASSUMES: first (k-1)(m choose k) are supported on H[0], etc
-             [so that N = |H|(k-1)(m choose k)]
+    ASSUMES: first (k-1)(m choose k) are supported on H[0],
+             second (k-1)(m choose k) are supported on H[1],
+             ...
[…]

### 2017-11-22 manuscripts/PNAS/second review/code/sample_complexity.py
chaz

@@ -1,0 +1,70 @@
+""" 
+Compute the probability that for every S in H, there are at least k vectors x_i supported there which share a support in B 
+"""
+
+import numpy as np
+from scipy.misc import comb
+
+def pigeonhole_bounded(num_balls, num_bins, max_balls_per_bin):
+    """ 
+    Returns the number of ways to allocate num_balls to num_bins without exceeding max_balls_per_bin in any bin
+
+    Source URL:
+    https://math.stackexchange.com/questions/553960/extended-stars-and-bars-problemwhere-the-upper-limit-of-the-variable-is-bounded
+    """
+    lim = int(min(num_bins, 1.*num_balls / (max_balls_per_bin+1)))
+    val = 0
+    for q in range(lim+1):
+        sgn = (-1)**q
+        term_1 = comb(num_bins, q)
+        term_2 = comb(num_balls - q*(max_balls_per_bin + 1) + num_bins - 1, num_bins - 1)
+        val += sgn * term_1 * term_2
+    return val
+
+def pigeonhole(num_balls, num_bins):
+    """ 
+    Returns the number of ways to allocate num_balls to num_bins.
+    """
+    return comb(num_balls + num_bins - 1, num_bins - 1)
+
+def prob_atleast_k(num_balls, num_bins, k):
+    """
+    Returns the probability that some bin contains at least k balls
+    """
+    bnded = pigeonhole_bounded( num_balls, num_bins, max_balls_per_bin = k-1)
+    tot = pigeonhole( num_balls, num_bins )
+    return 1 - bnded / tot
+
+"""
+There are N_supp vectors supported on each S in H. These are the balls.
+There are mCk k-sparse supports wrt. the n x m matrix B. These are the bins.
+What is the probability that for every S in H, at least k out of N_supp vectors supported there have the same support wrt. B? 
+
+We plot this as a function of m for fixed k.
+Assume H is the set of contiguous length-k intervals of [m] arranged in cyclic order, so that |H| = m.
+"""
+k = 3 # Fixed sparsity, i.e. H is k-uniform
+m_min = k+1 # since k < m required for H to satisfy SIP
+m_max = 20 # Max dictionary size
+prob = 0.999 # With what probability do we want the proof to work
+N_probabilistic = [] # Number of samples for proof to work with probability prob
[…]

### 2017-11-22 manuscripts/PNAS/second review/code/constants.py
updates

@@ -47,9 +47,11 @@ def C2(A, H, r):
     A: n x m dictionary matrix (2d numpy array)
     H: hypergraph (list of lists in range(m))
     r: regularity of H
+
+    Loops over subsets of H of size r+1
     """
     xi_Gs = [] # xi is in (0,1]
-    for G in itertools.combinations(H, r): # loop over subsets of H of size r
+    for G in itertools.combinations(H, r + 1): # loop over subsets of H of size r
         xi_Gs.append( xi(A, G) )
     max_A = np.max( np.linalg.norm(A, axis=0) )
     return len(H) * max_A / min(xi_Gs)
@@ -90,6 +92,15 @@ def C1_denom(A, Xs, H, num_rand_ksets = None):
         min_val = min(min_val, lk)
     return min_val
 
+def cyclic_hypergraph(m, k):
+    H = []
+    for i in range(m - k + 1):
+        H.append(list(range(i, i + k)))
+    for i in range(1, k):
+        j = k - i
+        H.append(list(range(m - j, m)) + list(range(0, k - j)))
+    return H
+
 if __name__ == '__main__':
     #np.random.seed(0)
     """
@@ -102,44 +113,83 @@ if __name__ == '__main__':
     r = 3
     """
     """ rows and cols of square grid """
+
+    # SQUARE GRID
     r = 2
-    k = 4;
-    m = k**2
-    n = m;
-    square_grid = np.reshape(range(m),(k,k))
-    H = [row.tolist() for row in square_grid] + [col.tolist() for col in square_grid.T]
-    N_per_support = int((k - 1) * choose(m, k))
-    N = len(H) * N_per_support
-    num_trials = 100
-    Cs = np.zeros((num_trials, 2))  # 0:C1, 1:C2
-    #pcntiles = np.zeros((num_trials, 2))  # 0:C1, 1:C2
-    for i in range(num_trials):
-        print("Trial %d" % i)
-        A = np.random.randn(n, m)
-        A = np.dot( A, np.diag(1./np.linalg.norm(A, axis=0)) ) # normalize
-        Xs = [np.random.randn(k, N_per_support) for S in H]
-        Xs = [np.dot(X, np.diag(1. / np.linalg.norm(X, axis=0))) for X in Xs] # normalize
[…]

### 2017-11-22 manuscripts/PNAS/second review/resub/chazthm_pnas_resub.tex

--- 2017-11-21 manuscripts/PNAS/second review/chazthm_pnas.tex
@@
 \begin{problem}[Sparse linear coding]\label{InverseProblem}
-Find a matrix $\mathbf{B}$ and $k$-sparse $\mathbf{\bar x}_1, \ldots, \mathbf{\bar x}_N \in \mathbb{R}^m$ so that $\|\mathbf{z}_i - \mathbf{B}\mathbf{\bar x}_i\|_2 \leq \eta$ for all $i$.
+Find a matrix $\mathbf{B}$ and $k$-sparse $\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N \in \mathbb{R}^m$ so that $\|\mathbf{z}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \eta$ for all $i$.
 \end{problem}
 
-Note that any particular solution $(\mathbf{B}, \mathbf{\bar x}_1 \ldots, \mathbf{\bar x}_N)$ to this problem gives rise to an orbit of equivalent solutions $(\mathbf{BPD}, \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\bar x}_1, \ldots, \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\bar x}_N)$, where $\mathbf{P}$ is any permutation matrix and $\mathbf{D}$ any invertible diagonal.
-Previous theoretical work addressing the noiseless case $\eta =0$ (e.g., \cite{li2004analysis, Georgiev05, Aharon06, Hillar15}) has shown that a solution to Prob.~\ref{InverseProblem} (when it exists) is indeed unique up to this inherent ambiguity provided the $\mathbf{x}_i$ are sufficiently diverse and the generating matrix $\mathbf{A}$ satisfies the \textit{spark condition} from compressed sensing:
+Note that any particular solution $(\mathbf{B}, \mathbf{\overline x}_1 \ldots, \mathbf{\overline x}_N)$ to this problem gives rise to an orbit of equivalent solutions $(\mathbf{BPD}, \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_1, \ldots, \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_N)$, where $\mathbf{P}$ is any permutation matrix and $\mathbf{D}$ any invertible diagonal.
+Previous theoretical work addressing the noiseless case $\eta =0$ (e.g., \cite{li2004analysis, Georgiev05, Aharon06, Hillar15}) has shown that a solution to Prob.~\ref{InverseProblem} (when it exists) is unique up to this  ambiguity provided the $\mathbf{x}_i$ are sufficiently diverse and the generating matrix $\mathbf{A}$ satisfies the \textit{spark condition}:
 \begin{align}\label{SparkCondition}
@@
 We say $Y$ has a \textbf{$k$-sparse representation in $\mathbb{R}^m$} if there exists a matrix $\mathbf{A}$ and $k$-sparse $\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$ such that $\mathbf{y}_i = \mathbf{A}\mathbf{x}_i$ for all $i$.
-This representation is \textbf{stable} if for every $\delta_1, \delta_2 \geq 0$, there exists some $\varepsilon = \varepsilon(\delta_1, \delta_2)$ that is strictly positive for positive $\delta_1$ and $\delta_2$ such that if $\mathbf{B}$ and $k$-sparse $\mathbf{\bar x}_1, \ldots, \mathbf{\bar x}_N \in \mathbb{R}^m$ satisfy:
+This representation is \textbf{stable} if for every $\delta_1, \delta_2 \geq 0$, there exists some $\varepsilon = \varepsilon(\delta_1, \delta_2)$ that is strictly positive for positive $\delta_1$ and $\delta_2$ such that if $\mathbf{B}$ and $k$-sparse $\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N \in \mathbb{R}^m$ satisfy:
 \begin{align*}
-	\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\bar x}_i\|_2 \leq \varepsilon(\delta_1, \delta_2),\ \ \   \text{for all $i$},
+	\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \varepsilon(\delta_1, \delta_2),\ \ \   \text{for all $i$},
 \end{align*}
@@
 \begin{align}\label{def1}
-\|\mathbf{A}_j - \mathbf{BPD}_j\|_2 \leq \delta_1 \ \ \text{and} \ \ \|\mathbf{x}_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\bar x}_i\|_1 \leq \delta_2.
+\|\mathbf{A}_j - \mathbf{BPD}_j\|_2 \leq \delta_1 \ \ \text{and} \ \ \|\mathbf{x}_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_i\|_1 \leq \delta_2.
 \end{align}
@@
 Consider now any dataset $Z$ generated as in \eqref{LinearModel} with $\eta \leq \frac{1}{2} \varepsilon(\delta_1, \delta_2)$.
-Then from the triangle inequality, it follows that any matrix $\mathbf{B}$ and $k$-sparse $\mathbf{\bar x}_1, \ldots, \mathbf{\bar x}_N \in \mathbb{R}^m$ solving Prob.~\ref{InverseProblem} are necessarily within $\delta_1, \delta_2$ of the original dictionary $\mathbf{A}$ and codes $\mathbf{x}_i$, respectively.
+Then from the triangle inequality, it follows that any matrix $\mathbf{B}$ and $k$-sparse $\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N \in \mathbb{R}^m$ solving Prob.~\ref{InverseProblem} are necessarily within $\delta_1, \delta_2$ of the original dictionary $\mathbf{A}$ and codes $\mathbf{x}_i$, respectively.
 
@@
 \begin{problem}\label{OptimizationProblem}
-Find $\mathbf{B}$ and \mbox{$\mathbf{\bar x}_1, \ldots, \mathbf{\bar x}_N \in \mathbb{R}^m$} that solve:
+Find $\mathbf{B}$ and \mbox{$\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N \in \mathbb{R}^m$} that solve:
 \begin{align}\label{minsum}
-\min \sum_{i = 1}^N \|\mathbf{\bar x}_i\|_0 \ \ 
-\text{subject to} \ \ \|\mathbf{z}_i - \mathbf{B}\mathbf{\bar x}_i\|_2 \leq \eta, \ \text{for all $i$}.
+\min \sum_{i = 1}^N \|\mathbf{\overline x}_i\|_0 \ \ 
+\text{subject to} \ \ \|\mathbf{z}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \eta, \ \text{for all $i$}.
 \end{align}
@@
 Fix an $n \times m$ matrix $\mathbf{A}$ with $L_{2\mathcal{H}}(\mathbf{A}) > 0$ for an $r$-regular $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP.
-If \mbox{$\{\mathbf{x}_1, \ldots, \mathbf{x}_N\} \subset \mathbb{R}^m$} contains, for each $S \in \mathcal{H}$, more than $(k-1){m \choose k}$ $k$-sparse vectors in general linear position supported in $S$, then there is $C_1 > 0$ with the following holding for all%\footnote{The condition $\varepsilon < L_2(\mathbf{A}) /C_1$ is necessary; otherwise,  with \mbox{$\mathbf{A}$ = $\mathbf{I}$} and $\mathbf{x}_i = \mathbf{e}_i$, there is a matrix $\mathbf{B}$ and $1$-sparse $\mathbf{\bar{x}}_i$ with $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\bar{x}}_i \|_2 \leq \varepsilon$ that nonetheless violates \eqref{Cstable}.} $\varepsilon < L_{2}(\mathbf{A}) / C_1$:
-\footnote{The condition $\varepsilon < L_2(\mathbf{A}) /C_1$ is necessary; otherwise, with \mbox{$\mathbf{A}$ = $\mathbf{I}$} and $\mathbf{x}_i = \mathbf{e}_i$, the matrix $\mathbf{B} = \left[\mathbf{0}, \frac{1}{2}(\mathbf{e}_1 + \mathbf{e}_2), \mathbf{e}_3, \ldots, \mathbf{e}_{m} \right]$ and 1-sparse codes $\mathbf{\bar x}_i = \mathbf{e}_2$ for $i = 1, 2$ and $\mathbf{\bar x}_i = \mathbf{e}_i$ for $i \geq 3$ satisfy $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\bar{x}}_i \|_2 \leq \varepsilon$ but nonetheless violate \eqref{Cstable}.} $\varepsilon < L_{2}(\mathbf{A}) / C_1$:
+If \mbox{$\{\mathbf{x}_1, \ldots, \mathbf{x}_N\} \subset \mathbb{R}^m$} contains, for each $S \in \mathcal{H}$, more than $(k-1){m \choose k}$ $k$-sparse vectors in general linear position supported in $S$, then there is $C_1 > 0$ with the following holding for all%\footnote{The condition $\varepsilon < L_2(\mathbf{A}) /C_1$ is necessary; otherwise,  with \mbox{$\mathbf{A}$ = $\mathbf{I}$} and $\mathbf{x}_i = \mathbf{e}_i$, there is a matrix $\mathbf{B}$ and $1$-sparse $\mathbf{\overline{x}}_i$ with $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline{x}}_i \|_2 \leq \varepsilon$ that nonetheless violates \eqref{Cstable}.} $\varepsilon < L_{2}(\mathbf{A}) / C_1$:
+\footnote{The condition $\varepsilon < L_2(\mathbf{A}) /C_1$ is necessary; otherwise, with \mbox{$\mathbf{A}$ = $\mathbf{I}$} and $\mathbf{x}_i = \mathbf{e}_i$, the matrix $\mathbf{B} = \left[\mathbf{0}, \frac{1}{2}(\mathbf{e}_1 + \mathbf{e}_2), \mathbf{e}_3, \ldots, \mathbf{e}_{m} \right]$ and 1-sparse codes $\mathbf{\overline x}_i = \mathbf{e}_2$ for $i = 1, 2$ and $\mathbf{\overline x}_i = \mathbf{e}_i$ for $i \geq 3$ satisfy $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline{x}}_i \|_2 \leq \varepsilon$ but nonetheless violate \eqref{Cstable}.} $\varepsilon < L_{2}(\mathbf{A}) / C_1$:
 
-Every $n \times \bar m$ matrix $\mathbf{B}$ for which there are $k$-sparse $\mathbf{\bar x}_1, \ldots, \mathbf{\bar x}_N$ satisfying \mbox{$\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\bar x}_i\|_2 \leq \varepsilon$} for all $i$ has $\bar m \geq m$ and, provided $\bar m < mr/(r-1)$,
+Every $n \times \overline m$ matrix $\mathbf{B}$ for which there are $k$-sparse $\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N$ satisfying \mbox{$\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \varepsilon$} for all $i$ has $\overline m \geq m$ and, provided $\overline m < mr/(r-1)$,
 \begin{align}\label{Cstable}
-\|\mathbf{A}_j- \mathbf{B}_{\bar J} \mathbf{PD}_j\|_2 \leq C_1 \varepsilon, \ \ \text{for all } j \in J,
+\|\mathbf{A}_j- \mathbf{B}_{\overline J} \mathbf{PD}_j\|_2 \leq C_1 \varepsilon, \ \ \text{for all } j \in J,
 \end{align}
 %
-for some nonempty $\bar J \subseteq [\bar m]$ and $J \subseteq [m]$ of size $\bar m - r(\bar m - m)$, permutation matrix $\mathbf{P}$, and and invertible diagonal matrix $\mathbf{D}$.
+for some nonempty $\overline J \subseteq [\overline m]$ and $J \subseteq [m]$ of size $\overline m - r(\overline m - m)$, permutation matrix $\mathbf{P}$, and and invertible diagonal matrix $\mathbf{D}$.
 
@@
 \begin{align}\label{b-PDa}
-%\|\mathbf{x}^J_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\bar x}^{\bar J}_i\|_1 &\leq  \left( \frac{ 1+C_1 \|\mathbf{x}^{J}_i\|_1 }{ L_{2k}(\mathbf{A}) -  C_1\varepsilon } \right) \varepsilon \ \  \text{for $i \in [N]$}.
-\|\mathbf{x}_i - \left(\mathbf{D}^{-1}\mathbf{P}^{\top}\right)_{\bar J}\mathbf{\bar x}_i\|_1 &\leq  \left( \frac{ 1+C_1 \|\mathbf{x}_i\|_1 }{ L_{2k}(\mathbf{A}) -  C_1\varepsilon } \right) \varepsilon, \ \  \text{for $i \in [N]$},
+%\|\mathbf{x}^J_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}^{\overline J}_i\|_1 &\leq  \left( \frac{ 1+C_1 \|\mathbf{x}^{J}_i\|_1 }{ L_{2k}(\mathbf{A}) -  C_1\varepsilon } \right) \varepsilon \ \  \text{for $i \in [N]$}.
+\|\mathbf{x}_i - \left(\mathbf{D}^{-1}\mathbf{P}^{\top}\right)_{\overline J}\mathbf{\overline x}_i\|_1 &\leq  \left( \frac{ 1+C_1 \|\mathbf{x}_i\|_1 }{ L_{2k}(\mathbf{A}) -  C_1\varepsilon } \right) \varepsilon, \ \  \text{for $i \in [N]$},
 \end{align}
 %
-where $\mathbf{x}_i$ and $\mathbf{\bar x}_i$ here represent subvectors formed from restricting to entries indexed by $J$ and $\bar J$, respectively. 
+where $\mathbf{x}_i$ and $\mathbf{\overline x}_i$ here represent subvectors formed from restricting to entries indexed by $J$ and $\overline J$, respectively. 
 \end{theorem}
@@
 %To be clear, the implication of Thm.~\ref{DeterministicUniquenessTheorem} is that $Y = \{\mathbf{Ax}_1, \ldots, \mathbf{Ax}_N\}$ has a stable $k$-sparse representation in $\mathbb{R}^m$, with \eqref{def1} guaranteed provided $\varepsilon$ in Def.~\ref{maindef} does not exceed:
-In words, Thm.~\ref{DeterministicUniquenessTheorem} says that the smaller the difference $\bar m - m$ between recovery and original latent dictionary sizes, the more columns and coefficients of the original dictionary $\mathbf{A}$ and codes $\mathbf{x}_i$ are contained (up to noise) in the appropriately scaled dictionary $\mathbf{B}$ and codes $\mathbf{\bar x}_i$.
-In the particular case when $\bar m = m$, the theorem directly implies that  $Y = \{\mathbf{Ax}_1, \ldots, \mathbf{Ax}_N\}$ has a stable $k$-sparse representation in $\mathbb{R}^m$, with inequalities \eqref{def1} guaranteed for $\varepsilon$ in Def.~\ref{maindef} given by:
+In words, Thm.~\ref{DeterministicUniquenessTheorem} says that the smaller the difference $\overline m - m$ between recovery and original latent dictionary sizes, the more columns and coefficients of the original dictionary $\mathbf{A}$ and codes $\mathbf{x}_i$ are contained (up to noise) in the appropriately scaled dictionary $\mathbf{B}$ and codes $\mathbf{\overline x}_i$.
+In the particular case when $\overline m = m$, the theorem directly implies that  $Y = \{\mathbf{Ax}_1, \ldots, \mathbf{Ax}_N\}$ has a stable $k$-sparse representation in $\mathbb{R}^m$, with inequalities \eqref{def1} guaranteed for $\varepsilon$ in Def.~\ref{maindef} given by:
 \begin{align}\label{epsdel}
@@
 %=======
-%An immediate practical implication of this result is that there exists a practical procedure to affirm if one's proposed solution $(\mathbf{B}, \mathbf{\bar x}_1, \ldots, \mathbf{x}_N)$ to Prob.~\ref{InverseProblem} is indeed unique (up to noise and inherent ambiguities): simply check that $\mathbf{B}$ and the $\mathbf{\bar x}_i$ satisfy the assumptions on $\mathbf{A}$ and the $\mathbf{x}_i$ in Thm.~\ref{DeterministicUniquenessTheorem}.
+%An immediate practical implication of this result is that there exists a practical procedure to affirm if one's proposed solution $(\mathbf{B}, \mathbf{\overline x}_1, \ldots, \mathbf{x}_N)$ to Prob.~\ref{InverseProblem} is indeed unique (up to noise and inherent ambiguities): simply check that $\mathbf{B}$ and the $\mathbf{\overline x}_i$ satisfy the assumptions on $\mathbf{A}$ and the $\mathbf{x}_i$ in Thm.~\ref{DeterministicUniquenessTheorem}.
 %
 %%In fact, a more general result (stated clearly in the next section) can be gleaned from our method of proving Thm.~\ref{DeterministicUniquenessTheorem}.
-Briefly, in cases where $\mathbf{B}$ has $\bar m \neq m$ columns, or $\mathcal{H}$ is not regular or only partially satisfying the SIP, a relation between $\bar m$ and the degree sequence of nodes in $\mathcal{H}$ gives indices $J \subseteq [m]$ defining a submatrix $\mathbf{A}_J$ and subvectors $\mathbf{x}_i^J$ that are recoverable in the sense of \eqref{Cstable} and \eqref{b-PDa}.
-For example, if $\mathcal{H}$ is $\ell$-regular with the SIP but $m \leq \bar m < m\ell/(\ell - 1)$ then we have nonzero $|J| = \bar m - \ell(\bar m - m)$.
-The implication here is that the smaller the difference $\bar m - m$, the more columns and code entries of the original $n \times m$ dictionary $\mathbf{A}$ and codes $\mathbf{x}_i$ contained (up to noise) in the appropriately scaled $n \times \bar m$ dictionary $\mathbf{B}$ and codes $\mathbf{\bar x}_i$.
-When $\bar m = m$, we recover Thm.~\ref{DeterministicUniquenessTheorem}.
+Briefly, in cases where $\mathbf{B}$ has $\overline m \neq m$ columns, or $\mathcal{H}$ is not regular or only partially satisfying the SIP, a relation between $\overline m$ and the degree sequence of nodes in $\mathcal{H}$ gives indices $J \subseteq [m]$ defining a submatrix $\mathbf{A}_J$ and subvectors $\mathbf{x}_i^J$ that are recoverable in the sense of \eqref{Cstable} and \eqref{b-PDa}.
+For example, if $\mathcal{H}$ is $\ell$-regular with the SIP but $m \leq \overline m < m\ell/(\ell - 1)$ then we have nonzero $|J| = \overline m - \ell(\overline m - m)$.
+The implication here is that the smaller the difference $\overline m - m$, the more columns and code entries of the original $n \times m$ dictionary $\mathbf{A}$ and codes $\mathbf{x}_i$ contained (up to noise) in the appropriately scaled $n \times \overline m$ dictionary $\mathbf{B}$ and codes $\mathbf{\overline x}_i$.
+When $\overline m = m$, we recover Thm.~\ref{DeterministicUniquenessTheorem}.
 %
-%%In fact, even if $\mathcal{H}$ is not regular or only partially satisfies the SIP, a relation between $\bar m$ and the degree sequence of nodes in $\mathcal{H}$ may give the indices $J \subseteq [m]$.
+%%In fact, even if $\mathcal{H}$ is not regular or only partially satisfies the SIP, a relation between $\overline m$ and the degree sequence of nodes in $\mathcal{H}$ may give the indices $J \subseteq [m]$.
 For sake of brevity, we delay to the next section a clear statement of this more general result.
@@
 Simply check that the matrix and codes satisfy the (computable) assumptions of Thm.~\ref{DeterministicUniquenessTheorem} on $\mathbf{A}$ and the $\mathbf{x}_i$.
-%Another practical implication of Thm.\ref{DeterministicUniquenessTheorem} is the following: there is an effective procedure sufficient to affirm if a proposed solution $(\mathbf{B}, \mathbf{\bar x}_1, \ldots, \mathbf{x}_N)$ to Prob.~\ref{InverseProblem} is indeed unique (up to noise and inherent ambiguities).
-One simply checks that $\mathbf{B}$ and the $\mathbf{\bar x}_i$ satisfy the respective assumptions of Thm.~\ref{DeterministicUniquenessTheorem}.
+%Another practical implication of Thm.\ref{DeterministicUniquenessTheorem} is the following: there is an effective procedure sufficient to affirm if a proposed solution $(\mathbf{B}, \mathbf{\overline x}_1, \ldots, \mathbf{x}_N)$ to Prob.~\ref{InverseProblem} is indeed unique (up to noise and inherent ambiguities).
+One simply checks that $\mathbf{B}$ and the $\mathbf{\overline x}_i$ satisfy the respective assumptions of Thm.~\ref{DeterministicUniquenessTheorem}.
 %. on $\mathbf{A}$ and the $\mathbf{x}_i$, respectively.
@@
 %In fact, a more general result (stated clearly in the next section) can be gleaned from our method of proving Thm.~\ref{DeterministicUniquenessTheorem}.
-Briefly, in cases where $\mathbf{B}$ has $\bar m \neq m$ columns, or $\mathcal{H}$ is not regular or only partially satisfying the SIP, a relation between $\bar m$ and the degree sequence of nodes in $\mathcal{H}$ gives indices $J \subseteq [m]$ defining a submatrix $\mathbf{A}_J$ and subvectors $\mathbf{x}_i^J$ that are recoverable in the sense of \eqref{Cstable} and \eqref{b-PDa}.
-For example, if $\mathcal{H}$ is $\ell$-regular with the SIP but $m \leq \bar m < m\ell/(\ell - 1)$ then we have nonzero $|J| = \bar m - \ell(\bar m - m)$.
-The implication here is that the smaller the difference $\bar m - m$, the more columns and code entries of the original $n \times m$ dictionary $\mathbf{A}$ and codes $\mathbf{x}_i$ contained (up to noise) in the appropriately scaled $n \times \bar m$ dictionary $\mathbf{B}$ and codes $\mathbf{\bar x}_i$.
-When $\bar m = m$, we recover Thm.~\ref{DeterministicUniquenessTheorem}.
+Briefly, in cases where $\mathbf{B}$ has $\overline m \neq m$ columns, or $\mathcal{H}$ is not regular or only partially satisfying the SIP, a relation between $\overline m$ and the degree sequence of nodes in $\mathcal{H}$ gives indices $J \subseteq [m]$ defining a submatrix $\mathbf{A}_J$ and subvectors $\mathbf{x}_i^J$ that are recoverable in the sense of \eqref{Cstable} and \eqref{b-PDa}.
+For example, if $\mathcal{H}$ is $\ell$-regular with the SIP but $m \leq \overline m < m\ell/(\ell - 1)$ then we have nonzero $|J| = \overline m - \ell(\overline m - m)$.
+The implication here is that the smaller the difference $\overline m - m$, the more columns and code entries of the original $n \times m$ dictionary $\mathbf{A}$ and codes $\mathbf{x}_i$ contained (up to noise) in the appropriately scaled $n \times \overline m$ dictionary $\mathbf{B}$ and codes $\mathbf{\overline x}_i$.
+When $\overline m = m$, we recover Thm.~\ref{DeterministicUniquenessTheorem}.
 
-%In fact, even if $\mathcal{H}$ is not regular or only partially satisfies the SIP, a relation between $\bar m$ and the degree sequence of nodes in $\mathcal{H}$ may give the indices $J \subseteq [m]$.
+%In fact, even if $\mathcal{H}$ is not regular or only partially satisfies the SIP, a relation between $\overline m$ and the degree sequence of nodes in $\mathcal{H}$ may give the indices $J \subseteq [m]$.
 For sake of brevity, we delay to the next section a clear statement of this more general result.
@@
 %(since $\{ \mathbf{A}_1, \mathbf{A}_3, \mathbf{A}_5, \mathbf{A}_6\}$ is not a linearly independent set).
-%This weakening allows for a practical (polynomial) amount of data to still guarantee a stable dictionary in the case where the set of sparse supports for the $\mathbf{\bar x}_i$ is known to have a size that grows polynomially in $m$ and $k$.
+%This weakening allows for a practical (polynomial) amount of data to still guarantee a stable dictionary in the case where the set of sparse supports for the $\mathbf{\overline x}_i$ is known to have a size that grows polynomially in $m$ and $k$.
 
@@
 \begin{theorem}\label{SLCopt}
-If the assumptions of Thm.~\ref{DeterministicUniquenessTheorem} hold, only now with more than $(k-1)\left[ {\bar m \choose k} + |\mathcal{H}|k{\bar m \choose k-1}\right]$ vectors $\mathbf{x}_i$ supported in each $S \in \mathcal{H}$, then all solutions to Prob.~\ref{OptimizationProblem} with $\eta \leq \varepsilon / 2$ necessarily satisfy recovery inequalities \eqref{Cstable} and \eqref{b-PDa} of Thm.~\ref{DeterministicUniquenessTheorem}.
+If the assumptions of Thm.~\ref{DeterministicUniquenessTheorem} hold, only now with more than $(k-1)\left[ {\overline m \choose k} + |\mathcal{H}|k{\overline m \choose k-1}\right]$ vectors $\mathbf{x}_i$ supported in each $S \in \mathcal{H}$, then all solutions to Prob.~\ref{OptimizationProblem} with $\eta \leq \varepsilon / 2$ necessarily satisfy recovery inequalities \eqref{Cstable} and \eqref{b-PDa} of Thm.~\ref{DeterministicUniquenessTheorem}.
 \end{theorem}
@@
 Our linear scaling for $\varepsilon$ in \eqref{epsdel} is essentially optimal (e.g., see \cite{arias2013fundamental}), but a basic open problem remains: how many samples are necessary to determine the sparse linear coding model?
-If $k$ is held fixed or if the size of the support set of reconstructing codes is known to be polynomial in $\bar m$ and $k$, then a practical (polynomial) amount of data suffices.\footnote{In the latter case, a reexamination of the pigeonholing argument in the proof of Thm.~\ref{DeterministicUniquenessTheorem} requires a polynomial number of samples distributed over a polynomial number of supports.} Reasons to be skeptical that this holds in general, however, can be found in \cite{tillmann2014computational, Tillmann15}.
+If $k$ is held fixed or if the size of the support set of reconstructing codes is known to be polynomial in $\overline m$ and $k$, then a practical (polynomial) amount of data suffices.\footnote{In the latter case, a reexamination of the pigeonholing argument in the proof of Thm.~\ref{DeterministicUniquenessTheorem} requires a polynomial number of samples distributed over a polynomial number of supports.} Reasons to be skeptical that this holds in general, however, can be found in \cite{tillmann2014computational, Tillmann15}.
 
@@
 %As mentioned in the previous section, Thm.~\ref{DeterministicUniquenessTheorem} is a particular case of a more general result that forgoes the assumption that $\mathcal{H} \subseteq {[m] \choose k}$ is regular and satisfies the SIP.
-If instead we require only that the stars $\cap \sigma(i)$ intersect at singletons for all $i \leq q$ (assuming that the nodes of $\mathcal{H}$ are labeled in some order of non-increasing degree), we have that $\bar m \geq k|\mathcal{H}| / \deg(1)$ and, provided $\bar m < k|\mathcal{H}| / (\deg(1) - 1)$, the nonempty submatrix $J$ is of size equal to the largest number $p$ satisfying:
+If instead we require only that the stars $\cap \sigma(i)$ intersect at singletons for all $i \leq q$ (assuming that the nodes of $\mathcal{H}$ are labeled in some order of non-increasing degree), we have that $\overline m \geq k|\mathcal{H}| / \deg(1)$ and, provided $\overline m < k|\mathcal{H}| / (\deg(1) - 1)$, the nonempty submatrix $J$ is of size equal to the largest number $p$ satisfying:
 %\begin{align}\label{pcond}
-%\sum_{i=\ell}^{m} \deg(i) > (\bar m + 1 - \ell) (\deg(\ell) - 1) \ \ \text{for all } \ell \leq p \leq q.
+%\sum_{i=\ell}^{m} \deg(i) > (\overline m + 1 - \ell) (\deg(\ell) - 1) \ \ \text{for all } \ell \leq p \leq q.
 %\end{align}
@@
 
-%As mentioned in the previous section, Thm.~\ref{DeterministicUniquenessTheorem} is a particular case of a more general result, which requires a looser set of constraints on the hypergraph $\mathcal{H}$ and which applies to $n \times \bar m$ matrices $\mathbf{B}$ (and $\bar m$-dimensional codes $\mathbf{\bar x}_i$) with $\bar m \neq m$:
+%As mentioned in the previous section, Thm.~\ref{DeterministicUniquenessTheorem} is a particular case of a more general result, which requires a looser set of constraints on the hypergraph $\mathcal{H}$ and which applies to $n \times \overline m$ matrices $\mathbf{B}$ (and $\overline m$-dimensional codes $\mathbf{\overline x}_i$) with $\overline m \neq m$:
 
-%Fix $\bar m$ and suppose the assumptions of Thm.~\ref{DeterministicUniquenessTheorem} hold, only now with the constraints on $\mathcal{H} \subseteq {[m] \choose k}$ being just that $|\cap H(i)| = 1$ for all $i \leq q$ (assuming w.l.o.g.
-that the nodes of $\mathcal{H}$ are labeled in some order of non-increasing degree), and with more than $(k-1){\bar m \choose k}$ vectors $\mathbf{x}_i$ supported in g.l.p.
+%Fix $\overline m$ and suppose the assumptions of Thm.~\ref{DeterministicUniquenessTheorem} hold, only now with the constraints on $\mathcal{H} \subseteq {[m] \choose k}$ being just that $|\cap H(i)| = 1$ for all $i \leq q$ (assuming w.l.o.g.
+that the nodes of $\mathcal{H}$ are labeled in some order of non-increasing degree), and with more than $(k-1){\overline m \choose k}$ vectors $\mathbf{x}_i$ supported in g.l.p.
 on each $S \in \mathcal{H}$.
-Then we must have $\bar m \geq k|\mathcal{H}| / \deg(1)$ and, provided $\bar m < k|\mathcal{H}| / (\deg(1) - 1)$, the guarantee \eqref{Cstable} holds for a submatrix $\mathbf{A}_J$, where $J \subseteq[m]$ is nonempty and of a size equal to the largest number $p$ satisfying:
+Then we must have $\overline m \geq k|\mathcal{H}| / \deg(1)$ and, provided $\overline m < k|\mathcal{H}| / (\deg(1) - 1)$, the guarantee \eqref{Cstable} holds for a submatrix $\mathbf{A}_J$, where $J \subseteq[m]$ is nonempty and of a size equal to the largest number $p$ satisfying:
 %\begin{align}\label{pcond}
-%\sum_{i=\ell}^{m} \deg(i) > (\bar m + 1 - \ell) (\deg(\ell) - 1) \ \ \text{for all } \ell \leq p \leq q.
+%\sum_{i=\ell}^{m} \deg(i) > (\overline m + 1 - \ell) (\deg(\ell) - 1) \ \ \text{for all } \ell \leq p \leq q.
 %\end{align}
@@
 
-%For the benefit of the reader, we prove below the case where we forgo only the constraint that $\bar m = m$.
-This yields the implication $\bar m \geq m$ and \eqref{pcond} reduces to $|J| = \bar m - r(\bar m - m)$.
+%For the benefit of the reader, we prove below the case where we forgo only the constraint that $\overline m = m$.
+This yields the implication $\overline m \geq m$ and \eqref{pcond} reduces to $|J| = \overline m - r(\overline m - m)$.
 The extension to the general result above can be seen by examining how exactly Lemma \ref{NonEmptyLemma} is incorporated into the overall proof.
@@
 
-We now begin our proof of Thm.~\ref{DeterministicUniquenessTheorem} by showing how dictionary recovery \eqref{Cstable} already implies sparse code recovery \eqref{b-PDa} when \mbox{$\varepsilon < L_{2k}(\mathbf{A}) / C_1$} (provided $\mathbf{A}$ satisfies \eqref{SparkCondition}), temporarily assuming (without loss of generality) that $\bar m = m$.
+We now begin our proof of Thm.~\ref{DeterministicUniquenessTheorem} by showing how dictionary recovery \eqref{Cstable} already implies sparse code recovery \eqref{b-PDa} when \mbox{$\varepsilon < L_{2k}(\mathbf{A}) / C_1$} (provided $\mathbf{A}$ satisfies \eqref{SparkCondition}), temporarily assuming (without loss of generality) that $\overline m = m$.
 For $2k$-sparse $\mathbf{x} \in \mathbb{R}^m$, the triangle inequality gives \mbox{$\|(\mathbf{A}-\mathbf{BPD})\mathbf{x}\|_2  \leq C_1\varepsilon \|\mathbf{x}\|_1 \leq C_1 \varepsilon \sqrt{2k}  \|\mathbf{x}\|_2$}.
@@
 \begin{align*}
-\|\mathbf{x}_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\bar x}_i \|_1
-&\leq \frac{\|\mathbf{BPD}(\mathbf{x}_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\bar x}_i)\|_2}{L_{2k}(\mathbf{BPD})} \\
-&\leq \frac{\|(\mathbf{BPD} - \mathbf{A})\mathbf{x}_i\|_2 + \|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\bar x}_i\|_2}{L_{2k}(\mathbf{BPD})} \\
+\|\mathbf{x}_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_i \|_1
+&\leq \frac{\|\mathbf{BPD}(\mathbf{x}_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_i)\|_2}{L_{2k}(\mathbf{BPD})} \\
+&\leq \frac{\|(\mathbf{BPD} - \mathbf{A})\mathbf{x}_i\|_2 + \|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline x}_i\|_2}{L_{2k}(\mathbf{BPD})} \\
 &\leq \frac{\varepsilon (1 + C_1 \|\mathbf{x}_i\|_1)}{L_{2k}(\mathbf{BPD})}.
@@
 
-Fix $\mathbf{A} \in \mathbb{R}^{n \times m}$ satisfying \eqref{SparkCondition} and suppose that for some $\mathbf{B}$ and $1$-sparse $\mathbf{\bar x}_i \in \mathbb{R}^{\bar m}$ we have  $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\bar x}_i\|_2 \leq \varepsilon < L_2(\mathbf{A}) / C_1$ for all $i$.
-Then, there exist $\bar{c}_1, \ldots, \bar{c}_m \in \mathbb{R}$ and a map $\pi: [m] \to [\bar m]$ such that:
+Fix $\mathbf{A} \in \mathbb{R}^{n \times m}$ satisfying \eqref{SparkCondition} and suppose that for some $\mathbf{B}$ and $1$-sparse $\mathbf{\overline x}_i \in \mathbb{R}^{\overline m}$ we have  $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \varepsilon < L_2(\mathbf{A}) / C_1$ for all $i$.
+Then, there exist $\overline{c}_1, \ldots, \overline{c}_m \in \mathbb{R}$ and a map $\pi: [m] \to [\overline m]$ such that:
 \begin{align}\label{1D}
-\|c_j\mathbf{A}_j - \bar{c}_j\mathbf{B}_{\pi(j)}\|_2 \leq \varepsilon,\ \ \text{for $j \in [m]$}.
+\|c_j\mathbf{A}_j - \overline{c}_j\mathbf{B}_{\pi(j)}\|_2 \leq \varepsilon,\ \ \text{for $j \in [m]$}.
 \end{align} 
-Note that $\bar{c}_j \neq 0$, since otherwise we have the contradiction $\|\mathbf{A}_j \|_2 \leq C_1 |c_j| \|\mathbf{A}_j \|_2  < L_2(\mathbf{A}) \leq L_1(\mathbf{A}) = \min_{i \in [m]} \|\mathbf{A}_i\|_2$.
+Note that $\overline{c}_j \neq 0$, since otherwise we have the contradiction $\|\mathbf{A}_j \|_2 \leq C_1 |c_j| \|\mathbf{A}_j \|_2  < L_2(\mathbf{A}) \leq L_1(\mathbf{A}) = \min_{i \in [m]} \|\mathbf{A}_i\|_2$.
 %implies by \eqref{delrho} the contradiction $|c_j| < \min_{\ell \in [m]} | c_\ell |$.
 
-We  now show that $\pi$ is injective (in particular, a permutation if $\bar m = m$).
+We  now show that $\pi$ is injective (in particular, a permutation if $\overline m = m$).
 Suppose that $\pi(i) = \pi(j) = \ell$ for some $i \neq j$ and $\ell$.
-Then, $\|c_{j}\mathbf{A}_{j} - \bar{c}_{j}\mathbf{B}_{\ell}\|_2 \leq \varepsilon$ and $\|c_{i}\mathbf{A}_{i} - \bar{c}_{i} \mathbf{B}_{\ell}\|_2  \leq \varepsilon$.
-Scaling and summing these inequalities by $|\bar{c}_{i}|$ and $|\bar{c}_{j}|$, respectively, and applying the triangle inequality, we obtain:
+Then, $\|c_{j}\mathbf{A}_{j} - \overline{c}_{j}\mathbf{B}_{\ell}\|_2 \leq \varepsilon$ and $\|c_{i}\mathbf{A}_{i} - \overline{c}_{i} \mathbf{B}_{\ell}\|_2  \leq \varepsilon$.
+Scaling and summing these inequalities by $|\overline{c}_{i}|$ and $|\overline{c}_{j}|$, respectively, and applying the triangle inequality, we obtain:
 \begin{align*}
-(|\bar{c}_{i}| + |\bar{c}_{j}|) \varepsilon
-&\geq\|\mathbf{A}(\bar{c}_{i}c_{j} \mathbf{e}_{j} - \bar{c}_{j}c_{i}\mathbf{e}_{i})\|_2 \nonumber \\ 
-&\geq  \left( |\bar{c}_{i}| + |\bar{c}_{j}| \right) L_2(\mathbf{A}) \min_{\ell \in [m]} |c_\ell |,
+(|\overline{c}_{i}| + |\overline{c}_{j}|) \varepsilon
+&\geq\|\mathbf{A}(\overline{c}_{i}c_{j} \mathbf{e}_{j} - \overline{c}_{j}c_{i}\mathbf{e}_{i})\|_2 \nonumber \\ 
+&\geq  \left( |\overline{c}_{i}| + |\overline{c}_{j}| \right) L_2(\mathbf{A}) \min_{\ell \in [m]} |c_\ell |,
 \end{align*}
 which contradicts the bound $\varepsilon < L_2(\mathbf{A})/C_1$.
-Hence, the map $\pi$ is injective and therefore $\bar m \geq m$.
-Setting $\bar J = \pi([m])$ and letting $P = \left( \mathbf{e}_{\pi(1)} \cdots \mathbf{e}_{\pi(m)}\right)$ and $D = \text{diag}(\frac{\bar{c}_1}{c_1},\ldots,\frac{\bar{c}_m}{c_m})$, we see that \eqref{1D} becomes, for all $j \in [m]$:
+Hence, the map $\pi$ is injective and therefore $\overline m \geq m$.
+Setting $\overline J = \pi([m])$ and letting $P = \left( \mathbf{e}_{\pi(1)} \cdots \mathbf{e}_{\pi(m)}\right)$ and $D = \text{diag}(\frac{\overline{c}_1}{c_1},\ldots,\frac{\overline{c}_m}{c_m})$, we see that \eqref{1D} becomes, for all $j \in [m]$:
 \begin{align*}
-\|\mathbf{A}_j - \mathbf{B}_{\bar J}\mathbf{PD}_j\|_2 
-= \|\mathbf{A}_j - \frac{\bar{c}_j}{c_j}\mathbf{B}_{\pi(j)}\|_2 
+\|\mathbf{A}_j - \mathbf{B}_{\overline J}\mathbf{PD}_j\|_2 
+= \|\mathbf{A}_j - \frac{\overline{c}_j}{c_j}\mathbf{B}_{\pi(j)}\|_2 
 \leq \frac{\varepsilon}{|c_j|} 
@@
 
-If for some $n \times \bar m$ matrix $\mathbf{B}$ and map $\pi: \mathcal{H} \mapsto {[\bar m] \choose k}$, we have:
+If for some $n \times \overline m$ matrix $\mathbf{B}$ and map $\pi: \mathcal{H} \mapsto {[\overline m] \choose k}$,
 \begin{align}\label{GapUpperBound}
@@
 \end{align}
-then $\bar m \geq m$, and, provided $\bar m < mr /(r-1)$, there is a permutation matrix $\mathbf{P}$ and invertible diagonal $\mathbf{D}$ such that:
+then $\overline m \geq m$, and, provided $\overline m < mr /(r-1)$, there is a permutation matrix $\mathbf{P}$ and invertible diagonal $\mathbf{D}$ such that:
 \begin{align}\label{MainLemmaBPD}
-\|\mathbf{A}_j - \mathbf{B}_{\bar J} \mathbf{PD}_j\|_2 \leq C_2 \varepsilon, \ \  \text{for } j \in J,
+\|\mathbf{A}_j - \mathbf{B}_{\overline J} \mathbf{PD}_j\|_2 \leq C_2 \varepsilon, \ \  \text{for } j \in J,
 \end{align}
-for some nonempty $J \subseteq [m]$ and $\bar J \subseteq[\bar{m}]$ of size $\bar m - r(\bar m - m)$.
+for some nonempty $J \subseteq [m]$ and $\overline J \subseteq[\overline{m}]$ of size $\overline m - r(\overline m - m)$.
 \end{lemma}
@@
 \end{definition}
-Note that $\theta \in (0,\frac{\pi}{2}]$ implies $0 < \xi \leq 1$.\footnote{We acknowledge the counter-intuitive property that $\theta =  \pi/2$ when $U \subseteq W$}  
+Note that $\theta \in (0,\frac{\pi}{2}]$ implies $0 < \xi \leq 1$.\footnote{We acknowledge the counter-intuitive property that $\theta =  \pi/2$ when $U \subseteq W$.}  
 The constant $C_2$ in Lem.~\ref{MainLemma} can then be expressed as:  
 \begin{align}\label{Cdef2}
-	C_2(\mathbf{A}, \mathcal{H}) := \frac{ (r+1) \max_{j \in [m]} \|\mathbf{A}_j\|_2}{ \min_{\mathcal{G} \subseteq {\mathcal{H} \choose r} \cup {\mathcal{H} \choose r+1}} \xi( \{ \bm{\mathcal{A}}_S \}_{S \in \mathcal{G}}) },
+	C_2(\mathbf{A}, \mathcal{H}) := \frac{ (r+1) \max_{j \in [m]} \|\mathbf{A}_j\|_2}{ \min_{\mathcal{G} \in {\mathcal{H} \choose r+1}} \xi( \{ \bm{\mathcal{A}}_S \}_{S \in \mathcal{G}}) },
 \end{align}
-%
+% C_2(\mathbf{A}, \mathcal{H}) := \frac{ (r+1) \max_{j \in [m]} \|\mathbf{A}_j\|_2}{ \min_{\mathcal{G} \in {\mathcal{H} \choose r} \cup {\mathcal{H} \choose r+1}} \xi( \{ \bm{\mathcal{A}}_S \}
 which we remark is consistent with the assumption on $C_1$ in the proof of the case $k=1$ at the beginning of this section.
@@
 \begin{proof}[Proof of Thm.~\ref{DeterministicUniquenessCorollary} for $k < m$] 
-We demonstrate the existence of a map $\pi: \mathcal{H} \to 2^{[\bar m]}$ for which the distance $d(\bm{\mathcal{A}}_S, \bm{\mathcal{B}}_{\pi(S)})$ is controlled by $\varepsilon$.
+We demonstrate the existence of a map $\pi: \mathcal{H} \to 2^{[\overline m]}$ for which the distance $d(\bm{\mathcal{A}}_S, \bm{\mathcal{B}}_{\pi(S)})$ is controlled by $\varepsilon$.
 Applying Lem.~\ref{MainLemma} then completes the proof.
 
-%We shall show that for every $S \in \mathcal{H}$ there is some $\bar S \in {[\bar m] \choose k}$ for which the distance $d(\bm{\mathcal{A}}_S, \bm{\mathcal{B}}_{\bar S})$ is controlled by $\varepsilon$.
-Applying Lem.~\ref{MainLemma} with the map $\pi$ defined by $S \mapsto \bar S$ then completes the proof.
+%We shall show that for every $S \in \mathcal{H}$ there is some $\overline S \in {[\overline m] \choose k}$ for which the distance $d(\bm{\mathcal{A}}_S, \bm{\mathcal{B}}_{\overline S})$ is controlled by $\varepsilon$.
+Applying Lem.~\ref{MainLemma} with the map $\pi$ defined by $S \mapsto \overline S$ then completes the proof.
 
-Since there are more than $(k-1){\bar m \choose k}$ vectors $\mathbf{x}_i$ supported in $S$, the pigeonhole principle gives $\bar S \in {[\bar m] \choose k}$ and a set of $k$ indices $K \subseteq I(S)$ with all $\mathbf{\bar x}_i$, $i \in K$, supported in $\bar S$.
+Since there are more than $(k-1){\overline m \choose k}$ vectors $\mathbf{x}_i$ supported in $S$, the pigeonhole principle gives $\overline S \in {[\overline m] \choose k}$ and a set of $k$ indices $K \subseteq I(S)$ with all $\mathbf{\overline x}_i$, $i \in K$, supported in $\overline S$.
 
@@
 Fixing $\mathbf{0} \neq \mathbf{y} \in \bm{\mathcal{A}}_S$, there then exists $\mathbf{0} \neq \mathbf{c} = (c_1, \ldots, c_k) \in \mathbb{R}^k$ such that $\mathbf{y} = \mathbf{AX}_K\mathbf{c}$.
-Setting \mbox{$\mathbf{\bar{y}} = \mathbf{B\bar{X}}_K\mathbf{c} \in \bm{\mathcal{B}}_{\bar S}$}, we have:
+Setting \mbox{$\mathbf{\overline{y}} = \mathbf{B\overline{X}}_K\mathbf{c} \in \bm{\mathcal{B}}_{\overline S}$}, we have:
 \begin{align*}
-\|\mathbf{y} - \mathbf{\bar{y}}\|_2 
-&= \|\sum_{i=1}^k c_i(\mathbf{AX}_K - \mathbf{B\bar{X}}_K)_i\|_2
+\|\mathbf{y} - \mathbf{\overline{y}}\|_2 
+&= \|\sum_{i=1}^k c_i(\mathbf{AX}_K - \mathbf{B\overline{X}}_K)_i\|_2
 \leq \varepsilon \sum_{i=1}^k |c_i| \\
@@
 \begin{align}\label{rhs222}
-d(\bm{\mathcal{A}}_S, \bm{\mathcal{B}}_{\bar S}) 
+d(\bm{\mathcal{A}}_S, \bm{\mathcal{B}}_{\overline S}) 
 \leq \frac{\varepsilon}{  L(\mathbf{AX}_{K}) } \leq \varepsilon \frac{C_1}{C_2},
@@
 \begin{proof}[Proof of Thm.~\ref{SLCopt}]
-We bound the number of $k$-sparse $\mathbf{\bar x}_i$ and then apply Thm.~\ref{DeterministicUniquenessCorollary}. 
-%We now apply this fact to bound the number of $k$-sparse $\mathbf{\bar x}_i$. 
-Let $n_p$ be the number of $\mathbf{\bar x}_i$ with $\|\mathbf{\bar x}_i\|_0 = p$.
+We bound the number of $k$-sparse $\mathbf{\overline x}_i$ and then apply Thm.~\ref{DeterministicUniquenessCorollary}. 
+%We now apply this fact to bound the number of $k$-sparse $\mathbf{\overline x}_i$. 
+Let $n_p$ be the number of $\mathbf{\overline x}_i$ with $\|\mathbf{\overline x}_i\|_0 = p$.
 Since the $\mathbf{x}_i$ are all $k$-sparse, by \eqref{minsum} we have:
-\mbox{$k \sum_{p = 0}^{\bar m} n_p \geq \sum_{i=0}^N \|\mathbf{x}_i\|_0 \geq \sum_{i=0}^N \|\mathbf{\bar x}_i\|_0 = \sum_{p=0}^{\bar m} p n_p.$}
+\mbox{$k \sum_{p = 0}^{\overline m} n_p \geq \sum_{i=0}^N \|\mathbf{x}_i\|_0 \geq \sum_{i=0}^N \|\mathbf{\overline x}_i\|_0 = \sum_{p=0}^{\overline m} p n_p.$}
 Hence,
 \begin{align}\label{eqn}
-\sum_{p = k+1}^{\bar m} n_p \leq \sum_{p = k+1}^{\bar m} (p-k) n_p \leq \sum_{p = 0}^k (k-p)n_p \leq k \sum_{p = 0}^{k-1} n_p,
+\sum_{p = k+1}^{\overline m} n_p \leq \sum_{p = k+1}^{\overline m} (p-k) n_p \leq \sum_{p = 0}^k (k-p)n_p \leq k \sum_{p = 0}^{k-1} n_p,
 \end{align}
 %
-demonstrating that the number vectors $\mathbf{\bar x}_i$ that are \emph{not} $k$-sparse is controlled by how many are $(k-1)$-sparse.
+demonstrating that the number vectors $\mathbf{\overline x}_i$ that are \emph{not} $k$-sparse is controlled by how many are $(k-1)$-sparse.
 
-Next, observe that no more than $(k-1)|\mathcal{H}|$ of the $\mathbf{\bar x}_i$ share a support $\bar S$ of size less than $k$; otherwise, by the pigeonhole principle, at least $k$ of these indices $i$ belong to the same $K \subseteq I(S)$ for some $S \in \mathcal{H}$ and (as argued previously) \eqref{rhs222} follows.
-Since the right-hand side of \eqref{rhs222} is less than one, by \eqref{dimLem} we have the contradiction $k = \dim(\bm{\mathcal{A}}_S) \leq \dim(\bm{\mathcal{B}}_{\bar S}) \leq |\bar S|.$
+Next, observe that no more than $(k-1)|\mathcal{H}|$ of the $\mathbf{\overline x}_i$ share a support $\overline S$ of size less than $k$; otherwise, by the pigeonhole principle, at least $k$ of these indices $i$ belong to the same $K \subseteq I(S)$ for some $S \in \mathcal{H}$ and (as argued previously) \eqref{rhs222} follows.
+Since the right-hand side of \eqref{rhs222} is less than one, by \eqref{dimLem} we have the contradiction $k = \dim(\bm{\mathcal{A}}_S) \leq \dim(\bm{\mathcal{B}}_{\overline S}) \leq |\overline S|.$
 
-The total number of $(k-1)$-sparse vectors $\mathbf{\bar x}_i$ thus can not exceed $|\mathcal{H}|(k-1){ \bar m \choose k-1}$.
-By \eqref{eqn}, no more than $|\mathcal{H}|k(k-1){ \bar m \choose k-1}$ vectors $\mathbf{\bar x}_i$ are not $k$-sparse.
-Since for every $S \in \mathcal{H}$ there are over $(k-1)\left[ {\bar m \choose k} + |\mathcal{H}|k{ \bar m \choose k-1} \right]$ vectors $\mathbf{x}_i$ supported there, it must be that more than $(k-1){\bar m \choose k}$ of them have corresponding $\mathbf{\bar x}_i$ that are $k$-sparse.
+The total number of $(k-1)$-sparse vectors $\mathbf{\overline x}_i$ thus can not exceed $|\mathcal{H}|(k-1){ \overline m \choose k-1}$.
+By \eqref{eqn}, no more than $|\mathcal{H}|k(k-1){ \overline m \choose k-1}$ vectors $\mathbf{\overline x}_i$ are not $k$-sparse.
+Since for every $S \in \mathcal{H}$ there are over $(k-1)\left[ {\overline m \choose k} + |\mathcal{H}|k{ \overline m \choose k-1} \right]$ vectors $\mathbf{x}_i$ supported there, it must be that more than $(k-1){\overline m \choose k}$ of them have corresponding $\mathbf{\overline x}_i$ that are $k$-sparse.
 The result now follows from Thm.~\ref{DeterministicUniquenessCorollary}.
@@
 \begin{proof}[Proof (sketch) of Thm.~\ref{robustPolythm}]
-Let $\textbf{M}$ be the matrix with columns $\mathbf{A}\mathbf{x}_i$, $i \in [N]$.  Consider the polynomial in the indeterminate entries of $\mathbf{A}$ and $\mathbf{x}_i$:
-\begin{align*}
-g(\mathbf{A}, \{\mathbf{x}_i\}_{i=1}^N) := \prod_{S \in {[N] \choose 2k}} \sum_{S' \in {[n] \choose 2k}} (\det \textbf{M}_{S',S})^2,
-\end{align*}
+Let $\textbf{M}$ be the matrix with columns $\mathbf{A}\mathbf{x}_i$, $i \in [N]$.  Consider the polynomial in the entries of $\mathbf{A}$ and $\mathbf{x}_i$:
+$g(\mathbf{A}, \{\mathbf{x}_i\}_{i=1}^N) := \prod_{S \in {[N] \choose 2k}} \sum_{S' \in {[n] \choose 2k}} (\det \textbf{M}_{S',S})^2$,
 with notation as in Sec.~\ref{Results}.  
@@
 \end{proof}
+
+\vspace{-.5 cm}
 
@@
 
+% \vspace{-.2 cm}
+
 \acknow{We thank Friedrich Sommer and Darren Rhea for early thoughts, and Ian Morris for posting \eqref{eqdim} online.}
@@
 
-%\vspace{-.15 cm}
+% \vspace{-.2 cm}
 
@@
 \begin{proof}
-By induction it is enough to prove the case $|n| = 2$, but this case follows directly from the assumption.
+By induction, it is enough to prove the trivial case $\ell = 2$.
 %Clearly, for any map $f$, if $w \in f(U \cap V)$ then $w \in f(U)$ and $w \in f(V)$, hence $w \in f(U) \cap f(V)$.
@@
 \end{proof}
-%\vspace{-.2 cm}
+% \vspace{-.4 cm}
+
 \begin{lemma}\label{DistanceToIntersectionLemma}
@@
 For  $\mathbf{x} \in \mathbb{R}^m$, we have (where $\xi$ is given in Def.~\ref{SpecialSupportSet}):
-%\vspace{-.2 cm}
 \begin{align}\label{DTILeq}
@@
 \end{lemma}
-%\vspace{-.3 cm}
+\vspace{-.3 cm}
 \begin{proof} 
@@
 Together with $\Pi_{V_\ell} \Pi_V = \Pi_V$ for all $\ell \in [k]$ and $\Pi_V^2 = \Pi_V$, this implies that $\|\Pi_{V_k} \cdots \Pi_{V_1}\mathbf{x}  - \Pi_V \mathbf{x} \|_2$ satisfies:
-\[\| ( \Pi_{V_k} \cdots\Pi_{V_1} - \Pi_V ) (\mathbf{x} - \Pi_V\mathbf{x})\|_2 \leq z\|\mathbf{x} - \Pi_V\mathbf{x}\|_2.\]
+$\| ( \Pi_{V_k} \cdots\Pi_{V_1} - \Pi_V ) (\mathbf{x} - \Pi_V\mathbf{x})\|_2 \leq z\|\mathbf{x} - \Pi_V\mathbf{x}\|_2$.
 
@@
 \end{proof}
-%\vspace{-.4 cm}
 \begin{lemma}\label{NonEmptyLemma} 
 Fix an $r$-regular hypergraph $\mathcal{H} \subseteq 2^{[m]}$ satisfying the SIP.
-If the map $\pi: \mathcal{H} \to 2^{[\bar m]}$ has $\sum_{S \in \mathcal{H}} |\pi(S)| \geq \sum_{S \in \mathcal{H}} |S|$ and:
+If the map $\pi: \mathcal{H} \to 2^{[\overline m]}$ has $\sum_{S \in \mathcal{H}} |\pi(S)| \geq \sum_{S \in \mathcal{H}} |S|$ and:
 \begin{align}\label{cond}
@@
 %
-then $\bar m \geq m$, and if $\bar m < mr / (r-1)$ then the association $i \mapsto \cap \pi(\sigma(i))$ is an injective map to $[\bar m]$ from some $J \subseteq [m]$ of size $\bar m - r(\bar m - m)$.
-%In particular, if $\bar m = m$ then $\pi$ is induced by a permutation on $[m]$.
+then $\overline m \geq m$, and if $\overline m < mr / (r-1)$ then the map $i \mapsto \cap \pi(\sigma(i))$ is an injective map to $[\overline m]$ from some $J \subseteq [m]$ of size $\overline m - r(\overline m - m)$.
+%In particular, if $\overline m = m$ then $\pi$ is induced by a permutation on $[m]$.
 \end{lemma}
+\begin{proof}
+Consider the set: $T_1 := \{(i, S): i \in \pi(S), S \in \mathcal{H}\}$, which number $|T_1| = \sum_{S \in \mathcal{H}} |\pi(S)| \geq \sum_{S \in \mathcal{H}} |S| = \sum_{i \in [m]} \deg_\mathcal{H}(i) = mr$.
+Note that \eqref{cond} implies $|T_1| \leq \overline m r$, since otherwise pigeonholing the elements of $T_1$ with respect to their possible first indices $[\overline m]$ would imply $\deg_\mathcal{H}(i) > r$ for some $i \in [m]$.
+Thus, $\overline m \geq m$.
 
-\begin{proof}
-Consider the collection of pairs: $T_1 := \{(i, S): i \in \pi(S), S \in \mathcal{H}\}$, which number $|T_1| = \sum_{S \in \mathcal{H}} |\pi(S)| \geq \sum_{S \in \mathcal{H}} |S| = \sum_{i \in [m]} \deg_\mathcal{H}(i) = mr$.
-Note that \eqref{cond} implies $|T_1| \leq \bar m r$, since otherwise pigeonholing the elements of $T_1$ with respect to their possible first indices $[\bar m]$ would imply $\deg_\mathcal{H}(i) > r$ for some $i \in [m]$.
-Thus $\bar m \geq m$.
-
-If $\bar m < mr / (r-1)$ then $p := \bar m - r( \bar m - m)$ is positive and $|T_1| \geq \bar m (r - 1) + p$.
-Pigeonholing $T_1$ into $[\bar m]$ again, there must be $r$ elements of $T_1$ sharing the same first index.
+If $\overline m < mr / (r-1)$, then $p := \overline m - r( \overline m - m)$ is positive and $|T_1| \geq \overline m (r - 1) + p$.
+Pigeonholing $T_1$ into $[\overline m]$ again, there must be $r$ elements of $T_1$ sharing the same first index.
 By \eqref{cond}, the intersection of the set $\mathcal{G}_1$ of their second indices is nonempty; hence, $|\cap \mathcal{G}_1| = 1$ by $r$-regularity and the SIP.
-Since $\cap \pi(\mathcal{G}_1)$ is nonempty, applying \eqref{cond} again gives $\cap \pi(\mathcal{G}_1) = \{i_1\}$ for some $i_1 \in [\bar m]$.
+Since $\cap \pi(\mathcal{G}_1)$ is nonempty, applying \eqref{cond} again gives $\cap \pi(\mathcal{G}_1) = \{i_1\}$ for some $i_1 \in [\overline m]$.
 If $p=1$, then we are done.
-Otherwise, define $T_2 := T_1 \setminus \{(i,S) \in T_1: i = i_1\}$, which contains $|T_2| = |T_1| - r \geq (\bar m - 1)(r-1) + (p-1)$ ordered pairs having $\bar m - 1$ distinct first indices.
-Repeating the above arguments produces a (necessarily, by $r$-regularity and the SIP) distinct $\mathcal{G}_2 \in {\mathcal{H} \choose r}$ and corresponding $i_2 \in [\bar m]$.
+Otherwise, define $T_2 := T_1 \setminus \{(i,S) \in T_1: i = i_1\}$, which contains $|T_2| = |T_1| - r \geq (\overline m - 1)(r-1) + (p-1)$ ordered pairs having $\overline m - 1$ distinct first indices.
+Repeating the above arguments produces a (necessarily, by $r$-regularity and the SIP) distinct $\mathcal{G}_2 \in {\mathcal{H} \choose r}$ and corresponding $i_2 \in [\overline m]$.
 Finally, iterating this $p$ times in total yields the set of singletons \mbox{$J = \{\cap \mathcal{G}_1, \ldots, \cap \mathcal{G}_p\} \subseteq [m]$}.
@@
 \begin{proof}[Proof of Lem.~\ref{MainLemma}]
-%We will show that the bound \eqref{GapUpperBound} trickles through the intersection semi-lattices of $\{\bm{\mathcal{A}}_S\}_{S \in \mathcal{H}}$ and $\{\bm{\mathcal{B}}_{\bar S}\}_{\bar S \in \pi(\mathcal{H})}$ to yield \eqref{MainLemmaBPD} by virtue of the SIP.
-
+%We will show that the bound \eqref{GapUpperBound} trickles through the intersection semi-lattices of $\{\bm{\mathcal{A}}_S\}_{S \in \mathcal{H}}$ and $\{\bm{\mathcal{B}}_{\overline S}\}_{\overline S \in \pi(\mathcal{H})}$ to yield \eqref{MainLemmaBPD} by virtue of the SIP.
 We begin by showing that $\dim(\bm{\mathcal{B}}_{\pi(S)}) = \dim(\bm{\mathcal{A}}_S)$ for all $S \in \mathcal{H}$.
@@
 Since $\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})} \subseteq \cap_{S \in \mathcal{G}} \bm{\mathcal{B}}_{\pi(S)}$, if $\cap_{S \in \mathcal{G}} \bm{\mathcal{B}}_{\pi(S)} = \{\textbf{0}\}$, then we must have $|\cap \pi(\mathcal{G})| = 0$ (as the columns of $\mathbf{B}_{\pi(S)}$ are linearly independent) and \eqref{cond} is trivially true.
-Suppose then that the intersection is not the zero vector.
+Suppose then that the intersection is not zero.
 Keeping in mind that $d(U',V) \leq d(U,V)$ whenever $U' \subseteq U$ and applying (in order) Lem.~\ref{spanIntersectionLemma}, Lem.~\ref{DistanceToIntersectionLemma}, \eqref{eqdim}, \eqref{GapUpperBound}, and \eqref{Cdef2} gives:
@@
 
-Now, by Lem.~\ref{NonEmptyLemma}, the association $i \mapsto \cap \pi(\sigma(i))$ defines an injective map $\bar \pi: J \to [\bar m]$ for some $J \subseteq [m]$ of size $\bar m - r(\bar m - m)$, and we can be sure that $\mathbf{B}_{\bar \pi(i)} \neq \mathbf{0}$ for all $i \in J$ since the columns of $\mathbf{B}_{\pi(S)}$ are linearly independent for all $S \in \mathcal{H}$.
-It then follows from \eqref{eqdim} and \eqref{randoml} that $d\left( \bm{\mathcal{A}}_i, \bm{\mathcal{B}}_{\bar \pi(i)} \right) \leq C_2 \varepsilon / \max_i \|\mathbf{A}_i\|_2$ for all $i \in J$.
-Fixing $\bar \varepsilon = C_2\varepsilon$ and letting $c_i = \|\mathbf{A}_i\|_2^{-1}$, we thus have that for every basis vector $\mathbf{e}_i \in \mathbb{R}^m$ with $i \in J$ there exists some $\bar{c}_i \in \mathbb{R}$ such that $\|c_i\mathbf{A}\mathbf{e}_i - \bar{c}_i \mathbf{B}\mathbf{e}_{\bar \pi(i)}\|_2 \leq \bar \varepsilon < L_2(\mathbf{A}) \min_{i\in J} |c_i|$.
+By Lem.~\ref{NonEmptyLemma}, the association $i \mapsto \cap \pi(\sigma(i))$ is an injective map $\overline \pi: J \to [\overline m]$ for some $J \subseteq [m]$ of size $\overline m - r(\overline m - m)$, and $\mathbf{B}_{\overline \pi(i)} \neq \mathbf{0}$ for all $i \in J$ since the columns of $\mathbf{B}_{\pi(S)}$ are linearly independent for all $S \in \mathcal{H}$.
+It then follows from \eqref{eqdim} and \eqref{randoml} that $d\left( \bm{\mathcal{A}}_i, \bm{\mathcal{B}}_{\overline \pi(i)} \right) \leq C_2 \varepsilon / \max_i \|\mathbf{A}_i\|_2$ for all $i \in J$.
+Fixing $\overline \varepsilon = C_2\varepsilon$ and letting $c_i = \|\mathbf{A}_i\|_2^{-1}$, we thus have that for each $\mathbf{e}_i \in \mathbb{R}^m$ with $i \in J$ there exists some $\overline{c}_i \in \mathbb{R}$ such that $\|c_i\mathbf{A}\mathbf{e}_i - \overline{c}_i \mathbf{B}\mathbf{e}_{\overline \pi(i)}\|_2 \leq \overline \varepsilon < L_2(\mathbf{A}) \min_{i\in J} |c_i|$.
 But this is exactly the supposition in \eqref{1D}, and the result follows from the case $k=1$ in Sec.~\ref{DUT} applied to the submatrix $\mathbf{A}_J$.
@@
 %\begin{problem}\label{OptimizationProblemL1}
-%Find a matrix $\mathbf{B}$ and vectors \mbox{$\mathbf{\bar x}_1, \ldots, \mathbf{\bar x}_N \in \mathbb{R}^m$} that solve:
+%Find a matrix $\mathbf{B}$ and vectors \mbox{$\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N \in \mathbb{R}^m$} that solve:
 %\begin{align}\label{minsum}
-%\min \sum_{i = 1}^N \|\mathbf{\bar x}_i\|_1 \ \ 
-%\text{subject to} \ \ \|\mathbf{z}_i - \mathbf{B}\mathbf{\bar x}_i\|_2 \leq \eta, \ \text{for all $i$}.
+%\min \sum_{i = 1}^N \|\mathbf{\overline x}_i\|_1 \ \ 
+%\text{subject to} \ \ \|\mathbf{z}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \eta, \ \text{for all $i$}.
 %\end{align}
@@
 %\item The coefficients of all $k$-sparse $\mathbf{x}_i$ are drawn from $[-\beta, \beta]$, where $\beta < \frac{\alpha(k+1)}{k}$.
-%\item More than $(k-1){\bar m \choose k} + q$ vectors $\mathbf{x}_i$ are supported in each $S \in \mathcal{H}$, where
-%\[ q = \left[\frac{\alpha}{\beta}(k+1) - k\right]^{-1}k|\mathcal{H}|(k-1){\bar m \choose k-1}. \]
+%\item More than $(k-1){\overline m \choose k} + q$ vectors $\mathbf{x}_i$ are supported in each $S \in \mathcal{H}$, where
+%\[ q = \left[\frac{\alpha}{\beta}(k+1) - k\right]^{-1}k|\mathcal{H}|(k-1){\overline m \choose k-1}. \]
 %\end{enumerate}
-%Then all solutions to Prob.~\ref{OptimizationProblemL1} for which the nonzero elements of all $\mathbf{\bar x}_i$ lie outside $[-\alpha, \alpha]$ necessarily satisfy the implications \eqref{Cstable} and \eqref{b-PDa} of Thm.~\ref{DeterministicUniquenessTheorem}.
+%Then all solutions to Prob.~\ref{OptimizationProblemL1} for which the nonzero elements of all $\mathbf{\overline x}_i$ lie outside $[-\alpha, \alpha]$ necessarily satisfy the implications \eqref{Cstable} and \eqref{b-PDa} of Thm.~\ref{DeterministicUniquenessTheorem}.
 %\end{corollary}
@@
 %\begin{proof}[Proof of Cor.~\ref{SLCopt}]
-%We bound the number of $k$-sparse $\mathbf{\bar x}_i$ and then apply Thm.~\ref{DeterministicUniquenessCorollary}.
-First, observe that no more than $(k-1)|\mathcal{H}|$ of the $\mathbf{\bar x}_i$ share a support $\bar S$ of size less than $k$; otherwise, by the pigeonhole principle, at least $k$ of these indices $i$ belong to the same $K \subseteq I(S)$ for some $S \in \mathcal{H}$ and (as argued previously) \eqref{rhs222} follows.
-Since the right-hand side of \eqref{rhs222} is less than one, by \eqref{dimLem} we have the contradiction $k = \dim(\bm{\mathcal{A}}_S) \leq \dim(\bm{\mathcal{B}}_{\bar S}) \leq |\bar S|.$ The total number of $(k-1)$-sparse vectors $\mathbf{\bar x}_i$ can thus not exceed $|\mathcal{H}|(k-1){ \bar m \choose k-1}$.
+%We bound the number of $k$-sparse $\mathbf{\overline x}_i$ and then apply Thm.~\ref{DeterministicUniquenessCorollary}.
+First, observe that no more than $(k-1)|\mathcal{H}|$ of the $\mathbf{\overline x}_i$ share a support $\overline S$ of size less than $k$; otherwise, by the pigeonhole principle, at least $k$ of these indices $i$ belong to the same $K \subseteq I(S)$ for some $S \in \mathcal{H}$ and (as argued previously) \eqref{rhs222} follows.
+Since the right-hand side of \eqref{rhs222} is less than one, by \eqref{dimLem} we have the contradiction $k = \dim(\bm{\mathcal{A}}_S) \leq \dim(\bm{\mathcal{B}}_{\overline S}) \leq |\overline S|.$ The total number of $(k-1)$-sparse vectors $\mathbf{\overline x}_i$ can thus not exceed $|\mathcal{H}|(k-1){ \overline m \choose k-1}$.
 
@@
 %\begin{align*}
-%\alpha \sum_i \|\mathbf{\bar x}_i\|_0 \leq \sum_i \|\mathbf{\bar x}_i\|_1 \leq \sum_i \|\mathbf{x}_i\|_1 \leq \beta \sum_i \|\mathbf{x}_i\|_0.
+%\alpha \sum_i \|\mathbf{\overline x}_i\|_0 \leq \sum_i \|\mathbf{\overline x}_i\|_1 \leq \sum_i \|\mathbf{x}_i\|_1 \leq \beta \sum_i \|\mathbf{x}_i\|_0.
 %\end{align*}
 
-%We now apply these facts to bound the number of $k$-sparse $\mathbf{\bar x}_i$.
-Let $n_p$ be the number of $\mathbf{\bar x}_i$ with $\|\mathbf{\bar x}_i\|_0 = p$.
+%We now apply these facts to bound the number of $k$-sparse $\mathbf{\overline x}_i$.
+Let $n_p$ be the number of $\mathbf{\overline x}_i$ with $\|\mathbf{\overline x}_i\|_0 = p$.
 Since the $\mathbf{x}_i$ are all $k$-sparse, we have:
 %\begin{align*}
-%k \sum_{p = 0}^{\bar m} n_p = k N \geq \sum_{i=0}^N \|\mathbf{x}_i\|_0 \geq \frac{\alpha}{\beta} \sum_{i=0}^N \|\mathbf{\bar x}_i\|_0 = \frac{\alpha}{\beta} \sum_{p=0}^{\bar m} p n_p.
+%k \sum_{p = 0}^{\overline m} n_p = k N \geq \sum_{i=0}^N \|\mathbf{x}_i\|_0 \geq \frac{\alpha}{\beta} \sum_{i=0}^N \|\mathbf{\overline x}_i\|_0 = \frac{\alpha}{\beta} \sum_{p=0}^{\overline m} p n_p.
 %\end{align*}
@@
 %\begin{align*}
-%\left[ \frac{\alpha(k+1)}{\beta} - k\right] \sum_{p = k+1}^{\bar m} n_p 
-%&\leq \sum_{p = k+1}^{\bar m} (\frac{\alpha}{\beta} p-k) n_p
+%\left[ \frac{\alpha(k+1)}{\beta} - k\right] \sum_{p = k+1}^{\overline m} n_p 
+%&\leq \sum_{p = k+1}^{\overline m} (\frac{\alpha}{\beta} p-k) n_p
 %\leq \sum_{p = 0}^k (k - \frac{\alpha}{\beta} p)n_p \\
 %&\leq k \sum_{p = 0}^k n_p 
-%\leq k(1-\frac{\alpha}{\beta})n_k + k|\mathcal{H}|(k-1){ \bar m \choose k-1}
+%\leq k(1-\frac{\alpha}{\beta})n_k + k|\mathcal{H}|(k-1){ \overline m \choose k-1}
 %\end{align*}
 
-%[Shit, we need $\alpha = \beta$.] Therefore, no more than $q$ vectors $\mathbf{\bar x}_i$ are \emph{not} $k$-sparse.
-Since for every $S \in \mathcal{H}$ there are over $(k-1){\bar m \choose k} + q$ vectors $\mathbf{x}_i$ supported there, it follows that more than $(k-1){\bar m \choose k}$ of them have corresponding $\mathbf{\bar x}_i$ that are $k$-sparse.
+%[Shit, we need $\alpha = \beta$.] Therefore, no more than $q$ vectors $\mathbf{\overline x}_i$ are \emph{not} $k$-sparse.
+Since for every $S \in \mathcal{H}$ there are over $(k-1){\overline m \choose k} + q$ vectors $\mathbf{x}_i$ supported there, it follows that more than $(k-1){\overline m \choose k}$ of them have corresponding $\mathbf{\overline x}_i$ that are $k$-sparse.
 The result now follows directly from Thm.~\ref{DeterministicUniquenessCorollary}.
@@
 %\begin{corollary}\label{SLCoptL1}
-%If all of the assumptions of Thm.\ref{DeterministicUniquenessTheorem} hold, only now with more than $(k-1)\left[ {\bar m \choose k} + |\mathcal{H}|k{\bar m \choose k-1}\right]$ vectors $\mathbf{x}_i$ supported in each $S \in \mathcal{H}$, then every solution to Prob.~\ref{OptimizationProblemL1} for which the average absolute nonzero coefficient of the $\mathbf{\bar x}_i$ is bounded below by that of the $\mathbf{x}_i$ necessarily satisfies the implications \eqref{Cstable} and \eqref{b-PDa} of Thm.~\ref{DeterministicUniquenessTheorem}.
+%If all of the assumptions of Thm.\ref{DeterministicUniquenessTheorem} hold, only now with more than $(k-1)\left[ {\overline m \choose k} + |\mathcal{H}|k{\overline m \choose k-1}\right]$ vectors $\mathbf{x}_i$ supported in each $S \in \mathcal{H}$, then every solution to Prob.~\ref{OptimizationProblemL1} for which the average absolute nonzero coefficient of the $\mathbf{\overline x}_i$ is bounded below by that of the $\mathbf{x}_i$ necessarily satisfies the implications \eqref{Cstable} and \eqref{b-PDa} of Thm.~\ref{DeterministicUniquenessTheorem}.
 %\end{corollary}
@@
 %\begin{align*}
-%\alpha \sum_i \|\mathbf{\bar x}_i\|_0 \leq \sum_i \|\mathbf{\bar x}_i\|_1 \leq \sum_i \|\mathbf{x}_i\|_1 = \alpha \sum_i \|\mathbf{x}_i\|_0.
+%\alpha \sum_i \|\mathbf{\overline x}_i\|_0 \leq \sum_i \|\mathbf{\overline x}_i\|_1 \leq \sum_i \|\mathbf{x}_i\|_1 = \alpha \sum_i \|\mathbf{x}_i\|_0.
 %\end{align*}

### 2017-11-23 manuscripts/PNAS/second review/resub/chazthm_pnas_resub.tex
notation

@@
 \begin{problem}\label{OptimizationProblem}
-Find $\mathbf{B}$ and \mbox{$\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N \in \mathbb{R}^m$} that solve:
+Find $\mathbf{B}$ and \mbox{$\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N \in \mathbb{R}^{\overline m}$} that solve:
 \begin{align}\label{minsum}
@@
 We generalize the  lower bound to a domain-restricted \emph{union of subspaces} model \cite{vidal2005generalized} derived from a hypergraph $\mathcal{H} \subseteq {[m] \choose k}$.
-Letting $\mathbf{M}_J$ denote the submatrix formed by the columns of $\mathbf{M}$ indexed by $J \subseteq [m]$ (with $\mathbf{M}_\emptyset := \mathbf{0}$), we define:
+Letting $\mathbf{M}_S$ denote the submatrix formed by the columns of $\mathbf{M}$ indexed by $S \subseteq [m]$ (with $\mathbf{M}_\emptyset := \mathbf{0}$), we define:
 %\begin{align*} 
@@
 Note also that $L_2 \geq L_{2\mathcal{H}} \geq L_{2k}$ if $\mathcal{H} \subseteq {[m] \choose k}$ has $\cup \mathcal{H} = [m]$.
+In the sections that follow, we will write $\bm{\mathcal{M}}_S$ to denote the column-span of a submatrix $\mathbf{M}_S$, and $\bm{\mathcal{M}}_\mathcal{G}$ to denote $\{\bm{\mathcal{M}}_S\}_{S \in \mathcal{G}}$.
 
@@
 
-Our result in combinatorial matrix analysis is the following. Let $\bm{\mathcal{M}}_S$ denote the column-span of a submatrix $\mathbf{M}_S$.
+Our result in combinatorial matrix analysis is the following.
 
@@
 \begin{definition}\label{SpecialSupportSet}\label{FriedrichsDefinition}
-For subspaces $V_1, \ldots, V_\ell \subseteq \mathbb{R}^m$, set $\xi := 1$ when $\ell = 1$ and define for $\ell \geq 2$:
+For a collection of real subspaces $\mathcal{V} = \{V_i\}_{i=1}^\ell$, define $\xi := 1$ when $|\mathcal{V}| = 1$ and otherwise:
 \begin{align*}
-\xi(\{V_i\}_{i=1}^\ell) := 1 - \left(1 -  \max \prod_{i=1}^{\ell-1} \sin^2  \theta \left(V_i, \cap_{j>i} V_j \right)  \right)^{1/2},
+\xi(\mathcal{V}) := 1 - \left(1 -  \max \prod_{i=1}^{\ell-1} \sin^2  \theta \left(V_i, \cap_{j>i} V_j \right)  \right)^{1/2},
 \end{align*} 
@@
 \end{definition}
-Note that $\theta \in (0,\frac{\pi}{2}]$ implies $0 < \xi \leq 1$.\footnote{We acknowledge the counter-intuitive property that $\theta =  \pi/2$ when $U \subseteq W$.}  
+Note that $\theta \in (0,\frac{\pi}{2}]$ implies $0 < \xi \leq 1$, and that $\xi(\mathcal{V}') \geq \xi(\mathcal{V})$ when $\mathcal{V}' \subseteq \mathcal{V}$.\footnote{We acknowledge the counter-intuitive property that $\theta =  \pi/2$ when $U \subseteq W$.}
 The constant $C_2$ in Lem.~\ref{MainLemma} can then be expressed as:  
 \begin{align}\label{Cdef2}
-	C_2(\mathbf{A}, \mathcal{H}) := \frac{ (r+1) \max_{j \in [m]} \|\mathbf{A}_j\|_2}{ \min_{\mathcal{G} \in {\mathcal{H} \choose r+1}} \xi( \{ \bm{\mathcal{A}}_S \}_{S \in \mathcal{G}}) },
+	C_2(\mathbf{A}, \mathcal{H}) := \frac{ (r+1) \max_{j \in [m]} \|\mathbf{A}_j\|_2}{ \min_{\mathcal{G} \in {\mathcal{H} \choose r+1}} \xi( \bm{\mathcal{A}}_\mathcal{G} ) },
 \end{align}
@@
 Fix $k \geq 2$.
-Let $V_1, \ldots, V_k$ be subspaces of $\mathbb{R}^m$ and set $V = \cap_{i = 1}^k V_i$.
+Let $\mathcal{V} = \{V_i\}_{i=1}^k$ be a collection of subspaces of $\mathbb{R}^m$ and set $V = \cap_{i = 1}^k V_i$.
 For  $\mathbf{x} \in \mathbb{R}^m$, we have (where $\xi$ is given in Def.~\ref{SpecialSupportSet}):
 \begin{align}\label{DTILeq}
-\text{\rm dist}(\mathbf{x}, V) \leq \frac{1}{\xi(\{V_i\}_{i = 1}^k)} \sum_{i=1}^k \text{\rm dist}(\mathbf{x}, V_i).
+\text{\rm dist}(\mathbf{x}, V) \leq \frac{1}{\xi(\mathcal{V})} \sum_{i=1}^k \text{\rm dist}(\mathbf{x}, V_i).
 \end{align}
@@
 
-Finally, substituting this into \eqref{f} and rearranging produces \eqref{DTILeq} after replacing $1 - z$ with $\xi(\{V_i\}_{i=1}^k)$.
+Finally, substituting this into \eqref{f} and rearranging produces \eqref{DTILeq} after replacing $1 - z$ with $\xi(\mathcal{V})$.
 \end{proof}
@@
 d(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}&, \bm{\mathcal{A}}_{\cap \mathcal{G}}  ) 
-\leq d\left( \cap_{S \in \mathcal{G}} \bm{\mathcal{B}}_{\pi(S)}, \cap_{S \in \mathcal{G}} \bm{\mathcal{A}}_S \right) \nonumber \\
-&\leq \sum_{T \in \mathcal{G}} \frac{ d\left( \cap_{S \in \mathcal{G}} \bm{\mathcal{B}}_{\pi(S)},\bm{\mathcal{A}_{T}} \right) }{ \xi(  \{\bm{\mathcal{A}}_S\}_{S \in \mathcal{G}}) }
-\leq \sum_{T \in \mathcal{G}} \frac{ d\left( \bm{\mathcal{B}}_{\pi(T)},\bm{\mathbf{A}}_{T} \right) }{ \xi( \{\bm{\mathcal{A}}_S\}_{S \in \mathcal{G}}) }\nonumber \\
-&\leq \frac{|\mathcal{G}| \varepsilon}{\xi( \{\bm{\mathcal{A}}_S\}_{S \in \mathcal{G}})} 
+\leq d\left( \cap \bm{\mathcal{B}}_{\pi(\mathcal{G})}, \cap \bm{\mathcal{A}}_\mathcal{G} \right)
+\leq \sum_{T \in \mathcal{G}} \frac{ d\left( \cap \bm{\mathcal{B}}_{\pi(\mathcal{G})},\bm{\mathcal{A}_{T}} \right) }{ \xi( \bm{\mathcal{A}}_\mathcal{G} ) } \nonumber \\
+&\leq \sum_{T \in \mathcal{G}} \frac{ d\left( \bm{\mathcal{B}}_{\pi(T)},\bm{\mathbf{A}}_{T} \right) }{ \xi( \bm{\mathcal{A}}_\mathcal{G} ) }
+\leq \frac{|\mathcal{G}| \varepsilon}{\xi( \bm{\mathcal{A}}_\mathcal{G} )} 
 \leq \frac{C_2 \varepsilon}{\max_j\|\mathbf{A}_j\|_2}. 

### 2017-11-23 manuscripts/PNAS/second review/resub/chazthm_pnas_resub.tex
new xi

@@
 The constant $C_2 = C_2(\mathbf{A}, \mathcal{H})$, in turn, will be presented relative to a quantity from \cite{Deutsch12} used to analyze the convergence of the alternating projections algorithm. 
-More specifically, in Lem.~\ref{DistanceToIntersectionLemma} below, the following definition is used to bound the distance between a point and the intersection of subspaces given an upper bound on its distance from each individual subspace.
+Specifically, in Lem.~\ref{DistanceToIntersectionLemma} below, the following definition is used to bound the distance between a point and the intersection of subspaces given an upper bound on its distance from each individual subspace.
 
 \begin{definition}\label{SpecialSupportSet}\label{FriedrichsDefinition}
-For a collection of real subspaces $\mathcal{V} = \{V_i\}_{i=1}^\ell$, define $\xi := 1$ when $|\mathcal{V}| = 1$ and otherwise:
-\begin{align*}
-\xi(\mathcal{V}) := 1 - \left(1 -  \max \prod_{i=1}^{\ell-1} \sin^2  \theta \left(V_i, \cap_{j>i} V_j \right)  \right)^{1/2},
-\end{align*} 
+For a collection of real subspaces $\mathcal{V} = \{V_i\}_{i=1}^\ell$, define $\xi^2 := 1$ when $|\mathcal{V}| = 1$, and otherwise:
+\begin{align}\label{xi}
+\xi^2(\mathcal{V}) := 1 -  \max \prod_{i=1}^{\ell-1} \sin^2  \theta \left(V_i, \cap_{j>i} V_j \right) ,
+\end{align} 
 %
@@
 \end{definition}
-Note that $\theta \in (0,\frac{\pi}{2}]$ implies $0 < \xi \leq 1$, and that $\xi(\mathcal{V}') \geq \xi(\mathcal{V})$ when $\mathcal{V}' \subseteq \mathcal{V}$.\footnote{We acknowledge the counter-intuitive property that $\theta =  \pi/2$ when $U \subseteq W$.}
-The constant $C_2$ in Lem.~\ref{MainLemma} can then be expressed as:  
+Note that $\theta \in (0,\frac{\pi}{2}]$ implies $0 < \xi \leq 1$, and that $\xi(\mathcal{V}') \leq \xi(\mathcal{V})$ when $\mathcal{V}' \subseteq \mathcal{V}$.\footnote{We acknowledge the counter-intuitive property that $\theta =  \pi/2$ when $U \subseteq W$.}
+The constant $C_2$ in Lem.~\ref{MainLemma} is then:  
 \begin{align}\label{Cdef2}
-	C_2(\mathbf{A}, \mathcal{H}) := \frac{ (r+1) \max_{j \in [m]} \|\mathbf{A}_j\|_2}{ \min_{\mathcal{G} \in {\mathcal{H} \choose r+1}} \xi( \bm{\mathcal{A}}_\mathcal{G} ) },
+	C_2(\mathbf{A}, \mathcal{H}) := \frac{ (r+1) \max_{j \in [m]} \|\mathbf{A}_j\|_2}{ 1- \max_{\mathcal{G} \in {\mathcal{H} \choose r+1}} \xi( \bm{\mathcal{A}}_\mathcal{G} ) },
 \end{align}
@@
 
-It follows from $L_{2\mathcal{H}}(\mathbf{A}) > 0$ and the general linear position of the $\mathbf{x}_i$ that $L(\mathbf{AX}_{K}) > 0$; that is, the columns of the $n \times k$ matrix $\mathbf{AX}_K$ form a basis for $\bm{\mathcal{A}}_S$.
+It follows from $L_{2\mathcal{H}}(\mathbf{A}) > 0$ and the general linear position of the $\mathbf{x}_i$ that $L_k(\mathbf{AX}_{K}) > 0$; that is, the columns of the $n \times k$ matrix $\mathbf{AX}_K$ form a basis for $\bm{\mathcal{A}}_S$.
 Fixing $\mathbf{0} \neq \mathbf{y} \in \bm{\mathcal{A}}_S$, there then exists $\mathbf{0} \neq \mathbf{c} = (c_1, \ldots, c_k) \in \mathbb{R}^k$ such that $\mathbf{y} = \mathbf{AX}_K\mathbf{c}$.
@@
 &\leq \varepsilon \sqrt{k}  \|\mathbf{c}\|_2 
-\leq \frac{\varepsilon}{L(\mathbf{AX}_K)} \|\mathbf{y}\|_2,
+\leq \frac{\varepsilon}{L_k(\mathbf{AX}_K)} \|\mathbf{y}\|_2,
 \end{align*}
@@
 d(\bm{\mathcal{A}}_S, \bm{\mathcal{B}}_{\overline S}) 
-\leq \frac{\varepsilon}{  L(\mathbf{AX}_{K}) } \leq \varepsilon \frac{C_1}{C_2},
+\leq \frac{\varepsilon}{  L_k(\mathbf{AX}_{K}) } \leq \varepsilon \frac{C_1}{C_2},
 \end{align}
 %
-where the second inequality is due to $L(\mathbf{AX}_{K}) \geq L_k(\mathbf{AX}_{I(S)})$ and \eqref{Cdef1}.
+where the second inequality is due to $L_k(\mathbf{AX}_{K}) \geq L_k(\mathbf{AX}_{I(S)})$ and \eqref{Cdef1}.
 Finally, apply Lem.~\ref{MainLemma} with $\varepsilon < L_2(\mathbf{A})/C_1$.
@@
 \begin{lemma}\label{DistanceToIntersectionLemma}
-Fix $k \geq 2$.
-Let $\mathcal{V} = \{V_i\}_{i=1}^k$ be a collection of subspaces of $\mathbb{R}^m$ and set $V = \cap_{i = 1}^k V_i$.
-For  $\mathbf{x} \in \mathbb{R}^m$, we have (where $\xi$ is given in Def.~\ref{SpecialSupportSet}):
+Fix $k \geq 2$. Let $\mathcal{V} = \{V_i\}_{i=1}^k$ be a collection of subspaces of $\mathbb{R}^m$ and set $V = \cap_{i = 1}^k V_i$. For  $\mathbf{x} \in \mathbb{R}^m$, we have (recalling \eqref{xi}):
 \begin{align}\label{DTILeq}
-\text{\rm dist}(\mathbf{x}, V) \leq \frac{1}{\xi(\mathcal{V})} \sum_{i=1}^k \text{\rm dist}(\mathbf{x}, V_i).
+\text{\rm dist}(\mathbf{x}, V) \leq \frac{1}{1 - \xi(\mathcal{V})} \sum_{i=1}^k \text{\rm dist}(\mathbf{x}, V_i).
 \end{align}
@@
 
-Finally, substituting this into \eqref{f} and rearranging produces \eqref{DTILeq} after replacing $1 - z$ with $\xi(\mathcal{V})$.
+Finally, substituting this into \eqref{f} and rearranging produces \eqref{DTILeq} after substituting $\xi(\mathcal{V})$ for $z$.
 \end{proof}
@@
 \begin{align}\label{randoml}
-d(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}&, \bm{\mathcal{A}}_{\cap \mathcal{G}}  ) 
+d(&\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}, \bm{\mathcal{A}}_{\cap \mathcal{G}}  ) 
 \leq d\left( \cap \bm{\mathcal{B}}_{\pi(\mathcal{G})}, \cap \bm{\mathcal{A}}_\mathcal{G} \right)
-\leq \sum_{T \in \mathcal{G}} \frac{ d\left( \cap \bm{\mathcal{B}}_{\pi(\mathcal{G})},\bm{\mathcal{A}_{T}} \right) }{ \xi( \bm{\mathcal{A}}_\mathcal{G} ) } \nonumber \\
-&\leq \sum_{T \in \mathcal{G}} \frac{ d\left( \bm{\mathcal{B}}_{\pi(T)},\bm{\mathbf{A}}_{T} \right) }{ \xi( \bm{\mathcal{A}}_\mathcal{G} ) }
-\leq \frac{|\mathcal{G}| \varepsilon}{\xi( \bm{\mathcal{A}}_\mathcal{G} )} 
+\leq \sum_{T \in \mathcal{G}} \frac{ d\left( \cap \bm{\mathcal{B}}_{\pi(\mathcal{G})},\bm{\mathcal{A}_{T}} \right) }{ 1 - \xi( \bm{\mathcal{A}}_\mathcal{G} ) } \nonumber \\
+&\leq \sum_{T \in \mathcal{G}} \frac{ d\left( \bm{\mathcal{B}}_{\pi(T)},\bm{\mathbf{A}}_{T} \right) }{ 1 - \xi( \bm{\mathcal{A}}_\mathcal{G} ) }
+\leq \frac{|\mathcal{G}| \varepsilon}{1 - \xi( \bm{\mathcal{A}}_\mathcal{G} )} 
 \leq \frac{C_2 \varepsilon}{\max_j\|\mathbf{A}_j\|_2}. 

### 2017-11-24 manuscripts/PNAS/second review/resub/chazthm_pnas_resub.tex
shit shit shit

@@
 We begin by showing that $\dim(\bm{\mathcal{B}}_{\pi(S)}) = \dim(\bm{\mathcal{A}}_S)$ for all $S \in \mathcal{H}$.
-Note that since $\|\mathbf{A}\mathbf{x}\|_2 \leq \max_j\|\mathbf{A}_j\|_2\|\mathbf{x}\|_1$ and $\|\mathbf{x}\|_1 \leq \sqrt{2} \|\mathbf{x}\|_2$ for all $2$-sparse $\mathbf{x}$, by \eqref{Ldef} we have $L_2(\mathbf{A}) \leq \max_j\|\mathbf{A}_j\|_2$ and therefore (as $\xi \leq 1$), the right-hand side of \eqref{GapUpperBound} is less than one.
-It follows from \eqref{dimLem} that $|\pi(S)| \geq \dim(\bm{\mathcal{B}}_{\pi(S)}) \geq \dim(\bm{\mathcal{A}}_S) = |S|$, with the equality by injectivity of $\mathbf{A}$.
+Note that since $\|\mathbf{A}\mathbf{x}\|_2 \leq \max_j\|\mathbf{A}_j\|_2\|\mathbf{x}\|_1$ and $\|\mathbf{x}\|_1 \leq \sqrt{2} \|\mathbf{x}\|_2$ for all $2$-sparse $\mathbf{x}$, by \eqref{Ldef} we have $L_2(\mathbf{A}) \leq \max_j\|\mathbf{A}_j\|_2$ and therefore (as $\xi > 0$), the right-hand side of \eqref{GapUpperBound} is less than one.
+It follows from \eqref{dimLem} that $|\pi(S)| \geq \dim(\bm{\mathcal{B}}_{\pi(S)}) \geq \dim(\bm{\mathcal{A}}_S) = |S|$, with the equality by injectivity of $\mathbf{A}_S$.
 Since $|S| = |\pi(S)|$, the required fact follows.
-Note that $\mathbf{B}_{\pi(S)}$ therefore has full column-rank for all $S \in \mathcal{H}$.
+Note therefore that $\mathbf{B}_{\pi(S)}$ has full-column rank for all $S \in \mathcal{H}$.
 
 We next show that \eqref{cond} holds.
-Fix $\mathcal{G} \subseteq {\mathcal{H} \choose r} \cup {\mathcal{H} \choose r+1}$.
-Since $\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})} \subseteq \cap_{S \in \mathcal{G}} \bm{\mathcal{B}}_{\pi(S)}$, if $\cap_{S \in \mathcal{G}} \bm{\mathcal{B}}_{\pi(S)} = \{\textbf{0}\}$, then we must have $|\cap \pi(\mathcal{G})| = 0$ (as the columns of $\mathbf{B}_{\pi(S)}$ are linearly independent) and \eqref{cond} is trivially true.
-Suppose then that the intersection is not zero.
-Keeping in mind that $d(U',V) \leq d(U,V)$ whenever $U' \subseteq U$ and applying (in order) Lem.~\ref{spanIntersectionLemma}, Lem.~\ref{DistanceToIntersectionLemma}, \eqref{eqdim}, \eqref{GapUpperBound}, and \eqref{Cdef2} gives:
-\begin{align}\label{randoml}
-d(&\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}, \bm{\mathcal{A}}_{\cap \mathcal{G}}  ) 
-\leq d\left( \cap \bm{\mathcal{B}}_{\pi(\mathcal{G})}, \cap \bm{\mathcal{A}}_\mathcal{G} \right)
-\leq \sum_{T \in \mathcal{G}} \frac{ d\left( \cap \bm{\mathcal{B}}_{\pi(\mathcal{G})},\bm{\mathcal{A}_{T}} \right) }{ 1 - \xi( \bm{\mathcal{A}}_\mathcal{G} ) } \nonumber \\
-&\leq \sum_{T \in \mathcal{G}} \frac{ d\left( \bm{\mathcal{B}}_{\pi(T)},\bm{\mathbf{A}}_{T} \right) }{ 1 - \xi( \bm{\mathcal{A}}_\mathcal{G} ) }
-\leq \frac{|\mathcal{G}| \varepsilon}{1 - \xi( \bm{\mathcal{A}}_\mathcal{G} )} 
-\leq \frac{C_2 \varepsilon}{\max_j\|\mathbf{A}_j\|_2}. 
+Fixing $\mathcal{G} \subseteq {\mathcal{H} \choose r} \cup {\mathcal{H} \choose r+1}$, it suffices to show that $d(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}, \bm{\mathcal{A}}_{\cap \mathcal{G}} ) < 1$, since by \eqref{dimLem} we then have $|\cap \pi(\mathcal{G})| = \dim(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}) \leq \dim(\bm{\mathcal{A}}_{\cap \mathcal{G}}) = |\cap \mathcal{G}|$, with equalities by injectivity of $\mathbf{A}_{S}$ and $\mathbf{B}_{\pi(S)}$ for all $S \in \mathcal{G}$.\footnote{Note that this assumes $\cap \bm{\mathcal{B}}_{\pi(\mathcal{G})} = \bf 0$ if $\cap \mathcal{G} = \emptyset$, since otherwise $d(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}, \bm{\mathcal{A}}_{\cap \mathcal{G}} ) = 1$; but this must be the case, since otherwise the deduction that follows would lead to a contradiction.}
+
+First, observe that $d(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}, \bm{\mathcal{A}}_{\cap \mathcal{G}}  ) 
+\leq d\left( \cap \bm{\mathcal{B}}_{\pi(\mathcal{G})}, \cap \bm{\mathcal{A}}_\mathcal{G} \right)$, since $\bm{\mathcal{A}}_{\cap \mathcal{G}} = \cap \bm{\mathcal{A}}_\mathcal{G}$ by Lem.~\ref{spanIntersectionLemma} and $d(U',V) \leq d(U,V)$ whenever $U' \subseteq U$.
+We then have, by Lem.~\ref{DistanceToIntersectionLemma}, \eqref{eqdim}, \eqref{GapUpperBound}, and \eqref{Cdef2} (applied in order):
+\begin{align}
+d\left( \cap \bm{\mathcal{B}}_{\pi(\mathcal{G})}, \cap \bm{\mathcal{A}}_\mathcal{G} \right)
+&= \sup_{\mathbf{u} \in \cap \bm{\mathcal{B}}_{\pi(\mathcal{G})}, \ \|\mathbf{u}\|_2 \leq 1} \text{\rm dist}\left( \mathbf{u}, \cap \bm{\mathcal{A}}_\mathcal{G} \right) \nonumber \\
+&\leq \sup_{\mathbf{u} \in \cap \bm{\mathcal{B}}_{\pi(\mathcal{G})}, \ \|\mathbf{u}\|_2 \leq 1} \sum_{S \in \mathcal{G}} \frac{ \text{\rm dist}\left( \mathbf{u},\bm{\mathcal{A}}_{S} \right) }{ 1 - \xi( \bm{\mathcal{A}}_\mathcal{G} ) } \nonumber \\
+&= \sum_{S \in \mathcal{G}} \frac{ d\left( \cap \bm{\mathcal{B}}_{\pi(\mathcal{G})},\bm{\mathcal{A}}_{S} \right) }{ 1 - \xi( \bm{\mathcal{A}}_\mathcal{G} ) } 
+\leq \sum_{S \in \mathcal{G}} \frac{ d\left( \bm{\mathcal{B}}_{\pi(S)},\bm{\mathcal{A}}_{S} \right) }{ 1 - \xi( \bm{\mathcal{A}}_\mathcal{G} ) } \nonumber \\
+&\leq \frac{|\mathcal{G}| \varepsilon}{1 - \xi( \bm{\mathcal{A}}_\mathcal{G} )} \nonumber \\
+&\leq \frac{C_2 \varepsilon}{\max_j\|\mathbf{A}_j\|_2},
 \end{align}
+%
+which is less than one, since $C_2 \varepsilon < L_2(\mathbf{A}) \leq \max_j\|\mathbf{A}_j\|_2$.
 
-Since $C_2 \varepsilon < L_2(\mathbf{A}) \leq \max_j\|\mathbf{A}_j\|_2$, we have by \eqref{dimLem} that $\dim(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}) \leq \dim(\bm{\mathcal{A}}_{\cap \mathcal{G}})$, and \eqref{cond} follows from the full column-rank of $\mathbf{A}_{S}$ and $\mathbf{B}_{\pi(S)}$ for all $S \in \mathcal{G}$.
+%Keeping in mind that $d(U',V) \leq d(U,V)$ whenever $U' \subseteq U$ and applying (in order) Lem.~\ref{spanIntersectionLemma}, Lem.~\ref{DistanceToIntersectionLemma}, \eqref{eqdim}, \eqref{GapUpperBound}, and \eqref{Cdef2} gives:
+%\begin{align}\label{randoml}
+%d(&\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}, \bm{\mathcal{A}}_{\cap \mathcal{G}}  ) 
+%\leq d\left( \cap \bm{\mathcal{B}}_{\pi(\mathcal{G})}, \cap \bm{\mathcal{A}}_\mathcal{G} \right)
+%\leq \sum_{T \in \mathcal{G}} \frac{ d\left( \cap \bm{\mathcal{B}}_{\pi(\mathcal{G})},\bm{\mathcal{A}}_{T} \right) }{ 1 - \xi( \bm{\mathcal{A}}_\mathcal{G} ) } \nonumber \\
+%&\leq \sum_{T \in \mathcal{G}} \frac{ d\left( \bm{\mathcal{B}}_{\pi(T)},\bm{\mathbf{A}}_{T} \right) }{ 1 - \xi( \bm{\mathcal{A}}_\mathcal{G} ) }
+%\leq \frac{|\mathcal{G}| \varepsilon}{1 - \xi( \bm{\mathcal{A}}_\mathcal{G} )} 
+%\leq \frac{C_2 \varepsilon}{\max_j\|\mathbf{A}_j\|_2},
+%\end{align}
+%
+%which is less than one, since $C_2 \varepsilon < L_2(\mathbf{A}) \leq \max_j\|\mathbf{A}_j\|_2$.
 

### 2017-11-26 manuscripts/PNAS/second review/resub/chazthm_pnas_resub.tex
lemma 1 proof

@@
 
-\begin{definition}\label{SpecialSupportSet}\label{FriedrichsDefinition}
+\begin{definition}\label{FriedrichsDefinition}
 For a collection of real subspaces $\mathcal{V} = \{V_i\}_{i=1}^\ell$, define $\xi^2 := 1$ when $|\mathcal{V}| = 1$, and otherwise:
@@
 \begin{lemma}\label{DistanceToIntersectionLemma}
-Fix $k \geq 2$. Let $\mathcal{V} = \{V_i\}_{i=1}^k$ be a collection of subspaces of $\mathbb{R}^m$ and set $V = \cap_{i = 1}^k V_i$. For  $\mathbf{x} \in \mathbb{R}^m$, we have (recalling \eqref{xi}):
+Let $\mathcal{V} = \{V_i\}_{i=1}^k$ be a set of two or more subspaces of $\mathbb{R}^m$ and let $V = \cap_{i = 1}^k V_i$.
+For  $\mathbf{x} \in \mathbb{R}^m$, we have (recall Defs.~\ref{dDef}~\&~\ref{FriedrichsDefinition}):
 \begin{align}\label{DTILeq}
@@
 \begin{proof} 
-Recall the orthogonal projection onto a subspace $V \subseteq \mathbb{R}^m$ is the mapping $\Pi_V: \mathbb{R}^m \to V$ that associates with each $\mathbf{x}$ its unique nearest point in $V$; i.e., $\|\mathbf{x} - \Pi_V\mathbf{x}\|_2 = \text{\rm dist}(\mathbf{x}, V)$.
+Recall the orthogonal projection onto the subspace $V \subseteq \mathbb{R}^m$ is the mapping $\Pi_V: \mathbb{R}^m \to V$ that associates with each $\mathbf{x}$ its unique nearest point in $V$; i.e., $\|\mathbf{x} - \Pi_V\mathbf{x}\|_2 = \text{\rm dist}(\mathbf{x}, V)$.
 Next, observe:
@@
 We begin by showing that $\dim(\bm{\mathcal{B}}_{\pi(S)}) = \dim(\bm{\mathcal{A}}_S)$ for all $S \in \mathcal{H}$.
-Note that since $\|\mathbf{A}\mathbf{x}\|_2 \leq \max_j\|\mathbf{A}_j\|_2\|\mathbf{x}\|_1$ and $\|\mathbf{x}\|_1 \leq \sqrt{2} \|\mathbf{x}\|_2$ for all $2$-sparse $\mathbf{x}$, by \eqref{Ldef} we have $L_2(\mathbf{A}) \leq \max_j\|\mathbf{A}_j\|_2$ and therefore (as $\xi > 0$), the right-hand side of \eqref{GapUpperBound} is less than one.
+Note that since $\|\mathbf{A}\mathbf{x}\|_2 \leq \max_j\|\mathbf{A}_j\|_2\|\mathbf{x}\|_1$ and $\|\mathbf{x}\|_1 \leq \sqrt{k} \|\mathbf{x}\|_2$ for all $k$-sparse $\mathbf{x}$, by \eqref{Ldef} we have $L_2(\mathbf{A}) \leq \max_j\|\mathbf{A}_j\|_2$ and therefore (as $\xi > 0$), the right-hand side of \eqref{GapUpperBound} is less than one.
 It follows from \eqref{dimLem} that $|\pi(S)| \geq \dim(\bm{\mathcal{B}}_{\pi(S)}) \geq \dim(\bm{\mathcal{A}}_S) = |S|$, with the equality by injectivity of $\mathbf{A}_S$.
-Since $|S| = |\pi(S)|$, the required fact follows.
+Given that $|S| = |\pi(S)|$, the required fact then follows.
 Note therefore that $\mathbf{B}_{\pi(S)}$ has full-column rank for all $S \in \mathcal{H}$.
@@
 We next show that \eqref{cond} holds.
-Fixing $\mathcal{G} \subseteq {\mathcal{H} \choose r} \cup {\mathcal{H} \choose r+1}$, it suffices to show that $d(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}, \bm{\mathcal{A}}_{\cap \mathcal{G}} ) < 1$, since by \eqref{dimLem} we then have $|\cap \pi(\mathcal{G})| = \dim(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}) \leq \dim(\bm{\mathcal{A}}_{\cap \mathcal{G}}) = |\cap \mathcal{G}|$, with equalities by injectivity of $\mathbf{A}_{S}$ and $\mathbf{B}_{\pi(S)}$ for all $S \in \mathcal{G}$.\footnote{Note that this assumes $\cap \bm{\mathcal{B}}_{\pi(\mathcal{G})} = \bf 0$ if $\cap \mathcal{G} = \emptyset$, since otherwise $d(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}, \bm{\mathcal{A}}_{\cap \mathcal{G}} ) = 1$; but this must be the case, since otherwise the deduction that follows would lead to a contradiction.}
-
-First, observe that $d(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}, \bm{\mathcal{A}}_{\cap \mathcal{G}}  ) 
+Fixing $\mathcal{G} \subseteq {\mathcal{H} \choose r} \cup {\mathcal{H} \choose r+1}$, it suffices to show that $d(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}, \bm{\mathcal{A}}_{\cap \mathcal{G}} ) < 1$, since by \eqref{dimLem} we then have $|\cap \pi(\mathcal{G})| = \dim(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}) \leq \dim(\bm{\mathcal{A}}_{\cap \mathcal{G}}) = |\cap \mathcal{G}|$, with equalities by the full column-ranks of $\mathbf{A}_{S}$ and $\mathbf{B}_{\pi(S)}$ for all $S \in \mathcal{H}$.\footnote{Note that if ever $\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})} \neq \bf 0$ while $\cap \mathcal{G} = \emptyset$, then we would have $d(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}, \bm 0 ) = 1$.
+This cannot be the case, however, since the deduction that follows would then lead to a contradiction.} Observe that $d(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}, \bm{\mathcal{A}}_{\cap \mathcal{G}}  )
 \leq d\left( \cap \bm{\mathcal{B}}_{\pi(\mathcal{G})}, \cap \bm{\mathcal{A}}_\mathcal{G} \right)$, since $\bm{\mathcal{A}}_{\cap \mathcal{G}} = \cap \bm{\mathcal{A}}_\mathcal{G}$ by Lem.~\ref{spanIntersectionLemma} and $d(U',V) \leq d(U,V)$ whenever $U' \subseteq U$.
-We then have, by Lem.~\ref{DistanceToIntersectionLemma}, \eqref{eqdim}, \eqref{GapUpperBound}, and \eqref{Cdef2} (applied in order):
+Recalling Def.~\ref{dDef}, we may apply Lem.~\ref{DistanceToIntersectionLemma} and carry the supremum through the sum:
 \begin{align}
 d\left( \cap \bm{\mathcal{B}}_{\pi(\mathcal{G})}, \cap \bm{\mathcal{A}}_\mathcal{G} \right)
-&= \sup_{\mathbf{u} \in \cap \bm{\mathcal{B}}_{\pi(\mathcal{G})}, \ \|\mathbf{u}\|_2 \leq 1} \text{\rm dist}\left( \mathbf{u}, \cap \bm{\mathcal{A}}_\mathcal{G} \right) \nonumber \\
-&\leq \sup_{\mathbf{u} \in \cap \bm{\mathcal{B}}_{\pi(\mathcal{G})}, \ \|\mathbf{u}\|_2 \leq 1} \sum_{S \in \mathcal{G}} \frac{ \text{\rm dist}\left( \mathbf{u},\bm{\mathcal{A}}_{S} \right) }{ 1 - \xi( \bm{\mathcal{A}}_\mathcal{G} ) } \nonumber \\
-&= \sum_{S \in \mathcal{G}} \frac{ d\left( \cap \bm{\mathcal{B}}_{\pi(\mathcal{G})},\bm{\mathcal{A}}_{S} \right) }{ 1 - \xi( \bm{\mathcal{A}}_\mathcal{G} ) } 
-\leq \sum_{S \in \mathcal{G}} \frac{ d\left( \bm{\mathcal{B}}_{\pi(S)},\bm{\mathcal{A}}_{S} \right) }{ 1 - \xi( \bm{\mathcal{A}}_\mathcal{G} ) } \nonumber \\
-&\leq \frac{|\mathcal{G}| \varepsilon}{1 - \xi( \bm{\mathcal{A}}_\mathcal{G} )} \nonumber \\
-&\leq \frac{C_2 \varepsilon}{\max_j\|\mathbf{A}_j\|_2},
+%&\leq \sup_{\mathbf{u} \in \cap \bm{\mathcal{B}}_{\pi(\mathcal{G})}, \ \|\mathbf{u}\|_2 \leq 1} \sum_{S \in \mathcal{G}} \frac{ \text{\rm dist}\left( \mathbf{u},\bm{\mathcal{A}}_{S} \right) }{ 1 - \xi( \bm{\mathcal{A}}_\mathcal{G} ) }
+\leq \sum_{S \in \mathcal{G}} \frac{ d\left( \cap \bm{\mathcal{B}}_{\pi(\mathcal{G})},\bm{\mathcal{A}}_{S} \right) }{ 1 - \xi( \bm{\mathcal{A}}_\mathcal{G} ) }.
 \end{align}
-%
+Since $\cap \bm{\mathcal{B}}_{\pi(\mathcal{G})} \subseteq \bm{\mathcal{B}}_{\pi(S)}$ for all $S \in \mathcal{G}$, the numerator of each term above is bounded by $d\left( \bm{\mathcal{B}}_{\pi(S)},\bm{\mathcal{A}}_{S} \right)$ and, recalling \eqref{eqdim} (since $\dim(\bm{\mathcal{B}}_{\pi(S)}) = \dim(\bm{\mathcal{A}}_S)$), by $d\left(\bm{\mathcal{A}}_{S}, \bm{\mathcal{B}}_{\pi(S)} \right) \leq \varepsilon$, in turn.
+Thus,
+\begin{align}
+d(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}, \bm{\mathcal{A}}_{\cap \mathcal{G}} )
+\leq \frac{|\mathcal{G}| \varepsilon}{1 - \xi( \bm{\mathcal{A}}_\mathcal{G} )}
+\leq \frac{C_2 \varepsilon}{\max_j\|\mathbf{A}_j\|_2},
+\end{align}
 which is less than one, since $C_2 \varepsilon < L_2(\mathbf{A}) \leq \max_j\|\mathbf{A}_j\|_2$.

### 2017-11-28 manuscripts/PNAS/second review/resub/chazthm_pnas_resub.tex
cjh edits from muddy waters

@@
 \begin{align*}
-	\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \varepsilon(\delta_1, \delta_2),\ \ \   \text{for all $i$},
+	\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \varepsilon(\delta_1, \delta_2),\ \ \   \text{for all $i=1,\ldots,N$},
 \end{align*}
@@
 \ref{InverseProblem}, suppose that $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$ and fix $\delta_1, \delta_2$ to be the desired recovery accuracy in \eqref{def1}.
-Consider now any dataset $Z$ generated as in \eqref{LinearModel} with $\eta \leq \frac{1}{2} \varepsilon(\delta_1, \delta_2)$.
+Consider any dataset $Z$ generated as in \eqref{LinearModel} with $\eta \leq \frac{1}{2} \varepsilon(\delta_1, \delta_2)$.
 Then from the triangle inequality, it follows that any matrix $\mathbf{B}$ and $k$-sparse $\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N \in \mathbb{R}^m$ solving Prob.~\ref{InverseProblem} are necessarily within $\delta_1, \delta_2$ of the original dictionary $\mathbf{A}$ and codes $\mathbf{x}_i$, respectively.
@@
 \end{problem}
-We then sketch the proof of a probabilistic extension of Thm.~\ref{DeterministicUniquenessTheorem} to random data and dictionaries (Thm.~\ref{robustPolythm} and Cor.~\ref{ProbabilisticCor}).
+We then sketch proofs of probabilistic extensions of Thm.~\ref{DeterministicUniquenessTheorem} to random data and dictionaries (Thm.~\ref{robustPolythm} and Cor.~\ref{ProbabilisticCor}).
 Finally, in Sec.~\ref{Discussion}, we discuss both theoretical and practical applications of our main mathematical findings.
@@
 
-Next, we describe a quantitative version of the spark condition.
-The \emph{lower bound} of a matrix $\mathbf{M} \in \mathbb R^{n \times m}$ is the largest $\alpha$ such that \mbox{$\|\mathbf{M}\mathbf{x}\|_2 \geq \alpha\|\mathbf{x}\|_2$} for all $\mathbf{x} \in \mathbb{R}^m$ \cite{Grcar10}.
-By compactness of the unit sphere, every injective linear map has nonzero lower bound; hence, if $\mathbf{M}$ satisfies \eqref{SparkCondition}, then each submatrix formed from $2k$ of its columns or less has a strictly positive lower bound.
+Next, we describe a quantitative spark condition.
+The \emph{lower bound} of a matrix $\mathbf{M} \in \mathbb R^{n \times m}$ is the largest $\alpha$ with \mbox{$\|\mathbf{M}\mathbf{x}\|_2 \geq \alpha\|\mathbf{x}\|_2$} for all $\mathbf{x} \in \mathbb{R}^m$ \cite{Grcar10}.
+By compactness of the unit sphere, injective linear maps have nonzero lower bound; hence, if $\mathbf{M}$ satisfies \eqref{SparkCondition}, then each submatrix formed from $2k$ of its columns or less has a strictly positive lower bound.
 
@@
 
-Every $n \times \overline m$ matrix $\mathbf{B}$ for which there are $k$-sparse $\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N$ satisfying \mbox{$\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \varepsilon$} for all $i$ has $\overline m \geq m$ and, provided $\overline m < mr/(r-1)$,
+Every $n \times \overline m$ matrix $\mathbf{B}$ for which there are $k$-sparse $\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N$ satisfying \mbox{$\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \varepsilon$} for all $i$ has $\overline m \geq m$ and, provided $(r-1) \overline m < mr$,
 \begin{align}\label{Cstable}
@@
 In this case, a direct consequence of Cor.~\ref{DeterministicUniquenessCorollary} is rigorous verification of the lower bound \mbox{$N = m(k-1){m \choose k} + m$} for sufficient sample size from the introduction.
-In many cases, however, the SIP is achievable with far fewer supports.
-For example, when $k = \sqrt{m}$, simply take $\mathcal{H}$ to be the $2k$ rows and columns formed by arranging $[m]$ in a square grid.
+Often, the SIP is achievable with fewer supports.
+For example, when $k = \sqrt{m}$, take $\mathcal{H}$ to be the $2k$ rows and columns formed by arranging $[m]$ into a square grid.
 
@@
 
-We furthermore note that unlike in previous works \cite{li2004analysis, Georgiev05, Aharon06, Hillar15}, the matrix $\mathbf{A}$ need not satisfy the spark condition to be recoverable from data.
+%\cite{li2004analysis, Georgiev05, Aharon06, Hillar15}
+We furthermore note that unlike in previous works, the matrix $\mathbf{A}$ need not satisfy the spark condition to be recoverable from data.
 As a simple example for $k=2$, let $\mathbf{A} = [ \mathbf{e}_1, \ldots, \mathbf{e}_5, \mathbf{v}]$ where $\mathbf{v} = \mathbf{e}_1 + \mathbf{e}_3 + \mathbf{e}_5$, and take $\mathcal{H}$ to be all consecutive pairs of $[m]$ arranged in cyclic order.
@@
 \begin{proposition}\label{neuroprop}
-Sparse neural population activity is recoverable from noisy random linear compression by any method that solves Prob.~\ref{DeterministicUniquenessTheorem} or \ref{SLCopt}; in particular, via biophysically plausible unsupervised sparse linear coding (e.g., \cite{rehnsommer2007, rozell2007neurally}).
+Sparse neural population activity is recoverable from noisy random linear compression by any method that solves Prob.~\ref{DeterministicUniquenessTheorem} or \ref{SLCopt}; in particular, via biophysically plausible unsupervised sparse linear coding (e.g., \cite{rehnsommer2007, rozell2007neurally, pehlevan2015normative}).
 \end{proposition}
@@
 \begin{definition}\label{FriedrichsDefinition}
-For a collection of real subspaces $\mathcal{V} = \{V_i\}_{i=1}^\ell$, define $\xi^2 := 1$ when $|\mathcal{V}| = 1$, and otherwise:
+For a collection of real subspaces $\mathcal{V} = \{V_i\}_{i=1}^\ell$, define $\xi^2 := 0$ when $|\mathcal{V}| = 1$, and otherwise:
 \begin{align}\label{xi}
@@
 \end{definition}
-Note that $\theta \in (0,\frac{\pi}{2}]$ implies $0 < \xi \leq 1$, and that $\xi(\mathcal{V}') \leq \xi(\mathcal{V})$ when $\mathcal{V}' \subseteq \mathcal{V}$.\footnote{We acknowledge the counter-intuitive property that $\theta =  \pi/2$ when $U \subseteq W$.}
+Note that $\theta \in (0,\frac{\pi}{2}]$ implies $0 \leq \xi < 1$, and that $\xi(\mathcal{V}') \leq \xi(\mathcal{V})$ when $\mathcal{V}' \subseteq \mathcal{V}$.\footnote{We acknowledge the counter-intuitive property that $\theta =  \pi/2$ when $U \subseteq W$.}
 The constant $C_2$ in Lem.~\ref{MainLemma} is then:  
 \begin{align}\label{Cdef2}
-	C_2(\mathbf{A}, \mathcal{H}) := \frac{ (r+1) \max_{j \in [m]} \|\mathbf{A}_j\|_2}{ 1- \max_{\mathcal{G} \in {\mathcal{H} \choose r+1}} \xi( \bm{\mathcal{A}}_\mathcal{G} ) },
+	C_2(\mathbf{A}, \mathcal{H}) := \frac{ r \max_{j \in [m]} \|\mathbf{A}_j\|_2}{ 1- \max_{\mathcal{G} \in {\mathcal{H} \choose r}} \xi( \bm{\mathcal{A}}_\mathcal{G} ) },
 \end{align}
@@
 
-Since there are more than $(k-1){\overline m \choose k}$ vectors $\mathbf{x}_i$ supported in $S$, the pigeonhole principle gives $\overline S \in {[\overline m] \choose k}$ and a set of $k$ indices $K \subseteq I(S)$ with all $\mathbf{\overline x}_i$, $i \in K$, supported in $\overline S$.
+Since there are more than $(k-1){\overline m \choose k}$ vectors $\mathbf{x}_i$ supported in each $S \in \mathcal{H}$, the pigeonhole principle gives $\overline S \in {[\overline m] \choose k}$ and a set of $k$ indices $K \subseteq I(S)$ with all $\mathbf{\overline x}_i$, $i \in K$, supported in $\pi(S) := \overline S$.
 
@@
 \begin{lemma}\label{spanIntersectionLemma}
-If $f: U \to V$ is an injective function, then $f\left(\cap_{i=1}^\ell U_i \right) =  \cap_{i=1}^\ell f\left(U_i\right)$ for any $U_1, \ldots, U_\ell \subseteq U$.
+If $f: U \to V$ is an injective function, then $f\left(\cap_{i=1}^\ell U_i \right) =  \cap_{i=1}^\ell f\left(U_i\right)$ for any $U_1, \ldots, U_\ell \subseteq U$. ($f(\emptyset):=\emptyset$.)
 %In particular, if for some $E \in 2^{[m]}$ the map $M \in \mathbb{R}^{n \times m}$ is injective on $\cup_{S \in \mathcal{H}} \text{span}\{e_i\}_{i \in S}$ then $\text{span}\{ M_{\cap_{S \in \mathcal{H}} S} \} = \cap_{S \in \mathcal{H}} \text{span}\{M_S\}$.
@@
 \begin{proof} 
-Recall the orthogonal projection onto the subspace $V \subseteq \mathbb{R}^m$ is the mapping $\Pi_V: \mathbb{R}^m \to V$ that associates with each $\mathbf{x}$ its unique nearest point in $V$; i.e., $\|\mathbf{x} - \Pi_V\mathbf{x}\|_2 = \text{\rm dist}(\mathbf{x}, V)$.
+% When $V = \{\mathbf{0}\}$, the result is trivial, so suppose otherwise.  
+Recall the projection onto the subspace $V \subseteq \mathbb{R}^m$ is the mapping $\Pi_V: \mathbb{R}^m \to V$ that associates with each $\mathbf{x}$ its unique nearest point in $V$; i.e., $\|\mathbf{x} - \Pi_V\mathbf{x}\|_2 = \text{\rm dist}(\mathbf{x}, V)$.
 Next, observe:
@@
 %
-then $\overline m \geq m$, and if $\overline m < mr / (r-1)$ then the map $i \mapsto \cap \pi(\sigma(i))$ is an injective map to $[\overline m]$ from some $J \subseteq [m]$ of size $\overline m - r(\overline m - m)$.
+then $\overline m \geq m$, and if $(r-1) \overline m < mr$ then the map $i \mapsto \cap \pi(\sigma(i))$ is an injective map to $[\overline m]$ from some $J \subseteq [m]$ of size $\overline m - r(\overline m - m)$.
 %In particular, if $\overline m = m$ then $\pi$ is induced by a permutation on $[m]$.
@@
 Note that since $\|\mathbf{A}\mathbf{x}\|_2 \leq \max_j\|\mathbf{A}_j\|_2\|\mathbf{x}\|_1$ and $\|\mathbf{x}\|_1 \leq \sqrt{k} \|\mathbf{x}\|_2$ for all $k$-sparse $\mathbf{x}$, by \eqref{Ldef} we have $L_2(\mathbf{A}) \leq \max_j\|\mathbf{A}_j\|_2$ and therefore (as $\xi > 0$), the right-hand side of \eqref{GapUpperBound} is less than one.
-It follows from \eqref{dimLem} that $|\pi(S)| \geq \dim(\bm{\mathcal{B}}_{\pi(S)}) \geq \dim(\bm{\mathcal{A}}_S) = |S|$, with the equality by injectivity of $\mathbf{A}_S$.
-Given that $|S| = |\pi(S)|$, the required fact then follows.
-Note therefore that $\mathbf{B}_{\pi(S)}$ has full-column rank for all $S \in \mathcal{H}$.
+From \eqref{dimLem}, we have $|\pi(S)| \geq \dim(\bm{\mathcal{B}}_{\pi(S)}) \geq \dim(\bm{\mathcal{A}}_S) = |S|$, with the equality by injectivity of $\mathbf{A}_S$.
+As $|\pi(S)| = |S|$, the claim follows.
+Note, therefore, that $\mathbf{B}_{\pi(S)}$ has full-column rank for all $S \in \mathcal{H}$.
 
-We next show that \eqref{cond} holds.
-Fixing $\mathcal{G} \subseteq {\mathcal{H} \choose r} \cup {\mathcal{H} \choose r+1}$, it suffices to show that $d(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}, \bm{\mathcal{A}}_{\cap \mathcal{G}} ) < 1$, since by \eqref{dimLem} we then have $|\cap \pi(\mathcal{G})| = \dim(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}) \leq \dim(\bm{\mathcal{A}}_{\cap \mathcal{G}}) = |\cap \mathcal{G}|$, with equalities by the full column-ranks of $\mathbf{A}_{S}$ and $\mathbf{B}_{\pi(S)}$ for all $S \in \mathcal{H}$.\footnote{Note that if ever $\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})} \neq \bf 0$ while $\cap \mathcal{G} = \emptyset$, then we would have $d(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}, \bm 0 ) = 1$.
+We next verify that \eqref{cond} holds.
+Fixing $\mathcal{G} \in {\mathcal{H} \choose r}$, it suffices to show that $d(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}, \bm{\mathcal{A}}_{\cap \mathcal{G}} ) < 1$, since by \eqref{dimLem} we then have $|\cap \pi(\mathcal{G})| = \dim(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}) \leq \dim(\bm{\mathcal{A}}_{\cap \mathcal{G}}) = |\cap \mathcal{G}|$, with equalities by the full column-ranks of $\mathbf{A}_{S}$ and $\mathbf{B}_{\pi(S)}$ for all $S \in \mathcal{H}$.\footnote{Note that if ever $\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})} \neq \bf 0$ while $\cap \mathcal{G} = \emptyset$, we would have $d(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}, \bm 0 ) = 1$.
 This cannot be the case, however, since the deduction that follows would then lead to a contradiction.} Observe that $d(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}, \bm{\mathcal{A}}_{\cap \mathcal{G}}  )

### 2017-11-28 manuscripts/PNAS/second review/resub/chazthm_pnas_resub.tex
tiny and and typo

@@
 %
-for some nonempty $\overline J \subseteq [\overline m]$ and $J \subseteq [m]$ of size $\overline m - r(\overline m - m)$, permutation matrix $\mathbf{P}$, and and invertible diagonal matrix $\mathbf{D}$.
+for some nonempty $\overline J \subseteq [\overline m]$ and $J \subseteq [m]$ of size $\overline m - r(\overline m - m)$, permutation matrix $\mathbf{P}$, and invertible diagonal matrix $\mathbf{D}$.
 

### 2017-11-28 manuscripts/PNAS/second review/resub/chazthm_pnas_resub.tex
lemma 4 more clear

--- 2017-11-26 manuscripts/PNAS/second review/resub/chazthm_pnas_resub.tex
@@
 \begin{proof}
-Consider the set: $T_1 := \{(i, S): i \in \pi(S), S \in \mathcal{H}\}$, which number $|T_1| = \sum_{S \in \mathcal{H}} |\pi(S)| \geq \sum_{S \in \mathcal{H}} |S| = \sum_{i \in [m]} \deg_\mathcal{H}(i) = mr$.
-Note that \eqref{cond} implies $|T_1| \leq \overline m r$, since otherwise pigeonholing the elements of $T_1$ with respect to their possible first indices $[\overline m]$ would imply $\deg_\mathcal{H}(i) > r$ for some $i \in [m]$.
+Consider the set: $T_1 := \{(i, S): i \in \pi(S), S \in \mathcal{H}\}$, which numbers $|T_1| = \sum_{S \in \mathcal{H}} |\pi(S)| \geq \sum_{S \in \mathcal{H}} |S| = \sum_{i \in [m]} \deg_\mathcal{H}(i) = mr$.
+Note that $|T_1| \leq \overline m r$ by \eqref{cond}, since otherwise pigeonholing the elements of $T_1$ with respect to their possible first indices $[\overline m]$ would imply $\deg_\mathcal{H}(i) \geq r$ for some $i \in [m]$.
 Thus, $\overline m \geq m$.
 
-If $\overline m < mr / (r-1)$, then $p := \overline m - r( \overline m - m)$ is positive and $|T_1| \geq \overline m (r - 1) + p$.
-Pigeonholing $T_1$ into $[\overline m]$ again, there must be $r$ elements of $T_1$ sharing the same first index.
-By \eqref{cond}, the intersection of the set $\mathcal{G}_1$ of their second indices is nonempty; hence, $|\cap \mathcal{G}_1| = 1$ by $r$-regularity and the SIP.
-Since $\cap \pi(\mathcal{G}_1)$ is nonempty, applying \eqref{cond} again gives $\cap \pi(\mathcal{G}_1) = \{i_1\}$ for some $i_1 \in [\overline m]$.
+Suppose $\overline m (r-1) < mr$, so that $|T_1| \geq mr = \overline m (r - 1) + p$ for positive $p := mr - \overline m (r-1)$.
+Pigeonholing $T_1$ into $[\overline m]$ again, there must be at least $r$ elements of $T_1$ that share a first index.
+Let $i_1 \in [\overline m]$ be such an index and note that, in fact, no more than $r$ elements of $T_1$ can have $i_1$ as a first index; otherwise, the set $\mathcal{G}_1$ of their second indices would contain $r+1$ elements with a non-empty intersection by \eqref{cond}, contradicting $r$-regularity of $\mathcal{H}$.
+Thus, $|\mathcal{G}_1| = r$, and \eqref{cond} implies $|\cap \mathcal{G}_1| = 1$ by $r$-regularity and the SIP.
 If $p=1$, then we are done.
 Otherwise, define $T_2 := T_1 \setminus \{(i,S) \in T_1: i = i_1\}$, which contains $|T_2| = |T_1| - r \geq (\overline m - 1)(r-1) + (p-1)$ ordered pairs having $\overline m - 1$ distinct first indices.
-Repeating the above arguments produces a (necessarily, by $r$-regularity and the SIP) distinct $\mathcal{G}_2 \in {\mathcal{H} \choose r}$ and corresponding $i_2 \in [\overline m]$.
-Finally, iterating this $p$ times in total yields the set of singletons \mbox{$J = \{\cap \mathcal{G}_1, \ldots, \cap \mathcal{G}_p\} \subseteq [m]$}.
+Repeating the above arguments thus produces a distinct $i_2 \in [\overline m]$ and $\mathcal{G}_2 \in {\mathcal{H} \choose r}$ with (necessarily, by $r$-regularity and the SIP) distinct singleton $\cap \mathcal{G}_2 \in [m]$.
+Finally, iterating this $p$ times in total yields the set of singletons \mbox{$J = \{\cap \mathcal{G}_1, \ldots, \cap \mathcal{G}_p\}$}.
 \end{proof}

### 2017-11-29 manuscripts/PNAS/second review/resub/chazthm_pnas_resub.tex
end of proof of lemma 1 explanation

@@
 Since the only 1-uniform hypergraph with the SIP is $[m]$, we have $\mathbf{x}_i = c_i \mathbf{e}_i$ for $c_i \in \mathbb{R} \setminus \{\mathbf{0}\}$, $i \in [m]$.
-In this case, we may take any $C_1 \geq 1/ \min_{\ell \in [m]} |c_{\ell}|$.
+In this case, we may take $C_1 = 1/ \min_{\ell \in [m]} |c_{\ell}|$.
 
@@
 Thus,
-\begin{align}
+\begin{align}\label{last}
 d(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}, \bm{\mathcal{A}}_{\cap \mathcal{G}} )
@@
 By Lem.~\ref{NonEmptyLemma}, the association $i \mapsto \cap \pi(\sigma(i))$ is an injective map $\overline \pi: J \to [\overline m]$ for some $J \subseteq [m]$ of size $\overline m - r(\overline m - m)$, and $\mathbf{B}_{\overline \pi(i)} \neq \mathbf{0}$ for all $i \in J$ since the columns of $\mathbf{B}_{\pi(S)}$ are linearly independent for all $S \in \mathcal{H}$.
-It then follows from \eqref{eqdim} and \eqref{randoml} that $d\left( \bm{\mathcal{A}}_i, \bm{\mathcal{B}}_{\overline \pi(i)} \right) \leq C_2 \varepsilon / \max_i \|\mathbf{A}_i\|_2$ for all $i \in J$.
-Fixing $\overline \varepsilon = C_2\varepsilon$ and letting $c_i = \|\mathbf{A}_i\|_2^{-1}$, we thus have that for each $\mathbf{e}_i \in \mathbb{R}^m$ with $i \in J$ there exists some $\overline{c}_i \in \mathbb{R}$ such that $\|c_i\mathbf{A}\mathbf{e}_i - \overline{c}_i \mathbf{B}\mathbf{e}_{\overline \pi(i)}\|_2 \leq \overline \varepsilon < L_2(\mathbf{A}) \min_{i\in J} |c_i|$.
+It then follows from \eqref{eqdim} and \eqref{last} that $d\left( \bm{\mathcal{A}}_i, \bm{\mathcal{B}}_{\overline \pi(i)} \right) \leq \overline \varepsilon$ for all $i \in J$, with $\overline \varepsilon := C_2 \varepsilon / \max_i \|\mathbf{A}_i\|_2$.
+%Fixing $\overline \varepsilon = C_2\varepsilon$ and letting $c_i = \|\mathbf{A}_i\|_2^{-1}$, we thus have that for each $\mathbf{e}_i \in \mathbb{R}^m$ with $i \in J$ there exists some $\overline{c}_i \in \mathbb{R}$ such that $\|c_i\mathbf{A}\mathbf{e}_i - \overline{c}_i \mathbf{B}\mathbf{e}_{\overline \pi(i)}\|_2 \leq \overline \varepsilon < L_2(\mathbf{A}) \min_{i\in J} |c_i|$.
+But this is exactly the supposition in \eqref{1D}, and the result follows from the case $k=1$ in Sec.~\ref{DUT} applied to the submatrix $\mathbf{A}_J$.
+Letting $c_i := \|\mathbf{A}_i\|_2^{-1}$, we have by Def.~\ref{dDef}:
+\begin{align*}
+d\left( \bm{\mathcal{A}}_i, \bm{\mathcal{B}}_{\overline \pi(i)} \right)
+&= \sup_{\bm{u} \in \bm{\mathcal{A}}_i, \|\bm{u}\|_2 \leq 1} \text{dist}\left(\bm{u}, \bm{\mathcal{B}}_{\overline \pi(i)} \right) \\
+&\geq  \text{dist}\left(c_i\bm{Ae}_i, \mathbf{Be}_{\overline \pi(i)} \right) \\
+&= \inf_{\overline x_i \in \mathbb{R}} \|c_i\bm{Ae}_i - \overline c_i \mathbf{Be}_{\overline \pi(i)} \|_2
+\end{align*}
+%
+and there must then exist some $\overline c_i$ such that $\|c_i\bm{Ae}_i - \overline c_i \mathbf{Be}_{\overline \pi(i)} \|_2 \leq \overline \varepsilon$ for $\overline \varepsilon < L_2(\mathbf{A}) \min_{i\in J} |c_i|$ (since $\varepsilon < L_2(\mathbf{A})/C_2$).
 But this is exactly the supposition in \eqref{1D}, and the result follows from the case $k=1$ in Sec.~\ref{DUT} applied to the submatrix $\mathbf{A}_J$.

### 2017-11-29 manuscripts/PNAS/second review/resub/chazthm_pnas_resub.tex
end of proof of lemma 1 explanation

@@
 \begin{align}\label{Cdef2}
-	C_2(\mathbf{A}, \mathcal{H}) := \frac{ r \max_{j \in [m]} \|\mathbf{A}_j\|_2}{ 1- \max_{\mathcal{G} \in {\mathcal{H} \choose r}} \xi( \bm{\mathcal{A}}_\mathcal{G} ) },
+	C_2(\mathbf{A}, \mathcal{H}) := \frac{ (r+1) \max_{j \in [m]} \|\mathbf{A}_j\|_2}{ 1- \max_{\mathcal{G} \in {\mathcal{H} \choose r+1}} \xi( \bm{\mathcal{A}}_\mathcal{G} ) },
 \end{align}
 % C_2(\mathbf{A}, \mathcal{H}) := \frac{ (r+1) \max_{j \in [m]} \|\mathbf{A}_j\|_2}{ \min_{\mathcal{G} \in {\mathcal{H} \choose r} \cup {\mathcal{H} \choose r+1}} \xi( \{ \bm{\mathcal{A}}_S \}
-which we remark is consistent with the assumption on $C_1$ in the proof of the case $k=1$ at the beginning of this section.
+which we remark yields $C_2 \geq 2\max_{j \in [m]}\|\mathbf{A}_j\|_2$, and thus $C_1 = ??$, when applied to the case $k=1$ considered at the beginning of this section, consistent with its proof.
 
@@
 We next verify that \eqref{cond} holds.
-Fixing $\mathcal{G} \in {\mathcal{H} \choose r}$, it suffices to show that $d(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}, \bm{\mathcal{A}}_{\cap \mathcal{G}} ) < 1$, since by \eqref{dimLem} we then have $|\cap \pi(\mathcal{G})| = \dim(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}) \leq \dim(\bm{\mathcal{A}}_{\cap \mathcal{G}}) = |\cap \mathcal{G}|$, with equalities by the full column-ranks of $\mathbf{A}_{S}$ and $\mathbf{B}_{\pi(S)}$ for all $S \in \mathcal{H}$.\footnote{Note that if ever $\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})} \neq \bf 0$ while $\cap \mathcal{G} = \emptyset$, we would have $d(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}, \bm 0 ) = 1$.
+Fixing $\mathcal{G} \in {\mathcal{H} \choose r} \cup {\mathcal{H} \choose r+1}$, it suffices to show that $d(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}, \bm{\mathcal{A}}_{\cap \mathcal{G}} ) < 1$, since by \eqref{dimLem} we then have $|\cap \pi(\mathcal{G})| = \dim(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}) \leq \dim(\bm{\mathcal{A}}_{\cap \mathcal{G}}) = |\cap \mathcal{G}|$, with equalities by the full column-ranks of $\mathbf{A}_{S}$ and $\mathbf{B}_{\pi(S)}$ for all $S \in \mathcal{H}$.\footnote{Note that if ever $\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})} \neq \bf 0$ while $\cap \mathcal{G} = \emptyset$, we would have $d(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}, \bm 0 ) = 1$.
 This cannot be the case, however, since the deduction that follows would then lead to a contradiction.} Observe that $d(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}, \bm{\mathcal{A}}_{\cap \mathcal{G}}  )

### 2017-12-01 manuscripts/PNAS/second review/resub/chazthm_pnas_resub.tex
edits

@@
 %\begin{align*} 
-%L_\mathcal{H}(\mathbf{M}) := \inf \left\{ \frac{ \|\mathbf{M}(\mathbf{x}_1-\mathbf{x}_2)\|_2 }{ \sqrt{2k} \|\mathbf{x}_1-\mathbf{x}_2\|_2} : \mathbf{x}_1, \mathbf{x}_2 \in \cup_{S \in \mathcal{H}} \bm{\mathcal{M}}_S \right\},
+%L_\mathcal{H}(\mathbf{M}) := \min \left\{ \frac{ \|\mathbf{M}(\mathbf{x}_1-\mathbf{x}_2)\|_2 }{ \sqrt{2k} \|\mathbf{x}_1-\mathbf{x}_2\|_2} : \mathbf{x}_1, \mathbf{x}_2 \in \cup_{S \in \mathcal{H}} \bm{\mathcal{M}}_S \right\},
 %\end{align*} 
@@
 %\begin{align*}
-%L_\mathcal{H}(\mathbf{M}) := \inf \left\{ \frac{ \|\mathbf{M}_S\mathbf{x}\|_2 }{ \sqrt{k} \|\mathbf{x}\|_2} : S \in \mathcal{H} \right\},
+%L_\mathcal{H}(\mathbf{M}) := \min \left\{ \frac{ \|\mathbf{M}_S\mathbf{x}\|_2 }{ \sqrt{k} \|\mathbf{x}\|_2} : S \in \mathcal{H} \right\},
 %\end{align*} 
@@
 Since the only 1-uniform hypergraph with the SIP is $[m]$, we have $\mathbf{x}_i = c_i \mathbf{e}_i$ for $c_i \in \mathbb{R} \setminus \{\mathbf{0}\}$, $i \in [m]$.
-In this case, we may take $C_1 = 1/ \min_{\ell \in [m]} |c_{\ell}|$.
+In this case, we may use any $C_1 \geq 1/ \min_{\ell \in [m]} |c_{\ell}|$.
 
@@
 \begin{definition}\label{dDef}
-For $\mathbf{u} \in \mathbb R^m$ and vector spaces $U,V \subseteq \mathbb{R}^m$, let $\text{\rm dist}(\mathbf{u}, V) := \inf \{\| \mathbf{u}-\mathbf{v} \|_2: \mathbf{v} \in V\}$ and define:
+For $\mathbf{u} \in \mathbb R^m$ and vector spaces $U,V \subseteq \mathbb{R}^m$, let $\text{\rm dist}(\mathbf{u}, V) := \min \{\| \mathbf{u}-\mathbf{v} \|_2: \mathbf{v} \in V\}$ and define:
 \begin{align}
-d(U,V) := \sup_{\mathbf{u} \in U, \ \|\mathbf{u}\|_2 \leq 1} \text{\rm dist}(\mathbf{u},V).
+d(U,V) := \max_{\mathbf{u} \in U, \ \|\mathbf{u}\|_2 \leq 1} \text{\rm dist}(\mathbf{u},V).
 \end{align}
@@
 % C_2(\mathbf{A}, \mathcal{H}) := \frac{ (r+1) \max_{j \in [m]} \|\mathbf{A}_j\|_2}{ \min_{\mathcal{G} \in {\mathcal{H} \choose r} \cup {\mathcal{H} \choose r+1}} \xi( \{ \bm{\mathcal{A}}_S \}
-which we remark yields $C_2 \geq 2\max_{j \in [m]}\|\mathbf{A}_j\|_2$, and thus $C_1 = ??$, when applied to the case $k=1$ considered at the beginning of this section, consistent with its proof.
+which we remark yields a constant $C_1$ consistent with the case $k=1$ considered at the beginning of this section.\footnote{For $\mathbf{x}_i = c_i\mathbf{e}_i$, the denominator in \eqref{Cdef1} becomes $\min_{i \in [m]} |c_i| \|\mathbf{A}_i\|_2$, hence with $r=1$ we have $C_1 \geq 2 / \min_{i \in [m]} |c_i|$.}
 
@@
 \begin{lemma}\label{spanIntersectionLemma}
-If $f: U \to V$ is an injective function, then $f\left(\cap_{i=1}^\ell U_i \right) =  \cap_{i=1}^\ell f\left(U_i\right)$ for any $U_1, \ldots, U_\ell \subseteq U$. ($f(\emptyset):=\emptyset$.)
+If $f: V \to W$ is an injective function, then $f\left(\cap_{i=1}^\ell V_i \right) =  \cap_{i=1}^\ell f\left(V_i\right)$ for any $V_1, \ldots, V_\ell \subseteq V$. ($f(\emptyset):=\emptyset$.)
 %In particular, if for some $E \in 2^{[m]}$ the map $M \in \mathbb{R}^{n \times m}$ is injective on $\cup_{S \in \mathcal{H}} \text{span}\{e_i\}_{i \in S}$ then $\text{span}\{ M_{\cap_{S \in \mathcal{H}} S} \} = \cap_{S \in \mathcal{H}} \text{span}\{M_S\}$.
@@
 \end{proof}
+In particular, if a matrix $\mathbf{A}$ satisfies $L_{2\mathcal{H}}(\mathbf{A}) > 0$, then letting $V$ be the set of vectors with supports in $2\mathcal{H}$, we have $\bm{\mathcal{A}}_{\cap \mathcal{G}} = \cap \bm{\mathcal{A}}_\mathcal{G}$ for all $\mathcal{G} \subseteq \mathcal{H}$.
 % \vspace{-.4 cm}
@@
 This cannot be the case, however, since the deduction that follows would then lead to a contradiction.} Observe that $d(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}, \bm{\mathcal{A}}_{\cap \mathcal{G}}  )
-\leq d\left( \cap \bm{\mathcal{B}}_{\pi(\mathcal{G})}, \cap \bm{\mathcal{A}}_\mathcal{G} \right)$, since $\bm{\mathcal{A}}_{\cap \mathcal{G}} = \cap \bm{\mathcal{A}}_\mathcal{G}$ by Lem.~\ref{spanIntersectionLemma} and $d(U',V) \leq d(U,V)$ whenever $U' \subseteq U$.
+\leq d\left( \cap \bm{\mathcal{B}}_{\pi(\mathcal{G})}, \cap \bm{\mathcal{A}}_\mathcal{G} \right)$, since $d(U',V) \leq d(U,V)$ whenever $U' \subseteq U$ and $\bm{\mathcal{A}}_{\cap \mathcal{G}} = \cap \bm{\mathcal{A}}_\mathcal{G}$ by Lem.~\ref{spanIntersectionLemma}.
 Recalling Def.~\ref{dDef}, we may apply Lem.~\ref{DistanceToIntersectionLemma} and carry the supremum through the sum:
@@
 d\left( \cap \bm{\mathcal{B}}_{\pi(\mathcal{G})}, \cap \bm{\mathcal{A}}_\mathcal{G} \right)
-%&\leq \sup_{\mathbf{u} \in \cap \bm{\mathcal{B}}_{\pi(\mathcal{G})}, \ \|\mathbf{u}\|_2 \leq 1} \sum_{S \in \mathcal{G}} \frac{ \text{\rm dist}\left( \mathbf{u},\bm{\mathcal{A}}_{S} \right) }{ 1 - \xi( \bm{\mathcal{A}}_\mathcal{G} ) }
+%&\leq \max_{\mathbf{u} \in \cap \bm{\mathcal{B}}_{\pi(\mathcal{G})}, \ \|\mathbf{u}\|_2 \leq 1} \sum_{S \in \mathcal{G}} \frac{ \text{\rm dist}\left( \mathbf{u},\bm{\mathcal{A}}_{S} \right) }{ 1 - \xi( \bm{\mathcal{A}}_\mathcal{G} ) }
 \leq \sum_{S \in \mathcal{G}} \frac{ d\left( \cap \bm{\mathcal{B}}_{\pi(\mathcal{G})},\bm{\mathcal{A}}_{S} \right) }{ 1 - \xi( \bm{\mathcal{A}}_\mathcal{G} ) }.
@@
 By Lem.~\ref{NonEmptyLemma}, the association $i \mapsto \cap \pi(\sigma(i))$ is an injective map $\overline \pi: J \to [\overline m]$ for some $J \subseteq [m]$ of size $\overline m - r(\overline m - m)$, and $\mathbf{B}_{\overline \pi(i)} \neq \mathbf{0}$ for all $i \in J$ since the columns of $\mathbf{B}_{\pi(S)}$ are linearly independent for all $S \in \mathcal{H}$.
-It then follows from \eqref{eqdim} and \eqref{last} that $d\left( \bm{\mathcal{A}}_i, \bm{\mathcal{B}}_{\overline \pi(i)} \right) \leq \overline \varepsilon$ for all $i \in J$, with $\overline \varepsilon := C_2 \varepsilon / \max_i \|\mathbf{A}_i\|_2$.
+Letting $\overline \varepsilon := C_2 \varepsilon / \max_i \|\mathbf{A}_i\|_2$, it follows from \eqref{eqdim} and \eqref{last} that $d\left( \bm{\mathcal{A}}_i, \bm{\mathcal{B}}_{\overline \pi(i)} \right) \leq \overline \varepsilon$ for all $i \in J$.
 %Fixing $\overline \varepsilon = C_2\varepsilon$ and letting $c_i = \|\mathbf{A}_i\|_2^{-1}$, we thus have that for each $\mathbf{e}_i \in \mathbb{R}^m$ with $i \in J$ there exists some $\overline{c}_i \in \mathbb{R}$ such that $\|c_i\mathbf{A}\mathbf{e}_i - \overline{c}_i \mathbf{B}\mathbf{e}_{\overline \pi(i)}\|_2 \leq \overline \varepsilon < L_2(\mathbf{A}) \min_{i\in J} |c_i|$.
 But this is exactly the supposition in \eqref{1D}, and the result follows from the case $k=1$ in Sec.~\ref{DUT} applied to the submatrix $\mathbf{A}_J$.
-Letting $c_i := \|\mathbf{A}_i\|_2^{-1}$, we have by Def.~\ref{dDef}:
+Setting $c_i := \|\mathbf{A}_i\|_2^{-1}$, by Def.~\ref{dDef} we have for all $i \in J$:
 \begin{align*}
-d\left( \bm{\mathcal{A}}_i, \bm{\mathcal{B}}_{\overline \pi(i)} \right)
-&= \sup_{\bm{u} \in \bm{\mathcal{A}}_i, \|\bm{u}\|_2 \leq 1} \text{dist}\left(\bm{u}, \bm{\mathcal{B}}_{\overline \pi(i)} \right) \\
-&\geq  \text{dist}\left(c_i\bm{Ae}_i, \mathbf{Be}_{\overline \pi(i)} \right) \\
-&= \inf_{\overline x_i \in \mathbb{R}} \|c_i\bm{Ae}_i - \overline c_i \mathbf{Be}_{\overline \pi(i)} \|_2
+\min_{\overline c_i \in \mathbb{R}} \|c_i\bm{Ae}_i - \overline c_i \mathbf{Be}_{\overline \pi(i)} \|_2
+\leq d\left( \bm{\mathcal{A}}_i, \bm{\mathcal{B}}_{\overline \pi(i)} \right)
+\leq \overline \varepsilon
+%&= \max_{\bm{u} \in \bm{\mathcal{A}}_i, \|\bm{u}\|_2 \leq 1} \text{dist}\left(\bm{u}, \bm{\mathcal{B}}_{\overline \pi(i)} \right) \\
+%&\geq  \text{dist}\left(c_i\bm{Ae}_i, \mathbf{Be}_{\overline \pi(i)} \right) \\
+%&= \min_{\overline c_i \in \mathbb{R}} \|c_i\bm{Ae}_i - \overline c_i \mathbf{Be}_{\overline \pi(i)} \|_2
 \end{align*}
 %
-and there must then exist some $\overline c_i$ such that $\|c_i\bm{Ae}_i - \overline c_i \mathbf{Be}_{\overline \pi(i)} \|_2 \leq \overline \varepsilon$ for $\overline \varepsilon < L_2(\mathbf{A}) \min_{i\in J} |c_i|$ (since $\varepsilon < L_2(\mathbf{A})/C_2$).
-But this is exactly the supposition in \eqref{1D}, and the result follows from the case $k=1$ in Sec.~\ref{DUT} applied to the submatrix $\mathbf{A}_J$.
+for $\overline \varepsilon < L_2(\mathbf{A})\min_{i \in [m]}|c_i|$.
+But this is exactly the supposition in \eqref{1D} (with $J$ in place of $[m]$), and the result thus follows from the case $k=1$ in Sec.~\ref{DUT} applied to the submatrix $\mathbf{A}_J$.
 \end{proof}

### 2017-12-01 manuscripts/PNAS/second review/resub/chazthm_pnas_resub.tex
more edits

@@
 \begin{problem}[Sparse linear coding]\label{InverseProblem}
-Find a matrix $\mathbf{B}$ and $k$-sparse $\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N \in \mathbb{R}^m$ so that $\|\mathbf{z}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \eta$ for all $i$.
+Find a matrix $\mathbf{B}$ and $k$-sparse $\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N \in \mathbb{R}^{\overline m}$ so that $\|\mathbf{z}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \eta$ for all $i$.
 \end{problem}
@@
 Note that any particular solution $(\mathbf{B}, \mathbf{\overline x}_1 \ldots, \mathbf{\overline x}_N)$ to this problem gives rise to an orbit of equivalent solutions $(\mathbf{BPD}, \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_1, \ldots, \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_N)$, where $\mathbf{P}$ is any permutation matrix and $\mathbf{D}$ any invertible diagonal.
-Previous theoretical work addressing the noiseless case $\eta =0$ (e.g., \cite{li2004analysis, Georgiev05, Aharon06, Hillar15}) has shown that a solution to Prob.~\ref{InverseProblem} (when it exists) is unique up to this  ambiguity provided the $\mathbf{x}_i$ are sufficiently diverse and the generating matrix $\mathbf{A}$ satisfies the \textit{spark condition}:
+Previous theoretical work addressing the noiseless case $\eta =0$ (e.g., \cite{li2004analysis, Georgiev05, Aharon06, Hillar15}) with $\overline m = m$ has shown that a solution to Prob.~\ref{InverseProblem} (when it exists) is unique up to this  ambiguity provided the $\mathbf{x}_i$ are sufficiently diverse and the matrix $\mathbf{A}$ satisfies the \textit{spark condition}:
 \begin{align}\label{SparkCondition}
@@
 We generalize the  lower bound to a domain-restricted \emph{union of subspaces} model \cite{vidal2005generalized} derived from a hypergraph $\mathcal{H} \subseteq {[m] \choose k}$.
-Letting $\mathbf{M}_S$ denote the submatrix formed by the columns of $\mathbf{M}$ indexed by $S \subseteq [m]$ (with $\mathbf{M}_\emptyset := \mathbf{0}$), we define:
+Let $\mathbf{M}_S$ denote the submatrix formed by the columns of $\mathbf{M}$ indexed by $S \subseteq [m]$, with $\mathbf{M}_\emptyset := \mathbf{0}$.
+(In the sections that follow, we will write $\bm{\mathcal{M}}_S$ to denote the column-span of a submatrix $\mathbf{M}_S$, and $\bm{\mathcal{M}}_\mathcal{G}$ to denote $\{\bm{\mathcal{M}}_S\}_{S \in \mathcal{G}}$.) Define:
 %\begin{align*} 
@@
 Note also that $L_2 \geq L_{2\mathcal{H}} \geq L_{2k}$ if $\mathcal{H} \subseteq {[m] \choose k}$ has $\cup \mathcal{H} = [m]$.
-In the sections that follow, we will write $\bm{\mathcal{M}}_S$ to denote the column-span of a submatrix $\mathbf{M}_S$, and $\bm{\mathcal{M}}_\mathcal{G}$ to denote $\{\bm{\mathcal{M}}_S\}_{S \in \mathcal{G}}$.
 
@@
 We leave the quantity $C_1 = C_1(\mathbf{A}, \{\mathbf{x}_i\}_{i=1}^N, \mathcal{H})$ undefined until Eq.~\eqref{Cdef1}.
+All of our theorems assume matrices consist of real numbers.
 
@@
 \begin{theorem}\label{robustPolythm}
-There is a polynomial $g$ in the entries of $\mathbf{A}$ and $\mathbf{x}_i$ with the following property:  if $g$ evaluates to a nonzero number and more than \mbox{$(k-1){m \choose k}$} of the resulting $\mathbf{x}_i$ are supported in each $S \in \mathcal{H}$ for some regular $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP, then $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$ (Def.~\ref{maindef}).
+There is a polynomial $g$ in the entries of $\mathbf{A} \in \mathbb{R}^{n \times m}$ and $\mathbf{x}_i \in \mathbb{R}^m$ with the following property:  if $g$ evaluates to a nonzero number and more than \mbox{$(k-1){m \choose k}$} of the resulting $\mathbf{x}_i$ are supported in each $S \in \mathcal{H}$ for some regular $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP, then $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$ (Def.~\ref{maindef}).
 In particular, all -- except for a Borel set of measure zero -- substitutions impart to $Y$ this property.
@@
 \end{align}
-for some nonempty $J \subseteq [m]$ and $\overline J \subseteq[\overline{m}]$ of size $\overline m - r(\overline m - m)$.
+for some nonempty $\overline J \subseteq[\overline{m}]$ and $J \subseteq [m]$ of size $\overline m - r(\overline m - m)$.
 \end{lemma}
@@
 \begin{proof}[Proof (sketch) of Thm.~\ref{robustPolythm}]
-Let $\textbf{M}$ be the matrix with columns $\mathbf{A}\mathbf{x}_i$, $i \in [N]$.  Consider the polynomial in the entries of $\mathbf{A}$ and $\mathbf{x}_i$:
-$g(\mathbf{A}, \{\mathbf{x}_i\}_{i=1}^N) := \prod_{S \in {[N] \choose 2k}} \sum_{S' \in {[n] \choose 2k}} (\det \textbf{M}_{S',S})^2$,
-with notation as in Sec.~\ref{Results}.  
-It can be checked that when $g$ is nonzero for a substitution of real numbers for the indeterminates, all of the genericity requirements on $\mathbf{A}$ and $\mathbf{x}_i$ in our proofs of stability in Thm.~\ref{DeterministicUniquenessTheorem} are satisfied (in particular, the spark condition on $\mathbf{A}$).
+Let $\textbf{M}$ be the matrix with columns $\mathbf{A}\mathbf{x}_i$, $i \in [N]$.
+Consider the polynomial $\prod_{S \in {[N] \choose 2k}} \sum_{S' \in {[n] \choose 2k}} (\det \textbf{M}_{S',S})^2$ in the indeterminate entries of $\mathbf{A}$ and $\mathbf{x}_i$, with notation as in Sec.~\ref{Results}.
+It can be checked that when this polynomial is nonzero for a substitution of real numbers for the indeterminates, all of the genericity requirements on $\mathbf{A}$ and $\mathbf{x}_i$ in our proofs of stability in Thm.~\ref{DeterministicUniquenessTheorem} are satisfied (in particular, the spark condition \eqref{SparkCondition} on $\mathbf{A}$).
 \end{proof}
@@
 \leq d\left( \cap \bm{\mathcal{B}}_{\pi(\mathcal{G})}, \cap \bm{\mathcal{A}}_\mathcal{G} \right)$, since $d(U',V) \leq d(U,V)$ whenever $U' \subseteq U$ and $\bm{\mathcal{A}}_{\cap \mathcal{G}} = \cap \bm{\mathcal{A}}_\mathcal{G}$ by Lem.~\ref{spanIntersectionLemma}.
-Recalling Def.~\ref{dDef}, we may apply Lem.~\ref{DistanceToIntersectionLemma} and carry the supremum through the sum:
+Recalling Def.~\ref{dDef}, we applying Lem.~\ref{DistanceToIntersectionLemma} and carrying the supremum through the sum yields:
 \begin{align}

### 2017-12-02 manuscripts/PNAS/second review/resub/chazthm_pnas_resub.tex
edits
minor things

@@
 Let $\mathbf{M}_S$ denote the submatrix formed by the columns of $\mathbf{M}$ indexed by $S \subseteq [m]$, with $\mathbf{M}_\emptyset := \mathbf{0}$.
-(In the sections that follow, we will write $\bm{\mathcal{M}}_S$ to denote the column-span of a submatrix $\mathbf{M}_S$, and $\bm{\mathcal{M}}_\mathcal{G}$ to denote $\{\bm{\mathcal{M}}_S\}_{S \in \mathcal{G}}$.) Define:
+(In the sections that follow, we write $\bm{\mathcal{M}}_S$ to denote the column-span of a submatrix $\mathbf{M}_S$, and $\bm{\mathcal{M}}_\mathcal{G}$ to denote $\{\bm{\mathcal{M}}_S\}_{S \in \mathcal{G}}$.) Define:
 %\begin{align*} 
@@
 %\cite{li2004analysis, Georgiev05, Aharon06, Hillar15}
-We furthermore note that unlike in previous works, the matrix $\mathbf{A}$ need not satisfy the spark condition to be recoverable from data.
-As a simple example for $k=2$, let $\mathbf{A} = [ \mathbf{e}_1, \ldots, \mathbf{e}_5, \mathbf{v}]$ where $\mathbf{v} = \mathbf{e}_1 + \mathbf{e}_3 + \mathbf{e}_5$, and take $\mathcal{H}$ to be all consecutive pairs of $[m]$ arranged in cyclic order.
+We furthermore note that unlike in previous works, the matrix $\mathbf{A}$ need not satisfy \eqref{SparkCondition} to be recoverable from data.
+As an example for $k=2$, let $\mathbf{A} = [ \mathbf{e}_1, \ldots, \mathbf{e}_5, \mathbf{v}]$ where $\mathbf{v} = \mathbf{e}_1 + \mathbf{e}_3 + \mathbf{e}_5$, and take $\mathcal{H}$ to be all consecutive pairs of $[m]$ arranged in cyclic order.
 Then, dictionary $\mathbf{A}$ satisfies the assumptions of Thm.~\ref{DeterministicUniquenessTheorem} underlying \eqref{Cstable} without satisfying \eqref{SparkCondition}.
@@
 \end{align} 
-Note that $\overline{c}_j \neq 0$, since otherwise we have the contradiction $\|\mathbf{A}_j \|_2 \leq C_1 |c_j| \|\mathbf{A}_j \|_2  < L_2(\mathbf{A}) \leq L_1(\mathbf{A}) = \min_{i \in [m]} \|\mathbf{A}_i\|_2$.
+Note that $\overline{c}_j \neq 0$, since otherwise we have the contradiction $\|\mathbf{A}_j \|_2 \leq C_1 |c_j| \|\mathbf{A}_j \|_2  < L_2(\mathbf{A}) \leq L_1(\mathbf{A}) = \min_{j \in [m]} \|\mathbf{A}_{j}\|_2$.
 %implies by \eqref{delrho} the contradiction $|c_j| < \min_{\ell \in [m]} | c_\ell |$.
@@
 There is no known fast computation of $L_k$ in general, however, since even $L_{k} > 0$ is NP-hard \cite{tillmann2014computational}; although fixing $k$ yields polynomial complexity.
-Moreover, calculating $C_2$ requires an exponential number of queries to $\xi$.
+Moreover, calculating $C_2$ requires an exponential number of queries to $\xi$ unless $r$ is held fixed, too (e.g., the ``cyclic order'' hypergraphs described above have $r=k$).
 Thus, as presented, $C_1$ and $C_2$ are not efficiently computable.
@@
 \begin{proof}[Proof of Thm.~\ref{DeterministicUniquenessCorollary} for $k < m$] 
-We demonstrate the existence of a map $\pi: \mathcal{H} \to 2^{[\overline m]}$ for which the distance $d(\bm{\mathcal{A}}_S, \bm{\mathcal{B}}_{\pi(S)})$ is controlled by $\varepsilon$.
+We find a map $\pi: \mathcal{H} \to 2^{[\overline m]}$ for which the distance $d(\bm{\mathcal{A}}_S, \bm{\mathcal{B}}_{\pi(S)})$ is controlled by $\varepsilon$.
 Applying Lem.~\ref{MainLemma} then completes the proof.
-
 %We shall show that for every $S \in \mathcal{H}$ there is some $\overline S \in {[\overline m] \choose k}$ for which the distance $d(\bm{\mathcal{A}}_S, \bm{\mathcal{B}}_{\overline S})$ is controlled by $\varepsilon$.
@@
 Since there are more than $(k-1){\overline m \choose k}$ vectors $\mathbf{x}_i$ supported in each $S \in \mathcal{H}$, the pigeonhole principle gives $\overline S \in {[\overline m] \choose k}$ and a set of $k$ indices $K \subseteq I(S)$ with all $\mathbf{\overline x}_i$, $i \in K$, supported in $\pi(S) := \overline S$.
+It also follows from $L_{2\mathcal{H}}(\mathbf{A}) > 0$ and the general linear position of the $\mathbf{x}_i$ that $L_k(\mathbf{AX}_{K}) > 0$; that is, the columns of the $n \times k$ matrix $\mathbf{AX}_K$ form a basis for $\bm{\mathcal{A}}_S$.
 
-It follows from $L_{2\mathcal{H}}(\mathbf{A}) > 0$ and the general linear position of the $\mathbf{x}_i$ that $L_k(\mathbf{AX}_{K}) > 0$; that is, the columns of the $n \times k$ matrix $\mathbf{AX}_K$ form a basis for $\bm{\mathcal{A}}_S$.
 Fixing $\mathbf{0} \neq \mathbf{y} \in \bm{\mathcal{A}}_S$, there then exists $\mathbf{0} \neq \mathbf{c} = (c_1, \ldots, c_k) \in \mathbb{R}^k$ such that $\mathbf{y} = \mathbf{AX}_K\mathbf{c}$.
@@
 \end{align}
-Since $\cap \bm{\mathcal{B}}_{\pi(\mathcal{G})} \subseteq \bm{\mathcal{B}}_{\pi(S)}$ for all $S \in \mathcal{G}$, the numerator of each term above is bounded by $d\left( \bm{\mathcal{B}}_{\pi(S)},\bm{\mathcal{A}}_{S} \right)$ and, recalling \eqref{eqdim} (since $\dim(\bm{\mathcal{B}}_{\pi(S)}) = \dim(\bm{\mathcal{A}}_S)$), by $d\left(\bm{\mathcal{A}}_{S}, \bm{\mathcal{B}}_{\pi(S)} \right) \leq \varepsilon$, in turn.
-Thus,
+Since $\cap \bm{\mathcal{B}}_{\pi(\mathcal{G})} \subseteq \bm{\mathcal{B}}_{\pi(S)}$ for all $S \in \mathcal{G}$, the numerator of each term above is bounded by $d\left( \bm{\mathcal{B}}_{\pi(S)},\bm{\mathcal{A}}_{S} \right)$ and, recalling \eqref{eqdim} (since $\dim(\bm{\mathcal{B}}_{\pi(S)}) = \dim(\bm{\mathcal{A}}_S)$), in turn by $d\left(\bm{\mathcal{A}}_{S}, \bm{\mathcal{B}}_{\pi(S)} \right) \leq \varepsilon$.
+Thus:
 \begin{align}\label{last}

### 2017-12-02 manuscripts/PNAS/second review/resub/chazthm_pnas_resub.tex
added SDL science refs

@@
 Answers to this question also have other real-world implications.
-For example, a sparse coding analysis of local painting style can be used for forgery detection \cite{hughes2010, Olshausen10}, but only if all dictionaries consistent with training data do not differ appreciably in their ability to sparsely encode new samples.
+For example, a sparse coding analysis of local painting style can be used for forgery detection \cite{hughes2010}, but only if all dictionaries consistent with training data do not differ appreciably in their ability to sparsely encode new samples.
 Fortunately, algorithms with proven recovery of generating dictionaries under certain 
@@
 For example, several groups have applied compressed sensing to signal processing tasks: MRI analysis \cite{lustig2008compressed}, image compression \cite{Duarte08}, and, more recently, the design of an ultrafast camera \cite{Gao14}.
-Given such effective uses of compressed sensing, it is only a matter of time before these systems incorporate dictionary learning to encode and process data (e.g., in a device that learns structure from motion \cite{kong2016prior}).
+Given such effective uses of compressed sensing, it is only a matter of time before these systems incorporate dictionary learning to encode and decode signals (e.g., in a device that learns structure from motion \cite{kong2016prior}) just as scientists have used it to make sense of their data \cite{jung2001imaging, Agarwal14, lee2016sparse, wu2016stability}.
 Assurances such as those offered by our theorems certify that different devices (with different initialization, etc.) will learn equivalent representations given enough data from statistically identical systems.\footnote{To contrast with the current hot topic of ``Deep Learning'', there are few such uniqueness guarantees for these models of data; moreover, even small noise can dramatically alter their output \cite{goodfellow2014explaining}.} Indeed, it seems a main reason for the sustained interest in dictionary learning as an unsupervised method for data analysis is the assumed well-posedness of parameter identification in the sparse linear coding model, confirmation of which forms the core of our theoretical findings.

### 2017-12-02 manuscripts/PNAS/second review/resub/chazthm_pnas_resub.tex
explanations

--- 2017-12-01 manuscripts/PNAS/second review/resub/chazthm_pnas_resub.tex
@@
 Since the only 1-uniform hypergraph with the SIP is $[m]$, we have $\mathbf{x}_i = c_i \mathbf{e}_i$ for $c_i \in \mathbb{R} \setminus \{\mathbf{0}\}$, $i \in [m]$.
-In this case, we may use any $C_1 \geq 1/ \min_{\ell \in [m]} |c_{\ell}|$.
+In this case, we require that $C_1 \geq 1/ \min_{\ell \in [m]} |c_{\ell}|$.
 
@@
 % C_2(\mathbf{A}, \mathcal{H}) := \frac{ (r+1) \max_{j \in [m]} \|\mathbf{A}_j\|_2}{ \min_{\mathcal{G} \in {\mathcal{H} \choose r} \cup {\mathcal{H} \choose r+1}} \xi( \{ \bm{\mathcal{A}}_S \}
-which we remark yields a constant $C_1$ consistent with the case $k=1$ considered at the beginning of this section.\footnote{For $\mathbf{x}_i = c_i\mathbf{e}_i$, the denominator in \eqref{Cdef1} becomes $\min_{i \in [m]} |c_i| \|\mathbf{A}_i\|_2$, hence with $r=1$ we have $C_1 \geq 2 / \min_{i \in [m]} |c_i|$.}
+which we remark yields a constant $C_1$ consistent with what is required for the case $k=1$ considered at the beginning of this section.\footnote{For $\mathbf{x}_i = c_i\mathbf{e}_i$, the denominator in \eqref{Cdef1} becomes $\min_{i \in [m]} |c_i| \|\mathbf{A}_i\|_2$, hence with $r=1$ we have $C_1 \geq 2 / \min_{i \in [m]} |c_i|$.}
 
@@
 There is no known fast computation of $L_k$ in general, however, since even $L_{k} > 0$ is NP-hard \cite{tillmann2014computational}; although fixing $k$ yields polynomial complexity.
-Moreover, calculating $C_2$ requires an exponential number of queries to $\xi$.
+Moreover, calculating $C_2$ requires an exponential number of queries to $\xi$ unless $r$ is held fixed, too (e.g., the `cyclic order' hypergraphs described above have $r=k$).
 Thus, as presented, $C_1$ and $C_2$ are not efficiently computable.
@@
 But this is exactly the supposition in \eqref{1D}, and the result follows from the case $k=1$ in Sec.~\ref{DUT} applied to the submatrix $\mathbf{A}_J$.
-Setting $c_i := \|\mathbf{A}_i\|_2^{-1}$, by Def.~\ref{dDef} we have for all $i \in J$:
+Setting $c_i := \|\mathbf{A}_i\|_2^{-1}$ so that $\|c_i\mathbf{Ae}_i\|_2 = 1$, by Def.~\ref{dDef} we have for all $i \in J$:
 \begin{align*}
-\min_{\overline c_i \in \mathbb{R}} \|c_i\bm{Ae}_i - \overline c_i \mathbf{Be}_{\overline \pi(i)} \|_2
+\min_{\overline c_i \in \mathbb{R}} \|c_i\mathbf{Ae}_i - \overline c_i \mathbf{Be}_{\overline \pi(i)} \|_2
 \leq d\left( \bm{\mathcal{A}}_i, \bm{\mathcal{B}}_{\overline \pi(i)} \right)
@@
 for $\overline \varepsilon < L_2(\mathbf{A})\min_{i \in [m]}|c_i|$.
-But this is exactly the supposition in \eqref{1D} (with $J$ in place of $[m]$), and the result thus follows from the case $k=1$ in Sec.~\ref{DUT} applied to the submatrix $\mathbf{A}_J$.
+But this is exactly the supposition in \eqref{1D}, with $J$ and $\overline \varepsilon$ in place of $[m]$ and $\varepsilon$, respectively.
+Thus, applying the arguments of the case $k=1$ in Sec.~\ref{DUT} to the submatrix $\mathbf{A}_J$, we have $\|\mathbf{A}_j - \mathbf{B}_{\overline J}\mathbf{PD}_j\|_2 \leq \overline  \varepsilon / |c_j|  \leq C_2 \varepsilon$ for $j \in J$.
 \end{proof}

### 2017-12-02 manuscripts/PNAS/second review/resub/chazthm_pnas_resub.tex
chs

@@
 \leq d\left( \cap \bm{\mathcal{B}}_{\pi(\mathcal{G})}, \cap \bm{\mathcal{A}}_\mathcal{G} \right)$, since $d(U',V) \leq d(U,V)$ whenever $U' \subseteq U$ and $\bm{\mathcal{A}}_{\cap \mathcal{G}} = \cap \bm{\mathcal{A}}_\mathcal{G}$ by Lem.~\ref{spanIntersectionLemma}.
-Recalling Def.~\ref{dDef}, we applying Lem.~\ref{DistanceToIntersectionLemma} and carrying the supremum through the sum yields:
+Recalling Def.~\ref{dDef}, applying Lem.~\ref{DistanceToIntersectionLemma} and carrying the supremum through the sum yields:
 \begin{align}
@@
 But this is exactly the supposition in \eqref{1D}, with $J$ and $\overline \varepsilon$ in place of $[m]$ and $\varepsilon$, respectively.
-Thus, applying the arguments of the case $k=1$ in Sec.~\ref{DUT} to the submatrix $\mathbf{A}_J$, we have $\|\mathbf{A}_j - \mathbf{B}_{\overline J}\mathbf{PD}_j\|_2 \leq \overline  \varepsilon / |c_j|  \leq C_2 \varepsilon$ for $j \in J$.
+Applying the arguments of the case $k=1$ in Sec.~\ref{DUT} to the submatrix $\mathbf{A}_J$ then finally yields $\|\mathbf{A}_j - \mathbf{B}_{\overline J}\mathbf{PD}_j\|_2 \leq \overline  \varepsilon / |c_j|  \leq C_2 \varepsilon$ for $j \in J$.
 \end{proof}

### 2017-12-02 manuscripts/PNAS/second review/code/constants.py
code update C2

@@ -13,7 +13,7 @@ def friedrichs(U,V):
     Alternatively, it is the (s+1)th principal angle when dim(U \cap V) = s.
     """
     angles = subspace_angles(U,V)
-    nz_angles = angles > np.finfo(float).eps
+    nz_angles = angles > 0  # np.finfo(float).eps
     if np.any(nz_angles):
         min_nz_angle = np.sort(angles[nz_angles])[0]
         return min_nz_angle
@@ -148,52 +148,52 @@ if __name__ == '__main__':
         pp.hist(C2s, bins=40)
         pp.show()
         pp.title('Grid C2s (m=%d, trials=%d)' % (m, num_trials))
-        plt.savefig('Grid_C2_m%d_nt%d.pdf' % (m, num_trials))
+        # plt.savefig('Grid_C2_m%d_nt%d.pdf' % (m, num_trials))
 
-    # CYLIC
-    Ks = [4, 8] # , 16, 32]
-    for k in Ks:
-        r = k
-        m = k ** 2
-        n = m
-        H = cyclic_hypergraph(m, k)
-        N_per_support = int((k - 1) * choose(m, k))
-        N = len(H) * N_per_support
-        num_trials = 5
-        Cs = np.zeros((num_trials, 2))  # 0:C1, 1:C2
-        #pcntiles = np.zeros((num_trials, 2))  # 0:C1, 1:C2
-        for i in range(num_trials):
-            print("Trial %d" % i)
-            A = np.random.randn(n, m)
-            A = np.dot( A, np.diag(1./np.linalg.norm(A, axis=0)) ) # normalize
-            # Xs = [np.random.randn(k, N_per_support) for S in H]
-            # Xs = [np.dot(X, np.diag(1. / np.linalg.norm(X, axis=0))) for X in Xs] # normalize
-            Cs[i, 1] = C2(A, H, r)
-            # Cs[i, 0] = Cs[i,1] / C1_denom(A, Xs, H, num_rand_ksets = 10)
-            #Cs[i,0] = Cs[i,1] / L_k( np.dot(A[:,H[0]], Xs[0]), k, n_samples = 10 )
-           # print('%1.3f' % c2)
-           # if (i > 1000) & (i % 100 == 0):
-           #     print(i)
-           #     pcntiles[i, 1] = np.percentile(Cs[:i, 1], 95)
-
-        import matplotlib.pyplot as pp
[…]

### 2017-12-02 manuscripts/PNAS/second review/response/compute_C2.py

@@ -11,7 +11,7 @@ def friedrichs(U,V):
     Alternatively, it is the (s+1)th principal angle when dim(U \cap V) = s.
     """
     angles = subspace_angles(U,V)
-    nz_angles = angles > np.finfo(float).eps
+    nz_angles = angles > 0  # np.finfo(float).eps
     if np.any(nz_angles):
         min_nz_angle = np.sort(angles[nz_angles])[0]
         return min_nz_angle
@@ -45,7 +45,7 @@ def C2(A, H, r):
     H: hypergraph (list of lists in range(m))
     r: regularity of H
 
-    Loops over subsets of H of size r+1
+    Loops over subsets of H of size r
     """
     xi_Gs = [] # xi is in (0,1]
     for G in itertools.combinations(H, r + 1): # loop over subsets of H of size r
@@ -64,12 +64,12 @@ def cyclic_hypergraph(m, k):
 
 if __name__ == '__main__':
     # SQUARE GRID
-    num_trials = 100
+    num_trials = 50
     r = 2
-    Ks = [4, 8, 16]
+    Ks = [32]
     for k in Ks:
         m = k**2
-        n = m;
+        n = m // 2;
         square_grid = np.reshape(range(m),(k,k))
         H = [row.tolist() for row in square_grid] + [col.tolist() for col in square_grid.T]
         N_per_support = int((k - 1) * choose(m, k))
@@ -87,5 +87,40 @@ if __name__ == '__main__':
         pp.figure()
         pp.hist(C2s, bins=40)
         pp.show()
-        pp.title('Grid C2s (m=%d, trials=%d)' % (m, num_trials))
-        pp.savefig('Grid_C2_m%d_nt%d.pdf' % (m, num_trials))
+        pp.title('Grid C2s (m=%d, n=%d, trials=%d)' % (m, n, num_trials))
+        pp.savefig('Grid_C2_m%d_n%d_r%d_ k%d_nt%d_r.pdf' % (m, n, r, k, num_trials))
+
+    # CYLIC
+    Ks = [4] # , 16, 32]
+    for k in Ks:
+        r = k
+        m = 16
+        n = 8
+        H = cyclic_hypergraph(m, k)
+        N_per_support = int((k - 1) * choose(m, k))
+        N = len(H) * N_per_support
+        num_trials = 5
+        Cs = np.zeros((num_trials, 2))  # 0:C1, 1:C2
[…]

### 2017-12-02 manuscripts/PNAS/second review/response/compute_C2.py
sml update

@@ -64,9 +64,9 @@ def cyclic_hypergraph(m, k):
 
 if __name__ == '__main__':
     # SQUARE GRID
-    num_trials = 50
+    num_trials = 200
     r = 2
-    Ks = [32]
+    Ks = [8]
     for k in Ks:
         m = k**2
         n = m // 2;
@@ -87,8 +87,8 @@ if __name__ == '__main__':
         pp.figure()
         pp.hist(C2s, bins=40)
         pp.show()
-        pp.title('Grid C2s (m=%d, n=%d, trials=%d)' % (m, n, num_trials))
-        pp.savefig('Grid_C2_m%d_n%d_r%d_ k%d_nt%d_r.pdf' % (m, n, r, k, num_trials))
+        pp.title('Grid C2s (m=%d, n=%d, k=%d, r=%d, trials=%d)' % (m, n, k, r, num_trials))
+        pp.savefig('C2_Grid_m%d_n%d_k%d_ r%d_nt%d_r.pdf' % (m, n, k, r, num_trials))
 
     # CYLIC
     Ks = [4] # , 16, 32]
@@ -123,4 +123,4 @@ if __name__ == '__main__':
         pp.hist(C2s, bins=40)
         pp.show()
         pp.title('Cyclic C2s (m=%d)' % m)
-        # plt.savefig('Cyclic_C2_m%d.pdf' % m)
+        plt.savefig('C2_Cyclic_m%d.pdf' % m)

### 2017-12-02 manuscripts/PNAS/second review/code/sample_complexity.py
chaz

@@ -1,5 +1,5 @@
-""" 
-Compute the probability that for every S in H, there are at least k vectors x_i supported there which share a support in B 
+"""
+Compute the probability that for every S in H, there are at least k vectors x_i supported there which share a support in B
 """
 # TODO: Try alternative formula for bounded pigeonhole
 
@@ -11,7 +11,7 @@ def pigeonhole_bounded_alt(num_balls, num_bins, max_balls_per_bin):
     pass
 
 def pigeonhole_bounded(num_balls, num_bins, max_balls_per_bin):
-    """ 
+    """
     Returns the number of ways to allocate num_balls to num_bins without exceeding max_balls_per_bin in any bin
 
     Source URL:
@@ -27,7 +27,7 @@ def pigeonhole_bounded(num_balls, num_bins, max_balls_per_bin):
     return val
 
 def pigeonhole(num_balls, num_bins):
-    """ 
+    """
     Returns the number of ways to allocate num_balls to num_bins.
     """
     return comb(num_balls + num_bins - 1, num_bins - 1)
@@ -40,51 +40,66 @@ def prob_atleast_k(num_balls, num_bins, k):
     tot = pigeonhole( num_balls, num_bins )
     return 1 - bnded / tot
 
-"""
-There are N_supp vectors supported on each S in H. These are the balls.
-There are mCk k-sparse supports wrt. the n x m matrix B. These are the bins.
-For what N_supp does the proof hold with a given probability?
+if __name__ == '__main__':
+    import matplotlib.pyplot as pp
+    pp.ion()
 
-We plot this as a function of m for fixed k.
-Assume H is the set of contiguous length-k intervals of [m] arranged in cyclic order, so that |H| = m.
-"""
-k = 3 # Fixed sparsity, i.e. H is k-uniform
-m_min = k+1 # since k < m required for H to satisfy SIP
-m_max = 20 # Max dictionary size
-prob = 0.999 # With what probability do we want the proof to work
-N_probabilistic = [] # Number of samples for proof to work with probability prob
-N_deterministic = [] # Number of samples for deterministic proof, i.e. with absolute certainty
-for m in range(m_min, m_max+1):
-    print(m)
-    prob_each_supp_req = np.exp(np.log(prob) / m) # with what probability do we need the pigeonholing for each S in H to succeed so that pigeonholing for all S in H succeeds with probability prob (recall |H| = m)?
[…]

### 2017-12-03 manuscripts/PNAS/second review/code/sample_complexity.py
yee

@@ -42,6 +42,11 @@ def prob_atleast_k(num_balls, num_bins, k):
 
 if __name__ == '__main__':
     import matplotlib.pyplot as pp
+    import os
+    try:
+        os.mkdir('./figures')
+    except:
+        pass
     pp.ion()
 
     """
@@ -60,10 +65,10 @@ if __name__ == '__main__':
     Ns = range(0, num_supps * samples_per_supp_deterministic, m) # N_supp per support in H, and there are m supports in H
     fig, ax = pp.subplots(1,1)
     ax.plot(Ns, probs)
-    ax.set_title('Probability that proof works vs. sample size (m=16, k=3)')
+    ax.set_title('Probability that proof works vs. sample size (m=16, k=%d)' % k)
     ax.set_xlabel('Sample size (up to deterministic sufficient number of samples)')
     ax.set_ylabel('Prob( proof works )')
-    pp.show()
+    pp.savefig('./figures/prob_vs_samples.png')
 
     """
     There are N_supp vectors supported on each S in H. These are the balls.
@@ -74,7 +79,6 @@ if __name__ == '__main__':
     Assume H is the set of contiguous length-k intervals of [m] arranged in cyclic order, so that |H| = m.
     """
     k = 3 # Fixed sparsity, i.e. H is k-uniform
-    num_supps = m # cyclic order hypergraph
     m_min = k+1 # since k < m required for H to satisfy SIP
     m_max = 20 # Max dictionary size
     prob = 0.999 # With what probability do we want the proof to work
@@ -82,6 +86,7 @@ if __name__ == '__main__':
     samples_deterministic = [] # Number of samples for deterministic proof, i.e. with absolute certainty
     for m in range(m_min, m_max+1):
         print(m)
+        num_supps = m # cyclic order hypergraph
         prob_each_supp_req = np.exp(np.log(prob) / m) # with what probability do we need the pigeonholing for each S in H to succeed so that pigeonholing for all S in H succeeds with probability prob (recall |H| = m)?
         samples_per_supp_min = k # need at least k
         samples_per_supp_deterministic = int((k-1) * comb(m,k) + 1) # with N_supp_max per support or more, probability is 1
@@ -91,7 +96,6 @@ if __name__ == '__main__':
             if prob_supp >= prob_each_supp_req:
[…]

### 2017-12-04 manuscripts/PNAS/second review/response/code/compute_C2.py
tidy up a bit

@@ -11,12 +11,13 @@ def friedrichs(U,V):
     Alternatively, it is the (s+1)th principal angle when dim(U \cap V) = s.
     """
     angles = subspace_angles(U,V)
-    nz_angles = angles > 0  # np.finfo(float).eps
-    if np.any(nz_angles):
-        min_nz_angle = np.sort(angles[nz_angles])[0]
-        return min_nz_angle
-    else:
-        return 0.
+    return np.sort(angles)[0]
+    # nz_angles = angles > 0  # np.finfo(float).eps
+    # if np.any(nz_angles):
+    #     min_nz_angle = np.sort(angles[nz_angles])[0]
+    #     return min_nz_angle
+    # else:
+    #     return 0.
 
 def xi(A, G):
     """
@@ -64,7 +65,7 @@ def cyclic_hypergraph(m, k):
 
 if __name__ == '__main__':
     # SQUARE GRID
-    num_trials = 200
+    num_trials = 100
     r = 2
     Ks = [8]
     for k in Ks:

### 2017-12-04 manuscripts/PNAS/second review/response/code/compute_C2.py
more sml

@@ -12,12 +12,6 @@ def friedrichs(U,V):
     """
     angles = subspace_angles(U,V)
     return np.sort(angles)[0]
-    # nz_angles = angles > 0  # np.finfo(float).eps
-    # if np.any(nz_angles):
-    #     min_nz_angle = np.sort(angles[nz_angles])[0]
-    #     return min_nz_angle
-    # else:
-    #     return 0.
 
 def xi(A, G):
     """
@@ -32,7 +26,7 @@ def xi(A, G):
         prod = 1.
         for i, Si in enumerate(Gseq[:-1]):
             cap_Sj = list(set.intersection(*map(set, Gseq[i+1:])))
-            if cap_Sj: # otherwise they intersect only at 0 and sin(theta) = 1, since every subspace forms pi/2 angle with 0 (weird)
+            if cap_Sj: # otherwise they intersect only at 0 and sin(theta) = 1, since every subspace forms pi/2 angle with 0
                 theta = friedrichs(A[:,Si], A[:,cap_Sj])
                 prod *=  np.sin(theta)**2
         prods.append(prod)
@@ -46,10 +40,10 @@ def C2(A, H, r):
     H: hypergraph (list of lists in range(m))
     r: regularity of H
 
-    Loops over subsets of H of size r
+    Loops over subsets of H of size r + 1
     """
     xi_Gs = [] # xi is in (0,1]
-    for G in itertools.combinations(H, r + 1): # loop over subsets of H of size r
+    for G in itertools.combinations(H, r + 1): # loop over subsets of H of size r + 1
         xi_Gs.append( xi(A, G) )
     max_A = np.max( np.linalg.norm(A, axis=0) )
     return len(H) * max_A / min(xi_Gs)
@@ -65,9 +59,9 @@ def cyclic_hypergraph(m, k):
 
 if __name__ == '__main__':
     # SQUARE GRID
-    num_trials = 100
+    num_trials = 20
     r = 2
-    Ks = [8]
+    Ks = [8, 10]
     for k in Ks:
         m = k**2
         n = m // 2;
@@ -89,10 +83,10 @@ if __name__ == '__main__':
         pp.hist(C2s, bins=40)
         pp.show()
         pp.title('Grid C2s (m=%d, n=%d, k=%d, r=%d, trials=%d)' % (m, n, k, r, num_trials))
[…]

### 2018-12-23 manuscripts/IEEE/chazthm_ieee_trans_sig.tex
start trans sig proc

--- 2017-12-02 manuscripts/PNAS/second review/resub/chazthm_pnas_resub.tex
@@
-\documentclass[9pt,twocolumn]{pnas-new}
-% Use the lineno option to display guide line numbers if required.
-% Note that the use of elements such as single-column equations may affect the guide line number alignment.
+% Notes:
+%
+% Can we prove in a line or two that the inverse problem is stable by arguing that the function is bijective and closed therefore a homeomorphism?
+% Should we mention the notion of Grassmannian manifolds and that Theta is a metric on this space?
+% Change robustness to stability?
+%
+\documentclass[journal, twocolumn]{IEEEtran}
 
-% TODO %
-% Mention all matrices are real
-% Do we mention that the Appendix contains proof of Lem. 1?
-% *** Put ell1 norm into the denominator of L_k *** ?
-% Give example of when we might expect k-uniformity, i.e. x_i in glp on k-dimensional subspaces. Orbit under group action of a k-dimensional subspace?
-% If not thousands...?
-
-%%% Subspace Arrangement..Semi-lattices..? %%%
-% Describe the connection between dictionary learning and union of subspace learning.
-Dictionaries are the top elements of the subspace intersection semi-lattice over reverse-inclusion.
-We identify subspaces generated by the elements of $A$ by showing that every $B$ must include these subspaces in its intersection semi-lattice.
-The dictionary elements are then inside these subspaces, so the lower the dimensionality of these subspaces the better.
-% Shoutout to research on subspace arrangements? Not just "union of subspaces" model?
-% Write Main Lemma or Lil lemma as a map between two intersection semi-lattices with a constraint (on the dimension of subspace? or on size of edge?)?
-%See pg. 257 of GPCA textbook that alludes to the connection between DL and deep learning -- could se way we take a step toward identifiability theory in deep learning? lol
-
-% IMPORTED PACKAGES
+% *** MATH PACKAGES ***
 \usepackage{amsmath, amssymb, amsthm} 
@@
 
-\renewcommand{\eqref}[1]{\textnormal{[\ref{#1}]}}
-
-%\usepackage[pdftex]{graphicx}
+\usepackage[pdftex]{graphicx}
 
@@
 \usepackage{array}
+\usepackage{cite}
 \usepackage{bm}
-%\usepackage{cite}
 
-\templatetype{pnasresearcharticle} % Choose template 
-% {pnasresearcharticle} = Template for a two-column research article
-% {pnasmathematics} = Template for a one-column mathematics article
-% {pnasinvited} = Template for a PNAS invited submission
+% correct bad hyphenation here
+%\hyphenation{op-tical net-works semi-conduc-tor}
 
-\title{On the uniqueness and stability of dictionaries for sparse representation of noisy signals}
+\begin{document}
 
-% Use letters for affiliations, numbers to show equal authorship (if applicable) and to indicate the corresponding author
-\author[a,b,1]{Charles J. Garfinkle}
-\author[a,1]{Christopher J. Hillar}
+%\title{When can a generating dictionary and sparse codes be recovered from noisy data?}
+%\title{When is the dictionary learning problem well-posed?}
+\title{When is sparse dictionary learning well-posed?}
+%\title{When is the dictionary learning problem for sparse coding well-posed?}
+%\title{When is the sparsest representation unique?}
+%\title{When are sparse codes identifiable from their unknown noisy compressive measurements?}
+% FRITZ2: The title doesn't reflect the amount of new stuff, it seems incremental from the last one. It's not very meaningful.
+% FRITZ: Not everyone knows what well-posed means. You should mention recovery from noisy data in the title.
 
-\affil[a]{Redwood Center for Theoretical Neuroscience, Berkeley, CA, USA}
-\affil[b]{Helen Wills Neuroscience Institute, UC Berkeley}
-
-% Please give the surname of the lead author for the running footer
-\leadauthor{Garfinkle}
-
-\significancestatement{Many natural signals (visual scenery, speech, EEG, etc.) lacking domain-specific formal models can nonetheless be usefully characterized as linear combinations of few elementary waveforms drawn from a large ``dictionary''.
-We give general conditions guaranteeing when such dictionaries are uniquely and stably determined by data.
-The result justifies the use of this model as a constraint for blind source separation and helps explain the observed universality of emergent representations in sparse models of certain natural phenomena.
+\author{Charles~J.~Garfinkle and Christopher~J.~Hillar \\
+Redwood Center for Theoretical Neuroscience, Berkeley, CA, USA
+%\thanks{%e-mails: cjg@berkeley.edu, chillar@msri.org.  
+%CG and CH supported, in part, by NSF grant IIS-1219212 and the Statistical and Applied Mathematical Sciences Institute, under NSF DMS-1127914.}
 }
 
-\authordeclaration{The authors declare no conflict of interest.}
-\correspondingauthor{\textsuperscript{1}To whom correspondence should be addressed. E-mail: chaz@berkeley.edu, chillar@msri.org}
+\maketitle
 
-\keywords{Sparse coding, dictionary learning, matrix factorization, compressed sensing, inverse problems, blind source separation}
+% \keywords{Sparse coding, dictionary learning, matrix factorization, compressed sensing, inverse problems, blind source separation}
 
@@
 
-% \dates{This manuscript was compiled on \today}
-\doi{\url{www.pnas.org/cgi/doi/10.1073/pnas.XXXXXXXXXX}}
-
-\begin{document}
-
 % Optional adjustment to line up main text (after abstract) of first page with line numbers, when using both lineno and twocolumn options.
 % You should only change this length when you've finalised the article contents.
-\verticaladjustment{-2pt}
 
-\maketitle
-\thispagestyle{firststyle}
-\ifthenelse{\boolean{shortarticle}}{\ifthenelse{\boolean{singlecolumn}}{\abscontentformatted}{\abscontent}}{}
+\section{Introduction}\label{Intro}
 
-% If your first paragraph (i.e.
-with the \dropcap) contains a list environment (quote, quotation, theorem, definition, enumerate, itemize...), the line after the list may have some extra indentation.
-If this is the case, add \parshape=0 to the end of the list environment.
-\dropcap{B}lind source separation is a classical problem in signal processing \cite{sato1975method}.
+\IEEEPARstart{B}{lind} source separation is a classical problem in signal processing \cite{sato1975method}.
 In one common modern formulation, each of $N$ observed $n$-dimensional signals is a (noisy) linear combination of at most $k$ elementary waveforms drawn from some unknown dictionary of size $m$, typically with $m \ll N$ (see \cite{Zhang15} for a comprehensive review of this and related models).
@@
 
-\vspace{-.5 cm}
-
 \section{Discussion}\label{Discussion}
@@
 
-\acknow{We thank Friedrich Sommer and Darren Rhea for early thoughts, and Ian Morris for posting \eqref{eqdim} online.}
-\showacknow % Display the acknowledgments section
+%\acknow{We thank Friedrich Sommer and Darren Rhea for early thoughts, and Ian Morris for posting \eqref{eqdim} online.}
+%\showacknow % Display the acknowledgments section
 
-\bibliography{chazthm_pnas}
+\bibliographystyle{IEEEtran}
+\bibliography{chazthm_ieee_trans_sig}
 
@@
 \end{lemma}
-\vspace{-.3 cm}
 \begin{proof} 
@@
 \leq d\left( \bm{\mathcal{A}}_i, \bm{\mathcal{B}}_{\overline \pi(i)} \right)
-\leq \overline \varepsilon
+\leq \overline \varepsilon,
 %&= \max_{\bm{u} \in \bm{\mathcal{A}}_i, \|\bm{u}\|_2 \leq 1} \text{dist}\left(\bm{u}, \bm{\mathcal{B}}_{\overline \pi(i)} \right) \\

### 2018-12-23 manuscripts/IEEE/chazthm_ieee_trans_sig.tex
cjh last edits

@@
 \begin{problem}[Sparse linear coding]\label{InverseProblem}
-Find a matrix $\mathbf{B}$ and $k$-sparse $\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N \in \mathbb{R}^{\overline m}$ so that $\|\mathbf{z}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \eta$ for all $i$.
+Find a matrix $\mathbf{B}$ and $k$-sparse $\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N \in \mathbb{R}^{\overline m}$ with $\|\mathbf{z}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \eta$ for all $i$.
 \end{problem}
 
-Note that any particular solution $(\mathbf{B}, \mathbf{\overline x}_1 \ldots, \mathbf{\overline x}_N)$ to this problem gives rise to an orbit of equivalent solutions $(\mathbf{BPD}, \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_1, \ldots, \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_N)$, where $\mathbf{P}$ is any permutation matrix and $\mathbf{D}$ any invertible diagonal.
+Note that any particular solution $(\mathbf{B}; \mathbf{\overline x}_1 \ldots, \mathbf{\overline x}_N)$ to this problem gives rise to an orbit of equivalent solutions $(\mathbf{BPD}; \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_1, \ldots, \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_N)$, where $\mathbf{P}$ is any permutation matrix and $\mathbf{D}$ any invertible diagonal.
 Previous theoretical work addressing the noiseless case $\eta =0$ (e.g., \cite{li2004analysis, Georgiev05, Aharon06, Hillar15}) with $\overline m = m$ has shown that a solution to Prob.~\ref{InverseProblem} (when it exists) is unique up to this  ambiguity provided the $\mathbf{x}_i$ are sufficiently diverse and the matrix $\mathbf{A}$ satisfies the \textit{spark condition}:
@@
 %
-demonstrating that the number vectors $\mathbf{\overline x}_i$ that are \emph{not} $k$-sparse is controlled by how many are $(k-1)$-sparse.
+demonstrating that the number of vectors $\mathbf{\overline x}_i$ that are \emph{not} $k$-sparse is controlled by how many are $(k-1)$-sparse.
 
@@
 The goal of this work was to explain the emergence of characteristic representations from sparse linear coding models fit to natural data, despite the varied assumptions underlying the many algorithms in current use.
-To this end, we have taken an important step toward unifying the hundreds (if not thousands) of publications on the topic by demonstrating very general, deterministic conditions under which the identification of parameters in this parsimonious model is not only possible but also robust to the inevitable uncertainty permeating measurement and model choice.
+To this end, we have taken an important step toward unifying the great number of publications on the topic by demonstrating very general, deterministic conditions under which identification of parameters in this parsimonious model is not only possible but also robust to the inevitable uncertainty permeating measurement and model choice.
 
@@
 
-An immediate application of our theoretical work is Prop.~\ref{neuroprop}, which certifies the validity of perhaps the only published theory of neurally-plausible bottleneck communication in the brain: that sparse linear coding in a compressed space of neural activity can recover sparse codes sent through a randomly-constructed (but unknown) noisy wiring bottleneck \cite{Isely10}.\footnote{We refer the reader to \cite{ganguli2012compressed} for more on interactions between dictionary learning and neuroscience.}
+An immediate application of our theoretical work is Prop.~\ref{neuroprop}, which certifies the validity of a theory of neurally-plausible bottleneck communication in the brain: that sparse linear coding in a compressed space of neural activity can recover sparse codes sent through a randomly-constructed (but unknown) noisy wiring bottleneck \cite{Isely10}.\footnote{We refer the reader to \cite{ganguli2012compressed} for more on interactions between dictionary learning and neuroscience.}
 
@@
 For example, several groups have applied compressed sensing to signal processing tasks: MRI analysis \cite{lustig2008compressed}, image compression \cite{Duarte08}, and, more recently, the design of an ultrafast camera \cite{Gao14}.
-Given such effective uses of compressed sensing, it is only a matter of time before these systems incorporate dictionary learning to encode and decode signals (e.g., in a device that learns structure from motion \cite{kong2016prior}) just as scientists have used it to make sense of their data \cite{jung2001imaging, Agarwal14, lee2016sparse, wu2016stability}.
+Given such effective uses of compressed sensing, it is only a matter of time before these systems incorporate dictionary learning to encode and decode signals (e.g., in a device that learns structure from motion \cite{kong2016prior}), just as scientists have used it to make sense of their data \cite{jung2001imaging, Agarwal14, lee2016sparse, wu2016stability}.
 Assurances such as those offered by our theorems certify that different devices (with different initialization, etc.) will learn equivalent representations given enough data from statistically identical systems.\footnote{To contrast with the current hot topic of ``Deep Learning'', there are few such uniqueness guarantees for these models of data; moreover, even small noise can dramatically alter their output \cite{goodfellow2014explaining}.} Indeed, it seems a main reason for the sustained interest in dictionary learning as an unsupervised method for data analysis is the assumed well-posedness of parameter identification in the sparse linear coding model, confirmation of which forms the core of our theoretical findings.
+
+\textbf{Acknowledgement.} We thank F. Sommer and D. Rhea for early thoughts, and I. Morris for posting \eqref{eqdim} online.
 
@@
 
-%\acknow{We thank Friedrich Sommer and Darren Rhea for early thoughts, and Ian Morris for posting \eqref{eqdim} online.}
 %\showacknow % Display the acknowledgments section

### 2018-12-24 manuscripts/IEEE/chazthm_ieee_trans_sig_CHAZ.tex
new intro

--- 2018-12-23 manuscripts/IEEE/chazthm_ieee_trans_sig.tex
@@
 %\title{When is the dictionary learning problem well-posed?}
-\title{When is sparse dictionary learning well-posed?}
+\title{On the uniqueness and stability of dictionaries for sparse representation of noisy signals}
 %\title{When is the dictionary learning problem for sparse coding well-posed?}
@@
 \begin{abstract}
-Dictionary learning for sparse linear coding has exposed characteristic properties of natural signals.
-However, a universal theorem guaranteeing the consistency of estimation in this model is lacking.
-Here, we prove that for all diverse enough datasets generated from the sparse coding model, latent dictionaries and codes are uniquely and stably determined up to measurement error.
+Learning optimal dictionaries for sparse coding has exposed characteristic sparse features of many natural signals.
+However, universal conditions guaranteeing the consistency of these learned features in the presence of measurement noise have yet to be stated.
+Here, we prove very generally that optimal dictionaries and sparse codes are uniquely and stably determined up to measurement error for all diverse enough datasets generated in accordance with the constraints assumed by sparse coding.
 Applications are given to data analysis, engineering, and neuroscience.
@@
 
-\IEEEPARstart{B}{lind} source separation is a classical problem in signal processing \cite{sato1975method}.
-In one common modern formulation, each of $N$ observed $n$-dimensional signals is a (noisy) linear combination of at most $k$ elementary waveforms drawn from some unknown dictionary of size $m$, typically with $m \ll N$ (see \cite{Zhang15} for a comprehensive review of this and related models).
-Approximating solutions to this sparsity-constrained inverse problem have provided insight into the structure of many signal classes lacking domain-specific formal models (e.g., in vision \cite{wang2015sparse}).
-In particular, it has been shown that response properties of simple-cell neurons in mammalian visual cortex emerge from optimizing a dictionary to represent small patches of natural images \cite{Olshausen96, hurri1996image, bell1997independent, van1998independent}, a major advance in computational neuroscience.
-A curious aspect of this finding is that the latent waveforms (e.g., ``Gabor'' wavelets) estimated from data appear to be canonical \cite{donoho2001can};
-i.e., they are found in learned dictionaries independent of algorithm or image training set.
+% \cite{sato1975method}
+\IEEEPARstart{A}{}common assumption underlying contemporary applications of signal processing and pattern analysis is that each of $N$ observed $n$-dimensional signal samples is a (noisy) linear combination of at most $k$ elementary waveforms drawn from some unknown \emph{dictionary} of size $m$, typically with $m \ll N$ (see \cite{Zhang15} for a comprehensive review of this and related models).
+Attempts to approximate solutions to this sparsity-constrained inverse problem have provided insight into the structure of many signal classes lacking idiosyncratic formal models (e.g., in vision \cite{wang2015sparse}).
+In fact, a seminal work in the field demonstrated that dictionaries optimized to sparsely represent small patches of natural images share many qualitative similarities to filters fit to the response properties of simple-cell neurons in mammalian visual cortex \cite{Olshausen96, hurri1996image, bell1997independent, van1998independent}, a major result in theoretical neuroscience.
+Moreover, these latent waveforms (e.g., ``Gabor'' wavelets) estimated from data appear to be canonical \cite{donoho2001can}; i.e.
+they emerge in dictionaries learned by a variety of algorithms trained with respect to different natural image datasets.
 
-Motivated by these discoveries and earlier work in the theory of neural communication \cite{Isely10}, we address when dictionaries and the sparse representations they induce are uniquely determined by data.
-Answers to this question also have other real-world implications.
-For example, a sparse coding analysis of local painting style can be used for forgery detection \cite{hughes2010}, but only if all dictionaries consistent with training data do not differ appreciably in their ability to sparsely encode new samples.
-Fortunately, algorithms with proven recovery of generating dictionaries under certain 
-conditions have recently been proposed (see \cite[Sec.~I-E]{Sun16} for a summary of the state-of-the-art).
-Few theorems, however, can be cited to explain this uniqueness more broadly; in particular, a universal guarantee in the context of noise has yet to emerge.
+Motivated by these discoveries and earlier work proposing a related theory of communication between sparsely active neural populations \cite{Isely10}, we address when dictionaries and the sparse representations they induce are uniquely determined by data.
+Answers to this question have real-world implications.
+For example, it has been demonstrated that a sparse coding analysis of painting style can detect forgeries \cite{hughes2010}; but this implies all dictionaries consistent with training data generalize in their ability to sparsely encode new samples.
+Fortunately, several algorithms have recently been proposed which provably recover latent dictionaries under idiosyncratic conditions (see \cite[Sec.~I-E]{Sun16} for a summary of the state-of-the-art).
+Few theorems, however, can be cited to explain the consistency of inference with respect to this model more broadly; in particular, a universal guarantee of uniqueness and stability in the context of noise has yet to emerge.
 
-Here, we prove very generally that uniqueness and stability is an expected property of the sparse linear coding model. 
-More specifically, dictionaries that preserve sparse codes (e.g., satisfy a ``spark condition'') are identifiable from as few as \mbox{$N = m(k-1){m \choose k} + m$} noisy sparse linear combinations of their columns up to an error that is linear in the noise (Thm.~\ref{DeterministicUniquenessTheorem}).
-In fact, provided $n \geq \min(2k,m)$, in almost all cases the dictionary learning problem is well-posed (as per Hadamard \cite{Hadamard1902}) given enough data (Cor.~\ref{ProbabilisticCor}).
-Moreover, these explicit, algorithm-independent guarantees hold without assuming the recovered matrix satisfies a spark condition, and even when the number $m$ of dictionary elements is unknown.
+Here, we prove very generally that uniqueness and stability of solutions is an expected property of both the sparse coding problem described above as well as a related (and perhaps more well-known) optimization formulation, which instead asks for a dictionary and sparse codes that minimize the mean sparsity over samples.
 
-More formally, let $\mathbf{A} \in \mathbb R^{n \times m}$ be a matrix with columns $\mathbf{A}_j$ ($j = 1,\ldots,m$) and let dataset $Z$ consist of measurements:
+Formally, let $\mathbf{A} \in \mathbb R^{n \times m}$ be a matrix with columns $\mathbf{A}_j$ ($j = 1,\ldots,m$) and let dataset $Z$ consist of measurements:
 \begin{align}\label{LinearModel}
@@
 for $k$-\emph{sparse} $\mathbf{x}_i \in \mathbb{R}^m$ having at most $k<m$ nonzero entries and \emph{noise} $\mathbf{n}_i \in \mathbb{R}^n$, with bounded norm $\| \mathbf{n}_i \|_2 \leq  \eta$ representing our combined worst-case uncertainty in  measuring $\mathbf{A}\mathbf{x}_i$.
-The first mathematical problem we address is the following.
+We show that dictionaries $\mathbf{A}$ injective on certain subsets of $k$-sparse codes are identifiable from as few as \mbox{$N = m(k-1){m \choose k} + m$} noisy sparse linear combinations of their columns up to an error that is linear in the noise (Thm.~\ref{DeterministicUniquenessTheorem}).
+Specifically, the first mathematical problem we consider is:
 
-\begin{problem}[Sparse linear coding]\label{InverseProblem}
-Find a matrix $\mathbf{B}$ and $k$-sparse $\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N \in \mathbb{R}^{\overline m}$ with $\|\mathbf{z}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \eta$ for all $i$.
+\begin{problem}\label{InverseProblem}
+Find a matrix $\mathbf{B}$ and $k$-sparse $\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N \in \mathbb{R}^{\overline m}$ satisfying $\|\mathbf{z}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \eta$ for all $i$.
 \end{problem}
 
-Note that any particular solution $(\mathbf{B}; \mathbf{\overline x}_1 \ldots, \mathbf{\overline x}_N)$ to this problem gives rise to an orbit of equivalent solutions $(\mathbf{BPD}; \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_1, \ldots, \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_N)$, where $\mathbf{P}$ is any permutation matrix and $\mathbf{D}$ any invertible diagonal.
-Previous theoretical work addressing the noiseless case $\eta =0$ (e.g., \cite{li2004analysis, Georgiev05, Aharon06, Hillar15}) with $\overline m = m$ has shown that a solution to Prob.~\ref{InverseProblem} (when it exists) is unique up to this  ambiguity provided the $\mathbf{x}_i$ are sufficiently diverse and the matrix $\mathbf{A}$ satisfies the \textit{spark condition}:
+Our claim is that there exist very general conditions under which any matrix $\mathbf{B}$ that solves this problem is always ``close" to $\mathbf{A}$, and likewise for the sparse codes $\mathbf{\overline x}_i$ and $\mathbf{x}_i$.
+In fact, provided $n \geq \min(2k,m)$, in almost all cases \ref{InverseProblem} is well-posed (as per Hadamard \cite{Hadamard1902}) given enough data (Cor.~\ref{ProbabilisticCor}).
+In particular, these explicit, universal guarantees hold without imposing \emph{any} constraints on the recovered matrix $\mathbf{B}$ (e.g.
+that it, too, satisfy any injectivity criteria), even the number $m$ of dictionary elements it should contain.
+
+Note that any particular solution to Problem \ref{InverseProblem} represents an infinity of equivalent solutions $\mathbf{BPD}$ and $\mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_1, \ldots, \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_N$ parametrized by a choice of permutation matrix $\mathbf{P}$ and invertible diagonal matrix $\mathbf{D}$ capturing the sparsity-preserving labeling and scaling ambiguities inherent to the problem statement.
+Previous theoretical work addressing the noiseless case $\eta =0$ (e.g., \cite{li2004analysis, Georgiev05, Aharon06, Hillar15}) with fixed $\overline m = m$ has shown that the solution to Prob.~\ref{InverseProblem}, when it exists, is unique up to these  ambiguities provided the $\mathbf{x}_i$ are sufficiently diverse and the matrix $\mathbf{A}$ satisfies:
 \begin{align}\label{SparkCondition}
@@
 %
-which would be, in any case, necessary for uniqueness of the $\mathbf{x}_i$. Here, we study stability in the practical setting of noise.
+also called the \textit{spark condition}, which in any case is necessary to guarantee the uniqueness of arbitrary sequences of $k$-sparse $\mathbf{x}_i$.
+We generalize these results to the practical setting of additive noise by incorporating the notion of stability with respect to noise.
 
@@
 To see how Def.
-\ref{maindef} directly relates to Prob.
+\ref{maindef} is motivated by Prob.
 \ref{InverseProblem}, suppose that $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$ and fix $\delta_1, \delta_2$ to be the desired recovery accuracy in \eqref{def1}.
-Consider any dataset $Z$ generated as in \eqref{LinearModel} with $\eta \leq \frac{1}{2} \varepsilon(\delta_1, \delta_2)$.
-Then from the triangle inequality, it follows that any matrix $\mathbf{B}$ and $k$-sparse $\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N \in \mathbb{R}^m$ solving Prob.~\ref{InverseProblem} are necessarily within $\delta_1, \delta_2$ of the original dictionary $\mathbf{A}$ and codes $\mathbf{x}_i$, respectively.
+Now, consider any dataset $Z$ generated as in \eqref{LinearModel} with $\eta \leq \frac{1}{2} \varepsilon(\delta_1, \delta_2)$.
+From the triangle inequality, it follows that any matrix $\mathbf{B}$ and $k$-sparse $\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N \in \mathbb{R}^m$ solving Prob.~\ref{InverseProblem} are necessarily within $\delta_1, \delta_2$ of the original dictionary $\mathbf{A}$ and codes $\mathbf{x}_i$, respectively.
 
@@
 We then prove our main theorem (Thm.~\ref{DeterministicUniquenessTheorem}) in Sec.~\ref{DUT} after stating some additional definitions and lemmas required for the proof, including a useful result in combinatorial matrix analysis (Lem.~\ref{MainLemma}, proven in Appendix).
-We also provide an argument that extends our guarantees to the following more common optimization formulation of the dictionary learning problem (Thm.~\ref{SLCopt}).
+We also provide a short argument extending our guarantees to the following more common formulation of the dictionary learning problem as an optimization over model parameters minimizing the total (or equivalently, the mean) number of non-zero entries in the sparse codes (Thm.~\ref{SLCopt}):
 
@@
 %To be clear, the implication of Thm.~\ref{DeterministicUniquenessTheorem} is that $Y = \{\mathbf{Ax}_1, \ldots, \mathbf{Ax}_N\}$ has a stable $k$-sparse representation in $\mathbb{R}^m$, with \eqref{def1} guaranteed provided $\varepsilon$ in Def.~\ref{maindef} does not exceed:
-In words, Thm.~\ref{DeterministicUniquenessTheorem} says that the smaller the difference $\overline m - m$ between recovery and original latent dictionary sizes, the more columns and coefficients of the original dictionary $\mathbf{A}$ and codes $\mathbf{x}_i$ are contained (up to noise) in the appropriately scaled dictionary $\mathbf{B}$ and codes $\mathbf{\overline x}_i$.
+In words, Thm.~\ref{DeterministicUniquenessTheorem} says that the smaller the difference $\overline m - m$ between assumed and actual latent dictionary sizes, the more columns and coefficients of the original dictionary $\mathbf{A}$ and codes $\mathbf{x}_i$ are contained (up to noise) in the appropriately scaled dictionary $\mathbf{B}$ and codes $\mathbf{\overline x}_i$.
 In the particular case when $\overline m = m$, the theorem directly implies that  $Y = \{\mathbf{Ax}_1, \ldots, \mathbf{Ax}_N\}$ has a stable $k$-sparse representation in $\mathbb{R}^m$, with inequalities \eqref{def1} guaranteed for $\varepsilon$ in Def.~\ref{maindef} given by:
@@
 Note that sparse codes $\mathbf{x}_i$ with a shared support that are in general linear position are straightforward to produce using a ``Vandermonde'' matrix construction (i.e., use the columns of the matrix $[\gamma_{i}^j]_{i,j=1}^{k,N}$, for distinct nonzero $\gamma_i$).
-Thus, the assumptions of Thm.~\ref{DeterministicUniquenessTheorem} are easily met, leading to the following direct application to uniqueness in sparse linear coding.
+Thus, the assumptions of Thm.~\ref{DeterministicUniquenessTheorem} are easily met, leading to the following direct application to uniqueness in sparse coding.
 % (Prob.~\ref{InverseProblem}).
@@
 There are other less direct consequences of Thm.~\ref{DeterministicUniquenessTheorem}.
-For instance, we use it to prove uniqueness for the optimization formulation of sparse linear coding, Prob.~\ref{SLCopt}, the main object of interest for those applying dictionary learning to their data.
+For instance, we apply it to prove uniqueness and stability of solutions to Prob.~\ref{SLCopt}, the usual optimization problem of interest for those applying dictionary learning to their data.
 
@@
 \begin{proposition}\label{neuroprop}
-Sparse neural population activity is recoverable from noisy random linear compression by any method that solves Prob.~\ref{DeterministicUniquenessTheorem} or \ref{SLCopt}; in particular, via biophysically plausible unsupervised sparse linear coding (e.g., \cite{rehnsommer2007, rozell2007neurally, pehlevan2015normative}).
+Sparse neural population activity is recoverable from noisy random linear compression by any method that solves Prob.~\ref{DeterministicUniquenessTheorem} or \ref{SLCopt}; in particular, via biophysically plausible unsupervised sparse coding (e.g., \cite{rehnsommer2007, rozell2007neurally, pehlevan2015normative}).
 \end{proposition}
@@
 We close this section with comments on optimality.
-Our linear scaling for $\varepsilon$ in \eqref{epsdel} is essentially optimal (e.g., see \cite{arias2013fundamental}), but a basic open problem remains: how many samples are necessary to determine the sparse linear coding model?
+Our linear scaling for $\varepsilon$ in \eqref{epsdel} is essentially optimal (e.g., see \cite{arias2013fundamental}), but a basic open problem remains: how many samples are necessary to determine the sparse coding model?
 If $k$ is held fixed or if the size of the support set of reconstructing codes is known to be polynomial in $\overline m$ and $k$, then a practical (polynomial) amount of data suffices.\footnote{In the latter case, a reexamination of the pigeonholing argument in the proof of Thm.~\ref{DeterministicUniquenessTheorem} requires a polynomial number of samples distributed over a polynomial number of supports.} Reasons to be skeptical that this holds in general, however, can be found in \cite{tillmann2014computational, Tillmann15}.
@@
 
-The goal of this work was to explain the emergence of characteristic representations from sparse linear coding models fit to natural data, despite the varied assumptions underlying the many algorithms in current use.
+The goal of this work was to explain the emergence of characteristic representations from sparse coding models fit to natural data, despite the varied assumptions underlying the many algorithms in current use.
 To this end, we have taken an important step toward unifying the great number of publications on the topic by demonstrating very general, deterministic conditions under which identification of parameters in this parsimonious model is not only possible but also robust to the inevitable uncertainty permeating measurement and model choice.
@@
 
-An immediate application of our theoretical work is Prop.~\ref{neuroprop}, which certifies the validity of a theory of neurally-plausible bottleneck communication in the brain: that sparse linear coding in a compressed space of neural activity can recover sparse codes sent through a randomly-constructed (but unknown) noisy wiring bottleneck \cite{Isely10}.\footnote{We refer the reader to \cite{ganguli2012compressed} for more on interactions between dictionary learning and neuroscience.}
+An immediate application of our theoretical work is Prop.~\ref{neuroprop}, which certifies the validity of a theory of neurally-plausible bottleneck communication in the brain: that sparse coding in a compressed space of neural activity can recover sparse codes sent through a randomly-constructed (but unknown) noisy wiring bottleneck \cite{Isely10}.\footnote{We refer the reader to \cite{ganguli2012compressed} for more on interactions between dictionary learning and neuroscience.}
 
@@
 Given such effective uses of compressed sensing, it is only a matter of time before these systems incorporate dictionary learning to encode and decode signals (e.g., in a device that learns structure from motion \cite{kong2016prior}), just as scientists have used it to make sense of their data \cite{jung2001imaging, Agarwal14, lee2016sparse, wu2016stability}.
-Assurances such as those offered by our theorems certify that different devices (with different initialization, etc.) will learn equivalent representations given enough data from statistically identical systems.\footnote{To contrast with the current hot topic of ``Deep Learning'', there are few such uniqueness guarantees for these models of data; moreover, even small noise can dramatically alter their output \cite{goodfellow2014explaining}.} Indeed, it seems a main reason for the sustained interest in dictionary learning as an unsupervised method for data analysis is the assumed well-posedness of parameter identification in the sparse linear coding model, confirmation of which forms the core of our theoretical findings.
+Assurances such as those offered by our theorems certify that different devices (with different initialization, etc.) will learn equivalent representations given enough data from statistically identical systems.\footnote{To contrast with the current hot topic of ``Deep Learning'', there are few such uniqueness guarantees for these models of data; moreover, even small noise can dramatically alter their output \cite{goodfellow2014explaining}.} Indeed, it seems a main reason for the sustained interest in dictionary learning as an unsupervised method for data analysis is the assumed well-posedness of parameter identification in the sparse coding model, confirmation of which forms the core of our theoretical findings.
 
@@
 
-%Since its inception some twenty years ago, sparse linear coding has become a standard tool in signal analysis, yielding myriad insights into the structure of natural signals across a variety of scientific domains.
+%Since its inception some twenty years ago, sparse coding has become a standard tool in signal analysis, yielding myriad insights into the structure of natural signals across a variety of scientific domains.
 In this work,

### 2018-12-24 manuscripts/IEEE/chazthm_ieee_trans_sig_CHAZ.tex
new intro

@@
 \end{problem}
-We then sketch proofs of probabilistic extensions of Thm.~\ref{DeterministicUniquenessTheorem} to random data and dictionaries (Thm.~\ref{robustPolythm} and Cor.~\ref{ProbabilisticCor}).
+We then sketch proofs of probabilistic extensions of Thm.~\ref{DeterministicUniquenessTheorem} to  data and dictionaries drawn from probability distributions (Thm.~\ref{robustPolythm} and Cor.~\ref{ProbabilisticCor}).
 Finally, in Sec.~\ref{Discussion}, we discuss both theoretical and practical applications of our main mathematical findings.
@@
 A set of $k$-sparse vectors is said to be in \emph{general linear position} when any $k$ of them are linearly independent.
-The following is a precise statement of our main result.
-We leave the quantity $C_1 = C_1(\mathbf{A}, \{\mathbf{x}_i\}_{i=1}^N, \mathcal{H})$ undefined until Eq.~\eqref{Cdef1}.
+The following is a precise statement of our main result, though we will leave the quantity $C_1 = C_1(\mathbf{A}, \{\mathbf{x}_i\}_{i=1}^N, \mathcal{H})$ undefined until Eq.~\eqref{Cdef1}.
 All of our theorems assume matrices consist of real numbers.
@@
 As an example for $k=2$, let $\mathbf{A} = [ \mathbf{e}_1, \ldots, \mathbf{e}_5, \mathbf{v}]$ where $\mathbf{v} = \mathbf{e}_1 + \mathbf{e}_3 + \mathbf{e}_5$, and take $\mathcal{H}$ to be all consecutive pairs of $[m]$ arranged in cyclic order.
-Then, dictionary $\mathbf{A}$ satisfies the assumptions of Thm.~\ref{DeterministicUniquenessTheorem} underlying \eqref{Cstable} without satisfying \eqref{SparkCondition}.
+Then, dictionary $\mathbf{A}$ satisfies the assumptions of Thm.~\ref{DeterministicUniquenessTheorem} guaranteeing \eqref{Cstable} without satisfying \eqref{SparkCondition}.
 %(since $\{ \mathbf{A}_1, \mathbf{A}_3, \mathbf{A}_5, \mathbf{A}_6\}$ is not a linearly independent set).
@@
 
-We remark that these results have an important application to theoretical neuroscience by mathematically justifying one of the few hypothesized theories of bottleneck communication between sparsely active neural populations \cite{Isely10}.
+We remark that these results have a potential application to theoretical neuroscience by mathematically justifying one of the few hypothesized theories of bottleneck communication between sparsely active neural populations \cite{Isely10}.
 
@@
 
-The goal of this work was to explain the emergence of characteristic representations from sparse coding models fit to natural data, despite the varied assumptions underlying the many algorithms in current use.
-To this end, we have taken an important step toward unifying the great number of publications on the topic by demonstrating very general, deterministic conditions under which identification of parameters in this parsimonious model is not only possible but also robust to the inevitable uncertainty permeating measurement and model choice.
+A goal of this work was to explain the emergence of characteristic representations from sparse coding models fit to natural data, despite the varied assumptions underlying the many algorithms in current use.
+To this end, we have taken an important step toward unifying the great number of publications on the topic by demonstrating very general, deterministic conditions under which identification of parameters in this model is not only possible but also robust to the inevitable uncertainty permeating measurement and model choice.
 
-Specifically, we have shown that, given sufficient data, the problem of seeking a dictionary and sparse codes with minimal average support size (Prob.~\ref{OptimizationProblem}) reduces to an instance of Prob.~\ref{InverseProblem}, to which our main result (Thm.~\ref{DeterministicUniquenessTheorem}) applies: every dictionary and sparse codes consistent with the data are equivalent up to inherent relabeling/scaling ambiguities and a discrepancy (error) that scales linearly with the measurement noise or modeling inaccuracy.
+We have shown that, given sufficient data, the problem of seeking a dictionary and sparse codes with minimal average support size (Prob.~\ref{OptimizationProblem}) reduces to an instance of Prob.~\ref{InverseProblem}, to which our main result (Thm.~\ref{DeterministicUniquenessTheorem}) applies: every dictionary and sequence of sparse codes consistent with the data are equivalent up to inherent relabeling/scaling ambiguities and a discrepancy (error) that scales linearly with the measurement noise or modeling inaccuracy.
 The constants we provide are explicit and computable; as such, there is an effective procedure that sufficiently affirms if a proposed solution to Probs.~\ref{DeterministicUniquenessTheorem} or \ref{OptimizationProblem} is indeed unique up to noise and inherent ambiguities.
 
-An immediate application of our theoretical work is Prop.~\ref{neuroprop}, which certifies the validity of a theory of neurally-plausible bottleneck communication in the brain: that sparse coding in a compressed space of neural activity can recover sparse codes sent through a randomly-constructed (but unknown) noisy wiring bottleneck \cite{Isely10}.\footnote{We refer the reader to \cite{ganguli2012compressed} for more on interactions between dictionary learning and neuroscience.}
+An immediate application of our theoretical work is Prop.~\ref{neuroprop}, which certifies the validity of a theory of biologically-plausible bottleneck communication in the brain: that sparse coding in a compressed space of neural activity can recover sparse codes sent through a randomly-constructed (but unknown) noisy wiring bottleneck \cite{Isely10}.\footnote{We refer the reader to \cite{ganguli2012compressed} for more on interactions between dictionary learning and neuroscience.}
 

### 2018-12-24 manuscripts/IEEE/final_submission.tex
last changes

--- 2018-12-24 manuscripts/IEEE/chazthm_ieee_trans_sig_CHAZ.tex
@@
 However, universal conditions guaranteeing the consistency of these learned features in the presence of measurement noise have yet to be stated.
-Here, we prove very generally that optimal dictionaries and sparse codes are uniquely and stably determined up to measurement error for all diverse enough datasets generated in accordance with the constraints assumed by sparse coding.
+Here, we prove very generally that optimal dictionaries and sparse codes are uniquely and stably determined up to measurement error for all diverse enough datasets generated by the sparse coding model.
 Applications are given to data analysis, engineering, and neuroscience.
@@
 % \cite{sato1975method}
-\IEEEPARstart{A}{}common assumption underlying contemporary applications of signal processing and pattern analysis is that each of $N$ observed $n$-dimensional signal samples is a (noisy) linear combination of at most $k$ elementary waveforms drawn from some unknown \emph{dictionary} of size $m$, typically with $m \ll N$ (see \cite{Zhang15} for a comprehensive review of this and related models).
-Attempts to approximate solutions to this sparsity-constrained inverse problem have provided insight into the structure of many signal classes lacking idiosyncratic formal models (e.g., in vision \cite{wang2015sparse}).
-In fact, a seminal work in the field demonstrated that dictionaries optimized to sparsely represent small patches of natural images share many qualitative similarities to filters fit to the response properties of simple-cell neurons in mammalian visual cortex \cite{Olshausen96, hurri1996image, bell1997independent, van1998independent}, a major result in theoretical neuroscience.
+\IEEEPARstart{A}{}common assumption underlying contemporary solutions to problems in signal processing and pattern analysis is that each of $N$ observed $n$-dimensional signal samples is a (noisy) linear combination of at most $k$ elementary waveforms drawn from some unknown ``dictionary" of size $m$, typically with $m \ll N$ (see \cite{Zhang15} for a comprehensive review of this and related models).
+Approximate solutions to this sparsity-constrained inverse problem and its relatives have revealed seemingly characteristic structure in signal classes lacking idiosyncratic formal models (e.g., in vision \cite{wang2015sparse}).
+Interestingly, a seminal work in the field demonstrated that dictionaries optimized with respect to small patches of natural images share qualitative similarities with filters fit to the response properties of simple-cell neurons in mammalian visual cortex \cite{Olshausen96, hurri1996image, bell1997independent, van1998independent}, a major result in theoretical neuroscience.
 Moreover, these latent waveforms (e.g., ``Gabor'' wavelets) estimated from data appear to be canonical \cite{donoho2001can}; i.e.
-they emerge in dictionaries learned by a variety of algorithms trained with respect to different natural image datasets.
+they appear in dictionaries learned by a variety of algorithms trained with respect to different natural image datasets.
 
-Motivated by these discoveries and earlier work proposing a related theory of communication between sparsely active neural populations \cite{Isely10}, we address when dictionaries and the sparse representations they induce are uniquely determined by data.
-Answers to this question have real-world implications.
+Motivated by these discoveries and earlier work which proposed a theory of communication between sparsely active neural populations contingent on uniqueness \cite{Isely10}, we address when dictionaries and the sparse representations they induce are uniquely determined by data.
+Answers to this question have other practical implications.
 For example, it has been demonstrated that a sparse coding analysis of painting style can detect forgeries \cite{hughes2010}; but this implies all dictionaries consistent with training data generalize in their ability to sparsely encode new samples.
 Fortunately, several algorithms have recently been proposed which provably recover latent dictionaries under idiosyncratic conditions (see \cite[Sec.~I-E]{Sun16} for a summary of the state-of-the-art).
-Few theorems, however, can be cited to explain the consistency of inference with respect to this model more broadly; in particular, a universal guarantee of uniqueness and stability in the context of noise has yet to emerge.
+Few theorems, however, can be cited to explain the consistency of inference under this model of data more broadly; in particular, a universal guarantee of uniqueness and stability in the context of noise has yet to emerge.
 
-Here, we prove very generally that uniqueness and stability of solutions is an expected property of both the sparse coding problem described above as well as a related (and perhaps more well-known) optimization formulation, which instead asks for a dictionary and sparse codes that minimize the mean sparsity over samples.
+Here, we prove very generally that uniqueness and stability of solutions is an expected property of the sparse coding problem described above as well as a related (and perhaps more well-known) optimization problem which asks for a dictionary and set of sparse codes that minimize the mean sparsity of the codes over all data samples.
 
@@
 Our claim is that there exist very general conditions under which any matrix $\mathbf{B}$ that solves this problem is always ``close" to $\mathbf{A}$, and likewise for the sparse codes $\mathbf{\overline x}_i$ and $\mathbf{x}_i$.
-In fact, provided $n \geq \min(2k,m)$, in almost all cases \ref{InverseProblem} is well-posed (as per Hadamard \cite{Hadamard1902}) given enough data (Cor.~\ref{ProbabilisticCor}).
-In particular, these explicit, universal guarantees hold without imposing \emph{any} constraints on the recovered matrix $\mathbf{B}$ (e.g.
-that it, too, satisfy any injectivity criteria), even the number $m$ of dictionary elements it should contain.
+In fact, provided $n \geq \min(2k,m)$, in almost all cases (\ref{InverseProblem}) is well-posed (as per Hadamard \cite{Hadamard1902}) given enough data (Cor.~\ref{ProbabilisticCor}).
+Importantly, these explicit, universal guarantees apply without the imposition of \emph{any} constraints on the recovered matrix $\mathbf{B}$ (e.g.
+that it, too, satisfy any injectivity criteria), beyond a cap on the number $m$ of dictionary elements it should contain.
 
-Note that any particular solution to Problem \ref{InverseProblem} represents an infinity of equivalent solutions $\mathbf{BPD}$ and $\mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_1, \ldots, \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_N$ parametrized by a choice of permutation matrix $\mathbf{P}$ and invertible diagonal matrix $\mathbf{D}$ capturing the sparsity-preserving labeling and scaling ambiguities inherent to the problem statement.
+We note that any particular solution to Problem \ref{InverseProblem} actually represents an infinity of equivalent solutions $\mathbf{BPD}$ and $\mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_1, \ldots, \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_N$ parametrized by a choice of permutation matrix $\mathbf{P}$ and invertible diagonal matrix $\mathbf{D}$ capturing the sparsity-preserving labeling and scaling ambiguities inherent to the problem statement.
 Previous theoretical work addressing the noiseless case $\eta =0$ (e.g., \cite{li2004analysis, Georgiev05, Aharon06, Hillar15}) with fixed $\overline m = m$ has shown that the solution to Prob.~\ref{InverseProblem}, when it exists, is unique up to these  ambiguities provided the $\mathbf{x}_i$ are sufficiently diverse and the matrix $\mathbf{A}$ satisfies:
@@
 also called the \textit{spark condition}, which in any case is necessary to guarantee the uniqueness of arbitrary sequences of $k$-sparse $\mathbf{x}_i$.
-We generalize these results to the practical setting of additive noise by incorporating the notion of stability with respect to noise.
+We generalize these results to the practical setting of additive noise by incorporating a notion of stability with respect to measurement error.
 
@@
 We then prove our main theorem (Thm.~\ref{DeterministicUniquenessTheorem}) in Sec.~\ref{DUT} after stating some additional definitions and lemmas required for the proof, including a useful result in combinatorial matrix analysis (Lem.~\ref{MainLemma}, proven in Appendix).
-We also provide a short argument extending our guarantees to the following more common formulation of the dictionary learning problem as an optimization over model parameters minimizing the total (or equivalently, the mean) number of non-zero entries in the sparse codes (Thm.~\ref{SLCopt}):
+We also provide an argument extending our guarantees to the following more common formulation of the dictionary learning problem as an optimization over model parameters minimizing the total (or equivalently, the mean) number of non-zero entries in the sparse codes (Thm.~\ref{SLCopt}):
 
@@
 \end{problem}
-We then sketch proofs of probabilistic extensions of Thm.~\ref{DeterministicUniquenessTheorem} to  data and dictionaries drawn from probability distributions (Thm.~\ref{robustPolythm} and Cor.~\ref{ProbabilisticCor}).
+We then sketch proofs of extensions of Thm.~\ref{DeterministicUniquenessTheorem} to data and dictionaries drawn from a probability distribution (Thm.~\ref{robustPolythm} and Cor.~\ref{ProbabilisticCor}).
 Finally, in Sec.~\ref{Discussion}, we discuss both theoretical and practical applications of our main mathematical findings.
@@
 
-Next, we describe a quantitative spark condition.
+Next, we describe a quantitative generalization of the spark condition.
 The \emph{lower bound} of a matrix $\mathbf{M} \in \mathbb R^{n \times m}$ is the largest $\alpha$ with \mbox{$\|\mathbf{M}\mathbf{x}\|_2 \geq \alpha\|\mathbf{x}\|_2$} for all $\mathbf{x} \in \mathbb{R}^m$ \cite{Grcar10}.
@@
 
-We generalize the  lower bound to a domain-restricted \emph{union of subspaces} model \cite{vidal2005generalized} derived from a hypergraph $\mathcal{H} \subseteq {[m] \choose k}$.
+We generalize this lower bound to a domain-restricted \emph{union of subspaces} model \cite{vidal2005generalized} derived from a hypergraph $\mathcal{H} \subseteq {[m] \choose k}$.
 Let $\mathbf{M}_S$ denote the submatrix formed by the columns of $\mathbf{M}$ indexed by $S \subseteq [m]$, with $\mathbf{M}_\emptyset := \mathbf{0}$.
@@
 A set of $k$-sparse vectors is said to be in \emph{general linear position} when any $k$ of them are linearly independent.
-The following is a precise statement of our main result, though we will leave the quantity $C_1 = C_1(\mathbf{A}, \{\mathbf{x}_i\}_{i=1}^N, \mathcal{H})$ undefined until Eq.~\eqref{Cdef1}.
+
+We are now in a position to give a precise statement of our main result, though we will leave the quantity $C_1 = C_1(\mathbf{A}, \{\mathbf{x}_i\}_{i=1}^N, \mathcal{H})$ undefined until Eq.~\eqref{Cdef1}.
 All of our theorems assume matrices consist of real numbers.
@@
 %To be clear, the implication of Thm.~\ref{DeterministicUniquenessTheorem} is that $Y = \{\mathbf{Ax}_1, \ldots, \mathbf{Ax}_N\}$ has a stable $k$-sparse representation in $\mathbb{R}^m$, with \eqref{def1} guaranteed provided $\varepsilon$ in Def.~\ref{maindef} does not exceed:
-In words, Thm.~\ref{DeterministicUniquenessTheorem} says that the smaller the difference $\overline m - m$ between assumed and actual latent dictionary sizes, the more columns and coefficients of the original dictionary $\mathbf{A}$ and codes $\mathbf{x}_i$ are contained (up to noise) in the appropriately scaled dictionary $\mathbf{B}$ and codes $\mathbf{\overline x}_i$.
+In words, Thm.~\ref{DeterministicUniquenessTheorem} says that the smaller the difference $\overline m - m$ between the assumed and actual number of latent dictionary elements, the more columns and coefficients of the original dictionary $\mathbf{A}$ and codes $\mathbf{x}_i$ are contained (up to noise) in the appropriately scaled recovered dictionary $\mathbf{B}$ and codes $\mathbf{\overline x}_i$, respectively.
 In the particular case when $\overline m = m$, the theorem directly implies that  $Y = \{\mathbf{Ax}_1, \ldots, \mathbf{Ax}_N\}$ has a stable $k$-sparse representation in $\mathbb{R}^m$, with inequalities \eqref{def1} guaranteed for $\varepsilon$ in Def.~\ref{maindef} given by:
@@
 Note that sparse codes $\mathbf{x}_i$ with a shared support that are in general linear position are straightforward to produce using a ``Vandermonde'' matrix construction (i.e., use the columns of the matrix $[\gamma_{i}^j]_{i,j=1}^{k,N}$, for distinct nonzero $\gamma_i$).
-Thus, the assumptions of Thm.~\ref{DeterministicUniquenessTheorem} are easily met, leading to the following direct application to uniqueness in sparse coding.
+Thus, the assumptions of Thm.~\ref{DeterministicUniquenessTheorem} are easily met.
 % (Prob.~\ref{InverseProblem}).
@@
 
-Another practical implication of Thm.~\ref{DeterministicUniquenessTheorem} is the following: there is an effective procedure sufficient to affirm if a proposed solution to Prob.~\ref{InverseProblem} is indeed unique (up to noise and inherent ambiguities).
-Simply check that the matrix and codes satisfy the (computable) assumptions of Thm.~\ref{DeterministicUniquenessTheorem} on $\mathbf{A}$ and the $\mathbf{x}_i$.
+A practical implication of Thm.~\ref{DeterministicUniquenessTheorem} is the following: there is an effective procedure sufficient to affirm if a proposed solution to Prob.~\ref{InverseProblem} is indeed unique (up to noise and inherent ambiguities).
+One need simply to check that the matrix and codes satisfy the (computable) assumptions of Thm.~\ref{DeterministicUniquenessTheorem} on $\mathbf{A}$ and the $\mathbf{x}_i$.
 %Another practical implication of Thm.\ref{DeterministicUniquenessTheorem} is the following: there is an effective procedure sufficient to affirm if a proposed solution $(\mathbf{B}, \mathbf{\overline x}_1, \ldots, \mathbf{x}_N)$ to Prob.~\ref{InverseProblem} is indeed unique (up to noise and inherent ambiguities).
@@
 There are other less direct consequences of Thm.~\ref{DeterministicUniquenessTheorem}.
-For instance, we apply it to prove uniqueness and stability of solutions to Prob.~\ref{SLCopt}, the usual optimization problem of interest for those applying dictionary learning to their data.
+For instance, we use it to prove uniqueness and stability of solutions to Prob.~\ref{SLCopt}, the usual optimization problem of interest for those applying dictionary learning to their data.
 
@@
 
-Thus, choosing the dictionary and codes ``randomly'' almost certainly generates data with a stable sparse representation.
+Thus, drawing the dictionary and sparse codes from any continuous probability distribution almost certainly generates data with a stable sparse representation.
 
@@
 
-A goal of this work was to explain the emergence of characteristic representations from sparse coding models fit to natural data, despite the varied assumptions underlying the many algorithms in current use.
+A motivation for this work was the emergence of seemingly characteristic representations from sparse coding models fit to natural data, despite the varied assumptions underlying the many algorithms in current use.
 To this end, we have taken an important step toward unifying the great number of publications on the topic by demonstrating very general, deterministic conditions under which identification of parameters in this model is not only possible but also robust to the inevitable uncertainty permeating measurement and model choice.
@@
 Beyond an original extension of existing noiseless guarantees \cite{Hillar15} to the noisy regime and their application to Prob.~\ref{OptimizationProblem}, a major innovation in our work is a theory of combinatorial designs for support sets key to the identification of the dictionary.
-We incorporate this idea into a new fundamental lemma in matrix theory (Lem.~\ref{MainLemma}) that draws upon the definition of a new matrix lower bound induced by a hypergraph.
+We incorporate this idea into a fundamental lemma in matrix theory (Lem.~\ref{MainLemma}) that draws upon the definition of a new matrix lower bound induced by a hypergraph.
 Insights enabled by our combinatorial approach include: 1) a subset of dictionary elements is recoverable even if dictionary size is overestimated, 2) data require only a polynomial number of distinct sparse supports, and 3) the spark condition is not a necessary property of recoverable dictionaries.
 
-A technical difficulty in proving Thm.~\ref{DeterministicUniquenessTheorem} is the absence of any assumption at all on dictionaries in solutions to Prob.~\ref{InverseProblem}.
-We sought such a guarantee because of the practical difficulty of ensuring that an algorithm maintain a dictionary satisfying the spark condition \eqref{SparkCondition} at each iteration, an implicit requirement of all previous works except \cite{Hillar15}; indeed, even certifying a dictionary has this property is NP-hard \cite{tillmann2014computational}.
+The absence of any assumption at all about dictionaries that solve Prob.~\ref{InverseProblem} was a major technical difficulty in proving Thm.~\ref{DeterministicUniquenessTheorem}.
+We sought such a general guarantee because of the practical difficulty of ensuring that an algorithm maintain a dictionary satisfying the spark condition \eqref{SparkCondition} at each iteration, an implicit requirement of all previous works except \cite{Hillar15}; indeed, even certifying a dictionary has this property is NP-hard \cite{tillmann2014computational}.
 

### 2018-12-25 manuscripts/IEEE/final_submission.tex
final sub

@@
 \begin{problem}\label{InverseProblem}
-Find a matrix $\mathbf{B}$ and $k$-sparse $\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N \in \mathbb{R}^{\overline m}$ satisfying $\|\mathbf{z}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \eta$ for all $i$.
+Find a real $n \times \overline m$ matrix $\mathbf{B}$ and $k$-sparse $\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N$ satisfying $\|\mathbf{z}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \eta$ for all $i$.
 \end{problem}
 
-Our claim is that there exist very general conditions under which any matrix $\mathbf{B}$ that solves this problem is always ``close" to $\mathbf{A}$, and likewise for the sparse codes $\mathbf{\overline x}_i$ and $\mathbf{x}_i$.
-In fact, provided $n \geq \min(2k,m)$, in almost all cases (\ref{InverseProblem}) is well-posed (as per Hadamard \cite{Hadamard1902}) given enough data (Cor.~\ref{ProbabilisticCor}).
+Our claim is that there exist very general conditions under which any such matrix $\mathbf{B}$ always contains a submatrix ``close" to some submatrix of $\mathbf{A}$, and similarly for the sparse codes $\mathbf{\overline x}_i$ and $\mathbf{x}_i$.
+In fact, provided $n \geq \min(2k,m)$, in almost all cases \ref{InverseProblem} is well-posed (as per Hadamard \cite{Hadamard1902}) given enough data (Cor.~\ref{ProbabilisticCor}).
 Importantly, these explicit, universal guarantees apply without the imposition of \emph{any} constraints on the recovered matrix $\mathbf{B}$ (e.g.
-that it, too, satisfy any injectivity criteria), beyond a cap on the number $m$ of dictionary elements it should contain.
+that it, too, satisfy any injectivity criteria) beyond an upper bound on its number of columns, $\overline m$.
 
@@
 Now, consider any dataset $Z$ generated as in \eqref{LinearModel} with $\eta \leq \frac{1}{2} \varepsilon(\delta_1, \delta_2)$.
-From the triangle inequality, it follows that any matrix $\mathbf{B}$ and $k$-sparse $\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N \in \mathbb{R}^m$ solving Prob.~\ref{InverseProblem} are necessarily within $\delta_1, \delta_2$ of the original dictionary $\mathbf{A}$ and codes $\mathbf{x}_i$, respectively.
+From the triangle inequality, it follows that any $n \times m$ matrix $\mathbf{B}$ and $k$-sparse $\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N$ solving Prob.~\ref{InverseProblem} are necessarily within $\delta_1, \delta_2$ of the original dictionary $\mathbf{A}$ and codes $\mathbf{x}_i$, respectively.
 
@@
 \begin{problem}\label{OptimizationProblem}
-Find $\mathbf{B}$ and \mbox{$\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N \in \mathbb{R}^{\overline m}$} that solve:
+Find real $\mathbf{B}$ and \mbox{$\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N$} that solve:
 \begin{align}\label{minsum}

### 2019-04-22 manuscripts/IEEE/final_submission.tex
chaz revision

@@
+% TODO: cite Fritz l0 paper in introduction for seemingly characteristic structure?
+
 % Notes:
@@
 % \cite{sato1975method}
-\IEEEPARstart{A}{}common assumption underlying contemporary solutions to problems in signal processing and pattern analysis is that each of $N$ observed $n$-dimensional signal samples is a (noisy) linear combination of at most $k$ elementary waveforms drawn from some unknown ``dictionary" of size $m$, typically with $m \ll N$ (see \cite{Zhang15} for a comprehensive review of this and related models).
-Approximate solutions to this sparsity-constrained inverse problem and its relatives have revealed seemingly characteristic structure in signal classes lacking idiosyncratic formal models (e.g., in vision \cite{wang2015sparse}).
-Interestingly, a seminal work in the field demonstrated that dictionaries optimized with respect to small patches of natural images share qualitative similarities with filters fit to the response properties of simple-cell neurons in mammalian visual cortex \cite{Olshausen96, hurri1996image, bell1997independent, van1998independent}, a major result in theoretical neuroscience.
-Moreover, these latent waveforms (e.g., ``Gabor'' wavelets) estimated from data appear to be canonical \cite{donoho2001can}; i.e.
-they appear in dictionaries learned by a variety of algorithms trained with respect to different natural image datasets.
+\IEEEPARstart{A}{}common assumption underlying contemporary solutions to problems in signal processing and pattern analysis is that each of $N$ observed $n$-dimensional signal is a (noisy) linear combination of at most $k$ elementary waveforms drawn from some unknown ``dictionary" of size $m \ll N$ (see \cite{Zhang15} for a comprehensive review of this and related models).
+Approximate solutions to inverse problems with these constraints and related sparsity constraints have revealed seemingly characteristic structure in several signal classes of current interest (e.g., in vision \cite{wang2015sparse}).
+Of particular note are the seminal works, which demonstrate that such dictionaries optimized with respect to small patches of natural images share qualitative features to linear filters fit to the response properties of simple-cell neurons in mammalian visual cortex \cite{Olshausen96, hurri1996image, bell1997independent, van1998independent}.
+Curiously, these waveforms (e.g., ``Gabor'' wavelets) appear in dictionaries learned by a variety of algorithms trained over different natural image datasets; as such, it appears these latent waveforms may be in some sense canonical \cite{donoho2001can}.
 
-Motivated by these discoveries and earlier work which proposed a theory of communication between sparsely active neural populations contingent on uniqueness \cite{Isely10}, we address when dictionaries and the sparse representations they induce are uniquely determined by data.
-Answers to this question have other practical implications.
-For example, it has been demonstrated that a sparse coding analysis of painting style can detect forgeries \cite{hughes2010}; but this implies all dictionaries consistent with training data generalize in their ability to sparsely encode new samples.
-Fortunately, several algorithms have recently been proposed which provably recover latent dictionaries under idiosyncratic conditions (see \cite[Sec.~I-E]{Sun16} for a summary of the state-of-the-art).
-Few theorems, however, can be cited to explain the consistency of inference under this model of data more broadly; in particular, a universal guarantee of uniqueness and stability in the context of noise has yet to emerge.
+Motivated by these discoveries and earlier work which outlined a theory of communication between sparsely active neural populations through a wiring bottleneck \cite{Isely10}, we address when dictionaries optimized to induce sparse representations are indeed identifiable from data.
+Answers to this question may have valuable implications in practice, for instance in justifying the identification of forged paintings by their anomalous sparse representations \cite{hughes2010}.
+While several algorithms have recently been proposed which provably recover unique latent dictionaries under specific conditions (see \cite[Sec.~I-E]{Sun16} for a summary of the state-of-the-art), few theorems can be cited to justify the consistency of inference under this model of data more broadly.
+In particular, a universal guarantee of the uniqueness and stability of learned sparse representations in the context of noise has yet to emerge in the literature.
 
-Here, we prove very generally that uniqueness and stability of solutions is an expected property of the sparse coding problem described above as well as a related (and perhaps more well-known) optimization problem which asks for a dictionary and set of sparse codes that minimize the mean sparsity of the codes over all data samples.
+Here, we prove very generally that uniqueness and stability is a typical property of the dictionary learning problem described above.
+More specifically,  we show that dictionaries injective on a sparse domain are identifiable from \mbox{$N = m(k-1){m \choose k} + m$} noisy sparse linear combinations of their columns up to an error that is linear in the noise (Thm.~\ref{DeterministicUniquenessTheorem}).
+In fact, provided $n \geq \min(2k,m)$, in almost all cases the problem is well-posed (as per Hadamard \cite{Hadamard1902}) given enough data (Cor.~\ref{ProbabilisticCor}).
+Similar guarantees can also be made for the related and perhaps more common optimization problem which instead seeks a dictionary minimizing the average sparsity of induced sparse codes over all data samples.
+Importantly, in both cases our explicit, universal guarantees apply without the imposition of \emph{any} constraints on the dictionaries of proposed solutions (e.g.
+that they, too, be injective over some sparse domain) beyond an upper bound on dictionary size, which is necessary in any case to avoid a trivial solution (e.g.
+letting $m = N$).
+%That is, every pair of solutions of comparable size has some number of dictionary elements in common (up to noise), and similarly so for the coefficients of sparse codes they induce.
 
-Formally, let $\mathbf{A} \in \mathbb R^{n \times m}$ be a matrix with columns $\mathbf{A}_j$ ($j = 1,\ldots,m$) and let dataset $Z$ consist of measurements:
+To state things properly, let $\mathbf{A} \in \mathbb R^{n \times m}$ be a matrix with columns $\mathbf{A}_j$ ($j = 1,\ldots,m$) and let dataset $Z$ consist of measurements:
 \begin{align}\label{LinearModel}
@@
 for $k$-\emph{sparse} $\mathbf{x}_i \in \mathbb{R}^m$ having at most $k<m$ nonzero entries and \emph{noise} $\mathbf{n}_i \in \mathbb{R}^n$, with bounded norm $\| \mathbf{n}_i \|_2 \leq  \eta$ representing our combined worst-case uncertainty in  measuring $\mathbf{A}\mathbf{x}_i$.
-We show that dictionaries $\mathbf{A}$ injective on certain subsets of $k$-sparse codes are identifiable from as few as \mbox{$N = m(k-1){m \choose k} + m$} noisy sparse linear combinations of their columns up to an error that is linear in the noise (Thm.~\ref{DeterministicUniquenessTheorem}).
-Specifically, the first mathematical problem we consider is:
+The first mathematical problem we consider is:
+
+%
 
 \begin{problem}\label{InverseProblem}
-Find a real $n \times \overline m$ matrix $\mathbf{B}$ and $k$-sparse $\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N$ satisfying $\|\mathbf{z}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \eta$ for all $i$.
+Find a real matrix $\mathbf{B}$ and $k$-sparse $\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N$ satisfying $\|\mathbf{z}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \eta$ for all $i$.
 \end{problem}
 
-Our claim is that there exist very general conditions under which any such matrix $\mathbf{B}$ always contains a submatrix ``close" to some submatrix of $\mathbf{A}$, and similarly for the sparse codes $\mathbf{\overline x}_i$ and $\mathbf{x}_i$.
-In fact, provided $n \geq \min(2k,m)$, in almost all cases \ref{InverseProblem} is well-posed (as per Hadamard \cite{Hadamard1902}) given enough data (Cor.~\ref{ProbabilisticCor}).
-Importantly, these explicit, universal guarantees apply without the imposition of \emph{any} constraints on the recovered matrix $\mathbf{B}$ (e.g.
-that it, too, satisfy any injectivity criteria) beyond an upper bound on its number of columns, $\overline m$.
-
-We note that any particular solution to Problem \ref{InverseProblem} actually represents an infinity of equivalent solutions $\mathbf{BPD}$ and $\mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_1, \ldots, \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_N$ parametrized by a choice of permutation matrix $\mathbf{P}$ and invertible diagonal matrix $\mathbf{D}$ capturing the sparsity-preserving labeling and scaling ambiguities inherent to the problem statement.
-Previous theoretical work addressing the noiseless case $\eta =0$ (e.g., \cite{li2004analysis, Georgiev05, Aharon06, Hillar15}) with fixed $\overline m = m$ has shown that the solution to Prob.~\ref{InverseProblem}, when it exists, is unique up to these  ambiguities provided the $\mathbf{x}_i$ are sufficiently diverse and the matrix $\mathbf{A}$ satisfies:
+Note there is some ambiguity in this problem statement, as any particular solution actually represents infinitely many alternative solutions $\mathbf{BPD}$ and $\mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_1, \ldots, \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_N$ parametrized by a choice of permutation matrix $\mathbf{P}$ and invertible diagonal matrix $\mathbf{D}$.
+Previous theoretical work addressing the noiseless case $\eta =0$ (e.g., \cite{li2004analysis, Georgiev05, Aharon06, Hillar15}) for matrices $\mathbf{B}$ having $m$ columns has shown that the solution to Prob.~\ref{InverseProblem}, when it exists, is unique up to these labeling and scaling ambiguities provided the $\mathbf{x}_i$ are sufficiently diverse and the matrix $\mathbf{A}$ satisfies the \textit{spark condition}:
 \begin{align}\label{SparkCondition}
@@
 %
-also called the \textit{spark condition}, which in any case is necessary to guarantee the uniqueness of arbitrary sequences of $k$-sparse $\mathbf{x}_i$.
-We generalize these results to the practical setting of additive noise by incorporating a notion of stability with respect to measurement error.
+which in any case is necessary to guarantee the uniqueness of arbitrary $k$-sparse $\mathbf{x}_i$.
+We generalize these results to the practical setting  $\eta > 0$ by considering a notion of stability with respect to measurement error.
 
@@
 
-To see how Def.
-\ref{maindef} is motivated by Prob.
-\ref{InverseProblem}, suppose that $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$ and fix $\delta_1, \delta_2$ to be the desired recovery accuracy in \eqref{def1}.
+To see how Prob.
+\ref{InverseProblem} motivates this definition, suppose that $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$ and fix $\delta_1, \delta_2$ to be the desired accuracy of recovery in \eqref{def1}.
 Now, consider any dataset $Z$ generated as in \eqref{LinearModel} with $\eta \leq \frac{1}{2} \varepsilon(\delta_1, \delta_2)$.
-From the triangle inequality, it follows that any $n \times m$ matrix $\mathbf{B}$ and $k$-sparse $\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N$ solving Prob.~\ref{InverseProblem} are necessarily within $\delta_1, \delta_2$ of the original dictionary $\mathbf{A}$ and codes $\mathbf{x}_i$, respectively.
+From the triangle inequality, it follows that any $n \times m$ matrix $\mathbf{B}$ and $k$-sparse $\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N$ solving Prob.~\ref{InverseProblem} are necessarily within $\delta_1, \delta_2$ of the original dictionary $\mathbf{A}$ and codes $\mathbf{x}_1, ..., \mathbf{x}_N$, respectively.\footnote{The different norms for the dictionary and codes in \eqref{def1} are meant only to reflect their typically distinct semantics in modeling.}
 
-In the next section, we give precise statements of our main results, which include an explicit form for $\varepsilon(\delta_1, \delta_2)$.
-We then prove our main theorem (Thm.~\ref{DeterministicUniquenessTheorem}) in Sec.~\ref{DUT} after stating some additional definitions and lemmas required for the proof, including a useful result in combinatorial matrix analysis (Lem.~\ref{MainLemma}, proven in Appendix).
-We also provide an argument extending our guarantees to the following more common formulation of the dictionary learning problem as an optimization over model parameters minimizing the total (or equivalently, the mean) number of non-zero entries in the sparse codes (Thm.~\ref{SLCopt}):
+In the next section, we give a precise statement of our main result (Thm.~\ref{DeterministicUniquenessTheorem}) from which an explicit form for $\varepsilon(\delta_1, \delta_2)$ may be derived.
+We then extend our guarantees to the following more common formulation of the dictionary learning problem as one of minimizing the total (or equivalently, the mean) number of non-zero entries in the sparse codes (Thm.~\ref{SLCopt}):
 
@@
 \end{problem}
-We then sketch proofs of extensions of Thm.~\ref{DeterministicUniquenessTheorem} to data and dictionaries drawn from a probability distribution (Thm.~\ref{robustPolythm} and Cor.~\ref{ProbabilisticCor}).
-Finally, in Sec.~\ref{Discussion}, we discuss both theoretical and practical applications of our main mathematical findings.
+
+The section closes with some brief arguments extending Thm.~\ref{DeterministicUniquenessTheorem} to data and dictionaries drawn from probability distributions (Cor.~\ref{ProbabilisticCor}).
+The more involved proofs of Thms.~\ref{DeterministicUniquenessTheorem} and~\ref{SLCopt} are defered to Sec.~\ref{DUT}, following some necessary preamble stating definitions and a useful result in combinatorial matrix analysis (Lem.~\ref{MainLemma}, proven in the Appendix).
+Finally, we discuss in Sec.~\ref{Discussion} some theoretical and practical applications of our main mathematical findings.
 
@@
 
-Before stating our results precisely, we identify criteria on the support sets of the generating codes $\mathbf{x}_i$ that imply stable sparse representations.
-Letting $\{1, \ldots, m\}$ be denoted $[m]$, its power set $2^{[m]}$, and ${[m] \choose k}$ the set of subsets of $[m]$ of size $k$, we say a hypergraph $\mathcal{H} \subseteq 2^{[m]}$ on vertices $[m]$ is \textit{$k$-uniform} when $\mathcal{H} \subseteq {[m] \choose k}$.
-The \emph{degree} $\deg_\mathcal{H}(i)$ of a node $i \in [m]$ is the number of sets in $\mathcal{H}$ that contain $i$, and we say $\mathcal{H}$ is \emph{regular} when for some $r$ we have $\deg_\mathcal{H}(i) = r$ for all $i$ (given such an $r$, we say $\mathcal{H}$ is \textit{$r$-regular}).
+%Denote by $\mathbf{x}^J$ the subvector formed from the entries of $\mathbf{x}$ indexed by $J$. 
+%A set of $k$-sparse vectors is said to be in \emph{general linear position} when any $k$ of them are linearly independent.
+
+To state our results precisely, we must first identify some combinatorial criteria on the supports\footnote{Recall a vector $\mathbf{x}$ is said to be \emph{supported} in $S$ when $\mathbf{x} \in \text{\rm span}\{\mathbf{e}_j: j\in S\}$, the $\mathbf{e}_j$ forming the standard column basis.} of sparse vectors.
+Let $\{1, \ldots, m\}$ be denoted $[m]$, its power set $2^{[m]}$, and ${[m] \choose k}$ the set of subsets of $[m]$ of size $k$.
+A \emph{hypergraph} on vertices $[m]$  is any subset $\mathcal{H} \subseteq 2^{[m]}$.
+We say $\mathcal{H}$ is \textit{$k$-uniform} when in fact $\mathcal{H} \subseteq {[m] \choose k}$.
+The \emph{degree} $\deg_\mathcal{H}(i)$ of a node $i \in [m]$ is the number of sets in $\mathcal{H}$ that contain $i$, and $\mathcal{H}$ is labeled as \emph{regular} when for some $r$ we have $\deg_\mathcal{H}(i) = r$ for all $i$ (given such an $r$, we say $\mathcal{H}$ is \textit{$r$-regular}).
 We also write $2\mathcal{H} := \{ S \cup S': S, S' \in \mathcal{H}\}$.
@@
 The \emph{lower bound} of a matrix $\mathbf{M} \in \mathbb R^{n \times m}$ is the largest $\alpha$ with \mbox{$\|\mathbf{M}\mathbf{x}\|_2 \geq \alpha\|\mathbf{x}\|_2$} for all $\mathbf{x} \in \mathbb{R}^m$ \cite{Grcar10}.
-By compactness of the unit sphere, injective linear maps have nonzero lower bound; hence, if $\mathbf{M}$ satisfies \eqref{SparkCondition}, then each submatrix formed from $2k$ of its columns or less has a strictly positive lower bound.
+By compactness of the unit sphere, every injective linear map has a positive lower bound; hence, if $\mathbf{M}$ satisfies \eqref{SparkCondition} then each submatrix formed from $2k$ of its columns or less has a strictly positive lower bound.
 
-We generalize this lower bound to a domain-restricted \emph{union of subspaces} model \cite{vidal2005generalized} derived from a hypergraph $\mathcal{H} \subseteq {[m] \choose k}$.
+We now generalize the matrix lower bound to apply only over a restricted union of subspaces\footnote{See \cite{vidal2005generalized} for an overview of union of subspace modeling.} associated with a hypergraph $\mathcal{H} \subseteq {[m] \choose k}$.
 Let $\mathbf{M}_S$ denote the submatrix formed by the columns of $\mathbf{M}$ indexed by $S \subseteq [m]$, with $\mathbf{M}_\emptyset := \mathbf{0}$.
-(In the sections that follow, we write $\bm{\mathcal{M}}_S$ to denote the column-span of a submatrix $\mathbf{M}_S$, and $\bm{\mathcal{M}}_\mathcal{G}$ to denote $\{\bm{\mathcal{M}}_S\}_{S \in \mathcal{G}}$.) Define:
+(In the sections that follow, we will write $\bm{\mathcal{M}}_S$ to denote the column-span of a submatrix $\mathbf{M}_S$, and $\bm{\mathcal{M}}_\mathcal{G}$ to denote $\{\bm{\mathcal{M}}_S\}_{S \in \mathcal{G}}$.) We define:
 %\begin{align*} 
@@
 %\begin{align*}
-%L_\mathcal{H}(\mathbf{M}) := \max \left\{ \alpha: \|\mathbf{M}_S\mathbf{x}\|_2 \geq \alpha \sqrt{k} \|\mathbf{x}\|_2 : S \in \mathcal{H}, \ \ \mathbf{x} \in \mathbb{R}^m \right\},
+%L_\mathcal{H}(\mathbf{M}) := \max \left\{ \ falpha: \|\mathbf{M}_S\mathbf{x}\|_2 \geq \alpha \sqrt{k} \|\mathbf{x}\|_2 : S \in \mathcal{H}, \ \ \mathbf{x} \in \mathbb{R}^m \right\},
 %\end{align*} 
 \begin{align}\label{Ldef}
-L_\mathcal{H}(\mathbf{M}) := \frac{1}{\sqrt{k}} \min \left\{ \frac{\|\mathbf{M}_S\mathbf{x}\|_2}{ \|\mathbf{x}\|_2} : S \in \mathcal{H}, \ \ \mathbf{x} \in \mathbb{R}^{|S|} \right\},
+L_\mathcal{H}(\mathbf{M}) := \frac{1}{\sqrt{k}} \min \left\{ \frac{\|\mathbf{M}_S\mathbf{x}\|_2}{ \|\mathbf{x}\|_2} : S \in \mathcal{H}, \ \ \mathbf{x} \in \mathbb{R}^{|S|} \right\}.
 \end{align} 
 %
-where we write $L_{k}$ when $\mathcal{H} = {[m] \choose k}$.\footnote{We note that $1 - \sqrt{k} L_k(\mathbf{M})$ is known as the asymmetric lower restricted isometry constant for matrices $\mathbf{M}$ with unit $\ell_2$-norm columns \cite{Blanchard2011}.} Clearly, $L_{2k}(\mathbf{M}) > 0$ for $\mathbf{M}$ satisfying \eqref{SparkCondition} and $L_{k'}(\mathbf{M}) \geq L_k(\mathbf{M})$ whenever $k' \leq k$.
-Note also that $L_2 \geq L_{2\mathcal{H}} \geq L_{2k}$ if $\mathcal{H} \subseteq {[m] \choose k}$ has $\cup \mathcal{H} = [m]$.
+We write $L_{k}$ in place of $L_\mathcal{H}$ when $\mathcal{H} = {[m] \choose k}$, and note that $1 - \sqrt{k} L_k(\mathbf{M})$ is known as the asymmetric lower restricted isometry constant for matrices $\mathbf{M}$ with unit $\ell_2$-norm columns \cite{Blanchard2011}.
+As explained previously, we have $L_{2k}(\mathbf{M}) > 0$ for all $\mathbf{M}$ satisfying \eqref{SparkCondition}.
+Clearly, $L_{k'}(\mathbf{M}) \geq L_k(\mathbf{M})$ whenever $k' \leq k$ and, by the same token, any $k$-uniform $\mathcal{H}$ satisfying $\cup \mathcal{H} = [m]$ has $L_2 \geq L_{2\mathcal{H}} \geq L_{2k}$.
 
-A vector $\mathbf{x}$ is said to be \emph{supported} in $S \subseteq [m]$ when $\mathbf{x} \in \text{\rm span}\{\mathbf{e}_j: j\in S\}$, where $\mathbf{e}_j$ form the standard column basis in $\mathbb R^m$.
-%Denote by $\mathbf{x}^J$ the subvector formed from the entries of $\mathbf{x}$ indexed by $J$. 
-A set of $k$-sparse vectors is said to be in \emph{general linear position} when any $k$ of them are linearly independent.
+Finally, we mention that a set of vectors sharing support $S$ are said to be in \emph{general linear position} when any $|S|$ of them form a linearly independent set.
 
-We are now in a position to give a precise statement of our main result, though we will leave the quantity $C_1 = C_1(\mathbf{A}, \{\mathbf{x}_i\}_{i=1}^N, \mathcal{H})$ undefined until Eq.~\eqref{Cdef1}.
-All of our theorems assume matrices consist of real numbers.
+We are now in a position to give a precise statement of our main result, though for expository purposes we will leave the quantity $C_1$ (a function of $\mathbf{A}$, $\mathbf{x}_1, ..., \mathbf{x}_N$, and $\mathcal{H}$) undefined until Eq.~\eqref{Cdef1} of Sec.~\ref{DUT}.
+We state here once that all of our theorems assume matrices consist of real numbers.
 
@@
 If \mbox{$\{\mathbf{x}_1, \ldots, \mathbf{x}_N\} \subset \mathbb{R}^m$} contains, for each $S \in \mathcal{H}$, more than $(k-1){m \choose k}$ $k$-sparse vectors in general linear position supported in $S$, then there is $C_1 > 0$ with the following holding for all%\footnote{The condition $\varepsilon < L_2(\mathbf{A}) /C_1$ is necessary; otherwise,  with \mbox{$\mathbf{A}$ = $\mathbf{I}$} and $\mathbf{x}_i = \mathbf{e}_i$, there is a matrix $\mathbf{B}$ and $1$-sparse $\mathbf{\overline{x}}_i$ with $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline{x}}_i \|_2 \leq \varepsilon$ that nonetheless violates \eqref{Cstable}.} $\varepsilon < L_{2}(\mathbf{A}) / C_1$:
-\footnote{The condition $\varepsilon < L_2(\mathbf{A}) /C_1$ is necessary; otherwise, with \mbox{$\mathbf{A}$ = $\mathbf{I}$} and $\mathbf{x}_i = \mathbf{e}_i$, the matrix $\mathbf{B} = \left[\mathbf{0}, \frac{1}{2}(\mathbf{e}_1 + \mathbf{e}_2), \mathbf{e}_3, \ldots, \mathbf{e}_{m} \right]$ and 1-sparse codes $\mathbf{\overline x}_i = \mathbf{e}_2$ for $i = 1, 2$ and $\mathbf{\overline x}_i = \mathbf{e}_i$ for $i \geq 3$ satisfy $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline{x}}_i \|_2 \leq \varepsilon$ but nonetheless violate \eqref{Cstable}.} $\varepsilon < L_{2}(\mathbf{A}) / C_1$:
+\footnote{Note that the condition $\varepsilon < L_2(\mathbf{A}) /C_1$ is necessary; otherwise, with \mbox{$\mathbf{A}$ = $\mathbf{I}$} (the identity matrix) and $\mathbf{x}_i = \mathbf{e}_i$, the matrix $\mathbf{B} = \left[\mathbf{0}, \frac{1}{2}(\mathbf{e}_1 + \mathbf{e}_2), \mathbf{e}_3, \ldots, \mathbf{e}_{m} \right]$ and sparse codes $\mathbf{\overline x}_i = \mathbf{e}_2$ for $i = 1, 2$ and $\mathbf{\overline x}_i = \mathbf{e}_i$ for $i \geq 3$ satisfy $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline{x}}_i \|_2 \leq \varepsilon$ but nonetheless violate \eqref{Cstable}.} $\varepsilon < L_{2}(\mathbf{A}) / C_1$:
 
-Every $n \times \overline m$ matrix $\mathbf{B}$ for which there are $k$-sparse $\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N$ satisfying \mbox{$\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \varepsilon$} for all $i$ has $\overline m \geq m$ and, provided $(r-1) \overline m < mr$,
+Every $n \times \overline m$ matrix $\mathbf{B}$ for which there are $k$-sparse $\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N$ satisfying \mbox{$\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \varepsilon$} for all $i$ has $\overline m \geq m$ and, provided $\overline m < mr / (r-1)$,
 \begin{align}\label{Cstable}
@@
 %
-for some nonempty $\overline J \subseteq [\overline m]$ and $J \subseteq [m]$ of size $\overline m - r(\overline m - m)$, permutation matrix $\mathbf{P}$, and invertible diagonal matrix $\mathbf{D}$.
+for some $\overline J \subseteq [\overline m]$ and $J \subseteq [m]$ of size \mbox{$m - (r-1)(\overline m - m)$}, a permutation matrix $\mathbf{P}$, and an invertible diagonal matrix $\mathbf{D}$. 
+% $\overline m - r(\overline m - m)$
 
@@
 %\|\mathbf{x}^J_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}^{\overline J}_i\|_1 &\leq  \left( \frac{ 1+C_1 \|\mathbf{x}^{J}_i\|_1 }{ L_{2k}(\mathbf{A}) -  C_1\varepsilon } \right) \varepsilon \ \  \text{for $i \in [N]$}.
-\|\mathbf{x}_i - \left(\mathbf{D}^{-1}\mathbf{P}^{\top}\right)_{\overline J}\mathbf{\overline x}_i\|_1 &\leq  \left( \frac{ 1+C_1 \|\mathbf{x}_i\|_1 }{ L_{2k}(\mathbf{A}) -  C_1\varepsilon } \right) \varepsilon, \ \  \text{for $i \in [N]$},
+\|(\mathbf{x}_i)_J - \left(\mathbf{D}^{-1}\mathbf{P}^{\top}\right)_{\overline J}(\mathbf{\overline x}_i)_{\overline J}|_1 &\leq  \left( \frac{ 1+C_1 \|\mathbf{x}_i\|_1 }{ L_{2k}(\mathbf{A}) -  C_1\varepsilon } \right) \varepsilon, \ \  \text{for $i \in [N]$},
 \end{align}
 %
-where $\mathbf{x}_i$ and $\mathbf{\overline x}_i$ here represent subvectors formed from restricting to entries indexed by $J$ and $\overline J$, respectively. 
+where $(\mathbf{x}_i)_J$ and $(\mathbf{\overline x}_i)_{\overline J}$ here represent subvectors formed from restricting to entries indexed by $J$ and $\overline J$, respectively. 
 \end{theorem}
@@
 %To be clear, the implication of Thm.~\ref{DeterministicUniquenessTheorem} is that $Y = \{\mathbf{Ax}_1, \ldots, \mathbf{Ax}_N\}$ has a stable $k$-sparse representation in $\mathbb{R}^m$, with \eqref{def1} guaranteed provided $\varepsilon$ in Def.~\ref{maindef} does not exceed:
-In words, Thm.~\ref{DeterministicUniquenessTheorem} says that the smaller the difference $\overline m - m$ between the assumed and actual number of latent dictionary elements, the more columns and coefficients of the original dictionary $\mathbf{A}$ and codes $\mathbf{x}_i$ are contained (up to noise) in the appropriately scaled recovered dictionary $\mathbf{B}$ and codes $\mathbf{\overline x}_i$, respectively.
+In words, Thm.~\ref{DeterministicUniquenessTheorem} says that the smaller the regularity $r$ or difference $\overline m - m$ between the assumed and actual number of latent dictionary elements, the more columns and coefficients of the original dictionary $\mathbf{A}$ and sparse codes $\mathbf{x}_i$ are guaranteed to be contained (up to noise) in the appropriately scaled recovered dictionary $\mathbf{B}$ and codes $\mathbf{\overline x}_i$, respectively.
 In the particular case when $\overline m = m$, the theorem directly implies that  $Y = \{\mathbf{Ax}_1, \ldots, \mathbf{Ax}_N\}$ has a stable $k$-sparse representation in $\mathbb{R}^m$, with inequalities \eqref{def1} guaranteed for $\varepsilon$ in Def.~\ref{maindef} given by:
@@
 
-Note that sparse codes $\mathbf{x}_i$ with a shared support that are in general linear position are straightforward to produce using a ``Vandermonde'' matrix construction (i.e., use the columns of the matrix $[\gamma_{i}^j]_{i,j=1}^{k,N}$, for distinct nonzero $\gamma_i$).
-Thus, the assumptions of Thm.~\ref{DeterministicUniquenessTheorem} are easily met.
+We note that the assumptions of Thm.~\ref{DeterministicUniquenessTheorem} are easily met with deterministic constructions.
+In particular, sparse codes with a shared support that are in general linear position are straightforward to produce using a ``Vandermonde'' matrix construction (i.e., use the columns of the matrix $[\gamma_{i}^j]_{i,j=1}^{k,N}$, for distinct nonzero $\gamma_i$).
 % (Prob.~\ref{InverseProblem}).
@@
 
-One can also easily verify that for every $k < m$, there are regular $k$-uniform hypergraphs with the SIP besides the obvious $\mathcal{H} = {[m] \choose k}$; for instance, take $\mathcal{H}$ to be the consecutive intervals of length $k$ in some cyclic order on $[m]$.
+One can also easily verify that for every $k < m$ there are regular $k$-uniform hypergraphs with the SIP besides the obvious $\mathcal{H} = {[m] \choose k}$.
+For instance, take $\mathcal{H}$ to be the $(k-1)$-regular set of consecutive intervals of length $k$ in some cyclic order on $[m]$.
 In this case, a direct consequence of Cor.~\ref{DeterministicUniquenessCorollary} is rigorous verification of the lower bound \mbox{$N = m(k-1){m \choose k} + m$} for sufficient sample size from the introduction.
-Often, the SIP is achievable with fewer supports.
-For example, when $k = \sqrt{m}$, take $\mathcal{H}$ to be the $2k$ rows and columns formed by arranging $[m]$ into a square grid.
+Special cases require even fewer supports, however.
+For example, if $k = \sqrt{m}$ then a 2-regular hypergraph with the SIP can be constructed as the $2k$ rows and columns formed by arranging the elements of $[m]$ into a square grid.
+
+%\cite{li2004analysis, Georgiev05, Aharon06, Hillar15}
+We should stress the point here that framing the problem in terms of hypergraphs has allowed us to show, unlike in previous works on the subject, that the matrix $\mathbf{A}$ need not satisfy \eqref{SparkCondition} to be recoverable from data.
+As an example, let $\mathbf{A} = [ \mathbf{e}_1, \ldots, \mathbf{e}_5, \mathbf{v}]$ where $\mathbf{v} = \mathbf{e}_1 + \mathbf{e}_3 + \mathbf{e}_5$, and take $\mathcal{H}$ to be all consecutive pairs of $1, ...
+,6$ arranged in cyclic order.
+Then, for $k=2$, $\mathbf{A}$ fails to satisfy \eqref{SparkCondition} while still satisfying the assumptions of Thm.~\ref{DeterministicUniquenessTheorem}.%, hence guaranteeing \eqref{Cstable} .
+%(since $\{ \mathbf{A}_1, \mathbf{A}_3, \mathbf{A}_5, \mathbf{A}_6\}$ is not a linearly independent set).
+%This weakening allows for a practical (polynomial) amount of data to still guarantee a stable dictionary in the case where the set of sparse supports for the $\mathbf{\overline x}_i$ is known to have a size that grows polynomially in $m$ and $k$.
 
 A practical implication of Thm.~\ref{DeterministicUniquenessTheorem} is the following: there is an effective procedure sufficient to affirm if a proposed solution to Prob.~\ref{InverseProblem} is indeed unique (up to noise and inherent ambiguities).
-One need simply to check that the matrix and codes satisfy the (computable) assumptions of Thm.~\ref{DeterministicUniquenessTheorem} on $\mathbf{A}$ and the $\mathbf{x}_i$.
+Simply check that the matrix and codes satisfy the (computable) assumptions of Thm.~\ref{DeterministicUniquenessTheorem} on $\mathbf{A}$ and the $\mathbf{x}_i$.
+In general, however, there is no efficient such procedure.
+We defer a brief discussion on this point to the next section.
 %Another practical implication of Thm.\ref{DeterministicUniquenessTheorem} is the following: there is an effective procedure sufficient to affirm if a proposed solution $(\mathbf{B}, \mathbf{\overline x}_1, \ldots, \mathbf{x}_N)$ to Prob.~\ref{InverseProblem} is indeed unique (up to noise and inherent ambiguities).
@@
 
-%\cite{li2004analysis, Georgiev05, Aharon06, Hillar15}
-We furthermore note that unlike in previous works, the matrix $\mathbf{A}$ need not satisfy \eqref{SparkCondition} to be recoverable from data.
-As an example for $k=2$, let $\mathbf{A} = [ \mathbf{e}_1, \ldots, \mathbf{e}_5, \mathbf{v}]$ where $\mathbf{v} = \mathbf{e}_1 + \mathbf{e}_3 + \mathbf{e}_5$, and take $\mathcal{H}$ to be all consecutive pairs of $[m]$ arranged in cyclic order.
-Then, dictionary $\mathbf{A}$ satisfies the assumptions of Thm.~\ref{DeterministicUniquenessTheorem} guaranteeing \eqref{Cstable} without satisfying \eqref{SparkCondition}.
-%(since $\{ \mathbf{A}_1, \mathbf{A}_3, \mathbf{A}_5, \mathbf{A}_6\}$ is not a linearly independent set).
-%This weakening allows for a practical (polynomial) amount of data to still guarantee a stable dictionary in the case where the set of sparse supports for the $\mathbf{\overline x}_i$ is known to have a size that grows polynomially in $m$ and $k$.
-
-There are other less direct consequences of Thm.~\ref{DeterministicUniquenessTheorem}.
-For instance, we use it to prove uniqueness and stability of solutions to Prob.~\ref{SLCopt}, the usual optimization problem of interest for those applying dictionary learning to their data.
+A less direct consequence of Thm.~\ref{DeterministicUniquenessTheorem} is the following uniqueness and stability guarantee for solutions to Prob.~\ref{SLCopt}, the usual optimization problem of interest for those applying dictionary learning to their data.
 
 \begin{theorem}\label{SLCopt}
-If the assumptions of Thm.~\ref{DeterministicUniquenessTheorem} hold, only now with more than $(k-1)\left[ {\overline m \choose k} + |\mathcal{H}|k{\overline m \choose k-1}\right]$ vectors $\mathbf{x}_i$ supported in each $S \in \mathcal{H}$, then all solutions to Prob.~\ref{OptimizationProblem} with $\eta \leq \varepsilon / 2$ necessarily satisfy recovery inequalities \eqref{Cstable} and \eqref{b-PDa} of Thm.~\ref{DeterministicUniquenessTheorem}.
+If the assumptions of Thm.~\ref{DeterministicUniquenessTheorem} hold, only now with more than $(k-1)\left[ {\overline m \choose k} + |\mathcal{H}|k{\overline m \choose k-1}\right]$ vectors $\mathbf{x}_i$ supported in each $S \in \mathcal{H}$, then all solutions to Prob.~\ref{OptimizationProblem} with $\eta \leq \varepsilon / 2$ necessarily satisfy recovery inequalities \eqref{Cstable} and \eqref{b-PDa}.% of Thm.~\ref{DeterministicUniquenessTheorem}.
 \end{theorem}
 
-Another extension of Thm.~\ref{DeterministicUniquenessTheorem} arises from the following analytic characterization of the spark condition.
+Another extension of Thm.~\ref{DeterministicUniquenessTheorem} can be derived from the following analytic characterization of the spark condition.
 Let $\mathbf{A}$  be the $n \times m$ matrix of $nm$ indeterminates $A_{ij}$.
-When real numbers are substituted for $A_{ij}$, the resulting matrix satisfies \eqref{SparkCondition} if and only if the following polynomial is nonzero:
+The reader may verify that substituting real numbers for the $A_{ij}$ yields a matrix satisfying \eqref{SparkCondition} if and only if the following polynomial also evaluates to a nonzero number:
 \begin{align*}
@@
 %
-where for any $S' \in {[n] \choose 2k}$ and $S \in {[m] \choose 2k}$, the symbol $\mathbf{A}_{S',S}$ denotes the submatrix of entries $A_{ij}$ with $(i,j) \in S' \times S$.
-We note that the large number of terms in this product is likely necessary due to the NP-hardness of deciding whether a given matrix $\mathbf{A}$ satisfies the spark condition \cite{tillmann2014computational}.
+where for any $S' \in {[n] \choose 2k}$ and $S \in {[m] \choose 2k}$, the symbol $\mathbf{A}_{S',S}$ denotes the submatrix of entries $A_{ij}$ with $(i,j) \in S' \times S$.\footnote{The large number of terms in this product is likely necessary given that deciding whether or not a matrix satisfies the spark condition is NP-hard \cite{tillmann2014computational}.}
 
-Since $f$ is analytic, having a single substitution of a real matrix $\mathbf{A}$ with $f(\mathbf{A}) \neq 0$ necessarily implies that the zeroes of $f$ form a set of (Borel) measure zero.
-Fortunately, such a matrix $\mathbf{A}$ is easily constructed by adding rows of zeroes to any $\min(2k,m) \times m$ Vandermonde matrix as described above (so that each term in the product above for $f$ is nonzero).
-Hence, almost every $n \times m$ matrix with $n \geq \min(2k,m)$ satisfies \eqref{SparkCondition}.
+Since $f$ is analytic, having a single substitution of a real matrix $\mathbf{A}$ satisfy $f(\mathbf{A}) \neq 0$ implies that the zeroes of $f$ form a set of (Borel) measure zero.
+A representative such matrix $\mathbf{A}$ is easily constructed by adding rows of zeroes to any $\min(2k,m) \times m$ Vandermonde matrix as described previously, so that every sum in the product defining $f$ above is strictly positive.
+Almost every $n \times m$ matrix with $n \geq \min(2k,m)$ therefore satisfies \eqref{SparkCondition}.
 
@@
 A similar phenomenon applies to datasets of vectors with a stable sparse representation.
-As in \cite[Sec.~IV]{Hillar15}, consider the ``symbolic'' dataset $Y = \{\mathbf{A}\mathbf{x}_1,\ldots,\mathbf{A} \mathbf{x}_N\}$ generated by indeterminate $\mathbf{A}$ and indeterminate $k$-sparse $\mathbf{x}_1, \ldots, \mathbf{x}_N$.
+Briefly, following the same procedure as in \cite[Sec.~IV]{Hillar15}, we may consider the ``symbolic'' dataset $Y = \{\mathbf{A}\mathbf{x}_1,\ldots,\mathbf{A} \mathbf{x}_N\}$ generated by indeterminate $\mathbf{A}$ and indeterminate $k$-sparse $\mathbf{x}_1, \ldots, \mathbf{x}_N$.
+Letting $\textbf{M}$ be the matrix with columns $\mathbf{A}\mathbf{x}_i$, $i \in [N]$, it can be checked that when $f(\mathbf{M}) \neq 0$ for a substitution of real numbers for the indeterminates, all of the assumptions on $\mathbf{A}$ and $\mathbf{x}_i$ in Thm.~\ref{DeterministicUniquenessTheorem} are satisfied; in particular, $\mathbf{A}$ satisfies \eqref{SparkCondition}.
+We therefore have the following result:
 
@@
 
+Note moreover that if a set of measure spaces $\{(X_{\ell}, \Sigma_{\ell}, \nu_{\ell})\}_{\ell=1}^p$ has $\nu_{\ell}$ absolutely continuous with respect to $\mu$ for all $\ell \in [p]$, where $\mu$ is the standard Borel measure on $\mathbb{R}$, then the product measure $\prod_{\ell=1}^p \nu_{\ell}$ is absolutely continuous with respect to the standard Borel product measure on $\mathbb{R}^p$.
+% for space:  (e.g.,  \cite{folland2013real}).
+By Thm.~\ref{robustPolythm}, there is then a polynomial that is nonzero when $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$; in particular, stability holds almost surely and we have the following:
+
 \begin{corollary}\label{ProbabilisticCor}
@@
 
-Thus, drawing the dictionary and sparse codes from any continuous probability distribution almost certainly generates data with a stable sparse representation.
+Thus, drawing the dictionary and sparse coefficients from any continuous probability distribution almost certainly generates data with a stable sparse representation.
 
-We remark that these results have a potential application to theoretical neuroscience by mathematically justifying one of the few hypothesized theories of bottleneck communication between sparsely active neural populations \cite{Isely10}.
-
-\begin{proposition}\label{neuroprop}
-Sparse neural population activity is recoverable from noisy random linear compression by any method that solves Prob.~\ref{DeterministicUniquenessTheorem} or \ref{SLCopt}; in particular, via biophysically plausible unsupervised sparse coding (e.g., \cite{rehnsommer2007, rozell2007neurally, pehlevan2015normative}).
-\end{proposition}
 %\cite{rehnsommer2007, rozell2007neurally, ganguli2012compressed, hu2014hebbian}
 
-We close this section with comments on optimality.
+We close this section with some comments on optimality.
 Our linear scaling for $\varepsilon$ in \eqref{epsdel} is essentially optimal (e.g., see \cite{arias2013fundamental}), but a basic open problem remains: how many samples are necessary to determine the sparse coding model?
@@
 
-We now begin our proof of Thm.~\ref{DeterministicUniquenessTheorem} by showing how dictionary recovery \eqref{Cstable} already implies sparse code recovery \eqref{b-PDa} when \mbox{$\varepsilon < L_{2k}(\mathbf{A}) / C_1$} (provided $\mathbf{A}$ satisfies \eqref{SparkCondition}), temporarily assuming (without loss of generality) that $\overline m = m$.
+We begin our proof of Thm.~\ref{DeterministicUniquenessTheorem} by showing how dictionary recovery \eqref{Cstable} already implies sparse code recovery \eqref{b-PDa} when \mbox{$\varepsilon < L_{2k}(\mathbf{A}) / C_1$} (provided $\mathbf{A}$ satisfies \eqref{SparkCondition}), temporarily assuming (without loss of generality) that $\overline m = m$.
 For $2k$-sparse $\mathbf{x} \in \mathbb{R}^m$, the triangle inequality gives \mbox{$\|(\mathbf{A}-\mathbf{BPD})\mathbf{x}\|_2  \leq C_1\varepsilon \|\mathbf{x}\|_1 \leq C_1 \varepsilon \sqrt{2k}  \|\mathbf{x}\|_2$}.
@@
 
-\begin{proof}[Proof (sketch) of Thm.~\ref{robustPolythm}]
-Let $\textbf{M}$ be the matrix with columns $\mathbf{A}\mathbf{x}_i$, $i \in [N]$.
+%\begin{proof}[Proof (sketch) of Thm.~\ref{robustPolythm}]
+%Let $\textbf{M}$ be the matrix with columns $\mathbf{A}\mathbf{x}_i$, $i \in [N]$.
 Consider the polynomial $\prod_{S \in {[N] \choose 2k}} \sum_{S' \in {[n] \choose 2k}} (\det \textbf{M}_{S',S})^2$ in the indeterminate entries of $\mathbf{A}$ and $\mathbf{x}_i$, with notation as in Sec.~\ref{Results}.
-It can be checked that when this polynomial is nonzero for a substitution of real numbers for the indeterminates, all of the genericity requirements on $\mathbf{A}$ and $\mathbf{x}_i$ in our proofs of stability in Thm.~\ref{DeterministicUniquenessTheorem} are satisfied (in particular, the spark condition \eqref{SparkCondition} on $\mathbf{A}$).
-\end{proof}
+%It can be checked that when this polynomial is nonzero for a substitution of real numbers for the indeterminates, all of the genericity requirements on $\mathbf{A}$ and $\mathbf{x}_i$ in our proofs of stability in Thm.~\ref{DeterministicUniquenessTheorem} are satisfied (in particular, the spark condition \eqref{SparkCondition} on $\mathbf{A}$).
+%\end{proof}
 
-\begin{proof}[Proof (sketch) of Cor.~\ref{ProbabilisticCor}]
-First, note that if a set of measure spaces $\{(X_{\ell}, \Sigma_{\ell}, \nu_{\ell})\}_{\ell=1}^p$ has that $\nu_{\ell}$ is absolutely continuous with respect to $\mu$ for all $\ell \in [p]$, where $\mu$ is the standard Borel measure on $\mathbb{R}$, then the product measure $\prod_{\ell=1}^p \nu_{\ell}$ is absolutely continuous with respect to the standard Borel product measure on $\mathbb{R}^p$.
+%\begin{proof}[Proof (sketch) of Cor.~\ref{ProbabilisticCor}]
+%First, note that if a set of measure spaces $\{(X_{\ell}, \Sigma_{\ell}, \nu_{\ell})\}_{\ell=1}^p$ has that $\nu_{\ell}$ is absolutely continuous with respect to $\mu$ for all $\ell \in [p]$, where $\mu$ is the standard Borel measure on $\mathbb{R}$, then the product measure $\prod_{\ell=1}^p \nu_{\ell}$ is absolutely continuous with respect to the standard Borel product measure on $\mathbb{R}^p$.
 % for space:  (e.g.,  \cite{folland2013real}).
-By Thm.~\ref{robustPolythm}, there is a polynomial that is nonzero when $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$; in particular, stability holds almost surely.
-\end{proof}
+%By Thm.~\ref{robustPolythm}, there is a polynomial that is nonzero when $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$; in particular, stability holds almost surely.
+%\end{proof}
 
@@
 A motivation for this work was the emergence of seemingly characteristic representations from sparse coding models fit to natural data, despite the varied assumptions underlying the many algorithms in current use.
-To this end, we have taken an important step toward unifying the great number of publications on the topic by demonstrating very general, deterministic conditions under which identification of parameters in this model is not only possible but also robust to the inevitable uncertainty permeating measurement and model choice.
+To this end, we have taken an important step toward unifying the many publications on the topic by demonstrating general sufficient, deterministic conditions under which identification of parameters in this model is not only possible but also robust to uncertainty in measurement and model choice.
 
@@
 
-An immediate application of our theoretical work is Prop.~\ref{neuroprop}, which certifies the validity of a theory of biologically-plausible bottleneck communication in the brain: that sparse coding in a compressed space of neural activity can recover sparse codes sent through a randomly-constructed (but unknown) noisy wiring bottleneck \cite{Isely10}.\footnote{We refer the reader to \cite{ganguli2012compressed} for more on interactions between dictionary learning and neuroscience.}
+Our theoretical work mathematically justifies one of the few hypothesized theories of bottleneck communication in the brain \cite{Isely10}: that sparse neural population activity is recoverable from its noisy linear compression through a randomly constructed (but unknown) wiring bottleneck by any biologically plausible unsupervised sparse coding method that solves Prob.~\ref{DeterministicUniquenessTheorem} or \ref{SLCopt} (e.g., \cite{rehnsommer2007, rozell2007neurally, pehlevan2015normative}).\footnote{We refer the reader to \cite{ganguli2012compressed} for more on interactions between dictionary learning and neuroscience.}
 
@@
 We incorporate this idea into a fundamental lemma in matrix theory (Lem.~\ref{MainLemma}) that draws upon the definition of a new matrix lower bound induced by a hypergraph.
-Insights enabled by our combinatorial approach include: 1) a subset of dictionary elements is recoverable even if dictionary size is overestimated, 2) data require only a polynomial number of distinct sparse supports, and 3) the spark condition is not a necessary property of recoverable dictionaries.
+Novel insights enabled by our combinatorial approach include: 1) a subset of dictionary elements is recoverable even if dictionary size is overestimated, 2) data require only a polynomial number of distinct sparse supports, and 3) recoverable dictionaries need not necessarily satisfy the spark condition.
 

### 2019-05-06 manuscripts/IEEE/final_submission.tex
Add files via upload

@@
-% TODO: cite Fritz l0 paper in introduction for seemingly characteristic structure?
+% TODO: cite Fritz l0 paper in introduction for seemingly characteristic structure? Use those mentioned in PNAS response?
+% Make L_H a definition..? Change def of L to be 1-norm so we don't need these sqrt k's?
+% When do we have polynomial complexity? Is it worth saying something about this for cyclic order (e.g. convolutions?)
+% mention regularity is probably not necessary
+% make theorem 3 a corollary?
+% have i talked about making deterministic A?
+(see reviewer comment, and comment about easily meeting thm 1 conditions w deterministic construction).
+also after f(A).
+we make L_2k(a) with vandermonde, clarify this is way more than necessary...but it is necessary if we care about sparse coefficient recovery too, which is part of df of stable sparse representation.
+% IS THEOREM 3 AND ITS COROLLARY CORRECTLY STATED??
 
@@
 Learning optimal dictionaries for sparse coding has exposed characteristic sparse features of many natural signals.
-However, universal conditions guaranteeing the consistency of these learned features in the presence of measurement noise have yet to be stated.
-Here, we prove very generally that optimal dictionaries and sparse codes are uniquely and stably determined up to measurement error for all diverse enough datasets generated by the sparse coding model.
+However, universal conditions guaranteeing the stability of these learned features in the presence of measurement noise have yet to be described.
+Here, we prove very generally that optimal dictionaries and sparse codes are unique up to measurement error for all diverse enough datasets generated by the sparse coding model.
 Applications are given to data analysis, engineering, and neuroscience.
@@
 \section{Introduction}\label{Intro}
+%\IEEEPARstart{L}{earning} sparse representations of data has become an important step in modern solutions to problems in signal processing and pattern analysis. 
+% \cite{sato1975method}
+\IEEEPARstart{A}{}common contemporary approach to problems in signal processing and pattern analysis is to view each of $N$ observed $n$-dimensional signal samples as a (noisy) linear combination of at most $k$ elementary waveforms drawn from some unknown ``dictionary" of size $m \ll N$ (see \cite{Zhang15} for a comprehensive review of this and related models).
+Optimizing dictionaries subject to this and related sparsity constraints has revealed seemingly characteristic sparse structure in several signal classes of current interest (e.g., in vision \cite{wang2015sparse}).
+Of particular note are the seminal works in the field \cite{Olshausen96, hurri1996image, bell1997independent, van1998independent}, which demonstrated that such dictionaries optimized with respect to small patches of ``natural" images share qualitative similarities with linear filters fit to the response properties of simple-cell neurons in mammalian visual cortex.
+Curiously, these waveforms (e.g., ``Gabor'' wavelets) appear in dictionaries learned by a variety of sparse coding algorithms trained over different natural image datasets; as such, it appears these latent features may be in some sense canonical \cite{donoho2001can}.
 
-% \cite{sato1975method}
-\IEEEPARstart{A}{}common assumption underlying contemporary solutions to problems in signal processing and pattern analysis is that each of $N$ observed $n$-dimensional signal is a (noisy) linear combination of at most $k$ elementary waveforms drawn from some unknown ``dictionary" of size $m \ll N$ (see \cite{Zhang15} for a comprehensive review of this and related models).
-Approximate solutions to inverse problems with these constraints and related sparsity constraints have revealed seemingly characteristic structure in several signal classes of current interest (e.g., in vision \cite{wang2015sparse}).
-Of particular note are the seminal works, which demonstrate that such dictionaries optimized with respect to small patches of natural images share qualitative features to linear filters fit to the response properties of simple-cell neurons in mammalian visual cortex \cite{Olshausen96, hurri1996image, bell1997independent, van1998independent}.
-Curiously, these waveforms (e.g., ``Gabor'' wavelets) appear in dictionaries learned by a variety of algorithms trained over different natural image datasets; as such, it appears these latent waveforms may be in some sense canonical \cite{donoho2001can}.
-
-Motivated by these discoveries and earlier work which outlined a theory of communication between sparsely active neural populations through a wiring bottleneck \cite{Isely10}, we address when dictionaries optimized to induce sparse representations are indeed identifiable from data.
-Answers to this question may have valuable implications in practice, for instance in justifying the identification of forged paintings by their anomalous sparse representations \cite{hughes2010}.
-While several algorithms have recently been proposed which provably recover unique latent dictionaries under specific conditions (see \cite[Sec.~I-E]{Sun16} for a summary of the state-of-the-art), few theorems can be cited to justify the consistency of inference under this model of data more broadly.
-In particular, a universal guarantee of the uniqueness and stability of learned sparse representations in the context of noise has yet to emerge in the literature.
+Motivated by these discoveries and more recent work linked to the young field of ``compressive sensing" which proposed a theory of information transmission through random wiring bottlenecks in the brain \cite{Isely10}, we address when optimal dictionaries for sparse representation are indeed identifiable from data.
+Answers to this question may also have relevant implications in practice; for example, in justifying the identification of forged paintings by their anomalous sparse representations \cite{hughes2010}, or [more citations?
+kinda weak imo].
+While several algorithms which provably recover unique latent dictionaries under specific conditions have recently been proposed (see \cite[Sec.~I-E]{Sun16} for a summary of the state-of-the-art), few theorems can be invoked to justify the consistency of inference under this model of data more broadly.
+To our knowledge, a universal guarantee of the uniqueness and stability of learned dictionaries and the sparse representations they induce over noisy data has yet to appear in the literature.
 
@@
 More specifically,  we show that dictionaries injective on a sparse domain are identifiable from \mbox{$N = m(k-1){m \choose k} + m$} noisy sparse linear combinations of their columns up to an error that is linear in the noise (Thm.~\ref{DeterministicUniquenessTheorem}).
-In fact, provided $n \geq \min(2k,m)$, in almost all cases the problem is well-posed (as per Hadamard \cite{Hadamard1902}) given enough data (Cor.~\ref{ProbabilisticCor}).
-Similar guarantees can also be made for the related and perhaps more common optimization problem which instead seeks a dictionary minimizing the average sparsity of induced sparse codes over all data samples.
-Importantly, in both cases our explicit, universal guarantees apply without the imposition of \emph{any} constraints on the dictionaries of proposed solutions (e.g.
-that they, too, be injective over some sparse domain) beyond an upper bound on dictionary size, which is necessary in any case to avoid a trivial solution (e.g.
-letting $m = N$).
+In fact, provided $n \geq \min(2k,m)$, in almost all cases the problem is well-posed\footnote{as per Hadamard \cite{Hadamard1902}} given enough data (Cor.~\ref{ProbabilisticCor}).
+These guarantees also hold for a related (and perhaps more commonly posed) optimization problem which instead seeks a dictionary minimizing the average number of elementary waveforms required to reconstruct each sample of the dataset.
+Importantly, in both cases our explicit, universal guarantees apply without the imposition of \emph{any} constraints on learned dictionaries  (e.g.
+that they, too, be injective over some domain) beyond an upper bound on dictionary size, which is necessary in any case to avoid a trivial solution (e.g.
+allowing for $m = N$ elementary waveforms).
 %That is, every pair of solutions of comparable size has some number of dictionary elements in common (up to noise), and similarly so for the coefficients of sparse codes they induce.
 
-To state things properly, let $\mathbf{A} \in \mathbb R^{n \times m}$ be a matrix with columns $\mathbf{A}_j$ ($j = 1,\ldots,m$) and let dataset $Z$ consist of measurements:
+To state things precisely, let $\mathbf{A} \in \mathbb R^{n \times m}$ be a matrix with columns $\mathbf{A}_j$ ($j = 1,\ldots,m$) and let dataset $Z$ consist of measurements:
 \begin{align}\label{LinearModel}
@@
 \end{align}
-for $k$-\emph{sparse} $\mathbf{x}_i \in \mathbb{R}^m$ having at most $k<m$ nonzero entries and \emph{noise} $\mathbf{n}_i \in \mathbb{R}^n$, with bounded norm $\| \mathbf{n}_i \|_2 \leq  \eta$ representing our combined worst-case uncertainty in  measuring $\mathbf{A}\mathbf{x}_i$.
+for $k$-\emph{sparse} $\mathbf{x}_i \in \mathbb{R}^m$ having at most $k<m$ nonzero entries and \emph{noise} $\mathbf{n}_i \in \mathbb{R}^n$, with bounded norm $\| \mathbf{n}_i \|_2 \leq  \eta$ representing our worst-case uncertainty\footnote{This captures uncertainty in model parameters $\mathbf{A}$ and $\mathbf{x}_i$ in addition to external sources of measurement error.} in measuring the product $\mathbf{A}\mathbf{x}_i$.
 The first mathematical problem we consider is:
@@
 \begin{problem}\label{InverseProblem}
-Find a real matrix $\mathbf{B}$ and $k$-sparse $\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N$ satisfying $\|\mathbf{z}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \eta$ for all $i$.
+Find a real matrix $\mathbf{B}$ and $k$-sparse $\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N$ that satisfy $\|\mathbf{z}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \eta$ for all $i$.
 \end{problem}
 
-Note there is some ambiguity in this problem statement, as any particular solution actually represents infinitely many alternative solutions $\mathbf{BPD}$ and $\mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_1, \ldots, \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_N$ parametrized by a choice of permutation matrix $\mathbf{P}$ and invertible diagonal matrix $\mathbf{D}$.
-Previous theoretical work addressing the noiseless case $\eta =0$ (e.g., \cite{li2004analysis, Georgiev05, Aharon06, Hillar15}) for matrices $\mathbf{B}$ having $m$ columns has shown that the solution to Prob.~\ref{InverseProblem}, when it exists, is unique up to these labeling and scaling ambiguities provided the $\mathbf{x}_i$ are sufficiently diverse and the matrix $\mathbf{A}$ satisfies the \textit{spark condition}:
+Note that, stated as such, every solution to this problem represents infinitely many equivalent alternatives $\mathbf{BPD}$ and $\mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_1, \ldots, \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_N$ parametrized by a choice of permutation matrix $\mathbf{P}$ and invertible diagonal matrix $\mathbf{D}$.
+Equating these alternatives amounts to identifying a set of elementary waveforms (the columns of $\mathbf{B}$)  up to some arbitrary scale and their associated sparse coefficients (the entries of $\mathbf{x}_i$) for reconstructing each data point $\mathbf{z}_i$.
+Previous theoretical work addressing the noiseless case $\eta =0$ (e.g., \cite{li2004analysis, Georgiev05, Aharon06, Hillar15}) for matrices $\mathbf{B}$ having $m$ columns has shown that the solution to Prob.~\ref{InverseProblem}, when it exists, is unique up to these equivalent labeling and scaling ambiguities provided the $\mathbf{x}_i$ are sufficiently diverse and the matrix $\mathbf{A}$ satisfies the \textit{spark condition}:
 \begin{align}\label{SparkCondition}
@@
 To see how Prob.
-\ref{InverseProblem} motivates this definition, suppose that $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$ and fix $\delta_1, \delta_2$ to be the desired accuracy of recovery in \eqref{def1}.
+\ref{InverseProblem} motivates this definition, suppose that $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$ and fix $\delta_1, \delta_2$ to be the desired accuracies of recovery in \eqref{def1}.
 Now, consider any dataset $Z$ generated as in \eqref{LinearModel} with $\eta \leq \frac{1}{2} \varepsilon(\delta_1, \delta_2)$.
-From the triangle inequality, it follows that any $n \times m$ matrix $\mathbf{B}$ and $k$-sparse $\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N$ solving Prob.~\ref{InverseProblem} are necessarily within $\delta_1, \delta_2$ of the original dictionary $\mathbf{A}$ and codes $\mathbf{x}_1, ..., \mathbf{x}_N$, respectively.\footnote{The different norms for the dictionary and codes in \eqref{def1} are meant only to reflect their typically distinct semantics in modeling.}
+It follows from the triangle inequality that any $n \times m$ matrix $\mathbf{B}$ and $k$-sparse $\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N$ solving Prob.~\ref{InverseProblem} are necessarily within $\delta_1$ and $\delta_2$ of the original dictionary $\mathbf{A}$ and codes $\mathbf{x}_1, ..., \mathbf{x}_N$, respectively.\footnote{We should mention the different norms measuring recovery in \eqref{def1} are meant only to reflect the typically distinct semantics of the dictionary and sparse codes in modeling data.}
 
-In the next section, we give a precise statement of our main result (Thm.~\ref{DeterministicUniquenessTheorem}) from which an explicit form for $\varepsilon(\delta_1, \delta_2)$ may be derived.
-We then extend our guarantees to the following more common formulation of the dictionary learning problem as one of minimizing the total (or equivalently, the mean) number of non-zero entries in the sparse codes (Thm.~\ref{SLCopt}):
+In the next section, we give precise statements of our main result (Thm.~\ref{DeterministicUniquenessTheorem}), from which we have derived an explicit form for $\varepsilon(\delta_1, \delta_2)$.
+We then extend the same guarantees to the following alternate formulation of the dictionary learning problem as one of minimizing the total (or equivalently, the mean) number of non-zero entries in the sparse codes (Thm.~\ref{SLCopt}):
 
@@
 \end{problem}
-
-The section closes with some brief arguments extending Thm.~\ref{DeterministicUniquenessTheorem} to data and dictionaries drawn from probability distributions (Cor.~\ref{ProbabilisticCor}).
-The more involved proofs of Thms.~\ref{DeterministicUniquenessTheorem} and~\ref{SLCopt} are defered to Sec.~\ref{DUT}, following some necessary preamble stating definitions and a useful result in combinatorial matrix analysis (Lem.~\ref{MainLemma}, proven in the Appendix).
+We also give brief arguments adapting our results to data and dictionaries drawn from probability distributions (Cor.~\ref{ProbabilisticCor}).
+We defer to Sec.~\ref{DUT} the more technically involved proofs of Thms.~\ref{DeterministicUniquenessTheorem} and ~\ref{SLCopt}, following some necessary definitions and a useful result in combinatorial matrix analysis (Lem.~\ref{MainLemma}).
 Finally, we discuss in Sec.~\ref{Discussion} some theoretical and practical applications of our main mathematical findings.
+The Appendix contains a proof of Lem.~\ref{MainLemma}.
 
@@
 
-To state our results precisely, we must first identify some combinatorial criteria on the supports\footnote{Recall a vector $\mathbf{x}$ is said to be \emph{supported} in $S$ when $\mathbf{x} \in \text{\rm span}\{\mathbf{e}_j: j\in S\}$, the $\mathbf{e}_j$ forming the standard column basis.} of sparse vectors.
+A detailed statement of our results requires that we first identify some combinatorial criteria on the supports\footnote{Recall a vector $\mathbf{x}$ is said to be \emph{supported} in $S$ when $\mathbf{x} \in \text{\rm span}\{\mathbf{e}_j: j\in S\}$, the $\mathbf{e}_j$ forming the standard column basis.} of sparse vectors.
 Let $\{1, \ldots, m\}$ be denoted $[m]$, its power set $2^{[m]}$, and ${[m] \choose k}$ the set of subsets of $[m]$ of size $k$.
-A \emph{hypergraph} on vertices $[m]$  is any subset $\mathcal{H} \subseteq 2^{[m]}$.
+A \emph{hypergraph} on vertices $[m]$  is just any subset $\mathcal{H} \subseteq 2^{[m]}$.
 We say $\mathcal{H}$ is \textit{$k$-uniform} when in fact $\mathcal{H} \subseteq {[m] \choose k}$.
-The \emph{degree} $\deg_\mathcal{H}(i)$ of a node $i \in [m]$ is the number of sets in $\mathcal{H}$ that contain $i$, and $\mathcal{H}$ is labeled as \emph{regular} when for some $r$ we have $\deg_\mathcal{H}(i) = r$ for all $i$ (given such an $r$, we say $\mathcal{H}$ is \textit{$r$-regular}).
+The \emph{degree} $\deg_\mathcal{H}(i)$ of a node $i \in [m]$ is the number of sets in $\mathcal{H}$ that contain $i$, and we say $\mathcal{H}$ is \emph{regular} when for some $r$ we have $\deg_\mathcal{H}(i) = r$ for all $i$ (given such an $r$, we say $\mathcal{H}$ is \textit{$r$-regular}).
 We also write $2\mathcal{H} := \{ S \cup S': S, S' \in \mathcal{H}\}$.
@@
 Next, we describe a quantitative generalization of the spark condition.
-The \emph{lower bound} of a matrix $\mathbf{M} \in \mathbb R^{n \times m}$ is the largest $\alpha$ with \mbox{$\|\mathbf{M}\mathbf{x}\|_2 \geq \alpha\|\mathbf{x}\|_2$} for all $\mathbf{x} \in \mathbb{R}^m$ \cite{Grcar10}.
+The \emph{lower bound} of a real $n \times m$ matrix $\mathbf{M}$ is the largest $\alpha$ with \mbox{$\|\mathbf{M}\mathbf{x}\|_2 \geq \alpha\|\mathbf{x}\|_2$} for all $\mathbf{x} \in \mathbb{R}^m$ \cite{Grcar10}.
 By compactness of the unit sphere, every injective linear map has a positive lower bound; hence, if $\mathbf{M}$ satisfies \eqref{SparkCondition} then each submatrix formed from $2k$ of its columns or less has a strictly positive lower bound.
 
-We now generalize the matrix lower bound to apply only over a restricted union of subspaces\footnote{See \cite{vidal2005generalized} for an overview of union of subspace modeling.} associated with a hypergraph $\mathcal{H} \subseteq {[m] \choose k}$.
-Let $\mathbf{M}_S$ denote the submatrix formed by the columns of $\mathbf{M}$ indexed by $S \subseteq [m]$, with $\mathbf{M}_\emptyset := \mathbf{0}$.
-(In the sections that follow, we will write $\bm{\mathcal{M}}_S$ to denote the column-span of a submatrix $\mathbf{M}_S$, and $\bm{\mathcal{M}}_\mathcal{G}$ to denote $\{\bm{\mathcal{M}}_S\}_{S \in \mathcal{G}}$.) We define:
+We generalize the matrix lower bound for our purposes by considering only the spans of certain submatrices\footnote{See \cite{vidal2005generalized} for an overview of the closely associated ``union of subspaces" model.} associated with a hypergraph $\mathcal{H} \subseteq {[m] \choose k}$ over column indices.
+Letting $\mathbf{M}_S$ denote the submatrix formed by the columns of $\mathbf{M}$ indexed by $S \subseteq [m]$, with $\mathbf{M}_\emptyset := \mathbf{0}$ (in the sections that follow, we will write $\bm{\mathcal{M}}_S$ to denote the column-span of a submatrix $\mathbf{M}_S$, and $\bm{\mathcal{M}}_\mathcal{G}$ to denote $\{\bm{\mathcal{M}}_S\}_{S \in \mathcal{G}}$), we define:
 %\begin{align*} 
@@
 \begin{align}\label{Ldef}
-L_\mathcal{H}(\mathbf{M}) := \frac{1}{\sqrt{k}} \min \left\{ \frac{\|\mathbf{M}_S\mathbf{x}\|_2}{ \|\mathbf{x}\|_2} : S \in \mathcal{H}, \ \ \mathbf{x} \in \mathbb{R}^{|S|} \right\}.
+L_\mathcal{H}(\mathbf{M}) := \frac{1}{\sqrt{k}} \min \left\{ \frac{\|\mathbf{M}_S\mathbf{x}\|_2}{ \|\mathbf{x}\|_2} : S \in \mathcal{H}, \ \ \mathbf{x} \in \mathbb{R}^{|S|} \right\},
 \end{align} 
 %
-We write $L_{k}$ in place of $L_\mathcal{H}$ when $\mathcal{H} = {[m] \choose k}$, and note that $1 - \sqrt{k} L_k(\mathbf{M})$ is known as the asymmetric lower restricted isometry constant for matrices $\mathbf{M}$ with unit $\ell_2$-norm columns \cite{Blanchard2011}.
-As explained previously, we have $L_{2k}(\mathbf{M}) > 0$ for all $\mathbf{M}$ satisfying \eqref{SparkCondition}.
-Clearly, $L_{k'}(\mathbf{M}) \geq L_k(\mathbf{M})$ whenever $k' \leq k$ and, by the same token, any $k$-uniform $\mathcal{H}$ satisfying $\cup \mathcal{H} = [m]$ has $L_2 \geq L_{2\mathcal{H}} \geq L_{2k}$.
+writing also $L_{k}$ in place of $L_\mathcal{H}$ when $\mathcal{H} = {[m] \choose k}$.\footnote{We note that \mbox{$1 - \sqrt{k} L_k(\mathbf{M})$} is known in the compressive sensing literature as the asymmetric lower restricted isometry constant for matrices $\mathbf{M}$ with unit $\ell_2$-norm columns \cite{Blanchard2011}}  As explained previously, by compactness we have $L_{2k}(\mathbf{M}) > 0$ for all $\mathbf{M}$ satisfying \eqref{SparkCondition}.
+Clearly, $L_{\mathcal{H}'}(\mathbf{M}) \geq L_\mathcal{H}(\mathbf{M})$ whenever $\mathcal{H}' \subseteq \mathcal{H}$ and, by the same token, any $k$-uniform $\mathcal{H}$ satisfying $\cup \mathcal{H} = [m]$ has $L_2 \geq L_{2\mathcal{H}} \geq L_{2k}$.
 
-Finally, we mention that a set of vectors sharing support $S$ are said to be in \emph{general linear position} when any $|S|$ of them form a linearly independent set.
+Finally, we mention that a set of vectors sharing a support $S$ are said to be in \emph{general linear position} when any $|S|$ of them form a linearly independent set.
 
-We are now in a position to give a precise statement of our main result, though for expository purposes we will leave the quantity $C_1$ (a function of $\mathbf{A}$, $\mathbf{x}_1, ..., \mathbf{x}_N$, and $\mathcal{H}$) undefined until Eq.~\eqref{Cdef1} of Sec.~\ref{DUT}.
-We state here once that all of our theorems assume matrices consist of real numbers.
+We are now in a position to state our main result, though for expository purposes we will leave the quantity $C_1$ (a function of $\mathbf{A}$, $\mathbf{x}_1, ..., \mathbf{x}_N$, and $\mathcal{H}$) undefined until Eq.~\eqref{Cdef1} of Sec.~\ref{DUT}.
+We state here once that all of our theorems assume matrices and vectors consist of real numbers.
 
@@
 \begin{theorem}\label{DeterministicUniquenessTheorem}
-Fix an $n \times m$ matrix $\mathbf{A}$ with $L_{2\mathcal{H}}(\mathbf{A}) > 0$ for an $r$-regular $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP.
-If \mbox{$\{\mathbf{x}_1, \ldots, \mathbf{x}_N\} \subset \mathbb{R}^m$} contains, for each $S \in \mathcal{H}$, more than $(k-1){m \choose k}$ $k$-sparse vectors in general linear position supported in $S$, then there is $C_1 > 0$ with the following holding for all%\footnote{The condition $\varepsilon < L_2(\mathbf{A}) /C_1$ is necessary; otherwise,  with \mbox{$\mathbf{A}$ = $\mathbf{I}$} and $\mathbf{x}_i = \mathbf{e}_i$, there is a matrix $\mathbf{B}$ and $1$-sparse $\mathbf{\overline{x}}_i$ with $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline{x}}_i \|_2 \leq \varepsilon$ that nonetheless violates \eqref{Cstable}.} $\varepsilon < L_{2}(\mathbf{A}) / C_1$:
+Fix integers $n, k, m$ and $\overline m$.
+Let the $n \times m$ matrix $\mathbf{A}$ satisfy $L_{2\mathcal{H}}(\mathbf{A}) > 0$ for some $r$-regular $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP.
+If $k$-sparse \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N$} include more than $(k-1){\overline m \choose k}$ vectors in general linear position supported in each $S \in \mathcal{H}$, then there is $C_1 > 0$ (given by \eqref{Cdef1}) for which the following holds for all%\footnote{The condition $\varepsilon < L_2(\mathbf{A}) /C_1$ is necessary; otherwise,  with \mbox{$\mathbf{A}$ = $\mathbf{I}$} and $\mathbf{x}_i = \mathbf{e}_i$, there is a matrix $\mathbf{B}$ and $1$-sparse $\mathbf{\overline{x}}_i$ with $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline{x}}_i \|_2 \leq \varepsilon$ that nonetheless violates \eqref{Cstable}.} $\varepsilon < L_{2}(\mathbf{A}) / C_1$:
 \footnote{Note that the condition $\varepsilon < L_2(\mathbf{A}) /C_1$ is necessary; otherwise, with \mbox{$\mathbf{A}$ = $\mathbf{I}$} (the identity matrix) and $\mathbf{x}_i = \mathbf{e}_i$, the matrix $\mathbf{B} = \left[\mathbf{0}, \frac{1}{2}(\mathbf{e}_1 + \mathbf{e}_2), \mathbf{e}_3, \ldots, \mathbf{e}_{m} \right]$ and sparse codes $\mathbf{\overline x}_i = \mathbf{e}_2$ for $i = 1, 2$ and $\mathbf{\overline x}_i = \mathbf{e}_i$ for $i \geq 3$ satisfy $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline{x}}_i \|_2 \leq \varepsilon$ but nonetheless violate \eqref{Cstable}.} $\varepsilon < L_{2}(\mathbf{A}) / C_1$:
 
-Every $n \times \overline m$ matrix $\mathbf{B}$ for which there are $k$-sparse $\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N$ satisfying \mbox{$\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \varepsilon$} for all $i$ has $\overline m \geq m$ and, provided $\overline m < mr / (r-1)$,
+Every $n \times \overline m$ matrix $\mathbf{B}$ for which there are $k$-sparse $\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N$ satisfying \mbox{$\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \varepsilon$} for $i = 0, \ldots, N$ has $\overline m \geq m$, and provided $\overline m < mr / (r-1)$, there is a permutation matrix $\mathbf{P}$ and an invertible diagonal matrix $\mathbf{D}$ such that:
 \begin{align}\label{Cstable}
-\|\mathbf{A}_j- \mathbf{B}_{\overline J} \mathbf{PD}_j\|_2 \leq C_1 \varepsilon, \ \ \text{for all } j \in J,
+\|\mathbf{A}_j- \mathbf{B}_{\overline J} \mathbf{PD}_j\|_2 \leq C_1 \varepsilon \ \ \text{for all } j \in J
 \end{align}
 %
-for some $\overline J \subseteq [\overline m]$ and $J \subseteq [m]$ of size \mbox{$m - (r-1)(\overline m - m)$}, a permutation matrix $\mathbf{P}$, and an invertible diagonal matrix $\mathbf{D}$. 
+for some $J$ and $\overline J$ both of size \mbox{$m - (r-1)(\overline m - m)$}. 
 % $\overline m - r(\overline m - m)$
 
-Moreover, if $A$ satisfies \eqref{SparkCondition} and $\varepsilon < L_{2k}(\mathbf{A}) / C_1$, then $L_{2k}(\mathbf{B}\mathbf{PD}) \geq L_{2k}(\mathbf{A}) - C_1 \varepsilon$ and:
+Moreover, if $\mathbf{A}$ satisfies \eqref{SparkCondition} and $\varepsilon < L_{2k}(\mathbf{A}) / C_1$, then $\mathbf{B}$ also satisfies \eqref{SparkCondition} with $L_{2k}(\mathbf{B}\mathbf{PD}) \geq L_{2k}(\mathbf{A}) - C_1 \varepsilon$ and for all $i \in [N]$:
 \begin{align}\label{b-PDa}
 %\|\mathbf{x}^J_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}^{\overline J}_i\|_1 &\leq  \left( \frac{ 1+C_1 \|\mathbf{x}^{J}_i\|_1 }{ L_{2k}(\mathbf{A}) -  C_1\varepsilon } \right) \varepsilon \ \  \text{for $i \in [N]$}.
-\|(\mathbf{x}_i)_J - \left(\mathbf{D}^{-1}\mathbf{P}^{\top}\right)_{\overline J}(\mathbf{\overline x}_i)_{\overline J}|_1 &\leq  \left( \frac{ 1+C_1 \|\mathbf{x}_i\|_1 }{ L_{2k}(\mathbf{A}) -  C_1\varepsilon } \right) \varepsilon, \ \  \text{for $i \in [N]$},
+\|(\mathbf{x}_i)_J - \left(\mathbf{D}^{-1}\mathbf{P}^{\top}\right)_{\overline J}(\mathbf{\overline x}_i)_{\overline J}\|_1 &\leq  \left( \frac{ 1+C_1 \|\mathbf{x}_i\|_1 }{ L_{2k}(\mathbf{A}) -  C_1\varepsilon } \right) \varepsilon,
 \end{align}
 %
-where $(\mathbf{x}_i)_J$ and $(\mathbf{\overline x}_i)_{\overline J}$ here represent subvectors formed from restricting to entries indexed by $J$ and $\overline J$, respectively. 
+where $(\mathbf{x}_i)_J$ and $(\mathbf{\overline x}_i)_{\overline J}$ here represent subvectors formed from restricting to coefficients indexed by $J$ and $\overline J$, respectively. 
 \end{theorem}
@@
 %To be clear, the implication of Thm.~\ref{DeterministicUniquenessTheorem} is that $Y = \{\mathbf{Ax}_1, \ldots, \mathbf{Ax}_N\}$ has a stable $k$-sparse representation in $\mathbb{R}^m$, with \eqref{def1} guaranteed provided $\varepsilon$ in Def.~\ref{maindef} does not exceed:
-In words, Thm.~\ref{DeterministicUniquenessTheorem} says that the smaller the regularity $r$ or difference $\overline m - m$ between the assumed and actual number of latent dictionary elements, the more columns and coefficients of the original dictionary $\mathbf{A}$ and sparse codes $\mathbf{x}_i$ are guaranteed to be contained (up to noise) in the appropriately scaled recovered dictionary $\mathbf{B}$ and codes $\mathbf{\overline x}_i$, respectively.
+In words, Thm.~\ref{DeterministicUniquenessTheorem} says that the smaller the regularity $r$ of $\mathcal{H}$ or the difference $\overline m - m$ between the assumed and actual number of columns in the latent dictionary, the more columns and coefficients of the original dictionary $\mathbf{A}$ and sparse codes $\mathbf{x}_i$ are guaranteed to be contained (up to noise) in the appropriately scaled recovered dictionary $\mathbf{B}$ and codes $\mathbf{\overline x}_i$, respectively.
 In the particular case when $\overline m = m$, the theorem directly implies that  $Y = \{\mathbf{Ax}_1, \ldots, \mathbf{Ax}_N\}$ has a stable $k$-sparse representation in $\mathbb{R}^m$, with inequalities \eqref{def1} guaranteed for $\varepsilon$ in Def.~\ref{maindef} given by:
@@
 
-We note that the assumptions of Thm.~\ref{DeterministicUniquenessTheorem} are easily met with deterministic constructions.
-In particular, sparse codes with a shared support that are in general linear position are straightforward to produce using a ``Vandermonde'' matrix construction (i.e., use the columns of the matrix $[\gamma_{i}^j]_{i,j=1}^{k,N}$, for distinct nonzero $\gamma_i$).
+We claim that the assumptions of Thm.~\ref{DeterministicUniquenessTheorem} are easily met with deterministic constructions.
+In particular, sparse codes in general linear position are straightforward to produce using a ``Vandermonde'' matrix construction (i.e.
+use the columns of the matrix $[\gamma_{i}^j]_{i,j=1}^{k,N}$, for distinct nonzero $\gamma_i$).
 % (Prob.~\ref{InverseProblem}).
@@
 \begin{corollary}\label{DeterministicUniquenessCorollary}
-Given a regular hypergraph $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP, there are $N =  |\mathcal{H}| \left[ (k-1){m \choose k} + 1  \right]$ vectors \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} such that every matrix $\mathbf{A}$ with $L_{2k}(\mathbf{A}) > 0$ generates a dataset $Y = \{\mathbf{A}\mathbf{x}_1, \ldots, \mathbf{A}\mathbf{x}_N\}$ with a stable $k$-sparse representation in $\mathbb{R}^m$ (with $\varepsilon(\delta_1,\delta_2)$ as in \eqref{epsdel}).
+Given any regular hypergraph $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP, there are $N =  |\mathcal{H}| \left[ (k-1){m \choose k} + 1  \right]$ vectors \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} such that every matrix $\mathbf{A}$ with $L_{2\mathcal{H}}(\mathbf{A}) > 0$ generates a dataset $Y = \{\mathbf{A}\mathbf{x}_1, \ldots, \mathbf{A}\mathbf{x}_N\}$ with a stable $k$-sparse representation in $\mathbb{R}^m$, with $\varepsilon(\delta_1,\delta_2)$ as in \eqref{epsdel}.
 \end{corollary}
@@
 
+%We also have the following refinement of a result in \cite{Hillar15}:
+%\begin{corollary}
+%Those square matrices $\mathbf{A}$ that satisfy \mbox{$L_{2\mathcal{H}}(\mathbf{A}) > 0$} for some regular $k$-uniform hypergraph $\mathcal{H}$ with the SIP and have the property that $\mathbf{Ax}$ is $k$-sparse for all $k$-sparse $\mathbf{x}$ with support in $\mathcal{H}$ are the matrices $\mathbf{PD}$, where $\mathbf{P}$ and $\mathbf{D}$ run over permutation and invertible diagonal matrices, respectively.
+%\end{corollary}
+
 One can also easily verify that for every $k < m$ there are regular $k$-uniform hypergraphs with the SIP besides the obvious $\mathcal{H} = {[m] \choose k}$.
-For instance, take $\mathcal{H}$ to be the $(k-1)$-regular set of consecutive intervals of length $k$ in some cyclic order on $[m]$.
+For instance, take $\mathcal{H}$ to be the $k$-regular set of consecutive intervals of length $k$ in some cyclic order on $[m]$.
 In this case, a direct consequence of Cor.~\ref{DeterministicUniquenessCorollary} is rigorous verification of the lower bound \mbox{$N = m(k-1){m \choose k} + m$} for sufficient sample size from the introduction.
-Special cases require even fewer supports, however.
-For example, if $k = \sqrt{m}$ then a 2-regular hypergraph with the SIP can be constructed as the $2k$ rows and columns formed by arranging the elements of $[m]$ into a square grid.
+Special cases allow for even smaller hypergraphs, however.
+For example, if $k = \sqrt{m}$ then a 2-regular $k$-uniform hypergraph with the SIP can be constructed as the $2k$ rows and columns formed by arranging the elements of $[m]$ into a square grid.
 
 %\cite{li2004analysis, Georgiev05, Aharon06, Hillar15}
-We should stress the point here that framing the problem in terms of hypergraphs has allowed us to show, unlike in previous works on the subject, that the matrix $\mathbf{A}$ need not satisfy \eqref{SparkCondition} to be recoverable from data.
-As an example, let $\mathbf{A} = [ \mathbf{e}_1, \ldots, \mathbf{e}_5, \mathbf{v}]$ where $\mathbf{v} = \mathbf{e}_1 + \mathbf{e}_3 + \mathbf{e}_5$, and take $\mathcal{H}$ to be all consecutive pairs of $1, ...
+We should stress the point here that framing the problem in terms of hypergraphs has allowed us to show, unlike in previous works on the subject, that the matrix $\mathbf{A}$ need not necessarily satisfy \eqref{SparkCondition} to be recoverable from data.
+As an example, let $\mathbf{A} = [ \mathbf{e}_1, \ldots, \mathbf{e}_5, \mathbf{v}]$ with $\mathbf{v} = \mathbf{e}_1 + \mathbf{e}_3 + \mathbf{e}_5$ and take $\mathcal{H}$ to be all consecutive pairs of indices $1, ...
 ,6$ arranged in cyclic order.
-Then, for $k=2$, $\mathbf{A}$ fails to satisfy \eqref{SparkCondition} while still satisfying the assumptions of Thm.~\ref{DeterministicUniquenessTheorem}.%, hence guaranteeing \eqref{Cstable} .
+Then for $k=2$, the matrix $\mathbf{A}$ fails to satisfy \eqref{SparkCondition} while still satisfying the assumptions of Thm.~\ref{DeterministicUniquenessTheorem}.%, hence guaranteeing \eqref{Cstable} .
 %(since $\{ \mathbf{A}_1, \mathbf{A}_3, \mathbf{A}_5, \mathbf{A}_6\}$ is not a linearly independent set).
@@
 A practical implication of Thm.~\ref{DeterministicUniquenessTheorem} is the following: there is an effective procedure sufficient to affirm if a proposed solution to Prob.~\ref{InverseProblem} is indeed unique (up to noise and inherent ambiguities).
-Simply check that the matrix and codes satisfy the (computable) assumptions of Thm.~\ref{DeterministicUniquenessTheorem} on $\mathbf{A}$ and the $\mathbf{x}_i$.
+One need simply check that the matrix and codes satisfy the (computable) assumptions of Thm.~\ref{DeterministicUniquenessTheorem} on $\mathbf{A}$ and the $\mathbf{x}_i$.
 In general, however, there is no efficient such procedure.
@@
 \begin{theorem}\label{SLCopt}
-If the assumptions of Thm.~\ref{DeterministicUniquenessTheorem} hold, only now with more than $(k-1)\left[ {\overline m \choose k} + |\mathcal{H}|k{\overline m \choose k-1}\right]$ vectors $\mathbf{x}_i$ supported in each $S \in \mathcal{H}$, then all solutions to Prob.~\ref{OptimizationProblem} with $\eta \leq \varepsilon / 2$ necessarily satisfy recovery inequalities \eqref{Cstable} and \eqref{b-PDa}.% of Thm.~\ref{DeterministicUniquenessTheorem}.
+Fix a matrix $\mathbf{A}$ and vectors $\mathbf{x}_i$ satisfying the assumptions of Thm.~\ref{DeterministicUniquenessTheorem}, only now with over $(k-1)\left[ {\overline m \choose k} + |\mathcal{H}|k{\overline m \choose k-1}\right]$ vectors supported in general linear position in each $S \in \mathcal{H}$.
+Every solution to Prob.~\ref{OptimizationProblem} (with $\eta \gets \varepsilon/2$) satisfies recovery guarantees \eqref{Cstable} and \eqref{b-PDa} when the corresponding bounds on $\eta$ are met.
 \end{theorem}
@@
 Let $\mathbf{A}$  be the $n \times m$ matrix of $nm$ indeterminates $A_{ij}$.
-The reader may verify that substituting real numbers for the $A_{ij}$ yields a matrix satisfying \eqref{SparkCondition} if and only if the following polynomial also evaluates to a nonzero number:
+The reader may work out for themself why substituting real numbers for the $A_{ij}$ yields a matrix satisfying \eqref{SparkCondition} if and only if the following polynomial also evaluates to a nonzero number:
 \begin{align*}
@@
 Since $f$ is analytic, having a single substitution of a real matrix $\mathbf{A}$ satisfy $f(\mathbf{A}) \neq 0$ implies that the zeroes of $f$ form a set of (Borel) measure zero.
-A representative such matrix $\mathbf{A}$ is easily constructed by adding rows of zeroes to any $\min(2k,m) \times m$ Vandermonde matrix as described previously, so that every sum in the product defining $f$ above is strictly positive.
+Such a matrix is easily constructed by adding rows of zeroes to any $\min(2k,m) \times m$ Vandermonde matrix as described previously, so that every sum in the product defining $f$ above is strictly positive.
 Almost every $n \times m$ matrix with $n \geq \min(2k,m)$ therefore satisfies \eqref{SparkCondition}.
@@
 
-A similar phenomenon applies to datasets of vectors with a stable sparse representation.
-Briefly, following the same procedure as in \cite[Sec.~IV]{Hillar15}, we may consider the ``symbolic'' dataset $Y = \{\mathbf{A}\mathbf{x}_1,\ldots,\mathbf{A} \mathbf{x}_N\}$ generated by indeterminate $\mathbf{A}$ and indeterminate $k$-sparse $\mathbf{x}_1, \ldots, \mathbf{x}_N$.
-Letting $\textbf{M}$ be the matrix with columns $\mathbf{A}\mathbf{x}_i$, $i \in [N]$, it can be checked that when $f(\mathbf{M}) \neq 0$ for a substitution of real numbers for the indeterminates, all of the assumptions on $\mathbf{A}$ and $\mathbf{x}_i$ in Thm.~\ref{DeterministicUniquenessTheorem} are satisfied; in particular, $\mathbf{A}$ satisfies \eqref{SparkCondition}.
+We claim a similar phenomenon applies to datasets of vectors with a stable sparse representation.
+Briefly, following the same procedure as in \cite[Sec.~IV]{Hillar15}, for $k < m$ and $n \geq \min(2k, m)$ we may consider the ``symbolic'' dataset $Y = \{\mathbf{A}\mathbf{x}_1,\ldots,\mathbf{A} \mathbf{x}_N\}$ generated by an indeterminate $n \times m$ matrix $\mathbf{A}$ and $m$-dimensional $k$-sparse vectors $\mathbf{x}_1, \ldots, \mathbf{x}_N$ indeterminate within their supports, which form a regular hypergraph $\mathcal{H} \subseteq {[m] \choose k}$ satisfying the SIP.
+Restricting \mbox{$(k-1){m \choose k} + 1$} indeterminate $\mathbf{x}_i$ to each support in $\mathcal{H}$, and letting $\textbf{M}$ be the $n \times N$ matrix with columns $\mathbf{A}\mathbf{x}_i$, it can be checked that when $f(\mathbf{M}) \neq 0$ for a substitution of real numbers for the indeterminates, all of the assumptions on $\mathbf{A}$ and $\mathbf{x}_i$ in Thm.~\ref{DeterministicUniquenessTheorem} are satisfied; in particular, $\mathbf{A}$ satisfies \eqref{SparkCondition}.
 We therefore have the following result:
@@
 \begin{theorem}\label{robustPolythm}
-There is a polynomial $g$ in the entries of $\mathbf{A} \in \mathbb{R}^{n \times m}$ and $\mathbf{x}_i \in \mathbb{R}^m$ with the following property:  if $g$ evaluates to a nonzero number and more than \mbox{$(k-1){m \choose k}$} of the resulting $\mathbf{x}_i$ are supported in each $S \in \mathcal{H}$ for some regular $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP, then $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$ (Def.~\ref{maindef}).
+%Let $\mathbf{A}$ and $\mathbf{x}_1, \ldots, \mathbf{x}_N$ be an indeterminate $n \times m$ matrix and sequence of $m$-dimensional vectors, respectively. 
+There is a polynomial in the entries of $\mathbf{A}$ and the $\mathbf{x}_i$ that evaluates to a nonzero number only when $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$.
 In particular, all -- except for a Borel set of measure zero -- substitutions impart to $Y$ this property.
@@
 \begin{corollary}\label{ProbabilisticCor}
-Fix $m > k$, $n \geq \min(2k, m)$, and let the entries of $\mathbf{A} \in \mathbb{R}^{n \times m}$ and $k$-sparse $\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$ be drawn independently from probability measures absolutely continuous with respect to the standard Borel measure.
-If more than $(k-1){m \choose k}$ of the vectors $\mathbf{x}_i$ are supported in each $S \in \mathcal{H}$ for a regular $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP, then $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$ with probability one.
+If the indeterminate entries of $\mathbf{A}$ and the $\mathbf{x}_i$ are drawn independently from probability measures absolutely continuous with respect to the standard Borel measure, then $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$ with probability one.
 \end{corollary}
 
-Thus, drawing the dictionary and sparse coefficients from any continuous probability distribution almost certainly generates data with a stable sparse representation.
+Thus, drawing the dictionary and supported sparse coefficients from any continuous probability distribution almost certainly generates data with a stable sparse representation.
 
@@
 
-We close this section with some comments on optimality.
+We close this section with some comments on the optimality of our results.
 Our linear scaling for $\varepsilon$ in \eqref{epsdel} is essentially optimal (e.g., see \cite{arias2013fundamental}), but a basic open problem remains: how many samples are necessary to determine the sparse coding model?
@@
 
-We begin our proof of Thm.~\ref{DeterministicUniquenessTheorem} by showing how dictionary recovery \eqref{Cstable} already implies sparse code recovery \eqref{b-PDa} when \mbox{$\varepsilon < L_{2k}(\mathbf{A}) / C_1$} (provided $\mathbf{A}$ satisfies \eqref{SparkCondition}), temporarily assuming (without loss of generality) that $\overline m = m$.
-For $2k$-sparse $\mathbf{x} \in \mathbb{R}^m$, the triangle inequality gives \mbox{$\|(\mathbf{A}-\mathbf{BPD})\mathbf{x}\|_2  \leq C_1\varepsilon \|\mathbf{x}\|_1 \leq C_1 \varepsilon \sqrt{2k}  \|\mathbf{x}\|_2$}.
-Thus:
+We begin our proof of Thm.~\ref{DeterministicUniquenessTheorem} by showing how dictionary recovery \eqref{Cstable} already implies sparse code recovery \eqref{b-PDa} when $\mathbf{A}$ satisfies \eqref{SparkCondition} and \mbox{$\varepsilon < L_{2k}(\mathbf{A}) / C_1$}, assuming for this purpose that $\overline m = m$ without loss of generality.
+Consider any $2k$-sparse $\mathbf{x} \in \mathbb{R}^m$ and note that $\|\mathbf{x}\|_1 \leq \sqrt{2k}  \|\mathbf{x}\|_2$.
+By definition of $L_{2k}$ in \eqref{Ldef}, we have:
+\begin{align}\label{stuff}
+\|\mathbf{x}_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_i \|_1 \nonumber
+&\leq \frac{\|\mathbf{BPD}(\mathbf{x}_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_i)\|_2}{L_{2k}(\mathbf{BPD})} \\ \nonumber
+&\leq \frac{\|(\mathbf{BPD} - \mathbf{A})\mathbf{x}_i\|_2 + \|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline x}_i\|_2}{L_{2k}(\mathbf{BPD})} \\
+&\leq \frac{C_1\varepsilon \|\mathbf{x}_i\|_1 + \varepsilon}{L_{2k}(\mathbf{BPD})},
+\end{align}
+where the term $C_1\varepsilon \|\mathbf{x}\|_1$ in the numerator above follows from the triangle inequality applied to \eqref{Cstable}.
+
+It remains for us to bound the denominator.  By the reverse triangle inequality:
 \begin{align*}
@@
 %
-since $\varepsilon < L_{2k}(\mathbf{A}) / C_1$. Hence, $L_{2k}(\mathbf{BPD}) \geq L_{2k}(\mathbf{A}) - C_1\varepsilon  > 0$, and \eqref{b-PDa} then follows from:
-\begin{align*}
-\|\mathbf{x}_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_i \|_1
-&\leq \frac{\|\mathbf{BPD}(\mathbf{x}_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_i)\|_2}{L_{2k}(\mathbf{BPD})} \\
-&\leq \frac{\|(\mathbf{BPD} - \mathbf{A})\mathbf{x}_i\|_2 + \|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline x}_i\|_2}{L_{2k}(\mathbf{BPD})} \\
-&\leq \frac{\varepsilon (1 + C_1 \|\mathbf{x}_i\|_1)}{L_{2k}(\mathbf{BPD})}.
-\end{align*}
+wherein removal of the absolute value is justified because of $C_1\varepsilon < L_{2k}(\mathbf{A})$.
+We therefore have that $L_{2k}(\mathbf{BPD}) \geq L_{2k}(\mathbf{A}) - C_1\varepsilon  > 0$, and \eqref{b-PDa} then follows from \eqref{stuff}.
 
-The heart of the matter is therefore \eqref{Cstable}, which we now establish, first in the important special case of $k = 1$.
+The heart of the matter is therefore \eqref{Cstable}, which we now establish beginning with the important special case of $k = 1$.
 
 \begin{proof}[Proof of Thm.~\ref{DeterministicUniquenessCorollary} for $k=1$]
-Since the only 1-uniform hypergraph with the SIP is $[m]$, we have $\mathbf{x}_i = c_i \mathbf{e}_i$ for $c_i \in \mathbb{R} \setminus \{\mathbf{0}\}$, $i \in [m]$.
-In this case, we require that $C_1 \geq 1/ \min_{\ell \in [m]} |c_{\ell}|$.
+Since the only 1-uniform hypergraph with the SIP is $[m]$, which is obviously regular, we require only $\mathbf{x}_i = c_i \mathbf{e}_i$ for $i \in [m]$, with $c_i \neq 0$ to guarantee  linear independence.
+While we have yet to define $C_1$ in general, in this case we may set $C_1 = 1/ \min_{\ell \in [m]} |c_{\ell}|$ so that $\varepsilon < L_2(\mathbf{A})  \min_{\ell \in [m]} |c_{\ell}|$.
 
-Fix $\mathbf{A} \in \mathbb{R}^{n \times m}$ satisfying \eqref{SparkCondition} and suppose that for some $\mathbf{B}$ and $1$-sparse $\mathbf{\overline x}_i \in \mathbb{R}^{\overline m}$ we have  $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \varepsilon < L_2(\mathbf{A}) / C_1$ for all $i$.
-Then, there exist $\overline{c}_1, \ldots, \overline{c}_m \in \mathbb{R}$ and a map $\pi: [m] \to [\overline m]$ such that:
+Fix $\mathbf{A} \in \mathbb{R}^{n \times m}$ satisfying $L_2(\mathbf{A}) > 0$, since here we have $2\mathcal{H} = {[m] \choose 2}$, and suppose that for some $\mathbf{B}$ and $1$-sparse $\mathbf{\overline x}_i \in \mathbb{R}^{\overline m}$ we have  $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \varepsilon < L_2(\mathbf{A}) / C_1$ for all $i$.
+Then there exist $\overline{c}_1, \ldots, \overline{c}_m \in \mathbb{R}$ and a map $\pi: [m] \to [\overline m]$ such that:
 \begin{align}\label{1D}
@@
 \end{align} 
-Note that $\overline{c}_j \neq 0$, since otherwise we have the contradiction $\|\mathbf{A}_j \|_2 \leq C_1 |c_j| \|\mathbf{A}_j \|_2  < L_2(\mathbf{A}) \leq L_1(\mathbf{A}) = \min_{j \in [m]} \|\mathbf{A}_{j}\|_2$.
+Note that $\overline{c}_j \neq 0$, since otherwise we would reach the contradiction $\|\mathbf{A}_j \|_2 \leq C_1 |c_j| \|\mathbf{A}_j \|_2  \leq C_1\varepsilon < L_2(\mathbf{A}) \leq L_1(\mathbf{A}) = \min_{j \in [m]} \|\mathbf{A}_{j}\|_2$.
 %implies by \eqref{delrho} the contradiction $|c_j| < \min_{\ell \in [m]} | c_\ell |$.
@@
 Suppose that $\pi(i) = \pi(j) = \ell$ for some $i \neq j$ and $\ell$.
-Then, $\|c_{j}\mathbf{A}_{j} - \overline{c}_{j}\mathbf{B}_{\ell}\|_2 \leq \varepsilon$ and $\|c_{i}\mathbf{A}_{i} - \overline{c}_{i} \mathbf{B}_{\ell}\|_2  \leq \varepsilon$.
-Scaling and summing these inequalities by $|\overline{c}_{i}|$ and $|\overline{c}_{j}|$, respectively, and applying the triangle inequality, we obtain:
+Then $\|c_{j}\mathbf{A}_{j} - \overline{c}_{j}\mathbf{B}_{\ell}\|_2 \leq \varepsilon$ and $\|c_{i}\mathbf{A}_{i} - \overline{c}_{i} \mathbf{B}_{\ell}\|_2  \leq \varepsilon$, and we have: %Scaling and summing these inequalities by $|\overline{c}_{i}|$ and $|\overline{c}_{j}|$, respectively, and applying the triangle inequality to annihilate the terms in $\mathbf{B}_\ell$, we obtain:
 \begin{align*}
 (|\overline{c}_{i}| + |\overline{c}_{j}|) \varepsilon
-&\geq\|\mathbf{A}(\overline{c}_{i}c_{j} \mathbf{e}_{j} - \overline{c}_{j}c_{i}\mathbf{e}_{i})\|_2 \nonumber \\ 
-&\geq  \left( |\overline{c}_{i}| + |\overline{c}_{j}| \right) L_2(\mathbf{A}) \min_{\ell \in [m]} |c_\ell |,
+&\geq |\overline{c}_{i}| \|c_{j}\mathbf{A}_{j} - \overline{c}_{j}\mathbf{B}_{\ell}\|_2  + |\overline{c}_{j}| \|c_{i}\mathbf{A}_{i} - \overline{c}_{i} \mathbf{B}_{\ell}\|_2 \nonumber \\
+&\geq \|\mathbf{A}(\overline{c}_{i}c_{j} \mathbf{e}_{j} - \overline{c}_{j}c_{i}\mathbf{e}_{i})\|_2 \nonumber \\ 
+&\geq  L_2(\mathbf{A}) \|\overline{c}_{i}c_{j} \mathbf{e}_{j} - \overline{c}_{j}c_{i}\mathbf{e}_{i}\|_2 \nonumber \\
+&\geq  L_2(\mathbf{A}) \left( |\overline{c}_{i}| + |\overline{c}_{j}| \right) \min_{\ell \in [m]} |c_\ell |,
 \end{align*}
-which contradicts the bound $\varepsilon < L_2(\mathbf{A})/C_1$.
-Hence, the map $\pi$ is injective and therefore $\overline m \geq m$.
-Setting $\overline J = \pi([m])$ and letting $P = \left( \mathbf{e}_{\pi(1)} \cdots \mathbf{e}_{\pi(m)}\right)$ and $D = \text{diag}(\frac{\overline{c}_1}{c_1},\ldots,\frac{\overline{c}_m}{c_m})$, we see that \eqref{1D} becomes, for all $j \in [m]$:
+contradicting our assumed upper bound on $\varepsilon$.
+Hence, the map $\pi$ is injective and it must be the case that $\overline m \geq m$.
+Setting $\overline J = \pi([m])$ and letting $P = \left( \mathbf{e}_{\pi(1)} \cdots \mathbf{e}_{\pi(m)}\right)$ and $D = \text{diag}(\frac{\overline{c}_1}{c_1},\ldots,\frac{\overline{c}_m}{c_m})$, we may rewrite \eqref{1D} to see that, for all $j \in [m]$:
 \begin{align*}
@@
 
-We require a few additional tools to extend the proof to the general case $k < m$.
-These include a generalized notion of distance (Def.~\ref{dDef}) and angle (Def.~\ref{FriedrichsDefinition}) between subspaces as well as a stability result in combinatorial matrix analysis (Lem.~\ref{MainLemma}).
+An extension of the proof to the general case $k < m$ requires that we introduce some additional tools which we have used to derive  our general expression \eqref{Cdef1} for the constant $C_1$.
+These including a generalized notion of distance (Def.~\ref{dDef}) and angle (Def.~\ref{FriedrichsDefinition}) between subspaces as well as a stability result in combinatorial matrix analysis (Lem.~\ref{MainLemma}).
 
@@
 
-We note the following facts. If $U' \subseteq U$, then $d(U',V) \leq d(U,V)$ and \cite[Ch.~4 Cor.~2.6]{Kato2013}: %Kato p.223
+We note the following facts about $d$. Clearly, 
+\begin{align}\label{UsubU}
+U' \subseteq U \implies d(U',V) \leq d(U,V).
+\end{align}
+From \cite[Ch.~4 Cor.~2.6]{Kato2013}, we have: %Kato p.223
 \begin{align}\label{dimLem}
-d(U,V) < 1 \implies \dim(U) \leq \dim(V).
+d(U,V) < 1 \implies \dim(U) \leq \dim(V),
 \end{align}
-Also, from \cite[Lem.~3.2]{Morris10}, we have:
+and from \cite[Lem.~3.2]{Morris10}:
 \begin{align}\label{eqdim}
@@
 
-Our result in combinatorial matrix analysis is the following.
+Our result in combinatorial matrix analysis, which hides most of the complexity in our proof of Thm.~\ref{DeterministicUniquenessTheorem}, is the following.
 
@@
 \begin{align}\label{GapUpperBound}
-d(\bm{\mathcal{A}}_S, \bm{\mathcal{B}}_{\pi(S)}) \leq \varepsilon, \ \  \text{for $S \in \mathcal{H}$};
+d(\bm{\mathcal{A}}_S, \bm{\mathcal{B}}_{\pi(S)}) \leq \varepsilon \ \  \text{for $S \in \mathcal{H}$},
 \end{align}
-then $\overline m \geq m$, and, provided $\overline m < mr /(r-1)$, there is a permutation matrix $\mathbf{P}$ and invertible diagonal $\mathbf{D}$ such that:
+then $\overline m \geq m$, and provided $\overline m < mr /(r-1)$, there is a permutation matrix $\mathbf{P}$ and invertible diagonal $\mathbf{D}$ such that:
 \begin{align}\label{MainLemmaBPD}
-\|\mathbf{A}_j - \mathbf{B}_{\overline J} \mathbf{PD}_j\|_2 \leq C_2 \varepsilon, \ \  \text{for } j \in J,
+\|\mathbf{A}_j - \mathbf{B}_{\overline J} \mathbf{PD}_j\|_2 \leq C_2 \varepsilon \ \  \text{for } j \in J
 \end{align}
-for some nonempty $\overline J \subseteq[\overline{m}]$ and $J \subseteq [m]$ of size $\overline m - r(\overline m - m)$.
+for some $J$ and $\overline J$ both of size \mbox{$m - (r-1)(\overline m - m)$}.
 \end{lemma}
@@
 
-The constant $C_1 > 0$ in Thm.~\ref{DeterministicUniquenessTheorem} is then given by\footnote{Note that $\|\mathbf{AX}_{I(S)}\mathbf{c}\|_2 \geq \sqrt{k} L_\mathcal{H}(\mathbf{A})\|\mathbf{X}_{I(S)}\mathbf{c}\|_2 \geq k L_\mathcal{H}(\mathbf{A}) L_k(\mathbf{X}_{I(S)})\|\mathbf{c}\|_2$ for $S \in \mathcal{H}$ and $k$-sparse $\mathbf{c}$.
-Therefore, $L_k(\mathbf{AX}_{I(S)}) \geq \sqrt{k} L_\mathcal{H}(\mathbf{A}) L_k(\mathbf{X}_{I(S)}) > 0$ since $L_{2\mathcal{H}}(\mathbf{A})> 0$ and $L_k(\mathbf{X}_{I(S)}) > 0$ by general linear position of the $\mathbf{x}_i$.
-Thus, $C_1 > 0$.}:
-\begin{align}\label{Cdef1}
-C_1(\mathbf{A}, \{\mathbf{x}_i\}_{i=1}^N, \mathcal{H}) := \frac{ C_2(\mathbf{A}, \mathcal{H}) } { \min_{S \in \mathcal{H}} L_k(\mathbf{AX}_{I(S)}) },
-\end{align}
-where, given vectors $\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$, we denote by $\mathbf{X}$ the $m \times N$ matrix with columns $\mathbf{x}_i$ and by $I(S)$ the set of indices $i$ for which $\mathbf{x}_i$ is supported in $S$.
-
-The constant $C_2 = C_2(\mathbf{A}, \mathcal{H})$, in turn, will be presented relative to a quantity from \cite{Deutsch12} used to analyze the convergence of the alternating projections algorithm. 
-Specifically, in Lem.~\ref{DistanceToIntersectionLemma} below, the following definition is used to bound the distance between a point and the intersection of subspaces given an upper bound on its distance from each individual subspace.
+We present the constant $C_2$ (a function of $\mathbf{A}$ and $\mathcal{H}$) relative to a quantity used in \cite{Deutsch12} to analyze the convergence of the ``alternating projections" algorithm for projecting a point onto the intersection of subspaces.
+We incorporate this quantity into the following definition, which we refer to in our proof of Lem.~\ref{DistanceToIntersectionLemma} in the Appendix; specifically, we use it to bound the distance between a point and the intersection of subspaces given an upper bound on its distance from each subspace individually.
 
 \begin{definition}\label{FriedrichsDefinition}
-For a collection of real subspaces $\mathcal{V} = \{V_i\}_{i=1}^\ell$, define $\xi^2 := 0$ when $|\mathcal{V}| = 1$, and otherwise:
+For a collection of real subspaces $\mathcal{V} = \{V_i\}_{i=1}^\ell$, define $\xi(\mathcal{V}) := 0$ when $|\mathcal{V}| = 1$, and otherwise:
 \begin{align}\label{xi}
@@
 %
-where the maximum is taken over all orderings 
+where the maximum is taken over all ways of ordering 
 %\footnote{We modify the quantity in \cite{Deutsch12} in this way since the subspace ordering is irrelevant to our purpose.} 
-of the $V_i$ and the angle $\theta \in (0,\frac{\pi}{2}]$ is defined implicitly as \cite[Def.~9.4]{Deutsch12}:
+the $V_i$ and the angle $\theta \in (0,\frac{\pi}{2}]$ is defined implicitly as \cite[Def.~9.4]{Deutsch12}:
 \begin{align*}
@@
 \end{definition}
-Note that $\theta \in (0,\frac{\pi}{2}]$ implies $0 \leq \xi < 1$, and that $\xi(\mathcal{V}') \leq \xi(\mathcal{V})$ when $\mathcal{V}' \subseteq \mathcal{V}$.\footnote{We acknowledge the counter-intuitive property that $\theta =  \pi/2$ when $U \subseteq W$.}
-The constant $C_2$ in Lem.~\ref{MainLemma} is then:  
+Note that $\theta \in (0,\frac{\pi}{2}]$ implies $0 \leq \xi < 1$, and that $\xi(\mathcal{V}') \leq \xi(\mathcal{V})$ when $\mathcal{V}' \subseteq \mathcal{V}$.\footnote{We acknowledge the potentially counter-intuitive property that $\theta =  \pi/2$ when $U \subseteq W$.}
+
+The constant $C_2 > 0$ of Lem.~\ref{MainLemma} is then given by:  
 \begin{align}\label{Cdef2}
-	C_2(\mathbf{A}, \mathcal{H}) := \frac{ (r+1) \max_{j \in [m]} \|\mathbf{A}_j\|_2}{ 1- \max_{\mathcal{G} \in {\mathcal{H} \choose r+1}} \xi( \bm{\mathcal{A}}_\mathcal{G} ) },
+	C_2(\mathbf{A}, \mathcal{H}) := \frac{ (r+1) \max_{j \in [m]} \|\mathbf{A}_j\|_2}{ 1- \max_{\mathcal{G} \in {\mathcal{H} \choose r+1}} \xi( \bm{\mathcal{A}}_\mathcal{G} ) }.
 \end{align}
+
+We now define the constant $C_1 > 0$ of Thm.~\ref{DeterministicUniquenessTheorem} in terms of $C_2$.
+Given vectors $\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$, let $\mathbf{X}$ denote the $m \times N$ matrix with columns $\mathbf{x}_i$ and let $I(S)$ denote the set of indices $i$ for which $\mathbf{x}_i$ is supported in $S$.
+\begin{align}\label{Cdef1}
+C_1(\mathbf{A}, \mathcal{H}, \{\mathbf{x}_i\}_{i=1}^N) := \frac{ C_2(\mathbf{A}, \mathcal{H}) } { \min_{S \in \mathcal{H}} L_k(\mathbf{AX}_{I(S)}) }.
+\end{align}
+We remark that given the assumptions of Thm.~\ref{DeterministicUniquenessTheorem} on $\mathbf{A}$ and the $\mathbf{x}_i$, this expression for $C_1$ is well-defined\footnote{\label{note1}Fixing $S \in \mathcal{H}$ and $k$-sparse $\mathbf{c}$, we have $\|\mathbf{AX}_{I(S)}\mathbf{c}\|_2 \geq \sqrt{k} L_\mathcal{H}(\mathbf{A})\|\mathbf{X}_{I(S)}\mathbf{c}\|_2 \geq k L_\mathcal{H}(\mathbf{A}) L_k(\mathbf{X}_{I(S)})\|\mathbf{c}\|_2$.
+Hence, $L_k(\mathbf{AX}_{I(S)}) \geq \sqrt{k} L_\mathcal{H}(\mathbf{A}) L_k(\mathbf{X}_{I(S)}) > 0$, since $L_{\mathcal{H}}(\mathbf{A}) \geq L_{2\mathcal{H}}(\mathbf{A})> 0$ and $L_k(\mathbf{X}_{I(S)}) > 0$ by general linear position of the $\mathbf{x}_i$.} and yields an upper bound on $\varepsilon$ consistent with that proven sufficient in the case $k=1$ considered at the beginning of this section.\footnote{When $\mathbf{x}_i = c_i\mathbf{e}_i$ we have $C_2 \geq 2\|\mathbf{A}_i\|_2$ and the denominator in \eqref{Cdef1} becomes $\min_{i \in [m]} |c_i| \|\mathbf{A}_i\|_2$, hence $C_1 \geq 2 / \min_{i \in [m]} |c_i|$.}
 % C_2(\mathbf{A}, \mathcal{H}) := \frac{ (r+1) \max_{j \in [m]} \|\mathbf{A}_j\|_2}{ \min_{\mathcal{G} \in {\mathcal{H} \choose r} \cup {\mathcal{H} \choose r+1}} \xi( \{ \bm{\mathcal{A}}_S \}
-which we remark yields a constant $C_1$ consistent with what is required for the case $k=1$ considered at the beginning of this section.\footnote{For $\mathbf{x}_i = c_i\mathbf{e}_i$, the denominator in \eqref{Cdef1} becomes $\min_{i \in [m]} |c_i| \|\mathbf{A}_i\|_2$, hence with $r=1$ we have $C_1 \geq 2 / \min_{i \in [m]} |c_i|$.}
 
-The pragmatic reader should note that the explicit constants $C_1$ and $C_2$ are effectively computable: the quantity $L_k$ may be calculated as the smallest singular value of a certain matrix, while the quantity $\xi$ involves computing ``canonical angles'' between subspaces, which reduce again to an efficient singular value decomposition.
+The practically-minded reader should note that the explicit constants $C_1$ and $C_2$ are effectively computable: the quantity $L_k$ may be calculated as the smallest singular value of a certain matrix, while the quantity $\xi$ involves computing ``canonical angles'' between subspaces, which reduce again to an efficient singular value decomposition.
 There is no known fast computation of $L_k$ in general, however, since even $L_{k} > 0$ is NP-hard \cite{tillmann2014computational}; although fixing $k$ yields polynomial complexity.
 Moreover, calculating $C_2$ requires an exponential number of queries to $\xi$ unless $r$ is held fixed, too (e.g., the ``cyclic order'' hypergraphs described above have $r=k$).
-Thus, as presented, $C_1$ and $C_2$ are not efficiently computable.
+Thus, as presented, $C_1$ and $C_2$ are not efficiently computable in general.
 
 \begin{proof}[Proof of Thm.~\ref{DeterministicUniquenessCorollary} for $k < m$] 
-We find a map $\pi: \mathcal{H} \to 2^{[\overline m]}$ for which the distance $d(\bm{\mathcal{A}}_S, \bm{\mathcal{B}}_{\pi(S)})$ is controlled by $\varepsilon$.
+We find a map $\pi: \mathcal{H} \to {[m] \choose k}$ for which the distance $d(\bm{\mathcal{A}}_S, \bm{\mathcal{B}}_{\pi(S)})$ is controlled by $\varepsilon$ for all $S \in \mathcal{H}$.
 Applying Lem.~\ref{MainLemma} then completes the proof.
@@
 
-Since there are more than $(k-1){\overline m \choose k}$ vectors $\mathbf{x}_i$ supported in each $S \in \mathcal{H}$, the pigeonhole principle gives $\overline S \in {[\overline m] \choose k}$ and a set of $k$ indices $K \subseteq I(S)$ with all $\mathbf{\overline x}_i$, $i \in K$, supported in $\pi(S) := \overline S$.
-It also follows from $L_{2\mathcal{H}}(\mathbf{A}) > 0$ and the general linear position of the $\mathbf{x}_i$ that $L_k(\mathbf{AX}_{K}) > 0$; that is, the columns of the $n \times k$ matrix $\mathbf{AX}_K$ form a basis for $\bm{\mathcal{A}}_S$.
+Fix $S \in \mathcal{H}$.
+Since there are more than $(k-1){\overline m \choose k}$ vectors $\mathbf{x}_i$ supported in $S$, by the pigeonhole principle there must be some $\overline S \in {[\overline m] \choose k}$ and a set of $k$ indices $K \subseteq I(S)$ for which all $\mathbf{\overline x}_i$ with $i \in K$ are supported in $\overline S$.
+It also follows\footnotemark[\ref{note1}] from $L_{2\mathcal{H}}(\mathbf{A}) > 0$ and the general linear position of the $\mathbf{x}_i$ that $L_k(\mathbf{AX}_{K}) > 0$; that is, the columns of the $n \times k$ matrix $\mathbf{AX}_K$ form a basis for $\bm{\mathcal{A}}_S$.
 
-Fixing $\mathbf{0} \neq \mathbf{y} \in \bm{\mathcal{A}}_S$, there then exists $\mathbf{0} \neq \mathbf{c} = (c_1, \ldots, c_k) \in \mathbb{R}^k$ such that $\mathbf{y} = \mathbf{AX}_K\mathbf{c}$.
-Setting \mbox{$\mathbf{\overline{y}} = \mathbf{B\overline{X}}_K\mathbf{c} \in \bm{\mathcal{B}}_{\overline S}$}, we have:
+Fixing $\mathbf{y} \in \bm{\mathcal{A}}_S \setminus \{\mathbf{0}\}$, there then exists $\mathbf{c} = (c_1, \ldots, c_k) \in \mathbb{R}^k \setminus \{\mathbf{0}\}$ such that $\mathbf{y} = \mathbf{AX}_K\mathbf{c}$.
+Setting \mbox{$\mathbf{\overline{y}} = \mathbf{B\overline{X}}_K\mathbf{c}$, which is in $\bm{\mathcal{B}}_{\overline S}$}, we have by triangle inequality:
 \begin{align*}
 \|\mathbf{y} - \mathbf{\overline{y}}\|_2 
-&= \|\sum_{i=1}^k c_i(\mathbf{AX}_K - \mathbf{B\overline{X}}_K)_i\|_2
-\leq \varepsilon \sum_{i=1}^k |c_i| \\
-&\leq \varepsilon \sqrt{k}  \|\mathbf{c}\|_2 
-\leq \frac{\varepsilon}{L_k(\mathbf{AX}_K)} \|\mathbf{y}\|_2,
+%&= \|\sum_{i=1}^k c_i(\mathbf{AX}_K - \mathbf{B\overline{X}}_K)_i\|_2
+&= \|(\mathbf{AX}_K - \mathbf{B\overline{X}}_K)\mathbf{c}\|_2
+%\leq \varepsilon \sum_{i=1}^k |c_i| \\
+\leq \varepsilon \|\mathbf{c}\|_1
+\leq \varepsilon \sqrt{k}  \|\mathbf{c}\|_2  \\
+&\leq \frac{\varepsilon}{L_k(\mathbf{AX}_K)} \|\mathbf{y}\|_2,
 \end{align*}
@@
 d(\bm{\mathcal{A}}_S, \bm{\mathcal{B}}_{\overline S}) 
-\leq \frac{\varepsilon}{  L_k(\mathbf{AX}_{K}) } \leq \varepsilon \frac{C_1}{C_2},
+\leq \frac{\varepsilon}{  L_k(\mathbf{AX}_{K}) } 
+\leq \frac{\varepsilon}{  L_k(\mathbf{AX}_{I(S)}) } 
+\leq \varepsilon \frac{C_1}{C_2}.
 \end{align}
 %
-where the second inequality is due to $L_k(\mathbf{AX}_{K}) \geq L_k(\mathbf{AX}_{I(S)})$ and \eqref{Cdef1}.
-Finally, apply Lem.~\ref{MainLemma} with $\varepsilon < L_2(\mathbf{A})/C_1$.
-% L_2(A) > 0 by def of L, since L_2H(A) > 0 and H covers [m]
+Now, apply Lem.~\ref{MainLemma} with $\varepsilon < L_2(\mathbf{A})/C_1$ and $\pi(S) := \overline S$. % L_2(A) > 0 by def of L, since L_2H(A) > 0 and H covers [m]
 \end{proof}
@@
 \begin{proof}[Proof of Thm.~\ref{SLCopt}]
-We bound the number of $k$-sparse $\mathbf{\overline x}_i$ and then apply Thm.~\ref{DeterministicUniquenessCorollary}. 
+We bound the number of $k$-sparse $\mathbf{\overline x}_i$ from below and then apply Thm.~\ref{DeterministicUniquenessCorollary}. 
 %We now apply this fact to bound the number of $k$-sparse $\mathbf{\overline x}_i$. 
@@
 Since the $\mathbf{x}_i$ are all $k$-sparse, by \eqref{minsum} we have:
-\mbox{$k \sum_{p = 0}^{\overline m} n_p \geq \sum_{i=0}^N \|\mathbf{x}_i\|_0 \geq \sum_{i=0}^N \|\mathbf{\overline x}_i\|_0 = \sum_{p=0}^{\overline m} p n_p.$}
-Hence,
+\begin{align*}
+%\mbox{$k \sum_{p = 0}^{\overline m} n_p \geq \sum_{i=0}^N \|\mathbf{x}_i\|_0 \geq \sum_{i=0}^N \|\mathbf{\overline x}_i\|_0 = \sum_{p=0}^{\overline m} p n_p.$}
+\sum_{p=0}^{\overline m} p n_p =  \sum_{i=0}^N \|\mathbf{\overline x}_i\|_0
+\leq \sum_{i=0}^N \|\mathbf{x}_i\|_0 
+\leq kN
+\end{align*}
+Since $N = \sum_{p = 0}^{\overline m} n_p$, we then have $\sum_{p = 0}^{\overline m} (p-k) n_p \leq 0$. Splitting the sum yields:
 \begin{align}\label{eqn}
@@
 %
-demonstrating that the number of vectors $\mathbf{\overline x}_i$ that are \emph{not} $k$-sparse is controlled by how many are $(k-1)$-sparse.
+demonstrating that the number of vectors $\mathbf{\overline x}_i$ that are \emph{not} $k$-sparse is bounded above by how many are $(k-1)$-sparse.
 
-Next, observe that no more than $(k-1)|\mathcal{H}|$ of the $\mathbf{\overline x}_i$ share a support $\overline S$ of size less than $k$; otherwise, by the pigeonhole principle, at least $k$ of these indices $i$ belong to the same $K \subseteq I(S)$ for some $S \in \mathcal{H}$ and (as argued previously) \eqref{rhs222} follows.
-Since the right-hand side of \eqref{rhs222} is less than one, by \eqref{dimLem} we have the contradiction $k = \dim(\bm{\mathcal{A}}_S) \leq \dim(\bm{\mathcal{B}}_{\overline S}) \leq |\overline S|.$
+We note that no more than $(k-1)|\mathcal{H}|$ of the $\mathbf{\overline x}_i$ share a support $\overline S$ of size less than $k$.
+Otherwise, by the pigeonhole principle, there is some $S \in \mathcal{H}$ and a set of $k$ indices $K \subseteq I(S)$ for which all $\mathbf{x}_i$ with $i \in K$ are supported in $S$; as argued previously, \eqref{rhs222} follows.
+It is simple to show that $L_2(\mathbf{A}) \leq \max_j\|\mathbf{A}_j\|_2$, and since $0 \leq \xi < 1$, the right-hand side of \eqref{rhs222} is less than one for $\varepsilon < L_2(\mathbf{A})/C_1$.
+Thus, by \eqref{dimLem} we would have the contradiction $k = \dim(\bm{\mathcal{A}}_S) \leq \dim(\bm{\mathcal{B}}_{\overline S}) \leq |\overline S| < k.$
 
-The total number of $(k-1)$-sparse vectors $\mathbf{\overline x}_i$ thus can not exceed $|\mathcal{H}|(k-1){ \overline m \choose k-1}$.
+The total number of $(k-1)$-sparse vectors $\mathbf{\overline x}_i$ thus cannot exceed $|\mathcal{H}|(k-1){ \overline m \choose k-1}$.
 By \eqref{eqn}, no more than $|\mathcal{H}|k(k-1){ \overline m \choose k-1}$ vectors $\mathbf{\overline x}_i$ are not $k$-sparse.
 Since for every $S \in \mathcal{H}$ there are over $(k-1)\left[ {\overline m \choose k} + |\mathcal{H}|k{ \overline m \choose k-1} \right]$ vectors $\mathbf{x}_i$ supported there, it must be that more than $(k-1){\overline m \choose k}$ of them have corresponding $\mathbf{\overline x}_i$ that are $k$-sparse.
-The result now follows from Thm.~\ref{DeterministicUniquenessCorollary}.
+The result now follows from Thm.~\ref{DeterministicUniquenessCorollary}, noting by the triangle inequality that $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline x}_i\| \leq 2\eta$ for $i = 1, \ldots, N$.
 \end{proof}
@@
 We have shown that, given sufficient data, the problem of seeking a dictionary and sparse codes with minimal average support size (Prob.~\ref{OptimizationProblem}) reduces to an instance of Prob.~\ref{InverseProblem}, to which our main result (Thm.~\ref{DeterministicUniquenessTheorem}) applies: every dictionary and sequence of sparse codes consistent with the data are equivalent up to inherent relabeling/scaling ambiguities and a discrepancy (error) that scales linearly with the measurement noise or modeling inaccuracy.
-The constants we provide are explicit and computable; as such, there is an effective procedure that sufficiently affirms if a proposed solution to Probs.~\ref{DeterministicUniquenessTheorem} or \ref{OptimizationProblem} is indeed unique up to noise and inherent ambiguities.
+The constants we provide are explicit and computable; as such, there is an effective procedure that sufficiently affirms if a proposed solution to these problems is indeed unique up to noise and inherent ambiguities, although this computation is not efficient in general.
 
@@
 
-In this section, we prove Lem.~\ref{MainLemma} and some auxiliary lemmas.  % stating and proving some auxiliary lemmas. 
+In this section, we prove Lem.~\ref{MainLemma} after stating some required auxiliary lemmas and their proofs.  % stating and proving some auxiliary lemmas. 
 %First, note that since $\|\mathbf{A}\mathbf{x}\|_2 \leq \max_j\|\mathbf{A}_j\|_2\|\mathbf{x}\|_1$ and $\|\mathbf{x}\|_1 \leq \sqrt{k} \|\mathbf{x}\|_2$ for $k$-sparse $\mathbf{x}$, by \eqref{Ldef} we have the following frequently applied inequality:
@@
 \begin{proof}
-By induction, it is enough to prove the trivial case $\ell = 2$.
-%Clearly, for any map $f$, if $w \in f(U \cap V)$ then $w \in f(U)$ and $w \in f(V)$, hence $w \in f(U) \cap f(V)$.
+By induction, it is enough to prove the case $\ell = 2$.
+Clearly, for any map $f$, if $w \in f(U \cap V)$ then $w \in f(U)$ and $w \in f(V)$, hence $w \in f(U) \cap f(V)$.
 If $w \in f(U) \cap f(V)$ then $w \in f(U)$ and $w \in f(V)$, hence $w = f(u) = f(v)$ for some $u \in U$ and $v \in V$, implying $u = v$ by injectivity of $f$.
@@
 \end{proof}
-In particular, if a matrix $\mathbf{A}$ satisfies $L_{2\mathcal{H}}(\mathbf{A}) > 0$, then letting $V$ be the set of vectors with supports in $2\mathcal{H}$, we have $\bm{\mathcal{A}}_{\cap \mathcal{G}} = \cap \bm{\mathcal{A}}_\mathcal{G}$ for all $\mathcal{G} \subseteq \mathcal{H}$.
+In particular, if a matrix $\mathbf{A}$ satisfies $L_{2\mathcal{H}}(\mathbf{A}) > 0$, then taking $V$ to be the union of subspaces consisting of vectors with supports in $2\mathcal{H}$, we have $\bm{\mathcal{A}}_{\cap \mathcal{G}} = \cap \bm{\mathcal{A}}_\mathcal{G}$ for all $\mathcal{G} \subseteq \mathcal{H}$.
 % \vspace{-.4 cm}
@@
 \begin{lemma}\label{DistanceToIntersectionLemma}
-Let $\mathcal{V} = \{V_i\}_{i=1}^k$ be a set of two or more subspaces of $\mathbb{R}^m$ and let $V = \cap_{i = 1}^k V_i$.
-For  $\mathbf{x} \in \mathbb{R}^m$, we have (recall Defs.~\ref{dDef}~\&~\ref{FriedrichsDefinition}):
+Let $\mathcal{V} = \{V_i\}_{i=1}^k$ be a set of two or more subspaces of $\mathbb{R}^m$ and let $V = \cap \mathcal{V} $.
+For  $\mathbf{u} \in \mathbb{R}^m$, we have (recall Defs.~\ref{dDef}~\&~\ref{FriedrichsDefinition}):
 \begin{align}\label{DTILeq}
-\text{\rm dist}(\mathbf{x}, V) \leq \frac{1}{1 - \xi(\mathcal{V})} \sum_{i=1}^k \text{\rm dist}(\mathbf{x}, V_i).
+\text{\rm dist}(\mathbf{u}, V) \leq \frac{1}{1 - \xi(\mathcal{V})} \sum_{i=1}^k \text{\rm dist}(\mathbf{u}, V_i).
 \end{align}
@@
 % When $V = \{\mathbf{0}\}$, the result is trivial, so suppose otherwise.  
-Recall the projection onto the subspace $V \subseteq \mathbb{R}^m$ is the mapping $\Pi_V: \mathbb{R}^m \to V$ that associates with each $\mathbf{x}$ its unique nearest point in $V$; i.e., $\|\mathbf{x} - \Pi_V\mathbf{x}\|_2 = \text{\rm dist}(\mathbf{x}, V)$.
-Next, observe:
+Recall the projection onto the subspace $V \subseteq \mathbb{R}^m$ is the mapping $\Pi_V: \mathbb{R}^m \to V$ that associates with each $\mathbf{u}$ its unique nearest point in $V$; i.e., $\|\mathbf{u} - \Pi_V\mathbf{u}\|_2 = \text{\rm dist}(\mathbf{u}, V)$.
+By repeated triangle inequality,
 \begin{align}\label{f}
-\|\mathbf{x} - \Pi_V\mathbf{x}\|_2 &\leq \|\mathbf{x} - \Pi_{V_k} \mathbf{x}\|_2 + \|\Pi_{V_k}  \mathbf{x} - \Pi_{V_k}\Pi_{V_{k-1}}\mathbf{x}\|_2 \nonumber \\
-&\ \ \ + \cdots + \|\Pi_{V_k} \Pi_{V_{k-1}}\cdots \Pi_{V_1} \mathbf{x} - \Pi_V \mathbf{x}\|_2 \nonumber \\
-&\leq \|\Pi_{V_k}\cdots\Pi_{V_{1}} \mathbf{x} - \Pi_V \mathbf{x}\|_2 + \sum_{\ell=1}^k \|\mathbf{x} - \Pi_{V_{\ell}} \mathbf{x}\|_2,
+\|\mathbf{u} - &\Pi_V\mathbf{u}\|_2 
+\leq \|\mathbf{u} - \Pi_{V_k} \mathbf{u}\|_2 + \|\Pi_{V_k}  \mathbf{u} - \Pi_{V_k}\Pi_{V_{k-1}}\mathbf{u}\|_2 \nonumber \\
+&\ \ \ \ \ \ \ \ \ \ \ + \cdots + \|\Pi_{V_k} \Pi_{V_{k-1}}\cdots \Pi_{V_1} \mathbf{u} - \Pi_V \mathbf{u}\|_2 \nonumber \\
+&\leq  \sum_{\ell=1}^k \|\mathbf{u} - \Pi_{V_{\ell}} \mathbf{u}\|_2 
++ \|(\Pi_{V_k}\cdots\Pi_{V_{1}} - \Pi_V) \mathbf{u}\|_2,
 \end{align}
-using the triangle inequality and that the spectral norm satisfies $\|\Pi_{V_{\ell}}\|_2 \leq 1$ for all $\ell$ (since $\Pi_{V_{\ell}}$ are orthogonal projections).
-
-The desired result, \eqref{DTILeq}, now follows by bounding the second term on the right-hand side using the following fact \cite[Thm.~9.33]{Deutsch12}:
+where we have also used that the spectral norm of the orthogonal projections $\Pi_{V_{\ell}}$ satisfies $\|\Pi_{V_{\ell}}\|_2 \leq 1$ for all $\ell$.
+It remains to bound the second term in \eqref{f} by $\xi(\mathcal{V}) \|\mathbf{u} - \Pi_V\mathbf{u}\|_2$.
+First, note that $\Pi_{V_\ell} \Pi_V = \Pi_V$ and $\Pi_V^2 = \Pi_V$, so we have $\|(\Pi_{V_k} \cdots \Pi_{V_1} - \Pi_V) \mathbf{u} \|_2
+= \| ( \Pi_{V_k} \cdots\Pi_{V_1} - \Pi_V ) (\mathbf{u} - \Pi_V\mathbf{u})\|_2$. % \leq z\|\mathbf{u} - \Pi_V\mathbf{u}\|_2$.
+The result \eqref{DTILeq} then follows from the following fact \cite[Thm.~9.33]{Deutsch12}:
 \begin{align}
-\|\Pi_{V_k}\Pi_{V_{k-1}}\cdots\Pi_{V_1} \mathbf{x} - \Pi_V\mathbf{x}\|_2 \leq z \|\mathbf{x}\|_2,
+\|\Pi_{V_k}\Pi_{V_{k-1}}\cdots\Pi_{V_1} \mathbf{x} - \Pi_V\mathbf{x}\|_2 \leq z \|\mathbf{x}\|_2 \ \ \text{for all } \mathbf{x},
 \end{align}
-for \mbox{$z^2= 1 - \prod_{\ell =1}^{k-1}(1-z_{\ell}^2)$} and \mbox{$z_{\ell} = \cos\theta\left(V_{\ell}, \cap_{s=\ell+1}^k V_s\right)$}, recalling $\theta$ from Def.~\ref{FriedrichsDefinition}.
-Together with $\Pi_{V_\ell} \Pi_V = \Pi_V$ for all $\ell \in [k]$ and $\Pi_V^2 = \Pi_V$, this implies that $\|\Pi_{V_k} \cdots \Pi_{V_1}\mathbf{x}  - \Pi_V \mathbf{x} \|_2$ satisfies:
-$\| ( \Pi_{V_k} \cdots\Pi_{V_1} - \Pi_V ) (\mathbf{x} - \Pi_V\mathbf{x})\|_2 \leq z\|\mathbf{x} - \Pi_V\mathbf{x}\|_2$.
-
-Finally, substituting this into \eqref{f} and rearranging produces \eqref{DTILeq} after substituting $\xi(\mathcal{V})$ for $z$.
+with \mbox{$z^2= 1 - \prod_{\ell =1}^{k-1}(1-z_{\ell}^2)$} and \mbox{$z_{\ell} = \cos\theta\left(V_{\ell}, \cap_{s=\ell+1}^k V_s\right)$} (recall $\theta$ from Def.~\ref{FriedrichsDefinition}), after substituting $\xi(\mathcal{V})$ for $z$ and rearranging terms.
 \end{proof}
@@
 %
-then $\overline m \geq m$, and if $(r-1) \overline m < mr$ then the map $i \mapsto \cap \pi(\sigma(i))$ is an injective map to $[\overline m]$ from some $J \subseteq [m]$ of size $\overline m - r(\overline m - m)$.
-%In particular, if $\overline m = m$ then $\pi$ is induced by a permutation on $[m]$.
+then $\overline m \geq m$, and if $\overline m < mr / (r-1)$ then the map $i \mapsto \cap \pi(\sigma(i))$ is an injective map to $[\overline m]$ from some $J \subseteq [m]$ of size $m - (r-1)(\overline m - m)$.\footnote{Recall $\sigma$ from Def.~\ref{sip}.}  %In particular, if $\overline m = m$ then $\pi$ is induced by a permutation on $[m]$.
 \end{lemma}
+
 \begin{proof}
-Consider the set: $T_1 := \{(i, S): i \in \pi(S), S \in \mathcal{H}\}$, which numbers $|T_1| = \sum_{S \in \mathcal{H}} |\pi(S)| \geq \sum_{S \in \mathcal{H}} |S| = \sum_{i \in [m]} \deg_\mathcal{H}(i) = mr$.
-Note that $|T_1| \leq \overline m r$ by \eqref{cond}, since otherwise pigeonholing the elements of $T_1$ with respect to their possible first indices $[\overline m]$ would imply $\deg_\mathcal{H}(i) \geq r$ for some $i \in [m]$.
+Consider the set: $T_1 := \{(i, S): i \in \pi(S), S \in \mathcal{H}\}$, which numbers $|T_1| = \sum_{S \in \mathcal{H}} |\pi(S)| \geq \sum_{S \in \mathcal{H}} |S| = \sum_{i \in [m]} \deg_\mathcal{H}(i) = mr$ by $r$-regularity of $\mathcal{H}$.
+Note that $|T_1| \leq \overline m r$; otherwise, pigeonholing the tuples of $T_1$ with respect to their $\overline m$ possible first elements would imply that more than $r$ of the tuples in $T_1$ share the same first element.
+This cannot be the case, however, since then some $\mathcal{G} \in {\mathcal{H} \choose r+1}$ formed from any $r+1$ of their second elements would satisfy $\cap \pi(\mathcal{G}) \neq 0$, hence $|\cap \mathcal{G}| \neq 0$ by \eqref{cond}, contradicting $r$-regularity of $\mathcal{H}$.
 Thus, $\overline m \geq m$.
 
-Suppose $\overline m (r-1) < mr$, so that $|T_1| \geq mr = \overline m (r - 1) + p$ for positive $p := mr - \overline m (r-1)$.
-Pigeonholing $T_1$ into $[\overline m]$ again, there must be at least $r$ elements of $T_1$ that share a first index.
-Let $i_1 \in [\overline m]$ be such an index and note that, in fact, no more than $r$ elements of $T_1$ can have $i_1$ as a first index; otherwise, the set $\mathcal{G}_1$ of their second indices would contain $r+1$ elements with a non-empty intersection by \eqref{cond}, contradicting $r$-regularity of $\mathcal{H}$.
-Thus, $|\mathcal{G}_1| = r$, and \eqref{cond} implies $|\cap \mathcal{G}_1| = 1$ by $r$-regularity and the SIP.
-If $p=1$, then we are done.
-Otherwise, define $T_2 := T_1 \setminus \{(i,S) \in T_1: i = i_1\}$, which contains $|T_2| = |T_1| - r \geq (\overline m - 1)(r-1) + (p-1)$ ordered pairs having $\overline m - 1$ distinct first indices.
-Repeating the above arguments thus produces a distinct $i_2 \in [\overline m]$ and $\mathcal{G}_2 \in {\mathcal{H} \choose r}$ with (necessarily, by $r$-regularity and the SIP) distinct singleton $\cap \mathcal{G}_2 \in [m]$.
-Finally, iterating this $p$ times in total yields the set of singletons \mbox{$J = \{\cap \mathcal{G}_1, \ldots, \cap \mathcal{G}_p\}$}.
+Suppose now that $\overline m (r-1) < mr$, so that $p := mr - \overline m (r-1)$ is positive and $|T_1| \geq \overline m (r - 1) + p$.
+Pigeonholing $T_1$ into $[\overline m]$ again, there must be at least $r$ tuples in $T_1$ that share some first element; that is, for some $\mathcal{G}_1 \subseteq \mathcal{H}$ of size $|\mathcal{G}_1| \geq r$ we have $|\cap \pi(\mathcal{G}_1)| \geq 1$ and (by \eqref{cond}) $|\cap \mathcal{G}_1| \geq 1$.
+Since no more than $r$ tuples of $T_1$ can share the same first element, we in fact have $|\mathcal{G}_1| = r$.
+It follows by $r$-regularity that $\mathcal{G}_1$ is a star of $\mathcal{H}$; hence, $|\cap \mathcal{G}_1| = 1$ by the SIP and $|\cap \pi(\mathcal{G}_1)|  = 1$ by \eqref{cond}.
+
+If $p=1$ then we are done.
+Otherwise, define $T_2 := T_1 \setminus \{(i,S) \in T_1: i = \cap \pi(\mathcal{G}_1)\}$, which contains $|T_2| = |T_1| - r \geq (\overline m - 1)(r-1) + (p-1)$ ordered pairs having $\overline m - 1$ distinct first indices.
+Pigeonholing $T_2$ into $[\overline m - 1]$ and repeating the above arguments produces the star $\mathcal{G}_2 \in {\mathcal{H} \choose r}$ with intersect $\cap \mathcal{G}_2$ necessarily distinct (by $r$-regularity) from $\cap \mathcal{G}_1$.
+Iterating this procedure $p$ times in total yields the stars $\mathcal{G}_i$ for which $\cap\mathcal{G}_i \mapsto \cap \pi(\mathcal{G}_i)$ defines an injective map to $[\overline m]$ from $J = \{\cap \mathcal{G}_1, \ldots, \cap \mathcal{G}_p\} \subseteq [m]$.
 \end{proof}
@@
 We begin by showing that $\dim(\bm{\mathcal{B}}_{\pi(S)}) = \dim(\bm{\mathcal{A}}_S)$ for all $S \in \mathcal{H}$.
-Note that since $\|\mathbf{A}\mathbf{x}\|_2 \leq \max_j\|\mathbf{A}_j\|_2\|\mathbf{x}\|_1$ and $\|\mathbf{x}\|_1 \leq \sqrt{k} \|\mathbf{x}\|_2$ for all $k$-sparse $\mathbf{x}$, by \eqref{Ldef} we have $L_2(\mathbf{A}) \leq \max_j\|\mathbf{A}_j\|_2$ and therefore (as $\xi > 0$), the right-hand side of \eqref{GapUpperBound} is less than one.
-From \eqref{dimLem}, we have $|\pi(S)| \geq \dim(\bm{\mathcal{B}}_{\pi(S)}) \geq \dim(\bm{\mathcal{A}}_S) = |S|$, with the equality by injectivity of $\mathbf{A}_S$.
+Note that since $\|\mathbf{A}\mathbf{x}\|_2 \leq \max_j\|\mathbf{A}_j\|_2\|\mathbf{x}\|_1$ and $\|\mathbf{x}\|_1 \leq \sqrt{k} \|\mathbf{x}\|_2$ for all $k$-sparse $\mathbf{x}$, by \eqref{Ldef} we have $L_2(\mathbf{A}) \leq \max_j\|\mathbf{A}_j\|_2$ and therefore (as $0 \leq \xi < 1$), the right-hand side of \eqref{GapUpperBound} is less than one.
+From \eqref{dimLem}, we have $|\pi(S)| \geq \dim(\bm{\mathcal{B}}_{\pi(S)}) \geq \dim(\bm{\mathcal{A}}_S) = |S|$, the final equality by injectivity of $\mathbf{A}_S$.
 As $|\pi(S)| = |S|$, the claim follows.
@@
 
-We next verify that \eqref{cond} holds.
+We next demonstrate that \eqref{cond} holds.
 Fixing $\mathcal{G} \in {\mathcal{H} \choose r} \cup {\mathcal{H} \choose r+1}$, it suffices to show that $d(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}, \bm{\mathcal{A}}_{\cap \mathcal{G}} ) < 1$, since by \eqref{dimLem} we then have $|\cap \pi(\mathcal{G})| = \dim(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}) \leq \dim(\bm{\mathcal{A}}_{\cap \mathcal{G}}) = |\cap \mathcal{G}|$, with equalities by the full column-ranks of $\mathbf{A}_{S}$ and $\mathbf{B}_{\pi(S)}$ for all $S \in \mathcal{H}$.\footnote{Note that if ever $\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})} \neq \bf 0$ while $\cap \mathcal{G} = \emptyset$, we would have $d(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}, \bm 0 ) = 1$.
 This cannot be the case, however, since the deduction that follows would then lead to a contradiction.} Observe that $d(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}, \bm{\mathcal{A}}_{\cap \mathcal{G}}  )
-\leq d\left( \cap \bm{\mathcal{B}}_{\pi(\mathcal{G})}, \cap \bm{\mathcal{A}}_\mathcal{G} \right)$, since $d(U',V) \leq d(U,V)$ whenever $U' \subseteq U$ and $\bm{\mathcal{A}}_{\cap \mathcal{G}} = \cap \bm{\mathcal{A}}_\mathcal{G}$ by Lem.~\ref{spanIntersectionLemma}.
-Recalling Def.~\ref{dDef}, applying Lem.~\ref{DistanceToIntersectionLemma} and carrying the supremum through the sum yields:
+\leq d\left( \cap \bm{\mathcal{B}}_{\pi(\mathcal{G})}, \cap \bm{\mathcal{A}}_\mathcal{G} \right)$, by \eqref{UsubU} since trivially $\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})} \subseteq \cap \bm{\mathcal{B}}_{\pi(\mathcal{G})}$ and since $\bm{\mathcal{A}}_{\cap \mathcal{G}} = \cap \bm{\mathcal{A}}_\mathcal{G}$ by Lem.~\ref{spanIntersectionLemma}.
+Recalling Def.~\ref{dDef} and applying Lem.~\ref{DistanceToIntersectionLemma} yields:
 \begin{align}
 d\left( \cap \bm{\mathcal{B}}_{\pi(\mathcal{G})}, \cap \bm{\mathcal{A}}_\mathcal{G} \right)
-%&\leq \max_{\mathbf{u} \in \cap \bm{\mathcal{B}}_{\pi(\mathcal{G})}, \ \|\mathbf{u}\|_2 \leq 1} \sum_{S \in \mathcal{G}} \frac{ \text{\rm dist}\left( \mathbf{u},\bm{\mathcal{A}}_{S} \right) }{ 1 - \xi( \bm{\mathcal{A}}_\mathcal{G} ) }
-\leq \sum_{S \in \mathcal{G}} \frac{ d\left( \cap \bm{\mathcal{B}}_{\pi(\mathcal{G})},\bm{\mathcal{A}}_{S} \right) }{ 1 - \xi( \bm{\mathcal{A}}_\mathcal{G} ) }.
+&\leq \max_{\mathbf{u} \in \cap \bm{\mathcal{B}}_{\pi(\mathcal{G})}, \ \|\mathbf{u}\|_2 \leq 1} \sum_{S \in \mathcal{G}} \frac{ \text{\rm dist}\left( \mathbf{u},\bm{\mathcal{A}}_{S} \right) }{ 1 - \xi( \bm{\mathcal{A}}_\mathcal{G} ) } \nonumber \\
+&= \sum_{S \in \mathcal{G}} \frac{ d\left( \cap \bm{\mathcal{B}}_{\pi(\mathcal{G})},\bm{\mathcal{A}}_{S} \right) }{ 1 - \xi( \bm{\mathcal{A}}_\mathcal{G} ) }, \nonumber
 \end{align}
-Since $\cap \bm{\mathcal{B}}_{\pi(\mathcal{G})} \subseteq \bm{\mathcal{B}}_{\pi(S)}$ for all $S \in \mathcal{G}$, the numerator of each term above is bounded by $d\left( \bm{\mathcal{B}}_{\pi(S)},\bm{\mathcal{A}}_{S} \right)$ and, recalling \eqref{eqdim} (since $\dim(\bm{\mathcal{B}}_{\pi(S)}) = \dim(\bm{\mathcal{A}}_S)$), in turn by $d\left(\bm{\mathcal{A}}_{S}, \bm{\mathcal{B}}_{\pi(S)} \right) \leq \varepsilon$.
-Thus:
+passing the maximum through the sum.
+Since $\cap \bm{\mathcal{B}}_{\pi(\mathcal{G})} \subseteq \bm{\mathcal{B}}_{\pi(S)}$ for all $S \in \mathcal{G}$, by \eqref{UsubU} the numerator of each term in the sum above is bounded by \mbox{$d\left( \bm{\mathcal{B}}_{\pi(S)},\bm{\mathcal{A}}_{S} \right) = d\left(\bm{\mathcal{A}}_{S}, \bm{\mathcal{B}}_{\pi(S)} \right) \leq \varepsilon$}, with equality by \eqref{eqdim} since $\dim(\bm{\mathcal{B}}_{\pi(S)}) = \dim(\bm{\mathcal{A}}_S)$.
+Thus, altogether:
 \begin{align}\label{last}
@@
 \end{align}
-which is less than one, since $C_2 \varepsilon < L_2(\mathbf{A}) \leq \max_j\|\mathbf{A}_j\|_2$.
+recalling the definition of $C_2$ in \eqref{Cdef2}.
+Lastly, since $C_2 \varepsilon < L_2(\mathbf{A}) \leq \max_j\|\mathbf{A}_j\|_2$, we have $d(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}, \bm{\mathcal{A}}_{\cap \mathcal{G}} ) \leq 1$ and therefore \eqref{cond} holds.
 
@@
 
-By Lem.~\ref{NonEmptyLemma}, the association $i \mapsto \cap \pi(\sigma(i))$ is an injective map $\overline \pi: J \to [\overline m]$ for some $J \subseteq [m]$ of size $\overline m - r(\overline m - m)$, and $\mathbf{B}_{\overline \pi(i)} \neq \mathbf{0}$ for all $i \in J$ since the columns of $\mathbf{B}_{\pi(S)}$ are linearly independent for all $S \in \mathcal{H}$.
-Letting $\overline \varepsilon := C_2 \varepsilon / \max_i \|\mathbf{A}_i\|_2$, it follows from \eqref{eqdim} and \eqref{last} that $d\left( \bm{\mathcal{A}}_i, \bm{\mathcal{B}}_{\overline \pi(i)} \right) \leq \overline \varepsilon$ for all $i \in J$.
+By Lem.~\ref{NonEmptyLemma}, the association $i \mapsto \cap \pi(\sigma(i))$ is an injective map $\overline \pi: J \to [\overline m]$ for some $J \subseteq [m]$ of size $m - (r-1)(\overline m - m)$, and $\mathbf{B}_{\overline \pi(i)} \neq \mathbf{0}$ for all $i \in J$ since we have shown the columns of $\mathbf{B}_{\pi(S)}$ to be linearly independent for all $S \in \mathcal{H}$.
+Letting $\overline \varepsilon := C_2 \varepsilon / \max_i \|\mathbf{A}_i\|_2$, it follows from \eqref{eqdim} and \eqref{last} that $d\left( \bm{\mathcal{A}}_i, \bm{\mathcal{B}}_{\overline \pi(i)} \right) = d\left(\bm{\mathcal{B}}_{\overline \pi(i)},  \bm{\mathcal{A}}_i \right)  \leq \overline \varepsilon$ for all $i \in J$.
 %Fixing $\overline \varepsilon = C_2\varepsilon$ and letting $c_i = \|\mathbf{A}_i\|_2^{-1}$, we thus have that for each $\mathbf{e}_i \in \mathbb{R}^m$ with $i \in J$ there exists some $\overline{c}_i \in \mathbb{R}$ such that $\|c_i\mathbf{A}\mathbf{e}_i - \overline{c}_i \mathbf{B}\mathbf{e}_{\overline \pi(i)}\|_2 \leq \overline \varepsilon < L_2(\mathbf{A}) \min_{i\in J} |c_i|$.
@@
 But this is exactly the supposition in \eqref{1D}, with $J$ and $\overline \varepsilon$ in place of $[m]$ and $\varepsilon$, respectively.
-Applying the arguments of the case $k=1$ in Sec.~\ref{DUT} to the submatrix $\mathbf{A}_J$ then finally yields $\|\mathbf{A}_j - \mathbf{B}_{\overline J}\mathbf{PD}_j\|_2 \leq \overline  \varepsilon / |c_j|  \leq C_2 \varepsilon$ for $j \in J$.
+The same arguments of the case $k=1$ in Sec.~\ref{DUT} can then be made to show that $\|\mathbf{A}_j - \mathbf{B}_{\overline \pi(J)}\mathbf{PD}_j\|_2 \leq \overline  \varepsilon / |c_j|  \leq C_2 \varepsilon$ for $j \in J$.
 \end{proof}

### 2019-05-06 manuscripts/IEEE/final_submission.tex
probabilistic pigeonholing

@@
 Equating these alternatives amounts to identifying a set of elementary waveforms (the columns of $\mathbf{B}$)  up to some arbitrary scale and their associated sparse coefficients (the entries of $\mathbf{x}_i$) for reconstructing each data point $\mathbf{z}_i$.
-Previous theoretical work addressing the noiseless case $\eta =0$ (e.g., \cite{li2004analysis, Georgiev05, Aharon06, Hillar15}) for matrices $\mathbf{B}$ having $m$ columns has shown that the solution to Prob.~\ref{InverseProblem}, when it exists, is unique up to these equivalent labeling and scaling ambiguities provided the $\mathbf{x}_i$ are sufficiently diverse and the matrix $\mathbf{A}$ satisfies the \textit{spark condition}:
+Previous theoretical work addressing the noiseless case $\eta =0$ (e.g., \cite{li2004analysis, Georgiev05, Aharon06, Hillar15}) for matrices $\mathbf{B}$ having exactly $m$ columns has shown that the solution to Prob.~\ref{InverseProblem}, when it exists, is unique up to these equivalent labeling and scaling ambiguities provided the $\mathbf{x}_i$ are sufficiently diverse and the matrix $\mathbf{A}$ satisfies the \textit{spark condition}:
 \begin{align}\label{SparkCondition}
@@
 Another extension of Thm.~\ref{DeterministicUniquenessTheorem} can be derived from the following analytic characterization of the spark condition.
-Let $\mathbf{A}$  be the $n \times m$ matrix of $nm$ indeterminates $A_{ij}$.
-The reader may work out for themself why substituting real numbers for the $A_{ij}$ yields a matrix satisfying \eqref{SparkCondition} if and only if the following polynomial also evaluates to a nonzero number:
+Letting $\mathbf{A}$ be the $n \times m$ matrix of $nm$ indeterminates $A_{ij}$, the reader may work out for themself why substituting real numbers for the $A_{ij}$ yields a matrix satisfying \eqref{SparkCondition} if and only if the following polynomial also evaluates to a nonzero number:
 \begin{align*}
@@
 Our linear scaling for $\varepsilon$ in \eqref{epsdel} is essentially optimal (e.g., see \cite{arias2013fundamental}), but a basic open problem remains: how many samples are necessary to determine the sparse coding model?
-If $k$ is held fixed or if the size of the support set of reconstructing codes is known to be polynomial in $\overline m$ and $k$, then a practical (polynomial) amount of data suffices.\footnote{In the latter case, a reexamination of the pigeonholing argument in the proof of Thm.~\ref{DeterministicUniquenessTheorem} requires a polynomial number of samples distributed over a polynomial number of supports.} Reasons to be skeptical that this holds in general, however, can be found in \cite{tillmann2014computational, Tillmann15}.
+Our results demonstrate that sparse codes $\mathbf{x}_i$ drawn from only a polynomial number of $k$-dimensional subspaces permit stable identification of the generating dictionary $\mathbf{A}$.
+This lends some legitimacy to the use of the sparse coding model in practice, where data in general are unlikely (if ever) to exhibit the exponentially many possible $k$-wise combinations of dictionary elements as required by (to our knowledge) all previously published results.
+Consequently, if $k$ is held fixed or if the size of the support set of reconstructing codes is known to be polynomial in $\overline m$ and $k$, then a practical (polynomial) amount of data suffices to identify the dictionary.\footnote{In the latter case, a reexamination of the pigeonholing argument in the proof of Thm.~\ref{DeterministicUniquenessTheorem} requires a polynomial number of samples distributed over a polynomial number of supports.} Reasons to be skeptical that this holds in general, however, can be found in \cite{tillmann2014computational, Tillmann15}.
+Even so, in the next section we discuss how probabilistic guarantees can in fact be made for any number of available samples.
 
@@
 \end{proof}
+
+Before moving onto a proof of Thm.~\ref{SLCopt}, we briefly revisit here our discussion on sample complexity from the previous section.
+While it may very well be impossible to exorcise exponentiality from the number of required samples in the deterministic or almost-certain case, our proof of Thm.~\ref{DeterministicUniquenessTheorem} can be extended to hold with some probability for \emph{any} number of samples by appealing instead to a probabilistic pigeonholing at the point in the proof where the deterministic pigeonhole principle is applied to demonstrate that for every $S \in \mathcal{H}$, there exist $k$ vectors $\mathbf{x}_i$ supported on $S$ whose corresponding $\mathbf{\overline x}_i$ all share the same support.\footnote{A famous example of such an argument is the counter-intuitive "birthday paradox", which demonstrates that the probability of two people having the same birthday in a room of twenty-three is in fact greater than 50\%.} Given insufficient samples, this point in the proof has some less-than-certain probability of success for each $S \in \mathcal{H}$.
+Nonetheless, simulations confirm that the probability of our guarantees holding saturates when the number of samples reaches only a small fraction of the deterministic sample complexity.
 

### 2019-05-07 manuscripts/IEEE/final_submission.tex
some prose

@@
 % mention regularity is probably not necessary
-% make theorem 3 a corollary?
 % have i talked about making deterministic A?
@@
 % IS THEOREM 3 AND ITS COROLLARY CORRECTLY STATED??
+% mention use of coherence instead of L_k? for practical criteria?
 
@@
 
-Motivated by these discoveries and more recent work linked to the young field of ``compressive sensing" which proposed a theory of information transmission through random wiring bottlenecks in the brain \cite{Isely10}, we address when optimal dictionaries for sparse representation are indeed identifiable from data.
-Answers to this question may also have relevant implications in practice; for example, in justifying the identification of forged paintings by their anomalous sparse representations \cite{hughes2010}, or [more citations?
-kinda weak imo].
+Motivated by these discoveries and more recent work proposing a theory of information transmission through random wiring bottlenecks in the brain \cite{Isely10}, linked to the young field of ``compressive sensing", we address when optimal dictionaries for sparse representation are indeed identifiable from data.
+Answers to this question may also have implications in practice wherever an appeal is made to the latent sparse structure of data (e.g.
+forgery detection \cite{hughes2010, olshausen2010applied}; brain recordings \cite{jung2001imaging, agarwal2014spatially, lee2016sparse}; and gene expression \cite{wu2016stability}).
 While several algorithms which provably recover unique latent dictionaries under specific conditions have recently been proposed (see \cite[Sec.~I-E]{Sun16} for a summary of the state-of-the-art), few theorems can be invoked to justify the consistency of inference under this model of data more broadly.
 To our knowledge, a universal guarantee of the uniqueness and stability of learned dictionaries and the sparse representations they induce over noisy data has yet to appear in the literature.
+% in justifying the identification of forged paintings by their anomalous sparse representations \cite{hughes2010},
 
@@
 
-Every $n \times \overline m$ matrix $\mathbf{B}$ for which there are $k$-sparse $\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N$ satisfying \mbox{$\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \varepsilon$} for $i = 0, \ldots, N$ has $\overline m \geq m$, and provided $\overline m < mr / (r-1)$, there is a permutation matrix $\mathbf{P}$ and an invertible diagonal matrix $\mathbf{D}$ such that:
+Every $n \times \overline m$ matrix $\mathbf{B}$ for which there are $k$-sparse $\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N$ satisfying \mbox{$\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \varepsilon$} for $i = 0, \ldots, N$ has $\overline m \geq m$, and provided $\overline m (r-1) < mr$, there is a permutation matrix $\mathbf{P}$ and an invertible diagonal matrix $\mathbf{D}$ such that:
 \begin{align}\label{Cstable}
@@
 There is a polynomial in the entries of $\mathbf{A}$ and the $\mathbf{x}_i$ that evaluates to a nonzero number only when $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$.
-In particular, all -- except for a Borel set of measure zero -- substitutions impart to $Y$ this property.
+In particular, almost all substitutions impart to $Y$ this property.
 \end{theorem}
@@
 
-Thus, drawing the dictionary and supported sparse coefficients from any continuous probability distribution almost certainly generates data with a stable sparse representation.
+Thus, drawing the dictionary and supported sparse coefficients from any continuous probability distribution almost always generates data with a stable sparse representation.
 
@@
 Our results demonstrate that sparse codes $\mathbf{x}_i$ drawn from only a polynomial number of $k$-dimensional subspaces permit stable identification of the generating dictionary $\mathbf{A}$.
-This lends some legitimacy to the use of the sparse coding model in practice, where data in general are unlikely (if ever) to exhibit the exponentially many possible $k$-wise combinations of dictionary elements as required by (to our knowledge) all previously published results.
+This lends some legitimacy to the use of the sparse coding model in practice, where data in general are unlikely (if ever) to exhibit the exponentially many possible $k$-wise combinations of dictionary elements required by (to our knowledge) all previously published results.
 Consequently, if $k$ is held fixed or if the size of the support set of reconstructing codes is known to be polynomial in $\overline m$ and $k$, then a practical (polynomial) amount of data suffices to identify the dictionary.\footnote{In the latter case, a reexamination of the pigeonholing argument in the proof of Thm.~\ref{DeterministicUniquenessTheorem} requires a polynomial number of samples distributed over a polynomial number of supports.} Reasons to be skeptical that this holds in general, however, can be found in \cite{tillmann2014computational, Tillmann15}.
@@
 \end{align}
-then $\overline m \geq m$, and provided $\overline m < mr /(r-1)$, there is a permutation matrix $\mathbf{P}$ and invertible diagonal $\mathbf{D}$ such that:
+then $\overline m \geq m$, and provided $\overline m (r-1) < mr$, there is a permutation matrix $\mathbf{P}$ and invertible diagonal $\mathbf{D}$ such that:
 \begin{align}\label{MainLemmaBPD}
@@
 The practically-minded reader should note that the explicit constants $C_1$ and $C_2$ are effectively computable: the quantity $L_k$ may be calculated as the smallest singular value of a certain matrix, while the quantity $\xi$ involves computing ``canonical angles'' between subspaces, which reduce again to an efficient singular value decomposition.
-There is no known fast computation of $L_k$ in general, however, since even $L_{k} > 0$ is NP-hard \cite{tillmann2014computational}; although fixing $k$ yields polynomial complexity.
+There is no known fast computation of $L_k$ in general, however, since even $L_{k} > 0$ is NP-hard \cite{tillmann2014computational}, although
+%efficiently computable bounds have been proposed (e.g. the ``mutual coherence" of a matrix \cite{donoho2003optimally}); alternatively, 
+fixing $k$ yields polynomial complexity.
 Moreover, calculating $C_2$ requires an exponential number of queries to $\xi$ unless $r$ is held fixed, too (e.g., the ``cyclic order'' hypergraphs described above have $r=k$).
-Thus, as presented, $C_1$ and $C_2$ are not efficiently computable in general.
+Thus, as presented, $C_1$ and $C_2$ are not efficiently computable in general, but efficient sub-cases do exist and may be of practical relevance.
 
@@
 
-Before moving onto a proof of Thm.~\ref{SLCopt}, we briefly revisit here our discussion on sample complexity from the previous section.
-While it may very well be impossible to exorcise exponentiality from the number of required samples in the deterministic or almost-certain case, our proof of Thm.~\ref{DeterministicUniquenessTheorem} can be extended to hold with some probability for \emph{any} number of samples by appealing instead to a probabilistic pigeonholing at the point in the proof where the deterministic pigeonhole principle is applied to demonstrate that for every $S \in \mathcal{H}$, there exist $k$ vectors $\mathbf{x}_i$ supported on $S$ whose corresponding $\mathbf{\overline x}_i$ all share the same support.\footnote{A famous example of such an argument is the counter-intuitive "birthday paradox", which demonstrates that the probability of two people having the same birthday in a room of twenty-three is in fact greater than 50\%.} Given insufficient samples, this point in the proof has some less-than-certain probability of success for each $S \in \mathcal{H}$.
-Nonetheless, simulations confirm that the probability of our guarantees holding saturates when the number of samples reaches only a small fraction of the deterministic sample complexity.
+Before moving on to our proof of Thm.~\ref{SLCopt}, we briefly revisit here our discussion on sample complexity from the end of the previous section.
+While an exponential number of samples may very well prove to be necessary in the deterministic or almost-certain case, our proof of Thm.~\ref{DeterministicUniquenessTheorem} can be extended to hold with some probability for \emph{any} number of samples by alternative appeal to a probabilistic pigeonholing at the point early in the proof where the (deterministic) pigeonhole principle is applied to show that for every $S \in \mathcal{H}$, there exist $k$ vectors $\mathbf{x}_i$ supported on $S$ whose corresponding $\mathbf{\overline x}_i$ all share the same support.\footnote{A famous example of such an argument is the counter-intuitive "birthday paradox", which demonstrates that the probability of two people having the same birthday in a room of twenty-three is in fact greater than 50\%.} Given insufficient samples, this argument has some less-than-certain probability of being valid for each $S \in \mathcal{H}$.
+Nonetheless, cursory simulations with small hypergraphs confirm that the probability of success very quickly approaches one once the number of samples $N$ surpasses a small fraction of the deterministic sample complexity.
 

### 2019-05-07 final_submission.tex
Chaz edits

--- 2019-05-07 manuscripts/IEEE/final_submission.tex
@@
 % \cite{sato1975method}
-\IEEEPARstart{A}{}common contemporary approach to problems in signal processing and pattern analysis is to view each of $N$ observed $n$-dimensional signal samples as a (noisy) linear combination of at most $k$ elementary waveforms drawn from some unknown ``dictionary" of size $m \ll N$ (see \cite{Zhang15} for a comprehensive review of this and related models).
+\IEEEPARstart{A}{}common modern approach to problems in signal processing and pattern analysis is to view each of $N$ observed $n$-dimensional signal samples as a (noisy) linear combination of at most $k$ elementary waveforms drawn from some unknown ``dictionary" of size $m \ll N$ (see \cite{Zhang15} for a comprehensive review of this and related models).
 Optimizing dictionaries subject to this and related sparsity constraints has revealed seemingly characteristic sparse structure in several signal classes of current interest (e.g., in vision \cite{wang2015sparse}).
@@
 More specifically,  we show that dictionaries injective on a sparse domain are identifiable from \mbox{$N = m(k-1){m \choose k} + m$} noisy sparse linear combinations of their columns up to an error that is linear in the noise (Thm.~\ref{DeterministicUniquenessTheorem}).
-In fact, provided $n \geq \min(2k,m)$, in almost all cases the problem is well-posed\footnote{as per Hadamard \cite{Hadamard1902}} given enough data (Cor.~\ref{ProbabilisticCor}).
+In fact, provided $n \geq \min(2k,m)$, in almost all cases the problem is well-posed (as per Hadamard \cite{Hadamard1902}) given enough data (Cor.~\ref{ProbabilisticCor}).
 These guarantees also hold for a related (and perhaps more commonly posed) optimization problem which instead seeks a dictionary minimizing the average number of elementary waveforms required to reconstruct each sample of the dataset.
@@
 \end{align}
-for $k$-\emph{sparse} $\mathbf{x}_i \in \mathbb{R}^m$ having at most $k<m$ nonzero entries and \emph{noise} $\mathbf{n}_i \in \mathbb{R}^n$, with bounded norm $\| \mathbf{n}_i \|_2 \leq  \eta$ representing our worst-case uncertainty\footnote{This captures uncertainty in model parameters $\mathbf{A}$ and $\mathbf{x}_i$ in addition to external sources of measurement error.} in measuring the product $\mathbf{A}\mathbf{x}_i$.
+for $k$-\emph{sparse} $\mathbf{x}_i \in \mathbb{R}^m$ having at most $k<m$ nonzero entries and \emph{noise} $\mathbf{n}_i \in \mathbb{R}^n$, with bounded norm $\| \mathbf{n}_i \|_2 \leq  \eta$ representing our worst-case uncertainty in measuring the product $\mathbf{A}\mathbf{x}_i$.
 The first mathematical problem we consider is:
@@
 Note that, stated as such, every solution to this problem represents infinitely many equivalent alternatives $\mathbf{BPD}$ and $\mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_1, \ldots, \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_N$ parametrized by a choice of permutation matrix $\mathbf{P}$ and invertible diagonal matrix $\mathbf{D}$.
-Equating these alternatives amounts to identifying a set of elementary waveforms (the columns of $\mathbf{B}$)  up to some arbitrary scale and their associated sparse coefficients (the entries of $\mathbf{x}_i$) for reconstructing each data point $\mathbf{z}_i$.
+Identifying these alternatives identifies a set of elementary waveforms (the columns of $\mathbf{B}$)  up to some arbitrary scale and their associated sparse coefficients (the entries of $\mathbf{x}_i$) for reconstructing each data point $\mathbf{z}_i$.
 Previous theoretical work addressing the noiseless case $\eta =0$ (e.g., \cite{li2004analysis, Georgiev05, Aharon06, Hillar15}) for matrices $\mathbf{B}$ having exactly $m$ columns has shown that the solution to Prob.~\ref{InverseProblem}, when it exists, is unique up to these equivalent labeling and scaling ambiguities provided the $\mathbf{x}_i$ are sufficiently diverse and the matrix $\mathbf{A}$ satisfies the \textit{spark condition}:
@@
 Now, consider any dataset $Z$ generated as in \eqref{LinearModel} with $\eta \leq \frac{1}{2} \varepsilon(\delta_1, \delta_2)$.
-It follows from the triangle inequality that any $n \times m$ matrix $\mathbf{B}$ and $k$-sparse $\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N$ solving Prob.~\ref{InverseProblem} are necessarily within $\delta_1$ and $\delta_2$ of the original dictionary $\mathbf{A}$ and codes $\mathbf{x}_1, ..., \mathbf{x}_N$, respectively.\footnote{We should mention the different norms measuring recovery in \eqref{def1} are meant only to reflect the typically distinct semantics of the dictionary and sparse codes in modeling data.}
+It follows from the triangle inequality that any $n \times m$ matrix $\mathbf{B}$ and $k$-sparse $\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N$ solving Prob.~\ref{InverseProblem} are necessarily within $\delta_1$ and $\delta_2$ of the original dictionary $\mathbf{A}$ and codes $\mathbf{x}_1, ..., \mathbf{x}_N$, respectively.\footnote{We should mention the different norms in \eqref{def1} reflect the distinct meanings typically ascribed to the dictionary and sparse codes in modeling data.}
 
@@
 \begin{align}\label{Cstable}
-\|\mathbf{A}_j- \mathbf{B}_{\overline J} \mathbf{PD}_j\|_2 \leq C_1 \varepsilon \ \ \text{for all } j \in J
+\|\mathbf{A}_j- \mathbf{BPD}_j\|_2 \leq C_1 \varepsilon \ \ \text{for all } j \in J
 \end{align}
 %
-for some $J$ and $\overline J$ both of size \mbox{$m - (r-1)(\overline m - m)$}. 
+for some $J$ of size \mbox{$m - (r-1)(\overline m - m)$}. 
 % $\overline m - r(\overline m - m)$
@@
 %\|\mathbf{x}^J_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}^{\overline J}_i\|_1 &\leq  \left( \frac{ 1+C_1 \|\mathbf{x}^{J}_i\|_1 }{ L_{2k}(\mathbf{A}) -  C_1\varepsilon } \right) \varepsilon \ \  \text{for $i \in [N]$}.
-\|(\mathbf{x}_i)_J - \left(\mathbf{D}^{-1}\mathbf{P}^{\top}\right)_{\overline J}(\mathbf{\overline x}_i)_{\overline J}\|_1 &\leq  \left( \frac{ 1+C_1 \|\mathbf{x}_i\|_1 }{ L_{2k}(\mathbf{A}) -  C_1\varepsilon } \right) \varepsilon,
+\|(\mathbf{x}_i)_J - (\mathbf{D}^{-1}\mathbf{P}^{\top} \mathbf{\overline x}_i)_J\|_1 &\leq  \left( \frac{ 1+C_1 \|\mathbf{x}_i\|_1 }{ L_{2k}(\mathbf{A}) -  C_1\varepsilon } \right) \varepsilon,
 \end{align}
 %
-where $(\mathbf{x}_i)_J$ and $(\mathbf{\overline x}_i)_{\overline J}$ here represent subvectors formed from restricting to coefficients indexed by $J$ and $\overline J$, respectively. 
+where $(\mathbf{x}_i)_J$ here represents the subvector formed from restricting to coefficients indexed by $J$. 
 \end{theorem}
@@
 Fix a matrix $\mathbf{A}$ and vectors $\mathbf{x}_i$ satisfying the assumptions of Thm.~\ref{DeterministicUniquenessTheorem}, only now with over $(k-1)\left[ {\overline m \choose k} + |\mathcal{H}|k{\overline m \choose k-1}\right]$ vectors supported in general linear position in each $S \in \mathcal{H}$.
-Every solution to Prob.~\ref{OptimizationProblem} (with $\eta \gets \varepsilon/2$) satisfies recovery guarantees \eqref{Cstable} and \eqref{b-PDa} when the corresponding bounds on $\eta$ are met.
+Every solution to Prob.~\ref{OptimizationProblem} (with $\eta = \varepsilon/2$) satisfies recovery guarantees \eqref{Cstable} and \eqref{b-PDa} when the corresponding bounds on $\eta$ are met.
 \end{theorem}
@@
 \end{align*}
-contradicting our assumed upper bound on $\varepsilon$.
-Hence, the map $\pi$ is injective and it must be the case that $\overline m \geq m$.
-Setting $\overline J = \pi([m])$ and letting $P = \left( \mathbf{e}_{\pi(1)} \cdots \mathbf{e}_{\pi(m)}\right)$ and $D = \text{diag}(\frac{\overline{c}_1}{c_1},\ldots,\frac{\overline{c}_m}{c_m})$, we may rewrite \eqref{1D} to see that, for all $j \in [m]$:
+contradicting our assumed upper bound on $\varepsilon$. Hence, the map $\pi$ is injective and it must be the case that $\overline m \geq m$. %Setting $\overline J = \pi([m])$ and 
+Letting $\mathbf{P}$ and $\mathbf{D}$ be the $\overline m \times \overline m$ permutation and invertible diagonal matrices with, respectively, columns $\mathbf{e}_{\pi(j)}$ and $\frac{\overline{c}_j}{c_j}\mathbf{e}_j$ for $j \in [m]$ (and, say, $\mathbf{e}_j$ otherwise), we may rewrite \eqref{1D} to see that for all $j \in [m]$:
 \begin{align*}
-\|\mathbf{A}_j - \mathbf{B}_{\overline J}\mathbf{PD}_j\|_2 
+\|\mathbf{A}_j - \mathbf{BPD}_j\|_2 
 = \|\mathbf{A}_j - \frac{\overline{c}_j}{c_j}\mathbf{B}_{\pi(j)}\|_2 
@@
 \begin{align}\label{MainLemmaBPD}
-\|\mathbf{A}_j - \mathbf{B}_{\overline J} \mathbf{PD}_j\|_2 \leq C_2 \varepsilon \ \  \text{for } j \in J
+\|\mathbf{A}_j - \mathbf{B}\mathbf{PD}_j\|_2 \leq C_2 \varepsilon \ \  \text{for } j \in J
 \end{align}
-for some $J$ and $\overline J$ both of size \mbox{$m - (r-1)(\overline m - m)$}.
+for some $J$ of size \mbox{$m - (r-1)(\overline m - m)$}.
 \end{lemma}
@@
 
+\section{EXTRA}
+An additional implication of Thm.~\ref{DeterministicUniquenessTheorem} of potential relevance to Prob.~\ref{OptimizationProblem} is the implied lower bound on $L_{2k}(\mathbf{B})$ in the case where $\mathbf{A}$ satisfies \eqref{SparkCondition}.
+Due to complexity issues, Prob.~\ref{SLCopt} is often solved by first replacing the $\|\cdot\|_0$-norm with the $\|\cdot\|_1$-norm.
+The compressive sensing literature informs us that sparse codes are in fact stably recoverable via minimization of the $\|\cdot\|_1$-norm provided $L_{2k}(\mathbf{A})$ is large enough.
+Thm.~\ref{DeterministicUniquenessTheorem} guarantees that for large enough $L_{2k}(\mathbf{A})$, all valid solutions also have the property that their sparse codes can be inferred by minimization of the $\|\cdot\|_1$ norm.
+Does this matter..?
+
 \textbf{Acknowledgement.} We thank F. Sommer and D. Rhea for early thoughts, and I. Morris for posting \eqref{eqdim} online.
@@
 %
-then $\overline m \geq m$, and if $\overline m < mr / (r-1)$ then the map $i \mapsto \cap \pi(\sigma(i))$ is an injective map to $[\overline m]$ from some $J \subseteq [m]$ of size $m - (r-1)(\overline m - m)$.\footnote{Recall $\sigma$ from Def.~\ref{sip}.}  %In particular, if $\overline m = m$ then $\pi$ is induced by a permutation on $[m]$.
+then $\overline m \geq m$, and if $\overline m  (r-1) < mr$ then the map $i \mapsto \cap \pi(\sigma(i))$ is an injective map to $[\overline m]$ from some $J \subseteq [m]$ of size $m - (r-1)(\overline m - m)$.\footnote{Recall $\sigma$ from Def.~\ref{sip}.}  %In particular, if $\overline m = m$ then $\pi$ is induced by a permutation on $[m]$.
 \end{lemma}
@@
 But this is exactly the supposition in \eqref{1D}, with $J$ and $\overline \varepsilon$ in place of $[m]$ and $\varepsilon$, respectively.
-The same arguments of the case $k=1$ in Sec.~\ref{DUT} can then be made to show that $\|\mathbf{A}_j - \mathbf{B}_{\overline \pi(J)}\mathbf{PD}_j\|_2 \leq \overline  \varepsilon / |c_j|  \leq C_2 \varepsilon$ for $j \in J$.
+The same arguments of the case $k=1$ in Sec.~\ref{DUT} can then be made to show that for any $\overline m \times \overline m$ permutation and invertible diagonal matrices $\mathbf{P}$ and $\mathbf{D}$ with, respectively, columns $\mathbf{e}_{\pi(i)}$ and $\frac{\overline{c}_i}{c_i}\mathbf{e}_i$ for $i \in J$ (and, say, $\mathbf{e}_i$ otherwise) we have $\|\mathbf{A}_i - \mathbf{B}\mathbf{PD}_i \|_2 \leq \overline  \varepsilon / |c_i|  \leq C_2 \varepsilon$ for all $i \in J$.
 \end{proof}

### 2019-05-07 manuscripts/IEEE/submission/referee_responses.txt
added response file

-------------------------------------
Author responses to referees:
"On the uniqueness and stability of dictionaries 
for sparse representation of noisy signals"
C. Garfinkle, C. Hillar
-------------------------------------

REVIEWER 1

Summary 
The paper provides conditions under which dictionary learning is stable (in particular to noise), which apply in almost all cases. This, the authors claim, provides some support for the empirical observation that different dictionary learning methods lead to very similar dictionaries.

Comments 
The paper is quite well-written. I am not an expert in dictionary learning per se, but if these are truly the first perturbation bounds for dictionary learning, then they are worth publishing in TSP.

Other comments
1. “then each submatrix formed from 2k of its columns or less has a strictly positive lower bound.” What is k here?

-------------------------------------
Response: The full sentence is: "By compactness of the unit sphere, injective linear maps have nonzero lower bound; hence, if M satisfies (2), then each submatrix formed from 2k of its columns or less has a strictly positive lower bound." Here, k is the sparsity referred to in (2), which states that a matrix M satisfies the spark condition if Mx1 = Mx2 implies x1 = x2, for all k-sparse x1, x2.
-------------------------------------

2. 3 lines below (5): why is ∪H = [m] required?

-------------------------------------
Response: The requirement becomes clearer recalling the definition L_k := L_(m choose k). Our statement is then:

L_(m choose 2) \geq L_2H \geq L_(m choose 2k)

The second inequality follows from the fact that 2H is a subset of (m choose 2k). The first inequality follows from the fact that (m choose 2) is a subset of 2H, provided ∪H = [m], since only then can every pair of columns be captured by the union of two supports in H.
-------------------------------------

3. Are J and Jbar in Theorem 1 of same size?

-------------------------------------
Response: Yes. We have clarified this ambiguity.
-------------------------------------

4. About Theorem 1. I am a little worried about C1 depending on A and the xi’s. It could make some of parts of the statement void. Presumably, one sees these as fixed, and looks at the possible B’s and possible \bar{x}_i’s satisfying |Ax_i − B\bar{x}_i|_2 \leq \epsilon?

-------------------------------------
Response: That is correct. We see no need to worry. Fixing A and the x_i's fixes the numbers L_2k(A) and C_1(A,x_i). Theorem 1 then states that, provided \epsilon < L_2k/C_1, all such B's and \bar{x}_i's are close to A and the x_i's, respectively (see (6) and (7)). To rephrase via the triangle inequality, all good enough B’s and \bar{x}_i’s are similar to one another, or identical when \epsilon = 0.
-------------------------------------

5. Also, in (7), using xi to denote the restriction of xi to J, and similarly for xi, could lead to confusion, in particular if the reader glances at the result without reading the last sentence.

-------------------------------------
Response: We have altered the notation to abate this potential confusion.
-------------------------------------

6. “A practical implication of Thm. 1 is the following: there is an effective procedure sufficient to affirm if a proposed solution to Prob. 1 is indeed unique (up to noise and inherent ambiguities). One need simply to check that the matrix and codes satisfy the (computable) assumptions of Thm. 1 on A and the xi.” I question whether the assumptions of Theorem 1 are indeed computable. Could the authors elaborate on that?

-------------------------------------
Response: The assumptions of Theorem 1 are:
i) L_2H(A) > 0 for an r-regular H with the SIP.
ii) For each S in H, there are more than (k-1)(mCk) k-sparse vectors x_i supported on S.
iii) \epsilon < L_2(A)/C_1 to guarantee (6) and \epsilon < L_2k(A)/C_1 to guarantee (7)

Conditions (i) and (ii) are obviously computable, though it is another question, and what we assume to be the reviewer's concern, whether or not there exists an efficient algorithm to do so. Condition (iii) relies on the definition of C1, which appears in Section III. Some comments on this appear in section III:

"The pragmatic reader should note that the explicit constants C1 and C2 are effectively computable: the quantity Lk may be calculated as the smallest singular value of a certain matrix, while the quantity ξ involves computing “canonical angles” between subspaces, which reduce again to an efficient singular value decomposition. There is no known fast computation of L in general, however, since even L > 0 is NP-hard [19]; although fixing k yields polynomial complexity. Moreover, calculating C2 requires an exponential number of queries to ξ unless r is held fixed, too (e.g., the “cyclic order” hypergraphs described above have r = k). Thus, as presented, C1 and C2 are not efficiently computable."
-------------------------------------

7. I am not sure what “substitutions” means in Theorem 3. Does that mean “choices” of A and x1, . . . , xN such that Axi = yi? Isn’t Theorem 3 a simple corollary of Theorem 1, together with the remark in the couple of paragraph above it? If so, I suggest making it a corollary. In the same vein, I am not sure that Proposition 1 is rigorous enough to make it a proposition. It could be stated as an informal claim instead.

-------------------------------------
Response: "Substitution" here mean such assignments or choices of real numbers to the indeterminate variables, yes. We frame it as a theorem and not a corollary because we draw the important Corollary 2 directly from it. We have no qualms downgrading Proposition 1 to an informal claim, however.

[NOTE: should we just make everything a corollary of Thm 1..? Even Thm 2?]
-------------------------------------

8. The perturbation bound is used by the authors to provide some explanation for why, in practice, different methods lead to similar dictionaries. Can that also be used to explain the second (bold) part of their observation that “[these waveforms] appear in dictionaries learned by a variety of algorithms trained with respect to different natural image datasets.”? Just curious.

-------------------------------------
Response: To be clear, this (bold) observation is just an observation which motivates the work. Imagining natural image patches to form a population which satisfies (1) with respect to some ground truth dictionary A, we have shown that there exists a sufficient number of samples to uniquely identify it or something close to it via approximate solutions. Given this fundamental stability and uniqueness of the problem solutions, the fact that a variety of methods geared to approximately solve Problems 1 and 2 all seem to capture similar structure is much less surprising. 
-------------------------------------

REVIEWER 2

Comments
This paper studies the conditions under which the dictionary learning problem is well-posed, under the assumption of additive noise. Overall I think it is nicely written.
I have some doubts about (1) efficiency of checking the assumption stated in theorem 1; (2) numerically solving the optimization problem as stated in eqn (4) in practice. I personally think rephrasing some of the graph theoretic terms will make the paper easier to follow, but that might just be personal preference.

REVIEWER 3

Comments:
This paper considers the uniqueness and stability of sparse dictionary learning problem. The paper is well written and organized. Although it is a pure theory paper, it is fairly easy to follow the key ideas without messing up with the proofs. Below are some more detailed comments:

1. This work considers the uniqueness and stability of SIP condition of the dictionary A. One of the fundamental questions is can the Problem 2 be solved to global optimality under these conditions? Because dictionary learning is a bilinear and hence nonconvex problems, solving Problem 2 with l0 norm could still be intractable even though uniqueness condition exists. Can the author comment on this issue of achieving global optimality for solving Problem 2?

-------------------------------------
Response: Theorem 2 guarantees that all globally optimal solutions to Problem 2 are identical up to noise and inherent permutation/scaling ambiguities. This doesn't change the fact that computing any one such global solution given data is still NP-hard.

As l0 norm is intractable, does all the properties still hold for l1 norm minimization? Can we solve it efficiently (polynomial time) to global optimality? Similar issue for other works, such as
https://arxiv.org/pdf/1807.05595.pdf

We make no claims in this paper about l1-norm minimization, though we are hopeful a clever reader may find some way to build off our results and derive related guarantees for this continuous relaxation of the sparse coding problem.

But heuristic methods are proposed there to check global optimality. A discussion and elaboration on this could be very helpful here.

Yes, we only claim that our general uniqueness criterion provide a (not necessarily efficient) means of checking the globality of a proposed solution. It could be that in certain restricted cases these conditions are efficiently computable, but this is not the case in general.
-------------------------------------

2. The number of samples N >= (k-1) ( m choose k) for the uniqueness condition grows exponentially with respect to k. Is this condition optimal w.r.t. SIP property, or can be reduced? On the other hand, is there any relationship between SIP and RIP conditions? The lower bound of (5) looks similar to RIP conditions.

-------------------------------------
Response: We comment on sample complexity in the last paragraph of Section II:

"We close this section with comments on optimality. Our linear scaling for ε in (8) is essentially optimal (e.g., see [23]), but a basic open problem remains: how many samples are necessary to determine the sparse coding model? If k is held fixed or if the size of the support set of reconstructing codes is known to be polynomial in m and k, then a practical (polynomial) amount of data suffices. [footnote: In the latter case, a reexamination of the pigeonholing argument in the proof of Thm. 1 requires a polynomial number of samples distributed over a polynomial number of supports.] Reasons to be skeptical that this holds in general, however, can be found in [19], [24]"

In general, our conditions are sufficient but not proven necessary, and we doubt we have achieved the tightest possible bounds all around.

As for the SIP and RIP, a footnote points out the relation between our matrix lower bound L_H(M) and the RIP:

"We note that $1 - \sqrt{k} L_k(\mathbf{M})$ is known as the asymmetric lower restricted isometry constant for matrices $\mathbf{M}$ with unit $\ell_2$-norm columns"
-------------------------------------

3. Corollary 2 suggests that A and x satisfying SIP can be generated by drawing the entries independently from a continuous distribution. This is often unrealizable in practice. Is there any deterministic way of generating A and x with SIP condition?

-------------------------------------
Response: In the prose surrounding Corollary 1 we give a deterministic construction of sparse vectors x_i satisfying the constraints of Theorem 1.

TODO : can we deterministically generate matrices injective on SIP hyper graphs? The (mCk)-hypergraph is one such possibility, so maybe not in general? But for special cases (convolution matrices..?)
-------------------------------------

### 2019-05-07 manuscripts/IEEE/final_submission.tex
small updates

@@
 However, universal conditions guaranteeing the stability of these learned features in the presence of measurement noise have yet to be described.
-Here, we prove very generally that optimal dictionaries and sparse codes are unique up to measurement error for all diverse enough datasets generated by the sparse coding model.
+We prove very generally that optimal dictionaries and sparse codes are unique up to measurement error for all diverse enough datasets generated by the sparse coding model.
 Applications are given to data analysis, engineering, and neuroscience.
@@
 
-Motivated by these discoveries and more recent work proposing a theory of information transmission through random wiring bottlenecks in the brain \cite{Isely10}, linked to the young field of ``compressive sensing", we address when optimal dictionaries for sparse representation are indeed identifiable from data.
+Motivated by these discoveries and more recent work proposing a theory of information transmission through random wiring bottlenecks in the brain \cite{Isely10}, linked to the field of ``compressed sensing", we address when optimal dictionaries for sparse representation are indeed identifiable from data.
 Answers to this question may also have implications in practice wherever an appeal is made to the latent sparse structure of data (e.g.
@@
 More specifically,  we show that dictionaries injective on a sparse domain are identifiable from \mbox{$N = m(k-1){m \choose k} + m$} noisy sparse linear combinations of their columns up to an error that is linear in the noise (Thm.~\ref{DeterministicUniquenessTheorem}).
-In fact, provided $n \geq \min(2k,m)$, in almost all cases the problem is well-posed\footnote{as per Hadamard \cite{Hadamard1902}} given enough data (Cor.~\ref{ProbabilisticCor}).
-These guarantees also hold for a related (and perhaps more commonly posed) optimization problem which instead seeks a dictionary minimizing the average number of elementary waveforms required to reconstruct each sample of the dataset.
+In fact, provided $n \geq \min(2k,m)$, in almost all cases the problem is well-posed (as per Hadamard \cite{Hadamard1902}) given enough data (Cor.~\ref{ProbabilisticCor}).
+These guarantees also hold for a related (and perhaps more commonly posed) optimization problem which seeks a dictionary minimizing the average number of elementary waveforms required to reconstruct each sample of the dataset.
 Importantly, in both cases our explicit, universal guarantees apply without the imposition of \emph{any} constraints on learned dictionaries  (e.g.
@@
 
-Note that, stated as such, every solution to this problem represents infinitely many equivalent alternatives $\mathbf{BPD}$ and $\mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_1, \ldots, \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_N$ parametrized by a choice of permutation matrix $\mathbf{P}$ and invertible diagonal matrix $\mathbf{D}$.
-Equating these alternatives amounts to identifying a set of elementary waveforms (the columns of $\mathbf{B}$)  up to some arbitrary scale and their associated sparse coefficients (the entries of $\mathbf{x}_i$) for reconstructing each data point $\mathbf{z}_i$.
+Note that as stated, every solution to this problem represents infinitely many equivalent alternatives $\mathbf{BPD}$ and $\mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_1, \ldots, \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_N$ parametrized by a choice of permutation matrix $\mathbf{P}$ and invertible diagonal matrix $\mathbf{D}$.
+Identifying these alternatives gives a set of elementary waveforms (the columns of $\mathbf{B}$)  up to some arbitrary scale and their associated sparse coefficients (the entries of $\mathbf{x}_i$) for reconstructing each data point $\mathbf{z}_i$.
 Previous theoretical work addressing the noiseless case $\eta =0$ (e.g., \cite{li2004analysis, Georgiev05, Aharon06, Hillar15}) for matrices $\mathbf{B}$ having exactly $m$ columns has shown that the solution to Prob.~\ref{InverseProblem}, when it exists, is unique up to these equivalent labeling and scaling ambiguities provided the $\mathbf{x}_i$ are sufficiently diverse and the matrix $\mathbf{A}$ satisfies the \textit{spark condition}:
@@
 To see how Prob.
-\ref{InverseProblem} motivates this definition, suppose that $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$ and fix $\delta_1, \delta_2$ to be the desired accuracies of recovery in \eqref{def1}.
+\ref{InverseProblem} motivates Def.
+\ref{maindef}, suppose that $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$ and fix $\delta_1, \delta_2$ to be the desired accuracies of recovery in \eqref{def1}.
 Now, consider any dataset $Z$ generated as in \eqref{LinearModel} with $\eta \leq \frac{1}{2} \varepsilon(\delta_1, \delta_2)$.
-It follows from the triangle inequality that any $n \times m$ matrix $\mathbf{B}$ and $k$-sparse $\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N$ solving Prob.~\ref{InverseProblem} are necessarily within $\delta_1$ and $\delta_2$ of the original dictionary $\mathbf{A}$ and codes $\mathbf{x}_1, ..., \mathbf{x}_N$, respectively.\footnote{We should mention the different norms measuring recovery in \eqref{def1} are meant only to reflect the typically distinct semantics of the dictionary and sparse codes in modeling data.}
+It follows from the triangle inequality that any $n \times m$ matrix $\mathbf{B}$ and $k$-sparse $\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N$ solving Prob.~\ref{InverseProblem} are necessarily within $\delta_1$ and $\delta_2$ of the original dictionary $\mathbf{A}$ and codes $\mathbf{x}_1, ..., \mathbf{x}_N$, respectively.\footnote{We should mention the different norms in \eqref{def1} reflect the distinct meanings typically ascribed to the dictionary and sparse codes in modeling data.}
 
@@
 
-A detailed statement of our results requires that we first identify some combinatorial criteria on the supports\footnote{Recall a vector $\mathbf{x}$ is said to be \emph{supported} in $S$ when $\mathbf{x} \in \text{\rm span}\{\mathbf{e}_j: j\in S\}$, the $\mathbf{e}_j$ forming the standard column basis.} of sparse vectors.
+A detailed statement of our results requires that we first identify some combinatorial criteria on the supports\footnote{Recall a vector $\mathbf{x}$ is said to be \emph{supported} in $S$ when $\mathbf{x} \in \text{\rm span}\{\mathbf{e}_j: j\in S\}$, with $\mathbf{e}_j$ forming the standard column basis.} of sparse vectors.
 Let $\{1, \ldots, m\}$ be denoted $[m]$, its power set $2^{[m]}$, and ${[m] \choose k}$ the set of subsets of $[m]$ of size $k$.
-A \emph{hypergraph} on vertices $[m]$  is just any subset $\mathcal{H} \subseteq 2^{[m]}$.
+A \emph{hypergraph} on vertices $[m]$  is simply any subset $\mathcal{H} \subseteq 2^{[m]}$.
 We say $\mathcal{H}$ is \textit{$k$-uniform} when in fact $\mathcal{H} \subseteq {[m] \choose k}$.
@@
 Another extension of Thm.~\ref{DeterministicUniquenessTheorem} can be derived from the following analytic characterization of the spark condition.
-Letting $\mathbf{A}$ be the $n \times m$ matrix of $nm$ indeterminates $A_{ij}$, the reader may work out for themself why substituting real numbers for the $A_{ij}$ yields a matrix satisfying \eqref{SparkCondition} if and only if the following polynomial also evaluates to a nonzero number:
+Letting $\mathbf{A}$ be the $n \times m$ matrix of $nm$ indeterminates $A_{ij}$, the reader may work out why substituting real numbers for the $A_{ij}$ yields a matrix satisfying \eqref{SparkCondition} if and only if the following polynomial also evaluates to a nonzero number:
 \begin{align*}
@@
 Such a matrix is easily constructed by adding rows of zeroes to any $\min(2k,m) \times m$ Vandermonde matrix as described previously, so that every sum in the product defining $f$ above is strictly positive.
-Almost every $n \times m$ matrix with $n \geq \min(2k,m)$ therefore satisfies \eqref{SparkCondition}.
+Almost every $n \times m$ matrix with $n \geq \min(2k,m)$ thus satisfies \eqref{SparkCondition}.
 
@@
 
-We claim a similar phenomenon applies to datasets of vectors with a stable sparse representation.
+We claim that a similar phenomenon applies to datasets of vectors with a stable sparse representation.
 Briefly, following the same procedure as in \cite[Sec.~IV]{Hillar15}, for $k < m$ and $n \geq \min(2k, m)$ we may consider the ``symbolic'' dataset $Y = \{\mathbf{A}\mathbf{x}_1,\ldots,\mathbf{A} \mathbf{x}_N\}$ generated by an indeterminate $n \times m$ matrix $\mathbf{A}$ and $m$-dimensional $k$-sparse vectors $\mathbf{x}_1, \ldots, \mathbf{x}_N$ indeterminate within their supports, which form a regular hypergraph $\mathcal{H} \subseteq {[m] \choose k}$ satisfying the SIP.
@@
 We close this section with some comments on the optimality of our results.
-Our linear scaling for $\varepsilon$ in \eqref{epsdel} is essentially optimal (e.g., see \cite{arias2013fundamental}), but a basic open problem remains: how many samples are necessary to determine the sparse coding model?
+The linear scaling for $\varepsilon$ in \eqref{epsdel} is essentially optimal (e.g., see \cite{arias2013fundamental}), but a basic open problem remains: how many samples are necessary to determine the sparse coding model?
 Our results demonstrate that sparse codes $\mathbf{x}_i$ drawn from only a polynomial number of $k$-dimensional subspaces permit stable identification of the generating dictionary $\mathbf{A}$.
@@
 Before moving on to our proof of Thm.~\ref{SLCopt}, we briefly revisit here our discussion on sample complexity from the end of the previous section.
-While an exponential number of samples may very well prove to be necessary in the deterministic or almost-certain case, our proof of Thm.~\ref{DeterministicUniquenessTheorem} can be extended to hold with some probability for \emph{any} number of samples by alternative appeal to a probabilistic pigeonholing at the point early in the proof where the (deterministic) pigeonhole principle is applied to show that for every $S \in \mathcal{H}$, there exist $k$ vectors $\mathbf{x}_i$ supported on $S$ whose corresponding $\mathbf{\overline x}_i$ all share the same support.\footnote{A famous example of such an argument is the counter-intuitive "birthday paradox", which demonstrates that the probability of two people having the same birthday in a room of twenty-three is in fact greater than 50\%.} Given insufficient samples, this argument has some less-than-certain probability of being valid for each $S \in \mathcal{H}$.
+While an exponential number of samples may very well prove to be necessary in the deterministic or almost-certain case, our proof of Thm.~\ref{DeterministicUniquenessTheorem} can be extended to hold with some probability for \emph{any} number of samples by alternative appeal to a probabilistic pigeonholing at the point early in the proof where the (deterministic) pigeonhole principle is applied to show that for every $S \in \mathcal{H}$, there exist $k$ vectors $\mathbf{x}_i$ supported on $S$ whose corresponding $\mathbf{\overline x}_i$ all share the same support.\footnote{A famous example of such an argument is the counter-intuitive ``birthday paradox", which demonstrates that the probability of two people having the same birthday in a room of twenty-three is in fact greater than 50\%.} Given insufficient samples, this argument has some less-than-certain probability of being valid for each $S \in \mathcal{H}$.
 Nonetheless, cursory simulations with small hypergraphs confirm that the probability of success very quickly approaches one once the number of samples $N$ surpasses a small fraction of the deterministic sample complexity.
@@
 Assurances such as those offered by our theorems certify that different devices (with different initialization, etc.) will learn equivalent representations given enough data from statistically identical systems.\footnote{To contrast with the current hot topic of ``Deep Learning'', there are few such uniqueness guarantees for these models of data; moreover, even small noise can dramatically alter their output \cite{goodfellow2014explaining}.} Indeed, it seems a main reason for the sustained interest in dictionary learning as an unsupervised method for data analysis is the assumed well-posedness of parameter identification in the sparse coding model, confirmation of which forms the core of our theoretical findings.
+
+\section{EXTRA}
+An additional implication of Thm.~\ref{DeterministicUniquenessTheorem} of potential relevance to Prob.~\ref{OptimizationProblem} is the implied lower bound on $L_{2k}(\mathbf{B})$ in the case where $\mathbf{A}$ satisfies \eqref{SparkCondition}.
+Due to complexity issues, Prob.~\ref{SLCopt} is often solved by first replacing the $\|\cdot\|_0$-norm with the $\|\cdot\|_1$-norm.
+The compressive sensing literature informs us that sparse codes are in fact stably recoverable via minimization of the $\|\cdot\|_1$-norm provided $L_{2k}(\mathbf{A})$ is large enough.
+Thm.~\ref{DeterministicUniquenessTheorem} guarantees that for large enough $L_{2k}(\mathbf{A})$, all valid solutions also have the property that their sparse codes can be inferred by minimization of the $\|\cdot\|_1$ norm.
+Does this matter..?
 

### 2019-05-07 manuscripts/IEEE/final_submission.tex
page 1 steam rolled

@@
 Learning optimal dictionaries for sparse coding has exposed characteristic sparse features of many natural signals.
-However, universal conditions guaranteeing the stability of these learned features in the presence of measurement noise have yet to be described.
-We prove very generally that optimal dictionaries and sparse codes are unique up to measurement error for all diverse enough datasets generated by the sparse coding model.
+However, there are few universal conditions guaranteeing the stability of such features in the presence of measurement noise.
+Here, we prove very generally that optimal dictionaries and sparse codes are unique up to measurement error for all diverse enough datasets generated by the sparse coding model.
 Applications are given to data analysis, engineering, and neuroscience.
@@
 % \cite{sato1975method}
-\IEEEPARstart{A}{}common modern approach to problems in signal processing and pattern analysis is to view each of $N$ observed $n$-dimensional signal samples as a (noisy) linear combination of at most $k$ elementary waveforms drawn from some unknown ``dictionary" of size $m \ll N$ (see \cite{Zhang15} for a comprehensive review of this and related models).
+\IEEEPARstart{A}{}common modern approach to pattern analysis in signal processing is to view each of $N$ observed $n$-dimensional signal samples as a (noisy) linear combination of at most $k$ elementary waveforms drawn from some unknown ``dictionary" of size $m \ll N$ (see \cite{Zhang15} for a comprehensive review).
 Optimizing dictionaries subject to this and related sparsity constraints has revealed seemingly characteristic sparse structure in several signal classes of current interest (e.g., in vision \cite{wang2015sparse}).
-Of particular note are the seminal works in the field \cite{Olshausen96, hurri1996image, bell1997independent, van1998independent}, which demonstrated that such dictionaries optimized with respect to small patches of ``natural" images share qualitative similarities with linear filters fit to the response properties of simple-cell neurons in mammalian visual cortex.
-Curiously, these waveforms (e.g., ``Gabor'' wavelets) appear in dictionaries learned by a variety of sparse coding algorithms trained over different natural image datasets; as such, it appears these latent features may be in some sense canonical \cite{donoho2001can}.
+Of particular note are the seminal works in the field \cite{Olshausen96, hurri1996image, bell1997independent, van1998independent}, which discovered that dictionaries optimized for coding small patches of ``natural" images share qualitative similarities with linear filters estimated from response properties of simple-cell neurons in mammalian visual cortex.
+Curiously, these waveforms (e.g., ``Gabor'' wavelets) appear in dictionaries learned by a variety of algorithms trained over different natural image datasets; in particular, sparse coding of  latent features in natural signals may, in some sense, be canonical \cite{donoho2001can}.
 
-Motivated by these discoveries and more recent work proposing a theory of information transmission through random wiring bottlenecks in the brain \cite{Isely10}, linked to the field of ``compressed sensing", we address when optimal dictionaries for sparse representation are indeed identifiable from data.
-Answers to this question may also have implications in practice wherever an appeal is made to the latent sparse structure of data (e.g.
-forgery detection \cite{hughes2010, olshausen2010applied}; brain recordings \cite{jung2001imaging, agarwal2014spatially, lee2016sparse}; and gene expression \cite{wu2016stability}).
-While several algorithms which provably recover unique latent dictionaries under specific conditions have recently been proposed (see \cite[Sec.~I-E]{Sun16} for a summary of the state-of-the-art), few theorems can be invoked to justify the consistency of inference under this model of data more broadly.
-To our knowledge, a universal guarantee of the uniqueness and stability of learned dictionaries and the sparse representations they induce over noisy data has yet to appear in the literature.
+Motivated by these discoveries and more recent work relating ``compressed sensing" to a theory of information transmission through random wiring bottlenecks in the brain \cite{Isely10}, we address when optimal dictionaries for sparse representation are indeed identifiable from data.
+Answers to this question may also have implications in practice wherever an appeal is made to latent sparse structure of data (e.g., forgery detection \cite{hughes2010, olshausen2010applied}; brain recordings \cite{jung2001imaging, agarwal2014spatially, lee2016sparse}; and gene expression \cite{wu2016stability}).
+While several algorithms have recently been proposed that provably recover unique dictionaries under specific conditions (see \cite[Sec.~I-E]{Sun16} for a summary of the state-of-the-art), few theorems can be invoked to justify the consistency of inference under this model of data more broadly.
+To our knowledge, a universal guarantee of the uniqueness and stability of learned dictionaries and the sparse representations they induce when data is noisy has yet to appear in the literature.
 % in justifying the identification of forged paintings by their anomalous sparse representations \cite{hughes2010},
 
-Here, we prove very generally that uniqueness and stability is a typical property of the dictionary learning problem described above.
+Here, we prove very generally that uniqueness and stability is a typical property of sparse dictionary learning.
 More specifically,  we show that dictionaries injective on a sparse domain are identifiable from \mbox{$N = m(k-1){m \choose k} + m$} noisy sparse linear combinations of their columns up to an error that is linear in the noise (Thm.~\ref{DeterministicUniquenessTheorem}).
 In fact, provided $n \geq \min(2k,m)$, in almost all cases the problem is well-posed (as per Hadamard \cite{Hadamard1902}) given enough data (Cor.~\ref{ProbabilisticCor}).
-These guarantees also hold for a related (and perhaps more commonly posed) optimization problem which seeks a dictionary minimizing the average number of elementary waveforms required to reconstruct each sample of the dataset.
+These guarantees also hold for a related (and perhaps more commonly posed) optimization problem which seeks a dictionary minimizing the average number of elementary waveforms required to reconstruct each sample of the dataset (Thm.~\ref{SLCopt}).
 Importantly, in both cases our explicit, universal guarantees apply without the imposition of \emph{any} constraints on learned dictionaries  (e.g.
-that they, too, be injective over some domain) beyond an upper bound on dictionary size, which is necessary in any case to avoid a trivial solution (e.g.
-allowing for $m = N$ elementary waveforms).
+that they, too, be injective over some domain) beyond an upper bound on dictionary size, which is necessary in any case to avoid a trivial solution (e.g., allowing for $m = N$ elementary waveforms).
 %That is, every pair of solutions of comparable size has some number of dictionary elements in common (up to noise), and similarly so for the coefficients of sparse codes they induce.
 
-To state things precisely, let $\mathbf{A} \in \mathbb R^{n \times m}$ be a matrix with columns $\mathbf{A}_j$ ($j = 1,\ldots,m$) and let dataset $Z$ consist of measurements:
+More precisely, let $\mathbf{A} \in \mathbb R^{n \times m}$ be a matrix with columns $\mathbf{A}_j$ ($j = 1,\ldots,m$) and let dataset $Z$ consist of measurements:
 \begin{align}\label{LinearModel}
@@
 for $k$-\emph{sparse} $\mathbf{x}_i \in \mathbb{R}^m$ having at most $k<m$ nonzero entries and \emph{noise} $\mathbf{n}_i \in \mathbb{R}^n$, with bounded norm $\| \mathbf{n}_i \|_2 \leq  \eta$ representing our worst-case uncertainty in measuring the product $\mathbf{A}\mathbf{x}_i$.
-The first mathematical problem we consider is:
+The first mathematical problem we consider is the following.
 
@@
 
-Note that as stated, every solution to this problem represents infinitely many equivalent alternatives $\mathbf{BPD}$ and $\mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_1, \ldots, \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_N$ parametrized by a choice of permutation matrix $\mathbf{P}$ and invertible diagonal matrix $\mathbf{D}$.
-Identifying these alternatives gives a set of elementary waveforms (the columns of $\mathbf{B}$)  up to some arbitrary scale and their associated sparse coefficients (the entries of $\mathbf{x}_i$) for reconstructing each data point $\mathbf{z}_i$.
-Previous theoretical work addressing the noiseless case $\eta =0$ (e.g., \cite{li2004analysis, Georgiev05, Aharon06, Hillar15}) for matrices $\mathbf{B}$ having exactly $m$ columns has shown that the solution to Prob.~\ref{InverseProblem}, when it exists, is unique up to these equivalent labeling and scaling ambiguities provided the $\mathbf{x}_i$ are sufficiently diverse and the matrix $\mathbf{A}$ satisfies the \textit{spark condition}:
+Note that every solution to Prob.~\ref{InverseProblem} represents infinitely many equivalent alternatives $\mathbf{BPD}$ and $\mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_1, \ldots, \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_N$ parametrized by a choice of permutation matrix $\mathbf{P}$ and invertible diagonal matrix $\mathbf{D}$.
+Identifying these ambiguities (labelling and scale) yields a set of elementary waveforms (the columns of $\mathbf{B}$) and their associated sparse coefficients (the entries of $\mathbf{\overline x}_i$) for reconstructing each data point $\mathbf{z}_i$.
+
+Previous theoretical work addressing the noiseless case $\eta =0$ (e.g., \cite{li2004analysis, Georgiev05, Aharon06, Hillar15}) for matrices $\mathbf{B}$ having exactly $m$ columns has shown that a solution to Prob.~\ref{InverseProblem}, when it exists, is unique up to such relabeling and rescaling provided the $\mathbf{x}_i$ are sufficiently diverse and $\mathbf{A}$ satisfies the \textit{spark condition}:
 \begin{align}\label{SparkCondition}
@@
 which in any case is necessary to guarantee the uniqueness of arbitrary $k$-sparse $\mathbf{x}_i$.
-We generalize these results to the practical setting  $\eta > 0$ by considering a notion of stability with respect to measurement error.
+We generalize these results to the practical setting  $\eta > 0$ by considering a natural notion of stability with respect to measurement error.
 

### 2019-05-07 manuscripts/IEEE/final_submission.tex
more small things

@@
 which in any case is necessary to guarantee the uniqueness of arbitrary $k$-sparse $\mathbf{x}_i$.
-We generalize these results to the practical setting  $\eta > 0$ by considering a natural notion of stability with respect to measurement error.
+We generalize these results to the practical setting  $\eta > 0$ by considering the following natural notion of stability with respect to measurement error.
 
@@
 \ref{maindef}, suppose that $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$ and fix $\delta_1, \delta_2$ to be the desired accuracies of recovery in \eqref{def1}.
-Now, consider any dataset $Z$ generated as in \eqref{LinearModel} with $\eta \leq \frac{1}{2} \varepsilon(\delta_1, \delta_2)$.
-It follows from the triangle inequality that any $n \times m$ matrix $\mathbf{B}$ and $k$-sparse $\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N$ solving Prob.~\ref{InverseProblem} are necessarily within $\delta_1$ and $\delta_2$ of the original dictionary $\mathbf{A}$ and codes $\mathbf{x}_1, ..., \mathbf{x}_N$, respectively.\footnote{We should mention the different norms in \eqref{def1} reflect the distinct meanings typically ascribed to the dictionary and sparse codes in modeling data.}
+Consider any dataset $Z$ generated as in \eqref{LinearModel} with $\eta \leq \frac{1}{2} \varepsilon(\delta_1, \delta_2)$.
+Using the triangle inequality, it follows that any $n \times m$ matrix $\mathbf{B}$ and $k$-sparse $\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N$ solving Prob.~\ref{InverseProblem} are necessarily within $\delta_1$ and $\delta_2$ of the original dictionary $\mathbf{A}$ and codes $\mathbf{x}_1, \ldots, \mathbf{x}_N$, respectively.\footnote{We mention that the different norms in \eqref{def1} reflect the distinct meanings typically ascribed to the dictionary and sparse codes in modeling data.}
 
@@
 \begin{align}\label{minsum}
-\min \sum_{i = 1}^N \|\mathbf{\overline x}_i\|_0 \ \
+\min \sum_{\ell = 1}^N \|\mathbf{\overline x}_{\ell}\|_0 \ \
 \text{subject to} \ \ \|\mathbf{z}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \eta, \ \text{for all $i$}.
@@
 
-We are now in a position to state our main result, though for expository purposes we will leave the quantity $C_1$ (a function of $\mathbf{A}$, $\mathbf{x}_1, ..., \mathbf{x}_N$, and $\mathcal{H}$) undefined until Eq.~\eqref{Cdef1} of Sec.~\ref{DUT}.
+We are now in a position to state our main result, though for expository purposes we will leave the quantity $C_1$ (a function of $\mathbf{A}$, $\mathbf{x}_1, \ldots, \mathbf{x}_N$, and $\mathcal{H}$) undefined until Eq.~\eqref{Cdef1} of Sec.~\ref{DUT}.
 We state here once that all of our theorems assume matrices and vectors consist of real numbers.
@@
 We should stress the point here that framing the problem in terms of hypergraphs has allowed us to show, unlike in previous works on the subject, that the matrix $\mathbf{A}$ need not necessarily satisfy \eqref{SparkCondition} to be recoverable from data.
-As an example, let $\mathbf{A} = [ \mathbf{e}_1, \ldots, \mathbf{e}_5, \mathbf{v}]$ with $\mathbf{v} = \mathbf{e}_1 + \mathbf{e}_3 + \mathbf{e}_5$ and take $\mathcal{H}$ to be all consecutive pairs of indices $1, ...
-,6$ arranged in cyclic order.
+As an example, let $\mathbf{A} = [ \mathbf{e}_1, \ldots, \mathbf{e}_5, \mathbf{v}]$ with $\mathbf{v} = \mathbf{e}_1 + \mathbf{e}_3 + \mathbf{e}_5$ and take $\mathcal{H}$ to be all consecutive pairs of indices $1, \ldots ,6$ arranged in cyclic order.
 Then for $k=2$, the matrix $\mathbf{A}$ fails to satisfy \eqref{SparkCondition} while still satisfying the assumptions of Thm.~\ref{DeterministicUniquenessTheorem}.%, hence guaranteeing \eqref{Cstable} .

### 2019-05-07 manuscripts/IEEE/final_submission.tex
more page 2

@@
 
-In the next section, we give precise statements of our main result (Thm.~\ref{DeterministicUniquenessTheorem}), from which we have derived an explicit form for $\varepsilon(\delta_1, \delta_2)$.
-We then extend the same guarantees to the following alternate formulation of the dictionary learning problem as one of minimizing the total (or equivalently, the mean) number of non-zero entries in the sparse codes (Thm.~\ref{SLCopt}):
+The main result of this work is a very general uniqueness theorem for sparse coding (Thm.~\ref{DeterministicUniquenessTheorem}) directly 
+implying (Cor.~\ref{DeterministicUniquenessCorollary}) that stable representations of a dataset $Z$ are guaranteed whenever generating dictionaries $A$ satisfy a spark condition on supports and the original sparse codes $\mathbf{x}_i$ are sufficiently diverse.
+Moreover, we provide an explicit, computable formula for $\varepsilon(\delta_1, \delta_2)$ in (\ref{epsdel}) that is linear in desired accuracy $\delta_1, \delta_2$.
+
+In the next section, we give precise statements of these results.
+We then extend the same guarantees to the following alternate formulation of the dictionary learning problem, which attempts to minimize the mean number of nonzero entries in the sparse codes (Thm.~\ref{SLCopt}).
 

### 2019-05-07 manuscripts/IEEE/final_submission.tex
end section 1

@@
 In the next section, we give precise statements of these results.
-We then extend the same guarantees to the following alternate formulation of the dictionary learning problem, which attempts to minimize the mean number of nonzero entries in the sparse codes (Thm.~\ref{SLCopt}).
+We then extend the same guarantees (Thm.~\ref{SLCopt}) to the following alternate formulation of dictionary learning, which minimizes the number of nonzero entries in sparse codes.
 
@@
 \end{problem}
-We also give brief arguments adapting our results to data and dictionaries drawn from probability distributions (Cor.~\ref{ProbabilisticCor}).
-We defer to Sec.~\ref{DUT} the more technically involved proofs of Thms.~\ref{DeterministicUniquenessTheorem} and ~\ref{SLCopt}, following some necessary definitions and a useful result in combinatorial matrix analysis (Lem.~\ref{MainLemma}).
-Finally, we discuss in Sec.~\ref{Discussion} some theoretical and practical applications of our main mathematical findings.
-The Appendix contains a proof of Lem.~\ref{MainLemma}.
+We also give brief arguments adapting our results to dictionaries and codes drawn from probability distributions (Cor.~\ref{ProbabilisticCor}).
+We defer to Sec.~\ref{DUT} the technical proofs of Thms.~\ref{DeterministicUniquenessTheorem} and ~\ref{SLCopt}, following some necessary definitions and a useful fact in combinatorial matrix analysis (Lem.~\ref{MainLemma}, proved in the Appendix).
+Finally, we discuss in Sec.~\ref{Discussion} theoretical and practical applications of our main mathematical findings.
+%The Appendix contains a proof of Lem.~\ref{MainLemma}.
 

### 2019-05-07 manuscripts/IEEE/final_submission.tex
finished section 1

@@
 
-In the next section, we give precise statements of these results.
+In the next section, we give precise statements of these findings.
 We then extend the same guarantees (Thm.~\ref{SLCopt}) to the following alternate formulation of dictionary learning, which minimizes the number of nonzero entries in sparse codes.
@@
 \end{problem}
+
+Our formulation of Thm.~\ref{DeterministicUniquenessTheorem} is general enough to provide uniqueness stability even when generating $A$ do not satisfy (\ref{SparkCondition}) and recovery dictionaries $B$ have more columns than $m$.
+Moreover, our approach incorporates a combinatorial theory for designing generating codes that should be of independent interest.
 We also give brief arguments adapting our results to dictionaries and codes drawn from probability distributions (Cor.~\ref{ProbabilisticCor}).
-We defer to Sec.~\ref{DUT} the technical proofs of Thms.~\ref{DeterministicUniquenessTheorem} and ~\ref{SLCopt}, following some necessary definitions and a useful fact in combinatorial matrix analysis (Lem.~\ref{MainLemma}, proved in the Appendix).
-Finally, we discuss in Sec.~\ref{Discussion} theoretical and practical applications of our main mathematical findings.
+We defer to Sec.~\ref{DUT} the technical proofs of Thms.~\ref{DeterministicUniquenessTheorem} and ~\ref{SLCopt}, following some necessary definitions and a useful fact in combinatorial matrix analysis (Lem.~\ref{MainLemma}; proved in the Appendix).
+Finally, we discuss in Sec.~\ref{Discussion} theoretical and practical applications of our mathematical observations.
 %The Appendix contains a proof of Lem.~\ref{MainLemma}.

### 2019-05-07 manuscripts/IEEE/final_submission.tex
up to page 2

@@
 implying (Cor.~\ref{DeterministicUniquenessCorollary}) that stable representations of a dataset $Z$ are guaranteed whenever generating dictionaries $A$ satisfy a spark condition on supports and the original sparse codes $\mathbf{x}_i$ are sufficiently diverse.
-Moreover, we provide an explicit, computable formula for $\varepsilon(\delta_1, \delta_2)$ in (\ref{epsdel}) that is linear in desired accuracy $\delta_1, \delta_2$.
+Moreover, we provide an explicit, computable expression for $\varepsilon(\delta_1, \delta_2)$ in (\ref{epsdel}) that is linear in desired accuracy $\delta_1, \delta_2$.
 
@@
 
-Our formulation of Thm.~\ref{DeterministicUniquenessTheorem} is general enough to provide uniqueness stability even when generating $A$ do not satisfy (\ref{SparkCondition}) and recovery dictionaries $B$ have more columns than $m$.
+Our development of Thm.~\ref{DeterministicUniquenessTheorem} is general enough to provide uniqueness stability even when generating $A$ do not fully satisfy (\ref{SparkCondition}) and recovery dictionaries $B$ have more columns than $A$.
 Moreover, our approach incorporates a combinatorial theory for designing generating codes that should be of independent interest.
@@
 
-A detailed statement of our results requires that we first identify some combinatorial criteria on the supports\footnote{Recall a vector $\mathbf{x}$ is said to be \emph{supported} in $S$ when $\mathbf{x} \in \text{\rm span}\{\mathbf{e}_j: j\in S\}$, with $\mathbf{e}_j$ forming the standard column basis.} of sparse vectors.
+Precise statements of our results require that we first identify some combinatorial criteria on the supports\footnote{Recall a vector $\mathbf{x}$ is said to be \emph{supported} in $S$ when $\mathbf{x} \in \text{\rm span}\{\mathbf{e}_j: j\in S\}$, with $\mathbf{e}_j$ forming the standard column basis.} of sparse vectors.
 Let $\{1, \ldots, m\}$ be denoted $[m]$, its power set $2^{[m]}$, and ${[m] \choose k}$ the set of subsets of $[m]$ of size $k$.
 A \emph{hypergraph} on vertices $[m]$  is simply any subset $\mathcal{H} \subseteq 2^{[m]}$.
-We say $\mathcal{H}$ is \textit{$k$-uniform} when in fact $\mathcal{H} \subseteq {[m] \choose k}$.
+We say that $\mathcal{H}$ is \textit{$k$-uniform} when $\mathcal{H} \subseteq {[m] \choose k}$.
 The \emph{degree} $\deg_\mathcal{H}(i)$ of a node $i \in [m]$ is the number of sets in $\mathcal{H}$ that contain $i$, and we say $\mathcal{H}$ is \emph{regular} when for some $r$ we have $\deg_\mathcal{H}(i) = r$ for all $i$ (given such an $r$, we say $\mathcal{H}$ is \textit{$r$-regular}).
@@
 
-Next, we describe a quantitative generalization of the spark condition.
-The \emph{lower bound} of a real $n \times m$ matrix $\mathbf{M}$ is the largest $\alpha$ with \mbox{$\|\mathbf{M}\mathbf{x}\|_2 \geq \alpha\|\mathbf{x}\|_2$} for all $\mathbf{x} \in \mathbb{R}^m$ \cite{Grcar10}.
-By compactness of the unit sphere, every injective linear map has a positive lower bound; hence, if $\mathbf{M}$ satisfies \eqref{SparkCondition} then each submatrix formed from $2k$ of its columns or less has a strictly positive lower bound.
+We next give a quantitative generalization of the spark condition (\ref{SparkCondition}) to combinatorial subsets of supports.
+The \emph{lower bound} of an $n \times m$ matrix $\mathbf{M}$ is the largest $\alpha$ with \mbox{$\|\mathbf{M}\mathbf{x}\|_2 \geq \alpha\|\mathbf{x}\|_2$} for all $\mathbf{x} \in \mathbb{R}^m$ \cite{Grcar10}.
+By compactness of the unit sphere, every injective linear map has a positive lower bound; hence, if $\mathbf{M}$ satisfies \eqref{SparkCondition}, then submatrices formed from $2k$ of its columns or less have strictly positive lower bounds.
 
-We generalize the matrix lower bound for our purposes by considering only the spans of certain submatrices\footnote{See \cite{vidal2005generalized} for an overview of the closely associated ``union of subspaces" model.} associated with a hypergraph $\mathcal{H} \subseteq {[m] \choose k}$ over column indices.
-Letting $\mathbf{M}_S$ denote the submatrix formed by the columns of $\mathbf{M}$ indexed by $S \subseteq [m]$, with $\mathbf{M}_\emptyset := \mathbf{0}$ (in the sections that follow, we will write $\bm{\mathcal{M}}_S$ to denote the column-span of a submatrix $\mathbf{M}_S$, and $\bm{\mathcal{M}}_\mathcal{G}$ to denote $\{\bm{\mathcal{M}}_S\}_{S \in \mathcal{G}}$), we define:
+We generalize the matrix lower bound for our purposes by restricting it to the spans of certain submatrices\footnote{See \cite{vidal2005generalized} for an overview of the related ``union of subspaces" model.} associated with a hypergraph $\mathcal{H} \subseteq {[m] \choose k}$ of column indices.
+Let $\mathbf{M}_S$ denote the submatrix formed by the columns of a matrix $\mathbf{M}$ indexed by $S \subseteq [m]$, with $\mathbf{M}_\emptyset := \mathbf{0}$.
+In the sections that follow, we also set $\bm{\mathcal{M}}_S$ to denote the column-span of a submatrix $\mathbf{M}_S$, and $\bm{\mathcal{M}}_\mathcal{G}$ to denote $\{\bm{\mathcal{M}}_S\}_{S \in \mathcal{G}}$.
+We define:  % Define $L_\mathcal{H}(\mathbf{M})$ as follows:
 %\begin{align*} 
@@
 \begin{align}\label{Ldef}
-L_\mathcal{H}(\mathbf{M}) := \frac{1}{\sqrt{k}} \min \left\{ \frac{\|\mathbf{M}_S\mathbf{x}\|_2}{ \|\mathbf{x}\|_2} : S \in \mathcal{H}, \ \ \mathbf{x} \in \mathbb{R}^{|S|} \right\},
+L_\mathcal{H}(\mathbf{M}) := \min \left\{ \frac{\|\mathbf{M}_S\mathbf{x}\|_2}{ \sqrt{k} \|\mathbf{x}\|_2} : S \in \mathcal{H}, \ \mathbf{0} \neq \mathbf{x} \in \mathbb{R}^{|S|} \right\},
 \end{align} 
 %
-writing also $L_{k}$ in place of $L_\mathcal{H}$ when $\mathcal{H} = {[m] \choose k}$.\footnote{We note that \mbox{$1 - \sqrt{k} L_k(\mathbf{M})$} is known in the compressive sensing literature as the asymmetric lower restricted isometry constant for matrices $\mathbf{M}$ with unit $\ell_2$-norm columns \cite{Blanchard2011}}  As explained previously, by compactness we have $L_{2k}(\mathbf{M}) > 0$ for all $\mathbf{M}$ satisfying \eqref{SparkCondition}.
-Clearly, $L_{\mathcal{H}'}(\mathbf{M}) \geq L_\mathcal{H}(\mathbf{M})$ whenever $\mathcal{H}' \subseteq \mathcal{H}$ and, by the same token, any $k$-uniform $\mathcal{H}$ satisfying $\cup \mathcal{H} = [m]$ has $L_2 \geq L_{2\mathcal{H}} \geq L_{2k}$.
+writing also $L_{k}$ in place of $L_\mathcal{H}$ when $\mathcal{H} = {[m] \choose k}$.\footnote{In compressed sensing literature, \mbox{$1 - \sqrt{k} L_k(\mathbf{M})$}  is the asymmetric lower restricted isometry constant for $\mathbf{M}$ with unit $\ell_2$-norm columns \cite{Blanchard2011}.}
 
-Finally, we mention that a set of vectors sharing a support $S$ are said to be in \emph{general linear position} when any $|S|$ of them form a linearly independent set.
+As explained above, compactness implies $L_{2k}(\mathbf{M}) > 0$ for all $\mathbf{M}$ satisfying \eqref{SparkCondition}.
+Clearly, $L_{\mathcal{H}'}(\mathbf{M}) \geq L_\mathcal{H}(\mathbf{M})$ whenever $\mathcal{H}' \subseteq \mathcal{H}$, and any $k$-uniform $\mathcal{H}$ satisfying $\cup \mathcal{H} = [m]$ has $L_2 \geq L_{2\mathcal{H}} \geq L_{2k}$.
+Finally, we say that a set of vectors sharing support $S$ are in \emph{general linear position} when any $|S|$ of them are linearly independent.
 
-We are now in a position to state our main result, though for expository purposes we will leave the quantity $C_1$ (a function of $\mathbf{A}$, $\mathbf{x}_1, \ldots, \mathbf{x}_N$, and $\mathcal{H}$) undefined until Eq.~\eqref{Cdef1} of Sec.~\ref{DUT}.
-We state here once that all of our theorems assume matrices and vectors consist of real numbers.
+We are now in a position to state our main result, though for expository purposes we leave the quantity $C_1$ (a function of $\mathbf{A}$, $\mathbf{x}_1, \ldots, \mathbf{x}_N$, and $\mathcal{H}$) undefined until Eqn.~\eqref{Cdef1} of Sec.~\ref{DUT}.
+All results results below assume real matrices and vectors.
 
@@
 Fix integers $n, k, m$ and $\overline m$.
-Let the $n \times m$ matrix $\mathbf{A}$ satisfy $L_{2\mathcal{H}}(\mathbf{A}) > 0$ for some $r$-regular $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP.
+Suppose that the $n \times m$ matrix $\mathbf{A}$ satisfies $L_{2\mathcal{H}}(\mathbf{A}) > 0$ for some $r$-regular $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP from Def.~\ref{sip}.
 If $k$-sparse \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N$} include more than $(k-1){\overline m \choose k}$ vectors in general linear position supported in each $S \in \mathcal{H}$, then there is $C_1 > 0$ (given by \eqref{Cdef1}) for which the following holds for all%\footnote{The condition $\varepsilon < L_2(\mathbf{A}) /C_1$ is necessary; otherwise,  with \mbox{$\mathbf{A}$ = $\mathbf{I}$} and $\mathbf{x}_i = \mathbf{e}_i$, there is a matrix $\mathbf{B}$ and $1$-sparse $\mathbf{\overline{x}}_i$ with $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline{x}}_i \|_2 \leq \varepsilon$ that nonetheless violates \eqref{Cstable}.} $\varepsilon < L_{2}(\mathbf{A}) / C_1$:
@@
 
-Every $n \times \overline m$ matrix $\mathbf{B}$ for which there are $k$-sparse $\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N$ satisfying \mbox{$\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \varepsilon$} for $i = 0, \ldots, N$ has $\overline m \geq m$, and provided $\overline m (r-1) < mr$, there is a permutation matrix $\mathbf{P}$ and an invertible diagonal matrix $\mathbf{D}$ such that:
+Every $n \times \overline m$ matrix $\mathbf{B}$ for which there are $k$-sparse $\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N$ satisfying \mbox{$\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \varepsilon$} for all $i \in [N]$ has $\overline m \geq m$, and provided $\overline m (r-1) < mr$, there is a permutation matrix $\mathbf{P}$ and an invertible diagonal matrix $\mathbf{D}$ such that:
 \begin{align}\label{Cstable}
-\|\mathbf{A}_j- \mathbf{BPD}_j\|_2 \leq C_1 \varepsilon \ \ \text{for all } j \in J
+\|\mathbf{A}_j- \mathbf{BPD}_j\|_2 \leq C_1 \varepsilon, \ \ \text{for all } j \in J,
 \end{align}
 %
-for some $J$ of size \mbox{$m - (r-1)(\overline m - m)$}. 
+for some $J \subseteq [m]$ of size \mbox{$m - (r-1)(\overline m - m)$}. 
 % $\overline m - r(\overline m - m)$
 
-Moreover, if $\mathbf{A}$ satisfies \eqref{SparkCondition} and $\varepsilon < L_{2k}(\mathbf{A}) / C_1$, then $\mathbf{B}$ also satisfies \eqref{SparkCondition} with $L_{2k}(\mathbf{B}\mathbf{PD}) \geq L_{2k}(\mathbf{A}) - C_1 \varepsilon$ and for all $i \in [N]$:
+Moreover, if $\mathbf{A}$ satisfies \eqref{SparkCondition} and $\varepsilon < L_{2k}(\mathbf{A}) / C_1$, then $\mathbf{B}$ also satisfies \eqref{SparkCondition} with $L_{2k}(\mathbf{B}\mathbf{PD}) \geq L_{2k}(\mathbf{A}) - C_1 \varepsilon$, and for all $i \in [N]$:
 \begin{align}\label{b-PDa}
@@
 %
-where $(\mathbf{x}_i)_J$ here represents the subvector formed from restricting to coefficients indexed by $J$. 
+where $(\mathbf{x}_i)_J$ represents the subvector formed from restricting to coefficients indexed by $J$. 
 \end{theorem}
@@
 As an example, let $\mathbf{A} = [ \mathbf{e}_1, \ldots, \mathbf{e}_5, \mathbf{v}]$ with $\mathbf{v} = \mathbf{e}_1 + \mathbf{e}_3 + \mathbf{e}_5$ and take $\mathcal{H}$ to be all consecutive pairs of indices $1, \ldots ,6$ arranged in cyclic order.
-Then for $k=2$, the matrix $\mathbf{A}$ fails to satisfy \eqref{SparkCondition} while still satisfying the assumptions of Thm.~\ref{DeterministicUniquenessTheorem}.%, hence guaranteeing \eqref{Cstable} .
+Then for $k=2$, the matrix $\mathbf{A}$ fails to satisfy \eqref{SparkCondition} while still satisfying the first assumptions of Thm.~\ref{DeterministicUniquenessTheorem}.%, hence guaranteeing \eqref{Cstable} .
 %(since $\{ \mathbf{A}_1, \mathbf{A}_3, \mathbf{A}_5, \mathbf{A}_6\}$ is not a linearly independent set).
@@
 Moreover, calculating $C_2$ requires an exponential number of queries to $\xi$ unless $r$ is held fixed, too (e.g., the ``cyclic order'' hypergraphs described above have $r=k$).
-Thus, as presented, $C_1$ and $C_2$ are not efficiently computable in general, but efficient sub-cases do exist and may be of practical relevance.
+Thus, as presented, $C_1$ and $C_2$ are not efficiently computable in general, but efficient subcases do exist and may be of practical relevance.
 
@@
 Due to complexity issues, Prob.~\ref{SLCopt} is often solved by first replacing the $\|\cdot\|_0$-norm with the $\|\cdot\|_1$-norm.
-The compressive sensing literature informs us that sparse codes are in fact stably recoverable via minimization of the $\|\cdot\|_1$-norm provided $L_{2k}(\mathbf{A})$ is large enough.
+The compressed sensing literature informs us that sparse codes are in fact stably recoverable via minimization of the $\|\cdot\|_1$-norm provided $L_{2k}(\mathbf{A})$ is large enough.
 Thm.~\ref{DeterministicUniquenessTheorem} guarantees that for large enough $L_{2k}(\mathbf{A})$, all valid solutions also have the property that their sparse codes can be inferred by minimization of the $\|\cdot\|_1$ norm.

### 2019-05-08 manuscripts/IEEE/final_submission.tex
fixed some minor things

@@
 We generalize the matrix lower bound for our purposes by restricting it to the spans of certain submatrices\footnote{See \cite{vidal2005generalized} for an overview of the related ``union of subspaces" model.} associated with a hypergraph $\mathcal{H} \subseteq {[m] \choose k}$ of column indices.
-Let $\mathbf{M}_S$ denote the submatrix formed by the columns of a matrix $\mathbf{M}$ indexed by $S \subseteq [m]$, with $\mathbf{M}_\emptyset := \mathbf{0}$.
+Let $\mathbf{M}_S$ denote the submatrix formed by the columns of a matrix $\mathbf{M}$ indexed by $S \subseteq [m]$ ($\mathbf{M}_\emptyset := \mathbf{0}$).
 In the sections that follow, we also set $\bm{\mathcal{M}}_S$ to denote the column-span of a submatrix $\mathbf{M}_S$, and $\bm{\mathcal{M}}_\mathcal{G}$ to denote $\{\bm{\mathcal{M}}_S\}_{S \in \mathcal{G}}$.
@@
 \begin{corollary}\label{DeterministicUniquenessCorollary}
-Given any regular hypergraph $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP, there are $N =  |\mathcal{H}| \left[ (k-1){m \choose k} + 1  \right]$ vectors \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} such that every matrix $\mathbf{A}$ with $L_{2\mathcal{H}}(\mathbf{A}) > 0$ generates a dataset $Y = \{\mathbf{A}\mathbf{x}_1, \ldots, \mathbf{A}\mathbf{x}_N\}$ with a stable $k$-sparse representation in $\mathbb{R}^m$, with $\varepsilon(\delta_1,\delta_2)$ as in \eqref{epsdel}.
+Given any regular hypergraph $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP, there are $N =  |\mathcal{H}| \left[ (k-1){m \choose k} + 1  \right]$ vectors \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} such that every matrix $\mathbf{A}$ with $L_{2\mathcal{H}}(\mathbf{A}) > 0$ generates a dataset $Y = \{\mathbf{A}\mathbf{x}_1, \ldots, \mathbf{A}\mathbf{x}_N\}$ with a stable $k$-sparse representation in $\mathbb{R}^m$ for $\varepsilon(\delta_1,\delta_2)$ as in \eqref{epsdel}.
 \end{corollary}
@@
 One need simply check that the matrix and codes satisfy the (computable) assumptions of Thm.~\ref{DeterministicUniquenessTheorem} on $\mathbf{A}$ and the $\mathbf{x}_i$.
-In general, however, there is no efficient such procedure.
+In general, however, there is no known efficient procedure.
 We defer a brief discussion on this point to the next section.
@@
 
-A less direct consequence of Thm.~\ref{DeterministicUniquenessTheorem} is the following uniqueness and stability guarantee for solutions to Prob.~\ref{SLCopt}, the usual optimization problem of interest for those applying dictionary learning to their data.
+A less direct consequence of Thm.~\ref{DeterministicUniquenessTheorem} is the following uniqueness and stability guarantee for solutions to Prob.~\ref{SLCopt}.
+%, the usual optimization problem of interest for those applying dictionary learning to their data.
 
 \begin{theorem}\label{SLCopt}
-Fix a matrix $\mathbf{A}$ and vectors $\mathbf{x}_i$ satisfying the assumptions of Thm.~\ref{DeterministicUniquenessTheorem}, only now with over $(k-1)\left[ {\overline m \choose k} + |\mathcal{H}|k{\overline m \choose k-1}\right]$ vectors supported in general linear position in each $S \in \mathcal{H}$.
+Fix a matrix $\mathbf{A}$ and vectors $\mathbf{x}_i$ satisfying the assumptions of Thm.~\ref{DeterministicUniquenessTheorem}, only now with over \mbox{$(k-1)\left[ {\overline m \choose k} + |\mathcal{H}|k{\overline m \choose k-1}\right]$} vectors supported in general linear position in each $S \in \mathcal{H}$.
 Every solution to Prob.~\ref{OptimizationProblem} (with $\eta = \varepsilon/2$) satisfies recovery guarantees \eqref{Cstable} and \eqref{b-PDa} when the corresponding bounds on $\eta$ are met.
@@
 Restricting \mbox{$(k-1){m \choose k} + 1$} indeterminate $\mathbf{x}_i$ to each support in $\mathcal{H}$, and letting $\textbf{M}$ be the $n \times N$ matrix with columns $\mathbf{A}\mathbf{x}_i$, it can be checked that when $f(\mathbf{M}) \neq 0$ for a substitution of real numbers for the indeterminates, all of the assumptions on $\mathbf{A}$ and $\mathbf{x}_i$ in Thm.~\ref{DeterministicUniquenessTheorem} are satisfied; in particular, $\mathbf{A}$ satisfies \eqref{SparkCondition}.
-We therefore have the following result:
+We therefore have the following result.
 
@@
 % for space:  (e.g.,  \cite{folland2013real}).
-By Thm.~\ref{robustPolythm}, there is then a polynomial that is nonzero when $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$; in particular, stability holds almost surely and we have the following:
+By Thm.~\ref{robustPolythm}, there is then a polynomial that is nonzero when $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$; in particular, stability holds almost surely.
 
 \begin{corollary}\label{ProbabilisticCor}
-If the indeterminate entries of $\mathbf{A}$ and the $\mathbf{x}_i$ are drawn independently from probability measures absolutely continuous with respect to the standard Borel measure, then $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$ with probability one.
+If indeterminate entries of $\mathbf{A}$ and $\mathbf{x}_i$ are drawn independently from probability measures absolutely continuous with respect to the standard Borel measure, then $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$ with probability one.
 \end{corollary}
@@
 \end{align}
-We remark that given the assumptions of Thm.~\ref{DeterministicUniquenessTheorem} on $\mathbf{A}$ and the $\mathbf{x}_i$, this expression for $C_1$ is well-defined\footnote{\label{note1}Fixing $S \in \mathcal{H}$ and $k$-sparse $\mathbf{c}$, we have $\|\mathbf{AX}_{I(S)}\mathbf{c}\|_2 \geq \sqrt{k} L_\mathcal{H}(\mathbf{A})\|\mathbf{X}_{I(S)}\mathbf{c}\|_2 \geq k L_\mathcal{H}(\mathbf{A}) L_k(\mathbf{X}_{I(S)})\|\mathbf{c}\|_2$.
-Hence, $L_k(\mathbf{AX}_{I(S)}) \geq \sqrt{k} L_\mathcal{H}(\mathbf{A}) L_k(\mathbf{X}_{I(S)}) > 0$, since $L_{\mathcal{H}}(\mathbf{A}) \geq L_{2\mathcal{H}}(\mathbf{A})> 0$ and $L_k(\mathbf{X}_{I(S)}) > 0$ by general linear position of the $\mathbf{x}_i$.} and yields an upper bound on $\varepsilon$ consistent with that proven sufficient in the case $k=1$ considered at the beginning of this section.\footnote{When $\mathbf{x}_i = c_i\mathbf{e}_i$ we have $C_2 \geq 2\|\mathbf{A}_i\|_2$ and the denominator in \eqref{Cdef1} becomes $\min_{i \in [m]} |c_i| \|\mathbf{A}_i\|_2$, hence $C_1 \geq 2 / \min_{i \in [m]} |c_i|$.}
+We remark that given the assumptions of Thm.~\ref{DeterministicUniquenessTheorem} on $\mathbf{A}$ and the $\mathbf{x}_i$, this expression for $C_1$ is well-defined\footnote{\label{note1}To see this, fix $S \in \mathcal{H}$ and $k$-sparse $\mathbf{c}$.
+Using the definitions, we have $\|\mathbf{AX}_{I(S)}\mathbf{c}\|_2 \geq \sqrt{k} L_\mathcal{H}(\mathbf{A})\|\mathbf{X}_{I(S)}\mathbf{c}\|_2 \geq k L_\mathcal{H}(\mathbf{A}) L_k(\mathbf{X}_{I(S)})\|\mathbf{c}\|_2$.
+Thus, $L_k(\mathbf{AX}_{I(S)}) \geq \sqrt{k} L_\mathcal{H}(\mathbf{A}) L_k(\mathbf{X}_{I(S)}) > 0$, since $L_{\mathcal{H}}(\mathbf{A}) \geq L_{2\mathcal{H}}(\mathbf{A})> 0$ and $L_k(\mathbf{X}_{I(S)}) > 0$ by general linear position of the $\mathbf{x}_i$.} and yields an upper bound on $\varepsilon$ consistent with that proven sufficient in the case $k=1$ considered at the beginning of this section.\footnote{When $\mathbf{x}_i = c_i\mathbf{e}_i$ we have $C_2 \geq 2\|\mathbf{A}_i\|_2$ and the denominator in \eqref{Cdef1} becomes $\min_{i \in [m]} |c_i| \|\mathbf{A}_i\|_2$, hence $C_1 \geq 2 / \min_{i \in [m]} |c_i|$.}
 % C_2(\mathbf{A}, \mathcal{H}) := \frac{ (r+1) \max_{j \in [m]} \|\mathbf{A}_j\|_2}{ \min_{\mathcal{G} \in {\mathcal{H} \choose r} \cup {\mathcal{H} \choose r+1}} \xi( \{ \bm{\mathcal{A}}_S \}

### 2019-05-08 manuscripts/IEEE/final_submission.tex
went over discussion

@@
 \begin{align}\label{minsum}
-\min \sum_{\ell = 1}^N \|\mathbf{\overline x}_{\ell}\|_0 \ \
+\min \sum_{i = 1}^N \|\mathbf{\overline x}_{i}\|_0 \ \
 \text{subject to} \ \ \|\mathbf{z}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \eta, \ \text{for all $i$}.
@@
 
-Our development of Thm.~\ref{DeterministicUniquenessTheorem} is general enough to provide uniqueness stability even when generating $A$ do not fully satisfy (\ref{SparkCondition}) and recovery dictionaries $B$ have more columns than $A$.
-Moreover, our approach incorporates a combinatorial theory for designing generating codes that should be of independent interest.
+Our development of Thm.~\ref{DeterministicUniquenessTheorem} is general enough to provide some uniqueness stability even when generating $A$ do not fully satisfy (\ref{SparkCondition}) and recovery dictionaries $B$ have more columns than $A$.
+Moreover, the approach incorporates a combinatorial theory for designing generating codes that should be of independent interest.
 We also give brief arguments adapting our results to dictionaries and codes drawn from probability distributions (Cor.~\ref{ProbabilisticCor}).
@@
 \begin{align}\label{Cstable}
-\|\mathbf{A}_j- \mathbf{BPD}_j\|_2 \leq C_1 \varepsilon, \ \ \text{for all } j \in J,
+\|\mathbf{A}_j- (\mathbf{BPD})_j\|_2 \leq C_1 \varepsilon, \ \ \text{for all } j \in J,
 \end{align}
@@
 %
-where $(\mathbf{x}_i)_J$ represents the subvector formed from restricting to coefficients indexed by $J$. 
+where $(\mathbf{x}_i)_J$ represents the subvector formed from restricting to coordinates indexed by $J$. 
 \end{theorem}
@@
 
-A motivation for this work was the emergence of seemingly characteristic representations from sparse coding models fit to natural data, despite the varied assumptions underlying the many algorithms in current use.
-To this end, we have taken an important step toward unifying the many publications on the topic by demonstrating general sufficient, deterministic conditions under which identification of parameters in this model is not only possible but also robust to uncertainty in measurement and model choice.
+A main motivation for this work is the emergence of seemingly unique representations from sparse coding models trained on natural data, despite the varied assumptions underlying the many algorithms in current use.
+Our results constitute an important step toward explaining these phenomena as well as unifying many publications on the topic by demonstrating general deterministic conditions under which identification of parameters in this model is not only possible but also robust to uncertainty in measurement and model choice.
 
-We have shown that, given sufficient data, the problem of seeking a dictionary and sparse codes with minimal average support size (Prob.~\ref{OptimizationProblem}) reduces to an instance of Prob.~\ref{InverseProblem}, to which our main result (Thm.~\ref{DeterministicUniquenessTheorem}) applies: every dictionary and sequence of sparse codes consistent with the data are equivalent up to inherent relabeling/scaling ambiguities and a discrepancy (error) that scales linearly with the measurement noise or modeling inaccuracy.
-The constants we provide are explicit and computable; as such, there is an effective procedure that sufficiently affirms if a proposed solution to these problems is indeed unique up to noise and inherent ambiguities, although this computation is not efficient in general.
+We have shown that, given sufficient data, the problem of determining a dictionary and sparse codes with minimal support size (Prob.~\ref{OptimizationProblem}) reduces to an instance of Prob.~\ref{InverseProblem}, to which our main result (Thm.~\ref{DeterministicUniquenessTheorem}) applies: every dictionary and sequence of sparse codes consistent with the data are equivalent up to inherent relabeling/scaling ambiguities and a discrepancy (error) that scales linearly with the measurement noise or modeling inaccuracy.
+The constants we provide are explicit and computable; as such, there is an effective procedure that sufficiently affirms if a proposed solution to these problems is indeed unique up to noise and inherent ambiguities, although it is not efficient in general.
 
-Our theoretical work mathematically justifies one of the few hypothesized theories of bottleneck communication in the brain \cite{Isely10}: that sparse neural population activity is recoverable from its noisy linear compression through a randomly constructed (but unknown) wiring bottleneck by any biologically plausible unsupervised sparse coding method that solves Prob.~\ref{DeterministicUniquenessTheorem} or \ref{SLCopt} (e.g., \cite{rehnsommer2007, rozell2007neurally, pehlevan2015normative}).\footnote{We refer the reader to \cite{ganguli2012compressed} for more on interactions between dictionary learning and neuroscience.}
+One direct application of our work is to neural theory, wherein our theorems justify the mathematical soundness of one of the few hypothesized theories of bottleneck communication in the brain \cite{Isely10}: that sparse neural population activity is recoverable from its noisy linear compression through a randomly constructed (but unknown) wiring bottleneck by any biologically plausible unsupervised sparse coding method that solves Prob.~\ref{DeterministicUniquenessTheorem} or \ref{SLCopt} (e.g., \cite{rehnsommer2007, rozell2007neurally, pehlevan2015normative}).\footnote{We refer the reader to \cite{ganguli2012compressed} for more on interactions between dictionary learning and neuroscience.}
 
@@
 
-Beyond an original extension of existing noiseless guarantees \cite{Hillar15} to the noisy regime and their application to Prob.~\ref{OptimizationProblem}, a major innovation in our work is a theory of combinatorial designs for support sets key to the identification of the dictionary.
+Beyond an extension of existing noiseless guarantees \cite{Hillar15} to the noisy regime and their novel application to Prob.~\ref{OptimizationProblem}, our work contains a theory of combinatorial designs for support sets key to the identification of the dictionary.
 We incorporate this idea into a fundamental lemma in matrix theory (Lem.~\ref{MainLemma}) that draws upon the definition of a new matrix lower bound induced by a hypergraph.
-Novel insights enabled by our combinatorial approach include: 1) a subset of dictionary elements is recoverable even if dictionary size is overestimated, 2) data require only a polynomial number of distinct sparse supports, and 3) recoverable dictionaries need not necessarily satisfy the spark condition.
+New insights enabled by this combinatorial approach include: 1) a subset of dictionary elements is recoverable even if dictionary size is overestimated, 2) data require only a polynomial number of distinct sparse supports, and 3) recoverable dictionaries need not necessarily satisfy the spark condition.
 
@@
 In fact, uniqueness guarantees with minimal assumptions apply to all areas of data science and engineering that utilize learned sparse structure.
-For example, several groups have applied compressed sensing to signal processing tasks: MRI analysis \cite{lustig2008compressed}, image compression \cite{Duarte08}, and, more recently, the design of an ultrafast camera \cite{Gao14}.
-Given such effective uses of compressed sensing, it is only a matter of time before these systems incorporate dictionary learning to encode and decode signals (e.g., in a device that learns structure from motion \cite{kong2016prior}), just as scientists have used it to make sense of their data \cite{jung2001imaging, Agarwal14, lee2016sparse, wu2016stability}.
-Assurances such as those offered by our theorems certify that different devices (with different initialization, etc.) will learn equivalent representations given enough data from statistically identical systems.\footnote{To contrast with the current hot topic of ``Deep Learning'', there are few such uniqueness guarantees for these models of data; moreover, even small noise can dramatically alter their output \cite{goodfellow2014explaining}.} Indeed, it seems a main reason for the sustained interest in dictionary learning as an unsupervised method for data analysis is the assumed well-posedness of parameter identification in the sparse coding model, confirmation of which forms the core of our theoretical findings.
+For example, several groups have applied compressed sensing to signal processing tasks; e.g., for MRI analysis \cite{lustig2008compressed}, image compression \cite{Duarte08}, and even the design of an ultrafast camera \cite{Gao14}.
+It is only a matter of time before these systems incorporate dictionary learning to encode and decode signals (e.g., in a device that learns structure from motion \cite{kong2016prior}), just as scientists have used it to make sense of their data \cite{jung2001imaging, Agarwal14, lee2016sparse, wu2016stability}.
+
+Assurances such as those offered by our theorems certify that different devices and algorithms (with different initialization, etc.) will learn equivalent representations given enough data from statistically identical systems.\footnote{To contrast with the current hot topic of ``Deep Learning'', there are few such uniqueness guarantees for these models of data; moreover, even small noise can dramatically alter their output \cite{goodfellow2014explaining}.} Indeed, a main reason for the sustained interest in dictionary learning as an unsupervised method for data analysis seems to be the assumed well-posedness of parameter identification in the sparse coding model, confirmation of which forms the core of our theoretical findings.
 

### 2019-05-08 manuscripts/IEEE/final_submission.tex
tiny changes in III

@@
 
-We begin our proof of Thm.~\ref{DeterministicUniquenessTheorem} by showing how dictionary recovery \eqref{Cstable} already implies sparse code recovery \eqref{b-PDa} when $\mathbf{A}$ satisfies \eqref{SparkCondition} and \mbox{$\varepsilon < L_{2k}(\mathbf{A}) / C_1$}, assuming for this purpose that $\overline m = m$ without loss of generality.
+We begin our proof of Thm.~\ref{DeterministicUniquenessTheorem} by showing how dictionary recovery \eqref{Cstable} already implies sparse code recovery \eqref{b-PDa} when $\mathbf{A}$ satisfies \eqref{SparkCondition} and \mbox{$\varepsilon < L_{2k}(\mathbf{A}) / C_1$}, assuming that $\overline m = m$ without loss of generality.
 Consider any $2k$-sparse $\mathbf{x} \in \mathbb{R}^m$ and note that $\|\mathbf{x}\|_1 \leq \sqrt{2k}  \|\mathbf{x}\|_2$.
@@
 \end{align}
-where the term $C_1\varepsilon \|\mathbf{x}\|_1$ in the numerator above follows from the triangle inequality applied to \eqref{Cstable}.
+where the term $C_1\varepsilon \|\mathbf{x}\|_1$ in the numerator above is a consequence of the triangle inequality applied to \eqref{Cstable}.
 
@@
 %
-wherein removal of the absolute value is justified because of $C_1\varepsilon < L_{2k}(\mathbf{A})$.
+wherein removal of the absolute value is justified since $C_1\varepsilon < L_{2k}(\mathbf{A})$.
 We therefore have that $L_{2k}(\mathbf{BPD}) \geq L_{2k}(\mathbf{A}) - C_1\varepsilon  > 0$, and \eqref{b-PDa} then follows from \eqref{stuff}.

### 2019-05-08 manuscripts/IEEE/final_submission.tex
tiny changes in appendix

@@
 
-In this section, we prove Lem.~\ref{MainLemma} after stating some required auxiliary lemmas and their proofs.  % stating and proving some auxiliary lemmas. 
+We prove Lem.~\ref{MainLemma} after the following auxiliary lemmas.  % stating and proving some auxiliary lemmas. 
 %First, note that since $\|\mathbf{A}\mathbf{x}\|_2 \leq \max_j\|\mathbf{A}_j\|_2\|\mathbf{x}\|_1$ and $\|\mathbf{x}\|_1 \leq \sqrt{k} \|\mathbf{x}\|_2$ for $k$-sparse $\mathbf{x}$, by \eqref{Ldef} we have the following frequently applied inequality:
@@
 \begin{lemma}\label{spanIntersectionLemma}
-If $f: V \to W$ is an injective function, then $f\left(\cap_{i=1}^\ell V_i \right) =  \cap_{i=1}^\ell f\left(V_i\right)$ for any $V_1, \ldots, V_\ell \subseteq V$. ($f(\emptyset):=\emptyset$.)
+If $f: V \to W$ is injective, then $f\left(\cap_{i=1}^\ell V_i \right) =  \cap_{i=1}^\ell f\left(V_i\right)$ for any $V_1, \ldots, V_\ell \subseteq V$. ($f(\emptyset):=\emptyset$.)
 %In particular, if for some $E \in 2^{[m]}$ the map $M \in \mathbb{R}^{n \times m}$ is injective on $\cup_{S \in \mathcal{H}} \text{span}\{e_i\}_{i \in S}$ then $\text{span}\{ M_{\cap_{S \in \mathcal{H}} S} \} = \cap_{S \in \mathcal{H}} \text{span}\{M_S\}$.
@@
 By induction, it is enough to prove the case $\ell = 2$.
-Clearly, for any map $f$, if $w \in f(U \cap V)$ then $w \in f(U)$ and $w \in f(V)$, hence $w \in f(U) \cap f(V)$.
-If $w \in f(U) \cap f(V)$ then $w \in f(U)$ and $w \in f(V)$, hence $w = f(u) = f(v)$ for some $u \in U$ and $v \in V$, implying $u = v$ by injectivity of $f$.
-Hence $u \in U \cap V$, and $w \in f(U \cap V)$.
+Clearly, for any map $f$, if $w \in f(U \cap V)$ then $w \in f(U)$ and $w \in f(V)$; hence, $w \in f(U) \cap f(V)$.
+If $w \in f(U) \cap f(V)$, then $w \in f(U)$ and $w \in f(V)$; thus, $w = f(u) = f(v)$ for some $u \in U$ and $v \in V$, implying $u = v$ by injectivity of $f$.
+It follows that $u \in U \cap V$ and $w \in f(U \cap V)$.
 \end{proof}
@@
 \begin{lemma}\label{DistanceToIntersectionLemma}
-Let $\mathcal{V} = \{V_i\}_{i=1}^k$ be a set of two or more subspaces of $\mathbb{R}^m$ and let $V = \cap \mathcal{V} $.
+Let $\mathcal{V} = \{V_i\}_{i=1}^k$ be a set of two or more subspaces of $\mathbb{R}^m$, and set $V = \cap \mathcal{V} $.
 For  $\mathbf{u} \in \mathbb{R}^m$, we have (recall Defs.~\ref{dDef}~\&~\ref{FriedrichsDefinition}):
@@
 Recall the projection onto the subspace $V \subseteq \mathbb{R}^m$ is the mapping $\Pi_V: \mathbb{R}^m \to V$ that associates with each $\mathbf{u}$ its unique nearest point in $V$; i.e., $\|\mathbf{u} - \Pi_V\mathbf{u}\|_2 = \text{\rm dist}(\mathbf{u}, V)$.
-By repeated triangle inequality,
+By repeatedly applying the triangle inequality, we have:
 \begin{align}\label{f}
@@
 = \| ( \Pi_{V_k} \cdots\Pi_{V_1} - \Pi_V ) (\mathbf{u} - \Pi_V\mathbf{u})\|_2$. % \leq z\|\mathbf{u} - \Pi_V\mathbf{u}\|_2$.
-The result \eqref{DTILeq} then follows from the following fact \cite[Thm.~9.33]{Deutsch12}:
+Inequality \eqref{DTILeq} then follows from the following fact \cite[Thm.~9.33]{Deutsch12}:
 \begin{align}
-\|\Pi_{V_k}\Pi_{V_{k-1}}\cdots\Pi_{V_1} \mathbf{x} - \Pi_V\mathbf{x}\|_2 \leq z \|\mathbf{x}\|_2 \ \ \text{for all } \mathbf{x},
+\|\Pi_{V_k}\Pi_{V_{k-1}}\cdots\Pi_{V_1} \mathbf{x} - \Pi_V\mathbf{x}\|_2 \leq z \|\mathbf{x}\|_2, \ \ \text{for all } \mathbf{x},
 \end{align}
@@
 %
-then $\overline m \geq m$, and if $\overline m  (r-1) < mr$ then the map $i \mapsto \cap \pi(\sigma(i))$ is an injective map to $[\overline m]$ from some $J \subseteq [m]$ of size $m - (r-1)(\overline m - m)$.\footnote{Recall $\sigma$ from Def.~\ref{sip}.}  %In particular, if $\overline m = m$ then $\pi$ is induced by a permutation on $[m]$.
+then $\overline m \geq m$; and if $\overline m  (r-1) < mr$, the map $i \mapsto \cap \pi(\sigma(i))$ is an injective function to $[\overline m]$ from some $J \subseteq [m]$ of size $m - (r-1)(\overline m - m)$ (recall $\sigma$ from Def.~\ref{sip}).
+%In particular, if $\overline m = m$ then $\pi$ is induced by a permutation on $[m]$.
 \end{lemma}
@@
 \begin{proof}
-Consider the set: $T_1 := \{(i, S): i \in \pi(S), S \in \mathcal{H}\}$, which numbers $|T_1| = \sum_{S \in \mathcal{H}} |\pi(S)| \geq \sum_{S \in \mathcal{H}} |S| = \sum_{i \in [m]} \deg_\mathcal{H}(i) = mr$ by $r$-regularity of $\mathcal{H}$.
+Consider the following set: $T_1 := \{(i, S): i \in \pi(S), S \in \mathcal{H}\}$, which numbers $|T_1| = \sum_{S \in \mathcal{H}} |\pi(S)| \geq \sum_{S \in \mathcal{H}} |S| = \sum_{i \in [m]} \deg_\mathcal{H}(i) = mr$ by $r$-regularity of $\mathcal{H}$.
 Note that $|T_1| \leq \overline m r$; otherwise, pigeonholing the tuples of $T_1$ with respect to their $\overline m$ possible first elements would imply that more than $r$ of the tuples in $T_1$ share the same first element.
-This cannot be the case, however, since then some $\mathcal{G} \in {\mathcal{H} \choose r+1}$ formed from any $r+1$ of their second elements would satisfy $\cap \pi(\mathcal{G}) \neq 0$, hence $|\cap \mathcal{G}| \neq 0$ by \eqref{cond}, contradicting $r$-regularity of $\mathcal{H}$.
-Thus, $\overline m \geq m$.
+This cannot be the case, however, since then some $\mathcal{G} \in {\mathcal{H} \choose r+1}$ formed from any $r+1$ of their second elements would satisfy $\cap \pi(\mathcal{G}) \neq 0$; hence, $|\cap \mathcal{G}| \neq 0$ by \eqref{cond}, contradicting $r$-regularity of $\mathcal{H}$.
+It follows that $\overline m \geq m$.
 
 Suppose now that $\overline m (r-1) < mr$, so that $p := mr - \overline m (r-1)$ is positive and $|T_1| \geq \overline m (r - 1) + p$.
-Pigeonholing $T_1$ into $[\overline m]$ again, there must be at least $r$ tuples in $T_1$ that share some first element; that is, for some $\mathcal{G}_1 \subseteq \mathcal{H}$ of size $|\mathcal{G}_1| \geq r$ we have $|\cap \pi(\mathcal{G}_1)| \geq 1$ and (by \eqref{cond}) $|\cap \mathcal{G}_1| \geq 1$.
+Pigeonholing $T_1$ into $[\overline m]$ again, there are at least $r$ tuples in $T_1$ sharing some first element; that is, for some $\mathcal{G}_1 \subseteq \mathcal{H}$ of size $|\mathcal{G}_1| \geq r$, we have $|\cap \pi(\mathcal{G}_1)| \geq 1$ and (by \eqref{cond}) $|\cap \mathcal{G}_1| \geq 1$.
 Since no more than $r$ tuples of $T_1$ can share the same first element, we in fact have $|\mathcal{G}_1| = r$.
@@
 
-If $p=1$ then we are done.
+If $p=1$, then we are done.
 Otherwise, define $T_2 := T_1 \setminus \{(i,S) \in T_1: i = \cap \pi(\mathcal{G}_1)\}$, which contains $|T_2| = |T_1| - r \geq (\overline m - 1)(r-1) + (p-1)$ ordered pairs having $\overline m - 1$ distinct first indices.
-Pigeonholing $T_2$ into $[\overline m - 1]$ and repeating the above arguments produces the star $\mathcal{G}_2 \in {\mathcal{H} \choose r}$ with intersect $\cap \mathcal{G}_2$ necessarily distinct (by $r$-regularity) from $\cap \mathcal{G}_1$.
+Pigeonholing $T_2$ into $[\overline m - 1]$ and repeating the above arguments produces the star $\mathcal{G}_2 \in {\mathcal{H} \choose r}$ with intersection $\cap \mathcal{G}_2$ necessarily distinct (by $r$-regularity) from $\cap \mathcal{G}_1$.
 Iterating this procedure $p$ times in total yields the stars $\mathcal{G}_i$ for which $\cap\mathcal{G}_i \mapsto \cap \pi(\mathcal{G}_i)$ defines an injective map to $[\overline m]$ from $J = \{\cap \mathcal{G}_1, \ldots, \cap \mathcal{G}_p\} \subseteq [m]$.
@@
 We begin by showing that $\dim(\bm{\mathcal{B}}_{\pi(S)}) = \dim(\bm{\mathcal{A}}_S)$ for all $S \in \mathcal{H}$.
-Note that since $\|\mathbf{A}\mathbf{x}\|_2 \leq \max_j\|\mathbf{A}_j\|_2\|\mathbf{x}\|_1$ and $\|\mathbf{x}\|_1 \leq \sqrt{k} \|\mathbf{x}\|_2$ for all $k$-sparse $\mathbf{x}$, by \eqref{Ldef} we have $L_2(\mathbf{A}) \leq \max_j\|\mathbf{A}_j\|_2$ and therefore (as $0 \leq \xi < 1$), the right-hand side of \eqref{GapUpperBound} is less than one.
-From \eqref{dimLem}, we have $|\pi(S)| \geq \dim(\bm{\mathcal{B}}_{\pi(S)}) \geq \dim(\bm{\mathcal{A}}_S) = |S|$, the final equality by injectivity of $\mathbf{A}_S$.
+Note that since $\|\mathbf{A}\mathbf{x}\|_2 \leq \max_j\|\mathbf{A}_j\|_2\|\mathbf{x}\|_1$ and $\|\mathbf{x}\|_1 \leq \sqrt{k} \|\mathbf{x}\|_2$ for all $k$-sparse $\mathbf{x}$, by \eqref{Ldef} we have $L_2(\mathbf{A}) \leq \max_j\|\mathbf{A}_j\|_2$ and therefore (as $0 \leq \xi < 1$) the right-hand side of \eqref{GapUpperBound} is less than one.
+From \eqref{dimLem}, we have $|\pi(S)| \geq \dim(\bm{\mathcal{B}}_{\pi(S)}) \geq \dim(\bm{\mathcal{A}}_S) = |S|$, the final equality holding by injectivity of $\mathbf{A}_S$.
 As $|\pi(S)| = |S|$, the claim follows.
@@
 We next demonstrate that \eqref{cond} holds.
-Fixing $\mathcal{G} \in {\mathcal{H} \choose r} \cup {\mathcal{H} \choose r+1}$, it suffices to show that $d(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}, \bm{\mathcal{A}}_{\cap \mathcal{G}} ) < 1$, since by \eqref{dimLem} we then have $|\cap \pi(\mathcal{G})| = \dim(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}) \leq \dim(\bm{\mathcal{A}}_{\cap \mathcal{G}}) = |\cap \mathcal{G}|$, with equalities by the full column-ranks of $\mathbf{A}_{S}$ and $\mathbf{B}_{\pi(S)}$ for all $S \in \mathcal{H}$.\footnote{Note that if ever $\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})} \neq \bf 0$ while $\cap \mathcal{G} = \emptyset$, we would have $d(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}, \bm 0 ) = 1$.
-This cannot be the case, however, since the deduction that follows would then lead to a contradiction.} Observe that $d(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}, \bm{\mathcal{A}}_{\cap \mathcal{G}}  )
-\leq d\left( \cap \bm{\mathcal{B}}_{\pi(\mathcal{G})}, \cap \bm{\mathcal{A}}_\mathcal{G} \right)$, by \eqref{UsubU} since trivially $\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})} \subseteq \cap \bm{\mathcal{B}}_{\pi(\mathcal{G})}$ and since $\bm{\mathcal{A}}_{\cap \mathcal{G}} = \cap \bm{\mathcal{A}}_\mathcal{G}$ by Lem.~\ref{spanIntersectionLemma}.
+Fixing $\mathcal{G} \in {\mathcal{H} \choose r} \cup {\mathcal{H} \choose r+1}$, it suffices to show that $d(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}, \bm{\mathcal{A}}_{\cap \mathcal{G}} ) < 1$, since by \eqref{dimLem} we then have $|\cap \pi(\mathcal{G})| = \dim(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}) \leq \dim(\bm{\mathcal{A}}_{\cap \mathcal{G}}) = |\cap \mathcal{G}|$, with equalities from the full column-ranks of $\mathbf{A}_{S}$ and $\mathbf{B}_{\pi(S)}$ for all $S \in \mathcal{H}$.\footnote{Note that if ever $\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})} \neq \bf 0$ while $\cap \mathcal{G} = \emptyset$, we would have $d(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}, \bm 0 ) = 1$.
+However, that leads to a contradiction.} Observe that $d(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}, \bm{\mathcal{A}}_{\cap \mathcal{G}}  )
+\leq d\left( \cap \bm{\mathcal{B}}_{\pi(\mathcal{G})}, \cap \bm{\mathcal{A}}_\mathcal{G} \right)$ by \eqref{UsubU}, since trivially $\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})} \subseteq \cap \bm{\mathcal{B}}_{\pi(\mathcal{G})}$ and also $\bm{\mathcal{A}}_{\cap \mathcal{G}} = \cap \bm{\mathcal{A}}_\mathcal{G}$ by Lem.~\ref{spanIntersectionLemma}.
 Recalling Def.~\ref{dDef} and applying Lem.~\ref{DistanceToIntersectionLemma} yields:
@@
 passing the maximum through the sum.
-Since $\cap \bm{\mathcal{B}}_{\pi(\mathcal{G})} \subseteq \bm{\mathcal{B}}_{\pi(S)}$ for all $S \in \mathcal{G}$, by \eqref{UsubU} the numerator of each term in the sum above is bounded by \mbox{$d\left( \bm{\mathcal{B}}_{\pi(S)},\bm{\mathcal{A}}_{S} \right) = d\left(\bm{\mathcal{A}}_{S}, \bm{\mathcal{B}}_{\pi(S)} \right) \leq \varepsilon$}, with equality by \eqref{eqdim} since $\dim(\bm{\mathcal{B}}_{\pi(S)}) = \dim(\bm{\mathcal{A}}_S)$.
+Since $\cap \bm{\mathcal{B}}_{\pi(\mathcal{G})} \subseteq \bm{\mathcal{B}}_{\pi(S)}$ for all $S \in \mathcal{G}$, by \eqref{UsubU} the numerator of each term in the sum above is bounded by \mbox{$d\left( \bm{\mathcal{B}}_{\pi(S)},\bm{\mathcal{A}}_{S} \right) = d\left(\bm{\mathcal{A}}_{S}, \bm{\mathcal{B}}_{\pi(S)} \right) \leq \varepsilon$}, with the equality from \eqref{eqdim} since $\dim(\bm{\mathcal{B}}_{\pi(S)}) = \dim(\bm{\mathcal{A}}_S)$.
 Thus, altogether:
@@
 
-By Lem.~\ref{NonEmptyLemma}, the association $i \mapsto \cap \pi(\sigma(i))$ is an injective map $\overline \pi: J \to [\overline m]$ for some $J \subseteq [m]$ of size $m - (r-1)(\overline m - m)$, and $\mathbf{B}_{\overline \pi(i)} \neq \mathbf{0}$ for all $i \in J$ since we have shown the columns of $\mathbf{B}_{\pi(S)}$ to be linearly independent for all $S \in \mathcal{H}$.
+Applying Lem.~\ref{NonEmptyLemma}, the association $i \mapsto \cap \pi(\sigma(i))$ is an injective map $\overline \pi: J \to [\overline m]$ for some $J \subseteq [m]$ of size $m - (r-1)(\overline m - m)$, and $\mathbf{B}_{\overline \pi(i)} \neq \mathbf{0}$ for all $i \in J$ since the columns of $\mathbf{B}_{\pi(S)}$ are linearly independent for all $S \in \mathcal{H}$.
 Letting $\overline \varepsilon := C_2 \varepsilon / \max_i \|\mathbf{A}_i\|_2$, it follows from \eqref{eqdim} and \eqref{last} that $d\left( \bm{\mathcal{A}}_i, \bm{\mathcal{B}}_{\overline \pi(i)} \right) = d\left(\bm{\mathcal{B}}_{\overline \pi(i)},  \bm{\mathcal{A}}_i \right)  \leq \overline \varepsilon$ for all $i \in J$.
@@
 But this is exactly the supposition in \eqref{1D}, and the result follows from the case $k=1$ in Sec.~\ref{DUT} applied to the submatrix $\mathbf{A}_J$.
-Setting $c_i := \|\mathbf{A}_i\|_2^{-1}$ so that $\|c_i\mathbf{Ae}_i\|_2 = 1$, by Def.~\ref{dDef} we have for all $i \in J$:
+Setting $c_i := \|\mathbf{A}_i\|_2^{-1}$ so that $\|c_i\mathbf{Ae}_i\|_2 = 1$, by Def.~\ref{dDef} for all $i \in J$:
 \begin{align*}
@@
 But this is exactly the supposition in \eqref{1D}, with $J$ and $\overline \varepsilon$ in place of $[m]$ and $\varepsilon$, respectively.
-The same arguments of the case $k=1$ in Sec.~\ref{DUT} can then be made to show that for any $\overline m \times \overline m$ permutation and invertible diagonal matrices $\mathbf{P}$ and $\mathbf{D}$ with, respectively, columns $\mathbf{e}_{\pi(i)}$ and $\frac{\overline{c}_i}{c_i}\mathbf{e}_i$ for $i \in J$ (and, say, $\mathbf{e}_i$ otherwise) we have $\|\mathbf{A}_i - \mathbf{B}\mathbf{PD}_i \|_2 \leq \overline  \varepsilon / |c_i|  \leq C_2 \varepsilon$ for all $i \in J$.
+The same arguments of the case $k=1$ in Sec.~\ref{DUT} can then be made to show that for any $\overline m \times \overline m$ permutation and invertible diagonal matrices $\mathbf{P}$ and $\mathbf{D}$ with, respectively, columns $\mathbf{e}_{\pi(i)}$ and $\frac{\overline{c}_i}{c_i}\mathbf{e}_i$ for $i \in J$ (and, say, $\mathbf{e}_i$ otherwise) we have $\|\mathbf{A}_i - (\mathbf{B}\mathbf{PD})_i \|_2 \leq \overline  \varepsilon / |c_i|  \leq C_2 \varepsilon$ for all $i \in J$.
 \end{proof}

### 2019-05-08 manuscripts/IEEE/final_submission.tex
tiny changes in sec III

@@
 implying (Cor.~\ref{DeterministicUniquenessCorollary}) that stable representations of a dataset $Z$ are guaranteed whenever generating dictionaries $A$ satisfy a spark condition on supports and the original sparse codes $\mathbf{x}_i$ are sufficiently diverse.
-Moreover, we provide an explicit, computable expression for $\varepsilon(\delta_1, \delta_2)$ in (\ref{epsdel}) that is linear in desired accuracy $\delta_1, \delta_2$.
+Moreover, we provide an explicit, computable $\varepsilon(\delta_1, \delta_2)$ in (\ref{epsdel}) that is essentially linear in desired accuracy $\delta_1, \delta_2$.
 
@@
 
-Note moreover that if a set of measure spaces $\{(X_{\ell}, \Sigma_{\ell}, \nu_{\ell})\}_{\ell=1}^p$ has $\nu_{\ell}$ absolutely continuous with respect to $\mu$ for all $\ell \in [p]$, where $\mu$ is the standard Borel measure on $\mathbb{R}$, then the product measure $\prod_{\ell=1}^p \nu_{\ell}$ is absolutely continuous with respect to the standard Borel product measure on $\mathbb{R}^p$.
-% for space:  (e.g.,  \cite{folland2013real}).
-By Thm.~\ref{robustPolythm}, there is then a polynomial that is nonzero when $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$; in particular, stability holds almost surely.
+To extend this observation to arbitrary probability distributions, note that if a set of measure spaces $\{(X_{\ell}, \Sigma_{\ell}, \nu_{\ell})\}_{\ell=1}^p$ has $\nu_{\ell}$ absolutely continuous with respect to $\mu$ for all $\ell \in [p]$, where $\mu$ is the standard Borel measure on $\mathbb{R}$, then the product measure $\prod_{\ell=1}^p \nu_{\ell}$ is absolutely continuous with respect to the standard Borel product measure on $\mathbb{R}^p$ (e.g.,  \cite{folland2013real}).
+This fact combined with Thm.~\ref{robustPolythm} implies the following.
 
@@
 Since the only 1-uniform hypergraph with the SIP is $[m]$, which is obviously regular, we require only $\mathbf{x}_i = c_i \mathbf{e}_i$ for $i \in [m]$, with $c_i \neq 0$ to guarantee  linear independence.
-While we have yet to define $C_1$ in general, in this case we may set $C_1 = 1/ \min_{\ell \in [m]} |c_{\ell}|$ so that $\varepsilon < L_2(\mathbf{A})  \min_{\ell \in [m]} |c_{\ell}|$.
+While we have yet to define $C_1$ generally, in this case we may set $C_1 = 1/ \min_{\ell \in [m]} |c_{\ell}|$ so that $\varepsilon < L_2(\mathbf{A})  \min_{\ell \in [m]} |c_{\ell}|$.
 
-Fix $\mathbf{A} \in \mathbb{R}^{n \times m}$ satisfying $L_2(\mathbf{A}) > 0$, since here we have $2\mathcal{H} = {[m] \choose 2}$, and suppose that for some $\mathbf{B}$ and $1$-sparse $\mathbf{\overline x}_i \in \mathbb{R}^{\overline m}$ we have  $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \varepsilon < L_2(\mathbf{A}) / C_1$ for all $i$.
-Then there exist $\overline{c}_1, \ldots, \overline{c}_m \in \mathbb{R}$ and a map $\pi: [m] \to [\overline m]$ such that:
+Fix $\mathbf{A} \in \mathbb{R}^{n \times m}$ satisfying $L_2(\mathbf{A}) > 0$, since here we have $2\mathcal{H} = {[m] \choose 2}$, and suppose some $\mathbf{B}$ and $1$-sparse $\mathbf{\overline x}_i \in \mathbb{R}^{\overline m}$ have  $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \varepsilon < L_2(\mathbf{A}) / C_1$ for all $i$.
+Then, there exist $\overline{c}_1, \ldots, \overline{c}_m \in \mathbb{R}$ and a map $\pi: [m] \to [\overline m]$ such that:
 \begin{align}\label{1D}
@@
 \end{align} 
-Note that $\overline{c}_j \neq 0$, since otherwise we would reach the contradiction $\|\mathbf{A}_j \|_2 \leq C_1 |c_j| \|\mathbf{A}_j \|_2  \leq C_1\varepsilon < L_2(\mathbf{A}) \leq L_1(\mathbf{A}) = \min_{j \in [m]} \|\mathbf{A}_{j}\|_2$.
+Note that $\overline{c}_j \neq 0$, since otherwise we would reach the following contradiction: $\|\mathbf{A}_j \|_2 \leq C_1 |c_j| \|\mathbf{A}_j \|_2  \leq C_1\varepsilon < L_2(\mathbf{A}) \leq L_1(\mathbf{A}) = \min_{j \in [m]} \|\mathbf{A}_{j}\|_2$.
 %implies by \eqref{delrho} the contradiction $|c_j| < \min_{\ell \in [m]} | c_\ell |$.
@@
 Suppose that $\pi(i) = \pi(j) = \ell$ for some $i \neq j$ and $\ell$.
-Then $\|c_{j}\mathbf{A}_{j} - \overline{c}_{j}\mathbf{B}_{\ell}\|_2 \leq \varepsilon$ and $\|c_{i}\mathbf{A}_{i} - \overline{c}_{i} \mathbf{B}_{\ell}\|_2  \leq \varepsilon$, and we have: %Scaling and summing these inequalities by $|\overline{c}_{i}|$ and $|\overline{c}_{j}|$, respectively, and applying the triangle inequality to annihilate the terms in $\mathbf{B}_\ell$, we obtain:
+Then, $\|c_{j}\mathbf{A}_{j} - \overline{c}_{j}\mathbf{B}_{\ell}\|_2 \leq \varepsilon$ and $\|c_{i}\mathbf{A}_{i} - \overline{c}_{i} \mathbf{B}_{\ell}\|_2  \leq \varepsilon$, and we have: %Scaling and summing these inequalities by $|\overline{c}_{i}|$ and $|\overline{c}_{j}|$, respectively, and applying the triangle inequality to annihilate the terms in $\mathbf{B}_\ell$, we obtain:
 \begin{align*}
@@
 \end{align*}
-contradicting our assumed upper bound on $\varepsilon$. Hence, the map $\pi$ is injective and it must be the case that $\overline m \geq m$. %Setting $\overline J = \pi([m])$ and 
+contradicting our assumed upper bound on $\varepsilon$. Hence, the map $\pi$ is injective and so $\overline m \geq m$. %Setting $\overline J = \pi([m])$ and 
 Letting $\mathbf{P}$ and $\mathbf{D}$ be the $\overline m \times \overline m$ permutation and invertible diagonal matrices with, respectively, columns $\mathbf{e}_{\pi(j)}$ and $\frac{\overline{c}_j}{c_j}\mathbf{e}_j$ for $j \in [m]$ (and, say, $\mathbf{e}_j$ otherwise), we may rewrite \eqref{1D} to see that for all $j \in [m]$:
 \begin{align*}
-\|\mathbf{A}_j - \mathbf{BPD}_j\|_2 
+\|\mathbf{A}_j - (\mathbf{BPD})_j\|_2 
 = \|\mathbf{A}_j - \frac{\overline{c}_j}{c_j}\mathbf{B}_{\pi(j)}\|_2 
@@
 
-An extension of the proof to the general case $k < m$ requires that we introduce some additional tools which we have used to derive  our general expression \eqref{Cdef1} for the constant $C_1$.
-These including a generalized notion of distance (Def.~\ref{dDef}) and angle (Def.~\ref{FriedrichsDefinition}) between subspaces as well as a stability result in combinatorial matrix analysis (Lem.~\ref{MainLemma}).
+An extension of the proof to the general case $k < m$ requires that we introduce some additional tools to derive the general expression \eqref{Cdef1} for the constant $C_1$.
+These include a generalized notion of distance (Def.~\ref{dDef}) and angle (Def.~\ref{FriedrichsDefinition}) between subspaces as well as a stability result in combinatorial matrix analysis (Lem.~\ref{MainLemma}).
 
@@
 \end{align}
-From \cite[Ch.~4 Cor.~2.6]{Kato2013}, we have: %Kato p.223
+From \cite[Ch.~4 Cor.~2.6]{Kato2013}, we also have: %Kato p.223
 \begin{align}\label{dimLem}
@@
 
-Our result in combinatorial matrix analysis, which hides most of the complexity in our proof of Thm.~\ref{DeterministicUniquenessTheorem}, is the following.
+We now state our result in combinatorial matrix analysis, which contains most of the complexity in the proof of Thm.~\ref{DeterministicUniquenessTheorem}.
 
@@
 \begin{align}\label{MainLemmaBPD}
-\|\mathbf{A}_j - \mathbf{B}\mathbf{PD}_j\|_2 \leq C_2 \varepsilon \ \  \text{for } j \in J
+\|\mathbf{A}_j - (\mathbf{B}\mathbf{PD})_j\|_2 \leq C_2 \varepsilon, \ \  \text{for } j \in J,
 \end{align}
-for some $J$ of size \mbox{$m - (r-1)(\overline m - m)$}.
+for some $J \subseteq [m]$ of size \mbox{$m - (r-1)(\overline m - m)$}.
 \end{lemma}
@@
 We present the constant $C_2$ (a function of $\mathbf{A}$ and $\mathcal{H}$) relative to a quantity used in \cite{Deutsch12} to analyze the convergence of the ``alternating projections" algorithm for projecting a point onto the intersection of subspaces.
-We incorporate this quantity into the following definition, which we refer to in our proof of Lem.~\ref{DistanceToIntersectionLemma} in the Appendix; specifically, we use it to bound the distance between a point and the intersection of subspaces given an upper bound on its distance from each subspace individually.
+We incorporate this quantity into the following definition, which we refer to in our proof of Lem.~\ref{DistanceToIntersectionLemma} in the Appendix; specifically, we use it to bound the distance between a point and the intersection of subspaces given an upper bound on its distance from each subspace.
 
@@
 \end{definition}
-Note that $\theta \in (0,\frac{\pi}{2}]$ implies $0 \leq \xi < 1$, and that $\xi(\mathcal{V}') \leq \xi(\mathcal{V})$ when $\mathcal{V}' \subseteq \mathcal{V}$.\footnote{We acknowledge the potentially counter-intuitive property that $\theta =  \pi/2$ when $U \subseteq W$.}
+Note that $\theta \in (0,\frac{\pi}{2}]$ implies $0 \leq \xi < 1$, and that $\xi(\mathcal{V}') \leq \xi(\mathcal{V})$ when $\mathcal{V}' \subseteq \mathcal{V}$.\footnote{We acknowledge the counter-intuitive property: $\theta =  \pi/2$ when $U \subseteq W$.}
 
@@
 Given vectors $\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$, let $\mathbf{X}$ denote the $m \times N$ matrix with columns $\mathbf{x}_i$ and let $I(S)$ denote the set of indices $i$ for which $\mathbf{x}_i$ is supported in $S$.
+We define:
 \begin{align}\label{Cdef1}
@@
 \end{align}
-We remark that given the assumptions of Thm.~\ref{DeterministicUniquenessTheorem} on $\mathbf{A}$ and the $\mathbf{x}_i$, this expression for $C_1$ is well-defined\footnote{\label{note1}To see this, fix $S \in \mathcal{H}$ and $k$-sparse $\mathbf{c}$.
+Given the assumptions of Thm.~\ref{DeterministicUniquenessTheorem} on $\mathbf{A}$ and the $\mathbf{x}_i$, this expression for $C_1$ is well-defined\footnote{\label{note1}To see this, fix $S \in \mathcal{H}$ and $k$-sparse $\mathbf{c}$.
 Using the definitions, we have $\|\mathbf{AX}_{I(S)}\mathbf{c}\|_2 \geq \sqrt{k} L_\mathcal{H}(\mathbf{A})\|\mathbf{X}_{I(S)}\mathbf{c}\|_2 \geq k L_\mathcal{H}(\mathbf{A}) L_k(\mathbf{X}_{I(S)})\|\mathbf{c}\|_2$.
@@
 Moreover, calculating $C_2$ requires an exponential number of queries to $\xi$ unless $r$ is held fixed, too (e.g., the ``cyclic order'' hypergraphs described above have $r=k$).
-Thus, as presented, $C_1$ and $C_2$ are not efficiently computable in general, but efficient subcases do exist and may be of practical relevance.
+Thus, as presented, $C_1$ and $C_2$ are not efficiently computable in general.
+% , but efficient subcases do exist and may be of practical relevance.
 
@@
 %
-Now, apply Lem.~\ref{MainLemma} with $\varepsilon < L_2(\mathbf{A})/C_1$ and $\pi(S) := \overline S$. % L_2(A) > 0 by def of L, since L_2H(A) > 0 and H covers [m]
+Finally, apply Lem.~\ref{MainLemma} with $\varepsilon < L_2(\mathbf{A})/C_1$ and $\pi(S) := \overline S$. % L_2(A) > 0 by def of L, since L_2H(A) > 0 and H covers [m]
 \end{proof}
@@
 Before moving on to our proof of Thm.~\ref{SLCopt}, we briefly revisit here our discussion on sample complexity from the end of the previous section.
-While an exponential number of samples may very well prove to be necessary in the deterministic or almost-certain case, our proof of Thm.~\ref{DeterministicUniquenessTheorem} can be extended to hold with some probability for \emph{any} number of samples by alternative appeal to a probabilistic pigeonholing at the point early in the proof where the (deterministic) pigeonhole principle is applied to show that for every $S \in \mathcal{H}$, there exist $k$ vectors $\mathbf{x}_i$ supported on $S$ whose corresponding $\mathbf{\overline x}_i$ all share the same support.\footnote{A famous example of such an argument is the counter-intuitive ``birthday paradox", which demonstrates that the probability of two people having the same birthday in a room of twenty-three is in fact greater than 50\%.} Given insufficient samples, this argument has some less-than-certain probability of being valid for each $S \in \mathcal{H}$.
-Nonetheless, cursory simulations with small hypergraphs confirm that the probability of success very quickly approaches one once the number of samples $N$ surpasses a small fraction of the deterministic sample complexity.
+While an exponential number of samples may very well prove to be necessary in the deterministic or almost-certain case, our proof of Thm.~\ref{DeterministicUniquenessTheorem} can be extended to hold with some probability for \emph{any} number of samples by alternative appeal to a probabilistic pigeonholing at the point early in the proof where the (deterministic) pigeonhole principle is applied to show that for every $S \in \mathcal{H}$, there exist $k$ vectors $\mathbf{x}_i$ supported on $S$ whose corresponding $\mathbf{\overline x}_i$ all share the same support.\footnote{A famous example of such an argument is the counter-intuitive ``birthday paradox", which demonstrates that the probability of two people having the same birthday in a room of twenty-three is greater than 50\%.} Given insufficient samples, this argument has some less-than-certain probability of being valid for each $S \in \mathcal{H}$.
+Nonetheless, simulations with small hypergraphs confirm that the probability of success very quickly approaches one once the number of samples $N$ surpasses a small fraction of the deterministic sample complexity.
 
@@
 
-We note that no more than $(k-1)|\mathcal{H}|$ of the $\mathbf{\overline x}_i$ share a support $\overline S$ of size less than $k$.
+Next, observe that no more than $(k-1)|\mathcal{H}|$ of the $\mathbf{\overline x}_i$ share a support $\overline S$ of size less than $k$.
 Otherwise, by the pigeonhole principle, there is some $S \in \mathcal{H}$ and a set of $k$ indices $K \subseteq I(S)$ for which all $\mathbf{x}_i$ with $i \in K$ are supported in $S$; as argued previously, \eqref{rhs222} follows.

### 2019-05-08 manuscripts/IEEE/final_submission.tex
chaz EXTRA

@@
 \section{EXTRA}
-An additional implication of Thm.~\ref{DeterministicUniquenessTheorem} of potential relevance to Prob.~\ref{OptimizationProblem} is the implied lower bound on $L_{2k}(\mathbf{B})$ in the case where $\mathbf{A}$ satisfies \eqref{SparkCondition}.
-Due to complexity issues, Prob.~\ref{SLCopt} is often solved by first replacing the $\|\cdot\|_0$-norm with the $\|\cdot\|_1$-norm.
-The compressed sensing literature informs us that sparse codes are in fact stably recoverable via minimization of the $\|\cdot\|_1$-norm provided $L_{2k}(\mathbf{A})$ is large enough.
-Thm.~\ref{DeterministicUniquenessTheorem} guarantees that for large enough $L_{2k}(\mathbf{A})$, all valid solutions also have the property that their sparse codes can be inferred by minimization of the $\|\cdot\|_1$ norm.
-Does this matter..?
+An additional consequence of Thm.~\ref{DeterministicUniquenessTheorem} of potential practical relevance to is the implied lower bound $L_{2k}(\mathbf{BPD}) \geq L_{2k}(\mathbf{A}) - C_1\varepsilon$ in the case where $\mathbf{A}$ satisfies \eqref{SparkCondition}.
+Since solving Prob.~\ref{SLCopt} directly requires a combinatorial search over sparse supports for the $\mathbf{\overline x}_i$ for each proposed dictionary $\mathbf{B}$, rendering it intractable in general, a common strategy is to replace the $\ell_0$-norm in \eqref{minsum} with the $\ell_1$-norm, thereby transforming the inference of sparse $\mathbf{\overline x}_i$ for a fixed dictionary $\mathbf{B}$ into a convex optimization solvable by a linear program.
+A major advance in compressive sensing was the discovery that, for fixed $\mathbf{B}$, solutions to \eqref{minsum} using either norm yield the same sparse vectors $\mathbf{\overline x}_i$ (up to noise) provided $L_{2k}(\mathbf{B})$ is large enough \cite{?}.
+What our results hint at are conditions on the generating dictionary $\mathbf{A}$ and $k$-sparse codes $\mathbf{x}_i$ under which \emph{all} matrices $\mathbf{B}$ (of bounded column-norm) that solve Prob.~\ref{OptimizationProblem} also share this property by virtue of uniqueness and stability; that is, conditions which guarantee that the sparse codes $\mathbf{\overline x}_i$ solving Prob.~\ref{OptimizationProblem} also solve the convexified problem when the corresponding dictionary $\mathbf{B}$ is held fixed.
+It remains to determine, however, what practical conditions preclude matrices that don't solve Prob.~\ref{OptimizationProblem} from nonetheless solving the convexified problem.
+
+Regardless, an implication of the above observation is that the following algorithm solves Prob.~\ref{OptimizationProblem} without appeal to combinatorial search:
+\begin{enumerate}
+\item List all matrices $\mathbf{B}$.
+\item For each matrix $\mathbf{B}$, solve $\mathbf{\overline x}_i = \arg \min \|\mathbf{v}\|_1$ s.t. $\|\mathbf{Bv} - \mathbf{z}_i\| \leq \eta$ for $i = 1, \ldots, N$.
+\item Quantify the proposed solution $\mathbf{B}$ and $\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N$ as $\rho(\mathbf{B}, \mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N) = \sum_{i=1}^{N} \|\mathbf{\overline x}_i\|_0$.
+\item Output $\arg \min_{\mathbf{B}, \mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N} \left( \rho \right)$.
+ \end{enumerate}
 

### 2019-05-08 manuscripts/IEEE/final_submission.tex
my changes
thm1

@@
-% TODO: cite Fritz l0 paper in introduction for seemingly characteristic structure? Use those mentioned in PNAS response?
+% TODO: 
+% cite Fritz l0 paper in introduction for seemingly characteristic structure? 
 % Make L_H a definition..? Change def of L to be 1-norm so we don't need these sqrt k's?
-% When do we have polynomial complexity? Is it worth saying something about this for cyclic order (e.g. convolutions?)
-% mention regularity is probably not necessary
-% have i talked about making deterministic A?
-(see reviewer comment, and comment about easily meeting thm 1 conditions w deterministic construction).
-also after f(A).
-we make L_2k(a) with vandermonde, clarify this is way more than necessary...but it is necessary if we care about sparse coefficient recovery too, which is part of df of stable sparse representation.
-% IS THEOREM 3 AND ITS COROLLARY CORRECTLY STATED??
-% mention use of coherence instead of L_k? for practical criteria?
+% C_1 depends on J in Thm 1
+% also in proof of (7) x need not be *any* 2k-sparse vector...can instead restrict to some H...then 2k is restricted to half being on H.
 
@@
 \begin{align}\label{def1}
-\|\mathbf{A}_j - \mathbf{BPD}_j\|_2 \leq \delta_1 \ \ \text{and} \ \ \|\mathbf{x}_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_i\|_1 \leq \delta_2.
+\|\mathbf{A}_j - (\mathbf{BPD})_j\|_2 \leq \delta_1 \ \ \text{and} \ \ \|\mathbf{x}_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_i\|_1 \leq \delta_2.
 \end{align}
@@
 
-Moreover, if $\mathbf{A}$ satisfies \eqref{SparkCondition} and $\varepsilon < L_{2k}(\mathbf{A}) / C_1$, then $\mathbf{B}$ also satisfies \eqref{SparkCondition} with $L_{2k}(\mathbf{B}\mathbf{PD}) \geq L_{2k}(\mathbf{A}) - C_1 \varepsilon$, and for all $i \in [N]$:
+Moreover, if $\mathbf{A}_J$ satisfies \eqref{SparkCondition} and $\varepsilon < L_{2k}(\mathbf{A}_J) / C_1$, then $(\mathbf{BPD})_J$ also satisfies \eqref{SparkCondition} with $L_{2k}((\mathbf{B}\mathbf{PD})_J) \geq L_{2k}(\mathbf{A}_J) - C_1 \varepsilon$, and for all $i \in [N]$:
 \begin{align}\label{b-PDa}
 %\|\mathbf{x}^J_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}^{\overline J}_i\|_1 &\leq  \left( \frac{ 1+C_1 \|\mathbf{x}^{J}_i\|_1 }{ L_{2k}(\mathbf{A}) -  C_1\varepsilon } \right) \varepsilon \ \  \text{for $i \in [N]$}.
-\|(\mathbf{x}_i)_J - (\mathbf{D}^{-1}\mathbf{P}^{\top} \mathbf{\overline x}_i)_J\|_1 &\leq  \left( \frac{ 1+C_1 \|\mathbf{x}_i\|_1 }{ L_{2k}(\mathbf{A}) -  C_1\varepsilon } \right) \varepsilon,
+\|(\mathbf{x}_i)_J - (\mathbf{D}^{-1}\mathbf{P}^{\top} \mathbf{\overline x}_i)_J\|_1 &\leq  \left( \frac{ 1+C_1 \|(\mathbf{x}_i)_J\|_1 }{ L_{2k}(\mathbf{A}_J) -  C_1\varepsilon } \right) \varepsilon,
 \end{align}
@@
 
-We begin our proof of Thm.~\ref{DeterministicUniquenessTheorem} by showing how dictionary recovery \eqref{Cstable} already implies sparse code recovery \eqref{b-PDa} when $\mathbf{A}$ satisfies \eqref{SparkCondition} and \mbox{$\varepsilon < L_{2k}(\mathbf{A}) / C_1$}, assuming that $\overline m = m$ without loss of generality.
-Consider any $2k$-sparse $\mathbf{x} \in \mathbb{R}^m$ and note that $\|\mathbf{x}\|_1 \leq \sqrt{2k}  \|\mathbf{x}\|_2$.
-By definition of $L_{2k}$ in \eqref{Ldef}, we have:
+We begin our proof of Thm.~\ref{DeterministicUniquenessTheorem} by showing how dictionary recovery \eqref{Cstable} already implies sparse code recovery \eqref{b-PDa} when $\mathbf{A}_J$ satisfies \eqref{SparkCondition} and \mbox{$\varepsilon < L_{2k}(\mathbf{A}_J) / C_1$}.
+%, assuming that $\overline m = m$ without loss of generality.
+Consider any $2k$-sparse $\mathbf{x} \in \mathbb{R}^m$ and note that $\|\mathbf{x}\|_1 \leq \sqrt{2k}  \|\mathbf{x}\|_2$. By definition of $L_{2k}$ in \eqref{Ldef}, we have:
 \begin{align}\label{stuff}
-\|\mathbf{x}_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_i \|_1 \nonumber
-&\leq \frac{\|\mathbf{BPD}(\mathbf{x}_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_i)\|_2}{L_{2k}(\mathbf{BPD})} \\ \nonumber
-&\leq \frac{\|(\mathbf{BPD} - \mathbf{A})\mathbf{x}_i\|_2 + \|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline x}_i\|_2}{L_{2k}(\mathbf{BPD})} \\
-&\leq \frac{C_1\varepsilon \|\mathbf{x}_i\|_1 + \varepsilon}{L_{2k}(\mathbf{BPD})},
+\|\mathbf{x}_J - &( \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x} )_J\|_1 \nonumber
+\leq \frac{\|(\mathbf{BPD})_J(\mathbf{x}_J - (\mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x})_J)\|_2}{L_{2k}((\mathbf{BPD})_J)} \\ \nonumber
+&\leq \frac{\|( (\mathbf{BPD})_J - \mathbf{A}_J) \mathbf{x}_J\|_2 + \|\mathbf{A}_J\mathbf{x}_J - \mathbf{B}_J\mathbf{\overline x}_J\|_2}{L_{2k}((\mathbf{BPD})_J)} \\
+&\leq \frac{C_1\varepsilon \|\mathbf{x}_J\|_1 + \varepsilon}{L_{2k}((\mathbf{BPD})_J)},
 \end{align}
-where the term $C_1\varepsilon \|\mathbf{x}\|_1$ in the numerator above is a consequence of the triangle inequality applied to \eqref{Cstable}.
+where the term $C_1\varepsilon \|\mathbf{x}_J\|_1$ in the numerator above is a consequence of the triangle inequality applied to \eqref{Cstable}.
 
@@
 \begin{align*}
-\|\mathbf{BPD}\mathbf{x}\|_2 
-&\geq | \|\mathbf{A}\mathbf{x}\|_2 - \|(\mathbf{A}-\mathbf{BPD})\mathbf{x}\|_2 | \\
-&\geq \sqrt{2k} (L_{2k}(\mathbf{A}) -  C_1\varepsilon) \|\mathbf{x}\|_2,
+\|(\mathbf{BPD})_J\mathbf{x}_J\|_2 
+&\geq | \|\mathbf{A}_J\mathbf{x}_J\|_2 - \|(\mathbf{A}_J - (\mathbf{BPD})_J)\mathbf{x}_J\|_2 | \\
+&\geq \sqrt{2k} (L_{2k}(\mathbf{A}_J) -  C_1\varepsilon) \|\mathbf{x}_J\|_2,
 \end{align*}
 %
-wherein removal of the absolute value is justified since $C_1\varepsilon < L_{2k}(\mathbf{A})$.
-We therefore have that $L_{2k}(\mathbf{BPD}) \geq L_{2k}(\mathbf{A}) - C_1\varepsilon  > 0$, and \eqref{b-PDa} then follows from \eqref{stuff}.
+wherein removal of the absolute value is justified since $C_1\varepsilon < L_{2k}(\mathbf{A}_J)$.
+We therefore have that $L_{2k}((\mathbf{BPD})_J) \geq L_{2k}(\mathbf{A}_J) - C_1\varepsilon  > 0$, and \eqref{b-PDa} then follows from \eqref{stuff}.
 

### 2019-05-08 manuscripts/IEEE/final_submission.tex
minor

--- 2019-05-08 manuscripts/IEEE/final_submission.tex
@@
 %\title{When is the dictionary learning problem well-posed?}
-\title{On the uniqueness and stability of dictionaries for sparse representation of noisy signals}
+\title{On the uniqueness and stability of dictionaries \\ for sparse representation of noisy signals}
 %\title{When is the dictionary learning problem for sparse coding well-posed?}
@@
 We defer to Sec.~\ref{DUT} the technical proofs of Thms.~\ref{DeterministicUniquenessTheorem} and ~\ref{SLCopt}, following some necessary definitions and a useful fact in combinatorial matrix analysis (Lem.~\ref{MainLemma}; proved in the Appendix).
-Finally, we discuss in Sec.~\ref{Discussion} theoretical and practical applications of our mathematical observations.
+Finally, we discuss in Sec.~\ref{Discussion} applications of our mathematical observations as well as open problems.
 %The Appendix contains a proof of Lem.~\ref{MainLemma}.
@@
 \end{align*}
-where the last inequality follows directly from \eqref{Ldef}. From Def.~\ref{dDef}:
+where the last inequality uses \eqref{Ldef}. From Def.~\ref{dDef}:
 \begin{align}\label{rhs222}

### 2019-05-08 final_submission.tex

@@
 
-Moreover, if $\mathbf{A}$ satisfies \eqref{SparkCondition} and $\varepsilon < L_{2k}(\mathbf{A}) / C_1$, then $\mathbf{B}$ also satisfies \eqref{SparkCondition} with $L_{2k}(\mathbf{B}\mathbf{PD}) \geq L_{2k}(\mathbf{A}) - C_1 \varepsilon$ and for all $i \in [N]$:
+Moreover, if $\mathbf{A}_J$ satisfies \eqref{SparkCondition} and $\varepsilon < L_{2k}(\mathbf{A}_J) / C_1$, then $\mathbf{BPD}_J$ also satisfies \eqref{SparkCondition} with $L_{2k}(\mathbf{BPD}_J) \geq L_{2k}(\mathbf{A}_J) - C_1 \varepsilon$ and for all $i \in [N]$:
 \begin{align}\label{b-PDa}
 %\|\mathbf{x}^J_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}^{\overline J}_i\|_1 &\leq  \left( \frac{ 1+C_1 \|\mathbf{x}^{J}_i\|_1 }{ L_{2k}(\mathbf{A}) -  C_1\varepsilon } \right) \varepsilon \ \  \text{for $i \in [N]$}.
-\|(\mathbf{x}_i)_J - (\mathbf{D}^{-1}\mathbf{P}^{\top} \mathbf{\overline x}_i)_J\|_1 &\leq  \left( \frac{ 1+C_1 \|\mathbf{x}_i\|_1 }{ L_{2k}(\mathbf{A}) -  C_1\varepsilon } \right) \varepsilon,
+\|(\mathbf{x}_i)_J - (\mathbf{D}^{-1}\mathbf{P}^{\top} \mathbf{\overline x}_i)_J\|_1 &\leq  \left( \frac{ 1+C_1 \|(\mathbf{x}_i)_J\|_1 }{ L_{2k}(\mathbf{A}_J) -  C_1\varepsilon } \right) \varepsilon,
 \end{align}
@@
 \begin{align}\label{stuff}
-\|\mathbf{x}_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_i \|_1 \nonumber
-&\leq \frac{\|\mathbf{BPD}(\mathbf{x}_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_i)\|_2}{L_{2k}(\mathbf{BPD})} \\ \nonumber
-&\leq \frac{\|(\mathbf{BPD} - \mathbf{A})\mathbf{x}_i\|_2 + \|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline x}_i\|_2}{L_{2k}(\mathbf{BPD})} \\
-&\leq \frac{C_1\varepsilon \|\mathbf{x}_i\|_1 + \varepsilon}{L_{2k}(\mathbf{BPD})},
+\|\mathbf{x} - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x} \|_1 \nonumber
+&\leq \frac{\|\mathbf{BPD}(\mathbf{x} - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x})\|_2}{L_{2k}(\mathbf{BPD})} \\ \nonumber
+&\leq \frac{\|(\mathbf{BPD} - \mathbf{A})\mathbf{x}\|_2 + \|\mathbf{A}\mathbf{x} - \mathbf{B}\mathbf{\overline x}\|_2}{L_{2k}(\mathbf{BPD})} \\
+&\leq \frac{C_1\varepsilon \|\mathbf{x}\|_1 + \varepsilon}{L_{2k}(\mathbf{BPD})},
 \end{align}
-where the term $C_1\varepsilon \|\mathbf{x}\|_1$ in the numerator above follows from the triangle inequality applied to \eqref{Cstable}.
+where the term $C_1\varepsilon \|\mathbf{x}\|_1$ in the numerator above follows from the triangle inequality and \eqref{Cstable}.
 

### 2019-05-08 manuscripts/IEEE/final_submission.tex
merge

@@
 
-To extend this observation to arbitrary probability distributions, note that if a set of measure spaces $\{(X_{\ell}, \Sigma_{\ell}, \nu_{\ell})\}_{\ell=1}^p$ has $\nu_{\ell}$ absolutely continuous with respect to $\mu$ for all $\ell \in [p]$, where $\mu$ is the standard Borel measure on $\mathbb{R}$, then the product measure $\prod_{\ell=1}^p \nu_{\ell}$ is absolutely continuous with respect to the standard Borel product measure on $\mathbb{R}^p$ (e.g.,  \cite{folland2013real}).
+To extend this observation to arbitrary probability distributions, note that if a set of measure spaces $\{(X_{\ell}, \Sigma_{\ell}, \nu_{\ell})\}_{\ell=1}^p$ has $\nu_{\ell}$ absolutely continuous with respect to $\mu$ for all $\ell \in [p]$, where $\mu$ is the standard Borel measure on $\mathbb{R}$, then the product measure $\prod_{\ell=1}^p \nu_{\ell}$ is absolutely continuous with respect to the standard Borel product measure on $\mathbb{R}^p$ (e.g., see \cite{folland2013real}).
 This fact combined with Thm.~\ref{robustPolythm} implies the following.

### 2019-05-08 manuscripts/IEEE/final_submission.tex
added noisy learning figure

@@
 %>>>>>>> d1407a275dc391dabad7bb62d3e659f9a4ac4624
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=.24 \linewidth]{figs/basis.png}
+% \includegraphics[width=.25 \linewidth]{figs/Ahat_FastICA_M640_K8_noise0_2042}
+\includegraphics[width=.24 \linewidth]{figs/Ahat_FastICA_M640_K8_noise0_4083.png}
+\includegraphics[width=.24 \linewidth]{figs/Ahat_FastICA_M640_K8_noise1_0205.png}
+\includegraphics[width=.24 \linewidth]{figs/Ahat_FastICA_M640_K8_noise2_0409.png}
+\caption{\textbf{Noisy dictionary learning}.
+Recovery of the $8 \times 8$ discrete cosine transform (DCT) basis (the 64 columns of first matrix above) from $8$-sparse samples with linearly increasing noise (using the FastICA algorithm \cite{hyvarinen2000independent}).}
+\label{projdata}
+\end{center}
+\end{figure}
 

### 2019-05-08 manuscripts/IEEE/final_submission.tex
final through page 2

@@
 These guarantees also hold for a related (and perhaps more commonly posed) optimization problem which seeks a dictionary minimizing the average number of elementary waveforms required to reconstruct each sample of the dataset (Thm.~\ref{SLCopt}).
-Importantly, in both cases our explicit, universal guarantees apply without the imposition of \emph{any} constraints on learned dictionaries  (e.g.
-that they, too, be injective over some domain) beyond an upper bound on dictionary size, which is necessary in any case to avoid a trivial solution (e.g., allowing for $m = N$ elementary waveforms).
+Importantly, our explicit, universal guarantees apply without the imposition of \emph{any} constraints on learned dictionaries  (e.g.
+that they, too, be injective over some domain) beyond an upper bound on dictionary size, which is necessary to avoid trivial solutions (e.g., allowing for $m = N$ elementary waveforms).
 %That is, every pair of solutions of comparable size has some number of dictionary elements in common (up to noise), and similarly so for the coefficients of sparse codes they induce.
@@
 We defer to Sec.~\ref{DUT} the technical proofs of Thms.~\ref{DeterministicUniquenessTheorem} and ~\ref{SLCopt}, following some necessary definitions and a useful fact in combinatorial matrix analysis (Lem.~\ref{MainLemma}; proved in the Appendix).
-Finally, we discuss in Sec.~\ref{Discussion} applications of our mathematical observations as well as open problems.
+Finally, we discuss in Sec.~\ref{Discussion} applications of our mathematical observations as well as open questions.
 %The Appendix contains a proof of Lem.~\ref{MainLemma}.
@@
 
-Precise statements of our results require that we first identify some combinatorial criteria on the supports\footnote{Recall a vector $\mathbf{x}$ is said to be \emph{supported} in $S$ when $\mathbf{x} \in \text{\rm span}\{\mathbf{e}_j: j\in S\}$, with $\mathbf{e}_j$ forming the standard column basis.} of sparse vectors.
+Precise statements of our results require that we first identify some combinatorial criteria on the supports\footnote{Recall that a vector $\mathbf{x}$ is said to be \emph{supported} in $S$ when $\mathbf{x} \in \text{\rm span}\{\mathbf{e}_j: j\in S\}$, with $\mathbf{e}_j$ forming the standard column basis.} of sparse vectors.
 Let $\{1, \ldots, m\}$ be denoted $[m]$, its power set $2^{[m]}$, and ${[m] \choose k}$ the set of subsets of $[m]$ of size $k$.
@@
 We also write $2\mathcal{H} := \{ S \cup S': S, S' \in \mathcal{H}\}$.
+The following class of structured hypergraphs are a key ingredient in this work.
 
 \begin{definition}\label{sip}
-Given $\mathcal{H} \subseteq 2^{[m]}$, the \textbf{star} $\sigma(i)$ is the collection of sets in $\mathcal{H}$ containing $i$.
-We say $\mathcal{H}$ has the \textbf{singleton intersection property} (\textbf{SIP}) when $\cap \sigma(i) = \{i\}$ for all $i \in [m]$.
+Given $\mathcal{H} \subseteq 2^{[m]}$, the \textbf{star} $\sigma(j)$ is the collection of sets in $\mathcal{H}$ containing $j$.
+We say $\mathcal{H}$ has the \textbf{singleton intersection property} (\textbf{SIP}) when $\cap \sigma(j) = \{j\}$ for all $j \in [m]$.
 \end{definition}
@@
 We generalize the matrix lower bound for our purposes by restricting it to the spans of certain submatrices\footnote{See \cite{vidal2005generalized} for an overview of the related ``union of subspaces" model.} associated with a hypergraph $\mathcal{H} \subseteq {[m] \choose k}$ of column indices.
-Let $\mathbf{M}_S$ denote the submatrix formed by the columns of a matrix $\mathbf{M}$ indexed by $S \subseteq [m]$ ($\mathbf{M}_\emptyset := \mathbf{0}$).
-In the sections that follow, we also set $\bm{\mathcal{M}}_S$ to denote the column-span of a submatrix $\mathbf{M}_S$, and $\bm{\mathcal{M}}_\mathcal{G}$ to denote $\{\bm{\mathcal{M}}_S\}_{S \in \mathcal{G}}$.
+Let $\mathbf{M}_S$ denote the submatrix formed by the columns of a matrix $\mathbf{M}$ indexed by $S \subseteq [m]$ (setting $\mathbf{M}_\emptyset := \mathbf{0}$).
+In the sections that follow, we shall also let $\bm{\mathcal{M}}_S$ denote the column-span of a submatrix $\mathbf{M}_S$, and $\bm{\mathcal{M}}_\mathcal{G}$ to denote $\{\bm{\mathcal{M}}_S\}_{S \in \mathcal{G}}$.
 We define:  % Define $L_\mathcal{H}(\mathbf{M})$ as follows:
@@
 
-As explained above, compactness implies $L_{2k}(\mathbf{M}) > 0$ for all $\mathbf{M}$ satisfying \eqref{SparkCondition}.
+As explained above, compactness implies that $L_{2k}(\mathbf{M}) > 0$ for all $\mathbf{M}$ satisfying \eqref{SparkCondition}.
 Clearly, $L_{\mathcal{H}'}(\mathbf{M}) \geq L_\mathcal{H}(\mathbf{M})$ whenever $\mathcal{H}' \subseteq \mathcal{H}$, and any $k$-uniform $\mathcal{H}$ satisfying $\cup \mathcal{H} = [m]$ has $L_2 \geq L_{2\mathcal{H}} \geq L_{2k}$.
@@
 We are now in a position to state our main result, though for expository purposes we leave the quantity $C_1$ (a function of $\mathbf{A}$, $\mathbf{x}_1, \ldots, \mathbf{x}_N$, and $\mathcal{H}$) undefined until Eqn.~\eqref{Cdef1} of Sec.~\ref{DUT}.
-All results results below assume real matrices and vectors.
+All results  below assume real matrices and vectors.
 
@@
 Suppose that the $n \times m$ matrix $\mathbf{A}$ satisfies $L_{2\mathcal{H}}(\mathbf{A}) > 0$ for some $r$-regular $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP from Def.~\ref{sip}.
-If $k$-sparse \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N$} include more than $(k-1){\overline m \choose k}$ vectors in general linear position supported in each $S \in \mathcal{H}$, then there is $C_1 > 0$ (given by \eqref{Cdef1}) for which the following holds for all%\footnote{The condition $\varepsilon < L_2(\mathbf{A}) /C_1$ is necessary; otherwise,  with \mbox{$\mathbf{A}$ = $\mathbf{I}$} and $\mathbf{x}_i = \mathbf{e}_i$, there is a matrix $\mathbf{B}$ and $1$-sparse $\mathbf{\overline{x}}_i$ with $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline{x}}_i \|_2 \leq \varepsilon$ that nonetheless violates \eqref{Cstable}.} $\varepsilon < L_{2}(\mathbf{A}) / C_1$:
+If $k$-sparse \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N$} include more than $(k-1){\overline m \choose k}$ vectors in general linear position supported in each $S \in \mathcal{H}$, then there is $C_1 > 0$ for which the following holds for all%\footnote{The condition $\varepsilon < L_2(\mathbf{A}) /C_1$ is necessary; otherwise,  with \mbox{$\mathbf{A}$ = $\mathbf{I}$} and $\mathbf{x}_i = \mathbf{e}_i$, there is a matrix $\mathbf{B}$ and $1$-sparse $\mathbf{\overline{x}}_i$ with $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline{x}}_i \|_2 \leq \varepsilon$ that nonetheless violates \eqref{Cstable}.} $\varepsilon < L_{2}(\mathbf{A}) / C_1$:
 \footnote{Note that the condition $\varepsilon < L_2(\mathbf{A}) /C_1$ is necessary; otherwise, with \mbox{$\mathbf{A}$ = $\mathbf{I}$} (the identity matrix) and $\mathbf{x}_i = \mathbf{e}_i$, the matrix $\mathbf{B} = \left[\mathbf{0}, \frac{1}{2}(\mathbf{e}_1 + \mathbf{e}_2), \mathbf{e}_3, \ldots, \mathbf{e}_{m} \right]$ and sparse codes $\mathbf{\overline x}_i = \mathbf{e}_2$ for $i = 1, 2$ and $\mathbf{\overline x}_i = \mathbf{e}_i$ for $i \geq 3$ satisfy $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline{x}}_i \|_2 \leq \varepsilon$ but nonetheless violate \eqref{Cstable}.} $\varepsilon < L_{2}(\mathbf{A}) / C_1$:
@@
 %>>>>>>> d1407a275dc391dabad7bb62d3e659f9a4ac4624
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=.24 \linewidth]{figs/basis.png}
-% \includegraphics[width=.25 \linewidth]{figs/Ahat_FastICA_M640_K8_noise0_2042}
-\includegraphics[width=.24 \linewidth]{figs/Ahat_FastICA_M640_K8_noise0_4083.png}
-\includegraphics[width=.24 \linewidth]{figs/Ahat_FastICA_M640_K8_noise1_0205.png}
-\includegraphics[width=.24 \linewidth]{figs/Ahat_FastICA_M640_K8_noise2_0409.png}
-\caption{\textbf{Noisy dictionary learning}.
-Recovery of the $8 \times 8$ discrete cosine transform (DCT) basis (the 64 columns of first matrix above) from $8$-sparse samples with linearly increasing noise (using the FastICA algorithm \cite{hyvarinen2000independent}).}
-\label{projdata}
-\end{center}
-\end{figure}
 
@@
 %As mentioned above, there exist $k$-uniform regular hypergraphs $\mathcal{H}$ with the SIP having cardinality $|\mathcal{H}| = m$,
+
+\begin{figure}[t!]
+\begin{center}
+\includegraphics[width=.24 \linewidth]{figs/basis.png}
+% \includegraphics[width=.25 \linewidth]{figs/Ahat_FastICA_M640_K8_noise0_2042}
+\includegraphics[width=.24 \linewidth]{figs/Ahat_FastICA_M640_K8_noise0_4083.png}
+\includegraphics[width=.24 \linewidth]{figs/Ahat_FastICA_M640_K8_noise1_0205.png}
+\includegraphics[width=.24 \linewidth]{figs/Ahat_FastICA_M640_K8_noise2_0409.png}
+\caption{\textbf{Noisy dictionary learning}.
+Recovery of the $8 \times 8$ discrete cosine transform (DCT) basis (the 64 columns of first matrix above) from $8$-sparse samples with linearly increasing noise (using the FastICA algorithm \cite{hyvarinen2000independent}).}
+\label{projdata}
+\end{center}
+\end{figure}
 

### 2019-05-08 manuscripts/IEEE/final_submission.tex
clearer txt after thm 1

@@
 Finally, we say that a set of vectors sharing support $S$ are in \emph{general linear position} when any $|S|$ of them are linearly independent.
+Note that sparse codes in general linear position are straightforward to produce deterministically with a ``Vandermonde''  construction (i.e., by choosing columns of the matrix $[\gamma_{i}^j]_{i,j=1}^{k,N}$, for distinct nonzero $\gamma_i$).
 
@@
 %To be clear, the implication of Thm.~\ref{DeterministicUniquenessTheorem} is that $Y = \{\mathbf{Ax}_1, \ldots, \mathbf{Ax}_N\}$ has a stable $k$-sparse representation in $\mathbb{R}^m$, with \eqref{def1} guaranteed provided $\varepsilon$ in Def.~\ref{maindef} does not exceed:
-In words, Thm.~\ref{DeterministicUniquenessTheorem} says that the smaller the regularity $r$ of $\mathcal{H}$ or the difference $\overline m - m$ between the assumed and actual number of columns in the latent dictionary, the more columns and coefficients of the original dictionary $\mathbf{A}$ and sparse codes $\mathbf{x}_i$ are guaranteed to be contained (up to noise) in the appropriately scaled recovered dictionary $\mathbf{B}$ and codes $\mathbf{\overline x}_i$, respectively.
-In the particular case when $\overline m = m$, the theorem directly implies that  $Y = \{\mathbf{Ax}_1, \ldots, \mathbf{Ax}_N\}$ has a stable $k$-sparse representation in $\mathbb{R}^m$, with inequalities \eqref{def1} guaranteed for $\varepsilon$ in Def.~\ref{maindef} given by:
+In words, Thm.~\ref{DeterministicUniquenessTheorem} says that the smaller the regularity $r$ of original support hypergraph $\mathcal{H}$ or the difference $\overline m - m$ between assumed and actual number of elements in the latent dictionary, the more columns and coefficients of the original dictionary $\mathbf{A}$ and sparse codes $\mathbf{x}_i$ are guaranteed to be contained (up to noise) in the appropriately labelled and scaled recovered dictionary $\mathbf{B}$ and codes $\mathbf{\overline x}_i$, respectively.
+
+In the important special case when $\overline m = m$, the theorem directly implies that  $Y = \{\mathbf{Ax}_1, \ldots, \mathbf{Ax}_N\}$ has a stable $k$-sparse representation in $\mathbb{R}^m$, with inequalities \eqref{def1} guaranteed in Def.~\ref{maindef} for the following worst-case error $\varepsilon$:
 \begin{align}\label{epsdel}
@@
 
-We claim that the assumptions of Thm.~\ref{DeterministicUniquenessTheorem} are easily met with deterministic constructions.
+\begin{corollary}\label{DeterministicUniquenessCorollary}
+Given any regular hypergraph $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP, there are $N =  |\mathcal{H}| \left[ (k-1){m \choose k} + 1  \right]$ vectors \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} such that every matrix $\mathbf{A}$ with $L_{2k}(\mathbf{A}) > 0$ generates a dataset $Y = \{\mathbf{A}\mathbf{x}_1, \ldots, \mathbf{A}\mathbf{x}_N\}$ with a stable $k$-sparse representation in $\mathbb{R}^m$ for $\varepsilon(\delta_1,\delta_2)$ given by \eqref{epsdel}.
+\end{corollary}
+
+% prev
+%\begin{corollary}\label{DeterministicUniquenessCorollary}
+%Given any regular hypergraph $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP, there are $N =  |\mathcal{H}| \left[ (k-1){m \choose k} + 1  \right]$ vectors \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} such that every matrix $\mathbf{A}$ with $L_{2\mathcal{H}}(\mathbf{A}) > 0$ generates a dataset $Y = \{\mathbf{A}\mathbf{x}_1, \ldots, \mathbf{A}\mathbf{x}_N\}$ with a stable $k$-sparse representation in $\mathbb{R}^m$ for $\varepsilon(\delta_1,\delta_2)$ as in \eqref{epsdel}.
+%\end{corollary}
+
+%We claim that the assumptions of Thm.~\ref{DeterministicUniquenessTheorem} are easily met with deterministic constructions.
 In particular, sparse codes in general linear position are straightforward to produce using a ``Vandermonde'' matrix construction (i.e.
 use the columns of the matrix $[\gamma_{i}^j]_{i,j=1}^{k,N}$, for distinct nonzero $\gamma_i$).
+%
+
 % (Prob.~\ref{InverseProblem}).
@@
 
-\begin{corollary}\label{DeterministicUniquenessCorollary}
-Given any regular hypergraph $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP, there are $N =  |\mathcal{H}| \left[ (k-1){m \choose k} + 1  \right]$ vectors \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} such that every matrix $\mathbf{A}$ with $L_{2\mathcal{H}}(\mathbf{A}) > 0$ generates a dataset $Y = \{\mathbf{A}\mathbf{x}_1, \ldots, \mathbf{A}\mathbf{x}_N\}$ with a stable $k$-sparse representation in $\mathbb{R}^m$ for $\varepsilon(\delta_1,\delta_2)$ as in \eqref{epsdel}.
-\end{corollary}
 % Needs to be L_{2k}(A) > 0 to guarantee sparse vector recovery
@@
 
-One can also easily verify that for every $k < m$ there are regular $k$-uniform hypergraphs with the SIP besides the obvious $\mathcal{H} = {[m] \choose k}$.
+One can easily verify that for every $k < m$ there are regular $k$-uniform hypergraphs $\mathcal{H}$ with the SIP besides the obvious $\mathcal{H} = {[m] \choose k}$.
 For instance, take $\mathcal{H}$ to be the $k$-regular set of consecutive intervals of length $k$ in some cyclic order on $[m]$.
@@
 Special cases allow for even smaller hypergraphs, however.
-For example, if $k = \sqrt{m}$ then a 2-regular $k$-uniform hypergraph with the SIP can be constructed as the $2k$ rows and columns formed by arranging the elements of $[m]$ into a square grid.
+For example, if $k = \sqrt{m}$, then a 2-regular $k$-uniform hypergraph with the SIP can be constructed as the $2k$ rows and columns formed by arranging the elements of $[m]$ into a square grid.
 
@@
 As an example, let $\mathbf{A} = [ \mathbf{e}_1, \ldots, \mathbf{e}_5, \mathbf{v}]$ with $\mathbf{v} = \mathbf{e}_1 + \mathbf{e}_3 + \mathbf{e}_5$ and take $\mathcal{H}$ to be all consecutive pairs of indices $1, \ldots ,6$ arranged in cyclic order.
-Then for $k=2$, the matrix $\mathbf{A}$ fails to satisfy \eqref{SparkCondition} while still satisfying the first assumptions of Thm.~\ref{DeterministicUniquenessTheorem}.%, hence guaranteeing \eqref{Cstable} .
+Then for $k=2$, the matrix $\mathbf{A}$ fails to satisfy \eqref{SparkCondition} while still satisfying the first set of assumptions in Thm.~\ref{DeterministicUniquenessTheorem}.%, hence guaranteeing \eqref{Cstable} .
 %(since $\{ \mathbf{A}_1, \mathbf{A}_3, \mathbf{A}_5, \mathbf{A}_6\}$ is not a linearly independent set).

### 2019-05-08 manuscripts/IEEE/final_submission.tex
final through page 3

@@
 As an example, let $\mathbf{A} = [ \mathbf{e}_1, \ldots, \mathbf{e}_5, \mathbf{v}]$ with $\mathbf{v} = \mathbf{e}_1 + \mathbf{e}_3 + \mathbf{e}_5$ and take $\mathcal{H}$ to be all consecutive pairs of indices $1, \ldots ,6$ arranged in cyclic order.
-Then for $k=2$, the matrix $\mathbf{A}$ fails to satisfy \eqref{SparkCondition} while still satisfying the first set of assumptions in Thm.~\ref{DeterministicUniquenessTheorem}.%, hence guaranteeing \eqref{Cstable} .
+Then for $k=2$, the matrix $\mathbf{A}$ fails to satisfy \eqref{SparkCondition} while still obeying the first set of assumptions in Thm.~\ref{DeterministicUniquenessTheorem}.%, hence guaranteeing \eqref{Cstable} .
 %(since $\{ \mathbf{A}_1, \mathbf{A}_3, \mathbf{A}_5, \mathbf{A}_6\}$ is not a linearly independent set).
@@
 Briefly, following the same procedure as in \cite[Sec.~IV]{Hillar15}, for $k < m$ and $n \geq \min(2k, m)$ we may consider the ``symbolic'' dataset $Y = \{\mathbf{A}\mathbf{x}_1,\ldots,\mathbf{A} \mathbf{x}_N\}$ generated by an indeterminate $n \times m$ matrix $\mathbf{A}$ and $m$-dimensional $k$-sparse vectors $\mathbf{x}_1, \ldots, \mathbf{x}_N$ indeterminate within their supports, which form a regular hypergraph $\mathcal{H} \subseteq {[m] \choose k}$ satisfying the SIP.
-Restricting \mbox{$(k-1){m \choose k} + 1$} indeterminate $\mathbf{x}_i$ to each support in $\mathcal{H}$, and letting $\textbf{M}$ be the $n \times N$ matrix with columns $\mathbf{A}\mathbf{x}_i$, it can be checked that when $f(\mathbf{M}) \neq 0$ for a substitution of real numbers for the indeterminates, all of the assumptions on $\mathbf{A}$ and $\mathbf{x}_i$ in Thm.~\ref{DeterministicUniquenessTheorem} are satisfied; in particular, $\mathbf{A}$ satisfies \eqref{SparkCondition}.
+Restricting \mbox{$(k-1){m \choose k} + 1$} indeterminate $\mathbf{x}_i$ to each support in $\mathcal{H}$, and letting $\textbf{M}$ be the $n \times N$ matrix with columns $\mathbf{A}\mathbf{x}_i$, it can be checked that when $f(\mathbf{M}) \neq 0$ for a substitution of real numbers for the indeterminates, all of the assumptions on $\mathbf{A}$ and $\mathbf{x}_i$ in Thm.~\ref{DeterministicUniquenessTheorem} are satisfied.
 We therefore have the following result.
+% ; in particular, $\mathbf{A}$ satisfies \eqref{SparkCondition}
 
@@
 
-To extend this observation to arbitrary probability distributions, note that if a set of measure spaces $\{(X_{\ell}, \Sigma_{\ell}, \nu_{\ell})\}_{\ell=1}^p$ has $\nu_{\ell}$ absolutely continuous with respect to $\mu$ for all $\ell \in [p]$, where $\mu$ is the standard Borel measure on $\mathbb{R}$, then the product measure $\prod_{\ell=1}^p \nu_{\ell}$ is absolutely continuous with respect to the standard Borel product measure on $\mathbb{R}^p$ (e.g., see \cite{folland2013real}).
+To extend this observation to arbitrary probability distributions, note that if a set of measure spaces $\{(X_{\ell}, \nu_{\ell})\}_{\ell=1}^p$ has $\nu_{\ell}$ absolutely continuous with respect to $\mu$ for all $\ell \in [p]$, where $\mu$ is the standard Borel measure on $\mathbb{R}$, then the product measure $\prod_{\ell=1}^p \nu_{\ell}$ is also absolutely continuous with respect to the standard Borel product measure on $\mathbb{R}^p$ (e.g., see \cite{folland2013real}).
 This fact combined with Thm.~\ref{robustPolythm} implies the following.

### 2019-05-08 manuscripts/IEEE/final_submission.tex
final through page 3

@@
 
-In the important special case when $\overline m = m$, the theorem directly implies that  $Y = \{\mathbf{Ax}_1, \ldots, \mathbf{Ax}_N\}$ has a stable $k$-sparse representation in $\mathbb{R}^m$, with inequalities \eqref{def1} guaranteed in Def.~\ref{maindef} for the following worst-case error $\varepsilon$:
+In the important special case when $\overline m = m$, the theorem directly implies (e.g., Fig.~\ref{noisyrecovery}) that  $Y = \{\mathbf{Ax}_1, \ldots, \mathbf{Ax}_N\}$ has a stable $k$-sparse representation in $\mathbb{R}^m$, with inequalities \eqref{def1} guaranteed in Def.~\ref{maindef} for the following worst-case error $\varepsilon$:
 \begin{align}\label{epsdel}
@@
 Recovery of the $8 \times 8$ discrete cosine transform (DCT) basis (the 64 columns of first matrix above) from $8$-sparse samples with linearly increasing noise (using the FastICA algorithm \cite{hyvarinen2000independent}).}
-\label{projdata}
+\vspace{-.6 cm}
+\label{noisyrecovery}
 \end{center}
@@
 Another extension of Thm.~\ref{DeterministicUniquenessTheorem} can be derived from the following analytic characterization of the spark condition.
-Letting $\mathbf{A}$ be the $n \times m$ matrix of $nm$ indeterminates $A_{ij}$, the reader may work out why substituting real numbers for the $A_{ij}$ yields a matrix satisfying \eqref{SparkCondition} if and only if the following polynomial also evaluates to a nonzero number:
+Letting $\mathbf{A}$ be the $n \times m$ matrix of $nm$ indeterminates $A_{ij}$, the reader may work out why substituting real numbers for the $A_{ij}$ yields a matrix satisfying \eqref{SparkCondition} if and only if the following polynomial evaluates to a nonzero number:
 \begin{align*}
@@
 
-Since $f$ is analytic, having a single substitution of a real matrix $\mathbf{A}$ satisfy $f(\mathbf{A}) \neq 0$ implies that the zeroes of $f$ form a set of (Borel) measure zero.
-Such a matrix is easily constructed by adding rows of zeroes to any $\min(2k,m) \times m$ Vandermonde matrix as described previously, so that every sum in the product defining $f$ above is strictly positive.
-Almost every $n \times m$ matrix with $n \geq \min(2k,m)$ thus satisfies \eqref{SparkCondition}.
+Since $f$ is analytic, having a single substitution of a real matrix $\mathbf{A}$ satisfying $f(\mathbf{A}) \neq 0$ implies that the zeroes of $f$ form a set of (Borel) measure zero.
+Such a matrix is easily constructed by adding rows of zeroes to a $\min(2k,m) \times m$ Vandermonde matrix as described previously, so that every sum in the product defining $f$ above is strictly positive.
+Thus, almost every $n \times m$ matrix with $n \geq \min(2k,m)$ satisfies \eqref{SparkCondition}.
 
@@
 We claim that a similar phenomenon applies to datasets of vectors with a stable sparse representation.
-Briefly, following the same procedure as in \cite[Sec.~IV]{Hillar15}, for $k < m$ and $n \geq \min(2k, m)$ we may consider the ``symbolic'' dataset $Y = \{\mathbf{A}\mathbf{x}_1,\ldots,\mathbf{A} \mathbf{x}_N\}$ generated by an indeterminate $n \times m$ matrix $\mathbf{A}$ and $m$-dimensional $k$-sparse vectors $\mathbf{x}_1, \ldots, \mathbf{x}_N$ indeterminate within their supports, which form a regular hypergraph $\mathcal{H} \subseteq {[m] \choose k}$ satisfying the SIP.
+Briefly, following the same procedure as in \cite[Sec.~IV]{Hillar15}, for $k < m$ and $n \geq \min(2k, m)$, we may consider the ``symbolic'' dataset $Y = \{\mathbf{A}\mathbf{x}_1,\ldots,\mathbf{A} \mathbf{x}_N\}$ generated by an indeterminate $n \times m$ matrix $\mathbf{A}$ and $m$-dimensional $k$-sparse vectors $\mathbf{x}_1, \ldots, \mathbf{x}_N$ indeterminate within their supports, which form a regular hypergraph $\mathcal{H} \subseteq {[m] \choose k}$ satisfying the SIP.
 Restricting \mbox{$(k-1){m \choose k} + 1$} indeterminate $\mathbf{x}_i$ to each support in $\mathcal{H}$, and letting $\textbf{M}$ be the $n \times N$ matrix with columns $\mathbf{A}\mathbf{x}_i$, it can be checked that when $f(\mathbf{M}) \neq 0$ for a substitution of real numbers for the indeterminates, all of the assumptions on $\mathbf{A}$ and $\mathbf{x}_i$ in Thm.~\ref{DeterministicUniquenessTheorem} are satisfied.

### 2019-05-08 manuscripts/IEEE/final_submission.tex
minor

@@
 Restricting \mbox{$(k-1){m \choose k} + 1$} indeterminate $\mathbf{x}_i$ to each support in $\mathcal{H}$, and letting $\textbf{M}$ be the $n \times N$ matrix with columns $\mathbf{A}\mathbf{x}_i$, it can be checked that when $f(\mathbf{M}) \neq 0$ for a substitution of real numbers for the indeterminates, all of the assumptions on $\mathbf{A}$ and $\mathbf{x}_i$ in Thm.~\ref{DeterministicUniquenessTheorem} are satisfied.
-We therefore have the following result.
+We therefore have the following.
 % ; in particular, $\mathbf{A}$ satisfies \eqref{SparkCondition}
@@
 Our results demonstrate that sparse codes $\mathbf{x}_i$ drawn from only a polynomial number of $k$-dimensional subspaces permit stable identification of the generating dictionary $\mathbf{A}$.
-This lends some legitimacy to the use of the sparse coding model in practice, where data in general are unlikely (if ever) to exhibit the exponentially many possible $k$-wise combinations of dictionary elements required by (to our knowledge) all previously published results.
-Consequently, if $k$ is held fixed or if the size of the support set of reconstructing codes is known to be polynomial in $\overline m$ and $k$, then a practical (polynomial) amount of data suffices to identify the dictionary.\footnote{In the latter case, a reexamination of the pigeonholing argument in the proof of Thm.~\ref{DeterministicUniquenessTheorem} requires a polynomial number of samples distributed over a polynomial number of supports.} Reasons to be skeptical that this holds in general, however, can be found in \cite{tillmann2014computational, Tillmann15}.
+This lends some legitimacy to the use of the model in practice, where data in general are unlikely (if ever) to exhibit the exponentially many possible $k$-wise combinations of dictionary elements required by (to our knowledge) all previously published results.
+Consequently, if $k$ is held fixed or if the size of the support set of reconstructing codes is polynomial in $\overline m$ and $k$, then a practical (polynomial) amount of data suffices to identify the dictionary.\footnote{In the latter case, a reexamination of the pigeonholing argument in the proof of Thm.~\ref{DeterministicUniquenessTheorem} requires a polynomial number of samples distributed over a polynomial number of supports.} Reasons to be skeptical that this holds in general, however, can be found in \cite{tillmann2014computational, Tillmann15}.
 Even so, in the next section we discuss how probabilistic guarantees can in fact be made for any number of available samples.

### 2019-05-08 manuscripts/IEEE/final_submission.tex
chaz incoherence comment

@@
 There is no known fast computation of $L_k$ in general, however, since even $L_{k} > 0$ is NP-hard \cite{tillmann2014computational}, although
-%efficiently computable bounds have been proposed (e.g. the ``mutual coherence" of a matrix \cite{donoho2003optimally}); alternatively, 
+efficiently computable bounds have been proposed (e.g., via the ``mutual coherence" of a matrix \cite{donoho2003optimally}); alternatively, 
 fixing $k$ yields polynomial complexity.

### 2019-05-08 manuscripts/IEEE/final_submission.tex
discussion edits

@@
 
-One direct application of our work is to neural theory, wherein our theorems justify the mathematical soundness of one of the few hypothesized theories of bottleneck communication in the brain \cite{Isely10}: that sparse neural population activity is recoverable from its noisy linear compression through a randomly constructed (but unknown) wiring bottleneck by any biologically plausible unsupervised sparse coding method that solves Prob.~\ref{DeterministicUniquenessTheorem} or \ref{SLCopt} (e.g., \cite{rehnsommer2007, rozell2007neurally, pehlevan2015normative}).\footnote{We refer the reader to \cite{ganguli2012compressed} for more on interactions between dictionary learning and neuroscience.}
+One direct application of this work is to theoretical neuroscience, wherein our theorems justify the mathematical soundness of one of the few hypothesized theories of bottleneck communication in the brain \cite{Isely10}: that sparse neural population activity is recoverable from its noisy linear compression through a randomly constructed (but unknown) wiring bottleneck by any biologically plausible unsupervised sparse coding method that solves Prob.~\ref{DeterministicUniquenessTheorem} or \ref{SLCopt} (e.g., \cite{rehnsommer2007, rozell2007neurally, pehlevan2015normative}).\footnote{We refer the reader to \cite{ganguli2012compressed} for more on interactions between dictionary learning and neuroscience.}
 
@@
 
-Beyond an extension of existing noiseless guarantees \cite{Hillar15} to the noisy regime and their novel application to Prob.~\ref{OptimizationProblem}, our work contains a theory of combinatorial designs for support sets key to the identification of the dictionary.
-We incorporate this idea into a fundamental lemma in matrix theory (Lem.~\ref{MainLemma}) that draws upon the definition of a new matrix lower bound induced by a hypergraph.
-New insights enabled by this combinatorial approach include: 1) a subset of dictionary elements is recoverable even if dictionary size is overestimated, 2) data require only a polynomial number of distinct sparse supports, and 3) recoverable dictionaries need not necessarily satisfy the spark condition.
+Beyond an extension of existing noiseless guarantees \cite{Hillar15} to the noisy regime and their novel application to Prob.~\ref{OptimizationProblem}, our work contains a theory of combinatorial designs for support sets key to identification of dictionaries.
+We incorporate this idea into a fundamental lemma in matrix theory (Lem.~\ref{MainLemma}) that draws upon the definition of a matrix lower bound induced by a hypergraph.
+New insights enabled by this combinatorial approach include: 1) a subset of dictionary elements is recoverable even if dictionary size is overestimated, 2) data require only a polynomial number of distinct sparse supports, and 3) recoverable dictionaries need not satisfy the spark condition.
 
-The absence of any assumption at all about dictionaries that solve Prob.~\ref{InverseProblem} was a major technical difficulty in proving Thm.~\ref{DeterministicUniquenessTheorem}.
-We sought such a general guarantee because of the practical difficulty of ensuring that an algorithm maintain a dictionary satisfying the spark condition \eqref{SparkCondition} at each iteration, an implicit requirement of all previous works except \cite{Hillar15}; indeed, even certifying a dictionary has this property is NP-hard \cite{tillmann2014computational}.
+The absence of any assumptions about dictionaries solving Prob.~\ref{InverseProblem} was a major technical difficulty in proving Thm.~\ref{DeterministicUniquenessTheorem}.
+We sought such a general guarantee because of the practical difficulty in ensuring that an algorithm maintain a dictionary satisfying the spark condition \eqref{SparkCondition} at each iteration, an implicit requirement of all previous works except \cite{Hillar15}; indeed, even certifying a dictionary has this property is NP-hard \cite{tillmann2014computational}.
 
 In fact, uniqueness guarantees with minimal assumptions apply to all areas of data science and engineering that utilize learned sparse structure.
-For example, several groups have applied compressed sensing to signal processing tasks; e.g., for MRI analysis \cite{lustig2008compressed}, image compression \cite{Duarte08}, and even the design of an ultrafast camera \cite{Gao14}.
-It is only a matter of time before these systems incorporate dictionary learning to encode and decode signals (e.g., in a device that learns structure from motion \cite{kong2016prior}), just as scientists have used it to make sense of their data \cite{jung2001imaging, Agarwal14, lee2016sparse, wu2016stability}.
+For example, several groups have applied compressed sensing to signal processing tasks; for instance, in MRI analysis \cite{lustig2008compressed}, image compression \cite{Duarte08}, and even the design of an ultrafast camera \cite{Gao14}.
+It is only a matter of time before these systems incorporate dictionary learning to encode and decode signals (e.g., in a device that learns structure from motion \cite{kong2016prior}), just as scientists have used sparse coding to make sense of their data \cite{jung2001imaging, agarwal2014spatially, lee2016sparse, wu2016stability}.
 
-Assurances such as those offered by our theorems certify that different devices and algorithms (with different initialization, etc.) will learn equivalent representations given enough data from statistically identical systems.\footnote{To contrast with the current hot topic of ``Deep Learning'', there are few such uniqueness guarantees for these models of data; moreover, even small noise can dramatically alter their output \cite{goodfellow2014explaining}.} Indeed, a main reason for the sustained interest in dictionary learning as an unsupervised method for data analysis seems to be the assumed well-posedness of parameter identification in the sparse coding model, confirmation of which forms the core of our theoretical findings.
+Assurances such as those offered by our theorems certify that different devices and algorithms will learn equivalent representations given enough data from statistically identical systems.\footnote{To contrast with the current hot topic of ``Deep Learning'', there are few such uniqueness guarantees for these models of data; moreover, even small noise can dramatically alter their output \cite{goodfellow2014explaining}.} Indeed, a main reason for the sustained interest in dictionary learning as an unsupervised method for data analysis seems to be the assumed well-posedness of parameter identification in the sparse coding model, confirmation of which forms the core of our theoretical findings.
 

### 2019-05-08 manuscripts/IEEE/final_submission.tex
added open questions end discussion

@@
 
+\begin{figure}[t!]
+\begin{center}
+\includegraphics[width=.24 \linewidth]{figs/basis.png}
+% \includegraphics[width=.25 \linewidth]{figs/Ahat_FastICA_M640_K8_noise0_2042}
+\includegraphics[width=.24 \linewidth]{figs/Ahat_FastICA_M640_K8_noise0_4083.png}
+\includegraphics[width=.24 \linewidth]{figs/Ahat_FastICA_M640_K8_noise1_0205.png}
+\includegraphics[width=.24 \linewidth]{figs/Ahat_FastICA_M640_K8_noise2_0409.png}
+\caption{\textbf{Noisy dictionary learning}.
+Recovery of the $8 \times 8$ discrete cosine transform (DCT) basis (the 64 columns of first matrix above) from $8$-sparse samples with linearly increasing noise (using the FastICA algorithm \cite{hyvarinen2000independent}).}
+\vspace{-.6 cm}
+\label{noisyrecovery}
+\end{center}
+\end{figure}
+
 We next give a quantitative generalization of the spark condition (\ref{SparkCondition}) to combinatorial subsets of supports.
@@
 %As mentioned above, there exist $k$-uniform regular hypergraphs $\mathcal{H}$ with the SIP having cardinality $|\mathcal{H}| = m$,
-
-\begin{figure}[t!]
-\begin{center}
-\includegraphics[width=.24 \linewidth]{figs/basis.png}
-% \includegraphics[width=.25 \linewidth]{figs/Ahat_FastICA_M640_K8_noise0_2042}
-\includegraphics[width=.24 \linewidth]{figs/Ahat_FastICA_M640_K8_noise0_4083.png}
-\includegraphics[width=.24 \linewidth]{figs/Ahat_FastICA_M640_K8_noise1_0205.png}
-\includegraphics[width=.24 \linewidth]{figs/Ahat_FastICA_M640_K8_noise2_0409.png}
-\caption{\textbf{Noisy dictionary learning}.
-Recovery of the $8 \times 8$ discrete cosine transform (DCT) basis (the 64 columns of first matrix above) from $8$-sparse samples with linearly increasing noise (using the FastICA algorithm \cite{hyvarinen2000independent}).}
-\vspace{-.6 cm}
-\label{noisyrecovery}
-\end{center}
-\end{figure}
 
@@
 
+We close with some remaining open questions.
+First, there is the basic problem of proving optimal lower bounds on sufficient sample size for uniquness and stability in sparse coding.
+Additionally, given the NP-hardness of verifying the spark condition for matrices, is approximating a solution to Prob.~\ref{InverseProblem} or \ref{OptimizationProblem} also computationally hard?
+Finally, as $\ell_1$ relaxations for inferring sparse vectors have, in many cases, the same solutions as for $\ell_0$, is there an $\ell_1$ version of Thm.~\ref{SLCopt}?
+
+\textbf{Acknowledgement.} We thank F. Sommer and D. Rhea for early thoughts, and I. Morris for posting \eqref{eqdim} online.
+
 \section{EXTRA}
@@
  \end{enumerate}
-
-\textbf{Acknowledgement.} We thank F. Sommer and D. Rhea for early thoughts, and I. Morris for posting \eqref{eqdim} online.
 

### 2019-05-08 manuscripts/IEEE/final_submission.tex
chaz edits

@@
 The main result of this work is a very general uniqueness theorem for sparse coding (Thm.~\ref{DeterministicUniquenessTheorem}) directly 
-implying (Cor.~\ref{DeterministicUniquenessCorollary}) that stable representations of a dataset $Z$ are guaranteed whenever generating dictionaries $A$ satisfy a spark condition on supports and the original sparse codes $\mathbf{x}_i$ are sufficiently diverse.
+implying (Cor.~\ref{DeterministicUniquenessCorollary}) that stable representations of a dataset $Z$ are guaranteed whenever generating dictionaries $\mathbf{A}$ satisfy a spark condition on supports and the original sparse codes $\mathbf{x}_i$ are sufficiently diverse.
 Moreover, we provide an explicit, computable $\varepsilon(\delta_1, \delta_2)$ in (\ref{epsdel}) that is essentially linear in desired accuracy $\delta_1, \delta_2$.
@@
 In the next section, we give precise statements of these findings.
-We then extend the same guarantees (Thm.~\ref{SLCopt}) to the following alternate formulation of dictionary learning, which minimizes the number of nonzero entries in sparse codes.
+We then extend the same guarantees (Thm.~\ref{SLCopt}) to the following alternate formulation of dictionary learning, which minimizes the total number of nonzero entries in sparse codes.
 
@@
 
-Our development of Thm.~\ref{DeterministicUniquenessTheorem} is general enough to provide some uniqueness stability even when generating $A$ do not fully satisfy (\ref{SparkCondition}) and recovery dictionaries $B$ have more columns than $A$.
+Our development of Thm.~\ref{DeterministicUniquenessTheorem} is general enough to provide some uniqueness and stability even when generating $\mathbf{A}$ do not fully satisfy (\ref{SparkCondition}) and recovery dictionaries $\mathbf{B}$ have more columns than $\mathbf{A}$.
 Moreover, the approach incorporates a combinatorial theory for designing generating codes that should be of independent interest.
@@
 %
-writing also $L_{k}$ in place of $L_\mathcal{H}$ when $\mathcal{H} = {[m] \choose k}$.\footnote{In compressed sensing literature, \mbox{$1 - \sqrt{k} L_k(\mathbf{M})$}  is the asymmetric lower restricted isometry constant for $\mathbf{M}$ with unit $\ell_2$-norm columns \cite{Blanchard2011}.}
-
-As explained above, compactness implies that $L_{2k}(\mathbf{M}) > 0$ for all $\mathbf{M}$ satisfying \eqref{SparkCondition}.
+writing also $L_{k}$ in place of $L_\mathcal{H}$ when $\mathcal{H} = {[m] \choose k}$.\footnote{In compressed sensing literature, \mbox{$1 - \sqrt{k} L_k(\mathbf{M})$}  is the asymmetric lower restricted isometry constant for $\mathbf{M}$ with unit $\ell_2$-norm columns \cite{Blanchard2011}.}  As explained above, compactness implies that $L_{2k}(\mathbf{M}) > 0$ for all $\mathbf{M}$ satisfying \eqref{SparkCondition}.
 Clearly, $L_{\mathcal{H}'}(\mathbf{M}) \geq L_\mathcal{H}(\mathbf{M})$ whenever $\mathcal{H}' \subseteq \mathcal{H}$, and any $k$-uniform $\mathcal{H}$ satisfying $\cup \mathcal{H} = [m]$ has $L_2 \geq L_{2\mathcal{H}} \geq L_{2k}$.
-Finally, we say that a set of vectors sharing support $S$ are in \emph{general linear position} when any $|S|$ of them are linearly independent.
-Note that sparse codes in general linear position are straightforward to produce deterministically with a ``Vandermonde''  construction (i.e., by choosing columns of the matrix $[\gamma_{i}^j]_{i,j=1}^{k,N}$, for distinct nonzero $\gamma_i$).
 
@@
 Suppose that the $n \times m$ matrix $\mathbf{A}$ satisfies $L_{2\mathcal{H}}(\mathbf{A}) > 0$ for some $r$-regular $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP from Def.~\ref{sip}.
-If $k$-sparse \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N$} include more than $(k-1){\overline m \choose k}$ vectors in general linear position supported in each $S \in \mathcal{H}$, then there is $C_1 > 0$ for which the following holds for all%\footnote{The condition $\varepsilon < L_2(\mathbf{A}) /C_1$ is necessary; otherwise,  with \mbox{$\mathbf{A}$ = $\mathbf{I}$} and $\mathbf{x}_i = \mathbf{e}_i$, there is a matrix $\mathbf{B}$ and $1$-sparse $\mathbf{\overline{x}}_i$ with $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline{x}}_i \|_2 \leq \varepsilon$ that nonetheless violates \eqref{Cstable}.} $\varepsilon < L_{2}(\mathbf{A}) / C_1$:
+If $k$-sparse \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N$} include more than $(k-1){\overline m \choose k}$ vectors in general linear position\footnote{Recall that a set of vectors sharing support $S$ are in \emph{general linear position} when any $|S|$ of them are linearly independent.} supported in each $S \in \mathcal{H}$, then there is $C_1 > 0$ for which the following holds for all%\footnote{The condition $\varepsilon < L_2(\mathbf{A}) /C_1$ is necessary; otherwise,  with \mbox{$\mathbf{A}$ = $\mathbf{I}$} and $\mathbf{x}_i = \mathbf{e}_i$, there is a matrix $\mathbf{B}$ and $1$-sparse $\mathbf{\overline{x}}_i$ with $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline{x}}_i \|_2 \leq \varepsilon$ that nonetheless violates \eqref{Cstable}.} $\varepsilon < L_{2}(\mathbf{A}) / C_1$:
 \footnote{Note that the condition $\varepsilon < L_2(\mathbf{A}) /C_1$ is necessary; otherwise, with \mbox{$\mathbf{A}$ = $\mathbf{I}$} (the identity matrix) and $\mathbf{x}_i = \mathbf{e}_i$, the matrix $\mathbf{B} = \left[\mathbf{0}, \frac{1}{2}(\mathbf{e}_1 + \mathbf{e}_2), \mathbf{e}_3, \ldots, \mathbf{e}_{m} \right]$ and sparse codes $\mathbf{\overline x}_i = \mathbf{e}_2$ for $i = 1, 2$ and $\mathbf{\overline x}_i = \mathbf{e}_i$ for $i \geq 3$ satisfy $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline{x}}_i \|_2 \leq \varepsilon$ but nonetheless violate \eqref{Cstable}.} $\varepsilon < L_{2}(\mathbf{A}) / C_1$:
@@
 In words, Thm.~\ref{DeterministicUniquenessTheorem} says that the smaller the regularity $r$ of original support hypergraph $\mathcal{H}$ or the difference $\overline m - m$ between assumed and actual number of elements in the latent dictionary, the more columns and coefficients of the original dictionary $\mathbf{A}$ and sparse codes $\mathbf{x}_i$ are guaranteed to be contained (up to noise) in the appropriately labelled and scaled recovered dictionary $\mathbf{B}$ and codes $\mathbf{\overline x}_i$, respectively.
-
 In the important special case when $\overline m = m$, the theorem directly implies (e.g., Fig.~\ref{noisyrecovery}) that  $Y = \{\mathbf{Ax}_1, \ldots, \mathbf{Ax}_N\}$ has a stable $k$-sparse representation in $\mathbb{R}^m$, with inequalities \eqref{def1} guaranteed in Def.~\ref{maindef} for the following worst-case error $\varepsilon$:
@@
 
+Note that sparse codes in general linear position are straightforward to produce deterministically with a ``Vandermonde''  construction (i.e., by choosing columns of the matrix $[\gamma_{i}^j]_{i,j=1}^{k,N}$, for distinct nonzero $\gamma_i$).
+We therefore have the following direct consequence of Thm.~\ref{DeterministicUniquenessTheorem}.
+
 \begin{corollary}\label{DeterministicUniquenessCorollary}
-Given any regular hypergraph $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP, there are $N =  |\mathcal{H}| \left[ (k-1){m \choose k} + 1  \right]$ vectors \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} such that every matrix $\mathbf{A}$ with $L_{2k}(\mathbf{A}) > 0$ generates a dataset $Y = \{\mathbf{A}\mathbf{x}_1, \ldots, \mathbf{A}\mathbf{x}_N\}$ with a stable $k$-sparse representation in $\mathbb{R}^m$ for $\varepsilon(\delta_1,\delta_2)$ given by \eqref{epsdel}.
+Given any regular hypergraph $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP, there are $N =  |\mathcal{H}| \left[ (k-1){m \choose k} + 1  \right]$ vectors \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} such that every matrix $\mathbf{A}$ with satisfying \eqref{SparkCondition} generates a dataset $Y = \{\mathbf{A}\mathbf{x}_1, \ldots, \mathbf{A}\mathbf{x}_N\}$ with a stable $k$-sparse representation in $\mathbb{R}^m$ for $\varepsilon(\delta_1,\delta_2)$ given by \eqref{epsdel}.
 \end{corollary}
@@
 
-To extend this observation to arbitrary probability distributions, note that if a set of measure spaces $\{(X_{\ell}, \nu_{\ell})\}_{\ell=1}^p$ has $\nu_{\ell}$ absolutely continuous with respect to $\mu$ for all $\ell \in [p]$, where $\mu$ is the standard Borel measure on $\mathbb{R}$, then the product measure $\prod_{\ell=1}^p \nu_{\ell}$ is also absolutely continuous with respect to the standard Borel product measure on $\mathbb{R}^p$ (e.g., see \cite{folland2013real}).
+To extend this observation to arbitrary probability distributions, note that if a set of measure spaces $\{(X_{\ell}, \nu_{\ell})\}_{\ell=1}^p$ has measures $\nu_{\ell}$ absolutely continuous with respect to the standard Borel measure on $\mathbb{R}$ for all $\ell \in [p]$, then the product measure $\prod_{\ell=1}^p \nu_{\ell}$ is also absolutely continuous with respect to the standard Borel product measure on $\mathbb{R}^p$ (e.g., see \cite{folland2013real}).
 This fact combined with Thm.~\ref{robustPolythm} implies the following.
@@
 \begin{corollary}\label{ProbabilisticCor}
-If indeterminate entries of $\mathbf{A}$ and $\mathbf{x}_i$ are drawn independently from probability measures absolutely continuous with respect to the standard Borel measure, then $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$ with probability one.
+If the indeterminate entries of $\mathbf{A}$ and the $\mathbf{x}_i$ are drawn independently from probability measures absolutely continuous with respect to the standard Borel measure, then $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$ with probability one.
 \end{corollary}
@@
 We close with some remaining open questions.
-First, there is the basic problem of proving optimal lower bounds on sufficient sample size for uniquness and stability in sparse coding.
+First, there is the basic problem of proving optimal lower bounds on sufficient sample size for uniqueness and stability in sparse coding.
 Additionally, given the NP-hardness of verifying the spark condition for matrices, is approximating a solution to Prob.~\ref{InverseProblem} or \ref{OptimizationProblem} also computationally hard?
 Finally, as $\ell_1$ relaxations for inferring sparse vectors have, in many cases, the same solutions as for $\ell_0$, is there an $\ell_1$ version of Thm.~\ref{SLCopt}?
+In what special cases is it efficient to check that a solution to the problems is optimal?
 

### 2019-05-08 manuscripts/IEEE/final_submission.tex
sigma

@@
 %
-then $\overline m \geq m$; and if $\overline m  (r-1) < mr$, the map $i \mapsto \cap \pi(\sigma(i))$ is an injective function to $[\overline m]$ from some $J \subseteq [m]$ of size $m - (r-1)(\overline m - m)$ (recall $\sigma$ from Def.~\ref{sip}).
+then $\overline m \geq m$; and if $\overline m  (r-1) < mr$, the map $i \mapsto \cap_{S \in \sigma(i)} \pi(S)$ is an injective function to $[\overline m]$ from some $J \subseteq [m]$ of size $m - (r-1)(\overline m - m)$ (recall $\sigma$ from Def.~\ref{sip}).
 %In particular, if $\overline m = m$ then $\pi$ is induced by a permutation on $[m]$.
@@
 
-Applying Lem.~\ref{NonEmptyLemma}, the association $i \mapsto \cap \pi(\sigma(i))$ is an injective map $\overline \pi: J \to [\overline m]$ for some $J \subseteq [m]$ of size $m - (r-1)(\overline m - m)$, and $\mathbf{B}_{\overline \pi(i)} \neq \mathbf{0}$ for all $i \in J$ since the columns of $\mathbf{B}_{\pi(S)}$ are linearly independent for all $S \in \mathcal{H}$.
+Applying Lem.~\ref{NonEmptyLemma}, the association $i \mapsto \cap_{S \in \sigma(i)} \pi(S)$ is an injective map $\overline \pi: J \to [\overline m]$ for some $J \subseteq [m]$ of size $m - (r-1)(\overline m - m)$, and $\mathbf{B}_{\overline \pi(i)} \neq \mathbf{0}$ for all $i \in J$ since the columns of $\mathbf{B}_{\pi(S)}$ are linearly independent for all $S \in \mathcal{H}$.
 Letting $\overline \varepsilon := C_2 \varepsilon / \max_i \|\mathbf{A}_i\|_2$, it follows from \eqref{eqdim} and \eqref{last} that $d\left( \bm{\mathcal{A}}_i, \bm{\mathcal{B}}_{\overline \pi(i)} \right) = d\left(\bm{\mathcal{B}}_{\overline \pi(i)},  \bm{\mathcal{A}}_i \right)  \leq \overline \varepsilon$ for all $i \in J$.

### 2019-05-08 manuscripts/IEEE/submission/referee_responses.txt
responses done

@@
 
+-------------------------------------
+Response: Thanks for your comments.  As far as we understand, our work is the first to prove stability of unique representations in sparse coding under deterministic noise.
+-------------------------------------
+
 Other comments
-1. “then each submatrix formed from 2k of its columns or less has a strictly positive lower bound.” What is k here?
+1. "then each submatrix formed from 2k of its columns or less has a strictly positive lower bound." What is k here?
 
@@
 The first inequality follows from the fact that (m choose 2) is a subset of 2H, provided ∪H = [m], since only then can every pair of columns be captured by the union of two supports in H.
+We have updated the text to explain this.
 -------------------------------------
@@
 Fixing A and the x_i's fixes the numbers L_2k(A) and C_1(A,x_i).
-Theorem 1 then states that, provided \epsilon < L_2k/C_1, all such B's and \bar{x}_i's are close to A and the x_i's, respectively (see (6) and (7)).
-To rephrase via the triangle inequality, all good enough B’s and \bar{x}_i’s are similar to one another, or identical when \epsilon = 0.
+Theorem 1 then states that, provided \epsilon < L_2k/C_1, all such B's and \bar{x}_i's are close (up to labelling/scaling) to A and the x_i's, respectively (see (6) and (7)).
+To rephrase via the triangle inequality, all good enough B’s and \bar{x}_i’s are nearly equivalent to one another, or equivalent when \epsilon = 0.
 -------------------------------------
@@
 -------------------------------------
-Response: We have altered the notation to abate this potential confusion.
+Response: We have altered the notation to remove this potential confusion.
 -------------------------------------
@@
 6.
-“A practical implication of Thm.
+"A practical implication of Thm.
 1 is the following: there is an effective procedure sufficient to affirm if a proposed solution to Prob.
@@
 One need simply to check that the matrix and codes satisfy the (computable) assumptions of Thm.
-1 on A and the xi.” I question whether the assumptions of Theorem 1 are indeed computable.
+1 on A and the xi." I question whether the assumptions of Theorem 1 are indeed computable.
 Could the authors elaborate on that?
@@
 -------------------------------------
-Response: The assumptions of Theorem 1 are:
+Response: Thanks, we have updated the manuscript to make computability more clear.  The assumptions of Theorem 1 are:
 i) L_2H(A) > 0 for an r-regular H with the SIP.
@@
 
-"The pragmatic reader should note that the explicit constants C1 and C2 are effectively computable: the quantity Lk may be calculated as the smallest singular value of a certain matrix, while the quantity ξ involves computing “canonical angles” between subspaces, which reduce again to an efficient singular value decomposition.
+"The pragmatic reader should note that the explicit constants C1 and C2 are effectively computable: the quantity Lk may be calculated as the smallest singular value of a certain matrix, while the quantity \xi involves computing "canonical angles" between subspaces, which reduce again to an efficient singular value decomposition.
 There is no known fast computation of L in general, however, since even L > 0 is NP-hard [19]; although fixing k yields polynomial complexity.
-Moreover, calculating C2 requires an exponential number of queries to ξ unless r is held fixed, too (e.g., the “cyclic order” hypergraphs described above have r = k).
+Moreover, calculating C2 requires an exponential number of queries to \xi unless r is held fixed, too (e.g., the "cyclic order" hypergraphs described above have r = k).
 Thus, as presented, C1 and C2 are not efficiently computable."
@@
 7.
-I am not sure what “substitutions” means in Theorem 3.
-Does that mean “choices” of A and x1, .
+I am not sure what "substitutions" means in Theorem 3.
+Does that mean "choices" of A and x1, .
 .
@@
 -------------------------------------
-Response: "Substitution" here mean such assignments or choices of real numbers to the indeterminate variables, yes.
+Response: Here for us, "Substitution" means such assignments or choices of real numbers to the indeterminate variables (i.e., the map from a direct product of R's to the corresponding matrix and vector spaces).
 We frame it as a theorem and not a corollary because we draw the important Corollary 2 directly from it.
-We have no qualms downgrading Proposition 1 to an informal claim, however.
-
-[NOTE: should we just make everything a corollary of Thm 1..? Even Thm 2?]
+We have downgraded Proposition 1 to an informal claim in the revised discussion.
 -------------------------------------
@@
 The perturbation bound is used by the authors to provide some explanation for why, in practice, different methods lead to similar dictionaries.
-Can that also be used to explain the second (bold) part of their observation that “[these waveforms] appear in dictionaries learned by a variety of algorithms trained with respect to different natural image datasets.”?
+Can that also be used to explain the second (bold) part of their observation that "[these waveforms] appear in dictionaries learned by a variety of algorithms trained with respect to different natural image datasets."?
 Just curious.
@@
 -------------------------------------
-Response: To be clear, this (bold) observation is just an observation which motivates the work.
-Imagining natural image patches to form a population which satisfies (1) with respect to some ground truth dictionary A, we have shown that there exists a sufficient number of samples to uniquely identify it or something close to it via approximate solutions.
+Response: We are curious as well, and this observation is a main motivation for our work.
+Imagining that natural image patches form a population which satisfies (1) with respect to some ground truth dictionary A, we have shown that there exists a sufficient number of samples to uniquely identify it or something close to it via approximate solutions.
 Given this fundamental stability and uniqueness of the problem solutions, the fact that a variety of methods geared to approximately solve Problems 1 and 2 all seem to capture similar structure is much less surprising.
@@
 I personally think rephrasing some of the graph theoretic terms will make the paper easier to follow, but that might just be personal preference.
+
+-------------------------------------
+Response: Thanks for your comments.
+(1) Although computable, indeed, checking the conditions of assumptions in our theorems is often NP-hard as we explain in the manuscript; we have updated the revision for more clarity on this.
+(2) We also believe that this numerical optimization is NP-hard and include this question in the revised discussion; we also pose there whether the more tractable l1 norm version implies the same uniqueness results.
+-------------------------------------
 
@@
 Response: Theorem 2 guarantees that all globally optimal solutions to Problem 2 are identical up to noise and inherent permutation/scaling ambiguities.
-This doesn't change the fact that computing any one such global solution given data is still NP-hard.
+Unfortunately, this does not change the fact that computing any one such global solution given data can be NP-hard.
+-------------------------------------
 
@@
 
-We make no claims in this paper about l1-norm minimization, though we are hopeful a clever reader may find some way to build off our results and derive related guarantees for this continuous relaxation of the sparse coding problem.
+-------------------------------------
+Response: We make no claims in this paper about l1-norm minimization, though we are hopeful a clever reader may find some way to build off our results and derive related guarantees for this continuous relaxation of the sparse coding problem (we pose this problem in the discussion).
+-------------------------------------
 
@@
 
-Yes, we only claim that our general uniqueness criterion provide a (not necessarily efficient) means of checking the globality of a proposed solution.
+-------------------------------------
+Response: We only claim that our general uniqueness criteria provide a (not necessarily efficient) means of checking the globality of a proposed solution.
 It could be that in certain restricted cases these conditions are efficiently computable, but this is not the case in general.
@@
 "We close this section with comments on optimality.
-Our linear scaling for ε in (8) is essentially optimal (e.g., see [23]), but a basic open problem remains: how many samples are necessary to determine the sparse coding model?
+Our linear scaling for \epsilon in (8) is essentially optimal (e.g., see [23]), but a basic open problem remains: how many samples are necessary to determine the sparse coding model?
 If k is held fixed or if the size of the support set of reconstructing codes is known to be polynomial in m and k, then a practical (polynomial) amount of data suffices.
@@
 
-In general, our conditions are sufficient but not proven necessary, and we doubt we have achieved the tightest possible bounds all around.
+In general, our conditions are sufficient but not proven necessary, and we doubt we have achieved the tightest possible bounds all around (which we pose now in the revised discussion).
 
@@
 -------------------------------------
-Response: In the prose surrounding Corollary 1 we give a deterministic construction of sparse vectors x_i satisfying the constraints of Theorem 1.
-
-TODO : can we deterministically generate matrices injective on SIP hyper graphs? The (mCk)-hypergraph is one such possibility, so maybe not in general? But for special cases (convolution matrices..?)
+Response: In the prose surrounding Corollary 1, we give a deterministic construction of sparse vectors x_i satisfying the constraints of Theorem 1. 
 -------------------------------------

### 2019-05-08 manuscripts/IEEE/final_submission.tex
chaz edits

@@
 \begin{align*}
-	\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \varepsilon(\delta_1, \delta_2),\ \ \   \text{for all $i=1,\ldots,N$},
+	\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \varepsilon(\delta_1, \delta_2),\ \   \text{for all $i=1,\ldots,N$},
 \end{align*}
@@
 \begin{align}\label{def1}
-\|\mathbf{A}_j - (\mathbf{BPD})_j\|_2 \leq \delta_1 \ \ \text{and} \ \ \|\mathbf{x}_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_i\|_1 \leq \delta_2.
+\|\mathbf{A}_j - (\mathbf{BPD})_j\|_2 \leq \delta_1 \ \text{and} \ \|\mathbf{x}_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_i\|_1 \leq \delta_2.
 \end{align}
@@
 \includegraphics[width=.24 \linewidth]{figs/Ahat_FastICA_M640_K8_noise2_0409.png}
-\caption{\textbf{Noisy dictionary learning}.
-Recovery of the $8 \times 8$ discrete cosine transform (DCT) basis (the 64 columns of first matrix above) from $8$-sparse samples with linearly increasing noise (using the FastICA algorithm \cite{hyvarinen2000independent}).}
+\caption{\textbf{Learning a dictionary from increasingly noisy data}.
+The (unraveled) basis elements of the $8 \times 8$ discrete cosine transform (DCT) form the 64 columns of the left-most matrix above.
+Three increasingly imprecise dictionaries are recovered by the FastICA algorithm \cite{hyvarinen2000independent} from noisy data generated from $8$-sparse linear combinations of DCT elements and additive noise increasing in power from left to right.}
 \vspace{-.6 cm}
@@
 writing also $L_{k}$ in place of $L_\mathcal{H}$ when $\mathcal{H} = {[m] \choose k}$.\footnote{In compressed sensing literature, \mbox{$1 - \sqrt{k} L_k(\mathbf{M})$}  is the asymmetric lower restricted isometry constant for $\mathbf{M}$ with unit $\ell_2$-norm columns \cite{Blanchard2011}.}  As explained above, compactness implies that $L_{2k}(\mathbf{M}) > 0$ for all $\mathbf{M}$ satisfying \eqref{SparkCondition}.
-Clearly, $L_{\mathcal{H}'}(\mathbf{M}) \geq L_\mathcal{H}(\mathbf{M})$ whenever $\mathcal{H}' \subseteq \mathcal{H}$, and any $k$-uniform $\mathcal{H}$ satisfying $\cup \mathcal{H} = [m]$ has $L_2 \geq L_{2\mathcal{H}} \geq L_{2k}$.
+Clearly, $L_{\mathcal{H}'}(\mathbf{M}) \geq L_\mathcal{H}(\mathbf{M})$ whenever $\mathcal{H}' \subseteq \mathcal{H}$, and any $k$-uniform $\mathcal{H}$ satisfying $\cup \mathcal{H} = [m]$ has $L_2 \geq L_{2\mathcal{H}} \geq L_{2k}$ (letting $L_{2k}$ := $L_m$ whenever $2k > m$).
 
-We are now in a position to state our main result, though for expository purposes we leave the quantity $C_1$ (a function of $\mathbf{A}$, $\mathbf{x}_1, \ldots, \mathbf{x}_N$, and $\mathcal{H}$) undefined until Eqn.~\eqref{Cdef1} of Sec.~\ref{DUT}.
-All results  below assume real matrices and vectors.
+We are now in a position to state our main result, though for expository purposes we leave the quantity $C_1$ %(a function of $\mathbf{A}$, $\mathbf{x}_1, \ldots, \mathbf{x}_N$, and $\mathcal{H}$) 
+undefined until Eqn.~\eqref{Cdef1} of Sec.~\ref{DUT}. All results  below assume real matrices and vectors.
 
@@
 Suppose that the $n \times m$ matrix $\mathbf{A}$ satisfies $L_{2\mathcal{H}}(\mathbf{A}) > 0$ for some $r$-regular $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP from Def.~\ref{sip}.
-If $k$-sparse \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N$} include more than $(k-1){\overline m \choose k}$ vectors in general linear position\footnote{Recall that a set of vectors sharing support $S$ are in \emph{general linear position} when any $|S|$ of them are linearly independent.} supported in each $S \in \mathcal{H}$, then there is $C_1 > 0$ for which the following holds for all%\footnote{The condition $\varepsilon < L_2(\mathbf{A}) /C_1$ is necessary; otherwise,  with \mbox{$\mathbf{A}$ = $\mathbf{I}$} and $\mathbf{x}_i = \mathbf{e}_i$, there is a matrix $\mathbf{B}$ and $1$-sparse $\mathbf{\overline{x}}_i$ with $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline{x}}_i \|_2 \leq \varepsilon$ that nonetheless violates \eqref{Cstable}.} $\varepsilon < L_{2}(\mathbf{A}) / C_1$:
-\footnote{Note that the condition $\varepsilon < L_2(\mathbf{A}) /C_1$ is necessary; otherwise, with \mbox{$\mathbf{A}$ = $\mathbf{I}$} (the identity matrix) and $\mathbf{x}_i = \mathbf{e}_i$, the matrix $\mathbf{B} = \left[\mathbf{0}, \frac{1}{2}(\mathbf{e}_1 + \mathbf{e}_2), \mathbf{e}_3, \ldots, \mathbf{e}_{m} \right]$ and sparse codes $\mathbf{\overline x}_i = \mathbf{e}_2$ for $i = 1, 2$ and $\mathbf{\overline x}_i = \mathbf{e}_i$ for $i \geq 3$ satisfy $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline{x}}_i \|_2 \leq \varepsilon$ but nonetheless violate \eqref{Cstable}.} $\varepsilon < L_{2}(\mathbf{A}) / C_1$:
+If $k$-sparse \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N$} include more than $(k-1){\overline m \choose k}$ vectors in general linear position\footnote{Recall that a set of vectors sharing support $S$ are in \emph{general linear position} when any $|S|$ of them are linearly independent.} supported in each $S \in \mathcal{H}$, then there is positive $C_1 = C_1(\mathbf{A}, \mathcal{H}, \{\mathbf{x}_i\}_{i=1}^N)$ for which the following recovery guarantees hold for all%\footnote{The condition $\varepsilon < L_2(\mathbf{A}) /C_1$ is necessary; otherwise,  with \mbox{$\mathbf{A}$ = $\mathbf{I}$} and $\mathbf{x}_i = \mathbf{e}_i$, there is a matrix $\mathbf{B}$ and $1$-sparse $\mathbf{\overline{x}}_i$ with $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline{x}}_i \|_2 \leq \varepsilon$ that nonetheless violates \eqref{Cstable}.} $\varepsilon < L_{2}(\mathbf{A}) / C_1$:
+\footnote{Note that the condition $\varepsilon < L_2(\mathbf{A}) /C_1$ is necessary; otherwise, with \mbox{$\mathbf{A}$ = $\mathbf{I}$} (the identity matrix) and $\mathbf{x}_i = \mathbf{e}_i$, the matrix $\mathbf{B} = \left[\mathbf{0}, \frac{1}{2}(\mathbf{e}_1 + \mathbf{e}_2), \mathbf{e}_3, \ldots, \mathbf{e}_{m} \right]$ and sparse codes $\mathbf{\overline x}_i = \mathbf{e}_2$ for $i = 1, 2$ and $\mathbf{\overline x}_i = \mathbf{e}_i$ for $i \geq 3$ satisfy $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline{x}}_i \|_2 \leq \varepsilon$ but nonetheless violate \eqref{Cstable}.} $\varepsilon < L_{2}(\mathbf{A}) / C_1$.
 
-Every $n \times \overline m$ matrix $\mathbf{B}$ for which there are $k$-sparse $\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N$ satisfying \mbox{$\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \varepsilon$} for all $i \in [N]$ has $\overline m \geq m$, and provided $\overline m (r-1) < mr$, there is a permutation matrix $\mathbf{P}$ and an invertible diagonal matrix $\mathbf{D}$ such that:
+\textbf{Dictionary Recovery:} Every $n \times \overline m$ matrix $\mathbf{B}$ for which there are $k$-sparse $\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N$ satisfying \mbox{$\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \varepsilon$} for all $i \in [N]$ has $\overline m \geq m$, and provided $\overline m (r-1) < mr$, there is a permutation matrix $\mathbf{P}$ and an invertible diagonal matrix $\mathbf{D}$ such that:
 \begin{align}\label{Cstable}
@@
 
-Moreover, if $\mathbf{A}_J$ satisfies \eqref{SparkCondition} and $\varepsilon < L_{2k}(\mathbf{A}_J) / C_1$, then $(\mathbf{BPD})_J$ also satisfies \eqref{SparkCondition} with $L_{2k}((\mathbf{B}\mathbf{PD})_J) \geq L_{2k}(\mathbf{A}_J) - C_1 \varepsilon$, and for all $i \in [N]$:
+\textbf{Code Recovery:} If $\mathbf{A}_J$ satisfies \eqref{SparkCondition} and $\varepsilon < L_{2k}(\mathbf{A}_J) / C_1$ then $\mathbf{BP}_J$ also satisfies \eqref{SparkCondition} with $L_{2k}(\mathbf{BPD}_J) \geq L_{2k}(\mathbf{A}_J) - C_1 \varepsilon$, and for all $i \in [N]$:
 \begin{align}\label{b-PDa}
@@
 %
-where $(\mathbf{x}_i)_J$ represents the subvector formed from restricting to coordinates indexed by $J$. 
+where subscript $(\cdot)_J$ here represents the subvector formed from restricting to coordinates indexed by $J$.
 \end{theorem}
@@
 \begin{corollary}\label{DeterministicUniquenessCorollary}
-Given any regular hypergraph $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP, there are $N =  |\mathcal{H}| \left[ (k-1){m \choose k} + 1  \right]$ vectors \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} such that every matrix $\mathbf{A}$ with satisfying \eqref{SparkCondition} generates a dataset $Y = \{\mathbf{A}\mathbf{x}_1, \ldots, \mathbf{A}\mathbf{x}_N\}$ with a stable $k$-sparse representation in $\mathbb{R}^m$ for $\varepsilon(\delta_1,\delta_2)$ given by \eqref{epsdel}.
+Given any regular hypergraph $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP, there are $N =  |\mathcal{H}| \left[ (k-1){m \choose k} + 1  \right]$ vectors \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} such that every matrix $\mathbf{A}$ satisfying \eqref{SparkCondition} generates $Y = \{\mathbf{A}\mathbf{x}_1, \ldots, \mathbf{A}\mathbf{x}_N\}$ with a stable $k$-sparse representation in $\mathbb{R}^m$ for $\varepsilon(\delta_1,\delta_2)$ given by \eqref{epsdel}.
 \end{corollary}
@@
 
-We begin our proof of Thm.~\ref{DeterministicUniquenessTheorem} by showing how dictionary recovery \eqref{Cstable} already implies sparse code recovery \eqref{b-PDa} when $\mathbf{A}_J$ satisfies \eqref{SparkCondition} and \mbox{$\varepsilon < L_{2k}(\mathbf{A}_J) / C_1$}.
+% WITH EXPLICIT J SUBSCRIPT
+%We begin our proof of Thm.~\ref{DeterministicUniquenessTheorem} by showing how dictionary recovery \eqref{Cstable} already implies sparse code recovery \eqref{b-PDa} when $\mathbf{A}_J$ satisfies \eqref{SparkCondition} and \mbox{$\varepsilon < L_{2k}(\mathbf{A}_J) / C_1$}.
 %, assuming that $\overline m = m$ without loss of generality.
+%Consider any $2k$-sparse $\mathbf{x} \in \mathbb{R}^m$ and note that $\|\mathbf{x}\|_1 \leq \sqrt{2k}  \|\mathbf{x}\|_2$. By definition of $L_{2k}$ in \eqref{Ldef}, we have:
+%\begin{align}\label{stuff}
+%\|\mathbf{x}_J - &( \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x} )_J\|_1 \nonumber
+%\leq \frac{\|(\mathbf{BPD})_J(\mathbf{x}_J - (\mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x})_J)\|_2}{L_{2k}((\mathbf{BPD})_J)} \\ \nonumber
+%&\leq \frac{\|( (\mathbf{BPD})_J - \mathbf{A}_J) \mathbf{x}_J\|_2 + \|\mathbf{A}_J\mathbf{x}_J - \mathbf{B}_J\mathbf{\overline x}_J\|_2}{L_{2k}((\mathbf{BPD})_J)} \\
+%&\leq \frac{C_1\varepsilon \|\mathbf{x}_J\|_1 + \varepsilon}{L_{2k}((\mathbf{BPD})_J)},
+%\end{align}
+%where the term $C_1\varepsilon \|\mathbf{x}_J\|_1$ in the numerator above is a consequence of the triangle inequality applied to \eqref{Cstable}.
+
+%It remains for us to bound the denominator.  By the reverse triangle inequality:
+%\begin{align*}
+%\|(\mathbf{BPD})_J\mathbf{x}_J\|_2 
+%&\geq | \|\mathbf{A}_J\mathbf{x}_J\|_2 - \|(\mathbf{A}_J - (\mathbf{BPD})_J)\mathbf{x}_J\|_2 | \\
+%&\geq \sqrt{2k} (L_{2k}(\mathbf{A}_J) -  C_1\varepsilon) \|\mathbf{x}_J\|_2,
+%\end{align*}
+%
+%wherein removal of the absolute value is justified since $C_1\varepsilon < L_{2k}(\mathbf{A}_J)$.
+We therefore have that $L_{2k}((\mathbf{BPD})_J) \geq L_{2k}(\mathbf{A}_J) - C_1\varepsilon  > 0$, and \eqref{b-PDa} then follows from \eqref{stuff}.
+
+% WITHOUT J SUBSCRIPT
+We begin our proof of Thm.~\ref{DeterministicUniquenessTheorem} by showing how dictionary recovery \eqref{Cstable} already implies sparse code recovery \eqref{b-PDa} when $\mathbf{A}$ satisfies \eqref{SparkCondition} and \mbox{$\varepsilon < L_{2k}\mathbf{A} / C_1$}, assuming that $\overline m = m$ (without loss of generality) so as to omit an otherwise requisite subscript $(\cdot)_J$ around certain matrices and vectors.
 Consider any $2k$-sparse $\mathbf{x} \in \mathbb{R}^m$ and note that $\|\mathbf{x}\|_1 \leq \sqrt{2k}  \|\mathbf{x}\|_2$. By definition of $L_{2k}$ in \eqref{Ldef}, we have:
 \begin{align}\label{stuff}
-\|\mathbf{x}_J - &( \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x} )_J\|_1 \nonumber
-\leq \frac{\|(\mathbf{BPD})_J(\mathbf{x}_J - (\mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x})_J)\|_2}{L_{2k}((\mathbf{BPD})_J)} \\ \nonumber
-&\leq \frac{\|( (\mathbf{BPD})_J - \mathbf{A}_J) \mathbf{x}_J\|_2 + \|\mathbf{A}_J\mathbf{x}_J - \mathbf{B}_J\mathbf{\overline x}_J\|_2}{L_{2k}((\mathbf{BPD})_J)} \\
-&\leq \frac{C_1\varepsilon \|\mathbf{x}_J\|_1 + \varepsilon}{L_{2k}((\mathbf{BPD})_J)},
+\|\mathbf{x} - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x} \|_1 \nonumber
+&\leq \frac{\|\mathbf{BPD}(\mathbf{x}_J - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x})\|_2}{L_{2k}(\mathbf{BPD})} \\ \nonumber
+&\leq \frac{\|( \mathbf{BPD} - \mathbf{A}) \mathbf{x}\|_2 + \|\mathbf{A}\mathbf{x} - \mathbf{B}\mathbf{\overline x}\|_2}{L_{2k}(\mathbf{BPD})} \\
+&\leq \frac{C_1\varepsilon \|\mathbf{x}\|_1 + \varepsilon}{L_{2k}(\mathbf{BPD})},
 \end{align}
@@
 \begin{align*}
-\|(\mathbf{BPD})_J\mathbf{x}_J\|_2 
-&\geq | \|\mathbf{A}_J\mathbf{x}_J\|_2 - \|(\mathbf{A}_J - (\mathbf{BPD})_J)\mathbf{x}_J\|_2 | \\
-&\geq \sqrt{2k} (L_{2k}(\mathbf{A}_J) -  C_1\varepsilon) \|\mathbf{x}_J\|_2,
+\|\mathbf{BPD}\mathbf{x}\|_2 
+&\geq | \|\mathbf{A}\mathbf{x}\|_2 - \|(\mathbf{A} - \mathbf{BPD})\mathbf{x}\|_2 | \\
+&\geq \sqrt{2k} (L_{2k}(\mathbf{A}) -  C_1\varepsilon) \|\mathbf{x}\|_2,
 \end{align*}
 %
-wherein removal of the absolute value is justified since $C_1\varepsilon < L_{2k}(\mathbf{A}_J)$.
-We therefore have that $L_{2k}((\mathbf{BPD})_J) \geq L_{2k}(\mathbf{A}_J) - C_1\varepsilon  > 0$, and \eqref{b-PDa} then follows from \eqref{stuff}.
+wherein removal of the absolute value is justified since $C_1\varepsilon < L_{2k}(\mathbf{A})$.
+We therefore have that $L_{2k}(\mathbf{BPD}) \geq L_{2k}(\mathbf{A}) - C_1\varepsilon  > 0$, and \eqref{b-PDa} then follows from \eqref{stuff}.
 

### 2019-05-08 manuscripts/IEEE/final_submission.tex
chaz edits

@@
 writing also $L_{k}$ in place of $L_\mathcal{H}$ when $\mathcal{H} = {[m] \choose k}$.\footnote{In compressed sensing literature, \mbox{$1 - \sqrt{k} L_k(\mathbf{M})$}  is the asymmetric lower restricted isometry constant for $\mathbf{M}$ with unit $\ell_2$-norm columns \cite{Blanchard2011}.}  As explained above, compactness implies that $L_{2k}(\mathbf{M}) > 0$ for all $\mathbf{M}$ satisfying \eqref{SparkCondition}.
-Clearly, $L_{\mathcal{H}'}(\mathbf{M}) \geq L_\mathcal{H}(\mathbf{M})$ whenever $\mathcal{H}' \subseteq \mathcal{H}$, and any $k$-uniform $\mathcal{H}$ satisfying $\cup \mathcal{H} = [m]$ has $L_2 \geq L_{2\mathcal{H}} \geq L_{2k}$ (letting $L_{2k}$ := $L_m$ whenever $2k > m$).
+Clearly, $L_{\mathcal{H}'}(\mathbf{M}) \geq L_\mathcal{H}(\mathbf{M})$ whenever $\mathcal{H}' \subseteq \mathcal{H}$, and similarly any $k$-uniform $\mathcal{H}$ satisfying $\cup \mathcal{H} = [m]$ has $L_2 \geq L_{2\mathcal{H}} \geq L_{2k}$ (letting $L_{2k}$ := $L_m$ whenever $2k > m$).
 
 We are now in a position to state our main result, though for expository purposes we leave the quantity $C_1$ %(a function of $\mathbf{A}$, $\mathbf{x}_1, \ldots, \mathbf{x}_N$, and $\mathcal{H}$) 
-undefined until Eqn.~\eqref{Cdef1} of Sec.~\ref{DUT}. All results  below assume real matrices and vectors.
+undefined until Sec.~\ref{DUT}. All results  below assume real matrices and vectors.
 
@@
 Suppose that the $n \times m$ matrix $\mathbf{A}$ satisfies $L_{2\mathcal{H}}(\mathbf{A}) > 0$ for some $r$-regular $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP from Def.~\ref{sip}.
-If $k$-sparse \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N$} include more than $(k-1){\overline m \choose k}$ vectors in general linear position\footnote{Recall that a set of vectors sharing support $S$ are in \emph{general linear position} when any $|S|$ of them are linearly independent.} supported in each $S \in \mathcal{H}$, then there is positive $C_1 = C_1(\mathbf{A}, \mathcal{H}, \{\mathbf{x}_i\}_{i=1}^N)$ for which the following recovery guarantees hold for all%\footnote{The condition $\varepsilon < L_2(\mathbf{A}) /C_1$ is necessary; otherwise,  with \mbox{$\mathbf{A}$ = $\mathbf{I}$} and $\mathbf{x}_i = \mathbf{e}_i$, there is a matrix $\mathbf{B}$ and $1$-sparse $\mathbf{\overline{x}}_i$ with $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline{x}}_i \|_2 \leq \varepsilon$ that nonetheless violates \eqref{Cstable}.} $\varepsilon < L_{2}(\mathbf{A}) / C_1$:
+If $k$-sparse \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N$} include more than $(k-1){\overline m \choose k}$ vectors in general linear position\footnote{Recall that a set of vectors sharing support $S$ are in \emph{general linear position} when any $|S|$ of them are linearly independent.} supported in each $S \in \mathcal{H}$, then there is a positive $C_1$ (given by \eqref{Cdef1}) for which the following recovery guarantees hold for all%\footnote{The condition $\varepsilon < L_2(\mathbf{A}) /C_1$ is necessary; otherwise,  with \mbox{$\mathbf{A}$ = $\mathbf{I}$} and $\mathbf{x}_i = \mathbf{e}_i$, there is a matrix $\mathbf{B}$ and $1$-sparse $\mathbf{\overline{x}}_i$ with $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline{x}}_i \|_2 \leq \varepsilon$ that nonetheless violates \eqref{Cstable}.} $\varepsilon < L_{2}(\mathbf{A}) / C_1$:
 \footnote{Note that the condition $\varepsilon < L_2(\mathbf{A}) /C_1$ is necessary; otherwise, with \mbox{$\mathbf{A}$ = $\mathbf{I}$} (the identity matrix) and $\mathbf{x}_i = \mathbf{e}_i$, the matrix $\mathbf{B} = \left[\mathbf{0}, \frac{1}{2}(\mathbf{e}_1 + \mathbf{e}_2), \mathbf{e}_3, \ldots, \mathbf{e}_{m} \right]$ and sparse codes $\mathbf{\overline x}_i = \mathbf{e}_2$ for $i = 1, 2$ and $\mathbf{\overline x}_i = \mathbf{e}_i$ for $i \geq 3$ satisfy $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline{x}}_i \|_2 \leq \varepsilon$ but nonetheless violate \eqref{Cstable}.} $\varepsilon < L_{2}(\mathbf{A}) / C_1$.
@@
 
-\textbf{Code Recovery:} If $\mathbf{A}_J$ satisfies \eqref{SparkCondition} and $\varepsilon < L_{2k}(\mathbf{A}_J) / C_1$ then $\mathbf{BP}_J$ also satisfies \eqref{SparkCondition} with $L_{2k}(\mathbf{BPD}_J) \geq L_{2k}(\mathbf{A}_J) - C_1 \varepsilon$, and for all $i \in [N]$:
+\textbf{Code Recovery:} If $\mathbf{A}_J$ satisfies \eqref{SparkCondition} and $\varepsilon < L_{2k}(\mathbf{A}_J) / C_1$ then $(\mathbf{BP})_J$ also satisfies \eqref{SparkCondition} with $L_{2k}(\mathbf{BPD}_J) \geq L_{2k}(\mathbf{A}_J) - C_1 \varepsilon$, and for all $i \in [N]$:
 \begin{align}\label{b-PDa}
@@
 \|\mathbf{x} - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x} \|_1 \nonumber
-&\leq \frac{\|\mathbf{BPD}(\mathbf{x}_J - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x})\|_2}{L_{2k}(\mathbf{BPD})} \\ \nonumber
+&\leq \frac{\|\mathbf{BPD}(\mathbf{x} - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x})\|_2}{L_{2k}(\mathbf{BPD})} \\ \nonumber
 &\leq \frac{\|( \mathbf{BPD} - \mathbf{A}) \mathbf{x}\|_2 + \|\mathbf{A}\mathbf{x} - \mathbf{B}\mathbf{\overline x}\|_2}{L_{2k}(\mathbf{BPD})} \\
@@
 \end{align}
-where the term $C_1\varepsilon \|\mathbf{x}_J\|_1$ in the numerator above is a consequence of the triangle inequality applied to \eqref{Cstable}.
+where the term $C_1\varepsilon \|\mathbf{x}\|_1$ in the numerator above is a consequence of the triangle inequality applied to \eqref{Cstable}.
 
-It remains for us to bound the denominator.  By the reverse triangle inequality:
+It remains for us to bound the denominator.  By the triangle inequality:
 \begin{align*}
 \|\mathbf{BPD}\mathbf{x}\|_2 
-&\geq | \|\mathbf{A}\mathbf{x}\|_2 - \|(\mathbf{A} - \mathbf{BPD})\mathbf{x}\|_2 | \\
+&\geq \|\mathbf{A}\mathbf{x}\|_2 - \|(\mathbf{A} - \mathbf{BPD})\mathbf{x}\|_2 \\
 &\geq \sqrt{2k} (L_{2k}(\mathbf{A}) -  C_1\varepsilon) \|\mathbf{x}\|_2,
@@
 %
-wherein removal of the absolute value is justified since $C_1\varepsilon < L_{2k}(\mathbf{A})$.
 We therefore have that $L_{2k}(\mathbf{BPD}) \geq L_{2k}(\mathbf{A}) - C_1\varepsilon  > 0$, and \eqref{b-PDa} then follows from \eqref{stuff}.

### 2019-05-08 manuscripts/IEEE/final_submission.tex
minor edits

@@
 The (unraveled) basis elements of the $8 \times 8$ discrete cosine transform (DCT) form the 64 columns of the left-most matrix above.
-Three increasingly imprecise dictionaries are recovered by the FastICA algorithm \cite{hyvarinen2000independent} from noisy data generated from $8$-sparse linear combinations of DCT elements and additive noise increasing in power from left to right.}
+Three increasingly imprecise dictionaries are recovered by the FastICA algorithm \cite{hyvarinen2000independent} with data generated from $8$-sparse linear combinations of DCT elements corrupted with additive noise increasing in intensity from left to right.}
 \vspace{-.6 cm}
@@
 
-Another extension of Thm.~\ref{DeterministicUniquenessTheorem} can be derived from the following analytic characterization of the spark condition.
+Another extension of Thm.~\ref{DeterministicUniquenessTheorem} can be derived from the following algebraic characterization of the spark condition.
 Letting $\mathbf{A}$ be the $n \times m$ matrix of $nm$ indeterminates $A_{ij}$, the reader may work out why substituting real numbers for the $A_{ij}$ yields a matrix satisfying \eqref{SparkCondition} if and only if the following polynomial evaluates to a nonzero number:
@@
 \begin{corollary}\label{ProbabilisticCor}
-If the indeterminate entries of $\mathbf{A}$ and the $\mathbf{x}_i$ are drawn independently from probability measures absolutely continuous with respect to the standard Borel measure, then $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$ with probability one.
+If indeterminate entries of $\mathbf{A}$ and $\mathbf{x}_i$ are drawn independently from probability distributions absolutely continuous with respect to the standard Borel measure, then $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$ with probability one.
 \end{corollary}
@@
 contradicting our assumed upper bound on $\varepsilon$. Hence, the map $\pi$ is injective and so $\overline m \geq m$. %Setting $\overline J = \pi([m])$ and
-Letting $\mathbf{P}$ and $\mathbf{D}$ be the $\overline m \times \overline m$ permutation and invertible diagonal matrices with, respectively, columns $\mathbf{e}_{\pi(j)}$ and $\frac{\overline{c}_j}{c_j}\mathbf{e}_j$ for $j \in [m]$ (and, say, $\mathbf{e}_j$ otherwise), we may rewrite \eqref{1D} to see that for all $j \in [m]$:
+
+Letting $\mathbf{P}$ and $\mathbf{D}$ be the $\overline m \times \overline m$ permutation and invertible diagonal matrices with, respectively, columns $\mathbf{e}_{\pi(j)}$ and $\frac{\overline{c}_j}{c_j}\mathbf{e}_j$ for $j \in [m]$ (otherwise, $\mathbf{e}_{j}$ for $j \in [\overline{m}] \setminus [m]$), we may rewrite \eqref{1D} to see that for all $j \in [m]$:
 \begin{align*}
@@
 
-An extension of the proof to the general case $k < m$ requires that we introduce some additional tools to derive the general expression \eqref{Cdef1} for the constant $C_1$.
+An extension of the proof to the general case $k < m$ requires some additional tools to derive the general expression \eqref{Cdef1} for $C_1$.
 These include a generalized notion of distance (Def.~\ref{dDef}) and angle (Def.~\ref{FriedrichsDefinition}) between subspaces as well as a stability result in combinatorial matrix analysis (Lem.~\ref{MainLemma}).
@@
 \begin{align}\label{GapUpperBound}
-d(\bm{\mathcal{A}}_S, \bm{\mathcal{B}}_{\pi(S)}) \leq \varepsilon \ \  \text{for $S \in \mathcal{H}$},
+d(\bm{\mathcal{A}}_S, \bm{\mathcal{B}}_{\pi(S)}) \leq \varepsilon, \ \  \text{for $S \in \mathcal{H}$},
 \end{align}
@@
 
-The practically-minded reader should note that the explicit constants $C_1$ and $C_2$ are effectively computable: the quantity $L_k$ may be calculated as the smallest singular value of a certain matrix, while the quantity $\xi$ involves computing ``canonical angles'' between subspaces, which reduce again to an efficient singular value decomposition.
+The practically-minded reader should note that the explicit constants $C_1$ and $C_2$ are effectively computable: the quantity $L_k$ may be calculated as the smallest singular value of a certain matrix, while the quantity $\xi$ involves computing ``canonical angles'' between subspaces, which reduces again to an efficient singular value decomposition.
 There is no known fast computation of $L_k$ in general, however, since even $L_{k} > 0$ is NP-hard \cite{tillmann2014computational}, although
@@
 
-We close with some remaining open questions.
+We close with some remaining open challenges.
 First, there is the basic problem of proving optimal lower bounds on sufficient sample size for uniqueness and stability in sparse coding.
@@
 But this is exactly the supposition in \eqref{1D}, with $J$ and $\overline \varepsilon$ in place of $[m]$ and $\varepsilon$, respectively.
-The same arguments of the case $k=1$ in Sec.~\ref{DUT} can then be made to show that for any $\overline m \times \overline m$ permutation and invertible diagonal matrices $\mathbf{P}$ and $\mathbf{D}$ with, respectively, columns $\mathbf{e}_{\pi(i)}$ and $\frac{\overline{c}_i}{c_i}\mathbf{e}_i$ for $i \in J$ (and, say, $\mathbf{e}_i$ otherwise) we have $\|\mathbf{A}_i - (\mathbf{B}\mathbf{PD})_i \|_2 \leq \overline  \varepsilon / |c_i|  \leq C_2 \varepsilon$ for all $i \in J$.
+The same arguments of the case $k=1$ in Sec.~\ref{DUT} can then be made to show that for any $\overline m \times \overline m$ permutation and invertible diagonal matrices $\mathbf{P}$ and $\mathbf{D}$ with, respectively, columns $\mathbf{e}_{\pi(i)}$ and $\frac{\overline{c}_i}{c_i}\mathbf{e}_i$ for $i \in J$ (otherwise, $\mathbf{e}_{i}$ for $i \in [\overline{m}] \setminus J$) we have $\|\mathbf{A}_i - (\mathbf{B}\mathbf{PD})_i \|_2 \leq \overline  \varepsilon / |c_i|  \leq C_2 \varepsilon$ for all $i \in J$.
 \end{proof}

### 2019-05-09 manuscripts/IEEE/final_submission.tex
minor

@@
 The main result of this work is a very general uniqueness theorem for sparse coding (Thm.~\ref{DeterministicUniquenessTheorem}) directly 
-implying (Cor.~\ref{DeterministicUniquenessCorollary}) that stable representations of a dataset $Z$ are guaranteed whenever generating dictionaries $\mathbf{A}$ satisfy a spark condition on supports and the original sparse codes $\mathbf{x}_i$ are sufficiently diverse.
-Moreover, we provide an explicit, computable $\varepsilon(\delta_1, \delta_2)$ in (\ref{epsdel}) that is essentially linear in desired accuracy $\delta_1, \delta_2$.
+implying (Cor.~\ref{DeterministicUniquenessCorollary}) that stable representations of a dataset $Z$ are guaranteed whenever generating dictionaries $\mathbf{A}$ satisfy a spark condition on supports and the original sparse codes $\mathbf{x}_i$ are sufficiently diverse (e.g., Fig.~\ref{noisyrecovery}).
+Moreover, we provide an explicit, computable $\varepsilon(\delta_1, \delta_2)$ in (\ref{epsdel}) that is linear in desired accuracy $\delta_1, \delta_2$.
 
@@
 In words, Thm.~\ref{DeterministicUniquenessTheorem} says that the smaller the regularity $r$ of original support hypergraph $\mathcal{H}$ or the difference $\overline m - m$ between assumed and actual number of elements in the latent dictionary, the more columns and coefficients of the original dictionary $\mathbf{A}$ and sparse codes $\mathbf{x}_i$ are guaranteed to be contained (up to noise) in the appropriately labelled and scaled recovered dictionary $\mathbf{B}$ and codes $\mathbf{\overline x}_i$, respectively.
-In the important special case when $\overline m = m$, the theorem directly implies (e.g., Fig.~\ref{noisyrecovery}) that  $Y = \{\mathbf{Ax}_1, \ldots, \mathbf{Ax}_N\}$ has a stable $k$-sparse representation in $\mathbb{R}^m$, with inequalities \eqref{def1} guaranteed in Def.~\ref{maindef} for the following worst-case error $\varepsilon$:
+In the important special case when $\overline m = m$, the theorem directly implies that  $Y = \{\mathbf{Ax}_1, \ldots, \mathbf{Ax}_N\}$ has a stable $k$-sparse representation in $\mathbb{R}^m$, with inequalities \eqref{def1} guaranteed in Def.~\ref{maindef} for the following worst-case error $\varepsilon$:
 \begin{align}\label{epsdel}
@@
 It is only a matter of time before these systems incorporate dictionary learning to encode and decode signals (e.g., in a device that learns structure from motion \cite{kong2016prior}), just as scientists have used sparse coding to make sense of their data \cite{jung2001imaging, agarwal2014spatially, lee2016sparse, wu2016stability}.
-
-Assurances such as those offered by our theorems certify that different devices and algorithms will learn equivalent representations given enough data from statistically identical systems.\footnote{To contrast with the current hot topic of ``Deep Learning'', there are few such uniqueness guarantees for these models of data; moreover, even small noise can dramatically alter their output \cite{goodfellow2014explaining}.} Indeed, a main reason for the sustained interest in dictionary learning as an unsupervised method for data analysis seems to be the assumed well-posedness of parameter identification in the sparse coding model, confirmation of which forms the core of our theoretical findings.
+Assurances offered by our theorems certify that different devices and algorithms will learn equivalent representations given enough data from statistically identical systems.\footnote{To contrast with the current hot topic of ``Deep Learning'', there are few such uniqueness guarantees for these models of data; moreover, even small noise can dramatically alter their output \cite{goodfellow2014explaining}.} Indeed, a main reason for the sustained interest in dictionary learning as an unsupervised method for data analysis seems to be the assumed well-posedness of parameter identification in the model, confirmation of which forms the core of our findings.
 
@@
 In what special cases is it efficient to check that a solution to the problems is optimal?
+[*** Incorporate this open problem with more words ***]
 
@@
 
-\section{EXTRA}
-An additional consequence of Thm.~\ref{DeterministicUniquenessTheorem} of potential practical relevance to is the implied lower bound $L_{2k}(\mathbf{BPD}) \geq L_{2k}(\mathbf{A}) - C_1\varepsilon$ in the case where $\mathbf{A}$ satisfies \eqref{SparkCondition}.
+%\section{EXTRA}
+%An additional consequence of Thm.~\ref{DeterministicUniquenessTheorem} of potential practical relevance to is the implied lower bound $L_{2k}(\mathbf{BPD}) \geq L_{2k}(\mathbf{A}) - C_1\varepsilon$ in the case where $\mathbf{A}$ satisfies \eqref{SparkCondition}.
 Since solving Prob.~\ref{SLCopt} directly requires a combinatorial search over sparse supports for the $\mathbf{\overline x}_i$ for each proposed dictionary $\mathbf{B}$, rendering it intractable in general, a common strategy is to replace the $\ell_0$-norm in \eqref{minsum} with the $\ell_1$-norm, thereby transforming the inference of sparse $\mathbf{\overline x}_i$ for a fixed dictionary $\mathbf{B}$ into a convex optimization solvable by a linear program.
@@
 It remains to determine, however, what practical conditions preclude matrices that don't solve Prob.~\ref{OptimizationProblem} from nonetheless solving the convexified problem.
-
-Regardless, an implication of the above observation is that the following algorithm solves Prob.~\ref{OptimizationProblem} without appeal to combinatorial search:
-\begin{enumerate}
-\item List all matrices $\mathbf{B}$.
-\item For each matrix $\mathbf{B}$, solve $\mathbf{\overline x}_i = \arg \min \|\mathbf{v}\|_1$ s.t. $\|\mathbf{Bv} - \mathbf{z}_i\| \leq \eta$ for $i = 1, \ldots, N$.
-\item Quantify the proposed solution $\mathbf{B}$ and $\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N$ as $\rho(\mathbf{B}, \mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N) = \sum_{i=1}^{N} \|\mathbf{\overline x}_i\|_0$.
-\item Output $\arg \min_{\mathbf{B}, \mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N} \left( \rho \right)$.
- \end{enumerate}
+%
+%Regardless, an implication of the above observation is that the following algorithm solves Prob.~\ref{OptimizationProblem} without appeal to combinatorial search:
+%\begin{enumerate}
+%\item List all matrices $\mathbf{B}$.
+%\item For each matrix $\mathbf{B}$, solve $\mathbf{\overline x}_i = \arg \min \|\mathbf{v}\|_1$ s.t. $\|\mathbf{Bv} - \mathbf{z}_i\| \leq \eta$ for $i = 1, \ldots, N$.
+%\item Quantify the proposed solution $\mathbf{B}$ and $\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N$ as $\rho(\mathbf{B}, \mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N) = \sum_{i=1}^{N} \|\mathbf{\overline x}_i\|_0$.
+%\item Output $\arg \min_{\mathbf{B}, \mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N} \left( \rho \right)$.
+% \end{enumerate}
 

### 2019-05-09 manuscripts/IEEE/final_submission.tex
my changes
complete manu draft

@@
 Additionally, given the NP-hardness of verifying the spark condition for matrices, is approximating a solution to Prob.~\ref{InverseProblem} or \ref{OptimizationProblem} also computationally hard?
-Finally, as $\ell_1$ relaxations for inferring sparse vectors have, in many cases, the same solutions as for $\ell_0$, is there an $\ell_1$ version of Thm.~\ref{SLCopt}?
+Finally, as $\ell_1$ relaxations for inferring sparse vectors have, in many cases \cite{eldar2012compressed}, the same solutions as for $\ell_0$, is there an $\ell_1$ version of Thm.~\ref{SLCopt}?
 In what special cases is it efficient to check that a solution to the problems is optimal?
-[*** Incorporate this open problem with more words ***]
+% [*** Incorporate this open problem with more words ***]
 

### 2019-05-09 manuscripts/IEEE/final_submission.tex
ref and fig caption update

@@
 The (unraveled) basis elements of the $8 \times 8$ discrete cosine transform (DCT) form the 64 columns of the left-most matrix above.
-Three increasingly imprecise dictionaries are recovered by the FastICA algorithm \cite{hyvarinen2000independent} with data generated from $8$-sparse linear combinations of DCT elements corrupted with additive noise increasing in intensity from left to right.}
+Three increasingly imprecise dictionaries (columns relabelled to best match original) are recovered by FastICA \cite{hyvarinen2000independent} with data generated from $8$-sparse linear combinations of DCT elements corrupted with additive noise increasing from left to right.}
 \vspace{-.6 cm}

### 2019-05-09 manuscripts/IEEE/final_submission.tex
no D

--- 2019-05-09 manuscripts/IEEE/final_submission.tex
@@
 Consider any $2k$-sparse $\mathbf{x} \in \mathbb{R}^m$ and note that $\|\mathbf{x}\|_1 \leq \sqrt{2k}  \|\mathbf{x}\|_2$. By definition of $L_{2k}$ in \eqref{Ldef}, we have:
+%\begin{align}\label{stuff}
+%\|\mathbf{x} - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x} \|_1 \nonumber
+%&\leq \frac{\|\mathbf{BPD}(\mathbf{x} - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x})\|_2}{L_{2k}(\mathbf{BPD})} \\ \nonumber
+%&\leq \frac{\|( \mathbf{BPD} - \mathbf{A}) \mathbf{x}\|_2 + \|\mathbf{A}\mathbf{x} - \mathbf{B}\mathbf{\overline x}\|_2}{L_{2k}(\mathbf{BPD})} \\
+%&\leq \frac{C_1\varepsilon \|\mathbf{x}\|_1 + \varepsilon}{L_{2k}(\mathbf{BPD})},
+%\end{align}
+
 \begin{align}\label{stuff}
-\|\mathbf{x} - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x} \|_1 \nonumber
-&\leq \frac{\|\mathbf{BPD}(\mathbf{x} - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x})\|_2}{L_{2k}(\mathbf{BPD})} \\ \nonumber
-&\leq \frac{\|( \mathbf{BPD} - \mathbf{A}) \mathbf{x}\|_2 + \|\mathbf{A}\mathbf{x} - \mathbf{B}\mathbf{\overline x}\|_2}{L_{2k}(\mathbf{BPD})} \\
-&\leq \frac{C_1\varepsilon \|\mathbf{x}\|_1 + \varepsilon}{L_{2k}(\mathbf{BPD})},
+\frac{ \|\mathbf{x} - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x} \|_1 } { \|\mathbf{D}^{-1}\|_1 }  \
+&\leq \|\mathbf{Dx} - \mathbf{P}^{\top}\mathbf{\overline x} \|_1 \\ \nonumber
+&\leq \frac{\|\mathbf{BP}(\mathbf{D}\mathbf{x} - \mathbf{P}^{\top}\mathbf{\overline x})\|_2}{L_{2k}(\mathbf{BP})} \\ \nonumber
+&\leq \frac{\|( \mathbf{BPD} - \mathbf{A}) \mathbf{x}\|_2 + \|\mathbf{A}\mathbf{x} - \mathbf{B}\mathbf{\overline x}\|_2}{L_{2k}(\mathbf{BP})} \\
+&\leq \frac{C_1\varepsilon \|\mathbf{x}\|_1 + \varepsilon}{L_{2k}(\mathbf{BP})},
 \end{align}
-where the term $C_1\varepsilon \|\mathbf{x}\|_1$ in the numerator above is a consequence of the triangle inequality applied to \eqref{Cstable}.
+where the term $C_1\varepsilon \|\mathbf{x}\|_1$ in the numerator above follows from the triangle inequality and \eqref{Cstable}.
 
 It remains for us to bound the denominator.  By the triangle inequality:
+%\begin{align*}
+%\|\mathbf{BPD}\mathbf{x}\|_2 
+%&\geq \|\mathbf{A}\mathbf{x}\|_2 - \|(\mathbf{A} - \mathbf{BPD})\mathbf{x}\|_2 \\
+%&\geq \sqrt{2k} (L_{2k}(\mathbf{A}) -  C_1\varepsilon) \|\mathbf{x}\|_2,
+%\end{align*}
+
 \begin{align*}
-\|\mathbf{BPD}\mathbf{x}\|_2 
-&\geq \|\mathbf{A}\mathbf{x}\|_2 - \|(\mathbf{A} - \mathbf{BPD})\mathbf{x}\|_2 \\
-&\geq \sqrt{2k} (L_{2k}(\mathbf{A}) -  C_1\varepsilon) \|\mathbf{x}\|_2,
+\|\mathbf{BP}\mathbf{x}\|_2 
+&\geq \|\mathbf{A}\mathbf{D}^{-1}\mathbf{x}\|_2 - \|(\mathbf{A} - \mathbf{BPD})\mathbf{D}^{-1}\mathbf{x}\|_2 \\
+&\geq \sqrt{2k} (L_{2k}(\mathbf{A}) -  C_1\varepsilon) \|\mathbf{D}^{-1}\mathbf{x}\|_2, \\ 
+&\geq \sqrt{2k} (L_{2k}(\mathbf{A}) -  C_1\varepsilon) \|\mathbf{D}^{-1}\|_{?} \| \mathbf{x}\|_2,
 \end{align*}

### 2019-05-09 manuscripts/IEEE/final_submission.tex
fig move

@@
 
-\begin{figure}[t!]
-\begin{center}
-\includegraphics[width=.24 \linewidth]{figs/basis.png}
-% \includegraphics[width=.25 \linewidth]{figs/Ahat_FastICA_M640_K8_noise0_2042}
-\includegraphics[width=.24 \linewidth]{figs/Ahat_FastICA_M640_K8_noise0_4083.png}
-\includegraphics[width=.24 \linewidth]{figs/Ahat_FastICA_M640_K8_noise1_0205.png}
-\includegraphics[width=.24 \linewidth]{figs/Ahat_FastICA_M640_K8_noise2_0409.png}
-\caption{\textbf{Learning a dictionary from increasingly noisy data}.
-The (unraveled) basis elements of the $8 \times 8$ discrete cosine transform (DCT) form the 64 columns of the left-most matrix above.
-Three increasingly imprecise dictionaries (columns relabelled to best match original) are recovered by FastICA \cite{hyvarinen2000independent} with data generated from $8$-sparse linear combinations of DCT elements corrupted with additive noise increasing from left to right.}
-\vspace{-.6 cm}
-\label{noisyrecovery}
-\end{center}
-\end{figure}
-
 We next give a quantitative generalization of the spark condition (\ref{SparkCondition}) to combinatorial subsets of supports.
@@
 \end{theorem}
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=.24 \linewidth]{figs/basis.png}
+% \includegraphics[width=.25 \linewidth]{figs/Ahat_FastICA_M640_K8_noise0_2042}
+\includegraphics[width=.24 \linewidth]{figs/Ahat_FastICA_M640_K8_noise0_4083.png}
+\includegraphics[width=.24 \linewidth]{figs/Ahat_FastICA_M640_K8_noise1_0205.png}
+\includegraphics[width=.24 \linewidth]{figs/Ahat_FastICA_M640_K8_noise2_0409.png}
+\caption{\textbf{Learning a dictionary from increasingly noisy data}.
+The (unraveled) basis elements of the $8 \times 8$ discrete cosine transform (DCT) form the 64 columns of the left-most matrix above.
+Three increasingly imprecise dictionaries (columns relabelled to best match original) are recovered by FastICA \cite{hyvarinen2000independent} trained on data generated from $8$-sparse linear combinations of DCT elements corrupted with additive noise (increasing from left to right).}
+\vspace{-.6 cm}
+\label{noisyrecovery}
+\end{center}
+\end{figure}
 
@@
 First, there is the basic problem of proving optimal lower bounds on sufficient sample size for uniqueness and stability in sparse coding.
-Additionally, given the NP-hardness of verifying the spark condition for matrices, is approximating a solution to Prob.~\ref{InverseProblem} or \ref{OptimizationProblem} also computationally hard?
+Additionally, given the NP-hardness of verifying the spark condition for matrices, are the corresponding approximation Probs.~\ref{InverseProblem} and \ref{OptimizationProblem} also computationally hard?
+In what special cases is it efficient to check that a solution is stably unique for these problems?
 Finally, as $\ell_1$ relaxations for inferring sparse vectors have, in many cases \cite{eldar2012compressed}, the same solutions as for $\ell_0$, is there an $\ell_1$ version of Thm.~\ref{SLCopt}?
-In what special cases is it efficient to check that a solution to the problems is optimal?
 % [*** Incorporate this open problem with more words ***]

### 2019-05-09 manuscripts/IEEE/final_submission.tex
minor edits first half

@@
 Optimizing dictionaries subject to this and related sparsity constraints has revealed seemingly characteristic sparse structure in several signal classes of current interest (e.g., in vision \cite{wang2015sparse}).
+
 Of particular note are the seminal works in the field \cite{Olshausen96, hurri1996image, bell1997independent, van1998independent}, which discovered that dictionaries optimized for coding small patches of ``natural" images share qualitative similarities with linear filters estimated from response properties of simple-cell neurons in mammalian visual cortex.
@@
 
-Motivated by these discoveries and more recent work relating ``compressed sensing" to a theory of information transmission through random wiring bottlenecks in the brain \cite{Isely10}, we address when optimal dictionaries for sparse representation are indeed identifiable from data.
+Motivated by these discoveries and more recent work relating compressed sensing \cite{eldar2012compressed} to a theory of information transmission through random wiring bottlenecks in the brain \cite{Isely10}, we address when optimal dictionaries for sparse representation are indeed identifiable from data.
 Answers to this question may also have implications in practice wherever an appeal is made to latent sparse structure of data (e.g., forgery detection \cite{hughes2010, olshausen2010applied}; brain recordings \cite{jung2001imaging, agarwal2014spatially, lee2016sparse}; and gene expression \cite{wu2016stability}).
-While several algorithms have recently been proposed that provably recover unique dictionaries under specific conditions (see \cite[Sec.~I-E]{Sun16} for a summary of the state-of-the-art), few theorems can be invoked to justify the consistency of inference under this model of data more broadly.
-To our knowledge, a universal guarantee of the uniqueness and stability of learned dictionaries and the sparse representations they induce when data is noisy has yet to appear in the literature.
+
+While several algorithms have been recently proposed to provably recover unique dictionaries under specific conditions (see \cite[Sec.~I-E]{Sun16} for a summary of the state-of-the-art), few theorems can be invoked to justify the consistency of inference under this model of data more broadly.
+To our knowledge, a universal guarantee of the uniqueness and stability of learned dictionaries and the sparse representations they induce when data has deterministic noise has yet to appear in the literature.
 % in justifying the identification of forged paintings by their anomalous sparse representations \cite{hughes2010},
@@
 More specifically,  we show that dictionaries injective on a sparse domain are identifiable from \mbox{$N = m(k-1){m \choose k} + m$} noisy sparse linear combinations of their columns up to an error that is linear in the noise (Thm.~\ref{DeterministicUniquenessTheorem}).
-In fact, provided $n \geq \min(2k,m)$, in almost all cases the problem is well-posed (as per Hadamard \cite{Hadamard1902}) given enough data (Cor.~\ref{ProbabilisticCor}).
-These guarantees also hold for a related (and perhaps more commonly posed) optimization problem which seeks a dictionary minimizing the average number of elementary waveforms required to reconstruct each sample of the dataset (Thm.~\ref{SLCopt}).
-Importantly, our explicit, universal guarantees apply without the imposition of \emph{any} constraints on learned dictionaries  (e.g.
-that they, too, be injective over some domain) beyond an upper bound on dictionary size, which is necessary to avoid trivial solutions (e.g., allowing for $m = N$ elementary waveforms).
+In fact, provided $n \geq \min(2k,m)$, in almost all cases the problem is well-posed, as per Hadamard \cite{Hadamard1902}, given a sufficient amount of data (Thm.~\ref{robustPolythm} and Cor.~\ref{ProbabilisticCor}).
+
+Our guarantees also hold for a related (and perhaps more commonly posed) optimization problem that seeks a dictionary minimizing the average number of elementary waveforms required to reconstruct each sample of the dataset (Thm.~\ref{SLCopt}).
+Importantly, we never make assumptions on learned dictionaries (e.g., that they, too, be injective over some domain) beyond an upper bound on dictionary size, which is necessary to avoid trivial solutions (e.g., allowing for $m = N$ waveforms).
 %That is, every pair of solutions of comparable size has some number of dictionary elements in common (up to noise), and similarly so for the coefficients of sparse codes they induce.
@@
 
-In the next section, we give precise statements of these findings.
+In the next section, we give formal statements of these findings.
 We then extend the same guarantees (Thm.~\ref{SLCopt}) to the following alternate formulation of dictionary learning, which minimizes the total number of nonzero entries in sparse codes.
@@
 We also give brief arguments adapting our results to dictionaries and codes drawn from probability distributions (Cor.~\ref{ProbabilisticCor}).
-We defer to Sec.~\ref{DUT} the technical proofs of Thms.~\ref{DeterministicUniquenessTheorem} and ~\ref{SLCopt}, following some necessary definitions and a useful fact in combinatorial matrix analysis (Lem.~\ref{MainLemma}; proved in the Appendix).
+The technical proofs of Thms.~\ref{DeterministicUniquenessTheorem} and ~\ref{SLCopt} are deferred to Sec.~\ref{DUT}, following some necessary definitions and a fact in combinatorial matrix analysis (Lem.~\ref{MainLemma}; proved in the Appendix).
 Finally, we discuss in Sec.~\ref{Discussion} applications of our mathematical observations as well as open questions.
@@
 We also write $2\mathcal{H} := \{ S \cup S': S, S' \in \mathcal{H}\}$.
-The following class of structured hypergraphs are a key ingredient in this work.
+The following class of structured hypergraphs is a key ingredient in this work.
 
@@
 In words, Thm.~\ref{DeterministicUniquenessTheorem} says that the smaller the regularity $r$ of original support hypergraph $\mathcal{H}$ or the difference $\overline m - m$ between assumed and actual number of elements in the latent dictionary, the more columns and coefficients of the original dictionary $\mathbf{A}$ and sparse codes $\mathbf{x}_i$ are guaranteed to be contained (up to noise) in the appropriately labelled and scaled recovered dictionary $\mathbf{B}$ and codes $\mathbf{\overline x}_i$, respectively.
+
 In the important special case when $\overline m = m$, the theorem directly implies that  $Y = \{\mathbf{Ax}_1, \ldots, \mathbf{Ax}_N\}$ has a stable $k$-sparse representation in $\mathbb{R}^m$, with inequalities \eqref{def1} guaranteed in Def.~\ref{maindef} for the following worst-case error $\varepsilon$:
@@
 \begin{corollary}\label{DeterministicUniquenessCorollary}
-Given any regular hypergraph $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP, there are $N =  |\mathcal{H}| \left[ (k-1){m \choose k} + 1  \right]$ vectors \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} such that every matrix $\mathbf{A}$ satisfying \eqref{SparkCondition} generates $Y = \{\mathbf{A}\mathbf{x}_1, \ldots, \mathbf{A}\mathbf{x}_N\}$ with a stable $k$-sparse representation in $\mathbb{R}^m$ for $\varepsilon(\delta_1,\delta_2)$ given by \eqref{epsdel}.
+Given any regular hypergraph $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP, there are $N =  |\mathcal{H}| \left[ (k-1){m \choose k} + 1  \right]$ vectors \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} such that every matrix $\mathbf{A}$ satisfying spark condition \eqref{SparkCondition} generates $Y = \{\mathbf{A}\mathbf{x}_1, \ldots, \mathbf{A}\mathbf{x}_N\}$ with a stable $k$-sparse representation in $\mathbb{R}^m$ for $\varepsilon(\delta_1,\delta_2)$ given by \eqref{epsdel}.
 \end{corollary}
@@
 In this case, a direct consequence of Cor.~\ref{DeterministicUniquenessCorollary} is rigorous verification of the lower bound \mbox{$N = m(k-1){m \choose k} + m$} for sufficient sample size from the introduction.
-Special cases allow for even smaller hypergraphs, however.
+Special cases allow for even smaller hypergraphs.
 For example, if $k = \sqrt{m}$, then a 2-regular $k$-uniform hypergraph with the SIP can be constructed as the $2k$ rows and columns formed by arranging the elements of $[m]$ into a square grid.
@@
 %\cite{li2004analysis, Georgiev05, Aharon06, Hillar15}
-We should stress the point here that framing the problem in terms of hypergraphs has allowed us to show, unlike in previous works on the subject, that the matrix $\mathbf{A}$ need not necessarily satisfy \eqref{SparkCondition} to be recoverable from data.
+We should stress here that framing the problem in terms of hypergraphs has allowed us to show, unlike in previous research on the subject, that the matrix $\mathbf{A}$ need not necessarily satisfy \eqref{SparkCondition} to be recoverable from data.
 As an example, let $\mathbf{A} = [ \mathbf{e}_1, \ldots, \mathbf{e}_5, \mathbf{v}]$ with $\mathbf{v} = \mathbf{e}_1 + \mathbf{e}_3 + \mathbf{e}_5$ and take $\mathcal{H}$ to be all consecutive pairs of indices $1, \ldots ,6$ arranged in cyclic order.
@@
 Our results demonstrate that sparse codes $\mathbf{x}_i$ drawn from only a polynomial number of $k$-dimensional subspaces permit stable identification of the generating dictionary $\mathbf{A}$.
+
 This lends some legitimacy to the use of the model in practice, where data in general are unlikely (if ever) to exhibit the exponentially many possible $k$-wise combinations of dictionary elements required by (to our knowledge) all previously published results.

### 2019-05-09 manuscripts/IEEE/final_submission.tex
chaz edits

--- 2019-05-09 manuscripts/IEEE/final_submission.tex
@@
 \begin{theorem}\label{DeterministicUniquenessTheorem}
-Fix integers $n, k, m$ and $\overline m$.
-Suppose that the $n \times m$ matrix $\mathbf{A}$ satisfies $L_{2\mathcal{H}}(\mathbf{A}) > 0$ for some $r$-regular $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP from Def.~\ref{sip}.
-If $k$-sparse \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N$} include more than $(k-1){\overline m \choose k}$ vectors in general linear position\footnote{Recall that a set of vectors sharing support $S$ are in \emph{general linear position} when any $|S|$ of them are linearly independent.} supported in each $S \in \mathcal{H}$, then there is a positive $C_1$ (given by \eqref{Cdef1}) for which the following recovery guarantees hold for all%\footnote{The condition $\varepsilon < L_2(\mathbf{A}) /C_1$ is necessary; otherwise,  with \mbox{$\mathbf{A}$ = $\mathbf{I}$} and $\mathbf{x}_i = \mathbf{e}_i$, there is a matrix $\mathbf{B}$ and $1$-sparse $\mathbf{\overline{x}}_i$ with $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline{x}}_i \|_2 \leq \varepsilon$ that nonetheless violates \eqref{Cstable}.} $\varepsilon < L_{2}(\mathbf{A}) / C_1$:
-\footnote{Note that the condition $\varepsilon < L_2(\mathbf{A}) /C_1$ is necessary; otherwise, with \mbox{$\mathbf{A}$ = $\mathbf{I}$} (the identity matrix) and $\mathbf{x}_i = \mathbf{e}_i$, the matrix $\mathbf{B} = \left[\mathbf{0}, \frac{1}{2}(\mathbf{e}_1 + \mathbf{e}_2), \mathbf{e}_3, \ldots, \mathbf{e}_{m} \right]$ and sparse codes $\mathbf{\overline x}_i = \mathbf{e}_2$ for $i = 1, 2$ and $\mathbf{\overline x}_i = \mathbf{e}_i$ for $i \geq 3$ satisfy $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline{x}}_i \|_2 \leq \varepsilon$ but nonetheless violate \eqref{Cstable}.} $\varepsilon < L_{2}(\mathbf{A}) / C_1$.
+%Fix integers $n, k, m$ and $\overline m$. 
+If an $n \times m$ matrix $\mathbf{A}$ satisfies $L_{2\mathcal{H}}(\mathbf{A}) > 0$ for some $r$-regular $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP, and $k$-sparse \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} include more than $(k-1){\overline m \choose k}$ vectors in general linear position\footnote{Recall that a set of vectors sharing support $S$ are in \emph{general linear position} when any $|S|$ of them are linearly independent.} supported in each $S \in \mathcal{H}$, then the following recovery guarantees hold for $C_1 > 0$ given by \eqref{Cdef1}.
 
-\textbf{Dictionary Recovery:} Every $n \times \overline m$ matrix $\mathbf{B}$ for which there are $k$-sparse $\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N$ satisfying \mbox{$\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \varepsilon$} for all $i \in [N]$ has $\overline m \geq m$, and provided $\overline m (r-1) < mr$, there is a permutation matrix $\mathbf{P}$ and an invertible diagonal matrix $\mathbf{D}$ such that:
+\textbf{Dictionary Recovery:} Fix $\varepsilon < L_{2}(\mathbf{A}) / C_1$.\footnote{Note that the condition $\varepsilon < L_2(\mathbf{A}) /C_1$ is necessary; otherwise, with \mbox{$\mathbf{A}$ = $\mathbf{I}$} (the identity matrix) and $\mathbf{x}_i = \mathbf{e}_i$, the matrix $\mathbf{B} = \left[\mathbf{0}, \frac{1}{2}(\mathbf{e}_1 + \mathbf{e}_2), \mathbf{e}_3, \ldots, \mathbf{e}_{m} \right]$ and sparse codes $\mathbf{\overline x}_i = \mathbf{e}_2$ for $i = 1, 2$ and $\mathbf{\overline x}_i = \mathbf{e}_i$ for $i \geq 3$ satisfy $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline{x}}_i \|_2 \leq \varepsilon$ but nonetheless violate \eqref{Cstable}.} If an $n \times \overline m$ matrix $\mathbf{B}$ has for every $i \in [N]$ an associated $k$-sparse $\mathbf{\overline x}_i$ satisfying \mbox{$\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \varepsilon$}, then $\overline m \geq m$, and provided $\overline m (r-1) < mr$, there is a permutation matrix $\mathbf{P}$ and an invertible diagonal matrix $\mathbf{D}$ such that:
 \begin{align}\label{Cstable}
@@
 
-\textbf{Code Recovery:} If $\mathbf{A}_J$ satisfies \eqref{SparkCondition} and $\varepsilon < L_{2k}(\mathbf{A}_J) / C_1$ then $(\mathbf{BP})_J$ also satisfies \eqref{SparkCondition} with $L_{2k}(\mathbf{BPD}_J) \geq L_{2k}(\mathbf{A}_J) - C_1 \varepsilon$, and for all $i \in [N]$:
+\textbf{Code Recovery:} If, moreover, $\mathbf{A}_J$ satisfies \eqref{SparkCondition} and $\varepsilon < L_{2k}(\mathbf{A}_J) / C_1$, then $(\mathbf{BP})_J$ also satisfies \eqref{SparkCondition} with $L_{2k}(\mathbf{BP}_J) \geq (L_{2k}(\mathbf{A}_J) - C_1 \varepsilon) / \|\mathbf{D}_J\|_1$, and for all $i \in [N]$:
 \begin{align}\label{b-PDa}
@@
 
-Note that sparse codes in general linear position are straightforward to produce deterministically with a ``Vandermonde''  construction (i.e., by choosing columns of the matrix $[\gamma_{i}^j]_{i,j=1}^{k,N}$, for distinct nonzero $\gamma_i$).
-We therefore have the following direct consequence of Thm.~\ref{DeterministicUniquenessTheorem}.
+Since sparse codes in general linear position are straightforward to produce deterministically with a ``Vandermonde''  construction (i.e., by choosing columns of the matrix $[\gamma_{i}^j]_{i,j=1}^{k,N}$, for distinct nonzero $\gamma_i$), we have the following direct consequence of Thm.~\ref{DeterministicUniquenessTheorem}.
 
@@
 Consider any $2k$-sparse $\mathbf{x} \in \mathbb{R}^m$ and note that $\|\mathbf{x}\|_1 \leq \sqrt{2k}  \|\mathbf{x}\|_2$. By definition of $L_{2k}$ in \eqref{Ldef}, we have:
+\begin{align}\label{stuff}
+\|\mathbf{x} - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x} \|_1 \nonumber
+&\leq \frac{\|\mathbf{BPD}(\mathbf{x} - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x})\|_2}{L_{2k}(\mathbf{BPD})} \\ \nonumber
+&\leq \frac{\|( \mathbf{BPD} - \mathbf{A}) \mathbf{x}\|_2 + \|\mathbf{A}\mathbf{x} - \mathbf{B}\mathbf{\overline x}\|_2}{L_{2k}(\mathbf{BPD})} \\
+&\leq \frac{C_1\varepsilon \|\mathbf{x}\|_1 + \varepsilon}{L_{2k}(\mathbf{BPD})},
+\end{align}
 %\begin{align}\label{stuff}
-%\|\mathbf{x} - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x} \|_1 \nonumber
-%&\leq \frac{\|\mathbf{BPD}(\mathbf{x} - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x})\|_2}{L_{2k}(\mathbf{BPD})} \\ \nonumber
-%&\leq \frac{\|( \mathbf{BPD} - \mathbf{A}) \mathbf{x}\|_2 + \|\mathbf{A}\mathbf{x} - \mathbf{B}\mathbf{\overline x}\|_2}{L_{2k}(\mathbf{BPD})} \\
-%&\leq \frac{C_1\varepsilon \|\mathbf{x}\|_1 + \varepsilon}{L_{2k}(\mathbf{BPD})},
+%\frac{ \|\mathbf{x} - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x} \|_1 } { \|\mathbf{D}^{-1}\|_1 }  \
+%&\leq \|\mathbf{Dx} - \mathbf{P}^{\top}\mathbf{\overline x} \|_1 \\ \nonumber
+%&\leq \frac{\|\mathbf{BP}(\mathbf{D}\mathbf{x} - \mathbf{P}^{\top}\mathbf{\overline x})\|_2}{L_{2k}(\mathbf{BP})} \\ \nonumber
+%&\leq \frac{\|( \mathbf{BPD} - \mathbf{A}) \mathbf{x}\|_2 + \|\mathbf{A}\mathbf{x} - \mathbf{B}\mathbf{\overline x}\|_2}{L_{2k}(\mathbf{BP})} \\
+%&\leq \frac{C_1\varepsilon \|\mathbf{x}\|_1 + \varepsilon}{L_{2k}(\mathbf{BP})},
 %\end{align}
-
-\begin{align}\label{stuff}
-\frac{ \|\mathbf{x} - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x} \|_1 } { \|\mathbf{D}^{-1}\|_1 }  \
-&\leq \|\mathbf{Dx} - \mathbf{P}^{\top}\mathbf{\overline x} \|_1 \\ \nonumber
-&\leq \frac{\|\mathbf{BP}(\mathbf{D}\mathbf{x} - \mathbf{P}^{\top}\mathbf{\overline x})\|_2}{L_{2k}(\mathbf{BP})} \\ \nonumber
-&\leq \frac{\|( \mathbf{BPD} - \mathbf{A}) \mathbf{x}\|_2 + \|\mathbf{A}\mathbf{x} - \mathbf{B}\mathbf{\overline x}\|_2}{L_{2k}(\mathbf{BP})} \\
-&\leq \frac{C_1\varepsilon \|\mathbf{x}\|_1 + \varepsilon}{L_{2k}(\mathbf{BP})},
-\end{align}
 where the term $C_1\varepsilon \|\mathbf{x}\|_1$ in the numerator above follows from the triangle inequality and \eqref{Cstable}.
@@
 It remains for us to bound the denominator.  By the triangle inequality:
+\begin{align*}
+\|\mathbf{BPD}\mathbf{x}\|_2 
+&\geq \|\mathbf{A}\mathbf{x}\|_2 - \|(\mathbf{A} - \mathbf{BPD})\mathbf{x}\|_2 \\
+&\geq \sqrt{2k} (L_{2k}(\mathbf{A}) -  C_1\varepsilon) \|\mathbf{x}\|_2,
+\end{align*}
+
 %\begin{align*}
-%\|\mathbf{BPD}\mathbf{x}\|_2 
-%&\geq \|\mathbf{A}\mathbf{x}\|_2 - \|(\mathbf{A} - \mathbf{BPD})\mathbf{x}\|_2 \\
-%&\geq \sqrt{2k} (L_{2k}(\mathbf{A}) -  C_1\varepsilon) \|\mathbf{x}\|_2,
+%\|\mathbf{BP}\mathbf{x}\|_2 
+%&\geq \|\mathbf{A}\mathbf{D}^{-1}\mathbf{x}\|_2 - \|(\mathbf{A} - \mathbf{BPD})\mathbf{D}^{-1}\mathbf{x}\|_2 \\
+%&\geq \sqrt{2k} (L_{2k}(\mathbf{A}) -  C_1\varepsilon) \|\mathbf{D}^{-1}\mathbf{x}\|_2, \\ 
+%&\geq \sqrt{2k} (L_{2k}(\mathbf{A}) -  C_1\varepsilon) \|\mathbf{D}^{-1}\|_{?} \| \mathbf{x}\|_2,
 %\end{align*}
-
-\begin{align*}
-\|\mathbf{BP}\mathbf{x}\|_2 
-&\geq \|\mathbf{A}\mathbf{D}^{-1}\mathbf{x}\|_2 - \|(\mathbf{A} - \mathbf{BPD})\mathbf{D}^{-1}\mathbf{x}\|_2 \\
-&\geq \sqrt{2k} (L_{2k}(\mathbf{A}) -  C_1\varepsilon) \|\mathbf{D}^{-1}\mathbf{x}\|_2, \\ 
-&\geq \sqrt{2k} (L_{2k}(\mathbf{A}) -  C_1\varepsilon) \|\mathbf{D}^{-1}\|_{?} \| \mathbf{x}\|_2,
-\end{align*}
 %
 We therefore have that $L_{2k}(\mathbf{BPD}) \geq L_{2k}(\mathbf{A}) - C_1\varepsilon  > 0$, and \eqref{b-PDa} then follows from \eqref{stuff}.
+The reader may verify that $L_{2k}(\mathbf{BP}) \geq L_{2k}(\mathbf{BPD}) / \|\mathbf{D}\|_1$.
 

### 2019-05-09 manuscripts/IEEE/final_submission.tex

@@
 \end{definition}
-
-\begin{figure}[t!]
-\begin{center}
-\includegraphics[width=.24 \linewidth]{figs/basis.png}
-% \includegraphics[width=.25 \linewidth]{figs/Ahat_FastICA_M640_K8_noise0_2042}
-\includegraphics[width=.24 \linewidth]{figs/Ahat_FastICA_M640_K8_noise0_4083.png}
-\includegraphics[width=.24 \linewidth]{figs/Ahat_FastICA_M640_K8_noise1_0205.png}
-\includegraphics[width=.24 \linewidth]{figs/Ahat_FastICA_M640_K8_noise2_0409.png}
-\caption{\textbf{Learning a dictionary from increasingly noisy data}.
-The (unraveled) basis elements of the $8 \times 8$ discrete cosine transform (DCT) form the 64 columns of the left-most matrix above.
-Three increasingly imprecise dictionaries (columns relabelled to best match original) are recovered by FastICA \cite{hyvarinen2000independent} with data generated from $8$-sparse linear combinations of DCT elements corrupted with additive noise increasing from left to right.}
-\vspace{-.6 cm}
-\label{noisyrecovery}
-\end{center}
-\end{figure}
 

### 2019-05-09 manuscripts/IEEE/final_submission.tex
thm 1 changes

@@
 
-\textbf{Dictionary Recovery:} Fix $\varepsilon < L_{2}(\mathbf{A}) / C_1$.\footnote{Note that the condition $\varepsilon < L_2(\mathbf{A}) /C_1$ is necessary; otherwise, with \mbox{$\mathbf{A}$ = $\mathbf{I}$} (the identity matrix) and $\mathbf{x}_i = \mathbf{e}_i$, the matrix $\mathbf{B} = \left[\mathbf{0}, \frac{1}{2}(\mathbf{e}_1 + \mathbf{e}_2), \mathbf{e}_3, \ldots, \mathbf{e}_{m} \right]$ and sparse codes $\mathbf{\overline x}_i = \mathbf{e}_2$ for $i = 1, 2$ and $\mathbf{\overline x}_i = \mathbf{e}_i$ for $i \geq 3$ satisfy $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline{x}}_i \|_2 \leq \varepsilon$ but nonetheless violate \eqref{Cstable}.} If an $n \times \overline m$ matrix $\mathbf{B}$ has for every $i \in [N]$ an associated $k$-sparse $\mathbf{\overline x}_i$ satisfying \mbox{$\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \varepsilon$}, then $\overline m \geq m$, and provided $\overline m (r-1) < mr$, there is a permutation matrix $\mathbf{P}$ and an invertible diagonal matrix $\mathbf{D}$ such that:
+\textbf{Dictionary Recovery:} Fix $\varepsilon < L_{2}(\mathbf{A}) / C_1$.\footnote{Note that the condition $\varepsilon < L_2(\mathbf{A}) /C_1$ is necessary; otherwise, with \mbox{$\mathbf{A}$ = $\mathbf{I}$} (the identity matrix) and $\mathbf{x}_i = \mathbf{e}_i$, the matrix $\mathbf{B} = \left[\mathbf{0}, \frac{1}{2}(\mathbf{e}_1 + \mathbf{e}_2), \mathbf{e}_3, \ldots, \mathbf{e}_{m} \right]$ and sparse codes $\mathbf{\overline x}_i = \mathbf{e}_2$ for $i = 1, 2$ and $\mathbf{\overline x}_i = \mathbf{e}_i$ for $i \geq 3$ satisfy $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline{x}}_i \|_2 \leq \varepsilon$ but nonetheless violate \eqref{Cstable}.} The only $n \times \overline m$ matrices $\mathbf{B}$ that have, for every $i \in [N]$, an associated $k$-sparse $\mathbf{\overline x}_i$ satisfying \mbox{$\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \varepsilon$} have $\overline m \geq m$, and provided that $\overline m (r-1) < mr$, there is a permutation matrix $\mathbf{P}$ and an invertible diagonal matrix $\mathbf{D}$ such that:
 \begin{align}\label{Cstable}

### 2019-05-09 manuscripts/IEEE/final_submission.tex
tiny edits

--- 2019-05-09 manuscripts/IEEE/final_submission.tex
@@
 \begin{theorem}\label{DeterministicUniquenessTheorem}
-%Fix integers $n, k, m$ and $\overline m$. 
-If an $n \times m$ matrix $\mathbf{A}$ satisfies $L_{2\mathcal{H}}(\mathbf{A}) > 0$ for some $r$-regular $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP, and $k$-sparse \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} include more than $(k-1){\overline m \choose k}$ vectors in general linear position\footnote{Recall that a set of vectors sharing support $S$ are in \emph{general linear position} when any $|S|$ of them are linearly independent.} supported in each $S \in \mathcal{H}$, then the following recovery guarantees hold for $C_1 > 0$ given by \eqref{Cdef1}.
+Fix integers $n, k, m$ and $\overline m$.
+Suppose that the $n \times m$ matrix $\mathbf{A}$ satisfies $L_{2\mathcal{H}}(\mathbf{A}) > 0$ for some $r$-regular $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP from Def.~\ref{sip}.
+If $k$-sparse \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N$} include more than $(k-1){\overline m \choose k}$ vectors in general linear position\footnote{Recall that a set of vectors sharing support $S$ are in \emph{general linear position} when any $|S|$ of them are linearly independent.} supported in each $S \in \mathcal{H}$, then there is a positive $C_1$ (given by \eqref{Cdef1}) for which the following recovery guarantees hold for all%\footnote{The condition $\varepsilon < L_2(\mathbf{A}) /C_1$ is necessary; otherwise,  with \mbox{$\mathbf{A}$ = $\mathbf{I}$} and $\mathbf{x}_i = \mathbf{e}_i$, there is a matrix $\mathbf{B}$ and $1$-sparse $\mathbf{\overline{x}}_i$ with $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline{x}}_i \|_2 \leq \varepsilon$ that nonetheless violates \eqref{Cstable}.} $\varepsilon < L_{2}(\mathbf{A}) / C_1$:
+\footnote{Note that the condition $\varepsilon < L_2(\mathbf{A}) /C_1$ is necessary; otherwise, with \mbox{$\mathbf{A}$ = $\mathbf{I}$} (the identity matrix) and $\mathbf{x}_i = \mathbf{e}_i$, the matrix $\mathbf{B} = \left[\mathbf{0}, \frac{1}{2}(\mathbf{e}_1 + \mathbf{e}_2), \mathbf{e}_3, \ldots, \mathbf{e}_{m} \right]$ and sparse codes $\mathbf{\overline x}_i = \mathbf{e}_2$ for $i = 1, 2$ and $\mathbf{\overline x}_i = \mathbf{e}_i$ for $i \geq 3$ satisfy $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline{x}}_i \|_2 \leq \varepsilon$ but nonetheless violate \eqref{Cstable}.} $\varepsilon < L_{2}(\mathbf{A}) / C_1$.
 
-\textbf{Dictionary Recovery:} Fix $\varepsilon < L_{2}(\mathbf{A}) / C_1$.\footnote{Note that the condition $\varepsilon < L_2(\mathbf{A}) /C_1$ is necessary; otherwise, with \mbox{$\mathbf{A}$ = $\mathbf{I}$} (the identity matrix) and $\mathbf{x}_i = \mathbf{e}_i$, the matrix $\mathbf{B} = \left[\mathbf{0}, \frac{1}{2}(\mathbf{e}_1 + \mathbf{e}_2), \mathbf{e}_3, \ldots, \mathbf{e}_{m} \right]$ and sparse codes $\mathbf{\overline x}_i = \mathbf{e}_2$ for $i = 1, 2$ and $\mathbf{\overline x}_i = \mathbf{e}_i$ for $i \geq 3$ satisfy $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline{x}}_i \|_2 \leq \varepsilon$ but nonetheless violate \eqref{Cstable}.} If an $n \times \overline m$ matrix $\mathbf{B}$ has for every $i \in [N]$ an associated $k$-sparse $\mathbf{\overline x}_i$ satisfying \mbox{$\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \varepsilon$}, then $\overline m \geq m$, and provided $\overline m (r-1) < mr$, there is a permutation matrix $\mathbf{P}$ and an invertible diagonal matrix $\mathbf{D}$ such that:
+\textbf{Dictionary Recovery:} Every $n \times \overline m$ matrix $\mathbf{B}$ for which there are $k$-sparse $\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N$ satisfying \mbox{$\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \varepsilon$} for all $i \in [N]$ has $\overline m \geq m$, and provided $\overline m (r-1) < mr$, there is a permutation matrix $\mathbf{P}$ and an invertible diagonal matrix $\mathbf{D}$ such that:
 \begin{align}\label{Cstable}
@@
 
-\textbf{Code Recovery:} If, moreover, $\mathbf{A}_J$ satisfies \eqref{SparkCondition} and $\varepsilon < L_{2k}(\mathbf{A}_J) / C_1$, then $(\mathbf{BP})_J$ also satisfies \eqref{SparkCondition} with $L_{2k}(\mathbf{BP}_J) \geq (L_{2k}(\mathbf{A}_J) - C_1 \varepsilon) / \|\mathbf{D}_J\|_1$, and for all $i \in [N]$:
+\textbf{Code Recovery:} If $\mathbf{A}_J$ satisfies \eqref{SparkCondition} and $\varepsilon < L_{2k}(\mathbf{A}_J) / C_1$ then $(\mathbf{BP})_J$ also satisfies \eqref{SparkCondition} with $L_{2k}(\mathbf{BPD}_J) \geq L_{2k}(\mathbf{A}_J) - C_1 \varepsilon$, and for all $i \in [N]$:
 \begin{align}\label{b-PDa}
@@
 
-Since sparse codes in general linear position are straightforward to produce deterministically with a ``Vandermonde''  construction (i.e., by choosing columns of the matrix $[\gamma_{i}^j]_{i,j=1}^{k,N}$, for distinct nonzero $\gamma_i$), we have the following direct consequence of Thm.~\ref{DeterministicUniquenessTheorem}.
+Note that sparse codes in general linear position are straightforward to produce deterministically with a ``Vandermonde''  construction (i.e., by choosing columns of the matrix $[\gamma_{i}^j]_{i,j=1}^{k,N}$, for distinct nonzero $\gamma_i$).
+We therefore have the following direct consequence of Thm.~\ref{DeterministicUniquenessTheorem}.
 
@@
 Consider any $2k$-sparse $\mathbf{x} \in \mathbb{R}^m$ and note that $\|\mathbf{x}\|_1 \leq \sqrt{2k}  \|\mathbf{x}\|_2$. By definition of $L_{2k}$ in \eqref{Ldef}, we have:
+%\begin{align}\label{stuff}
+%\|\mathbf{x} - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x} \|_1 \nonumber
+%&\leq \frac{\|\mathbf{BPD}(\mathbf{x} - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x})\|_2}{L_{2k}(\mathbf{BPD})} \\ \nonumber
+%&\leq \frac{\|( \mathbf{BPD} - \mathbf{A}) \mathbf{x}\|_2 + \|\mathbf{A}\mathbf{x} - \mathbf{B}\mathbf{\overline x}\|_2}{L_{2k}(\mathbf{BPD})} \\
+%&\leq \frac{C_1\varepsilon \|\mathbf{x}\|_1 + \varepsilon}{L_{2k}(\mathbf{BPD})},
+%\end{align}
+
 \begin{align}\label{stuff}
-\|\mathbf{x} - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x} \|_1 \nonumber
-&\leq \frac{\|\mathbf{BPD}(\mathbf{x} - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x})\|_2}{L_{2k}(\mathbf{BPD})} \\ \nonumber
-&\leq \frac{\|( \mathbf{BPD} - \mathbf{A}) \mathbf{x}\|_2 + \|\mathbf{A}\mathbf{x} - \mathbf{B}\mathbf{\overline x}\|_2}{L_{2k}(\mathbf{BPD})} \\
-&\leq \frac{C_1\varepsilon \|\mathbf{x}\|_1 + \varepsilon}{L_{2k}(\mathbf{BPD})},
+\frac{ \|\mathbf{x} - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x} \|_1 } { \|\mathbf{D}^{-1}\|_1 }  \
+&\leq \|\mathbf{Dx} - \mathbf{P}^{\top}\mathbf{\overline x} \|_1 \\ \nonumber
+&\leq \frac{\|\mathbf{BP}(\mathbf{D}\mathbf{x} - \mathbf{P}^{\top}\mathbf{\overline x})\|_2}{L_{2k}(\mathbf{BP})} \\ \nonumber
+&\leq \frac{\|( \mathbf{BPD} - \mathbf{A}) \mathbf{x}\|_2 + \|\mathbf{A}\mathbf{x} - \mathbf{B}\mathbf{\overline x}\|_2}{L_{2k}(\mathbf{BP})} \\
+&\leq \frac{C_1\varepsilon \|\mathbf{x}\|_1 + \varepsilon}{L_{2k}(\mathbf{BP})},
 \end{align}
-%\begin{align}\label{stuff}
-%\frac{ \|\mathbf{x} - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x} \|_1 } { \|\mathbf{D}^{-1}\|_1 }  \
-%&\leq \|\mathbf{Dx} - \mathbf{P}^{\top}\mathbf{\overline x} \|_1 \\ \nonumber
-%&\leq \frac{\|\mathbf{BP}(\mathbf{D}\mathbf{x} - \mathbf{P}^{\top}\mathbf{\overline x})\|_2}{L_{2k}(\mathbf{BP})} \\ \nonumber
-%&\leq \frac{\|( \mathbf{BPD} - \mathbf{A}) \mathbf{x}\|_2 + \|\mathbf{A}\mathbf{x} - \mathbf{B}\mathbf{\overline x}\|_2}{L_{2k}(\mathbf{BP})} \\
-%&\leq \frac{C_1\varepsilon \|\mathbf{x}\|_1 + \varepsilon}{L_{2k}(\mathbf{BP})},
-%\end{align}
 where the term $C_1\varepsilon \|\mathbf{x}\|_1$ in the numerator above follows from the triangle inequality and \eqref{Cstable}.
@@
 It remains for us to bound the denominator.  By the triangle inequality:
+%\begin{align*}
+%\|\mathbf{BPD}\mathbf{x}\|_2 
+%&\geq \|\mathbf{A}\mathbf{x}\|_2 - \|(\mathbf{A} - \mathbf{BPD})\mathbf{x}\|_2 \\
+%&\geq \sqrt{2k} (L_{2k}(\mathbf{A}) -  C_1\varepsilon) \|\mathbf{x}\|_2,
+%\end{align*}
+
 \begin{align*}
-\|\mathbf{BPD}\mathbf{x}\|_2 
-&\geq \|\mathbf{A}\mathbf{x}\|_2 - \|(\mathbf{A} - \mathbf{BPD})\mathbf{x}\|_2 \\
-&\geq \sqrt{2k} (L_{2k}(\mathbf{A}) -  C_1\varepsilon) \|\mathbf{x}\|_2,
+\|\mathbf{BP}\mathbf{x}\|_2 
+&\geq \|\mathbf{A}\mathbf{D}^{-1}\mathbf{x}\|_2 - \|(\mathbf{A} - \mathbf{BPD})\mathbf{D}^{-1}\mathbf{x}\|_2 \\
+&\geq \sqrt{2k} (L_{2k}(\mathbf{A}) -  C_1\varepsilon) \|\mathbf{D}^{-1}\mathbf{x}\|_2, \\ 
+&\geq \sqrt{2k} (L_{2k}(\mathbf{A}) -  C_1\varepsilon) \|\mathbf{D}^{-1}\|_{?} \| \mathbf{x}\|_2,
 \end{align*}
-
-%\begin{align*}
-%\|\mathbf{BP}\mathbf{x}\|_2 
-%&\geq \|\mathbf{A}\mathbf{D}^{-1}\mathbf{x}\|_2 - \|(\mathbf{A} - \mathbf{BPD})\mathbf{D}^{-1}\mathbf{x}\|_2 \\
-%&\geq \sqrt{2k} (L_{2k}(\mathbf{A}) -  C_1\varepsilon) \|\mathbf{D}^{-1}\mathbf{x}\|_2, \\ 
-%&\geq \sqrt{2k} (L_{2k}(\mathbf{A}) -  C_1\varepsilon) \|\mathbf{D}^{-1}\|_{?} \| \mathbf{x}\|_2,
-%\end{align*}
 %
 We therefore have that $L_{2k}(\mathbf{BPD}) \geq L_{2k}(\mathbf{A}) - C_1\varepsilon  > 0$, and \eqref{b-PDa} then follows from \eqref{stuff}.
-The reader may verify that $L_{2k}(\mathbf{BP}) \geq L_{2k}(\mathbf{BPD}) / \|\mathbf{D}\|_1$.
 
@@
 It is only a matter of time before these systems incorporate dictionary learning to encode and decode signals (e.g., in a device that learns structure from motion \cite{kong2016prior}), just as scientists have used sparse coding to make sense of their data \cite{jung2001imaging, agarwal2014spatially, lee2016sparse, wu2016stability}.
-Assurances offered by our theorems certify that different devices and algorithms will learn equivalent representations given enough data from statistically identical systems.\footnote{To contrast with the current hot topic of ``Deep Learning'', there are few such uniqueness guarantees for these models of data; moreover, even small noise can dramatically alter their output \cite{goodfellow2014explaining}.} Indeed, a main reason for the sustained interest in dictionary learning as an unsupervised method for data analysis seems to be the assumed well-posedness of parameter identification in the model, confirmation of which forms the core of our findings.
+
+Assurances offered by our theorems certify that different devices and algorithms learn equivalent representations given enough data from statistically identical systems.\footnote{To contrast with the current hot topic of ``Deep Learning'', there are few such uniqueness guarantees for these models of data; moreover, even small noise can dramatically alter their output \cite{goodfellow2014explaining}.}
+Indeed, a main reason for the sustained interest in dictionary learning as an unsupervised method for data analysis seems to be the assumed well-posedness of parameter identification in the model, confirmation of which forms the core of our findings.
 
 We close with some remaining open challenges.
-First, there is the basic problem of proving optimal lower bounds on sufficient sample size for uniqueness and stability in sparse coding.
-Additionally, given the NP-hardness of verifying the spark condition for matrices, are the corresponding approximation Probs.~\ref{InverseProblem} and \ref{OptimizationProblem} also computationally hard?
+First, there is the basic problem of proving optimal lower bounds on sufficient sample size guaranteeing uniqueness and stability in sparse coding.
+Additionally, given the NP-hardness of verifying spark conditions for matrices, are the corresponding approximation Probs.~\ref{InverseProblem} and \ref{OptimizationProblem} also computationally hard?
 In what special cases is it efficient to check that a solution is stably unique for these problems?

### 2019-05-09 manuscripts/IEEE/final_submission.tex
ye
Rehn shout out

@@
 
-Our guarantees also hold for a related (and perhaps more commonly posed) optimization problem that seeks a dictionary minimizing the average number of elementary waveforms required to reconstruct each sample of the dataset (Thm.~\ref{SLCopt}).
-Importantly, we never make assumptions on learned dictionaries (e.g., that they, too, be injective over some domain) beyond an upper bound on dictionary size, which is necessary to avoid trivial solutions (e.g., allowing for $m = N$ waveforms).
+Our guarantees also hold for a related (and perhaps more commonly posed, e.g.
+\cite{rehnsommer2007}) optimization problem seeking a dictionary minimizing the average number of elementary waveforms required to reconstruct each sample of the dataset (Thm.~\ref{SLCopt}).
+Importantly, we never make assumptions on learned dictionaries (e.g., that they, too, be injective over some domain) beyond an upper bound on dictionary size, which is necessary to avoid trivial solutions (e.g., allowing $m = N$).
 %That is, every pair of solutions of comparable size has some number of dictionary elements in common (up to noise), and similarly so for the coefficients of sparse codes they induce.

### 2019-05-09 manuscripts/IEEE/final_submission.tex
tidying up

@@
 
-%
-
 \begin{problem}\label{InverseProblem}
-Find a real matrix $\mathbf{B}$ and $k$-sparse $\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N$ that satisfy $\|\mathbf{z}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \eta$ for all $i$.
+Find a real matrix $\mathbf{B}$ and $k$-sparse $\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N$ that satisfy $\|\mathbf{z}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \eta$ for all $i = 1,\ldots,N$.
 \end{problem}
@@
 
-We generalize the matrix lower bound for our purposes by restricting it to the spans of certain submatrices\footnote{See \cite{vidal2005generalized} for an overview of the related ``union of subspaces" model.} associated with a hypergraph $\mathcal{H} \subseteq {[m] \choose k}$ of column indices.
+The lower bound of a matrix is generalized below in (\ref{Ldef}) by restricting it to the spans of certain submatrices\footnote{See \cite{vidal2005generalized} for an overview of the related ``union of subspaces" model.} associated with a hypergraph $\mathcal{H} \subseteq {[m] \choose k}$ of column indices.
 Let $\mathbf{M}_S$ denote the submatrix formed by the columns of a matrix $\mathbf{M}$ indexed by $S \subseteq [m]$ (setting $\mathbf{M}_\emptyset := \mathbf{0}$).
@@
 
-Since sparse codes in general linear position are straightforward to produce deterministically with a ``Vandermonde''  construction (i.e., by choosing columns of the matrix $[\gamma_{i}^j]_{i,j=1}^{k,N}$, for distinct nonzero $\gamma_i$), we have the following direct consequence of Thm.~\ref{DeterministicUniquenessTheorem}.
+Since sparse codes in general linear position are straightforward to produce with a ``Vandermonde''  construction (i.e., by choosing columns of the matrix $[\gamma_{i}^j]_{i,j=1}^{k,N}$, for distinct nonzero $\gamma_i$), we have the following direct consequence of Thm.~\ref{DeterministicUniquenessTheorem}.
 
@@
 We therefore have that $L_{2k}(\mathbf{BPD}) \geq L_{2k}(\mathbf{A}) - C_1\varepsilon  > 0$, and \eqref{b-PDa} then follows from \eqref{stuff}.
-The reader may verify that $L_{2k}(\mathbf{BP}) \geq L_{2k}(\mathbf{BPD}) / \|\mathbf{D}\|_1$.
+The reader may also verify that $L_{2k}(\mathbf{BP}) \geq L_{2k}(\mathbf{BPD}) / \|\mathbf{D}\|_1$.
 
@@
 
-We now state our result in combinatorial matrix analysis, which contains most of the complexity in the proof of Thm.~\ref{DeterministicUniquenessTheorem}.
+The following is our result in combinatorial matrix analysis; it contains most of the complexity in the proof of Thm.~\ref{DeterministicUniquenessTheorem}.
 
@@
 
-The constant $C_2 > 0$ of Lem.~\ref{MainLemma} is then given by:  
+The constant $C_2 > 0$ of Lem.~\ref{MainLemma} can now be expressed as:  
 \begin{align}\label{Cdef2}
@@
 
-We now define the constant $C_1 > 0$ of Thm.~\ref{DeterministicUniquenessTheorem} in terms of $C_2$.
+We next define the constant $C_1 > 0$ of Thm.~\ref{DeterministicUniquenessTheorem} in terms of $C_2$.
 Given vectors $\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$, let $\mathbf{X}$ denote the $m \times N$ matrix with columns $\mathbf{x}_i$ and let $I(S)$ denote the set of indices $i$ for which $\mathbf{x}_i$ is supported in $S$.
@@
 Using the definitions, we have $\|\mathbf{AX}_{I(S)}\mathbf{c}\|_2 \geq \sqrt{k} L_\mathcal{H}(\mathbf{A})\|\mathbf{X}_{I(S)}\mathbf{c}\|_2 \geq k L_\mathcal{H}(\mathbf{A}) L_k(\mathbf{X}_{I(S)})\|\mathbf{c}\|_2$.
-Thus, $L_k(\mathbf{AX}_{I(S)}) \geq \sqrt{k} L_\mathcal{H}(\mathbf{A}) L_k(\mathbf{X}_{I(S)}) > 0$, since $L_{\mathcal{H}}(\mathbf{A}) \geq L_{2\mathcal{H}}(\mathbf{A})> 0$ and $L_k(\mathbf{X}_{I(S)}) > 0$ by general linear position of the $\mathbf{x}_i$.} and yields an upper bound on $\varepsilon$ consistent with that proven sufficient in the case $k=1$ considered at the beginning of this section.\footnote{When $\mathbf{x}_i = c_i\mathbf{e}_i$ we have $C_2 \geq 2\|\mathbf{A}_i\|_2$ and the denominator in \eqref{Cdef1} becomes $\min_{i \in [m]} |c_i| \|\mathbf{A}_i\|_2$, hence $C_1 \geq 2 / \min_{i \in [m]} |c_i|$.}
+Thus, $L_k(\mathbf{AX}_{I(S)}) \geq \sqrt{k} L_\mathcal{H}(\mathbf{A}) L_k(\mathbf{X}_{I(S)}) > 0$, since $L_{\mathcal{H}}(\mathbf{A}) \geq L_{2\mathcal{H}}(\mathbf{A})> 0$ and $L_k(\mathbf{X}_{I(S)}) > 0$ by general linear position of the $\mathbf{x}_i$.} and yields an upper bound on $\varepsilon$ consistent with that proven sufficient in the case $k=1$ considered at the beginning of this section.\footnote{When $\mathbf{x}_i = c_i\mathbf{e}_i$, we have $C_2 \geq 2\|\mathbf{A}_i\|_2$ and the denominator in \eqref{Cdef1} becomes $\min_{i \in [m]} |c_i| \|\mathbf{A}_i\|_2$; hence, $C_1 \geq 2 / \min_{i \in [m]} |c_i|$.}
 % C_2(\mathbf{A}, \mathcal{H}) := \frac{ (r+1) \max_{j \in [m]} \|\mathbf{A}_j\|_2}{ \min_{\mathcal{G} \in {\mathcal{H} \choose r} \cup {\mathcal{H} \choose r+1}} \xi( \{ \bm{\mathcal{A}}_S \}

### 2019-05-09 manuscripts/IEEE/final_submission.tex
l1 ramble

--- 2019-05-09 manuscripts/IEEE/final_submission.tex
@@
 % [*** Incorporate this open problem with more words ***]
+
+Solving Prob.~\ref{SLCopt} directly is intractable in general since it necessitates, for each proposed dictionary $\mathbf{B}$, a combinatorial search for the supports of the associated sparse codes $\mathbf{\overline x}_i$.
+A common work-around is to convexify the problem (for fixed $\mathbf{B}$) by substituting the norm $\|\cdot\|_0$ with $\|\cdot\|_1$, impelled the fact that matrices $\mathbf{A}$ with large enough $L_{2k}(\mathbf{A})$ induce the same sparse codes via minimization of either norm \cite{?}.
+To this end, the lower bound $L_{2k}(\mathbf{BP}) \geq (L_{2k}(\mathbf{A}) - C_1\varepsilon) / \|\mathbf{D}\|_1$ implied by Thm.~\ref{DeterministicUniquenessTheorem} hints at conditions on the generating dictionary $\mathbf{A}$ and $k$-sparse codes $\mathbf{x}_i$ under which \emph{all} matrices $\mathbf{B}$ (of bounded column-norm) that solve Prob.~\ref{OptimizationProblem} also share this property of $\mathbf{A}$ by virtue of uniqueness and stability.
+One might then imagine an inference procedure whereby sparse codes are inferred via minimization of $\|\cdot\|_1$, but solutions still evaluated by their collective support size, yielding unique optimal solutions to Prob.~\ref{SLCopt} if only constraints could be imposed such that the learning procedure eventually guides $\mathbf{B}$ through an optimal dictionary.
+% (e.g.
+the dictionary is a member of a known finite set).
 

### 2019-05-09 manuscripts/IEEE/final_submission.tex

--- 2019-05-09 manuscripts/IEEE/final_submission.tex
@@
 
+Solving Prob.~\ref{SLCopt} directly is intractable in general since it necessitates, for each proposed dictionary $\mathbf{B}$, a combinatorial search for the supports of the associated sparse codes $\mathbf{\overline x}_i$.
+A common work-around is to convexify the problem (for fixed $\mathbf{B}$) by substituting the norm $\|\cdot\|_0$ with $\|\cdot\|_1$, impelled the fact that matrices $\mathbf{A}$ with large enough $L_{2k}(\mathbf{A})$ induce the same sparse codes via minimization of either norm \cite{?}.
+To this end, the lower bound $L_{2k}(\mathbf{BP}) \geq (L_{2k}(\mathbf{A}) - C_1\varepsilon) / \|\mathbf{D}\|_1$ implied by Thm.~\ref{DeterministicUniquenessTheorem} hints at conditions on the generating dictionary $\mathbf{A}$ and $k$-sparse codes $\mathbf{x}_i$ under which \emph{all} matrices $\mathbf{B}$ (of bounded column-norm) that solve Prob.~\ref{OptimizationProblem} also share this property of $\mathbf{A}$ by virtue of uniqueness and stability.
+One might then imagine an inference procedure whereby sparse codes are inferred via minimization of $\|\cdot\|_1$, but solutions still evaluated by their collective support size, yielding unique optimal solutions to Prob.~\ref{SLCopt} if only constraints could be imposed such that the learning procedure eventually guides $\mathbf{B}$ through an optimal dictionary.
+% (e.g.
+the dictionary is a member of a known finite set).
+
 \textbf{Acknowledgement.} We thank F. Sommer and D. Rhea for early thoughts, and I. Morris for posting \eqref{eqdim} online.

### 2019-05-09 manuscripts/IEEE/final_submission.tex
more tidying up

--- 2019-05-09 manuscripts/IEEE/final_submission.tex
@@
 Before moving on to our proof of Thm.~\ref{SLCopt}, we briefly revisit here our discussion on sample complexity from the end of the previous section.
-While an exponential number of samples may very well prove to be necessary in the deterministic or almost-certain case, our proof of Thm.~\ref{DeterministicUniquenessTheorem} can be extended to hold with some probability for \emph{any} number of samples by alternative appeal to a probabilistic pigeonholing at the point early in the proof where the (deterministic) pigeonhole principle is applied to show that for every $S \in \mathcal{H}$, there exist $k$ vectors $\mathbf{x}_i$ supported on $S$ whose corresponding $\mathbf{\overline x}_i$ all share the same support.\footnote{A famous example of such an argument is the counter-intuitive ``birthday paradox", which demonstrates that the probability of two people having the same birthday in a room of twenty-three is greater than 50\%.} Given insufficient samples, this argument has some less-than-certain probability of being valid for each $S \in \mathcal{H}$.
+While an exponential number of samples may very well prove to be necessary in the deterministic or almost-certain case, our proof of Thm.~\ref{DeterministicUniquenessTheorem} can be extended to hold with some probability for \emph{any} number of samples by alternative appeal to a probabilistic pigeonholing at the point early in the proof where the (deterministic) pigeonhole principle is applied to show that for every $S \in \mathcal{H}$, there exist $k$ vectors $\mathbf{x}_i$ supported on $S$ whose corresponding $\mathbf{\overline x}_i$ all share the same support.\footnote{A famous example of such an argument is the counter-intuitive ``birthday paradox", which demonstrates that the probability of two people having the same birthday in a room of twenty-three is greater than 50\%.}
+
+Given insufficient samples, this argument has some less-than-certain probability of being valid for each $S \in \mathcal{H}$.
 Nonetheless, simulations with small hypergraphs confirm that the probability of success very quickly approaches one once the number of samples $N$ surpasses a small fraction of the deterministic sample complexity.
@@
 Beyond an extension of existing noiseless guarantees \cite{Hillar15} to the noisy regime and their novel application to Prob.~\ref{OptimizationProblem}, our work contains a theory of combinatorial designs for support sets key to identification of dictionaries.
-We incorporate this idea into a fundamental lemma in matrix theory (Lem.~\ref{MainLemma}) that draws upon the definition of a matrix lower bound induced by a hypergraph.
+We incorporate this idea into a fundamental lemma in matrix theory (Lem.~\ref{MainLemma}) that draws upon the definition of a matrix lower bound (\ref{Ldef}) induced by a hypergraph.
 New insights enabled by this combinatorial approach include: 1) a subset of dictionary elements is recoverable even if dictionary size is overestimated, 2) data require only a polynomial number of distinct sparse supports, and 3) recoverable dictionaries need not satisfy the spark condition.
 
-The absence of any assumptions about dictionaries solving Prob.~\ref{InverseProblem} was a major technical difficulty in proving Thm.~\ref{DeterministicUniquenessTheorem}.
+The absence of any assumptions about dictionaries solving Prob.~\ref{InverseProblem} was a major technical obstruction in proving Thm.~\ref{DeterministicUniquenessTheorem}.
 We sought such a general guarantee because of the practical difficulty in ensuring that an algorithm maintain a dictionary satisfying the spark condition \eqref{SparkCondition} at each iteration, an implicit requirement of all previous works except \cite{Hillar15}; indeed, even certifying a dictionary has this property is NP-hard \cite{tillmann2014computational}.
@@
 where we have also used that the spectral norm of the orthogonal projections $\Pi_{V_{\ell}}$ satisfies $\|\Pi_{V_{\ell}}\|_2 \leq 1$ for all $\ell$.
+
 It remains to bound the second term in \eqref{f} by $\xi(\mathcal{V}) \|\mathbf{u} - \Pi_V\mathbf{u}\|_2$.
@@
 = \| ( \Pi_{V_k} \cdots\Pi_{V_1} - \Pi_V ) (\mathbf{u} - \Pi_V\mathbf{u})\|_2$. % \leq z\|\mathbf{u} - \Pi_V\mathbf{u}\|_2$.
-Inequality \eqref{DTILeq} then follows from the following fact \cite[Thm.~9.33]{Deutsch12}:
+Consequently, inequality \eqref{DTILeq} follows from \cite[Thm.~9.33]{Deutsch12}:
 \begin{align}

### 2019-05-09 manuscripts/IEEE/final_submission.tex
final edits
open problems

--- 2019-05-09 manuscripts/IEEE/final_submission.tex
@@
 
-We close with some remaining open challenges.
-First, there is the basic problem of proving optimal lower bounds on sufficient sample size guaranteeing uniqueness and stability in sparse coding.
+We close with some challenges left open by our work.
+First, there is the basic problem of proving optimal lower bounds on sufficient sample size $N$ guaranteeing the uniqueness and stability of sparse representations.
+The pigeonholing argument in the proof of Thm.~\ref{DeterministicUniquenessTheorem} is loose in that it assigns to each support $S \in \mathcal{H}$ a corresponding support $\overline S$ without consideration of previously matched pairs; although we doubt tightening in this way will lead to sub-exponential sample sizes.
+Sample complexity will also benefit from lowering the number of required supports, i.e.
+the size of regular uniform hypergraphs satisfying the SIP.
+The regularity requirement on support hypergraphs can be loosened to allow for certain non-regular hypergraphs satisfying constraints on the degree sequence of nodes; though we impose regularity for clarity of exposition.
+It is then natural to ask: what is the smallest hypergraph satisfying the required constraints forgiven $m$ and $k$?
+Finally, the error bounds can be improved by tightening the constant $C_1$, e.g.
+via an improvement in Lemma ?.
+
 Additionally, given the NP-hardness of verifying spark conditions for matrices, are the corresponding approximation Probs.~\ref{InverseProblem} and \ref{OptimizationProblem} also computationally hard?

### 2019-05-09 manuscripts/IEEE/final_submission.tex

--- 2019-05-09 manuscripts/IEEE/final_submission.tex
@@
 % [*** Incorporate this open problem with more words ***]
+
+%Solving Prob.~\ref{SLCopt} directly is intractable in general since it necessitates, for each proposed dictionary $\mathbf{B}$, a combinatorial search for the supports of the associated sparse codes $\mathbf{\overline x}_i$.
+A common work-around is to convexify the problem (for fixed $\mathbf{B}$) by substituting the norm $\|\cdot\|_0$ with $\|\cdot\|_1$, impelled the fact that matrices $\mathbf{A}$ with large enough $L_{2k}(\mathbf{A})$ induce the same sparse codes via minimization of either norm \cite{?}.
+To this end, the lower bound $L_{2k}(\mathbf{BP}) \geq (L_{2k}(\mathbf{A}) - C_1\varepsilon) / \|\mathbf{D}\|_1$ implied by Thm.~\ref{DeterministicUniquenessTheorem} hints at conditions on the generating dictionary $\mathbf{A}$ and $k$-sparse codes $\mathbf{x}_i$ under which \emph{all} matrices $\mathbf{B}$ (of bounded column-norm) that solve Prob.~\ref{OptimizationProblem} also share this property of $\mathbf{A}$ by virtue of uniqueness and stability.
+One might then imagine an inference procedure whereby sparse codes are inferred via minimization of $\|\cdot\|_1$, but solutions still evaluated by their collective support size, yielding unique optimal solutions to Prob.~\ref{SLCopt} if only constraints could be imposed such that the learning procedure eventually guides $\mathbf{B}$ through an optimal dictionary.
+% (e.g.
+the dictionary is a member of a known finite set).
 

### 2019-05-09 manuscripts/IEEE/final_submission.tex
discussion

@@
 We close with some challenges left open by our work.
+All of our conditions guaranteeing the uniqueness and stability of sparse representations have only been proven sufficient; there therefore remains the open problem of extending them to necessary conditions, be they optimal lower bounds on required sample size, conditions on the support set hypergraphs of generating codes, or tolerable error bounds.
+On this last note in particular, we remark that our constants have been derived for deterministic ``worst-case'' noise, whereas the ``effective'' noise might be significantly reduced when sampled from a concentrated distribution.
+It would be interesting to see how drastically all conditions can be tightened (to practical benefit) by requiring only probabilistic guarantees in this way, or in the spirit of the discussion on sample complexity following our proof of Thm.~\ref{DeterministicUniquenessTheorem}.
+
+Another interesting question that remains is: in what special cases is it efficient to check that a solution to Probs.~\ref{InverseProblem} or \ref{OptimizationProblem} is unique (and stable)?
+Given the NP-hardness of computing our sufficient conditions for checking this in general, are the corresponding problems also computationally hard?
+Finally, since substituting the norm $\|\cdot\|_0$ with $\|\cdot\|_1$ yields the same optimal sparse codes for dictionaries with large enough lower bounds \cite{eldar2012compressed}, is there a version of Thm.~\ref{SLCopt} guaranteeing that Prob.~\ref{OptimizationProblem} can be solved while inferring sparse codes in this way?
+% [*** Incorporate this open problem with more words ***]
+
+%We close with some challenges left open by our work.
 First, there is the basic problem of proving optimal lower bounds on sufficient sample size $N$ guaranteeing the uniqueness and stability of sparse representations.
@@
 via an improvement in Lemma ?.
-
-Additionally, given the NP-hardness of verifying spark conditions for matrices, are the corresponding approximation Probs.~\ref{InverseProblem} and \ref{OptimizationProblem} also computationally hard?
-In what special cases is it efficient to check that a solution is stably unique for these problems?
-Finally, as $\ell_1$ relaxations for inferring sparse vectors have, in many cases \cite{eldar2012compressed}, the same solutions as for $\ell_0$, is there an $\ell_1$ version of Thm.~\ref{SLCopt}?
-% [*** Incorporate this open problem with more words ***]
 

### 2019-05-09 manuscripts/IEEE/final_submission.tex
tiny

--- 2019-05-09 manuscripts/IEEE/final_submission.tex
@@
 But this is exactly the supposition in \eqref{1D}, with $J$ and $\overline \varepsilon$ in place of $[m]$ and $\varepsilon$, respectively.
-The same arguments of the case $k=1$ in Sec.~\ref{DUT} can then be made to show that for any $\overline m \times \overline m$ permutation and invertible diagonal matrices $\mathbf{P}$ and $\mathbf{D}$ with, respectively, columns $\mathbf{e}_{\pi(i)}$ and $\frac{\overline{c}_i}{c_i}\mathbf{e}_i$ for $i \in J$ (otherwise, $\mathbf{e}_{i}$ for $i \in [\overline{m}] \setminus J$) we have $\|\mathbf{A}_i - (\mathbf{B}\mathbf{PD})_i \|_2 \leq \overline  \varepsilon / |c_i|  \leq C_2 \varepsilon$ for all $i \in J$.
+The same arguments of the case $k=1$ in Sec.~\ref{DUT} can then be made to show that for any $\overline m \times \overline m$ permutation and invertible diagonal matrices $\mathbf{P}$ and $\mathbf{D}$ with, respectively, columns $\mathbf{e}_{\pi(i)}$ and $\frac{\overline{c}_i}{c_i}\mathbf{e}_i$ for $i \in J$ (otherwise, $\mathbf{e}_{i}$ for $i \in [\overline{m}] \setminus J$), we have $\|\mathbf{A}_i - (\mathbf{B}\mathbf{PD})_i \|_2 \leq \overline  \varepsilon / |c_i|  \leq C_2 \varepsilon$ for all $i \in J$.
 \end{proof}

### 2019-05-09 manuscripts/IEEE/final_submission.tex
discusion final edits

@@
 
+There are still several challenges left open by our work.
+All conditions here guaranteeing uniqueness and stability of sparse representations have only been shown sufficient; it remains open, therefore, to extend them to necessary conditions, be they optimal lower bounds on required sample size, conditions on the support set hypergraphs of generating codes, or tolerable error bounds.
+On this last note, we remark that our constants have been derived for deterministic ``worst-case" noise, whereas the ``effective" noise might be significantly reduced when sampled from a concentrated distribution.
+It would be interesting to see how drastically all conditions can be tightened (to practical benefit) by requiring only probabilistic guarantees in this way, or in the spirit of the discussion on sample complexity following our proof of Thm.~\ref{DeterministicUniquenessTheorem}.
+
+Another interesting question that remains is for which special cases is it efficient to check that a solution to Probs.~\ref{InverseProblem} or \ref{OptimizationProblem} is unique (and stable).
+Given the NP-hardness of computing sufficient conditions for checking this in general, are the corresponding problems also computationally hard?
+Finally, since substituting the norm $\|\cdot\|_0$ with $\|\cdot\|_1$ yields the same optimal sparse codes for dictionaries with large enough lower bounds \cite{eldar2012compressed}, is there a version of Thm.~\ref{SLCopt} certifying that Prob.~\ref{OptimizationProblem} can be solved while inferring sparse codes in this way?
+% [*** Incorporate this open problem with more words ***]
+
 The absence of any assumptions about dictionaries solving Prob.~\ref{InverseProblem} was a major technical obstruction in proving Thm.~\ref{DeterministicUniquenessTheorem}.
@@
 Indeed, a main reason for the sustained interest in dictionary learning as an unsupervised method for data analysis seems to be the assumed well-posedness of parameter identification in the model, confirmation of which forms the core of our findings.
-
-We close with some challenges left open by our work.
-All of our conditions guaranteeing the uniqueness and stability of sparse representations have only been proven sufficient; there therefore remains the open problem of extending them to necessary conditions, be they optimal lower bounds on required sample size, conditions on the support set hypergraphs of generating codes, or tolerable error bounds.
-On this last note in particular, we remark that our constants have been derived for deterministic ``worst-case'' noise, whereas the ``effective'' noise might be significantly reduced when sampled from a concentrated distribution.
-It would be interesting to see how drastically all conditions can be tightened (to practical benefit) by requiring only probabilistic guarantees in this way, or in the spirit of the discussion on sample complexity following our proof of Thm.~\ref{DeterministicUniquenessTheorem}.
-
-Another interesting question that remains is: in what special cases is it efficient to check that a solution to Probs.~\ref{InverseProblem} or \ref{OptimizationProblem} is unique (and stable)?
-Given the NP-hardness of computing our sufficient conditions for checking this in general, are the corresponding problems also computationally hard?
-Finally, since substituting the norm $\|\cdot\|_0$ with $\|\cdot\|_1$ yields the same optimal sparse codes for dictionaries with large enough lower bounds \cite{eldar2012compressed}, is there a version of Thm.~\ref{SLCopt} guaranteeing that Prob.~\ref{OptimizationProblem} can be solved while inferring sparse codes in this way?
-% [*** Incorporate this open problem with more words ***]
 

### 2019-05-09 manuscripts/IEEE/final_submission.tex
disc

@@
 
-There are still several challenges left open by our work.
-All conditions here guaranteeing uniqueness and stability of sparse representations have only been shown sufficient; it remains open, therefore, to extend them to necessary conditions, be they optimal lower bounds on required sample size, conditions on the support set hypergraphs of generating codes, or tolerable error bounds.
-On this last note, we remark that our constants have been derived for deterministic ``worst-case" noise, whereas the ``effective" noise might be significantly reduced when sampled from a concentrated distribution.
-It would be interesting to see how drastically all conditions can be tightened (to practical benefit) by requiring only probabilistic guarantees in this way, or in the spirit of the discussion on sample complexity following our proof of Thm.~\ref{DeterministicUniquenessTheorem}.
-
-Another interesting question that remains is for which special cases is it efficient to check that a solution to Probs.~\ref{InverseProblem} or \ref{OptimizationProblem} is unique (and stable).
-Given the NP-hardness of computing sufficient conditions for checking this in general, are the corresponding problems also computationally hard?
-Finally, since substituting the norm $\|\cdot\|_0$ with $\|\cdot\|_1$ yields the same optimal sparse codes for dictionaries with large enough lower bounds \cite{eldar2012compressed}, is there a version of Thm.~\ref{SLCopt} certifying that Prob.~\ref{OptimizationProblem} can be solved while inferring sparse codes in this way?
-% [*** Incorporate this open problem with more words ***]
-
 The absence of any assumptions about dictionaries solving Prob.~\ref{InverseProblem} was a major technical obstruction in proving Thm.~\ref{DeterministicUniquenessTheorem}.
@@
 
+We close with some challenges left open by our work.
+All conditions here guaranteeing uniqueness and stability of sparse representations have only been shown sufficient; it remains open, therefore, to extend them to necessary conditions, be they optimal bounds on required sample size, conditions on the support set hypergraphs of generating codes, or tolerable error bounds.
+On this last note, we remark that our constants have been derived for deterministic ``worst-case" noise, whereas the ``effective" noise might be significantly reduced when sampled from a concentrated distribution.
+It would be interesting to see how drastically all conditions can be relaxed (to practical benefit) by requiring only probabilistic guarantees in this way, or in the spirit of the discussion on sample complexity following our proof of Thm.~\ref{DeterministicUniquenessTheorem}.
+
+Another interesting question is for which special cases is it efficient to check that a solution to Prob.~\ref{InverseProblem} or \ref{OptimizationProblem} is unique (and stable).
+Considering that our sufficient conditions for checking this in general are NP-hard to compute, are the corresponding problems also hard?
+Finally, since substituting the norm $\|\cdot\|_0$ with $\|\cdot\|_1$ yields the same optimal sparse codes for dictionaries with large enough lower bounds \cite{eldar2012compressed}, is there a version of Thm.~\ref{SLCopt} certifying that Prob.~\ref{OptimizationProblem} can be solved while inferring sparse codes in this way?
+% [*** Incorporate this open problem with more words ***]
+It is our hope that these remaining challenges peak the interest of the community enough to pick up where we have left off.
 %We close with some challenges left open by our work.

### 2019-05-09 manuscripts/IEEE/final_submission.tex
final

@@
 \begin{corollary}\label{ProbabilisticCor}
-If indeterminate entries of $\mathbf{A}$ and $\mathbf{x}_i$ are drawn independently from probability distributions absolutely continuous with respect to the standard Borel measure, then $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$ with probability one.
+If indeterminate entries of $\mathbf{A}$ and the $\mathbf{x}_i$ are drawn independently from probability distributions absolutely continuous with respect to the standard Borel measure, then $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$ with probability one.
 \end{corollary}

### 2019-05-10 manuscripts/IEEE/final_submission.tex
discussion

@@
 
-One direct application of this work is to theoretical neuroscience, wherein our theorems justify the mathematical soundness of one of the few hypothesized theories of bottleneck communication in the brain \cite{Isely10}: that sparse neural population activity is recoverable from its noisy linear compression through a randomly constructed (but unknown) wiring bottleneck by any biologically plausible unsupervised sparse coding method that solves Prob.~\ref{DeterministicUniquenessTheorem} or \ref{SLCopt} (e.g., \cite{rehnsommer2007, rozell2007neurally, pehlevan2015normative}).\footnote{We refer the reader to \cite{ganguli2012compressed} for more on interactions between dictionary learning and neuroscience.}
-
 %A compelling feature of this model is its simple instantiation of the principle of Occam's razor: a natural video, for instance, is modeled as a linear combination of a small number of spatiotemporal building blocks, each representing an archetypical feature latent in the data.
@@
 We incorporate this idea into a fundamental lemma in matrix theory (Lem.~\ref{MainLemma}) that draws upon the definition of a matrix lower bound (\ref{Ldef}) induced by a hypergraph.
-New insights enabled by this combinatorial approach include: 1) a subset of dictionary elements is recoverable even if dictionary size is overestimated, 2) data require only a polynomial number of distinct sparse supports, and 3) recoverable dictionaries need not satisfy the spark condition.
+The new insight offered by this combinatorial approach allows for guaranteed recovery of some or all dictionary elements even if: 1) dictionary size is overestimated, 2) data cover only a polynomial number of distinct sparse supports, and 3) dictionaries do not satisfy the spark condition.
 
@@
 We sought such a general guarantee because of the practical difficulty in ensuring that an algorithm maintain a dictionary satisfying the spark condition \eqref{SparkCondition} at each iteration, an implicit requirement of all previous works except \cite{Hillar15}; indeed, even certifying a dictionary has this property is NP-hard \cite{tillmann2014computational}.
+
+One direct application of this work is to theoretical neuroscience, wherein our theorems justify the mathematical soundness of one of the few hypothesized theories of bottleneck communication in the brain \cite{Isely10}: that sparse neural population activity is recoverable from its noisy linear compression through a randomly constructed (but unknown) wiring bottleneck by any biologically plausible unsupervised sparse coding method that solves Prob.~\ref{DeterministicUniquenessTheorem} or \ref{SLCopt} (e.g., \cite{rehnsommer2007, rozell2007neurally, pehlevan2015normative}).\footnote{We refer the reader to \cite{ganguli2012compressed} for more on interactions between dictionary learning and neuroscience.}
 
@@
 We close with some challenges left open by our work.
-All conditions here guaranteeing uniqueness and stability of sparse representations have only been shown sufficient; it remains open, therefore, to extend them to necessary conditions, be they optimal bounds on required sample size, conditions on the support set hypergraphs of generating codes, or tolerable error bounds.
-On this last note, we remark that our constants have been derived for deterministic ``worst-case" noise, whereas the ``effective" noise might be significantly reduced when sampled from a concentrated distribution.
-It would be interesting to see how drastically all conditions can be relaxed (to practical benefit) by requiring only probabilistic guarantees in this way, or in the spirit of the discussion on sample complexity following our proof of Thm.~\ref{DeterministicUniquenessTheorem}.
-
-Another interesting question is for which special cases is it efficient to check that a solution to Prob.~\ref{InverseProblem} or \ref{OptimizationProblem} is unique (and stable).
-Considering that our sufficient conditions for checking this in general are NP-hard to compute, are the corresponding problems also hard?
-Finally, since substituting the norm $\|\cdot\|_0$ with $\|\cdot\|_1$ yields the same optimal sparse codes for dictionaries with large enough lower bounds \cite{eldar2012compressed}, is there a version of Thm.~\ref{SLCopt} certifying that Prob.~\ref{OptimizationProblem} can be solved while inferring sparse codes in this way?
+All conditions stated here guaranteeing the uniqueness and stability of sparse representations have only been shown sufficient; it remains open, therefore, to extend them to necessary conditions, be they on required sample size, the structure of support set hypergraphs, or tolerable error bounds.
+On this last note, we remark that our deterministic treatment considers always the ``worst-case" noise, whereas the ``effective" noise sampled from a concentrated distribution might be significantly reduced, especially for high-dimensional data.
+It would be of great practical benefit to see how drastically all conditions can be relaxed by requiring only probabilistic guarantees in this way, or in the spirit of the discussion on probabilistic pigeonholing for reducing sample complexity (as in the famous ``birthday paradox") following our proof of Thm.~\ref{DeterministicUniquenessTheorem} .
+
+Another interesting question raised by our work is for which special cases is it efficient to check that a solution to Prob.~\ref{InverseProblem} or \ref{OptimizationProblem} is unique up to noise and inherent ambiguities.
+Considering that the sufficient conditions we have described for checking this in general are NP-hard to compute, are the necessary conditions hard?
+Are Probs.~\ref{InverseProblem} and \ref{OptimizationProblem} then also hard \cite{tilman?}?
+Finally, since solving Prob.~\ref{SLCopt} directly is intractable in general, but efficiently solvable by $\ell_1$-norm minimization for fixed matrices with large enough lower bounds over sparse domains \cite{?}, is there a version of Thm.~\ref{SLCopt} certifying when Prob.~\ref{OptimizationProblem} can be solved efficiently in a similar way?
 % [*** Incorporate this open problem with more words ***]
-It is our hope that these remaining challenges peak the interest of the community enough to pick up where we have left off.
+
+We hope that these remaining challenges pique the interest of the community in picking up where we have left off, and that the theoretical tools we have showcased here may be of use to this end.
+
 %We close with some challenges left open by our work.

### 2019-05-10 manuscripts/IEEE/final_submission.tex
edit start

--- 2019-05-09 manuscripts/IEEE/final_submission.tex
@@
 % TODO: 
-% cite Fritz l0 paper in introduction for seemingly characteristic structure? 
 % Make L_H a definition..? Change def of L to be 1-norm so we don't need these sqrt k's?
@@
 \section{Introduction}\label{Intro}
-%\IEEEPARstart{L}{earning} sparse representations of data has become an important step in modern solutions to problems in signal processing and pattern analysis. 
-% \cite{sato1975method}
 \IEEEPARstart{A}{}common modern approach to pattern analysis in signal processing is to view each of $N$ observed $n$-dimensional signal samples as a (noisy) linear combination of at most $k$ elementary waveforms drawn from some unknown ``dictionary" of size $m \ll N$ (see \cite{Zhang15} for a comprehensive review).
@@
 
-Motivated by these discoveries and more recent work relating compressed sensing \cite{eldar2012compressed} to a theory of information transmission through random wiring bottlenecks in the brain \cite{Isely10}, we address when optimal dictionaries for sparse representation are indeed identifiable from data.
+Motivated by these discoveries and more recent work relating compressed sensing \cite{eldar2012compressed} to a theory of information transmission through random wiring bottlenecks in the brain \cite{Isely10}, we address when dictionaries for sparse representation are indeed identifiable from data.
 Answers to this question may also have implications in practice wherever an appeal is made to latent sparse structure of data (e.g., forgery detection \cite{hughes2010, olshausen2010applied}; brain recordings \cite{jung2001imaging, agarwal2014spatially, lee2016sparse}; and gene expression \cite{wu2016stability}).
@@
 Here, we prove very generally that uniqueness and stability is a typical property of sparse dictionary learning.
-More specifically,  we show that dictionaries injective on a sparse domain are identifiable from \mbox{$N = m(k-1){m \choose k} + m$} noisy sparse linear combinations of their columns up to an error that is linear in the noise (Thm.~\ref{DeterministicUniquenessTheorem}).
+More specifically,  we show that dictionaries injective on a sparse domain are identifiable from \mbox{$N = m(k-1){m \choose k} + m$} noisy k-sparse linear combinations of their $m$ columns up to an error that is linear in the noise (Thm.~\ref{DeterministicUniquenessTheorem}).
 In fact, provided $n \geq \min(2k,m)$, in almost all cases the problem is well-posed, as per Hadamard \cite{Hadamard1902}, given a sufficient amount of data (Thm.~\ref{robustPolythm} and Cor.~\ref{ProbabilisticCor}).

### 2019-05-10 manuscripts/IEEE/final_submission.tex
merge

@@
 Here, we prove very generally that uniqueness and stability is a typical property of sparse dictionary learning.
-More specifically,  we show that dictionaries injective on a sparse domain are identifiable from \mbox{$N = m(k-1){m \choose k} + m$} noisy k-sparse linear combinations of their $m$ columns up to an error that is linear in the noise (Thm.~\ref{DeterministicUniquenessTheorem}).
+More specifically,  we show that dictionaries injective on a sparse domain are identifiable from \mbox{$N = m(k-1){m \choose k} + m$} noisy sparse linear combinations of $k$ of their $m$ columns up to an error that is linear in the noise (Thm.~\ref{DeterministicUniquenessTheorem}).
 In fact, provided $n \geq \min(2k,m)$, in almost all cases the problem is well-posed, as per Hadamard \cite{Hadamard1902}, given a sufficient amount of data (Thm.~\ref{robustPolythm} and Cor.~\ref{ProbabilisticCor}).
@@
 Considering that the sufficient conditions we have described for checking this in general are NP-hard to compute, are the necessary conditions hard?
-Are Probs.~\ref{InverseProblem} and \ref{OptimizationProblem} then also hard \cite{tilman?}?
-Finally, since solving Prob.~\ref{SLCopt} directly is intractable in general, but efficiently solvable by $\ell_1$-norm minimization for fixed matrices with large enough lower bounds over sparse domains \cite{?}, is there a version of Thm.~\ref{SLCopt} certifying when Prob.~\ref{OptimizationProblem} can be solved efficiently in a similar way?
+Are Probs.~\ref{InverseProblem} and \ref{OptimizationProblem} then also hard \cite{Tillmann15}?
+Finally, since solving Prob.~\ref{SLCopt} directly is intractable in general, but efficiently solvable by $\ell_1$-norm minimization for fixed matrices with large enough lower bounds over sparse domains \cite{eldar2012compressed}, is there a version of Thm.~\ref{SLCopt} certifying when Prob.~\ref{OptimizationProblem} can be solved efficiently in a similar way?
 % [*** Incorporate this open problem with more words ***]

### 2019-05-10 manuscripts/IEEE/final_submission.tex
pgs 1 2 edits

@@
 Here, we prove very generally that uniqueness and stability is a typical property of sparse dictionary learning.
-More specifically,  we show that dictionaries injective on a sparse domain are identifiable from \mbox{$N = m(k-1){m \choose k} + m$} noisy sparse linear combinations of $k$ of their $m$ columns up to an error that is linear in the noise (Thm.~\ref{DeterministicUniquenessTheorem}).
+More specifically, we show that matrices injective on a sparse domain are identifiable from \mbox{$N = m(k-1){m \choose k} + m$} noisy linear combinations of $k$ of their $m$ columns up to an error that is linear in the noise (Thm.~\ref{DeterministicUniquenessTheorem}).
 In fact, provided $n \geq \min(2k,m)$, in almost all cases the problem is well-posed, as per Hadamard \cite{Hadamard1902}, given a sufficient amount of data (Thm.~\ref{robustPolythm} and Cor.~\ref{ProbabilisticCor}).
@@
 for $k$-\emph{sparse} $\mathbf{x}_i \in \mathbb{R}^m$ having at most $k<m$ nonzero entries and \emph{noise} $\mathbf{n}_i \in \mathbb{R}^n$, with bounded norm $\| \mathbf{n}_i \|_2 \leq  \eta$ representing our worst-case uncertainty in measuring the product $\mathbf{A}\mathbf{x}_i$.
-The first mathematical problem we consider is the following.
+We first consider the following formulation of sparse coding.
+%The first mathematical problem we consider is the following.
 
 \begin{problem}\label{InverseProblem}
-Find a real matrix $\mathbf{B}$ and $k$-sparse $\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N$ that satisfy $\|\mathbf{z}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \eta$ for all $i = 1,\ldots,N$.
+Find a dictionary matrix $\mathbf{B}$ and $k$-sparse codes $\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N$ that satisfy $\|\mathbf{z}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \eta$ for all $i = 1,\ldots,N$.
 \end{problem}
@@
 \begin{problem}\label{OptimizationProblem}
-Find real $\mathbf{B}$ and \mbox{$\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N$} that solve:
+Find matrices $\mathbf{B}$ and vectors \mbox{$\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N$} solving:
 \begin{align}\label{minsum}
@@
 
-\textbf{Dictionary Recovery:} Fix $\varepsilon < L_{2}(\mathbf{A}) / C_1$.\footnote{Note that the condition $\varepsilon < L_2(\mathbf{A}) /C_1$ is necessary; otherwise, with \mbox{$\mathbf{A}$ = $\mathbf{I}$} (the identity matrix) and $\mathbf{x}_i = \mathbf{e}_i$, the matrix $\mathbf{B} = \left[\mathbf{0}, \frac{1}{2}(\mathbf{e}_1 + \mathbf{e}_2), \mathbf{e}_3, \ldots, \mathbf{e}_{m} \right]$ and sparse codes $\mathbf{\overline x}_i = \mathbf{e}_2$ for $i = 1, 2$ and $\mathbf{\overline x}_i = \mathbf{e}_i$ for $i \geq 3$ satisfy $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline{x}}_i \|_2 \leq \varepsilon$ but nonetheless violate \eqref{Cstable}.} The only $n \times \overline m$ matrices $\mathbf{B}$ that have, for every $i \in [N]$, an associated $k$-sparse $\mathbf{\overline x}_i$ satisfying \mbox{$\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \varepsilon$} have $\overline m \geq m$, and provided that $\overline m (r-1) < mr$, there is a permutation matrix $\mathbf{P}$ and an invertible diagonal matrix $\mathbf{D}$ such that:
+\textbf{Dictionary Recovery:} Fix $\varepsilon < L_{2}(\mathbf{A}) / C_1$.\footnote{Note that the condition $\varepsilon < L_2(\mathbf{A}) /C_1$ is necessary; otherwise, with \mbox{$\mathbf{A}$ = $\mathbf{I}$} (the identity matrix) and $\mathbf{x}_i = \mathbf{e}_i$, the matrix $\mathbf{B} = \left[\mathbf{0}, \frac{1}{2}(\mathbf{e}_1 + \mathbf{e}_2), \mathbf{e}_3, \ldots, \mathbf{e}_{m} \right]$ and sparse codes $\mathbf{\overline x}_i = \mathbf{e}_2$ for $i = 1, 2$ and $\mathbf{\overline x}_i = \mathbf{e}_i$ for $i \geq 3$ satisfy $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline{x}}_i \|_2 \leq \varepsilon$ but nonetheless violate \eqref{Cstable}.} If an $n \times \overline m$ matrix $\mathbf{B}$ has, for every $i \in [N]$, an associated $k$-sparse $\mathbf{\overline x}_i$ satisfying \mbox{$\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \varepsilon$}, then $\overline m \geq m$, and provided that $\overline m (r-1) < mr$, there is a permutation matrix $\mathbf{P}$ and an invertible diagonal matrix $\mathbf{D}$ such that:
 \begin{align}\label{Cstable}
@@
 The (unraveled) basis elements of the $8 \times 8$ discrete cosine transform (DCT) form the 64 columns of the left-most matrix above.
-Three increasingly imprecise dictionaries (columns relabelled to best match original) are recovered by FastICA \cite{hyvarinen2000independent} trained on data generated from $8$-sparse linear combinations of DCT elements corrupted with additive noise (increasing from left to right).}
+Three increasingly imprecise dictionaries (columns reordered to best match original) are recovered by FastICA \cite{hyvarinen2000independent} trained on data generated from $8$-sparse linear combinations of DCT elements corrupted with additive noise (increasing from left to right).}
 \vspace{-.6 cm}
@@
 A main motivation for this work is the emergence of seemingly unique representations from sparse coding models trained on natural data, despite the varied assumptions underlying the many algorithms in current use.
-Our results constitute an important step toward explaining these phenomena as well as unifying many publications on the topic by demonstrating general deterministic conditions under which identification of parameters in this model is not only possible but also robust to uncertainty in measurement and model choice.
+Our results constitute an important step toward explaining these phenomena as well as unifying many publications on the topic by deriving general deterministic conditions under which identification of parameters in this model is not only possible but also robust to uncertainty in measurement and model choice.
 

### 2019-05-10 manuscripts/IEEE/final_submission.tex
i

--- 2019-05-10 manuscripts/IEEE/final_submission.tex
@@
 % TODO: 
+% cite Fritz l0 paper in introduction for seemingly characteristic structure? 
 % Make L_H a definition..? Change def of L to be 1-norm so we don't need these sqrt k's?
@@
 \section{Introduction}\label{Intro}
+%\IEEEPARstart{L}{earning} sparse representations of data has become an important step in modern solutions to problems in signal processing and pattern analysis. 
+% \cite{sato1975method}
 \IEEEPARstart{A}{}common modern approach to pattern analysis in signal processing is to view each of $N$ observed $n$-dimensional signal samples as a (noisy) linear combination of at most $k$ elementary waveforms drawn from some unknown ``dictionary" of size $m \ll N$ (see \cite{Zhang15} for a comprehensive review).
@@
 
-Motivated by these discoveries and more recent work relating compressed sensing \cite{eldar2012compressed} to a theory of information transmission through random wiring bottlenecks in the brain \cite{Isely10}, we address when dictionaries for sparse representation are indeed identifiable from data.
+Motivated by these discoveries and more recent work relating compressed sensing \cite{eldar2012compressed} to a theory of information transmission through random wiring bottlenecks in the brain \cite{Isely10}, we address when optimal dictionaries for sparse representation are indeed identifiable from data.
 Answers to this question may also have implications in practice wherever an appeal is made to latent sparse structure of data (e.g., forgery detection \cite{hughes2010, olshausen2010applied}; brain recordings \cite{jung2001imaging, agarwal2014spatially, lee2016sparse}; and gene expression \cite{wu2016stability}).
@@
 Here, we prove very generally that uniqueness and stability is a typical property of sparse dictionary learning.
-More specifically,  we show that dictionaries injective on a sparse domain are identifiable from \mbox{$N = m(k-1){m \choose k} + m$} noisy k-sparse linear combinations of their $m$ columns up to an error that is linear in the noise (Thm.~\ref{DeterministicUniquenessTheorem}).
+More specifically,  we show that dictionaries injective on a sparse domain are identifiable from \mbox{$N = m(k-1){m \choose k} + m$} noisy sparse linear combinations of their columns up to an error that is linear in the noise (Thm.~\ref{DeterministicUniquenessTheorem}).
 In fact, provided $n \geq \min(2k,m)$, in almost all cases the problem is well-posed, as per Hadamard \cite{Hadamard1902}, given a sufficient amount of data (Thm.~\ref{robustPolythm} and Cor.~\ref{ProbabilisticCor}).
@@
 \begin{definition}\label{sip}
-Given $\mathcal{H} \subseteq 2^{[m]}$, the \textbf{star} $\sigma(j)$ is the collection of sets in $\mathcal{H}$ containing $j$.
-We say $\mathcal{H}$ has the \textbf{singleton intersection property} (\textbf{SIP}) when $\cap \sigma(j) = \{j\}$ for all $j \in [m]$.
+Given $\mathcal{H} \subseteq 2^{[m]}$, the \textbf{star} $\sigma(i)$ is the collection of sets in $\mathcal{H}$ containing $i$.
+We say $\mathcal{H}$ has the \textbf{singleton intersection property} (\textbf{SIP}) when $\cap \sigma(j) = \{i\}$ for all $i \in [m]$.
 \end{definition}

### 2019-05-10 manuscripts/IEEE/final_submission.tex
is and js

@@
 Given $\mathcal{H} \subseteq 2^{[m]}$, the \textbf{star} $\sigma(i)$ is the collection of sets in $\mathcal{H}$ containing $i$.
-We say $\mathcal{H}$ has the \textbf{singleton intersection property} (\textbf{SIP}) when $\cap \sigma(j) = \{i\}$ for all $i \in [m]$.
+We say $\mathcal{H}$ has the \textbf{singleton intersection property} (\textbf{SIP}) when $\cap \sigma(i) = \{i\}$ for all $i \in [m]$.
 \end{definition}
@@
 \begin{align}\label{1D}
-\|c_j\mathbf{A}_j - \overline{c}_j\mathbf{B}_{\pi(j)}\|_2 \leq \varepsilon,\ \ \text{for $j \in [m]$}.
-\end{align} 
-Note that $\overline{c}_j \neq 0$, since otherwise we would reach the following contradiction: $\|\mathbf{A}_j \|_2 \leq C_1 |c_j| \|\mathbf{A}_j \|_2  \leq C_1\varepsilon < L_2(\mathbf{A}) \leq L_1(\mathbf{A}) = \min_{j \in [m]} \|\mathbf{A}_{j}\|_2$.
-%implies by \eqref{delrho} the contradiction $|c_j| < \min_{\ell \in [m]} | c_\ell |$.
+\|c_i\mathbf{A}_i - \overline{c}_i\mathbf{B}_{\pi(i)}\|_2 \leq \varepsilon,\ \ \text{for $i \in [m]$}.
+\end{align} 
+Note that $\overline{c}_i \neq 0$, since otherwise we would reach the following contradiction: $\|\mathbf{A}_i \|_2 \leq C_1 |c_i| \|\mathbf{A}_i \|_2  \leq C_1\varepsilon < L_2(\mathbf{A}) \leq L_1(\mathbf{A}) = \min_{i \in [m]} \|\mathbf{A}_{i}\|_2$.
+%implies by \eqref{delrho} the contradiction $|c_i| < \min_{\ell \in [m]} | c_\ell |$.
 
@@
 Suppose that $\pi(i) = \pi(j) = \ell$ for some $i \neq j$ and $\ell$.
-Then, $\|c_{j}\mathbf{A}_{j} - \overline{c}_{j}\mathbf{B}_{\ell}\|_2 \leq \varepsilon$ and $\|c_{i}\mathbf{A}_{i} - \overline{c}_{i} \mathbf{B}_{\ell}\|_2  \leq \varepsilon$, and we have: %Scaling and summing these inequalities by $|\overline{c}_{i}|$ and $|\overline{c}_{j}|$, respectively, and applying the triangle inequality to annihilate the terms in $\mathbf{B}_\ell$, we obtain:
+Then, $\|c_{i}\mathbf{A}_{i} - \overline{c}_{i} \mathbf{B}_{\ell}\|_2  \leq \varepsilon$ and $\|c_{j}\mathbf{A}_{j} - \overline{c}_{j}\mathbf{B}_{\ell}\|_2 \leq \varepsilon$, and we have: %Scaling and summing these inequalities by $|\overline{c}_{i}|$ and $|\overline{c}_{j}|$, respectively, and applying the triangle inequality to annihilate the terms in $\mathbf{B}_\ell$, we obtain:
 \begin{align*}
@@
 &\geq \|\mathbf{A}(\overline{c}_{i}c_{j} \mathbf{e}_{j} - \overline{c}_{j}c_{i}\mathbf{e}_{i})\|_2 \nonumber \\ 
-&\geq  L_2(\mathbf{A}) \|\overline{c}_{i}c_{j} \mathbf{e}_{j} - \overline{c}_{j}c_{i}\mathbf{e}_{i}\|_2 \nonumber \\
+&\geq \sqrt{2}  L_2(\mathbf{A}) \|\overline{c}_{i}c_{j} \mathbf{e}_{j} - \overline{c}_{j}c_{i}\mathbf{e}_{i}\|_2 \nonumber \\
 &\geq  L_2(\mathbf{A}) \left( |\overline{c}_{i}| + |\overline{c}_{j}| \right) \min_{\ell \in [m]} |c_\ell |,
@@
 
-Letting $\mathbf{P}$ and $\mathbf{D}$ be the $\overline m \times \overline m$ permutation and invertible diagonal matrices with, respectively, columns $\mathbf{e}_{\pi(j)}$ and $\frac{\overline{c}_j}{c_j}\mathbf{e}_j$ for $j \in [m]$ (otherwise, $\mathbf{e}_{j}$ for $j \in [\overline{m}] \setminus [m]$), we may rewrite \eqref{1D} to see that for all $j \in [m]$:
+Letting $\mathbf{P}$ and $\mathbf{D}$ be the $\overline m \times \overline m$ permutation and invertible diagonal matrices with, respectively, columns $\mathbf{e}_{\pi(i)}$ and $\frac{\overline{c}_i}{c_i}\mathbf{e}_i$ for $i \in [m]$ (otherwise, $\mathbf{e}_{i}$ for $i \in [\overline{m}] \setminus [m]$), we may rewrite \eqref{1D} to see that for all $i \in [m]$:
 \begin{align*}
-\|\mathbf{A}_j - (\mathbf{BPD})_j\|_2 
-= \|\mathbf{A}_j - \frac{\overline{c}_j}{c_j}\mathbf{B}_{\pi(j)}\|_2 
-\leq \frac{\varepsilon}{|c_j|} 
+\|\mathbf{A}_i - (\mathbf{BPD})_i\|_2 
+= \|\mathbf{A}_i - \frac{\overline{c}_i}{c_i}\mathbf{B}_{\pi(i)}\|_2 
+\leq \frac{\varepsilon}{|c_i|} 
 \leq C_1\varepsilon.
@@
 \begin{align}\label{MainLemmaBPD}
-\|\mathbf{A}_j - (\mathbf{B}\mathbf{PD})_j\|_2 \leq C_2 \varepsilon, \ \  \text{for } j \in J,
+\|\mathbf{A}_i - (\mathbf{B}\mathbf{PD})_i\|_2 \leq C_2 \varepsilon, \ \  \text{for } i \in J,
 \end{align}

### 2019-05-10 manuscripts/IEEE/final_submission.tex
chaz

@@
 While an exponential number of samples may very well prove to be necessary in the deterministic or almost-certain case, our proof of Thm.~\ref{DeterministicUniquenessTheorem} can be extended to hold with some probability for \emph{any} number of samples by alternative appeal to a probabilistic pigeonholing at the point early in the proof where the (deterministic) pigeonhole principle is applied to show that for every $S \in \mathcal{H}$, there exist $k$ vectors $\mathbf{x}_i$ supported on $S$ whose corresponding $\mathbf{\overline x}_i$ all share the same support.\footnote{A famous example of such an argument is the counter-intuitive ``birthday paradox", which demonstrates that the probability of two people having the same birthday in a room of twenty-three is greater than 50\%.}
-
 Given insufficient samples, this argument has some less-than-certain probability of being valid for each $S \in \mathcal{H}$.
@@
 On this last note, we remark that our deterministic treatment considers always the ``worst-case" noise, whereas the ``effective" noise sampled from a concentrated distribution might be significantly reduced, especially for high-dimensional data.
-It would be of great practical benefit to see how drastically all conditions can be relaxed by requiring only probabilistic guarantees in this way, or in the spirit of the discussion on probabilistic pigeonholing for reducing sample complexity (as in the famous ``birthday paradox") following our proof of Thm.~\ref{DeterministicUniquenessTheorem} .
+It would be of great practical benefit to see how drastically all conditions can be relaxed by requiring only probabilistic guarantees in this way, or in the spirit of our discussion on probabilistic pigeonholing to reduce sample complexity (as in the famous ``birthday paradox") following the proof of Thm.~\ref{DeterministicUniquenessTheorem}.
 
@@
 Considering that the sufficient conditions we have described for checking this in general are NP-hard to compute, are the necessary conditions hard?
-Are Probs.~\ref{InverseProblem} and \ref{OptimizationProblem} then also hard \cite{Tillmann15}?
-Finally, since solving Prob.~\ref{SLCopt} directly is intractable in general, but efficiently solvable by $\ell_1$-norm minimization for fixed matrices with large enough lower bounds over sparse domains \cite{eldar2012compressed}, is there a version of Thm.~\ref{SLCopt} certifying when Prob.~\ref{OptimizationProblem} can be solved efficiently in a similar way?
+Are Probs.~\ref{InverseProblem} and \ref{OptimizationProblem} then also hard (e.g., see \cite{Tillmann15})?
+Finally, since Prob.~\ref{SLCopt} is intractable in general, but efficiently solvable by $\ell_1$-norm minimization when the matrix is known (and has a large enough lower bound over sparse domains \cite{eldar2012compressed}), is there a version of Thm.~\ref{SLCopt} certifying when Prob.~\ref{OptimizationProblem} can be solved efficiently in full by similar means?
 % [*** Incorporate this open problem with more words ***]
@@
 
-\textbf{Acknowledgement.} We thank F. Sommer and D. Rhea for early thoughts, and I. Morris for posting \eqref{eqdim} online.
+\textbf{Acknowledgement.} We thank Fritz Sommer and Darren Rhea for early thoughts, and Ian Morris for posting \eqref{eqdim} online.
 

### 2019-05-10 manuscripts/IEEE/final_submission.tex
chaz

@@
 Here, we prove very generally that uniqueness and stability is a typical property of sparse dictionary learning.
-More specifically, we show that matrices injective on a sparse domain are identifiable from \mbox{$N = m(k-1){m \choose k} + m$} noisy linear combinations of $k$ of their $m$ columns up to an error that is linear in the noise (Thm.~\ref{DeterministicUniquenessTheorem}).
+More specifically, we show that matrices injective on a $k$-sparse domain are identifiable from \mbox{$N = m(k-1){m \choose k} + m$} noisy linear combinations of $k$ of their $m$ columns up to an error that is linear in the noise (Thm.~\ref{DeterministicUniquenessTheorem}).
 In fact, provided $n \geq \min(2k,m)$, in almost all cases the problem is well-posed, as per Hadamard \cite{Hadamard1902}, given a sufficient amount of data (Thm.~\ref{robustPolythm} and Cor.~\ref{ProbabilisticCor}).

### 2019-05-10 manuscripts/IEEE/final_submission.tex
fixed

@@
 We begin our proof of Thm.~\ref{DeterministicUniquenessTheorem} by showing how dictionary recovery \eqref{Cstable} already implies sparse code recovery \eqref{b-PDa} when $\mathbf{A}$ satisfies \eqref{SparkCondition} and \mbox{$\varepsilon < L_{2k}\mathbf{A} / C_1$}, assuming that $\overline m = m$ (without loss of generality) so as to omit an otherwise requisite subscript $(\cdot)_J$ around certain matrices and vectors.
-Consider any $2k$-sparse $\mathbf{x} \in \mathbb{R}^m$ and note that $\|\mathbf{x}\|_1 \leq \sqrt{2k}  \|\mathbf{x}\|_2$. By definition of $L_{2k}$ in \eqref{Ldef}, we have:
+By definition of $L_{2k}$ in \eqref{Ldef}, we have for all $i \in [N[$:
 \begin{align}\label{stuff}
-\|\mathbf{x} - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x} \|_1 \nonumber
-&\leq \frac{\|\mathbf{BPD}(\mathbf{x} - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x})\|_2}{L_{2k}(\mathbf{BPD})} \\ \nonumber
-&\leq \frac{\|( \mathbf{BPD} - \mathbf{A}) \mathbf{x}\|_2 + \|\mathbf{A}\mathbf{x} - \mathbf{B}\mathbf{\overline x}\|_2}{L_{2k}(\mathbf{BPD})} \\
-&\leq \frac{C_1\varepsilon \|\mathbf{x}\|_1 + \varepsilon}{L_{2k}(\mathbf{BPD})},
+\|\mathbf{x}_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_i \|_1 \nonumber
+&\leq \frac{\|\mathbf{BPD}(\mathbf{x}_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_i)\|_2}{L_{2k}(\mathbf{BPD})} \\ \nonumber
+&\leq \frac{\|( \mathbf{BPD} - \mathbf{A}) \mathbf{x}_i\|_2 + \|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline x}_i\|_2}{L_{2k}(\mathbf{BPD})} \\
+&\leq \frac{C_1\varepsilon \|\mathbf{x}_i\|_1 + \varepsilon}{L_{2k}(\mathbf{BPD})},
 \end{align}
@@
 %\end{align}
-where the term $C_1\varepsilon \|\mathbf{x}\|_1$ in the numerator above follows from the triangle inequality and \eqref{Cstable}.
-
-It remains for us to bound the denominator.  By the triangle inequality:
+where the term $C_1\varepsilon \|\mathbf{x}_i\|_1$ in the numerator above follows from the triangle inequality and \eqref{Cstable}.
+
+It remains for us to bound the denominator. For any $2k$-sparse $\mathbf{x}$, we have by the triangle inequality:
 \begin{align*}

### 2019-05-10 manuscripts/IEEE/final_submission.tex
missing parentheses

@@
 
-\textbf{Dictionary Recovery:} Fix $\varepsilon < L_{2}(\mathbf{A}) / C_1$.\footnote{Note that the condition $\varepsilon < L_2(\mathbf{A}) /C_1$ is necessary; otherwise, with \mbox{$\mathbf{A}$ = $\mathbf{I}$} (the identity matrix) and $\mathbf{x}_i = \mathbf{e}_i$, the matrix $\mathbf{B} = \left[\mathbf{0}, \frac{1}{2}(\mathbf{e}_1 + \mathbf{e}_2), \mathbf{e}_3, \ldots, \mathbf{e}_{m} \right]$ and sparse codes $\mathbf{\overline x}_i = \mathbf{e}_2$ for $i = 1, 2$ and $\mathbf{\overline x}_i = \mathbf{e}_i$ for $i \geq 3$ satisfy $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline{x}}_i \|_2 \leq \varepsilon$ but nonetheless violate \eqref{Cstable}.} If an $n \times \overline m$ matrix $\mathbf{B}$ has, for every $i \in [N]$, an associated $k$-sparse $\mathbf{\overline x}_i$ satisfying \mbox{$\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \varepsilon$}, then $\overline m \geq m$, and provided that $\overline m (r-1) < mr$, there is a permutation matrix $\mathbf{P}$ and an invertible diagonal matrix $\mathbf{D}$ such that:
+\textbf{Dictionary Recovery:} Fix $\varepsilon < L_{2}(\mathbf{A}) / C_1$.\footnote{Note that the condition $\varepsilon < L_2(\mathbf{A}) /C_1$ is necessary; otherwise, with \mbox{$\mathbf{A}$ = $\mathbf{I}$} (the identity matrix) and $\mathbf{x}_i = \mathbf{e}_i$, the matrix $\mathbf{B} = \left[\mathbf{0}, \frac{1}{2}(\mathbf{e}_1 + \mathbf{e}_2), \mathbf{e}_3, \ldots, \mathbf{e}_{m} \right]$ and sparse codes $\mathbf{\overline x}_i = \mathbf{e}_2$ for $i = 1, 2$ and $\mathbf{\overline x}_i = \mathbf{e}_i$ for $i \geq 3$ satisfy $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline x}_i \|_2 \leq \varepsilon$ but nonetheless violate \eqref{Cstable}.} If an $n \times \overline m$ matrix $\mathbf{B}$ has, for every $i \in [N]$, an associated $k$-sparse $\mathbf{\overline x}_i$ satisfying \mbox{$\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \varepsilon$}, then $\overline m \geq m$, and provided that $\overline m (r-1) < mr$, there is a permutation matrix $\mathbf{P}$ and an invertible diagonal matrix $\mathbf{D}$ such that:
 \begin{align}\label{Cstable}
@@
 % WITHOUT J SUBSCRIPT
-We begin our proof of Thm.~\ref{DeterministicUniquenessTheorem} by showing how dictionary recovery \eqref{Cstable} already implies sparse code recovery \eqref{b-PDa} when $\mathbf{A}$ satisfies \eqref{SparkCondition} and \mbox{$\varepsilon < L_{2k}\mathbf{A} / C_1$}, assuming that $\overline m = m$ (without loss of generality) so as to omit an otherwise requisite subscript $(\cdot)_J$ around certain matrices and vectors.
+We begin our proof of Thm.~\ref{DeterministicUniquenessTheorem} by showing how dictionary recovery \eqref{Cstable} already implies sparse code recovery \eqref{b-PDa} when $\mathbf{A}$ satisfies \eqref{SparkCondition} and \mbox{$\varepsilon < L_{2k}(\mathbf{A}) / C_1$}, assuming that $\overline m = m$ (without loss of generality) so as to omit an otherwise requisite subscript $(\cdot)_J$ around certain matrices and vectors.
 By definition of $L_{2k}$ in \eqref{Ldef}, we have for all $i \in [N[$:

### 2019-05-10 manuscripts/IEEE/final_submission.tex
edits

@@
 \begin{corollary}\label{ProbabilisticCor}
-If indeterminate entries of $\mathbf{A}$ and the $\mathbf{x}_i$ are drawn independently from probability distributions absolutely continuous with respect to the standard Borel measure, then $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$ with probability one.
+If the indeterminate entries of $\mathbf{A}$ and the $\mathbf{x}_i$ are drawn independently from probability distributions absolutely continuous with respect to the standard Borel measure, then $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$ with probability one.
 \end{corollary}

### 2019-05-10 manuscripts/IEEE/final_submission.tex
chaz edits today

@@
 \begin{abstract}
-Learning optimal dictionaries for sparse coding has exposed characteristic sparse features of many natural signals.
-However, there are few universal conditions guaranteeing the stability of such features in the presence of measurement noise.
+%Learning optimal dictionaries for sparse coding has exposed characteristic sparse features of many natural signals.
+However, there are few universal conditions guaranteeing the stability of such features in the presence of noise.
 Here, we prove very generally that optimal dictionaries and sparse codes are unique up to measurement error for all diverse enough datasets generated by the sparse coding model.
 Applications are given to data analysis, engineering, and neuroscience.
+Learning optimal dictionaries for sparse coding has exposed characteristic sparse features of many natural signals.
+However, universal guarantees of the stability of such features in the presence of noise are lacking.
+Here, we provide very general conditions guaranteeing when dictionaries yielding the sparsest encodings are unique and stable with respect to measurement or modeling error.
+We demonstrate that some or all dictionary elements are recoverable from noisy data even if the dictionary fails to satisfy the spark condition, its size is overestimated, or it induces only polynomial number of distinct sparse supports for the data.
+Importantly, we derive these guarantees without requiring any constraints on the recovered dictionary beyond a natural upper bound on its size.
+Our results yield an effective procedure sufficient to affirm if a proposed solution to the dictionary learning problem is unique within bounds commensurate with the noise.
+We suggest applications to data analysis, engineering, and neuroscience and close with some remaining challenges left open by our work.
 \end{abstract}
@@
 \section{Introduction}\label{Intro}
-\IEEEPARstart{A}{}common modern approach to pattern analysis in signal processing is to view each of $N$ observed $n$-dimensional signal samples as a (noisy) linear combination of at most $k$ elementary waveforms drawn from some unknown ``dictionary" of size $m \ll N$ (see \cite{Zhang15} for a comprehensive review).
+\IEEEPARstart{S}{parse} coding is a common modern approach to pattern analysis in signal processing whereby each of $N$ observed $n$-dimensional signal samples is viewed as a (noisy) linear combination of at most $k$ elementary waveforms drawn from some unknown ``dictionary" of size $m \ll N$ (see \cite{Zhang15} for a comprehensive review).
+%\IEEEPARstart{A}{}common modern approach to pattern analysis in signal processing is to view each of $N$ observed $n$-dimensional signal samples as a (noisy) linear combination of at most $k$ elementary waveforms drawn from some unknown ``dictionary" of size $m \ll N$ (see \cite{Zhang15} for a comprehensive review).
 Optimizing dictionaries subject to this and related sparsity constraints has revealed seemingly characteristic sparse structure in several signal classes of current interest (e.g., in vision \cite{wang2015sparse}).
@@
 Of particular note are the seminal works in the field \cite{Olshausen96, hurri1996image, bell1997independent, van1998independent}, which discovered that dictionaries optimized for coding small patches of ``natural" images share qualitative similarities with linear filters estimated from response properties of simple-cell neurons in mammalian visual cortex.
-Curiously, these waveforms (e.g., ``Gabor'' wavelets) appear in dictionaries learned by a variety of algorithms trained over different natural image datasets; in particular, sparse coding of  latent features in natural signals may, in some sense, be canonical \cite{donoho2001can}.
+Curiously, these waveforms (e.g., ``Gabor'' wavelets) appear in dictionaries learned by a variety of algorithms trained over different natural image datasets, suggesting these learned features in natural signals may, in some sense, be canonical \cite{donoho2001can}.
 
@@
 While several algorithms have been recently proposed to provably recover unique dictionaries under specific conditions (see \cite[Sec.~I-E]{Sun16} for a summary of the state-of-the-art), few theorems can be invoked to justify the consistency of inference under this model of data more broadly.
-To our knowledge, a universal guarantee of the uniqueness and stability of learned dictionaries and the sparse representations they induce when data has deterministic noise has yet to appear in the literature.
+To our knowledge, a universal guarantee of the uniqueness and stability of learned dictionaries and the sparse representations they induce over noisy data has yet to appear in the literature.
 % in justifying the identification of forged paintings by their anomalous sparse representations \cite{hughes2010},
@@
 Here, we prove very generally that uniqueness and stability is a typical property of sparse dictionary learning.
-More specifically, we show that matrices injective on a $k$-sparse domain are identifiable from \mbox{$N = m(k-1){m \choose k} + m$} noisy linear combinations of $k$ of their $m$ columns up to an error that is linear in the noise (Thm.~\ref{DeterministicUniquenessTheorem}).
+More specifically, we show that matrices injective on a sparse domain are identifiable from \mbox{$N = m(k-1){m \choose k} + m$} noisy linear combinations of $k$ of their $m$ columns up to an error that is linear in the noise (Thm.~\ref{DeterministicUniquenessTheorem}).
 In fact, provided $n \geq \min(2k,m)$, in almost all cases the problem is well-posed, as per Hadamard \cite{Hadamard1902}, given a sufficient amount of data (Thm.~\ref{robustPolythm} and Cor.~\ref{ProbabilisticCor}).
@@
 \cite{rehnsommer2007}) optimization problem seeking a dictionary minimizing the average number of elementary waveforms required to reconstruct each sample of the dataset (Thm.~\ref{SLCopt}).
-Importantly, we never make assumptions on learned dictionaries (e.g., that they, too, be injective over some domain) beyond an upper bound on dictionary size, which is necessary to avoid trivial solutions (e.g., allowing $m = N$).
+To practical benefit, our results impose no restrictions on learned dictionaries (e.g., that they, too, be injective over some sparse domain) beyond an upper bound on dictionary size, which is necessary in any case to avoid trivial solutions (e.g., allowing $m = N$).
 %That is, every pair of solutions of comparable size has some number of dictionary elements in common (up to noise), and similarly so for the coefficients of sparse codes they induce.
@@
 Note that every solution to Prob.~\ref{InverseProblem} represents infinitely many equivalent alternatives $\mathbf{BPD}$ and $\mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_1, \ldots, \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_N$ parametrized by a choice of permutation matrix $\mathbf{P}$ and invertible diagonal matrix $\mathbf{D}$.
-Identifying these ambiguities (labelling and scale) yields a set of elementary waveforms (the columns of $\mathbf{B}$) and their associated sparse coefficients (the entries of $\mathbf{\overline x}_i$) for reconstructing each data point $\mathbf{z}_i$.
+Identifying these ambiguities (labelling and scale) yields a set of elementary waveforms (the columns of $\mathbf{B}$) and their associated sparse coefficients (the entries of $\mathbf{\overline x}_i$) for approximating each data point $\mathbf{z}_i$.
 
@@
 %
-which in any case is necessary to guarantee the uniqueness of arbitrary $k$-sparse $\mathbf{x}_i$.
+which is necessary to guarantee the uniqueness of arbitrary $k$-sparse $\mathbf{x}_i$.
 We generalize these results to the practical setting  $\eta > 0$ by considering the following natural notion of stability with respect to measurement error.
@@
 The main result of this work is a very general uniqueness theorem for sparse coding (Thm.~\ref{DeterministicUniquenessTheorem}) directly 
-implying (Cor.~\ref{DeterministicUniquenessCorollary}) that stable representations of a dataset $Z$ are guaranteed whenever generating dictionaries $\mathbf{A}$ satisfy a spark condition on supports and the original sparse codes $\mathbf{x}_i$ are sufficiently diverse (e.g., Fig.~\ref{noisyrecovery}).
+implying (Cor.~\ref{DeterministicUniquenessCorollary}), which guarantees that sparse representations of a dataset $Z$ are unique up to noise whenever generating dictionaries $\mathbf{A}$ satisfy a spark condition on supports and the original sparse codes $\mathbf{x}_i$ are sufficiently diverse (e.g., Fig.~\ref{noisyrecovery}).
 Moreover, we provide an explicit, computable $\varepsilon(\delta_1, \delta_2)$ in (\ref{epsdel}) that is linear in desired accuracy $\delta_1, \delta_2$.
@@
 We also give brief arguments adapting our results to dictionaries and codes drawn from probability distributions (Cor.~\ref{ProbabilisticCor}).
-The technical proofs of Thms.~\ref{DeterministicUniquenessTheorem} and ~\ref{SLCopt} are deferred to Sec.~\ref{DUT}, following some necessary definitions and a fact in combinatorial matrix analysis (Lem.~\ref{MainLemma}; proved in the Appendix).
+The technical proofs of Thms.~\ref{DeterministicUniquenessTheorem} and ~\ref{SLCopt} are deferred to Sec.~\ref{DUT}, following some necessary definitions and a fact in combinatorial matrix analysis (Lem.~\ref{MainLemma}; proven in the Appendix).
 Finally, we discuss in Sec.~\ref{Discussion} applications of our mathematical observations as well as open questions.
@@
 %To be clear, the implication of Thm.~\ref{DeterministicUniquenessTheorem} is that $Y = \{\mathbf{Ax}_1, \ldots, \mathbf{Ax}_N\}$ has a stable $k$-sparse representation in $\mathbb{R}^m$, with \eqref{def1} guaranteed provided $\varepsilon$ in Def.~\ref{maindef} does not exceed:
-In words, Thm.~\ref{DeterministicUniquenessTheorem} says that the smaller the regularity $r$ of original support hypergraph $\mathcal{H}$ or the difference $\overline m - m$ between assumed and actual number of elements in the latent dictionary, the more columns and coefficients of the original dictionary $\mathbf{A}$ and sparse codes $\mathbf{x}_i$ are guaranteed to be contained (up to noise) in the appropriately labelled and scaled recovered dictionary $\mathbf{B}$ and codes $\mathbf{\overline x}_i$, respectively.
+In words, Thm.~\ref{DeterministicUniquenessTheorem} says that the smaller the regularity $r$ of the original support hypergraph $\mathcal{H}$ or the difference $\overline m - m$ between the assumed and actual number of elements in the latent dictionary, the more columns and coefficients of the original dictionary $\mathbf{A}$ and sparse codes $\mathbf{x}_i$ are guaranteed to be contained (up to noise) in the appropriately labelled and scaled recovered dictionary $\mathbf{B}$ and codes $\mathbf{\overline x}_i$, respectively.
 
@@
 As an example, let $\mathbf{A} = [ \mathbf{e}_1, \ldots, \mathbf{e}_5, \mathbf{v}]$ with $\mathbf{v} = \mathbf{e}_1 + \mathbf{e}_3 + \mathbf{e}_5$ and take $\mathcal{H}$ to be all consecutive pairs of indices $1, \ldots ,6$ arranged in cyclic order.
-Then for $k=2$, the matrix $\mathbf{A}$ fails to satisfy \eqref{SparkCondition} while still obeying the first set of assumptions in Thm.~\ref{DeterministicUniquenessTheorem}.%, hence guaranteeing \eqref{Cstable} .
+Then for $k=2$, the matrix $\mathbf{A}$ fails to satisfy \eqref{SparkCondition} while still obeying the assumptions of Thm.~\ref{DeterministicUniquenessTheorem} for dictionary recovery.%, hence guaranteeing \eqref{Cstable} .
 %(since $\{ \mathbf{A}_1, \mathbf{A}_3, \mathbf{A}_5, \mathbf{A}_6\}$ is not a linearly independent set).
@@
 Since $f$ is analytic, having a single substitution of a real matrix $\mathbf{A}$ satisfying $f(\mathbf{A}) \neq 0$ implies that the zeroes of $f$ form a set of (Borel) measure zero.
-Such a matrix is easily constructed by adding rows of zeroes to a $\min(2k,m) \times m$ Vandermonde matrix as described previously, so that every sum in the product defining $f$ above is strictly positive.
+Such a matrix is easily constructed by adding rows of zeroes to a $\min(2k,m) \times m$ Vandermonde matrix as mentioned previously, so that every sum in the product defining $f$ above is strictly positive.
 Thus, almost every $n \times m$ matrix with $n \geq \min(2k,m)$ satisfies \eqref{SparkCondition}.
@@
 Briefly, following the same procedure as in \cite[Sec.~IV]{Hillar15}, for $k < m$ and $n \geq \min(2k, m)$, we may consider the ``symbolic'' dataset $Y = \{\mathbf{A}\mathbf{x}_1,\ldots,\mathbf{A} \mathbf{x}_N\}$ generated by an indeterminate $n \times m$ matrix $\mathbf{A}$ and $m$-dimensional $k$-sparse vectors $\mathbf{x}_1, \ldots, \mathbf{x}_N$ indeterminate within their supports, which form a regular hypergraph $\mathcal{H} \subseteq {[m] \choose k}$ satisfying the SIP.
-Restricting \mbox{$(k-1){m \choose k} + 1$} indeterminate $\mathbf{x}_i$ to each support in $\mathcal{H}$, and letting $\textbf{M}$ be the $n \times N$ matrix with columns $\mathbf{A}\mathbf{x}_i$, it can be checked that when $f(\mathbf{M}) \neq 0$ for a substitution of real numbers for the indeterminates, all of the assumptions on $\mathbf{A}$ and $\mathbf{x}_i$ in Thm.~\ref{DeterministicUniquenessTheorem} are satisfied.
+Restricting \mbox{$(k-1){m \choose k} + 1$} indeterminate $\mathbf{x}_i$ to each support in $\mathcal{H}$, and letting $\textbf{M}$ be the $n \times N$ matrix with columns $\mathbf{A}\mathbf{x}_i$, it can be checked that when $f(\mathbf{M}) \neq 0$ for a substitution of real numbers for the indeterminates, all of the assumptions on $\mathbf{A}$ and the $\mathbf{x}_i$ in Thm.~\ref{DeterministicUniquenessTheorem} are satisfied.
 We therefore have the following.
@@
 
-To extend this observation to arbitrary probability distributions, note that if a set of measure spaces $\{(X_{\ell}, \nu_{\ell})\}_{\ell=1}^p$ has measures $\nu_{\ell}$ absolutely continuous with respect to the standard Borel measure on $\mathbb{R}$ for all $\ell \in [p]$, then the product measure $\prod_{\ell=1}^p \nu_{\ell}$ is also absolutely continuous with respect to the standard Borel product measure on $\mathbb{R}^p$ (e.g., see \cite{folland2013real}).
+%To extend this observation to arbitrary probability distributions, note that if a set of measure spaces $\{(X_{\ell}, \nu_{\ell})\}_{\ell=1}^p$ has measures $\nu_{\ell}$ absolutely continuous with respect to the standard Borel measure on $\mathbb{R}$ for all $\ell \in [p]$, then the product measure $\prod_{\ell=1}^p \nu_{\ell}$ is also absolutely continuous with respect to the standard Borel product measure on $\mathbb{R}^p$ (e.g., see \cite{folland2013real}).
 This fact combined with Thm.~\ref{robustPolythm} implies the following.
+To extend this observation to arbitrary probability distributions, note that if a set of $p$ measure spaces has all measures absolutely continuous with respect to the standard Borel measure on $\mathbb{R}$, then the product measure is also absolutely continuous with respect to the standard Borel product measure on $\mathbb{R}^p$ (e.g., see \cite{folland2013real}).
+This fact combined with Thm.~\ref{robustPolythm} implies the following.\footnote{We refer the reader to \cite{Hillar15} for a detailed explanation of these arguments.}
 
@@
 Our results demonstrate that sparse codes $\mathbf{x}_i$ drawn from only a polynomial number of $k$-dimensional subspaces permit stable identification of the generating dictionary $\mathbf{A}$. 
-
 This lends some legitimacy to the use of the model in practice, where data in general are unlikely (if ever) to exhibit the exponentially many possible $k$-wise combinations of dictionary elements required by (to our knowledge) all previously published results.
+
 Consequently, if $k$ is held fixed or if the size of the support set of reconstructing codes is polynomial in $\overline m$ and $k$, then a practical (polynomial) amount of data suffices to identify the dictionary.\footnote{In the latter case, a reexamination of the pigeonholing argument in the proof of Thm.~\ref{DeterministicUniquenessTheorem} requires a polynomial number of samples distributed over a polynomial number of supports.} Reasons to be skeptical that this holds in general, however, can be found in \cite{tillmann2014computational, Tillmann15}.
@@
 % WITHOUT J SUBSCRIPT
-We begin our proof of Thm.~\ref{DeterministicUniquenessTheorem} by showing how dictionary recovery \eqref{Cstable} already implies sparse code recovery \eqref{b-PDa} when $\mathbf{A}$ satisfies \eqref{SparkCondition} and \mbox{$\varepsilon < L_{2k}(\mathbf{A}) / C_1$}, assuming that $\overline m = m$ (without loss of generality) so as to omit an otherwise requisite subscript $(\cdot)_J$ around certain matrices and vectors.
-By definition of $L_{2k}$ in \eqref{Ldef}, we have for all $i \in [N[$:
+We begin our proof of Thm.~\ref{DeterministicUniquenessTheorem} by showing how dictionary recovery \eqref{Cstable} already implies sparse code recovery \eqref{b-PDa} when $\mathbf{A}$ satisfies \eqref{SparkCondition} and \mbox{$\varepsilon < L_{2k}(\mathbf{A}) / C_1$}.
+We temporarily assume (without loss of generality) that $\overline m = m$, so as to omit an otherwise requisite subscript $(\cdot)_J$ around certain matrices and vectors.
+By definition of $L_{2k}$ in \eqref{Ldef}, and noting that $\sqrt{k} \|\mathbf{v}\|_2 \geq \|\mathbf{v}\|_1$ for $k$-sparse $\mathbf{v}$, we have for all $i \in [N[$:
 \begin{align}\label{stuff}
@@
 %\end{align}
-where the term $C_1\varepsilon \|\mathbf{x}_i\|_1$ in the numerator above follows from the triangle inequality and \eqref{Cstable}.
+where the first term in the numerator above follows from the triangle inequality and \eqref{Cstable}.
 
@@
 \begin{lemma}\label{MainLemma}
-Suppose the $n \times m$ matrix $\mathbf{A}$ has $L_{2\mathcal{H}}(\mathbf{A}) > 0$ for some $r$-regular $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP.
-There exists $C_2 > 0$ for which the following holds for all $\varepsilon < L_2(\mathbf{A}) / C_2$:
-
-If for some $n \times \overline m$ matrix $\mathbf{B}$ and map $\pi: \mathcal{H} \mapsto {[\overline m] \choose k}$,
+If an $n \times m$ matrix $\mathbf{A}$ has $L_{2\mathcal{H}}(\mathbf{A}) > 0$ for some $r$-regular $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP, then the following holds for $C_2 > 0$ given by \eqref{Cdef2}:
+
+Fix $\varepsilon < L_2(\mathbf{A}) / C_2$. If for some $n \times \overline m$ matrix $\mathbf{B}$ and map $\pi: \mathcal{H} \mapsto {[\overline m] \choose k}$,
 \begin{align}\label{GapUpperBound}
@@
 
-Before moving on to our proof of Thm.~\ref{SLCopt}, we briefly revisit here our discussion on sample complexity from the end of the previous section.
+Before moving on to our proof of Thm.~\ref{SLCopt}, we briefly revisit our discussion on sample complexity from the end of the previous section.
 While an exponential number of samples may very well prove to be necessary in the deterministic or almost-certain case, our proof of Thm.~\ref{DeterministicUniquenessTheorem} can be extended to hold with some probability for \emph{any} number of samples by alternative appeal to a probabilistic pigeonholing at the point early in the proof where the (deterministic) pigeonhole principle is applied to show that for every $S \in \mathcal{H}$, there exist $k$ vectors $\mathbf{x}_i$ supported on $S$ whose corresponding $\mathbf{\overline x}_i$ all share the same support.\footnote{A famous example of such an argument is the counter-intuitive ``birthday paradox", which demonstrates that the probability of two people having the same birthday in a room of twenty-three is greater than 50\%.}

### 2019-05-10 manuscripts/IEEE/final_submission.tex
premerge

--- 2019-05-10 manuscripts/IEEE/final_submission.tex
@@
 Note that every solution to Prob.~\ref{InverseProblem} represents infinitely many equivalent alternatives $\mathbf{BPD}$ and $\mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_1, \ldots, \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_N$ parametrized by a choice of permutation matrix $\mathbf{P}$ and invertible diagonal matrix $\mathbf{D}$.
-Identifying these ambiguities (labelling and scale) yields a set of elementary waveforms (the columns of $\mathbf{B}$) and their associated sparse coefficients (the entries of $\mathbf{\overline x}_i$) for reconstructing each data point $\mathbf{z}_i$.
+Identifying these ambiguities (labelling and scale) yields an orbit 
+represented by a particular set of elementary waveforms (the columns of $\mathbf{B}$) and their associated sparse coefficients (the entries of $\mathbf{\overline x}_i$) for reconstructing each data point $\mathbf{z}_i$.
 
@@
 \begin{definition}\label{sip}
-Given $\mathcal{H} \subseteq 2^{[m]}$, the \textbf{star} $\sigma(i)$ is the collection of sets in $\mathcal{H}$ containing $i$.
-We say $\mathcal{H}$ has the \textbf{singleton intersection property} (\textbf{SIP}) when $\cap \sigma(i) = \{i\}$ for all $i \in [m]$.
+Given $\mathcal{H} \subseteq 2^{[m]}$, the \textbf{star} $\sigma(j)$ is the collection of sets in $\mathcal{H}$ containing $j$.
+We say $\mathcal{H}$ has the \textbf{singleton intersection property} (\textbf{SIP}) when $\cap \sigma(j) = \{j\}$ for all $j \in [m]$.
 \end{definition}
@@
 
-\textbf{Dictionary Recovery:} Fix $\varepsilon < L_{2}(\mathbf{A}) / C_1$.\footnote{Note that the condition $\varepsilon < L_2(\mathbf{A}) /C_1$ is necessary; otherwise, with \mbox{$\mathbf{A}$ = $\mathbf{I}$} (the identity matrix) and $\mathbf{x}_i = \mathbf{e}_i$, the matrix $\mathbf{B} = \left[\mathbf{0}, \frac{1}{2}(\mathbf{e}_1 + \mathbf{e}_2), \mathbf{e}_3, \ldots, \mathbf{e}_{m} \right]$ and sparse codes $\mathbf{\overline x}_i = \mathbf{e}_2$ for $i = 1, 2$ and $\mathbf{\overline x}_i = \mathbf{e}_i$ for $i \geq 3$ satisfy $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline x}_i \|_2 \leq \varepsilon$ but nonetheless violate \eqref{Cstable}.} If an $n \times \overline m$ matrix $\mathbf{B}$ has, for every $i \in [N]$, an associated $k$-sparse $\mathbf{\overline x}_i$ satisfying \mbox{$\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \varepsilon$}, then $\overline m \geq m$, and provided that $\overline m (r-1) < mr$, there is a permutation matrix $\mathbf{P}$ and an invertible diagonal matrix $\mathbf{D}$ such that:
+\textbf{Dictionary Recovery:} Fix $\varepsilon < L_{2}(\mathbf{A}) / C_1$.\footnote{Note that the condition $\varepsilon < L_2(\mathbf{A}) /C_1$ is necessary; otherwise, with \mbox{$\mathbf{A}$ = $\mathbf{I}$} (the identity matrix) and $\mathbf{x}_i = \mathbf{e}_i$, the matrix $\mathbf{B} = \left[\mathbf{0}, \frac{1}{2}(\mathbf{e}_1 + \mathbf{e}_2), \mathbf{e}_3, \ldots, \mathbf{e}_{m} \right]$ and sparse codes $\mathbf{\overline x}_i = \mathbf{e}_2$ for $i = 1, 2$ and $\mathbf{\overline x}_i = \mathbf{e}_i$ for $i \geq 3$ satisfy $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline{x}}_i \|_2 \leq \varepsilon$ but nonetheless violate \eqref{Cstable}.} If an $n \times \overline m$ matrix $\mathbf{B}$ has, for every $i \in [N]$, an associated $k$-sparse $\mathbf{\overline x}_i$ satisfying \mbox{$\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \varepsilon$}, then $\overline m \geq m$, and provided that $\overline m (r-1) < mr$, there is a permutation matrix $\mathbf{P}$ and an invertible diagonal matrix $\mathbf{D}$ such that:
 \begin{align}\label{Cstable}
@@
 % WITHOUT J SUBSCRIPT
-We begin our proof of Thm.~\ref{DeterministicUniquenessTheorem} by showing how dictionary recovery \eqref{Cstable} already implies sparse code recovery \eqref{b-PDa} when $\mathbf{A}$ satisfies \eqref{SparkCondition} and \mbox{$\varepsilon < L_{2k}(\mathbf{A}) / C_1$}, assuming that $\overline m = m$ (without loss of generality) so as to omit an otherwise requisite subscript $(\cdot)_J$ around certain matrices and vectors.
-By definition of $L_{2k}$ in \eqref{Ldef}, we have for all $i \in [N[$:
+We begin our proof of Thm.~\ref{DeterministicUniquenessTheorem} by showing how dictionary recovery \eqref{Cstable} already implies sparse code recovery \eqref{b-PDa} when $\mathbf{A}$ satisfies \eqref{SparkCondition} and \mbox{$\varepsilon < L_{2k}\mathbf{A} / C_1$}, assuming that $\overline m = m$ (without loss of generality) so as to omit an otherwise requisite subscript $(\cdot)_J$ around certain matrices and vectors.
+Consider any $2k$-sparse $\mathbf{x} \in \mathbb{R}^m$ and note that $\|\mathbf{x}\|_1 \leq \sqrt{2k}  \|\mathbf{x}\|_2$. By definition of $L_{2k}$ in \eqref{Ldef}, we have:
 \begin{align}\label{stuff}
-\|\mathbf{x}_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_i \|_1 \nonumber
-&\leq \frac{\|\mathbf{BPD}(\mathbf{x}_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_i)\|_2}{L_{2k}(\mathbf{BPD})} \\ \nonumber
-&\leq \frac{\|( \mathbf{BPD} - \mathbf{A}) \mathbf{x}_i\|_2 + \|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline x}_i\|_2}{L_{2k}(\mathbf{BPD})} \\
-&\leq \frac{C_1\varepsilon \|\mathbf{x}_i\|_1 + \varepsilon}{L_{2k}(\mathbf{BPD})},
+\|\mathbf{x} - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x} \|_1 \nonumber
+&\leq \frac{\|\mathbf{BPD}(\mathbf{x} - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x})\|_2}{L_{2k}(\mathbf{BPD})} \\ \nonumber
+&\leq \frac{\|( \mathbf{BPD} - \mathbf{A}) \mathbf{x}\|_2 + \|\mathbf{A}\mathbf{x} - \mathbf{B}\mathbf{\overline x}\|_2}{L_{2k}(\mathbf{BPD})} \\
+&\leq \frac{C_1\varepsilon \|\mathbf{x}\|_1 + \varepsilon}{L_{2k}(\mathbf{BPD})},
 \end{align}
@@
 %\end{align}
-where the term $C_1\varepsilon \|\mathbf{x}_i\|_1$ in the numerator above follows from the triangle inequality and \eqref{Cstable}.
-
-It remains for us to bound the denominator. For any $2k$-sparse $\mathbf{x}$, we have by the triangle inequality:
+where the term $C_1\varepsilon \|\mathbf{x}\|_1$ in the numerator above follows from the triangle inequality and \eqref{Cstable}.
+
+It remains for us to bound the denominator.  By the triangle inequality:
 \begin{align*}
@@
 \begin{align}\label{1D}
-\|c_i\mathbf{A}_i - \overline{c}_i\mathbf{B}_{\pi(i)}\|_2 \leq \varepsilon,\ \ \text{for $i \in [m]$}.
-\end{align} 
-Note that $\overline{c}_i \neq 0$, since otherwise we would reach the following contradiction: $\|\mathbf{A}_i \|_2 \leq C_1 |c_i| \|\mathbf{A}_i \|_2  \leq C_1\varepsilon < L_2(\mathbf{A}) \leq L_1(\mathbf{A}) = \min_{i \in [m]} \|\mathbf{A}_{i}\|_2$.
-%implies by \eqref{delrho} the contradiction $|c_i| < \min_{\ell \in [m]} | c_\ell |$.
+\|c_j\mathbf{A}_j - \overline{c}_j\mathbf{B}_{\pi(j)}\|_2 \leq \varepsilon,\ \ \text{for $j \in [m]$}.
+\end{align} 
+Note that $\overline{c}_j \neq 0$, since otherwise we would reach the following contradiction: $\|\mathbf{A}_j \|_2 \leq C_1 |c_j| \|\mathbf{A}_j \|_2  \leq C_1\varepsilon < L_2(\mathbf{A}) \leq L_1(\mathbf{A}) = \min_{j \in [m]} \|\mathbf{A}_{j}\|_2$.
+%implies by \eqref{delrho} the contradiction $|c_j| < \min_{\ell \in [m]} | c_\ell |$.
 
@@
 Suppose that $\pi(i) = \pi(j) = \ell$ for some $i \neq j$ and $\ell$.
-Then, $\|c_{i}\mathbf{A}_{i} - \overline{c}_{i} \mathbf{B}_{\ell}\|_2  \leq \varepsilon$ and $\|c_{j}\mathbf{A}_{j} - \overline{c}_{j}\mathbf{B}_{\ell}\|_2 \leq \varepsilon$, and we have: %Scaling and summing these inequalities by $|\overline{c}_{i}|$ and $|\overline{c}_{j}|$, respectively, and applying the triangle inequality to annihilate the terms in $\mathbf{B}_\ell$, we obtain:
+Then, $\|c_{j}\mathbf{A}_{j} - \overline{c}_{j}\mathbf{B}_{\ell}\|_2 \leq \varepsilon$ and $\|c_{i}\mathbf{A}_{i} - \overline{c}_{i} \mathbf{B}_{\ell}\|_2  \leq \varepsilon$, and we have: %Scaling and summing these inequalities by $|\overline{c}_{i}|$ and $|\overline{c}_{j}|$, respectively, and applying the triangle inequality to annihilate the terms in $\mathbf{B}_\ell$, we obtain:
 \begin{align*}
@@
 &\geq \|\mathbf{A}(\overline{c}_{i}c_{j} \mathbf{e}_{j} - \overline{c}_{j}c_{i}\mathbf{e}_{i})\|_2 \nonumber \\ 
-&\geq \sqrt{2}  L_2(\mathbf{A}) \|\overline{c}_{i}c_{j} \mathbf{e}_{j} - \overline{c}_{j}c_{i}\mathbf{e}_{i}\|_2 \nonumber \\
+&\geq  L_2(\mathbf{A}) \|\overline{c}_{i}c_{j} \mathbf{e}_{j} - \overline{c}_{j}c_{i}\mathbf{e}_{i}\|_2 \nonumber \\
 &\geq  L_2(\mathbf{A}) \left( |\overline{c}_{i}| + |\overline{c}_{j}| \right) \min_{\ell \in [m]} |c_\ell |,
@@
 
-Letting $\mathbf{P}$ and $\mathbf{D}$ be the $\overline m \times \overline m$ permutation and invertible diagonal matrices with, respectively, columns $\mathbf{e}_{\pi(i)}$ and $\frac{\overline{c}_i}{c_i}\mathbf{e}_i$ for $i \in [m]$ (otherwise, $\mathbf{e}_{i}$ for $i \in [\overline{m}] \setminus [m]$), we may rewrite \eqref{1D} to see that for all $i \in [m]$:
+Letting $\mathbf{P}$ and $\mathbf{D}$ be the $\overline m \times \overline m$ permutation and invertible diagonal matrices with, respectively, columns $\mathbf{e}_{\pi(j)}$ and $\frac{\overline{c}_j}{c_j}\mathbf{e}_j$ for $j \in [m]$ (otherwise, $\mathbf{e}_{j}$ for $j \in [\overline{m}] \setminus [m]$), we may rewrite \eqref{1D} to see that for all $j \in [m]$:
 \begin{align*}
-\|\mathbf{A}_i - (\mathbf{BPD})_i\|_2 
-= \|\mathbf{A}_i - \frac{\overline{c}_i}{c_i}\mathbf{B}_{\pi(i)}\|_2 
-\leq \frac{\varepsilon}{|c_i|} 
+\|\mathbf{A}_j - (\mathbf{BPD})_j\|_2 
+= \|\mathbf{A}_j - \frac{\overline{c}_j}{c_j}\mathbf{B}_{\pi(j)}\|_2 
+\leq \frac{\varepsilon}{|c_j|} 
 \leq C_1\varepsilon.
@@
 \begin{align}\label{MainLemmaBPD}
-\|\mathbf{A}_i - (\mathbf{B}\mathbf{PD})_i\|_2 \leq C_2 \varepsilon, \ \  \text{for } i \in J,
+\|\mathbf{A}_j - (\mathbf{B}\mathbf{PD})_j\|_2 \leq C_2 \varepsilon, \ \  \text{for } j \in J,
 \end{align}
@@
 While an exponential number of samples may very well prove to be necessary in the deterministic or almost-certain case, our proof of Thm.~\ref{DeterministicUniquenessTheorem} can be extended to hold with some probability for \emph{any} number of samples by alternative appeal to a probabilistic pigeonholing at the point early in the proof where the (deterministic) pigeonhole principle is applied to show that for every $S \in \mathcal{H}$, there exist $k$ vectors $\mathbf{x}_i$ supported on $S$ whose corresponding $\mathbf{\overline x}_i$ all share the same support.\footnote{A famous example of such an argument is the counter-intuitive ``birthday paradox", which demonstrates that the probability of two people having the same birthday in a room of twenty-three is greater than 50\%.}
+
 Given insufficient samples, this argument has some less-than-certain probability of being valid for each $S \in \mathcal{H}$.
@@
 On this last note, we remark that our deterministic treatment considers always the ``worst-case" noise, whereas the ``effective" noise sampled from a concentrated distribution might be significantly reduced, especially for high-dimensional data.
-It would be of great practical benefit to see how drastically all conditions can be relaxed by requiring only probabilistic guarantees in this way, or in the spirit of our discussion on probabilistic pigeonholing to reduce sample complexity (as in the famous ``birthday paradox") following the proof of Thm.~\ref{DeterministicUniquenessTheorem}.
+It would be of great practical benefit to see how drastically all conditions can be relaxed by requiring only probabilistic guarantees in this way, or in the spirit of the discussion on probabilistic pigeonholing for reducing sample complexity (as in the famous ``birthday paradox") following our proof of Thm.~\ref{DeterministicUniquenessTheorem} .
 
@@
 Considering that the sufficient conditions we have described for checking this in general are NP-hard to compute, are the necessary conditions hard?
-Are Probs.~\ref{InverseProblem} and \ref{OptimizationProblem} then also hard (e.g., see \cite{Tillmann15})?
-Finally, since Prob.~\ref{SLCopt} is intractable in general, but efficiently solvable by $\ell_1$-norm minimization when the matrix is known (and has a large enough lower bound over sparse domains \cite{eldar2012compressed}), is there a version of Thm.~\ref{SLCopt} certifying when Prob.~\ref{OptimizationProblem} can be solved efficiently in full by similar means?
+Are Probs.~\ref{InverseProblem} and \ref{OptimizationProblem} then also hard \cite{Tillmann15}?
+Finally, since solving Prob.~\ref{SLCopt} directly is intractable in general, but efficiently solvable by $\ell_1$-norm minimization for fixed matrices with large enough lower bounds over sparse domains \cite{eldar2012compressed}, is there a version of Thm.~\ref{SLCopt} certifying when Prob.~\ref{OptimizationProblem} can be solved efficiently in a similar way?
 % [*** Incorporate this open problem with more words ***]
@@
 
-\textbf{Acknowledgement.} We thank Fritz Sommer and Darren Rhea for early thoughts, and Ian Morris for posting \eqref{eqdim} online.
+\textbf{Acknowledgement.} We thank F. Sommer and D. Rhea for early thoughts, and I. Morris for posting \eqref{eqdim} online.
 

### 2019-05-10 manuscripts/IEEE/final_submission.tex

--- 2019-05-10 manuscripts/IEEE/final_submission.tex
@@
 Note that every solution to Prob.~\ref{InverseProblem} represents infinitely many equivalent alternatives $\mathbf{BPD}$ and $\mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_1, \ldots, \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_N$ parametrized by a choice of permutation matrix $\mathbf{P}$ and invertible diagonal matrix $\mathbf{D}$.
-Identifying these ambiguities (labelling and scale) yields a set of elementary waveforms (the columns of $\mathbf{B}$) and their associated sparse coefficients (the entries of $\mathbf{\overline x}_i$) for approximating each data point $\mathbf{z}_i$.
+Identifying these ambiguities (labelling and scale) yields an orbit 
+represented by a particular set of elementary waveforms (the columns of $\mathbf{B}$) and their associated sparse coefficients (the entries of $\mathbf{\overline x}_i$) for reconstructing each data point $\mathbf{z}_i$.
 

### 2019-05-10 manuscripts/IEEE/final_submission.tex
sml and fig

--- 2019-05-10 manuscripts/IEEE/final_submission.tex
@@
 Here, we provide very general conditions guaranteeing when dictionaries yielding the sparsest encodings are unique and stable with respect to measurement or modeling error.
-We demonstrate that some or all dictionary elements are recoverable from noisy data even if the dictionary fails to satisfy the spark condition, its size is overestimated, or it induces only polynomial number of distinct sparse supports for the data.
+We demonstrate that some or all dictionary elements are recoverable from noisy data even if the dictionary fails to satisfy the spark condition, its size is overestimated, or only a polynomial number of distinct sparse supports appear in the data.
 Importantly, we derive these guarantees without requiring any constraints on the recovered dictionary beyond a natural upper bound on its size.
@@
 Note that every solution to Prob.~\ref{InverseProblem} represents infinitely many equivalent alternatives $\mathbf{BPD}$ and $\mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_1, \ldots, \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_N$ parametrized by a choice of permutation matrix $\mathbf{P}$ and invertible diagonal matrix $\mathbf{D}$.
-Identifying these ambiguities (labelling and scale) yields a set of elementary waveforms (the columns of $\mathbf{B}$) and their associated sparse coefficients (the entries of $\mathbf{\overline x}_i$) for approximating each data point $\mathbf{z}_i$.
+Identifying these ambiguities (labelling and scale) yields a single orbit of solutions represented by any particular set of elementary waveforms (the columns of $\mathbf{B}$) and their associated sparse coefficients (the entries of $\mathbf{\overline x}_i$) that reconstruct each data point $\mathbf{z}_i$.
 
@@
 % \includegraphics[width=.25 \linewidth]{figs/Ahat_FastICA_M640_K8_noise0_2042}
-\includegraphics[width=.24 \linewidth]{figs/Ahat_FastICA_M640_K8_noise0_4083.png}
+%\includegraphics[width=.24 \linewidth]{figs/Ahat_FastICA_M640_K8_noise0_4083.png}
 \includegraphics[width=.24 \linewidth]{figs/Ahat_FastICA_M640_K8_noise1_0205.png}
 \includegraphics[width=.24 \linewidth]{figs/Ahat_FastICA_M640_K8_noise2_0409.png}
+\includegraphics[width=.24 \linewidth]{figs/Ahat_FastICA_M640_K8_noise5_1021.png}
 \caption{\textbf{Learning a dictionary from increasingly noisy data}.

### 2019-05-10 manuscripts/IEEE/final_submission.tex
sml abstract

@@
 Here, we provide very general conditions guaranteeing when dictionaries yielding the sparsest encodings are unique and stable with respect to measurement or modeling error.
-We demonstrate that some or all dictionary elements are recoverable from noisy data even if the dictionary fails to satisfy the spark condition, its size is overestimated, or only a polynomial number of distinct sparse supports appear in the data.
+We demonstrate that some or all original dictionary elements are recoverable from noisy data even if the dictionary fails to satisfy the spark condition, its size is overestimated, or only a polynomial number of distinct sparse supports appear in the data.
 Importantly, we derive these guarantees without requiring any constraints on the recovered dictionary beyond a natural upper bound on its size.
-Our results yield an effective procedure sufficient to affirm if a proposed solution to the dictionary learning problem is unique within bounds commensurate with the noise.
+Our results also yield an effective procedure sufficient to affirm if a proposed solution to the dictionary learning problem is unique within bounds commensurate with the noise.
 We suggest applications to data analysis, engineering, and neuroscience and close with some remaining challenges left open by our work.

### 2019-05-10 manuscripts/IEEE/final_submission.tex
delta

@@
 implying (Cor.~\ref{DeterministicUniquenessCorollary}), which guarantees that sparse representations of a dataset $Z$ are unique up to noise whenever generating dictionaries $\mathbf{A}$ satisfy a spark condition on supports and the original sparse codes $\mathbf{x}_i$ are sufficiently diverse (e.g., Fig.~\ref{noisyrecovery}).
-Moreover, we provide an explicit, computable $\varepsilon(\delta_1, \delta_2)$ in (\ref{epsdel}) that is linear in desired accuracy $\delta_1, \delta_2$.
+Moreover, we provide an explicit, computable $\varepsilon(\delta_1, \delta_2)$ in (\ref{epsdel}) that is linear in desired accuracy $\delta_1$, and essentially so in $\delta_2$.
 

### 2019-05-10 manuscripts/IEEE/final_submission.tex
delta

@@
 To extend this observation to arbitrary probability distributions, note that if a set of $p$ measure spaces has all measures absolutely continuous with respect to the standard Borel measure on $\mathbb{R}$, then the product measure is also absolutely continuous with respect to the standard Borel product measure on $\mathbb{R}^p$ (e.g., see \cite{folland2013real}).
-This fact combined with Thm.~\ref{robustPolythm} implies the following.\footnote{We refer the reader to \cite{Hillar15} for a detailed explanation of these arguments.}
+This fact combined with Thm.~\ref{robustPolythm} implies the following.\footnote{We refer the reader to \cite{Hillar15} for a more detailed explanation of these arguments.}
 

### 2019-05-10 manuscripts/IEEE/final_submission.tex
tiny

@@
 Of particular note are the seminal works in the field \cite{Olshausen96, hurri1996image, bell1997independent, van1998independent}, which discovered that dictionaries optimized for coding small patches of ``natural" images share qualitative similarities with linear filters estimated from response properties of simple-cell neurons in mammalian visual cortex.
-Curiously, these waveforms (e.g., ``Gabor'' wavelets) appear in dictionaries learned by a variety of algorithms trained over different natural image datasets, suggesting these learned features in natural signals may, in some sense, be canonical \cite{donoho2001can}.
+Curiously, these waveforms (e.g., ``Gabor'' wavelets) appear in dictionaries learned by a variety of algorithms trained over different natural image datasets, suggesting that learned features in natural signals may, in some sense, be canonical \cite{donoho2001can}.
 
@@
 
-Before moving on to our proof of Thm.~\ref{SLCopt}, we briefly revisit our discussion on sample complexity from the end of the previous section.
+Before moving on to the proof of Thm.~\ref{SLCopt}, we briefly revisit our discussion on sample complexity from the end of the previous section.
 While an exponential number of samples may very well prove to be necessary in the deterministic or almost-certain case, our proof of Thm.~\ref{DeterministicUniquenessTheorem} can be extended to hold with some probability for \emph{any} number of samples by alternative appeal to a probabilistic pigeonholing at the point early in the proof where the (deterministic) pigeonhole principle is applied to show that for every $S \in \mathcal{H}$, there exist $k$ vectors $\mathbf{x}_i$ supported on $S$ whose corresponding $\mathbf{\overline x}_i$ all share the same support.\footnote{A famous example of such an argument is the counter-intuitive ``birthday paradox", which demonstrates that the probability of two people having the same birthday in a room of twenty-three is greater than 50\%.}
@@
 
-We hope that these remaining challenges pique the interest of the community in picking up where we have left off, and that the theoretical tools we have showcased here may be of use to this end.
+We hope that these remaining challenges pique the interest of the community in picking up where we have left off and that the theoretical tools we have showcased here may be of use to this end.
 

### 2019-05-10 manuscripts/IEEE/final_submission.tex
final fina

@@
 
-We hope that these remaining challenges pique the interest of the community in picking up where we have left off and that the theoretical tools we have showcased here may be of use to this end.
+We hope these remaining challenges pique the interest of the community to pick up where we have left off and that the theoretical tools showcased here may be of use to this end.
 

### 2019-07-22 manuscripts/IEEE/final_submission_final.tex
Updates from Overleaf

--- 2019-05-10 manuscripts/IEEE/final_submission.tex
@@
 \begin{center}
-\includegraphics[width=.24 \linewidth]{figs/basis.png}
+\includegraphics[width=.24 \linewidth]{manuscripts/IEEE/figs/Basis_.png}
 % \includegraphics[width=.25 \linewidth]{figs/Ahat_FastICA_M640_K8_noise0_2042}
 %\includegraphics[width=.24 \linewidth]{figs/Ahat_FastICA_M640_K8_noise0_4083.png}
-\includegraphics[width=.24 \linewidth]{figs/Ahat_FastICA_M640_K8_noise1_0205.png}
-\includegraphics[width=.24 \linewidth]{figs/Ahat_FastICA_M640_K8_noise2_0409.png}
-\includegraphics[width=.24 \linewidth]{figs/Ahat_FastICA_M640_K8_noise5_1021.png}
+\includegraphics[width=.24 \linewidth]{manuscripts/IEEE/figs/Ahat_FastICA_M1280_K8_noise0_0001.png}
+\includegraphics[width=.24 \linewidth]{manuscripts/IEEE/figs/Ahat_FastICA_M1280_K8_noise2_0513.png}
+\includegraphics[width=.24 \linewidth]{manuscripts/IEEE/figs/Ahat_FastICA_M1280_K8_noise3_9744.png}
 \caption{\textbf{Learning a dictionary from increasingly noisy data}.

### 2019-07-30 manuscripts/IEEE/final_submission.tex
final figs
updated final figs
Updates from Overleaf
chaz changes

@@
 The main result of this work is a very general uniqueness theorem for sparse coding (Thm.~\ref{DeterministicUniquenessTheorem}) directly 
-implying (Cor.~\ref{DeterministicUniquenessCorollary}), which guarantees that sparse representations of a dataset $Z$ are unique up to noise whenever generating dictionaries $\mathbf{A}$ satisfy a spark condition on supports and the original sparse codes $\mathbf{x}_i$ are sufficiently diverse (e.g., Fig.~\ref{noisyrecovery}).
+implying Cor.~\ref{DeterministicUniquenessCorollary}, which guarantees that sparse representations of a dataset $Z$ are unique up to noise whenever generating dictionaries $\mathbf{A}$ satisfy a spark condition on supports and the original sparse codes $\mathbf{x}_i$ are sufficiently diverse (e.g., Fig.~\ref{noisyrecovery}).
 Moreover, we provide an explicit, computable $\varepsilon(\delta_1, \delta_2)$ in (\ref{epsdel}) that is linear in desired accuracy $\delta_1$, and essentially so in $\delta_2$.
@@
 \begin{center}
-\includegraphics[width=.24 \linewidth]{figs/basis.png}
+\includegraphics[width=.24 \linewidth]{figs/Ahat_FastICA_M1280_K8_1.png}
 % \includegraphics[width=.25 \linewidth]{figs/Ahat_FastICA_M640_K8_noise0_2042}
 %\includegraphics[width=.24 \linewidth]{figs/Ahat_FastICA_M640_K8_noise0_4083.png}
-\includegraphics[width=.24 \linewidth]{figs/Ahat_FastICA_M640_K8_noise1_0205.png}
-\includegraphics[width=.24 \linewidth]{figs/Ahat_FastICA_M640_K8_noise2_0409.png}
-\includegraphics[width=.24 \linewidth]{figs/Ahat_FastICA_M640_K8_noise5_1021.png}
+\includegraphics[width=.24 \linewidth]{figs/Ahat_FastICA_M1280_K8_2.png}
+\includegraphics[width=.24 \linewidth]{figs/Ahat_FastICA_M1280_K8_3.png}
+\includegraphics[width=.24 \linewidth]{figs/Ahat_FastICA_M1280_K8_4.png}
 \caption{\textbf{Learning a dictionary from increasingly noisy data}.
@@
 
-We hope these remaining challenges pique the interest of the community to pick up where we have left off and that the theoretical tools showcased here may be of use to this end.
+It is our hope that the theoretical tools showcased here will be of some use to the community in answering these remaining questions.
 

### 2019-07-30 manuscripts/IEEE/final_submission.tex
no exam jams

@@
 
-\textbf{Acknowledgement.} We thank Fritz Sommer and Darren Rhea for early thoughts, and Ian Morris for posting \eqref{eqdim} online.
+%\textbf{Acknowledgement.} We thank Fritz Sommer and Darren Rhea for early thoughts, and Ian Morris for posting \eqref{eqdim} online.
+
+\textbf{Acknowledgement.} We thank Fritz Sommer for turning our attention to the dictionary learning problem and Darren Rhea for sharing early explorations.
+We also thank Ian Morris for posting a reference to his proof of \eqref{eqdim} online at Stack Exchange.
+Finally, we thank Bizzyskillet (www.soundcloud.com/bizzyskillet) for the “No-Exam Jams”, to which many of our proofs were designed and constructed.}
 

### 2019-07-30 manuscripts/IEEE/final_submission.tex
fixed minor bug
Updates from Overleaf

@@
 
-It is our hope that the theoretical tools showcased here will be of some use to the community in answering these remaining questions.
+It is our hope that the theoretical tools showcased here will be of use to the community in answering these remaining questions.
 
@@
 We also thank Ian Morris for posting a reference to his proof of \eqref{eqdim} online at Stack Exchange.
-Finally, we thank Bizzyskillet (www.soundcloud.com/bizzyskillet) for the “No-Exam Jams”, to which many of our proofs were designed and constructed.}
+Finally, we thank Bizzyskillet (www.soundcloud.com/bizzyskillet) for ``The No-Exam Jams'' to which many of our proofs were designed and constructed.
 

### 2020-07-16 manuscripts/thesis/abstract.tex
thesis

--- 2019-05-10 manuscripts/IEEE/final_submission.tex
@@
-% TODO: 
-% Make L_H a definition..? Change def of L to be 1-norm so we don't need these sqrt k's?
-% C_1 depends on J in Thm 1
-% also in proof of (7) x need not be *any* 2k-sparse vector...can instead restrict to some H...then 2k is restricted to half being on H.
-
-% Notes:
-%
-% Can we prove in a line or two that the inverse problem is stable by arguing that the function is bijective and closed therefore a homeomorphism?
-% Should we mention the notion of Grassmannian manifolds and that Theta is a metric on this space?
-% Change robustness to stability?
-%
-\documentclass[journal, twocolumn]{IEEEtran}
-
-% *** MATH PACKAGES ***
-\usepackage{amsmath, amssymb, amsthm} 
-\newtheorem{theorem}{Theorem}
-\newtheorem{lemma}{Lemma}
-\newtheorem{conjecture}{Conjecture}
-\newtheorem{problem}{Problem}
-\newtheorem{question}{Question}
-\newtheorem{proposition}{Proposition}
-\newtheorem{definition}{Definition}
-\newtheorem{corollary}{Corollary}
-\newtheorem{remark}{Remark}
-\newtheorem{example}{Example}
-
-\usepackage[pdftex]{graphicx}
-
-% *** ALIGNMENT PACKAGES ***
-\usepackage{array}
-\usepackage{cite}
-\usepackage{bm}
-
-% correct bad hyphenation here
-%\hyphenation{op-tical net-works semi-conduc-tor}
-
-\begin{document}
-
-%\title{When can a generating dictionary and sparse codes be recovered from noisy data?}
-%\title{When is the dictionary learning problem well-posed?}
-\title{On the uniqueness and stability of dictionaries \\ for sparse representation of noisy signals}
-%\title{When is the dictionary learning problem for sparse coding well-posed?}
-%\title{When is the sparsest representation unique?}
-%\title{When are sparse codes identifiable from their unknown noisy compressive measurements?}
-% FRITZ2: The title doesn't reflect the amount of new stuff, it seems incremental from the last one. It's not very meaningful.
-% FRITZ: Not everyone knows what well-posed means. You should mention recovery from noisy data in the title.
-
-\author{Charles~J.~Garfinkle and Christopher~J.~Hillar \\
-Redwood Center for Theoretical Neuroscience, Berkeley, CA, USA
-%\thanks{%e-mails: cjg@berkeley.edu, chillar@msri.org.  
-%CG and CH supported, in part, by NSF grant IIS-1219212 and the Statistical and Applied Mathematical Sciences Institute, under NSF DMS-1127914.}
-}
-
-\maketitle
-
-% \keywords{Sparse coding, dictionary learning, matrix factorization, compressed sensing, inverse problems, blind source separation}
-
 \begin{abstract}
-%Learning optimal dictionaries for sparse coding has exposed characteristic sparse features of many natural signals.
-However, there are few universal conditions guaranteeing the stability of such features in the presence of noise.
-Here, we prove very generally that optimal dictionaries and sparse codes are unique up to measurement error for all diverse enough datasets generated by the sparse coding model.
-Applications are given to data analysis, engineering, and neuroscience.
 Learning optimal dictionaries for sparse coding has exposed characteristic sparse features of many natural signals.
@@
 \end{abstract}
-
-% Optional adjustment to line up main text (after abstract) of first page with line numbers, when using both lineno and twocolumn options.
-% You should only change this length when you've finalised the article contents.
-
-\section{Introduction}\label{Intro}
-\IEEEPARstart{S}{parse} coding is a common modern approach to pattern analysis in signal processing whereby each of $N$ observed $n$-dimensional signal samples is viewed as a (noisy) linear combination of at most $k$ elementary waveforms drawn from some unknown ``dictionary" of size $m \ll N$ (see \cite{Zhang15} for a comprehensive review).
-%\IEEEPARstart{A}{}common modern approach to pattern analysis in signal processing is to view each of $N$ observed $n$-dimensional signal samples as a (noisy) linear combination of at most $k$ elementary waveforms drawn from some unknown ``dictionary" of size $m \ll N$ (see \cite{Zhang15} for a comprehensive review).
-Optimizing dictionaries subject to this and related sparsity constraints has revealed seemingly characteristic sparse structure in several signal classes of current interest (e.g., in vision \cite{wang2015sparse}).
-
-Of particular note are the seminal works in the field \cite{Olshausen96, hurri1996image, bell1997independent, van1998independent}, which discovered that dictionaries optimized for coding small patches of ``natural" images share qualitative similarities with linear filters estimated from response properties of simple-cell neurons in mammalian visual cortex.
-Curiously, these waveforms (e.g., ``Gabor'' wavelets) appear in dictionaries learned by a variety of algorithms trained over different natural image datasets, suggesting that learned features in natural signals may, in some sense, be canonical \cite{donoho2001can}.
-
-Motivated by these discoveries and more recent work relating compressed sensing \cite{eldar2012compressed} to a theory of information transmission through random wiring bottlenecks in the brain \cite{Isely10}, we address when dictionaries for sparse representation are indeed identifiable from data.
-Answers to this question may also have implications in practice wherever an appeal is made to latent sparse structure of data (e.g., forgery detection \cite{hughes2010, olshausen2010applied}; brain recordings \cite{jung2001imaging, agarwal2014spatially, lee2016sparse}; and gene expression \cite{wu2016stability}).
-
-While several algorithms have been recently proposed to provably recover unique dictionaries under specific conditions (see \cite[Sec.~I-E]{Sun16} for a summary of the state-of-the-art), few theorems can be invoked to justify the consistency of inference under this model of data more broadly.
-To our knowledge, a universal guarantee of the uniqueness and stability of learned dictionaries and the sparse representations they induce over noisy data has yet to appear in the literature.
-% in justifying the identification of forged paintings by their anomalous sparse representations \cite{hughes2010},
-
-Here, we prove very generally that uniqueness and stability is a typical property of sparse dictionary learning.
-More specifically, we show that matrices injective on a sparse domain are identifiable from \mbox{$N = m(k-1){m \choose k} + m$} noisy linear combinations of $k$ of their $m$ columns up to an error that is linear in the noise (Thm.~\ref{DeterministicUniquenessTheorem}).
-In fact, provided $n \geq \min(2k,m)$, in almost all cases the problem is well-posed, as per Hadamard \cite{Hadamard1902}, given a sufficient amount of data (Thm.~\ref{robustPolythm} and Cor.~\ref{ProbabilisticCor}).
-
-Our guarantees also hold for a related (and perhaps more commonly posed, e.g.
-\cite{rehnsommer2007}) optimization problem seeking a dictionary minimizing the average number of elementary waveforms required to reconstruct each sample of the dataset (Thm.~\ref{SLCopt}).
-To practical benefit, our results impose no restrictions on learned dictionaries (e.g., that they, too, be injective over some sparse domain) beyond an upper bound on dictionary size, which is necessary in any case to avoid trivial solutions (e.g., allowing $m = N$).
-%That is, every pair of solutions of comparable size has some number of dictionary elements in common (up to noise), and similarly so for the coefficients of sparse codes they induce.
-
-More precisely, let $\mathbf{A} \in \mathbb R^{n \times m}$ be a matrix with columns $\mathbf{A}_j$ ($j = 1,\ldots,m$) and let dataset $Z$ consist of measurements:
-\begin{align}\label{LinearModel}
-\mathbf{z}_i = \mathbf{A}\mathbf{x}_i + \mathbf{n}_i,\ \ \  \text{$i=1,\ldots,N$},
-\end{align}
-for $k$-\emph{sparse} $\mathbf{x}_i \in \mathbb{R}^m$ having at most $k<m$ nonzero entries and \emph{noise} $\mathbf{n}_i \in \mathbb{R}^n$, with bounded norm $\| \mathbf{n}_i \|_2 \leq  \eta$ representing our worst-case uncertainty in measuring the product $\mathbf{A}\mathbf{x}_i$.
-We first consider the following formulation of sparse coding.
-%The first mathematical problem we consider is the following.
-
-\begin{problem}\label{InverseProblem}
-Find a dictionary matrix $\mathbf{B}$ and $k$-sparse codes $\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N$ that satisfy $\|\mathbf{z}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \eta$ for all $i = 1,\ldots,N$.
-\end{problem}
-
-Note that every solution to Prob.~\ref{InverseProblem} represents infinitely many equivalent alternatives $\mathbf{BPD}$ and $\mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_1, \ldots, \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_N$ parametrized by a choice of permutation matrix $\mathbf{P}$ and invertible diagonal matrix $\mathbf{D}$.
-Identifying these ambiguities (labelling and scale) yields a single orbit of solutions represented by any particular set of elementary waveforms (the columns of $\mathbf{B}$) and their associated sparse coefficients (the entries of $\mathbf{\overline x}_i$) that reconstruct each data point $\mathbf{z}_i$.
-
-Previous theoretical work addressing the noiseless case $\eta =0$ (e.g., \cite{li2004analysis, Georgiev05, Aharon06, Hillar15}) for matrices $\mathbf{B}$ having exactly $m$ columns has shown that a solution to Prob.~\ref{InverseProblem}, when it exists, is unique up to such relabeling and rescaling provided the $\mathbf{x}_i$ are sufficiently diverse and $\mathbf{A}$ satisfies the \textit{spark condition}:
-\begin{align}\label{SparkCondition}
-\mathbf{A}\mathbf{x}_1 = \mathbf{A}\mathbf{x}_2 \implies \mathbf{x}_1 = \mathbf{x}_2, \ \ \ \text{for all $k$-sparse } \mathbf{x}_1, \mathbf{x}_2,
-\end{align}
-%
-which is necessary to guarantee the uniqueness of arbitrary $k$-sparse $\mathbf{x}_i$.
-We generalize these results to the practical setting  $\eta > 0$ by considering the following natural notion of stability with respect to measurement error.
-
-\begin{definition}\label{maindef}
-Fix $Y = \{ \mathbf{y}_1, \ldots, \mathbf{y}_N\} \subset \mathbb{R}^n$.
-We say $Y$ has a \textbf{$k$-sparse representation in $\mathbb{R}^m$} if there exists a matrix $\mathbf{A}$ and $k$-sparse $\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$ such that $\mathbf{y}_i = \mathbf{A}\mathbf{x}_i$ for all $i$.
-This representation is \textbf{stable} if for every $\delta_1, \delta_2 \geq 0$, there exists some $\varepsilon = \varepsilon(\delta_1, \delta_2)$ that is strictly positive for positive $\delta_1$ and $\delta_2$ such that if $\mathbf{B}$ and $k$-sparse $\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N \in \mathbb{R}^m$ satisfy:
-\begin{align*}
-	\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \varepsilon(\delta_1, \delta_2),\ \   \text{for all $i=1,\ldots,N$},
-\end{align*}
-then there is some permutation matrix $\mathbf{P}$ and invertible diagonal matrix $\mathbf{D}$ such that for all $i, j$:
-\begin{align}\label{def1}
-\|\mathbf{A}_j - (\mathbf{BPD})_j\|_2 \leq \delta_1 \ \text{and} \ \|\mathbf{x}_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_i\|_1 \leq \delta_2.
-\end{align}
-\end{definition}
-
-To see how Prob.
-\ref{InverseProblem} motivates Def.
-\ref{maindef}, suppose that $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$ and fix $\delta_1, \delta_2$ to be the desired accuracies of recovery in \eqref{def1}.
-Consider any dataset $Z$ generated as in \eqref{LinearModel} with $\eta \leq \frac{1}{2} \varepsilon(\delta_1, \delta_2)$.
-Using the triangle inequality, it follows that any $n \times m$ matrix $\mathbf{B}$ and $k$-sparse $\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N$ solving Prob.~\ref{InverseProblem} are necessarily within $\delta_1$ and $\delta_2$ of the original dictionary $\mathbf{A}$ and codes $\mathbf{x}_1, \ldots, \mathbf{x}_N$, respectively.\footnote{We mention that the different norms in \eqref{def1} reflect the distinct meanings typically ascribed to the dictionary and sparse codes in modeling data.}
-
-The main result of this work is a very general uniqueness theorem for sparse coding (Thm.~\ref{DeterministicUniquenessTheorem}) directly 
-implying (Cor.~\ref{DeterministicUniquenessCorollary}), which guarantees that sparse representations of a dataset $Z$ are unique up to noise whenever generating dictionaries $\mathbf{A}$ satisfy a spark condition on supports and the original sparse codes $\mathbf{x}_i$ are sufficiently diverse (e.g., Fig.~\ref{noisyrecovery}).
-Moreover, we provide an explicit, computable $\varepsilon(\delta_1, \delta_2)$ in (\ref{epsdel}) that is linear in desired accuracy $\delta_1$, and essentially so in $\delta_2$.
-
-In the next section, we give formal statements of these findings.
-We then extend the same guarantees (Thm.~\ref{SLCopt}) to the following alternate formulation of dictionary learning, which minimizes the total number of nonzero entries in sparse codes.
-
-\begin{problem}\label{OptimizationProblem}
-Find matrices $\mathbf{B}$ and vectors \mbox{$\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N$} solving:
-\begin{align}\label{minsum}
-\min \sum_{i = 1}^N \|\mathbf{\overline x}_{i}\|_0 \ \
-\text{subject to} \ \ \|\mathbf{z}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \eta, \ \text{for all $i$}.
-\end{align}
-\end{problem}
-
-Our development of Thm.~\ref{DeterministicUniquenessTheorem} is general enough to provide some uniqueness and stability even when generating $\mathbf{A}$ do not fully satisfy (\ref{SparkCondition}) and recovery dictionaries $\mathbf{B}$ have more columns than $\mathbf{A}$.
-Moreover, the approach incorporates a combinatorial theory for designing generating codes that should be of independent interest.
-We also give brief arguments adapting our results to dictionaries and codes drawn from probability distributions (Cor.~\ref{ProbabilisticCor}).
-The technical proofs of Thms.~\ref{DeterministicUniquenessTheorem} and ~\ref{SLCopt} are deferred to Sec.~\ref{DUT}, following some necessary definitions and a fact in combinatorial matrix analysis (Lem.~\ref{MainLemma}; proven in the Appendix).
-Finally, we discuss in Sec.~\ref{Discussion} applications of our mathematical observations as well as open questions.
-%The Appendix contains a proof of Lem.~\ref{MainLemma}.
-
-\section{Results}\label{Results}
-
-%Denote by $\mathbf{x}^J$ the subvector formed from the entries of $\mathbf{x}$ indexed by $J$. 
-%A set of $k$-sparse vectors is said to be in \emph{general linear position} when any $k$ of them are linearly independent.
-
-Precise statements of our results require that we first identify some combinatorial criteria on the supports\footnote{Recall that a vector $\mathbf{x}$ is said to be \emph{supported} in $S$ when $\mathbf{x} \in \text{\rm span}\{\mathbf{e}_j: j\in S\}$, with $\mathbf{e}_j$ forming the standard column basis.} of sparse vectors.
-Let $\{1, \ldots, m\}$ be denoted $[m]$, its power set $2^{[m]}$, and ${[m] \choose k}$ the set of subsets of $[m]$ of size $k$.
-A \emph{hypergraph} on vertices $[m]$  is simply any subset $\mathcal{H} \subseteq 2^{[m]}$.
-We say that $\mathcal{H}$ is \textit{$k$-uniform} when $\mathcal{H} \subseteq {[m] \choose k}$.
-The \emph{degree} $\deg_\mathcal{H}(i)$ of a node $i \in [m]$ is the number of sets in $\mathcal{H}$ that contain $i$, and we say $\mathcal{H}$ is \emph{regular} when for some $r$ we have $\deg_\mathcal{H}(i) = r$ for all $i$ (given such an $r$, we say $\mathcal{H}$ is \textit{$r$-regular}).
-We also write $2\mathcal{H} := \{ S \cup S': S, S' \in \mathcal{H}\}$.
-The following class of structured hypergraphs is a key ingredient in this work.
-
-\begin{definition}\label{sip}
-Given $\mathcal{H} \subseteq 2^{[m]}$, the \textbf{star} $\sigma(i)$ is the collection of sets in $\mathcal{H}$ containing $i$.
-We say $\mathcal{H}$ has the \textbf{singleton intersection property} (\textbf{SIP}) when $\cap \sigma(i) = \{i\}$ for all $i \in [m]$.
-\end{definition}
-
-We next give a quantitative generalization of the spark condition (\ref{SparkCondition}) to combinatorial subsets of supports.
-The \emph{lower bound} of an $n \times m$ matrix $\mathbf{M}$ is the largest $\alpha$ with \mbox{$\|\mathbf{M}\mathbf{x}\|_2 \geq \alpha\|\mathbf{x}\|_2$} for all $\mathbf{x} \in \mathbb{R}^m$ \cite{Grcar10}.
-By compactness of the unit sphere, every injective linear map has a positive lower bound; hence, if $\mathbf{M}$ satisfies \eqref{SparkCondition}, then submatrices formed from $2k$ of its columns or less have strictly positive lower bounds.
-
-The lower bound of a matrix is generalized below in (\ref{Ldef}) by restricting it to the spans of certain submatrices\footnote{See \cite{vidal2005generalized} for an overview of the related ``union of subspaces" model.} associated with a hypergraph $\mathcal{H} \subseteq {[m] \choose k}$ of column indices.
-Let $\mathbf{M}_S$ denote the submatrix formed by the columns of a matrix $\mathbf{M}$ indexed by $S \subseteq [m]$ (setting $\mathbf{M}_\emptyset := \mathbf{0}$).
-In the sections that follow, we shall also let $\bm{\mathcal{M}}_S$ denote the column-span of a submatrix $\mathbf{M}_S$, and $\bm{\mathcal{M}}_\mathcal{G}$ to denote $\{\bm{\mathcal{M}}_S\}_{S \in \mathcal{G}}$.
-We define:  % Define $L_\mathcal{H}(\mathbf{M})$ as follows:
-%\begin{align*} 
-%L_\mathcal{H}(\mathbf{M}) := \min \left\{ \frac{ \|\mathbf{M}(\mathbf{x}_1-\mathbf{x}_2)\|_2 }{ \sqrt{2k} \|\mathbf{x}_1-\mathbf{x}_2\|_2} : \mathbf{x}_1, \mathbf{x}_2 \in \cup_{S \in \mathcal{H}} \bm{\mathcal{M}}_S \right\},
-%\end{align*} 
-%
-%where we write $L_{2k}$ in place of $L_\mathcal{H}$ when $\mathcal{H} = {[m] \choose k}$.
-Note that if $\mathcal{H}$ covers $[m]$, then $L_2 > L_\mathcal{H}$.\footnote{The reader should beware that $L_2 = L_{[m]}$, whereas $L = L_{\{[m]\}}$.
-For even $k$, the quantity $1 - \sqrt{k} L_k(\mathbf{M})$ is also known in the compressed sensing literature as the (asymmetric) lower restricted isometry constant \cite{Blanchard2011}.} Clearly, for any $\mathbf{M}$ satisfying \eqref{SparkCondition}, we have $L_{k'}(\mathbf{M}) > 0$ for  $k' \leq 2k$.
-%\begin{align*}
-%L_\mathcal{H}(\mathbf{M}) := \min \left\{ \frac{ \|\mathbf{M}_S\mathbf{x}\|_2 }{ \sqrt{k} \|\mathbf{x}\|_2} : S \in \mathcal{H} \right\},
-%\end{align*} 
-%\begin{align*}
-%L_\mathcal{H}(\mathbf{M}) := \max \left\{ \ falpha: \|\mathbf{M}_S\mathbf{x}\|_2 \geq \alpha \sqrt{k} \|\mathbf{x}\|_2 : S \in \mathcal{H}, \ \ \mathbf{x} \in \mathbb{R}^m \right\},
-%\end{align*} 
-\begin{align}\label{Ldef}
-L_\mathcal{H}(\mathbf{M}) := \min \left\{ \frac{\|\mathbf{M}_S\mathbf{x}\|_2}{ \sqrt{k} \|\mathbf{x}\|_2} : S \in \mathcal{H}, \ \mathbf{0} \neq \mathbf{x} \in \mathbb{R}^{|S|} \right\},
-\end{align} 
-%
-writing also $L_{k}$ in place of $L_\mathcal{H}$ when $\mathcal{H} = {[m] \choose k}$.\footnote{In compressed sensing literature, \mbox{$1 - \sqrt{k} L_k(\mathbf{M})$}  is the asymmetric lower restricted isometry constant for $\mathbf{M}$ with unit $\ell_2$-norm columns \cite{Blanchard2011}.}  As explained above, compactness implies that $L_{2k}(\mathbf{M}) > 0$ for all $\mathbf{M}$ satisfying \eqref{SparkCondition}.
-Clearly, $L_{\mathcal{H}'}(\mathbf{M}) \geq L_\mathcal{H}(\mathbf{M})$ whenever $\mathcal{H}' \subseteq \mathcal{H}$, and similarly any $k$-uniform $\mathcal{H}$ satisfying $\cup \mathcal{H} = [m]$ has $L_2 \geq L_{2\mathcal{H}} \geq L_{2k}$ (letting $L_{2k}$ := $L_m$ whenever $2k > m$).
-
-We are now in a position to state our main result, though for expository purposes we leave the quantity $C_1$ %(a function of $\mathbf{A}$, $\mathbf{x}_1, \ldots, \mathbf{x}_N$, and $\mathcal{H}$) 
-undefined until Sec.~\ref{DUT}. All results  below assume real matrices and vectors.
-
-%eps-tightness COUNTER-EXAMPLE:
-%Consider the alternate dictionary $B = \left(\mathbf{0}, \frac{1}{2}(\mathbf{e}_1 + \mathbf{e}_2), \mathbf{e}_3, \ldots, \mathbf{e}_{m} \right)$ and sparse codes $\mathbf{b}_i = \mathbf{e}_2$ for $i = 1, 2$ and $\mathbf{b}_i = \mathbf{e}_i$ for $i = 3, \ldots, m$.
-Then $|A\mathbf{a}_i - B\mathbf{b}_i| = 1/\sqrt{2}$ for $i = 1, 2$ (and $0$ otherwise).
-If there were permutation and invertible diagonal matrices $P \in \mathbb{R}^{m \times m}$ and $D \in \mathbb{R}^{m \times m}$ such that $|(A-BPD)\mathbf{e}_i| \leq C\varepsilon$ for all $i \in [m]$, then we would reach the contradiction $1 = |P^{-1}\mathbf{e}_1|_2 = |(A-BPD)P^{-1}\mathbf{e}_1|_2 \leq 1/\sqrt{2}$.
-
-\begin{theorem}\label{DeterministicUniquenessTheorem}
-%Fix integers $n, k, m$ and $\overline m$. 
-If an $n \times m$ matrix $\mathbf{A}$ satisfies $L_{2\mathcal{H}}(\mathbf{A}) > 0$ for some $r$-regular $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP, and $k$-sparse \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} include more than $(k-1){\overline m \choose k}$ vectors in general linear position\footnote{Recall that a set of vectors sharing support $S$ are in \emph{general linear position} when any $|S|$ of them are linearly independent.} supported in each $S \in \mathcal{H}$, then the following recovery guarantees hold for $C_1 > 0$ given by \eqref{Cdef1}.
-
-\textbf{Dictionary Recovery:} Fix $\varepsilon < L_{2}(\mathbf{A}) / C_1$.\footnote{Note that the condition $\varepsilon < L_2(\mathbf{A}) /C_1$ is necessary; otherwise, with \mbox{$\mathbf{A}$ = $\mathbf{I}$} (the identity matrix) and $\mathbf{x}_i = \mathbf{e}_i$, the matrix $\mathbf{B} = \left[\mathbf{0}, \frac{1}{2}(\mathbf{e}_1 + \mathbf{e}_2), \mathbf{e}_3, \ldots, \mathbf{e}_{m} \right]$ and sparse codes $\mathbf{\overline x}_i = \mathbf{e}_2$ for $i = 1, 2$ and $\mathbf{\overline x}_i = \mathbf{e}_i$ for $i \geq 3$ satisfy $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline x}_i \|_2 \leq \varepsilon$ but nonetheless violate \eqref{Cstable}.} If an $n \times \overline m$ matrix $\mathbf{B}$ has, for every $i \in [N]$, an associated $k$-sparse $\mathbf{\overline x}_i$ satisfying \mbox{$\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \varepsilon$}, then $\overline m \geq m$, and provided that $\overline m (r-1) < mr$, there is a permutation matrix $\mathbf{P}$ and an invertible diagonal matrix $\mathbf{D}$ such that:
-\begin{align}\label{Cstable}
-\|\mathbf{A}_j- (\mathbf{BPD})_j\|_2 \leq C_1 \varepsilon, \ \ \text{for all } j \in J,
-\end{align}
-%
-for some $J \subseteq [m]$ of size \mbox{$m - (r-1)(\overline m - m)$}. 
-% $\overline m - r(\overline m - m)$
-
-\textbf{Code Recovery:} If, moreover, $\mathbf{A}_J$ satisfies \eqref{SparkCondition} and $\varepsilon < L_{2k}(\mathbf{A}_J) / C_1$, then $(\mathbf{BP})_J$ also satisfies \eqref{SparkCondition} with $L_{2k}(\mathbf{BP}_J) \geq (L_{2k}(\mathbf{A}_J) - C_1 \varepsilon) / \|\mathbf{D}_J\|_1$, and for all $i \in [N]$:
-\begin{align}\label{b-PDa}
-%\|\mathbf{x}^J_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}^{\overline J}_i\|_1 &\leq  \left( \frac{ 1+C_1 \|\mathbf{x}^{J}_i\|_1 }{ L_{2k}(\mathbf{A}) -  C_1\varepsilon } \right) \varepsilon \ \  \text{for $i \in [N]$}.
-\|(\mathbf{x}_i)_J - (\mathbf{D}^{-1}\mathbf{P}^{\top} \mathbf{\overline x}_i)_J\|_1 &\leq  \left( \frac{ 1+C_1 \|(\mathbf{x}_i)_J\|_1 }{ L_{2k}(\mathbf{A}_J) -  C_1\varepsilon } \right) \varepsilon,
-\end{align}
-%
-where subscript $(\cdot)_J$ here represents the subvector formed from restricting to coordinates indexed by $J$.
-\end{theorem}
-
-%We delay defining the explicit constant $C_1$ until Section \ref{DUT} (\eqref{Cdef1}).
-%To be clear, the implication of Thm.~\ref{DeterministicUniquenessTheorem} is that $Y = \{\mathbf{Ax}_1, \ldots, \mathbf{Ax}_N\}$ has a stable $k$-sparse representation in $\mathbb{R}^m$, with \eqref{def1} guaranteed provided $\varepsilon$ in Def.~\ref{maindef} does not exceed:
-In words, Thm.~\ref{DeterministicUniquenessTheorem} says that the smaller the regularity $r$ of the original support hypergraph $\mathcal{H}$ or the difference $\overline m - m$ between the assumed and actual number of elements in the latent dictionary, the more columns and coefficients of the original dictionary $\mathbf{A}$ and sparse codes $\mathbf{x}_i$ are guaranteed to be contained (up to noise) in the appropriately labelled and scaled recovered dictionary $\mathbf{B}$ and codes $\mathbf{\overline x}_i$, respectively.
-
-In the important special case when $\overline m = m$, the theorem directly implies that  $Y = \{\mathbf{Ax}_1, \ldots, \mathbf{Ax}_N\}$ has a stable $k$-sparse representation in $\mathbb{R}^m$, with inequalities \eqref{def1} guaranteed in Def.~\ref{maindef} for the following worst-case error $\varepsilon$:
-\begin{align}\label{epsdel}
-\varepsilon(\delta_1, \delta_2) := \min \left\{ \frac{\delta_1}{ C_1 }, \frac{ \delta_2 L_{2k}(\mathbf{A})}{ 1 + C_1 \left( \delta_2 + \max_{i \in [N]} \|\mathbf{x}_i\|_1  \right) } \right\}.
-\end{align}
-
-Since sparse codes in general linear position are straightforward to produce with a ``Vandermonde''  construction (i.e., by choosing columns of the matrix $[\gamma_{i}^j]_{i,j=1}^{k,N}$, for distinct nonzero $\gamma_i$), we have the following direct consequence of Thm.~\ref{DeterministicUniquenessTheorem}.
-
-\begin{corollary}\label{DeterministicUniquenessCorollary}
-Given any regular hypergraph $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP, there are $N =  |\mathcal{H}| \left[ (k-1){m \choose k} + 1  \right]$ vectors \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} such that every matrix $\mathbf{A}$ satisfying spark condition \eqref{SparkCondition} generates $Y = \{\mathbf{A}\mathbf{x}_1, \ldots, \mathbf{A}\mathbf{x}_N\}$ with a stable $k$-sparse representation in $\mathbb{R}^m$ for $\varepsilon(\delta_1,\delta_2)$ given by \eqref{epsdel}.
-\end{corollary}
-
-% prev
-%\begin{corollary}\label{DeterministicUniquenessCorollary}
-%Given any regular hypergraph $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP, there are $N =  |\mathcal{H}| \left[ (k-1){m \choose k} + 1  \right]$ vectors \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} such that every matrix $\mathbf{A}$ with $L_{2\mathcal{H}}(\mathbf{A}) > 0$ generates a dataset $Y = \{\mathbf{A}\mathbf{x}_1, \ldots, \mathbf{A}\mathbf{x}_N\}$ with a stable $k$-sparse representation in $\mathbb{R}^m$ for $\varepsilon(\delta_1,\delta_2)$ as in \eqref{epsdel}.
-%\end{corollary}
-
-%We claim that the assumptions of Thm.~\ref{DeterministicUniquenessTheorem} are easily met with deterministic constructions.
-In particular, sparse codes in general linear position are straightforward to produce using a ``Vandermonde'' matrix construction (i.e.
-use the columns of the matrix $[\gamma_{i}^j]_{i,j=1}^{k,N}$, for distinct nonzero $\gamma_i$).
-%
-
-% (Prob.~\ref{InverseProblem}).
-%=======
-%An immediate practical implication of this result is that there exists a practical procedure to affirm if one's proposed solution $(\mathbf{B}, \mathbf{\overline x}_1, \ldots, \mathbf{x}_N)$ to Prob.~\ref{InverseProblem} is indeed unique (up to noise and inherent ambiguities): simply check that $\mathbf{B}$ and the $\mathbf{\overline x}_i$ satisfy the assumptions on $\mathbf{A}$ and the $\mathbf{x}_i$ in Thm.~\ref{DeterministicUniquenessTheorem}.
-%
-%%In fact, a more general result (stated clearly in the next section) can be gleaned from our method of proving Thm.~\ref{DeterministicUniquenessTheorem}.
-Briefly, in cases where $\mathbf{B}$ has $\overline m \neq m$ columns, or $\mathcal{H}$ is not regular or only partially satisfying the SIP, a relation between $\overline m$ and the degree sequence of nodes in $\mathcal{H}$ gives indices $J \subseteq [m]$ defining a submatrix $\mathbf{A}_J$ and subvectors $\mathbf{x}_i^J$ that are recoverable in the sense of \eqref{Cstable} and \eqref{b-PDa}.
-For example, if $\mathcal{H}$ is $\ell$-regular with the SIP but $m \leq \overline m < m\ell/(\ell - 1)$ then we have nonzero $|J| = \overline m - \ell(\overline m - m)$.
-The implication here is that the smaller the difference $\overline m - m$, the more columns and code entries of the original $n \times m$ dictionary $\mathbf{A}$ and codes $\mathbf{x}_i$ contained (up to noise) in the appropriately scaled $n \times \overline m$ dictionary $\mathbf{B}$ and codes $\mathbf{\overline x}_i$.
-When $\overline m = m$, we recover Thm.~\ref{DeterministicUniquenessTheorem}.
-%
-%%In fact, even if $\mathcal{H}$ is not regular or only partially satisfies the SIP, a relation between $\overline m$ and the degree sequence of nodes in $\mathcal{H}$ may give the indices $J \subseteq [m]$.
-For sake of brevity, we delay to the next section a clear statement of this more general result.
-%
-%Regarding the assumptions of Thm.~\ref{DeterministicUniquenessTheorem}, it so happens that sparse codes $\mathbf{x}_i$ in general linear position are straightforward to produce with a ``Vandermonde'' matrix construction \cite{Hillar15}, leading to the following.
-%>>>>>>> d1407a275dc391dabad7bb62d3e659f9a4ac4624
-
-% Needs to be L_{2k}(A) > 0 to guarantee sparse vector recovery
-
-%We also have the following refinement of a result in \cite{Hillar15}:
-%\begin{corollary}
-%Those square matrices $\mathbf{A}$ that satisfy \mbox{$L_{2\mathcal{H}}(\mathbf{A}) > 0$} for some regular $k$-uniform hypergraph $\mathcal{H}$ with the SIP and have the property that $\mathbf{Ax}$ is $k$-sparse for all $k$-sparse $\mathbf{x}$ with support in $\mathcal{H}$ are the matrices $\mathbf{PD}$, where $\mathbf{P}$ and $\mathbf{D}$ run over permutation and invertible diagonal matrices, respectively.
-%\end{corollary}
-
-One can easily verify that for every $k < m$ there are regular $k$-uniform hypergraphs $\mathcal{H}$ with the SIP besides the obvious $\mathcal{H} = {[m] \choose k}$.
-For instance, take $\mathcal{H}$ to be the $k$-regular set of consecutive intervals of length $k$ in some cyclic order on $[m]$.
-In this case, a direct consequence of Cor.~\ref{DeterministicUniquenessCorollary} is rigorous verification of the lower bound \mbox{$N = m(k-1){m \choose k} + m$} for sufficient sample size from the introduction.
-Special cases allow for even smaller hypergraphs.
-For example, if $k = \sqrt{m}$, then a 2-regular $k$-uniform hypergraph with the SIP can be constructed as the $2k$ rows and columns formed by arranging the elements of $[m]$ into a square grid.
-
-%\cite{li2004analysis, Georgiev05, Aharon06, Hillar15}
-We should stress here that framing the problem in terms of hypergraphs has allowed us to show, unlike in previous research on the subject, that the matrix $\mathbf{A}$ need not necessarily satisfy \eqref{SparkCondition} to be recoverable from data.
-As an example, let $\mathbf{A} = [ \mathbf{e}_1, \ldots, \mathbf{e}_5, \mathbf{v}]$ with $\mathbf{v} = \mathbf{e}_1 + \mathbf{e}_3 + \mathbf{e}_5$ and take $\mathcal{H}$ to be all consecutive pairs of indices $1, \ldots ,6$ arranged in cyclic order.
-Then for $k=2$, the matrix $\mathbf{A}$ fails to satisfy \eqref{SparkCondition} while still obeying the assumptions of Thm.~\ref{DeterministicUniquenessTheorem} for dictionary recovery.%, hence guaranteeing \eqref{Cstable} .
-%(since $\{ \mathbf{A}_1, \mathbf{A}_3, \mathbf{A}_5, \mathbf{A}_6\}$ is not a linearly independent set).
-%This weakening allows for a practical (polynomial) amount of data to still guarantee a stable dictionary in the case where the set of sparse supports for the $\mathbf{\overline x}_i$ is known to have a size that grows polynomially in $m$ and $k$.
-
-A practical implication of Thm.~\ref{DeterministicUniquenessTheorem} is the following: there is an effective procedure sufficient to affirm if a proposed solution to Prob.~\ref{InverseProblem} is indeed unique (up to noise and inherent ambiguities).
-One need simply check that the matrix and codes satisfy the (computable) assumptions of Thm.~\ref{DeterministicUniquenessTheorem} on $\mathbf{A}$ and the $\mathbf{x}_i$.
-In general, however, there is no known efficient procedure.
-We defer a brief discussion on this point to the next section.
-%Another practical implication of Thm.\ref{DeterministicUniquenessTheorem} is the following: there is an effective procedure sufficient to affirm if a proposed solution $(\mathbf{B}, \mathbf{\overline x}_1, \ldots, \mathbf{x}_N)$ to Prob.~\ref{InverseProblem} is indeed unique (up to noise and inherent ambiguities).
-One simply checks that $\mathbf{B}$ and the $\mathbf{\overline x}_i$ satisfy the respective assumptions of Thm.~\ref{DeterministicUniquenessTheorem}.
-%. on $\mathbf{A}$ and the $\mathbf{x}_i$, respectively.
-
-%In fact, a more general result (stated clearly in the next section) can be gleaned from our method of proving Thm.~\ref{DeterministicUniquenessTheorem}.
-Briefly, in cases where $\mathbf{B}$ has $\overline m \neq m$ columns, or $\mathcal{H}$ is not regular or only partially satisfying the SIP, a relation between $\overline m$ and the degree sequence of nodes in $\mathcal{H}$ gives indices $J \subseteq [m]$ defining a submatrix $\mathbf{A}_J$ and subvectors $\mathbf{x}_i^J$ that are recoverable in the sense of \eqref{Cstable} and \eqref{b-PDa}.
-For example, if $\mathcal{H}$ is $\ell$-regular with the SIP but $m \leq \overline m < m\ell/(\ell - 1)$ then we have nonzero $|J| = \overline m - \ell(\overline m - m)$.
-The implication here is that the smaller the difference $\overline m - m$, the more columns and code entries of the original $n \times m$ dictionary $\mathbf{A}$ and codes $\mathbf{x}_i$ contained (up to noise) in the appropriately scaled $n \times \overline m$ dictionary $\mathbf{B}$ and codes $\mathbf{\overline x}_i$.
-When $\overline m = m$, we recover Thm.~\ref{DeterministicUniquenessTheorem}.
-
-%In fact, even if $\mathcal{H}$ is not regular or only partially satisfies the SIP, a relation between $\overline m$ and the degree sequence of nodes in $\mathcal{H}$ may give the indices $J \subseteq [m]$.
-For sake of brevity, we delay to the next section a clear statement of this more general result.
-
-%=======
-%One can also verify that for every $k < m$, there is a regular $k$-uniform hypergraph that satisfies the SIP; for instance, take $\mathcal{H}$ to be the consecutive intervals of length $k$ in some cyclic order on $[m]$, for which Cor.~\ref{DeterministicUniquenessCorollary} implies the lower bound for sample size $N$ from the introduction.
-In many cases, however, the SIP is achievable with far fewer supports; for example, when $k = \sqrt{m}$, take $\mathcal{H}$ to be the $2k$ rows and columns formed by arranging $[m]$ in a square grid.
-%>>>>>>> d1407a275dc391dabad7bb62d3e659f9a4ac4624
-
-%As mentioned above, there exist $k$-uniform regular hypergraphs $\mathcal{H}$ with the SIP having cardinality $|\mathcal{H}| = m$,
-
-A less direct consequence of Thm.~\ref{DeterministicUniquenessTheorem} is the following uniqueness and stability guarantee for solutions to Prob.~\ref{SLCopt}.
-%, the usual optimization problem of interest for those applying dictionary learning to their data.
-
-\begin{theorem}\label{SLCopt}
-Fix a matrix $\mathbf{A}$ and vectors $\mathbf{x}_i$ satisfying the assumptions of Thm.~\ref{DeterministicUniquenessTheorem}, only now with over \mbox{$(k-1)\left[ {\overline m \choose k} + |\mathcal{H}|k{\overline m \choose k-1}\right]$} vectors supported in general linear position in each $S \in \mathcal{H}$.
-Every solution to Prob.~\ref{OptimizationProblem} (with $\eta = \varepsilon/2$) satisfies recovery guarantees \eqref{Cstable} and \eqref{b-PDa} when the corresponding bounds on $\eta$ are met.
-\end{theorem}
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=.24 \linewidth]{figs/basis.png}
-% \includegraphics[width=.25 \linewidth]{figs/Ahat_FastICA_M640_K8_noise0_2042}
-%\includegraphics[width=.24 \linewidth]{figs/Ahat_FastICA_M640_K8_noise0_4083.png}
-\includegraphics[width=.24 \linewidth]{figs/Ahat_FastICA_M640_K8_noise1_0205.png}
-\includegraphics[width=.24 \linewidth]{figs/Ahat_FastICA_M640_K8_noise2_0409.png}
-\includegraphics[width=.24 \linewidth]{figs/Ahat_FastICA_M640_K8_noise5_1021.png}
-\caption{\textbf{Learning a dictionary from increasingly noisy data}.
-The (unraveled) basis elements of the $8 \times 8$ discrete cosine transform (DCT) form the 64 columns of the left-most matrix above.
-Three increasingly imprecise dictionaries (columns reordered to best match original) are recovered by FastICA \cite{hyvarinen2000independent} trained on data generated from $8$-sparse linear combinations of DCT elements corrupted with additive noise (increasing from left to right).}
-\vspace{-.6 cm}
-\label{noisyrecovery}
-\end{center}
-\end{figure}
-
-Another extension of Thm.~\ref{DeterministicUniquenessTheorem} can be derived from the following algebraic characterization of the spark condition.
-Letting $\mathbf{A}$ be the $n \times m$ matrix of $nm$ indeterminates $A_{ij}$, the reader may work out why substituting real numbers for the $A_{ij}$ yields a matrix satisfying \eqref{SparkCondition} if and only if the following polynomial evaluates to a nonzero number:
-\begin{align*}
-f(\mathbf{A}) := \prod_{S \in {[m] \choose 2k}} \sum_{S' \in {[n] \choose 2k}} (\det \mathbf{A}_{S',S})^2,
-\end{align*}
-%
-where for any $S' \in {[n] \choose 2k}$ and $S \in {[m] \choose 2k}$, the symbol $\mathbf{A}_{S',S}$ denotes the submatrix of entries $A_{ij}$ with $(i,j) \in S' \times S$.\footnote{The large number of terms in this product is likely necessary given that deciding whether or not a matrix satisfies the spark condition is NP-hard \cite{tillmann2014computational}.}
-
-Since $f$ is analytic, having a single substitution of a real matrix $\mathbf{A}$ satisfying $f(\mathbf{A}) \neq 0$ implies that the zeroes of $f$ form a set of (Borel) measure zero.
-Such a matrix is easily constructed by adding rows of zeroes to a $\min(2k,m) \times m$ Vandermonde matrix as mentioned previously, so that every sum in the product defining $f$ above is strictly positive.
-Thus, almost every $n \times m$ matrix with $n \geq \min(2k,m)$ satisfies \eqref{SparkCondition}.
-
-%Another extension of Thm.~\ref{DeterministicUniquenessTheorem} arises from the following analytic characterization of the spark condition.
-Let $\mathbf{A}$  be the $n \times m$ matrix of $nm$ indeterminates $A_{ij}$.
-When real numbers are substituted for $A_{ij}$, the resulting matrix satisfies \eqref{SparkCondition} if and only if the following polynomial is nonzero:
-%\begin{align*}
-%f(\mathbf{A}) := \prod_{S \in {[m] \choose k}} \sum_{S' \in {[n] \choose k}} (\det \mathbf{A}_{S',S})^2,
-%\end{align*}
-%
-%where for any $S' \in {[n] \choose k}$ and $S \in {[m] \choose k}$, the symbol $\mathbf{A}_{S',S}$ denotes the submatrix of entries $A_{ij}$ with $(i,j) \in S' \times S$.
-We note that the large number of terms in this product is likely necessary due to the NP-hardness of deciding whether a given matrix $\mathbf{A}$ satisfies the spark condition \cite{tillmann2014computational}.
-
-%Since $f$ is analytic, having a single substitution of a real matrix $\mathbf{A}$ with $f(\mathbf{A}) \neq 0$ necessarily implies that the zeroes of $f$ form a set of measure zero.
-Fortunately, such a matrix $\mathbf{A}$ is easily constructed by adding rows of zeroes to any $\min(2k,m) \times m$ Vandermonde matrix as described above (so that each term in the product above for $f$ is nonzero).
-Hence, almost every $n \times m$ matrix with $n \geq \min(2k,m)$ satisfies \eqref{SparkCondition}.
-
-We claim that a similar phenomenon applies to datasets of vectors with a stable sparse representation.
-Briefly, following the same procedure as in \cite[Sec.~IV]{Hillar15}, for $k < m$ and $n \geq \min(2k, m)$, we may consider the ``symbolic'' dataset $Y = \{\mathbf{A}\mathbf{x}_1,\ldots,\mathbf{A} \mathbf{x}_N\}$ generated by an indeterminate $n \times m$ matrix $\mathbf{A}$ and $m$-dimensional $k$-sparse vectors $\mathbf{x}_1, \ldots, \mathbf{x}_N$ indeterminate within their supports, which form a regular hypergraph $\mathcal{H} \subseteq {[m] \choose k}$ satisfying the SIP.
-Restricting \mbox{$(k-1){m \choose k} + 1$} indeterminate $\mathbf{x}_i$ to each support in $\mathcal{H}$, and letting $\textbf{M}$ be the $n \times N$ matrix with columns $\mathbf{A}\mathbf{x}_i$, it can be checked that when $f(\mathbf{M}) \neq 0$ for a substitution of real numbers for the indeterminates, all of the assumptions on $\mathbf{A}$ and the $\mathbf{x}_i$ in Thm.~\ref{DeterministicUniquenessTheorem} are satisfied.
-We therefore have the following.
-% ; in particular, $\mathbf{A}$ satisfies \eqref{SparkCondition}
-
-\begin{theorem}\label{robustPolythm}
-%Let $\mathbf{A}$ and $\mathbf{x}_1, \ldots, \mathbf{x}_N$ be an indeterminate $n \times m$ matrix and sequence of $m$-dimensional vectors, respectively. 
-There is a polynomial in the entries of $\mathbf{A}$ and the $\mathbf{x}_i$ that evaluates to a nonzero number only when $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$.
-In particular, almost all substitutions impart to $Y$ this property.
-\end{theorem}
-
-%To extend this observation to arbitrary probability distributions, note that if a set of measure spaces $\{(X_{\ell}, \nu_{\ell})\}_{\ell=1}^p$ has measures $\nu_{\ell}$ absolutely continuous with respect to the standard Borel measure on $\mathbb{R}$ for all $\ell \in [p]$, then the product measure $\prod_{\ell=1}^p \nu_{\ell}$ is also absolutely continuous with respect to the standard Borel product measure on $\mathbb{R}^p$ (e.g., see \cite{folland2013real}).
-This fact combined with Thm.~\ref{robustPolythm} implies the following.
-To extend this observation to arbitrary probability distributions, note that if a set of $p$ measure spaces has all measures absolutely continuous with respect to the standard Borel measure on $\mathbb{R}$, then the product measure is also absolutely continuous with respect to the standard Borel product measure on $\mathbb{R}^p$ (e.g., see \cite{folland2013real}).
-This fact combined with Thm.~\ref{robustPolythm} implies the following.\footnote{We refer the reader to \cite{Hillar15} for a more detailed explanation of these arguments.}
-
-\begin{corollary}\label{ProbabilisticCor}
-If the indeterminate entries of $\mathbf{A}$ and the $\mathbf{x}_i$ are drawn independently from probability distributions absolutely continuous with respect to the standard Borel measure, then $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$ with probability one.
-\end{corollary}
-
-Thus, drawing the dictionary and supported sparse coefficients from any continuous probability distribution almost always generates data with a stable sparse representation.
-
-%\cite{rehnsommer2007, rozell2007neurally, ganguli2012compressed, hu2014hebbian}
-
-We close this section with some comments on the optimality of our results.
-The linear scaling for $\varepsilon$ in \eqref{epsdel} is essentially optimal (e.g., see \cite{arias2013fundamental}), but a basic open problem remains: how many samples are necessary to determine the sparse coding model?
-Our results demonstrate that sparse codes $\mathbf{x}_i$ drawn from only a polynomial number of $k$-dimensional subspaces permit stable identification of the generating dictionary $\mathbf{A}$. 
-This lends some legitimacy to the use of the model in practice, where data in general are unlikely (if ever) to exhibit the exponentially many possible $k$-wise combinations of dictionary elements required by (to our knowledge) all previously published results.
-
-Consequently, if $k$ is held fixed or if the size of the support set of reconstructing codes is polynomial in $\overline m$ and $k$, then a practical (polynomial) amount of data suffices to identify the dictionary.\footnote{In the latter case, a reexamination of the pigeonholing argument in the proof of Thm.~\ref{DeterministicUniquenessTheorem} requires a polynomial number of samples distributed over a polynomial number of supports.} Reasons to be skeptical that this holds in general, however, can be found in \cite{tillmann2014computational, Tillmann15}.
-Even so, in the next section we discuss how probabilistic guarantees can in fact be made for any number of available samples.
-
-\section{Proofs}\label{DUT} % of Theorems~\ref{DeterministicUniquenessTheorem} and ~\ref{SLCopt}}\label{DUT}
-
-%%%%%%%%%%%%%%
-% need to cut maybe: 
-%As mentioned in the previous section, Thm.~\ref{DeterministicUniquenessTheorem} is a particular case of a more general result that forgoes the assumption that $\mathcal{H} \subseteq {[m] \choose k}$ is regular and satisfies the SIP.
-If instead we require only that the stars $\cap \sigma(i)$ intersect at singletons for all $i \leq q$ (assuming that the nodes of $\mathcal{H}$ are labeled in some order of non-increasing degree), we have that $\overline m \geq k|\mathcal{H}| / \deg(1)$ and, provided $\overline m < k|\mathcal{H}| / (\deg(1) - 1)$, the nonempty submatrix $J$ is of size equal to the largest number $p$ satisfying:
-%\begin{align}\label{pcond}
-%\sum_{i=\ell}^{m} \deg(i) > (\overline m + 1 - \ell) (\deg(\ell) - 1) \ \ \text{for all } \ell \leq p \leq q.
-%\end{align}
-%Specifically, $J$ contains all nodes of degree exceeding $\deg(p)$ and some subset of those with degreee equal to $\deg(p)$.
-For the benefit of the reader, we do not prove explicitly this more general result below; it can be discerned from how exactly Lemma \ref{NonEmptyLemma} is incorporated into the proof of Lem.~\ref{MainLemma}.
-%%%%%%%%%%%%%%%%
-
-%As mentioned in the previous section, Thm.~\ref{DeterministicUniquenessTheorem} is a particular case of a more general result, which requires a looser set of constraints on the hypergraph $\mathcal{H}$ and which applies to $n \times \overline m$ matrices $\mathbf{B}$ (and $\overline m$-dimensional codes $\mathbf{\overline x}_i$) with $\overline m \neq m$:
-
-%Fix $\overline m$ and suppose the assumptions of Thm.~\ref{DeterministicUniquenessTheorem} hold, only now with the constraints on $\mathcal{H} \subseteq {[m] \choose k}$ being just that $|\cap H(i)| = 1$ for all $i \leq q$ (assuming w.l.o.g.
-that the nodes of $\mathcal{H}$ are labeled in some order of non-increasing degree), and with more than $(k-1){\overline m \choose k}$ vectors $\mathbf{x}_i$ supported in g.l.p.
-on each $S \in \mathcal{H}$.
-Then we must have $\overline m \geq k|\mathcal{H}| / \deg(1)$ and, provided $\overline m < k|\mathcal{H}| / (\deg(1) - 1)$, the guarantee \eqref{Cstable} holds for a submatrix $\mathbf{A}_J$, where $J \subseteq[m]$ is nonempty and of a size equal to the largest number $p$ satisfying:
-%\begin{align}\label{pcond}
-%\sum_{i=\ell}^{m} \deg(i) > (\overline m + 1 - \ell) (\deg(\ell) - 1) \ \ \text{for all } \ell \leq p \leq q.
-%\end{align}
-%Specifically, $J$ consists of the union of the set of all nodes of degree exceeding $\deg(p)$ and some subset of those nodes with degrees equal to $\deg(p)$.
-
-%For the benefit of the reader, we prove below the case where we forgo only the constraint that $\overline m = m$.
-This yields the implication $\overline m \geq m$ and \eqref{pcond} reduces to $|J| = \overline m - r(\overline m - m)$.
-The extension to the general result above can be seen by examining how exactly Lemma \ref{NonEmptyLemma} is incorporated into the overall proof.
-
-% ======== b - PDa =========
-
-% WITH EXPLICIT J SUBSCRIPT
-%We begin our proof of Thm.~\ref{DeterministicUniquenessTheorem} by showing how dictionary recovery \eqref{Cstable} already implies sparse code recovery \eqref{b-PDa} when $\mathbf{A}_J$ satisfies \eqref{SparkCondition} and \mbox{$\varepsilon < L_{2k}(\mathbf{A}_J) / C_1$}.
-%, assuming that $\overline m = m$ without loss of generality.
-%Consider any $2k$-sparse $\mathbf{x} \in \mathbb{R}^m$ and note that $\|\mathbf{x}\|_1 \leq \sqrt{2k}  \|\mathbf{x}\|_2$. By definition of $L_{2k}$ in \eqref{Ldef}, we have:
-%\begin{align}\label{stuff}
-%\|\mathbf{x}_J - &( \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x} )_J\|_1 \nonumber
-%\leq \frac{\|(\mathbf{BPD})_J(\mathbf{x}_J - (\mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x})_J)\|_2}{L_{2k}((\mathbf{BPD})_J)} \\ \nonumber
-%&\leq \frac{\|( (\mathbf{BPD})_J - \mathbf{A}_J) \mathbf{x}_J\|_2 + \|\mathbf{A}_J\mathbf{x}_J - \mathbf{B}_J\mathbf{\overline x}_J\|_2}{L_{2k}((\mathbf{BPD})_J)} \\
-%&\leq \frac{C_1\varepsilon \|\mathbf{x}_J\|_1 + \varepsilon}{L_{2k}((\mathbf{BPD})_J)},
-%\end{align}
-%where the term $C_1\varepsilon \|\mathbf{x}_J\|_1$ in the numerator above is a consequence of the triangle inequality applied to \eqref{Cstable}.
-
-%It remains for us to bound the denominator.  By the reverse triangle inequality:
-%\begin{align*}
-%\|(\mathbf{BPD})_J\mathbf{x}_J\|_2 
-%&\geq | \|\mathbf{A}_J\mathbf{x}_J\|_2 - \|(\mathbf{A}_J - (\mathbf{BPD})_J)\mathbf{x}_J\|_2 | \\
-%&\geq \sqrt{2k} (L_{2k}(\mathbf{A}_J) -  C_1\varepsilon) \|\mathbf{x}_J\|_2,
-%\end{align*}
-%
-%wherein removal of the absolute value is justified since $C_1\varepsilon < L_{2k}(\mathbf{A}_J)$.
-We therefore have that $L_{2k}((\mathbf{BPD})_J) \geq L_{2k}(\mathbf{A}_J) - C_1\varepsilon  > 0$, and \eqref{b-PDa} then follows from \eqref{stuff}.
-
-% WITHOUT J SUBSCRIPT
-We begin our proof of Thm.~\ref{DeterministicUniquenessTheorem} by showing how dictionary recovery \eqref{Cstable} already implies sparse code recovery \eqref{b-PDa} when $\mathbf{A}$ satisfies \eqref{SparkCondition} and \mbox{$\varepsilon < L_{2k}(\mathbf{A}) / C_1$}.
-We temporarily assume (without loss of generality) that $\overline m = m$, so as to omit an otherwise requisite subscript $(\cdot)_J$ around certain matrices and vectors.
-By definition of $L_{2k}$ in \eqref{Ldef}, and noting that $\sqrt{k} \|\mathbf{v}\|_2 \geq \|\mathbf{v}\|_1$ for $k$-sparse $\mathbf{v}$, we have for all $i \in [N[$:
-\begin{align}\label{stuff}
-\|\mathbf{x}_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_i \|_1 \nonumber
-&\leq \frac{\|\mathbf{BPD}(\mathbf{x}_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_i)\|_2}{L_{2k}(\mathbf{BPD})} \\ \nonumber
-&\leq \frac{\|( \mathbf{BPD} - \mathbf{A}) \mathbf{x}_i\|_2 + \|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline x}_i\|_2}{L_{2k}(\mathbf{BPD})} \\
-&\leq \frac{C_1\varepsilon \|\mathbf{x}_i\|_1 + \varepsilon}{L_{2k}(\mathbf{BPD})},
-\end{align}
-%\begin{align}\label{stuff}
-%\frac{ \|\mathbf{x} - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x} \|_1 } { \|\mathbf{D}^{-1}\|_1 }  \
-%&\leq \|\mathbf{Dx} - \mathbf{P}^{\top}\mathbf{\overline x} \|_1 \\ \nonumber
-%&\leq \frac{\|\mathbf{BP}(\mathbf{D}\mathbf{x} - \mathbf{P}^{\top}\mathbf{\overline x})\|_2}{L_{2k}(\mathbf{BP})} \\ \nonumber
-%&\leq \frac{\|( \mathbf{BPD} - \mathbf{A}) \mathbf{x}\|_2 + \|\mathbf{A}\mathbf{x} - \mathbf{B}\mathbf{\overline x}\|_2}{L_{2k}(\mathbf{BP})} \\
-%&\leq \frac{C_1\varepsilon \|\mathbf{x}\|_1 + \varepsilon}{L_{2k}(\mathbf{BP})},
-%\end{align}
-where the first term in the numerator above follows from the triangle inequality and \eqref{Cstable}.
-
-It remains for us to bound the denominator. For any $2k$-sparse $\mathbf{x}$, we have by the triangle inequality:
-\begin{align*}
-\|\mathbf{BPD}\mathbf{x}\|_2 
-&\geq \|\mathbf{A}\mathbf{x}\|_2 - \|(\mathbf{A} - \mathbf{BPD})\mathbf{x}\|_2 \\
-&\geq \sqrt{2k} (L_{2k}(\mathbf{A}) -  C_1\varepsilon) \|\mathbf{x}\|_2,
-\end{align*}
-
-%\begin{align*}
-%\|\mathbf{BP}\mathbf{x}\|_2 
-%&\geq \|\mathbf{A}\mathbf{D}^{-1}\mathbf{x}\|_2 - \|(\mathbf{A} - \mathbf{BPD})\mathbf{D}^{-1}\mathbf{x}\|_2 \\
-%&\geq \sqrt{2k} (L_{2k}(\mathbf{A}) -  C_1\varepsilon) \|\mathbf{D}^{-1}\mathbf{x}\|_2, \\ 
-%&\geq \sqrt{2k} (L_{2k}(\mathbf{A}) -  C_1\varepsilon) \|\mathbf{D}^{-1}\|_{?} \| \mathbf{x}\|_2,
-%\end{align*}
-%
-We therefore have that $L_{2k}(\mathbf{BPD}) \geq L_{2k}(\mathbf{A}) - C_1\varepsilon  > 0$, and \eqref{b-PDa} then follows from \eqref{stuff}.
-The reader may also verify that $L_{2k}(\mathbf{BP}) \geq L_{2k}(\mathbf{BPD}) / \|\mathbf{D}\|_1$.
-
-The heart of the matter is therefore \eqref{Cstable}, which we now establish beginning with the important special case of $k = 1$.
-
-\begin{proof}[Proof of Thm.~\ref{DeterministicUniquenessCorollary} for $k=1$]
-Since the only 1-uniform hypergraph with the SIP is $[m]$, which is obviously regular, we require only $\mathbf{x}_i = c_i \mathbf{e}_i$ for $i \in [m]$, with $c_i \neq 0$ to guarantee  linear independence.
-While we have yet to define $C_1$ generally, in this case we may set $C_1 = 1/ \min_{\ell \in [m]} |c_{\ell}|$ so that $\varepsilon < L_2(\mathbf{A})  \min_{\ell \in [m]} |c_{\ell}|$.
-
-Fix $\mathbf{A} \in \mathbb{R}^{n \times m}$ satisfying $L_2(\mathbf{A}) > 0$, since here we have $2\mathcal{H} = {[m] \choose 2}$, and suppose some $\mathbf{B}$ and $1$-sparse $\mathbf{\overline x}_i \in \mathbb{R}^{\overline m}$ have  $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \varepsilon < L_2(\mathbf{A}) / C_1$ for all $i$.
-Then, there exist $\overline{c}_1, \ldots, \overline{c}_m \in \mathbb{R}$ and a map $\pi: [m] \to [\overline m]$ such that:
-\begin{align}\label{1D}
-\|c_i\mathbf{A}_i - \overline{c}_i\mathbf{B}_{\pi(i)}\|_2 \leq \varepsilon,\ \ \text{for $i \in [m]$}.
-\end{align} 
-Note that $\overline{c}_i \neq 0$, since otherwise we would reach the following contradiction: $\|\mathbf{A}_i \|_2 \leq C_1 |c_i| \|\mathbf{A}_i \|_2  \leq C_1\varepsilon < L_2(\mathbf{A}) \leq L_1(\mathbf{A}) = \min_{i \in [m]} \|\mathbf{A}_{i}\|_2$.
-%implies by \eqref{delrho} the contradiction $|c_i| < \min_{\ell \in [m]} | c_\ell |$.
-
-We now show that $\pi$ is injective (in particular, a permutation if $\overline m = m$).
-Suppose that $\pi(i) = \pi(j) = \ell$ for some $i \neq j$ and $\ell$.
-Then, $\|c_{i}\mathbf{A}_{i} - \overline{c}_{i} \mathbf{B}_{\ell}\|_2  \leq \varepsilon$ and $\|c_{j}\mathbf{A}_{j} - \overline{c}_{j}\mathbf{B}_{\ell}\|_2 \leq \varepsilon$, and we have: %Scaling and summing these inequalities by $|\overline{c}_{i}|$ and $|\overline{c}_{j}|$, respectively, and applying the triangle inequality to annihilate the terms in $\mathbf{B}_\ell$, we obtain:
-\begin{align*}
-(|\overline{c}_{i}| + |\overline{c}_{j}|) \varepsilon
-&\geq |\overline{c}_{i}| \|c_{j}\mathbf{A}_{j} - \overline{c}_{j}\mathbf{B}_{\ell}\|_2  + |\overline{c}_{j}| \|c_{i}\mathbf{A}_{i} - \overline{c}_{i} \mathbf{B}_{\ell}\|_2 \nonumber \\
-&\geq \|\mathbf{A}(\overline{c}_{i}c_{j} \mathbf{e}_{j} - \overline{c}_{j}c_{i}\mathbf{e}_{i})\|_2 \nonumber \\ 
-&\geq \sqrt{2}  L_2(\mathbf{A}) \|\overline{c}_{i}c_{j} \mathbf{e}_{j} - \overline{c}_{j}c_{i}\mathbf{e}_{i}\|_2 \nonumber \\
-&\geq  L_2(\mathbf{A}) \left( |\overline{c}_{i}| + |\overline{c}_{j}| \right) \min_{\ell \in [m]} |c_\ell |,
-\end{align*}
-contradicting our assumed upper bound on $\varepsilon$. Hence, the map $\pi$ is injective and so $\overline m \geq m$. %Setting $\overline J = \pi([m])$ and
-
-Letting $\mathbf{P}$ and $\mathbf{D}$ be the $\overline m \times \overline m$ permutation and invertible diagonal matrices with, respectively, columns $\mathbf{e}_{\pi(i)}$ and $\frac{\overline{c}_i}{c_i}\mathbf{e}_i$ for $i \in [m]$ (otherwise, $\mathbf{e}_{i}$ for $i \in [\overline{m}] \setminus [m]$), we may rewrite \eqref{1D} to see that for all $i \in [m]$:
-\begin{align*}
-\|\mathbf{A}_i - (\mathbf{BPD})_i\|_2 
-= \|\mathbf{A}_i - \frac{\overline{c}_i}{c_i}\mathbf{B}_{\pi(i)}\|_2 
-\leq \frac{\varepsilon}{|c_i|} 
-\leq C_1\varepsilon.
-\end{align*}
-%\vspace{-.2 cm}
-\end{proof}
-
-An extension of the proof to the general case $k < m$ requires some additional tools to derive the general expression \eqref{Cdef1} for $C_1$.
-These include a generalized notion of distance (Def.~\ref{dDef}) and angle (Def.~\ref{FriedrichsDefinition}) between subspaces as well as a stability result in combinatorial matrix analysis (Lem.~\ref{MainLemma}).
-
-\begin{definition}\label{dDef}
-For $\mathbf{u} \in \mathbb R^m$ and vector spaces $U,V \subseteq \mathbb{R}^m$, let $\text{\rm dist}(\mathbf{u}, V) := \min \{\| \mathbf{u}-\mathbf{v} \|_2: \mathbf{v} \in V\}$ and define:
-\begin{align}
-d(U,V) := \max_{\mathbf{u} \in U, \ \|\mathbf{u}\|_2 \leq 1} \text{\rm dist}(\mathbf{u},V).
-\end{align}
-\end{definition}
-
-We note the following facts about $d$. Clearly, 
-\begin{align}\label{UsubU}
-U' \subseteq U \implies d(U',V) \leq d(U,V).
-\end{align}
-From \cite[Ch.~4 Cor.~2.6]{Kato2013}, we also have: %Kato p.223
-\begin{align}\label{dimLem}
-d(U,V) < 1 \implies \dim(U) \leq \dim(V),
-\end{align}
-and from \cite[Lem.~3.2]{Morris10}:
-\begin{align}\label{eqdim}
-\dim(U) = \dim(V) \implies d(U,V) = d(V,U).
-\end{align}
-
-The following is our result in combinatorial matrix analysis; it contains most of the complexity in the proof of Thm.~\ref{DeterministicUniquenessTheorem}.
-
-\begin{lemma}\label{MainLemma}
-If an $n \times m$ matrix $\mathbf{A}$ has $L_{2\mathcal{H}}(\mathbf{A}) > 0$ for some $r$-regular $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP, then the following holds for $C_2 > 0$ given by \eqref{Cdef2}:
-
-Fix $\varepsilon < L_2(\mathbf{A}) / C_2$. If for some $n \times \overline m$ matrix $\mathbf{B}$ and map $\pi: \mathcal{H} \mapsto {[\overline m] \choose k}$,
-\begin{align}\label{GapUpperBound}
-d(\bm{\mathcal{A}}_S, \bm{\mathcal{B}}_{\pi(S)}) \leq \varepsilon, \ \  \text{for $S \in \mathcal{H}$},
-\end{align}
-then $\overline m \geq m$, and provided $\overline m (r-1) < mr$, there is a permutation matrix $\mathbf{P}$ and invertible diagonal $\mathbf{D}$ such that:
-\begin{align}\label{MainLemmaBPD}
-\|\mathbf{A}_i - (\mathbf{B}\mathbf{PD})_i\|_2 \leq C_2 \varepsilon, \ \  \text{for } i \in J,
-\end{align}
-for some $J \subseteq [m]$ of size \mbox{$m - (r-1)(\overline m - m)$}.
-\end{lemma}
-
-%\begin{lemma}\label{MainLemma}
-%Fix $\mathbf{A} \in \mathbb{R}^{n \times m}$ with $L_\mathcal{H}(\mathbf{A}) > 0$ for some regular $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP.
-There exists a constant $C_2 > 0$ for which the following holds for all $\varepsilon < L_2(\mathbf{A}) / C_2$:
-
-%If a matrix $\mathbf{B} \in \mathbb{R}^{n \times m}$ and map $\pi: E \mapsto {m \choose k}$ satisfy:
-%\begin{align}\label{GapUpperBound}
-%d(\text{\rm span}\{\mathbf{A}_{S}\}, \bm{\mathcal{B}}_{\pi(S)}) \leq \varepsilon, \ \ \text{for $S \in \mathcal{H}$},
-%\end{align}
-%then there exist a permutation matrix $\mathbf{P}$ and invertible diagonal matrix $\mathbf{D}$ such that:
-%\begin{align}\label{MainLemmaBPD}
-%\|\mathbf{A}_j - \mathbf{BPD}_j\|_2 \leq C_2 \varepsilon, \ \  \text{for } j \in [m],
-%\end{align}
-%\end{lemma}
-
-We present the constant $C_2$ (a function of $\mathbf{A}$ and $\mathcal{H}$) relative to a quantity used in \cite{Deutsch12} to analyze the convergence of the ``alternating projections" algorithm for projecting a point onto the intersection of subspaces.
-We incorporate this quantity into the following definition, which we refer to in our proof of Lem.~\ref{DistanceToIntersectionLemma} in the Appendix; specifically, we use it to bound the distance between a point and the intersection of subspaces given an upper bound on its distance from each subspace.
-
-\begin{definition}\label{FriedrichsDefinition}
-For a collection of real subspaces $\mathcal{V} = \{V_i\}_{i=1}^\ell$, define $\xi(\mathcal{V}) := 0$ when $|\mathcal{V}| = 1$, and otherwise:
-\begin{align}\label{xi}
-\xi^2(\mathcal{V}) := 1 -  \max \prod_{i=1}^{\ell-1} \sin^2  \theta \left(V_i, \cap_{j>i} V_j \right) ,
-\end{align} 
-%
-where the maximum is taken over all ways of ordering 
-%\footnote{We modify the quantity in \cite{Deutsch12} in this way since the subspace ordering is irrelevant to our purpose.} 
-the $V_i$ and the angle $\theta \in (0,\frac{\pi}{2}]$ is defined implicitly as \cite[Def.~9.4]{Deutsch12}:
-\begin{align*}
-\cos{\theta(U,W)} := \max\left\{ |\langle \mathbf{u}, \mathbf{w} \rangle|: \substack{ \mathbf{u} \in U \cap (U \cap W)^\perp, \ \|\mathbf{u}\|_2 \leq 1 \\ \mathbf{w} \in W \cap (U \cap W)^\perp, \  \|\mathbf{w}\|_2 \leq 1 } \right\}.
-\end{align*}
-\end{definition}
-Note that $\theta \in (0,\frac{\pi}{2}]$ implies $0 \leq \xi < 1$, and that $\xi(\mathcal{V}') \leq \xi(\mathcal{V})$ when $\mathcal{V}' \subseteq \mathcal{V}$.\footnote{We acknowledge the counter-intuitive property: $\theta =  \pi/2$ when $U \subseteq W$.}
-
-The constant $C_2 > 0$ of Lem.~\ref{MainLemma} can now be expressed as:  
-\begin{align}\label{Cdef2}
-	C_2(\mathbf{A}, \mathcal{H}) := \frac{ (r+1) \max_{j \in [m]} \|\mathbf{A}_j\|_2}{ 1- \max_{\mathcal{G} \in {\mathcal{H} \choose r+1}} \xi( \bm{\mathcal{A}}_\mathcal{G} ) }.
-\end{align}
-
-We next define the constant $C_1 > 0$ of Thm.~\ref{DeterministicUniquenessTheorem} in terms of $C_2$.
-Given vectors $\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$, let $\mathbf{X}$ denote the $m \times N$ matrix with columns $\mathbf{x}_i$ and let $I(S)$ denote the set of indices $i$ for which $\mathbf{x}_i$ is supported in $S$.
-We define:
-\begin{align}\label{Cdef1}
-C_1(\mathbf{A}, \mathcal{H}, \{\mathbf{x}_i\}_{i=1}^N) := \frac{ C_2(\mathbf{A}, \mathcal{H}) } { \min_{S \in \mathcal{H}} L_k(\mathbf{AX}_{I(S)}) }.
-\end{align}
-Given the assumptions of Thm.~\ref{DeterministicUniquenessTheorem} on $\mathbf{A}$ and the $\mathbf{x}_i$, this expression for $C_1$ is well-defined\footnote{\label{note1}To see this, fix $S \in \mathcal{H}$ and $k$-sparse $\mathbf{c}$.
-Using the definitions, we have $\|\mathbf{AX}_{I(S)}\mathbf{c}\|_2 \geq \sqrt{k} L_\mathcal{H}(\mathbf{A})\|\mathbf{X}_{I(S)}\mathbf{c}\|_2 \geq k L_\mathcal{H}(\mathbf{A}) L_k(\mathbf{X}_{I(S)})\|\mathbf{c}\|_2$.
-Thus, $L_k(\mathbf{AX}_{I(S)}) \geq \sqrt{k} L_\mathcal{H}(\mathbf{A}) L_k(\mathbf{X}_{I(S)}) > 0$, since $L_{\mathcal{H}}(\mathbf{A}) \geq L_{2\mathcal{H}}(\mathbf{A})> 0$ and $L_k(\mathbf{X}_{I(S)}) > 0$ by general linear position of the $\mathbf{x}_i$.} and yields an upper bound on $\varepsilon$ consistent with that proven sufficient in the case $k=1$ considered at the beginning of this section.\footnote{When $\mathbf{x}_i = c_i\mathbf{e}_i$, we have $C_2 \geq 2\|\mathbf{A}_i\|_2$ and the denominator in \eqref{Cdef1} becomes $\min_{i \in [m]} |c_i| \|\mathbf{A}_i\|_2$; hence, $C_1 \geq 2 / \min_{i \in [m]} |c_i|$.}
-% C_2(\mathbf{A}, \mathcal{H}) := \frac{ (r+1) \max_{j \in [m]} \|\mathbf{A}_j\|_2}{ \min_{\mathcal{G} \in {\mathcal{H} \choose r} \cup {\mathcal{H} \choose r+1}} \xi( \{ \bm{\mathcal{A}}_S \}
-
-The practically-minded reader should note that the explicit constants $C_1$ and $C_2$ are effectively computable: the quantity $L_k$ may be calculated as the smallest singular value of a certain matrix, while the quantity $\xi$ involves computing ``canonical angles'' between subspaces, which reduces again to an efficient singular value decomposition.
-There is no known fast computation of $L_k$ in general, however, since even $L_{k} > 0$ is NP-hard \cite{tillmann2014computational}, although 
-efficiently computable bounds have been proposed (e.g., via the ``mutual coherence" of a matrix \cite{donoho2003optimally}); alternatively, 
-fixing $k$ yields polynomial complexity.
-Moreover, calculating $C_2$ requires an exponential number of queries to $\xi$ unless $r$ is held fixed, too (e.g., the ``cyclic order'' hypergraphs described above have $r=k$).
-Thus, as presented, $C_1$ and $C_2$ are not efficiently computable in general.
-% , but efficient subcases do exist and may be of practical relevance.
-
-\begin{proof}[Proof of Thm.~\ref{DeterministicUniquenessCorollary} for $k < m$] 
-We find a map $\pi: \mathcal{H} \to {[m] \choose k}$ for which the distance $d(\bm{\mathcal{A}}_S, \bm{\mathcal{B}}_{\pi(S)})$ is controlled by $\varepsilon$ for all $S \in \mathcal{H}$.
-Applying Lem.~\ref{MainLemma} then completes the proof.
-%We shall show that for every $S \in \mathcal{H}$ there is some $\overline S \in {[\overline m] \choose k}$ for which the distance $d(\bm{\mathcal{A}}_S, \bm{\mathcal{B}}_{\overline S})$ is controlled by $\varepsilon$.
-Applying Lem.~\ref{MainLemma} with the map $\pi$ defined by $S \mapsto \overline S$ then completes the proof.
-
-Fix $S \in \mathcal{H}$.
-Since there are more than $(k-1){\overline m \choose k}$ vectors $\mathbf{x}_i$ supported in $S$, by the pigeonhole principle there must be some $\overline S \in {[\overline m] \choose k}$ and a set of $k$ indices $K \subseteq I(S)$ for which all $\mathbf{\overline x}_i$ with $i \in K$ are supported in $\overline S$.
-It also follows\footnotemark[\ref{note1}] from $L_{2\mathcal{H}}(\mathbf{A}) > 0$ and the general linear position of the $\mathbf{x}_i$ that $L_k(\mathbf{AX}_{K}) > 0$; that is, the columns of the $n \times k$ matrix $\mathbf{AX}_K$ form a basis for $\bm{\mathcal{A}}_S$.
-
-Fixing $\mathbf{y} \in \bm{\mathcal{A}}_S \setminus \{\mathbf{0}\}$, there then exists $\mathbf{c} = (c_1, \ldots, c_k) \in \mathbb{R}^k \setminus \{\mathbf{0}\}$ such that $\mathbf{y} = \mathbf{AX}_K\mathbf{c}$.
-Setting \mbox{$\mathbf{\overline{y}} = \mathbf{B\overline{X}}_K\mathbf{c}$, which is in $\bm{\mathcal{B}}_{\overline S}$}, we have by triangle inequality:
-\begin{align*}
-\|\mathbf{y} - \mathbf{\overline{y}}\|_2 
-%&= \|\sum_{i=1}^k c_i(\mathbf{AX}_K - \mathbf{B\overline{X}}_K)_i\|_2
-&= \|(\mathbf{AX}_K - \mathbf{B\overline{X}}_K)\mathbf{c}\|_2
-%\leq \varepsilon \sum_{i=1}^k |c_i| \\
-\leq \varepsilon \|\mathbf{c}\|_1
-\leq \varepsilon \sqrt{k}  \|\mathbf{c}\|_2  \\
-&\leq \frac{\varepsilon}{L_k(\mathbf{AX}_K)} \|\mathbf{y}\|_2,
-\end{align*}
-where the last inequality uses \eqref{Ldef}. From Def.~\ref{dDef}:
-\begin{align}\label{rhs222}
-d(\bm{\mathcal{A}}_S, \bm{\mathcal{B}}_{\overline S}) 
-\leq \frac{\varepsilon}{  L_k(\mathbf{AX}_{K}) } 
-\leq \frac{\varepsilon}{  L_k(\mathbf{AX}_{I(S)}) } 
-\leq \varepsilon \frac{C_1}{C_2}.
-\end{align}
-%
-Finally, apply Lem.~\ref{MainLemma} with $\varepsilon < L_2(\mathbf{A})/C_1$ and $\pi(S) := \overline S$. % L_2(A) > 0 by def of L, since L_2H(A) > 0 and H covers [m]
-\end{proof}
-
-Before moving on to the proof of Thm.~\ref{SLCopt}, we briefly revisit our discussion on sample complexity from the end of the previous section.
-While an exponential number of samples may very well prove to be necessary in the deterministic or almost-certain case, our proof of Thm.~\ref{DeterministicUniquenessTheorem} can be extended to hold with some probability for \emph{any} number of samples by alternative appeal to a probabilistic pigeonholing at the point early in the proof where the (deterministic) pigeonhole principle is applied to show that for every $S \in \mathcal{H}$, there exist $k$ vectors $\mathbf{x}_i$ supported on $S$ whose corresponding $\mathbf{\overline x}_i$ all share the same support.\footnote{A famous example of such an argument is the counter-intuitive ``birthday paradox", which demonstrates that the probability of two people having the same birthday in a room of twenty-three is greater than 50\%.}
-Given insufficient samples, this argument has some less-than-certain probability of being valid for each $S \in \mathcal{H}$.
-Nonetheless, simulations with small hypergraphs confirm that the probability of success very quickly approaches one once the number of samples $N$ surpasses a small fraction of the deterministic sample complexity.
-
-\begin{proof}[Proof of Thm.~\ref{SLCopt}]
-We bound the number of $k$-sparse $\mathbf{\overline x}_i$ from below and then apply Thm.~\ref{DeterministicUniquenessCorollary}. 
-%We now apply this fact to bound the number of $k$-sparse $\mathbf{\overline x}_i$. 
-Let $n_p$ be the number of $\mathbf{\overline x}_i$ with $\|\mathbf{\overline x}_i\|_0 = p$.
-Since the $\mathbf{x}_i$ are all $k$-sparse, by \eqref{minsum} we have:
-\begin{align*}
-%\mbox{$k \sum_{p = 0}^{\overline m} n_p \geq \sum_{i=0}^N \|\mathbf{x}_i\|_0 \geq \sum_{i=0}^N \|\mathbf{\overline x}_i\|_0 = \sum_{p=0}^{\overline m} p n_p.$}
-\sum_{p=0}^{\overline m} p n_p =  \sum_{i=0}^N \|\mathbf{\overline x}_i\|_0
-\leq \sum_{i=0}^N \|\mathbf{x}_i\|_0 
-\leq kN
-\end{align*}
-Since $N = \sum_{p = 0}^{\overline m} n_p$, we then have $\sum_{p = 0}^{\overline m} (p-k) n_p \leq 0$. Splitting the sum yields:
-\begin{align}\label{eqn}
-\sum_{p = k+1}^{\overline m} n_p \leq \sum_{p = k+1}^{\overline m} (p-k) n_p \leq \sum_{p = 0}^k (k-p)n_p \leq k \sum_{p = 0}^{k-1} n_p,
-\end{align}
-%
-demonstrating that the number of vectors $\mathbf{\overline x}_i$ that are \emph{not} $k$-sparse is bounded above by how many are $(k-1)$-sparse.
-
-Next, observe that no more than $(k-1)|\mathcal{H}|$ of the $\mathbf{\overline x}_i$ share a support $\overline S$ of size less than $k$.
-Otherwise, by the pigeonhole principle, there is some $S \in \mathcal{H}$ and a set of $k$ indices $K \subseteq I(S)$ for which all $\mathbf{x}_i$ with $i \in K$ are supported in $S$; as argued previously, \eqref{rhs222} follows.
-It is simple to show that $L_2(\mathbf{A}) \leq \max_j\|\mathbf{A}_j\|_2$, and since $0 \leq \xi < 1$, the right-hand side of \eqref{rhs222} is less than one for $\varepsilon < L_2(\mathbf{A})/C_1$.
-Thus, by \eqref{dimLem} we would have the contradiction $k = \dim(\bm{\mathcal{A}}_S) \leq \dim(\bm{\mathcal{B}}_{\overline S}) \leq |\overline S| < k.$
-
-The total number of $(k-1)$-sparse vectors $\mathbf{\overline x}_i$ thus cannot exceed $|\mathcal{H}|(k-1){ \overline m \choose k-1}$.
-By \eqref{eqn}, no more than $|\mathcal{H}|k(k-1){ \overline m \choose k-1}$ vectors $\mathbf{\overline x}_i$ are not $k$-sparse.
-Since for every $S \in \mathcal{H}$ there are over $(k-1)\left[ {\overline m \choose k} + |\mathcal{H}|k{ \overline m \choose k-1} \right]$ vectors $\mathbf{x}_i$ supported there, it must be that more than $(k-1){\overline m \choose k}$ of them have corresponding $\mathbf{\overline x}_i$ that are $k$-sparse.
-The result now follows from Thm.~\ref{DeterministicUniquenessCorollary}, noting by the triangle inequality that $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline x}_i\| \leq 2\eta$ for $i = 1, \ldots, N$.
-\end{proof}
-
-%\begin{proof}[Proof (sketch) of Thm.~\ref{robustPolythm}]
-%Let $\textbf{M}$ be the matrix with columns $\mathbf{A}\mathbf{x}_i$, $i \in [N]$.
-Consider the polynomial $\prod_{S \in {[N] \choose 2k}} \sum_{S' \in {[n] \choose 2k}} (\det \textbf{M}_{S',S})^2$ in the indeterminate entries of $\mathbf{A}$ and $\mathbf{x}_i$, with notation as in Sec.~\ref{Results}.
-%It can be checked that when this polynomial is nonzero for a substitution of real numbers for the indeterminates, all of the genericity requirements on $\mathbf{A}$ and $\mathbf{x}_i$ in our proofs of stability in Thm.~\ref{DeterministicUniquenessTheorem} are satisfied (in particular, the spark condition \eqref{SparkCondition} on $\mathbf{A}$).
-%\end{proof}
-
-%\begin{proof}[Proof (sketch) of Cor.~\ref{ProbabilisticCor}]
-%First, note that if a set of measure spaces $\{(X_{\ell}, \Sigma_{\ell}, \nu_{\ell})\}_{\ell=1}^p$ has that $\nu_{\ell}$ is absolutely continuous with respect to $\mu$ for all $\ell \in [p]$, where $\mu$ is the standard Borel measure on $\mathbb{R}$, then the product measure $\prod_{\ell=1}^p \nu_{\ell}$ is absolutely continuous with respect to the standard Borel product measure on $\mathbb{R}^p$.
-% for space:  (e.g.,  \cite{folland2013real}).
-%By Thm.~\ref{robustPolythm}, there is a polynomial that is nonzero when $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$; in particular, stability holds almost surely.
-%\end{proof}
-
-\section{Discussion}\label{Discussion}
-
-A main motivation for this work is the emergence of seemingly unique representations from sparse coding models trained on natural data, despite the varied assumptions underlying the many algorithms in current use.
-Our results constitute an important step toward explaining these phenomena as well as unifying many publications on the topic by deriving general deterministic conditions under which identification of parameters in this model is not only possible but also robust to uncertainty in measurement and model choice.
-
-We have shown that, given sufficient data, the problem of determining a dictionary and sparse codes with minimal support size (Prob.~\ref{OptimizationProblem}) reduces to an instance of Prob.~\ref{InverseProblem}, to which our main result (Thm.~\ref{DeterministicUniquenessTheorem}) applies: every dictionary and sequence of sparse codes consistent with the data are equivalent up to inherent relabeling/scaling ambiguities and a discrepancy (error) that scales linearly with the measurement noise or modeling inaccuracy.
-The constants we provide are explicit and computable; as such, there is an effective procedure that sufficiently affirms if a proposed solution to these problems is indeed unique up to noise and inherent ambiguities, although it is not efficient in general.
-
-%A compelling feature of this model is its simple instantiation of the principle of Occam's razor: a natural video, for instance, is modeled as a linear combination of a small number of spatiotemporal building blocks, each representing an archetypical feature latent in the data.
-
-%For theoretical neuroscience in particular, dictionary learning and related methods have recovered characteristic components of natural images \cite{Olshausen96, hurri1996image, bell1997independent, van1998independent} and sounds \cite{bellsejnowski1996, smithlewicki2006} that reproduce response properties of certain cortical neurons.
-
-%to the recovery of ``mouse neuronal activity representing location on a track \cite{agarwal2014spatially}
-
-%Moreover, we show that even if the meta-parameter for the number of dictionary elements is overestimated, a subset of parameters may still be identifiable up to noise.
-
-Beyond an extension of existing noiseless guarantees \cite{Hillar15} to the noisy regime and their novel application to Prob.~\ref{OptimizationProblem}, our work contains a theory of combinatorial designs for support sets key to identification of dictionaries.
-We incorporate this idea into a fundamental lemma in matrix theory (Lem.~\ref{MainLemma}) that draws upon the definition of a matrix lower bound (\ref{Ldef}) induced by a hypergraph.
-The new insight offered by this combinatorial approach allows for guaranteed recovery of some or all dictionary elements even if: 1) dictionary size is overestimated, 2) data cover only a polynomial number of distinct sparse supports, and 3) dictionaries do not satisfy the spark condition.
-
-The absence of any assumptions about dictionaries solving Prob.~\ref{InverseProblem} was a major technical obstruction in proving Thm.~\ref{DeterministicUniquenessTheorem}.
-We sought such a general guarantee because of the practical difficulty in ensuring that an algorithm maintain a dictionary satisfying the spark condition \eqref{SparkCondition} at each iteration, an implicit requirement of all previous works except \cite{Hillar15}; indeed, even certifying a dictionary has this property is NP-hard \cite{tillmann2014computational}.
-
-One direct application of this work is to theoretical neuroscience, wherein our theorems justify the mathematical soundness of one of the few hypothesized theories of bottleneck communication in the brain \cite{Isely10}: that sparse neural population activity is recoverable from its noisy linear compression through a randomly constructed (but unknown) wiring bottleneck by any biologically plausible unsupervised sparse coding method that solves Prob.~\ref{DeterministicUniquenessTheorem} or \ref{SLCopt} (e.g., \cite{rehnsommer2007, rozell2007neurally, pehlevan2015normative}).\footnote{We refer the reader to \cite{ganguli2012compressed} for more on interactions between dictionary learning and neuroscience.}
-
-In fact, uniqueness guarantees with minimal assumptions apply to all areas of data science and engineering that utilize learned sparse structure.
-For example, several groups have applied compressed sensing to signal processing tasks; for instance, in MRI analysis \cite{lustig2008compressed}, image compression \cite{Duarte08}, and even the design of an ultrafast camera \cite{Gao14}.
-It is only a matter of time before these systems incorporate dictionary learning to encode and decode signals (e.g., in a device that learns structure from motion \cite{kong2016prior}), just as scientists have used sparse coding to make sense of their data \cite{jung2001imaging, agarwal2014spatially, lee2016sparse, wu2016stability}.
-
-Assurances offered by our theorems certify that different devices and algorithms learn equivalent representations given enough data from statistically identical systems.\footnote{To contrast with the current hot topic of ``Deep Learning'', there are few such uniqueness guarantees for these models of data; moreover, even small noise can dramatically alter their output \cite{goodfellow2014explaining}.}
-Indeed, a main reason for the sustained interest in dictionary learning as an unsupervised method for data analysis seems to be the assumed well-posedness of parameter identification in the model, confirmation of which forms the core of our findings.
-
-We close with some challenges left open by our work.
-All conditions stated here guaranteeing the uniqueness and stability of sparse representations have only been shown sufficient; it remains open, therefore, to extend them to necessary conditions, be they on required sample size, the structure of support set hypergraphs, or tolerable error bounds.
-On this last note, we remark that our deterministic treatment considers always the ``worst-case" noise, whereas the ``effective" noise sampled from a concentrated distribution might be significantly reduced, especially for high-dimensional data.
-It would be of great practical benefit to see how drastically all conditions can be relaxed by requiring only probabilistic guarantees in this way, or in the spirit of our discussion on probabilistic pigeonholing to reduce sample complexity (as in the famous ``birthday paradox") following the proof of Thm.~\ref{DeterministicUniquenessTheorem}.
-
-Another interesting question raised by our work is for which special cases is it efficient to check that a solution to Prob.~\ref{InverseProblem} or \ref{OptimizationProblem} is unique up to noise and inherent ambiguities.
-Considering that the sufficient conditions we have described for checking this in general are NP-hard to compute, are the necessary conditions hard?
-Are Probs.~\ref{InverseProblem} and \ref{OptimizationProblem} then also hard (e.g., see \cite{Tillmann15})?
-Finally, since Prob.~\ref{SLCopt} is intractable in general, but efficiently solvable by $\ell_1$-norm minimization when the matrix is known (and has a large enough lower bound over sparse domains \cite{eldar2012compressed}), is there a version of Thm.~\ref{SLCopt} certifying when Prob.~\ref{OptimizationProblem} can be solved efficiently in full by similar means?
-% [*** Incorporate this open problem with more words ***]
-
-We hope these remaining challenges pique the interest of the community to pick up where we have left off and that the theoretical tools showcased here may be of use to this end.
-
-%We close with some challenges left open by our work.
-First, there is the basic problem of proving optimal lower bounds on sufficient sample size $N$ guaranteeing the uniqueness and stability of sparse representations.
-The pigeonholing argument in the proof of Thm.~\ref{DeterministicUniquenessTheorem} is loose in that it assigns to each support $S \in \mathcal{H}$ a corresponding support $\overline S$ without consideration of previously matched pairs; although we doubt tightening in this way will lead to sub-exponential sample sizes.
-Sample complexity will also benefit from lowering the number of required supports, i.e.
-the size of regular uniform hypergraphs satisfying the SIP.
-The regularity requirement on support hypergraphs can be loosened to allow for certain non-regular hypergraphs satisfying constraints on the degree sequence of nodes; though we impose regularity for clarity of exposition.
-It is then natural to ask: what is the smallest hypergraph satisfying the required constraints forgiven $m$ and $k$?
-Finally, the error bounds can be improved by tightening the constant $C_1$, e.g.
-via an improvement in Lemma ?.
-
-%Solving Prob.~\ref{SLCopt} directly is intractable in general since it necessitates, for each proposed dictionary $\mathbf{B}$, a combinatorial search for the supports of the associated sparse codes $\mathbf{\overline x}_i$.
-A common work-around is to convexify the problem (for fixed $\mathbf{B}$) by substituting the norm $\|\cdot\|_0$ with $\|\cdot\|_1$, impelled the fact that matrices $\mathbf{A}$ with large enough $L_{2k}(\mathbf{A})$ induce the same sparse codes via minimization of either norm \cite{?}.
-To this end, the lower bound $L_{2k}(\mathbf{BP}) \geq (L_{2k}(\mathbf{A}) - C_1\varepsilon) / \|\mathbf{D}\|_1$ implied by Thm.~\ref{DeterministicUniquenessTheorem} hints at conditions on the generating dictionary $\mathbf{A}$ and $k$-sparse codes $\mathbf{x}_i$ under which \emph{all} matrices $\mathbf{B}$ (of bounded column-norm) that solve Prob.~\ref{OptimizationProblem} also share this property of $\mathbf{A}$ by virtue of uniqueness and stability.
-One might then imagine an inference procedure whereby sparse codes are inferred via minimization of $\|\cdot\|_1$, but solutions still evaluated by their collective support size, yielding unique optimal solutions to Prob.~\ref{SLCopt} if only constraints could be imposed such that the learning procedure eventually guides $\mathbf{B}$ through an optimal dictionary.
-% (e.g.
-the dictionary is a member of a known finite set).
-
-\textbf{Acknowledgement.} We thank Fritz Sommer and Darren Rhea for early thoughts, and Ian Morris for posting \eqref{eqdim} online.
-
-%\section{EXTRA}
-%An additional consequence of Thm.~\ref{DeterministicUniquenessTheorem} of potential practical relevance to is the implied lower bound $L_{2k}(\mathbf{BPD}) \geq L_{2k}(\mathbf{A}) - C_1\varepsilon$ in the case where $\mathbf{A}$ satisfies \eqref{SparkCondition}.
-Since solving Prob.~\ref{SLCopt} directly requires a combinatorial search over sparse supports for the $\mathbf{\overline x}_i$ for each proposed dictionary $\mathbf{B}$, rendering it intractable in general, a common strategy is to replace the $\ell_0$-norm in \eqref{minsum} with the $\ell_1$-norm, thereby transforming the inference of sparse $\mathbf{\overline x}_i$ for a fixed dictionary $\mathbf{B}$ into a convex optimization solvable by a linear program.
-A major advance in compressive sensing was the discovery that, for fixed $\mathbf{B}$, solutions to \eqref{minsum} using either norm yield the same sparse vectors $\mathbf{\overline x}_i$ (up to noise) provided $L_{2k}(\mathbf{B})$ is large enough \cite{?}.
-What our results hint at are conditions on the generating dictionary $\mathbf{A}$ and $k$-sparse codes $\mathbf{x}_i$ under which \emph{all} matrices $\mathbf{B}$ (of bounded column-norm) that solve Prob.~\ref{OptimizationProblem} also share this property by virtue of uniqueness and stability; that is, conditions which guarantee that the sparse codes $\mathbf{\overline x}_i$ solving Prob.~\ref{OptimizationProblem} also solve the convexified problem when the corresponding dictionary $\mathbf{B}$ is held fixed.
-It remains to determine, however, what practical conditions preclude matrices that don't solve Prob.~\ref{OptimizationProblem} from nonetheless solving the convexified problem.
-%
-%Regardless, an implication of the above observation is that the following algorithm solves Prob.~\ref{OptimizationProblem} without appeal to combinatorial search:
-%\begin{enumerate}
-%\item List all matrices $\mathbf{B}$.
-%\item For each matrix $\mathbf{B}$, solve $\mathbf{\overline x}_i = \arg \min \|\mathbf{v}\|_1$ s.t. $\|\mathbf{Bv} - \mathbf{z}_i\| \leq \eta$ for $i = 1, \ldots, N$.
-%\item Quantify the proposed solution $\mathbf{B}$ and $\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N$ as $\rho(\mathbf{B}, \mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N) = \sum_{i=1}^{N} \|\mathbf{\overline x}_i\|_0$.
-%\item Output $\arg \min_{\mathbf{B}, \mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N} \left( \rho \right)$.
-% \end{enumerate}
-
-%Since its inception some twenty years ago, sparse coding has become a standard tool in signal analysis, yielding myriad insights into the structure of natural signals across a variety of scientific domains.
-In this work,
-
-%We make a final remark about the tightness of our results and the computability of our derived constants.
-%We remark that our constants have been derived for deterministic ``worst-case'' noise, whereas the ``effective'' noise might be smaller when sampled from a distribution.
-
-%Our results suggest that this correspondence could be due to the ``universality'' of sparse representations in natural data, an early idea in neural theory \cite{pitts1947}.
-
-% \vspace{-.2 cm}
-
-%\showacknow % Display the acknowledgments section
-
-\bibliographystyle{IEEEtran}
-\bibliography{chazthm_ieee_trans_sig}
-
-% \vspace{-.2 cm}
-
-\section{Appendix}\label{proofs}
-
-We prove Lem.~\ref{MainLemma} after the following auxiliary lemmas.  % stating and proving some auxiliary lemmas. 
-%First, note that since $\|\mathbf{A}\mathbf{x}\|_2 \leq \max_j\|\mathbf{A}_j\|_2\|\mathbf{x}\|_1$ and $\|\mathbf{x}\|_1 \leq \sqrt{k} \|\mathbf{x}\|_2$ for $k$-sparse $\mathbf{x}$, by \eqref{Ldef} we have the following frequently applied inequality:
-%\begin{align}\label{delrho}
-%L_{k'}(\mathbf{A}) \leq  \max_j\|\mathbf{A}_j\|_2 \ \ \text{for all $k' \leq 2k$}.
-%\end{align}
-
-% and then sketch the proofs of Thm.~\ref{robustPolythm} and Cor.~\ref{ProbabilisticCor}.
-
-%\begin{lemma}\label{spanIntersectionLemma}
-%Let $\mathbf{M} \in \mathbb{R}^{n \times m}$. If every $2k$ columns of $\mathbf{M}$ are linearly independent, then for any $F \subseteq {[m] \choose k}$:
-%\begin{align*}
-%\text{\rm span}\{\mathbf{M}_{\cap F}\}  = \bigcap_{S \in F} \text{\rm span}\{\mathbf{M}_S\}.
-%\end{align*}
-%\end{lemma}
-%\begin{proof}
-%Using induction on $|F|$, it is enough to prove the lemma when $|F| = 2$; but this case follows directly from the assumption.
-%\end{proof}
-
-\begin{lemma}\label{spanIntersectionLemma}
-If $f: V \to W$ is injective, then $f\left(\cap_{i=1}^\ell V_i \right) =  \cap_{i=1}^\ell f\left(V_i\right)$ for any $V_1, \ldots, V_\ell \subseteq V$. ($f(\emptyset):=\emptyset$.)
-%In particular, if for some $E \in 2^{[m]}$ the map $M \in \mathbb{R}^{n \times m}$ is injective on $\cup_{S \in \mathcal{H}} \text{span}\{e_i\}_{i \in S}$ then $\text{span}\{ M_{\cap_{S \in \mathcal{H}} S} \} = \cap_{S \in \mathcal{H}} \text{span}\{M_S\}$.
-\end{lemma}
-\begin{proof}
-By induction, it is enough to prove the case $\ell = 2$.
-Clearly, for any map $f$, if $w \in f(U \cap V)$ then $w \in f(U)$ and $w \in f(V)$; hence, $w \in f(U) \cap f(V)$.
-If $w \in f(U) \cap f(V)$, then $w \in f(U)$ and $w \in f(V)$; thus, $w = f(u) = f(v)$ for some $u \in U$ and $v \in V$, implying $u = v$ by injectivity of $f$.
-It follows that $u \in U \cap V$ and $w \in f(U \cap V)$.
-\end{proof}
-In particular, if a matrix $\mathbf{A}$ satisfies $L_{2\mathcal{H}}(\mathbf{A}) > 0$, then taking $V$ to be the union of subspaces consisting of vectors with supports in $2\mathcal{H}$, we have $\bm{\mathcal{A}}_{\cap \mathcal{G}} = \cap \bm{\mathcal{A}}_\mathcal{G}$ for all $\mathcal{G} \subseteq \mathcal{H}$.
-% \vspace{-.4 cm}
-
-\begin{lemma}\label{DistanceToIntersectionLemma}
-Let $\mathcal{V} = \{V_i\}_{i=1}^k$ be a set of two or more subspaces of $\mathbb{R}^m$, and set $V = \cap \mathcal{V} $.
-For  $\mathbf{u} \in \mathbb{R}^m$, we have (recall Defs.~\ref{dDef}~\&~\ref{FriedrichsDefinition}):
-\begin{align}\label{DTILeq}
-\text{\rm dist}(\mathbf{u}, V) \leq \frac{1}{1 - \xi(\mathcal{V})} \sum_{i=1}^k \text{\rm dist}(\mathbf{u}, V_i).
-\end{align}
-\end{lemma}
-\begin{proof} 
-% When $V = \{\mathbf{0}\}$, the result is trivial, so suppose otherwise.  
-Recall the projection onto the subspace $V \subseteq \mathbb{R}^m$ is the mapping $\Pi_V: \mathbb{R}^m \to V$ that associates with each $\mathbf{u}$ its unique nearest point in $V$; i.e., $\|\mathbf{u} - \Pi_V\mathbf{u}\|_2 = \text{\rm dist}(\mathbf{u}, V)$.
-By repeatedly applying the triangle inequality, we have:
-\begin{align}\label{f}
-\|\mathbf{u} - &\Pi_V\mathbf{u}\|_2 
-\leq \|\mathbf{u} - \Pi_{V_k} \mathbf{u}\|_2 + \|\Pi_{V_k}  \mathbf{u} - \Pi_{V_k}\Pi_{V_{k-1}}\mathbf{u}\|_2 \nonumber \\
-&\ \ \ \ \ \ \ \ \ \ \ + \cdots + \|\Pi_{V_k} \Pi_{V_{k-1}}\cdots \Pi_{V_1} \mathbf{u} - \Pi_V \mathbf{u}\|_2 \nonumber \\
-&\leq  \sum_{\ell=1}^k \|\mathbf{u} - \Pi_{V_{\ell}} \mathbf{u}\|_2 
-+ \|(\Pi_{V_k}\cdots\Pi_{V_{1}} - \Pi_V) \mathbf{u}\|_2,
-\end{align}
-where we have also used that the spectral norm of the orthogonal projections $\Pi_{V_{\ell}}$ satisfies $\|\Pi_{V_{\ell}}\|_2 \leq 1$ for all $\ell$.
-
-It remains to bound the second term in \eqref{f} by $\xi(\mathcal{V}) \|\mathbf{u} - \Pi_V\mathbf{u}\|_2$.
-First, note that $\Pi_{V_\ell} \Pi_V = \Pi_V$ and $\Pi_V^2 = \Pi_V$, so we have $\|(\Pi_{V_k} \cdots \Pi_{V_1} - \Pi_V) \mathbf{u} \|_2
-= \| ( \Pi_{V_k} \cdots\Pi_{V_1} - \Pi_V ) (\mathbf{u} - \Pi_V\mathbf{u})\|_2$. % \leq z\|\mathbf{u} - \Pi_V\mathbf{u}\|_2$.
-Consequently, inequality \eqref{DTILeq} follows from \cite[Thm.~9.33]{Deutsch12}:
-\begin{align}
-\|\Pi_{V_k}\Pi_{V_{k-1}}\cdots\Pi_{V_1} \mathbf{x} - \Pi_V\mathbf{x}\|_2 \leq z \|\mathbf{x}\|_2, \ \ \text{for all } \mathbf{x},
-\end{align}
-with \mbox{$z^2= 1 - \prod_{\ell =1}^{k-1}(1-z_{\ell}^2)$} and \mbox{$z_{\ell} = \cos\theta\left(V_{\ell}, \cap_{s=\ell+1}^k V_s\right)$} (recall $\theta$ from Def.~\ref{FriedrichsDefinition}), after substituting $\xi(\mathcal{V})$ for $z$ and rearranging terms.
-\end{proof}
-\begin{lemma}\label{NonEmptyLemma} 
-Fix an $r$-regular hypergraph $\mathcal{H} \subseteq 2^{[m]}$ satisfying the SIP.
-If the map $\pi: \mathcal{H} \to 2^{[\overline m]}$ has $\sum_{S \in \mathcal{H}} |\pi(S)| \geq \sum_{S \in \mathcal{H}} |S|$ and:
-\begin{align}\label{cond}
-	|\cap \pi(\mathcal{G})| \leq |\cap \mathcal{G} |,\ \ \   \text{for } \mathcal{G} \in {\mathcal{H} \choose r} \cup {\mathcal{H} \choose r+1},
-\end{align}
-%
-then $\overline m \geq m$; and if $\overline m  (r-1) < mr$, the map $i \mapsto \cap_{S \in \sigma(i)} \pi(S)$ is an injective function to $[\overline m]$ from some $J \subseteq [m]$ of size $m - (r-1)(\overline m - m)$ (recall $\sigma$ from Def.~\ref{sip}).
-%In particular, if $\overline m = m$ then $\pi$ is induced by a permutation on $[m]$.
-\end{lemma}
-
-\begin{proof}
-Consider the following set: $T_1 := \{(i, S): i \in \pi(S), S \in \mathcal{H}\}$, which numbers $|T_1| = \sum_{S \in \mathcal{H}} |\pi(S)| \geq \sum_{S \in \mathcal{H}} |S| = \sum_{i \in [m]} \deg_\mathcal{H}(i) = mr$ by $r$-regularity of $\mathcal{H}$.
-Note that $|T_1| \leq \overline m r$; otherwise, pigeonholing the tuples of $T_1$ with respect to their $\overline m$ possible first elements would imply that more than $r$ of the tuples in $T_1$ share the same first element.
-This cannot be the case, however, since then some $\mathcal{G} \in {\mathcal{H} \choose r+1}$ formed from any $r+1$ of their second elements would satisfy $\cap \pi(\mathcal{G}) \neq 0$; hence, $|\cap \mathcal{G}| \neq 0$ by \eqref{cond}, contradicting $r$-regularity of $\mathcal{H}$.
-It follows that $\overline m \geq m$.
-
-Suppose now that $\overline m (r-1) < mr$, so that $p := mr - \overline m (r-1)$ is positive and $|T_1| \geq \overline m (r - 1) + p$.
-Pigeonholing $T_1$ into $[\overline m]$ again, there are at least $r$ tuples in $T_1$ sharing some first element; that is, for some $\mathcal{G}_1 \subseteq \mathcal{H}$ of size $|\mathcal{G}_1| \geq r$, we have $|\cap \pi(\mathcal{G}_1)| \geq 1$ and (by \eqref{cond}) $|\cap \mathcal{G}_1| \geq 1$.
-Since no more than $r$ tuples of $T_1$ can share the same first element, we in fact have $|\mathcal{G}_1| = r$.
-It follows by $r$-regularity that $\mathcal{G}_1$ is a star of $\mathcal{H}$; hence, $|\cap \mathcal{G}_1| = 1$ by the SIP and $|\cap \pi(\mathcal{G}_1)|  = 1$ by \eqref{cond}.
-
-If $p=1$, then we are done.
-Otherwise, define $T_2 := T_1 \setminus \{(i,S) \in T_1: i = \cap \pi(\mathcal{G}_1)\}$, which contains $|T_2| = |T_1| - r \geq (\overline m - 1)(r-1) + (p-1)$ ordered pairs having $\overline m - 1$ distinct first indices.
-Pigeonholing $T_2$ into $[\overline m - 1]$ and repeating the above arguments produces the star $\mathcal{G}_2 \in {\mathcal{H} \choose r}$ with intersection $\cap \mathcal{G}_2$ necessarily distinct (by $r$-regularity) from $\cap \mathcal{G}_1$.
-Iterating this procedure $p$ times in total yields the stars $\mathcal{G}_i$ for which $\cap\mathcal{G}_i \mapsto \cap \pi(\mathcal{G}_i)$ defines an injective map to $[\overline m]$ from $J = \{\cap \mathcal{G}_1, \ldots, \cap \mathcal{G}_p\} \subseteq [m]$.
-\end{proof}
-
-\begin{proof}[Proof of Lem.~\ref{MainLemma}]
-%We will show that the bound \eqref{GapUpperBound} trickles through the intersection semi-lattices of $\{\bm{\mathcal{A}}_S\}_{S \in \mathcal{H}}$ and $\{\bm{\mathcal{B}}_{\overline S}\}_{\overline S \in \pi(\mathcal{H})}$ to yield \eqref{MainLemmaBPD} by virtue of the SIP.
-We begin by showing that $\dim(\bm{\mathcal{B}}_{\pi(S)}) = \dim(\bm{\mathcal{A}}_S)$ for all $S \in \mathcal{H}$.
-Note that since $\|\mathbf{A}\mathbf{x}\|_2 \leq \max_j\|\mathbf{A}_j\|_2\|\mathbf{x}\|_1$ and $\|\mathbf{x}\|_1 \leq \sqrt{k} \|\mathbf{x}\|_2$ for all $k$-sparse $\mathbf{x}$, by \eqref{Ldef} we have $L_2(\mathbf{A}) \leq \max_j\|\mathbf{A}_j\|_2$ and therefore (as $0 \leq \xi < 1$) the right-hand side of \eqref{GapUpperBound} is less than one.
-From \eqref{dimLem}, we have $|\pi(S)| \geq \dim(\bm{\mathcal{B}}_{\pi(S)}) \geq \dim(\bm{\mathcal{A}}_S) = |S|$, the final equality holding by injectivity of $\mathbf{A}_S$.
-As $|\pi(S)| = |S|$, the claim follows.
-Note, therefore, that $\mathbf{B}_{\pi(S)}$ has full-column rank for all $S \in \mathcal{H}$.
-
-We next demonstrate that \eqref{cond} holds.
-Fixing $\mathcal{G} \in {\mathcal{H} \choose r} \cup {\mathcal{H} \choose r+1}$, it suffices to show that $d(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}, \bm{\mathcal{A}}_{\cap \mathcal{G}} ) < 1$, since by \eqref{dimLem} we then have $|\cap \pi(\mathcal{G})| = \dim(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}) \leq \dim(\bm{\mathcal{A}}_{\cap \mathcal{G}}) = |\cap \mathcal{G}|$, with equalities from the full column-ranks of $\mathbf{A}_{S}$ and $\mathbf{B}_{\pi(S)}$ for all $S \in \mathcal{H}$.\footnote{Note that if ever $\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})} \neq \bf 0$ while $\cap \mathcal{G} = \emptyset$, we would have $d(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}, \bm 0 ) = 1$.
-However, that leads to a contradiction.} Observe that $d(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}, \bm{\mathcal{A}}_{\cap \mathcal{G}}  )
-\leq d\left( \cap \bm{\mathcal{B}}_{\pi(\mathcal{G})}, \cap \bm{\mathcal{A}}_\mathcal{G} \right)$ by \eqref{UsubU}, since trivially $\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})} \subseteq \cap \bm{\mathcal{B}}_{\pi(\mathcal{G})}$ and also $\bm{\mathcal{A}}_{\cap \mathcal{G}} = \cap \bm{\mathcal{A}}_\mathcal{G}$ by Lem.~\ref{spanIntersectionLemma}.
-Recalling Def.~\ref{dDef} and applying Lem.~\ref{DistanceToIntersectionLemma} yields:
-\begin{align}
-d\left( \cap \bm{\mathcal{B}}_{\pi(\mathcal{G})}, \cap \bm{\mathcal{A}}_\mathcal{G} \right)
-&\leq \max_{\mathbf{u} \in \cap \bm{\mathcal{B}}_{\pi(\mathcal{G})}, \ \|\mathbf{u}\|_2 \leq 1} \sum_{S \in \mathcal{G}} \frac{ \text{\rm dist}\left( \mathbf{u},\bm{\mathcal{A}}_{S} \right) }{ 1 - \xi( \bm{\mathcal{A}}_\mathcal{G} ) } \nonumber \\
-&= \sum_{S \in \mathcal{G}} \frac{ d\left( \cap \bm{\mathcal{B}}_{\pi(\mathcal{G})},\bm{\mathcal{A}}_{S} \right) }{ 1 - \xi( \bm{\mathcal{A}}_\mathcal{G} ) }, \nonumber
-\end{align}
-passing the maximum through the sum.
-Since $\cap \bm{\mathcal{B}}_{\pi(\mathcal{G})} \subseteq \bm{\mathcal{B}}_{\pi(S)}$ for all $S \in \mathcal{G}$, by \eqref{UsubU} the numerator of each term in the sum above is bounded by \mbox{$d\left( \bm{\mathcal{B}}_{\pi(S)},\bm{\mathcal{A}}_{S} \right) = d\left(\bm{\mathcal{A}}_{S}, \bm{\mathcal{B}}_{\pi(S)} \right) \leq \varepsilon$}, with the equality from \eqref{eqdim} since $\dim(\bm{\mathcal{B}}_{\pi(S)}) = \dim(\bm{\mathcal{A}}_S)$.
-Thus, altogether:
-\begin{align}\label{last}
-d(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}, \bm{\mathcal{A}}_{\cap \mathcal{G}} )
-\leq \frac{|\mathcal{G}| \varepsilon}{1 - \xi( \bm{\mathcal{A}}_\mathcal{G} )}
-\leq \frac{C_2 \varepsilon}{\max_j\|\mathbf{A}_j\|_2},
-\end{align}
-recalling the definition of $C_2$ in \eqref{Cdef2}.
-Lastly, since $C_2 \varepsilon < L_2(\mathbf{A}) \leq \max_j\|\mathbf{A}_j\|_2$, we have $d(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}, \bm{\mathcal{A}}_{\cap \mathcal{G}} ) \leq 1$ and therefore \eqref{cond} holds.
-
-%Keeping in mind that $d(U',V) \leq d(U,V)$ whenever $U' \subseteq U$ and applying (in order) Lem.~\ref{spanIntersectionLemma}, Lem.~\ref{DistanceToIntersectionLemma}, \eqref{eqdim}, \eqref{GapUpperBound}, and \eqref{Cdef2} gives:
-%\begin{align}\label{randoml}
-%d(&\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}, \bm{\mathcal{A}}_{\cap \mathcal{G}}  ) 
-%\leq d\left( \cap \bm{\mathcal{B}}_{\pi(\mathcal{G})}, \cap \bm{\mathcal{A}}_\mathcal{G} \right)
-%\leq \sum_{T \in \mathcal{G}} \frac{ d\left( \cap \bm{\mathcal{B}}_{\pi(\mathcal{G})},\bm{\mathcal{A}}_{T} \right) }{ 1 - \xi( \bm{\mathcal{A}}_\mathcal{G} ) } \nonumber \\
-%&\leq \sum_{T \in \mathcal{G}} \frac{ d\left( \bm{\mathcal{B}}_{\pi(T)},\bm{\mathbf{A}}_{T} \right) }{ 1 - \xi( \bm{\mathcal{A}}_\mathcal{G} ) }
-%\leq \frac{|\mathcal{G}| \varepsilon}{1 - \xi( \bm{\mathcal{A}}_\mathcal{G} )} 
-%\leq \frac{C_2 \varepsilon}{\max_j\|\mathbf{A}_j\|_2},
-%\end{align}
-%
-%which is less than one, since $C_2 \varepsilon < L_2(\mathbf{A}) \leq \max_j\|\mathbf{A}_j\|_2$.
-
-Applying Lem.~\ref{NonEmptyLemma}, the association $i \mapsto \cap_{S \in \sigma(i)} \pi(S)$ is an injective map $\overline \pi: J \to [\overline m]$ for some $J \subseteq [m]$ of size $m - (r-1)(\overline m - m)$, and $\mathbf{B}_{\overline \pi(i)} \neq \mathbf{0}$ for all $i \in J$ since the columns of $\mathbf{B}_{\pi(S)}$ are linearly independent for all $S \in \mathcal{H}$.
-Letting $\overline \varepsilon := C_2 \varepsilon / \max_i \|\mathbf{A}_i\|_2$, it follows from \eqref{eqdim} and \eqref{last} that $d\left( \bm{\mathcal{A}}_i, \bm{\mathcal{B}}_{\overline \pi(i)} \right) = d\left(\bm{\mathcal{B}}_{\overline \pi(i)},  \bm{\mathcal{A}}_i \right)  \leq \overline \varepsilon$ for all $i \in J$.
-%Fixing $\overline \varepsilon = C_2\varepsilon$ and letting $c_i = \|\mathbf{A}_i\|_2^{-1}$, we thus have that for each $\mathbf{e}_i \in \mathbb{R}^m$ with $i \in J$ there exists some $\overline{c}_i \in \mathbb{R}$ such that $\|c_i\mathbf{A}\mathbf{e}_i - \overline{c}_i \mathbf{B}\mathbf{e}_{\overline \pi(i)}\|_2 \leq \overline \varepsilon < L_2(\mathbf{A}) \min_{i\in J} |c_i|$.
-But this is exactly the supposition in \eqref{1D}, and the result follows from the case $k=1$ in Sec.~\ref{DUT} applied to the submatrix $\mathbf{A}_J$.
-Setting $c_i := \|\mathbf{A}_i\|_2^{-1}$ so that $\|c_i\mathbf{Ae}_i\|_2 = 1$, by Def.~\ref{dDef} for all $i \in J$:
-\begin{align*}
-\min_{\overline c_i \in \mathbb{R}} \|c_i\mathbf{Ae}_i - \overline c_i \mathbf{Be}_{\overline \pi(i)} \|_2
-\leq d\left( \bm{\mathcal{A}}_i, \bm{\mathcal{B}}_{\overline \pi(i)} \right)
-\leq \overline \varepsilon,
-%&= \max_{\bm{u} \in \bm{\mathcal{A}}_i, \|\bm{u}\|_2 \leq 1} \text{dist}\left(\bm{u}, \bm{\mathcal{B}}_{\overline \pi(i)} \right) \\
-%&\geq  \text{dist}\left(c_i\bm{Ae}_i, \mathbf{Be}_{\overline \pi(i)} \right) \\
-%&= \min_{\overline c_i \in \mathbb{R}} \|c_i\bm{Ae}_i - \overline c_i \mathbf{Be}_{\overline \pi(i)} \|_2
-\end{align*}
-%
-for $\overline \varepsilon < L_2(\mathbf{A})\min_{i \in [m]}|c_i|$.
-But this is exactly the supposition in \eqref{1D}, with $J$ and $\overline \varepsilon$ in place of $[m]$ and $\varepsilon$, respectively.
-The same arguments of the case $k=1$ in Sec.~\ref{DUT} can then be made to show that for any $\overline m \times \overline m$ permutation and invertible diagonal matrices $\mathbf{P}$ and $\mathbf{D}$ with, respectively, columns $\mathbf{e}_{\pi(i)}$ and $\frac{\overline{c}_i}{c_i}\mathbf{e}_i$ for $i \in J$ (otherwise, $\mathbf{e}_{i}$ for $i \in [\overline{m}] \setminus J$), we have $\|\mathbf{A}_i - (\mathbf{B}\mathbf{PD})_i \|_2 \leq \overline  \varepsilon / |c_i|  \leq C_2 \varepsilon$ for all $i \in J$.
-\end{proof}
-
-%\section{Proofs of Thm.~\ref{robustPolythm} and Cor.~\ref{ProbabilisticCor}}
-
-%\clearpage
-
-%\section{$\ell_1$-norm Extension}
-%
-%\begin{problem}\label{OptimizationProblemL1}
-%Find a matrix $\mathbf{B}$ and vectors \mbox{$\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N \in \mathbb{R}^m$} that solve:
-%\begin{align}\label{minsum}
-%\min \sum_{i = 1}^N \|\mathbf{\overline x}_i\|_1 \ \ 
-%\text{subject to} \ \ \|\mathbf{z}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \eta, \ \text{for all $i$}.
-%\end{align}
-%\end{problem}
-
-%\begin{corollary}\label{SLCopt}
-%Fix $\alpha > 0$ and suppose all of the assumptions of Thm.\ref{DeterministicUniquenessTheorem} hold with the following modifications:
-%\begin{enumerate}
-%\item The coefficients of all $k$-sparse $\mathbf{x}_i$ are drawn from $[-\beta, \beta]$, where $\beta < \frac{\alpha(k+1)}{k}$.
-%\item More than $(k-1){\overline m \choose k} + q$ vectors $\mathbf{x}_i$ are supported in each $S \in \mathcal{H}$, where
-%\[ q = \left[\frac{\alpha}{\beta}(k+1) - k\right]^{-1}k|\mathcal{H}|(k-1){\overline m \choose k-1}. \]
-%\end{enumerate}
-%Then all solutions to Prob.~\ref{OptimizationProblemL1} for which the nonzero elements of all $\mathbf{\overline x}_i$ lie outside $[-\alpha, \alpha]$ necessarily satisfy the implications \eqref{Cstable} and \eqref{b-PDa} of Thm.~\ref{DeterministicUniquenessTheorem}.
-%\end{corollary}
-
-%\begin{proof}[Proof of Cor.~\ref{SLCopt}]
-%We bound the number of $k$-sparse $\mathbf{\overline x}_i$ and then apply Thm.~\ref{DeterministicUniquenessCorollary}.
-First, observe that no more than $(k-1)|\mathcal{H}|$ of the $\mathbf{\overline x}_i$ share a support $\overline S$ of size less than $k$; otherwise, by the pigeonhole principle, at least $k$ of these indices $i$ belong to the same $K \subseteq I(S)$ for some $S \in \mathcal{H}$ and (as argued previously) \eqref{rhs222} follows.
-Since the right-hand side of \eqref{rhs222} is less than one, by \eqref{dimLem} we have the contradiction $k = \dim(\bm{\mathcal{A}}_S) \leq \dim(\bm{\mathcal{B}}_{\overline S}) \leq |\overline S|.$ The total number of $(k-1)$-sparse vectors $\mathbf{\overline x}_i$ can thus not exceed $|\mathcal{H}|(k-1){ \overline m \choose k-1}$.
-
-%Next, observe that the assumptions of the lemma imply:
-%\begin{align*}
-%\alpha \sum_i \|\mathbf{\overline x}_i\|_0 \leq \sum_i \|\mathbf{\overline x}_i\|_1 \leq \sum_i \|\mathbf{x}_i\|_1 \leq \beta \sum_i \|\mathbf{x}_i\|_0.
-%\end{align*}
-
-%We now apply these facts to bound the number of $k$-sparse $\mathbf{\overline x}_i$.
-Let $n_p$ be the number of $\mathbf{\overline x}_i$ with $\|\mathbf{\overline x}_i\|_0 = p$.
-Since the $\mathbf{x}_i$ are all $k$-sparse, we have:
-%\begin{align*}
-%k \sum_{p = 0}^{\overline m} n_p = k N \geq \sum_{i=0}^N \|\mathbf{x}_i\|_0 \geq \frac{\alpha}{\beta} \sum_{i=0}^N \|\mathbf{\overline x}_i\|_0 = \frac{\alpha}{\beta} \sum_{p=0}^{\overline m} p n_p.
-%\end{align*}
-%Hence, 
-%\begin{align*}
-%\left[ \frac{\alpha(k+1)}{\beta} - k\right] \sum_{p = k+1}^{\overline m} n_p 
-%&\leq \sum_{p = k+1}^{\overline m} (\frac{\alpha}{\beta} p-k) n_p
-%\leq \sum_{p = 0}^k (k - \frac{\alpha}{\beta} p)n_p \\
-%&\leq k \sum_{p = 0}^k n_p 
-%\leq k(1-\frac{\alpha}{\beta})n_k + k|\mathcal{H}|(k-1){ \overline m \choose k-1}
-%\end{align*}
-
-%[Shit, we need $\alpha = \beta$.] Therefore, no more than $q$ vectors $\mathbf{\overline x}_i$ are \emph{not} $k$-sparse.
-Since for every $S \in \mathcal{H}$ there are over $(k-1){\overline m \choose k} + q$ vectors $\mathbf{x}_i$ supported there, it follows that more than $(k-1){\overline m \choose k}$ of them have corresponding $\mathbf{\overline x}_i$ that are $k$-sparse.
-The result now follows directly from Thm.~\ref{DeterministicUniquenessCorollary}.
-%\end{proof}
-
-%\pagebreak
-
-%\begin{corollary}\label{SLCoptL1}
-%If all of the assumptions of Thm.\ref{DeterministicUniquenessTheorem} hold, only now with more than $(k-1)\left[ {\overline m \choose k} + |\mathcal{H}|k{\overline m \choose k-1}\right]$ vectors $\mathbf{x}_i$ supported in each $S \in \mathcal{H}$, then every solution to Prob.~\ref{OptimizationProblemL1} for which the average absolute nonzero coefficient of the $\mathbf{\overline x}_i$ is bounded below by that of the $\mathbf{x}_i$ necessarily satisfies the implications \eqref{Cstable} and \eqref{b-PDa} of Thm.~\ref{DeterministicUniquenessTheorem}.
-%\end{corollary}
-
-%\begin{proof}[Proof of Cor.~\ref{SLCoptL1}]
-%Since the average absolute nonzero coefficient of the $\mathbf{x}_i$ is given by $\alpha = \sum_i \|\mathbf{x}_i\|_1 / \sum_i \|\mathbf{x}_i\|_0$, we have:
-%\begin{align*}
-%\alpha \sum_i \|\mathbf{\overline x}_i\|_0 \leq \sum_i \|\mathbf{\overline x}_i\|_1 \leq \sum_i \|\mathbf{x}_i\|_1 = \alpha \sum_i \|\mathbf{x}_i\|_0.
-%\end{align*}
-%
-%and the result follows by the same arguments as in the proof of Cor.~\ref{SLCopt}.
-%\end{proof}
-
-\end{document}

### 2020-07-16 manuscripts/thesis/appendix.tex
thesis

--- 2019-05-10 manuscripts/IEEE/final_submission.tex
@@
-% TODO: 
-% Make L_H a definition..? Change def of L to be 1-norm so we don't need these sqrt k's?
-% C_1 depends on J in Thm 1
-% also in proof of (7) x need not be *any* 2k-sparse vector...can instead restrict to some H...then 2k is restricted to half being on H.
-
-% Notes:
-%
-% Can we prove in a line or two that the inverse problem is stable by arguing that the function is bijective and closed therefore a homeomorphism?
-% Should we mention the notion of Grassmannian manifolds and that Theta is a metric on this space?
-% Change robustness to stability?
-%
-\documentclass[journal, twocolumn]{IEEEtran}
-
-% *** MATH PACKAGES ***
-\usepackage{amsmath, amssymb, amsthm} 
-\newtheorem{theorem}{Theorem}
-\newtheorem{lemma}{Lemma}
-\newtheorem{conjecture}{Conjecture}
-\newtheorem{problem}{Problem}
-\newtheorem{question}{Question}
-\newtheorem{proposition}{Proposition}
-\newtheorem{definition}{Definition}
-\newtheorem{corollary}{Corollary}
-\newtheorem{remark}{Remark}
-\newtheorem{example}{Example}
-
-\usepackage[pdftex]{graphicx}
-
-% *** ALIGNMENT PACKAGES ***
-\usepackage{array}
-\usepackage{cite}
-\usepackage{bm}
-
-% correct bad hyphenation here
-%\hyphenation{op-tical net-works semi-conduc-tor}
-
-\begin{document}
-
-%\title{When can a generating dictionary and sparse codes be recovered from noisy data?}
-%\title{When is the dictionary learning problem well-posed?}
-\title{On the uniqueness and stability of dictionaries \\ for sparse representation of noisy signals}
-%\title{When is the dictionary learning problem for sparse coding well-posed?}
-%\title{When is the sparsest representation unique?}
-%\title{When are sparse codes identifiable from their unknown noisy compressive measurements?}
-% FRITZ2: The title doesn't reflect the amount of new stuff, it seems incremental from the last one. It's not very meaningful.
-% FRITZ: Not everyone knows what well-posed means. You should mention recovery from noisy data in the title.
-
-\author{Charles~J.~Garfinkle and Christopher~J.~Hillar \\
-Redwood Center for Theoretical Neuroscience, Berkeley, CA, USA
-%\thanks{%e-mails: cjg@berkeley.edu, chillar@msri.org.  
-%CG and CH supported, in part, by NSF grant IIS-1219212 and the Statistical and Applied Mathematical Sciences Institute, under NSF DMS-1127914.}
-}
-
-\maketitle
-
-% \keywords{Sparse coding, dictionary learning, matrix factorization, compressed sensing, inverse problems, blind source separation}
-
-\begin{abstract}
-%Learning optimal dictionaries for sparse coding has exposed characteristic sparse features of many natural signals.
-However, there are few universal conditions guaranteeing the stability of such features in the presence of noise.
-Here, we prove very generally that optimal dictionaries and sparse codes are unique up to measurement error for all diverse enough datasets generated by the sparse coding model.
-Applications are given to data analysis, engineering, and neuroscience.
-Learning optimal dictionaries for sparse coding has exposed characteristic sparse features of many natural signals.
-However, universal guarantees of the stability of such features in the presence of noise are lacking.
-Here, we provide very general conditions guaranteeing when dictionaries yielding the sparsest encodings are unique and stable with respect to measurement or modeling error.
-We demonstrate that some or all original dictionary elements are recoverable from noisy data even if the dictionary fails to satisfy the spark condition, its size is overestimated, or only a polynomial number of distinct sparse supports appear in the data.
-Importantly, we derive these guarantees without requiring any constraints on the recovered dictionary beyond a natural upper bound on its size.
-Our results also yield an effective procedure sufficient to affirm if a proposed solution to the dictionary learning problem is unique within bounds commensurate with the noise.
-We suggest applications to data analysis, engineering, and neuroscience and close with some remaining challenges left open by our work.
-\end{abstract}
-
-% Optional adjustment to line up main text (after abstract) of first page with line numbers, when using both lineno and twocolumn options.
-% You should only change this length when you've finalised the article contents.
-
-\section{Introduction}\label{Intro}
-\IEEEPARstart{S}{parse} coding is a common modern approach to pattern analysis in signal processing whereby each of $N$ observed $n$-dimensional signal samples is viewed as a (noisy) linear combination of at most $k$ elementary waveforms drawn from some unknown ``dictionary" of size $m \ll N$ (see \cite{Zhang15} for a comprehensive review).
-%\IEEEPARstart{A}{}common modern approach to pattern analysis in signal processing is to view each of $N$ observed $n$-dimensional signal samples as a (noisy) linear combination of at most $k$ elementary waveforms drawn from some unknown ``dictionary" of size $m \ll N$ (see \cite{Zhang15} for a comprehensive review).
-Optimizing dictionaries subject to this and related sparsity constraints has revealed seemingly characteristic sparse structure in several signal classes of current interest (e.g., in vision \cite{wang2015sparse}).
-
-Of particular note are the seminal works in the field \cite{Olshausen96, hurri1996image, bell1997independent, van1998independent}, which discovered that dictionaries optimized for coding small patches of ``natural" images share qualitative similarities with linear filters estimated from response properties of simple-cell neurons in mammalian visual cortex.
-Curiously, these waveforms (e.g., ``Gabor'' wavelets) appear in dictionaries learned by a variety of algorithms trained over different natural image datasets, suggesting that learned features in natural signals may, in some sense, be canonical \cite{donoho2001can}.
-
-Motivated by these discoveries and more recent work relating compressed sensing \cite{eldar2012compressed} to a theory of information transmission through random wiring bottlenecks in the brain \cite{Isely10}, we address when dictionaries for sparse representation are indeed identifiable from data.
-Answers to this question may also have implications in practice wherever an appeal is made to latent sparse structure of data (e.g., forgery detection \cite{hughes2010, olshausen2010applied}; brain recordings \cite{jung2001imaging, agarwal2014spatially, lee2016sparse}; and gene expression \cite{wu2016stability}).
-
-While several algorithms have been recently proposed to provably recover unique dictionaries under specific conditions (see \cite[Sec.~I-E]{Sun16} for a summary of the state-of-the-art), few theorems can be invoked to justify the consistency of inference under this model of data more broadly.
-To our knowledge, a universal guarantee of the uniqueness and stability of learned dictionaries and the sparse representations they induce over noisy data has yet to appear in the literature.
-% in justifying the identification of forged paintings by their anomalous sparse representations \cite{hughes2010},
-
-Here, we prove very generally that uniqueness and stability is a typical property of sparse dictionary learning.
-More specifically, we show that matrices injective on a sparse domain are identifiable from \mbox{$N = m(k-1){m \choose k} + m$} noisy linear combinations of $k$ of their $m$ columns up to an error that is linear in the noise (Thm.~\ref{DeterministicUniquenessTheorem}).
-In fact, provided $n \geq \min(2k,m)$, in almost all cases the problem is well-posed, as per Hadamard \cite{Hadamard1902}, given a sufficient amount of data (Thm.~\ref{robustPolythm} and Cor.~\ref{ProbabilisticCor}).
-
-Our guarantees also hold for a related (and perhaps more commonly posed, e.g.
-\cite{rehnsommer2007}) optimization problem seeking a dictionary minimizing the average number of elementary waveforms required to reconstruct each sample of the dataset (Thm.~\ref{SLCopt}).
-To practical benefit, our results impose no restrictions on learned dictionaries (e.g., that they, too, be injective over some sparse domain) beyond an upper bound on dictionary size, which is necessary in any case to avoid trivial solutions (e.g., allowing $m = N$).
-%That is, every pair of solutions of comparable size has some number of dictionary elements in common (up to noise), and similarly so for the coefficients of sparse codes they induce.
-
-More precisely, let $\mathbf{A} \in \mathbb R^{n \times m}$ be a matrix with columns $\mathbf{A}_j$ ($j = 1,\ldots,m$) and let dataset $Z$ consist of measurements:
-\begin{align}\label{LinearModel}
-\mathbf{z}_i = \mathbf{A}\mathbf{x}_i + \mathbf{n}_i,\ \ \  \text{$i=1,\ldots,N$},
-\end{align}
-for $k$-\emph{sparse} $\mathbf{x}_i \in \mathbb{R}^m$ having at most $k<m$ nonzero entries and \emph{noise} $\mathbf{n}_i \in \mathbb{R}^n$, with bounded norm $\| \mathbf{n}_i \|_2 \leq  \eta$ representing our worst-case uncertainty in measuring the product $\mathbf{A}\mathbf{x}_i$.
-We first consider the following formulation of sparse coding.
-%The first mathematical problem we consider is the following.
-
-\begin{problem}\label{InverseProblem}
-Find a dictionary matrix $\mathbf{B}$ and $k$-sparse codes $\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N$ that satisfy $\|\mathbf{z}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \eta$ for all $i = 1,\ldots,N$.
-\end{problem}
-
-Note that every solution to Prob.~\ref{InverseProblem} represents infinitely many equivalent alternatives $\mathbf{BPD}$ and $\mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_1, \ldots, \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_N$ parametrized by a choice of permutation matrix $\mathbf{P}$ and invertible diagonal matrix $\mathbf{D}$.
-Identifying these ambiguities (labelling and scale) yields a single orbit of solutions represented by any particular set of elementary waveforms (the columns of $\mathbf{B}$) and their associated sparse coefficients (the entries of $\mathbf{\overline x}_i$) that reconstruct each data point $\mathbf{z}_i$.
-
-Previous theoretical work addressing the noiseless case $\eta =0$ (e.g., \cite{li2004analysis, Georgiev05, Aharon06, Hillar15}) for matrices $\mathbf{B}$ having exactly $m$ columns has shown that a solution to Prob.~\ref{InverseProblem}, when it exists, is unique up to such relabeling and rescaling provided the $\mathbf{x}_i$ are sufficiently diverse and $\mathbf{A}$ satisfies the \textit{spark condition}:
-\begin{align}\label{SparkCondition}
-\mathbf{A}\mathbf{x}_1 = \mathbf{A}\mathbf{x}_2 \implies \mathbf{x}_1 = \mathbf{x}_2, \ \ \ \text{for all $k$-sparse } \mathbf{x}_1, \mathbf{x}_2,
-\end{align}
-%
-which is necessary to guarantee the uniqueness of arbitrary $k$-sparse $\mathbf{x}_i$.
-We generalize these results to the practical setting  $\eta > 0$ by considering the following natural notion of stability with respect to measurement error.
-
-\begin{definition}\label{maindef}
-Fix $Y = \{ \mathbf{y}_1, \ldots, \mathbf{y}_N\} \subset \mathbb{R}^n$.
-We say $Y$ has a \textbf{$k$-sparse representation in $\mathbb{R}^m$} if there exists a matrix $\mathbf{A}$ and $k$-sparse $\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$ such that $\mathbf{y}_i = \mathbf{A}\mathbf{x}_i$ for all $i$.
-This representation is \textbf{stable} if for every $\delta_1, \delta_2 \geq 0$, there exists some $\varepsilon = \varepsilon(\delta_1, \delta_2)$ that is strictly positive for positive $\delta_1$ and $\delta_2$ such that if $\mathbf{B}$ and $k$-sparse $\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N \in \mathbb{R}^m$ satisfy:
-\begin{align*}
-	\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \varepsilon(\delta_1, \delta_2),\ \   \text{for all $i=1,\ldots,N$},
-\end{align*}
-then there is some permutation matrix $\mathbf{P}$ and invertible diagonal matrix $\mathbf{D}$ such that for all $i, j$:
-\begin{align}\label{def1}
-\|\mathbf{A}_j - (\mathbf{BPD})_j\|_2 \leq \delta_1 \ \text{and} \ \|\mathbf{x}_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_i\|_1 \leq \delta_2.
-\end{align}
-\end{definition}
-
-To see how Prob.
-\ref{InverseProblem} motivates Def.
-\ref{maindef}, suppose that $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$ and fix $\delta_1, \delta_2$ to be the desired accuracies of recovery in \eqref{def1}.
-Consider any dataset $Z$ generated as in \eqref{LinearModel} with $\eta \leq \frac{1}{2} \varepsilon(\delta_1, \delta_2)$.
-Using the triangle inequality, it follows that any $n \times m$ matrix $\mathbf{B}$ and $k$-sparse $\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N$ solving Prob.~\ref{InverseProblem} are necessarily within $\delta_1$ and $\delta_2$ of the original dictionary $\mathbf{A}$ and codes $\mathbf{x}_1, \ldots, \mathbf{x}_N$, respectively.\footnote{We mention that the different norms in \eqref{def1} reflect the distinct meanings typically ascribed to the dictionary and sparse codes in modeling data.}
-
-The main result of this work is a very general uniqueness theorem for sparse coding (Thm.~\ref{DeterministicUniquenessTheorem}) directly 
-implying (Cor.~\ref{DeterministicUniquenessCorollary}), which guarantees that sparse representations of a dataset $Z$ are unique up to noise whenever generating dictionaries $\mathbf{A}$ satisfy a spark condition on supports and the original sparse codes $\mathbf{x}_i$ are sufficiently diverse (e.g., Fig.~\ref{noisyrecovery}).
-Moreover, we provide an explicit, computable $\varepsilon(\delta_1, \delta_2)$ in (\ref{epsdel}) that is linear in desired accuracy $\delta_1$, and essentially so in $\delta_2$.
-
-In the next section, we give formal statements of these findings.
-We then extend the same guarantees (Thm.~\ref{SLCopt}) to the following alternate formulation of dictionary learning, which minimizes the total number of nonzero entries in sparse codes.
-
-\begin{problem}\label{OptimizationProblem}
-Find matrices $\mathbf{B}$ and vectors \mbox{$\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N$} solving:
-\begin{align}\label{minsum}
-\min \sum_{i = 1}^N \|\mathbf{\overline x}_{i}\|_0 \ \
-\text{subject to} \ \ \|\mathbf{z}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \eta, \ \text{for all $i$}.
-\end{align}
-\end{problem}
-
-Our development of Thm.~\ref{DeterministicUniquenessTheorem} is general enough to provide some uniqueness and stability even when generating $\mathbf{A}$ do not fully satisfy (\ref{SparkCondition}) and recovery dictionaries $\mathbf{B}$ have more columns than $\mathbf{A}$.
-Moreover, the approach incorporates a combinatorial theory for designing generating codes that should be of independent interest.
-We also give brief arguments adapting our results to dictionaries and codes drawn from probability distributions (Cor.~\ref{ProbabilisticCor}).
-The technical proofs of Thms.~\ref{DeterministicUniquenessTheorem} and ~\ref{SLCopt} are deferred to Sec.~\ref{DUT}, following some necessary definitions and a fact in combinatorial matrix analysis (Lem.~\ref{MainLemma}; proven in the Appendix).
-Finally, we discuss in Sec.~\ref{Discussion} applications of our mathematical observations as well as open questions.
-%The Appendix contains a proof of Lem.~\ref{MainLemma}.
-
-\section{Results}\label{Results}
-
-%Denote by $\mathbf{x}^J$ the subvector formed from the entries of $\mathbf{x}$ indexed by $J$. 
-%A set of $k$-sparse vectors is said to be in \emph{general linear position} when any $k$ of them are linearly independent.
-
-Precise statements of our results require that we first identify some combinatorial criteria on the supports\footnote{Recall that a vector $\mathbf{x}$ is said to be \emph{supported} in $S$ when $\mathbf{x} \in \text{\rm span}\{\mathbf{e}_j: j\in S\}$, with $\mathbf{e}_j$ forming the standard column basis.} of sparse vectors.
-Let $\{1, \ldots, m\}$ be denoted $[m]$, its power set $2^{[m]}$, and ${[m] \choose k}$ the set of subsets of $[m]$ of size $k$.
-A \emph{hypergraph} on vertices $[m]$  is simply any subset $\mathcal{H} \subseteq 2^{[m]}$.
-We say that $\mathcal{H}$ is \textit{$k$-uniform} when $\mathcal{H} \subseteq {[m] \choose k}$.
-The \emph{degree} $\deg_\mathcal{H}(i)$ of a node $i \in [m]$ is the number of sets in $\mathcal{H}$ that contain $i$, and we say $\mathcal{H}$ is \emph{regular} when for some $r$ we have $\deg_\mathcal{H}(i) = r$ for all $i$ (given such an $r$, we say $\mathcal{H}$ is \textit{$r$-regular}).
-We also write $2\mathcal{H} := \{ S \cup S': S, S' \in \mathcal{H}\}$.
-The following class of structured hypergraphs is a key ingredient in this work.
-
-\begin{definition}\label{sip}
-Given $\mathcal{H} \subseteq 2^{[m]}$, the \textbf{star} $\sigma(i)$ is the collection of sets in $\mathcal{H}$ containing $i$.
-We say $\mathcal{H}$ has the \textbf{singleton intersection property} (\textbf{SIP}) when $\cap \sigma(i) = \{i\}$ for all $i \in [m]$.
-\end{definition}
-
-We next give a quantitative generalization of the spark condition (\ref{SparkCondition}) to combinatorial subsets of supports.
-The \emph{lower bound} of an $n \times m$ matrix $\mathbf{M}$ is the largest $\alpha$ with \mbox{$\|\mathbf{M}\mathbf{x}\|_2 \geq \alpha\|\mathbf{x}\|_2$} for all $\mathbf{x} \in \mathbb{R}^m$ \cite{Grcar10}.
-By compactness of the unit sphere, every injective linear map has a positive lower bound; hence, if $\mathbf{M}$ satisfies \eqref{SparkCondition}, then submatrices formed from $2k$ of its columns or less have strictly positive lower bounds.
-
-The lower bound of a matrix is generalized below in (\ref{Ldef}) by restricting it to the spans of certain submatrices\footnote{See \cite{vidal2005generalized} for an overview of the related ``union of subspaces" model.} associated with a hypergraph $\mathcal{H} \subseteq {[m] \choose k}$ of column indices.
-Let $\mathbf{M}_S$ denote the submatrix formed by the columns of a matrix $\mathbf{M}$ indexed by $S \subseteq [m]$ (setting $\mathbf{M}_\emptyset := \mathbf{0}$).
-In the sections that follow, we shall also let $\bm{\mathcal{M}}_S$ denote the column-span of a submatrix $\mathbf{M}_S$, and $\bm{\mathcal{M}}_\mathcal{G}$ to denote $\{\bm{\mathcal{M}}_S\}_{S \in \mathcal{G}}$.
-We define:  % Define $L_\mathcal{H}(\mathbf{M})$ as follows:
-%\begin{align*} 
-%L_\mathcal{H}(\mathbf{M}) := \min \left\{ \frac{ \|\mathbf{M}(\mathbf{x}_1-\mathbf{x}_2)\|_2 }{ \sqrt{2k} \|\mathbf{x}_1-\mathbf{x}_2\|_2} : \mathbf{x}_1, \mathbf{x}_2 \in \cup_{S \in \mathcal{H}} \bm{\mathcal{M}}_S \right\},
-%\end{align*} 
-%
-%where we write $L_{2k}$ in place of $L_\mathcal{H}$ when $\mathcal{H} = {[m] \choose k}$.
-Note that if $\mathcal{H}$ covers $[m]$, then $L_2 > L_\mathcal{H}$.\footnote{The reader should beware that $L_2 = L_{[m]}$, whereas $L = L_{\{[m]\}}$.
-For even $k$, the quantity $1 - \sqrt{k} L_k(\mathbf{M})$ is also known in the compressed sensing literature as the (asymmetric) lower restricted isometry constant \cite{Blanchard2011}.} Clearly, for any $\mathbf{M}$ satisfying \eqref{SparkCondition}, we have $L_{k'}(\mathbf{M}) > 0$ for  $k' \leq 2k$.
-%\begin{align*}
-%L_\mathcal{H}(\mathbf{M}) := \min \left\{ \frac{ \|\mathbf{M}_S\mathbf{x}\|_2 }{ \sqrt{k} \|\mathbf{x}\|_2} : S \in \mathcal{H} \right\},
-%\end{align*} 
-%\begin{align*}
-%L_\mathcal{H}(\mathbf{M}) := \max \left\{ \ falpha: \|\mathbf{M}_S\mathbf{x}\|_2 \geq \alpha \sqrt{k} \|\mathbf{x}\|_2 : S \in \mathcal{H}, \ \ \mathbf{x} \in \mathbb{R}^m \right\},
-%\end{align*} 
-\begin{align}\label{Ldef}
-L_\mathcal{H}(\mathbf{M}) := \min \left\{ \frac{\|\mathbf{M}_S\mathbf{x}\|_2}{ \sqrt{k} \|\mathbf{x}\|_2} : S \in \mathcal{H}, \ \mathbf{0} \neq \mathbf{x} \in \mathbb{R}^{|S|} \right\},
-\end{align} 
-%
-writing also $L_{k}$ in place of $L_\mathcal{H}$ when $\mathcal{H} = {[m] \choose k}$.\footnote{In compressed sensing literature, \mbox{$1 - \sqrt{k} L_k(\mathbf{M})$}  is the asymmetric lower restricted isometry constant for $\mathbf{M}$ with unit $\ell_2$-norm columns \cite{Blanchard2011}.}  As explained above, compactness implies that $L_{2k}(\mathbf{M}) > 0$ for all $\mathbf{M}$ satisfying \eqref{SparkCondition}.
-Clearly, $L_{\mathcal{H}'}(\mathbf{M}) \geq L_\mathcal{H}(\mathbf{M})$ whenever $\mathcal{H}' \subseteq \mathcal{H}$, and similarly any $k$-uniform $\mathcal{H}$ satisfying $\cup \mathcal{H} = [m]$ has $L_2 \geq L_{2\mathcal{H}} \geq L_{2k}$ (letting $L_{2k}$ := $L_m$ whenever $2k > m$).
-
-We are now in a position to state our main result, though for expository purposes we leave the quantity $C_1$ %(a function of $\mathbf{A}$, $\mathbf{x}_1, \ldots, \mathbf{x}_N$, and $\mathcal{H}$) 
-undefined until Sec.~\ref{DUT}. All results  below assume real matrices and vectors.
-
-%eps-tightness COUNTER-EXAMPLE:
-%Consider the alternate dictionary $B = \left(\mathbf{0}, \frac{1}{2}(\mathbf{e}_1 + \mathbf{e}_2), \mathbf{e}_3, \ldots, \mathbf{e}_{m} \right)$ and sparse codes $\mathbf{b}_i = \mathbf{e}_2$ for $i = 1, 2$ and $\mathbf{b}_i = \mathbf{e}_i$ for $i = 3, \ldots, m$.
-Then $|A\mathbf{a}_i - B\mathbf{b}_i| = 1/\sqrt{2}$ for $i = 1, 2$ (and $0$ otherwise).
-If there were permutation and invertible diagonal matrices $P \in \mathbb{R}^{m \times m}$ and $D \in \mathbb{R}^{m \times m}$ such that $|(A-BPD)\mathbf{e}_i| \leq C\varepsilon$ for all $i \in [m]$, then we would reach the contradiction $1 = |P^{-1}\mathbf{e}_1|_2 = |(A-BPD)P^{-1}\mathbf{e}_1|_2 \leq 1/\sqrt{2}$.
-
-\begin{theorem}\label{DeterministicUniquenessTheorem}
-%Fix integers $n, k, m$ and $\overline m$. 
-If an $n \times m$ matrix $\mathbf{A}$ satisfies $L_{2\mathcal{H}}(\mathbf{A}) > 0$ for some $r$-regular $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP, and $k$-sparse \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} include more than $(k-1){\overline m \choose k}$ vectors in general linear position\footnote{Recall that a set of vectors sharing support $S$ are in \emph{general linear position} when any $|S|$ of them are linearly independent.} supported in each $S \in \mathcal{H}$, then the following recovery guarantees hold for $C_1 > 0$ given by \eqref{Cdef1}.
-
-\textbf{Dictionary Recovery:} Fix $\varepsilon < L_{2}(\mathbf{A}) / C_1$.\footnote{Note that the condition $\varepsilon < L_2(\mathbf{A}) /C_1$ is necessary; otherwise, with \mbox{$\mathbf{A}$ = $\mathbf{I}$} (the identity matrix) and $\mathbf{x}_i = \mathbf{e}_i$, the matrix $\mathbf{B} = \left[\mathbf{0}, \frac{1}{2}(\mathbf{e}_1 + \mathbf{e}_2), \mathbf{e}_3, \ldots, \mathbf{e}_{m} \right]$ and sparse codes $\mathbf{\overline x}_i = \mathbf{e}_2$ for $i = 1, 2$ and $\mathbf{\overline x}_i = \mathbf{e}_i$ for $i \geq 3$ satisfy $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline x}_i \|_2 \leq \varepsilon$ but nonetheless violate \eqref{Cstable}.} If an $n \times \overline m$ matrix $\mathbf{B}$ has, for every $i \in [N]$, an associated $k$-sparse $\mathbf{\overline x}_i$ satisfying \mbox{$\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \varepsilon$}, then $\overline m \geq m$, and provided that $\overline m (r-1) < mr$, there is a permutation matrix $\mathbf{P}$ and an invertible diagonal matrix $\mathbf{D}$ such that:
-\begin{align}\label{Cstable}
-\|\mathbf{A}_j- (\mathbf{BPD})_j\|_2 \leq C_1 \varepsilon, \ \ \text{for all } j \in J,
-\end{align}
-%
-for some $J \subseteq [m]$ of size \mbox{$m - (r-1)(\overline m - m)$}. 
-% $\overline m - r(\overline m - m)$
-
-\textbf{Code Recovery:} If, moreover, $\mathbf{A}_J$ satisfies \eqref{SparkCondition} and $\varepsilon < L_{2k}(\mathbf{A}_J) / C_1$, then $(\mathbf{BP})_J$ also satisfies \eqref{SparkCondition} with $L_{2k}(\mathbf{BP}_J) \geq (L_{2k}(\mathbf{A}_J) - C_1 \varepsilon) / \|\mathbf{D}_J\|_1$, and for all $i \in [N]$:
-\begin{align}\label{b-PDa}
-%\|\mathbf{x}^J_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}^{\overline J}_i\|_1 &\leq  \left( \frac{ 1+C_1 \|\mathbf{x}^{J}_i\|_1 }{ L_{2k}(\mathbf{A}) -  C_1\varepsilon } \right) \varepsilon \ \  \text{for $i \in [N]$}.
-\|(\mathbf{x}_i)_J - (\mathbf{D}^{-1}\mathbf{P}^{\top} \mathbf{\overline x}_i)_J\|_1 &\leq  \left( \frac{ 1+C_1 \|(\mathbf{x}_i)_J\|_1 }{ L_{2k}(\mathbf{A}_J) -  C_1\varepsilon } \right) \varepsilon,
-\end{align}
-%
-where subscript $(\cdot)_J$ here represents the subvector formed from restricting to coordinates indexed by $J$.
-\end{theorem}
-
-%We delay defining the explicit constant $C_1$ until Section \ref{DUT} (\eqref{Cdef1}).
-%To be clear, the implication of Thm.~\ref{DeterministicUniquenessTheorem} is that $Y = \{\mathbf{Ax}_1, \ldots, \mathbf{Ax}_N\}$ has a stable $k$-sparse representation in $\mathbb{R}^m$, with \eqref{def1} guaranteed provided $\varepsilon$ in Def.~\ref{maindef} does not exceed:
-In words, Thm.~\ref{DeterministicUniquenessTheorem} says that the smaller the regularity $r$ of the original support hypergraph $\mathcal{H}$ or the difference $\overline m - m$ between the assumed and actual number of elements in the latent dictionary, the more columns and coefficients of the original dictionary $\mathbf{A}$ and sparse codes $\mathbf{x}_i$ are guaranteed to be contained (up to noise) in the appropriately labelled and scaled recovered dictionary $\mathbf{B}$ and codes $\mathbf{\overline x}_i$, respectively.
-
-In the important special case when $\overline m = m$, the theorem directly implies that  $Y = \{\mathbf{Ax}_1, \ldots, \mathbf{Ax}_N\}$ has a stable $k$-sparse representation in $\mathbb{R}^m$, with inequalities \eqref{def1} guaranteed in Def.~\ref{maindef} for the following worst-case error $\varepsilon$:
-\begin{align}\label{epsdel}
-\varepsilon(\delta_1, \delta_2) := \min \left\{ \frac{\delta_1}{ C_1 }, \frac{ \delta_2 L_{2k}(\mathbf{A})}{ 1 + C_1 \left( \delta_2 + \max_{i \in [N]} \|\mathbf{x}_i\|_1  \right) } \right\}.
-\end{align}
-
-Since sparse codes in general linear position are straightforward to produce with a ``Vandermonde''  construction (i.e., by choosing columns of the matrix $[\gamma_{i}^j]_{i,j=1}^{k,N}$, for distinct nonzero $\gamma_i$), we have the following direct consequence of Thm.~\ref{DeterministicUniquenessTheorem}.
-
-\begin{corollary}\label{DeterministicUniquenessCorollary}
-Given any regular hypergraph $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP, there are $N =  |\mathcal{H}| \left[ (k-1){m \choose k} + 1  \right]$ vectors \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} such that every matrix $\mathbf{A}$ satisfying spark condition \eqref{SparkCondition} generates $Y = \{\mathbf{A}\mathbf{x}_1, \ldots, \mathbf{A}\mathbf{x}_N\}$ with a stable $k$-sparse representation in $\mathbb{R}^m$ for $\varepsilon(\delta_1,\delta_2)$ given by \eqref{epsdel}.
-\end{corollary}
-
-% prev
-%\begin{corollary}\label{DeterministicUniquenessCorollary}
-%Given any regular hypergraph $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP, there are $N =  |\mathcal{H}| \left[ (k-1){m \choose k} + 1  \right]$ vectors \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} such that every matrix $\mathbf{A}$ with $L_{2\mathcal{H}}(\mathbf{A}) > 0$ generates a dataset $Y = \{\mathbf{A}\mathbf{x}_1, \ldots, \mathbf{A}\mathbf{x}_N\}$ with a stable $k$-sparse representation in $\mathbb{R}^m$ for $\varepsilon(\delta_1,\delta_2)$ as in \eqref{epsdel}.
-%\end{corollary}
-
-%We claim that the assumptions of Thm.~\ref{DeterministicUniquenessTheorem} are easily met with deterministic constructions.
-In particular, sparse codes in general linear position are straightforward to produce using a ``Vandermonde'' matrix construction (i.e.
-use the columns of the matrix $[\gamma_{i}^j]_{i,j=1}^{k,N}$, for distinct nonzero $\gamma_i$).
-%
-
-% (Prob.~\ref{InverseProblem}).
-%=======
-%An immediate practical implication of this result is that there exists a practical procedure to affirm if one's proposed solution $(\mathbf{B}, \mathbf{\overline x}_1, \ldots, \mathbf{x}_N)$ to Prob.~\ref{InverseProblem} is indeed unique (up to noise and inherent ambiguities): simply check that $\mathbf{B}$ and the $\mathbf{\overline x}_i$ satisfy the assumptions on $\mathbf{A}$ and the $\mathbf{x}_i$ in Thm.~\ref{DeterministicUniquenessTheorem}.
-%
-%%In fact, a more general result (stated clearly in the next section) can be gleaned from our method of proving Thm.~\ref{DeterministicUniquenessTheorem}.
-Briefly, in cases where $\mathbf{B}$ has $\overline m \neq m$ columns, or $\mathcal{H}$ is not regular or only partially satisfying the SIP, a relation between $\overline m$ and the degree sequence of nodes in $\mathcal{H}$ gives indices $J \subseteq [m]$ defining a submatrix $\mathbf{A}_J$ and subvectors $\mathbf{x}_i^J$ that are recoverable in the sense of \eqref{Cstable} and \eqref{b-PDa}.
-For example, if $\mathcal{H}$ is $\ell$-regular with the SIP but $m \leq \overline m < m\ell/(\ell - 1)$ then we have nonzero $|J| = \overline m - \ell(\overline m - m)$.
-The implication here is that the smaller the difference $\overline m - m$, the more columns and code entries of the original $n \times m$ dictionary $\mathbf{A}$ and codes $\mathbf{x}_i$ contained (up to noise) in the appropriately scaled $n \times \overline m$ dictionary $\mathbf{B}$ and codes $\mathbf{\overline x}_i$.
-When $\overline m = m$, we recover Thm.~\ref{DeterministicUniquenessTheorem}.
-%
-%%In fact, even if $\mathcal{H}$ is not regular or only partially satisfies the SIP, a relation between $\overline m$ and the degree sequence of nodes in $\mathcal{H}$ may give the indices $J \subseteq [m]$.
-For sake of brevity, we delay to the next section a clear statement of this more general result.
-%
-%Regarding the assumptions of Thm.~\ref{DeterministicUniquenessTheorem}, it so happens that sparse codes $\mathbf{x}_i$ in general linear position are straightforward to produce with a ``Vandermonde'' matrix construction \cite{Hillar15}, leading to the following.
-%>>>>>>> d1407a275dc391dabad7bb62d3e659f9a4ac4624
-
-% Needs to be L_{2k}(A) > 0 to guarantee sparse vector recovery
-
-%We also have the following refinement of a result in \cite{Hillar15}:
-%\begin{corollary}
-%Those square matrices $\mathbf{A}$ that satisfy \mbox{$L_{2\mathcal{H}}(\mathbf{A}) > 0$} for some regular $k$-uniform hypergraph $\mathcal{H}$ with the SIP and have the property that $\mathbf{Ax}$ is $k$-sparse for all $k$-sparse $\mathbf{x}$ with support in $\mathcal{H}$ are the matrices $\mathbf{PD}$, where $\mathbf{P}$ and $\mathbf{D}$ run over permutation and invertible diagonal matrices, respectively.
-%\end{corollary}
-
-One can easily verify that for every $k < m$ there are regular $k$-uniform hypergraphs $\mathcal{H}$ with the SIP besides the obvious $\mathcal{H} = {[m] \choose k}$.
-For instance, take $\mathcal{H}$ to be the $k$-regular set of consecutive intervals of length $k$ in some cyclic order on $[m]$.
-In this case, a direct consequence of Cor.~\ref{DeterministicUniquenessCorollary} is rigorous verification of the lower bound \mbox{$N = m(k-1){m \choose k} + m$} for sufficient sample size from the introduction.
-Special cases allow for even smaller hypergraphs.
-For example, if $k = \sqrt{m}$, then a 2-regular $k$-uniform hypergraph with the SIP can be constructed as the $2k$ rows and columns formed by arranging the elements of $[m]$ into a square grid.
-
-%\cite{li2004analysis, Georgiev05, Aharon06, Hillar15}
-We should stress here that framing the problem in terms of hypergraphs has allowed us to show, unlike in previous research on the subject, that the matrix $\mathbf{A}$ need not necessarily satisfy \eqref{SparkCondition} to be recoverable from data.
-As an example, let $\mathbf{A} = [ \mathbf{e}_1, \ldots, \mathbf{e}_5, \mathbf{v}]$ with $\mathbf{v} = \mathbf{e}_1 + \mathbf{e}_3 + \mathbf{e}_5$ and take $\mathcal{H}$ to be all consecutive pairs of indices $1, \ldots ,6$ arranged in cyclic order.
-Then for $k=2$, the matrix $\mathbf{A}$ fails to satisfy \eqref{SparkCondition} while still obeying the assumptions of Thm.~\ref{DeterministicUniquenessTheorem} for dictionary recovery.%, hence guaranteeing \eqref{Cstable} .
-%(since $\{ \mathbf{A}_1, \mathbf{A}_3, \mathbf{A}_5, \mathbf{A}_6\}$ is not a linearly independent set).
-%This weakening allows for a practical (polynomial) amount of data to still guarantee a stable dictionary in the case where the set of sparse supports for the $\mathbf{\overline x}_i$ is known to have a size that grows polynomially in $m$ and $k$.
-
-A practical implication of Thm.~\ref{DeterministicUniquenessTheorem} is the following: there is an effective procedure sufficient to affirm if a proposed solution to Prob.~\ref{InverseProblem} is indeed unique (up to noise and inherent ambiguities).
-One need simply check that the matrix and codes satisfy the (computable) assumptions of Thm.~\ref{DeterministicUniquenessTheorem} on $\mathbf{A}$ and the $\mathbf{x}_i$.
-In general, however, there is no known efficient procedure.
-We defer a brief discussion on this point to the next section.
-%Another practical implication of Thm.\ref{DeterministicUniquenessTheorem} is the following: there is an effective procedure sufficient to affirm if a proposed solution $(\mathbf{B}, \mathbf{\overline x}_1, \ldots, \mathbf{x}_N)$ to Prob.~\ref{InverseProblem} is indeed unique (up to noise and inherent ambiguities).
-One simply checks that $\mathbf{B}$ and the $\mathbf{\overline x}_i$ satisfy the respective assumptions of Thm.~\ref{DeterministicUniquenessTheorem}.
-%. on $\mathbf{A}$ and the $\mathbf{x}_i$, respectively.
-
-%In fact, a more general result (stated clearly in the next section) can be gleaned from our method of proving Thm.~\ref{DeterministicUniquenessTheorem}.
-Briefly, in cases where $\mathbf{B}$ has $\overline m \neq m$ columns, or $\mathcal{H}$ is not regular or only partially satisfying the SIP, a relation between $\overline m$ and the degree sequence of nodes in $\mathcal{H}$ gives indices $J \subseteq [m]$ defining a submatrix $\mathbf{A}_J$ and subvectors $\mathbf{x}_i^J$ that are recoverable in the sense of \eqref{Cstable} and \eqref{b-PDa}.
-For example, if $\mathcal{H}$ is $\ell$-regular with the SIP but $m \leq \overline m < m\ell/(\ell - 1)$ then we have nonzero $|J| = \overline m - \ell(\overline m - m)$.
-The implication here is that the smaller the difference $\overline m - m$, the more columns and code entries of the original $n \times m$ dictionary $\mathbf{A}$ and codes $\mathbf{x}_i$ contained (up to noise) in the appropriately scaled $n \times \overline m$ dictionary $\mathbf{B}$ and codes $\mathbf{\overline x}_i$.
-When $\overline m = m$, we recover Thm.~\ref{DeterministicUniquenessTheorem}.
-
-%In fact, even if $\mathcal{H}$ is not regular or only partially satisfies the SIP, a relation between $\overline m$ and the degree sequence of nodes in $\mathcal{H}$ may give the indices $J \subseteq [m]$.
-For sake of brevity, we delay to the next section a clear statement of this more general result.
-
-%=======
-%One can also verify that for every $k < m$, there is a regular $k$-uniform hypergraph that satisfies the SIP; for instance, take $\mathcal{H}$ to be the consecutive intervals of length $k$ in some cyclic order on $[m]$, for which Cor.~\ref{DeterministicUniquenessCorollary} implies the lower bound for sample size $N$ from the introduction.
-In many cases, however, the SIP is achievable with far fewer supports; for example, when $k = \sqrt{m}$, take $\mathcal{H}$ to be the $2k$ rows and columns formed by arranging $[m]$ in a square grid.
-%>>>>>>> d1407a275dc391dabad7bb62d3e659f9a4ac4624
-
-%As mentioned above, there exist $k$-uniform regular hypergraphs $\mathcal{H}$ with the SIP having cardinality $|\mathcal{H}| = m$,
-
-A less direct consequence of Thm.~\ref{DeterministicUniquenessTheorem} is the following uniqueness and stability guarantee for solutions to Prob.~\ref{SLCopt}.
-%, the usual optimization problem of interest for those applying dictionary learning to their data.
-
-\begin{theorem}\label{SLCopt}
-Fix a matrix $\mathbf{A}$ and vectors $\mathbf{x}_i$ satisfying the assumptions of Thm.~\ref{DeterministicUniquenessTheorem}, only now with over \mbox{$(k-1)\left[ {\overline m \choose k} + |\mathcal{H}|k{\overline m \choose k-1}\right]$} vectors supported in general linear position in each $S \in \mathcal{H}$.
-Every solution to Prob.~\ref{OptimizationProblem} (with $\eta = \varepsilon/2$) satisfies recovery guarantees \eqref{Cstable} and \eqref{b-PDa} when the corresponding bounds on $\eta$ are met.
-\end{theorem}
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=.24 \linewidth]{figs/basis.png}
-% \includegraphics[width=.25 \linewidth]{figs/Ahat_FastICA_M640_K8_noise0_2042}
-%\includegraphics[width=.24 \linewidth]{figs/Ahat_FastICA_M640_K8_noise0_4083.png}
-\includegraphics[width=.24 \linewidth]{figs/Ahat_FastICA_M640_K8_noise1_0205.png}
-\includegraphics[width=.24 \linewidth]{figs/Ahat_FastICA_M640_K8_noise2_0409.png}
-\includegraphics[width=.24 \linewidth]{figs/Ahat_FastICA_M640_K8_noise5_1021.png}
-\caption{\textbf{Learning a dictionary from increasingly noisy data}.
-The (unraveled) basis elements of the $8 \times 8$ discrete cosine transform (DCT) form the 64 columns of the left-most matrix above.
-Three increasingly imprecise dictionaries (columns reordered to best match original) are recovered by FastICA \cite{hyvarinen2000independent} trained on data generated from $8$-sparse linear combinations of DCT elements corrupted with additive noise (increasing from left to right).}
-\vspace{-.6 cm}
-\label{noisyrecovery}
-\end{center}
-\end{figure}
-
-Another extension of Thm.~\ref{DeterministicUniquenessTheorem} can be derived from the following algebraic characterization of the spark condition.
-Letting $\mathbf{A}$ be the $n \times m$ matrix of $nm$ indeterminates $A_{ij}$, the reader may work out why substituting real numbers for the $A_{ij}$ yields a matrix satisfying \eqref{SparkCondition} if and only if the following polynomial evaluates to a nonzero number:
-\begin{align*}
-f(\mathbf{A}) := \prod_{S \in {[m] \choose 2k}} \sum_{S' \in {[n] \choose 2k}} (\det \mathbf{A}_{S',S})^2,
-\end{align*}
-%
-where for any $S' \in {[n] \choose 2k}$ and $S \in {[m] \choose 2k}$, the symbol $\mathbf{A}_{S',S}$ denotes the submatrix of entries $A_{ij}$ with $(i,j) \in S' \times S$.\footnote{The large number of terms in this product is likely necessary given that deciding whether or not a matrix satisfies the spark condition is NP-hard \cite{tillmann2014computational}.}
-
-Since $f$ is analytic, having a single substitution of a real matrix $\mathbf{A}$ satisfying $f(\mathbf{A}) \neq 0$ implies that the zeroes of $f$ form a set of (Borel) measure zero.
-Such a matrix is easily constructed by adding rows of zeroes to a $\min(2k,m) \times m$ Vandermonde matrix as mentioned previously, so that every sum in the product defining $f$ above is strictly positive.
-Thus, almost every $n \times m$ matrix with $n \geq \min(2k,m)$ satisfies \eqref{SparkCondition}.
-
-%Another extension of Thm.~\ref{DeterministicUniquenessTheorem} arises from the following analytic characterization of the spark condition.
-Let $\mathbf{A}$  be the $n \times m$ matrix of $nm$ indeterminates $A_{ij}$.
-When real numbers are substituted for $A_{ij}$, the resulting matrix satisfies \eqref{SparkCondition} if and only if the following polynomial is nonzero:
-%\begin{align*}
-%f(\mathbf{A}) := \prod_{S \in {[m] \choose k}} \sum_{S' \in {[n] \choose k}} (\det \mathbf{A}_{S',S})^2,
-%\end{align*}
-%
-%where for any $S' \in {[n] \choose k}$ and $S \in {[m] \choose k}$, the symbol $\mathbf{A}_{S',S}$ denotes the submatrix of entries $A_{ij}$ with $(i,j) \in S' \times S$.
-We note that the large number of terms in this product is likely necessary due to the NP-hardness of deciding whether a given matrix $\mathbf{A}$ satisfies the spark condition \cite{tillmann2014computational}.
-
-%Since $f$ is analytic, having a single substitution of a real matrix $\mathbf{A}$ with $f(\mathbf{A}) \neq 0$ necessarily implies that the zeroes of $f$ form a set of measure zero.
-Fortunately, such a matrix $\mathbf{A}$ is easily constructed by adding rows of zeroes to any $\min(2k,m) \times m$ Vandermonde matrix as described above (so that each term in the product above for $f$ is nonzero).
-Hence, almost every $n \times m$ matrix with $n \geq \min(2k,m)$ satisfies \eqref{SparkCondition}.
-
-We claim that a similar phenomenon applies to datasets of vectors with a stable sparse representation.
-Briefly, following the same procedure as in \cite[Sec.~IV]{Hillar15}, for $k < m$ and $n \geq \min(2k, m)$, we may consider the ``symbolic'' dataset $Y = \{\mathbf{A}\mathbf{x}_1,\ldots,\mathbf{A} \mathbf{x}_N\}$ generated by an indeterminate $n \times m$ matrix $\mathbf{A}$ and $m$-dimensional $k$-sparse vectors $\mathbf{x}_1, \ldots, \mathbf{x}_N$ indeterminate within their supports, which form a regular hypergraph $\mathcal{H} \subseteq {[m] \choose k}$ satisfying the SIP.
-Restricting \mbox{$(k-1){m \choose k} + 1$} indeterminate $\mathbf{x}_i$ to each support in $\mathcal{H}$, and letting $\textbf{M}$ be the $n \times N$ matrix with columns $\mathbf{A}\mathbf{x}_i$, it can be checked that when $f(\mathbf{M}) \neq 0$ for a substitution of real numbers for the indeterminates, all of the assumptions on $\mathbf{A}$ and the $\mathbf{x}_i$ in Thm.~\ref{DeterministicUniquenessTheorem} are satisfied.
-We therefore have the following.
-% ; in particular, $\mathbf{A}$ satisfies \eqref{SparkCondition}
-
-\begin{theorem}\label{robustPolythm}
-%Let $\mathbf{A}$ and $\mathbf{x}_1, \ldots, \mathbf{x}_N$ be an indeterminate $n \times m$ matrix and sequence of $m$-dimensional vectors, respectively. 
-There is a polynomial in the entries of $\mathbf{A}$ and the $\mathbf{x}_i$ that evaluates to a nonzero number only when $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$.
-In particular, almost all substitutions impart to $Y$ this property.
-\end{theorem}
-
-%To extend this observation to arbitrary probability distributions, note that if a set of measure spaces $\{(X_{\ell}, \nu_{\ell})\}_{\ell=1}^p$ has measures $\nu_{\ell}$ absolutely continuous with respect to the standard Borel measure on $\mathbb{R}$ for all $\ell \in [p]$, then the product measure $\prod_{\ell=1}^p \nu_{\ell}$ is also absolutely continuous with respect to the standard Borel product measure on $\mathbb{R}^p$ (e.g., see \cite{folland2013real}).
-This fact combined with Thm.~\ref{robustPolythm} implies the following.
-To extend this observation to arbitrary probability distributions, note that if a set of $p$ measure spaces has all measures absolutely continuous with respect to the standard Borel measure on $\mathbb{R}$, then the product measure is also absolutely continuous with respect to the standard Borel product measure on $\mathbb{R}^p$ (e.g., see \cite{folland2013real}).
-This fact combined with Thm.~\ref{robustPolythm} implies the following.\footnote{We refer the reader to \cite{Hillar15} for a more detailed explanation of these arguments.}
-
-\begin{corollary}\label{ProbabilisticCor}
-If the indeterminate entries of $\mathbf{A}$ and the $\mathbf{x}_i$ are drawn independently from probability distributions absolutely continuous with respect to the standard Borel measure, then $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$ with probability one.
-\end{corollary}
-
-Thus, drawing the dictionary and supported sparse coefficients from any continuous probability distribution almost always generates data with a stable sparse representation.
-
-%\cite{rehnsommer2007, rozell2007neurally, ganguli2012compressed, hu2014hebbian}
-
-We close this section with some comments on the optimality of our results.
-The linear scaling for $\varepsilon$ in \eqref{epsdel} is essentially optimal (e.g., see \cite{arias2013fundamental}), but a basic open problem remains: how many samples are necessary to determine the sparse coding model?
-Our results demonstrate that sparse codes $\mathbf{x}_i$ drawn from only a polynomial number of $k$-dimensional subspaces permit stable identification of the generating dictionary $\mathbf{A}$. 
-This lends some legitimacy to the use of the model in practice, where data in general are unlikely (if ever) to exhibit the exponentially many possible $k$-wise combinations of dictionary elements required by (to our knowledge) all previously published results.
-
-Consequently, if $k$ is held fixed or if the size of the support set of reconstructing codes is polynomial in $\overline m$ and $k$, then a practical (polynomial) amount of data suffices to identify the dictionary.\footnote{In the latter case, a reexamination of the pigeonholing argument in the proof of Thm.~\ref{DeterministicUniquenessTheorem} requires a polynomial number of samples distributed over a polynomial number of supports.} Reasons to be skeptical that this holds in general, however, can be found in \cite{tillmann2014computational, Tillmann15}.
-Even so, in the next section we discuss how probabilistic guarantees can in fact be made for any number of available samples.
-
-\section{Proofs}\label{DUT} % of Theorems~\ref{DeterministicUniquenessTheorem} and ~\ref{SLCopt}}\label{DUT}
-
-%%%%%%%%%%%%%%
-% need to cut maybe: 
-%As mentioned in the previous section, Thm.~\ref{DeterministicUniquenessTheorem} is a particular case of a more general result that forgoes the assumption that $\mathcal{H} \subseteq {[m] \choose k}$ is regular and satisfies the SIP.
-If instead we require only that the stars $\cap \sigma(i)$ intersect at singletons for all $i \leq q$ (assuming that the nodes of $\mathcal{H}$ are labeled in some order of non-increasing degree), we have that $\overline m \geq k|\mathcal{H}| / \deg(1)$ and, provided $\overline m < k|\mathcal{H}| / (\deg(1) - 1)$, the nonempty submatrix $J$ is of size equal to the largest number $p$ satisfying:
-%\begin{align}\label{pcond}
-%\sum_{i=\ell}^{m} \deg(i) > (\overline m + 1 - \ell) (\deg(\ell) - 1) \ \ \text{for all } \ell \leq p \leq q.
-%\end{align}
-%Specifically, $J$ contains all nodes of degree exceeding $\deg(p)$ and some subset of those with degreee equal to $\deg(p)$.
-For the benefit of the reader, we do not prove explicitly this more general result below; it can be discerned from how exactly Lemma \ref{NonEmptyLemma} is incorporated into the proof of Lem.~\ref{MainLemma}.
-%%%%%%%%%%%%%%%%
-
-%As mentioned in the previous section, Thm.~\ref{DeterministicUniquenessTheorem} is a particular case of a more general result, which requires a looser set of constraints on the hypergraph $\mathcal{H}$ and which applies to $n \times \overline m$ matrices $\mathbf{B}$ (and $\overline m$-dimensional codes $\mathbf{\overline x}_i$) with $\overline m \neq m$:
-
-%Fix $\overline m$ and suppose the assumptions of Thm.~\ref{DeterministicUniquenessTheorem} hold, only now with the constraints on $\mathcal{H} \subseteq {[m] \choose k}$ being just that $|\cap H(i)| = 1$ for all $i \leq q$ (assuming w.l.o.g.
-that the nodes of $\mathcal{H}$ are labeled in some order of non-increasing degree), and with more than $(k-1){\overline m \choose k}$ vectors $\mathbf{x}_i$ supported in g.l.p.
-on each $S \in \mathcal{H}$.
-Then we must have $\overline m \geq k|\mathcal{H}| / \deg(1)$ and, provided $\overline m < k|\mathcal{H}| / (\deg(1) - 1)$, the guarantee \eqref{Cstable} holds for a submatrix $\mathbf{A}_J$, where $J \subseteq[m]$ is nonempty and of a size equal to the largest number $p$ satisfying:
-%\begin{align}\label{pcond}
-%\sum_{i=\ell}^{m} \deg(i) > (\overline m + 1 - \ell) (\deg(\ell) - 1) \ \ \text{for all } \ell \leq p \leq q.
-%\end{align}
-%Specifically, $J$ consists of the union of the set of all nodes of degree exceeding $\deg(p)$ and some subset of those nodes with degrees equal to $\deg(p)$.
-
-%For the benefit of the reader, we prove below the case where we forgo only the constraint that $\overline m = m$.
-This yields the implication $\overline m \geq m$ and \eqref{pcond} reduces to $|J| = \overline m - r(\overline m - m)$.
-The extension to the general result above can be seen by examining how exactly Lemma \ref{NonEmptyLemma} is incorporated into the overall proof.
-
-% ======== b - PDa =========
-
-% WITH EXPLICIT J SUBSCRIPT
-%We begin our proof of Thm.~\ref{DeterministicUniquenessTheorem} by showing how dictionary recovery \eqref{Cstable} already implies sparse code recovery \eqref{b-PDa} when $\mathbf{A}_J$ satisfies \eqref{SparkCondition} and \mbox{$\varepsilon < L_{2k}(\mathbf{A}_J) / C_1$}.
-%, assuming that $\overline m = m$ without loss of generality.
-%Consider any $2k$-sparse $\mathbf{x} \in \mathbb{R}^m$ and note that $\|\mathbf{x}\|_1 \leq \sqrt{2k}  \|\mathbf{x}\|_2$. By definition of $L_{2k}$ in \eqref{Ldef}, we have:
-%\begin{align}\label{stuff}
-%\|\mathbf{x}_J - &( \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x} )_J\|_1 \nonumber
-%\leq \frac{\|(\mathbf{BPD})_J(\mathbf{x}_J - (\mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x})_J)\|_2}{L_{2k}((\mathbf{BPD})_J)} \\ \nonumber
-%&\leq \frac{\|( (\mathbf{BPD})_J - \mathbf{A}_J) \mathbf{x}_J\|_2 + \|\mathbf{A}_J\mathbf{x}_J - \mathbf{B}_J\mathbf{\overline x}_J\|_2}{L_{2k}((\mathbf{BPD})_J)} \\
-%&\leq \frac{C_1\varepsilon \|\mathbf{x}_J\|_1 + \varepsilon}{L_{2k}((\mathbf{BPD})_J)},
-%\end{align}
-%where the term $C_1\varepsilon \|\mathbf{x}_J\|_1$ in the numerator above is a consequence of the triangle inequality applied to \eqref{Cstable}.
-
-%It remains for us to bound the denominator.  By the reverse triangle inequality:
-%\begin{align*}
-%\|(\mathbf{BPD})_J\mathbf{x}_J\|_2 
-%&\geq | \|\mathbf{A}_J\mathbf{x}_J\|_2 - \|(\mathbf{A}_J - (\mathbf{BPD})_J)\mathbf{x}_J\|_2 | \\
-%&\geq \sqrt{2k} (L_{2k}(\mathbf{A}_J) -  C_1\varepsilon) \|\mathbf{x}_J\|_2,
-%\end{align*}
-%
-%wherein removal of the absolute value is justified since $C_1\varepsilon < L_{2k}(\mathbf{A}_J)$.
-We therefore have that $L_{2k}((\mathbf{BPD})_J) \geq L_{2k}(\mathbf{A}_J) - C_1\varepsilon  > 0$, and \eqref{b-PDa} then follows from \eqref{stuff}.
-
-% WITHOUT J SUBSCRIPT
-We begin our proof of Thm.~\ref{DeterministicUniquenessTheorem} by showing how dictionary recovery \eqref{Cstable} already implies sparse code recovery \eqref{b-PDa} when $\mathbf{A}$ satisfies \eqref{SparkCondition} and \mbox{$\varepsilon < L_{2k}(\mathbf{A}) / C_1$}.
-We temporarily assume (without loss of generality) that $\overline m = m$, so as to omit an otherwise requisite subscript $(\cdot)_J$ around certain matrices and vectors.
-By definition of $L_{2k}$ in \eqref{Ldef}, and noting that $\sqrt{k} \|\mathbf{v}\|_2 \geq \|\mathbf{v}\|_1$ for $k$-sparse $\mathbf{v}$, we have for all $i \in [N[$:
-\begin{align}\label{stuff}
-\|\mathbf{x}_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_i \|_1 \nonumber
-&\leq \frac{\|\mathbf{BPD}(\mathbf{x}_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_i)\|_2}{L_{2k}(\mathbf{BPD})} \\ \nonumber
-&\leq \frac{\|( \mathbf{BPD} - \mathbf{A}) \mathbf{x}_i\|_2 + \|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline x}_i\|_2}{L_{2k}(\mathbf{BPD})} \\
-&\leq \frac{C_1\varepsilon \|\mathbf{x}_i\|_1 + \varepsilon}{L_{2k}(\mathbf{BPD})},
-\end{align}
-%\begin{align}\label{stuff}
-%\frac{ \|\mathbf{x} - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x} \|_1 } { \|\mathbf{D}^{-1}\|_1 }  \
-%&\leq \|\mathbf{Dx} - \mathbf{P}^{\top}\mathbf{\overline x} \|_1 \\ \nonumber
-%&\leq \frac{\|\mathbf{BP}(\mathbf{D}\mathbf{x} - \mathbf{P}^{\top}\mathbf{\overline x})\|_2}{L_{2k}(\mathbf{BP})} \\ \nonumber
-%&\leq \frac{\|( \mathbf{BPD} - \mathbf{A}) \mathbf{x}\|_2 + \|\mathbf{A}\mathbf{x} - \mathbf{B}\mathbf{\overline x}\|_2}{L_{2k}(\mathbf{BP})} \\
-%&\leq \frac{C_1\varepsilon \|\mathbf{x}\|_1 + \varepsilon}{L_{2k}(\mathbf{BP})},
-%\end{align}
-where the first term in the numerator above follows from the triangle inequality and \eqref{Cstable}.
-
-It remains for us to bound the denominator. For any $2k$-sparse $\mathbf{x}$, we have by the triangle inequality:
-\begin{align*}
-\|\mathbf{BPD}\mathbf{x}\|_2 
-&\geq \|\mathbf{A}\mathbf{x}\|_2 - \|(\mathbf{A} - \mathbf{BPD})\mathbf{x}\|_2 \\
-&\geq \sqrt{2k} (L_{2k}(\mathbf{A}) -  C_1\varepsilon) \|\mathbf{x}\|_2,
-\end{align*}
-
-%\begin{align*}
-%\|\mathbf{BP}\mathbf{x}\|_2 
-%&\geq \|\mathbf{A}\mathbf{D}^{-1}\mathbf{x}\|_2 - \|(\mathbf{A} - \mathbf{BPD})\mathbf{D}^{-1}\mathbf{x}\|_2 \\
-%&\geq \sqrt{2k} (L_{2k}(\mathbf{A}) -  C_1\varepsilon) \|\mathbf{D}^{-1}\mathbf{x}\|_2, \\ 
-%&\geq \sqrt{2k} (L_{2k}(\mathbf{A}) -  C_1\varepsilon) \|\mathbf{D}^{-1}\|_{?} \| \mathbf{x}\|_2,
-%\end{align*}
-%
-We therefore have that $L_{2k}(\mathbf{BPD}) \geq L_{2k}(\mathbf{A}) - C_1\varepsilon  > 0$, and \eqref{b-PDa} then follows from \eqref{stuff}.
-The reader may also verify that $L_{2k}(\mathbf{BP}) \geq L_{2k}(\mathbf{BPD}) / \|\mathbf{D}\|_1$.
-
-The heart of the matter is therefore \eqref{Cstable}, which we now establish beginning with the important special case of $k = 1$.
-
-\begin{proof}[Proof of Thm.~\ref{DeterministicUniquenessCorollary} for $k=1$]
-Since the only 1-uniform hypergraph with the SIP is $[m]$, which is obviously regular, we require only $\mathbf{x}_i = c_i \mathbf{e}_i$ for $i \in [m]$, with $c_i \neq 0$ to guarantee  linear independence.
-While we have yet to define $C_1$ generally, in this case we may set $C_1 = 1/ \min_{\ell \in [m]} |c_{\ell}|$ so that $\varepsilon < L_2(\mathbf{A})  \min_{\ell \in [m]} |c_{\ell}|$.
-
-Fix $\mathbf{A} \in \mathbb{R}^{n \times m}$ satisfying $L_2(\mathbf{A}) > 0$, since here we have $2\mathcal{H} = {[m] \choose 2}$, and suppose some $\mathbf{B}$ and $1$-sparse $\mathbf{\overline x}_i \in \mathbb{R}^{\overline m}$ have  $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \varepsilon < L_2(\mathbf{A}) / C_1$ for all $i$.
-Then, there exist $\overline{c}_1, \ldots, \overline{c}_m \in \mathbb{R}$ and a map $\pi: [m] \to [\overline m]$ such that:
-\begin{align}\label{1D}
-\|c_i\mathbf{A}_i - \overline{c}_i\mathbf{B}_{\pi(i)}\|_2 \leq \varepsilon,\ \ \text{for $i \in [m]$}.
-\end{align} 
-Note that $\overline{c}_i \neq 0$, since otherwise we would reach the following contradiction: $\|\mathbf{A}_i \|_2 \leq C_1 |c_i| \|\mathbf{A}_i \|_2  \leq C_1\varepsilon < L_2(\mathbf{A}) \leq L_1(\mathbf{A}) = \min_{i \in [m]} \|\mathbf{A}_{i}\|_2$.
-%implies by \eqref{delrho} the contradiction $|c_i| < \min_{\ell \in [m]} | c_\ell |$.
-
-We now show that $\pi$ is injective (in particular, a permutation if $\overline m = m$).
-Suppose that $\pi(i) = \pi(j) = \ell$ for some $i \neq j$ and $\ell$.
-Then, $\|c_{i}\mathbf{A}_{i} - \overline{c}_{i} \mathbf{B}_{\ell}\|_2  \leq \varepsilon$ and $\|c_{j}\mathbf{A}_{j} - \overline{c}_{j}\mathbf{B}_{\ell}\|_2 \leq \varepsilon$, and we have: %Scaling and summing these inequalities by $|\overline{c}_{i}|$ and $|\overline{c}_{j}|$, respectively, and applying the triangle inequality to annihilate the terms in $\mathbf{B}_\ell$, we obtain:
-\begin{align*}
-(|\overline{c}_{i}| + |\overline{c}_{j}|) \varepsilon
-&\geq |\overline{c}_{i}| \|c_{j}\mathbf{A}_{j} - \overline{c}_{j}\mathbf{B}_{\ell}\|_2  + |\overline{c}_{j}| \|c_{i}\mathbf{A}_{i} - \overline{c}_{i} \mathbf{B}_{\ell}\|_2 \nonumber \\
-&\geq \|\mathbf{A}(\overline{c}_{i}c_{j} \mathbf{e}_{j} - \overline{c}_{j}c_{i}\mathbf{e}_{i})\|_2 \nonumber \\ 
-&\geq \sqrt{2}  L_2(\mathbf{A}) \|\overline{c}_{i}c_{j} \mathbf{e}_{j} - \overline{c}_{j}c_{i}\mathbf{e}_{i}\|_2 \nonumber \\
-&\geq  L_2(\mathbf{A}) \left( |\overline{c}_{i}| + |\overline{c}_{j}| \right) \min_{\ell \in [m]} |c_\ell |,
-\end{align*}
-contradicting our assumed upper bound on $\varepsilon$. Hence, the map $\pi$ is injective and so $\overline m \geq m$. %Setting $\overline J = \pi([m])$ and
-
-Letting $\mathbf{P}$ and $\mathbf{D}$ be the $\overline m \times \overline m$ permutation and invertible diagonal matrices with, respectively, columns $\mathbf{e}_{\pi(i)}$ and $\frac{\overline{c}_i}{c_i}\mathbf{e}_i$ for $i \in [m]$ (otherwise, $\mathbf{e}_{i}$ for $i \in [\overline{m}] \setminus [m]$), we may rewrite \eqref{1D} to see that for all $i \in [m]$:
-\begin{align*}
-\|\mathbf{A}_i - (\mathbf{BPD})_i\|_2 
-= \|\mathbf{A}_i - \frac{\overline{c}_i}{c_i}\mathbf{B}_{\pi(i)}\|_2 
-\leq \frac{\varepsilon}{|c_i|} 
-\leq C_1\varepsilon.
-\end{align*}
-%\vspace{-.2 cm}
-\end{proof}
-
-An extension of the proof to the general case $k < m$ requires some additional tools to derive the general expression \eqref{Cdef1} for $C_1$.
-These include a generalized notion of distance (Def.~\ref{dDef}) and angle (Def.~\ref{FriedrichsDefinition}) between subspaces as well as a stability result in combinatorial matrix analysis (Lem.~\ref{MainLemma}).
-
-\begin{definition}\label{dDef}
-For $\mathbf{u} \in \mathbb R^m$ and vector spaces $U,V \subseteq \mathbb{R}^m$, let $\text{\rm dist}(\mathbf{u}, V) := \min \{\| \mathbf{u}-\mathbf{v} \|_2: \mathbf{v} \in V\}$ and define:
-\begin{align}
-d(U,V) := \max_{\mathbf{u} \in U, \ \|\mathbf{u}\|_2 \leq 1} \text{\rm dist}(\mathbf{u},V).
-\end{align}
-\end{definition}
-
-We note the following facts about $d$. Clearly, 
-\begin{align}\label{UsubU}
-U' \subseteq U \implies d(U',V) \leq d(U,V).
-\end{align}
-From \cite[Ch.~4 Cor.~2.6]{Kato2013}, we also have: %Kato p.223
-\begin{align}\label{dimLem}
-d(U,V) < 1 \implies \dim(U) \leq \dim(V),
-\end{align}
-and from \cite[Lem.~3.2]{Morris10}:
-\begin{align}\label{eqdim}
-\dim(U) = \dim(V) \implies d(U,V) = d(V,U).
-\end{align}
-
-The following is our result in combinatorial matrix analysis; it contains most of the complexity in the proof of Thm.~\ref{DeterministicUniquenessTheorem}.
-
-\begin{lemma}\label{MainLemma}
-If an $n \times m$ matrix $\mathbf{A}$ has $L_{2\mathcal{H}}(\mathbf{A}) > 0$ for some $r$-regular $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP, then the following holds for $C_2 > 0$ given by \eqref{Cdef2}:
-
-Fix $\varepsilon < L_2(\mathbf{A}) / C_2$. If for some $n \times \overline m$ matrix $\mathbf{B}$ and map $\pi: \mathcal{H} \mapsto {[\overline m] \choose k}$,
-\begin{align}\label{GapUpperBound}
-d(\bm{\mathcal{A}}_S, \bm{\mathcal{B}}_{\pi(S)}) \leq \varepsilon, \ \  \text{for $S \in \mathcal{H}$},
-\end{align}
-then $\overline m \geq m$, and provided $\overline m (r-1) < mr$, there is a permutation matrix $\mathbf{P}$ and invertible diagonal $\mathbf{D}$ such that:
-\begin{align}\label{MainLemmaBPD}
-\|\mathbf{A}_i - (\mathbf{B}\mathbf{PD})_i\|_2 \leq C_2 \varepsilon, \ \  \text{for } i \in J,
-\end{align}
-for some $J \subseteq [m]$ of size \mbox{$m - (r-1)(\overline m - m)$}.
-\end{lemma}
-
-%\begin{lemma}\label{MainLemma}
-%Fix $\mathbf{A} \in \mathbb{R}^{n \times m}$ with $L_\mathcal{H}(\mathbf{A}) > 0$ for some regular $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP.
-There exists a constant $C_2 > 0$ for which the following holds for all $\varepsilon < L_2(\mathbf{A}) / C_2$:
-
-%If a matrix $\mathbf{B} \in \mathbb{R}^{n \times m}$ and map $\pi: E \mapsto {m \choose k}$ satisfy:
-%\begin{align}\label{GapUpperBound}
-%d(\text{\rm span}\{\mathbf{A}_{S}\}, \bm{\mathcal{B}}_{\pi(S)}) \leq \varepsilon, \ \ \text{for $S \in \mathcal{H}$},
-%\end{align}
-%then there exist a permutation matrix $\mathbf{P}$ and invertible diagonal matrix $\mathbf{D}$ such that:
-%\begin{align}\label{MainLemmaBPD}
-%\|\mathbf{A}_j - \mathbf{BPD}_j\|_2 \leq C_2 \varepsilon, \ \  \text{for } j \in [m],
-%\end{align}
-%\end{lemma}
-
-We present the constant $C_2$ (a function of $\mathbf{A}$ and $\mathcal{H}$) relative to a quantity used in \cite{Deutsch12} to analyze the convergence of the ``alternating projections" algorithm for projecting a point onto the intersection of subspaces.
-We incorporate this quantity into the following definition, which we refer to in our proof of Lem.~\ref{DistanceToIntersectionLemma} in the Appendix; specifically, we use it to bound the distance between a point and the intersection of subspaces given an upper bound on its distance from each subspace.
-
-\begin{definition}\label{FriedrichsDefinition}
-For a collection of real subspaces $\mathcal{V} = \{V_i\}_{i=1}^\ell$, define $\xi(\mathcal{V}) := 0$ when $|\mathcal{V}| = 1$, and otherwise:
-\begin{align}\label{xi}
-\xi^2(\mathcal{V}) := 1 -  \max \prod_{i=1}^{\ell-1} \sin^2  \theta \left(V_i, \cap_{j>i} V_j \right) ,
-\end{align} 
-%
-where the maximum is taken over all ways of ordering 
-%\footnote{We modify the quantity in \cite{Deutsch12} in this way since the subspace ordering is irrelevant to our purpose.} 
-the $V_i$ and the angle $\theta \in (0,\frac{\pi}{2}]$ is defined implicitly as \cite[Def.~9.4]{Deutsch12}:
-\begin{align*}
-\cos{\theta(U,W)} := \max\left\{ |\langle \mathbf{u}, \mathbf{w} \rangle|: \substack{ \mathbf{u} \in U \cap (U \cap W)^\perp, \ \|\mathbf{u}\|_2 \leq 1 \\ \mathbf{w} \in W \cap (U \cap W)^\perp, \  \|\mathbf{w}\|_2 \leq 1 } \right\}.
-\end{align*}
-\end{definition}
-Note that $\theta \in (0,\frac{\pi}{2}]$ implies $0 \leq \xi < 1$, and that $\xi(\mathcal{V}') \leq \xi(\mathcal{V})$ when $\mathcal{V}' \subseteq \mathcal{V}$.\footnote{We acknowledge the counter-intuitive property: $\theta =  \pi/2$ when $U \subseteq W$.}
-
-The constant $C_2 > 0$ of Lem.~\ref{MainLemma} can now be expressed as:  
-\begin{align}\label{Cdef2}
-	C_2(\mathbf{A}, \mathcal{H}) := \frac{ (r+1) \max_{j \in [m]} \|\mathbf{A}_j\|_2}{ 1- \max_{\mathcal{G} \in {\mathcal{H} \choose r+1}} \xi( \bm{\mathcal{A}}_\mathcal{G} ) }.
-\end{align}
-
-We next define the constant $C_1 > 0$ of Thm.~\ref{DeterministicUniquenessTheorem} in terms of $C_2$.
-Given vectors $\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$, let $\mathbf{X}$ denote the $m \times N$ matrix with columns $\mathbf{x}_i$ and let $I(S)$ denote the set of indices $i$ for which $\mathbf{x}_i$ is supported in $S$.
-We define:
-\begin{align}\label{Cdef1}
-C_1(\mathbf{A}, \mathcal{H}, \{\mathbf{x}_i\}_{i=1}^N) := \frac{ C_2(\mathbf{A}, \mathcal{H}) } { \min_{S \in \mathcal{H}} L_k(\mathbf{AX}_{I(S)}) }.
-\end{align}
-Given the assumptions of Thm.~\ref{DeterministicUniquenessTheorem} on $\mathbf{A}$ and the $\mathbf{x}_i$, this expression for $C_1$ is well-defined\footnote{\label{note1}To see this, fix $S \in \mathcal{H}$ and $k$-sparse $\mathbf{c}$.
-Using the definitions, we have $\|\mathbf{AX}_{I(S)}\mathbf{c}\|_2 \geq \sqrt{k} L_\mathcal{H}(\mathbf{A})\|\mathbf{X}_{I(S)}\mathbf{c}\|_2 \geq k L_\mathcal{H}(\mathbf{A}) L_k(\mathbf{X}_{I(S)})\|\mathbf{c}\|_2$.
-Thus, $L_k(\mathbf{AX}_{I(S)}) \geq \sqrt{k} L_\mathcal{H}(\mathbf{A}) L_k(\mathbf{X}_{I(S)}) > 0$, since $L_{\mathcal{H}}(\mathbf{A}) \geq L_{2\mathcal{H}}(\mathbf{A})> 0$ and $L_k(\mathbf{X}_{I(S)}) > 0$ by general linear position of the $\mathbf{x}_i$.} and yields an upper bound on $\varepsilon$ consistent with that proven sufficient in the case $k=1$ considered at the beginning of this section.\footnote{When $\mathbf{x}_i = c_i\mathbf{e}_i$, we have $C_2 \geq 2\|\mathbf{A}_i\|_2$ and the denominator in \eqref{Cdef1} becomes $\min_{i \in [m]} |c_i| \|\mathbf{A}_i\|_2$; hence, $C_1 \geq 2 / \min_{i \in [m]} |c_i|$.}
-% C_2(\mathbf{A}, \mathcal{H}) := \frac{ (r+1) \max_{j \in [m]} \|\mathbf{A}_j\|_2}{ \min_{\mathcal{G} \in {\mathcal{H} \choose r} \cup {\mathcal{H} \choose r+1}} \xi( \{ \bm{\mathcal{A}}_S \}
-
-The practically-minded reader should note that the explicit constants $C_1$ and $C_2$ are effectively computable: the quantity $L_k$ may be calculated as the smallest singular value of a certain matrix, while the quantity $\xi$ involves computing ``canonical angles'' between subspaces, which reduces again to an efficient singular value decomposition.
-There is no known fast computation of $L_k$ in general, however, since even $L_{k} > 0$ is NP-hard \cite{tillmann2014computational}, although 
-efficiently computable bounds have been proposed (e.g., via the ``mutual coherence" of a matrix \cite{donoho2003optimally}); alternatively, 
-fixing $k$ yields polynomial complexity.
-Moreover, calculating $C_2$ requires an exponential number of queries to $\xi$ unless $r$ is held fixed, too (e.g., the ``cyclic order'' hypergraphs described above have $r=k$).
-Thus, as presented, $C_1$ and $C_2$ are not efficiently computable in general.
-% , but efficient subcases do exist and may be of practical relevance.
-
-\begin{proof}[Proof of Thm.~\ref{DeterministicUniquenessCorollary} for $k < m$] 
-We find a map $\pi: \mathcal{H} \to {[m] \choose k}$ for which the distance $d(\bm{\mathcal{A}}_S, \bm{\mathcal{B}}_{\pi(S)})$ is controlled by $\varepsilon$ for all $S \in \mathcal{H}$.
-Applying Lem.~\ref{MainLemma} then completes the proof.
-%We shall show that for every $S \in \mathcal{H}$ there is some $\overline S \in {[\overline m] \choose k}$ for which the distance $d(\bm{\mathcal{A}}_S, \bm{\mathcal{B}}_{\overline S})$ is controlled by $\varepsilon$.
-Applying Lem.~\ref{MainLemma} with the map $\pi$ defined by $S \mapsto \overline S$ then completes the proof.
-
-Fix $S \in \mathcal{H}$.
-Since there are more than $(k-1){\overline m \choose k}$ vectors $\mathbf{x}_i$ supported in $S$, by the pigeonhole principle there must be some $\overline S \in {[\overline m] \choose k}$ and a set of $k$ indices $K \subseteq I(S)$ for which all $\mathbf{\overline x}_i$ with $i \in K$ are supported in $\overline S$.
-It also follows\footnotemark[\ref{note1}] from $L_{2\mathcal{H}}(\mathbf{A}) > 0$ and the general linear position of the $\mathbf{x}_i$ that $L_k(\mathbf{AX}_{K}) > 0$; that is, the columns of the $n \times k$ matrix $\mathbf{AX}_K$ form a basis for $\bm{\mathcal{A}}_S$.
-
-Fixing $\mathbf{y} \in \bm{\mathcal{A}}_S \setminus \{\mathbf{0}\}$, there then exists $\mathbf{c} = (c_1, \ldots, c_k) \in \mathbb{R}^k \setminus \{\mathbf{0}\}$ such that $\mathbf{y} = \mathbf{AX}_K\mathbf{c}$.
-Setting \mbox{$\mathbf{\overline{y}} = \mathbf{B\overline{X}}_K\mathbf{c}$, which is in $\bm{\mathcal{B}}_{\overline S}$}, we have by triangle inequality:
-\begin{align*}
-\|\mathbf{y} - \mathbf{\overline{y}}\|_2 
-%&= \|\sum_{i=1}^k c_i(\mathbf{AX}_K - \mathbf{B\overline{X}}_K)_i\|_2
-&= \|(\mathbf{AX}_K - \mathbf{B\overline{X}}_K)\mathbf{c}\|_2
-%\leq \varepsilon \sum_{i=1}^k |c_i| \\
-\leq \varepsilon \|\mathbf{c}\|_1
-\leq \varepsilon \sqrt{k}  \|\mathbf{c}\|_2  \\
-&\leq \frac{\varepsilon}{L_k(\mathbf{AX}_K)} \|\mathbf{y}\|_2,
-\end{align*}
-where the last inequality uses \eqref{Ldef}. From Def.~\ref{dDef}:
-\begin{align}\label{rhs222}
-d(\bm{\mathcal{A}}_S, \bm{\mathcal{B}}_{\overline S}) 
-\leq \frac{\varepsilon}{  L_k(\mathbf{AX}_{K}) } 
-\leq \frac{\varepsilon}{  L_k(\mathbf{AX}_{I(S)}) } 
-\leq \varepsilon \frac{C_1}{C_2}.
-\end{align}
-%
-Finally, apply Lem.~\ref{MainLemma} with $\varepsilon < L_2(\mathbf{A})/C_1$ and $\pi(S) := \overline S$. % L_2(A) > 0 by def of L, since L_2H(A) > 0 and H covers [m]
-\end{proof}
-
-Before moving on to the proof of Thm.~\ref{SLCopt}, we briefly revisit our discussion on sample complexity from the end of the previous section.
-While an exponential number of samples may very well prove to be necessary in the deterministic or almost-certain case, our proof of Thm.~\ref{DeterministicUniquenessTheorem} can be extended to hold with some probability for \emph{any} number of samples by alternative appeal to a probabilistic pigeonholing at the point early in the proof where the (deterministic) pigeonhole principle is applied to show that for every $S \in \mathcal{H}$, there exist $k$ vectors $\mathbf{x}_i$ supported on $S$ whose corresponding $\mathbf{\overline x}_i$ all share the same support.\footnote{A famous example of such an argument is the counter-intuitive ``birthday paradox", which demonstrates that the probability of two people having the same birthday in a room of twenty-three is greater than 50\%.}
-Given insufficient samples, this argument has some less-than-certain probability of being valid for each $S \in \mathcal{H}$.
-Nonetheless, simulations with small hypergraphs confirm that the probability of success very quickly approaches one once the number of samples $N$ surpasses a small fraction of the deterministic sample complexity.
-
-\begin{proof}[Proof of Thm.~\ref{SLCopt}]
-We bound the number of $k$-sparse $\mathbf{\overline x}_i$ from below and then apply Thm.~\ref{DeterministicUniquenessCorollary}. 
-%We now apply this fact to bound the number of $k$-sparse $\mathbf{\overline x}_i$. 
-Let $n_p$ be the number of $\mathbf{\overline x}_i$ with $\|\mathbf{\overline x}_i\|_0 = p$.
-Since the $\mathbf{x}_i$ are all $k$-sparse, by \eqref{minsum} we have:
-\begin{align*}
-%\mbox{$k \sum_{p = 0}^{\overline m} n_p \geq \sum_{i=0}^N \|\mathbf{x}_i\|_0 \geq \sum_{i=0}^N \|\mathbf{\overline x}_i\|_0 = \sum_{p=0}^{\overline m} p n_p.$}
-\sum_{p=0}^{\overline m} p n_p =  \sum_{i=0}^N \|\mathbf{\overline x}_i\|_0
-\leq \sum_{i=0}^N \|\mathbf{x}_i\|_0 
-\leq kN
-\end{align*}
-Since $N = \sum_{p = 0}^{\overline m} n_p$, we then have $\sum_{p = 0}^{\overline m} (p-k) n_p \leq 0$. Splitting the sum yields:
-\begin{align}\label{eqn}
-\sum_{p = k+1}^{\overline m} n_p \leq \sum_{p = k+1}^{\overline m} (p-k) n_p \leq \sum_{p = 0}^k (k-p)n_p \leq k \sum_{p = 0}^{k-1} n_p,
-\end{align}
-%
-demonstrating that the number of vectors $\mathbf{\overline x}_i$ that are \emph{not} $k$-sparse is bounded above by how many are $(k-1)$-sparse.
-
-Next, observe that no more than $(k-1)|\mathcal{H}|$ of the $\mathbf{\overline x}_i$ share a support $\overline S$ of size less than $k$.
-Otherwise, by the pigeonhole principle, there is some $S \in \mathcal{H}$ and a set of $k$ indices $K \subseteq I(S)$ for which all $\mathbf{x}_i$ with $i \in K$ are supported in $S$; as argued previously, \eqref{rhs222} follows.
-It is simple to show that $L_2(\mathbf{A}) \leq \max_j\|\mathbf{A}_j\|_2$, and since $0 \leq \xi < 1$, the right-hand side of \eqref{rhs222} is less than one for $\varepsilon < L_2(\mathbf{A})/C_1$.
-Thus, by \eqref{dimLem} we would have the contradiction $k = \dim(\bm{\mathcal{A}}_S) \leq \dim(\bm{\mathcal{B}}_{\overline S}) \leq |\overline S| < k.$
-
-The total number of $(k-1)$-sparse vectors $\mathbf{\overline x}_i$ thus cannot exceed $|\mathcal{H}|(k-1){ \overline m \choose k-1}$.
-By \eqref{eqn}, no more than $|\mathcal{H}|k(k-1){ \overline m \choose k-1}$ vectors $\mathbf{\overline x}_i$ are not $k$-sparse.
-Since for every $S \in \mathcal{H}$ there are over $(k-1)\left[ {\overline m \choose k} + |\mathcal{H}|k{ \overline m \choose k-1} \right]$ vectors $\mathbf{x}_i$ supported there, it must be that more than $(k-1){\overline m \choose k}$ of them have corresponding $\mathbf{\overline x}_i$ that are $k$-sparse.
-The result now follows from Thm.~\ref{DeterministicUniquenessCorollary}, noting by the triangle inequality that $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline x}_i\| \leq 2\eta$ for $i = 1, \ldots, N$.
-\end{proof}
-
-%\begin{proof}[Proof (sketch) of Thm.~\ref{robustPolythm}]
-%Let $\textbf{M}$ be the matrix with columns $\mathbf{A}\mathbf{x}_i$, $i \in [N]$.
-Consider the polynomial $\prod_{S \in {[N] \choose 2k}} \sum_{S' \in {[n] \choose 2k}} (\det \textbf{M}_{S',S})^2$ in the indeterminate entries of $\mathbf{A}$ and $\mathbf{x}_i$, with notation as in Sec.~\ref{Results}.
-%It can be checked that when this polynomial is nonzero for a substitution of real numbers for the indeterminates, all of the genericity requirements on $\mathbf{A}$ and $\mathbf{x}_i$ in our proofs of stability in Thm.~\ref{DeterministicUniquenessTheorem} are satisfied (in particular, the spark condition \eqref{SparkCondition} on $\mathbf{A}$).
-%\end{proof}
-
-%\begin{proof}[Proof (sketch) of Cor.~\ref{ProbabilisticCor}]
-%First, note that if a set of measure spaces $\{(X_{\ell}, \Sigma_{\ell}, \nu_{\ell})\}_{\ell=1}^p$ has that $\nu_{\ell}$ is absolutely continuous with respect to $\mu$ for all $\ell \in [p]$, where $\mu$ is the standard Borel measure on $\mathbb{R}$, then the product measure $\prod_{\ell=1}^p \nu_{\ell}$ is absolutely continuous with respect to the standard Borel product measure on $\mathbb{R}^p$.
-% for space:  (e.g.,  \cite{folland2013real}).
-%By Thm.~\ref{robustPolythm}, there is a polynomial that is nonzero when $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$; in particular, stability holds almost surely.
-%\end{proof}
-
-\section{Discussion}\label{Discussion}
-
-A main motivation for this work is the emergence of seemingly unique representations from sparse coding models trained on natural data, despite the varied assumptions underlying the many algorithms in current use.
-Our results constitute an important step toward explaining these phenomena as well as unifying many publications on the topic by deriving general deterministic conditions under which identification of parameters in this model is not only possible but also robust to uncertainty in measurement and model choice.
-
-We have shown that, given sufficient data, the problem of determining a dictionary and sparse codes with minimal support size (Prob.~\ref{OptimizationProblem}) reduces to an instance of Prob.~\ref{InverseProblem}, to which our main result (Thm.~\ref{DeterministicUniquenessTheorem}) applies: every dictionary and sequence of sparse codes consistent with the data are equivalent up to inherent relabeling/scaling ambiguities and a discrepancy (error) that scales linearly with the measurement noise or modeling inaccuracy.
-The constants we provide are explicit and computable; as such, there is an effective procedure that sufficiently affirms if a proposed solution to these problems is indeed unique up to noise and inherent ambiguities, although it is not efficient in general.
-
-%A compelling feature of this model is its simple instantiation of the principle of Occam's razor: a natural video, for instance, is modeled as a linear combination of a small number of spatiotemporal building blocks, each representing an archetypical feature latent in the data.
-
-%For theoretical neuroscience in particular, dictionary learning and related methods have recovered characteristic components of natural images \cite{Olshausen96, hurri1996image, bell1997independent, van1998independent} and sounds \cite{bellsejnowski1996, smithlewicki2006} that reproduce response properties of certain cortical neurons.
-
-%to the recovery of ``mouse neuronal activity representing location on a track \cite{agarwal2014spatially}
-
-%Moreover, we show that even if the meta-parameter for the number of dictionary elements is overestimated, a subset of parameters may still be identifiable up to noise.
-
-Beyond an extension of existing noiseless guarantees \cite{Hillar15} to the noisy regime and their novel application to Prob.~\ref{OptimizationProblem}, our work contains a theory of combinatorial designs for support sets key to identification of dictionaries.
-We incorporate this idea into a fundamental lemma in matrix theory (Lem.~\ref{MainLemma}) that draws upon the definition of a matrix lower bound (\ref{Ldef}) induced by a hypergraph.
-The new insight offered by this combinatorial approach allows for guaranteed recovery of some or all dictionary elements even if: 1) dictionary size is overestimated, 2) data cover only a polynomial number of distinct sparse supports, and 3) dictionaries do not satisfy the spark condition.
-
-The absence of any assumptions about dictionaries solving Prob.~\ref{InverseProblem} was a major technical obstruction in proving Thm.~\ref{DeterministicUniquenessTheorem}.
-We sought such a general guarantee because of the practical difficulty in ensuring that an algorithm maintain a dictionary satisfying the spark condition \eqref{SparkCondition} at each iteration, an implicit requirement of all previous works except \cite{Hillar15}; indeed, even certifying a dictionary has this property is NP-hard \cite{tillmann2014computational}.
-
-One direct application of this work is to theoretical neuroscience, wherein our theorems justify the mathematical soundness of one of the few hypothesized theories of bottleneck communication in the brain \cite{Isely10}: that sparse neural population activity is recoverable from its noisy linear compression through a randomly constructed (but unknown) wiring bottleneck by any biologically plausible unsupervised sparse coding method that solves Prob.~\ref{DeterministicUniquenessTheorem} or \ref{SLCopt} (e.g., \cite{rehnsommer2007, rozell2007neurally, pehlevan2015normative}).\footnote{We refer the reader to \cite{ganguli2012compressed} for more on interactions between dictionary learning and neuroscience.}
-
-In fact, uniqueness guarantees with minimal assumptions apply to all areas of data science and engineering that utilize learned sparse structure.
-For example, several groups have applied compressed sensing to signal processing tasks; for instance, in MRI analysis \cite{lustig2008compressed}, image compression \cite{Duarte08}, and even the design of an ultrafast camera \cite{Gao14}.
-It is only a matter of time before these systems incorporate dictionary learning to encode and decode signals (e.g., in a device that learns structure from motion \cite{kong2016prior}), just as scientists have used sparse coding to make sense of their data \cite{jung2001imaging, agarwal2014spatially, lee2016sparse, wu2016stability}.
-
-Assurances offered by our theorems certify that different devices and algorithms learn equivalent representations given enough data from statistically identical systems.\footnote{To contrast with the current hot topic of ``Deep Learning'', there are few such uniqueness guarantees for these models of data; moreover, even small noise can dramatically alter their output \cite{goodfellow2014explaining}.}
-Indeed, a main reason for the sustained interest in dictionary learning as an unsupervised method for data analysis seems to be the assumed well-posedness of parameter identification in the model, confirmation of which forms the core of our findings.
-
-We close with some challenges left open by our work.
-All conditions stated here guaranteeing the uniqueness and stability of sparse representations have only been shown sufficient; it remains open, therefore, to extend them to necessary conditions, be they on required sample size, the structure of support set hypergraphs, or tolerable error bounds.
-On this last note, we remark that our deterministic treatment considers always the ``worst-case" noise, whereas the ``effective" noise sampled from a concentrated distribution might be significantly reduced, especially for high-dimensional data.
-It would be of great practical benefit to see how drastically all conditions can be relaxed by requiring only probabilistic guarantees in this way, or in the spirit of our discussion on probabilistic pigeonholing to reduce sample complexity (as in the famous ``birthday paradox") following the proof of Thm.~\ref{DeterministicUniquenessTheorem}.
-
-Another interesting question raised by our work is for which special cases is it efficient to check that a solution to Prob.~\ref{InverseProblem} or \ref{OptimizationProblem} is unique up to noise and inherent ambiguities.
-Considering that the sufficient conditions we have described for checking this in general are NP-hard to compute, are the necessary conditions hard?
-Are Probs.~\ref{InverseProblem} and \ref{OptimizationProblem} then also hard (e.g., see \cite{Tillmann15})?
-Finally, since Prob.~\ref{SLCopt} is intractable in general, but efficiently solvable by $\ell_1$-norm minimization when the matrix is known (and has a large enough lower bound over sparse domains \cite{eldar2012compressed}), is there a version of Thm.~\ref{SLCopt} certifying when Prob.~\ref{OptimizationProblem} can be solved efficiently in full by similar means?
-% [*** Incorporate this open problem with more words ***]
-
-We hope these remaining challenges pique the interest of the community to pick up where we have left off and that the theoretical tools showcased here may be of use to this end.
-
-%We close with some challenges left open by our work.
-First, there is the basic problem of proving optimal lower bounds on sufficient sample size $N$ guaranteeing the uniqueness and stability of sparse representations.
-The pigeonholing argument in the proof of Thm.~\ref{DeterministicUniquenessTheorem} is loose in that it assigns to each support $S \in \mathcal{H}$ a corresponding support $\overline S$ without consideration of previously matched pairs; although we doubt tightening in this way will lead to sub-exponential sample sizes.
-Sample complexity will also benefit from lowering the number of required supports, i.e.
-the size of regular uniform hypergraphs satisfying the SIP.
-The regularity requirement on support hypergraphs can be loosened to allow for certain non-regular hypergraphs satisfying constraints on the degree sequence of nodes; though we impose regularity for clarity of exposition.
-It is then natural to ask: what is the smallest hypergraph satisfying the required constraints forgiven $m$ and $k$?
-Finally, the error bounds can be improved by tightening the constant $C_1$, e.g.
-via an improvement in Lemma ?.
-
-%Solving Prob.~\ref{SLCopt} directly is intractable in general since it necessitates, for each proposed dictionary $\mathbf{B}$, a combinatorial search for the supports of the associated sparse codes $\mathbf{\overline x}_i$.
-A common work-around is to convexify the problem (for fixed $\mathbf{B}$) by substituting the norm $\|\cdot\|_0$ with $\|\cdot\|_1$, impelled the fact that matrices $\mathbf{A}$ with large enough $L_{2k}(\mathbf{A})$ induce the same sparse codes via minimization of either norm \cite{?}.
-To this end, the lower bound $L_{2k}(\mathbf{BP}) \geq (L_{2k}(\mathbf{A}) - C_1\varepsilon) / \|\mathbf{D}\|_1$ implied by Thm.~\ref{DeterministicUniquenessTheorem} hints at conditions on the generating dictionary $\mathbf{A}$ and $k$-sparse codes $\mathbf{x}_i$ under which \emph{all} matrices $\mathbf{B}$ (of bounded column-norm) that solve Prob.~\ref{OptimizationProblem} also share this property of $\mathbf{A}$ by virtue of uniqueness and stability.
-One might then imagine an inference procedure whereby sparse codes are inferred via minimization of $\|\cdot\|_1$, but solutions still evaluated by their collective support size, yielding unique optimal solutions to Prob.~\ref{SLCopt} if only constraints could be imposed such that the learning procedure eventually guides $\mathbf{B}$ through an optimal dictionary.
-% (e.g.
-the dictionary is a member of a known finite set).
-
-\textbf{Acknowledgement.} We thank Fritz Sommer and Darren Rhea for early thoughts, and Ian Morris for posting \eqref{eqdim} online.
-
-%\section{EXTRA}
-%An additional consequence of Thm.~\ref{DeterministicUniquenessTheorem} of potential practical relevance to is the implied lower bound $L_{2k}(\mathbf{BPD}) \geq L_{2k}(\mathbf{A}) - C_1\varepsilon$ in the case where $\mathbf{A}$ satisfies \eqref{SparkCondition}.
-Since solving Prob.~\ref{SLCopt} directly requires a combinatorial search over sparse supports for the $\mathbf{\overline x}_i$ for each proposed dictionary $\mathbf{B}$, rendering it intractable in general, a common strategy is to replace the $\ell_0$-norm in \eqref{minsum} with the $\ell_1$-norm, thereby transforming the inference of sparse $\mathbf{\overline x}_i$ for a fixed dictionary $\mathbf{B}$ into a convex optimization solvable by a linear program.
-A major advance in compressive sensing was the discovery that, for fixed $\mathbf{B}$, solutions to \eqref{minsum} using either norm yield the same sparse vectors $\mathbf{\overline x}_i$ (up to noise) provided $L_{2k}(\mathbf{B})$ is large enough \cite{?}.
-What our results hint at are conditions on the generating dictionary $\mathbf{A}$ and $k$-sparse codes $\mathbf{x}_i$ under which \emph{all} matrices $\mathbf{B}$ (of bounded column-norm) that solve Prob.~\ref{OptimizationProblem} also share this property by virtue of uniqueness and stability; that is, conditions which guarantee that the sparse codes $\mathbf{\overline x}_i$ solving Prob.~\ref{OptimizationProblem} also solve the convexified problem when the corresponding dictionary $\mathbf{B}$ is held fixed.
-It remains to determine, however, what practical conditions preclude matrices that don't solve Prob.~\ref{OptimizationProblem} from nonetheless solving the convexified problem.
-%
-%Regardless, an implication of the above observation is that the following algorithm solves Prob.~\ref{OptimizationProblem} without appeal to combinatorial search:
-%\begin{enumerate}
-%\item List all matrices $\mathbf{B}$.
-%\item For each matrix $\mathbf{B}$, solve $\mathbf{\overline x}_i = \arg \min \|\mathbf{v}\|_1$ s.t. $\|\mathbf{Bv} - \mathbf{z}_i\| \leq \eta$ for $i = 1, \ldots, N$.
-%\item Quantify the proposed solution $\mathbf{B}$ and $\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N$ as $\rho(\mathbf{B}, \mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N) = \sum_{i=1}^{N} \|\mathbf{\overline x}_i\|_0$.
-%\item Output $\arg \min_{\mathbf{B}, \mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N} \left( \rho \right)$.
-% \end{enumerate}
-
-%Since its inception some twenty years ago, sparse coding has become a standard tool in signal analysis, yielding myriad insights into the structure of natural signals across a variety of scientific domains.
-In this work,
-
-%We make a final remark about the tightness of our results and the computability of our derived constants.
-%We remark that our constants have been derived for deterministic ``worst-case'' noise, whereas the ``effective'' noise might be smaller when sampled from a distribution.
-
-%Our results suggest that this correspondence could be due to the ``universality'' of sparse representations in natural data, an early idea in neural theory \cite{pitts1947}.
-
-% \vspace{-.2 cm}
-
-%\showacknow % Display the acknowledgments section
-
-\bibliographystyle{IEEEtran}
-\bibliography{chazthm_ieee_trans_sig}
-
-% \vspace{-.2 cm}
-
 \section{Appendix}\label{proofs}
@@
 %\begin{align*}
-%\text{\rm span}\{\mathbf{M}_{\cap F}\}  = \bigcap_{S \in F} \text{\rm span}\{\mathbf{M}_S\}.
+%\text{\rmfamily span}\{\mathbf{M}_{\cap F}\}  = \bigcap_{S \in F} \text{\rmfamily span}\{\mathbf{M}_S\}.
 %\end{align*}
@@
 \begin{align}\label{DTILeq}
-\text{\rm dist}(\mathbf{u}, V) \leq \frac{1}{1 - \xi(\mathcal{V})} \sum_{i=1}^k \text{\rm dist}(\mathbf{u}, V_i).
+\text{\rmfamily dist}(\mathbf{u}, V) \leq \frac{1}{1 - \xi(\mathcal{V})} \sum_{i=1}^k \text{\rmfamily dist}(\mathbf{u}, V_i).
 \end{align}
@@
 % When $V = \{\mathbf{0}\}$, the result is trivial, so suppose otherwise.  
-Recall the projection onto the subspace $V \subseteq \mathbb{R}^m$ is the mapping $\Pi_V: \mathbb{R}^m \to V$ that associates with each $\mathbf{u}$ its unique nearest point in $V$; i.e., $\|\mathbf{u} - \Pi_V\mathbf{u}\|_2 = \text{\rm dist}(\mathbf{u}, V)$.
+Recall the projection onto the subspace $V \subseteq \mathbb{R}^m$ is the mapping $\Pi_V: \mathbb{R}^m \to V$ that associates with each $\mathbf{u}$ its unique nearest point in $V$; i.e., $\|\mathbf{u} - \Pi_V\mathbf{u}\|_2 = \text{\rmfamily dist}(\mathbf{u}, V)$.
 By repeatedly applying the triangle inequality, we have:
@@
 We next demonstrate that \eqref{cond} holds.
-Fixing $\mathcal{G} \in {\mathcal{H} \choose r} \cup {\mathcal{H} \choose r+1}$, it suffices to show that $d(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}, \bm{\mathcal{A}}_{\cap \mathcal{G}} ) < 1$, since by \eqref{dimLem} we then have $|\cap \pi(\mathcal{G})| = \dim(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}) \leq \dim(\bm{\mathcal{A}}_{\cap \mathcal{G}}) = |\cap \mathcal{G}|$, with equalities from the full column-ranks of $\mathbf{A}_{S}$ and $\mathbf{B}_{\pi(S)}$ for all $S \in \mathcal{H}$.\footnote{Note that if ever $\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})} \neq \bf 0$ while $\cap \mathcal{G} = \emptyset$, we would have $d(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}, \bm 0 ) = 1$.
+Fixing $\mathcal{G} \in {\mathcal{H} \choose r} \cup {\mathcal{H} \choose r+1}$, it suffices to show that $d(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}, \bm{\mathcal{A}}_{\cap \mathcal{G}} ) < 1$, since by \eqref{dimLem} we then have $|\cap \pi(\mathcal{G})| = \dim(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}) \leq \dim(\bm{\mathcal{A}}_{\cap \mathcal{G}}) = |\cap \mathcal{G}|$, with equalities from the full column-ranks of $\mathbf{A}_{S}$ and $\mathbf{B}_{\pi(S)}$ for all $S \in \mathcal{H}$.\footnote{Note that if ever $\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})} \neq /bfseries 0$ while $\cap \mathcal{G} = \emptyset$, we would have $d(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}, \bm 0 ) = 1$.
 However, that leads to a contradiction.} Observe that $d(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}, \bm{\mathcal{A}}_{\cap \mathcal{G}}  )
@@
 d\left( \cap \bm{\mathcal{B}}_{\pi(\mathcal{G})}, \cap \bm{\mathcal{A}}_\mathcal{G} \right)
-&\leq \max_{\mathbf{u} \in \cap \bm{\mathcal{B}}_{\pi(\mathcal{G})}, \ \|\mathbf{u}\|_2 \leq 1} \sum_{S \in \mathcal{G}} \frac{ \text{\rm dist}\left( \mathbf{u},\bm{\mathcal{A}}_{S} \right) }{ 1 - \xi( \bm{\mathcal{A}}_\mathcal{G} ) } \nonumber \\
+&\leq \max_{\mathbf{u} \in \cap \bm{\mathcal{B}}_{\pi(\mathcal{G})}, \ \|\mathbf{u}\|_2 \leq 1} \sum_{S \in \mathcal{G}} \frac{ \text{\rmfamily dist}\left( \mathbf{u},\bm{\mathcal{A}}_{S} \right) }{ 1 - \xi( \bm{\mathcal{A}}_\mathcal{G} ) } \nonumber \\
 &= \sum_{S \in \mathcal{G}} \frac{ d\left( \cap \bm{\mathcal{B}}_{\pi(\mathcal{G})},\bm{\mathcal{A}}_{S} \right) }{ 1 - \xi( \bm{\mathcal{A}}_\mathcal{G} ) }, \nonumber
@@
 \end{proof}
-
-%\section{Proofs of Thm.~\ref{robustPolythm} and Cor.~\ref{ProbabilisticCor}}
-
-%\clearpage
-
-%\section{$\ell_1$-norm Extension}
-%
-%\begin{problem}\label{OptimizationProblemL1}
-%Find a matrix $\mathbf{B}$ and vectors \mbox{$\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N \in \mathbb{R}^m$} that solve:
-%\begin{align}\label{minsum}
-%\min \sum_{i = 1}^N \|\mathbf{\overline x}_i\|_1 \ \ 
-%\text{subject to} \ \ \|\mathbf{z}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \eta, \ \text{for all $i$}.
-%\end{align}
-%\end{problem}
-
-%\begin{corollary}\label{SLCopt}
-%Fix $\alpha > 0$ and suppose all of the assumptions of Thm.\ref{DeterministicUniquenessTheorem} hold with the following modifications:
-%\begin{enumerate}
-%\item The coefficients of all $k$-sparse $\mathbf{x}_i$ are drawn from $[-\beta, \beta]$, where $\beta < \frac{\alpha(k+1)}{k}$.
-%\item More than $(k-1){\overline m \choose k} + q$ vectors $\mathbf{x}_i$ are supported in each $S \in \mathcal{H}$, where
-%\[ q = \left[\frac{\alpha}{\beta}(k+1) - k\right]^{-1}k|\mathcal{H}|(k-1){\overline m \choose k-1}. \]
-%\end{enumerate}
-%Then all solutions to Prob.~\ref{OptimizationProblemL1} for which the nonzero elements of all $\mathbf{\overline x}_i$ lie outside $[-\alpha, \alpha]$ necessarily satisfy the implications \eqref{Cstable} and \eqref{b-PDa} of Thm.~\ref{DeterministicUniquenessTheorem}.
-%\end{corollary}
-
-%\begin{proof}[Proof of Cor.~\ref{SLCopt}]
-%We bound the number of $k$-sparse $\mathbf{\overline x}_i$ and then apply Thm.~\ref{DeterministicUniquenessCorollary}.
-First, observe that no more than $(k-1)|\mathcal{H}|$ of the $\mathbf{\overline x}_i$ share a support $\overline S$ of size less than $k$; otherwise, by the pigeonhole principle, at least $k$ of these indices $i$ belong to the same $K \subseteq I(S)$ for some $S \in \mathcal{H}$ and (as argued previously) \eqref{rhs222} follows.
-Since the right-hand side of \eqref{rhs222} is less than one, by \eqref{dimLem} we have the contradiction $k = \dim(\bm{\mathcal{A}}_S) \leq \dim(\bm{\mathcal{B}}_{\overline S}) \leq |\overline S|.$ The total number of $(k-1)$-sparse vectors $\mathbf{\overline x}_i$ can thus not exceed $|\mathcal{H}|(k-1){ \overline m \choose k-1}$.
-
-%Next, observe that the assumptions of the lemma imply:
-%\begin{align*}
-%\alpha \sum_i \|\mathbf{\overline x}_i\|_0 \leq \sum_i \|\mathbf{\overline x}_i\|_1 \leq \sum_i \|\mathbf{x}_i\|_1 \leq \beta \sum_i \|\mathbf{x}_i\|_0.
-%\end{align*}
-
-%We now apply these facts to bound the number of $k$-sparse $\mathbf{\overline x}_i$.
-Let $n_p$ be the number of $\mathbf{\overline x}_i$ with $\|\mathbf{\overline x}_i\|_0 = p$.
-Since the $\mathbf{x}_i$ are all $k$-sparse, we have:
-%\begin{align*}
-%k \sum_{p = 0}^{\overline m} n_p = k N \geq \sum_{i=0}^N \|\mathbf{x}_i\|_0 \geq \frac{\alpha}{\beta} \sum_{i=0}^N \|\mathbf{\overline x}_i\|_0 = \frac{\alpha}{\beta} \sum_{p=0}^{\overline m} p n_p.
-%\end{align*}
-%Hence, 
-%\begin{align*}
-%\left[ \frac{\alpha(k+1)}{\beta} - k\right] \sum_{p = k+1}^{\overline m} n_p 
-%&\leq \sum_{p = k+1}^{\overline m} (\frac{\alpha}{\beta} p-k) n_p
-%\leq \sum_{p = 0}^k (k - \frac{\alpha}{\beta} p)n_p \\
-%&\leq k \sum_{p = 0}^k n_p 
-%\leq k(1-\frac{\alpha}{\beta})n_k + k|\mathcal{H}|(k-1){ \overline m \choose k-1}
-%\end{align*}
-
-%[Shit, we need $\alpha = \beta$.] Therefore, no more than $q$ vectors $\mathbf{\overline x}_i$ are \emph{not} $k$-sparse.
-Since for every $S \in \mathcal{H}$ there are over $(k-1){\overline m \choose k} + q$ vectors $\mathbf{x}_i$ supported there, it follows that more than $(k-1){\overline m \choose k}$ of them have corresponding $\mathbf{\overline x}_i$ that are $k$-sparse.
-The result now follows directly from Thm.~\ref{DeterministicUniquenessCorollary}.
-%\end{proof}
-
-%\pagebreak
-
-%\begin{corollary}\label{SLCoptL1}
-%If all of the assumptions of Thm.\ref{DeterministicUniquenessTheorem} hold, only now with more than $(k-1)\left[ {\overline m \choose k} + |\mathcal{H}|k{\overline m \choose k-1}\right]$ vectors $\mathbf{x}_i$ supported in each $S \in \mathcal{H}$, then every solution to Prob.~\ref{OptimizationProblemL1} for which the average absolute nonzero coefficient of the $\mathbf{\overline x}_i$ is bounded below by that of the $\mathbf{x}_i$ necessarily satisfies the implications \eqref{Cstable} and \eqref{b-PDa} of Thm.~\ref{DeterministicUniquenessTheorem}.
-%\end{corollary}
-
-%\begin{proof}[Proof of Cor.~\ref{SLCoptL1}]
-%Since the average absolute nonzero coefficient of the $\mathbf{x}_i$ is given by $\alpha = \sum_i \|\mathbf{x}_i\|_1 / \sum_i \|\mathbf{x}_i\|_0$, we have:
-%\begin{align*}
-%\alpha \sum_i \|\mathbf{\overline x}_i\|_0 \leq \sum_i \|\mathbf{\overline x}_i\|_1 \leq \sum_i \|\mathbf{x}_i\|_1 = \alpha \sum_i \|\mathbf{x}_i\|_0.
-%\end{align*}
-%
-%and the result follows by the same arguments as in the proof of Cor.~\ref{SLCopt}.
-%\end{proof}
-
-\end{document}

### 2020-07-16 manuscripts/thesis/conclusions.tex
thesis

\section{Conclusions}\label{conclusions}

HOW DO WE IMPROVE ON HS15?

??????

REVIEWER: Specifically, the authors could address why going from the noise-free case to the noisy case is not incremental. PNAS specifically targets submissions that go beyond what could be published in a more specialized journal. Could the authors, for example, contrast the proof technique between the noisy and noise-free cases? Or, perhaps, the practical implications?

RESPONSE: With all due respect to the reviewer, we believe the most compelling practical implication of a noisy result over a noiseless result is plainly evident: never has there been an experiment without noise and an unstable model is therefore useless in practice. We assume the reviewer must instead be concerned with what additional practical "take-away" message our manuscript contains.  One significant one is the outline of a procedure that can (sufficiently) affirm if one?s proposed solution to Prob. 1 or Prob. 2 is indeed unique. We have updated the manuscript with an explicit statement of this fact, and we outline one such procedure here:

Given a dictionary A and codes x-i that solve Problem 1 (e.g., learned by any algorithm), check that that they satisfy the assumptions of Thm. 1:
   - List the support sets of the x-i.
   - Discard those for which there are (k-1)(m /choose k) or fewer x-i with that support.
   - Discard those for which the supported x-i are not in general linear position. (This should also exclude any supports less than k in size.)
   - From the support sets that remain, list all SIP-satisfying hypergraphs that are subsets of this set.
   - Discard those for which L-(2H)(A) = 0.
   - For each of the remaining hypergraphs, determine the constant C-1 from A and the x-i (or for every subset of the x-i of size (k-1)(m /choose k)).
   - Check that the derived upper bound on /varepsilon exceeds that of the original problem. If yes, the solution is "unique".

There are other practical (polynomial time) implications of our discovery of sufficient combinatorial designs for support sets of generating codes x-i. Moreover, we have shown that a subset of dictionary elements are recoverable even if the number of dictionary elements in total is unknown; these observations are discussed in more detail below.

The reviewer also raises the concern that, regardless of practical implications, our results may amount to an incremental advance over those of (HS15) by way of similar techniques. We disagree with this assessment on both counts: our main result (Thm. 1) goes far beyond a straightforward extension of that in (HS15) to the noisy case and this required a significant deviation from their approach.

It is understandable that the reviewer may have thought otherwise, considering how the proof of Thm. 1 is presented in the manuscript. As observed by our second reviewer, however, the extension to the noisy case did indeed require a novel combination of several results in the literature. Specifically, the main difficulty was to generalize Lemma 1 to the case where the k-dimensional subspaces spanned by corresponding (through the map /pi) submatrices of A and B are assumed only to be proximal (small ?d?), and not identical as in (HS15). In contrast to the noiseless case, here it must be explicitly demonstrated that this proximity relation is propagated through the repeated intersections of these submatrix spans all the way down to the spans of dictionary elements themselves. We designed and proved Lemma 3 to address this issue, which draws its bound from the convergence guarantees of an alternating projections algorithm first proposed by von Neumann. This result, combined with a little known fact about the distance ?d? requiring proof in (M10), constitute the more obscure components of the deduction in Eq. (26). To reiterate, this step is completely trivial in the noiseless case and required no mention for the inductive steps taken in (HS15).

Our proof of Lemma 1 diverges perhaps even more significantly from the approach taken in (HS15) by way of Lemma 4. Key to our reduction of the sample complexity given in (HS15) by an exponential factor is the introduction of a combinatorial design (the "singleton intersection property") for support sets. Since in this case the map /pi from supports in the hypergraph to ([m] /choose k) is not surjective, one can not apply the same inductive method as in (HS15), which freely chooses supports in the codomain to intersect at (k-1) nodes and map back to some corresponding (k-1)-sized intersection of supports in the domain. Instead, we demonstrate the surprising fact that by pigeonholing the images of supports in the (SIP-satisfying) hypergraph H, one can still guarantee a bijection between the nodes and therefore the subspaces spanned by individual dictionary elements. We note that it was necessary to forgo inductive methods altogether in order to prove this fact for all hypergraphs satisfying the SIP; otherwise, we would require that the supports in the hypergraph have intersections of size k? for every k? < k (e.g., this is not the case for the small SIP example we give consisting of the rows and columns of nodes arranged in a square grid). Again, to our surprise, it so happens that this new induction-less argument easily generalizes to the case where B has an arbitrary number of columns, in which case we find that a one-to-one correspondence exists between a subset of columns of A and B of a size that has a nice closed-form expression for regular SIP hypergraphs.

To be clear, the new perspective we take on the problem yields the following powerful conclusions beyond those of a straightforward extension of (HS15) to the noisy case:

1) An extension to the case where the number of dictionary elements is unknown: The results of (HS15) only apply to the case where the matrix B has the same number of columns as A. We forgo this assumption and show that B must have at least as many columns as A and contains (up to noise) a subset of the columns of A. The size of this subset depends on a simple relation between the number of columns of B and the regularity of the support-set hypergraph.

2) A significant reduction in sample complexity: To identify the n x m generating dictionary A, (HS15) require that data be sampled from every k-dimensional subspace spanned by the m columns of A (that is, (m /choose k) subspaces in total). We show that the data need only be sampled from m subspaces in total (e.g. those supported by consecutive intervals of length k in some cyclic order on [m]) and in some cases as few as 2/sqrt(m) (e.g. when m = k**2, take the supports to be the rows and columns of [m] arranged in a square grid). Moreover, if the size of the support set of reconstructing codes is known to be polynomial in m and k, then the pigeonholing argument in the proof of Thm. 1 requires only a polynomial number of samples distributed over a polynomial number of supports; thus, N is then polynomial in /bar m, k. This point was only hinted at in the Discussion section of our original submission, but we have included it in the updated manuscript to make clear the power of our approach over that taken in (HS15).

3) No spark condition requirement for the generating matrix A: One of the mathematically significant contributions made by (HS15) was to forgo the constraint that the recovery matrix B also satisfy the spark condition, in contrast to all previously known uniqueness results which (either explicitly or implicitly) made this assumption.  Our proof is powerful enough to show that, in fact, even the matrix A need not satisfy the spark condition to be identifiable! Rather, it need only be injective on the union of subspaces with supports that form sets in a hypergraph satisfying the singleton intersection property (SIP). (For example, consider the matrix A = [e-1,.., e-5, v] where v = e-1 + e-3 + e-5, and take H to be the set of all consecutive pairs of [m] arranged in cyclic order. Then A satisfies the assumptions of Thm. 1 for dictionary recovery without satisfying the spark condition.) We had omitted this point in our original submission of the manuscript to keep things simple, but we have decided to include this fact in our revision. This also required us to redefine the restricted matrix lower bound L-k to be in terms of a hypergraph H (L-H in the revised manuscript), which is an interesting object for further study in its own right.

We must also reiterate here that our solution to Prob. 2, that of most interest to practitioners of dictionary learning methods, is to our knowledge the first of its kind in both the noise-free and noisy domains. We recognize that this was not clearly communicated in the Discussion section of our submitted manuscript.

Finally, we should mention that our main mathematical results justify the neurally plausible model of bottleneck communication between brain regions, first explained in depth in this NIPS paper (IHS10) and then in a review of sparse linear coding applications to neuroscience (GS12).

-----------------

REVIEWER:The paper could also compare the sample complexity results on N with those given in the noise-free case. For example, Table I in reference (18) gives a comparison of sample complexity requirements for different conditions in the noise-free case. Where would the results of this paper stand in that table?

RESPONSE: In brief, since all of the theorems and corollaries in (HS15) are corollaries of our theorems, all sample complexities improve by our work. The main point of difference between our statements about sample complexity and those of (HS15) is the assumed constraint on the underlying support set of sparse codes x-i. Our theory of combinatorial designs (the ?singleton intersection property?) requires only that there be a sufficient number of x-i drawn from each support in a hypergraph satisfying the SIP, whereas the theory in (HS15) requires that a sufficient number of x-i be drawn from every support of size k in [m]. Below, we make an explicit comparison with Table I in (HS15) row by row, assuming for our results that sufficient data have been sampled from all supports in a hypergraph H satisfying the SIP:

ROW I. Our result here is |H|(k-1)(m /choose k) + 1. We improve on the result in (HS15) by an exponential factor since our theory does not require that data be sampled with every possible support of size k in [m]; as noted in our manuscript, for every k < m there exists a hypergraph H with |H| = m that satisfies the SIP.

ROW 2. Our result here is again |H|(k-1)(m /choose k) + 1 with certainty, not with almost certainty (i.e. probability 1) as in (HS15). Here, the authors in (HS15) have applied probabilistic arguments to achieve an almost certain result with a sample complexity on the same order as that for which we have achieved a certain result by means of our theory of combinatorial designs.

ROW 3. We cannot make a direct comparison here because we have not calculated the probability that a random set of supports satisfy the SIP (see our response to a similar question by the second reviewer). We think this is an interesting problem for the community to solve; regardless, the result of (HS15) here is still implied by our more general theory.

ROW 4. Our result here is |H|(k-1)(m /choose k) + 1 with probability 1. Here is the only case where the sample complexity stated in (HS15) is technically better than ours, but it differs in flavor: their x-i are assumed to be distributed as (k+1) samples per support for every support of size k in [m], whereas ours supposes that (k-1)(m /choose k) codes x-i are distributed over each support in some hypergraph H satisfying the SIP. Regardless, the (technically) better result of (HS15) is still implied by our more general theory in the case /varepsilon = 0 with the addition of their probabilistic argument.

ROW 5: Again, we cannot make a direct comparison here for the reason stated in ROW 3.

To sum up, while we appreciate this question, we feel that since our results improve in every case except for one noise-free technicality (ROW 4), and since the results of (HS15) are all entailed anyway by our more general theory, an explicit comparison such as that which we provided above would not be the best use of our limited space in the manuscript; although we are willing to add a discussion about this if necessary. Many thanks for your careful review of the mathematics. We have tried and continue to try to be as clear, concise, and correct as we possibly can to elevate this work into the top echelon of applied mathematical theory papers.

??

REVIEWER: An editor who doesn't want to get suckered is always looking at papers
to find a very specific 'gadget' or 'gadgets' that mark the distinction
between the submitted work and 'obvious', 'trivial' work.

I can't really tell if the hypergraph construct is such a gadget. It's
really only handled in passing and only two examples are mentioned.

-------------------------------------

RESPONSE:

In our previous response, we described in detail how the definition of a new matrix lower bound induced by a hypergraph enables the following advancements in our understanding of Prob. 1 beyond an extension of previous results to the noisy case:

1) a subset of dictionary elements is recoverable even if dictionary size is overestimated,
2) data require only a polynomial number of distinct sparse supports,
3) the spark condition is not a necessary property of recoverable dictionaries.

Given these insights, we believe the term "gadget" strongly downplays the power of this construct. Certainly, we don't see it as being only treated in passing, as it is incorporated into every one of our theorems. The examples we provide briefly demonstrate the gains to be made from this discovery, so as to entice the community into fully exploring the ramifications of an underlying theory of hypergraphs in practice.

??????

REVIEWER: So I'm at a standstill. I would need to be convinced that you have actual
gadgets that go beyond what I would have come up with and that the
identifiability problem is dramatically different than what an 'obvious' or
'easy-to-guess' solution might say, by showing me something very concrete
that I can understand. The lack of any explicit implementation on a
computer on a specific example doesn't help.

-------------------------------------

RESPONSE:

It seems to us that assessing a solution as "obvious" after-the-fact -- when it has already informed one's intuition -- is a bit unfair. It is always easy to guess, easier to guess wrong, and hardest to prove. Still, if unintuitive results are what sell these days, we offer a nice surprise for everyone who reads our paper and realizes how strange it is that they have never come across a definition of the problem akin to Def. 1 anywhere in the literature on dictionary learning before.

Problems 1 and 2 have been studied for two decades now, and no one has pointed out the relation between them, nor the existence of the underlying hypergraph structure. Our solution to Prob. 2, that of most interest to practitioners of dictionary learning methods, is the first of its kind in both the noise-free and noisy domains. If these solutions are the "easy-to-guess", "obvious" solutions, then so be it; we cannot change geometry. Actually, we prefer results for which intuition can play its role in lending credence to the truth.

PRACTICAL IMPLICATIONS:

REVIEWER: When is it possible to determine (numerically) if enough data has been gathered to obtain an accurate estimate of the underlying sparsity dictionary?
-----------------

RESPONSE: A statement of this very general nature requires that we calculate the probability that all of the conditions of Thm. 1 are satisfied by random data. We have provided an "almost certain" guarantee of this flavor in Cor 2, wherein the sparse vector supports are constrained to form a hypergraph satisfying the SIP. It would be useful and interesting to calculate furthermore the probability that random supports form a hypergraph satisfying the SIP. We have opted not to include these calculations due in part to space constraints, but also because we believe that what sets our work apart from the vast majority of results in the field is their deterministic nature, e.g. they do not depend on any kind of assumption about the particular random distribution from which the sparse supports, coefficients, or dictionary entries are drawn.

-----------------
Is there any new intuition to be had regarding the necessary sampling of the union of subspaces from this analysis (with respect to the intuition obtained from existing uniqueness results)?
-----------------

RESPONSE: Yes, there is indeed. While all existing uniqueness results require a sufficient number of samples be drawn from each of (m /choose k) possible supports, we have shown that it is enough that a sufficient number of samples be drawn from every support in a subset of drastically smaller size, provided this subset forms a regular hypergraph satisfying the SIP. As was pointed out in our manuscript, a support set of size m satisfying these criteria can always be constructed for any k < m (e.g. take the consecutive intervals of length k in some cyclic order on [m]), and in certain cases such a set can be constructed from as few as 2/sqrt(m) supports (e.g. when m = k**2, take the supports to be the rows and columns of [m] arranged in a square grid).

??

REVIEWER: 
This is at best about local stability, rather than stability. The size
of the neighborhood where you're getting stability is presumably almost
infinitesimal in general. While I agree that the paper is written in a
quantitative way and has as you say constants which can be quantitative, it
is I would say after a few readings, more
seemingly-quantitative-but-actually-purely-qualitative.
If it could be shown to be surprisingly effective in some specific case, I
might withdraw from this position.

-------------------------------------

RESPONSE:

[Files included: 2017-06210R-AuthorResponseManuscript.pdf, compute-C2.py, decomp-svd.py, sample-complexity.py, C2-Grid-m64-n32-k8-r2-nt500.pdf, C2-Grid-m256-n128-k16-r2-nt500.pdf, C2-Grid-m1024-n512-k32-r2-nt50.pdf, prob-vs-samples.png, samples-vs-m.png]

We are somewhat confused by this statement as we understand even the tightest possible noise bound to be necessarily "local" and approaching zero as the domain-restricted matrix lower-bound vanishes, e.g. as the number of dictionary elements grows. One need only consider the case k=1, where every dictionary element spans a ray through the origin, and each identifiable datum generated from the model of Eq. 1 lies within a cylinder of radius /eta around one (and only one) of these rays. Clearly, for bounded data in a finite dimensional space, this radius cannot remain finite in the limit of infinitely many distinct rays.

The issue seems to rather be that the bound (defined using the constant C1, which depends in turn on the constant C2) is, in general, so small that it is "practically infinitesimal". As is the case for any deterministic guarantee, we must entertain the "worst-case" scenario, where noise is isotropic and "what can go wrong, will go wrong?. Consequently, some degree of pessimism is forced upon us here, whereas calculations specific to the data at hand would consider the probability distribution of confounding noise and likely yield more forgiving probabilistic bounds. To respond to this valid concern nonetheless, we have investigated our deterministic constants more thoroughly.

The denominator of C1 involves a relatively standard quantity in the field of compressed sensing (the "restricted isometry constant"), and it is known to be reasonable for many random distributions generating original dictionaries A and codes. The constant C2, on the other hand, depends on a much less well studied quantity /xi computed from the "Friedrichs angle" between certain spans of A's columns.

Upon re-examination of our proof, we have determined that our expression for C2 was egregiously sub-optimal. As it turns out, the minimum in the denominator of C2 need only be computed over subsets of H of size r+1 (where r is the regularity of the hypergraph) -- not over all subsets of H. Moreover, the 2**|H| in the numerator -- which in fact need only have been |H| in our previous submission -- can actually be set to r+1 (e.g. for the SIP hypergraph consisting of consecutive intervals of length k in [m] we have |H| = m, whereas r=k).

To determine the practical utility of this adjusted constant, we have performed computer experiments (Python code "compute-C2.py", "decomp-svd.py" included) calculating it for some generic matrices with example hypergraphs from our paper's introduction (i.e. the rows and columns formed by arranging [m] into a square grid). The results suggest that the bound is actually quite reasonable; certainly, it is not ?practically infinitesimal" (Figures "C2-Grid-m64-n32-k8-r2-nt500.pdf", "C2-Grid-m256-n128-k16-r2-nt500.pdf", "C2-Grid-m1024-n512-k32-r2-nt50.pdf", included over different latent dimensions m=64,256,1024).

-------------------------------------

REVIEWER: I can't really tell if your cardinality bound on the number of samples
needed for a stable representation is one such gadget. I am unable on my
own to conjure up an example where I might have thought an exponential
number of samples would be required but you show me very explicitly that
no, a dramatically smaller number is required.

RESPONSE:

If there is any one "gadget" to which we may credit our results, it is the pigeonhole principle, which we have applied in a way (see Lem. 4) that demonstrates that only a polynomial number of sparse supports are necessary in general for stable identification of the generating dictionary. In our view, this lends much more legitimacy to the use of the sparse linear coding model in practice, where data in general are unlikely (if ever) to exhibit the exponentially many possible k-wise combinations of dictionary elements, as all previous results have required.

It may very well be impossible to to exorcise exponentiality from the number of required samples in the deterministic or almost-certain case. However, our guarantees can easily be extended to hold with some probability for any number of samples by appealing instead to a probabilistic pigeonholing at the point in our proof of Thm. 1 where the deterministic pigeonhole principle is applied to demonstrate that for every S in H, there exist k vectors x-i supported on S whose corresponding /bar x-i all share the same support. (A famous example of such an argument is the counter-intuitive "birthday paradox", which demonstrates that the probability of two people having the same birthday in a room of twenty-three is in fact greater than 50pcnt.) This point in the proof then has some probability of success, which must occur for all S in H in order for the proof as a whole to be valid.

In this spirit, we have computed for all sample sizes up to our deterministic sample complexity the probability with which our guarantees still hold when H is one of the two example hypergraphs from our paper's introduction, the set of consecutive intervals of length k in a cyclic order on [m] (Figure "prob-vs-samples.png", Python code "sample-complexity.py"). The probability of our guarantees holding saturates when the number of samples reaches only a fraction of the deterministic sample complexity.

We have also computed the number of samples required for our guarantees to hold with probability 99.9percent for fixed k as m increases (Figure "samples-vs-m.png"). The ratio of the number of samples required for this 99.9percent guarantee with respect to the number of samples required by the deterministic 100percent guarantee of Thm. 1 tends to zero as m increases.

It would be a simple matter to add discussion of these facts to the manuscript, if so desired.

-------------------------------------

REVIEWER:
In my opinion, while the extension from exact to noisy stability of
dictionary learning (DL) is significant, the fact that the analysis relies
on metrics of the data that are not feasible to compute limits its impact
to the scientific community beyond computer science and applied
mathematics. While the authors state in their response that their results
validate the extensive successful use of DL in practice, there seems to be
little impact to this given that the methodology is already in widespread
use; instead, practical criteria that allows practitioners to establish
whether the data model obtained from DL is optimal or not would have very
high impact. My questions in the review were probing whether any
contribution of this type was present, and the responses appear to point
toward a negative answer.

-------------------------------------

RESPONSE:

What sets our work apart from the vast majority of results in the field is that they are deterministic, and do not depend on any kind of assumption about the particular random distribution from which the sparse supports, coefficients, or dictionary entries are drawn. Consequently, our paper directly justifies only "in principle" the inferences of those who apply dictionary learning methods to inverse problems in their research. But this is unavoidably the case for NP-hard problems.

In the realm of practicality, we have spelled-out the problem (i.e. estimate C1) for statisticians, who will derive from our deterministic guarantees the statistical criteria for inference in more domain-specific probabilistic models, and we have cut in half the work it takes a computer scientist to prove the consistency of any dictionary learning algorithm (i.e. prove that the algorithm converges to any solution encoding the data to within the epsilon in Eq. 8). Our work is the assist to these many impactful results to come, and (just as in hockey) we feel this deserves as much acknowledgement as any contingent goal.

-------------------------------------

THEORETICAL IMPLICATIONS

REVIEWER: 
Point (a) is important because when you say these results somehow
validate various neuroscience ideas, I am saying in the back of my mind
that you're bravely talking yourself on a ledge. Namely, nothing in
neuroscience can really depend on infinitesimal stability. Trying to make a
claim like this seems to undermine your credibility with me. It seems the
referees had the same problem.

-------------------------------------

RESPONSE:

Our response to point (a) aside, and though we are not inclined to assume that neural circuits are incapable of extreme precision when necessary, we actually share your skepticism here regarding the modern theory of "sparse coding" (O04) for efficient representation of sensory input in brains (vision: (O96), (H96), (B97), (vH98); audio: (B96), (S06), (C12)), as well as corresponding models of bottleneck communication between neurons that utilize ideas from compressed sensing ((C10), (I10), (G12)). Nonetheless, our paper confirms the well-posedness of the central noisy sensory coding problem that specialists in these fields have suggested neural circuits might be solving, and we have verified (for the first time) that the bottleneck communication model represents a neurally plausible way of faithfully transmitting sparse sensory representations through a noisy bandwidth-limited channel.

If the editors are still reluctant to become complicit in propagating unproven hypotheses of neural computation, we have no qualms downplaying this application in the manuscript. Perhaps instead, we could elaborate more on implications for the repeatability of discoveries in experimental science contingent on machine learning, which includes an explanation for the universality of the above results (e.g. "Gabors") in sensory representation (independent of any particular theory of brain computation). For example, over the years there have been many appeals to dictionary learning with sparseness constraint for uncovering latent structure in data (e.g. forgery detection (H10), (O10); brain recordings (J01), (A14), (L16); gene expression (Wu16)), several of which appear in PNAS.

-------------------------------------

REVIEWER: It's not clear why exact uniqueness should be so important for
neuroscience. It seems more likely that mere similarity is what's maybe
important. In the same sense it's not clear why formal Lipschitz stability
in the mathematical sense should be so important for neuroscience. It seems
more important that some sort of qualitative similarity should persist
under perturbations.

RESPONSE:

Unfortunately, how brains work is still largely a mystery. There are, however, some ideas for why certain models are more appealing than others. Here is how we rationalize the application of unsupervised sparse coding to the theory of bottleneck communication:

Suppose some quantities of interest are encoded in the sparse activity of neurons in a sending region (it has been proposed that neural activity in certain brain regions is "sparse", e.g. for energy efficiency). These quantities are to be transmitted to some other region through as few wires (axons) as possible, e.g. due to space constraints inside the skull.

The hypothesis is that the brain, up-to date on the latest fad, solves this problem by applying a (noisy) "random" projection into the lower-dimensional space spanned by these axons. The neurons in the receiving region are then tasked with decoding the quantities of interest from this compressed signal. Suppose, however, that they cannot read out this information directly from the compressed signal. Rather, the neurons in the receiving region must first reproduce to some extent the original sparse pattern of activity before they can decode from it the quantities of interest (perhaps a sparse representation is necessary or advantageous in the receiving region, just as in the sending region). Moreover - and this is central to the hypothesis - they must accomplish this feat without knowledge of the random projection applied by the sender, i.e. via dictionary learning with a sparseness constraint.

In this way, the persistence of a "qualitative similarity", modeled mathematically as the formal similarity between the decodable quantities of interest in the two regions, is contingent on the uniqueness and stability of sparse representations. We have proven that any dictionary learning procedure implemented in the receiving region (biologically plausible algorithms are an active area of research (P15)) that does "well enough" will indeed yield a sparse activity pattern that is similar (at least, up to inherent relabelling ambiguity) to the original pattern in the sending region, as required.

It is entirely possible, and in our opinion very likely, that the encoding and decoding procedures implemented in nervous tissue are far more sophisticated. The science is just not there yet. At the very least, we have demonstrated that the only published hypothesis regarding how this could be done is well-founded, mathematically.

-------------------------------------

REVIEWER:
The perturbation bound is used by the authors to provide some explanation for why, in practice, different methods lead to similar dictionaries. Can that also be used to explain the second (bold) part of their observation that ?[these waveforms] appear in dictionaries learned by a variety of algorithms trained with respect to different natural image datasets.?? Just curious.

RESPONSE:
To be clear, this (bold) observation is just an observation which motivates the work. Imagining natural image patches to form a population which satisfies (1) with respect to some ground truth dictionary A, we have shown that there exists a sufficient number of samples to uniquely identify it or something close to it via approximate solutions. Given this fundamental stability and uniqueness of the problem solutions, the fact that a variety of methods geared to approximately solve Problems 1 and 2 all seem to capture similar structure is much less surprising.

FUTURE DIRECTIONS

NOTE: Structured dictionaries? Just derive the bounds specific to them. Could be efficiently computable in specific cases.

REVIEWER

As l0 norm is intractable, does all the properties still hold for l1 norm minimization? Can we solve it efficiently (polynomial time) to global optimality? Similar issue for other works, such as
https://arxiv.org/pdf/1807.05595.pdf

RESPONSE:
We make no claims in this paper about l1-norm minimization, though we are hopeful a clever reader may find some way to build off our results and derive related guarantees for this continuous relaxation of the sparse coding problem.

TODO : can we deterministically generate matrices injective on SIP hyper graphs? The (mCk)-hypergraph is one such possibility, so maybe not in general? But for special cases (convolution matrices..?)

### 2020-07-16 manuscripts/thesis/discussion.tex
thesis

--- 2019-05-10 manuscripts/IEEE/final_submission.tex
@@
-% TODO: 
-% Make L_H a definition..? Change def of L to be 1-norm so we don't need these sqrt k's?
-% C_1 depends on J in Thm 1
-% also in proof of (7) x need not be *any* 2k-sparse vector...can instead restrict to some H...then 2k is restricted to half being on H.
-
-% Notes:
-%
-% Can we prove in a line or two that the inverse problem is stable by arguing that the function is bijective and closed therefore a homeomorphism?
-% Should we mention the notion of Grassmannian manifolds and that Theta is a metric on this space?
-% Change robustness to stability?
-%
-\documentclass[journal, twocolumn]{IEEEtran}
-
-% *** MATH PACKAGES ***
-\usepackage{amsmath, amssymb, amsthm} 
-\newtheorem{theorem}{Theorem}
-\newtheorem{lemma}{Lemma}
-\newtheorem{conjecture}{Conjecture}
-\newtheorem{problem}{Problem}
-\newtheorem{question}{Question}
-\newtheorem{proposition}{Proposition}
-\newtheorem{definition}{Definition}
-\newtheorem{corollary}{Corollary}
-\newtheorem{remark}{Remark}
-\newtheorem{example}{Example}
-
-\usepackage[pdftex]{graphicx}
-
-% *** ALIGNMENT PACKAGES ***
-\usepackage{array}
-\usepackage{cite}
-\usepackage{bm}
-
-% correct bad hyphenation here
-%\hyphenation{op-tical net-works semi-conduc-tor}
-
-\begin{document}
-
-%\title{When can a generating dictionary and sparse codes be recovered from noisy data?}
-%\title{When is the dictionary learning problem well-posed?}
-\title{On the uniqueness and stability of dictionaries \\ for sparse representation of noisy signals}
-%\title{When is the dictionary learning problem for sparse coding well-posed?}
-%\title{When is the sparsest representation unique?}
-%\title{When are sparse codes identifiable from their unknown noisy compressive measurements?}
-% FRITZ2: The title doesn't reflect the amount of new stuff, it seems incremental from the last one. It's not very meaningful.
-% FRITZ: Not everyone knows what well-posed means. You should mention recovery from noisy data in the title.
-
-\author{Charles~J.~Garfinkle and Christopher~J.~Hillar \\
-Redwood Center for Theoretical Neuroscience, Berkeley, CA, USA
-%\thanks{%e-mails: cjg@berkeley.edu, chillar@msri.org.  
-%CG and CH supported, in part, by NSF grant IIS-1219212 and the Statistical and Applied Mathematical Sciences Institute, under NSF DMS-1127914.}
-}
-
-\maketitle
-
-% \keywords{Sparse coding, dictionary learning, matrix factorization, compressed sensing, inverse problems, blind source separation}
-
-\begin{abstract}
-%Learning optimal dictionaries for sparse coding has exposed characteristic sparse features of many natural signals.
-However, there are few universal conditions guaranteeing the stability of such features in the presence of noise.
-Here, we prove very generally that optimal dictionaries and sparse codes are unique up to measurement error for all diverse enough datasets generated by the sparse coding model.
-Applications are given to data analysis, engineering, and neuroscience.
-Learning optimal dictionaries for sparse coding has exposed characteristic sparse features of many natural signals.
-However, universal guarantees of the stability of such features in the presence of noise are lacking.
-Here, we provide very general conditions guaranteeing when dictionaries yielding the sparsest encodings are unique and stable with respect to measurement or modeling error.
-We demonstrate that some or all original dictionary elements are recoverable from noisy data even if the dictionary fails to satisfy the spark condition, its size is overestimated, or only a polynomial number of distinct sparse supports appear in the data.
-Importantly, we derive these guarantees without requiring any constraints on the recovered dictionary beyond a natural upper bound on its size.
-Our results also yield an effective procedure sufficient to affirm if a proposed solution to the dictionary learning problem is unique within bounds commensurate with the noise.
-We suggest applications to data analysis, engineering, and neuroscience and close with some remaining challenges left open by our work.
-\end{abstract}
-
-% Optional adjustment to line up main text (after abstract) of first page with line numbers, when using both lineno and twocolumn options.
-% You should only change this length when you've finalised the article contents.
-
-\section{Introduction}\label{Intro}
-\IEEEPARstart{S}{parse} coding is a common modern approach to pattern analysis in signal processing whereby each of $N$ observed $n$-dimensional signal samples is viewed as a (noisy) linear combination of at most $k$ elementary waveforms drawn from some unknown ``dictionary" of size $m \ll N$ (see \cite{Zhang15} for a comprehensive review).
-%\IEEEPARstart{A}{}common modern approach to pattern analysis in signal processing is to view each of $N$ observed $n$-dimensional signal samples as a (noisy) linear combination of at most $k$ elementary waveforms drawn from some unknown ``dictionary" of size $m \ll N$ (see \cite{Zhang15} for a comprehensive review).
-Optimizing dictionaries subject to this and related sparsity constraints has revealed seemingly characteristic sparse structure in several signal classes of current interest (e.g., in vision \cite{wang2015sparse}).
-
-Of particular note are the seminal works in the field \cite{Olshausen96, hurri1996image, bell1997independent, van1998independent}, which discovered that dictionaries optimized for coding small patches of ``natural" images share qualitative similarities with linear filters estimated from response properties of simple-cell neurons in mammalian visual cortex.
-Curiously, these waveforms (e.g., ``Gabor'' wavelets) appear in dictionaries learned by a variety of algorithms trained over different natural image datasets, suggesting that learned features in natural signals may, in some sense, be canonical \cite{donoho2001can}.
-
-Motivated by these discoveries and more recent work relating compressed sensing \cite{eldar2012compressed} to a theory of information transmission through random wiring bottlenecks in the brain \cite{Isely10}, we address when dictionaries for sparse representation are indeed identifiable from data.
-Answers to this question may also have implications in practice wherever an appeal is made to latent sparse structure of data (e.g., forgery detection \cite{hughes2010, olshausen2010applied}; brain recordings \cite{jung2001imaging, agarwal2014spatially, lee2016sparse}; and gene expression \cite{wu2016stability}).
-
-While several algorithms have been recently proposed to provably recover unique dictionaries under specific conditions (see \cite[Sec.~I-E]{Sun16} for a summary of the state-of-the-art), few theorems can be invoked to justify the consistency of inference under this model of data more broadly.
-To our knowledge, a universal guarantee of the uniqueness and stability of learned dictionaries and the sparse representations they induce over noisy data has yet to appear in the literature.
-% in justifying the identification of forged paintings by their anomalous sparse representations \cite{hughes2010},
-
-Here, we prove very generally that uniqueness and stability is a typical property of sparse dictionary learning.
-More specifically, we show that matrices injective on a sparse domain are identifiable from \mbox{$N = m(k-1){m \choose k} + m$} noisy linear combinations of $k$ of their $m$ columns up to an error that is linear in the noise (Thm.~\ref{DeterministicUniquenessTheorem}).
-In fact, provided $n \geq \min(2k,m)$, in almost all cases the problem is well-posed, as per Hadamard \cite{Hadamard1902}, given a sufficient amount of data (Thm.~\ref{robustPolythm} and Cor.~\ref{ProbabilisticCor}).
-
-Our guarantees also hold for a related (and perhaps more commonly posed, e.g.
-\cite{rehnsommer2007}) optimization problem seeking a dictionary minimizing the average number of elementary waveforms required to reconstruct each sample of the dataset (Thm.~\ref{SLCopt}).
-To practical benefit, our results impose no restrictions on learned dictionaries (e.g., that they, too, be injective over some sparse domain) beyond an upper bound on dictionary size, which is necessary in any case to avoid trivial solutions (e.g., allowing $m = N$).
-%That is, every pair of solutions of comparable size has some number of dictionary elements in common (up to noise), and similarly so for the coefficients of sparse codes they induce.
-
-More precisely, let $\mathbf{A} \in \mathbb R^{n \times m}$ be a matrix with columns $\mathbf{A}_j$ ($j = 1,\ldots,m$) and let dataset $Z$ consist of measurements:
-\begin{align}\label{LinearModel}
-\mathbf{z}_i = \mathbf{A}\mathbf{x}_i + \mathbf{n}_i,\ \ \  \text{$i=1,\ldots,N$},
-\end{align}
-for $k$-\emph{sparse} $\mathbf{x}_i \in \mathbb{R}^m$ having at most $k<m$ nonzero entries and \emph{noise} $\mathbf{n}_i \in \mathbb{R}^n$, with bounded norm $\| \mathbf{n}_i \|_2 \leq  \eta$ representing our worst-case uncertainty in measuring the product $\mathbf{A}\mathbf{x}_i$.
-We first consider the following formulation of sparse coding.
-%The first mathematical problem we consider is the following.
-
-\begin{problem}\label{InverseProblem}
-Find a dictionary matrix $\mathbf{B}$ and $k$-sparse codes $\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N$ that satisfy $\|\mathbf{z}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \eta$ for all $i = 1,\ldots,N$.
-\end{problem}
-
-Note that every solution to Prob.~\ref{InverseProblem} represents infinitely many equivalent alternatives $\mathbf{BPD}$ and $\mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_1, \ldots, \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_N$ parametrized by a choice of permutation matrix $\mathbf{P}$ and invertible diagonal matrix $\mathbf{D}$.
-Identifying these ambiguities (labelling and scale) yields a single orbit of solutions represented by any particular set of elementary waveforms (the columns of $\mathbf{B}$) and their associated sparse coefficients (the entries of $\mathbf{\overline x}_i$) that reconstruct each data point $\mathbf{z}_i$.
-
-Previous theoretical work addressing the noiseless case $\eta =0$ (e.g., \cite{li2004analysis, Georgiev05, Aharon06, Hillar15}) for matrices $\mathbf{B}$ having exactly $m$ columns has shown that a solution to Prob.~\ref{InverseProblem}, when it exists, is unique up to such relabeling and rescaling provided the $\mathbf{x}_i$ are sufficiently diverse and $\mathbf{A}$ satisfies the \textit{spark condition}:
-\begin{align}\label{SparkCondition}
-\mathbf{A}\mathbf{x}_1 = \mathbf{A}\mathbf{x}_2 \implies \mathbf{x}_1 = \mathbf{x}_2, \ \ \ \text{for all $k$-sparse } \mathbf{x}_1, \mathbf{x}_2,
-\end{align}
-%
-which is necessary to guarantee the uniqueness of arbitrary $k$-sparse $\mathbf{x}_i$.
-We generalize these results to the practical setting  $\eta > 0$ by considering the following natural notion of stability with respect to measurement error.
-
-\begin{definition}\label{maindef}
-Fix $Y = \{ \mathbf{y}_1, \ldots, \mathbf{y}_N\} \subset \mathbb{R}^n$.
-We say $Y$ has a \textbf{$k$-sparse representation in $\mathbb{R}^m$} if there exists a matrix $\mathbf{A}$ and $k$-sparse $\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$ such that $\mathbf{y}_i = \mathbf{A}\mathbf{x}_i$ for all $i$.
-This representation is \textbf{stable} if for every $\delta_1, \delta_2 \geq 0$, there exists some $\varepsilon = \varepsilon(\delta_1, \delta_2)$ that is strictly positive for positive $\delta_1$ and $\delta_2$ such that if $\mathbf{B}$ and $k$-sparse $\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N \in \mathbb{R}^m$ satisfy:
-\begin{align*}
-	\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \varepsilon(\delta_1, \delta_2),\ \   \text{for all $i=1,\ldots,N$},
-\end{align*}
-then there is some permutation matrix $\mathbf{P}$ and invertible diagonal matrix $\mathbf{D}$ such that for all $i, j$:
-\begin{align}\label{def1}
-\|\mathbf{A}_j - (\mathbf{BPD})_j\|_2 \leq \delta_1 \ \text{and} \ \|\mathbf{x}_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_i\|_1 \leq \delta_2.
-\end{align}
-\end{definition}
-
-To see how Prob.
-\ref{InverseProblem} motivates Def.
-\ref{maindef}, suppose that $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$ and fix $\delta_1, \delta_2$ to be the desired accuracies of recovery in \eqref{def1}.
-Consider any dataset $Z$ generated as in \eqref{LinearModel} with $\eta \leq \frac{1}{2} \varepsilon(\delta_1, \delta_2)$.
-Using the triangle inequality, it follows that any $n \times m$ matrix $\mathbf{B}$ and $k$-sparse $\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N$ solving Prob.~\ref{InverseProblem} are necessarily within $\delta_1$ and $\delta_2$ of the original dictionary $\mathbf{A}$ and codes $\mathbf{x}_1, \ldots, \mathbf{x}_N$, respectively.\footnote{We mention that the different norms in \eqref{def1} reflect the distinct meanings typically ascribed to the dictionary and sparse codes in modeling data.}
-
-The main result of this work is a very general uniqueness theorem for sparse coding (Thm.~\ref{DeterministicUniquenessTheorem}) directly 
-implying (Cor.~\ref{DeterministicUniquenessCorollary}), which guarantees that sparse representations of a dataset $Z$ are unique up to noise whenever generating dictionaries $\mathbf{A}$ satisfy a spark condition on supports and the original sparse codes $\mathbf{x}_i$ are sufficiently diverse (e.g., Fig.~\ref{noisyrecovery}).
-Moreover, we provide an explicit, computable $\varepsilon(\delta_1, \delta_2)$ in (\ref{epsdel}) that is linear in desired accuracy $\delta_1$, and essentially so in $\delta_2$.
-
-In the next section, we give formal statements of these findings.
-We then extend the same guarantees (Thm.~\ref{SLCopt}) to the following alternate formulation of dictionary learning, which minimizes the total number of nonzero entries in sparse codes.
-
-\begin{problem}\label{OptimizationProblem}
-Find matrices $\mathbf{B}$ and vectors \mbox{$\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N$} solving:
-\begin{align}\label{minsum}
-\min \sum_{i = 1}^N \|\mathbf{\overline x}_{i}\|_0 \ \
-\text{subject to} \ \ \|\mathbf{z}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \eta, \ \text{for all $i$}.
-\end{align}
-\end{problem}
-
-Our development of Thm.~\ref{DeterministicUniquenessTheorem} is general enough to provide some uniqueness and stability even when generating $\mathbf{A}$ do not fully satisfy (\ref{SparkCondition}) and recovery dictionaries $\mathbf{B}$ have more columns than $\mathbf{A}$.
-Moreover, the approach incorporates a combinatorial theory for designing generating codes that should be of independent interest.
-We also give brief arguments adapting our results to dictionaries and codes drawn from probability distributions (Cor.~\ref{ProbabilisticCor}).
-The technical proofs of Thms.~\ref{DeterministicUniquenessTheorem} and ~\ref{SLCopt} are deferred to Sec.~\ref{DUT}, following some necessary definitions and a fact in combinatorial matrix analysis (Lem.~\ref{MainLemma}; proven in the Appendix).
-Finally, we discuss in Sec.~\ref{Discussion} applications of our mathematical observations as well as open questions.
-%The Appendix contains a proof of Lem.~\ref{MainLemma}.
-
-\section{Results}\label{Results}
-
-%Denote by $\mathbf{x}^J$ the subvector formed from the entries of $\mathbf{x}$ indexed by $J$. 
-%A set of $k$-sparse vectors is said to be in \emph{general linear position} when any $k$ of them are linearly independent.
-
-Precise statements of our results require that we first identify some combinatorial criteria on the supports\footnote{Recall that a vector $\mathbf{x}$ is said to be \emph{supported} in $S$ when $\mathbf{x} \in \text{\rm span}\{\mathbf{e}_j: j\in S\}$, with $\mathbf{e}_j$ forming the standard column basis.} of sparse vectors.
-Let $\{1, \ldots, m\}$ be denoted $[m]$, its power set $2^{[m]}$, and ${[m] \choose k}$ the set of subsets of $[m]$ of size $k$.
-A \emph{hypergraph} on vertices $[m]$  is simply any subset $\mathcal{H} \subseteq 2^{[m]}$.
-We say that $\mathcal{H}$ is \textit{$k$-uniform} when $\mathcal{H} \subseteq {[m] \choose k}$.
-The \emph{degree} $\deg_\mathcal{H}(i)$ of a node $i \in [m]$ is the number of sets in $\mathcal{H}$ that contain $i$, and we say $\mathcal{H}$ is \emph{regular} when for some $r$ we have $\deg_\mathcal{H}(i) = r$ for all $i$ (given such an $r$, we say $\mathcal{H}$ is \textit{$r$-regular}).
-We also write $2\mathcal{H} := \{ S \cup S': S, S' \in \mathcal{H}\}$.
-The following class of structured hypergraphs is a key ingredient in this work.
-
-\begin{definition}\label{sip}
-Given $\mathcal{H} \subseteq 2^{[m]}$, the \textbf{star} $\sigma(i)$ is the collection of sets in $\mathcal{H}$ containing $i$.
-We say $\mathcal{H}$ has the \textbf{singleton intersection property} (\textbf{SIP}) when $\cap \sigma(i) = \{i\}$ for all $i \in [m]$.
-\end{definition}
-
-We next give a quantitative generalization of the spark condition (\ref{SparkCondition}) to combinatorial subsets of supports.
-The \emph{lower bound} of an $n \times m$ matrix $\mathbf{M}$ is the largest $\alpha$ with \mbox{$\|\mathbf{M}\mathbf{x}\|_2 \geq \alpha\|\mathbf{x}\|_2$} for all $\mathbf{x} \in \mathbb{R}^m$ \cite{Grcar10}.
-By compactness of the unit sphere, every injective linear map has a positive lower bound; hence, if $\mathbf{M}$ satisfies \eqref{SparkCondition}, then submatrices formed from $2k$ of its columns or less have strictly positive lower bounds.
-
-The lower bound of a matrix is generalized below in (\ref{Ldef}) by restricting it to the spans of certain submatrices\footnote{See \cite{vidal2005generalized} for an overview of the related ``union of subspaces" model.} associated with a hypergraph $\mathcal{H} \subseteq {[m] \choose k}$ of column indices.
-Let $\mathbf{M}_S$ denote the submatrix formed by the columns of a matrix $\mathbf{M}$ indexed by $S \subseteq [m]$ (setting $\mathbf{M}_\emptyset := \mathbf{0}$).
-In the sections that follow, we shall also let $\bm{\mathcal{M}}_S$ denote the column-span of a submatrix $\mathbf{M}_S$, and $\bm{\mathcal{M}}_\mathcal{G}$ to denote $\{\bm{\mathcal{M}}_S\}_{S \in \mathcal{G}}$.
-We define:  % Define $L_\mathcal{H}(\mathbf{M})$ as follows:
-%\begin{align*} 
-%L_\mathcal{H}(\mathbf{M}) := \min \left\{ \frac{ \|\mathbf{M}(\mathbf{x}_1-\mathbf{x}_2)\|_2 }{ \sqrt{2k} \|\mathbf{x}_1-\mathbf{x}_2\|_2} : \mathbf{x}_1, \mathbf{x}_2 \in \cup_{S \in \mathcal{H}} \bm{\mathcal{M}}_S \right\},
-%\end{align*} 
-%
-%where we write $L_{2k}$ in place of $L_\mathcal{H}$ when $\mathcal{H} = {[m] \choose k}$.
-Note that if $\mathcal{H}$ covers $[m]$, then $L_2 > L_\mathcal{H}$.\footnote{The reader should beware that $L_2 = L_{[m]}$, whereas $L = L_{\{[m]\}}$.
-For even $k$, the quantity $1 - \sqrt{k} L_k(\mathbf{M})$ is also known in the compressed sensing literature as the (asymmetric) lower restricted isometry constant \cite{Blanchard2011}.} Clearly, for any $\mathbf{M}$ satisfying \eqref{SparkCondition}, we have $L_{k'}(\mathbf{M}) > 0$ for  $k' \leq 2k$.
-%\begin{align*}
-%L_\mathcal{H}(\mathbf{M}) := \min \left\{ \frac{ \|\mathbf{M}_S\mathbf{x}\|_2 }{ \sqrt{k} \|\mathbf{x}\|_2} : S \in \mathcal{H} \right\},
-%\end{align*} 
-%\begin{align*}
-%L_\mathcal{H}(\mathbf{M}) := \max \left\{ \ falpha: \|\mathbf{M}_S\mathbf{x}\|_2 \geq \alpha \sqrt{k} \|\mathbf{x}\|_2 : S \in \mathcal{H}, \ \ \mathbf{x} \in \mathbb{R}^m \right\},
-%\end{align*} 
-\begin{align}\label{Ldef}
-L_\mathcal{H}(\mathbf{M}) := \min \left\{ \frac{\|\mathbf{M}_S\mathbf{x}\|_2}{ \sqrt{k} \|\mathbf{x}\|_2} : S \in \mathcal{H}, \ \mathbf{0} \neq \mathbf{x} \in \mathbb{R}^{|S|} \right\},
-\end{align} 
-%
-writing also $L_{k}$ in place of $L_\mathcal{H}$ when $\mathcal{H} = {[m] \choose k}$.\footnote{In compressed sensing literature, \mbox{$1 - \sqrt{k} L_k(\mathbf{M})$}  is the asymmetric lower restricted isometry constant for $\mathbf{M}$ with unit $\ell_2$-norm columns \cite{Blanchard2011}.}  As explained above, compactness implies that $L_{2k}(\mathbf{M}) > 0$ for all $\mathbf{M}$ satisfying \eqref{SparkCondition}.
-Clearly, $L_{\mathcal{H}'}(\mathbf{M}) \geq L_\mathcal{H}(\mathbf{M})$ whenever $\mathcal{H}' \subseteq \mathcal{H}$, and similarly any $k$-uniform $\mathcal{H}$ satisfying $\cup \mathcal{H} = [m]$ has $L_2 \geq L_{2\mathcal{H}} \geq L_{2k}$ (letting $L_{2k}$ := $L_m$ whenever $2k > m$).
-
-We are now in a position to state our main result, though for expository purposes we leave the quantity $C_1$ %(a function of $\mathbf{A}$, $\mathbf{x}_1, \ldots, \mathbf{x}_N$, and $\mathcal{H}$) 
-undefined until Sec.~\ref{DUT}. All results  below assume real matrices and vectors.
-
-%eps-tightness COUNTER-EXAMPLE:
-%Consider the alternate dictionary $B = \left(\mathbf{0}, \frac{1}{2}(\mathbf{e}_1 + \mathbf{e}_2), \mathbf{e}_3, \ldots, \mathbf{e}_{m} \right)$ and sparse codes $\mathbf{b}_i = \mathbf{e}_2$ for $i = 1, 2$ and $\mathbf{b}_i = \mathbf{e}_i$ for $i = 3, \ldots, m$.
-Then $|A\mathbf{a}_i - B\mathbf{b}_i| = 1/\sqrt{2}$ for $i = 1, 2$ (and $0$ otherwise).
-If there were permutation and invertible diagonal matrices $P \in \mathbb{R}^{m \times m}$ and $D \in \mathbb{R}^{m \times m}$ such that $|(A-BPD)\mathbf{e}_i| \leq C\varepsilon$ for all $i \in [m]$, then we would reach the contradiction $1 = |P^{-1}\mathbf{e}_1|_2 = |(A-BPD)P^{-1}\mathbf{e}_1|_2 \leq 1/\sqrt{2}$.
-
-\begin{theorem}\label{DeterministicUniquenessTheorem}
-%Fix integers $n, k, m$ and $\overline m$. 
-If an $n \times m$ matrix $\mathbf{A}$ satisfies $L_{2\mathcal{H}}(\mathbf{A}) > 0$ for some $r$-regular $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP, and $k$-sparse \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} include more than $(k-1){\overline m \choose k}$ vectors in general linear position\footnote{Recall that a set of vectors sharing support $S$ are in \emph{general linear position} when any $|S|$ of them are linearly independent.} supported in each $S \in \mathcal{H}$, then the following recovery guarantees hold for $C_1 > 0$ given by \eqref{Cdef1}.
-
-\textbf{Dictionary Recovery:} Fix $\varepsilon < L_{2}(\mathbf{A}) / C_1$.\footnote{Note that the condition $\varepsilon < L_2(\mathbf{A}) /C_1$ is necessary; otherwise, with \mbox{$\mathbf{A}$ = $\mathbf{I}$} (the identity matrix) and $\mathbf{x}_i = \mathbf{e}_i$, the matrix $\mathbf{B} = \left[\mathbf{0}, \frac{1}{2}(\mathbf{e}_1 + \mathbf{e}_2), \mathbf{e}_3, \ldots, \mathbf{e}_{m} \right]$ and sparse codes $\mathbf{\overline x}_i = \mathbf{e}_2$ for $i = 1, 2$ and $\mathbf{\overline x}_i = \mathbf{e}_i$ for $i \geq 3$ satisfy $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline x}_i \|_2 \leq \varepsilon$ but nonetheless violate \eqref{Cstable}.} If an $n \times \overline m$ matrix $\mathbf{B}$ has, for every $i \in [N]$, an associated $k$-sparse $\mathbf{\overline x}_i$ satisfying \mbox{$\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \varepsilon$}, then $\overline m \geq m$, and provided that $\overline m (r-1) < mr$, there is a permutation matrix $\mathbf{P}$ and an invertible diagonal matrix $\mathbf{D}$ such that:
-\begin{align}\label{Cstable}
-\|\mathbf{A}_j- (\mathbf{BPD})_j\|_2 \leq C_1 \varepsilon, \ \ \text{for all } j \in J,
-\end{align}
-%
-for some $J \subseteq [m]$ of size \mbox{$m - (r-1)(\overline m - m)$}. 
-% $\overline m - r(\overline m - m)$
-
-\textbf{Code Recovery:} If, moreover, $\mathbf{A}_J$ satisfies \eqref{SparkCondition} and $\varepsilon < L_{2k}(\mathbf{A}_J) / C_1$, then $(\mathbf{BP})_J$ also satisfies \eqref{SparkCondition} with $L_{2k}(\mathbf{BP}_J) \geq (L_{2k}(\mathbf{A}_J) - C_1 \varepsilon) / \|\mathbf{D}_J\|_1$, and for all $i \in [N]$:
-\begin{align}\label{b-PDa}
-%\|\mathbf{x}^J_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}^{\overline J}_i\|_1 &\leq  \left( \frac{ 1+C_1 \|\mathbf{x}^{J}_i\|_1 }{ L_{2k}(\mathbf{A}) -  C_1\varepsilon } \right) \varepsilon \ \  \text{for $i \in [N]$}.
-\|(\mathbf{x}_i)_J - (\mathbf{D}^{-1}\mathbf{P}^{\top} \mathbf{\overline x}_i)_J\|_1 &\leq  \left( \frac{ 1+C_1 \|(\mathbf{x}_i)_J\|_1 }{ L_{2k}(\mathbf{A}_J) -  C_1\varepsilon } \right) \varepsilon,
-\end{align}
-%
-where subscript $(\cdot)_J$ here represents the subvector formed from restricting to coordinates indexed by $J$.
-\end{theorem}
-
-%We delay defining the explicit constant $C_1$ until Section \ref{DUT} (\eqref{Cdef1}).
-%To be clear, the implication of Thm.~\ref{DeterministicUniquenessTheorem} is that $Y = \{\mathbf{Ax}_1, \ldots, \mathbf{Ax}_N\}$ has a stable $k$-sparse representation in $\mathbb{R}^m$, with \eqref{def1} guaranteed provided $\varepsilon$ in Def.~\ref{maindef} does not exceed:
-In words, Thm.~\ref{DeterministicUniquenessTheorem} says that the smaller the regularity $r$ of the original support hypergraph $\mathcal{H}$ or the difference $\overline m - m$ between the assumed and actual number of elements in the latent dictionary, the more columns and coefficients of the original dictionary $\mathbf{A}$ and sparse codes $\mathbf{x}_i$ are guaranteed to be contained (up to noise) in the appropriately labelled and scaled recovered dictionary $\mathbf{B}$ and codes $\mathbf{\overline x}_i$, respectively.
-
-In the important special case when $\overline m = m$, the theorem directly implies that  $Y = \{\mathbf{Ax}_1, \ldots, \mathbf{Ax}_N\}$ has a stable $k$-sparse representation in $\mathbb{R}^m$, with inequalities \eqref{def1} guaranteed in Def.~\ref{maindef} for the following worst-case error $\varepsilon$:
-\begin{align}\label{epsdel}
-\varepsilon(\delta_1, \delta_2) := \min \left\{ \frac{\delta_1}{ C_1 }, \frac{ \delta_2 L_{2k}(\mathbf{A})}{ 1 + C_1 \left( \delta_2 + \max_{i \in [N]} \|\mathbf{x}_i\|_1  \right) } \right\}.
-\end{align}
-
-Since sparse codes in general linear position are straightforward to produce with a ``Vandermonde''  construction (i.e., by choosing columns of the matrix $[\gamma_{i}^j]_{i,j=1}^{k,N}$, for distinct nonzero $\gamma_i$), we have the following direct consequence of Thm.~\ref{DeterministicUniquenessTheorem}.
-
-\begin{corollary}\label{DeterministicUniquenessCorollary}
-Given any regular hypergraph $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP, there are $N =  |\mathcal{H}| \left[ (k-1){m \choose k} + 1  \right]$ vectors \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} such that every matrix $\mathbf{A}$ satisfying spark condition \eqref{SparkCondition} generates $Y = \{\mathbf{A}\mathbf{x}_1, \ldots, \mathbf{A}\mathbf{x}_N\}$ with a stable $k$-sparse representation in $\mathbb{R}^m$ for $\varepsilon(\delta_1,\delta_2)$ given by \eqref{epsdel}.
-\end{corollary}
-
-% prev
-%\begin{corollary}\label{DeterministicUniquenessCorollary}
-%Given any regular hypergraph $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP, there are $N =  |\mathcal{H}| \left[ (k-1){m \choose k} + 1  \right]$ vectors \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} such that every matrix $\mathbf{A}$ with $L_{2\mathcal{H}}(\mathbf{A}) > 0$ generates a dataset $Y = \{\mathbf{A}\mathbf{x}_1, \ldots, \mathbf{A}\mathbf{x}_N\}$ with a stable $k$-sparse representation in $\mathbb{R}^m$ for $\varepsilon(\delta_1,\delta_2)$ as in \eqref{epsdel}.
-%\end{corollary}
-
-%We claim that the assumptions of Thm.~\ref{DeterministicUniquenessTheorem} are easily met with deterministic constructions.
-In particular, sparse codes in general linear position are straightforward to produce using a ``Vandermonde'' matrix construction (i.e.
-use the columns of the matrix $[\gamma_{i}^j]_{i,j=1}^{k,N}$, for distinct nonzero $\gamma_i$).
-%
-
-% (Prob.~\ref{InverseProblem}).
-%=======
-%An immediate practical implication of this result is that there exists a practical procedure to affirm if one's proposed solution $(\mathbf{B}, \mathbf{\overline x}_1, \ldots, \mathbf{x}_N)$ to Prob.~\ref{InverseProblem} is indeed unique (up to noise and inherent ambiguities): simply check that $\mathbf{B}$ and the $\mathbf{\overline x}_i$ satisfy the assumptions on $\mathbf{A}$ and the $\mathbf{x}_i$ in Thm.~\ref{DeterministicUniquenessTheorem}.
-%
-%%In fact, a more general result (stated clearly in the next section) can be gleaned from our method of proving Thm.~\ref{DeterministicUniquenessTheorem}.
-Briefly, in cases where $\mathbf{B}$ has $\overline m \neq m$ columns, or $\mathcal{H}$ is not regular or only partially satisfying the SIP, a relation between $\overline m$ and the degree sequence of nodes in $\mathcal{H}$ gives indices $J \subseteq [m]$ defining a submatrix $\mathbf{A}_J$ and subvectors $\mathbf{x}_i^J$ that are recoverable in the sense of \eqref{Cstable} and \eqref{b-PDa}.
-For example, if $\mathcal{H}$ is $\ell$-regular with the SIP but $m \leq \overline m < m\ell/(\ell - 1)$ then we have nonzero $|J| = \overline m - \ell(\overline m - m)$.
-The implication here is that the smaller the difference $\overline m - m$, the more columns and code entries of the original $n \times m$ dictionary $\mathbf{A}$ and codes $\mathbf{x}_i$ contained (up to noise) in the appropriately scaled $n \times \overline m$ dictionary $\mathbf{B}$ and codes $\mathbf{\overline x}_i$.
-When $\overline m = m$, we recover Thm.~\ref{DeterministicUniquenessTheorem}.
-%
-%%In fact, even if $\mathcal{H}$ is not regular or only partially satisfies the SIP, a relation between $\overline m$ and the degree sequence of nodes in $\mathcal{H}$ may give the indices $J \subseteq [m]$.
-For sake of brevity, we delay to the next section a clear statement of this more general result.
-%
-%Regarding the assumptions of Thm.~\ref{DeterministicUniquenessTheorem}, it so happens that sparse codes $\mathbf{x}_i$ in general linear position are straightforward to produce with a ``Vandermonde'' matrix construction \cite{Hillar15}, leading to the following.
-%>>>>>>> d1407a275dc391dabad7bb62d3e659f9a4ac4624
-
-% Needs to be L_{2k}(A) > 0 to guarantee sparse vector recovery
-
-%We also have the following refinement of a result in \cite{Hillar15}:
-%\begin{corollary}
-%Those square matrices $\mathbf{A}$ that satisfy \mbox{$L_{2\mathcal{H}}(\mathbf{A}) > 0$} for some regular $k$-uniform hypergraph $\mathcal{H}$ with the SIP and have the property that $\mathbf{Ax}$ is $k$-sparse for all $k$-sparse $\mathbf{x}$ with support in $\mathcal{H}$ are the matrices $\mathbf{PD}$, where $\mathbf{P}$ and $\mathbf{D}$ run over permutation and invertible diagonal matrices, respectively.
-%\end{corollary}
-
-One can easily verify that for every $k < m$ there are regular $k$-uniform hypergraphs $\mathcal{H}$ with the SIP besides the obvious $\mathcal{H} = {[m] \choose k}$.
-For instance, take $\mathcal{H}$ to be the $k$-regular set of consecutive intervals of length $k$ in some cyclic order on $[m]$.
-In this case, a direct consequence of Cor.~\ref{DeterministicUniquenessCorollary} is rigorous verification of the lower bound \mbox{$N = m(k-1){m \choose k} + m$} for sufficient sample size from the introduction.
-Special cases allow for even smaller hypergraphs.
-For example, if $k = \sqrt{m}$, then a 2-regular $k$-uniform hypergraph with the SIP can be constructed as the $2k$ rows and columns formed by arranging the elements of $[m]$ into a square grid.
-
-%\cite{li2004analysis, Georgiev05, Aharon06, Hillar15}
-We should stress here that framing the problem in terms of hypergraphs has allowed us to show, unlike in previous research on the subject, that the matrix $\mathbf{A}$ need not necessarily satisfy \eqref{SparkCondition} to be recoverable from data.
-As an example, let $\mathbf{A} = [ \mathbf{e}_1, \ldots, \mathbf{e}_5, \mathbf{v}]$ with $\mathbf{v} = \mathbf{e}_1 + \mathbf{e}_3 + \mathbf{e}_5$ and take $\mathcal{H}$ to be all consecutive pairs of indices $1, \ldots ,6$ arranged in cyclic order.
-Then for $k=2$, the matrix $\mathbf{A}$ fails to satisfy \eqref{SparkCondition} while still obeying the assumptions of Thm.~\ref{DeterministicUniquenessTheorem} for dictionary recovery.%, hence guaranteeing \eqref{Cstable} .
-%(since $\{ \mathbf{A}_1, \mathbf{A}_3, \mathbf{A}_5, \mathbf{A}_6\}$ is not a linearly independent set).
-%This weakening allows for a practical (polynomial) amount of data to still guarantee a stable dictionary in the case where the set of sparse supports for the $\mathbf{\overline x}_i$ is known to have a size that grows polynomially in $m$ and $k$.
-
-A practical implication of Thm.~\ref{DeterministicUniquenessTheorem} is the following: there is an effective procedure sufficient to affirm if a proposed solution to Prob.~\ref{InverseProblem} is indeed unique (up to noise and inherent ambiguities).
-One need simply check that the matrix and codes satisfy the (computable) assumptions of Thm.~\ref{DeterministicUniquenessTheorem} on $\mathbf{A}$ and the $\mathbf{x}_i$.
-In general, however, there is no known efficient procedure.
-We defer a brief discussion on this point to the next section.
-%Another practical implication of Thm.\ref{DeterministicUniquenessTheorem} is the following: there is an effective procedure sufficient to affirm if a proposed solution $(\mathbf{B}, \mathbf{\overline x}_1, \ldots, \mathbf{x}_N)$ to Prob.~\ref{InverseProblem} is indeed unique (up to noise and inherent ambiguities).
-One simply checks that $\mathbf{B}$ and the $\mathbf{\overline x}_i$ satisfy the respective assumptions of Thm.~\ref{DeterministicUniquenessTheorem}.
-%. on $\mathbf{A}$ and the $\mathbf{x}_i$, respectively.
-
-%In fact, a more general result (stated clearly in the next section) can be gleaned from our method of proving Thm.~\ref{DeterministicUniquenessTheorem}.
-Briefly, in cases where $\mathbf{B}$ has $\overline m \neq m$ columns, or $\mathcal{H}$ is not regular or only partially satisfying the SIP, a relation between $\overline m$ and the degree sequence of nodes in $\mathcal{H}$ gives indices $J \subseteq [m]$ defining a submatrix $\mathbf{A}_J$ and subvectors $\mathbf{x}_i^J$ that are recoverable in the sense of \eqref{Cstable} and \eqref{b-PDa}.
-For example, if $\mathcal{H}$ is $\ell$-regular with the SIP but $m \leq \overline m < m\ell/(\ell - 1)$ then we have nonzero $|J| = \overline m - \ell(\overline m - m)$.
-The implication here is that the smaller the difference $\overline m - m$, the more columns and code entries of the original $n \times m$ dictionary $\mathbf{A}$ and codes $\mathbf{x}_i$ contained (up to noise) in the appropriately scaled $n \times \overline m$ dictionary $\mathbf{B}$ and codes $\mathbf{\overline x}_i$.
-When $\overline m = m$, we recover Thm.~\ref{DeterministicUniquenessTheorem}.
-
-%In fact, even if $\mathcal{H}$ is not regular or only partially satisfies the SIP, a relation between $\overline m$ and the degree sequence of nodes in $\mathcal{H}$ may give the indices $J \subseteq [m]$.
-For sake of brevity, we delay to the next section a clear statement of this more general result.
-
-%=======
-%One can also verify that for every $k < m$, there is a regular $k$-uniform hypergraph that satisfies the SIP; for instance, take $\mathcal{H}$ to be the consecutive intervals of length $k$ in some cyclic order on $[m]$, for which Cor.~\ref{DeterministicUniquenessCorollary} implies the lower bound for sample size $N$ from the introduction.
-In many cases, however, the SIP is achievable with far fewer supports; for example, when $k = \sqrt{m}$, take $\mathcal{H}$ to be the $2k$ rows and columns formed by arranging $[m]$ in a square grid.
-%>>>>>>> d1407a275dc391dabad7bb62d3e659f9a4ac4624
-
-%As mentioned above, there exist $k$-uniform regular hypergraphs $\mathcal{H}$ with the SIP having cardinality $|\mathcal{H}| = m$,
-
-A less direct consequence of Thm.~\ref{DeterministicUniquenessTheorem} is the following uniqueness and stability guarantee for solutions to Prob.~\ref{SLCopt}.
-%, the usual optimization problem of interest for those applying dictionary learning to their data.
-
-\begin{theorem}\label{SLCopt}
-Fix a matrix $\mathbf{A}$ and vectors $\mathbf{x}_i$ satisfying the assumptions of Thm.~\ref{DeterministicUniquenessTheorem}, only now with over \mbox{$(k-1)\left[ {\overline m \choose k} + |\mathcal{H}|k{\overline m \choose k-1}\right]$} vectors supported in general linear position in each $S \in \mathcal{H}$.
-Every solution to Prob.~\ref{OptimizationProblem} (with $\eta = \varepsilon/2$) satisfies recovery guarantees \eqref{Cstable} and \eqref{b-PDa} when the corresponding bounds on $\eta$ are met.
-\end{theorem}
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=.24 \linewidth]{figs/basis.png}
-% \includegraphics[width=.25 \linewidth]{figs/Ahat_FastICA_M640_K8_noise0_2042}
-%\includegraphics[width=.24 \linewidth]{figs/Ahat_FastICA_M640_K8_noise0_4083.png}
-\includegraphics[width=.24 \linewidth]{figs/Ahat_FastICA_M640_K8_noise1_0205.png}
-\includegraphics[width=.24 \linewidth]{figs/Ahat_FastICA_M640_K8_noise2_0409.png}
-\includegraphics[width=.24 \linewidth]{figs/Ahat_FastICA_M640_K8_noise5_1021.png}
-\caption{\textbf{Learning a dictionary from increasingly noisy data}.
-The (unraveled) basis elements of the $8 \times 8$ discrete cosine transform (DCT) form the 64 columns of the left-most matrix above.
-Three increasingly imprecise dictionaries (columns reordered to best match original) are recovered by FastICA \cite{hyvarinen2000independent} trained on data generated from $8$-sparse linear combinations of DCT elements corrupted with additive noise (increasing from left to right).}
-\vspace{-.6 cm}
-\label{noisyrecovery}
-\end{center}
-\end{figure}
-
-Another extension of Thm.~\ref{DeterministicUniquenessTheorem} can be derived from the following algebraic characterization of the spark condition.
-Letting $\mathbf{A}$ be the $n \times m$ matrix of $nm$ indeterminates $A_{ij}$, the reader may work out why substituting real numbers for the $A_{ij}$ yields a matrix satisfying \eqref{SparkCondition} if and only if the following polynomial evaluates to a nonzero number:
-\begin{align*}
-f(\mathbf{A}) := \prod_{S \in {[m] \choose 2k}} \sum_{S' \in {[n] \choose 2k}} (\det \mathbf{A}_{S',S})^2,
-\end{align*}
-%
-where for any $S' \in {[n] \choose 2k}$ and $S \in {[m] \choose 2k}$, the symbol $\mathbf{A}_{S',S}$ denotes the submatrix of entries $A_{ij}$ with $(i,j) \in S' \times S$.\footnote{The large number of terms in this product is likely necessary given that deciding whether or not a matrix satisfies the spark condition is NP-hard \cite{tillmann2014computational}.}
-
-Since $f$ is analytic, having a single substitution of a real matrix $\mathbf{A}$ satisfying $f(\mathbf{A}) \neq 0$ implies that the zeroes of $f$ form a set of (Borel) measure zero.
-Such a matrix is easily constructed by adding rows of zeroes to a $\min(2k,m) \times m$ Vandermonde matrix as mentioned previously, so that every sum in the product defining $f$ above is strictly positive.
-Thus, almost every $n \times m$ matrix with $n \geq \min(2k,m)$ satisfies \eqref{SparkCondition}.
-
-%Another extension of Thm.~\ref{DeterministicUniquenessTheorem} arises from the following analytic characterization of the spark condition.
-Let $\mathbf{A}$  be the $n \times m$ matrix of $nm$ indeterminates $A_{ij}$.
-When real numbers are substituted for $A_{ij}$, the resulting matrix satisfies \eqref{SparkCondition} if and only if the following polynomial is nonzero:
-%\begin{align*}
-%f(\mathbf{A}) := \prod_{S \in {[m] \choose k}} \sum_{S' \in {[n] \choose k}} (\det \mathbf{A}_{S',S})^2,
-%\end{align*}
-%
-%where for any $S' \in {[n] \choose k}$ and $S \in {[m] \choose k}$, the symbol $\mathbf{A}_{S',S}$ denotes the submatrix of entries $A_{ij}$ with $(i,j) \in S' \times S$.
-We note that the large number of terms in this product is likely necessary due to the NP-hardness of deciding whether a given matrix $\mathbf{A}$ satisfies the spark condition \cite{tillmann2014computational}.
-
-%Since $f$ is analytic, having a single substitution of a real matrix $\mathbf{A}$ with $f(\mathbf{A}) \neq 0$ necessarily implies that the zeroes of $f$ form a set of measure zero.
-Fortunately, such a matrix $\mathbf{A}$ is easily constructed by adding rows of zeroes to any $\min(2k,m) \times m$ Vandermonde matrix as described above (so that each term in the product above for $f$ is nonzero).
-Hence, almost every $n \times m$ matrix with $n \geq \min(2k,m)$ satisfies \eqref{SparkCondition}.
-
-We claim that a similar phenomenon applies to datasets of vectors with a stable sparse representation.
-Briefly, following the same procedure as in \cite[Sec.~IV]{Hillar15}, for $k < m$ and $n \geq \min(2k, m)$, we may consider the ``symbolic'' dataset $Y = \{\mathbf{A}\mathbf{x}_1,\ldots,\mathbf{A} \mathbf{x}_N\}$ generated by an indeterminate $n \times m$ matrix $\mathbf{A}$ and $m$-dimensional $k$-sparse vectors $\mathbf{x}_1, \ldots, \mathbf{x}_N$ indeterminate within their supports, which form a regular hypergraph $\mathcal{H} \subseteq {[m] \choose k}$ satisfying the SIP.
-Restricting \mbox{$(k-1){m \choose k} + 1$} indeterminate $\mathbf{x}_i$ to each support in $\mathcal{H}$, and letting $\textbf{M}$ be the $n \times N$ matrix with columns $\mathbf{A}\mathbf{x}_i$, it can be checked that when $f(\mathbf{M}) \neq 0$ for a substitution of real numbers for the indeterminates, all of the assumptions on $\mathbf{A}$ and the $\mathbf{x}_i$ in Thm.~\ref{DeterministicUniquenessTheorem} are satisfied.
-We therefore have the following.
-% ; in particular, $\mathbf{A}$ satisfies \eqref{SparkCondition}
-
-\begin{theorem}\label{robustPolythm}
-%Let $\mathbf{A}$ and $\mathbf{x}_1, \ldots, \mathbf{x}_N$ be an indeterminate $n \times m$ matrix and sequence of $m$-dimensional vectors, respectively. 
-There is a polynomial in the entries of $\mathbf{A}$ and the $\mathbf{x}_i$ that evaluates to a nonzero number only when $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$.
-In particular, almost all substitutions impart to $Y$ this property.
-\end{theorem}
-
-%To extend this observation to arbitrary probability distributions, note that if a set of measure spaces $\{(X_{\ell}, \nu_{\ell})\}_{\ell=1}^p$ has measures $\nu_{\ell}$ absolutely continuous with respect to the standard Borel measure on $\mathbb{R}$ for all $\ell \in [p]$, then the product measure $\prod_{\ell=1}^p \nu_{\ell}$ is also absolutely continuous with respect to the standard Borel product measure on $\mathbb{R}^p$ (e.g., see \cite{folland2013real}).
-This fact combined with Thm.~\ref{robustPolythm} implies the following.
-To extend this observation to arbitrary probability distributions, note that if a set of $p$ measure spaces has all measures absolutely continuous with respect to the standard Borel measure on $\mathbb{R}$, then the product measure is also absolutely continuous with respect to the standard Borel product measure on $\mathbb{R}^p$ (e.g., see \cite{folland2013real}).
-This fact combined with Thm.~\ref{robustPolythm} implies the following.\footnote{We refer the reader to \cite{Hillar15} for a more detailed explanation of these arguments.}
-
-\begin{corollary}\label{ProbabilisticCor}
-If the indeterminate entries of $\mathbf{A}$ and the $\mathbf{x}_i$ are drawn independently from probability distributions absolutely continuous with respect to the standard Borel measure, then $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$ with probability one.
-\end{corollary}
-
-Thus, drawing the dictionary and supported sparse coefficients from any continuous probability distribution almost always generates data with a stable sparse representation.
-
-%\cite{rehnsommer2007, rozell2007neurally, ganguli2012compressed, hu2014hebbian}
-
-We close this section with some comments on the optimality of our results.
-The linear scaling for $\varepsilon$ in \eqref{epsdel} is essentially optimal (e.g., see \cite{arias2013fundamental}), but a basic open problem remains: how many samples are necessary to determine the sparse coding model?
-Our results demonstrate that sparse codes $\mathbf{x}_i$ drawn from only a polynomial number of $k$-dimensional subspaces permit stable identification of the generating dictionary $\mathbf{A}$. 
-This lends some legitimacy to the use of the model in practice, where data in general are unlikely (if ever) to exhibit the exponentially many possible $k$-wise combinations of dictionary elements required by (to our knowledge) all previously published results.
-
-Consequently, if $k$ is held fixed or if the size of the support set of reconstructing codes is polynomial in $\overline m$ and $k$, then a practical (polynomial) amount of data suffices to identify the dictionary.\footnote{In the latter case, a reexamination of the pigeonholing argument in the proof of Thm.~\ref{DeterministicUniquenessTheorem} requires a polynomial number of samples distributed over a polynomial number of supports.} Reasons to be skeptical that this holds in general, however, can be found in \cite{tillmann2014computational, Tillmann15}.
-Even so, in the next section we discuss how probabilistic guarantees can in fact be made for any number of available samples.
-
-\section{Proofs}\label{DUT} % of Theorems~\ref{DeterministicUniquenessTheorem} and ~\ref{SLCopt}}\label{DUT}
-
-%%%%%%%%%%%%%%
-% need to cut maybe: 
-%As mentioned in the previous section, Thm.~\ref{DeterministicUniquenessTheorem} is a particular case of a more general result that forgoes the assumption that $\mathcal{H} \subseteq {[m] \choose k}$ is regular and satisfies the SIP.
-If instead we require only that the stars $\cap \sigma(i)$ intersect at singletons for all $i \leq q$ (assuming that the nodes of $\mathcal{H}$ are labeled in some order of non-increasing degree), we have that $\overline m \geq k|\mathcal{H}| / \deg(1)$ and, provided $\overline m < k|\mathcal{H}| / (\deg(1) - 1)$, the nonempty submatrix $J$ is of size equal to the largest number $p$ satisfying:
-%\begin{align}\label{pcond}
-%\sum_{i=\ell}^{m} \deg(i) > (\overline m + 1 - \ell) (\deg(\ell) - 1) \ \ \text{for all } \ell \leq p \leq q.
-%\end{align}
-%Specifically, $J$ contains all nodes of degree exceeding $\deg(p)$ and some subset of those with degreee equal to $\deg(p)$.
-For the benefit of the reader, we do not prove explicitly this more general result below; it can be discerned from how exactly Lemma \ref{NonEmptyLemma} is incorporated into the proof of Lem.~\ref{MainLemma}.
-%%%%%%%%%%%%%%%%
-
-%As mentioned in the previous section, Thm.~\ref{DeterministicUniquenessTheorem} is a particular case of a more general result, which requires a looser set of constraints on the hypergraph $\mathcal{H}$ and which applies to $n \times \overline m$ matrices $\mathbf{B}$ (and $\overline m$-dimensional codes $\mathbf{\overline x}_i$) with $\overline m \neq m$:
-
-%Fix $\overline m$ and suppose the assumptions of Thm.~\ref{DeterministicUniquenessTheorem} hold, only now with the constraints on $\mathcal{H} \subseteq {[m] \choose k}$ being just that $|\cap H(i)| = 1$ for all $i \leq q$ (assuming w.l.o.g.
-that the nodes of $\mathcal{H}$ are labeled in some order of non-increasing degree), and with more than $(k-1){\overline m \choose k}$ vectors $\mathbf{x}_i$ supported in g.l.p.
-on each $S \in \mathcal{H}$.
-Then we must have $\overline m \geq k|\mathcal{H}| / \deg(1)$ and, provided $\overline m < k|\mathcal{H}| / (\deg(1) - 1)$, the guarantee \eqref{Cstable} holds for a submatrix $\mathbf{A}_J$, where $J \subseteq[m]$ is nonempty and of a size equal to the largest number $p$ satisfying:
-%\begin{align}\label{pcond}
-%\sum_{i=\ell}^{m} \deg(i) > (\overline m + 1 - \ell) (\deg(\ell) - 1) \ \ \text{for all } \ell \leq p \leq q.
-%\end{align}
-%Specifically, $J$ consists of the union of the set of all nodes of degree exceeding $\deg(p)$ and some subset of those nodes with degrees equal to $\deg(p)$.
-
-%For the benefit of the reader, we prove below the case where we forgo only the constraint that $\overline m = m$.
-This yields the implication $\overline m \geq m$ and \eqref{pcond} reduces to $|J| = \overline m - r(\overline m - m)$.
-The extension to the general result above can be seen by examining how exactly Lemma \ref{NonEmptyLemma} is incorporated into the overall proof.
-
-% ======== b - PDa =========
-
-% WITH EXPLICIT J SUBSCRIPT
-%We begin our proof of Thm.~\ref{DeterministicUniquenessTheorem} by showing how dictionary recovery \eqref{Cstable} already implies sparse code recovery \eqref{b-PDa} when $\mathbf{A}_J$ satisfies \eqref{SparkCondition} and \mbox{$\varepsilon < L_{2k}(\mathbf{A}_J) / C_1$}.
-%, assuming that $\overline m = m$ without loss of generality.
-%Consider any $2k$-sparse $\mathbf{x} \in \mathbb{R}^m$ and note that $\|\mathbf{x}\|_1 \leq \sqrt{2k}  \|\mathbf{x}\|_2$. By definition of $L_{2k}$ in \eqref{Ldef}, we have:
-%\begin{align}\label{stuff}
-%\|\mathbf{x}_J - &( \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x} )_J\|_1 \nonumber
-%\leq \frac{\|(\mathbf{BPD})_J(\mathbf{x}_J - (\mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x})_J)\|_2}{L_{2k}((\mathbf{BPD})_J)} \\ \nonumber
-%&\leq \frac{\|( (\mathbf{BPD})_J - \mathbf{A}_J) \mathbf{x}_J\|_2 + \|\mathbf{A}_J\mathbf{x}_J - \mathbf{B}_J\mathbf{\overline x}_J\|_2}{L_{2k}((\mathbf{BPD})_J)} \\
-%&\leq \frac{C_1\varepsilon \|\mathbf{x}_J\|_1 + \varepsilon}{L_{2k}((\mathbf{BPD})_J)},
-%\end{align}
-%where the term $C_1\varepsilon \|\mathbf{x}_J\|_1$ in the numerator above is a consequence of the triangle inequality applied to \eqref{Cstable}.
-
-%It remains for us to bound the denominator.  By the reverse triangle inequality:
-%\begin{align*}
-%\|(\mathbf{BPD})_J\mathbf{x}_J\|_2 
-%&\geq | \|\mathbf{A}_J\mathbf{x}_J\|_2 - \|(\mathbf{A}_J - (\mathbf{BPD})_J)\mathbf{x}_J\|_2 | \\
-%&\geq \sqrt{2k} (L_{2k}(\mathbf{A}_J) -  C_1\varepsilon) \|\mathbf{x}_J\|_2,
-%\end{align*}
-%
-%wherein removal of the absolute value is justified since $C_1\varepsilon < L_{2k}(\mathbf{A}_J)$.
-We therefore have that $L_{2k}((\mathbf{BPD})_J) \geq L_{2k}(\mathbf{A}_J) - C_1\varepsilon  > 0$, and \eqref{b-PDa} then follows from \eqref{stuff}.
-
-% WITHOUT J SUBSCRIPT
-We begin our proof of Thm.~\ref{DeterministicUniquenessTheorem} by showing how dictionary recovery \eqref{Cstable} already implies sparse code recovery \eqref{b-PDa} when $\mathbf{A}$ satisfies \eqref{SparkCondition} and \mbox{$\varepsilon < L_{2k}(\mathbf{A}) / C_1$}.
-We temporarily assume (without loss of generality) that $\overline m = m$, so as to omit an otherwise requisite subscript $(\cdot)_J$ around certain matrices and vectors.
-By definition of $L_{2k}$ in \eqref{Ldef}, and noting that $\sqrt{k} \|\mathbf{v}\|_2 \geq \|\mathbf{v}\|_1$ for $k$-sparse $\mathbf{v}$, we have for all $i \in [N[$:
-\begin{align}\label{stuff}
-\|\mathbf{x}_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_i \|_1 \nonumber
-&\leq \frac{\|\mathbf{BPD}(\mathbf{x}_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_i)\|_2}{L_{2k}(\mathbf{BPD})} \\ \nonumber
-&\leq \frac{\|( \mathbf{BPD} - \mathbf{A}) \mathbf{x}_i\|_2 + \|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline x}_i\|_2}{L_{2k}(\mathbf{BPD})} \\
-&\leq \frac{C_1\varepsilon \|\mathbf{x}_i\|_1 + \varepsilon}{L_{2k}(\mathbf{BPD})},
-\end{align}
-%\begin{align}\label{stuff}
-%\frac{ \|\mathbf{x} - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x} \|_1 } { \|\mathbf{D}^{-1}\|_1 }  \
-%&\leq \|\mathbf{Dx} - \mathbf{P}^{\top}\mathbf{\overline x} \|_1 \\ \nonumber
-%&\leq \frac{\|\mathbf{BP}(\mathbf{D}\mathbf{x} - \mathbf{P}^{\top}\mathbf{\overline x})\|_2}{L_{2k}(\mathbf{BP})} \\ \nonumber
-%&\leq \frac{\|( \mathbf{BPD} - \mathbf{A}) \mathbf{x}\|_2 + \|\mathbf{A}\mathbf{x} - \mathbf{B}\mathbf{\overline x}\|_2}{L_{2k}(\mathbf{BP})} \\
-%&\leq \frac{C_1\varepsilon \|\mathbf{x}\|_1 + \varepsilon}{L_{2k}(\mathbf{BP})},
-%\end{align}
-where the first term in the numerator above follows from the triangle inequality and \eqref{Cstable}.
-
-It remains for us to bound the denominator. For any $2k$-sparse $\mathbf{x}$, we have by the triangle inequality:
-\begin{align*}
-\|\mathbf{BPD}\mathbf{x}\|_2 
-&\geq \|\mathbf{A}\mathbf{x}\|_2 - \|(\mathbf{A} - \mathbf{BPD})\mathbf{x}\|_2 \\
-&\geq \sqrt{2k} (L_{2k}(\mathbf{A}) -  C_1\varepsilon) \|\mathbf{x}\|_2,
-\end{align*}
-
-%\begin{align*}
-%\|\mathbf{BP}\mathbf{x}\|_2 
-%&\geq \|\mathbf{A}\mathbf{D}^{-1}\mathbf{x}\|_2 - \|(\mathbf{A} - \mathbf{BPD})\mathbf{D}^{-1}\mathbf{x}\|_2 \\
-%&\geq \sqrt{2k} (L_{2k}(\mathbf{A}) -  C_1\varepsilon) \|\mathbf{D}^{-1}\mathbf{x}\|_2, \\ 
-%&\geq \sqrt{2k} (L_{2k}(\mathbf{A}) -  C_1\varepsilon) \|\mathbf{D}^{-1}\|_{?} \| \mathbf{x}\|_2,
-%\end{align*}
-%
-We therefore have that $L_{2k}(\mathbf{BPD}) \geq L_{2k}(\mathbf{A}) - C_1\varepsilon  > 0$, and \eqref{b-PDa} then follows from \eqref{stuff}.
-The reader may also verify that $L_{2k}(\mathbf{BP}) \geq L_{2k}(\mathbf{BPD}) / \|\mathbf{D}\|_1$.
-
-The heart of the matter is therefore \eqref{Cstable}, which we now establish beginning with the important special case of $k = 1$.
-
-\begin{proof}[Proof of Thm.~\ref{DeterministicUniquenessCorollary} for $k=1$]
-Since the only 1-uniform hypergraph with the SIP is $[m]$, which is obviously regular, we require only $\mathbf{x}_i = c_i \mathbf{e}_i$ for $i \in [m]$, with $c_i \neq 0$ to guarantee  linear independence.
-While we have yet to define $C_1$ generally, in this case we may set $C_1 = 1/ \min_{\ell \in [m]} |c_{\ell}|$ so that $\varepsilon < L_2(\mathbf{A})  \min_{\ell \in [m]} |c_{\ell}|$.
-
-Fix $\mathbf{A} \in \mathbb{R}^{n \times m}$ satisfying $L_2(\mathbf{A}) > 0$, since here we have $2\mathcal{H} = {[m] \choose 2}$, and suppose some $\mathbf{B}$ and $1$-sparse $\mathbf{\overline x}_i \in \mathbb{R}^{\overline m}$ have  $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \varepsilon < L_2(\mathbf{A}) / C_1$ for all $i$.
-Then, there exist $\overline{c}_1, \ldots, \overline{c}_m \in \mathbb{R}$ and a map $\pi: [m] \to [\overline m]$ such that:
-\begin{align}\label{1D}
-\|c_i\mathbf{A}_i - \overline{c}_i\mathbf{B}_{\pi(i)}\|_2 \leq \varepsilon,\ \ \text{for $i \in [m]$}.
-\end{align} 
-Note that $\overline{c}_i \neq 0$, since otherwise we would reach the following contradiction: $\|\mathbf{A}_i \|_2 \leq C_1 |c_i| \|\mathbf{A}_i \|_2  \leq C_1\varepsilon < L_2(\mathbf{A}) \leq L_1(\mathbf{A}) = \min_{i \in [m]} \|\mathbf{A}_{i}\|_2$.
-%implies by \eqref{delrho} the contradiction $|c_i| < \min_{\ell \in [m]} | c_\ell |$.
-
-We now show that $\pi$ is injective (in particular, a permutation if $\overline m = m$).
-Suppose that $\pi(i) = \pi(j) = \ell$ for some $i \neq j$ and $\ell$.
-Then, $\|c_{i}\mathbf{A}_{i} - \overline{c}_{i} \mathbf{B}_{\ell}\|_2  \leq \varepsilon$ and $\|c_{j}\mathbf{A}_{j} - \overline{c}_{j}\mathbf{B}_{\ell}\|_2 \leq \varepsilon$, and we have: %Scaling and summing these inequalities by $|\overline{c}_{i}|$ and $|\overline{c}_{j}|$, respectively, and applying the triangle inequality to annihilate the terms in $\mathbf{B}_\ell$, we obtain:
-\begin{align*}
-(|\overline{c}_{i}| + |\overline{c}_{j}|) \varepsilon
-&\geq |\overline{c}_{i}| \|c_{j}\mathbf{A}_{j} - \overline{c}_{j}\mathbf{B}_{\ell}\|_2  + |\overline{c}_{j}| \|c_{i}\mathbf{A}_{i} - \overline{c}_{i} \mathbf{B}_{\ell}\|_2 \nonumber \\
-&\geq \|\mathbf{A}(\overline{c}_{i}c_{j} \mathbf{e}_{j} - \overline{c}_{j}c_{i}\mathbf{e}_{i})\|_2 \nonumber \\ 
-&\geq \sqrt{2}  L_2(\mathbf{A}) \|\overline{c}_{i}c_{j} \mathbf{e}_{j} - \overline{c}_{j}c_{i}\mathbf{e}_{i}\|_2 \nonumber \\
-&\geq  L_2(\mathbf{A}) \left( |\overline{c}_{i}| + |\overline{c}_{j}| \right) \min_{\ell \in [m]} |c_\ell |,
-\end{align*}
-contradicting our assumed upper bound on $\varepsilon$. Hence, the map $\pi$ is injective and so $\overline m \geq m$. %Setting $\overline J = \pi([m])$ and
-
-Letting $\mathbf{P}$ and $\mathbf{D}$ be the $\overline m \times \overline m$ permutation and invertible diagonal matrices with, respectively, columns $\mathbf{e}_{\pi(i)}$ and $\frac{\overline{c}_i}{c_i}\mathbf{e}_i$ for $i \in [m]$ (otherwise, $\mathbf{e}_{i}$ for $i \in [\overline{m}] \setminus [m]$), we may rewrite \eqref{1D} to see that for all $i \in [m]$:
-\begin{align*}
-\|\mathbf{A}_i - (\mathbf{BPD})_i\|_2 
-= \|\mathbf{A}_i - \frac{\overline{c}_i}{c_i}\mathbf{B}_{\pi(i)}\|_2 
-\leq \frac{\varepsilon}{|c_i|} 
-\leq C_1\varepsilon.
-\end{align*}
-%\vspace{-.2 cm}
-\end{proof}
-
-An extension of the proof to the general case $k < m$ requires some additional tools to derive the general expression \eqref{Cdef1} for $C_1$.
-These include a generalized notion of distance (Def.~\ref{dDef}) and angle (Def.~\ref{FriedrichsDefinition}) between subspaces as well as a stability result in combinatorial matrix analysis (Lem.~\ref{MainLemma}).
-
-\begin{definition}\label{dDef}
-For $\mathbf{u} \in \mathbb R^m$ and vector spaces $U,V \subseteq \mathbb{R}^m$, let $\text{\rm dist}(\mathbf{u}, V) := \min \{\| \mathbf{u}-\mathbf{v} \|_2: \mathbf{v} \in V\}$ and define:
-\begin{align}
-d(U,V) := \max_{\mathbf{u} \in U, \ \|\mathbf{u}\|_2 \leq 1} \text{\rm dist}(\mathbf{u},V).
-\end{align}
-\end{definition}
-
-We note the following facts about $d$. Clearly, 
-\begin{align}\label{UsubU}
-U' \subseteq U \implies d(U',V) \leq d(U,V).
-\end{align}
-From \cite[Ch.~4 Cor.~2.6]{Kato2013}, we also have: %Kato p.223
-\begin{align}\label{dimLem}
-d(U,V) < 1 \implies \dim(U) \leq \dim(V),
-\end{align}
-and from \cite[Lem.~3.2]{Morris10}:
-\begin{align}\label{eqdim}
-\dim(U) = \dim(V) \implies d(U,V) = d(V,U).
-\end{align}
-
-The following is our result in combinatorial matrix analysis; it contains most of the complexity in the proof of Thm.~\ref{DeterministicUniquenessTheorem}.
-
-\begin{lemma}\label{MainLemma}
-If an $n \times m$ matrix $\mathbf{A}$ has $L_{2\mathcal{H}}(\mathbf{A}) > 0$ for some $r$-regular $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP, then the following holds for $C_2 > 0$ given by \eqref{Cdef2}:
-
-Fix $\varepsilon < L_2(\mathbf{A}) / C_2$. If for some $n \times \overline m$ matrix $\mathbf{B}$ and map $\pi: \mathcal{H} \mapsto {[\overline m] \choose k}$,
-\begin{align}\label{GapUpperBound}
-d(\bm{\mathcal{A}}_S, \bm{\mathcal{B}}_{\pi(S)}) \leq \varepsilon, \ \  \text{for $S \in \mathcal{H}$},
-\end{align}
-then $\overline m \geq m$, and provided $\overline m (r-1) < mr$, there is a permutation matrix $\mathbf{P}$ and invertible diagonal $\mathbf{D}$ such that:
-\begin{align}\label{MainLemmaBPD}
-\|\mathbf{A}_i - (\mathbf{B}\mathbf{PD})_i\|_2 \leq C_2 \varepsilon, \ \  \text{for } i \in J,
-\end{align}
-for some $J \subseteq [m]$ of size \mbox{$m - (r-1)(\overline m - m)$}.
-\end{lemma}
-
-%\begin{lemma}\label{MainLemma}
-%Fix $\mathbf{A} \in \mathbb{R}^{n \times m}$ with $L_\mathcal{H}(\mathbf{A}) > 0$ for some regular $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP.
-There exists a constant $C_2 > 0$ for which the following holds for all $\varepsilon < L_2(\mathbf{A}) / C_2$:
-
-%If a matrix $\mathbf{B} \in \mathbb{R}^{n \times m}$ and map $\pi: E \mapsto {m \choose k}$ satisfy:
-%\begin{align}\label{GapUpperBound}
-%d(\text{\rm span}\{\mathbf{A}_{S}\}, \bm{\mathcal{B}}_{\pi(S)}) \leq \varepsilon, \ \ \text{for $S \in \mathcal{H}$},
-%\end{align}
-%then there exist a permutation matrix $\mathbf{P}$ and invertible diagonal matrix $\mathbf{D}$ such that:
-%\begin{align}\label{MainLemmaBPD}
-%\|\mathbf{A}_j - \mathbf{BPD}_j\|_2 \leq C_2 \varepsilon, \ \  \text{for } j \in [m],
-%\end{align}
-%\end{lemma}
-
-We present the constant $C_2$ (a function of $\mathbf{A}$ and $\mathcal{H}$) relative to a quantity used in \cite{Deutsch12} to analyze the convergence of the ``alternating projections" algorithm for projecting a point onto the intersection of subspaces.
-We incorporate this quantity into the following definition, which we refer to in our proof of Lem.~\ref{DistanceToIntersectionLemma} in the Appendix; specifically, we use it to bound the distance between a point and the intersection of subspaces given an upper bound on its distance from each subspace.
-
-\begin{definition}\label{FriedrichsDefinition}
-For a collection of real subspaces $\mathcal{V} = \{V_i\}_{i=1}^\ell$, define $\xi(\mathcal{V}) := 0$ when $|\mathcal{V}| = 1$, and otherwise:
-\begin{align}\label{xi}
-\xi^2(\mathcal{V}) := 1 -  \max \prod_{i=1}^{\ell-1} \sin^2  \theta \left(V_i, \cap_{j>i} V_j \right) ,
-\end{align} 
-%
-where the maximum is taken over all ways of ordering 
-%\footnote{We modify the quantity in \cite{Deutsch12} in this way since the subspace ordering is irrelevant to our purpose.} 
-the $V_i$ and the angle $\theta \in (0,\frac{\pi}{2}]$ is defined implicitly as \cite[Def.~9.4]{Deutsch12}:
-\begin{align*}
-\cos{\theta(U,W)} := \max\left\{ |\langle \mathbf{u}, \mathbf{w} \rangle|: \substack{ \mathbf{u} \in U \cap (U \cap W)^\perp, \ \|\mathbf{u}\|_2 \leq 1 \\ \mathbf{w} \in W \cap (U \cap W)^\perp, \  \|\mathbf{w}\|_2 \leq 1 } \right\}.
-\end{align*}
-\end{definition}
-Note that $\theta \in (0,\frac{\pi}{2}]$ implies $0 \leq \xi < 1$, and that $\xi(\mathcal{V}') \leq \xi(\mathcal{V})$ when $\mathcal{V}' \subseteq \mathcal{V}$.\footnote{We acknowledge the counter-intuitive property: $\theta =  \pi/2$ when $U \subseteq W$.}
-
-The constant $C_2 > 0$ of Lem.~\ref{MainLemma} can now be expressed as:  
-\begin{align}\label{Cdef2}
-	C_2(\mathbf{A}, \mathcal{H}) := \frac{ (r+1) \max_{j \in [m]} \|\mathbf{A}_j\|_2}{ 1- \max_{\mathcal{G} \in {\mathcal{H} \choose r+1}} \xi( \bm{\mathcal{A}}_\mathcal{G} ) }.
-\end{align}
-
-We next define the constant $C_1 > 0$ of Thm.~\ref{DeterministicUniquenessTheorem} in terms of $C_2$.
-Given vectors $\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$, let $\mathbf{X}$ denote the $m \times N$ matrix with columns $\mathbf{x}_i$ and let $I(S)$ denote the set of indices $i$ for which $\mathbf{x}_i$ is supported in $S$.
-We define:
-\begin{align}\label{Cdef1}
-C_1(\mathbf{A}, \mathcal{H}, \{\mathbf{x}_i\}_{i=1}^N) := \frac{ C_2(\mathbf{A}, \mathcal{H}) } { \min_{S \in \mathcal{H}} L_k(\mathbf{AX}_{I(S)}) }.
-\end{align}
-Given the assumptions of Thm.~\ref{DeterministicUniquenessTheorem} on $\mathbf{A}$ and the $\mathbf{x}_i$, this expression for $C_1$ is well-defined\footnote{\label{note1}To see this, fix $S \in \mathcal{H}$ and $k$-sparse $\mathbf{c}$.
-Using the definitions, we have $\|\mathbf{AX}_{I(S)}\mathbf{c}\|_2 \geq \sqrt{k} L_\mathcal{H}(\mathbf{A})\|\mathbf{X}_{I(S)}\mathbf{c}\|_2 \geq k L_\mathcal{H}(\mathbf{A}) L_k(\mathbf{X}_{I(S)})\|\mathbf{c}\|_2$.
-Thus, $L_k(\mathbf{AX}_{I(S)}) \geq \sqrt{k} L_\mathcal{H}(\mathbf{A}) L_k(\mathbf{X}_{I(S)}) > 0$, since $L_{\mathcal{H}}(\mathbf{A}) \geq L_{2\mathcal{H}}(\mathbf{A})> 0$ and $L_k(\mathbf{X}_{I(S)}) > 0$ by general linear position of the $\mathbf{x}_i$.} and yields an upper bound on $\varepsilon$ consistent with that proven sufficient in the case $k=1$ considered at the beginning of this section.\footnote{When $\mathbf{x}_i = c_i\mathbf{e}_i$, we have $C_2 \geq 2\|\mathbf{A}_i\|_2$ and the denominator in \eqref{Cdef1} becomes $\min_{i \in [m]} |c_i| \|\mathbf{A}_i\|_2$; hence, $C_1 \geq 2 / \min_{i \in [m]} |c_i|$.}
-% C_2(\mathbf{A}, \mathcal{H}) := \frac{ (r+1) \max_{j \in [m]} \|\mathbf{A}_j\|_2}{ \min_{\mathcal{G} \in {\mathcal{H} \choose r} \cup {\mathcal{H} \choose r+1}} \xi( \{ \bm{\mathcal{A}}_S \}
-
-The practically-minded reader should note that the explicit constants $C_1$ and $C_2$ are effectively computable: the quantity $L_k$ may be calculated as the smallest singular value of a certain matrix, while the quantity $\xi$ involves computing ``canonical angles'' between subspaces, which reduces again to an efficient singular value decomposition.
-There is no known fast computation of $L_k$ in general, however, since even $L_{k} > 0$ is NP-hard \cite{tillmann2014computational}, although 
-efficiently computable bounds have been proposed (e.g., via the ``mutual coherence" of a matrix \cite{donoho2003optimally}); alternatively, 
-fixing $k$ yields polynomial complexity.
-Moreover, calculating $C_2$ requires an exponential number of queries to $\xi$ unless $r$ is held fixed, too (e.g., the ``cyclic order'' hypergraphs described above have $r=k$).
-Thus, as presented, $C_1$ and $C_2$ are not efficiently computable in general.
-% , but efficient subcases do exist and may be of practical relevance.
-
-\begin{proof}[Proof of Thm.~\ref{DeterministicUniquenessCorollary} for $k < m$] 
-We find a map $\pi: \mathcal{H} \to {[m] \choose k}$ for which the distance $d(\bm{\mathcal{A}}_S, \bm{\mathcal{B}}_{\pi(S)})$ is controlled by $\varepsilon$ for all $S \in \mathcal{H}$.
-Applying Lem.~\ref{MainLemma} then completes the proof.
-%We shall show that for every $S \in \mathcal{H}$ there is some $\overline S \in {[\overline m] \choose k}$ for which the distance $d(\bm{\mathcal{A}}_S, \bm{\mathcal{B}}_{\overline S})$ is controlled by $\varepsilon$.
-Applying Lem.~\ref{MainLemma} with the map $\pi$ defined by $S \mapsto \overline S$ then completes the proof.
-
-Fix $S \in \mathcal{H}$.
-Since there are more than $(k-1){\overline m \choose k}$ vectors $\mathbf{x}_i$ supported in $S$, by the pigeonhole principle there must be some $\overline S \in {[\overline m] \choose k}$ and a set of $k$ indices $K \subseteq I(S)$ for which all $\mathbf{\overline x}_i$ with $i \in K$ are supported in $\overline S$.
-It also follows\footnotemark[\ref{note1}] from $L_{2\mathcal{H}}(\mathbf{A}) > 0$ and the general linear position of the $\mathbf{x}_i$ that $L_k(\mathbf{AX}_{K}) > 0$; that is, the columns of the $n \times k$ matrix $\mathbf{AX}_K$ form a basis for $\bm{\mathcal{A}}_S$.
-
-Fixing $\mathbf{y} \in \bm{\mathcal{A}}_S \setminus \{\mathbf{0}\}$, there then exists $\mathbf{c} = (c_1, \ldots, c_k) \in \mathbb{R}^k \setminus \{\mathbf{0}\}$ such that $\mathbf{y} = \mathbf{AX}_K\mathbf{c}$.
-Setting \mbox{$\mathbf{\overline{y}} = \mathbf{B\overline{X}}_K\mathbf{c}$, which is in $\bm{\mathcal{B}}_{\overline S}$}, we have by triangle inequality:
-\begin{align*}
-\|\mathbf{y} - \mathbf{\overline{y}}\|_2 
-%&= \|\sum_{i=1}^k c_i(\mathbf{AX}_K - \mathbf{B\overline{X}}_K)_i\|_2
-&= \|(\mathbf{AX}_K - \mathbf{B\overline{X}}_K)\mathbf{c}\|_2
-%\leq \varepsilon \sum_{i=1}^k |c_i| \\
-\leq \varepsilon \|\mathbf{c}\|_1
-\leq \varepsilon \sqrt{k}  \|\mathbf{c}\|_2  \\
-&\leq \frac{\varepsilon}{L_k(\mathbf{AX}_K)} \|\mathbf{y}\|_2,
-\end{align*}
-where the last inequality uses \eqref{Ldef}. From Def.~\ref{dDef}:
-\begin{align}\label{rhs222}
-d(\bm{\mathcal{A}}_S, \bm{\mathcal{B}}_{\overline S}) 
-\leq \frac{\varepsilon}{  L_k(\mathbf{AX}_{K}) } 
-\leq \frac{\varepsilon}{  L_k(\mathbf{AX}_{I(S)}) } 
-\leq \varepsilon \frac{C_1}{C_2}.
-\end{align}
-%
-Finally, apply Lem.~\ref{MainLemma} with $\varepsilon < L_2(\mathbf{A})/C_1$ and $\pi(S) := \overline S$. % L_2(A) > 0 by def of L, since L_2H(A) > 0 and H covers [m]
-\end{proof}
-
-Before moving on to the proof of Thm.~\ref{SLCopt}, we briefly revisit our discussion on sample complexity from the end of the previous section.
-While an exponential number of samples may very well prove to be necessary in the deterministic or almost-certain case, our proof of Thm.~\ref{DeterministicUniquenessTheorem} can be extended to hold with some probability for \emph{any} number of samples by alternative appeal to a probabilistic pigeonholing at the point early in the proof where the (deterministic) pigeonhole principle is applied to show that for every $S \in \mathcal{H}$, there exist $k$ vectors $\mathbf{x}_i$ supported on $S$ whose corresponding $\mathbf{\overline x}_i$ all share the same support.\footnote{A famous example of such an argument is the counter-intuitive ``birthday paradox", which demonstrates that the probability of two people having the same birthday in a room of twenty-three is greater than 50\%.}
-Given insufficient samples, this argument has some less-than-certain probability of being valid for each $S \in \mathcal{H}$.
-Nonetheless, simulations with small hypergraphs confirm that the probability of success very quickly approaches one once the number of samples $N$ surpasses a small fraction of the deterministic sample complexity.
-
-\begin{proof}[Proof of Thm.~\ref{SLCopt}]
-We bound the number of $k$-sparse $\mathbf{\overline x}_i$ from below and then apply Thm.~\ref{DeterministicUniquenessCorollary}. 
-%We now apply this fact to bound the number of $k$-sparse $\mathbf{\overline x}_i$. 
-Let $n_p$ be the number of $\mathbf{\overline x}_i$ with $\|\mathbf{\overline x}_i\|_0 = p$.
-Since the $\mathbf{x}_i$ are all $k$-sparse, by \eqref{minsum} we have:
-\begin{align*}
-%\mbox{$k \sum_{p = 0}^{\overline m} n_p \geq \sum_{i=0}^N \|\mathbf{x}_i\|_0 \geq \sum_{i=0}^N \|\mathbf{\overline x}_i\|_0 = \sum_{p=0}^{\overline m} p n_p.$}
-\sum_{p=0}^{\overline m} p n_p =  \sum_{i=0}^N \|\mathbf{\overline x}_i\|_0
-\leq \sum_{i=0}^N \|\mathbf{x}_i\|_0 
-\leq kN
-\end{align*}
-Since $N = \sum_{p = 0}^{\overline m} n_p$, we then have $\sum_{p = 0}^{\overline m} (p-k) n_p \leq 0$. Splitting the sum yields:
-\begin{align}\label{eqn}
-\sum_{p = k+1}^{\overline m} n_p \leq \sum_{p = k+1}^{\overline m} (p-k) n_p \leq \sum_{p = 0}^k (k-p)n_p \leq k \sum_{p = 0}^{k-1} n_p,
-\end{align}
-%
-demonstrating that the number of vectors $\mathbf{\overline x}_i$ that are \emph{not} $k$-sparse is bounded above by how many are $(k-1)$-sparse.
-
-Next, observe that no more than $(k-1)|\mathcal{H}|$ of the $\mathbf{\overline x}_i$ share a support $\overline S$ of size less than $k$.
-Otherwise, by the pigeonhole principle, there is some $S \in \mathcal{H}$ and a set of $k$ indices $K \subseteq I(S)$ for which all $\mathbf{x}_i$ with $i \in K$ are supported in $S$; as argued previously, \eqref{rhs222} follows.
-It is simple to show that $L_2(\mathbf{A}) \leq \max_j\|\mathbf{A}_j\|_2$, and since $0 \leq \xi < 1$, the right-hand side of \eqref{rhs222} is less than one for $\varepsilon < L_2(\mathbf{A})/C_1$.
-Thus, by \eqref{dimLem} we would have the contradiction $k = \dim(\bm{\mathcal{A}}_S) \leq \dim(\bm{\mathcal{B}}_{\overline S}) \leq |\overline S| < k.$
-
-The total number of $(k-1)$-sparse vectors $\mathbf{\overline x}_i$ thus cannot exceed $|\mathcal{H}|(k-1){ \overline m \choose k-1}$.
-By \eqref{eqn}, no more than $|\mathcal{H}|k(k-1){ \overline m \choose k-1}$ vectors $\mathbf{\overline x}_i$ are not $k$-sparse.
-Since for every $S \in \mathcal{H}$ there are over $(k-1)\left[ {\overline m \choose k} + |\mathcal{H}|k{ \overline m \choose k-1} \right]$ vectors $\mathbf{x}_i$ supported there, it must be that more than $(k-1){\overline m \choose k}$ of them have corresponding $\mathbf{\overline x}_i$ that are $k$-sparse.
-The result now follows from Thm.~\ref{DeterministicUniquenessCorollary}, noting by the triangle inequality that $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline x}_i\| \leq 2\eta$ for $i = 1, \ldots, N$.
-\end{proof}
-
-%\begin{proof}[Proof (sketch) of Thm.~\ref{robustPolythm}]
-%Let $\textbf{M}$ be the matrix with columns $\mathbf{A}\mathbf{x}_i$, $i \in [N]$.
-Consider the polynomial $\prod_{S \in {[N] \choose 2k}} \sum_{S' \in {[n] \choose 2k}} (\det \textbf{M}_{S',S})^2$ in the indeterminate entries of $\mathbf{A}$ and $\mathbf{x}_i$, with notation as in Sec.~\ref{Results}.
-%It can be checked that when this polynomial is nonzero for a substitution of real numbers for the indeterminates, all of the genericity requirements on $\mathbf{A}$ and $\mathbf{x}_i$ in our proofs of stability in Thm.~\ref{DeterministicUniquenessTheorem} are satisfied (in particular, the spark condition \eqref{SparkCondition} on $\mathbf{A}$).
-%\end{proof}
-
-%\begin{proof}[Proof (sketch) of Cor.~\ref{ProbabilisticCor}]
-%First, note that if a set of measure spaces $\{(X_{\ell}, \Sigma_{\ell}, \nu_{\ell})\}_{\ell=1}^p$ has that $\nu_{\ell}$ is absolutely continuous with respect to $\mu$ for all $\ell \in [p]$, where $\mu$ is the standard Borel measure on $\mathbb{R}$, then the product measure $\prod_{\ell=1}^p \nu_{\ell}$ is absolutely continuous with respect to the standard Borel product measure on $\mathbb{R}^p$.
-% for space:  (e.g.,  \cite{folland2013real}).
-%By Thm.~\ref{robustPolythm}, there is a polynomial that is nonzero when $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$; in particular, stability holds almost surely.
-%\end{proof}
-
 \section{Discussion}\label{Discussion}
@@
 
-We close with some challenges left open by our work.
+\section{Future Directions}
+
+There are many challenges left open by this work.
 All conditions stated here guaranteeing the uniqueness and stability of sparse representations have only been shown sufficient; it remains open, therefore, to extend them to necessary conditions, be they on required sample size, the structure of support set hypergraphs, or tolerable error bounds.
-On this last note, we remark that our deterministic treatment considers always the ``worst-case" noise, whereas the ``effective" noise sampled from a concentrated distribution might be significantly reduced, especially for high-dimensional data.
+On this last note, we remark that the deterministic conditions derived here must consider always the ``worst-case" noise, whereas the ``effective" noise sampled from a concentrated distribution might be significantly reduced, especially for high-dimensional data.
 It would be of great practical benefit to see how drastically all conditions can be relaxed by requiring only probabilistic guarantees in this way, or in the spirit of our discussion on probabilistic pigeonholing to reduce sample complexity (as in the famous ``birthday paradox") following the proof of Thm.~\ref{DeterministicUniquenessTheorem}.
 
-Another interesting question raised by our work is for which special cases is it efficient to check that a solution to Prob.~\ref{InverseProblem} or \ref{OptimizationProblem} is unique up to noise and inherent ambiguities.
+Another interesting question raised by this work is for which special cases is it efficient to check that a solution to Prob.~\ref{InverseProblem} or \ref{OptimizationProblem} is unique up to noise and inherent ambiguities.
 Considering that the sufficient conditions we have described for checking this in general are NP-hard to compute, are the necessary conditions hard?
@@
 the dictionary is a member of a known finite set).
-
-\textbf{Acknowledgement.} We thank Fritz Sommer and Darren Rhea for early thoughts, and Ian Morris for posting \eqref{eqdim} online.
 
@@
 
-\bibliographystyle{IEEEtran}
-\bibliography{chazthm_ieee_trans_sig}
+%The problem is to count integer solution to the problem $\sum_i a_i = N$ subject to $a_i < i$ for all $i$.
+There is as far as [internet person] knows no closed formula for this general problem, but there is a formula that allows the number of solutions to be computed in a number of operations independent of ??.
+Consider first the case that all limits are equal ??1=??2=?=????=??.
+Then the number is the coefficient of ????
+in the polynomial (1+??+?+????)??.
+By writing this as a rational function of ??...
+%see:
+%https://math.stackexchange.com/questions/553960/extended-stars-and-bars-problemwhere-the-upper-limit-of-the-variable-is-bounded
 
-% \vspace{-.2 cm}
+\begin{figure}\label{probpigeon}
+\begin{center}
+\includegraphics[width=1 \linewidth]{figures/prob_vs_samples.png}
+\caption{Probability of successful dictionary and code recovery (as per Thm.
+\ref{DeterministicUniquenessTheorem}) for a number of samples $N$ given as a fraction of the deterministic sample complexity $N = |\mathcal{H}|[(k-1){m \choose k} + 1]$ when $\mathcal{H}$ is taken to be the set of $m$ consecutive intervals of length $k$ in a cyclic order on $[m]$ (i.e.
+$|\mathcal{H}|=m$).
+Successful recovery is nearly certain far below the deterministic sample complexity.}
+\vspace{-.6 cm}
+\label{probvsamples}
+\end{center}
+\end{figure}
 
-\section{Appendix}\label{proofs}
-
-We prove Lem.~\ref{MainLemma} after the following auxiliary lemmas.  % stating and proving some auxiliary lemmas. 
-%First, note that since $\|\mathbf{A}\mathbf{x}\|_2 \leq \max_j\|\mathbf{A}_j\|_2\|\mathbf{x}\|_1$ and $\|\mathbf{x}\|_1 \leq \sqrt{k} \|\mathbf{x}\|_2$ for $k$-sparse $\mathbf{x}$, by \eqref{Ldef} we have the following frequently applied inequality:
-%\begin{align}\label{delrho}
-%L_{k'}(\mathbf{A}) \leq  \max_j\|\mathbf{A}_j\|_2 \ \ \text{for all $k' \leq 2k$}.
-%\end{align}
-
-% and then sketch the proofs of Thm.~\ref{robustPolythm} and Cor.~\ref{ProbabilisticCor}.
-
-%\begin{lemma}\label{spanIntersectionLemma}
-%Let $\mathbf{M} \in \mathbb{R}^{n \times m}$. If every $2k$ columns of $\mathbf{M}$ are linearly independent, then for any $F \subseteq {[m] \choose k}$:
-%\begin{align*}
-%\text{\rm span}\{\mathbf{M}_{\cap F}\}  = \bigcap_{S \in F} \text{\rm span}\{\mathbf{M}_S\}.
-%\end{align*}
-%\end{lemma}
-%\begin{proof}
-%Using induction on $|F|$, it is enough to prove the lemma when $|F| = 2$; but this case follows directly from the assumption.
-%\end{proof}
-
-\begin{lemma}\label{spanIntersectionLemma}
-If $f: V \to W$ is injective, then $f\left(\cap_{i=1}^\ell V_i \right) =  \cap_{i=1}^\ell f\left(V_i\right)$ for any $V_1, \ldots, V_\ell \subseteq V$. ($f(\emptyset):=\emptyset$.)
-%In particular, if for some $E \in 2^{[m]}$ the map $M \in \mathbb{R}^{n \times m}$ is injective on $\cup_{S \in \mathcal{H}} \text{span}\{e_i\}_{i \in S}$ then $\text{span}\{ M_{\cap_{S \in \mathcal{H}} S} \} = \cap_{S \in \mathcal{H}} \text{span}\{M_S\}$.
-\end{lemma}
-\begin{proof}
-By induction, it is enough to prove the case $\ell = 2$.
-Clearly, for any map $f$, if $w \in f(U \cap V)$ then $w \in f(U)$ and $w \in f(V)$; hence, $w \in f(U) \cap f(V)$.
-If $w \in f(U) \cap f(V)$, then $w \in f(U)$ and $w \in f(V)$; thus, $w = f(u) = f(v)$ for some $u \in U$ and $v \in V$, implying $u = v$ by injectivity of $f$.
-It follows that $u \in U \cap V$ and $w \in f(U \cap V)$.
-\end{proof}
-In particular, if a matrix $\mathbf{A}$ satisfies $L_{2\mathcal{H}}(\mathbf{A}) > 0$, then taking $V$ to be the union of subspaces consisting of vectors with supports in $2\mathcal{H}$, we have $\bm{\mathcal{A}}_{\cap \mathcal{G}} = \cap \bm{\mathcal{A}}_\mathcal{G}$ for all $\mathcal{G} \subseteq \mathcal{H}$.
-% \vspace{-.4 cm}
-
-\begin{lemma}\label{DistanceToIntersectionLemma}
-Let $\mathcal{V} = \{V_i\}_{i=1}^k$ be a set of two or more subspaces of $\mathbb{R}^m$, and set $V = \cap \mathcal{V} $.
-For  $\mathbf{u} \in \mathbb{R}^m$, we have (recall Defs.~\ref{dDef}~\&~\ref{FriedrichsDefinition}):
-\begin{align}\label{DTILeq}
-\text{\rm dist}(\mathbf{u}, V) \leq \frac{1}{1 - \xi(\mathcal{V})} \sum_{i=1}^k \text{\rm dist}(\mathbf{u}, V_i).
-\end{align}
-\end{lemma}
-\begin{proof} 
-% When $V = \{\mathbf{0}\}$, the result is trivial, so suppose otherwise.  
-Recall the projection onto the subspace $V \subseteq \mathbb{R}^m$ is the mapping $\Pi_V: \mathbb{R}^m \to V$ that associates with each $\mathbf{u}$ its unique nearest point in $V$; i.e., $\|\mathbf{u} - \Pi_V\mathbf{u}\|_2 = \text{\rm dist}(\mathbf{u}, V)$.
-By repeatedly applying the triangle inequality, we have:
-\begin{align}\label{f}
-\|\mathbf{u} - &\Pi_V\mathbf{u}\|_2 
-\leq \|\mathbf{u} - \Pi_{V_k} \mathbf{u}\|_2 + \|\Pi_{V_k}  \mathbf{u} - \Pi_{V_k}\Pi_{V_{k-1}}\mathbf{u}\|_2 \nonumber \\
-&\ \ \ \ \ \ \ \ \ \ \ + \cdots + \|\Pi_{V_k} \Pi_{V_{k-1}}\cdots \Pi_{V_1} \mathbf{u} - \Pi_V \mathbf{u}\|_2 \nonumber \\
-&\leq  \sum_{\ell=1}^k \|\mathbf{u} - \Pi_{V_{\ell}} \mathbf{u}\|_2 
-+ \|(\Pi_{V_k}\cdots\Pi_{V_{1}} - \Pi_V) \mathbf{u}\|_2,
-\end{align}
-where we have also used that the spectral norm of the orthogonal projections $\Pi_{V_{\ell}}$ satisfies $\|\Pi_{V_{\ell}}\|_2 \leq 1$ for all $\ell$.
-
-It remains to bound the second term in \eqref{f} by $\xi(\mathcal{V}) \|\mathbf{u} - \Pi_V\mathbf{u}\|_2$.
-First, note that $\Pi_{V_\ell} \Pi_V = \Pi_V$ and $\Pi_V^2 = \Pi_V$, so we have $\|(\Pi_{V_k} \cdots \Pi_{V_1} - \Pi_V) \mathbf{u} \|_2
-= \| ( \Pi_{V_k} \cdots\Pi_{V_1} - \Pi_V ) (\mathbf{u} - \Pi_V\mathbf{u})\|_2$. % \leq z\|\mathbf{u} - \Pi_V\mathbf{u}\|_2$.
-Consequently, inequality \eqref{DTILeq} follows from \cite[Thm.~9.33]{Deutsch12}:
-\begin{align}
-\|\Pi_{V_k}\Pi_{V_{k-1}}\cdots\Pi_{V_1} \mathbf{x} - \Pi_V\mathbf{x}\|_2 \leq z \|\mathbf{x}\|_2, \ \ \text{for all } \mathbf{x},
-\end{align}
-with \mbox{$z^2= 1 - \prod_{\ell =1}^{k-1}(1-z_{\ell}^2)$} and \mbox{$z_{\ell} = \cos\theta\left(V_{\ell}, \cap_{s=\ell+1}^k V_s\right)$} (recall $\theta$ from Def.~\ref{FriedrichsDefinition}), after substituting $\xi(\mathcal{V})$ for $z$ and rearranging terms.
-\end{proof}
-\begin{lemma}\label{NonEmptyLemma} 
-Fix an $r$-regular hypergraph $\mathcal{H} \subseteq 2^{[m]}$ satisfying the SIP.
-If the map $\pi: \mathcal{H} \to 2^{[\overline m]}$ has $\sum_{S \in \mathcal{H}} |\pi(S)| \geq \sum_{S \in \mathcal{H}} |S|$ and:
-\begin{align}\label{cond}
-	|\cap \pi(\mathcal{G})| \leq |\cap \mathcal{G} |,\ \ \   \text{for } \mathcal{G} \in {\mathcal{H} \choose r} \cup {\mathcal{H} \choose r+1},
-\end{align}
-%
-then $\overline m \geq m$; and if $\overline m  (r-1) < mr$, the map $i \mapsto \cap_{S \in \sigma(i)} \pi(S)$ is an injective function to $[\overline m]$ from some $J \subseteq [m]$ of size $m - (r-1)(\overline m - m)$ (recall $\sigma$ from Def.~\ref{sip}).
-%In particular, if $\overline m = m$ then $\pi$ is induced by a permutation on $[m]$.
-\end{lemma}
-
-\begin{proof}
-Consider the following set: $T_1 := \{(i, S): i \in \pi(S), S \in \mathcal{H}\}$, which numbers $|T_1| = \sum_{S \in \mathcal{H}} |\pi(S)| \geq \sum_{S \in \mathcal{H}} |S| = \sum_{i \in [m]} \deg_\mathcal{H}(i) = mr$ by $r$-regularity of $\mathcal{H}$.
-Note that $|T_1| \leq \overline m r$; otherwise, pigeonholing the tuples of $T_1$ with respect to their $\overline m$ possible first elements would imply that more than $r$ of the tuples in $T_1$ share the same first element.
-This cannot be the case, however, since then some $\mathcal{G} \in {\mathcal{H} \choose r+1}$ formed from any $r+1$ of their second elements would satisfy $\cap \pi(\mathcal{G}) \neq 0$; hence, $|\cap \mathcal{G}| \neq 0$ by \eqref{cond}, contradicting $r$-regularity of $\mathcal{H}$.
-It follows that $\overline m \geq m$.
-
-Suppose now that $\overline m (r-1) < mr$, so that $p := mr - \overline m (r-1)$ is positive and $|T_1| \geq \overline m (r - 1) + p$.
-Pigeonholing $T_1$ into $[\overline m]$ again, there are at least $r$ tuples in $T_1$ sharing some first element; that is, for some $\mathcal{G}_1 \subseteq \mathcal{H}$ of size $|\mathcal{G}_1| \geq r$, we have $|\cap \pi(\mathcal{G}_1)| \geq 1$ and (by \eqref{cond}) $|\cap \mathcal{G}_1| \geq 1$.
-Since no more than $r$ tuples of $T_1$ can share the same first element, we in fact have $|\mathcal{G}_1| = r$.
-It follows by $r$-regularity that $\mathcal{G}_1$ is a star of $\mathcal{H}$; hence, $|\cap \mathcal{G}_1| = 1$ by the SIP and $|\cap \pi(\mathcal{G}_1)|  = 1$ by \eqref{cond}.
-
-If $p=1$, then we are done.
-Otherwise, define $T_2 := T_1 \setminus \{(i,S) \in T_1: i = \cap \pi(\mathcal{G}_1)\}$, which contains $|T_2| = |T_1| - r \geq (\overline m - 1)(r-1) + (p-1)$ ordered pairs having $\overline m - 1$ distinct first indices.
-Pigeonholing $T_2$ into $[\overline m - 1]$ and repeating the above arguments produces the star $\mathcal{G}_2 \in {\mathcal{H} \choose r}$ with intersection $\cap \mathcal{G}_2$ necessarily distinct (by $r$-regularity) from $\cap \mathcal{G}_1$.
-Iterating this procedure $p$ times in total yields the stars $\mathcal{G}_i$ for which $\cap\mathcal{G}_i \mapsto \cap \pi(\mathcal{G}_i)$ defines an injective map to $[\overline m]$ from $J = \{\cap \mathcal{G}_1, \ldots, \cap \mathcal{G}_p\} \subseteq [m]$.
-\end{proof}
-
-\begin{proof}[Proof of Lem.~\ref{MainLemma}]
-%We will show that the bound \eqref{GapUpperBound} trickles through the intersection semi-lattices of $\{\bm{\mathcal{A}}_S\}_{S \in \mathcal{H}}$ and $\{\bm{\mathcal{B}}_{\overline S}\}_{\overline S \in \pi(\mathcal{H})}$ to yield \eqref{MainLemmaBPD} by virtue of the SIP.
-We begin by showing that $\dim(\bm{\mathcal{B}}_{\pi(S)}) = \dim(\bm{\mathcal{A}}_S)$ for all $S \in \mathcal{H}$.
-Note that since $\|\mathbf{A}\mathbf{x}\|_2 \leq \max_j\|\mathbf{A}_j\|_2\|\mathbf{x}\|_1$ and $\|\mathbf{x}\|_1 \leq \sqrt{k} \|\mathbf{x}\|_2$ for all $k$-sparse $\mathbf{x}$, by \eqref{Ldef} we have $L_2(\mathbf{A}) \leq \max_j\|\mathbf{A}_j\|_2$ and therefore (as $0 \leq \xi < 1$) the right-hand side of \eqref{GapUpperBound} is less than one.
-From \eqref{dimLem}, we have $|\pi(S)| \geq \dim(\bm{\mathcal{B}}_{\pi(S)}) \geq \dim(\bm{\mathcal{A}}_S) = |S|$, the final equality holding by injectivity of $\mathbf{A}_S$.
-As $|\pi(S)| = |S|$, the claim follows.
-Note, therefore, that $\mathbf{B}_{\pi(S)}$ has full-column rank for all $S \in \mathcal{H}$.
-
-We next demonstrate that \eqref{cond} holds.
-Fixing $\mathcal{G} \in {\mathcal{H} \choose r} \cup {\mathcal{H} \choose r+1}$, it suffices to show that $d(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}, \bm{\mathcal{A}}_{\cap \mathcal{G}} ) < 1$, since by \eqref{dimLem} we then have $|\cap \pi(\mathcal{G})| = \dim(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}) \leq \dim(\bm{\mathcal{A}}_{\cap \mathcal{G}}) = |\cap \mathcal{G}|$, with equalities from the full column-ranks of $\mathbf{A}_{S}$ and $\mathbf{B}_{\pi(S)}$ for all $S \in \mathcal{H}$.\footnote{Note that if ever $\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})} \neq \bf 0$ while $\cap \mathcal{G} = \emptyset$, we would have $d(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}, \bm 0 ) = 1$.
-However, that leads to a contradiction.} Observe that $d(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}, \bm{\mathcal{A}}_{\cap \mathcal{G}}  )
-\leq d\left( \cap \bm{\mathcal{B}}_{\pi(\mathcal{G})}, \cap \bm{\mathcal{A}}_\mathcal{G} \right)$ by \eqref{UsubU}, since trivially $\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})} \subseteq \cap \bm{\mathcal{B}}_{\pi(\mathcal{G})}$ and also $\bm{\mathcal{A}}_{\cap \mathcal{G}} = \cap \bm{\mathcal{A}}_\mathcal{G}$ by Lem.~\ref{spanIntersectionLemma}.
-Recalling Def.~\ref{dDef} and applying Lem.~\ref{DistanceToIntersectionLemma} yields:
-\begin{align}
-d\left( \cap \bm{\mathcal{B}}_{\pi(\mathcal{G})}, \cap \bm{\mathcal{A}}_\mathcal{G} \right)
-&\leq \max_{\mathbf{u} \in \cap \bm{\mathcal{B}}_{\pi(\mathcal{G})}, \ \|\mathbf{u}\|_2 \leq 1} \sum_{S \in \mathcal{G}} \frac{ \text{\rm dist}\left( \mathbf{u},\bm{\mathcal{A}}_{S} \right) }{ 1 - \xi( \bm{\mathcal{A}}_\mathcal{G} ) } \nonumber \\
-&= \sum_{S \in \mathcal{G}} \frac{ d\left( \cap \bm{\mathcal{B}}_{\pi(\mathcal{G})},\bm{\mathcal{A}}_{S} \right) }{ 1 - \xi( \bm{\mathcal{A}}_\mathcal{G} ) }, \nonumber
-\end{align}
-passing the maximum through the sum.
-Since $\cap \bm{\mathcal{B}}_{\pi(\mathcal{G})} \subseteq \bm{\mathcal{B}}_{\pi(S)}$ for all $S \in \mathcal{G}$, by \eqref{UsubU} the numerator of each term in the sum above is bounded by \mbox{$d\left( \bm{\mathcal{B}}_{\pi(S)},\bm{\mathcal{A}}_{S} \right) = d\left(\bm{\mathcal{A}}_{S}, \bm{\mathcal{B}}_{\pi(S)} \right) \leq \varepsilon$}, with the equality from \eqref{eqdim} since $\dim(\bm{\mathcal{B}}_{\pi(S)}) = \dim(\bm{\mathcal{A}}_S)$.
-Thus, altogether:
-\begin{align}\label{last}
-d(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}, \bm{\mathcal{A}}_{\cap \mathcal{G}} )
-\leq \frac{|\mathcal{G}| \varepsilon}{1 - \xi( \bm{\mathcal{A}}_\mathcal{G} )}
-\leq \frac{C_2 \varepsilon}{\max_j\|\mathbf{A}_j\|_2},
-\end{align}
-recalling the definition of $C_2$ in \eqref{Cdef2}.
-Lastly, since $C_2 \varepsilon < L_2(\mathbf{A}) \leq \max_j\|\mathbf{A}_j\|_2$, we have $d(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}, \bm{\mathcal{A}}_{\cap \mathcal{G}} ) \leq 1$ and therefore \eqref{cond} holds.
-
-%Keeping in mind that $d(U',V) \leq d(U,V)$ whenever $U' \subseteq U$ and applying (in order) Lem.~\ref{spanIntersectionLemma}, Lem.~\ref{DistanceToIntersectionLemma}, \eqref{eqdim}, \eqref{GapUpperBound}, and \eqref{Cdef2} gives:
-%\begin{align}\label{randoml}
-%d(&\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}, \bm{\mathcal{A}}_{\cap \mathcal{G}}  ) 
-%\leq d\left( \cap \bm{\mathcal{B}}_{\pi(\mathcal{G})}, \cap \bm{\mathcal{A}}_\mathcal{G} \right)
-%\leq \sum_{T \in \mathcal{G}} \frac{ d\left( \cap \bm{\mathcal{B}}_{\pi(\mathcal{G})},\bm{\mathcal{A}}_{T} \right) }{ 1 - \xi( \bm{\mathcal{A}}_\mathcal{G} ) } \nonumber \\
-%&\leq \sum_{T \in \mathcal{G}} \frac{ d\left( \bm{\mathcal{B}}_{\pi(T)},\bm{\mathbf{A}}_{T} \right) }{ 1 - \xi( \bm{\mathcal{A}}_\mathcal{G} ) }
-%\leq \frac{|\mathcal{G}| \varepsilon}{1 - \xi( \bm{\mathcal{A}}_\mathcal{G} )} 
-%\leq \frac{C_2 \varepsilon}{\max_j\|\mathbf{A}_j\|_2},
-%\end{align}
-%
-%which is less than one, since $C_2 \varepsilon < L_2(\mathbf{A}) \leq \max_j\|\mathbf{A}_j\|_2$.
-
-Applying Lem.~\ref{NonEmptyLemma}, the association $i \mapsto \cap_{S \in \sigma(i)} \pi(S)$ is an injective map $\overline \pi: J \to [\overline m]$ for some $J \subseteq [m]$ of size $m - (r-1)(\overline m - m)$, and $\mathbf{B}_{\overline \pi(i)} \neq \mathbf{0}$ for all $i \in J$ since the columns of $\mathbf{B}_{\pi(S)}$ are linearly independent for all $S \in \mathcal{H}$.
-Letting $\overline \varepsilon := C_2 \varepsilon / \max_i \|\mathbf{A}_i\|_2$, it follows from \eqref{eqdim} and \eqref{last} that $d\left( \bm{\mathcal{A}}_i, \bm{\mathcal{B}}_{\overline \pi(i)} \right) = d\left(\bm{\mathcal{B}}_{\overline \pi(i)},  \bm{\mathcal{A}}_i \right)  \leq \overline \varepsilon$ for all $i \in J$.
-%Fixing $\overline \varepsilon = C_2\varepsilon$ and letting $c_i = \|\mathbf{A}_i\|_2^{-1}$, we thus have that for each $\mathbf{e}_i \in \mathbb{R}^m$ with $i \in J$ there exists some $\overline{c}_i \in \mathbb{R}$ such that $\|c_i\mathbf{A}\mathbf{e}_i - \overline{c}_i \mathbf{B}\mathbf{e}_{\overline \pi(i)}\|_2 \leq \overline \varepsilon < L_2(\mathbf{A}) \min_{i\in J} |c_i|$.
-But this is exactly the supposition in \eqref{1D}, and the result follows from the case $k=1$ in Sec.~\ref{DUT} applied to the submatrix $\mathbf{A}_J$.
-Setting $c_i := \|\mathbf{A}_i\|_2^{-1}$ so that $\|c_i\mathbf{Ae}_i\|_2 = 1$, by Def.~\ref{dDef} for all $i \in J$:
-\begin{align*}
-\min_{\overline c_i \in \mathbb{R}} \|c_i\mathbf{Ae}_i - \overline c_i \mathbf{Be}_{\overline \pi(i)} \|_2
-\leq d\left( \bm{\mathcal{A}}_i, \bm{\mathcal{B}}_{\overline \pi(i)} \right)
-\leq \overline \varepsilon,
-%&= \max_{\bm{u} \in \bm{\mathcal{A}}_i, \|\bm{u}\|_2 \leq 1} \text{dist}\left(\bm{u}, \bm{\mathcal{B}}_{\overline \pi(i)} \right) \\
-%&\geq  \text{dist}\left(c_i\bm{Ae}_i, \mathbf{Be}_{\overline \pi(i)} \right) \\
-%&= \min_{\overline c_i \in \mathbb{R}} \|c_i\bm{Ae}_i - \overline c_i \mathbf{Be}_{\overline \pi(i)} \|_2
-\end{align*}
-%
-for $\overline \varepsilon < L_2(\mathbf{A})\min_{i \in [m]}|c_i|$.
-But this is exactly the supposition in \eqref{1D}, with $J$ and $\overline \varepsilon$ in place of $[m]$ and $\varepsilon$, respectively.
-The same arguments of the case $k=1$ in Sec.~\ref{DUT} can then be made to show that for any $\overline m \times \overline m$ permutation and invertible diagonal matrices $\mathbf{P}$ and $\mathbf{D}$ with, respectively, columns $\mathbf{e}_{\pi(i)}$ and $\frac{\overline{c}_i}{c_i}\mathbf{e}_i$ for $i \in J$ (otherwise, $\mathbf{e}_{i}$ for $i \in [\overline{m}] \setminus J$), we have $\|\mathbf{A}_i - (\mathbf{B}\mathbf{PD})_i \|_2 \leq \overline  \varepsilon / |c_i|  \leq C_2 \varepsilon$ for all $i \in J$.
-\end{proof}
-
-%\section{Proofs of Thm.~\ref{robustPolythm} and Cor.~\ref{ProbabilisticCor}}
-
-%\clearpage
-
-%\section{$\ell_1$-norm Extension}
-%
-%\begin{problem}\label{OptimizationProblemL1}
-%Find a matrix $\mathbf{B}$ and vectors \mbox{$\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N \in \mathbb{R}^m$} that solve:
-%\begin{align}\label{minsum}
-%\min \sum_{i = 1}^N \|\mathbf{\overline x}_i\|_1 \ \ 
-%\text{subject to} \ \ \|\mathbf{z}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \eta, \ \text{for all $i$}.
-%\end{align}
-%\end{problem}
-
-%\begin{corollary}\label{SLCopt}
-%Fix $\alpha > 0$ and suppose all of the assumptions of Thm.\ref{DeterministicUniquenessTheorem} hold with the following modifications:
-%\begin{enumerate}
-%\item The coefficients of all $k$-sparse $\mathbf{x}_i$ are drawn from $[-\beta, \beta]$, where $\beta < \frac{\alpha(k+1)}{k}$.
-%\item More than $(k-1){\overline m \choose k} + q$ vectors $\mathbf{x}_i$ are supported in each $S \in \mathcal{H}$, where
-%\[ q = \left[\frac{\alpha}{\beta}(k+1) - k\right]^{-1}k|\mathcal{H}|(k-1){\overline m \choose k-1}. \]
-%\end{enumerate}
-%Then all solutions to Prob.~\ref{OptimizationProblemL1} for which the nonzero elements of all $\mathbf{\overline x}_i$ lie outside $[-\alpha, \alpha]$ necessarily satisfy the implications \eqref{Cstable} and \eqref{b-PDa} of Thm.~\ref{DeterministicUniquenessTheorem}.
-%\end{corollary}
-
-%\begin{proof}[Proof of Cor.~\ref{SLCopt}]
-%We bound the number of $k$-sparse $\mathbf{\overline x}_i$ and then apply Thm.~\ref{DeterministicUniquenessCorollary}.
-First, observe that no more than $(k-1)|\mathcal{H}|$ of the $\mathbf{\overline x}_i$ share a support $\overline S$ of size less than $k$; otherwise, by the pigeonhole principle, at least $k$ of these indices $i$ belong to the same $K \subseteq I(S)$ for some $S \in \mathcal{H}$ and (as argued previously) \eqref{rhs222} follows.
-Since the right-hand side of \eqref{rhs222} is less than one, by \eqref{dimLem} we have the contradiction $k = \dim(\bm{\mathcal{A}}_S) \leq \dim(\bm{\mathcal{B}}_{\overline S}) \leq |\overline S|.$ The total number of $(k-1)$-sparse vectors $\mathbf{\overline x}_i$ can thus not exceed $|\mathcal{H}|(k-1){ \overline m \choose k-1}$.
-
-%Next, observe that the assumptions of the lemma imply:
-%\begin{align*}
-%\alpha \sum_i \|\mathbf{\overline x}_i\|_0 \leq \sum_i \|\mathbf{\overline x}_i\|_1 \leq \sum_i \|\mathbf{x}_i\|_1 \leq \beta \sum_i \|\mathbf{x}_i\|_0.
-%\end{align*}
-
-%We now apply these facts to bound the number of $k$-sparse $\mathbf{\overline x}_i$.
-Let $n_p$ be the number of $\mathbf{\overline x}_i$ with $\|\mathbf{\overline x}_i\|_0 = p$.
-Since the $\mathbf{x}_i$ are all $k$-sparse, we have:
-%\begin{align*}
-%k \sum_{p = 0}^{\overline m} n_p = k N \geq \sum_{i=0}^N \|\mathbf{x}_i\|_0 \geq \frac{\alpha}{\beta} \sum_{i=0}^N \|\mathbf{\overline x}_i\|_0 = \frac{\alpha}{\beta} \sum_{p=0}^{\overline m} p n_p.
-%\end{align*}
-%Hence, 
-%\begin{align*}
-%\left[ \frac{\alpha(k+1)}{\beta} - k\right] \sum_{p = k+1}^{\overline m} n_p 
-%&\leq \sum_{p = k+1}^{\overline m} (\frac{\alpha}{\beta} p-k) n_p
-%\leq \sum_{p = 0}^k (k - \frac{\alpha}{\beta} p)n_p \\
-%&\leq k \sum_{p = 0}^k n_p 
-%\leq k(1-\frac{\alpha}{\beta})n_k + k|\mathcal{H}|(k-1){ \overline m \choose k-1}
-%\end{align*}
-
-%[Shit, we need $\alpha = \beta$.] Therefore, no more than $q$ vectors $\mathbf{\overline x}_i$ are \emph{not} $k$-sparse.
-Since for every $S \in \mathcal{H}$ there are over $(k-1){\overline m \choose k} + q$ vectors $\mathbf{x}_i$ supported there, it follows that more than $(k-1){\overline m \choose k}$ of them have corresponding $\mathbf{\overline x}_i$ that are $k$-sparse.
-The result now follows directly from Thm.~\ref{DeterministicUniquenessCorollary}.
-%\end{proof}
-
-%\pagebreak
-
-%\begin{corollary}\label{SLCoptL1}
-%If all of the assumptions of Thm.\ref{DeterministicUniquenessTheorem} hold, only now with more than $(k-1)\left[ {\overline m \choose k} + |\mathcal{H}|k{\overline m \choose k-1}\right]$ vectors $\mathbf{x}_i$ supported in each $S \in \mathcal{H}$, then every solution to Prob.~\ref{OptimizationProblemL1} for which the average absolute nonzero coefficient of the $\mathbf{\overline x}_i$ is bounded below by that of the $\mathbf{x}_i$ necessarily satisfies the implications \eqref{Cstable} and \eqref{b-PDa} of Thm.~\ref{DeterministicUniquenessTheorem}.
-%\end{corollary}
-
-%\begin{proof}[Proof of Cor.~\ref{SLCoptL1}]
-%Since the average absolute nonzero coefficient of the $\mathbf{x}_i$ is given by $\alpha = \sum_i \|\mathbf{x}_i\|_1 / \sum_i \|\mathbf{x}_i\|_0$, we have:
-%\begin{align*}
-%\alpha \sum_i \|\mathbf{\overline x}_i\|_0 \leq \sum_i \|\mathbf{\overline x}_i\|_1 \leq \sum_i \|\mathbf{x}_i\|_1 = \alpha \sum_i \|\mathbf{x}_i\|_0.
-%\end{align*}
-%
-%and the result follows by the same arguments as in the proof of Cor.~\ref{SLCopt}.
-%\end{proof}
-
-\end{document}
+\begin{figure}\label{reasonableC2}
+\begin{center}
+\includegraphics[width=1 \linewidth]{figures/C2_m36_nt1000.pdf}
+\caption{The constant $C_2(\mathbf{A}, \mathcal{H})$ computed for generic unit-norm matrices $\mathbf{A} \in \mathbb{R}^{n \times m}$ and the hypergraph $\mathcal{H}$ consisting of the rows and columns formed by arranging  the elements of $[m]$ into a square grid.
+The results suggest that the bound is typically concentrated around a reasonable value.}
+\vspace{-.6 cm}
+\label{samples_vs_m}
+\end{center}
+\end{figure}

### 2020-07-16 manuscripts/thesis/introduction.tex
thesis

--- 2019-05-10 manuscripts/IEEE/final_submission.tex
@@
-% TODO: 
-% Make L_H a definition..? Change def of L to be 1-norm so we don't need these sqrt k's?
-% C_1 depends on J in Thm 1
-% also in proof of (7) x need not be *any* 2k-sparse vector...can instead restrict to some H...then 2k is restricted to half being on H.
+\section{Introduction}\label{Intro}
 
-% Notes:
-%
-% Can we prove in a line or two that the inverse problem is stable by arguing that the function is bijective and closed therefore a homeomorphism?
-% Should we mention the notion of Grassmannian manifolds and that Theta is a metric on this space?
-% Change robustness to stability?
-%
-\documentclass[journal, twocolumn]{IEEEtran}
+\begin{itemize}
+\item Background to the topic.
+\item Brief review of current knowledge.
+\item Indicate the gap in knowledge. State the aim of the research and how it fits into the gap.
+\item Can include an outline of what follows.
+\end{itemize}
 
-% *** MATH PACKAGES ***
-\usepackage{amsmath, amssymb, amsthm} 
-\newtheorem{theorem}{Theorem}
-\newtheorem{lemma}{Lemma}
-\newtheorem{conjecture}{Conjecture}
-\newtheorem{problem}{Problem}
-\newtheorem{question}{Question}
-\newtheorem{proposition}{Proposition}
-\newtheorem{definition}{Definition}
-\newtheorem{corollary}{Corollary}
-\newtheorem{remark}{Remark}
-\newtheorem{example}{Example}
+%Why do neuroscientists care about dictionary learning?
 
-\usepackage[pdftex]{graphicx}
-
-% *** ALIGNMENT PACKAGES ***
-\usepackage{array}
-\usepackage{cite}
-\usepackage{bm}
-
-% correct bad hyphenation here
-%\hyphenation{op-tical net-works semi-conduc-tor}
-
-\begin{document}
-
-%\title{When can a generating dictionary and sparse codes be recovered from noisy data?}
-%\title{When is the dictionary learning problem well-posed?}
-\title{On the uniqueness and stability of dictionaries \\ for sparse representation of noisy signals}
-%\title{When is the dictionary learning problem for sparse coding well-posed?}
-%\title{When is the sparsest representation unique?}
-%\title{When are sparse codes identifiable from their unknown noisy compressive measurements?}
-% FRITZ2: The title doesn't reflect the amount of new stuff, it seems incremental from the last one. It's not very meaningful.
-% FRITZ: Not everyone knows what well-posed means. You should mention recovery from noisy data in the title.
-
-\author{Charles~J.~Garfinkle and Christopher~J.~Hillar \\
-Redwood Center for Theoretical Neuroscience, Berkeley, CA, USA
-%\thanks{%e-mails: cjg@berkeley.edu, chillar@msri.org.  
-%CG and CH supported, in part, by NSF grant IIS-1219212 and the Statistical and Applied Mathematical Sciences Institute, under NSF DMS-1127914.}
-}
-
-\maketitle
-
-% \keywords{Sparse coding, dictionary learning, matrix factorization, compressed sensing, inverse problems, blind source separation}
-
-\begin{abstract}
-%Learning optimal dictionaries for sparse coding has exposed characteristic sparse features of many natural signals.
-However, there are few universal conditions guaranteeing the stability of such features in the presence of noise.
-Here, we prove very generally that optimal dictionaries and sparse codes are unique up to measurement error for all diverse enough datasets generated by the sparse coding model.
-Applications are given to data analysis, engineering, and neuroscience.
-Learning optimal dictionaries for sparse coding has exposed characteristic sparse features of many natural signals.
-However, universal guarantees of the stability of such features in the presence of noise are lacking.
-Here, we provide very general conditions guaranteeing when dictionaries yielding the sparsest encodings are unique and stable with respect to measurement or modeling error.
-We demonstrate that some or all original dictionary elements are recoverable from noisy data even if the dictionary fails to satisfy the spark condition, its size is overestimated, or only a polynomial number of distinct sparse supports appear in the data.
-Importantly, we derive these guarantees without requiring any constraints on the recovered dictionary beyond a natural upper bound on its size.
-Our results also yield an effective procedure sufficient to affirm if a proposed solution to the dictionary learning problem is unique within bounds commensurate with the noise.
-We suggest applications to data analysis, engineering, and neuroscience and close with some remaining challenges left open by our work.
-\end{abstract}
-
-% Optional adjustment to line up main text (after abstract) of first page with line numbers, when using both lineno and twocolumn options.
-% You should only change this length when you've finalised the article contents.
-
-\section{Introduction}\label{Intro}
-\IEEEPARstart{S}{parse} coding is a common modern approach to pattern analysis in signal processing whereby each of $N$ observed $n$-dimensional signal samples is viewed as a (noisy) linear combination of at most $k$ elementary waveforms drawn from some unknown ``dictionary" of size $m \ll N$ (see \cite{Zhang15} for a comprehensive review).
+Sparse coding is a common modern approach to pattern analysis in signal processing whereby each of $N$ observed $n$-dimensional signal samples is viewed as a (noisy) linear combination of at most $k$ elementary waveforms drawn from some unknown ``dictionary" of size $m \ll N$ (see \cite{Zhang15} for a comprehensive review).
 %\IEEEPARstart{A}{}common modern approach to pattern analysis in signal processing is to view each of $N$ observed $n$-dimensional signal samples as a (noisy) linear combination of at most $k$ elementary waveforms drawn from some unknown ``dictionary" of size $m \ll N$ (see \cite{Zhang15} for a comprehensive review).
@@
 To our knowledge, a universal guarantee of the uniqueness and stability of learned dictionaries and the sparse representations they induce over noisy data has yet to appear in the literature.
-% in justifying the identification of forged paintings by their anomalous sparse representations \cite{hughes2010},
 
@@
 %The Appendix contains a proof of Lem.~\ref{MainLemma}.
-
-\section{Results}\label{Results}
-
-%Denote by $\mathbf{x}^J$ the subvector formed from the entries of $\mathbf{x}$ indexed by $J$. 
-%A set of $k$-sparse vectors is said to be in \emph{general linear position} when any $k$ of them are linearly independent.
-
-Precise statements of our results require that we first identify some combinatorial criteria on the supports\footnote{Recall that a vector $\mathbf{x}$ is said to be \emph{supported} in $S$ when $\mathbf{x} \in \text{\rm span}\{\mathbf{e}_j: j\in S\}$, with $\mathbf{e}_j$ forming the standard column basis.} of sparse vectors.
-Let $\{1, \ldots, m\}$ be denoted $[m]$, its power set $2^{[m]}$, and ${[m] \choose k}$ the set of subsets of $[m]$ of size $k$.
-A \emph{hypergraph} on vertices $[m]$  is simply any subset $\mathcal{H} \subseteq 2^{[m]}$.
-We say that $\mathcal{H}$ is \textit{$k$-uniform} when $\mathcal{H} \subseteq {[m] \choose k}$.
-The \emph{degree} $\deg_\mathcal{H}(i)$ of a node $i \in [m]$ is the number of sets in $\mathcal{H}$ that contain $i$, and we say $\mathcal{H}$ is \emph{regular} when for some $r$ we have $\deg_\mathcal{H}(i) = r$ for all $i$ (given such an $r$, we say $\mathcal{H}$ is \textit{$r$-regular}).
-We also write $2\mathcal{H} := \{ S \cup S': S, S' \in \mathcal{H}\}$.
-The following class of structured hypergraphs is a key ingredient in this work.
-
-\begin{definition}\label{sip}
-Given $\mathcal{H} \subseteq 2^{[m]}$, the \textbf{star} $\sigma(i)$ is the collection of sets in $\mathcal{H}$ containing $i$.
-We say $\mathcal{H}$ has the \textbf{singleton intersection property} (\textbf{SIP}) when $\cap \sigma(i) = \{i\}$ for all $i \in [m]$.
-\end{definition}
-
-We next give a quantitative generalization of the spark condition (\ref{SparkCondition}) to combinatorial subsets of supports.
-The \emph{lower bound} of an $n \times m$ matrix $\mathbf{M}$ is the largest $\alpha$ with \mbox{$\|\mathbf{M}\mathbf{x}\|_2 \geq \alpha\|\mathbf{x}\|_2$} for all $\mathbf{x} \in \mathbb{R}^m$ \cite{Grcar10}.
-By compactness of the unit sphere, every injective linear map has a positive lower bound; hence, if $\mathbf{M}$ satisfies \eqref{SparkCondition}, then submatrices formed from $2k$ of its columns or less have strictly positive lower bounds.
-
-The lower bound of a matrix is generalized below in (\ref{Ldef}) by restricting it to the spans of certain submatrices\footnote{See \cite{vidal2005generalized} for an overview of the related ``union of subspaces" model.} associated with a hypergraph $\mathcal{H} \subseteq {[m] \choose k}$ of column indices.
-Let $\mathbf{M}_S$ denote the submatrix formed by the columns of a matrix $\mathbf{M}$ indexed by $S \subseteq [m]$ (setting $\mathbf{M}_\emptyset := \mathbf{0}$).
-In the sections that follow, we shall also let $\bm{\mathcal{M}}_S$ denote the column-span of a submatrix $\mathbf{M}_S$, and $\bm{\mathcal{M}}_\mathcal{G}$ to denote $\{\bm{\mathcal{M}}_S\}_{S \in \mathcal{G}}$.
-We define:  % Define $L_\mathcal{H}(\mathbf{M})$ as follows:
-%\begin{align*} 
-%L_\mathcal{H}(\mathbf{M}) := \min \left\{ \frac{ \|\mathbf{M}(\mathbf{x}_1-\mathbf{x}_2)\|_2 }{ \sqrt{2k} \|\mathbf{x}_1-\mathbf{x}_2\|_2} : \mathbf{x}_1, \mathbf{x}_2 \in \cup_{S \in \mathcal{H}} \bm{\mathcal{M}}_S \right\},
-%\end{align*} 
-%
-%where we write $L_{2k}$ in place of $L_\mathcal{H}$ when $\mathcal{H} = {[m] \choose k}$.
-Note that if $\mathcal{H}$ covers $[m]$, then $L_2 > L_\mathcal{H}$.\footnote{The reader should beware that $L_2 = L_{[m]}$, whereas $L = L_{\{[m]\}}$.
-For even $k$, the quantity $1 - \sqrt{k} L_k(\mathbf{M})$ is also known in the compressed sensing literature as the (asymmetric) lower restricted isometry constant \cite{Blanchard2011}.} Clearly, for any $\mathbf{M}$ satisfying \eqref{SparkCondition}, we have $L_{k'}(\mathbf{M}) > 0$ for  $k' \leq 2k$.
-%\begin{align*}
-%L_\mathcal{H}(\mathbf{M}) := \min \left\{ \frac{ \|\mathbf{M}_S\mathbf{x}\|_2 }{ \sqrt{k} \|\mathbf{x}\|_2} : S \in \mathcal{H} \right\},
-%\end{align*} 
-%\begin{align*}
-%L_\mathcal{H}(\mathbf{M}) := \max \left\{ \ falpha: \|\mathbf{M}_S\mathbf{x}\|_2 \geq \alpha \sqrt{k} \|\mathbf{x}\|_2 : S \in \mathcal{H}, \ \ \mathbf{x} \in \mathbb{R}^m \right\},
-%\end{align*} 
-\begin{align}\label{Ldef}
-L_\mathcal{H}(\mathbf{M}) := \min \left\{ \frac{\|\mathbf{M}_S\mathbf{x}\|_2}{ \sqrt{k} \|\mathbf{x}\|_2} : S \in \mathcal{H}, \ \mathbf{0} \neq \mathbf{x} \in \mathbb{R}^{|S|} \right\},
-\end{align} 
-%
-writing also $L_{k}$ in place of $L_\mathcal{H}$ when $\mathcal{H} = {[m] \choose k}$.\footnote{In compressed sensing literature, \mbox{$1 - \sqrt{k} L_k(\mathbf{M})$}  is the asymmetric lower restricted isometry constant for $\mathbf{M}$ with unit $\ell_2$-norm columns \cite{Blanchard2011}.}  As explained above, compactness implies that $L_{2k}(\mathbf{M}) > 0$ for all $\mathbf{M}$ satisfying \eqref{SparkCondition}.
-Clearly, $L_{\mathcal{H}'}(\mathbf{M}) \geq L_\mathcal{H}(\mathbf{M})$ whenever $\mathcal{H}' \subseteq \mathcal{H}$, and similarly any $k$-uniform $\mathcal{H}$ satisfying $\cup \mathcal{H} = [m]$ has $L_2 \geq L_{2\mathcal{H}} \geq L_{2k}$ (letting $L_{2k}$ := $L_m$ whenever $2k > m$).
-
-We are now in a position to state our main result, though for expository purposes we leave the quantity $C_1$ %(a function of $\mathbf{A}$, $\mathbf{x}_1, \ldots, \mathbf{x}_N$, and $\mathcal{H}$) 
-undefined until Sec.~\ref{DUT}. All results  below assume real matrices and vectors.
-
-%eps-tightness COUNTER-EXAMPLE:
-%Consider the alternate dictionary $B = \left(\mathbf{0}, \frac{1}{2}(\mathbf{e}_1 + \mathbf{e}_2), \mathbf{e}_3, \ldots, \mathbf{e}_{m} \right)$ and sparse codes $\mathbf{b}_i = \mathbf{e}_2$ for $i = 1, 2$ and $\mathbf{b}_i = \mathbf{e}_i$ for $i = 3, \ldots, m$.
-Then $|A\mathbf{a}_i - B\mathbf{b}_i| = 1/\sqrt{2}$ for $i = 1, 2$ (and $0$ otherwise).
-If there were permutation and invertible diagonal matrices $P \in \mathbb{R}^{m \times m}$ and $D \in \mathbb{R}^{m \times m}$ such that $|(A-BPD)\mathbf{e}_i| \leq C\varepsilon$ for all $i \in [m]$, then we would reach the contradiction $1 = |P^{-1}\mathbf{e}_1|_2 = |(A-BPD)P^{-1}\mathbf{e}_1|_2 \leq 1/\sqrt{2}$.
-
-\begin{theorem}\label{DeterministicUniquenessTheorem}
-%Fix integers $n, k, m$ and $\overline m$. 
-If an $n \times m$ matrix $\mathbf{A}$ satisfies $L_{2\mathcal{H}}(\mathbf{A}) > 0$ for some $r$-regular $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP, and $k$-sparse \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} include more than $(k-1){\overline m \choose k}$ vectors in general linear position\footnote{Recall that a set of vectors sharing support $S$ are in \emph{general linear position} when any $|S|$ of them are linearly independent.} supported in each $S \in \mathcal{H}$, then the following recovery guarantees hold for $C_1 > 0$ given by \eqref{Cdef1}.
-
-\textbf{Dictionary Recovery:} Fix $\varepsilon < L_{2}(\mathbf{A}) / C_1$.\footnote{Note that the condition $\varepsilon < L_2(\mathbf{A}) /C_1$ is necessary; otherwise, with \mbox{$\mathbf{A}$ = $\mathbf{I}$} (the identity matrix) and $\mathbf{x}_i = \mathbf{e}_i$, the matrix $\mathbf{B} = \left[\mathbf{0}, \frac{1}{2}(\mathbf{e}_1 + \mathbf{e}_2), \mathbf{e}_3, \ldots, \mathbf{e}_{m} \right]$ and sparse codes $\mathbf{\overline x}_i = \mathbf{e}_2$ for $i = 1, 2$ and $\mathbf{\overline x}_i = \mathbf{e}_i$ for $i \geq 3$ satisfy $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline x}_i \|_2 \leq \varepsilon$ but nonetheless violate \eqref{Cstable}.} If an $n \times \overline m$ matrix $\mathbf{B}$ has, for every $i \in [N]$, an associated $k$-sparse $\mathbf{\overline x}_i$ satisfying \mbox{$\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \varepsilon$}, then $\overline m \geq m$, and provided that $\overline m (r-1) < mr$, there is a permutation matrix $\mathbf{P}$ and an invertible diagonal matrix $\mathbf{D}$ such that:
-\begin{align}\label{Cstable}
-\|\mathbf{A}_j- (\mathbf{BPD})_j\|_2 \leq C_1 \varepsilon, \ \ \text{for all } j \in J,
-\end{align}
-%
-for some $J \subseteq [m]$ of size \mbox{$m - (r-1)(\overline m - m)$}. 
-% $\overline m - r(\overline m - m)$
-
-\textbf{Code Recovery:} If, moreover, $\mathbf{A}_J$ satisfies \eqref{SparkCondition} and $\varepsilon < L_{2k}(\mathbf{A}_J) / C_1$, then $(\mathbf{BP})_J$ also satisfies \eqref{SparkCondition} with $L_{2k}(\mathbf{BP}_J) \geq (L_{2k}(\mathbf{A}_J) - C_1 \varepsilon) / \|\mathbf{D}_J\|_1$, and for all $i \in [N]$:
-\begin{align}\label{b-PDa}
-%\|\mathbf{x}^J_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}^{\overline J}_i\|_1 &\leq  \left( \frac{ 1+C_1 \|\mathbf{x}^{J}_i\|_1 }{ L_{2k}(\mathbf{A}) -  C_1\varepsilon } \right) \varepsilon \ \  \text{for $i \in [N]$}.
-\|(\mathbf{x}_i)_J - (\mathbf{D}^{-1}\mathbf{P}^{\top} \mathbf{\overline x}_i)_J\|_1 &\leq  \left( \frac{ 1+C_1 \|(\mathbf{x}_i)_J\|_1 }{ L_{2k}(\mathbf{A}_J) -  C_1\varepsilon } \right) \varepsilon,
-\end{align}
-%
-where subscript $(\cdot)_J$ here represents the subvector formed from restricting to coordinates indexed by $J$.
-\end{theorem}
-
-%We delay defining the explicit constant $C_1$ until Section \ref{DUT} (\eqref{Cdef1}).
-%To be clear, the implication of Thm.~\ref{DeterministicUniquenessTheorem} is that $Y = \{\mathbf{Ax}_1, \ldots, \mathbf{Ax}_N\}$ has a stable $k$-sparse representation in $\mathbb{R}^m$, with \eqref{def1} guaranteed provided $\varepsilon$ in Def.~\ref{maindef} does not exceed:
-In words, Thm.~\ref{DeterministicUniquenessTheorem} says that the smaller the regularity $r$ of the original support hypergraph $\mathcal{H}$ or the difference $\overline m - m$ between the assumed and actual number of elements in the latent dictionary, the more columns and coefficients of the original dictionary $\mathbf{A}$ and sparse codes $\mathbf{x}_i$ are guaranteed to be contained (up to noise) in the appropriately labelled and scaled recovered dictionary $\mathbf{B}$ and codes $\mathbf{\overline x}_i$, respectively.
-
-In the important special case when $\overline m = m$, the theorem directly implies that  $Y = \{\mathbf{Ax}_1, \ldots, \mathbf{Ax}_N\}$ has a stable $k$-sparse representation in $\mathbb{R}^m$, with inequalities \eqref{def1} guaranteed in Def.~\ref{maindef} for the following worst-case error $\varepsilon$:
-\begin{align}\label{epsdel}
-\varepsilon(\delta_1, \delta_2) := \min \left\{ \frac{\delta_1}{ C_1 }, \frac{ \delta_2 L_{2k}(\mathbf{A})}{ 1 + C_1 \left( \delta_2 + \max_{i \in [N]} \|\mathbf{x}_i\|_1  \right) } \right\}.
-\end{align}
-
-Since sparse codes in general linear position are straightforward to produce with a ``Vandermonde''  construction (i.e., by choosing columns of the matrix $[\gamma_{i}^j]_{i,j=1}^{k,N}$, for distinct nonzero $\gamma_i$), we have the following direct consequence of Thm.~\ref{DeterministicUniquenessTheorem}.
-
-\begin{corollary}\label{DeterministicUniquenessCorollary}
-Given any regular hypergraph $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP, there are $N =  |\mathcal{H}| \left[ (k-1){m \choose k} + 1  \right]$ vectors \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} such that every matrix $\mathbf{A}$ satisfying spark condition \eqref{SparkCondition} generates $Y = \{\mathbf{A}\mathbf{x}_1, \ldots, \mathbf{A}\mathbf{x}_N\}$ with a stable $k$-sparse representation in $\mathbb{R}^m$ for $\varepsilon(\delta_1,\delta_2)$ given by \eqref{epsdel}.
-\end{corollary}
-
-% prev
-%\begin{corollary}\label{DeterministicUniquenessCorollary}
-%Given any regular hypergraph $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP, there are $N =  |\mathcal{H}| \left[ (k-1){m \choose k} + 1  \right]$ vectors \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} such that every matrix $\mathbf{A}$ with $L_{2\mathcal{H}}(\mathbf{A}) > 0$ generates a dataset $Y = \{\mathbf{A}\mathbf{x}_1, \ldots, \mathbf{A}\mathbf{x}_N\}$ with a stable $k$-sparse representation in $\mathbb{R}^m$ for $\varepsilon(\delta_1,\delta_2)$ as in \eqref{epsdel}.
-%\end{corollary}
-
-%We claim that the assumptions of Thm.~\ref{DeterministicUniquenessTheorem} are easily met with deterministic constructions.
-In particular, sparse codes in general linear position are straightforward to produce using a ``Vandermonde'' matrix construction (i.e.
-use the columns of the matrix $[\gamma_{i}^j]_{i,j=1}^{k,N}$, for distinct nonzero $\gamma_i$).
-%
-
-% (Prob.~\ref{InverseProblem}).
-%=======
-%An immediate practical implication of this result is that there exists a practical procedure to affirm if one's proposed solution $(\mathbf{B}, \mathbf{\overline x}_1, \ldots, \mathbf{x}_N)$ to Prob.~\ref{InverseProblem} is indeed unique (up to noise and inherent ambiguities): simply check that $\mathbf{B}$ and the $\mathbf{\overline x}_i$ satisfy the assumptions on $\mathbf{A}$ and the $\mathbf{x}_i$ in Thm.~\ref{DeterministicUniquenessTheorem}.
-%
-%%In fact, a more general result (stated clearly in the next section) can be gleaned from our method of proving Thm.~\ref{DeterministicUniquenessTheorem}.
-Briefly, in cases where $\mathbf{B}$ has $\overline m \neq m$ columns, or $\mathcal{H}$ is not regular or only partially satisfying the SIP, a relation between $\overline m$ and the degree sequence of nodes in $\mathcal{H}$ gives indices $J \subseteq [m]$ defining a submatrix $\mathbf{A}_J$ and subvectors $\mathbf{x}_i^J$ that are recoverable in the sense of \eqref{Cstable} and \eqref{b-PDa}.
-For example, if $\mathcal{H}$ is $\ell$-regular with the SIP but $m \leq \overline m < m\ell/(\ell - 1)$ then we have nonzero $|J| = \overline m - \ell(\overline m - m)$.
-The implication here is that the smaller the difference $\overline m - m$, the more columns and code entries of the original $n \times m$ dictionary $\mathbf{A}$ and codes $\mathbf{x}_i$ contained (up to noise) in the appropriately scaled $n \times \overline m$ dictionary $\mathbf{B}$ and codes $\mathbf{\overline x}_i$.
-When $\overline m = m$, we recover Thm.~\ref{DeterministicUniquenessTheorem}.
-%
-%%In fact, even if $\mathcal{H}$ is not regular or only partially satisfies the SIP, a relation between $\overline m$ and the degree sequence of nodes in $\mathcal{H}$ may give the indices $J \subseteq [m]$.
-For sake of brevity, we delay to the next section a clear statement of this more general result.
-%
-%Regarding the assumptions of Thm.~\ref{DeterministicUniquenessTheorem}, it so happens that sparse codes $\mathbf{x}_i$ in general linear position are straightforward to produce with a ``Vandermonde'' matrix construction \cite{Hillar15}, leading to the following.
-%>>>>>>> d1407a275dc391dabad7bb62d3e659f9a4ac4624
-
-% Needs to be L_{2k}(A) > 0 to guarantee sparse vector recovery
-
-%We also have the following refinement of a result in \cite{Hillar15}:
-%\begin{corollary}
-%Those square matrices $\mathbf{A}$ that satisfy \mbox{$L_{2\mathcal{H}}(\mathbf{A}) > 0$} for some regular $k$-uniform hypergraph $\mathcal{H}$ with the SIP and have the property that $\mathbf{Ax}$ is $k$-sparse for all $k$-sparse $\mathbf{x}$ with support in $\mathcal{H}$ are the matrices $\mathbf{PD}$, where $\mathbf{P}$ and $\mathbf{D}$ run over permutation and invertible diagonal matrices, respectively.
-%\end{corollary}
-
-One can easily verify that for every $k < m$ there are regular $k$-uniform hypergraphs $\mathcal{H}$ with the SIP besides the obvious $\mathcal{H} = {[m] \choose k}$.
-For instance, take $\mathcal{H}$ to be the $k$-regular set of consecutive intervals of length $k$ in some cyclic order on $[m]$.
-In this case, a direct consequence of Cor.~\ref{DeterministicUniquenessCorollary} is rigorous verification of the lower bound \mbox{$N = m(k-1){m \choose k} + m$} for sufficient sample size from the introduction.
-Special cases allow for even smaller hypergraphs.
-For example, if $k = \sqrt{m}$, then a 2-regular $k$-uniform hypergraph with the SIP can be constructed as the $2k$ rows and columns formed by arranging the elements of $[m]$ into a square grid.
-
-%\cite{li2004analysis, Georgiev05, Aharon06, Hillar15}
-We should stress here that framing the problem in terms of hypergraphs has allowed us to show, unlike in previous research on the subject, that the matrix $\mathbf{A}$ need not necessarily satisfy \eqref{SparkCondition} to be recoverable from data.
-As an example, let $\mathbf{A} = [ \mathbf{e}_1, \ldots, \mathbf{e}_5, \mathbf{v}]$ with $\mathbf{v} = \mathbf{e}_1 + \mathbf{e}_3 + \mathbf{e}_5$ and take $\mathcal{H}$ to be all consecutive pairs of indices $1, \ldots ,6$ arranged in cyclic order.
-Then for $k=2$, the matrix $\mathbf{A}$ fails to satisfy \eqref{SparkCondition} while still obeying the assumptions of Thm.~\ref{DeterministicUniquenessTheorem} for dictionary recovery.%, hence guaranteeing \eqref{Cstable} .
-%(since $\{ \mathbf{A}_1, \mathbf{A}_3, \mathbf{A}_5, \mathbf{A}_6\}$ is not a linearly independent set).
-%This weakening allows for a practical (polynomial) amount of data to still guarantee a stable dictionary in the case where the set of sparse supports for the $\mathbf{\overline x}_i$ is known to have a size that grows polynomially in $m$ and $k$.
-
-A practical implication of Thm.~\ref{DeterministicUniquenessTheorem} is the following: there is an effective procedure sufficient to affirm if a proposed solution to Prob.~\ref{InverseProblem} is indeed unique (up to noise and inherent ambiguities).
-One need simply check that the matrix and codes satisfy the (computable) assumptions of Thm.~\ref{DeterministicUniquenessTheorem} on $\mathbf{A}$ and the $\mathbf{x}_i$.
-In general, however, there is no known efficient procedure.
-We defer a brief discussion on this point to the next section.
-%Another practical implication of Thm.\ref{DeterministicUniquenessTheorem} is the following: there is an effective procedure sufficient to affirm if a proposed solution $(\mathbf{B}, \mathbf{\overline x}_1, \ldots, \mathbf{x}_N)$ to Prob.~\ref{InverseProblem} is indeed unique (up to noise and inherent ambiguities).
-One simply checks that $\mathbf{B}$ and the $\mathbf{\overline x}_i$ satisfy the respective assumptions of Thm.~\ref{DeterministicUniquenessTheorem}.
-%. on $\mathbf{A}$ and the $\mathbf{x}_i$, respectively.
-
-%In fact, a more general result (stated clearly in the next section) can be gleaned from our method of proving Thm.~\ref{DeterministicUniquenessTheorem}.
-Briefly, in cases where $\mathbf{B}$ has $\overline m \neq m$ columns, or $\mathcal{H}$ is not regular or only partially satisfying the SIP, a relation between $\overline m$ and the degree sequence of nodes in $\mathcal{H}$ gives indices $J \subseteq [m]$ defining a submatrix $\mathbf{A}_J$ and subvectors $\mathbf{x}_i^J$ that are recoverable in the sense of \eqref{Cstable} and \eqref{b-PDa}.
-For example, if $\mathcal{H}$ is $\ell$-regular with the SIP but $m \leq \overline m < m\ell/(\ell - 1)$ then we have nonzero $|J| = \overline m - \ell(\overline m - m)$.
-The implication here is that the smaller the difference $\overline m - m$, the more columns and code entries of the original $n \times m$ dictionary $\mathbf{A}$ and codes $\mathbf{x}_i$ contained (up to noise) in the appropriately scaled $n \times \overline m$ dictionary $\mathbf{B}$ and codes $\mathbf{\overline x}_i$.
-When $\overline m = m$, we recover Thm.~\ref{DeterministicUniquenessTheorem}.
-
-%In fact, even if $\mathcal{H}$ is not regular or only partially satisfies the SIP, a relation between $\overline m$ and the degree sequence of nodes in $\mathcal{H}$ may give the indices $J \subseteq [m]$.
-For sake of brevity, we delay to the next section a clear statement of this more general result.
-
-%=======
-%One can also verify that for every $k < m$, there is a regular $k$-uniform hypergraph that satisfies the SIP; for instance, take $\mathcal{H}$ to be the consecutive intervals of length $k$ in some cyclic order on $[m]$, for which Cor.~\ref{DeterministicUniquenessCorollary} implies the lower bound for sample size $N$ from the introduction.
-In many cases, however, the SIP is achievable with far fewer supports; for example, when $k = \sqrt{m}$, take $\mathcal{H}$ to be the $2k$ rows and columns formed by arranging $[m]$ in a square grid.
-%>>>>>>> d1407a275dc391dabad7bb62d3e659f9a4ac4624
-
-%As mentioned above, there exist $k$-uniform regular hypergraphs $\mathcal{H}$ with the SIP having cardinality $|\mathcal{H}| = m$,
-
-A less direct consequence of Thm.~\ref{DeterministicUniquenessTheorem} is the following uniqueness and stability guarantee for solutions to Prob.~\ref{SLCopt}.
-%, the usual optimization problem of interest for those applying dictionary learning to their data.
-
-\begin{theorem}\label{SLCopt}
-Fix a matrix $\mathbf{A}$ and vectors $\mathbf{x}_i$ satisfying the assumptions of Thm.~\ref{DeterministicUniquenessTheorem}, only now with over \mbox{$(k-1)\left[ {\overline m \choose k} + |\mathcal{H}|k{\overline m \choose k-1}\right]$} vectors supported in general linear position in each $S \in \mathcal{H}$.
-Every solution to Prob.~\ref{OptimizationProblem} (with $\eta = \varepsilon/2$) satisfies recovery guarantees \eqref{Cstable} and \eqref{b-PDa} when the corresponding bounds on $\eta$ are met.
-\end{theorem}
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=.24 \linewidth]{figs/basis.png}
-% \includegraphics[width=.25 \linewidth]{figs/Ahat_FastICA_M640_K8_noise0_2042}
-%\includegraphics[width=.24 \linewidth]{figs/Ahat_FastICA_M640_K8_noise0_4083.png}
-\includegraphics[width=.24 \linewidth]{figs/Ahat_FastICA_M640_K8_noise1_0205.png}
-\includegraphics[width=.24 \linewidth]{figs/Ahat_FastICA_M640_K8_noise2_0409.png}
-\includegraphics[width=.24 \linewidth]{figs/Ahat_FastICA_M640_K8_noise5_1021.png}
-\caption{\textbf{Learning a dictionary from increasingly noisy data}.
-The (unraveled) basis elements of the $8 \times 8$ discrete cosine transform (DCT) form the 64 columns of the left-most matrix above.
-Three increasingly imprecise dictionaries (columns reordered to best match original) are recovered by FastICA \cite{hyvarinen2000independent} trained on data generated from $8$-sparse linear combinations of DCT elements corrupted with additive noise (increasing from left to right).}
-\vspace{-.6 cm}
-\label{noisyrecovery}
-\end{center}
-\end{figure}
-
-Another extension of Thm.~\ref{DeterministicUniquenessTheorem} can be derived from the following algebraic characterization of the spark condition.
-Letting $\mathbf{A}$ be the $n \times m$ matrix of $nm$ indeterminates $A_{ij}$, the reader may work out why substituting real numbers for the $A_{ij}$ yields a matrix satisfying \eqref{SparkCondition} if and only if the following polynomial evaluates to a nonzero number:
-\begin{align*}
-f(\mathbf{A}) := \prod_{S \in {[m] \choose 2k}} \sum_{S' \in {[n] \choose 2k}} (\det \mathbf{A}_{S',S})^2,
-\end{align*}
-%
-where for any $S' \in {[n] \choose 2k}$ and $S \in {[m] \choose 2k}$, the symbol $\mathbf{A}_{S',S}$ denotes the submatrix of entries $A_{ij}$ with $(i,j) \in S' \times S$.\footnote{The large number of terms in this product is likely necessary given that deciding whether or not a matrix satisfies the spark condition is NP-hard \cite{tillmann2014computational}.}
-
-Since $f$ is analytic, having a single substitution of a real matrix $\mathbf{A}$ satisfying $f(\mathbf{A}) \neq 0$ implies that the zeroes of $f$ form a set of (Borel) measure zero.
-Such a matrix is easily constructed by adding rows of zeroes to a $\min(2k,m) \times m$ Vandermonde matrix as mentioned previously, so that every sum in the product defining $f$ above is strictly positive.
-Thus, almost every $n \times m$ matrix with $n \geq \min(2k,m)$ satisfies \eqref{SparkCondition}.
-
-%Another extension of Thm.~\ref{DeterministicUniquenessTheorem} arises from the following analytic characterization of the spark condition.
-Let $\mathbf{A}$  be the $n \times m$ matrix of $nm$ indeterminates $A_{ij}$.
-When real numbers are substituted for $A_{ij}$, the resulting matrix satisfies \eqref{SparkCondition} if and only if the following polynomial is nonzero:
-%\begin{align*}
-%f(\mathbf{A}) := \prod_{S \in {[m] \choose k}} \sum_{S' \in {[n] \choose k}} (\det \mathbf{A}_{S',S})^2,
-%\end{align*}
-%
-%where for any $S' \in {[n] \choose k}$ and $S \in {[m] \choose k}$, the symbol $\mathbf{A}_{S',S}$ denotes the submatrix of entries $A_{ij}$ with $(i,j) \in S' \times S$.
-We note that the large number of terms in this product is likely necessary due to the NP-hardness of deciding whether a given matrix $\mathbf{A}$ satisfies the spark condition \cite{tillmann2014computational}.
-
-%Since $f$ is analytic, having a single substitution of a real matrix $\mathbf{A}$ with $f(\mathbf{A}) \neq 0$ necessarily implies that the zeroes of $f$ form a set of measure zero.
-Fortunately, such a matrix $\mathbf{A}$ is easily constructed by adding rows of zeroes to any $\min(2k,m) \times m$ Vandermonde matrix as described above (so that each term in the product above for $f$ is nonzero).
-Hence, almost every $n \times m$ matrix with $n \geq \min(2k,m)$ satisfies \eqref{SparkCondition}.
-
-We claim that a similar phenomenon applies to datasets of vectors with a stable sparse representation.
-Briefly, following the same procedure as in \cite[Sec.~IV]{Hillar15}, for $k < m$ and $n \geq \min(2k, m)$, we may consider the ``symbolic'' dataset $Y = \{\mathbf{A}\mathbf{x}_1,\ldots,\mathbf{A} \mathbf{x}_N\}$ generated by an indeterminate $n \times m$ matrix $\mathbf{A}$ and $m$-dimensional $k$-sparse vectors $\mathbf{x}_1, \ldots, \mathbf{x}_N$ indeterminate within their supports, which form a regular hypergraph $\mathcal{H} \subseteq {[m] \choose k}$ satisfying the SIP.
-Restricting \mbox{$(k-1){m \choose k} + 1$} indeterminate $\mathbf{x}_i$ to each support in $\mathcal{H}$, and letting $\textbf{M}$ be the $n \times N$ matrix with columns $\mathbf{A}\mathbf{x}_i$, it can be checked that when $f(\mathbf{M}) \neq 0$ for a substitution of real numbers for the indeterminates, all of the assumptions on $\mathbf{A}$ and the $\mathbf{x}_i$ in Thm.~\ref{DeterministicUniquenessTheorem} are satisfied.
-We therefore have the following.
-% ; in particular, $\mathbf{A}$ satisfies \eqref{SparkCondition}
-
-\begin{theorem}\label{robustPolythm}
-%Let $\mathbf{A}$ and $\mathbf{x}_1, \ldots, \mathbf{x}_N$ be an indeterminate $n \times m$ matrix and sequence of $m$-dimensional vectors, respectively. 
-There is a polynomial in the entries of $\mathbf{A}$ and the $\mathbf{x}_i$ that evaluates to a nonzero number only when $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$.
-In particular, almost all substitutions impart to $Y$ this property.
-\end{theorem}
-
-%To extend this observation to arbitrary probability distributions, note that if a set of measure spaces $\{(X_{\ell}, \nu_{\ell})\}_{\ell=1}^p$ has measures $\nu_{\ell}$ absolutely continuous with respect to the standard Borel measure on $\mathbb{R}$ for all $\ell \in [p]$, then the product measure $\prod_{\ell=1}^p \nu_{\ell}$ is also absolutely continuous with respect to the standard Borel product measure on $\mathbb{R}^p$ (e.g., see \cite{folland2013real}).
-This fact combined with Thm.~\ref{robustPolythm} implies the following.
-To extend this observation to arbitrary probability distributions, note that if a set of $p$ measure spaces has all measures absolutely continuous with respect to the standard Borel measure on $\mathbb{R}$, then the product measure is also absolutely continuous with respect to the standard Borel product measure on $\mathbb{R}^p$ (e.g., see \cite{folland2013real}).
-This fact combined with Thm.~\ref{robustPolythm} implies the following.\footnote{We refer the reader to \cite{Hillar15} for a more detailed explanation of these arguments.}
-
-\begin{corollary}\label{ProbabilisticCor}
-If the indeterminate entries of $\mathbf{A}$ and the $\mathbf{x}_i$ are drawn independently from probability distributions absolutely continuous with respect to the standard Borel measure, then $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$ with probability one.
-\end{corollary}
-
-Thus, drawing the dictionary and supported sparse coefficients from any continuous probability distribution almost always generates data with a stable sparse representation.
-
-%\cite{rehnsommer2007, rozell2007neurally, ganguli2012compressed, hu2014hebbian}
-
-We close this section with some comments on the optimality of our results.
-The linear scaling for $\varepsilon$ in \eqref{epsdel} is essentially optimal (e.g., see \cite{arias2013fundamental}), but a basic open problem remains: how many samples are necessary to determine the sparse coding model?
-Our results demonstrate that sparse codes $\mathbf{x}_i$ drawn from only a polynomial number of $k$-dimensional subspaces permit stable identification of the generating dictionary $\mathbf{A}$. 
-This lends some legitimacy to the use of the model in practice, where data in general are unlikely (if ever) to exhibit the exponentially many possible $k$-wise combinations of dictionary elements required by (to our knowledge) all previously published results.
-
-Consequently, if $k$ is held fixed or if the size of the support set of reconstructing codes is polynomial in $\overline m$ and $k$, then a practical (polynomial) amount of data suffices to identify the dictionary.\footnote{In the latter case, a reexamination of the pigeonholing argument in the proof of Thm.~\ref{DeterministicUniquenessTheorem} requires a polynomial number of samples distributed over a polynomial number of supports.} Reasons to be skeptical that this holds in general, however, can be found in \cite{tillmann2014computational, Tillmann15}.
-Even so, in the next section we discuss how probabilistic guarantees can in fact be made for any number of available samples.
-
-\section{Proofs}\label{DUT} % of Theorems~\ref{DeterministicUniquenessTheorem} and ~\ref{SLCopt}}\label{DUT}
-
-%%%%%%%%%%%%%%
-% need to cut maybe: 
-%As mentioned in the previous section, Thm.~\ref{DeterministicUniquenessTheorem} is a particular case of a more general result that forgoes the assumption that $\mathcal{H} \subseteq {[m] \choose k}$ is regular and satisfies the SIP.
-If instead we require only that the stars $\cap \sigma(i)$ intersect at singletons for all $i \leq q$ (assuming that the nodes of $\mathcal{H}$ are labeled in some order of non-increasing degree), we have that $\overline m \geq k|\mathcal{H}| / \deg(1)$ and, provided $\overline m < k|\mathcal{H}| / (\deg(1) - 1)$, the nonempty submatrix $J$ is of size equal to the largest number $p$ satisfying:
-%\begin{align}\label{pcond}
-%\sum_{i=\ell}^{m} \deg(i) > (\overline m + 1 - \ell) (\deg(\ell) - 1) \ \ \text{for all } \ell \leq p \leq q.
-%\end{align}
-%Specifically, $J$ contains all nodes of degree exceeding $\deg(p)$ and some subset of those with degreee equal to $\deg(p)$.
-For the benefit of the reader, we do not prove explicitly this more general result below; it can be discerned from how exactly Lemma \ref{NonEmptyLemma} is incorporated into the proof of Lem.~\ref{MainLemma}.
-%%%%%%%%%%%%%%%%
-
-%As mentioned in the previous section, Thm.~\ref{DeterministicUniquenessTheorem} is a particular case of a more general result, which requires a looser set of constraints on the hypergraph $\mathcal{H}$ and which applies to $n \times \overline m$ matrices $\mathbf{B}$ (and $\overline m$-dimensional codes $\mathbf{\overline x}_i$) with $\overline m \neq m$:
-
-%Fix $\overline m$ and suppose the assumptions of Thm.~\ref{DeterministicUniquenessTheorem} hold, only now with the constraints on $\mathcal{H} \subseteq {[m] \choose k}$ being just that $|\cap H(i)| = 1$ for all $i \leq q$ (assuming w.l.o.g.
-that the nodes of $\mathcal{H}$ are labeled in some order of non-increasing degree), and with more than $(k-1){\overline m \choose k}$ vectors $\mathbf{x}_i$ supported in g.l.p.
-on each $S \in \mathcal{H}$.
-Then we must have $\overline m \geq k|\mathcal{H}| / \deg(1)$ and, provided $\overline m < k|\mathcal{H}| / (\deg(1) - 1)$, the guarantee \eqref{Cstable} holds for a submatrix $\mathbf{A}_J$, where $J \subseteq[m]$ is nonempty and of a size equal to the largest number $p$ satisfying:
-%\begin{align}\label{pcond}
-%\sum_{i=\ell}^{m} \deg(i) > (\overline m + 1 - \ell) (\deg(\ell) - 1) \ \ \text{for all } \ell \leq p \leq q.
-%\end{align}
-%Specifically, $J$ consists of the union of the set of all nodes of degree exceeding $\deg(p)$ and some subset of those nodes with degrees equal to $\deg(p)$.
-
-%For the benefit of the reader, we prove below the case where we forgo only the constraint that $\overline m = m$.
-This yields the implication $\overline m \geq m$ and \eqref{pcond} reduces to $|J| = \overline m - r(\overline m - m)$.
-The extension to the general result above can be seen by examining how exactly Lemma \ref{NonEmptyLemma} is incorporated into the overall proof.
-
-% ======== b - PDa =========
-
-% WITH EXPLICIT J SUBSCRIPT
-%We begin our proof of Thm.~\ref{DeterministicUniquenessTheorem} by showing how dictionary recovery \eqref{Cstable} already implies sparse code recovery \eqref{b-PDa} when $\mathbf{A}_J$ satisfies \eqref{SparkCondition} and \mbox{$\varepsilon < L_{2k}(\mathbf{A}_J) / C_1$}.
-%, assuming that $\overline m = m$ without loss of generality.
-%Consider any $2k$-sparse $\mathbf{x} \in \mathbb{R}^m$ and note that $\|\mathbf{x}\|_1 \leq \sqrt{2k}  \|\mathbf{x}\|_2$. By definition of $L_{2k}$ in \eqref{Ldef}, we have:
-%\begin{align}\label{stuff}
-%\|\mathbf{x}_J - &( \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x} )_J\|_1 \nonumber
-%\leq \frac{\|(\mathbf{BPD})_J(\mathbf{x}_J - (\mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x})_J)\|_2}{L_{2k}((\mathbf{BPD})_J)} \\ \nonumber
-%&\leq \frac{\|( (\mathbf{BPD})_J - \mathbf{A}_J) \mathbf{x}_J\|_2 + \|\mathbf{A}_J\mathbf{x}_J - \mathbf{B}_J\mathbf{\overline x}_J\|_2}{L_{2k}((\mathbf{BPD})_J)} \\
-%&\leq \frac{C_1\varepsilon \|\mathbf{x}_J\|_1 + \varepsilon}{L_{2k}((\mathbf{BPD})_J)},
-%\end{align}
-%where the term $C_1\varepsilon \|\mathbf{x}_J\|_1$ in the numerator above is a consequence of the triangle inequality applied to \eqref{Cstable}.
-
-%It remains for us to bound the denominator.  By the reverse triangle inequality:
-%\begin{align*}
-%\|(\mathbf{BPD})_J\mathbf{x}_J\|_2 
-%&\geq | \|\mathbf{A}_J\mathbf{x}_J\|_2 - \|(\mathbf{A}_J - (\mathbf{BPD})_J)\mathbf{x}_J\|_2 | \\
-%&\geq \sqrt{2k} (L_{2k}(\mathbf{A}_J) -  C_1\varepsilon) \|\mathbf{x}_J\|_2,
-%\end{align*}
-%
-%wherein removal of the absolute value is justified since $C_1\varepsilon < L_{2k}(\mathbf{A}_J)$.
-We therefore have that $L_{2k}((\mathbf{BPD})_J) \geq L_{2k}(\mathbf{A}_J) - C_1\varepsilon  > 0$, and \eqref{b-PDa} then follows from \eqref{stuff}.
-
-% WITHOUT J SUBSCRIPT
-We begin our proof of Thm.~\ref{DeterministicUniquenessTheorem} by showing how dictionary recovery \eqref{Cstable} already implies sparse code recovery \eqref{b-PDa} when $\mathbf{A}$ satisfies \eqref{SparkCondition} and \mbox{$\varepsilon < L_{2k}(\mathbf{A}) / C_1$}.
-We temporarily assume (without loss of generality) that $\overline m = m$, so as to omit an otherwise requisite subscript $(\cdot)_J$ around certain matrices and vectors.
-By definition of $L_{2k}$ in \eqref{Ldef}, and noting that $\sqrt{k} \|\mathbf{v}\|_2 \geq \|\mathbf{v}\|_1$ for $k$-sparse $\mathbf{v}$, we have for all $i \in [N[$:
-\begin{align}\label{stuff}
-\|\mathbf{x}_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_i \|_1 \nonumber
-&\leq \frac{\|\mathbf{BPD}(\mathbf{x}_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_i)\|_2}{L_{2k}(\mathbf{BPD})} \\ \nonumber
-&\leq \frac{\|( \mathbf{BPD} - \mathbf{A}) \mathbf{x}_i\|_2 + \|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline x}_i\|_2}{L_{2k}(\mathbf{BPD})} \\
-&\leq \frac{C_1\varepsilon \|\mathbf{x}_i\|_1 + \varepsilon}{L_{2k}(\mathbf{BPD})},
-\end{align}
-%\begin{align}\label{stuff}
-%\frac{ \|\mathbf{x} - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x} \|_1 } { \|\mathbf{D}^{-1}\|_1 }  \
-%&\leq \|\mathbf{Dx} - \mathbf{P}^{\top}\mathbf{\overline x} \|_1 \\ \nonumber
-%&\leq \frac{\|\mathbf{BP}(\mathbf{D}\mathbf{x} - \mathbf{P}^{\top}\mathbf{\overline x})\|_2}{L_{2k}(\mathbf{BP})} \\ \nonumber
-%&\leq \frac{\|( \mathbf{BPD} - \mathbf{A}) \mathbf{x}\|_2 + \|\mathbf{A}\mathbf{x} - \mathbf{B}\mathbf{\overline x}\|_2}{L_{2k}(\mathbf{BP})} \\
-%&\leq \frac{C_1\varepsilon \|\mathbf{x}\|_1 + \varepsilon}{L_{2k}(\mathbf{BP})},
-%\end{align}
-where the first term in the numerator above follows from the triangle inequality and \eqref{Cstable}.
-
-It remains for us to bound the denominator. For any $2k$-sparse $\mathbf{x}$, we have by the triangle inequality:
-\begin{align*}
-\|\mathbf{BPD}\mathbf{x}\|_2 
-&\geq \|\mathbf{A}\mathbf{x}\|_2 - \|(\mathbf{A} - \mathbf{BPD})\mathbf{x}\|_2 \\
-&\geq \sqrt{2k} (L_{2k}(\mathbf{A}) -  C_1\varepsilon) \|\mathbf{x}\|_2,
-\end{align*}
-
-%\begin{align*}
-%\|\mathbf{BP}\mathbf{x}\|_2 
-%&\geq \|\mathbf{A}\mathbf{D}^{-1}\mathbf{x}\|_2 - \|(\mathbf{A} - \mathbf{BPD})\mathbf{D}^{-1}\mathbf{x}\|_2 \\
-%&\geq \sqrt{2k} (L_{2k}(\mathbf{A}) -  C_1\varepsilon) \|\mathbf{D}^{-1}\mathbf{x}\|_2, \\ 
-%&\geq \sqrt{2k} (L_{2k}(\mathbf{A}) -  C_1\varepsilon) \|\mathbf{D}^{-1}\|_{?} \| \mathbf{x}\|_2,
-%\end{align*}
-%
-We therefore have that $L_{2k}(\mathbf{BPD}) \geq L_{2k}(\mathbf{A}) - C_1\varepsilon  > 0$, and \eqref{b-PDa} then follows from \eqref{stuff}.
-The reader may also verify that $L_{2k}(\mathbf{BP}) \geq L_{2k}(\mathbf{BPD}) / \|\mathbf{D}\|_1$.
-
-The heart of the matter is therefore \eqref{Cstable}, which we now establish beginning with the important special case of $k = 1$.
-
-\begin{proof}[Proof of Thm.~\ref{DeterministicUniquenessCorollary} for $k=1$]
-Since the only 1-uniform hypergraph with the SIP is $[m]$, which is obviously regular, we require only $\mathbf{x}_i = c_i \mathbf{e}_i$ for $i \in [m]$, with $c_i \neq 0$ to guarantee  linear independence.
-While we have yet to define $C_1$ generally, in this case we may set $C_1 = 1/ \min_{\ell \in [m]} |c_{\ell}|$ so that $\varepsilon < L_2(\mathbf{A})  \min_{\ell \in [m]} |c_{\ell}|$.
-
-Fix $\mathbf{A} \in \mathbb{R}^{n \times m}$ satisfying $L_2(\mathbf{A}) > 0$, since here we have $2\mathcal{H} = {[m] \choose 2}$, and suppose some $\mathbf{B}$ and $1$-sparse $\mathbf{\overline x}_i \in \mathbb{R}^{\overline m}$ have  $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \varepsilon < L_2(\mathbf{A}) / C_1$ for all $i$.
-Then, there exist $\overline{c}_1, \ldots, \overline{c}_m \in \mathbb{R}$ and a map $\pi: [m] \to [\overline m]$ such that:
-\begin{align}\label{1D}
-\|c_i\mathbf{A}_i - \overline{c}_i\mathbf{B}_{\pi(i)}\|_2 \leq \varepsilon,\ \ \text{for $i \in [m]$}.
-\end{align} 
-Note that $\overline{c}_i \neq 0$, since otherwise we would reach the following contradiction: $\|\mathbf{A}_i \|_2 \leq C_1 |c_i| \|\mathbf{A}_i \|_2  \leq C_1\varepsilon < L_2(\mathbf{A}) \leq L_1(\mathbf{A}) = \min_{i \in [m]} \|\mathbf{A}_{i}\|_2$.
-%implies by \eqref{delrho} the contradiction $|c_i| < \min_{\ell \in [m]} | c_\ell |$.
-
-We now show that $\pi$ is injective (in particular, a permutation if $\overline m = m$).
-Suppose that $\pi(i) = \pi(j) = \ell$ for some $i \neq j$ and $\ell$.
-Then, $\|c_{i}\mathbf{A}_{i} - \overline{c}_{i} \mathbf{B}_{\ell}\|_2  \leq \varepsilon$ and $\|c_{j}\mathbf{A}_{j} - \overline{c}_{j}\mathbf{B}_{\ell}\|_2 \leq \varepsilon$, and we have: %Scaling and summing these inequalities by $|\overline{c}_{i}|$ and $|\overline{c}_{j}|$, respectively, and applying the triangle inequality to annihilate the terms in $\mathbf{B}_\ell$, we obtain:
-\begin{align*}
-(|\overline{c}_{i}| + |\overline{c}_{j}|) \varepsilon
-&\geq |\overline{c}_{i}| \|c_{j}\mathbf{A}_{j} - \overline{c}_{j}\mathbf{B}_{\ell}\|_2  + |\overline{c}_{j}| \|c_{i}\mathbf{A}_{i} - \overline{c}_{i} \mathbf{B}_{\ell}\|_2 \nonumber \\
-&\geq \|\mathbf{A}(\overline{c}_{i}c_{j} \mathbf{e}_{j} - \overline{c}_{j}c_{i}\mathbf{e}_{i})\|_2 \nonumber \\ 
-&\geq \sqrt{2}  L_2(\mathbf{A}) \|\overline{c}_{i}c_{j} \mathbf{e}_{j} - \overline{c}_{j}c_{i}\mathbf{e}_{i}\|_2 \nonumber \\
-&\geq  L_2(\mathbf{A}) \left( |\overline{c}_{i}| + |\overline{c}_{j}| \right) \min_{\ell \in [m]} |c_\ell |,
-\end{align*}
-contradicting our assumed upper bound on $\varepsilon$. Hence, the map $\pi$ is injective and so $\overline m \geq m$. %Setting $\overline J = \pi([m])$ and
-
-Letting $\mathbf{P}$ and $\mathbf{D}$ be the $\overline m \times \overline m$ permutation and invertible diagonal matrices with, respectively, columns $\mathbf{e}_{\pi(i)}$ and $\frac{\overline{c}_i}{c_i}\mathbf{e}_i$ for $i \in [m]$ (otherwise, $\mathbf{e}_{i}$ for $i \in [\overline{m}] \setminus [m]$), we may rewrite \eqref{1D} to see that for all $i \in [m]$:
-\begin{align*}
-\|\mathbf{A}_i - (\mathbf{BPD})_i\|_2 
-= \|\mathbf{A}_i - \frac{\overline{c}_i}{c_i}\mathbf{B}_{\pi(i)}\|_2 
-\leq \frac{\varepsilon}{|c_i|} 
-\leq C_1\varepsilon.
-\end{align*}
-%\vspace{-.2 cm}
-\end{proof}
-
-An extension of the proof to the general case $k < m$ requires some additional tools to derive the general expression \eqref{Cdef1} for $C_1$.
-These include a generalized notion of distance (Def.~\ref{dDef}) and angle (Def.~\ref{FriedrichsDefinition}) between subspaces as well as a stability result in combinatorial matrix analysis (Lem.~\ref{MainLemma}).
-
-\begin{definition}\label{dDef}
-For $\mathbf{u} \in \mathbb R^m$ and vector spaces $U,V \subseteq \mathbb{R}^m$, let $\text{\rm dist}(\mathbf{u}, V) := \min \{\| \mathbf{u}-\mathbf{v} \|_2: \mathbf{v} \in V\}$ and define:
-\begin{align}
-d(U,V) := \max_{\mathbf{u} \in U, \ \|\mathbf{u}\|_2 \leq 1} \text{\rm dist}(\mathbf{u},V).
-\end{align}
-\end{definition}
-
-We note the following facts about $d$. Clearly, 
-\begin{align}\label{UsubU}
-U' \subseteq U \implies d(U',V) \leq d(U,V).
-\end{align}
-From \cite[Ch.~4 Cor.~2.6]{Kato2013}, we also have: %Kato p.223
-\begin{align}\label{dimLem}
-d(U,V) < 1 \implies \dim(U) \leq \dim(V),
-\end{align}
-and from \cite[Lem.~3.2]{Morris10}:
-\begin{align}\label{eqdim}
-\dim(U) = \dim(V) \implies d(U,V) = d(V,U).
-\end{align}
-
-The following is our result in combinatorial matrix analysis; it contains most of the complexity in the proof of Thm.~\ref{DeterministicUniquenessTheorem}.
-
-\begin{lemma}\label{MainLemma}
-If an $n \times m$ matrix $\mathbf{A}$ has $L_{2\mathcal{H}}(\mathbf{A}) > 0$ for some $r$-regular $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP, then the following holds for $C_2 > 0$ given by \eqref{Cdef2}:
-
-Fix $\varepsilon < L_2(\mathbf{A}) / C_2$. If for some $n \times \overline m$ matrix $\mathbf{B}$ and map $\pi: \mathcal{H} \mapsto {[\overline m] \choose k}$,
-\begin{align}\label{GapUpperBound}
-d(\bm{\mathcal{A}}_S, \bm{\mathcal{B}}_{\pi(S)}) \leq \varepsilon, \ \  \text{for $S \in \mathcal{H}$},
-\end{align}
-then $\overline m \geq m$, and provided $\overline m (r-1) < mr$, there is a permutation matrix $\mathbf{P}$ and invertible diagonal $\mathbf{D}$ such that:
-\begin{align}\label{MainLemmaBPD}
-\|\mathbf{A}_i - (\mathbf{B}\mathbf{PD})_i\|_2 \leq C_2 \varepsilon, \ \  \text{for } i \in J,
-\end{align}
-for some $J \subseteq [m]$ of size \mbox{$m - (r-1)(\overline m - m)$}.
-\end{lemma}
-
-%\begin{lemma}\label{MainLemma}
-%Fix $\mathbf{A} \in \mathbb{R}^{n \times m}$ with $L_\mathcal{H}(\mathbf{A}) > 0$ for some regular $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP.
-There exists a constant $C_2 > 0$ for which the following holds for all $\varepsilon < L_2(\mathbf{A}) / C_2$:
-
-%If a matrix $\mathbf{B} \in \mathbb{R}^{n \times m}$ and map $\pi: E \mapsto {m \choose k}$ satisfy:
-%\begin{align}\label{GapUpperBound}
-%d(\text{\rm span}\{\mathbf{A}_{S}\}, \bm{\mathcal{B}}_{\pi(S)}) \leq \varepsilon, \ \ \text{for $S \in \mathcal{H}$},
-%\end{align}
-%then there exist a permutation matrix $\mathbf{P}$ and invertible diagonal matrix $\mathbf{D}$ such that:
-%\begin{align}\label{MainLemmaBPD}
-%\|\mathbf{A}_j - \mathbf{BPD}_j\|_2 \leq C_2 \varepsilon, \ \  \text{for } j \in [m],
-%\end{align}
-%\end{lemma}
-
-We present the constant $C_2$ (a function of $\mathbf{A}$ and $\mathcal{H}$) relative to a quantity used in \cite{Deutsch12} to analyze the convergence of the ``alternating projections" algorithm for projecting a point onto the intersection of subspaces.
-We incorporate this quantity into the following definition, which we refer to in our proof of Lem.~\ref{DistanceToIntersectionLemma} in the Appendix; specifically, we use it to bound the distance between a point and the intersection of subspaces given an upper bound on its distance from each subspace.
-
-\begin{definition}\label{FriedrichsDefinition}
-For a collection of real subspaces $\mathcal{V} = \{V_i\}_{i=1}^\ell$, define $\xi(\mathcal{V}) := 0$ when $|\mathcal{V}| = 1$, and otherwise:
-\begin{align}\label{xi}
-\xi^2(\mathcal{V}) := 1 -  \max \prod_{i=1}^{\ell-1} \sin^2  \theta \left(V_i, \cap_{j>i} V_j \right) ,
-\end{align} 
-%
-where the maximum is taken over all ways of ordering 
-%\footnote{We modify the quantity in \cite{Deutsch12} in this way since the subspace ordering is irrelevant to our purpose.} 
-the $V_i$ and the angle $\theta \in (0,\frac{\pi}{2}]$ is defined implicitly as \cite[Def.~9.4]{Deutsch12}:
-\begin{align*}
-\cos{\theta(U,W)} := \max\left\{ |\langle \mathbf{u}, \mathbf{w} \rangle|: \substack{ \mathbf{u} \in U \cap (U \cap W)^\perp, \ \|\mathbf{u}\|_2 \leq 1 \\ \mathbf{w} \in W \cap (U \cap W)^\perp, \  \|\mathbf{w}\|_2 \leq 1 } \right\}.
-\end{align*}
-\end{definition}
-Note that $\theta \in (0,\frac{\pi}{2}]$ implies $0 \leq \xi < 1$, and that $\xi(\mathcal{V}') \leq \xi(\mathcal{V})$ when $\mathcal{V}' \subseteq \mathcal{V}$.\footnote{We acknowledge the counter-intuitive property: $\theta =  \pi/2$ when $U \subseteq W$.}
-
-The constant $C_2 > 0$ of Lem.~\ref{MainLemma} can now be expressed as:  
-\begin{align}\label{Cdef2}
-	C_2(\mathbf{A}, \mathcal{H}) := \frac{ (r+1) \max_{j \in [m]} \|\mathbf{A}_j\|_2}{ 1- \max_{\mathcal{G} \in {\mathcal{H} \choose r+1}} \xi( \bm{\mathcal{A}}_\mathcal{G} ) }.
-\end{align}
-
-We next define the constant $C_1 > 0$ of Thm.~\ref{DeterministicUniquenessTheorem} in terms of $C_2$.
-Given vectors $\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$, let $\mathbf{X}$ denote the $m \times N$ matrix with columns $\mathbf{x}_i$ and let $I(S)$ denote the set of indices $i$ for which $\mathbf{x}_i$ is supported in $S$.
-We define:
-\begin{align}\label{Cdef1}
-C_1(\mathbf{A}, \mathcal{H}, \{\mathbf{x}_i\}_{i=1}^N) := \frac{ C_2(\mathbf{A}, \mathcal{H}) } { \min_{S \in \mathcal{H}} L_k(\mathbf{AX}_{I(S)}) }.
-\end{align}
-Given the assumptions of Thm.~\ref{DeterministicUniquenessTheorem} on $\mathbf{A}$ and the $\mathbf{x}_i$, this expression for $C_1$ is well-defined\footnote{\label{note1}To see this, fix $S \in \mathcal{H}$ and $k$-sparse $\mathbf{c}$.
-Using the definitions, we have $\|\mathbf{AX}_{I(S)}\mathbf{c}\|_2 \geq \sqrt{k} L_\mathcal{H}(\mathbf{A})\|\mathbf{X}_{I(S)}\mathbf{c}\|_2 \geq k L_\mathcal{H}(\mathbf{A}) L_k(\mathbf{X}_{I(S)})\|\mathbf{c}\|_2$.
-Thus, $L_k(\mathbf{AX}_{I(S)}) \geq \sqrt{k} L_\mathcal{H}(\mathbf{A}) L_k(\mathbf{X}_{I(S)}) > 0$, since $L_{\mathcal{H}}(\mathbf{A}) \geq L_{2\mathcal{H}}(\mathbf{A})> 0$ and $L_k(\mathbf{X}_{I(S)}) > 0$ by general linear position of the $\mathbf{x}_i$.} and yields an upper bound on $\varepsilon$ consistent with that proven sufficient in the case $k=1$ considered at the beginning of this section.\footnote{When $\mathbf{x}_i = c_i\mathbf{e}_i$, we have $C_2 \geq 2\|\mathbf{A}_i\|_2$ and the denominator in \eqref{Cdef1} becomes $\min_{i \in [m]} |c_i| \|\mathbf{A}_i\|_2$; hence, $C_1 \geq 2 / \min_{i \in [m]} |c_i|$.}
-% C_2(\mathbf{A}, \mathcal{H}) := \frac{ (r+1) \max_{j \in [m]} \|\mathbf{A}_j\|_2}{ \min_{\mathcal{G} \in {\mathcal{H} \choose r} \cup {\mathcal{H} \choose r+1}} \xi( \{ \bm{\mathcal{A}}_S \}
-
-The practically-minded reader should note that the explicit constants $C_1$ and $C_2$ are effectively computable: the quantity $L_k$ may be calculated as the smallest singular value of a certain matrix, while the quantity $\xi$ involves computing ``canonical angles'' between subspaces, which reduces again to an efficient singular value decomposition.
-There is no known fast computation of $L_k$ in general, however, since even $L_{k} > 0$ is NP-hard \cite{tillmann2014computational}, although 
-efficiently computable bounds have been proposed (e.g., via the ``mutual coherence" of a matrix \cite{donoho2003optimally}); alternatively, 
-fixing $k$ yields polynomial complexity.
-Moreover, calculating $C_2$ requires an exponential number of queries to $\xi$ unless $r$ is held fixed, too (e.g., the ``cyclic order'' hypergraphs described above have $r=k$).
-Thus, as presented, $C_1$ and $C_2$ are not efficiently computable in general.
-% , but efficient subcases do exist and may be of practical relevance.
-
-\begin{proof}[Proof of Thm.~\ref{DeterministicUniquenessCorollary} for $k < m$] 
-We find a map $\pi: \mathcal{H} \to {[m] \choose k}$ for which the distance $d(\bm{\mathcal{A}}_S, \bm{\mathcal{B}}_{\pi(S)})$ is controlled by $\varepsilon$ for all $S \in \mathcal{H}$.
-Applying Lem.~\ref{MainLemma} then completes the proof.
-%We shall show that for every $S \in \mathcal{H}$ there is some $\overline S \in {[\overline m] \choose k}$ for which the distance $d(\bm{\mathcal{A}}_S, \bm{\mathcal{B}}_{\overline S})$ is controlled by $\varepsilon$.
-Applying Lem.~\ref{MainLemma} with the map $\pi$ defined by $S \mapsto \overline S$ then completes the proof.
-
-Fix $S \in \mathcal{H}$.
-Since there are more than $(k-1){\overline m \choose k}$ vectors $\mathbf{x}_i$ supported in $S$, by the pigeonhole principle there must be some $\overline S \in {[\overline m] \choose k}$ and a set of $k$ indices $K \subseteq I(S)$ for which all $\mathbf{\overline x}_i$ with $i \in K$ are supported in $\overline S$.
-It also follows\footnotemark[\ref{note1}] from $L_{2\mathcal{H}}(\mathbf{A}) > 0$ and the general linear position of the $\mathbf{x}_i$ that $L_k(\mathbf{AX}_{K}) > 0$; that is, the columns of the $n \times k$ matrix $\mathbf{AX}_K$ form a basis for $\bm{\mathcal{A}}_S$.
-
-Fixing $\mathbf{y} \in \bm{\mathcal{A}}_S \setminus \{\mathbf{0}\}$, there then exists $\mathbf{c} = (c_1, \ldots, c_k) \in \mathbb{R}^k \setminus \{\mathbf{0}\}$ such that $\mathbf{y} = \mathbf{AX}_K\mathbf{c}$.
-Setting \mbox{$\mathbf{\overline{y}} = \mathbf{B\overline{X}}_K\mathbf{c}$, which is in $\bm{\mathcal{B}}_{\overline S}$}, we have by triangle inequality:
-\begin{align*}
-\|\mathbf{y} - \mathbf{\overline{y}}\|_2 
-%&= \|\sum_{i=1}^k c_i(\mathbf{AX}_K - \mathbf{B\overline{X}}_K)_i\|_2
-&= \|(\mathbf{AX}_K - \mathbf{B\overline{X}}_K)\mathbf{c}\|_2
-%\leq \varepsilon \sum_{i=1}^k |c_i| \\
-\leq \varepsilon \|\mathbf{c}\|_1
-\leq \varepsilon \sqrt{k}  \|\mathbf{c}\|_2  \\
-&\leq \frac{\varepsilon}{L_k(\mathbf{AX}_K)} \|\mathbf{y}\|_2,
-\end{align*}
-where the last inequality uses \eqref{Ldef}. From Def.~\ref{dDef}:
-\begin{align}\label{rhs222}
-d(\bm{\mathcal{A}}_S, \bm{\mathcal{B}}_{\overline S}) 
-\leq \frac{\varepsilon}{  L_k(\mathbf{AX}_{K}) } 
-\leq \frac{\varepsilon}{  L_k(\mathbf{AX}_{I(S)}) } 
-\leq \varepsilon \frac{C_1}{C_2}.
-\end{align}
-%
-Finally, apply Lem.~\ref{MainLemma} with $\varepsilon < L_2(\mathbf{A})/C_1$ and $\pi(S) := \overline S$. % L_2(A) > 0 by def of L, since L_2H(A) > 0 and H covers [m]
-\end{proof}
-
-Before moving on to the proof of Thm.~\ref{SLCopt}, we briefly revisit our discussion on sample complexity from the end of the previous section.
-While an exponential number of samples may very well prove to be necessary in the deterministic or almost-certain case, our proof of Thm.~\ref{DeterministicUniquenessTheorem} can be extended to hold with some probability for \emph{any} number of samples by alternative appeal to a probabilistic pigeonholing at the point early in the proof where the (deterministic) pigeonhole principle is applied to show that for every $S \in \mathcal{H}$, there exist $k$ vectors $\mathbf{x}_i$ supported on $S$ whose corresponding $\mathbf{\overline x}_i$ all share the same support.\footnote{A famous example of such an argument is the counter-intuitive ``birthday paradox", which demonstrates that the probability of two people having the same birthday in a room of twenty-three is greater than 50\%.}
-Given insufficient samples, this argument has some less-than-certain probability of being valid for each $S \in \mathcal{H}$.
-Nonetheless, simulations with small hypergraphs confirm that the probability of success very quickly approaches one once the number of samples $N$ surpasses a small fraction of the deterministic sample complexity.
-
-\begin{proof}[Proof of Thm.~\ref{SLCopt}]
-We bound the number of $k$-sparse $\mathbf{\overline x}_i$ from below and then apply Thm.~\ref{DeterministicUniquenessCorollary}. 
-%We now apply this fact to bound the number of $k$-sparse $\mathbf{\overline x}_i$. 
-Let $n_p$ be the number of $\mathbf{\overline x}_i$ with $\|\mathbf{\overline x}_i\|_0 = p$.
-Since the $\mathbf{x}_i$ are all $k$-sparse, by \eqref{minsum} we have:
-\begin{align*}
-%\mbox{$k \sum_{p = 0}^{\overline m} n_p \geq \sum_{i=0}^N \|\mathbf{x}_i\|_0 \geq \sum_{i=0}^N \|\mathbf{\overline x}_i\|_0 = \sum_{p=0}^{\overline m} p n_p.$}
-\sum_{p=0}^{\overline m} p n_p =  \sum_{i=0}^N \|\mathbf{\overline x}_i\|_0
-\leq \sum_{i=0}^N \|\mathbf{x}_i\|_0 
-\leq kN
-\end{align*}
-Since $N = \sum_{p = 0}^{\overline m} n_p$, we then have $\sum_{p = 0}^{\overline m} (p-k) n_p \leq 0$. Splitting the sum yields:
-\begin{align}\label{eqn}
-\sum_{p = k+1}^{\overline m} n_p \leq \sum_{p = k+1}^{\overline m} (p-k) n_p \leq \sum_{p = 0}^k (k-p)n_p \leq k \sum_{p = 0}^{k-1} n_p,
-\end{align}
-%
-demonstrating that the number of vectors $\mathbf{\overline x}_i$ that are \emph{not} $k$-sparse is bounded above by how many are $(k-1)$-sparse.
-
-Next, observe that no more than $(k-1)|\mathcal{H}|$ of the $\mathbf{\overline x}_i$ share a support $\overline S$ of size less than $k$.
-Otherwise, by the pigeonhole principle, there is some $S \in \mathcal{H}$ and a set of $k$ indices $K \subseteq I(S)$ for which all $\mathbf{x}_i$ with $i \in K$ are supported in $S$; as argued previously, \eqref{rhs222} follows.
-It is simple to show that $L_2(\mathbf{A}) \leq \max_j\|\mathbf{A}_j\|_2$, and since $0 \leq \xi < 1$, the right-hand side of \eqref{rhs222} is less than one for $\varepsilon < L_2(\mathbf{A})/C_1$.
-Thus, by \eqref{dimLem} we would have the contradiction $k = \dim(\bm{\mathcal{A}}_S) \leq \dim(\bm{\mathcal{B}}_{\overline S}) \leq |\overline S| < k.$
-
-The total number of $(k-1)$-sparse vectors $\mathbf{\overline x}_i$ thus cannot exceed $|\mathcal{H}|(k-1){ \overline m \choose k-1}$.
-By \eqref{eqn}, no more than $|\mathcal{H}|k(k-1){ \overline m \choose k-1}$ vectors $\mathbf{\overline x}_i$ are not $k$-sparse.
-Since for every $S \in \mathcal{H}$ there are over $(k-1)\left[ {\overline m \choose k} + |\mathcal{H}|k{ \overline m \choose k-1} \right]$ vectors $\mathbf{x}_i$ supported there, it must be that more than $(k-1){\overline m \choose k}$ of them have corresponding $\mathbf{\overline x}_i$ that are $k$-sparse.
-The result now follows from Thm.~\ref{DeterministicUniquenessCorollary}, noting by the triangle inequality that $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline x}_i\| \leq 2\eta$ for $i = 1, \ldots, N$.
-\end{proof}
-
-%\begin{proof}[Proof (sketch) of Thm.~\ref{robustPolythm}]
-%Let $\textbf{M}$ be the matrix with columns $\mathbf{A}\mathbf{x}_i$, $i \in [N]$.
-Consider the polynomial $\prod_{S \in {[N] \choose 2k}} \sum_{S' \in {[n] \choose 2k}} (\det \textbf{M}_{S',S})^2$ in the indeterminate entries of $\mathbf{A}$ and $\mathbf{x}_i$, with notation as in Sec.~\ref{Results}.
-%It can be checked that when this polynomial is nonzero for a substitution of real numbers for the indeterminates, all of the genericity requirements on $\mathbf{A}$ and $\mathbf{x}_i$ in our proofs of stability in Thm.~\ref{DeterministicUniquenessTheorem} are satisfied (in particular, the spark condition \eqref{SparkCondition} on $\mathbf{A}$).
-%\end{proof}
-
-%\begin{proof}[Proof (sketch) of Cor.~\ref{ProbabilisticCor}]
-%First, note that if a set of measure spaces $\{(X_{\ell}, \Sigma_{\ell}, \nu_{\ell})\}_{\ell=1}^p$ has that $\nu_{\ell}$ is absolutely continuous with respect to $\mu$ for all $\ell \in [p]$, where $\mu$ is the standard Borel measure on $\mathbb{R}$, then the product measure $\prod_{\ell=1}^p \nu_{\ell}$ is absolutely continuous with respect to the standard Borel product measure on $\mathbb{R}^p$.
-% for space:  (e.g.,  \cite{folland2013real}).
-%By Thm.~\ref{robustPolythm}, there is a polynomial that is nonzero when $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$; in particular, stability holds almost surely.
-%\end{proof}
-
-\section{Discussion}\label{Discussion}
-
-A main motivation for this work is the emergence of seemingly unique representations from sparse coding models trained on natural data, despite the varied assumptions underlying the many algorithms in current use.
-Our results constitute an important step toward explaining these phenomena as well as unifying many publications on the topic by deriving general deterministic conditions under which identification of parameters in this model is not only possible but also robust to uncertainty in measurement and model choice.
-
-We have shown that, given sufficient data, the problem of determining a dictionary and sparse codes with minimal support size (Prob.~\ref{OptimizationProblem}) reduces to an instance of Prob.~\ref{InverseProblem}, to which our main result (Thm.~\ref{DeterministicUniquenessTheorem}) applies: every dictionary and sequence of sparse codes consistent with the data are equivalent up to inherent relabeling/scaling ambiguities and a discrepancy (error) that scales linearly with the measurement noise or modeling inaccuracy.
-The constants we provide are explicit and computable; as such, there is an effective procedure that sufficiently affirms if a proposed solution to these problems is indeed unique up to noise and inherent ambiguities, although it is not efficient in general.
-
-%A compelling feature of this model is its simple instantiation of the principle of Occam's razor: a natural video, for instance, is modeled as a linear combination of a small number of spatiotemporal building blocks, each representing an archetypical feature latent in the data.
-
-%For theoretical neuroscience in particular, dictionary learning and related methods have recovered characteristic components of natural images \cite{Olshausen96, hurri1996image, bell1997independent, van1998independent} and sounds \cite{bellsejnowski1996, smithlewicki2006} that reproduce response properties of certain cortical neurons.
-
-%to the recovery of ``mouse neuronal activity representing location on a track \cite{agarwal2014spatially}
-
-%Moreover, we show that even if the meta-parameter for the number of dictionary elements is overestimated, a subset of parameters may still be identifiable up to noise.
-
-Beyond an extension of existing noiseless guarantees \cite{Hillar15} to the noisy regime and their novel application to Prob.~\ref{OptimizationProblem}, our work contains a theory of combinatorial designs for support sets key to identification of dictionaries.
-We incorporate this idea into a fundamental lemma in matrix theory (Lem.~\ref{MainLemma}) that draws upon the definition of a matrix lower bound (\ref{Ldef}) induced by a hypergraph.
-The new insight offered by this combinatorial approach allows for guaranteed recovery of some or all dictionary elements even if: 1) dictionary size is overestimated, 2) data cover only a polynomial number of distinct sparse supports, and 3) dictionaries do not satisfy the spark condition.
-
-The absence of any assumptions about dictionaries solving Prob.~\ref{InverseProblem} was a major technical obstruction in proving Thm.~\ref{DeterministicUniquenessTheorem}.
-We sought such a general guarantee because of the practical difficulty in ensuring that an algorithm maintain a dictionary satisfying the spark condition \eqref{SparkCondition} at each iteration, an implicit requirement of all previous works except \cite{Hillar15}; indeed, even certifying a dictionary has this property is NP-hard \cite{tillmann2014computational}.
-
-One direct application of this work is to theoretical neuroscience, wherein our theorems justify the mathematical soundness of one of the few hypothesized theories of bottleneck communication in the brain \cite{Isely10}: that sparse neural population activity is recoverable from its noisy linear compression through a randomly constructed (but unknown) wiring bottleneck by any biologically plausible unsupervised sparse coding method that solves Prob.~\ref{DeterministicUniquenessTheorem} or \ref{SLCopt} (e.g., \cite{rehnsommer2007, rozell2007neurally, pehlevan2015normative}).\footnote{We refer the reader to \cite{ganguli2012compressed} for more on interactions between dictionary learning and neuroscience.}
-
-In fact, uniqueness guarantees with minimal assumptions apply to all areas of data science and engineering that utilize learned sparse structure.
-For example, several groups have applied compressed sensing to signal processing tasks; for instance, in MRI analysis \cite{lustig2008compressed}, image compression \cite{Duarte08}, and even the design of an ultrafast camera \cite{Gao14}.
-It is only a matter of time before these systems incorporate dictionary learning to encode and decode signals (e.g., in a device that learns structure from motion \cite{kong2016prior}), just as scientists have used sparse coding to make sense of their data \cite{jung2001imaging, agarwal2014spatially, lee2016sparse, wu2016stability}.
-
-Assurances offered by our theorems certify that different devices and algorithms learn equivalent representations given enough data from statistically identical systems.\footnote{To contrast with the current hot topic of ``Deep Learning'', there are few such uniqueness guarantees for these models of data; moreover, even small noise can dramatically alter their output \cite{goodfellow2014explaining}.}
-Indeed, a main reason for the sustained interest in dictionary learning as an unsupervised method for data analysis seems to be the assumed well-posedness of parameter identification in the model, confirmation of which forms the core of our findings.
-
-We close with some challenges left open by our work.
-All conditions stated here guaranteeing the uniqueness and stability of sparse representations have only been shown sufficient; it remains open, therefore, to extend them to necessary conditions, be they on required sample size, the structure of support set hypergraphs, or tolerable error bounds.
-On this last note, we remark that our deterministic treatment considers always the ``worst-case" noise, whereas the ``effective" noise sampled from a concentrated distribution might be significantly reduced, especially for high-dimensional data.
-It would be of great practical benefit to see how drastically all conditions can be relaxed by requiring only probabilistic guarantees in this way, or in the spirit of our discussion on probabilistic pigeonholing to reduce sample complexity (as in the famous ``birthday paradox") following the proof of Thm.~\ref{DeterministicUniquenessTheorem}.
-
-Another interesting question raised by our work is for which special cases is it efficient to check that a solution to Prob.~\ref{InverseProblem} or \ref{OptimizationProblem} is unique up to noise and inherent ambiguities.
-Considering that the sufficient conditions we have described for checking this in general are NP-hard to compute, are the necessary conditions hard?
-Are Probs.~\ref{InverseProblem} and \ref{OptimizationProblem} then also hard (e.g., see \cite{Tillmann15})?
-Finally, since Prob.~\ref{SLCopt} is intractable in general, but efficiently solvable by $\ell_1$-norm minimization when the matrix is known (and has a large enough lower bound over sparse domains \cite{eldar2012compressed}), is there a version of Thm.~\ref{SLCopt} certifying when Prob.~\ref{OptimizationProblem} can be solved efficiently in full by similar means?
-% [*** Incorporate this open problem with more words ***]
-
-We hope these remaining challenges pique the interest of the community to pick up where we have left off and that the theoretical tools showcased here may be of use to this end.
-
-%We close with some challenges left open by our work.
-First, there is the basic problem of proving optimal lower bounds on sufficient sample size $N$ guaranteeing the uniqueness and stability of sparse representations.
-The pigeonholing argument in the proof of Thm.~\ref{DeterministicUniquenessTheorem} is loose in that it assigns to each support $S \in \mathcal{H}$ a corresponding support $\overline S$ without consideration of previously matched pairs; although we doubt tightening in this way will lead to sub-exponential sample sizes.
-Sample complexity will also benefit from lowering the number of required supports, i.e.
-the size of regular uniform hypergraphs satisfying the SIP.
-The regularity requirement on support hypergraphs can be loosened to allow for certain non-regular hypergraphs satisfying constraints on the degree sequence of nodes; though we impose regularity for clarity of exposition.
-It is then natural to ask: what is the smallest hypergraph satisfying the required constraints forgiven $m$ and $k$?
-Finally, the error bounds can be improved by tightening the constant $C_1$, e.g.
-via an improvement in Lemma ?.
-
-%Solving Prob.~\ref{SLCopt} directly is intractable in general since it necessitates, for each proposed dictionary $\mathbf{B}$, a combinatorial search for the supports of the associated sparse codes $\mathbf{\overline x}_i$.
-A common work-around is to convexify the problem (for fixed $\mathbf{B}$) by substituting the norm $\|\cdot\|_0$ with $\|\cdot\|_1$, impelled the fact that matrices $\mathbf{A}$ with large enough $L_{2k}(\mathbf{A})$ induce the same sparse codes via minimization of either norm \cite{?}.
-To this end, the lower bound $L_{2k}(\mathbf{BP}) \geq (L_{2k}(\mathbf{A}) - C_1\varepsilon) / \|\mathbf{D}\|_1$ implied by Thm.~\ref{DeterministicUniquenessTheorem} hints at conditions on the generating dictionary $\mathbf{A}$ and $k$-sparse codes $\mathbf{x}_i$ under which \emph{all} matrices $\mathbf{B}$ (of bounded column-norm) that solve Prob.~\ref{OptimizationProblem} also share this property of $\mathbf{A}$ by virtue of uniqueness and stability.
-One might then imagine an inference procedure whereby sparse codes are inferred via minimization of $\|\cdot\|_1$, but solutions still evaluated by their collective support size, yielding unique optimal solutions to Prob.~\ref{SLCopt} if only constraints could be imposed such that the learning procedure eventually guides $\mathbf{B}$ through an optimal dictionary.
-% (e.g.
-the dictionary is a member of a known finite set).
-
-\textbf{Acknowledgement.} We thank Fritz Sommer and Darren Rhea for early thoughts, and Ian Morris for posting \eqref{eqdim} online.
-
-%\section{EXTRA}
-%An additional consequence of Thm.~\ref{DeterministicUniquenessTheorem} of potential practical relevance to is the implied lower bound $L_{2k}(\mathbf{BPD}) \geq L_{2k}(\mathbf{A}) - C_1\varepsilon$ in the case where $\mathbf{A}$ satisfies \eqref{SparkCondition}.
-Since solving Prob.~\ref{SLCopt} directly requires a combinatorial search over sparse supports for the $\mathbf{\overline x}_i$ for each proposed dictionary $\mathbf{B}$, rendering it intractable in general, a common strategy is to replace the $\ell_0$-norm in \eqref{minsum} with the $\ell_1$-norm, thereby transforming the inference of sparse $\mathbf{\overline x}_i$ for a fixed dictionary $\mathbf{B}$ into a convex optimization solvable by a linear program.
-A major advance in compressive sensing was the discovery that, for fixed $\mathbf{B}$, solutions to \eqref{minsum} using either norm yield the same sparse vectors $\mathbf{\overline x}_i$ (up to noise) provided $L_{2k}(\mathbf{B})$ is large enough \cite{?}.
-What our results hint at are conditions on the generating dictionary $\mathbf{A}$ and $k$-sparse codes $\mathbf{x}_i$ under which \emph{all} matrices $\mathbf{B}$ (of bounded column-norm) that solve Prob.~\ref{OptimizationProblem} also share this property by virtue of uniqueness and stability; that is, conditions which guarantee that the sparse codes $\mathbf{\overline x}_i$ solving Prob.~\ref{OptimizationProblem} also solve the convexified problem when the corresponding dictionary $\mathbf{B}$ is held fixed.
-It remains to determine, however, what practical conditions preclude matrices that don't solve Prob.~\ref{OptimizationProblem} from nonetheless solving the convexified problem.
-%
-%Regardless, an implication of the above observation is that the following algorithm solves Prob.~\ref{OptimizationProblem} without appeal to combinatorial search:
-%\begin{enumerate}
-%\item List all matrices $\mathbf{B}$.
-%\item For each matrix $\mathbf{B}$, solve $\mathbf{\overline x}_i = \arg \min \|\mathbf{v}\|_1$ s.t. $\|\mathbf{Bv} - \mathbf{z}_i\| \leq \eta$ for $i = 1, \ldots, N$.
-%\item Quantify the proposed solution $\mathbf{B}$ and $\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N$ as $\rho(\mathbf{B}, \mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N) = \sum_{i=1}^{N} \|\mathbf{\overline x}_i\|_0$.
-%\item Output $\arg \min_{\mathbf{B}, \mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N} \left( \rho \right)$.
-% \end{enumerate}
-
-%Since its inception some twenty years ago, sparse coding has become a standard tool in signal analysis, yielding myriad insights into the structure of natural signals across a variety of scientific domains.
-In this work,
-
-%We make a final remark about the tightness of our results and the computability of our derived constants.
-%We remark that our constants have been derived for deterministic ``worst-case'' noise, whereas the ``effective'' noise might be smaller when sampled from a distribution.
-
-%Our results suggest that this correspondence could be due to the ``universality'' of sparse representations in natural data, an early idea in neural theory \cite{pitts1947}.
-
-% \vspace{-.2 cm}
-
-%\showacknow % Display the acknowledgments section
-
-\bibliographystyle{IEEEtran}
-\bibliography{chazthm_ieee_trans_sig}
-
-% \vspace{-.2 cm}
-
-\section{Appendix}\label{proofs}
-
-We prove Lem.~\ref{MainLemma} after the following auxiliary lemmas.  % stating and proving some auxiliary lemmas. 
-%First, note that since $\|\mathbf{A}\mathbf{x}\|_2 \leq \max_j\|\mathbf{A}_j\|_2\|\mathbf{x}\|_1$ and $\|\mathbf{x}\|_1 \leq \sqrt{k} \|\mathbf{x}\|_2$ for $k$-sparse $\mathbf{x}$, by \eqref{Ldef} we have the following frequently applied inequality:
-%\begin{align}\label{delrho}
-%L_{k'}(\mathbf{A}) \leq  \max_j\|\mathbf{A}_j\|_2 \ \ \text{for all $k' \leq 2k$}.
-%\end{align}
-
-% and then sketch the proofs of Thm.~\ref{robustPolythm} and Cor.~\ref{ProbabilisticCor}.
-
-%\begin{lemma}\label{spanIntersectionLemma}
-%Let $\mathbf{M} \in \mathbb{R}^{n \times m}$. If every $2k$ columns of $\mathbf{M}$ are linearly independent, then for any $F \subseteq {[m] \choose k}$:
-%\begin{align*}
-%\text{\rm span}\{\mathbf{M}_{\cap F}\}  = \bigcap_{S \in F} \text{\rm span}\{\mathbf{M}_S\}.
-%\end{align*}
-%\end{lemma}
-%\begin{proof}
-%Using induction on $|F|$, it is enough to prove the lemma when $|F| = 2$; but this case follows directly from the assumption.
-%\end{proof}
-
-\begin{lemma}\label{spanIntersectionLemma}
-If $f: V \to W$ is injective, then $f\left(\cap_{i=1}^\ell V_i \right) =  \cap_{i=1}^\ell f\left(V_i\right)$ for any $V_1, \ldots, V_\ell \subseteq V$. ($f(\emptyset):=\emptyset$.)
-%In particular, if for some $E \in 2^{[m]}$ the map $M \in \mathbb{R}^{n \times m}$ is injective on $\cup_{S \in \mathcal{H}} \text{span}\{e_i\}_{i \in S}$ then $\text{span}\{ M_{\cap_{S \in \mathcal{H}} S} \} = \cap_{S \in \mathcal{H}} \text{span}\{M_S\}$.
-\end{lemma}
-\begin{proof}
-By induction, it is enough to prove the case $\ell = 2$.
-Clearly, for any map $f$, if $w \in f(U \cap V)$ then $w \in f(U)$ and $w \in f(V)$; hence, $w \in f(U) \cap f(V)$.
-If $w \in f(U) \cap f(V)$, then $w \in f(U)$ and $w \in f(V)$; thus, $w = f(u) = f(v)$ for some $u \in U$ and $v \in V$, implying $u = v$ by injectivity of $f$.
-It follows that $u \in U \cap V$ and $w \in f(U \cap V)$.
-\end{proof}
-In particular, if a matrix $\mathbf{A}$ satisfies $L_{2\mathcal{H}}(\mathbf{A}) > 0$, then taking $V$ to be the union of subspaces consisting of vectors with supports in $2\mathcal{H}$, we have $\bm{\mathcal{A}}_{\cap \mathcal{G}} = \cap \bm{\mathcal{A}}_\mathcal{G}$ for all $\mathcal{G} \subseteq \mathcal{H}$.
-% \vspace{-.4 cm}
-
-\begin{lemma}\label{DistanceToIntersectionLemma}
-Let $\mathcal{V} = \{V_i\}_{i=1}^k$ be a set of two or more subspaces of $\mathbb{R}^m$, and set $V = \cap \mathcal{V} $.
-For  $\mathbf{u} \in \mathbb{R}^m$, we have (recall Defs.~\ref{dDef}~\&~\ref{FriedrichsDefinition}):
-\begin{align}\label{DTILeq}
-\text{\rm dist}(\mathbf{u}, V) \leq \frac{1}{1 - \xi(\mathcal{V})} \sum_{i=1}^k \text{\rm dist}(\mathbf{u}, V_i).
-\end{align}
-\end{lemma}
-\begin{proof} 
-% When $V = \{\mathbf{0}\}$, the result is trivial, so suppose otherwise.  
-Recall the projection onto the subspace $V \subseteq \mathbb{R}^m$ is the mapping $\Pi_V: \mathbb{R}^m \to V$ that associates with each $\mathbf{u}$ its unique nearest point in $V$; i.e., $\|\mathbf{u} - \Pi_V\mathbf{u}\|_2 = \text{\rm dist}(\mathbf{u}, V)$.
-By repeatedly applying the triangle inequality, we have:
-\begin{align}\label{f}
-\|\mathbf{u} - &\Pi_V\mathbf{u}\|_2 
-\leq \|\mathbf{u} - \Pi_{V_k} \mathbf{u}\|_2 + \|\Pi_{V_k}  \mathbf{u} - \Pi_{V_k}\Pi_{V_{k-1}}\mathbf{u}\|_2 \nonumber \\
-&\ \ \ \ \ \ \ \ \ \ \ + \cdots + \|\Pi_{V_k} \Pi_{V_{k-1}}\cdots \Pi_{V_1} \mathbf{u} - \Pi_V \mathbf{u}\|_2 \nonumber \\
-&\leq  \sum_{\ell=1}^k \|\mathbf{u} - \Pi_{V_{\ell}} \mathbf{u}\|_2 
-+ \|(\Pi_{V_k}\cdots\Pi_{V_{1}} - \Pi_V) \mathbf{u}\|_2,
-\end{align}
-where we have also used that the spectral norm of the orthogonal projections $\Pi_{V_{\ell}}$ satisfies $\|\Pi_{V_{\ell}}\|_2 \leq 1$ for all $\ell$.
-
-It remains to bound the second term in \eqref{f} by $\xi(\mathcal{V}) \|\mathbf{u} - \Pi_V\mathbf{u}\|_2$.
-First, note that $\Pi_{V_\ell} \Pi_V = \Pi_V$ and $\Pi_V^2 = \Pi_V$, so we have $\|(\Pi_{V_k} \cdots \Pi_{V_1} - \Pi_V) \mathbf{u} \|_2
-= \| ( \Pi_{V_k} \cdots\Pi_{V_1} - \Pi_V ) (\mathbf{u} - \Pi_V\mathbf{u})\|_2$. % \leq z\|\mathbf{u} - \Pi_V\mathbf{u}\|_2$.
-Consequently, inequality \eqref{DTILeq} follows from \cite[Thm.~9.33]{Deutsch12}:
-\begin{align}
-\|\Pi_{V_k}\Pi_{V_{k-1}}\cdots\Pi_{V_1} \mathbf{x} - \Pi_V\mathbf{x}\|_2 \leq z \|\mathbf{x}\|_2, \ \ \text{for all } \mathbf{x},
-\end{align}
-with \mbox{$z^2= 1 - \prod_{\ell =1}^{k-1}(1-z_{\ell}^2)$} and \mbox{$z_{\ell} = \cos\theta\left(V_{\ell}, \cap_{s=\ell+1}^k V_s\right)$} (recall $\theta$ from Def.~\ref{FriedrichsDefinition}), after substituting $\xi(\mathcal{V})$ for $z$ and rearranging terms.
-\end{proof}
-\begin{lemma}\label{NonEmptyLemma} 
-Fix an $r$-regular hypergraph $\mathcal{H} \subseteq 2^{[m]}$ satisfying the SIP.
-If the map $\pi: \mathcal{H} \to 2^{[\overline m]}$ has $\sum_{S \in \mathcal{H}} |\pi(S)| \geq \sum_{S \in \mathcal{H}} |S|$ and:
-\begin{align}\label{cond}
-	|\cap \pi(\mathcal{G})| \leq |\cap \mathcal{G} |,\ \ \   \text{for } \mathcal{G} \in {\mathcal{H} \choose r} \cup {\mathcal{H} \choose r+1},
-\end{align}
-%
-then $\overline m \geq m$; and if $\overline m  (r-1) < mr$, the map $i \mapsto \cap_{S \in \sigma(i)} \pi(S)$ is an injective function to $[\overline m]$ from some $J \subseteq [m]$ of size $m - (r-1)(\overline m - m)$ (recall $\sigma$ from Def.~\ref{sip}).
-%In particular, if $\overline m = m$ then $\pi$ is induced by a permutation on $[m]$.
-\end{lemma}
-
-\begin{proof}
-Consider the following set: $T_1 := \{(i, S): i \in \pi(S), S \in \mathcal{H}\}$, which numbers $|T_1| = \sum_{S \in \mathcal{H}} |\pi(S)| \geq \sum_{S \in \mathcal{H}} |S| = \sum_{i \in [m]} \deg_\mathcal{H}(i) = mr$ by $r$-regularity of $\mathcal{H}$.
-Note that $|T_1| \leq \overline m r$; otherwise, pigeonholing the tuples of $T_1$ with respect to their $\overline m$ possible first elements would imply that more than $r$ of the tuples in $T_1$ share the same first element.
-This cannot be the case, however, since then some $\mathcal{G} \in {\mathcal{H} \choose r+1}$ formed from any $r+1$ of their second elements would satisfy $\cap \pi(\mathcal{G}) \neq 0$; hence, $|\cap \mathcal{G}| \neq 0$ by \eqref{cond}, contradicting $r$-regularity of $\mathcal{H}$.
-It follows that $\overline m \geq m$.
-
-Suppose now that $\overline m (r-1) < mr$, so that $p := mr - \overline m (r-1)$ is positive and $|T_1| \geq \overline m (r - 1) + p$.
-Pigeonholing $T_1$ into $[\overline m]$ again, there are at least $r$ tuples in $T_1$ sharing some first element; that is, for some $\mathcal{G}_1 \subseteq \mathcal{H}$ of size $|\mathcal{G}_1| \geq r$, we have $|\cap \pi(\mathcal{G}_1)| \geq 1$ and (by \eqref{cond}) $|\cap \mathcal{G}_1| \geq 1$.
-Since no more than $r$ tuples of $T_1$ can share the same first element, we in fact have $|\mathcal{G}_1| = r$.
-It follows by $r$-regularity that $\mathcal{G}_1$ is a star of $\mathcal{H}$; hence, $|\cap \mathcal{G}_1| = 1$ by the SIP and $|\cap \pi(\mathcal{G}_1)|  = 1$ by \eqref{cond}.
-
-If $p=1$, then we are done.
-Otherwise, define $T_2 := T_1 \setminus \{(i,S) \in T_1: i = \cap \pi(\mathcal{G}_1)\}$, which contains $|T_2| = |T_1| - r \geq (\overline m - 1)(r-1) + (p-1)$ ordered pairs having $\overline m - 1$ distinct first indices.
-Pigeonholing $T_2$ into $[\overline m - 1]$ and repeating the above arguments produces the star $\mathcal{G}_2 \in {\mathcal{H} \choose r}$ with intersection $\cap \mathcal{G}_2$ necessarily distinct (by $r$-regularity) from $\cap \mathcal{G}_1$.
-Iterating this procedure $p$ times in total yields the stars $\mathcal{G}_i$ for which $\cap\mathcal{G}_i \mapsto \cap \pi(\mathcal{G}_i)$ defines an injective map to $[\overline m]$ from $J = \{\cap \mathcal{G}_1, \ldots, \cap \mathcal{G}_p\} \subseteq [m]$.
-\end{proof}
-
-\begin{proof}[Proof of Lem.~\ref{MainLemma}]
-%We will show that the bound \eqref{GapUpperBound} trickles through the intersection semi-lattices of $\{\bm{\mathcal{A}}_S\}_{S \in \mathcal{H}}$ and $\{\bm{\mathcal{B}}_{\overline S}\}_{\overline S \in \pi(\mathcal{H})}$ to yield \eqref{MainLemmaBPD} by virtue of the SIP.
-We begin by showing that $\dim(\bm{\mathcal{B}}_{\pi(S)}) = \dim(\bm{\mathcal{A}}_S)$ for all $S \in \mathcal{H}$.
-Note that since $\|\mathbf{A}\mathbf{x}\|_2 \leq \max_j\|\mathbf{A}_j\|_2\|\mathbf{x}\|_1$ and $\|\mathbf{x}\|_1 \leq \sqrt{k} \|\mathbf{x}\|_2$ for all $k$-sparse $\mathbf{x}$, by \eqref{Ldef} we have $L_2(\mathbf{A}) \leq \max_j\|\mathbf{A}_j\|_2$ and therefore (as $0 \leq \xi < 1$) the right-hand side of \eqref{GapUpperBound} is less than one.
-From \eqref{dimLem}, we have $|\pi(S)| \geq \dim(\bm{\mathcal{B}}_{\pi(S)}) \geq \dim(\bm{\mathcal{A}}_S) = |S|$, the final equality holding by injectivity of $\mathbf{A}_S$.
-As $|\pi(S)| = |S|$, the claim follows.
-Note, therefore, that $\mathbf{B}_{\pi(S)}$ has full-column rank for all $S \in \mathcal{H}$.
-
-We next demonstrate that \eqref{cond} holds.
-Fixing $\mathcal{G} \in {\mathcal{H} \choose r} \cup {\mathcal{H} \choose r+1}$, it suffices to show that $d(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}, \bm{\mathcal{A}}_{\cap \mathcal{G}} ) < 1$, since by \eqref{dimLem} we then have $|\cap \pi(\mathcal{G})| = \dim(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}) \leq \dim(\bm{\mathcal{A}}_{\cap \mathcal{G}}) = |\cap \mathcal{G}|$, with equalities from the full column-ranks of $\mathbf{A}_{S}$ and $\mathbf{B}_{\pi(S)}$ for all $S \in \mathcal{H}$.\footnote{Note that if ever $\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})} \neq \bf 0$ while $\cap \mathcal{G} = \emptyset$, we would have $d(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}, \bm 0 ) = 1$.
-However, that leads to a contradiction.} Observe that $d(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}, \bm{\mathcal{A}}_{\cap \mathcal{G}}  )
-\leq d\left( \cap \bm{\mathcal{B}}_{\pi(\mathcal{G})}, \cap \bm{\mathcal{A}}_\mathcal{G} \right)$ by \eqref{UsubU}, since trivially $\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})} \subseteq \cap \bm{\mathcal{B}}_{\pi(\mathcal{G})}$ and also $\bm{\mathcal{A}}_{\cap \mathcal{G}} = \cap \bm{\mathcal{A}}_\mathcal{G}$ by Lem.~\ref{spanIntersectionLemma}.
-Recalling Def.~\ref{dDef} and applying Lem.~\ref{DistanceToIntersectionLemma} yields:
-\begin{align}
-d\left( \cap \bm{\mathcal{B}}_{\pi(\mathcal{G})}, \cap \bm{\mathcal{A}}_\mathcal{G} \right)
-&\leq \max_{\mathbf{u} \in \cap \bm{\mathcal{B}}_{\pi(\mathcal{G})}, \ \|\mathbf{u}\|_2 \leq 1} \sum_{S \in \mathcal{G}} \frac{ \text{\rm dist}\left( \mathbf{u},\bm{\mathcal{A}}_{S} \right) }{ 1 - \xi( \bm{\mathcal{A}}_\mathcal{G} ) } \nonumber \\
-&= \sum_{S \in \mathcal{G}} \frac{ d\left( \cap \bm{\mathcal{B}}_{\pi(\mathcal{G})},\bm{\mathcal{A}}_{S} \right) }{ 1 - \xi( \bm{\mathcal{A}}_\mathcal{G} ) }, \nonumber
-\end{align}
-passing the maximum through the sum.
-Since $\cap \bm{\mathcal{B}}_{\pi(\mathcal{G})} \subseteq \bm{\mathcal{B}}_{\pi(S)}$ for all $S \in \mathcal{G}$, by \eqref{UsubU} the numerator of each term in the sum above is bounded by \mbox{$d\left( \bm{\mathcal{B}}_{\pi(S)},\bm{\mathcal{A}}_{S} \right) = d\left(\bm{\mathcal{A}}_{S}, \bm{\mathcal{B}}_{\pi(S)} \right) \leq \varepsilon$}, with the equality from \eqref{eqdim} since $\dim(\bm{\mathcal{B}}_{\pi(S)}) = \dim(\bm{\mathcal{A}}_S)$.
-Thus, altogether:
-\begin{align}\label{last}
-d(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}, \bm{\mathcal{A}}_{\cap \mathcal{G}} )
-\leq \frac{|\mathcal{G}| \varepsilon}{1 - \xi( \bm{\mathcal{A}}_\mathcal{G} )}
-\leq \frac{C_2 \varepsilon}{\max_j\|\mathbf{A}_j\|_2},
-\end{align}
-recalling the definition of $C_2$ in \eqref{Cdef2}.
-Lastly, since $C_2 \varepsilon < L_2(\mathbf{A}) \leq \max_j\|\mathbf{A}_j\|_2$, we have $d(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}, \bm{\mathcal{A}}_{\cap \mathcal{G}} ) \leq 1$ and therefore \eqref{cond} holds.
-
-%Keeping in mind that $d(U',V) \leq d(U,V)$ whenever $U' \subseteq U$ and applying (in order) Lem.~\ref{spanIntersectionLemma}, Lem.~\ref{DistanceToIntersectionLemma}, \eqref{eqdim}, \eqref{GapUpperBound}, and \eqref{Cdef2} gives:
-%\begin{align}\label{randoml}
-%d(&\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}, \bm{\mathcal{A}}_{\cap \mathcal{G}}  ) 
-%\leq d\left( \cap \bm{\mathcal{B}}_{\pi(\mathcal{G})}, \cap \bm{\mathcal{A}}_\mathcal{G} \right)
-%\leq \sum_{T \in \mathcal{G}} \frac{ d\left( \cap \bm{\mathcal{B}}_{\pi(\mathcal{G})},\bm{\mathcal{A}}_{T} \right) }{ 1 - \xi( \bm{\mathcal{A}}_\mathcal{G} ) } \nonumber \\
-%&\leq \sum_{T \in \mathcal{G}} \frac{ d\left( \bm{\mathcal{B}}_{\pi(T)},\bm{\mathbf{A}}_{T} \right) }{ 1 - \xi( \bm{\mathcal{A}}_\mathcal{G} ) }
-%\leq \frac{|\mathcal{G}| \varepsilon}{1 - \xi( \bm{\mathcal{A}}_\mathcal{G} )} 
-%\leq \frac{C_2 \varepsilon}{\max_j\|\mathbf{A}_j\|_2},
-%\end{align}
-%
-%which is less than one, since $C_2 \varepsilon < L_2(\mathbf{A}) \leq \max_j\|\mathbf{A}_j\|_2$.
-
-Applying Lem.~\ref{NonEmptyLemma}, the association $i \mapsto \cap_{S \in \sigma(i)} \pi(S)$ is an injective map $\overline \pi: J \to [\overline m]$ for some $J \subseteq [m]$ of size $m - (r-1)(\overline m - m)$, and $\mathbf{B}_{\overline \pi(i)} \neq \mathbf{0}$ for all $i \in J$ since the columns of $\mathbf{B}_{\pi(S)}$ are linearly independent for all $S \in \mathcal{H}$.
-Letting $\overline \varepsilon := C_2 \varepsilon / \max_i \|\mathbf{A}_i\|_2$, it follows from \eqref{eqdim} and \eqref{last} that $d\left( \bm{\mathcal{A}}_i, \bm{\mathcal{B}}_{\overline \pi(i)} \right) = d\left(\bm{\mathcal{B}}_{\overline \pi(i)},  \bm{\mathcal{A}}_i \right)  \leq \overline \varepsilon$ for all $i \in J$.
-%Fixing $\overline \varepsilon = C_2\varepsilon$ and letting $c_i = \|\mathbf{A}_i\|_2^{-1}$, we thus have that for each $\mathbf{e}_i \in \mathbb{R}^m$ with $i \in J$ there exists some $\overline{c}_i \in \mathbb{R}$ such that $\|c_i\mathbf{A}\mathbf{e}_i - \overline{c}_i \mathbf{B}\mathbf{e}_{\overline \pi(i)}\|_2 \leq \overline \varepsilon < L_2(\mathbf{A}) \min_{i\in J} |c_i|$.
-But this is exactly the supposition in \eqref{1D}, and the result follows from the case $k=1$ in Sec.~\ref{DUT} applied to the submatrix $\mathbf{A}_J$.
-Setting $c_i := \|\mathbf{A}_i\|_2^{-1}$ so that $\|c_i\mathbf{Ae}_i\|_2 = 1$, by Def.~\ref{dDef} for all $i \in J$:
-\begin{align*}
-\min_{\overline c_i \in \mathbb{R}} \|c_i\mathbf{Ae}_i - \overline c_i \mathbf{Be}_{\overline \pi(i)} \|_2
-\leq d\left( \bm{\mathcal{A}}_i, \bm{\mathcal{B}}_{\overline \pi(i)} \right)
-\leq \overline \varepsilon,
-%&= \max_{\bm{u} \in \bm{\mathcal{A}}_i, \|\bm{u}\|_2 \leq 1} \text{dist}\left(\bm{u}, \bm{\mathcal{B}}_{\overline \pi(i)} \right) \\
-%&\geq  \text{dist}\left(c_i\bm{Ae}_i, \mathbf{Be}_{\overline \pi(i)} \right) \\
-%&= \min_{\overline c_i \in \mathbb{R}} \|c_i\bm{Ae}_i - \overline c_i \mathbf{Be}_{\overline \pi(i)} \|_2
-\end{align*}
-%
-for $\overline \varepsilon < L_2(\mathbf{A})\min_{i \in [m]}|c_i|$.
-But this is exactly the supposition in \eqref{1D}, with $J$ and $\overline \varepsilon$ in place of $[m]$ and $\varepsilon$, respectively.
-The same arguments of the case $k=1$ in Sec.~\ref{DUT} can then be made to show that for any $\overline m \times \overline m$ permutation and invertible diagonal matrices $\mathbf{P}$ and $\mathbf{D}$ with, respectively, columns $\mathbf{e}_{\pi(i)}$ and $\frac{\overline{c}_i}{c_i}\mathbf{e}_i$ for $i \in J$ (otherwise, $\mathbf{e}_{i}$ for $i \in [\overline{m}] \setminus J$), we have $\|\mathbf{A}_i - (\mathbf{B}\mathbf{PD})_i \|_2 \leq \overline  \varepsilon / |c_i|  \leq C_2 \varepsilon$ for all $i \in J$.
-\end{proof}
-
-%\section{Proofs of Thm.~\ref{robustPolythm} and Cor.~\ref{ProbabilisticCor}}
-
-%\clearpage
-
-%\section{$\ell_1$-norm Extension}
-%
-%\begin{problem}\label{OptimizationProblemL1}
-%Find a matrix $\mathbf{B}$ and vectors \mbox{$\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N \in \mathbb{R}^m$} that solve:
-%\begin{align}\label{minsum}
-%\min \sum_{i = 1}^N \|\mathbf{\overline x}_i\|_1 \ \ 
-%\text{subject to} \ \ \|\mathbf{z}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \eta, \ \text{for all $i$}.
-%\end{align}
-%\end{problem}
-
-%\begin{corollary}\label{SLCopt}
-%Fix $\alpha > 0$ and suppose all of the assumptions of Thm.\ref{DeterministicUniquenessTheorem} hold with the following modifications:
-%\begin{enumerate}
-%\item The coefficients of all $k$-sparse $\mathbf{x}_i$ are drawn from $[-\beta, \beta]$, where $\beta < \frac{\alpha(k+1)}{k}$.
-%\item More than $(k-1){\overline m \choose k} + q$ vectors $\mathbf{x}_i$ are supported in each $S \in \mathcal{H}$, where
-%\[ q = \left[\frac{\alpha}{\beta}(k+1) - k\right]^{-1}k|\mathcal{H}|(k-1){\overline m \choose k-1}. \]
-%\end{enumerate}
-%Then all solutions to Prob.~\ref{OptimizationProblemL1} for which the nonzero elements of all $\mathbf{\overline x}_i$ lie outside $[-\alpha, \alpha]$ necessarily satisfy the implications \eqref{Cstable} and \eqref{b-PDa} of Thm.~\ref{DeterministicUniquenessTheorem}.
-%\end{corollary}
-
-%\begin{proof}[Proof of Cor.~\ref{SLCopt}]
-%We bound the number of $k$-sparse $\mathbf{\overline x}_i$ and then apply Thm.~\ref{DeterministicUniquenessCorollary}.
-First, observe that no more than $(k-1)|\mathcal{H}|$ of the $\mathbf{\overline x}_i$ share a support $\overline S$ of size less than $k$; otherwise, by the pigeonhole principle, at least $k$ of these indices $i$ belong to the same $K \subseteq I(S)$ for some $S \in \mathcal{H}$ and (as argued previously) \eqref{rhs222} follows.
-Since the right-hand side of \eqref{rhs222} is less than one, by \eqref{dimLem} we have the contradiction $k = \dim(\bm{\mathcal{A}}_S) \leq \dim(\bm{\mathcal{B}}_{\overline S}) \leq |\overline S|.$ The total number of $(k-1)$-sparse vectors $\mathbf{\overline x}_i$ can thus not exceed $|\mathcal{H}|(k-1){ \overline m \choose k-1}$.
-
-%Next, observe that the assumptions of the lemma imply:
-%\begin{align*}
-%\alpha \sum_i \|\mathbf{\overline x}_i\|_0 \leq \sum_i \|\mathbf{\overline x}_i\|_1 \leq \sum_i \|\mathbf{x}_i\|_1 \leq \beta \sum_i \|\mathbf{x}_i\|_0.
-%\end{align*}
-
-%We now apply these facts to bound the number of $k$-sparse $\mathbf{\overline x}_i$.
-Let $n_p$ be the number of $\mathbf{\overline x}_i$ with $\|\mathbf{\overline x}_i\|_0 = p$.
-Since the $\mathbf{x}_i$ are all $k$-sparse, we have:
-%\begin{align*}
-%k \sum_{p = 0}^{\overline m} n_p = k N \geq \sum_{i=0}^N \|\mathbf{x}_i\|_0 \geq \frac{\alpha}{\beta} \sum_{i=0}^N \|\mathbf{\overline x}_i\|_0 = \frac{\alpha}{\beta} \sum_{p=0}^{\overline m} p n_p.
-%\end{align*}
-%Hence, 
-%\begin{align*}
-%\left[ \frac{\alpha(k+1)}{\beta} - k\right] \sum_{p = k+1}^{\overline m} n_p 
-%&\leq \sum_{p = k+1}^{\overline m} (\frac{\alpha}{\beta} p-k) n_p
-%\leq \sum_{p = 0}^k (k - \frac{\alpha}{\beta} p)n_p \\
-%&\leq k \sum_{p = 0}^k n_p 
-%\leq k(1-\frac{\alpha}{\beta})n_k + k|\mathcal{H}|(k-1){ \overline m \choose k-1}
-%\end{align*}
-
-%[Shit, we need $\alpha = \beta$.] Therefore, no more than $q$ vectors $\mathbf{\overline x}_i$ are \emph{not} $k$-sparse.
-Since for every $S \in \mathcal{H}$ there are over $(k-1){\overline m \choose k} + q$ vectors $\mathbf{x}_i$ supported there, it follows that more than $(k-1){\overline m \choose k}$ of them have corresponding $\mathbf{\overline x}_i$ that are $k$-sparse.
-The result now follows directly from Thm.~\ref{DeterministicUniquenessCorollary}.
-%\end{proof}
-
-%\pagebreak
-
-%\begin{corollary}\label{SLCoptL1}
-%If all of the assumptions of Thm.\ref{DeterministicUniquenessTheorem} hold, only now with more than $(k-1)\left[ {\overline m \choose k} + |\mathcal{H}|k{\overline m \choose k-1}\right]$ vectors $\mathbf{x}_i$ supported in each $S \in \mathcal{H}$, then every solution to Prob.~\ref{OptimizationProblemL1} for which the average absolute nonzero coefficient of the $\mathbf{\overline x}_i$ is bounded below by that of the $\mathbf{x}_i$ necessarily satisfies the implications \eqref{Cstable} and \eqref{b-PDa} of Thm.~\ref{DeterministicUniquenessTheorem}.
-%\end{corollary}
-
-%\begin{proof}[Proof of Cor.~\ref{SLCoptL1}]
-%Since the average absolute nonzero coefficient of the $\mathbf{x}_i$ is given by $\alpha = \sum_i \|\mathbf{x}_i\|_1 / \sum_i \|\mathbf{x}_i\|_0$, we have:
-%\begin{align*}
-%\alpha \sum_i \|\mathbf{\overline x}_i\|_0 \leq \sum_i \|\mathbf{\overline x}_i\|_1 \leq \sum_i \|\mathbf{x}_i\|_1 = \alpha \sum_i \|\mathbf{x}_i\|_0.
-%\end{align*}
-%
-%and the result follows by the same arguments as in the proof of Cor.~\ref{SLCopt}.
-%\end{proof}
-
-\end{document}

### 2020-07-16 manuscripts/thesis/proofs.tex
thesis

--- 2019-05-10 manuscripts/IEEE/final_submission.tex
@@
-% TODO: 
-% Make L_H a definition..? Change def of L to be 1-norm so we don't need these sqrt k's?
-% C_1 depends on J in Thm 1
-% also in proof of (7) x need not be *any* 2k-sparse vector...can instead restrict to some H...then 2k is restricted to half being on H.
-
-% Notes:
-%
-% Can we prove in a line or two that the inverse problem is stable by arguing that the function is bijective and closed therefore a homeomorphism?
-% Should we mention the notion of Grassmannian manifolds and that Theta is a metric on this space?
-% Change robustness to stability?
-%
-\documentclass[journal, twocolumn]{IEEEtran}
-
-% *** MATH PACKAGES ***
-\usepackage{amsmath, amssymb, amsthm} 
-\newtheorem{theorem}{Theorem}
-\newtheorem{lemma}{Lemma}
-\newtheorem{conjecture}{Conjecture}
-\newtheorem{problem}{Problem}
-\newtheorem{question}{Question}
-\newtheorem{proposition}{Proposition}
-\newtheorem{definition}{Definition}
-\newtheorem{corollary}{Corollary}
-\newtheorem{remark}{Remark}
-\newtheorem{example}{Example}
-
-\usepackage[pdftex]{graphicx}
-
-% *** ALIGNMENT PACKAGES ***
-\usepackage{array}
-\usepackage{cite}
-\usepackage{bm}
-
-% correct bad hyphenation here
-%\hyphenation{op-tical net-works semi-conduc-tor}
-
-\begin{document}
-
-%\title{When can a generating dictionary and sparse codes be recovered from noisy data?}
-%\title{When is the dictionary learning problem well-posed?}
-\title{On the uniqueness and stability of dictionaries \\ for sparse representation of noisy signals}
-%\title{When is the dictionary learning problem for sparse coding well-posed?}
-%\title{When is the sparsest representation unique?}
-%\title{When are sparse codes identifiable from their unknown noisy compressive measurements?}
-% FRITZ2: The title doesn't reflect the amount of new stuff, it seems incremental from the last one. It's not very meaningful.
-% FRITZ: Not everyone knows what well-posed means. You should mention recovery from noisy data in the title.
-
-\author{Charles~J.~Garfinkle and Christopher~J.~Hillar \\
-Redwood Center for Theoretical Neuroscience, Berkeley, CA, USA
-%\thanks{%e-mails: cjg@berkeley.edu, chillar@msri.org.  
-%CG and CH supported, in part, by NSF grant IIS-1219212 and the Statistical and Applied Mathematical Sciences Institute, under NSF DMS-1127914.}
-}
-
-\maketitle
-
-% \keywords{Sparse coding, dictionary learning, matrix factorization, compressed sensing, inverse problems, blind source separation}
-
-\begin{abstract}
-%Learning optimal dictionaries for sparse coding has exposed characteristic sparse features of many natural signals.
-However, there are few universal conditions guaranteeing the stability of such features in the presence of noise.
-Here, we prove very generally that optimal dictionaries and sparse codes are unique up to measurement error for all diverse enough datasets generated by the sparse coding model.
-Applications are given to data analysis, engineering, and neuroscience.
-Learning optimal dictionaries for sparse coding has exposed characteristic sparse features of many natural signals.
-However, universal guarantees of the stability of such features in the presence of noise are lacking.
-Here, we provide very general conditions guaranteeing when dictionaries yielding the sparsest encodings are unique and stable with respect to measurement or modeling error.
-We demonstrate that some or all original dictionary elements are recoverable from noisy data even if the dictionary fails to satisfy the spark condition, its size is overestimated, or only a polynomial number of distinct sparse supports appear in the data.
-Importantly, we derive these guarantees without requiring any constraints on the recovered dictionary beyond a natural upper bound on its size.
-Our results also yield an effective procedure sufficient to affirm if a proposed solution to the dictionary learning problem is unique within bounds commensurate with the noise.
-We suggest applications to data analysis, engineering, and neuroscience and close with some remaining challenges left open by our work.
-\end{abstract}
-
-% Optional adjustment to line up main text (after abstract) of first page with line numbers, when using both lineno and twocolumn options.
-% You should only change this length when you've finalised the article contents.
-
-\section{Introduction}\label{Intro}
-\IEEEPARstart{S}{parse} coding is a common modern approach to pattern analysis in signal processing whereby each of $N$ observed $n$-dimensional signal samples is viewed as a (noisy) linear combination of at most $k$ elementary waveforms drawn from some unknown ``dictionary" of size $m \ll N$ (see \cite{Zhang15} for a comprehensive review).
-%\IEEEPARstart{A}{}common modern approach to pattern analysis in signal processing is to view each of $N$ observed $n$-dimensional signal samples as a (noisy) linear combination of at most $k$ elementary waveforms drawn from some unknown ``dictionary" of size $m \ll N$ (see \cite{Zhang15} for a comprehensive review).
-Optimizing dictionaries subject to this and related sparsity constraints has revealed seemingly characteristic sparse structure in several signal classes of current interest (e.g., in vision \cite{wang2015sparse}).
-
-Of particular note are the seminal works in the field \cite{Olshausen96, hurri1996image, bell1997independent, van1998independent}, which discovered that dictionaries optimized for coding small patches of ``natural" images share qualitative similarities with linear filters estimated from response properties of simple-cell neurons in mammalian visual cortex.
-Curiously, these waveforms (e.g., ``Gabor'' wavelets) appear in dictionaries learned by a variety of algorithms trained over different natural image datasets, suggesting that learned features in natural signals may, in some sense, be canonical \cite{donoho2001can}.
-
-Motivated by these discoveries and more recent work relating compressed sensing \cite{eldar2012compressed} to a theory of information transmission through random wiring bottlenecks in the brain \cite{Isely10}, we address when dictionaries for sparse representation are indeed identifiable from data.
-Answers to this question may also have implications in practice wherever an appeal is made to latent sparse structure of data (e.g., forgery detection \cite{hughes2010, olshausen2010applied}; brain recordings \cite{jung2001imaging, agarwal2014spatially, lee2016sparse}; and gene expression \cite{wu2016stability}).
-
-While several algorithms have been recently proposed to provably recover unique dictionaries under specific conditions (see \cite[Sec.~I-E]{Sun16} for a summary of the state-of-the-art), few theorems can be invoked to justify the consistency of inference under this model of data more broadly.
-To our knowledge, a universal guarantee of the uniqueness and stability of learned dictionaries and the sparse representations they induce over noisy data has yet to appear in the literature.
-% in justifying the identification of forged paintings by their anomalous sparse representations \cite{hughes2010},
-
-Here, we prove very generally that uniqueness and stability is a typical property of sparse dictionary learning.
-More specifically, we show that matrices injective on a sparse domain are identifiable from \mbox{$N = m(k-1){m \choose k} + m$} noisy linear combinations of $k$ of their $m$ columns up to an error that is linear in the noise (Thm.~\ref{DeterministicUniquenessTheorem}).
-In fact, provided $n \geq \min(2k,m)$, in almost all cases the problem is well-posed, as per Hadamard \cite{Hadamard1902}, given a sufficient amount of data (Thm.~\ref{robustPolythm} and Cor.~\ref{ProbabilisticCor}).
-
-Our guarantees also hold for a related (and perhaps more commonly posed, e.g.
-\cite{rehnsommer2007}) optimization problem seeking a dictionary minimizing the average number of elementary waveforms required to reconstruct each sample of the dataset (Thm.~\ref{SLCopt}).
-To practical benefit, our results impose no restrictions on learned dictionaries (e.g., that they, too, be injective over some sparse domain) beyond an upper bound on dictionary size, which is necessary in any case to avoid trivial solutions (e.g., allowing $m = N$).
-%That is, every pair of solutions of comparable size has some number of dictionary elements in common (up to noise), and similarly so for the coefficients of sparse codes they induce.
-
-More precisely, let $\mathbf{A} \in \mathbb R^{n \times m}$ be a matrix with columns $\mathbf{A}_j$ ($j = 1,\ldots,m$) and let dataset $Z$ consist of measurements:
-\begin{align}\label{LinearModel}
-\mathbf{z}_i = \mathbf{A}\mathbf{x}_i + \mathbf{n}_i,\ \ \  \text{$i=1,\ldots,N$},
-\end{align}
-for $k$-\emph{sparse} $\mathbf{x}_i \in \mathbb{R}^m$ having at most $k<m$ nonzero entries and \emph{noise} $\mathbf{n}_i \in \mathbb{R}^n$, with bounded norm $\| \mathbf{n}_i \|_2 \leq  \eta$ representing our worst-case uncertainty in measuring the product $\mathbf{A}\mathbf{x}_i$.
-We first consider the following formulation of sparse coding.
-%The first mathematical problem we consider is the following.
-
-\begin{problem}\label{InverseProblem}
-Find a dictionary matrix $\mathbf{B}$ and $k$-sparse codes $\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N$ that satisfy $\|\mathbf{z}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \eta$ for all $i = 1,\ldots,N$.
-\end{problem}
-
-Note that every solution to Prob.~\ref{InverseProblem} represents infinitely many equivalent alternatives $\mathbf{BPD}$ and $\mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_1, \ldots, \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_N$ parametrized by a choice of permutation matrix $\mathbf{P}$ and invertible diagonal matrix $\mathbf{D}$.
-Identifying these ambiguities (labelling and scale) yields a single orbit of solutions represented by any particular set of elementary waveforms (the columns of $\mathbf{B}$) and their associated sparse coefficients (the entries of $\mathbf{\overline x}_i$) that reconstruct each data point $\mathbf{z}_i$.
-
-Previous theoretical work addressing the noiseless case $\eta =0$ (e.g., \cite{li2004analysis, Georgiev05, Aharon06, Hillar15}) for matrices $\mathbf{B}$ having exactly $m$ columns has shown that a solution to Prob.~\ref{InverseProblem}, when it exists, is unique up to such relabeling and rescaling provided the $\mathbf{x}_i$ are sufficiently diverse and $\mathbf{A}$ satisfies the \textit{spark condition}:
-\begin{align}\label{SparkCondition}
-\mathbf{A}\mathbf{x}_1 = \mathbf{A}\mathbf{x}_2 \implies \mathbf{x}_1 = \mathbf{x}_2, \ \ \ \text{for all $k$-sparse } \mathbf{x}_1, \mathbf{x}_2,
-\end{align}
-%
-which is necessary to guarantee the uniqueness of arbitrary $k$-sparse $\mathbf{x}_i$.
-We generalize these results to the practical setting  $\eta > 0$ by considering the following natural notion of stability with respect to measurement error.
-
-\begin{definition}\label{maindef}
-Fix $Y = \{ \mathbf{y}_1, \ldots, \mathbf{y}_N\} \subset \mathbb{R}^n$.
-We say $Y$ has a \textbf{$k$-sparse representation in $\mathbb{R}^m$} if there exists a matrix $\mathbf{A}$ and $k$-sparse $\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$ such that $\mathbf{y}_i = \mathbf{A}\mathbf{x}_i$ for all $i$.
-This representation is \textbf{stable} if for every $\delta_1, \delta_2 \geq 0$, there exists some $\varepsilon = \varepsilon(\delta_1, \delta_2)$ that is strictly positive for positive $\delta_1$ and $\delta_2$ such that if $\mathbf{B}$ and $k$-sparse $\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N \in \mathbb{R}^m$ satisfy:
-\begin{align*}
-	\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \varepsilon(\delta_1, \delta_2),\ \   \text{for all $i=1,\ldots,N$},
-\end{align*}
-then there is some permutation matrix $\mathbf{P}$ and invertible diagonal matrix $\mathbf{D}$ such that for all $i, j$:
-\begin{align}\label{def1}
-\|\mathbf{A}_j - (\mathbf{BPD})_j\|_2 \leq \delta_1 \ \text{and} \ \|\mathbf{x}_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_i\|_1 \leq \delta_2.
-\end{align}
-\end{definition}
-
-To see how Prob.
-\ref{InverseProblem} motivates Def.
-\ref{maindef}, suppose that $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$ and fix $\delta_1, \delta_2$ to be the desired accuracies of recovery in \eqref{def1}.
-Consider any dataset $Z$ generated as in \eqref{LinearModel} with $\eta \leq \frac{1}{2} \varepsilon(\delta_1, \delta_2)$.
-Using the triangle inequality, it follows that any $n \times m$ matrix $\mathbf{B}$ and $k$-sparse $\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N$ solving Prob.~\ref{InverseProblem} are necessarily within $\delta_1$ and $\delta_2$ of the original dictionary $\mathbf{A}$ and codes $\mathbf{x}_1, \ldots, \mathbf{x}_N$, respectively.\footnote{We mention that the different norms in \eqref{def1} reflect the distinct meanings typically ascribed to the dictionary and sparse codes in modeling data.}
-
-The main result of this work is a very general uniqueness theorem for sparse coding (Thm.~\ref{DeterministicUniquenessTheorem}) directly 
-implying (Cor.~\ref{DeterministicUniquenessCorollary}), which guarantees that sparse representations of a dataset $Z$ are unique up to noise whenever generating dictionaries $\mathbf{A}$ satisfy a spark condition on supports and the original sparse codes $\mathbf{x}_i$ are sufficiently diverse (e.g., Fig.~\ref{noisyrecovery}).
-Moreover, we provide an explicit, computable $\varepsilon(\delta_1, \delta_2)$ in (\ref{epsdel}) that is linear in desired accuracy $\delta_1$, and essentially so in $\delta_2$.
-
-In the next section, we give formal statements of these findings.
-We then extend the same guarantees (Thm.~\ref{SLCopt}) to the following alternate formulation of dictionary learning, which minimizes the total number of nonzero entries in sparse codes.
-
-\begin{problem}\label{OptimizationProblem}
-Find matrices $\mathbf{B}$ and vectors \mbox{$\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N$} solving:
-\begin{align}\label{minsum}
-\min \sum_{i = 1}^N \|\mathbf{\overline x}_{i}\|_0 \ \
-\text{subject to} \ \ \|\mathbf{z}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \eta, \ \text{for all $i$}.
-\end{align}
-\end{problem}
-
-Our development of Thm.~\ref{DeterministicUniquenessTheorem} is general enough to provide some uniqueness and stability even when generating $\mathbf{A}$ do not fully satisfy (\ref{SparkCondition}) and recovery dictionaries $\mathbf{B}$ have more columns than $\mathbf{A}$.
-Moreover, the approach incorporates a combinatorial theory for designing generating codes that should be of independent interest.
-We also give brief arguments adapting our results to dictionaries and codes drawn from probability distributions (Cor.~\ref{ProbabilisticCor}).
-The technical proofs of Thms.~\ref{DeterministicUniquenessTheorem} and ~\ref{SLCopt} are deferred to Sec.~\ref{DUT}, following some necessary definitions and a fact in combinatorial matrix analysis (Lem.~\ref{MainLemma}; proven in the Appendix).
-Finally, we discuss in Sec.~\ref{Discussion} applications of our mathematical observations as well as open questions.
-%The Appendix contains a proof of Lem.~\ref{MainLemma}.
-
-\section{Results}\label{Results}
-
-%Denote by $\mathbf{x}^J$ the subvector formed from the entries of $\mathbf{x}$ indexed by $J$. 
-%A set of $k$-sparse vectors is said to be in \emph{general linear position} when any $k$ of them are linearly independent.
-
-Precise statements of our results require that we first identify some combinatorial criteria on the supports\footnote{Recall that a vector $\mathbf{x}$ is said to be \emph{supported} in $S$ when $\mathbf{x} \in \text{\rm span}\{\mathbf{e}_j: j\in S\}$, with $\mathbf{e}_j$ forming the standard column basis.} of sparse vectors.
-Let $\{1, \ldots, m\}$ be denoted $[m]$, its power set $2^{[m]}$, and ${[m] \choose k}$ the set of subsets of $[m]$ of size $k$.
-A \emph{hypergraph} on vertices $[m]$  is simply any subset $\mathcal{H} \subseteq 2^{[m]}$.
-We say that $\mathcal{H}$ is \textit{$k$-uniform} when $\mathcal{H} \subseteq {[m] \choose k}$.
-The \emph{degree} $\deg_\mathcal{H}(i)$ of a node $i \in [m]$ is the number of sets in $\mathcal{H}$ that contain $i$, and we say $\mathcal{H}$ is \emph{regular} when for some $r$ we have $\deg_\mathcal{H}(i) = r$ for all $i$ (given such an $r$, we say $\mathcal{H}$ is \textit{$r$-regular}).
-We also write $2\mathcal{H} := \{ S \cup S': S, S' \in \mathcal{H}\}$.
-The following class of structured hypergraphs is a key ingredient in this work.
-
-\begin{definition}\label{sip}
-Given $\mathcal{H} \subseteq 2^{[m]}$, the \textbf{star} $\sigma(i)$ is the collection of sets in $\mathcal{H}$ containing $i$.
-We say $\mathcal{H}$ has the \textbf{singleton intersection property} (\textbf{SIP}) when $\cap \sigma(i) = \{i\}$ for all $i \in [m]$.
-\end{definition}
-
-We next give a quantitative generalization of the spark condition (\ref{SparkCondition}) to combinatorial subsets of supports.
-The \emph{lower bound} of an $n \times m$ matrix $\mathbf{M}$ is the largest $\alpha$ with \mbox{$\|\mathbf{M}\mathbf{x}\|_2 \geq \alpha\|\mathbf{x}\|_2$} for all $\mathbf{x} \in \mathbb{R}^m$ \cite{Grcar10}.
-By compactness of the unit sphere, every injective linear map has a positive lower bound; hence, if $\mathbf{M}$ satisfies \eqref{SparkCondition}, then submatrices formed from $2k$ of its columns or less have strictly positive lower bounds.
-
-The lower bound of a matrix is generalized below in (\ref{Ldef}) by restricting it to the spans of certain submatrices\footnote{See \cite{vidal2005generalized} for an overview of the related ``union of subspaces" model.} associated with a hypergraph $\mathcal{H} \subseteq {[m] \choose k}$ of column indices.
-Let $\mathbf{M}_S$ denote the submatrix formed by the columns of a matrix $\mathbf{M}$ indexed by $S \subseteq [m]$ (setting $\mathbf{M}_\emptyset := \mathbf{0}$).
-In the sections that follow, we shall also let $\bm{\mathcal{M}}_S$ denote the column-span of a submatrix $\mathbf{M}_S$, and $\bm{\mathcal{M}}_\mathcal{G}$ to denote $\{\bm{\mathcal{M}}_S\}_{S \in \mathcal{G}}$.
-We define:  % Define $L_\mathcal{H}(\mathbf{M})$ as follows:
-%\begin{align*} 
-%L_\mathcal{H}(\mathbf{M}) := \min \left\{ \frac{ \|\mathbf{M}(\mathbf{x}_1-\mathbf{x}_2)\|_2 }{ \sqrt{2k} \|\mathbf{x}_1-\mathbf{x}_2\|_2} : \mathbf{x}_1, \mathbf{x}_2 \in \cup_{S \in \mathcal{H}} \bm{\mathcal{M}}_S \right\},
-%\end{align*} 
-%
-%where we write $L_{2k}$ in place of $L_\mathcal{H}$ when $\mathcal{H} = {[m] \choose k}$.
-Note that if $\mathcal{H}$ covers $[m]$, then $L_2 > L_\mathcal{H}$.\footnote{The reader should beware that $L_2 = L_{[m]}$, whereas $L = L_{\{[m]\}}$.
-For even $k$, the quantity $1 - \sqrt{k} L_k(\mathbf{M})$ is also known in the compressed sensing literature as the (asymmetric) lower restricted isometry constant \cite{Blanchard2011}.} Clearly, for any $\mathbf{M}$ satisfying \eqref{SparkCondition}, we have $L_{k'}(\mathbf{M}) > 0$ for  $k' \leq 2k$.
-%\begin{align*}
-%L_\mathcal{H}(\mathbf{M}) := \min \left\{ \frac{ \|\mathbf{M}_S\mathbf{x}\|_2 }{ \sqrt{k} \|\mathbf{x}\|_2} : S \in \mathcal{H} \right\},
-%\end{align*} 
-%\begin{align*}
-%L_\mathcal{H}(\mathbf{M}) := \max \left\{ \ falpha: \|\mathbf{M}_S\mathbf{x}\|_2 \geq \alpha \sqrt{k} \|\mathbf{x}\|_2 : S \in \mathcal{H}, \ \ \mathbf{x} \in \mathbb{R}^m \right\},
-%\end{align*} 
-\begin{align}\label{Ldef}
-L_\mathcal{H}(\mathbf{M}) := \min \left\{ \frac{\|\mathbf{M}_S\mathbf{x}\|_2}{ \sqrt{k} \|\mathbf{x}\|_2} : S \in \mathcal{H}, \ \mathbf{0} \neq \mathbf{x} \in \mathbb{R}^{|S|} \right\},
-\end{align} 
-%
-writing also $L_{k}$ in place of $L_\mathcal{H}$ when $\mathcal{H} = {[m] \choose k}$.\footnote{In compressed sensing literature, \mbox{$1 - \sqrt{k} L_k(\mathbf{M})$}  is the asymmetric lower restricted isometry constant for $\mathbf{M}$ with unit $\ell_2$-norm columns \cite{Blanchard2011}.}  As explained above, compactness implies that $L_{2k}(\mathbf{M}) > 0$ for all $\mathbf{M}$ satisfying \eqref{SparkCondition}.
-Clearly, $L_{\mathcal{H}'}(\mathbf{M}) \geq L_\mathcal{H}(\mathbf{M})$ whenever $\mathcal{H}' \subseteq \mathcal{H}$, and similarly any $k$-uniform $\mathcal{H}$ satisfying $\cup \mathcal{H} = [m]$ has $L_2 \geq L_{2\mathcal{H}} \geq L_{2k}$ (letting $L_{2k}$ := $L_m$ whenever $2k > m$).
-
-We are now in a position to state our main result, though for expository purposes we leave the quantity $C_1$ %(a function of $\mathbf{A}$, $\mathbf{x}_1, \ldots, \mathbf{x}_N$, and $\mathcal{H}$) 
-undefined until Sec.~\ref{DUT}. All results  below assume real matrices and vectors.
-
-%eps-tightness COUNTER-EXAMPLE:
-%Consider the alternate dictionary $B = \left(\mathbf{0}, \frac{1}{2}(\mathbf{e}_1 + \mathbf{e}_2), \mathbf{e}_3, \ldots, \mathbf{e}_{m} \right)$ and sparse codes $\mathbf{b}_i = \mathbf{e}_2$ for $i = 1, 2$ and $\mathbf{b}_i = \mathbf{e}_i$ for $i = 3, \ldots, m$.
-Then $|A\mathbf{a}_i - B\mathbf{b}_i| = 1/\sqrt{2}$ for $i = 1, 2$ (and $0$ otherwise).
-If there were permutation and invertible diagonal matrices $P \in \mathbb{R}^{m \times m}$ and $D \in \mathbb{R}^{m \times m}$ such that $|(A-BPD)\mathbf{e}_i| \leq C\varepsilon$ for all $i \in [m]$, then we would reach the contradiction $1 = |P^{-1}\mathbf{e}_1|_2 = |(A-BPD)P^{-1}\mathbf{e}_1|_2 \leq 1/\sqrt{2}$.
-
-\begin{theorem}\label{DeterministicUniquenessTheorem}
-%Fix integers $n, k, m$ and $\overline m$. 
-If an $n \times m$ matrix $\mathbf{A}$ satisfies $L_{2\mathcal{H}}(\mathbf{A}) > 0$ for some $r$-regular $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP, and $k$-sparse \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} include more than $(k-1){\overline m \choose k}$ vectors in general linear position\footnote{Recall that a set of vectors sharing support $S$ are in \emph{general linear position} when any $|S|$ of them are linearly independent.} supported in each $S \in \mathcal{H}$, then the following recovery guarantees hold for $C_1 > 0$ given by \eqref{Cdef1}.
-
-\textbf{Dictionary Recovery:} Fix $\varepsilon < L_{2}(\mathbf{A}) / C_1$.\footnote{Note that the condition $\varepsilon < L_2(\mathbf{A}) /C_1$ is necessary; otherwise, with \mbox{$\mathbf{A}$ = $\mathbf{I}$} (the identity matrix) and $\mathbf{x}_i = \mathbf{e}_i$, the matrix $\mathbf{B} = \left[\mathbf{0}, \frac{1}{2}(\mathbf{e}_1 + \mathbf{e}_2), \mathbf{e}_3, \ldots, \mathbf{e}_{m} \right]$ and sparse codes $\mathbf{\overline x}_i = \mathbf{e}_2$ for $i = 1, 2$ and $\mathbf{\overline x}_i = \mathbf{e}_i$ for $i \geq 3$ satisfy $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline x}_i \|_2 \leq \varepsilon$ but nonetheless violate \eqref{Cstable}.} If an $n \times \overline m$ matrix $\mathbf{B}$ has, for every $i \in [N]$, an associated $k$-sparse $\mathbf{\overline x}_i$ satisfying \mbox{$\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \varepsilon$}, then $\overline m \geq m$, and provided that $\overline m (r-1) < mr$, there is a permutation matrix $\mathbf{P}$ and an invertible diagonal matrix $\mathbf{D}$ such that:
-\begin{align}\label{Cstable}
-\|\mathbf{A}_j- (\mathbf{BPD})_j\|_2 \leq C_1 \varepsilon, \ \ \text{for all } j \in J,
-\end{align}
-%
-for some $J \subseteq [m]$ of size \mbox{$m - (r-1)(\overline m - m)$}. 
-% $\overline m - r(\overline m - m)$
-
-\textbf{Code Recovery:} If, moreover, $\mathbf{A}_J$ satisfies \eqref{SparkCondition} and $\varepsilon < L_{2k}(\mathbf{A}_J) / C_1$, then $(\mathbf{BP})_J$ also satisfies \eqref{SparkCondition} with $L_{2k}(\mathbf{BP}_J) \geq (L_{2k}(\mathbf{A}_J) - C_1 \varepsilon) / \|\mathbf{D}_J\|_1$, and for all $i \in [N]$:
-\begin{align}\label{b-PDa}
-%\|\mathbf{x}^J_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}^{\overline J}_i\|_1 &\leq  \left( \frac{ 1+C_1 \|\mathbf{x}^{J}_i\|_1 }{ L_{2k}(\mathbf{A}) -  C_1\varepsilon } \right) \varepsilon \ \  \text{for $i \in [N]$}.
-\|(\mathbf{x}_i)_J - (\mathbf{D}^{-1}\mathbf{P}^{\top} \mathbf{\overline x}_i)_J\|_1 &\leq  \left( \frac{ 1+C_1 \|(\mathbf{x}_i)_J\|_1 }{ L_{2k}(\mathbf{A}_J) -  C_1\varepsilon } \right) \varepsilon,
-\end{align}
-%
-where subscript $(\cdot)_J$ here represents the subvector formed from restricting to coordinates indexed by $J$.
-\end{theorem}
-
-%We delay defining the explicit constant $C_1$ until Section \ref{DUT} (\eqref{Cdef1}).
-%To be clear, the implication of Thm.~\ref{DeterministicUniquenessTheorem} is that $Y = \{\mathbf{Ax}_1, \ldots, \mathbf{Ax}_N\}$ has a stable $k$-sparse representation in $\mathbb{R}^m$, with \eqref{def1} guaranteed provided $\varepsilon$ in Def.~\ref{maindef} does not exceed:
-In words, Thm.~\ref{DeterministicUniquenessTheorem} says that the smaller the regularity $r$ of the original support hypergraph $\mathcal{H}$ or the difference $\overline m - m$ between the assumed and actual number of elements in the latent dictionary, the more columns and coefficients of the original dictionary $\mathbf{A}$ and sparse codes $\mathbf{x}_i$ are guaranteed to be contained (up to noise) in the appropriately labelled and scaled recovered dictionary $\mathbf{B}$ and codes $\mathbf{\overline x}_i$, respectively.
-
-In the important special case when $\overline m = m$, the theorem directly implies that  $Y = \{\mathbf{Ax}_1, \ldots, \mathbf{Ax}_N\}$ has a stable $k$-sparse representation in $\mathbb{R}^m$, with inequalities \eqref{def1} guaranteed in Def.~\ref{maindef} for the following worst-case error $\varepsilon$:
-\begin{align}\label{epsdel}
-\varepsilon(\delta_1, \delta_2) := \min \left\{ \frac{\delta_1}{ C_1 }, \frac{ \delta_2 L_{2k}(\mathbf{A})}{ 1 + C_1 \left( \delta_2 + \max_{i \in [N]} \|\mathbf{x}_i\|_1  \right) } \right\}.
-\end{align}
-
-Since sparse codes in general linear position are straightforward to produce with a ``Vandermonde''  construction (i.e., by choosing columns of the matrix $[\gamma_{i}^j]_{i,j=1}^{k,N}$, for distinct nonzero $\gamma_i$), we have the following direct consequence of Thm.~\ref{DeterministicUniquenessTheorem}.
-
-\begin{corollary}\label{DeterministicUniquenessCorollary}
-Given any regular hypergraph $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP, there are $N =  |\mathcal{H}| \left[ (k-1){m \choose k} + 1  \right]$ vectors \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} such that every matrix $\mathbf{A}$ satisfying spark condition \eqref{SparkCondition} generates $Y = \{\mathbf{A}\mathbf{x}_1, \ldots, \mathbf{A}\mathbf{x}_N\}$ with a stable $k$-sparse representation in $\mathbb{R}^m$ for $\varepsilon(\delta_1,\delta_2)$ given by \eqref{epsdel}.
-\end{corollary}
-
-% prev
-%\begin{corollary}\label{DeterministicUniquenessCorollary}
-%Given any regular hypergraph $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP, there are $N =  |\mathcal{H}| \left[ (k-1){m \choose k} + 1  \right]$ vectors \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} such that every matrix $\mathbf{A}$ with $L_{2\mathcal{H}}(\mathbf{A}) > 0$ generates a dataset $Y = \{\mathbf{A}\mathbf{x}_1, \ldots, \mathbf{A}\mathbf{x}_N\}$ with a stable $k$-sparse representation in $\mathbb{R}^m$ for $\varepsilon(\delta_1,\delta_2)$ as in \eqref{epsdel}.
-%\end{corollary}
-
-%We claim that the assumptions of Thm.~\ref{DeterministicUniquenessTheorem} are easily met with deterministic constructions.
-In particular, sparse codes in general linear position are straightforward to produce using a ``Vandermonde'' matrix construction (i.e.
-use the columns of the matrix $[\gamma_{i}^j]_{i,j=1}^{k,N}$, for distinct nonzero $\gamma_i$).
-%
-
-% (Prob.~\ref{InverseProblem}).
-%=======
-%An immediate practical implication of this result is that there exists a practical procedure to affirm if one's proposed solution $(\mathbf{B}, \mathbf{\overline x}_1, \ldots, \mathbf{x}_N)$ to Prob.~\ref{InverseProblem} is indeed unique (up to noise and inherent ambiguities): simply check that $\mathbf{B}$ and the $\mathbf{\overline x}_i$ satisfy the assumptions on $\mathbf{A}$ and the $\mathbf{x}_i$ in Thm.~\ref{DeterministicUniquenessTheorem}.
-%
-%%In fact, a more general result (stated clearly in the next section) can be gleaned from our method of proving Thm.~\ref{DeterministicUniquenessTheorem}.
-Briefly, in cases where $\mathbf{B}$ has $\overline m \neq m$ columns, or $\mathcal{H}$ is not regular or only partially satisfying the SIP, a relation between $\overline m$ and the degree sequence of nodes in $\mathcal{H}$ gives indices $J \subseteq [m]$ defining a submatrix $\mathbf{A}_J$ and subvectors $\mathbf{x}_i^J$ that are recoverable in the sense of \eqref{Cstable} and \eqref{b-PDa}.
-For example, if $\mathcal{H}$ is $\ell$-regular with the SIP but $m \leq \overline m < m\ell/(\ell - 1)$ then we have nonzero $|J| = \overline m - \ell(\overline m - m)$.
-The implication here is that the smaller the difference $\overline m - m$, the more columns and code entries of the original $n \times m$ dictionary $\mathbf{A}$ and codes $\mathbf{x}_i$ contained (up to noise) in the appropriately scaled $n \times \overline m$ dictionary $\mathbf{B}$ and codes $\mathbf{\overline x}_i$.
-When $\overline m = m$, we recover Thm.~\ref{DeterministicUniquenessTheorem}.
-%
-%%In fact, even if $\mathcal{H}$ is not regular or only partially satisfies the SIP, a relation between $\overline m$ and the degree sequence of nodes in $\mathcal{H}$ may give the indices $J \subseteq [m]$.
-For sake of brevity, we delay to the next section a clear statement of this more general result.
-%
-%Regarding the assumptions of Thm.~\ref{DeterministicUniquenessTheorem}, it so happens that sparse codes $\mathbf{x}_i$ in general linear position are straightforward to produce with a ``Vandermonde'' matrix construction \cite{Hillar15}, leading to the following.
-%>>>>>>> d1407a275dc391dabad7bb62d3e659f9a4ac4624
-
-% Needs to be L_{2k}(A) > 0 to guarantee sparse vector recovery
-
-%We also have the following refinement of a result in \cite{Hillar15}:
-%\begin{corollary}
-%Those square matrices $\mathbf{A}$ that satisfy \mbox{$L_{2\mathcal{H}}(\mathbf{A}) > 0$} for some regular $k$-uniform hypergraph $\mathcal{H}$ with the SIP and have the property that $\mathbf{Ax}$ is $k$-sparse for all $k$-sparse $\mathbf{x}$ with support in $\mathcal{H}$ are the matrices $\mathbf{PD}$, where $\mathbf{P}$ and $\mathbf{D}$ run over permutation and invertible diagonal matrices, respectively.
-%\end{corollary}
-
-One can easily verify that for every $k < m$ there are regular $k$-uniform hypergraphs $\mathcal{H}$ with the SIP besides the obvious $\mathcal{H} = {[m] \choose k}$.
-For instance, take $\mathcal{H}$ to be the $k$-regular set of consecutive intervals of length $k$ in some cyclic order on $[m]$.
-In this case, a direct consequence of Cor.~\ref{DeterministicUniquenessCorollary} is rigorous verification of the lower bound \mbox{$N = m(k-1){m \choose k} + m$} for sufficient sample size from the introduction.
-Special cases allow for even smaller hypergraphs.
-For example, if $k = \sqrt{m}$, then a 2-regular $k$-uniform hypergraph with the SIP can be constructed as the $2k$ rows and columns formed by arranging the elements of $[m]$ into a square grid.
-
-%\cite{li2004analysis, Georgiev05, Aharon06, Hillar15}
-We should stress here that framing the problem in terms of hypergraphs has allowed us to show, unlike in previous research on the subject, that the matrix $\mathbf{A}$ need not necessarily satisfy \eqref{SparkCondition} to be recoverable from data.
-As an example, let $\mathbf{A} = [ \mathbf{e}_1, \ldots, \mathbf{e}_5, \mathbf{v}]$ with $\mathbf{v} = \mathbf{e}_1 + \mathbf{e}_3 + \mathbf{e}_5$ and take $\mathcal{H}$ to be all consecutive pairs of indices $1, \ldots ,6$ arranged in cyclic order.
-Then for $k=2$, the matrix $\mathbf{A}$ fails to satisfy \eqref{SparkCondition} while still obeying the assumptions of Thm.~\ref{DeterministicUniquenessTheorem} for dictionary recovery.%, hence guaranteeing \eqref{Cstable} .
-%(since $\{ \mathbf{A}_1, \mathbf{A}_3, \mathbf{A}_5, \mathbf{A}_6\}$ is not a linearly independent set).
-%This weakening allows for a practical (polynomial) amount of data to still guarantee a stable dictionary in the case where the set of sparse supports for the $\mathbf{\overline x}_i$ is known to have a size that grows polynomially in $m$ and $k$.
-
-A practical implication of Thm.~\ref{DeterministicUniquenessTheorem} is the following: there is an effective procedure sufficient to affirm if a proposed solution to Prob.~\ref{InverseProblem} is indeed unique (up to noise and inherent ambiguities).
-One need simply check that the matrix and codes satisfy the (computable) assumptions of Thm.~\ref{DeterministicUniquenessTheorem} on $\mathbf{A}$ and the $\mathbf{x}_i$.
-In general, however, there is no known efficient procedure.
-We defer a brief discussion on this point to the next section.
-%Another practical implication of Thm.\ref{DeterministicUniquenessTheorem} is the following: there is an effective procedure sufficient to affirm if a proposed solution $(\mathbf{B}, \mathbf{\overline x}_1, \ldots, \mathbf{x}_N)$ to Prob.~\ref{InverseProblem} is indeed unique (up to noise and inherent ambiguities).
-One simply checks that $\mathbf{B}$ and the $\mathbf{\overline x}_i$ satisfy the respective assumptions of Thm.~\ref{DeterministicUniquenessTheorem}.
-%. on $\mathbf{A}$ and the $\mathbf{x}_i$, respectively.
-
-%In fact, a more general result (stated clearly in the next section) can be gleaned from our method of proving Thm.~\ref{DeterministicUniquenessTheorem}.
-Briefly, in cases where $\mathbf{B}$ has $\overline m \neq m$ columns, or $\mathcal{H}$ is not regular or only partially satisfying the SIP, a relation between $\overline m$ and the degree sequence of nodes in $\mathcal{H}$ gives indices $J \subseteq [m]$ defining a submatrix $\mathbf{A}_J$ and subvectors $\mathbf{x}_i^J$ that are recoverable in the sense of \eqref{Cstable} and \eqref{b-PDa}.
-For example, if $\mathcal{H}$ is $\ell$-regular with the SIP but $m \leq \overline m < m\ell/(\ell - 1)$ then we have nonzero $|J| = \overline m - \ell(\overline m - m)$.
-The implication here is that the smaller the difference $\overline m - m$, the more columns and code entries of the original $n \times m$ dictionary $\mathbf{A}$ and codes $\mathbf{x}_i$ contained (up to noise) in the appropriately scaled $n \times \overline m$ dictionary $\mathbf{B}$ and codes $\mathbf{\overline x}_i$.
-When $\overline m = m$, we recover Thm.~\ref{DeterministicUniquenessTheorem}.
-
-%In fact, even if $\mathcal{H}$ is not regular or only partially satisfies the SIP, a relation between $\overline m$ and the degree sequence of nodes in $\mathcal{H}$ may give the indices $J \subseteq [m]$.
-For sake of brevity, we delay to the next section a clear statement of this more general result.
-
-%=======
-%One can also verify that for every $k < m$, there is a regular $k$-uniform hypergraph that satisfies the SIP; for instance, take $\mathcal{H}$ to be the consecutive intervals of length $k$ in some cyclic order on $[m]$, for which Cor.~\ref{DeterministicUniquenessCorollary} implies the lower bound for sample size $N$ from the introduction.
-In many cases, however, the SIP is achievable with far fewer supports; for example, when $k = \sqrt{m}$, take $\mathcal{H}$ to be the $2k$ rows and columns formed by arranging $[m]$ in a square grid.
-%>>>>>>> d1407a275dc391dabad7bb62d3e659f9a4ac4624
-
-%As mentioned above, there exist $k$-uniform regular hypergraphs $\mathcal{H}$ with the SIP having cardinality $|\mathcal{H}| = m$,
-
-A less direct consequence of Thm.~\ref{DeterministicUniquenessTheorem} is the following uniqueness and stability guarantee for solutions to Prob.~\ref{SLCopt}.
-%, the usual optimization problem of interest for those applying dictionary learning to their data.
-
-\begin{theorem}\label{SLCopt}
-Fix a matrix $\mathbf{A}$ and vectors $\mathbf{x}_i$ satisfying the assumptions of Thm.~\ref{DeterministicUniquenessTheorem}, only now with over \mbox{$(k-1)\left[ {\overline m \choose k} + |\mathcal{H}|k{\overline m \choose k-1}\right]$} vectors supported in general linear position in each $S \in \mathcal{H}$.
-Every solution to Prob.~\ref{OptimizationProblem} (with $\eta = \varepsilon/2$) satisfies recovery guarantees \eqref{Cstable} and \eqref{b-PDa} when the corresponding bounds on $\eta$ are met.
-\end{theorem}
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=.24 \linewidth]{figs/basis.png}
-% \includegraphics[width=.25 \linewidth]{figs/Ahat_FastICA_M640_K8_noise0_2042}
-%\includegraphics[width=.24 \linewidth]{figs/Ahat_FastICA_M640_K8_noise0_4083.png}
-\includegraphics[width=.24 \linewidth]{figs/Ahat_FastICA_M640_K8_noise1_0205.png}
-\includegraphics[width=.24 \linewidth]{figs/Ahat_FastICA_M640_K8_noise2_0409.png}
-\includegraphics[width=.24 \linewidth]{figs/Ahat_FastICA_M640_K8_noise5_1021.png}
-\caption{\textbf{Learning a dictionary from increasingly noisy data}.
-The (unraveled) basis elements of the $8 \times 8$ discrete cosine transform (DCT) form the 64 columns of the left-most matrix above.
-Three increasingly imprecise dictionaries (columns reordered to best match original) are recovered by FastICA \cite{hyvarinen2000independent} trained on data generated from $8$-sparse linear combinations of DCT elements corrupted with additive noise (increasing from left to right).}
-\vspace{-.6 cm}
-\label{noisyrecovery}
-\end{center}
-\end{figure}
-
-Another extension of Thm.~\ref{DeterministicUniquenessTheorem} can be derived from the following algebraic characterization of the spark condition.
-Letting $\mathbf{A}$ be the $n \times m$ matrix of $nm$ indeterminates $A_{ij}$, the reader may work out why substituting real numbers for the $A_{ij}$ yields a matrix satisfying \eqref{SparkCondition} if and only if the following polynomial evaluates to a nonzero number:
-\begin{align*}
-f(\mathbf{A}) := \prod_{S \in {[m] \choose 2k}} \sum_{S' \in {[n] \choose 2k}} (\det \mathbf{A}_{S',S})^2,
-\end{align*}
-%
-where for any $S' \in {[n] \choose 2k}$ and $S \in {[m] \choose 2k}$, the symbol $\mathbf{A}_{S',S}$ denotes the submatrix of entries $A_{ij}$ with $(i,j) \in S' \times S$.\footnote{The large number of terms in this product is likely necessary given that deciding whether or not a matrix satisfies the spark condition is NP-hard \cite{tillmann2014computational}.}
-
-Since $f$ is analytic, having a single substitution of a real matrix $\mathbf{A}$ satisfying $f(\mathbf{A}) \neq 0$ implies that the zeroes of $f$ form a set of (Borel) measure zero.
-Such a matrix is easily constructed by adding rows of zeroes to a $\min(2k,m) \times m$ Vandermonde matrix as mentioned previously, so that every sum in the product defining $f$ above is strictly positive.
-Thus, almost every $n \times m$ matrix with $n \geq \min(2k,m)$ satisfies \eqref{SparkCondition}.
-
-%Another extension of Thm.~\ref{DeterministicUniquenessTheorem} arises from the following analytic characterization of the spark condition.
-Let $\mathbf{A}$  be the $n \times m$ matrix of $nm$ indeterminates $A_{ij}$.
-When real numbers are substituted for $A_{ij}$, the resulting matrix satisfies \eqref{SparkCondition} if and only if the following polynomial is nonzero:
-%\begin{align*}
-%f(\mathbf{A}) := \prod_{S \in {[m] \choose k}} \sum_{S' \in {[n] \choose k}} (\det \mathbf{A}_{S',S})^2,
-%\end{align*}
-%
-%where for any $S' \in {[n] \choose k}$ and $S \in {[m] \choose k}$, the symbol $\mathbf{A}_{S',S}$ denotes the submatrix of entries $A_{ij}$ with $(i,j) \in S' \times S$.
-We note that the large number of terms in this product is likely necessary due to the NP-hardness of deciding whether a given matrix $\mathbf{A}$ satisfies the spark condition \cite{tillmann2014computational}.
-
-%Since $f$ is analytic, having a single substitution of a real matrix $\mathbf{A}$ with $f(\mathbf{A}) \neq 0$ necessarily implies that the zeroes of $f$ form a set of measure zero.
-Fortunately, such a matrix $\mathbf{A}$ is easily constructed by adding rows of zeroes to any $\min(2k,m) \times m$ Vandermonde matrix as described above (so that each term in the product above for $f$ is nonzero).
-Hence, almost every $n \times m$ matrix with $n \geq \min(2k,m)$ satisfies \eqref{SparkCondition}.
-
-We claim that a similar phenomenon applies to datasets of vectors with a stable sparse representation.
-Briefly, following the same procedure as in \cite[Sec.~IV]{Hillar15}, for $k < m$ and $n \geq \min(2k, m)$, we may consider the ``symbolic'' dataset $Y = \{\mathbf{A}\mathbf{x}_1,\ldots,\mathbf{A} \mathbf{x}_N\}$ generated by an indeterminate $n \times m$ matrix $\mathbf{A}$ and $m$-dimensional $k$-sparse vectors $\mathbf{x}_1, \ldots, \mathbf{x}_N$ indeterminate within their supports, which form a regular hypergraph $\mathcal{H} \subseteq {[m] \choose k}$ satisfying the SIP.
-Restricting \mbox{$(k-1){m \choose k} + 1$} indeterminate $\mathbf{x}_i$ to each support in $\mathcal{H}$, and letting $\textbf{M}$ be the $n \times N$ matrix with columns $\mathbf{A}\mathbf{x}_i$, it can be checked that when $f(\mathbf{M}) \neq 0$ for a substitution of real numbers for the indeterminates, all of the assumptions on $\mathbf{A}$ and the $\mathbf{x}_i$ in Thm.~\ref{DeterministicUniquenessTheorem} are satisfied.
-We therefore have the following.
-% ; in particular, $\mathbf{A}$ satisfies \eqref{SparkCondition}
-
-\begin{theorem}\label{robustPolythm}
-%Let $\mathbf{A}$ and $\mathbf{x}_1, \ldots, \mathbf{x}_N$ be an indeterminate $n \times m$ matrix and sequence of $m$-dimensional vectors, respectively. 
-There is a polynomial in the entries of $\mathbf{A}$ and the $\mathbf{x}_i$ that evaluates to a nonzero number only when $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$.
-In particular, almost all substitutions impart to $Y$ this property.
-\end{theorem}
-
-%To extend this observation to arbitrary probability distributions, note that if a set of measure spaces $\{(X_{\ell}, \nu_{\ell})\}_{\ell=1}^p$ has measures $\nu_{\ell}$ absolutely continuous with respect to the standard Borel measure on $\mathbb{R}$ for all $\ell \in [p]$, then the product measure $\prod_{\ell=1}^p \nu_{\ell}$ is also absolutely continuous with respect to the standard Borel product measure on $\mathbb{R}^p$ (e.g., see \cite{folland2013real}).
-This fact combined with Thm.~\ref{robustPolythm} implies the following.
-To extend this observation to arbitrary probability distributions, note that if a set of $p$ measure spaces has all measures absolutely continuous with respect to the standard Borel measure on $\mathbb{R}$, then the product measure is also absolutely continuous with respect to the standard Borel product measure on $\mathbb{R}^p$ (e.g., see \cite{folland2013real}).
-This fact combined with Thm.~\ref{robustPolythm} implies the following.\footnote{We refer the reader to \cite{Hillar15} for a more detailed explanation of these arguments.}
-
-\begin{corollary}\label{ProbabilisticCor}
-If the indeterminate entries of $\mathbf{A}$ and the $\mathbf{x}_i$ are drawn independently from probability distributions absolutely continuous with respect to the standard Borel measure, then $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$ with probability one.
-\end{corollary}
-
-Thus, drawing the dictionary and supported sparse coefficients from any continuous probability distribution almost always generates data with a stable sparse representation.
-
-%\cite{rehnsommer2007, rozell2007neurally, ganguli2012compressed, hu2014hebbian}
-
-We close this section with some comments on the optimality of our results.
-The linear scaling for $\varepsilon$ in \eqref{epsdel} is essentially optimal (e.g., see \cite{arias2013fundamental}), but a basic open problem remains: how many samples are necessary to determine the sparse coding model?
-Our results demonstrate that sparse codes $\mathbf{x}_i$ drawn from only a polynomial number of $k$-dimensional subspaces permit stable identification of the generating dictionary $\mathbf{A}$. 
-This lends some legitimacy to the use of the model in practice, where data in general are unlikely (if ever) to exhibit the exponentially many possible $k$-wise combinations of dictionary elements required by (to our knowledge) all previously published results.
-
-Consequently, if $k$ is held fixed or if the size of the support set of reconstructing codes is polynomial in $\overline m$ and $k$, then a practical (polynomial) amount of data suffices to identify the dictionary.\footnote{In the latter case, a reexamination of the pigeonholing argument in the proof of Thm.~\ref{DeterministicUniquenessTheorem} requires a polynomial number of samples distributed over a polynomial number of supports.} Reasons to be skeptical that this holds in general, however, can be found in \cite{tillmann2014computational, Tillmann15}.
-Even so, in the next section we discuss how probabilistic guarantees can in fact be made for any number of available samples.
-
 \section{Proofs}\label{DUT} % of Theorems~\ref{DeterministicUniquenessTheorem} and ~\ref{SLCopt}}\label{DUT}
@@
 \begin{definition}\label{dDef}
-For $\mathbf{u} \in \mathbb R^m$ and vector spaces $U,V \subseteq \mathbb{R}^m$, let $\text{\rm dist}(\mathbf{u}, V) := \min \{\| \mathbf{u}-\mathbf{v} \|_2: \mathbf{v} \in V\}$ and define:
+For $\mathbf{u} \in \mathbb R^m$ and vector spaces $U,V \subseteq \mathbb{R}^m$, let $\text{\rmfamily dist}(\mathbf{u}, V) := \min \{\| \mathbf{u}-\mathbf{v} \|_2: \mathbf{v} \in V\}$ and define:
 \begin{align}
-d(U,V) := \max_{\mathbf{u} \in U, \ \|\mathbf{u}\|_2 \leq 1} \text{\rm dist}(\mathbf{u},V).
+d(U,V) := \max_{\mathbf{u} \in U, \ \|\mathbf{u}\|_2 \leq 1} \text{\rmfamily dist}(\mathbf{u},V).
 \end{align}
@@
 %\begin{align}\label{GapUpperBound}
-%d(\text{\rm span}\{\mathbf{A}_{S}\}, \bm{\mathcal{B}}_{\pi(S)}) \leq \varepsilon, \ \ \text{for $S \in \mathcal{H}$},
+%d(\text{\rmfamily span}\{\mathbf{A}_{S}\}, \bm{\mathcal{B}}_{\pi(S)}) \leq \varepsilon, \ \ \text{for $S \in \mathcal{H}$},
 %\end{align}
@@
 
-The practically-minded reader should note that the explicit constants $C_1$ and $C_2$ are effectively computable: the quantity $L_k$ may be calculated as the smallest singular value of a certain matrix, while the quantity $\xi$ involves computing ``canonical angles'' between subspaces, which reduces again to an efficient singular value decomposition.
+The practically-minded reader should note that the explicit constants $C_1$ and $C_2$ are effectively computable: the denominator of $C_1$ involves a quantity $L_k$ that may be calculated as the smallest singular value of a certain matrix, while computing the quantity $\xi$ in the denominator of $C_2$ involves computing ``canonical angles'' between subspaces, which reduces again to an efficient singular value decomposition.
 There is no known fast computation of $L_k$ in general, however, since even $L_{k} > 0$ is NP-hard \cite{tillmann2014computational}, although 
@@
 % , but efficient subcases do exist and may be of practical relevance.
+
+We note also that these constants likely have reasonable values in general.
+The quantity $L_k$ is a relatively standard quantity in the field of compressed sensing (the ``restricted isometry constant") and it is known to be reasonable for many random distributions generating dictionaries $\mathbf{A}$ and sparse codes $\mathbf{x}_i$.
+The more obscure quantity $\xi$, on the other hand, is computed from the ``Friedrichs angle" between certain spans of subsets of the columns of $\mathbf{A}$.
+Simulations for small random matrices $\mathbf{A}$ and hypergraphs $\mathcal{H}$ satisfying the SIP suggest nonetheless that the constant $C_2$ is reasonable as well (Fig.
+\ref{reasonableC2}).
 
@@
 Since there are more than $(k-1){\overline m \choose k}$ vectors $\mathbf{x}_i$ supported in $S$, by the pigeonhole principle there must be some $\overline S \in {[\overline m] \choose k}$ and a set of $k$ indices $K \subseteq I(S)$ for which all $\mathbf{\overline x}_i$ with $i \in K$ are supported in $\overline S$.
-It also follows\footnotemark[\ref{note1}] from $L_{2\mathcal{H}}(\mathbf{A}) > 0$ and the general linear position of the $\mathbf{x}_i$ that $L_k(\mathbf{AX}_{K}) > 0$; that is, the columns of the $n \times k$ matrix $\mathbf{AX}_K$ form a basis for $\bm{\mathcal{A}}_S$.
+It also follows\footnote{See footnote \ref{note1}.} from $L_{2\mathcal{H}}(\mathbf{A}) > 0$ and the general linear position of the $\mathbf{x}_i$ that $L_k(\mathbf{AX}_{K}) > 0$; that is, the columns of the $n \times k$ matrix $\mathbf{AX}_K$ form a basis for $\bm{\mathcal{A}}_S$.
 
@@
 Given insufficient samples, this argument has some less-than-certain probability of being valid for each $S \in \mathcal{H}$.
-Nonetheless, simulations with small hypergraphs confirm that the probability of success very quickly approaches one once the number of samples $N$ surpasses a small fraction of the deterministic sample complexity.
+Nonetheless, simulations with small hypergraphs demonstrate that successful recovery is nearly certainly even when $N$ is only a fraction of the deterministic sample complexity (Fig.
+\ref{probpigeon}).
 
@@
 %\end{proof}
-
-\section{Discussion}\label{Discussion}
-
-A main motivation for this work is the emergence of seemingly unique representations from sparse coding models trained on natural data, despite the varied assumptions underlying the many algorithms in current use.
-Our results constitute an important step toward explaining these phenomena as well as unifying many publications on the topic by deriving general deterministic conditions under which identification of parameters in this model is not only possible but also robust to uncertainty in measurement and model choice.
-
-We have shown that, given sufficient data, the problem of determining a dictionary and sparse codes with minimal support size (Prob.~\ref{OptimizationProblem}) reduces to an instance of Prob.~\ref{InverseProblem}, to which our main result (Thm.~\ref{DeterministicUniquenessTheorem}) applies: every dictionary and sequence of sparse codes consistent with the data are equivalent up to inherent relabeling/scaling ambiguities and a discrepancy (error) that scales linearly with the measurement noise or modeling inaccuracy.
-The constants we provide are explicit and computable; as such, there is an effective procedure that sufficiently affirms if a proposed solution to these problems is indeed unique up to noise and inherent ambiguities, although it is not efficient in general.
-
-%A compelling feature of this model is its simple instantiation of the principle of Occam's razor: a natural video, for instance, is modeled as a linear combination of a small number of spatiotemporal building blocks, each representing an archetypical feature latent in the data.
-
-%For theoretical neuroscience in particular, dictionary learning and related methods have recovered characteristic components of natural images \cite{Olshausen96, hurri1996image, bell1997independent, van1998independent} and sounds \cite{bellsejnowski1996, smithlewicki2006} that reproduce response properties of certain cortical neurons.
-
-%to the recovery of ``mouse neuronal activity representing location on a track \cite{agarwal2014spatially}
-
-%Moreover, we show that even if the meta-parameter for the number of dictionary elements is overestimated, a subset of parameters may still be identifiable up to noise.
-
-Beyond an extension of existing noiseless guarantees \cite{Hillar15} to the noisy regime and their novel application to Prob.~\ref{OptimizationProblem}, our work contains a theory of combinatorial designs for support sets key to identification of dictionaries.
-We incorporate this idea into a fundamental lemma in matrix theory (Lem.~\ref{MainLemma}) that draws upon the definition of a matrix lower bound (\ref{Ldef}) induced by a hypergraph.
-The new insight offered by this combinatorial approach allows for guaranteed recovery of some or all dictionary elements even if: 1) dictionary size is overestimated, 2) data cover only a polynomial number of distinct sparse supports, and 3) dictionaries do not satisfy the spark condition.
-
-The absence of any assumptions about dictionaries solving Prob.~\ref{InverseProblem} was a major technical obstruction in proving Thm.~\ref{DeterministicUniquenessTheorem}.
-We sought such a general guarantee because of the practical difficulty in ensuring that an algorithm maintain a dictionary satisfying the spark condition \eqref{SparkCondition} at each iteration, an implicit requirement of all previous works except \cite{Hillar15}; indeed, even certifying a dictionary has this property is NP-hard \cite{tillmann2014computational}.
-
-One direct application of this work is to theoretical neuroscience, wherein our theorems justify the mathematical soundness of one of the few hypothesized theories of bottleneck communication in the brain \cite{Isely10}: that sparse neural population activity is recoverable from its noisy linear compression through a randomly constructed (but unknown) wiring bottleneck by any biologically plausible unsupervised sparse coding method that solves Prob.~\ref{DeterministicUniquenessTheorem} or \ref{SLCopt} (e.g., \cite{rehnsommer2007, rozell2007neurally, pehlevan2015normative}).\footnote{We refer the reader to \cite{ganguli2012compressed} for more on interactions between dictionary learning and neuroscience.}
-
-In fact, uniqueness guarantees with minimal assumptions apply to all areas of data science and engineering that utilize learned sparse structure.
-For example, several groups have applied compressed sensing to signal processing tasks; for instance, in MRI analysis \cite{lustig2008compressed}, image compression \cite{Duarte08}, and even the design of an ultrafast camera \cite{Gao14}.
-It is only a matter of time before these systems incorporate dictionary learning to encode and decode signals (e.g., in a device that learns structure from motion \cite{kong2016prior}), just as scientists have used sparse coding to make sense of their data \cite{jung2001imaging, agarwal2014spatially, lee2016sparse, wu2016stability}.
-
-Assurances offered by our theorems certify that different devices and algorithms learn equivalent representations given enough data from statistically identical systems.\footnote{To contrast with the current hot topic of ``Deep Learning'', there are few such uniqueness guarantees for these models of data; moreover, even small noise can dramatically alter their output \cite{goodfellow2014explaining}.}
-Indeed, a main reason for the sustained interest in dictionary learning as an unsupervised method for data analysis seems to be the assumed well-posedness of parameter identification in the model, confirmation of which forms the core of our findings.
-
-We close with some challenges left open by our work.
-All conditions stated here guaranteeing the uniqueness and stability of sparse representations have only been shown sufficient; it remains open, therefore, to extend them to necessary conditions, be they on required sample size, the structure of support set hypergraphs, or tolerable error bounds.
-On this last note, we remark that our deterministic treatment considers always the ``worst-case" noise, whereas the ``effective" noise sampled from a concentrated distribution might be significantly reduced, especially for high-dimensional data.
-It would be of great practical benefit to see how drastically all conditions can be relaxed by requiring only probabilistic guarantees in this way, or in the spirit of our discussion on probabilistic pigeonholing to reduce sample complexity (as in the famous ``birthday paradox") following the proof of Thm.~\ref{DeterministicUniquenessTheorem}.
-
-Another interesting question raised by our work is for which special cases is it efficient to check that a solution to Prob.~\ref{InverseProblem} or \ref{OptimizationProblem} is unique up to noise and inherent ambiguities.
-Considering that the sufficient conditions we have described for checking this in general are NP-hard to compute, are the necessary conditions hard?
-Are Probs.~\ref{InverseProblem} and \ref{OptimizationProblem} then also hard (e.g., see \cite{Tillmann15})?
-Finally, since Prob.~\ref{SLCopt} is intractable in general, but efficiently solvable by $\ell_1$-norm minimization when the matrix is known (and has a large enough lower bound over sparse domains \cite{eldar2012compressed}), is there a version of Thm.~\ref{SLCopt} certifying when Prob.~\ref{OptimizationProblem} can be solved efficiently in full by similar means?
-% [*** Incorporate this open problem with more words ***]
-
-We hope these remaining challenges pique the interest of the community to pick up where we have left off and that the theoretical tools showcased here may be of use to this end.
-
-%We close with some challenges left open by our work.
-First, there is the basic problem of proving optimal lower bounds on sufficient sample size $N$ guaranteeing the uniqueness and stability of sparse representations.
-The pigeonholing argument in the proof of Thm.~\ref{DeterministicUniquenessTheorem} is loose in that it assigns to each support $S \in \mathcal{H}$ a corresponding support $\overline S$ without consideration of previously matched pairs; although we doubt tightening in this way will lead to sub-exponential sample sizes.
-Sample complexity will also benefit from lowering the number of required supports, i.e.
-the size of regular uniform hypergraphs satisfying the SIP.
-The regularity requirement on support hypergraphs can be loosened to allow for certain non-regular hypergraphs satisfying constraints on the degree sequence of nodes; though we impose regularity for clarity of exposition.
-It is then natural to ask: what is the smallest hypergraph satisfying the required constraints forgiven $m$ and $k$?
-Finally, the error bounds can be improved by tightening the constant $C_1$, e.g.
-via an improvement in Lemma ?.
-
-%Solving Prob.~\ref{SLCopt} directly is intractable in general since it necessitates, for each proposed dictionary $\mathbf{B}$, a combinatorial search for the supports of the associated sparse codes $\mathbf{\overline x}_i$.
-A common work-around is to convexify the problem (for fixed $\mathbf{B}$) by substituting the norm $\|\cdot\|_0$ with $\|\cdot\|_1$, impelled the fact that matrices $\mathbf{A}$ with large enough $L_{2k}(\mathbf{A})$ induce the same sparse codes via minimization of either norm \cite{?}.
-To this end, the lower bound $L_{2k}(\mathbf{BP}) \geq (L_{2k}(\mathbf{A}) - C_1\varepsilon) / \|\mathbf{D}\|_1$ implied by Thm.~\ref{DeterministicUniquenessTheorem} hints at conditions on the generating dictionary $\mathbf{A}$ and $k$-sparse codes $\mathbf{x}_i$ under which \emph{all} matrices $\mathbf{B}$ (of bounded column-norm) that solve Prob.~\ref{OptimizationProblem} also share this property of $\mathbf{A}$ by virtue of uniqueness and stability.
-One might then imagine an inference procedure whereby sparse codes are inferred via minimization of $\|\cdot\|_1$, but solutions still evaluated by their collective support size, yielding unique optimal solutions to Prob.~\ref{SLCopt} if only constraints could be imposed such that the learning procedure eventually guides $\mathbf{B}$ through an optimal dictionary.
-% (e.g.
-the dictionary is a member of a known finite set).
-
-\textbf{Acknowledgement.} We thank Fritz Sommer and Darren Rhea for early thoughts, and Ian Morris for posting \eqref{eqdim} online.
-
-%\section{EXTRA}
-%An additional consequence of Thm.~\ref{DeterministicUniquenessTheorem} of potential practical relevance to is the implied lower bound $L_{2k}(\mathbf{BPD}) \geq L_{2k}(\mathbf{A}) - C_1\varepsilon$ in the case where $\mathbf{A}$ satisfies \eqref{SparkCondition}.
-Since solving Prob.~\ref{SLCopt} directly requires a combinatorial search over sparse supports for the $\mathbf{\overline x}_i$ for each proposed dictionary $\mathbf{B}$, rendering it intractable in general, a common strategy is to replace the $\ell_0$-norm in \eqref{minsum} with the $\ell_1$-norm, thereby transforming the inference of sparse $\mathbf{\overline x}_i$ for a fixed dictionary $\mathbf{B}$ into a convex optimization solvable by a linear program.
-A major advance in compressive sensing was the discovery that, for fixed $\mathbf{B}$, solutions to \eqref{minsum} using either norm yield the same sparse vectors $\mathbf{\overline x}_i$ (up to noise) provided $L_{2k}(\mathbf{B})$ is large enough \cite{?}.
-What our results hint at are conditions on the generating dictionary $\mathbf{A}$ and $k$-sparse codes $\mathbf{x}_i$ under which \emph{all} matrices $\mathbf{B}$ (of bounded column-norm) that solve Prob.~\ref{OptimizationProblem} also share this property by virtue of uniqueness and stability; that is, conditions which guarantee that the sparse codes $\mathbf{\overline x}_i$ solving Prob.~\ref{OptimizationProblem} also solve the convexified problem when the corresponding dictionary $\mathbf{B}$ is held fixed.
-It remains to determine, however, what practical conditions preclude matrices that don't solve Prob.~\ref{OptimizationProblem} from nonetheless solving the convexified problem.
-%
-%Regardless, an implication of the above observation is that the following algorithm solves Prob.~\ref{OptimizationProblem} without appeal to combinatorial search:
-%\begin{enumerate}
-%\item List all matrices $\mathbf{B}$.
-%\item For each matrix $\mathbf{B}$, solve $\mathbf{\overline x}_i = \arg \min \|\mathbf{v}\|_1$ s.t. $\|\mathbf{Bv} - \mathbf{z}_i\| \leq \eta$ for $i = 1, \ldots, N$.
-%\item Quantify the proposed solution $\mathbf{B}$ and $\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N$ as $\rho(\mathbf{B}, \mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N) = \sum_{i=1}^{N} \|\mathbf{\overline x}_i\|_0$.
-%\item Output $\arg \min_{\mathbf{B}, \mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N} \left( \rho \right)$.
-% \end{enumerate}
-
-%Since its inception some twenty years ago, sparse coding has become a standard tool in signal analysis, yielding myriad insights into the structure of natural signals across a variety of scientific domains.
-In this work,
-
-%We make a final remark about the tightness of our results and the computability of our derived constants.
-%We remark that our constants have been derived for deterministic ``worst-case'' noise, whereas the ``effective'' noise might be smaller when sampled from a distribution.
-
-%Our results suggest that this correspondence could be due to the ``universality'' of sparse representations in natural data, an early idea in neural theory \cite{pitts1947}.
-
-% \vspace{-.2 cm}
-
-%\showacknow % Display the acknowledgments section
-
-\bibliographystyle{IEEEtran}
-\bibliography{chazthm_ieee_trans_sig}
-
-% \vspace{-.2 cm}
-
-\section{Appendix}\label{proofs}
-
-We prove Lem.~\ref{MainLemma} after the following auxiliary lemmas.  % stating and proving some auxiliary lemmas. 
-%First, note that since $\|\mathbf{A}\mathbf{x}\|_2 \leq \max_j\|\mathbf{A}_j\|_2\|\mathbf{x}\|_1$ and $\|\mathbf{x}\|_1 \leq \sqrt{k} \|\mathbf{x}\|_2$ for $k$-sparse $\mathbf{x}$, by \eqref{Ldef} we have the following frequently applied inequality:
-%\begin{align}\label{delrho}
-%L_{k'}(\mathbf{A}) \leq  \max_j\|\mathbf{A}_j\|_2 \ \ \text{for all $k' \leq 2k$}.
-%\end{align}
-
-% and then sketch the proofs of Thm.~\ref{robustPolythm} and Cor.~\ref{ProbabilisticCor}.
-
-%\begin{lemma}\label{spanIntersectionLemma}
-%Let $\mathbf{M} \in \mathbb{R}^{n \times m}$. If every $2k$ columns of $\mathbf{M}$ are linearly independent, then for any $F \subseteq {[m] \choose k}$:
-%\begin{align*}
-%\text{\rm span}\{\mathbf{M}_{\cap F}\}  = \bigcap_{S \in F} \text{\rm span}\{\mathbf{M}_S\}.
-%\end{align*}
-%\end{lemma}
-%\begin{proof}
-%Using induction on $|F|$, it is enough to prove the lemma when $|F| = 2$; but this case follows directly from the assumption.
-%\end{proof}
-
-\begin{lemma}\label{spanIntersectionLemma}
-If $f: V \to W$ is injective, then $f\left(\cap_{i=1}^\ell V_i \right) =  \cap_{i=1}^\ell f\left(V_i\right)$ for any $V_1, \ldots, V_\ell \subseteq V$. ($f(\emptyset):=\emptyset$.)
-%In particular, if for some $E \in 2^{[m]}$ the map $M \in \mathbb{R}^{n \times m}$ is injective on $\cup_{S \in \mathcal{H}} \text{span}\{e_i\}_{i \in S}$ then $\text{span}\{ M_{\cap_{S \in \mathcal{H}} S} \} = \cap_{S \in \mathcal{H}} \text{span}\{M_S\}$.
-\end{lemma}
-\begin{proof}
-By induction, it is enough to prove the case $\ell = 2$.
-Clearly, for any map $f$, if $w \in f(U \cap V)$ then $w \in f(U)$ and $w \in f(V)$; hence, $w \in f(U) \cap f(V)$.
-If $w \in f(U) \cap f(V)$, then $w \in f(U)$ and $w \in f(V)$; thus, $w = f(u) = f(v)$ for some $u \in U$ and $v \in V$, implying $u = v$ by injectivity of $f$.
-It follows that $u \in U \cap V$ and $w \in f(U \cap V)$.
-\end{proof}
-In particular, if a matrix $\mathbf{A}$ satisfies $L_{2\mathcal{H}}(\mathbf{A}) > 0$, then taking $V$ to be the union of subspaces consisting of vectors with supports in $2\mathcal{H}$, we have $\bm{\mathcal{A}}_{\cap \mathcal{G}} = \cap \bm{\mathcal{A}}_\mathcal{G}$ for all $\mathcal{G} \subseteq \mathcal{H}$.
-% \vspace{-.4 cm}
-
-\begin{lemma}\label{DistanceToIntersectionLemma}
-Let $\mathcal{V} = \{V_i\}_{i=1}^k$ be a set of two or more subspaces of $\mathbb{R}^m$, and set $V = \cap \mathcal{V} $.
-For  $\mathbf{u} \in \mathbb{R}^m$, we have (recall Defs.~\ref{dDef}~\&~\ref{FriedrichsDefinition}):
-\begin{align}\label{DTILeq}
-\text{\rm dist}(\mathbf{u}, V) \leq \frac{1}{1 - \xi(\mathcal{V})} \sum_{i=1}^k \text{\rm dist}(\mathbf{u}, V_i).
-\end{align}
-\end{lemma}
-\begin{proof} 
-% When $V = \{\mathbf{0}\}$, the result is trivial, so suppose otherwise.  
-Recall the projection onto the subspace $V \subseteq \mathbb{R}^m$ is the mapping $\Pi_V: \mathbb{R}^m \to V$ that associates with each $\mathbf{u}$ its unique nearest point in $V$; i.e., $\|\mathbf{u} - \Pi_V\mathbf{u}\|_2 = \text{\rm dist}(\mathbf{u}, V)$.
-By repeatedly applying the triangle inequality, we have:
-\begin{align}\label{f}
-\|\mathbf{u} - &\Pi_V\mathbf{u}\|_2 
-\leq \|\mathbf{u} - \Pi_{V_k} \mathbf{u}\|_2 + \|\Pi_{V_k}  \mathbf{u} - \Pi_{V_k}\Pi_{V_{k-1}}\mathbf{u}\|_2 \nonumber \\
-&\ \ \ \ \ \ \ \ \ \ \ + \cdots + \|\Pi_{V_k} \Pi_{V_{k-1}}\cdots \Pi_{V_1} \mathbf{u} - \Pi_V \mathbf{u}\|_2 \nonumber \\
-&\leq  \sum_{\ell=1}^k \|\mathbf{u} - \Pi_{V_{\ell}} \mathbf{u}\|_2 
-+ \|(\Pi_{V_k}\cdots\Pi_{V_{1}} - \Pi_V) \mathbf{u}\|_2,
-\end{align}
-where we have also used that the spectral norm of the orthogonal projections $\Pi_{V_{\ell}}$ satisfies $\|\Pi_{V_{\ell}}\|_2 \leq 1$ for all $\ell$.
-
-It remains to bound the second term in \eqref{f} by $\xi(\mathcal{V}) \|\mathbf{u} - \Pi_V\mathbf{u}\|_2$.
-First, note that $\Pi_{V_\ell} \Pi_V = \Pi_V$ and $\Pi_V^2 = \Pi_V$, so we have $\|(\Pi_{V_k} \cdots \Pi_{V_1} - \Pi_V) \mathbf{u} \|_2
-= \| ( \Pi_{V_k} \cdots\Pi_{V_1} - \Pi_V ) (\mathbf{u} - \Pi_V\mathbf{u})\|_2$. % \leq z\|\mathbf{u} - \Pi_V\mathbf{u}\|_2$.
-Consequently, inequality \eqref{DTILeq} follows from \cite[Thm.~9.33]{Deutsch12}:
-\begin{align}
-\|\Pi_{V_k}\Pi_{V_{k-1}}\cdots\Pi_{V_1} \mathbf{x} - \Pi_V\mathbf{x}\|_2 \leq z \|\mathbf{x}\|_2, \ \ \text{for all } \mathbf{x},
-\end{align}
-with \mbox{$z^2= 1 - \prod_{\ell =1}^{k-1}(1-z_{\ell}^2)$} and \mbox{$z_{\ell} = \cos\theta\left(V_{\ell}, \cap_{s=\ell+1}^k V_s\right)$} (recall $\theta$ from Def.~\ref{FriedrichsDefinition}), after substituting $\xi(\mathcal{V})$ for $z$ and rearranging terms.
-\end{proof}
-\begin{lemma}\label{NonEmptyLemma} 
-Fix an $r$-regular hypergraph $\mathcal{H} \subseteq 2^{[m]}$ satisfying the SIP.
-If the map $\pi: \mathcal{H} \to 2^{[\overline m]}$ has $\sum_{S \in \mathcal{H}} |\pi(S)| \geq \sum_{S \in \mathcal{H}} |S|$ and:
-\begin{align}\label{cond}
-	|\cap \pi(\mathcal{G})| \leq |\cap \mathcal{G} |,\ \ \   \text{for } \mathcal{G} \in {\mathcal{H} \choose r} \cup {\mathcal{H} \choose r+1},
-\end{align}
-%
-then $\overline m \geq m$; and if $\overline m  (r-1) < mr$, the map $i \mapsto \cap_{S \in \sigma(i)} \pi(S)$ is an injective function to $[\overline m]$ from some $J \subseteq [m]$ of size $m - (r-1)(\overline m - m)$ (recall $\sigma$ from Def.~\ref{sip}).
-%In particular, if $\overline m = m$ then $\pi$ is induced by a permutation on $[m]$.
-\end{lemma}
-
-\begin{proof}
-Consider the following set: $T_1 := \{(i, S): i \in \pi(S), S \in \mathcal{H}\}$, which numbers $|T_1| = \sum_{S \in \mathcal{H}} |\pi(S)| \geq \sum_{S \in \mathcal{H}} |S| = \sum_{i \in [m]} \deg_\mathcal{H}(i) = mr$ by $r$-regularity of $\mathcal{H}$.
-Note that $|T_1| \leq \overline m r$; otherwise, pigeonholing the tuples of $T_1$ with respect to their $\overline m$ possible first elements would imply that more than $r$ of the tuples in $T_1$ share the same first element.
-This cannot be the case, however, since then some $\mathcal{G} \in {\mathcal{H} \choose r+1}$ formed from any $r+1$ of their second elements would satisfy $\cap \pi(\mathcal{G}) \neq 0$; hence, $|\cap \mathcal{G}| \neq 0$ by \eqref{cond}, contradicting $r$-regularity of $\mathcal{H}$.
-It follows that $\overline m \geq m$.
-
-Suppose now that $\overline m (r-1) < mr$, so that $p := mr - \overline m (r-1)$ is positive and $|T_1| \geq \overline m (r - 1) + p$.
-Pigeonholing $T_1$ into $[\overline m]$ again, there are at least $r$ tuples in $T_1$ sharing some first element; that is, for some $\mathcal{G}_1 \subseteq \mathcal{H}$ of size $|\mathcal{G}_1| \geq r$, we have $|\cap \pi(\mathcal{G}_1)| \geq 1$ and (by \eqref{cond}) $|\cap \mathcal{G}_1| \geq 1$.
-Since no more than $r$ tuples of $T_1$ can share the same first element, we in fact have $|\mathcal{G}_1| = r$.
-It follows by $r$-regularity that $\mathcal{G}_1$ is a star of $\mathcal{H}$; hence, $|\cap \mathcal{G}_1| = 1$ by the SIP and $|\cap \pi(\mathcal{G}_1)|  = 1$ by \eqref{cond}.
-
-If $p=1$, then we are done.
-Otherwise, define $T_2 := T_1 \setminus \{(i,S) \in T_1: i = \cap \pi(\mathcal{G}_1)\}$, which contains $|T_2| = |T_1| - r \geq (\overline m - 1)(r-1) + (p-1)$ ordered pairs having $\overline m - 1$ distinct first indices.
-Pigeonholing $T_2$ into $[\overline m - 1]$ and repeating the above arguments produces the star $\mathcal{G}_2 \in {\mathcal{H} \choose r}$ with intersection $\cap \mathcal{G}_2$ necessarily distinct (by $r$-regularity) from $\cap \mathcal{G}_1$.
-Iterating this procedure $p$ times in total yields the stars $\mathcal{G}_i$ for which $\cap\mathcal{G}_i \mapsto \cap \pi(\mathcal{G}_i)$ defines an injective map to $[\overline m]$ from $J = \{\cap \mathcal{G}_1, \ldots, \cap \mathcal{G}_p\} \subseteq [m]$.
-\end{proof}
-
-\begin{proof}[Proof of Lem.~\ref{MainLemma}]
-%We will show that the bound \eqref{GapUpperBound} trickles through the intersection semi-lattices of $\{\bm{\mathcal{A}}_S\}_{S \in \mathcal{H}}$ and $\{\bm{\mathcal{B}}_{\overline S}\}_{\overline S \in \pi(\mathcal{H})}$ to yield \eqref{MainLemmaBPD} by virtue of the SIP.
-We begin by showing that $\dim(\bm{\mathcal{B}}_{\pi(S)}) = \dim(\bm{\mathcal{A}}_S)$ for all $S \in \mathcal{H}$.
-Note that since $\|\mathbf{A}\mathbf{x}\|_2 \leq \max_j\|\mathbf{A}_j\|_2\|\mathbf{x}\|_1$ and $\|\mathbf{x}\|_1 \leq \sqrt{k} \|\mathbf{x}\|_2$ for all $k$-sparse $\mathbf{x}$, by \eqref{Ldef} we have $L_2(\mathbf{A}) \leq \max_j\|\mathbf{A}_j\|_2$ and therefore (as $0 \leq \xi < 1$) the right-hand side of \eqref{GapUpperBound} is less than one.
-From \eqref{dimLem}, we have $|\pi(S)| \geq \dim(\bm{\mathcal{B}}_{\pi(S)}) \geq \dim(\bm{\mathcal{A}}_S) = |S|$, the final equality holding by injectivity of $\mathbf{A}_S$.
-As $|\pi(S)| = |S|$, the claim follows.
-Note, therefore, that $\mathbf{B}_{\pi(S)}$ has full-column rank for all $S \in \mathcal{H}$.
-
-We next demonstrate that \eqref{cond} holds.
-Fixing $\mathcal{G} \in {\mathcal{H} \choose r} \cup {\mathcal{H} \choose r+1}$, it suffices to show that $d(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}, \bm{\mathcal{A}}_{\cap \mathcal{G}} ) < 1$, since by \eqref{dimLem} we then have $|\cap \pi(\mathcal{G})| = \dim(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}) \leq \dim(\bm{\mathcal{A}}_{\cap \mathcal{G}}) = |\cap \mathcal{G}|$, with equalities from the full column-ranks of $\mathbf{A}_{S}$ and $\mathbf{B}_{\pi(S)}$ for all $S \in \mathcal{H}$.\footnote{Note that if ever $\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})} \neq \bf 0$ while $\cap \mathcal{G} = \emptyset$, we would have $d(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}, \bm 0 ) = 1$.
-However, that leads to a contradiction.} Observe that $d(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}, \bm{\mathcal{A}}_{\cap \mathcal{G}}  )
-\leq d\left( \cap \bm{\mathcal{B}}_{\pi(\mathcal{G})}, \cap \bm{\mathcal{A}}_\mathcal{G} \right)$ by \eqref{UsubU}, since trivially $\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})} \subseteq \cap \bm{\mathcal{B}}_{\pi(\mathcal{G})}$ and also $\bm{\mathcal{A}}_{\cap \mathcal{G}} = \cap \bm{\mathcal{A}}_\mathcal{G}$ by Lem.~\ref{spanIntersectionLemma}.
-Recalling Def.~\ref{dDef} and applying Lem.~\ref{DistanceToIntersectionLemma} yields:
-\begin{align}
-d\left( \cap \bm{\mathcal{B}}_{\pi(\mathcal{G})}, \cap \bm{\mathcal{A}}_\mathcal{G} \right)
-&\leq \max_{\mathbf{u} \in \cap \bm{\mathcal{B}}_{\pi(\mathcal{G})}, \ \|\mathbf{u}\|_2 \leq 1} \sum_{S \in \mathcal{G}} \frac{ \text{\rm dist}\left( \mathbf{u},\bm{\mathcal{A}}_{S} \right) }{ 1 - \xi( \bm{\mathcal{A}}_\mathcal{G} ) } \nonumber \\
-&= \sum_{S \in \mathcal{G}} \frac{ d\left( \cap \bm{\mathcal{B}}_{\pi(\mathcal{G})},\bm{\mathcal{A}}_{S} \right) }{ 1 - \xi( \bm{\mathcal{A}}_\mathcal{G} ) }, \nonumber
-\end{align}
-passing the maximum through the sum.
-Since $\cap \bm{\mathcal{B}}_{\pi(\mathcal{G})} \subseteq \bm{\mathcal{B}}_{\pi(S)}$ for all $S \in \mathcal{G}$, by \eqref{UsubU} the numerator of each term in the sum above is bounded by \mbox{$d\left( \bm{\mathcal{B}}_{\pi(S)},\bm{\mathcal{A}}_{S} \right) = d\left(\bm{\mathcal{A}}_{S}, \bm{\mathcal{B}}_{\pi(S)} \right) \leq \varepsilon$}, with the equality from \eqref{eqdim} since $\dim(\bm{\mathcal{B}}_{\pi(S)}) = \dim(\bm{\mathcal{A}}_S)$.
-Thus, altogether:
-\begin{align}\label{last}
-d(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}, \bm{\mathcal{A}}_{\cap \mathcal{G}} )
-\leq \frac{|\mathcal{G}| \varepsilon}{1 - \xi( \bm{\mathcal{A}}_\mathcal{G} )}
-\leq \frac{C_2 \varepsilon}{\max_j\|\mathbf{A}_j\|_2},
-\end{align}
-recalling the definition of $C_2$ in \eqref{Cdef2}.
-Lastly, since $C_2 \varepsilon < L_2(\mathbf{A}) \leq \max_j\|\mathbf{A}_j\|_2$, we have $d(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}, \bm{\mathcal{A}}_{\cap \mathcal{G}} ) \leq 1$ and therefore \eqref{cond} holds.
-
-%Keeping in mind that $d(U',V) \leq d(U,V)$ whenever $U' \subseteq U$ and applying (in order) Lem.~\ref{spanIntersectionLemma}, Lem.~\ref{DistanceToIntersectionLemma}, \eqref{eqdim}, \eqref{GapUpperBound}, and \eqref{Cdef2} gives:
-%\begin{align}\label{randoml}
-%d(&\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}, \bm{\mathcal{A}}_{\cap \mathcal{G}}  ) 
-%\leq d\left( \cap \bm{\mathcal{B}}_{\pi(\mathcal{G})}, \cap \bm{\mathcal{A}}_\mathcal{G} \right)
-%\leq \sum_{T \in \mathcal{G}} \frac{ d\left( \cap \bm{\mathcal{B}}_{\pi(\mathcal{G})},\bm{\mathcal{A}}_{T} \right) }{ 1 - \xi( \bm{\mathcal{A}}_\mathcal{G} ) } \nonumber \\
-%&\leq \sum_{T \in \mathcal{G}} \frac{ d\left( \bm{\mathcal{B}}_{\pi(T)},\bm{\mathbf{A}}_{T} \right) }{ 1 - \xi( \bm{\mathcal{A}}_\mathcal{G} ) }
-%\leq \frac{|\mathcal{G}| \varepsilon}{1 - \xi( \bm{\mathcal{A}}_\mathcal{G} )} 
-%\leq \frac{C_2 \varepsilon}{\max_j\|\mathbf{A}_j\|_2},
-%\end{align}
-%
-%which is less than one, since $C_2 \varepsilon < L_2(\mathbf{A}) \leq \max_j\|\mathbf{A}_j\|_2$.
-
-Applying Lem.~\ref{NonEmptyLemma}, the association $i \mapsto \cap_{S \in \sigma(i)} \pi(S)$ is an injective map $\overline \pi: J \to [\overline m]$ for some $J \subseteq [m]$ of size $m - (r-1)(\overline m - m)$, and $\mathbf{B}_{\overline \pi(i)} \neq \mathbf{0}$ for all $i \in J$ since the columns of $\mathbf{B}_{\pi(S)}$ are linearly independent for all $S \in \mathcal{H}$.
-Letting $\overline \varepsilon := C_2 \varepsilon / \max_i \|\mathbf{A}_i\|_2$, it follows from \eqref{eqdim} and \eqref{last} that $d\left( \bm{\mathcal{A}}_i, \bm{\mathcal{B}}_{\overline \pi(i)} \right) = d\left(\bm{\mathcal{B}}_{\overline \pi(i)},  \bm{\mathcal{A}}_i \right)  \leq \overline \varepsilon$ for all $i \in J$.
-%Fixing $\overline \varepsilon = C_2\varepsilon$ and letting $c_i = \|\mathbf{A}_i\|_2^{-1}$, we thus have that for each $\mathbf{e}_i \in \mathbb{R}^m$ with $i \in J$ there exists some $\overline{c}_i \in \mathbb{R}$ such that $\|c_i\mathbf{A}\mathbf{e}_i - \overline{c}_i \mathbf{B}\mathbf{e}_{\overline \pi(i)}\|_2 \leq \overline \varepsilon < L_2(\mathbf{A}) \min_{i\in J} |c_i|$.
-But this is exactly the supposition in \eqref{1D}, and the result follows from the case $k=1$ in Sec.~\ref{DUT} applied to the submatrix $\mathbf{A}_J$.
-Setting $c_i := \|\mathbf{A}_i\|_2^{-1}$ so that $\|c_i\mathbf{Ae}_i\|_2 = 1$, by Def.~\ref{dDef} for all $i \in J$:
-\begin{align*}
-\min_{\overline c_i \in \mathbb{R}} \|c_i\mathbf{Ae}_i - \overline c_i \mathbf{Be}_{\overline \pi(i)} \|_2
-\leq d\left( \bm{\mathcal{A}}_i, \bm{\mathcal{B}}_{\overline \pi(i)} \right)
-\leq \overline \varepsilon,
-%&= \max_{\bm{u} \in \bm{\mathcal{A}}_i, \|\bm{u}\|_2 \leq 1} \text{dist}\left(\bm{u}, \bm{\mathcal{B}}_{\overline \pi(i)} \right) \\
-%&\geq  \text{dist}\left(c_i\bm{Ae}_i, \mathbf{Be}_{\overline \pi(i)} \right) \\
-%&= \min_{\overline c_i \in \mathbb{R}} \|c_i\bm{Ae}_i - \overline c_i \mathbf{Be}_{\overline \pi(i)} \|_2
-\end{align*}
-%
-for $\overline \varepsilon < L_2(\mathbf{A})\min_{i \in [m]}|c_i|$.
-But this is exactly the supposition in \eqref{1D}, with $J$ and $\overline \varepsilon$ in place of $[m]$ and $\varepsilon$, respectively.
-The same arguments of the case $k=1$ in Sec.~\ref{DUT} can then be made to show that for any $\overline m \times \overline m$ permutation and invertible diagonal matrices $\mathbf{P}$ and $\mathbf{D}$ with, respectively, columns $\mathbf{e}_{\pi(i)}$ and $\frac{\overline{c}_i}{c_i}\mathbf{e}_i$ for $i \in J$ (otherwise, $\mathbf{e}_{i}$ for $i \in [\overline{m}] \setminus J$), we have $\|\mathbf{A}_i - (\mathbf{B}\mathbf{PD})_i \|_2 \leq \overline  \varepsilon / |c_i|  \leq C_2 \varepsilon$ for all $i \in J$.
-\end{proof}
-
-%\section{Proofs of Thm.~\ref{robustPolythm} and Cor.~\ref{ProbabilisticCor}}
-
-%\clearpage
-
-%\section{$\ell_1$-norm Extension}
-%
-%\begin{problem}\label{OptimizationProblemL1}
-%Find a matrix $\mathbf{B}$ and vectors \mbox{$\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N \in \mathbb{R}^m$} that solve:
-%\begin{align}\label{minsum}
-%\min \sum_{i = 1}^N \|\mathbf{\overline x}_i\|_1 \ \ 
-%\text{subject to} \ \ \|\mathbf{z}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \eta, \ \text{for all $i$}.
-%\end{align}
-%\end{problem}
-
-%\begin{corollary}\label{SLCopt}
-%Fix $\alpha > 0$ and suppose all of the assumptions of Thm.\ref{DeterministicUniquenessTheorem} hold with the following modifications:
-%\begin{enumerate}
-%\item The coefficients of all $k$-sparse $\mathbf{x}_i$ are drawn from $[-\beta, \beta]$, where $\beta < \frac{\alpha(k+1)}{k}$.
-%\item More than $(k-1){\overline m \choose k} + q$ vectors $\mathbf{x}_i$ are supported in each $S \in \mathcal{H}$, where
-%\[ q = \left[\frac{\alpha}{\beta}(k+1) - k\right]^{-1}k|\mathcal{H}|(k-1){\overline m \choose k-1}. \]
-%\end{enumerate}
-%Then all solutions to Prob.~\ref{OptimizationProblemL1} for which the nonzero elements of all $\mathbf{\overline x}_i$ lie outside $[-\alpha, \alpha]$ necessarily satisfy the implications \eqref{Cstable} and \eqref{b-PDa} of Thm.~\ref{DeterministicUniquenessTheorem}.
-%\end{corollary}
-
-%\begin{proof}[Proof of Cor.~\ref{SLCopt}]
-%We bound the number of $k$-sparse $\mathbf{\overline x}_i$ and then apply Thm.~\ref{DeterministicUniquenessCorollary}.
-First, observe that no more than $(k-1)|\mathcal{H}|$ of the $\mathbf{\overline x}_i$ share a support $\overline S$ of size less than $k$; otherwise, by the pigeonhole principle, at least $k$ of these indices $i$ belong to the same $K \subseteq I(S)$ for some $S \in \mathcal{H}$ and (as argued previously) \eqref{rhs222} follows.
-Since the right-hand side of \eqref{rhs222} is less than one, by \eqref{dimLem} we have the contradiction $k = \dim(\bm{\mathcal{A}}_S) \leq \dim(\bm{\mathcal{B}}_{\overline S}) \leq |\overline S|.$ The total number of $(k-1)$-sparse vectors $\mathbf{\overline x}_i$ can thus not exceed $|\mathcal{H}|(k-1){ \overline m \choose k-1}$.
-
-%Next, observe that the assumptions of the lemma imply:
-%\begin{align*}
-%\alpha \sum_i \|\mathbf{\overline x}_i\|_0 \leq \sum_i \|\mathbf{\overline x}_i\|_1 \leq \sum_i \|\mathbf{x}_i\|_1 \leq \beta \sum_i \|\mathbf{x}_i\|_0.
-%\end{align*}
-
-%We now apply these facts to bound the number of $k$-sparse $\mathbf{\overline x}_i$.
-Let $n_p$ be the number of $\mathbf{\overline x}_i$ with $\|\mathbf{\overline x}_i\|_0 = p$.
-Since the $\mathbf{x}_i$ are all $k$-sparse, we have:
-%\begin{align*}
-%k \sum_{p = 0}^{\overline m} n_p = k N \geq \sum_{i=0}^N \|\mathbf{x}_i\|_0 \geq \frac{\alpha}{\beta} \sum_{i=0}^N \|\mathbf{\overline x}_i\|_0 = \frac{\alpha}{\beta} \sum_{p=0}^{\overline m} p n_p.
-%\end{align*}
-%Hence, 
-%\begin{align*}
-%\left[ \frac{\alpha(k+1)}{\beta} - k\right] \sum_{p = k+1}^{\overline m} n_p 
-%&\leq \sum_{p = k+1}^{\overline m} (\frac{\alpha}{\beta} p-k) n_p
-%\leq \sum_{p = 0}^k (k - \frac{\alpha}{\beta} p)n_p \\
-%&\leq k \sum_{p = 0}^k n_p 
-%\leq k(1-\frac{\alpha}{\beta})n_k + k|\mathcal{H}|(k-1){ \overline m \choose k-1}
-%\end{align*}
-
-%[Shit, we need $\alpha = \beta$.] Therefore, no more than $q$ vectors $\mathbf{\overline x}_i$ are \emph{not} $k$-sparse.
-Since for every $S \in \mathcal{H}$ there are over $(k-1){\overline m \choose k} + q$ vectors $\mathbf{x}_i$ supported there, it follows that more than $(k-1){\overline m \choose k}$ of them have corresponding $\mathbf{\overline x}_i$ that are $k$-sparse.
-The result now follows directly from Thm.~\ref{DeterministicUniquenessCorollary}.
-%\end{proof}
-
-%\pagebreak
-
-%\begin{corollary}\label{SLCoptL1}
-%If all of the assumptions of Thm.\ref{DeterministicUniquenessTheorem} hold, only now with more than $(k-1)\left[ {\overline m \choose k} + |\mathcal{H}|k{\overline m \choose k-1}\right]$ vectors $\mathbf{x}_i$ supported in each $S \in \mathcal{H}$, then every solution to Prob.~\ref{OptimizationProblemL1} for which the average absolute nonzero coefficient of the $\mathbf{\overline x}_i$ is bounded below by that of the $\mathbf{x}_i$ necessarily satisfies the implications \eqref{Cstable} and \eqref{b-PDa} of Thm.~\ref{DeterministicUniquenessTheorem}.
-%\end{corollary}
-
-%\begin{proof}[Proof of Cor.~\ref{SLCoptL1}]
-%Since the average absolute nonzero coefficient of the $\mathbf{x}_i$ is given by $\alpha = \sum_i \|\mathbf{x}_i\|_1 / \sum_i \|\mathbf{x}_i\|_0$, we have:
-%\begin{align*}
-%\alpha \sum_i \|\mathbf{\overline x}_i\|_0 \leq \sum_i \|\mathbf{\overline x}_i\|_1 \leq \sum_i \|\mathbf{x}_i\|_1 = \alpha \sum_i \|\mathbf{x}_i\|_0.
-%\end{align*}
-%
-%and the result follows by the same arguments as in the proof of Cor.~\ref{SLCopt}.
-%\end{proof}
-
-\end{document}

### 2020-07-16 manuscripts/thesis/results.tex
thesis

--- 2019-05-10 manuscripts/IEEE/final_submission.tex
@@
-% TODO: 
-% Make L_H a definition..? Change def of L to be 1-norm so we don't need these sqrt k's?
-% C_1 depends on J in Thm 1
-% also in proof of (7) x need not be *any* 2k-sparse vector...can instead restrict to some H...then 2k is restricted to half being on H.
-
-% Notes:
-%
-% Can we prove in a line or two that the inverse problem is stable by arguing that the function is bijective and closed therefore a homeomorphism?
-% Should we mention the notion of Grassmannian manifolds and that Theta is a metric on this space?
-% Change robustness to stability?
-%
-\documentclass[journal, twocolumn]{IEEEtran}
-
-% *** MATH PACKAGES ***
-\usepackage{amsmath, amssymb, amsthm} 
-\newtheorem{theorem}{Theorem}
-\newtheorem{lemma}{Lemma}
-\newtheorem{conjecture}{Conjecture}
-\newtheorem{problem}{Problem}
-\newtheorem{question}{Question}
-\newtheorem{proposition}{Proposition}
-\newtheorem{definition}{Definition}
-\newtheorem{corollary}{Corollary}
-\newtheorem{remark}{Remark}
-\newtheorem{example}{Example}
-
-\usepackage[pdftex]{graphicx}
-
-% *** ALIGNMENT PACKAGES ***
-\usepackage{array}
-\usepackage{cite}
-\usepackage{bm}
-
-% correct bad hyphenation here
-%\hyphenation{op-tical net-works semi-conduc-tor}
-
-\begin{document}
-
-%\title{When can a generating dictionary and sparse codes be recovered from noisy data?}
-%\title{When is the dictionary learning problem well-posed?}
-\title{On the uniqueness and stability of dictionaries \\ for sparse representation of noisy signals}
-%\title{When is the dictionary learning problem for sparse coding well-posed?}
-%\title{When is the sparsest representation unique?}
-%\title{When are sparse codes identifiable from their unknown noisy compressive measurements?}
-% FRITZ2: The title doesn't reflect the amount of new stuff, it seems incremental from the last one. It's not very meaningful.
-% FRITZ: Not everyone knows what well-posed means. You should mention recovery from noisy data in the title.
-
-\author{Charles~J.~Garfinkle and Christopher~J.~Hillar \\
-Redwood Center for Theoretical Neuroscience, Berkeley, CA, USA
-%\thanks{%e-mails: cjg@berkeley.edu, chillar@msri.org.  
-%CG and CH supported, in part, by NSF grant IIS-1219212 and the Statistical and Applied Mathematical Sciences Institute, under NSF DMS-1127914.}
-}
-
-\maketitle
-
-% \keywords{Sparse coding, dictionary learning, matrix factorization, compressed sensing, inverse problems, blind source separation}
-
-\begin{abstract}
-%Learning optimal dictionaries for sparse coding has exposed characteristic sparse features of many natural signals.
-However, there are few universal conditions guaranteeing the stability of such features in the presence of noise.
-Here, we prove very generally that optimal dictionaries and sparse codes are unique up to measurement error for all diverse enough datasets generated by the sparse coding model.
-Applications are given to data analysis, engineering, and neuroscience.
-Learning optimal dictionaries for sparse coding has exposed characteristic sparse features of many natural signals.
-However, universal guarantees of the stability of such features in the presence of noise are lacking.
-Here, we provide very general conditions guaranteeing when dictionaries yielding the sparsest encodings are unique and stable with respect to measurement or modeling error.
-We demonstrate that some or all original dictionary elements are recoverable from noisy data even if the dictionary fails to satisfy the spark condition, its size is overestimated, or only a polynomial number of distinct sparse supports appear in the data.
-Importantly, we derive these guarantees without requiring any constraints on the recovered dictionary beyond a natural upper bound on its size.
-Our results also yield an effective procedure sufficient to affirm if a proposed solution to the dictionary learning problem is unique within bounds commensurate with the noise.
-We suggest applications to data analysis, engineering, and neuroscience and close with some remaining challenges left open by our work.
-\end{abstract}
-
-% Optional adjustment to line up main text (after abstract) of first page with line numbers, when using both lineno and twocolumn options.
-% You should only change this length when you've finalised the article contents.
-
-\section{Introduction}\label{Intro}
-\IEEEPARstart{S}{parse} coding is a common modern approach to pattern analysis in signal processing whereby each of $N$ observed $n$-dimensional signal samples is viewed as a (noisy) linear combination of at most $k$ elementary waveforms drawn from some unknown ``dictionary" of size $m \ll N$ (see \cite{Zhang15} for a comprehensive review).
-%\IEEEPARstart{A}{}common modern approach to pattern analysis in signal processing is to view each of $N$ observed $n$-dimensional signal samples as a (noisy) linear combination of at most $k$ elementary waveforms drawn from some unknown ``dictionary" of size $m \ll N$ (see \cite{Zhang15} for a comprehensive review).
-Optimizing dictionaries subject to this and related sparsity constraints has revealed seemingly characteristic sparse structure in several signal classes of current interest (e.g., in vision \cite{wang2015sparse}).
-
-Of particular note are the seminal works in the field \cite{Olshausen96, hurri1996image, bell1997independent, van1998independent}, which discovered that dictionaries optimized for coding small patches of ``natural" images share qualitative similarities with linear filters estimated from response properties of simple-cell neurons in mammalian visual cortex.
-Curiously, these waveforms (e.g., ``Gabor'' wavelets) appear in dictionaries learned by a variety of algorithms trained over different natural image datasets, suggesting that learned features in natural signals may, in some sense, be canonical \cite{donoho2001can}.
-
-Motivated by these discoveries and more recent work relating compressed sensing \cite{eldar2012compressed} to a theory of information transmission through random wiring bottlenecks in the brain \cite{Isely10}, we address when dictionaries for sparse representation are indeed identifiable from data.
-Answers to this question may also have implications in practice wherever an appeal is made to latent sparse structure of data (e.g., forgery detection \cite{hughes2010, olshausen2010applied}; brain recordings \cite{jung2001imaging, agarwal2014spatially, lee2016sparse}; and gene expression \cite{wu2016stability}).
-
-While several algorithms have been recently proposed to provably recover unique dictionaries under specific conditions (see \cite[Sec.~I-E]{Sun16} for a summary of the state-of-the-art), few theorems can be invoked to justify the consistency of inference under this model of data more broadly.
-To our knowledge, a universal guarantee of the uniqueness and stability of learned dictionaries and the sparse representations they induce over noisy data has yet to appear in the literature.
-% in justifying the identification of forged paintings by their anomalous sparse representations \cite{hughes2010},
-
-Here, we prove very generally that uniqueness and stability is a typical property of sparse dictionary learning.
-More specifically, we show that matrices injective on a sparse domain are identifiable from \mbox{$N = m(k-1){m \choose k} + m$} noisy linear combinations of $k$ of their $m$ columns up to an error that is linear in the noise (Thm.~\ref{DeterministicUniquenessTheorem}).
-In fact, provided $n \geq \min(2k,m)$, in almost all cases the problem is well-posed, as per Hadamard \cite{Hadamard1902}, given a sufficient amount of data (Thm.~\ref{robustPolythm} and Cor.~\ref{ProbabilisticCor}).
-
-Our guarantees also hold for a related (and perhaps more commonly posed, e.g.
-\cite{rehnsommer2007}) optimization problem seeking a dictionary minimizing the average number of elementary waveforms required to reconstruct each sample of the dataset (Thm.~\ref{SLCopt}).
-To practical benefit, our results impose no restrictions on learned dictionaries (e.g., that they, too, be injective over some sparse domain) beyond an upper bound on dictionary size, which is necessary in any case to avoid trivial solutions (e.g., allowing $m = N$).
-%That is, every pair of solutions of comparable size has some number of dictionary elements in common (up to noise), and similarly so for the coefficients of sparse codes they induce.
-
-More precisely, let $\mathbf{A} \in \mathbb R^{n \times m}$ be a matrix with columns $\mathbf{A}_j$ ($j = 1,\ldots,m$) and let dataset $Z$ consist of measurements:
-\begin{align}\label{LinearModel}
-\mathbf{z}_i = \mathbf{A}\mathbf{x}_i + \mathbf{n}_i,\ \ \  \text{$i=1,\ldots,N$},
-\end{align}
-for $k$-\emph{sparse} $\mathbf{x}_i \in \mathbb{R}^m$ having at most $k<m$ nonzero entries and \emph{noise} $\mathbf{n}_i \in \mathbb{R}^n$, with bounded norm $\| \mathbf{n}_i \|_2 \leq  \eta$ representing our worst-case uncertainty in measuring the product $\mathbf{A}\mathbf{x}_i$.
-We first consider the following formulation of sparse coding.
-%The first mathematical problem we consider is the following.
-
-\begin{problem}\label{InverseProblem}
-Find a dictionary matrix $\mathbf{B}$ and $k$-sparse codes $\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N$ that satisfy $\|\mathbf{z}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \eta$ for all $i = 1,\ldots,N$.
-\end{problem}
-
-Note that every solution to Prob.~\ref{InverseProblem} represents infinitely many equivalent alternatives $\mathbf{BPD}$ and $\mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_1, \ldots, \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_N$ parametrized by a choice of permutation matrix $\mathbf{P}$ and invertible diagonal matrix $\mathbf{D}$.
-Identifying these ambiguities (labelling and scale) yields a single orbit of solutions represented by any particular set of elementary waveforms (the columns of $\mathbf{B}$) and their associated sparse coefficients (the entries of $\mathbf{\overline x}_i$) that reconstruct each data point $\mathbf{z}_i$.
-
-Previous theoretical work addressing the noiseless case $\eta =0$ (e.g., \cite{li2004analysis, Georgiev05, Aharon06, Hillar15}) for matrices $\mathbf{B}$ having exactly $m$ columns has shown that a solution to Prob.~\ref{InverseProblem}, when it exists, is unique up to such relabeling and rescaling provided the $\mathbf{x}_i$ are sufficiently diverse and $\mathbf{A}$ satisfies the \textit{spark condition}:
-\begin{align}\label{SparkCondition}
-\mathbf{A}\mathbf{x}_1 = \mathbf{A}\mathbf{x}_2 \implies \mathbf{x}_1 = \mathbf{x}_2, \ \ \ \text{for all $k$-sparse } \mathbf{x}_1, \mathbf{x}_2,
-\end{align}
-%
-which is necessary to guarantee the uniqueness of arbitrary $k$-sparse $\mathbf{x}_i$.
-We generalize these results to the practical setting  $\eta > 0$ by considering the following natural notion of stability with respect to measurement error.
-
-\begin{definition}\label{maindef}
-Fix $Y = \{ \mathbf{y}_1, \ldots, \mathbf{y}_N\} \subset \mathbb{R}^n$.
-We say $Y$ has a \textbf{$k$-sparse representation in $\mathbb{R}^m$} if there exists a matrix $\mathbf{A}$ and $k$-sparse $\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$ such that $\mathbf{y}_i = \mathbf{A}\mathbf{x}_i$ for all $i$.
-This representation is \textbf{stable} if for every $\delta_1, \delta_2 \geq 0$, there exists some $\varepsilon = \varepsilon(\delta_1, \delta_2)$ that is strictly positive for positive $\delta_1$ and $\delta_2$ such that if $\mathbf{B}$ and $k$-sparse $\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N \in \mathbb{R}^m$ satisfy:
-\begin{align*}
-	\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \varepsilon(\delta_1, \delta_2),\ \   \text{for all $i=1,\ldots,N$},
-\end{align*}
-then there is some permutation matrix $\mathbf{P}$ and invertible diagonal matrix $\mathbf{D}$ such that for all $i, j$:
-\begin{align}\label{def1}
-\|\mathbf{A}_j - (\mathbf{BPD})_j\|_2 \leq \delta_1 \ \text{and} \ \|\mathbf{x}_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_i\|_1 \leq \delta_2.
-\end{align}
-\end{definition}
-
-To see how Prob.
-\ref{InverseProblem} motivates Def.
-\ref{maindef}, suppose that $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$ and fix $\delta_1, \delta_2$ to be the desired accuracies of recovery in \eqref{def1}.
-Consider any dataset $Z$ generated as in \eqref{LinearModel} with $\eta \leq \frac{1}{2} \varepsilon(\delta_1, \delta_2)$.
-Using the triangle inequality, it follows that any $n \times m$ matrix $\mathbf{B}$ and $k$-sparse $\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N$ solving Prob.~\ref{InverseProblem} are necessarily within $\delta_1$ and $\delta_2$ of the original dictionary $\mathbf{A}$ and codes $\mathbf{x}_1, \ldots, \mathbf{x}_N$, respectively.\footnote{We mention that the different norms in \eqref{def1} reflect the distinct meanings typically ascribed to the dictionary and sparse codes in modeling data.}
-
-The main result of this work is a very general uniqueness theorem for sparse coding (Thm.~\ref{DeterministicUniquenessTheorem}) directly 
-implying (Cor.~\ref{DeterministicUniquenessCorollary}), which guarantees that sparse representations of a dataset $Z$ are unique up to noise whenever generating dictionaries $\mathbf{A}$ satisfy a spark condition on supports and the original sparse codes $\mathbf{x}_i$ are sufficiently diverse (e.g., Fig.~\ref{noisyrecovery}).
-Moreover, we provide an explicit, computable $\varepsilon(\delta_1, \delta_2)$ in (\ref{epsdel}) that is linear in desired accuracy $\delta_1$, and essentially so in $\delta_2$.
-
-In the next section, we give formal statements of these findings.
-We then extend the same guarantees (Thm.~\ref{SLCopt}) to the following alternate formulation of dictionary learning, which minimizes the total number of nonzero entries in sparse codes.
-
-\begin{problem}\label{OptimizationProblem}
-Find matrices $\mathbf{B}$ and vectors \mbox{$\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N$} solving:
-\begin{align}\label{minsum}
-\min \sum_{i = 1}^N \|\mathbf{\overline x}_{i}\|_0 \ \
-\text{subject to} \ \ \|\mathbf{z}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \eta, \ \text{for all $i$}.
-\end{align}
-\end{problem}
-
-Our development of Thm.~\ref{DeterministicUniquenessTheorem} is general enough to provide some uniqueness and stability even when generating $\mathbf{A}$ do not fully satisfy (\ref{SparkCondition}) and recovery dictionaries $\mathbf{B}$ have more columns than $\mathbf{A}$.
-Moreover, the approach incorporates a combinatorial theory for designing generating codes that should be of independent interest.
-We also give brief arguments adapting our results to dictionaries and codes drawn from probability distributions (Cor.~\ref{ProbabilisticCor}).
-The technical proofs of Thms.~\ref{DeterministicUniquenessTheorem} and ~\ref{SLCopt} are deferred to Sec.~\ref{DUT}, following some necessary definitions and a fact in combinatorial matrix analysis (Lem.~\ref{MainLemma}; proven in the Appendix).
-Finally, we discuss in Sec.~\ref{Discussion} applications of our mathematical observations as well as open questions.
-%The Appendix contains a proof of Lem.~\ref{MainLemma}.
-
+%\chapter{Results}
 \section{Results}\label{Results}
@@
 
-Precise statements of our results require that we first identify some combinatorial criteria on the supports\footnote{Recall that a vector $\mathbf{x}$ is said to be \emph{supported} in $S$ when $\mathbf{x} \in \text{\rm span}\{\mathbf{e}_j: j\in S\}$, with $\mathbf{e}_j$ forming the standard column basis.} of sparse vectors.
+Precise statements of our results require that we first identify some combinatorial criteria on the supports\footnote{Recall that a vector $\mathbf{x}$ is said to be \emph{supported} in $S$ when $\mathbf{x} \in \text{\rmfamily span}\{\mathbf{e}_j: j\in S\}$, with $\mathbf{e}_j$ forming the standard column basis.} of sparse vectors.
 Let $\{1, \ldots, m\}$ be denoted $[m]$, its power set $2^{[m]}$, and ${[m] \choose k}$ the set of subsets of $[m]$ of size $k$.
@@
 \begin{center}
-\includegraphics[width=.24 \linewidth]{figs/basis.png}
-% \includegraphics[width=.25 \linewidth]{figs/Ahat_FastICA_M640_K8_noise0_2042}
-%\includegraphics[width=.24 \linewidth]{figs/Ahat_FastICA_M640_K8_noise0_4083.png}
-\includegraphics[width=.24 \linewidth]{figs/Ahat_FastICA_M640_K8_noise1_0205.png}
-\includegraphics[width=.24 \linewidth]{figs/Ahat_FastICA_M640_K8_noise2_0409.png}
-\includegraphics[width=.24 \linewidth]{figs/Ahat_FastICA_M640_K8_noise5_1021.png}
+\includegraphics[width=.24 \linewidth]{figures/Basis.png}
+\includegraphics[width=.24 \linewidth]{figures/Ahat_FastICA_M640_K8_noise1_0205.png}
+\includegraphics[width=.24 \linewidth]{figures/Ahat_FastICA_M640_K8_noise2_0409.png}
+\includegraphics[width=.24 \linewidth]{figures/Ahat_FastICA_M640_K8_noise5_1021.png}
 \caption{\textbf{Learning a dictionary from increasingly noisy data}.
@@
 Even so, in the next section we discuss how probabilistic guarantees can in fact be made for any number of available samples.
-
-\section{Proofs}\label{DUT} % of Theorems~\ref{DeterministicUniquenessTheorem} and ~\ref{SLCopt}}\label{DUT}
-
-%%%%%%%%%%%%%%
-% need to cut maybe: 
-%As mentioned in the previous section, Thm.~\ref{DeterministicUniquenessTheorem} is a particular case of a more general result that forgoes the assumption that $\mathcal{H} \subseteq {[m] \choose k}$ is regular and satisfies the SIP.
-If instead we require only that the stars $\cap \sigma(i)$ intersect at singletons for all $i \leq q$ (assuming that the nodes of $\mathcal{H}$ are labeled in some order of non-increasing degree), we have that $\overline m \geq k|\mathcal{H}| / \deg(1)$ and, provided $\overline m < k|\mathcal{H}| / (\deg(1) - 1)$, the nonempty submatrix $J$ is of size equal to the largest number $p$ satisfying:
-%\begin{align}\label{pcond}
-%\sum_{i=\ell}^{m} \deg(i) > (\overline m + 1 - \ell) (\deg(\ell) - 1) \ \ \text{for all } \ell \leq p \leq q.
-%\end{align}
-%Specifically, $J$ contains all nodes of degree exceeding $\deg(p)$ and some subset of those with degreee equal to $\deg(p)$.
-For the benefit of the reader, we do not prove explicitly this more general result below; it can be discerned from how exactly Lemma \ref{NonEmptyLemma} is incorporated into the proof of Lem.~\ref{MainLemma}.
-%%%%%%%%%%%%%%%%
-
-%As mentioned in the previous section, Thm.~\ref{DeterministicUniquenessTheorem} is a particular case of a more general result, which requires a looser set of constraints on the hypergraph $\mathcal{H}$ and which applies to $n \times \overline m$ matrices $\mathbf{B}$ (and $\overline m$-dimensional codes $\mathbf{\overline x}_i$) with $\overline m \neq m$:
-
-%Fix $\overline m$ and suppose the assumptions of Thm.~\ref{DeterministicUniquenessTheorem} hold, only now with the constraints on $\mathcal{H} \subseteq {[m] \choose k}$ being just that $|\cap H(i)| = 1$ for all $i \leq q$ (assuming w.l.o.g.
-that the nodes of $\mathcal{H}$ are labeled in some order of non-increasing degree), and with more than $(k-1){\overline m \choose k}$ vectors $\mathbf{x}_i$ supported in g.l.p.
-on each $S \in \mathcal{H}$.
-Then we must have $\overline m \geq k|\mathcal{H}| / \deg(1)$ and, provided $\overline m < k|\mathcal{H}| / (\deg(1) - 1)$, the guarantee \eqref{Cstable} holds for a submatrix $\mathbf{A}_J$, where $J \subseteq[m]$ is nonempty and of a size equal to the largest number $p$ satisfying:
-%\begin{align}\label{pcond}
-%\sum_{i=\ell}^{m} \deg(i) > (\overline m + 1 - \ell) (\deg(\ell) - 1) \ \ \text{for all } \ell \leq p \leq q.
-%\end{align}
-%Specifically, $J$ consists of the union of the set of all nodes of degree exceeding $\deg(p)$ and some subset of those nodes with degrees equal to $\deg(p)$.
-
-%For the benefit of the reader, we prove below the case where we forgo only the constraint that $\overline m = m$.
-This yields the implication $\overline m \geq m$ and \eqref{pcond} reduces to $|J| = \overline m - r(\overline m - m)$.
-The extension to the general result above can be seen by examining how exactly Lemma \ref{NonEmptyLemma} is incorporated into the overall proof.
-
-% ======== b - PDa =========
-
-% WITH EXPLICIT J SUBSCRIPT
-%We begin our proof of Thm.~\ref{DeterministicUniquenessTheorem} by showing how dictionary recovery \eqref{Cstable} already implies sparse code recovery \eqref{b-PDa} when $\mathbf{A}_J$ satisfies \eqref{SparkCondition} and \mbox{$\varepsilon < L_{2k}(\mathbf{A}_J) / C_1$}.
-%, assuming that $\overline m = m$ without loss of generality.
-%Consider any $2k$-sparse $\mathbf{x} \in \mathbb{R}^m$ and note that $\|\mathbf{x}\|_1 \leq \sqrt{2k}  \|\mathbf{x}\|_2$. By definition of $L_{2k}$ in \eqref{Ldef}, we have:
-%\begin{align}\label{stuff}
-%\|\mathbf{x}_J - &( \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x} )_J\|_1 \nonumber
-%\leq \frac{\|(\mathbf{BPD})_J(\mathbf{x}_J - (\mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x})_J)\|_2}{L_{2k}((\mathbf{BPD})_J)} \\ \nonumber
-%&\leq \frac{\|( (\mathbf{BPD})_J - \mathbf{A}_J) \mathbf{x}_J\|_2 + \|\mathbf{A}_J\mathbf{x}_J - \mathbf{B}_J\mathbf{\overline x}_J\|_2}{L_{2k}((\mathbf{BPD})_J)} \\
-%&\leq \frac{C_1\varepsilon \|\mathbf{x}_J\|_1 + \varepsilon}{L_{2k}((\mathbf{BPD})_J)},
-%\end{align}
-%where the term $C_1\varepsilon \|\mathbf{x}_J\|_1$ in the numerator above is a consequence of the triangle inequality applied to \eqref{Cstable}.
-
-%It remains for us to bound the denominator.  By the reverse triangle inequality:
-%\begin{align*}
-%\|(\mathbf{BPD})_J\mathbf{x}_J\|_2 
-%&\geq | \|\mathbf{A}_J\mathbf{x}_J\|_2 - \|(\mathbf{A}_J - (\mathbf{BPD})_J)\mathbf{x}_J\|_2 | \\
-%&\geq \sqrt{2k} (L_{2k}(\mathbf{A}_J) -  C_1\varepsilon) \|\mathbf{x}_J\|_2,
-%\end{align*}
-%
-%wherein removal of the absolute value is justified since $C_1\varepsilon < L_{2k}(\mathbf{A}_J)$.
-We therefore have that $L_{2k}((\mathbf{BPD})_J) \geq L_{2k}(\mathbf{A}_J) - C_1\varepsilon  > 0$, and \eqref{b-PDa} then follows from \eqref{stuff}.
-
-% WITHOUT J SUBSCRIPT
-We begin our proof of Thm.~\ref{DeterministicUniquenessTheorem} by showing how dictionary recovery \eqref{Cstable} already implies sparse code recovery \eqref{b-PDa} when $\mathbf{A}$ satisfies \eqref{SparkCondition} and \mbox{$\varepsilon < L_{2k}(\mathbf{A}) / C_1$}.
-We temporarily assume (without loss of generality) that $\overline m = m$, so as to omit an otherwise requisite subscript $(\cdot)_J$ around certain matrices and vectors.
-By definition of $L_{2k}$ in \eqref{Ldef}, and noting that $\sqrt{k} \|\mathbf{v}\|_2 \geq \|\mathbf{v}\|_1$ for $k$-sparse $\mathbf{v}$, we have for all $i \in [N[$:
-\begin{align}\label{stuff}
-\|\mathbf{x}_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_i \|_1 \nonumber
-&\leq \frac{\|\mathbf{BPD}(\mathbf{x}_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_i)\|_2}{L_{2k}(\mathbf{BPD})} \\ \nonumber
-&\leq \frac{\|( \mathbf{BPD} - \mathbf{A}) \mathbf{x}_i\|_2 + \|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline x}_i\|_2}{L_{2k}(\mathbf{BPD})} \\
-&\leq \frac{C_1\varepsilon \|\mathbf{x}_i\|_1 + \varepsilon}{L_{2k}(\mathbf{BPD})},
-\end{align}
-%\begin{align}\label{stuff}
-%\frac{ \|\mathbf{x} - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x} \|_1 } { \|\mathbf{D}^{-1}\|_1 }  \
-%&\leq \|\mathbf{Dx} - \mathbf{P}^{\top}\mathbf{\overline x} \|_1 \\ \nonumber
-%&\leq \frac{\|\mathbf{BP}(\mathbf{D}\mathbf{x} - \mathbf{P}^{\top}\mathbf{\overline x})\|_2}{L_{2k}(\mathbf{BP})} \\ \nonumber
-%&\leq \frac{\|( \mathbf{BPD} - \mathbf{A}) \mathbf{x}\|_2 + \|\mathbf{A}\mathbf{x} - \mathbf{B}\mathbf{\overline x}\|_2}{L_{2k}(\mathbf{BP})} \\
-%&\leq \frac{C_1\varepsilon \|\mathbf{x}\|_1 + \varepsilon}{L_{2k}(\mathbf{BP})},
-%\end{align}
-where the first term in the numerator above follows from the triangle inequality and \eqref{Cstable}.
-
-It remains for us to bound the denominator. For any $2k$-sparse $\mathbf{x}$, we have by the triangle inequality:
-\begin{align*}
-\|\mathbf{BPD}\mathbf{x}\|_2 
-&\geq \|\mathbf{A}\mathbf{x}\|_2 - \|(\mathbf{A} - \mathbf{BPD})\mathbf{x}\|_2 \\
-&\geq \sqrt{2k} (L_{2k}(\mathbf{A}) -  C_1\varepsilon) \|\mathbf{x}\|_2,
-\end{align*}
-
-%\begin{align*}
-%\|\mathbf{BP}\mathbf{x}\|_2 
-%&\geq \|\mathbf{A}\mathbf{D}^{-1}\mathbf{x}\|_2 - \|(\mathbf{A} - \mathbf{BPD})\mathbf{D}^{-1}\mathbf{x}\|_2 \\
-%&\geq \sqrt{2k} (L_{2k}(\mathbf{A}) -  C_1\varepsilon) \|\mathbf{D}^{-1}\mathbf{x}\|_2, \\ 
-%&\geq \sqrt{2k} (L_{2k}(\mathbf{A}) -  C_1\varepsilon) \|\mathbf{D}^{-1}\|_{?} \| \mathbf{x}\|_2,
-%\end{align*}
-%
-We therefore have that $L_{2k}(\mathbf{BPD}) \geq L_{2k}(\mathbf{A}) - C_1\varepsilon  > 0$, and \eqref{b-PDa} then follows from \eqref{stuff}.
-The reader may also verify that $L_{2k}(\mathbf{BP}) \geq L_{2k}(\mathbf{BPD}) / \|\mathbf{D}\|_1$.
-
-The heart of the matter is therefore \eqref{Cstable}, which we now establish beginning with the important special case of $k = 1$.
-
-\begin{proof}[Proof of Thm.~\ref{DeterministicUniquenessCorollary} for $k=1$]
-Since the only 1-uniform hypergraph with the SIP is $[m]$, which is obviously regular, we require only $\mathbf{x}_i = c_i \mathbf{e}_i$ for $i \in [m]$, with $c_i \neq 0$ to guarantee  linear independence.
-While we have yet to define $C_1$ generally, in this case we may set $C_1 = 1/ \min_{\ell \in [m]} |c_{\ell}|$ so that $\varepsilon < L_2(\mathbf{A})  \min_{\ell \in [m]} |c_{\ell}|$.
-
-Fix $\mathbf{A} \in \mathbb{R}^{n \times m}$ satisfying $L_2(\mathbf{A}) > 0$, since here we have $2\mathcal{H} = {[m] \choose 2}$, and suppose some $\mathbf{B}$ and $1$-sparse $\mathbf{\overline x}_i \in \mathbb{R}^{\overline m}$ have  $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \varepsilon < L_2(\mathbf{A}) / C_1$ for all $i$.
-Then, there exist $\overline{c}_1, \ldots, \overline{c}_m \in \mathbb{R}$ and a map $\pi: [m] \to [\overline m]$ such that:
-\begin{align}\label{1D}
-\|c_i\mathbf{A}_i - \overline{c}_i\mathbf{B}_{\pi(i)}\|_2 \leq \varepsilon,\ \ \text{for $i \in [m]$}.
-\end{align} 
-Note that $\overline{c}_i \neq 0$, since otherwise we would reach the following contradiction: $\|\mathbf{A}_i \|_2 \leq C_1 |c_i| \|\mathbf{A}_i \|_2  \leq C_1\varepsilon < L_2(\mathbf{A}) \leq L_1(\mathbf{A}) = \min_{i \in [m]} \|\mathbf{A}_{i}\|_2$.
-%implies by \eqref{delrho} the contradiction $|c_i| < \min_{\ell \in [m]} | c_\ell |$.
-
-We now show that $\pi$ is injective (in particular, a permutation if $\overline m = m$).
-Suppose that $\pi(i) = \pi(j) = \ell$ for some $i \neq j$ and $\ell$.
-Then, $\|c_{i}\mathbf{A}_{i} - \overline{c}_{i} \mathbf{B}_{\ell}\|_2  \leq \varepsilon$ and $\|c_{j}\mathbf{A}_{j} - \overline{c}_{j}\mathbf{B}_{\ell}\|_2 \leq \varepsilon$, and we have: %Scaling and summing these inequalities by $|\overline{c}_{i}|$ and $|\overline{c}_{j}|$, respectively, and applying the triangle inequality to annihilate the terms in $\mathbf{B}_\ell$, we obtain:
-\begin{align*}
-(|\overline{c}_{i}| + |\overline{c}_{j}|) \varepsilon
-&\geq |\overline{c}_{i}| \|c_{j}\mathbf{A}_{j} - \overline{c}_{j}\mathbf{B}_{\ell}\|_2  + |\overline{c}_{j}| \|c_{i}\mathbf{A}_{i} - \overline{c}_{i} \mathbf{B}_{\ell}\|_2 \nonumber \\
-&\geq \|\mathbf{A}(\overline{c}_{i}c_{j} \mathbf{e}_{j} - \overline{c}_{j}c_{i}\mathbf{e}_{i})\|_2 \nonumber \\ 
-&\geq \sqrt{2}  L_2(\mathbf{A}) \|\overline{c}_{i}c_{j} \mathbf{e}_{j} - \overline{c}_{j}c_{i}\mathbf{e}_{i}\|_2 \nonumber \\
-&\geq  L_2(\mathbf{A}) \left( |\overline{c}_{i}| + |\overline{c}_{j}| \right) \min_{\ell \in [m]} |c_\ell |,
-\end{align*}
-contradicting our assumed upper bound on $\varepsilon$. Hence, the map $\pi$ is injective and so $\overline m \geq m$. %Setting $\overline J = \pi([m])$ and
-
-Letting $\mathbf{P}$ and $\mathbf{D}$ be the $\overline m \times \overline m$ permutation and invertible diagonal matrices with, respectively, columns $\mathbf{e}_{\pi(i)}$ and $\frac{\overline{c}_i}{c_i}\mathbf{e}_i$ for $i \in [m]$ (otherwise, $\mathbf{e}_{i}$ for $i \in [\overline{m}] \setminus [m]$), we may rewrite \eqref{1D} to see that for all $i \in [m]$:
-\begin{align*}
-\|\mathbf{A}_i - (\mathbf{BPD})_i\|_2 
-= \|\mathbf{A}_i - \frac{\overline{c}_i}{c_i}\mathbf{B}_{\pi(i)}\|_2 
-\leq \frac{\varepsilon}{|c_i|} 
-\leq C_1\varepsilon.
-\end{align*}
-%\vspace{-.2 cm}
-\end{proof}
-
-An extension of the proof to the general case $k < m$ requires some additional tools to derive the general expression \eqref{Cdef1} for $C_1$.
-These include a generalized notion of distance (Def.~\ref{dDef}) and angle (Def.~\ref{FriedrichsDefinition}) between subspaces as well as a stability result in combinatorial matrix analysis (Lem.~\ref{MainLemma}).
-
-\begin{definition}\label{dDef}
-For $\mathbf{u} \in \mathbb R^m$ and vector spaces $U,V \subseteq \mathbb{R}^m$, let $\text{\rm dist}(\mathbf{u}, V) := \min \{\| \mathbf{u}-\mathbf{v} \|_2: \mathbf{v} \in V\}$ and define:
-\begin{align}
-d(U,V) := \max_{\mathbf{u} \in U, \ \|\mathbf{u}\|_2 \leq 1} \text{\rm dist}(\mathbf{u},V).
-\end{align}
-\end{definition}
-
-We note the following facts about $d$. Clearly, 
-\begin{align}\label{UsubU}
-U' \subseteq U \implies d(U',V) \leq d(U,V).
-\end{align}
-From \cite[Ch.~4 Cor.~2.6]{Kato2013}, we also have: %Kato p.223
-\begin{align}\label{dimLem}
-d(U,V) < 1 \implies \dim(U) \leq \dim(V),
-\end{align}
-and from \cite[Lem.~3.2]{Morris10}:
-\begin{align}\label{eqdim}
-\dim(U) = \dim(V) \implies d(U,V) = d(V,U).
-\end{align}
-
-The following is our result in combinatorial matrix analysis; it contains most of the complexity in the proof of Thm.~\ref{DeterministicUniquenessTheorem}.
-
-\begin{lemma}\label{MainLemma}
-If an $n \times m$ matrix $\mathbf{A}$ has $L_{2\mathcal{H}}(\mathbf{A}) > 0$ for some $r$-regular $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP, then the following holds for $C_2 > 0$ given by \eqref{Cdef2}:
-
-Fix $\varepsilon < L_2(\mathbf{A}) / C_2$. If for some $n \times \overline m$ matrix $\mathbf{B}$ and map $\pi: \mathcal{H} \mapsto {[\overline m] \choose k}$,
-\begin{align}\label{GapUpperBound}
-d(\bm{\mathcal{A}}_S, \bm{\mathcal{B}}_{\pi(S)}) \leq \varepsilon, \ \  \text{for $S \in \mathcal{H}$},
-\end{align}
-then $\overline m \geq m$, and provided $\overline m (r-1) < mr$, there is a permutation matrix $\mathbf{P}$ and invertible diagonal $\mathbf{D}$ such that:
-\begin{align}\label{MainLemmaBPD}
-\|\mathbf{A}_i - (\mathbf{B}\mathbf{PD})_i\|_2 \leq C_2 \varepsilon, \ \  \text{for } i \in J,
-\end{align}
-for some $J \subseteq [m]$ of size \mbox{$m - (r-1)(\overline m - m)$}.
-\end{lemma}
-
-%\begin{lemma}\label{MainLemma}
-%Fix $\mathbf{A} \in \mathbb{R}^{n \times m}$ with $L_\mathcal{H}(\mathbf{A}) > 0$ for some regular $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP.
-There exists a constant $C_2 > 0$ for which the following holds for all $\varepsilon < L_2(\mathbf{A}) / C_2$:
-
-%If a matrix $\mathbf{B} \in \mathbb{R}^{n \times m}$ and map $\pi: E \mapsto {m \choose k}$ satisfy:
-%\begin{align}\label{GapUpperBound}
-%d(\text{\rm span}\{\mathbf{A}_{S}\}, \bm{\mathcal{B}}_{\pi(S)}) \leq \varepsilon, \ \ \text{for $S \in \mathcal{H}$},
-%\end{align}
-%then there exist a permutation matrix $\mathbf{P}$ and invertible diagonal matrix $\mathbf{D}$ such that:
-%\begin{align}\label{MainLemmaBPD}
-%\|\mathbf{A}_j - \mathbf{BPD}_j\|_2 \leq C_2 \varepsilon, \ \  \text{for } j \in [m],
-%\end{align}
-%\end{lemma}
-
-We present the constant $C_2$ (a function of $\mathbf{A}$ and $\mathcal{H}$) relative to a quantity used in \cite{Deutsch12} to analyze the convergence of the ``alternating projections" algorithm for projecting a point onto the intersection of subspaces.
-We incorporate this quantity into the following definition, which we refer to in our proof of Lem.~\ref{DistanceToIntersectionLemma} in the Appendix; specifically, we use it to bound the distance between a point and the intersection of subspaces given an upper bound on its distance from each subspace.
-
-\begin{definition}\label{FriedrichsDefinition}
-For a collection of real subspaces $\mathcal{V} = \{V_i\}_{i=1}^\ell$, define $\xi(\mathcal{V}) := 0$ when $|\mathcal{V}| = 1$, and otherwise:
-\begin{align}\label{xi}
-\xi^2(\mathcal{V}) := 1 -  \max \prod_{i=1}^{\ell-1} \sin^2  \theta \left(V_i, \cap_{j>i} V_j \right) ,
-\end{align} 
-%
-where the maximum is taken over all ways of ordering 
-%\footnote{We modify the quantity in \cite{Deutsch12} in this way since the subspace ordering is irrelevant to our purpose.} 
-the $V_i$ and the angle $\theta \in (0,\frac{\pi}{2}]$ is defined implicitly as \cite[Def.~9.4]{Deutsch12}:
-\begin{align*}
-\cos{\theta(U,W)} := \max\left\{ |\langle \mathbf{u}, \mathbf{w} \rangle|: \substack{ \mathbf{u} \in U \cap (U \cap W)^\perp, \ \|\mathbf{u}\|_2 \leq 1 \\ \mathbf{w} \in W \cap (U \cap W)^\perp, \  \|\mathbf{w}\|_2 \leq 1 } \right\}.
-\end{align*}
-\end{definition}
-Note that $\theta \in (0,\frac{\pi}{2}]$ implies $0 \leq \xi < 1$, and that $\xi(\mathcal{V}') \leq \xi(\mathcal{V})$ when $\mathcal{V}' \subseteq \mathcal{V}$.\footnote{We acknowledge the counter-intuitive property: $\theta =  \pi/2$ when $U \subseteq W$.}
-
-The constant $C_2 > 0$ of Lem.~\ref{MainLemma} can now be expressed as:  
-\begin{align}\label{Cdef2}
-	C_2(\mathbf{A}, \mathcal{H}) := \frac{ (r+1) \max_{j \in [m]} \|\mathbf{A}_j\|_2}{ 1- \max_{\mathcal{G} \in {\mathcal{H} \choose r+1}} \xi( \bm{\mathcal{A}}_\mathcal{G} ) }.
-\end{align}
-
-We next define the constant $C_1 > 0$ of Thm.~\ref{DeterministicUniquenessTheorem} in terms of $C_2$.
-Given vectors $\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$, let $\mathbf{X}$ denote the $m \times N$ matrix with columns $\mathbf{x}_i$ and let $I(S)$ denote the set of indices $i$ for which $\mathbf{x}_i$ is supported in $S$.
-We define:
-\begin{align}\label{Cdef1}
-C_1(\mathbf{A}, \mathcal{H}, \{\mathbf{x}_i\}_{i=1}^N) := \frac{ C_2(\mathbf{A}, \mathcal{H}) } { \min_{S \in \mathcal{H}} L_k(\mathbf{AX}_{I(S)}) }.
-\end{align}
-Given the assumptions of Thm.~\ref{DeterministicUniquenessTheorem} on $\mathbf{A}$ and the $\mathbf{x}_i$, this expression for $C_1$ is well-defined\footnote{\label{note1}To see this, fix $S \in \mathcal{H}$ and $k$-sparse $\mathbf{c}$.
-Using the definitions, we have $\|\mathbf{AX}_{I(S)}\mathbf{c}\|_2 \geq \sqrt{k} L_\mathcal{H}(\mathbf{A})\|\mathbf{X}_{I(S)}\mathbf{c}\|_2 \geq k L_\mathcal{H}(\mathbf{A}) L_k(\mathbf{X}_{I(S)})\|\mathbf{c}\|_2$.
-Thus, $L_k(\mathbf{AX}_{I(S)}) \geq \sqrt{k} L_\mathcal{H}(\mathbf{A}) L_k(\mathbf{X}_{I(S)}) > 0$, since $L_{\mathcal{H}}(\mathbf{A}) \geq L_{2\mathcal{H}}(\mathbf{A})> 0$ and $L_k(\mathbf{X}_{I(S)}) > 0$ by general linear position of the $\mathbf{x}_i$.} and yields an upper bound on $\varepsilon$ consistent with that proven sufficient in the case $k=1$ considered at the beginning of this section.\footnote{When $\mathbf{x}_i = c_i\mathbf{e}_i$, we have $C_2 \geq 2\|\mathbf{A}_i\|_2$ and the denominator in \eqref{Cdef1} becomes $\min_{i \in [m]} |c_i| \|\mathbf{A}_i\|_2$; hence, $C_1 \geq 2 / \min_{i \in [m]} |c_i|$.}
-% C_2(\mathbf{A}, \mathcal{H}) := \frac{ (r+1) \max_{j \in [m]} \|\mathbf{A}_j\|_2}{ \min_{\mathcal{G} \in {\mathcal{H} \choose r} \cup {\mathcal{H} \choose r+1}} \xi( \{ \bm{\mathcal{A}}_S \}
-
-The practically-minded reader should note that the explicit constants $C_1$ and $C_2$ are effectively computable: the quantity $L_k$ may be calculated as the smallest singular value of a certain matrix, while the quantity $\xi$ involves computing ``canonical angles'' between subspaces, which reduces again to an efficient singular value decomposition.
-There is no known fast computation of $L_k$ in general, however, since even $L_{k} > 0$ is NP-hard \cite{tillmann2014computational}, although 
-efficiently computable bounds have been proposed (e.g., via the ``mutual coherence" of a matrix \cite{donoho2003optimally}); alternatively, 
-fixing $k$ yields polynomial complexity.
-Moreover, calculating $C_2$ requires an exponential number of queries to $\xi$ unless $r$ is held fixed, too (e.g., the ``cyclic order'' hypergraphs described above have $r=k$).
-Thus, as presented, $C_1$ and $C_2$ are not efficiently computable in general.
-% , but efficient subcases do exist and may be of practical relevance.
-
-\begin{proof}[Proof of Thm.~\ref{DeterministicUniquenessCorollary} for $k < m$] 
-We find a map $\pi: \mathcal{H} \to {[m] \choose k}$ for which the distance $d(\bm{\mathcal{A}}_S, \bm{\mathcal{B}}_{\pi(S)})$ is controlled by $\varepsilon$ for all $S \in \mathcal{H}$.
-Applying Lem.~\ref{MainLemma} then completes the proof.
-%We shall show that for every $S \in \mathcal{H}$ there is some $\overline S \in {[\overline m] \choose k}$ for which the distance $d(\bm{\mathcal{A}}_S, \bm{\mathcal{B}}_{\overline S})$ is controlled by $\varepsilon$.
-Applying Lem.~\ref{MainLemma} with the map $\pi$ defined by $S \mapsto \overline S$ then completes the proof.
-
-Fix $S \in \mathcal{H}$.
-Since there are more than $(k-1){\overline m \choose k}$ vectors $\mathbf{x}_i$ supported in $S$, by the pigeonhole principle there must be some $\overline S \in {[\overline m] \choose k}$ and a set of $k$ indices $K \subseteq I(S)$ for which all $\mathbf{\overline x}_i$ with $i \in K$ are supported in $\overline S$.
-It also follows\footnotemark[\ref{note1}] from $L_{2\mathcal{H}}(\mathbf{A}) > 0$ and the general linear position of the $\mathbf{x}_i$ that $L_k(\mathbf{AX}_{K}) > 0$; that is, the columns of the $n \times k$ matrix $\mathbf{AX}_K$ form a basis for $\bm{\mathcal{A}}_S$.
-
-Fixing $\mathbf{y} \in \bm{\mathcal{A}}_S \setminus \{\mathbf{0}\}$, there then exists $\mathbf{c} = (c_1, \ldots, c_k) \in \mathbb{R}^k \setminus \{\mathbf{0}\}$ such that $\mathbf{y} = \mathbf{AX}_K\mathbf{c}$.
-Setting \mbox{$\mathbf{\overline{y}} = \mathbf{B\overline{X}}_K\mathbf{c}$, which is in $\bm{\mathcal{B}}_{\overline S}$}, we have by triangle inequality:
-\begin{align*}
-\|\mathbf{y} - \mathbf{\overline{y}}\|_2 
-%&= \|\sum_{i=1}^k c_i(\mathbf{AX}_K - \mathbf{B\overline{X}}_K)_i\|_2
-&= \|(\mathbf{AX}_K - \mathbf{B\overline{X}}_K)\mathbf{c}\|_2
-%\leq \varepsilon \sum_{i=1}^k |c_i| \\
-\leq \varepsilon \|\mathbf{c}\|_1
-\leq \varepsilon \sqrt{k}  \|\mathbf{c}\|_2  \\
-&\leq \frac{\varepsilon}{L_k(\mathbf{AX}_K)} \|\mathbf{y}\|_2,
-\end{align*}
-where the last inequality uses \eqref{Ldef}. From Def.~\ref{dDef}:
-\begin{align}\label{rhs222}
-d(\bm{\mathcal{A}}_S, \bm{\mathcal{B}}_{\overline S}) 
-\leq \frac{\varepsilon}{  L_k(\mathbf{AX}_{K}) } 
-\leq \frac{\varepsilon}{  L_k(\mathbf{AX}_{I(S)}) } 
-\leq \varepsilon \frac{C_1}{C_2}.
-\end{align}
-%
-Finally, apply Lem.~\ref{MainLemma} with $\varepsilon < L_2(\mathbf{A})/C_1$ and $\pi(S) := \overline S$. % L_2(A) > 0 by def of L, since L_2H(A) > 0 and H covers [m]
-\end{proof}
-
-Before moving on to the proof of Thm.~\ref{SLCopt}, we briefly revisit our discussion on sample complexity from the end of the previous section.
-While an exponential number of samples may very well prove to be necessary in the deterministic or almost-certain case, our proof of Thm.~\ref{DeterministicUniquenessTheorem} can be extended to hold with some probability for \emph{any} number of samples by alternative appeal to a probabilistic pigeonholing at the point early in the proof where the (deterministic) pigeonhole principle is applied to show that for every $S \in \mathcal{H}$, there exist $k$ vectors $\mathbf{x}_i$ supported on $S$ whose corresponding $\mathbf{\overline x}_i$ all share the same support.\footnote{A famous example of such an argument is the counter-intuitive ``birthday paradox", which demonstrates that the probability of two people having the same birthday in a room of twenty-three is greater than 50\%.}
-Given insufficient samples, this argument has some less-than-certain probability of being valid for each $S \in \mathcal{H}$.
-Nonetheless, simulations with small hypergraphs confirm that the probability of success very quickly approaches one once the number of samples $N$ surpasses a small fraction of the deterministic sample complexity.
-
-\begin{proof}[Proof of Thm.~\ref{SLCopt}]
-We bound the number of $k$-sparse $\mathbf{\overline x}_i$ from below and then apply Thm.~\ref{DeterministicUniquenessCorollary}. 
-%We now apply this fact to bound the number of $k$-sparse $\mathbf{\overline x}_i$. 
-Let $n_p$ be the number of $\mathbf{\overline x}_i$ with $\|\mathbf{\overline x}_i\|_0 = p$.
-Since the $\mathbf{x}_i$ are all $k$-sparse, by \eqref{minsum} we have:
-\begin{align*}
-%\mbox{$k \sum_{p = 0}^{\overline m} n_p \geq \sum_{i=0}^N \|\mathbf{x}_i\|_0 \geq \sum_{i=0}^N \|\mathbf{\overline x}_i\|_0 = \sum_{p=0}^{\overline m} p n_p.$}
-\sum_{p=0}^{\overline m} p n_p =  \sum_{i=0}^N \|\mathbf{\overline x}_i\|_0
-\leq \sum_{i=0}^N \|\mathbf{x}_i\|_0 
-\leq kN
-\end{align*}
-Since $N = \sum_{p = 0}^{\overline m} n_p$, we then have $\sum_{p = 0}^{\overline m} (p-k) n_p \leq 0$. Splitting the sum yields:
-\begin{align}\label{eqn}
-\sum_{p = k+1}^{\overline m} n_p \leq \sum_{p = k+1}^{\overline m} (p-k) n_p \leq \sum_{p = 0}^k (k-p)n_p \leq k \sum_{p = 0}^{k-1} n_p,
-\end{align}
-%
-demonstrating that the number of vectors $\mathbf{\overline x}_i$ that are \emph{not} $k$-sparse is bounded above by how many are $(k-1)$-sparse.
-
-Next, observe that no more than $(k-1)|\mathcal{H}|$ of the $\mathbf{\overline x}_i$ share a support $\overline S$ of size less than $k$.
-Otherwise, by the pigeonhole principle, there is some $S \in \mathcal{H}$ and a set of $k$ indices $K \subseteq I(S)$ for which all $\mathbf{x}_i$ with $i \in K$ are supported in $S$; as argued previously, \eqref{rhs222} follows.
-It is simple to show that $L_2(\mathbf{A}) \leq \max_j\|\mathbf{A}_j\|_2$, and since $0 \leq \xi < 1$, the right-hand side of \eqref{rhs222} is less than one for $\varepsilon < L_2(\mathbf{A})/C_1$.
-Thus, by \eqref{dimLem} we would have the contradiction $k = \dim(\bm{\mathcal{A}}_S) \leq \dim(\bm{\mathcal{B}}_{\overline S}) \leq |\overline S| < k.$
-
-The total number of $(k-1)$-sparse vectors $\mathbf{\overline x}_i$ thus cannot exceed $|\mathcal{H}|(k-1){ \overline m \choose k-1}$.
-By \eqref{eqn}, no more than $|\mathcal{H}|k(k-1){ \overline m \choose k-1}$ vectors $\mathbf{\overline x}_i$ are not $k$-sparse.
-Since for every $S \in \mathcal{H}$ there are over $(k-1)\left[ {\overline m \choose k} + |\mathcal{H}|k{ \overline m \choose k-1} \right]$ vectors $\mathbf{x}_i$ supported there, it must be that more than $(k-1){\overline m \choose k}$ of them have corresponding $\mathbf{\overline x}_i$ that are $k$-sparse.
-The result now follows from Thm.~\ref{DeterministicUniquenessCorollary}, noting by the triangle inequality that $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline x}_i\| \leq 2\eta$ for $i = 1, \ldots, N$.
-\end{proof}
-
-%\begin{proof}[Proof (sketch) of Thm.~\ref{robustPolythm}]
-%Let $\textbf{M}$ be the matrix with columns $\mathbf{A}\mathbf{x}_i$, $i \in [N]$.
-Consider the polynomial $\prod_{S \in {[N] \choose 2k}} \sum_{S' \in {[n] \choose 2k}} (\det \textbf{M}_{S',S})^2$ in the indeterminate entries of $\mathbf{A}$ and $\mathbf{x}_i$, with notation as in Sec.~\ref{Results}.
-%It can be checked that when this polynomial is nonzero for a substitution of real numbers for the indeterminates, all of the genericity requirements on $\mathbf{A}$ and $\mathbf{x}_i$ in our proofs of stability in Thm.~\ref{DeterministicUniquenessTheorem} are satisfied (in particular, the spark condition \eqref{SparkCondition} on $\mathbf{A}$).
-%\end{proof}
-
-%\begin{proof}[Proof (sketch) of Cor.~\ref{ProbabilisticCor}]
-%First, note that if a set of measure spaces $\{(X_{\ell}, \Sigma_{\ell}, \nu_{\ell})\}_{\ell=1}^p$ has that $\nu_{\ell}$ is absolutely continuous with respect to $\mu$ for all $\ell \in [p]$, where $\mu$ is the standard Borel measure on $\mathbb{R}$, then the product measure $\prod_{\ell=1}^p \nu_{\ell}$ is absolutely continuous with respect to the standard Borel product measure on $\mathbb{R}^p$.
-% for space:  (e.g.,  \cite{folland2013real}).
-%By Thm.~\ref{robustPolythm}, there is a polynomial that is nonzero when $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$; in particular, stability holds almost surely.
-%\end{proof}
-
-\section{Discussion}\label{Discussion}
-
-A main motivation for this work is the emergence of seemingly unique representations from sparse coding models trained on natural data, despite the varied assumptions underlying the many algorithms in current use.
-Our results constitute an important step toward explaining these phenomena as well as unifying many publications on the topic by deriving general deterministic conditions under which identification of parameters in this model is not only possible but also robust to uncertainty in measurement and model choice.
-
-We have shown that, given sufficient data, the problem of determining a dictionary and sparse codes with minimal support size (Prob.~\ref{OptimizationProblem}) reduces to an instance of Prob.~\ref{InverseProblem}, to which our main result (Thm.~\ref{DeterministicUniquenessTheorem}) applies: every dictionary and sequence of sparse codes consistent with the data are equivalent up to inherent relabeling/scaling ambiguities and a discrepancy (error) that scales linearly with the measurement noise or modeling inaccuracy.
-The constants we provide are explicit and computable; as such, there is an effective procedure that sufficiently affirms if a proposed solution to these problems is indeed unique up to noise and inherent ambiguities, although it is not efficient in general.
-
-%A compelling feature of this model is its simple instantiation of the principle of Occam's razor: a natural video, for instance, is modeled as a linear combination of a small number of spatiotemporal building blocks, each representing an archetypical feature latent in the data.
-
-%For theoretical neuroscience in particular, dictionary learning and related methods have recovered characteristic components of natural images \cite{Olshausen96, hurri1996image, bell1997independent, van1998independent} and sounds \cite{bellsejnowski1996, smithlewicki2006} that reproduce response properties of certain cortical neurons.
-
-%to the recovery of ``mouse neuronal activity representing location on a track \cite{agarwal2014spatially}
-
-%Moreover, we show that even if the meta-parameter for the number of dictionary elements is overestimated, a subset of parameters may still be identifiable up to noise.
-
-Beyond an extension of existing noiseless guarantees \cite{Hillar15} to the noisy regime and their novel application to Prob.~\ref{OptimizationProblem}, our work contains a theory of combinatorial designs for support sets key to identification of dictionaries.
-We incorporate this idea into a fundamental lemma in matrix theory (Lem.~\ref{MainLemma}) that draws upon the definition of a matrix lower bound (\ref{Ldef}) induced by a hypergraph.
-The new insight offered by this combinatorial approach allows for guaranteed recovery of some or all dictionary elements even if: 1) dictionary size is overestimated, 2) data cover only a polynomial number of distinct sparse supports, and 3) dictionaries do not satisfy the spark condition.
-
-The absence of any assumptions about dictionaries solving Prob.~\ref{InverseProblem} was a major technical obstruction in proving Thm.~\ref{DeterministicUniquenessTheorem}.
-We sought such a general guarantee because of the practical difficulty in ensuring that an algorithm maintain a dictionary satisfying the spark condition \eqref{SparkCondition} at each iteration, an implicit requirement of all previous works except \cite{Hillar15}; indeed, even certifying a dictionary has this property is NP-hard \cite{tillmann2014computational}.
-
-One direct application of this work is to theoretical neuroscience, wherein our theorems justify the mathematical soundness of one of the few hypothesized theories of bottleneck communication in the brain \cite{Isely10}: that sparse neural population activity is recoverable from its noisy linear compression through a randomly constructed (but unknown) wiring bottleneck by any biologically plausible unsupervised sparse coding method that solves Prob.~\ref{DeterministicUniquenessTheorem} or \ref{SLCopt} (e.g., \cite{rehnsommer2007, rozell2007neurally, pehlevan2015normative}).\footnote{We refer the reader to \cite{ganguli2012compressed} for more on interactions between dictionary learning and neuroscience.}
-
-In fact, uniqueness guarantees with minimal assumptions apply to all areas of data science and engineering that utilize learned sparse structure.
-For example, several groups have applied compressed sensing to signal processing tasks; for instance, in MRI analysis \cite{lustig2008compressed}, image compression \cite{Duarte08}, and even the design of an ultrafast camera \cite{Gao14}.
-It is only a matter of time before these systems incorporate dictionary learning to encode and decode signals (e.g., in a device that learns structure from motion \cite{kong2016prior}), just as scientists have used sparse coding to make sense of their data \cite{jung2001imaging, agarwal2014spatially, lee2016sparse, wu2016stability}.
-
-Assurances offered by our theorems certify that different devices and algorithms learn equivalent representations given enough data from statistically identical systems.\footnote{To contrast with the current hot topic of ``Deep Learning'', there are few such uniqueness guarantees for these models of data; moreover, even small noise can dramatically alter their output \cite{goodfellow2014explaining}.}
-Indeed, a main reason for the sustained interest in dictionary learning as an unsupervised method for data analysis seems to be the assumed well-posedness of parameter identification in the model, confirmation of which forms the core of our findings.
-
-We close with some challenges left open by our work.
-All conditions stated here guaranteeing the uniqueness and stability of sparse representations have only been shown sufficient; it remains open, therefore, to extend them to necessary conditions, be they on required sample size, the structure of support set hypergraphs, or tolerable error bounds.
-On this last note, we remark that our deterministic treatment considers always the ``worst-case" noise, whereas the ``effective" noise sampled from a concentrated distribution might be significantly reduced, especially for high-dimensional data.
-It would be of great practical benefit to see how drastically all conditions can be relaxed by requiring only probabilistic guarantees in this way, or in the spirit of our discussion on probabilistic pigeonholing to reduce sample complexity (as in the famous ``birthday paradox") following the proof of Thm.~\ref{DeterministicUniquenessTheorem}.
-
-Another interesting question raised by our work is for which special cases is it efficient to check that a solution to Prob.~\ref{InverseProblem} or \ref{OptimizationProblem} is unique up to noise and inherent ambiguities.
-Considering that the sufficient conditions we have described for checking this in general are NP-hard to compute, are the necessary conditions hard?
-Are Probs.~\ref{InverseProblem} and \ref{OptimizationProblem} then also hard (e.g., see \cite{Tillmann15})?
-Finally, since Prob.~\ref{SLCopt} is intractable in general, but efficiently solvable by $\ell_1$-norm minimization when the matrix is known (and has a large enough lower bound over sparse domains \cite{eldar2012compressed}), is there a version of Thm.~\ref{SLCopt} certifying when Prob.~\ref{OptimizationProblem} can be solved efficiently in full by similar means?
-% [*** Incorporate this open problem with more words ***]
-
-We hope these remaining challenges pique the interest of the community to pick up where we have left off and that the theoretical tools showcased here may be of use to this end.
-
-%We close with some challenges left open by our work.
-First, there is the basic problem of proving optimal lower bounds on sufficient sample size $N$ guaranteeing the uniqueness and stability of sparse representations.
-The pigeonholing argument in the proof of Thm.~\ref{DeterministicUniquenessTheorem} is loose in that it assigns to each support $S \in \mathcal{H}$ a corresponding support $\overline S$ without consideration of previously matched pairs; although we doubt tightening in this way will lead to sub-exponential sample sizes.
-Sample complexity will also benefit from lowering the number of required supports, i.e.
-the size of regular uniform hypergraphs satisfying the SIP.
-The regularity requirement on support hypergraphs can be loosened to allow for certain non-regular hypergraphs satisfying constraints on the degree sequence of nodes; though we impose regularity for clarity of exposition.
-It is then natural to ask: what is the smallest hypergraph satisfying the required constraints forgiven $m$ and $k$?
-Finally, the error bounds can be improved by tightening the constant $C_1$, e.g.
-via an improvement in Lemma ?.
-
-%Solving Prob.~\ref{SLCopt} directly is intractable in general since it necessitates, for each proposed dictionary $\mathbf{B}$, a combinatorial search for the supports of the associated sparse codes $\mathbf{\overline x}_i$.
-A common work-around is to convexify the problem (for fixed $\mathbf{B}$) by substituting the norm $\|\cdot\|_0$ with $\|\cdot\|_1$, impelled the fact that matrices $\mathbf{A}$ with large enough $L_{2k}(\mathbf{A})$ induce the same sparse codes via minimization of either norm \cite{?}.
-To this end, the lower bound $L_{2k}(\mathbf{BP}) \geq (L_{2k}(\mathbf{A}) - C_1\varepsilon) / \|\mathbf{D}\|_1$ implied by Thm.~\ref{DeterministicUniquenessTheorem} hints at conditions on the generating dictionary $\mathbf{A}$ and $k$-sparse codes $\mathbf{x}_i$ under which \emph{all} matrices $\mathbf{B}$ (of bounded column-norm) that solve Prob.~\ref{OptimizationProblem} also share this property of $\mathbf{A}$ by virtue of uniqueness and stability.
-One might then imagine an inference procedure whereby sparse codes are inferred via minimization of $\|\cdot\|_1$, but solutions still evaluated by their collective support size, yielding unique optimal solutions to Prob.~\ref{SLCopt} if only constraints could be imposed such that the learning procedure eventually guides $\mathbf{B}$ through an optimal dictionary.
-% (e.g.
-the dictionary is a member of a known finite set).
-
-\textbf{Acknowledgement.} We thank Fritz Sommer and Darren Rhea for early thoughts, and Ian Morris for posting \eqref{eqdim} online.
-
-%\section{EXTRA}
-%An additional consequence of Thm.~\ref{DeterministicUniquenessTheorem} of potential practical relevance to is the implied lower bound $L_{2k}(\mathbf{BPD}) \geq L_{2k}(\mathbf{A}) - C_1\varepsilon$ in the case where $\mathbf{A}$ satisfies \eqref{SparkCondition}.
-Since solving Prob.~\ref{SLCopt} directly requires a combinatorial search over sparse supports for the $\mathbf{\overline x}_i$ for each proposed dictionary $\mathbf{B}$, rendering it intractable in general, a common strategy is to replace the $\ell_0$-norm in \eqref{minsum} with the $\ell_1$-norm, thereby transforming the inference of sparse $\mathbf{\overline x}_i$ for a fixed dictionary $\mathbf{B}$ into a convex optimization solvable by a linear program.
-A major advance in compressive sensing was the discovery that, for fixed $\mathbf{B}$, solutions to \eqref{minsum} using either norm yield the same sparse vectors $\mathbf{\overline x}_i$ (up to noise) provided $L_{2k}(\mathbf{B})$ is large enough \cite{?}.
-What our results hint at are conditions on the generating dictionary $\mathbf{A}$ and $k$-sparse codes $\mathbf{x}_i$ under which \emph{all} matrices $\mathbf{B}$ (of bounded column-norm) that solve Prob.~\ref{OptimizationProblem} also share this property by virtue of uniqueness and stability; that is, conditions which guarantee that the sparse codes $\mathbf{\overline x}_i$ solving Prob.~\ref{OptimizationProblem} also solve the convexified problem when the corresponding dictionary $\mathbf{B}$ is held fixed.
-It remains to determine, however, what practical conditions preclude matrices that don't solve Prob.~\ref{OptimizationProblem} from nonetheless solving the convexified problem.
-%
-%Regardless, an implication of the above observation is that the following algorithm solves Prob.~\ref{OptimizationProblem} without appeal to combinatorial search:
-%\begin{enumerate}
-%\item List all matrices $\mathbf{B}$.
-%\item For each matrix $\mathbf{B}$, solve $\mathbf{\overline x}_i = \arg \min \|\mathbf{v}\|_1$ s.t. $\|\mathbf{Bv} - \mathbf{z}_i\| \leq \eta$ for $i = 1, \ldots, N$.
-%\item Quantify the proposed solution $\mathbf{B}$ and $\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N$ as $\rho(\mathbf{B}, \mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N) = \sum_{i=1}^{N} \|\mathbf{\overline x}_i\|_0$.
-%\item Output $\arg \min_{\mathbf{B}, \mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N} \left( \rho \right)$.
-% \end{enumerate}
-
-%Since its inception some twenty years ago, sparse coding has become a standard tool in signal analysis, yielding myriad insights into the structure of natural signals across a variety of scientific domains.
-In this work,
-
-%We make a final remark about the tightness of our results and the computability of our derived constants.
-%We remark that our constants have been derived for deterministic ``worst-case'' noise, whereas the ``effective'' noise might be smaller when sampled from a distribution.
-
-%Our results suggest that this correspondence could be due to the ``universality'' of sparse representations in natural data, an early idea in neural theory \cite{pitts1947}.
-
-% \vspace{-.2 cm}
-
-%\showacknow % Display the acknowledgments section
-
-\bibliographystyle{IEEEtran}
-\bibliography{chazthm_ieee_trans_sig}
-
-% \vspace{-.2 cm}
-
-\section{Appendix}\label{proofs}
-
-We prove Lem.~\ref{MainLemma} after the following auxiliary lemmas.  % stating and proving some auxiliary lemmas. 
-%First, note that since $\|\mathbf{A}\mathbf{x}\|_2 \leq \max_j\|\mathbf{A}_j\|_2\|\mathbf{x}\|_1$ and $\|\mathbf{x}\|_1 \leq \sqrt{k} \|\mathbf{x}\|_2$ for $k$-sparse $\mathbf{x}$, by \eqref{Ldef} we have the following frequently applied inequality:
-%\begin{align}\label{delrho}
-%L_{k'}(\mathbf{A}) \leq  \max_j\|\mathbf{A}_j\|_2 \ \ \text{for all $k' \leq 2k$}.
-%\end{align}
-
-% and then sketch the proofs of Thm.~\ref{robustPolythm} and Cor.~\ref{ProbabilisticCor}.
-
-%\begin{lemma}\label{spanIntersectionLemma}
-%Let $\mathbf{M} \in \mathbb{R}^{n \times m}$. If every $2k$ columns of $\mathbf{M}$ are linearly independent, then for any $F \subseteq {[m] \choose k}$:
-%\begin{align*}
-%\text{\rm span}\{\mathbf{M}_{\cap F}\}  = \bigcap_{S \in F} \text{\rm span}\{\mathbf{M}_S\}.
-%\end{align*}
-%\end{lemma}
-%\begin{proof}
-%Using induction on $|F|$, it is enough to prove the lemma when $|F| = 2$; but this case follows directly from the assumption.
-%\end{proof}
-
-\begin{lemma}\label{spanIntersectionLemma}
-If $f: V \to W$ is injective, then $f\left(\cap_{i=1}^\ell V_i \right) =  \cap_{i=1}^\ell f\left(V_i\right)$ for any $V_1, \ldots, V_\ell \subseteq V$. ($f(\emptyset):=\emptyset$.)
-%In particular, if for some $E \in 2^{[m]}$ the map $M \in \mathbb{R}^{n \times m}$ is injective on $\cup_{S \in \mathcal{H}} \text{span}\{e_i\}_{i \in S}$ then $\text{span}\{ M_{\cap_{S \in \mathcal{H}} S} \} = \cap_{S \in \mathcal{H}} \text{span}\{M_S\}$.
-\end{lemma}
-\begin{proof}
-By induction, it is enough to prove the case $\ell = 2$.
-Clearly, for any map $f$, if $w \in f(U \cap V)$ then $w \in f(U)$ and $w \in f(V)$; hence, $w \in f(U) \cap f(V)$.
-If $w \in f(U) \cap f(V)$, then $w \in f(U)$ and $w \in f(V)$; thus, $w = f(u) = f(v)$ for some $u \in U$ and $v \in V$, implying $u = v$ by injectivity of $f$.
-It follows that $u \in U \cap V$ and $w \in f(U \cap V)$.
-\end{proof}
-In particular, if a matrix $\mathbf{A}$ satisfies $L_{2\mathcal{H}}(\mathbf{A}) > 0$, then taking $V$ to be the union of subspaces consisting of vectors with supports in $2\mathcal{H}$, we have $\bm{\mathcal{A}}_{\cap \mathcal{G}} = \cap \bm{\mathcal{A}}_\mathcal{G}$ for all $\mathcal{G} \subseteq \mathcal{H}$.
-% \vspace{-.4 cm}
-
-\begin{lemma}\label{DistanceToIntersectionLemma}
-Let $\mathcal{V} = \{V_i\}_{i=1}^k$ be a set of two or more subspaces of $\mathbb{R}^m$, and set $V = \cap \mathcal{V} $.
-For  $\mathbf{u} \in \mathbb{R}^m$, we have (recall Defs.~\ref{dDef}~\&~\ref{FriedrichsDefinition}):
-\begin{align}\label{DTILeq}
-\text{\rm dist}(\mathbf{u}, V) \leq \frac{1}{1 - \xi(\mathcal{V})} \sum_{i=1}^k \text{\rm dist}(\mathbf{u}, V_i).
-\end{align}
-\end{lemma}
-\begin{proof} 
-% When $V = \{\mathbf{0}\}$, the result is trivial, so suppose otherwise.  
-Recall the projection onto the subspace $V \subseteq \mathbb{R}^m$ is the mapping $\Pi_V: \mathbb{R}^m \to V$ that associates with each $\mathbf{u}$ its unique nearest point in $V$; i.e., $\|\mathbf{u} - \Pi_V\mathbf{u}\|_2 = \text{\rm dist}(\mathbf{u}, V)$.
-By repeatedly applying the triangle inequality, we have:
-\begin{align}\label{f}
-\|\mathbf{u} - &\Pi_V\mathbf{u}\|_2 
-\leq \|\mathbf{u} - \Pi_{V_k} \mathbf{u}\|_2 + \|\Pi_{V_k}  \mathbf{u} - \Pi_{V_k}\Pi_{V_{k-1}}\mathbf{u}\|_2 \nonumber \\
-&\ \ \ \ \ \ \ \ \ \ \ + \cdots + \|\Pi_{V_k} \Pi_{V_{k-1}}\cdots \Pi_{V_1} \mathbf{u} - \Pi_V \mathbf{u}\|_2 \nonumber \\
-&\leq  \sum_{\ell=1}^k \|\mathbf{u} - \Pi_{V_{\ell}} \mathbf{u}\|_2 
-+ \|(\Pi_{V_k}\cdots\Pi_{V_{1}} - \Pi_V) \mathbf{u}\|_2,
-\end{align}
-where we have also used that the spectral norm of the orthogonal projections $\Pi_{V_{\ell}}$ satisfies $\|\Pi_{V_{\ell}}\|_2 \leq 1$ for all $\ell$.
-
-It remains to bound the second term in \eqref{f} by $\xi(\mathcal{V}) \|\mathbf{u} - \Pi_V\mathbf{u}\|_2$.
-First, note that $\Pi_{V_\ell} \Pi_V = \Pi_V$ and $\Pi_V^2 = \Pi_V$, so we have $\|(\Pi_{V_k} \cdots \Pi_{V_1} - \Pi_V) \mathbf{u} \|_2
-= \| ( \Pi_{V_k} \cdots\Pi_{V_1} - \Pi_V ) (\mathbf{u} - \Pi_V\mathbf{u})\|_2$. % \leq z\|\mathbf{u} - \Pi_V\mathbf{u}\|_2$.
-Consequently, inequality \eqref{DTILeq} follows from \cite[Thm.~9.33]{Deutsch12}:
-\begin{align}
-\|\Pi_{V_k}\Pi_{V_{k-1}}\cdots\Pi_{V_1} \mathbf{x} - \Pi_V\mathbf{x}\|_2 \leq z \|\mathbf{x}\|_2, \ \ \text{for all } \mathbf{x},
-\end{align}
-with \mbox{$z^2= 1 - \prod_{\ell =1}^{k-1}(1-z_{\ell}^2)$} and \mbox{$z_{\ell} = \cos\theta\left(V_{\ell}, \cap_{s=\ell+1}^k V_s\right)$} (recall $\theta$ from Def.~\ref{FriedrichsDefinition}), after substituting $\xi(\mathcal{V})$ for $z$ and rearranging terms.
-\end{proof}
-\begin{lemma}\label{NonEmptyLemma} 
-Fix an $r$-regular hypergraph $\mathcal{H} \subseteq 2^{[m]}$ satisfying the SIP.
-If the map $\pi: \mathcal{H} \to 2^{[\overline m]}$ has $\sum_{S \in \mathcal{H}} |\pi(S)| \geq \sum_{S \in \mathcal{H}} |S|$ and:
-\begin{align}\label{cond}
-	|\cap \pi(\mathcal{G})| \leq |\cap \mathcal{G} |,\ \ \   \text{for } \mathcal{G} \in {\mathcal{H} \choose r} \cup {\mathcal{H} \choose r+1},
-\end{align}
-%
-then $\overline m \geq m$; and if $\overline m  (r-1) < mr$, the map $i \mapsto \cap_{S \in \sigma(i)} \pi(S)$ is an injective function to $[\overline m]$ from some $J \subseteq [m]$ of size $m - (r-1)(\overline m - m)$ (recall $\sigma$ from Def.~\ref{sip}).
-%In particular, if $\overline m = m$ then $\pi$ is induced by a permutation on $[m]$.
-\end{lemma}
-
-\begin{proof}
-Consider the following set: $T_1 := \{(i, S): i \in \pi(S), S \in \mathcal{H}\}$, which numbers $|T_1| = \sum_{S \in \mathcal{H}} |\pi(S)| \geq \sum_{S \in \mathcal{H}} |S| = \sum_{i \in [m]} \deg_\mathcal{H}(i) = mr$ by $r$-regularity of $\mathcal{H}$.
-Note that $|T_1| \leq \overline m r$; otherwise, pigeonholing the tuples of $T_1$ with respect to their $\overline m$ possible first elements would imply that more than $r$ of the tuples in $T_1$ share the same first element.
-This cannot be the case, however, since then some $\mathcal{G} \in {\mathcal{H} \choose r+1}$ formed from any $r+1$ of their second elements would satisfy $\cap \pi(\mathcal{G}) \neq 0$; hence, $|\cap \mathcal{G}| \neq 0$ by \eqref{cond}, contradicting $r$-regularity of $\mathcal{H}$.
-It follows that $\overline m \geq m$.
-
-Suppose now that $\overline m (r-1) < mr$, so that $p := mr - \overline m (r-1)$ is positive and $|T_1| \geq \overline m (r - 1) + p$.
-Pigeonholing $T_1$ into $[\overline m]$ again, there are at least $r$ tuples in $T_1$ sharing some first element; that is, for some $\mathcal{G}_1 \subseteq \mathcal{H}$ of size $|\mathcal{G}_1| \geq r$, we have $|\cap \pi(\mathcal{G}_1)| \geq 1$ and (by \eqref{cond}) $|\cap \mathcal{G}_1| \geq 1$.
-Since no more than $r$ tuples of $T_1$ can share the same first element, we in fact have $|\mathcal{G}_1| = r$.
-It follows by $r$-regularity that $\mathcal{G}_1$ is a star of $\mathcal{H}$; hence, $|\cap \mathcal{G}_1| = 1$ by the SIP and $|\cap \pi(\mathcal{G}_1)|  = 1$ by \eqref{cond}.
-
-If $p=1$, then we are done.
-Otherwise, define $T_2 := T_1 \setminus \{(i,S) \in T_1: i = \cap \pi(\mathcal{G}_1)\}$, which contains $|T_2| = |T_1| - r \geq (\overline m - 1)(r-1) + (p-1)$ ordered pairs having $\overline m - 1$ distinct first indices.
-Pigeonholing $T_2$ into $[\overline m - 1]$ and repeating the above arguments produces the star $\mathcal{G}_2 \in {\mathcal{H} \choose r}$ with intersection $\cap \mathcal{G}_2$ necessarily distinct (by $r$-regularity) from $\cap \mathcal{G}_1$.
-Iterating this procedure $p$ times in total yields the stars $\mathcal{G}_i$ for which $\cap\mathcal{G}_i \mapsto \cap \pi(\mathcal{G}_i)$ defines an injective map to $[\overline m]$ from $J = \{\cap \mathcal{G}_1, \ldots, \cap \mathcal{G}_p\} \subseteq [m]$.
-\end{proof}
-
-\begin{proof}[Proof of Lem.~\ref{MainLemma}]
-%We will show that the bound \eqref{GapUpperBound} trickles through the intersection semi-lattices of $\{\bm{\mathcal{A}}_S\}_{S \in \mathcal{H}}$ and $\{\bm{\mathcal{B}}_{\overline S}\}_{\overline S \in \pi(\mathcal{H})}$ to yield \eqref{MainLemmaBPD} by virtue of the SIP.
-We begin by showing that $\dim(\bm{\mathcal{B}}_{\pi(S)}) = \dim(\bm{\mathcal{A}}_S)$ for all $S \in \mathcal{H}$.
-Note that since $\|\mathbf{A}\mathbf{x}\|_2 \leq \max_j\|\mathbf{A}_j\|_2\|\mathbf{x}\|_1$ and $\|\mathbf{x}\|_1 \leq \sqrt{k} \|\mathbf{x}\|_2$ for all $k$-sparse $\mathbf{x}$, by \eqref{Ldef} we have $L_2(\mathbf{A}) \leq \max_j\|\mathbf{A}_j\|_2$ and therefore (as $0 \leq \xi < 1$) the right-hand side of \eqref{GapUpperBound} is less than one.
-From \eqref{dimLem}, we have $|\pi(S)| \geq \dim(\bm{\mathcal{B}}_{\pi(S)}) \geq \dim(\bm{\mathcal{A}}_S) = |S|$, the final equality holding by injectivity of $\mathbf{A}_S$.
-As $|\pi(S)| = |S|$, the claim follows.
-Note, therefore, that $\mathbf{B}_{\pi(S)}$ has full-column rank for all $S \in \mathcal{H}$.
-
-We next demonstrate that \eqref{cond} holds.
-Fixing $\mathcal{G} \in {\mathcal{H} \choose r} \cup {\mathcal{H} \choose r+1}$, it suffices to show that $d(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}, \bm{\mathcal{A}}_{\cap \mathcal{G}} ) < 1$, since by \eqref{dimLem} we then have $|\cap \pi(\mathcal{G})| = \dim(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}) \leq \dim(\bm{\mathcal{A}}_{\cap \mathcal{G}}) = |\cap \mathcal{G}|$, with equalities from the full column-ranks of $\mathbf{A}_{S}$ and $\mathbf{B}_{\pi(S)}$ for all $S \in \mathcal{H}$.\footnote{Note that if ever $\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})} \neq \bf 0$ while $\cap \mathcal{G} = \emptyset$, we would have $d(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}, \bm 0 ) = 1$.
-However, that leads to a contradiction.} Observe that $d(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}, \bm{\mathcal{A}}_{\cap \mathcal{G}}  )
-\leq d\left( \cap \bm{\mathcal{B}}_{\pi(\mathcal{G})}, \cap \bm{\mathcal{A}}_\mathcal{G} \right)$ by \eqref{UsubU}, since trivially $\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})} \subseteq \cap \bm{\mathcal{B}}_{\pi(\mathcal{G})}$ and also $\bm{\mathcal{A}}_{\cap \mathcal{G}} = \cap \bm{\mathcal{A}}_\mathcal{G}$ by Lem.~\ref{spanIntersectionLemma}.
-Recalling Def.~\ref{dDef} and applying Lem.~\ref{DistanceToIntersectionLemma} yields:
-\begin{align}
-d\left( \cap \bm{\mathcal{B}}_{\pi(\mathcal{G})}, \cap \bm{\mathcal{A}}_\mathcal{G} \right)
-&\leq \max_{\mathbf{u} \in \cap \bm{\mathcal{B}}_{\pi(\mathcal{G})}, \ \|\mathbf{u}\|_2 \leq 1} \sum_{S \in \mathcal{G}} \frac{ \text{\rm dist}\left( \mathbf{u},\bm{\mathcal{A}}_{S} \right) }{ 1 - \xi( \bm{\mathcal{A}}_\mathcal{G} ) } \nonumber \\
-&= \sum_{S \in \mathcal{G}} \frac{ d\left( \cap \bm{\mathcal{B}}_{\pi(\mathcal{G})},\bm{\mathcal{A}}_{S} \right) }{ 1 - \xi( \bm{\mathcal{A}}_\mathcal{G} ) }, \nonumber
-\end{align}
-passing the maximum through the sum.
-Since $\cap \bm{\mathcal{B}}_{\pi(\mathcal{G})} \subseteq \bm{\mathcal{B}}_{\pi(S)}$ for all $S \in \mathcal{G}$, by \eqref{UsubU} the numerator of each term in the sum above is bounded by \mbox{$d\left( \bm{\mathcal{B}}_{\pi(S)},\bm{\mathcal{A}}_{S} \right) = d\left(\bm{\mathcal{A}}_{S}, \bm{\mathcal{B}}_{\pi(S)} \right) \leq \varepsilon$}, with the equality from \eqref{eqdim} since $\dim(\bm{\mathcal{B}}_{\pi(S)}) = \dim(\bm{\mathcal{A}}_S)$.
-Thus, altogether:
-\begin{align}\label{last}
-d(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}, \bm{\mathcal{A}}_{\cap \mathcal{G}} )
-\leq \frac{|\mathcal{G}| \varepsilon}{1 - \xi( \bm{\mathcal{A}}_\mathcal{G} )}
-\leq \frac{C_2 \varepsilon}{\max_j\|\mathbf{A}_j\|_2},
-\end{align}
-recalling the definition of $C_2$ in \eqref{Cdef2}.
-Lastly, since $C_2 \varepsilon < L_2(\mathbf{A}) \leq \max_j\|\mathbf{A}_j\|_2$, we have $d(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}, \bm{\mathcal{A}}_{\cap \mathcal{G}} ) \leq 1$ and therefore \eqref{cond} holds.
-
-%Keeping in mind that $d(U',V) \leq d(U,V)$ whenever $U' \subseteq U$ and applying (in order) Lem.~\ref{spanIntersectionLemma}, Lem.~\ref{DistanceToIntersectionLemma}, \eqref{eqdim}, \eqref{GapUpperBound}, and \eqref{Cdef2} gives:
-%\begin{align}\label{randoml}
-%d(&\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}, \bm{\mathcal{A}}_{\cap \mathcal{G}}  ) 
-%\leq d\left( \cap \bm{\mathcal{B}}_{\pi(\mathcal{G})}, \cap \bm{\mathcal{A}}_\mathcal{G} \right)
-%\leq \sum_{T \in \mathcal{G}} \frac{ d\left( \cap \bm{\mathcal{B}}_{\pi(\mathcal{G})},\bm{\mathcal{A}}_{T} \right) }{ 1 - \xi( \bm{\mathcal{A}}_\mathcal{G} ) } \nonumber \\
-%&\leq \sum_{T \in \mathcal{G}} \frac{ d\left( \bm{\mathcal{B}}_{\pi(T)},\bm{\mathbf{A}}_{T} \right) }{ 1 - \xi( \bm{\mathcal{A}}_\mathcal{G} ) }
-%\leq \frac{|\mathcal{G}| \varepsilon}{1 - \xi( \bm{\mathcal{A}}_\mathcal{G} )} 
-%\leq \frac{C_2 \varepsilon}{\max_j\|\mathbf{A}_j\|_2},
-%\end{align}
-%
-%which is less than one, since $C_2 \varepsilon < L_2(\mathbf{A}) \leq \max_j\|\mathbf{A}_j\|_2$.
-
-Applying Lem.~\ref{NonEmptyLemma}, the association $i \mapsto \cap_{S \in \sigma(i)} \pi(S)$ is an injective map $\overline \pi: J \to [\overline m]$ for some $J \subseteq [m]$ of size $m - (r-1)(\overline m - m)$, and $\mathbf{B}_{\overline \pi(i)} \neq \mathbf{0}$ for all $i \in J$ since the columns of $\mathbf{B}_{\pi(S)}$ are linearly independent for all $S \in \mathcal{H}$.
-Letting $\overline \varepsilon := C_2 \varepsilon / \max_i \|\mathbf{A}_i\|_2$, it follows from \eqref{eqdim} and \eqref{last} that $d\left( \bm{\mathcal{A}}_i, \bm{\mathcal{B}}_{\overline \pi(i)} \right) = d\left(\bm{\mathcal{B}}_{\overline \pi(i)},  \bm{\mathcal{A}}_i \right)  \leq \overline \varepsilon$ for all $i \in J$.
-%Fixing $\overline \varepsilon = C_2\varepsilon$ and letting $c_i = \|\mathbf{A}_i\|_2^{-1}$, we thus have that for each $\mathbf{e}_i \in \mathbb{R}^m$ with $i \in J$ there exists some $\overline{c}_i \in \mathbb{R}$ such that $\|c_i\mathbf{A}\mathbf{e}_i - \overline{c}_i \mathbf{B}\mathbf{e}_{\overline \pi(i)}\|_2 \leq \overline \varepsilon < L_2(\mathbf{A}) \min_{i\in J} |c_i|$.
-But this is exactly the supposition in \eqref{1D}, and the result follows from the case $k=1$ in Sec.~\ref{DUT} applied to the submatrix $\mathbf{A}_J$.
-Setting $c_i := \|\mathbf{A}_i\|_2^{-1}$ so that $\|c_i\mathbf{Ae}_i\|_2 = 1$, by Def.~\ref{dDef} for all $i \in J$:
-\begin{align*}
-\min_{\overline c_i \in \mathbb{R}} \|c_i\mathbf{Ae}_i - \overline c_i \mathbf{Be}_{\overline \pi(i)} \|_2
-\leq d\left( \bm{\mathcal{A}}_i, \bm{\mathcal{B}}_{\overline \pi(i)} \right)
-\leq \overline \varepsilon,
-%&= \max_{\bm{u} \in \bm{\mathcal{A}}_i, \|\bm{u}\|_2 \leq 1} \text{dist}\left(\bm{u}, \bm{\mathcal{B}}_{\overline \pi(i)} \right) \\
-%&\geq  \text{dist}\left(c_i\bm{Ae}_i, \mathbf{Be}_{\overline \pi(i)} \right) \\
-%&= \min_{\overline c_i \in \mathbb{R}} \|c_i\bm{Ae}_i - \overline c_i \mathbf{Be}_{\overline \pi(i)} \|_2
-\end{align*}
-%
-for $\overline \varepsilon < L_2(\mathbf{A})\min_{i \in [m]}|c_i|$.
-But this is exactly the supposition in \eqref{1D}, with $J$ and $\overline \varepsilon$ in place of $[m]$ and $\varepsilon$, respectively.
-The same arguments of the case $k=1$ in Sec.~\ref{DUT} can then be made to show that for any $\overline m \times \overline m$ permutation and invertible diagonal matrices $\mathbf{P}$ and $\mathbf{D}$ with, respectively, columns $\mathbf{e}_{\pi(i)}$ and $\frac{\overline{c}_i}{c_i}\mathbf{e}_i$ for $i \in J$ (otherwise, $\mathbf{e}_{i}$ for $i \in [\overline{m}] \setminus J$), we have $\|\mathbf{A}_i - (\mathbf{B}\mathbf{PD})_i \|_2 \leq \overline  \varepsilon / |c_i|  \leq C_2 \varepsilon$ for all $i \in J$.
-\end{proof}
-
-%\section{Proofs of Thm.~\ref{robustPolythm} and Cor.~\ref{ProbabilisticCor}}
-
-%\clearpage
-
-%\section{$\ell_1$-norm Extension}
-%
-%\begin{problem}\label{OptimizationProblemL1}
-%Find a matrix $\mathbf{B}$ and vectors \mbox{$\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N \in \mathbb{R}^m$} that solve:
-%\begin{align}\label{minsum}
-%\min \sum_{i = 1}^N \|\mathbf{\overline x}_i\|_1 \ \ 
-%\text{subject to} \ \ \|\mathbf{z}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \eta, \ \text{for all $i$}.
-%\end{align}
-%\end{problem}
-
-%\begin{corollary}\label{SLCopt}
-%Fix $\alpha > 0$ and suppose all of the assumptions of Thm.\ref{DeterministicUniquenessTheorem} hold with the following modifications:
-%\begin{enumerate}
-%\item The coefficients of all $k$-sparse $\mathbf{x}_i$ are drawn from $[-\beta, \beta]$, where $\beta < \frac{\alpha(k+1)}{k}$.
-%\item More than $(k-1){\overline m \choose k} + q$ vectors $\mathbf{x}_i$ are supported in each $S \in \mathcal{H}$, where
-%\[ q = \left[\frac{\alpha}{\beta}(k+1) - k\right]^{-1}k|\mathcal{H}|(k-1){\overline m \choose k-1}. \]
-%\end{enumerate}
-%Then all solutions to Prob.~\ref{OptimizationProblemL1} for which the nonzero elements of all $\mathbf{\overline x}_i$ lie outside $[-\alpha, \alpha]$ necessarily satisfy the implications \eqref{Cstable} and \eqref{b-PDa} of Thm.~\ref{DeterministicUniquenessTheorem}.
-%\end{corollary}
-
-%\begin{proof}[Proof of Cor.~\ref{SLCopt}]
-%We bound the number of $k$-sparse $\mathbf{\overline x}_i$ and then apply Thm.~\ref{DeterministicUniquenessCorollary}.
-First, observe that no more than $(k-1)|\mathcal{H}|$ of the $\mathbf{\overline x}_i$ share a support $\overline S$ of size less than $k$; otherwise, by the pigeonhole principle, at least $k$ of these indices $i$ belong to the same $K \subseteq I(S)$ for some $S \in \mathcal{H}$ and (as argued previously) \eqref{rhs222} follows.
-Since the right-hand side of \eqref{rhs222} is less than one, by \eqref{dimLem} we have the contradiction $k = \dim(\bm{\mathcal{A}}_S) \leq \dim(\bm{\mathcal{B}}_{\overline S}) \leq |\overline S|.$ The total number of $(k-1)$-sparse vectors $\mathbf{\overline x}_i$ can thus not exceed $|\mathcal{H}|(k-1){ \overline m \choose k-1}$.
-
-%Next, observe that the assumptions of the lemma imply:
-%\begin{align*}
-%\alpha \sum_i \|\mathbf{\overline x}_i\|_0 \leq \sum_i \|\mathbf{\overline x}_i\|_1 \leq \sum_i \|\mathbf{x}_i\|_1 \leq \beta \sum_i \|\mathbf{x}_i\|_0.
-%\end{align*}
-
-%We now apply these facts to bound the number of $k$-sparse $\mathbf{\overline x}_i$.
-Let $n_p$ be the number of $\mathbf{\overline x}_i$ with $\|\mathbf{\overline x}_i\|_0 = p$.
-Since the $\mathbf{x}_i$ are all $k$-sparse, we have:
-%\begin{align*}
-%k \sum_{p = 0}^{\overline m} n_p = k N \geq \sum_{i=0}^N \|\mathbf{x}_i\|_0 \geq \frac{\alpha}{\beta} \sum_{i=0}^N \|\mathbf{\overline x}_i\|_0 = \frac{\alpha}{\beta} \sum_{p=0}^{\overline m} p n_p.
-%\end{align*}
-%Hence, 
-%\begin{align*}
-%\left[ \frac{\alpha(k+1)}{\beta} - k\right] \sum_{p = k+1}^{\overline m} n_p 
-%&\leq \sum_{p = k+1}^{\overline m} (\frac{\alpha}{\beta} p-k) n_p
-%\leq \sum_{p = 0}^k (k - \frac{\alpha}{\beta} p)n_p \\
-%&\leq k \sum_{p = 0}^k n_p 
-%\leq k(1-\frac{\alpha}{\beta})n_k + k|\mathcal{H}|(k-1){ \overline m \choose k-1}
-%\end{align*}
-
-%[Shit, we need $\alpha = \beta$.] Therefore, no more than $q$ vectors $\mathbf{\overline x}_i$ are \emph{not} $k$-sparse.
-Since for every $S \in \mathcal{H}$ there are over $(k-1){\overline m \choose k} + q$ vectors $\mathbf{x}_i$ supported there, it follows that more than $(k-1){\overline m \choose k}$ of them have corresponding $\mathbf{\overline x}_i$ that are $k$-sparse.
-The result now follows directly from Thm.~\ref{DeterministicUniquenessCorollary}.
-%\end{proof}
-
-%\pagebreak
-
-%\begin{corollary}\label{SLCoptL1}
-%If all of the assumptions of Thm.\ref{DeterministicUniquenessTheorem} hold, only now with more than $(k-1)\left[ {\overline m \choose k} + |\mathcal{H}|k{\overline m \choose k-1}\right]$ vectors $\mathbf{x}_i$ supported in each $S \in \mathcal{H}$, then every solution to Prob.~\ref{OptimizationProblemL1} for which the average absolute nonzero coefficient of the $\mathbf{\overline x}_i$ is bounded below by that of the $\mathbf{x}_i$ necessarily satisfies the implications \eqref{Cstable} and \eqref{b-PDa} of Thm.~\ref{DeterministicUniquenessTheorem}.
-%\end{corollary}
-
-%\begin{proof}[Proof of Cor.~\ref{SLCoptL1}]
-%Since the average absolute nonzero coefficient of the $\mathbf{x}_i$ is given by $\alpha = \sum_i \|\mathbf{x}_i\|_1 / \sum_i \|\mathbf{x}_i\|_0$, we have:
-%\begin{align*}
-%\alpha \sum_i \|\mathbf{\overline x}_i\|_0 \leq \sum_i \|\mathbf{\overline x}_i\|_1 \leq \sum_i \|\mathbf{x}_i\|_1 = \alpha \sum_i \|\mathbf{x}_i\|_0.
-%\end{align*}
-%
-%and the result follows by the same arguments as in the proof of Cor.~\ref{SLCopt}.
-%\end{proof}
-
-\end{document}

### 2020-07-16 manuscripts/thesis/thesis.tex
thesis

%% thesis.tex 2014/04/11
%
% Based on sample files of unknown authorship.
%
% The Current Maintainer of this work is Paul Vojta.
%
% To compile this file, run "latex thesis", then "biber thesis"
% (or "bibtex thesis", if the output from latex asks for that instead),
% and then "latex thesis" (without the quotes in each case).

\documentclass{ucbthesis}

% *** CITATION STUFF ***
%\usepackage{biblatex} 
%\bibliography{references} 
% the above doesn't work, using this instead:
\usepackage[backend=bibtex,style=numeric]{biblatex}
\addbibresource{references}

% *** MATH STUFF ***
\usepackage{amsmath, amssymb, amsthm} 
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{conjecture}{Conjecture}
\newtheorem{problem}{Problem}
\newtheorem{question}{Question}
\newtheorem{proposition}{Proposition}
\newtheorem{definition}{Definition}
\newtheorem{corollary}{Corollary}
\newtheorem{remark}{Remark}
\newtheorem{example}{Example}

% *** ALIGNMENT STUFF***
\usepackage{array}
\usepackage{bm}
\usepackage{rotating} % provides sidewaystable and sidewaysfigure

% Double spacing, if you want it.  Do not use for the final copy.
% \def\dsp{\def\baselinestretch{2.0}\large\normalsize}
% \dsp

% If the Grad. Division insists that the first paragraph of a section
% be indented (like the others), then include this line:
% \usepackage{indentfirst}

\addtolength{\abovecaptionskip}{\baselineskip}

%\hyphenation{mar-gin-al-ia}
%\hyphenation{bra-va-do}

\begin{document}

% Declarations for Front Matter

\title{On the uniqueness and stability of dictionaries for sparse representation of noisy signals}
\author{Charles Garfinkle}
\degreesemester{Summer}
\degreeyear{2020}
\degree{Doctor of Philosophy}
\chair{Friedrich Sommer}
\othermembers{Bruno Olshausen \\
  Mike Deweese \\
  Bin Yu}
% For a co-chair who is subordinate to the \chair listed above
% \cochair{Professor Benedict Francis Pope}
% For two co-chairs of equal standing (do not use \chair with this one)
% \cochairs{Professor Richard Francis Sony}{Professor Benedict Francis Pope}
\numberofmembers{4}
% Previous degrees are no longer to be listed on the title page.
% \prevdegrees{B.A. (University of Northern South Dakota at Hoople) 1978 \\
%   M.S. (Ed's School of Quantum Mechanics and Muffler Repair) 1989}
\field{Neuroscience}
% Designated Emphasis -- this is optional, and rare
% \emphasis{Colloidal Telemetry}
% This is optional, and rare
% \jointinstitution{University of Western Maryland}
% This is optional (default is Berkeley)
% \campus{Berkeley}

% For a masters thesis, replace the above \documentclass line with
% \documentclass[masters]{ucbthesis}
% This affects the title and approval pages, which by default calls this
% document a "dissertation", not a "thesis".

\maketitle
% Delete (or comment out) the \approvalpage line for the final version.
\approvalpage
\copyrightpage

\include{abstract}

\begin{frontmatter}

\begin{dedication}
\null\vfil
%\begin{center}
Dedication
%I want to dedicate this to my dad. At the same time, I don't want to, because the results on display here can't be matched to the time with him I traded to produce them, and it feels as though dedicating this work to him would be measuring his life up against the theorems contained here-in. I knew very well this work wasn't so important; these theorems, while fundamental, are just something people might cite to feel better about whatever sketchy sparse coding analysis they were already going to do, anyway. And yet, despite total freedom offered by the Helen Wills Neuroscience Institute, I worried the brain was so dauntingly complex that I should feel lucky to have at last been offered a well-defined relevant problem to work on, particularly one I felt even remotely equipped to solve myself, so as to feel deserving of a Ph.D. from UC Berkeley. The fact is that whatever the eventual effect of this work on the scientific ecosystem, these truths could have waited, arrived at their own pace, via myself or another, and I could have been more present with my dad as he waited for death. I couldn't really fathom what it actually meant for him to die, to never see or talk to or hug him again, while the idea of putting original work out there, of crafting my own piece of the overwhelming puzzle that is neuroscience, was tantalizing. Let's say, then, that this dedication is the first bit of a life's work, real work void of any prestigious position or degree and the associated self-doubt and pressure, put toward passionate id	eas, solving problems I care about and that actually matter, loving and caring for others or, as my dad would say, ``being a mensch". May this dedication serve to hold myself publicly accountable to that. Also I love you, mom. I dedicate and don't dedicate this and everything to come to you, too.
\vspace{12pt}
%\end{center}
\vfil\null
\end{dedication}

% You can delete the \clearpage lines if you don't want these to start on
% separate pages.

\tableofcontents
\clearpage
\listoffigures
\clearpage
%\listoftables

\begin{acknowledgements}
I would like to thank Chris Hillar for laying down the groundwork and vetting all my proofs. He gave me a lot of his time for little if anything in return. Fritz Sommer for taking on the role of my advisor. The Berkeley Student Cooperative for a really awesome and transformative time. CZ or Die. 
We thank Darren Rhea for early thoughts, and Ian Morris for posting \eqref{eqdim} online.

\end{acknowledgements}

\end{frontmatter}

\pagestyle{headings}

% (Optional)
 \part{Main Text}

\include{introduction}
\include{results}
\include{proofs}
\include{discussion}
\include{conclusions}

\include{appendix} 
%\include{conclusions}

\printbibliography

\end{document}

### 2020-07-16 manuscripts/thesis/code/constants.py

@@ -1,0 +1,156 @@
+#from decomp_svd import subspace_angles
+from scipy.linalg.decomp_svd import subspace_angles
+import numpy as np
+import itertools
+import operator as op
+from scipy.special import comb as choose
+
+def friedrichs(U,V):
+    """
+    Calculates the Friedrichs angle between subspaces U and V (in radians).
+
+    The Friedrichs angle is the smallest nonzero principle angle.
+
+    Alternatively, it is the (s+1)th principal angle when dim(U \cap V) = s.
+    """
+    angles = subspace_angles(U,V)
+    nz_angles = angles > 0  # np.finfo(float).eps
+    if np.any(nz_angles):
+        min_nz_angle = np.sort(angles[nz_angles])[0]
+        return min_nz_angle
+    else:
+        return 0.
+
+def xi(A, G):
+    """
+    Calculates xi({A_S}_{S \in G})
+
+    (Assumes A is injective on H, so the intersection of the span is the span of the intersection.)
+    """
+    if len(G) == 1:
+        return 1 # by definition
+    Gs = itertools.permutations(G)
+    prods = []
+    for Gseq in Gs: # loop through all orderings of elements in G
+        prod = 1.
+        for i, Si in enumerate(Gseq[:-1]):
+            cap_Sj = list(set.intersection(*map(set, Gseq[i+1:])))
+            if cap_Sj: # otherwise they intersect only at 0 and sin(theta) = 1, since every subspace forms pi/2 angle with 0 (weird)
+                theta = friedrichs(A[:,Si], A[:,cap_Sj])
+                prod *=  np.sin(theta)**2
+        prods.append(prod)
+    return 1 - np.sqrt(1 - np.max(prods))
+
+def C2(A, H, r):
+    """
+    Ouputs the constant C2
+
+    A: n x m dictionary matrix (2d numpy array)
+    H: hypergraph (list of lists in range(m))
+    r: regularity of H
+
+    Loops over subsets of H of size r+1
+    """
+    xi_Gs = [] # xi is in (0,1]
+    for G in itertools.combinations(H, r + 1): # loop over subsets of H of size r
+        xi_Gs.append( xi(A, G) )
+    max_A = np.max( np.linalg.norm(A, axis=0) )
+    return len(H) * max_A / min(xi_Gs)
+
+def L_k(M, k, n_samples = None):
+    vals = []
+    if n_samples is None:
[…]

### 2020-07-16 manuscripts/thesis/code/decomp_svd.py

@@ -1,0 +1,404 @@
+"""SVD decomposition functions."""
+from __future__ import division, print_function, absolute_import
+
+import numpy
+from numpy import zeros, r_, diag, dot, arccos, arcsin, where, clip
+
+# Local imports.
+from .misc import LinAlgError, _datacopied
+from .lapack import get_lapack_funcs, _compute_lwork
+from .decomp import _asarray_validated
+from scipy._lib.six import string_types
+
+__all__ = ['svd', 'svdvals', 'diagsvd', 'orth', 'subspace_angles', 'null_space']
+
+
+def svd(a, full_matrices=True, compute_uv=True, overwrite_a=False,
+        check_finite=True, lapack_driver='gesdd'):
+    """
+    Singular Value Decomposition.
+    Factorizes the matrix `a` into two unitary matrices ``U`` and ``Vh``, and
+    a 1-D array ``s`` of singular values (real, non-negative) such that
+    ``a == U @ S @ Vh``, where ``S`` is a suitably shaped matrix of zeros with
+    main diagonal ``s``.
+    Parameters
+    ----------
+    a : (M, N) array_like
+        Matrix to decompose.
+    full_matrices : bool, optional
+        If True (default), `U` and `Vh` are of shape ``(M, M)``, ``(N, N)``.
+        If False, the shapes are ``(M, K)`` and ``(K, N)``, where
+        ``K = min(M, N)``.
+    compute_uv : bool, optional
+        Whether to compute also ``U`` and ``Vh`` in addition to ``s``.
+        Default is True.
+    overwrite_a : bool, optional
+        Whether to overwrite `a`; may improve performance.
+        Default is False.
+    check_finite : bool, optional
+        Whether to check that the input matrix contains only finite numbers.
+        Disabling may give a performance gain, but may result in problems
+        (crashes, non-termination) if the inputs do contain infinities or NaNs.
+    lapack_driver : {'gesdd', 'gesvd'}, optional
+        Whether to use the more efficient divide-and-conquer approach
+        (``'gesdd'``) or general rectangular approach (``'gesvd'``)
+        to compute the SVD. MATLAB and Octave use the ``'gesvd'`` approach.
+        Default is ``'gesdd'``.
+        .. versionadded:: 0.18
+    Returns
+    -------
+    U : ndarray
+        Unitary matrix having left singular vectors as columns.
[…]

### 2020-07-16 manuscripts/thesis/code/sample_complexity.py

@@ -1,0 +1,120 @@
+"""
+Compute the probability that for every S in H, there are at least k vectors x_i supported there which share a support in B
+"""
+# TODO: Try alternative formula for bounded pigeonhole
+
+import numpy as np
+from scipy.special import comb
+
+COMB_EXACT = True
+
+def pigeonhole_bounded_large_N(N, n, r):
+    """
+    Supposed to be better for large N
+
+    Source URL:
+    https://math.stackexchange.com/questions/553960/extended-stars-and-bars-problemwhere-the-upper-limit-of-the-variable-is-bounded
+    """
+    val = 0
+    lo = int(np.ceil( (N+n) / (r+1) ))
+    hi = int(n)
+    for q in range(lo, hi+1):
+        sgn = (-1)**(n-q)
+        term_1 = comb(n, q, exact=COMB_EXACT)
+        term_2 = comb(q*(r+1) - 1 - N, n - 1, exact=COMB_EXACT)
+        val += sgn * term_1 * term_2
+    return val
+
+def pigeonhole_bounded(N, n, r):
+    """
+    Returns the number of ways to allocate N indistinguishable balls to n distinct bins with at most r balls per bin
+
+    Source URL:
+    https://math.stackexchange.com/questions/553960/extended-stars-and-bars-problemwhere-the-upper-limit-of-the-variable-is-bounded
+    """
+    val = 0
+    lim = int(min(n, 1.*N / (r+1)))
+    for q in range(lim+1):
+        sgn = (-1)**q
+        term_1 = comb(n, q, exact=COMB_EXACT)
+        term_2 = comb(N - q*(r + 1) + n - 1, n - 1, exact=COMB_EXACT)
+        val += sgn * term_1 * term_2
+    return val
+
+def pigeonhole(N, n):
+    """
+    Returns the number of ways to allocate N indistinguishable balls to n distinct bins.
+    """
+    return comb(N + n - 1, n - 1, exact=COMB_EXACT)
+
+def prob_atleast_k_balls_in_some_bin(num_balls, num_bins, k):
+    """
+    Returns the probability that some bin contains at least k balls
+    """
+    num_ways_all_less_than_k = pigeonhole_bounded(num_balls, num_bins, k-1) # number of ways to allocate balls so that every bin has fewer than k balls
+    #bnded = pigeonhole_bounded_large_N( num_balls, num_bins, k-1) # number of ways to allocate balls so that bin contains k or more balls
+    num_ways = pigeonhole(num_balls, num_bins) # number of ways to allocate balls
[…]

### 2020-07-17 manuscripts/thesis/discussion.tex
update

@@
 There are many challenges left open by this work.
-All conditions stated here guaranteeing the uniqueness and stability of sparse representations have only been shown sufficient; it remains open, therefore, to extend them to necessary conditions, be they on required sample size, the structure of support set hypergraphs, or tolerable error bounds.
-On this last note, we remark that the deterministic conditions derived here must consider always the ``worst-case" noise, whereas the ``effective" noise sampled from a concentrated distribution might be significantly reduced, especially for high-dimensional data.
-It would be of great practical benefit to see how drastically all conditions can be relaxed by requiring only probabilistic guarantees in this way, or in the spirit of our discussion on probabilistic pigeonholing to reduce sample complexity (as in the famous ``birthday paradox") following the proof of Thm.~\ref{DeterministicUniquenessTheorem}.
+All conditions stated here guaranteeing the uniqueness and stability of sparse representations have only been shown sufficient; it remains open, therefore, to extend them to necessary conditions, be they on the required number of samples, the structure of the support set hypergraph, or tolerable signal-to-noise ratio for a given recovery error.
+On this last note, the reader should be aware that the deterministic conditions derived here accomodate always the ``worst-case" noise, whereas the ``effective" noise sampled from a concentrated distribution might be significantly reduced, especially for high-dimensional data.
+It would be of great practical benefit to see how drastically all conditions can be relaxed by requiring less-than-certain guarantees in this way and others, such as by probabilistic pigeonholing for reducing sample complexity as discussed following the proof of Thm.~\ref{DeterministicUniquenessTheorem}.
 
@@
 
-We hope these remaining challenges pique the interest of the community to pick up where we have left off and that the theoretical tools showcased here may be of use to this end.
+It is my hope that these remaining challenges pique the interest of the community in applying the theoretical tools showcased here to derive practical guidelines for researchers to bolster their analyses.
+I briefly outline some of these directions below.
 
-%We close with some challenges left open by our work.
-First, there is the basic problem of proving optimal lower bounds on sufficient sample size $N$ guaranteeing the uniqueness and stability of sparse representations.
-The pigeonholing argument in the proof of Thm.~\ref{DeterministicUniquenessTheorem} is loose in that it assigns to each support $S \in \mathcal{H}$ a corresponding support $\overline S$ without consideration of previously matched pairs; although we doubt tightening in this way will lead to sub-exponential sample sizes.
-Sample complexity will also benefit from lowering the number of required supports, i.e.
-the size of regular uniform hypergraphs satisfying the SIP.
-The regularity requirement on support hypergraphs can be loosened to allow for certain non-regular hypergraphs satisfying constraints on the degree sequence of nodes; though we impose regularity for clarity of exposition.
-It is then natural to ask: what is the smallest hypergraph satisfying the required constraints forgiven $m$ and $k$?
-Finally, the error bounds can be improved by tightening the constant $C_1$, e.g.
-via an improvement in Lemma ?.
+% THIS SECTION ADDRESSES REVIEWER COMPLAINTS:
 
-%Solving Prob.~\ref{SLCopt} directly is intractable in general since it necessitates, for each proposed dictionary $\mathbf{B}$, a combinatorial search for the supports of the associated sparse codes $\mathbf{\overline x}_i$.
-A common work-around is to convexify the problem (for fixed $\mathbf{B}$) by substituting the norm $\|\cdot\|_0$ with $\|\cdot\|_1$, impelled the fact that matrices $\mathbf{A}$ with large enough $L_{2k}(\mathbf{A})$ induce the same sparse codes via minimization of either norm \cite{?}.
-To this end, the lower bound $L_{2k}(\mathbf{BP}) \geq (L_{2k}(\mathbf{A}) - C_1\varepsilon) / \|\mathbf{D}\|_1$ implied by Thm.~\ref{DeterministicUniquenessTheorem} hints at conditions on the generating dictionary $\mathbf{A}$ and $k$-sparse codes $\mathbf{x}_i$ under which \emph{all} matrices $\mathbf{B}$ (of bounded column-norm) that solve Prob.~\ref{OptimizationProblem} also share this property of $\mathbf{A}$ by virtue of uniqueness and stability.
-One might then imagine an inference procedure whereby sparse codes are inferred via minimization of $\|\cdot\|_1$, but solutions still evaluated by their collective support size, yielding unique optimal solutions to Prob.~\ref{SLCopt} if only constraints could be imposed such that the learning procedure eventually guides $\mathbf{B}$ through an optimal dictionary.
-% (e.g.
-the dictionary is a member of a known finite set).
+\subsection{Tolerable Error Bounds}
 
-%\section{EXTRA}
-%An additional consequence of Thm.~\ref{DeterministicUniquenessTheorem} of potential practical relevance to is the implied lower bound $L_{2k}(\mathbf{BPD}) \geq L_{2k}(\mathbf{A}) - C_1\varepsilon$ in the case where $\mathbf{A}$ satisfies \eqref{SparkCondition}.
+A concern raised in peer review of this work was the size of the constant $C_1$, which sets the tolerable signal-to-noise ratio for dictionary and code recovery up to an acceptable error.
+Referring to the definition of $C_1$ in \eqref{Cdef1}, the reader should note that $L_k$ is a standard quantity in the field of compressed sensing (the ``restricted isometry constant", see footnote \ref{ripfootnote}) and it is known to be reasonable for many random distributions generating dictionaries $\mathbf{A}$ and sparse codes $\mathbf{x}_i$ [CITATION].
+The constant $C_2$, on the other hand, incorporates the more obscure quantity $\xi$ defined in \eqref{FriedrichsDefinition}, which is computed from the ``Friedrichs angle" between certain spans of subsets of the columns of $\mathbf{A}$.
+Simulations for small (pseudo-)randomly generated dictionaries $\mathbf{A}$ suggest nonetheless that the constant $C_2$ is likely reasonable in general as well, at least for the case where $m=k^2$ and $\mathcal{H}$ is taken to be the set of rows and columns formed by arranging the elements of $[m]$ in a square grid (see Fig.
+\ref{reasonableC2}).
+
+Finally, the error bounds can be improved by tightening the constant $C_1$, e.g. via an improvement in Lemma ?.
+
+\subsection{Sample Complexity and Support Set Hypergraphs}
+
+Deterministic sample complexity can be reduced by tightening the pigeonholing argument in the proof of Thm.~\ref{DeterministicUniquenessTheorem}.
+The argument iterates over supports $S \in \mathcal{H}$, in each case determining a corresponding support $\overline S \in {\bar m \choose k}$ without consideration of previously matched support pairs, whereas the assumption $L_\mathcal{H}(\mathbf{A}) > 0$ implies that no two supports in $\mathcal{H}$ can correspond to the same $\overline S$.
+The number of bins to pigeonhole into therefore decreases by one at each iteration.
+
+There is also the number of sparse supports to consider for fixed $m$ and $k$, i.e.
+the size of the SIP-satisfying, regular, $k$-uniform hypergraph $\mathcal{H}$ over $[m]$.
+These requirements can be loosened, too; in particular, though imposing regularity allows for better clarity of exposition, a close examination of Lemma (?) reveals that non-regular hypergraphs suffice so long as they satisfy a constraint on the sequence of node degrees to maintain compatibility with the iterative argument.
+It is natural to ask, then, what are the necessary constraints on the support set hypergraph, and what is the smallest hypergraph that satisfies these constraints for given $m$ and $k$?
+
+As discussed following the proof of Thm.~\ref{DeterministicUniquenessTheorem}, probabilistic guarantees can be ....
+
+The problem reduces to counting integer solutions to the problem $\sum_i n_i = N$ subject to $n_i < k$ for all $i$.
+It appears there is no closed formula for this problem, but the number of solutions can be computed in a number of operations independent of $N$.
+The number is the coefficient of $X_N$ in the polynomial $(1 + X + \ldots + X^k)^n$.
+Written as a rational function of $X$,
+
+%see:
+%https://math.stackexchange.com/questions/553960/extended-stars-and-bars-problemwhere-the-upper-limit-of-the-variable-is-bounded
+
+\subsection{Guarantees for Convex Optimization}
+
+An additional consequence of Thm.~\ref{DeterministicUniquenessTheorem} of potential practical relevance to is the implied lower bound $L_{2k}(\mathbf{B}) \geq \left(L_{2k}(\mathbf{A}) - C_1\varepsilon \right) / \|\mathbf{D}\|_1$ in the case where $\mathbf{A}$ satisfies \eqref{SparkCondition}.
 Since solving Prob.~\ref{SLCopt} directly requires a combinatorial search over sparse supports for the $\mathbf{\overline x}_i$ for each proposed dictionary $\mathbf{B}$, rendering it intractable in general, a common strategy is to replace the $\ell_0$-norm in \eqref{minsum} with the $\ell_1$-norm, thereby transforming the inference of sparse $\mathbf{\overline x}_i$ for a fixed dictionary $\mathbf{B}$ into a convex optimization solvable by a linear program.
 A major advance in compressive sensing was the discovery that, for fixed $\mathbf{B}$, solutions to \eqref{minsum} using either norm yield the same sparse vectors $\mathbf{\overline x}_i$ (up to noise) provided $L_{2k}(\mathbf{B})$ is large enough \cite{?}.
-What our results hint at are conditions on the generating dictionary $\mathbf{A}$ and $k$-sparse codes $\mathbf{x}_i$ under which \emph{all} matrices $\mathbf{B}$ (of bounded column-norm) that solve Prob.~\ref{OptimizationProblem} also share this property by virtue of uniqueness and stability; that is, conditions which guarantee that the sparse codes $\mathbf{\overline x}_i$ solving Prob.~\ref{OptimizationProblem} also solve the convexified problem when the corresponding dictionary $\mathbf{B}$ is held fixed.
-It remains to determine, however, what practical conditions preclude matrices that don't solve Prob.~\ref{OptimizationProblem} from nonetheless solving the convexified problem.
+What the current work provides are conditions on the generating dictionary $\mathbf{A}$ and $k$-sparse codes $\mathbf{x}_i$ under which \emph{all} matrices $\mathbf{B}$ (of bounded column-norm) that solve Prob.~\ref{OptimizationProblem} also share this property by virtue of uniqueness and stability; that is, conditions which guarantee that the sparse codes $\mathbf{\overline x}_i$ solving Prob.~\ref{OptimizationProblem} also solve the convexified problem when the corresponding dictionary $\mathbf{B}$ is held fixed.
+It remains to determine practical conditions that reject matrices not solving Prob.~\ref{OptimizationProblem} from nonetheless solving the convexified problem.
 %
-%Regardless, an implication of the above observation is that the following algorithm solves Prob.~\ref{OptimizationProblem} without appeal to combinatorial search:
-%\begin{enumerate}
-%\item List all matrices $\mathbf{B}$.
-%\item For each matrix $\mathbf{B}$, solve $\mathbf{\overline x}_i = \arg \min \|\mathbf{v}\|_1$ s.t. $\|\mathbf{Bv} - \mathbf{z}_i\| \leq \eta$ for $i = 1, \ldots, N$.
-%\item Quantify the proposed solution $\mathbf{B}$ and $\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N$ as $\rho(\mathbf{B}, \mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N) = \sum_{i=1}^{N} \|\mathbf{\overline x}_i\|_0$.
-%\item Output $\arg \min_{\mathbf{B}, \mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N} \left( \rho \right)$.
-% \end{enumerate}
+
+Regardless, an implication of the above observation is that the following algorithm solves Prob.~\ref{OptimizationProblem} without appeal to combinatorial search through supports:
+\begin{enumerate}
+\item List all matrices $\mathbf{B}$.
+\item For each matrix $\mathbf{B}$, solve $\mathbf{\overline x}_i = \arg \min \|\mathbf{v}\|_1$ s.t. $\|\mathbf{Bv} - \mathbf{z}_i\| \leq \eta$ for $i = 1, \ldots, N$.
+\item Quantify the proposed solution of the previous step as $\rho(\mathbf{B}, \mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N) = \sum_{i=1}^{N} \|\mathbf{\overline x}_i\|_0$.
+\item Output $\arg \min_{\mathbf{B}, \mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N} \left( \rho \right)$.
+ \end{enumerate}
+%
 
@@
 
-%The problem is to count integer solution to the problem $\sum_i a_i = N$ subject to $a_i < i$ for all $i$.
-There is as far as [internet person] knows no closed formula for this general problem, but there is a formula that allows the number of solutions to be computed in a number of operations independent of ??.
-Consider first the case that all limits are equal ??1=??2=?=????=??.
-Then the number is the coefficient of ????
-in the polynomial (1+??+?+????)??.
-By writing this as a rational function of ??...
-%see:
-%https://math.stackexchange.com/questions/553960/extended-stars-and-bars-problemwhere-the-upper-limit-of-the-variable-is-bounded
-
 \begin{figure}\label{probpigeon}
@@
 \caption{Probability of successful dictionary and code recovery (as per Thm.
-\ref{DeterministicUniquenessTheorem}) for a number of samples $N$ given as a fraction of the deterministic sample complexity $N = |\mathcal{H}|[(k-1){m \choose k} + 1]$ when $\mathcal{H}$ is taken to be the set of $m$ consecutive intervals of length $k$ in a cyclic order on $[m]$ (i.e.
-$|\mathcal{H}|=m$).
-Successful recovery is nearly certain far below the deterministic sample complexity.}
+\ref{DeterministicUniquenessTheorem}) for a number of samples $N$ given as a fraction of the deterministic sample complexity $N = |\mathcal{H}|[(k-1){m \choose k} + 1]$ when the support set hypergraph $\mathcal{H}$ is the set of $m$ consecutive intervals of length $k$ in a cyclic order on $[m]$.
+Each plot has $k$ ranging from $2$ to $m-1$ (the case $k=1$ requires $N=m$), with lighter grey lines corresponding to larger $k$.
+Successful recovery is nearly certain with far fewer samples than the deterministic sample complexity.
+}
 \vspace{-.6 cm}
@@
 \includegraphics[width=1 \linewidth]{figures/C2_m36_nt1000.pdf}
-\caption{The constant $C_2(\mathbf{A}, \mathcal{H})$ computed for generic unit-norm matrices $\mathbf{A} \in \mathbb{R}^{n \times m}$ and the hypergraph $\mathcal{H}$ consisting of the rows and columns formed by arranging  the elements of $[m]$ into a square grid.
-The results suggest that the bound is typically concentrated around a reasonable value.}
+\caption{Constant $C_2(\mathbf{A}, \mathcal{H})$ computed for generic unit-norm overcomplete dictionaries $\mathbf{A} \in \mathbb{R}^{n \times m}$ (with $m = 2n$) when the support set hypergraph $\mathcal{H}$ consists of the rows and columns formed by arranging  the elements of $[m]$ into a square grid (i.e.
+$m = k^2$.
+The form of the distribution suggests a reasonable value should generally be expected.}
 \vspace{-.6 cm}

### 2020-07-17 manuscripts/thesis/proofs.tex
update

@@
 
-We note also that these constants likely have reasonable values in general.
-The quantity $L_k$ is a relatively standard quantity in the field of compressed sensing (the ``restricted isometry constant") and it is known to be reasonable for many random distributions generating dictionaries $\mathbf{A}$ and sparse codes $\mathbf{x}_i$.
-The more obscure quantity $\xi$, on the other hand, is computed from the ``Friedrichs angle" between certain spans of subsets of the columns of $\mathbf{A}$.
-Simulations for small random matrices $\mathbf{A}$ and hypergraphs $\mathcal{H}$ satisfying the SIP suggest nonetheless that the constant $C_2$ is reasonable as well (Fig.
-\ref{reasonableC2}).
-
 \begin{proof}[Proof of Thm.~\ref{DeterministicUniquenessCorollary} for $k < m$] 
@@
 Given insufficient samples, this argument has some less-than-certain probability of being valid for each $S \in \mathcal{H}$.
-Nonetheless, simulations with small hypergraphs demonstrate that successful recovery is nearly certainly even when $N$ is only a fraction of the deterministic sample complexity (Fig.
+Nonetheless, simulations with small hypergraphs demonstrate that successful recovery is nearly certainly even when $N$ is only a fraction of the deterministic sample complexity (see Fig.
 \ref{probpigeon}).

### 2020-07-17 manuscripts/thesis/results.tex
update

@@
 %
-writing also $L_{k}$ in place of $L_\mathcal{H}$ when $\mathcal{H} = {[m] \choose k}$.\footnote{In compressed sensing literature, \mbox{$1 - \sqrt{k} L_k(\mathbf{M})$}  is the asymmetric lower restricted isometry constant for $\mathbf{M}$ with unit $\ell_2$-norm columns \cite{Blanchard2011}.}  As explained above, compactness implies that $L_{2k}(\mathbf{M}) > 0$ for all $\mathbf{M}$ satisfying \eqref{SparkCondition}.
+writing also $L_{k}$ in place of $L_\mathcal{H}$ when $\mathcal{H} = {[m] \choose k}$.\footnote{In compressed sensing literature, \mbox{$1 - \sqrt{k} L_k(\mathbf{M})$}  is the asymmetric lower restricted isometry constant for $\mathbf{M}$ with unit $\ell_2$-norm columns \cite{Blanchard2011}.\label{ripfootnote}}  As explained above, compactness implies that $L_{2k}(\mathbf{M}) > 0$ for all $\mathbf{M}$ satisfying \eqref{SparkCondition}.
 Clearly, $L_{\mathcal{H}'}(\mathbf{M}) \geq L_\mathcal{H}(\mathbf{M})$ whenever $\mathcal{H}' \subseteq \mathcal{H}$, and similarly any $k$-uniform $\mathcal{H}$ satisfying $\cup \mathcal{H} = [m]$ has $L_2 \geq L_{2\mathcal{H}} \geq L_{2k}$ (letting $L_{2k}$ := $L_m$ whenever $2k > m$).

### 2020-07-17 manuscripts/thesis/code/constants.py

@@ -124,12 +124,16 @@ if __name__ == '__main__':
     """
     """ rows and cols of square grid """
 
-    ks = range(2,7)
-    fig, ax = pp.subplots(len(ks), 1, figsize=(20,10))
+    ks = range(4,9)
+    fig, ax = pp.subplots(len(ks), 1, figsize=(20,10), sharex=True)
+    fig.add_subplot(111, frameon=False)
+    pp.tick_params(labelcolor='none', top=False, bottom=False, left=False, right=False)
+    pp.ylabel("Histogram of $C_2(\mathbf{A}, \mathcal{H})$")
     for i, k in enumerate(ks):
+        print("k=%d" % k)
         # SQUARE
         m = k**2
-        n = m
+        n = (3*m)//4
         H = square_hypergraph(m, k)
         r = 2 # since SIP satisfied by (row,col) pair
 
@@ -149,8 +153,9 @@ if __name__ == '__main__':
             c2s[t] = C2(A, H, r)
 
         c2s = np.sort(c2s[c2s < np.inf])
-        imax = int(0.9*len(c2s))
-        ax[i].hist(c2s[:imax], bins=100)
-        ax[i].set_title('$C_2$ ($m$=%d)' % m)
-        pp.savefig('C2_m%d_nt%d.pdf' % (m, num_trials))
+        c2max = 1000 #c2s[int(0.95*len(c2s))]
+        ax[i].hist(c2s[c2s<c2max], bins=100)
+        ax[i].legend(["$m=%d$" % m], loc='upper right', handlelength=0, handletextpad=0)
+        pp.savefig('C2.pdf')
         pp.show()
+        # TODO: do relative histogram so as to share y axis

### 2020-07-17 manuscripts/thesis/code/sample_complexity.py

@@ -67,54 +67,57 @@ if __name__ == '__main__':
         pass
     pp.ion()
 
+    #H = 'cyclic'
+    H = 'square'
+
     """
     Given N_supp samples per support, what is the probability that for every S in H,
     at least k out of N_supp vectors supported there have the same support wrt. B?
     """
 
-    ms = [m for m in range(3, 12)]
-    fig, ax = pp.subplots(len(ms),len(ms))
+    if H == 'cyclic':
+        ms = [m for m in range(3, 10+1)]
+    elif H == 'square':
+        ms = [k**2 for k in range(2, 4+1)] # square
+    
+    fig, ax = pp.subplots(len(ms), 1, sharex=True, sharey=True, figsize=(11,8.5))
+    fig.add_subplot(111, frameon=False)
+    # hide tick and tick label of the big axis
+    pp.tick_params(labelcolor='none', top=False, bottom=False, left=False, right=False)
+    pp.ylabel("Probability of successful recovery")
+    #pp.ylabel("common Y")
     fig.tight_layout()
-    for i, m in enumerate(ms):
-        for j, k in enumerate(ms):
-            ax[i][j].xaxis.set_visible(False)
-            ax[i][j].yaxis.set_visible(False)
-            ax[i][j].set_visible(False)
 
     for i, m in enumerate(ms):
-        ks = [k for k in range(2, m)]
-        for j, k in enumerate(ks):
+        if H == 'cyclic':
+            ks = [k for k in range(2, m)]
+        elif H == 'square':
+            ks = [int(np.sqrt(m))]
+        for k in ks:
             print("%d" % k)
             samples_per_supp_deterministic = int((k-1) * comb(m,k)) + 1 # with N_deterministic per support or more, probability is 1 (deterministic case)
             probs = []
             for samples_per_supp in range(0, samples_per_supp_deterministic+1):
                 prob_supp = prob_atleast_k_balls_in_some_bin(num_balls = samples_per_supp, num_bins = comb(m,k), k = k) # probability of success
-                num_supps = m # assume H is cyclic order hypergraph, i.e. |H| = m
+                if H == 'cyclic':
+                    num_supps = m # assume H is cyclic order hypergraph, i.e. |H| = m
+                elif H == 'square':
+                    num_supps = 2 * k
[…]

### 2020-08-04 manuscripts/thesis/abstract.tex
update

@@
 Learning optimal dictionaries for sparse coding has exposed characteristic sparse features of many natural signals.
-However, universal guarantees of the stability of such features in the presence of noise are lacking.
-Here, we provide very general conditions guaranteeing when dictionaries yielding the sparsest encodings are unique and stable with respect to measurement or modeling error.
-We demonstrate that some or all original dictionary elements are recoverable from noisy data even if the dictionary fails to satisfy the spark condition, its size is overestimated, or only a polynomial number of distinct sparse supports appear in the data.
-Importantly, we derive these guarantees without requiring any constraints on the recovered dictionary beyond a natural upper bound on its size.
-Our results also yield an effective procedure sufficient to affirm if a proposed solution to the dictionary learning problem is unique within bounds commensurate with the noise.
-We suggest applications to data analysis, engineering, and neuroscience and close with some remaining challenges left open by our work.
+However, universal guarantees of the uniqueness and stability of such features in the presence of noise are lacking.
+This work presents very general conditions guaranteeing when dictionaries yielding the sparsest encodings of a dataset are unique and stable with respect to measurement or modeling error.
+The stability constants are explicit and computable; as such, there is an effective procedure sufficient to affirm if a proposed solution to the dictionary learning problem is unique within bounds commensurate with the noise.
+Beyond the extension of existing results to the noisy regime, a theory of combinatorial designs for sparse supports is introduced to demonstrate that some or all generating dictionary elements are recoverable from noisy data even if the dictionary fails to satisfy the spark condition, its size is overestimated, or only a polynomial number of distinct supports appear in the encoded data.
+Importantly, the guarantees derived here assume no constraints on the recovered dictionary beyond a natural upper bound on its size.
+The work closes with a lengthy discussion of the results and some remaining open challenges seeding future research directions.
 \end{abstract}

### 2020-08-04 manuscripts/thesis/discussion.tex
update

@@
 
-A main motivation for this work is the emergence of seemingly unique representations from sparse coding models trained on natural data, despite the varied assumptions underlying the many algorithms in current use.
-Our results constitute an important step toward explaining these phenomena as well as unifying many publications on the topic by deriving general deterministic conditions under which identification of parameters in this model is not only possible but also robust to uncertainty in measurement and model choice.
+The main motivation for this work was the observation that characteristic sparse representations emerge from sparse coding models trained over a variety of natural scene datasets by a variety of learning algorithms.
+The theorems proven here provide some insight into this phenomenon by establishing very general conditions under which identification of the model parameters is not only possible but also robust to measurement and modeling error.
 
-We have shown that, given sufficient data, the problem of determining a dictionary and sparse codes with minimal support size (Prob.~\ref{OptimizationProblem}) reduces to an instance of Prob.~\ref{InverseProblem}, to which our main result (Thm.~\ref{DeterministicUniquenessTheorem}) applies: every dictionary and sequence of sparse codes consistent with the data are equivalent up to inherent relabeling/scaling ambiguities and a discrepancy (error) that scales linearly with the measurement noise or modeling inaccuracy.
-The constants we provide are explicit and computable; as such, there is an effective procedure that sufficiently affirms if a proposed solution to these problems is indeed unique up to noise and inherent ambiguities, although it is not efficient in general.
-
-%A compelling feature of this model is its simple instantiation of the principle of Occam's razor: a natural video, for instance, is modeled as a linear combination of a small number of spatiotemporal building blocks, each representing an archetypical feature latent in the data.
-
-%For theoretical neuroscience in particular, dictionary learning and related methods have recovered characteristic components of natural images \cite{Olshausen96, hurri1996image, bell1997independent, van1998independent} and sounds \cite{bellsejnowski1996, smithlewicki2006} that reproduce response properties of certain cortical neurons.
+The guarantees concerning the identification of a dictionary and corresponding sparse codes of minimal average support size (Thm.~\ref{SLCopt}), which is the optimization problem of most interest to practitioners (Prob.~\ref{OptimizationProblem}), are to my knowledge the first of their kind in both the noise-free and noisy domains.
+It has been shown here that, given sufficient data, this problem reduces to an instance of Prob.~\ref{InverseProblem} to which the main result (Thm.~\ref{DeterministicUniquenessTheorem}) then applies: every dictionary and corresponding set of sparse codes consistent with the data are equivalent up to inherent relabeling/scaling ambiguities and a discrepancy (error) that scales linearly with the noise.
+In fact, %provided $n \geq \min(2k,m)$, 
+in almost all cases these problems are well-posed given a sufficient amount of data (Thm.~\ref{robustPolythm} and Cor.~\ref{ProbabilisticCor}). 
+Furthermore, the derived scaling constants are explicit and computable; as such, there is an effective procedure that suffices to affirm if a proposed solution to these problems is indeed unique up to noise and inherent ambiguities, although it is not efficient in general.
+%Specifically, given a dictionary and sparse codes purported to solve to Prob.~\ref{InverseProblem}, one checks that that they satisfy the corresponding constraints on $\mathbf{A}$ and the $\mathbf{x_i}$ given in the statement of Thm.~\ref{DeterministicUniquenessTheorem}.
 
@@
 
-%Moreover, we show that even if the meta-parameter for the number of dictionary elements is overestimated, a subset of parameters may still be identifiable up to noise.
+The absence of any assumptions at all about dictionaries that solve Prob.~\ref{InverseProblem} was a major technical hurdle in proving Thm.~\ref{DeterministicUniquenessTheorem}. 
+This very general guarantee was sought because of the practical difficulty of ensuring that an algorithm maintain a dictionary satisfying the spark condition \eqref{SparkCondition} at each iteration, which (to my knowledge) has been an explicit or implicit assumption of all previous works except \cite{Hillar15}; indeed, even certifying a dictionary has this property is NP-hard \cite{tillmann2014computational}.
 
-Beyond an extension of existing noiseless guarantees \cite{Hillar15} to the noisy regime and their novel application to Prob.~\ref{OptimizationProblem}, our work contains a theory of combinatorial designs for support sets key to identification of dictionaries.
-We incorporate this idea into a fundamental lemma in matrix theory (Lem.~\ref{MainLemma}) that draws upon the definition of a matrix lower bound (\ref{Ldef}) induced by a hypergraph.
-The new insight offered by this combinatorial approach allows for guaranteed recovery of some or all dictionary elements even if: 1) dictionary size is overestimated, 2) data cover only a polynomial number of distinct sparse supports, and 3) dictionaries do not satisfy the spark condition.
+Several results in the literature had to be combined to extend the guarantees derived in \cite{Hillar15} into the noisy regime.
+The main challenge was to generalize Lem.~\ref{MainLemma} to the case where the $k$-dimensional subspaces spanned by corresponding submatrices $\mathbf{A}_S$ and $\mathbf{B}_{\pi(S)}$ are assumed to be``close" but not identical.
+Unlike in \cite{Hillar15} where an inductive argument could be applied to the noiseless case, here it had to be explicitly demonstrated that this proximity relation is propagated through iterated intersections right down to the spans of the dictionary elements themselves.
+Lem.~\ref{DistanceToIntersectionLemma} was designed to encapsulate this fact, proven by appeal to a convergence guarantee for an alternating projections algorithm first proposed by von Neumann.
+This result, combined with a little known fact \eqref{eqdim} about the distance metric between subspaces, make up the more obscure components of the deduction.
 
-The absence of any assumptions about dictionaries solving Prob.~\ref{InverseProblem} was a major technical obstruction in proving Thm.~\ref{DeterministicUniquenessTheorem}.
-We sought such a general guarantee because of the practical difficulty in ensuring that an algorithm maintain a dictionary satisfying the spark condition \eqref{SparkCondition} at each iteration, an implicit requirement of all previous works except \cite{Hillar15}; indeed, even certifying a dictionary has this property is NP-hard \cite{tillmann2014computational}.
+The proof of Lem.~\ref{MainLemma} diverges most significantly from the approach taken in \cite{Hillar15} by way of Lem.~\ref{NonEmptyLemma}, which utilizes a combinatorial design for support sets (the ``singleton intersection property") to reduce the deterministic sample complexity by an exponential factor.
+This constitutes a significant advance toward legitimizing dictionary learning in practice, since data must otherwise exhibit the exponentially many possible $k$-wise combinations of dictionary elements required by (to my knowledge) all previously published results; although an exponential number of samples per support is still required (unless $k$ is held fixed).
+The issue is that the map $\pi:\mathcal{H} \to {[m] \choose k}$ is surjective only when $\mathcal{H}$ is taken to be ${[m] \choose k}$, in which case one may proceed by induction as in \cite{Hillar15}, freely choosing supports in the codomain of $\pi$ to intersect over $(k-1)$ indices to then map back to some corresponding set of $(k-1)$ indices at the intersection of supports in the domain.
+Here, for $\mathcal{H} \subset {[m] \choose k}$, a bijection between indices had to instead be established by pigeonholing the image of $\pi$ under constraints imposed by the SIP, which was formulated specifically for this purpose.
+It just so happened that this more general argument for a non-surjective $\pi$ constrained by the SIP applied just as well to the situation where the number of dictionary elements $m$ is over-estimated (i.e.
+$\overline m > m$), in which case a one-to-one correspondence can be guaranteed between a subset of columns of $\mathbf{A}$ and $\mathbf{B}$ of a size simply expressed in terms of the width of each matrix and the regularity of $\mathcal{H}$.
 
-One direct application of this work is to theoretical neuroscience, wherein our theorems justify the mathematical soundness of one of the few hypothesized theories of bottleneck communication in the brain \cite{Isely10}: that sparse neural population activity is recoverable from its noisy linear compression through a randomly constructed (but unknown) wiring bottleneck by any biologically plausible unsupervised sparse coding method that solves Prob.~\ref{DeterministicUniquenessTheorem} or \ref{SLCopt} (e.g., \cite{rehnsommer2007, rozell2007neurally, pehlevan2015normative}).\footnote{We refer the reader to \cite{ganguli2012compressed} for more on interactions between dictionary learning and neuroscience.}
+One of the mathematically significant achievements in \cite{Hillar15} was to break free from the constraint that the recovery matrix $\mathbf{B}$ satisfy the spark condition in addition to the generating dictionary $\mathbf{A}$.
+%, in contrast to all previously known uniqueness results which (to my knowledge) have all either explicitly or implicitly made this assumption.
+Here, it has been demonstrated that, in fact, even $\mathbf{A}$ need not satisfy the spark condition!
+Rather, $\mathbf{A}$ need only be injective on the union of subspaces with supports forming a regular $k$-uniform hypergraph satisfying the SIP (a distinguishing example is given in Sec.~\ref{Results}).
+This relaxation of constraints inspired the definition of the restricted matrix lower bound $L_{\mathcal{H}}$ in \eqref{Ldef}, which generalizes the well-known (see footnote \ref{ripfootnote}) restricted matrix lower bound $L_k$ to be in terms of a hypergraph $\mathcal{H}$, and an interesting object for further study in its own right.
+%(For instance, how hard is it to check that $L_\mathcal{H}(\mathbf{A}) > 0$?)
+%The absence of any restrictions on dictionaries solving Prob.~\ref{InverseProblem} is a major technical obstruction, but highly desirable because of the practical difficulty in ensuring that an algorithm maintain a dictionary satisfying the spark condition \eqref{SparkCondition} at each iteration; indeed, even certifying a dictionary has this property is NP-hard \cite{tillmann2014computational}.
 
-In fact, uniqueness guarantees with minimal assumptions apply to all areas of data science and engineering that utilize learned sparse structure.
-For example, several groups have applied compressed sensing to signal processing tasks; for instance, in MRI analysis \cite{lustig2008compressed}, image compression \cite{Duarte08}, and even the design of an ultrafast camera \cite{Gao14}.
-It is only a matter of time before these systems incorporate dictionary learning to encode and decode signals (e.g., in a device that learns structure from motion \cite{kong2016prior}), just as scientists have used sparse coding to make sense of their data \cite{jung2001imaging, agarwal2014spatially, lee2016sparse, wu2016stability}.
+To reiterate, the methods applied here to prove Thm.~\ref{DeterministicUniquenessTheorem} yield the following results beyond a straightforward extension of those in \cite{Hillar15} to the noisy case:
 
-Assurances offered by our theorems certify that different devices and algorithms learn equivalent representations given enough data from statistically identical systems.\footnote{To contrast with the current hot topic of ``Deep Learning'', there are few such uniqueness guarantees for these models of data; moreover, even small noise can dramatically alter their output \cite{goodfellow2014explaining}.}
-Indeed, a main reason for the sustained interest in dictionary learning as an unsupervised method for data analysis seems to be the assumed well-posedness of parameter identification in the model, confirmation of which forms the core of our findings.
+\begin{enumerate}
+\item A reduction in deterministic sample complexity: To identify the $n \times m$ generating dictionary $\mathbf{A}$, it is required in \cite{Hillar15} that $k{m \choose k}$ data points be sampled from each of the ${m \choose k}$ subspaces spanned by subsets of $k$ columns of $\mathbf{A}$.
+It is shown here that in fact it suffices to sample from at most $m$ such subspaces (see Cor.~\ref{DeterministicUniquenessCorollary}).
+%; thus, for fixed $k$, the deterministic sample complexity is polynomial in $m$.
+%HS15 was already poly for fixed k
+\item An extension of guarantees to the case where the number of dictionary elements is unknown: The results of \cite{Hillar15} only apply to the case where the matrix $\mathbf{B}$ has the same number of columns as $\mathbf{A}$.
+It is shown here that if $\mathbf{B}$ has at least as many columns as $\mathbf{A}$ then it contains (up to noise) a subset of the columns of $\mathbf{A}$.
+\item Relaxed requirements (no spark condition) on the generating matrix $\mathbf{A}$: Rather, $\mathbf{A}$ need only be injective on the union of subspaces with supports that form a regular uniform hypergraph satisfying the SIP.
+\end{enumerate}
 
-\section{Future Directions}
+As it seemed to benefit a reviewer of this work, a brief discussion on how the deterministic sample complexity $N = |\mathcal{H}\left[|(k-1){m \choose k} + 1\right]$ derived here compares to those listed in the the top two rows listed in Table I of \cite{Hillar15} may be in order.
+To be clear, the theory developed here is strictly more general, since $\mathcal{H}$ can always be taken to be ${[m] \choose k}$.
+The point of difference in this comparison is the assumed set of supports for sparse codes, which is always ${[m] \choose k}$ in \cite{Hillar15}, whereas here it can be assumed to be any regular $k$-uniform hypergraph that satisfies the SIP.
+By row, %, assuming for our results that sufficient data have been sampled from all supports in a hypergraph H satisfying the SIP:
+\begin{enumerate}
+\item[I.] The result here improves upon the listed $k{m \choose k}^2$ by an exponential factor, since for every $k < m$ there exists a regular $k$-uniform hypergraph $\mathcal{H}$ with $|\mathcal{H}| = m$ satisfying the SIP.
+\item[II.] The authors in \cite{Hillar15} have applied measure-theoretic arguments to achieve $(k+1){m \choose k}$ with almost-certainty (i.e.
+with probability one), a factor of $m$ reduction over that for which certainty can alternatively be guaranteed here.
+%\item[III.] A direct comparison cannot be made because it is an open question as to the probability that a random set of supports satisfies the SIP.
+This would be an interesting problem for the community to solve; regardless, the result of \cite{Hillar15} is still implied by the more general theory given here.
+%\item[IV.] The result here is $|\mathcal{H}\left[|(k-1){m \choose k} + 1\right]$ with probability one compared to $(k+1){m \choose k}$ with probability one.
+In this case the sample complexity stated in \cite{Hillar15} is marginally better, but it relies on a noise-free technicality unique to their assumption $\mathcal{H} = {m \choose k}$.
+%differs in flavor: their $\mathbf{x_i}$ are assumed to be distributed as $(k+1)$ samples per support for every support of size $k \in [m]$, whereas here it is assumed that $(k-1){m \choose k}$ codes $\mathbf{x_i}$ are distributed over each support in some hypergraph $\mathcal{H}$ satisfying the SIP.
+%\item[V.] Again, a direct comparison cannot be made for the reason stated for row III.
+\end{enumerate}
+
+%Beyond an extension of existing noiseless guarantees \cite{Hillar15} to the noisy regime and their novel application to Prob.~\ref{OptimizationProblem}, this work contains a theory of combinatorial designs for support sets key to identification of dictionaries.
+This idea is incorporated into a fundamental lemma in matrix theory (Lem.~\ref{MainLemma}) that draws upon the definition of a matrix lower bound (\ref{Ldef}) induced by a hypergraph.
+As a consequence of this combinatorial approach, recovery of some or all dictionary elements can be guaranteed even if: i) dictionary size is overestimated, ii) data cover only a polynomial number of distinct sparse supports, and iii) dictionaries do not satisfy the spark condition.
+
+Another reviewer of this work lamented that while the extension from exact recovery to the noisy stability of dictionary learning is significant, the fact that the analysis relies on metrics of the data that are not feasible to compute limits its impact to the scientific community beyond computer science and applied mathematics.
+What sets the main results of this work apart from the vast majority of results in the field is that they are deterministic, and do not depend on any kind of assumption about the particular random distribution from which the sparse supports, coefficients, or dictionary entries are drawn (though Cor.~\ref{ProbabilisticCor} makes a sweeping statement applicable to all continuous distributions).
+Consequently, the inferences of those applying dictionary learning methods to inverse problems in their research are justified only in principle; but this is unavoidably the case for NP-hard problems.
+
+Indeed, theoretical validation makes little practical difference if the methodology is already in widespread use, while practical criteria establishing whether the data models obtained by practitioners are optimal or not would have very high impact.
+To this end, the work has been laid out for those wanting to derive statistical criteria for inference with respect to more domain-specific structured dictionaries and codes (i.e.
+estimate $C_1$), and reduced by half for those hoping to prove the consistency of any dictionary learning algorithm (i.e.
+prove convergence to within $\varepsilon(\delta_1,\delta_2)$ given in \eqref{epsdel}).
+%who will derive from our deterministic guarantees the statistical criteria for inference in more domain-specific probabilistic models
+
+Nonetheless, a main reason for the sustained interest in dictionary learning as an unsupervised method for data analysis seems to be the assumed well-posedness of parameter identification in the model, confirmation of which forms the core of these findings.
+Several groups have applied compressed sensing to signal processing tasks; for instance, in MRI analysis \cite{lustig2008compressed}, image compression \cite{Duarte08}, and even the design of an ultrafast camera \cite{Gao14}.
+It is only a matter of time before these systems incorporate dictionary learning to encode and decode signals (e.g., in a device that learns structure from motion \cite{kong2016prior}), just as scientists have used sparse coding to %make sense of their data \cite{jung2001imaging, agarwal2014spatially, lee2016sparse, wu2016stability}.
+uncover latent structure in data (e.g., forgery detection \cite{hughes2010, olshausen2010applied}; brain recordings \cite{jung2001imaging, agarwal2014spatially, lee2016sparse}; and gene expression \cite{wu2016stability}).
+As uniqueness guarantees with minimal assumptions apply to all areas of data science and engineering that utilize learned sparse structure, assurances offered by these theorems give hope that different devices and algorithms may learn equivalent representations given enough data from statistically identical systems.\footnote{To contrast with the current hot topic of ``Deep Learning'', there are few such uniqueness guarantees for these models of data; moreover, even small noise can dramatically alter their output \cite{goodfellow2014explaining}.}
+
+Within the field of theoretical neuroscience in particular, dictionary learning for sparse coding and related methods have recovered characteristic components of natural images \cite{Olshausen96, hyvarinen1999fast, bell1997independent, van1998independent} and sounds \cite{bellsejnowski1996, smithlewicki2006, Carlson12} that reproduce response properties of cortical neurons.
+The results of this work suggest that this correspondence could be due to the ``universality" of sparse representations in natural data, an early mathematical idea in neural theory \cite{pitts1947}.
+Furthermore, they justify the soundness of one of the few hypothesized theories of bottleneck communication in the brain \cite{Isely10}: that sparse neural population activity is recoverable from its noisy linear compression through a randomly constructed (but unknown) wiring bottleneck by any biologically plausible unsupervised sparse coding method that solves Prob.~\ref{DeterministicUniquenessTheorem} or \ref{SLCopt} (e.g., \cite{rehnsommer2007, rozell2007neurally, pehlevan2015normative}).\footnote{We refer the reader to \cite{ganguli2012compressed} for more on interactions between dictionary learning and neuroscience.}
+
+%The solution to Prob.~\ref{OptimizationProblem}, that of most interest to practitioners of dictionary learning methods, is (to my knowledge) the first of its kind in both the noise-free and noisy domains.
+
+\section{Future Directions}\label{FutureDirections}
 
 There are many challenges left open by this work.
-All conditions stated here guaranteeing the uniqueness and stability of sparse representations have only been shown sufficient; it remains open, therefore, to extend them to necessary conditions, be they on the required number of samples, the structure of the support set hypergraph, or tolerable signal-to-noise ratio for a given recovery error.
-On this last note, the reader should be aware that the deterministic conditions derived here accomodate always the ``worst-case" noise, whereas the ``effective" noise sampled from a concentrated distribution might be significantly reduced, especially for high-dimensional data.
-It would be of great practical benefit to see how drastically all conditions can be relaxed by requiring less-than-certain guarantees in this way and others, such as by probabilistic pigeonholing for reducing sample complexity as discussed following the proof of Thm.~\ref{DeterministicUniquenessTheorem}.
+First and foremost, it should be stressed that all conditions stated here which guarantee the uniqueness and stability of sparse representations have only been shown sufficient; it remains open to work out a set of necessary conditions on all fronts, be it on the number of required samples per support, the structure of support set hypergraphs, or the tolerable signal-to-noise ratio for a bounded recovery error.
+It is also worth stressing that the deterministic conditions derived here must accommodate always the worst possible cases.
+It would be of great practical benefit to see how drastically all conditions can be relaxed by requiring less-than-certain guarantees, as (for instance) exhibited in the discussion on probabilistic pigeonholing following the proof of Thm.~\ref{DeterministicUniquenessTheorem}.
+In a similar vein, the tolerable signal-to-noise ratio can be reduced by considering the probability that noise sampled from a concentrated isotropic distribution will point in a harmful direction, which may be especially low in high-dimensional spaces or for certain support set hypergraphs.
 
-Another interesting question raised by this work is for which special cases is it efficient to check that a solution to Prob.~\ref{InverseProblem} or \ref{OptimizationProblem} is unique up to noise and inherent ambiguities.
-Considering that the sufficient conditions we have described for checking this in general are NP-hard to compute, are the necessary conditions hard?
-Are Probs.~\ref{InverseProblem} and \ref{OptimizationProblem} then also hard (e.g., see \cite{Tillmann15})?
-Finally, since Prob.~\ref{SLCopt} is intractable in general, but efficiently solvable by $\ell_1$-norm minimization when the matrix is known (and has a large enough lower bound over sparse domains \cite{eldar2012compressed}), is there a version of Thm.~\ref{SLCopt} certifying when Prob.~\ref{OptimizationProblem} can be solved efficiently in full by similar means?
+Another interesting remaining challenge is to work out for which special cases it is efficient to check that a solution to Prob.~\ref{InverseProblem} or \ref{OptimizationProblem} is unique up to noise and inherent ambiguities.
+Considering that the sufficient conditions detailed here are in general NP-hard to compute, are the necessary conditions also hard to compute?
+Are Probs.~\ref{InverseProblem} and \ref{OptimizationProblem} then also hard (e.g., see \cite{tillmann2015computational})?
+Since Prob.~\ref{SLCopt} is intractable in general (i.e.
+including the noiseless case), but efficiently solvable by convex relaxation when the matrix $\mathbf{A}$ is known and has a large enough lower bound over sparse domains \cite{eldar2012compressed}, is there a version of Thm.~\ref{SLCopt} that lays down general conditions under which Prob.~\ref{OptimizationProblem} can be solved efficiently in full by similar means?
 % [*** Incorporate this open problem with more words ***]
 
-It is my hope that these remaining challenges pique the interest of the community in applying the theoretical tools showcased here to derive practical guidelines for researchers to bolster their analyses.
-I briefly outline some of these directions below.
+%Finally, it was noted that the combinatorial approach applied here allows for guaranteed recovery of some or all dictionary elements even if the dictionary is overestimated (i.e.
+$\overline m > m$).
+What if it is underestimated?
+How then would the recovered dictionary elements relate to the original columns of $\mathbf{A}$?
+
+%Our results suggest that this correspondence could be due to the ``universality'' of sparse representations in natural data, an early idea in neural theory \cite{pitts1947}.
+
+I briefly expand on some of these directions below.
+It is my hope that these remaining challenges pique the interest of the community, and that practical guidelines can be established using the theoretical tools showcased here to support researchers applying sparse coding techniques.
 
@@
 
-\subsection{Tolerable Error Bounds}
+\subsection{Signal-to-Noise Ratio}
 
-A concern raised in peer review of this work was the size of the constant $C_1$, which sets the tolerable signal-to-noise ratio for dictionary and code recovery up to an acceptable error.
-Referring to the definition of $C_1$ in \eqref{Cdef1}, the reader should note that $L_k$ is a standard quantity in the field of compressed sensing (the ``restricted isometry constant", see footnote \ref{ripfootnote}) and it is known to be reasonable for many random distributions generating dictionaries $\mathbf{A}$ and sparse codes $\mathbf{x}_i$ [CITATION].
-The constant $C_2$, on the other hand, incorporates the more obscure quantity $\xi$ defined in \eqref{FriedrichsDefinition}, which is computed from the ``Friedrichs angle" between certain spans of subsets of the columns of $\mathbf{A}$.
-Simulations for small (pseudo-)randomly generated dictionaries $\mathbf{A}$ suggest nonetheless that the constant $C_2$ is likely reasonable in general as well, at least for the case where $m=k^2$ and $\mathcal{H}$ is taken to be the set of rows and columns formed by arranging the elements of $[m]$ in a square grid (see Fig.
+A concern raised in peer review of this work was the typical size of the constant $C_1$, which sets the tolerable signal-to-noise ratio for dictionary and code recovery up to an acceptable error.
+Referring to the definition of this constant in \eqref{Cdef1}, the reader should note that the denominator involves $L_k$, a standard quantity in the field of compressed sensing (the ``restricted isometry constant", see footnote \ref{ripfootnote}), which is known to be reasonable for many random distributions generating dictionaries $\mathbf{A}$ and sparse codes $\mathbf{x}_i$ \cite{baraniuk2008simple}.
+The numerator $C_2$, on the other hand, incorporates the more obscure quantity $\xi$ defined in \eqref{FriedrichsDefinition}, which is computed from the ``Friedrichs angle" between certain spans of subsets of the columns of $\mathbf{A}$.
+Simulations for small (pseudo-)randomly generated dictionaries $\mathbf{A}$ suggest nonetheless that the constant $C_2$ is likely reasonable in general as well (at least, for the case where $m=k^2$ and $\mathcal{H}$ is taken to be the set of rows and columns formed by arranging the elements of $[m]$ into a square grid; see Fig.
 \ref{reasonableC2}).
+These observations motivate the following conjecture:
 
-Finally, the error bounds can be improved by tightening the constant $C_1$, e.g. via an improvement in Lemma ?.
+\begin{conjecture}
+For all $t > 0$,
+\begin{equation*}
+Pr[ \left| C_2- \mathbb{E}[C_2 ] \right| > t] \to 0 \ \ \text{as $k \to \infty$ and $k/m \to 0$} 
+\end{equation*}
+provided the assumptions of Thm. \ref{DeterministicUniquenessTheorem} are satisfied.
+\end{conjecture}
+%Finally, the error bounds can be improved by tightening the constant $C_1$, e.g. via an improvement in Lemma ?.
+%$C_1 = C_1(\mathbf{A}, \mathcal{H}, \{ \mathbf{x_i} \}_{i=0}^N)$
 
-\subsection{Sample Complexity and Support Set Hypergraphs}
+\subsection{Sample Complexity}
 
-Deterministic sample complexity can be reduced by tightening the pigeonholing argument in the proof of Thm.~\ref{DeterministicUniquenessTheorem}.
-The argument iterates over supports $S \in \mathcal{H}$, in each case determining a corresponding support $\overline S \in {\bar m \choose k}$ without consideration of previously matched support pairs, whereas the assumption $L_\mathcal{H}(\mathbf{A}) > 0$ implies that no two supports in $\mathcal{H}$ can correspond to the same $\overline S$.
-The number of bins to pigeonhole into therefore decreases by one at each iteration.
+It is possible to tighten the pigeonholing argument in the proof of Thm.~\ref{DeterministicUniquenessTheorem} and thereby reduce the deterministic sample complexity without recourse to uncertainty (as previously suggested).
+The argument as presented iterates over supports $S \in \mathcal{H}$, in each case determining a corresponding support $\overline S \in {[\overline m] \choose k}$ without consideration of previously matched support pairs; and yet the assumption $L_{2\mathcal{H}}(\mathbf{A}) > 0$ implies that no two supports in $\mathcal{H}$ can map to the same $\overline S$.
+The number of bins to pigeonhole into thus decreases every iteration, though this is a drop in a bucket of exponential size.
+It would be interesting to see how much the deterministic sample complexity can be reduced by imposing these constraints holistically, given the specific structure of the hypergraph $\mathcal{H}$.
 
-There is also the number of sparse supports to consider for fixed $m$ and $k$, i.e.
-the size of the SIP-satisfying, regular, $k$-uniform hypergraph $\mathcal{H}$ over $[m]$.
-These requirements can be loosened, too; in particular, though imposing regularity allows for better clarity of exposition, a close examination of Lemma (?) reveals that non-regular hypergraphs suffice so long as they satisfy a constraint on the sequence of node degrees to maintain compatibility with the iterative argument.
-It is natural to ask, then, what are the necessary constraints on the support set hypergraph, and what is the smallest hypergraph that satisfies these constraints for given $m$ and $k$?
+Incidentally, there is also room to breathe in the restrictions on $\mathcal{H}$.
+Already, the results of this work motivate the following question, which is only one among many combinatorial problems brought to mind by the SIP (Def.~\ref{sip}):
+\begin{question}
+Fix integers $m$ and $k < m$. What is the smallest regular hypergraph $\mathcal{H} \subseteq {[m] \choose k}$ satisfying the SIP?
+\end{question}
 
-As discussed following the proof of Thm.~\ref{DeterministicUniquenessTheorem}, probabilistic guarantees can be ....
+A close examination of the proof of Lemma \ref{NonEmptyLemma} (see the Appendix) reveals, however, that $\mathcal{H}$ need not be regular so long as it satisfies a constraint on the sequence of node degrees compatible with the iterative argument.
+It is then natural to wonder: what are the necessary constraints on $\mathcal{H}$, and what is the smallest hypergraph satisfying these constraints for given $m$ and $k$?
 
-The problem reduces to counting integer solutions to the problem $\sum_i n_i = N$ subject to $n_i < k$ for all $i$.
-It appears there is no closed formula for this problem, but the number of solutions can be computed in a number of operations independent of $N$.
-The number is the coefficient of $X_N$ in the polynomial $(1 + X + \ldots + X^k)^n$.
+Opening ourselves up to uncertainty, we can furthermore ask:
+\begin{question}\label{probofsip}
+Fix $k < m$. What is the probability that a random subset of ${[m] \choose k}$ is regular and satisfies the SIP?
+\end{question}
+
+Within the realm of uncertain guarantees, we can also elaborate on the probabilistic pigeonholing strategy outlined in the discussion following the proof of Thm.~\ref{DeterministicUniquenessTheorem}.
+The problem is to count the number of ways in which vectors supported in $S \in \mathcal{H}$ can be partitioned among supports in ${\overline m \choose k}$ without allocating $k$ or more to any individual one (in which case the logic of the proof fails to imply the result; we are interested in the probability that it doesn't).
+These are integer solutions to the problem $\sum_i n_i = N$ subject to $n_i < k$ for all $i$, where $i = 1, \ldots, {\overline m \choose k}$.
+Following closely the exposition in \cite{stackexchangeanswer}, it appears there is no closed formula for this problem, but the number of solutions can be computed in a number of operations independent of $N$.
+Writing $p = {\overline m \choose k}$, the number is the coefficient of $X^N$ in the polynomial $(1 + X + \ldots + X^{k-1})^p$.
 Written as a rational function of $X$,
 
-%see:
-%https://math.stackexchange.com/questions/553960/extended-stars-and-bars-problemwhere-the-upper-limit-of-the-variable-is-bounded
+\begin{equation*}
+(1 + X + \ldots + X^{k-1})^p = \left(\frac{1 - X^k}{1 - X} \right)^p = \frac{\left(1 - X^k \right)^p}{\left(1 - X\right)^p}
+\end{equation*}
+the coeffiecient of $X^i$ in the numerator is zero unless $i$ is a multiple $qk$ of $k$, in which case it is $(-1)^q{p \choose q}$, and the coefficient of $X^j$ in the inverse of the denominator is $(-1)^j {-p \choose j} = {j + p-1 \choose j}$, which is zero unless $j \geq 0$ and otherwise equal to ${j + p-1 \choose p-1}$.
+It remains to sum over all $i + j = N$, which gives:
 
-\subsection{Guarantees for Convex Optimization}
+\begin{equation*}
+n_\text{fails} = \sum_{q=0}^{\text{min}(p, N/k)} (-1)^q {p \choose q} {N - qk + p - 1 \choose p - 1}
+\end{equation*}
+where the summation is truncated to ensure that $N - qk \geq 0$ (the condition $j \geq 0$) and has at most $p+1 = {\overline m \choose k} + 1$ terms.
 
-An additional consequence of Thm.~\ref{DeterministicUniquenessTheorem} of potential practical relevance to is the implied lower bound $L_{2k}(\mathbf{B}) \geq \left(L_{2k}(\mathbf{A}) - C_1\varepsilon \right) / \|\mathbf{D}\|_1$ in the case where $\mathbf{A}$ satisfies \eqref{SparkCondition}.
-Since solving Prob.~\ref{SLCopt} directly requires a combinatorial search over sparse supports for the $\mathbf{\overline x}_i$ for each proposed dictionary $\mathbf{B}$, rendering it intractable in general, a common strategy is to replace the $\ell_0$-norm in \eqref{minsum} with the $\ell_1$-norm, thereby transforming the inference of sparse $\mathbf{\overline x}_i$ for a fixed dictionary $\mathbf{B}$ into a convex optimization solvable by a linear program.
-A major advance in compressive sensing was the discovery that, for fixed $\mathbf{B}$, solutions to \eqref{minsum} using either norm yield the same sparse vectors $\mathbf{\overline x}_i$ (up to noise) provided $L_{2k}(\mathbf{B})$ is large enough \cite{?}.
-What the current work provides are conditions on the generating dictionary $\mathbf{A}$ and $k$-sparse codes $\mathbf{x}_i$ under which \emph{all} matrices $\mathbf{B}$ (of bounded column-norm) that solve Prob.~\ref{OptimizationProblem} also share this property by virtue of uniqueness and stability; that is, conditions which guarantee that the sparse codes $\mathbf{\overline x}_i$ solving Prob.~\ref{OptimizationProblem} also solve the convexified problem when the corresponding dictionary $\mathbf{B}$ is held fixed.
-It remains to determine practical conditions that reject matrices not solving Prob.~\ref{OptimizationProblem} from nonetheless solving the convexified problem.
-%
+The total number of ways to pigeonhole is $n_\text{total} = {N +p- 1 \choose p - 1}$, and so the probability of full recovery is $\left(1 - n_\text{fails} / n_\text{total} \right)^{|\mathcal{H}|}$. 
+The curves computed in this way in Fig.
+\ref{probpigeon} suggest that, while it may very well be impossible to exorcise exponentiality from the number of required samples in the deterministic or almost-certain case, perhaps it is possible with high-probability by one way or another.
+Informally,
 
-Regardless, an implication of the above observation is that the following algorithm solves Prob.~\ref{OptimizationProblem} without appeal to combinatorial search through supports:
-\begin{enumerate}
-\item List all matrices $\mathbf{B}$.
-\item For each matrix $\mathbf{B}$, solve $\mathbf{\overline x}_i = \arg \min \|\mathbf{v}\|_1$ s.t. $\|\mathbf{Bv} - \mathbf{z}_i\| \leq \eta$ for $i = 1, \ldots, N$.
-\item Quantify the proposed solution of the previous step as $\rho(\mathbf{B}, \mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N) = \sum_{i=1}^{N} \|\mathbf{\overline x}_i\|_0$.
-\item Output $\arg \min_{\mathbf{B}, \mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N} \left( \rho \right)$.
- \end{enumerate}
-%
+\begin{question}
+While fixing $k$ yields polynomial deterministic sample complexity in $m$ (see Cor.~\ref{DeterministicUniquenessCorollary}), is there some more general probablistic sense (perhaps for some restricted class of hypergraphs) by which sample complexity is polynomial in both $m$ and $k$?
+\end{question}
+%Referring to Fig.
+\ref{probpigeon}, which computes these probabilities for some small hypergraphs, one is led to wonder if it may be possible to exorcise exponentiality from the sample complexity asymptotically in this way or another.
 
-%Since its inception some twenty years ago, sparse coding has become a standard tool in signal analysis, yielding myriad insights into the structure of natural signals across a variety of scientific domains.
-In this work,
+%\begin{question}
+%Is there a class of hypergraphs $\mathcal{H} = \mathcal{H}(m,k)$ and a polynomial $p(m,k)$ such that $N \geq p(m,k)$ implies successful dictionary and code recovery with a probability approaching one for generic $\mathbf{A}$ and $\mathbf{x}_i$ supported in $\mathcal{H}$ as $m \to \infty$?
+%Is there a class of hypergraphs $\mathcal{H}$ for which a number of samples $N$ polynomial in both $m$ and $k$ suffices to guarantee stable recovery of $\mathbf{A}$ and sparse codes $\mathbf{x}_i$ as $k/m \to 0$?
+%\end{question}
 
-%We make a final remark about the tightness of our results and the computability of our derived constants.
-%We remark that our constants have been derived for deterministic ``worst-case'' noise, whereas the ``effective'' noise might be smaller when sampled from a distribution.
+\subsection{Convex Optimization}
 
-%Our results suggest that this correspondence could be due to the ``universality'' of sparse representations in natural data, an early idea in neural theory \cite{pitts1947}.
+A commonly applied workaround to the intractability of Prob.~\ref{SLCopt} (see \cite{tillmann2015computational}) is to swap out the norm $\|\cdot\|_0$ in \eqref{minsum} for $\|\cdot\|_1$, thereby transforming the inference of sparse $\mathbf{\overline x}_i$ for a given $\mathbf{B}$ into a convex optimization solvable by a linear program.
+A major advance in compressive sensing was the discovery that \eqref{minsum} can in fact be solved in this way for fixed $\mathbf{B}$ provided $L_{2k}(\mathbf{B})$ is large enough \cite{eldar2012compressed}.
+The current work provides conditions on the generating dictionary $\mathbf{A}$ and $k$-sparse codes $\mathbf{x}_i$ under which \emph{all} matrices $\mathbf{B}$ (of bounded column-norm) that solve Prob.~\ref{OptimizationProblem} have $L_{2k}(\mathbf{B})$ bounded from below; specifically, $L_{2k}(\mathbf{B}) \geq \left(L_{2k}(\mathbf{A}) - C_1\varepsilon \right) / \|\mathbf{D}\|_1$ in the case where $\mathbf{A}$ satisfies \eqref{SparkCondition}.
+Thus, there is some noise bound inside of which all solutions to Prob.~\ref{OptimizationProblem} are solutions to the convexified problem as well.
+It remains to determine practical constraints that would exclude alternative dictionaries which may solve the convefixied problem without solving Prob.~\ref{OptimizationProblem}.
 
-% \vspace{-.2 cm}
-
-%\showacknow % Display the acknowledgments section
+% SOLUTION CHECKING ALGORITHM:
+%\begin{enumerate}
+ %  \item For each $\mathbf{x_i}$, determine its support $S$ and increment a counter corresponding to that support.
+  % \item For each support $S$ with count greater than $(k-1){m \choose k}$, check the $\mathbf{x_i}$ supported there are in general linear position (i.e.
+the determinant of the matrix having $\mathbf{x}_i$ as its columns is nonzero) and discard $S$ if not.
+ %  \item Check the remaining set of supports satisfies the SIP. 
+  % \item If so, list all of its regular $k$-uniform sub-hypergraphs and discard those for which $L_{2\mathcal{H}}(\mathbf{A}) = 0$. 
+  % \item For each of the remaining hypergraphs, compute the constant $C_1$ from $\mathbf{A}$ and the $\mathbf{x_i}$.% (or for every subset of the  $\mathbf{x_i}$ of size $(k-1){m \choose k}$).
+ %  \item Check that $\varepsilon < L_2(\mathbf{A})$. If yes, the solution is "unique".
+%\end{enumerate}
 
@@
 \begin{center}
-\includegraphics[width=1 \linewidth]{figures/C2_m36_nt1000.pdf}
-\caption{Constant $C_2(\mathbf{A}, \mathcal{H})$ computed for generic unit-norm overcomplete dictionaries $\mathbf{A} \in \mathbb{R}^{n \times m}$ (with $m = 2n$) when the support set hypergraph $\mathcal{H}$ consists of the rows and columns formed by arranging  the elements of $[m]$ into a square grid (i.e.
-$m = k^2$.
-The form of the distribution suggests a reasonable value should generally be expected.}
+\includegraphics[width=1 \linewidth]{figures/C2.pdf}
+\caption{Distribution of $C_2(\mathbf{A}, \mathcal{H})$ computed for 1.33x overcomplete generic unit-norm dictionaries $\mathbf{A} \in \mathbb{R}^{n \times m}$ (i.e.
+with $n = 3m/4$) when the support set hypergraph $\mathcal{H}$ consists of the rows and columns formed by arranging  the elements of $[m]$ into a square grid (i.e.
+$m = k^2$).
+The distribution becomes more concentrated as $m$ grows.}
 \vspace{-.6 cm}

### 2020-08-04 manuscripts/thesis/introduction.tex
update

@@
 
-\begin{itemize}
-\item Background to the topic.
-\item Brief review of current knowledge.
-\item Indicate the gap in knowledge. State the aim of the research and how it fits into the gap.
-\item Can include an outline of what follows.
-\end{itemize}
+%\begin{itemize}
+%\item Background to the topic.
+%\item Brief review of current knowledge.
+%\item Indicate the gap in knowledge. State the aim of the research and how it fits into the gap.
+%\item Can include an outline of what follows.
+%\end{itemize}
 
@@
 
-Sparse coding is a common modern approach to pattern analysis in signal processing whereby each of $N$ observed $n$-dimensional signal samples is viewed as a (noisy) linear combination of at most $k$ elementary waveforms drawn from some unknown ``dictionary" of size $m \ll N$ (see \cite{Zhang15} for a comprehensive review).
+Sparse coding is a common modern signal processing technique that views each of $N$ observed $n$-dimensional signal samples as a (noisy) linear combination of at most $k$ elementary waveforms drawn from some unknown ``dictionary" of size $m \ll N$ (see \cite{Zhang15} for a comprehensive review).
 %\IEEEPARstart{A}{}common modern approach to pattern analysis in signal processing is to view each of $N$ observed $n$-dimensional signal samples as a (noisy) linear combination of at most $k$ elementary waveforms drawn from some unknown ``dictionary" of size $m \ll N$ (see \cite{Zhang15} for a comprehensive review).
@@
 
-While several algorithms have been recently proposed to provably recover unique dictionaries under specific conditions (see \cite[Sec.~I-E]{Sun16} for a summary of the state-of-the-art), few theorems can be invoked to justify the consistency of inference under this model of data more broadly.
+While several algorithms have recently been proposed to provably recover unique dictionaries under specific conditions (see \cite[Sec.~I-E]{Sun16} for a summary of the state-of-the-art), few theorems can be invoked to justify the consistency of inference under this model of data more broadly.
 To our knowledge, a universal guarantee of the uniqueness and stability of learned dictionaries and the sparse representations they induce over noisy data has yet to appear in the literature.
@@
 for $k$-\emph{sparse} $\mathbf{x}_i \in \mathbb{R}^m$ having at most $k<m$ nonzero entries and \emph{noise} $\mathbf{n}_i \in \mathbb{R}^n$, with bounded norm $\| \mathbf{n}_i \|_2 \leq  \eta$ representing our worst-case uncertainty in measuring the product $\mathbf{A}\mathbf{x}_i$.
-We first consider the following formulation of sparse coding.
+We first consider the following decidable\footnote{Note that Prob.~\ref{InverseProblem} is decidable for rational inputs $\mathbf{z}_i$ \cite{chrishillar} since the statement that it has a solution can be expressed as a logical sentence in the theory of algebraically closed fields, and this theory has quantifier elimination \cite{basu2006algorithms}.} formulation of sparse coding.
 %The first mathematical problem we consider is the following.
@@
 Our development of Thm.~\ref{DeterministicUniquenessTheorem} is general enough to provide some uniqueness and stability even when generating $\mathbf{A}$ do not fully satisfy (\ref{SparkCondition}) and recovery dictionaries $\mathbf{B}$ have more columns than $\mathbf{A}$.
-Moreover, the approach incorporates a combinatorial theory for designing generating codes that should be of independent interest.
+Moreover, the approach incorporates a theory of combinatorial designs for the sparse supports of generating codes $\mathbf{x}_i$ that should be of independent interest.
 We also give brief arguments adapting our results to dictionaries and codes drawn from probability distributions (Cor.~\ref{ProbabilisticCor}).
 The technical proofs of Thms.~\ref{DeterministicUniquenessTheorem} and ~\ref{SLCopt} are deferred to Sec.~\ref{DUT}, following some necessary definitions and a fact in combinatorial matrix analysis (Lem.~\ref{MainLemma}; proven in the Appendix).
-Finally, we discuss in Sec.~\ref{Discussion} applications of our mathematical observations as well as open questions.
+We discuss these results and their applications in depth in Sec.~\ref{Discussion} and outline open questions and directions for future research in Sec.~\ref{FutureDirections}.
 %The Appendix contains a proof of Lem.~\ref{MainLemma}.

### 2020-08-04 manuscripts/thesis/results.tex
update

@@
 
-Consequently, if $k$ is held fixed or if the size of the support set of reconstructing codes is polynomial in $\overline m$ and $k$, then a practical (polynomial) amount of data suffices to identify the dictionary.\footnote{In the latter case, a reexamination of the pigeonholing argument in the proof of Thm.~\ref{DeterministicUniquenessTheorem} requires a polynomial number of samples distributed over a polynomial number of supports.} Reasons to be skeptical that this holds in general, however, can be found in \cite{tillmann2014computational, Tillmann15}.
+Consequently, if $k$ is held fixed or if the size of the support set of reconstructing codes is polynomial in $\overline m$ and $k$, then a practical (polynomial) amount of data suffices to identify the dictionary.\footnote{In the latter case, a reexamination of the pigeonholing argument in the proof of Thm.~\ref{DeterministicUniquenessTheorem} requires a polynomial number of samples distributed over a polynomial number of supports.} Reasons to be skeptical that this holds in general, however, can be found in \cite{tillmann2014computational, tillmann2015computational}.
 Even so, in the next section we discuss how probabilistic guarantees can in fact be made for any number of available samples.

### 2020-08-04 manuscripts/thesis/reviewers.tex
update

--- 2020-07-16 manuscripts/thesis/conclusions.tex
@@
 
-Given a dictionary A and codes x-i that solve Problem 1 (e.g., learned by any algorithm), check that that they satisfy the assumptions of Thm. 1:
-   - List the support sets of the x-i.
-   - Discard those for which there are (k-1)(m /choose k) or fewer x-i with that support.
-   - Discard those for which the supported x-i are not in general linear position. (This should also exclude any supports less than k in size.)
+Given a dictionary A and codes  that solve Problem 1 (e.g., learned by any algorithm), check that that they satisfy the assumptions of Thm. 1:
+   - List the support sets of the $\mathbf{x_i}$.
+   - Discard those for which there are $(k-1){m \choose k}$ or fewer \mathbf{x_i} with that support.
+   - Discard those for which the supported $\mathbf{x_i$} are not in general linear position. (This should also exclude any supports less than k in size.)
    - From the support sets that remain, list all SIP-satisfying hypergraphs that are subsets of this set.
-   - Discard those for which L-(2H)(A) = 0.
-   - For each of the remaining hypergraphs, determine the constant C-1 from A and the x-i (or for every subset of the x-i of size (k-1)(m /choose k)).
-   - Check that the derived upper bound on /varepsilon exceeds that of the original problem. If yes, the solution is "unique".
+   - Discard those for which $L_{2\mathcal{H}}(\mathbf{A}) = 0$.
+   - For each of the remaining hypergraphs, determine the constant $C_1$ from \mathbf{A} and the $\mathbf{x_i}$ (or for every subset of the  $\mathbf{x_i}$ of size $(k-1){m \choose k}$).
+   - Check that the derived upper bound on $\varepsilon$ exceeds that of the original problem. If yes, the solution is "unique".
 
@@
 
+!HERE!
+
 REVIEWER:
@@
 
-NOTE: Structured dictionaries? Just derive the bounds specific to them. Could be efficiently computable in specific cases.
-
-REVIEWER
-
-As l0 norm is intractable, does all the properties still hold for l1 norm minimization? Can we solve it efficiently (polynomial time) to global optimality? Similar issue for other works, such as
-https://arxiv.org/pdf/1807.05595.pdf
-
-RESPONSE:
-We make no claims in this paper about l1-norm minimization, though we are hopeful a clever reader may find some way to build off our results and derive related guarantees for this continuous relaxation of the sparse coding problem.
-
 TODO : can we deterministically generate matrices injective on SIP hyper graphs? The (mCk)-hypergraph is one such possibility, so maybe not in general? But for special cases (convolution matrices..?)

### 2020-08-04 manuscripts/thesis/thesis.tex
update

@@
 \usepackage{rotating} % provides sidewaystable and sidewaysfigure
+\usepackage{url}
 
@@
 
-\begin{dedication}
-\null\vfil
+%\begin{dedication}
+%\null\vfil
 %\begin{center}
-Dedication
 %I want to dedicate this to my dad.
-At the same time, I don't want to, because the results on display here can't be matched to the time with him I traded to produce them, and it feels as though dedicating this work to him would be measuring his life up against the theorems contained here-in.
-I knew very well this work wasn't so important; these theorems, while fundamental, are just something people might cite to feel better about whatever sketchy sparse coding analysis they were already going to do, anyway.
+At the same time, I don't want to, because the results on display here can't be matched to the time with him I traded to produce them, and it feels as though dedicating this work to him would be measuring his life up against them.
+These theorems, while fundamental, are just something people might cite to feel better about the sparse coding analyses they were already going to do, anyway.
 And yet, despite total freedom offered by the Helen Wills Neuroscience Institute, I worried the brain was so dauntingly complex that I should feel lucky to have at last been offered a well-defined relevant problem to work on, particularly one I felt even remotely equipped to solve myself, so as to feel deserving of a Ph.D.
@@
 I dedicate and don't dedicate this and everything to come to you, too.
-\vspace{12pt}
+%\vspace{12pt}
 %\end{center}
-\vfil\null
-\end{dedication}
+%\vfil\null
+%\end{dedication}
 
@@
 
-\begin{acknowledgements}
-I would like to thank Chris Hillar for laying down the groundwork and vetting all my proofs.
-He gave me a lot of his time for little if anything in return.
-Fritz Sommer for taking on the role of my advisor.
-The Berkeley Student Cooperative for a really awesome and transformative time.
-CZ or Die.
-We thank Darren Rhea for early thoughts, and Ian Morris for posting \eqref{eqdim} online.
-
-\end{acknowledgements}
+%\begin{acknowledgements}
+%I would like to thank: Chris Hillar for laying down the groundwork and vetting all of my proofs many times over.
+He lent me a lot of his time and expertise for little in return.
+Fritz Sommer for advising me and pointing me toward a tractable problem to solve.
+The Berkeley Student Cooperative for the amazing experience living co-operatively in Berkeley.
+CZ or die.
+%\end{acknowledgements}
 
@@
 
+\section{Foreword}
+This thesis presents results published Dec.~2019 in a paper of the same name in \emph{IEEE Transactions on Signal Processing}, largely verbatim.
+Readers should refer to the Discussion and Future Directions as well as Figures \ref{probpigeon} and \ref{reasonableC2} for additional insights not offered in the paper.
+
 % (Optional)
- \part{Main Text}
+ %\part{Main Text}
 
@@
 \include{discussion}
-\include{conclusions}
-
+%\include{reviewers}
 \include{appendix}
-%\include{conclusions}
 

### 2020-08-04 manuscripts/thesis/thesis_expanded.tex
update

--- 2019-05-10 manuscripts/IEEE/final_submission.tex
@@
-% TODO: 
-% Make L_H a definition..? Change def of L to be 1-norm so we don't need these sqrt k's?
-% C_1 depends on J in Thm 1
-% also in proof of (7) x need not be *any* 2k-sparse vector...can instead restrict to some H...then 2k is restricted to half being on H.
-
-% Notes:
-%
-% Can we prove in a line or two that the inverse problem is stable by arguing that the function is bijective and closed therefore a homeomorphism?
-% Should we mention the notion of Grassmannian manifolds and that Theta is a metric on this space?
-% Change robustness to stability?
-%
-\documentclass[journal, twocolumn]{IEEEtran}
-
-% *** MATH PACKAGES ***
+%% thesis.tex 2014/04/11
+%
+% Based on sample files of unknown authorship.
+%
+% The Current Maintainer of this work is Paul Vojta.
+%
+% To compile this file, run "latex thesis", then "biber thesis"
+% (or "bibtex thesis", if the output from latex asks for that instead),
+% and then "latex thesis" (without the quotes in each case).
+
+\documentclass{ucbthesis}
+
+% *** CITATION STUFF ***
+%\usepackage{biblatex} 
+%\bibliography{references} 
+% the above doesn't work, using this instead:
+\usepackage[backend=bibtex,style=numeric]{biblatex}
+\addbibresource{references}
+
+% *** MATH STUFF ***
 \usepackage{amsmath, amssymb, amsthm} 
@@
 
-\usepackage[pdftex]{graphicx}
-
-% *** ALIGNMENT PACKAGES ***
+% *** ALIGNMENT STUFF***
 \usepackage{array}
-\usepackage{cite}
 \usepackage{bm}
-
-% correct bad hyphenation here
-%\hyphenation{op-tical net-works semi-conduc-tor}
+\usepackage{rotating} % provides sidewaystable and sidewaysfigure
+
+% Double spacing, if you want it.  Do not use for the final copy.
+% \def\dsp{\def\baselinestretch{2.0}\large\normalsize}
+% \dsp
+
+% If the Grad. Division insists that the first paragraph of a section
+% be indented (like the others), then include this line:
+% \usepackage{indentfirst}
+
+\addtolength{\abovecaptionskip}{\baselineskip}
+
+%\hyphenation{mar-gin-al-ia}
+%\hyphenation{bra-va-do}
 
@@
 
-%\title{When can a generating dictionary and sparse codes be recovered from noisy data?}
-%\title{When is the dictionary learning problem well-posed?}
-\title{On the uniqueness and stability of dictionaries \\ for sparse representation of noisy signals}
-%\title{When is the dictionary learning problem for sparse coding well-posed?}
-%\title{When is the sparsest representation unique?}
-%\title{When are sparse codes identifiable from their unknown noisy compressive measurements?}
-% FRITZ2: The title doesn't reflect the amount of new stuff, it seems incremental from the last one. It's not very meaningful.
-% FRITZ: Not everyone knows what well-posed means. You should mention recovery from noisy data in the title.
-
-\author{Charles~J.~Garfinkle and Christopher~J.~Hillar \\
-Redwood Center for Theoretical Neuroscience, Berkeley, CA, USA
-%\thanks{%e-mails: cjg@berkeley.edu, chillar@msri.org.  
-%CG and CH supported, in part, by NSF grant IIS-1219212 and the Statistical and Applied Mathematical Sciences Institute, under NSF DMS-1127914.}
-}
+% Declarations for Front Matter
+
+\title{On the uniqueness and stability of dictionaries for sparse representation of noisy signals}
+\author{Charles Garfinkle}
+\degreesemester{Summer}
+\degreeyear{2020}
+\degree{Doctor of Philosophy}
+\chair{Friedrich Sommer}
+\othermembers{Bruno Olshausen \\
+  Mike Deweese \\
+  Bin Yu}
+% For a co-chair who is subordinate to the \chair listed above
+% \cochair{Professor Benedict Francis Pope}
+% For two co-chairs of equal standing (do not use \chair with this one)
+% \cochairs{Professor Richard Francis Sony}{Professor Benedict Francis Pope}
+\numberofmembers{4}
+% Previous degrees are no longer to be listed on the title page.
+% \prevdegrees{B.A. (University of Northern South Dakota at Hoople) 1978 \\
+%   M.S. (Ed's School of Quantum Mechanics and Muffler Repair) 1989}
+\field{Neuroscience}
+% Designated Emphasis -- this is optional, and rare
+% \emphasis{Colloidal Telemetry}
+% This is optional, and rare
+% \jointinstitution{University of Western Maryland}
+% This is optional (default is Berkeley)
+% \campus{Berkeley}
+
+% For a masters thesis, replace the above \documentclass line with
+% \documentclass[masters]{ucbthesis}
+% This affects the title and approval pages, which by default calls this
+% document a "dissertation", not a "thesis".
 
 \maketitle
-
-% \keywords{Sparse coding, dictionary learning, matrix factorization, compressed sensing, inverse problems, blind source separation}
-
-\begin{abstract}
-%Learning optimal dictionaries for sparse coding has exposed characteristic sparse features of many natural signals.
-However, there are few universal conditions guaranteeing the stability of such features in the presence of noise.
-Here, we prove very generally that optimal dictionaries and sparse codes are unique up to measurement error for all diverse enough datasets generated by the sparse coding model.
-Applications are given to data analysis, engineering, and neuroscience.
-Learning optimal dictionaries for sparse coding has exposed characteristic sparse features of many natural signals.
-However, universal guarantees of the stability of such features in the presence of noise are lacking.
-Here, we provide very general conditions guaranteeing when dictionaries yielding the sparsest encodings are unique and stable with respect to measurement or modeling error.
-We demonstrate that some or all original dictionary elements are recoverable from noisy data even if the dictionary fails to satisfy the spark condition, its size is overestimated, or only a polynomial number of distinct sparse supports appear in the data.
-Importantly, we derive these guarantees without requiring any constraints on the recovered dictionary beyond a natural upper bound on its size.
-Our results also yield an effective procedure sufficient to affirm if a proposed solution to the dictionary learning problem is unique within bounds commensurate with the noise.
-We suggest applications to data analysis, engineering, and neuroscience and close with some remaining challenges left open by our work.
-\end{abstract}
-
-% Optional adjustment to line up main text (after abstract) of first page with line numbers, when using both lineno and twocolumn options.
-% You should only change this length when you've finalised the article contents.
+% Delete (or comment out) the \approvalpage line for the final version.
+\approvalpage
+\copyrightpage
+
+\include{abstract}
+
+\begin{frontmatter}
+
+\begin{dedication}
+\null\vfil
+%\begin{center}
+Dedication
+%I want to dedicate this to my dad.
+At the same time, I don't want to, because the results on display here can't be matched to the time with him I traded to produce them, and it feels as though dedicating this work to him would be measuring his life up against the theorems contained here-in.
+I knew very well this work wasn't so important; these theorems, while fundamental, are just something people might cite to feel better about whatever sketchy sparse coding analysis they were already going to do, anyway.
+And yet, despite total freedom offered by the Helen Wills Neuroscience Institute, I worried the brain was so dauntingly complex that I should feel lucky to have at last been offered a well-defined relevant problem to work on, particularly one I felt even remotely equipped to solve myself, so as to feel deserving of a Ph.D.
+from UC Berkeley.
+The fact is that whatever the eventual effect of this work on the scientific ecosystem, these truths could have waited, arrived at their own pace, via myself or another, and I could have been more present with my dad as he waited for death.
+I couldn't really fathom what it actually meant for him to die, to never see or talk to or hug him again, while the idea of putting original work out there, of crafting my own piece of the overwhelming puzzle that is neuroscience, was tantalizing.
+Let's say, then, that this dedication is the first bit of a life's work, real work void of any prestigious position or degree and the associated self-doubt and pressure, put toward passionate id	eas, solving problems I care about and that actually matter, loving and caring for others or, as my dad would say, ``being a mensch".
+May this dedication serve to hold myself publicly accountable to that.
+Also I love you, mom.
+I dedicate and don't dedicate this and everything to come to you, too.
+\vspace{12pt}
+%\end{center}
+\vfil\null
+\end{dedication}
+
+% You can delete the \clearpage lines if you don't want these to start on
+% separate pages.
+
+\tableofcontents
+\clearpage
+\listoffigures
+\clearpage
+%\listoftables
+
+\begin{acknowledgements}
+I would like to thank: Chris Hillar for laying down the groundwork and vetting all of my proofs many times over.
+He lent me a lot of his time and expertise for little in return.
+Fritz Sommer for advising me and pointing me toward a tractable problem to solve.
+The Berkeley Student Cooperative for the amazing experience living co-operatively in Berkeley.
+CZ or die.
+\end{acknowledgements}
+
+\section{Foreword}
+This thesis presents results published Dec.~2019 in IEEE Transactions on Signal Processing in a paper of the same name, largely verbatim.
+Readers can refer to the Discussion and Future Directions for additional insights not offered in the paper.
+
+\end{frontmatter}
+
+\pagestyle{headings}
+
+% (Optional)
+ \part{Main Text}
 
 \section{Introduction}\label{Intro}
-\IEEEPARstart{S}{parse} coding is a common modern approach to pattern analysis in signal processing whereby each of $N$ observed $n$-dimensional signal samples is viewed as a (noisy) linear combination of at most $k$ elementary waveforms drawn from some unknown ``dictionary" of size $m \ll N$ (see \cite{Zhang15} for a comprehensive review).
+
+%\begin{itemize}
+%\item Background to the topic.
+%\item Brief review of current knowledge.
+%\item Indicate the gap in knowledge. State the aim of the research and how it fits into the gap.
+%\item Can include an outline of what follows.
+%\end{itemize}
+
+%Why do neuroscientists care about dictionary learning?
+
+Sparse coding is a common modern signal processing technique that views each of $N$ observed $n$-dimensional signal samples as a (noisy) linear combination of at most $k$ elementary waveforms drawn from some unknown ``dictionary" of size $m \ll N$ (see \cite{Zhang15} for a comprehensive review).
 %\IEEEPARstart{A}{}common modern approach to pattern analysis in signal processing is to view each of $N$ observed $n$-dimensional signal samples as a (noisy) linear combination of at most $k$ elementary waveforms drawn from some unknown ``dictionary" of size $m \ll N$ (see \cite{Zhang15} for a comprehensive review).
@@
 The technical proofs of Thms.~\ref{DeterministicUniquenessTheorem} and ~\ref{SLCopt} are deferred to Sec.~\ref{DUT}, following some necessary definitions and a fact in combinatorial matrix analysis (Lem.~\ref{MainLemma}; proven in the Appendix).
-Finally, we discuss in Sec.~\ref{Discussion} applications of our mathematical observations as well as open questions.
+We discuss these results and their applications in depth in Sec.~\ref{Discussion} and outline open questions and future research directions in Sec.~\ref{FutureDirections}.
 %The Appendix contains a proof of Lem.~\ref{MainLemma}.
 
+%\chapter{Results}
 \section{Results}\label{Results}
@@
 Given insufficient samples, this argument has some less-than-certain probability of being valid for each $S \in \mathcal{H}$.
-Nonetheless, simulations with small hypergraphs confirm that the probability of success very quickly approaches one once the number of samples $N$ surpasses a small fraction of the deterministic sample complexity.
+Nonetheless, simulations with small hypergraphs demonstrate that successful recovery is nearly certainly even when $N$ is only a fraction of the deterministic sample complexity (see Fig.
+\ref{probpigeon}).
 
@@
 
-A main motivation for this work is the emergence of seemingly unique representations from sparse coding models trained on natural data, despite the varied assumptions underlying the many algorithms in current use.
-Our results constitute an important step toward explaining these phenomena as well as unifying many publications on the topic by deriving general deterministic conditions under which identification of parameters in this model is not only possible but also robust to uncertainty in measurement and model choice.
-
-We have shown that, given sufficient data, the problem of determining a dictionary and sparse codes with minimal support size (Prob.~\ref{OptimizationProblem}) reduces to an instance of Prob.~\ref{InverseProblem}, to which our main result (Thm.~\ref{DeterministicUniquenessTheorem}) applies: every dictionary and sequence of sparse codes consistent with the data are equivalent up to inherent relabeling/scaling ambiguities and a discrepancy (error) that scales linearly with the measurement noise or modeling inaccuracy.
-The constants we provide are explicit and computable; as such, there is an effective procedure that sufficiently affirms if a proposed solution to these problems is indeed unique up to noise and inherent ambiguities, although it is not efficient in general.
-
-%A compelling feature of this model is its simple instantiation of the principle of Occam's razor: a natural video, for instance, is modeled as a linear combination of a small number of spatiotemporal building blocks, each representing an archetypical feature latent in the data.
-
-%For theoretical neuroscience in particular, dictionary learning and related methods have recovered characteristic components of natural images \cite{Olshausen96, hurri1996image, bell1997independent, van1998independent} and sounds \cite{bellsejnowski1996, smithlewicki2006} that reproduce response properties of certain cortical neurons.
+The main motivation for this work is the observation that characteristic sparse representations seem to emerge from sparse coding models trained over a variety of natural scene datasets by a variety of learning algorithms.
+The theorems proven here provide some insight into this phenomenon by establishing very general deterministic conditions under which identification of the model parameters is not only possible but also robust to uncertainty.
+
+The guarantees concerning the identification of a dictionary and corresponding sparse codes of minimal average support size (Thm.~\ref{SLCopt}), which is the optimization problem of most interest to practitioners (Prob.~\ref{OptimizationProblem}), are to my knowledge the first of their kind in both the noise-free and noisy domains.
+It has been shown here that, given sufficient data, this problem reduces to an instance of Prob.~\ref{InverseProblem} to which the main result (Thm.~\ref{DeterministicUniquenessTheorem}) may then be applied: every dictionary and corresponding sparse codes consistent with the data are equivalent up to inherent relabeling/scaling ambiguities and a discrepancy (error) that scales linearly with the measurement noise or modeling inaccuracy.
+In fact, %provided $n \geq \min(2k,m)$, 
+in almost all cases these problems are well-posed given a sufficient amount of data (Thm.~\ref{robustPolythm} and Cor.~\ref{ProbabilisticCor}). 
+Furthermore, the derived scaling constants are explicit and computable; as such, there is an effective procedure that suffices to affirm if a proposed solution to these problems is indeed unique up to noise and inherent ambiguities, although it is not efficient in general.
+%Specifically, given a dictionary and sparse codes purported to solve to Prob.~\ref{InverseProblem}, one checks that that they satisfy the corresponding constraints on $\mathbf{A}$ and the $\mathbf{x_i}$ given in the statement of Thm.~\ref{DeterministicUniquenessTheorem}.
 
@@
 
-%Moreover, we show that even if the meta-parameter for the number of dictionary elements is overestimated, a subset of parameters may still be identifiable up to noise.
-
-Beyond an extension of existing noiseless guarantees \cite{Hillar15} to the noisy regime and their novel application to Prob.~\ref{OptimizationProblem}, our work contains a theory of combinatorial designs for support sets key to identification of dictionaries.
-We incorporate this idea into a fundamental lemma in matrix theory (Lem.~\ref{MainLemma}) that draws upon the definition of a matrix lower bound (\ref{Ldef}) induced by a hypergraph.
-The new insight offered by this combinatorial approach allows for guaranteed recovery of some or all dictionary elements even if: 1) dictionary size is overestimated, 2) data cover only a polynomial number of distinct sparse supports, and 3) dictionaries do not satisfy the spark condition.
-
-The absence of any assumptions about dictionaries solving Prob.~\ref{InverseProblem} was a major technical obstruction in proving Thm.~\ref{DeterministicUniquenessTheorem}.
-We sought such a general guarantee because of the practical difficulty in ensuring that an algorithm maintain a dictionary satisfying the spark condition \eqref{SparkCondition} at each iteration, an implicit requirement of all previous works except \cite{Hillar15}; indeed, even certifying a dictionary has this property is NP-hard \cite{tillmann2014computational}.
-
-One direct application of this work is to theoretical neuroscience, wherein our theorems justify the mathematical soundness of one of the few hypothesized theories of bottleneck communication in the brain \cite{Isely10}: that sparse neural population activity is recoverable from its noisy linear compression through a randomly constructed (but unknown) wiring bottleneck by any biologically plausible unsupervised sparse coding method that solves Prob.~\ref{DeterministicUniquenessTheorem} or \ref{SLCopt} (e.g., \cite{rehnsommer2007, rozell2007neurally, pehlevan2015normative}).\footnote{We refer the reader to \cite{ganguli2012compressed} for more on interactions between dictionary learning and neuroscience.}
-
-In fact, uniqueness guarantees with minimal assumptions apply to all areas of data science and engineering that utilize learned sparse structure.
-For example, several groups have applied compressed sensing to signal processing tasks; for instance, in MRI analysis \cite{lustig2008compressed}, image compression \cite{Duarte08}, and even the design of an ultrafast camera \cite{Gao14}.
-It is only a matter of time before these systems incorporate dictionary learning to encode and decode signals (e.g., in a device that learns structure from motion \cite{kong2016prior}), just as scientists have used sparse coding to make sense of their data \cite{jung2001imaging, agarwal2014spatially, lee2016sparse, wu2016stability}.
-
-Assurances offered by our theorems certify that different devices and algorithms learn equivalent representations given enough data from statistically identical systems.\footnote{To contrast with the current hot topic of ``Deep Learning'', there are few such uniqueness guarantees for these models of data; moreover, even small noise can dramatically alter their output \cite{goodfellow2014explaining}.}
-Indeed, a main reason for the sustained interest in dictionary learning as an unsupervised method for data analysis seems to be the assumed well-posedness of parameter identification in the model, confirmation of which forms the core of our findings.
-
-We close with some challenges left open by our work.
-All conditions stated here guaranteeing the uniqueness and stability of sparse representations have only been shown sufficient; it remains open, therefore, to extend them to necessary conditions, be they on required sample size, the structure of support set hypergraphs, or tolerable error bounds.
-On this last note, we remark that our deterministic treatment considers always the ``worst-case" noise, whereas the ``effective" noise sampled from a concentrated distribution might be significantly reduced, especially for high-dimensional data.
-It would be of great practical benefit to see how drastically all conditions can be relaxed by requiring only probabilistic guarantees in this way, or in the spirit of our discussion on probabilistic pigeonholing to reduce sample complexity (as in the famous ``birthday paradox") following the proof of Thm.~\ref{DeterministicUniquenessTheorem}.
-
-Another interesting question raised by our work is for which special cases is it efficient to check that a solution to Prob.~\ref{InverseProblem} or \ref{OptimizationProblem} is unique up to noise and inherent ambiguities.
-Considering that the sufficient conditions we have described for checking this in general are NP-hard to compute, are the necessary conditions hard?
-Are Probs.~\ref{InverseProblem} and \ref{OptimizationProblem} then also hard (e.g., see \cite{Tillmann15})?
-Finally, since Prob.~\ref{SLCopt} is intractable in general, but efficiently solvable by $\ell_1$-norm minimization when the matrix is known (and has a large enough lower bound over sparse domains \cite{eldar2012compressed}), is there a version of Thm.~\ref{SLCopt} certifying when Prob.~\ref{OptimizationProblem} can be solved efficiently in full by similar means?
+The absence of any assumption at all about dictionaries that solve Prob.~\ref{InverseProblem} was a major technical hurdle. % in proving Thm.~\ref{DeterministicUniquenessTheorem}. 
+This very general guarantee was sought because of the practical difficulty of ensuring that an algorithm maintain a dictionary satisfying the spark condition \eqref{SparkCondition} at each iteration, which (to my knowledge) has been explicitly or implicitly assumed in all previous works except \cite{Hillar15}; indeed, even certifying a dictionary has this property is NP-hard \cite{tillmann2014computational}.
+
+Several results in the literature had to be combined to extend the guarantees derived in \cite{Hillar15} into the noisy regime.
+The main challenge was to generalize Lem.~\ref{MainLemma} to the case where the $k$-dimensional subspaces spanned by corresponding submatrices $\mathbf{A}_S$ and $\mathbf{B}_{\pi(S)}$ are assumed to be``close" but not identical.
+Unlike the inductive argument in \cite{Hillar15} for the noiseless case, here it had to be explicitly demonstrated that this proximity relation is propagated through iterated intersections right down to the spans of the dictionary elements themselves.
+Lem.~\ref{DistanceToIntersectionLemma} was designed to encapsulate this fact, and proven by appeal to a convergence guarantee for an alternating projections algorithm first proposed by von Neumann.
+This result, combined with a little known fact \eqref{eqdim} about the distance metric between subspaces and requiring proof in \cite{Morris10}, constitute the more obscure components of the deduction.
+
+The proof of Lem.~\ref{MainLemma} diverges most significantly from the approach taken in \cite{Hillar15} by way of Lem.~\ref{NonEmptyLemma}, which utilizes a combinatorial design for support sets (the ``singleton intersection property") to reduce the deterministic sample complexity by an exponential factor.
+This constitutes a significant advance toward legitimizing dictionary learning in practice, since data must otherwise exhibit the exponentially many possible $k$-wise combinations of dictionary elements required by (to my knowledge) all previously published results; although an exponential number of samples per support is still required (unless $k$ is held fixed).
+The issue in this case is that the map $\pi:\mathcal{H} \to {[m] \choose k}$ is surjective only when $\mathcal{H}$ is taken to be ${[m] \choose k}$, as assumed in \cite{Hillar15} so as to enable an inductive argument, which freely chooses supports in the codomain of $\pi$ to intersect over $(k-1)$ indices to then map back to some corresponding set of $(k-1)$ indices at the intersection of supports in the domain.
+For $\mathcal{H} \subset {[m] \choose k}$, a bijection between indices had to instead be established here by pigeonholing the image of $\pi$ under constraints imposed by the SIP, which was formulated specifically for this purpose.
+It just so happened that this more general argument for a non-surjective $\pi$ constrained by the SIP applied just as well to the situation where the number of dictionary elements is over-estimated, in which case a one-to-one correspondence can be guaranteed between a subset of columns of $\mathbf{A}$ and $\mathbf{B}$ of a size simply expressed in terms of the width of each matrix and the regularity of $\mathcal{H}$.
+
+One of the mathematically significant achievements in \cite{Hillar15} was to break free from the constraint that the recovery matrix $\mathbf{B}$ satisfy the spark condition in addition to the generating dictionary $\mathbf{A}$.
+%, in contrast to all previously known uniqueness results which (to my knowledge) have all either explicitly or implicitly made this assumption.
+Here, it has been demonstrated that, in fact, even $\mathbf{A}$ need not satisfy the spark condition!
+Rather, $\mathbf{A}$ need only be injective on the union of subspaces with supports forming a regular $k$-uniform hypergraph satisfying the SIP (a distinguishing example is given in Sec.~\ref{Results}).
+This relaxation of constraints inspired the definition of $L_{\mathcal{H}}$ in \eqref{Ldef}, which is a reformulation of the well-known (see footnote \ref{ripfootnote}) restricted matrix lower bound $L_k$ in terms of a hypergraph $\mathcal{H}$, and an interesting object for further study in its own right.
+%(For instance, how hard is it to check that $L_\mathcal{H}(\mathbf{A}) > 0$?)
+%The absence of any restrictions on dictionaries solving Prob.~\ref{InverseProblem} is a major technical obstruction, but highly desirable because of the practical difficulty in ensuring that an algorithm maintain a dictionary satisfying the spark condition \eqref{SparkCondition} at each iteration; indeed, even certifying a dictionary has this property is NP-hard \cite{tillmann2014computational}.
+
+To reiterate, the methods applied here to prove Thm.~\ref{DeterministicUniquenessTheorem} yield the following results beyond a straightforward extension of those in \cite{Hillar15} to the noisy case:
+
+\begin{enumerate}
+\item A reduction in deterministic sample complexity: To identify the $n \times m$ generating dictionary $\mathbf{A}$, it is required in \cite{Hillar15} that $k{m \choose k}$ data points be sampled from each of the ${m \choose k}$ subspaces spanned by subsets of $k$ columns of $\mathbf{A}$.
+It is shown here that in fact it suffices to sample from at most $m$ such subspaces (see Cor.~\ref{DeterministicUniquenessCorollary}); thus, for fixed $k$, the deterministic sample complexity is polynomial in $m$.
+\item An extension of guarantees to the case where the number of dictionary elements is unknown: The results of \cite{Hillar15} only apply to the case where the matrix $\mathbf{B}$ has the same number of columns as $\mathbf{A}$.
+It is shown here that if $\mathbf{B}$ has at least as many columns as $\mathbf{A}$ then it contains (up to noise) a subset of the columns of $\mathbf{A}$.
+\item Looser requirements (no spark condition) on the generating matrix $\mathbf{A}$: Rather, $\mathbf{A}$ need only be injective on the union of subspaces with supports that form a regular uniform hypergraph satisfying the SIP.
+\end{enumerate}
+
+As it seemed to benefit a reviewer of this work, a brief discussion on how the deterministic sample complexity $N = |\mathcal{H}\left[|(k-1){m \choose k} + 1\right]$ derived in this work compares to those listed in the the top two rows listed in Table I of \cite{Hillar15} may be in order.
+To be clear, the theory developed here is strictly more general, since $\mathcal{H}$ can always be taken to be ${[m] \choose k}$.
+The point of difference in this comparison is the assumed set of supports for sparse codes, which is always ${[m] \choose k}$ in \cite{Hillar15}, whereas here it can be assumed to be any regular $k$-uniform hypergraph that satisfies the SIP.
+By row, %, assuming for our results that sufficient data have been sampled from all supports in a hypergraph H satisfying the SIP:
+\begin{enumerate}
+\item[I.] The result here improves upon the listed $k{m \choose k}^2$ by an exponential factor, since for every $k < m$ there exists a regular $k$-uniform hypergraph $\mathcal{H}$ with $|\mathcal{H}| = m$ satisfying the SIP.
+\item[II.] The result here can be stated with certainty, compared to the commensurate listed $(k+1){m \choose k}$ with almost certainty (i.e.
+with probability one).
+The authors in \cite{Hillar15} have applied measure-theoretic arguments to achieve an almost certain result with a reduced sample complexity than that for which certainty can be claimed here by use of combinatorial designs.
+%\item[III.] A direct comparison cannot be made because it is an open question as to the probability that a random set of supports satisfies the SIP.
+This would be an interesting problem for the community to solve; regardless, the result of \cite{Hillar15} is still implied by the more general theory given here.
+%\item[IV.] The result here is $|\mathcal{H}\left[|(k-1){m \choose k} + 1\right]$ with probability one compared to $(k+1){m \choose k}$ with probability one.
+In this case the sample complexity stated in \cite{Hillar15} is marginally better, but it relies on a noise-free technicality unique to their assumption $\mathcal{H} = {m \choose k}$.
+%differs in flavor: their $\mathbf{x_i}$ are assumed to be distributed as $(k+1)$ samples per support for every support of size $k \in [m]$, whereas here it is assumed that $(k-1){m \choose k}$ codes $\mathbf{x_i}$ are distributed over each support in some hypergraph $\mathcal{H}$ satisfying the SIP.
+%\item[V.] Again, a direct comparison cannot be made for the reason stated for row III.
+\end{enumerate}
+
+%Beyond an extension of existing noiseless guarantees \cite{Hillar15} to the noisy regime and their novel application to Prob.~\ref{OptimizationProblem}, this work contains a theory of combinatorial designs for support sets key to identification of dictionaries.
+This idea is incorporated into a fundamental lemma in matrix theory (Lem.~\ref{MainLemma}) that draws upon the definition of a matrix lower bound (\ref{Ldef}) induced by a hypergraph.
+As a consequence of this combinatorial approach, recovery of some or all dictionary elements can be guaranteed even if: i) dictionary size is overestimated, ii) data cover only a polynomial number of distinct sparse supports, and iii) dictionaries do not satisfy the spark condition.
+
+Another reviewer of this work lamented that while the extension from exact recovery to the noisy stability of dictionary learning is significant, the fact that the analysis relies on metrics of the data that are not feasible to compute limits its impact to the scientific community beyond computer science and applied mathematics.
+What sets the main results of this work apart from the vast majority of results in the field is that they are deterministic, and do not depend on any kind of assumption about the particular random distribution from which the sparse supports, coefficients, or dictionary entries are drawn (though Cor.~\ref{ProbabilisticCor} makes a sweeping statement applicable to all continuous distributions).
+Consequently, the inferences of those applying dictionary learning methods to inverse problems in their research is justified only in principle; but this is unavoidably the case for NP-hard problems.
+
+Indeed, theoretical validation makes little practical difference if the methodology is already in widespread use, while practical criteria establishing whether the data models obtained by practitioners are optimal or not would have very high impact.
+To this end, the work has been laid out for those willing to derive statistical criteria for inference with respect to more domain-specific structured dictionaries and codes (i.e.
+estimate $C_1$), and reduced by half for those wishing to prove the consistency of any dictionary learning algorithm (i.e.
+prove convergence to within $\varepsilon(\delta_1,\delta_2)$ given in \eqref{epsdel}).
+%who will derive from our deterministic guarantees the statistical criteria for inference in more domain-specific probabilistic models
+
+Nonetheless, a main reason for the sustained interest in dictionary learning as an unsupervised method for data analysis seems to be the assumed well-posedness of parameter identification in the model, confirmation of which forms the core of these findings.
+Several groups have applied compressed sensing to signal processing tasks; for instance, in MRI analysis \cite{lustig2008compressed}, image compression \cite{Duarte08}, and even the design of an ultrafast camera \cite{Gao14}.
+As uniqueness guarantees with minimal assumptions apply to all areas of data science and engineering that utilize learned sparse structure, it is only a matter of time before these systems incorporate dictionary learning to encode and decode signals (e.g., in a device that learns structure from motion \cite{kong2016prior}), just as scientists have used sparse coding to %make sense of their data \cite{jung2001imaging, agarwal2014spatially, lee2016sparse, wu2016stability}.
+uncover latent structure in data (e.g., forgery detection \cite{hughes2010, olshausen2010applied}; brain recordings \cite{jung2001imaging, agarwal2014spatially, lee2016sparse}; and gene expression \cite{wu2016stability}).
+Assurances offered by these theorems give hope that different devices and algorithms may learn equivalent representations given enough data from statistically identical systems.\footnote{To contrast with the current hot topic of ``Deep Learning'', there are few such uniqueness guarantees for these models of data; moreover, even small noise can dramatically alter their output \cite{goodfellow2014explaining}.}
+
+Within the field of theoretical neuroscience in particular, dictionary learning for sparse coding and related methods have recovered characteristic components of natural images \cite{Olshausen96, hyvarinen1999fast, bell1997independent, van1998independent} and sounds \cite{bellsejnowski1996, smithlewicki2006, Carlson12} that reproduce response properties of cortical neurons.
+The results of this work suggest that this correspondence could be due to the ``universality" of sparse representations in natural data, an early mathematical idea in neural theory \cite{pitts1947}.
+Furthermore, they justify the soundness of one of the few hypothesized theories of bottleneck communication in the brain \cite{Isely10}: that sparse neural population activity is recoverable from its noisy linear compression through a randomly constructed (but unknown) wiring bottleneck by any biologically plausible unsupervised sparse coding method that solves Prob.~\ref{DeterministicUniquenessTheorem} or \ref{SLCopt} (e.g., \cite{rehnsommer2007, rozell2007neurally, pehlevan2015normative}).\footnote{We refer the reader to \cite{ganguli2012compressed} for more on interactions between dictionary learning and neuroscience.}
+
+%The solution to Prob.~\ref{OptimizationProblem}, that of most interest to practitioners of dictionary learning methods, is (to my knowledge) the first of its kind in both the noise-free and noisy domains.
+
+\section{Future Directions}\label{FutureDirections}
+
+There are many challenges left open by this work.
+First and foremost, it should be stressed that all conditions stated here which guarantee the uniqueness and stability of sparse representations have only been shown sufficient; it remains open to work out a set of necessary conditions on all fronts, be it on the number of required samples, the structure of support set hypergraphs, or the tolerable signal-to-noise ratio for a bounded recovery error.
+It is also worth stressing that the deterministic conditions derived here must accommodate always the worst possible cases.
+It would be of great practical benefit to see how drastically all conditions can be relaxed by requiring less-than-certain guarantees, as (for instance) exhibited in the discussion on probabilistic pigeonholing following the proof of Thm.~\ref{DeterministicUniquenessTheorem}.
+In a similar vein, the tolerable signal-to-noise ratio can be reduced by considering the probability that noise sampled from a concentrated isotropic distribution will point in a harmful direction, which may be especially low in high-dimensional spaces for certain hypergraphs.
+
+Another interesting remaining challenge is to work out for which special cases it is efficient to check that a solution to Prob.~\ref{InverseProblem} or \ref{OptimizationProblem} is unique up to noise and inherent ambiguities.
+Considering that the sufficient conditions detailed here are in general NP-hard to compute, are the necessary conditions also NP-hard to compute?
+Are Probs.~\ref{InverseProblem} and \ref{OptimizationProblem} then also NP-hard (e.g., see \cite{Tillmann15})?
+Since Prob.~\ref{SLCopt} is intractable in general, but efficiently solvable by convex relaxation when the matrix $\mathbf{A}$ is known (and has a large enough lower bound over sparse domains \cite{eldar2012compressed}), is there a version of Thm.~\ref{SLCopt} that lays down general conditions under which Prob.~\ref{OptimizationProblem} can be solved efficiently in full by similar means?
 % [*** Incorporate this open problem with more words ***]
 
-We hope these remaining challenges pique the interest of the community to pick up where we have left off and that the theoretical tools showcased here may be of use to this end.
-
-%We close with some challenges left open by our work.
-First, there is the basic problem of proving optimal lower bounds on sufficient sample size $N$ guaranteeing the uniqueness and stability of sparse representations.
-The pigeonholing argument in the proof of Thm.~\ref{DeterministicUniquenessTheorem} is loose in that it assigns to each support $S \in \mathcal{H}$ a corresponding support $\overline S$ without consideration of previously matched pairs; although we doubt tightening in this way will lead to sub-exponential sample sizes.
-Sample complexity will also benefit from lowering the number of required supports, i.e.
-the size of regular uniform hypergraphs satisfying the SIP.
-The regularity requirement on support hypergraphs can be loosened to allow for certain non-regular hypergraphs satisfying constraints on the degree sequence of nodes; though we impose regularity for clarity of exposition.
-It is then natural to ask: what is the smallest hypergraph satisfying the required constraints forgiven $m$ and $k$?
-Finally, the error bounds can be improved by tightening the constant $C_1$, e.g.
-via an improvement in Lemma ?.
-
-%Solving Prob.~\ref{SLCopt} directly is intractable in general since it necessitates, for each proposed dictionary $\mathbf{B}$, a combinatorial search for the supports of the associated sparse codes $\mathbf{\overline x}_i$.
-A common work-around is to convexify the problem (for fixed $\mathbf{B}$) by substituting the norm $\|\cdot\|_0$ with $\|\cdot\|_1$, impelled the fact that matrices $\mathbf{A}$ with large enough $L_{2k}(\mathbf{A})$ induce the same sparse codes via minimization of either norm \cite{?}.
-To this end, the lower bound $L_{2k}(\mathbf{BP}) \geq (L_{2k}(\mathbf{A}) - C_1\varepsilon) / \|\mathbf{D}\|_1$ implied by Thm.~\ref{DeterministicUniquenessTheorem} hints at conditions on the generating dictionary $\mathbf{A}$ and $k$-sparse codes $\mathbf{x}_i$ under which \emph{all} matrices $\mathbf{B}$ (of bounded column-norm) that solve Prob.~\ref{OptimizationProblem} also share this property of $\mathbf{A}$ by virtue of uniqueness and stability.
-One might then imagine an inference procedure whereby sparse codes are inferred via minimization of $\|\cdot\|_1$, but solutions still evaluated by their collective support size, yielding unique optimal solutions to Prob.~\ref{SLCopt} if only constraints could be imposed such that the learning procedure eventually guides $\mathbf{B}$ through an optimal dictionary.
-% (e.g.
-the dictionary is a member of a known finite set).
-
-\textbf{Acknowledgement.} We thank Fritz Sommer and Darren Rhea for early thoughts, and Ian Morris for posting \eqref{eqdim} online.
-
-%\section{EXTRA}
-%An additional consequence of Thm.~\ref{DeterministicUniquenessTheorem} of potential practical relevance to is the implied lower bound $L_{2k}(\mathbf{BPD}) \geq L_{2k}(\mathbf{A}) - C_1\varepsilon$ in the case where $\mathbf{A}$ satisfies \eqref{SparkCondition}.
-Since solving Prob.~\ref{SLCopt} directly requires a combinatorial search over sparse supports for the $\mathbf{\overline x}_i$ for each proposed dictionary $\mathbf{B}$, rendering it intractable in general, a common strategy is to replace the $\ell_0$-norm in \eqref{minsum} with the $\ell_1$-norm, thereby transforming the inference of sparse $\mathbf{\overline x}_i$ for a fixed dictionary $\mathbf{B}$ into a convex optimization solvable by a linear program.
-A major advance in compressive sensing was the discovery that, for fixed $\mathbf{B}$, solutions to \eqref{minsum} using either norm yield the same sparse vectors $\mathbf{\overline x}_i$ (up to noise) provided $L_{2k}(\mathbf{B})$ is large enough \cite{?}.
-What our results hint at are conditions on the generating dictionary $\mathbf{A}$ and $k$-sparse codes $\mathbf{x}_i$ under which \emph{all} matrices $\mathbf{B}$ (of bounded column-norm) that solve Prob.~\ref{OptimizationProblem} also share this property by virtue of uniqueness and stability; that is, conditions which guarantee that the sparse codes $\mathbf{\overline x}_i$ solving Prob.~\ref{OptimizationProblem} also solve the convexified problem when the corresponding dictionary $\mathbf{B}$ is held fixed.
-It remains to determine, however, what practical conditions preclude matrices that don't solve Prob.~\ref{OptimizationProblem} from nonetheless solving the convexified problem.
-%
-%Regardless, an implication of the above observation is that the following algorithm solves Prob.~\ref{OptimizationProblem} without appeal to combinatorial search:
+%Finally, it was noted that the combinatorial approach applied here allows for guaranteed recovery of some or all dictionary elements even if the dictionary is overestimated (i.e.
+$\overline m > m$).
+What if it is underestimated?
+How then would the recovered dictionary elements relate to the original columns of $\mathbf{A}$?
+
+%Our results suggest that this correspondence could be due to the ``universality'' of sparse representations in natural data, an early idea in neural theory \cite{pitts1947}.
+
+I briefly expand on some of these directions below.
+It is my hope that these remaining challenges pique the interest of the community, and that the theoretical tools showcased here can be applied to derive practical guidelines supporting sparse coding analyses.
+
+% THIS SECTION ADDRESSES REVIEWER COMPLAINTS:
+
+\subsection{Signal-to-Noise Ratio}
+
+A concern raised in peer review of this work was the typical size of the constant $C_1$, which sets the tolerable signal-to-noise ratio for dictionary and code recovery up to an acceptable error.
+Referring to the definition of this constant in \eqref{Cdef1}, the reader should note that the denominator involves $L_k$, a standard quantity in the field of compressed sensing (the ``restricted isometry constant", see footnote \ref{ripfootnote}), which is known to be reasonable for many random distributions generating dictionaries $\mathbf{A}$ and sparse codes $\mathbf{x}_i$ \cite{baraniuk2008simple}.
+The numerator $C_2$, on the other hand, incorporates the more obscure quantity $\xi$ defined in \eqref{FriedrichsDefinition}, which is computed from the ``Friedrichs angle" between certain spans of subsets of the columns of $\mathbf{A}$.
+Simulations for small (pseudo-)randomly generated dictionaries $\mathbf{A}$ suggest nonetheless that the constant $C_2$ is likely reasonable in general as well (at least for the case where $m=k^2$ and $\mathcal{H}$ is taken to be the set of rows and columns formed by arranging the elements of $[m]$ in a square grid; see Fig.
+\ref{reasonableC2}).
+These observations motivate the following conjecture:
+
+\begin{conjecture}
+For all $t > 0$,
+\begin{equation*}
+Pr[ \left| C_2- \mathbb{E}[C_2 ] \right| > t] \to 0 \ \ \text{as $k \to \infty$ and $k/m \to 0$} 
+\end{equation*}
+provided the assumptions of Thm. \ref{DeterministicUniquenessTheorem} are satisfied.
+\end{conjecture}
+%Finally, the error bounds can be improved by tightening the constant $C_1$, e.g. via an improvement in Lemma ?.
+%$C_1 = C_1(\mathbf{A}, \mathcal{H}, \{ \mathbf{x_i} \}_{i=0}^N)$
+
+\subsection{Sample Complexity}
+
+It is possible to tighten the pigeonholing argument in the proof of Thm.~\ref{DeterministicUniquenessTheorem} and reduce the deterministic sample complexity without recourse to uncertainty as previously suggested.
+The argument iterates over supports $S \in \mathcal{H}$, in each case determining a corresponding support $\overline S \in {[\overline m] \choose k}$ without consideration of previously matched support pairs; and yet the assumption $L_{2\mathcal{H}}(\mathbf{A}) > 0$ implies that no two supports in $\mathcal{H}$ can map to the same $\overline S$.
+Thus the number of bins to pigeonhole into decreases every iteration, though this is a drop in a bucket of exponential size.
+It would be interesting to see how much the deterministic sample complexity can be reduced by imposing these constraints holistically, given the specific structure of the hypergraph $\mathcal{H}$.
+
+Incidentally, there is also room to breathe in the restrictions on $\mathcal{H}$.
+Already, the results of this work motivate the following question, which is only one among many combinatorial problems brought to mind by the SIP:
+\begin{question}
+Fix integers $m$ and $k < m$. What is the smallest regular hypergraph $\mathcal{H} \subseteq {[m] \choose k}$ satisfying the SIP?
+\end{question}
+
+A close examination of Lemma \ref{NonEmptyLemma} reveals, however, that $\mathcal{H}$ need not be regular so long as it satisfies a constraint on the sequence of node degrees to remain compatible with the iterative argument.
+It is then natural to ask: what are the necessary constraints on $\mathcal{H}$, and what is the smallest hypergraph satisfying these constraints for given $m$ and $k$?
+
+Opening ourselves up to uncertainty, we can furthermore ask:
+\begin{question}\label{probofsip}
+Fix $k < m$. What is the probability that a random subset of ${[m] \choose k}$ contains a regular hypergraph satisfying the SIP?
+\end{question}
+
+We can also elaborate on the probabilistic pigeonholing strategy outlined in the discussion following the proof of Thm.~\ref{DeterministicUniquenessTheorem}.
+The problem is to count the number of ways in which vectors supported in $S \in \mathcal{H}$ can be partitioned among supports $\overline S \in {\overline m \choose k}$ without allocating $k$ or more to any individual $\overline S$ (in which case the logic of the proof stalls; we are interested in the probability that it doesn't).
+These are integer solutions to the problem $\sum_i n_i = N$ subject to $n_i < k$ for all $i$, where $i = 1, \ldots, {\overline m \choose k}$.
+Following verbatim the exposition in \cite{stackexchangeanswer} It appears there is no closed formula for this problem, but the number of solutions can be computed in a number of operations independent of $N$.
+Writing $p = {\overline m \choose k}$, the number is the coefficient of $X^N$ in the polynomial $(1 + X + \ldots + X^{k-1})^p$.
+Written as a rational function of $X$,
+
+\begin{equation*}
+(1 + X + \ldots + X^{k-1})^p = \left(\frac{1 - X^k}{1 - X} \right)^p = \frac{\left(1 - X^k \right)^p}{\left(1 - X\right)^p}
+\end{equation*}
+the coeffiecient of $X^i$ in the numerator is zero unless $i$ is a multiple $qk$ of $k$, in which case it is $(-1)^q{p \choose q}$, and the coefficient of $X^j$ in the inverse of the denominator is $(-1)^j {-p \choose j} = {j + p-1 \choose j}$, which is zero unless $j \geq 0$ and otherwise equal to ${j + p-1 \choose p-1}$.
+It remains to sum over all $i + j = N$, which gives:
+
+\begin{equation*}
+\sum_{q=0}^{\text{min}(p, N/k)} (-1)^q {p \choose q} {N - qk + p - 1 \choose p - 1}
+\end{equation*}
+where the summation is truncated to ensure that $N - qk \geq 0$ (the condition $j \geq 0$) and has at most $p+1 = {\overline m \choose k} + 1$ terms.
+
+The total number of ways to pigeonhole is ${N +p- 1 \choose p - 1}$, and so the probability of full recovery is $\left(1 - (\text{num.
+stalls}) / (\text{num.
+total}) \right)^{|\mathcal{H}|}$ (see Fig.
+\ref{probpigeon}).
+While it may very well be impossible to to exorcise exponentiality from the number of required samples in the deterministic or almost-certain case, the figure suggests it may be possible with high-probability by one way or another.
+Informally,
+
+\begin{question}
+While fixing $k$ yields polynomial deterministic sample complexity in $m$ (see Cor.~\ref{DeterministicUniquenessCorollary}), is there some more general probablistic sense (perhaps for some restricted class of hypergraphs) by which sample complexity is polynomial in both $m$ and $k$?
+\end{question}
+%Referring to Fig.
+\ref{probpigeon}, which computes these probabilities for some small hypergraphs, one is led to wonder if it may be possible to exorcise exponentiality from the sample complexity asymptotically in this way or another.
+
+%\begin{question}
+%Is there a class of hypergraphs $\mathcal{H} = \mathcal{H}(m,k)$ and a polynomial $p(m,k)$ such that $N \geq p(m,k)$ implies successful dictionary and code recovery with a probability approaching one for generic $\mathbf{A}$ and $\mathbf{x}_i$ supported in $\mathcal{H}$ as $m \to \infty$?
+%Is there a class of hypergraphs $\mathcal{H}$ for which a number of samples $N$ polynomial in both $m$ and $k$ suffices to guarantee stable recovery of $\mathbf{A}$ and sparse codes $\mathbf{x}_i$ as $k/m \to 0$?
+%\end{question}
+
+\subsection{Convex Optimization}
+
+A commonly applied workaround to the intractability of Prob.~\ref{SLCopt} (see \cite{tillmann2015computational}) is to swap out the norm $\|\cdot\|_0$ in \eqref{minsum} for $\|\cdot\|_1$, thereby transforms the inference of sparse $\mathbf{\overline x}_i$ for a given $\mathbf{B}$ into a convex optimization solvable by a linear program.
+A major advance in compressive sensing was the discovery that \eqref{minsum} can in fact be solved in this way for fixed $\mathbf{B}$ provided $L_{2k}(\mathbf{B})$ is large enough.
+The current work provides conditions on the generating dictionary $\mathbf{A}$ and $k$-sparse codes $\mathbf{x}_i$ under which \emph{all} matrices $\mathbf{B}$ (of bounded column-norm) that solve Prob.~\ref{OptimizationProblem} have $L_{2k}(\mathbf{B})$ bounded from below; specifically, $L_{2k}(\mathbf{B}) \geq \left(L_{2k}(\mathbf{A}) - C_1\varepsilon \right) / \|\mathbf{D}\|_1$ in the case where $\mathbf{A}$ satisfies \eqref{SparkCondition}.
+Thus, there is some noise bound inside of which all solutions to Prob.~\ref{OptimizationProblem} are solutions to the convexified problem as well.
+It remains to determine which practical constraints would preclude matrices from solving the convexified problem without solving Prob.~\ref{OptimizationProblem}.
+%
+
+% SOLUTION CHECKING ALGORITHM:
 %\begin{enumerate}
-%\item List all matrices $\mathbf{B}$.
-%\item For each matrix $\mathbf{B}$, solve $\mathbf{\overline x}_i = \arg \min \|\mathbf{v}\|_1$ s.t. $\|\mathbf{Bv} - \mathbf{z}_i\| \leq \eta$ for $i = 1, \ldots, N$.
-%\item Quantify the proposed solution $\mathbf{B}$ and $\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N$ as $\rho(\mathbf{B}, \mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N) = \sum_{i=1}^{N} \|\mathbf{\overline x}_i\|_0$.
-%\item Output $\arg \min_{\mathbf{B}, \mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N} \left( \rho \right)$.
-% \end{enumerate}
-
-%Since its inception some twenty years ago, sparse coding has become a standard tool in signal analysis, yielding myriad insights into the structure of natural signals across a variety of scientific domains.
-In this work,
-
-%We make a final remark about the tightness of our results and the computability of our derived constants.
-%We remark that our constants have been derived for deterministic ``worst-case'' noise, whereas the ``effective'' noise might be smaller when sampled from a distribution.
-
-%Our results suggest that this correspondence could be due to the ``universality'' of sparse representations in natural data, an early idea in neural theory \cite{pitts1947}.
-
-% \vspace{-.2 cm}
-
-%\showacknow % Display the acknowledgments section
-
-\bibliographystyle{IEEEtran}
-\bibliography{chazthm_ieee_trans_sig}
-
-% \vspace{-.2 cm}
+ %  \item For each $\mathbf{x_i}$, determine its support $S$ and increment a counter corresponding to that support.
+  % \item For each support $S$ with count greater than $(k-1){m \choose k}$, check the $\mathbf{x_i}$ supported there are in general linear position (i.e.
+the determinant of the matrix having $\mathbf{x}_i$ as its columns is nonzero) and discard $S$ if not.
+ %  \item Check the remaining set of supports satisfies the SIP. 
+  % \item If so, list all of its regular $k$-uniform sub-hypergraphs and discard those for which $L_{2\mathcal{H}}(\mathbf{A}) = 0$. 
+  % \item For each of the remaining hypergraphs, compute the constant $C_1$ from $\mathbf{A}$ and the $\mathbf{x_i}$.% (or for every subset of the  $\mathbf{x_i}$ of size $(k-1){m \choose k}$).
+ %  \item Check that $\varepsilon < L_2(\mathbf{A})$. If yes, the solution is "unique".
+%\end{enumerate}
+
+\begin{figure}\label{probpigeon}
+\begin{center}
+\includegraphics[width=1 \linewidth]{figures/prob_vs_samples.png}
+\caption{Probability of successful dictionary and code recovery (as per Thm.
+\ref{DeterministicUniquenessTheorem}) for a number of samples $N$ given as a fraction of the deterministic sample complexity $N = |\mathcal{H}|[(k-1){m \choose k} + 1]$ when the support set hypergraph $\mathcal{H}$ is the set of $m$ consecutive intervals of length $k$ in a cyclic order on $[m]$.
+Each plot has $k$ ranging from $2$ to $m-1$ (the case $k=1$ requires $N=m$), with lighter grey lines corresponding to larger $k$.
+Successful recovery is nearly certain with far fewer samples than the deterministic sample complexity.
+}
+\vspace{-.6 cm}
+\label{probvsamples}
+\end{center}
+\end{figure}
+
+\begin{figure}\label{reasonableC2}
+\begin{center}
+\includegraphics[width=1 \linewidth]{figures/C2.pdf}
+\caption{Distribution of $C_2(\mathbf{A}, \mathcal{H})$ computed for 1.33x overcomplete generic unit-norm dictionaries $\mathbf{A} \in \mathbb{R}^{n \times m}$ (i.e.
+with $n = 3m/4$) when the support set hypergraph $\mathcal{H}$ consists of the rows and columns formed by arranging  the elements of $[m]$ into a square grid (i.e.
+$m = k^2$).
+The distribution becomes more concentrated as $m$ grows.}
+\vspace{-.6 cm}
+\label{samples_vs_m}
+\end{center}
+\end{figure}
 
@@
 
-%\section{Proofs of Thm.~\ref{robustPolythm} and Cor.~\ref{ProbabilisticCor}}
-
-%\clearpage
-
-%\section{$\ell_1$-norm Extension}
-%
-%\begin{problem}\label{OptimizationProblemL1}
-%Find a matrix $\mathbf{B}$ and vectors \mbox{$\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N \in \mathbb{R}^m$} that solve:
-%\begin{align}\label{minsum}
-%\min \sum_{i = 1}^N \|\mathbf{\overline x}_i\|_1 \ \ 
-%\text{subject to} \ \ \|\mathbf{z}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \eta, \ \text{for all $i$}.
-%\end{align}
-%\end{problem}
-
-%\begin{corollary}\label{SLCopt}
-%Fix $\alpha > 0$ and suppose all of the assumptions of Thm.\ref{DeterministicUniquenessTheorem} hold with the following modifications:
-%\begin{enumerate}
-%\item The coefficients of all $k$-sparse $\mathbf{x}_i$ are drawn from $[-\beta, \beta]$, where $\beta < \frac{\alpha(k+1)}{k}$.
-%\item More than $(k-1){\overline m \choose k} + q$ vectors $\mathbf{x}_i$ are supported in each $S \in \mathcal{H}$, where
-%\[ q = \left[\frac{\alpha}{\beta}(k+1) - k\right]^{-1}k|\mathcal{H}|(k-1){\overline m \choose k-1}. \]
-%\end{enumerate}
-%Then all solutions to Prob.~\ref{OptimizationProblemL1} for which the nonzero elements of all $\mathbf{\overline x}_i$ lie outside $[-\alpha, \alpha]$ necessarily satisfy the implications \eqref{Cstable} and \eqref{b-PDa} of Thm.~\ref{DeterministicUniquenessTheorem}.
-%\end{corollary}
-
-%\begin{proof}[Proof of Cor.~\ref{SLCopt}]
-%We bound the number of $k$-sparse $\mathbf{\overline x}_i$ and then apply Thm.~\ref{DeterministicUniquenessCorollary}.
-First, observe that no more than $(k-1)|\mathcal{H}|$ of the $\mathbf{\overline x}_i$ share a support $\overline S$ of size less than $k$; otherwise, by the pigeonhole principle, at least $k$ of these indices $i$ belong to the same $K \subseteq I(S)$ for some $S \in \mathcal{H}$ and (as argued previously) \eqref{rhs222} follows.
-Since the right-hand side of \eqref{rhs222} is less than one, by \eqref{dimLem} we have the contradiction $k = \dim(\bm{\mathcal{A}}_S) \leq \dim(\bm{\mathcal{B}}_{\overline S}) \leq |\overline S|.$ The total number of $(k-1)$-sparse vectors $\mathbf{\overline x}_i$ can thus not exceed $|\mathcal{H}|(k-1){ \overline m \choose k-1}$.
-
-%Next, observe that the assumptions of the lemma imply:
-%\begin{align*}
-%\alpha \sum_i \|\mathbf{\overline x}_i\|_0 \leq \sum_i \|\mathbf{\overline x}_i\|_1 \leq \sum_i \|\mathbf{x}_i\|_1 \leq \beta \sum_i \|\mathbf{x}_i\|_0.
-%\end{align*}
-
-%We now apply these facts to bound the number of $k$-sparse $\mathbf{\overline x}_i$.
-Let $n_p$ be the number of $\mathbf{\overline x}_i$ with $\|\mathbf{\overline x}_i\|_0 = p$.
-Since the $\mathbf{x}_i$ are all $k$-sparse, we have:
-%\begin{align*}
-%k \sum_{p = 0}^{\overline m} n_p = k N \geq \sum_{i=0}^N \|\mathbf{x}_i\|_0 \geq \frac{\alpha}{\beta} \sum_{i=0}^N \|\mathbf{\overline x}_i\|_0 = \frac{\alpha}{\beta} \sum_{p=0}^{\overline m} p n_p.
-%\end{align*}
-%Hence, 
-%\begin{align*}
-%\left[ \frac{\alpha(k+1)}{\beta} - k\right] \sum_{p = k+1}^{\overline m} n_p 
-%&\leq \sum_{p = k+1}^{\overline m} (\frac{\alpha}{\beta} p-k) n_p
-%\leq \sum_{p = 0}^k (k - \frac{\alpha}{\beta} p)n_p \\
-%&\leq k \sum_{p = 0}^k n_p 
-%\leq k(1-\frac{\alpha}{\beta})n_k + k|\mathcal{H}|(k-1){ \overline m \choose k-1}
-%\end{align*}
-
-%[Shit, we need $\alpha = \beta$.] Therefore, no more than $q$ vectors $\mathbf{\overline x}_i$ are \emph{not} $k$-sparse.
-Since for every $S \in \mathcal{H}$ there are over $(k-1){\overline m \choose k} + q$ vectors $\mathbf{x}_i$ supported there, it follows that more than $(k-1){\overline m \choose k}$ of them have corresponding $\mathbf{\overline x}_i$ that are $k$-sparse.
-The result now follows directly from Thm.~\ref{DeterministicUniquenessCorollary}.
-%\end{proof}
-
-%\pagebreak
-
-%\begin{corollary}\label{SLCoptL1}
-%If all of the assumptions of Thm.\ref{DeterministicUniquenessTheorem} hold, only now with more than $(k-1)\left[ {\overline m \choose k} + |\mathcal{H}|k{\overline m \choose k-1}\right]$ vectors $\mathbf{x}_i$ supported in each $S \in \mathcal{H}$, then every solution to Prob.~\ref{OptimizationProblemL1} for which the average absolute nonzero coefficient of the $\mathbf{\overline x}_i$ is bounded below by that of the $\mathbf{x}_i$ necessarily satisfies the implications \eqref{Cstable} and \eqref{b-PDa} of Thm.~\ref{DeterministicUniquenessTheorem}.
-%\end{corollary}
-
-%\begin{proof}[Proof of Cor.~\ref{SLCoptL1}]
-%Since the average absolute nonzero coefficient of the $\mathbf{x}_i$ is given by $\alpha = \sum_i \|\mathbf{x}_i\|_1 / \sum_i \|\mathbf{x}_i\|_0$, we have:
-%\begin{align*}
-%\alpha \sum_i \|\mathbf{\overline x}_i\|_0 \leq \sum_i \|\mathbf{\overline x}_i\|_1 \leq \sum_i \|\mathbf{x}_i\|_1 = \alpha \sum_i \|\mathbf{x}_i\|_0.
-%\end{align*}
-%
-%and the result follows by the same arguments as in the proof of Cor.~\ref{SLCopt}.
-%\end{proof}
+\printbibliography
 

### 2020-08-04 manuscripts/thesis/code/compute_c2.py

@@ -124,18 +124,12 @@ if __name__ == '__main__':
     """
     """ rows and cols of square grid """
 
-    ks = range(4,7)
-    fig, ax = pp.subplots(len(ks), 1, figsize=(20,10), sharex=True)
-    if len(ks) == 1:
-        ax = [ax]
-    fig.add_subplot(111, frameon=False)
-    pp.tick_params(labelcolor='none', top=False, bottom=False, left=False, right=False)
-    pp.ylabel("Histogram of $C_2(\mathbf{A}, \mathcal{H})$")
+    ks = range(4,12+1)
     for i, k in enumerate(ks):
         print("k=%d" % k)
         # SQUARE
         m = k**2
-        n = (3*m)//4
+        n = m//2#(3*m)//4
         H = square_hypergraph(m, k)
         r = 2 # since SIP satisfied by (row,col) pair
 
@@ -146,18 +140,14 @@ if __name__ == '__main__':
 
         N_per_support = int((k - 1) * choose(m, k, exact=True)) + 1
         N = len(H) * N_per_support
-        num_trials = 10
+        num_trials = 1000
         c2s = np.zeros(num_trials)
         for t in range(num_trials):
             print("Trial %d" % t, end='\r')
             A = np.random.randn(n, m)
             A = np.dot( A, np.diag(1./np.linalg.norm(A, axis=0)) ) # normalize
             c2s[t] = C2(A, H, r)
+            if t % 100 == 0:
+                np.save("./c2s_k=%d_2x" % k, np.sort(c2s[c2s < np.inf])) 
 
-        c2s = np.sort(c2s[c2s < np.inf])
-        c2max = c2s[int(0.95*len(c2s))]
-        ax[i].hist(c2s[c2s<c2max], bins=100)
-        ax[i].legend(["$m=%d$" % m], loc='upper right', handlelength=0, handletextpad=0)
-        pp.savefig('C2.pdf')
-        pp.show()
-        # TODO: do relative histogram so as to share y axis
+        np.save("./c2s_k=%d_2x" % k, np.sort(c2s[c2s < np.inf])) 

### 2020-08-04 manuscripts/thesis/code/plot_c2s.py

@@ -1,0 +1,45 @@
+import matplotlib.pyplot as pp
+import numpy as np
+
+s = 1
+ks = range(5,10+1,s)
+
+#fig, ax = pp.subplots(len(ks), 1, figsize=(20,10), sharex=True)
+#if len(ks) == 1:
+    #ax = [ax]
+#fig.add_subplot(111, frameon=False)
+#pp.tick_params(labelcolor='none', top=False, bottom=False, left=False, right=False)
+#pp.ylabel("Pr[$C_2(\mathbf{A}, \mathcal{H}) = x]$")
+#pp.xlabel("x")
+
+fig, ax = pp.subplots(1,1)#,figsize=(10,20))
+ax = [ax]
+pp.ylabel("Pr[$C_2(\mathbf{A}, \mathcal{H}) = x]$")
+pp.xlabel("x")
+
+
+# set bounds
+c2s = np.load("c2s_k=%d_2x.npy" % ks[0])
+p = 0.3#0.95
+c2max = c2s[int(p*len(c2s))]
+
+for i, k in enumerate(ks[::-1]):
+    m = k**2
+    #c2s = np.load("c2s_k=%d.npy" % k)
+    c2s = np.load("c2s_k=%d_2x.npy" % k)
+    bins = np.linspace(0, c2max, 151)
+    hist, bins = np.histogram(c2s[np.logical_and(c2s>0, c2s<c2max)], bins)
+    hist = hist / hist.sum()
+    j=0
+    ax[j].bar(bins[:-1], hist, width=bins[1]-bins[0], color=str(np.linspace(0,1,(ks[-1]-ks[0])//s+2)[i]))
+    #ax[j].legend(["$m=%d, k=%d$" % (m,k)], loc='upper left', handlelength=0, handletextpad=0)
+    ax[j].spines['right'].set_visible(False)
+    ax[j].spines['top'].set_visible(False)
+    ax[j].set_ylim([0, 0.3])
+    ax[j].set_xlim([0,c2max])
+    ax[j].set_yticks([0, 0.1, 0.2, 0.3])
+    # TODO: do relative histogram so as to share y axis
+
+ax[j].legend(["$m=%d^2$" % k for k in ks[::-1]], loc='upper right')
+pp.savefig('C2_2x.pdf')
+pp.show()

### 2020-08-04 manuscripts/IEEE/chazthm_ieee_trans_sig.tex
title
everything

@@
 \begin{abstract}
-Dictionary learning for sparse linear coding has exposed characteristic properties of natural signals.
-However, a universal theorem guaranteeing the consistency of estimation in this model is lacking.
-Here, we prove that for all diverse enough datasets generated from the sparse coding model, latent dictionaries and codes are uniquely and stably determined up to measurement error.
+Learning optimal dictionaries for sparse coding has exposed characteristic sparse features of many natural signals.
+However, universal conditions guaranteeing the consistency of these learned features in the presence of measurement noise have yet to be stated.
+Here, we prove very generally that optimal dictionaries and sparse codes are uniquely and stably determined up to measurement error for all diverse enough datasets generated by the sparse coding model.
 Applications are given to data analysis, engineering, and neuroscience.
@@
 
-\IEEEPARstart{B}{lind} source separation is a classical problem in signal processing \cite{sato1975method}.
-In one common modern formulation, each of $N$ observed $n$-dimensional signals is a (noisy) linear combination of at most $k$ elementary waveforms drawn from some unknown dictionary of size $m$, typically with $m \ll N$ (see \cite{Zhang15} for a comprehensive review of this and related models).
-Approximating solutions to this sparsity-constrained inverse problem have provided insight into the structure of many signal classes lacking domain-specific formal models (e.g., in vision \cite{wang2015sparse}).
-In particular, it has been shown that response properties of simple-cell neurons in mammalian visual cortex emerge from optimizing a dictionary to represent small patches of natural images \cite{Olshausen96, hurri1996image, bell1997independent, van1998independent}, a major advance in computational neuroscience.
-A curious aspect of this finding is that the latent waveforms (e.g., ``Gabor'' wavelets) estimated from data appear to be canonical \cite{donoho2001can};
-i.e., they are found in learned dictionaries independent of algorithm or image training set.
+% \cite{sato1975method}
+\IEEEPARstart{A}{}common assumption underlying contemporary solutions to problems in signal processing and pattern analysis is that each of $N$ observed $n$-dimensional signal samples is a (noisy) linear combination of at most $k$ elementary waveforms drawn from some unknown ``dictionary" of size $m$, typically with $m \ll N$ (see \cite{Zhang15} for a comprehensive review of this and related models).
+Approximate solutions to this sparsity-constrained inverse problem and related problems have revealed seemingly characteristic structure in signal classes lacking idiosyncratic formal models (e.g., in vision \cite{wang2015sparse}).
+Interestingly, a seminal work in the field demonstrated that dictionaries optimized with respect to small patches of natural images share qualitative similarities with filters fit to the response properties of simple-cell neurons in mammalian visual cortex \cite{Olshausen96, hurri1996image, bell1997independent, van1998independent}, a major result in theoretical neuroscience.
+Moreover, these latent waveforms (e.g., ``Gabor'' wavelets) estimated from data appear to be canonical \cite{donoho2001can}; i.e.
+they appear in dictionaries learned by a variety of algorithms trained with respect to different natural image datasets.
 
-Motivated by these discoveries and earlier work in the theory of neural communication \cite{Isely10}, we address when dictionaries and the sparse representations they induce are uniquely determined by data.
-Answers to this question also have other real-world implications.
-For example, a sparse coding analysis of local painting style can be used for forgery detection \cite{hughes2010}, but only if all dictionaries consistent with training data do not differ appreciably in their ability to sparsely encode new samples.
-Fortunately, algorithms with proven recovery of generating dictionaries under certain 
-conditions have recently been proposed (see \cite[Sec.~I-E]{Sun16} for a summary of the state-of-the-art).
-Few theorems, however, can be cited to explain this uniqueness more broadly; in particular, a universal guarantee in the context of noise has yet to emerge.
+Motivated by these discoveries and earlier work which proposed a theory of communication between sparsely active neural populations contingent on uniqueness \cite{Isely10}, we address when dictionaries and the sparse representations they induce are uniquely determined by data.
+Answers to this question have other practical implications.
+For example, it has been demonstrated that a sparse coding analysis of painting style can detect forgeries \cite{hughes2010}; but this implies all dictionaries consistent with training data generalize in their ability to sparsely encode new samples.
+Fortunately, several algorithms have recently been proposed which provably recover latent dictionaries under idiosyncratic conditions (see \cite[Sec.~I-E]{Sun16} for a summary of the state-of-the-art).
+Few theorems, however, can be cited to explain the consistency of inference under this model of data more broadly; in particular, a universal guarantee of uniqueness and stability in the context of noise has yet to emerge.
 
-Here, we prove very generally that uniqueness and stability is an expected property of the sparse linear coding model. 
-More specifically, dictionaries that preserve sparse codes (e.g., satisfy a ``spark condition'') are identifiable from as few as \mbox{$N = m(k-1){m \choose k} + m$} noisy sparse linear combinations of their columns up to an error that is linear in the noise (Thm.~\ref{DeterministicUniquenessTheorem}).
-In fact, provided $n \geq \min(2k,m)$, in almost all cases the dictionary learning problem is well-posed (as per Hadamard \cite{Hadamard1902}) given enough data (Cor.~\ref{ProbabilisticCor}).
-Moreover, these explicit, algorithm-independent guarantees hold without assuming the recovered matrix satisfies a spark condition, and even when the number $m$ of dictionary elements is unknown.
+Here, we prove very generally that uniqueness and stability of solutions is an expected property of the sparse coding problem described above as well as a related (and perhaps more well-known) optimization problem which asks for a dictionary and set of sparse codes that minimize the mean sparsity of the codes over all data samples.
 
-More formally, let $\mathbf{A} \in \mathbb R^{n \times m}$ be a matrix with columns $\mathbf{A}_j$ ($j = 1,\ldots,m$) and let dataset $Z$ consist of measurements:
+Formally, let $\mathbf{A}$ be a real $n \times m$ matrix with columns $\mathbf{A}_j$ ($j = 1,\ldots,m$) and let dataset $Z$ consist of measurements:
 \begin{align}\label{LinearModel}
@@
 for $k$-\emph{sparse} $\mathbf{x}_i \in \mathbb{R}^m$ having at most $k<m$ nonzero entries and \emph{noise} $\mathbf{n}_i \in \mathbb{R}^n$, with bounded norm $\| \mathbf{n}_i \|_2 \leq  \eta$ representing our combined worst-case uncertainty in  measuring $\mathbf{A}\mathbf{x}_i$.
-The first mathematical problem we address is the following.
+We show that dictionaries $\mathbf{A}$ injective on certain subsets of $k$-sparse codes are identifiable from as few as \mbox{$N = m(k-1){m \choose k} + m$} noisy sparse linear combinations of their columns up to an error that is linear in the noise (Thm.~\ref{DeterministicUniquenessTheorem}).
+Specifically, the first mathematical problem we consider is:
 
-\begin{problem}[Sparse linear coding]\label{InverseProblem}
-Find a matrix $\mathbf{B}$ and $k$-sparse $\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N \in \mathbb{R}^{\overline m}$ with $\|\mathbf{z}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \eta$ for all $i$.
+\begin{problem}\label{InverseProblem}
+Find a real $n \times \overline m$ matrix $\mathbf{B}$ and $k$-sparse $\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N$ satisfying $\|\mathbf{z}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \eta$ for all $i$.
 \end{problem}
 
-Note that any particular solution $(\mathbf{B}; \mathbf{\overline x}_1 \ldots, \mathbf{\overline x}_N)$ to this problem gives rise to an orbit of equivalent solutions $(\mathbf{BPD}; \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_1, \ldots, \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_N)$, where $\mathbf{P}$ is any permutation matrix and $\mathbf{D}$ any invertible diagonal.
-Previous theoretical work addressing the noiseless case $\eta =0$ (e.g., \cite{li2004analysis, Georgiev05, Aharon06, Hillar15}) with $\overline m = m$ has shown that a solution to Prob.~\ref{InverseProblem} (when it exists) is unique up to this  ambiguity provided the $\mathbf{x}_i$ are sufficiently diverse and the matrix $\mathbf{A}$ satisfies the \textit{spark condition}:
+Our claim is that there exist very general conditions under which any such matrix $\mathbf{B}$ always contains a submatrix ``close" to some submatrix of $\mathbf{A}$, and similarly for the sparse codes $\mathbf{\overline x}_i$ and $\mathbf{x}_i$.
+In fact, provided $n \geq \min(2k,m)$, in almost all cases \ref{InverseProblem} is well-posed (as per Hadamard \cite{Hadamard1902}) given enough data (Cor.~\ref{ProbabilisticCor}).
+Importantly, these explicit, universal guarantees apply without the imposition of \emph{any} constraints on the recovered matrix $\mathbf{B}$ (e.g.
+that it, too, satisfy any injectivity criteria) beyond an upper bound on its number of columns, $\overline m$.
+
+We note that any particular solution to Problem \ref{InverseProblem} actually represents an infinity of equivalent solutions $\mathbf{BPD}$ and $\mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_1, \ldots, \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_N$ parametrized by a choice of permutation matrix $\mathbf{P}$ and invertible diagonal matrix $\mathbf{D}$ capturing the sparsity-preserving labeling and scaling ambiguities inherent to the problem statement.
+Previous theoretical work addressing the noiseless case $\eta =0$ (e.g., \cite{li2004analysis, Georgiev05, Aharon06, Hillar15}) with fixed $\overline m = m$ has shown that the solution to Prob.~\ref{InverseProblem}, when it exists, is unique up to these  ambiguities provided the $\mathbf{x}_i$ are sufficiently diverse and the matrix $\mathbf{A}$ satisfies:
 \begin{align}\label{SparkCondition}
@@
 %
-which would be, in any case, necessary for uniqueness of the $\mathbf{x}_i$. Here, we study stability in the practical setting of noise.
+also called the \textit{spark condition}, which in any case is necessary to guarantee the uniqueness of arbitrary sequences of $k$-sparse $\mathbf{x}_i$.
+We generalize these results to the practical setting of additive noise by incorporating a notion of stability with respect to noise.
 
@@
 To see how Def.
-\ref{maindef} directly relates to Prob.
+\ref{maindef} is motivated by Prob.
 \ref{InverseProblem}, suppose that $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$ and fix $\delta_1, \delta_2$ to be the desired recovery accuracy in \eqref{def1}.
-Consider any dataset $Z$ generated as in \eqref{LinearModel} with $\eta \leq \frac{1}{2} \varepsilon(\delta_1, \delta_2)$.
-Then from the triangle inequality, it follows that any matrix $\mathbf{B}$ and $k$-sparse $\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N \in \mathbb{R}^m$ solving Prob.~\ref{InverseProblem} are necessarily within $\delta_1, \delta_2$ of the original dictionary $\mathbf{A}$ and codes $\mathbf{x}_i$, respectively.
+Now, consider any dataset $Z$ generated as in \eqref{LinearModel} with $\eta \leq \frac{1}{2} \varepsilon(\delta_1, \delta_2)$.
+From the triangle inequality, it follows that any $n \times m$ matrix $\mathbf{B}$ and $k$-sparse $\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N$ solving Prob.~\ref{InverseProblem} are necessarily within $\delta_1, \delta_2$ of the original dictionary $\mathbf{A}$ and codes $\mathbf{x}_i$, respectively.
 
@@
 We then prove our main theorem (Thm.~\ref{DeterministicUniquenessTheorem}) in Sec.~\ref{DUT} after stating some additional definitions and lemmas required for the proof, including a useful result in combinatorial matrix analysis (Lem.~\ref{MainLemma}, proven in Appendix).
-We also provide an argument that extends our guarantees to the following more common optimization formulation of the dictionary learning problem (Thm.~\ref{SLCopt}).
+We also provide an argument extending our guarantees to the following more common formulation of the dictionary learning problem as an optimization over model parameters minimizing the total (or equivalently, the mean) number of non-zero entries in the sparse codes (Thm.~\ref{SLCopt}):
 
 \begin{problem}\label{OptimizationProblem}
-Find $\mathbf{B}$ and \mbox{$\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N \in \mathbb{R}^{\overline m}$} that solve:
+Find real $\mathbf{B}$ and \mbox{$\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N$} that solve:
 \begin{align}\label{minsum}
@@
 \end{problem}
-We then sketch proofs of probabilistic extensions of Thm.~\ref{DeterministicUniquenessTheorem} to random data and dictionaries (Thm.~\ref{robustPolythm} and Cor.~\ref{ProbabilisticCor}).
+We then sketch proofs of extensions of Thm.~\ref{DeterministicUniquenessTheorem} to data and dictionaries drawn from a probability distribution (Thm.~\ref{robustPolythm} and Cor.~\ref{ProbabilisticCor}).
 Finally, in Sec.~\ref{Discussion}, we discuss both theoretical and practical applications of our main mathematical findings.
@@
 A set of $k$-sparse vectors is said to be in \emph{general linear position} when any $k$ of them are linearly independent.
-The following is a precise statement of our main result.
-We leave the quantity $C_1 = C_1(\mathbf{A}, \{\mathbf{x}_i\}_{i=1}^N, \mathcal{H})$ undefined until Eq.~\eqref{Cdef1}.
+
+We are now in a position to give a precise statement of our main result, though we will leave the quantity $C_1 = C_1(\mathbf{A}, \{\mathbf{x}_i\}_{i=1}^N, \mathcal{H})$ undefined until Eq.~\eqref{Cdef1}.
 All of our theorems assume matrices consist of real numbers.
@@
 %To be clear, the implication of Thm.~\ref{DeterministicUniquenessTheorem} is that $Y = \{\mathbf{Ax}_1, \ldots, \mathbf{Ax}_N\}$ has a stable $k$-sparse representation in $\mathbb{R}^m$, with \eqref{def1} guaranteed provided $\varepsilon$ in Def.~\ref{maindef} does not exceed:
-In words, Thm.~\ref{DeterministicUniquenessTheorem} says that the smaller the difference $\overline m - m$ between recovery and original latent dictionary sizes, the more columns and coefficients of the original dictionary $\mathbf{A}$ and codes $\mathbf{x}_i$ are contained (up to noise) in the appropriately scaled dictionary $\mathbf{B}$ and codes $\mathbf{\overline x}_i$.
+In words, Thm.~\ref{DeterministicUniquenessTheorem} says that the smaller the difference $\overline m - m$ between the assumed and actual number of latent dictionary elements, the more columns and coefficients of the original dictionary $\mathbf{A}$ and codes $\mathbf{x}_i$ are contained (up to noise) in the appropriately scaled recovered dictionary $\mathbf{B}$ and codes $\mathbf{\overline x}_i$, respectively.
 In the particular case when $\overline m = m$, the theorem directly implies that  $Y = \{\mathbf{Ax}_1, \ldots, \mathbf{Ax}_N\}$ has a stable $k$-sparse representation in $\mathbb{R}^m$, with inequalities \eqref{def1} guaranteed for $\varepsilon$ in Def.~\ref{maindef} given by:
@@
 Note that sparse codes $\mathbf{x}_i$ with a shared support that are in general linear position are straightforward to produce using a ``Vandermonde'' matrix construction (i.e., use the columns of the matrix $[\gamma_{i}^j]_{i,j=1}^{k,N}$, for distinct nonzero $\gamma_i$).
-Thus, the assumptions of Thm.~\ref{DeterministicUniquenessTheorem} are easily met, leading to the following direct application to uniqueness in sparse linear coding.
+Thus, the assumptions of Thm.~\ref{DeterministicUniquenessTheorem} are easily met.
 % (Prob.~\ref{InverseProblem}).
@@
 There are other less direct consequences of Thm.~\ref{DeterministicUniquenessTheorem}.
-For instance, we use it to prove uniqueness for the optimization formulation of sparse linear coding, Prob.~\ref{SLCopt}, the main object of interest for those applying dictionary learning to their data.
+For instance, we use it to prove uniqueness and stability of solutions to Prob.~\ref{SLCopt}, the usual optimization problem of interest for those applying dictionary learning to their data.
 
@@
 
-Thus, choosing the dictionary and codes ``randomly'' almost certainly generates data with a stable sparse representation.
+Thus, drawing the dictionary and sparse codes from any continuous probability distribution almost certainly generates data with a stable sparse representation.
 
-We remark that these results have an important application to theoretical neuroscience by mathematically justifying one of the few hypothesized theories of bottleneck communication between sparsely active neural populations \cite{Isely10}.
+We remark that these results have a potential application to theoretical neuroscience by mathematically justifying one of the few hypothesized theories of bottleneck communication between sparsely active neural populations \cite{Isely10}.
 
 \begin{proposition}\label{neuroprop}
-Sparse neural population activity is recoverable from noisy random linear compression by any method that solves Prob.~\ref{DeterministicUniquenessTheorem} or \ref{SLCopt}; in particular, via biophysically plausible unsupervised sparse linear coding (e.g., \cite{rehnsommer2007, rozell2007neurally, pehlevan2015normative}).
+Sparse neural population activity is recoverable from noisy random linear compression by any method that solves Prob.~\ref{DeterministicUniquenessTheorem} or \ref{SLCopt}; in particular, via biophysically plausible unsupervised sparse coding (e.g., \cite{rehnsommer2007, rozell2007neurally, pehlevan2015normative}).
 \end{proposition}
@@
 
-The goal of this work was to explain the emergence of characteristic representations from sparse linear coding models fit to natural data, despite the varied assumptions underlying the many algorithms in current use.
-To this end, we have taken an important step toward unifying the great number of publications on the topic by demonstrating very general, deterministic conditions under which identification of parameters in this parsimonious model is not only possible but also robust to the inevitable uncertainty permeating measurement and model choice.
+A motivation for this work was the emergence of seemingly characteristic representations from sparse coding models fit to natural data, despite the varied assumptions underlying the many algorithms in current use.
+To this end, we have taken an important step toward unifying the great number of publications on the topic by demonstrating very general, deterministic conditions under which identification of parameters in this model is not only possible but also robust to the inevitable uncertainty permeating measurement and model choice.
 
-Specifically, we have shown that, given sufficient data, the problem of seeking a dictionary and sparse codes with minimal average support size (Prob.~\ref{OptimizationProblem}) reduces to an instance of Prob.~\ref{InverseProblem}, to which our main result (Thm.~\ref{DeterministicUniquenessTheorem}) applies: every dictionary and sparse codes consistent with the data are equivalent up to inherent relabeling/scaling ambiguities and a discrepancy (error) that scales linearly with the measurement noise or modeling inaccuracy.
+We have shown that, given sufficient data, the problem of seeking a dictionary and sparse codes with minimal average support size (Prob.~\ref{OptimizationProblem}) reduces to an instance of Prob.~\ref{InverseProblem}, to which our main result (Thm.~\ref{DeterministicUniquenessTheorem}) applies: every dictionary and sequence of sparse codes consistent with the data are equivalent up to inherent relabeling/scaling ambiguities and a discrepancy (error) that scales linearly with the measurement noise or modeling inaccuracy.
 The constants we provide are explicit and computable; as such, there is an effective procedure that sufficiently affirms if a proposed solution to Probs.~\ref{DeterministicUniquenessTheorem} or \ref{OptimizationProblem} is indeed unique up to noise and inherent ambiguities.
 
-An immediate application of our theoretical work is Prop.~\ref{neuroprop}, which certifies the validity of a theory of neurally-plausible bottleneck communication in the brain: that sparse linear coding in a compressed space of neural activity can recover sparse codes sent through a randomly-constructed (but unknown) noisy wiring bottleneck \cite{Isely10}.\footnote{We refer the reader to \cite{ganguli2012compressed} for more on interactions between dictionary learning and neuroscience.}
+An immediate application of our theoretical work is Prop.~\ref{neuroprop}, which certifies the validity of a theory of biologically-plausible bottleneck communication in the brain: that sparse coding in a compressed space of neural activity can recover sparse codes sent through a randomly-constructed (but unknown) noisy wiring bottleneck \cite{Isely10}.\footnote{We refer the reader to \cite{ganguli2012compressed} for more on interactions between dictionary learning and neuroscience.}
 

### 2020-08-04 manuscripts/IEEE/final_submission.tex
everything

--- 2019-07-30 manuscripts/IEEE/final_submission.tex
@@
-% TODO: 
+% TODO: cite Fritz l0 paper in introduction for seemingly characteristic structure? Use those mentioned in PNAS response?
 % Make L_H a definition..? Change def of L to be 1-norm so we don't need these sqrt k's?
-% C_1 depends on J in Thm 1
-% also in proof of (7) x need not be *any* 2k-sparse vector...can instead restrict to some H...then 2k is restricted to half being on H.
+% When do we have polynomial complexity? Is it worth saying something about this for cyclic order (e.g. convolutions?)
+% mention regularity is probably not necessary
+% have i talked about making deterministic A?
+(see reviewer comment, and comment about easily meeting thm 1 conditions w deterministic construction).
+also after f(A).
+we make L_2k(a) with vandermonde, clarify this is way more than necessary...but it is necessary if we care about sparse coefficient recovery too, which is part of df of stable sparse representation.
+% IS THEOREM 3 AND ITS COROLLARY CORRECTLY STATED??
+% mention use of coherence instead of L_k? for practical criteria?
 
@@
 %\title{When is the dictionary learning problem well-posed?}
-\title{On the uniqueness and stability of dictionaries \\ for sparse representation of noisy signals}
+\title{On the uniqueness and stability of dictionaries for sparse representation of noisy signals}
 %\title{When is the dictionary learning problem for sparse coding well-posed?}
@@
 \begin{abstract}
-%Learning optimal dictionaries for sparse coding has exposed characteristic sparse features of many natural signals.
-However, there are few universal conditions guaranteeing the stability of such features in the presence of noise.
+Learning optimal dictionaries for sparse coding has exposed characteristic sparse features of many natural signals.
+However, universal conditions guaranteeing the stability of these learned features in the presence of measurement noise have yet to be described.
 Here, we prove very generally that optimal dictionaries and sparse codes are unique up to measurement error for all diverse enough datasets generated by the sparse coding model.
 Applications are given to data analysis, engineering, and neuroscience.
-Learning optimal dictionaries for sparse coding has exposed characteristic sparse features of many natural signals.
-However, universal guarantees of the stability of such features in the presence of noise are lacking.
-Here, we provide very general conditions guaranteeing when dictionaries yielding the sparsest encodings are unique and stable with respect to measurement or modeling error.
-We demonstrate that some or all original dictionary elements are recoverable from noisy data even if the dictionary fails to satisfy the spark condition, its size is overestimated, or only a polynomial number of distinct sparse supports appear in the data.
-Importantly, we derive these guarantees without requiring any constraints on the recovered dictionary beyond a natural upper bound on its size.
-Our results also yield an effective procedure sufficient to affirm if a proposed solution to the dictionary learning problem is unique within bounds commensurate with the noise.
-We suggest applications to data analysis, engineering, and neuroscience and close with some remaining challenges left open by our work.
 \end{abstract}
@@
 \section{Introduction}\label{Intro}
-\IEEEPARstart{S}{parse} coding is a common modern approach to pattern analysis in signal processing whereby each of $N$ observed $n$-dimensional signal samples is viewed as a (noisy) linear combination of at most $k$ elementary waveforms drawn from some unknown ``dictionary" of size $m \ll N$ (see \cite{Zhang15} for a comprehensive review).
-%\IEEEPARstart{A}{}common modern approach to pattern analysis in signal processing is to view each of $N$ observed $n$-dimensional signal samples as a (noisy) linear combination of at most $k$ elementary waveforms drawn from some unknown ``dictionary" of size $m \ll N$ (see \cite{Zhang15} for a comprehensive review).
+%\IEEEPARstart{L}{earning} sparse representations of data has become an important step in modern solutions to problems in signal processing and pattern analysis. 
+% \cite{sato1975method}
+\IEEEPARstart{A}{}common modern approach to problems in signal processing and pattern analysis is to view each of $N$ observed $n$-dimensional signal samples as a (noisy) linear combination of at most $k$ elementary waveforms drawn from some unknown ``dictionary" of size $m \ll N$ (see \cite{Zhang15} for a comprehensive review of this and related models).
 Optimizing dictionaries subject to this and related sparsity constraints has revealed seemingly characteristic sparse structure in several signal classes of current interest (e.g., in vision \cite{wang2015sparse}).
+Of particular note are the seminal works in the field \cite{Olshausen96, hurri1996image, bell1997independent, van1998independent}, which demonstrated that such dictionaries optimized with respect to small patches of ``natural" images share qualitative similarities with linear filters fit to the response properties of simple-cell neurons in mammalian visual cortex.
+Curiously, these waveforms (e.g., ``Gabor'' wavelets) appear in dictionaries learned by a variety of sparse coding algorithms trained over different natural image datasets; as such, it appears these latent features may be in some sense canonical \cite{donoho2001can}.
 
-Of particular note are the seminal works in the field \cite{Olshausen96, hurri1996image, bell1997independent, van1998independent}, which discovered that dictionaries optimized for coding small patches of ``natural" images share qualitative similarities with linear filters estimated from response properties of simple-cell neurons in mammalian visual cortex.
-Curiously, these waveforms (e.g., ``Gabor'' wavelets) appear in dictionaries learned by a variety of algorithms trained over different natural image datasets, suggesting that learned features in natural signals may, in some sense, be canonical \cite{donoho2001can}.
-
-Motivated by these discoveries and more recent work relating compressed sensing \cite{eldar2012compressed} to a theory of information transmission through random wiring bottlenecks in the brain \cite{Isely10}, we address when dictionaries for sparse representation are indeed identifiable from data.
-Answers to this question may also have implications in practice wherever an appeal is made to latent sparse structure of data (e.g., forgery detection \cite{hughes2010, olshausen2010applied}; brain recordings \cite{jung2001imaging, agarwal2014spatially, lee2016sparse}; and gene expression \cite{wu2016stability}).
-
-While several algorithms have been recently proposed to provably recover unique dictionaries under specific conditions (see \cite[Sec.~I-E]{Sun16} for a summary of the state-of-the-art), few theorems can be invoked to justify the consistency of inference under this model of data more broadly.
+Motivated by these discoveries and more recent work proposing a theory of information transmission through random wiring bottlenecks in the brain \cite{Isely10}, linked to the young field of ``compressive sensing", we address when optimal dictionaries for sparse representation are indeed identifiable from data.
+Answers to this question may also have implications in practice wherever an appeal is made to the latent sparse structure of data (e.g.
+forgery detection \cite{hughes2010, olshausen2010applied}; brain recordings \cite{jung2001imaging, agarwal2014spatially, lee2016sparse}; and gene expression \cite{wu2016stability}).
+While several algorithms which provably recover unique latent dictionaries under specific conditions have recently been proposed (see \cite[Sec.~I-E]{Sun16} for a summary of the state-of-the-art), few theorems can be invoked to justify the consistency of inference under this model of data more broadly.
 To our knowledge, a universal guarantee of the uniqueness and stability of learned dictionaries and the sparse representations they induce over noisy data has yet to appear in the literature.
@@
 
-Here, we prove very generally that uniqueness and stability is a typical property of sparse dictionary learning.
-More specifically, we show that matrices injective on a sparse domain are identifiable from \mbox{$N = m(k-1){m \choose k} + m$} noisy linear combinations of $k$ of their $m$ columns up to an error that is linear in the noise (Thm.~\ref{DeterministicUniquenessTheorem}).
-In fact, provided $n \geq \min(2k,m)$, in almost all cases the problem is well-posed, as per Hadamard \cite{Hadamard1902}, given a sufficient amount of data (Thm.~\ref{robustPolythm} and Cor.~\ref{ProbabilisticCor}).
-
-Our guarantees also hold for a related (and perhaps more commonly posed, e.g.
-\cite{rehnsommer2007}) optimization problem seeking a dictionary minimizing the average number of elementary waveforms required to reconstruct each sample of the dataset (Thm.~\ref{SLCopt}).
-To practical benefit, our results impose no restrictions on learned dictionaries (e.g., that they, too, be injective over some sparse domain) beyond an upper bound on dictionary size, which is necessary in any case to avoid trivial solutions (e.g., allowing $m = N$).
+Here, we prove very generally that uniqueness and stability is a typical property of the dictionary learning problem described above.
+More specifically,  we show that dictionaries injective on a sparse domain are identifiable from \mbox{$N = m(k-1){m \choose k} + m$} noisy sparse linear combinations of their columns up to an error that is linear in the noise (Thm.~\ref{DeterministicUniquenessTheorem}).
+In fact, provided $n \geq \min(2k,m)$, in almost all cases the problem is well-posed (as per Hadamard \cite{Hadamard1902}) given enough data (Cor.~\ref{ProbabilisticCor}).
+These guarantees also hold for a related (and perhaps more commonly posed) optimization problem which instead seeks a dictionary minimizing the average number of elementary waveforms required to reconstruct each sample of the dataset.
+Importantly, in both cases our explicit, universal guarantees apply without the imposition of \emph{any} constraints on learned dictionaries  (e.g.
+that they, too, be injective over some domain) beyond an upper bound on dictionary size, which is necessary in any case to avoid a trivial solution (e.g.
+allowing for $m = N$ elementary waveforms).
 %That is, every pair of solutions of comparable size has some number of dictionary elements in common (up to noise), and similarly so for the coefficients of sparse codes they induce.
 
-More precisely, let $\mathbf{A} \in \mathbb R^{n \times m}$ be a matrix with columns $\mathbf{A}_j$ ($j = 1,\ldots,m$) and let dataset $Z$ consist of measurements:
+To state things precisely, let $\mathbf{A} \in \mathbb R^{n \times m}$ be a matrix with columns $\mathbf{A}_j$ ($j = 1,\ldots,m$) and let dataset $Z$ consist of measurements:
 \begin{align}\label{LinearModel}
@@
 for $k$-\emph{sparse} $\mathbf{x}_i \in \mathbb{R}^m$ having at most $k<m$ nonzero entries and \emph{noise} $\mathbf{n}_i \in \mathbb{R}^n$, with bounded norm $\| \mathbf{n}_i \|_2 \leq  \eta$ representing our worst-case uncertainty in measuring the product $\mathbf{A}\mathbf{x}_i$.
-We first consider the following formulation of sparse coding.
-%The first mathematical problem we consider is the following.
+The first mathematical problem we consider is:
+
+%
 
 \begin{problem}\label{InverseProblem}
-Find a dictionary matrix $\mathbf{B}$ and $k$-sparse codes $\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N$ that satisfy $\|\mathbf{z}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \eta$ for all $i = 1,\ldots,N$.
+Find a real matrix $\mathbf{B}$ and $k$-sparse $\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N$ that satisfy $\|\mathbf{z}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \eta$ for all $i$.
 \end{problem}
 
-Note that every solution to Prob.~\ref{InverseProblem} represents infinitely many equivalent alternatives $\mathbf{BPD}$ and $\mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_1, \ldots, \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_N$ parametrized by a choice of permutation matrix $\mathbf{P}$ and invertible diagonal matrix $\mathbf{D}$.
-Identifying these ambiguities (labelling and scale) yields a single orbit of solutions represented by any particular set of elementary waveforms (the columns of $\mathbf{B}$) and their associated sparse coefficients (the entries of $\mathbf{\overline x}_i$) that reconstruct each data point $\mathbf{z}_i$.
-
-Previous theoretical work addressing the noiseless case $\eta =0$ (e.g., \cite{li2004analysis, Georgiev05, Aharon06, Hillar15}) for matrices $\mathbf{B}$ having exactly $m$ columns has shown that a solution to Prob.~\ref{InverseProblem}, when it exists, is unique up to such relabeling and rescaling provided the $\mathbf{x}_i$ are sufficiently diverse and $\mathbf{A}$ satisfies the \textit{spark condition}:
+Note that, stated as such, every solution to this problem represents infinitely many equivalent alternatives $\mathbf{BPD}$ and $\mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_1, \ldots, \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_N$ parametrized by a choice of permutation matrix $\mathbf{P}$ and invertible diagonal matrix $\mathbf{D}$.
+Identifying these alternatives identifies a set of elementary waveforms (the columns of $\mathbf{B}$)  up to some arbitrary scale and their associated sparse coefficients (the entries of $\mathbf{x}_i$) for reconstructing each data point $\mathbf{z}_i$.
+Previous theoretical work addressing the noiseless case $\eta =0$ (e.g., \cite{li2004analysis, Georgiev05, Aharon06, Hillar15}) for matrices $\mathbf{B}$ having exactly $m$ columns has shown that the solution to Prob.~\ref{InverseProblem}, when it exists, is unique up to these equivalent labeling and scaling ambiguities provided the $\mathbf{x}_i$ are sufficiently diverse and the matrix $\mathbf{A}$ satisfies the \textit{spark condition}:
 \begin{align}\label{SparkCondition}
@@
 %
-which is necessary to guarantee the uniqueness of arbitrary $k$-sparse $\mathbf{x}_i$.
-We generalize these results to the practical setting  $\eta > 0$ by considering the following natural notion of stability with respect to measurement error.
+which in any case is necessary to guarantee the uniqueness of arbitrary $k$-sparse $\mathbf{x}_i$.
+We generalize these results to the practical setting  $\eta > 0$ by considering a notion of stability with respect to measurement error.
 
@@
 \begin{align*}
-	\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \varepsilon(\delta_1, \delta_2),\ \   \text{for all $i=1,\ldots,N$},
+	\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \varepsilon(\delta_1, \delta_2),\ \ \   \text{for all $i=1,\ldots,N$},
 \end{align*}
@@
 \begin{align}\label{def1}
-\|\mathbf{A}_j - (\mathbf{BPD})_j\|_2 \leq \delta_1 \ \text{and} \ \|\mathbf{x}_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_i\|_1 \leq \delta_2.
+\|\mathbf{A}_j - \mathbf{BPD}_j\|_2 \leq \delta_1 \ \ \text{and} \ \ \|\mathbf{x}_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_i\|_1 \leq \delta_2.
 \end{align}
@@
 To see how Prob.
-\ref{InverseProblem} motivates Def.
-\ref{maindef}, suppose that $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$ and fix $\delta_1, \delta_2$ to be the desired accuracies of recovery in \eqref{def1}.
-Consider any dataset $Z$ generated as in \eqref{LinearModel} with $\eta \leq \frac{1}{2} \varepsilon(\delta_1, \delta_2)$.
-Using the triangle inequality, it follows that any $n \times m$ matrix $\mathbf{B}$ and $k$-sparse $\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N$ solving Prob.~\ref{InverseProblem} are necessarily within $\delta_1$ and $\delta_2$ of the original dictionary $\mathbf{A}$ and codes $\mathbf{x}_1, \ldots, \mathbf{x}_N$, respectively.\footnote{We mention that the different norms in \eqref{def1} reflect the distinct meanings typically ascribed to the dictionary and sparse codes in modeling data.}
+\ref{InverseProblem} motivates this definition, suppose that $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$ and fix $\delta_1, \delta_2$ to be the desired accuracies of recovery in \eqref{def1}.
+Now, consider any dataset $Z$ generated as in \eqref{LinearModel} with $\eta \leq \frac{1}{2} \varepsilon(\delta_1, \delta_2)$.
+It follows from the triangle inequality that any $n \times m$ matrix $\mathbf{B}$ and $k$-sparse $\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N$ solving Prob.~\ref{InverseProblem} are necessarily within $\delta_1$ and $\delta_2$ of the original dictionary $\mathbf{A}$ and codes $\mathbf{x}_1, ..., \mathbf{x}_N$, respectively.\footnote{We should mention the different norms in \eqref{def1} reflect the distinct meanings typically ascribed to the dictionary and sparse codes in modeling data.}
 
-The main result of this work is a very general uniqueness theorem for sparse coding (Thm.~\ref{DeterministicUniquenessTheorem}) directly 
-implying Cor.~\ref{DeterministicUniquenessCorollary}, which guarantees that sparse representations of a dataset $Z$ are unique up to noise whenever generating dictionaries $\mathbf{A}$ satisfy a spark condition on supports and the original sparse codes $\mathbf{x}_i$ are sufficiently diverse (e.g., Fig.~\ref{noisyrecovery}).
-Moreover, we provide an explicit, computable $\varepsilon(\delta_1, \delta_2)$ in (\ref{epsdel}) that is linear in desired accuracy $\delta_1$, and essentially so in $\delta_2$.
-
-In the next section, we give formal statements of these findings.
-We then extend the same guarantees (Thm.~\ref{SLCopt}) to the following alternate formulation of dictionary learning, which minimizes the total number of nonzero entries in sparse codes.
+In the next section, we give precise statements of our main result (Thm.~\ref{DeterministicUniquenessTheorem}), from which we have derived an explicit form for $\varepsilon(\delta_1, \delta_2)$.
+We then extend the same guarantees to the following alternate formulation of the dictionary learning problem as one of minimizing the total (or equivalently, the mean) number of non-zero entries in the sparse codes (Thm.~\ref{SLCopt}):
 
 \begin{problem}\label{OptimizationProblem}
-Find matrices $\mathbf{B}$ and vectors \mbox{$\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N$} solving:
+Find real $\mathbf{B}$ and \mbox{$\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N$} that solve:
 \begin{align}\label{minsum}
-\min \sum_{i = 1}^N \|\mathbf{\overline x}_{i}\|_0 \ \
+\min \sum_{i = 1}^N \|\mathbf{\overline x}_i\|_0 \ \
 \text{subject to} \ \ \|\mathbf{z}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \eta, \ \text{for all $i$}.
@@
 \end{problem}
-
-Our development of Thm.~\ref{DeterministicUniquenessTheorem} is general enough to provide some uniqueness and stability even when generating $\mathbf{A}$ do not fully satisfy (\ref{SparkCondition}) and recovery dictionaries $\mathbf{B}$ have more columns than $\mathbf{A}$.
-Moreover, the approach incorporates a combinatorial theory for designing generating codes that should be of independent interest.
-We also give brief arguments adapting our results to dictionaries and codes drawn from probability distributions (Cor.~\ref{ProbabilisticCor}).
-The technical proofs of Thms.~\ref{DeterministicUniquenessTheorem} and ~\ref{SLCopt} are deferred to Sec.~\ref{DUT}, following some necessary definitions and a fact in combinatorial matrix analysis (Lem.~\ref{MainLemma}; proven in the Appendix).
-Finally, we discuss in Sec.~\ref{Discussion} applications of our mathematical observations as well as open questions.
-%The Appendix contains a proof of Lem.~\ref{MainLemma}.
+We also give brief arguments adapting our results to data and dictionaries drawn from probability distributions (Cor.~\ref{ProbabilisticCor}).
+We defer to Sec.~\ref{DUT} the more technically involved proofs of Thms.~\ref{DeterministicUniquenessTheorem} and ~\ref{SLCopt}, following some necessary definitions and a useful result in combinatorial matrix analysis (Lem.~\ref{MainLemma}).
+Finally, we discuss in Sec.~\ref{Discussion} some theoretical and practical applications of our main mathematical findings.
+The Appendix contains a proof of Lem.~\ref{MainLemma}.
 
@@
 
-Precise statements of our results require that we first identify some combinatorial criteria on the supports\footnote{Recall that a vector $\mathbf{x}$ is said to be \emph{supported} in $S$ when $\mathbf{x} \in \text{\rm span}\{\mathbf{e}_j: j\in S\}$, with $\mathbf{e}_j$ forming the standard column basis.} of sparse vectors.
+A detailed statement of our results requires that we first identify some combinatorial criteria on the supports\footnote{Recall a vector $\mathbf{x}$ is said to be \emph{supported} in $S$ when $\mathbf{x} \in \text{\rm span}\{\mathbf{e}_j: j\in S\}$, the $\mathbf{e}_j$ forming the standard column basis.} of sparse vectors.
 Let $\{1, \ldots, m\}$ be denoted $[m]$, its power set $2^{[m]}$, and ${[m] \choose k}$ the set of subsets of $[m]$ of size $k$.
-A \emph{hypergraph} on vertices $[m]$  is simply any subset $\mathcal{H} \subseteq 2^{[m]}$.
-We say that $\mathcal{H}$ is \textit{$k$-uniform} when $\mathcal{H} \subseteq {[m] \choose k}$.
+A \emph{hypergraph} on vertices $[m]$  is just any subset $\mathcal{H} \subseteq 2^{[m]}$.
+We say $\mathcal{H}$ is \textit{$k$-uniform} when in fact $\mathcal{H} \subseteq {[m] \choose k}$.
 The \emph{degree} $\deg_\mathcal{H}(i)$ of a node $i \in [m]$ is the number of sets in $\mathcal{H}$ that contain $i$, and we say $\mathcal{H}$ is \emph{regular} when for some $r$ we have $\deg_\mathcal{H}(i) = r$ for all $i$ (given such an $r$, we say $\mathcal{H}$ is \textit{$r$-regular}).
 We also write $2\mathcal{H} := \{ S \cup S': S, S' \in \mathcal{H}\}$.
-The following class of structured hypergraphs is a key ingredient in this work.
 
@@
 
-We next give a quantitative generalization of the spark condition (\ref{SparkCondition}) to combinatorial subsets of supports.
-The \emph{lower bound} of an $n \times m$ matrix $\mathbf{M}$ is the largest $\alpha$ with \mbox{$\|\mathbf{M}\mathbf{x}\|_2 \geq \alpha\|\mathbf{x}\|_2$} for all $\mathbf{x} \in \mathbb{R}^m$ \cite{Grcar10}.
-By compactness of the unit sphere, every injective linear map has a positive lower bound; hence, if $\mathbf{M}$ satisfies \eqref{SparkCondition}, then submatrices formed from $2k$ of its columns or less have strictly positive lower bounds.
+Next, we describe a quantitative generalization of the spark condition.
+The \emph{lower bound} of a real $n \times m$ matrix $\mathbf{M}$ is the largest $\alpha$ with \mbox{$\|\mathbf{M}\mathbf{x}\|_2 \geq \alpha\|\mathbf{x}\|_2$} for all $\mathbf{x} \in \mathbb{R}^m$ \cite{Grcar10}.
+By compactness of the unit sphere, every injective linear map has a positive lower bound; hence, if $\mathbf{M}$ satisfies \eqref{SparkCondition} then each submatrix formed from $2k$ of its columns or less has a strictly positive lower bound.
 
-The lower bound of a matrix is generalized below in (\ref{Ldef}) by restricting it to the spans of certain submatrices\footnote{See \cite{vidal2005generalized} for an overview of the related ``union of subspaces" model.} associated with a hypergraph $\mathcal{H} \subseteq {[m] \choose k}$ of column indices.
-Let $\mathbf{M}_S$ denote the submatrix formed by the columns of a matrix $\mathbf{M}$ indexed by $S \subseteq [m]$ (setting $\mathbf{M}_\emptyset := \mathbf{0}$).
-In the sections that follow, we shall also let $\bm{\mathcal{M}}_S$ denote the column-span of a submatrix $\mathbf{M}_S$, and $\bm{\mathcal{M}}_\mathcal{G}$ to denote $\{\bm{\mathcal{M}}_S\}_{S \in \mathcal{G}}$.
-We define:  % Define $L_\mathcal{H}(\mathbf{M})$ as follows:
+We generalize the matrix lower bound for our purposes by considering only the spans of certain submatrices\footnote{See \cite{vidal2005generalized} for an overview of the closely associated ``union of subspaces" model.} associated with a hypergraph $\mathcal{H} \subseteq {[m] \choose k}$ over column indices.
+Letting $\mathbf{M}_S$ denote the submatrix formed by the columns of $\mathbf{M}$ indexed by $S \subseteq [m]$, with $\mathbf{M}_\emptyset := \mathbf{0}$ (in the sections that follow, we will write $\bm{\mathcal{M}}_S$ to denote the column-span of a submatrix $\mathbf{M}_S$, and $\bm{\mathcal{M}}_\mathcal{G}$ to denote $\{\bm{\mathcal{M}}_S\}_{S \in \mathcal{G}}$), we define:
 %\begin{align*} 
@@
 \begin{align}\label{Ldef}
-L_\mathcal{H}(\mathbf{M}) := \min \left\{ \frac{\|\mathbf{M}_S\mathbf{x}\|_2}{ \sqrt{k} \|\mathbf{x}\|_2} : S \in \mathcal{H}, \ \mathbf{0} \neq \mathbf{x} \in \mathbb{R}^{|S|} \right\},
+L_\mathcal{H}(\mathbf{M}) := \frac{1}{\sqrt{k}} \min \left\{ \frac{\|\mathbf{M}_S\mathbf{x}\|_2}{ \|\mathbf{x}\|_2} : S \in \mathcal{H}, \ \ \mathbf{x} \in \mathbb{R}^{|S|} \right\},
 \end{align} 
 %
-writing also $L_{k}$ in place of $L_\mathcal{H}$ when $\mathcal{H} = {[m] \choose k}$.\footnote{In compressed sensing literature, \mbox{$1 - \sqrt{k} L_k(\mathbf{M})$}  is the asymmetric lower restricted isometry constant for $\mathbf{M}$ with unit $\ell_2$-norm columns \cite{Blanchard2011}.}  As explained above, compactness implies that $L_{2k}(\mathbf{M}) > 0$ for all $\mathbf{M}$ satisfying \eqref{SparkCondition}.
-Clearly, $L_{\mathcal{H}'}(\mathbf{M}) \geq L_\mathcal{H}(\mathbf{M})$ whenever $\mathcal{H}' \subseteq \mathcal{H}$, and similarly any $k$-uniform $\mathcal{H}$ satisfying $\cup \mathcal{H} = [m]$ has $L_2 \geq L_{2\mathcal{H}} \geq L_{2k}$ (letting $L_{2k}$ := $L_m$ whenever $2k > m$).
+writing also $L_{k}$ in place of $L_\mathcal{H}$ when $\mathcal{H} = {[m] \choose k}$.\footnote{We note that \mbox{$1 - \sqrt{k} L_k(\mathbf{M})$} is known in the compressive sensing literature as the asymmetric lower restricted isometry constant for matrices $\mathbf{M}$ with unit $\ell_2$-norm columns \cite{Blanchard2011}}  As explained previously, by compactness we have $L_{2k}(\mathbf{M}) > 0$ for all $\mathbf{M}$ satisfying \eqref{SparkCondition}.
+Clearly, $L_{\mathcal{H}'}(\mathbf{M}) \geq L_\mathcal{H}(\mathbf{M})$ whenever $\mathcal{H}' \subseteq \mathcal{H}$ and, by the same token, any $k$-uniform $\mathcal{H}$ satisfying $\cup \mathcal{H} = [m]$ has $L_2 \geq L_{2\mathcal{H}} \geq L_{2k}$.
 
-We are now in a position to state our main result, though for expository purposes we leave the quantity $C_1$ %(a function of $\mathbf{A}$, $\mathbf{x}_1, \ldots, \mathbf{x}_N$, and $\mathcal{H}$) 
-undefined until Sec.~\ref{DUT}. All results  below assume real matrices and vectors.
+Finally, we mention that a set of vectors sharing a support $S$ are said to be in \emph{general linear position} when any $|S|$ of them form a linearly independent set.
+
+We are now in a position to state our main result, though for expository purposes we will leave the quantity $C_1$ (a function of $\mathbf{A}$, $\mathbf{x}_1, ..., \mathbf{x}_N$, and $\mathcal{H}$) undefined until Eq.~\eqref{Cdef1} of Sec.~\ref{DUT}.
+We state here once that all of our theorems assume matrices and vectors consist of real numbers.
 
@@
 \begin{theorem}\label{DeterministicUniquenessTheorem}
-%Fix integers $n, k, m$ and $\overline m$. 
-If an $n \times m$ matrix $\mathbf{A}$ satisfies $L_{2\mathcal{H}}(\mathbf{A}) > 0$ for some $r$-regular $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP, and $k$-sparse \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} include more than $(k-1){\overline m \choose k}$ vectors in general linear position\footnote{Recall that a set of vectors sharing support $S$ are in \emph{general linear position} when any $|S|$ of them are linearly independent.} supported in each $S \in \mathcal{H}$, then the following recovery guarantees hold for $C_1 > 0$ given by \eqref{Cdef1}.
+Fix integers $n, k, m$ and $\overline m$.
+Let the $n \times m$ matrix $\mathbf{A}$ satisfy $L_{2\mathcal{H}}(\mathbf{A}) > 0$ for some $r$-regular $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP.
+If $k$-sparse \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N$} include more than $(k-1){\overline m \choose k}$ vectors in general linear position supported in each $S \in \mathcal{H}$, then there is $C_1 > 0$ (given by \eqref{Cdef1}) for which the following holds for all%\footnote{The condition $\varepsilon < L_2(\mathbf{A}) /C_1$ is necessary; otherwise,  with \mbox{$\mathbf{A}$ = $\mathbf{I}$} and $\mathbf{x}_i = \mathbf{e}_i$, there is a matrix $\mathbf{B}$ and $1$-sparse $\mathbf{\overline{x}}_i$ with $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline{x}}_i \|_2 \leq \varepsilon$ that nonetheless violates \eqref{Cstable}.} $\varepsilon < L_{2}(\mathbf{A}) / C_1$:
+\footnote{Note that the condition $\varepsilon < L_2(\mathbf{A}) /C_1$ is necessary; otherwise, with \mbox{$\mathbf{A}$ = $\mathbf{I}$} (the identity matrix) and $\mathbf{x}_i = \mathbf{e}_i$, the matrix $\mathbf{B} = \left[\mathbf{0}, \frac{1}{2}(\mathbf{e}_1 + \mathbf{e}_2), \mathbf{e}_3, \ldots, \mathbf{e}_{m} \right]$ and sparse codes $\mathbf{\overline x}_i = \mathbf{e}_2$ for $i = 1, 2$ and $\mathbf{\overline x}_i = \mathbf{e}_i$ for $i \geq 3$ satisfy $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline{x}}_i \|_2 \leq \varepsilon$ but nonetheless violate \eqref{Cstable}.} $\varepsilon < L_{2}(\mathbf{A}) / C_1$:
 
-\textbf{Dictionary Recovery:} Fix $\varepsilon < L_{2}(\mathbf{A}) / C_1$.\footnote{Note that the condition $\varepsilon < L_2(\mathbf{A}) /C_1$ is necessary; otherwise, with \mbox{$\mathbf{A}$ = $\mathbf{I}$} (the identity matrix) and $\mathbf{x}_i = \mathbf{e}_i$, the matrix $\mathbf{B} = \left[\mathbf{0}, \frac{1}{2}(\mathbf{e}_1 + \mathbf{e}_2), \mathbf{e}_3, \ldots, \mathbf{e}_{m} \right]$ and sparse codes $\mathbf{\overline x}_i = \mathbf{e}_2$ for $i = 1, 2$ and $\mathbf{\overline x}_i = \mathbf{e}_i$ for $i \geq 3$ satisfy $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline x}_i \|_2 \leq \varepsilon$ but nonetheless violate \eqref{Cstable}.} If an $n \times \overline m$ matrix $\mathbf{B}$ has, for every $i \in [N]$, an associated $k$-sparse $\mathbf{\overline x}_i$ satisfying \mbox{$\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \varepsilon$}, then $\overline m \geq m$, and provided that $\overline m (r-1) < mr$, there is a permutation matrix $\mathbf{P}$ and an invertible diagonal matrix $\mathbf{D}$ such that:
+Every $n \times \overline m$ matrix $\mathbf{B}$ for which there are $k$-sparse $\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N$ satisfying \mbox{$\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \varepsilon$} for $i = 0, \ldots, N$ has $\overline m \geq m$, and provided that $\overline m (r-1) < mr$, we have:
 \begin{align}\label{Cstable}
-\|\mathbf{A}_j- (\mathbf{BPD})_j\|_2 \leq C_1 \varepsilon, \ \ \text{for all } j \in J,
+\|\mathbf{A}_j- \mathbf{BPD}_j\|_2 \leq C_1 \varepsilon \ \ \text{for all } j \in J,
+\end{align}
+for a non-empty $J \subseteq [m]$ of size \mbox{$m - (r-1)(\overline m - m)$}, some permutation matrix $\mathbf{P}$ and an invertible diagonal matrix $\mathbf{D}$.
+%
+% $\overline m - r(\overline m - m)$
+% , t
+
+Moreover, if $\mathbf{A}$ satisfies \eqref{SparkCondition} and $\varepsilon < L_{2k}(\mathbf{A}) / C_1$, then $\mathbf{B}$ also satisfies \eqref{SparkCondition} with $L_{2k}(\mathbf{B}\mathbf{PD}) \geq L_{2k}(\mathbf{A}) - C_1 \varepsilon$ and for all $i \in [N]$:
+\begin{align}\label{b-PDa}
+%\|\mathbf{x}^J_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}^{\overline J}_i\|_1 &\leq  \left( \frac{ 1+C_1 \|\mathbf{x}^{J}_i\|_1 }{ L_{2k}(\mathbf{A}) -  C_1\varepsilon } \right) \varepsilon \ \  \text{for $i \in [N]$}.
+\|(\mathbf{x}_i)_J - (\mathbf{D}^{-1}\mathbf{P}^{\top} \mathbf{\overline x}_i)_J\|_1 &\leq  \left( \frac{ 1+C_1 \|\mathbf{x}_i\|_1 }{ L_{2k}(\mathbf{A}) -  C_1\varepsilon } \right) \varepsilon,
 \end{align}
 %
-for some $J \subseteq [m]$ of size \mbox{$m - (r-1)(\overline m - m)$}. 
-% $\overline m - r(\overline m - m)$
-
-\textbf{Code Recovery:} If, moreover, $\mathbf{A}_J$ satisfies \eqref{SparkCondition} and $\varepsilon < L_{2k}(\mathbf{A}_J) / C_1$, then $(\mathbf{BP})_J$ also satisfies \eqref{SparkCondition} with $L_{2k}(\mathbf{BP}_J) \geq (L_{2k}(\mathbf{A}_J) - C_1 \varepsilon) / \|\mathbf{D}_J\|_1$, and for all $i \in [N]$:
-\begin{align}\label{b-PDa}
-%\|\mathbf{x}^J_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}^{\overline J}_i\|_1 &\leq  \left( \frac{ 1+C_1 \|\mathbf{x}^{J}_i\|_1 }{ L_{2k}(\mathbf{A}) -  C_1\varepsilon } \right) \varepsilon \ \  \text{for $i \in [N]$}.
-\|(\mathbf{x}_i)_J - (\mathbf{D}^{-1}\mathbf{P}^{\top} \mathbf{\overline x}_i)_J\|_1 &\leq  \left( \frac{ 1+C_1 \|(\mathbf{x}_i)_J\|_1 }{ L_{2k}(\mathbf{A}_J) -  C_1\varepsilon } \right) \varepsilon,
-\end{align}
-%
-where subscript $(\cdot)_J$ here represents the subvector formed from restricting to coordinates indexed by $J$.
+where $(\mathbf{x}_i)_J$ here represents the subvector formed from restricting to coefficients indexed by $J$. 
 \end{theorem}
@@
 %To be clear, the implication of Thm.~\ref{DeterministicUniquenessTheorem} is that $Y = \{\mathbf{Ax}_1, \ldots, \mathbf{Ax}_N\}$ has a stable $k$-sparse representation in $\mathbb{R}^m$, with \eqref{def1} guaranteed provided $\varepsilon$ in Def.~\ref{maindef} does not exceed:
-In words, Thm.~\ref{DeterministicUniquenessTheorem} says that the smaller the regularity $r$ of the original support hypergraph $\mathcal{H}$ or the difference $\overline m - m$ between the assumed and actual number of elements in the latent dictionary, the more columns and coefficients of the original dictionary $\mathbf{A}$ and sparse codes $\mathbf{x}_i$ are guaranteed to be contained (up to noise) in the appropriately labelled and scaled recovered dictionary $\mathbf{B}$ and codes $\mathbf{\overline x}_i$, respectively.
-
-In the important special case when $\overline m = m$, the theorem directly implies that  $Y = \{\mathbf{Ax}_1, \ldots, \mathbf{Ax}_N\}$ has a stable $k$-sparse representation in $\mathbb{R}^m$, with inequalities \eqref{def1} guaranteed in Def.~\ref{maindef} for the following worst-case error $\varepsilon$:
+In words, Thm.~\ref{DeterministicUniquenessTheorem} says that the smaller the regularity $r$ of $\mathcal{H}$ or the difference $\overline m - m$ between the assumed and actual number of columns in the latent dictionary, the more columns and coefficients of the original dictionary $\mathbf{A}$ and sparse codes $\mathbf{x}_i$ are guaranteed to be contained (up to noise) in the appropriately scaled recovered dictionary $\mathbf{B}$ and codes $\mathbf{\overline x}_i$, respectively.
+In the particular case when $\overline m = m$, the theorem directly implies that  $Y = \{\mathbf{Ax}_1, \ldots, \mathbf{Ax}_N\}$ has a stable $k$-sparse representation in $\mathbb{R}^m$, with inequalities \eqref{def1} guaranteed for $\varepsilon$ in Def.~\ref{maindef} given by:
 \begin{align}\label{epsdel}
@@
 
-Since sparse codes in general linear position are straightforward to produce with a ``Vandermonde''  construction (i.e., by choosing columns of the matrix $[\gamma_{i}^j]_{i,j=1}^{k,N}$, for distinct nonzero $\gamma_i$), we have the following direct consequence of Thm.~\ref{DeterministicUniquenessTheorem}.
-
-\begin{corollary}\label{DeterministicUniquenessCorollary}
-Given any regular hypergraph $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP, there are $N =  |\mathcal{H}| \left[ (k-1){m \choose k} + 1  \right]$ vectors \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} such that every matrix $\mathbf{A}$ satisfying spark condition \eqref{SparkCondition} generates $Y = \{\mathbf{A}\mathbf{x}_1, \ldots, \mathbf{A}\mathbf{x}_N\}$ with a stable $k$-sparse representation in $\mathbb{R}^m$ for $\varepsilon(\delta_1,\delta_2)$ given by \eqref{epsdel}.
-\end{corollary}
-
-% prev
-%\begin{corollary}\label{DeterministicUniquenessCorollary}
-%Given any regular hypergraph $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP, there are $N =  |\mathcal{H}| \left[ (k-1){m \choose k} + 1  \right]$ vectors \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} such that every matrix $\mathbf{A}$ with $L_{2\mathcal{H}}(\mathbf{A}) > 0$ generates a dataset $Y = \{\mathbf{A}\mathbf{x}_1, \ldots, \mathbf{A}\mathbf{x}_N\}$ with a stable $k$-sparse representation in $\mathbb{R}^m$ for $\varepsilon(\delta_1,\delta_2)$ as in \eqref{epsdel}.
-%\end{corollary}
-
-%We claim that the assumptions of Thm.~\ref{DeterministicUniquenessTheorem} are easily met with deterministic constructions.
+We claim that the assumptions of Thm.~\ref{DeterministicUniquenessTheorem} are easily met with deterministic constructions.
 In particular, sparse codes in general linear position are straightforward to produce using a ``Vandermonde'' matrix construction (i.e.
 use the columns of the matrix $[\gamma_{i}^j]_{i,j=1}^{k,N}$, for distinct nonzero $\gamma_i$).
-%
-
 % (Prob.~\ref{InverseProblem}).
@@
 
+\begin{corollary}\label{DeterministicUniquenessCorollary}
+Given any regular hypergraph $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP, there are $N =  |\mathcal{H}| \left[ (k-1){m \choose k} + 1  \right]$ vectors \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} such that every matrix $\mathbf{A}$ with $L_{2\mathcal{H}}(\mathbf{A}) > 0$ generates a dataset $Y = \{\mathbf{A}\mathbf{x}_1, \ldots, \mathbf{A}\mathbf{x}_N\}$ with a stable $k$-sparse representation in $\mathbb{R}^m$, with $\varepsilon(\delta_1,\delta_2)$ as in \eqref{epsdel}.
+\end{corollary}
 % Needs to be L_{2k}(A) > 0 to guarantee sparse vector recovery
@@
 
-One can easily verify that for every $k < m$ there are regular $k$-uniform hypergraphs $\mathcal{H}$ with the SIP besides the obvious $\mathcal{H} = {[m] \choose k}$.
+One can also easily verify that for every $k < m$ there are regular $k$-uniform hypergraphs with the SIP besides the obvious $\mathcal{H} = {[m] \choose k}$.
 For instance, take $\mathcal{H}$ to be the $k$-regular set of consecutive intervals of length $k$ in some cyclic order on $[m]$.
 In this case, a direct consequence of Cor.~\ref{DeterministicUniquenessCorollary} is rigorous verification of the lower bound \mbox{$N = m(k-1){m \choose k} + m$} for sufficient sample size from the introduction.
-Special cases allow for even smaller hypergraphs.
-For example, if $k = \sqrt{m}$, then a 2-regular $k$-uniform hypergraph with the SIP can be constructed as the $2k$ rows and columns formed by arranging the elements of $[m]$ into a square grid.
+Special cases allow for even smaller hypergraphs, however.
+For example, if $k = \sqrt{m}$ then a 2-regular $k$-uniform hypergraph with the SIP can be constructed as the $2k$ rows and columns formed by arranging the elements of $[m]$ into a square grid.
 
 %\cite{li2004analysis, Georgiev05, Aharon06, Hillar15}
-We should stress here that framing the problem in terms of hypergraphs has allowed us to show, unlike in previous research on the subject, that the matrix $\mathbf{A}$ need not necessarily satisfy \eqref{SparkCondition} to be recoverable from data.
-As an example, let $\mathbf{A} = [ \mathbf{e}_1, \ldots, \mathbf{e}_5, \mathbf{v}]$ with $\mathbf{v} = \mathbf{e}_1 + \mathbf{e}_3 + \mathbf{e}_5$ and take $\mathcal{H}$ to be all consecutive pairs of indices $1, \ldots ,6$ arranged in cyclic order.
-Then for $k=2$, the matrix $\mathbf{A}$ fails to satisfy \eqref{SparkCondition} while still obeying the assumptions of Thm.~\ref{DeterministicUniquenessTheorem} for dictionary recovery.%, hence guaranteeing \eqref{Cstable} .
+We should stress the point here that framing the problem in terms of hypergraphs has allowed us to show, unlike in previous works on the subject, that the matrix $\mathbf{A}$ need not necessarily satisfy \eqref{SparkCondition} to be recoverable from data.
+As an example, let $\mathbf{A} = [ \mathbf{e}_1, \ldots, \mathbf{e}_5, \mathbf{v}]$ with $\mathbf{v} = \mathbf{e}_1 + \mathbf{e}_3 + \mathbf{e}_5$ and take $\mathcal{H}$ to be all consecutive pairs of indices $1, ...
+,6$ arranged in cyclic order.
+Then for $k=2$, the matrix $\mathbf{A}$ fails to satisfy \eqref{SparkCondition} while still satisfying the assumptions of Thm.~\ref{DeterministicUniquenessTheorem}.%, hence guaranteeing \eqref{Cstable} .
 %(since $\{ \mathbf{A}_1, \mathbf{A}_3, \mathbf{A}_5, \mathbf{A}_6\}$ is not a linearly independent set).
@@
 One need simply check that the matrix and codes satisfy the (computable) assumptions of Thm.~\ref{DeterministicUniquenessTheorem} on $\mathbf{A}$ and the $\mathbf{x}_i$.
-In general, however, there is no known efficient procedure.
+In general, however, there is no efficient such procedure.
 We defer a brief discussion on this point to the next section.
@@
 
-A less direct consequence of Thm.~\ref{DeterministicUniquenessTheorem} is the following uniqueness and stability guarantee for solutions to Prob.~\ref{SLCopt}.
-%, the usual optimization problem of interest for those applying dictionary learning to their data.
+A less direct consequence of Thm.~\ref{DeterministicUniquenessTheorem} is the following uniqueness and stability guarantee for solutions to Prob.~\ref{SLCopt}, the usual optimization problem of interest for those applying dictionary learning to their data.
 
 \begin{theorem}\label{SLCopt}
-Fix a matrix $\mathbf{A}$ and vectors $\mathbf{x}_i$ satisfying the assumptions of Thm.~\ref{DeterministicUniquenessTheorem}, only now with over \mbox{$(k-1)\left[ {\overline m \choose k} + |\mathcal{H}|k{\overline m \choose k-1}\right]$} vectors supported in general linear position in each $S \in \mathcal{H}$.
+Fix a matrix $\mathbf{A}$ and vectors $\mathbf{x}_i$ satisfying the assumptions of Thm.~\ref{DeterministicUniquenessTheorem}, only now with over $(k-1)\left[ {\overline m \choose k} + |\mathcal{H}|k{\overline m \choose k-1}\right]$ vectors supported in general linear position in each $S \in \mathcal{H}$.
 Every solution to Prob.~\ref{OptimizationProblem} (with $\eta = \varepsilon/2$) satisfies recovery guarantees \eqref{Cstable} and \eqref{b-PDa} when the corresponding bounds on $\eta$ are met.
@@
 
-\begin{figure}
-\begin{center}
-\includegraphics[width=.24 \linewidth]{figs/Ahat_FastICA_M1280_K8_1.png}
-% \includegraphics[width=.25 \linewidth]{figs/Ahat_FastICA_M640_K8_noise0_2042}
-%\includegraphics[width=.24 \linewidth]{figs/Ahat_FastICA_M640_K8_noise0_4083.png}
-\includegraphics[width=.24 \linewidth]{figs/Ahat_FastICA_M1280_K8_2.png}
-\includegraphics[width=.24 \linewidth]{figs/Ahat_FastICA_M1280_K8_3.png}
-\includegraphics[width=.24 \linewidth]{figs/Ahat_FastICA_M1280_K8_4.png}
-\caption{\textbf{Learning a dictionary from increasingly noisy data}.
-The (unraveled) basis elements of the $8 \times 8$ discrete cosine transform (DCT) form the 64 columns of the left-most matrix above.
-Three increasingly imprecise dictionaries (columns reordered to best match original) are recovered by FastICA \cite{hyvarinen2000independent} trained on data generated from $8$-sparse linear combinations of DCT elements corrupted with additive noise (increasing from left to right).}
-\vspace{-.6 cm}
-\label{noisyrecovery}
-\end{center}
-\end{figure}
-
-Another extension of Thm.~\ref{DeterministicUniquenessTheorem} can be derived from the following algebraic characterization of the spark condition.
-Letting $\mathbf{A}$ be the $n \times m$ matrix of $nm$ indeterminates $A_{ij}$, the reader may work out why substituting real numbers for the $A_{ij}$ yields a matrix satisfying \eqref{SparkCondition} if and only if the following polynomial evaluates to a nonzero number:
+Another extension of Thm.~\ref{DeterministicUniquenessTheorem} can be derived from the following analytic characterization of the spark condition.
+Letting $\mathbf{A}$ be the $n \times m$ matrix of $nm$ indeterminates $A_{ij}$, the reader may work out for themself why substituting real numbers for the $A_{ij}$ yields a matrix satisfying \eqref{SparkCondition} if and only if the following polynomial also evaluates to a nonzero number:
 \begin{align*}
@@
 
-Since $f$ is analytic, having a single substitution of a real matrix $\mathbf{A}$ satisfying $f(\mathbf{A}) \neq 0$ implies that the zeroes of $f$ form a set of (Borel) measure zero.
-Such a matrix is easily constructed by adding rows of zeroes to a $\min(2k,m) \times m$ Vandermonde matrix as mentioned previously, so that every sum in the product defining $f$ above is strictly positive.
-Thus, almost every $n \times m$ matrix with $n \geq \min(2k,m)$ satisfies \eqref{SparkCondition}.
+Since $f$ is analytic, having a single substitution of a real matrix $\mathbf{A}$ satisfy $f(\mathbf{A}) \neq 0$ implies that the zeroes of $f$ form a set of (Borel) measure zero.
+Such a matrix is easily constructed by adding rows of zeroes to any $\min(2k,m) \times m$ Vandermonde matrix as described previously, so that every sum in the product defining $f$ above is strictly positive.
+Almost every $n \times m$ matrix with $n \geq \min(2k,m)$ therefore satisfies \eqref{SparkCondition}.
 
@@
 
-We claim that a similar phenomenon applies to datasets of vectors with a stable sparse representation.
-Briefly, following the same procedure as in \cite[Sec.~IV]{Hillar15}, for $k < m$ and $n \geq \min(2k, m)$, we may consider the ``symbolic'' dataset $Y = \{\mathbf{A}\mathbf{x}_1,\ldots,\mathbf{A} \mathbf{x}_N\}$ generated by an indeterminate $n \times m$ matrix $\mathbf{A}$ and $m$-dimensional $k$-sparse vectors $\mathbf{x}_1, \ldots, \mathbf{x}_N$ indeterminate within their supports, which form a regular hypergraph $\mathcal{H} \subseteq {[m] \choose k}$ satisfying the SIP.
-Restricting \mbox{$(k-1){m \choose k} + 1$} indeterminate $\mathbf{x}_i$ to each support in $\mathcal{H}$, and letting $\textbf{M}$ be the $n \times N$ matrix with columns $\mathbf{A}\mathbf{x}_i$, it can be checked that when $f(\mathbf{M}) \neq 0$ for a substitution of real numbers for the indeterminates, all of the assumptions on $\mathbf{A}$ and the $\mathbf{x}_i$ in Thm.~\ref{DeterministicUniquenessTheorem} are satisfied.
-We therefore have the following.
-% ; in particular, $\mathbf{A}$ satisfies \eqref{SparkCondition}
+We claim a similar phenomenon applies to datasets of vectors with a stable sparse representation.
+Briefly, following the same procedure as in \cite[Sec.~IV]{Hillar15}, for $k < m$ and $n \geq \min(2k, m)$ we may consider the ``symbolic'' dataset $Y = \{\mathbf{A}\mathbf{x}_1,\ldots,\mathbf{A} \mathbf{x}_N\}$ generated by an indeterminate $n \times m$ matrix $\mathbf{A}$ and $m$-dimensional $k$-sparse vectors $\mathbf{x}_1, \ldots, \mathbf{x}_N$ indeterminate within their supports, which form a regular hypergraph $\mathcal{H} \subseteq {[m] \choose k}$ satisfying the SIP.
+Restricting \mbox{$(k-1){m \choose k} + 1$} indeterminate $\mathbf{x}_i$ to each support in $\mathcal{H}$, and letting $\textbf{M}$ be the $n \times N$ matrix with columns $\mathbf{A}\mathbf{x}_i$, it can be checked that when $f(\mathbf{M}) \neq 0$ for a substitution of real numbers for the indeterminates, all of the assumptions on $\mathbf{A}$ and $\mathbf{x}_i$ in Thm.~\ref{DeterministicUniquenessTheorem} are satisfied; in particular, $\mathbf{A}$ satisfies \eqref{SparkCondition}.
+We therefore have the following result:
 
@@
 
-%To extend this observation to arbitrary probability distributions, note that if a set of measure spaces $\{(X_{\ell}, \nu_{\ell})\}_{\ell=1}^p$ has measures $\nu_{\ell}$ absolutely continuous with respect to the standard Borel measure on $\mathbb{R}$ for all $\ell \in [p]$, then the product measure $\prod_{\ell=1}^p \nu_{\ell}$ is also absolutely continuous with respect to the standard Borel product measure on $\mathbb{R}^p$ (e.g., see \cite{folland2013real}).
-This fact combined with Thm.~\ref{robustPolythm} implies the following.
-To extend this observation to arbitrary probability distributions, note that if a set of $p$ measure spaces has all measures absolutely continuous with respect to the standard Borel measure on $\mathbb{R}$, then the product measure is also absolutely continuous with respect to the standard Borel product measure on $\mathbb{R}^p$ (e.g., see \cite{folland2013real}).
-This fact combined with Thm.~\ref{robustPolythm} implies the following.\footnote{We refer the reader to \cite{Hillar15} for a more detailed explanation of these arguments.}
+Note moreover that if a set of measure spaces $\{(X_{\ell}, \Sigma_{\ell}, \nu_{\ell})\}_{\ell=1}^p$ has $\nu_{\ell}$ absolutely continuous with respect to $\mu$ for all $\ell \in [p]$, where $\mu$ is the standard Borel measure on $\mathbb{R}$, then the product measure $\prod_{\ell=1}^p \nu_{\ell}$ is absolutely continuous with respect to the standard Borel product measure on $\mathbb{R}^p$.
+% for space:  (e.g.,  \cite{folland2013real}).
+By Thm.~\ref{robustPolythm}, there is then a polynomial that is nonzero when $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$; in particular, stability holds almost surely and we have the following:
 
 \begin{corollary}\label{ProbabilisticCor}
-If the indeterminate entries of $\mathbf{A}$ and the $\mathbf{x}_i$ are drawn independently from probability distributions absolutely continuous with respect to the standard Borel measure, then $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$ with probability one.
+If the indeterminate entries of $\mathbf{A}$ and the $\mathbf{x}_i$ are drawn independently from probability measures absolutely continuous with respect to the standard Borel measure, then $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$ with probability one.
 \end{corollary}
@@
 We close this section with some comments on the optimality of our results.
-The linear scaling for $\varepsilon$ in \eqref{epsdel} is essentially optimal (e.g., see \cite{arias2013fundamental}), but a basic open problem remains: how many samples are necessary to determine the sparse coding model?
+Our linear scaling for $\varepsilon$ in \eqref{epsdel} is essentially optimal (e.g., see \cite{arias2013fundamental}), but a basic open problem remains: how many samples are necessary to determine the sparse coding model?
 Our results demonstrate that sparse codes $\mathbf{x}_i$ drawn from only a polynomial number of $k$-dimensional subspaces permit stable identification of the generating dictionary $\mathbf{A}$.
-This lends some legitimacy to the use of the model in practice, where data in general are unlikely (if ever) to exhibit the exponentially many possible $k$-wise combinations of dictionary elements required by (to our knowledge) all previously published results.
-
-Consequently, if $k$ is held fixed or if the size of the support set of reconstructing codes is polynomial in $\overline m$ and $k$, then a practical (polynomial) amount of data suffices to identify the dictionary.\footnote{In the latter case, a reexamination of the pigeonholing argument in the proof of Thm.~\ref{DeterministicUniquenessTheorem} requires a polynomial number of samples distributed over a polynomial number of supports.} Reasons to be skeptical that this holds in general, however, can be found in \cite{tillmann2014computational, Tillmann15}.
+This lends some legitimacy to the use of the sparse coding model in practice, where data in general are unlikely (if ever) to exhibit the exponentially many possible $k$-wise combinations of dictionary elements required by (to our knowledge) all previously published results.
+Consequently, if $k$ is held fixed or if the size of the support set of reconstructing codes is known to be polynomial in $\overline m$ and $k$, then a practical (polynomial) amount of data suffices to identify the dictionary.\footnote{In the latter case, a reexamination of the pigeonholing argument in the proof of Thm.~\ref{DeterministicUniquenessTheorem} requires a polynomial number of samples distributed over a polynomial number of supports.} Reasons to be skeptical that this holds in general, however, can be found in \cite{tillmann2014computational, Tillmann15}.
 Even so, in the next section we discuss how probabilistic guarantees can in fact be made for any number of available samples.
@@
 
-% WITH EXPLICIT J SUBSCRIPT
-%We begin our proof of Thm.~\ref{DeterministicUniquenessTheorem} by showing how dictionary recovery \eqref{Cstable} already implies sparse code recovery \eqref{b-PDa} when $\mathbf{A}_J$ satisfies \eqref{SparkCondition} and \mbox{$\varepsilon < L_{2k}(\mathbf{A}_J) / C_1$}.
-%, assuming that $\overline m = m$ without loss of generality.
-%Consider any $2k$-sparse $\mathbf{x} \in \mathbb{R}^m$ and note that $\|\mathbf{x}\|_1 \leq \sqrt{2k}  \|\mathbf{x}\|_2$. By definition of $L_{2k}$ in \eqref{Ldef}, we have:
-%\begin{align}\label{stuff}
-%\|\mathbf{x}_J - &( \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x} )_J\|_1 \nonumber
-%\leq \frac{\|(\mathbf{BPD})_J(\mathbf{x}_J - (\mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x})_J)\|_2}{L_{2k}((\mathbf{BPD})_J)} \\ \nonumber
-%&\leq \frac{\|( (\mathbf{BPD})_J - \mathbf{A}_J) \mathbf{x}_J\|_2 + \|\mathbf{A}_J\mathbf{x}_J - \mathbf{B}_J\mathbf{\overline x}_J\|_2}{L_{2k}((\mathbf{BPD})_J)} \\
-%&\leq \frac{C_1\varepsilon \|\mathbf{x}_J\|_1 + \varepsilon}{L_{2k}((\mathbf{BPD})_J)},
-%\end{align}
-%where the term $C_1\varepsilon \|\mathbf{x}_J\|_1$ in the numerator above is a consequence of the triangle inequality applied to \eqref{Cstable}.
-
-%It remains for us to bound the denominator.  By the reverse triangle inequality:
-%\begin{align*}
-%\|(\mathbf{BPD})_J\mathbf{x}_J\|_2 
-%&\geq | \|\mathbf{A}_J\mathbf{x}_J\|_2 - \|(\mathbf{A}_J - (\mathbf{BPD})_J)\mathbf{x}_J\|_2 | \\
-%&\geq \sqrt{2k} (L_{2k}(\mathbf{A}_J) -  C_1\varepsilon) \|\mathbf{x}_J\|_2,
-%\end{align*}
-%
-%wherein removal of the absolute value is justified since $C_1\varepsilon < L_{2k}(\mathbf{A}_J)$.
-We therefore have that $L_{2k}((\mathbf{BPD})_J) \geq L_{2k}(\mathbf{A}_J) - C_1\varepsilon  > 0$, and \eqref{b-PDa} then follows from \eqref{stuff}.
-
-% WITHOUT J SUBSCRIPT
-We begin our proof of Thm.~\ref{DeterministicUniquenessTheorem} by showing how dictionary recovery \eqref{Cstable} already implies sparse code recovery \eqref{b-PDa} when $\mathbf{A}$ satisfies \eqref{SparkCondition} and \mbox{$\varepsilon < L_{2k}(\mathbf{A}) / C_1$}.
-We temporarily assume (without loss of generality) that $\overline m = m$, so as to omit an otherwise requisite subscript $(\cdot)_J$ around certain matrices and vectors.
-By definition of $L_{2k}$ in \eqref{Ldef}, and noting that $\sqrt{k} \|\mathbf{v}\|_2 \geq \|\mathbf{v}\|_1$ for $k$-sparse $\mathbf{v}$, we have for all $i \in [N[$:
+We begin our proof of Thm.~\ref{DeterministicUniquenessTheorem} by showing how dictionary recovery \eqref{Cstable} already implies sparse code recovery \eqref{b-PDa} when $\mathbf{A}$ satisfies \eqref{SparkCondition} and \mbox{$\varepsilon < L_{2k}(\mathbf{A}) / C_1$}, assuming for this purpose that $\overline m = m$ without loss of generality.
+Consider any $2k$-sparse $\mathbf{x} \in \mathbb{R}^m$ and note that $\|\mathbf{x}\|_1 \leq \sqrt{2k}  \|\mathbf{x}\|_2$.
+By definition of $L_{2k}$ in \eqref{Ldef}, we have:
 \begin{align}\label{stuff}
@@
 &\leq \frac{\|\mathbf{BPD}(\mathbf{x}_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_i)\|_2}{L_{2k}(\mathbf{BPD})} \\ \nonumber
-&\leq \frac{\|( \mathbf{BPD} - \mathbf{A}) \mathbf{x}_i\|_2 + \|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline x}_i\|_2}{L_{2k}(\mathbf{BPD})} \\
+&\leq \frac{\|(\mathbf{BPD} - \mathbf{A})\mathbf{x}_i\|_2 + \|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline x}_i\|_2}{L_{2k}(\mathbf{BPD})} \\
 &\leq \frac{C_1\varepsilon \|\mathbf{x}_i\|_1 + \varepsilon}{L_{2k}(\mathbf{BPD})},
 \end{align}
-%\begin{align}\label{stuff}
-%\frac{ \|\mathbf{x} - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x} \|_1 } { \|\mathbf{D}^{-1}\|_1 }  \
-%&\leq \|\mathbf{Dx} - \mathbf{P}^{\top}\mathbf{\overline x} \|_1 \\ \nonumber
-%&\leq \frac{\|\mathbf{BP}(\mathbf{D}\mathbf{x} - \mathbf{P}^{\top}\mathbf{\overline x})\|_2}{L_{2k}(\mathbf{BP})} \\ \nonumber
-%&\leq \frac{\|( \mathbf{BPD} - \mathbf{A}) \mathbf{x}\|_2 + \|\mathbf{A}\mathbf{x} - \mathbf{B}\mathbf{\overline x}\|_2}{L_{2k}(\mathbf{BP})} \\
-%&\leq \frac{C_1\varepsilon \|\mathbf{x}\|_1 + \varepsilon}{L_{2k}(\mathbf{BP})},
-%\end{align}
-where the first term in the numerator above follows from the triangle inequality and \eqref{Cstable}.
+where the term $C_1\varepsilon \|\mathbf{x}\|_1$ in the numerator above follows from the triangle inequality applied to \eqref{Cstable}.
 
-It remains for us to bound the denominator. For any $2k$-sparse $\mathbf{x}$, we have by the triangle inequality:
+It remains for us to bound the denominator.  By the reverse triangle inequality:
 \begin{align*}
 \|\mathbf{BPD}\mathbf{x}\|_2 
-&\geq \|\mathbf{A}\mathbf{x}\|_2 - \|(\mathbf{A} - \mathbf{BPD})\mathbf{x}\|_2 \\
+&\geq | \|\mathbf{A}\mathbf{x}\|_2 - \|(\mathbf{A}-\mathbf{BPD})\mathbf{x}\|_2 | \\
 &\geq \sqrt{2k} (L_{2k}(\mathbf{A}) -  C_1\varepsilon) \|\mathbf{x}\|_2,
 \end{align*}
-
-%\begin{align*}
-%\|\mathbf{BP}\mathbf{x}\|_2 
-%&\geq \|\mathbf{A}\mathbf{D}^{-1}\mathbf{x}\|_2 - \|(\mathbf{A} - \mathbf{BPD})\mathbf{D}^{-1}\mathbf{x}\|_2 \\
-%&\geq \sqrt{2k} (L_{2k}(\mathbf{A}) -  C_1\varepsilon) \|\mathbf{D}^{-1}\mathbf{x}\|_2, \\ 
-%&\geq \sqrt{2k} (L_{2k}(\mathbf{A}) -  C_1\varepsilon) \|\mathbf{D}^{-1}\|_{?} \| \mathbf{x}\|_2,
-%\end{align*}
 %
+wherein removal of the absolute value is justified because of $C_1\varepsilon < L_{2k}(\mathbf{A})$.
 We therefore have that $L_{2k}(\mathbf{BPD}) \geq L_{2k}(\mathbf{A}) - C_1\varepsilon  > 0$, and \eqref{b-PDa} then follows from \eqref{stuff}.
-The reader may also verify that $L_{2k}(\mathbf{BP}) \geq L_{2k}(\mathbf{BPD}) / \|\mathbf{D}\|_1$.
 
@@
 Since the only 1-uniform hypergraph with the SIP is $[m]$, which is obviously regular, we require only $\mathbf{x}_i = c_i \mathbf{e}_i$ for $i \in [m]$, with $c_i \neq 0$ to guarantee  linear independence.
-While we have yet to define $C_1$ generally, in this case we may set $C_1 = 1/ \min_{\ell \in [m]} |c_{\ell}|$ so that $\varepsilon < L_2(\mathbf{A})  \min_{\ell \in [m]} |c_{\ell}|$.
+While we have yet to define $C_1$ in general, in this case we may set $C_1 = 1/ \min_{\ell \in [m]} |c_{\ell}|$ so that $\varepsilon < L_2(\mathbf{A})  \min_{\ell \in [m]} |c_{\ell}|$.
 
-Fix $\mathbf{A} \in \mathbb{R}^{n \times m}$ satisfying $L_2(\mathbf{A}) > 0$, since here we have $2\mathcal{H} = {[m] \choose 2}$, and suppose some $\mathbf{B}$ and $1$-sparse $\mathbf{\overline x}_i \in \mathbb{R}^{\overline m}$ have  $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \varepsilon < L_2(\mathbf{A}) / C_1$ for all $i$.
-Then, there exist $\overline{c}_1, \ldots, \overline{c}_m \in \mathbb{R}$ and a map $\pi: [m] \to [\overline m]$ such that:
+Fix $\mathbf{A} \in \mathbb{R}^{n \times m}$ satisfying $L_2(\mathbf{A}) > 0$, since here we have $2\mathcal{H} = {[m] \choose 2}$, and suppose that for some $\mathbf{B}$ and $1$-sparse $\mathbf{\overline x}_i \in \mathbb{R}^{\overline m}$ we have  $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \varepsilon < L_2(\mathbf{A}) / C_1$ for all $i$.
+Then there exist $\overline{c}_1, \ldots, \overline{c}_m \in \mathbb{R}$ and a map $\pi: [m] \to [\overline m]$ such that:
 \begin{align}\label{1D}
-\|c_i\mathbf{A}_i - \overline{c}_i\mathbf{B}_{\pi(i)}\|_2 \leq \varepsilon,\ \ \text{for $i \in [m]$}.
+\|c_j\mathbf{A}_j - \overline{c}_j\mathbf{B}_{\pi(j)}\|_2 \leq \varepsilon,\ \ \text{for $j \in [m]$}.
 \end{align} 
-Note that $\overline{c}_i \neq 0$, since otherwise we would reach the following contradiction: $\|\mathbf{A}_i \|_2 \leq C_1 |c_i| \|\mathbf{A}_i \|_2  \leq C_1\varepsilon < L_2(\mathbf{A}) \leq L_1(\mathbf{A}) = \min_{i \in [m]} \|\mathbf{A}_{i}\|_2$.
-%implies by \eqref{delrho} the contradiction $|c_i| < \min_{\ell \in [m]} | c_\ell |$.
+Note that $\overline{c}_j \neq 0$, since otherwise we would reach the contradiction $\|\mathbf{A}_j \|_2 \leq C_1 |c_j| \|\mathbf{A}_j \|_2  \leq C_1\varepsilon < L_2(\mathbf{A}) \leq L_1(\mathbf{A}) = \min_{j \in [m]} \|\mathbf{A}_{j}\|_2$.
+%implies by \eqref{delrho} the contradiction $|c_j| < \min_{\ell \in [m]} | c_\ell |$.
 
@@
 Suppose that $\pi(i) = \pi(j) = \ell$ for some $i \neq j$ and $\ell$.
-Then, $\|c_{i}\mathbf{A}_{i} - \overline{c}_{i} \mathbf{B}_{\ell}\|_2  \leq \varepsilon$ and $\|c_{j}\mathbf{A}_{j} - \overline{c}_{j}\mathbf{B}_{\ell}\|_2 \leq \varepsilon$, and we have: %Scaling and summing these inequalities by $|\overline{c}_{i}|$ and $|\overline{c}_{j}|$, respectively, and applying the triangle inequality to annihilate the terms in $\mathbf{B}_\ell$, we obtain:
+Then $\|c_{j}\mathbf{A}_{j} - \overline{c}_{j}\mathbf{B}_{\ell}\|_2 \leq \varepsilon$ and $\|c_{i}\mathbf{A}_{i} - \overline{c}_{i} \mathbf{B}_{\ell}\|_2  \leq \varepsilon$, and we have: %Scaling and summing these inequalities by $|\overline{c}_{i}|$ and $|\overline{c}_{j}|$, respectively, and applying the triangle inequality to annihilate the terms in $\mathbf{B}_\ell$, we obtain:
 \begin{align*}
@@
 &\geq \|\mathbf{A}(\overline{c}_{i}c_{j} \mathbf{e}_{j} - \overline{c}_{j}c_{i}\mathbf{e}_{i})\|_2 \nonumber \\ 
-&\geq \sqrt{2}  L_2(\mathbf{A}) \|\overline{c}_{i}c_{j} \mathbf{e}_{j} - \overline{c}_{j}c_{i}\mathbf{e}_{i}\|_2 \nonumber \\
+&\geq  L_2(\mathbf{A}) \|\overline{c}_{i}c_{j} \mathbf{e}_{j} - \overline{c}_{j}c_{i}\mathbf{e}_{i}\|_2 \nonumber \\
 &\geq  L_2(\mathbf{A}) \left( |\overline{c}_{i}| + |\overline{c}_{j}| \right) \min_{\ell \in [m]} |c_\ell |,
 \end{align*}
-contradicting our assumed upper bound on $\varepsilon$. Hence, the map $\pi$ is injective and so $\overline m \geq m$. %Setting $\overline J = \pi([m])$ and
-
-Letting $\mathbf{P}$ and $\mathbf{D}$ be the $\overline m \times \overline m$ permutation and invertible diagonal matrices with, respectively, columns $\mathbf{e}_{\pi(i)}$ and $\frac{\overline{c}_i}{c_i}\mathbf{e}_i$ for $i \in [m]$ (otherwise, $\mathbf{e}_{i}$ for $i \in [\overline{m}] \setminus [m]$), we may rewrite \eqref{1D} to see that for all $i \in [m]$:
+contradicting our assumed upper bound on $\varepsilon$. Hence, the map $\pi$ is injective and it must be the case that $\overline m \geq m$. %Setting $\overline J = \pi([m])$ and 
+Letting $\mathbf{P}$ and $\mathbf{D}$ be the $\overline m \times \overline m$ permutation and invertible diagonal matrices with, respectively, columns $\mathbf{e}_{\pi(j)}$ and $\frac{\overline{c}_j}{c_j}\mathbf{e}_j$ for $j \in [m]$ (and, say, $\mathbf{e}_j$ otherwise), we may rewrite \eqref{1D} to see that for all $j \in [m]$:
 \begin{align*}
-\|\mathbf{A}_i - (\mathbf{BPD})_i\|_2 
-= \|\mathbf{A}_i - \frac{\overline{c}_i}{c_i}\mathbf{B}_{\pi(i)}\|_2 
-\leq \frac{\varepsilon}{|c_i|} 
+\|\mathbf{A}_j - \mathbf{BPD}_j\|_2 
+= \|\mathbf{A}_j - \frac{\overline{c}_j}{c_j}\mathbf{B}_{\pi(j)}\|_2 
+\leq \frac{\varepsilon}{|c_j|} 
 \leq C_1\varepsilon.
@@
 
-An extension of the proof to the general case $k < m$ requires some additional tools to derive the general expression \eqref{Cdef1} for $C_1$.
-These include a generalized notion of distance (Def.~\ref{dDef}) and angle (Def.~\ref{FriedrichsDefinition}) between subspaces as well as a stability result in combinatorial matrix analysis (Lem.~\ref{MainLemma}).
+An extension of the proof to the general case $k < m$ requires that we introduce some additional tools which we have used to derive  our general expression \eqref{Cdef1} for the constant $C_1$.
+These including a generalized notion of distance (Def.~\ref{dDef}) and angle (Def.~\ref{FriedrichsDefinition}) between subspaces as well as a stability result in combinatorial matrix analysis (Lem.~\ref{MainLemma}).
 
@@
 \end{align}
-From \cite[Ch.~4 Cor.~2.6]{Kato2013}, we also have: %Kato p.223
+From \cite[Ch.~4 Cor.~2.6]{Kato2013}, we have: %Kato p.223
 \begin{align}\label{dimLem}
@@
 
-The following is our result in combinatorial matrix analysis; it contains most of the complexity in the proof of Thm.~\ref{DeterministicUniquenessTheorem}.
+Our result in combinatorial matrix analysis, which hides most of the complexity in our proof of Thm.~\ref{DeterministicUniquenessTheorem}, is the following.
 
 \begin{lemma}\label{MainLemma}
-If an $n \times m$ matrix $\mathbf{A}$ has $L_{2\mathcal{H}}(\mathbf{A}) > 0$ for some $r$-regular $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP, then the following holds for $C_2 > 0$ given by \eqref{Cdef2}:
+Suppose the $n \times m$ matrix $\mathbf{A}$ has $L_{2\mathcal{H}}(\mathbf{A}) > 0$ for some $r$-regular $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP.
+There exists $C_2 > 0$ for which the following holds for all $\varepsilon < L_2(\mathbf{A}) / C_2$:
 
-Fix $\varepsilon < L_2(\mathbf{A}) / C_2$. If for some $n \times \overline m$ matrix $\mathbf{B}$ and map $\pi: \mathcal{H} \mapsto {[\overline m] \choose k}$,
+If for some $n \times \overline m$ matrix $\mathbf{B}$ and map $\pi: \mathcal{H} \mapsto {[\overline m] \choose k}$,
 \begin{align}\label{GapUpperBound}
-d(\bm{\mathcal{A}}_S, \bm{\mathcal{B}}_{\pi(S)}) \leq \varepsilon, \ \  \text{for $S \in \mathcal{H}$},
+d(\bm{\mathcal{A}}_S, \bm{\mathcal{B}}_{\pi(S)}) \leq \varepsilon \ \  \text{for $S \in \mathcal{H}$},
 \end{align}
@@
 \begin{align}\label{MainLemmaBPD}
-\|\mathbf{A}_i - (\mathbf{B}\mathbf{PD})_i\|_2 \leq C_2 \varepsilon, \ \  \text{for } i \in J,
+\|\mathbf{A}_j - \mathbf{B}\mathbf{PD}_j\|_2 \leq C_2 \varepsilon \ \  \text{for } j \in J
 \end{align}
-for some $J \subseteq [m]$ of size \mbox{$m - (r-1)(\overline m - m)$}.
+for some $J$ of size \mbox{$m - (r-1)(\overline m - m)$}.
 \end{lemma}
@@
 We present the constant $C_2$ (a function of $\mathbf{A}$ and $\mathcal{H}$) relative to a quantity used in \cite{Deutsch12} to analyze the convergence of the ``alternating projections" algorithm for projecting a point onto the intersection of subspaces.
-We incorporate this quantity into the following definition, which we refer to in our proof of Lem.~\ref{DistanceToIntersectionLemma} in the Appendix; specifically, we use it to bound the distance between a point and the intersection of subspaces given an upper bound on its distance from each subspace.
+We incorporate this quantity into the following definition, which we refer to in our proof of Lem.~\ref{DistanceToIntersectionLemma} in the Appendix; specifically, we use it to bound the distance between a point and the intersection of subspaces given an upper bound on its distance from each subspace individually.
 
@@
 \end{definition}
-Note that $\theta \in (0,\frac{\pi}{2}]$ implies $0 \leq \xi < 1$, and that $\xi(\mathcal{V}') \leq \xi(\mathcal{V})$ when $\mathcal{V}' \subseteq \mathcal{V}$.\footnote{We acknowledge the counter-intuitive property: $\theta =  \pi/2$ when $U \subseteq W$.}
+Note that $\theta \in (0,\frac{\pi}{2}]$ implies $0 \leq \xi < 1$, and that $\xi(\mathcal{V}') \leq \xi(\mathcal{V})$ when $\mathcal{V}' \subseteq \mathcal{V}$.\footnote{We acknowledge the potentially counter-intuitive property that $\theta =  \pi/2$ when $U \subseteq W$.}
 
-The constant $C_2 > 0$ of Lem.~\ref{MainLemma} can now be expressed as:  
+The constant $C_2 > 0$ of Lem.~\ref{MainLemma} is then given by:  
 \begin{align}\label{Cdef2}
@@
 
-We next define the constant $C_1 > 0$ of Thm.~\ref{DeterministicUniquenessTheorem} in terms of $C_2$.
+We now define the constant $C_1 > 0$ of Thm.~\ref{DeterministicUniquenessTheorem} in terms of $C_2$.
 Given vectors $\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$, let $\mathbf{X}$ denote the $m \times N$ matrix with columns $\mathbf{x}_i$ and let $I(S)$ denote the set of indices $i$ for which $\mathbf{x}_i$ is supported in $S$.
-We define:
 \begin{align}\label{Cdef1}
@@
 \end{align}
-Given the assumptions of Thm.~\ref{DeterministicUniquenessTheorem} on $\mathbf{A}$ and the $\mathbf{x}_i$, this expression for $C_1$ is well-defined\footnote{\label{note1}To see this, fix $S \in \mathcal{H}$ and $k$-sparse $\mathbf{c}$.
-Using the definitions, we have $\|\mathbf{AX}_{I(S)}\mathbf{c}\|_2 \geq \sqrt{k} L_\mathcal{H}(\mathbf{A})\|\mathbf{X}_{I(S)}\mathbf{c}\|_2 \geq k L_\mathcal{H}(\mathbf{A}) L_k(\mathbf{X}_{I(S)})\|\mathbf{c}\|_2$.
-Thus, $L_k(\mathbf{AX}_{I(S)}) \geq \sqrt{k} L_\mathcal{H}(\mathbf{A}) L_k(\mathbf{X}_{I(S)}) > 0$, since $L_{\mathcal{H}}(\mathbf{A}) \geq L_{2\mathcal{H}}(\mathbf{A})> 0$ and $L_k(\mathbf{X}_{I(S)}) > 0$ by general linear position of the $\mathbf{x}_i$.} and yields an upper bound on $\varepsilon$ consistent with that proven sufficient in the case $k=1$ considered at the beginning of this section.\footnote{When $\mathbf{x}_i = c_i\mathbf{e}_i$, we have $C_2 \geq 2\|\mathbf{A}_i\|_2$ and the denominator in \eqref{Cdef1} becomes $\min_{i \in [m]} |c_i| \|\mathbf{A}_i\|_2$; hence, $C_1 \geq 2 / \min_{i \in [m]} |c_i|$.}
+We remark that given the assumptions of Thm.~\ref{DeterministicUniquenessTheorem} on $\mathbf{A}$ and the $\mathbf{x}_i$, this expression for $C_1$ is well-defined\footnote{\label{note1}Fixing $S \in \mathcal{H}$ and $k$-sparse $\mathbf{c}$, we have $\|\mathbf{AX}_{I(S)}\mathbf{c}\|_2 \geq \sqrt{k} L_\mathcal{H}(\mathbf{A})\|\mathbf{X}_{I(S)}\mathbf{c}\|_2 \geq k L_\mathcal{H}(\mathbf{A}) L_k(\mathbf{X}_{I(S)})\|\mathbf{c}\|_2$.
+Hence, $L_k(\mathbf{AX}_{I(S)}) \geq \sqrt{k} L_\mathcal{H}(\mathbf{A}) L_k(\mathbf{X}_{I(S)}) > 0$, since $L_{\mathcal{H}}(\mathbf{A}) \geq L_{2\mathcal{H}}(\mathbf{A})> 0$ and $L_k(\mathbf{X}_{I(S)}) > 0$ by general linear position of the $\mathbf{x}_i$.} and yields an upper bound on $\varepsilon$ consistent with that proven sufficient in the case $k=1$ considered at the beginning of this section.\footnote{When $\mathbf{x}_i = c_i\mathbf{e}_i$ we have $C_2 \geq 2\|\mathbf{A}_i\|_2$ and the denominator in \eqref{Cdef1} becomes $\min_{i \in [m]} |c_i| \|\mathbf{A}_i\|_2$, hence $C_1 \geq 2 / \min_{i \in [m]} |c_i|$.}
 % C_2(\mathbf{A}, \mathcal{H}) := \frac{ (r+1) \max_{j \in [m]} \|\mathbf{A}_j\|_2}{ \min_{\mathcal{G} \in {\mathcal{H} \choose r} \cup {\mathcal{H} \choose r+1}} \xi( \{ \bm{\mathcal{A}}_S \}
 
-The practically-minded reader should note that the explicit constants $C_1$ and $C_2$ are effectively computable: the quantity $L_k$ may be calculated as the smallest singular value of a certain matrix, while the quantity $\xi$ involves computing ``canonical angles'' between subspaces, which reduces again to an efficient singular value decomposition.
-There is no known fast computation of $L_k$ in general, however, since even $L_{k} > 0$ is NP-hard \cite{tillmann2014computational}, although 
-efficiently computable bounds have been proposed (e.g., via the ``mutual coherence" of a matrix \cite{donoho2003optimally}); alternatively, 
+The practically-minded reader should note that the explicit constants $C_1$ and $C_2$ are effectively computable: the quantity $L_k$ may be calculated as the smallest singular value of a certain matrix, while the quantity $\xi$ involves computing ``canonical angles'' between subspaces, which reduce again to an efficient singular value decomposition.
+There is no known fast computation of $L_k$ in general, however, since even $L_{k} > 0$ is NP-hard \cite{tillmann2014computational}, although efficiently computable bounds have been proposed (e.g.
+via the ``mutual coherence" of a matrix \cite{donoho2003optimally}); alternatively,
 fixing $k$ yields polynomial complexity.
 Moreover, calculating $C_2$ requires an exponential number of queries to $\xi$ unless $r$ is held fixed, too (e.g., the ``cyclic order'' hypergraphs described above have $r=k$).
-Thus, as presented, $C_1$ and $C_2$ are not efficiently computable in general.
-% , but efficient subcases do exist and may be of practical relevance.
+Thus, as presented, $C_1$ and $C_2$ are not efficiently computable in general, but efficient sub-cases do exist and may be of practical relevance.
 
@@
 \end{align*}
-where the last inequality uses \eqref{Ldef}. From Def.~\ref{dDef}:
+where the last inequality follows directly from \eqref{Ldef}. From Def.~\ref{dDef}:
 \begin{align}\label{rhs222}
@@
 %
-Finally, apply Lem.~\ref{MainLemma} with $\varepsilon < L_2(\mathbf{A})/C_1$ and $\pi(S) := \overline S$. % L_2(A) > 0 by def of L, since L_2H(A) > 0 and H covers [m]
+Now, apply Lem.~\ref{MainLemma} with $\varepsilon < L_2(\mathbf{A})/C_1$ and $\pi(S) := \overline S$. % L_2(A) > 0 by def of L, since L_2H(A) > 0 and H covers [m]
 \end{proof}
 
-Before moving on to the proof of Thm.~\ref{SLCopt}, we briefly revisit our discussion on sample complexity from the end of the previous section.
-While an exponential number of samples may very well prove to be necessary in the deterministic or almost-certain case, our proof of Thm.~\ref{DeterministicUniquenessTheorem} can be extended to hold with some probability for \emph{any} number of samples by alternative appeal to a probabilistic pigeonholing at the point early in the proof where the (deterministic) pigeonhole principle is applied to show that for every $S \in \mathcal{H}$, there exist $k$ vectors $\mathbf{x}_i$ supported on $S$ whose corresponding $\mathbf{\overline x}_i$ all share the same support.\footnote{A famous example of such an argument is the counter-intuitive ``birthday paradox", which demonstrates that the probability of two people having the same birthday in a room of twenty-three is greater than 50\%.}
-Given insufficient samples, this argument has some less-than-certain probability of being valid for each $S \in \mathcal{H}$.
-Nonetheless, simulations with small hypergraphs confirm that the probability of success very quickly approaches one once the number of samples $N$ surpasses a small fraction of the deterministic sample complexity.
+Before moving on to our proof of Thm.~\ref{SLCopt}, we briefly revisit here our discussion on sample complexity from the end of the previous section.
+While an exponential number of samples may very well prove to be necessary in the deterministic or almost-certain case, our proof of Thm.~\ref{DeterministicUniquenessTheorem} can be extended to hold with some probability for \emph{any} number of samples by alternative appeal to a probabilistic pigeonholing at the point early in the proof where the (deterministic) pigeonhole principle is applied to show that for every $S \in \mathcal{H}$, there exist $k$ vectors $\mathbf{x}_i$ supported on $S$ whose corresponding $\mathbf{\overline x}_i$ all share the same support.\footnote{A famous example of such an argument is the counter-intuitive "birthday paradox", which demonstrates that the probability of two people having the same birthday in a room of twenty-three is in fact greater than 50\%.} Given insufficient samples, this argument has some less-than-certain probability of being valid for each $S \in \mathcal{H}$.
+Nonetheless, cursory simulations with small hypergraphs confirm that the probability of success very quickly approaches one once the number of samples $N$ surpasses a small fraction of the deterministic sample complexity.
 
@@
 
-Next, observe that no more than $(k-1)|\mathcal{H}|$ of the $\mathbf{\overline x}_i$ share a support $\overline S$ of size less than $k$.
+We note that no more than $(k-1)|\mathcal{H}|$ of the $\mathbf{\overline x}_i$ share a support $\overline S$ of size less than $k$.
 Otherwise, by the pigeonhole principle, there is some $S \in \mathcal{H}$ and a set of $k$ indices $K \subseteq I(S)$ for which all $\mathbf{x}_i$ with $i \in K$ are supported in $S$; as argued previously, \eqref{rhs222} follows.
@@
 
-A main motivation for this work is the emergence of seemingly unique representations from sparse coding models trained on natural data, despite the varied assumptions underlying the many algorithms in current use.
-Our results constitute an important step toward explaining these phenomena as well as unifying many publications on the topic by deriving general deterministic conditions under which identification of parameters in this model is not only possible but also robust to uncertainty in measurement and model choice.
+A motivation for this work was the emergence of seemingly characteristic representations from sparse coding models fit to natural data, despite the varied assumptions underlying the many algorithms in current use.
+To this end, we have taken an important step toward unifying the many publications on the topic by demonstrating general sufficient, deterministic conditions under which identification of parameters in this model is not only possible but also robust to uncertainty in measurement and model choice.
 
-We have shown that, given sufficient data, the problem of determining a dictionary and sparse codes with minimal support size (Prob.~\ref{OptimizationProblem}) reduces to an instance of Prob.~\ref{InverseProblem}, to which our main result (Thm.~\ref{DeterministicUniquenessTheorem}) applies: every dictionary and sequence of sparse codes consistent with the data are equivalent up to inherent relabeling/scaling ambiguities and a discrepancy (error) that scales linearly with the measurement noise or modeling inaccuracy.
-The constants we provide are explicit and computable; as such, there is an effective procedure that sufficiently affirms if a proposed solution to these problems is indeed unique up to noise and inherent ambiguities, although it is not efficient in general.
+We have shown that, given sufficient data, the problem of seeking a dictionary and sparse codes with minimal average support size (Prob.~\ref{OptimizationProblem}) reduces to an instance of Prob.~\ref{InverseProblem}, to which our main result (Thm.~\ref{DeterministicUniquenessTheorem}) applies: every dictionary and sequence of sparse codes consistent with the data are equivalent up to inherent relabeling/scaling ambiguities and a discrepancy (error) that scales linearly with the measurement noise or modeling inaccuracy.
+The constants we provide are explicit and computable; as such, there is an effective procedure that sufficiently affirms if a proposed solution to these problems is indeed unique up to noise and inherent ambiguities, although this computation is not efficient in general.
+
+Our theoretical work mathematically justifies one of the few hypothesized theories of bottleneck communication in the brain \cite{Isely10}: that sparse neural population activity is recoverable from its noisy linear compression through a randomly constructed (but unknown) wiring bottleneck by any biologically plausible unsupervised sparse coding method that solves Prob.~\ref{DeterministicUniquenessTheorem} or \ref{SLCopt} (e.g., \cite{rehnsommer2007, rozell2007neurally, pehlevan2015normative}).\footnote{We refer the reader to \cite{ganguli2012compressed} for more on interactions between dictionary learning and neuroscience.}
 
@@
 
-Beyond an extension of existing noiseless guarantees \cite{Hillar15} to the noisy regime and their novel application to Prob.~\ref{OptimizationProblem}, our work contains a theory of combinatorial designs for support sets key to identification of dictionaries.
-We incorporate this idea into a fundamental lemma in matrix theory (Lem.~\ref{MainLemma}) that draws upon the definition of a matrix lower bound (\ref{Ldef}) induced by a hypergraph.
-The new insight offered by this combinatorial approach allows for guaranteed recovery of some or all dictionary elements even if: 1) dictionary size is overestimated, 2) data cover only a polynomial number of distinct sparse supports, and 3) dictionaries do not satisfy the spark condition.
+Beyond an original extension of existing noiseless guarantees \cite{Hillar15} to the noisy regime and their application to Prob.~\ref{OptimizationProblem}, a major innovation in our work is a theory of combinatorial designs for support sets key to the identification of the dictionary.
+We incorporate this idea into a fundamental lemma in matrix theory (Lem.~\ref{MainLemma}) that draws upon the definition of a new matrix lower bound induced by a hypergraph.
+Novel insights enabled by our combinatorial approach include: 1) a subset of dictionary elements is recoverable even if dictionary size is overestimated, 2) data require only a polynomial number of distinct sparse supports, and 3) recoverable dictionaries need not necessarily satisfy the spark condition.
 
-The absence of any assumptions about dictionaries solving Prob.~\ref{InverseProblem} was a major technical obstruction in proving Thm.~\ref{DeterministicUniquenessTheorem}.
-We sought such a general guarantee because of the practical difficulty in ensuring that an algorithm maintain a dictionary satisfying the spark condition \eqref{SparkCondition} at each iteration, an implicit requirement of all previous works except \cite{Hillar15}; indeed, even certifying a dictionary has this property is NP-hard \cite{tillmann2014computational}.
-
-One direct application of this work is to theoretical neuroscience, wherein our theorems justify the mathematical soundness of one of the few hypothesized theories of bottleneck communication in the brain \cite{Isely10}: that sparse neural population activity is recoverable from its noisy linear compression through a randomly constructed (but unknown) wiring bottleneck by any biologically plausible unsupervised sparse coding method that solves Prob.~\ref{DeterministicUniquenessTheorem} or \ref{SLCopt} (e.g., \cite{rehnsommer2007, rozell2007neurally, pehlevan2015normative}).\footnote{We refer the reader to \cite{ganguli2012compressed} for more on interactions between dictionary learning and neuroscience.}
+The absence of any assumption at all about dictionaries that solve Prob.~\ref{InverseProblem} was a major technical difficulty in proving Thm.~\ref{DeterministicUniquenessTheorem}.
+We sought such a general guarantee because of the practical difficulty of ensuring that an algorithm maintain a dictionary satisfying the spark condition \eqref{SparkCondition} at each iteration, an implicit requirement of all previous works except \cite{Hillar15}; indeed, even certifying a dictionary has this property is NP-hard \cite{tillmann2014computational}.
 
 In fact, uniqueness guarantees with minimal assumptions apply to all areas of data science and engineering that utilize learned sparse structure.
-For example, several groups have applied compressed sensing to signal processing tasks; for instance, in MRI analysis \cite{lustig2008compressed}, image compression \cite{Duarte08}, and even the design of an ultrafast camera \cite{Gao14}.
-It is only a matter of time before these systems incorporate dictionary learning to encode and decode signals (e.g., in a device that learns structure from motion \cite{kong2016prior}), just as scientists have used sparse coding to make sense of their data \cite{jung2001imaging, agarwal2014spatially, lee2016sparse, wu2016stability}.
+For example, several groups have applied compressed sensing to signal processing tasks: MRI analysis \cite{lustig2008compressed}, image compression \cite{Duarte08}, and, more recently, the design of an ultrafast camera \cite{Gao14}.
+Given such effective uses of compressed sensing, it is only a matter of time before these systems incorporate dictionary learning to encode and decode signals (e.g., in a device that learns structure from motion \cite{kong2016prior}), just as scientists have used it to make sense of their data \cite{jung2001imaging, Agarwal14, lee2016sparse, wu2016stability}.
+Assurances such as those offered by our theorems certify that different devices (with different initialization, etc.) will learn equivalent representations given enough data from statistically identical systems.\footnote{To contrast with the current hot topic of ``Deep Learning'', there are few such uniqueness guarantees for these models of data; moreover, even small noise can dramatically alter their output \cite{goodfellow2014explaining}.} Indeed, it seems a main reason for the sustained interest in dictionary learning as an unsupervised method for data analysis is the assumed well-posedness of parameter identification in the sparse coding model, confirmation of which forms the core of our theoretical findings.
 
-Assurances offered by our theorems certify that different devices and algorithms learn equivalent representations given enough data from statistically identical systems.\footnote{To contrast with the current hot topic of ``Deep Learning'', there are few such uniqueness guarantees for these models of data; moreover, even small noise can dramatically alter their output \cite{goodfellow2014explaining}.}
-Indeed, a main reason for the sustained interest in dictionary learning as an unsupervised method for data analysis seems to be the assumed well-posedness of parameter identification in the model, confirmation of which forms the core of our findings.
-
-We close with some challenges left open by our work.
-All conditions stated here guaranteeing the uniqueness and stability of sparse representations have only been shown sufficient; it remains open, therefore, to extend them to necessary conditions, be they on required sample size, the structure of support set hypergraphs, or tolerable error bounds.
-On this last note, we remark that our deterministic treatment considers always the ``worst-case" noise, whereas the ``effective" noise sampled from a concentrated distribution might be significantly reduced, especially for high-dimensional data.
-It would be of great practical benefit to see how drastically all conditions can be relaxed by requiring only probabilistic guarantees in this way, or in the spirit of our discussion on probabilistic pigeonholing to reduce sample complexity (as in the famous ``birthday paradox") following the proof of Thm.~\ref{DeterministicUniquenessTheorem}.
-
-Another interesting question raised by our work is for which special cases is it efficient to check that a solution to Prob.~\ref{InverseProblem} or \ref{OptimizationProblem} is unique up to noise and inherent ambiguities.
-Considering that the sufficient conditions we have described for checking this in general are NP-hard to compute, are the necessary conditions hard?
-Are Probs.~\ref{InverseProblem} and \ref{OptimizationProblem} then also hard (e.g., see \cite{Tillmann15})?
-Finally, since Prob.~\ref{SLCopt} is intractable in general, but efficiently solvable by $\ell_1$-norm minimization when the matrix is known (and has a large enough lower bound over sparse domains \cite{eldar2012compressed}), is there a version of Thm.~\ref{SLCopt} certifying when Prob.~\ref{OptimizationProblem} can be solved efficiently in full by similar means?
-% [*** Incorporate this open problem with more words ***]
-
-It is our hope that the theoretical tools showcased here will be of some use to the community in answering these remaining questions.
-
-%We close with some challenges left open by our work.
-First, there is the basic problem of proving optimal lower bounds on sufficient sample size $N$ guaranteeing the uniqueness and stability of sparse representations.
-The pigeonholing argument in the proof of Thm.~\ref{DeterministicUniquenessTheorem} is loose in that it assigns to each support $S \in \mathcal{H}$ a corresponding support $\overline S$ without consideration of previously matched pairs; although we doubt tightening in this way will lead to sub-exponential sample sizes.
-Sample complexity will also benefit from lowering the number of required supports, i.e.
-the size of regular uniform hypergraphs satisfying the SIP.
-The regularity requirement on support hypergraphs can be loosened to allow for certain non-regular hypergraphs satisfying constraints on the degree sequence of nodes; though we impose regularity for clarity of exposition.
-It is then natural to ask: what is the smallest hypergraph satisfying the required constraints forgiven $m$ and $k$?
-Finally, the error bounds can be improved by tightening the constant $C_1$, e.g.
-via an improvement in Lemma ?.
-
-%Solving Prob.~\ref{SLCopt} directly is intractable in general since it necessitates, for each proposed dictionary $\mathbf{B}$, a combinatorial search for the supports of the associated sparse codes $\mathbf{\overline x}_i$.
-A common work-around is to convexify the problem (for fixed $\mathbf{B}$) by substituting the norm $\|\cdot\|_0$ with $\|\cdot\|_1$, impelled the fact that matrices $\mathbf{A}$ with large enough $L_{2k}(\mathbf{A})$ induce the same sparse codes via minimization of either norm \cite{?}.
-To this end, the lower bound $L_{2k}(\mathbf{BP}) \geq (L_{2k}(\mathbf{A}) - C_1\varepsilon) / \|\mathbf{D}\|_1$ implied by Thm.~\ref{DeterministicUniquenessTheorem} hints at conditions on the generating dictionary $\mathbf{A}$ and $k$-sparse codes $\mathbf{x}_i$ under which \emph{all} matrices $\mathbf{B}$ (of bounded column-norm) that solve Prob.~\ref{OptimizationProblem} also share this property of $\mathbf{A}$ by virtue of uniqueness and stability.
-One might then imagine an inference procedure whereby sparse codes are inferred via minimization of $\|\cdot\|_1$, but solutions still evaluated by their collective support size, yielding unique optimal solutions to Prob.~\ref{SLCopt} if only constraints could be imposed such that the learning procedure eventually guides $\mathbf{B}$ through an optimal dictionary.
-% (e.g.
-the dictionary is a member of a known finite set).
-
-\textbf{Acknowledgement.} We thank Fritz Sommer and Darren Rhea for early thoughts, and Ian Morris for posting \eqref{eqdim} online.
-
-%\section{EXTRA}
-%An additional consequence of Thm.~\ref{DeterministicUniquenessTheorem} of potential practical relevance to is the implied lower bound $L_{2k}(\mathbf{BPD}) \geq L_{2k}(\mathbf{A}) - C_1\varepsilon$ in the case where $\mathbf{A}$ satisfies \eqref{SparkCondition}.
+\section{EXTRA}
+An additional consequence of Thm.~\ref{DeterministicUniquenessTheorem} of potential practical relevance to is the implied lower bound $L_{2k}(\mathbf{BPD}) \geq L_{2k}(\mathbf{A}) - C_1\varepsilon$ in the case where $\mathbf{A}$ satisfies \eqref{SparkCondition}.
 Since solving Prob.~\ref{SLCopt} directly requires a combinatorial search over sparse supports for the $\mathbf{\overline x}_i$ for each proposed dictionary $\mathbf{B}$, rendering it intractable in general, a common strategy is to replace the $\ell_0$-norm in \eqref{minsum} with the $\ell_1$-norm, thereby transforming the inference of sparse $\mathbf{\overline x}_i$ for a fixed dictionary $\mathbf{B}$ into a convex optimization solvable by a linear program.
@@
 It remains to determine, however, what practical conditions preclude matrices that don't solve Prob.~\ref{OptimizationProblem} from nonetheless solving the convexified problem.
+
+Regardless, an implication of the above observation is that the following algorithm solves Prob.~\ref{OptimizationProblem} without appeal to combinatorial search:
+\begin{enumerate}
+\item List all matrices $\mathbf{B}$.
+\item For each matrix $\mathbf{B}$, solve $\mathbf{\overline x}_i = \arg \min \|\mathbf{v}\|_1$ s.t. $\|\mathbf{Bv} - \mathbf{z}_i\| \leq \eta$ for $i = 1, \ldots, N$.
+\item Quantify the proposed solution $\mathbf{B}$ and $\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N$ as $\rho(\mathbf{B}, \mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N) = \sum_{i=1}^{N} \|\mathbf{\overline x}_i\|_0$.
+\item Output $\arg \min_{\mathbf{B}, \mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N} \left( \rho \right)$.
+ \end{enumerate}
+
 %
-%Regardless, an implication of the above observation is that the following algorithm solves Prob.~\ref{OptimizationProblem} without appeal to combinatorial search:
-%\begin{enumerate}
-%\item List all matrices $\mathbf{B}$.
-%\item For each matrix $\mathbf{B}$, solve $\mathbf{\overline x}_i = \arg \min \|\mathbf{v}\|_1$ s.t. $\|\mathbf{Bv} - \mathbf{z}_i\| \leq \eta$ for $i = 1, \ldots, N$.
-%\item Quantify the proposed solution $\mathbf{B}$ and $\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N$ as $\rho(\mathbf{B}, \mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N) = \sum_{i=1}^{N} \|\mathbf{\overline x}_i\|_0$.
-%\item Output $\arg \min_{\mathbf{B}, \mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N} \left( \rho \right)$.
-% \end{enumerate}
+
+\textbf{Acknowledgement.} We thank F. Sommer and D. Rhea for early thoughts, and I. Morris for posting \eqref{eqdim} online.
 
@@
 
-We prove Lem.~\ref{MainLemma} after the following auxiliary lemmas.  % stating and proving some auxiliary lemmas. 
+In this section, we prove Lem.~\ref{MainLemma} after stating some required auxiliary lemmas and their proofs.  % stating and proving some auxiliary lemmas. 
 %First, note that since $\|\mathbf{A}\mathbf{x}\|_2 \leq \max_j\|\mathbf{A}_j\|_2\|\mathbf{x}\|_1$ and $\|\mathbf{x}\|_1 \leq \sqrt{k} \|\mathbf{x}\|_2$ for $k$-sparse $\mathbf{x}$, by \eqref{Ldef} we have the following frequently applied inequality:
@@
 \begin{lemma}\label{spanIntersectionLemma}
-If $f: V \to W$ is injective, then $f\left(\cap_{i=1}^\ell V_i \right) =  \cap_{i=1}^\ell f\left(V_i\right)$ for any $V_1, \ldots, V_\ell \subseteq V$. ($f(\emptyset):=\emptyset$.)
+If $f: V \to W$ is an injective function, then $f\left(\cap_{i=1}^\ell V_i \right) =  \cap_{i=1}^\ell f\left(V_i\right)$ for any $V_1, \ldots, V_\ell \subseteq V$. ($f(\emptyset):=\emptyset$.)
 %In particular, if for some $E \in 2^{[m]}$ the map $M \in \mathbb{R}^{n \times m}$ is injective on $\cup_{S \in \mathcal{H}} \text{span}\{e_i\}_{i \in S}$ then $\text{span}\{ M_{\cap_{S \in \mathcal{H}} S} \} = \cap_{S \in \mathcal{H}} \text{span}\{M_S\}$.
@@
 By induction, it is enough to prove the case $\ell = 2$.
-Clearly, for any map $f$, if $w \in f(U \cap V)$ then $w \in f(U)$ and $w \in f(V)$; hence, $w \in f(U) \cap f(V)$.
-If $w \in f(U) \cap f(V)$, then $w \in f(U)$ and $w \in f(V)$; thus, $w = f(u) = f(v)$ for some $u \in U$ and $v \in V$, implying $u = v$ by injectivity of $f$.
-It follows that $u \in U \cap V$ and $w \in f(U \cap V)$.
+Clearly, for any map $f$, if $w \in f(U \cap V)$ then $w \in f(U)$ and $w \in f(V)$, hence $w \in f(U) \cap f(V)$.
+If $w \in f(U) \cap f(V)$ then $w \in f(U)$ and $w \in f(V)$, hence $w = f(u) = f(v)$ for some $u \in U$ and $v \in V$, implying $u = v$ by injectivity of $f$.
+Hence $u \in U \cap V$, and $w \in f(U \cap V)$.
 \end{proof}
@@
 \begin{lemma}\label{DistanceToIntersectionLemma}
-Let $\mathcal{V} = \{V_i\}_{i=1}^k$ be a set of two or more subspaces of $\mathbb{R}^m$, and set $V = \cap \mathcal{V} $.
+Let $\mathcal{V} = \{V_i\}_{i=1}^k$ be a set of two or more subspaces of $\mathbb{R}^m$ and let $V = \cap \mathcal{V} $.
 For  $\mathbf{u} \in \mathbb{R}^m$, we have (recall Defs.~\ref{dDef}~\&~\ref{FriedrichsDefinition}):
@@
 Recall the projection onto the subspace $V \subseteq \mathbb{R}^m$ is the mapping $\Pi_V: \mathbb{R}^m \to V$ that associates with each $\mathbf{u}$ its unique nearest point in $V$; i.e., $\|\mathbf{u} - \Pi_V\mathbf{u}\|_2 = \text{\rm dist}(\mathbf{u}, V)$.
-By repeatedly applying the triangle inequality, we have:
+By repeated triangle inequality,
 \begin{align}\label{f}
@@
 where we have also used that the spectral norm of the orthogonal projections $\Pi_{V_{\ell}}$ satisfies $\|\Pi_{V_{\ell}}\|_2 \leq 1$ for all $\ell$.
-
 It remains to bound the second term in \eqref{f} by $\xi(\mathcal{V}) \|\mathbf{u} - \Pi_V\mathbf{u}\|_2$.
@@
 = \| ( \Pi_{V_k} \cdots\Pi_{V_1} - \Pi_V ) (\mathbf{u} - \Pi_V\mathbf{u})\|_2$. % \leq z\|\mathbf{u} - \Pi_V\mathbf{u}\|_2$.
-Consequently, inequality \eqref{DTILeq} follows from \cite[Thm.~9.33]{Deutsch12}:
+The result \eqref{DTILeq} then follows from the following fact \cite[Thm.~9.33]{Deutsch12}:
 \begin{align}
-\|\Pi_{V_k}\Pi_{V_{k-1}}\cdots\Pi_{V_1} \mathbf{x} - \Pi_V\mathbf{x}\|_2 \leq z \|\mathbf{x}\|_2, \ \ \text{for all } \mathbf{x},
+\|\Pi_{V_k}\Pi_{V_{k-1}}\cdots\Pi_{V_1} \mathbf{x} - \Pi_V\mathbf{x}\|_2 \leq z \|\mathbf{x}\|_2 \ \ \text{for all } \mathbf{x},
 \end{align}
@@
 %
-then $\overline m \geq m$; and if $\overline m  (r-1) < mr$, the map $i \mapsto \cap_{S \in \sigma(i)} \pi(S)$ is an injective function to $[\overline m]$ from some $J \subseteq [m]$ of size $m - (r-1)(\overline m - m)$ (recall $\sigma$ from Def.~\ref{sip}).
-%In particular, if $\overline m = m$ then $\pi$ is induced by a permutation on $[m]$.
+then $\overline m \geq m$, and if $\overline m  (r-1) < mr$ then the map $i \mapsto \cap \pi(\sigma(i))$ is an injective map to $[\overline m]$ from some $J \subseteq [m]$ of size $m - (r-1)(\overline m - m)$.\footnote{Recall $\sigma$ from Def.~\ref{sip}.}  %In particular, if $\overline m = m$ then $\pi$ is induced by a permutation on $[m]$.
 \end{lemma}
@@
 \begin{proof}
-Consider the following set: $T_1 := \{(i, S): i \in \pi(S), S \in \mathcal{H}\}$, which numbers $|T_1| = \sum_{S \in \mathcal{H}} |\pi(S)| \geq \sum_{S \in \mathcal{H}} |S| = \sum_{i \in [m]} \deg_\mathcal{H}(i) = mr$ by $r$-regularity of $\mathcal{H}$.
+Consider the set: $T_1 := \{(i, S): i \in \pi(S), S \in \mathcal{H}\}$, which numbers $|T_1| = \sum_{S \in \mathcal{H}} |\pi(S)| \geq \sum_{S \in \mathcal{H}} |S| = \sum_{i \in [m]} \deg_\mathcal{H}(i) = mr$ by $r$-regularity of $\mathcal{H}$.
 Note that $|T_1| \leq \overline m r$; otherwise, pigeonholing the tuples of $T_1$ with respect to their $\overline m$ possible first elements would imply that more than $r$ of the tuples in $T_1$ share the same first element.
-This cannot be the case, however, since then some $\mathcal{G} \in {\mathcal{H} \choose r+1}$ formed from any $r+1$ of their second elements would satisfy $\cap \pi(\mathcal{G}) \neq 0$; hence, $|\cap \mathcal{G}| \neq 0$ by \eqref{cond}, contradicting $r$-regularity of $\mathcal{H}$.
-It follows that $\overline m \geq m$.
+This cannot be the case, however, since then some $\mathcal{G} \in {\mathcal{H} \choose r+1}$ formed from any $r+1$ of their second elements would satisfy $\cap \pi(\mathcal{G}) \neq 0$, hence $|\cap \mathcal{G}| \neq 0$ by \eqref{cond}, contradicting $r$-regularity of $\mathcal{H}$.
+Thus, $\overline m \geq m$.
 
 Suppose now that $\overline m (r-1) < mr$, so that $p := mr - \overline m (r-1)$ is positive and $|T_1| \geq \overline m (r - 1) + p$.
-Pigeonholing $T_1$ into $[\overline m]$ again, there are at least $r$ tuples in $T_1$ sharing some first element; that is, for some $\mathcal{G}_1 \subseteq \mathcal{H}$ of size $|\mathcal{G}_1| \geq r$, we have $|\cap \pi(\mathcal{G}_1)| \geq 1$ and (by \eqref{cond}) $|\cap \mathcal{G}_1| \geq 1$.
+Pigeonholing $T_1$ into $[\overline m]$ again, there must be at least $r$ tuples in $T_1$ that share some first element; that is, for some $\mathcal{G}_1 \subseteq \mathcal{H}$ of size $|\mathcal{G}_1| \geq r$ we have $|\cap \pi(\mathcal{G}_1)| \geq 1$ and (by \eqref{cond}) $|\cap \mathcal{G}_1| \geq 1$.
 Since no more than $r$ tuples of $T_1$ can share the same first element, we in fact have $|\mathcal{G}_1| = r$.
@@
 
-If $p=1$, then we are done.
+If $p=1$ then we are done.
 Otherwise, define $T_2 := T_1 \setminus \{(i,S) \in T_1: i = \cap \pi(\mathcal{G}_1)\}$, which contains $|T_2| = |T_1| - r \geq (\overline m - 1)(r-1) + (p-1)$ ordered pairs having $\overline m - 1$ distinct first indices.
-Pigeonholing $T_2$ into $[\overline m - 1]$ and repeating the above arguments produces the star $\mathcal{G}_2 \in {\mathcal{H} \choose r}$ with intersection $\cap \mathcal{G}_2$ necessarily distinct (by $r$-regularity) from $\cap \mathcal{G}_1$.
+Pigeonholing $T_2$ into $[\overline m - 1]$ and repeating the above arguments produces the star $\mathcal{G}_2 \in {\mathcal{H} \choose r}$ with intersect $\cap \mathcal{G}_2$ necessarily distinct (by $r$-regularity) from $\cap \mathcal{G}_1$.
 Iterating this procedure $p$ times in total yields the stars $\mathcal{G}_i$ for which $\cap\mathcal{G}_i \mapsto \cap \pi(\mathcal{G}_i)$ defines an injective map to $[\overline m]$ from $J = \{\cap \mathcal{G}_1, \ldots, \cap \mathcal{G}_p\} \subseteq [m]$.
@@
 We begin by showing that $\dim(\bm{\mathcal{B}}_{\pi(S)}) = \dim(\bm{\mathcal{A}}_S)$ for all $S \in \mathcal{H}$.
-Note that since $\|\mathbf{A}\mathbf{x}\|_2 \leq \max_j\|\mathbf{A}_j\|_2\|\mathbf{x}\|_1$ and $\|\mathbf{x}\|_1 \leq \sqrt{k} \|\mathbf{x}\|_2$ for all $k$-sparse $\mathbf{x}$, by \eqref{Ldef} we have $L_2(\mathbf{A}) \leq \max_j\|\mathbf{A}_j\|_2$ and therefore (as $0 \leq \xi < 1$) the right-hand side of \eqref{GapUpperBound} is less than one.
-From \eqref{dimLem}, we have $|\pi(S)| \geq \dim(\bm{\mathcal{B}}_{\pi(S)}) \geq \dim(\bm{\mathcal{A}}_S) = |S|$, the final equality holding by injectivity of $\mathbf{A}_S$.
+Note that since $\|\mathbf{A}\mathbf{x}\|_2 \leq \max_j\|\mathbf{A}_j\|_2\|\mathbf{x}\|_1$ and $\|\mathbf{x}\|_1 \leq \sqrt{k} \|\mathbf{x}\|_2$ for all $k$-sparse $\mathbf{x}$, by \eqref{Ldef} we have $L_2(\mathbf{A}) \leq \max_j\|\mathbf{A}_j\|_2$ and therefore (as $0 \leq \xi < 1$), the right-hand side of \eqref{GapUpperBound} is less than one.
+From \eqref{dimLem}, we have $|\pi(S)| \geq \dim(\bm{\mathcal{B}}_{\pi(S)}) \geq \dim(\bm{\mathcal{A}}_S) = |S|$, the final equality by injectivity of $\mathbf{A}_S$.
 As $|\pi(S)| = |S|$, the claim follows.
@@
 We next demonstrate that \eqref{cond} holds.
-Fixing $\mathcal{G} \in {\mathcal{H} \choose r} \cup {\mathcal{H} \choose r+1}$, it suffices to show that $d(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}, \bm{\mathcal{A}}_{\cap \mathcal{G}} ) < 1$, since by \eqref{dimLem} we then have $|\cap \pi(\mathcal{G})| = \dim(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}) \leq \dim(\bm{\mathcal{A}}_{\cap \mathcal{G}}) = |\cap \mathcal{G}|$, with equalities from the full column-ranks of $\mathbf{A}_{S}$ and $\mathbf{B}_{\pi(S)}$ for all $S \in \mathcal{H}$.\footnote{Note that if ever $\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})} \neq \bf 0$ while $\cap \mathcal{G} = \emptyset$, we would have $d(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}, \bm 0 ) = 1$.
-However, that leads to a contradiction.} Observe that $d(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}, \bm{\mathcal{A}}_{\cap \mathcal{G}}  )
-\leq d\left( \cap \bm{\mathcal{B}}_{\pi(\mathcal{G})}, \cap \bm{\mathcal{A}}_\mathcal{G} \right)$ by \eqref{UsubU}, since trivially $\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})} \subseteq \cap \bm{\mathcal{B}}_{\pi(\mathcal{G})}$ and also $\bm{\mathcal{A}}_{\cap \mathcal{G}} = \cap \bm{\mathcal{A}}_\mathcal{G}$ by Lem.~\ref{spanIntersectionLemma}.
+Fixing $\mathcal{G} \in {\mathcal{H} \choose r} \cup {\mathcal{H} \choose r+1}$, it suffices to show that $d(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}, \bm{\mathcal{A}}_{\cap \mathcal{G}} ) < 1$, since by \eqref{dimLem} we then have $|\cap \pi(\mathcal{G})| = \dim(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}) \leq \dim(\bm{\mathcal{A}}_{\cap \mathcal{G}}) = |\cap \mathcal{G}|$, with equalities by the full column-ranks of $\mathbf{A}_{S}$ and $\mathbf{B}_{\pi(S)}$ for all $S \in \mathcal{H}$.\footnote{Note that if ever $\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})} \neq \bf 0$ while $\cap \mathcal{G} = \emptyset$, we would have $d(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}, \bm 0 ) = 1$.
+This cannot be the case, however, since the deduction that follows would then lead to a contradiction.} Observe that $d(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}, \bm{\mathcal{A}}_{\cap \mathcal{G}}  )
+\leq d\left( \cap \bm{\mathcal{B}}_{\pi(\mathcal{G})}, \cap \bm{\mathcal{A}}_\mathcal{G} \right)$, by \eqref{UsubU} since trivially $\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})} \subseteq \cap \bm{\mathcal{B}}_{\pi(\mathcal{G})}$ and since $\bm{\mathcal{A}}_{\cap \mathcal{G}} = \cap \bm{\mathcal{A}}_\mathcal{G}$ by Lem.~\ref{spanIntersectionLemma}.
 Recalling Def.~\ref{dDef} and applying Lem.~\ref{DistanceToIntersectionLemma} yields:
@@
 passing the maximum through the sum.
-Since $\cap \bm{\mathcal{B}}_{\pi(\mathcal{G})} \subseteq \bm{\mathcal{B}}_{\pi(S)}$ for all $S \in \mathcal{G}$, by \eqref{UsubU} the numerator of each term in the sum above is bounded by \mbox{$d\left( \bm{\mathcal{B}}_{\pi(S)},\bm{\mathcal{A}}_{S} \right) = d\left(\bm{\mathcal{A}}_{S}, \bm{\mathcal{B}}_{\pi(S)} \right) \leq \varepsilon$}, with the equality from \eqref{eqdim} since $\dim(\bm{\mathcal{B}}_{\pi(S)}) = \dim(\bm{\mathcal{A}}_S)$.
+Since $\cap \bm{\mathcal{B}}_{\pi(\mathcal{G})} \subseteq \bm{\mathcal{B}}_{\pi(S)}$ for all $S \in \mathcal{G}$, by \eqref{UsubU} the numerator of each term in the sum above is bounded by \mbox{$d\left( \bm{\mathcal{B}}_{\pi(S)},\bm{\mathcal{A}}_{S} \right) = d\left(\bm{\mathcal{A}}_{S}, \bm{\mathcal{B}}_{\pi(S)} \right) \leq \varepsilon$}, with equality by \eqref{eqdim} since $\dim(\bm{\mathcal{B}}_{\pi(S)}) = \dim(\bm{\mathcal{A}}_S)$.
 Thus, altogether:
@@
 
-Applying Lem.~\ref{NonEmptyLemma}, the association $i \mapsto \cap_{S \in \sigma(i)} \pi(S)$ is an injective map $\overline \pi: J \to [\overline m]$ for some $J \subseteq [m]$ of size $m - (r-1)(\overline m - m)$, and $\mathbf{B}_{\overline \pi(i)} \neq \mathbf{0}$ for all $i \in J$ since the columns of $\mathbf{B}_{\pi(S)}$ are linearly independent for all $S \in \mathcal{H}$.
+By Lem.~\ref{NonEmptyLemma}, the association $i \mapsto \cap \pi(\sigma(i))$ is an injective map $\overline \pi: J \to [\overline m]$ for some $J \subseteq [m]$ of size $m - (r-1)(\overline m - m)$, and $\mathbf{B}_{\overline \pi(i)} \neq \mathbf{0}$ for all $i \in J$ since we have shown the columns of $\mathbf{B}_{\pi(S)}$ to be linearly independent for all $S \in \mathcal{H}$.
 Letting $\overline \varepsilon := C_2 \varepsilon / \max_i \|\mathbf{A}_i\|_2$, it follows from \eqref{eqdim} and \eqref{last} that $d\left( \bm{\mathcal{A}}_i, \bm{\mathcal{B}}_{\overline \pi(i)} \right) = d\left(\bm{\mathcal{B}}_{\overline \pi(i)},  \bm{\mathcal{A}}_i \right)  \leq \overline \varepsilon$ for all $i \in J$.
@@
 But this is exactly the supposition in \eqref{1D}, and the result follows from the case $k=1$ in Sec.~\ref{DUT} applied to the submatrix $\mathbf{A}_J$.
-Setting $c_i := \|\mathbf{A}_i\|_2^{-1}$ so that $\|c_i\mathbf{Ae}_i\|_2 = 1$, by Def.~\ref{dDef} for all $i \in J$:
+Setting $c_i := \|\mathbf{A}_i\|_2^{-1}$ so that $\|c_i\mathbf{Ae}_i\|_2 = 1$, by Def.~\ref{dDef} we have for all $i \in J$:
 \begin{align*}
@@
 But this is exactly the supposition in \eqref{1D}, with $J$ and $\overline \varepsilon$ in place of $[m]$ and $\varepsilon$, respectively.
-The same arguments of the case $k=1$ in Sec.~\ref{DUT} can then be made to show that for any $\overline m \times \overline m$ permutation and invertible diagonal matrices $\mathbf{P}$ and $\mathbf{D}$ with, respectively, columns $\mathbf{e}_{\pi(i)}$ and $\frac{\overline{c}_i}{c_i}\mathbf{e}_i$ for $i \in J$ (otherwise, $\mathbf{e}_{i}$ for $i \in [\overline{m}] \setminus J$), we have $\|\mathbf{A}_i - (\mathbf{B}\mathbf{PD})_i \|_2 \leq \overline  \varepsilon / |c_i|  \leq C_2 \varepsilon$ for all $i \in J$.
+The same arguments of the case $k=1$ in Sec.~\ref{DUT} can then be made to show that for any $\overline m \times \overline m$ permutation and invertible diagonal matrices $\mathbf{P}$ and $\mathbf{D}$ with, respectively, columns $\mathbf{e}_{\pi(i)}$ and $\frac{\overline{c}_i}{c_i}\mathbf{e}_i$ for $i \in J$ (and, say, $\mathbf{e}_i$ otherwise) we have $\|\mathbf{A}_i - \mathbf{B}\mathbf{PD}_i \|_2 \leq \overline  \varepsilon / |c_i|  \leq C_2 \varepsilon$ for all $i \in J$.
 \end{proof}

### 2020-08-04 manuscripts/PNAS/second review/code/constants.py

@@ -119,7 +119,7 @@ if __name__ == '__main__':
     Ks = [4, 8, 16]
     for k in Ks:
         m = k**2
-        n = m;
+        n = m
         square_grid = np.reshape(range(m),(k,k))
         H = [row.tolist() for row in square_grid] + [col.tolist() for col in square_grid.T]
         N_per_support = int((k - 1) * choose(m, k))

### 2020-08-04 manuscripts/PNAS/second review/code/sample_complexity.py

@@ -77,7 +77,7 @@ if __name__ == '__main__':
 
     We plot this as a function of m for fixed k.
     Assume H is the set of contiguous length-k intervals of [m] arranged in cyclic order, so that |H| = m.
-    """
+
     k = 3 # Fixed sparsity, i.e. H is k-uniform
     m_min = k+1 # since k < m required for H to satisfy SIP
     m_max = 20 # Max dictionary size
@@ -108,3 +108,4 @@ if __name__ == '__main__':
     pp.savefig('./figures/samples_vs_m.png')
 
     #axes[1].plot(range(m_min,m_max+1), [Np / Nd for Np, Nd in zip(N_probabilistic, N_deterministic)])
+    """

### 2020-08-04 manuscripts/IEEE/revisions/response.txt
everything

--- 2019-05-07 manuscripts/IEEE/submission/referee_responses.txt
@@
--------------------------------------
-Author responses to referees:
-"On the uniqueness and stability of dictionaries 
-for sparse representation of noisy signals"
-C. Garfinkle, C. Hillar
--------------------------------------
-
 REVIEWER 1
@@
 
--------------------------------------
-Response: The full sentence is: "By compactness of the unit sphere, injective linear maps have nonzero lower bound; hence, if M satisfies (2), then each submatrix formed from 2k of its columns or less has a strictly positive lower bound." Here, k is the sparsity referred to in (2), which states that a matrix M satisfies the spark condition if Mx1 = Mx2 implies x1 = x2, for all k-sparse x1, x2.
--------------------------------------
+The full sentence is: "By compactness of the unit sphere, injective linear maps have nonzero lower bound; hence, if M satisfies (2), then each submatrix formed from 2k of its columns or less has a strictly positive lower bound." Here, k is the sparsity referred to in (2), which states that a matrix M satisfies the spark condition if Mx1 = Mx2 implies x1 = x2, for all k-sparse x1, x2.
 
@@
 
--------------------------------------
-Response: The requirement becomes clearer recalling the definition L_k := L_(m choose k). Our statement is then:
+The requirement becomes clearer recalling the definition L_k := L_(m choose k). Our statement is then:
 
@@
 The first inequality follows from the fact that (m choose 2) is a subset of 2H, provided ∪H = [m], since only then can every pair of columns be captured by the union of two supports in H.
--------------------------------------
 
@@
 
--------------------------------------
-Response: Yes. We have clarified this ambiguity.
--------------------------------------
+Yes. We have clarified this ambiguity.
 
@@
 
--------------------------------------
-Response: That is correct.
+That is correct.
 We see no need to worry.
@@
 To rephrase via the triangle inequality, all good enough B’s and \bar{x}_i’s are similar to one another, or identical when \epsilon = 0.
--------------------------------------
 
@@
 
--------------------------------------
-Response: We have altered the notation to abate this potential confusion.
--------------------------------------
+We have altered the notation to abate this potential confusion.
 
@@
 
--------------------------------------
-Response: The assumptions of Theorem 1 are:
+The assumptions of Theorem 1 are:
 i) L_2H(A) > 0 for an r-regular H with the SIP.
@@
 Thus, as presented, C1 and C2 are not efficiently computable."
--------------------------------------
 
@@
 
--------------------------------------
-Response: "Substitution" here mean such assignments or choices of real numbers to the indeterminate variables, yes.
+"Substitution" here mean such assignments or choices of real numbers to the indeterminate variables, yes.
 We frame it as a theorem and not a corollary because we draw the important Corollary 2 directly from it.
@@
 [NOTE: should we just make everything a corollary of Thm 1..? Even Thm 2?]
--------------------------------------
 
@@
 
--------------------------------------
-Response: To be clear, this (bold) observation is just an observation which motivates the work.
+To be clear, this (bold) observation is just an observation which motivates the work.
 Imagining natural image patches to form a population which satisfies (1) with respect to some ground truth dictionary A, we have shown that there exists a sufficient number of samples to uniquely identify it or something close to it via approximate solutions.
 Given this fundamental stability and uniqueness of the problem solutions, the fact that a variety of methods geared to approximately solve Problems 1 and 2 all seem to capture similar structure is much less surprising.
--------------------------------------
 
@@
 
--------------------------------------
-Response: Theorem 2 guarantees that all globally optimal solutions to Problem 2 are identical up to noise and inherent permutation/scaling ambiguities.
+Theorem 2 guarantees that all globally optimal solutions to Problem 2 are identical up to noise and inherent permutation/scaling ambiguities.
 This doesn't change the fact that computing any one such global solution given data is still NP-hard.
@@
 It could be that in certain restricted cases these conditions are efficiently computable, but this is not the case in general.
--------------------------------------
 
@@
 
--------------------------------------
-Response: We comment on sample complexity in the last paragraph of Section II:
+We comment on sample complexity in the last paragraph of Section II:
 
@@
 "We note that $1 - \sqrt{k} L_k(\mathbf{M})$ is known as the asymmetric lower restricted isometry constant for matrices $\mathbf{M}$ with unit $\ell_2$-norm columns"
--------------------------------------
 
@@
 
--------------------------------------
-Response: In the prose surrounding Corollary 1 we give a deterministic construction of sparse vectors x_i satisfying the constraints of Theorem 1.
+In the prose surrounding Corollary 1 we give a deterministic construction of sparse vectors x_i satisfying the constraints of Theorem 1.
 
 TODO : can we deterministically generate matrices injective on SIP hyper graphs? The (mCk)-hypergraph is one such possibility, so maybe not in general? But for special cases (convolution matrices..?)
--------------------------------------

### 2020-08-04 manuscripts/PNAS/first review/point_by_point_response.txt
everything

--- 2017-08-21 manuscripts/PNAS/review/point_by_point_response.txt
@@
 However, our main result (Thm.
-1) generalizes the noise-free result of (HS15) far beyond a simple extension to the noisy case in ways which provide valuable insight into the dictionary learning model and, moreover, a significant deviation from the approach taken in (HS15) was necessary to prove these new facts.
+1) generalizes the noise-free result of (HS15) far beyond a simple extension to the noisy case in ways that provide valuable insight into the dictionary learning model; and, moreover, a significant deviation from the approach taken in (HS15) was necessary to prove these new facts.
 Additionally, our solution (Cor.
@@
 
-We next respond to the reviewer's question about the mathematical "tightness" for the three types of quantities in our results : (a) required coding error eps(delta_1, delta_2) sufficient to guarantee uniqueness in terms of desired dictionary delta_1 and sparse representation error delta_2, (b) the constants C_1 and C_2 involved in our sufficient linear bound on eps(delta_1, delta_2) in terms of the noise, and (c) the number of sufficient samples N guaranteeing uniqueness.
+We next respond to the reviewer's question about the mathematical "tightness" for the three types of quantities in our results : (a) required coding error eps(delta_1, delta_2) sufficient to guarantee uniqueness in terms of desired dictionary, delta_1, and sparse representation error, delta_2; (b) the constants C_1 and C_2 involved in our sufficient linear bound on eps(delta_1, delta_2) in terms of the noise; and (c) the number of sufficient samples N guaranteeing uniqueness.
 With respect to (a), even with fixed dictionary, the recovery of sparse representations up to an error that is linear in the noise is essentially optimal (ACD13) (up to constants).
-Thus, the fact that we have a sufficient error in coding for uniqueness being linear for both the desired dictionary and sparse vector recovery error is optimal.
+Thus, the fact that we have a sufficient error in coding for uniqueness being (asymptotically) linear for both the desired dictionary and sparse vector recovery error is optimal.
 Although optimal, our solution to Problem 1 involves constants C_1 and C_2, and it would be interesting and relevant for practical applications to determine the minimal such constants.
@@
 Finally, with respect to (c), we regard this as a fundamental open problem in the field: how many sparsely generated samples determine the linear coding model?
-(One reason to be skeptical that a polynomial suffice is again (TP14, T15).)  However, there is some good news -- if k is fixed or if the sparse codes \bar x_i are known to come from a polynomial number of supports, then a polynomial number of samples N is enough to guarantee uniqueness.
-We have revised the manuscript to discuss this last fact (which, incidentally, does not follow from the results of (HS15) in the noiseless case).
+(One reason to be skeptical that a polynomial suffice is (TP14, T15).)  However, there is some good news -- if k is fixed or if the sparse codes \bar x_i are known to come from a polynomial number of supports, then a polynomial number of samples N is enough to guarantee uniqueness (which, incidentally, does not follow from the results of (HS15) in the noiseless case).
+We have revised the manuscript to discuss these points.
 
@@
 2 is indeed unique.
-We have updated the manuscript with an explicit statement of this fact, and outline one such procedure here:
+We have updated the manuscript with an explicit statement of this fact, and we outline one such procedure here:
 
-Given a dictionary A and codes x_i that solve Problem 1 (e.g. learned by any algorithm), check that that they satisfy the assumptions of Thm. 1:
-   - List the support sets of the x_i 
+Given a dictionary A and codes x_i that solve Problem 1 (e.g., learned by any algorithm), check that that they satisfy the assumptions of Thm. 1:
+   - List the support sets of the x_i.
    - Discard those for which there are (k-1){m \choose k} or fewer x_i with that support.
    - Discard those for which the supported x_i are not in general linear position. (This should also exclude any supports less than k in size.)
-   - From the support sets that remain, list all SIP-satisfying hypergraphs that are subsets of this set
+   - From the support sets that remain, list all SIP-satisfying hypergraphs that are subsets of this set.
    - Discard those for which L_{2H}(A) = 0.
-   - For each of the remaining hypergraphs, determine the constant C_1 from A and the x_i (or for every subset of the x_i of size (k-1){m \choose k})
+   - For each of the remaining hypergraphs, determine the constant C_1 from A and the x_i (or for every subset of the x_i of size (k-1){m \choose k}).
    - Check that the derived upper bound on \varepsilon exceeds that of the original problem. If yes, the solution is "unique".
@@
 In contrast to the noiseless case, here it must be explicitly demonstrated that this proximity relation is propagated through the repeated intersections of these submatrix spans all the way down to the spans of dictionary elements themselves.
-We designed and proved Lemma 4 to address this issue, which draws its bound from the convergence guarantees of an alternating projections algorithm first proposed by von Neumann.
+We designed and proved Lemma 3 to address this issue, which draws its bound from the convergence guarantees of an alternating projections algorithm first proposed by von Neumann.
 This result, combined with a little known fact about the distance ‘d’ requiring proof in (M10), constitute the more obscure components of the deduction in Eq.
@@
 
-Our proof of Lemma 1 diverges perhaps even more significantly from the approach taken in (HS15) by way of Lemma 5.
+Our proof of Lemma 1 diverges perhaps even more significantly from the approach taken in (HS15) by way of Lemma 4.
 Key to our reduction of the sample complexity given in (HS15) by an exponential factor is the introduction of a combinatorial design (the "singleton intersection property") for support sets.
-Since in this case the map \pi from supports in the hypergraph to {[m] \choose k} is not surjective, one cannot apply the same inductive method as in (HS15), which freely chooses supports in the codomain to intersect at (k-1) nodes and map back to some corresponding (k-1)-sized intersection of supports in the domain.
+Since in this case the map \pi from supports in the hypergraph to {[m] \choose k} is not surjective, one can not apply the same inductive method as in (HS15), which freely chooses supports in the codomain to intersect at (k-1) nodes and map back to some corresponding (k-1)-sized intersection of supports in the domain.
 Instead, we demonstrate the surprising fact that by pigeonholing the images of supports in the (SIP-satisfying) hypergraph H, one can still guarantee a bijection between the nodes and therefore the subspaces spanned by individual dictionary elements.
-We note that it was necessary to forgo inductive methods altogether in order to prove this fact for all hypergraphs satisfying the SIP; otherwise, we would require that the supports in the hypergraph have intersections of size k’ for every k’ < k (e.g.
-this is not the case for the small SIP example we give consisting of the rows and columns of nodes arranged in a square grid).
+We note that it was necessary to forgo inductive methods altogether in order to prove this fact for all hypergraphs satisfying the SIP; otherwise, we would require that the supports in the hypergraph have intersections of size k’ for every k’ < k (e.g., this is not the case for the small SIP example we give consisting of the rows and columns of nodes arranged in a square grid).
 Again, to our surprise, it so happens that this new induction-less argument easily generalizes to the case where B has an arbitrary number of columns, in which case we find that a one-to-one correspondence exists between a subset of columns of A and B of a size that has a nice closed-form expression for regular SIP hypergraphs.
@@
 Then A satisfies the assumptions of Thm.
-1 for dictionary recovery without satisfying the spark condition.) We had omitted this point in our original submission of the manuscript to keep things simple, but have decided to include this fact in our resubmission.
+1 for dictionary recovery without satisfying the spark condition.) We had omitted this point in our original submission of the manuscript to keep things simple, but we have decided to include this fact in our revision.
 This also required us to redefine the restricted matrix lower bound L_k to be in terms of a hypergraph H (L_H in the revised manuscript), which is an interesting object for further study in its own right.
@@
 (2) can be obtained from the construction based on a Vandermonde matrix which we provide; rather, the point is that almost every matrix satisfies Eq.
-(2) because at least one matrix does (e.g.
-our construction) and therefore, since f is analytic, the set of all those that do not satisfy the condition has measure zero.
+(2) because at least one matrix does (e.g., our construction) and therefore, since f is analytic, the set of all those that do not satisfy the condition has measure zero.
 We have updated the manuscript to clarify this argument for our readers.

### 2020-08-04 berkeley_thesis_template/abstract.tex
everything

\begin{abstract}

The general problem of solving systems of polynomial equations has a rich history and progression.  We study a collection of problems that give rise to systems of equations with nice structure.  We exploit such special structure using a variety of techniques, thereby solving the original problems.

Our tools are diverse, involving algebraic combinatorics, semigroup algebras, Brouwer degree theory, fixed-point methods, and the theory of Gr\"obner bases, to name a few.

\abstractsignature
\end{abstract}

### 2020-08-04 berkeley_thesis_template/ch1.tex
everything

 \chapter{Outline of Techniques}

Before embarking on our thesis journey, we present here the collection of techniques, tools, and definitions that underlie the proofs of our main results.  They are listed here primarily because readers might find them useful for other applications.

\section{Gr\"obner Bases}

\section{Brouwer Mapping Degree and Fixed-Point Theory}

In this section, we give a brief overview of degree theory, and
some of its main implications.  The bulk of this discussion is material taken from \cite{degthy, teschl}.  First we introduce some notation.  Let $U$ be a bounded open subset of $\mathbb R^m$.  We denote the set of $r$-times differentiable functions from $U$ ($\overline{U}$) to $\mathbb R^m$ by $C^r(U,\mathbb R^m)$ ($C^r(\overline{U},\mathbb R^m)$) (when $r = 0$, $C^r(U,\mathbb R^m)$ is the set of continuous functions).  The \textit{identity function} id satisfies id$(\mathbf x) = \mathbf x$.  If $f \in C^1(U,\mathbb R^m)$, then the \textit{Jacobi matrix} of $f$ at a point $\mathbf {x} \in U$ is \[f'(\mathbf {x}) = \left(  \frac{\partial f_j}{\partial x_i}(\mathbf{x}) \right)_{1\leq i,j \leq m}\] and the \textit{Jacobi determinant} (or simply \textit{Jacobian}) of $f$ at $\mathbf{x}$ is \[ J_f(\mathbf{x}) = \det f'(\mathbf{x}).\]  The set of \textit{regular values} of $f$ is \[\text{RV}(f) = \left\{\mathbf{y}\in \mathbb R^m : \forall \mathbf{x} \in f^{-1}(\mathbf{y}), \ J_f(\mathbf{x}) \neq 0\right\}\] and for $\mathbf{y} \in \mathbb R^m$, we set \[D^r_{\mathbf{y}}(\overline{U},\mathbb R^m) = \left\{ f \in C^r( \overline{U},\mathbb R^m) : \mathbf{y} \notin f(\partial U) \right\} .\]

A function $\text{deg}: D^{0}_{\mathbf{y}}(\overline{U},\mathbb R^m) \to \mathbb R$ which assigns to each $f \in D^{0}_{\mathbf{y}}(\overline{U},\mathbb R^m)$ and $\mathbf{y} \in R^m$ a real number deg$(f,U,\mathbf{y})$ will be called a \textit{degree} if it satisfies the following conditions.

%\renewcommand{\enumi}{$D$}

\begin{enumerate}
\item $\deg(f,U,\mathbf{y}) = \deg(f-\mathbf y, U, 0)$ (\textit{translation invariance}).
\item $\deg(\mathrm{id}, U, \mathbf y) = 1$ if $\mathbf y \in U$ (\textit{normalization}).
\item If $U_1$ and $U_2$ are open, disjoint subsets of $U$ such that $\mathbf  y \notin f(\overline{U} \setminus (U_1 \cup U_2))$, then $\deg(f,U,\mathbf y) = \deg(f,U_1,\mathbf y) +\deg(f,U_2,\mathbf y)$ (\textit{additivity}). 
\item If $H(t) = tf + (1-t)g \in D^{0}_{\mathbf{y}}(\overline{U},\mathbb R^m)$ for all $t \in [0,1]$, then $\deg(f,U,\mathbf y) = \deg(g,U,\mathbf y)$ (\textit{homotopy invariance}).
\end{enumerate}

Motivationally, one should think of a degree map as somehow ``counting'' the number of solutions to $f(\mathbf x) = \mathbf y$.  Condition $(1)$ reflects that the solutions to $f(\mathbf x) = \mathbf y$ are the same as those of $f(\mathbf x)- \mathbf y = 0$, and since any multiple of a degree will satisfy $(1)$, $(3)$, and $(4)$, the condition $(2)$ is a normalization.  Additionally, $(3)$ is natural since it requires $\deg$ to be additive with respect to components.

Of course, we need a theorem guaranteeing that a degree even exists.

\begin{theorem}
There is a unique degree $\deg$.  Moreover, $\deg(\cdot, U, \mathbf y):  D^0_{\mathbf{y}}(\overline{U},\mathbb R^m) \to \mathbb Z$.
\end{theorem}

When functions are differentiable, a degree can be calculated explicitly in terms of Jacobians at solutions to the equation $f(\mathbf x) = \mathbf y$.

\begin{theorem}\label{sumjacob}
Suppose that $f \in D^1_{\mathbf y}(\overline{U},\mathbb R^m)$ and $\mathbf y \in \text{\rm{RV}}$.  Then a degree satisfies \[\deg(f,U,\mathbf y) = \sum_{\mathbf x \in f^{-1}(\mathbf y)} {\text{\rm{sgn}} \  J_f(\mathbf x)},\] where this sum is finite and we adopt the convention that $\sum_{\mathbf x \subseteq  \emptyset} = 0$.
\end{theorem}

\section{Algebraic Combinatorics and Generating Functions}

\section{Well-Quasi-Orderings}

A {\bf quasi-ordering} on a set
$S$ is a binary relation $\leq$ on $S$ which is reflexive and
transitive. 
A {\bf quasi-ordered
set} is a pair $(S,\leq)$ consisting of a set $S$ and a quasi-ordering $\leq$
on $S$. (If no confusion is possible, we will omit $\leq$ from the notation,
and just call $S$ a quasi-ordered set.)
If in addition the relation $\leq$ is anti-symmetric,
then $\leq$ is called an {\bf ordering} on the set $S$, and
$(S,\leq)$ (or $S$) is called an {\bf ordered set.}
A quasi-ordering $\leq$ on a set $S$ induces an
ordering on the set $S/{\sim}=\{a/{\sim}:a\in S\}$ 
of equivalence classes of the equivalence
relation $x\sim y 
\Longleftrightarrow x\leq y \ \&\ y\leq x$ on 
$S$ in a natural way. 
If $x$ and $y$ are elements of a  quasi-ordered set $(S,\leq)$, 
we write as usual $x\leq y$ also as $y\geq x$, and 
we write $x<y$ if $x\leq y$ and $y\not\leq x$.

Suppose that $(S,{\leq}_S)$ is a quasi-ordered set.
The restriction ${\leq_U}:={{\leq_S}\cap (U\times U)}$ 
of the quasi-ordering $\leq_S$ makes $U\subseteq S$
into a quasi-ordered set. If $\leq_S$ is an ordering, then
so is  $\leq_U$.  
Let $(T,{\leq}_T)$ be another quasi-ordered set.
The cartesian product $S\times T$ of $S$ and $T$ can be
made into a quasi-ordered set by means of the {\bf product quasi-ordering}
$(x,y) \leq_{S\times T} (x',y') \Longleftrightarrow x\leq_S x' \text{ and }
y\leq_T y'$.
If $\leq_S$ and $\leq_T$ are orderings, then so is $\leq_{S\times T}$.
Taking $S=T$ and repeating this construction yields 
the product quasi-ordering on $S^n$.

\begin{example}\label{example-Nn}
We consider $\N=\{0,1,2,\dots\}$ as an ordered set with its usual ordering, and we equip
$\N^n$ with 
the product ordering. 
\end{example}

\subsection*{Final segments and antichains}
A {\bf final segment} of a  quasi-ordered set $(S,\leq)$ is a
subset $F \subseteq S$ which is closed upwards:
$x\leq y \wedge x\in F \Rightarrow y\in F$, for all $x,y\in S$.
We construe the set ${\cal F}(S)$ of final segments of $S$ as
an ordered set, with the ordering given by {\sl reverse}\/ inclusion.
Given a subset $M$ of $S$, the set 
$\bigl\{y \in S : \exists x \in M\ ( x \leq y ) \bigr\}$
is a final segment of $S$,  the final segment {\bf generated by $M$.}
An {\bf antichain} of $S$ is a subset $A \subseteq S$
such that $x \not\leq y$ and $y\not\leq x$ for all  $x\not\sim y$ in $A$.

\subsection*{Well-quasi-orderings}
A quasi-ordered set $S$ is {\bf well-founded} if 
there is no
infinite strictly decreasing sequence $x_0 > x_1 > \cdots $ in $S$. 
A quasi-ordered set $S$ is {\bf well-quasi-ordered}
if it is well-founded, and every antichain of $S$ is finite.
The following characterization of well-quasi-orderings is classical.
(See, e.g., \cite{Kruskal}.) An infinite sequence 
$s_0,s_1,\dots$
in $S$ such that $s_i\leq s_j$ for some indices $i<j$
is called {\bf good}, and {\bf bad} otherwise.

\begin{prop}
The following are equivalent, for a quasi-ordered set $S$:
\begin{enumerate}
\item $S$ is a well-quasi-ordering.
\item Every infinite sequence in $S$ is good. 
\item Every infinite sequence in $S$ contains an infinite increasing
subsequence.
\item Any final segment of $S$ is finitely generated.
\item $\bigl(\mathcal{F} ( S ),\supseteq\bigr)$ is well-founded \textup{(}i.e., the ascending chain
condition with respect to inclusion holds for final segments of $S$\textup{).} \qed
\end{enumerate}
\end{prop}

Suppose $(S,{\leq}_S)$ and
$(T,{\leq}_T)$ are well-quasi-ordered sets. Then
the induced quasi-ordering on a subset of $S$ is a
well-quasi-ordering, and 
the cartesian product $S\times T$ of $S$ and $T$ is well-quasi-ordered.
(Easily seen, e.g., using the equivalence of (1) and (3) above.)
Inductively, it follows that the product quasi-ordering on
$S^n$ is a well-quasi-ordering, for
every $n>0$. (With $S=\N$ this is known as ``Dickson's Lemma''.)

### 2020-08-04 berkeley_thesis_template/ch2.tex
everything

\chapter{Infinite Permutation Ideals in Countable Polynomial Rings are Noetherian}

\section{Finiteness result}

Let $\Omega$ be the set of monomials in indeterminates $p_1, p_2,
\ldots$ (including the ``monomial'' $1$).  Order these monomials
lexicographically with $p_1 < p_2 < \cdots$.  The following fact
is immeadiate.

\begin{lemma}
The ordering $\leq$ is a well-ordering.
\end{lemma}

\begin{proof} Let $S$ be any nonempty set of monomials and $m = p_1^{a_1}\cdots
p_n^{a_n} \in S$.  It suffices to show that $T = \{q \in S: q <
m\}$ has a smallest element. If $q = p_1^{b_1}\cdots p_t^{b_t} \in
T$ with $b_t \neq 0$, then $t \leq n$.  In particular, $q$ only
involves the variables $p_1,\ldots,p_n$.  But it is well-known
that a set of monomials in the variables $p_1,\ldots,p_n$ with
lexicographic order has a least element (``Dickson's Lemma'').
\end{proof}

Consider the $\C$-algebra $R = \C[p_1,p_2,\ldots]$ generated by
$\Omega$ with the natural ring operations.  Also, let $R {\frak
S}_{\infty}$ be the (right) group ring with multiplication $r
\sigma \cdot s \tau = rs (\sigma \tau)$, and view $R$ as an $R
{\frak S}_{\infty}$-module in the standard way.  Suppose one has
an ideal $I$ of $R$ invariant under $R {\frak S}_{\infty}$; that
is, ${\frak S}_{\infty}I \subseteq I$ (so that $R{\frak
S}_{\infty}I \subseteq I$).  A natural question is the following.

\begin{question}
Is $I$ finitely generated as a $R {\frak S}_{\infty}$-module?
\end{question}

Before answering this question in the affirmative, we gather some
preliminary results.  Given the set of monomials $\Omega$, we
define a quasi-ordering as follows:
\begin{definition}
\[P \preceq Q \quad
:\Longleftrightarrow \quad \begin{cases} &\text{\parbox{160pt}{$P
\leq Q$, there exist $\sigma \in {\frak S}_{\infty}$ and a
monomial $m \in \Omega$ with $Q = m \sigma P$, and $U \leq P
\Rightarrow m \sigma U \leq Q$}}\end{cases}\]
\end{definition}

\begin{example}
As an example of this quasi-ordering, consider the following
chain, \[p_1^2 \preceq p_1p_2^2 \preceq p_1^3p_2p_3^2.\]  To
verify the first inequality, notice that $p_1p_2^2 = p_1 \sigma
(p_1^2)$, in which $\sigma$ is the transposition $(12)$.  If $U =
p_1^{u_1}\cdots p_n^{u_n} \leq p_1^2$, then it follows that $n =
1$ and $u_1 \leq 2$.  In particular, $p_1 \sigma U = p_1p_2^{u_1}
\leq p_1p_2^2$.

For the second relationship, we have that $p_1^3p_2p_3^2 = p_1^3
\tau (p_1p_2^2)$, in which $\tau$ is the cycle $(123)$.
Additionally, if $U = p_1^{u_1}\cdots p_n^{u_n} \leq p_1p_2^2$,
then $n = 2$ and $u_2 \leq 2$.  Also, if $u_2 = 2$, then $u_1 \leq
1$.  It follows, therefore, that $p_1^3 \tau U = p_1^3
p_2^{u_1}p_3^{u_2} \leq p_1^3p_2p_3^2$. \qed
\end{example}

Although this definition appears technical, the reason for its
introduction will become clear in the proof of the theorem above.
Since our ordering of monomials is linear ($u \leq v
\Longleftrightarrow uw \leq vw$ for all monomials $u,v,w$), this
last condition may be rewritten as $U \leq P \Rightarrow \sigma U
\leq \sigma P$.  Let us see that it is a quasi-ordering. First
notice that $P \preceq P$ since we may take $m = 1$ and $\sigma$,
the identity permutation.  Next, suppose that $P \preceq Q \preceq
T$. Then, there exist permutations $\sigma$, $\tau$ and monomials
$m_1,m_2$ such that $Q = m_1 \sigma P$, $T = m_2 \tau Q$.  In
particular, $T = m_2 (\tau m_1)(\tau \sigma P)$.  Additionally, if
$U \leq P$, then $m_1 \sigma U \leq Q$ so that $m_2 \tau (m_1
\sigma U) \leq T$.  It follows that $m_2 (\tau m_1)(\tau \sigma U)
\leq T$, which is the requirement for transitivity.

We shall also prove that $\preceq$ is a well-quasi-ordering. We
begin with some preliminary lemmas.  In what follows, it will be
convenient to represent monomials $p_1^{a_1}\cdots p_n^{a_n}$ as
vectors ($a_1,\ldots,a_n,0,\ldots$), and we will move freely from
one representation to the other.

\begin{lemma}\label{oneshiftuplem}
Suppose that $(a_1,\ldots,a_n,0,\ldots) \preceq
(b_1,\ldots,b_t,0,\ldots)$. Then, for any $c \in \N$,
$(a_1,\ldots,a_n,0,\ldots) \preceq (c,b_1,\ldots,b_t,0,\ldots)$.
\end{lemma}

\begin{proof}
First notice that we may assume that $n \leq t$ since
$(a_1,\ldots,a_n,0,\ldots)$ $\leq (b_1,\ldots,b_t,0,\ldots)$.  Let
$(c_1,c_2,\ldots,c_{t+1},0,\ldots)$ =
$(c,b_1,\ldots,b_t,0,\ldots)$, in which $c_1 = c$ and $c_i =
b_{i-1}$ for $i > 1$.  Since $(a_1,\ldots,a_n,0,\ldots) \preceq
(b_1,\ldots,b_t,0,\ldots)$, there exists a permutation $\sigma$
such that $p_{\sigma(1)}^{a_1} \cdots p_{\sigma(n)}^{a_n} \, \mid
\, p_{1}^{b_1} \cdots p_{t}^{b_t}$. Let $\tau$ be the cyclic
permutation $\tau = (123 \cdots (t+1))$.   Then, $\hat{\sigma} =
\tau \sigma$ is such that $p_{\hat{\sigma}(1)}^{a_1} \cdots
p_{\hat{\sigma}(n)}^{a_n} \, \mid \, p_{1}^{c_1} \cdots
p_{t+1}^{c_{t+1}}$.

Next, suppose that $U = p_1^{u_1} \cdots p_n^{u_n} \leq
p_{1}^{a_1} \cdots p_{n}^{a_n} = P$.  By assumption, $\sigma U
\leq \sigma P$, so that \[\hat{\sigma} U = p_{\sigma(1)+1}^{u_1}
\cdots p_{\sigma(n)+1}^{u_n} \leq p_{\sigma(1)+1}^{a_1} \cdots
p_{\sigma(n)+1}^{a_n} = \hat{\sigma} P\] since we are using lex
order.  Finally, the condition $p_{1}^{a_1} \cdots p_{n}^{a_n}
\leq p_{1}^{c_1} \cdots p_{t+1}^{c_{t+1}}$ is obvious, completing
the proof.
\end{proof}

\begin{lemma}\label{twoshiftuplem}
If $(a_1,\ldots,a_n,0,\ldots) \preceq (b_1,\ldots,b_t,0,\ldots)$
and $a,b \in \N$ are such that $a \leq b$, then
$(a,a_1,\ldots,a_n,0,\ldots) \preceq (b,b_1,\ldots,b_t,0,\ldots)$.
\end{lemma}

\begin{proof}
As before, we may assume that $n \leq t$.  Since we are using lex
order, it is clear that $(a, a_1,\ldots,a_n,0,\ldots) \leq
(b,b_1,\ldots,b_t,0,\ldots)$.  Let $\sigma \in {\frak S}_t$ be
such that $p_{\sigma(1)}^{a_1} \cdots p_{\sigma(n)}^{a_n} \, \mid
\, p_{1}^{b_1} \cdots p_{t}^{b_t}$, and let $\tau$ be the cyclic
permutation $\tau = (12 \cdots (t+1))$.  Setting $\hat{\sigma} =
\tau \sigma \tau^{-1}$, we have
\begin{equation*}
\begin{split}
\hat{\sigma} \left(p_1^a p_{2}^{a_1} \cdots p_{n+1}^{a_n} \right)
= \ &  \tau \sigma
\left(p_{t+1}^a p_{1}^{a_1} \cdots p_{n}^{a_n}\right)  \\
= \ & \tau \left(p_{t+1}^a p_{\sigma(1)}^{a_1} \cdots
p_{\sigma(n)}^{a_n}\right) \\
= \ & p_{1}^a p_{\sigma(1)+1}^{a_1} \cdots p_{\sigma(n)+1}^{a_n}.
\\
\end{split}
\end{equation*}
It is easily seen that this last expression divides
$p_{1}^{b}p_{2}^{b_1} \cdots p_{t+1}^{b_t}$.

Finally, suppose that $U = p_1^{u_1} \cdots p_{n+1}^{u_{n+1}} \leq
p_1^{a}p_{2}^{a_1} \cdots p_{n+1}^{a_n} = P$.  Then, since we are
using lex order, it follows that \[p_2^{u_2} \cdots
p_{n}^{u_{n+1}} \leq p_{2}^{a_1} \cdots p_{n+1}^{a_n}.\] By
assumption, however, this implies that $\sigma \tau^{-1} p_2^{u_2}
\cdots p_{n+1}^{u_{n+1}} \leq \sigma \tau^{-1} p_{2}^{a_1} \cdots
p_{n+1}^{a_n}$ and thus $\hat{\sigma} p_2^{u_2} \cdots
p_{n+1}^{u_{n+1}} \leq \hat{\sigma} p_{2}^{a_1} \cdots
p_{n+1}^{a_n}$.  It follows that if $\hat{\sigma} p_2^{u_2} \cdots
p_{n+1}^{u_{n+1}} \neq \hat{\sigma} p_{2}^{a_1} \cdots
p_{n+1}^{a_n}$, we must have $\hat{\sigma} U < \hat{\sigma} P$. On
the other hand, if $p_2^{u_2} \cdots p_{n+1}^{u_{n+1}} =
p_{2}^{a_1} \cdots p_{n+1}^{a_n}$, then $u_1 \leq a$, in which
case we still have $\hat{\sigma} U \leq \hat{\sigma} P$ (since
$\hat{\sigma}p_1 = p_1$).  This completes the proof.
\end{proof}

We finally have enough to prove the well-quasi-ordering of
$\preceq$.

\begin{theorem}
The quasi-order relation $\preceq$ is a well-quasi-ordering.
\end{theorem}

\begin{proof}
The proof uses some ideas from Nash-Williams' proof \cite{NW} of a
result of Higman \cite{Higman}. Assume for the sake of
contradiction that $m^{(1)},m^{(2)},\dots$ is a bad sequence in
$\Omega$, in which $m^{(i)}=(m^{(i)}_1,m^{(i)}_2,\dots)$.  Given a
monomial $m \in \Omega$, we let $j(s)$ denote the smallest index
$j$ such that $m_{j}=m_{j+1}=\cdots$.  We may assume that the bad
sequence is chosen in such a way that for every $i$, $j(m^{(i)})$
is {\it minimal} among the $j(m)$, where $m$ ranges over all
elements of $\Omega$ with the property that
$m^{(1)},m^{(2)},\dots,m^{(i-1)},m$ can be continued to a bad
 sequence in $\Omega$.   Clearly, we have
$j(m^{(i)})>1$ for all $i$.  Let
$t^{(i)}=(m_2^{(i)},m_3^{(i)},\dots) \in \Omega$ so that
$j(t^{(i)})=j(m^{(i)})-1$, for all $i$.  Now consider the sequence
$m^{(1)}_1,m^{(2)}_1,\dots,m^{(i)}_1,\dots$ of elements of $\N$.
Since $\N$ is well-ordered, there is an infinite sequence $1\leq
i_1<i_2<\cdots$ of indices such that $m^{(i_1)}_1 \leq m^{(i_2)}_1
\leq \cdots$. By minimality of $m^{(1)},m^{(2)},\dots$, the
sequence
$m^{(1)},m^{(2)},\dots,m^{(i_1-1)},t^{(i_1)},t^{(i_2)},\dots$ is
good; that is, there exist $j < i_1$ and $k$ with $m^{(j)} \preceq
t^{(i_k)}$, or $k<l$ with $t^{(i_k)} \preceq t^{(i_l)}$. In the
first case we have $m^{(j)}\preceq m^{(i_k)}$ by Lemma
\ref{oneshiftuplem}; and in the second case, $m^{(i_k)}\preceq
m^{(i_l)}$ by Lemma \ref{twoshiftuplem}. This contradicts the
badness of our sequence $m^{(1)},m^{(2)},\dots$.
\end{proof}

If $f \in R$, we define the \textit{leading monomial} of $f$,
lm$(f)$, to be the largest monomial occurring in $f$ with respect
to $\leq$. We now come to our main result.

\begin{theorem}\label{onevarfinitegenthm}
Let $I$ be an ideal of $R = \C[p_1,p_2,\ldots]$ such that ${\frak
S}_{\infty}I \subseteq I$.  Then, $I$ is finitely generated as a
$R {\frak S}_{\infty}$-module.
\end{theorem}

\begin{proof}
Let $I$ be an ideal of $R$ with ${\frak S}_{\infty}I \subseteq I$
that is not finitely generated.  Define a sequence of elements of
$I$ as follows:  $f_1$ is an element of $I$ with minimal leading
monomial;  $f_{i+1}$ is an element of $I \setminus
\<f_1,\ldots,f_i \>_{R{\frak S}_{\infty}}$ with minimal leading
monomial.  Of course, if $f_1 \in \C$, then $I = R$ or $I = (0)$
is finitely generated.

It is clear that lm($f_i$) $\leq$ lm($f_{i+1}$).  If lm($f_i$) $=$
lm($f_{i+1}$), then for a suitable $a \in \C$, $f_{i+1} - af_i \in
I \setminus \<f_1,\ldots,f_i \>_{R{\frak S}_{\infty}}$ has a
smaller leading term, a contradiction.  Thus, lm($f_i$) $<$
lm($f_{i+1}$).

We, therefore, obtain a sequence of (strictly) increasing
monomials $m_i =$ lm($f_i$). By the well-quasi-ordering theorem
above, there exist $i < j$ such that $m_i \preceq m_j$.  Let
$\sigma$ be the permutation inducing $m_i \preceq m_j$.  Then,
$m_j = m \sigma m_i$ for some monomial $m$.  Examine the element
\[g = f_{i+1} - am \sigma f_{i} \in I \setminus \<f_1,\ldots,f_i
\>_{R{\frak S}_{\infty}},\] in which $a \in \C$ is chosen so that
the leading term of $f_{i+1}$ cancels.  The leading monomial of
$g$ cannot come from any of the (necessarily, strictly smaller)
monomials occurring in $f_{i+1}$ by our choice of $f_{i+1}$.

On the other hand, any monomial occurring in $m \sigma f_{i}$ is
of the form $m \sigma u$ for $u$ occurring in $f_{i}$.  Since $u <
$ lm($f_i$) $= m_i$, the relation $m_i \preceq m_j$ implies that
$m \sigma u < m_j$.  In particular, $g$ again has a smaller
leading term than $f_{i+1}$.  This contradiction finishes the
proof.
\end{proof}

### 2020-08-04 berkeley_thesis_template/uniquewordeqs.tex
everything

 % ----------------------------------------------------------------
% AMS-LaTeX Paper ************************************************
% **** -----------------------------------------------------------

\documentclass{amsart}
\usepackage{amssymb}

%\documentclass{amsart}

%\documentclass[10pt]{article}
%\documentstyle[11pt]{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
%\usepackage[dvips]{graphicx,color}

% ----------------------------------------------------------------
\vfuzz2pt % Don't report over-full v-boxes if over-edge is small
\hfuzz2pt % Don't report over-full h-boxes if over-edge is small
% THEOREMS -------------------------------------------------------
\newtheorem{thm}{Theorem}[section]
\newtheorem{cor}[thm]{Corollary}
\newtheorem{ex}[thm]{Example}
\newtheorem{conj}[thm]{Conjecture}
\newtheorem{prob}[thm]{Problem}
\newtheorem{lem}[thm]{Lemma}
\newtheorem{prop}[thm]{Proposition}
\theoremstyle{definition}
\newtheorem{defn}[thm]{Definition}
\theoremstyle{remark}
\newtheorem{rem}[thm]{Remark}
\numberwithin{equation}{section}
% MATH -----------------------------------------------------------
\newcommand{\norm}[1]{\left\Vert#1\right\Vert}
\newcommand{\abs}[1]{\left\vert#1\right\vert}
\newcommand{\set}[1]{\left\{#1\right\}}
\newcommand{\Real}{\mathbb R}
\newcommand{\eps}{\varepsilon}
\newcommand{\To}{\longrightarrow}
\newcommand{\BX}{\mathbf{B}(X)}
\newcommand{\A}{\mathcal{A}}
\newcommand{\bbold}{\mathbb}
\newcommand{\cal}{\mathcal}
\newcommand{\Cal}{\mathcal}
\newcommand{\rom}{\textup}
\newcommand{\<}{\langle}
\renewcommand{\>}{\rangle}
\def \N { {\bbold N} }
\def \C { {\bbold C} }
\def \Q { {\bbold Q} }
\def \Z { {\bbold Z} }
\def \k { {\bbold R} }
% ----------------------------------------------------------------
\begin{document}
\title[Symmetric Word Equations]{Unique Solvability of Symmetric Word \\ Equations in Positive Definite Letters}%

\author[S. N. Armstrong]{Scott N. Armstrong}
\address{Department of Mathematics, University of California, Berkeley, CA 94720}
\email{sarm@math.berkeley.edu}

\author[C.J. Hillar]{Christopher J. Hillar}
\address{Department of Mathematics, University of California, Berkeley, CA 94720}
\email{chillar@math.berkeley.edu}

%\thanks{}%
%\subjclass{}%
%\keywords{}%
%\date{}
%\dedicatory{}%
%\commby{}%

\begin{abstract}
Let $S(X,B)$ be a symmetric (``palindromic'') word in two letters  $X$ and $B$. We are interested in the matrices that result when the letters
are positive semidefinite (complex Hermitian) $n$-by-$n$
matrices.  For each pair of real positive semidefinite matrices $P$ and $B$, we prove that there is a unique real positive semidefinite solution $X$ to the word equation $S(X,B) = P$.  This settles the real version of a conjecture of C. Hillar and C. R. Johnson.  A more general situation involving arbitrary numbers of letters is also considered and solved.  As an application, we discuss how the result relates to a trace conjecture involving products of positive definite matrices.
\end{abstract}
% ----------------------------------------------------------------
\maketitle
% ----------------------------------------------------------------

\section{Introduction}

This paper considers a natural matrix generalization to the elementary scalar equation \[bx^m = p,\] in which $b > 0$, $p \geq 0$, $m \in \Z_+$ and $x$ is a nonnegative real indeterminate.  One difficulty with an extension is dealing with matrix noncommutativity, while another is in determining what should be meant by the words ``real'' and ``nonnegative.''  Fortunately for us, the latter concerns have already long been addressed:  the natural matrix interpretation of the reals are the Hermitian matrices, while nonnegative (positive) numbers correspond to those complex Hermitian matrices with all nonnegative (positive) eigenvalues, the so-called (\textit{positive semidefinite}) \textit{positive definite} matrices.  The issue of noncommutativity, however, is of a more subtle nature, and we first introduce some notation before addressing it.

Let $W = W(X,B_1,\ldots,B_k)$ be a word in
the letters $X$ and $B_1,\ldots,B_k$.  The {\it reversal} of $W$ is the word written in reverse order, and it is denoted by $W^{*}$.  A word is {\it symmetric} if it is identical to its reversal
(in other contexts, the name ``palindromic'' is also used).   As we shall soon see, formulating our generalization requires restriction to a special class of words.  For the purposes of this work, an {\it interlaced} word $W = W(X,B_1,\ldots,B_k)$ in the \textit{interlacing} letter $X$ is a juxtaposition of powers of letters that alternate in $X$.  More precisely, an interlaced word is an expression of the form 
\begin{equation}\label{interlacedef}
W = B_{i_1}^{q_1}\prod_{j=1}^{m} {X^{p_j}B_{i_{j+1}}^{q_{j+1}}},
\end{equation}
in which the exponents $p_{j} > 0, q_j \geq 0$ are nonnegative integers and $\{i_1,\ldots,i_{m+1} \} \subseteq \{1,\ldots,k\}$.   (Here, of course, we consider the zeroth power of a letter to be the empty word, the identity element of the monoid).

The interlacing letter $X$ is distinguished, and is to be viewed as an indeterminate $n$-by-$n$ positive semidefinite matrix, whereas the letters $B_i$ correspond to fixed $n$-by-$n$ positive definite matrices.   For convenience, the letters $X$ and $B_i$ will also represent the substituted matrices (the context will make the distinction clear).  Notice that when $k = 1$, the set of interlaced words is simply the set of all words in two letters.

Returning to our motivating example, notice that there is a unique nonnegative solution to the equation $bx^m = p$ for every pair of positive $b$ and nonnegative $p$;  we would like to generalize this observation.  Our introductory remarks prepare us to make the following definition.

\begin{defn}\label{symmwordeqdef}
A {\it symmetric word equation} is an equation, $S(X,B_i) = P$, in
which $S(X,B_i)$ is an interlaced symmetric word. If the $B_i$ are positive definite and $P$ is positive semidefinite, then any positive semidefinite matrix $X$ for which the equation holds is called a {\it solution} to the
symmetric word equation.
\end{defn}

A symmetric word equation will be called {\it solvable} if there
exists a solution for every positive definite $n$-by-$n$ matrices $B_i$ and $n$-by-$n$ positive semidefinite $P$. Moreover, if each such $B_i$ and $P$ give rise to a unique solution, the equation will be called {\it uniquely solvable}.  Utilizing fixed point methods, the authors of \cite{JH2} give a proof of the following \cite[Theorem 7.1]{JH2} in the case when $P$ (and therefore necessarily $X$) is positive definite.

\begin{thm}\label{HJexistencethm}
Every symmetric word equation with a positive definite $P$ is solvable.  Moreover, if the parameters $P$ and $B_i$ are real, then there is a real solution. 
\end{thm}

The stipulation that $P$ is positive definite can be removed without too much difficulty, and this is the content of Theorem \ref{mainthmpsd} below.

\begin{ex}
Let $P$ be any positive definite matrix and let $S(X) = X^m$, for a positive integer $m$.  Then, there is a unique positive semidefinite solution $X$.  In fact, writing $P = UDU^*$ for a unitary matrix $U$, and a nonnegative
diagonal matrix $D$, we have $X = UD^{1/m}U^{*}$.
\end{ex}

One may view the solvability of a symmetric word equation as a generalization of the (well-known) fact that PD matrices have unique $m$-th roots for positive integers $m$.

Recall that two $n$-by-$n$ matrices $X$ and $Y$ are said to be
{\it congruent} if there is an invertible $n$-by-$n$ matrix $Z$
such that $Y = Z^{*}XZ$; and that congruence on Hermitian matrices
preserves inertia (the ordered triple consisting of the number of
positive, negative, and zero eigenvalues) and, thus, positive
definiteness \cite[p. 223]{HJ1}. A symmetric word evaluated at positive definite matrices is inductively congruent to the ``center,'' positive definite matrix. We conclude that

\begin{lem}\label{symwordpdlem}
A symmetric word evaluated at positive definite matrices is positive
definite.
\end{lem}

One might also wonder if it is necessary to focus attention on equations involving symmetric words.  In Section \ref{wordrelationssection}, we show that symmetric words are the only words that are positive definite for all positive definite substitutions.  Therefore, in light of Definition \ref{symmwordeqdef}, our restriction seems appropriate.

\section{An Application}

Symmetric word equations were first encountered while studying a trace conjecture \cite{JH} involving words in two letters $A$ and $B$ (see also \cite{JHcplx,HJS}).  The conjecture is

\begin{conj}\label{traceconjecture}
A word in two letters $A$ and $B$ has positive trace for every pair of real positive definite $A$ and $B$ if and only if the word is symmetric or a product (juxtaposition) of 2 symmetric words.
\end{conj}

It turns out that for each solvable symmetric word equation, one
can identify an infinite class of words that admit real PD
matrices $A$ and $B$ giving those words a negative trace.  
The following is a brief description of this application.  Consider the word $W = BABAAB$, which is not symmetric nor a product of two symmetric words. In light of Conjecture \ref{traceconjecture}, we would like to verify that there exist real positive definite matrices $A$ and $B$ giving $W$ a negative trace.  This is surprisingly difficult, as the methods in \cite{JH} show.  Resulting
$A$ and $B$ that exhibit a negative trace are, for example,
\[A_1=\left[\begin{array}{@{}ccc@{}}
1&20&210\\
20&402&4240\\
210&4240&44903
\end{array}\right]\quad \mbox{and}\quad B_1=\left[\begin{array}{@{}ccc@{}}
36501&-3820&190\\
-3820&401&-20\\
190&-20&1
\end{array}\right].\]

Consider now the following extension.  Let $T$ be the word given by $T=S_1S_2$, in which $S_1$ and $S_2$ are symmetric words in the letters $A$ and $B$.  If the simultaneous word equations
\[\begin{array}{c}
S_1(A,B)=B_1,\\[3pt]
S_2(A,B)=A_1
\end{array}\]
may be solved for positive definite $A$ and $B$ given positive
definite $A_1$ and $B_1$, then the word $TTT^{*}$ can have negative
trace.  Specializing to the case that $S_2$ is simply the word $A$, we have the following.

\begin{cor}
Let $S = S(A,B)$ be any symmetric word.  Then the word $SASAAS$ admits real positive definite matrices $A$ and $B$ giving it negative trace.
\end{cor}

\begin{proof}
The matrix $B_1A_1B_1A_1A_1B_1$ has negative trace.   Using Theorem \ref{HJexistencethm}, the  equation $S(A_1,X) = B_1$ has a real PD solution $X = B_2$.  The two matrices $B_2$ and $A_1$ are the desired witnesses.  
\end{proof}

In this paper, we study a conjecture \cite{JH2} of Hillar and Johnson that generalizes Theorem \ref{HJexistencethm}.

\begin{conj}\label{mainuniqueconj}
Every symmetric word equation is uniquely solvable.
\end{conj}

Of course, when the matrices $B_i$ and $P$ are real, this conjecture and Theorem \ref{HJexistencethm} imply that the unique solution $X$ is always real.  Our main theorem, while weaker than Conjecture \ref{mainuniqueconj}, verifies this last implication (see also Theorem \ref{mainthmpsd} below for the real positive semidefinite case).

\begin{thm}\label{ourmainthm}
Every symmetric word equation with real positive definite $B_i$ and $P$ has a unique real positive definite solution.
\end{thm}

We prove this result first by bounding solutions to symmetric word equations and then appealing to the general theory of Brouwer mapping degree.  The technique, unfortunately, does not readily generalize to the complex Hermitian positive definite case, and more is needed to verify the complete Conjecture \ref{mainuniqueconj}.  In the final two sections of this article, we examine the uniqueness of positive definite word representations and algorithms for finding solutions to symmetric word equations.

\section{Symmetric words}

Recall that two $n$-by-$n$ matrices $X$ and $Y$ are said to be
{\it congruent} if there is an invertible $n$-by-$n$ matrix $Z$
such that $Y = Z^{*}XZ$; and that congruence on Hermitian matrices
preserves inertia (the ordered triple consisting of the number of
positive, negative, and zero eigenvalues) and, thus, positive
definiteness \cite[p. 223]{HJ1}. A symmetric word evaluated at positive definite matrices is inductively congruent to the ``center,'' positive definite matrix. We conclude that

\begin{lem}\label{symwordpdlem}
A symmetric word evaluated at positive definite matrices is positive
definite.
\end{lem}

Fixing positive definite matrices $B_i$ ($i = 1,\ldots,k$), it is natural to ask if the map from the set of PD matrices to itself given by $S: X \mapsto S(X,B_i)$ is (injective) surjective.  In the complex case, Theorem \ref{HJexistencethm} implies that the map is surjective, while our main result verifies that in the real case, it is bijective.  Although not obvious, it is possible to extend this last assertion to positive semidefinite matrices.  First, we establish a useful lemma.

\begin{lem}\label{kerlemma}
Let $p_1,\ldots,p_k > 0$ and $B_1,\ldots,B_k$ be positive definite
matrices. Then, for any positive semidefinite matrix $X$, we have
\[ \ker X = \ker X^{p_{k}}B_{k-1}  \cdots B_2 X^{p_2}B_1 X^{p_1}.\]
\end{lem}

\begin{proof}
Set $X = UDU^*$ for a unitary matrix $U$ and $D = \text{diag}(\lambda_1,\ldots,\lambda_n)$, in which $\lambda_1 \geq \ldots \geq \lambda_n \geq 0$.  Let $Y=X^{p_{k}}B_{k-1} \cdots B_2 X^{p_2}B_1 X^{p_1}$, and notice that $\ker U^*XU = \ker U^*YU$ if and only if $\ker X = \ker Y$.  Thus, it suffices to argue that \[ \ker D = \ker D^{p_{k}}B_{k-1} \cdots B_2 D^{p_2} B_1 D^{p_1}, \] whenever the $B_i$ are positive definite matrices.

Let $m$ be the largest integer such that $\lambda_m  \neq 0$, and for each $i$, let $\widetilde B_i$ denote the $m$-by-$m$ leading principal submatrix of $B_i$, which will be positive definite (see, for instance, \cite[p.472]{HJ1}).  Additionally, set $\widetilde D = \text{diag}(\lambda_1,\ldots,\lambda_m)$.  A straightforward block matrix multiplication then gives us that \[D^{p_{k}} B_{k-1} \cdots B_2 D^{p_2} B_1 D^{p_1} = \left[\begin{array}{cc} \widetilde D^{p_{k}} \widetilde B_{k-1} \cdots \widetilde B_2 \widetilde D^{p_2} \widetilde B_1 \widetilde D^{p_1} 
 & 0 \\0 & 0\end{array}\right]. \]  Since the leading principal $m$-by-$m$ matrix in this direct sum is invertible, the claim follows.
\end{proof}

Using this lemma and assuming our main theorem (Theorem \ref{ourmainthm}), we can prove the following extensions.

\begin{thm} \label{mainthmpsd}
Every symmetric word equation with real positive definite $B_i$ and positive semidefinite $P$ has a unique real positive semidefinite solution.
\end{thm}

\begin{proof}
Performing a uniform unitary similarity, we may prove the theorem with the supposition that $P$ is of the form \[\left[\begin{array}{cc} \widetilde P & 0 \\0 & 0\end{array}\right]\] for a positive diagonal matrix $\widetilde P$ of rank $m$.  Lemma \ref{kerlemma} implies that any positive semidefinite solution $X$ to the symmetric word equation $S(X,B_i) = P$ has the same block form as $P$.  As in the lemma, let $\widetilde B_i$ denote the $m$-by-$m$ leading principal (positive definite) submatrix of $B_i$.

From these observations, it follows that positive semidefinite solutions $X$ to the equation $S(X,B_i) = P$ correspond in a one-to-one manner with positive definite solutions $\widetilde X$ to the equation $S(\widetilde X,\widetilde B_i) = \widetilde P$.  An application of Theorem \ref{ourmainthm} completes the proof.
\end{proof}

\begin{thm}\label{unitballhomeo}
Fix real positive definite matrices $B_i$ in the unit ball and a
symmetric word $S(X,B_i)$.  Then, the mapping $S(X,B_i)$ from the
set of (real) positive semidefinite matrices in the unit ball to
itself is a homeomorphism.
\end{thm}

\begin{proof}
Theorem \ref{mainthmpsd} shows that our map is bijective.  Since the set of positive semidefinite matrices in the unit ball is compact, it follows that it is also a homeomorphism.
\end{proof}

Let us remark at this point that Theorem \ref{mainthmpsd} (and thus Theorem \ref{unitballhomeo}) is false if we allow for arbitrary symmetric words in the letters $B_i$ and $X$.  For example, suppose that \[ B_1 = \left[\begin{array}{cc}4 & -1 \\-1 & 1\end{array}\right] \ \text{and}  \ \ B_2 = \left[\begin{array}{cc}2 & 1 \\1 & 1\end{array}\right].\]  Then, as is easily verified, the equation $XB_1B_2XB_2B_1X =  0$ has at least two positive semidefinite solutions: $X = 0$ and $X = \text{diag}(0,1)$.  The difficulty here is that the multiple $B_i$ can cause an inversion of the block structure of a solution $X$.  In this case, we had $B_1B_2XB_2B_1 =  \text{diag}(9,0)$.

One might also wonder if it is necessary to focus attention on equations involving symmetric words.  In Section \ref{wordrelationssection}, we show that symmetric words are the only words that are positive definite for all positive definite substitutions.  Therefore, in light of Definition \ref{symmwordeqdef}, our restriction seems appropriate.

\section{Explicit Solutions}

In this section, we describe a class of words that are uniquely solvable with explicit solutions.

\begin{defn}
A symmetric word is called \textit{totally symmetric} if it can be expressed as a composition of maps of the form
\begin{itemize}
\item  $\pi_{m,B_i}(W) = (WB_i)^mW$, $m$ a positive integer
\item $\varphi_m (W) = W^m$, $m$ a positive integer
\item $s_{B_i}(W) = B_iWB_i$
\end{itemize}
applied to the letter $X$.
\end{defn}

For example, the word $W = B_1X^2B_2X^2B_2X^2B_1$ may be expressed as the composition, $s_{B_1} \circ \pi_{2,B_2} \circ \varphi_2 (X)$.  The utility of this definition becomes clear from the following

\begin{prop}
For every totally symmetric word $S(X,B_i)$ and each pair of positive definite $P,B_i$, the equation $S(X,B_i) = P$ has a unique positive definite solution $X$.  Moreover, the solution $X$ can be expressed in terms of radicals.
\end{prop}

\begin{proof}
We induct on the number of compositions involved in the word $W$; the base case $W = X$ being trivial.  If $W = \varphi_m(V)$ for some word $V$, then $V = P^{1/m}$ is a smaller totally symmetric word equation and any solution $X$ to $W(X,B_i) = P$ satisfies it.  A similar statement holds for $W = s_{B_i}(V)$, leaving us to deal with $\pi_{m,B_i}$.

Without loss of generality, we prove the result for the equation $(XB)^mX = P$.  Assume that $B$ and $P$ are given PD matrices and that $X$ is a solution to $(XB)^mX = P$.  Set $Y = B^{1/2}XB^{1/2}$, so that $X = B^{-1/2}YB^{-1/2}$. Then, \[B = (B^{-1/2}YB^{1/2})^mB^{-1/2}YB^{-1/2} = B^{-1/2}Y^{m+1}B^{-1/2}.\] Therefore, $Y^{m+1} = B^{1/2}PB^{1/2}$, from which it follows that $Y$ is uniquely determined as $(B^{1/2}PB^{1/2})^{1/(m+1)}$. Hence, $X$ must be $B^{-1/2}(B^{1/2}PB^{1/2})^{1/(m+1)}B^{-1/2}$. Finally, substituting this $X$ into the original equation does verify that it is a solution.  This completes the proof
\end{proof}

The smallest symmetric word equation without a known explicit solution is $XBX^3BX = P$.  An exploration of which equations give rise to explicit solutions is the focus of a future work.

\section{Bounding Solutions}

We will be using the spectral matrix norm throughout (see \cite[p.
295]{HJ1}).  This norm is useful because for positive semidefinite
$A$, it is just the largest eigenvalue of $A$.

Let $X_k$ be a sequence of PD solutions to a fixed symmetric word
equation $S(X,B_i) = P$.  We prove that the $X_k$ are bounded.  More
generally, consider the collection of word equations
$S(X,tB_i+(1-t)I) = P$ in which $I$ is the $n$-by-$n$ identity matrix and each $B_i$ is replaced by $B_i(t) := tB_i+(1-t)I$ for a real parameter $0 \leq t \leq
1$.  We show that solutions $X$ are bounded uniformly in $t$.

\begin{prop}\label{boundprop}
Let $B_i$ and $P$ be fixed positive definite matrices, and let $S(A,B_i)$ be a symmetric word.  Then, there exists a positive number $M$ such that any solution $X$ to an
equation $S(X,B_it+(1-t)I) = P$ with $0 \leq t \leq 1$
necessarily has $\|X\| < M$.
\end{prop}

\begin{proof}
Suppose, by way of contradiction, that $X_{k}$ ($k= 1,2,\ldots$)
is an unbounded sequence of positive definite matrices and $t_k$ a
sequence of real numbers in $[0,1]$ such that
\[S\left(X_{k},t_kB_i+(1-t_k)I \right) = P\] for all $k$. By taking a subsequence, if necessary, we may assume that $\{t_k\}$
converges to a real number $t \in [0,1]$.  Set $X_{k} =
U_{k}D_{k}U_{k}^{*}$ for unitary $U_{k}$ and $D_{k} =$
diag$(\lambda_{1k}, \lambda_{2k} , \ldots, \lambda_{nk})$ in which
$0 < \lambda_{1k} \leq \lambda_{2k} \leq \ldots \leq \lambda_{nk}$
are the eigenvalues of $X_{k}$. To simplify matters later, we assume that $\{U_{k}\}$ converges to a unitary $U$ by
passing to a subsequence (the set of unitary matrices is compact).

We first arrange for a subsequence of $X_{k}/\|X_k\|$ to have a
special form.  Observe that \[\frac{X_{k}}{\|X_k\|} = U_{k}\left[
{\begin{array}{*{20}c}
   {\frac{{\lambda _{1k} }}
{{\lambda _{nk} }}} & {} & {} & {}  \\
   {} & {\frac{{\lambda _{2k} }}
{{\lambda _{nk} }}} & {} & {}  \\
   {} & {} &  \ddots  & {}  \\
   {} & {} & {} & 1  \\
 \end{array} } \right]U_{k}^{*},\] in which each of the diagonal entries satisfies
the inequality $0 < \lambda_{ik}/\lambda_{nk} \leq 1$ ($i =
1,\ldots,n$). It follows easily that there is a subsequence
$\{k_j\}$ such that $\mathop {\lim }\limits_{j \to \infty }
\;\;\frac{{X_{k_j }}}{{\left\| X_{k_j} \right\|}}$ exists and is
of the form
\[L = U\left[
 {\begin{matrix}
   h_1 &  \ldots  & 0  \\
    \vdots  &  \ddots  &  \vdots   \\
   0 &  \cdots  & {1 }  \\
 \end{matrix}} \right]U^*,\] in which $0 \leq h_1 \leq
 \cdots \leq h_{n-1} \leq 1$.  In what follows, we
replace our original sequence $X_k$ with the subsequence
constructed above.

Returning to the proof, consider the equations, \[S \left(\frac{X_{k}}{\|X_k\|},t_kB_i+(1-t_k)I \right) =
\|X_k\|^{-s}P,\] in which $s$ is the sum of all the powers of $X$
in $S(X,B_i) = P$.  By assumption $\|X_k\| = \lambda_{nk}$ goes to
infinity, and consequently, the limit of these expressions is
\begin{equation}\label{wordeqzero}
S(L,tB_i+(1-t)I) = 0.
\end{equation}
Let $m$ be the largest element of $\{1,\ldots,n-1\}$ such that
$h_m = 0$.  Notice that by construction, $h_i = 0$ for $i \leq m$.  Applying Lemma \ref{kerlemma} to equation (\ref{wordeqzero}), it follows that $\ker L$ is all of $\mathbb C^n$.  In particular, $L$ is the zero matrix, a contradiction that finishes the proof.
\end{proof}

In light of Proposition \ref{boundprop}, a natural question is
whether one can obtain explicit bounds for solutions $X$
(necessarily depending on $B_i$ and $P$).  As a partial answer, we
offer the following sequence of results.

\begin{lem} \label{b1}
If $A$ and $B$ are positive definite matrices, then
\begin{eqnarray}
\| B \|& \leq & \| A^{-1}\|^2 \| A B A \| \label{bn1} \\
\| B^{-1}\| & \leq & \| A \|^2 \| (A B A)^{-1}\| \label{bn2}\\
\| A \| &\ \leq & \| B^{-1} \|^{1/2} \| A B A \|^{1/2} \label{bn3}\\
\| A^{-1} \| & \leq & \| B \|^{1/2} \| (A B A)^{-1} \|^{1/2}
\label{bn4}
\end{eqnarray}
\end{lem}

\begin{proof}
Let $P=ABA$. Writing $B = A^{-1} P A^{-1}$, we estimate
\[ \| B \| = \| A^{-1} P A^{-1} \| \leq \| A^{-1}\|^2 \| P\|, \]
which is (\ref{bn1}).

Recall that for any positive definite matrix $A$ and any vector
$\eta$
\[ (A\eta)\cdot \eta \geq \| A^{-1}\|^{-1} |\eta|^2.\]
Let $\xi$ be a unit vector such that $|\xi |=1$ and $\| A \| =
|A\xi|$. Then
\[ \| P \| \geq \xi \cdot (P\xi) = \xi \cdot (ABA\xi) =
(A\xi)\cdot (BA\xi) \geq \| B^{-1} \|^{-1} |A\xi|^2 = \| B^{-1}
\|^{-1} \| A \|^2, \] and rearranging we get (\ref{bn3}). We get
(\ref{bn2}) and (\ref{bn4}) by noticing that $A^{-1}B^{-1}A^{-1} =
P^{-1}$ and applying (\ref{bn1}) and (\ref{bn3}), respectively.
\end{proof}

\begin{thm}
Let $p$, $q > 0$ and suppose that $B_1$, $B_2$, $P$ and $X$ are
positive definite matrices satisfying
\[ X^p B_1 X^q B_2 X^q B_1 X^p = P. \]
If $q\geq p$ then
\begin{equation} \label{be3}
\| X \| \leq \| B_1^{-1}\|^{1/(p+q)} \| B_2^{-1} \|^{1/2(p+q)} \|
P \|^{1/2(p+q)}.
\end{equation}
If $q<p$ then
\begin{equation} \label{be4}
\| X \| \leq \|B_1 \|^{q\delta} \|B_1^{-1}\|^{p\delta}
\|B_2\|^{q\delta/2} \|B_2^{-1}\|^{p\delta/2} \| P \|^{p\delta/2}
\| P^{-1}\|^{q\delta/2}
\end{equation}
where $\delta = (p^2 - q^2)^{-1}$.
\end{thm}

\begin{proof}
If $q\geq p$ then
\[ X^q B_1 X^q B_2 X^q B_1 X^q = X^{q-p} P X^{q-p}.\]
Using Lemma \ref{b1} we estimate
\begin{eqnarray*}
\| X \|^q & \leq & \| B_1^{-1} \|^{1/2} \|X^q B_1 X^q \|^{1/2}\\
& \leq & \| B_1^{-1} \|^{1/2} \left( \| B_2^{-1} \|^{1/2} \|
X^{q-p} P X^{q-p} \|^{1/2} \right)^{1/2}\\
& = & \| B_1^{-1} \|^{1/2} \| B_2^{-1} \|^{1/4} \| X^{q-p} P
X^{q-p} \|^{1/4}\\
& \leq & \| B_1^{-1} \|^{1/2} \| B_2^{-1} \|^{1/4} \| P \|^{1/4}
\| X^{q-p} \|^{1/2}\\
& = & \| B_1^{-1} \|^{1/2} \| B_2^{-1} \|^{1/4} \| P \|^{1/4} \| X
\|^{(q-p)/2}.\\
\end{eqnarray*}
Therefore
\begin{equation*}
\| X \|^{(q+p)/2} \leq \| B_1^{-1} \|^{1/2} \| B_2^{-1} \|^{1/4}
\| P \|^{1/4}
\end{equation*}
from which we obtain (\ref{be3}).

Now suppose $q < p$. Using Lemma \ref{b1} we estimate
\begin{eqnarray*}
\| X \|^p & \leq & \|(B_1 X^q B_2 X^q B_1)^{-1}\|^{1/2} \| P
\|^{1/2}\\
& \leq & \| B_1^{-1} \| \|B_2^{-1} \|^{1/2} \|X^{-1}\|^q
\|P\|^{1/2}.
\end{eqnarray*}
In a similar way we obtain
\[ \| X^{-1} \|^p \leq \| B_1 \| \|B_2 \|^{1/2} \|X \|^q
\|P^{-1} \|^{1/2}.\] Therefore
\begin{equation*}
\| X \|^p \leq \| B_1^{-1} \| \|B_2^{-1} \|^{1/2} \left( \| B_1 \|
\|B_2 \|^{1/2} \|X \|^q \|P^{-1} \|^{1/2} \right)^{q/p}
\|P\|^{1/2}.
\end{equation*}
Rearranging we obtain
\begin{equation*}
\| X \|^{(p^2-q^2)/p} \leq \| B_1 \|^{q/p} \| B_1^{-1} \| \|B_2
\|^{q/2p} \|B_2^{-1} \|^{1/2} \|P\|^{1/2} \|P^{-1} \|^{q/2p}
\end{equation*}
which is equivalent to (\ref{be4}).
\end{proof}

\begin{cor}
Let $p$, $q > 0$ and suppose that $B$, $P$ and $X$ are positive
definite matrices satisfying
\[ X^p B X^q B X^p = P.\]
If $q\geq 2p$, then
\[ \| X \| \leq \| B^{-1} \|^{2/(2p+q)} \| P \|^{1/(2p+q)}.\]
If $q < 2p$, then
\[ \| X \| \leq \|B \|^{2q\delta} \|B^{-1}\|^{4p\delta}
\| P \|^{2p\delta} \| P^{-1}\|^{q\delta} \] where $\delta =
(4p^2-q^2)^{-1}$.
\end{cor}

\begin{proof}
Notice that $X$ satisfies
\[ X^p B X^{q/2} I X^{q/2} B X^p = P \]
and apply the previous theorem.
\end{proof}

It is possible to use the techniques above to obtain explicit
bounds for solutions of longer and more complex word equations, but
the proofs are likewise more difficult.

\section{Brouwer Mapping Degree}

In this section, we give a brief overview of degree theory, and
some of its main implications.  The bulk of this discussion is material taken from \cite{degthy, teschl}.  First we introduce some notation.  Let $U$ be a bounded open subset of $\mathbb R^m$.  We denote the set of $r$-times differentiable functions from $U$ ($\overline{U}$) to $\mathbb R^m$ by $C^r(U,\mathbb R^m)$ ($C^r(\overline{U},\mathbb R^m)$) (when $r = 0$, $C^r(U,\mathbb R^m)$ is the set of continuous functions).  The \textit{identity function} id satisfies id$(\mathbf x) = \mathbf x$.  If $f \in C^1(U,\mathbb R^m)$, then the \textit{Jacobi matrix} of $f$ at a point $\mathbf {x} \in U$ is \[f'(\mathbf {x}) = \left(  \frac{\partial f_j}{\partial x_i}(\mathbf{x}) \right)_{1\leq i,j \leq m}\] and the \textit{Jacobi determinant} (or simply \textit{Jacobian}) of $f$ at $\mathbf{x}$ is \[ J_f(\mathbf{x}) = \det f'(\mathbf{x}).\]  The set of \textit{regular values} of $f$ is \[\text{RV}(f) = \left\{\mathbf{y}\in \mathbb R^m : \forall \mathbf{x} \in f^{-1}(\mathbf{y}), \ J_f(\mathbf{x}) \neq 0\right\}\] and for $\mathbf{y} \in \mathbb R^m$, we set \[D^r_{\mathbf{y}}(\overline{U},\mathbb R^m) = \left\{ f \in C^r( \overline{U},\mathbb R^m) : \mathbf{y} \notin f(\partial U) \right\} .\]

A function $\text{deg}: D^{0}_{\mathbf{y}}(\overline{U},\mathbb R^m) \to \mathbb R$ which assigns to each $f \in D^{0}_{\mathbf{y}}(\overline{U},\mathbb R^m)$ and $\mathbf{y} \in R^m$ a real number deg$(f,U,\mathbf{y})$ will be called a \textit{degree} if it satisfies the following conditions.

%\renewcommand{\enumi}{$D$}

\begin{enumerate}
\item $\deg(f,U,\mathbf{y}) = \deg(f-\mathbf y, U, 0)$ (\textit{translation invariance}).
\item $\deg(\mathrm{id}, U, \mathbf y) = 1$ if $\mathbf y \in U$ (\textit{normalization}).
\item If $U_1$ and $U_2$ are open, disjoint subsets of $U$ such that $\mathbf  y \notin f(\overline{U} \setminus (U_1 \cup U_2))$, then $\deg(f,U,\mathbf y) = \deg(f,U_1,\mathbf y) +\deg(f,U_2,\mathbf y)$ (\textit{additivity}). 
\item If $H(t) = tf + (1-t)g \in D^{0}_{\mathbf{y}}(\overline{U},\mathbb R^m)$ for all $t \in [0,1]$, then $\deg(f,U,\mathbf y) = \deg(g,U,\mathbf y)$ (\textit{homotopy invariance}).
\end{enumerate}

Motivationally, one should think of a degree map as somehow ``counting'' the number of solutions to $f(\mathbf x) = \mathbf y$.  Condition $(1)$ reflects that the solutions to $f(\mathbf x) = \mathbf y$ are the same as those of $f(\mathbf x)- \mathbf y = 0$, and since any multiple of a degree will satisfy $(1)$, $(3)$, and $(4)$, the condition $(2)$ is a normalization.  Additionally, $(3)$ is natural since it requires $\deg$ to be additive with respect to components.

Of course, we need a theorem guaranteeing that a degree even exists.

\begin{thm}
There is a unique degree $\deg$.  Moreover, $\deg(\cdot, U, \mathbf y):  D^0_{\mathbf{y}}(\overline{U},\mathbb R^m) \to \mathbb Z$.
\end{thm}

When functions are differentiable, a degree can be calculated explicitly in terms of Jacobians at solutions to the equation $f(\mathbf x) = \mathbf y$.

\begin{thm}\label{sumjacob}
Suppose that $f \in D^1_{\mathbf y}(\overline{U},\mathbb R^m)$ and $\mathbf y \in \text{\rm{RV}}$.  Then a degree satisfies \[\deg(f,U,\mathbf y) = \sum_{\mathbf x \in f^{-1}(\mathbf y)} {\text{\rm{sgn}} \  J_f(\mathbf x)},\] where this sum is finite and we adopt the convention that $\sum_{\mathbf x \subseteq  \emptyset} = 0$.
\end{thm}

As the above theorem shows, understanding Jacobians is essential when calculating the degree of a function $f$.  Therefore, the remainder of this section is devoted to computing them for the map $f(X) = S(X,B_i) - P$.  View the space of symmetric $n$-by-$n$ matrices as $\mathbb R^{m}$, in which $m = {n+1 \choose 2}$ .  With this identification in hand, we are interested in computing the determinant of the Jacobian of the map $X \mapsto S(X,B_i)$ from an open set $U$ of bounded positive definite matrices into the space of symmetric matrices over $\mathbb R$.

\begin{lem}
The Jacobian of the map $f(X) = BXB$ is given by [insert here].
\end{lem}
\begin{proof}

\end{proof}

\begin{lem}
For a positive integer $n$, the Jacobian of the map $f(X) = X^n$ is given by [insert here].
\end{lem}
\begin{proof}

\end{proof}

These two lemmas allow us to compute the Jacobian for our general situation.

\begin{cor}\label{signjacobian}
The determinant of the Jacobian for the map $f(X) =
S(X,B_i) - P$ is positive.
\end{cor}
\begin{proof}

\end{proof}

In light of these computations, a natural question is whether one can extend these ideas to deal with the complex case.  We present a simple example that exhibits some of the difficulty in pursuing such a generalization.

\begin{ex}
Show example where determinant of Jacobian can be zero.
\end{ex}

\section{Unique Solvability of Word Equations}

Before proving our main theorem, we first describe an important fact.  As in the previous section, we view the space of real symmetric $n$-by-$n$ matrices as $\text{Sym}_n(\mathbb R)  = \mathbb R^{n+1 \choose 2}$.  For positive $M$, we also set $U_M$ to be the open set of positive definite matrices with norm less than $M$.  Additionally, the value of $\mathbf y$ that we take will always be $\mathbf y = 0$.

\begin{prop}\label{degcountprop}
Let $B_i$ and $P$ be $n$-by-$n$ positive definite matrices and let $S(X,B_i)$ be a symmetric word.  For sufficiently large $M$, the degree of the map $f(X) = S(X,B_i) - P$ on $U_M$ is equal to the number of solutions to $f(X) = 0$ in $U_M$.
\end{prop}

\begin{proof}
Using Corollary \ref{signjacobian}, it follows that $0$ is a regular value for the differentiable map $f(X) = S(X,B_i) -P$.  The properties of Brouwer degree (Theorem \ref{sumjacob}) therefore imply that the degree of $f$ is a sum of Jacobian signs over the set of solutions to $f(X) = 0$.  Again by Corollary \ref{signjacobian}, each sign value is $1$, and the claim now follows.
\end{proof}

We are now ready to prove our main theorem.

\begin{proof}[Proof of Theorem \ref{ourmainthm}]
Let $B_i$, $P$ be $n$-by-$n$ PD matrices and let $S(X,B_i)$ be a symmetric word.  Using Proposition \ref{boundprop}, there exists an $M$ such that any solution $X$ to an
equation $S(X,B_it+(1-t)I) = P$ with $0 \leq t \leq 1$ has $\|X\| < M$.

Let $U_M$ be the open set of positive definite matrices with norm less than $M$.  Consider the mapping $f: \text{Sym}_n(\mathbb R) \to \text{Sym}_n(\mathbb R)$ given by $f(X) =  S(X,B_i)-P$.  We are interested in the fiber $f^{-1}(0)$, restricted to the open set $U_M$.

We first verify that the degree of the mapping $f$ with respect to $U_M$ is $1$.  From our choice of $M$, it follows that $f(X) \neq 0$ when $X$ is positive definite with norm $M$.  Moreover, if $X$ is singular, then taking a determinant shows that $f(X) \neq 0$.  It follows that $f(X)$ is never $0$ for $X$ on the boundary of $U_M$.

Consider the homotopy $f_t(X) = S(X,tB_i + (1-t)I)-P$ for $t \in [0,1]$.  Again, from our choice of $M$, we have $f_t \neq 0$ on the boundary of $U_M$.  The properties of Brouwer degree now imply that the degree of $f = f_1$ is the same as the degree of $f_{0}$.  It remains, therefore, to compute the Brouwer degree of the mapping $f_0(X) = X^s-P$, in which $s$ is the sum of the powers of the variable $X$ in $S(X,B_i)$.  The proposition above computes this integer to be $1$ and, therefore, equals the degree of $f$.

The proof is now finished with another application of Proposition \ref{degcountprop}.
\end{proof}

\section{Relations between positive definite
words}\label{wordrelationssection}

The purpose of this section is to explain the significance of the
symmetric restriction in the definition of ``symmetric word
equation.''  Specifically, we prove that a generalized word is
positive definite for all positive definite $A$ and $B$ if and
only if the word is symmetric.

\section{Approximate solutions}

We now make some remarks about finding approximate solutions to
symmetric word equations.  We detail a method that has been quite
effective in practice at finding solutions (in the case of
positive integral powers).

Given a symmetric word $S(A,B)$ with positive integral exponents,
start with an initial PD matrix, $A_{0}$, (usually $I$), and
expand the expression, $S(A_{0}+D,B)$.  Consider the formal sum,
$S'(A_{0}+D,B)$, of the terms in this expansion with at most a
single $D$. Now, solve the linear system \[S'(A_{0}+D,B) = P\] for
the matrix $D$ and set $A_{1}$ $ \leftarrow$ $A_{0} + D$.
Repeating this process gives our algorithm.  As a simple example,
the repeated equations for $ABA = P$ are given by
\[A_{i-1}BD + DBA_{i-1} = P - A_{i-1}BA_{i-1}\] \[A_{i} = A_{i-1}
+ D.\]  Curiously enough, there seems to be no guarantee in
general that these $A_{i}$ will be positive definite, nor is it
clear that the linear system for $D$ above will always have a
solution.  Nonetheless, experimentation has shown that these
iterations always converge to the same PD solution regardless of
initial starting point.

Of course, this scheme is just a version of Newton's method.
General theory, therefore, tells us that if $A_0$ is near the
unique solution $A$, iteration will converge to $A$.

\begin{thebibliography}{1}

\bibitem{JHcplx}
C. Hillar and C. R. Johnson, \textit{Positive Eigenvalues of Generalized Words in Two Hermitian Positive Definite Matrices}. Novel approaches to hard discrete optimization (Waterloo, ON, 2001), 111-122, Fields Inst. Commun., 37, Amer. Math. Soc., Providence, RI, 2003

\bibitem{JH2}
C. Hillar and C. R. Johnson, \emph{Symmetric Word Equations in Two
Positive Definite Letters}, Proc. Amer. Math. Soc., \textbf{132}
(2004), 945-953.

\bibitem{HJS}
C. Hillar, C. R. Johnson, and I. M. Spitkovsky, \textit{Positive  Eigenvalues and Two-letter Generalized Words}, Electron. J. Linear Algebra,  \textbf{9} (2002), 21-26.

\bibitem{HJ1}
R. Horn and C. R. Johnson, \emph{Matrix Analysis}, Cambridge
University Press, New York, 1985.

\bibitem{HJ2}
R. Horn and C. R. Johnson, \emph{Topics in Matrix Analysis},
Cambridge University Press, New York, 1991.

\bibitem{JH}
C. R. Johnson and C. Hillar, \emph{Eigenvalues of Words in Two
Positive Definite Letters}, SIAM J. Matrix Anal. Appl.,
\textbf{23} (2002), 916--928.

\bibitem{degthy}
N. Lloyd, \emph{Degree Theory}, Cambridge University Press, London, 1978.

\bibitem{teschl}
G. Teschl, \emph{Nonlinear Functional Analysis}, www.mat.univie.ac.at/~gerald/ftp/book-nlfa/.

\end{thebibliography}

\end{document}
% ----------------------------------------------------------------

### 2020-08-04 manuscripts/arxiv/final_submission.tex
everything

--- 2019-05-10 manuscripts/IEEE/final_submission.tex
@@
 % Can we prove in a line or two that the inverse problem is stable by arguing that the function is bijective and closed therefore a homeomorphism?
-% Should we mention the notion of Grassmannian manifolds and that Theta is a metric on this space?
 % Change robustness to stability?
@@
 \begin{center}
-\includegraphics[width=.24 \linewidth]{figs/basis.png}
-% \includegraphics[width=.25 \linewidth]{figs/Ahat_FastICA_M640_K8_noise0_2042}
-%\includegraphics[width=.24 \linewidth]{figs/Ahat_FastICA_M640_K8_noise0_4083.png}
-\includegraphics[width=.24 \linewidth]{figs/Ahat_FastICA_M640_K8_noise1_0205.png}
-\includegraphics[width=.24 \linewidth]{figs/Ahat_FastICA_M640_K8_noise2_0409.png}
-\includegraphics[width=.24 \linewidth]{figs/Ahat_FastICA_M640_K8_noise5_1021.png}
+\includegraphics[width=.24 \linewidth]{Basis.png}
+\includegraphics[width=.24 \linewidth]{Ahat_FastICA_M640_K8_noise1_0205.png}
+\includegraphics[width=.24 \linewidth]{Ahat_FastICA_M640_K8_noise2_0409.png}
+\includegraphics[width=.24 \linewidth]{Ahat_FastICA_M640_K8_noise5_1021.png}
 \caption{\textbf{Learning a dictionary from increasingly noisy data}.

### 2020-08-04 2017-06210R-AuthorResponse-2/code/compute_C2.py

@@ -1,0 +1,112 @@
+from decomp_svd import subspace_angles
+import numpy as np
+import itertools
+import operator as op
+from scipy.misc import comb as choose
+
+def friedrichs(U,V):
+    """
+    Calculates the Friedrichs angle between subspaces U and V (in radians).
+    The Friedrichs angle is the smallest nonzero principle angle.
+    Alternatively, it is the (s+1)th principal angle when dim(U \cap V) = s.
+    """
+    angles = subspace_angles(U,V)
+    return np.sort(angles)[0]
+
+def xi(A, G):
+    """
+    Calculates xi({A_S}_{S \in G})
+    (Assumes A is injective on H, so the intersection of the span is the span of the intersection.)
+    """
+    if len(G) == 1:
+        return 1 # by definition
+    Gs = itertools.permutations(G)
+    prods = []
+    for Gseq in Gs: # loop through all orderings of elements in G
+        prod = 1.
+        for i, Si in enumerate(Gseq[:-1]):
+            cap_Sj = list(set.intersection(*map(set, Gseq[i+1:])))
+            if cap_Sj: # otherwise they intersect only at 0 and sin(theta) = 1, since every subspace forms pi/2 angle with 0
+                theta = friedrichs(A[:,Si], A[:,cap_Sj])
+                prod *=  np.sin(theta)**2
+        prods.append(prod)
+    return 1 - np.sqrt(1 - np.max(prods))
+
+def C2(A, H, r):
+    """
+    Ouputs the constant C2
+
+    A: n x m dictionary matrix (2d numpy array)
+    H: hypergraph (list of lists in range(m))
+    r: regularity of H
+
+    Loops over subsets of H of size r + 1
+    """
+    xi_Gs = [] # xi is in (0,1]
+    for G in itertools.combinations(H, r + 1): # loop over subsets of H of size r + 1
+        xi_Gs.append( xi(A, G) )
+    max_A = np.max( np.linalg.norm(A, axis=0) )
+    return len(H) * max_A / min(xi_Gs)
+
+def cyclic_hypergraph(m, k):
+    H = []
+    for i in range(m - k + 1):
+        H.append(list(range(i, i + k)))
+    for i in range(1, k):
+        j = k - i
+        H.append(list(range(m - j, m)) + list(range(0, k - j)))
+    return H
+
[…]

### 2020-08-04 2017-06210R-AuthorResponse-2/code/decomp_svd.py

@@ -1,0 +1,404 @@
+"""SVD decomposition functions."""
+from __future__ import division, print_function, absolute_import
+
+import numpy
+from numpy import zeros, r_, diag, dot, arccos, arcsin, where, clip
+
+# Local imports.
+from scipy.linalg.misc import LinAlgError, _datacopied
+from scipy.linalg.lapack import get_lapack_funcs, _compute_lwork
+from scipy.linalg.decomp import _asarray_validated
+from scipy._lib.six import string_types
+
+__all__ = ['svd', 'svdvals', 'diagsvd', 'orth', 'subspace_angles', 'null_space']
+
+
+def svd(a, full_matrices=True, compute_uv=True, overwrite_a=False,
+        check_finite=True, lapack_driver='gesdd'):
+    """
+    Singular Value Decomposition.
+    Factorizes the matrix `a` into two unitary matrices ``U`` and ``Vh``, and
+    a 1-D array ``s`` of singular values (real, non-negative) such that
+    ``a == U @ S @ Vh``, where ``S`` is a suitably shaped matrix of zeros with
+    main diagonal ``s``.
+    Parameters
+    ----------
+    a : (M, N) array_like
+        Matrix to decompose.
+    full_matrices : bool, optional
+        If True (default), `U` and `Vh` are of shape ``(M, M)``, ``(N, N)``.
+        If False, the shapes are ``(M, K)`` and ``(K, N)``, where
+        ``K = min(M, N)``.
+    compute_uv : bool, optional
+        Whether to compute also ``U`` and ``Vh`` in addition to ``s``.
+        Default is True.
+    overwrite_a : bool, optional
+        Whether to overwrite `a`; may improve performance.
+        Default is False.
+    check_finite : bool, optional
+        Whether to check that the input matrix contains only finite numbers.
+        Disabling may give a performance gain, but may result in problems
+        (crashes, non-termination) if the inputs do contain infinities or NaNs.
+    lapack_driver : {'gesdd', 'gesvd'}, optional
+        Whether to use the more efficient divide-and-conquer approach
+        (``'gesdd'``) or general rectangular approach (``'gesvd'``)
+        to compute the SVD. MATLAB and Octave use the ``'gesvd'`` approach.
+        Default is ``'gesdd'``.
+        .. versionadded:: 0.18
+    Returns
+    -------
+    U : ndarray
[…]

### 2020-08-04 2017-06210R-AuthorResponse-2/code/sample_complexity.py

@@ -1,0 +1,110 @@
+"""
+Compute the probability that for every S in H, there are at least k vectors x_i supported there which share a support in B
+"""
+# TODO: Try alternative formula for bounded pigeonhole
+
+import numpy as np
+from scipy.misc import comb
+
+def pigeonhole_bounded_alt(num_balls, num_bins, max_balls_per_bin):
+    # TODO: supposed to work better for large N
+    pass
+
+def pigeonhole_bounded(num_balls, num_bins, max_balls_per_bin):
+    """
+    Returns the number of ways to allocate num_balls to num_bins without exceeding max_balls_per_bin in any bin
+
+    Source URL:
+    https://math.stackexchange.com/questions/553960/extended-stars-and-bars-problemwhere-the-upper-limit-of-the-variable-is-bounded
+    """
+    lim = int(min(num_bins, 1.*num_balls / (max_balls_per_bin+1)))
+    val = 0
+    for q in range(lim+1):
+        sgn = (-1)**q
+        term_1 = comb(num_bins, q)
+        term_2 = comb(num_balls - q*(max_balls_per_bin + 1) + num_bins - 1, num_bins - 1)
+        val += sgn * term_1 * term_2
+    return val
+
+def pigeonhole(num_balls, num_bins):
+    """
+    Returns the number of ways to allocate num_balls to num_bins.
+    """
+    return comb(num_balls + num_bins - 1, num_bins - 1)
+
+def prob_atleast_k(num_balls, num_bins, k):
+    """
+    Returns the probability that some bin contains at least k balls
+    """
+    bnded = pigeonhole_bounded( num_balls, num_bins, max_balls_per_bin = k-1)
+    tot = pigeonhole( num_balls, num_bins )
+    return 1 - bnded / tot
+
+if __name__ == '__main__':
+    import matplotlib.pyplot as pp
+    import os
+    try:
+        os.mkdir('./figures')
+    except:
+        pass
+    pp.ion()
+
+    """
+    Given N_supp samples per support, what is the probability that for every S in H,
+    at least k out of N_supp vectors supported there have the same support wrt. B?
+    """
+    m = 16
+    k = 2
+    num_supps = m # cyclic order hypergraph
+    samples_per_supp_deterministic = int((k-1) * comb(m,k)) + 1 # with N_deterministic per support or more, probability is 1 (deterministic case)
+    probs = []
+    for samples_per_supp in range(samples_per_supp_deterministic):
[…]

### 2020-08-04 manuscripts/IEEE/submission/referee-responses.txt

--- 2019-05-08 manuscripts/IEEE/submission/referee_responses.txt
@@
 -------------------------------------
-Response: Thanks for your comments.  As far as we understand, our work is the first to prove stability of unique representations in sparse coding under deterministic noise.
+Response: Thank you for your comments.
 -------------------------------------
@@
 The first inequality follows from the fact that (m choose 2) is a subset of 2H, provided ∪H = [m], since only then can every pair of columns be captured by the union of two supports in H.
-We have updated the text to explain this.
 -------------------------------------
@@
 -------------------------------------
-Response: Here for us, "Substitution" means such assignments or choices of real numbers to the indeterminate variables (i.e., the map from a direct product of R's to the corresponding matrix and vector spaces).
-We frame it as a theorem and not a corollary because we draw the important Corollary 2 directly from it.
+Response: Yes, "substitution" means assignments or choices of real numbers for the indeterminate variables.
+We feel it is better framed as a theorem as: a) it is an importnat stand-alone fact, and b) we draw the important Corollary 2 directly from it.
 We have downgraded Proposition 1 to an informal claim in the revised discussion.
@@
 -------------------------------------
-Response: Thanks for your comments.
+Response: Thank you for your comments.
 (1) Although computable, indeed, checking the conditions of assumptions in our theorems is often NP-hard as we explain in the manuscript; we have updated the revision for more clarity on this.
-(2) We also believe that this numerical optimization is NP-hard and include this question in the revised discussion; we also pose there whether the more tractable l1 norm version implies the same uniqueness results.
+(2) We also believe that this numerical optimization is NP-hard and include this question in the revised discussion; further, we now pose the problem of whether the more tractable l1 norm version implies the same uniqueness results.
 -------------------------------------
@@
 Below are some more detailed comments:
+
+-------------------------------------
+Response: Thank you for your comments. 
+-------------------------------------
 
@@
 https://arxiv.org/pdf/1807.05595.pdf
-
--------------------------------------
-Response: We make no claims in this paper about l1-norm minimization, though we are hopeful a clever reader may find some way to build off our results and derive related guarantees for this continuous relaxation of the sparse coding problem (we pose this problem in the discussion).
--------------------------------------
-
 But heuristic methods are proposed there to check global optimality. A discussion and elaboration on this could be very helpful here.
@@
 -------------------------------------
-Response: We only claim that our general uniqueness criteria provide a (not necessarily efficient) means of checking the globality of a proposed solution.
-It could be that in certain restricted cases these conditions are efficiently computable, but this is not the case in general.
+Response: We make no claims in this paper about l1-norm minimization, though we are hopeful a clever reader may find some way to build off our results and derive related guarantees for this continuous relaxation of the sparse coding problem.
+We elaborate more on this in the revised discussion, including adding open challenges for researchers.
 -------------------------------------
@@
 Response: In the prose surrounding Corollary 1, we give a deterministic construction of sparse vectors x_i satisfying the constraints of Theorem 1.
+We have made this more clear in the revised submission.
 -------------------------------------

### 2020-08-04 manuscripts/IEEE/submission/referee_responses.txt

@@
 (1) Although computable, indeed, checking the conditions of assumptions in our theorems is often NP-hard as we explain in the manuscript; we have updated the revision for more clarity on this.
-(2) We also believe that this numerical optimization is NP-hard and include this question in the revised discussion; we also pose there whether the more tractable l1 norm version implies the same uniqueness results.
+(2) We also believe that this numerical optimization is NP-hard and include this question in the revised discussion; further, we now pose the problem of whether the more tractable l1 norm version implies the same uniqueness results.
 -------------------------------------

### 2020-08-05 manuscripts/newthesis/appendix.tex
newthesis

--- 2019-05-10 manuscripts/IEEE/final_submission.tex
@@
-% TODO: 
-% Make L_H a definition..? Change def of L to be 1-norm so we don't need these sqrt k's?
-% C_1 depends on J in Thm 1
-% also in proof of (7) x need not be *any* 2k-sparse vector...can instead restrict to some H...then 2k is restricted to half being on H.
-
-% Notes:
-%
-% Can we prove in a line or two that the inverse problem is stable by arguing that the function is bijective and closed therefore a homeomorphism?
-% Should we mention the notion of Grassmannian manifolds and that Theta is a metric on this space?
-% Change robustness to stability?
-%
-\documentclass[journal, twocolumn]{IEEEtran}
-
-% *** MATH PACKAGES ***
-\usepackage{amsmath, amssymb, amsthm} 
-\newtheorem{theorem}{Theorem}
-\newtheorem{lemma}{Lemma}
-\newtheorem{conjecture}{Conjecture}
-\newtheorem{problem}{Problem}
-\newtheorem{question}{Question}
-\newtheorem{proposition}{Proposition}
-\newtheorem{definition}{Definition}
-\newtheorem{corollary}{Corollary}
-\newtheorem{remark}{Remark}
-\newtheorem{example}{Example}
-
-\usepackage[pdftex]{graphicx}
-
-% *** ALIGNMENT PACKAGES ***
-\usepackage{array}
-\usepackage{cite}
-\usepackage{bm}
-
-% correct bad hyphenation here
-%\hyphenation{op-tical net-works semi-conduc-tor}
-
-\begin{document}
-
-%\title{When can a generating dictionary and sparse codes be recovered from noisy data?}
-%\title{When is the dictionary learning problem well-posed?}
-\title{On the uniqueness and stability of dictionaries \\ for sparse representation of noisy signals}
-%\title{When is the dictionary learning problem for sparse coding well-posed?}
-%\title{When is the sparsest representation unique?}
-%\title{When are sparse codes identifiable from their unknown noisy compressive measurements?}
-% FRITZ2: The title doesn't reflect the amount of new stuff, it seems incremental from the last one. It's not very meaningful.
-% FRITZ: Not everyone knows what well-posed means. You should mention recovery from noisy data in the title.
-
-\author{Charles~J.~Garfinkle and Christopher~J.~Hillar \\
-Redwood Center for Theoretical Neuroscience, Berkeley, CA, USA
-%\thanks{%e-mails: cjg@berkeley.edu, chillar@msri.org.  
-%CG and CH supported, in part, by NSF grant IIS-1219212 and the Statistical and Applied Mathematical Sciences Institute, under NSF DMS-1127914.}
-}
-
-\maketitle
-
-% \keywords{Sparse coding, dictionary learning, matrix factorization, compressed sensing, inverse problems, blind source separation}
-
-\begin{abstract}
-%Learning optimal dictionaries for sparse coding has exposed characteristic sparse features of many natural signals.
-However, there are few universal conditions guaranteeing the stability of such features in the presence of noise.
-Here, we prove very generally that optimal dictionaries and sparse codes are unique up to measurement error for all diverse enough datasets generated by the sparse coding model.
-Applications are given to data analysis, engineering, and neuroscience.
-Learning optimal dictionaries for sparse coding has exposed characteristic sparse features of many natural signals.
-However, universal guarantees of the stability of such features in the presence of noise are lacking.
-Here, we provide very general conditions guaranteeing when dictionaries yielding the sparsest encodings are unique and stable with respect to measurement or modeling error.
-We demonstrate that some or all original dictionary elements are recoverable from noisy data even if the dictionary fails to satisfy the spark condition, its size is overestimated, or only a polynomial number of distinct sparse supports appear in the data.
-Importantly, we derive these guarantees without requiring any constraints on the recovered dictionary beyond a natural upper bound on its size.
-Our results also yield an effective procedure sufficient to affirm if a proposed solution to the dictionary learning problem is unique within bounds commensurate with the noise.
-We suggest applications to data analysis, engineering, and neuroscience and close with some remaining challenges left open by our work.
-\end{abstract}
-
-% Optional adjustment to line up main text (after abstract) of first page with line numbers, when using both lineno and twocolumn options.
-% You should only change this length when you've finalised the article contents.
-
-\section{Introduction}\label{Intro}
-\IEEEPARstart{S}{parse} coding is a common modern approach to pattern analysis in signal processing whereby each of $N$ observed $n$-dimensional signal samples is viewed as a (noisy) linear combination of at most $k$ elementary waveforms drawn from some unknown ``dictionary" of size $m \ll N$ (see \cite{Zhang15} for a comprehensive review).
-%\IEEEPARstart{A}{}common modern approach to pattern analysis in signal processing is to view each of $N$ observed $n$-dimensional signal samples as a (noisy) linear combination of at most $k$ elementary waveforms drawn from some unknown ``dictionary" of size $m \ll N$ (see \cite{Zhang15} for a comprehensive review).
-Optimizing dictionaries subject to this and related sparsity constraints has revealed seemingly characteristic sparse structure in several signal classes of current interest (e.g., in vision \cite{wang2015sparse}).
-
-Of particular note are the seminal works in the field \cite{Olshausen96, hurri1996image, bell1997independent, van1998independent}, which discovered that dictionaries optimized for coding small patches of ``natural" images share qualitative similarities with linear filters estimated from response properties of simple-cell neurons in mammalian visual cortex.
-Curiously, these waveforms (e.g., ``Gabor'' wavelets) appear in dictionaries learned by a variety of algorithms trained over different natural image datasets, suggesting that learned features in natural signals may, in some sense, be canonical \cite{donoho2001can}.
-
-Motivated by these discoveries and more recent work relating compressed sensing \cite{eldar2012compressed} to a theory of information transmission through random wiring bottlenecks in the brain \cite{Isely10}, we address when dictionaries for sparse representation are indeed identifiable from data.
-Answers to this question may also have implications in practice wherever an appeal is made to latent sparse structure of data (e.g., forgery detection \cite{hughes2010, olshausen2010applied}; brain recordings \cite{jung2001imaging, agarwal2014spatially, lee2016sparse}; and gene expression \cite{wu2016stability}).
-
-While several algorithms have been recently proposed to provably recover unique dictionaries under specific conditions (see \cite[Sec.~I-E]{Sun16} for a summary of the state-of-the-art), few theorems can be invoked to justify the consistency of inference under this model of data more broadly.
-To our knowledge, a universal guarantee of the uniqueness and stability of learned dictionaries and the sparse representations they induce over noisy data has yet to appear in the literature.
-% in justifying the identification of forged paintings by their anomalous sparse representations \cite{hughes2010},
-
-Here, we prove very generally that uniqueness and stability is a typical property of sparse dictionary learning.
-More specifically, we show that matrices injective on a sparse domain are identifiable from \mbox{$N = m(k-1){m \choose k} + m$} noisy linear combinations of $k$ of their $m$ columns up to an error that is linear in the noise (Thm.~\ref{DeterministicUniquenessTheorem}).
-In fact, provided $n \geq \min(2k,m)$, in almost all cases the problem is well-posed, as per Hadamard \cite{Hadamard1902}, given a sufficient amount of data (Thm.~\ref{robustPolythm} and Cor.~\ref{ProbabilisticCor}).
-
-Our guarantees also hold for a related (and perhaps more commonly posed, e.g.
-\cite{rehnsommer2007}) optimization problem seeking a dictionary minimizing the average number of elementary waveforms required to reconstruct each sample of the dataset (Thm.~\ref{SLCopt}).
-To practical benefit, our results impose no restrictions on learned dictionaries (e.g., that they, too, be injective over some sparse domain) beyond an upper bound on dictionary size, which is necessary in any case to avoid trivial solutions (e.g., allowing $m = N$).
-%That is, every pair of solutions of comparable size has some number of dictionary elements in common (up to noise), and similarly so for the coefficients of sparse codes they induce.
-
-More precisely, let $\mathbf{A} \in \mathbb R^{n \times m}$ be a matrix with columns $\mathbf{A}_j$ ($j = 1,\ldots,m$) and let dataset $Z$ consist of measurements:
-\begin{align}\label{LinearModel}
-\mathbf{z}_i = \mathbf{A}\mathbf{x}_i + \mathbf{n}_i,\ \ \  \text{$i=1,\ldots,N$},
-\end{align}
-for $k$-\emph{sparse} $\mathbf{x}_i \in \mathbb{R}^m$ having at most $k<m$ nonzero entries and \emph{noise} $\mathbf{n}_i \in \mathbb{R}^n$, with bounded norm $\| \mathbf{n}_i \|_2 \leq  \eta$ representing our worst-case uncertainty in measuring the product $\mathbf{A}\mathbf{x}_i$.
-We first consider the following formulation of sparse coding.
-%The first mathematical problem we consider is the following.
-
-\begin{problem}\label{InverseProblem}
-Find a dictionary matrix $\mathbf{B}$ and $k$-sparse codes $\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N$ that satisfy $\|\mathbf{z}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \eta$ for all $i = 1,\ldots,N$.
-\end{problem}
-
-Note that every solution to Prob.~\ref{InverseProblem} represents infinitely many equivalent alternatives $\mathbf{BPD}$ and $\mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_1, \ldots, \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_N$ parametrized by a choice of permutation matrix $\mathbf{P}$ and invertible diagonal matrix $\mathbf{D}$.
-Identifying these ambiguities (labelling and scale) yields a single orbit of solutions represented by any particular set of elementary waveforms (the columns of $\mathbf{B}$) and their associated sparse coefficients (the entries of $\mathbf{\overline x}_i$) that reconstruct each data point $\mathbf{z}_i$.
-
-Previous theoretical work addressing the noiseless case $\eta =0$ (e.g., \cite{li2004analysis, Georgiev05, Aharon06, Hillar15}) for matrices $\mathbf{B}$ having exactly $m$ columns has shown that a solution to Prob.~\ref{InverseProblem}, when it exists, is unique up to such relabeling and rescaling provided the $\mathbf{x}_i$ are sufficiently diverse and $\mathbf{A}$ satisfies the \textit{spark condition}:
-\begin{align}\label{SparkCondition}
-\mathbf{A}\mathbf{x}_1 = \mathbf{A}\mathbf{x}_2 \implies \mathbf{x}_1 = \mathbf{x}_2, \ \ \ \text{for all $k$-sparse } \mathbf{x}_1, \mathbf{x}_2,
-\end{align}
-%
-which is necessary to guarantee the uniqueness of arbitrary $k$-sparse $\mathbf{x}_i$.
-We generalize these results to the practical setting  $\eta > 0$ by considering the following natural notion of stability with respect to measurement error.
-
-\begin{definition}\label{maindef}
-Fix $Y = \{ \mathbf{y}_1, \ldots, \mathbf{y}_N\} \subset \mathbb{R}^n$.
-We say $Y$ has a \textbf{$k$-sparse representation in $\mathbb{R}^m$} if there exists a matrix $\mathbf{A}$ and $k$-sparse $\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$ such that $\mathbf{y}_i = \mathbf{A}\mathbf{x}_i$ for all $i$.
-This representation is \textbf{stable} if for every $\delta_1, \delta_2 \geq 0$, there exists some $\varepsilon = \varepsilon(\delta_1, \delta_2)$ that is strictly positive for positive $\delta_1$ and $\delta_2$ such that if $\mathbf{B}$ and $k$-sparse $\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N \in \mathbb{R}^m$ satisfy:
-\begin{align*}
-	\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \varepsilon(\delta_1, \delta_2),\ \   \text{for all $i=1,\ldots,N$},
-\end{align*}
-then there is some permutation matrix $\mathbf{P}$ and invertible diagonal matrix $\mathbf{D}$ such that for all $i, j$:
-\begin{align}\label{def1}
-\|\mathbf{A}_j - (\mathbf{BPD})_j\|_2 \leq \delta_1 \ \text{and} \ \|\mathbf{x}_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_i\|_1 \leq \delta_2.
-\end{align}
-\end{definition}
-
-To see how Prob.
-\ref{InverseProblem} motivates Def.
-\ref{maindef}, suppose that $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$ and fix $\delta_1, \delta_2$ to be the desired accuracies of recovery in \eqref{def1}.
-Consider any dataset $Z$ generated as in \eqref{LinearModel} with $\eta \leq \frac{1}{2} \varepsilon(\delta_1, \delta_2)$.
-Using the triangle inequality, it follows that any $n \times m$ matrix $\mathbf{B}$ and $k$-sparse $\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N$ solving Prob.~\ref{InverseProblem} are necessarily within $\delta_1$ and $\delta_2$ of the original dictionary $\mathbf{A}$ and codes $\mathbf{x}_1, \ldots, \mathbf{x}_N$, respectively.\footnote{We mention that the different norms in \eqref{def1} reflect the distinct meanings typically ascribed to the dictionary and sparse codes in modeling data.}
-
-The main result of this work is a very general uniqueness theorem for sparse coding (Thm.~\ref{DeterministicUniquenessTheorem}) directly 
-implying (Cor.~\ref{DeterministicUniquenessCorollary}), which guarantees that sparse representations of a dataset $Z$ are unique up to noise whenever generating dictionaries $\mathbf{A}$ satisfy a spark condition on supports and the original sparse codes $\mathbf{x}_i$ are sufficiently diverse (e.g., Fig.~\ref{noisyrecovery}).
-Moreover, we provide an explicit, computable $\varepsilon(\delta_1, \delta_2)$ in (\ref{epsdel}) that is linear in desired accuracy $\delta_1$, and essentially so in $\delta_2$.
-
-In the next section, we give formal statements of these findings.
-We then extend the same guarantees (Thm.~\ref{SLCopt}) to the following alternate formulation of dictionary learning, which minimizes the total number of nonzero entries in sparse codes.
-
-\begin{problem}\label{OptimizationProblem}
-Find matrices $\mathbf{B}$ and vectors \mbox{$\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N$} solving:
-\begin{align}\label{minsum}
-\min \sum_{i = 1}^N \|\mathbf{\overline x}_{i}\|_0 \ \
-\text{subject to} \ \ \|\mathbf{z}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \eta, \ \text{for all $i$}.
-\end{align}
-\end{problem}
-
-Our development of Thm.~\ref{DeterministicUniquenessTheorem} is general enough to provide some uniqueness and stability even when generating $\mathbf{A}$ do not fully satisfy (\ref{SparkCondition}) and recovery dictionaries $\mathbf{B}$ have more columns than $\mathbf{A}$.
-Moreover, the approach incorporates a combinatorial theory for designing generating codes that should be of independent interest.
-We also give brief arguments adapting our results to dictionaries and codes drawn from probability distributions (Cor.~\ref{ProbabilisticCor}).
-The technical proofs of Thms.~\ref{DeterministicUniquenessTheorem} and ~\ref{SLCopt} are deferred to Sec.~\ref{DUT}, following some necessary definitions and a fact in combinatorial matrix analysis (Lem.~\ref{MainLemma}; proven in the Appendix).
-Finally, we discuss in Sec.~\ref{Discussion} applications of our mathematical observations as well as open questions.
-%The Appendix contains a proof of Lem.~\ref{MainLemma}.
-
-\section{Results}\label{Results}
-
-%Denote by $\mathbf{x}^J$ the subvector formed from the entries of $\mathbf{x}$ indexed by $J$. 
-%A set of $k$-sparse vectors is said to be in \emph{general linear position} when any $k$ of them are linearly independent.
-
-Precise statements of our results require that we first identify some combinatorial criteria on the supports\footnote{Recall that a vector $\mathbf{x}$ is said to be \emph{supported} in $S$ when $\mathbf{x} \in \text{\rm span}\{\mathbf{e}_j: j\in S\}$, with $\mathbf{e}_j$ forming the standard column basis.} of sparse vectors.
-Let $\{1, \ldots, m\}$ be denoted $[m]$, its power set $2^{[m]}$, and ${[m] \choose k}$ the set of subsets of $[m]$ of size $k$.
-A \emph{hypergraph} on vertices $[m]$  is simply any subset $\mathcal{H} \subseteq 2^{[m]}$.
-We say that $\mathcal{H}$ is \textit{$k$-uniform} when $\mathcal{H} \subseteq {[m] \choose k}$.
-The \emph{degree} $\deg_\mathcal{H}(i)$ of a node $i \in [m]$ is the number of sets in $\mathcal{H}$ that contain $i$, and we say $\mathcal{H}$ is \emph{regular} when for some $r$ we have $\deg_\mathcal{H}(i) = r$ for all $i$ (given such an $r$, we say $\mathcal{H}$ is \textit{$r$-regular}).
-We also write $2\mathcal{H} := \{ S \cup S': S, S' \in \mathcal{H}\}$.
-The following class of structured hypergraphs is a key ingredient in this work.
-
-\begin{definition}\label{sip}
-Given $\mathcal{H} \subseteq 2^{[m]}$, the \textbf{star} $\sigma(i)$ is the collection of sets in $\mathcal{H}$ containing $i$.
-We say $\mathcal{H}$ has the \textbf{singleton intersection property} (\textbf{SIP}) when $\cap \sigma(i) = \{i\}$ for all $i \in [m]$.
-\end{definition}
-
-We next give a quantitative generalization of the spark condition (\ref{SparkCondition}) to combinatorial subsets of supports.
-The \emph{lower bound} of an $n \times m$ matrix $\mathbf{M}$ is the largest $\alpha$ with \mbox{$\|\mathbf{M}\mathbf{x}\|_2 \geq \alpha\|\mathbf{x}\|_2$} for all $\mathbf{x} \in \mathbb{R}^m$ \cite{Grcar10}.
-By compactness of the unit sphere, every injective linear map has a positive lower bound; hence, if $\mathbf{M}$ satisfies \eqref{SparkCondition}, then submatrices formed from $2k$ of its columns or less have strictly positive lower bounds.
-
-The lower bound of a matrix is generalized below in (\ref{Ldef}) by restricting it to the spans of certain submatrices\footnote{See \cite{vidal2005generalized} for an overview of the related ``union of subspaces" model.} associated with a hypergraph $\mathcal{H} \subseteq {[m] \choose k}$ of column indices.
-Let $\mathbf{M}_S$ denote the submatrix formed by the columns of a matrix $\mathbf{M}$ indexed by $S \subseteq [m]$ (setting $\mathbf{M}_\emptyset := \mathbf{0}$).
-In the sections that follow, we shall also let $\bm{\mathcal{M}}_S$ denote the column-span of a submatrix $\mathbf{M}_S$, and $\bm{\mathcal{M}}_\mathcal{G}$ to denote $\{\bm{\mathcal{M}}_S\}_{S \in \mathcal{G}}$.
-We define:  % Define $L_\mathcal{H}(\mathbf{M})$ as follows:
-%\begin{align*} 
-%L_\mathcal{H}(\mathbf{M}) := \min \left\{ \frac{ \|\mathbf{M}(\mathbf{x}_1-\mathbf{x}_2)\|_2 }{ \sqrt{2k} \|\mathbf{x}_1-\mathbf{x}_2\|_2} : \mathbf{x}_1, \mathbf{x}_2 \in \cup_{S \in \mathcal{H}} \bm{\mathcal{M}}_S \right\},
-%\end{align*} 
-%
-%where we write $L_{2k}$ in place of $L_\mathcal{H}$ when $\mathcal{H} = {[m] \choose k}$.
-Note that if $\mathcal{H}$ covers $[m]$, then $L_2 > L_\mathcal{H}$.\footnote{The reader should beware that $L_2 = L_{[m]}$, whereas $L = L_{\{[m]\}}$.
-For even $k$, the quantity $1 - \sqrt{k} L_k(\mathbf{M})$ is also known in the compressed sensing literature as the (asymmetric) lower restricted isometry constant \cite{Blanchard2011}.} Clearly, for any $\mathbf{M}$ satisfying \eqref{SparkCondition}, we have $L_{k'}(\mathbf{M}) > 0$ for  $k' \leq 2k$.
-%\begin{align*}
-%L_\mathcal{H}(\mathbf{M}) := \min \left\{ \frac{ \|\mathbf{M}_S\mathbf{x}\|_2 }{ \sqrt{k} \|\mathbf{x}\|_2} : S \in \mathcal{H} \right\},
-%\end{align*} 
-%\begin{align*}
-%L_\mathcal{H}(\mathbf{M}) := \max \left\{ \ falpha: \|\mathbf{M}_S\mathbf{x}\|_2 \geq \alpha \sqrt{k} \|\mathbf{x}\|_2 : S \in \mathcal{H}, \ \ \mathbf{x} \in \mathbb{R}^m \right\},
-%\end{align*} 
-\begin{align}\label{Ldef}
-L_\mathcal{H}(\mathbf{M}) := \min \left\{ \frac{\|\mathbf{M}_S\mathbf{x}\|_2}{ \sqrt{k} \|\mathbf{x}\|_2} : S \in \mathcal{H}, \ \mathbf{0} \neq \mathbf{x} \in \mathbb{R}^{|S|} \right\},
-\end{align} 
-%
-writing also $L_{k}$ in place of $L_\mathcal{H}$ when $\mathcal{H} = {[m] \choose k}$.\footnote{In compressed sensing literature, \mbox{$1 - \sqrt{k} L_k(\mathbf{M})$}  is the asymmetric lower restricted isometry constant for $\mathbf{M}$ with unit $\ell_2$-norm columns \cite{Blanchard2011}.}  As explained above, compactness implies that $L_{2k}(\mathbf{M}) > 0$ for all $\mathbf{M}$ satisfying \eqref{SparkCondition}.
-Clearly, $L_{\mathcal{H}'}(\mathbf{M}) \geq L_\mathcal{H}(\mathbf{M})$ whenever $\mathcal{H}' \subseteq \mathcal{H}$, and similarly any $k$-uniform $\mathcal{H}$ satisfying $\cup \mathcal{H} = [m]$ has $L_2 \geq L_{2\mathcal{H}} \geq L_{2k}$ (letting $L_{2k}$ := $L_m$ whenever $2k > m$).
-
-We are now in a position to state our main result, though for expository purposes we leave the quantity $C_1$ %(a function of $\mathbf{A}$, $\mathbf{x}_1, \ldots, \mathbf{x}_N$, and $\mathcal{H}$) 
-undefined until Sec.~\ref{DUT}. All results  below assume real matrices and vectors.
-
-%eps-tightness COUNTER-EXAMPLE:
-%Consider the alternate dictionary $B = \left(\mathbf{0}, \frac{1}{2}(\mathbf{e}_1 + \mathbf{e}_2), \mathbf{e}_3, \ldots, \mathbf{e}_{m} \right)$ and sparse codes $\mathbf{b}_i = \mathbf{e}_2$ for $i = 1, 2$ and $\mathbf{b}_i = \mathbf{e}_i$ for $i = 3, \ldots, m$.
-Then $|A\mathbf{a}_i - B\mathbf{b}_i| = 1/\sqrt{2}$ for $i = 1, 2$ (and $0$ otherwise).
-If there were permutation and invertible diagonal matrices $P \in \mathbb{R}^{m \times m}$ and $D \in \mathbb{R}^{m \times m}$ such that $|(A-BPD)\mathbf{e}_i| \leq C\varepsilon$ for all $i \in [m]$, then we would reach the contradiction $1 = |P^{-1}\mathbf{e}_1|_2 = |(A-BPD)P^{-1}\mathbf{e}_1|_2 \leq 1/\sqrt{2}$.
-
-\begin{theorem}\label{DeterministicUniquenessTheorem}
-%Fix integers $n, k, m$ and $\overline m$. 
-If an $n \times m$ matrix $\mathbf{A}$ satisfies $L_{2\mathcal{H}}(\mathbf{A}) > 0$ for some $r$-regular $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP, and $k$-sparse \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} include more than $(k-1){\overline m \choose k}$ vectors in general linear position\footnote{Recall that a set of vectors sharing support $S$ are in \emph{general linear position} when any $|S|$ of them are linearly independent.} supported in each $S \in \mathcal{H}$, then the following recovery guarantees hold for $C_1 > 0$ given by \eqref{Cdef1}.
-
-\textbf{Dictionary Recovery:} Fix $\varepsilon < L_{2}(\mathbf{A}) / C_1$.\footnote{Note that the condition $\varepsilon < L_2(\mathbf{A}) /C_1$ is necessary; otherwise, with \mbox{$\mathbf{A}$ = $\mathbf{I}$} (the identity matrix) and $\mathbf{x}_i = \mathbf{e}_i$, the matrix $\mathbf{B} = \left[\mathbf{0}, \frac{1}{2}(\mathbf{e}_1 + \mathbf{e}_2), \mathbf{e}_3, \ldots, \mathbf{e}_{m} \right]$ and sparse codes $\mathbf{\overline x}_i = \mathbf{e}_2$ for $i = 1, 2$ and $\mathbf{\overline x}_i = \mathbf{e}_i$ for $i \geq 3$ satisfy $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline x}_i \|_2 \leq \varepsilon$ but nonetheless violate \eqref{Cstable}.} If an $n \times \overline m$ matrix $\mathbf{B}$ has, for every $i \in [N]$, an associated $k$-sparse $\mathbf{\overline x}_i$ satisfying \mbox{$\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \varepsilon$}, then $\overline m \geq m$, and provided that $\overline m (r-1) < mr$, there is a permutation matrix $\mathbf{P}$ and an invertible diagonal matrix $\mathbf{D}$ such that:
-\begin{align}\label{Cstable}
-\|\mathbf{A}_j- (\mathbf{BPD})_j\|_2 \leq C_1 \varepsilon, \ \ \text{for all } j \in J,
-\end{align}
-%
-for some $J \subseteq [m]$ of size \mbox{$m - (r-1)(\overline m - m)$}. 
-% $\overline m - r(\overline m - m)$
-
-\textbf{Code Recovery:} If, moreover, $\mathbf{A}_J$ satisfies \eqref{SparkCondition} and $\varepsilon < L_{2k}(\mathbf{A}_J) / C_1$, then $(\mathbf{BP})_J$ also satisfies \eqref{SparkCondition} with $L_{2k}(\mathbf{BP}_J) \geq (L_{2k}(\mathbf{A}_J) - C_1 \varepsilon) / \|\mathbf{D}_J\|_1$, and for all $i \in [N]$:
-\begin{align}\label{b-PDa}
-%\|\mathbf{x}^J_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}^{\overline J}_i\|_1 &\leq  \left( \frac{ 1+C_1 \|\mathbf{x}^{J}_i\|_1 }{ L_{2k}(\mathbf{A}) -  C_1\varepsilon } \right) \varepsilon \ \  \text{for $i \in [N]$}.
-\|(\mathbf{x}_i)_J - (\mathbf{D}^{-1}\mathbf{P}^{\top} \mathbf{\overline x}_i)_J\|_1 &\leq  \left( \frac{ 1+C_1 \|(\mathbf{x}_i)_J\|_1 }{ L_{2k}(\mathbf{A}_J) -  C_1\varepsilon } \right) \varepsilon,
-\end{align}
-%
-where subscript $(\cdot)_J$ here represents the subvector formed from restricting to coordinates indexed by $J$.
-\end{theorem}
-
-%We delay defining the explicit constant $C_1$ until Section \ref{DUT} (\eqref{Cdef1}).
-%To be clear, the implication of Thm.~\ref{DeterministicUniquenessTheorem} is that $Y = \{\mathbf{Ax}_1, \ldots, \mathbf{Ax}_N\}$ has a stable $k$-sparse representation in $\mathbb{R}^m$, with \eqref{def1} guaranteed provided $\varepsilon$ in Def.~\ref{maindef} does not exceed:
-In words, Thm.~\ref{DeterministicUniquenessTheorem} says that the smaller the regularity $r$ of the original support hypergraph $\mathcal{H}$ or the difference $\overline m - m$ between the assumed and actual number of elements in the latent dictionary, the more columns and coefficients of the original dictionary $\mathbf{A}$ and sparse codes $\mathbf{x}_i$ are guaranteed to be contained (up to noise) in the appropriately labelled and scaled recovered dictionary $\mathbf{B}$ and codes $\mathbf{\overline x}_i$, respectively.
-
-In the important special case when $\overline m = m$, the theorem directly implies that  $Y = \{\mathbf{Ax}_1, \ldots, \mathbf{Ax}_N\}$ has a stable $k$-sparse representation in $\mathbb{R}^m$, with inequalities \eqref{def1} guaranteed in Def.~\ref{maindef} for the following worst-case error $\varepsilon$:
-\begin{align}\label{epsdel}
-\varepsilon(\delta_1, \delta_2) := \min \left\{ \frac{\delta_1}{ C_1 }, \frac{ \delta_2 L_{2k}(\mathbf{A})}{ 1 + C_1 \left( \delta_2 + \max_{i \in [N]} \|\mathbf{x}_i\|_1  \right) } \right\}.
-\end{align}
-
-Since sparse codes in general linear position are straightforward to produce with a ``Vandermonde''  construction (i.e., by choosing columns of the matrix $[\gamma_{i}^j]_{i,j=1}^{k,N}$, for distinct nonzero $\gamma_i$), we have the following direct consequence of Thm.~\ref{DeterministicUniquenessTheorem}.
-
-\begin{corollary}\label{DeterministicUniquenessCorollary}
-Given any regular hypergraph $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP, there are $N =  |\mathcal{H}| \left[ (k-1){m \choose k} + 1  \right]$ vectors \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} such that every matrix $\mathbf{A}$ satisfying spark condition \eqref{SparkCondition} generates $Y = \{\mathbf{A}\mathbf{x}_1, \ldots, \mathbf{A}\mathbf{x}_N\}$ with a stable $k$-sparse representation in $\mathbb{R}^m$ for $\varepsilon(\delta_1,\delta_2)$ given by \eqref{epsdel}.
-\end{corollary}
-
-% prev
-%\begin{corollary}\label{DeterministicUniquenessCorollary}
-%Given any regular hypergraph $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP, there are $N =  |\mathcal{H}| \left[ (k-1){m \choose k} + 1  \right]$ vectors \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} such that every matrix $\mathbf{A}$ with $L_{2\mathcal{H}}(\mathbf{A}) > 0$ generates a dataset $Y = \{\mathbf{A}\mathbf{x}_1, \ldots, \mathbf{A}\mathbf{x}_N\}$ with a stable $k$-sparse representation in $\mathbb{R}^m$ for $\varepsilon(\delta_1,\delta_2)$ as in \eqref{epsdel}.
-%\end{corollary}
-
-%We claim that the assumptions of Thm.~\ref{DeterministicUniquenessTheorem} are easily met with deterministic constructions.
-In particular, sparse codes in general linear position are straightforward to produce using a ``Vandermonde'' matrix construction (i.e.
-use the columns of the matrix $[\gamma_{i}^j]_{i,j=1}^{k,N}$, for distinct nonzero $\gamma_i$).
-%
-
-% (Prob.~\ref{InverseProblem}).
-%=======
-%An immediate practical implication of this result is that there exists a practical procedure to affirm if one's proposed solution $(\mathbf{B}, \mathbf{\overline x}_1, \ldots, \mathbf{x}_N)$ to Prob.~\ref{InverseProblem} is indeed unique (up to noise and inherent ambiguities): simply check that $\mathbf{B}$ and the $\mathbf{\overline x}_i$ satisfy the assumptions on $\mathbf{A}$ and the $\mathbf{x}_i$ in Thm.~\ref{DeterministicUniquenessTheorem}.
-%
-%%In fact, a more general result (stated clearly in the next section) can be gleaned from our method of proving Thm.~\ref{DeterministicUniquenessTheorem}.
-Briefly, in cases where $\mathbf{B}$ has $\overline m \neq m$ columns, or $\mathcal{H}$ is not regular or only partially satisfying the SIP, a relation between $\overline m$ and the degree sequence of nodes in $\mathcal{H}$ gives indices $J \subseteq [m]$ defining a submatrix $\mathbf{A}_J$ and subvectors $\mathbf{x}_i^J$ that are recoverable in the sense of \eqref{Cstable} and \eqref{b-PDa}.
-For example, if $\mathcal{H}$ is $\ell$-regular with the SIP but $m \leq \overline m < m\ell/(\ell - 1)$ then we have nonzero $|J| = \overline m - \ell(\overline m - m)$.
-The implication here is that the smaller the difference $\overline m - m$, the more columns and code entries of the original $n \times m$ dictionary $\mathbf{A}$ and codes $\mathbf{x}_i$ contained (up to noise) in the appropriately scaled $n \times \overline m$ dictionary $\mathbf{B}$ and codes $\mathbf{\overline x}_i$.
-When $\overline m = m$, we recover Thm.~\ref{DeterministicUniquenessTheorem}.
-%
-%%In fact, even if $\mathcal{H}$ is not regular or only partially satisfies the SIP, a relation between $\overline m$ and the degree sequence of nodes in $\mathcal{H}$ may give the indices $J \subseteq [m]$.
-For sake of brevity, we delay to the next section a clear statement of this more general result.
-%
-%Regarding the assumptions of Thm.~\ref{DeterministicUniquenessTheorem}, it so happens that sparse codes $\mathbf{x}_i$ in general linear position are straightforward to produce with a ``Vandermonde'' matrix construction \cite{Hillar15}, leading to the following.
-%>>>>>>> d1407a275dc391dabad7bb62d3e659f9a4ac4624
-
-% Needs to be L_{2k}(A) > 0 to guarantee sparse vector recovery
-
-%We also have the following refinement of a result in \cite{Hillar15}:
-%\begin{corollary}
-%Those square matrices $\mathbf{A}$ that satisfy \mbox{$L_{2\mathcal{H}}(\mathbf{A}) > 0$} for some regular $k$-uniform hypergraph $\mathcal{H}$ with the SIP and have the property that $\mathbf{Ax}$ is $k$-sparse for all $k$-sparse $\mathbf{x}$ with support in $\mathcal{H}$ are the matrices $\mathbf{PD}$, where $\mathbf{P}$ and $\mathbf{D}$ run over permutation and invertible diagonal matrices, respectively.
-%\end{corollary}
-
-One can easily verify that for every $k < m$ there are regular $k$-uniform hypergraphs $\mathcal{H}$ with the SIP besides the obvious $\mathcal{H} = {[m] \choose k}$.
-For instance, take $\mathcal{H}$ to be the $k$-regular set of consecutive intervals of length $k$ in some cyclic order on $[m]$.
-In this case, a direct consequence of Cor.~\ref{DeterministicUniquenessCorollary} is rigorous verification of the lower bound \mbox{$N = m(k-1){m \choose k} + m$} for sufficient sample size from the introduction.
-Special cases allow for even smaller hypergraphs.
-For example, if $k = \sqrt{m}$, then a 2-regular $k$-uniform hypergraph with the SIP can be constructed as the $2k$ rows and columns formed by arranging the elements of $[m]$ into a square grid.
-
-%\cite{li2004analysis, Georgiev05, Aharon06, Hillar15}
-We should stress here that framing the problem in terms of hypergraphs has allowed us to show, unlike in previous research on the subject, that the matrix $\mathbf{A}$ need not necessarily satisfy \eqref{SparkCondition} to be recoverable from data.
-As an example, let $\mathbf{A} = [ \mathbf{e}_1, \ldots, \mathbf{e}_5, \mathbf{v}]$ with $\mathbf{v} = \mathbf{e}_1 + \mathbf{e}_3 + \mathbf{e}_5$ and take $\mathcal{H}$ to be all consecutive pairs of indices $1, \ldots ,6$ arranged in cyclic order.
-Then for $k=2$, the matrix $\mathbf{A}$ fails to satisfy \eqref{SparkCondition} while still obeying the assumptions of Thm.~\ref{DeterministicUniquenessTheorem} for dictionary recovery.%, hence guaranteeing \eqref{Cstable} .
-%(since $\{ \mathbf{A}_1, \mathbf{A}_3, \mathbf{A}_5, \mathbf{A}_6\}$ is not a linearly independent set).
-%This weakening allows for a practical (polynomial) amount of data to still guarantee a stable dictionary in the case where the set of sparse supports for the $\mathbf{\overline x}_i$ is known to have a size that grows polynomially in $m$ and $k$.
-
-A practical implication of Thm.~\ref{DeterministicUniquenessTheorem} is the following: there is an effective procedure sufficient to affirm if a proposed solution to Prob.~\ref{InverseProblem} is indeed unique (up to noise and inherent ambiguities).
-One need simply check that the matrix and codes satisfy the (computable) assumptions of Thm.~\ref{DeterministicUniquenessTheorem} on $\mathbf{A}$ and the $\mathbf{x}_i$.
-In general, however, there is no known efficient procedure.
-We defer a brief discussion on this point to the next section.
-%Another practical implication of Thm.\ref{DeterministicUniquenessTheorem} is the following: there is an effective procedure sufficient to affirm if a proposed solution $(\mathbf{B}, \mathbf{\overline x}_1, \ldots, \mathbf{x}_N)$ to Prob.~\ref{InverseProblem} is indeed unique (up to noise and inherent ambiguities).
-One simply checks that $\mathbf{B}$ and the $\mathbf{\overline x}_i$ satisfy the respective assumptions of Thm.~\ref{DeterministicUniquenessTheorem}.
-%. on $\mathbf{A}$ and the $\mathbf{x}_i$, respectively.
-
-%In fact, a more general result (stated clearly in the next section) can be gleaned from our method of proving Thm.~\ref{DeterministicUniquenessTheorem}.
-Briefly, in cases where $\mathbf{B}$ has $\overline m \neq m$ columns, or $\mathcal{H}$ is not regular or only partially satisfying the SIP, a relation between $\overline m$ and the degree sequence of nodes in $\mathcal{H}$ gives indices $J \subseteq [m]$ defining a submatrix $\mathbf{A}_J$ and subvectors $\mathbf{x}_i^J$ that are recoverable in the sense of \eqref{Cstable} and \eqref{b-PDa}.
-For example, if $\mathcal{H}$ is $\ell$-regular with the SIP but $m \leq \overline m < m\ell/(\ell - 1)$ then we have nonzero $|J| = \overline m - \ell(\overline m - m)$.
-The implication here is that the smaller the difference $\overline m - m$, the more columns and code entries of the original $n \times m$ dictionary $\mathbf{A}$ and codes $\mathbf{x}_i$ contained (up to noise) in the appropriately scaled $n \times \overline m$ dictionary $\mathbf{B}$ and codes $\mathbf{\overline x}_i$.
-When $\overline m = m$, we recover Thm.~\ref{DeterministicUniquenessTheorem}.
-
-%In fact, even if $\mathcal{H}$ is not regular or only partially satisfies the SIP, a relation between $\overline m$ and the degree sequence of nodes in $\mathcal{H}$ may give the indices $J \subseteq [m]$.
-For sake of brevity, we delay to the next section a clear statement of this more general result.
-
-%=======
-%One can also verify that for every $k < m$, there is a regular $k$-uniform hypergraph that satisfies the SIP; for instance, take $\mathcal{H}$ to be the consecutive intervals of length $k$ in some cyclic order on $[m]$, for which Cor.~\ref{DeterministicUniquenessCorollary} implies the lower bound for sample size $N$ from the introduction.
-In many cases, however, the SIP is achievable with far fewer supports; for example, when $k = \sqrt{m}$, take $\mathcal{H}$ to be the $2k$ rows and columns formed by arranging $[m]$ in a square grid.
-%>>>>>>> d1407a275dc391dabad7bb62d3e659f9a4ac4624
-
-%As mentioned above, there exist $k$-uniform regular hypergraphs $\mathcal{H}$ with the SIP having cardinality $|\mathcal{H}| = m$,
-
-A less direct consequence of Thm.~\ref{DeterministicUniquenessTheorem} is the following uniqueness and stability guarantee for solutions to Prob.~\ref{SLCopt}.
-%, the usual optimization problem of interest for those applying dictionary learning to their data.
-
-\begin{theorem}\label{SLCopt}
-Fix a matrix $\mathbf{A}$ and vectors $\mathbf{x}_i$ satisfying the assumptions of Thm.~\ref{DeterministicUniquenessTheorem}, only now with over \mbox{$(k-1)\left[ {\overline m \choose k} + |\mathcal{H}|k{\overline m \choose k-1}\right]$} vectors supported in general linear position in each $S \in \mathcal{H}$.
-Every solution to Prob.~\ref{OptimizationProblem} (with $\eta = \varepsilon/2$) satisfies recovery guarantees \eqref{Cstable} and \eqref{b-PDa} when the corresponding bounds on $\eta$ are met.
-\end{theorem}
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=.24 \linewidth]{figs/basis.png}
-% \includegraphics[width=.25 \linewidth]{figs/Ahat_FastICA_M640_K8_noise0_2042}
-%\includegraphics[width=.24 \linewidth]{figs/Ahat_FastICA_M640_K8_noise0_4083.png}
-\includegraphics[width=.24 \linewidth]{figs/Ahat_FastICA_M640_K8_noise1_0205.png}
-\includegraphics[width=.24 \linewidth]{figs/Ahat_FastICA_M640_K8_noise2_0409.png}
-\includegraphics[width=.24 \linewidth]{figs/Ahat_FastICA_M640_K8_noise5_1021.png}
-\caption{\textbf{Learning a dictionary from increasingly noisy data}.
-The (unraveled) basis elements of the $8 \times 8$ discrete cosine transform (DCT) form the 64 columns of the left-most matrix above.
-Three increasingly imprecise dictionaries (columns reordered to best match original) are recovered by FastICA \cite{hyvarinen2000independent} trained on data generated from $8$-sparse linear combinations of DCT elements corrupted with additive noise (increasing from left to right).}
-\vspace{-.6 cm}
-\label{noisyrecovery}
-\end{center}
-\end{figure}
-
-Another extension of Thm.~\ref{DeterministicUniquenessTheorem} can be derived from the following algebraic characterization of the spark condition.
-Letting $\mathbf{A}$ be the $n \times m$ matrix of $nm$ indeterminates $A_{ij}$, the reader may work out why substituting real numbers for the $A_{ij}$ yields a matrix satisfying \eqref{SparkCondition} if and only if the following polynomial evaluates to a nonzero number:
-\begin{align*}
-f(\mathbf{A}) := \prod_{S \in {[m] \choose 2k}} \sum_{S' \in {[n] \choose 2k}} (\det \mathbf{A}_{S',S})^2,
-\end{align*}
-%
-where for any $S' \in {[n] \choose 2k}$ and $S \in {[m] \choose 2k}$, the symbol $\mathbf{A}_{S',S}$ denotes the submatrix of entries $A_{ij}$ with $(i,j) \in S' \times S$.\footnote{The large number of terms in this product is likely necessary given that deciding whether or not a matrix satisfies the spark condition is NP-hard \cite{tillmann2014computational}.}
-
-Since $f$ is analytic, having a single substitution of a real matrix $\mathbf{A}$ satisfying $f(\mathbf{A}) \neq 0$ implies that the zeroes of $f$ form a set of (Borel) measure zero.
-Such a matrix is easily constructed by adding rows of zeroes to a $\min(2k,m) \times m$ Vandermonde matrix as mentioned previously, so that every sum in the product defining $f$ above is strictly positive.
-Thus, almost every $n \times m$ matrix with $n \geq \min(2k,m)$ satisfies \eqref{SparkCondition}.
-
-%Another extension of Thm.~\ref{DeterministicUniquenessTheorem} arises from the following analytic characterization of the spark condition.
-Let $\mathbf{A}$  be the $n \times m$ matrix of $nm$ indeterminates $A_{ij}$.
-When real numbers are substituted for $A_{ij}$, the resulting matrix satisfies \eqref{SparkCondition} if and only if the following polynomial is nonzero:
-%\begin{align*}
-%f(\mathbf{A}) := \prod_{S \in {[m] \choose k}} \sum_{S' \in {[n] \choose k}} (\det \mathbf{A}_{S',S})^2,
-%\end{align*}
-%
-%where for any $S' \in {[n] \choose k}$ and $S \in {[m] \choose k}$, the symbol $\mathbf{A}_{S',S}$ denotes the submatrix of entries $A_{ij}$ with $(i,j) \in S' \times S$.
-We note that the large number of terms in this product is likely necessary due to the NP-hardness of deciding whether a given matrix $\mathbf{A}$ satisfies the spark condition \cite{tillmann2014computational}.
-
-%Since $f$ is analytic, having a single substitution of a real matrix $\mathbf{A}$ with $f(\mathbf{A}) \neq 0$ necessarily implies that the zeroes of $f$ form a set of measure zero.
-Fortunately, such a matrix $\mathbf{A}$ is easily constructed by adding rows of zeroes to any $\min(2k,m) \times m$ Vandermonde matrix as described above (so that each term in the product above for $f$ is nonzero).
-Hence, almost every $n \times m$ matrix with $n \geq \min(2k,m)$ satisfies \eqref{SparkCondition}.
-
-We claim that a similar phenomenon applies to datasets of vectors with a stable sparse representation.
-Briefly, following the same procedure as in \cite[Sec.~IV]{Hillar15}, for $k < m$ and $n \geq \min(2k, m)$, we may consider the ``symbolic'' dataset $Y = \{\mathbf{A}\mathbf{x}_1,\ldots,\mathbf{A} \mathbf{x}_N\}$ generated by an indeterminate $n \times m$ matrix $\mathbf{A}$ and $m$-dimensional $k$-sparse vectors $\mathbf{x}_1, \ldots, \mathbf{x}_N$ indeterminate within their supports, which form a regular hypergraph $\mathcal{H} \subseteq {[m] \choose k}$ satisfying the SIP.
-Restricting \mbox{$(k-1){m \choose k} + 1$} indeterminate $\mathbf{x}_i$ to each support in $\mathcal{H}$, and letting $\textbf{M}$ be the $n \times N$ matrix with columns $\mathbf{A}\mathbf{x}_i$, it can be checked that when $f(\mathbf{M}) \neq 0$ for a substitution of real numbers for the indeterminates, all of the assumptions on $\mathbf{A}$ and the $\mathbf{x}_i$ in Thm.~\ref{DeterministicUniquenessTheorem} are satisfied.
-We therefore have the following.
-% ; in particular, $\mathbf{A}$ satisfies \eqref{SparkCondition}
-
-\begin{theorem}\label{robustPolythm}
-%Let $\mathbf{A}$ and $\mathbf{x}_1, \ldots, \mathbf{x}_N$ be an indeterminate $n \times m$ matrix and sequence of $m$-dimensional vectors, respectively. 
-There is a polynomial in the entries of $\mathbf{A}$ and the $\mathbf{x}_i$ that evaluates to a nonzero number only when $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$.
-In particular, almost all substitutions impart to $Y$ this property.
-\end{theorem}
-
-%To extend this observation to arbitrary probability distributions, note that if a set of measure spaces $\{(X_{\ell}, \nu_{\ell})\}_{\ell=1}^p$ has measures $\nu_{\ell}$ absolutely continuous with respect to the standard Borel measure on $\mathbb{R}$ for all $\ell \in [p]$, then the product measure $\prod_{\ell=1}^p \nu_{\ell}$ is also absolutely continuous with respect to the standard Borel product measure on $\mathbb{R}^p$ (e.g., see \cite{folland2013real}).
-This fact combined with Thm.~\ref{robustPolythm} implies the following.
-To extend this observation to arbitrary probability distributions, note that if a set of $p$ measure spaces has all measures absolutely continuous with respect to the standard Borel measure on $\mathbb{R}$, then the product measure is also absolutely continuous with respect to the standard Borel product measure on $\mathbb{R}^p$ (e.g., see \cite{folland2013real}).
-This fact combined with Thm.~\ref{robustPolythm} implies the following.\footnote{We refer the reader to \cite{Hillar15} for a more detailed explanation of these arguments.}
-
-\begin{corollary}\label{ProbabilisticCor}
-If the indeterminate entries of $\mathbf{A}$ and the $\mathbf{x}_i$ are drawn independently from probability distributions absolutely continuous with respect to the standard Borel measure, then $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$ with probability one.
-\end{corollary}
-
-Thus, drawing the dictionary and supported sparse coefficients from any continuous probability distribution almost always generates data with a stable sparse representation.
-
-%\cite{rehnsommer2007, rozell2007neurally, ganguli2012compressed, hu2014hebbian}
-
-We close this section with some comments on the optimality of our results.
-The linear scaling for $\varepsilon$ in \eqref{epsdel} is essentially optimal (e.g., see \cite{arias2013fundamental}), but a basic open problem remains: how many samples are necessary to determine the sparse coding model?
-Our results demonstrate that sparse codes $\mathbf{x}_i$ drawn from only a polynomial number of $k$-dimensional subspaces permit stable identification of the generating dictionary $\mathbf{A}$. 
-This lends some legitimacy to the use of the model in practice, where data in general are unlikely (if ever) to exhibit the exponentially many possible $k$-wise combinations of dictionary elements required by (to our knowledge) all previously published results.
-
-Consequently, if $k$ is held fixed or if the size of the support set of reconstructing codes is polynomial in $\overline m$ and $k$, then a practical (polynomial) amount of data suffices to identify the dictionary.\footnote{In the latter case, a reexamination of the pigeonholing argument in the proof of Thm.~\ref{DeterministicUniquenessTheorem} requires a polynomial number of samples distributed over a polynomial number of supports.} Reasons to be skeptical that this holds in general, however, can be found in \cite{tillmann2014computational, Tillmann15}.
-Even so, in the next section we discuss how probabilistic guarantees can in fact be made for any number of available samples.
-
-\section{Proofs}\label{DUT} % of Theorems~\ref{DeterministicUniquenessTheorem} and ~\ref{SLCopt}}\label{DUT}
-
-%%%%%%%%%%%%%%
-% need to cut maybe: 
-%As mentioned in the previous section, Thm.~\ref{DeterministicUniquenessTheorem} is a particular case of a more general result that forgoes the assumption that $\mathcal{H} \subseteq {[m] \choose k}$ is regular and satisfies the SIP.
-If instead we require only that the stars $\cap \sigma(i)$ intersect at singletons for all $i \leq q$ (assuming that the nodes of $\mathcal{H}$ are labeled in some order of non-increasing degree), we have that $\overline m \geq k|\mathcal{H}| / \deg(1)$ and, provided $\overline m < k|\mathcal{H}| / (\deg(1) - 1)$, the nonempty submatrix $J$ is of size equal to the largest number $p$ satisfying:
-%\begin{align}\label{pcond}
-%\sum_{i=\ell}^{m} \deg(i) > (\overline m + 1 - \ell) (\deg(\ell) - 1) \ \ \text{for all } \ell \leq p \leq q.
-%\end{align}
-%Specifically, $J$ contains all nodes of degree exceeding $\deg(p)$ and some subset of those with degreee equal to $\deg(p)$.
-For the benefit of the reader, we do not prove explicitly this more general result below; it can be discerned from how exactly Lemma \ref{NonEmptyLemma} is incorporated into the proof of Lem.~\ref{MainLemma}.
-%%%%%%%%%%%%%%%%
-
-%As mentioned in the previous section, Thm.~\ref{DeterministicUniquenessTheorem} is a particular case of a more general result, which requires a looser set of constraints on the hypergraph $\mathcal{H}$ and which applies to $n \times \overline m$ matrices $\mathbf{B}$ (and $\overline m$-dimensional codes $\mathbf{\overline x}_i$) with $\overline m \neq m$:
-
-%Fix $\overline m$ and suppose the assumptions of Thm.~\ref{DeterministicUniquenessTheorem} hold, only now with the constraints on $\mathcal{H} \subseteq {[m] \choose k}$ being just that $|\cap H(i)| = 1$ for all $i \leq q$ (assuming w.l.o.g.
-that the nodes of $\mathcal{H}$ are labeled in some order of non-increasing degree), and with more than $(k-1){\overline m \choose k}$ vectors $\mathbf{x}_i$ supported in g.l.p.
-on each $S \in \mathcal{H}$.
-Then we must have $\overline m \geq k|\mathcal{H}| / \deg(1)$ and, provided $\overline m < k|\mathcal{H}| / (\deg(1) - 1)$, the guarantee \eqref{Cstable} holds for a submatrix $\mathbf{A}_J$, where $J \subseteq[m]$ is nonempty and of a size equal to the largest number $p$ satisfying:
-%\begin{align}\label{pcond}
-%\sum_{i=\ell}^{m} \deg(i) > (\overline m + 1 - \ell) (\deg(\ell) - 1) \ \ \text{for all } \ell \leq p \leq q.
-%\end{align}
-%Specifically, $J$ consists of the union of the set of all nodes of degree exceeding $\deg(p)$ and some subset of those nodes with degrees equal to $\deg(p)$.
-
-%For the benefit of the reader, we prove below the case where we forgo only the constraint that $\overline m = m$.
-This yields the implication $\overline m \geq m$ and \eqref{pcond} reduces to $|J| = \overline m - r(\overline m - m)$.
-The extension to the general result above can be seen by examining how exactly Lemma \ref{NonEmptyLemma} is incorporated into the overall proof.
-
-% ======== b - PDa =========
-
-% WITH EXPLICIT J SUBSCRIPT
-%We begin our proof of Thm.~\ref{DeterministicUniquenessTheorem} by showing how dictionary recovery \eqref{Cstable} already implies sparse code recovery \eqref{b-PDa} when $\mathbf{A}_J$ satisfies \eqref{SparkCondition} and \mbox{$\varepsilon < L_{2k}(\mathbf{A}_J) / C_1$}.
-%, assuming that $\overline m = m$ without loss of generality.
-%Consider any $2k$-sparse $\mathbf{x} \in \mathbb{R}^m$ and note that $\|\mathbf{x}\|_1 \leq \sqrt{2k}  \|\mathbf{x}\|_2$. By definition of $L_{2k}$ in \eqref{Ldef}, we have:
-%\begin{align}\label{stuff}
-%\|\mathbf{x}_J - &( \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x} )_J\|_1 \nonumber
-%\leq \frac{\|(\mathbf{BPD})_J(\mathbf{x}_J - (\mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x})_J)\|_2}{L_{2k}((\mathbf{BPD})_J)} \\ \nonumber
-%&\leq \frac{\|( (\mathbf{BPD})_J - \mathbf{A}_J) \mathbf{x}_J\|_2 + \|\mathbf{A}_J\mathbf{x}_J - \mathbf{B}_J\mathbf{\overline x}_J\|_2}{L_{2k}((\mathbf{BPD})_J)} \\
-%&\leq \frac{C_1\varepsilon \|\mathbf{x}_J\|_1 + \varepsilon}{L_{2k}((\mathbf{BPD})_J)},
-%\end{align}
-%where the term $C_1\varepsilon \|\mathbf{x}_J\|_1$ in the numerator above is a consequence of the triangle inequality applied to \eqref{Cstable}.
-
-%It remains for us to bound the denominator.  By the reverse triangle inequality:
-%\begin{align*}
-%\|(\mathbf{BPD})_J\mathbf{x}_J\|_2 
-%&\geq | \|\mathbf{A}_J\mathbf{x}_J\|_2 - \|(\mathbf{A}_J - (\mathbf{BPD})_J)\mathbf{x}_J\|_2 | \\
-%&\geq \sqrt{2k} (L_{2k}(\mathbf{A}_J) -  C_1\varepsilon) \|\mathbf{x}_J\|_2,
-%\end{align*}
-%
-%wherein removal of the absolute value is justified since $C_1\varepsilon < L_{2k}(\mathbf{A}_J)$.
-We therefore have that $L_{2k}((\mathbf{BPD})_J) \geq L_{2k}(\mathbf{A}_J) - C_1\varepsilon  > 0$, and \eqref{b-PDa} then follows from \eqref{stuff}.
-
-% WITHOUT J SUBSCRIPT
-We begin our proof of Thm.~\ref{DeterministicUniquenessTheorem} by showing how dictionary recovery \eqref{Cstable} already implies sparse code recovery \eqref{b-PDa} when $\mathbf{A}$ satisfies \eqref{SparkCondition} and \mbox{$\varepsilon < L_{2k}(\mathbf{A}) / C_1$}.
-We temporarily assume (without loss of generality) that $\overline m = m$, so as to omit an otherwise requisite subscript $(\cdot)_J$ around certain matrices and vectors.
-By definition of $L_{2k}$ in \eqref{Ldef}, and noting that $\sqrt{k} \|\mathbf{v}\|_2 \geq \|\mathbf{v}\|_1$ for $k$-sparse $\mathbf{v}$, we have for all $i \in [N[$:
-\begin{align}\label{stuff}
-\|\mathbf{x}_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_i \|_1 \nonumber
-&\leq \frac{\|\mathbf{BPD}(\mathbf{x}_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_i)\|_2}{L_{2k}(\mathbf{BPD})} \\ \nonumber
-&\leq \frac{\|( \mathbf{BPD} - \mathbf{A}) \mathbf{x}_i\|_2 + \|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline x}_i\|_2}{L_{2k}(\mathbf{BPD})} \\
-&\leq \frac{C_1\varepsilon \|\mathbf{x}_i\|_1 + \varepsilon}{L_{2k}(\mathbf{BPD})},
-\end{align}
-%\begin{align}\label{stuff}
-%\frac{ \|\mathbf{x} - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x} \|_1 } { \|\mathbf{D}^{-1}\|_1 }  \
-%&\leq \|\mathbf{Dx} - \mathbf{P}^{\top}\mathbf{\overline x} \|_1 \\ \nonumber
-%&\leq \frac{\|\mathbf{BP}(\mathbf{D}\mathbf{x} - \mathbf{P}^{\top}\mathbf{\overline x})\|_2}{L_{2k}(\mathbf{BP})} \\ \nonumber
-%&\leq \frac{\|( \mathbf{BPD} - \mathbf{A}) \mathbf{x}\|_2 + \|\mathbf{A}\mathbf{x} - \mathbf{B}\mathbf{\overline x}\|_2}{L_{2k}(\mathbf{BP})} \\
-%&\leq \frac{C_1\varepsilon \|\mathbf{x}\|_1 + \varepsilon}{L_{2k}(\mathbf{BP})},
-%\end{align}
-where the first term in the numerator above follows from the triangle inequality and \eqref{Cstable}.
-
-It remains for us to bound the denominator. For any $2k$-sparse $\mathbf{x}$, we have by the triangle inequality:
-\begin{align*}
-\|\mathbf{BPD}\mathbf{x}\|_2 
-&\geq \|\mathbf{A}\mathbf{x}\|_2 - \|(\mathbf{A} - \mathbf{BPD})\mathbf{x}\|_2 \\
-&\geq \sqrt{2k} (L_{2k}(\mathbf{A}) -  C_1\varepsilon) \|\mathbf{x}\|_2,
-\end{align*}
-
-%\begin{align*}
-%\|\mathbf{BP}\mathbf{x}\|_2 
-%&\geq \|\mathbf{A}\mathbf{D}^{-1}\mathbf{x}\|_2 - \|(\mathbf{A} - \mathbf{BPD})\mathbf{D}^{-1}\mathbf{x}\|_2 \\
-%&\geq \sqrt{2k} (L_{2k}(\mathbf{A}) -  C_1\varepsilon) \|\mathbf{D}^{-1}\mathbf{x}\|_2, \\ 
-%&\geq \sqrt{2k} (L_{2k}(\mathbf{A}) -  C_1\varepsilon) \|\mathbf{D}^{-1}\|_{?} \| \mathbf{x}\|_2,
-%\end{align*}
-%
-We therefore have that $L_{2k}(\mathbf{BPD}) \geq L_{2k}(\mathbf{A}) - C_1\varepsilon  > 0$, and \eqref{b-PDa} then follows from \eqref{stuff}.
-The reader may also verify that $L_{2k}(\mathbf{BP}) \geq L_{2k}(\mathbf{BPD}) / \|\mathbf{D}\|_1$.
-
-The heart of the matter is therefore \eqref{Cstable}, which we now establish beginning with the important special case of $k = 1$.
-
-\begin{proof}[Proof of Thm.~\ref{DeterministicUniquenessCorollary} for $k=1$]
-Since the only 1-uniform hypergraph with the SIP is $[m]$, which is obviously regular, we require only $\mathbf{x}_i = c_i \mathbf{e}_i$ for $i \in [m]$, with $c_i \neq 0$ to guarantee  linear independence.
-While we have yet to define $C_1$ generally, in this case we may set $C_1 = 1/ \min_{\ell \in [m]} |c_{\ell}|$ so that $\varepsilon < L_2(\mathbf{A})  \min_{\ell \in [m]} |c_{\ell}|$.
-
-Fix $\mathbf{A} \in \mathbb{R}^{n \times m}$ satisfying $L_2(\mathbf{A}) > 0$, since here we have $2\mathcal{H} = {[m] \choose 2}$, and suppose some $\mathbf{B}$ and $1$-sparse $\mathbf{\overline x}_i \in \mathbb{R}^{\overline m}$ have  $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \varepsilon < L_2(\mathbf{A}) / C_1$ for all $i$.
-Then, there exist $\overline{c}_1, \ldots, \overline{c}_m \in \mathbb{R}$ and a map $\pi: [m] \to [\overline m]$ such that:
-\begin{align}\label{1D}
-\|c_i\mathbf{A}_i - \overline{c}_i\mathbf{B}_{\pi(i)}\|_2 \leq \varepsilon,\ \ \text{for $i \in [m]$}.
-\end{align} 
-Note that $\overline{c}_i \neq 0$, since otherwise we would reach the following contradiction: $\|\mathbf{A}_i \|_2 \leq C_1 |c_i| \|\mathbf{A}_i \|_2  \leq C_1\varepsilon < L_2(\mathbf{A}) \leq L_1(\mathbf{A}) = \min_{i \in [m]} \|\mathbf{A}_{i}\|_2$.
-%implies by \eqref{delrho} the contradiction $|c_i| < \min_{\ell \in [m]} | c_\ell |$.
-
-We now show that $\pi$ is injective (in particular, a permutation if $\overline m = m$).
-Suppose that $\pi(i) = \pi(j) = \ell$ for some $i \neq j$ and $\ell$.
-Then, $\|c_{i}\mathbf{A}_{i} - \overline{c}_{i} \mathbf{B}_{\ell}\|_2  \leq \varepsilon$ and $\|c_{j}\mathbf{A}_{j} - \overline{c}_{j}\mathbf{B}_{\ell}\|_2 \leq \varepsilon$, and we have: %Scaling and summing these inequalities by $|\overline{c}_{i}|$ and $|\overline{c}_{j}|$, respectively, and applying the triangle inequality to annihilate the terms in $\mathbf{B}_\ell$, we obtain:
-\begin{align*}
-(|\overline{c}_{i}| + |\overline{c}_{j}|) \varepsilon
-&\geq |\overline{c}_{i}| \|c_{j}\mathbf{A}_{j} - \overline{c}_{j}\mathbf{B}_{\ell}\|_2  + |\overline{c}_{j}| \|c_{i}\mathbf{A}_{i} - \overline{c}_{i} \mathbf{B}_{\ell}\|_2 \nonumber \\
-&\geq \|\mathbf{A}(\overline{c}_{i}c_{j} \mathbf{e}_{j} - \overline{c}_{j}c_{i}\mathbf{e}_{i})\|_2 \nonumber \\ 
-&\geq \sqrt{2}  L_2(\mathbf{A}) \|\overline{c}_{i}c_{j} \mathbf{e}_{j} - \overline{c}_{j}c_{i}\mathbf{e}_{i}\|_2 \nonumber \\
-&\geq  L_2(\mathbf{A}) \left( |\overline{c}_{i}| + |\overline{c}_{j}| \right) \min_{\ell \in [m]} |c_\ell |,
-\end{align*}
-contradicting our assumed upper bound on $\varepsilon$. Hence, the map $\pi$ is injective and so $\overline m \geq m$. %Setting $\overline J = \pi([m])$ and
-
-Letting $\mathbf{P}$ and $\mathbf{D}$ be the $\overline m \times \overline m$ permutation and invertible diagonal matrices with, respectively, columns $\mathbf{e}_{\pi(i)}$ and $\frac{\overline{c}_i}{c_i}\mathbf{e}_i$ for $i \in [m]$ (otherwise, $\mathbf{e}_{i}$ for $i \in [\overline{m}] \setminus [m]$), we may rewrite \eqref{1D} to see that for all $i \in [m]$:
-\begin{align*}
-\|\mathbf{A}_i - (\mathbf{BPD})_i\|_2 
-= \|\mathbf{A}_i - \frac{\overline{c}_i}{c_i}\mathbf{B}_{\pi(i)}\|_2 
-\leq \frac{\varepsilon}{|c_i|} 
-\leq C_1\varepsilon.
-\end{align*}
-%\vspace{-.2 cm}
-\end{proof}
-
-An extension of the proof to the general case $k < m$ requires some additional tools to derive the general expression \eqref{Cdef1} for $C_1$.
-These include a generalized notion of distance (Def.~\ref{dDef}) and angle (Def.~\ref{FriedrichsDefinition}) between subspaces as well as a stability result in combinatorial matrix analysis (Lem.~\ref{MainLemma}).
-
-\begin{definition}\label{dDef}
-For $\mathbf{u} \in \mathbb R^m$ and vector spaces $U,V \subseteq \mathbb{R}^m$, let $\text{\rm dist}(\mathbf{u}, V) := \min \{\| \mathbf{u}-\mathbf{v} \|_2: \mathbf{v} \in V\}$ and define:
-\begin{align}
-d(U,V) := \max_{\mathbf{u} \in U, \ \|\mathbf{u}\|_2 \leq 1} \text{\rm dist}(\mathbf{u},V).
-\end{align}
-\end{definition}
-
-We note the following facts about $d$. Clearly, 
-\begin{align}\label{UsubU}
-U' \subseteq U \implies d(U',V) \leq d(U,V).
-\end{align}
-From \cite[Ch.~4 Cor.~2.6]{Kato2013}, we also have: %Kato p.223
-\begin{align}\label{dimLem}
-d(U,V) < 1 \implies \dim(U) \leq \dim(V),
-\end{align}
-and from \cite[Lem.~3.2]{Morris10}:
-\begin{align}\label{eqdim}
-\dim(U) = \dim(V) \implies d(U,V) = d(V,U).
-\end{align}
-
-The following is our result in combinatorial matrix analysis; it contains most of the complexity in the proof of Thm.~\ref{DeterministicUniquenessTheorem}.
-
-\begin{lemma}\label{MainLemma}
-If an $n \times m$ matrix $\mathbf{A}$ has $L_{2\mathcal{H}}(\mathbf{A}) > 0$ for some $r$-regular $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP, then the following holds for $C_2 > 0$ given by \eqref{Cdef2}:
-
-Fix $\varepsilon < L_2(\mathbf{A}) / C_2$. If for some $n \times \overline m$ matrix $\mathbf{B}$ and map $\pi: \mathcal{H} \mapsto {[\overline m] \choose k}$,
-\begin{align}\label{GapUpperBound}
-d(\bm{\mathcal{A}}_S, \bm{\mathcal{B}}_{\pi(S)}) \leq \varepsilon, \ \  \text{for $S \in \mathcal{H}$},
-\end{align}
-then $\overline m \geq m$, and provided $\overline m (r-1) < mr$, there is a permutation matrix $\mathbf{P}$ and invertible diagonal $\mathbf{D}$ such that:
-\begin{align}\label{MainLemmaBPD}
-\|\mathbf{A}_i - (\mathbf{B}\mathbf{PD})_i\|_2 \leq C_2 \varepsilon, \ \  \text{for } i \in J,
-\end{align}
-for some $J \subseteq [m]$ of size \mbox{$m - (r-1)(\overline m - m)$}.
-\end{lemma}
-
-%\begin{lemma}\label{MainLemma}
-%Fix $\mathbf{A} \in \mathbb{R}^{n \times m}$ with $L_\mathcal{H}(\mathbf{A}) > 0$ for some regular $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP.
-There exists a constant $C_2 > 0$ for which the following holds for all $\varepsilon < L_2(\mathbf{A}) / C_2$:
-
-%If a matrix $\mathbf{B} \in \mathbb{R}^{n \times m}$ and map $\pi: E \mapsto {m \choose k}$ satisfy:
-%\begin{align}\label{GapUpperBound}
-%d(\text{\rm span}\{\mathbf{A}_{S}\}, \bm{\mathcal{B}}_{\pi(S)}) \leq \varepsilon, \ \ \text{for $S \in \mathcal{H}$},
-%\end{align}
-%then there exist a permutation matrix $\mathbf{P}$ and invertible diagonal matrix $\mathbf{D}$ such that:
-%\begin{align}\label{MainLemmaBPD}
-%\|\mathbf{A}_j - \mathbf{BPD}_j\|_2 \leq C_2 \varepsilon, \ \  \text{for } j \in [m],
-%\end{align}
-%\end{lemma}
-
-We present the constant $C_2$ (a function of $\mathbf{A}$ and $\mathcal{H}$) relative to a quantity used in \cite{Deutsch12} to analyze the convergence of the ``alternating projections" algorithm for projecting a point onto the intersection of subspaces.
-We incorporate this quantity into the following definition, which we refer to in our proof of Lem.~\ref{DistanceToIntersectionLemma} in the Appendix; specifically, we use it to bound the distance between a point and the intersection of subspaces given an upper bound on its distance from each subspace.
-
-\begin{definition}\label{FriedrichsDefinition}
-For a collection of real subspaces $\mathcal{V} = \{V_i\}_{i=1}^\ell$, define $\xi(\mathcal{V}) := 0$ when $|\mathcal{V}| = 1$, and otherwise:
-\begin{align}\label{xi}
-\xi^2(\mathcal{V}) := 1 -  \max \prod_{i=1}^{\ell-1} \sin^2  \theta \left(V_i, \cap_{j>i} V_j \right) ,
-\end{align} 
-%
-where the maximum is taken over all ways of ordering 
-%\footnote{We modify the quantity in \cite{Deutsch12} in this way since the subspace ordering is irrelevant to our purpose.} 
-the $V_i$ and the angle $\theta \in (0,\frac{\pi}{2}]$ is defined implicitly as \cite[Def.~9.4]{Deutsch12}:
-\begin{align*}
-\cos{\theta(U,W)} := \max\left\{ |\langle \mathbf{u}, \mathbf{w} \rangle|: \substack{ \mathbf{u} \in U \cap (U \cap W)^\perp, \ \|\mathbf{u}\|_2 \leq 1 \\ \mathbf{w} \in W \cap (U \cap W)^\perp, \  \|\mathbf{w}\|_2 \leq 1 } \right\}.
-\end{align*}
-\end{definition}
-Note that $\theta \in (0,\frac{\pi}{2}]$ implies $0 \leq \xi < 1$, and that $\xi(\mathcal{V}') \leq \xi(\mathcal{V})$ when $\mathcal{V}' \subseteq \mathcal{V}$.\footnote{We acknowledge the counter-intuitive property: $\theta =  \pi/2$ when $U \subseteq W$.}
-
-The constant $C_2 > 0$ of Lem.~\ref{MainLemma} can now be expressed as:  
-\begin{align}\label{Cdef2}
-	C_2(\mathbf{A}, \mathcal{H}) := \frac{ (r+1) \max_{j \in [m]} \|\mathbf{A}_j\|_2}{ 1- \max_{\mathcal{G} \in {\mathcal{H} \choose r+1}} \xi( \bm{\mathcal{A}}_\mathcal{G} ) }.
-\end{align}
-
-We next define the constant $C_1 > 0$ of Thm.~\ref{DeterministicUniquenessTheorem} in terms of $C_2$.
-Given vectors $\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$, let $\mathbf{X}$ denote the $m \times N$ matrix with columns $\mathbf{x}_i$ and let $I(S)$ denote the set of indices $i$ for which $\mathbf{x}_i$ is supported in $S$.
-We define:
-\begin{align}\label{Cdef1}
-C_1(\mathbf{A}, \mathcal{H}, \{\mathbf{x}_i\}_{i=1}^N) := \frac{ C_2(\mathbf{A}, \mathcal{H}) } { \min_{S \in \mathcal{H}} L_k(\mathbf{AX}_{I(S)}) }.
-\end{align}
-Given the assumptions of Thm.~\ref{DeterministicUniquenessTheorem} on $\mathbf{A}$ and the $\mathbf{x}_i$, this expression for $C_1$ is well-defined\footnote{\label{note1}To see this, fix $S \in \mathcal{H}$ and $k$-sparse $\mathbf{c}$.
-Using the definitions, we have $\|\mathbf{AX}_{I(S)}\mathbf{c}\|_2 \geq \sqrt{k} L_\mathcal{H}(\mathbf{A})\|\mathbf{X}_{I(S)}\mathbf{c}\|_2 \geq k L_\mathcal{H}(\mathbf{A}) L_k(\mathbf{X}_{I(S)})\|\mathbf{c}\|_2$.
-Thus, $L_k(\mathbf{AX}_{I(S)}) \geq \sqrt{k} L_\mathcal{H}(\mathbf{A}) L_k(\mathbf{X}_{I(S)}) > 0$, since $L_{\mathcal{H}}(\mathbf{A}) \geq L_{2\mathcal{H}}(\mathbf{A})> 0$ and $L_k(\mathbf{X}_{I(S)}) > 0$ by general linear position of the $\mathbf{x}_i$.} and yields an upper bound on $\varepsilon$ consistent with that proven sufficient in the case $k=1$ considered at the beginning of this section.\footnote{When $\mathbf{x}_i = c_i\mathbf{e}_i$, we have $C_2 \geq 2\|\mathbf{A}_i\|_2$ and the denominator in \eqref{Cdef1} becomes $\min_{i \in [m]} |c_i| \|\mathbf{A}_i\|_2$; hence, $C_1 \geq 2 / \min_{i \in [m]} |c_i|$.}
-% C_2(\mathbf{A}, \mathcal{H}) := \frac{ (r+1) \max_{j \in [m]} \|\mathbf{A}_j\|_2}{ \min_{\mathcal{G} \in {\mathcal{H} \choose r} \cup {\mathcal{H} \choose r+1}} \xi( \{ \bm{\mathcal{A}}_S \}
-
-The practically-minded reader should note that the explicit constants $C_1$ and $C_2$ are effectively computable: the quantity $L_k$ may be calculated as the smallest singular value of a certain matrix, while the quantity $\xi$ involves computing ``canonical angles'' between subspaces, which reduces again to an efficient singular value decomposition.
-There is no known fast computation of $L_k$ in general, however, since even $L_{k} > 0$ is NP-hard \cite{tillmann2014computational}, although 
-efficiently computable bounds have been proposed (e.g., via the ``mutual coherence" of a matrix \cite{donoho2003optimally}); alternatively, 
-fixing $k$ yields polynomial complexity.
-Moreover, calculating $C_2$ requires an exponential number of queries to $\xi$ unless $r$ is held fixed, too (e.g., the ``cyclic order'' hypergraphs described above have $r=k$).
-Thus, as presented, $C_1$ and $C_2$ are not efficiently computable in general.
-% , but efficient subcases do exist and may be of practical relevance.
-
-\begin{proof}[Proof of Thm.~\ref{DeterministicUniquenessCorollary} for $k < m$] 
-We find a map $\pi: \mathcal{H} \to {[m] \choose k}$ for which the distance $d(\bm{\mathcal{A}}_S, \bm{\mathcal{B}}_{\pi(S)})$ is controlled by $\varepsilon$ for all $S \in \mathcal{H}$.
-Applying Lem.~\ref{MainLemma} then completes the proof.
-%We shall show that for every $S \in \mathcal{H}$ there is some $\overline S \in {[\overline m] \choose k}$ for which the distance $d(\bm{\mathcal{A}}_S, \bm{\mathcal{B}}_{\overline S})$ is controlled by $\varepsilon$.
-Applying Lem.~\ref{MainLemma} with the map $\pi$ defined by $S \mapsto \overline S$ then completes the proof.
-
-Fix $S \in \mathcal{H}$.
-Since there are more than $(k-1){\overline m \choose k}$ vectors $\mathbf{x}_i$ supported in $S$, by the pigeonhole principle there must be some $\overline S \in {[\overline m] \choose k}$ and a set of $k$ indices $K \subseteq I(S)$ for which all $\mathbf{\overline x}_i$ with $i \in K$ are supported in $\overline S$.
-It also follows\footnotemark[\ref{note1}] from $L_{2\mathcal{H}}(\mathbf{A}) > 0$ and the general linear position of the $\mathbf{x}_i$ that $L_k(\mathbf{AX}_{K}) > 0$; that is, the columns of the $n \times k$ matrix $\mathbf{AX}_K$ form a basis for $\bm{\mathcal{A}}_S$.
-
-Fixing $\mathbf{y} \in \bm{\mathcal{A}}_S \setminus \{\mathbf{0}\}$, there then exists $\mathbf{c} = (c_1, \ldots, c_k) \in \mathbb{R}^k \setminus \{\mathbf{0}\}$ such that $\mathbf{y} = \mathbf{AX}_K\mathbf{c}$.
-Setting \mbox{$\mathbf{\overline{y}} = \mathbf{B\overline{X}}_K\mathbf{c}$, which is in $\bm{\mathcal{B}}_{\overline S}$}, we have by triangle inequality:
-\begin{align*}
-\|\mathbf{y} - \mathbf{\overline{y}}\|_2 
-%&= \|\sum_{i=1}^k c_i(\mathbf{AX}_K - \mathbf{B\overline{X}}_K)_i\|_2
-&= \|(\mathbf{AX}_K - \mathbf{B\overline{X}}_K)\mathbf{c}\|_2
-%\leq \varepsilon \sum_{i=1}^k |c_i| \\
-\leq \varepsilon \|\mathbf{c}\|_1
-\leq \varepsilon \sqrt{k}  \|\mathbf{c}\|_2  \\
-&\leq \frac{\varepsilon}{L_k(\mathbf{AX}_K)} \|\mathbf{y}\|_2,
-\end{align*}
-where the last inequality uses \eqref{Ldef}. From Def.~\ref{dDef}:
-\begin{align}\label{rhs222}
-d(\bm{\mathcal{A}}_S, \bm{\mathcal{B}}_{\overline S}) 
-\leq \frac{\varepsilon}{  L_k(\mathbf{AX}_{K}) } 
-\leq \frac{\varepsilon}{  L_k(\mathbf{AX}_{I(S)}) } 
-\leq \varepsilon \frac{C_1}{C_2}.
-\end{align}
-%
-Finally, apply Lem.~\ref{MainLemma} with $\varepsilon < L_2(\mathbf{A})/C_1$ and $\pi(S) := \overline S$. % L_2(A) > 0 by def of L, since L_2H(A) > 0 and H covers [m]
-\end{proof}
-
-Before moving on to the proof of Thm.~\ref{SLCopt}, we briefly revisit our discussion on sample complexity from the end of the previous section.
-While an exponential number of samples may very well prove to be necessary in the deterministic or almost-certain case, our proof of Thm.~\ref{DeterministicUniquenessTheorem} can be extended to hold with some probability for \emph{any} number of samples by alternative appeal to a probabilistic pigeonholing at the point early in the proof where the (deterministic) pigeonhole principle is applied to show that for every $S \in \mathcal{H}$, there exist $k$ vectors $\mathbf{x}_i$ supported on $S$ whose corresponding $\mathbf{\overline x}_i$ all share the same support.\footnote{A famous example of such an argument is the counter-intuitive ``birthday paradox", which demonstrates that the probability of two people having the same birthday in a room of twenty-three is greater than 50\%.}
-Given insufficient samples, this argument has some less-than-certain probability of being valid for each $S \in \mathcal{H}$.
-Nonetheless, simulations with small hypergraphs confirm that the probability of success very quickly approaches one once the number of samples $N$ surpasses a small fraction of the deterministic sample complexity.
-
-\begin{proof}[Proof of Thm.~\ref{SLCopt}]
-We bound the number of $k$-sparse $\mathbf{\overline x}_i$ from below and then apply Thm.~\ref{DeterministicUniquenessCorollary}. 
-%We now apply this fact to bound the number of $k$-sparse $\mathbf{\overline x}_i$. 
-Let $n_p$ be the number of $\mathbf{\overline x}_i$ with $\|\mathbf{\overline x}_i\|_0 = p$.
-Since the $\mathbf{x}_i$ are all $k$-sparse, by \eqref{minsum} we have:
-\begin{align*}
-%\mbox{$k \sum_{p = 0}^{\overline m} n_p \geq \sum_{i=0}^N \|\mathbf{x}_i\|_0 \geq \sum_{i=0}^N \|\mathbf{\overline x}_i\|_0 = \sum_{p=0}^{\overline m} p n_p.$}
-\sum_{p=0}^{\overline m} p n_p =  \sum_{i=0}^N \|\mathbf{\overline x}_i\|_0
-\leq \sum_{i=0}^N \|\mathbf{x}_i\|_0 
-\leq kN
-\end{align*}
-Since $N = \sum_{p = 0}^{\overline m} n_p$, we then have $\sum_{p = 0}^{\overline m} (p-k) n_p \leq 0$. Splitting the sum yields:
-\begin{align}\label{eqn}
-\sum_{p = k+1}^{\overline m} n_p \leq \sum_{p = k+1}^{\overline m} (p-k) n_p \leq \sum_{p = 0}^k (k-p)n_p \leq k \sum_{p = 0}^{k-1} n_p,
-\end{align}
-%
-demonstrating that the number of vectors $\mathbf{\overline x}_i$ that are \emph{not} $k$-sparse is bounded above by how many are $(k-1)$-sparse.
-
-Next, observe that no more than $(k-1)|\mathcal{H}|$ of the $\mathbf{\overline x}_i$ share a support $\overline S$ of size less than $k$.
-Otherwise, by the pigeonhole principle, there is some $S \in \mathcal{H}$ and a set of $k$ indices $K \subseteq I(S)$ for which all $\mathbf{x}_i$ with $i \in K$ are supported in $S$; as argued previously, \eqref{rhs222} follows.
-It is simple to show that $L_2(\mathbf{A}) \leq \max_j\|\mathbf{A}_j\|_2$, and since $0 \leq \xi < 1$, the right-hand side of \eqref{rhs222} is less than one for $\varepsilon < L_2(\mathbf{A})/C_1$.
-Thus, by \eqref{dimLem} we would have the contradiction $k = \dim(\bm{\mathcal{A}}_S) \leq \dim(\bm{\mathcal{B}}_{\overline S}) \leq |\overline S| < k.$
-
-The total number of $(k-1)$-sparse vectors $\mathbf{\overline x}_i$ thus cannot exceed $|\mathcal{H}|(k-1){ \overline m \choose k-1}$.
-By \eqref{eqn}, no more than $|\mathcal{H}|k(k-1){ \overline m \choose k-1}$ vectors $\mathbf{\overline x}_i$ are not $k$-sparse.
-Since for every $S \in \mathcal{H}$ there are over $(k-1)\left[ {\overline m \choose k} + |\mathcal{H}|k{ \overline m \choose k-1} \right]$ vectors $\mathbf{x}_i$ supported there, it must be that more than $(k-1){\overline m \choose k}$ of them have corresponding $\mathbf{\overline x}_i$ that are $k$-sparse.
-The result now follows from Thm.~\ref{DeterministicUniquenessCorollary}, noting by the triangle inequality that $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline x}_i\| \leq 2\eta$ for $i = 1, \ldots, N$.
-\end{proof}
-
-%\begin{proof}[Proof (sketch) of Thm.~\ref{robustPolythm}]
-%Let $\textbf{M}$ be the matrix with columns $\mathbf{A}\mathbf{x}_i$, $i \in [N]$.
-Consider the polynomial $\prod_{S \in {[N] \choose 2k}} \sum_{S' \in {[n] \choose 2k}} (\det \textbf{M}_{S',S})^2$ in the indeterminate entries of $\mathbf{A}$ and $\mathbf{x}_i$, with notation as in Sec.~\ref{Results}.
-%It can be checked that when this polynomial is nonzero for a substitution of real numbers for the indeterminates, all of the genericity requirements on $\mathbf{A}$ and $\mathbf{x}_i$ in our proofs of stability in Thm.~\ref{DeterministicUniquenessTheorem} are satisfied (in particular, the spark condition \eqref{SparkCondition} on $\mathbf{A}$).
-%\end{proof}
-
-%\begin{proof}[Proof (sketch) of Cor.~\ref{ProbabilisticCor}]
-%First, note that if a set of measure spaces $\{(X_{\ell}, \Sigma_{\ell}, \nu_{\ell})\}_{\ell=1}^p$ has that $\nu_{\ell}$ is absolutely continuous with respect to $\mu$ for all $\ell \in [p]$, where $\mu$ is the standard Borel measure on $\mathbb{R}$, then the product measure $\prod_{\ell=1}^p \nu_{\ell}$ is absolutely continuous with respect to the standard Borel product measure on $\mathbb{R}^p$.
-% for space:  (e.g.,  \cite{folland2013real}).
-%By Thm.~\ref{robustPolythm}, there is a polynomial that is nonzero when $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$; in particular, stability holds almost surely.
-%\end{proof}
-
-\section{Discussion}\label{Discussion}
-
-A main motivation for this work is the emergence of seemingly unique representations from sparse coding models trained on natural data, despite the varied assumptions underlying the many algorithms in current use.
-Our results constitute an important step toward explaining these phenomena as well as unifying many publications on the topic by deriving general deterministic conditions under which identification of parameters in this model is not only possible but also robust to uncertainty in measurement and model choice.
-
-We have shown that, given sufficient data, the problem of determining a dictionary and sparse codes with minimal support size (Prob.~\ref{OptimizationProblem}) reduces to an instance of Prob.~\ref{InverseProblem}, to which our main result (Thm.~\ref{DeterministicUniquenessTheorem}) applies: every dictionary and sequence of sparse codes consistent with the data are equivalent up to inherent relabeling/scaling ambiguities and a discrepancy (error) that scales linearly with the measurement noise or modeling inaccuracy.
-The constants we provide are explicit and computable; as such, there is an effective procedure that sufficiently affirms if a proposed solution to these problems is indeed unique up to noise and inherent ambiguities, although it is not efficient in general.
-
-%A compelling feature of this model is its simple instantiation of the principle of Occam's razor: a natural video, for instance, is modeled as a linear combination of a small number of spatiotemporal building blocks, each representing an archetypical feature latent in the data.
-
-%For theoretical neuroscience in particular, dictionary learning and related methods have recovered characteristic components of natural images \cite{Olshausen96, hurri1996image, bell1997independent, van1998independent} and sounds \cite{bellsejnowski1996, smithlewicki2006} that reproduce response properties of certain cortical neurons.
-
-%to the recovery of ``mouse neuronal activity representing location on a track \cite{agarwal2014spatially}
-
-%Moreover, we show that even if the meta-parameter for the number of dictionary elements is overestimated, a subset of parameters may still be identifiable up to noise.
-
-Beyond an extension of existing noiseless guarantees \cite{Hillar15} to the noisy regime and their novel application to Prob.~\ref{OptimizationProblem}, our work contains a theory of combinatorial designs for support sets key to identification of dictionaries.
-We incorporate this idea into a fundamental lemma in matrix theory (Lem.~\ref{MainLemma}) that draws upon the definition of a matrix lower bound (\ref{Ldef}) induced by a hypergraph.
-The new insight offered by this combinatorial approach allows for guaranteed recovery of some or all dictionary elements even if: 1) dictionary size is overestimated, 2) data cover only a polynomial number of distinct sparse supports, and 3) dictionaries do not satisfy the spark condition.
-
-The absence of any assumptions about dictionaries solving Prob.~\ref{InverseProblem} was a major technical obstruction in proving Thm.~\ref{DeterministicUniquenessTheorem}.
-We sought such a general guarantee because of the practical difficulty in ensuring that an algorithm maintain a dictionary satisfying the spark condition \eqref{SparkCondition} at each iteration, an implicit requirement of all previous works except \cite{Hillar15}; indeed, even certifying a dictionary has this property is NP-hard \cite{tillmann2014computational}.
-
-One direct application of this work is to theoretical neuroscience, wherein our theorems justify the mathematical soundness of one of the few hypothesized theories of bottleneck communication in the brain \cite{Isely10}: that sparse neural population activity is recoverable from its noisy linear compression through a randomly constructed (but unknown) wiring bottleneck by any biologically plausible unsupervised sparse coding method that solves Prob.~\ref{DeterministicUniquenessTheorem} or \ref{SLCopt} (e.g., \cite{rehnsommer2007, rozell2007neurally, pehlevan2015normative}).\footnote{We refer the reader to \cite{ganguli2012compressed} for more on interactions between dictionary learning and neuroscience.}
-
-In fact, uniqueness guarantees with minimal assumptions apply to all areas of data science and engineering that utilize learned sparse structure.
-For example, several groups have applied compressed sensing to signal processing tasks; for instance, in MRI analysis \cite{lustig2008compressed}, image compression \cite{Duarte08}, and even the design of an ultrafast camera \cite{Gao14}.
-It is only a matter of time before these systems incorporate dictionary learning to encode and decode signals (e.g., in a device that learns structure from motion \cite{kong2016prior}), just as scientists have used sparse coding to make sense of their data \cite{jung2001imaging, agarwal2014spatially, lee2016sparse, wu2016stability}.
-
-Assurances offered by our theorems certify that different devices and algorithms learn equivalent representations given enough data from statistically identical systems.\footnote{To contrast with the current hot topic of ``Deep Learning'', there are few such uniqueness guarantees for these models of data; moreover, even small noise can dramatically alter their output \cite{goodfellow2014explaining}.}
-Indeed, a main reason for the sustained interest in dictionary learning as an unsupervised method for data analysis seems to be the assumed well-posedness of parameter identification in the model, confirmation of which forms the core of our findings.
-
-We close with some challenges left open by our work.
-All conditions stated here guaranteeing the uniqueness and stability of sparse representations have only been shown sufficient; it remains open, therefore, to extend them to necessary conditions, be they on required sample size, the structure of support set hypergraphs, or tolerable error bounds.
-On this last note, we remark that our deterministic treatment considers always the ``worst-case" noise, whereas the ``effective" noise sampled from a concentrated distribution might be significantly reduced, especially for high-dimensional data.
-It would be of great practical benefit to see how drastically all conditions can be relaxed by requiring only probabilistic guarantees in this way, or in the spirit of our discussion on probabilistic pigeonholing to reduce sample complexity (as in the famous ``birthday paradox") following the proof of Thm.~\ref{DeterministicUniquenessTheorem}.
-
-Another interesting question raised by our work is for which special cases is it efficient to check that a solution to Prob.~\ref{InverseProblem} or \ref{OptimizationProblem} is unique up to noise and inherent ambiguities.
-Considering that the sufficient conditions we have described for checking this in general are NP-hard to compute, are the necessary conditions hard?
-Are Probs.~\ref{InverseProblem} and \ref{OptimizationProblem} then also hard (e.g., see \cite{Tillmann15})?
-Finally, since Prob.~\ref{SLCopt} is intractable in general, but efficiently solvable by $\ell_1$-norm minimization when the matrix is known (and has a large enough lower bound over sparse domains \cite{eldar2012compressed}), is there a version of Thm.~\ref{SLCopt} certifying when Prob.~\ref{OptimizationProblem} can be solved efficiently in full by similar means?
-% [*** Incorporate this open problem with more words ***]
-
-We hope these remaining challenges pique the interest of the community to pick up where we have left off and that the theoretical tools showcased here may be of use to this end.
-
-%We close with some challenges left open by our work.
-First, there is the basic problem of proving optimal lower bounds on sufficient sample size $N$ guaranteeing the uniqueness and stability of sparse representations.
-The pigeonholing argument in the proof of Thm.~\ref{DeterministicUniquenessTheorem} is loose in that it assigns to each support $S \in \mathcal{H}$ a corresponding support $\overline S$ without consideration of previously matched pairs; although we doubt tightening in this way will lead to sub-exponential sample sizes.
-Sample complexity will also benefit from lowering the number of required supports, i.e.
-the size of regular uniform hypergraphs satisfying the SIP.
-The regularity requirement on support hypergraphs can be loosened to allow for certain non-regular hypergraphs satisfying constraints on the degree sequence of nodes; though we impose regularity for clarity of exposition.
-It is then natural to ask: what is the smallest hypergraph satisfying the required constraints forgiven $m$ and $k$?
-Finally, the error bounds can be improved by tightening the constant $C_1$, e.g.
-via an improvement in Lemma ?.
-
-%Solving Prob.~\ref{SLCopt} directly is intractable in general since it necessitates, for each proposed dictionary $\mathbf{B}$, a combinatorial search for the supports of the associated sparse codes $\mathbf{\overline x}_i$.
-A common work-around is to convexify the problem (for fixed $\mathbf{B}$) by substituting the norm $\|\cdot\|_0$ with $\|\cdot\|_1$, impelled the fact that matrices $\mathbf{A}$ with large enough $L_{2k}(\mathbf{A})$ induce the same sparse codes via minimization of either norm \cite{?}.
-To this end, the lower bound $L_{2k}(\mathbf{BP}) \geq (L_{2k}(\mathbf{A}) - C_1\varepsilon) / \|\mathbf{D}\|_1$ implied by Thm.~\ref{DeterministicUniquenessTheorem} hints at conditions on the generating dictionary $\mathbf{A}$ and $k$-sparse codes $\mathbf{x}_i$ under which \emph{all} matrices $\mathbf{B}$ (of bounded column-norm) that solve Prob.~\ref{OptimizationProblem} also share this property of $\mathbf{A}$ by virtue of uniqueness and stability.
-One might then imagine an inference procedure whereby sparse codes are inferred via minimization of $\|\cdot\|_1$, but solutions still evaluated by their collective support size, yielding unique optimal solutions to Prob.~\ref{SLCopt} if only constraints could be imposed such that the learning procedure eventually guides $\mathbf{B}$ through an optimal dictionary.
-% (e.g.
-the dictionary is a member of a known finite set).
-
-\textbf{Acknowledgement.} We thank Fritz Sommer and Darren Rhea for early thoughts, and Ian Morris for posting \eqref{eqdim} online.
-
-%\section{EXTRA}
-%An additional consequence of Thm.~\ref{DeterministicUniquenessTheorem} of potential practical relevance to is the implied lower bound $L_{2k}(\mathbf{BPD}) \geq L_{2k}(\mathbf{A}) - C_1\varepsilon$ in the case where $\mathbf{A}$ satisfies \eqref{SparkCondition}.
-Since solving Prob.~\ref{SLCopt} directly requires a combinatorial search over sparse supports for the $\mathbf{\overline x}_i$ for each proposed dictionary $\mathbf{B}$, rendering it intractable in general, a common strategy is to replace the $\ell_0$-norm in \eqref{minsum} with the $\ell_1$-norm, thereby transforming the inference of sparse $\mathbf{\overline x}_i$ for a fixed dictionary $\mathbf{B}$ into a convex optimization solvable by a linear program.
-A major advance in compressive sensing was the discovery that, for fixed $\mathbf{B}$, solutions to \eqref{minsum} using either norm yield the same sparse vectors $\mathbf{\overline x}_i$ (up to noise) provided $L_{2k}(\mathbf{B})$ is large enough \cite{?}.
-What our results hint at are conditions on the generating dictionary $\mathbf{A}$ and $k$-sparse codes $\mathbf{x}_i$ under which \emph{all} matrices $\mathbf{B}$ (of bounded column-norm) that solve Prob.~\ref{OptimizationProblem} also share this property by virtue of uniqueness and stability; that is, conditions which guarantee that the sparse codes $\mathbf{\overline x}_i$ solving Prob.~\ref{OptimizationProblem} also solve the convexified problem when the corresponding dictionary $\mathbf{B}$ is held fixed.
-It remains to determine, however, what practical conditions preclude matrices that don't solve Prob.~\ref{OptimizationProblem} from nonetheless solving the convexified problem.
-%
-%Regardless, an implication of the above observation is that the following algorithm solves Prob.~\ref{OptimizationProblem} without appeal to combinatorial search:
-%\begin{enumerate}
-%\item List all matrices $\mathbf{B}$.
-%\item For each matrix $\mathbf{B}$, solve $\mathbf{\overline x}_i = \arg \min \|\mathbf{v}\|_1$ s.t. $\|\mathbf{Bv} - \mathbf{z}_i\| \leq \eta$ for $i = 1, \ldots, N$.
-%\item Quantify the proposed solution $\mathbf{B}$ and $\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N$ as $\rho(\mathbf{B}, \mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N) = \sum_{i=1}^{N} \|\mathbf{\overline x}_i\|_0$.
-%\item Output $\arg \min_{\mathbf{B}, \mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N} \left( \rho \right)$.
-% \end{enumerate}
-
-%Since its inception some twenty years ago, sparse coding has become a standard tool in signal analysis, yielding myriad insights into the structure of natural signals across a variety of scientific domains.
-In this work,
-
-%We make a final remark about the tightness of our results and the computability of our derived constants.
-%We remark that our constants have been derived for deterministic ``worst-case'' noise, whereas the ``effective'' noise might be smaller when sampled from a distribution.
-
-%Our results suggest that this correspondence could be due to the ``universality'' of sparse representations in natural data, an early idea in neural theory \cite{pitts1947}.
-
-% \vspace{-.2 cm}
-
-%\showacknow % Display the acknowledgments section
-
-\bibliographystyle{IEEEtran}
-\bibliography{chazthm_ieee_trans_sig}
-
-% \vspace{-.2 cm}
-
-\section{Appendix}\label{proofs}
+\chapter{Appendix: Proof of Main Lemma}\label{proofs}
 

### 2020-08-05 manuscripts/newthesis/discussion.tex
newthesis

--- 2020-08-04 manuscripts/thesis/discussion.tex
@@
-\section{Discussion}\label{Discussion}
+\chapter{Discussion}\label{Discussion}
+
+\section{Conclusions}
 
@@
 %The solution to Prob.~\ref{OptimizationProblem}, that of most interest to practitioners of dictionary learning methods, is (to my knowledge) the first of its kind in both the noise-free and noisy domains.
-
-\section{Future Directions}\label{FutureDirections}
-
-There are many challenges left open by this work.
-First and foremost, it should be stressed that all conditions stated here which guarantee the uniqueness and stability of sparse representations have only been shown sufficient; it remains open to work out a set of necessary conditions on all fronts, be it on the number of required samples per support, the structure of support set hypergraphs, or the tolerable signal-to-noise ratio for a bounded recovery error.
-It is also worth stressing that the deterministic conditions derived here must accommodate always the worst possible cases.
-It would be of great practical benefit to see how drastically all conditions can be relaxed by requiring less-than-certain guarantees, as (for instance) exhibited in the discussion on probabilistic pigeonholing following the proof of Thm.~\ref{DeterministicUniquenessTheorem}.
-In a similar vein, the tolerable signal-to-noise ratio can be reduced by considering the probability that noise sampled from a concentrated isotropic distribution will point in a harmful direction, which may be especially low in high-dimensional spaces or for certain support set hypergraphs.
-
-Another interesting remaining challenge is to work out for which special cases it is efficient to check that a solution to Prob.~\ref{InverseProblem} or \ref{OptimizationProblem} is unique up to noise and inherent ambiguities.
-Considering that the sufficient conditions detailed here are in general NP-hard to compute, are the necessary conditions also hard to compute?
-Are Probs.~\ref{InverseProblem} and \ref{OptimizationProblem} then also hard (e.g., see \cite{tillmann2015computational})?
-Since Prob.~\ref{SLCopt} is intractable in general (i.e.
-including the noiseless case), but efficiently solvable by convex relaxation when the matrix $\mathbf{A}$ is known and has a large enough lower bound over sparse domains \cite{eldar2012compressed}, is there a version of Thm.~\ref{SLCopt} that lays down general conditions under which Prob.~\ref{OptimizationProblem} can be solved efficiently in full by similar means?
-% [*** Incorporate this open problem with more words ***]
-
-%Finally, it was noted that the combinatorial approach applied here allows for guaranteed recovery of some or all dictionary elements even if the dictionary is overestimated (i.e.
-$\overline m > m$).
-What if it is underestimated?
-How then would the recovered dictionary elements relate to the original columns of $\mathbf{A}$?
-
-%Our results suggest that this correspondence could be due to the ``universality'' of sparse representations in natural data, an early idea in neural theory \cite{pitts1947}.
-
-I briefly expand on some of these directions below.
-It is my hope that these remaining challenges pique the interest of the community, and that practical guidelines can be established using the theoretical tools showcased here to support researchers applying sparse coding techniques.
-
-% THIS SECTION ADDRESSES REVIEWER COMPLAINTS:
-
-\subsection{Signal-to-Noise Ratio}
-
-A concern raised in peer review of this work was the typical size of the constant $C_1$, which sets the tolerable signal-to-noise ratio for dictionary and code recovery up to an acceptable error.
-Referring to the definition of this constant in \eqref{Cdef1}, the reader should note that the denominator involves $L_k$, a standard quantity in the field of compressed sensing (the ``restricted isometry constant", see footnote \ref{ripfootnote}), which is known to be reasonable for many random distributions generating dictionaries $\mathbf{A}$ and sparse codes $\mathbf{x}_i$ \cite{baraniuk2008simple}.
-The numerator $C_2$, on the other hand, incorporates the more obscure quantity $\xi$ defined in \eqref{FriedrichsDefinition}, which is computed from the ``Friedrichs angle" between certain spans of subsets of the columns of $\mathbf{A}$.
-Simulations for small (pseudo-)randomly generated dictionaries $\mathbf{A}$ suggest nonetheless that the constant $C_2$ is likely reasonable in general as well (at least, for the case where $m=k^2$ and $\mathcal{H}$ is taken to be the set of rows and columns formed by arranging the elements of $[m]$ into a square grid; see Fig.
-\ref{reasonableC2}).
-These observations motivate the following conjecture:
-
-\begin{conjecture}
-For all $t > 0$,
-\begin{equation*}
-Pr[ \left| C_2- \mathbb{E}[C_2 ] \right| > t] \to 0 \ \ \text{as $k \to \infty$ and $k/m \to 0$} 
-\end{equation*}
-provided the assumptions of Thm. \ref{DeterministicUniquenessTheorem} are satisfied.
-\end{conjecture}
-%Finally, the error bounds can be improved by tightening the constant $C_1$, e.g. via an improvement in Lemma ?.
-%$C_1 = C_1(\mathbf{A}, \mathcal{H}, \{ \mathbf{x_i} \}_{i=0}^N)$
-
-\subsection{Sample Complexity}
-
-It is possible to tighten the pigeonholing argument in the proof of Thm.~\ref{DeterministicUniquenessTheorem} and thereby reduce the deterministic sample complexity without recourse to uncertainty (as previously suggested).
-The argument as presented iterates over supports $S \in \mathcal{H}$, in each case determining a corresponding support $\overline S \in {[\overline m] \choose k}$ without consideration of previously matched support pairs; and yet the assumption $L_{2\mathcal{H}}(\mathbf{A}) > 0$ implies that no two supports in $\mathcal{H}$ can map to the same $\overline S$.
-The number of bins to pigeonhole into thus decreases every iteration, though this is a drop in a bucket of exponential size.
-It would be interesting to see how much the deterministic sample complexity can be reduced by imposing these constraints holistically, given the specific structure of the hypergraph $\mathcal{H}$.
-
-Incidentally, there is also room to breathe in the restrictions on $\mathcal{H}$.
-Already, the results of this work motivate the following question, which is only one among many combinatorial problems brought to mind by the SIP (Def.~\ref{sip}):
-\begin{question}
-Fix integers $m$ and $k < m$. What is the smallest regular hypergraph $\mathcal{H} \subseteq {[m] \choose k}$ satisfying the SIP?
-\end{question}
-
-A close examination of the proof of Lemma \ref{NonEmptyLemma} (see the Appendix) reveals, however, that $\mathcal{H}$ need not be regular so long as it satisfies a constraint on the sequence of node degrees compatible with the iterative argument.
-It is then natural to wonder: what are the necessary constraints on $\mathcal{H}$, and what is the smallest hypergraph satisfying these constraints for given $m$ and $k$?
-
-Opening ourselves up to uncertainty, we can furthermore ask:
-\begin{question}\label{probofsip}
-Fix $k < m$. What is the probability that a random subset of ${[m] \choose k}$ is regular and satisfies the SIP?
-\end{question}
-
-Within the realm of uncertain guarantees, we can also elaborate on the probabilistic pigeonholing strategy outlined in the discussion following the proof of Thm.~\ref{DeterministicUniquenessTheorem}.
-The problem is to count the number of ways in which vectors supported in $S \in \mathcal{H}$ can be partitioned among supports in ${\overline m \choose k}$ without allocating $k$ or more to any individual one (in which case the logic of the proof fails to imply the result; we are interested in the probability that it doesn't).
-These are integer solutions to the problem $\sum_i n_i = N$ subject to $n_i < k$ for all $i$, where $i = 1, \ldots, {\overline m \choose k}$.
-Following closely the exposition in \cite{stackexchangeanswer}, it appears there is no closed formula for this problem, but the number of solutions can be computed in a number of operations independent of $N$.
-Writing $p = {\overline m \choose k}$, the number is the coefficient of $X^N$ in the polynomial $(1 + X + \ldots + X^{k-1})^p$.
-Written as a rational function of $X$,
-
-\begin{equation*}
-(1 + X + \ldots + X^{k-1})^p = \left(\frac{1 - X^k}{1 - X} \right)^p = \frac{\left(1 - X^k \right)^p}{\left(1 - X\right)^p}
-\end{equation*}
-the coeffiecient of $X^i$ in the numerator is zero unless $i$ is a multiple $qk$ of $k$, in which case it is $(-1)^q{p \choose q}$, and the coefficient of $X^j$ in the inverse of the denominator is $(-1)^j {-p \choose j} = {j + p-1 \choose j}$, which is zero unless $j \geq 0$ and otherwise equal to ${j + p-1 \choose p-1}$.
-It remains to sum over all $i + j = N$, which gives:
-
-\begin{equation*}
-n_\text{fails} = \sum_{q=0}^{\text{min}(p, N/k)} (-1)^q {p \choose q} {N - qk + p - 1 \choose p - 1}
-\end{equation*}
-where the summation is truncated to ensure that $N - qk \geq 0$ (the condition $j \geq 0$) and has at most $p+1 = {\overline m \choose k} + 1$ terms.
-
-The total number of ways to pigeonhole is $n_\text{total} = {N +p- 1 \choose p - 1}$, and so the probability of full recovery is $\left(1 - n_\text{fails} / n_\text{total} \right)^{|\mathcal{H}|}$. 
-The curves computed in this way in Fig.
-\ref{probpigeon} suggest that, while it may very well be impossible to exorcise exponentiality from the number of required samples in the deterministic or almost-certain case, perhaps it is possible with high-probability by one way or another.
-Informally,
-
-\begin{question}
-While fixing $k$ yields polynomial deterministic sample complexity in $m$ (see Cor.~\ref{DeterministicUniquenessCorollary}), is there some more general probablistic sense (perhaps for some restricted class of hypergraphs) by which sample complexity is polynomial in both $m$ and $k$?
-\end{question}
-%Referring to Fig.
-\ref{probpigeon}, which computes these probabilities for some small hypergraphs, one is led to wonder if it may be possible to exorcise exponentiality from the sample complexity asymptotically in this way or another.
-
-%\begin{question}
-%Is there a class of hypergraphs $\mathcal{H} = \mathcal{H}(m,k)$ and a polynomial $p(m,k)$ such that $N \geq p(m,k)$ implies successful dictionary and code recovery with a probability approaching one for generic $\mathbf{A}$ and $\mathbf{x}_i$ supported in $\mathcal{H}$ as $m \to \infty$?
-%Is there a class of hypergraphs $\mathcal{H}$ for which a number of samples $N$ polynomial in both $m$ and $k$ suffices to guarantee stable recovery of $\mathbf{A}$ and sparse codes $\mathbf{x}_i$ as $k/m \to 0$?
-%\end{question}
-
-\subsection{Convex Optimization}
-
-A commonly applied workaround to the intractability of Prob.~\ref{SLCopt} (see \cite{tillmann2015computational}) is to swap out the norm $\|\cdot\|_0$ in \eqref{minsum} for $\|\cdot\|_1$, thereby transforming the inference of sparse $\mathbf{\overline x}_i$ for a given $\mathbf{B}$ into a convex optimization solvable by a linear program.
-A major advance in compressive sensing was the discovery that \eqref{minsum} can in fact be solved in this way for fixed $\mathbf{B}$ provided $L_{2k}(\mathbf{B})$ is large enough \cite{eldar2012compressed}.
-The current work provides conditions on the generating dictionary $\mathbf{A}$ and $k$-sparse codes $\mathbf{x}_i$ under which \emph{all} matrices $\mathbf{B}$ (of bounded column-norm) that solve Prob.~\ref{OptimizationProblem} have $L_{2k}(\mathbf{B})$ bounded from below; specifically, $L_{2k}(\mathbf{B}) \geq \left(L_{2k}(\mathbf{A}) - C_1\varepsilon \right) / \|\mathbf{D}\|_1$ in the case where $\mathbf{A}$ satisfies \eqref{SparkCondition}.
-Thus, there is some noise bound inside of which all solutions to Prob.~\ref{OptimizationProblem} are solutions to the convexified problem as well.
-It remains to determine practical constraints that would exclude alternative dictionaries which may solve the convefixied problem without solving Prob.~\ref{OptimizationProblem}.
-
-% SOLUTION CHECKING ALGORITHM:
-%\begin{enumerate}
- %  \item For each $\mathbf{x_i}$, determine its support $S$ and increment a counter corresponding to that support.
-  % \item For each support $S$ with count greater than $(k-1){m \choose k}$, check the $\mathbf{x_i}$ supported there are in general linear position (i.e.
-the determinant of the matrix having $\mathbf{x}_i$ as its columns is nonzero) and discard $S$ if not.
- %  \item Check the remaining set of supports satisfies the SIP. 
-  % \item If so, list all of its regular $k$-uniform sub-hypergraphs and discard those for which $L_{2\mathcal{H}}(\mathbf{A}) = 0$. 
-  % \item For each of the remaining hypergraphs, compute the constant $C_1$ from $\mathbf{A}$ and the $\mathbf{x_i}$.% (or for every subset of the  $\mathbf{x_i}$ of size $(k-1){m \choose k}$).
- %  \item Check that $\varepsilon < L_2(\mathbf{A})$. If yes, the solution is "unique".
-%\end{enumerate}
-
-\begin{figure}\label{probpigeon}
-\begin{center}
-\includegraphics[width=1 \linewidth]{figures/prob_vs_samples.png}
-\caption{Probability of successful dictionary and code recovery (as per Thm.
-\ref{DeterministicUniquenessTheorem}) for a number of samples $N$ given as a fraction of the deterministic sample complexity $N = |\mathcal{H}|[(k-1){m \choose k} + 1]$ when the support set hypergraph $\mathcal{H}$ is the set of $m$ consecutive intervals of length $k$ in a cyclic order on $[m]$.
-Each plot has $k$ ranging from $2$ to $m-1$ (the case $k=1$ requires $N=m$), with lighter grey lines corresponding to larger $k$.
-Successful recovery is nearly certain with far fewer samples than the deterministic sample complexity.
-}
-\vspace{-.6 cm}
-\label{probvsamples}
-\end{center}
-\end{figure}
-
-\begin{figure}\label{reasonableC2}
-\begin{center}
-\includegraphics[width=1 \linewidth]{figures/C2.pdf}
-\caption{Distribution of $C_2(\mathbf{A}, \mathcal{H})$ computed for 1.33x overcomplete generic unit-norm dictionaries $\mathbf{A} \in \mathbb{R}^{n \times m}$ (i.e.
-with $n = 3m/4$) when the support set hypergraph $\mathcal{H}$ consists of the rows and columns formed by arranging  the elements of $[m]$ into a square grid (i.e.
-$m = k^2$).
-The distribution becomes more concentrated as $m$ grows.}
-\vspace{-.6 cm}
-\label{samples_vs_m}
-\end{center}
-\end{figure}

### 2020-08-05 manuscripts/newthesis/future.tex
newthesis

--- 2020-08-04 manuscripts/thesis/discussion.tex
@@
-\section{Discussion}\label{Discussion}
-
-The main motivation for this work was the observation that characteristic sparse representations emerge from sparse coding models trained over a variety of natural scene datasets by a variety of learning algorithms.
-The theorems proven here provide some insight into this phenomenon by establishing very general conditions under which identification of the model parameters is not only possible but also robust to measurement and modeling error.
-
-The guarantees concerning the identification of a dictionary and corresponding sparse codes of minimal average support size (Thm.~\ref{SLCopt}), which is the optimization problem of most interest to practitioners (Prob.~\ref{OptimizationProblem}), are to my knowledge the first of their kind in both the noise-free and noisy domains.
-It has been shown here that, given sufficient data, this problem reduces to an instance of Prob.~\ref{InverseProblem} to which the main result (Thm.~\ref{DeterministicUniquenessTheorem}) then applies: every dictionary and corresponding set of sparse codes consistent with the data are equivalent up to inherent relabeling/scaling ambiguities and a discrepancy (error) that scales linearly with the noise.
-In fact, %provided $n \geq \min(2k,m)$, 
-in almost all cases these problems are well-posed given a sufficient amount of data (Thm.~\ref{robustPolythm} and Cor.~\ref{ProbabilisticCor}). 
-Furthermore, the derived scaling constants are explicit and computable; as such, there is an effective procedure that suffices to affirm if a proposed solution to these problems is indeed unique up to noise and inherent ambiguities, although it is not efficient in general.
-%Specifically, given a dictionary and sparse codes purported to solve to Prob.~\ref{InverseProblem}, one checks that that they satisfy the corresponding constraints on $\mathbf{A}$ and the $\mathbf{x_i}$ given in the statement of Thm.~\ref{DeterministicUniquenessTheorem}.
-
-%to the recovery of ``mouse neuronal activity representing location on a track \cite{agarwal2014spatially}
-
-The absence of any assumptions at all about dictionaries that solve Prob.~\ref{InverseProblem} was a major technical hurdle in proving Thm.~\ref{DeterministicUniquenessTheorem}. 
-This very general guarantee was sought because of the practical difficulty of ensuring that an algorithm maintain a dictionary satisfying the spark condition \eqref{SparkCondition} at each iteration, which (to my knowledge) has been an explicit or implicit assumption of all previous works except \cite{Hillar15}; indeed, even certifying a dictionary has this property is NP-hard \cite{tillmann2014computational}.
-
-Several results in the literature had to be combined to extend the guarantees derived in \cite{Hillar15} into the noisy regime.
-The main challenge was to generalize Lem.~\ref{MainLemma} to the case where the $k$-dimensional subspaces spanned by corresponding submatrices $\mathbf{A}_S$ and $\mathbf{B}_{\pi(S)}$ are assumed to be``close" but not identical.
-Unlike in \cite{Hillar15} where an inductive argument could be applied to the noiseless case, here it had to be explicitly demonstrated that this proximity relation is propagated through iterated intersections right down to the spans of the dictionary elements themselves.
-Lem.~\ref{DistanceToIntersectionLemma} was designed to encapsulate this fact, proven by appeal to a convergence guarantee for an alternating projections algorithm first proposed by von Neumann.
-This result, combined with a little known fact \eqref{eqdim} about the distance metric between subspaces, make up the more obscure components of the deduction.
-
-The proof of Lem.~\ref{MainLemma} diverges most significantly from the approach taken in \cite{Hillar15} by way of Lem.~\ref{NonEmptyLemma}, which utilizes a combinatorial design for support sets (the ``singleton intersection property") to reduce the deterministic sample complexity by an exponential factor.
-This constitutes a significant advance toward legitimizing dictionary learning in practice, since data must otherwise exhibit the exponentially many possible $k$-wise combinations of dictionary elements required by (to my knowledge) all previously published results; although an exponential number of samples per support is still required (unless $k$ is held fixed).
-The issue is that the map $\pi:\mathcal{H} \to {[m] \choose k}$ is surjective only when $\mathcal{H}$ is taken to be ${[m] \choose k}$, in which case one may proceed by induction as in \cite{Hillar15}, freely choosing supports in the codomain of $\pi$ to intersect over $(k-1)$ indices to then map back to some corresponding set of $(k-1)$ indices at the intersection of supports in the domain.
-Here, for $\mathcal{H} \subset {[m] \choose k}$, a bijection between indices had to instead be established by pigeonholing the image of $\pi$ under constraints imposed by the SIP, which was formulated specifically for this purpose.
-It just so happened that this more general argument for a non-surjective $\pi$ constrained by the SIP applied just as well to the situation where the number of dictionary elements $m$ is over-estimated (i.e.
-$\overline m > m$), in which case a one-to-one correspondence can be guaranteed between a subset of columns of $\mathbf{A}$ and $\mathbf{B}$ of a size simply expressed in terms of the width of each matrix and the regularity of $\mathcal{H}$.
-
-One of the mathematically significant achievements in \cite{Hillar15} was to break free from the constraint that the recovery matrix $\mathbf{B}$ satisfy the spark condition in addition to the generating dictionary $\mathbf{A}$.
-%, in contrast to all previously known uniqueness results which (to my knowledge) have all either explicitly or implicitly made this assumption.
-Here, it has been demonstrated that, in fact, even $\mathbf{A}$ need not satisfy the spark condition!
-Rather, $\mathbf{A}$ need only be injective on the union of subspaces with supports forming a regular $k$-uniform hypergraph satisfying the SIP (a distinguishing example is given in Sec.~\ref{Results}).
-This relaxation of constraints inspired the definition of the restricted matrix lower bound $L_{\mathcal{H}}$ in \eqref{Ldef}, which generalizes the well-known (see footnote \ref{ripfootnote}) restricted matrix lower bound $L_k$ to be in terms of a hypergraph $\mathcal{H}$, and an interesting object for further study in its own right.
-%(For instance, how hard is it to check that $L_\mathcal{H}(\mathbf{A}) > 0$?)
-%The absence of any restrictions on dictionaries solving Prob.~\ref{InverseProblem} is a major technical obstruction, but highly desirable because of the practical difficulty in ensuring that an algorithm maintain a dictionary satisfying the spark condition \eqref{SparkCondition} at each iteration; indeed, even certifying a dictionary has this property is NP-hard \cite{tillmann2014computational}.
-
-To reiterate, the methods applied here to prove Thm.~\ref{DeterministicUniquenessTheorem} yield the following results beyond a straightforward extension of those in \cite{Hillar15} to the noisy case:
-
-\begin{enumerate}
-\item A reduction in deterministic sample complexity: To identify the $n \times m$ generating dictionary $\mathbf{A}$, it is required in \cite{Hillar15} that $k{m \choose k}$ data points be sampled from each of the ${m \choose k}$ subspaces spanned by subsets of $k$ columns of $\mathbf{A}$.
-It is shown here that in fact it suffices to sample from at most $m$ such subspaces (see Cor.~\ref{DeterministicUniquenessCorollary}).
-%; thus, for fixed $k$, the deterministic sample complexity is polynomial in $m$.
-%HS15 was already poly for fixed k
-\item An extension of guarantees to the case where the number of dictionary elements is unknown: The results of \cite{Hillar15} only apply to the case where the matrix $\mathbf{B}$ has the same number of columns as $\mathbf{A}$.
-It is shown here that if $\mathbf{B}$ has at least as many columns as $\mathbf{A}$ then it contains (up to noise) a subset of the columns of $\mathbf{A}$.
-\item Relaxed requirements (no spark condition) on the generating matrix $\mathbf{A}$: Rather, $\mathbf{A}$ need only be injective on the union of subspaces with supports that form a regular uniform hypergraph satisfying the SIP.
-\end{enumerate}
-
-As it seemed to benefit a reviewer of this work, a brief discussion on how the deterministic sample complexity $N = |\mathcal{H}\left[|(k-1){m \choose k} + 1\right]$ derived here compares to those listed in the the top two rows listed in Table I of \cite{Hillar15} may be in order.
-To be clear, the theory developed here is strictly more general, since $\mathcal{H}$ can always be taken to be ${[m] \choose k}$.
-The point of difference in this comparison is the assumed set of supports for sparse codes, which is always ${[m] \choose k}$ in \cite{Hillar15}, whereas here it can be assumed to be any regular $k$-uniform hypergraph that satisfies the SIP.
-By row, %, assuming for our results that sufficient data have been sampled from all supports in a hypergraph H satisfying the SIP:
-\begin{enumerate}
-\item[I.] The result here improves upon the listed $k{m \choose k}^2$ by an exponential factor, since for every $k < m$ there exists a regular $k$-uniform hypergraph $\mathcal{H}$ with $|\mathcal{H}| = m$ satisfying the SIP.
-\item[II.] The authors in \cite{Hillar15} have applied measure-theoretic arguments to achieve $(k+1){m \choose k}$ with almost-certainty (i.e.
-with probability one), a factor of $m$ reduction over that for which certainty can alternatively be guaranteed here.
-%\item[III.] A direct comparison cannot be made because it is an open question as to the probability that a random set of supports satisfies the SIP.
-This would be an interesting problem for the community to solve; regardless, the result of \cite{Hillar15} is still implied by the more general theory given here.
-%\item[IV.] The result here is $|\mathcal{H}\left[|(k-1){m \choose k} + 1\right]$ with probability one compared to $(k+1){m \choose k}$ with probability one.
-In this case the sample complexity stated in \cite{Hillar15} is marginally better, but it relies on a noise-free technicality unique to their assumption $\mathcal{H} = {m \choose k}$.
-%differs in flavor: their $\mathbf{x_i}$ are assumed to be distributed as $(k+1)$ samples per support for every support of size $k \in [m]$, whereas here it is assumed that $(k-1){m \choose k}$ codes $\mathbf{x_i}$ are distributed over each support in some hypergraph $\mathcal{H}$ satisfying the SIP.
-%\item[V.] Again, a direct comparison cannot be made for the reason stated for row III.
-\end{enumerate}
-
-%Beyond an extension of existing noiseless guarantees \cite{Hillar15} to the noisy regime and their novel application to Prob.~\ref{OptimizationProblem}, this work contains a theory of combinatorial designs for support sets key to identification of dictionaries.
-This idea is incorporated into a fundamental lemma in matrix theory (Lem.~\ref{MainLemma}) that draws upon the definition of a matrix lower bound (\ref{Ldef}) induced by a hypergraph.
-As a consequence of this combinatorial approach, recovery of some or all dictionary elements can be guaranteed even if: i) dictionary size is overestimated, ii) data cover only a polynomial number of distinct sparse supports, and iii) dictionaries do not satisfy the spark condition.
-
-Another reviewer of this work lamented that while the extension from exact recovery to the noisy stability of dictionary learning is significant, the fact that the analysis relies on metrics of the data that are not feasible to compute limits its impact to the scientific community beyond computer science and applied mathematics.
-What sets the main results of this work apart from the vast majority of results in the field is that they are deterministic, and do not depend on any kind of assumption about the particular random distribution from which the sparse supports, coefficients, or dictionary entries are drawn (though Cor.~\ref{ProbabilisticCor} makes a sweeping statement applicable to all continuous distributions).
-Consequently, the inferences of those applying dictionary learning methods to inverse problems in their research are justified only in principle; but this is unavoidably the case for NP-hard problems.
-
-Indeed, theoretical validation makes little practical difference if the methodology is already in widespread use, while practical criteria establishing whether the data models obtained by practitioners are optimal or not would have very high impact.
-To this end, the work has been laid out for those wanting to derive statistical criteria for inference with respect to more domain-specific structured dictionaries and codes (i.e.
-estimate $C_1$), and reduced by half for those hoping to prove the consistency of any dictionary learning algorithm (i.e.
-prove convergence to within $\varepsilon(\delta_1,\delta_2)$ given in \eqref{epsdel}).
-%who will derive from our deterministic guarantees the statistical criteria for inference in more domain-specific probabilistic models
-
-Nonetheless, a main reason for the sustained interest in dictionary learning as an unsupervised method for data analysis seems to be the assumed well-posedness of parameter identification in the model, confirmation of which forms the core of these findings.
-Several groups have applied compressed sensing to signal processing tasks; for instance, in MRI analysis \cite{lustig2008compressed}, image compression \cite{Duarte08}, and even the design of an ultrafast camera \cite{Gao14}.
-It is only a matter of time before these systems incorporate dictionary learning to encode and decode signals (e.g., in a device that learns structure from motion \cite{kong2016prior}), just as scientists have used sparse coding to %make sense of their data \cite{jung2001imaging, agarwal2014spatially, lee2016sparse, wu2016stability}.
-uncover latent structure in data (e.g., forgery detection \cite{hughes2010, olshausen2010applied}; brain recordings \cite{jung2001imaging, agarwal2014spatially, lee2016sparse}; and gene expression \cite{wu2016stability}).
-As uniqueness guarantees with minimal assumptions apply to all areas of data science and engineering that utilize learned sparse structure, assurances offered by these theorems give hope that different devices and algorithms may learn equivalent representations given enough data from statistically identical systems.\footnote{To contrast with the current hot topic of ``Deep Learning'', there are few such uniqueness guarantees for these models of data; moreover, even small noise can dramatically alter their output \cite{goodfellow2014explaining}.}
-
-Within the field of theoretical neuroscience in particular, dictionary learning for sparse coding and related methods have recovered characteristic components of natural images \cite{Olshausen96, hyvarinen1999fast, bell1997independent, van1998independent} and sounds \cite{bellsejnowski1996, smithlewicki2006, Carlson12} that reproduce response properties of cortical neurons.
-The results of this work suggest that this correspondence could be due to the ``universality" of sparse representations in natural data, an early mathematical idea in neural theory \cite{pitts1947}.
-Furthermore, they justify the soundness of one of the few hypothesized theories of bottleneck communication in the brain \cite{Isely10}: that sparse neural population activity is recoverable from its noisy linear compression through a randomly constructed (but unknown) wiring bottleneck by any biologically plausible unsupervised sparse coding method that solves Prob.~\ref{DeterministicUniquenessTheorem} or \ref{SLCopt} (e.g., \cite{rehnsommer2007, rozell2007neurally, pehlevan2015normative}).\footnote{We refer the reader to \cite{ganguli2012compressed} for more on interactions between dictionary learning and neuroscience.}
-
-%The solution to Prob.~\ref{OptimizationProblem}, that of most interest to practitioners of dictionary learning methods, is (to my knowledge) the first of its kind in both the noise-free and noisy domains.
-
 \section{Future Directions}\label{FutureDirections}
@@
 
-\subsection{Signal-to-Noise Ratio}
+\subsection{Increasing Signal-to-Noise Ratio}
 
@@
 
-\subsection{Sample Complexity}
+\subsection{Reducing Sample Complexity}
 
@@
 
-\subsection{Convex Optimization}
+\subsection{Dictionary Learning via $\ell_1$-norm minimization}
 
@@
 %\end{enumerate}
-
-\begin{figure}\label{probpigeon}
-\begin{center}
-\includegraphics[width=1 \linewidth]{figures/prob_vs_samples.png}
-\caption{Probability of successful dictionary and code recovery (as per Thm.
-\ref{DeterministicUniquenessTheorem}) for a number of samples $N$ given as a fraction of the deterministic sample complexity $N = |\mathcal{H}|[(k-1){m \choose k} + 1]$ when the support set hypergraph $\mathcal{H}$ is the set of $m$ consecutive intervals of length $k$ in a cyclic order on $[m]$.
-Each plot has $k$ ranging from $2$ to $m-1$ (the case $k=1$ requires $N=m$), with lighter grey lines corresponding to larger $k$.
-Successful recovery is nearly certain with far fewer samples than the deterministic sample complexity.
-}
-\vspace{-.6 cm}
-\label{probvsamples}
-\end{center}
-\end{figure}
-
-\begin{figure}\label{reasonableC2}
-\begin{center}
-\includegraphics[width=1 \linewidth]{figures/C2.pdf}
-\caption{Distribution of $C_2(\mathbf{A}, \mathcal{H})$ computed for 1.33x overcomplete generic unit-norm dictionaries $\mathbf{A} \in \mathbb{R}^{n \times m}$ (i.e.
-with $n = 3m/4$) when the support set hypergraph $\mathcal{H}$ consists of the rows and columns formed by arranging  the elements of $[m]$ into a square grid (i.e.
-$m = k^2$).
-The distribution becomes more concentrated as $m$ grows.}
-\vspace{-.6 cm}
-\label{samples_vs_m}
-\end{center}
-\end{figure}

### 2020-08-05 manuscripts/newthesis/introduction.tex
newthesis

--- 2020-08-04 manuscripts/thesis/introduction.tex
@@
-\section{Introduction}\label{Intro}
-
-%\begin{itemize}
-%\item Background to the topic.
-%\item Brief review of current knowledge.
-%\item Indicate the gap in knowledge. State the aim of the research and how it fits into the gap.
-%\item Can include an outline of what follows.
-%\end{itemize}
-
-%Why do neuroscientists care about dictionary learning?
+\chapter{Introduction}\label{Intro}
 
@@
 
-Here, we prove very generally that uniqueness and stability is a typical property of sparse dictionary learning.
-More specifically, we show that matrices injective on a sparse domain are identifiable from \mbox{$N = m(k-1){m \choose k} + m$} noisy linear combinations of $k$ of their $m$ columns up to an error that is linear in the noise (Thm.~\ref{DeterministicUniquenessTheorem}).
-In fact, provided $n \geq \min(2k,m)$, in almost all cases the problem is well-posed, as per Hadamard \cite{Hadamard1902}, given a sufficient amount of data (Thm.~\ref{robustPolythm} and Cor.~\ref{ProbabilisticCor}).
+\section{Transform Coding}
 
-Our guarantees also hold for a related (and perhaps more commonly posed, e.g.
-\cite{rehnsommer2007}) optimization problem seeking a dictionary minimizing the average number of elementary waveforms required to reconstruct each sample of the dataset (Thm.~\ref{SLCopt}).
-To practical benefit, our results impose no restrictions on learned dictionaries (e.g., that they, too, be injective over some sparse domain) beyond an upper bound on dictionary size, which is necessary in any case to avoid trivial solutions (e.g., allowing $m = N$).
-%That is, every pair of solutions of comparable size has some number of dictionary elements in common (up to noise), and similarly so for the coefficients of sparse codes they induce.
+\section{Sparse Representations}
 
-More precisely, let $\mathbf{A} \in \mathbb R^{n \times m}$ be a matrix with columns $\mathbf{A}_j$ ($j = 1,\ldots,m$) and let dataset $Z$ consist of measurements:
-\begin{align}\label{LinearModel}
-\mathbf{z}_i = \mathbf{A}\mathbf{x}_i + \mathbf{n}_i,\ \ \  \text{$i=1,\ldots,N$},
-\end{align}
-for $k$-\emph{sparse} $\mathbf{x}_i \in \mathbb{R}^m$ having at most $k<m$ nonzero entries and \emph{noise} $\mathbf{n}_i \in \mathbb{R}^n$, with bounded norm $\| \mathbf{n}_i \|_2 \leq  \eta$ representing our worst-case uncertainty in measuring the product $\mathbf{A}\mathbf{x}_i$.
-We first consider the following decidable\footnote{Note that Prob.~\ref{InverseProblem} is decidable for rational inputs $\mathbf{z}_i$ \cite{chrishillar} since the statement that it has a solution can be expressed as a logical sentence in the theory of algebraically closed fields, and this theory has quantifier elimination \cite{basu2006algorithms}.} formulation of sparse coding.
-%The first mathematical problem we consider is the following.
+\section{Analytic vs. Learned Dictionaries for Sparse Representation}
 
-\begin{problem}\label{InverseProblem}
-Find a dictionary matrix $\mathbf{B}$ and $k$-sparse codes $\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N$ that satisfy $\|\mathbf{z}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \eta$ for all $i = 1,\ldots,N$.
-\end{problem}
+\section{Thesis Outline}
 
-Note that every solution to Prob.~\ref{InverseProblem} represents infinitely many equivalent alternatives $\mathbf{BPD}$ and $\mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_1, \ldots, \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_N$ parametrized by a choice of permutation matrix $\mathbf{P}$ and invertible diagonal matrix $\mathbf{D}$.
-Identifying these ambiguities (labelling and scale) yields a single orbit of solutions represented by any particular set of elementary waveforms (the columns of $\mathbf{B}$) and their associated sparse coefficients (the entries of $\mathbf{\overline x}_i$) that reconstruct each data point $\mathbf{z}_i$.
-
-Previous theoretical work addressing the noiseless case $\eta =0$ (e.g., \cite{li2004analysis, Georgiev05, Aharon06, Hillar15}) for matrices $\mathbf{B}$ having exactly $m$ columns has shown that a solution to Prob.~\ref{InverseProblem}, when it exists, is unique up to such relabeling and rescaling provided the $\mathbf{x}_i$ are sufficiently diverse and $\mathbf{A}$ satisfies the \textit{spark condition}:
-\begin{align}\label{SparkCondition}
-\mathbf{A}\mathbf{x}_1 = \mathbf{A}\mathbf{x}_2 \implies \mathbf{x}_1 = \mathbf{x}_2, \ \ \ \text{for all $k$-sparse } \mathbf{x}_1, \mathbf{x}_2,
-\end{align}
-%
-which is necessary to guarantee the uniqueness of arbitrary $k$-sparse $\mathbf{x}_i$.
-We generalize these results to the practical setting  $\eta > 0$ by considering the following natural notion of stability with respect to measurement error.
-
-\begin{definition}\label{maindef}
-Fix $Y = \{ \mathbf{y}_1, \ldots, \mathbf{y}_N\} \subset \mathbb{R}^n$.
-We say $Y$ has a \textbf{$k$-sparse representation in $\mathbb{R}^m$} if there exists a matrix $\mathbf{A}$ and $k$-sparse $\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$ such that $\mathbf{y}_i = \mathbf{A}\mathbf{x}_i$ for all $i$.
-This representation is \textbf{stable} if for every $\delta_1, \delta_2 \geq 0$, there exists some $\varepsilon = \varepsilon(\delta_1, \delta_2)$ that is strictly positive for positive $\delta_1$ and $\delta_2$ such that if $\mathbf{B}$ and $k$-sparse $\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N \in \mathbb{R}^m$ satisfy:
-\begin{align*}
-	\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \varepsilon(\delta_1, \delta_2),\ \   \text{for all $i=1,\ldots,N$},
-\end{align*}
-then there is some permutation matrix $\mathbf{P}$ and invertible diagonal matrix $\mathbf{D}$ such that for all $i, j$:
-\begin{align}\label{def1}
-\|\mathbf{A}_j - (\mathbf{BPD})_j\|_2 \leq \delta_1 \ \text{and} \ \|\mathbf{x}_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_i\|_1 \leq \delta_2.
-\end{align}
-\end{definition}
-
-To see how Prob.
-\ref{InverseProblem} motivates Def.
-\ref{maindef}, suppose that $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$ and fix $\delta_1, \delta_2$ to be the desired accuracies of recovery in \eqref{def1}.
-Consider any dataset $Z$ generated as in \eqref{LinearModel} with $\eta \leq \frac{1}{2} \varepsilon(\delta_1, \delta_2)$.
-Using the triangle inequality, it follows that any $n \times m$ matrix $\mathbf{B}$ and $k$-sparse $\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N$ solving Prob.~\ref{InverseProblem} are necessarily within $\delta_1$ and $\delta_2$ of the original dictionary $\mathbf{A}$ and codes $\mathbf{x}_1, \ldots, \mathbf{x}_N$, respectively.\footnote{We mention that the different norms in \eqref{def1} reflect the distinct meanings typically ascribed to the dictionary and sparse codes in modeling data.}
-
-The main result of this work is a very general uniqueness theorem for sparse coding (Thm.~\ref{DeterministicUniquenessTheorem}) directly 
-implying (Cor.~\ref{DeterministicUniquenessCorollary}), which guarantees that sparse representations of a dataset $Z$ are unique up to noise whenever generating dictionaries $\mathbf{A}$ satisfy a spark condition on supports and the original sparse codes $\mathbf{x}_i$ are sufficiently diverse (e.g., Fig.~\ref{noisyrecovery}).
-Moreover, we provide an explicit, computable $\varepsilon(\delta_1, \delta_2)$ in (\ref{epsdel}) that is linear in desired accuracy $\delta_1$, and essentially so in $\delta_2$.
-
-In the next section, we give formal statements of these findings.
-We then extend the same guarantees (Thm.~\ref{SLCopt}) to the following alternate formulation of dictionary learning, which minimizes the total number of nonzero entries in sparse codes.
-
-\begin{problem}\label{OptimizationProblem}
-Find matrices $\mathbf{B}$ and vectors \mbox{$\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N$} solving:
-\begin{align}\label{minsum}
-\min \sum_{i = 1}^N \|\mathbf{\overline x}_{i}\|_0 \ \
-\text{subject to} \ \ \|\mathbf{z}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \eta, \ \text{for all $i$}.
-\end{align}
-\end{problem}
-
-Our development of Thm.~\ref{DeterministicUniquenessTheorem} is general enough to provide some uniqueness and stability even when generating $\mathbf{A}$ do not fully satisfy (\ref{SparkCondition}) and recovery dictionaries $\mathbf{B}$ have more columns than $\mathbf{A}$.
-Moreover, the approach incorporates a theory of combinatorial designs for the sparse supports of generating codes $\mathbf{x}_i$ that should be of independent interest.
-We also give brief arguments adapting our results to dictionaries and codes drawn from probability distributions (Cor.~\ref{ProbabilisticCor}).
-The technical proofs of Thms.~\ref{DeterministicUniquenessTheorem} and ~\ref{SLCopt} are deferred to Sec.~\ref{DUT}, following some necessary definitions and a fact in combinatorial matrix analysis (Lem.~\ref{MainLemma}; proven in the Appendix).
-We discuss these results and their applications in depth in Sec.~\ref{Discussion} and outline open questions and directions for future research in Sec.~\ref{FutureDirections}.
-%The Appendix contains a proof of Lem.~\ref{MainLemma}.
+\begin{itemize}
+\item Indicate the gap in knowledge. State the aim of the research and how it fits into the gap.
+\item Outline what follows.
+\end{itemize}

### 2020-08-05 manuscripts/newthesis/proofs.tex
newthesis

--- 2019-05-10 manuscripts/IEEE/final_submission.tex
@@
-% TODO: 
-% Make L_H a definition..? Change def of L to be 1-norm so we don't need these sqrt k's?
-% C_1 depends on J in Thm 1
-% also in proof of (7) x need not be *any* 2k-sparse vector...can instead restrict to some H...then 2k is restricted to half being on H.
+\chapter{Proofs}
 
-% Notes:
-%
-% Can we prove in a line or two that the inverse problem is stable by arguing that the function is bijective and closed therefore a homeomorphism?
-% Should we mention the notion of Grassmannian manifolds and that Theta is a metric on this space?
-% Change robustness to stability?
-%
-\documentclass[journal, twocolumn]{IEEEtran}
+\section{Introduction}
 
-% *** MATH PACKAGES ***
-\usepackage{amsmath, amssymb, amsthm} 
-\newtheorem{theorem}{Theorem}
-\newtheorem{lemma}{Lemma}
-\newtheorem{conjecture}{Conjecture}
-\newtheorem{problem}{Problem}
-\newtheorem{question}{Question}
-\newtheorem{proposition}{Proposition}
-\newtheorem{definition}{Definition}
-\newtheorem{corollary}{Corollary}
-\newtheorem{remark}{Remark}
-\newtheorem{example}{Example}
+For pedagogical reasons we separate the proofs from the statements of results.
 
-\usepackage[pdftex]{graphicx}
-
-% *** ALIGNMENT PACKAGES ***
-\usepackage{array}
-\usepackage{cite}
-\usepackage{bm}
-
-% correct bad hyphenation here
-%\hyphenation{op-tical net-works semi-conduc-tor}
-
-\begin{document}
-
-%\title{When can a generating dictionary and sparse codes be recovered from noisy data?}
-%\title{When is the dictionary learning problem well-posed?}
-\title{On the uniqueness and stability of dictionaries \\ for sparse representation of noisy signals}
-%\title{When is the dictionary learning problem for sparse coding well-posed?}
-%\title{When is the sparsest representation unique?}
-%\title{When are sparse codes identifiable from their unknown noisy compressive measurements?}
-% FRITZ2: The title doesn't reflect the amount of new stuff, it seems incremental from the last one. It's not very meaningful.
-% FRITZ: Not everyone knows what well-posed means. You should mention recovery from noisy data in the title.
-
-\author{Charles~J.~Garfinkle and Christopher~J.~Hillar \\
-Redwood Center for Theoretical Neuroscience, Berkeley, CA, USA
-%\thanks{%e-mails: cjg@berkeley.edu, chillar@msri.org.  
-%CG and CH supported, in part, by NSF grant IIS-1219212 and the Statistical and Applied Mathematical Sciences Institute, under NSF DMS-1127914.}
-}
-
-\maketitle
-
-% \keywords{Sparse coding, dictionary learning, matrix factorization, compressed sensing, inverse problems, blind source separation}
-
-\begin{abstract}
-%Learning optimal dictionaries for sparse coding has exposed characteristic sparse features of many natural signals.
-However, there are few universal conditions guaranteeing the stability of such features in the presence of noise.
-Here, we prove very generally that optimal dictionaries and sparse codes are unique up to measurement error for all diverse enough datasets generated by the sparse coding model.
-Applications are given to data analysis, engineering, and neuroscience.
-Learning optimal dictionaries for sparse coding has exposed characteristic sparse features of many natural signals.
-However, universal guarantees of the stability of such features in the presence of noise are lacking.
-Here, we provide very general conditions guaranteeing when dictionaries yielding the sparsest encodings are unique and stable with respect to measurement or modeling error.
-We demonstrate that some or all original dictionary elements are recoverable from noisy data even if the dictionary fails to satisfy the spark condition, its size is overestimated, or only a polynomial number of distinct sparse supports appear in the data.
-Importantly, we derive these guarantees without requiring any constraints on the recovered dictionary beyond a natural upper bound on its size.
-Our results also yield an effective procedure sufficient to affirm if a proposed solution to the dictionary learning problem is unique within bounds commensurate with the noise.
-We suggest applications to data analysis, engineering, and neuroscience and close with some remaining challenges left open by our work.
-\end{abstract}
-
-% Optional adjustment to line up main text (after abstract) of first page with line numbers, when using both lineno and twocolumn options.
-% You should only change this length when you've finalised the article contents.
-
-\section{Introduction}\label{Intro}
-\IEEEPARstart{S}{parse} coding is a common modern approach to pattern analysis in signal processing whereby each of $N$ observed $n$-dimensional signal samples is viewed as a (noisy) linear combination of at most $k$ elementary waveforms drawn from some unknown ``dictionary" of size $m \ll N$ (see \cite{Zhang15} for a comprehensive review).
-%\IEEEPARstart{A}{}common modern approach to pattern analysis in signal processing is to view each of $N$ observed $n$-dimensional signal samples as a (noisy) linear combination of at most $k$ elementary waveforms drawn from some unknown ``dictionary" of size $m \ll N$ (see \cite{Zhang15} for a comprehensive review).
-Optimizing dictionaries subject to this and related sparsity constraints has revealed seemingly characteristic sparse structure in several signal classes of current interest (e.g., in vision \cite{wang2015sparse}).
-
-Of particular note are the seminal works in the field \cite{Olshausen96, hurri1996image, bell1997independent, van1998independent}, which discovered that dictionaries optimized for coding small patches of ``natural" images share qualitative similarities with linear filters estimated from response properties of simple-cell neurons in mammalian visual cortex.
-Curiously, these waveforms (e.g., ``Gabor'' wavelets) appear in dictionaries learned by a variety of algorithms trained over different natural image datasets, suggesting that learned features in natural signals may, in some sense, be canonical \cite{donoho2001can}.
-
-Motivated by these discoveries and more recent work relating compressed sensing \cite{eldar2012compressed} to a theory of information transmission through random wiring bottlenecks in the brain \cite{Isely10}, we address when dictionaries for sparse representation are indeed identifiable from data.
-Answers to this question may also have implications in practice wherever an appeal is made to latent sparse structure of data (e.g., forgery detection \cite{hughes2010, olshausen2010applied}; brain recordings \cite{jung2001imaging, agarwal2014spatially, lee2016sparse}; and gene expression \cite{wu2016stability}).
-
-While several algorithms have been recently proposed to provably recover unique dictionaries under specific conditions (see \cite[Sec.~I-E]{Sun16} for a summary of the state-of-the-art), few theorems can be invoked to justify the consistency of inference under this model of data more broadly.
-To our knowledge, a universal guarantee of the uniqueness and stability of learned dictionaries and the sparse representations they induce over noisy data has yet to appear in the literature.
-% in justifying the identification of forged paintings by their anomalous sparse representations \cite{hughes2010},
-
-Here, we prove very generally that uniqueness and stability is a typical property of sparse dictionary learning.
-More specifically, we show that matrices injective on a sparse domain are identifiable from \mbox{$N = m(k-1){m \choose k} + m$} noisy linear combinations of $k$ of their $m$ columns up to an error that is linear in the noise (Thm.~\ref{DeterministicUniquenessTheorem}).
-In fact, provided $n \geq \min(2k,m)$, in almost all cases the problem is well-posed, as per Hadamard \cite{Hadamard1902}, given a sufficient amount of data (Thm.~\ref{robustPolythm} and Cor.~\ref{ProbabilisticCor}).
-
-Our guarantees also hold for a related (and perhaps more commonly posed, e.g.
-\cite{rehnsommer2007}) optimization problem seeking a dictionary minimizing the average number of elementary waveforms required to reconstruct each sample of the dataset (Thm.~\ref{SLCopt}).
-To practical benefit, our results impose no restrictions on learned dictionaries (e.g., that they, too, be injective over some sparse domain) beyond an upper bound on dictionary size, which is necessary in any case to avoid trivial solutions (e.g., allowing $m = N$).
-%That is, every pair of solutions of comparable size has some number of dictionary elements in common (up to noise), and similarly so for the coefficients of sparse codes they induce.
-
-More precisely, let $\mathbf{A} \in \mathbb R^{n \times m}$ be a matrix with columns $\mathbf{A}_j$ ($j = 1,\ldots,m$) and let dataset $Z$ consist of measurements:
-\begin{align}\label{LinearModel}
-\mathbf{z}_i = \mathbf{A}\mathbf{x}_i + \mathbf{n}_i,\ \ \  \text{$i=1,\ldots,N$},
-\end{align}
-for $k$-\emph{sparse} $\mathbf{x}_i \in \mathbb{R}^m$ having at most $k<m$ nonzero entries and \emph{noise} $\mathbf{n}_i \in \mathbb{R}^n$, with bounded norm $\| \mathbf{n}_i \|_2 \leq  \eta$ representing our worst-case uncertainty in measuring the product $\mathbf{A}\mathbf{x}_i$.
-We first consider the following formulation of sparse coding.
-%The first mathematical problem we consider is the following.
-
-\begin{problem}\label{InverseProblem}
-Find a dictionary matrix $\mathbf{B}$ and $k$-sparse codes $\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N$ that satisfy $\|\mathbf{z}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \eta$ for all $i = 1,\ldots,N$.
-\end{problem}
-
-Note that every solution to Prob.~\ref{InverseProblem} represents infinitely many equivalent alternatives $\mathbf{BPD}$ and $\mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_1, \ldots, \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_N$ parametrized by a choice of permutation matrix $\mathbf{P}$ and invertible diagonal matrix $\mathbf{D}$.
-Identifying these ambiguities (labelling and scale) yields a single orbit of solutions represented by any particular set of elementary waveforms (the columns of $\mathbf{B}$) and their associated sparse coefficients (the entries of $\mathbf{\overline x}_i$) that reconstruct each data point $\mathbf{z}_i$.
-
-Previous theoretical work addressing the noiseless case $\eta =0$ (e.g., \cite{li2004analysis, Georgiev05, Aharon06, Hillar15}) for matrices $\mathbf{B}$ having exactly $m$ columns has shown that a solution to Prob.~\ref{InverseProblem}, when it exists, is unique up to such relabeling and rescaling provided the $\mathbf{x}_i$ are sufficiently diverse and $\mathbf{A}$ satisfies the \textit{spark condition}:
-\begin{align}\label{SparkCondition}
-\mathbf{A}\mathbf{x}_1 = \mathbf{A}\mathbf{x}_2 \implies \mathbf{x}_1 = \mathbf{x}_2, \ \ \ \text{for all $k$-sparse } \mathbf{x}_1, \mathbf{x}_2,
-\end{align}
-%
-which is necessary to guarantee the uniqueness of arbitrary $k$-sparse $\mathbf{x}_i$.
-We generalize these results to the practical setting  $\eta > 0$ by considering the following natural notion of stability with respect to measurement error.
-
-\begin{definition}\label{maindef}
-Fix $Y = \{ \mathbf{y}_1, \ldots, \mathbf{y}_N\} \subset \mathbb{R}^n$.
-We say $Y$ has a \textbf{$k$-sparse representation in $\mathbb{R}^m$} if there exists a matrix $\mathbf{A}$ and $k$-sparse $\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$ such that $\mathbf{y}_i = \mathbf{A}\mathbf{x}_i$ for all $i$.
-This representation is \textbf{stable} if for every $\delta_1, \delta_2 \geq 0$, there exists some $\varepsilon = \varepsilon(\delta_1, \delta_2)$ that is strictly positive for positive $\delta_1$ and $\delta_2$ such that if $\mathbf{B}$ and $k$-sparse $\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N \in \mathbb{R}^m$ satisfy:
-\begin{align*}
-	\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \varepsilon(\delta_1, \delta_2),\ \   \text{for all $i=1,\ldots,N$},
-\end{align*}
-then there is some permutation matrix $\mathbf{P}$ and invertible diagonal matrix $\mathbf{D}$ such that for all $i, j$:
-\begin{align}\label{def1}
-\|\mathbf{A}_j - (\mathbf{BPD})_j\|_2 \leq \delta_1 \ \text{and} \ \|\mathbf{x}_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_i\|_1 \leq \delta_2.
-\end{align}
-\end{definition}
-
-To see how Prob.
-\ref{InverseProblem} motivates Def.
-\ref{maindef}, suppose that $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$ and fix $\delta_1, \delta_2$ to be the desired accuracies of recovery in \eqref{def1}.
-Consider any dataset $Z$ generated as in \eqref{LinearModel} with $\eta \leq \frac{1}{2} \varepsilon(\delta_1, \delta_2)$.
-Using the triangle inequality, it follows that any $n \times m$ matrix $\mathbf{B}$ and $k$-sparse $\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N$ solving Prob.~\ref{InverseProblem} are necessarily within $\delta_1$ and $\delta_2$ of the original dictionary $\mathbf{A}$ and codes $\mathbf{x}_1, \ldots, \mathbf{x}_N$, respectively.\footnote{We mention that the different norms in \eqref{def1} reflect the distinct meanings typically ascribed to the dictionary and sparse codes in modeling data.}
-
-The main result of this work is a very general uniqueness theorem for sparse coding (Thm.~\ref{DeterministicUniquenessTheorem}) directly 
-implying (Cor.~\ref{DeterministicUniquenessCorollary}), which guarantees that sparse representations of a dataset $Z$ are unique up to noise whenever generating dictionaries $\mathbf{A}$ satisfy a spark condition on supports and the original sparse codes $\mathbf{x}_i$ are sufficiently diverse (e.g., Fig.~\ref{noisyrecovery}).
-Moreover, we provide an explicit, computable $\varepsilon(\delta_1, \delta_2)$ in (\ref{epsdel}) that is linear in desired accuracy $\delta_1$, and essentially so in $\delta_2$.
-
-In the next section, we give formal statements of these findings.
-We then extend the same guarantees (Thm.~\ref{SLCopt}) to the following alternate formulation of dictionary learning, which minimizes the total number of nonzero entries in sparse codes.
-
-\begin{problem}\label{OptimizationProblem}
-Find matrices $\mathbf{B}$ and vectors \mbox{$\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N$} solving:
-\begin{align}\label{minsum}
-\min \sum_{i = 1}^N \|\mathbf{\overline x}_{i}\|_0 \ \
-\text{subject to} \ \ \|\mathbf{z}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \eta, \ \text{for all $i$}.
-\end{align}
-\end{problem}
-
-Our development of Thm.~\ref{DeterministicUniquenessTheorem} is general enough to provide some uniqueness and stability even when generating $\mathbf{A}$ do not fully satisfy (\ref{SparkCondition}) and recovery dictionaries $\mathbf{B}$ have more columns than $\mathbf{A}$.
-Moreover, the approach incorporates a combinatorial theory for designing generating codes that should be of independent interest.
-We also give brief arguments adapting our results to dictionaries and codes drawn from probability distributions (Cor.~\ref{ProbabilisticCor}).
-The technical proofs of Thms.~\ref{DeterministicUniquenessTheorem} and ~\ref{SLCopt} are deferred to Sec.~\ref{DUT}, following some necessary definitions and a fact in combinatorial matrix analysis (Lem.~\ref{MainLemma}; proven in the Appendix).
-Finally, we discuss in Sec.~\ref{Discussion} applications of our mathematical observations as well as open questions.
-%The Appendix contains a proof of Lem.~\ref{MainLemma}.
-
-\section{Results}\label{Results}
-
-%Denote by $\mathbf{x}^J$ the subvector formed from the entries of $\mathbf{x}$ indexed by $J$. 
-%A set of $k$-sparse vectors is said to be in \emph{general linear position} when any $k$ of them are linearly independent.
-
-Precise statements of our results require that we first identify some combinatorial criteria on the supports\footnote{Recall that a vector $\mathbf{x}$ is said to be \emph{supported} in $S$ when $\mathbf{x} \in \text{\rm span}\{\mathbf{e}_j: j\in S\}$, with $\mathbf{e}_j$ forming the standard column basis.} of sparse vectors.
-Let $\{1, \ldots, m\}$ be denoted $[m]$, its power set $2^{[m]}$, and ${[m] \choose k}$ the set of subsets of $[m]$ of size $k$.
-A \emph{hypergraph} on vertices $[m]$  is simply any subset $\mathcal{H} \subseteq 2^{[m]}$.
-We say that $\mathcal{H}$ is \textit{$k$-uniform} when $\mathcal{H} \subseteq {[m] \choose k}$.
-The \emph{degree} $\deg_\mathcal{H}(i)$ of a node $i \in [m]$ is the number of sets in $\mathcal{H}$ that contain $i$, and we say $\mathcal{H}$ is \emph{regular} when for some $r$ we have $\deg_\mathcal{H}(i) = r$ for all $i$ (given such an $r$, we say $\mathcal{H}$ is \textit{$r$-regular}).
-We also write $2\mathcal{H} := \{ S \cup S': S, S' \in \mathcal{H}\}$.
-The following class of structured hypergraphs is a key ingredient in this work.
-
-\begin{definition}\label{sip}
-Given $\mathcal{H} \subseteq 2^{[m]}$, the \textbf{star} $\sigma(i)$ is the collection of sets in $\mathcal{H}$ containing $i$.
-We say $\mathcal{H}$ has the \textbf{singleton intersection property} (\textbf{SIP}) when $\cap \sigma(i) = \{i\}$ for all $i \in [m]$.
-\end{definition}
-
-We next give a quantitative generalization of the spark condition (\ref{SparkCondition}) to combinatorial subsets of supports.
-The \emph{lower bound} of an $n \times m$ matrix $\mathbf{M}$ is the largest $\alpha$ with \mbox{$\|\mathbf{M}\mathbf{x}\|_2 \geq \alpha\|\mathbf{x}\|_2$} for all $\mathbf{x} \in \mathbb{R}^m$ \cite{Grcar10}.
-By compactness of the unit sphere, every injective linear map has a positive lower bound; hence, if $\mathbf{M}$ satisfies \eqref{SparkCondition}, then submatrices formed from $2k$ of its columns or less have strictly positive lower bounds.
-
-The lower bound of a matrix is generalized below in (\ref{Ldef}) by restricting it to the spans of certain submatrices\footnote{See \cite{vidal2005generalized} for an overview of the related ``union of subspaces" model.} associated with a hypergraph $\mathcal{H} \subseteq {[m] \choose k}$ of column indices.
-Let $\mathbf{M}_S$ denote the submatrix formed by the columns of a matrix $\mathbf{M}$ indexed by $S \subseteq [m]$ (setting $\mathbf{M}_\emptyset := \mathbf{0}$).
-In the sections that follow, we shall also let $\bm{\mathcal{M}}_S$ denote the column-span of a submatrix $\mathbf{M}_S$, and $\bm{\mathcal{M}}_\mathcal{G}$ to denote $\{\bm{\mathcal{M}}_S\}_{S \in \mathcal{G}}$.
-We define:  % Define $L_\mathcal{H}(\mathbf{M})$ as follows:
-%\begin{align*} 
-%L_\mathcal{H}(\mathbf{M}) := \min \left\{ \frac{ \|\mathbf{M}(\mathbf{x}_1-\mathbf{x}_2)\|_2 }{ \sqrt{2k} \|\mathbf{x}_1-\mathbf{x}_2\|_2} : \mathbf{x}_1, \mathbf{x}_2 \in \cup_{S \in \mathcal{H}} \bm{\mathcal{M}}_S \right\},
-%\end{align*} 
-%
-%where we write $L_{2k}$ in place of $L_\mathcal{H}$ when $\mathcal{H} = {[m] \choose k}$.
-Note that if $\mathcal{H}$ covers $[m]$, then $L_2 > L_\mathcal{H}$.\footnote{The reader should beware that $L_2 = L_{[m]}$, whereas $L = L_{\{[m]\}}$.
-For even $k$, the quantity $1 - \sqrt{k} L_k(\mathbf{M})$ is also known in the compressed sensing literature as the (asymmetric) lower restricted isometry constant \cite{Blanchard2011}.} Clearly, for any $\mathbf{M}$ satisfying \eqref{SparkCondition}, we have $L_{k'}(\mathbf{M}) > 0$ for  $k' \leq 2k$.
-%\begin{align*}
-%L_\mathcal{H}(\mathbf{M}) := \min \left\{ \frac{ \|\mathbf{M}_S\mathbf{x}\|_2 }{ \sqrt{k} \|\mathbf{x}\|_2} : S \in \mathcal{H} \right\},
-%\end{align*} 
-%\begin{align*}
-%L_\mathcal{H}(\mathbf{M}) := \max \left\{ \ falpha: \|\mathbf{M}_S\mathbf{x}\|_2 \geq \alpha \sqrt{k} \|\mathbf{x}\|_2 : S \in \mathcal{H}, \ \ \mathbf{x} \in \mathbb{R}^m \right\},
-%\end{align*} 
-\begin{align}\label{Ldef}
-L_\mathcal{H}(\mathbf{M}) := \min \left\{ \frac{\|\mathbf{M}_S\mathbf{x}\|_2}{ \sqrt{k} \|\mathbf{x}\|_2} : S \in \mathcal{H}, \ \mathbf{0} \neq \mathbf{x} \in \mathbb{R}^{|S|} \right\},
-\end{align} 
-%
-writing also $L_{k}$ in place of $L_\mathcal{H}$ when $\mathcal{H} = {[m] \choose k}$.\footnote{In compressed sensing literature, \mbox{$1 - \sqrt{k} L_k(\mathbf{M})$}  is the asymmetric lower restricted isometry constant for $\mathbf{M}$ with unit $\ell_2$-norm columns \cite{Blanchard2011}.}  As explained above, compactness implies that $L_{2k}(\mathbf{M}) > 0$ for all $\mathbf{M}$ satisfying \eqref{SparkCondition}.
-Clearly, $L_{\mathcal{H}'}(\mathbf{M}) \geq L_\mathcal{H}(\mathbf{M})$ whenever $\mathcal{H}' \subseteq \mathcal{H}$, and similarly any $k$-uniform $\mathcal{H}$ satisfying $\cup \mathcal{H} = [m]$ has $L_2 \geq L_{2\mathcal{H}} \geq L_{2k}$ (letting $L_{2k}$ := $L_m$ whenever $2k > m$).
-
-We are now in a position to state our main result, though for expository purposes we leave the quantity $C_1$ %(a function of $\mathbf{A}$, $\mathbf{x}_1, \ldots, \mathbf{x}_N$, and $\mathcal{H}$) 
-undefined until Sec.~\ref{DUT}. All results  below assume real matrices and vectors.
-
-%eps-tightness COUNTER-EXAMPLE:
-%Consider the alternate dictionary $B = \left(\mathbf{0}, \frac{1}{2}(\mathbf{e}_1 + \mathbf{e}_2), \mathbf{e}_3, \ldots, \mathbf{e}_{m} \right)$ and sparse codes $\mathbf{b}_i = \mathbf{e}_2$ for $i = 1, 2$ and $\mathbf{b}_i = \mathbf{e}_i$ for $i = 3, \ldots, m$.
-Then $|A\mathbf{a}_i - B\mathbf{b}_i| = 1/\sqrt{2}$ for $i = 1, 2$ (and $0$ otherwise).
-If there were permutation and invertible diagonal matrices $P \in \mathbb{R}^{m \times m}$ and $D \in \mathbb{R}^{m \times m}$ such that $|(A-BPD)\mathbf{e}_i| \leq C\varepsilon$ for all $i \in [m]$, then we would reach the contradiction $1 = |P^{-1}\mathbf{e}_1|_2 = |(A-BPD)P^{-1}\mathbf{e}_1|_2 \leq 1/\sqrt{2}$.
-
-\begin{theorem}\label{DeterministicUniquenessTheorem}
-%Fix integers $n, k, m$ and $\overline m$. 
-If an $n \times m$ matrix $\mathbf{A}$ satisfies $L_{2\mathcal{H}}(\mathbf{A}) > 0$ for some $r$-regular $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP, and $k$-sparse \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} include more than $(k-1){\overline m \choose k}$ vectors in general linear position\footnote{Recall that a set of vectors sharing support $S$ are in \emph{general linear position} when any $|S|$ of them are linearly independent.} supported in each $S \in \mathcal{H}$, then the following recovery guarantees hold for $C_1 > 0$ given by \eqref{Cdef1}.
-
-\textbf{Dictionary Recovery:} Fix $\varepsilon < L_{2}(\mathbf{A}) / C_1$.\footnote{Note that the condition $\varepsilon < L_2(\mathbf{A}) /C_1$ is necessary; otherwise, with \mbox{$\mathbf{A}$ = $\mathbf{I}$} (the identity matrix) and $\mathbf{x}_i = \mathbf{e}_i$, the matrix $\mathbf{B} = \left[\mathbf{0}, \frac{1}{2}(\mathbf{e}_1 + \mathbf{e}_2), \mathbf{e}_3, \ldots, \mathbf{e}_{m} \right]$ and sparse codes $\mathbf{\overline x}_i = \mathbf{e}_2$ for $i = 1, 2$ and $\mathbf{\overline x}_i = \mathbf{e}_i$ for $i \geq 3$ satisfy $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline x}_i \|_2 \leq \varepsilon$ but nonetheless violate \eqref{Cstable}.} If an $n \times \overline m$ matrix $\mathbf{B}$ has, for every $i \in [N]$, an associated $k$-sparse $\mathbf{\overline x}_i$ satisfying \mbox{$\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \varepsilon$}, then $\overline m \geq m$, and provided that $\overline m (r-1) < mr$, there is a permutation matrix $\mathbf{P}$ and an invertible diagonal matrix $\mathbf{D}$ such that:
-\begin{align}\label{Cstable}
-\|\mathbf{A}_j- (\mathbf{BPD})_j\|_2 \leq C_1 \varepsilon, \ \ \text{for all } j \in J,
-\end{align}
-%
-for some $J \subseteq [m]$ of size \mbox{$m - (r-1)(\overline m - m)$}. 
-% $\overline m - r(\overline m - m)$
-
-\textbf{Code Recovery:} If, moreover, $\mathbf{A}_J$ satisfies \eqref{SparkCondition} and $\varepsilon < L_{2k}(\mathbf{A}_J) / C_1$, then $(\mathbf{BP})_J$ also satisfies \eqref{SparkCondition} with $L_{2k}(\mathbf{BP}_J) \geq (L_{2k}(\mathbf{A}_J) - C_1 \varepsilon) / \|\mathbf{D}_J\|_1$, and for all $i \in [N]$:
-\begin{align}\label{b-PDa}
-%\|\mathbf{x}^J_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}^{\overline J}_i\|_1 &\leq  \left( \frac{ 1+C_1 \|\mathbf{x}^{J}_i\|_1 }{ L_{2k}(\mathbf{A}) -  C_1\varepsilon } \right) \varepsilon \ \  \text{for $i \in [N]$}.
-\|(\mathbf{x}_i)_J - (\mathbf{D}^{-1}\mathbf{P}^{\top} \mathbf{\overline x}_i)_J\|_1 &\leq  \left( \frac{ 1+C_1 \|(\mathbf{x}_i)_J\|_1 }{ L_{2k}(\mathbf{A}_J) -  C_1\varepsilon } \right) \varepsilon,
-\end{align}
-%
-where subscript $(\cdot)_J$ here represents the subvector formed from restricting to coordinates indexed by $J$.
-\end{theorem}
-
-%We delay defining the explicit constant $C_1$ until Section \ref{DUT} (\eqref{Cdef1}).
-%To be clear, the implication of Thm.~\ref{DeterministicUniquenessTheorem} is that $Y = \{\mathbf{Ax}_1, \ldots, \mathbf{Ax}_N\}$ has a stable $k$-sparse representation in $\mathbb{R}^m$, with \eqref{def1} guaranteed provided $\varepsilon$ in Def.~\ref{maindef} does not exceed:
-In words, Thm.~\ref{DeterministicUniquenessTheorem} says that the smaller the regularity $r$ of the original support hypergraph $\mathcal{H}$ or the difference $\overline m - m$ between the assumed and actual number of elements in the latent dictionary, the more columns and coefficients of the original dictionary $\mathbf{A}$ and sparse codes $\mathbf{x}_i$ are guaranteed to be contained (up to noise) in the appropriately labelled and scaled recovered dictionary $\mathbf{B}$ and codes $\mathbf{\overline x}_i$, respectively.
-
-In the important special case when $\overline m = m$, the theorem directly implies that  $Y = \{\mathbf{Ax}_1, \ldots, \mathbf{Ax}_N\}$ has a stable $k$-sparse representation in $\mathbb{R}^m$, with inequalities \eqref{def1} guaranteed in Def.~\ref{maindef} for the following worst-case error $\varepsilon$:
-\begin{align}\label{epsdel}
-\varepsilon(\delta_1, \delta_2) := \min \left\{ \frac{\delta_1}{ C_1 }, \frac{ \delta_2 L_{2k}(\mathbf{A})}{ 1 + C_1 \left( \delta_2 + \max_{i \in [N]} \|\mathbf{x}_i\|_1  \right) } \right\}.
-\end{align}
-
-Since sparse codes in general linear position are straightforward to produce with a ``Vandermonde''  construction (i.e., by choosing columns of the matrix $[\gamma_{i}^j]_{i,j=1}^{k,N}$, for distinct nonzero $\gamma_i$), we have the following direct consequence of Thm.~\ref{DeterministicUniquenessTheorem}.
-
-\begin{corollary}\label{DeterministicUniquenessCorollary}
-Given any regular hypergraph $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP, there are $N =  |\mathcal{H}| \left[ (k-1){m \choose k} + 1  \right]$ vectors \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} such that every matrix $\mathbf{A}$ satisfying spark condition \eqref{SparkCondition} generates $Y = \{\mathbf{A}\mathbf{x}_1, \ldots, \mathbf{A}\mathbf{x}_N\}$ with a stable $k$-sparse representation in $\mathbb{R}^m$ for $\varepsilon(\delta_1,\delta_2)$ given by \eqref{epsdel}.
-\end{corollary}
-
-% prev
-%\begin{corollary}\label{DeterministicUniquenessCorollary}
-%Given any regular hypergraph $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP, there are $N =  |\mathcal{H}| \left[ (k-1){m \choose k} + 1  \right]$ vectors \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} such that every matrix $\mathbf{A}$ with $L_{2\mathcal{H}}(\mathbf{A}) > 0$ generates a dataset $Y = \{\mathbf{A}\mathbf{x}_1, \ldots, \mathbf{A}\mathbf{x}_N\}$ with a stable $k$-sparse representation in $\mathbb{R}^m$ for $\varepsilon(\delta_1,\delta_2)$ as in \eqref{epsdel}.
-%\end{corollary}
-
-%We claim that the assumptions of Thm.~\ref{DeterministicUniquenessTheorem} are easily met with deterministic constructions.
-In particular, sparse codes in general linear position are straightforward to produce using a ``Vandermonde'' matrix construction (i.e.
-use the columns of the matrix $[\gamma_{i}^j]_{i,j=1}^{k,N}$, for distinct nonzero $\gamma_i$).
-%
-
-% (Prob.~\ref{InverseProblem}).
-%=======
-%An immediate practical implication of this result is that there exists a practical procedure to affirm if one's proposed solution $(\mathbf{B}, \mathbf{\overline x}_1, \ldots, \mathbf{x}_N)$ to Prob.~\ref{InverseProblem} is indeed unique (up to noise and inherent ambiguities): simply check that $\mathbf{B}$ and the $\mathbf{\overline x}_i$ satisfy the assumptions on $\mathbf{A}$ and the $\mathbf{x}_i$ in Thm.~\ref{DeterministicUniquenessTheorem}.
-%
-%%In fact, a more general result (stated clearly in the next section) can be gleaned from our method of proving Thm.~\ref{DeterministicUniquenessTheorem}.
-Briefly, in cases where $\mathbf{B}$ has $\overline m \neq m$ columns, or $\mathcal{H}$ is not regular or only partially satisfying the SIP, a relation between $\overline m$ and the degree sequence of nodes in $\mathcal{H}$ gives indices $J \subseteq [m]$ defining a submatrix $\mathbf{A}_J$ and subvectors $\mathbf{x}_i^J$ that are recoverable in the sense of \eqref{Cstable} and \eqref{b-PDa}.
-For example, if $\mathcal{H}$ is $\ell$-regular with the SIP but $m \leq \overline m < m\ell/(\ell - 1)$ then we have nonzero $|J| = \overline m - \ell(\overline m - m)$.
-The implication here is that the smaller the difference $\overline m - m$, the more columns and code entries of the original $n \times m$ dictionary $\mathbf{A}$ and codes $\mathbf{x}_i$ contained (up to noise) in the appropriately scaled $n \times \overline m$ dictionary $\mathbf{B}$ and codes $\mathbf{\overline x}_i$.
-When $\overline m = m$, we recover Thm.~\ref{DeterministicUniquenessTheorem}.
-%
-%%In fact, even if $\mathcal{H}$ is not regular or only partially satisfies the SIP, a relation between $\overline m$ and the degree sequence of nodes in $\mathcal{H}$ may give the indices $J \subseteq [m]$.
-For sake of brevity, we delay to the next section a clear statement of this more general result.
-%
-%Regarding the assumptions of Thm.~\ref{DeterministicUniquenessTheorem}, it so happens that sparse codes $\mathbf{x}_i$ in general linear position are straightforward to produce with a ``Vandermonde'' matrix construction \cite{Hillar15}, leading to the following.
-%>>>>>>> d1407a275dc391dabad7bb62d3e659f9a4ac4624
-
-% Needs to be L_{2k}(A) > 0 to guarantee sparse vector recovery
-
-%We also have the following refinement of a result in \cite{Hillar15}:
-%\begin{corollary}
-%Those square matrices $\mathbf{A}$ that satisfy \mbox{$L_{2\mathcal{H}}(\mathbf{A}) > 0$} for some regular $k$-uniform hypergraph $\mathcal{H}$ with the SIP and have the property that $\mathbf{Ax}$ is $k$-sparse for all $k$-sparse $\mathbf{x}$ with support in $\mathcal{H}$ are the matrices $\mathbf{PD}$, where $\mathbf{P}$ and $\mathbf{D}$ run over permutation and invertible diagonal matrices, respectively.
-%\end{corollary}
-
-One can easily verify that for every $k < m$ there are regular $k$-uniform hypergraphs $\mathcal{H}$ with the SIP besides the obvious $\mathcal{H} = {[m] \choose k}$.
-For instance, take $\mathcal{H}$ to be the $k$-regular set of consecutive intervals of length $k$ in some cyclic order on $[m]$.
-In this case, a direct consequence of Cor.~\ref{DeterministicUniquenessCorollary} is rigorous verification of the lower bound \mbox{$N = m(k-1){m \choose k} + m$} for sufficient sample size from the introduction.
-Special cases allow for even smaller hypergraphs.
-For example, if $k = \sqrt{m}$, then a 2-regular $k$-uniform hypergraph with the SIP can be constructed as the $2k$ rows and columns formed by arranging the elements of $[m]$ into a square grid.
-
-%\cite{li2004analysis, Georgiev05, Aharon06, Hillar15}
-We should stress here that framing the problem in terms of hypergraphs has allowed us to show, unlike in previous research on the subject, that the matrix $\mathbf{A}$ need not necessarily satisfy \eqref{SparkCondition} to be recoverable from data.
-As an example, let $\mathbf{A} = [ \mathbf{e}_1, \ldots, \mathbf{e}_5, \mathbf{v}]$ with $\mathbf{v} = \mathbf{e}_1 + \mathbf{e}_3 + \mathbf{e}_5$ and take $\mathcal{H}$ to be all consecutive pairs of indices $1, \ldots ,6$ arranged in cyclic order.
-Then for $k=2$, the matrix $\mathbf{A}$ fails to satisfy \eqref{SparkCondition} while still obeying the assumptions of Thm.~\ref{DeterministicUniquenessTheorem} for dictionary recovery.%, hence guaranteeing \eqref{Cstable} .
-%(since $\{ \mathbf{A}_1, \mathbf{A}_3, \mathbf{A}_5, \mathbf{A}_6\}$ is not a linearly independent set).
-%This weakening allows for a practical (polynomial) amount of data to still guarantee a stable dictionary in the case where the set of sparse supports for the $\mathbf{\overline x}_i$ is known to have a size that grows polynomially in $m$ and $k$.
-
-A practical implication of Thm.~\ref{DeterministicUniquenessTheorem} is the following: there is an effective procedure sufficient to affirm if a proposed solution to Prob.~\ref{InverseProblem} is indeed unique (up to noise and inherent ambiguities).
-One need simply check that the matrix and codes satisfy the (computable) assumptions of Thm.~\ref{DeterministicUniquenessTheorem} on $\mathbf{A}$ and the $\mathbf{x}_i$.
-In general, however, there is no known efficient procedure.
-We defer a brief discussion on this point to the next section.
-%Another practical implication of Thm.\ref{DeterministicUniquenessTheorem} is the following: there is an effective procedure sufficient to affirm if a proposed solution $(\mathbf{B}, \mathbf{\overline x}_1, \ldots, \mathbf{x}_N)$ to Prob.~\ref{InverseProblem} is indeed unique (up to noise and inherent ambiguities).
-One simply checks that $\mathbf{B}$ and the $\mathbf{\overline x}_i$ satisfy the respective assumptions of Thm.~\ref{DeterministicUniquenessTheorem}.
-%. on $\mathbf{A}$ and the $\mathbf{x}_i$, respectively.
-
-%In fact, a more general result (stated clearly in the next section) can be gleaned from our method of proving Thm.~\ref{DeterministicUniquenessTheorem}.
-Briefly, in cases where $\mathbf{B}$ has $\overline m \neq m$ columns, or $\mathcal{H}$ is not regular or only partially satisfying the SIP, a relation between $\overline m$ and the degree sequence of nodes in $\mathcal{H}$ gives indices $J \subseteq [m]$ defining a submatrix $\mathbf{A}_J$ and subvectors $\mathbf{x}_i^J$ that are recoverable in the sense of \eqref{Cstable} and \eqref{b-PDa}.
-For example, if $\mathcal{H}$ is $\ell$-regular with the SIP but $m \leq \overline m < m\ell/(\ell - 1)$ then we have nonzero $|J| = \overline m - \ell(\overline m - m)$.
-The implication here is that the smaller the difference $\overline m - m$, the more columns and code entries of the original $n \times m$ dictionary $\mathbf{A}$ and codes $\mathbf{x}_i$ contained (up to noise) in the appropriately scaled $n \times \overline m$ dictionary $\mathbf{B}$ and codes $\mathbf{\overline x}_i$.
-When $\overline m = m$, we recover Thm.~\ref{DeterministicUniquenessTheorem}.
-
-%In fact, even if $\mathcal{H}$ is not regular or only partially satisfies the SIP, a relation between $\overline m$ and the degree sequence of nodes in $\mathcal{H}$ may give the indices $J \subseteq [m]$.
-For sake of brevity, we delay to the next section a clear statement of this more general result.
-
-%=======
-%One can also verify that for every $k < m$, there is a regular $k$-uniform hypergraph that satisfies the SIP; for instance, take $\mathcal{H}$ to be the consecutive intervals of length $k$ in some cyclic order on $[m]$, for which Cor.~\ref{DeterministicUniquenessCorollary} implies the lower bound for sample size $N$ from the introduction.
-In many cases, however, the SIP is achievable with far fewer supports; for example, when $k = \sqrt{m}$, take $\mathcal{H}$ to be the $2k$ rows and columns formed by arranging $[m]$ in a square grid.
-%>>>>>>> d1407a275dc391dabad7bb62d3e659f9a4ac4624
-
-%As mentioned above, there exist $k$-uniform regular hypergraphs $\mathcal{H}$ with the SIP having cardinality $|\mathcal{H}| = m$,
-
-A less direct consequence of Thm.~\ref{DeterministicUniquenessTheorem} is the following uniqueness and stability guarantee for solutions to Prob.~\ref{SLCopt}.
-%, the usual optimization problem of interest for those applying dictionary learning to their data.
-
-\begin{theorem}\label{SLCopt}
-Fix a matrix $\mathbf{A}$ and vectors $\mathbf{x}_i$ satisfying the assumptions of Thm.~\ref{DeterministicUniquenessTheorem}, only now with over \mbox{$(k-1)\left[ {\overline m \choose k} + |\mathcal{H}|k{\overline m \choose k-1}\right]$} vectors supported in general linear position in each $S \in \mathcal{H}$.
-Every solution to Prob.~\ref{OptimizationProblem} (with $\eta = \varepsilon/2$) satisfies recovery guarantees \eqref{Cstable} and \eqref{b-PDa} when the corresponding bounds on $\eta$ are met.
-\end{theorem}
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=.24 \linewidth]{figs/basis.png}
-% \includegraphics[width=.25 \linewidth]{figs/Ahat_FastICA_M640_K8_noise0_2042}
-%\includegraphics[width=.24 \linewidth]{figs/Ahat_FastICA_M640_K8_noise0_4083.png}
-\includegraphics[width=.24 \linewidth]{figs/Ahat_FastICA_M640_K8_noise1_0205.png}
-\includegraphics[width=.24 \linewidth]{figs/Ahat_FastICA_M640_K8_noise2_0409.png}
-\includegraphics[width=.24 \linewidth]{figs/Ahat_FastICA_M640_K8_noise5_1021.png}
-\caption{\textbf{Learning a dictionary from increasingly noisy data}.
-The (unraveled) basis elements of the $8 \times 8$ discrete cosine transform (DCT) form the 64 columns of the left-most matrix above.
-Three increasingly imprecise dictionaries (columns reordered to best match original) are recovered by FastICA \cite{hyvarinen2000independent} trained on data generated from $8$-sparse linear combinations of DCT elements corrupted with additive noise (increasing from left to right).}
-\vspace{-.6 cm}
-\label{noisyrecovery}
-\end{center}
-\end{figure}
-
-Another extension of Thm.~\ref{DeterministicUniquenessTheorem} can be derived from the following algebraic characterization of the spark condition.
-Letting $\mathbf{A}$ be the $n \times m$ matrix of $nm$ indeterminates $A_{ij}$, the reader may work out why substituting real numbers for the $A_{ij}$ yields a matrix satisfying \eqref{SparkCondition} if and only if the following polynomial evaluates to a nonzero number:
-\begin{align*}
-f(\mathbf{A}) := \prod_{S \in {[m] \choose 2k}} \sum_{S' \in {[n] \choose 2k}} (\det \mathbf{A}_{S',S})^2,
-\end{align*}
-%
-where for any $S' \in {[n] \choose 2k}$ and $S \in {[m] \choose 2k}$, the symbol $\mathbf{A}_{S',S}$ denotes the submatrix of entries $A_{ij}$ with $(i,j) \in S' \times S$.\footnote{The large number of terms in this product is likely necessary given that deciding whether or not a matrix satisfies the spark condition is NP-hard \cite{tillmann2014computational}.}
-
-Since $f$ is analytic, having a single substitution of a real matrix $\mathbf{A}$ satisfying $f(\mathbf{A}) \neq 0$ implies that the zeroes of $f$ form a set of (Borel) measure zero.
-Such a matrix is easily constructed by adding rows of zeroes to a $\min(2k,m) \times m$ Vandermonde matrix as mentioned previously, so that every sum in the product defining $f$ above is strictly positive.
-Thus, almost every $n \times m$ matrix with $n \geq \min(2k,m)$ satisfies \eqref{SparkCondition}.
-
-%Another extension of Thm.~\ref{DeterministicUniquenessTheorem} arises from the following analytic characterization of the spark condition.
-Let $\mathbf{A}$  be the $n \times m$ matrix of $nm$ indeterminates $A_{ij}$.
-When real numbers are substituted for $A_{ij}$, the resulting matrix satisfies \eqref{SparkCondition} if and only if the following polynomial is nonzero:
-%\begin{align*}
-%f(\mathbf{A}) := \prod_{S \in {[m] \choose k}} \sum_{S' \in {[n] \choose k}} (\det \mathbf{A}_{S',S})^2,
-%\end{align*}
-%
-%where for any $S' \in {[n] \choose k}$ and $S \in {[m] \choose k}$, the symbol $\mathbf{A}_{S',S}$ denotes the submatrix of entries $A_{ij}$ with $(i,j) \in S' \times S$.
-We note that the large number of terms in this product is likely necessary due to the NP-hardness of deciding whether a given matrix $\mathbf{A}$ satisfies the spark condition \cite{tillmann2014computational}.
-
-%Since $f$ is analytic, having a single substitution of a real matrix $\mathbf{A}$ with $f(\mathbf{A}) \neq 0$ necessarily implies that the zeroes of $f$ form a set of measure zero.
-Fortunately, such a matrix $\mathbf{A}$ is easily constructed by adding rows of zeroes to any $\min(2k,m) \times m$ Vandermonde matrix as described above (so that each term in the product above for $f$ is nonzero).
-Hence, almost every $n \times m$ matrix with $n \geq \min(2k,m)$ satisfies \eqref{SparkCondition}.
-
-We claim that a similar phenomenon applies to datasets of vectors with a stable sparse representation.
-Briefly, following the same procedure as in \cite[Sec.~IV]{Hillar15}, for $k < m$ and $n \geq \min(2k, m)$, we may consider the ``symbolic'' dataset $Y = \{\mathbf{A}\mathbf{x}_1,\ldots,\mathbf{A} \mathbf{x}_N\}$ generated by an indeterminate $n \times m$ matrix $\mathbf{A}$ and $m$-dimensional $k$-sparse vectors $\mathbf{x}_1, \ldots, \mathbf{x}_N$ indeterminate within their supports, which form a regular hypergraph $\mathcal{H} \subseteq {[m] \choose k}$ satisfying the SIP.
-Restricting \mbox{$(k-1){m \choose k} + 1$} indeterminate $\mathbf{x}_i$ to each support in $\mathcal{H}$, and letting $\textbf{M}$ be the $n \times N$ matrix with columns $\mathbf{A}\mathbf{x}_i$, it can be checked that when $f(\mathbf{M}) \neq 0$ for a substitution of real numbers for the indeterminates, all of the assumptions on $\mathbf{A}$ and the $\mathbf{x}_i$ in Thm.~\ref{DeterministicUniquenessTheorem} are satisfied.
-We therefore have the following.
-% ; in particular, $\mathbf{A}$ satisfies \eqref{SparkCondition}
-
-\begin{theorem}\label{robustPolythm}
-%Let $\mathbf{A}$ and $\mathbf{x}_1, \ldots, \mathbf{x}_N$ be an indeterminate $n \times m$ matrix and sequence of $m$-dimensional vectors, respectively. 
-There is a polynomial in the entries of $\mathbf{A}$ and the $\mathbf{x}_i$ that evaluates to a nonzero number only when $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$.
-In particular, almost all substitutions impart to $Y$ this property.
-\end{theorem}
-
-%To extend this observation to arbitrary probability distributions, note that if a set of measure spaces $\{(X_{\ell}, \nu_{\ell})\}_{\ell=1}^p$ has measures $\nu_{\ell}$ absolutely continuous with respect to the standard Borel measure on $\mathbb{R}$ for all $\ell \in [p]$, then the product measure $\prod_{\ell=1}^p \nu_{\ell}$ is also absolutely continuous with respect to the standard Borel product measure on $\mathbb{R}^p$ (e.g., see \cite{folland2013real}).
-This fact combined with Thm.~\ref{robustPolythm} implies the following.
-To extend this observation to arbitrary probability distributions, note that if a set of $p$ measure spaces has all measures absolutely continuous with respect to the standard Borel measure on $\mathbb{R}$, then the product measure is also absolutely continuous with respect to the standard Borel product measure on $\mathbb{R}^p$ (e.g., see \cite{folland2013real}).
-This fact combined with Thm.~\ref{robustPolythm} implies the following.\footnote{We refer the reader to \cite{Hillar15} for a more detailed explanation of these arguments.}
-
-\begin{corollary}\label{ProbabilisticCor}
-If the indeterminate entries of $\mathbf{A}$ and the $\mathbf{x}_i$ are drawn independently from probability distributions absolutely continuous with respect to the standard Borel measure, then $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$ with probability one.
-\end{corollary}
-
-Thus, drawing the dictionary and supported sparse coefficients from any continuous probability distribution almost always generates data with a stable sparse representation.
-
-%\cite{rehnsommer2007, rozell2007neurally, ganguli2012compressed, hu2014hebbian}
-
-We close this section with some comments on the optimality of our results.
-The linear scaling for $\varepsilon$ in \eqref{epsdel} is essentially optimal (e.g., see \cite{arias2013fundamental}), but a basic open problem remains: how many samples are necessary to determine the sparse coding model?
-Our results demonstrate that sparse codes $\mathbf{x}_i$ drawn from only a polynomial number of $k$-dimensional subspaces permit stable identification of the generating dictionary $\mathbf{A}$. 
-This lends some legitimacy to the use of the model in practice, where data in general are unlikely (if ever) to exhibit the exponentially many possible $k$-wise combinations of dictionary elements required by (to our knowledge) all previously published results.
-
-Consequently, if $k$ is held fixed or if the size of the support set of reconstructing codes is polynomial in $\overline m$ and $k$, then a practical (polynomial) amount of data suffices to identify the dictionary.\footnote{In the latter case, a reexamination of the pigeonholing argument in the proof of Thm.~\ref{DeterministicUniquenessTheorem} requires a polynomial number of samples distributed over a polynomial number of supports.} Reasons to be skeptical that this holds in general, however, can be found in \cite{tillmann2014computational, Tillmann15}.
-Even so, in the next section we discuss how probabilistic guarantees can in fact be made for any number of available samples.
-
-\section{Proofs}\label{DUT} % of Theorems~\ref{DeterministicUniquenessTheorem} and ~\ref{SLCopt}}\label{DUT}
+\section{Proof of Theorem~\ref{DeterministicUniquenessTheorem} }\label{DUT} % of Theorems~\ref{DeterministicUniquenessTheorem} and ~\ref{SLCopt}}\label{DUT}
 
@@
 Given insufficient samples, this argument has some less-than-certain probability of being valid for each $S \in \mathcal{H}$.
-Nonetheless, simulations with small hypergraphs confirm that the probability of success very quickly approaches one once the number of samples $N$ surpasses a small fraction of the deterministic sample complexity.
+Nonetheless, simulations with small hypergraphs demonstrate that successful recovery is nearly certainly even when $N$ is only a fraction of the deterministic sample complexity (see Fig.
+\ref{probpigeon}).
+
+\section{Proof of Theorem~\ref{SLCopt}}
 
@@
 
-%\begin{proof}[Proof (sketch) of Thm.~\ref{robustPolythm}]
-%Let $\textbf{M}$ be the matrix with columns $\mathbf{A}\mathbf{x}_i$, $i \in [N]$.
-Consider the polynomial $\prod_{S \in {[N] \choose 2k}} \sum_{S' \in {[n] \choose 2k}} (\det \textbf{M}_{S',S})^2$ in the indeterminate entries of $\mathbf{A}$ and $\mathbf{x}_i$, with notation as in Sec.~\ref{Results}.
-%It can be checked that when this polynomial is nonzero for a substitution of real numbers for the indeterminates, all of the genericity requirements on $\mathbf{A}$ and $\mathbf{x}_i$ in our proofs of stability in Thm.~\ref{DeterministicUniquenessTheorem} are satisfied (in particular, the spark condition \eqref{SparkCondition} on $\mathbf{A}$).
-%\end{proof}
+\section{Discussion}
 
-%\begin{proof}[Proof (sketch) of Cor.~\ref{ProbabilisticCor}]
-%First, note that if a set of measure spaces $\{(X_{\ell}, \Sigma_{\ell}, \nu_{\ell})\}_{\ell=1}^p$ has that $\nu_{\ell}$ is absolutely continuous with respect to $\mu$ for all $\ell \in [p]$, where $\mu$ is the standard Borel measure on $\mathbb{R}$, then the product measure $\prod_{\ell=1}^p \nu_{\ell}$ is absolutely continuous with respect to the standard Borel product measure on $\mathbb{R}^p$.
-% for space:  (e.g.,  \cite{folland2013real}).
-%By Thm.~\ref{robustPolythm}, there is a polynomial that is nonzero when $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$; in particular, stability holds almost surely.
-%\end{proof}
-
-\section{Discussion}\label{Discussion}
-
-A main motivation for this work is the emergence of seemingly unique representations from sparse coding models trained on natural data, despite the varied assumptions underlying the many algorithms in current use.
-Our results constitute an important step toward explaining these phenomena as well as unifying many publications on the topic by deriving general deterministic conditions under which identification of parameters in this model is not only possible but also robust to uncertainty in measurement and model choice.
-
-We have shown that, given sufficient data, the problem of determining a dictionary and sparse codes with minimal support size (Prob.~\ref{OptimizationProblem}) reduces to an instance of Prob.~\ref{InverseProblem}, to which our main result (Thm.~\ref{DeterministicUniquenessTheorem}) applies: every dictionary and sequence of sparse codes consistent with the data are equivalent up to inherent relabeling/scaling ambiguities and a discrepancy (error) that scales linearly with the measurement noise or modeling inaccuracy.
-The constants we provide are explicit and computable; as such, there is an effective procedure that sufficiently affirms if a proposed solution to these problems is indeed unique up to noise and inherent ambiguities, although it is not efficient in general.
-
-%A compelling feature of this model is its simple instantiation of the principle of Occam's razor: a natural video, for instance, is modeled as a linear combination of a small number of spatiotemporal building blocks, each representing an archetypical feature latent in the data.
-
-%For theoretical neuroscience in particular, dictionary learning and related methods have recovered characteristic components of natural images \cite{Olshausen96, hurri1996image, bell1997independent, van1998independent} and sounds \cite{bellsejnowski1996, smithlewicki2006} that reproduce response properties of certain cortical neurons.
-
-%to the recovery of ``mouse neuronal activity representing location on a track \cite{agarwal2014spatially}
-
-%Moreover, we show that even if the meta-parameter for the number of dictionary elements is overestimated, a subset of parameters may still be identifiable up to noise.
-
-Beyond an extension of existing noiseless guarantees \cite{Hillar15} to the noisy regime and their novel application to Prob.~\ref{OptimizationProblem}, our work contains a theory of combinatorial designs for support sets key to identification of dictionaries.
-We incorporate this idea into a fundamental lemma in matrix theory (Lem.~\ref{MainLemma}) that draws upon the definition of a matrix lower bound (\ref{Ldef}) induced by a hypergraph.
-The new insight offered by this combinatorial approach allows for guaranteed recovery of some or all dictionary elements even if: 1) dictionary size is overestimated, 2) data cover only a polynomial number of distinct sparse supports, and 3) dictionaries do not satisfy the spark condition.
-
-The absence of any assumptions about dictionaries solving Prob.~\ref{InverseProblem} was a major technical obstruction in proving Thm.~\ref{DeterministicUniquenessTheorem}.
-We sought such a general guarantee because of the practical difficulty in ensuring that an algorithm maintain a dictionary satisfying the spark condition \eqref{SparkCondition} at each iteration, an implicit requirement of all previous works except \cite{Hillar15}; indeed, even certifying a dictionary has this property is NP-hard \cite{tillmann2014computational}.
-
-One direct application of this work is to theoretical neuroscience, wherein our theorems justify the mathematical soundness of one of the few hypothesized theories of bottleneck communication in the brain \cite{Isely10}: that sparse neural population activity is recoverable from its noisy linear compression through a randomly constructed (but unknown) wiring bottleneck by any biologically plausible unsupervised sparse coding method that solves Prob.~\ref{DeterministicUniquenessTheorem} or \ref{SLCopt} (e.g., \cite{rehnsommer2007, rozell2007neurally, pehlevan2015normative}).\footnote{We refer the reader to \cite{ganguli2012compressed} for more on interactions between dictionary learning and neuroscience.}
-
-In fact, uniqueness guarantees with minimal assumptions apply to all areas of data science and engineering that utilize learned sparse structure.
-For example, several groups have applied compressed sensing to signal processing tasks; for instance, in MRI analysis \cite{lustig2008compressed}, image compression \cite{Duarte08}, and even the design of an ultrafast camera \cite{Gao14}.
-It is only a matter of time before these systems incorporate dictionary learning to encode and decode signals (e.g., in a device that learns structure from motion \cite{kong2016prior}), just as scientists have used sparse coding to make sense of their data \cite{jung2001imaging, agarwal2014spatially, lee2016sparse, wu2016stability}.
-
-Assurances offered by our theorems certify that different devices and algorithms learn equivalent representations given enough data from statistically identical systems.\footnote{To contrast with the current hot topic of ``Deep Learning'', there are few such uniqueness guarantees for these models of data; moreover, even small noise can dramatically alter their output \cite{goodfellow2014explaining}.}
-Indeed, a main reason for the sustained interest in dictionary learning as an unsupervised method for data analysis seems to be the assumed well-posedness of parameter identification in the model, confirmation of which forms the core of our findings.
-
-We close with some challenges left open by our work.
-All conditions stated here guaranteeing the uniqueness and stability of sparse representations have only been shown sufficient; it remains open, therefore, to extend them to necessary conditions, be they on required sample size, the structure of support set hypergraphs, or tolerable error bounds.
-On this last note, we remark that our deterministic treatment considers always the ``worst-case" noise, whereas the ``effective" noise sampled from a concentrated distribution might be significantly reduced, especially for high-dimensional data.
-It would be of great practical benefit to see how drastically all conditions can be relaxed by requiring only probabilistic guarantees in this way, or in the spirit of our discussion on probabilistic pigeonholing to reduce sample complexity (as in the famous ``birthday paradox") following the proof of Thm.~\ref{DeterministicUniquenessTheorem}.
-
-Another interesting question raised by our work is for which special cases is it efficient to check that a solution to Prob.~\ref{InverseProblem} or \ref{OptimizationProblem} is unique up to noise and inherent ambiguities.
-Considering that the sufficient conditions we have described for checking this in general are NP-hard to compute, are the necessary conditions hard?
-Are Probs.~\ref{InverseProblem} and \ref{OptimizationProblem} then also hard (e.g., see \cite{Tillmann15})?
-Finally, since Prob.~\ref{SLCopt} is intractable in general, but efficiently solvable by $\ell_1$-norm minimization when the matrix is known (and has a large enough lower bound over sparse domains \cite{eldar2012compressed}), is there a version of Thm.~\ref{SLCopt} certifying when Prob.~\ref{OptimizationProblem} can be solved efficiently in full by similar means?
-% [*** Incorporate this open problem with more words ***]
-
-We hope these remaining challenges pique the interest of the community to pick up where we have left off and that the theoretical tools showcased here may be of use to this end.
-
-%We close with some challenges left open by our work.
-First, there is the basic problem of proving optimal lower bounds on sufficient sample size $N$ guaranteeing the uniqueness and stability of sparse representations.
-The pigeonholing argument in the proof of Thm.~\ref{DeterministicUniquenessTheorem} is loose in that it assigns to each support $S \in \mathcal{H}$ a corresponding support $\overline S$ without consideration of previously matched pairs; although we doubt tightening in this way will lead to sub-exponential sample sizes.
-Sample complexity will also benefit from lowering the number of required supports, i.e.
-the size of regular uniform hypergraphs satisfying the SIP.
-The regularity requirement on support hypergraphs can be loosened to allow for certain non-regular hypergraphs satisfying constraints on the degree sequence of nodes; though we impose regularity for clarity of exposition.
-It is then natural to ask: what is the smallest hypergraph satisfying the required constraints forgiven $m$ and $k$?
-Finally, the error bounds can be improved by tightening the constant $C_1$, e.g.
-via an improvement in Lemma ?.
-
-%Solving Prob.~\ref{SLCopt} directly is intractable in general since it necessitates, for each proposed dictionary $\mathbf{B}$, a combinatorial search for the supports of the associated sparse codes $\mathbf{\overline x}_i$.
-A common work-around is to convexify the problem (for fixed $\mathbf{B}$) by substituting the norm $\|\cdot\|_0$ with $\|\cdot\|_1$, impelled the fact that matrices $\mathbf{A}$ with large enough $L_{2k}(\mathbf{A})$ induce the same sparse codes via minimization of either norm \cite{?}.
-To this end, the lower bound $L_{2k}(\mathbf{BP}) \geq (L_{2k}(\mathbf{A}) - C_1\varepsilon) / \|\mathbf{D}\|_1$ implied by Thm.~\ref{DeterministicUniquenessTheorem} hints at conditions on the generating dictionary $\mathbf{A}$ and $k$-sparse codes $\mathbf{x}_i$ under which \emph{all} matrices $\mathbf{B}$ (of bounded column-norm) that solve Prob.~\ref{OptimizationProblem} also share this property of $\mathbf{A}$ by virtue of uniqueness and stability.
-One might then imagine an inference procedure whereby sparse codes are inferred via minimization of $\|\cdot\|_1$, but solutions still evaluated by their collective support size, yielding unique optimal solutions to Prob.~\ref{SLCopt} if only constraints could be imposed such that the learning procedure eventually guides $\mathbf{B}$ through an optimal dictionary.
-% (e.g.
-the dictionary is a member of a known finite set).
-
-\textbf{Acknowledgement.} We thank Fritz Sommer and Darren Rhea for early thoughts, and Ian Morris for posting \eqref{eqdim} online.
-
-%\section{EXTRA}
-%An additional consequence of Thm.~\ref{DeterministicUniquenessTheorem} of potential practical relevance to is the implied lower bound $L_{2k}(\mathbf{BPD}) \geq L_{2k}(\mathbf{A}) - C_1\varepsilon$ in the case where $\mathbf{A}$ satisfies \eqref{SparkCondition}.
-Since solving Prob.~\ref{SLCopt} directly requires a combinatorial search over sparse supports for the $\mathbf{\overline x}_i$ for each proposed dictionary $\mathbf{B}$, rendering it intractable in general, a common strategy is to replace the $\ell_0$-norm in \eqref{minsum} with the $\ell_1$-norm, thereby transforming the inference of sparse $\mathbf{\overline x}_i$ for a fixed dictionary $\mathbf{B}$ into a convex optimization solvable by a linear program.
-A major advance in compressive sensing was the discovery that, for fixed $\mathbf{B}$, solutions to \eqref{minsum} using either norm yield the same sparse vectors $\mathbf{\overline x}_i$ (up to noise) provided $L_{2k}(\mathbf{B})$ is large enough \cite{?}.
-What our results hint at are conditions on the generating dictionary $\mathbf{A}$ and $k$-sparse codes $\mathbf{x}_i$ under which \emph{all} matrices $\mathbf{B}$ (of bounded column-norm) that solve Prob.~\ref{OptimizationProblem} also share this property by virtue of uniqueness and stability; that is, conditions which guarantee that the sparse codes $\mathbf{\overline x}_i$ solving Prob.~\ref{OptimizationProblem} also solve the convexified problem when the corresponding dictionary $\mathbf{B}$ is held fixed.
-It remains to determine, however, what practical conditions preclude matrices that don't solve Prob.~\ref{OptimizationProblem} from nonetheless solving the convexified problem.
-%
-%Regardless, an implication of the above observation is that the following algorithm solves Prob.~\ref{OptimizationProblem} without appeal to combinatorial search:
-%\begin{enumerate}
-%\item List all matrices $\mathbf{B}$.
-%\item For each matrix $\mathbf{B}$, solve $\mathbf{\overline x}_i = \arg \min \|\mathbf{v}\|_1$ s.t. $\|\mathbf{Bv} - \mathbf{z}_i\| \leq \eta$ for $i = 1, \ldots, N$.
-%\item Quantify the proposed solution $\mathbf{B}$ and $\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N$ as $\rho(\mathbf{B}, \mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N) = \sum_{i=1}^{N} \|\mathbf{\overline x}_i\|_0$.
-%\item Output $\arg \min_{\mathbf{B}, \mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N} \left( \rho \right)$.
-% \end{enumerate}
-
-%Since its inception some twenty years ago, sparse coding has become a standard tool in signal analysis, yielding myriad insights into the structure of natural signals across a variety of scientific domains.
-In this work,
-
-%We make a final remark about the tightness of our results and the computability of our derived constants.
-%We remark that our constants have been derived for deterministic ``worst-case'' noise, whereas the ``effective'' noise might be smaller when sampled from a distribution.
-
-%Our results suggest that this correspondence could be due to the ``universality'' of sparse representations in natural data, an early idea in neural theory \cite{pitts1947}.
-
-% \vspace{-.2 cm}
-
-%\showacknow % Display the acknowledgments section
-
-\bibliographystyle{IEEEtran}
-\bibliography{chazthm_ieee_trans_sig}
-
-% \vspace{-.2 cm}
-
-\section{Appendix}\label{proofs}
-
-We prove Lem.~\ref{MainLemma} after the following auxiliary lemmas.  % stating and proving some auxiliary lemmas. 
-%First, note that since $\|\mathbf{A}\mathbf{x}\|_2 \leq \max_j\|\mathbf{A}_j\|_2\|\mathbf{x}\|_1$ and $\|\mathbf{x}\|_1 \leq \sqrt{k} \|\mathbf{x}\|_2$ for $k$-sparse $\mathbf{x}$, by \eqref{Ldef} we have the following frequently applied inequality:
-%\begin{align}\label{delrho}
-%L_{k'}(\mathbf{A}) \leq  \max_j\|\mathbf{A}_j\|_2 \ \ \text{for all $k' \leq 2k$}.
-%\end{align}
-
-% and then sketch the proofs of Thm.~\ref{robustPolythm} and Cor.~\ref{ProbabilisticCor}.
-
-%\begin{lemma}\label{spanIntersectionLemma}
-%Let $\mathbf{M} \in \mathbb{R}^{n \times m}$. If every $2k$ columns of $\mathbf{M}$ are linearly independent, then for any $F \subseteq {[m] \choose k}$:
-%\begin{align*}
-%\text{\rm span}\{\mathbf{M}_{\cap F}\}  = \bigcap_{S \in F} \text{\rm span}\{\mathbf{M}_S\}.
-%\end{align*}
-%\end{lemma}
-%\begin{proof}
-%Using induction on $|F|$, it is enough to prove the lemma when $|F| = 2$; but this case follows directly from the assumption.
-%\end{proof}
-
-\begin{lemma}\label{spanIntersectionLemma}
-If $f: V \to W$ is injective, then $f\left(\cap_{i=1}^\ell V_i \right) =  \cap_{i=1}^\ell f\left(V_i\right)$ for any $V_1, \ldots, V_\ell \subseteq V$. ($f(\emptyset):=\emptyset$.)
-%In particular, if for some $E \in 2^{[m]}$ the map $M \in \mathbb{R}^{n \times m}$ is injective on $\cup_{S \in \mathcal{H}} \text{span}\{e_i\}_{i \in S}$ then $\text{span}\{ M_{\cap_{S \in \mathcal{H}} S} \} = \cap_{S \in \mathcal{H}} \text{span}\{M_S\}$.
-\end{lemma}
-\begin{proof}
-By induction, it is enough to prove the case $\ell = 2$.
-Clearly, for any map $f$, if $w \in f(U \cap V)$ then $w \in f(U)$ and $w \in f(V)$; hence, $w \in f(U) \cap f(V)$.
-If $w \in f(U) \cap f(V)$, then $w \in f(U)$ and $w \in f(V)$; thus, $w = f(u) = f(v)$ for some $u \in U$ and $v \in V$, implying $u = v$ by injectivity of $f$.
-It follows that $u \in U \cap V$ and $w \in f(U \cap V)$.
-\end{proof}
-In particular, if a matrix $\mathbf{A}$ satisfies $L_{2\mathcal{H}}(\mathbf{A}) > 0$, then taking $V$ to be the union of subspaces consisting of vectors with supports in $2\mathcal{H}$, we have $\bm{\mathcal{A}}_{\cap \mathcal{G}} = \cap \bm{\mathcal{A}}_\mathcal{G}$ for all $\mathcal{G} \subseteq \mathcal{H}$.
-% \vspace{-.4 cm}
-
-\begin{lemma}\label{DistanceToIntersectionLemma}
-Let $\mathcal{V} = \{V_i\}_{i=1}^k$ be a set of two or more subspaces of $\mathbb{R}^m$, and set $V = \cap \mathcal{V} $.
-For  $\mathbf{u} \in \mathbb{R}^m$, we have (recall Defs.~\ref{dDef}~\&~\ref{FriedrichsDefinition}):
-\begin{align}\label{DTILeq}
-\text{\rm dist}(\mathbf{u}, V) \leq \frac{1}{1 - \xi(\mathcal{V})} \sum_{i=1}^k \text{\rm dist}(\mathbf{u}, V_i).
-\end{align}
-\end{lemma}
-\begin{proof} 
-% When $V = \{\mathbf{0}\}$, the result is trivial, so suppose otherwise.  
-Recall the projection onto the subspace $V \subseteq \mathbb{R}^m$ is the mapping $\Pi_V: \mathbb{R}^m \to V$ that associates with each $\mathbf{u}$ its unique nearest point in $V$; i.e., $\|\mathbf{u} - \Pi_V\mathbf{u}\|_2 = \text{\rm dist}(\mathbf{u}, V)$.
-By repeatedly applying the triangle inequality, we have:
-\begin{align}\label{f}
-\|\mathbf{u} - &\Pi_V\mathbf{u}\|_2 
-\leq \|\mathbf{u} - \Pi_{V_k} \mathbf{u}\|_2 + \|\Pi_{V_k}  \mathbf{u} - \Pi_{V_k}\Pi_{V_{k-1}}\mathbf{u}\|_2 \nonumber \\
-&\ \ \ \ \ \ \ \ \ \ \ + \cdots + \|\Pi_{V_k} \Pi_{V_{k-1}}\cdots \Pi_{V_1} \mathbf{u} - \Pi_V \mathbf{u}\|_2 \nonumber \\
-&\leq  \sum_{\ell=1}^k \|\mathbf{u} - \Pi_{V_{\ell}} \mathbf{u}\|_2 
-+ \|(\Pi_{V_k}\cdots\Pi_{V_{1}} - \Pi_V) \mathbf{u}\|_2,
-\end{align}
-where we have also used that the spectral norm of the orthogonal projections $\Pi_{V_{\ell}}$ satisfies $\|\Pi_{V_{\ell}}\|_2 \leq 1$ for all $\ell$.
-
-It remains to bound the second term in \eqref{f} by $\xi(\mathcal{V}) \|\mathbf{u} - \Pi_V\mathbf{u}\|_2$.
-First, note that $\Pi_{V_\ell} \Pi_V = \Pi_V$ and $\Pi_V^2 = \Pi_V$, so we have $\|(\Pi_{V_k} \cdots \Pi_{V_1} - \Pi_V) \mathbf{u} \|_2
-= \| ( \Pi_{V_k} \cdots\Pi_{V_1} - \Pi_V ) (\mathbf{u} - \Pi_V\mathbf{u})\|_2$. % \leq z\|\mathbf{u} - \Pi_V\mathbf{u}\|_2$.
-Consequently, inequality \eqref{DTILeq} follows from \cite[Thm.~9.33]{Deutsch12}:
-\begin{align}
-\|\Pi_{V_k}\Pi_{V_{k-1}}\cdots\Pi_{V_1} \mathbf{x} - \Pi_V\mathbf{x}\|_2 \leq z \|\mathbf{x}\|_2, \ \ \text{for all } \mathbf{x},
-\end{align}
-with \mbox{$z^2= 1 - \prod_{\ell =1}^{k-1}(1-z_{\ell}^2)$} and \mbox{$z_{\ell} = \cos\theta\left(V_{\ell}, \cap_{s=\ell+1}^k V_s\right)$} (recall $\theta$ from Def.~\ref{FriedrichsDefinition}), after substituting $\xi(\mathcal{V})$ for $z$ and rearranging terms.
-\end{proof}
-\begin{lemma}\label{NonEmptyLemma} 
-Fix an $r$-regular hypergraph $\mathcal{H} \subseteq 2^{[m]}$ satisfying the SIP.
-If the map $\pi: \mathcal{H} \to 2^{[\overline m]}$ has $\sum_{S \in \mathcal{H}} |\pi(S)| \geq \sum_{S \in \mathcal{H}} |S|$ and:
-\begin{align}\label{cond}
-	|\cap \pi(\mathcal{G})| \leq |\cap \mathcal{G} |,\ \ \   \text{for } \mathcal{G} \in {\mathcal{H} \choose r} \cup {\mathcal{H} \choose r+1},
-\end{align}
-%
-then $\overline m \geq m$; and if $\overline m  (r-1) < mr$, the map $i \mapsto \cap_{S \in \sigma(i)} \pi(S)$ is an injective function to $[\overline m]$ from some $J \subseteq [m]$ of size $m - (r-1)(\overline m - m)$ (recall $\sigma$ from Def.~\ref{sip}).
-%In particular, if $\overline m = m$ then $\pi$ is induced by a permutation on $[m]$.
-\end{lemma}
-
-\begin{proof}
-Consider the following set: $T_1 := \{(i, S): i \in \pi(S), S \in \mathcal{H}\}$, which numbers $|T_1| = \sum_{S \in \mathcal{H}} |\pi(S)| \geq \sum_{S \in \mathcal{H}} |S| = \sum_{i \in [m]} \deg_\mathcal{H}(i) = mr$ by $r$-regularity of $\mathcal{H}$.
-Note that $|T_1| \leq \overline m r$; otherwise, pigeonholing the tuples of $T_1$ with respect to their $\overline m$ possible first elements would imply that more than $r$ of the tuples in $T_1$ share the same first element.
-This cannot be the case, however, since then some $\mathcal{G} \in {\mathcal{H} \choose r+1}$ formed from any $r+1$ of their second elements would satisfy $\cap \pi(\mathcal{G}) \neq 0$; hence, $|\cap \mathcal{G}| \neq 0$ by \eqref{cond}, contradicting $r$-regularity of $\mathcal{H}$.
-It follows that $\overline m \geq m$.
-
-Suppose now that $\overline m (r-1) < mr$, so that $p := mr - \overline m (r-1)$ is positive and $|T_1| \geq \overline m (r - 1) + p$.
-Pigeonholing $T_1$ into $[\overline m]$ again, there are at least $r$ tuples in $T_1$ sharing some first element; that is, for some $\mathcal{G}_1 \subseteq \mathcal{H}$ of size $|\mathcal{G}_1| \geq r$, we have $|\cap \pi(\mathcal{G}_1)| \geq 1$ and (by \eqref{cond}) $|\cap \mathcal{G}_1| \geq 1$.
-Since no more than $r$ tuples of $T_1$ can share the same first element, we in fact have $|\mathcal{G}_1| = r$.
-It follows by $r$-regularity that $\mathcal{G}_1$ is a star of $\mathcal{H}$; hence, $|\cap \mathcal{G}_1| = 1$ by the SIP and $|\cap \pi(\mathcal{G}_1)|  = 1$ by \eqref{cond}.
-
-If $p=1$, then we are done.
-Otherwise, define $T_2 := T_1 \setminus \{(i,S) \in T_1: i = \cap \pi(\mathcal{G}_1)\}$, which contains $|T_2| = |T_1| - r \geq (\overline m - 1)(r-1) + (p-1)$ ordered pairs having $\overline m - 1$ distinct first indices.
-Pigeonholing $T_2$ into $[\overline m - 1]$ and repeating the above arguments produces the star $\mathcal{G}_2 \in {\mathcal{H} \choose r}$ with intersection $\cap \mathcal{G}_2$ necessarily distinct (by $r$-regularity) from $\cap \mathcal{G}_1$.
-Iterating this procedure $p$ times in total yields the stars $\mathcal{G}_i$ for which $\cap\mathcal{G}_i \mapsto \cap \pi(\mathcal{G}_i)$ defines an injective map to $[\overline m]$ from $J = \{\cap \mathcal{G}_1, \ldots, \cap \mathcal{G}_p\} \subseteq [m]$.
-\end{proof}
-
-\begin{proof}[Proof of Lem.~\ref{MainLemma}]
-%We will show that the bound \eqref{GapUpperBound} trickles through the intersection semi-lattices of $\{\bm{\mathcal{A}}_S\}_{S \in \mathcal{H}}$ and $\{\bm{\mathcal{B}}_{\overline S}\}_{\overline S \in \pi(\mathcal{H})}$ to yield \eqref{MainLemmaBPD} by virtue of the SIP.
-We begin by showing that $\dim(\bm{\mathcal{B}}_{\pi(S)}) = \dim(\bm{\mathcal{A}}_S)$ for all $S \in \mathcal{H}$.
-Note that since $\|\mathbf{A}\mathbf{x}\|_2 \leq \max_j\|\mathbf{A}_j\|_2\|\mathbf{x}\|_1$ and $\|\mathbf{x}\|_1 \leq \sqrt{k} \|\mathbf{x}\|_2$ for all $k$-sparse $\mathbf{x}$, by \eqref{Ldef} we have $L_2(\mathbf{A}) \leq \max_j\|\mathbf{A}_j\|_2$ and therefore (as $0 \leq \xi < 1$) the right-hand side of \eqref{GapUpperBound} is less than one.
-From \eqref{dimLem}, we have $|\pi(S)| \geq \dim(\bm{\mathcal{B}}_{\pi(S)}) \geq \dim(\bm{\mathcal{A}}_S) = |S|$, the final equality holding by injectivity of $\mathbf{A}_S$.
-As $|\pi(S)| = |S|$, the claim follows.
-Note, therefore, that $\mathbf{B}_{\pi(S)}$ has full-column rank for all $S \in \mathcal{H}$.
-
-We next demonstrate that \eqref{cond} holds.
-Fixing $\mathcal{G} \in {\mathcal{H} \choose r} \cup {\mathcal{H} \choose r+1}$, it suffices to show that $d(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}, \bm{\mathcal{A}}_{\cap \mathcal{G}} ) < 1$, since by \eqref{dimLem} we then have $|\cap \pi(\mathcal{G})| = \dim(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}) \leq \dim(\bm{\mathcal{A}}_{\cap \mathcal{G}}) = |\cap \mathcal{G}|$, with equalities from the full column-ranks of $\mathbf{A}_{S}$ and $\mathbf{B}_{\pi(S)}$ for all $S \in \mathcal{H}$.\footnote{Note that if ever $\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})} \neq \bf 0$ while $\cap \mathcal{G} = \emptyset$, we would have $d(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}, \bm 0 ) = 1$.
-However, that leads to a contradiction.} Observe that $d(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}, \bm{\mathcal{A}}_{\cap \mathcal{G}}  )
-\leq d\left( \cap \bm{\mathcal{B}}_{\pi(\mathcal{G})}, \cap \bm{\mathcal{A}}_\mathcal{G} \right)$ by \eqref{UsubU}, since trivially $\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})} \subseteq \cap \bm{\mathcal{B}}_{\pi(\mathcal{G})}$ and also $\bm{\mathcal{A}}_{\cap \mathcal{G}} = \cap \bm{\mathcal{A}}_\mathcal{G}$ by Lem.~\ref{spanIntersectionLemma}.
-Recalling Def.~\ref{dDef} and applying Lem.~\ref{DistanceToIntersectionLemma} yields:
-\begin{align}
-d\left( \cap \bm{\mathcal{B}}_{\pi(\mathcal{G})}, \cap \bm{\mathcal{A}}_\mathcal{G} \right)
-&\leq \max_{\mathbf{u} \in \cap \bm{\mathcal{B}}_{\pi(\mathcal{G})}, \ \|\mathbf{u}\|_2 \leq 1} \sum_{S \in \mathcal{G}} \frac{ \text{\rm dist}\left( \mathbf{u},\bm{\mathcal{A}}_{S} \right) }{ 1 - \xi( \bm{\mathcal{A}}_\mathcal{G} ) } \nonumber \\
-&= \sum_{S \in \mathcal{G}} \frac{ d\left( \cap \bm{\mathcal{B}}_{\pi(\mathcal{G})},\bm{\mathcal{A}}_{S} \right) }{ 1 - \xi( \bm{\mathcal{A}}_\mathcal{G} ) }, \nonumber
-\end{align}
-passing the maximum through the sum.
-Since $\cap \bm{\mathcal{B}}_{\pi(\mathcal{G})} \subseteq \bm{\mathcal{B}}_{\pi(S)}$ for all $S \in \mathcal{G}$, by \eqref{UsubU} the numerator of each term in the sum above is bounded by \mbox{$d\left( \bm{\mathcal{B}}_{\pi(S)},\bm{\mathcal{A}}_{S} \right) = d\left(\bm{\mathcal{A}}_{S}, \bm{\mathcal{B}}_{\pi(S)} \right) \leq \varepsilon$}, with the equality from \eqref{eqdim} since $\dim(\bm{\mathcal{B}}_{\pi(S)}) = \dim(\bm{\mathcal{A}}_S)$.
-Thus, altogether:
-\begin{align}\label{last}
-d(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}, \bm{\mathcal{A}}_{\cap \mathcal{G}} )
-\leq \frac{|\mathcal{G}| \varepsilon}{1 - \xi( \bm{\mathcal{A}}_\mathcal{G} )}
-\leq \frac{C_2 \varepsilon}{\max_j\|\mathbf{A}_j\|_2},
-\end{align}
-recalling the definition of $C_2$ in \eqref{Cdef2}.
-Lastly, since $C_2 \varepsilon < L_2(\mathbf{A}) \leq \max_j\|\mathbf{A}_j\|_2$, we have $d(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}, \bm{\mathcal{A}}_{\cap \mathcal{G}} ) \leq 1$ and therefore \eqref{cond} holds.
-
-%Keeping in mind that $d(U',V) \leq d(U,V)$ whenever $U' \subseteq U$ and applying (in order) Lem.~\ref{spanIntersectionLemma}, Lem.~\ref{DistanceToIntersectionLemma}, \eqref{eqdim}, \eqref{GapUpperBound}, and \eqref{Cdef2} gives:
-%\begin{align}\label{randoml}
-%d(&\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}, \bm{\mathcal{A}}_{\cap \mathcal{G}}  ) 
-%\leq d\left( \cap \bm{\mathcal{B}}_{\pi(\mathcal{G})}, \cap \bm{\mathcal{A}}_\mathcal{G} \right)
-%\leq \sum_{T \in \mathcal{G}} \frac{ d\left( \cap \bm{\mathcal{B}}_{\pi(\mathcal{G})},\bm{\mathcal{A}}_{T} \right) }{ 1 - \xi( \bm{\mathcal{A}}_\mathcal{G} ) } \nonumber \\
-%&\leq \sum_{T \in \mathcal{G}} \frac{ d\left( \bm{\mathcal{B}}_{\pi(T)},\bm{\mathbf{A}}_{T} \right) }{ 1 - \xi( \bm{\mathcal{A}}_\mathcal{G} ) }
-%\leq \frac{|\mathcal{G}| \varepsilon}{1 - \xi( \bm{\mathcal{A}}_\mathcal{G} )} 
-%\leq \frac{C_2 \varepsilon}{\max_j\|\mathbf{A}_j\|_2},
-%\end{align}
-%
-%which is less than one, since $C_2 \varepsilon < L_2(\mathbf{A}) \leq \max_j\|\mathbf{A}_j\|_2$.
-
-Applying Lem.~\ref{NonEmptyLemma}, the association $i \mapsto \cap_{S \in \sigma(i)} \pi(S)$ is an injective map $\overline \pi: J \to [\overline m]$ for some $J \subseteq [m]$ of size $m - (r-1)(\overline m - m)$, and $\mathbf{B}_{\overline \pi(i)} \neq \mathbf{0}$ for all $i \in J$ since the columns of $\mathbf{B}_{\pi(S)}$ are linearly independent for all $S \in \mathcal{H}$.
-Letting $\overline \varepsilon := C_2 \varepsilon / \max_i \|\mathbf{A}_i\|_2$, it follows from \eqref{eqdim} and \eqref{last} that $d\left( \bm{\mathcal{A}}_i, \bm{\mathcal{B}}_{\overline \pi(i)} \right) = d\left(\bm{\mathcal{B}}_{\overline \pi(i)},  \bm{\mathcal{A}}_i \right)  \leq \overline \varepsilon$ for all $i \in J$.
-%Fixing $\overline \varepsilon = C_2\varepsilon$ and letting $c_i = \|\mathbf{A}_i\|_2^{-1}$, we thus have that for each $\mathbf{e}_i \in \mathbb{R}^m$ with $i \in J$ there exists some $\overline{c}_i \in \mathbb{R}$ such that $\|c_i\mathbf{A}\mathbf{e}_i - \overline{c}_i \mathbf{B}\mathbf{e}_{\overline \pi(i)}\|_2 \leq \overline \varepsilon < L_2(\mathbf{A}) \min_{i\in J} |c_i|$.
-But this is exactly the supposition in \eqref{1D}, and the result follows from the case $k=1$ in Sec.~\ref{DUT} applied to the submatrix $\mathbf{A}_J$.
-Setting $c_i := \|\mathbf{A}_i\|_2^{-1}$ so that $\|c_i\mathbf{Ae}_i\|_2 = 1$, by Def.~\ref{dDef} for all $i \in J$:
-\begin{align*}
-\min_{\overline c_i \in \mathbb{R}} \|c_i\mathbf{Ae}_i - \overline c_i \mathbf{Be}_{\overline \pi(i)} \|_2
-\leq d\left( \bm{\mathcal{A}}_i, \bm{\mathcal{B}}_{\overline \pi(i)} \right)
-\leq \overline \varepsilon,
-%&= \max_{\bm{u} \in \bm{\mathcal{A}}_i, \|\bm{u}\|_2 \leq 1} \text{dist}\left(\bm{u}, \bm{\mathcal{B}}_{\overline \pi(i)} \right) \\
-%&\geq  \text{dist}\left(c_i\bm{Ae}_i, \mathbf{Be}_{\overline \pi(i)} \right) \\
-%&= \min_{\overline c_i \in \mathbb{R}} \|c_i\bm{Ae}_i - \overline c_i \mathbf{Be}_{\overline \pi(i)} \|_2
-\end{align*}
-%
-for $\overline \varepsilon < L_2(\mathbf{A})\min_{i \in [m]}|c_i|$.
-But this is exactly the supposition in \eqref{1D}, with $J$ and $\overline \varepsilon$ in place of $[m]$ and $\varepsilon$, respectively.
-The same arguments of the case $k=1$ in Sec.~\ref{DUT} can then be made to show that for any $\overline m \times \overline m$ permutation and invertible diagonal matrices $\mathbf{P}$ and $\mathbf{D}$ with, respectively, columns $\mathbf{e}_{\pi(i)}$ and $\frac{\overline{c}_i}{c_i}\mathbf{e}_i$ for $i \in J$ (otherwise, $\mathbf{e}_{i}$ for $i \in [\overline{m}] \setminus J$), we have $\|\mathbf{A}_i - (\mathbf{B}\mathbf{PD})_i \|_2 \leq \overline  \varepsilon / |c_i|  \leq C_2 \varepsilon$ for all $i \in J$.
-\end{proof}
-
-%\section{Proofs of Thm.~\ref{robustPolythm} and Cor.~\ref{ProbabilisticCor}}
-
-%\clearpage
-
-%\section{$\ell_1$-norm Extension}
-%
-%\begin{problem}\label{OptimizationProblemL1}
-%Find a matrix $\mathbf{B}$ and vectors \mbox{$\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N \in \mathbb{R}^m$} that solve:
-%\begin{align}\label{minsum}
-%\min \sum_{i = 1}^N \|\mathbf{\overline x}_i\|_1 \ \ 
-%\text{subject to} \ \ \|\mathbf{z}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \eta, \ \text{for all $i$}.
-%\end{align}
-%\end{problem}
-
-%\begin{corollary}\label{SLCopt}
-%Fix $\alpha > 0$ and suppose all of the assumptions of Thm.\ref{DeterministicUniquenessTheorem} hold with the following modifications:
-%\begin{enumerate}
-%\item The coefficients of all $k$-sparse $\mathbf{x}_i$ are drawn from $[-\beta, \beta]$, where $\beta < \frac{\alpha(k+1)}{k}$.
-%\item More than $(k-1){\overline m \choose k} + q$ vectors $\mathbf{x}_i$ are supported in each $S \in \mathcal{H}$, where
-%\[ q = \left[\frac{\alpha}{\beta}(k+1) - k\right]^{-1}k|\mathcal{H}|(k-1){\overline m \choose k-1}. \]
-%\end{enumerate}
-%Then all solutions to Prob.~\ref{OptimizationProblemL1} for which the nonzero elements of all $\mathbf{\overline x}_i$ lie outside $[-\alpha, \alpha]$ necessarily satisfy the implications \eqref{Cstable} and \eqref{b-PDa} of Thm.~\ref{DeterministicUniquenessTheorem}.
-%\end{corollary}
-
-%\begin{proof}[Proof of Cor.~\ref{SLCopt}]
-%We bound the number of $k$-sparse $\mathbf{\overline x}_i$ and then apply Thm.~\ref{DeterministicUniquenessCorollary}.
-First, observe that no more than $(k-1)|\mathcal{H}|$ of the $\mathbf{\overline x}_i$ share a support $\overline S$ of size less than $k$; otherwise, by the pigeonhole principle, at least $k$ of these indices $i$ belong to the same $K \subseteq I(S)$ for some $S \in \mathcal{H}$ and (as argued previously) \eqref{rhs222} follows.
-Since the right-hand side of \eqref{rhs222} is less than one, by \eqref{dimLem} we have the contradiction $k = \dim(\bm{\mathcal{A}}_S) \leq \dim(\bm{\mathcal{B}}_{\overline S}) \leq |\overline S|.$ The total number of $(k-1)$-sparse vectors $\mathbf{\overline x}_i$ can thus not exceed $|\mathcal{H}|(k-1){ \overline m \choose k-1}$.
-
-%Next, observe that the assumptions of the lemma imply:
-%\begin{align*}
-%\alpha \sum_i \|\mathbf{\overline x}_i\|_0 \leq \sum_i \|\mathbf{\overline x}_i\|_1 \leq \sum_i \|\mathbf{x}_i\|_1 \leq \beta \sum_i \|\mathbf{x}_i\|_0.
-%\end{align*}
-
-%We now apply these facts to bound the number of $k$-sparse $\mathbf{\overline x}_i$.
-Let $n_p$ be the number of $\mathbf{\overline x}_i$ with $\|\mathbf{\overline x}_i\|_0 = p$.
-Since the $\mathbf{x}_i$ are all $k$-sparse, we have:
-%\begin{align*}
-%k \sum_{p = 0}^{\overline m} n_p = k N \geq \sum_{i=0}^N \|\mathbf{x}_i\|_0 \geq \frac{\alpha}{\beta} \sum_{i=0}^N \|\mathbf{\overline x}_i\|_0 = \frac{\alpha}{\beta} \sum_{p=0}^{\overline m} p n_p.
-%\end{align*}
-%Hence, 
-%\begin{align*}
-%\left[ \frac{\alpha(k+1)}{\beta} - k\right] \sum_{p = k+1}^{\overline m} n_p 
-%&\leq \sum_{p = k+1}^{\overline m} (\frac{\alpha}{\beta} p-k) n_p
-%\leq \sum_{p = 0}^k (k - \frac{\alpha}{\beta} p)n_p \\
-%&\leq k \sum_{p = 0}^k n_p 
-%\leq k(1-\frac{\alpha}{\beta})n_k + k|\mathcal{H}|(k-1){ \overline m \choose k-1}
-%\end{align*}
-
-%[Shit, we need $\alpha = \beta$.] Therefore, no more than $q$ vectors $\mathbf{\overline x}_i$ are \emph{not} $k$-sparse.
-Since for every $S \in \mathcal{H}$ there are over $(k-1){\overline m \choose k} + q$ vectors $\mathbf{x}_i$ supported there, it follows that more than $(k-1){\overline m \choose k}$ of them have corresponding $\mathbf{\overline x}_i$ that are $k$-sparse.
-The result now follows directly from Thm.~\ref{DeterministicUniquenessCorollary}.
-%\end{proof}
-
-%\pagebreak
-
-%\begin{corollary}\label{SLCoptL1}
-%If all of the assumptions of Thm.\ref{DeterministicUniquenessTheorem} hold, only now with more than $(k-1)\left[ {\overline m \choose k} + |\mathcal{H}|k{\overline m \choose k-1}\right]$ vectors $\mathbf{x}_i$ supported in each $S \in \mathcal{H}$, then every solution to Prob.~\ref{OptimizationProblemL1} for which the average absolute nonzero coefficient of the $\mathbf{\overline x}_i$ is bounded below by that of the $\mathbf{x}_i$ necessarily satisfies the implications \eqref{Cstable} and \eqref{b-PDa} of Thm.~\ref{DeterministicUniquenessTheorem}.
-%\end{corollary}
-
-%\begin{proof}[Proof of Cor.~\ref{SLCoptL1}]
-%Since the average absolute nonzero coefficient of the $\mathbf{x}_i$ is given by $\alpha = \sum_i \|\mathbf{x}_i\|_1 / \sum_i \|\mathbf{x}_i\|_0$, we have:
-%\begin{align*}
-%\alpha \sum_i \|\mathbf{\overline x}_i\|_0 \leq \sum_i \|\mathbf{\overline x}_i\|_1 \leq \sum_i \|\mathbf{x}_i\|_1 = \alpha \sum_i \|\mathbf{x}_i\|_0.
-%\end{align*}
-%
-%and the result follows by the same arguments as in the proof of Cor.~\ref{SLCopt}.
-%\end{proof}
-
-\end{document}
+TODO

### 2020-08-05 manuscripts/newthesis/results.tex
newthesis

--- 2019-05-10 manuscripts/IEEE/final_submission.tex
@@
-% TODO: 
-% Make L_H a definition..? Change def of L to be 1-norm so we don't need these sqrt k's?
-% C_1 depends on J in Thm 1
-% also in proof of (7) x need not be *any* 2k-sparse vector...can instead restrict to some H...then 2k is restricted to half being on H.
-
-% Notes:
-%
-% Can we prove in a line or two that the inverse problem is stable by arguing that the function is bijective and closed therefore a homeomorphism?
-% Should we mention the notion of Grassmannian manifolds and that Theta is a metric on this space?
-% Change robustness to stability?
-%
-\documentclass[journal, twocolumn]{IEEEtran}
-
-% *** MATH PACKAGES ***
-\usepackage{amsmath, amssymb, amsthm} 
-\newtheorem{theorem}{Theorem}
-\newtheorem{lemma}{Lemma}
-\newtheorem{conjecture}{Conjecture}
-\newtheorem{problem}{Problem}
-\newtheorem{question}{Question}
-\newtheorem{proposition}{Proposition}
-\newtheorem{definition}{Definition}
-\newtheorem{corollary}{Corollary}
-\newtheorem{remark}{Remark}
-\newtheorem{example}{Example}
-
-\usepackage[pdftex]{graphicx}
-
-% *** ALIGNMENT PACKAGES ***
-\usepackage{array}
-\usepackage{cite}
-\usepackage{bm}
-
-% correct bad hyphenation here
-%\hyphenation{op-tical net-works semi-conduc-tor}
-
-\begin{document}
-
-%\title{When can a generating dictionary and sparse codes be recovered from noisy data?}
-%\title{When is the dictionary learning problem well-posed?}
-\title{On the uniqueness and stability of dictionaries \\ for sparse representation of noisy signals}
-%\title{When is the dictionary learning problem for sparse coding well-posed?}
-%\title{When is the sparsest representation unique?}
-%\title{When are sparse codes identifiable from their unknown noisy compressive measurements?}
-% FRITZ2: The title doesn't reflect the amount of new stuff, it seems incremental from the last one. It's not very meaningful.
-% FRITZ: Not everyone knows what well-posed means. You should mention recovery from noisy data in the title.
-
-\author{Charles~J.~Garfinkle and Christopher~J.~Hillar \\
-Redwood Center for Theoretical Neuroscience, Berkeley, CA, USA
-%\thanks{%e-mails: cjg@berkeley.edu, chillar@msri.org.  
-%CG and CH supported, in part, by NSF grant IIS-1219212 and the Statistical and Applied Mathematical Sciences Institute, under NSF DMS-1127914.}
-}
-
-\maketitle
-
-% \keywords{Sparse coding, dictionary learning, matrix factorization, compressed sensing, inverse problems, blind source separation}
-
-\begin{abstract}
-%Learning optimal dictionaries for sparse coding has exposed characteristic sparse features of many natural signals.
-However, there are few universal conditions guaranteeing the stability of such features in the presence of noise.
-Here, we prove very generally that optimal dictionaries and sparse codes are unique up to measurement error for all diverse enough datasets generated by the sparse coding model.
-Applications are given to data analysis, engineering, and neuroscience.
-Learning optimal dictionaries for sparse coding has exposed characteristic sparse features of many natural signals.
-However, universal guarantees of the stability of such features in the presence of noise are lacking.
-Here, we provide very general conditions guaranteeing when dictionaries yielding the sparsest encodings are unique and stable with respect to measurement or modeling error.
-We demonstrate that some or all original dictionary elements are recoverable from noisy data even if the dictionary fails to satisfy the spark condition, its size is overestimated, or only a polynomial number of distinct sparse supports appear in the data.
-Importantly, we derive these guarantees without requiring any constraints on the recovered dictionary beyond a natural upper bound on its size.
-Our results also yield an effective procedure sufficient to affirm if a proposed solution to the dictionary learning problem is unique within bounds commensurate with the noise.
-We suggest applications to data analysis, engineering, and neuroscience and close with some remaining challenges left open by our work.
-\end{abstract}
-
-% Optional adjustment to line up main text (after abstract) of first page with line numbers, when using both lineno and twocolumn options.
-% You should only change this length when you've finalised the article contents.
+\chapter{Uniqueness and Stability of Learned Dictionaries}\label{Results}
 
 \section{Introduction}\label{Intro}
-\IEEEPARstart{S}{parse} coding is a common modern approach to pattern analysis in signal processing whereby each of $N$ observed $n$-dimensional signal samples is viewed as a (noisy) linear combination of at most $k$ elementary waveforms drawn from some unknown ``dictionary" of size $m \ll N$ (see \cite{Zhang15} for a comprehensive review).
-%\IEEEPARstart{A}{}common modern approach to pattern analysis in signal processing is to view each of $N$ observed $n$-dimensional signal samples as a (noisy) linear combination of at most $k$ elementary waveforms drawn from some unknown ``dictionary" of size $m \ll N$ (see \cite{Zhang15} for a comprehensive review).
-Optimizing dictionaries subject to this and related sparsity constraints has revealed seemingly characteristic sparse structure in several signal classes of current interest (e.g., in vision \cite{wang2015sparse}).
 
-Of particular note are the seminal works in the field \cite{Olshausen96, hurri1996image, bell1997independent, van1998independent}, which discovered that dictionaries optimized for coding small patches of ``natural" images share qualitative similarities with linear filters estimated from response properties of simple-cell neurons in mammalian visual cortex.
-Curiously, these waveforms (e.g., ``Gabor'' wavelets) appear in dictionaries learned by a variety of algorithms trained over different natural image datasets, suggesting that learned features in natural signals may, in some sense, be canonical \cite{donoho2001can}.
+%\begin{itemize}
+%\item Background to the topic.
+%\item Brief review of current knowledge.
+%\item Indicate the gap in knowledge. State the aim of the research and how it fits into the gap.
+%\item Can include an outline of what follows.
+%\end{itemize}
 
-Motivated by these discoveries and more recent work relating compressed sensing \cite{eldar2012compressed} to a theory of information transmission through random wiring bottlenecks in the brain \cite{Isely10}, we address when dictionaries for sparse representation are indeed identifiable from data.
-Answers to this question may also have implications in practice wherever an appeal is made to latent sparse structure of data (e.g., forgery detection \cite{hughes2010, olshausen2010applied}; brain recordings \cite{jung2001imaging, agarwal2014spatially, lee2016sparse}; and gene expression \cite{wu2016stability}).
+%Why do neuroscientists care about dictionary learning?
 
-While several algorithms have been recently proposed to provably recover unique dictionaries under specific conditions (see \cite[Sec.~I-E]{Sun16} for a summary of the state-of-the-art), few theorems can be invoked to justify the consistency of inference under this model of data more broadly.
-To our knowledge, a universal guarantee of the uniqueness and stability of learned dictionaries and the sparse representations they induce over noisy data has yet to appear in the literature.
-% in justifying the identification of forged paintings by their anomalous sparse representations \cite{hughes2010},
-
-Here, we prove very generally that uniqueness and stability is a typical property of sparse dictionary learning.
-More specifically, we show that matrices injective on a sparse domain are identifiable from \mbox{$N = m(k-1){m \choose k} + m$} noisy linear combinations of $k$ of their $m$ columns up to an error that is linear in the noise (Thm.~\ref{DeterministicUniquenessTheorem}).
+In this chapter, we will develop some necessary language before stating the very general main result of this work: that uniqueness and stability is a typical property of learned dictionaries for sparse coding of noisy signals.
+More specifically, it is stated that matrices injective on a sparse domain are identifiable from \mbox{$N = m(k-1){m \choose k} + m$} noisy linear combinations of $k$ of their $m$ columns up to an error that is linear in the noise (Thm.~\ref{DeterministicUniquenessTheorem}).
 In fact, provided $n \geq \min(2k,m)$, in almost all cases the problem is well-posed, as per Hadamard \cite{Hadamard1902}, given a sufficient amount of data (Thm.~\ref{robustPolythm} and Cor.~\ref{ProbabilisticCor}).
 
-Our guarantees also hold for a related (and perhaps more commonly posed, e.g.
+We will find these guarantees also hold for a related (and perhaps more commonly posed, e.g.
 \cite{rehnsommer2007}) optimization problem seeking a dictionary minimizing the average number of elementary waveforms required to reconstruct each sample of the dataset (Thm.~\ref{SLCopt}).
-To practical benefit, our results impose no restrictions on learned dictionaries (e.g., that they, too, be injective over some sparse domain) beyond an upper bound on dictionary size, which is necessary in any case to avoid trivial solutions (e.g., allowing $m = N$).
+To practical benefit, no restrictions are imposed on learned dictionaries (e.g., that they, too, be injective over some sparse domain) beyond an upper bound on dictionary size, which is necessary in any case to avoid trivial solutions (e.g., allowing $m = N$).
 %That is, every pair of solutions of comparable size has some number of dictionary elements in common (up to noise), and similarly so for the coefficients of sparse codes they induce.
+
+\section{Definitions and Problem Statements}
 
@@
 for $k$-\emph{sparse} $\mathbf{x}_i \in \mathbb{R}^m$ having at most $k<m$ nonzero entries and \emph{noise} $\mathbf{n}_i \in \mathbb{R}^n$, with bounded norm $\| \mathbf{n}_i \|_2 \leq  \eta$ representing our worst-case uncertainty in measuring the product $\mathbf{A}\mathbf{x}_i$.
-We first consider the following formulation of sparse coding.
+Let us first consider the following decidable\footnote{Note that Prob.~\ref{InverseProblem} is decidable for rational inputs $\mathbf{z}_i$ \cite{chrishillar} since the statement that it has a solution can be expressed as a logical sentence in the theory of algebraically closed fields, and this theory has quantifier elimination \cite{basu2006algorithms}.} formulation of the dictionary learning problem.
 %The first mathematical problem we consider is the following.
@@
 which is necessary to guarantee the uniqueness of arbitrary $k$-sparse $\mathbf{x}_i$.
-We generalize these results to the practical setting  $\eta > 0$ by considering the following natural notion of stability with respect to measurement error.
+The following natural notion of stability with respect to measurement error serves to generalize these results to the practical setting  $\eta > 0$.
 
@@
 implying (Cor.~\ref{DeterministicUniquenessCorollary}), which guarantees that sparse representations of a dataset $Z$ are unique up to noise whenever generating dictionaries $\mathbf{A}$ satisfy a spark condition on supports and the original sparse codes $\mathbf{x}_i$ are sufficiently diverse (e.g., Fig.~\ref{noisyrecovery}).
-Moreover, we provide an explicit, computable $\varepsilon(\delta_1, \delta_2)$ in (\ref{epsdel}) that is linear in desired accuracy $\delta_1$, and essentially so in $\delta_2$.
+Moreover, an explicit, computable $\varepsilon(\delta_1, \delta_2)$ is defined in (\ref{epsdel}) that is linear in desired accuracy $\delta_1$, and essentially so in $\delta_2$.
 
-In the next section, we give formal statements of these findings.
-We then extend the same guarantees (Thm.~\ref{SLCopt}) to the following alternate formulation of dictionary learning, which minimizes the total number of nonzero entries in sparse codes.
+Formal statements of these findings will follow.
+They will then be extended (Thm.~\ref{SLCopt}) to the following alternate formulation of dictionary learning, which minimizes the total number of nonzero entries in sparse codes.
 
@@
 
-Our development of Thm.~\ref{DeterministicUniquenessTheorem} is general enough to provide some uniqueness and stability even when generating $\mathbf{A}$ do not fully satisfy (\ref{SparkCondition}) and recovery dictionaries $\mathbf{B}$ have more columns than $\mathbf{A}$.
-Moreover, the approach incorporates a combinatorial theory for designing generating codes that should be of independent interest.
+Surprisingly, the development of Thm.~\ref{DeterministicUniquenessTheorem} is general enough to provide some uniqueness and stability even when generating $\mathbf{A}$ do not fully satisfy (\ref{SparkCondition}) and recovery dictionaries $\mathbf{B}$ have more columns than $\mathbf{A}$.
+Moreover, the approach incorporates a theory of combinatorial designs for the sparse supports of generating codes $\mathbf{x}_i$ that should be of independent interest.
 We also give brief arguments adapting our results to dictionaries and codes drawn from probability distributions (Cor.~\ref{ProbabilisticCor}).
 The technical proofs of Thms.~\ref{DeterministicUniquenessTheorem} and ~\ref{SLCopt} are deferred to Sec.~\ref{DUT}, following some necessary definitions and a fact in combinatorial matrix analysis (Lem.~\ref{MainLemma}; proven in the Appendix).
-Finally, we discuss in Sec.~\ref{Discussion} applications of our mathematical observations as well as open questions.
+We discuss these results and their applications in depth in Sec.~\ref{Discussion} and outline open questions and directions for future research in Sec.~\ref{FutureDirections}.
 %The Appendix contains a proof of Lem.~\ref{MainLemma}.
-
-\section{Results}\label{Results}
 
@@
 %
-writing also $L_{k}$ in place of $L_\mathcal{H}$ when $\mathcal{H} = {[m] \choose k}$.\footnote{In compressed sensing literature, \mbox{$1 - \sqrt{k} L_k(\mathbf{M})$}  is the asymmetric lower restricted isometry constant for $\mathbf{M}$ with unit $\ell_2$-norm columns \cite{Blanchard2011}.}  As explained above, compactness implies that $L_{2k}(\mathbf{M}) > 0$ for all $\mathbf{M}$ satisfying \eqref{SparkCondition}.
+writing also $L_{k}$ in place of $L_\mathcal{H}$ when $\mathcal{H} = {[m] \choose k}$.\footnote{In compressed sensing literature, \mbox{$1 - \sqrt{k} L_k(\mathbf{M})$}  is the asymmetric lower restricted isometry constant for $\mathbf{M}$ with unit $\ell_2$-norm columns \cite{Blanchard2011}.\label{ripfootnote}}  As explained above, compactness implies that $L_{2k}(\mathbf{M}) > 0$ for all $\mathbf{M}$ satisfying \eqref{SparkCondition}.
 Clearly, $L_{\mathcal{H}'}(\mathbf{M}) \geq L_\mathcal{H}(\mathbf{M})$ whenever $\mathcal{H}' \subseteq \mathcal{H}$, and similarly any $k$-uniform $\mathcal{H}$ satisfying $\cup \mathcal{H} = [m]$ has $L_2 \geq L_{2\mathcal{H}} \geq L_{2k}$ (letting $L_{2k}$ := $L_m$ whenever $2k > m$).
+
+\section{Deterministic Guarantees}
 
@@
 \end{figure}
+
+\section{Uncertain Guarantees}
 
@@
 
-Consequently, if $k$ is held fixed or if the size of the support set of reconstructing codes is polynomial in $\overline m$ and $k$, then a practical (polynomial) amount of data suffices to identify the dictionary.\footnote{In the latter case, a reexamination of the pigeonholing argument in the proof of Thm.~\ref{DeterministicUniquenessTheorem} requires a polynomial number of samples distributed over a polynomial number of supports.} Reasons to be skeptical that this holds in general, however, can be found in \cite{tillmann2014computational, Tillmann15}.
+Consequently, if $k$ is held fixed or if the size of the support set of reconstructing codes is polynomial in $\overline m$ and $k$, then a practical (polynomial) amount of data suffices to identify the dictionary.\footnote{In the latter case, a reexamination of the pigeonholing argument in the proof of Thm.~\ref{DeterministicUniquenessTheorem} requires a polynomial number of samples distributed over a polynomial number of supports.} Reasons to be skeptical that this holds in general, however, can be found in \cite{tillmann2014computational, tillmann2015computational}.
 Even so, in the next section we discuss how probabilistic guarantees can in fact be made for any number of available samples.
 
-\section{Proofs}\label{DUT} % of Theorems~\ref{DeterministicUniquenessTheorem} and ~\ref{SLCopt}}\label{DUT}
+\section{Discussion}
 
-%%%%%%%%%%%%%%
-% need to cut maybe: 
-%As mentioned in the previous section, Thm.~\ref{DeterministicUniquenessTheorem} is a particular case of a more general result that forgoes the assumption that $\mathcal{H} \subseteq {[m] \choose k}$ is regular and satisfies the SIP.
-If instead we require only that the stars $\cap \sigma(i)$ intersect at singletons for all $i \leq q$ (assuming that the nodes of $\mathcal{H}$ are labeled in some order of non-increasing degree), we have that $\overline m \geq k|\mathcal{H}| / \deg(1)$ and, provided $\overline m < k|\mathcal{H}| / (\deg(1) - 1)$, the nonempty submatrix $J$ is of size equal to the largest number $p$ satisfying:
-%\begin{align}\label{pcond}
-%\sum_{i=\ell}^{m} \deg(i) > (\overline m + 1 - \ell) (\deg(\ell) - 1) \ \ \text{for all } \ell \leq p \leq q.
-%\end{align}
-%Specifically, $J$ contains all nodes of degree exceeding $\deg(p)$ and some subset of those with degreee equal to $\deg(p)$.
-For the benefit of the reader, we do not prove explicitly this more general result below; it can be discerned from how exactly Lemma \ref{NonEmptyLemma} is incorporated into the proof of Lem.~\ref{MainLemma}.
-%%%%%%%%%%%%%%%%
-
-%As mentioned in the previous section, Thm.~\ref{DeterministicUniquenessTheorem} is a particular case of a more general result, which requires a looser set of constraints on the hypergraph $\mathcal{H}$ and which applies to $n \times \overline m$ matrices $\mathbf{B}$ (and $\overline m$-dimensional codes $\mathbf{\overline x}_i$) with $\overline m \neq m$:
-
-%Fix $\overline m$ and suppose the assumptions of Thm.~\ref{DeterministicUniquenessTheorem} hold, only now with the constraints on $\mathcal{H} \subseteq {[m] \choose k}$ being just that $|\cap H(i)| = 1$ for all $i \leq q$ (assuming w.l.o.g.
-that the nodes of $\mathcal{H}$ are labeled in some order of non-increasing degree), and with more than $(k-1){\overline m \choose k}$ vectors $\mathbf{x}_i$ supported in g.l.p.
-on each $S \in \mathcal{H}$.
-Then we must have $\overline m \geq k|\mathcal{H}| / \deg(1)$ and, provided $\overline m < k|\mathcal{H}| / (\deg(1) - 1)$, the guarantee \eqref{Cstable} holds for a submatrix $\mathbf{A}_J$, where $J \subseteq[m]$ is nonempty and of a size equal to the largest number $p$ satisfying:
-%\begin{align}\label{pcond}
-%\sum_{i=\ell}^{m} \deg(i) > (\overline m + 1 - \ell) (\deg(\ell) - 1) \ \ \text{for all } \ell \leq p \leq q.
-%\end{align}
-%Specifically, $J$ consists of the union of the set of all nodes of degree exceeding $\deg(p)$ and some subset of those nodes with degrees equal to $\deg(p)$.
-
-%For the benefit of the reader, we prove below the case where we forgo only the constraint that $\overline m = m$.
-This yields the implication $\overline m \geq m$ and \eqref{pcond} reduces to $|J| = \overline m - r(\overline m - m)$.
-The extension to the general result above can be seen by examining how exactly Lemma \ref{NonEmptyLemma} is incorporated into the overall proof.
-
-% ======== b - PDa =========
-
-% WITH EXPLICIT J SUBSCRIPT
-%We begin our proof of Thm.~\ref{DeterministicUniquenessTheorem} by showing how dictionary recovery \eqref{Cstable} already implies sparse code recovery \eqref{b-PDa} when $\mathbf{A}_J$ satisfies \eqref{SparkCondition} and \mbox{$\varepsilon < L_{2k}(\mathbf{A}_J) / C_1$}.
-%, assuming that $\overline m = m$ without loss of generality.
-%Consider any $2k$-sparse $\mathbf{x} \in \mathbb{R}^m$ and note that $\|\mathbf{x}\|_1 \leq \sqrt{2k}  \|\mathbf{x}\|_2$. By definition of $L_{2k}$ in \eqref{Ldef}, we have:
-%\begin{align}\label{stuff}
-%\|\mathbf{x}_J - &( \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x} )_J\|_1 \nonumber
-%\leq \frac{\|(\mathbf{BPD})_J(\mathbf{x}_J - (\mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x})_J)\|_2}{L_{2k}((\mathbf{BPD})_J)} \\ \nonumber
-%&\leq \frac{\|( (\mathbf{BPD})_J - \mathbf{A}_J) \mathbf{x}_J\|_2 + \|\mathbf{A}_J\mathbf{x}_J - \mathbf{B}_J\mathbf{\overline x}_J\|_2}{L_{2k}((\mathbf{BPD})_J)} \\
-%&\leq \frac{C_1\varepsilon \|\mathbf{x}_J\|_1 + \varepsilon}{L_{2k}((\mathbf{BPD})_J)},
-%\end{align}
-%where the term $C_1\varepsilon \|\mathbf{x}_J\|_1$ in the numerator above is a consequence of the triangle inequality applied to \eqref{Cstable}.
-
-%It remains for us to bound the denominator.  By the reverse triangle inequality:
-%\begin{align*}
-%\|(\mathbf{BPD})_J\mathbf{x}_J\|_2 
-%&\geq | \|\mathbf{A}_J\mathbf{x}_J\|_2 - \|(\mathbf{A}_J - (\mathbf{BPD})_J)\mathbf{x}_J\|_2 | \\
-%&\geq \sqrt{2k} (L_{2k}(\mathbf{A}_J) -  C_1\varepsilon) \|\mathbf{x}_J\|_2,
-%\end{align*}
-%
-%wherein removal of the absolute value is justified since $C_1\varepsilon < L_{2k}(\mathbf{A}_J)$.
-We therefore have that $L_{2k}((\mathbf{BPD})_J) \geq L_{2k}(\mathbf{A}_J) - C_1\varepsilon  > 0$, and \eqref{b-PDa} then follows from \eqref{stuff}.
-
-% WITHOUT J SUBSCRIPT
-We begin our proof of Thm.~\ref{DeterministicUniquenessTheorem} by showing how dictionary recovery \eqref{Cstable} already implies sparse code recovery \eqref{b-PDa} when $\mathbf{A}$ satisfies \eqref{SparkCondition} and \mbox{$\varepsilon < L_{2k}(\mathbf{A}) / C_1$}.
-We temporarily assume (without loss of generality) that $\overline m = m$, so as to omit an otherwise requisite subscript $(\cdot)_J$ around certain matrices and vectors.
-By definition of $L_{2k}$ in \eqref{Ldef}, and noting that $\sqrt{k} \|\mathbf{v}\|_2 \geq \|\mathbf{v}\|_1$ for $k$-sparse $\mathbf{v}$, we have for all $i \in [N[$:
-\begin{align}\label{stuff}
-\|\mathbf{x}_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_i \|_1 \nonumber
-&\leq \frac{\|\mathbf{BPD}(\mathbf{x}_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_i)\|_2}{L_{2k}(\mathbf{BPD})} \\ \nonumber
-&\leq \frac{\|( \mathbf{BPD} - \mathbf{A}) \mathbf{x}_i\|_2 + \|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline x}_i\|_2}{L_{2k}(\mathbf{BPD})} \\
-&\leq \frac{C_1\varepsilon \|\mathbf{x}_i\|_1 + \varepsilon}{L_{2k}(\mathbf{BPD})},
-\end{align}
-%\begin{align}\label{stuff}
-%\frac{ \|\mathbf{x} - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x} \|_1 } { \|\mathbf{D}^{-1}\|_1 }  \
-%&\leq \|\mathbf{Dx} - \mathbf{P}^{\top}\mathbf{\overline x} \|_1 \\ \nonumber
-%&\leq \frac{\|\mathbf{BP}(\mathbf{D}\mathbf{x} - \mathbf{P}^{\top}\mathbf{\overline x})\|_2}{L_{2k}(\mathbf{BP})} \\ \nonumber
-%&\leq \frac{\|( \mathbf{BPD} - \mathbf{A}) \mathbf{x}\|_2 + \|\mathbf{A}\mathbf{x} - \mathbf{B}\mathbf{\overline x}\|_2}{L_{2k}(\mathbf{BP})} \\
-%&\leq \frac{C_1\varepsilon \|\mathbf{x}\|_1 + \varepsilon}{L_{2k}(\mathbf{BP})},
-%\end{align}
-where the first term in the numerator above follows from the triangle inequality and \eqref{Cstable}.
-
-It remains for us to bound the denominator. For any $2k$-sparse $\mathbf{x}$, we have by the triangle inequality:
-\begin{align*}
-\|\mathbf{BPD}\mathbf{x}\|_2 
-&\geq \|\mathbf{A}\mathbf{x}\|_2 - \|(\mathbf{A} - \mathbf{BPD})\mathbf{x}\|_2 \\
-&\geq \sqrt{2k} (L_{2k}(\mathbf{A}) -  C_1\varepsilon) \|\mathbf{x}\|_2,
-\end{align*}
-
-%\begin{align*}
-%\|\mathbf{BP}\mathbf{x}\|_2 
-%&\geq \|\mathbf{A}\mathbf{D}^{-1}\mathbf{x}\|_2 - \|(\mathbf{A} - \mathbf{BPD})\mathbf{D}^{-1}\mathbf{x}\|_2 \\
-%&\geq \sqrt{2k} (L_{2k}(\mathbf{A}) -  C_1\varepsilon) \|\mathbf{D}^{-1}\mathbf{x}\|_2, \\ 
-%&\geq \sqrt{2k} (L_{2k}(\mathbf{A}) -  C_1\varepsilon) \|\mathbf{D}^{-1}\|_{?} \| \mathbf{x}\|_2,
-%\end{align*}
-%
-We therefore have that $L_{2k}(\mathbf{BPD}) \geq L_{2k}(\mathbf{A}) - C_1\varepsilon  > 0$, and \eqref{b-PDa} then follows from \eqref{stuff}.
-The reader may also verify that $L_{2k}(\mathbf{BP}) \geq L_{2k}(\mathbf{BPD}) / \|\mathbf{D}\|_1$.
-
-The heart of the matter is therefore \eqref{Cstable}, which we now establish beginning with the important special case of $k = 1$.
-
-\begin{proof}[Proof of Thm.~\ref{DeterministicUniquenessCorollary} for $k=1$]
-Since the only 1-uniform hypergraph with the SIP is $[m]$, which is obviously regular, we require only $\mathbf{x}_i = c_i \mathbf{e}_i$ for $i \in [m]$, with $c_i \neq 0$ to guarantee  linear independence.
-While we have yet to define $C_1$ generally, in this case we may set $C_1 = 1/ \min_{\ell \in [m]} |c_{\ell}|$ so that $\varepsilon < L_2(\mathbf{A})  \min_{\ell \in [m]} |c_{\ell}|$.
-
-Fix $\mathbf{A} \in \mathbb{R}^{n \times m}$ satisfying $L_2(\mathbf{A}) > 0$, since here we have $2\mathcal{H} = {[m] \choose 2}$, and suppose some $\mathbf{B}$ and $1$-sparse $\mathbf{\overline x}_i \in \mathbb{R}^{\overline m}$ have  $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \varepsilon < L_2(\mathbf{A}) / C_1$ for all $i$.
-Then, there exist $\overline{c}_1, \ldots, \overline{c}_m \in \mathbb{R}$ and a map $\pi: [m] \to [\overline m]$ such that:
-\begin{align}\label{1D}
-\|c_i\mathbf{A}_i - \overline{c}_i\mathbf{B}_{\pi(i)}\|_2 \leq \varepsilon,\ \ \text{for $i \in [m]$}.
-\end{align} 
-Note that $\overline{c}_i \neq 0$, since otherwise we would reach the following contradiction: $\|\mathbf{A}_i \|_2 \leq C_1 |c_i| \|\mathbf{A}_i \|_2  \leq C_1\varepsilon < L_2(\mathbf{A}) \leq L_1(\mathbf{A}) = \min_{i \in [m]} \|\mathbf{A}_{i}\|_2$.
-%implies by \eqref{delrho} the contradiction $|c_i| < \min_{\ell \in [m]} | c_\ell |$.
-
-We now show that $\pi$ is injective (in particular, a permutation if $\overline m = m$).
-Suppose that $\pi(i) = \pi(j) = \ell$ for some $i \neq j$ and $\ell$.
-Then, $\|c_{i}\mathbf{A}_{i} - \overline{c}_{i} \mathbf{B}_{\ell}\|_2  \leq \varepsilon$ and $\|c_{j}\mathbf{A}_{j} - \overline{c}_{j}\mathbf{B}_{\ell}\|_2 \leq \varepsilon$, and we have: %Scaling and summing these inequalities by $|\overline{c}_{i}|$ and $|\overline{c}_{j}|$, respectively, and applying the triangle inequality to annihilate the terms in $\mathbf{B}_\ell$, we obtain:
-\begin{align*}
-(|\overline{c}_{i}| + |\overline{c}_{j}|) \varepsilon
-&\geq |\overline{c}_{i}| \|c_{j}\mathbf{A}_{j} - \overline{c}_{j}\mathbf{B}_{\ell}\|_2  + |\overline{c}_{j}| \|c_{i}\mathbf{A}_{i} - \overline{c}_{i} \mathbf{B}_{\ell}\|_2 \nonumber \\
-&\geq \|\mathbf{A}(\overline{c}_{i}c_{j} \mathbf{e}_{j} - \overline{c}_{j}c_{i}\mathbf{e}_{i})\|_2 \nonumber \\ 
-&\geq \sqrt{2}  L_2(\mathbf{A}) \|\overline{c}_{i}c_{j} \mathbf{e}_{j} - \overline{c}_{j}c_{i}\mathbf{e}_{i}\|_2 \nonumber \\
-&\geq  L_2(\mathbf{A}) \left( |\overline{c}_{i}| + |\overline{c}_{j}| \right) \min_{\ell \in [m]} |c_\ell |,
-\end{align*}
-contradicting our assumed upper bound on $\varepsilon$. Hence, the map $\pi$ is injective and so $\overline m \geq m$. %Setting $\overline J = \pi([m])$ and
-
-Letting $\mathbf{P}$ and $\mathbf{D}$ be the $\overline m \times \overline m$ permutation and invertible diagonal matrices with, respectively, columns $\mathbf{e}_{\pi(i)}$ and $\frac{\overline{c}_i}{c_i}\mathbf{e}_i$ for $i \in [m]$ (otherwise, $\mathbf{e}_{i}$ for $i \in [\overline{m}] \setminus [m]$), we may rewrite \eqref{1D} to see that for all $i \in [m]$:
-\begin{align*}
-\|\mathbf{A}_i - (\mathbf{BPD})_i\|_2 
-= \|\mathbf{A}_i - \frac{\overline{c}_i}{c_i}\mathbf{B}_{\pi(i)}\|_2 
-\leq \frac{\varepsilon}{|c_i|} 
-\leq C_1\varepsilon.
-\end{align*}
-%\vspace{-.2 cm}
-\end{proof}
-
-An extension of the proof to the general case $k < m$ requires some additional tools to derive the general expression \eqref{Cdef1} for $C_1$.
-These include a generalized notion of distance (Def.~\ref{dDef}) and angle (Def.~\ref{FriedrichsDefinition}) between subspaces as well as a stability result in combinatorial matrix analysis (Lem.~\ref{MainLemma}).
-
-\begin{definition}\label{dDef}
-For $\mathbf{u} \in \mathbb R^m$ and vector spaces $U,V \subseteq \mathbb{R}^m$, let $\text{\rm dist}(\mathbf{u}, V) := \min \{\| \mathbf{u}-\mathbf{v} \|_2: \mathbf{v} \in V\}$ and define:
-\begin{align}
-d(U,V) := \max_{\mathbf{u} \in U, \ \|\mathbf{u}\|_2 \leq 1} \text{\rm dist}(\mathbf{u},V).
-\end{align}
-\end{definition}
-
-We note the following facts about $d$. Clearly, 
-\begin{align}\label{UsubU}
-U' \subseteq U \implies d(U',V) \leq d(U,V).
-\end{align}
-From \cite[Ch.~4 Cor.~2.6]{Kato2013}, we also have: %Kato p.223
-\begin{align}\label{dimLem}
-d(U,V) < 1 \implies \dim(U) \leq \dim(V),
-\end{align}
-and from \cite[Lem.~3.2]{Morris10}:
-\begin{align}\label{eqdim}
-\dim(U) = \dim(V) \implies d(U,V) = d(V,U).
-\end{align}
-
-The following is our result in combinatorial matrix analysis; it contains most of the complexity in the proof of Thm.~\ref{DeterministicUniquenessTheorem}.
-
-\begin{lemma}\label{MainLemma}
-If an $n \times m$ matrix $\mathbf{A}$ has $L_{2\mathcal{H}}(\mathbf{A}) > 0$ for some $r$-regular $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP, then the following holds for $C_2 > 0$ given by \eqref{Cdef2}:
-
-Fix $\varepsilon < L_2(\mathbf{A}) / C_2$. If for some $n \times \overline m$ matrix $\mathbf{B}$ and map $\pi: \mathcal{H} \mapsto {[\overline m] \choose k}$,
-\begin{align}\label{GapUpperBound}
-d(\bm{\mathcal{A}}_S, \bm{\mathcal{B}}_{\pi(S)}) \leq \varepsilon, \ \  \text{for $S \in \mathcal{H}$},
-\end{align}
-then $\overline m \geq m$, and provided $\overline m (r-1) < mr$, there is a permutation matrix $\mathbf{P}$ and invertible diagonal $\mathbf{D}$ such that:
-\begin{align}\label{MainLemmaBPD}
-\|\mathbf{A}_i - (\mathbf{B}\mathbf{PD})_i\|_2 \leq C_2 \varepsilon, \ \  \text{for } i \in J,
-\end{align}
-for some $J \subseteq [m]$ of size \mbox{$m - (r-1)(\overline m - m)$}.
-\end{lemma}
-
-%\begin{lemma}\label{MainLemma}
-%Fix $\mathbf{A} \in \mathbb{R}^{n \times m}$ with $L_\mathcal{H}(\mathbf{A}) > 0$ for some regular $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP.
-There exists a constant $C_2 > 0$ for which the following holds for all $\varepsilon < L_2(\mathbf{A}) / C_2$:
-
-%If a matrix $\mathbf{B} \in \mathbb{R}^{n \times m}$ and map $\pi: E \mapsto {m \choose k}$ satisfy:
-%\begin{align}\label{GapUpperBound}
-%d(\text{\rm span}\{\mathbf{A}_{S}\}, \bm{\mathcal{B}}_{\pi(S)}) \leq \varepsilon, \ \ \text{for $S \in \mathcal{H}$},
-%\end{align}
-%then there exist a permutation matrix $\mathbf{P}$ and invertible diagonal matrix $\mathbf{D}$ such that:
-%\begin{align}\label{MainLemmaBPD}
-%\|\mathbf{A}_j - \mathbf{BPD}_j\|_2 \leq C_2 \varepsilon, \ \  \text{for } j \in [m],
-%\end{align}
-%\end{lemma}
-
-We present the constant $C_2$ (a function of $\mathbf{A}$ and $\mathcal{H}$) relative to a quantity used in \cite{Deutsch12} to analyze the convergence of the ``alternating projections" algorithm for projecting a point onto the intersection of subspaces.
-We incorporate this quantity into the following definition, which we refer to in our proof of Lem.~\ref{DistanceToIntersectionLemma} in the Appendix; specifically, we use it to bound the distance between a point and the intersection of subspaces given an upper bound on its distance from each subspace.
-
-\begin{definition}\label{FriedrichsDefinition}
-For a collection of real subspaces $\mathcal{V} = \{V_i\}_{i=1}^\ell$, define $\xi(\mathcal{V}) := 0$ when $|\mathcal{V}| = 1$, and otherwise:
-\begin{align}\label{xi}
-\xi^2(\mathcal{V}) := 1 -  \max \prod_{i=1}^{\ell-1} \sin^2  \theta \left(V_i, \cap_{j>i} V_j \right) ,
-\end{align} 
-%
-where the maximum is taken over all ways of ordering 
-%\footnote{We modify the quantity in \cite{Deutsch12} in this way since the subspace ordering is irrelevant to our purpose.} 
-the $V_i$ and the angle $\theta \in (0,\frac{\pi}{2}]$ is defined implicitly as \cite[Def.~9.4]{Deutsch12}:
-\begin{align*}
-\cos{\theta(U,W)} := \max\left\{ |\langle \mathbf{u}, \mathbf{w} \rangle|: \substack{ \mathbf{u} \in U \cap (U \cap W)^\perp, \ \|\mathbf{u}\|_2 \leq 1 \\ \mathbf{w} \in W \cap (U \cap W)^\perp, \  \|\mathbf{w}\|_2 \leq 1 } \right\}.
-\end{align*}
-\end{definition}
-Note that $\theta \in (0,\frac{\pi}{2}]$ implies $0 \leq \xi < 1$, and that $\xi(\mathcal{V}') \leq \xi(\mathcal{V})$ when $\mathcal{V}' \subseteq \mathcal{V}$.\footnote{We acknowledge the counter-intuitive property: $\theta =  \pi/2$ when $U \subseteq W$.}
-
-The constant $C_2 > 0$ of Lem.~\ref{MainLemma} can now be expressed as:  
-\begin{align}\label{Cdef2}
-	C_2(\mathbf{A}, \mathcal{H}) := \frac{ (r+1) \max_{j \in [m]} \|\mathbf{A}_j\|_2}{ 1- \max_{\mathcal{G} \in {\mathcal{H} \choose r+1}} \xi( \bm{\mathcal{A}}_\mathcal{G} ) }.
-\end{align}
-
-We next define the constant $C_1 > 0$ of Thm.~\ref{DeterministicUniquenessTheorem} in terms of $C_2$.
-Given vectors $\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$, let $\mathbf{X}$ denote the $m \times N$ matrix with columns $\mathbf{x}_i$ and let $I(S)$ denote the set of indices $i$ for which $\mathbf{x}_i$ is supported in $S$.
-We define:
-\begin{align}\label{Cdef1}
-C_1(\mathbf{A}, \mathcal{H}, \{\mathbf{x}_i\}_{i=1}^N) := \frac{ C_2(\mathbf{A}, \mathcal{H}) } { \min_{S \in \mathcal{H}} L_k(\mathbf{AX}_{I(S)}) }.
-\end{align}
-Given the assumptions of Thm.~\ref{DeterministicUniquenessTheorem} on $\mathbf{A}$ and the $\mathbf{x}_i$, this expression for $C_1$ is well-defined\footnote{\label{note1}To see this, fix $S \in \mathcal{H}$ and $k$-sparse $\mathbf{c}$.
-Using the definitions, we have $\|\mathbf{AX}_{I(S)}\mathbf{c}\|_2 \geq \sqrt{k} L_\mathcal{H}(\mathbf{A})\|\mathbf{X}_{I(S)}\mathbf{c}\|_2 \geq k L_\mathcal{H}(\mathbf{A}) L_k(\mathbf{X}_{I(S)})\|\mathbf{c}\|_2$.
-Thus, $L_k(\mathbf{AX}_{I(S)}) \geq \sqrt{k} L_\mathcal{H}(\mathbf{A}) L_k(\mathbf{X}_{I(S)}) > 0$, since $L_{\mathcal{H}}(\mathbf{A}) \geq L_{2\mathcal{H}}(\mathbf{A})> 0$ and $L_k(\mathbf{X}_{I(S)}) > 0$ by general linear position of the $\mathbf{x}_i$.} and yields an upper bound on $\varepsilon$ consistent with that proven sufficient in the case $k=1$ considered at the beginning of this section.\footnote{When $\mathbf{x}_i = c_i\mathbf{e}_i$, we have $C_2 \geq 2\|\mathbf{A}_i\|_2$ and the denominator in \eqref{Cdef1} becomes $\min_{i \in [m]} |c_i| \|\mathbf{A}_i\|_2$; hence, $C_1 \geq 2 / \min_{i \in [m]} |c_i|$.}
-% C_2(\mathbf{A}, \mathcal{H}) := \frac{ (r+1) \max_{j \in [m]} \|\mathbf{A}_j\|_2}{ \min_{\mathcal{G} \in {\mathcal{H} \choose r} \cup {\mathcal{H} \choose r+1}} \xi( \{ \bm{\mathcal{A}}_S \}
-
-The practically-minded reader should note that the explicit constants $C_1$ and $C_2$ are effectively computable: the quantity $L_k$ may be calculated as the smallest singular value of a certain matrix, while the quantity $\xi$ involves computing ``canonical angles'' between subspaces, which reduces again to an efficient singular value decomposition.
-There is no known fast computation of $L_k$ in general, however, since even $L_{k} > 0$ is NP-hard \cite{tillmann2014computational}, although 
-efficiently computable bounds have been proposed (e.g., via the ``mutual coherence" of a matrix \cite{donoho2003optimally}); alternatively, 
-fixing $k$ yields polynomial complexity.
-Moreover, calculating $C_2$ requires an exponential number of queries to $\xi$ unless $r$ is held fixed, too (e.g., the ``cyclic order'' hypergraphs described above have $r=k$).
-Thus, as presented, $C_1$ and $C_2$ are not efficiently computable in general.
-% , but efficient subcases do exist and may be of practical relevance.
-
-\begin{proof}[Proof of Thm.~\ref{DeterministicUniquenessCorollary} for $k < m$] 
-We find a map $\pi: \mathcal{H} \to {[m] \choose k}$ for which the distance $d(\bm{\mathcal{A}}_S, \bm{\mathcal{B}}_{\pi(S)})$ is controlled by $\varepsilon$ for all $S \in \mathcal{H}$.
-Applying Lem.~\ref{MainLemma} then completes the proof.
-%We shall show that for every $S \in \mathcal{H}$ there is some $\overline S \in {[\overline m] \choose k}$ for which the distance $d(\bm{\mathcal{A}}_S, \bm{\mathcal{B}}_{\overline S})$ is controlled by $\varepsilon$.
-Applying Lem.~\ref{MainLemma} with the map $\pi$ defined by $S \mapsto \overline S$ then completes the proof.
-
-Fix $S \in \mathcal{H}$.
-Since there are more than $(k-1){\overline m \choose k}$ vectors $\mathbf{x}_i$ supported in $S$, by the pigeonhole principle there must be some $\overline S \in {[\overline m] \choose k}$ and a set of $k$ indices $K \subseteq I(S)$ for which all $\mathbf{\overline x}_i$ with $i \in K$ are supported in $\overline S$.
-It also follows\footnotemark[\ref{note1}] from $L_{2\mathcal{H}}(\mathbf{A}) > 0$ and the general linear position of the $\mathbf{x}_i$ that $L_k(\mathbf{AX}_{K}) > 0$; that is, the columns of the $n \times k$ matrix $\mathbf{AX}_K$ form a basis for $\bm{\mathcal{A}}_S$.
-
-Fixing $\mathbf{y} \in \bm{\mathcal{A}}_S \setminus \{\mathbf{0}\}$, there then exists $\mathbf{c} = (c_1, \ldots, c_k) \in \mathbb{R}^k \setminus \{\mathbf{0}\}$ such that $\mathbf{y} = \mathbf{AX}_K\mathbf{c}$.
-Setting \mbox{$\mathbf{\overline{y}} = \mathbf{B\overline{X}}_K\mathbf{c}$, which is in $\bm{\mathcal{B}}_{\overline S}$}, we have by triangle inequality:
-\begin{align*}
-\|\mathbf{y} - \mathbf{\overline{y}}\|_2 
-%&= \|\sum_{i=1}^k c_i(\mathbf{AX}_K - \mathbf{B\overline{X}}_K)_i\|_2
-&= \|(\mathbf{AX}_K - \mathbf{B\overline{X}}_K)\mathbf{c}\|_2
-%\leq \varepsilon \sum_{i=1}^k |c_i| \\
-\leq \varepsilon \|\mathbf{c}\|_1
-\leq \varepsilon \sqrt{k}  \|\mathbf{c}\|_2  \\
-&\leq \frac{\varepsilon}{L_k(\mathbf{AX}_K)} \|\mathbf{y}\|_2,
-\end{align*}
-where the last inequality uses \eqref{Ldef}. From Def.~\ref{dDef}:
-\begin{align}\label{rhs222}
-d(\bm{\mathcal{A}}_S, \bm{\mathcal{B}}_{\overline S}) 
-\leq \frac{\varepsilon}{  L_k(\mathbf{AX}_{K}) } 
-\leq \frac{\varepsilon}{  L_k(\mathbf{AX}_{I(S)}) } 
-\leq \varepsilon \frac{C_1}{C_2}.
-\end{align}
-%
-Finally, apply Lem.~\ref{MainLemma} with $\varepsilon < L_2(\mathbf{A})/C_1$ and $\pi(S) := \overline S$. % L_2(A) > 0 by def of L, since L_2H(A) > 0 and H covers [m]
-\end{proof}
-
-Before moving on to the proof of Thm.~\ref{SLCopt}, we briefly revisit our discussion on sample complexity from the end of the previous section.
-While an exponential number of samples may very well prove to be necessary in the deterministic or almost-certain case, our proof of Thm.~\ref{DeterministicUniquenessTheorem} can be extended to hold with some probability for \emph{any} number of samples by alternative appeal to a probabilistic pigeonholing at the point early in the proof where the (deterministic) pigeonhole principle is applied to show that for every $S \in \mathcal{H}$, there exist $k$ vectors $\mathbf{x}_i$ supported on $S$ whose corresponding $\mathbf{\overline x}_i$ all share the same support.\footnote{A famous example of such an argument is the counter-intuitive ``birthday paradox", which demonstrates that the probability of two people having the same birthday in a room of twenty-three is greater than 50\%.}
-Given insufficient samples, this argument has some less-than-certain probability of being valid for each $S \in \mathcal{H}$.
-Nonetheless, simulations with small hypergraphs confirm that the probability of success very quickly approaches one once the number of samples $N$ surpasses a small fraction of the deterministic sample complexity.
-
-\begin{proof}[Proof of Thm.~\ref{SLCopt}]
-We bound the number of $k$-sparse $\mathbf{\overline x}_i$ from below and then apply Thm.~\ref{DeterministicUniquenessCorollary}. 
-%We now apply this fact to bound the number of $k$-sparse $\mathbf{\overline x}_i$. 
-Let $n_p$ be the number of $\mathbf{\overline x}_i$ with $\|\mathbf{\overline x}_i\|_0 = p$.
-Since the $\mathbf{x}_i$ are all $k$-sparse, by \eqref{minsum} we have:
-\begin{align*}
-%\mbox{$k \sum_{p = 0}^{\overline m} n_p \geq \sum_{i=0}^N \|\mathbf{x}_i\|_0 \geq \sum_{i=0}^N \|\mathbf{\overline x}_i\|_0 = \sum_{p=0}^{\overline m} p n_p.$}
-\sum_{p=0}^{\overline m} p n_p =  \sum_{i=0}^N \|\mathbf{\overline x}_i\|_0
-\leq \sum_{i=0}^N \|\mathbf{x}_i\|_0 
-\leq kN
-\end{align*}
-Since $N = \sum_{p = 0}^{\overline m} n_p$, we then have $\sum_{p = 0}^{\overline m} (p-k) n_p \leq 0$. Splitting the sum yields:
-\begin{align}\label{eqn}
-\sum_{p = k+1}^{\overline m} n_p \leq \sum_{p = k+1}^{\overline m} (p-k) n_p \leq \sum_{p = 0}^k (k-p)n_p \leq k \sum_{p = 0}^{k-1} n_p,
-\end{align}
-%
-demonstrating that the number of vectors $\mathbf{\overline x}_i$ that are \emph{not} $k$-sparse is bounded above by how many are $(k-1)$-sparse.
-
-Next, observe that no more than $(k-1)|\mathcal{H}|$ of the $\mathbf{\overline x}_i$ share a support $\overline S$ of size less than $k$.
-Otherwise, by the pigeonhole principle, there is some $S \in \mathcal{H}$ and a set of $k$ indices $K \subseteq I(S)$ for which all $\mathbf{x}_i$ with $i \in K$ are supported in $S$; as argued previously, \eqref{rhs222} follows.
-It is simple to show that $L_2(\mathbf{A}) \leq \max_j\|\mathbf{A}_j\|_2$, and since $0 \leq \xi < 1$, the right-hand side of \eqref{rhs222} is less than one for $\varepsilon < L_2(\mathbf{A})/C_1$.
-Thus, by \eqref{dimLem} we would have the contradiction $k = \dim(\bm{\mathcal{A}}_S) \leq \dim(\bm{\mathcal{B}}_{\overline S}) \leq |\overline S| < k.$
-
-The total number of $(k-1)$-sparse vectors $\mathbf{\overline x}_i$ thus cannot exceed $|\mathcal{H}|(k-1){ \overline m \choose k-1}$.
-By \eqref{eqn}, no more than $|\mathcal{H}|k(k-1){ \overline m \choose k-1}$ vectors $\mathbf{\overline x}_i$ are not $k$-sparse.
-Since for every $S \in \mathcal{H}$ there are over $(k-1)\left[ {\overline m \choose k} + |\mathcal{H}|k{ \overline m \choose k-1} \right]$ vectors $\mathbf{x}_i$ supported there, it must be that more than $(k-1){\overline m \choose k}$ of them have corresponding $\mathbf{\overline x}_i$ that are $k$-sparse.
-The result now follows from Thm.~\ref{DeterministicUniquenessCorollary}, noting by the triangle inequality that $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline x}_i\| \leq 2\eta$ for $i = 1, \ldots, N$.
-\end{proof}
-
-%\begin{proof}[Proof (sketch) of Thm.~\ref{robustPolythm}]
-%Let $\textbf{M}$ be the matrix with columns $\mathbf{A}\mathbf{x}_i$, $i \in [N]$.
-Consider the polynomial $\prod_{S \in {[N] \choose 2k}} \sum_{S' \in {[n] \choose 2k}} (\det \textbf{M}_{S',S})^2$ in the indeterminate entries of $\mathbf{A}$ and $\mathbf{x}_i$, with notation as in Sec.~\ref{Results}.
-%It can be checked that when this polynomial is nonzero for a substitution of real numbers for the indeterminates, all of the genericity requirements on $\mathbf{A}$ and $\mathbf{x}_i$ in our proofs of stability in Thm.~\ref{DeterministicUniquenessTheorem} are satisfied (in particular, the spark condition \eqref{SparkCondition} on $\mathbf{A}$).
-%\end{proof}
-
-%\begin{proof}[Proof (sketch) of Cor.~\ref{ProbabilisticCor}]
-%First, note that if a set of measure spaces $\{(X_{\ell}, \Sigma_{\ell}, \nu_{\ell})\}_{\ell=1}^p$ has that $\nu_{\ell}$ is absolutely continuous with respect to $\mu$ for all $\ell \in [p]$, where $\mu$ is the standard Borel measure on $\mathbb{R}$, then the product measure $\prod_{\ell=1}^p \nu_{\ell}$ is absolutely continuous with respect to the standard Borel product measure on $\mathbb{R}^p$.
-% for space:  (e.g.,  \cite{folland2013real}).
-%By Thm.~\ref{robustPolythm}, there is a polynomial that is nonzero when $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$; in particular, stability holds almost surely.
-%\end{proof}
-
-\section{Discussion}\label{Discussion}
-
-A main motivation for this work is the emergence of seemingly unique representations from sparse coding models trained on natural data, despite the varied assumptions underlying the many algorithms in current use.
-Our results constitute an important step toward explaining these phenomena as well as unifying many publications on the topic by deriving general deterministic conditions under which identification of parameters in this model is not only possible but also robust to uncertainty in measurement and model choice.
-
-We have shown that, given sufficient data, the problem of determining a dictionary and sparse codes with minimal support size (Prob.~\ref{OptimizationProblem}) reduces to an instance of Prob.~\ref{InverseProblem}, to which our main result (Thm.~\ref{DeterministicUniquenessTheorem}) applies: every dictionary and sequence of sparse codes consistent with the data are equivalent up to inherent relabeling/scaling ambiguities and a discrepancy (error) that scales linearly with the measurement noise or modeling inaccuracy.
-The constants we provide are explicit and computable; as such, there is an effective procedure that sufficiently affirms if a proposed solution to these problems is indeed unique up to noise and inherent ambiguities, although it is not efficient in general.
-
-%A compelling feature of this model is its simple instantiation of the principle of Occam's razor: a natural video, for instance, is modeled as a linear combination of a small number of spatiotemporal building blocks, each representing an archetypical feature latent in the data.
-
-%For theoretical neuroscience in particular, dictionary learning and related methods have recovered characteristic components of natural images \cite{Olshausen96, hurri1996image, bell1997independent, van1998independent} and sounds \cite{bellsejnowski1996, smithlewicki2006} that reproduce response properties of certain cortical neurons.
-
-%to the recovery of ``mouse neuronal activity representing location on a track \cite{agarwal2014spatially}
-
-%Moreover, we show that even if the meta-parameter for the number of dictionary elements is overestimated, a subset of parameters may still be identifiable up to noise.
-
-Beyond an extension of existing noiseless guarantees \cite{Hillar15} to the noisy regime and their novel application to Prob.~\ref{OptimizationProblem}, our work contains a theory of combinatorial designs for support sets key to identification of dictionaries.
-We incorporate this idea into a fundamental lemma in matrix theory (Lem.~\ref{MainLemma}) that draws upon the definition of a matrix lower bound (\ref{Ldef}) induced by a hypergraph.
-The new insight offered by this combinatorial approach allows for guaranteed recovery of some or all dictionary elements even if: 1) dictionary size is overestimated, 2) data cover only a polynomial number of distinct sparse supports, and 3) dictionaries do not satisfy the spark condition.
-
-The absence of any assumptions about dictionaries solving Prob.~\ref{InverseProblem} was a major technical obstruction in proving Thm.~\ref{DeterministicUniquenessTheorem}.
-We sought such a general guarantee because of the practical difficulty in ensuring that an algorithm maintain a dictionary satisfying the spark condition \eqref{SparkCondition} at each iteration, an implicit requirement of all previous works except \cite{Hillar15}; indeed, even certifying a dictionary has this property is NP-hard \cite{tillmann2014computational}.
-
-One direct application of this work is to theoretical neuroscience, wherein our theorems justify the mathematical soundness of one of the few hypothesized theories of bottleneck communication in the brain \cite{Isely10}: that sparse neural population activity is recoverable from its noisy linear compression through a randomly constructed (but unknown) wiring bottleneck by any biologically plausible unsupervised sparse coding method that solves Prob.~\ref{DeterministicUniquenessTheorem} or \ref{SLCopt} (e.g., \cite{rehnsommer2007, rozell2007neurally, pehlevan2015normative}).\footnote{We refer the reader to \cite{ganguli2012compressed} for more on interactions between dictionary learning and neuroscience.}
-
-In fact, uniqueness guarantees with minimal assumptions apply to all areas of data science and engineering that utilize learned sparse structure.
-For example, several groups have applied compressed sensing to signal processing tasks; for instance, in MRI analysis \cite{lustig2008compressed}, image compression \cite{Duarte08}, and even the design of an ultrafast camera \cite{Gao14}.
-It is only a matter of time before these systems incorporate dictionary learning to encode and decode signals (e.g., in a device that learns structure from motion \cite{kong2016prior}), just as scientists have used sparse coding to make sense of their data \cite{jung2001imaging, agarwal2014spatially, lee2016sparse, wu2016stability}.
-
-Assurances offered by our theorems certify that different devices and algorithms learn equivalent representations given enough data from statistically identical systems.\footnote{To contrast with the current hot topic of ``Deep Learning'', there are few such uniqueness guarantees for these models of data; moreover, even small noise can dramatically alter their output \cite{goodfellow2014explaining}.}
-Indeed, a main reason for the sustained interest in dictionary learning as an unsupervised method for data analysis seems to be the assumed well-posedness of parameter identification in the model, confirmation of which forms the core of our findings.
-
-We close with some challenges left open by our work.
-All conditions stated here guaranteeing the uniqueness and stability of sparse representations have only been shown sufficient; it remains open, therefore, to extend them to necessary conditions, be they on required sample size, the structure of support set hypergraphs, or tolerable error bounds.
-On this last note, we remark that our deterministic treatment considers always the ``worst-case" noise, whereas the ``effective" noise sampled from a concentrated distribution might be significantly reduced, especially for high-dimensional data.
-It would be of great practical benefit to see how drastically all conditions can be relaxed by requiring only probabilistic guarantees in this way, or in the spirit of our discussion on probabilistic pigeonholing to reduce sample complexity (as in the famous ``birthday paradox") following the proof of Thm.~\ref{DeterministicUniquenessTheorem}.
-
-Another interesting question raised by our work is for which special cases is it efficient to check that a solution to Prob.~\ref{InverseProblem} or \ref{OptimizationProblem} is unique up to noise and inherent ambiguities.
-Considering that the sufficient conditions we have described for checking this in general are NP-hard to compute, are the necessary conditions hard?
-Are Probs.~\ref{InverseProblem} and \ref{OptimizationProblem} then also hard (e.g., see \cite{Tillmann15})?
-Finally, since Prob.~\ref{SLCopt} is intractable in general, but efficiently solvable by $\ell_1$-norm minimization when the matrix is known (and has a large enough lower bound over sparse domains \cite{eldar2012compressed}), is there a version of Thm.~\ref{SLCopt} certifying when Prob.~\ref{OptimizationProblem} can be solved efficiently in full by similar means?
-% [*** Incorporate this open problem with more words ***]
-
-We hope these remaining challenges pique the interest of the community to pick up where we have left off and that the theoretical tools showcased here may be of use to this end.
-
-%We close with some challenges left open by our work.
-First, there is the basic problem of proving optimal lower bounds on sufficient sample size $N$ guaranteeing the uniqueness and stability of sparse representations.
-The pigeonholing argument in the proof of Thm.~\ref{DeterministicUniquenessTheorem} is loose in that it assigns to each support $S \in \mathcal{H}$ a corresponding support $\overline S$ without consideration of previously matched pairs; although we doubt tightening in this way will lead to sub-exponential sample sizes.
-Sample complexity will also benefit from lowering the number of required supports, i.e.
-the size of regular uniform hypergraphs satisfying the SIP.
-The regularity requirement on support hypergraphs can be loosened to allow for certain non-regular hypergraphs satisfying constraints on the degree sequence of nodes; though we impose regularity for clarity of exposition.
-It is then natural to ask: what is the smallest hypergraph satisfying the required constraints forgiven $m$ and $k$?
-Finally, the error bounds can be improved by tightening the constant $C_1$, e.g.
-via an improvement in Lemma ?.
-
-%Solving Prob.~\ref{SLCopt} directly is intractable in general since it necessitates, for each proposed dictionary $\mathbf{B}$, a combinatorial search for the supports of the associated sparse codes $\mathbf{\overline x}_i$.
-A common work-around is to convexify the problem (for fixed $\mathbf{B}$) by substituting the norm $\|\cdot\|_0$ with $\|\cdot\|_1$, impelled the fact that matrices $\mathbf{A}$ with large enough $L_{2k}(\mathbf{A})$ induce the same sparse codes via minimization of either norm \cite{?}.
-To this end, the lower bound $L_{2k}(\mathbf{BP}) \geq (L_{2k}(\mathbf{A}) - C_1\varepsilon) / \|\mathbf{D}\|_1$ implied by Thm.~\ref{DeterministicUniquenessTheorem} hints at conditions on the generating dictionary $\mathbf{A}$ and $k$-sparse codes $\mathbf{x}_i$ under which \emph{all} matrices $\mathbf{B}$ (of bounded column-norm) that solve Prob.~\ref{OptimizationProblem} also share this property of $\mathbf{A}$ by virtue of uniqueness and stability.
-One might then imagine an inference procedure whereby sparse codes are inferred via minimization of $\|\cdot\|_1$, but solutions still evaluated by their collective support size, yielding unique optimal solutions to Prob.~\ref{SLCopt} if only constraints could be imposed such that the learning procedure eventually guides $\mathbf{B}$ through an optimal dictionary.
-% (e.g.
-the dictionary is a member of a known finite set).
-
-\textbf{Acknowledgement.} We thank Fritz Sommer and Darren Rhea for early thoughts, and Ian Morris for posting \eqref{eqdim} online.
-
-%\section{EXTRA}
-%An additional consequence of Thm.~\ref{DeterministicUniquenessTheorem} of potential practical relevance to is the implied lower bound $L_{2k}(\mathbf{BPD}) \geq L_{2k}(\mathbf{A}) - C_1\varepsilon$ in the case where $\mathbf{A}$ satisfies \eqref{SparkCondition}.
-Since solving Prob.~\ref{SLCopt} directly requires a combinatorial search over sparse supports for the $\mathbf{\overline x}_i$ for each proposed dictionary $\mathbf{B}$, rendering it intractable in general, a common strategy is to replace the $\ell_0$-norm in \eqref{minsum} with the $\ell_1$-norm, thereby transforming the inference of sparse $\mathbf{\overline x}_i$ for a fixed dictionary $\mathbf{B}$ into a convex optimization solvable by a linear program.
-A major advance in compressive sensing was the discovery that, for fixed $\mathbf{B}$, solutions to \eqref{minsum} using either norm yield the same sparse vectors $\mathbf{\overline x}_i$ (up to noise) provided $L_{2k}(\mathbf{B})$ is large enough \cite{?}.
-What our results hint at are conditions on the generating dictionary $\mathbf{A}$ and $k$-sparse codes $\mathbf{x}_i$ under which \emph{all} matrices $\mathbf{B}$ (of bounded column-norm) that solve Prob.~\ref{OptimizationProblem} also share this property by virtue of uniqueness and stability; that is, conditions which guarantee that the sparse codes $\mathbf{\overline x}_i$ solving Prob.~\ref{OptimizationProblem} also solve the convexified problem when the corresponding dictionary $\mathbf{B}$ is held fixed.
-It remains to determine, however, what practical conditions preclude matrices that don't solve Prob.~\ref{OptimizationProblem} from nonetheless solving the convexified problem.
-%
-%Regardless, an implication of the above observation is that the following algorithm solves Prob.~\ref{OptimizationProblem} without appeal to combinatorial search:
-%\begin{enumerate}
-%\item List all matrices $\mathbf{B}$.
-%\item For each matrix $\mathbf{B}$, solve $\mathbf{\overline x}_i = \arg \min \|\mathbf{v}\|_1$ s.t. $\|\mathbf{Bv} - \mathbf{z}_i\| \leq \eta$ for $i = 1, \ldots, N$.
-%\item Quantify the proposed solution $\mathbf{B}$ and $\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N$ as $\rho(\mathbf{B}, \mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N) = \sum_{i=1}^{N} \|\mathbf{\overline x}_i\|_0$.
-%\item Output $\arg \min_{\mathbf{B}, \mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N} \left( \rho \right)$.
-% \end{enumerate}
-
-%Since its inception some twenty years ago, sparse coding has become a standard tool in signal analysis, yielding myriad insights into the structure of natural signals across a variety of scientific domains.
-In this work,
-
-%We make a final remark about the tightness of our results and the computability of our derived constants.
-%We remark that our constants have been derived for deterministic ``worst-case'' noise, whereas the ``effective'' noise might be smaller when sampled from a distribution.
-
-%Our results suggest that this correspondence could be due to the ``universality'' of sparse representations in natural data, an early idea in neural theory \cite{pitts1947}.
-
-% \vspace{-.2 cm}
-
-%\showacknow % Display the acknowledgments section
-
-\bibliographystyle{IEEEtran}
-\bibliography{chazthm_ieee_trans_sig}
-
-% \vspace{-.2 cm}
-
-\section{Appendix}\label{proofs}
-
-We prove Lem.~\ref{MainLemma} after the following auxiliary lemmas.  % stating and proving some auxiliary lemmas. 
-%First, note that since $\|\mathbf{A}\mathbf{x}\|_2 \leq \max_j\|\mathbf{A}_j\|_2\|\mathbf{x}\|_1$ and $\|\mathbf{x}\|_1 \leq \sqrt{k} \|\mathbf{x}\|_2$ for $k$-sparse $\mathbf{x}$, by \eqref{Ldef} we have the following frequently applied inequality:
-%\begin{align}\label{delrho}
-%L_{k'}(\mathbf{A}) \leq  \max_j\|\mathbf{A}_j\|_2 \ \ \text{for all $k' \leq 2k$}.
-%\end{align}
-
-% and then sketch the proofs of Thm.~\ref{robustPolythm} and Cor.~\ref{ProbabilisticCor}.
-
-%\begin{lemma}\label{spanIntersectionLemma}
-%Let $\mathbf{M} \in \mathbb{R}^{n \times m}$. If every $2k$ columns of $\mathbf{M}$ are linearly independent, then for any $F \subseteq {[m] \choose k}$:
-%\begin{align*}
-%\text{\rm span}\{\mathbf{M}_{\cap F}\}  = \bigcap_{S \in F} \text{\rm span}\{\mathbf{M}_S\}.
-%\end{align*}
-%\end{lemma}
-%\begin{proof}
-%Using induction on $|F|$, it is enough to prove the lemma when $|F| = 2$; but this case follows directly from the assumption.
-%\end{proof}
-
-\begin{lemma}\label{spanIntersectionLemma}
-If $f: V \to W$ is injective, then $f\left(\cap_{i=1}^\ell V_i \right) =  \cap_{i=1}^\ell f\left(V_i\right)$ for any $V_1, \ldots, V_\ell \subseteq V$. ($f(\emptyset):=\emptyset$.)
-%In particular, if for some $E \in 2^{[m]}$ the map $M \in \mathbb{R}^{n \times m}$ is injective on $\cup_{S \in \mathcal{H}} \text{span}\{e_i\}_{i \in S}$ then $\text{span}\{ M_{\cap_{S \in \mathcal{H}} S} \} = \cap_{S \in \mathcal{H}} \text{span}\{M_S\}$.
-\end{lemma}
-\begin{proof}
-By induction, it is enough to prove the case $\ell = 2$.
-Clearly, for any map $f$, if $w \in f(U \cap V)$ then $w \in f(U)$ and $w \in f(V)$; hence, $w \in f(U) \cap f(V)$.
-If $w \in f(U) \cap f(V)$, then $w \in f(U)$ and $w \in f(V)$; thus, $w = f(u) = f(v)$ for some $u \in U$ and $v \in V$, implying $u = v$ by injectivity of $f$.
-It follows that $u \in U \cap V$ and $w \in f(U \cap V)$.
-\end{proof}
-In particular, if a matrix $\mathbf{A}$ satisfies $L_{2\mathcal{H}}(\mathbf{A}) > 0$, then taking $V$ to be the union of subspaces consisting of vectors with supports in $2\mathcal{H}$, we have $\bm{\mathcal{A}}_{\cap \mathcal{G}} = \cap \bm{\mathcal{A}}_\mathcal{G}$ for all $\mathcal{G} \subseteq \mathcal{H}$.
-% \vspace{-.4 cm}
-
-\begin{lemma}\label{DistanceToIntersectionLemma}
-Let $\mathcal{V} = \{V_i\}_{i=1}^k$ be a set of two or more subspaces of $\mathbb{R}^m$, and set $V = \cap \mathcal{V} $.
-For  $\mathbf{u} \in \mathbb{R}^m$, we have (recall Defs.~\ref{dDef}~\&~\ref{FriedrichsDefinition}):
-\begin{align}\label{DTILeq}
-\text{\rm dist}(\mathbf{u}, V) \leq \frac{1}{1 - \xi(\mathcal{V})} \sum_{i=1}^k \text{\rm dist}(\mathbf{u}, V_i).
-\end{align}
-\end{lemma}
-\begin{proof} 
-% When $V = \{\mathbf{0}\}$, the result is trivial, so suppose otherwise.  
-Recall the projection onto the subspace $V \subseteq \mathbb{R}^m$ is the mapping $\Pi_V: \mathbb{R}^m \to V$ that associates with each $\mathbf{u}$ its unique nearest point in $V$; i.e., $\|\mathbf{u} - \Pi_V\mathbf{u}\|_2 = \text{\rm dist}(\mathbf{u}, V)$.
-By repeatedly applying the triangle inequality, we have:
-\begin{align}\label{f}
-\|\mathbf{u} - &\Pi_V\mathbf{u}\|_2 
-\leq \|\mathbf{u} - \Pi_{V_k} \mathbf{u}\|_2 + \|\Pi_{V_k}  \mathbf{u} - \Pi_{V_k}\Pi_{V_{k-1}}\mathbf{u}\|_2 \nonumber \\
-&\ \ \ \ \ \ \ \ \ \ \ + \cdots + \|\Pi_{V_k} \Pi_{V_{k-1}}\cdots \Pi_{V_1} \mathbf{u} - \Pi_V \mathbf{u}\|_2 \nonumber \\
-&\leq  \sum_{\ell=1}^k \|\mathbf{u} - \Pi_{V_{\ell}} \mathbf{u}\|_2 
-+ \|(\Pi_{V_k}\cdots\Pi_{V_{1}} - \Pi_V) \mathbf{u}\|_2,
-\end{align}
-where we have also used that the spectral norm of the orthogonal projections $\Pi_{V_{\ell}}$ satisfies $\|\Pi_{V_{\ell}}\|_2 \leq 1$ for all $\ell$.
-
-It remains to bound the second term in \eqref{f} by $\xi(\mathcal{V}) \|\mathbf{u} - \Pi_V\mathbf{u}\|_2$.
-First, note that $\Pi_{V_\ell} \Pi_V = \Pi_V$ and $\Pi_V^2 = \Pi_V$, so we have $\|(\Pi_{V_k} \cdots \Pi_{V_1} - \Pi_V) \mathbf{u} \|_2
-= \| ( \Pi_{V_k} \cdots\Pi_{V_1} - \Pi_V ) (\mathbf{u} - \Pi_V\mathbf{u})\|_2$. % \leq z\|\mathbf{u} - \Pi_V\mathbf{u}\|_2$.
-Consequently, inequality \eqref{DTILeq} follows from \cite[Thm.~9.33]{Deutsch12}:
-\begin{align}
-\|\Pi_{V_k}\Pi_{V_{k-1}}\cdots\Pi_{V_1} \mathbf{x} - \Pi_V\mathbf{x}\|_2 \leq z \|\mathbf{x}\|_2, \ \ \text{for all } \mathbf{x},
-\end{align}
-with \mbox{$z^2= 1 - \prod_{\ell =1}^{k-1}(1-z_{\ell}^2)$} and \mbox{$z_{\ell} = \cos\theta\left(V_{\ell}, \cap_{s=\ell+1}^k V_s\right)$} (recall $\theta$ from Def.~\ref{FriedrichsDefinition}), after substituting $\xi(\mathcal{V})$ for $z$ and rearranging terms.
-\end{proof}
-\begin{lemma}\label{NonEmptyLemma} 
-Fix an $r$-regular hypergraph $\mathcal{H} \subseteq 2^{[m]}$ satisfying the SIP.
-If the map $\pi: \mathcal{H} \to 2^{[\overline m]}$ has $\sum_{S \in \mathcal{H}} |\pi(S)| \geq \sum_{S \in \mathcal{H}} |S|$ and:
-\begin{align}\label{cond}
-	|\cap \pi(\mathcal{G})| \leq |\cap \mathcal{G} |,\ \ \   \text{for } \mathcal{G} \in {\mathcal{H} \choose r} \cup {\mathcal{H} \choose r+1},
-\end{align}
-%
-then $\overline m \geq m$; and if $\overline m  (r-1) < mr$, the map $i \mapsto \cap_{S \in \sigma(i)} \pi(S)$ is an injective function to $[\overline m]$ from some $J \subseteq [m]$ of size $m - (r-1)(\overline m - m)$ (recall $\sigma$ from Def.~\ref{sip}).
-%In particular, if $\overline m = m$ then $\pi$ is induced by a permutation on $[m]$.
-\end{lemma}
-
-\begin{proof}
-Consider the following set: $T_1 := \{(i, S): i \in \pi(S), S \in \mathcal{H}\}$, which numbers $|T_1| = \sum_{S \in \mathcal{H}} |\pi(S)| \geq \sum_{S \in \mathcal{H}} |S| = \sum_{i \in [m]} \deg_\mathcal{H}(i) = mr$ by $r$-regularity of $\mathcal{H}$.
-Note that $|T_1| \leq \overline m r$; otherwise, pigeonholing the tuples of $T_1$ with respect to their $\overline m$ possible first elements would imply that more than $r$ of the tuples in $T_1$ share the same first element.
-This cannot be the case, however, since then some $\mathcal{G} \in {\mathcal{H} \choose r+1}$ formed from any $r+1$ of their second elements would satisfy $\cap \pi(\mathcal{G}) \neq 0$; hence, $|\cap \mathcal{G}| \neq 0$ by \eqref{cond}, contradicting $r$-regularity of $\mathcal{H}$.
-It follows that $\overline m \geq m$.
-
-Suppose now that $\overline m (r-1) < mr$, so that $p := mr - \overline m (r-1)$ is positive and $|T_1| \geq \overline m (r - 1) + p$.
-Pigeonholing $T_1$ into $[\overline m]$ again, there are at least $r$ tuples in $T_1$ sharing some first element; that is, for some $\mathcal{G}_1 \subseteq \mathcal{H}$ of size $|\mathcal{G}_1| \geq r$, we have $|\cap \pi(\mathcal{G}_1)| \geq 1$ and (by \eqref{cond}) $|\cap \mathcal{G}_1| \geq 1$.
-Since no more than $r$ tuples of $T_1$ can share the same first element, we in fact have $|\mathcal{G}_1| = r$.
-It follows by $r$-regularity that $\mathcal{G}_1$ is a star of $\mathcal{H}$; hence, $|\cap \mathcal{G}_1| = 1$ by the SIP and $|\cap \pi(\mathcal{G}_1)|  = 1$ by \eqref{cond}.
-
-If $p=1$, then we are done.
-Otherwise, define $T_2 := T_1 \setminus \{(i,S) \in T_1: i = \cap \pi(\mathcal{G}_1)\}$, which contains $|T_2| = |T_1| - r \geq (\overline m - 1)(r-1) + (p-1)$ ordered pairs having $\overline m - 1$ distinct first indices.
-Pigeonholing $T_2$ into $[\overline m - 1]$ and repeating the above arguments produces the star $\mathcal{G}_2 \in {\mathcal{H} \choose r}$ with intersection $\cap \mathcal{G}_2$ necessarily distinct (by $r$-regularity) from $\cap \mathcal{G}_1$.
-Iterating this procedure $p$ times in total yields the stars $\mathcal{G}_i$ for which $\cap\mathcal{G}_i \mapsto \cap \pi(\mathcal{G}_i)$ defines an injective map to $[\overline m]$ from $J = \{\cap \mathcal{G}_1, \ldots, \cap \mathcal{G}_p\} \subseteq [m]$.
-\end{proof}
-
-\begin{proof}[Proof of Lem.~\ref{MainLemma}]
-%We will show that the bound \eqref{GapUpperBound} trickles through the intersection semi-lattices of $\{\bm{\mathcal{A}}_S\}_{S \in \mathcal{H}}$ and $\{\bm{\mathcal{B}}_{\overline S}\}_{\overline S \in \pi(\mathcal{H})}$ to yield \eqref{MainLemmaBPD} by virtue of the SIP.
-We begin by showing that $\dim(\bm{\mathcal{B}}_{\pi(S)}) = \dim(\bm{\mathcal{A}}_S)$ for all $S \in \mathcal{H}$.
-Note that since $\|\mathbf{A}\mathbf{x}\|_2 \leq \max_j\|\mathbf{A}_j\|_2\|\mathbf{x}\|_1$ and $\|\mathbf{x}\|_1 \leq \sqrt{k} \|\mathbf{x}\|_2$ for all $k$-sparse $\mathbf{x}$, by \eqref{Ldef} we have $L_2(\mathbf{A}) \leq \max_j\|\mathbf{A}_j\|_2$ and therefore (as $0 \leq \xi < 1$) the right-hand side of \eqref{GapUpperBound} is less than one.
-From \eqref{dimLem}, we have $|\pi(S)| \geq \dim(\bm{\mathcal{B}}_{\pi(S)}) \geq \dim(\bm{\mathcal{A}}_S) = |S|$, the final equality holding by injectivity of $\mathbf{A}_S$.
-As $|\pi(S)| = |S|$, the claim follows.
-Note, therefore, that $\mathbf{B}_{\pi(S)}$ has full-column rank for all $S \in \mathcal{H}$.
-
-We next demonstrate that \eqref{cond} holds.
-Fixing $\mathcal{G} \in {\mathcal{H} \choose r} \cup {\mathcal{H} \choose r+1}$, it suffices to show that $d(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}, \bm{\mathcal{A}}_{\cap \mathcal{G}} ) < 1$, since by \eqref{dimLem} we then have $|\cap \pi(\mathcal{G})| = \dim(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}) \leq \dim(\bm{\mathcal{A}}_{\cap \mathcal{G}}) = |\cap \mathcal{G}|$, with equalities from the full column-ranks of $\mathbf{A}_{S}$ and $\mathbf{B}_{\pi(S)}$ for all $S \in \mathcal{H}$.\footnote{Note that if ever $\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})} \neq \bf 0$ while $\cap \mathcal{G} = \emptyset$, we would have $d(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}, \bm 0 ) = 1$.
-However, that leads to a contradiction.} Observe that $d(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}, \bm{\mathcal{A}}_{\cap \mathcal{G}}  )
-\leq d\left( \cap \bm{\mathcal{B}}_{\pi(\mathcal{G})}, \cap \bm{\mathcal{A}}_\mathcal{G} \right)$ by \eqref{UsubU}, since trivially $\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})} \subseteq \cap \bm{\mathcal{B}}_{\pi(\mathcal{G})}$ and also $\bm{\mathcal{A}}_{\cap \mathcal{G}} = \cap \bm{\mathcal{A}}_\mathcal{G}$ by Lem.~\ref{spanIntersectionLemma}.
-Recalling Def.~\ref{dDef} and applying Lem.~\ref{DistanceToIntersectionLemma} yields:
-\begin{align}
-d\left( \cap \bm{\mathcal{B}}_{\pi(\mathcal{G})}, \cap \bm{\mathcal{A}}_\mathcal{G} \right)
-&\leq \max_{\mathbf{u} \in \cap \bm{\mathcal{B}}_{\pi(\mathcal{G})}, \ \|\mathbf{u}\|_2 \leq 1} \sum_{S \in \mathcal{G}} \frac{ \text{\rm dist}\left( \mathbf{u},\bm{\mathcal{A}}_{S} \right) }{ 1 - \xi( \bm{\mathcal{A}}_\mathcal{G} ) } \nonumber \\
-&= \sum_{S \in \mathcal{G}} \frac{ d\left( \cap \bm{\mathcal{B}}_{\pi(\mathcal{G})},\bm{\mathcal{A}}_{S} \right) }{ 1 - \xi( \bm{\mathcal{A}}_\mathcal{G} ) }, \nonumber
-\end{align}
-passing the maximum through the sum.
-Since $\cap \bm{\mathcal{B}}_{\pi(\mathcal{G})} \subseteq \bm{\mathcal{B}}_{\pi(S)}$ for all $S \in \mathcal{G}$, by \eqref{UsubU} the numerator of each term in the sum above is bounded by \mbox{$d\left( \bm{\mathcal{B}}_{\pi(S)},\bm{\mathcal{A}}_{S} \right) = d\left(\bm{\mathcal{A}}_{S}, \bm{\mathcal{B}}_{\pi(S)} \right) \leq \varepsilon$}, with the equality from \eqref{eqdim} since $\dim(\bm{\mathcal{B}}_{\pi(S)}) = \dim(\bm{\mathcal{A}}_S)$.
-Thus, altogether:
-\begin{align}\label{last}
-d(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}, \bm{\mathcal{A}}_{\cap \mathcal{G}} )
-\leq \frac{|\mathcal{G}| \varepsilon}{1 - \xi( \bm{\mathcal{A}}_\mathcal{G} )}
-\leq \frac{C_2 \varepsilon}{\max_j\|\mathbf{A}_j\|_2},
-\end{align}
-recalling the definition of $C_2$ in \eqref{Cdef2}.
-Lastly, since $C_2 \varepsilon < L_2(\mathbf{A}) \leq \max_j\|\mathbf{A}_j\|_2$, we have $d(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}, \bm{\mathcal{A}}_{\cap \mathcal{G}} ) \leq 1$ and therefore \eqref{cond} holds.
-
-%Keeping in mind that $d(U',V) \leq d(U,V)$ whenever $U' \subseteq U$ and applying (in order) Lem.~\ref{spanIntersectionLemma}, Lem.~\ref{DistanceToIntersectionLemma}, \eqref{eqdim}, \eqref{GapUpperBound}, and \eqref{Cdef2} gives:
-%\begin{align}\label{randoml}
-%d(&\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}, \bm{\mathcal{A}}_{\cap \mathcal{G}}  ) 
-%\leq d\left( \cap \bm{\mathcal{B}}_{\pi(\mathcal{G})}, \cap \bm{\mathcal{A}}_\mathcal{G} \right)
-%\leq \sum_{T \in \mathcal{G}} \frac{ d\left( \cap \bm{\mathcal{B}}_{\pi(\mathcal{G})},\bm{\mathcal{A}}_{T} \right) }{ 1 - \xi( \bm{\mathcal{A}}_\mathcal{G} ) } \nonumber \\
-%&\leq \sum_{T \in \mathcal{G}} \frac{ d\left( \bm{\mathcal{B}}_{\pi(T)},\bm{\mathbf{A}}_{T} \right) }{ 1 - \xi( \bm{\mathcal{A}}_\mathcal{G} ) }
-%\leq \frac{|\mathcal{G}| \varepsilon}{1 - \xi( \bm{\mathcal{A}}_\mathcal{G} )} 
-%\leq \frac{C_2 \varepsilon}{\max_j\|\mathbf{A}_j\|_2},
-%\end{align}
-%
-%which is less than one, since $C_2 \varepsilon < L_2(\mathbf{A}) \leq \max_j\|\mathbf{A}_j\|_2$.
-
-Applying Lem.~\ref{NonEmptyLemma}, the association $i \mapsto \cap_{S \in \sigma(i)} \pi(S)$ is an injective map $\overline \pi: J \to [\overline m]$ for some $J \subseteq [m]$ of size $m - (r-1)(\overline m - m)$, and $\mathbf{B}_{\overline \pi(i)} \neq \mathbf{0}$ for all $i \in J$ since the columns of $\mathbf{B}_{\pi(S)}$ are linearly independent for all $S \in \mathcal{H}$.
-Letting $\overline \varepsilon := C_2 \varepsilon / \max_i \|\mathbf{A}_i\|_2$, it follows from \eqref{eqdim} and \eqref{last} that $d\left( \bm{\mathcal{A}}_i, \bm{\mathcal{B}}_{\overline \pi(i)} \right) = d\left(\bm{\mathcal{B}}_{\overline \pi(i)},  \bm{\mathcal{A}}_i \right)  \leq \overline \varepsilon$ for all $i \in J$.
-%Fixing $\overline \varepsilon = C_2\varepsilon$ and letting $c_i = \|\mathbf{A}_i\|_2^{-1}$, we thus have that for each $\mathbf{e}_i \in \mathbb{R}^m$ with $i \in J$ there exists some $\overline{c}_i \in \mathbb{R}$ such that $\|c_i\mathbf{A}\mathbf{e}_i - \overline{c}_i \mathbf{B}\mathbf{e}_{\overline \pi(i)}\|_2 \leq \overline \varepsilon < L_2(\mathbf{A}) \min_{i\in J} |c_i|$.
-But this is exactly the supposition in \eqref{1D}, and the result follows from the case $k=1$ in Sec.~\ref{DUT} applied to the submatrix $\mathbf{A}_J$.
-Setting $c_i := \|\mathbf{A}_i\|_2^{-1}$ so that $\|c_i\mathbf{Ae}_i\|_2 = 1$, by Def.~\ref{dDef} for all $i \in J$:
-\begin{align*}
-\min_{\overline c_i \in \mathbb{R}} \|c_i\mathbf{Ae}_i - \overline c_i \mathbf{Be}_{\overline \pi(i)} \|_2
-\leq d\left( \bm{\mathcal{A}}_i, \bm{\mathcal{B}}_{\overline \pi(i)} \right)
-\leq \overline \varepsilon,
-%&= \max_{\bm{u} \in \bm{\mathcal{A}}_i, \|\bm{u}\|_2 \leq 1} \text{dist}\left(\bm{u}, \bm{\mathcal{B}}_{\overline \pi(i)} \right) \\
-%&\geq  \text{dist}\left(c_i\bm{Ae}_i, \mathbf{Be}_{\overline \pi(i)} \right) \\
-%&= \min_{\overline c_i \in \mathbb{R}} \|c_i\bm{Ae}_i - \overline c_i \mathbf{Be}_{\overline \pi(i)} \|_2
-\end{align*}
-%
-for $\overline \varepsilon < L_2(\mathbf{A})\min_{i \in [m]}|c_i|$.
-But this is exactly the supposition in \eqref{1D}, with $J$ and $\overline \varepsilon$ in place of $[m]$ and $\varepsilon$, respectively.
-The same arguments of the case $k=1$ in Sec.~\ref{DUT} can then be made to show that for any $\overline m \times \overline m$ permutation and invertible diagonal matrices $\mathbf{P}$ and $\mathbf{D}$ with, respectively, columns $\mathbf{e}_{\pi(i)}$ and $\frac{\overline{c}_i}{c_i}\mathbf{e}_i$ for $i \in J$ (otherwise, $\mathbf{e}_{i}$ for $i \in [\overline{m}] \setminus J$), we have $\|\mathbf{A}_i - (\mathbf{B}\mathbf{PD})_i \|_2 \leq \overline  \varepsilon / |c_i|  \leq C_2 \varepsilon$ for all $i \in J$.
-\end{proof}
-
-%\section{Proofs of Thm.~\ref{robustPolythm} and Cor.~\ref{ProbabilisticCor}}
-
-%\clearpage
-
-%\section{$\ell_1$-norm Extension}
-%
-%\begin{problem}\label{OptimizationProblemL1}
-%Find a matrix $\mathbf{B}$ and vectors \mbox{$\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N \in \mathbb{R}^m$} that solve:
-%\begin{align}\label{minsum}
-%\min \sum_{i = 1}^N \|\mathbf{\overline x}_i\|_1 \ \ 
-%\text{subject to} \ \ \|\mathbf{z}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \eta, \ \text{for all $i$}.
-%\end{align}
-%\end{problem}
-
-%\begin{corollary}\label{SLCopt}
-%Fix $\alpha > 0$ and suppose all of the assumptions of Thm.\ref{DeterministicUniquenessTheorem} hold with the following modifications:
-%\begin{enumerate}
-%\item The coefficients of all $k$-sparse $\mathbf{x}_i$ are drawn from $[-\beta, \beta]$, where $\beta < \frac{\alpha(k+1)}{k}$.
-%\item More than $(k-1){\overline m \choose k} + q$ vectors $\mathbf{x}_i$ are supported in each $S \in \mathcal{H}$, where
-%\[ q = \left[\frac{\alpha}{\beta}(k+1) - k\right]^{-1}k|\mathcal{H}|(k-1){\overline m \choose k-1}. \]
-%\end{enumerate}
-%Then all solutions to Prob.~\ref{OptimizationProblemL1} for which the nonzero elements of all $\mathbf{\overline x}_i$ lie outside $[-\alpha, \alpha]$ necessarily satisfy the implications \eqref{Cstable} and \eqref{b-PDa} of Thm.~\ref{DeterministicUniquenessTheorem}.
-%\end{corollary}
-
-%\begin{proof}[Proof of Cor.~\ref{SLCopt}]
-%We bound the number of $k$-sparse $\mathbf{\overline x}_i$ and then apply Thm.~\ref{DeterministicUniquenessCorollary}.
-First, observe that no more than $(k-1)|\mathcal{H}|$ of the $\mathbf{\overline x}_i$ share a support $\overline S$ of size less than $k$; otherwise, by the pigeonhole principle, at least $k$ of these indices $i$ belong to the same $K \subseteq I(S)$ for some $S \in \mathcal{H}$ and (as argued previously) \eqref{rhs222} follows.
-Since the right-hand side of \eqref{rhs222} is less than one, by \eqref{dimLem} we have the contradiction $k = \dim(\bm{\mathcal{A}}_S) \leq \dim(\bm{\mathcal{B}}_{\overline S}) \leq |\overline S|.$ The total number of $(k-1)$-sparse vectors $\mathbf{\overline x}_i$ can thus not exceed $|\mathcal{H}|(k-1){ \overline m \choose k-1}$.
-
-%Next, observe that the assumptions of the lemma imply:
-%\begin{align*}
-%\alpha \sum_i \|\mathbf{\overline x}_i\|_0 \leq \sum_i \|\mathbf{\overline x}_i\|_1 \leq \sum_i \|\mathbf{x}_i\|_1 \leq \beta \sum_i \|\mathbf{x}_i\|_0.
-%\end{align*}
-
-%We now apply these facts to bound the number of $k$-sparse $\mathbf{\overline x}_i$.
-Let $n_p$ be the number of $\mathbf{\overline x}_i$ with $\|\mathbf{\overline x}_i\|_0 = p$.
-Since the $\mathbf{x}_i$ are all $k$-sparse, we have:
-%\begin{align*}
-%k \sum_{p = 0}^{\overline m} n_p = k N \geq \sum_{i=0}^N \|\mathbf{x}_i\|_0 \geq \frac{\alpha}{\beta} \sum_{i=0}^N \|\mathbf{\overline x}_i\|_0 = \frac{\alpha}{\beta} \sum_{p=0}^{\overline m} p n_p.
-%\end{align*}
-%Hence, 
-%\begin{align*}
-%\left[ \frac{\alpha(k+1)}{\beta} - k\right] \sum_{p = k+1}^{\overline m} n_p 
-%&\leq \sum_{p = k+1}^{\overline m} (\frac{\alpha}{\beta} p-k) n_p
-%\leq \sum_{p = 0}^k (k - \frac{\alpha}{\beta} p)n_p \\
-%&\leq k \sum_{p = 0}^k n_p 
-%\leq k(1-\frac{\alpha}{\beta})n_k + k|\mathcal{H}|(k-1){ \overline m \choose k-1}
-%\end{align*}
-
-%[Shit, we need $\alpha = \beta$.] Therefore, no more than $q$ vectors $\mathbf{\overline x}_i$ are \emph{not} $k$-sparse.
-Since for every $S \in \mathcal{H}$ there are over $(k-1){\overline m \choose k} + q$ vectors $\mathbf{x}_i$ supported there, it follows that more than $(k-1){\overline m \choose k}$ of them have corresponding $\mathbf{\overline x}_i$ that are $k$-sparse.
-The result now follows directly from Thm.~\ref{DeterministicUniquenessCorollary}.
-%\end{proof}
-
-%\pagebreak
-
-%\begin{corollary}\label{SLCoptL1}
-%If all of the assumptions of Thm.\ref{DeterministicUniquenessTheorem} hold, only now with more than $(k-1)\left[ {\overline m \choose k} + |\mathcal{H}|k{\overline m \choose k-1}\right]$ vectors $\mathbf{x}_i$ supported in each $S \in \mathcal{H}$, then every solution to Prob.~\ref{OptimizationProblemL1} for which the average absolute nonzero coefficient of the $\mathbf{\overline x}_i$ is bounded below by that of the $\mathbf{x}_i$ necessarily satisfies the implications \eqref{Cstable} and \eqref{b-PDa} of Thm.~\ref{DeterministicUniquenessTheorem}.
-%\end{corollary}
-
-%\begin{proof}[Proof of Cor.~\ref{SLCoptL1}]
-%Since the average absolute nonzero coefficient of the $\mathbf{x}_i$ is given by $\alpha = \sum_i \|\mathbf{x}_i\|_1 / \sum_i \|\mathbf{x}_i\|_0$, we have:
-%\begin{align*}
-%\alpha \sum_i \|\mathbf{\overline x}_i\|_0 \leq \sum_i \|\mathbf{\overline x}_i\|_1 \leq \sum_i \|\mathbf{x}_i\|_1 = \alpha \sum_i \|\mathbf{x}_i\|_0.
-%\end{align*}
-%
-%and the result follows by the same arguments as in the proof of Cor.~\ref{SLCopt}.
-%\end{proof}
-
-\end{document}
+TODO

### 2020-08-05 manuscripts/thesis/discussion.tex
chapters

@@
 
-The absence of any assumptions at all about dictionaries that solve Prob.~\ref{InverseProblem} was a major technical hurdle in proving Thm.~\ref{DeterministicUniquenessTheorem}. 
-This very general guarantee was sought because of the practical difficulty of ensuring that an algorithm maintain a dictionary satisfying the spark condition \eqref{SparkCondition} at each iteration, which (to my knowledge) has been an explicit or implicit assumption of all previous works except \cite{Hillar15}; indeed, even certifying a dictionary has this property is NP-hard \cite{tillmann2014computational}.
-
-Several results in the literature had to be combined to extend the guarantees derived in \cite{Hillar15} into the noisy regime.
-The main challenge was to generalize Lem.~\ref{MainLemma} to the case where the $k$-dimensional subspaces spanned by corresponding submatrices $\mathbf{A}_S$ and $\mathbf{B}_{\pi(S)}$ are assumed to be``close" but not identical.
-Unlike in \cite{Hillar15} where an inductive argument could be applied to the noiseless case, here it had to be explicitly demonstrated that this proximity relation is propagated through iterated intersections right down to the spans of the dictionary elements themselves.
-Lem.~\ref{DistanceToIntersectionLemma} was designed to encapsulate this fact, proven by appeal to a convergence guarantee for an alternating projections algorithm first proposed by von Neumann.
-This result, combined with a little known fact \eqref{eqdim} about the distance metric between subspaces, make up the more obscure components of the deduction.
-
-The proof of Lem.~\ref{MainLemma} diverges most significantly from the approach taken in \cite{Hillar15} by way of Lem.~\ref{NonEmptyLemma}, which utilizes a combinatorial design for support sets (the ``singleton intersection property") to reduce the deterministic sample complexity by an exponential factor.
-This constitutes a significant advance toward legitimizing dictionary learning in practice, since data must otherwise exhibit the exponentially many possible $k$-wise combinations of dictionary elements required by (to my knowledge) all previously published results; although an exponential number of samples per support is still required (unless $k$ is held fixed).
-The issue is that the map $\pi:\mathcal{H} \to {[m] \choose k}$ is surjective only when $\mathcal{H}$ is taken to be ${[m] \choose k}$, in which case one may proceed by induction as in \cite{Hillar15}, freely choosing supports in the codomain of $\pi$ to intersect over $(k-1)$ indices to then map back to some corresponding set of $(k-1)$ indices at the intersection of supports in the domain.
-Here, for $\mathcal{H} \subset {[m] \choose k}$, a bijection between indices had to instead be established by pigeonholing the image of $\pi$ under constraints imposed by the SIP, which was formulated specifically for this purpose.
-It just so happened that this more general argument for a non-surjective $\pi$ constrained by the SIP applied just as well to the situation where the number of dictionary elements $m$ is over-estimated (i.e.
-$\overline m > m$), in which case a one-to-one correspondence can be guaranteed between a subset of columns of $\mathbf{A}$ and $\mathbf{B}$ of a size simply expressed in terms of the width of each matrix and the regularity of $\mathcal{H}$.
-
-One of the mathematically significant achievements in \cite{Hillar15} was to break free from the constraint that the recovery matrix $\mathbf{B}$ satisfy the spark condition in addition to the generating dictionary $\mathbf{A}$.
-%, in contrast to all previously known uniqueness results which (to my knowledge) have all either explicitly or implicitly made this assumption.
-Here, it has been demonstrated that, in fact, even $\mathbf{A}$ need not satisfy the spark condition!
-Rather, $\mathbf{A}$ need only be injective on the union of subspaces with supports forming a regular $k$-uniform hypergraph satisfying the SIP (a distinguishing example is given in Sec.~\ref{Results}).
-This relaxation of constraints inspired the definition of the restricted matrix lower bound $L_{\mathcal{H}}$ in \eqref{Ldef}, which generalizes the well-known (see footnote \ref{ripfootnote}) restricted matrix lower bound $L_k$ to be in terms of a hypergraph $\mathcal{H}$, and an interesting object for further study in its own right.
-%(For instance, how hard is it to check that $L_\mathcal{H}(\mathbf{A}) > 0$?)
-%The absence of any restrictions on dictionaries solving Prob.~\ref{InverseProblem} is a major technical obstruction, but highly desirable because of the practical difficulty in ensuring that an algorithm maintain a dictionary satisfying the spark condition \eqref{SparkCondition} at each iteration; indeed, even certifying a dictionary has this property is NP-hard \cite{tillmann2014computational}.
-
-To reiterate, the methods applied here to prove Thm.~\ref{DeterministicUniquenessTheorem} yield the following results beyond a straightforward extension of those in \cite{Hillar15} to the noisy case:
-
-\begin{enumerate}
-\item A reduction in deterministic sample complexity: To identify the $n \times m$ generating dictionary $\mathbf{A}$, it is required in \cite{Hillar15} that $k{m \choose k}$ data points be sampled from each of the ${m \choose k}$ subspaces spanned by subsets of $k$ columns of $\mathbf{A}$.
-It is shown here that in fact it suffices to sample from at most $m$ such subspaces (see Cor.~\ref{DeterministicUniquenessCorollary}).
-%; thus, for fixed $k$, the deterministic sample complexity is polynomial in $m$.
-%HS15 was already poly for fixed k
-\item An extension of guarantees to the case where the number of dictionary elements is unknown: The results of \cite{Hillar15} only apply to the case where the matrix $\mathbf{B}$ has the same number of columns as $\mathbf{A}$.
-It is shown here that if $\mathbf{B}$ has at least as many columns as $\mathbf{A}$ then it contains (up to noise) a subset of the columns of $\mathbf{A}$.
-\item Relaxed requirements (no spark condition) on the generating matrix $\mathbf{A}$: Rather, $\mathbf{A}$ need only be injective on the union of subspaces with supports that form a regular uniform hypergraph satisfying the SIP.
-\end{enumerate}
-
-As it seemed to benefit a reviewer of this work, a brief discussion on how the deterministic sample complexity $N = |\mathcal{H}\left[|(k-1){m \choose k} + 1\right]$ derived here compares to those listed in the the top two rows listed in Table I of \cite{Hillar15} may be in order.
-To be clear, the theory developed here is strictly more general, since $\mathcal{H}$ can always be taken to be ${[m] \choose k}$.
-The point of difference in this comparison is the assumed set of supports for sparse codes, which is always ${[m] \choose k}$ in \cite{Hillar15}, whereas here it can be assumed to be any regular $k$-uniform hypergraph that satisfies the SIP.
-By row, %, assuming for our results that sufficient data have been sampled from all supports in a hypergraph H satisfying the SIP:
-\begin{enumerate}
-\item[I.] The result here improves upon the listed $k{m \choose k}^2$ by an exponential factor, since for every $k < m$ there exists a regular $k$-uniform hypergraph $\mathcal{H}$ with $|\mathcal{H}| = m$ satisfying the SIP.
-\item[II.] The authors in \cite{Hillar15} have applied measure-theoretic arguments to achieve $(k+1){m \choose k}$ with almost-certainty (i.e.
-with probability one), a factor of $m$ reduction over that for which certainty can alternatively be guaranteed here.
-%\item[III.] A direct comparison cannot be made because it is an open question as to the probability that a random set of supports satisfies the SIP.
-This would be an interesting problem for the community to solve; regardless, the result of \cite{Hillar15} is still implied by the more general theory given here.
-%\item[IV.] The result here is $|\mathcal{H}\left[|(k-1){m \choose k} + 1\right]$ with probability one compared to $(k+1){m \choose k}$ with probability one.
-In this case the sample complexity stated in \cite{Hillar15} is marginally better, but it relies on a noise-free technicality unique to their assumption $\mathcal{H} = {m \choose k}$.
-%differs in flavor: their $\mathbf{x_i}$ are assumed to be distributed as $(k+1)$ samples per support for every support of size $k \in [m]$, whereas here it is assumed that $(k-1){m \choose k}$ codes $\mathbf{x_i}$ are distributed over each support in some hypergraph $\mathcal{H}$ satisfying the SIP.
-%\item[V.] Again, a direct comparison cannot be made for the reason stated for row III.
-\end{enumerate}
-
 %Beyond an extension of existing noiseless guarantees \cite{Hillar15} to the noisy regime and their novel application to Prob.~\ref{OptimizationProblem}, this work contains a theory of combinatorial designs for support sets key to identification of dictionaries.
@@
 
-Another reviewer of this work lamented that while the extension from exact recovery to the noisy stability of dictionary learning is significant, the fact that the analysis relies on metrics of the data that are not feasible to compute limits its impact to the scientific community beyond computer science and applied mathematics.
+A reviewer of this work lamented that while the extension from exact recovery to the noisy stability of dictionary learning is significant, the fact that the analysis relies on metrics of the data that are not feasible to compute limits its impact to the scientific community beyond computer science and applied mathematics.
 What sets the main results of this work apart from the vast majority of results in the field is that they are deterministic, and do not depend on any kind of assumption about the particular random distribution from which the sparse supports, coefficients, or dictionary entries are drawn (though Cor.~\ref{ProbabilisticCor} makes a sweeping statement applicable to all continuous distributions).
@@
 
-\section{Future Directions}\label{FutureDirections}
+\section{Future directions}\label{FutureDirections}
 
@@
 It is then natural to wonder: what are the necessary constraints on $\mathcal{H}$, and what is the smallest hypergraph satisfying these constraints for given $m$ and $k$?
+
+%%%%%%%%%%%%%%
+% need to cut maybe: 
+%As mentioned in the previous section, Thm.~\ref{DeterministicUniquenessTheorem} is a particular case of a more general result that forgoes the assumption that $\mathcal{H} \subseteq {[m] \choose k}$ is regular and satisfies the SIP.
+If instead we require only that the stars $\cap \sigma(i)$ intersect at singletons for all $i \leq q$ (assuming that the nodes of $\mathcal{H}$ are labeled in some order of non-increasing degree), we have that $\overline m \geq k|\mathcal{H}| / \deg(1)$ and, provided $\overline m < k|\mathcal{H}| / (\deg(1) - 1)$, the nonempty submatrix $J$ is of size equal to the largest number $p$ satisfying:
+%\begin{align}\label{pcond}
+%\sum_{i=\ell}^{m} \deg(i) > (\overline m + 1 - \ell) (\deg(\ell) - 1) \ \ \text{for all } \ell \leq p \leq q.
+%\end{align}
+%Specifically, $J$ contains all nodes of degree exceeding $\deg(p)$ and some subset of those with degreee equal to $\deg(p)$.
+For the benefit of the reader, we do not prove explicitly this more general result below; it can be discerned from how exactly Lemma \ref{NonEmptyLemma} is incorporated into the proof of Lem.~\ref{MainLemma}.
+%%%%%%%%%%%%%%%%
 

### 2020-08-05 manuscripts/thesis/introduction.tex
chapters

@@
-\section{Introduction}\label{Intro}
+\chapter{Introduction}\label{Intro}
 
@@
 
-Here, we prove very generally that uniqueness and stability is a typical property of sparse dictionary learning.
-More specifically, we show that matrices injective on a sparse domain are identifiable from \mbox{$N = m(k-1){m \choose k} + m$} noisy linear combinations of $k$ of their $m$ columns up to an error that is linear in the noise (Thm.~\ref{DeterministicUniquenessTheorem}).
+In this work, it is proven very generally that uniqueness and stability is a typical property of sparse dictionary learning.
+More specifically, it is demonstrated that matrices injective on a sparse domain are identifiable from \mbox{$N = m(k-1){m \choose k} + m$} noisy linear combinations of $k$ of their $m$ columns up to an error that is linear in the noise (Thm.~\ref{DeterministicUniquenessTheorem}).
 In fact, provided $n \geq \min(2k,m)$, in almost all cases the problem is well-posed, as per Hadamard \cite{Hadamard1902}, given a sufficient amount of data (Thm.~\ref{robustPolythm} and Cor.~\ref{ProbabilisticCor}).
 
-Our guarantees also hold for a related (and perhaps more commonly posed, e.g.
+These guarantees also hold for a related (and perhaps more commonly posed, e.g.
 \cite{rehnsommer2007}) optimization problem seeking a dictionary minimizing the average number of elementary waveforms required to reconstruct each sample of the dataset (Thm.~\ref{SLCopt}).
-To practical benefit, our results impose no restrictions on learned dictionaries (e.g., that they, too, be injective over some sparse domain) beyond an upper bound on dictionary size, which is necessary in any case to avoid trivial solutions (e.g., allowing $m = N$).
+To practical benefit, the derivations impose no restrictions on learned dictionaries (e.g., that they, too, be injective over some sparse domain) beyond an upper bound on dictionary size, which is necessary in any case to avoid trivial solutions (e.g., allowing $m = N$).
 %That is, every pair of solutions of comparable size has some number of dictionary elements in common (up to noise), and similarly so for the coefficients of sparse codes they induce.
 
-More precisely, let $\mathbf{A} \in \mathbb R^{n \times m}$ be a matrix with columns $\mathbf{A}_j$ ($j = 1,\ldots,m$) and let dataset $Z$ consist of measurements:
+\section{The dictionary learning problem(s)}
+
+Let $\mathbf{A} \in \mathbb R^{n \times m}$ be a matrix with columns $\mathbf{A}_j$ ($j = 1,\ldots,m$) and let dataset $Z$ consist of measurements:
 \begin{align}\label{LinearModel}

### 2020-08-05 manuscripts/thesis/proofs.tex
chapters

@@
-\section{Proofs}\label{DUT} % of Theorems~\ref{DeterministicUniquenessTheorem} and ~\ref{SLCopt}}\label{DUT}
+\chapter{Definitions and Proofs}\label{DUT} % of Theorems~\ref{DeterministicUniquenessTheorem} and ~\ref{SLCopt}}\label{DUT}
 
-%%%%%%%%%%%%%%
-% need to cut maybe: 
-%As mentioned in the previous section, Thm.~\ref{DeterministicUniquenessTheorem} is a particular case of a more general result that forgoes the assumption that $\mathcal{H} \subseteq {[m] \choose k}$ is regular and satisfies the SIP.
-If instead we require only that the stars $\cap \sigma(i)$ intersect at singletons for all $i \leq q$ (assuming that the nodes of $\mathcal{H}$ are labeled in some order of non-increasing degree), we have that $\overline m \geq k|\mathcal{H}| / \deg(1)$ and, provided $\overline m < k|\mathcal{H}| / (\deg(1) - 1)$, the nonempty submatrix $J$ is of size equal to the largest number $p$ satisfying:
-%\begin{align}\label{pcond}
-%\sum_{i=\ell}^{m} \deg(i) > (\overline m + 1 - \ell) (\deg(\ell) - 1) \ \ \text{for all } \ell \leq p \leq q.
-%\end{align}
-%Specifically, $J$ contains all nodes of degree exceeding $\deg(p)$ and some subset of those with degreee equal to $\deg(p)$.
-For the benefit of the reader, we do not prove explicitly this more general result below; it can be discerned from how exactly Lemma \ref{NonEmptyLemma} is incorporated into the proof of Lem.~\ref{MainLemma}.
-%%%%%%%%%%%%%%%%
+%It has been shown here that, given sufficient data, this problem reduces to an instance of Prob.~\ref{InverseProblem} to which the main result (Thm.~\ref{DeterministicUniquenessTheorem}) then applies.
 
@@
 % WITHOUT J SUBSCRIPT
+
+\section{Proving the case $k=1$}
+
 We begin our proof of Thm.~\ref{DeterministicUniquenessTheorem} by showing how dictionary recovery \eqref{Cstable} already implies sparse code recovery \eqref{b-PDa} when $\mathbf{A}$ satisfies \eqref{SparkCondition} and \mbox{$\varepsilon < L_{2k}(\mathbf{A}) / C_1$}.
@@
 \end{proof}
+
+\section{The main lemma}
 
@@
 
+\section{Proving the general case $k<m$}
+
 We next define the constant $C_1 > 0$ of Thm.~\ref{DeterministicUniquenessTheorem} in terms of $C_2$.
@@
 Using the definitions, we have $\|\mathbf{AX}_{I(S)}\mathbf{c}\|_2 \geq \sqrt{k} L_\mathcal{H}(\mathbf{A})\|\mathbf{X}_{I(S)}\mathbf{c}\|_2 \geq k L_\mathcal{H}(\mathbf{A}) L_k(\mathbf{X}_{I(S)})\|\mathbf{c}\|_2$.
-Thus, $L_k(\mathbf{AX}_{I(S)}) \geq \sqrt{k} L_\mathcal{H}(\mathbf{A}) L_k(\mathbf{X}_{I(S)}) > 0$, since $L_{\mathcal{H}}(\mathbf{A}) \geq L_{2\mathcal{H}}(\mathbf{A})> 0$ and $L_k(\mathbf{X}_{I(S)}) > 0$ by general linear position of the $\mathbf{x}_i$.} and yields an upper bound on $\varepsilon$ consistent with that proven sufficient in the case $k=1$ considered at the beginning of this section.\footnote{When $\mathbf{x}_i = c_i\mathbf{e}_i$, we have $C_2 \geq 2\|\mathbf{A}_i\|_2$ and the denominator in \eqref{Cdef1} becomes $\min_{i \in [m]} |c_i| \|\mathbf{A}_i\|_2$; hence, $C_1 \geq 2 / \min_{i \in [m]} |c_i|$.}
+Thus, $L_k(\mathbf{AX}_{I(S)}) \geq \sqrt{k} L_\mathcal{H}(\mathbf{A}) L_k(\mathbf{X}_{I(S)}) > 0$, since $L_{\mathcal{H}}(\mathbf{A}) \geq L_{2\mathcal{H}}(\mathbf{A})> 0$ and $L_k(\mathbf{X}_{I(S)}) > 0$ by general linear position of the $\mathbf{x}_i$.} and yields an upper bound on $\varepsilon$ consistent with that proven sufficient in the case $k=1$ considered at the beginning of this chapter.\footnote{When $\mathbf{x}_i = c_i\mathbf{e}_i$, we have $C_2 \geq 2\|\mathbf{A}_i\|_2$ and the denominator in \eqref{Cdef1} becomes $\min_{i \in [m]} |c_i| \|\mathbf{A}_i\|_2$; hence, $C_1 \geq 2 / \min_{i \in [m]} |c_i|$.}
 % C_2(\mathbf{A}, \mathcal{H}) := \frac{ (r+1) \max_{j \in [m]} \|\mathbf{A}_j\|_2}{ \min_{\mathcal{G} \in {\mathcal{H} \choose r} \cup {\mathcal{H} \choose r+1}} \xi( \{ \bm{\mathcal{A}}_S \}
@@
 %\end{proof}
+
+\section{Discussion}
+
+The absence of any assumptions at all about dictionaries that solve Prob.~\ref{InverseProblem} was a major technical hurdle in proving Thm.~\ref{DeterministicUniquenessTheorem}. 
+This very general guarantee was sought because of the practical difficulty of ensuring that an algorithm maintain a dictionary satisfying the spark condition \eqref{SparkCondition} at each iteration, which (to my knowledge) has been an explicit or implicit assumption of all previous works except \cite{Hillar15}; indeed, even certifying a dictionary has this property is NP-hard \cite{tillmann2014computational}.
+
+Several results in the literature had to be combined to extend the guarantees derived in \cite{Hillar15} into the noisy regime.
+The main challenge was to generalize Lem.~\ref{MainLemma} to the case where the $k$-dimensional subspaces spanned by corresponding submatrices $\mathbf{A}_S$ and $\mathbf{B}_{\pi(S)}$ are assumed to be``close" but not identical.
+Unlike in \cite{Hillar15} where an inductive argument could be applied to the noiseless case, here it had to be explicitly demonstrated that this proximity relation is propagated through iterated intersections right down to the spans of the dictionary elements themselves.
+Lem.~\ref{DistanceToIntersectionLemma} was designed to encapsulate this fact, proven by appeal to a convergence guarantee for an alternating projections algorithm first proposed by von Neumann.
+This result, combined with a little known fact \eqref{eqdim} about the distance metric between subspaces, make up the more obscure components of the deduction.
+
+The proof of Lem.~\ref{MainLemma} diverges most significantly from the approach taken in \cite{Hillar15} by way of Lem.~\ref{NonEmptyLemma}, which utilizes a combinatorial design for support sets (the ``singleton intersection property") to reduce the deterministic sample complexity by an exponential factor.
+This constitutes a significant advance toward legitimizing dictionary learning in practice, since data must otherwise exhibit the exponentially many possible $k$-wise combinations of dictionary elements required by (to my knowledge) all previously published results; although an exponential number of samples per support is still required (unless $k$ is held fixed).
+The issue is that the map $\pi:\mathcal{H} \to {[m] \choose k}$ is surjective only when $\mathcal{H}$ is taken to be ${[m] \choose k}$, in which case one may proceed by induction as in \cite{Hillar15}, freely choosing supports in the codomain of $\pi$ to intersect over $(k-1)$ indices to then map back to some corresponding set of $(k-1)$ indices at the intersection of supports in the domain.
+Here, for $\mathcal{H} \subset {[m] \choose k}$, a bijection between indices had to instead be established by pigeonholing the image of $\pi$ under constraints imposed by the SIP, which was formulated specifically for this purpose.
+It just so happened that this more general argument for a non-surjective $\pi$ constrained by the SIP applied just as well to the situation where the number of dictionary elements $m$ is over-estimated (i.e.
+$\overline m > m$), in which case a one-to-one correspondence can be guaranteed between a subset of columns of $\mathbf{A}$ and $\mathbf{B}$ of a size simply expressed in terms of the width of each matrix and the regularity of $\mathcal{H}$.
+
+One of the mathematically significant achievements in \cite{Hillar15} was to break free from the constraint that the recovery matrix $\mathbf{B}$ satisfy the spark condition in addition to the generating dictionary $\mathbf{A}$.
+%, in contrast to all previously known uniqueness results which (to my knowledge) have all either explicitly or implicitly made this assumption.
+Here, it has been demonstrated that, in fact, even $\mathbf{A}$ need not satisfy the spark condition!
+Rather, $\mathbf{A}$ need only be injective on the union of subspaces with supports forming a regular $k$-uniform hypergraph satisfying the SIP (a distinguishing example is given in Sec.~\ref{Results}).
+This relaxation of constraints inspired the definition of the restricted matrix lower bound $L_{\mathcal{H}}$ in \eqref{Ldef}, which generalizes the well-known (see footnote \ref{ripfootnote}) restricted matrix lower bound $L_k$ to be in terms of a hypergraph $\mathcal{H}$, and an interesting object for further study in its own right.
+%(For instance, how hard is it to check that $L_\mathcal{H}(\mathbf{A}) > 0$?)
+%The absence of any restrictions on dictionaries solving Prob.~\ref{InverseProblem} is a major technical obstruction, but highly desirable because of the practical difficulty in ensuring that an algorithm maintain a dictionary satisfying the spark condition \eqref{SparkCondition} at each iteration; indeed, even certifying a dictionary has this property is NP-hard \cite{tillmann2014computational}.
+
+To reiterate, the methods applied here to prove Thm.~\ref{DeterministicUniquenessTheorem} yield the following results beyond a straightforward extension of those in \cite{Hillar15} to the noisy case:
+
+\begin{enumerate}
+\item A reduction in deterministic sample complexity: To identify the $n \times m$ generating dictionary $\mathbf{A}$, it is required in \cite{Hillar15} that $k{m \choose k}$ data points be sampled from each of the ${m \choose k}$ subspaces spanned by subsets of $k$ columns of $\mathbf{A}$.
+It is shown here that in fact it suffices to sample from at most $m$ such subspaces (see Cor.~\ref{DeterministicUniquenessCorollary}).
+%; thus, for fixed $k$, the deterministic sample complexity is polynomial in $m$.
+%HS15 was already poly for fixed k
+\item An extension of guarantees to the case where the number of dictionary elements is unknown: The results of \cite{Hillar15} only apply to the case where the matrix $\mathbf{B}$ has the same number of columns as $\mathbf{A}$.
+It is shown here that if $\mathbf{B}$ has at least as many columns as $\mathbf{A}$ then it contains (up to noise) a subset of the columns of $\mathbf{A}$.
+\item Relaxed requirements (no spark condition) on the generating matrix $\mathbf{A}$: Rather, $\mathbf{A}$ need only be injective on the union of subspaces with supports that form a regular uniform hypergraph satisfying the SIP.
+\end{enumerate}
+
+As it seemed to benefit a reviewer of this work, a brief discussion on how the deterministic sample complexity $N = |\mathcal{H}\left[|(k-1){m \choose k} + 1\right]$ derived here compares to those listed in the the top two rows listed in Table I of \cite{Hillar15} may be in order.
+To be clear, the theory developed here is strictly more general, since $\mathcal{H}$ can always be taken to be ${[m] \choose k}$.
+The point of difference in this comparison is the assumed set of supports for sparse codes, which is always ${[m] \choose k}$ in \cite{Hillar15}, whereas here it can be assumed to be any regular $k$-uniform hypergraph that satisfies the SIP.
+By row, %, assuming for our results that sufficient data have been sampled from all supports in a hypergraph H satisfying the SIP:
+\begin{enumerate}
+\item[I.] The result here improves upon the listed $k{m \choose k}^2$ by an exponential factor, since for every $k < m$ there exists a regular $k$-uniform hypergraph $\mathcal{H}$ with $|\mathcal{H}| = m$ satisfying the SIP.
+\item[II.] The authors in \cite{Hillar15} have applied measure-theoretic arguments to achieve $(k+1){m \choose k}$ with almost-certainty (i.e.
+with probability one), a factor of $m$ reduction over that for which certainty can alternatively be guaranteed here.
+%\item[III.] A direct comparison cannot be made because it is an open question as to the probability that a random set of supports satisfies the SIP.
+This would be an interesting problem for the community to solve; regardless, the result of \cite{Hillar15} is still implied by the more general theory given here.
+%\item[IV.] The result here is $|\mathcal{H}\left[|(k-1){m \choose k} + 1\right]$ with probability one compared to $(k+1){m \choose k}$ with probability one.
+In this case the sample complexity stated in \cite{Hillar15} is marginally better, but it relies on a noise-free technicality unique to their assumption $\mathcal{H} = {m \choose k}$.
+%differs in flavor: their $\mathbf{x_i}$ are assumed to be distributed as $(k+1)$ samples per support for every support of size $k \in [m]$, whereas here it is assumed that $(k-1){m \choose k}$ codes $\mathbf{x_i}$ are distributed over each support in some hypergraph $\mathcal{H}$ satisfying the SIP.
+%\item[V.] Again, a direct comparison cannot be made for the reason stated for row III.
+\end{enumerate}

### 2020-08-05 manuscripts/thesis/thesis.tex
chapters

@@
 
-\title{On the uniqueness and stability of dictionaries for sparse representation of noisy signals}
+%\title{On the uniqueness and stability of dictionaries for sparse representation of noisy signals}
+\title{A Tale of Two Dictionary Learning Problems}
 \author{Charles Garfinkle}
@@
 
-\section{Foreword}
-This thesis presents results published Dec.~2019 in a paper of the same name in \emph{IEEE Transactions on Signal Processing}, largely verbatim.
+%\section{Foreword}
+%This thesis presents results published Dec.~2019 in a paper of the same name in \emph{IEEE Transactions on Signal Processing}, largely verbatim.
 Readers should refer to the Discussion and Future Directions as well as Figures \ref{probpigeon} and \ref{reasonableC2} for additional insights not offered in the paper.
@@
 \include{discussion}
-%\include{reviewers}
 \include{appendix}

### 2020-08-05 manuscripts/thesis/appendix.tex
chapters

@@
-\section{Appendix}\label{proofs}
+\chapter{Appendix: Proving the main lemma}\label{proofs}
 
-We prove Lem.~\ref{MainLemma} after the following auxiliary lemmas.  % stating and proving some auxiliary lemmas. 
+We shall prove Lem.~\ref{MainLemma} after the following auxiliary lemmas.  % stating and proving some auxiliary lemmas. 
 %First, note that since $\|\mathbf{A}\mathbf{x}\|_2 \leq \max_j\|\mathbf{A}_j\|_2\|\mathbf{x}\|_1$ and $\|\mathbf{x}\|_1 \leq \sqrt{k} \|\mathbf{x}\|_2$ for $k$-sparse $\mathbf{x}$, by \eqref{Ldef} we have the following frequently applied inequality:
@@
 %We will show that the bound \eqref{GapUpperBound} trickles through the intersection semi-lattices of $\{\bm{\mathcal{A}}_S\}_{S \in \mathcal{H}}$ and $\{\bm{\mathcal{B}}_{\overline S}\}_{\overline S \in \pi(\mathcal{H})}$ to yield \eqref{MainLemmaBPD} by virtue of the SIP.
-We begin by showing that $\dim(\bm{\mathcal{B}}_{\pi(S)}) = \dim(\bm{\mathcal{A}}_S)$ for all $S \in \mathcal{H}$.
+Let us begin by showing that $\dim(\bm{\mathcal{B}}_{\pi(S)}) = \dim(\bm{\mathcal{A}}_S)$ for all $S \in \mathcal{H}$.
 Note that since $\|\mathbf{A}\mathbf{x}\|_2 \leq \max_j\|\mathbf{A}_j\|_2\|\mathbf{x}\|_1$ and $\|\mathbf{x}\|_1 \leq \sqrt{k} \|\mathbf{x}\|_2$ for all $k$-sparse $\mathbf{x}$, by \eqref{Ldef} we have $L_2(\mathbf{A}) \leq \max_j\|\mathbf{A}_j\|_2$ and therefore (as $0 \leq \xi < 1$) the right-hand side of \eqref{GapUpperBound} is less than one.
@@
 
-We next demonstrate that \eqref{cond} holds.
+We shall next demonstrate that \eqref{cond} holds.
 Fixing $\mathcal{G} \in {\mathcal{H} \choose r} \cup {\mathcal{H} \choose r+1}$, it suffices to show that $d(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}, \bm{\mathcal{A}}_{\cap \mathcal{G}} ) < 1$, since by \eqref{dimLem} we then have $|\cap \pi(\mathcal{G})| = \dim(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}) \leq \dim(\bm{\mathcal{A}}_{\cap \mathcal{G}}) = |\cap \mathcal{G}|$, with equalities from the full column-ranks of $\mathbf{A}_{S}$ and $\mathbf{B}_{\pi(S)}$ for all $S \in \mathcal{H}$.\footnote{Note that if ever $\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})} \neq /bfseries 0$ while $\cap \mathcal{G} = \emptyset$, we would have $d(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}, \bm 0 ) = 1$.

### 2020-08-05 manuscripts/thesis/discussion.tex
chapters

@@
 
-A reviewer of this work lamented that while the extension from exact recovery to the noisy stability of dictionary learning is significant, the fact that the analysis relies on metrics of the data that are not feasible to compute limits its impact to the scientific community beyond computer science and applied mathematics.
+While the extension from exact recovery to the noisy stability of dictionary learning is significant, the fact that the analysis relies on metrics of the data that are not feasible to compute limits its impact to the scientific community beyond computer science and applied mathematics.
 What sets the main results of this work apart from the vast majority of results in the field is that they are deterministic, and do not depend on any kind of assumption about the particular random distribution from which the sparse supports, coefficients, or dictionary entries are drawn (though Cor.~\ref{ProbabilisticCor} makes a sweeping statement applicable to all continuous distributions).
@@
 
-\subsection{Convex Optimization}
+\subsection{Dictionary learning via $\ell_1$-norm minimization}
 
-A commonly applied workaround to the intractability of Prob.~\ref{SLCopt} (see \cite{tillmann2015computational}) is to swap out the norm $\|\cdot\|_0$ in \eqref{minsum} for $\|\cdot\|_1$, thereby transforming the inference of sparse $\mathbf{\overline x}_i$ for a given $\mathbf{B}$ into a convex optimization solvable by a linear program.
+A commonly applied workaround to the intractability of Prob.~\ref{SLCopt} (see \cite{tillmann2015computational}) is to swap out the $\ell_0$-norm in \eqref{minsum} for $\ell_1$-norm, thereby transforming the inference of sparse $\mathbf{\overline x}_i$ for a given $\mathbf{B}$ into a convex optimization solvable by a linear program.
 A major advance in compressive sensing was the discovery that \eqref{minsum} can in fact be solved in this way for fixed $\mathbf{B}$ provided $L_{2k}(\mathbf{B})$ is large enough \cite{eldar2012compressed}.
@@
 \includegraphics[width=1 \linewidth]{figures/prob_vs_samples.png}
-\caption{Probability of successful dictionary and code recovery (as per Thm.
+\caption{\textbf{Learning a dictionary from an arbitrary number of samples.} Probability of successful dictionary and code recovery (as per Thm.
 \ref{DeterministicUniquenessTheorem}) for a number of samples $N$ given as a fraction of the deterministic sample complexity $N = |\mathcal{H}|[(k-1){m \choose k} + 1]$ when the support set hypergraph $\mathcal{H}$ is the set of $m$ consecutive intervals of length $k$ in a cyclic order on $[m]$.
@@
 \includegraphics[width=1 \linewidth]{figures/C2.pdf}
-\caption{Distribution of $C_2(\mathbf{A}, \mathcal{H})$ computed for 1.33x overcomplete generic unit-norm dictionaries $\mathbf{A} \in \mathbb{R}^{n \times m}$ (i.e.
+\caption{\textbf{Concentration of the constant $C_2$.} Distribution of $C_2(\mathbf{A}, \mathcal{H})$ computed for 1.33x overcomplete generic unit-norm dictionaries $\mathbf{A} \in \mathbb{R}^{n \times m}$ (i.e.
 with $n = 3m/4$) when the support set hypergraph $\mathcal{H}$ consists of the rows and columns formed by arranging  the elements of $[m]$ into a square grid (i.e.

### 2020-08-05 manuscripts/thesis/introduction.tex
chapters

@@
 
-Sparse coding is a common modern signal processing technique that views each of $N$ observed $n$-dimensional signal samples as a (noisy) linear combination of at most $k$ elementary waveforms drawn from some unknown ``dictionary" of size $m \ll N$ (see \cite{Zhang15} for a comprehensive review).
+Sparse coding is a modern signal processing technique that views each of $N$ observed $n$-dimensional signal samples as a (noisy) linear combination of at most $k$ elementary waveforms drawn from some unknown ``dictionary" of size $m \ll N$ (see \cite{Zhang15} for a comprehensive review).
 %\IEEEPARstart{A}{}common modern approach to pattern analysis in signal processing is to view each of $N$ observed $n$-dimensional signal samples as a (noisy) linear combination of at most $k$ elementary waveforms drawn from some unknown ``dictionary" of size $m \ll N$ (see \cite{Zhang15} for a comprehensive review).
 Optimizing dictionaries subject to this and related sparsity constraints has revealed seemingly characteristic sparse structure in several signal classes of current interest (e.g., in vision \cite{wang2015sparse}).
-
 Of particular note are the seminal works in the field \cite{Olshausen96, hurri1996image, bell1997independent, van1998independent}, which discovered that dictionaries optimized for coding small patches of ``natural" images share qualitative similarities with linear filters estimated from response properties of simple-cell neurons in mammalian visual cortex.
@@
 
-Motivated by these discoveries and more recent work relating compressed sensing \cite{eldar2012compressed} to a theory of information transmission through random wiring bottlenecks in the brain \cite{Isely10}, we address when dictionaries for sparse representation are indeed identifiable from data.
+Motivated by these discoveries and more recent work relating compressed sensing \cite{eldar2012compressed} to a theory of information transmission through random wiring bottlenecks in the brain \cite{Isely10}, this thesis addresses when dictionaries for sparse representation are indeed identifiable from data.
 Answers to this question may also have implications in practice wherever an appeal is made to latent sparse structure of data (e.g., forgery detection \cite{hughes2010, olshausen2010applied}; brain recordings \cite{jung2001imaging, agarwal2014spatially, lee2016sparse}; and gene expression \cite{wu2016stability}).
+While several algorithms have recently been proposed to provably recover unique dictionaries under specific conditions (see \cite[Sec.~I-E]{Sun16} for a summary of the state-of-the-art), few theorems can be invoked to justify the consistency of inference under this model of data more broadly.
+To my knowledge, a universal guarantee of the uniqueness and stability of learned dictionaries and the sparse representations they induce over noisy data has yet to appear in the literature.
 
-While several algorithms have recently been proposed to provably recover unique dictionaries under specific conditions (see \cite[Sec.~I-E]{Sun16} for a summary of the state-of-the-art), few theorems can be invoked to justify the consistency of inference under this model of data more broadly.
-To our knowledge, a universal guarantee of the uniqueness and stability of learned dictionaries and the sparse representations they induce over noisy data has yet to appear in the literature.
-
-In this work, it is proven very generally that uniqueness and stability is a typical property of sparse dictionary learning.
+In this work, it is proven very generally that uniqueness and stability is a typical property of learned dictionaries.
 More specifically, it is demonstrated that matrices injective on a sparse domain are identifiable from \mbox{$N = m(k-1){m \choose k} + m$} noisy linear combinations of $k$ of their $m$ columns up to an error that is linear in the noise (Thm.~\ref{DeterministicUniquenessTheorem}).
 In fact, provided $n \geq \min(2k,m)$, in almost all cases the problem is well-posed, as per Hadamard \cite{Hadamard1902}, given a sufficient amount of data (Thm.~\ref{robustPolythm} and Cor.~\ref{ProbabilisticCor}).
-
-These guarantees also hold for a related (and perhaps more commonly posed, e.g.
+These guarantees also hold for the related (and perhaps more commonly posed, e.g.
 \cite{rehnsommer2007}) optimization problem seeking a dictionary minimizing the average number of elementary waveforms required to reconstruct each sample of the dataset (Thm.~\ref{SLCopt}).
@@
 for $k$-\emph{sparse} $\mathbf{x}_i \in \mathbb{R}^m$ having at most $k<m$ nonzero entries and \emph{noise} $\mathbf{n}_i \in \mathbb{R}^n$, with bounded norm $\| \mathbf{n}_i \|_2 \leq  \eta$ representing our worst-case uncertainty in measuring the product $\mathbf{A}\mathbf{x}_i$.
-We first consider the following decidable\footnote{Note that Prob.~\ref{InverseProblem} is decidable for rational inputs $\mathbf{z}_i$ \cite{chrishillar} since the statement that it has a solution can be expressed as a logical sentence in the theory of algebraically closed fields, and this theory has quantifier elimination \cite{basu2006algorithms}.} formulation of sparse coding.
+Let us first consider the following decidable\footnote{Note that Prob.~\ref{InverseProblem} is decidable for rational inputs $\mathbf{z}_i$ \cite{chrishillar} since the statement that it has a solution can be expressed as a logical sentence in the theory of algebraically closed fields, and this theory has quantifier elimination \cite{basu2006algorithms}.} formulation of the dictionary learning problem.
 %The first mathematical problem we consider is the following.
@@
 which is necessary to guarantee the uniqueness of arbitrary $k$-sparse $\mathbf{x}_i$.
-We generalize these results to the practical setting  $\eta > 0$ by considering the following natural notion of stability with respect to measurement error.
+These results can be generalized to the practical setting  $\eta > 0$ by considering the following natural notion of stability with respect to measurement error.
 
@@
 
-The main result of this work is a very general uniqueness theorem for sparse coding (Thm.~\ref{DeterministicUniquenessTheorem}) directly 
+The main result of this work is a very general uniqueness theorem (Thm.~\ref{DeterministicUniquenessTheorem}) directly 
 implying (Cor.~\ref{DeterministicUniquenessCorollary}), which guarantees that sparse representations of a dataset $Z$ are unique up to noise whenever generating dictionaries $\mathbf{A}$ satisfy a spark condition on supports and the original sparse codes $\mathbf{x}_i$ are sufficiently diverse (e.g., Fig.~\ref{noisyrecovery}).
-Moreover, we provide an explicit, computable $\varepsilon(\delta_1, \delta_2)$ in (\ref{epsdel}) that is linear in desired accuracy $\delta_1$, and essentially so in $\delta_2$.
+Moreover, an explicit, computable $\varepsilon(\delta_1, \delta_2)$ that is linear in desired accuracy $\delta_1$, and essentially so in $\delta_2$, is defined in (\ref{epsdel}).
 
-In the next section, we give formal statements of these findings.
-We then extend the same guarantees (Thm.~\ref{SLCopt}) to the following alternate formulation of dictionary learning, which minimizes the total number of nonzero entries in sparse codes.
+The next chapter gives formal statements of these findings.
+The same guarantees are then extended (Thm.~\ref{SLCopt}) to the following alternate formulation of the dictionary learning problem, which seeks to minimize the total number of nonzero entries in sparse codes.
 
@@
 
-Our development of Thm.~\ref{DeterministicUniquenessTheorem} is general enough to provide some uniqueness and stability even when generating $\mathbf{A}$ do not fully satisfy (\ref{SparkCondition}) and recovery dictionaries $\mathbf{B}$ have more columns than $\mathbf{A}$.
+Surprisingly, the development of Thm.~\ref{DeterministicUniquenessTheorem} is general enough to provide some uniqueness and stability even when generating $\mathbf{A}$ do not fully satisfy (\ref{SparkCondition}) and recovery dictionaries $\mathbf{B}$ have more columns than $\mathbf{A}$.
 Moreover, the approach incorporates a theory of combinatorial designs for the sparse supports of generating codes $\mathbf{x}_i$ that should be of independent interest.
-We also give brief arguments adapting our results to dictionaries and codes drawn from probability distributions (Cor.~\ref{ProbabilisticCor}).
-The technical proofs of Thms.~\ref{DeterministicUniquenessTheorem} and ~\ref{SLCopt} are deferred to Sec.~\ref{DUT}, following some necessary definitions and a fact in combinatorial matrix analysis (Lem.~\ref{MainLemma}; proven in the Appendix).
-We discuss these results and their applications in depth in Sec.~\ref{Discussion} and outline open questions and directions for future research in Sec.~\ref{FutureDirections}.
+These results are then adapted to apply to dictionaries and codes drawn from arbitrary (continuous) probability distributions (Cor.~\ref{ProbabilisticCor}).
+
+\section{Outline of the thesis}
+
+TODO 
+%The technical proofs of Thms.~\ref{DeterministicUniquenessTheorem} and ~\ref{SLCopt} are deferred to Chap.~\ref{DUT}, following some necessary definitions and a fact in combinatorial matrix analysis (Lem.~\ref{MainLemma}; proven in the Appendix).
+%These results and their applications are discussed in Chap.~\ref{Discussion} and outline open questions and directions for future research in Sec.~\ref{FutureDirections}.
 %The Appendix contains a proof of Lem.~\ref{MainLemma}.

### 2020-08-05 manuscripts/thesis/proofs.tex
chapters

@@
 \chapter{Definitions and Proofs}\label{DUT} % of Theorems~\ref{DeterministicUniquenessTheorem} and ~\ref{SLCopt}}\label{DUT}
+
+\section{Introduction}
 
@@
 
-\section{Proving the case $k=1$}
-
-We begin our proof of Thm.~\ref{DeterministicUniquenessTheorem} by showing how dictionary recovery \eqref{Cstable} already implies sparse code recovery \eqref{b-PDa} when $\mathbf{A}$ satisfies \eqref{SparkCondition} and \mbox{$\varepsilon < L_{2k}(\mathbf{A}) / C_1$}.
-We temporarily assume (without loss of generality) that $\overline m = m$, so as to omit an otherwise requisite subscript $(\cdot)_J$ around certain matrices and vectors.
+It is instructive to begin the proof of Thm.~\ref{DeterministicUniquenessTheorem} by showing how dictionary recovery \eqref{Cstable} already implies sparse code recovery \eqref{b-PDa} when $\mathbf{A}$ satisfies \eqref{SparkCondition} and \mbox{$\varepsilon < L_{2k}(\mathbf{A}) / C_1$}.
+We shall temporarily assume (without loss of generality) that $\overline m = m$, so as to omit an otherwise requisite subscript $(\cdot)_J$ around certain matrices and vectors.
 By definition of $L_{2k}$ in \eqref{Ldef}, and noting that $\sqrt{k} \|\mathbf{v}\|_2 \geq \|\mathbf{v}\|_1$ for $k$-sparse $\mathbf{v}$, we have for all $i \in [N[$:
@@
 
-The heart of the matter is therefore \eqref{Cstable}, which we now establish beginning with the important special case of $k = 1$.
+The heart of the matter is therefore \eqref{Cstable}, which we shall now establish beginning with the important special case of $k = 1$.
+
+\section{Proving the case $k=1$}
+
+Since the only 1-uniform hypergraph with the SIP is $[m]$, which is obviously regular, we require only $\mathbf{x}_i = c_i \mathbf{e}_i$ for $i \in [m]$, with $c_i \neq 0$ to guarantee  linear independence.
+While we have yet to define $C_1$ generally, in this case we may set $C_1 = 1/ \min_{\ell \in [m]} |c_{\ell}|$ so that $\varepsilon < L_2(\mathbf{A})  \min_{\ell \in [m]} |c_{\ell}|$.
 
 \begin{proof}[Proof of Thm.~\ref{DeterministicUniquenessCorollary} for $k=1$]
-Since the only 1-uniform hypergraph with the SIP is $[m]$, which is obviously regular, we require only $\mathbf{x}_i = c_i \mathbf{e}_i$ for $i \in [m]$, with $c_i \neq 0$ to guarantee  linear independence.
-While we have yet to define $C_1$ generally, in this case we may set $C_1 = 1/ \min_{\ell \in [m]} |c_{\ell}|$ so that $\varepsilon < L_2(\mathbf{A})  \min_{\ell \in [m]} |c_{\ell}|$.
 
@@
 
-We now show that $\pi$ is injective (in particular, a permutation if $\overline m = m$).
+Let us now show that $\pi$ is injective (in particular, a permutation if $\overline m = m$).
 Suppose that $\pi(i) = \pi(j) = \ell$ for some $i \neq j$ and $\ell$.
@@
 An extension of the proof to the general case $k < m$ requires some additional tools to derive the general expression \eqref{Cdef1} for $C_1$.
-These include a generalized notion of distance (Def.~\ref{dDef}) and angle (Def.~\ref{FriedrichsDefinition}) between subspaces as well as a stability result in combinatorial matrix analysis (Lem.~\ref{MainLemma}).
+These include a generalized notion of distance (Def.~\ref{dDef}) and angle (Def.~\ref{FriedrichsDefinition}) between subspaces as well as a stability result in combinatorial matrix analysis (Lem.~\ref{MainLemma}), which is the main lemma doing most of the heavy lifting in the proof of Thm.~\ref{DeterministicUniquenessTheorem}.
 
@@
 
-We note the following facts about $d$. Clearly, 
+Note the following facts about $d$. Clearly, 
 \begin{align}\label{UsubU}
@@
 
-The following is our result in combinatorial matrix analysis; it contains most of the complexity in the proof of Thm.~\ref{DeterministicUniquenessTheorem}.
+The required stability result in combinatorial matrix analysis is the following.
 
@@
 
-We present the constant $C_2$ (a function of $\mathbf{A}$ and $\mathcal{H}$) relative to a quantity used in \cite{Deutsch12} to analyze the convergence of the ``alternating projections" algorithm for projecting a point onto the intersection of subspaces.
-We incorporate this quantity into the following definition, which we refer to in our proof of Lem.~\ref{DistanceToIntersectionLemma} in the Appendix; specifically, we use it to bound the distance between a point and the intersection of subspaces given an upper bound on its distance from each subspace.
+The constant $C_2$ (a function of $\mathbf{A}$ and $\mathcal{H}$) will be presented relative to a quantity used in \cite{Deutsch12} to analyze the convergence of the ``alternating projections" algorithm for projecting a point onto the intersection of subspaces.
+This quantity is incorporated into the following definition, which we shall refer to in the proof of Lem.~\ref{DistanceToIntersectionLemma} in the Appendix; specifically, it will be used to bound the distance between a point and the intersection of subspaces given an upper bound on its distance from each subspace.
 
@@
 
-We next define the constant $C_1 > 0$ of Thm.~\ref{DeterministicUniquenessTheorem} in terms of $C_2$.
+We may now define the constant $C_1 > 0$ of Thm.~\ref{DeterministicUniquenessTheorem} in terms of $C_2$.
 Given vectors $\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$, let $\mathbf{X}$ denote the $m \times N$ matrix with columns $\mathbf{x}_i$ and let $I(S)$ denote the set of indices $i$ for which $\mathbf{x}_i$ is supported in $S$.
-We define:
+Define:
 \begin{align}\label{Cdef1}
@@
 \begin{proof}[Proof of Thm.~\ref{DeterministicUniquenessCorollary} for $k < m$] 
-We find a map $\pi: \mathcal{H} \to {[m] \choose k}$ for which the distance $d(\bm{\mathcal{A}}_S, \bm{\mathcal{B}}_{\pi(S)})$ is controlled by $\varepsilon$ for all $S \in \mathcal{H}$.
+We shall find a map $\pi: \mathcal{H} \to {[m] \choose k}$ for which the distance $d(\bm{\mathcal{A}}_S, \bm{\mathcal{B}}_{\pi(S)})$ is controlled by $\varepsilon$ for all $S \in \mathcal{H}$.
 Applying Lem.~\ref{MainLemma} then completes the proof.
@@
 
-Before moving on to the proof of Thm.~\ref{SLCopt}, we briefly revisit our discussion on sample complexity from the end of the previous section.
+Before moving on to the proof of Thm.~\ref{SLCopt}, let us briefly revisit the discussion on sample complexity from the end of the previous chapter.
 While an exponential number of samples may very well prove to be necessary in the deterministic or almost-certain case, our proof of Thm.~\ref{DeterministicUniquenessTheorem} can be extended to hold with some probability for \emph{any} number of samples by alternative appeal to a probabilistic pigeonholing at the point early in the proof where the (deterministic) pigeonhole principle is applied to show that for every $S \in \mathcal{H}$, there exist $k$ vectors $\mathbf{x}_i$ supported on $S$ whose corresponding $\mathbf{\overline x}_i$ all share the same support.\footnote{A famous example of such an argument is the counter-intuitive ``birthday paradox", which demonstrates that the probability of two people having the same birthday in a room of twenty-three is greater than 50\%.}
@@
 \begin{proof}[Proof of Thm.~\ref{SLCopt}]
-We bound the number of $k$-sparse $\mathbf{\overline x}_i$ from below and then apply Thm.~\ref{DeterministicUniquenessCorollary}. 
+We shall bound the number of $k$-sparse $\mathbf{\overline x}_i$ from below and then apply Thm.~\ref{DeterministicUniquenessCorollary}. 
 %We now apply this fact to bound the number of $k$-sparse $\mathbf{\overline x}_i$. 

### 2020-08-05 manuscripts/thesis/results.tex
chapters

@@
-%\chapter{Results}
-\section{Results}\label{Results}
+\chapter{Results}\label{Results}
+
+\section{Introduction}
+
+TODO
 
@@
 
-Precise statements of our results require that we first identify some combinatorial criteria on the supports\footnote{Recall that a vector $\mathbf{x}$ is said to be \emph{supported} in $S$ when $\mathbf{x} \in \text{\rmfamily span}\{\mathbf{e}_j: j\in S\}$, with $\mathbf{e}_j$ forming the standard column basis.} of sparse vectors.
+\section{Combinatorial designs for sparse supports}
+
+A precise statement of the results requires first the identification of some combinatorial criteria on the supports\footnote{Recall that a vector $\mathbf{x}$ is said to be \emph{supported} in $S$ when $\mathbf{x} \in \text{\rmfamily span}\{\mathbf{e}_j: j\in S\}$, with $\mathbf{e}_j$ forming the standard column basis.} of sparse vectors.
 Let $\{1, \ldots, m\}$ be denoted $[m]$, its power set $2^{[m]}$, and ${[m] \choose k}$ the set of subsets of $[m]$ of size $k$.
 A \emph{hypergraph} on vertices $[m]$  is simply any subset $\mathcal{H} \subseteq 2^{[m]}$.
-We say that $\mathcal{H}$ is \textit{$k$-uniform} when $\mathcal{H} \subseteq {[m] \choose k}$.
+Let us say that $\mathcal{H}$ is \textit{$k$-uniform} when $\mathcal{H} \subseteq {[m] \choose k}$.
 The \emph{degree} $\deg_\mathcal{H}(i)$ of a node $i \in [m]$ is the number of sets in $\mathcal{H}$ that contain $i$, and we say $\mathcal{H}$ is \emph{regular} when for some $r$ we have $\deg_\mathcal{H}(i) = r$ for all $i$ (given such an $r$, we say $\mathcal{H}$ is \textit{$r$-regular}).
-We also write $2\mathcal{H} := \{ S \cup S': S, S' \in \mathcal{H}\}$.
+Let us also write $2\mathcal{H} := \{ S \cup S': S, S' \in \mathcal{H}\}$.
 The following class of structured hypergraphs is a key ingredient in this work.
@@
 
-We next give a quantitative generalization of the spark condition (\ref{SparkCondition}) to combinatorial subsets of supports.
+Next, a quantitative generalization of the spark condition (\ref{SparkCondition}) to combinatorial subsets of supports is given.
 The \emph{lower bound} of an $n \times m$ matrix $\mathbf{M}$ is the largest $\alpha$ with \mbox{$\|\mathbf{M}\mathbf{x}\|_2 \geq \alpha\|\mathbf{x}\|_2$} for all $\mathbf{x} \in \mathbb{R}^m$ \cite{Grcar10}.
@@
 Let $\mathbf{M}_S$ denote the submatrix formed by the columns of a matrix $\mathbf{M}$ indexed by $S \subseteq [m]$ (setting $\mathbf{M}_\emptyset := \mathbf{0}$).
-In the sections that follow, we shall also let $\bm{\mathcal{M}}_S$ denote the column-span of a submatrix $\mathbf{M}_S$, and $\bm{\mathcal{M}}_\mathcal{G}$ to denote $\{\bm{\mathcal{M}}_S\}_{S \in \mathcal{G}}$.
-We define:  % Define $L_\mathcal{H}(\mathbf{M})$ as follows:
+In the sections that follow, let $\bm{\mathcal{M}}_S$ denote the column-span of a submatrix $\mathbf{M}_S$, and $\bm{\mathcal{M}}_\mathcal{G}$ to denote $\{\bm{\mathcal{M}}_S\}_{S \in \mathcal{G}}$.
+Define: % Define $L_\mathcal{H}(\mathbf{M})$ as follows:
 %\begin{align*} 
@@
 
-We are now in a position to state our main result, though for expository purposes we leave the quantity $C_1$ %(a function of $\mathbf{A}$, $\mathbf{x}_1, \ldots, \mathbf{x}_N$, and $\mathcal{H}$) 
+\section{Deterministic uniqueness theorems}
+
+We are now in a position to state the main result, though for expository purposes the quantity $C_1$ will be left%(a function of $\mathbf{A}$, $\mathbf{x}_1, \ldots, \mathbf{x}_N$, and $\mathcal{H}$) 
 undefined until Sec.~\ref{DUT}. All results  below assume real matrices and vectors.
@@
 %\cite{li2004analysis, Georgiev05, Aharon06, Hillar15}
-We should stress here that framing the problem in terms of hypergraphs has allowed us to show, unlike in previous research on the subject, that the matrix $\mathbf{A}$ need not necessarily satisfy \eqref{SparkCondition} to be recoverable from data.
+It should be stressed here that framing the problem in terms of hypergraphs will allowed us to show, unlike in previous research on the subject, that the matrix $\mathbf{A}$ need not necessarily satisfy \eqref{SparkCondition} to be recoverable from data.
 As an example, let $\mathbf{A} = [ \mathbf{e}_1, \ldots, \mathbf{e}_5, \mathbf{v}]$ with $\mathbf{v} = \mathbf{e}_1 + \mathbf{e}_3 + \mathbf{e}_5$ and take $\mathcal{H}$ to be all consecutive pairs of indices $1, \ldots ,6$ arranged in cyclic order.
@@
 In general, however, there is no known efficient procedure.
-We defer a brief discussion on this point to the next section.
+A brief discussion on this point is deferred until later.
 %Another practical implication of Thm.\ref{DeterministicUniquenessTheorem} is the following: there is an effective procedure sufficient to affirm if a proposed solution $(\mathbf{B}, \mathbf{\overline x}_1, \ldots, \mathbf{x}_N)$ to Prob.~\ref{InverseProblem} is indeed unique (up to noise and inherent ambiguities).
@@
 
+\section{Probabilistic uniqueness theorems}
+
 Another extension of Thm.~\ref{DeterministicUniquenessTheorem} can be derived from the following algebraic characterization of the spark condition.
@@
 
-We claim that a similar phenomenon applies to datasets of vectors with a stable sparse representation.
+It turns out that a similar phenomenon applies to datasets of vectors with a stable sparse representation.
 Briefly, following the same procedure as in \cite[Sec.~IV]{Hillar15}, for $k < m$ and $n \geq \min(2k, m)$, we may consider the ``symbolic'' dataset $Y = \{\mathbf{A}\mathbf{x}_1,\ldots,\mathbf{A} \mathbf{x}_N\}$ generated by an indeterminate $n \times m$ matrix $\mathbf{A}$ and $m$-dimensional $k$-sparse vectors $\mathbf{x}_1, \ldots, \mathbf{x}_N$ indeterminate within their supports, which form a regular hypergraph $\mathcal{H} \subseteq {[m] \choose k}$ satisfying the SIP.
@@
 
-We close this section with some comments on the optimality of our results.
+\section{Discussion}
+
+Let us conclude this chapter with some comments on the optimality of these results.
 The linear scaling for $\varepsilon$ in \eqref{epsdel} is essentially optimal (e.g., see \cite{arias2013fundamental}), but a basic open problem remains: how many samples are necessary to determine the sparse coding model?
-Our results demonstrate that sparse codes $\mathbf{x}_i$ drawn from only a polynomial number of $k$-dimensional subspaces permit stable identification of the generating dictionary $\mathbf{A}$. 
-This lends some legitimacy to the use of the model in practice, where data in general are unlikely (if ever) to exhibit the exponentially many possible $k$-wise combinations of dictionary elements required by (to our knowledge) all previously published results.
+These results demonstrate that sparse codes $\mathbf{x}_i$ drawn from only a polynomial number of $k$-dimensional subspaces permit stable identification of the generating dictionary $\mathbf{A}$. 
+This lends some legitimacy to the use of the model in practice, where data in general are unlikely (if ever) to exhibit the exponentially many possible $k$-wise combinations of dictionary elements required by (to my knowledge) all previously published results.
 
 Consequently, if $k$ is held fixed or if the size of the support set of reconstructing codes is polynomial in $\overline m$ and $k$, then a practical (polynomial) amount of data suffices to identify the dictionary.\footnote{In the latter case, a reexamination of the pigeonholing argument in the proof of Thm.~\ref{DeterministicUniquenessTheorem} requires a polynomial number of samples distributed over a polynomial number of supports.} Reasons to be skeptical that this holds in general, however, can be found in \cite{tillmann2014computational, tillmann2015computational}.
-Even so, in the next section we discuss how probabilistic guarantees can in fact be made for any number of available samples.
+Even so, in the next chapter it will be discussed how probabilistic guarantees can in fact be made for any number of available samples.

### 2020-08-05 manuscripts/thesis/results.tex
chapters

@@
 
-\section{Combinatorial designs for sparse supports}
+\section{Combinatorial designs}
 
@@
 
-\section{Deterministic uniqueness theorems}
+\section{Uniqueness Theorems}
+
+\subsection{Deterministic Uniqueness Theorems}
 
 We are now in a position to state the main result, though for expository purposes the quantity $C_1$ will be left%(a function of $\mathbf{A}$, $\mathbf{x}_1, \ldots, \mathbf{x}_N$, and $\mathcal{H}$) 
-undefined until Sec.~\ref{DUT}. All results  below assume real matrices and vectors.
+undefined until Chap.~\ref{DUT}.
+ All results  below assume real matrices and vectors.
 
@@
 \begin{corollary}\label{DeterministicUniquenessCorollary}
-Given any regular hypergraph $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP, there are $N =  |\mathcal{H}| \left[ (k-1){m \choose k} + 1  \right]$ vectors \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} such that every matrix $\mathbf{A}$ satisfying spark condition \eqref{SparkCondition} generates $Y = \{\mathbf{A}\mathbf{x}_1, \ldots, \mathbf{A}\mathbf{x}_N\}$ with a stable $k$-sparse representation in $\mathbb{R}^m$ for $\varepsilon(\delta_1,\delta_2)$ given by \eqref{epsdel}.
+Given any regular hypergraph $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP, there are \mbox{$N =  |\mathcal{H}| \left[ (k-1){m \choose k} + 1  \right]$} vectors \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} such that every matrix $\mathbf{A}$ satisfying spark condition \eqref{SparkCondition} generates $Y = \{\mathbf{A}\mathbf{x}_1, \ldots, \mathbf{A}\mathbf{x}_N\}$ with a stable $k$-sparse representation in $\mathbb{R}^m$ for $\varepsilon(\delta_1,\delta_2)$ given by \eqref{epsdel}.
 \end{corollary}
@@
 
-\section{Probabilistic uniqueness theorems}
+\subsection{Probabilistic uniqueness theorems}
 

### 2020-08-05 manuscripts/thesis/introduction.tex
new intro

@@
 
-Sparse coding is a modern signal processing technique that views each of $N$ observed $n$-dimensional signal samples as a (noisy) linear combination of at most $k$ elementary waveforms drawn from some unknown ``dictionary" of size $m \ll N$ (see \cite{Zhang15} for a comprehensive review).
+%Sparse representation modeling is an approach to signal processing that seeks to describe signals as linear combinations of a few elementary waveforms selected from a pre-specified ``dictionary".
+
+It is a longstanding practice in the field of signal processing to describe signals as linear combinations of elementary waveforms from a pre-specified ``dictionary".
+When this dictionary forms a basis for the signal space, every signal has a unique decomposition into these atomic components.
+In the simplest case, the basis is orthonormal and the representational coefficient scaling a given elementary waveform is merely the inner product of that waveform with the signal.
+%When non-orthogonal, the coefficients are computed by taking the inner product with respect to the components of the dictionary inverse.
+
+Until recently, bases have been the default form of signal representation due largely to their simplicity.
+For many signal analysis tasks, however, there is no one basis expressive enough to reveal clearly all of the relevant features of the signal.
+For example, a signal can be decomposed into its constituent frequencies via the Fourier transform, a linear change of basis.
+If our signal can be either a sine wave or a delta function, neither the standard basis nor the Fourier basis can capture one case as effectively as it can the other.
+
+The need for greater freedom of expression led to the development of redundant signal representations utilizing overcomplete dictionaries containing more atoms than there are dimensions of the signal.
+In this case, there are infinitely many ways in which a signal may be decomposed into its constituent components, and the intention to seek the most informative such representation as measured by some task-specific cost function.
+
+A popular approach to the design of overcomplete dictionaries has been to seek one with respect to which every signal in the signal class of interest has a sparse representation; that is, it can be represented, or at least well-approximated, as a combination of only a few dictionary elements from the bunch.
+Concluding our example, the union of the standard basis with the Fourier basis is an over-complete dictionary with respect to which both sines and delta functions (or any superposition thereof) have the sparsest possible representations as combinations of its elementary waveforms.
+
+Early approaches to sparse coding assumed, as was assumed in our recurring example, a model of the signal class from which a suitable sparsifying dictionary could then be derived.
+While such dictionaries are typically characterized by an analytic formulation and a fast implicit implementation, these models tend to be over-simplistic when applied to natural phenomena.
+
+In contrast, an alternative approach to dictionary design is conditioned on the assumption that the structure of complex natural phenomena can be more accurately extracted directly from a training dataset of signals, a process referred to as dictionary learning.
+In the seminal work \cite{Olshausen96}, the authors trained a dictionary for sparse representation of small image patches collected from a number of images of the natural environment.
+Remarkably, the relatively simple algorithm they applied produced dictionary elements sharing qualitative similarities with linear filters estimated from response properties of simple-cell neurons in mammalian visual cortex, which until then were more weakly described by the analytic Gabor filters (see also \cite{hurri1996image, bell1997independent, van1998independent}).
+Curiously, these waveforms (e.g., Gabor'-like wavelets) appear in dictionaries learned by a variety of algorithms trained over different natural image datasets, suggesting that learned features in natural signals may, in some sense, be canonical \cite{donoho2001can}.
+
+% C&P: A key contribution to the area of dictionary learning was provided by Olshausen and Field in 1996 [34].
+In their widely celebrated paper, the authors trained a dictionary for sparse representation of small image patches collected from a number of natural images.
+With relatively simple algorithmic machinery, the authors were able to show a remarkable resultVthe trained atoms they obtained were incredibly similar to the mammalian simple-cell receptive fields, which until then were only weakly explained via Gabor filters.
+The finding was highly motivating to the sparse representation community, as it demonstrated that the single assumption of sparsity could account for a fundamental biological visual behavior.
+Also, the results demonstrated the potential in example-based methods to uncover elementary structures in complex signal data.
+
+Sparse coding is a modern signal processing technique that views each of $N$ observed $n$-dimensional signal samples as a (noisy) linear combination of at most $k$ elementary waveforms drawn from a ``dictionary" of size $m \ll N$ (see \cite{Zhang15} for a comprehensive review).
 %\IEEEPARstart{A}{}common modern approach to pattern analysis in signal processing is to view each of $N$ observed $n$-dimensional signal samples as a (noisy) linear combination of at most $k$ elementary waveforms drawn from some unknown ``dictionary" of size $m \ll N$ (see \cite{Zhang15} for a comprehensive review).
@@
 
-Motivated by these discoveries and more recent work relating compressed sensing \cite{eldar2012compressed} to a theory of information transmission through random wiring bottlenecks in the brain \cite{Isely10}, this thesis addresses when dictionaries for sparse representation are indeed identifiable from data.
+Motivated by these discoveries and more recent work relating compressed sensing \cite{eldar2012compressed} to a theory of information transmission through random wiring bottlenecks in the brain \cite{Isely10}, this thesis concerns itself with the following question: when is a dictionary indeed identifiable from data?
 Answers to this question may also have implications in practice wherever an appeal is made to latent sparse structure of data (e.g., forgery detection \cite{hughes2010, olshausen2010applied}; brain recordings \cite{jung2001imaging, agarwal2014spatially, lee2016sparse}; and gene expression \cite{wu2016stability}).

### 2020-08-05 manuscripts/thesis/introduction.tex
new intro

--- 2020-08-05 manuscripts/thesis/introduction.tex
@@
 
-Sparse coding is a modern signal processing technique that views each of $N$ observed $n$-dimensional signal samples as a (noisy) linear combination of at most $k$ elementary waveforms drawn from some unknown ``dictionary" of size $m \ll N$ (see \cite{Zhang15} for a comprehensive review).
-%\IEEEPARstart{A}{}common modern approach to pattern analysis in signal processing is to view each of $N$ observed $n$-dimensional signal samples as a (noisy) linear combination of at most $k$ elementary waveforms drawn from some unknown ``dictionary" of size $m \ll N$ (see \cite{Zhang15} for a comprehensive review).
-Optimizing dictionaries subject to this and related sparsity constraints has revealed seemingly characteristic sparse structure in several signal classes of current interest (e.g., in vision \cite{wang2015sparse}).
-Of particular note are the seminal works in the field \cite{Olshausen96, hurri1996image, bell1997independent, van1998independent}, which discovered that dictionaries optimized for coding small patches of ``natural" images share qualitative similarities with linear filters estimated from response properties of simple-cell neurons in mammalian visual cortex.
-Curiously, these waveforms (e.g., ``Gabor'' wavelets) appear in dictionaries learned by a variety of algorithms trained over different natural image datasets, suggesting that learned features in natural signals may, in some sense, be canonical \cite{donoho2001can}.
+%Sparse representation modeling is an approach to signal processing that seeks to describe signals as linear combinations of a few elementary waveforms selected from a pre-specified ``dictionary".
 
-Motivated by these discoveries and more recent work relating compressed sensing \cite{eldar2012compressed} to a theory of information transmission through random wiring bottlenecks in the brain \cite{Isely10}, this thesis addresses when dictionaries for sparse representation are indeed identifiable from data.
-Answers to this question may also have implications in practice wherever an appeal is made to latent sparse structure of data (e.g., forgery detection \cite{hughes2010, olshausen2010applied}; brain recordings \cite{jung2001imaging, agarwal2014spatially, lee2016sparse}; and gene expression \cite{wu2016stability}).
-While several algorithms have recently been proposed to provably recover unique dictionaries under specific conditions (see \cite[Sec.~I-E]{Sun16} for a summary of the state-of-the-art), few theorems can be invoked to justify the consistency of inference under this model of data more broadly.
-To my knowledge, a universal guarantee of the uniqueness and stability of learned dictionaries and the sparse representations they induce over noisy data has yet to appear in the literature.
+It is a longstanding practice in the field of signal processing to describe signals as linear combinations of elementary waveforms from a pre-specified ``dictionary".
+When this dictionary forms a basis for the signal space, every signal has a unique decomposition into these atomic components.
+In the simplest such case, the basis is orthonormal and the representational coefficient scaling a given elementary waveform is merely the inner product of that waveform with the signal.
+%When non-orthogonal, the coefficients are computed by taking the inner product with respect to the components of the dictionary inverse.
 
+Until recently, bases have been the default form of signal representation due largely to their simplicity.
+For many signal analysis tasks, however, there is no one basis expressive enough to reveal clearly all of the relevant features of the signal.
+For example, a signal can be decomposed into its constituent frequencies via the Fourier transform, a linear change of basis.
+If our signal can be either a sine wave or a delta function, neither the standard basis nor the Fourier basis can capture one case as effectively as it can the other.
+
+The need for greater freedom of expression eventually led to the development of redundant signal representations utilizing overcomplete dictionaries containing more atoms than there are dimensions of the signal.
+In this case, there are infinitely many ways in which a signal may be decomposed into its constituent components, and the intention is to seek the most informative such representation as measured by some task-specific cost function.
+
+A popular approach to the design of overcomplete dictionaries has been to seek one with respect to which every signal in the signal class of interest admits a sparse representation; that is, it can be represented, or at least well-approximated, as a combination of only a few dictionary elements from the bunch.
+Finishing with our example, the union of the standard basis with the Fourier basis is an over-complete dictionary with respect to which both sines and delta functions (or any finite superpositions thereof) achieve the sparsest possible representation.
+
+Early approaches to sparse representation modeling assumed a model of the signal class from which a suitable sparsifying dictionary could then be derived, as we have in our recurring example.
+While such dictionaries are typically characterized by an analytic formulation and a fast implicit implementation, they unfortunately tend to be over-simplistic models when applied to natural phenomena.
+
+An alternative modern approach to dictionary design is conditioned on the assumption that the sparse structure of signals conveying information about complex natural phenomena can be more accurately extracted directly from a training dataset, a process referred to as dictionary learning  (see \cite{Zhang15} for a comprehensive review).
+In the seminal work \cite{Olshausen96}, a dictionary trained over a collection of small patches extracted from images of the natural environment was shown to share qualitative similarities with linear filters estimated from the response properties of simple-cell neurons in mammalian visual cortex, which until then had been more weakly described analytically as Gabor filters (see also \cite{hurri1996image, bell1997independent, van1998independent}).
+This remarkable discovery showed that the assumption of sparsity alone could potentially account for a fundamental property of the visual system, and demonstrated the potential of the machine learning approach to dictionary design.
+Even more curiously, these waveforms (e.g., Gabor-like wavelets) have since tended to appear in dictionaries learned by a variety of machine learning algorithms trained over different natural image datasets, suggesting that the optimal dictionaries for these signals may, in some sense, be canonical \cite{donoho2001can}.
+
+%Sparse coding is a modern signal processing technique that views each of $N$ observed $n$-dimensional signal samples as a (noisy) linear combination of at most $k$ elementary waveforms drawn from a ``dictionary" of size $m \ll N$ (see \cite{Zhang15} for a comprehensive review).
+
+%and more recent work relating compressed sensing \cite{eldar2012compressed} to a theory of information transmission through random wiring bottlenecks in the brain \cite{Isely10}, 
+It is natural to wonder, in light of these discoveries, when a dictionary admitting optimally sparse representations of a signal class is indeed identifiable from a representative sample.
+Answers to this question have implications in practice whenever an appeal is made to latent sparse structure of data (e.g., forgery detection \cite{hughes2010, olshausen2010applied}; brain recordings \cite{jung2001imaging, agarwal2014spatially, lee2016sparse}; and gene expression \cite{wu2016stability}).
+Even though several algorithms have recently been proposed to provably recover a unique dictionary under specific conditions (see \cite[Sec.~I-E]{Sun16} for a summary of the state of the art), few theorems can be invoked to justify the consistency of inference under this model of data more broadly.
+Surprisingly, despite the now ubiquitous application of dictionary learning methods in practice, a universal guarantee of the uniqueness and stability of learned dictionaries and the sparse representations they induce over noisy data (noise being inevitable in practice) has yet, to the best of my knowledge, to appear in the literature.
+
+%injective on a sparse domain
 In this work, it is proven very generally that uniqueness and stability is a typical property of learned dictionaries.
-More specifically, it is demonstrated that matrices injective on a sparse domain are identifiable from \mbox{$N = m(k-1){m \choose k} + m$} noisy linear combinations of $k$ of their $m$ columns up to an error that is linear in the noise (Thm.~\ref{DeterministicUniquenessTheorem}).
+Specifically, if each of $N$ observed $n$-dimensional signal samples is viewed as a (noisy) linear combination of at most $k$ elementary waveforms drawn from a suitable dictionary of size $m \ll N$, then the dictionary is identifiable from \mbox{$N = m(k-1){m \choose k} + m$} noisy linear combinations of $k$ of its columns up to an error that is linear in the noise (Thm.~\ref{DeterministicUniquenessTheorem}).
 In fact, provided $n \geq \min(2k,m)$, in almost all cases the problem is well-posed, as per Hadamard \cite{Hadamard1902}, given a sufficient amount of data (Thm.~\ref{robustPolythm} and Cor.~\ref{ProbabilisticCor}).
-These guarantees also hold for the related (and perhaps more commonly posed, e.g.
+Similar guarantees also hold for the related (and perhaps more commonly posed, e.g.
 \cite{rehnsommer2007}) optimization problem seeking a dictionary minimizing the average number of elementary waveforms required to reconstruct each sample of the dataset (Thm.~\ref{SLCopt}).
-To practical benefit, the derivations impose no restrictions on learned dictionaries (e.g., that they, too, be injective over some sparse domain) beyond an upper bound on dictionary size, which is necessary in any case to avoid trivial solutions (e.g., allowing $m = N$).
+To great practical benefit (and technical pain!), these guarantees apply without imposing any assumptions at all on learned dictionaries beyond an upper bound on their size, which is necessary in any case to avoid trivial solutions (e.g., allowing $m = N$).
 %That is, every pair of solutions of comparable size has some number of dictionary elements in common (up to noise), and similarly so for the coefficients of sparse codes they induce.
@@
 
-Let $\mathbf{A} \in \mathbb R^{n \times m}$ be a matrix with columns $\mathbf{A}_j$ ($j = 1,\ldots,m$) and let dataset $Z$ consist of measurements:
+Let us proceed to rigorously define the two formulations of the dictionary learning problem with which this thesis is concerned.
+Fix a matrix $\mathbf{A} \in \mathbb R^{n \times m}$ with the elementary waveforms of the dictionary as its columns  $\mathbf{A}_j$ ($j = 1,\ldots,m$) and let dataset $Z$ consist of measurements:
 \begin{align}\label{LinearModel}
@@
 for $k$-\emph{sparse} $\mathbf{x}_i \in \mathbb{R}^m$ having at most $k<m$ nonzero entries and \emph{noise} $\mathbf{n}_i \in \mathbb{R}^n$, with bounded norm $\| \mathbf{n}_i \|_2 \leq  \eta$ representing our worst-case uncertainty in measuring the product $\mathbf{A}\mathbf{x}_i$.
-Let us first consider the following decidable\footnote{Note that Prob.~\ref{InverseProblem} is decidable for rational inputs $\mathbf{z}_i$ \cite{chrishillar} since the statement that it has a solution can be expressed as a logical sentence in the theory of algebraically closed fields, and this theory has quantifier elimination \cite{basu2006algorithms}.} formulation of the dictionary learning problem.
+We shall first consider the following decidable\footnote{Note that Prob.~\ref{InverseProblem} is decidable for rational inputs $\mathbf{z}_i$ \cite{chrishillar} since the statement that it has a solution can be expressed as a logical sentence in the theory of algebraically closed fields, and this theory has quantifier elimination \cite{basu2006algorithms}.} formulation of the dictionary learning problem.
 %The first mathematical problem we consider is the following.
@@
 \begin{problem}\label{InverseProblem}
-Find a dictionary matrix $\mathbf{B}$ and $k$-sparse codes $\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N$ that satisfy $\|\mathbf{z}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \eta$ for all $i = 1,\ldots,N$.
+Find a matrix $\mathbf{B}$ and $k$-sparse codes $\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N$ that satisfy $\|\mathbf{z}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \eta$ for all $i = 1,\ldots,N$.
 \end{problem}
@@
 which is necessary to guarantee the uniqueness of arbitrary $k$-sparse $\mathbf{x}_i$.
-These results can be generalized to the practical setting  $\eta > 0$ by considering the following natural notion of stability with respect to measurement error.
+We shall generalize these results to the practical setting  $\eta > 0$ by considering the following natural notion of stability with respect to measurement error.
 
@@
 implying (Cor.~\ref{DeterministicUniquenessCorollary}), which guarantees that sparse representations of a dataset $Z$ are unique up to noise whenever generating dictionaries $\mathbf{A}$ satisfy a spark condition on supports and the original sparse codes $\mathbf{x}_i$ are sufficiently diverse (e.g., Fig.~\ref{noisyrecovery}).
-Moreover, an explicit, computable $\varepsilon(\delta_1, \delta_2)$ that is linear in desired accuracy $\delta_1$, and essentially so in $\delta_2$, is defined in (\ref{epsdel}).
+Moreover, (\ref{epsdel}) defines an explicit, computable $\varepsilon(\delta_1, \delta_2)$ that is linear in desired accuracy $\delta_1$, and essentially so in $\delta_2$.
 
-The next chapter gives formal statements of these findings.
+Formal statements of these findings are given in the next chapter.
 The same guarantees are then extended (Thm.~\ref{SLCopt}) to the following alternate formulation of the dictionary learning problem, which seeks to minimize the total number of nonzero entries in sparse codes.

### 2020-08-05 manuscripts/thesis/discussion.tex
new intro

@@
 
-\section{Conclusions}
-
-The main motivation for this work was the observation that characteristic sparse representations emerge from sparse coding models trained over a variety of natural scene datasets by a variety of learning algorithms.
+The main motivation for this work was the observation that characteristic sparse representations tend to emerge from sparse coding models trained over a variety of natural scene datasets by a variety of learning algorithms.
 The theorems proven here provide some insight into this phenomenon by establishing very general conditions under which identification of the model parameters is not only possible but also robust to measurement and modeling error.
@@
 
-While the extension from exact recovery to the noisy stability of dictionary learning is significant, the fact that the analysis relies on metrics of the data that are not feasible to compute limits its impact to the scientific community beyond computer science and applied mathematics.
-What sets the main results of this work apart from the vast majority of results in the field is that they are deterministic, and do not depend on any kind of assumption about the particular random distribution from which the sparse supports, coefficients, or dictionary entries are drawn (though Cor.~\ref{ProbabilisticCor} makes a sweeping statement applicable to all continuous distributions).
+While the extension from exact recovery to the noisy stability of dictionary learning may be significant, the fact that the analysis relies on metrics of the data that are not feasible to compute limits its impact to the scientific community beyond computer science and applied mathematics.
 Consequently, the inferences of those applying dictionary learning methods to inverse problems in their research are justified only in principle; but this is unavoidably the case for NP-hard problems.
+What sets the main results of this work apart from the vast majority of results in the field, however, is their deterministic nature.
+They do not depend on any kind of assumption about the particular random distribution from which the sparse supports, coefficients, or dictionary entries are drawn (e.g., Cor.~\ref{ProbabilisticCor} makes a sweeping statement applicable to all continuous distributions).
 
@@
 
-It is possible to tighten the pigeonholing argument in the proof of Thm.~\ref{DeterministicUniquenessTheorem} and thereby reduce the deterministic sample complexity without recourse to uncertainty (as previously suggested).
+It is possible to tighten the pigeonholing argument in the proof of Thm.~\ref{DeterministicUniquenessTheorem} and thereby reduce the deterministic sample complexity without recourse to uncertainty.
 The argument as presented iterates over supports $S \in \mathcal{H}$, in each case determining a corresponding support $\overline S \in {[\overline m] \choose k}$ without consideration of previously matched support pairs; and yet the assumption $L_{2\mathcal{H}}(\mathbf{A}) > 0$ implies that no two supports in $\mathcal{H}$ can map to the same $\overline S$.
@@
 
-A commonly applied workaround to the intractability of Prob.~\ref{SLCopt} (see \cite{tillmann2015computational}) is to swap out the $\ell_0$-norm in \eqref{minsum} for $\ell_1$-norm, thereby transforming the inference of sparse $\mathbf{\overline x}_i$ for a given $\mathbf{B}$ into a convex optimization solvable by a linear program.
+A commonly applied workaround to the intractability of Prob.~\ref{SLCopt} (see \cite{tillmann2015computational}) is to swap out the $\ell_0$-norm in \eqref{minsum} for $\ell_1$-norm, thereby transforming the inference of sparse $\mathbf{\overline x}_i$ for a fixed $\mathbf{B}$ into a convex optimization solvable by a linear program.
 A major advance in compressive sensing was the discovery that \eqref{minsum} can in fact be solved in this way for fixed $\mathbf{B}$ provided $L_{2k}(\mathbf{B})$ is large enough \cite{eldar2012compressed}.
+
 The current work provides conditions on the generating dictionary $\mathbf{A}$ and $k$-sparse codes $\mathbf{x}_i$ under which \emph{all} matrices $\mathbf{B}$ (of bounded column-norm) that solve Prob.~\ref{OptimizationProblem} have $L_{2k}(\mathbf{B})$ bounded from below; specifically, $L_{2k}(\mathbf{B}) \geq \left(L_{2k}(\mathbf{A}) - C_1\varepsilon \right) / \|\mathbf{D}\|_1$ in the case where $\mathbf{A}$ satisfies \eqref{SparkCondition}.
 Thus, there is some noise bound inside of which all solutions to Prob.~\ref{OptimizationProblem} are solutions to the convexified problem as well.
-It remains to determine practical constraints that would exclude alternative dictionaries which may solve the convefixied problem without solving Prob.~\ref{OptimizationProblem}.
+It is an open question as to whether there exist practical constraints that would exclude any remaining solutions to the convefixied problem that don't also solve Prob.~\ref{OptimizationProblem}.
 

### 2020-08-05 manuscripts/thesis/introduction.tex
new intro

@@
 implying (Cor.~\ref{DeterministicUniquenessCorollary}), which guarantees that sparse representations of a dataset $Z$ are unique up to noise whenever generating dictionaries $\mathbf{A}$ satisfy a spark condition on supports and the original sparse codes $\mathbf{x}_i$ are sufficiently diverse (e.g., Fig.~\ref{noisyrecovery}).
-Moreover, (\ref{epsdel}) defines an explicit, computable $\varepsilon(\delta_1, \delta_2)$ that is linear in desired accuracy $\delta_1$, and essentially so in $\delta_2$.
+Moreover, an explicit, computable $\varepsilon(\delta_1, \delta_2)$ is given in (\ref{epsdel}) that is linear in desired accuracy $\delta_1$, and essentially so in $\delta_2$.
 
-Formal statements of these findings are given in the next chapter.
-The same guarantees are then extended (Thm.~\ref{SLCopt}) to the following alternate formulation of the dictionary learning problem, which seeks to minimize the total number of nonzero entries in sparse codes.
+The same guarantees can be extended (Thm.~\ref{SLCopt}) to the following alternate formulation of the dictionary learning problem, which seeks to minimize the total number of nonzero entries in sparse codes.
 
@@
 Moreover, the approach incorporates a theory of combinatorial designs for the sparse supports of generating codes $\mathbf{x}_i$ that should be of independent interest.
-These results are then adapted to apply to dictionaries and codes drawn from arbitrary (continuous) probability distributions (Cor.~\ref{ProbabilisticCor}).
 
@@
 
-TODO 
-%The technical proofs of Thms.~\ref{DeterministicUniquenessTheorem} and ~\ref{SLCopt} are deferred to Chap.~\ref{DUT}, following some necessary definitions and a fact in combinatorial matrix analysis (Lem.~\ref{MainLemma}; proven in the Appendix).
-%These results and their applications are discussed in Chap.~\ref{Discussion} and outline open questions and directions for future research in Sec.~\ref{FutureDirections}.
+Formal statements of the main findings described above are given in Chap.~\ref{Results}, along with their adaptation to dictionaries and codes drawn from arbitrary (continuous) probability distributions (Cor.~\ref{ProbabilisticCor}).
+For clarity of exposition, the technical proofs of Thms.~\ref{DeterministicUniquenessTheorem} and ~\ref{SLCopt} are deferred to Chap.~\ref{DUT}, following some necessary definitions and the statement of a key lemma in combinatorial matrix analysis (Lem.~\ref{MainLemma}; proven in the Appendix).
+These results and their applications are discussed in Chap.~\ref{Discussion}, which concludes with some open questions and directions for future research seeded in part by the results of more practically-minded simulations.
 %The Appendix contains a proof of Lem.~\ref{MainLemma}.

### 2020-08-05 manuscripts/thesis/proofs.tex
chapters
new intro

@@
-\chapter{Definitions and Proofs}\label{DUT} % of Theorems~\ref{DeterministicUniquenessTheorem} and ~\ref{SLCopt}}\label{DUT}
-
-\section{Introduction}
+\chapter{Proofs}\label{DUT} % of Theorems~\ref{DeterministicUniquenessTheorem} and ~\ref{SLCopt}}\label{DUT}
 
@@
 
-\section{The main lemma}
+\section{Stating the main lemma}
 
 An extension of the proof to the general case $k < m$ requires some additional tools to derive the general expression \eqref{Cdef1} for $C_1$.
-These include a generalized notion of distance (Def.~\ref{dDef}) and angle (Def.~\ref{FriedrichsDefinition}) between subspaces as well as a stability result in combinatorial matrix analysis (Lem.~\ref{MainLemma}), which is the main lemma doing most of the heavy lifting in the proof of Thm.~\ref{DeterministicUniquenessTheorem}.
+These include a generalized notion of distance (Def.~\ref{dDef}) and angle (Def.~\ref{FriedrichsDefinition}) between subspaces as well as a stability result in combinatorial matrix analysis (Lem.~\ref{MainLemma}), which contains most of the complexity of the proof of Thm.~\ref{DeterministicUniquenessTheorem}.
 
@@
 
-The required stability result in combinatorial matrix analysis is the following.
+The required stability result in combinatorial matrix analysis is the following. For expository purposes, the proof of this fact is relegated to the Appendix.
 
@@
 The main challenge was to generalize Lem.~\ref{MainLemma} to the case where the $k$-dimensional subspaces spanned by corresponding submatrices $\mathbf{A}_S$ and $\mathbf{B}_{\pi(S)}$ are assumed to be``close" but not identical.
-Unlike in \cite{Hillar15} where an inductive argument could be applied to the noiseless case, here it had to be explicitly demonstrated that this proximity relation is propagated through iterated intersections right down to the spans of the dictionary elements themselves.
+Referring now to the proof in the Appendix, the situation is unlike that in \cite{Hillar15}, where an inductive argument could be applied to the noiseless case.
+Rather, here it has to be explicitly demonstrated that this proximity relation is propagated through iterated intersections right down to the spans of the dictionary elements themselves.
 Lem.~\ref{DistanceToIntersectionLemma} was designed to encapsulate this fact, proven by appeal to a convergence guarantee for an alternating projections algorithm first proposed by von Neumann.
@@
 
-As it seemed to benefit a reviewer of this work, a brief discussion on how the deterministic sample complexity $N = |\mathcal{H}\left[|(k-1){m \choose k} + 1\right]$ derived here compares to those listed in the the top two rows listed in Table I of \cite{Hillar15} may be in order.
-To be clear, the theory developed here is strictly more general, since $\mathcal{H}$ can always be taken to be ${[m] \choose k}$.
-The point of difference in this comparison is the assumed set of supports for sparse codes, which is always ${[m] \choose k}$ in \cite{Hillar15}, whereas here it can be assumed to be any regular $k$-uniform hypergraph that satisfies the SIP.
-By row, %, assuming for our results that sufficient data have been sampled from all supports in a hypergraph H satisfying the SIP:
-\begin{enumerate}
-\item[I.] The result here improves upon the listed $k{m \choose k}^2$ by an exponential factor, since for every $k < m$ there exists a regular $k$-uniform hypergraph $\mathcal{H}$ with $|\mathcal{H}| = m$ satisfying the SIP.
-\item[II.] The authors in \cite{Hillar15} have applied measure-theoretic arguments to achieve $(k+1){m \choose k}$ with almost-certainty (i.e.
-with probability one), a factor of $m$ reduction over that for which certainty can alternatively be guaranteed here.
-%\item[III.] A direct comparison cannot be made because it is an open question as to the probability that a random set of supports satisfies the SIP.
-This would be an interesting problem for the community to solve; regardless, the result of \cite{Hillar15} is still implied by the more general theory given here.
-%\item[IV.] The result here is $|\mathcal{H}\left[|(k-1){m \choose k} + 1\right]$ with probability one compared to $(k+1){m \choose k}$ with probability one.
-In this case the sample complexity stated in \cite{Hillar15} is marginally better, but it relies on a noise-free technicality unique to their assumption $\mathcal{H} = {m \choose k}$.
-%differs in flavor: their $\mathbf{x_i}$ are assumed to be distributed as $(k+1)$ samples per support for every support of size $k \in [m]$, whereas here it is assumed that $(k-1){m \choose k}$ codes $\mathbf{x_i}$ are distributed over each support in some hypergraph $\mathcal{H}$ satisfying the SIP.
-%\item[V.] Again, a direct comparison cannot be made for the reason stated for row III.
-\end{enumerate}
+\section{Appendix: Proving the main lemma}\label{proofs}
+
+We shall prove Lem.~\ref{MainLemma} after the following auxiliary lemmas.  % stating and proving some auxiliary lemmas. 
+%First, note that since $\|\mathbf{A}\mathbf{x}\|_2 \leq \max_j\|\mathbf{A}_j\|_2\|\mathbf{x}\|_1$ and $\|\mathbf{x}\|_1 \leq \sqrt{k} \|\mathbf{x}\|_2$ for $k$-sparse $\mathbf{x}$, by \eqref{Ldef} we have the following frequently applied inequality:
+%\begin{align}\label{delrho}
+%L_{k'}(\mathbf{A}) \leq  \max_j\|\mathbf{A}_j\|_2 \ \ \text{for all $k' \leq 2k$}.
+%\end{align}
+
+% and then sketch the proofs of Thm.~\ref{robustPolythm} and Cor.~\ref{ProbabilisticCor}.
+
+%\begin{lemma}\label{spanIntersectionLemma}
+%Let $\mathbf{M} \in \mathbb{R}^{n \times m}$. If every $2k$ columns of $\mathbf{M}$ are linearly independent, then for any $F \subseteq {[m] \choose k}$:
+%\begin{align*}
+%\text{\rmfamily span}\{\mathbf{M}_{\cap F}\}  = \bigcap_{S \in F} \text{\rmfamily span}\{\mathbf{M}_S\}.
+%\end{align*}
+%\end{lemma}
+%\begin{proof}
+%Using induction on $|F|$, it is enough to prove the lemma when $|F| = 2$; but this case follows directly from the assumption.
+%\end{proof}
+
+\begin{lemma}\label{spanIntersectionLemma}
+If $f: V \to W$ is injective, then $f\left(\cap_{i=1}^\ell V_i \right) =  \cap_{i=1}^\ell f\left(V_i\right)$ for any $V_1, \ldots, V_\ell \subseteq V$. ($f(\emptyset):=\emptyset$.)
+%In particular, if for some $E \in 2^{[m]}$ the map $M \in \mathbb{R}^{n \times m}$ is injective on $\cup_{S \in \mathcal{H}} \text{span}\{e_i\}_{i \in S}$ then $\text{span}\{ M_{\cap_{S \in \mathcal{H}} S} \} = \cap_{S \in \mathcal{H}} \text{span}\{M_S\}$.
+\end{lemma}
+\begin{proof}
+By induction, it is enough to prove the case $\ell = 2$.
+Clearly, for any map $f$, if $w \in f(U \cap V)$ then $w \in f(U)$ and $w \in f(V)$; hence, $w \in f(U) \cap f(V)$.
+If $w \in f(U) \cap f(V)$, then $w \in f(U)$ and $w \in f(V)$; thus, $w = f(u) = f(v)$ for some $u \in U$ and $v \in V$, implying $u = v$ by injectivity of $f$.
+It follows that $u \in U \cap V$ and $w \in f(U \cap V)$.
+\end{proof}
+In particular, if a matrix $\mathbf{A}$ satisfies $L_{2\mathcal{H}}(\mathbf{A}) > 0$, then taking $V$ to be the union of subspaces consisting of vectors with supports in $2\mathcal{H}$, we have $\bm{\mathcal{A}}_{\cap \mathcal{G}} = \cap \bm{\mathcal{A}}_\mathcal{G}$ for all $\mathcal{G} \subseteq \mathcal{H}$.
+% \vspace{-.4 cm}
+
+\begin{lemma}\label{DistanceToIntersectionLemma}
+Let $\mathcal{V} = \{V_i\}_{i=1}^k$ be a set of two or more subspaces of $\mathbb{R}^m$, and set $V = \cap \mathcal{V} $.
+For  $\mathbf{u} \in \mathbb{R}^m$, we have (recall Defs.~\ref{dDef}~\&~\ref{FriedrichsDefinition}):
+\begin{align}\label{DTILeq}
+\text{\rmfamily dist}(\mathbf{u}, V) \leq \frac{1}{1 - \xi(\mathcal{V})} \sum_{i=1}^k \text{\rmfamily dist}(\mathbf{u}, V_i).
+\end{align}
+\end{lemma}
+\begin{proof} 
+% When $V = \{\mathbf{0}\}$, the result is trivial, so suppose otherwise.  
+Recall the projection onto the subspace $V \subseteq \mathbb{R}^m$ is the mapping $\Pi_V: \mathbb{R}^m \to V$ that associates with each $\mathbf{u}$ its unique nearest point in $V$; i.e., $\|\mathbf{u} - \Pi_V\mathbf{u}\|_2 = \text{\rmfamily dist}(\mathbf{u}, V)$.
+By repeatedly applying the triangle inequality, we have:
+\begin{align}\label{f}
+\|\mathbf{u} - &\Pi_V\mathbf{u}\|_2 
+\leq \|\mathbf{u} - \Pi_{V_k} \mathbf{u}\|_2 + \|\Pi_{V_k}  \mathbf{u} - \Pi_{V_k}\Pi_{V_{k-1}}\mathbf{u}\|_2 \nonumber \\
+&\ \ \ \ \ \ \ \ \ \ \ + \cdots + \|\Pi_{V_k} \Pi_{V_{k-1}}\cdots \Pi_{V_1} \mathbf{u} - \Pi_V \mathbf{u}\|_2 \nonumber \\
+&\leq  \sum_{\ell=1}^k \|\mathbf{u} - \Pi_{V_{\ell}} \mathbf{u}\|_2 
++ \|(\Pi_{V_k}\cdots\Pi_{V_{1}} - \Pi_V) \mathbf{u}\|_2,
+\end{align}
+where we have also used that the spectral norm of the orthogonal projections $\Pi_{V_{\ell}}$ satisfies $\|\Pi_{V_{\ell}}\|_2 \leq 1$ for all $\ell$.
+
+It remains to bound the second term in \eqref{f} by $\xi(\mathcal{V}) \|\mathbf{u} - \Pi_V\mathbf{u}\|_2$.
+First, note that $\Pi_{V_\ell} \Pi_V = \Pi_V$ and $\Pi_V^2 = \Pi_V$, so we have $\|(\Pi_{V_k} \cdots \Pi_{V_1} - \Pi_V) \mathbf{u} \|_2
+= \| ( \Pi_{V_k} \cdots\Pi_{V_1} - \Pi_V ) (\mathbf{u} - \Pi_V\mathbf{u})\|_2$. % \leq z\|\mathbf{u} - \Pi_V\mathbf{u}\|_2$.
+Consequently, inequality \eqref{DTILeq} follows from \cite[Thm.~9.33]{Deutsch12}:
+\begin{align}
+\|\Pi_{V_k}\Pi_{V_{k-1}}\cdots\Pi_{V_1} \mathbf{x} - \Pi_V\mathbf{x}\|_2 \leq z \|\mathbf{x}\|_2, \ \ \text{for all } \mathbf{x},
+\end{align}
+with \mbox{$z^2= 1 - \prod_{\ell =1}^{k-1}(1-z_{\ell}^2)$} and \mbox{$z_{\ell} = \cos\theta\left(V_{\ell}, \cap_{s=\ell+1}^k V_s\right)$} (recall $\theta$ from Def.~\ref{FriedrichsDefinition}), after substituting $\xi(\mathcal{V})$ for $z$ and rearranging terms.
+\end{proof}
+\begin{lemma}\label{NonEmptyLemma} 
+Fix an $r$-regular hypergraph $\mathcal{H} \subseteq 2^{[m]}$ satisfying the SIP.
+If the map $\pi: \mathcal{H} \to 2^{[\overline m]}$ has $\sum_{S \in \mathcal{H}} |\pi(S)| \geq \sum_{S \in \mathcal{H}} |S|$ and:
+\begin{align}\label{cond}
+	|\cap \pi(\mathcal{G})| \leq |\cap \mathcal{G} |,\ \ \   \text{for } \mathcal{G} \in {\mathcal{H} \choose r} \cup {\mathcal{H} \choose r+1},
+\end{align}
+%
+then $\overline m \geq m$; and if $\overline m  (r-1) < mr$, the map $i \mapsto \cap_{S \in \sigma(i)} \pi(S)$ is an injective function to $[\overline m]$ from some $J \subseteq [m]$ of size $m - (r-1)(\overline m - m)$ (recall $\sigma$ from Def.~\ref{sip}).
+%In particular, if $\overline m = m$ then $\pi$ is induced by a permutation on $[m]$.
+\end{lemma}
+
+\begin{proof}
+Consider the following set: $T_1 := \{(i, S): i \in \pi(S), S \in \mathcal{H}\}$, which numbers $|T_1| = \sum_{S \in \mathcal{H}} |\pi(S)| \geq \sum_{S \in \mathcal{H}} |S| = \sum_{i \in [m]} \deg_\mathcal{H}(i) = mr$ by $r$-regularity of $\mathcal{H}$.
+Note that $|T_1| \leq \overline m r$; otherwise, pigeonholing the tuples of $T_1$ with respect to their $\overline m$ possible first elements would imply that more than $r$ of the tuples in $T_1$ share the same first element.
+This cannot be the case, however, since then some $\mathcal{G} \in {\mathcal{H} \choose r+1}$ formed from any $r+1$ of their second elements would satisfy $\cap \pi(\mathcal{G}) \neq 0$; hence, $|\cap \mathcal{G}| \neq 0$ by \eqref{cond}, contradicting $r$-regularity of $\mathcal{H}$.
+It follows that $\overline m \geq m$.
+
+Suppose now that $\overline m (r-1) < mr$, so that $p := mr - \overline m (r-1)$ is positive and $|T_1| \geq \overline m (r - 1) + p$.
+Pigeonholing $T_1$ into $[\overline m]$ again, there are at least $r$ tuples in $T_1$ sharing some first element; that is, for some $\mathcal{G}_1 \subseteq \mathcal{H}$ of size $|\mathcal{G}_1| \geq r$, we have $|\cap \pi(\mathcal{G}_1)| \geq 1$ and (by \eqref{cond}) $|\cap \mathcal{G}_1| \geq 1$.
+Since no more than $r$ tuples of $T_1$ can share the same first element, we in fact have $|\mathcal{G}_1| = r$.
+It follows by $r$-regularity that $\mathcal{G}_1$ is a star of $\mathcal{H}$; hence, $|\cap \mathcal{G}_1| = 1$ by the SIP and $|\cap \pi(\mathcal{G}_1)|  = 1$ by \eqref{cond}.
+
+If $p=1$, then we are done.
+Otherwise, define $T_2 := T_1 \setminus \{(i,S) \in T_1: i = \cap \pi(\mathcal{G}_1)\}$, which contains $|T_2| = |T_1| - r \geq (\overline m - 1)(r-1) + (p-1)$ ordered pairs having $\overline m - 1$ distinct first indices.
+Pigeonholing $T_2$ into $[\overline m - 1]$ and repeating the above arguments produces the star $\mathcal{G}_2 \in {\mathcal{H} \choose r}$ with intersection $\cap \mathcal{G}_2$ necessarily distinct (by $r$-regularity) from $\cap \mathcal{G}_1$.
+Iterating this procedure $p$ times in total yields the stars $\mathcal{G}_i$ for which $\cap\mathcal{G}_i \mapsto \cap \pi(\mathcal{G}_i)$ defines an injective map to $[\overline m]$ from $J = \{\cap \mathcal{G}_1, \ldots, \cap \mathcal{G}_p\} \subseteq [m]$.
+\end{proof}
+
+\begin{proof}[Proof of Lem.~\ref{MainLemma}]
+%We will show that the bound \eqref{GapUpperBound} trickles through the intersection semi-lattices of $\{\bm{\mathcal{A}}_S\}_{S \in \mathcal{H}}$ and $\{\bm{\mathcal{B}}_{\overline S}\}_{\overline S \in \pi(\mathcal{H})}$ to yield \eqref{MainLemmaBPD} by virtue of the SIP.
+Let us begin by showing that $\dim(\bm{\mathcal{B}}_{\pi(S)}) = \dim(\bm{\mathcal{A}}_S)$ for all $S \in \mathcal{H}$.
+Note that since $\|\mathbf{A}\mathbf{x}\|_2 \leq \max_j\|\mathbf{A}_j\|_2\|\mathbf{x}\|_1$ and $\|\mathbf{x}\|_1 \leq \sqrt{k} \|\mathbf{x}\|_2$ for all $k$-sparse $\mathbf{x}$, by \eqref{Ldef} we have $L_2(\mathbf{A}) \leq \max_j\|\mathbf{A}_j\|_2$ and therefore (as $0 \leq \xi < 1$) the right-hand side of \eqref{GapUpperBound} is less than one.
+From \eqref{dimLem}, we have $|\pi(S)| \geq \dim(\bm{\mathcal{B}}_{\pi(S)}) \geq \dim(\bm{\mathcal{A}}_S) = |S|$, the final equality holding by injectivity of $\mathbf{A}_S$.
+As $|\pi(S)| = |S|$, the claim follows.
+Note, therefore, that $\mathbf{B}_{\pi(S)}$ has full-column rank for all $S \in \mathcal{H}$.
+
+We shall next demonstrate that \eqref{cond} holds.
+Fixing $\mathcal{G} \in {\mathcal{H} \choose r} \cup {\mathcal{H} \choose r+1}$, it suffices to show that $d(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}, \bm{\mathcal{A}}_{\cap \mathcal{G}} ) < 1$, since by \eqref{dimLem} we then have $|\cap \pi(\mathcal{G})| = \dim(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}) \leq \dim(\bm{\mathcal{A}}_{\cap \mathcal{G}}) = |\cap \mathcal{G}|$, with equalities from the full column-ranks of $\mathbf{A}_{S}$ and $\mathbf{B}_{\pi(S)}$ for all $S \in \mathcal{H}$.\footnote{Note that if ever $\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})} \neq /bfseries 0$ while $\cap \mathcal{G} = \emptyset$, we would have $d(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}, \bm 0 ) = 1$.
+However, that leads to a contradiction.} Observe that $d(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}, \bm{\mathcal{A}}_{\cap \mathcal{G}}  )
+\leq d\left( \cap \bm{\mathcal{B}}_{\pi(\mathcal{G})}, \cap \bm{\mathcal{A}}_\mathcal{G} \right)$ by \eqref{UsubU}, since trivially $\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})} \subseteq \cap \bm{\mathcal{B}}_{\pi(\mathcal{G})}$ and also $\bm{\mathcal{A}}_{\cap \mathcal{G}} = \cap \bm{\mathcal{A}}_\mathcal{G}$ by Lem.~\ref{spanIntersectionLemma}.
+Recalling Def.~\ref{dDef} and applying Lem.~\ref{DistanceToIntersectionLemma} yields:
+\begin{align}
+d\left( \cap \bm{\mathcal{B}}_{\pi(\mathcal{G})}, \cap \bm{\mathcal{A}}_\mathcal{G} \right)
+&\leq \max_{\mathbf{u} \in \cap \bm{\mathcal{B}}_{\pi(\mathcal{G})}, \ \|\mathbf{u}\|_2 \leq 1} \sum_{S \in \mathcal{G}} \frac{ \text{\rmfamily dist}\left( \mathbf{u},\bm{\mathcal{A}}_{S} \right) }{ 1 - \xi( \bm{\mathcal{A}}_\mathcal{G} ) } \nonumber \\
+&= \sum_{S \in \mathcal{G}} \frac{ d\left( \cap \bm{\mathcal{B}}_{\pi(\mathcal{G})},\bm{\mathcal{A}}_{S} \right) }{ 1 - \xi( \bm{\mathcal{A}}_\mathcal{G} ) }, \nonumber
+\end{align}
+passing the maximum through the sum.
+Since $\cap \bm{\mathcal{B}}_{\pi(\mathcal{G})} \subseteq \bm{\mathcal{B}}_{\pi(S)}$ for all $S \in \mathcal{G}$, by \eqref{UsubU} the numerator of each term in the sum above is bounded by \mbox{$d\left( \bm{\mathcal{B}}_{\pi(S)},\bm{\mathcal{A}}_{S} \right) = d\left(\bm{\mathcal{A}}_{S}, \bm{\mathcal{B}}_{\pi(S)} \right) \leq \varepsilon$}, with the equality from \eqref{eqdim} since $\dim(\bm{\mathcal{B}}_{\pi(S)}) = \dim(\bm{\mathcal{A}}_S)$.
+Thus, altogether:
+\begin{align}\label{last}
+d(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}, \bm{\mathcal{A}}_{\cap \mathcal{G}} )
+\leq \frac{|\mathcal{G}| \varepsilon}{1 - \xi( \bm{\mathcal{A}}_\mathcal{G} )}
+\leq \frac{C_2 \varepsilon}{\max_j\|\mathbf{A}_j\|_2},
+\end{align}
+recalling the definition of $C_2$ in \eqref{Cdef2}.
+Lastly, since $C_2 \varepsilon < L_2(\mathbf{A}) \leq \max_j\|\mathbf{A}_j\|_2$, we have $d(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}, \bm{\mathcal{A}}_{\cap \mathcal{G}} ) \leq 1$ and therefore \eqref{cond} holds.
+
+%Keeping in mind that $d(U',V) \leq d(U,V)$ whenever $U' \subseteq U$ and applying (in order) Lem.~\ref{spanIntersectionLemma}, Lem.~\ref{DistanceToIntersectionLemma}, \eqref{eqdim}, \eqref{GapUpperBound}, and \eqref{Cdef2} gives:
+%\begin{align}\label{randoml}
+%d(&\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}, \bm{\mathcal{A}}_{\cap \mathcal{G}}  ) 
+%\leq d\left( \cap \bm{\mathcal{B}}_{\pi(\mathcal{G})}, \cap \bm{\mathcal{A}}_\mathcal{G} \right)
+%\leq \sum_{T \in \mathcal{G}} \frac{ d\left( \cap \bm{\mathcal{B}}_{\pi(\mathcal{G})},\bm{\mathcal{A}}_{T} \right) }{ 1 - \xi( \bm{\mathcal{A}}_\mathcal{G} ) } \nonumber \\
+%&\leq \sum_{T \in \mathcal{G}} \frac{ d\left( \bm{\mathcal{B}}_{\pi(T)},\bm{\mathbf{A}}_{T} \right) }{ 1 - \xi( \bm{\mathcal{A}}_\mathcal{G} ) }
+%\leq \frac{|\mathcal{G}| \varepsilon}{1 - \xi( \bm{\mathcal{A}}_\mathcal{G} )} 
+%\leq \frac{C_2 \varepsilon}{\max_j\|\mathbf{A}_j\|_2},
+%\end{align}
+%
+%which is less than one, since $C_2 \varepsilon < L_2(\mathbf{A}) \leq \max_j\|\mathbf{A}_j\|_2$.
+
+Applying Lem.~\ref{NonEmptyLemma}, the association $i \mapsto \cap_{S \in \sigma(i)} \pi(S)$ is an injective map $\overline \pi: J \to [\overline m]$ for some $J \subseteq [m]$ of size $m - (r-1)(\overline m - m)$, and $\mathbf{B}_{\overline \pi(i)} \neq \mathbf{0}$ for all $i \in J$ since the columns of $\mathbf{B}_{\pi(S)}$ are linearly independent for all $S \in \mathcal{H}$.
+Letting $\overline \varepsilon := C_2 \varepsilon / \max_i \|\mathbf{A}_i\|_2$, it follows from \eqref{eqdim} and \eqref{last} that $d\left( \bm{\mathcal{A}}_i, \bm{\mathcal{B}}_{\overline \pi(i)} \right) = d\left(\bm{\mathcal{B}}_{\overline \pi(i)},  \bm{\mathcal{A}}_i \right)  \leq \overline \varepsilon$ for all $i \in J$.
+%Fixing $\overline \varepsilon = C_2\varepsilon$ and letting $c_i = \|\mathbf{A}_i\|_2^{-1}$, we thus have that for each $\mathbf{e}_i \in \mathbb{R}^m$ with $i \in J$ there exists some $\overline{c}_i \in \mathbb{R}$ such that $\|c_i\mathbf{A}\mathbf{e}_i - \overline{c}_i \mathbf{B}\mathbf{e}_{\overline \pi(i)}\|_2 \leq \overline \varepsilon < L_2(\mathbf{A}) \min_{i\in J} |c_i|$.
+But this is exactly the supposition in \eqref{1D}, and the result follows from the case $k=1$ in Sec.~\ref{DUT} applied to the submatrix $\mathbf{A}_J$.
+Setting $c_i := \|\mathbf{A}_i\|_2^{-1}$ so that $\|c_i\mathbf{Ae}_i\|_2 = 1$, by Def.~\ref{dDef} for all $i \in J$:
+\begin{align*}
+\min_{\overline c_i \in \mathbb{R}} \|c_i\mathbf{Ae}_i - \overline c_i \mathbf{Be}_{\overline \pi(i)} \|_2
+\leq d\left( \bm{\mathcal{A}}_i, \bm{\mathcal{B}}_{\overline \pi(i)} \right)
+\leq \overline \varepsilon,
+%&= \max_{\bm{u} \in \bm{\mathcal{A}}_i, \|\bm{u}\|_2 \leq 1} \text{dist}\left(\bm{u}, \bm{\mathcal{B}}_{\overline \pi(i)} \right) \\
+%&\geq  \text{dist}\left(c_i\bm{Ae}_i, \mathbf{Be}_{\overline \pi(i)} \right) \\
+%&= \min_{\overline c_i \in \mathbb{R}} \|c_i\bm{Ae}_i - \overline c_i \mathbf{Be}_{\overline \pi(i)} \|_2
+\end{align*}
+%
+for $\overline \varepsilon < L_2(\mathbf{A})\min_{i \in [m]}|c_i|$.
+But this is exactly the supposition in \eqref{1D}, with $J$ and $\overline \varepsilon$ in place of $[m]$ and $\varepsilon$, respectively.
+The same arguments of the case $k=1$ in Sec.~\ref{DUT} can then be made to show that for any $\overline m \times \overline m$ permutation and invertible diagonal matrices $\mathbf{P}$ and $\mathbf{D}$ with, respectively, columns $\mathbf{e}_{\pi(i)}$ and $\frac{\overline{c}_i}{c_i}\mathbf{e}_i$ for $i \in J$ (otherwise, $\mathbf{e}_{i}$ for $i \in [\overline{m}] \setminus J$), we have $\|\mathbf{A}_i - (\mathbf{B}\mathbf{PD})_i \|_2 \leq \overline  \varepsilon / |c_i|  \leq C_2 \varepsilon$ for all $i \in J$.
+\end{proof}

### 2020-08-05 manuscripts/thesis/results.tex
new intro

@@
 \chapter{Results}\label{Results}
-
-\section{Introduction}
-
-TODO
 
@@
 
-\section{Combinatorial designs}
+\section{Definitions}
 
@@
 
-\section{Uniqueness Theorems}
+\section{Uniqueness theorems}
 
@@
 
-Let us conclude this chapter with some comments on the optimality of these results.
+It is befitting to conclude this chapter with some comments on the optimality of these results.
 The linear scaling for $\varepsilon$ in \eqref{epsdel} is essentially optimal (e.g., see \cite{arias2013fundamental}), but a basic open problem remains: how many samples are necessary to determine the sparse coding model?
@@
 Consequently, if $k$ is held fixed or if the size of the support set of reconstructing codes is polynomial in $\overline m$ and $k$, then a practical (polynomial) amount of data suffices to identify the dictionary.\footnote{In the latter case, a reexamination of the pigeonholing argument in the proof of Thm.~\ref{DeterministicUniquenessTheorem} requires a polynomial number of samples distributed over a polynomial number of supports.} Reasons to be skeptical that this holds in general, however, can be found in \cite{tillmann2014computational, tillmann2015computational}.
-Even so, in the next chapter it will be discussed how probabilistic guarantees can in fact be made for any number of available samples.
+Even so, the next chapter contains a discussion on how probabilistic guarantees can in fact be made for any number of available samples.
+
+As it seemed to benefit a reviewer of this work, some clarification may be in order on how the deterministic sample complexity $N = |\mathcal{H}\left[|(k-1){m \choose k} + 1\right]$ given here compares to those listed in the the top two rows listed in Table I of \cite{Hillar15}.
+To be clear, the theory developed here (Cor.~\ref{DeterministicUniquenessCorollary}) is strictly more general, since $\mathcal{H}$ can always be taken to be ${[m] \choose k}$.
+The point of difference in this comparison is the assumed set of supports for sparse codes, which is always ${[m] \choose k}$ in \cite{Hillar15}, whereas here it can be assumed to be any regular $k$-uniform hypergraph that satisfies the SIP.
+By row, %, assuming for our results that sufficient data have been sampled from all supports in a hypergraph H satisfying the SIP:
+\begin{enumerate}
+\item[I.] The result here improves upon the listed $k{m \choose k}^2$ by an exponential factor, since for every $k < m$ there exists a regular $k$-uniform hypergraph $\mathcal{H}$ with $|\mathcal{H}| = m$ satisfying the SIP.
+\item[II.] The authors in \cite{Hillar15} have applied measure-theoretic arguments to achieve $(k+1){m \choose k}$ with almost-certainty (i.e.
+with probability one), a factor of $m$ reduction over that for which certainty can alternatively be guaranteed here.
+%\item[III.] A direct comparison cannot be made because it is an open question as to the probability that a random set of supports satisfies the SIP.
+This would be an interesting problem for the community to solve; regardless, the result of \cite{Hillar15} is still implied by the more general theory given here.
+%\item[IV.] The result here is $|\mathcal{H}\left[|(k-1){m \choose k} + 1\right]$ with probability one compared to $(k+1){m \choose k}$ with probability one.
+In this case the sample complexity stated in \cite{Hillar15} is marginally better, but it relies on a noise-free technicality unique to their assumption $\mathcal{H} = {m \choose k}$.
+%differs in flavor: their $\mathbf{x_i}$ are assumed to be distributed as $(k+1)$ samples per support for every support of size $k \in [m]$, whereas here it is assumed that $(k-1){m \choose k}$ codes $\mathbf{x_i}$ are distributed over each support in some hypergraph $\mathcal{H}$ satisfying the SIP.
+%\item[V.] Again, a direct comparison cannot be made for the reason stated for row III.
+\end{enumerate}

### 2020-08-05 manuscripts/thesis/introduction.tex
new intro

@@
 
-It is a longstanding practice in the field of signal processing to describe signals as linear combinations of elementary waveforms from a pre-specified ``dictionary".
+It is a longstanding practice in the field of signal processing to describe signals as linear combinations of elementary waveforms selected from a pre-specified ``dictionary".
 When this dictionary forms a basis for the signal space, every signal has a unique decomposition into these atomic components.
-In the simplest such case, the basis is orthonormal and the representational coefficient scaling a given elementary waveform is merely the inner product of that waveform with the signal.
+In the most basic such case, the basis is orthonormal and the representational coefficient scaling a given elementary waveform is simply the inner product of that waveform with the signal.
 %When non-orthogonal, the coefficients are computed by taking the inner product with respect to the components of the dictionary inverse.
@@
 
-The need for greater freedom of expression eventually led to the development of redundant signal representations utilizing overcomplete dictionaries containing more atoms than there are dimensions of the signal.
-In this case, there are infinitely many ways in which a signal may be decomposed into its constituent components, and the intention is to seek the most informative such representation as measured by some task-specific cost function.
+The need for such freedom of expression eventually led to the development of redundant signal representations utilizing overcomplete dictionaries, which contain more atoms than there are dimensions of the signal.
+In such cases, there are infinitely many ways in which a signal may be decomposed into a superposition of the waveforms constituting the dictionary, and the intention is rather to seek the most informative such representation as measured by some task-specific cost function.
 
@@
 
-Early approaches to sparse representation modeling assumed a model of the signal class from which a suitable sparsifying dictionary could then be derived, as we have in our recurring example.
+Early approaches to sparse representation modeling assumed a model of the signal class from which a suitable sparsifying dictionary could be derived, as we have in our recurring example.
 While such dictionaries are typically characterized by an analytic formulation and a fast implicit implementation, they unfortunately tend to be over-simplistic models when applied to natural phenomena.
@@
 This remarkable discovery showed that the assumption of sparsity alone could potentially account for a fundamental property of the visual system, and demonstrated the potential of the machine learning approach to dictionary design.
-Even more curiously, these waveforms (e.g., Gabor-like wavelets) have since tended to appear in dictionaries learned by a variety of machine learning algorithms trained over different natural image datasets, suggesting that the optimal dictionaries for these signals may, in some sense, be canonical \cite{donoho2001can}.
+Even more curiously, these waveforms (e.g., Gabor-like wavelets) tend to appear in dictionaries learned by a variety of machine learning algorithms trained over different natural image datasets, suggesting that the optimal dictionaries for these signals may, in some sense, be canonical \cite{donoho2001can}.
 
@@
 %and more recent work relating compressed sensing \cite{eldar2012compressed} to a theory of information transmission through random wiring bottlenecks in the brain \cite{Isely10}, 
-It is natural to wonder, in light of these discoveries, when a dictionary admitting optimally sparse representations of a signal class is indeed identifiable from a representative sample.
+In light of these discoveries, it is natural to wonder when a dictionary admitting optimally sparse representations of a signal class is indeed identifiable from a representative sample.
 Answers to this question have implications in practice whenever an appeal is made to latent sparse structure of data (e.g., forgery detection \cite{hughes2010, olshausen2010applied}; brain recordings \cite{jung2001imaging, agarwal2014spatially, lee2016sparse}; and gene expression \cite{wu2016stability}).
@@
 
-Let us proceed to rigorously define the two formulations of the dictionary learning problem with which this thesis is concerned.
+Let us proceed to rigorously define the two formulations of the dictionary learning problem with which this work concerns itself.
 Fix a matrix $\mathbf{A} \in \mathbb R^{n \times m}$ with the elementary waveforms of the dictionary as its columns  $\mathbf{A}_j$ ($j = 1,\ldots,m$) and let dataset $Z$ consist of measurements:
@@
 Formal statements of the main findings described above are given in Chap.~\ref{Results}, along with their adaptation to dictionaries and codes drawn from arbitrary (continuous) probability distributions (Cor.~\ref{ProbabilisticCor}).
-For clarity of exposition, the technical proofs of Thms.~\ref{DeterministicUniquenessTheorem} and ~\ref{SLCopt} are deferred to Chap.~\ref{DUT}, following some necessary definitions and the statement of a key lemma in combinatorial matrix analysis (Lem.~\ref{MainLemma}; proven in the Appendix).
+All results assume real matrices and vectors.
+For clarity of exposition, the technical proofs of Thms.~\ref{DeterministicUniquenessTheorem} and ~\ref{SLCopt} are deferred to Chap.~\ref{DUT}, following some necessary definitions and the statement of a key lemma in combinatorial matrix analysis (Lem.~\ref{MainLemma}, the proof of which is relegated to the chapter's Appendix).
 These results and their applications are discussed in Chap.~\ref{Discussion}, which concludes with some open questions and directions for future research seeded in part by the results of more practically-minded simulations.

### 2020-08-05 manuscripts/thesis/proofs.tex
new intro

@@
 % WITHOUT J SUBSCRIPT
+We shall prove Thm.~\ref{DeterministicUniquenessTheorem} and then prove Thm.~\ref{SLCopt} by arguing that Prob.~\ref{OptimizationProblem} reduces to an instance of Prob.~\ref{InverseProblem} given sufficient data.
 
@@
 
-The required stability result in combinatorial matrix analysis is the following. For expository purposes, the proof of this fact is relegated to the Appendix.
+The required stability result in combinatorial matrix analysis is the following. For expository purposes, the proof of this fact is relegated to Sec.~\ref{proofs}.
 
@@
 The constant $C_2$ (a function of $\mathbf{A}$ and $\mathcal{H}$) will be presented relative to a quantity used in \cite{Deutsch12} to analyze the convergence of the ``alternating projections" algorithm for projecting a point onto the intersection of subspaces.
-This quantity is incorporated into the following definition, which we shall refer to in the proof of Lem.~\ref{DistanceToIntersectionLemma} in the Appendix; specifically, it will be used to bound the distance between a point and the intersection of subspaces given an upper bound on its distance from each subspace.
+This quantity is incorporated into the following definition, which we shall refer to in the proof of Lem.~\ref{DistanceToIntersectionLemma} in the Sec.~\ref{proofs}; specifically, it will be used to bound the distance between a point and the intersection of subspaces given an upper bound on its distance from each subspace.
 
@@
 The main challenge was to generalize Lem.~\ref{MainLemma} to the case where the $k$-dimensional subspaces spanned by corresponding submatrices $\mathbf{A}_S$ and $\mathbf{B}_{\pi(S)}$ are assumed to be``close" but not identical.
-Referring now to the proof in the Appendix, the situation is unlike that in \cite{Hillar15}, where an inductive argument could be applied to the noiseless case.
+Referring now to the proof in this chapter's Appendix, the situation is unlike that in \cite{Hillar15}, where an inductive argument could be applied to the noiseless case.
 Rather, here it has to be explicitly demonstrated that this proximity relation is propagated through iterated intersections right down to the spans of the dictionary elements themselves.

### 2020-08-05 manuscripts/thesis/results.tex
new intro

@@
 
-A precise statement of the results requires first the identification of some combinatorial criteria on the supports\footnote{Recall that a vector $\mathbf{x}$ is said to be \emph{supported} in $S$ when $\mathbf{x} \in \text{\rmfamily span}\{\mathbf{e}_j: j\in S\}$, with $\mathbf{e}_j$ forming the standard column basis.} of sparse vectors.
+To state precisely the results of this work, we will require first the identification of some combinatorial criteria on the supports\footnote{Recall that a vector $\mathbf{x}$ is said to be \emph{supported} in $S$ when $\mathbf{x} \in \text{\rmfamily span}\{\mathbf{e}_j: j\in S\}$, with $\mathbf{e}_j$ forming the standard column basis.} of sparse vectors.
 Let $\{1, \ldots, m\}$ be denoted $[m]$, its power set $2^{[m]}$, and ${[m] \choose k}$ the set of subsets of $[m]$ of size $k$.
@@
 
-Next, a quantitative generalization of the spark condition (\ref{SparkCondition}) to combinatorial subsets of supports is given.
+Next, we will require a quantitative generalization of the spark condition (\ref{SparkCondition}) to combinatorial subsets of supports.
 The \emph{lower bound} of an $n \times m$ matrix $\mathbf{M}$ is the largest $\alpha$ with \mbox{$\|\mathbf{M}\mathbf{x}\|_2 \geq \alpha\|\mathbf{x}\|_2$} for all $\mathbf{x} \in \mathbb{R}^m$ \cite{Grcar10}.
@@
 
-We are now in a position to state the main result, though for expository purposes the quantity $C_1$ will be left%(a function of $\mathbf{A}$, $\mathbf{x}_1, \ldots, \mathbf{x}_N$, and $\mathcal{H}$) 
-undefined until Chap.~\ref{DUT}.
- All results  below assume real matrices and vectors.
+The following is the statement of the main result.
+For expository purposes the quantity $C_1$ (a function of $\mathbf{A}$, $\mathbf{x}_1, \ldots, \mathbf{x}_N$, and $\mathcal{H}$) will be left undefined until Chap.~\ref{DUT}.
 
@@
 
-It is befitting to conclude this chapter with some comments on the optimality of these results.
+It is befitting to comment on the optimality of these results.
 The linear scaling for $\varepsilon$ in \eqref{epsdel} is essentially optimal (e.g., see \cite{arias2013fundamental}), but a basic open problem remains: how many samples are necessary to determine the sparse coding model?
@@
 
-As it seemed to benefit a reviewer of this work, some clarification may be in order on how the deterministic sample complexity $N = |\mathcal{H}\left[|(k-1){m \choose k} + 1\right]$ given here compares to those listed in the the top two rows listed in Table I of \cite{Hillar15}.
-To be clear, the theory developed here (Cor.~\ref{DeterministicUniquenessCorollary}) is strictly more general, since $\mathcal{H}$ can always be taken to be ${[m] \choose k}$.
+As it seemed to benefit a reviewer of this work, some clarification may be in order on how the deterministic sample complexity $N = |\mathcal{H}\left[|(k-1){m \choose k} + 1\right]$ given here (Cor.~\ref{DeterministicUniquenessCorollary}) compares to those listed in the the top two rows listed in Table I of \cite{Hillar15}.
+To be clear, the theory developed here is strictly more general, since $\mathcal{H}$ can always be taken to be ${[m] \choose k}$.
 The point of difference in this comparison is the assumed set of supports for sparse codes, which is always ${[m] \choose k}$ in \cite{Hillar15}, whereas here it can be assumed to be any regular $k$-uniform hypergraph that satisfies the SIP.

### 2020-08-06 manuscripts/thesis/abstract.tex
chapters
new intro

@@
 \begin{abstract}
-Learning optimal dictionaries for sparse coding has exposed characteristic sparse features of many natural signals.
+Learning optimal dictionaries for sparse representation modeling has led to the discovery of characteristic features in many natural signals. 
 However, universal guarantees of the uniqueness and stability of such features in the presence of noise are lacking. 
@@
 The stability constants are explicit and computable; as such, there is an effective procedure sufficient to affirm if a proposed solution to the dictionary learning problem is unique within bounds commensurate with the noise.
-Beyond the extension of existing results to the noisy regime, a theory of combinatorial designs for sparse supports is introduced to demonstrate that some or all generating dictionary elements are recoverable from noisy data even if the dictionary fails to satisfy the spark condition, its size is overestimated, or only a polynomial number of distinct supports appear in the encoded data.
-Importantly, the guarantees derived here assume no constraints on the recovered dictionary beyond a natural upper bound on its size.
-The work closes with a lengthy discussion of the results and some remaining open challenges seeding future research directions.
+
+The first formulation of the dictionary learning problem to be considered concerns itself with the maximal support size over a dataset.
+Beyond the original extension of existing guarantees to the noisy regime, a theory of combinatorial designs for sparse supports is introduced to demonstrate that some or all dictionary elements are recoverable from noisy data even if the dictionary fails to satisfy the spark condition, its size is overestimated, or only a polynomial number of distinct supports appear in the encoded data.
+
+The second formulation of the dictionary learning problem to be considered concerns itself with the average support size over a dataset.
+Guarantees are extended to this problem, becoming the first of their kind in both the noise-free and noisy domains, by showing that this problem in fact an instance of the first problem, given sufficient data.
+Importantly, in all cases the guarantees apply without imposing any assumptions at all on learned dictionaries beyond a natural upper bound on their size.
+
+This work serves to justify, in principle, the application of dictionary learning to discover latent sparse structure in data, though much work remains to be done deriving criteria that can be used in practice.
+%The work closes with some open questions and directions for future research, seeded in part by the results of more practically-minded simulations. 
 \end{abstract}

### 2020-08-06 manuscripts/thesis/discussion.tex
new intro

@@
 I briefly expand on some of these directions below.
-It is my hope that these remaining challenges pique the interest of the community, and that practical guidelines can be established using the theoretical tools showcased here to support researchers applying sparse coding techniques.
+It is my hope that these remaining challenges pique the interest of the community, and that practical guidelines can be established using the theoretical tools showcased here to support researchers applying sparse coding techniques in their data analysis pipelines.
 

### 2020-08-06 manuscripts/thesis/introduction.tex
new intro

@@
 It is a longstanding practice in the field of signal processing to describe signals as linear combinations of elementary waveforms selected from a pre-specified ``dictionary".
-When this dictionary forms a basis for the signal space, every signal has a unique decomposition into these atomic components.
-In the most basic such case, the basis is orthonormal and the representational coefficient scaling a given elementary waveform is simply the inner product of that waveform with the signal.
+Every signal has a unique representation in terms of these atomic components when the dictionary forms what is called a basis.
+For example, a signal can be decomposed into its constituent frequencies via the Fourier transform, a linear change of basis.
+%When the basis is orthonormal, the representational coefficient scaling a given elementary waveform is simply the inner product of that waveform with the signal.
+Equally simple decomposition rules apply when the basis is non-orthogonal.
 %When non-orthogonal, the coefficients are computed by taking the inner product with respect to the components of the dictionary inverse.
+Bases have been the dominant form of signal representation until recently, due largely to their simplicity.
 
-Until recently, bases have been the default form of signal representation due largely to their simplicity.
-For many signal analysis tasks, however, there is no one basis expressive enough to reveal clearly all of the relevant features of the signal.
-For example, a signal can be decomposed into its constituent frequencies via the Fourier transform, a linear change of basis.
-If our signal can be either a sine wave or a delta function, neither the standard basis nor the Fourier basis can capture one case as effectively as it can the other.
+For many signal analysis tasks, however, no one basis can convey clearly all of the relevant information in the signal.
+For instance, if a signal can be either a sine wave or a delta function, then neither the standard basis nor the Fourier basis will indicate one case as explicitly as it does the other.
+The need for such freedom of expression led to the development of redundant signal representations utilizing overcomplete dictionaries, which consist of more atoms than there are dimensions of the signal.
+An overcomplete dictionary admits infinitely many possible ways to decompose a signal into a linear superposition its constituent atoms, and the intention is to seek the optimal such representation as measured by some task-specific cost function.
 
-The need for such freedom of expression eventually led to the development of redundant signal representations utilizing overcomplete dictionaries, which contain more atoms than there are dimensions of the signal.
-In such cases, there are infinitely many ways in which a signal may be decomposed into a superposition of the waveforms constituting the dictionary, and the intention is rather to seek the most informative such representation as measured by some task-specific cost function.
+A popular approach to the design of overcomplete dictionaries has been to seek one which admits a sparse representation for every signal of interest; that is, each signal can be represented, or at least well-approximated, as a combination of only a few dictionary elements from the bunch.
+Continuing with our example, the union of the standard basis with the Fourier basis is an overcomplete dictionary with respect to which both sine waves and delta functions (or any finite superpositions thereof) achieve the sparsest possible representation.
 
-A popular approach to the design of overcomplete dictionaries has been to seek one with respect to which every signal in the signal class of interest admits a sparse representation; that is, it can be represented, or at least well-approximated, as a combination of only a few dictionary elements from the bunch.
-Finishing with our example, the union of the standard basis with the Fourier basis is an over-complete dictionary with respect to which both sines and delta functions (or any finite superpositions thereof) achieve the sparsest possible representation.
-
-Early approaches to sparse representation modeling assumed a model of the signal class from which a suitable sparsifying dictionary could be derived, as we have in our recurring example.
-While such dictionaries are typically characterized by an analytic formulation and a fast implicit implementation, they unfortunately tend to be over-simplistic models when applied to natural phenomena.
+Early approaches to sparse representation modeling assumed a model of the signal class from which a suitable sparsifying dictionary could be derived, as we have in our trivial example.
+Such dictionaries are typically characterized by an analytic formulation and a fast implicit implementation; yet they tend to be over-simplistic models when applied to natural phenomena.
 
 An alternative modern approach to dictionary design is conditioned on the assumption that the sparse structure of signals conveying information about complex natural phenomena can be more accurately extracted directly from a training dataset, a process referred to as dictionary learning  (see \cite{Zhang15} for a comprehensive review).
-In the seminal work \cite{Olshausen96}, a dictionary trained over a collection of small patches extracted from images of the natural environment was shown to share qualitative similarities with linear filters estimated from the response properties of simple-cell neurons in mammalian visual cortex, which until then had been more weakly described analytically as Gabor filters (see also \cite{hurri1996image, bell1997independent, van1998independent}).
-This remarkable discovery showed that the assumption of sparsity alone could potentially account for a fundamental property of the visual system, and demonstrated the potential of the machine learning approach to dictionary design.
-Even more curiously, these waveforms (e.g., Gabor-like wavelets) tend to appear in dictionaries learned by a variety of machine learning algorithms trained over different natural image datasets, suggesting that the optimal dictionaries for these signals may, in some sense, be canonical \cite{donoho2001can}.
+In the seminal work \cite{Olshausen96} (see also \cite{hurri1996image, bell1997independent, van1998independent}), a dictionary trained over a collection of small patches extracted from images of the natural environment was shown to share qualitative similarities with linear filters estimated from the response properties of simple-cell neurons in mammalian visual cortex, which until then had been more weakly described analytically as Gabor filters.
+This remarkable discovery demonstrated that the assumption of sparsity alone could potentially account for a fundamental property of the visual system, and showcased the potential of the machine-learning approach to dictionary design.
+Even more curiously, these waveforms (e.g., Gabor-like wavelets) tend to appear in dictionaries optimized with respect to different natural image datasets by a variety of dictionary learning algorithms, suggesting that the optimal dictionaries for sparse representation of these signals may, in some sense, be canonical \cite{donoho2001can}.
 
@@
 %and more recent work relating compressed sensing \cite{eldar2012compressed} to a theory of information transmission through random wiring bottlenecks in the brain \cite{Isely10}, 
-In light of these discoveries, it is natural to wonder when a dictionary admitting optimally sparse representations of a signal class is indeed identifiable from a representative sample.
-Answers to this question have implications in practice whenever an appeal is made to latent sparse structure of data (e.g., forgery detection \cite{hughes2010, olshausen2010applied}; brain recordings \cite{jung2001imaging, agarwal2014spatially, lee2016sparse}; and gene expression \cite{wu2016stability}).
-Even though several algorithms have recently been proposed to provably recover a unique dictionary under specific conditions (see \cite[Sec.~I-E]{Sun16} for a summary of the state of the art), few theorems can be invoked to justify the consistency of inference under this model of data more broadly.
-Surprisingly, despite the now ubiquitous application of dictionary learning methods in practice, a universal guarantee of the uniqueness and stability of learned dictionaries and the sparse representations they induce over noisy data (noise being inevitable in practice) has yet, to the best of my knowledge, to appear in the literature.
+In light of these observations, it is natural to wonder to what extent the optimal dictionary can be identified given a representative sample from a signal class.
+Answers to this question have implications in practice; wherever an appeal is made to latent sparse structure of data (e.g., forgery detection \cite{hughes2010, olshausen2010applied}; brain recordings \cite{jung2001imaging, agarwal2014spatially, lee2016sparse}; and gene expression \cite{wu2016stability}), it is assumed this structure captures some identifiable physical or causal variable.
+
+Even though several dictionary learning algorithms have recently been proposed to provably recover a unique dictionary under specific conditions (see \cite[Sec.~I-E]{Sun16} for a summary of the state of the art), few theorems can be invoked to justify inference with respect to this model of data more broadly.
+Despite the now ubiquitous application of dictionary learning methods in practice, to the best of my knowledge a universal guarantee of the uniqueness and stability of learned dictionaries and the sparse representations they induce over real, uncertain data has yet to appear in the literature.
 
@@
 In this work, it is proven very generally that uniqueness and stability is a typical property of learned dictionaries. 
-Specifically, if each of $N$ observed $n$-dimensional signal samples is viewed as a (noisy) linear combination of at most $k$ elementary waveforms drawn from a suitable dictionary of size $m \ll N$, then the dictionary is identifiable from \mbox{$N = m(k-1){m \choose k} + m$} noisy linear combinations of $k$ of its columns up to an error that is linear in the noise (Thm.~\ref{DeterministicUniquenessTheorem}).
+Specifically, if each of $N$ observed $n$-dimensional real signals is truly a (noisy) linear combination of at most $k$ elementary waveforms drawn from a suitable dictionary of size $m \ll N$, that dictionary is uniquely specified up to an error that is linear in the noise given \mbox{$N = m(k-1){m \choose k} + m$} such signals (Thm.~\ref{DeterministicUniquenessTheorem} and Cor.~\ref{DeterministicUniquenessCorollary}).
 In fact, provided $n \geq \min(2k,m)$, in almost all cases the problem is well-posed, as per Hadamard \cite{Hadamard1902}, given a sufficient amount of data (Thm.~\ref{robustPolythm} and Cor.~\ref{ProbabilisticCor}).
@@
 \cite{rehnsommer2007}) optimization problem seeking a dictionary minimizing the average number of elementary waveforms required to reconstruct each sample of the dataset (Thm.~\ref{SLCopt}).
-To great practical benefit (and technical pain!), these guarantees apply without imposing any assumptions at all on learned dictionaries beyond an upper bound on their size, which is necessary in any case to avoid trivial solutions (e.g., allowing $m = N$).
+To great practical benefit (and technical pain!), these guarantees apply without any assumptions at all on learned dictionaries beyond an upper bound on their size, which is necessary in any case to avoid trivial solutions (e.g., allowing $m = N$).
 %That is, every pair of solutions of comparable size has some number of dictionary elements in common (up to noise), and similarly so for the coefficients of sparse codes they induce.
@@
 
-Formal statements of the main findings described above are given in Chap.~\ref{Results}, along with their adaptation to dictionaries and codes drawn from arbitrary (continuous) probability distributions (Cor.~\ref{ProbabilisticCor}).
+Formal statements of the main findings described above are given in Chap.~\ref{Results}, along with their adaptation to dictionaries and codes drawn from arbitrary (continuous) probability distributions (Thm.~\ref{robustPolythm} and Cor.~\ref{ProbabilisticCor}).
 All results assume real matrices and vectors.
-For clarity of exposition, the technical proofs of Thms.~\ref{DeterministicUniquenessTheorem} and ~\ref{SLCopt} are deferred to Chap.~\ref{DUT}, following some necessary definitions and the statement of a key lemma in combinatorial matrix analysis (Lem.~\ref{MainLemma}, the proof of which is relegated to the chapter's Appendix).
-These results and their applications are discussed in Chap.~\ref{Discussion}, which concludes with some open questions and directions for future research seeded in part by the results of more practically-minded simulations.
+For clarity of exposition, the technical proofs of Thms.~\ref{DeterministicUniquenessTheorem} and ~\ref{SLCopt} are deferred to Chap.~\ref{DUT}, following some necessary definitions and the statement of a key lemma in combinatorial matrix analysis (Lem.~\ref{MainLemma}, proven in the chapter's Appendix).
+These results and their applications are discussed in Chap.~\ref{Discussion}, which concludes with some open questions and directions for future research seeded in part by practically-minded simulations.
 %The Appendix contains a proof of Lem.~\ref{MainLemma}.

### 2020-08-06 manuscripts/thesis/introduction.tex
new intro

@@
 The need for such freedom of expression led to the development of redundant signal representations utilizing overcomplete dictionaries, which consist of more atoms than there are dimensions of the signal.
-An overcomplete dictionary admits infinitely many possible ways to decompose a signal into a linear superposition its constituent atoms, and the intention is to seek the optimal such representation as measured by some task-specific cost function.
+An overcomplete dictionary admits infinitely many possible ways to decompose a signal into a linear superposition its constituent atoms.
+The intention is then to seek the best such representation, be it by some analytic criteria, or as measured by some task-specific cost function.
 

### 2020-08-07 manuscripts/thesis/discussion.tex
l1

@@
 
-\subsection{Dictionary learning via $\ell_1$-norm minimization}
+\subsection{Dictionary learning via convex optimization}
 
-A commonly applied workaround to the intractability of Prob.~\ref{SLCopt} (see \cite{tillmann2015computational}) is to swap out the $\ell_0$-norm in \eqref{minsum} for $\ell_1$-norm, thereby transforming the inference of sparse $\mathbf{\overline x}_i$ for a fixed $\mathbf{B}$ into a convex optimization solvable by a linear program.
-A major advance in compressive sensing was the discovery that \eqref{minsum} can in fact be solved in this way for fixed $\mathbf{B}$ provided $L_{2k}(\mathbf{B})$ is large enough \cite{eldar2012compressed}.
+A commonly applied workaround to the intractability of Prob.~\ref{SLCopt} (see \cite{tillmann2015computational}) is to relax the sparsity measuring norm $\|\mathbf{x}\|_0$ to be $\|\mathbf{x}\|_1$, thereby transforming the inference of sparse $\mathbf{\overline x}_i$ for a fixed $\mathbf{B}$ into a convex optimization solvable by a linear program.
+Recalling the definition of $\mathbf{z}_i$ in \eqref{LinearModel}, the approach is rather:
 
-The current work provides conditions on the generating dictionary $\mathbf{A}$ and $k$-sparse codes $\mathbf{x}_i$ under which \emph{all} matrices $\mathbf{B}$ (of bounded column-norm) that solve Prob.~\ref{OptimizationProblem} have $L_{2k}(\mathbf{B})$ bounded from below; specifically, $L_{2k}(\mathbf{B}) \geq \left(L_{2k}(\mathbf{A}) - C_1\varepsilon \right) / \|\mathbf{D}\|_1$ in the case where $\mathbf{A}$ satisfies \eqref{SparkCondition}.
+\begin{problem}\label{ConvexifiedOptimizationProblem}
+Find a matrix $\mathbf{B}$ and vectors \mbox{$\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N$} solving:
+\begin{equation}\label{l1minsum}
+\min \sum_{i = 1}^N \|\mathbf{\overline x}_{i}\|_1 \ \
+\text{subject to} \ \ \|\mathbf{z}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \eta, \ \text{for all $i$}.
+\end{equation}
+\end{problem}
+
+A major advance in compressive sensing was the discovery that, when $\mathbf{B}$ is held fixed, solutions to \eqref{l1minsum} are in fact solutions to \eqref{minsum} provided $L_{2k}(\mathbf{B})$ is large enough \cite{eldar2012compressed}.
+Interestingly, the current work provides conditions on the generating dictionary $\mathbf{A}$ and $k$-sparse codes $\mathbf{x}_i$ under which \emph{all} matrices $\mathbf{B}$ (of bounded column-norm) that solve Prob.~\ref{OptimizationProblem} have $L_{2k}(\mathbf{B})$ bounded from below; specifically, $L_{2k}(\mathbf{B}) \geq \left(L_{2k}(\mathbf{A}) - C_1\varepsilon \right) / \|\mathbf{D}\|_1$ in the case where $\mathbf{A}$ satisfies \eqref{SparkCondition}.
 Thus, there is some noise bound inside of which all solutions to Prob.~\ref{OptimizationProblem} are solutions to the convexified problem as well.
-It is an open question as to whether there exist practical constraints that would exclude any remaining solutions to the convefixied problem that don't also solve Prob.~\ref{OptimizationProblem}.
+It is an open question as to whether practical constraints would exclude any remaining solutions to the convefixied problem that don't also solve Prob.~\ref{OptimizationProblem}.
+
+As an intuitive example to kickstart these efforts, consider the simple noiseless ($\eta = 0$) case for $k=1$ where the matrix $\mathbf{A}$ has linearly independent unit-norm columns and $\mathbf{x}_i = c\mathbf{e}_i$ for some $c \geq 1$ for all $i \in [m]$.
+Suppose that for some $\mathbf{B}$ also having linearly independent unit-norm columns there are vectors $\mathbf{\overline x}_i$ satisfying $\|\mathbf{\overline x}_i\|_1 \leq c$ and $\mathbf{B \overline x}_i = \mathbf{Ax}_i$ for all $i \in [m]$.
+Intuitively, the only vectors in the convex polygon $\{ \mathbf{B \overline x}: \|\mathbf{\overline x}\|_1 \leq c\}$ for which $\|\mathbf{B \overline x}_i\|_2 = \|\mathbf{Ax}_i\|_2 = \|c\mathbf{Ae}_i\|_2 = c$ are its corners $\mathbf{B}(\pm c\mathbf{e}_j)$ for $j \in [m]$, so the $\mathbf{\overline x}_i$ must also be 1-sparse and we can apply Thm.~\ref{DeterministicUniquenessTheorem}.
+
+%Alternatively, it may be the case that $L_{2k}(\mathbf{B}) > 0$ is a necessary constraint to impose to guarantee recovery of $\mathbf{A}$ by solving \eqref{l1minsum}.
 

### 2020-08-07 manuscripts/thesis/introduction.tex
l1

--- 2020-08-06 manuscripts/thesis/introduction.tex
@@
 It is a longstanding practice in the field of signal processing to describe signals as linear combinations of elementary waveforms selected from a pre-specified ``dictionary".
-Every signal has a unique representation in terms of these atomic components when the dictionary forms what is called a basis.
-For example, a signal can be decomposed into its constituent frequencies via the Fourier transform, a linear change of basis.
+Every signal has a unique representation in terms of these atomic components when the dictionary forms a basis.
+For example, a signal can be decomposed into its constituent frequencies via the Fourier transform, which performs a linear change of basis.
 %When the basis is orthonormal, the representational coefficient scaling a given elementary waveform is simply the inner product of that waveform with the signal.
@@
 %When non-orthogonal, the coefficients are computed by taking the inner product with respect to the components of the dictionary inverse.
-Bases have been the dominant form of signal representation until recently, due largely to their simplicity.
+Until recently, bases have been the dominant form of signal representation due largely to their simplicity.
 
-For many signal analysis tasks, however, no one basis can convey clearly all of the relevant information in the signal.
-For instance, if a signal can be either a sine wave or a delta function, then neither the standard basis nor the Fourier basis will indicate one case as explicitly as it does the other.
+For many signal analysis tasks, no one basis can convey clearly all of the relevant information in the signal.
+If a signal can be either a sine wave or a delta function, then neither the standard basis nor the Fourier basis will indicate one case as explicitly as it does the other.
 The need for such freedom of expression led to the development of redundant signal representations utilizing overcomplete dictionaries, which consist of more atoms than there are dimensions of the signal.
-An overcomplete dictionary admits infinitely many possible ways to decompose a signal into a linear superposition its constituent atoms, and the intention is to seek the optimal such representation as measured by some task-specific cost function.
+While an overcomplete dictionary admits infinitely many possible ways to decompose a signal into a linear superposition its constituent atoms, the intention is to seek the best such representation, be it by some analytic criteria, or as measured by some task-specific cost function.
 
 A popular approach to the design of overcomplete dictionaries has been to seek one which admits a sparse representation for every signal of interest; that is, each signal can be represented, or at least well-approximated, as a combination of only a few dictionary elements from the bunch.
-Continuing with our example, the union of the standard basis with the Fourier basis is an overcomplete dictionary with respect to which both sine waves and delta functions (or any finite superpositions thereof) achieve the sparsest possible representation.
+Continuing with our example, the union of the standard basis with the Fourier basis is an overcomplete dictionary with respect to which both sine waves and delta functions (or any finite superpositions thereof) achieve the sparsest possible representation as a scaling of a single elementary waveform from the dictionary.
 
 Early approaches to sparse representation modeling assumed a model of the signal class from which a suitable sparsifying dictionary could be derived, as we have in our trivial example.
-Such dictionaries are typically characterized by an analytic formulation and a fast implicit implementation; yet they tend to be over-simplistic models when applied to natural phenomena.
+Such dictionaries are characterized by an analytic formulation and a fast implicit implementation; yet they tend to be over-simplistic models when applied to natural phenomena.
 
@@
 %and more recent work relating compressed sensing \cite{eldar2012compressed} to a theory of information transmission through random wiring bottlenecks in the brain \cite{Isely10}, 
-In light of these observations, it is natural to wonder to what extent the optimal dictionary can be identified given a representative sample from a signal class.
-Answers to this question have implications in practice; wherever an appeal is made to latent sparse structure of data (e.g., forgery detection \cite{hughes2010, olshausen2010applied}; brain recordings \cite{jung2001imaging, agarwal2014spatially, lee2016sparse}; and gene expression \cite{wu2016stability}), it is assumed this structure captures some identifiable physical or causal variable.
+In light of these observations, it is natural to wonder when and to what extent the optimal dictionary for sparse representation modeling can be identified given a representative sample from a signal class.
+Answers to this question have implications in practice wherever an appeal is made to latent sparse structure of data (e.g., forgery detection \cite{hughes2010, olshausen2010applied}; brain recordings \cite{jung2001imaging, agarwal2014spatially, lee2016sparse}; and gene expression \cite{wu2016stability}), the assumption being that this structure captures some identifiable physical or logically causal variable.
 
@@
 In this work, it is proven very generally that uniqueness and stability is a typical property of learned dictionaries. 
-Specifically, if each of $N$ observed $n$-dimensional real signals is truly a (noisy) linear combination of at most $k$ elementary waveforms drawn from a suitable dictionary of size $m \ll N$, that dictionary is uniquely specified up to an error that is linear in the noise given \mbox{$N = m(k-1){m \choose k} + m$} such signals (Thm.~\ref{DeterministicUniquenessTheorem} and Cor.~\ref{DeterministicUniquenessCorollary}).
-In fact, provided $n \geq \min(2k,m)$, in almost all cases the problem is well-posed, as per Hadamard \cite{Hadamard1902}, given a sufficient amount of data (Thm.~\ref{robustPolythm} and Cor.~\ref{ProbabilisticCor}).
+Specifically, if each of $N$ observed $n$-dimensional real signals is truly a (noisy) linear combination of at most $k$ elementary waveforms drawn from a suitable dictionary of size $m \ll N$, that dictionary is uniquely specified by the data up to an error that is linear in the noise given \mbox{$N = m(k-1){m \choose k} + m$} such signals (Thm.~\ref{DeterministicUniquenessTheorem} and Cor.~\ref{DeterministicUniquenessCorollary}).
+In fact, provided $n \geq \min(2k,m)$, in almost all cases the problem is well-posed, as per Hadamard \cite{Hadamard1902}, given enough data (Thm.~\ref{robustPolythm} and Cor.~\ref{ProbabilisticCor}).
 Similar guarantees also hold for the related (and perhaps more commonly posed, e.g.
 \cite{rehnsommer2007}) optimization problem seeking a dictionary minimizing the average number of elementary waveforms required to reconstruct each sample of the dataset (Thm.~\ref{SLCopt}).
-To great practical benefit (and technical pain!), these guarantees apply without any assumptions at all on learned dictionaries beyond an upper bound on their size, which is necessary in any case to avoid trivial solutions (e.g., allowing $m = N$).
+To great practical benefit (and technical pain!), these guarantees apply without the imposition of any constraints at all on learned dictionaries beyond an upper bound on their size, which is necessary in any case to avoid trivial solutions (e.g., allowing $m = N$).
 %That is, every pair of solutions of comparable size has some number of dictionary elements in common (up to noise), and similarly so for the coefficients of sparse codes they induce.
@@
 \begin{problem}\label{OptimizationProblem}
-Find matrices $\mathbf{B}$ and vectors \mbox{$\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N$} solving:
+Find a matrix $\mathbf{B}$ and vectors \mbox{$\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N$} solving:
 \begin{align}\label{minsum}

### 2020-08-07 manuscripts/thesis/l1min.tex
l1

%% thesis.tex 2014/04/11
%
% Based on sample files of unknown authorship.
%
% The Current Maintainer of this work is Paul Vojta.
%
% To compile this file, run "latex thesis", then "biber thesis"
% (or "bibtex thesis", if the output from latex asks for that instead),
% and then "latex thesis" (without the quotes in each case).

\documentclass{ucbthesis}

% *** CITATION STUFF ***
%\usepackage{biblatex} 
%\bibliography{references} 
% the above doesn't work, using this instead:
\usepackage[backend=bibtex,style=numeric]{biblatex}
\addbibresource{references}

% *** MATH STUFF ***
\usepackage{amsmath, amssymb, amsthm} 
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{conjecture}{Conjecture}
\newtheorem{problem}{Problem}
\newtheorem{question}{Question}
\newtheorem{proposition}{Proposition}
\newtheorem{definition}{Definition}
\newtheorem{corollary}{Corollary}
\newtheorem{remark}{Remark}
\newtheorem{example}{Example}

% *** ALIGNMENT STUFF***
\usepackage{array}
\usepackage{bm}
\usepackage{rotating} % provides sidewaystable and sidewaysfigure
\usepackage{url}

% Double spacing, if you want it.  Do not use for the final copy.
% \def\dsp{\def\baselinestretch{2.0}\large\normalsize}
% \dsp

% If the Grad. Division insists that the first paragraph of a section
% be indented (like the others), then include this line:
% \usepackage{indentfirst}

\addtolength{\abovecaptionskip}{\baselineskip}

%\hyphenation{mar-gin-al-ia}
%\hyphenation{bra-va-do}

\begin{document}

We can already see this may be possible by examining the case $k=1$. Consider the dataset generated as in \eqref{LinearModel} in the noiseless case $\eta = 0$, i.e.:
\begin{align}\label{LinearModel}
\mathbf{z}_i = \mathbf{A}\mathbf{x}_i,\ \ \  \text{$i=1,\ldots,N$},
\end{align}
with the additional constraint that $\|\mathbf{Ae}_i\|_2 = 1$ for all $i \in [m]$ and  $\|\mathbf{A}\|_2 \leq 1$. Consider the following ``convexified" version of Prob.~\ref{OptimizationProblem}:

\begin{problem}\label{ConvexifiedOptimizationProblem}
Find a matrix $\mathbf{B}$ with $\|\mathbf{B}\|_2 \leq 1$ and vectors \mbox{$\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N$} solving:
\begin{equation}\label{l1min}
\min \sum_{i = 1}^N \|\mathbf{\overline x}_{i}\|_1 \ \
\text{subject to} \ \ \mathbf{z}_i = \mathbf{B}\mathbf{\overline x}_i, \ \text{for all $i$}.
\end{equation}
\end{problem}

%\begin{conjecture}
%Fix a matrix $\mathbf{A}$ with $\|\mathbf{A}\|_2=1$ and vectors $\mathbf{x}_i$ satisfying also the assumptions of Thm.~\ref{SLCopt}. Every solution to Prob.~\ref{ConvexifiedOptimizationProblem} satisfies BLAH and BLAH.
%\end{conjecture}

\begin{proposition}
%Suppose the $\mathbf{x}_i$ are 1-sparse. 
Fix $c > 1$. If $\mathbf{x}_i = c\mathbf{e}_i$ for $i = 1, \ldots, m$, then every solution to Prob.~\ref{ConvexifiedOptimizationProblem} satisfies $\mathbf{A} = \mathbf{BP}$ and $\mathbf{x}_i = \mathbf{P}^\top \mathbf{\overline x}_i$ for some $m \times m$ permutation matrix $\mathbf{P}$.
\end{proposition}

\begin{proof}
For all $i \in [m]$, since $\mathbf{B \overline x}_i = c\mathbf{Ae}_i$, we have:
\begin{equation}\label{dunnoyo}
c = c \|\mathbf{Ae}_i\|_2 = \|\mathbf{Bx}_i\|_2 \leq \|\mathbf{B}\|_2 \|\mathbf{\overline x}_i\|_2 \leq \|\mathbf{\overline x}_i\|_2 \leq \|\mathbf{\overline x}_i\|_1.
%c = c \|\mathbf{Ae}_i\|_1 = \|\mathbf{Bx}_i\|_1 \leq \|\mathbf{B}\|_1 \|\mathbf{\overline x}_i\|_1 \leq \|\mathbf{\overline x}_i\|_1.
\end{equation}
Since $\mathbf{A}$ and $c \mathbf{e}_i$ ($i = 1, \ldots, m$) solve \eqref{l1min}, we must have:
\begin{equation}
\sum_{i=1}^m \|\mathbf{\overline x}_i\|_1 \leq \sum_{i=1}^m \|c \mathbf{e}_i\|_1 = m c .
\end{equation}
thus by \eqref{dunnoyo} it must be the case that $\|\mathbf{\overline x}_i\|_2 = \|\mathbf{\overline x}_i\|_1 = c$.  Now, writing $\mathbf{\overline x}_i = \sum_{j=1}^m \overline c_j\mathbf{e}_j$, we have:
\begin{align}
\sum_{j=1}^m \overline c_j^2 =  \left( \sum_{j=1}^m  |\overline c_j| \right)^2 = \sum_{j=1}^m \overline c_j^2 + \sum_{j=1}^m |\overline c_j |\sum_{\ell \neq j} | \overline c_\ell |
\end{align}
We therefore have $\overline c_j \sum_{\ell \neq j} | \overline c_\ell | = 0$ for all $j \in [m]$. Since $\mathbf{\overline x}_i \neq 0$, we must have $\overline c_j \neq 0$ for at least some $j \in [m]$, in which case $c_\ell = 0$ for all $\ell \neq j$, and we can be sure $\mathbf{\overline x}_i$ is a $1$-sparse vector. Since this applies for all $i \in [m]$, we may appeal to Thm.~\ref{DeterministicUniquenessTheorem} (with $k=1$).
\end{proof}

\end{document}

### 2020-08-07 manuscripts/thesis/discussion.tex
l1

@@
 Indeed, theoretical validation makes little practical difference if the methodology is already in widespread use, while practical criteria establishing whether the data models obtained by practitioners are optimal or not would have very high impact.
-To this end, the work has been laid out for those wanting to derive statistical criteria for inference with respect to more domain-specific structured dictionaries and codes (i.e.
+To this end, the work has been laid out for those wanting to derive statistical criteria for inference with respect to more domain-specific parametric dictionaries and codes (i.e.
 estimate $C_1$), and reduced by half for those hoping to prove the consistency of any dictionary learning algorithm (i.e.

### 2020-08-10 manuscripts/thesis/discussion.tex
l1

@@
 Thus, there is some noise bound inside of which all solutions to Prob.~\ref{OptimizationProblem} are solutions to the convexified problem as well.
-It is an open question as to whether practical constraints would exclude any remaining solutions to the convefixied problem that don't also solve Prob.~\ref{OptimizationProblem}.
+It is an open question as to whether there exist solutions to the convefixied problem that don't also solve Prob.~\ref{OptimizationProblem}, and if so, what practical constraints may exclude them.
 
-As an intuitive example to kickstart these efforts, consider the simple noiseless ($\eta = 0$) case for $k=1$ where the matrix $\mathbf{A}$ has linearly independent unit-norm columns and $\mathbf{x}_i = c\mathbf{e}_i$ for some $c \geq 1$ for all $i \in [m]$.
-Suppose that for some $\mathbf{B}$ also having linearly independent unit-norm columns there are vectors $\mathbf{\overline x}_i$ satisfying $\|\mathbf{\overline x}_i\|_1 \leq c$ and $\mathbf{B \overline x}_i = \mathbf{Ax}_i$ for all $i \in [m]$.
-Intuitively, the only vectors in the convex polygon $\{ \mathbf{B \overline x}: \|\mathbf{\overline x}\|_1 \leq c\}$ for which $\|\mathbf{B \overline x}_i\|_2 = \|\mathbf{Ax}_i\|_2 = \|c\mathbf{Ae}_i\|_2 = c$ are its corners $\mathbf{B}(\pm c\mathbf{e}_j)$ for $j \in [m]$, so the $\mathbf{\overline x}_i$ must also be 1-sparse and we can apply Thm.~\ref{DeterministicUniquenessTheorem}.
+We can already see the guarantees derived in this work may readily extend themselves to Prob.~\ref{ConvexifiedOptimizationProblem} by examining the case $k=1$.
+Consider the dataset generated as in \eqref{LinearModel} in the noiseless case $\eta = 0$, i.e.:
+\begin{align}\label{LinearModel}
+\mathbf{z}_i = \mathbf{A}\mathbf{x}_i,\ \ \  \text{$i=1,\ldots,N$},
+\end{align}
+with the additional constraint that $\|\mathbf{Ae}_i\|_2 = 1$ for all $i \in [m]$. 
+%\begin{conjecture}
+%Fix a matrix $\mathbf{A}$ with $\|\mathbf{A}\|_2=1$ and vectors $\mathbf{x}_i$ satisfying also the assumptions of Thm.~\ref{SLCopt}.
+Every solution to Prob.~\ref{ConvexifiedOptimizationProblem} satisfies BLAH and BLAH.
+%\end{conjecture}
+
+\begin{proposition}
+Fix $c > 0$.
+If $\mathbf{x}_i = c\mathbf{e}_i$ for $i = 1, \ldots, m$, then every solution to Prob.~\ref{ConvexifiedOptimizationProblem} with $\|\mathbf{Be}_i\|_2 = 1$ for all $i \in [m]$ satisfies $\mathbf{A} = \mathbf{BP}$ and $\mathbf{x}_i = \mathbf{P}^\top \mathbf{\overline x}_i$ for some $m \times m$ permutation matrix $\mathbf{P}$.
+\end{proposition}
+
+\begin{proof}
+We will show that the $\mathbf{\overline x}_i$ are $1$-sparse and then apply Thm.~\ref{DeterministicUniquenessTheorem}.
+Fix $i \in [m]$.
+Writing $\mathbf{\overline x}_i = \sum_{j=1}^m \overline c^{(i)}_j \mathbf{e}_j$, we have:
+\begin{align}\label{gtc}
+c = \|c\mathbf{Ae}_i\|_2 = \|\mathbf{B \overline x}_i\|_2 = \|\sum_{j=1}^m \overline c^{(i)}_j \mathbf{Be}_j\|_2 \leq \sum_{j=1}^m |\overline c^{(i)}_j| \|\mathbf{Be}_j\|_2 = \|\mathbf{\overline x}_i\|_1
+\end{align}
+So $\|\mathbf{\overline x}_i\|_1 \geq c$ for all $i \in [m]$.
+Therefore $\sum_{i=1}^m \|\mathbf{\overline x}_i\|_1 \geq mc$.
+But since $\mathbf{B} = \mathbf{A}$ and $\mathbf{\overline x}_i = \mathbf{x}_i$ ($i = 1, \ldots, m$) satisfy the constraints of the minimization problem, we must have $\sum_{i=1}^m \|\mathbf{\overline x}_i\|_1 \leq \sum_{i=1}^m \|\mathbf{x}_i\|_1 = mc$ also.
+Thus $\sum_{i=1}^m \|\mathbf{\overline x}_i\|_1 = mc$.
+Since again $\|\mathbf{\overline x}_i\|_1 \geq c$ for all $i \in [m]$, we must have $\| \mathbf{\overline x}_i\|_1 = c$ for all $i \in [m]$.
+
+Recalling \eqref{gtc} we therefore have $c = \|\mathbf{B\overline x}_i\|_2 \leq \|\mathbf{\overline x}_i\|_1 = c$, with equality only when $\overline c^{(i)}_j \mathbf{Be}_j$ are colinear.
+This would be the case either if $\mathbf{\overline x}_i$ is $1$-sparse, in which case we may apply Thm.~\ref{DeterministicUniquenessTheorem} to guarantee both dictionary and code recovery, or $\mathbf{B}$ has colinear columns.
+In the latter case, the same guarantees hold for a suitable submatrix of $\mathbf{B}$ containing one representative column from every colinear set (note that since $\|\mathbf{Be}_j\| = 1$ for all $j \in [m]$, these columns are identical up to a sign).
+\end{proof}
+
+%\begin{conjecture}\label{l1conjecture}
+%Fix a matrix $\mathbf{A}$ with $\|\mathbf{Ae}_i\|_2 = 1$ for $i \in [m]$ and vectors $\mathbf{x}_i$ satisfying the assumptions of Thm.~\ref{SLCopt}.
+Every solution to Prob.~\ref{ConvexifiedOptimizationProblem} (with $\eta = \varepsilon/2$) and $\|\mathbf{Be}_i\|_2 = 1$.
+satisfies recovery guarantees \eqref{Cstable} and \eqref{b-PDa} when the corresponding bounds on $\eta$ are met.
+%\end{theorem}
 

### 2020-08-10 manuscripts/thesis/l1min.tex
l1

@@
 \end{align}
-with the additional constraint that $\|\mathbf{Ae}_i\|_2 = 1$ for all $i \in [m]$ and  $\|\mathbf{A}\|_2 \leq 1$. Consider the following ``convexified" version of Prob.~\ref{OptimizationProblem}:
+with the additional constraint that $\|\mathbf{Ae}_i\|_2 = 1$ for all $i \in [m]$. Consider the following ``convexified" version of 
+%Prob.~\ref{OptimizationProblem}:
+Prob. 2:
 
 \begin{problem}\label{ConvexifiedOptimizationProblem}
-Find a matrix $\mathbf{B}$ with $\|\mathbf{B}\|_2 \leq 1$ and vectors \mbox{$\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N$} solving:
+Find a $n \times m$ matrix $\mathbf{B}$ with $\|\mathbf{Be}_i\|_2 = 1$ for all $i \in [m]$ and vectors \mbox{$\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N$} solving:
 \begin{equation}\label{l1min}
@@
 \begin{proposition}
-%Suppose the $\mathbf{x}_i$ are 1-sparse. 
-Fix $c > 1$.
+Fix $c > 0$.
 If $\mathbf{x}_i = c\mathbf{e}_i$ for $i = 1, \ldots, m$, then every solution to Prob.~\ref{ConvexifiedOptimizationProblem} satisfies $\mathbf{A} = \mathbf{BP}$ and $\mathbf{x}_i = \mathbf{P}^\top \mathbf{\overline x}_i$ for some $m \times m$ permutation matrix $\mathbf{P}$.
@@
 \begin{proof}
-For all $i \in [m]$, since $\mathbf{B \overline x}_i = c\mathbf{Ae}_i$, we have:
-\begin{equation}\label{dunnoyo}
-c = c \|\mathbf{Ae}_i\|_2 = \|\mathbf{Bx}_i\|_2 \leq \|\mathbf{B}\|_2 \|\mathbf{\overline x}_i\|_2 \leq \|\mathbf{\overline x}_i\|_2 \leq \|\mathbf{\overline x}_i\|_1.
-%c = c \|\mathbf{Ae}_i\|_1 = \|\mathbf{Bx}_i\|_1 \leq \|\mathbf{B}\|_1 \|\mathbf{\overline x}_i\|_1 \leq \|\mathbf{\overline x}_i\|_1.
-\end{equation}
-Since $\mathbf{A}$ and $c \mathbf{e}_i$ ($i = 1, \ldots, m$) solve \eqref{l1min}, we must have:
-\begin{equation}
-\sum_{i=1}^m \|\mathbf{\overline x}_i\|_1 \leq \sum_{i=1}^m \|c \mathbf{e}_i\|_1 = m c .
-\end{equation}
-thus by \eqref{dunnoyo} it must be the case that $\|\mathbf{\overline x}_i\|_2 = \|\mathbf{\overline x}_i\|_1 = c$.
-Now, writing $\mathbf{\overline x}_i = \sum_{j=1}^m \overline c_j\mathbf{e}_j$, we have:
-\begin{align}
-\sum_{j=1}^m \overline c_j^2 =  \left( \sum_{j=1}^m  |\overline c_j| \right)^2 = \sum_{j=1}^m \overline c_j^2 + \sum_{j=1}^m |\overline c_j |\sum_{\ell \neq j} | \overline c_\ell |
+Fix $i \in [m]$. Writing $\mathbf{\overline x}_i = \sum_{j=1}^m \overline c^{(i)}_j \mathbf{e}_j$, we have:
+\begin{align}\label{gtc}
+c = \|c\mathbf{Ae}_i\|_2 = \|\mathbf{B \overline x}_i\|_2 = \|\sum_{j=1}^m \overline c^{(i)}_j \mathbf{Be}_j\|_2 \leq \sum_{j=1}^m |\overline c^{(i)}_j| \|\mathbf{Be}_j\|_2 = \|\mathbf{\overline x}_i\|_1
 \end{align}
-We therefore have $\overline c_j \sum_{\ell \neq j} | \overline c_\ell | = 0$ for all $j \in [m]$.
+So $\|\mathbf{\overline x}_i\|_1 \geq c$ for all $i \in [m]$.
+Therefore $\sum_{i=1}^m \|\mathbf{\overline x}_i\|_1 \geq mc$.
+But since $\mathbf{B} = \mathbf{A}$ and $\mathbf{\overline x}_i = \mathbf{x}_i$ ($i = 1, \ldots, m$) satisfy the constraints of the minimization problem, we must have $\sum_{i=1}^m \|\mathbf{\overline x}_i\|_1 \leq \sum_{i=1}^m \|\mathbf{x}_i\|_1 = mc$ also.
+Thus $\sum_{i=1}^m \|\mathbf{\overline x}_i\|_1 = mc$.
+Since again $\|\mathbf{\overline x}_i\|_1 \geq c$ for all $i \in [m]$, we must have $\| \mathbf{\overline x}_i\|_1 = c$ for all $i \in [m]$.
+
+Recalling \eqref{gtc} we therefore have $c = \|\mathbf{B\overline x}_i\|_2 \leq \|\mathbf{\overline x}_i\|_1 = c$, with equality only when $\overline c^{(i)}_j \mathbf{Be}_j$ are colinear.
+This would be the case either if $\mathbf{\overline x}_i$ is $1$-sparse, in which case we may apply
+%Thm.~\ref{DeterministicUniquenessTheorem}
+Thm. 1
+to guarantee both dictionary and code recovery, or $\mathbf{B}$ has colinear columns.
+In the latter case, the same guarantees hold for a suitable submatrix of $\mathbf{B}$ containing one representative column from every colinear set (note that since $\|\mathbf{Be}_j\| = 1$ for all $j \in [m]$, these columns are identical up to a sign).
+\end{proof}
+
+%\begin{proof}
+%Now, writing $\mathbf{\overline x}_i = \sum_{j=1}^m \overline c_j\mathbf{e}_j$, we have:
+%\begin{align}
+%\sum_{j=1}^m \overline c_j^2 =  \left( \sum_{j=1}^m  |\overline c_j| \right)^2 = \sum_{j=1}^m \overline c_j^2 + \sum_{j=1}^m |\overline c_j |\sum_{\ell \neq j} | \overline c_\ell |
+%\end{align}
+%We therefore have $\overline c_j \sum_{\ell \neq j} | \overline c_\ell | = 0$ for all $j \in [m]$.
 Since $\mathbf{\overline x}_i \neq 0$, we must have $\overline c_j \neq 0$ for at least some $j \in [m]$, in which case $c_\ell = 0$ for all $\ell \neq j$, and we can be sure $\mathbf{\overline x}_i$ is a $1$-sparse vector.
 Since this applies for all $i \in [m]$, we may appeal to Thm.~\ref{DeterministicUniquenessTheorem} (with $k=1$).
-\end{proof}
+%\end{proof}
 

### 2020-08-13 manuscripts/thesis/abstract.tex
redid abstract

--- 2020-08-04 manuscripts/thesis/abstract.tex
@@
 \begin{abstract}
-Learning optimal dictionaries for sparse coding has exposed characteristic sparse features of many natural signals.
+Learning optimal dictionaries for sparse representation modeling has led to the discovery of characteristic sparse features in many natural signals. 
 However, universal guarantees of the uniqueness and stability of such features in the presence of noise are lacking. 
@@
 The stability constants are explicit and computable; as such, there is an effective procedure sufficient to affirm if a proposed solution to the dictionary learning problem is unique within bounds commensurate with the noise.
-Beyond the extension of existing results to the noisy regime, a theory of combinatorial designs for sparse supports is introduced to demonstrate that some or all generating dictionary elements are recoverable from noisy data even if the dictionary fails to satisfy the spark condition, its size is overestimated, or only a polynomial number of distinct supports appear in the encoded data.
-Importantly, the guarantees derived here assume no constraints on the recovered dictionary beyond a natural upper bound on its size.
-The work closes with a lengthy discussion of the results and some remaining open challenges seeding future research directions.
+
+Two formulations of the dictionary learning problem are considered.
+The first seeks a dictionary admitting a sparse representation of bounded support size for each point in a dataset.
+The second seeks a dictionary which minimizes the average induced support size over the dataset.
+In the first case, beyond the original extension of existing guarantees to the noisy regime, a theory of combinatorial designs for sparse supports is introduced to demonstrate that in almost all cases some or all dictionary elements are recoverable up to an error commensurate with the noise even if the dictionary fails to satisfy the spark condition, its size is overestimated, or data are distributed over only a polynomial number of subspaces spanned by the dictionary.
+These guarantees are then extended to the second case, becoming the first such guarantees in both in the noiseless and noisy regimes, by demonstrating that the second problem reduces to an instance of the first, given sufficient data.
+Importantly, in both cases the guarantees apply without imposing any assumptions at all on learned dictionaries beyond a natural upper bound on their size.
+
+This work serves to justify, in principle, the application of dictionary learning to discover latent sparse structure in data; though much work remains to be done deriving practical criteria for use in applications.
+%The work closes with some open questions and directions for future research, seeded in part by the results of more practically-minded simulations. 
 \end{abstract}

### 2020-08-13 manuscripts/thesis/discussion.tex
redid abstract

--- 2020-08-07 manuscripts/thesis/discussion.tex
@@
 
-A commonly applied workaround to the intractability of Prob.~\ref{SLCopt} (see \cite{tillmann2015computational}) is to relax the sparsity measuring norm $\|\mathbf{x}\|_0$ to be $\|\mathbf{x}\|_1$, thereby transforming the inference of sparse $\mathbf{\overline x}_i$ for a fixed $\mathbf{B}$ into a convex optimization solvable by a linear program.
-Recalling the definition of $\mathbf{z}_i$ in \eqref{LinearModel}, the approach is rather:
+A commonly applied workaround to the intractability (see \cite{tillmann2015computational}) of Prob.~\ref{SLCopt} is to replace the norm $\|\mathbf{x}\|_0$ in \eqref{minsum} with its best convex approximation, $\|\mathbf{x}\|_1$, thereby transforming the inference of sparsest $\mathbf{\overline x}_i$ for fixed $\mathbf{B}$ into a convex optimization problem solvable by a linear program.
+Recalling the linear model \eqref{LinearModel} of data $\mathbf{z}_i$, the approach is to solve the following problem instead of attempting to solve Prob~\ref{SLCopt} directly.:
 
@@
 \min \sum_{i = 1}^N \|\mathbf{\overline x}_{i}\|_1 \ \
-\text{subject to} \ \ \|\mathbf{z}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \eta, \ \text{for all $i$}.
+\text{subject to} \ \ \|\mathbf{z}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \eta, \ \text{for all $i$},
 \end{equation}
@@
 
-A major advance in compressive sensing was the discovery that, when $\mathbf{B}$ is held fixed, solutions to \eqref{l1minsum} are in fact solutions to \eqref{minsum} provided $L_{2k}(\mathbf{B})$ is large enough \cite{eldar2012compressed}.
-Interestingly, the current work provides conditions on the generating dictionary $\mathbf{A}$ and $k$-sparse codes $\mathbf{x}_i$ under which \emph{all} matrices $\mathbf{B}$ (of bounded column-norm) that solve Prob.~\ref{OptimizationProblem} have $L_{2k}(\mathbf{B})$ bounded from below; specifically, $L_{2k}(\mathbf{B}) \geq \left(L_{2k}(\mathbf{A}) - C_1\varepsilon \right) / \|\mathbf{D}\|_1$ in the case where $\mathbf{A}$ satisfies \eqref{SparkCondition}.
-Thus, there is some noise bound inside of which all solutions to Prob.~\ref{OptimizationProblem} are solutions to the convexified problem as well.
-It is an open question as to whether practical constraints would exclude any remaining solutions to the convefixied problem that don't also solve Prob.~\ref{OptimizationProblem}.
+A major advance in compressive sensing was the discovery that, when the matrix $\mathbf{B}$ is held fixed, the vectors $\mathbf{\overline x}_i$ that solve \eqref{l1minsum} also in fact minimize \eqref{minsum} provided $L_{2k}(\mathbf{B})$ is large enough \cite{eldar2012compressed}.
+Interestingly, the current work provides conditions on the generating dictionary $\mathbf{A}$ and $k$-sparse codes $\mathbf{x}_i$ under which \emph{all} matrices $\mathbf{B}$ solving Prob.~\ref{OptimizationProblem} have $L_{2k}(\mathbf{B})$ bounded from below; specifically, $L_{2k}(\mathbf{B}) \geq \left(L_{2k}(\mathbf{A}) - 2\eta C_1 \right) / \|\mathbf{D}\|_1$ in the case where $\mathbf{A}$ satisfies the spark condition \eqref{SparkCondition}.
+Thus, for suitable $\mathbf{A}$ there is some noise bound inside of which all solutions to Prob.~\ref{OptimizationProblem} are solutions to Prob.~\ref{ConvexifiedOptimizationProblem} as well.
+It is an open question as to whether there exist practical constraints which reject solutions to Prob.~\ref{ConvexifiedOptimizationProblem} that don't also solve Prob.~\ref{OptimizationProblem}.
 
-As an intuitive example to kickstart these efforts, consider the simple noiseless ($\eta = 0$) case for $k=1$ where the matrix $\mathbf{A}$ has linearly independent unit-norm columns and $\mathbf{x}_i = c\mathbf{e}_i$ for some $c \geq 1$ for all $i \in [m]$.
-Suppose that for some $\mathbf{B}$ also having linearly independent unit-norm columns there are vectors $\mathbf{\overline x}_i$ satisfying $\|\mathbf{\overline x}_i\|_1 \leq c$ and $\mathbf{B \overline x}_i = \mathbf{Ax}_i$ for all $i \in [m]$.
-Intuitively, the only vectors in the convex polygon $\{ \mathbf{B \overline x}: \|\mathbf{\overline x}\|_1 \leq c\}$ for which $\|\mathbf{B \overline x}_i\|_2 = \|\mathbf{Ax}_i\|_2 = \|c\mathbf{Ae}_i\|_2 = c$ are its corners $\mathbf{B}(\pm c\mathbf{e}_j)$ for $j \in [m]$, so the $\mathbf{\overline x}_i$ must also be 1-sparse and we can apply Thm.~\ref{DeterministicUniquenessTheorem}.
+We can already see this may be possible by examining the simple case $k=1$ without noise, i.e. $\eta = 0$.
+%Consider the dataset generated as in \eqref{LinearModel} in the noiseless case $\eta = 0$, i.e.:
+%\begin{align*}
+%\mathbf{z}_i = \mathbf{A}\mathbf{x}_i,\ \ \  \text{$i=1,\ldots,N$}.
+%\end{align*}
+%with the additional constraint that $\|\mathbf{Ae}_i\|_2 = 1$ for all $i \in [m]$. 
+%\begin{conjecture}
+%Fix a matrix $\mathbf{A}$ with $\|\mathbf{A}\|_2=1$ and vectors $\mathbf{x}_i$ satisfying also the assumptions of Thm.~\ref{SLCopt}.
+Every solution to Prob.~\ref{ConvexifiedOptimizationProblem} satisfies BLAH and BLAH.
+%\end{conjecture}
+
+\begin{proposition}
+If $\mathbf{A}$ has $L_2(\mathbf{A}) > 0$ and unit length-columns, and $\mathbf{x}_i = c_i\mathbf{e}_i$ with $c_i \neq 0$ for $i = 1, \ldots, m$, then every solution to Prob.~\ref{ConvexifiedOptimizationProblem} with matrices $\mathbf{B}$ having $m$ unit-length columns satisfies $\mathbf{A} = \mathbf{BP}$ and $\mathbf{x}_i = \mathbf{P}^\top \mathbf{\overline x}_i$ for some $m \times m$ permutation matrix $\mathbf{P}$.
+\end{proposition}
+
+\begin{proof}
+We will show that the $\mathbf{\overline x}_i$ must in fact be $1$-sparse and then apply Thm.~\ref{DeterministicUniquenessTheorem}.
+Fix $i \in [m]$.
+Writing $\mathbf{\overline x}_i = \sum_{j=1}^m \overline c_{j} \mathbf{e}_j$, we have:
+\begin{align}\label{gtc}
+c_i = \|c_i\mathbf{Ae}_i\|_2 = \|\mathbf{B \overline x}_i\|_2 = \|\sum_{j=1}^m \overline c_{j} \mathbf{Be}_j\|_2 \leq \sum_{j=1}^m |\overline c_{j}| \|\mathbf{Be}_j\|_2 = \|\mathbf{\overline x}_i\|_1
+\end{align}
+So $\|\mathbf{\overline x}_i\|_1 \geq c_i$ for all $i \in [m]$.
+Therefore $\sum_{i=1}^m \|\mathbf{\overline x}_i\|_1 \geq \sum_i c_i$.
+But since $\mathbf{A}$ and the $\mathbf{x}_i$ satisfy the constraints of the minimization problem, we must also have $\sum_{i=1}^m \|\mathbf{\overline x}_i\|_1 \leq \sum_{i=1}^m \|\mathbf{x}_i\|_1 = \sum_i c_i$.
+Thus $\sum_{i=1}^m \|\mathbf{\overline x}_i\|_1 = \sum_i c_i$.
+Since again $\|\mathbf{\overline x}_i\|_1 \geq c_i$ for all $i \in [m]$, we must have $\| \mathbf{\overline x}_i\|_1 = c_i$ for all $i \in [m]$.
+
+Revisiting \eqref{gtc}, we therefore have $c_i = \|\mathbf{B\overline x}_i\|_2 \leq \|\mathbf{\overline x}_i\|_1 = c_i$ for all $i \in [m]$, with equality holding only when $\overline c^{(i)}_j \mathbf{Be}_j$ are colinear.
+This would be the case either if the $\mathbf{\overline x}_i$ are $1$-sparse, in which case we may apply Thm.~\ref{DeterministicUniquenessTheorem} to guarantee both dictionary and code recovery, or if $\mathbf{B}$ has colinear columns.
+We can rule out the latter case because if that were so, we could consolidate all sets of colinear columns to form a dictionary with fewer than $m$ linearly independent columns and yet for which there must exist $1$-sparse $\mathbf{\overline x}_i$ solving Prob.~\ref{ConvexifiedOptimizationProblem}; but this would contradict the fact that $L_2(\mathbf{A}) > 0$.
+\end{proof}
+
+%\begin{conjecture}\label{l1conjecture}
+%Fix a matrix $\mathbf{A}$ with $\|\mathbf{Ae}_i\|_2 = 1$ for $i \in [m]$ and vectors $\mathbf{x}_i$ satisfying the assumptions of Thm.~\ref{SLCopt}.
+Every solution to Prob.~\ref{ConvexifiedOptimizationProblem} (with $\eta = \varepsilon/2$) and $\|\mathbf{Be}_i\|_2 = 1$.
+satisfies recovery guarantees \eqref{Cstable} and \eqref{b-PDa} when the corresponding bounds on $\eta$ are met.
+%\end{theorem}
 

### 2020-08-13 manuscripts/thesis/introduction.tex
redid abstract

@@
 For clarity of exposition, the technical proofs of Thms.~\ref{DeterministicUniquenessTheorem} and ~\ref{SLCopt} are deferred to Chap.~\ref{DUT}, following some necessary definitions and the statement of a key lemma in combinatorial matrix analysis (Lem.~\ref{MainLemma}, proven in the chapter's Appendix).
-These results and their applications are discussed in Chap.~\ref{Discussion}, which concludes with some open questions and directions for future research seeded in part by practically-minded simulations.
+These results and their applications are discussed in Chap.~\ref{Discussion}, which concludes with some open questions and directions for future research seeded in part by some practically-minded simulations.
 %The Appendix contains a proof of Lem.~\ref{MainLemma}.

### 2020-08-13 manuscripts/thesis/results.tex
new intro
redid abstract

@@
 
-\subsection{Deterministic Uniqueness Theorems}
+\subsection{Deterministic guarantees}
 
@@
 
-\subsection{Probabilistic uniqueness theorems}
+\subsection{Probabilistic guarantees}
 
@@
 
-As it seemed to benefit a reviewer of this work, some clarification may be in order on how the deterministic sample complexity $N = |\mathcal{H}\left[|(k-1){m \choose k} + 1\right]$ given here (Cor.~\ref{DeterministicUniquenessCorollary}) compares to those listed in the the top two rows listed in Table I of \cite{Hillar15}.
+As it seemed to benefit a reviewer of this work, some clarification may be in order on how the deterministic sample complexity $N = |\mathcal{H}|\left[(k-1){m \choose k} + 1\right]$ given here (Cor.~\ref{DeterministicUniquenessCorollary}) compares to those listed in the the top two rows listed in Table I of \cite{Hillar15}.
 To be clear, the theory developed here is strictly more general, since $\mathcal{H}$ can always be taken to be ${[m] \choose k}$.

### 2020-08-13 manuscripts/thesis/discussion.tex
redid abstract

@@
 Since Prob.~\ref{SLCopt} is intractable in general (i.e.
-including the noiseless case), but efficiently solvable by convex relaxation when the matrix $\mathbf{A}$ is known and has a large enough lower bound over sparse domains \cite{eldar2012compressed}, is there a version of Thm.~\ref{SLCopt} that lays down general conditions under which Prob.~\ref{OptimizationProblem} can be solved efficiently in full by similar means?
+including the noiseless case), but solvable in practice by convex relaxation when the matrix $\mathbf{A}$ is known and has a large enough lower bound over sparse domains \cite{eldar2012compressed}, is there a version of Thm.~\ref{SLCopt} that lays down general conditions under which Prob.~\ref{OptimizationProblem} can be solved efficiently in full by similar means?
 % [*** Incorporate this open problem with more words ***]
@@
 I briefly expand on some of these directions below.
-It is my hope that these remaining challenges pique the interest of the community, and that practical guidelines can be established using the theoretical tools showcased here to support researchers applying sparse coding techniques in their data analysis pipelines.
+It is my hope that these remaining challenges pique the interest of the community and that the theoretical tools showcased here can be applied to derive practical dictionary learning guidelines for sparse representation modeling of real data.
 
@@
 
-A commonly applied workaround to the intractability (see \cite{tillmann2015computational}) of Prob.~\ref{SLCopt} is to replace the norm $\|\mathbf{x}\|_0$ in \eqref{minsum} with its best convex approximation, $\|\mathbf{x}\|_1$, thereby transforming the inference of sparsest $\mathbf{\overline x}_i$ for fixed $\mathbf{B}$ into a convex optimization problem solvable by a linear program.
-Recalling the linear model \eqref{LinearModel} of data $\mathbf{z}_i$, the approach is to solve the following problem instead of attempting to solve Prob~\ref{SLCopt} directly.:
+A commonly applied workaround to the intractability (see \cite{tillmann2015computational}) of Prob.~\ref{SLCopt} is to replace the $\ell_0$-norm in \eqref{minsum} with its best convex approximation, the $\ell_1$-norm, thereby transforming the inference of sparsest $\mathbf{\overline x}_i$ for fixed $\mathbf{B}$ into a convex optimization problem solvable by a linear program.
+Recalling the linear model \eqref{LinearModel} of data $\mathbf{z}_i$, the approach is to solve the following problem rather than solving Prob~\ref{SLCopt} directly.:
 
@@
 
-A major advance in compressive sensing was the discovery that, when the matrix $\mathbf{B}$ is held fixed, the vectors $\mathbf{\overline x}_i$ that solve \eqref{l1minsum} also in fact minimize \eqref{minsum} provided $L_{2k}(\mathbf{B})$ is large enough \cite{eldar2012compressed}.
+A major advance in compressive sensing was the discovery of practical criteria guaranteeing that, when the matrix $\mathbf{B}$ is held fixed, the vectors $\mathbf{\overline x}_i$ that solve \eqref{l1minsum} also in fact solve \eqref{minsum} provided $L_{2k}(\mathbf{B})$ is large enough \cite{eldar2012compressed}.
 Interestingly, the current work provides conditions on the generating dictionary $\mathbf{A}$ and $k$-sparse codes $\mathbf{x}_i$ under which \emph{all} matrices $\mathbf{B}$ solving Prob.~\ref{OptimizationProblem} have $L_{2k}(\mathbf{B})$ bounded from below; specifically, $L_{2k}(\mathbf{B}) \geq \left(L_{2k}(\mathbf{A}) - 2\eta C_1 \right) / \|\mathbf{D}\|_1$ in the case where $\mathbf{A}$ satisfies the spark condition \eqref{SparkCondition}.
-Thus, for suitable $\mathbf{A}$ there is some noise bound inside of which all solutions to Prob.~\ref{OptimizationProblem} are solutions to Prob.~\ref{ConvexifiedOptimizationProblem} as well.
+Thus, for suitable $\mathbf{A}$ there should be some noise bound inside of which all solutions to Prob.~\ref{OptimizationProblem} are solutions to Prob.~\ref{ConvexifiedOptimizationProblem} as well.
 It is an open question as to whether there exist practical constraints which reject solutions to Prob.~\ref{ConvexifiedOptimizationProblem} that don't also solve Prob.~\ref{OptimizationProblem}.
@@
 \begin{proposition}
-If $\mathbf{A}$ has $L_2(\mathbf{A}) > 0$ and unit length-columns, and $\mathbf{x}_i = c_i\mathbf{e}_i$ with $c_i \neq 0$ for $i = 1, \ldots, m$, then every solution to Prob.~\ref{ConvexifiedOptimizationProblem} with matrices $\mathbf{B}$ having $m$ unit-length columns satisfies $\mathbf{A} = \mathbf{BP}$ and $\mathbf{x}_i = \mathbf{P}^\top \mathbf{\overline x}_i$ for some $m \times m$ permutation matrix $\mathbf{P}$.
+If the matrix $\mathbf{A}$ has unit length-columns with $L_2(\mathbf{A}) > 0$ and $\mathbf{x}_i = c_i\mathbf{e}_i$ with $c_i \neq 0$ for $i = 1, \ldots, m$, then every solution to Prob.~\ref{ConvexifiedOptimizationProblem} with $\mathbf{B}$ also having $m$ unit-length columns satisfies $\mathbf{A} = \mathbf{BP}$ and $\mathbf{x}_i = \mathbf{P}^\top \mathbf{\overline x}_i$ for some $m \times m$ permutation matrix $\mathbf{P}$.
 \end{proposition}
@@
 We will show that the $\mathbf{\overline x}_i$ must in fact be $1$-sparse and then apply Thm.~\ref{DeterministicUniquenessTheorem}.
-Fix $i \in [m]$.
-Writing $\mathbf{\overline x}_i = \sum_{j=1}^m \overline c_{j} \mathbf{e}_j$, we have:
+Fixing $i \in [m]$ and writing $\mathbf{\overline x}_i = \sum_{j=1}^m \overline c_{j} \mathbf{e}_j$, we have:
 \begin{align}\label{gtc}
-c_i = \|c_i\mathbf{Ae}_i\|_2 = \|\mathbf{B \overline x}_i\|_2 = \|\sum_{j=1}^m \overline c_{j} \mathbf{Be}_j\|_2 \leq \sum_{j=1}^m |\overline c_{j}| \|\mathbf{Be}_j\|_2 = \|\mathbf{\overline x}_i\|_1
+c_i = \|\mathbf{Ax}_i\|_2 = \|\mathbf{B \overline x}_i\|_2 = \|\sum_{j=1}^m \overline c_{j} \mathbf{Be}_j\|_2 \leq \sum_{j=1}^m |\overline c_{j}| \|\mathbf{Be}_j\|_2 = \|\mathbf{\overline x}_i\|_1
 \end{align}
-So $\|\mathbf{\overline x}_i\|_1 \geq c_i$ for all $i \in [m]$.
-Therefore $\sum_{i=1}^m \|\mathbf{\overline x}_i\|_1 \geq \sum_i c_i$.
-But since $\mathbf{A}$ and the $\mathbf{x}_i$ satisfy the constraints of the minimization problem, we must also have $\sum_{i=1}^m \|\mathbf{\overline x}_i\|_1 \leq \sum_{i=1}^m \|\mathbf{x}_i\|_1 = \sum_i c_i$.
-Thus $\sum_{i=1}^m \|\mathbf{\overline x}_i\|_1 = \sum_i c_i$.
-Since again $\|\mathbf{\overline x}_i\|_1 \geq c_i$ for all $i \in [m]$, we must have $\| \mathbf{\overline x}_i\|_1 = c_i$ for all $i \in [m]$.
+So $\|\mathbf{\overline x}_i\|_1 \geq c_i$ for all $i \in [m]$, and we have $\sum_{i=1}^m \|\mathbf{\overline x}_i\|_1 \geq \sum_{i=1}^m  c_i$.
+But since $\mathbf{A}$ and the $\mathbf{x}_i$ satisfy the constraints of the minimization problem, we must also have $\sum_{i=1}^m \|\mathbf{\overline x}_i\|_1 \leq \sum_{i=1}^m \|\mathbf{x}_i\|_1 = \sum_{i=1}^m  c_i$.
+Thus, $\sum_{i=1}^m \|\mathbf{\overline x}_i\|_1 = \sum_{i=1}^m  c_i$.
+Since again $\|\mathbf{\overline x}_i\|_1 \geq c_i$, it must be the case that in fact $\| \mathbf{\overline x}_i\|_1 = c_i$ for all $i \in [m]$.
 
-Revisiting \eqref{gtc}, we therefore have $c_i = \|\mathbf{B\overline x}_i\|_2 \leq \|\mathbf{\overline x}_i\|_1 = c_i$ for all $i \in [m]$, with equality holding only when $\overline c^{(i)}_j \mathbf{Be}_j$ are colinear.
-This would be the case either if the $\mathbf{\overline x}_i$ are $1$-sparse, in which case we may apply Thm.~\ref{DeterministicUniquenessTheorem} to guarantee both dictionary and code recovery, or if $\mathbf{B}$ has colinear columns.
-We can rule out the latter case because if that were so, we could consolidate all sets of colinear columns to form a dictionary with fewer than $m$ linearly independent columns and yet for which there must exist $1$-sparse $\mathbf{\overline x}_i$ solving Prob.~\ref{ConvexifiedOptimizationProblem}; but this would contradict the fact that $L_2(\mathbf{A}) > 0$.
+Revisiting \eqref{gtc}, for a given $i \in [m]$ we have $c_i = \|\mathbf{B\overline x}_i\|_2 \leq \|\mathbf{\overline x}_i\|_1 = c_i$, with equality holding only when the vectors $\overline c_j \mathbf{Be}_j$ are colinear.
+This would be the case either if $\mathbf{\overline x}_i$ is $1$-sparse, or if $\mathbf{B}$ has colinear columns.
+We can rule out the latter case because if that were so, we could consolidate all sets of colinear columns to form a dictionary with fewer than $m$ columns and yet for which there must exist $1$-sparse $\mathbf{\overline x}_i$, $i = 1, \ldots, m$ solving Prob.~\ref{ConvexifiedOptimizationProblem}; but this would contradict the fact that $L_2(\mathbf{A}) > 0$.
+So it must be the case that in fact the $\mathbf{\overline x}_i$ are all $1$-sparse, and we may apply Thm.~\ref{DeterministicUniquenessTheorem}.
 \end{proof}
 
+The approach here was to show that the points $\mathbf{B \overline x}_i$ lie on a polytype which may identify with all of the data $\mathbf{z}_i = c_i\mathbf{Ae}_i$ only at its vertices, and that the $\mathbf{\overline x}_i$ must therefore be $1$-sparse.
+It seems reasonable to believe similar arguments would apply in the general case $k < m$, where the points $\mathbf{B \overline x}_i$ may align with all of the data only at the $k-1$-dimensional boundaries of the polytope.
+%As a next step toward this general case, I propose the following simple conjecture:
+
 %\begin{conjecture}\label{l1conjecture}
-%Fix a matrix $\mathbf{A}$ with $\|\mathbf{Ae}_i\|_2 = 1$ for $i \in [m]$ and vectors $\mathbf{x}_i$ satisfying the assumptions of Thm.~\ref{SLCopt}.
-Every solution to Prob.~\ref{ConvexifiedOptimizationProblem} (with $\eta = \varepsilon/2$) and $\|\mathbf{Be}_i\|_2 = 1$.
-satisfies recovery guarantees \eqref{Cstable} and \eqref{b-PDa} when the corresponding bounds on $\eta$ are met.
-%\end{theorem}
+%Fix a matrix $\mathbf{A}$ with unit-length columns and vectors $\mathbf{x}_i \in \mathbb{R}^m$ with $\|\mathbf{x}_i\|_1 = c$ $(c > 0)$ for all $i \in [m]$ satisfying the assumptions of Thm.~\ref{SLCopt}.
+Assume data $\mathbf{z}_i = \mathbf{Ax}_i$ for all $i \in [m]$.
+Every solution to Prob.~\ref{ConvexifiedOptimizationProblem} (with $\eta = 0$) for which $\mathbf{B}$ also has $m$ unit-length columns satisfies recovery guarantees \eqref{Cstable} and \eqref{b-PDa}.
+%\end{conjecture}
 

### 2020-08-13 manuscripts/thesis/results.tex
redid abstract

@@
 Fix a matrix $\mathbf{A}$ and vectors $\mathbf{x}_i$ satisfying the assumptions of Thm.~\ref{DeterministicUniquenessTheorem}, only now with over \mbox{$(k-1)\left[ {\overline m \choose k} + |\mathcal{H}|k{\overline m \choose k-1}\right]$} vectors supported in general linear position in each $S \in \mathcal{H}$.
-Every solution to Prob.~\ref{OptimizationProblem} (with $\eta = \varepsilon/2$) satisfies recovery guarantees \eqref{Cstable} and \eqref{b-PDa} when the corresponding bounds on $\eta$ are met.
+Every solution to Prob.~\ref{OptimizationProblem} (with $\eta = \varepsilon/2$) satisfies the dictionary recovery and code recovery guarantees of Thm.~\ref{DeterministicUniquenessTheorem} when the corresponding bounds on $\varepsilon$ are met.
 \end{theorem}

### 2020-08-13 manuscripts/thesis/abstract.tex
redid abstract

--- 2020-08-04 manuscripts/thesis/abstract.tex
@@
 \begin{abstract}
-Learning optimal dictionaries for sparse coding has exposed characteristic sparse features of many natural signals.
+Learning optimal dictionaries for sparse representation modeling has led to the discovery of characteristic sparse features in several classes of natural signals. 
 However, universal guarantees of the uniqueness and stability of such features in the presence of noise are lacking. 
@@
 The stability constants are explicit and computable; as such, there is an effective procedure sufficient to affirm if a proposed solution to the dictionary learning problem is unique within bounds commensurate with the noise.
-Beyond the extension of existing results to the noisy regime, a theory of combinatorial designs for sparse supports is introduced to demonstrate that some or all generating dictionary elements are recoverable from noisy data even if the dictionary fails to satisfy the spark condition, its size is overestimated, or only a polynomial number of distinct supports appear in the encoded data.
-Importantly, the guarantees derived here assume no constraints on the recovered dictionary beyond a natural upper bound on its size.
-The work closes with a lengthy discussion of the results and some remaining open challenges seeding future research directions.
+
+Two formulations of the dictionary learning problem are considered.
+The first seeks a dictionary which admits a sparse representation of bounded support size for each point in a dataset.
+In this case, beyond the original extension of existing guarantees to the noisy regime, a theory of combinatorial designs for sparse supports is introduced to demonstrate that the dictionary and corresponding sparse codes are almost always identifiable up to scaling/labeling ambiguities and an error commensurate with the noise, given sufficient data.
+This is the case even if the dictionary fails to satisfy the spark condition, its size is overestimated, or the data is distributed over only a polynomial number of subspaces spanned by the dictionary.
+
+The second formulation of the problem seeks a dictionary which minimizes the average support size of the induced sparse representations of the data.
+The guarantees in this case are the first of their kind in both in the noiseless and noisy regimes, and are derived by demonstrating that in fact, given sufficient data, this second problem reduces to an instance of the first.
+Importantly, in both cases the guarantees apply without imposing any assumptions at all on learned dictionaries beyond a natural upper bound on their size.
+
+This work serves to justify, in principle, dictionary learning in general as means of discovering latent sparse structure in real data.
+Though much work remains to be done deriving criteria for use in practice, it is my hope that the theoretical tools developed herein will be of use to this end.
+%The work closes with some open questions and directions for future research, seeded in part by the results of more practically-minded simulations. 
 \end{abstract}

### 2020-08-13 manuscripts/thesis/discussion.tex
redid abstract

@@
 
-It is possible to tighten the pigeonholing argument in the proof of Thm.~\ref{DeterministicUniquenessTheorem} and thereby reduce the deterministic sample complexity without recourse to uncertainty.
+It is possible to tighten the pigeonholing argument in the proof of Thm.~\ref{DeterministicUniquenessTheorem} and thereby reduce the deterministic sample complexity without recourse to uncertain guarantees.
 The argument as presented iterates over supports $S \in \mathcal{H}$, in each case determining a corresponding support $\overline S \in {[\overline m] \choose k}$ without consideration of previously matched support pairs; and yet the assumption $L_{2\mathcal{H}}(\mathbf{A}) > 0$ implies that no two supports in $\mathcal{H}$ can map to the same $\overline S$.
@@
 
-A close examination of the proof of Lemma \ref{NonEmptyLemma} (see the Appendix) reveals, however, that $\mathcal{H}$ need not be regular so long as it satisfies a constraint on the sequence of node degrees compatible with the iterative argument.
-It is then natural to wonder: what are the necessary constraints on $\mathcal{H}$, and what is the smallest hypergraph satisfying these constraints for given $m$ and $k$?
-
-%%%%%%%%%%%%%%
-% need to cut maybe: 
-%As mentioned in the previous section, Thm.~\ref{DeterministicUniquenessTheorem} is a particular case of a more general result that forgoes the assumption that $\mathcal{H} \subseteq {[m] \choose k}$ is regular and satisfies the SIP.
-If instead we require only that the stars $\cap \sigma(i)$ intersect at singletons for all $i \leq q$ (assuming that the nodes of $\mathcal{H}$ are labeled in some order of non-increasing degree), we have that $\overline m \geq k|\mathcal{H}| / \deg(1)$ and, provided $\overline m < k|\mathcal{H}| / (\deg(1) - 1)$, the nonempty submatrix $J$ is of size equal to the largest number $p$ satisfying:
-%\begin{align}\label{pcond}
-%\sum_{i=\ell}^{m} \deg(i) > (\overline m + 1 - \ell) (\deg(\ell) - 1) \ \ \text{for all } \ell \leq p \leq q.
-%\end{align}
-%Specifically, $J$ contains all nodes of degree exceeding $\deg(p)$ and some subset of those with degreee equal to $\deg(p)$.
-For the benefit of the reader, we do not prove explicitly this more general result below; it can be discerned from how exactly Lemma \ref{NonEmptyLemma} is incorporated into the proof of Lem.~\ref{MainLemma}.
+A close examination of how exactly Lemma \ref{NonEmptyLemma} is incorporated into the proof of Lem.~\ref{MainLemma} reveals, however, that looser constraints on $\mathcal{H}$ maintain compatibility with the iterative argument to some degree.
+If instead we require only that the stars $\cap \sigma(i)$ intersect at singletons for all $i \leq q$ for some positive $q$ (assuming that the nodes of $\mathcal{H}$ are labeled in some order of non-increasing degree), we have that $\overline m \geq k|\mathcal{H}| / \deg(1)$ and, provided $\overline m < k|\mathcal{H}| / (\deg(1) - 1)$, the nonempty subset $J$ is of size equal to the largest number $p$ satisfying:
+\begin{align*}
+\sum_{i=\ell}^{m} \deg(i) > (\overline m + 1 - \ell) (\deg(\ell) - 1) \ \ \text{for all } \ell \leq p \leq q.
+\end{align*}
+Specifically, $J$ contains all nodes of degree exceeding $\deg(p)$ and some subset of those with degree equal to $\deg(p)$.
+It is thus natural to ask: what are the necessary constraints on $\mathcal{H}$ for full recovery, and what is the smallest hypergraph satisfying these constraints for given $m$ and $k$?
 %%%%%%%%%%%%%%%%
 
-Opening ourselves up to uncertainty, we can furthermore ask:
+Opening ourselves up instead to uncertain guarantees, we can ask:
 \begin{question}\label{probofsip}
@@
 
-Within the realm of uncertain guarantees, we can also elaborate on the probabilistic pigeonholing strategy outlined in the discussion following the proof of Thm.~\ref{DeterministicUniquenessTheorem}.
-The problem is to count the number of ways in which vectors supported in $S \in \mathcal{H}$ can be partitioned among supports in ${\overline m \choose k}$ without allocating $k$ or more to any individual one (in which case the logic of the proof fails to imply the result; we are interested in the probability that it doesn't).
+In the spirit of uncertainty, we can also elaborate on the probabilistic pigeonholing strategy outlined in the discussion following the proof of Thm.~\ref{DeterministicUniquenessTheorem}.
+The problem is to count the number of ways in which vectors supported in $S \in \mathcal{H}$ can be partitioned among supports in ${[\overline m] \choose k}$ without allocating $k$ or more to any individual one (in which case the logic of the proof fails to imply the result; we are interested in the probability that it doesn't).
 These are integer solutions to the problem $\sum_i n_i = N$ subject to $n_i < k$ for all $i$, where $i = 1, \ldots, {\overline m \choose k}$.
@@
 The total number of ways to pigeonhole is $n_\text{total} = {N +p- 1 \choose p - 1}$, and so the probability of full recovery is $\left(1 - n_\text{fails} / n_\text{total} \right)^{|\mathcal{H}|}$. 
-The curves computed in this way in Fig.
-\ref{probpigeon} suggest that, while it may very well be impossible to exorcise exponentiality from the number of required samples in the deterministic or almost-certain case, perhaps it is possible with high-probability by one way or another.
+Curves computed in this way in (see Fig.
+\ref{probpigeon}) suggest that while it may very well be impossible to exorcise exponentiality from the number of required samples in the deterministic or almost-certain case, perhaps it is possible with high-probability by one way or another.
 Informally,
@@
 
-The approach here was to show that the points $\mathbf{B \overline x}_i$ lie on a polytype which may identify with all of the data $\mathbf{z}_i = c_i\mathbf{Ae}_i$ only at its vertices, and that the $\mathbf{\overline x}_i$ must therefore be $1$-sparse.
-It seems reasonable to believe similar arguments would apply in the general case $k < m$, where the points $\mathbf{B \overline x}_i$ may align with all of the data only at the $k-1$-dimensional boundaries of the polytope.
+The approach taken here was to show that the points $\mathbf{B \overline x}_i$ lie on a polytype which identifies with all of the data $\mathbf{z}_i = c_i\mathbf{Ae}_i$ only at its vertices, and that the $\mathbf{\overline x}_i$ must therefore be $1$-sparse.
+Intuitively, it seems that similar arguments should apply in the general case $k < m$, where the points $\mathbf{B \overline x}_i$ may align with all of the data only at the $k-1$-dimensional boundaries of the polytope.
 %As a next step toward this general case, I propose the following simple conjecture:

### 2020-08-13 manuscripts/thesis/introduction.tex
redid abstract

--- 2020-08-07 manuscripts/thesis/introduction.tex
@@
 
-It is a longstanding practice in the field of signal processing to describe signals as linear combinations of elementary waveforms selected from a pre-specified ``dictionary".
-Every signal has a unique representation in terms of these atomic components when the dictionary forms a basis.
-For example, a signal can be decomposed into its constituent frequencies via the Fourier transform, which performs a linear change of basis.
+It is a long-standing practice in the field of signal processing to describe signals as linear combinations of elementary waveforms selected from a pre-specified ``dictionary".
+Every signal has a unique representation in terms of these components when the dictionary forms a basis.
+For example, a signal can be decomposed into its constituent frequencies via the Fourier transform, which performs a change of basis.
 %When the basis is orthonormal, the representational coefficient scaling a given elementary waveform is simply the inner product of that waveform with the signal.
@@
 %When non-orthogonal, the coefficients are computed by taking the inner product with respect to the components of the dictionary inverse.
-Until recently, bases have been the dominant form of signal representation due largely to their simplicity.
 
-For many signal analysis tasks, no one basis can convey clearly all of the relevant information in the signal.
-If a signal can be either a sine wave or a delta function, then neither the standard basis nor the Fourier basis will indicate one case as explicitly as it does the other.
-The need for such freedom of expression led to the development of redundant signal representations utilizing overcomplete dictionaries, which consist of more atoms than there are dimensions of the signal.
-While an overcomplete dictionary admits infinitely many possible ways to decompose a signal into a linear superposition its constituent atoms, the intention is to seek the best such representation, be it by some analytic criteria, or as measured by some task-specific cost function.
+Bases have been the dominant form of signal representation until recently due largely to their simplicity.
+For many signal analysis tasks, however, no one basis can convey clearly all of the relevant information in the signal.
+For instance, if a signal can be either a sine wave or a delta function, then neither the standard basis nor the Fourier basis will indicate one case as explicitly as it does the other.
 
-A popular approach to the design of overcomplete dictionaries has been to seek one which admits a sparse representation for every signal of interest; that is, each signal can be represented, or at least well-approximated, as a combination of only a few dictionary elements from the bunch.
-Continuing with our example, the union of the standard basis with the Fourier basis is an overcomplete dictionary with respect to which both sine waves and delta functions (or any finite superpositions thereof) achieve the sparsest possible representation as a scaling of a single elementary waveform from the dictionary.
+This need for more freedom of expression has led to the development of redundant signal representations utilizing overcomplete dictionaries, which contain more waveforms than there are dimensions of the signal.
+An overcomplete dictionary admits infinitely many possible ways to decompose a signal into a linear superposition its constituent components.
+The intention is then to seek the best such representation, be it by some analytic criteria, or as measured by some task-specific cost function.
 
-Early approaches to sparse representation modeling assumed a model of the signal class from which a suitable sparsifying dictionary could be derived, as we have in our trivial example.
-Such dictionaries are characterized by an analytic formulation and a fast implicit implementation; yet they tend to be over-simplistic models when applied to natural phenomena.
+A popular approach to the design of overcomplete dictionaries in the latter case has been to seek one which admits a sparse representation for every signal of interest; that is, each signal can be reconstructed, or at least well-approximated, by a combination of only a few dictionary elements from the bunch.
+Carrying on with our running example, the union of the standard basis with the Fourier basis is an overcomplete dictionary with respect to which both sine waves and delta functions achieve the sparsest possible representation as the scaling of a single elementary waveform from the dictionary.
+
+Early approaches to sparse representation modeling would assume a model of the signal class from which a suitable sparsifying dictionary could be derived, as we have in our trivial example.
+Such dictionaries are characterized by an analytic formulation and a fast implicit implementation; yet they tend to be over-simplistic when applied to model natural phenomena.
 
@@
 %and more recent work relating compressed sensing \cite{eldar2012compressed} to a theory of information transmission through random wiring bottlenecks in the brain \cite{Isely10}, 
-In light of these observations, it is natural to wonder when and to what extent the optimal dictionary for sparse representation modeling can be identified given a representative sample from a signal class.
-Answers to this question have implications in practice wherever an appeal is made to latent sparse structure of data (e.g., forgery detection \cite{hughes2010, olshausen2010applied}; brain recordings \cite{jung2001imaging, agarwal2014spatially, lee2016sparse}; and gene expression \cite{wu2016stability}), the assumption being that this structure captures some identifiable physical or logically causal variable.
+In light of these observations, it is natural to wonder when the optimal dictionary for sparse representation modeling can be identified given a representative sample from a signal class.
+Answers to this question have implications in practice wherever an appeal is made to latent sparse structure of data (e.g., forgery detection \cite{hughes2010, olshausen2010applied}; brain recordings \cite{jung2001imaging, agarwal2014spatially, lee2016sparse}; and gene expression \cite{wu2016stability}), since the assumption is that this structure captures some identifiable physical or logically causal variable.
 
 Even though several dictionary learning algorithms have recently been proposed to provably recover a unique dictionary under specific conditions (see \cite[Sec.~I-E]{Sun16} for a summary of the state of the art), few theorems can be invoked to justify inference with respect to this model of data more broadly.
-Despite the now ubiquitous application of dictionary learning methods in practice, to the best of my knowledge a universal guarantee of the uniqueness and stability of learned dictionaries and the sparse representations they induce over real, uncertain data has yet to appear in the literature.
+Despite the now ubiquitous application of dictionary learning methods in practice, to the best of my knowledge a universal guarantee of the uniqueness and stability of learned dictionaries and the sparse representations they induce over real data in the presence of noise has yet to appear in the literature.
 
@@
 
-Let us proceed to rigorously define the two formulations of the dictionary learning problem with which this work concerns itself.
+Let us now rigorously define the two formulations of the dictionary learning problem with which this work concerns itself.
 Fix a matrix $\mathbf{A} \in \mathbb R^{n \times m}$ with the elementary waveforms of the dictionary as its columns  $\mathbf{A}_j$ ($j = 1,\ldots,m$) and let dataset $Z$ consist of measurements:
@@
 
-The same guarantees can be extended (Thm.~\ref{SLCopt}) to the following alternate formulation of the dictionary learning problem, which seeks to minimize the total number of nonzero entries in sparse codes.
+The same guarantees can be extended (Thm.~\ref{SLCopt}) to the following alternate formulation of the dictionary learning problem, which seeks to minimize the average number of nonzero entries in sparse codes.
 
@@
 
-Surprisingly, the development of Thm.~\ref{DeterministicUniquenessTheorem} is general enough to provide some uniqueness and stability even when generating $\mathbf{A}$ do not fully satisfy (\ref{SparkCondition}) and recovery dictionaries $\mathbf{B}$ have more columns than $\mathbf{A}$.
-Moreover, the approach incorporates a theory of combinatorial designs for the sparse supports of generating codes $\mathbf{x}_i$ that should be of independent interest.
+Surprisingly, the development of Thm.~\ref{DeterministicUniquenessTheorem} is general enough to guarantee uniqueness and stability even when generating $\mathbf{A}$ do not fully satisfy (\ref{SparkCondition}), and to some degree even when recovery dictionaries $\mathbf{B}$ have more columns than $\mathbf{A}$.
+The approach incorporates a theory of combinatorial designs for the sparse supports of generating codes $\mathbf{x}_i$ that should also be of independent interest.
 
@@
 For clarity of exposition, the technical proofs of Thms.~\ref{DeterministicUniquenessTheorem} and ~\ref{SLCopt} are deferred to Chap.~\ref{DUT}, following some necessary definitions and the statement of a key lemma in combinatorial matrix analysis (Lem.~\ref{MainLemma}, proven in the chapter's Appendix).
-These results and their applications are discussed in Chap.~\ref{Discussion}, which concludes with some open questions and directions for future research seeded in part by practically-minded simulations.
+These results and their applications are discussed in Chap.~\ref{Discussion}, which concludes with some open questions and directions for future research, which are seeded in part by some practically-minded simulations.
 %The Appendix contains a proof of Lem.~\ref{MainLemma}.

### 2020-08-13 manuscripts/thesis/proofs.tex
redid abstract

@@
 Rather, $\mathbf{A}$ need only be injective on the union of subspaces with supports forming a regular $k$-uniform hypergraph satisfying the SIP (a distinguishing example is given in Sec.~\ref{Results}).
-This relaxation of constraints inspired the definition of the restricted matrix lower bound $L_{\mathcal{H}}$ in \eqref{Ldef}, which generalizes the well-known (see footnote \ref{ripfootnote}) restricted matrix lower bound $L_k$ to be in terms of a hypergraph $\mathcal{H}$, and an interesting object for further study in its own right.
+This relaxation of constraints inspired the definition of the restricted matrix lower bound $L_{\mathcal{H}}$ in \eqref{Ldef}, which generalizes the well-known (see footnote \ref{ripfootnote}) restricted matrix lower bound $L_k$ to be in terms of a hypergraph $\mathcal{H}$, and is an interesting object for further study in its own right.
 %(For instance, how hard is it to check that $L_\mathcal{H}(\mathbf{A}) > 0$?)

### 2020-08-13 manuscripts/thesis/results.tex
redid abstract

@@
 Consequently, if $k$ is held fixed or if the size of the support set of reconstructing codes is polynomial in $\overline m$ and $k$, then a practical (polynomial) amount of data suffices to identify the dictionary.\footnote{In the latter case, a reexamination of the pigeonholing argument in the proof of Thm.~\ref{DeterministicUniquenessTheorem} requires a polynomial number of samples distributed over a polynomial number of supports.} Reasons to be skeptical that this holds in general, however, can be found in \cite{tillmann2014computational, tillmann2015computational}.
-Even so, the next chapter contains a discussion on how probabilistic guarantees can in fact be made for any number of available samples.
+Even so, the next chapter contains a discussion on how probabilistic guarantees can in fact be made for any number of available samples (see also Fig.~\ref{probpigeon}).
 
@@
 with probability one), a factor of $m$ reduction over that for which certainty can alternatively be guaranteed here.
+In their case, $(k+1)$ vectors need to be allocated to each of ${m \choose k}$ distinct supports, whereas here $(k-1){m \choose k} + 1$ vectors are allocated to each of $m$ distinct supports.
 %\item[III.] A direct comparison cannot be made because it is an open question as to the probability that a random set of supports satisfies the SIP.

### 2020-08-13 manuscripts/thesis/thesis.tex
new intro
l1
redid abstract

@@
 
-%\begin{dedication}
-%\null\vfil
+\begin{dedication}
+\null\vfil
 %\begin{center} 
-%I want to dedicate this to my dad.
-At the same time, I don't want to, because the results on display here can't be matched to the time with him I traded to produce them, and it feels as though dedicating this work to him would be measuring his life up against them.
-These theorems, while fundamental, are just something people might cite to feel better about the sparse coding analyses they were already going to do, anyway.
+I want to dedicate this to my dad.
+At the same time, I don't want to, because the results of this work can't be matched to the time with him I traded to produce them, and it feels as though dedicating this work to him would in some sense be measuring his life up against them.
+%These theorems, while fundamental, are just something people might cite to feel better about the sparse coding analyses they were already going to do, anyway.
 And yet, despite total freedom offered by the Helen Wills Neuroscience Institute, I worried the brain was so dauntingly complex that I should feel lucky to have at last been offered a well-defined relevant problem to work on, particularly one I felt even remotely equipped to solve myself, so as to feel deserving of a Ph.D.
 from UC Berkeley.
-The fact is that whatever the eventual effect of this work on the scientific ecosystem, these truths could have waited, arrived at their own pace, via myself or another, and I could have been more present with my dad as he waited for death.
-I couldn't really fathom what it actually meant for him to die, to never see or talk to or hug him again, while the idea of putting original work out there, of crafting my own piece of the overwhelming puzzle that is neuroscience, was tantalizing.
-Let's say, then, that this dedication is the first bit of a life's work, real work void of any prestigious position or degree and the associated self-doubt and pressure, put toward passionate id	eas, solving problems I care about and that actually matter, loving and caring for others or, as my dad would say, ``being a mensch".
-May this dedication serve to hold myself publicly accountable to that.
+The fact is that whatever may be the eventual butterfly effect of this work on the scientific ecosystem, these truths could have waited, arrived at their own pace, via myself or another, and I could have been more present with my dad as he waited patiently for a terminal cancer to take his life.
+
+While I couldn't really fathom what it actually meant for him to die -- to never see or talk to or hug him again -- the idea of putting original work out there, of crafting my own piece of the overwhelming puzzle that is neuroscience, was alluring.
+Yet, I feel as though it was a feeling of inadequacy, of having to prove myself worthy of the position I had come to find myself in after a first failed project that really drove these efforts.
+
+Let's just say, then, that this dedication is the first bit of a life's work, real work devoid of any prestigious position and the associated self-doubt, pressure, or delusions of grandeur; a life dedicated to passionate ideas, to solving problems I care about and that really matter, to loving and caring for others or, as my dad would say, to ``being a mensch".
+May this dedication serve to hold me publicly accountable to that.
 Also I love you, mom.
 I dedicate and don't dedicate this and everything to come to you, too.
-%\vspace{12pt}
+
+\vspace{12pt}
 %\end{center}
-%\vfil\null
-%\end{dedication}
+\vfil\null
+\end{dedication}
 
@@
 
-%\begin{acknowledgements}
-%I would like to thank: Chris Hillar for laying down the groundwork and vetting all of my proofs many times over.
-He lent me a lot of his time and expertise for little in return.
-Fritz Sommer for advising me and pointing me toward a tractable problem to solve.
-The Berkeley Student Cooperative for the amazing experience living co-operatively in Berkeley.
+\begin{acknowledgements}
+First and foremost, I would like to thank Chris Hillar for clearing the path in his original work on the dictionary problem, and for vetting all of my proofs many, many times over.
+He asked for nothing in return for his time, attention, and mathematical expertise, and continues to extend this generosity to anyone nerdy enough to handle it.
+Fritz Sommer for recommending my acceptance to Berkeley and for advising me as his student; although I eventually had to leave his lab to work on other problems of interest to me, he kindly lent me his time over the course of four years.
+The other members of my thesis committee: Bruno Olshausen, Mike DeWeese, and Bin Yu for their time and consideration as well.
+My mom would have killed me if I didn't claim this degree, so they saved my life.
+The graduate program managers of the Helen Wills Neuroscience Institute: Tony Leonard and Candace Groskreutz for their kindness and patience, and to the HWNI itself.
+The Redwood Center for Theoretical Neuroscience and the friends I made in the lab; I hope we remain in each other's lives.
+Finally, a heartfelt thank you to Eric Weiss for pointing me to the student co-ops, and The Berkeley Student Cooperative for the work they do providing the amazing experience of living co-operatively in Berkeley.
+The co-ops changed my life, and I am forever grateful -- thank you so, so much to the hundreds of talented, creative, passionate, intelligent, kind, thoughtful, absurd, inspiring people I have lived with throughout the years.
+The co-operative journey is only just beginning!
 CZ or die.
-%\end{acknowledgements}
+\end{acknowledgements}
 
@@
 \include{discussion}
-\include{appendix}
+%\include{appendix}
 

### 2020-08-13 manuscripts/thesis/thesis.tex
redid abstract

@@
 from UC Berkeley.
-The fact is that whatever may be the eventual butterfly effect of this work on the scientific ecosystem, these truths could have waited, arrived at their own pace, via myself or another, and I could have been more present with my dad as he waited patiently for a terminal cancer to take his life.
+The fact is that whatever may be the eventual butterfly effect of this work on the scientific ecosystem, these mathematical truths could have waited, arrived at their own pace, via myself or another, and I could have been more present with my dad as he waited patiently for a terminal cancer to take his life.
 
 While I couldn't really fathom what it actually meant for him to die -- to never see or talk to or hug him again -- the idea of putting original work out there, of crafting my own piece of the overwhelming puzzle that is neuroscience, was alluring.
-Yet, I feel as though it was a feeling of inadequacy, of having to prove myself worthy of the position I had come to find myself in after a first failed project that really drove these efforts.
+Yet, I feel as though it was a feeling of inadequacy, of having to prove myself worthy of the position I had come to find myself in after a first failed project that largely drove these efforts.
 
@@
 Fritz Sommer for recommending my acceptance to Berkeley and for advising me as his student; although I eventually had to leave his lab to work on other problems of interest to me, he kindly lent me his time over the course of four years.
-The other members of my thesis committee: Bruno Olshausen, Mike DeWeese, and Bin Yu for their time and consideration as well.
+The other members of my thesis committee: Bruno Olshausen, Mike DeWeese, and Bin Yu, for their time and consideration over the years as well, and for approving this dissertation.
 My mom would have killed me if I didn't claim this degree, so they saved my life.
@@
 The Redwood Center for Theoretical Neuroscience and the friends I made in the lab; I hope we remain in each other's lives.
-Finally, a heartfelt thank you to Eric Weiss for pointing me to the student co-ops, and The Berkeley Student Cooperative for the work they do providing the amazing experience of living co-operatively in Berkeley.
-The co-ops changed my life, and I am forever grateful -- thank you so, so much to the hundreds of talented, creative, passionate, intelligent, kind, thoughtful, absurd, inspiring people I have lived with throughout the years.
-The co-operative journey is only just beginning!
+Finally, a heartfelt thank you to Eric Weiss for pointing me to the student co-ops, and the Berkeley Student Cooperative (www.bsc.coop) for the work they do providing the amazing experience of living co-operatively in Berkeley.
+The co-ops changed my life, and I am forever grateful -- thank you so, so much to the hundreds of talented, creative, weird, passionate, intelligent, kind, thoughtful, absurd, inspiring people I have lived with throughout the years.
 CZ or die.

### 2020-08-14 manuscripts/thesis/abstract.tex
almost done

@@
 Two formulations of the dictionary learning problem are considered. 
-The first seeks a dictionary which admits a sparse representation of bounded support size for each point in a dataset.
-In this case, beyond the original extension of existing guarantees to the noisy regime, a theory of combinatorial designs for sparse supports is introduced to demonstrate that the dictionary and corresponding sparse codes are almost always identifiable up to scaling/labeling ambiguities and an error commensurate with the noise, given sufficient data.
-This is the case even if the dictionary fails to satisfy the spark condition, its size is overestimated, or the data is distributed over only a polynomial number of subspaces spanned by the dictionary.
+The first seeks a dictionary for which each signal in a dataset is well-approximated by a linear superposition of a limited number of dictionary elements.
+%he first seeks a dictionary admitting a sparse representation of limited support size for each signal in a dataset. 
+%In this case, beyond an original extension of existing guarantees to the noisy regime, a theory of combinatorial designs is introduced to show that the dictionary and corresponding sparse codes are almost always identifiable up to an error commensurate with the noise even if the dictionary fails to satisfy the spark condition, its size is overestimated, or it induces only a polynomial number of distinct sparse supports in the data.
+In this case, existing guarantees are extended to the noisy regime to demonstrate that such dictionaries and the sparse representations they induce are almost always identifiable up to an error commensurate with the noise.
+Moreover, a theory of combinatorial designs is introduced to demonstrate this is the case even if the dictionary fails to satisfy the spark condition, the data are distributed over only a polynomial set of subspaces spanned by the dictionary, or (to some extent) even if the dictionary is overestimated in size.
 
-The second formulation of the problem seeks a dictionary which minimizes the average support size of the induced sparse representations of the data.
-The guarantees in this case are the first of their kind in both in the noiseless and noisy regimes, and are derived by demonstrating that in fact, given sufficient data, this second problem reduces to an instance of the first.
-Importantly, in both cases the guarantees apply without imposing any assumptions at all on learned dictionaries beyond a natural upper bound on their size.
+The second formulation of the problem seeks a dictionary which minimizes the average number of dictionary elements required to approximate each signal in the dataset.
+The guarantees in this case are the first of their kind in both in the noiseless and noisy regimes and derive from the fact that, given sufficient data, this second problem actually reduces to an instance of the first.
+Importantly, in both cases, no constraints whatsoever are imposed on learned dictionaries beyond a natural upper bound on their size.
 
-This work serves to justify, in principle, dictionary learning in general as means of discovering latent sparse structure in real data.
-Though much work remains to be done deriving criteria for use in practice, it is my hope that the theoretical tools developed herein will be of use to this end.
+This work serves to justify, in principle, dictionary learning in general as a means of discovering latent sparse structure in real data.
+Though much work remains to be done deriving criteria for use in practice, the theoretical tools developed herein should be of use to this end.
 %The work closes with some open questions and directions for future research, seeded in part by the results of more practically-minded simulations. 

### 2020-08-14 manuscripts/thesis/discussion.tex
almost done

@@
 
-A close examination of how exactly Lemma \ref{NonEmptyLemma} is incorporated into the proof of Lem.~\ref{MainLemma} reveals, however, that looser constraints on $\mathcal{H}$ maintain compatibility with the iterative argument to some degree.
-If instead we require only that the stars $\cap \sigma(i)$ intersect at singletons for all $i \leq q$ for some positive $q$ (assuming that the nodes of $\mathcal{H}$ are labeled in some order of non-increasing degree), we have that $\overline m \geq k|\mathcal{H}| / \deg(1)$ and, provided $\overline m < k|\mathcal{H}| / (\deg(1) - 1)$, the nonempty subset $J$ is of size equal to the largest number $p$ satisfying:
+A close examination of how exactly Lemma \ref{NonEmptyLemma} is incorporated into the proof of Lem.~\ref{MainLemma} reveals, however, that looser constraints on $\mathcal{H}$ maintain compatibility with the argument to some degree.
+Assuming that the nodes of $\mathcal{H}$ are labeled in some order of non-increasing degree, if instead of the full SIP we require only that the stars $\cap \sigma(i)$ intersect at singletons for all $i \leq q$ for some positive $q$, we have that $\overline m \geq k|\mathcal{H}| / \deg(1)$ and, provided $\overline m < k|\mathcal{H}| / (\deg(1) - 1)$, the nonempty subset $J$ is of size equal to the largest number $p$ satisfying:
 \begin{align*}
@@
 Specifically, $J$ contains all nodes of degree exceeding $\deg(p)$ and some subset of those with degree equal to $\deg(p)$.
-It is thus natural to ask: what are the necessary constraints on $\mathcal{H}$ for full recovery, and what is the smallest hypergraph satisfying these constraints for given $m$ and $k$?
+It is thus natural to ask: what are the necessary constraints on the hypergraph $\mathcal{H}$, and what is the smallest hypergraph satisfying these constraints for given $m$ and $k$?
 %%%%%%%%%%%%%%%%
@@
 
-In the spirit of uncertainty, we can also elaborate on the probabilistic pigeonholing strategy outlined in the discussion following the proof of Thm.~\ref{DeterministicUniquenessTheorem}.
+We may also elaborate on the probabilistic pigeonholing strategy outlined in the discussion following the proof of Thm.~\ref{DeterministicUniquenessTheorem}.
 The problem is to count the number of ways in which vectors supported in $S \in \mathcal{H}$ can be partitioned among supports in ${[\overline m] \choose k}$ without allocating $k$ or more to any individual one (in which case the logic of the proof fails to imply the result; we are interested in the probability that it doesn't).

### 2020-08-14 manuscripts/thesis/thesis.tex
almost done

--- 2020-08-05 manuscripts/thesis/thesis.tex
@@
 
-%\begin{dedication}
-%\null\vfil
+\begin{dedication}
+\null\vfil
 %\begin{center} 
-%I want to dedicate this to my dad.
-At the same time, I don't want to, because the results on display here can't be matched to the time with him I traded to produce them, and it feels as though dedicating this work to him would be measuring his life up against them.
-These theorems, while fundamental, are just something people might cite to feel better about the sparse coding analyses they were already going to do, anyway.
-And yet, despite total freedom offered by the Helen Wills Neuroscience Institute, I worried the brain was so dauntingly complex that I should feel lucky to have at last been offered a well-defined relevant problem to work on, particularly one I felt even remotely equipped to solve myself, so as to feel deserving of a Ph.D.
-from UC Berkeley.
-The fact is that whatever the eventual effect of this work on the scientific ecosystem, these truths could have waited, arrived at their own pace, via myself or another, and I could have been more present with my dad as he waited for death.
-I couldn't really fathom what it actually meant for him to die, to never see or talk to or hug him again, while the idea of putting original work out there, of crafting my own piece of the overwhelming puzzle that is neuroscience, was tantalizing.
-Let's say, then, that this dedication is the first bit of a life's work, real work void of any prestigious position or degree and the associated self-doubt and pressure, put toward passionate id	eas, solving problems I care about and that actually matter, loving and caring for others or, as my dad would say, ``being a mensch".
-May this dedication serve to hold myself publicly accountable to that.
+I want to dedicate this work to my dad.
+At the same time, I don't want to, because these results can't be matched to the time with him I traded to produce them, and it feels as though dedicating this work to him would in some sense be measuring his life up against them.
+
+The fact is that whatever may be the eventual butterfly effect of this work on the scientific ecosystem, these mathematical truths could have waited, arrived at their own pace, via myself or another, and I could have been more present with my dad as he waited patiently to die of cancer.
+
+I suppose that I couldn't really fathom what it actually meant for this to happen -- to never see or talk to or hug him again -- while the idea of putting original work out there, of crafting my own piece of the overwhelming puzzle that is neuroscience, was tantalizing.
+Yet it was more-so a feeling of desperation, of having to accomplish something and prove myself worthy of the position I had come to find myself in after 25+ years of schooling and a first failed project of my own design, that I feel largely drove these efforts.
+Truth be told, I initially had no particular interest in dictionary learning other than as a means to passing my qualifying exam; and by that time, I worried the brain was so dauntingly complex that I should feel lucky to have at least been offered a well-defined and arguably relevant problem in neuroscience to work on, particularly one I felt even remotely equipped to solve myself.
+
+Let's say, then, that this is the first bit of a life's work dedicated to my dad, real work devoid of any prestigious position and the associated self-doubt, pressure, or delusions of grandeur; a life dedicated to passionate ideas, to solving problems I care about and that really matter, to loving and caring for others or, as my dad would say, to ``being a mensch".
+May this dedication serve to hold me publicly accountable to that.
 Also I love you, mom.
 I dedicate and don't dedicate this and everything to come to you, too.
-%\vspace{12pt}
+
+\vspace{12pt}
 %\end{center}
-%\vfil\null
-%\end{dedication}
+\vfil\null
+\end{dedication}
 
@@
 
-%\begin{acknowledgements}
-%I would like to thank: Chris Hillar for laying down the groundwork and vetting all of my proofs many times over.
-He lent me a lot of his time and expertise for little in return.
-Fritz Sommer for advising me and pointing me toward a tractable problem to solve.
-The Berkeley Student Cooperative for the amazing experience living co-operatively in Berkeley.
+\begin{acknowledgements}
+First and foremost, I would like to thank Chris Hillar for clearing the path in his original work on the dictionary problem, and for vetting all of my proofs many, many times over.
+He asked for nothing in return for his time, attention, and mathematical expertise, and continues to extend this generosity to anyone nerdy enough to handle it.
+
+Thank you to Fritz Sommer for recommending my acceptance to Berkeley and for advising me as his student; although I eventually had to leave his lab to work on other problems of interest to me, he kindly lent me his time over the course of four years.
+To the other members of my thesis committee: Bruno Olshausen, Mike DeWeese, and Bin Yu, for their time and consideration over the years as well, and for approving this dissertation.
+My mom would have killed me if I didn't claim this degree, so they saved my life.
+To the graduate program manager of the Helen Wills Neuroscience Institute, Candace Groskreutz, for her kindness, patience, and support. 
+To the HWNI itself, the Redwood Center for Theoretical Neuroscience, and the friends I made in the lab and elsewhere; I hope we remain in each other's lives.
+
+Finally, a heartfelt thank you to Eric Weiss in particular for introducing me to the student co-ops, and to the Berkeley Student Cooperative (www.bsc.coop) for the work they do providing the amazing experience of living co-operatively in Berkeley.
+The co-ops changed my life, and I am forever grateful -- thank you so, so much to the hundreds of talented, creative, weird, passionate, intelligent, kind, thoughtful, absurd, inspiring people I have lived with throughout the years for all of the wonderful and weird times.
 CZ or die.
-%\end{acknowledgements}
+\end{acknowledgements}
 

### 2020-08-14 manuscripts/thesis/abstract.tex
almost done

@@
 Two formulations of the dictionary learning problem are considered. 
-The first seeks a dictionary for which each signal in a dataset is well-approximated by a linear superposition of a limited number of dictionary elements.
+The first seeks a dictionary for which each signal in a dataset is well-approximated by a linear superposition of only a limited number of dictionary elements.
 %he first seeks a dictionary admitting a sparse representation of limited support size for each signal in a dataset. 
@@
 This work serves to justify, in principle, dictionary learning in general as a means of discovering latent sparse structure in real data.
-Though much work remains to be done deriving criteria for use in practice, the theoretical tools developed herein should be of use to this end.
+Though much work remains to be done deriving criteria for use in practice, the theoretical tools developed here should be of use to this end.
 %The work closes with some open questions and directions for future research, seeded in part by the results of more practically-minded simulations. 

### 2020-08-14 manuscripts/thesis/discussion.tex
almost done

@@
 
-\subsection{Signal-to-Noise Ratio}
+\subsection{Reducing the required signal-to-noise ratio}
 
@@
 
-\subsection{Sample Complexity}
+\subsection{Reducing the required number of samples}
 
@@
 
-A close examination of how exactly Lemma \ref{NonEmptyLemma} is incorporated into the proof of Lem.~\ref{MainLemma} reveals, however, that looser constraints on $\mathcal{H}$ maintain compatibility with the argument to some degree.
-Assuming that the nodes of $\mathcal{H}$ are labeled in some order of non-increasing degree, if instead of the full SIP we require only that the stars $\cap \sigma(i)$ intersect at singletons for all $i \leq q$ for some positive $q$, we have that $\overline m \geq k|\mathcal{H}| / \deg(1)$ and, provided $\overline m < k|\mathcal{H}| / (\deg(1) - 1)$, the nonempty subset $J$ is of size equal to the largest number $p$ satisfying:
+A close examination of the proof of Lemma \ref{NonEmptyLemma} and its incorporation into the proof of Lem.~\ref{MainLemma} reveals, however, that looser constraints on $\mathcal{H}$ maintain compatibility with the argument to some degree.
+Assuming that the nodes of $\mathcal{H}$ are labeled in order of non-increasing degree, if instead of the full SIP we require only that the stars $\cap \sigma(i)$ intersect at singletons for all $i \leq q$ for some positive $q$, we have that $\overline m \geq k|\mathcal{H}| / \deg(1)$ and, provided $\overline m < k|\mathcal{H}| / (\deg(1) - 1)$, the nonempty subset $J$ is of size equal to the largest number $p$ satisfying:
 \begin{align*}
@@
 
-We may also elaborate on the probabilistic pigeonholing strategy outlined in the discussion following the proof of Thm.~\ref{DeterministicUniquenessTheorem}.
+We may also elaborate on the probabilistic pigeonholing strategy outlined in Sec.~\ref{DUT} following the proof of Thm.~\ref{DeterministicUniquenessTheorem}.
 The problem is to count the number of ways in which vectors supported in $S \in \mathcal{H}$ can be partitioned among supports in ${[\overline m] \choose k}$ without allocating $k$ or more to any individual one (in which case the logic of the proof fails to imply the result; we are interested in the probability that it doesn't).
@@
 
-\subsection{Dictionary learning via convex optimization}
+\subsection{Dictionary learning via $\ell_1$-norm minimization}
 

### 2020-08-14 manuscripts/thesis/thesis.tex
almost done

@@
 At the same time, I don't want to, because these results can't be matched to the time with him I traded to produce them, and it feels as though dedicating this work to him would in some sense be measuring his life up against them.
-
 The fact is that whatever may be the eventual butterfly effect of this work on the scientific ecosystem, these mathematical truths could have waited, arrived at their own pace, via myself or another, and I could have been more present with my dad as he waited patiently to die of cancer.
@@
 Yet it was more-so a feeling of desperation, of having to accomplish something and prove myself worthy of the position I had come to find myself in after 25+ years of schooling and a first failed project of my own design, that I feel largely drove these efforts.
-Truth be told, I initially had no particular interest in dictionary learning other than as a means to passing my qualifying exam; and by that time, I worried the brain was so dauntingly complex that I should feel lucky to have at least been offered a well-defined and arguably relevant problem in neuroscience to work on, particularly one I felt even remotely equipped to solve myself.
+Truth be told, I initially had no particular interest in dictionary learning other than as a means to passing my qualifying exam; and by that time, I worried the brain was so dauntingly complex that I should feel lucky to have at least been offered a well-defined problem of arguable relevance to neuroscience to work on, particularly one I felt even remotely equipped to solve myself.
 
-Let's say, then, that this is the first bit of a life's work dedicated to my dad, real work devoid of any prestigious position and the associated self-doubt, pressure, or delusions of grandeur; a life dedicated to passionate ideas, to solving problems I care about and that really matter, to loving and caring for others or, as my dad would say, to ``being a mensch".
+Let's say, then, that this is the first bit of a life's work dedicated to my dad, work devoid of any prestigious position and the associated self-doubt, pressure, or delusions of grandeur; a life dedicated to passionate ideas, to solving problems I actually care about and that really matter, to loving and caring for others or, as my dad would say, to ``being a mensch".
 May this dedication serve to hold me publicly accountable to that.

### 2020-08-17 manuscripts/thesis/thesis.tex
final

@@
 
-%\title{On the uniqueness and stability of dictionaries for sparse representation of noisy signals}
 \title{A Tale of Two Dictionary Learning Problems}
-\author{Charles Garfinkle}
+\author{Charles J. Garfinkle}
 \degreesemester{Summer}
@@
 \degree{Doctor of Philosophy}
-\chair{Friedrich Sommer}
-\othermembers{Bruno Olshausen \\
-  Mike Deweese \\
-  Bin Yu}
+\chair{Adjunct Professor Friedrich Sommer}
+\othermembers{Professor Bruno Olshausen \\
+  Associate Professor Mike Deweese \\
+  Chancellor's Professor Bin Yu}
 % For a co-chair who is subordinate to the \chair listed above
@@
 % Delete (or comment out) the \approvalpage line for the final version.
-\approvalpage
+%\approvalpage
 \copyrightpage
@@
 At the same time, I don't want to, because these results can't be matched to the time with him I traded to produce them, and it feels as though dedicating this work to him would in some sense be measuring his life up against them.
-The fact is that whatever may be the eventual butterfly effect of this work on the scientific ecosystem, these mathematical truths could have waited, arrived at their own pace, via myself or another, and I could have been more present with my dad as he waited patiently to die of cancer.
+The fact is that whatever may be the butterfly effect of this work on the scientific ecosystem, these mathematical truths could have waited, arrived at their own pace, via myself or another, and I could have been more present with my dad as he waited patiently to die of cancer.
 
@@
 
-Let's say, then, that this is the first bit of a life's work dedicated to my dad, work devoid of any prestigious position and the associated self-doubt, pressure, or delusions of grandeur; a life dedicated to passionate ideas, to solving problems I actually care about and that really matter, to loving and caring for others or, as my dad would say, to ``being a mensch".
+Let's say, then, that this is the first bit of a life's work dedicated to my dad, work devoid of any prestigious position and the associated self-doubt, pressure, or delusions of grandeur; a life dedicated to passionate ideas, to solving problems I care about and that really matter, to loving and caring for others or, as my dad would say, to ``being a mensch".
 May this dedication serve to hold me publicly accountable to that.
 Also I love you, mom.
-I dedicate and don't dedicate this and everything to come to you, too.
+I dedicate this and everything to come to you, too.
 

### 2020-08-17 manuscripts/thesis/abstract.tex
final

@@
 Two formulations of the dictionary learning problem are considered. 
-The first seeks a dictionary for which each signal in a dataset is well-approximated by a linear superposition of only a limited number of dictionary elements.
+The first seeks a dictionary for which each signal in a dataset is approximated up to some bounded error by a linear superposition of only a limited number of dictionary elements.
 %he first seeks a dictionary admitting a sparse representation of limited support size for each signal in a dataset. 
 %In this case, beyond an original extension of existing guarantees to the noisy regime, a theory of combinatorial designs is introduced to show that the dictionary and corresponding sparse codes are almost always identifiable up to an error commensurate with the noise even if the dictionary fails to satisfy the spark condition, its size is overestimated, or it induces only a polynomial number of distinct sparse supports in the data.
-In this case, existing guarantees are extended to the noisy regime to demonstrate that such dictionaries and the sparse representations they induce are almost always identifiable up to an error commensurate with the noise.
-Moreover, a theory of combinatorial designs is introduced to demonstrate this is the case even if the dictionary fails to satisfy the spark condition, the data are distributed over only a polynomial set of subspaces spanned by the dictionary, or (to some extent) even if the dictionary is overestimated in size.
+In this case, existing guarantees are extended to the noisy regime to show that such dictionaries and the sparse representations they induce are almost always identifiable up to an error commensurate with the approximation error.
+A theory of combinatorial designs is introduced furthermore to demonstrate this is so even if the dictionary fails to satisfy the spark condition, the data are distributed over only a polynomial set of subspaces spanned by the dictionary, or (to some extent) even if the dictionary is overestimated in size.
 
-The second formulation of the problem seeks a dictionary which minimizes the average number of dictionary elements required to approximate each signal in the dataset.
-The guarantees in this case are the first of their kind in both in the noiseless and noisy regimes and derive from the fact that, given sufficient data, this second problem actually reduces to an instance of the first.
+The second formulation of the problem seeks a dictionary which minimizes the average number of dictionary elements required to approximate each signal in the dataset up to some bounded error.
+The guarantees in this case, the first of their kind in both in the noiseless and noisy regimes, derive from the fact that this second problem actually reduces to an instance of the first.
 Importantly, in both cases, no constraints whatsoever are imposed on learned dictionaries beyond a natural upper bound on their size.

### 2020-08-17 manuscripts/thesis/thesis.tex
final

@@
 I want to dedicate this work to my dad.
-At the same time, I don't want to, because these results can't be matched to the time with him I traded to produce them, and it feels as though dedicating this work to him would in some sense be measuring his life up against them.
-The fact is that whatever may be the butterfly effect of this work on the scientific ecosystem, these mathematical truths could have waited, arrived at their own pace, via myself or another, and I could have been more present with my dad as he waited patiently to die of cancer.
+Yet it feels as though that would in some sense be measuring his life up against these results, which can't possibly match the time with him I traded to produce them.
+The fact is that whatever may be the eventual effect of this work on the scientific ecosystem, these mathematical truths could have waited.
+They could have arrived at their own pace, via myself or another, and I could have been more present with my dad as he waited patiently to die of cancer.
 
-I suppose that I couldn't really fathom what it actually meant for this to happen -- to never see or talk to or hug him again -- while the idea of putting original work out there, of crafting my own piece of the overwhelming puzzle that is neuroscience, was tantalizing.
-Yet it was more-so a feeling of desperation, of having to accomplish something and prove myself worthy of the position I had come to find myself in after 25+ years of schooling and a first failed project of my own design, that I feel largely drove these efforts.
+I suppose that I couldn't really fathom what it actually meant for this to happen -- to never see or talk to or hug him again -- while the idea of putting original work out there, of crafting my own theorems to lay down as pieces of the overwhelming puzzle that is neuroscience, was tantalizing.
+Yet I feel it was very much a sense of desperation, of having to accomplish something and prove myself worthy of the position I had come to find myself in after 25+ years of schooling and a first failed project, that largely drove these efforts.
 Truth be told, I initially had no particular interest in dictionary learning other than as a means to passing my qualifying exam; and by that time, I worried the brain was so dauntingly complex that I should feel lucky to have at least been offered a well-defined problem of arguable relevance to neuroscience to work on, particularly one I felt even remotely equipped to solve myself.
 
-Let's say, then, that this is the first bit of a life's work dedicated to my dad, work devoid of any prestigious position and the associated self-doubt, pressure, or delusions of grandeur; a life dedicated to passionate ideas, to solving problems I care about and that really matter, to loving and caring for others or, as my dad would say, to ``being a mensch".
-May this dedication serve to hold me publicly accountable to that.
-Also I love you, mom.
+So let's just say that this is the first bit of a life's work dedicated to my dad.
+A life of work uninfluenced by position or status and the associated self-doubt, pressure, or delusions of grandeur; one dedicated to passionate ideas, to solving problems I care about and that really matter, to loving and caring for others or, as my dad would say, to ``being a mensch".
+May this dedication serve to hold me accountable for that.
+Also, I love you, mom.
 I dedicate this and everything to come to you, too.
@@
 Finally, a heartfelt thank you to Eric Weiss in particular for introducing me to the student co-ops, and to the Berkeley Student Cooperative (www.bsc.coop) for the work they do providing the amazing experience of living co-operatively in Berkeley.
-The co-ops changed my life, and I am forever grateful -- thank you so, so much to the hundreds of talented, creative, weird, passionate, intelligent, kind, thoughtful, absurd, inspiring people I have lived with throughout the years for all of the wonderful and weird times.
+The co-ops changed my life, and I am forever grateful -- thank you so, so much to the hundreds of talented, creative, weird, passionate, intelligent, kind, thoughtful, absurd, and inspiring people I have lived with throughout the years for all of the wonderful and weird times.
 CZ or die.

### 2021-10-19 manuscripts/L1-norm/L1-norm.tex
new stuff

\documentclass[journal, onecolumn]{IEEEtran}

% *** MATH PACKAGES ***
\usepackage{amsmath, amssymb, amsthm} 
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{conjecture}{Conjecture}
\newtheorem{problem}{Problem}
\newtheorem{question}{Question}
\newtheorem{proposition}{Proposition}
\newtheorem{definition}{Definition}
\newtheorem{corollary}{Corollary}
\newtheorem{remark}{Remark}
\newtheorem{example}{Example}

\usepackage[pdftex]{graphicx}

% *** ALIGNMENT PACKAGES ***
\usepackage{array}
\usepackage{cite}
\usepackage{bm}

% correct bad hyphenation here
%\hyphenation{op-tical net-works semi-conduc-tor}

\begin{document}

\title{$\ell_1$-norm minimization}
\author{Charles~J.~Garfinkle}

\maketitle

\begin{theorem}[Noiseless recovery]
Suppose the $n \times m$ matrix $\mathbf{A}$ has $\|\mathbf{A}_j\|_2 = 1$ for $j = 1, \ldots, m$ and $L_2(\mathbf{A}) > 0$. Let $\mathbf{x}_i \in \mathbb{R}^m$ be such that $\mathbf{x}_i = c_i \mathbf{e}_i$ ($c_i \neq 0$) for $i = 1, \ldots, m$. Suppose $n \times m'$ matrix $\mathbf{B}$ with $\|\mathbf{B}_j\|_2 = 1$ for $j = 1, \ldots, m'$ and vectors $\mathbf{\overline x}_i, \ldots, \mathbf{\overline x}_m$ together solve:
\begin{align}\label{minsum}
\min \sum_{i = 1}^m \|\mathbf{\overline x}_i\|_1 \ \
\text{subject to} \ \ \mathbf{B}\mathbf{\overline x}_i = \mathbf{Ax}_i \ \ \text{for $i = 1, \ldots, m$}.
\end{align}
Then $\mathbf{A} = \mathbf{B}_S \mathbf{P}$ for some $S \subseteq [m']$ of size $m$ and $m \times m$ permutation matrix $\mathbf{P}$. 
\end{theorem}

\begin{proof}
Fixing $i$, we have
\begin{equation}
\|\mathbf{x}_i\|_1 = |c_i| \|\mathbf{Ae}_i\|_2 = \|\mathbf{Ax}_i\|_2 = \|\mathbf{B \overline x}_i\|_2 \leq \sum_j |\bar c_j| \|\mathbf{Be}_j\|_2 = \|\mathbf{\overline x}_i\|_1
\end{equation}
so that $\|\mathbf{\overline x}_i\|_1 = \|\mathbf{x}_i\|_1 + \varepsilon_i$ for some $\varepsilon_i \geq 0$. But also,
\begin{equation}
\sum_i \|\mathbf{x}_i\|_1 \geq \sum_i \|\mathbf{\overline x}_i\|_1 = \sum_i \left( \|\mathbf{x}_i\|_1 + \varepsilon_i \right)
\end{equation}
Hence $\sum_i \varepsilon_i \leq 0$. But since every $\varepsilon_i$ is non-negative, it must but that $\varepsilon_i = 0$ for $i = 1, \ldots, m$. Thus,
\begin{equation}
\|\mathbf{\overline x}_i\|_1 = \|\mathbf{x}_i\|_1 =  \|\mathbf{B \overline x}_i\|_2.
\end{equation}

\begin{lemma}\label{lemma1}
If $\|\mathbf{Tv}\|_2 = \|\mathbf{v}\|_1$ for $\mathbf{T}$ with $\|\mathbf{T}_j\|_2 = 1$ for all $j$ and $|\mathbf{T}_i \cdot \mathbf{T}_j| < 1$ for all $i, j$ then $\mathbf{v}$ has at most one non-zero entry. 
\end{lemma}

\begin{proof}
Let $\mathbf{v} = \sum_j c_j e_j$. Then,
\begin{equation}
\mathbf{Tv} 
= \sum_j c_j \mathbf{T}_j 
= \sum_j c_j \sum_i \mathbf{T}_{ij} \mathbf{e}_i 
= \sum_i \sum_j c_j \mathbf{T}_{ij} \mathbf{e}_i 
= \sum_i d_i \mathbf{e}_i \ \ \text{where } d_i 
= \sum_j c_j \mathbf{T}_{ij} 
\end{equation}
So that 
\begin{align}
\|\mathbf{Tv}\|_2^2 
&= \sum_i d_i^2 
= \sum_i \left( \sum_j c_j \mathbf{T}_{ij} \right)^2  \\
&= \sum_i \left( \sum_j \left(c_j \mathbf{T}_{ij} \right)^2 + \sum_j \sum_{k \neq j} \left(c_j \mathbf{T}_{ij} \right) \left( c_k \mathbf{T}_{ik} \right) \right) \\
&= \sum_j c_j^2 \sum_i \mathbf{T}_{ij}^2 + \sum_j \sum_{k \neq j} c_j c_k \sum_i \mathbf{T}_{ij} \mathbf{T}_{ik} \\
&= \sum_j c_j^2 + \sum_j \sum_{k \neq j} c_j c_k \left( \mathbf{T}_j \cdot \mathbf{T}_k \right)
\end{align}
where we have applied the formula $\left( \sum_i a_i \right)^2 = \sum_i a_i^2 + \sum_i \sum_{j \neq i} a_i a_j$. Next, observe 
\begin{equation}
\|\mathbf{v}\|_1^2 = \left( \sum_j |c_j| \right)^2 = \sum_j c_j^2 + \sum_j \sum_{k \neq j} |c_j| |c_k|
\end{equation}
so that$\|\mathbf{Tv}\|_2^2 = \|\mathbf{v}\|_1$ implies $\sum_i \sum_{j\neq i} \alpha_{ij} = 0$ for $\alpha_{ij} = |c_i| |c_j| - c_i c_j \left(\mathbf{T}_i \cdot \mathbf{T}_j \right)$. Now,
\begin{equation}
\alpha_{ij} 
\geq |c_i| |c_j| - |c_i c_j \left(\mathbf{T}_i \cdot \mathbf{T}_j \right)|
= |c_i| |c_j| \left(1 - |\mathbf{T}_i \cdot \mathbf{T}_j | \right)
\geq 0
\end{equation}
since $\|\mathbf{T}_j\|_2 = 1$ for all $j$. Thus $\alpha_{ij} = 0$ for all $i, j$ and we have $|c_i| |c_j| = |c_i| |c_j| |\mathbf{T}_i \cdot \mathbf{T}_j |$, or $ |c_i| |c_j| \left(1 - |\mathbf{T}_i \cdot \mathbf{T}_j | \right) = 0$. Since $|\mathbf{T}_i \cdot \mathbf{T}_j| < 1$, this implies $|c_i| |c_j| = 0$ for all $i, j$. Thus, $\mathbf{v}$ has at most one nonzero entry, since if $c_i \neq 0$ then $c_j = 0$ for all $j \neq i$.
\end{proof}

By Lemma \ref{lemma1}, either $\mathbf{B}$ has colinear columns or the $\mathbf{\overline x}_i$ are all 1-sparse vectors.

It is easy to see that if $\mathbf{B}$ has colinear columns, there exists some $S \subset [m']$ such that the submatrix $\mathbf{B}_S$ has no colinear columns and satisfies $\mathbf{B}_S \mathbf{\overline x}_i' = \mathbf{B} \mathbf{\overline x}_i$ for some $\mathbf{\overline x}_i' \in \mathbb{R}^{|S|}$ with $\|\mathbf{\overline x}_i'\|_1 = \|\mathbf{\overline x}_i\|_1$ for all $i$. Simply set $S = [m']$ and $\mathbf{\overline x}_i' = \mathbf{\overline x}_i$ and let $i=1$. Iterating through $j \neq i$, if $| \mathbf{B}_i \cdot \mathbf{B}_j| = 1$, let $S \to S \setminus \{j\}$ and $\overline c_i' \to \overline c_i' + \overline c_j \cdot \text{sgn}(\mathbf{B}_i \cdot \mathbf{B}_j)$. Induct on $i$.

By the above claim, there is some $S \subseteq [m']$ such that $\mathbf{B}_S$ has no colinear columns (i.e. $L_2(\mathbf{B}) > 0$) and satisfies the assumptions of the theorem for some $\mathbf{\overline x}_i' \in \mathbb{R}^{|S|}$ for which $\|\mathbf{\overline x}_i'\|_1 = \|\mathbf{\overline x}_i\|_1$ for all $i$. By the lemma, then, the $\mathbf{\overline x}_i'$ must all have at most one non-zero entry (i.e. they are 1-sparse) and the result follows by application of the $\ell_0$-norm theorem.

\end{proof}

\begin{theorem}[Noisy recovery]
Suppose the $n \times m$ matrix $\mathbf{A}$ has $\|\mathbf{A}_j\|_2 = 1$ for $j = 1, \ldots, m$ and $L_2(\mathbf{A}) > 0$. Let $\mathbf{x}_i \in \mathbb{R}^m$ be such that $\mathbf{x}_i = c_i \mathbf{e}_i$ ($c_i \neq 0$) for $i = 1, \ldots, m$. Suppose $n \times m'$ matrix $\mathbf{B}$ with $\|\mathbf{B}_j\|_2 = 1$ for $j = 1, \ldots, m'$ and vectors $\mathbf{\overline x}_i, \ldots, \mathbf{\overline x}_m$ together solve:
\begin{align}\label{minsum}
\min \sum_{i = 1}^m \|\mathbf{\overline x}_i\|_1 \ \
\text{subject to} \ \ \| \mathbf{B}\mathbf{\overline x}_i - \mathbf{Ax}_i \|_2 \leq \varepsilon \ \ \text{for $i = 1, \ldots, m$}.
\end{align}
Then $\mathbf{A} = \mathbf{B}_S \mathbf{P}$ for some $S \subseteq [m']$ of size $m$ and $m \times m$ permutation matrix $\mathbf{P}$.
\end{theorem}

\begin{proof}
By the reverse triangle inequality, we have for all $i$:
\begin{equation}
\varepsilon \geq \|\mathbf{Ax}_i - \mathbf{B \overline x}_i\|_2 \geq \left| \|\mathbf{Ax}_i \| - \|\mathbf{B \overline x}_i\|_2 \right| .
\end{equation}
So,
\begin{equation}\label{geq}
\|\mathbf{\overline x}_i\|_1 \geq \|\mathbf{B \overline x}_i\|_2 \geq \|\mathbf{Ax}_i \|_2 - \varepsilon = |c_i| - \varepsilon .
\end{equation}

It is trivial to show that letting $\mathbf{B}=\mathbf{A}$ and $\mathbf{\overline x}_i = \left(1 - \frac{\varepsilon}{ |c_i| }\right) \mathbf{x}_i$ for all $i$ is a particular solution satisfying the constraints, since then $\| \mathbf{B}\mathbf{\overline x}_i - \mathbf{Ax}_i \|_2 = \varepsilon$. Thus, a solution to the minimization problem must satisfy:
\begin{equation}
\sum_{i=1}^m \|\mathbf{\overline x}_i\|_1 \leq \sum_i \left( |c_i| - \varepsilon \right).
\end{equation}

Taken together with Eq. \ref{geq}, this implies that $\|\mathbf{\overline x}_i\|_1 = |c_i| - \varepsilon$ for all $i$, thus $\|\mathbf{\overline x}_i\|_1 = \|\mathbf{B \overline x}_i\|_2$ for all $i$. By Lemma \ref{lemma1}, either $\mathbf{B}$ has colinear columns or the $\mathbf{\overline x}_i$ are all 1-sparse vectors.

It is easy to see that if $\mathbf{B}$ has colinear columns, there exists some $S \subset [m']$ such that the submatrix $\mathbf{B}_S$ has no colinear columns and satisfies $\mathbf{B}_S \mathbf{\overline x}_i' = \mathbf{B} \mathbf{\overline x}_i$ for some $\mathbf{\overline x}_i' \in \mathbb{R}^{|S|}$ with $\|\mathbf{\overline x}_i'\|_1 = \|\mathbf{\overline x}_i\|_1$ for all $i$. Simply set $S = [m']$ and $\mathbf{\overline x}_i' = \mathbf{\overline x}_i$ and let $i=1$. Iterating through $j \neq i$, if $| \mathbf{B}_i \cdot \mathbf{B}_j| = 1$, let $S \to S \setminus \{j\}$ and $\overline c_i' \to \overline c_i' + \overline c_j \cdot \text{sgn}(\mathbf{B}_i \cdot \mathbf{B}_j)$. Induct on $i$.

By the above claim, there is some $S \subseteq [m']$ such that $\mathbf{B}_S$ has no colinear columns (i.e. $L_2(\mathbf{B}) > 0$) and satisfies the assumptions of the theorem for some $\mathbf{\overline x}_i' \in \mathbb{R}^{|S|}$ for which $\|\mathbf{\overline x}_i'\|_1 = \|\mathbf{\overline x}_i\|_1$ for all $i$. By the lemma, then, these $\mathbf{\overline x}_i'$ must all have at most one non-zero entry (i.e. they are 1-sparse). Therefore, there exist $\overline c_1, \ldots, \overline c_{\overline m}$ and a map $\pi: [m] \to [\overline m]$ such that 
\begin{equation}
\|c_i \mathbf{A}_i - \overline c_i \mathbf{B}_{\pi(i)}\|_2 \leq \varepsilon \ \ \text{for all $i$}
\end{equation}
We could end here by applying the noisy $\ell_0$-norm theorem; this would imply dictionary recovery up to an error commensurate with $\varepsilon$. Instead, we wil go further by using the fact that in this case we know $|\overline c_i| = |c_i| - \varepsilon$ for all $i$.

\begin{lemma}\label{lemma2}
$\|\mathbf{u} - \mathbf{v}\|_2 \leq \varepsilon$ for $\|\mathbf{v}\|_2 = \|\mathbf{u}\|_2 - \varepsilon \implies \|\mathbf{v}\|_2 \mathbf{u} = \|\mathbf{u}\|_2 \mathbf{v}$.
\end{lemma}

\begin{proof}
Observe that 
\begin{align}
\varepsilon^2 &\geq \|\mathbf{u}\|_2^2 +  \|\mathbf{v}\|_2^2 - 2 \left<\mathbf{u}, \mathbf{v}\right> \\
&=  \|\mathbf{u}\|_2^2 + \left( \|\mathbf{u}\|_2 - \varepsilon \right)^2 - 2 \left<\mathbf{u}, \mathbf{v}\right> \\
&=  2 \|\mathbf{u}\|_2^2 - 2\|\mathbf{u}\|_2 \varepsilon + \varepsilon^2 - 2 \left<\mathbf{u}, \mathbf{v}\right> \\
&\implies \left<\mathbf{u}, \mathbf{v}\right> \geq \|\mathbf{u}\|_2 \left( \|\mathbf{u}\|_2 - \varepsilon \right)
= \|\mathbf{u}\|_2 \|\mathbf{v}\|_2
\end{align}
But $\left<\mathbf{u}, \mathbf{v}\right>  \leq \|\mathbf{u}\|_2 \|\mathbf{v}\|_2$ always, thus $\left<\mathbf{u}, \mathbf{v}\right>  = \|\mathbf{u}\|_2 \|\mathbf{v}\|_2$. Therefore, 
\begin{align}
\| \|\mathbf{u}\|_2\mathbf{v} - \|\mathbf{v}\|_2\mathbf{u} \|_2^2 
= \left( \|\mathbf{u}\|_2 \|\mathbf{v}\|_2 \right)^2 +  \left( \|\mathbf{v}\|_2 \|\mathbf{u}\|_2 \right)^2 - 2  \|\mathbf{u}\|_2 \|\mathbf{v}\|_2 \left<\mathbf{u}, \mathbf{v}\right>
= 0
\end{align}
So $\|\mathbf{u}\|_2\mathbf{v} = \|\mathbf{v}\|_2\mathbf{u} $.
\end{proof}
By Lemma \ref{lemma2} (i.e. with $c_i\mathbf{A}_i = \mathbf{u}$ and $\overline c_i \mathbf{B}_{\pi(i)} = \mathbf{v}$), we have for all $i$ that $|c_i| \overline c_i \mathbf{B}_{\pi(i)} = |\overline c_i| c_i \mathbf{A}_i$, or 
\begin{equation}
\overline c_i' \mathbf{B}_{\pi(i)} = c_i \mathbf{A}_i \ \ \text{for all $i$}
\end{equation}
for $\overline c_i' = \text{sign}(\overline c_i) \cdot |c_i|$, and the result follows by application of the noiseless $\ell_0$-norm theorem. (Alternatively, we may directly infer $\mathbf{B}_{\pi(i)} = \text{sign}(c_i \overline c_j) \mathbf{A}_i$) and apply only the argument of the the $\ell_0$-norm proof establishing that $\pi$ is a permutation.)
\end{proof}

\end{document}

### 2021-10-19 manuscripts/L1_old/L1.tex
new stuff

\documentclass[journal, onecolumn]{IEEEtran}

% *** MATH PACKAGES ***
\usepackage{amsmath, amssymb, amsthm} 
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{conjecture}{Conjecture}
\newtheorem{problem}{Problem}
\newtheorem{question}{Question}
\newtheorem{proposition}{Proposition}
\newtheorem{definition}{Definition}
\newtheorem{corollary}{Corollary}
\newtheorem{remark}{Remark}
\newtheorem{example}{Example}

\usepackage[pdftex]{graphicx}

% *** ALIGNMENT PACKAGES ***
\usepackage{array}
\usepackage{cite}
\usepackage{bm}

% correct bad hyphenation here
%\hyphenation{op-tical net-works semi-conduc-tor}

\begin{document}

\title{$\ell_1$-norm minimization}
\author{Charles~J.~Garfinkle}

\maketitle

\begin{problem}\label{OptimizationProblem}
Find matrices $\mathbf{B}$ and vectors \mbox{$\mathbf{\overline x}^{(1)}, \ldots, \mathbf{\overline x}^{(N)}$} solving:
\begin{align}\label{minsum}
\min \sum_{i = 1}^N \|\mathbf{\overline x}^{(i)}\|_0 \ \
\text{subject to} \ \ \|\mathbf{z}^{(i)} - \mathbf{B}\mathbf{\overline x}^{(i)}\|_2 \leq \eta_0, \ \text{for all $i$}
\end{align}
by solving:
\begin{align}\label{minsum}
\min \sum_{i = 1}^N \|\mathbf{\overline x}^{(i)}\|_1 \ \
\text{subject to} \ \ \|\mathbf{z}^{(i)} - \mathbf{B}\mathbf{\overline x}^{(i)}\|_2 \leq \eta_1, \ \text{for all $i$}.
\end{align}
\end{problem}

\begin{proof}[Proof for $k=1$]
Since the only 1-uniform hypergraph with the SIP is $[m]$, which is obviously regular, we require only $\mathbf{x}^{(i)} = c_i \mathbf{e}_i$ for $i \in [m]$, with $c_i \neq 0$ to guarantee  linear independence. While we have yet to define $C_1$ generally, in this case we may set $C_1 = 1/ \min_{\ell \in [m]} |c_{\ell}|$. % L_2(\mathbf{A})  \min_{\ell \in [m]} |c_{\ell}| - \max_{\ell \in [m]} |c_\ell|$.

Fix $\mathbf{A} \in \mathbb{R}^{n \times m}$ satisfying $L_2(\mathbf{A}) > 0$, since here we have $2\mathcal{H} = {[m] \choose 2}$, and suppose some matrix $\mathbf{B}$ and vectors $\mathbf{\overline x}^{(i)} \in \mathbb{R}^{\overline m}$ have  $\|\mathbf{A}\mathbf{x}^{(i)} - \mathbf{B}\mathbf{\overline x}^{(i)}\|_2 \leq \varepsilon$ for all $i$. Note that $\mathbf{\overline x}^{(i)} \neq 0$, since otherwise we would reach the following contradiction: $\|\mathbf{A}_i \|_2 \leq C_1 |c_i| \|\mathbf{A}_i \|_2  \leq \|\mathbf{Ax}_i\|_2 \leq C_1\varepsilon \leq  (?) < \min_{\ell \in [m]} \|\mathbf{A}_\ell\|_2$. %< L_2(\mathbf{A}) \leq L_1(\mathbf{A}) = \min_{i \in [m]} \|\mathbf{A}_{i}\|_2$.

Let $\mathbf{\overline x}^{(i)} = \sum_{j=1}^m \overline c^{(i)}_j \mathbf{e}_j$ and let $\pi: [m] \to [\overline m]$ be the map $\pi(i) = \arg \max_j \overline c^{(i)}_j$. By the triangle inequality,
\begin{align}\label{1D}
\|c_i\mathbf{A}_i - \overline{c}^{(i)}_{\pi(i)}\mathbf{B}_{\pi(i)}\|_2  -  \|\sum_{k \neq \pi(i)} \mathbf{B}_k \overline c^{(i)}_k \|_2
\leq \|\mathbf{A}\mathbf{x}^{(i)} - \mathbf{B}\mathbf{\overline x}^{(i)}\|_2 
\leq \varepsilon
\end{align}

Hence, %assuming $\|\mathbf{B}\|_2 \leq \|\mathbf{A}\|_2$ for all $i \in [m]$,
\begin{align}\label{1D}
%(|c_i| - |\overline{c}^{(i)}_{\pi(i)}|) \|\mathbf{A}_i\|_2 
%= \|\mathbf{A}_i (c_i - \overline{c}^{(i)}_{\pi(i)})\|_2 
%\leq 
\|c_i\mathbf{A}_i - \overline{c}^{(i)}_{\pi(i)}\mathbf{B}_{\pi(i)}\|_2 
&\leq \varepsilon + \|\sum_{k \neq \pi(i)} \mathbf{B}_k \overline c^{(i)}_k \|_2 \\
%&= \varepsilon + \|\mathbf{B}_{\pi(j)} \overline c^{(i)}_{\pi(j)} + \sum_{k \neq \pi(i) \neq \pi(j)} \mathbf{B}_k \overline c^{(i)}_k\|_2 \\
%&\leq \varepsilon + \|\mathbf{B}_{\pi(j)} \overline c^{(i)}_{\pi(j)} - c_j\mathbf{A}_j\|_2 + \|c_j\mathbf{A}_j - \sum_{k \neq \pi(i) \neq \pi(j)} \mathbf{B}_k \overline c^{(i)}_k\|_2 \\
&\leq \varepsilon + \|\mathbf{B}\|_2 \| \mathbf{\overline x}^{(i)}_{\pi(i)=0} \|_1 \\
&= \varepsilon + \|\mathbf{A}\|_2 \| \mathbf{\overline x}^{(i)}_{\pi(i)=0} \|_1 \\
%&\leq \varepsilon + \|\mathbf{A}\|_2 (|c_i| - |\overline c_{\pi(i)}^{(i)}|)
%\leq \varepsilon +  \|\mathbf{\overline x}^{(i)} \|_1
%\leq \varepsilon + |c_i|
\end{align}

%Split x's in two, scale them, use A and B?

%Or for $m=2$, 
%\begin{align}\label{1D}
%\|c_1\mathbf{A}_1 - \overline{c}^{(1)}_{\pi(1)}\mathbf{B}_{\pi(1)}\|_2 
%&\leq \varepsilon + \| \mathbf{B}_k \overline c^{(1)}_{k \neq \pi(1)} \|_2 \\
%\|c_2\mathbf{A}_2 - \overline{c}^{(2)}_{\pi(2)}\mathbf{B}_{\pi(2)}\|_2 
%&\leq \varepsilon + \| \mathbf{B}_k \overline c^{(2)}_{k \neq \pi(2)} \|_2 
%\end{align}

%We now show that the second term is also controlled by $\varepsilon$ (due to the fact that the other columns of the dictionary must also be coded for?).

%\begin{align}\label{1D}
%|\overline{c}^{(j)}_\ell| \|c_{i}\mathbf{A}_{i} - \overline{c}^{(i)}_\ell \mathbf{B}_{\ell}\|_2 
%-
%|\overline{c}^{(i)}_\ell| \|c_{j}\mathbf{A}_{j} - \overline{c}^{(j)}_\ell\mathbf{B}_{\ell}\|_2 
%&\leq \varepsilon + \|\mathbf{A}\|_2 \| \mathbf{\overline x}^{(i)}_{\pi(i)=0} \|_1 \\
%&\leq \varepsilon + \|\mathbf{A}\|_2 (|c_i| - |\overline c_{\pi(i)}^{(i)}|)
%\leq \varepsilon +  \|\mathbf{\overline x}^{(i)} \|_1
%\leq \varepsilon + |c_i|
%\end{align}

%\begin{align}\label{1D}
%|\overline{c}^{(i)}_\ell| \|c_{j}\mathbf{A}_{j} - \overline{c}^{(j)}_\ell\mathbf{B}_{\ell}\|_2  + |\overline{c}^{(j)}_\ell| \|c_{i}\mathbf{A}_{i} - \overline{c}^{(i)}_\ell \mathbf{B}_{\ell}\|_2 
%&\leq (|\overline{c}^{(i)}_\ell|  +  |\overline{c}^{(j)}_\ell|) \varepsilon 
%+ |\overline{c}^{(j)}_\ell| \|\sum_{k \neq \ell} \mathbf{B}_k \overline c^{(i)}_k \|_2
%+ |\overline{c}^{(i)}_\ell| \|\sum_{k \neq \ell} \mathbf{B}_k \overline c^{(j)}_k \|_2 \\
%&\leq \varepsilon + \|\mathbf{A}\|_2 \| \mathbf{\overline x}^{(i)}_{\pi(i)=0} \|_1 \\
%&\leq \varepsilon + \|\mathbf{A}\|_2 (|c_i| - |\overline c_{\pi(i)}^{(i)}|)
%\leq \varepsilon +  \|\mathbf{\overline x}^{(i)} \|_1
%\leq \varepsilon + |c_i|
%\end{align}

We now show that $\pi$ is injective (in particular, a permutation if $\overline m = m$). Suppose that $\pi(i) = \pi(j) = \ell$ for some $i \neq j$ and $\ell$. Then we have: %Scaling and summing these inequalities by $|\overline{c}_{i}|$ and $|\overline{c}_{j}|$, respectively, and applying the triangle inequality to annihilate the terms in $\mathbf{B}_\ell$, we obtain:
\begin{align*}
(|\overline{c}^{(i)}_\ell| + |\overline{c}^{(j)}_\ell|) \left(\varepsilon + \|\mathbf{A}\|_2 \| \mathbf{\overline x}^{(i)}_{\pi(i)=0} \|_1 \right) 
%+ \|\mathbf{A}\|_2 \left( |\overline{c}^{(j)}_\ell| (|c_i| - |\overline{c}^{(i)}_\ell| ) + |\overline{c}^{(i)}_\ell| (|c_j| - |\overline{c}^{(j)}_\ell| ) \right)
&\geq |\overline{c}^{(i)}_\ell| \|c_{j}\mathbf{A}_{j} - \overline{c}^{(j)}_\ell\mathbf{B}_{\ell}\|_2  + |\overline{c}^{(j)}_\ell| \|c_{i}\mathbf{A}_{i} - \overline{c}^{(i)}_\ell \mathbf{B}_{\ell}\|_2 \nonumber \\
&\geq \|\mathbf{A}(\overline{c}^{(i)}_\ell c_{j} \mathbf{e}_{j} - \overline{c}^{(j)}_\ell c_{i}\mathbf{e}_{i})\|_2 \nonumber \\ 
&\geq \sqrt{2}  L_2(\mathbf{A}) \|\overline{c}^{(i)}_\ell c_{j} \mathbf{e}_{j} - \overline{c}^{(j)}_\ell c_{i}\mathbf{e}_{i}\|_2 \nonumber \\
&\geq  L_2(\mathbf{A}) (|\overline{c}^{(i)}_\ell| + |\overline{c}^{(j)}_\ell|) \min_{\ell \in [m]} |c_\ell |,
\end{align*}
hence, assuming $\|\mathbf{A}\|_2 = 1$,
\begin{align*}
\varepsilon  &\geq  L_2(\mathbf{A})  \min_{\ell \in [m]} |c_\ell | - \| \mathbf{\overline x}^{(i)}_{\pi(i)=0} \|_1 \\
&=
\end{align*}
contradicting our assumed upper bound on $\varepsilon$. Hence, the map $\pi$ is injective and so $\overline m \geq m$. %Setting $\overline J = \pi([m])$ and

Letting $\mathbf{P}$ and $\mathbf{D}$ be the $\overline m \times \overline m$ permutation and invertible diagonal matrices with, respectively, columns $\mathbf{e}_{\pi(i)}$ and $\frac{\overline{c}_i}{c_i}\mathbf{e}_i$ for $i \in [m]$ (otherwise, $\mathbf{e}_{i}$ for $i \in [\overline{m}] \setminus [m]$), we may rewrite \eqref{1D} to see that for all $i \in [m]$:
\begin{align*}
\|\mathbf{A}_i - (\mathbf{BPD})_i\|_2 
= \|\mathbf{A}_i - \frac{\overline{c}_i}{c_i}\mathbf{B}_{\pi(i)}\|_2 
\leq \frac{\varepsilon + |c_i|}{|c_i|} 
\leq C_1\varepsilon + 1.
\end{align*}
%\vspace{-.2 cm}
\end{proof}

\end{document}

### 2021-10-19 manuscripts/newthesis/discussion.tex
new stuff

@@
 
+%Specifically, given a dictionary and sparse codes purported to solve to Prob.~\ref{InverseProblem}, one checks that that they satisfy the corresponding constraints on $\mathbf{A}$ and the $\mathbf{x_i}$ given in the statement of Thm.~\ref{DeterministicUniquenessTheorem}.
+
 The guarantees concerning the identification of a dictionary and corresponding sparse codes of minimal average support size (Thm.~\ref{SLCopt}), which is the optimization problem of most interest to practitioners (Prob.~\ref{OptimizationProblem}), are to my knowledge the first of their kind in both the noise-free and noisy domains.
@@
 Furthermore, the derived scaling constants are explicit and computable; as such, there is an effective procedure that suffices to affirm if a proposed solution to these problems is indeed unique up to noise and inherent ambiguities, although it is not efficient in general.
-%Specifically, given a dictionary and sparse codes purported to solve to Prob.~\ref{InverseProblem}, one checks that that they satisfy the corresponding constraints on $\mathbf{A}$ and the $\mathbf{x_i}$ given in the statement of Thm.~\ref{DeterministicUniquenessTheorem}.
 
 %to the recovery of ``mouse neuronal activity representing location on a track \cite{agarwal2014spatially}
-
-The absence of any assumptions at all about dictionaries that solve Prob.~\ref{InverseProblem} was a major technical hurdle in proving Thm.~\ref{DeterministicUniquenessTheorem}. 
-This very general guarantee was sought because of the practical difficulty of ensuring that an algorithm maintain a dictionary satisfying the spark condition \eqref{SparkCondition} at each iteration, which (to my knowledge) has been an explicit or implicit assumption of all previous works except \cite{Hillar15}; indeed, even certifying a dictionary has this property is NP-hard \cite{tillmann2014computational}.
-
-Several results in the literature had to be combined to extend the guarantees derived in \cite{Hillar15} into the noisy regime.
-The main challenge was to generalize Lem.~\ref{MainLemma} to the case where the $k$-dimensional subspaces spanned by corresponding submatrices $\mathbf{A}_S$ and $\mathbf{B}_{\pi(S)}$ are assumed to be``close" but not identical.
-Unlike in \cite{Hillar15} where an inductive argument could be applied to the noiseless case, here it had to be explicitly demonstrated that this proximity relation is propagated through iterated intersections right down to the spans of the dictionary elements themselves.
-Lem.~\ref{DistanceToIntersectionLemma} was designed to encapsulate this fact, proven by appeal to a convergence guarantee for an alternating projections algorithm first proposed by von Neumann.
-This result, combined with a little known fact \eqref{eqdim} about the distance metric between subspaces, make up the more obscure components of the deduction.
-
-The proof of Lem.~\ref{MainLemma} diverges most significantly from the approach taken in \cite{Hillar15} by way of Lem.~\ref{NonEmptyLemma}, which utilizes a combinatorial design for support sets (the ``singleton intersection property") to reduce the deterministic sample complexity by an exponential factor.
-This constitutes a significant advance toward legitimizing dictionary learning in practice, since data must otherwise exhibit the exponentially many possible $k$-wise combinations of dictionary elements required by (to my knowledge) all previously published results; although an exponential number of samples per support is still required (unless $k$ is held fixed).
-The issue is that the map $\pi:\mathcal{H} \to {[m] \choose k}$ is surjective only when $\mathcal{H}$ is taken to be ${[m] \choose k}$, in which case one may proceed by induction as in \cite{Hillar15}, freely choosing supports in the codomain of $\pi$ to intersect over $(k-1)$ indices to then map back to some corresponding set of $(k-1)$ indices at the intersection of supports in the domain.
-Here, for $\mathcal{H} \subset {[m] \choose k}$, a bijection between indices had to instead be established by pigeonholing the image of $\pi$ under constraints imposed by the SIP, which was formulated specifically for this purpose.
-It just so happened that this more general argument for a non-surjective $\pi$ constrained by the SIP applied just as well to the situation where the number of dictionary elements $m$ is over-estimated (i.e.
-$\overline m > m$), in which case a one-to-one correspondence can be guaranteed between a subset of columns of $\mathbf{A}$ and $\mathbf{B}$ of a size simply expressed in terms of the width of each matrix and the regularity of $\mathcal{H}$.
-
-One of the mathematically significant achievements in \cite{Hillar15} was to break free from the constraint that the recovery matrix $\mathbf{B}$ satisfy the spark condition in addition to the generating dictionary $\mathbf{A}$.
-%, in contrast to all previously known uniqueness results which (to my knowledge) have all either explicitly or implicitly made this assumption.
-Here, it has been demonstrated that, in fact, even $\mathbf{A}$ need not satisfy the spark condition!
-Rather, $\mathbf{A}$ need only be injective on the union of subspaces with supports forming a regular $k$-uniform hypergraph satisfying the SIP (a distinguishing example is given in Sec.~\ref{Results}).
-This relaxation of constraints inspired the definition of the restricted matrix lower bound $L_{\mathcal{H}}$ in \eqref{Ldef}, which generalizes the well-known (see footnote \ref{ripfootnote}) restricted matrix lower bound $L_k$ to be in terms of a hypergraph $\mathcal{H}$, and an interesting object for further study in its own right.
-%(For instance, how hard is it to check that $L_\mathcal{H}(\mathbf{A}) > 0$?)
-%The absence of any restrictions on dictionaries solving Prob.~\ref{InverseProblem} is a major technical obstruction, but highly desirable because of the practical difficulty in ensuring that an algorithm maintain a dictionary satisfying the spark condition \eqref{SparkCondition} at each iteration; indeed, even certifying a dictionary has this property is NP-hard \cite{tillmann2014computational}.
-
-To reiterate, the methods applied here to prove Thm.~\ref{DeterministicUniquenessTheorem} yield the following results beyond a straightforward extension of those in \cite{Hillar15} to the noisy case:
-
-\begin{enumerate}
-\item A reduction in deterministic sample complexity: To identify the $n \times m$ generating dictionary $\mathbf{A}$, it is required in \cite{Hillar15} that $k{m \choose k}$ data points be sampled from each of the ${m \choose k}$ subspaces spanned by subsets of $k$ columns of $\mathbf{A}$.
-It is shown here that in fact it suffices to sample from at most $m$ such subspaces (see Cor.~\ref{DeterministicUniquenessCorollary}).
-%; thus, for fixed $k$, the deterministic sample complexity is polynomial in $m$.
-%HS15 was already poly for fixed k
-\item An extension of guarantees to the case where the number of dictionary elements is unknown: The results of \cite{Hillar15} only apply to the case where the matrix $\mathbf{B}$ has the same number of columns as $\mathbf{A}$.
-It is shown here that if $\mathbf{B}$ has at least as many columns as $\mathbf{A}$ then it contains (up to noise) a subset of the columns of $\mathbf{A}$.
-\item Relaxed requirements (no spark condition) on the generating matrix $\mathbf{A}$: Rather, $\mathbf{A}$ need only be injective on the union of subspaces with supports that form a regular uniform hypergraph satisfying the SIP.
-\end{enumerate}
-
-As it seemed to benefit a reviewer of this work, a brief discussion on how the deterministic sample complexity $N = |\mathcal{H}\left[|(k-1){m \choose k} + 1\right]$ derived here compares to those listed in the the top two rows listed in Table I of \cite{Hillar15} may be in order.
-To be clear, the theory developed here is strictly more general, since $\mathcal{H}$ can always be taken to be ${[m] \choose k}$.
-The point of difference in this comparison is the assumed set of supports for sparse codes, which is always ${[m] \choose k}$ in \cite{Hillar15}, whereas here it can be assumed to be any regular $k$-uniform hypergraph that satisfies the SIP.
-By row, %, assuming for our results that sufficient data have been sampled from all supports in a hypergraph H satisfying the SIP:
-\begin{enumerate}
-\item[I.] The result here improves upon the listed $k{m \choose k}^2$ by an exponential factor, since for every $k < m$ there exists a regular $k$-uniform hypergraph $\mathcal{H}$ with $|\mathcal{H}| = m$ satisfying the SIP.
-\item[II.] The authors in \cite{Hillar15} have applied measure-theoretic arguments to achieve $(k+1){m \choose k}$ with almost-certainty (i.e.
-with probability one), a factor of $m$ reduction over that for which certainty can alternatively be guaranteed here.
-%\item[III.] A direct comparison cannot be made because it is an open question as to the probability that a random set of supports satisfies the SIP.
-This would be an interesting problem for the community to solve; regardless, the result of \cite{Hillar15} is still implied by the more general theory given here.
-%\item[IV.] The result here is $|\mathcal{H}\left[|(k-1){m \choose k} + 1\right]$ with probability one compared to $(k+1){m \choose k}$ with probability one.
-In this case the sample complexity stated in \cite{Hillar15} is marginally better, but it relies on a noise-free technicality unique to their assumption $\mathcal{H} = {m \choose k}$.
-%differs in flavor: their $\mathbf{x_i}$ are assumed to be distributed as $(k+1)$ samples per support for every support of size $k \in [m]$, whereas here it is assumed that $(k-1){m \choose k}$ codes $\mathbf{x_i}$ are distributed over each support in some hypergraph $\mathcal{H}$ satisfying the SIP.
-%\item[V.] Again, a direct comparison cannot be made for the reason stated for row III.
-\end{enumerate}
 

### 2021-10-19 manuscripts/newthesis/introduction.tex
new stuff

@@
 
-Sparse coding is a common modern signal processing technique that views each of $N$ observed $n$-dimensional signal samples as a (noisy) linear combination of at most $k$ elementary waveforms drawn from some unknown ``dictionary" of size $m \ll N$ (see \cite{Zhang15} for a comprehensive review).
-%\IEEEPARstart{A}{}common modern approach to pattern analysis in signal processing is to view each of $N$ observed $n$-dimensional signal samples as a (noisy) linear combination of at most $k$ elementary waveforms drawn from some unknown ``dictionary" of size $m \ll N$ (see \cite{Zhang15} for a comprehensive review).
+\section{Sparse Representations}
+
+Sparse coding is a common modern signal processing technique that views each of $N$ observed $n$-dimensional signal samples as a (noisy) linear combination of at most $k$ elementary waveforms drawn from a``dictionary" of size $m \ll N$.
+% (see \cite{Zhang15} for a comprehensive review).
+
+\section{Dictionary Learning}
+
 Optimizing dictionaries subject to this and related sparsity constraints has revealed seemingly characteristic sparse structure in several signal classes of current interest (e.g., in vision \cite{wang2015sparse}).
@@
 While several algorithms have recently been proposed to provably recover unique dictionaries under specific conditions (see \cite[Sec.~I-E]{Sun16} for a summary of the state-of-the-art), few theorems can be invoked to justify the consistency of inference under this model of data more broadly.
-To our knowledge, a universal guarantee of the uniqueness and stability of learned dictionaries and the sparse representations they induce over noisy data has yet to appear in the literature.
+To my knowledge, the results of this work constitute the first  universal guarantee of the uniqueness and stability of learned dictionaries and the sparse representations they induce over noisy data to appear in the literature.
 
-\section{Transform Coding}
-
-\section{Sparse Representations}
-
-\section{Analytic vs. Learned Dictionaries for Sparse Representation}
-
-\section{Thesis Outline}
+\section{Summary of Results}
 

### 2021-10-19 manuscripts/newthesis/proofs.tex
new stuff

@@
-\chapter{Proofs}
+\chapter{Theory and Methods}
 
@@
 
+\section{Proof of Main Lemma}\label{proofs}
+
+We prove Lem.~\ref{MainLemma} after the following auxiliary lemmas.  % stating and proving some auxiliary lemmas. 
+%First, note that since $\|\mathbf{A}\mathbf{x}\|_2 \leq \max_j\|\mathbf{A}_j\|_2\|\mathbf{x}\|_1$ and $\|\mathbf{x}\|_1 \leq \sqrt{k} \|\mathbf{x}\|_2$ for $k$-sparse $\mathbf{x}$, by \eqref{Ldef} we have the following frequently applied inequality:
+%\begin{align}\label{delrho}
+%L_{k'}(\mathbf{A}) \leq  \max_j\|\mathbf{A}_j\|_2 \ \ \text{for all $k' \leq 2k$}.
+%\end{align}
+
+% and then sketch the proofs of Thm.~\ref{robustPolythm} and Cor.~\ref{ProbabilisticCor}.
+
+%\begin{lemma}\label{spanIntersectionLemma}
+%Let $\mathbf{M} \in \mathbb{R}^{n \times m}$. If every $2k$ columns of $\mathbf{M}$ are linearly independent, then for any $F \subseteq {[m] \choose k}$:
+%\begin{align*}
+%\text{\rmfamily span}\{\mathbf{M}_{\cap F}\}  = \bigcap_{S \in F} \text{\rmfamily span}\{\mathbf{M}_S\}.
+%\end{align*}
+%\end{lemma}
+%\begin{proof}
+%Using induction on $|F|$, it is enough to prove the lemma when $|F| = 2$; but this case follows directly from the assumption.
+%\end{proof}
+
+\begin{lemma}\label{spanIntersectionLemma}
+If $f: V \to W$ is injective, then $f\left(\cap_{i=1}^\ell V_i \right) =  \cap_{i=1}^\ell f\left(V_i\right)$ for any $V_1, \ldots, V_\ell \subseteq V$. ($f(\emptyset):=\emptyset$.)
+%In particular, if for some $E \in 2^{[m]}$ the map $M \in \mathbb{R}^{n \times m}$ is injective on $\cup_{S \in \mathcal{H}} \text{span}\{e_i\}_{i \in S}$ then $\text{span}\{ M_{\cap_{S \in \mathcal{H}} S} \} = \cap_{S \in \mathcal{H}} \text{span}\{M_S\}$.
+\end{lemma}
+\begin{proof}
+By induction, it is enough to prove the case $\ell = 2$.
+Clearly, for any map $f$, if $w \in f(U \cap V)$ then $w \in f(U)$ and $w \in f(V)$; hence, $w \in f(U) \cap f(V)$.
+If $w \in f(U) \cap f(V)$, then $w \in f(U)$ and $w \in f(V)$; thus, $w = f(u) = f(v)$ for some $u \in U$ and $v \in V$, implying $u = v$ by injectivity of $f$.
+It follows that $u \in U \cap V$ and $w \in f(U \cap V)$.
+\end{proof}
+In particular, if a matrix $\mathbf{A}$ satisfies $L_{2\mathcal{H}}(\mathbf{A}) > 0$, then taking $V$ to be the union of subspaces consisting of vectors with supports in $2\mathcal{H}$, we have $\bm{\mathcal{A}}_{\cap \mathcal{G}} = \cap \bm{\mathcal{A}}_\mathcal{G}$ for all $\mathcal{G} \subseteq \mathcal{H}$.
+% \vspace{-.4 cm}
+
+\begin{lemma}\label{DistanceToIntersectionLemma}
+Let $\mathcal{V} = \{V_i\}_{i=1}^k$ be a set of two or more subspaces of $\mathbb{R}^m$, and set $V = \cap \mathcal{V} $.
+For  $\mathbf{u} \in \mathbb{R}^m$, we have (recall Defs.~\ref{dDef}~\&~\ref{FriedrichsDefinition}):
+\begin{align}\label{DTILeq}
+\text{\rmfamily dist}(\mathbf{u}, V) \leq \frac{1}{1 - \xi(\mathcal{V})} \sum_{i=1}^k \text{\rmfamily dist}(\mathbf{u}, V_i).
+\end{align}
+\end{lemma}
+\begin{proof} 
+% When $V = \{\mathbf{0}\}$, the result is trivial, so suppose otherwise.  
+Recall the projection onto the subspace $V \subseteq \mathbb{R}^m$ is the mapping $\Pi_V: \mathbb{R}^m \to V$ that associates with each $\mathbf{u}$ its unique nearest point in $V$; i.e., $\|\mathbf{u} - \Pi_V\mathbf{u}\|_2 = \text{\rmfamily dist}(\mathbf{u}, V)$.
+By repeatedly applying the triangle inequality, we have:
+\begin{align}\label{f}
+\|\mathbf{u} - &\Pi_V\mathbf{u}\|_2 
+\leq \|\mathbf{u} - \Pi_{V_k} \mathbf{u}\|_2 + \|\Pi_{V_k}  \mathbf{u} - \Pi_{V_k}\Pi_{V_{k-1}}\mathbf{u}\|_2 \nonumber \\
+&\ \ \ \ \ \ \ \ \ \ \ + \cdots + \|\Pi_{V_k} \Pi_{V_{k-1}}\cdots \Pi_{V_1} \mathbf{u} - \Pi_V \mathbf{u}\|_2 \nonumber \\
+&\leq  \sum_{\ell=1}^k \|\mathbf{u} - \Pi_{V_{\ell}} \mathbf{u}\|_2 
++ \|(\Pi_{V_k}\cdots\Pi_{V_{1}} - \Pi_V) \mathbf{u}\|_2,
+\end{align}
+where we have also used that the spectral norm of the orthogonal projections $\Pi_{V_{\ell}}$ satisfies $\|\Pi_{V_{\ell}}\|_2 \leq 1$ for all $\ell$.
+
+It remains to bound the second term in \eqref{f} by $\xi(\mathcal{V}) \|\mathbf{u} - \Pi_V\mathbf{u}\|_2$.
+First, note that $\Pi_{V_\ell} \Pi_V = \Pi_V$ and $\Pi_V^2 = \Pi_V$, so we have $\|(\Pi_{V_k} \cdots \Pi_{V_1} - \Pi_V) \mathbf{u} \|_2
+= \| ( \Pi_{V_k} \cdots\Pi_{V_1} - \Pi_V ) (\mathbf{u} - \Pi_V\mathbf{u})\|_2$. % \leq z\|\mathbf{u} - \Pi_V\mathbf{u}\|_2$.
+Consequently, inequality \eqref{DTILeq} follows from \cite[Thm.~9.33]{Deutsch12}:
+\begin{align}
+\|\Pi_{V_k}\Pi_{V_{k-1}}\cdots\Pi_{V_1} \mathbf{x} - \Pi_V\mathbf{x}\|_2 \leq z \|\mathbf{x}\|_2, \ \ \text{for all } \mathbf{x},
+\end{align}
+with \mbox{$z^2= 1 - \prod_{\ell =1}^{k-1}(1-z_{\ell}^2)$} and \mbox{$z_{\ell} = \cos\theta\left(V_{\ell}, \cap_{s=\ell+1}^k V_s\right)$} (recall $\theta$ from Def.~\ref{FriedrichsDefinition}), after substituting $\xi(\mathcal{V})$ for $z$ and rearranging terms.
+\end{proof}
+\begin{lemma}\label{NonEmptyLemma} 
+Fix an $r$-regular hypergraph $\mathcal{H} \subseteq 2^{[m]}$ satisfying the SIP.
+If the map $\pi: \mathcal{H} \to 2^{[\overline m]}$ has $\sum_{S \in \mathcal{H}} |\pi(S)| \geq \sum_{S \in \mathcal{H}} |S|$ and:
+\begin{align}\label{cond}
+	|\cap \pi(\mathcal{G})| \leq |\cap \mathcal{G} |,\ \ \   \text{for } \mathcal{G} \in {\mathcal{H} \choose r} \cup {\mathcal{H} \choose r+1},
+\end{align}
+%
+then $\overline m \geq m$; and if $\overline m  (r-1) < mr$, the map $i \mapsto \cap_{S \in \sigma(i)} \pi(S)$ is an injective function to $[\overline m]$ from some $J \subseteq [m]$ of size $m - (r-1)(\overline m - m)$ (recall $\sigma$ from Def.~\ref{sip}).
+%In particular, if $\overline m = m$ then $\pi$ is induced by a permutation on $[m]$.
+\end{lemma}
+
+\begin{proof}
+Consider the following set: $T_1 := \{(i, S): i \in \pi(S), S \in \mathcal{H}\}$, which numbers $|T_1| = \sum_{S \in \mathcal{H}} |\pi(S)| \geq \sum_{S \in \mathcal{H}} |S| = \sum_{i \in [m]} \deg_\mathcal{H}(i) = mr$ by $r$-regularity of $\mathcal{H}$.
+Note that $|T_1| \leq \overline m r$; otherwise, pigeonholing the tuples of $T_1$ with respect to their $\overline m$ possible first elements would imply that more than $r$ of the tuples in $T_1$ share the same first element.
+This cannot be the case, however, since then some $\mathcal{G} \in {\mathcal{H} \choose r+1}$ formed from any $r+1$ of their second elements would satisfy $\cap \pi(\mathcal{G}) \neq 0$; hence, $|\cap \mathcal{G}| \neq 0$ by \eqref{cond}, contradicting $r$-regularity of $\mathcal{H}$.
+It follows that $\overline m \geq m$.
+
+Suppose now that $\overline m (r-1) < mr$, so that $p := mr - \overline m (r-1)$ is positive and $|T_1| \geq \overline m (r - 1) + p$.
+Pigeonholing $T_1$ into $[\overline m]$ again, there are at least $r$ tuples in $T_1$ sharing some first element; that is, for some $\mathcal{G}_1 \subseteq \mathcal{H}$ of size $|\mathcal{G}_1| \geq r$, we have $|\cap \pi(\mathcal{G}_1)| \geq 1$ and (by \eqref{cond}) $|\cap \mathcal{G}_1| \geq 1$.
+Since no more than $r$ tuples of $T_1$ can share the same first element, we in fact have $|\mathcal{G}_1| = r$.
+It follows by $r$-regularity that $\mathcal{G}_1$ is a star of $\mathcal{H}$; hence, $|\cap \mathcal{G}_1| = 1$ by the SIP and $|\cap \pi(\mathcal{G}_1)|  = 1$ by \eqref{cond}.
+
+If $p=1$, then we are done.
+Otherwise, define $T_2 := T_1 \setminus \{(i,S) \in T_1: i = \cap \pi(\mathcal{G}_1)\}$, which contains $|T_2| = |T_1| - r \geq (\overline m - 1)(r-1) + (p-1)$ ordered pairs having $\overline m - 1$ distinct first indices.
+Pigeonholing $T_2$ into $[\overline m - 1]$ and repeating the above arguments produces the star $\mathcal{G}_2 \in {\mathcal{H} \choose r}$ with intersection $\cap \mathcal{G}_2$ necessarily distinct (by $r$-regularity) from $\cap \mathcal{G}_1$.
+Iterating this procedure $p$ times in total yields the stars $\mathcal{G}_i$ for which $\cap\mathcal{G}_i \mapsto \cap \pi(\mathcal{G}_i)$ defines an injective map to $[\overline m]$ from $J = \{\cap \mathcal{G}_1, \ldots, \cap \mathcal{G}_p\} \subseteq [m]$.
+\end{proof}
+
+\begin{proof}[Proof of Lem.~\ref{MainLemma}]
+%We will show that the bound \eqref{GapUpperBound} trickles through the intersection semi-lattices of $\{\bm{\mathcal{A}}_S\}_{S \in \mathcal{H}}$ and $\{\bm{\mathcal{B}}_{\overline S}\}_{\overline S \in \pi(\mathcal{H})}$ to yield \eqref{MainLemmaBPD} by virtue of the SIP.
+We begin by showing that $\dim(\bm{\mathcal{B}}_{\pi(S)}) = \dim(\bm{\mathcal{A}}_S)$ for all $S \in \mathcal{H}$.
+Note that since $\|\mathbf{A}\mathbf{x}\|_2 \leq \max_j\|\mathbf{A}_j\|_2\|\mathbf{x}\|_1$ and $\|\mathbf{x}\|_1 \leq \sqrt{k} \|\mathbf{x}\|_2$ for all $k$-sparse $\mathbf{x}$, by \eqref{Ldef} we have $L_2(\mathbf{A}) \leq \max_j\|\mathbf{A}_j\|_2$ and therefore (as $0 \leq \xi < 1$) the right-hand side of \eqref{GapUpperBound} is less than one.
+From \eqref{dimLem}, we have $|\pi(S)| \geq \dim(\bm{\mathcal{B}}_{\pi(S)}) \geq \dim(\bm{\mathcal{A}}_S) = |S|$, the final equality holding by injectivity of $\mathbf{A}_S$.
+As $|\pi(S)| = |S|$, the claim follows.
+Note, therefore, that $\mathbf{B}_{\pi(S)}$ has full-column rank for all $S \in \mathcal{H}$.
+
+We next demonstrate that \eqref{cond} holds.
+Fixing $\mathcal{G} \in {\mathcal{H} \choose r} \cup {\mathcal{H} \choose r+1}$, it suffices to show that $d(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}, \bm{\mathcal{A}}_{\cap \mathcal{G}} ) < 1$, since by \eqref{dimLem} we then have $|\cap \pi(\mathcal{G})| = \dim(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}) \leq \dim(\bm{\mathcal{A}}_{\cap \mathcal{G}}) = |\cap \mathcal{G}|$, with equalities from the full column-ranks of $\mathbf{A}_{S}$ and $\mathbf{B}_{\pi(S)}$ for all $S \in \mathcal{H}$.\footnote{Note that if ever $\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})} \neq /bfseries 0$ while $\cap \mathcal{G} = \emptyset$, we would have $d(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}, \bm 0 ) = 1$.
+However, that leads to a contradiction.} Observe that $d(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}, \bm{\mathcal{A}}_{\cap \mathcal{G}}  )
+\leq d\left( \cap \bm{\mathcal{B}}_{\pi(\mathcal{G})}, \cap \bm{\mathcal{A}}_\mathcal{G} \right)$ by \eqref{UsubU}, since trivially $\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})} \subseteq \cap \bm{\mathcal{B}}_{\pi(\mathcal{G})}$ and also $\bm{\mathcal{A}}_{\cap \mathcal{G}} = \cap \bm{\mathcal{A}}_\mathcal{G}$ by Lem.~\ref{spanIntersectionLemma}.
+Recalling Def.~\ref{dDef} and applying Lem.~\ref{DistanceToIntersectionLemma} yields:
+\begin{align}
+d\left( \cap \bm{\mathcal{B}}_{\pi(\mathcal{G})}, \cap \bm{\mathcal{A}}_\mathcal{G} \right)
+&\leq \max_{\mathbf{u} \in \cap \bm{\mathcal{B}}_{\pi(\mathcal{G})}, \ \|\mathbf{u}\|_2 \leq 1} \sum_{S \in \mathcal{G}} \frac{ \text{\rmfamily dist}\left( \mathbf{u},\bm{\mathcal{A}}_{S} \right) }{ 1 - \xi( \bm{\mathcal{A}}_\mathcal{G} ) } \nonumber \\
+&= \sum_{S \in \mathcal{G}} \frac{ d\left( \cap \bm{\mathcal{B}}_{\pi(\mathcal{G})},\bm{\mathcal{A}}_{S} \right) }{ 1 - \xi( \bm{\mathcal{A}}_\mathcal{G} ) }, \nonumber
+\end{align}
+passing the maximum through the sum.
+Since $\cap \bm{\mathcal{B}}_{\pi(\mathcal{G})} \subseteq \bm{\mathcal{B}}_{\pi(S)}$ for all $S \in \mathcal{G}$, by \eqref{UsubU} the numerator of each term in the sum above is bounded by \mbox{$d\left( \bm{\mathcal{B}}_{\pi(S)},\bm{\mathcal{A}}_{S} \right) = d\left(\bm{\mathcal{A}}_{S}, \bm{\mathcal{B}}_{\pi(S)} \right) \leq \varepsilon$}, with the equality from \eqref{eqdim} since $\dim(\bm{\mathcal{B}}_{\pi(S)}) = \dim(\bm{\mathcal{A}}_S)$.
+Thus, altogether:
+\begin{align}\label{last}
+d(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}, \bm{\mathcal{A}}_{\cap \mathcal{G}} )
+\leq \frac{|\mathcal{G}| \varepsilon}{1 - \xi( \bm{\mathcal{A}}_\mathcal{G} )}
+\leq \frac{C_2 \varepsilon}{\max_j\|\mathbf{A}_j\|_2},
+\end{align}
+recalling the definition of $C_2$ in \eqref{Cdef2}.
+Lastly, since $C_2 \varepsilon < L_2(\mathbf{A}) \leq \max_j\|\mathbf{A}_j\|_2$, we have $d(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}, \bm{\mathcal{A}}_{\cap \mathcal{G}} ) \leq 1$ and therefore \eqref{cond} holds.
+
+%Keeping in mind that $d(U',V) \leq d(U,V)$ whenever $U' \subseteq U$ and applying (in order) Lem.~\ref{spanIntersectionLemma}, Lem.~\ref{DistanceToIntersectionLemma}, \eqref{eqdim}, \eqref{GapUpperBound}, and \eqref{Cdef2} gives:
+%\begin{align}\label{randoml}
+%d(&\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}, \bm{\mathcal{A}}_{\cap \mathcal{G}}  ) 
+%\leq d\left( \cap \bm{\mathcal{B}}_{\pi(\mathcal{G})}, \cap \bm{\mathcal{A}}_\mathcal{G} \right)
+%\leq \sum_{T \in \mathcal{G}} \frac{ d\left( \cap \bm{\mathcal{B}}_{\pi(\mathcal{G})},\bm{\mathcal{A}}_{T} \right) }{ 1 - \xi( \bm{\mathcal{A}}_\mathcal{G} ) } \nonumber \\
+%&\leq \sum_{T \in \mathcal{G}} \frac{ d\left( \bm{\mathcal{B}}_{\pi(T)},\bm{\mathbf{A}}_{T} \right) }{ 1 - \xi( \bm{\mathcal{A}}_\mathcal{G} ) }
+%\leq \frac{|\mathcal{G}| \varepsilon}{1 - \xi( \bm{\mathcal{A}}_\mathcal{G} )} 
+%\leq \frac{C_2 \varepsilon}{\max_j\|\mathbf{A}_j\|_2},
+%\end{align}
+%
+%which is less than one, since $C_2 \varepsilon < L_2(\mathbf{A}) \leq \max_j\|\mathbf{A}_j\|_2$.
+
+Applying Lem.~\ref{NonEmptyLemma}, the association $i \mapsto \cap_{S \in \sigma(i)} \pi(S)$ is an injective map $\overline \pi: J \to [\overline m]$ for some $J \subseteq [m]$ of size $m - (r-1)(\overline m - m)$, and $\mathbf{B}_{\overline \pi(i)} \neq \mathbf{0}$ for all $i \in J$ since the columns of $\mathbf{B}_{\pi(S)}$ are linearly independent for all $S \in \mathcal{H}$.
+Letting $\overline \varepsilon := C_2 \varepsilon / \max_i \|\mathbf{A}_i\|_2$, it follows from \eqref{eqdim} and \eqref{last} that $d\left( \bm{\mathcal{A}}_i, \bm{\mathcal{B}}_{\overline \pi(i)} \right) = d\left(\bm{\mathcal{B}}_{\overline \pi(i)},  \bm{\mathcal{A}}_i \right)  \leq \overline \varepsilon$ for all $i \in J$.
+%Fixing $\overline \varepsilon = C_2\varepsilon$ and letting $c_i = \|\mathbf{A}_i\|_2^{-1}$, we thus have that for each $\mathbf{e}_i \in \mathbb{R}^m$ with $i \in J$ there exists some $\overline{c}_i \in \mathbb{R}$ such that $\|c_i\mathbf{A}\mathbf{e}_i - \overline{c}_i \mathbf{B}\mathbf{e}_{\overline \pi(i)}\|_2 \leq \overline \varepsilon < L_2(\mathbf{A}) \min_{i\in J} |c_i|$.
+But this is exactly the supposition in \eqref{1D}, and the result follows from the case $k=1$ in Sec.~\ref{DUT} applied to the submatrix $\mathbf{A}_J$.
+Setting $c_i := \|\mathbf{A}_i\|_2^{-1}$ so that $\|c_i\mathbf{Ae}_i\|_2 = 1$, by Def.~\ref{dDef} for all $i \in J$:
+\begin{align*}
+\min_{\overline c_i \in \mathbb{R}} \|c_i\mathbf{Ae}_i - \overline c_i \mathbf{Be}_{\overline \pi(i)} \|_2
+\leq d\left( \bm{\mathcal{A}}_i, \bm{\mathcal{B}}_{\overline \pi(i)} \right)
+\leq \overline \varepsilon,
+%&= \max_{\bm{u} \in \bm{\mathcal{A}}_i, \|\bm{u}\|_2 \leq 1} \text{dist}\left(\bm{u}, \bm{\mathcal{B}}_{\overline \pi(i)} \right) \\
+%&\geq  \text{dist}\left(c_i\bm{Ae}_i, \mathbf{Be}_{\overline \pi(i)} \right) \\
+%&= \min_{\overline c_i \in \mathbb{R}} \|c_i\bm{Ae}_i - \overline c_i \mathbf{Be}_{\overline \pi(i)} \|_2
+\end{align*}
+%
+for $\overline \varepsilon < L_2(\mathbf{A})\min_{i \in [m]}|c_i|$.
+But this is exactly the supposition in \eqref{1D}, with $J$ and $\overline \varepsilon$ in place of $[m]$ and $\varepsilon$, respectively.
+The same arguments of the case $k=1$ in Sec.~\ref{DUT} can then be made to show that for any $\overline m \times \overline m$ permutation and invertible diagonal matrices $\mathbf{P}$ and $\mathbf{D}$ with, respectively, columns $\mathbf{e}_{\pi(i)}$ and $\frac{\overline{c}_i}{c_i}\mathbf{e}_i$ for $i \in J$ (otherwise, $\mathbf{e}_{i}$ for $i \in [\overline{m}] \setminus J$), we have $\|\mathbf{A}_i - (\mathbf{B}\mathbf{PD})_i \|_2 \leq \overline  \varepsilon / |c_i|  \leq C_2 \varepsilon$ for all $i \in J$.
+\end{proof}
+
 \section{Discussion}
 
-TODO
+The absence of any assumptions at all about dictionaries that solve Prob.~\ref{InverseProblem} was a major technical hurdle in proving Thm.~\ref{DeterministicUniquenessTheorem}. 
+This very general guarantee was sought because of the practical difficulty of ensuring that an algorithm maintain a dictionary satisfying the spark condition \eqref{SparkCondition} at each iteration, which (to my knowledge) has been an explicit or implicit assumption of all previous works except \cite{Hillar15}; indeed, even certifying a dictionary has this property is NP-hard \cite{tillmann2014computational}.
+
+Several results in the literature had to be combined to extend the guarantees derived in \cite{Hillar15} into the noisy regime.
+The main challenge was to generalize Lem.~\ref{MainLemma} to the case where the $k$-dimensional subspaces spanned by corresponding submatrices $\mathbf{A}_S$ and $\mathbf{B}_{\pi(S)}$ are assumed to be``close" but not identical.
+Unlike in \cite{Hillar15} where an inductive argument could be applied to the noiseless case, here it had to be explicitly demonstrated that this proximity relation is propagated through iterated intersections right down to the spans of the dictionary elements themselves.
+Lem.~\ref{DistanceToIntersectionLemma} was designed to encapsulate this fact, proven by appeal to a convergence guarantee for an alternating projections algorithm first proposed by von Neumann.
+This result, combined with a little known fact \eqref{eqdim} about the distance metric between subspaces, make up the more obscure components of the deduction.
+
+The proof of Lem.~\ref{MainLemma} diverges most significantly from the approach taken in \cite{Hillar15} by way of Lem.~\ref{NonEmptyLemma}, which utilizes a combinatorial design for support sets (the ``singleton intersection property") to reduce the deterministic sample complexity by an exponential factor.
+This constitutes a significant advance toward legitimizing dictionary learning in practice, since data must otherwise exhibit the exponentially many possible $k$-wise combinations of dictionary elements required by (to my knowledge) all previously published results; although an exponential number of samples per support is still required (unless $k$ is held fixed).
+The issue is that the map $\pi:\mathcal{H} \to {[m] \choose k}$ is surjective only when $\mathcal{H}$ is taken to be ${[m] \choose k}$, in which case one may proceed by induction as in \cite{Hillar15}, freely choosing supports in the codomain of $\pi$ to intersect over $(k-1)$ indices to then map back to some corresponding set of $(k-1)$ indices at the intersection of supports in the domain.
+Here, for $\mathcal{H} \subset {[m] \choose k}$, a bijection between indices had to instead be established by pigeonholing the image of $\pi$ under constraints imposed by the SIP, which was formulated specifically for this purpose.
+It just so happened that this more general argument for a non-surjective $\pi$ constrained by the SIP applied just as well to the situation where the number of dictionary elements $m$ is over-estimated (i.e.
+$\overline m > m$), in which case a one-to-one correspondence can be guaranteed between a subset of columns of $\mathbf{A}$ and $\mathbf{B}$ of a size simply expressed in terms of the width of each matrix and the regularity of $\mathcal{H}$.
+
+One of the mathematically significant achievements in \cite{Hillar15} was to break free from the constraint that the recovery matrix $\mathbf{B}$ satisfy the spark condition in addition to the generating dictionary $\mathbf{A}$.
+%, in contrast to all previously known uniqueness results which (to my knowledge) have all either explicitly or implicitly made this assumption.
+Here, it has been demonstrated that, in fact, even $\mathbf{A}$ need not satisfy the spark condition!
+Rather, $\mathbf{A}$ need only be injective on the union of subspaces with supports forming a regular $k$-uniform hypergraph satisfying the SIP (a distinguishing example is given in Sec.~\ref{Results}).
+This relaxation of constraints inspired the definition of the restricted matrix lower bound $L_{\mathcal{H}}$ in \eqref{Ldef}, which generalizes the well-known (see footnote \ref{ripfootnote}) restricted matrix lower bound $L_k$ to be in terms of a hypergraph $\mathcal{H}$, and an interesting object for further study in its own right.
+%(For instance, how hard is it to check that $L_\mathcal{H}(\mathbf{A}) > 0$?)
+%The absence of any restrictions on dictionaries solving Prob.~\ref{InverseProblem} is a major technical obstruction, but highly desirable because of the practical difficulty in ensuring that an algorithm maintain a dictionary satisfying the spark condition \eqref{SparkCondition} at each iteration; indeed, even certifying a dictionary has this property is NP-hard \cite{tillmann2014computational}.
+
+To reiterate, the methods applied here to prove Thm.~\ref{DeterministicUniquenessTheorem} yield the following results beyond a straightforward extension of those in \cite{Hillar15} to the noisy case:
+
+\begin{enumerate}
+\item A reduction in deterministic sample complexity: To identify the $n \times m$ generating dictionary $\mathbf{A}$, it is required in \cite{Hillar15} that $k{m \choose k}$ data points be sampled from each of the ${m \choose k}$ subspaces spanned by subsets of $k$ columns of $\mathbf{A}$.
+It is shown here that in fact it suffices to sample from at most $m$ such subspaces (see Cor.~\ref{DeterministicUniquenessCorollary}).
+%; thus, for fixed $k$, the deterministic sample complexity is polynomial in $m$.
+%HS15 was already poly for fixed k
+\item An extension of guarantees to the case where the number of dictionary elements is unknown: The results of \cite{Hillar15} only apply to the case where the matrix $\mathbf{B}$ has the same number of columns as $\mathbf{A}$.
+It is shown here that if $\mathbf{B}$ has at least as many columns as $\mathbf{A}$ then it contains (up to noise) a subset of the columns of $\mathbf{A}$.
+\item Relaxed requirements (no spark condition) on the generating matrix $\mathbf{A}$: Rather, $\mathbf{A}$ need only be injective on the union of subspaces with supports that form a regular uniform hypergraph satisfying the SIP.
+\end{enumerate}
+
+As it seemed to benefit a reviewer of this work, a brief discussion on how the deterministic sample complexity $N = |\mathcal{H}\left[|(k-1){m \choose k} + 1\right]$ derived here compares to those listed in the the top two rows listed in Table I of \cite{Hillar15} may be in order.
+To be clear, the theory developed here is strictly more general, since $\mathcal{H}$ can always be taken to be ${[m] \choose k}$.
+The point of difference in this comparison is the assumed set of supports for sparse codes, which is always ${[m] \choose k}$ in \cite{Hillar15}, whereas here it can be assumed to be any regular $k$-uniform hypergraph that satisfies the SIP.
+By row, %, assuming for our results that sufficient data have been sampled from all supports in a hypergraph H satisfying the SIP:
+\begin{enumerate}
+\item[I.] The result here improves upon the listed $k{m \choose k}^2$ by an exponential factor, since for every $k < m$ there exists a regular $k$-uniform hypergraph $\mathcal{H}$ with $|\mathcal{H}| = m$ satisfying the SIP.
+\item[II.] The authors in \cite{Hillar15} have applied measure-theoretic arguments to achieve $(k+1){m \choose k}$ with almost-certainty (i.e.
+with probability one), a factor of $m$ reduction over that for which certainty can alternatively be guaranteed here.
+%\item[III.] A direct comparison cannot be made because it is an open question as to the probability that a random set of supports satisfies the SIP.
+This would be an interesting problem for the community to solve; regardless, the result of \cite{Hillar15} is still implied by the more general theory given here.
+%\item[IV.] The result here is $|\mathcal{H}\left[|(k-1){m \choose k} + 1\right]$ with probability one compared to $(k+1){m \choose k}$ with probability one.
+In this case the sample complexity stated in \cite{Hillar15} is marginally better, but it relies on a noise-free technicality unique to their assumption $\mathcal{H} = {m \choose k}$.
+%differs in flavor: their $\mathbf{x_i}$ are assumed to be distributed as $(k+1)$ samples per support for every support of size $k \in [m]$, whereas here it is assumed that $(k-1){m \choose k}$ codes $\mathbf{x_i}$ are distributed over each support in some hypergraph $\mathcal{H}$ satisfying the SIP.
+%\item[V.] Again, a direct comparison cannot be made for the reason stated for row III.
+\end{enumerate}

### 2021-10-19 manuscripts/newthesis/results.tex
new stuff

@@
 
-In this chapter, we will develop some necessary language before stating the very general main result of this work: that uniqueness and stability is a typical property of learned dictionaries for sparse coding of noisy signals.
+This chapter presents the main results of this work: that uniqueness and stability is a typical property of learned dictionaries for sparse coding of noisy signals.
+
 More specifically, it is stated that matrices injective on a sparse domain are identifiable from \mbox{$N = m(k-1){m \choose k} + m$} noisy linear combinations of $k$ of their $m$ columns up to an error that is linear in the noise (Thm.~\ref{DeterministicUniquenessTheorem}).
@@
 
-\section{Definitions and Problem Statements}
-
-More precisely, let $\mathbf{A} \in \mathbb R^{n \times m}$ be a matrix with columns $\mathbf{A}_j$ ($j = 1,\ldots,m$) and let dataset $Z$ consist of measurements:
+Let $\mathbf{A} \in \mathbb R^{n \times m}$ be a matrix with columns $\mathbf{A}_j$ ($j = 1,\ldots,m$) and let dataset $Z$ consist of measurements:
 \begin{align}\label{LinearModel}
@@
 %A set of $k$-sparse vectors is said to be in \emph{general linear position} when any $k$ of them are linearly independent.
+
+\section{Combinatorial Designs}
 
@@
 
+\section{Discussion}
+
 We close this section with some comments on the optimality of our results.
@@
 Even so, in the next section we discuss how probabilistic guarantees can in fact be made for any number of available samples.
-
-\section{Discussion}
-
-TODO

### 2021-10-19 manuscripts/thesis/thesis.tex
new stuff

@@
 \usepackage{url}
+\usepackage{indentfirst}
 
@@
 \othermembers{Professor Bruno Olshausen \\
-  Associate Professor Mike Deweese \\
+  Associate Professor Michael DeWeese \\
   Chancellor's Professor Bin Yu}
@@
 
-\include{abstract}
+%\include{abstract}
+\begin{abstract}
+Learning optimal dictionaries for sparse representation modeling has led to the discovery of characteristic sparse features in several classes of natural signals.
+However, universal guarantees of the uniqueness and stability of such features in the presence of noise are lacking.
+This work presents very general conditions guaranteeing when dictionaries yielding the sparsest encodings of a dataset are unique and stable with respect to noise.
+The stability constants are explicit and computable; as such, there is an effective procedure sufficient to affirm if a proposed solution to the dictionary learning problem is unique within bounds commensurate with the noise.
+\\
+Two formulations of the dictionary learning problem are considered.
+The first seeks a dictionary for which each signal in a dataset is approximated up to some bounded error by a linear superposition of only a limited number of dictionary elements.
+In this case, existing guarantees are extended to the noisy regime to show that such dictionaries and the sparse representations they induce are almost always identifiable up to an error commensurate with the approximation error.
+Moreover, a theory of combinatorial designs is introduced to demonstrate that this is so even if the dictionary fails to satisfy the spark condition, the data are distributed over only a polynomial set of subspaces spanned by the dictionary, or (to some extent) even if the dictionary is overestimated in size.
+\\
+The second formulation of the problem seeks a dictionary which minimizes the average number of dictionary elements required to approximate each signal in the dataset up to some bounded error.
+The guarantees in this case, the first of their kind in both in the noiseless and noisy regimes, are derived by demonstrating that this second problem actually reduces to an instance of the first.
+Importantly, in both cases, no constraints whatsoever are imposed on learned dictionaries beyond a natural upper bound on their size.
+\\
+This work serves to justify, in principle, dictionary learning in general as a means of discovering latent sparse structure in real data.
+Though much work remains to be done deriving criteria for use in practice, the theoretical tools developed here should be of use to this end.
+\end{abstract}
 
@@
 I want to dedicate this work to my dad.
-Yet it feels as though that would in some sense be measuring his life up against these results, which can't possibly match the time with him I traded to produce them.
-The fact is that whatever may be the eventual effect of this work on the scientific ecosystem, these mathematical truths could have waited.
+Yet it feels as though doing so would in some sense measure his life up against these results, which can't possibly be matched to the time with him I traded to produce them.
+Whatever the eventual effect of this work on the scientific ecosystem may be, these mathematical truths could have waited.
 They could have arrived at their own pace, via myself or another, and I could have been more present with my dad as he waited patiently to die of cancer.
 
-I suppose that I couldn't really fathom what it actually meant for this to happen -- to never see or talk to or hug him again -- while the idea of putting original work out there, of crafting my own theorems to lay down as pieces of the overwhelming puzzle that is neuroscience, was tantalizing.
-Yet I feel it was very much a sense of desperation, of having to accomplish something and prove myself worthy of the position I had come to find myself in after 25+ years of schooling and a first failed project, that largely drove these efforts.
+I suppose that I couldn't really fathom what it actually meant for this to happen -- to never see or talk to or hug him again -- while the idea of putting original work out there, of crafting my own piece of the overwhelming puzzle that is neuroscience, was tantalizing.
+Yet I feel that it was very much a sense of desperation, of having to accomplish something and prove myself worthy of the position I had come to find myself in after 25+ years of schooling and a first failed project, that largely drove these efforts.
 Truth be told, I initially had no particular interest in dictionary learning other than as a means to passing my qualifying exam; and by that time, I worried the brain was so dauntingly complex that I should feel lucky to have at least been offered a well-defined problem of arguable relevance to neuroscience to work on, particularly one I felt even remotely equipped to solve myself.
